### 2018-05-09 draft/accordionComplexSurfaces.tex
first draft

\documentclass{amsart}

\usepackage[T1]{fontenc}
\usepackage{enumerate, amsmath, amsfonts, amssymb, amsthm, mathrsfs, wasysym, graphics, graphicx, xcolor, url, hyperref, hypcap,  shuffle, xargs, multicol, overpic, pdflscape, multirow, hvfloat, minibox, accents, array, xifthen, ae, aecompl, blkarray, pifont, mathtools, a4wide}
\usepackage{marginnote}
\hypersetup{colorlinks=true, citecolor=darkblue, linkcolor=darkblue}
\usepackage[all]{xy}
\usepackage[bottom]{footmisc}
\usepackage{tikz}
\usepackage{tkz-graph}
\usetikzlibrary{trees, decorations, decorations.markings, shapes, arrows, matrix, calc, fit, intersections, patterns, angles}
\graphicspath{{figures/}}
\makeatletter\def\input@path{{figures/}}\makeatother
\usepackage{caption}
\captionsetup{width=\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% theorems
\newtheorem{theorem}{Theorem}[]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem*{theorem*}{Theorem}%[section]

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{question}[theorem]{Question}
\newtheorem{notation}[theorem]{Notation}
\newtheorem{assumption}[theorem]{Assumption}

% math special letters
\newcommand{\R}{\mathbb{R}} % reals
\newcommand{\N}{\mathbb{N}} % naturals
\newcommand{\Z}{\mathbb{Z}} % integers
\newcommand{\C}{\mathbb{C}} % complex
\newcommand{\I}{\mathbb{I}} % set of integers
\newcommand{\HH}{\mathbb{H}} % hyperplane
\newcommand{\K}{k} % field
\newcommand{\fA}{\mathfrak{A}} % alternating group
\newcommand{\fS}{\mathfrak{S}} % symmetric group
\newcommand{\cA}{\mathcal{A}} % algebra
\newcommand{\cC}{\mathcal{C}} % collection
\newcommand{\cS}{\mathcal{S}} % ground set
\newcommand{\uR}{\underline{R}} % underline set
\newcommand{\uS}{\underline{S}} % underline set
\newcommand{\uT}{\underline{T}} % underline set
\newcommand{\oS}{\overline{S}} % overline set
\newcommand{\ucS}{\underline{\cS}} % underline ground set
\renewcommand{\b}[1]{\mathbf{#1}} % bold letters
\newcommand{\h}{\widehat} % hat letters

% math commands
\newcommand{\set}[2]{\left\{ #1 \;\middle|\; #2 \right\}} % set notation
\newcommand{\bigset}[2]{\big\{ #1 \;\big|\; #2 \big\}} % big set notation
\newcommand{\Bigset}[2]{\Big\{ #1 \;\Big|\; #2 \Big\}} % Big set notation
\newcommand{\setangle}[2]{\left\langle #1 \;\middle|\; #2 \right\rangle} % set notation
\newcommand{\ssm}{\smallsetminus} % small set minus
\newcommand{\dotprod}[2]{\left\langle \, #1 \; \middle| \; #2 \, \right\rangle} % dot product
\newcommand{\symdif}{\,\triangle\,} % symmetric difference
\newcommand{\one}{{1\!\!1}} % the all one vector
\newcommand{\eqdef}{\mbox{\,\raisebox{0.2ex}{\scriptsize\ensuremath{\mathrm:}}\ensuremath{=}\,}} % :=
\newcommand{\defeq}{\mbox{~\ensuremath{=}\raisebox{0.2ex}{\scriptsize\ensuremath{\mathrm:}} }} % =:
\newcommand{\simplex}{\triangle} % simplex
\renewcommand{\implies}{\Rightarrow} % imply sign
\newcommand{\transpose}[1]{{#1}^t} % transpose matrix

% operators
\DeclareMathOperator{\conv}{conv} % convex hull
\DeclareMathOperator{\vect}{vect} % linear span
\DeclareMathOperator{\cone}{cone} % cone hull
\DeclareMathOperator{\inv}{inv} % inversions
\DeclareMathOperator{\ascents}{asc} % ascents
\DeclareMathOperator{\descents}{des} % descents

% others
\newcommand{\fref}[1]{Figure~\ref{#1}} % reference figures
\newcommand{\ie}{\textit{i.e.}~} % id est
\newcommand{\eg}{\textit{e.g.}~} % exempli gratia
\newcommand{\Eg}{\textit{E.g.}~} % exempli gratia
\newcommand{\apriori}{\textit{a priori}} % a priori
\newcommand{\viceversa}{\textit{vice versa}} % vice versa
\newcommand{\versus}{\textit{vs.}~} % versus
\newcommand{\aka}{\textit{a.k.a.}~} % also known as
\newcommand{\perse}{\textit{per se}} % per se
\newcommand{\ordinal}{\textsuperscript{th}} % th for ordinals
\newcommand{\ordinalst}{\textsuperscript{st}} % st for ordinals
\definecolor{darkblue}{rgb}{0,0,0.7} % darkblue color
\definecolor{green}{RGB}{57,181,74} % green color
\definecolor{violet}{RGB}{147,39,143} % violet color
\newcommand{\darkblue}{\color{darkblue}} % darkblue command
\newcommand{\defn}[1]{\textsl{\darkblue #1}} % emphasis of a definition
\newcommand{\para}[1]{\medskip\noindent\textbf{#1.}} % paragraph
\renewcommand{\topfraction}{1} % possibility to have one page of pictures
\renewcommand{\bottomfraction}{1} % possibility to have one page of pictures
%\renewcommand\labelitemi{$\diamond$} % redefine itemize default symbol
\newcommand{\ex}{_{\textrm{exm}}} % examples
\newcommand{\pa}{_{\textrm{pa}}} % path

% marginal comments
\usepackage{todonotes}
\newcommand{\yann}[1]{\textbf{#1 --- Y.}} % {\todo[color=red!30]{#1 \\ \hfill --- Y.}}
\newcommand{\vincent}[1]{\todo[color=blue!30]{#1 \\ \hfill --- V.}}
\newcommand{\pierreguy}[1]{\todo[color=green!30]{#1 \\ \hfill --- PG.}}

% SPECIFIC NON-KISSING COMPLEX

% COMBINATORICS
% quiver
\newcommand{\blossom}{^\text{\ding{96}}} % blossom
\newcommand{\blinkers}[1]{_{\LEFTCIRCLE \!\! #1 \!\! \RIGHTCIRCLE}} % blossom
\newcommand{\indeg}{\mathrm{indeg}} % in-degree
\newcommand{\outdeg}{\mathrm{outdeg}} % out-degree
%\newcommand{\tai}{\mathsf{tai}} % target incompatible
%\newcommand{\tac}{\mathsf{tac}} % target compatible
%\newcommand{\soi}{\mathsf{soi}} % source incompatible
%\newcommand{\soc}{\mathsf{soc}} % source compatible
%\newcommand{\cso}{\mathsf{cso}} % cosource
%\newcommand{\cta}{\mathsf{cta}} % cotarget

% walks
\newcommand{\strings}{\mathcal{S}} % strings
\newcommand{\distinguishableStrings}{\mathcal{S}_\mathrm{dist}} % distinguishable strings
\newcommand{\lfStrings}{\underline{\mathcal{S}}} % loop-free strings
\newcommand{\walks}{\mathcal{W}} % walks
\newcommand{\straightWalks}{\mathcal{W}_\mathrm{str}} % straight walks
\newcommand{\bendingWalks}{\mathcal{W}_\mathrm{bend}} % bending walks
\newcommand{\NKWalks}{\mathcal{W}_\mathrm{nk}} % non-kissing walks
\newcommand{\peaks}[1]{\mathsf{peaks}(#1)} % peaks
\newcommand{\deeps}[1]{\mathsf{deeps}(#1)} % deeps
\newcommand{\distinguishedWalk}[2]{\mathsf{dw}(#1,#2)} % distinguished walk
\newcommand{\distinguishedArrows}[2]{\mathsf{da}(#1,#2)} % distinguished arrows
\newcommand{\distinguishedString}[2]{\mathsf{ds}(#1,#2)} % distinguished string
\newcommand{\distinguishedSign}[2]{\varepsilon(#1,#2)} % distinguished sign

% non-kissing complex, lattice, flip graph
\newcommand{\kn}{\kappa} % kissing number
\newcommand{\KN}{\textsc{kn}} % Kissing Number
\newcommandx{\NKC}[1][1=\bar Q]{\mathcal{K}_{\mathrm{nk}}(#1)} % non-kissing complex
\newcommandx{\RNKC}[1][1=\bar Q]{\mathcal{C}_{\mathrm{nk}}(#1)} % non-kissing complex
\newcommandx{\NKL}[1][1=\bar Q]{\mathcal{L}_{\mathrm{nk}}(#1)} % non-kissing lattice
\newcommandx{\NKG}[1][1=\bar Q]{\mathcal{G}_{\mathrm{nk}}(#1)} % non-kissing flip graph
\newcommandx{\NFC}[1][1=\bar Q]{\mathcal{C}_{\mathrm{nf}}(#1)} % non-friendly complex
\newcommand{\peak}{\mathrm{peak}} % bottom dissection
\newcommand{\deep}{\mathrm{deep}} % top dissection
\newcommand{\reversed}[1]{#1^{\mathrm{rev}}} % reverse all arrows
\renewcommand{\top}{\mathrm{top}} % top
\newcommand{\bottom}{\mathrm{bot}} % bottom

% accordion and zigzag complexes
\newcommand{\surface}{\mathcal{S}} % an orientable surface
\newcommand{\dual}{^*} % duality
\newcommand{\dissection}{\mathrm{D}} % dissection of a marked surface
\newcommand{\faces}{\mathcal{F}} % faces of a dissection

% lattices
\newcommand{\meet}{\wedge} % meet
\newcommand{\join}{\vee} % join
\newcommand{\bigMeet}{\bigwedge} % meet
\newcommand{\bigJoin}{\bigvee} % join
\newcommand{\closure}[1]{#1^{\mathrm{cl}}} % closure operator
\newcommand{\coclosure}[1]{#1^{\mathrm{cocl}}} % coclosure operator
\newcommand{\uclosure}[1]{#1^{\underline{\mathrm{cl}}}} % loop free closure operator
\newcommand{\Bicl}[1]{\mathsf{Bic}(#1)} % biclosed sets
\newcommand{\projDown}{\pi_\downarrow} % down projection map
\newcommand{\projUp}{\pi^\uparrow} % up projection map
\newcommand{\JI}{\mathsf{JI}} % join-irreducible
\newcommand{\MI}{\mathsf{MI}} % meet-irreducible
\newcommand{\Cong}{\mathsf{Cong}} % congruence lattice
\newcommand{\con}{\mathrm{con}} % congruence contracting a cover relation
\newcommand{\ji}{\mathsf{ji}} % join irreducible
\newcommand{\mi}{\mathsf{mi}} % meet irreducible

% GEOMETRY
% g-vectors
\newcommand{\gvector}[1]{\mathbf{g}(#1)} % g-vector of the path #1
\newcommand{\gvectors}[1]{\mathbf{g}(#1)} % g-vectors of the paths #1
\newcommandx{\gvectorFan}[1][1=\bar Q]{\mathcal{F}^\mathbf{g}(#1)} % g-vector fan
% c-vectors
\newcommand{\cvector}[2]{\mathbf{c}(#1 \in #2)} % c-vector of the path #1 in the facet #2
\newcommand{\cvectors}[1]{\mathbf{c}(#1)} % c-vectors of the paths #1
\newcommandx{\allcvectors}[1][1=\bar Q]{\mathbf{C}(#1)} % all c-vectors with respect to the initial cluster #1
\newcommandx{\cvectorFan}[1][1=\bar Q]{\mathcal{F}^\mathbf{c}(#1)} % fan of hyperplanes orthogonal to all c-vectors
% points, hyperplanes, half-spaces
\newcommand{\point}[1]{\mathbf{p}(#1)} % vertex of the grid associahedron corresponding to the cluster #1
\newcommand{\ray}{\mathbf{r}} % ray
\newcommand{\rays}{\mathbf{R}} % rays
\newcommand{\hs}{\mathbf{H}^{\le}} % half space
\newcommand{\HS}[1]{\mathbf{H}^{\le}(#1)} % half space
\newcommand{\hyp}{\mathbf{H}^{=}} % hyperplane
\newcommand{\Hyp}[1]{\mathbf{H}^{=}(#1)} % hyperplane
\newcommand{\fix}[1]{\mathrm{Fix}(#1)} % fix space
% polytopes
\newcommandx{\Asso}[2][1=\bar Q,2={}]{\mathsf{Asso}^{#2}(#1)} % associahedron
\newcommandx{\Zono}[2][1=\bar Q,2={}]{\mathsf{Zono}^{#2}(#1)} % zonotope
\newcommand{\Fan}{\mathcal{F}} % fan
\newcommand{\multiplicityVector}{\b{m}} % multiplicity vector

% ALGEBRA
\newcommand{\Hom}[1]{\operatorname{{\rm Hom}}_{#1}}
\newcommand{\Ext}[1]{\operatorname{{\rm Ext}}_{#1}}
\newcommandx{\AR}[1][1=\bar Q]{\mathrm{AR}(#1)} % Auslander-Reiten quiver
\newcommandx{\tTC}[1][1=\bar Q]{\mathcal{K}^{\textrm{s$\tau$-tilt}}(#1)} % tau-tilting complex
\newcommand{\rep}{\operatorname{{\rm rep}}}
\newcommand{\proj}{\operatorname{{\rm proj}}}

%% formating the part command
%\makeatletter
%\def\part{\@startsection{part}{1}%
%\z@{.7\linespacing\@plus\linespacing}{.8\linespacing}%
%{\LARGE\sffamily\centering}}
%\@addtoreset{section}{part}
%\makeatother
%\renewcommand{\thesection}{\arabic{part}.\arabic{section}}

% formating the table of contents
\makeatletter
\def\l@section{\@tocline{1}{2pt}{0pc}{}{}}
\makeatother
\let\oldtocpart=\tocpart
\renewcommand{\tocpart}[2]{\bf\large\oldtocpart{#1}{#2}}
\let\oldtocsection=\tocsection
\renewcommand{\tocsection}[2]{\bf\oldtocsection{#1}{#2}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Accordion complexes versus non-kissing complexes}

\thanks{YP, VP and PGP were partially supported by the French ANR grant SC3A~(15\,CE40\,0004\,01).}

\author{Yann Palu}
\address[Yann Palu]{LAMFA, Universit\'e Picardie Jules Verne, Amiens}
\email{yann.palu@u-picardie.fr}
\urladdr{\url{http://www.lamfa.u-picardie.fr/palu/}}

\author{Vincent Pilaud}
\address[Vincent Pilaud]{CNRS \& LIX, \'Ecole Polytechnique, Palaiseau}
\email{vincent.pilaud@lix.polytechnique.fr}
\urladdr{\url{http://www.lix.polytechnique.fr/~pilaud/}}

\author{Pierre-Guy Plamondon}
\address[Pierre-Guy Plamondon]{Laboratoire de Math\'ematiques d'Orsay, Universit\'e Paris-Sud, CNRS, Universit\'e Paris-Saclay}
\email{pierre-guy.plamondon@math.u-psud.fr}
\urladdr{\url{https://www.math.u-psud.fr/~plamondon/}}

\author{Sibylle Schroll}
\address[Sibylle Schroll]{}
\email{}
\urladdr{\url{}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{abstract}
\end{abstract}

%\vspace*{.3cm}

\maketitle

\section{Non-kissing complex}

\subsection{Gentle bound quivers and their blossoming quivers}

We consider a \defn{bound quiver}~$\bar Q = (Q,I)$, formed by a quiver~$Q$ and an admissible ideal~$I$ of the path algebra~$kQ$, so that the quotient algebra~$kQ/I$ is finite dimensional.

\begin{definition}[\cite{ButlerRingel}]
\label{def:gentleQuiver}
A \defn{gentle bound quiver}~$\bar Q \eqdef (Q,I)$ is a bound quiver such that
\begin{itemize}
\item each vertex~$v \in Q_0$ has at most two incoming and two outgoing arrows,
\item the ideal~$I$ is generated by paths of length exactly two,
\item for any arrow~$\beta \in Q_1$, there is at most one arrow~$\alpha \in Q_1$ such that~$t(\alpha) = s(\beta)$ and~${\alpha\beta\notin I}$ (resp.~$\alpha\beta \in I$) and at most one arrow~$\gamma \in Q_1$ such that~$t(\beta) = s(\gamma)$~and~${\beta\gamma\notin I}$~(resp.~${\beta\gamma \in I}$).
\end{itemize}
The algebra~$kQ/I$ is called a \defn{gentle algebra}.
\end{definition}

\begin{definition}[\cite{PaluPilaudPlamondon}]
\label{def:blossomingQuiver}
A gentle bound quiver~$\bar Q$ is \defn{complete} if any vertex~$v \in Q_0$ is incident to either one ($v$ is a leaf) or four arrows ($v$ is an internal vertex).
The \defn{pruned subquiver} of a quiver $\bar Q$ is the gentle quiver obtained by deleting all leaves of~$\bar Q$ (degree one vertices) and their incident arrows.
The \defn{blossoming quiver} of a gentle bound quiver~$\bar Q$ is the complete gentle bound quiver~$\bar Q\blossom$ whose pruned subquiver is~$\bar Q$.
The vertices of~$Q\blossom_0 \ssm Q_0$ are called \defn{blossom vertices}, and the arrows~$Q\blossom_1 \ssm Q_1$ are called \defn{blossom arrows}.
\end{definition}

\vincent{Examples}

\subsection{Strings and walks}

\begin{definition}
\label{def:string}
Let~$\bar Q = (Q,I)$ be a gentle bound quiver.
A \defn{string} for~$\bar Q$ is a word of the form
\(
\rho = \alpha_1^{\varepsilon_1}\alpha_2^{\varepsilon_2}\cdots \alpha_\ell^{\varepsilon_\ell},
\)
where
	\begin{itemize}
	\item $\alpha_i \in Q_1$ and~$\varepsilon_i \in \{-1,1\}$ for all~$i \in [\ell]$,
	\item $t(\alpha_i^{\varepsilon_i}) = s(\alpha_{i+1}^{\varepsilon_{i+1}})$ for all~$i \in [\ell-1]$,
	\item there is no path~$\pi \in I$ such that~$\pi$ or~$\pi^{-1}$ appears as a factor of~$\rho$, and
	\item $\rho$ is reduced, in the sense that no factor~$\alpha\alpha^{-1}$ or~$\alpha^{-1}\alpha$ appears in~$\rho$, for~$\alpha \in Q_1$.
	\end{itemize}
The integer~$\ell$ is called the \defn{length} of the string~$\rho$.
We let~$s(\rho) \eqdef s(\alpha_1^{\varepsilon_1})$ and~$t(\rho) \eqdef t(\alpha_\ell^{\varepsilon_\ell})$ denote the source and target of~$\rho$.
For each vertex~$v \in Q_0$, there is also a \defn{string of length zero}, denoted by~$\varepsilon_v$, that starts and ends at~$v$.
%We denote by~$\strings(\bar Q)$ the set of strings on~$\bar Q$.
%We usually denote strings by~$\rho, \sigma, \tau$.
We often implicitly identify the two inverse strings~$\rho$ and~$\rho^{-1}$, and we let~$\strings^\pm(\bar Q) \eqdef \set{\{\rho, \rho^{-1}\}}{\rho \in \strings(\bar Q)}$ denote the collection of all \defn{undirected strings} of~$\bar Q$.

%We call \defn{negative simple string} a formal word of length zero of the form $-v$, where $v$ is any vertex of $Q_0$. We denote by
%\(
%\strings^\pm_{\ge -1}(\bar Q) \eqdef \strings^\pm(\bar Q) \sqcup \set{-v}{v \in Q_0}
%\)
%the set of \defn{almost positive unoriented strings}.
%Note that~$\varepsilon_v$ and~$-v$ are different almost positive strings.
%\end{enumerate}
\end{definition}

\begin{definition}
\label{def:walk}
A \defn{walk} of a gentle quiver~$\bar Q$ is a maximal string of its blossoming quiver~$\bar Q \blossom$ (thus joining two blossom vertices of~$\bar Q \blossom$).
We denote by~$\walks(\bar Q)$ the set of all walks on~$\bar Q$.
As for strings, we implicitly identify the two inverse walks~$\omega$ and~$\omega^{-1}$, and we let~$\walks^\pm(\bar Q) \eqdef \set{\{\omega, \omega^{-1}\}}{\omega \in \walks(\bar Q)}$ denote the set of \defn{undirected walks} of~$\bar Q$.
\end{definition}

\begin{definition}
\label{def:substrings}
A \defn{substring} of a walk~$\omega = \alpha_1^{\varepsilon_1} \dots \alpha_\ell^{\varepsilon_\ell} \in \walks(\bar Q)$ is a string~$\sigma = \alpha_i^{\varepsilon_i} \dots \alpha_j^{\varepsilon_j}$ of~$\strings(\bar Q)$ for some~$1 < i \le j < \ell$.
Note that 
\begin{itemize}
\item the endpoints of~$\sigma$ are not allowed to be the blossom endpoints of~$\omega$,
\item the position of~$\sigma$ as a factor of~$\omega$ matters (the same string at a different position is considered a different substring),
\item the string~$\varepsilon_v$ is a substring of~$\omega$ for each occurence of~$v$ as a vertex of~$\omega$.
\end{itemize}
The substring~$\sigma = \alpha_i^{\varepsilon_i} \dots \alpha_j^{\varepsilon_j}$ is \defn{at the bottom} (resp.~\defn{on top}) of the walk~$\omega = \alpha_1^{\varepsilon_1} \dots \alpha_\ell^{\varepsilon_\ell}$ if~$\varepsilon_{i-1} = 1$ and~$\varepsilon_{j+1} = -1$ (resp.~if~$\varepsilon_{i-1} = -1$ and~$\varepsilon_{j+1} = 1$), that is, the two arrows of~$\omega$ incident to the endpoints of~$\sigma$ point towards~$\sigma$ (resp.~outwards from~$\sigma$).
We let~$\Sigma(\omega)$ be the set of substrings of~$\omega$ and~$\Sigma_\bottom(\omega)$ and~$\Sigma_\top(\omega)$ be the sets of bottom and top substrings of~$\omega$ respectively.
We use the same notations for undirected walks (of course, substrings of an undirected walk are undirected).
\end{definition}

\begin{definition}
\label{def:straightBended}
A \defn{peak} (resp.~\defn{deep}) of a walk~$\omega$ is a substring of~$\omega$ of length zero which is on top (resp.~at the bottom of~$\omega$).
A \defn{corner} is either a peak or a deep (in other words, it is a vertex of~$\omega$ where the arrows change direction).
A walk~$\omega$ is \defn{straight} if it has no corner (\ie if~$\omega$ or~$\omega^{-1}$ is a path in~$\bar Q\blossom$), and \defn{bending} otherwise. Let $\straightWalks(\bar Q)$ and~$\bendingWalks(\bar Q)$ denote the sets of straight and bending walks of~$\bar Q$ and let~$\straightWalks^\pm(\bar Q) \eqdef \set{\{\omega, \omega^{-1}\}}{\omega \in \straightWalks(\bar Q)}$ and~$\bendingWalks^\pm(\bar Q) \eqdef \set{\{\omega, \omega^{-1}\}}{\omega \in \bendingWalks(\bar Q)}$.
A \defn{peak walk} (resp.~\defn{deep walk}) is a walk with a unique corner (in other words, it switches orientation only once), which is a peak (resp.~deep). For~$v \in Q_0$, we denote by~$v_\peak$ the peak walk with peak at~$v$ and by~$v_\deep$ the deep walk with deep~at~$v$.
\end{definition}

\subsection{Non-kissing complex}

\begin{definition}
\label{def:kiss}
Let~$\omega,\omega' \in \walks^\pm(\bar Q)$ be two undirected walks on~$\bar Q$.
We say that~$\omega$ \defn{kisses}~$\omega'$ if~$\Sigma_\top(\omega) \cap \Sigma_\bottom(\omega') \ne \varnothing$.
See \fref{fig:kissingCrossing}.
% \ie if there exist a common substring~$\sigma \in \strings^\pm(\bar Q)$ of~$\omega$ and~$\omega'$ such that the arrows of~$\omega$ incident to~$\sigma$ are both outgoing while the arrows of~$\omega'$ incident to~$\sigma$ are both incoming.
We say that~$\omega$ and~$\omega'$ are \defn{kissing} if~$\omega$ kisses~$\omega'$ or~$\omega'$ kisses~$\omega$ (or both).
Note that we authorize the situation where~$\sigma$ is reduced to a vertex~$v$, meaning that~$v$ is a peak of~$\omega$ and a deep of~$\omega'$.
Observe also that~$\omega$ can kiss~$\omega'$ several times, that~$\omega$ and~$\omega'$ can mutually kiss, and that~$\omega$ can kiss itself.
We denote by~$\NKWalks(\bar Q)$ the walks on~$\bar Q$ which are not self-kissing and by~$\NKWalks^\pm(\bar Q) \eqdef \set{\{\omega, \omega^{-1}\}}{\omega \in \NKWalks(\bar Q)}$ their undirected version.
\end{definition}

\begin{figure}
	\capstart
	\centerline{\includegraphics[scale=1]{kissingCrossing}}
	\caption{A schematic representation of two kissing walks (left) and two crossing walks~(right): $\omega$~kisses~$\omega'$ (left) while~$\mu$~crosses~$\nu$ (right). For the crossing walks, we have~$\mu \prec_\gamma \nu$ while~$\nu \prec_\delta \mu$.}
	\label{fig:kissingCrossing}
\end{figure}

\begin{definition}
\label{def:nKc}
The \defn{non-kissing complex} of~$\bar Q$ is the simplicial complex~$\NKC$ whose faces are the collections of pairwise non-kissing walks of~$\NKWalks^\pm(\bar Q)$.
Note that self-kissing walks never appear in~$\NKC$ by definition.
In contrast, no straight walk can kiss another walk by definition, so that they appear in all facets of~$\NKC$.
We thus consider the \defn{reduced non-kissing complex}~$\RNKC$ to be the deletion of all straight walks from~$\NKC$.
\end{definition}

\begin{theorem}[{\cite[Cor.~2.27 \& Cor.~2.33]{PaluPilaudPlamondon}}]
The reduced non-kissing complex~$\RNKC$ is pure of dimension~$|Q_0|$ (\ie all maximal faces have dimension~$|Q_0|$) and thin (\ie all codimension~$1$ faces are contained in exactly two facets).
\end{theorem}

This result follows from the existence of flips in non-kissing facets.
This operation is illustrated in \fref{fig:flip}.

\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=1]{flip}}
	\caption{A schematic representation of flips in the non-kissing complex. The flip exchanges the walk~$\omega = \rho \sigma \tau$ in the facet~$F$ (left) with the walk~$\omega' = \rho' \sigma \tau'$ in the facet~$F'$ (middle), using the walks~$\mu = \rho' \sigma \tau$ and~$\nu = \rho \sigma \tau'$. The walk~$\omega'$ kisses~$\omega$ but no other walk of~$F$ (right).}
	\label{fig:flip}
\end{figure}

\section{Accordion complex and zigzag complex}

\subsection{Dual dissections of a surface}

\begin{definition}
A \defn{marked surface}~$\bar\surface \eqdef (\surface,M)$ is an orientable surface~$\surface$ with boundaries, together with a set~$M$ of marked points which can be on the boundary of~$\surface$ or not.
An \defn{arc} on~$\bar\surface$ is a curve on~$\surface$ connecting two marked points of~$M$ and whose interior is disjoint from~$M$ and the boundary of~$\surface$ (note that arcs homotopic to boundary arcs are allowed here).
As usual, arcs are considered up to homotopy relative to their endpoints in~$\surface \ssm M$.
Two arcs \defn{cross} when they intersect in their interior.
\end{definition}

\begin{definition}
A \defn{dissection} of~$\bar\surface$ is a collection~$\dissection$ of pairwise non-crossing arcs on~$\bar\surface$.
The \defn{faces} of a dissection~$\dissection$ are the connected components of the complement of the union of the arcs of~$\dissection$ in the surface~$\surface$.
We denote by~$\faces(\dissection)$ the set of faces of~$\dissection$.
The dissection~$\dissection$ is \defn{cellular} if all its faces are disks.
\end{definition}

\begin{definition}
Let~$\surface$ be a surface with two sets~$M$ and~$M\dual$ of marked points so that~$M$ and~$M\dual$ alternate along the boundary of~$\surface$.
A dissection~$\dissection$ of~$(\surface, M)$ and a dissection~$\dissection\dual$ of~$(\surface, M\dual)$ are \defn{dual dissections} if there are pairs of mutually inverse bijections~$M\dual \leftrightarrow \faces(\dissection)$ and~$M \leftrightarrow \faces(\dissection\dual)$, denoted~$\dual$ in both directions, such that the dissection~$\dissection$ has an edge joining its vertices~$u,v \in M$ and separating its faces~$f,g \in  \faces(\dissection)$ if and only if~$\dissection\dual$ has an edge joining its vertices~$f\dual, g\dual \in M\dual$ and separating its faces~$u\dual, v\dual \in \faces(\dissection\dual)$.
\end{definition}

Note that contrarily to the usual conventions, the dual vertex of a face~$f$ is not always in the interior of the face.
More precisely, there are two situations:
\begin{itemize}
\item if a face~$f$ has no edge on the boundary of~$\surface$, its dual vertex~$f\dual$ lies in the interior~of~$f$,
\item if a face~$f$ has an edge on the boundary of~$\surface$, then it has exactly one such edge and its dual vertex~$f\dual$ lies on this edge.
\end{itemize}
In fact, the second point forces the following characterization of the dissections that admit a dual dissection.

\begin{proposition}
\label{prop:conditionsDualDissections}
For a dissection~$\dissection$ of a marked surface~$(\surface, M)$, there exists a set~$M\dual$ of points of~$\surface$ and a dissection~$\dissection\dual$ of~$(\surface, M\dual)$ such that~$\dissection$ and~$\dissection\dual$ are dual dissections if and only if each face of~$\dissection$ has at most one boundary edge.
Moreover, the set~$M\dual$ is unique.
\end{proposition}

\begin{proof}
\vincent{Todo}
\end{proof}

\begin{remark}
In Proposition~\ref{prop:conditionsDualDissections}, note that although the set~$M\dual$ of dual marked points is unique, the dual dissection~$\dissection\dual$ is not when~$\dissection$ is not cellular.
\end{remark}

\begin{example}
Two examples of dual dissections on a surface are represented in \fref{fig:dissections}.
\end{example}

\subsection{Accordions and zigzags}

Let~$\surface$ be a surface with two sets~$M$ and~$M\dual$ of marked points and two dual dissections~$\dissection$ and~$\dissection\dual$.
We consider a set~$B$ of points on the boundary of the surface~$\surface$ such that~$B$ and~$M \cup M\dual$ alternate along the boundary of~$\surface$.
The points of~$B$ are called the \defn{blossom points}.

\begin{definition}
\label{def:accordion}
A \defn{$\dissection$-accordion} is ...
\end{definition}

\begin{definition}
\label{def:zigzag}
A \defn{$\dissection\dual$-zigzag} is ...
\end{definition}

\begin{remark}
Note that the $\dissection$-accordions do not depend on~$\dissection\dual$, only on~$\dissection$ (and~$M\dual$ which is determined by~$\dissection$ by Proposition~\ref{prop:conditionsDualDissections}).
Similarly, the $\dissection\dual$-zigzags do not depend on~$\dissection$.
\end{remark}

\begin{remark}
The $\dissection$-zigzags and the $\dissection\dual$-accordions are defined dually.
\end{remark}

\subsection{Accordion complex and zigzag complex}

\newpage

\end{document}

### 2018-05-09 draft/accordionComplexSurfaces.tex
essai
adresse Sibylle
sketch of the content

@@
 \newcommand{\faces}{\mathcal{F}} % faces of a dissection
+\renewcommandx{\AC}[1][1=\dissection]{\mathcal{K}_{\mathrm{acc}}(#1)} % accordion complex
+\newcommandx{\ZC}[1][1=\dissection\dual]{\mathcal{K}_{\mathrm{zz}}(#1)} % zigzag complex
 
@@
 
-\title{Accordion complexes versus non-kissing complexes}
+\title{Accordion / zigzag / non-kissing / support $\tau$-tilting complexes all coincide}
 
@@
 \address[Sibylle Schroll]{}
-\email{}
+\email{schroll@leicester.ac.uk}
 \urladdr{\url{}}
@@
 
-\subsection{Accordions and zigzags}
+\begin{definition}
+Interior points, blossom points.
+Half-edges.
+
+We consider a set~$B$ of points on the boundary of the surface~$\surface$ such that~$B$ and~$M \cup M\dual$ alternate along the boundary of~$\surface$.
+The points of~$B$ are called the \defn{blossom points}.
+\vincent{I am tempted to define here the interior points and blossom points and to only consider arcs passing though these points. Still need to think about it.}
+\end{definition}
+
+\subsection{Accordion complex and zigzag complex}
 
 Let~$\surface$ be a surface with two sets~$M$ and~$M\dual$ of marked points and two dual dissections~$\dissection$ and~$\dissection\dual$.
-We consider a set~$B$ of points on the boundary of the surface~$\surface$ such that~$B$ and~$M \cup M\dual$ alternate along the boundary of~$\surface$.
-The points of~$B$ are called the \defn{blossom points}.
+Let~$I$ denote the interior points and $B$ the blossom points.
 
@@
 \label{def:accordion}
-A \defn{$\dissection$-accordion} is ...
+A \defn{$\dissection$-accordion} is an arc of~$(\surface, B)$ so that for each face~$f \in \faces(\dissection)$ ...
+\end{definition}
+
+\begin{definition}
+\label{def:accordionComplex}
+The \defn{$\dissection$-accordion complex}~$\AC$ is the simplicial complex of pairwise non-crossing $\dissection$-accordions.
+\vincent{Reduced accordion complex.}
 \end{definition}
@@
 \label{def:zigzag}
-A \defn{$\dissection\dual$-zigzag} is ...
+A \defn{$\dissection\dual$-zigzag} is an arc of~$(\surface, B)$ so that for each face~$f \in \faces(\dissection)$ ...
+\end{definition}
+
+\begin{definition}
+\label{def:zigzagComplex}
+The \defn{$\dissection\dual$-zigzag complex}~$\ZC$ is the simplicial complex of pairwise non-crossing $\dissection$-zigzags.
+\vincent{Reduced zigzag complex.}
 \end{definition}
@@
 
+\begin{proposition}
+\label{prop:accordionsZigzags}
+For two dual dissections~$\dissection$ and~$\dissection\dual$, the $\dissection$-accordions are precisely the $\dissection\dual$-zigzags and the $\dissection$-accordion complex coincides with the $\dissection\dual$-zigzag complex.
+\end{proposition}
+
+\begin{proof}
+\vincent{Todo}
+\end{proof}
+
 \begin{remark}
-The $\dissection$-zigzags and the $\dissection\dual$-accordions are defined dually.
+To clearly visualize Proposition~\ref{prop:accordionsZigzags}, we follow the convention to draw the $\dissection$-accordions (resp.~$\dissection\dual$-zigzags) so that they intersect the arcs of~$\dissection$ (resp.~of~$\dissection\dual$) only at the intersection points of the arcs of~$\dissection$ with the arcs of~$\dissection\dual$.
+\vincent{That is interior points}
 \end{remark}
 
-\subsection{Accordion complex and zigzag complex}
+\begin{remark}
+The $\dissection$-zigzags and the $\dissection\dual$-accordions are defined dually and also coincide.
+\end{remark}
 
-\newpage
+\begin{remark}
+A quick disclaimer about accordion complexes and zigzag complexes of arbitrary dissections.
+As stated in Proposition~\ref{prop:conditionsDualDissections}, a dissection~$\dissection$ with a face containing more than one boundary edge does not admit a dual dissection~$\dissection\dual$.
+This prevents to use the definitions given in this section.
+Although its accordion complex (resp.~zigzag complex) could still be defined as in~\cite{MannevillePilaud-accordion} (resp.~\cite{GarverMcConville}) for the disk, the resulting complexes would be join of smaller accordion complexes (resp.~zigzag complexes) defined in this paper.
+See \cite[Prop.~2.4]{MannevillePilaud-accordion} for a detailed statement in the case of the disk.
+\end{remark}
+
+\section{All complexes coincide}
+
+\vincent{This section is just sketched at the moment.}
+
+\subsection{The bound quiver of a dissection}
+
+\begin{definition}
+\label{def:quiverDualDissections}
+The bound quiver of a dissection~$\dissection$ is defined rotating around each face of~$\dissection$.
+Define also the blossoming quiver of~$\dissection$.
+Note that boundary edges of~$\dissection$ get two blossoms.
+\end{definition}
+
+\begin{proposition}
+\label{prop:dualityKozul1}
+For two dual dissections~$\dissection$ and~$\dissection\dual$ of an oriented surface, the quivers~$\bar Q(\dissection)$ and~$\bar Q(\dissection\dual)$ are Kozul duals.
+\end{proposition}
+
+\subsection{The surface of a quiver}
+
+\begin{definition}
+\label{def:surfaceQuiver}
+The surface~$\surface(\bar Q)$ of a gentle bound quiver~$\bar Q = (Q,I)$ is obtained by glueing lozanges around arrows of~$Q$ following the rule given by the relations~$I$.
+The construction also automatically defines two dual dissections~$\dissection(\bar Q)$ and~$\dissection\dual(\bar Q)$ of the surface~$\surface(\bar Q)$.
+\end{definition}
+
+\begin{proposition}
+\label{prop:dualityKozul2}
+For any gentle bound quiver~$\bar Q$ with Kozul dual~$\bar Q\dual$, the surfaces~$\surface(\bar Q)$ and~$\surface(\bar Q\dual)$ coincide, but~$\dissection(\bar Q\dual) = \dissection\dual(\bar Q)$ and~$\dissection\dual(\bar Q\dual) = \dissection(\bar Q)$.
+\end{proposition}
+
+\subsection{Accordion, zigzag and non-kissing complexe coincide}
+
+\begin{lemma}
+\label{lem:walks=arcs}
+Walks of $\bar Q$ are precisely arcs between blossom points.
+\end{lemma}
+
+\begin{lemma}
+\label{lem:nonKissing=nonCrossing}
+Non-kissing walks = non-crossing arcs.
+\end{lemma}
+
+\begin{theorem}
+\label{thm:complexesCoincide}
+\begin{itemize}
+\item For any gentle bound quiver~$\bar Q$, the non-kissing complex~$\NKC$ is isomorphic to the accordion complex~$\AC[\dissection(\bar Q)]$ and to the zigzag complex~$\ZC[\dissection\dual(\bar Q)]$.
+\item For any pair of dual dissections~$\dissection, \dissection\dual$ of an oriented surface, the accordion complex~$\AC$ and the zigzag complex~$\ZC$ are isomorphic to the non-kissing complex~$\NKC[\bar Q(\dissection)]$.
+\end{itemize}
+\end{theorem}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\bibliographystyle{alpha}
+\bibliography{accordionComplexSurfaces}
+\label{sec:biblio}
 

### 2018-05-10 draft/accordionComplexSurfaces.tex
more details

@@
 \newcommandx{\ZC}[1][1=\dissection\dual]{\mathcal{K}_{\mathrm{zz}}(#1)} % zigzag complex
+\newcommandx{\NCC}[1][1={\dissection, \dissection\dual}]{\mathcal{K}_{\mathrm{nc}}(#1)} % non-crossing complex
 
@@
 
-\title{Accordion / zigzag / non-kissing / support $\tau$-tilting complexes all coincide}
+\title[Non-kissing and non-crossing complexes for gentle algebras]{Non-kissing and non-crossing complexes \\ for gentle algebras}
 
@@
 \begin{abstract}
+We consider three combinatorial models for the support $\tau$-tilting complex of a gentle bound quiver: the accordion complex, the zigzag complex, and the non-kissing complex.
+We unify these models in the same picture.
 \end{abstract}
@@
 \maketitle
+
+Possible titles, depending on what we want to insist on:
+\begin{enumerate}
+\item Accordion / zigzag / non-kissing / support $\tau$-tilting complexes all coincide for gentle algebras
+\item Non-kissing and non-crossing complexes for gentle algebras
+\item Combinatorial models for support $\tau$-tilting on gentle algebras: accordion, zigzag and non-kissing complexes
+\end{enumerate}
 
@@
 \vincent{Examples}
+\vincent{Should we introduce Koszul duality here and say what it does on quivers?}
 
@@
 
-\section{Accordion complex and zigzag complex}
+\section{Accordion complex, zigzag complex, and non-crossing complex}
 
@@
 
-\subsection{Accordion complex and zigzag complex}
+\subsection{Accordion complex, zigzag complex, and non-crossing complex}
 
@@
 \begin{proof}
-\vincent{Todo}
+\vincent{Todo. I have the impression here that we need cellular embeddings.}
 \end{proof}
+
+\begin{definition}
+\label{def:noncrossingComplex}
+We call \defn{non-crossing complex} of the pair of dual dissections~$(\dissection, \dissection\dual)$ the simplicial complex~$\NCC = \AC = \ZC$.
+\end{definition}
 
@@
 
-\section{All complexes coincide}
+\section{Non-kissing versus non-crossing}
+
+In this section, we show that non-kissing complexes and non-crossing complexes actually coincide.
+Namely, any pair of dual dissections~$(\dissection, \dissection\dual)$ defines a gentle bound quiver~$\bar Q_{\dissection, \dissection\dual}$ such that the non-crossing complex~$\NCC$ is isomorphic to the non-kissing complex~$\NKC[\bar Q_{\dissection, \dissection\dual}]$.
+Conversely, any gentle bound quiver~$\bar Q$ gives rise to a surface~$\surface_{\bar Q}$ equipped with a pair of dual dissections~$\dissection_{\bar Q}$ and~$\dissection\dual_{\bar Q}$ such that the non-kissing complex~$\NKC$ is isomorphic to the non-crossing complex~$\NCC[\dissection_{\bar Q}, \dissection\dual_{\bar Q}]$.
+In fact, we show that the accordion, zigzag, and non-kissing complexes can all be pictured in a unique way on the surface.
+Interestingly, via the correspondence between pairs of dual dissections and gentle bound quivers, the duality between the dissections~$\dissection$ and~$\dissection\dual$ translates to the Koszul duality between the gentle algebras of~$\bar Q$ and~$\bar Q\dual$.
 
@@
 \subsection{The bound quiver of a dissection}
+
+Let~$\surface$ be a surface with two sets~$M$ and~$M\dual$ of marked points and two dual dissections~$\dissection$ and~$\dissection\dual$.
+Let~$I$ denote the interior points and $B$ the blossom points.
 
@@
 \begin{proposition}
-\label{prop:dualityKozul1}
-For two dual dissections~$\dissection$ and~$\dissection\dual$ of an oriented surface, the quivers~$\bar Q(\dissection)$ and~$\bar Q(\dissection\dual)$ are Kozul duals.
+\label{prop:dualityKoszul1}
+For two dual dissections~$\dissection$ and~$\dissection\dual$ of an oriented surface, the quivers~$\bar Q_{\dissection}$ and~$\bar Q_{\dissection\dual}$ are Koszul duals.
+\vincent{Here I mean that the gentle algebras are Koszul duals. We need to define that somewhere and discuss it on gentle quivers.}
 \end{proposition}
@@
 The surface~$\surface(\bar Q)$ of a gentle bound quiver~$\bar Q = (Q,I)$ is obtained by glueing lozanges around arrows of~$Q$ following the rule given by the relations~$I$.
-The construction also automatically defines two dual dissections~$\dissection(\bar Q)$ and~$\dissection\dual(\bar Q)$ of the surface~$\surface(\bar Q)$.
+The construction also automatically defines two dual dissections~$\dissection_{\bar Q}$ and~$\dissection\dual_{\bar Q}$ of the surface~$\surface_{\bar Q}$.
 \end{definition}
@@
 \begin{proposition}
-\label{prop:dualityKozul2}
-For any gentle bound quiver~$\bar Q$ with Kozul dual~$\bar Q\dual$, the surfaces~$\surface(\bar Q)$ and~$\surface(\bar Q\dual)$ coincide, but~$\dissection(\bar Q\dual) = \dissection\dual(\bar Q)$ and~$\dissection\dual(\bar Q\dual) = \dissection(\bar Q)$.
+\label{prop:dualityKoszul2}
+For any gentle bound quiver~$\bar Q$ with Koszul dual~$\bar Q\dual$, the surfaces~$\surface_{\bar Q}$ and~$\surface_{\bar Q\dual}$ coincide, but~$\dissection_{\bar Q\dual} = \dissection\dual_{\bar Q}$ and~$\dissection\dual_{\bar Q\dual} = \dissection_{\bar Q}$.
 \end{proposition}
@@
 \begin{itemize}
-\item For any gentle bound quiver~$\bar Q$, the non-kissing complex~$\NKC$ is isomorphic to the accordion complex~$\AC[\dissection(\bar Q)]$ and to the zigzag complex~$\ZC[\dissection\dual(\bar Q)]$.
-\item For any pair of dual dissections~$\dissection, \dissection\dual$ of an oriented surface, the accordion complex~$\AC$ and the zigzag complex~$\ZC$ are isomorphic to the non-kissing complex~$\NKC[\bar Q(\dissection)]$.
+\item For any gentle bound quiver~$\bar Q$, the non-kissing complex~$\NKC$ is isomorphic to the non-crossing complex~$\NCC[\dissection_{\bar Q}, \dissection\dual_{\bar Q}]$, therefore to the accordion complex~$\AC[\dissection_{\bar Q}]$ and to the zigzag complex~$\ZC[\dissection\dual_{\bar Q}]$.
+\item For any pair of dual dissections~$\dissection, \dissection\dual$ of an oriented surface, the non-crossing complex~$\NCC$ is isomorphic to the non-kissing complex~$\NKC[\bar Q_{\dissection, \dissection\dual}]$.
 \end{itemize}

### 2018-05-23 draft/accordionComplexSurfaces.tex
Tentative de definition d'accordeon.

@@
 \label{def:accordion}
-A \defn{$\dissection$-accordion} is an arc of~$(\surface, B)$ so that for each face~$f \in \faces(\dissection)$ ...
+A \defn{$\dissection$-accordion} is an arc~$\gamma$ of~$(\surface, B)$ such that any two arcs of $\dissection$ crossed consecutively by~$\gamma$
+share a marked point with the property that the region bounded by~$\gamma$ and the two arcs around the marked point is homeomorphic to a disk
+(in particular, it contains no punctures).
 \end{definition}

### 2018-05-24 draft/accordionComplexSurfaces.tex
cellular

--- 2018-05-10 draft/accordionComplexSurfaces.tex
@@
 \newtheorem{assumption}[theorem]{Assumption}
+\newtheorem{convention}[theorem]{Convention}
 
@@
 
+\begin{convention}
+\textbf{All throughout the paper, all dissections are considered cellular.}
+The case of non-cellular dissections will be discussed in Section~\ref{sec:nonCellularDissections}.
+\end{convention}
+
 \begin{definition}
 Let~$\surface$ be a surface with two sets~$M$ and~$M\dual$ of marked points so that~$M$ and~$M\dual$ alternate along the boundary of~$\surface$.
-A dissection~$\dissection$ of~$(\surface, M)$ and a dissection~$\dissection\dual$ of~$(\surface, M\dual)$ are \defn{dual dissections} if there are pairs of mutually inverse bijections~$M\dual \leftrightarrow \faces(\dissection)$ and~$M \leftrightarrow \faces(\dissection\dual)$, denoted~$\dual$ in both directions, such that the dissection~$\dissection$ has an edge joining its vertices~$u,v \in M$ and separating its faces~$f,g \in  \faces(\dissection)$ if and only if~$\dissection\dual$ has an edge joining its vertices~$f\dual, g\dual \in M\dual$ and separating its faces~$u\dual, v\dual \in \faces(\dissection\dual)$.
+A cellular dissection~$\dissection$ of~$(\surface, M)$ and a cellular dissection~$\dissection\dual$ of~$(\surface, M\dual)$ are \defn{dual cellular dissections} if there are pairs of mutually inverse bijections~$M\dual \leftrightarrow \faces(\dissection)$ and~$M \leftrightarrow \faces(\dissection\dual)$, denoted~$\dual$ in both directions, such that~$\dissection$ has an arc joining its vertices~$u,v \in M$ and separating its faces~$f,g \in  \faces(\dissection)$ if and only if~$\dissection\dual$ has an arc joining its vertices~$f\dual, g\dual \in M\dual$ and separating its faces~$u\dual, v\dual \in \faces(\dissection\dual)$.
 \end{definition}
@@
 \begin{itemize}
-\item if a face~$f$ has no edge on the boundary of~$\surface$, its dual vertex~$f\dual$ lies in the interior~of~$f$,
-\item if a face~$f$ has an edge on the boundary of~$\surface$, then it has exactly one such edge and its dual vertex~$f\dual$ lies on this edge.
+\item if a face~$f$ has no arc on the boundary of~$\surface$, its dual vertex~$f\dual$ lies in the interior~of~$f$,
+\item if a face~$f$ has an arc on the boundary of~$\surface$, then it has exactly one such arc and its dual vertex~$f\dual$ lies on this arc.
 \end{itemize}
-In fact, the second point forces the following characterization of the dissections that admit a dual dissection.
+In fact, the second point forces the following characterization of the cellular dissections that admit a dual cellular dissection.
 
@@
 \label{prop:conditionsDualDissections}
-For a dissection~$\dissection$ of a marked surface~$(\surface, M)$, there exists a set~$M\dual$ of points of~$\surface$ and a dissection~$\dissection\dual$ of~$(\surface, M\dual)$ such that~$\dissection$ and~$\dissection\dual$ are dual dissections if and only if each face of~$\dissection$ has at most one boundary edge.
-Moreover, the set~$M\dual$ is unique.
+For a cellular dissection~$\dissection$ of a marked surface~$(\surface, M)$, the following assertions are equivalent:
+\begin{enumerate}[(i)]
+\item there exists a set~$M\dual$ of points of~$\surface$ and a cellular dissection~$\dissection\dual$ of~$(\surface, M\dual)$ such that~$\dissection$ and~$\dissection\dual$ are dual cellular dissections,
+\item each face of~$\dissection$ has at most one boundary arc.
+\end{enumerate}
+Moreover, the set~$M\dual$ and the cellular dissection~$\dissection\dual$ are both uniquely determined.
 \end{proposition}
@@
 \begin{proof}
-\vincent{Todo}
+Assume first that~$\dissection$ and~$\dissection\dual$ are dual cellular dissections.
+If a face~$F$ of~$\dissection$ had two boundary arcs~$a, b$, then it would contain two points of~$M\dual$, one on~$a$ and one on~$b$.
+Conversely, if each face of~$\dissection$ has at most one boundary arc, we construct the set of points~$M\dual$ with one point on each boundary arc of~$\surface$ and one point in the interior of each interior face of~$\dissection$.
+Clearly, $M\dual$ has one point~$f\dual$ in each face~$f$ of~$\dissection$.
+We then construct half-arcs of~$\dissection\dual$ in each face~$f$ of~$\dissection$ by joining the dual point~$f\dual$ to the middle of each boundary arc of~$f$ that is not a boundary arc of~$\surface$.
+For each arc~$a$ of~$\dissection$, the half-arcs incident to the middle of~$a$ in the two faces of~$\dissection$ containing~$a$ form the dual arc~$a\dual$ of~$a$.
+All these dual arcs do not cross (as the half-arcs do not cross in each face of~$\dissection$) and form the dual cellular dissection~$\dissection\dual$ of~$\dissection$.
+More details can be found in~\cite{PlamondonSchroll}.
 \end{proof}
 
-\begin{remark}
-In Proposition~\ref{prop:conditionsDualDissections}, note that although the set~$M\dual$ of dual marked points is unique, the dual dissection~$\dissection\dual$ is not when~$\dissection$ is not cellular.
-\end{remark}
+%\begin{remark}
+%In Proposition~\ref{prop:conditionsDualDissections}, note that although the set~$M\dual$ of dual marked points is unique, the dual dissection~$\dissection\dual$ is not when~$\dissection$ is not cellular.
+%\end{remark}
 
 \begin{example}
-Two examples of dual dissections on a surface are represented in \fref{fig:dissections}.
+Two examples of dual cellular dissections on a surface are represented in \fref{fig:dissections}.
 \end{example}
@@
 Interior points, blossom points.
-Half-edges.
+Half-arcs.
 
@@
 
-Let~$\surface$ be a surface with two sets~$M$ and~$M\dual$ of marked points and two dual dissections~$\dissection$ and~$\dissection\dual$.
+Let~$\surface$ be a surface with two sets~$M$ and~$M\dual$ of marked points and two dual cellular dissections~$\dissection$ and~$\dissection\dual$.
 Let~$I$ denote the interior points and $B$ the blossom points.
@@
 \label{prop:accordionsZigzags}
-For two dual dissections~$\dissection$ and~$\dissection\dual$, the $\dissection$-accordions are precisely the $\dissection\dual$-zigzags and the $\dissection$-accordion complex coincides with the $\dissection\dual$-zigzag complex.
+For two dual cellular dissections~$\dissection$ and~$\dissection\dual$, the $\dissection$-accordions are precisely the $\dissection\dual$-zigzags and the $\dissection$-accordion complex coincides with the $\dissection\dual$-zigzag complex.
 \end{proposition}
@@
 \label{def:noncrossingComplex}
-We call \defn{non-crossing complex} of the pair of dual dissections~$(\dissection, \dissection\dual)$ the simplicial complex~$\NCC = \AC = \ZC$.
+We call \defn{non-crossing complex} of the pair of dual cellular dissections~$(\dissection, \dissection\dual)$ the simplicial complex~$\NCC = \AC = \ZC$.
 \end{definition}
@@
 A quick disclaimer about accordion complexes and zigzag complexes of arbitrary dissections.
-As stated in Proposition~\ref{prop:conditionsDualDissections}, a dissection~$\dissection$ with a face containing more than one boundary edge does not admit a dual dissection~$\dissection\dual$.
+As stated in Proposition~\ref{prop:conditionsDualDissections}, a dissection~$\dissection$ with a face containing more than one boundary edge does not admit a dual cellular dissection~$\dissection\dual$.
 This prevents to use the definitions given in this section.
@@
 In this section, we show that non-kissing complexes and non-crossing complexes actually coincide.
-Namely, any pair of dual dissections~$(\dissection, \dissection\dual)$ defines a gentle bound quiver~$\bar Q_{\dissection, \dissection\dual}$ such that the non-crossing complex~$\NCC$ is isomorphic to the non-kissing complex~$\NKC[\bar Q_{\dissection, \dissection\dual}]$.
-Conversely, any gentle bound quiver~$\bar Q$ gives rise to a surface~$\surface_{\bar Q}$ equipped with a pair of dual dissections~$\dissection_{\bar Q}$ and~$\dissection\dual_{\bar Q}$ such that the non-kissing complex~$\NKC$ is isomorphic to the non-crossing complex~$\NCC[\dissection_{\bar Q}, \dissection\dual_{\bar Q}]$.
+Namely, any pair of dual cellular dissections~$(\dissection, \dissection\dual)$ defines a gentle bound quiver~$\bar Q_{\dissection, \dissection\dual}$ such that the non-crossing complex~$\NCC$ is isomorphic to the non-kissing complex~$\NKC[\bar Q_{\dissection, \dissection\dual}]$.
+Conversely, any gentle bound quiver~$\bar Q$ gives rise to a surface~$\surface_{\bar Q}$ equipped with a pair of dual cellular dissections~$\dissection_{\bar Q}$ and~$\dissection\dual_{\bar Q}$ such that the non-kissing complex~$\NKC$ is isomorphic to the non-crossing complex~$\NCC[\dissection_{\bar Q}, \dissection\dual_{\bar Q}]$.
 In fact, we show that the accordion, zigzag, and non-kissing complexes can all be pictured in a unique way on the surface.
-Interestingly, via the correspondence between pairs of dual dissections and gentle bound quivers, the duality between the dissections~$\dissection$ and~$\dissection\dual$ translates to the Koszul duality between the gentle algebras of~$\bar Q$ and~$\bar Q\dual$.
+Interestingly, via the correspondence between pairs of dual cellular dissections and gentle bound quivers, the duality between the dissections~$\dissection$ and~$\dissection\dual$ translates to the Koszul duality between the gentle algebras of~$\bar Q$ and~$\bar Q\dual$.
 
@@
 \label{prop:dualityKoszul1}
-For two dual dissections~$\dissection$ and~$\dissection\dual$ of an oriented surface, the quivers~$\bar Q_{\dissection}$ and~$\bar Q_{\dissection\dual}$ are Koszul duals.
+For two dual cellular dissections~$\dissection$ and~$\dissection\dual$ of an oriented surface, the quivers~$\bar Q_{\dissection}$ and~$\bar Q_{\dissection\dual}$ are Koszul duals.
 \vincent{Here I mean that the gentle algebras are Koszul duals. We need to define that somewhere and discuss it on gentle quivers.}
@@
 The surface~$\surface(\bar Q)$ of a gentle bound quiver~$\bar Q = (Q,I)$ is obtained by glueing lozanges around arrows of~$Q$ following the rule given by the relations~$I$.
-The construction also automatically defines two dual dissections~$\dissection_{\bar Q}$ and~$\dissection\dual_{\bar Q}$ of the surface~$\surface_{\bar Q}$.
+The construction also automatically defines two dual cellular dissections~$\dissection_{\bar Q}$ and~$\dissection\dual_{\bar Q}$ of the surface~$\surface_{\bar Q}$.
 \end{definition}
@@
 \item For any gentle bound quiver~$\bar Q$, the non-kissing complex~$\NKC$ is isomorphic to the non-crossing complex~$\NCC[\dissection_{\bar Q}, \dissection\dual_{\bar Q}]$, therefore to the accordion complex~$\AC[\dissection_{\bar Q}]$ and to the zigzag complex~$\ZC[\dissection\dual_{\bar Q}]$.
-\item For any pair of dual dissections~$\dissection, \dissection\dual$ of an oriented surface, the non-crossing complex~$\NCC$ is isomorphic to the non-kissing complex~$\NKC[\bar Q_{\dissection, \dissection\dual}]$.
+\item For any pair of dual cellular dissections~$\dissection, \dissection\dual$ of an oriented surface, the non-crossing complex~$\NCC$ is isomorphic to the non-kissing complex~$\NKC[\bar Q_{\dissection, \dissection\dual}]$.
 \end{itemize}

### 2018-05-28 draft/accordionComplexSurfaces.tex
tentative definition of zig-zags and proof of Prop 22

@@
 \begin{proof}
+We mimick the proof of~\cite[Proposition 1.12]{OpperPlamondonSchroll}.
 Assume first that~$\dissection$ and~$\dissection\dual$ are dual cellular dissections.
@@
 All these dual arcs do not cross (as the half-arcs do not cross in each face of~$\dissection$) and form the dual cellular dissection~$\dissection\dual$ of~$\dissection$.
-More details can be found in~\cite{PlamondonSchroll}.
+More details can be found in~\cite{OpperPlamondonSchroll}.
 \end{proof}
@@
 (in particular, it contains no punctures).
+\yann{Il faut probablement ajouter des conditions aux bords}
 \end{definition}
@@
 \label{def:zigzag}
-A \defn{$\dissection\dual$-zigzag} is an arc of~$(\surface, B)$ so that for each face~$f \in \faces(\dissection)$ ...
+A \defn{$\dissection\dual$-zigzag} is an arc~$\alpha$ of~$(\surface, B)$ such that, for each pair of faces~$(f,g) \in \faces(\dissection\dual)$ that~$\alpha$ enters consecutively by crossing~$\beta\in\dissection\dual$,~$\alpha$ cuts the union of the two cells $f$ and $g$ glued along~$\beta$ into two components, one containing the marked point $f\dual$ and the other containing $g\dual$.
 \end{definition}
@@
 \vincent{Todo. I have the impression here that we need cellular embeddings.}
+Let~$\alpha$ be a~$\dissection$-accordion.
+Let~$\beta$,~$\gamma$,~$\delta$ be three consecutive arcs of~$\dissection$ crossed by~$\gamma$.
+Let~$m\in\dissection$ be the common endpoint of~$\beta$ and $\gamma$ given by Definition~\ref{def:accordion} and let~$n\in\dissection$ be the common endpoint of~$\gamma$ and~$\delta$.
+If $m=n$, then the segment of~$\alpha$ between~$\beta$ and~$\delta$ stays in the same face of~$\dissection\dual$.
+Otherwise, when crossing~$\gamma$, the accordion~$\alpha$ leaves the face~$m\dual$ of $\dissection\dual$ and enters the face~$n\dual$.
+In the surface obtained by glueing the two cells~$m\dual$ and~$n\dual$ along~$\gamma\dual$, the marked points~$m$ and~$n$ are separated by~$\alpha$.
+Conversely, assume that~$\alpha$ is an arc of~$(\surface, B)$ which is not a $\dissection$-accordion.
+We are in one of the following cases.
+
+Case 1: The arc~$\alpha$ consecutively crosses two arcs~$\beta$ and~$\gamma$ of~$\dissection$ that do not share a common endpoint.
+Let~$f$ be the face of~$\dissection$ that contain the segment of~$\alpha$ between~$\beta$ and~$\gamma$.
+Consider the connected component of~$f\setminus\alpha$ that do not contain~$f\dual$.
+The boundaty of this component contains an arc~$\delta\in\dissection\setminus\{\beta\}$ that share a common endpoint with~$\beta$.
+Let~$m,n$ be the endpoints of~$\delta$.
+Then~$\alpha$ cuts the cells $m\dual,n\dual$ glued along~$\delta\dual$ into two connected component, one containing both endpoints of~$\delta$.
+
+Case 2: The arc~$\alpha$ consecutively crosses two arcs~$\beta$ and~$\gamma$ of~$\dissection$ that share a unique common endpoint, but the region delimited by~$\alpha$,~$\beta$ and~$\gamma$ is not a disk.
+Since the dissection~$\dissection$ is cellular, that region has to contain some marked point~$m\in\dissection\dual$.
+One conclude that~$\alpha$ is not a~$\dissection\dual$-zigzag similarly as in the first case, by considering the component of~$m\dual\setminus\alpha$ that do not contain~$m$.
+
+Case 3: The arc~$\alpha$ consecutively crosses two arcs~$\beta$ and~$\gamma$ of~$\dissection$ that share two different endpoints, and none of the two regions delimited by~$\alpha$,~$\beta$ and~$\gamma$ is a disk.
+Since the dissection~$\dissection$ is cellular, both regions have to contain a puncture.
+This contradicts the assumption that the dissections~$\dissection$ and~$\dissection\dual$ are dual to each other.
 \end{proof}

### 2018-05-30 draft/accordionComplexSurfaces.tex
minor changes

@@
 \usepackage[T1]{fontenc}
-\usepackage{enumerate, amsmath, amsfonts, amssymb, amsthm, mathrsfs, wasysym, graphics, graphicx, xcolor, url, hyperref, hypcap,  shuffle, xargs, multicol, overpic, pdflscape, multirow, hvfloat, minibox, accents, array, xifthen, ae, aecompl, blkarray, pifont, mathtools, a4wide}
+\usepackage{enumerate, amsmath, amsfonts, amssymb, amsthm, mathrsfs, wasysym, graphics, graphicx, xcolor, url, hyperref, hypcap, xargs, multicol, overpic, pdflscape, multirow, hvfloat, minibox, accents, array, xifthen, ae, aecompl, blkarray, pifont, mathtools, a4wide}
 \usepackage{marginnote}
@@
 
-% accordion and zigzag complexes
+% accordion and slalom complexes
 \newcommand{\surface}{\mathcal{S}} % an orientable surface
@@
 \renewcommandx{\AC}[1][1=\dissection]{\mathcal{K}_{\mathrm{acc}}(#1)} % accordion complex
-\newcommandx{\ZC}[1][1=\dissection\dual]{\mathcal{K}_{\mathrm{zz}}(#1)} % zigzag complex
+\newcommandx{\SC}[1][1=\dissection\dual]{\mathcal{K}_{\mathrm{sla}}(#1)} % slalom complex
 \newcommandx{\NCC}[1][1={\dissection, \dissection\dual}]{\mathcal{K}_{\mathrm{nc}}(#1)} % non-crossing complex
@@
 \begin{abstract}
-We consider three combinatorial models for the support $\tau$-tilting complex of a gentle bound quiver: the accordion complex, the zigzag complex, and the non-kissing complex.
+We consider three combinatorial models for the support $\tau$-tilting complex of a gentle bound quiver: the accordion complex, the slalom complex, and the non-kissing complex.
 We unify these models in the same picture.
@@
 \begin{enumerate}
-\item Accordion / zigzag / non-kissing / support $\tau$-tilting complexes all coincide for gentle algebras
+\item Accordion / slalom / non-kissing / support $\tau$-tilting complexes all coincide for gentle algebras
 \item Non-kissing and non-crossing complexes for gentle algebras
-\item Combinatorial models for support $\tau$-tilting on gentle algebras: accordion, zigzag and non-kissing complexes
+\item Combinatorial models for support $\tau$-tilting on gentle algebras: accordion, slalom and non-kissing complexes
 \end{enumerate}
@@
 
-\section{Accordion complex, zigzag complex, and non-crossing complex}
+\section{Accordion complex, slalom complex, and non-crossing complex}
 
@@
 \begin{definition}
-A \defn{marked surface}~$\bar\surface \eqdef (\surface,M)$ is an orientable surface~$\surface$ with boundaries, together with a set~$M$ of marked points which can be on the boundary of~$\surface$ or not.
+A \defn{marked surface}~$\bar\surface \eqdef (\surface, M)$ is an orientable surface~$\surface$ with boundaries, together with a set~$M$ of marked points which can be on the boundary of~$\surface$ or not.
 An \defn{arc} on~$\bar\surface$ is a curve on~$\surface$ connecting two marked points of~$M$ and whose interior is disjoint from~$M$ and the boundary of~$\surface$ (note that arcs homotopic to boundary arcs are allowed here).
@@
 
-\subsection{Accordion complex, zigzag complex, and non-crossing complex}
+\subsection{Accordion complex, slalom complex, and non-crossing complex}
 
@@
 \label{def:accordion}
-A \defn{$\dissection$-accordion} is an arc~$\gamma$ of~$(\surface, B)$ such that any two arcs of $\dissection$ crossed consecutively by~$\gamma$
-share a marked point with the property that the region bounded by~$\gamma$ and the two arcs around the marked point is homeomorphic to a disk
-(in particular, it contains no punctures).
-\yann{Il faut probablement ajouter des conditions aux bords}
+A \defn{$\dissection$-accordion} is an arc~$\gamma$ of~$(\surface, B)$ such that whenever~$\gamma$ crosses a face~$f$ of~$\dissection$, it crosses two edges of~$f$ that share a marked point of~$v \in M$ in such a way that~$v$ and~$f\dual$ lie on opposite sides of~$\gamma$.
+
+% the two edges of~$f$ crossed by~$\gamma$ share a marked point~$v \in M$, and~$v$ and~$f\dual$ are on opposite sides of~$\gamma$ in~$f$.
+% any two arcs of $\dissection$ crossed consecutively by~$\gamma$ share a marked point with the property that the region bounded by~$\gamma$ and the two arcs around the marked point does not contain.
 \end{definition}
@@
 \begin{definition}
-\label{def:zigzag}
-A \defn{$\dissection\dual$-zigzag} is an arc~$\alpha$ of~$(\surface, B)$ such that, for each pair of faces~$(f,g) \in \faces(\dissection\dual)$ that~$\alpha$ enters consecutively by crossing~$\beta\in\dissection\dual$,~$\alpha$ cuts the union of the two cells $f$ and $g$ glued along~$\beta$ into two components, one containing the marked point $f\dual$ and the other containing $g\dual$.
+\label{def:slalom}
+A \defn{$\dissection\dual$-slalom} is an arc~$\alpha$ of~$(\surface, B)$ such that, for each pair of faces~$(f,g) \in \faces(\dissection\dual)$ that~$\alpha$ enters consecutively by crossing~$\beta\in\dissection\dual$,~$\alpha$ cuts the union of the two cells $f$ and $g$ glued along~$\beta$ into two components, one containing the marked point $f\dual$ and the other containing $g\dual$.
 \end{definition}
@@
 \begin{definition}
-\label{def:zigzagComplex}
-The \defn{$\dissection\dual$-zigzag complex}~$\ZC$ is the simplicial complex of pairwise non-crossing $\dissection$-zigzags.
-\vincent{Reduced zigzag complex.}
+\label{def:slalomComplex}
+The \defn{$\dissection\dual$-slalom complex}~$\SC$ is the simplicial complex of pairwise non-crossing $\dissection$-slaloms.
+\vincent{Reduced slalom complex.}
 \end{definition}
 
-\begin{remark}
-Note that the $\dissection$-accordions do not depend on~$\dissection\dual$, only on~$\dissection$ (and~$M\dual$ which is determined by~$\dissection$ by Proposition~\ref{prop:conditionsDualDissections}).
-Similarly, the $\dissection\dual$-zigzags do not depend on~$\dissection$.
-\end{remark}
+%\begin{remark}
+%Note that the $\dissection$-accordions do not depend on~$\dissection\dual$, only on~$\dissection$ (and~$M\dual$ which is determined by~$\dissection$ by Proposition~\ref{prop:conditionsDualDissections}).
+%Similarly, the $\dissection\dual$-slaloms do not depend on~$\dissection$.
+%\end{remark}
 
 \begin{proposition}
-\label{prop:accordionsZigzags}
-For two dual cellular dissections~$\dissection$ and~$\dissection\dual$, the $\dissection$-accordions are precisely the $\dissection\dual$-zigzags and the $\dissection$-accordion complex coincides with the $\dissection\dual$-zigzag complex.
+\label{prop:accordionsSlaloms}
+For two dual cellular dissections~$\dissection$ and~$\dissection\dual$, the $\dissection$-accordions are precisely the $\dissection\dual$-slaloms and the $\dissection$-accordion complex coincides with the $\dissection\dual$-slalom complex.
 \end{proposition}
@@
 Since the dissection~$\dissection$ is cellular, that region has to contain some marked point~$m\in\dissection\dual$.
-One conclude that~$\alpha$ is not a~$\dissection\dual$-zigzag similarly as in the first case, by considering the component of~$m\dual\setminus\alpha$ that do not contain~$m$.
+One conclude that~$\alpha$ is not a~$\dissection\dual$-slalom similarly as in the first case, by considering the component of~$m\dual\setminus\alpha$ that do not contain~$m$.
 
@@
 \label{def:noncrossingComplex}
-We call \defn{non-crossing complex} of the pair of dual cellular dissections~$(\dissection, \dissection\dual)$ the simplicial complex~$\NCC = \AC = \ZC$.
+We call \defn{non-crossing complex} of the pair of dual cellular dissections~$(\dissection, \dissection\dual)$ the simplicial complex~$\NCC = \AC = \SC$.
 \end{definition}
@@
 \begin{remark}
-To clearly visualize Proposition~\ref{prop:accordionsZigzags}, we follow the convention to draw the $\dissection$-accordions (resp.~$\dissection\dual$-zigzags) so that they intersect the arcs of~$\dissection$ (resp.~of~$\dissection\dual$) only at the intersection points of the arcs of~$\dissection$ with the arcs of~$\dissection\dual$.
+To clearly visualize Proposition~\ref{prop:accordionsSlaloms}, we follow the convention to draw the $\dissection$-accordions (resp.~$\dissection\dual$-slaloms) so that they intersect the arcs of~$\dissection$ (resp.~of~$\dissection\dual$) only at the intersection points of the arcs of~$\dissection$ with the arcs of~$\dissection\dual$.
 \vincent{That is interior points}
@@
 \begin{remark}
-The $\dissection$-zigzags and the $\dissection\dual$-accordions are defined dually and also coincide.
+The $\dissection$-slaloms and the $\dissection\dual$-accordions are defined dually and also coincide.
 \end{remark}
@@
 \begin{remark}
-A quick disclaimer about accordion complexes and zigzag complexes of arbitrary dissections.
+A quick disclaimer about accordion complexes and slalom complexes of arbitrary dissections, non-necessarily cellular.
 As stated in Proposition~\ref{prop:conditionsDualDissections}, a dissection~$\dissection$ with a face containing more than one boundary edge does not admit a dual cellular dissection~$\dissection\dual$.
 This prevents to use the definitions given in this section.
-Although its accordion complex (resp.~zigzag complex) could still be defined as in~\cite{MannevillePilaud-accordion} (resp.~\cite{GarverMcConville}) for the disk, the resulting complexes would be join of smaller accordion complexes (resp.~zigzag complexes) defined in this paper.
+Although its accordion complex (resp.~slalom complex) could still be defined as in~\cite{MannevillePilaud-accordion} (resp.~\cite{GarverMcConville}) for the disk, the resulting complexes would be join of smaller accordion complexes (resp.~slalom complexes) defined in this paper.
 See \cite[Prop.~2.4]{MannevillePilaud-accordion} for a detailed statement in the case of the disk.
@@
 Conversely, any gentle bound quiver~$\bar Q$ gives rise to a surface~$\surface_{\bar Q}$ equipped with a pair of dual cellular dissections~$\dissection_{\bar Q}$ and~$\dissection\dual_{\bar Q}$ such that the non-kissing complex~$\NKC$ is isomorphic to the non-crossing complex~$\NCC[\dissection_{\bar Q}, \dissection\dual_{\bar Q}]$.
-In fact, we show that the accordion, zigzag, and non-kissing complexes can all be pictured in a unique way on the surface.
+In fact, we show that the accordion, slalom, and non-kissing complexes can all be pictured in a unique way on the surface.
 Interestingly, via the correspondence between pairs of dual cellular dissections and gentle bound quivers, the duality between the dissections~$\dissection$ and~$\dissection\dual$ translates to the Koszul duality between the gentle algebras of~$\bar Q$ and~$\bar Q\dual$.
@@
 
-\subsection{Accordion, zigzag and non-kissing complexe coincide}
+\subsection{Accordion, slalom and non-kissing complexe coincide}
 
@@
 \begin{itemize}
-\item For any gentle bound quiver~$\bar Q$, the non-kissing complex~$\NKC$ is isomorphic to the non-crossing complex~$\NCC[\dissection_{\bar Q}, \dissection\dual_{\bar Q}]$, therefore to the accordion complex~$\AC[\dissection_{\bar Q}]$ and to the zigzag complex~$\ZC[\dissection\dual_{\bar Q}]$.
+\item For any gentle bound quiver~$\bar Q$, the non-kissing complex~$\NKC$ is isomorphic to the non-crossing complex~$\NCC[\dissection_{\bar Q}, \dissection\dual_{\bar Q}]$, therefore to the accordion complex~$\AC[\dissection_{\bar Q}]$ and to the slalom complex~$\SC[\dissection\dual_{\bar Q}]$.
 \item For any pair of dual cellular dissections~$\dissection, \dissection\dual$ of an oriented surface, the non-crossing complex~$\NCC$ is isomorphic to the non-kissing complex~$\NKC[\bar Q_{\dissection, \dissection\dual}]$.

### 2018-05-30 draft/accordionComplexSurfaces.tex
minor changes

@@
 \usepackage[T1]{fontenc}
-\usepackage{enumerate, amsmath, amsfonts, amssymb, amsthm, mathrsfs, wasysym, graphics, graphicx, xcolor, url, hyperref, hypcap, xargs, multicol, overpic, pdflscape, multirow, hvfloat, minibox, accents, array, xifthen, ae, aecompl, blkarray, pifont, mathtools, a4wide}
+\usepackage{enumerate, amsmath, amsfonts, amssymb, amsthm, mathrsfs, wasysym, graphics, graphicx, xcolor, url, hyperref, hypcap, xargs, multicol, overpic, pdflscape, multirow, hvfloat, array, ae, aecompl, pifont, mathtools, a4wide}
 \usepackage{marginnote}
@@
 \usepackage[all]{xy}
-\usepackage[bottom]{footmisc}
+%\usepackage[bottom]{footmisc}
 \usepackage{tikz}
@@
 A \defn{marked surface}~$\bar\surface \eqdef (\surface, M)$ is an orientable surface~$\surface$ with boundaries, together with a set~$M$ of marked points which can be on the boundary of~$\surface$ or not.
-An \defn{arc} on~$\bar\surface$ is a curve on~$\surface$ connecting two marked points of~$M$ and whose interior is disjoint from~$M$ and the boundary of~$\surface$ (note that arcs homotopic to boundary arcs are allowed here).
-As usual, arcs are considered up to homotopy relative to their endpoints in~$\surface \ssm M$.
-Two arcs \defn{cross} when they intersect in their interior.
+For~$V \subset \surface$, a \defn{$V$-arc} on~$\bar\surface$ is a curve on~$\surface$ connecting two points of~$V$ and whose interior is disjoint from~$M$ and the boundary of~$\surface$.
+As usual, arcs are considered up to homotopy relative to their endpoints in~$\surface \ssm M$, and curves homotopic to a boundary are not allowed.
+Two arcs \defn{cross} when they intersect in~their~interior.
 \end{definition}
@@
 The dissection~$\dissection$ is \defn{cellular} if all its faces are disks.
+For~$V \subseteq M$, a \defn{$V$-dissection} is a dissection with only $V$-arcs.
 \end{definition}
@@
 \begin{definition}
-Let~$\surface$ be a surface with two sets~$M$ and~$M\dual$ of marked points so that~$M$ and~$M\dual$ alternate along the boundary of~$\surface$.
-A cellular dissection~$\dissection$ of~$(\surface, M)$ and a cellular dissection~$\dissection\dual$ of~$(\surface, M\dual)$ are \defn{dual cellular dissections} if there are pairs of mutually inverse bijections~$M\dual \leftrightarrow \faces(\dissection)$ and~$M \leftrightarrow \faces(\dissection\dual)$, denoted~$\dual$ in both directions, such that~$\dissection$ has an arc joining its vertices~$u,v \in M$ and separating its faces~$f,g \in  \faces(\dissection)$ if and only if~$\dissection\dual$ has an arc joining its vertices~$f\dual, g\dual \in M\dual$ and separating its faces~$u\dual, v\dual \in \faces(\dissection\dual)$.
+Consider a marked surface~$\bar\surface = (\surface, V \sqcup V\dual)$, where~$V$ and~$V\dual$ are two disjoint sets of marked points so that the points of~$V$ and~$V\dual$ that are on the boundary of~$\surface$ alternate.
+A cellular $V$-dissection~$\dissection$ of~$\bar\surface$ and a cellular $V\dual$-dissection~$\dissection\dual$ of~$\bar\surface$ are \defn{dual cellular dissections} if there are pairs of mutually inverse bijections~$V\dual \leftrightarrow \faces(\dissection)$ and~$V \leftrightarrow \faces(\dissection\dual)$, denoted~$\dual$ in both directions, such that~$\dissection$ has an arc joining its vertices~$u,v \in V$ and separating its faces~$f,g \in  \faces(\dissection)$ if and only if~$\dissection\dual$ has an arc joining its vertices~$f\dual, g\dual \in V\dual$ and separating its faces~$u\dual, v\dual \in \faces(\dissection\dual)$.
 \end{definition}
 
-Note that contrarily to the usual conventions, the dual vertex of a face~$f$ is not always in the interior of the face.
+Note that contrarily to the usual conventions, the dual vertex~$f\dual$ of a face~$f$ of~$\dissection$ is not always in the interior of the face~$f$.
 More precisely, there are two situations:
@@
 \label{prop:conditionsDualDissections}
-For a cellular dissection~$\dissection$ of a marked surface~$(\surface, M)$, the following assertions are equivalent:
+For a cellular $V$-dissection~$\dissection$ of a marked surface~$\bar\surface = (\surface, V \sqcup V\dual)$, the following assertions are equivalent:
 \begin{enumerate}[(i)]
-\item there exists a set~$M\dual$ of points of~$\surface$ and a cellular dissection~$\dissection\dual$ of~$(\surface, M\dual)$ such that~$\dissection$ and~$\dissection\dual$ are dual cellular dissections,
-\item each face of~$\dissection$ has at most one boundary arc.
+\item there exists a cellular $V\dual$-dissection~$\dissection\dual$ of~$\bar\surface$ such that~$\dissection$ and~$\dissection\dual$ are dual cellular dissections,
+\item each face of~$\dissection$ contains exactly one point of~$V\dual$.
 \end{enumerate}
-Moreover, the set~$M\dual$ and the cellular dissection~$\dissection\dual$ are both uniquely determined.
+Moreover, the cellular dissection~$\dissection\dual$ is uniquely determined.
 \end{proposition}
@@
 \begin{proof}
-We mimick the proof of~\cite[Proposition 1.12]{OpperPlamondonSchroll}.
-Assume first that~$\dissection$ and~$\dissection\dual$ are dual cellular dissections.
-If a face~$F$ of~$\dissection$ had two boundary arcs~$a, b$, then it would contain two points of~$M\dual$, one on~$a$ and one on~$b$.
-Conversely, if each face of~$\dissection$ has at most one boundary arc, we construct the set of points~$M\dual$ with one point on each boundary arc of~$\surface$ and one point in the interior of each interior face of~$\dissection$.
+We mimick the proof of~\cite[Prop.~1.12]{OpperPlamondonSchroll}.
+%Assume first that~$\dissection$ and~$\dissection\dual$ are dual cellular dissections.
+If a face~$f$ of~$\dissection$ had two boundary arcs~$a, b$, then it would contain two points of~$M\dual$, one on~$a$ and one on~$b$.
+%Conversely, if each face of~$\dissection$ has at most one boundary arc, we construct the set of points~$M\dual$ with one point on each boundary arc of~$\surface$ and one point in the interior of each interior face of~$\dissection$.
 Clearly, $M\dual$ has one point~$f\dual$ in each face~$f$ of~$\dissection$.
@@
 All these dual arcs do not cross (as the half-arcs do not cross in each face of~$\dissection$) and form the dual cellular dissection~$\dissection\dual$ of~$\dissection$.
-More details can be found in~\cite{OpperPlamondonSchroll}.
+%More details can be found in~\cite{OpperPlamondonSchroll}.
+The direct implication is immediate by definition.
+Assume conversely that each face~$f$ of~$\dissection$ contains exactly one point~$f\dual$ of~$V\dual$.
+We construct half-arcs of~$\dissection\dual$ in each face~$f$ of~$\dissection$ by joining the dual point~$f\dual$ to the middle of each boundary arc of~$f$ that is not a boundary arc of~$\surface$.
+For each arc~$a$ of~$\dissection$, the half-arcs incident to the middle of~$a$ in the two faces of~$\dissection$ containing~$a$ form the dual arc~$a\dual$ of~$a$.
+All these dual arcs do not cross (as the half-arcs do not cross in each face of~$\dissection$) and form the dual cellular dissection~$\dissection\dual$~of~$\dissection$.
 \end{proof}
@@
 \subsection{Accordion complex, slalom complex, and non-crossing complex}
-
-Let~$\surface$ be a surface with two sets~$M$ and~$M\dual$ of marked points and two dual cellular dissections~$\dissection$ and~$\dissection\dual$.
-Let~$I$ denote the interior points and $B$ the blossom points.
+Let~$\surface$ be a surface with two disjoint sets~$V$ and~$V\dual$ of marked points, let~$B$ be the corresponding blossoming points, and consider the marked surface~$\bar\surface = (\surface, V \sqcup V\dual \sqcup B)$.
+Consider two dual cellular dissections~$\dissection$ and~$\dissection\dual$ of~$\bar\surface = (\surface, V \sqcup V\dual)$.
+%Let~$I$ denote the interior points and $B$ the blossom points.
 
@@
 \label{def:accordion}
-A \defn{$\dissection$-accordion} is an arc~$\gamma$ of~$(\surface, B)$ such that whenever~$\gamma$ crosses a face~$f$ of~$\dissection$, it crosses two edges of~$f$ that share a marked point of~$v \in M$ in such a way that~$v$ and~$f\dual$ lie on opposite sides of~$\gamma$.
+A \defn{$\dissection$-accordion} is a $B$-arc~$\gamma$ of~$\bar\surface$ such that whenever~$\gamma$ crosses a face~$f$ of~$\dissection$, it crosses two edges of~$f$ that share a marked point of~$v \in M$ in such a way that~$v$ and~$f\dual$ lie on opposite sides of~$\gamma$.
 
@@
 \label{def:slalom}
-A \defn{$\dissection\dual$-slalom} is an arc~$\alpha$ of~$(\surface, B)$ such that, for each pair of faces~$(f,g) \in \faces(\dissection\dual)$ that~$\alpha$ enters consecutively by crossing~$\beta\in\dissection\dual$,~$\alpha$ cuts the union of the two cells $f$ and $g$ glued along~$\beta$ into two components, one containing the marked point $f\dual$ and the other containing $g\dual$.
+A \defn{$\dissection\dual$-slalom} is a $B$-arc~$\alpha$ of~$\bar\surface$ such that, for each pair of faces~$(f,g) \in \faces(\dissection\dual)$ that~$\alpha$ enters consecutively by crossing~$\beta\in\dissection\dual$,~$\alpha$ cuts the union of the two cells $f$ and $g$ glued along~$\beta$ into two components, one containing the marked point $f\dual$ and the other containing $g\dual$.
 \end{definition}

### 2018-05-30 draft/accordionComplexSurfaces.tex
definitions accordion - slalom

@@
 \newcommand{\dissection}{\mathrm{D}} % dissection of a marked surface
+\newcommand{\vertices}{\mathcal{V}} % vertices of a dissection
+\newcommand{\edges}{\mathcal{E}} % edges of a dissection
 \newcommand{\faces}{\mathcal{F}} % faces of a dissection
@@
 A \defn{dissection} of~$\bar\surface$ is a collection~$\dissection$ of pairwise non-crossing arcs on~$\bar\surface$.
-The \defn{faces} of a dissection~$\dissection$ are the connected components of the complement of the union of the arcs of~$\dissection$ in the surface~$\surface$.
-We denote by~$\faces(\dissection)$ the set of faces of~$\dissection$.
+The \defn{edges} of~$\dissection$ are its arcs together with the boundary arcs of~$\bar\surface$.
+The \defn{faces} of~$\dissection$ are the connected components of the complement of the union of the edges of~$\dissection$ in the surface~$\surface$.
+We denote by~$\vertices(\dissection)$, $\edges(\dissection)$ and~$\faces(\dissection)$ the sets of vertices, edges and faces of~$\dissection$ respectively.
 The dissection~$\dissection$ is \defn{cellular} if all its faces are disks.
@@
 Consider a marked surface~$\bar\surface = (\surface, V \sqcup V\dual)$, where~$V$ and~$V\dual$ are two disjoint sets of marked points so that the points of~$V$ and~$V\dual$ that are on the boundary of~$\surface$ alternate.
-A cellular $V$-dissection~$\dissection$ of~$\bar\surface$ and a cellular $V\dual$-dissection~$\dissection\dual$ of~$\bar\surface$ are \defn{dual cellular dissections} if there are pairs of mutually inverse bijections~$V\dual \leftrightarrow \faces(\dissection)$ and~$V \leftrightarrow \faces(\dissection\dual)$, denoted~$\dual$ in both directions, such that~$\dissection$ has an arc joining its vertices~$u,v \in V$ and separating its faces~$f,g \in  \faces(\dissection)$ if and only if~$\dissection\dual$ has an arc joining its vertices~$f\dual, g\dual \in V\dual$ and separating its faces~$u\dual, v\dual \in \faces(\dissection\dual)$.
+A cellular $V$-dissection~$\dissection$ of~$\bar\surface$ and a cellular $V\dual$-dissection~$\dissection\dual$ of~$\bar\surface$ are \defn{dual cellular dissections} if there are pairs of mutually inverse bijections~$V\dual \leftrightarrow \faces(\dissection)$ and~$V \leftrightarrow \faces(\dissection\dual)$, denoted~$\dual$ in both directions, such that~$\dissection$ has an edge joining its vertices~$u,v \in V$ and separating its faces~$f,g \in  \faces(\dissection)$ if and only if~$\dissection\dual$ has an edge joining its vertices~$f\dual, g\dual \in V\dual$ and separating its faces~$u\dual, v\dual \in \faces(\dissection\dual)$.
 \end{definition}
@@
 \begin{itemize}
-\item if a face~$f$ has no arc on the boundary of~$\surface$, its dual vertex~$f\dual$ lies in the interior~of~$f$,
-\item if a face~$f$ has an arc on the boundary of~$\surface$, then it has exactly one such arc and its dual vertex~$f\dual$ lies on this arc.
+\item if a face~$f$ has no edge on the boundary of~$\surface$, its dual vertex~$f\dual$ lies in the interior~of~$f$,
+\item if a face~$f$ has an edge on the boundary of~$\surface$, then it has exactly one such edge and its dual vertex~$f\dual$ lies on this edge.
 \end{itemize}
@@
 Assume conversely that each face~$f$ of~$\dissection$ contains exactly one point~$f\dual$ of~$V\dual$.
-We construct half-arcs of~$\dissection\dual$ in each face~$f$ of~$\dissection$ by joining the dual point~$f\dual$ to the middle of each boundary arc of~$f$ that is not a boundary arc of~$\surface$.
-For each arc~$a$ of~$\dissection$, the half-arcs incident to the middle of~$a$ in the two faces of~$\dissection$ containing~$a$ form the dual arc~$a\dual$ of~$a$.
-All these dual arcs do not cross (as the half-arcs do not cross in each face of~$\dissection$) and form the dual cellular dissection~$\dissection\dual$~of~$\dissection$.
+We construct half-edges of~$\dissection\dual$ in each face~$f$ of~$\dissection$ by joining the dual point~$f\dual$ to the middle of each boundary edge of~$f$ that is not a boundary edge of~$\surface$.
+For each edge~$a$ of~$\dissection$, the half-edges incident to the middle of~$a$ in the two faces of~$\dissection$ containing~$a$ form the dual edge~$a\dual$ of~$a$.
+All these dual edges do not cross (as the half-edges do not cross in each face of~$\dissection$) and form the dual cellular dissection~$\dissection\dual$~of~$\dissection$.
 \end{proof}
@@
 \subsection{Accordion complex, slalom complex, and non-crossing complex}
-Let~$\surface$ be a surface with two disjoint sets~$V$ and~$V\dual$ of marked points, let~$B$ be the corresponding blossoming points, and consider the marked surface~$\bar\surface = (\surface, V \sqcup V\dual \sqcup B)$.
-Consider two dual cellular dissections~$\dissection$ and~$\dissection\dual$ of~$\bar\surface = (\surface, V \sqcup V\dual)$.
+Let~$\bar\surface = (\surface, V \sqcup V\dual)$ be a surface with two disjoint sets~$V$ and~$V\dual$ of marked points, and let~$B$ be the corresponding blossom points.
+Consider two dual cellular dissections~$\dissection$ and~$\dissection\dual$ of~$\bar\surface$.
 %Let~$I$ denote the interior points and $B$ the blossom points.
@@
 \label{def:accordion}
-A \defn{$\dissection$-accordion} is a $B$-arc~$\gamma$ of~$\bar\surface$ such that whenever~$\gamma$ crosses a face~$f$ of~$\dissection$, it crosses two edges of~$f$ that share a marked point of~$v \in M$ in such a way that~$v$ and~$f\dual$ lie on opposite sides of~$\gamma$.
-
-% the two edges of~$f$ crossed by~$\gamma$ share a marked point~$v \in M$, and~$v$ and~$f\dual$ are on opposite sides of~$\gamma$ in~$f$.
-% any two arcs of $\dissection$ crossed consecutively by~$\gamma$ share a marked point with the property that the region bounded by~$\gamma$ and the two arcs around the marked point does not contain.
+A \defn{$\dissection$-accordion} is a $B$-arc~$\alpha$ of~$\bar\surface$ such that whenever~$\alpha$ crosses a face~$f$ of~$\dissection$,
+\begin{itemize}
+\item the two edges of~$f$ crossed by~$\alpha$ share a marked point~$v \in M$,
+\item the marked points~$v$ and~$f\dual$ lie on opposite sides of~$\alpha$ in~$f$
+\end{itemize}
 \end{definition}
@@
 \label{def:slalom}
-A \defn{$\dissection\dual$-slalom} is a $B$-arc~$\alpha$ of~$\bar\surface$ such that, for each pair of faces~$(f,g) \in \faces(\dissection\dual)$ that~$\alpha$ enters consecutively by crossing~$\beta\in\dissection\dual$,~$\alpha$ cuts the union of the two cells $f$ and $g$ glued along~$\beta$ into two components, one containing the marked point $f\dual$ and the other containing $g\dual$.
+A \defn{$\dissection\dual$-slalom} is a $B$-arc~$\alpha$ of~$\bar\surface$ such that, whenever~$\alpha$ crosses an edge~$a$ of~$\dissection$ contained in two faces~$f,g$ of~$\dissection$, the marked points~$f\dual$ and~$g\dual$ lie on opposite sides of~$\alpha$ in the union of~$f$ and~$g$ glued along~$a$.
 \end{definition}

### 2018-05-30 draft/accordionComplexSurfaces.tex
Definition of the bound quiver of a dissection.

--- 2018-05-30 draft/accordionComplexSurfaces.tex
@@
 \usepackage[T1]{fontenc}
-\usepackage{enumerate, amsmath, amsfonts, amssymb, amsthm, mathrsfs, wasysym, graphics, graphicx, xcolor, url, hyperref, hypcap, xargs, multicol, overpic, pdflscape, multirow, hvfloat, array, ae, aecompl, pifont, mathtools, a4wide}
+\usepackage{enumerate, amsmath, amsfonts, amssymb, amsthm, mathrsfs, wasysym, graphics, graphicx, xcolor, url, hyperref, hypcap, xargs, multicol, pdflscape, multirow, hvfloat, array, ae, aecompl, pifont, mathtools, a4wide}
 \usepackage{marginnote}
@@
 
-Let~$\surface$ be a surface with two sets~$M$ and~$M\dual$ of marked points and two dual cellular dissections~$\dissection$ and~$\dissection\dual$.
-Let~$I$ denote the interior points and $B$ the blossom points.
+Let~$\dissection$ and~$\dissection\dual$ be two dual cellular dissections of a marked surface~$(\surface, V\sqcup V\dual)$.
+Let $B$ be the set of blossom points.
 
@@
 \label{def:quiverDualDissections}
-The bound quiver of a dissection~$\dissection$ is defined rotating around each face of~$\dissection$.
-Define also the blossoming quiver of~$\dissection$.
-Note that boundary edges of~$\dissection$ get two blossoms.
+The bound quiver of the dissection~$\dissection$ is the bound quiver $\bar Q_{\dissection} = (Q_{\dissection}, I_{\dissection})$ defined as follows:
+\begin{itemize}
+ \item the set of vertices of~$Q_{\dissection}$ is the set or edges of $\dissection$;
+ \item there is an arrow from~$a$ to~$b$ for each common endpoint~$v$ of~$a$ and~$b$ such that~$b$ comes immediately after~$a$ in the clockwise order around~$v$;
+ \item the ideal~$I_{\dissection}$ is generated by the paths of length two in~$Q_{\dissection}$ obtained by composing arrows which correspond to triples of consecutive edges in a face of~$\dissection$.
+\end{itemize}
+The bound quiver of the dissection~$\dissection\dual$ is the bound quiver $\bar Q_{\dissection\dual} = (Q_{\dissection\dual}, I_{\dissection\dual})$ defined by replacing~$\dissection$ by~$\dissection\dual$ in the above.
 \end{definition}
+
+It is not hard to see that~$\bar Q_{\dissection} = (Q_{\dissection}, I_{\dissection})$ is a gentle bound quiver,
+and that the vertices corresponding to boundary edges of~$\dissection$ are blossoming vertices.
+\pierreguy{Be more precise on the ``are blossiming vertices'' part of this sentence.}
 

### 2018-05-30 draft/accordionComplexSurfaces.tex
reduced complexes

--- 2018-05-30 draft/accordionComplexSurfaces.tex
@@
 \renewcommandx{\AC}[1][1=\dissection]{\mathcal{K}_{\mathrm{acc}}(#1)} % accordion complex
+\newcommandx{\RAC}[1][1=\dissection]{\mathcal{C}_{\mathrm{acc}}(#1)} % reduced accordion complex
 \newcommandx{\SC}[1][1=\dissection\dual]{\mathcal{K}_{\mathrm{sla}}(#1)} % slalom complex
+\newcommandx{\RSC}[1][1=\dissection\dual]{\mathcal{C}_{\mathrm{sla}}(#1)} % reduced slalom complex
 \newcommandx{\NCC}[1][1={\dissection, \dissection\dual}]{\mathcal{K}_{\mathrm{nc}}(#1)} % non-crossing complex
+\newcommandx{\RNCC}[1][1={\dissection, \dissection\dual}]{\mathcal{C}_{\mathrm{nc}}(#1)} % non-crossing complex
 
@@
 The points of~$B$ are called the \defn{blossom points}.
-\vincent{I am tempted to define here the interior points and blossom points and to only consider arcs passing though these points. Still need to think about it.}
 \end{definition}
@@
 %Let~$I$ denote the interior points and $B$ the blossom points.
+We say that a $B$-arc is \defn{external} if it is homotopic to a boundary arc of~$\surface \ssm B$, and \defn{internal} otherwise.
+Note that no $B$-arc can cross an external $B$-arc.
 
@@
 The \defn{$\dissection$-accordion complex}~$\AC$ is the simplicial complex of pairwise non-crossing $\dissection$-accordions.
-\vincent{Reduced accordion complex.}
+The \defn{reduced $\dissection$-accordion complex}~$\RAC$ is the simplicial complex of pairwise non-crossing internal $\dissection$-accordions.
 \end{definition}
@@
 The \defn{$\dissection\dual$-slalom complex}~$\SC$ is the simplicial complex of pairwise non-crossing $\dissection$-slaloms.
-\vincent{Reduced slalom complex.}
+The \defn{reduced $\dissection\dual$-slalom complex}~$\RAC$ is the simplicial complex of pairwise non-crossing internal $\dissection\dual$-slaloms.
 \end{definition}
@@
 \label{prop:accordionsSlaloms}
-For two dual cellular dissections~$\dissection$ and~$\dissection\dual$, the $\dissection$-accordions are precisely the $\dissection\dual$-slaloms and the $\dissection$-accordion complex coincides with the $\dissection\dual$-slalom complex.
+For two dual cellular dissections~$\dissection$ and~$\dissection\dual$, the $\dissection$-accordions are precisely the $\dissection\dual$-slaloms and the (reduced) $\dissection$-accordion complex coincides with the (reduced) $\dissection\dual$-slalom complex.
 \end{proposition}
@@
 We call \defn{non-crossing complex} of the pair of dual cellular dissections~$(\dissection, \dissection\dual)$ the simplicial complex~$\NCC = \AC = \SC$.
+Similarly, the \defn{reduced non-crossing complex} of~$(\dissection, \dissection\dual)$ is~$\RNCC = \RAC = \RAC$.
 \end{definition}
@@
 \begin{remark}
-A quick disclaimer about accordion complexes and slalom complexes of arbitrary dissections, non-necessarily cellular.
+A quick disclaimer about accordion complexes and slalom complexes of arbitrary dissections.
 As stated in Proposition~\ref{prop:conditionsDualDissections}, a dissection~$\dissection$ with a face containing more than one boundary edge does not admit a dual cellular dissection~$\dissection\dual$.
@@
 See \cite[Prop.~2.4]{MannevillePilaud-accordion} for a detailed statement in the case of the disk.
+\vincent{A retravailler}
 \end{remark}

### 2018-05-30 draft/accordionComplexSurfaces.tex
Definition of Koszul dual.

--- 2018-05-30 draft/accordionComplexSurfaces.tex
@@
 \newcommand{\proj}{\operatorname{{\rm proj}}}
+\newcommand{\koszul}{^!} % duality
 
@@
 
+\begin{example}
+ An example on the annulus...
+\end{example}
+
+\begin{definition}
+\label{defi:koszulDual}
+The \defn{Koszul dual} of a gentle bound quiver~$\bar Q = (Q,I)$ is the bound quiver~$\bar Q\koszul = (Q\koszul, I\koszul)$ defined as follows:
+\begin{itemize}
+ \item the quiver~$Q\koszul$ is equal to~$Q$;
+ \item the ideal~$I\koszul$ is generated by the paths of length two in~$Q$ that do not appear in~$I$.
+\end{itemize}
+\end{definition}
+\pierreguy{Justify this definition.}
+Note that~$\bar Q\koszul$ is gentle, and that~$(\bar Q\koszul)\koszul = \bar Q$.
+
 \begin{proposition}
 \label{prop:dualityKoszul1}
-For two dual cellular dissections~$\dissection$ and~$\dissection\dual$ of an oriented surface, the quivers~$\bar Q_{\dissection}$ and~$\bar Q_{\dissection\dual}$ are Koszul duals.
-\vincent{Here I mean that the gentle algebras are Koszul duals. We need to define that somewhere and discuss it on gentle quivers.}
+Let~$\dissection$ and~$\dissection\dual$ be two dual cellular dissections of a marked surface~$(\surface, V\sqcup V\dual)$.
+The bound quivers~$\bar Q_{\dissection}$ and~$\bar Q_{\dissection\dual}$ are Koszul dual to each other.
 \end{proposition}

### 2018-06-04 draft/accordionComplexSurfaces.tex
Changed the definition of dissection.

@@
 
+We will always assume that collections of arcs on a surface are in minimal position, in the sense that they cross each other transversaly, and the number of crossings is minimal.
+This is always possible up to homotopy. \pierreguy{Reference?}
+With this assumption, each segment of a~$B$-arc that lies in a face~$f$ of the dissection~$\dissection$ has two intersection points (called crossings) with the edges of~$f$.
+Note that the edges of~$f$ may be on the boundary of the surface.
+
 \begin{definition}
@@
 \begin{itemize}
-\item the two edges of~$f$ crossed by~$\alpha$ share a marked point~$v \in M$,
-\item the marked points~$v$ and~$f\dual$ lie on opposite sides of~$\alpha$ in~$f$
+\item the two edges~$e_1$ and~$e_2$ of~$f$ crossed by~$\alpha$ are adjacent on the boundary of~$f$,
+\item there exists a marked points~$v$ shared by~$e_1$ and~$e_2$ such that~$v$ and~$f\dual$ lie on opposite sides of~$\alpha$ in~$f$.
 \end{itemize}

### 2018-06-06 draft/accordionComplexSurfaces.tex
minor changes

--- 2018-05-30 draft/accordionComplexSurfaces.tex
@@
 \newcommand{\proj}{\operatorname{{\rm proj}}}
-\newcommand{\koszul}{^!} % duality
 
@@
 We call \defn{non-crossing complex} of the pair of dual cellular dissections~$(\dissection, \dissection\dual)$ the simplicial complex~$\NCC = \AC = \SC$.
-Similarly, the \defn{reduced non-crossing complex} of~$(\dissection, \dissection\dual)$ is~$\RNCC = \RAC = \RAC$.
+Similarly, the \defn{reduced non-crossing complex} of~$(\dissection, \dissection\dual)$ is~$\RNCC = \RAC = \RSC$.
 \end{definition}
@@
 
-\begin{example}
- An example on the annulus...
-\end{example}
-
-\begin{definition}
-\label{defi:koszulDual}
-The \defn{Koszul dual} of a gentle bound quiver~$\bar Q = (Q,I)$ is the bound quiver~$\bar Q\koszul = (Q\koszul, I\koszul)$ defined as follows:
-\begin{itemize}
- \item the quiver~$Q\koszul$ is equal to~$Q$;
- \item the ideal~$I\koszul$ is generated by the paths of length two in~$Q$ that do not appear in~$I$.
-\end{itemize}
-\end{definition}
-\pierreguy{Justify this definition.}
-Note that~$\bar Q\koszul$ is gentle, and that~$(\bar Q\koszul)\koszul = \bar Q$.
-
 \begin{proposition}
 \label{prop:dualityKoszul1}
-Let~$\dissection$ and~$\dissection\dual$ be two dual cellular dissections of a marked surface~$(\surface, V\sqcup V\dual)$.
-The bound quivers~$\bar Q_{\dissection}$ and~$\bar Q_{\dissection\dual}$ are Koszul dual to each other.
+For two dual cellular dissections~$\dissection$ and~$\dissection\dual$ of an oriented surface, the quivers~$\bar Q_{\dissection}$ and~$\bar Q_{\dissection\dual}$ are Koszul duals.
+\vincent{Here I mean that the gentle algebras are Koszul duals. We need to define that somewhere and discuss it on gentle quivers.}
 \end{proposition}

### 2018-07-02 draft/accordionComplexSurfaces.tex
definition curve

--- 2018-06-04 draft/accordionComplexSurfaces.tex
@@
 Let~$\bar\surface = (\surface, V \sqcup V\dual)$ be a surface with two disjoint sets~$V$ and~$V\dual$ of marked points, and let~$B$ be the corresponding blossom points.
-Consider two dual cellular dissections~$\dissection$ and~$\dissection\dual$ of~$\bar\surface$.
+
+\begin{definition}
+A \defn{$B$-curve} is a curve on~$\surface$ which at each end either reaches a point of~$B$ or infinitely circles around and finally reaches a puncture of~$V \sqcup V\dual$.
+Curves are considered up to homotopy relative to their endpoints in~$\surface \ssm (B \sqcup V \sqcup V\dual)$, and curves homotopic to a boundary are not allowed.
+\end{definition}
+
 %Let~$I$ denote the interior points and $B$ the blossom points.
@@
 Note that no $B$-arc can cross an external $B$-arc.
+Consider two dual cellular dissections~$\dissection$ and~$\dissection\dual$ of~$\bar\surface$.
 
@@
 \item the two edges~$e_1$ and~$e_2$ of~$f$ crossed by~$\alpha$ are adjacent on the boundary of~$f$,
-\item there exists a marked points~$v$ shared by~$e_1$ and~$e_2$ such that~$v$ and~$f\dual$ lie on opposite sides of~$\alpha$ in~$f$.
+\item $\alpha$, $e_1$ and~$e_2$ bound a disk inside~$f$ that does not contain~$f\dual{}$.
 \end{itemize}
 \end{definition}
+
+\begin{remark}
+In Definition~\ref{def:accordion}, observe that
+\begin{itemize}
+\item the edges of~$e_1$ and~$e_2$ of~$f$ crossed by~$\alpha$ might coincide, see ...
+\item the second condition is automatically satisfied if~$f\dual$ is not a puncture.
+\end{itemize}
+\end{remark}
 

### 2018-07-02 draft/accordionComplexSurfaces.tex
definition curve

@@
 A \defn{marked surface}~$\bar\surface \eqdef (\surface, M)$ is an orientable surface~$\surface$ with boundaries, together with a set~$M$ of marked points which can be on the boundary of~$\surface$ or not.
-For~$V \subset \surface$, a \defn{$V$-arc} on~$\bar\surface$ is a curve on~$\surface$ connecting two points of~$V$ and whose interior is disjoint from~$M$ and the boundary of~$\surface$.
-As usual, arcs are considered up to homotopy relative to their endpoints in~$\surface \ssm M$, and curves homotopic to a boundary are not allowed.
-Two arcs \defn{cross} when they intersect in~their~interior.
+For~$V \subset \surface$,
+\begin{itemize}
+\item a \defn{$V$-arc} on~$\bar\surface$ is a curve on~$\surface$ connecting two points of~$V$ and whose interior is disjoint from~$M$ and the boundary of~$\surface$.
+\item a \defn{$V$-curve} on~$\bar\surface$ is a curve on~$\surface$ which at each end either reaches a point of~$V$ or infinitely circles around and finally reaches a puncture of~$M$.
+\end{itemize}
+As usual, curves and arcs are considered up to homotopy relative to their endpoints in~$\surface \ssm M$, and curves homotopic to a boundary are not allowed.
+\end{definition}
+
+\begin{definition}
+Two curves or arcs \defn{cross} when they intersect in~their~interior.
+We will always assume that collections of arcs on a surface are in minimal position, in the sense that they cross each other transversaly, and the number of crossings is minimal.
+This is always possible up to homotopy. \pierreguy{Reference?}
 \end{definition}
@@
 Let~$\bar\surface = (\surface, V \sqcup V\dual)$ be a surface with two disjoint sets~$V$ and~$V\dual$ of marked points, and let~$B$ be the corresponding blossom points.
-
-\begin{definition}
-A \defn{$B$-curve} is a curve on~$\surface$ which at each end either reaches a point of~$B$ or infinitely circles around and finally reaches a puncture of~$V \sqcup V\dual$.
-Curves are considered up to homotopy relative to their endpoints in~$\surface \ssm (B \sqcup V \sqcup V\dual)$, and curves homotopic to a boundary are not allowed.
-\end{definition}
-
+%
+%\begin{definition}
+%A \defn{$B$-curve} is a curve on~$\surface$ which at each end either reaches a point of~$B$ or infinitely circles around and finally reaches a puncture of~$V \sqcup V\dual$.
+%Curves are considered up to homotopy relative to their endpoints in~$\surface \ssm (B \sqcup V \sqcup V\dual)$, and curves homotopic to a boundary are not allowed.
+%\end{definition}
+%
 %Let~$I$ denote the interior points and $B$ the blossom points.
-We say that a $B$-arc is \defn{external} if it is homotopic to a boundary arc of~$\surface \ssm B$, and \defn{internal} otherwise.
-Note that no $B$-arc can cross an external $B$-arc.
+We say that a $B$-curve is \defn{external} if it is homotopic to a boundary arc of~$\surface \ssm B$, and \defn{internal} otherwise.
+Note that no $B$-curve can cross an external $B$-arc.
 Consider two dual cellular dissections~$\dissection$ and~$\dissection\dual$ of~$\bar\surface$.
 
-We will always assume that collections of arcs on a surface are in minimal position, in the sense that they cross each other transversaly, and the number of crossings is minimal.
-This is always possible up to homotopy. \pierreguy{Reference?}
-With this assumption, each segment of a~$B$-arc that lies in a face~$f$ of the dissection~$\dissection$ has two intersection points (called crossings) with the edges of~$f$.
-Note that the edges of~$f$ may be on the boundary of the surface.
+%With this assumption, each segment of a~$B$-arc that lies in a face~$f$ of the dissection~$\dissection$ has two intersection points (called crossings) with the edges of~$f$.
+%Note that the edges of~$f$ may be on the boundary of the surface.
 
@@
 \label{def:accordion}
-A \defn{$\dissection$-accordion} is a $B$-arc~$\alpha$ of~$\bar\surface$ such that whenever~$\alpha$ crosses a face~$f$ of~$\dissection$,
+A \defn{$\dissection$-accordion} is a $B$-curve~$\alpha$ of~$\bar\surface$ such that whenever~$\alpha$ meets a face~$f$~of~$\dissection$,
 \begin{itemize}
+\item it enters crossing an edge~$e_1$ and leaves crossing an edge~$e_2$ (in other words, $\alpha$ is not allowed to circle around~$f\dual$ when~$f\dual$ is a puncture),
 \item the two edges~$e_1$ and~$e_2$ of~$f$ crossed by~$\alpha$ are adjacent on the boundary of~$f$,

### 2018-07-02 draft/accordionComplexSurfaces.tex
definition slalom

@@
 \label{def:slalom}
-A \defn{$\dissection\dual$-slalom} is a $B$-arc~$\alpha$ of~$\bar\surface$ such that, whenever~$\alpha$ crosses an edge~$a$ of~$\dissection$ contained in two faces~$f,g$ of~$\dissection$, the marked points~$f\dual$ and~$g\dual$ lie on opposite sides of~$\alpha$ in the union of~$f$ and~$g$ glued along~$a$.
+A \defn{$\dissection\dual$-slalom} is a $B$-curve~$\alpha$ of~$\bar\surface$ such that, whenever~$\alpha$ crosses an edge~$a$ of~$\dissection$ contained in two faces~$f,g$ of~$\dissection$, the marked points~$f\dual$ and~$g\dual$ lie on opposite sides of~$\alpha$ in the union of~$f$ and~$g$ glued along~$a$.
+Here, we consider that~$f\dual$ lies on the right (resp.~left) of~$\alpha$ when~$\alpha$ circles clockwise (resp.~counterclockwise) around~$f\dual$.
 \end{definition}

### 2018-07-02 draft/accordionComplexSurfaces.tex
ajout d'un cas dans la demo accoreons = slalom\dual
general walks

@@
 
-We consider a \defn{bound quiver}~$\bar Q = (Q,I)$, formed by a quiver~$Q$ and an admissible ideal~$I$ of the path algebra~$kQ$, so that the quotient algebra~$kQ/I$ is finite dimensional.
+%We consider a \defn{bound quiver}~$\bar Q = (Q,I)$, formed by a quiver~$Q$ and an admissible ideal~$I$ of the path algebra~$kQ$, so that the quotient algebra~$kQ/I$ is finite dimensional.
+We consider a \defn{bound quiver}~$\bar Q = (Q,I)$, formed by a quiver~$Q$ and an admissible ideal~$I$ of the path algebra~$kQ$.
+Note that we \textbf{do not require} that the quotient algebra~$kQ/I$ be finite dimensional.
 
@@
 \label{def:walk}
-A \defn{walk} of a gentle quiver~$\bar Q$ is a maximal string of its blossoming quiver~$\bar Q \blossom$ (thus joining two blossom vertices of~$\bar Q \blossom$).
+A \defn{walk} of a gentle quiver~$\bar Q$ is a maximal string of its blossoming quiver~$\bar Q \blossom$, meaning that at each end it either reaches a blossom vertex of~$\bar Q \blossom$ or enters an infinite cycle.
 We denote by~$\walks(\bar Q)$ the set of all walks on~$\bar Q$.
@@
 \item it enters crossing an edge~$e_1$ and leaves crossing an edge~$e_2$ (in other words, $\alpha$ is not allowed to circle around~$f\dual$ when~$f\dual$ is a puncture),
-\item the two edges~$e_1$ and~$e_2$ of~$f$ crossed by~$\alpha$ are adjacent on the boundary of~$f$,
+\item the two edges~$e_1$ and~$e_2$ of~$f$ crossed by~$\alpha$ are consecutive on the boundary of~$f$,
 \item $\alpha$, $e_1$ and~$e_2$ bound a disk inside~$f$ that does not contain~$f\dual{}$.
@@
 Namely, any pair of dual cellular dissections~$(\dissection, \dissection\dual)$ defines a gentle bound quiver~$\bar Q_{\dissection, \dissection\dual}$ such that the non-crossing complex~$\NCC$ is isomorphic to the non-kissing complex~$\NKC[\bar Q_{\dissection, \dissection\dual}]$.
-Conversely, any gentle bound quiver~$\bar Q$ gives rise to a surface~$\surface_{\bar Q}$ equipped with a pair of dual cellular dissections~$\dissection_{\bar Q}$ and~$\dissection\dual_{\bar Q}$ such that the non-kissing complex~$\NKC$ is isomorphic to the non-crossing complex~$\NCC[\dissection_{\bar Q}, \dissection\dual_{\bar Q}]$.
+Conversely, any gentle bound quiver~$\bar Q$ gives rise to a surface~$\surface_{\bar Q}$ equipped with a pair of dual cellular dissections~$\dissection_{\bar Q}$ and~${\dissection_{\bar Q}}\dual$ such that the non-kissing complex~$\NKC$ is isomorphic to the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$.
 In fact, we show that the accordion, slalom, and non-kissing complexes can all be pictured in a unique way on the surface.
@@
 The surface~$\surface(\bar Q)$ of a gentle bound quiver~$\bar Q = (Q,I)$ is obtained by glueing lozanges around arrows of~$Q$ following the rule given by the relations~$I$.
-The construction also automatically defines two dual cellular dissections~$\dissection_{\bar Q}$ and~$\dissection\dual_{\bar Q}$ of the surface~$\surface_{\bar Q}$.
+The construction also automatically defines two dual cellular dissections~$\dissection_{\bar Q}$ and~${\dissection_{\bar Q}}\dual$ of the surface~$\surface_{\bar Q}$.
 \end{definition}
@@
 \label{prop:dualityKoszul2}
-For any gentle bound quiver~$\bar Q$ with Koszul dual~$\bar Q\dual$, the surfaces~$\surface_{\bar Q}$ and~$\surface_{\bar Q\dual}$ coincide, but~$\dissection_{\bar Q\dual} = \dissection\dual_{\bar Q}$ and~$\dissection\dual_{\bar Q\dual} = \dissection_{\bar Q}$.
+For any gentle bound quiver~$\bar Q$ with Koszul dual~$\bar Q\koszul$, the surfaces~$\surface_{\bar Q}$ and~$\surface_{\bar Q\koszul}$ coincide, but~$\dissection_{\bar Q\koszul} = {\dissection_{\bar Q}}\dual$ and~${\dissection_{\bar Q\koszul}}\dual = \dissection_{\bar Q}$.
 \end{proposition}
 
-\subsection{Accordion, slalom and non-kissing complexe coincide}
+\subsection{Non-crossing and non-kissing complexe coincide}
 
@@
 \label{lem:nonKissing=nonCrossing}
-Non-kissing walks = non-crossing arcs.
+Non-kissing walks = non-crossing $\dissection$-accordion curves = non-crossing $\dissection\dual$-slalom curves.
 \end{lemma}
@@
 \begin{itemize}
-\item For any gentle bound quiver~$\bar Q$, the non-kissing complex~$\NKC$ is isomorphic to the non-crossing complex~$\NCC[\dissection_{\bar Q}, \dissection\dual_{\bar Q}]$, therefore to the accordion complex~$\AC[\dissection_{\bar Q}]$ and to the slalom complex~$\SC[\dissection\dual_{\bar Q}]$.
+\item For any gentle bound quiver~$\bar Q$, the non-kissing complex~$\NKC$ is isomorphic to the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$, therefore to the accordion complex~$\AC[\dissection_{\bar Q}]$ and to the slalom complex~$\SC[{\dissection_{\bar Q}}\dual]$.
 \item For any pair of dual cellular dissections~$\dissection, \dissection\dual$ of an oriented surface, the non-crossing complex~$\NCC$ is isomorphic to the non-kissing complex~$\NKC[\bar Q_{\dissection, \dissection\dual}]$.
@@
 \end{theorem}
+
+\section{Pseudomanifolds}
+
+In this section, we show that the non-crossing and non-kissing complexes are \defn{pseudomanifold}, \ie that there are
+\begin{enumerate}[(i)]
+\item \defn{pure}: all maximal $\dissection$-accordion simplices have the same number of $B$-curves as~$\dissection$, and
+\item \defn{thin}: any codimension~$1$ simplex of~$\AC$ is contained in exactly two maximal $\dissection$-accordion simplices.
+\end{enumerate}
+
+\vincent{Peut-on utiliser une projection d'une alg\`ebre ammass\'ee ? Apparement non... On peut avoir le Koszul dual d'une alg\`ebre ammass\'ee.}
 

### 2018-07-02 draft/accordionComplexSurfaces.tex
Gentle has been replaced by locally gentle.

@@
 
-\title[Non-kissing and non-crossing complexes for gentle algebras]{Non-kissing and non-crossing complexes \\ for gentle algebras}
+\title[Non-kissing and non-crossing complexes for locally gentle algebras]{Non-kissing and non-crossing complexes \\ for locally gentle algebras}
 
@@
 \begin{abstract}
-We consider three combinatorial models for the support $\tau$-tilting complex of a gentle bound quiver: the accordion complex, the slalom complex, and the non-kissing complex.
+We consider three combinatorial models for the support $\tau$-tilting complex of a locally gentle bound quiver: the accordion complex, the slalom complex, and the non-kissing complex.
 We unify these models in the same picture.
@@
 
-\subsection{Gentle bound quivers and their blossoming quivers}
+\subsection{Locally gentle bound quivers and their blossoming quivers}
 
 %We consider a \defn{bound quiver}~$\bar Q = (Q,I)$, formed by a quiver~$Q$ and an admissible ideal~$I$ of the path algebra~$kQ$, so that the quotient algebra~$kQ/I$ is finite dimensional.
-We consider a \defn{bound quiver}~$\bar Q = (Q,I)$, formed by a quiver~$Q$ and an admissible ideal~$I$ of the path algebra~$kQ$.
+We consider a \defn{bound quiver}~$\bar Q = (Q,I)$, formed by a quiver~$Q$ and an ideal~$I$ of the path algebra~$kQ$ such that $I$ is generated by linear combinations of paths of length at least two.
 Note that we \textbf{do not require} that the quotient algebra~$kQ/I$ be finite dimensional.
@@
 \label{def:gentleQuiver}
-A \defn{gentle bound quiver}~$\bar Q \eqdef (Q,I)$ is a bound quiver such that
+A \defn{locally gentle bound quiver}~$\bar Q \eqdef (Q,I)$ is a bound quiver such that
 \begin{itemize}
@@
 \end{itemize}
-The algebra~$kQ/I$ is called a \defn{gentle algebra}.
+The algebra~$kQ/I$ is called a \defn{locally gentle algebra}.
+A \defn{gentle bound quiver} is a locally bound quiver~$\bar Q$ such that the algebra $kQ/I$ is finite-dimensional; the algebra is then called a \defn{gentle algebra}.
 \end{definition}
@@
 \label{def:blossomingQuiver}
-A gentle bound quiver~$\bar Q$ is \defn{complete} if any vertex~$v \in Q_0$ is incident to either one ($v$ is a leaf) or four arrows ($v$ is an internal vertex).
-The \defn{pruned subquiver} of a quiver $\bar Q$ is the gentle quiver obtained by deleting all leaves of~$\bar Q$ (degree one vertices) and their incident arrows.
-The \defn{blossoming quiver} of a gentle bound quiver~$\bar Q$ is the complete gentle bound quiver~$\bar Q\blossom$ whose pruned subquiver is~$\bar Q$.
+A locally gentle bound quiver~$\bar Q$ is \defn{complete} if any vertex~$v \in Q_0$ is incident to either one ($v$ is a leaf) or four arrows ($v$ is an internal vertex).
+The \defn{pruned subquiver} of a quiver $\bar Q$ is the locally gentle quiver obtained by deleting all leaves of~$\bar Q$ (degree one vertices) and their incident arrows.
+The \defn{blossoming quiver} of a locally gentle bound quiver~$\bar Q$ is the complete locally gentle bound quiver~$\bar Q\blossom$ whose pruned subquiver is~$\bar Q$.
 The vertices of~$Q\blossom_0 \ssm Q_0$ are called \defn{blossom vertices}, and the arrows~$Q\blossom_1 \ssm Q_1$ are called \defn{blossom arrows}.
@@
 \label{def:string}
-Let~$\bar Q = (Q,I)$ be a gentle bound quiver.
+Let~$\bar Q = (Q,I)$ be a locally gentle bound quiver.
 A \defn{string} for~$\bar Q$ is a word of the form
@@
 \label{def:walk}
-A \defn{walk} of a gentle quiver~$\bar Q$ is a maximal string of its blossoming quiver~$\bar Q \blossom$, meaning that at each end it either reaches a blossom vertex of~$\bar Q \blossom$ or enters an infinite cycle.
+A \defn{walk} of a locally gentle quiver~$\bar Q$ is a maximal string of its blossoming quiver~$\bar Q \blossom$, meaning that at each end it either reaches a blossom vertex of~$\bar Q \blossom$ or enters an infinite cycle.
 We denote by~$\walks(\bar Q)$ the set of all walks on~$\bar Q$.
@@
 This contradicts the assumption that the dissections~$\dissection$ and~$\dissection\dual$ are dual to each other.
+
+Case 4: If $\alpha$ stays inside a blue cell, then it rolls around a $\dissection\dual$ puncture.
+There is a $\dissection\dual$-arc $\beta$ ending in that puncture.
+When $\alpha$ crosses $\beta$, the puncture stays on the same side of $\alpha$, hence $\alpha$ is not a $\dissection\dual$-slalom.
 \end{proof}
@@
 In this section, we show that non-kissing complexes and non-crossing complexes actually coincide.
-Namely, any pair of dual cellular dissections~$(\dissection, \dissection\dual)$ defines a gentle bound quiver~$\bar Q_{\dissection, \dissection\dual}$ such that the non-crossing complex~$\NCC$ is isomorphic to the non-kissing complex~$\NKC[\bar Q_{\dissection, \dissection\dual}]$.
-Conversely, any gentle bound quiver~$\bar Q$ gives rise to a surface~$\surface_{\bar Q}$ equipped with a pair of dual cellular dissections~$\dissection_{\bar Q}$ and~${\dissection_{\bar Q}}\dual$ such that the non-kissing complex~$\NKC$ is isomorphic to the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$.
+Namely, any pair of dual cellular dissections~$(\dissection, \dissection\dual)$ defines a locally gentle bound quiver~$\bar Q_{\dissection, \dissection\dual}$ such that the non-crossing complex~$\NCC$ is isomorphic to the non-kissing complex~$\NKC[\bar Q_{\dissection, \dissection\dual}]$.
+Conversely, any locally gentle bound quiver~$\bar Q$ gives rise to a surface~$\surface_{\bar Q}$ equipped with a pair of dual cellular dissections~$\dissection_{\bar Q}$ and~${\dissection_{\bar Q}}\dual$ such that the non-kissing complex~$\NKC$ is isomorphic to the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$.
 In fact, we show that the accordion, slalom, and non-kissing complexes can all be pictured in a unique way on the surface.
-Interestingly, via the correspondence between pairs of dual cellular dissections and gentle bound quivers, the duality between the dissections~$\dissection$ and~$\dissection\dual$ translates to the Koszul duality between the gentle algebras of~$\bar Q$ and~$\bar Q\dual$.
+Interestingly, via the correspondence between pairs of dual cellular dissections and locally gentle bound quivers, the duality between the dissections~$\dissection$ and~$\dissection\dual$ translates to the Koszul duality between the locally gentle algebras of~$\bar Q$ and~$\bar Q\dual$.
 
@@
 
-It is not hard to see that~$\bar Q_{\dissection} = (Q_{\dissection}, I_{\dissection})$ is a gentle bound quiver,
+It is not hard to see that~$\bar Q_{\dissection} = (Q_{\dissection}, I_{\dissection})$ is a locally gentle bound quiver,
 and that the vertices corresponding to boundary edges of~$\dissection$ are blossoming vertices.
@@
 \label{defi:koszulDual}
-The \defn{Koszul dual} of a gentle bound quiver~$\bar Q = (Q,I)$ is the bound quiver~$\bar Q\koszul = (Q\koszul, I\koszul)$ defined as follows:
+The \defn{Koszul dual} of a locally gentle bound quiver~$\bar Q = (Q,I)$ is the bound quiver~$\bar Q\koszul = (Q\koszul, I\koszul)$ defined as follows:
 \begin{itemize}
@@
 \label{def:surfaceQuiver}
-The surface~$\surface(\bar Q)$ of a gentle bound quiver~$\bar Q = (Q,I)$ is obtained by glueing lozanges around arrows of~$Q$ following the rule given by the relations~$I$.
+The surface~$\surface(\bar Q)$ of a locally gentle bound quiver~$\bar Q = (Q,I)$ is obtained by glueing lozanges around arrows of~$Q$ following the rule given by the relations~$I$.
 The construction also automatically defines two dual cellular dissections~$\dissection_{\bar Q}$ and~${\dissection_{\bar Q}}\dual$ of the surface~$\surface_{\bar Q}$.
@@
 \begin{itemize}
-\item For any gentle bound quiver~$\bar Q$, the non-kissing complex~$\NKC$ is isomorphic to the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$, therefore to the accordion complex~$\AC[\dissection_{\bar Q}]$ and to the slalom complex~$\SC[{\dissection_{\bar Q}}\dual]$.
+\item For any locally gentle bound quiver~$\bar Q$, the non-kissing complex~$\NKC$ is isomorphic to the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$, therefore to the accordion complex~$\AC[\dissection_{\bar Q}]$ and to the slalom complex~$\SC[{\dissection_{\bar Q}}\dual]$.
 \item For any pair of dual cellular dissections~$\dissection, \dissection\dual$ of an oriented surface, the non-crossing complex~$\NCC$ is isomorphic to the non-kissing complex~$\NKC[\bar Q_{\dissection, \dissection\dual}]$.

### 2018-07-02 draft/accordionComplexSurfaces.tex
blabla proof pseudomanifold

--- 2018-07-02 draft/accordionComplexSurfaces.tex
@@
 
-\begin{theorem}[{\cite[Cor.~2.27 \& Cor.~2.33]{PaluPilaudPlamondon}}]
+\begin{theorem}[{\cite[Cor.~2.27 \& Cor.~2.33]{PaluPilaudPlamondon}}\footnote{As the main objective of~\cite[Cor.~2.27 \& Cor.~2.33]{PaluPilaudPlamondon} was a combinatorial model for support $\tau$-tilting complexes of gentle algebras, we did require that the ideal~$I$ was admissible so that~$kQ/I$ was finite dimensional.
+However, the same proof directly applies in the generality of this paper.}]
 The reduced non-kissing complex~$\RNKC$ is pure of dimension~$|Q_0|$ (\ie all maximal faces have dimension~$|Q_0|$) and thin (\ie all codimension~$1$ faces are contained in exactly two facets).
@@
 
-In this section, we show that the non-crossing and non-kissing complexes are \defn{pseudomanifold}, \ie that there are
+In this section, we show that the non-kissing complex is a \defn{pseudomanifold},~\ie
 \begin{enumerate}[(i)]
-\item \defn{pure}: all maximal $\dissection$-accordion simplices have the same number of $B$-curves as~$\dissection$, and
-\item \defn{thin}: any codimension~$1$ simplex of~$\AC$ is contained in exactly two maximal $\dissection$-accordion simplices.
+\item \defn{pure}: all maximal non-kissing simplices have the same number of walks as~$\dissection$, and
+\item \defn{thin}: any codimension~$1$ simplex of~$\NKC$ is contained in exactly two maximal non-kissing simplices.
 \end{enumerate}

### 2018-07-02 draft/accordionComplexSurfaces.tex
added proof Koszul dual

--- 2018-07-02 draft/accordionComplexSurfaces.tex
@@
 
-\begin{theorem}[{\cite[Cor.~2.27 \& Cor.~2.33]{PaluPilaudPlamondon}}\footnote{As the main objective of~\cite[Cor.~2.27 \& Cor.~2.33]{PaluPilaudPlamondon} was a combinatorial model for support $\tau$-tilting complexes of gentle algebras, we did require that the ideal~$I$ was admissible so that~$kQ/I$ was finite dimensional.
-However, the same proof directly applies in the generality of this paper.}]
+\begin{theorem}[{\cite[Cor.~2.27 \& Cor.~2.33]{PaluPilaudPlamondon}}]
 The reduced non-kissing complex~$\RNKC$ is pure of dimension~$|Q_0|$ (\ie all maximal faces have dimension~$|Q_0|$) and thin (\ie all codimension~$1$ faces are contained in exactly two facets).
@@
 
+\begin{proof}
+ The duality gives a bijection~$v\in (Q_\dissection)_0\mapsto v\dual\in (Q_{\dissection\dual})_0$, and induces a bijection~$\alpha\in (Q_\dissection)_1\mapsto \alpha\dual\in (Q_{\dissection\dual})_1$ with~$s(\alpha\dual)=s(\alpha)\dual$ and~$t(\alpha\dual)=t(\alpha)\dual$.
+ Moreover, for any two composable arrows~$\alpha,\beta\in(Q_\dissection)_0$, we have~$\alpha\beta\in I_\dissection$ if and only if~$s(\alpha),t(\alpha),t(\beta)$ are three consecutive edges of a~$\dissection$-cell~$f$, if and only if~$s(\alpha)\dual,t(\alpha)\dual,t(\beta)\dual$ are three consecutive arcs in~$\dissection\dual$ ending in~$f\dual$, if and only if~$\beta\dual\alpha\dual\notin I_{\dissection\dual}$.
+\end{proof}
+
 \subsection{The surface of a quiver}
@@
 
-In this section, we show that the non-kissing complex is a \defn{pseudomanifold},~\ie
+In this section, we show that the non-crossing and non-kissing complexes are \defn{pseudomanifold}, \ie that there are
 \begin{enumerate}[(i)]
-\item \defn{pure}: all maximal non-kissing simplices have the same number of walks as~$\dissection$, and
-\item \defn{thin}: any codimension~$1$ simplex of~$\NKC$ is contained in exactly two maximal non-kissing simplices.
+\item \defn{pure}: all maximal $\dissection$-accordion simplices have the same number of $B$-curves as~$\dissection$, and
+\item \defn{thin}: any codimension~$1$ simplex of~$\AC$ is contained in exactly two maximal $\dissection$-accordion simplices.
 \end{enumerate}

### 2018-07-02 draft/accordionComplexSurfaces.tex
minor modif

@@
 
-Case 4: If $\alpha$ stays inside a blue cell, then it rolls around a $\dissection\dual$ puncture.
-There is a $\dissection\dual$-arc $\beta$ ending in that puncture.
-When $\alpha$ crosses $\beta$, the puncture stays on the same side of $\alpha$, hence $\alpha$ is not a $\dissection\dual$-slalom.
+Case 4: If~$\alpha$ stays inside a blue cell, then it rolls around a~$\dissection\dual$ puncture.
+There is a~$\dissection\dual$-arc~$\beta$ ending in that puncture. When~$\alpha$ crosses~$\beta$, the puncture stays on the same side of~$\alpha$, hence~$\alpha$ is not a~$\dissection\dual$-slalom.
 \end{proof}
@@
 \label{lem:walks=arcs}
-Walks of $\bar Q$ are precisely arcs between blossom points.
+Walks of~$\bar Q$ are precisely~$\dissection$ accordions.
 \end{lemma}
@@
 \label{lem:nonKissing=nonCrossing}
-Non-kissing walks = non-crossing $\dissection$-accordion curves = non-crossing $\dissection\dual$-slalom curves.
+Non-kissing walks = non-crossing $\dissection$-accordion curves.
 \end{lemma}

### 2018-07-02 draft/accordionComplexSurfaces.tex
Outline of section on representations
surface

--- 2018-07-02 draft/accordionComplexSurfaces.tex
@@
 %\newcommand{\cta}{\mathsf{cta}} % cotarget
+\newcommand{\Enrs}[1]{E_{nr}^{s}(#1)}
+\newcommand{\Ers}[1]{E_{r}^{s}(#1)}
+\newcommand{\Enrt}[1]{E_{nr}^{t}(#1)}
+\newcommand{\Ert}[1]{E_{r}^{t}(#1)}
 
@@
 \end{itemize}
+By convention, we also consider that the punctures of~$V\dual$ are $\dissection$-accordions.
 \end{definition}
@@
 Here, we consider that~$f\dual$ lies on the right (resp.~left) of~$\alpha$ when~$\alpha$ circles clockwise (resp.~counterclockwise) around~$f\dual$.
+By convention, we also consider that the punctures of~$V$ are $\dissection\dual$-slaloms.
 \end{definition}
@@
 \pierreguy{Be more precise on the ``are blossiming vertices'' part of this sentence.}
+\vincent{Explain also that we can get the blossoming quiver using the blossom points.}
 
@@
 
-\begin{proof}
- The duality gives a bijection~$v\in (Q_\dissection)_0\mapsto v\dual\in (Q_{\dissection\dual})_0$, and induces a bijection~$\alpha\in (Q_\dissection)_1\mapsto \alpha\dual\in (Q_{\dissection\dual})_1$ with~$s(\alpha\dual)=s(\alpha)\dual$ and~$t(\alpha\dual)=t(\alpha)\dual$.
- Moreover, for any two composable arrows~$\alpha,\beta\in(Q_\dissection)_0$, we have~$\alpha\beta\in I_\dissection$ if and only if~$s(\alpha),t(\alpha),t(\beta)$ are three consecutive edges of a~$\dissection$-cell~$f$, if and only if~$s(\alpha)\dual,t(\alpha)\dual,t(\beta)\dual$ are three consecutive arcs in~$\dissection\dual$ ending in~$f\dual$, if and only if~$\beta\dual\alpha\dual\notin I_{\dissection\dual}$.
-\end{proof}
+\subsection{The surface of a quiver}
 
-\subsection{The surface of a quiver}
+We now associate a surface to a locally gentle bound quiver.
 
@@
 \label{def:surfaceQuiver}
-The surface~$\surface(\bar Q)$ of a locally gentle bound quiver~$\bar Q = (Q,I)$ is obtained by glueing lozanges around arrows of~$Q$ following the rule given by the relations~$I$.
+The surface~$\surface(\bar Q)$ of a locally gentle bound quiver~$\bar Q = (Q,I)$ is the orientable surface obtained from the blossoming quiver~$\bar Q\blossom$ as follows:
+\begin{itemize}
+\item for each arrow~$\alpha \in Q_1\blossom$, consider a lozange~$L(\alpha)$ with four (oriented) sides~$\Enrs{\alpha} = [s(\alpha), v]$, $\Enrt{\alpha} = [v, t(\alpha)]$ (colored green) and~$\Ers{\alpha} = [s(\alpha), v\dual]$ and~$\Ert{\alpha} = [v\dual, t(\alpha)]$ (colored red) as follows:
+\vincent{Figure}
+\item for any~$\alpha, \beta \in Q_1\blossom$ with~$t(\alpha) = s(\alpha)$, proceed to the following identifications:
+    \begin{itemize}
+    \item if~$\alpha\beta \in I$, then glue~$\Ert{\alpha}$ with~$\Ers{\beta}$,
+    \item if~$\alpha\beta \notin I$, then glue~$\Enrt{\alpha}$ with~$\Enrs{\beta}$.
+    \end{itemize}
+\end{itemize}
 The construction also automatically defines two dual cellular dissections~$\dissection_{\bar Q}$ and~${\dissection_{\bar Q}}\dual$ of the surface~$\surface_{\bar Q}$.
 \end{definition}
+
+\begin{example}
+\vincent{TODO.}
+\end{example}
 
@@
 
-\section{Pseudomanifolds}
-
-In this section, we show that the non-kissing complex is a \defn{pseudomanifold},~\ie
-\begin{enumerate}[(i)]
-\item \defn{pure}: all maximal non-kissing simplices have the same number of walks as~$\dissection$, and
-\item \defn{thin}: any codimension~$1$ simplex of~$\NKC$ is contained in exactly two maximal non-kissing simplices.
-\end{enumerate}
-
-\vincent{Peut-on utiliser une projection d'une alg\`ebre ammass\'ee ? Apparement non... On peut avoir le Koszul dual d'une alg\`ebre ammass\'ee.}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-07-02 draft/accordionComplexSurfaces.tex

@@
 
+\section{Representation-theoretic interpretation}
+
+\subsection{$\dissection$-accordions and string modules}
+
+\subsection{$\dissection\dual$-slaloms and minimal projective presentations}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-07-02 draft/accordionComplexSurfaces.tex
midor edits
dissections of a quiver

@@
 \label{def:surfaceQuiver}
-The surface~$\surface(\bar Q)$ of a locally gentle bound quiver~$\bar Q = (Q,I)$ is the orientable surface obtained from the blossoming quiver~$\bar Q\blossom$ as follows:
-\begin{itemize}
-\item for each arrow~$\alpha \in Q_1\blossom$, consider a lozange~$L(\alpha)$ with four (oriented) sides~$\Enrs{\alpha} = [s(\alpha), v]$, $\Enrt{\alpha} = [v, t(\alpha)]$ (colored green) and~$\Ers{\alpha} = [s(\alpha), v\dual]$ and~$\Ert{\alpha} = [v\dual, t(\alpha)]$ (colored red) as follows:
+The surface~$\surface(\bar Q)$ of a locally gentle bound quiver~$\bar Q = (Q,I)$ is the surface obtained from the blossoming quiver~$\bar Q\blossom$ as follows:
+\begin{enumerate}[(i)]
+\item for each arrow~$\alpha \in Q_1\blossom$, consider a lozange~$L(\alpha)$ with four (oriented) sides~$\Enrs{\alpha} = [s(\alpha), v(\alpha)]$, $\Enrt{\alpha} = [v(\alpha), t(\alpha)]$ (colored green) and~$\Ers{\alpha} = [s(\alpha), v\dual(\alpha)]$ and~$\Ert{\alpha} = [v\dual(\alpha), t(\alpha)]$ (colored red) as follows:
 \vincent{Figure}
@@
     \end{itemize}
+\end{enumerate}
+This defines an orientable surface~$\surface(\bar Q)$ with boundaries, endowed with two disjoint sets~$V_{\bar Q}$ and~$V\dual_{\bar Q}$ of marked points and two dual dissections~$\dissection_{\bar Q}$ and~$\dissection\dual_{\bar Q}$ defined as follows:
+\begin{itemize}
+\item $V_{\bar Q}$ is the set of points~$v(\alpha)$ for~$\alpha \in Q_1\blossom$ after the identifications given by~(ii),
+\item $\dissection_{\bar Q}$ is the $V_{\bar Q}$-dissection with one arc for each vertex~$p \in Q_0$ obtained by concataining the sides~$\Ert{\alpha} = \Ers{\beta}$ and~$\Ert{\alpha'} = \Ers{\beta'}$ where~$p = t(\alpha) = s(\beta) = t(\alpha') = s(\beta')$, $\alpha\beta \in I$ and~$\alpha'\beta' \in I$.
+\item $V\dual_{\bar Q}$ and~$\dissection\dual_{\bar Q}$ are defined dually.
 \end{itemize}
-The construction also automatically defines two dual cellular dissections~$\dissection_{\bar Q}$ and~${\dissection_{\bar Q}}\dual$ of the surface~$\surface_{\bar Q}$.
 \end{definition}
@@
 \label{lem:walks=arcs}
-Walks of~$\bar Q$ are precisely~$\dissection$ accordions.
+Walks of~$\bar Q$ are precisely~$\dissection$-accordions.
 \end{lemma}

### 2018-07-03 draft/accordionComplexSurfaces.tex
first pictures

--- 2018-07-02 draft/accordionComplexSurfaces.tex
@@
 \definecolor{violet}{RGB}{147,39,143} % violet color
+\newcommand{\red}{\color{red}} % red command
+\newcommand{\green}{\color{green}} % green command
 \newcommand{\darkblue}{\color{darkblue}} % darkblue command
@@
 
-\author{Sibylle Schroll}
-\address[Sibylle Schroll]{}
-\email{schroll@leicester.ac.uk}
-\urladdr{\url{}}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\vincent{Examples}
+Examples are represented on \fref{fig:quivers}.
+
+\begin{figure}[t]
+	\capstart
+	\centerline{\includegraphics[scale=.4]{quivers}}
+	\caption{Some locally gentle quivers and their blossoming quivers. Initial vertices are solid and labeled while blossom vertices are hollow, and initial arcs are bold while blossom arcs are thin.}
+	\label{fig:quivers}
+\end{figure}
+
 \vincent{Should we introduce Koszul duality here and say what it does on quivers?}
@@
 \pierreguy{Justify this definition.}
-Note that~$\bar Q\koszul$ is gentle, and that~$(\bar Q\koszul)\koszul = \bar Q$.
+Note that~$\bar Q\koszul$ is gentle, and that koszul duality is an involution and commutes with blossoming:~$(\bar Q\koszul)\koszul = \bar Q$ and~$(\bar Q\koszul)\blossom = (\bar Q\blossom)\koszul$.
+Examples are represented on \fref{fig:koszulQuivers}.
+
+\begin{figure}[t]
+	\capstart
+	\centerline{\includegraphics[scale=.4]{koszulQuivers}}
+	\caption{The Koszul duals of the (blossoming) quivers of \fref{fig:quivers}.}
+	\label{fig:koszulQuivers}
+\end{figure}
 
@@
 \label{def:surfaceQuiver}
-The surface~$\surface(\bar Q)$ of a locally gentle bound quiver~$\bar Q = (Q,I)$ is the orientable surface obtained from the blossoming quiver~$\bar Q\blossom$ as follows:
-\begin{itemize}
-\item for each arrow~$\alpha \in Q_1\blossom$, consider a lozange~$L(\alpha)$ with four (oriented) sides~$\Enrs{\alpha} = [s(\alpha), v]$, $\Enrt{\alpha} = [v, t(\alpha)]$ (colored green) and~$\Ers{\alpha} = [s(\alpha), v\dual]$ and~$\Ert{\alpha} = [v\dual, t(\alpha)]$ (colored red) as follows:
-\vincent{Figure}
-\item for any~$\alpha, \beta \in Q_1\blossom$ with~$t(\alpha) = s(\alpha)$, proceed to the following identifications:
+The surface~$\surface(\bar Q)$ of a locally gentle bound quiver~$\bar Q = (Q,I)$ is the surface obtained from the blossoming quiver~$\bar Q\blossom$ as follows:
+\begin{enumerate}[(i)]
+\item for each arrow~$\alpha \in Q_1\blossom$, consider a lozange~$L(\alpha)$ with four (oriented) sides
+\begin{alignat*}{2}
+& \Enrs{\alpha} = [v(\alpha), s(\alpha)] \qquad & \Enrt{\alpha} = [v(\alpha), t(\alpha)] \qquad & \text{(colored green)} \\
+\text{and} \qquad & \Ers{\alpha} = [v\dual(\alpha), s(\alpha)] \qquad & \Ert{\alpha} = [v\dual(\alpha), t(\alpha)] \qquad & \text{(colored red)}
+\end{alignat*}
+placed as follows:
+
+\centerline{
+\begin{tikzpicture}[scale=2, thick]
+	\node (s) at (-1,0) {$s(\alpha)$};
+	\node (t) at (1,0) {$t(\alpha)$};
+	\node (v) at (0,1) {$\green v(\alpha)$};
+	\node (vd) at (0,-1) {$\red v\dual(\alpha)$};
+	\draw[color=black, ->] (s) -> (t) node[midway, above] {$\alpha$};
+	\pic [draw, angle radius=.7cm] {angle = s--t--vd};
+	\pic [draw, angle radius=.7cm] {angle = vd--s--t};
+	\draw[color=green, ->] (v) -> (s) node[midway, above left] {$\green \Enrs{\alpha}$};
+	\draw[color=green, ->] (v) -> (t) node[midway, above right] {$\green \Enrt{\alpha}$};
+	\draw[color=red, ->] (vd) -> (s) node[midway, below left] {$\red \Ers{\alpha}$};
+	\draw[color=red, ->] (vd) -> (t) node[midway, below right] {$\red \Ert{\alpha}$};
+\end{tikzpicture}
+}
+
+\item for any~$\alpha, \beta \in Q_1\blossom$ with~$t(\alpha) = s(\beta)$, proceed to the following identifications:
     \begin{itemize}
@@
     \end{itemize}
-\end{itemize}
-The construction also automatically defines two dual cellular dissections~$\dissection_{\bar Q}$ and~${\dissection_{\bar Q}}\dual$ of the surface~$\surface_{\bar Q}$.
+\end{enumerate}
 \end{definition}
@@
 \vincent{TODO.}
+\end{example}
+
+Definition~\ref{def:surfaceQuiver} constructs an orientable surface~$\surface(\bar Q)$ with boundaries.
+This surface is actually endowed with two disjoint sets~$V_{\bar Q}$ and~${V_{\bar Q}}\dual$ of marked points and two dual dissections~$\dissection_{\bar Q}$ and~${\dissection_{\bar Q}}\dual$ defined as follows.
+
+\begin{definition}
+\label{def:dissectionQuiver}
+The surface~$\surface(\bar Q)$ is endowed with
+\begin{itemize}
+\item the set~$V_{\bar Q}$ of points~$v(\alpha)$ for~$\alpha \in Q_1\blossom$ after the identifications given by~(ii),
+\item the $V_{\bar Q}$-dissection~$\dissection_{\bar Q}$ given by all sides~$\Enrs{\alpha}$ and~$\Enrt{\alpha}$ for~$\alpha \in Q_1\blossom$ after the identifications given by~(ii).
+\end{itemize}
+The set~${V_{\bar Q}}\dual$ and the ${V_{\bar Q}}\dual$-dissection~${\dissection_{\bar Q}}\dual$ are defined dually.
+\end{definition}
+
+\begin{remark}
+Observe that
+\begin{itemize}
+\item $V_{\bar Q}$ has one vertex for each straight walk in~$\bar Q$,
+\item $\dissection_{\bar Q}$ has one arc for each vertex~$p \in \bar Q_0$, obtained by concataining the sides~$\Enrt{\alpha} = \Enrs{\beta}$ and~$\Enrt{\alpha'} = \Enrs{\beta'}$ where~$p = t(\alpha) = s(\beta) = t(\alpha') = s(\beta')$, $\alpha\beta \notin I$ and~$\alpha'\beta' \notin I$.
+\end{itemize}
+A similar remark holds dually for~${V_{\bar Q}}\dual$ and~${\dissection_{\bar Q}}\dual$.
+\end{remark}
+
+\begin{example}
+Consider the following family of locally gentle quivers:
+\vincent{TODO}
 \end{example}

### 2018-07-03 firstPaper/figures/gridQuiver.tex
first paper

\begin{tikzpicture}[scale=1.4]
    \node[inner sep = 1pt] (a) at (1,3) {$\bullet$};
    \node[inner sep = 1pt] (b) at (2,3) {$\bullet$};
    \node[inner sep = 1pt] (c) at (1,2) {$\bullet$};
    \node[inner sep = 1pt] (d) at (2,2) {$\bullet$};
    \node[inner sep = 1pt] (e) at (3,2) {$\bullet$};
    \node[inner sep = 1pt] (f) at (4,2) {$\bullet$};
    \node[inner sep = 1pt] (g) at (2,1) {$\bullet$};
    \node[inner sep = 1pt] (h) at (3,1) {$\bullet$};
    \node (x1) at (.2,3) {};
    \node (x2) at (.2,2) {};
    \node (x3) at (1,1.2) {};
    \node (x4) at (1.2,1) {};
    \node (x5) at (2,.2) {};
    \node (x6) at (3,.2) {};
    \node (x7) at (3.8,1) {};
    \node (x8) at (4,1.2) {};
    \node (x9) at (4.8,2) {};
    \node (x10) at (4,2.8) {};
    \node (x11) at (3,2.8) {};
    \node (x12) at (2.8,3) {};
    \node (x13) at (2,3.8) {};
    \node (x14) at (1,3.8) {};
    \path [->, ultra thick] (a) edge (b);
    \path [->, ultra thick] (c) edge (a);
    \path [->, ultra thick] (d) edge (b);
    \path [->, ultra thick] (c) edge (d);
    \path [->, ultra thick] (d) edge (e);
    \path [->, ultra thick] (e) edge (f);
    \path [->, ultra thick] (g) edge (d);
    \path [->, ultra thick] (h) edge (e);
    \path [->, ultra thick] (g) edge (h);
    \path [->] (x1) edge (a);
    \path [->] (x2) edge (c);
    \path [->] (x3) edge (c);
    \path [->] (x4) edge (g);
    \path [->] (x5) edge (g);
    \path [->] (x6) edge (h);
    \path [->] (h) edge (x7);
    \path [->] (x8) edge (f);
    \path [->] (f) edge (x9);
    \path [->] (f) edge (x10);
    \path [->] (e) edge (x11);
    \path [->] (b) edge (x12);
    \path [->] (b) edge (x13);
    \path [->] (a) edge (x14);
    \draw pic[draw, angle eccentricity=1.2, angle radius=.4cm, ultra thick]{angle=c--a--b};
    \draw pic[draw, angle eccentricity=1.2, angle radius=.4cm, ultra thick]{angle=b--d--c};
    \draw pic[draw, angle eccentricity=1.2, angle radius=.4cm, ultra thick]{angle=g--d--e};
    \draw pic[draw, angle eccentricity=1.2, angle radius=.4cm, ultra thick]{angle=e--h--g};
    \draw pic[draw, angle eccentricity=1.2, angle radius=.4cm, ultra thick]{angle=h--e--f};
    \draw pic[draw, angle eccentricity=1.2, angle radius=.4cm]{angle=x14--a--x1};
    \draw pic[draw, angle eccentricity=1.2, angle radius=.4cm]{angle=a--c--x2};
    \draw pic[draw, angle eccentricity=1.2, angle radius=.4cm]{angle=x3--c--d};
    \draw pic[draw, angle eccentricity=1.2, angle radius=.4cm]{angle=d--g--x4};
    \draw pic[draw, angle eccentricity=1.2, angle radius=.4cm]{angle=x5--g--h};
    \draw pic[draw, angle eccentricity=1.2, angle radius=.4cm]{angle=x6--h--x7};
    \draw pic[draw, angle eccentricity=1.2, angle radius=.4cm]{angle=x8--f--x9};
    \draw pic[draw, angle eccentricity=1.2, angle radius=.4cm]{angle=x10--f--e};
    \draw pic[draw, angle eccentricity=1.2, angle radius=.4cm]{angle=x11--e--d};
    \draw pic[draw, angle eccentricity=1.2, angle radius=.4cm]{angle=d--b--x12};
    \draw pic[draw, angle eccentricity=1.2, angle radius=.4cm]{angle=x13--b--a};
\end{tikzpicture}

### 2018-07-03 draft/accordionComplexSurfaces.tex
Fixed Koszul duality definition and added reference.

@@
 \begin{itemize}
- \item the quiver~$Q\koszul$ is equal to~$Q$;
- \item the ideal~$I\koszul$ is generated by the paths of length two in~$Q$ that do not appear in~$I$.
+ \item the quiver~$Q\koszul$ is equal to the opposite quiver of~$Q$, that is, the quiver obtained from~$Q$ by reversing all arrows;
+ \item the ideal~$I\koszul$ is generated by the opposites of the paths of length two in~$Q$ that do not appear in~$I$.
 \end{itemize}
 \end{definition}
-\pierreguy{Justify this definition.}
-Note that~$\bar Q\koszul$ is gentle, and that koszul duality is an involution and commutes with blossoming:~$(\bar Q\koszul)\koszul = \bar Q$ and~$(\bar Q\koszul)\blossom = (\bar Q\blossom)\koszul$.
+It is seen in \cite{BessenrodtHolm} that the (ungraded version of the) Koszul dual of a locally gentle algebra~$kQ/I$ is isomorphic to~$kQ\koszul/I\koszul$.
+Note that~$\bar Q\koszul$ is gentle, and that Koszul duality is an involution and commutes with blossoming:~$(\bar Q\koszul)\koszul = \bar Q$ and~$(\bar Q\koszul)\blossom = (\bar Q\blossom)\koszul$.
 Examples are represented on \fref{fig:koszulQuivers}.

### 2018-07-03 firstPaper/nonKissingComplex.tex

\documentclass{amsart}

\usepackage[T1]{fontenc}
\usepackage{enumerate, amsmath, amsfonts, amssymb, amsthm, mathrsfs, wasysym, graphics, graphicx, xcolor, url, hyperref, hypcap,  shuffle, xargs, multicol, overpic, pdflscape, multirow, hvfloat, minibox, accents, array, xifthen, ae, aecompl, blkarray, pifont, mathtools, a4wide}
\usepackage{marginnote}
\hypersetup{colorlinks=true, citecolor=darkblue, linkcolor=darkblue}
\usepackage[all]{xy}
\usepackage[bottom]{footmisc}
\usepackage{tikz}
\usepackage{tkz-graph}
\usetikzlibrary{trees, decorations, decorations.markings, shapes, arrows, matrix, calc, fit, intersections, patterns, angles}
\graphicspath{{figures/}}
\makeatletter\def\input@path{{figures/}}\makeatother
\usepackage{caption}
\captionsetup{width=\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% theorems
\newtheorem{theorem}{Theorem}[part]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem*{theorem*}{Theorem}%[section]

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{question}[theorem]{Question}
\newtheorem{notation}[theorem]{Notation}
\newtheorem{assumption}[theorem]{Assumption}

% math special letters
\newcommand{\R}{\mathbb{R}} % reals
\newcommand{\N}{\mathbb{N}} % naturals
\newcommand{\Z}{\mathbb{Z}} % integers
\newcommand{\C}{\mathbb{C}} % complex
\newcommand{\I}{\mathbb{I}} % set of integers
\newcommand{\HH}{\mathbb{H}} % hyperplane
\newcommand{\K}{k} % field
\newcommand{\fA}{\mathfrak{A}} % alternating group
\newcommand{\fS}{\mathfrak{S}} % symmetric group
\newcommand{\cA}{\mathcal{A}} % algebra
\newcommand{\cC}{\mathcal{C}} % collection
\newcommand{\cS}{\mathcal{S}} % ground set
\newcommand{\uR}{\underline{R}} % underline set
\newcommand{\uS}{\underline{S}} % underline set
\newcommand{\uT}{\underline{T}} % underline set
\newcommand{\oS}{\overline{S}} % overline set
\newcommand{\ucS}{\underline{\cS}} % underline ground set
\renewcommand{\b}[1]{\mathbf{#1}} % bold letters
\newcommand{\h}{\widehat} % hat letters

% math commands
\newcommand{\set}[2]{\left\{ #1 \;\middle|\; #2 \right\}} % set notation
\newcommand{\bigset}[2]{\big\{ #1 \;\big|\; #2 \big\}} % big set notation
\newcommand{\Bigset}[2]{\Big\{ #1 \;\Big|\; #2 \Big\}} % Big set notation
\newcommand{\setangle}[2]{\left\langle #1 \;\middle|\; #2 \right\rangle} % set notation
\newcommand{\ssm}{\smallsetminus} % small set minus
\newcommand{\dotprod}[2]{\left\langle \, #1 \; \middle| \; #2 \, \right\rangle} % dot product
\newcommand{\symdif}{\,\triangle\,} % symmetric difference
\newcommand{\one}{{1\!\!1}} % the all one vector
\newcommand{\eqdef}{\mbox{\,\raisebox{0.2ex}{\scriptsize\ensuremath{\mathrm:}}\ensuremath{=}\,}} % :=
\newcommand{\defeq}{\mbox{~\ensuremath{=}\raisebox{0.2ex}{\scriptsize\ensuremath{\mathrm:}} }} % =:
\newcommand{\simplex}{\triangle} % simplex
\renewcommand{\implies}{\Rightarrow} % imply sign
\newcommand{\transpose}[1]{{#1}^t} % transpose matrix

% operators
\DeclareMathOperator{\conv}{conv} % convex hull
\DeclareMathOperator{\vect}{vect} % linear span
\DeclareMathOperator{\cone}{cone} % cone hull
\DeclareMathOperator{\inv}{inv} % inversions
\DeclareMathOperator{\ascents}{asc} % ascents
\DeclareMathOperator{\descents}{des} % descents

% others
\newcommand{\fref}[1]{Figure~\ref{#1}} % reference figures
\newcommand{\ie}{\textit{i.e.}~} % id est
\newcommand{\eg}{\textit{e.g.}~} % exempli gratia
\newcommand{\Eg}{\textit{E.g.}~} % exempli gratia
\newcommand{\apriori}{\textit{a priori}} % a priori
\newcommand{\viceversa}{\textit{vice versa}} % vice versa
\newcommand{\versus}{\textit{vs.}~} % versus
\newcommand{\aka}{\textit{a.k.a.}~} % also known as
\newcommand{\perse}{\textit{per se}} % per se
\newcommand{\ordinal}{\textsuperscript{th}} % th for ordinals
\newcommand{\ordinalst}{\textsuperscript{st}} % st for ordinals
\definecolor{darkblue}{rgb}{0,0,0.7} % darkblue color
\definecolor{green}{RGB}{57,181,74} % green color
\definecolor{violet}{RGB}{147,39,143} % violet color
\newcommand{\darkblue}{\color{darkblue}} % darkblue command
\newcommand{\defn}[1]{\textsl{\darkblue #1}} % emphasis of a definition
\newcommand{\para}[1]{\medskip\noindent\textbf{#1.}} % paragraph
\renewcommand{\topfraction}{1} % possibility to have one page of pictures
\renewcommand{\bottomfraction}{1} % possibility to have one page of pictures
%\renewcommand\labelitemi{$\diamond$} % redefine itemize default symbol
\newcommand{\ex}{_{\textrm{exm}}} % examples
\newcommand{\pa}{_{\textrm{pa}}} % path

% marginal comments
\usepackage{todonotes}
\newcommand{\yann}[1]{\textbf{#1 --- Y.}} % {\todo[color=red!30]{#1 \\ \hfill --- Y.}}
\newcommand{\vincent}[1]{\todo[color=blue!30]{#1 \\ \hfill --- V.}}
\newcommand{\pierreguy}[1]{\todo[color=green!30]{#1 \\ \hfill --- PG.}}

% SPECIFIC NON-KISSING COMPLEX

% COMBINATORICS
% quiver
\newcommand{\blossom}{^\text{\ding{96}}} % blossom
\newcommand{\blinkers}[1]{_{\LEFTCIRCLE \!\! #1 \!\! \RIGHTCIRCLE}} % blossom
\newcommand{\indeg}{\mathrm{indeg}} % in-degree
\newcommand{\outdeg}{\mathrm{outdeg}} % out-degree
%\newcommand{\tai}{\mathsf{tai}} % target incompatible
%\newcommand{\tac}{\mathsf{tac}} % target compatible
%\newcommand{\soi}{\mathsf{soi}} % source incompatible
%\newcommand{\soc}{\mathsf{soc}} % source compatible
%\newcommand{\cso}{\mathsf{cso}} % cosource
%\newcommand{\cta}{\mathsf{cta}} % cotarget

% walks
\newcommand{\strings}{\mathcal{S}} % strings
\newcommand{\distinguishableStrings}{\mathcal{S}_\mathrm{dist}} % distinguishable strings
\newcommand{\lfStrings}{\underline{\mathcal{S}}} % loop-free strings
\newcommand{\walks}{\mathcal{W}} % walks
\newcommand{\straightWalks}{\mathcal{W}_\mathrm{str}} % straight walks
\newcommand{\bendingWalks}{\mathcal{W}_\mathrm{bend}} % bending walks
\newcommand{\NKWalks}{\mathcal{W}_\mathrm{nk}} % non-kissing walks
\newcommand{\peaks}[1]{\mathsf{peaks}(#1)} % peaks
\newcommand{\deeps}[1]{\mathsf{deeps}(#1)} % deeps
\newcommand{\distinguishedWalk}[2]{\mathsf{dw}(#1,#2)} % distinguished walk
\newcommand{\distinguishedArrows}[2]{\mathsf{da}(#1,#2)} % distinguished arrows
\newcommand{\distinguishedString}[2]{\mathsf{ds}(#1,#2)} % distinguished string
\newcommand{\distinguishedSign}[2]{\varepsilon(#1,#2)} % distinguished sign

% non-kissing complex, lattice, flip graph
\newcommand{\kn}{\kappa} % kissing number
\newcommand{\KN}{\textsc{kn}} % Kissing Number
\newcommandx{\NKC}[1][1=\bar Q]{\mathcal{K}_{\mathrm{nk}}(#1)} % non-kissing complex
\newcommandx{\RNKC}[1][1=\bar Q]{\mathcal{C}_{\mathrm{nk}}(#1)} % non-kissing complex
\newcommandx{\NKL}[1][1=\bar Q]{\mathcal{L}_{\mathrm{nk}}(#1)} % non-kissing lattice
\newcommandx{\NKG}[1][1=\bar Q]{\mathcal{G}_{\mathrm{nk}}(#1)} % non-kissing flip graph
\newcommandx{\NFC}[1][1=\bar Q]{\mathcal{C}_{\mathrm{nf}}(#1)} % non-friendly complex
\newcommand{\peak}{\mathrm{peak}} % bottom dissection
\newcommand{\deep}{\mathrm{deep}} % top dissection
\newcommand{\reversed}[1]{#1^{\mathrm{rev}}} % reverse all arrows
\renewcommand{\top}{\mathrm{top}} % top
\newcommand{\bottom}{\mathrm{bot}} % bottom

% lattices
\newcommand{\meet}{\wedge} % meet
\newcommand{\join}{\vee} % join
\newcommand{\bigMeet}{\bigwedge} % meet
\newcommand{\bigJoin}{\bigvee} % join
\newcommand{\closure}[1]{#1^{\mathrm{cl}}} % closure operator
\newcommand{\coclosure}[1]{#1^{\mathrm{cocl}}} % coclosure operator
\newcommand{\uclosure}[1]{#1^{\underline{\mathrm{cl}}}} % loop free closure operator
\newcommand{\Bicl}[1]{\mathsf{Bic}(#1)} % biclosed sets
\newcommand{\projDown}{\pi_\downarrow} % down projection map
\newcommand{\projUp}{\pi^\uparrow} % up projection map
\newcommand{\JI}{\mathsf{JI}} % join-irreducible
\newcommand{\MI}{\mathsf{MI}} % meet-irreducible
\newcommand{\Cong}{\mathsf{Cong}} % congruence lattice
\newcommand{\con}{\mathrm{con}} % congruence contracting a cover relation
\newcommand{\ji}{\mathsf{ji}} % join irreducible
\newcommand{\mi}{\mathsf{mi}} % meet irreducible

% GEOMETRY
% g-vectors
\newcommand{\gvector}[1]{\mathbf{g}(#1)} % g-vector of the path #1
\newcommand{\gvectors}[1]{\mathbf{g}(#1)} % g-vectors of the paths #1
\newcommandx{\gvectorFan}[1][1=\bar Q]{\mathcal{F}^\mathbf{g}(#1)} % g-vector fan
% c-vectors
\newcommand{\cvector}[2]{\mathbf{c}(#1 \in #2)} % c-vector of the path #1 in the facet #2
\newcommand{\cvectors}[1]{\mathbf{c}(#1)} % c-vectors of the paths #1
\newcommandx{\allcvectors}[1][1=\bar Q]{\mathbf{C}(#1)} % all c-vectors with respect to the initial cluster #1
\newcommandx{\cvectorFan}[1][1=\bar Q]{\mathcal{F}^\mathbf{c}(#1)} % fan of hyperplanes orthogonal to all c-vectors
% points, hyperplanes, half-spaces
\newcommand{\point}[1]{\mathbf{p}(#1)} % vertex of the grid associahedron corresponding to the cluster #1
\newcommand{\ray}{\mathbf{r}} % ray
\newcommand{\rays}{\mathbf{R}} % rays
\newcommand{\hs}{\mathbf{H}^{\le}} % half space
\newcommand{\HS}[1]{\mathbf{H}^{\le}(#1)} % half space
\newcommand{\hyp}{\mathbf{H}^{=}} % hyperplane
\newcommand{\Hyp}[1]{\mathbf{H}^{=}(#1)} % hyperplane
\newcommand{\fix}[1]{\mathrm{Fix}(#1)} % fix space
% polytopes
\newcommandx{\Asso}[2][1=\bar Q,2={}]{\mathsf{Asso}^{#2}(#1)} % associahedron
\newcommandx{\Zono}[2][1=\bar Q,2={}]{\mathsf{Zono}^{#2}(#1)} % zonotope
\newcommand{\Fan}{\mathcal{F}} % fan
\newcommand{\multiplicityVector}{\b{m}} % multiplicity vector

% ALGEBRA
\newcommand{\Hom}[1]{\operatorname{{\rm Hom}}_{#1}}
\newcommand{\Ext}[1]{\operatorname{{\rm Ext}}_{#1}}
\newcommandx{\AR}[1][1=\bar Q]{\mathrm{AR}(#1)} % Auslander-Reiten quiver
\newcommandx{\tTC}[1][1=\bar Q]{\mathcal{K}^{\textrm{s$\tau$-tilt}}(#1)} % tau-tilting complex
\newcommand{\rep}{\operatorname{{\rm rep}}}
\newcommand{\proj}{\operatorname{{\rm proj}}}

% formating the part command
\makeatletter
\def\part{\@startsection{part}{1}%
\z@{.7\linespacing\@plus\linespacing}{.8\linespacing}%
{\LARGE\sffamily\centering}}
\@addtoreset{section}{part}
\makeatother
\renewcommand{\thesection}{\arabic{part}.\arabic{section}}

% formating the table of contents
\makeatletter
\def\l@section{\@tocline{1}{2pt}{0pc}{}{}}
\makeatother
\let\oldtocpart=\tocpart
\renewcommand{\tocpart}[2]{\bf\large\oldtocpart{#1}{#2}}
\let\oldtocsection=\tocsection
\renewcommand{\tocsection}[2]{\bf\oldtocsection{#1}{#2}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Non-kissing complexes and tau-tilting for gentle algebras}
%\title[Non-kissing complexes and tau-tilting for gentle algebras]{Non-kissing complexes and tau-tilting for gentle algebras \\ {\rm Preliminary version --- please do not distribute}}

\thanks{The three authors were partially supported by the French ANR grant SC3A~(15\,CE40\,0004\,01).}

\author{Yann Palu}
\address[Yann Palu]{LAMFA, Universit\'e Picardie Jules Verne, Amiens}
\email{yann.palu@u-picardie.fr}
\urladdr{\url{http://www.lamfa.u-picardie.fr/palu/}}

\author{Vincent Pilaud}
\address[Vincent Pilaud]{CNRS \& LIX, \'Ecole Polytechnique, Palaiseau}
\email{vincent.pilaud@lix.polytechnique.fr}
\urladdr{\url{http://www.lix.polytechnique.fr/~pilaud/}}

\author{Pierre-Guy Plamondon}
\address[Pierre-Guy Plamondon]{Laboratoire de Math\'ematiques d'Orsay, Universit\'e Paris-Sud, CNRS, Universit\'e Paris-Saclay}
\email{pierre-guy.plamondon@math.u-psud.fr}
\urladdr{\url{https://www.math.u-psud.fr/~plamondon/}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{abstract}
We interpret the support $\tau$-tilting complex of any gentle bound quiver as the non-kissing complex of walks on its blossoming quiver.
Particularly relevant examples were previously studied for quivers defined by a subset of the grid or by a dissection of a polygon.
We then focus on the case when the non-kissing complex is finite.
We show that the graph of increasing flips on its facets is the Hasse diagram of a congruence-uniform lattice.
Finally, we study its $\b{g}$-vector fan and prove that it is the normal fan of a non-kissing associahedron.
\end{abstract}

%\vspace*{.3cm}

\maketitle

\vspace*{.3cm}
\tableofcontents

\vspace*{-.9cm}
\enlargethispage{.4cm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage
\section*{Introduction}

\subsection*{Non-kissing complex and support $\tau$-tilting complex}

The non-kissing complex is a simplicial complex of pairwise non-kissing paths in a fixed shape of a grid.
It was introduced by T.~K.~Petersen, P.~Pylyavskyy and D.~Speyer in~\cite{PetersenPylyavskyySpeyer} for a staircase shape, studied by F.~Santos, C.~Stump and V.~Welker~\cite{SantosStumpWelker} for rectangular shapes, and extended by T.~McConville in~\cite{McConville} for arbitrary shapes.
This complex is known to be a simplicial sphere, and it was actually realized as a polytope using successive edge stellations and suspensions in~\cite[Sect.~4]{McConville}.
Moreover, the dual graph of the non-kissing complex has a natural orientation which equips its facets with a lattice structure~\cite[Thm. 1.1, Sect.~5--8]{McConville}.
Further lattice theoretic and geometric aspects of this complex were recently developed by A.~Garver and T.~McConville in~\cite{GarverMcConville-grid}.

The interest for non-kissing complexes is motivated by relevant instances arising from particular shapes.
As already observed in~\cite[Sect.~10]{McConville}, when the shape is a ribbon, the non-kissing complex is an associahedron (the simplicial complex of dissections of a polygon), and the non-kissing lattice is a type~$A$ Cambrian lattice of N.~Reading~\cite{Reading-CambrianLattices}.
In particular, the straight ribbon corresponds to the Tamari lattice, an object at the heart of a deep research area~\cite{TamariFestschrift}.
When the shape is a rectangle (or even a staircase), the non-kissing complex was studied in~\cite{PetersenPylyavskyySpeyer, SantosStumpWelker} as the Grassmann associahedron, in connection to non-crossing subsets of~$[n]$.

Other instances of such complexes arise naturally from the representation theory of associative algebras.  
The notion of support $\tau$-tilting module over an algebra was introduced by T.~Adachi, O.~Iyama and I.~Reiten in \cite{AdachiIyamaReiten}, and has proved to be a successful generalization of tilting and cluster-tilting theory.  
Over a given algebra, indecomposable $\tau$-rigid modules form a complex. 
For an account of the various algebraic interpretations of this complex, we refer the reader to \cite{BrustleYang}.  
For example, in the case of the path algebra of a quiver which is a straight line, the support $\tau$-tilting complex is, again, an associahedron.

The aim of this paper is twofold.
On the one hand, we provide a realization of any non-kissing complex as the support $\tau$-tilting complex of a well-chosen associative algebra.
The algebras that occur are certain gentle algebras, a special case of the well-studied string algebras of M.~C.~R.~Butler and C.~Ringel~\cite{ButlerRingel}.
On the other hand, we extend the notion of non-kissing complex and show that the support $\tau$-tilting complex of any gentle algebra can be interpreted as an extended non-kissing complex.
More precisely, starting from any gentle bound quiver~$\bar Q = (Q,I)$, we attach additional incoming and outgoing arrows, called blossoms, to make each initial vertex \mbox{$4$-valent}. The resulting gentle bound quiver~$\bar Q\blossom = (Q\blossom, I\blossom)$ is called the blossoming quiver of~$\bar Q$ (see Section~\ref{subsec:blossomingQuiver}). 
We then define a combinatorial notion of compatibility on walks in $\bar Q \blossom$, called the non-kissing relation (see Section~\ref{sec:nonKissingComplex}).
The motivating result of this paper is Theorem \ref{thm:nkc/sttiltc}.

\begin{theorem*}
For any gentle bound quiver~$\bar Q = (Q,I)$, the non-kissing complex of walks in the blossoming quiver~$\bar Q \blossom$ is isomorphic to the support $\tau$-tilting complex of the gentle algebra~$kQ/I$.
\end{theorem*}

In short, to any walk in $\bar Q \blossom$ corresponds a representation of $\bar Q$, and this correspondence takes non-kissing walks to $\tau$-compatible representations.
This connection between the combinatorially-flavored non-kissing complex and the algebraically-flavoured support $\tau$-tilting complex opens a bridge to go back and forth between the two worlds.
It allows us, for instance, to combinatorially define mutation of support $\tau$-tilting modules (see Section \ref{subsec:flips}).
This seems worthwhile, as the mutation of support $\tau$-tilting modules over an arbitrary algebra is generally difficult to carry out~explicitly.
%
Table~\ref{table:dictionary} provides a dictionary to translate between the algebraic notions on the support $\tau$-tilting complex of a gentle algebra and the combinatorial notions on the non-kissing complex of its blossoming quiver.

\newcommandx{\multiLinesBox}[2][2=6cm]{
\begin{minipage}{#2}\vspace{.1cm}\begin{center}
#1
\end{center}\vspace{0cm}\end{minipage}
}

\begin{table}
	\capstart{}
    \centerline{
    \begin{tabular}{|c|c|c|}
    \hline
    String modules on~$\bar Q$ &
    Walks on~$\bar Q\blossom$  &
    Reference
    \\ \hline \hline
    almost positive strings (Def.~\ref{def:stringsBands}) &
    bending walks (Def.~\ref{def:straightBended}) &
    Fig.~\ref{exm:exmBijectionStringsWalks1} \& \ref{fig:exmAuslanderReitenQuiver}
    \\ \hline
    ?\footnotemark[1] &
    straight walks (Def.~\ref{def:straightBended}) &
    Fig.~\ref{exm:exmBijectionStringsWalks1} \& \ref{fig:exmAuslanderReitenQuiver}
    \\ \hline
    \multiLinesBox{$P(v)$ and $P(v)[1]$ \\ $A=kQ/I$ and~$A[1]$ \\ ~} &
    \multiLinesBox{$v_\peak$ and $v_\deep$ \\ $F_\peak$ and~$F_\deep$ \\ (Exm.~\ref{example: Fdeep Fpeak} and Def.~\ref{def: deep walk})} &
    Lem.~\ref{lem:bijections-STTC-NKC}
    \\ \hline
    ?\footnotemark[2] &
    countercurrent order~$\prec_\alpha$ &
    ---
    \\ \hline
    $\tau$-compatibility (Def.~\ref{def: tau-compatibility}) &
    non-kissing (Def.~\ref{def: kissing}) &
    Thm.~\ref{thm:nkc/sttiltc}
    \\ \hline
    support~$\tau$-tilting object (Def.~\ref{def: tau-rigid and stautilt}) &
    maximal non-kissing collection of walks &
    Thm.~\ref{thm:nkc/sttiltc}
    \\ \hline
    support~$\tau$-tilting complex~$\tTC$ (Def.~\ref{def: stautilt complex}) &
    reduced non-kissing complex~$\RNKC$ (Def.~\ref{def: nKc}) &
    Thm.~\ref{thm:nkc/sttiltc}
    \\ \hline
    \multiLinesBox{(left) mutation of support \\ $\tau$-tilting objects (Thm.~\ref{thm: mutation of stautilts}~\cite{AdachiIyamaReiten})} &
    \multiLinesBox{(increasing) flip \\ (Prop.~\ref{prop:flip} and Def.~\ref{def:flip} \& \ref{def:increasingFlip})} &
    Thm.~\ref{thm:nkc/sttiltc}
    \\ \hline
    lattice of torsion classes &
    non-kissing lattice~$\NKL$ (Thm.~\ref{thm:lattice}) &
    Thm.~\ref{thm:nkc/sttiltc}
    \\ \hline
    bricks &
    \multiLinesBox{distinguishable strings (Def.~\ref{def:distinguishedSubstring})} &
    Prop.~\ref{prop:characterizationDistinguishableStrings}
    \\ \hline
    collections of pairwise Hom-orthogonal bricks &
    non-friendly complex (Def.~\ref{def: friendly}) &
    Prop.~\ref{prop:characterizationDistinguishableStrings}
    \\ \hline
    \multiLinesBox{bijection between indecomposable~$\tau$-rigid representations and bricks (Thm. 6.1 in~\cite{DemonetIyamaJasso})} &
    \multiLinesBox{bijection between non-kissing walks that are not peak walks and distinguishable strings (Prop.~\ref{prop:bijectionDistinguishableStringsWalks})} &
    \multiLinesBox{Conjectural \\ cf.~Prop.~\ref{prop:bijectionDistinguishableStringsJI}}[2cm]
    \\ \hline
    \multiLinesBox{Bongartz cocompletion of a~$\tau$-rigid indecomposable representation $N=M(\rho)$ whose associated brick is~$M(\sigma)$. Moreover $\sigma = \distinguishedWalk{\omega(\rho)}{F}$} &
    \multiLinesBox{$F=\eta\left(\closure{\Sigma_\bottom(\sigma)}\right)$, where $\sigma$ is a distinguishable string} &
    Rem.~\ref{rem: Bongartz}
    \\ \hline
    Bongartz completion &
    $\eta\left(\closure{\Sigma_\top(\sigma)}\right)$ &
    Rem.~\ref{rem: Bongartz}
    \\ \hline
    $\b{g}$-vector or index of a module (Def.~\ref{definition: g-vector of representation}) &
    $\b{g}$-vector of a walk (Def.~\ref{def: g-vectors for walks}) &
    Rem.~\ref{rem: g-vectors coincide}
    \\ \hline
    $\dim \Hom{A} \big( M(\sigma), \tau M(\sigma') \big)$ (Sec.~\ref{subsec:tautilting}) &
    kissing number~$\kappa \big( \omega(\sigma), \omega(\sigma') \big)$ (Def.~\ref{def: kissing number}) &
    Rem.~\ref{rem:KNvsTau}
    \\ \hline
    \end{tabular}
    }
    \caption{Dictionary between algebraic notions on the support $\tau$-tilting complex and combinatorial notions on the non-kissing complex.}
    \label{table:dictionary}    
\end{table}

\subsection*{The non-kissing lattice and the non-kissing associahedron}

Besides this algebraic connection, we study the non-kissing complex on any gentle bound quiver with a triple perspective.

On the combinatorial side, we provide a purely combinatorial proof that the non-kissing complex over a gentle bound quiver is a pseudomanifold.
This involves in particular a precise description of the flip inspired from~\cite[Sect.~3]{McConville}.

On the lattice-theoretical side, we consider the graph of increasing flips between non-kissing facets.
When the quiver is a directed path, this increasing flip graph is the Hasse diagram of the classical Tamari lattice.
In general, when $\bar Q$ is $\tau$-tilting finite, the transitive closure of the increasing flip graph is isomorphic to the lattice of torsion classes, and we therefore call it the non-kissing lattice.
Our main lattice-theoretic result is the following extension of a remarquable result of T.~McConville~\cite{McConville}.

\begin{theorem*}
For any gentle bound quiver~$\bar Q$ whose non-kissing complex is finite, the non-kissing lattice is congruence-uniform.
In fact, the non-kissing lattice is both a lattice quotient and a sublattice of a lattice of biclosed sets on strings in~$\bar Q$.
\end{theorem*}

\noindent
It is then natural to study the canonical join complex of the non-kissing lattice, which we call the non-friendly complex following~\cite{GarverMcConville-grid}.
This complex corresponds to the classical non-crossing partitions in Catalan combinatorics.

Finally, on the geometric side, we study realizations of non-kissing complexes as polyhedral fans and polytopes.
Geometric prototypes are given by the type~$A$ Cambrian fans of N.~Reading and D.~Speyer~\cite{ReadingSpeyer} and their polytopal realization by C.~Hohlweg and C.~Lange~\cite{HohlwegLange}.
We define $\b{g}$- and $\b{c}$-vectors for walks in the non-kissing complex of any gentle bound quiver and provide a simple combinatorial proof of the following geometric statement.

\begin{theorem*}
Consider a gentle bound quiver~$\bar Q$ whose non-kissing complex is finite.
Then the \mbox{$\b{g}$-vectors} of the walks in the blossoming quiver~$\bar Q\blossom$ support a complete simplicial fan which realizes the non-kissing complex of~$\bar Q$.
Moreover, this fan is the normal fan of a polytope, called the non-kissing associahedron.
\end{theorem*}

\noindent
The non-kissing complex provides an instrumental combinatorial model to understand the linear dependences among $\b{g}$-vectors of adjacent $\b{g}$-vector cones, which leads to simple polytopal realizations.
In fact, this understanding even extends to arbitrary $\tau$-tilting finite algebras.

\footnotetext[1]{The straight walks should morally correspond to some projective-injective objects in an exact category. We plan to further investigate the situation depicted in Figure~\ref{fig:exmAuslanderReitenQuiver}.}
\footnotetext[2]{We do not know of an algebraic interpretation of the countercurrent order yet. We nonetheless included it in the table above since we think it might be of interest to find one.}

\subsection*{Grid and dissection bound quivers}

\enlargethispage{.4cm}
Particular instances of gentle bound quivers enable us to connect previous results and to answer open conjectures from previous works:
\begin{enumerate}[(i)]
\item \textbf{Grid quivers}: Our combinatorial and lattice-theoretic results are directly inspired from that of~\cite{PetersenPylyavskyySpeyer, SantosStumpWelker, McConville, GarverMcConville-grid} for quivers arising from the $\Z^2$ grid. Our approach provides an interpretation of the non-kissing complex of a grid in terms of $\tau$-tilting theory of gentle algebras and answers open questions of~\cite{GarverMcConville-grid} concerning its geometry.
\item \textbf{Dissection quivers}: Each dissection of a polygon is classically associated with a gentle quiver. Its non-kissing complex is isomorphic to the accordion complex of the dissection, defined and developed in the works of Y.~Baryshnikov~\cite{Baryshnikov}, F.~Chapoton~\cite{Chapoton-quadrangulations}, A.~Garver and T.~McConville~\cite{GarverMcConville} and T.~Manneville and V.~Pilaud~\cite{MannevillePilaud-accordion}. As far as we know, this provides the first connection between non-kissing complexes and accordion complexes.
\item \textbf{Path quivers}: When the quiver is a path, the non-kissing complex is a simplicial associahedron, the non-kissing lattice is a type~$A$ Cambrian lattice of N.~Reading~\cite{Reading-CambrianLattices} (including the classical Tamari lattice), and the non-kissing associahedron is an associahedron of C.~Hohlweg and C.~Lange~\cite{HohlwegLange} (including the classical associahedron of J.-L.~Loday~\cite{Loday}).
\end{enumerate}

\subsection*{Organization}

The paper is organized as follows.
Part~\ref{part:algebra} gathers the algebraic aspects of the paper.
In Section~\ref{sec:recollectionsStringAlgebras}, we recall elements of the representation theory of bound quiver algebras in general and of string algebras in particular.
The definition and essential properties of support \mbox{$\tau$-tilting} modules are given in Section~\ref{subsec:tautilting}.  
The combinatorics of strings and bands is also introduced in Sections~\ref{subsec:stringsBands} and~\ref{subsec:stringBandModules}, and used in \ref{sec:stringModules} to derive combinatorial descriptions of $\b{g}$-vectors and $\tau$-compatibility for string modules.

Part~\ref{part:combinatorics} connects the support $\tau$-tilting complex to the non-kissing complex.
Sections~\ref{sec:blossomingQuivers} and \ref{sec:nonKissingComplex} are devoted to our main definitions: those of the blossoming quiver of a gentle bound quiver, and of its non-kissing complex.  
Theorem \ref{thm:nkc/sttiltc} linking the non-kissing complex to the support $\tau$-tilting complex is then proved in Section \ref{sec:nkcvsttc}.

Part~\ref{part:lattice} is devoted to the non-kissing lattice.
After a brief reminder on lattice congruences and congruence-uniform lattices in Section~\ref{sec:latticeTheory}, we define a closure operator on strings of~$\bar Q$ and study the lattice of biclosed sets in Section~\ref{sec:biclosedStrings}.
We then introduce a lattice congruence on biclosed sets in Section~\ref{sec:latticeCongruence} and show that the non-kissing lattice is isomorphic to the lattice quotient of this congruence in Section~\ref{sec:biclosedSetsToNKF}.
Finally, we describe the join-irreducible elements and the canonical join complex of the non-kissing lattice in Section~\ref{sec:nonFriendlyComplex}.

We construct geometric realizations of the non-kissing complex in Part~\ref{part:geometry}.
After recalling classical definitions and characterizations of simplicial fans and polytopal realizations in Section~\ref{sec:polyhedralGeometry}, we define the $\b{g}$- and $\b{c}$-vectors in Section~\ref{subsec:gcvectors}, construct the $\b{g}$-vector fan in Section~\ref{subsec:gvectorFan} and the non-kissing associahedron in Section~\ref{subsec:associahedron}.
Further geometric topics are discussed in Sections~\ref{subsec:geomLattice}~and~\ref{subsec:zonotope}.

\subsection*{Connections to recent or ongoing projects}

In an advanced stage of our project, we became aware of recent projects of other research groups which partially intersect or complete our work:
\begin{enumerate}[(i)]
\item First and foremost, T.~Br\"ustle, G.~Douville, K.~Mousavand, H.~Thomas and E.~Y\i{}ld\i{}r\i{}m also observed independently in~\cite{BrustleDouvilleMousavandThomasYildirim} that the support $\tau$-tilting complex of a gentle bound quiver is isomorphic to the non-kissing complex of its blossoming quiver (that they call fringed quiver). Their work is more oriented on the algebraic aspects of this connection.
\item Our paper is largely inspired from the paper of T.~McConville~\cite{McConville} and a preliminary version of the recent preprint of A.~Garver and T.~McConville~\cite{GarverMcConville-grid}. Although we follow the same construction for the $\b{g}$-vector fan (but in the general context of gentle bound quivers), our proof is independent and instrumental in the construction of the non-kissing associahedron.
\item Recently, L.~Demonet, O.~Iyama, N.~Reading, I.~Reiten and H.~Thomas proved that the lattice of torsion classes of any $\tau$-tilting finite algebra is congruence-uniform~\cite{DemonetIyamaReadingReitenThomas}. It seems however that a general notion of biclosed sets still remains to be found.
\end{enumerate}
We are grateful to all our colleagues for sharing their ideas with us at different preliminary stages.

\subsection*{Conventions}

We conclude by outlining certain conventions that might be unusual for the reader.
%
We let~$[n] \eqdef \{1, \dots, n\}$.
%
If~$Q$ is a quiver and~$k$ is a field, we denote by~$kQ$ the path algebra of~$Q$.
We try to denote vertices by~$u,v,w$, arrows by~$\alpha, \beta, \gamma$, strings by~$\rho, \sigma, \tau$, and walks by~$\omega, \lambda, \mu, \nu$.
Arrows are composed from left to right: if \raisebox{-.04cm}{\includegraphics[scale=.3]{composeArrows}} is a quiver, then~$\alpha\beta$ is a path while~$\beta\alpha$ is not.
Modules over an algebra are assumed to be right modules.
By these conventions, a module over~$kQ$ is equivalent to a representation of~$Q$.
%
Finally, we also stick to the following picture conventions.
The Hasse diagram of a poset is represented bottom-up and a $3$-dimensional fan is represented by the stereographic projection of its trace on the unit sphere.
Many pictures are difficult to visualize without colors; we refer the reader to the online~version.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage
\part{String modules}
\label{part:algebra}

In this section, we first fix our notations (\ref{subsec:pathAlgebra}) on quivers, path algebras, their representations, and their support $\tau$-tilting complexes (\ref{subsec:tautilting}).
We then focus on string algebras (\ref{subsec:stringGentleAlgebra} to \ref{subsec:morphismsStringModules}): following~\cite{ButlerRingel}, we present a combinatorial description of the indecomposable representations of a string algebra and of the Auslander-Reiten translation~$\tau$.
We then provide a convenient combinatorial description of the $\tau$-compatibility between string modules (\ref{sec:stringModules}).

\section{Recollections on string algebras}
\label{sec:recollectionsStringAlgebras}

\subsection{Path algebras}
\label{subsec:pathAlgebra}

We start by recalling standard notions on quivers, paths, and path algebras.
We refer to the textbooks of I.~Assem, D.~Simson and A.~Skowro\'nski~\cite{AssemSimsonSkowronski} and R.~Schiffler~\cite{Schiffler} for more details.

A \defn{quiver}~$Q$ is an oriented graph, represented by a quadruple~$(Q_0, Q_1, s, t)$ where~$Q_0$ is the set of \defn{vertices}, $Q_1$ is the set of \defn{arrows}, and~$s, t : Q_1 \to Q_0$ are the \defn{source map} and the \defn{target map} respectively.
Throughout, we always assume that~$Q$ is \defn{finite}, that is, it has only finitely many vertices and arrows.
We usually denote the vertices of~$Q$ by~$u,v,w$ and the arrows of~$Q$~by~$\alpha, \beta, \gamma$.

A \defn{path} in~$Q$ is a sequence~$\pi = \alpha_1 \dots \alpha_\ell$ of~$Q_1$ such that~$t(\alpha_k) = s(\alpha_{k+1})$ for all~${k \in [\ell-1]}$ (note that we compose arrows from left to right).
The \defn{source} (resp.~\defn{target}) of~$\pi$ is~$s(\pi) \eqdef s(\alpha_1)$ (resp.~$t(\pi) \eqdef t(\alpha_\ell)$), and the \defn{length} of~$\pi$ is~$\ell(\pi) \eqdef \ell$.
Note that for each vertex~$v \in Q_0$, we also consider the \defn{path~$\varepsilon_v$ of length zero} with source and target~$s(\varepsilon_v) = t(\varepsilon_v) = v$.

Let~$k$ denote a field.
The \defn{path algebra} of~$Q$ is the $k$-algebra~$kQ$ generated by all paths in~$Q$, and where the product of two paths is defined by~$p \cdot q = pq$ (concatenation) if~$s(p) = t(q)$ and~$p \cdot q = 0$ if~$s(p) \ne t(q)$.
Note that~$kQ$ is graded by~$kQ = \bigoplus_{\ell \ge 0} kQ_\ell$ where~$kQ_\ell$ is the subvector space generated by paths of length~$\ell$.
Observe also that~$kQ$ is finite dimensional if and only if~$Q$ is acyclic (meaning that it has no oriented cycle).

The \defn{arrow ideal} of~$kQ$ is the ideal~$R \eqdef \bigoplus_{\ell \ge 1} kQ_\ell$ generated by the arrows of~$Q$.
A two-sided ideal~$I$ of~$kQ$ is \defn{admissible} if there exists~$m \ge 2$ such that~$R^m \subseteq I \subseteq R^2$ (the condition~$R^m \subseteq I$ ensures that~$kQ/I$ is finite dimensional, and the condition~$I \subseteq R^2$ ensures that~$Q$ can be recovered form~$kQ/I$).
The pair~$\bar Q \eqdef (Q,I)$ is then called a \defn{bound quiver} and the quotient~$kQ/I$ is a \defn{bound quiver algebra} and is finite dimensional.

Two quivers~$Q = (Q_0, Q_1, s, t)$ and~$Q' = (Q_0', Q_1', s', t')$ are said to be \defn{isomorphic} if there exists $\phi \eqdef (\phi_0, \phi_1)$ where~$\phi_0 : Q_0 \to Q_0'$ and~$\phi_1 : Q_1 \to Q_1'$ are bijections such that~${s'(\phi_1(\alpha)) = \phi_0(s(\alpha))}$ and~${t'(\phi_1(\alpha)) = \phi_0(t(\alpha))}$ for all~$\alpha \in Q_1$.
The bijection~$\phi_1 : Q_1 \to Q_1'$ naturally extends to a bijection on paths by~$\phi_1(\alpha_1 \cdots \alpha_\ell) = \phi_1(\alpha_1) \cdots \phi_1(\alpha_\ell)$, and thus to a morphism~$\phi_1 : kQ \to kQ'$ of path algebras by linearity.
We say that two bound quivers~$\bar Q = (Q,I)$ and~$\bar Q' = (Q',I')$ are \defn{isomorphic} if there there is an isomorphism~$\phi = (\phi_0, \phi_1)$ between the quivers~$Q$ and~$Q'$ such that~$\phi_1(I) = I'$.

For a quiver~$Q = (Q_0, Q_1, s, t)$, define its \defn{reversed quiver} by~$\reversed{Q} \eqdef (Q_0, Q_1, t, s)$.
For a path~$\pi$ on~$Q$, define its \defn{reversed path} on~$\reversed{Q}$ by~$\reversed{(\alpha_1 \cdots \alpha_\ell)} = \alpha_\ell \cdots \alpha_1$, and extend it by linearity to a morphism~$kQ \to k\reversed{Q}$ of path algebras.
The \defn{reversed bound quiver} of a bound quiver~$\bar Q = (Q,I)$ is the bound quiver~$\reversed{\bar Q} \eqdef (\reversed{Q},\reversed{I})$.

\subsection{Auslander-Reiten theory and $\tau$-tilting theory}
\label{subsec:tautilting}

This short section is mainly meant to fix notations and recall some definitions.  The interested reader is referred to \cite{AssemSimsonSkowronski, Schiffler} for detailed accounts of Auslander-Reiten theory, and to \cite{AdachiIyamaReiten} for $\tau$-tilting theory.

\begin{definition}
Let~$k$ be a field.
A \defn{representation} of a bound quiver~$\bar Q = (Q,I)$ is a pair ${M = \big( (M_v)_{v\in Q_0}, (M_\alpha)_{\alpha\in Q_1} \big)}$, where
\begin{itemize}
\item $M_v$ is a~$k$-vector space for all~$v\in Q_0$, and
\item $M_\alpha: M_{s(\alpha)} \to M_{t(\alpha)}$ is a linear map for all~$\alpha \in Q_1$, such that~$M_\pi \eqdef M_{\alpha_\ell} \circ \dots \circ M_{\alpha_1} = 0$ for any path~$\pi = \alpha_1 \dots \alpha_\ell$ in~$I$.
\end{itemize}
%
We will always assume that representations are finite-dimensional, that is, that all the spaces~$M_v$ are finite-dimensional.

A \defn{morphism of representations}~$f:M\to N$ from a representation~$M$ to a representation~$N$ is a tuple~$f=(f_v)_{v\in Q_0}$, where
\begin{itemize}
\item $f_v:M_v\to N_v$ is a linear map for all~$v\in Q_0$, and
\item for all~$\alpha\in Q_1$, the equality~$N_\alpha \circ f_{s(\alpha)} = f_{t(\alpha)} \circ M_\alpha$ holds.
\end{itemize}
\end{definition}

Representations of a bound quiver~$\bar Q$, together with morphisms of representations, form a category~$\rep \bar Q$.
This category is equivalent to the category of finite-dimensional modules over the algebra~$kQ/I$.
As consequences of this,~$\rep \bar Q$ is abelian, has enough projective and injective objects, and thus every object of $\rep \bar Q$ admits a projective and an injective resolution.
Projective and injective representations can be explicitly computed (see, for instance, \cite[Chapter III.2]{AssemSimsonSkowronski}).
In particular, there is a canonical bijection~$v\mapsto P(v)$ from~$Q_0$ to a set of representatives for the isoclasses of indecomposable projective representations of~$\bar Q$.
Another consequence is that any representation can be written in a unique way as a direct sum of indecomposable representations, up to isomorphism.
In other words, the category~$\rep \bar Q$ satisfies the \mbox{Azuyama\,--\,Krull\,--\,Remak\,--\,Schmidt} Theorem.
In view of the above, we will often use the words ``module'' and ``representation'' to mean the same thing.

An important operation on representations is the Auslander-Reiten translation (see \cite[Chap.~IV]{AssemSimsonSkowronski}).  For an indecomposable representation~$M$, let 
\[
 P_1^M \stackrel{f^M}{\to} P_0^M \to M \to 0 
\]
be a minimal projective presentation.  Applying the \defn{Nakayama functor}~$\nu = D\circ \Hom{kQ/I}(-, kQ/I)$, where~$D = \Hom{k}(-, k)$ is the standard vector space duality, one gets a morphism between injective representations
\[
\nu P_1^M \stackrel{\nu f^M}{\longrightarrow} \nu P_0^M.
\]
\begin{definition}
 \begin{enumerate}
  \item Using the above notation, the \defn{Auslander-Reiten translation}~$\tau M$ of~$M$ is defined to be the kernel of~$\nu f^M$.
  \item \cite{AdachiIyamaReiten} A representation~$M$ is \defn{$\tau$-rigid} if~$\Hom{\bar Q}(M, \tau M) = 0$.
 \end{enumerate}
\end{definition}

It is convenient to introduce the following notation and terminology.  If~$P$ is a projective representation of~$\bar Q$, then the associated \defn{shifted projective} is the symbol~$P[1]$.  We treat~$P[1]$ as an object, and allow ourselves to form direct sums of shifted projectives with other shifted projectives and with ordinary representations of~$\bar Q$.  By convention, the shifted projectives are $\tau$-rigid.

\begin{definition}
\label{def: tau-rigid and stautilt}
With this notation, and following \cite{AdachiIyamaReiten}, we say that~$M\oplus P[1]$ is
\begin{enumerate}
 \item a \defn{$\tau$-rigid representation} if
   \begin{itemize}
     \item $M$ is a representation of~$\bar Q$ and~$P$ is a projective representation of~$\bar Q$,
     \item $M$ is~$\tau$-rigid, and
     \item $\Hom{\bar Q}(P,M) = 0$.
   \end{itemize}
 \item a \defn{support~$\tau$-tilting representation} if moreover the number of pairwise non-isomorphic indecomposable summands of $M\oplus P$ is the number of vertices of~$Q$.
\end{enumerate}
Note that~$A = kQ/I$ and~$A[1]$ are always support~$\tau$-tilting modules.
\end{definition}

\begin{definition}\label{def: tau-compatibility}
 Two representations or shifted projectives~$M, N$ of~$\bar Q$ are said to be \defn{$\tau$-compatible} precisely when $M\oplus N$ is a~$\tau$-rigid representation of~$\bar Q$.
\end{definition}

\begin{remark}
In \cite{AdachiIyamaReiten}, the notation~$(M,P)$ is used instead of~$M\oplus P[1]$.  Our choice of notation is motivated by the link between~$\tau$-rigid representations and so-called $2$-terms silting complexes.
\end{remark}

\begin{remark}
Let~$v\in Q_0$, then~$\Hom{\bar Q} \big( P(v), M \big) = 0$ if and only if~$M_v=0$. More generally, if~$v_1, \ldots, v_r$ are vertices of~$Q$, then~$\Hom{\bar Q}\big( {\oplus_{j \in [r]} P(v_j)}, M \big) = 0$ if and only if~$M_{v_j}=0$ for all~$j \in [r]$. 
\end{remark}

One of the most important results on support~$\tau$-tilting objects is the existence and uniqueness of a \defn{mutation}.

\begin{theorem}[\cite{AdachiIyamaReiten}]\label{thm: mutation of stautilts}
Let~$N = \bigoplus_{i \in [n]} N_i$ be a support~$\tau$-tilting object, where each~$N_i$ is either an indecomposable representation or a shifted indecomposable projective representation.
Then for any~${i \in [n]}$, there exists a unique indecomposable representation or shifted indecomposable projective representation~$N'_i$ not isomorphic to~$N_i$ and such that
\[
\mu_i(N) \eqdef N'_i \oplus \bigoplus_{j\neq i} N_j
\]
is a support~$\tau$-tilting object (called mutation of~$N$ at~$N_i$).
\end{theorem}

\begin{definition}\label{def: stautilt complex}
Let~$\bar Q = (Q,I)$ be a bound quiver and $A = kQ/I$ be its bound algebra.
\begin{itemize}
\item The \defn{support $\tau$-tilting complex}~$\tTC$ is the simplicial complex whose vertices are the isomorphism classes of indecomposable $\tau$-rigid or shifted projective representations of~$A$ and whose faces are the collections of representations~$\{M_1, \dots, M_k\}$ such that $M_1 \oplus \dots \oplus M_k$ is $\tau$-rigid.
\item The \defn{support $\tau$-tilting graph}~$\tTC^*$ is the dual graph of~$\tTC$ with a vertex for each isomorphism class of support $\tau$-tilting modules over~$A$ and an edge between two vertices~$T$ and~$U$ if and only if~$U$ is a mutation of~$T$.
\end{itemize}
\end{definition}

\begin{example}
 Two examples of support $\tau$-tilting graphs and support $\tau$-tilting complexes are given in Figure~\ref{fig:exmtTC}.
\end{example}

\subsection{String and gentle algebras}
\label{subsec:stringGentleAlgebra}

String algebras are a class of path algebras defined by generators and particularly nice relations.
The study of their representations goes back to \cite{GelfandPonomarev}, see also \cite{DonovanFreislich} and \cite{WaldWaschbusch}.
We will follow the general framework established in \cite{ButlerRingel}.

\begin{definition}[\cite{ButlerRingel}]
A \defn{string bound quiver}~$\bar Q \eqdef (Q,I)$ is a bound quiver such that
\begin{itemize}
\item each vertex~$v \in Q_0$ has at most two incoming and two outgoing arrows,
\item the ideal~$I$ is generated by paths,
\item for any arrow~$\beta \in Q_1$, there is at most one arrow~$\alpha \in Q_1$ such that~$t(\alpha) = s(\beta)$ and~$\alpha\beta\notin I$,
\item for any arrow~$\beta \in Q_1$, there is at most one arrow~$\gamma \in Q_1$ such that~$t(\beta) = s(\gamma)$ and~$\beta\gamma\notin I$.
\end{itemize}
The algebra~$kQ/I$ is called a \defn{string algebra}.
\end{definition}

\begin{example}
\label{exm:stringAlgebras}
We have represented in \fref{fig:exmQuiver} four examples of string bound quivers.
Throughout the paper, we draw \raisebox{-.04cm}{\includegraphics[scale=.3]{relation}} to indicate that~$\alpha\beta \in I$.

\begin{figure}[b]
	\capstart
	\centerline{
		\begin{tabular}{c@{\quad}|@{\quad}c@{\quad}|@{\quad}c@{\quad}|@{\quad}c}
			$Q = \vcenter{\hbox{\includegraphics[scale=.5]{exmQuiver1}}}$ &
			$Q = \vcenter{\hbox{\includegraphics[scale=.5]{exmQuiver2}}}$ &
			$Q = \vcenter{\hbox{\includegraphics[scale=.5]{exmQuiver3}}}$ &
			$Q = \vcenter{\hbox{\includegraphics[scale=.5]{exmQuiver4}}}$ \\[1.1cm]
			$I = (\alpha\beta, \gamma\delta)$ & 
			$I = (\alpha\beta, \gamma\delta, \alpha\delta)$ & 
			$I = (\alpha\beta, \beta\gamma, \beta^5)$ & 
			$I = (\beta\gamma)$
		\end{tabular}
	}
	\caption{Four string bound quivers. The leftmost and rightmost are gentle bound quivers.}
	\label{fig:exmQuiver}
\end{figure}
\end{example}

\begin{definition}[\cite{ButlerRingel}]
\label{def:gentleQuiver}
A \defn{gentle bound quiver}~$\bar Q \eqdef (Q,I)$ is a string bound quiver such that
\begin{itemize}
\item $I$ is generated by paths of length exactly two,
\item for any arrow~$\beta \in Q_1$, there is at most one arrow~$\alpha \in Q_1$ such that~$t(\alpha) = s(\beta)$ and~$\alpha\beta \in I$,
\item for any arrow~$\beta \in Q_1$, there is at most one arrow~$\gamma \in Q_1$ such that~$t(\beta) = s(\gamma)$ and~$\beta\gamma \in I$.
\end{itemize}
The algebra~$kQ/I$ is called a \defn{gentle algebra}.
\end{definition}

\begin{example}
In Example~\ref{exm:stringAlgebras}, only the first and last bound quivers are gentle.
\end{example}

String algebras enjoy a particularly nice representation theory: they are tame algebras (as proved in~\cite{ButlerRingel}) and their indecomposable representations are completely classified.  We will make heavy use of this classification, which we recall in the next two sections.

\subsection{Strings and bands}
\label{subsec:stringsBands}

For any arrow~$\alpha$ of any quiver~$Q$, define a formal inverse~$\alpha^{-1}$ with the properties that~$s(\alpha^{-1}) = t(\alpha)$, $t(\alpha^{-1}) = s(\alpha)$, $\alpha^{-1}\alpha = \varepsilon_{t(\alpha)}$ and~$\alpha\alpha^{-1} = \varepsilon_{s(\alpha)}$, where~$\varepsilon_v$ is the path of length zero starting and ending at the vertex~$v \in Q_0$.  Furthermore, let~$(\alpha^{-1})^{-1}=\alpha$; thus~$(-)^{-1}$ is an involution on the set of arrows and formal inverses of arrows of~$Q$.  We extend this involution to the set of all paths involving arrows or their formal inverses by further setting~$(\varepsilon_v)^{-1} = \varepsilon_v$ for all vertices~$v \in Q_0$.

\begin{definition}
\label{def:stringsBands}
Let~$\bar Q = (Q,I)$ be a string bound quiver.
\begin{enumerate}
\item A \defn{string} for~$\bar Q$ is a word of the form
\(
\rho = \alpha_1^{\varepsilon_1}\alpha_2^{\varepsilon_2}\cdots \alpha_\ell^{\varepsilon_\ell},
\)
where
	\begin{itemize}
	\item $\alpha_i \in Q_1$ and~$\varepsilon_i \in \{-1,1\}$ for all~$i \in [\ell]$,
	\item $t(\alpha_i^{\varepsilon_i}) = s(\alpha_{i+1}^{\varepsilon_{i+1}})$ for all~$i \in [\ell-1]$,
	\item there is no path~$\pi \in I$ such that~$\pi$ or~$\pi^{-1}$ appears as a factor of~$\rho$, and
	\item $\rho$ is reduced, in the sense that no factor~$\alpha\alpha^{-1}$ or~$\alpha^{-1}\alpha$ appears in~$\rho$, for~$\alpha \in Q_1$.
	\end{itemize}
The integer~$\ell$ is called the \defn{length} of the string~$\rho$.
Moreover, we still denote by~$s(\rho) \eqdef s(\alpha_1^{\varepsilon_1})$ and~$t(\rho) \eqdef t(\alpha_\ell^{\varepsilon_\ell})$ the source and target of~$\rho$.
For each vertex~$v \in Q_0$, there is also a \defn{string of length zero}, denoted by~$\varepsilon_v$, that starts and ends at~$v$.
We denote by~$\strings(\bar Q)$ the set of strings on~$\bar Q$.
We usually denote strings by~$\rho, \sigma, \tau$.
For reasons that will be explicit later, we often implicitly identify the two inverse strings~$\rho$ and~$\rho^{-1}$.
More formally, an \defn{undirected string} is a pair~$\{\rho, \rho^{-1}\}$ and we let~$\strings^\pm(\bar Q) \eqdef \set{\{\rho, \rho^{-1}\}}{\rho \in \strings(\bar Q)}$ denote the collection of all undirected strings of~$\bar Q$.

\item We call \defn{negative simple string} a formal word of length zero of the form $-v$, where $v$ is any vertex of $Q_0$. We denote by
\(
\strings^\pm_{\ge -1}(\bar Q) \eqdef \strings^\pm(\bar Q) \sqcup \set{-v}{v \in Q_0}
\)
the set of \defn{almost positive unoriented strings}.
Note that~$\varepsilon_v$ and~$-v$ are different almost positive strings.

\item A \defn{band} for~$\bar Q$ is a string~$\varpi$ of length at least one such that
	\begin{itemize}
	\item $s(\varpi) = t(\varpi)$,
	\item all powers of~$\varpi$ are strings, and
	\item $\varpi$ is not itself a power of a strictly smaller string.
	\end{itemize}

\end{enumerate}
\end{definition}

\begin{example}
\label{exm:aStringAlgebra}
For the algebra
\[
\vcenter{\hbox{\includegraphics[scale=.5]{exmQuiver5}}} \qquad I = (\beta\delta)
\]
some almost positive strings are~$-u, -v, -w, -x, \varepsilon_u$, $\varepsilon_v$, $\varepsilon_w$, $\varepsilon_x$, $\alpha^\pm$, $\beta^\pm$, $\gamma^\pm$, $\delta^\pm$, $\gamma\delta$, $\beta\gamma^{-1}$, etc. The only bands are~$\beta\gamma^{-1}\alpha$, $\alpha\beta\gamma^{-1}$, $\gamma^{-1}\alpha\beta$ and their inverses.
\end{example}

\begin{notation}
The following notation, taken from \cite{ButlerRingel}, will be useful for dealing with strings.
%
For a given string~$\rho = \alpha_1^{\varepsilon_1}\alpha_2^{\varepsilon_2}\cdots \alpha_\ell^{\varepsilon_\ell}$, we draw~$\rho$ as follows:
  \begin{itemize}
    \item draw all arrows~$\alpha_1, \ldots, \alpha_\ell$ from left to right;
    \item draw all arrows pointing downwards.
  \end{itemize}
%
Moreover, the strings~$\varepsilon_v$ of length zero are depicted simply as~$v$.
Be aware that even if the string is depicted linearly form left to right, it might have cycles since some substrings can be repeated along the string.
\end{notation}

\begin{example}
\label{exm:drawingString}
For the algebra defined in Example~\ref{exm:aStringAlgebra}, the string~$\rho = \gamma\beta^{-1}\alpha^{-1}\gamma\beta^{-1}\alpha^{-1}\gamma\delta$ is drawn as follows:
\[
\rho = \;\vcenter{\hbox{\includegraphics[scale=0.3]{exmString1}}}
\]
\end{example}

\begin{definition}
A \defn{substring} of a string~$\rho$ is a factor of~$\rho$.
Note that the position of the substring in~$\rho$ is important and that a word can appear as distinct substrings of~$\rho$ in different positions.
Observe also that we allow substrings of length~$0$, which we will abusively call \defn{vertices} of~$\rho$.
If~$u,v$ are two vertices of~$\rho$, we denote by~$\rho[u,v]$ the substring of~$\rho$ between~$u$ and~$v$.
We also abbreviate~$\rho[s(\rho),v]$ by~$\rho[\,\cdot\,,v]$ and~$\rho[u,t(\rho)]$ by~$\rho[u,\cdot\,]$.
A substring of~$\rho$ is \defn{strict} if it is distinct from~$\rho$ itself.
Finally, we denote by~$\Sigma(\rho)$ the set of all substrings~of~$\rho$.
\end{definition}

\begin{definition}
\label{def:topBottom}
A substring~$\rho = \alpha_i^{\varepsilon_i} \cdots \alpha_j^{\varepsilon_j}$ of a string~$\sigma = \alpha_1^{\varepsilon_1} \cdots \alpha_\ell^{\varepsilon_\ell}$ of~$\bar Q$ is said to be:

\begin{itemize}    
\item \defn{on top of~$\sigma$} (or a \defn{top substring of~$\sigma$}) if~$\sigma$ either ends or has an outgoing arrow at each endpoint of~$\rho$, \ie if $i = 1$ or~$\varepsilon_{i-1} = -1$, and $j = \ell$ or~$\varepsilon_{j+1} = 1$.
\item \defn{at the bottom of~$\rho$} (or a \defn{bottom substring of~$\rho$}) if~$\sigma$ either ends or has an incoming arrow at each endpoint of~$\rho$, \ie if $i = 1$ or~$\varepsilon_{i-1} = 1$, and $j = \ell$ or~$\varepsilon_{j+1} = -1$.
\end{itemize}
We denote by $\Sigma_\top(\rho)$ and~$\Sigma_\bottom(\rho)$ the sets of top and bottom substrings of~$\rho$ respectively.
Note that~$\rho$ is both in~$\Sigma_\top(\rho)$ and in~$\Sigma_\bottom(\rho)$.
\end{definition}

\begin{example}
\fref{fig:exmTopBottom} represents examples of top and bottom substrings.

\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=.3]{exmTopBottom}}
	\caption{Two top substrings (left) and two bottom substrings (right). Note that substrings of~$\rho$ can be reduced to a vertex and can end at an endpoint of~$\rho$.}
	\label{fig:exmTopBottom}
\end{figure}
\end{example}

\begin{definition}
A \defn{peak} (resp.~\defn{deep}) of a string~$\rho$ is a vertex~$v$ of~$\rho$ (substring of length~$0$) which is on top (resp.~at the bottom) of~$\rho$.
We call \defn{corners} of~$\rho$ the peaks and the deeps of~$\rho$.
A corner is \defn{strict} if it is not an endpoint of~$\rho$.
In other words, $v$ is a strict peak (resp.~deep) if the two incident arrows of~$\rho$ at~$v$ are both outgoing (resp.~incoming).
\end{definition}

\begin{example}
The string of \fref{fig:exmTopBottom} has~$4$ peaks and~$5$ deeps ($3$ of which are strict).
\end{example}

\begin{remark}
\label{rem:reverseStrings}
Note that reversing the quiver preserves the set of strings and their substrings but exchanges top with bottom:
$\Sigma(\reversed{\rho}) = \Sigma(\reversed{\rho})$ but~$\Sigma_\bottom(\reversed{\rho}) = \Sigma_\top(\rho)$ and~$\Sigma_\top(\reversed{\rho}) = \Sigma_\bottom(\rho)$.
\end{remark}

\subsection{String and band modules}
\label{subsec:stringBandModules}

Following~\cite{ButlerRingel}, we now define $A$-modules corresponding to the strings and bands of a string algebra~$A = kQ/I$.

\begin{definition}[\cite{ButlerRingel}]
Let~$\rho = \alpha_1^{\varepsilon_1}\alpha_2^{\varepsilon_2}\cdots \alpha_\ell^{\varepsilon_\ell}$ be a string for a string algebra~$A=kQ/I$.  The \defn{string module}~$M(\rho)$ is the $A$-module defined as a representation of~$Q$ as follows.

  \begin{itemize}
    \item Let~$v_0 = s(\alpha_1^{\varepsilon_1})$, and~$v_m = t(\alpha_m^{\varepsilon_m})$ for each~$m \in [\ell]$.

    \item For each vertex~$u \in Q_0$, let~$M(\rho)_u$ be the vector space with basis given by~$\{x_m \ | \ v_m = u\}$.

    \item For each arrow~$\beta$ of~$Q$, the linear map~$M(\rho)_\beta : M(\rho)_{s(\beta)} \to M(\rho)_{t(\beta)}$ is defined on the basis of~$M(\rho)_{s(\beta)}$ by
     \[
        M(\rho)_\beta(x_m) =
        \begin{cases}
			x_{m-1} & \text{if~$\alpha_{m} = \beta$ and~$\varepsilon_{m} = -1$}, \\
			x_{m+1} & \text{if~$\alpha_{m+1} = \beta$ and~$\varepsilon_{m+1} = 1$}, \\
            0 & \text{otherwise}.
       \end{cases}
     \]
  \end{itemize}
\end{definition}

It follows from the definition that for any string~$\rho$, the string modules~$M(\rho)$ and~$M(\rho^{-1})$ are isomorphic.
This explains why we will often consider undirected strings.

\begin{example}
For the algebra given in Example~\ref{exm:aStringAlgebra}, let~$\rho = \gamma\beta^{-1}\alpha^{-1}\gamma\beta^{-1}\alpha^{-1}\gamma\delta$.
Then~$M(\rho)$ is given by

\[
	\begin{overpic}[scale=0.6]{exmQuiver5bis}
	\put(8,2){$k^3$}
	\put(8,47){$k^2$}
	\put(47,25){$k^3$}
	\put(90,25){$k$}
	\put(-20,23){$\big[\!\begin{smallmatrix} 0 & 1 & 0 \\ 0 & 0 & 1 \end{smallmatrix}\!\big]$}
	\put(30,50){$\left[\!\begin{smallmatrix} 1 & 0 \\ 0 & 1 \\ 0 & 0 \end{smallmatrix}\!\right]$}
	\put(30,0){$\left[\!\begin{smallmatrix} 1 & 0 & 0 \\ 0 & 1 & 0 \\ 0 & 0 & 1 \end{smallmatrix}\!\right]$}
	\put(60,17){$[\!\begin{smallmatrix} 0 & 0 & 1 \end{smallmatrix}\!]$}
	\end{overpic}
\]
\vspace{-.2cm}
\end{example}

\begin{notation}
 \begin{itemize}
  \item For convenience, even though~$0$ is not a string by our definition, we will define~$M(0)$ to be the zero module.
  \item For any vertex~$v \in Q_0$, the projective~$P(v)$ is $M(v_\peak)$ where~$v_\peak$ is the maximal string of~$\bar Q$ with a single peak at~$v$.
  \item We will also make use of the following convention: for any~$v\in Q_0$, we let~$M(-v)$ be the shifted projective~$P(v)[1]$.
 \end{itemize}
\end{notation}

\begin{definition}[\cite{ButlerRingel}]
Let~$\varpi = \alpha_1^{\varepsilon_1}\alpha_2^{\varepsilon_2}\cdots \alpha_\ell^{\varepsilon_\ell}$ be a band for a string algebra~$A=kQ/I$.
Moreover, let~$\lambda\in k^*$, and let~$d \in \N_{>0}$.
The \defn{band module}~$M(\varpi, \lambda, d)$ is defined as follows.
  \begin{itemize}
    \item For each vertex~$v \in Q_0$, the vector space~$M(\varpi, \lambda, d)_j$ is equal to~$k^d$.
    \item For each arrow~$\gamma \in Q_1$ different from~$\alpha_\ell$, the linear map~$M(\varpi, \lambda, d)_\gamma$ is the identity.
    \item The linear map~$M(\varpi, \lambda, d)_{\alpha_\ell}$ is equal to~$J_d(\lambda^{\varepsilon_\ell})$, where
     \[
        J_d(\lambda) =
        \begin{pmatrix} 
        \lambda & 0 & \cdots & \cdots & 0 \\
        1 & \lambda & \ddots & & \vdots \\
        0 & 1 & \ddots & \ddots & \vdots \\
        \vdots & \ddots & \ddots & \lambda & 0 \\
        0 & \cdots & 0 & 1 & \lambda                                        
        \end{pmatrix}
     \]
    is the~$d\times d$ Jordan block of type~$\lambda$.
  \end{itemize}
\end{definition}

It follows from the definition that the band modules~$M(\varpi, \lambda, d)$ and~$M(\varpi^{-1}, \lambda^{-1}, d)$ are isomorphic.  Moreover, if~$\varpi$ and~$\varpi'$ are two bands that are \defn{cyclically equivalent}, in the sense that one is obtained from the other by cyclically permuting the arrows that constitute it, then we also have that~$M(\varpi, \lambda, d)$ and~$M(\varpi', \lambda, d)$ are isomorphic.

\begin{example}
For the algebra defined in Example~\ref{exm:aStringAlgebra}, let~$\varpi=\alpha\beta\gamma^{-1}$.  Then~$\varpi$ is a band, and the following are band modules

\[
	M(\varpi, \lambda, 1) = \vcenter{\hbox{
	\begin{overpic}[scale=0.6]{exmQuiver5bis}
	\put(10,2){$k$}
	\put(10,47){$k$}
	\put(49,25){$k$}
	\put(90,25){$0$}
	\put(2,23){$1$}
	\put(30,46){$1$}
	\put(30,4){$\lambda^{-1}$}
	\put(68,17){$0$}
	\end{overpic}}}
	\hspace{1cm}
	M(\varpi, \lambda, 3) = \vcenter{\hbox{
	\begin{overpic}[scale=0.6]{exmQuiver5bis}
	\put(8,2){$k^3$}
	\put(8,47){$k^3$}
	\put(47,25){$k^3$}
	\put(90,25){$0$}
	\put(0,23){$\mathrm{Id}$}
	\put(30,46){$\mathrm{Id}$}
	\put(23,-5){$\left[\!\begin{smallmatrix} \lambda^{-1} & 0 & 0 \\ 1 & \lambda^{-1} & 0 \\ 0 & 1 & \lambda^{-1} \end{smallmatrix}\!\right]$}
	\put(68,17){$0$}
	\end{overpic}}}
\]
\vspace{.5cm}
\end{example}

\begin{theorem}[{\cite[p.\,161]{ButlerRingel}}]
Assume that~$k$ is algebraically closed and consider a string algebra~$A$.
Then the string and band modules over~$A$ form a complete list of indecomposable $A$-modules, up to isomorphism.
Moreover,
  \begin{itemize}
    \item A string module is never isomorphic to a band module.
    \item Two string modules~$M(\rho)$ and~$M(\rho')$ are isomorphic if and only if~$\rho' = \rho^{\pm 1}$.
    \item Two band modules~$M(\varpi,\lambda, d)$ and~$M(\varpi', \lambda', d')$ are isomorphic if and only if~$d=d'$, and  
       \begin{itemize}
         \item either $\varpi$ is cyclically equivalent to~$\varpi'$, and~$\lambda = \lambda'$,
         \item or~$\varpi^{-1}$ is cyclically equivalent to~$\varpi'$, and~$\lambda^{-1} = \lambda'$.
       \end{itemize}
  \end{itemize}
\end{theorem}

\subsection{Auslander-Reiten translation of string modules}
\label{subsec:ARtranslationStringModules}

Our goal in this section is to describe the Auslander-Reiten translation in a string algebra.
This description requires some additional definitions and notations.

\begin{definition}
\label{def:peaksDeeps}
We say that a string~$\rho$
  \begin{itemize}
    \item \defn{starts} (resp.~\defn{ends}) \defn{on a peak} if there is no arrow~$\alpha$ such that~$\alpha \rho$ (resp.~$\rho\alpha^{-1}$) is a string,
    \item \defn{starts} (resp.~\defn{ends}) \defn{in a deep} if there is no arrow~$\alpha$ such that~$\alpha^{-1} \rho$ (resp.~$\rho \alpha$) is a string.
  \end{itemize}
\end{definition}

\begin{remark}
Definition~\ref{def:peaksDeeps} is best understood by drawing strings.  Starting (or ending) on a peak means that one cannot add an arrow at the start (or the end) of~$\rho$ such that the starting point (or ending point) of the new string would be higher in the picture than that of~$\rho$.  The same applies when replacing ``on a peak'' by ``in a deep'' and  ``higher'' by ``lower''.
\end{remark}

\begin{example}
The string in Example~\ref{exm:drawingString} starts and ends on a peak, and also ends in a deep.
\end{example}

\begin{definition}
\label{def:addingRemovingHooksCohooks}
  \begin{enumerate}
    \item Let~$\rho$ be a string that does not start on a peak. Let~$\alpha, \alpha_1, \ldots, \alpha_r$ be arrows such that~$_h \rho \eqdef \alpha_r^{-1}\cdots \alpha_1^{-1} \alpha \rho$ starts in a deep.  We say that~$_h \rho$ is obtained from~$\rho$ by \defn{adding a hook at the start of~$\rho$}.

    \item Dually, let~$\rho$ be a string that does not end on a peak.  Define $\rho_h \eqdef (_h ( \rho )^{-1} )^{-1}$ to be the string obtained by \defn{adding a hook at the end of~$\rho$}.

    %Let~$\beta, \beta_1, \ldots, \beta_r$ be arrows such that~$\rho_h \eqdef \rho \beta^{-1} \beta_1 \cdots \beta_r$ ends in a deep.  We say that~$\rho_h$ is obtained from~$\rho$ by \defn{adding a hook at the end of~$\rho$}.

    \item Let~$\rho$ be a string that does not start in a deep. Let~$\alpha, \alpha_1, \ldots, \alpha_r$ be arrows such that ${_c \rho =  \alpha_r \cdots \alpha_1 \alpha^{-1} \rho}$ starts on a peak. We say that~$_c \rho$ is obtained from~$\rho$ by \defn{adding a cohook at the start of~$\rho$}.

    \item Dually, let~$\rho$ be a string that does not end in a deep.  Define $\rho_c \eqdef (_c ( \rho )^{-1} )^{-1}$ to be the string obtained by \defn{adding a cohook at the end of~$\rho$}.

    %Let~$\beta, \beta_1, \ldots, \beta_r$ be arrows such that~${\rho_c =  \rho\beta\beta_1^{-1} \cdots \beta_r^{-1}}$ ends on a peak. We say that~$\rho_c$ is obtained from~$\rho$ by \defn{adding a cohook at the end of~$\rho$}.
  \end{enumerate}
\end{definition}

\begin{remark}
Note that in Definition~\ref{def:addingRemovingHooksCohooks}:
  \begin{enumerate}
    \item Unless~$\rho$ has length zero, the strings~$_h\rho$, $\rho_h$, $_c\rho$ and~$\rho_c$, when they are defined, are uniquely determined. If~$\rho$ has length zero, then one can exchange~$_h\rho$ with $\rho_h$ and~$_c\rho$ with~$\rho_c$.
    \item In all $4$ cases, it is possible that~$r=0$, meaning that the added hook (resp.~cohook) is restricted to a single incoming (resp.~outgoing) arrow.
  \end{enumerate}    
\end{remark}

\begin{remark}
In pictures, hooks and cohooks always look like

\bigskip
\centerline{
\begin{overpic}[scale=0.3]{exmHooksCohooks}
\put(18,-5){hooks}
\put(74,-5){cohooks}
\end{overpic}
}
\vspace{.8cm}
\end{remark}

\begin{example}
In the quiver of Example~\ref{exm:aStringAlgebra}, the string~$\rho = \gamma\beta^{-1}\alpha^{-1}\gamma\beta^{-1}\alpha^{-1}\gamma\delta$ of Example~\ref{exm:drawingString} does not start on a deep, and we have
\[
\rho = \;\vcenter{\hbox{\includegraphics[scale=0.3]{exmString1}}}
\hspace{1.3cm}
_c\rho = \;\vcenter{\hbox{\includegraphics[scale=0.3]{exmString2}}}
\]
Still in the same quiver of Example~\ref{exm:aStringAlgebra}, the string~$\rho = \delta$ does not start on a peak, and we have
\[
\rho = \;\vcenter{\hbox{\includegraphics[scale=0.3]{exmString3}}}
\hspace{1.3cm}
_h\rho = \;\vcenter{\hbox{\includegraphics[scale=0.3]{exmString4}}}
\]
\end{example}

\begin{lemma}[and Definition]
Let~$\rho$ be a string for a string bound quiver~$\bar Q$.

  \begin{enumerate}
    \item If~$\rho$ starts on a peak and is not a path in~$\bar Q$, then there exists a unique string~$\rho'$ such that~$\rho'$ does not start in a deep, and~$\rho = \phantom{}_c\rho'$. We say that~$\rho'$ is obtained by \defn{removing a cohook at the start of~$\rho$} and denote it by~$_{c^{-1}}\rho$. If~$\rho$ is a path in~$\bar Q$, then we put~$_{c^{-1}}\rho =0$.

    \item Dually, if~$\rho$ ends on a peak and is not the inverse of a path in~$\bar Q$, then define the string obtained by \defn{removing a cohook at the end of~$\rho$} as~${\rho_{c^{-1}} \eqdef (_{c^{-1}} (\rho^{-1}) )^{-1}}$.

    %then there exists a unique string~$\rho'$ such that~$\rho'$ does not end in a deep, and~$\rho = \rho'_c$. We say that~$\rho'$ is obtained by \defn{removing a cohook at the end of~$\rho$} and denote it by~$\rho_{c^{-1}}$. If~$\rho$ is the inverse of a path in~$\bar Q$, then we put~$\rho_{c^{-1}} =0$.

    \item If~$\rho$ starts in a deep and is not the inverse of a path in~$\bar Q$, then there exists a unique string~$\rho'$ such that~$\rho'$ does not start on a peak, and~$\rho = \phantom{} _h\rho'$. We say that~$\rho'$ is obtained by \defn{removing a hook at the start of~$\rho$} and denote it by~$_{h^{-1}}\rho$. If~$\rho$ is a the inverse of a path in~$\bar Q$, then we put~$_{h^{-1}}\rho =0$.

    \item Dually, if~$\rho$ ends in a deep and is not a path in~$\bar Q$, then define the string obtained by \defn{removing a hook at the end of~$\rho$} as~${\rho_{h^{-1}} \eqdef (_{h^{-1}} (\rho^{-1}) )^{-1}}$.

    %then there exists a unique string~$\rho'$ such that~$\rho'$ does not end on a peak, and~$\rho = \rho'_h$. We say that~$\rho'$ is obtained by \defn{removing a hook at the end of~$\rho$} and denote it by~$\rho_{h^{-1}}$. If~$\rho$ is a path in~$\bar Q$, then we put~$\rho_{h^{-1}} =0$.
  \end{enumerate}
\end{lemma}

\begin{example}
For the algebra defined in Example~\ref{exm:aStringAlgebra}, the string
\[
\rho = \gamma\beta^{-1}\alpha^{-1}\gamma\beta^{-1}\alpha^{-1}\gamma\delta =  \;\vcenter{\hbox{\includegraphics[scale=0.3]{exmString1}}}
\]
starts and ends on a peak, and also ends in a deep. Moreover, we have
\[
_{c^{-1}}\rho = \;\vcenter{\hbox{\includegraphics[scale=0.3]{exmString5}}}
\qquad
_{h^{-1}}\rho = \;\vcenter{\hbox{\includegraphics[scale=0.3]{exmString6}}}
\qquad
\rho_{c^{-1}} = \;\vcenter{\hbox{\includegraphics[scale=0.3]{exmString7}}}
\]
\end{example}

We now have all definitions to describe the Auslander-Reiten translate of a string module.

\begin{theorem}[\cite{ButlerRingel}]
\label{theorem: tau for strings}
Consider a string algebra~$A = kQ/I$.
The Auslander-Reiten translation transforms string modules to string modules: for a string~$\rho$ of~$\bar Q$, we have~${\tau \big( M(\rho) \big) = M(\rho')}$, where the string~$\rho'$ is obtained by following the table below.
\\[.3cm]
	\centerline{
	\begin{tabular}{|c|c|c|} 
      \hline 
      & $\rho$ does not start in a deep & $\rho$ starts in a deep \\
      \hline
      $\rho$ does not end in a deep & $\rho' = {}_c\rho_c$ & $\rho' = {}_{h^{-1}}(\rho_c)$ \\
      \hline
      $\rho$ ends in a deep & $\rho' = (_c\rho)_{h^{-1}}$ & $\rho' = {}_{h^{-1}}\rho_{h^{-1}}$ \\
      \hline
    \end{tabular}
    }
\\[.3cm]
Dually, we have~$\tau^{-1} \big( M(\rho) \big) = M(\rho'')$, where~$\rho''$ is the string given in the table below.
\\[.3cm]
	\centerline{
    \begin{tabular}{|c|c|c|} 
      \hline 
      & $\rho$ does not start on a peak & $\rho$ starts on a peak \\
      \hline
      $\rho$ does not end on a peak & $\rho'' = {}_h\rho_h$ & $\rho'' = {}_{c^{-1}}(\rho_h)$ \\
      \hline
      $\rho$ ends on a peak & $\rho'' = (_h\rho)_{c^{-1}}$ & $\rho'' = {}_{c^{-1}}\rho_{c^{-1}}$ \\
      \hline
    \end{tabular}
	}
\\[.3cm]
Finally, both the Auslander-Reiten translation~$\tau$ and its inverse~$\tau^{-1}$ preserve the band modules: for a band~$\varpi$ of~$\bar Q$, we have~$\tau \big( M(\varpi) \big) = M(\varpi) = \tau^{-1} \big( M(\varpi) \big)$.
\end{theorem}

\subsection{Morphisms between string modules}
\label{subsec:morphismsStringModules}

Morphisms between string modules can be read directly from the combinatorics of strings.  The following result is folklore in the theory.

\begin{proposition}
\label{prop:morphismsStringModules}
Let~$\rho$ and~$\rho'$ be two strings for a string algebra~$A$.
Then the dimension of the $k$-vector space~$\Hom{A} \big( M(\rho), M(\rho') \big)$ is equal to

\smallskip
\centerline{
\(
\sum\limits_{\xi \text{ string}}  (\#\textrm{ of substrings equal to~$\xi$ on top of~$\rho$}) \cdot  (\#\textrm{ of substrings equal to~$\xi$ or~$\xi^{-1}$ at the bottom of~$\rho'$}).
\)
}
\end{proposition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{$\b{g}$-vectors and $\tau$-compatibility for string modules}
\label{sec:stringModules}

\subsection{$\b{g}$-vectors}
\label{subsec:gvectors}

The following definition takes its roots in the additive categorification of cluster algebras, see \cite{DehyKeller};
it also appears naturally in the theory of $\tau$-tilting, see \cite[Sect.~5.1]{AdachiIyamaReiten}.

\begin{definition}
\label{definition: g-vector of representation}
 Let $M$ be a representation of a bound quiver $\bar Q$, and let
 \[
  P^M_1 \to P^M_0 \to M \to 0
 \]
 be a minimal projective presentation of $M$.  
 The \defn{$\b{g}$-vector} of $M$ is the element 
 \[
  \b{g}(M) = [P_0^M­] - [P_1^M]
 \]
 of the Grothendieck group $K_0(\proj \bar Q)$ of the additive category $\proj \bar Q$ of projective representations of $\bar Q$. 
 If $P$ is a projective representation, then the $\b{g}$-vector of the shifted projective $P[1]$ is $\b{g}(P[1]) \eqdef -[P]$.
\end{definition}

\begin{remark}
 A more practical way to think of $\b{g}$-vectors is by noting that $K_0(\proj \bar Q)$ is isomorphic to the free abelian group
 $\bigoplus_{v\in Q_0} \Z [P(v)] \cong \Z^{Q_0}$.  Thus, in the notation of Definition \ref{definition: g-vector of representation},
 if we put $P_0^M = \bigoplus_{v\in Q_0}P(v)^{\oplus a_v}$ and $P_1^M = \bigoplus_{v\in Q_0}P(v)^{\oplus b_v}$, 
 then
 \[
  \b{g}(M) = (a_v - b_v)_{v\in Q_0} \in \Z^{Q_0}.
 \] 
 Moreover, if $P = \bigoplus_{v\in Q_0}P(v)^{\oplus n_v}$, then $\b{g}(P[1]) = (-n_v)_{v\in Q_0}$.
\end{remark}

An application of the combinatorics of strings allows us to compute the $\b{g}$-vector of any string module.

\begin{proposition}
 Let $\bar Q$ be a string bound quiver, and let $\rho$ be a string for $\bar Q$.  
 Let $A$ be the set of vertices on top of $\rho$, and let $P(A) = \bigoplus_{v\in A} P(v)$.
 Let $B$ be the set of vertices at the bottom of $\rho$ which are not at the start or the end of $\rho$,
 and let $P(B) = \bigoplus_{v\in B} P(v)$.  Finally, let 
 \[
  R = \begin{cases}
          0 & \textrm{if $\rho$ starts and ends in a deep,} \\
          P({t(\alpha)})   & \textrm{if $\rho$ ends in a deep and $\alpha^{-1}\rho$ is a string, with $\alpha\in Q_1$,} \\
          P({t(\beta)})    & \textrm{if $\rho$ starts in a deep and $\rho\beta$ is a string, with $\beta\in Q_1$,} \\
          P({t(\alpha)}) \oplus P({t(\beta)})  & \textrm{if $\alpha^{-1}\rho\beta$ is a string, with $\alpha, \beta\in Q_1$.}
        \end{cases}
 \]
 Then a minimal projective presentation of the string module $M(\rho)$ has the form
 \[
  R\oplus P(B) \to P(A) \to M(\rho) \to 0.
 \]
\end{proposition}

\begin{corollary}
 The $\b{g}$-vector of a string module $M(\rho)$ is given by $\b{g}(M) = \b{a} - \b{b} - \b{r}$, where
 \begin{itemize}
  \item $\b{a} = (a_v)_{v\in Q_0}$, where $a_v$ is the number of times the vertex $v$ is found at the top of $\rho$;
  \item $\b{b} = (b_v)_{v\in Q_0}$, where $b_v$ is the number of times the vertex $v$ is found at the bottom of $\rho$,
        but not at its start or end;
        \medskip
  \item 
  		\(
         \b{r} = \begin{cases}
                   0 & \textrm{if $\rho$ starts and ends in a deep,} \\
                   \b{e}_{t(\alpha)}   & \textrm{if $\rho$ ends in a deep and $\alpha^{-1}\rho$ is a string, with $\alpha\in Q_1$,} \\
                   \b{e}_{t(\beta)}    & \textrm{if $\rho$ starts in a deep and $\rho\beta$ is a string, with $\beta\in Q_1$,} \\
                   \b{e}_{t(\alpha)} + \b{e}_{t(\beta)}  & \textrm{if $\alpha^{-1}\rho\beta$ is a string, with $\alpha, \beta\in Q_1$,}
                  \end{cases}
        \) \\
        \medskip
        where $(\b{e}_v)_{v \in Q_0}$ is the standard basis of~$\Z^{Q_0}$.
 \end{itemize}
\end{corollary}

\begin{definition}
Let $\bar Q$ be a string bound quiver.
\begin{enumerate}
  \item If $\rho$ is a string for $\bar Q$, we define its \defn{$\b{g}$-vector} as $\b{g}(\rho) \eqdef \b{g} \big( M(\rho) \big)$.
  \item If $-v$ is a negative simple string for $\bar Q$, we define its \defn{$\b{g}$-vector} as $\b{g}(-v) \eqdef \b{g} \big( P(v)[1] \big) = -\b{e}_v$.
\end{enumerate}
\end{definition}

\subsection{$\tau$-compatibility}
\label{subsec:compatibility}

Consider a string bound quiver~$\bar Q = (Q,I)$ and its string algebra~${A = kQ/I}$.
We now provide a combinatorial criterion for $\tau$-compatibility of string modules over~$A$.

\begin{notation}
In the diagrams of this section, we will make repeated use of the following notation:
\begin{itemize}
 \item waves~$\xy \ar@{~} (0,0);(7,0) \endxy$ mean ``any string'' (possibly of length 0);
 \item brackets~$( \hspace{1pc} )$ mean ``either empty or of the form given inside the brackets'';
 \item plain arrows have to be there;
 \item straight lines stand for hooks or cohooks and might thus be of any length (possibly~$0$);
 \item dotted arrows mean ``there exists''.
\end{itemize}
\end{notation}

\begin{definition}
\label{definition: dance and attract}
Let~$\rho$ and~$\rho'$ be two strings of~$\bar Q$. The string~$\rho$ is said to
\begin{itemize}
\item[(i)] \defn{attract}~$\rho'$ (or~$(\rho')^{-1}$) if the starting vertex~$v$ of~$\rho'$ is not a deep and there exists an arrow~$\alpha \in Q_1$ from~$v$ to~$u$ such that
	\begin{enumerate}[(a)]
	\item $\alpha^{-1}\rho'$ is a string of~$\bar Q$ and
	\item $\rho$ ends in~$u$ or contains an arrow starting at~$u$ (see Figure~\ref{fig:def-attracts});
	\end{enumerate}
\item[(ii)] \defn{dance} with~$\rho'$ (or~$(\rho')^{-1}$) if there is some common substring~$\xi$ on top of~$\rho$ and at the bottom of~$\rho'$ satisfying the swinging arms condition explained thereafter. In this definition only, we call \defn{left and right arms} of~$\rho$ (resp.~$\rho'$) the (at most) two arrows in the string~$\rho$ (resp.~$\rho'$) incident with~$\xi$. The \defn{swinging arms condition} (as illustrated in Figure~\ref{fig: swinging arms}) is the following: 
\begin{itemize}
\item if~$\rho'$ has no left arm, then~$\rho$ has a left arm~$\alpha$ and~$\alpha^{-1}\rho'$ is a string of~$\bar Q$,
\item if~$\rho'$ has no right arm, then~$\rho$ has a right arm~$\beta$ and~$\rho'\beta$ is a string of~$\bar Q$,
\end{itemize}
\end{itemize}
\begin{figure}[t]
 	\capstart
% 	\centerline{
\[
\xy
%
(28,7)*+{v}="14";
(42,7)="16";
(49,7)*+{\rho'}="17";
%
(0,0)*+{\rho}="0";
(7,0)="1";
(21,0)*+{u}="3";
%
(28,-7)*+{\bullet}="-4";
(42,-7)="-6";
%
{\ar@{~} "1";"3"};
{\ar "3";"-4"};
{\ar@{~} "-4";"-6"};
%
{\ar@{~} "14";"16"};
%
{\ar@{..>}_{\alpha} "14";"3"};
%
{\ar@/_.3pc/@{-} (23,0);(23,-9)};
{\ar@/^.3pc/@{-} (44,0);(44,-9)};
%
\endxy
\]
% 		    }
	\caption{The string~$\rho$ attracts~$\rho'$, as in Definition~\ref{definition: dance and attract} (i).}
	\label{fig:def-attracts}
\end{figure}

\begin{figure}[t]
 	\capstart
\[
\xy
%
(-35,14)*+{\rho'};
(-28,14)="-14";
(-14,14)*+{\bullet}="-12";
(-7,7)*+{\bullet}="-11";
(7,7)*+{\bullet}="11";
(14,14)*+{\bullet}="12";
(28,14)="14";
%
(0,0)*+{\xi};
%
(-35,-14)*+{\rho};
(-28,-14)="-4";
(-14,-14)*+{\bullet}="-2";
(-7,-7)*+{\bullet}="-1";
(7,-7)*+{\bullet}="1";
(14,-14)*+{\bullet}="2";
(28,-14)="4";
%
{\ar@{~} "-14";"-12"};
{\ar "-12";"-11"};
{\ar@{~} "-11";"11"};
{\ar "12";"11"};
{\ar@{~} "12";"14"};
%
{\ar@/_.3pc/@{-} (-30,15);(-30,6)};
{\ar@/^.3pc/@{-} (-9,15);(-9,6)};
%
{\ar@/^.3pc/@{-} (30,15);(30,6)};
{\ar@/_.3pc/@{-} (9,15);(9,6)};
%
{\ar@/^.3pc/@{-} (-30,-15);(-30,-6)};
{\ar@/_.3pc/@{-} (-9,-15);(-9,-6)};
%
{\ar@/_.3pc/@{-} (30,-15);(30,-6)};
{\ar@/^.3pc/@{-} (9,-15);(9,-6)};
%
{\ar@{~} "-4";"-2"};
{\ar "-1";"-2"};
{\ar@{~} "-1";"1"};
{\ar "1";"2"};
{\ar@{~} "2";"4"};
%
\endxy
\]
	\caption{The string~$\rho$ dances with~$\rho'$, as in Definition~\ref{definition: dance and attract} (ii).}
	\label{fig:def-dances}
\end{figure}

\begin{figure}[t]
 	\capstart
\[
\xy
%
(-35,14)*+{\rho'};
(-28,14)="-14";
(-14,14)*+{\bullet}="-12";
(-7,7)*+{\bullet}="-11";
(7,7)*+{\bullet}="11";
%
(-14,7)*+{\textcolor{blue}{\bullet}}="a";
(-7,0)*+{\textcolor{blue}{\bullet}}="b";
(7,0)*+{\textcolor{blue}{\bullet}}="c";
(14,-7)*+{\textcolor{blue}{\bullet}}="d";
%
(-35,-14)*+{\rho};
(-28,-14)="-4";
(-14,-14)*+{\bullet}="-2";
(-7,-7)*+{\bullet}="-1";
(7,-7)*+{\bullet}="1";
(14,-14)*+{\bullet}="2";
(28,-14)="4";
%
{\ar@{~} "-14";"-12"};
{\ar^\alpha "-12";"-11"};
{\ar@{~} "-11";"11"};
%
{\ar@/^.3pc/@{-} (-30,-15);(-30,-6)};
{\ar@/_.3pc/@{-} (-9,-15);(-9,-6)};
%
{\ar@{~} "-4";"-2"};
{\ar "-1";"-2"};
{\ar@{~} "-1";"1"};
{\ar_\beta "1";"2"};
{\ar@{~} "2";"4"};
%
{\textcolor{blue}{\ar_\alpha "a";"b"}};
{\textcolor{blue}{\ar@{~} "b";"c"}};
{\textcolor{blue}{\ar^\beta "c";"d"}};
%
\endxy
\]
	\caption{The swinging arms condition, as in Definition~\ref{definition: dance and attract} (ii).}
	\label{fig: swinging arms}
\end{figure}
\end{definition}

\begin{remark}
If~$\xi$ is not reduced to a vertex, then the conditions~$\alpha^{-1}\rho'$ (resp.~$\rho'\beta$) are strings follows from the fact that~$\alpha^{-1}\xi$ (resp.~$\xi\beta$) is a substring of~$\rho$. If~$\xi$ is reduced to a vertex, then this condition is non-empty since it requires~$\alpha\beta \notin I$.
\end{remark}

We extend the relation of dancing or attracting to the set~$\strings^\pm_{\ge -1}(\bar Q) \eqdef \strings^\pm(\bar Q) \sqcup \set{-v}{v \in Q_0}$ of almost positive strings as follows.

\begin{definition}
\label{def:negativeSimpleDance}
Let $\sigma$ be a string in $\strings^\pm(\bar Q)$ and let~$v$ be a vertex of~$\bar Q$.
We say that the negative simple string $-v$ dances with the string $\sigma$ if~$v$ is a vertex of~$\sigma$.
On the other hand, no almost positive string dances with the negative simple string~$-v$.
\end{definition}

\begin{notation}
\label{not:explanationNegativeSimpleDance}
In the proposition below, we will make use of the following convention.
If~$P[1]$ is a shifted projective, then 
\begin{itemize}
\item $\Hom{A} (M, \tau P[1]) = 0$ for any representation or shifted projective~$M$,
\item $\Hom{A} (P[1], \tau M) = \Hom{A} (P,M)$ for any representation~$M$.
\end{itemize}
These choices are motivated by the isomorphism
\[
\Hom{A} (M, \tau N) \cong \Hom{K^b(\operatorname{proj} A)}(P_M, P_N[1]),
\]
where~$P_M$ and~$P_N$ are the minimal projective presentations of the representations~$M$ and~$N$.
\end{notation}

\begin{remark}
While writing up a first version of the paper, we noticed that a result similar to the following proposition can be found in~\cite{EiseleJanssensRaedschelders}. 
Since our notation and statement differ from those of~\cite{EiseleJanssensRaedschelders}, we nonetheless include a proof. We also note that, in the proof below, we work directly with modules over~$A$, while the proof in~\cite{EiseleJanssensRaedschelders} uses two-term complexes of projectives.
\end{remark}

\begin{proposition}
\label{proposition: attract or dance and tau compatibility}
Let~$\rho$ and~$\rho'$ be two almost positive strings for the string algebra~$A$ and let~$M(\rho)$ and~$M(\rho')$ be the associated string modules.
Then~$\Hom{A} \big( M(\rho), \tau M(\rho') \big) \ne 0$ if and only if~$\rho$ attracts~$\rho'$ or dances with~$\rho'$.
\end{proposition}

\begin{proof}
The case where $\rho$ or~$\rho'$ is a negative simple string directly follows from Definition~\ref{def:negativeSimpleDance} and Notation~\ref{not:explanationNegativeSimpleDance}.
We therefore assume that~$\rho$ and~$\rho'$ are positive strings.
We let~$\rho''$ be the string corresponding to~$\tau M(\rho')$ obtained from~$\rho'$ by the rules of Theorem~\ref{theorem: tau for strings}.

Assume first that~$\rho$ attracts~$\rho'$ (Figure~\ref{fig:rho attracts rho'}), and let~$\alpha$ be as in Definition~\ref{definition: dance and attract}.
Since~$\rho'$ does not start in a deep,~$\rho''$ starts at some substring~$\alpha_1\cdots\alpha_r$, where~$\alpha_r\cdots\alpha_1\alpha^{-1}$ is the cohook at the start of~$\rho'$.
Let~$0\leq k\leq r$ be maximal such that~$\alpha_k\cdots\alpha_1$ is a substring (possibly a vertex if $k=0$) of~$\rho$ ending in~$u$, where~$u$ is as in Definition~\ref{definition: dance and attract}.
By definition of a cohook,~$\alpha_k\cdots\alpha_1$ has to be on top of~$\rho$, and is at the bottom of~$\rho''$.
By Proposition~\ref{prop:morphismsStringModules}, this implies the existence of a non-zero morphism from~$M(\rho)$ to~$M(\rho'') = \tau M(\rho')$.

\begin{figure}[h]
\[
\xy
%
(7,14)="peak";
%
(0,7)*+{\rho''}="10";
(28,7)*+{v}="14";
(42,7)="16";
%
(21,0)*+{u}="3";
%
(0,-7)*+{\rho}="-0";
(7,-7)="-1";
(21,-7)*+{u}="-3";
%
(28,-14)*+{\bullet}="-14";
(42,-14)="-16";
%
{\ar@{~} "-1";"-3"};
{\ar "-3";"-14"};
{\ar@{~} "-14";"-16"};
%
{\ar@{~} "14";"16"};
%
{\ar^{\alpha} "14";"3"};
{\ar@{-} "peak";"3"};
%
{\ar@/_.3pc/@{-} (23,9);(23,0)};
{\ar@/^.3pc/@{-} (44,9);(44,0)};
%
{\ar@/_.3pc/@{-} (23,-7);(23,-16)};
{\ar@/^.3pc/@{-} (44,-7);(44,-16)};
%
\endxy
\]
    \caption{If the string~$\rho$ attracts~$\rho'$, then~$\rho''$ is of the form given above.}
    \vspace{-.5cm}
    \label{fig:rho attracts rho'}
\end{figure}

Assume now that~$\rho$ dances with~$\rho'$, and let~$\xi$ be as in Definition~\ref{definition: dance and attract}.
We distinguish four cases:

\begin{enumerate}[(a)]
\item If~$\rho'=\xi$ (see Figure~\ref{fig:dance case a}). Then~$\rho'$ does not start and does not end in a deep so that ${\rho''= \alpha_r\cdots\alpha_1\alpha^{-1}\rho'\beta\beta_1^{-1}\cdots\beta_s^{-1}}$, where~$\alpha_r\cdots\alpha_1\alpha^{-1}$ and~$\beta\beta_1^{-1}\cdots\beta_s^{-1}$ are cohooks for~$\rho'$.
 By assumption, ~$\alpha^{-1}\rho'\beta$ is a substring of~$\rho$. Let~$0\leq i\leq r$ and~$0\leq j\leq s$ be maximal such that~$\alpha_i\cdots\alpha_1\alpha^{-1}\rho'\beta\beta_1^{-1}\cdots\beta_j^{-1}~$ is a substring of~$\rho$.
 This substring is on top of~$\rho$ and at the bottom of~$\rho''$, which shows that~$\Hom{A} \big( M(\rho), \tau M(\rho') \big) \ne 0$ by Proposition~\ref{prop:morphismsStringModules}.

\begin{figure}[h]
 	\capstart
\[
\xy
%
(7,14)="lpeak";
(63,14)="rpeak";
%
(0,7)*+{\rho''}="10";
(28,7)="14";
(42,7)="16";
%
(21,0)="3";
(49,0)="7";
%
{\ar@{~}^{\rho'} "14";"16"};
%
{\ar^{\alpha} "14";"3"};
{\ar@{-} "lpeak";"3"};
%
{\ar_{\beta} "16";"7"};
{\ar@{-} "rpeak";"7"};
%
\endxy
\]
    \caption{The string~$\rho''$, when~$\rho$ dances with~$\rho'$ and~$\rho'=\xi$ as in case (a).}
    \vspace{-.5cm}
    \label{fig:dance case a}
\end{figure}

\item If there are arrows~$\alpha, \beta$ such that~$\alpha\xi\beta^{-1}$ is a substring of~$\rho'$ (see Figure~\ref{fig:dance case b}).
 Then~$\rho''$ contains~$(\alpha)\xi(\beta^{-1})$ where the brackets have to be understood as follows:~$\rho''$ either contains~$\xi\beta^{-1}$ or ends in~$\xi$ and either contains~$\alpha\xi$ or starts at~$\xi$.
 In any case,~$\xi$ is at the bottom of~$\rho''$. Since~$\xi$ is at the top of~$\rho$ by assumption, we have~$\Hom{A} \big( M(\rho), \tau M(\rho') \big)\neq 0$ by Proposition~\ref{prop:morphismsStringModules}.

\begin{figure}[h]
 	\capstart
\[
\xy
%
(-35,14)*+{\rho'};
(-28,14)="-14";
(-14,14)*+{\bullet}="-12";
(-7,7)*+{\bullet}="-11";
(7,7)*+{\bullet}="11";
(14,14)*+{\bullet}="12";
(28,14)="14";
%
{\ar@{~} "-14";"-12"};
{\ar^{\alpha} "-12";"-11"};
{\ar@{~}^{\xi} "-11";"11"};
{\ar_{\beta} "12";"11"};
{\ar@{~} "12";"14"};
%
\endxy
\]
    \caption{When~$\rho$ dances with~$\rho'$ and~$\rho'$ contains a substring~$\alpha\xi\beta^{-1}$ as in case (b).}
    \vspace{-.5cm}
    \label{fig:dance case b}
\end{figure}

\item If~$\rho'$ is of the form~$\xi\beta^{-1}\sigma$ (for some~$\beta\in Q_1$ and some substring~$\sigma$) and satisfies the swinging arms condition of Definition~\ref{definition: dance and attract}\,(ii) (see Figure~\ref{fig:dance case c}).
 Then the beginning of~$\rho''$ is~$c\xi(\beta^{-1})$, where~$c$ is a cohook for~$\rho'$. Note that the swinging arms condition ensures that the cohook~$c$ ends in~$\alpha^{-1}$.
 One concludes, similarly as in case (a), that there is some substring on top of~$\rho$ which is at the bottom of~$\rho''$, so that~$\Hom{A} \big( M(\rho), \tau M(\rho') \big) \ne 0$ by Proposition~\ref{prop:morphismsStringModules}.

 \begin{figure}[h]
 	\capstart
\[
\xy
%
(-35,7)*+{\rho''};
(-28,14)="peak";
(-14,5)*+{c};
(-14,0)="-12";
(-7,7)*+{\bullet}="-11";
(7,7)*+{\bullet}="11";
(14,14)*+{\bullet}="12";
(28,14)="14";
%
(-35,-14)*+{\rho};
(-28,-14)="-4";
(-14,-14)*+{\bullet}="-2";
(-7,-7)*+{\bullet}="-1";
(7,-7)*+{\bullet}="1";
(14,-14)*+{\bullet}="2";
(28,-14)="4";
%
{\ar@{-} "peak";"-12"};
{\ar^{\alpha} "-11";"-12"};
{\ar@{~}^\xi "-11";"11"};
{\ar^{\beta} "12";"11"};
{\ar@{~} "12";"14"};
%
{\ar@/^.3pc/@{-} (30,15);(30,6)};
{\ar@/_.3pc/@{-} (9,15);(9,6)};
%
{\ar@/_.3pc/@{-} (30,-16);(30,-7)};
{\ar@/^.3pc/@{-} (9,-16);(9,-7)};
%
{\ar@{~} "-4";"-2"};
{\ar^{\alpha} "-1";"-2"};
{\ar@{~}^\xi "-1";"1"};
{\ar "1";"2"};
{\ar@{~} "2";"4"};
%
\endxy
\]
    \caption{When~$\rho$ dances with~$\rho'$ and~$\rho'=\xi\beta^{-1}\sigma$ as in case (c).}
    \vspace{-.5cm}
    \label{fig:dance case c}
\end{figure}

\item If~$\rho'$ is of the form~$\sigma\alpha\xi$, then~$(\rho')^{-1}$ is as in case (c), so that~$\Hom{A} \big( M(\rho), \tau M(\rho') \big) \ne 0$.
\end{enumerate}
This concludes the proof that~$\Hom{A} \big( M(\rho), \tau M(\rho') \big) \ne 0$ when~$\rho$ attracts~$\rho'$ or dances with~$\rho'$.

\bigskip
Conversely, assume that~$\Hom{A} \big( M(\rho), \tau M(\rho') \big) \ne 0$.
Then there is some substring~$\nu$ on top of~$\rho$ and at the bottom of~$\rho''$.
Let~$\xi$ be the longest substring common to~$\nu$ and~$\rho'$.
We again distinguish three cases:

\begin{enumerate}[(a)]
\item If~$\xi$ is empty (see Figure~\ref{fig:not tau compatible case a}).
The substring~$\nu$ has to be contained in some cohook for~$\rho'$.
We may assume that it is a left cohook.
The string~$\rho''$ is of the form~$\rho''= \alpha_r\cdots\alpha_1(\alpha^{-1}\sigma)$ where~$\alpha_r\cdots\alpha_1\alpha^{-1}$ is a left cohook for~$\rho'$.
(We note that removing a right hook to~$\rho'_c$ might remove~$\alpha^{-1}$ from~$\rho''$, which explains the brackets).
In particular,~$\rho'$ does not end in a deep.
Moreover,~$\nu$ does not intersect~$\rho'$ so that it is of the form~$\alpha_i\cdots\alpha_1$, for some~$0\leq i \leq r$.
Here, we use the following convention: let~$v$ be the source of~$\alpha$ and~$u$ be its target; then~$i=0$ means that~$\nu = u$.
Since~$\rho'$ starts at~$v$ and~$\nu$ is on top of~$\rho$, we deduce that~$\rho$ attracts~$\rho'$.

\begin{figure}[h]
 	\capstart
\[
\xy
%
(0,0)*+{\rho''};
(7,7)="1";
(11.8,2.2)*+{w}="2";
(21,-7)*+{u}="3";
(28,0)*+{v}="4";
(42,0)="6";
%
{\ar@{-} "1";"2"};
{\ar@{-}_{\nu} "2";"3"};
{\ar^{\alpha} "4";"3"};
{\ar@{~} "4";"6"};
%
{\ar@/^.3pc/@{-} (23,-9);(23,2)};
{\ar@/_.3pc/@{-} (43,-9);(43,2)};
%
(32,7)*+{v\in \rho'\ssm\nu};
%
%
%
(55,0)*+{\rho};
(63,-4)="11";
(70,-4)="12";
(77,2)*+{w}="13";
(88,-7)*+{u}="14";
(95,-14)*+{\bullet}="15";
(104,-14)="16";
%
{\ar@{~} "11";"12"};
{\ar "13";"12"};
{\ar@{-}^{\nu} "13";"14"};
{\ar "14";"15"};
{\ar@{~} "15";"16"};
%
{\ar@/^.3pc/@{-} (62,-6);(62,2)};
{\ar@/_.3pc/@{-} (75,-6);(75,2)};
%
{\ar@/_.3pc/@{-} (90,-7);(90,-16)};
{\ar@/^.3pc/@{-} (105,-7);(105,-16)};
%
\endxy
\]
    \caption{When~$\Hom{A} \big( M(\rho), \tau M(\rho') \big) \ne 0$, case (a).}
    \label{fig:not tau compatible case a}
\end{figure}

\item If~$\xi=\nu$. By Lemma~\ref{lemma: xi equals nu} below and the fact that~$\xi$ is on top of~$\rho$, we have that~$\rho$ dances with~$\rho'$.

\item Assume now that~$\xi$ is a non-empty strict substring of~$\nu$. Since~$\xi$ is not all of~$\nu$, at least one cohook was added to~$\rho'$ when forming~$\rho''$. We distinguish two cases:

\begin{enumerate}[(c1)]
\item If~$\nu$ intersects exactly one cohook that was added to~$\rho'$ (see Figure~\ref{fig: not tau compatible case c1}).
By symmetry, we may assume that it is a left cohook.
In that case,~$\rho'$ does not start in a deep and~$\rho''$ is of the form~$\rho''=\alpha_r\cdots\alpha_1\alpha^{-1}\xi(\beta^{-1}\sigma)$ for some substring~$\sigma$, some arrow~$\beta$ and some cohook~$\alpha_r\cdots\alpha_1\alpha^{-1}$.
Moreover, there is some~$0\leq i\leq r$ such that~$\nu=\alpha_i\cdots\alpha_1\alpha^{-1}\xi$.
The proof of Lemma~\ref{lemma: xi equals nu} shows that~$\rho'$ is of the form~$\xi\beta^{-1}\sigma'$.
Since~$\nu$ is on top of~$\rho$, we have~$\rho=\rho_1\alpha^{-1}\xi(\beta\rho_2)$ for some substrings~$\rho_1,\rho_2$ and some arrow~$\beta$.
This shows that~$\rho$ dances with~$\rho'$ (we note that the swinging arms condition is satisfied).

\begin{figure}[h]
 	\capstart
\[
\xy
%
(-35,7)*+{\rho''};
(-28,14)="peak";
(-14,0)="-12";
(-7,7)*+{\bullet}="-11";
(7,7)*+{\bullet}="11";
(14,14)*+{\bullet}="12";
(28,14)="14";
%
(-35,-14)*+{\rho};
(-28,-7)="-4";
(-21,-7)="-3";
(-14,-14)="-2";
(-7,-7)*+{\bullet}="-1";
(7,-7)*+{\bullet}="1";
(14,-14)*+{\bullet}="2";
(28,-14)="4";
%
{\ar@{-} "peak";"-12"};
{\ar^{\alpha} "-11";"-12"};
{\ar@{~}^\xi "-11";"11"};
{\ar^{\beta} "12";"11"};
{\ar@{~}^\sigma "12";"14"};
%
{\ar@/^.3pc/@{-} (30,15);(30,6)};
{\ar@/_.3pc/@{-} (9,15);(9,6)};
%
{\ar@/_.3pc/@{-} (30,-16);(30,-7)};
{\ar@/^.3pc/@{-} (9,-16);(9,-7)};
%
{\ar@{~} "-4";"-3"};
{\ar@{-} "-3";"-2"};
{\ar^{\alpha} "-1";"-2"};
{\ar@{~}^\xi "-1";"1"};
{\ar "1";"2"};
{\ar@{~} "2";"4"};
%
%
%
(-35,24)*+{\rho'};
(-7,21)*+{\bullet}="-21";
(7,21)*+{\bullet}="21";
(14,28)*+{\bullet}="22";
(28,28)="24";
%
{\ar@{~}^\xi "-21";"21"};
{\ar^{\beta} "22";"21"};
{\ar@{~}^{\sigma'} "22";"24"};
%
\endxy
\]
    \caption{Case (c1): the string~$\nu$ intersects exactly one cohook.}
    \label{fig: not tau compatible case c1}
    \vspace{-.3cm}
\end{figure}

\item Assume that~$\nu$ intersects two cohooks that where added to~$\rho'$ (see Figure~\ref{fig: not tau compatible case c2}).
In that case,~$\rho''$ is of the form~$\rho''=\alpha_r\cdots\alpha_1\alpha^{-1}\xi\beta\beta_1^{-1}\cdots\beta_s^{-1}$ where~$\alpha_r\cdots\alpha_1\alpha^{-1}$ and~$\beta\beta_1^{-1}\cdots\beta_s^{-1}$ are cohooks for~$\xi$.
Then~$\rho'=\xi$ does not start nor end in a deep.
Moreover,~$\nu$ is at the bottom of~$\rho''$ so that it contains~$\alpha^{-1}\xi\beta$.
The string~$\rho$ also contains~$\alpha^{-1}\xi\beta$ and therefore dances with~$\xi=\rho'$.

\begin{figure}[h]
 	\capstart
\[
\xy
%
(-35,7)*+{\rho''};
(-28,14)="lpeak";
(-14,0)="-12";
(-7,7)*+{\bullet}="-11";
(7,7)*+{\bullet}="11";
(14,0)="12";
(28,14)="rpeak";
%
(-35,-14)*+{\rho};
(-28,-14)="-4";
(-14,-14)*+{\bullet}="-2";
(-7,-7)*+{\bullet}="-1";
(7,-7)*+{\bullet}="1";
(14,-14)*+{\bullet}="2";
(28,-14)="4";
%
{\ar@{-} "lpeak";"-12"};
{\ar_{\alpha} "-11";"-12"};
{\ar@{~}^{\xi=\rho'} "-11";"11"};
{\ar^{\beta} "11";"12"};
{\ar@{-} "12";"rpeak"};
%
{\ar@{~} "-4";"-2"};
{\ar_{\alpha} "-1";"-2"};
{\ar@{~}^\xi "-1";"1"};
{\ar^\beta "1";"2"};
{\ar@{~} "2";"4"};
%
\endxy
\]
    \caption{Case (c2): the string~$\nu$ intersects two cohooks.}
    \label{fig: not tau compatible case c2}
\end{figure}
%
\vspace*{-1.2cm}
\qedhere
\end{enumerate}
\end{enumerate}
\end{proof}

\begin{lemma}\label{lemma: xi equals nu}
Let~$\rho'$ be a string for~$A$ and~$\rho''$ be the string obtained when computing~$\tau M(\rho')$ as in Theorem~\ref{theorem: tau for strings}.
Assume that~$\xi$ is a substring common to~$\rho'$ and~$\rho''$, and that~$\xi$ is at the bottom of~$\rho''$.
Then~$\rho'$ has a substring of the form~$\alpha\xi\beta^{-1}$, for some arrows~$\alpha, \beta$.
\end{lemma}

\begin{figure}[h]
 	\capstart
\[
\xy
%
(-37,10.5)*+{\rho''};
(-28,14)="-14";
(-14,14)*+{\bullet}="-12";
(-7,7)*+{\bullet}="-11";
(7,7)*+{\bullet}="11";
(14,14)*+{\bullet}="12";
(28,14)="14";
%
{\ar@{~}^{\sigma_1} "-14";"-12"};
{\ar^{\!\!\gamma} "-12";"-11"};
{\ar@{~}^{\xi} "-11";"11"};
{\ar_{\delta\!\!} "12";"11"};
{\ar@{~}^{\sigma_2} "12";"14"};
%
{\ar@/^.3pc/@{-} (-29,5);(-29,16)};
{\ar@/_.3pc/@{-} (-9,5);(-9,16)};
%
{\ar@/^.3pc/@{-} (9,5);(9,16)};
{\ar@/_.3pc/@{-} (29,5);(29,16)};
%
%
%
(-37,-2)*+{\rho'};
(-28,0)="-4";
(-14,0)*+{\bullet}="-2";
(-7,-7)*+{\bullet}="-1";
(7,-7)*+{\bullet}="1";
(14,0)*+{\bullet}="2";
(28,0)="4";
%
{\ar@{~} "-4";"-2"};
{\ar^{\alpha} "-2";"-1"};
{\ar@{~}^{\xi} "-1";"1"};
{\ar_{\beta} "2";"1"};
{\ar@{~} "2";"4"};
%
{\ar@/^.2pc/@{-} (-28,-2);(-28,2)};
{\ar@/_.2pc/@{-} (-16.5,-2);(-16.5,2)};
%
{\ar@/_.2pc/@{-} (28,-2);(28,2)};
{\ar@/^.2pc/@{-} (16.5,-2);(16.5,2)};
%
\endxy
\]
    \caption{A substring~$\xi$ at the bottom of~$\rho''$ which is also a substring of~$\rho$.}
    \label{fig: xi equals nu}
    \vspace{-.3cm}
\end{figure}

\begin{proof}
 Since~$\xi$ is at the bottom of~$\rho''$, we have~$\rho''=(\sigma_1\gamma)\xi(\delta^{-1}\sigma_2)$, for some substrings~$\sigma_1,\sigma_2$ and arrows~$\gamma,\delta$.
 If the substring~$\gamma$ (resp.~$\delta^{-1}$) belongs to the string~$\rho''$, then it already belongs to the string~$\rho'$.
 Indeed, adding a cohook to~$\rho'$ cannot create~$\gamma$ nor~$\delta^{-1}$ as in the string~$\rho''$.
 If~$\gamma$ does not appear in the string~$\rho''$, then~$\rho''$ starts by~$\xi$.
 Since~$\xi$ also appears in~$\rho'$, the string~$\rho'$ is of the form~$h\xi\sigma_3$ for some substring~$\sigma_3$ and some hook~$h$.
 In particular,~$\rho'$ contain a substring of the form~$\alpha\xi$.
 In case~$\delta^{-1}$ does not appear in~$\rho''$, a similar argument shows that some~$\xi\beta^{-1}$ is a substring of~$\rho'$.
\end{proof}

\begin{corollary}
\label{coro: stautilt complex from strings}
The support $\tau$-tilting complex of~$\bar Q$ is isomorphic to the clique complex of the graph whose vertices are the unoriented strings of~$\bar Q$ and whose edges link two strings which do not attract nor dance with each other.
\end{corollary}

\begin{remark}
The criterion of Proposition \ref{proposition: attract or dance and tau compatibility} for $\tau$-compatibility between string modules can be compared with a similar criterion obtained recently in \cite{CanakciPauksztelloSchroll} for the existence of extensions between two string modules.
The similarity between the two criteria is explained by the Auslander--Reiten formula asserting that $\Ext{}^1(N,M)$ is a quotient of the space $\Hom{}(M,\tau N)$ (see \cite[Theorem IV.2.13]{AssemSimsonSkowronski}).
\end{remark}

\begin{example}
Two examples of support~$\tau$-tilting complexes of gentle algebras, illustrating Corollary~\ref{coro: stautilt complex from strings}, are shown in Figure~\ref{fig:exmtTC}.
The support~$\tau$-tilting complexes of the gentle algebras for all connected gentle bound quivers with~$2$ vertices are illustrated on \fref{fig:all2}.

\begin{figure}[h]
	\capstart
	\centerline{\includegraphics[scale=.5]{exmtTC}}
	\caption{The support $\tau$-tilting complex~$\tTC$ (left) and its dual graph (right). The string module~$M(\rho)$ is represented by the string~$\rho$ of~$\bar Q$ and the preprojective module~$P(v)[1]$ is represented by a hollow vertex at~$v$.}
	\label{fig:exmtTC}
\end{figure}
\end{example}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage
\part{The non-kissing complex}
\label{part:combinatorics}

This section focuses on the non-kissing complex of a gentle bound quiver, defined as the clique complex of a non-kissing relation among walks in a blossoming version of the quiver~(\ref{sec:blossomingQuivers}).
We prove combinatorially that this complex is a pseudomanifold~(\ref{sec:nonKissingComplex}), introducing along the way the definitions of distinguished walks, arrows and substrings~(\ref{subsec:distinguished}) and the operation of flips~(\ref{subsec:flips}) that will be fundamental tools all throughout the paper.
We then prove the motivating result of this paper, namely that the support $\tau$-tilting complex is isomorphic to the non-kissing complex for any gentle bound quiver~(\ref{sec:nkcvsttc}).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Blossoming quivers}
\label{sec:blossomingQuivers}

\subsection{Blossoming quiver of a gentle bound quiver}
\label{subsec:blossomingQuiver}

Let~${\bar Q = (Q,I)}$ be a gentle bound quiver.
Denote by~$\indeg(v) \eqdef |t^{-1}(v)|$ and~$\outdeg(v) \eqdef |s^{-1}(v)|$ the \defn{in-} and \defn{out-degrees} of a vertex~${v \in Q_0}$ and by~$\deg(v) \eqdef \indeg(v) + \outdeg(v)$ its \defn{degree}.
We start by completing~$\bar Q$ such that each vertex gets four neighbors.

\begin{definition}
The \defn{blossoming quiver} of a gentle bound quiver~${\bar Q = (Q,I)}$ is the gentle bound quiver~$\bar Q\blossom \eqdef (Q\blossom, I\blossom)$ obtained by adding at each vertex~$v \in Q_0$:
\begin{itemize}
\item $2-\indeg(v)$ incoming arrows and~$2-\outdeg(v)$ outgoing arrows,
\item relations such that vertex~$v$ fulfills the gentle bound quiver conditions of Definition~\ref{def:gentleQuiver}.
\end{itemize}
Note that each vertex of~$Q_0$ has precisely two incoming and two outgoing arrows in~$Q\blossom$.
The vertices of~$Q\blossom_0 \ssm Q_0$ are called \defn{blossom vertices}, and the arrows~$Q\blossom_1 \ssm Q_1$ are called \defn{blossom arrows}.
\end{definition}

\begin{example}
A gentle bound quiver~$\bar Q\ex$ and its blossoming gentle bound quiver~$\bar Q\ex\blossom$ are represented in \fref{fig:exmBlossomingQuiver}.
\vspace*{-.4cm}

\begin{figure}[h]
	\capstart
	\centerline{\includegraphics[scale=.7]{exmBlossomingQuiver}}
	\caption{A gentle bound quiver~$\bar Q\ex$~(left) and its blossoming gentle bound quiver~$\bar Q\blossom\ex$~(right). Blossom vertices are white and blossom edges are thin.}
	\label{fig:exmBlossomingQuiver}
\end{figure}
\end{example}

The following lemma is immediate and left to the reader.
See \fref{fig:exmBlossomingQuiver} for an example.

\begin{lemma}
The number of vertices and arrows of the blossoming quiver~$Q\blossom$ are given by
\[
|Q\blossom_0| = |Q_0| + 2\Delta = 5|Q_0|-2|Q_1|
\qquad\text{while}\qquad
|Q\blossom_1| = |Q_1| + 2\Delta = 4|Q_0|-|Q_1|,
\]
where
\[
\Delta \eqdef 2|Q_0| - |Q_1| = \frac{1}{2} \sum_{v \in Q_0} \big( 4-\deg(v) \big) = \sum_{v \in Q_0} \big( 2-\indeg(v) \big) = \sum_{v \in Q_0} \big( 2-\outdeg(v) \big)
\]
is the number of incoming (or equivalently outgoing) blossom arrows of~$\bar Q\blossom$.
\end{lemma}

%By definition, any arrow~$\alpha \in Q_1$ is incident with~$6$ other arrows of~$Q\blossom_1$ denoted as follows
%
%\medskip
%\begin{center}
%\begin{tikzpicture}
%	\node[inner sep = 1pt] (x) at (0,0) {$\bullet$};
%	\node[inner sep = 1pt] (y) at (1.5,-1.5) {$\bullet$};
%	\node[label={right: = \defn{target incompatible}}] (tai) at (1,1) {$\tai(\alpha)$};
%	\node[label={left: \defn{target compatible} = }] (tac) at (-1,1) {$\tac(\alpha)$};
%	\node[label={left: \defn{cosource} = }] (cso) at (-1,-1) {$\cso(\alpha)$};
%	\node[label={left: \defn{source incompatible} = }] (soi) at (0.5,-2.5) {$\soi(\alpha)$};
%	\node[label={right: = \defn{source compatible}}] (soc) at (2.5,-2.5) {$\soc(\alpha)$};
%	\node[label={right: = \defn{cotarget}}] (cta) at (2.5,-0.5) {$\cta(\alpha)$};
%    \path [->] (x) edge node[above right] {$\alpha$} (y);
%    \path [->] (tai) edge (x);
%    \path [->] (tac) edge (x);
%    \path [->] (x) edge (cso);
%    \path [->] (cta) edge (y);
%    \path [->] (y) edge (soc);
%    \path [->] (y) edge (soi);
%	\draw pic[draw, angle eccentricity=1.2, angle radius=.4cm]{angle=y--x--tai};
%	\draw pic[draw, angle eccentricity=1.2, angle radius=.4cm]{angle=tac--x--cso};
%	\draw pic[draw, angle eccentricity=1.2, angle radius=.4cm]{angle=soc--y--cta};
%	\draw pic[draw, angle eccentricity=1.2, angle radius=.4cm]{angle=x--y--soi};
%\end{tikzpicture}
%\end{center}
%Here, $\tai$ (resp.~$\tac$, resp.~$\cta$) stand for \defn{target incompatible} (resp.~\defn{target compatible}, resp.~\defn{cotarget}), and similarly for sources.

Note that any arrow~$\alpha \in Q_1$ is incident with~$6$ other arrows of~$Q\blossom_1$.
Therefore, any~$\alpha \in Q_1$ can be continued to a string both at its source and target in two ways (switching or not orientation).
It follows that a string in~$\bar Q\blossom$ is maximal if and only if it joins two blossom vertices of~$\bar Q\blossom$.

\begin{definition}
A \defn{walk} of~$\bar Q$ is a maximal string in~$\bar Q\blossom$ (thus joining two blossom vertices of~$\bar Q\blossom$).
We denote by~$\walks(\bar Q)$ the set of all walks on~$\bar Q$.
Note that~$\walks(\bar Q)$ is finite if and only if~$\bar Q$ has a relation in any non-kissing cycle.
As for strings, we often implicitly identify the two inverse walks~$\omega$ and~$\omega^{-1}$, and we let~$\walks^\pm(\bar Q) \eqdef \set{\{\omega, \omega^{-1}\}}{\omega \in \walks(\bar Q)}$ denote the set of undirected~walks.
\end{definition}

\begin{example}
\fref{fig:exmFacet} shows many examples of walks on the gentle quiver~$\bar Q\ex$ of \fref{fig:exmBlossomingQuiver}.
\end{example}

\begin{definition}
\label{def:substrings}
We call \defn{substring} of a walk~$\omega \in \walks(\bar Q)$ the strings of~$\strings(\bar Q)$ which are factors of~$\omega$.
We insist on the fact that we forbid the blossom endpoints of~$\omega$ to belong to a substring of~$\omega$.
We denote by~$\Sigma(\omega)$ the set of substrings of~$\omega$ and by~$\Sigma_\top(\omega)$ and~$\Sigma_\bottom(\omega)$ the sets of top and bottom substrings of~$\omega$ respectively.
We use the same notations for undirected walks (of course, substrings of an undirected walk are undirected).
\end{definition}

\begin{definition}
\label{def:straightBended}
A walk~$\omega$ is \defn{straight} if it has no corner (\ie if~$\omega$ or~$\omega^{-1}$ is a path in~$\bar Q\blossom$), and \defn{bending} otherwise. Let $\straightWalks(\bar Q)$ and~$\bendingWalks(\bar Q)$ denote the sets of straight and bending walks of~$\bar Q$ and let~$\straightWalks^\pm(\bar Q) \eqdef \set{\{\omega, \omega^{-1}\}}{\omega \in \straightWalks(\bar Q)}$ and~$\bendingWalks^\pm(\bar Q) \eqdef \set{\{\omega, \omega^{-1}\}}{\omega \in \bendingWalks(\bar Q)}$.
\end{definition}

\begin{definition}
\label{def: deep walk}
A \defn{peak walk} (resp.~\defn{deep walk}) is a walk that switches orientation only once, at a peak (resp.~deep). For~$v \in Q_0$, we denote by~$v_\peak$ the peak walk with peak at~$v$ and by~$v_\deep$ the deep walk with deep~at~$v$.
\end{definition}

\begin{remark}
\label{rem:reverseBlossomingQuiver}
Observe that blossoming and reversing commute:~$(\reversed{\bar Q})\blossom = \reversed{(\bar Q\blossom)}$.
In particular, the undirected walks in~$\bar Q$ coincide with the undirected walks in~$\reversed{\bar Q}$.
However, bottom and top substrings are reversed: $\Sigma_\bottom(\reversed{\omega}) = \reversed{\big( \Sigma_\top(\omega) \big)}$ and~$\Sigma_\top(\reversed{\omega}) = \reversed{\big( \Sigma_\bottom(\omega) \big)}$.
\end{remark}

\subsection{Dissection and grid bound quivers}
\label{subsec:dissectionGridQuivers}

\begin{figure}[b]
	\capstart
	\centerline{$\vcenter{\hbox{\includegraphics[scale=1.2]{exmDissection}}}$ \hspace*{1.5cm}~$\vcenter{\hbox{\includegraphics[scale=.45]{exmGrid}}}$}
	\caption{A dissection bound quiver~$\bar Q(D)$~(left) and a grid bound quiver~$\bar Q(L)$~(right), together with their blossoming quivers.}
	\label{fig:dissectionGridQuivers}
\end{figure}

\enlargethispage{.2cm}
Throughout the paper, we will illustrate our results with two specific families of gentle bound quivers:

\para{Dissection quivers}
The following is motivated by the works of Y.~Baryshnikov~\cite{Baryshnikov}, F.~Chapoton~\cite{Chapoton-quadrangulations}, and A.~Garver and T.~McConville~\cite{GarverMcConville}.
% could even do dissections on surfaces/orbifolds.
Consider a convex polygon~$P$ and a \defn{dissection}~$D$ of~$P$, \ie a collection of pairwise non-crossing internal diagonals of~$P$.
%Maximal dissections are called \defn{triangulations} as they decompose~$P$ into triangles.
The \defn{dissection bound quiver} of~$D$ is the gentle bound quiver~$\bar Q(D)$ with a vertex for each diagonal of~$D$, with an arrow connecting any two diagonals of~$D$ that are counterclockwise consecutive edges of a cell of~$D$, and with a relation between any two arrows connecting three counterclockwise consecutive edges of a cell of~$D$.
Note that the blossoming quiver~$\bar Q\blossom(D)$ of~$\bar Q(D)$ is obtained similarly by considering as well the boundary edges of the polygon~$P$ (however, observe that a boundary edge whose endpoints are both incident to a diagonal of~$D$ should be duplicated into two distinct blossom vertices).
See \fref{fig:dissectionGridQuivers}\,(left).
Note that the walks of~$\bar Q(D)$ correspond to the diagonals joining two blossom vertices of~$\bar Q\blossom(D)$ and intersecting a connected set of diagonals of~$D$.
These diagonals are called \defn{accordion diagonals} of~$D$ in~\cite{MannevillePilaud-accordion} (they correspond to accordions in~$D$).
%\begin{itemize}
%\item the strings of~$\bar Q(D)$ are the \defn{accordions} in~$D$ (\ie sets~$A$ of edges such that two particular cells of~$D$ contain one diagonal of~$A$ while all other cells contain either~$2$ or~$0$ diagonals~of~$A$),
%\item the walks of~$\bar Q(D)$ correspond to the maximal accordions in~$D \cup P$, the accordions in~$D$ starting and ending at a boundary edge of~$P$.
%\end{itemize}

\para{Grid quivers}
The following is motivated by the works of T.~K.~Petersen, P.~Pylyavskyy and D.~Speyer for staircase shapes~\cite{PetersenPylyavskyySpeyer}, of F.~Santos, C.~Stump and V.~Welker on Grassmann associahedra~\cite{SantosStumpWelker}, and of T.~McConville~\cite{McConville} and A.~Garver and T.~McConville~\cite{GarverMcConville-grid} for arbitrary grid bound quivers.
Consider a connected subset~$L$ of the integer grid~$\Z^2$.
The \defn{grid bound quiver} of~$L$ is the gentle bound quiver~$\bar Q(L)$ obtained as the induced subgraph of the grid where edges are oriented in the direction of the increasing coordinates (meaning north and east), and with a relation for each length~$2$ path with a vertical and a horizontal steps.
The blossoming quiver~$\bar Q\blossom(L)$ of~$\bar Q(L)$ is obtained similarly by considering as well the neighbors of~$L$ (however, observe that a vertex of the grid with two or more neighbors in~$L$ should be duplicated into two or more distinct blossom vertices).
See \fref{fig:dissectionGridQuivers}\,(right) for an illustration.
Note that the walks of~$\bar Q(L)$ correspond to the maximal south-east lattice paths in~$\bar Q\blossom(L)$.
%\begin{itemize}
%\item the strings of~$\bar Q(L)$ are the south-east lattice paths in~$L$,
%\item the walks of~$\bar Q(L)$ correspond to the maximal south-east lattice paths in~$\bar Q\blossom(L)$.
%\end{itemize}

\para{Oriented paths}
Some quivers are simultaneously dissection and grid bound quivers. This is in particular the case of any oriented path, which is both the dissection bound quiver of an acyclic triangulation (with no internal triangle) and the grid bound quiver of a ribbon of~$\Z^2$. This is illustrated in \fref{fig:exmBijectionAssociahedron}\,(left).

\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=1.4]{exmBijectionAssociahedron}}
	\caption{An oriented path~$\bar Q\pa$ is simultaneously a triangulation and a grid bound quiver (left). A facet of the reduced non-kissing complex~$\RNKC[\bar Q\pa]$ can be seen equivalently as a triangulation or as a collection of non-kissing south-east paths (right).}
	\label{fig:exmBijectionAssociahedron}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{The non-kissing complex}
\label{sec:nonKissingComplex}

We now define and study first elementary properties of the non-kissing complex of a quiver.
This section is inspired from previous works on grid bound quivers~\cite{PetersenPylyavskyySpeyer, SantosStumpWelker, McConville, GarverMcConville}.

\subsection{The non-kissing complex}

Let~$\bar Q = (Q,I)$ be a gentle bound quiver and~$\bar Q\blossom = (Q\blossom,I\blossom)$ denote its blossoming quiver.
The following definition is schematically illustrated in \fref{fig:kissingCrossing}\,(left).

\begin{definition}\label{def: kissing}
Let~$\omega,\omega' \in \walks^\pm(\bar Q)$ be two undirected walks on~$\bar Q$.
We say that~$\omega$ \defn{kisses}~$\omega'$ if~$\Sigma_\top(\omega) \cap \Sigma_\bottom(\omega') \ne \varnothing$, \ie if there exist a common substring~$\sigma \in \strings^\pm(\bar Q)$ of~$\omega$ and~$\omega'$ such that the arrows of~$\omega$ incident to~$\sigma$ are both outgoing while the arrows of~$\omega'$ incident to~$\sigma$ are both incoming.
We say that~$\omega$ and~$\omega'$ are \defn{kissing} if~$\omega$ kisses~$\omega'$ or~$\omega'$ kisses~$\omega$ (or both).
\end{definition}

Note that we authorize the situation where~$\sigma$ is reduced to a vertex~$v$, meaning that~$v$ is a peak of~$\omega$ and a deep of~$\omega'$.
Observe also that~$\omega$ can kiss~$\omega'$ several times, that~$\omega$ and~$\omega'$ can mutually kiss, and that~$\omega$ can kiss itself.
We denote by~$\NKWalks(\bar Q)$ the walks on~$\bar Q$ which are not self-kissing and by~$\NKWalks^\pm(\bar Q) \eqdef \set{\{\omega, \omega^{-1}\}}{\omega \in \NKWalks(\bar Q)}$ their undirected version.

\begin{figure}[b]
	\capstart
	\centerline{\includegraphics[scale=1]{kissingCrossing}}
	\caption{A schematic representation of two kissing walks (left) and two crossing walks~(right): $\omega$~kisses~$\omega'$ (left) while~$\mu$~crosses~$\nu$ (right). For the crossing walks, we have~$\mu \prec_\gamma \nu$ while~$\nu \prec_\delta \mu$.}
	\label{fig:kissingCrossing}
\end{figure}

\begin{example}
\fref{fig:exmFacet}~(left) provides examples of kissing and non-kissing walks.
%
\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=.7]{exmFacet}}
	\caption{(Left) Three walks on the quiver~$\bar Q\ex$ of \fref{fig:exmBlossomingQuiver}: the dotted red and orange walks are non-kissing, but both kiss the plain blue walk. (Right) A maximal collection~$F\ex$ of pairwise non-kissing walks on the quiver~$\bar Q\ex$: the thin light blue walks are straight, the others~are~bending.}
	\label{fig:exmFacet}
\end{figure}
\end{example}

\begin{definition}\label{def: nKc}
The \defn{non-kissing complex} of~$\bar Q$ is the simplicial complex~$\NKC$ whose faces are the collections of pairwise non-kissing walks of~$\NKWalks^\pm(\bar Q)$.
Note that self-kissing walks never appear in~$\NKC$ by definition.
In contrast, no straight walk can kiss another walk by definition, so that they appear in all facets of~$\NKC$.
We thus consider the \defn{reduced non-kissing complex}~$\RNKC$ to be the deletion of all straight walks from~$\NKC$.
\end{definition}

\begin{example}
\fref{fig:exmFacet}\,(right) shows a facet~$F\ex$ of the non-kissing complex~$\NKC[\bar Q\ex]$ for the quiver~$\bar Q\ex$ of \fref{fig:exmBlossomingQuiver}.
The reduced non-kissing complexes of all connected gentle bound quivers with~$2$ vertices are illustrated on \fref{fig:all2}.
The reduced non-kissing complexes of two gentle bound quivers with~$3$ vertices are illustrated on \fref{fig:exmNKC}\,(left).
\end{example}

\begin{example}\label{example: Fdeep Fpeak}
For any vertices~$v,w \in Q_0$:
\begin{itemize}
\item the two peak walks~$v_\peak$ and~$w_\peak$ are non-kissing,
\item the two deep walks~$v_\deep$ and~$w_\deep$ are non-kissing,
\item the peak walk~$v_\peak$ kisses the deep walk~$w_\deep$ if and only if there is an oriented path from~$v$ to~$w$ in~$\bar Q$.
\end{itemize}
Therefore, the sets~$F_\peak \eqdef \set{v_\peak}{v \in Q_0}$ and~$F_\deep \eqdef \set{v_\deep}{v \in Q_0}$ are both in~$\RNKC$.
It will follow from Corollary~\ref{coro:pure} that~$F_\peak$ and~$F_\deep$ are in fact both non-kissing facets of~$\RNKC$ that we call the \defn{peak facet} and the \defn{deep facet}.
\end{example}

\begin{example}
The non-kissing complex of the dissection and grid bound quivers introduced in Section~\ref{subsec:dissectionGridQuivers} have been studied in details in the literature:
\begin{itemize}
\item For a dissection~$D$, the non-kissing complex~$\RNKC[\bar Q(D)]$ was studied by A.~Garver and T.~McConville~\cite{GarverMcConville} and T.~Manneville and V.~Pilaud~\cite{MannevillePilaud-accordion}, motivated by preliminary works of Y.~Baryshnikov~\cite{Baryshnikov} and F.~Chapoton~\cite{Chapoton-quadrangulations} on quadrangulations. The faces of~$\RNKC[\bar Q(D)]$ correspond to sets of pairwise non-crossing accordion diagonals~of~$D$.
\item For a subset~$L$ of the integer grid~$\Z^2$, the non-kissing complex~$\RNKC[\bar Q(L)]$ was studied by T.~K.~Petersen, P.~Pylyavskyy and D.~Speyer for staircase shapes~\cite{PetersenPylyavskyySpeyer}, by F.~Santos, C.~Stump and V.~Welker on rectangular shapes~\cite{SantosStumpWelker}, and by T.~McConville~\cite{McConville} and A.~Garver and T.~McConville~\cite{GarverMcConville-grid} on arbitrary grid bound quivers. %The last two papers motivated our work.
\item The non-kissing complex of an oriented path is a simplicial associahedron. \fref{fig:exmBijectionAssociahedron}\,(right) shows the correspondence between triangulations of an $(n+3)$-gon and facets of the non-kissing complex of an $n$-path. The simplicial associahedron was introduced in early works of D.~Tamari~\cite{Tamari} and J.~Stasheff~\cite{Stasheff}, in connection to associative schemes and topological motivations.
\end{itemize}
\end{example}

\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=.5]{exmNKC}}
	\caption{The reduced non-kissing complex~$\RNKC$ (left) and the non-kissing oriented flip graph~$\NKG$ (right). The graph is oriented from bottom to top: the peak facet~$F_\peak$ appears at the bottom while the deep facet~$F_\deep$ appear on top.}
	\label{fig:exmNKC}
\end{figure}

\begin{remark}
\label{rem:reverseNKC}
For any gentle bound quivers~$\bar Q, \bar Q'$, if~$\bar Q'$ is isomorphic to either~$\bar Q$ or~$\reversed{\bar Q}$, then the non-kissing complexes~$\NKC[\bar Q]$ and~$\NKC[\bar Q']$ are isomorphic simplicial complexes.
\end{remark}

\subsection{Distinguished walks, arrows and substrings}
\label{subsec:distinguished}

%Our first task is to show that the non-kissing complex~$\NKC$ is a \defn{pseudomanifold}, \ie that it is both:
%\begin{itemize}
%\item \defn{pure}: all maximal non-kissing facets of~$\NKC$ have the same number of walks, and
%\item \defn{thin}: any codimension~$1$ non-kissing face of~$\NKC$ is contained in exactly two non-kissing facets of~$\NKC$.
%\end{itemize}
Our next task is to show that the non-kissing complex~$\NKC$ is \defn{pure}, \ie that all maximal non-kissing facets of~$\NKC$ have the same number of walks.
We follow the proof of~\cite[Thm~3.2\,(1--2)]{McConville}, but we adapt the arguments to cover our level of generality.
We introduce along the way the convenient notions of distinguished walks, arrows and substrings that will be used throughout the paper.

\begin{definition}
A \defn{marked walk}~$\omega_\star$ is a walk~$\omega = \alpha_1^{\varepsilon_1} \cdots \alpha_\ell^{\varepsilon_\ell} \in \walks(\bar Q)$ with a marked arrow~$\alpha_i^{\varepsilon_i}$.
Note that if~$\omega$ contains several occurrences of~$\alpha_i^\pm$, only one occurrence is marked.
\end{definition}

\begin{definition}
Consider an arrow~$\alpha \in Q\blossom_1$ and any two distinct non-kissing walks~$\mu_\star, \nu_\star$ marked at an occurrence of~$\alpha^\pm$.
Let~$\sigma$ denote their maximal common substring containing that occurrence of~$\alpha$.
Since~$\mu_\star \ne \nu_\star$, their common substring~$\sigma$ is strict, so that~$\mu_\star$ and~$\nu_\star$ split at least at one endpoint of~$\sigma$.
We define the \defn{countercurrent order at~$\alpha$} by~$\mu_\star \prec_\alpha \nu_\star$ when~$\mu_\star$ enters and/or exits~$\sigma$ in the direction pointed by~$\alpha$, while~$\nu_\star$ enters and/or exits~$\sigma$ in the direction opposite to~$\alpha$.
\end{definition}

\begin{example}
On the schematic illustration of \fref{fig:kissingCrossing}\,(right), the walks~$\mu$ and~$\nu$ are non-kissing and for the walks~$\mu_\star, \nu_\star$ marked at~$\gamma$ (resp.~at~$\delta$), we have~$\mu_\star \prec_\gamma \nu_\star$ (resp.~$\nu_\star \prec_\delta \mu_\star$).
\end{example}

\begin{remark}
Note that the countercurrent order~$\prec_\alpha$
\begin{itemize}
\item is well-defined: if both endpoints of~$\sigma$ are in~$Q_0$, $\mu_\star$ (resp.~$\nu_\star$) should enter and exit~$\sigma$ in the same direction since~$\mu_\star$ and~$\nu_\star$ are non-kissing;
\item is independent of the orientation of~$\mu_\star$ and~$\nu_\star$:~${\mu_\star \prec_\alpha \nu_\star \!\iff\! (\mu_\star)^{-1} \prec_\alpha \nu_\star \!\iff\! \mu_\star \prec_\alpha (\nu_\star)^{-1}}$; we thus also consider~$\prec_\alpha$ as a relation on undirected marked walks;
\item depends on which occurrence of~$\alpha$ is marked on~$\mu$ and~$\nu$.
\end{itemize}
\end{remark}

%We need the following property of~$\prec_\alpha$.

\begin{lemma}
For any face~$F$ of~$\NKC$, the countercurrent order~$\prec_\alpha$ defines a total order on the walks of~$F$ marked at an occurrence of~$\alpha$.
\end{lemma}

\begin{proof}
We prove that~$\prec_\alpha$ is transitive.
Let~$\lambda_\star$, $\mu_\star$, $\nu_\star$ be three pairwise non-kissing walks marked at an occurrence of~$\alpha$ such that~${\lambda_\star \prec_\alpha \mu_\star \prec_\alpha \nu_\star}$. Let~$v$ be a vertex where~$\lambda_\star$ and~$\mu_\star$ split. Then
%Let~$\sigma$ (resp.~$\tau$, resp.~$\rho$) denote the common substring of~$\lambda_\star$ and~$\mu_\star$ (resp.~of~$\mu_\star$ and~$\nu_\star$, resp.~of~$\lambda_\star$ and~$\nu_\star$) containing that occurrence of~$\alpha$. We distinguish two situations:
\begin{itemize}
\item either~$\nu_\star$ contains~$v$, then it must follow~$\mu_\star$ (otherwise~$\nu_\star \prec_\alpha \mu_\star$), so that~$\lambda_\star \prec_\alpha \nu_\star$.
\item or~$\nu_\star$ does not contain~$v$, then~$\nu_\star$ and~$\mu_\star$ split at a vertex~$w$ between~$\alpha$ and~$v$. Since~${\mu_\star \prec_\alpha \nu_\star}$, $\mu$ (and thus~$\lambda$) leaves~$w$ with an arrow in the same direction as~$\alpha$, while~$\nu$ leaves~$w$ with an arrow opposite to the direction of~$\alpha$, so that~$\lambda_\star \prec_\alpha \nu_\star$.
\end{itemize}
Moreover, $\prec_\alpha$ is antisymmetric by definition.
Finally, any two distinct walks of~$F$ marked at an occurrence of~$\alpha$ are comparable in~$\prec_\alpha$.
Therefore, the reflexive closure of~$\prec_\alpha$ defines a total order on the walks of~$F$ marked at an occurrence of~$\alpha$.
\end{proof}

\begin{notation}
In all pictures, we represent the walks passing through~$\alpha$ in increasing order of~$\prec_\alpha$ from the left side to the right side of~$\alpha$. See for example \fref{fig:exmFacet}\,(right).
\end{notation}

Consider now an arrow~$\alpha \in Q\blossom_1$ and a non-kissing face~$F \in \NKC$ containing the straight walk passing through~$\alpha$.
Let~$F_\alpha$ be the set of walks of~$F$ containing~$\alpha$, marked at an occurrence of~$\alpha$.
Note that~$F_\alpha \ne \varnothing$ since it contains at least the straight walk passing through~$\alpha$, marked at~$\alpha$.
Observe that this straight walk is always the minimal marked walk of~$F_\alpha$ for the order~$\prec_\alpha$, since it always agrees with the direction of~$\alpha$.
On the other hand, we can consider the maximal marked walk of~$F_\alpha$ for the order~$\prec_\alpha$.
Intuitively, it is the most countercurrent walk passing through~$\alpha$ with respect to the direction of~$\alpha$.

\begin{definition}
For an arrow~$\alpha \in Q\blossom_1$ and a non-kissing face~$F \in \NKC$ containing the straight walk passing through~$\alpha$, consider the marked walk~$\omega_\star \eqdef \max_{\prec_\alpha} F_\alpha$ and let~$\omega$ be the walk obtained by forgetting the mark in~$\omega_\star$. We say that~$\omega$ is the \defn{distinguished walk} of~$F$ at~$\alpha$ and that~$\alpha$ is a \defn{distinguished arrow} on~$\omega \in F$.
We write
\[
\distinguishedWalk{\alpha}{F} \eqdef \max\nolimits_{\prec_\alpha} F_\alpha
\qquad\text{and}\qquad
\distinguishedArrows{\omega}{F} \eqdef \set{\alpha \in \omega}{\distinguishedWalk{\alpha}{F} = \omega}.
\]
\end{definition}

\begin{example}
Distinguished arrows and walks are illustrated on \fref{fig:exmFlip}\,(left).
\end{example}

\begin{example}
For any~$v \in Q_0$, the distinguished arrows of the peak walk~$v_\peak$ in the peak facet~$F_\peak$ are the two outgoing arrows at~$v$, and the distinguished arrows of the deep walk~$v_\deep$ in the deep facet~$F_\deep$ are the two incoming arrows at~$v$.
\end{example}

The following statement extends~\cite[Thm.~3.2]{McConville}.

\begin{proposition}
\label{prop:distinguishedArrows}
For any non-kissing facet~$F \in \NKC$, each bending (resp.~straight) walk of~$F$ contains precisely~$2$ (resp.~$1$) distinguished arrows in~$F$ pointing in opposite directions (resp.~in the direction~of~the~walk).
\end{proposition}

\begin{proof}
We first prove that each walk of~$F$ contains at most one distinguished arrow in each direction.
Assume that a walk~$\omega$ has two distinguished arrows~$\alpha, \beta$ pointing in the same direction.
Orient~$\omega$ in this same direction and assume without loss of generality that~$\alpha$ appears before~$\beta$ along~$\omega$.
%Note that we also allow a priori~$\alpha, \beta$ to be different occurrences along~$\omega$ of the same arrow of~$Q\blossom_1$.
Let~$\gamma$ be the incoming arrow at~$v \eqdef s(\beta)$ such that~$\gamma\beta \in I$.
Let~$\nu \eqdef \distinguishedWalk{\gamma}{F}$ denote the distinguished walk of~$F$ at~$\gamma$, considered oriented backward~$\gamma$.
We denote by~$\sigma$ the maximal common substring of~$\omega$ and~$\nu$ (it can be reduced to~$\varepsilon_v$).
Note that~$\sigma$ cannot contain~$\alpha$ since otherwise we would have~$\omega \prec_\alpha \nu$ contradicting the assumption that~$\omega = \distinguishedWalk{\alpha}{F}$. 
Since~$\omega$ and~$\nu$ are non-kissing, $\omega$ (resp.~$\nu$) enters~$\sigma$ with an incoming (resp.~outgoing) arrow.
Let~$\mu \eqdef \omega[\,\cdot\,, v] \, \nu[v, \cdot\,]$ be the walk connecting~$s(\omega)$ to~$t(\nu)$ via~$v$, using the prefix of~$\omega$ ending at~$v$ followed by the suffix of~$\nu$ starting at~$v$.
All these notations are illustrated in \fref{fig:pure}\,(left).
We claim that~$\mu$ is non-kissing with any walk of~$F$, contradicting the maximality~of~$F$.

Assume for the sake of contradiction that there is~$\lambda \in F$ such that~$\lambda$ and~$\mu$ are kissing.
Let~$\tau$ be a maximal common substring of~$\lambda$ and~$\mu$ where they kiss.
Since~$\lambda$ does not kiss~$\omega$ nor~$\nu$ (as they all belong to~$F$), we obtain that~$\tau$ contains~$v$ and strictly contains~$\sigma$.
%To prove this claim, observe first that~$\mu$ is non-kissing with~$\omega$ and~$\nu$ (since~$\omega$ and~$\nu$ are non-kissing).
%Consider another walk~$\lambda \in F$ and assume that~$\lambda$ and~$\mu$ are kissing.
%Note that the maximal common substring~$\tau$ of~$\omega$ and~$\lambda$ containing~$v$ is non-empty (otherwise~$\lambda$ would kiss~$\omega$ or~$\nu$) and contains strictly~$\sigma$ (otherwise~$\lambda$ would kiss~$\nu$).
We now distinguish two cases (see \fref{fig:pure}\,(left)):
\begin{enumerate}[(i)]
\item If~$\lambda$ passes through~$\beta$, then it enters~$\tau$ with an outgoing arrow (since it kisses~$\mu$), contradicting the maximality of~$\omega$~in~$\prec_\beta$.
\item If~$\lambda$ passes through~$\gamma$, then it enters~$\sigma$ with an incoming arrow (since~$\tau$ strictly contains~$\sigma$), contradicting the maximality of~$\nu$ in~$\prec_\gamma$. 
\end{enumerate}
We obtained a contradiction in all cases, which shows that~$\mu$ is non-kissing with any other walk~of~$F$.

\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=1]{pure}}
	\caption{A schematic illustration of the proof of Proposition~\ref{prop:distinguishedArrows}:~$\omega$ cannot have two distinguished arrows~$\alpha, \beta$ in the same direction (left), and for each arrow~$\alpha$ on~$\omega$, there is a distinguished arrow on~$\omega$ in the direction of~$\alpha$ (right). See the proof of Proposition~\ref{prop:distinguishedArrows} for a detailed description.}
	\label{fig:pure}
\end{figure}

\smallskip
We now prove that for any arrow~$\alpha$ on a walk~$\omega$ in a face~$F$ of~$\NKC$, there is a distinguished arrow on~$\omega \in F$ in the direction of~$\alpha$.
If~$\omega$ is not the distinguished walk of~$F$ at~$\alpha$, consider~${\mu \eqdef \min_{\prec_\alpha} \set{\nu \in F_\alpha}{\omega \prec_\alpha \nu}}$.
Let~$\sigma$ denote the maximal common substring of~$\omega$ and~$\mu$ containing~$\alpha$.
Since~$\omega$ and~$\mu$ are distinct, they split at an endpoint of~$\sigma$.
At this endpoint, the arrow~$\beta$ of~$\omega$ not in~$\sigma$ points in the same direction as~$\alpha$ since~$\omega \prec_\alpha \mu$.
Let~$\lambda$ be the distinguished walk of~$F$ at~$\beta$.
If~$\lambda \ne \omega$, then~$\lambda$ either kisses~$\mu$ or contradicts the minimality of~$\mu$ among the walks~$\set{\nu \in F_\alpha}{\omega \prec_\alpha \nu}$.
See \fref{fig:pure}\,(right) for an illustration.
We conclude that~$\lambda = \omega$ has a distinguished arrow~$\beta$ in the direction of~$\alpha$.
\end{proof}

\begin{corollary}
\label{coro:pure}
The non-kissing complex~$\NKC$ is pure of dimension~$|Q_0| + \Delta = 3|Q_0|-|Q_1|$. The reduced non-kissing complex~$\RNKC$ is pure of dimension~$|Q_0|$.
\end{corollary}

\begin{proof}
Let~$b$ (resp.~$s$) be the number of bending (resp.~straight) walks in a non-kissing facet~$F$ of~$\NKC$.
Since each straight walk uses two blossom arrows of~$\bar Q\blossom$, we have~$s = \Delta = 2|Q_0|-|Q_1|$.
From Proposition~\ref{prop:distinguishedArrows}, we obtain by double counting that
\[
2b+s = |Q\blossom_1| = 4|Q_0|-|Q_1|,
\qquad\text{thus}\qquad
b = |Q_0|
\qquad\text{and}\qquad
b+s = 3|Q_0|-|Q_1|.
\qedhere
\]
\end{proof}

Since each bending walk in a non-kissing facet of~$\RNKC$ has two distinguished arrows, we can consider the substring they surround.

\begin{definition}
\label{def:distinguishedSubstring}
The \defn{distinguished string}~$\distinguishedString{\omega}{F}$ of a bending walk~$\omega$ in a non-kissing facet~$F$ of~$\NKC$ is the substring of~$\omega$ located in between the two distinguished arrows of~$\omega \in F$.
A string~${\sigma \in \strings^\pm(\bar Q)}$ is \defn{distinguishable} if there exists a walk~$\omega$ in a non-kissing facet~$F \in \NKC$ such that~$\sigma = \distinguishedString{\omega}{F}$ is the distinguished string of~$\omega \in F$.
We denote by~$\distinguishableStrings^\pm(\bar Q)$ the set of distinguishable strings~of~$\bar Q$.
\end{definition}

\begin{example}
%For any~$v \in Q_1$, the distinguished string of the peak walk~$v_\peak$ in the peak facet~$F_\peak$ is~$v$ and the distinguished string of the peak walk~$v_\peak$ in the peak facet~$F_\peak$ is~$v$.
For any~$v \in Q_1$, we have~$\distinguishedString{v_\peak}{F_\peak} = \distinguishedString{v_\deep}{F_\deep} = \varepsilon_v$.
\end{example}

Using material from Part~\ref{part:lattice}, we will characterize distinguishable strings of~$\bar Q$ in Section~\ref{subsec:distinguishableStrings}.

\medskip
We close this section by a technical lemma about distinguished arrows, which will be helpful to understand the different possible situations in Proposition~\ref{prop:flip}.

\begin{lemma}
\label{lem:weirdDistinguishedArrows}
Consider a bending walk~$\omega$ in a non-kissing facet~$F \in \NKC$.
\begin{enumerate}[(i)]
\item If a distinguished arrow~$\alpha$ of~$\omega$ is a loop, then there is a string~$\sigma$ such that~${\omega = \sigma \alpha \sigma^{-1}}$. In particular, $\omega$ cannot be distinguished at two loops.
\item If the distinguished arrows~$\alpha, \beta$ of~$\omega$ are not loops, then~$\alpha \beta \notin I$ and~$\beta \alpha \notin I$.
\end{enumerate}
\end{lemma}

\begin{proof}
For~(i), write~$\omega = \rho \sigma \alpha \sigma^{-1} \tau$ for some strings~$\rho, \sigma, \tau$ with~$\sigma$ maximal, and assume that~$\rho$ and~$\tau$ are non-empty.
Then the last arrow~$\gamma$ of~$\rho$ points towards~$\sigma$ (otherwise, by maximality of~$\sigma$, the first arrow of~$\tau$ would point outwards~$\sigma$ so that~$\omega$ would be self-kissing).
Let~$\lambda$ be the distinguished walk of~$F$ at~$\gamma$ and let~$\xi$ be the substring of~$\sigma$ contained in~$\lambda$.
Since~$\omega$ is distinguished at~$\alpha$, and since~$\alpha$ is a loop, $\xi$ is a strict substring of~$\sigma$.
Since~$\omega$ and~$\lambda$ are non-kissing, $\lambda$ (resp.~$\omega$) leaves~$\xi$ with an outgoing (resp.~incoming) arrow.
This implies that~$\lambda \prec_\gamma \omega$, a contradiction.
This shows that~$\rho = \varnothing = \tau$~and~$\omega = \sigma \alpha \sigma^{-1}$.

For~(ii), assume for example that~$\alpha\beta \in I$ and that~$\omega = \rho \alpha \sigma \tau \beta^{-1} \sigma \xi$ for some strings~$\rho, \sigma, \tau, \xi$ with~$\sigma$ maximal (we leave it to the reader to check that the other cases are similar).
Since~$\omega$ is not self-kissing, the first arrow~$\gamma$ of~$\xi$ points towards~$\sigma$.
Let~$\lambda$ be the distinguished walk of~$F$ at~$\gamma$ and let~$\zeta$ be the substring of~$\sigma$ contained in~$\lambda$.
Since~$\omega$ is distinguished at~$\alpha$ and~$\beta$, $\tau$ is a strict substring of~$\sigma$.
Since~$\omega$ and~$\lambda$ are non-kissing, $\lambda$ (resp.~$\omega$) leaves~$\zeta$ with an outgoing (resp.~incoming) arrow.
This implies that~$\lambda \prec_\gamma \omega$, a contradiction.
This shows~(ii).
\end{proof}

\subsection{Flips}
\label{subsec:flips}

\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=.7]{exmFlip}}
	\caption{The flip of the orange walk~$\omega$ in the facet~$F\ex$ of \fref{fig:exmFacet}. The other two walks~$\mu, \nu$ of~$F\ex$ involved in the flip are the yellow and green walks. The distinguished arrows on each walk of~$F\ex$ are marked with triple arrows.}
	\label{fig:exmFlip}
\end{figure}

We now show that the non-kissing complex~$\RNKC$ is \defn{thin}, \ie that any codimension~$1$ non-kissing face of~$\RNKC$ is contained in exactly two non-kissing facets of~$\RNKC$.
Here again, it is more convenient to work with the unreduced non-kissing complex~$\NKC$.
We adapt the proof of~\cite[Thm~3.2\,(3)]{McConville}.
The following statement is schematized in \fref{fig:flip}.

\begin{proposition}
\label{prop:flip}
Consider a non-kissing facet~$F \in \NKC$ and a bending walk~$\omega \in F$.
Let~$\alpha$ and~$\beta$ be the distinguished arrows of~$\omega$, and~$\sigma$ be the distinguished substring of~$\omega$, which splits~$\omega$ into~$\omega = \rho \sigma \tau$.
Let~$\alpha'$ and~$\beta'$ be the other two arrows of~$Q_1\blossom$ incident to the endpoints of~$\sigma$ and such that~$\alpha'\alpha \in I$ or~$\alpha\alpha' \in I$, and $\beta'\beta \in I$ or~$\beta\beta' \in I$.
Let~$\mu \eqdef \distinguishedWalk{\alpha'}{F \ssm \{\omega\}}$ and~$\nu \eqdef \distinguishedWalk{\beta'}{F \ssm \{\omega\}}$ be the distinguished walks of~$F \ssm \{\omega\}$ at~$\alpha'$ and~$\beta'$ respectively.
Then
\begin{enumerate}[(i)]
\item The walk~$\mu$ splits into~$\mu = \rho' \sigma \tau$ and the walk~$\nu$ splits into~$\nu = \rho \sigma \tau'$.
\item The walk~$\omega' \eqdef \rho' \sigma \tau'$ is kissing~$\omega$ but no other~walk~of~$F$. Moreover, $\omega'$ is the only other (undirected) walk besides~$\omega$ which is not kissing any other walk of~$F \ssm \{\omega\}$.
\end{enumerate}
\end{proposition}

\begin{proof}
Let~$v$ (resp.~$w$) be the endpoint of~$\sigma$ incident to~$\alpha$ and~$\alpha'$ (resp.~to~$\beta$ and~$\beta'$).
%Assume for sake of contradiction that~$\sigma \tau$ is not a final substring of~$\mu$.
The walk~$\mu$ splits into~$\rho' \mu'$ where~$t(\rho') = v$ and~$\rho'$ finishes with the marked occurrence of~$\alpha'$ along~$\mu$.
Consider the walk~$\lambda \eqdef \rho' \sigma \tau$.
We claim that~$\lambda$ is non-kissing with all walks of~$F$.
Indeed, assume that there is a walk~$\theta \in F$ kissing~$\lambda$, and let~$\xi$ denote a maximal common substring of~$\lambda$ and~$\theta$ where they kiss.
Since~$\theta$ does not kiss~$\mu$ nor~$\omega$, the substring~$\xi$ must contain~$v$.
We now distinguish two cases:
\begin{itemize}
\item If~$\theta$ contains~$\alpha$, then it enters~$\xi$ with an outgoing arrow and thus leaves~$\xi$ with an outgoing arrow as well, thus contradicting the maximality of~$\omega$ for~$\prec_\alpha$.
\item If~$\theta$ contains~$\alpha'$, then it enters~$\sigma\tau$ with an incoming arrow and thus leaves~$\sigma\tau$ with an outgoing arrow (otherwise it would kiss~$\omega$). Therefore, it enters and leaves~$\xi$ with an outgoing arrow, thus contradicting the maximality of~$\mu$~for~$\prec_{\alpha'}$.
\end{itemize}
Since both cases raise a contradiction, we obtained that~$\lambda$ is non-kissing with all walks of~$F$.
Since~$F$ is a maximal non-kissing set of walks, we obtain that~$\lambda \in F$.
Assume for contradiction that~$\lambda \ne \mu$, and let~$\xi$ be the maximal common substring of~$\mu$ and~$\omega$ containing~$v$.
Since~$\mu$ and~$\omega$ are non-kissing, and~$\mu$ enters~$\xi$ with an incoming arrow, it leaves~$\xi$ with an incoming arrow as well.
This implies that~$\mu \prec_\alpha \lambda$, contradicting the maximality of~$\mu$ for~$\prec_\alpha$.
We conclude that~$\lambda = \mu$, so that the walk~$\mu$ splits into~$\rho' \sigma \tau$ and similarly the walk~$\nu$ splits into~${\rho \sigma \tau'}$.
In particular, the string~$\sigma$ is common to~$\omega$ and~$\mu$ and~$\nu$.

We now show that no walk of~$F \ssm \{\omega\}$ can kiss~$\omega'$.
Let~$\lambda$ be a walk of~$F$ kissing~$\omega'$, and let~$\xi$ denote a maximal common substring of~$\lambda$ and~$\omega'$ where they kiss.
Since~$\lambda \in F$, it does not kiss~$\mu$ or~$\nu$, which implies that~$\xi$ contains~$\sigma$.
Assume first that~$\lambda$ enters~$\sigma$ at~$v$ by the arrow~$\alpha'$.
Since~$\lambda$ and~$\omega$ are non-kissing, it forces~$\lambda$ to leave~$\sigma$, and thus~$\xi$, at~$w$ by the arrow~$\beta$.
For~$\lambda$ and~$\omega'$ to kiss, $\lambda$ thus enters~$\xi$ with an arrow in the opposite direction of~$\beta$, which contradicts the maximality of~$\mu$ for~$\prec_{\alpha'}$.
By symmetry, we obtain that~$\lambda$ contains the arrows~$\alpha$ and~$\beta$.
Now by maximality of~$\omega$ for both orders~$\prec_\alpha$ and~$\prec_\beta$, the walks~$\lambda$ and~$\omega$ of~$F$ cannot split before~$\alpha$ or after~$\beta$.
We conclude that~$\lambda = \omega$.

Finally, we prove that~$\omega'$ is the only walk distinct from~$\omega$ which is non-kissing with any walk of~$F \ssm \{\omega\}$.
Let~$\lambda$ be a walk such that~$G = F \symdif \{\omega, \lambda\}$ is non-kissing.
Note that in the face~$F \ssm \{\omega\}$, the walk~$\mu$ is maximal for both~$\prec_{\alpha'}$ and~$\prec_\beta$, while the walk~$\nu$ is maximal for both~$\prec_\alpha$ and~$\prec_{\beta'}$.
Therefore, in the facet~$G$, the walk~$\lambda$ should have a distinguished arrow among~$\{\alpha', \beta\}$ and a distinguished arrow among~$\{\alpha, \beta'\}$.
Since~$\lambda$ cannot contain~$\{\alpha, \alpha'\}$ or~$\{\beta, \beta'\}$, this imposes that the distinguished arrows of~$\lambda$ are either~$\{\alpha, \beta\}$, or~$\{\alpha', \beta'\}$.
Assume for example that~$\lambda$ is distinguished at~$\{\alpha, \beta\}$.
If~$\lambda \ne \omega$, then~$\lambda$ and~$\omega$ are kissing by Corollary~\ref{coro:pure}.
This is incompatible with the maximality of~$\lambda$ for both~$\prec_\alpha$ and~$\prec_\beta$.
We conclude that~$\lambda = \omega$.
We obtain similarly that if~$\lambda$ is distinguished at~$\{\alpha', \beta'\}$, then~$\lambda = \omega'$.
\end{proof}

\begin{remark}
\label{rem:changeDistinguishedArrows}
For latter purposes, observe that one can update distinguished arrows when transforming~$F$ to~$F'$:
%This is computationally useful if one wants to search the flip graph (see below) and will also be helpful for latter geometric purposes.
\begin{itemize}
\item On~$\omega$ and~$\omega'$, we always have
\[
\omega = \distinguishedWalk{\alpha}{F} = \distinguishedWalk{\beta}{F}
\qquad\text{and}\qquad
\omega' = \distinguishedWalk{\alpha'}{F'} = \distinguishedWalk{\beta'}{F'}.
\]

\item On~$\mu$ and~$\nu$, be aware that two different situations can happen:
\begin{itemize}
\item If~$\alpha = \alpha'$ is a loop, then it follows from Lemma~\ref{lem:weirdDistinguishedArrows} that
\[
\mu = \nu = \distinguishedWalk{\alpha}{F \ssm \{\omega\}} = \distinguishedWalk{\beta'}{F} = \distinguishedWalk{\beta}{F'}.
\]
(The situation is symmetric when~$\beta = \beta'$ is a loop).
\item If neither~$\alpha$ nor~$\beta$ are loops, then~$\alpha, \beta, \alpha', \beta'$ are all distinct by Lemma~\ref{lem:weirdDistinguishedArrows} and
\[
\mu = \distinguishedWalk{\alpha'}{F} = \distinguishedWalk{\beta}{F'}
\qquad\text{and}\qquad
\nu = \distinguishedWalk{\alpha}{F'} = \distinguishedWalk{\beta'}{F}.
\]
Note that it can still happen that~$\mu = \nu$ or that~$\mu$ or~$\nu$ are straight walks.
\end{itemize}
\item Finally, all the other distinguished arrows on the walks of~$F \cap F'$ are preserved.
\end{itemize}
%Be aware that Proposition~\ref{prop:flip} encompasses two quite different situations:
%\begin{itemize}
%\item If~$\alpha = \alpha'$ is a loop, then
%\begin{gather*}
%\omega = \distinguishedWalk{\alpha}{F} = \distinguishedWalk{\beta}{F},
%\qquad
%\omega' = \distinguishedWalk{\alpha'}{F'} = \distinguishedWalk{\beta'}{F'},
%\\
%\text{and} \quad \mu = \nu = \distinguishedWalk{\alpha}{F \ssm \{\omega\}} = \distinguishedWalk{\beta'}{F} = \distinguishedWalk{\beta}{F'}.
%\end{gather*}
%while the distinguished arrows on all other walks of~$F \cap F'$ are preserved.
%(The situation is symmetric when~$\beta = \beta'$ is a loop).
%\item If neither~$\alpha$ nor~$\beta$ are loops, then %~$\alpha, \beta, \alpha', \beta'$ are all distinct by Lemma~\ref{} and
%\[
%\begin{array}{ccc}
%\omega = \distinguishedWalk{\alpha}{F} = \distinguishedWalk{\beta}{F}
%& \text{and} &
%\omega' = \distinguishedWalk{\alpha'}{F'} = \distinguishedWalk{\beta'}{F'}
%\\
%\mu = \distinguishedWalk{\alpha'}{F} = \distinguishedWalk{\beta}{F'}
%& \text{and} &
%\nu = \distinguishedWalk{\alpha}{F'} = \distinguishedWalk{\beta'}{F}.
%\end{array}
%\]
%while the distinguished arrows on all other walks of~$F \cap F'$ are preserved.
%However, it can still happen that~$\mu = \nu$ or that~$\mu$ or~$\nu$ (or even both) are straight walks.
%\end{itemize}
\end{remark}

%\begin{remark}
%\label{rem:changeDistinguishedArrows}
%Observe for later purposes that in the situation of Proposition~\ref{prop:flip},
%\[
%\begin{array}[b]{c@{\qquad}c@{\qquad}c}
%\omega = \distinguishedWalk{\alpha}{F} = \distinguishedWalk{\beta}{F}
%& &
%\omega' = \distinguishedWalk{\alpha'}{F'} = \distinguishedWalk{\beta'}{F'}
%\\
%\mu = \distinguishedWalk{\alpha'}{F \ssm \{\omega\}} = \distinguishedWalk{\beta}{F' \ssm \{\omega'\}}
%& \text{and} &
%\nu = \distinguishedWalk{\alpha}{F' \ssm \{\omega'\}} = \distinguishedWalk{\beta'}{F \ssm \{\omega\}},
%\end{array}
%\]
%while the distinguished arrows on all other walks of~$F \cap F'$ are preserved.
%In other words, it is straightforward to update distinguished arrows when transforming~$F$ to~$F'$.
%This is computationally useful if one wants to search the flip graph defined below.
%\end{remark}

\begin{corollary}
The non-kissing complex~$\RNKC$ is a pseudomanifold without boundary.
\end{corollary}

\begin{definition}
\label{def:flip}
The non-kissing facet~$F' \eqdef F \symdif \{\omega, \omega'\}$ is obtained from~$F$ by the \defn{flip} of~$\omega$.
We say that the flip is \defn{supported} by the common substring~$\sigma = \distinguishedString{\omega}{F} = \distinguishedString{\omega'}{F'}$ of~$\omega$ and~$\omega'$.
The facets~$F$ and~$F'$ are \defn{adjacent facets}.
The (non-kissing) \defn{flip graph} of~$\bar Q$ is the dual graph~$\NKG$ of~$\RNKC$, whose vertices are the non-kissing facets of~$\RNKC$ and whose edges are pairs of adjacent non-kissing facets.
\end{definition}

\begin{example}
\fref{fig:exmFlip} illustrates a flip in the non-kissing complex of the quiver of \fref{fig:exmBlossomingQuiver}.

\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=1]{flip}}
	\caption{A schematic representation of flips in the non-kissing complex (see Proposition~\ref{prop:flip}). The flip exchanges the walk~$\omega = \rho \sigma \tau$ in the facet~$F$ (left) with the walk~$\omega' = \rho' \sigma \tau'$ in the facet~$F'$ (middle), using the walks~$\mu = \rho' \sigma \tau = \distinguishedWalk{\alpha'}{F \ssm \{\omega\}}$ and~$\nu = \rho \sigma \tau' = \distinguishedWalk{\beta'}{F \ssm \{\omega\}}$. The walk~$\omega'$ kisses~$\omega$ but no other walk of~$F$ (right).}
	\label{fig:flip}
\end{figure}
\end{example}

%Note that since~$\omega$ and~$\omega'$ are kissing along~$\sigma$, one has two outgoing arrows while the other has two incoming arrows at the endpoints of~$\sigma$.

\begin{definition}
\label{def:increasingFlip}
\enlargethispage{.3cm}
If the common substring~$\sigma$ of~$\omega$ and~$\omega'$ is on top of~$\omega$ and at the bottom of~$\omega'$, then we say that the flip~$F \to F'$ is \defn{increasing} and that the common substring~$\sigma$ is an \defn{ascent} of~$F$ and a \defn{descent} of~$F'$.
We denote by~$\ascents(F) \subseteq \strings^\pm(\bar Q)$ and $\descents(F) \subseteq \strings^\pm(\bar Q)$ the sets of ascents and descents of~$F$ respectively.
%In the opposite situation, the flip is \defn{decreasing} and~$\sigma$ is a descent of~$F$ and an ascent of~$F'$.
\end{definition}

This provides a natural orientation of the non-kissing flip graph~$\NKG$.
We still denote by~$\NKG$ the oriented flip graph.
The purpose of Part~\ref{part:lattice} is to show that the non-kissing oriented flip graph is the Hasse diagram of a congruence-uniform lattice when~$\RNKC$ is finite.

\begin{example}
The non-kissing oriented flip graph is represented in \fref{fig:all2} for all connected gentle bound quivers with~$2$ vertices and in \fref{fig:exmNKC}\,(left) for two gentle bound quivers with~$3$ vertices.
In all pictures, graphs are oriented bottom-up.
\end{example}

\begin{example}
Oriented flip graphs were studied carefully in~\cite{GarverMcConville, MannevillePilaud-accordion, McConville} for the dissection and grid bound quivers introduced in Section~\ref{subsec:dissectionGridQuivers}.
Note that when the quiver is an oriented path~$\bar Q\pa$, a flip in a facet of the non-kissing complex~$\NKC[\bar Q\pa]$ corresponds to the classical flip of a diagonal in the corresponding triangulation (see \fref{fig:exmBijectionAssociahedron}).
Moreover, the flip is increasing if and only if the slope of the diagonal increases along the flip.
\end{example}

\begin{remark}
\label{rem:reverseFlipGraph}
Reversing all arrows reverses the orientation of the flips: $\NKG[\reversed{\bar Q}] = \reversed{\NKG[\bar Q]}$.
\end{remark}

%\subsection{Quiver of a non-kissing facet}
%
%For a non-kissing facet~$F \in \NKC$, we define a quiver with relations~$\bar Q^F \eqdef (Q^F, I^F)$ as follows:
%\begin{itemize}
%\item the vertices of~$Q^F_0$ are the walks of~$F$,
%\item there is an arrow from~$\omega$ to~$\omega'$ in~$Q^F_1$ if~$\omega \prec_\alpha \omega'$ is a cover relation of~$\prec_\alpha$ for some blossom arrow~$\alpha \in Q\blossom_1 \ssm Q_1$,
%\item for two arrows~$\alpha : \mu \to \omega$ and~$\beta : \omega \to \nu$, there is a relation~$\alpha\beta = 0$ in~$I^F$ if~$\alpha$ and~$\beta$ are not cover relations at the same blossom of~$\omega$.
%\end{itemize}
%
%\vincent{What can we say of this quiver combinatorially? It is important algebraically, see later.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Non-kissing complexes versus support $\tau$-tilting complexes}
\label{sec:nkcvsttc}

In this section, we start the dictionary of Table~\ref{table:dictionary} between algebraic notions on the support $\tau$-tilting complex of a gentle algebra and the combinatorial notions on the non-kissing complex of its blossoming quiver.

\subsection{From walks to strings}
\label{subsec:walks2strings}

Recall that $\bar Q = (Q,I)$ is a gentle bound quiver.
Since~$\bar Q$ is a subquiver of~$\bar Q\blossom$, we can identify a string~$\sigma$ of~$\bar Q$ with a string~$\sigma\blossom$ of~$\bar Q\blossom$ with endpoints in~$Q_0$.
The following lemma is immediate from the definition of a blossoming quiver.

\begin{lemma}
\label{lem:bijections-STTC-NKC}
For a directed string~$\sigma \in \strings(\bar Q)$, the string~$\sigma\blossom$ does not start or end in a deep, so that we can define a bending walk~$\omega(\sigma) = \phantom{}_c (\sigma\blossom) \phantom{}_c \in \bendingWalks^\pm(\bar Q)$.
Conversely, for a directed bending walk~$\omega \in \bendingWalks^\pm(\bar Q)$ not in the deep facet~$F_\deep$, the string~$\phantom{}_{c^{-1}} \omega \phantom{}_{c^{-1}}$ has endpoints in~$Q_0$, so that it is a string~$\sigma(\omega) \in \strings(\bar Q)$.
The induced maps
\[
\strings^\pm(\bar Q) \xrightleftharpoons[\quad\mbox{$\sigma$}\;\quad]{\mbox{$\omega$}} \bendingWalks^\pm(\bar Q) \ssm F_\deep
\]
are inverse bijections.
Putting~$\omega(-v) = v_\deep$ and~$\sigma(v_\deep) = -v$, they extend to inverse bijections
\[
\strings_{\ge-1}^\pm(\bar Q) \xrightleftharpoons[\quad\mbox{$\sigma$}\;\quad]{\mbox{$\omega$}} \bendingWalks^\pm(\bar Q).
\]
\end{lemma}

\begin{example}
\label{exm:exmBijectionStringsWalks1}
\fref{fig:exmBijectionStringsWalks1} illustrates the map~$\sigma = \omega^{-1}$ for two quivers on $3$ vertices.

\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=.4]{exmBijectionStringsWalks1}}
	\caption{The inverse bijections~$\sigma$ and~$\omega$ for two specific quivers.}
	\label{fig:exmBijectionStringsWalks1}
\end{figure}
\end{example}

\begin{remark}
In the case of gentle algebras arising from grids, the computation of the string module $M(\sigma)$ is made easier by the fact that the indecomposable representations are determined by their dimension vectors.
This dimension vector is computed by counting the number of kissings between~$\omega(\sigma)$ and the deep walks.
More precisely, for any string~$\sigma \in \strings^\pm(\bar Q)$ and any vertex~$v \in Q_0$, the dimension of~$M(\sigma)_v$ is the number of kisses between the deep walk~$v_\deep$ and the walk~$\omega(\sigma)$.
\end{remark}

\begin{lemma}\label{lem: attract or dance vs kiss}
Let~$\sigma$ and~$\sigma'$ be two strings for the gentle bound quiver~$\bar Q$.
Then~$\sigma$ attracts~$\sigma'$ or dances with~$\sigma'$ if and only if~$\omega(\sigma)$ kisses~$\omega(\sigma')$.
\end{lemma}

\begin{proof}
In this proof, we freely identify a string~$\rho$ for~$\bar Q$ with the corresponding string~$\rho\blossom$ for~$\bar Q\blossom$.

Assume that~$\sigma$ attracts~$\sigma'$.
Then~$\omega(\sigma')$ is of the form~$\alpha_r\cdots\alpha_1\alpha^{-1}\sigma'\beta\beta_1^{-1}\cdots\beta_s^{-1}$ for some~${r \geq 1}$, ${s\geq 0}$ and cohooks~$\alpha_r\cdots\alpha_1\alpha^{-1}$ and~$\beta\beta_1^{-1}\cdots\beta_s^{-1}$.
We note that the arrow~$\alpha$ is in~$Q_1$ by Definition~\ref{definition: dance and attract} and that all arrows in~$\omega(\sigma')$ belong to~$Q_1$ except for the blossoming arrows~$\alpha_r$ and~$\beta_s$.
Since the arrow~$\alpha_r$ is blossoming, there is some substring~$\alpha_i\cdots\alpha_1$, with~$0\leq i \leq r$, which is on top of~$\omega(\sigma)$ (see Figure~\ref{fig: sigma attracts sigma'}).
Here again, we use the convention that~$\alpha_i\cdots\alpha_1 = t(\alpha)= u$ if~$i=0$. 
Moreover,~$\alpha_i\cdots\alpha_1$ is at the bottom of~$\omega(\sigma')$, so that the walk~$\omega(\sigma)$ kisses~$\omega(\sigma')$.

\begin{figure}[h]
 	\capstart
\[
\xy
%
(35,10)*+{\omega(\sigma')};
(-28,14)="lpeak";
(-14,0)*+{u}="-12";
(-7,7)*+{v}="-11";
(7,7)*+{\bullet}="11";
(14,0)="12";
(28,14)="rpeak";
%
(35,-10)*+{\omega(\sigma)};
(-55,1)="1";
(-45,-9)="2";
(-40,-4)*+{\bullet}="3";
(-30,-4)*+{\bullet}="4";
(-24,3)="5";
(-14,-7)*+{u}="u";
(-7,-14)*+{\bullet}="a";
(7,-14)*+{\bullet}="b";
(14,-21)="c";
(25,-10)="d";
%
{\ar^{\alpha_r\blossom} (-32,18);"lpeak"};
{\ar@{-} "lpeak";"-12"};
{\ar_{\alpha} "-11";"-12"};
{\ar@{~}^{\sigma'} "-11";"11"};
{\ar^{\beta} "11";"12"};
{\ar@{-} "12";"rpeak"};
%
{\ar@{-} "1";"2"};
{\ar "3";"2"};
{\ar@{~} "3";"4"};
{\ar "5";"4"};
{\ar@{-} "5";"u"};
{\ar "u";"a"};
{\ar@{~} "a";"b"};
{\ar "b";"c"};
{\ar@{-} "c";"d"};
%
{\ar@/_.3pc/@{-} (-11.5,-5);(-11.5,-16)};
{\ar@/^.3pc/@{-} (8,-5);(8,-16)};
%
{\ar@/_.3pc/@{-} (-41,5);(-41,-6)};
{\ar@/^.3pc/@{-} (-25,5);(-25,-6)};
%
\endxy
\]
    \caption{The walks~$\omega(\sigma)$ and~$\omega(\sigma')$ when~$\sigma$ attracts~$\sigma'$.}
    \label{fig: sigma attracts sigma'}
\end{figure}

Assume that~$\sigma$ dances with~$\sigma'$, and let~$\xi$ be the substring on top of~$\sigma$ and at the bottom of~$\sigma'$, as in Definition~\ref{definition: dance and attract}\,(ii).
We distinguish three cases:

\begin{enumerate}[(a)]
\item If~$\xi=\sigma'$, then~$\sigma = \sigma_1\alpha^{-1}\xi\beta\sigma_2$ for some substrings~$\sigma_1,\sigma_2$ and arrows~$\alpha,\beta\in Q_1$.
As a consequence,~$\omega(\sigma')$ is of the form~$\alpha_r\cdots\alpha_1\alpha^{-1}\sigma'\beta\beta_1^{-1}\cdots\beta_s^{-1}$ for some~$r,s\geq 1$, and cohooks~$\alpha_r\cdots\alpha_1\alpha^{-1}$ and~$\beta\beta_1^{-1}\cdots\beta_s^{-1}$ where~$\alpha_r,\beta_s$ are blossoming.
There exist~$0\leq i\leq r$ and~$0\leq j\leq s$ such that~$\alpha_i\cdots\alpha_1\alpha^{-1}\xi\beta\beta_1^{-1}\cdots\beta_j^{-1}$ is a substring on top of~$\omega(\sigma)$ (see Figure~\ref{fig: dance case a}).
Since it is at the bottom of~$\omega(\sigma')$, the walk~$\omega(\sigma)$ kisses~$\omega(\sigma')$.

\item If~$\sigma'$ is of the form~$\sigma'_1\alpha\xi\beta^{-1}\sigma'_2$, then~$\omega(\sigma')$ contains~$\alpha\xi\beta^{-1}$ as a substring.
Moreover,~$\xi$ being on top of~$\sigma$,~$\omega(\sigma)$ contains some substring of the form~$\gamma^{-1}\xi\delta$.
This shows that~$\omega(\sigma)$ kisses~$\omega(\sigma')$.

\item If~$\sigma'=\sigma'_1\alpha\xi$ for some substring~$\sigma'_1$ and some arrow~$\alpha$, then~$\sigma$ is of the form~$\sigma=(\sigma_1\gamma^{-1})\xi\beta\sigma_2$, where~$\alpha\xi\beta$ is a string for~$\bar Q$.
It follows that~$\omega(\sigma)$ kisses~$\omega(\sigma')$ along some substring~$\xi\beta\beta_1^{-1}\cdots\beta_j^{-1}$ (see Figure~\ref{fig: dance case c}), where~$\beta\beta_1^{-1}\cdots\beta_j^{-1}\cdots\beta_s^{-1}$ is a cohook for~$\sigma\blossom$ and~${j>0}$.
\end{enumerate}

We now assume that $\omega(\sigma)$ kisses $\omega(\sigma')$.
Let $\xi$ be a substring which is strictly on top of $\omega(\sigma)$ and strictly at the bottom of $\omega(\sigma')$.
Note that this implies that $\xi$ is also on top of $\sigma$ (but not necessarily strictly on top).
It is possible to show that $\sigma$ attracts or dances with $\sigma'$ by using the same method as in the proof of Proposition~\ref{proposition: attract or dance and tau compatibility}.
However, we choose an alternative proof, showing instead that $\Hom{A} \big( M(\sigma), \tau M(\sigma') \big) \ne 0$, which implies the result by Proposition~\ref{proposition: attract or dance and tau compatibility}. 
Write $\omega(\sigma')=\alpha_r \cdots \alpha_1 \alpha^{-1} \sigma' \beta \beta_1^{-1} \cdots \beta_s^{-1}$ where $r,s\geq 0$, and where if $r\geq 1$, $\alpha_r$ is a blossoming arrow and $\alpha_1,\cdots,\alpha_{r-1},\alpha\in Q_1$ while if $r=0$ $\alpha$ is a blossoming arrow; and similarly for $\beta\beta_1^{-1}\cdots\beta_s^{-1}$.

Assume first that $r$ and $s$ are positive.
Then $\tau M(\sigma')$ is given by the string $\sigma''=\alpha_{r-1} \cdots \alpha_1 \alpha^{-1} \sigma' \beta \beta_1^{-1} \cdots \beta_{s-1}^{-1}$.
Thus, $\xi$ is at the bottom of $\sigma''$ and $\Hom{A} \big( M(\sigma), \tau M(\sigma') \big) \neq 0$.

Assume that exactly one of $r,s$ equals $0$.
By symmetry, we may assume that $r=0$, which is equivalent to $\sigma'$ starting in a deep.
Since $\xi$ is strictly at the bottom of $\alpha^{-1}\sigma'\beta\beta_1^{-1}\cdots\beta_s^{-1}$, it is also strictly at the bottom of $\sigma'\beta\beta_1^{-1}\cdots\beta_s^{-1}$ (see Figure~\ref{fig: r=0}).
This implies that $\xi$ is at the bottom of $_{h^{-1}}(\sigma'\beta\beta_1^{-1}\cdots\beta_{s-1}^{-1})$, so that $\Hom{A} \big( M(\sigma), \tau M(\sigma') \big) \ne 0$.

\begin{figure}[h]
 	\capstart
\[
\xy
%
(-33,16)="-14";
(-28,21)="-13";
(-14,21)="-12";
(-7,14)*+{\bullet}="-11";
(0,25)*+{\omega(\sigma')};
(7,14)*+{\bullet}="11";
(14,7)="12";
(25,18)="13";
(30,23)="14";
%
{\ar@{~} "-13";"-12"};
{\ar^{\gamma} "-12";"-11"};
{\ar@{~}^{\text{ beginning of }\xi} "-11";"11"};
{\ar_\beta "11";"12"};
{\ar@{-} "12";"13"};
{\ar_{\beta_s\blossom} "14";"13"};
%
\endxy
\]
    \caption{The walk $\omega(\sigma')$ when $r=0$ and $s>0$. The arrow $\gamma$ ``protects'' $\xi$ from being deleted when removing a left hook for $\sigma'$.}
    \label{fig: r=0}
\end{figure}

Finally, assume that $r=0$ and $s=0$.
In that case, $\xi$ is strictly at the bottom of $\sigma'$.
It is thus at the bottom of $_{h^{-1}}(\sigma')_{h^{-1}}$ and this gives a non-zero morphism in $\Hom{A} \big( M(\sigma), \tau M(\sigma') \big)$.
\end{proof}

\begin{figure}[p]
\[
\xy
%
(-33,26)="-14";
(-28,21)="-13";
(-14,7)="-12";
(-7,14)*+{\bullet}="-11";
(0,21)*+{\omega(\sigma')};
(7,14)*+{\bullet}="11";
(14,7)="12";
(25,18)="13";
(30,23)="14";
%
{\ar^{\alpha_r\blossom} "-14";"-13"};
{\ar@{-} "-13";"-12"};
{\ar^\alpha "-11";"-12"};
{\ar@{~}_\xi "-11";"11"};
{\ar_\beta "11";"12"};
{\ar@{-} "12";"13"};
{\ar_{\beta_s\blossom} "14";"13"};
%
%
(-50,-6)="-7";
(-40,-16)="-6";
(-35,-11)="-5";
(-27,-11)="-4";
(-22,-6)="-3";
(-14,-14)="-2";
(-7,-7)*+{\bullet}="-1";
(0,-14)*+{\omega(\sigma)};
(7,-7)*+{\bullet}="1";
(14,-14)="2";
(25,-3)="3";
(30,-8)="4";
(37,-8)="5";
(42,-13)="6";
(55,0)="7";
%
{\ar@{-} "-7";"-6"};
{\ar "-5";"-6"};
{\ar@{~} "-5";"-4"};
{\ar "-3";"-4"};
{\ar@{-} "-3";"-2"};
{\ar_\alpha "-1";"-2"};
{\ar@{~}^\xi "-1";"1"};
{\ar^\beta "1";"2"};
{\ar@{-} "2";"3"};
{\ar "3";"4"};
{\ar@{~} "4";"5"};
{\ar "5";"6"};
{\ar@{-} "6";"7"};
%
{\ar@/^.3pc/@{-} (-23,-5);(-23,-13)};
{\ar@/_.3pc/@{-} (-34,-5);(-34,-13)};
%
{\ar@/_.3pc/@{-} (26,-2);(26,-10)};
{\ar@/^.3pc/@{-} (36,-2);(36,-10)};
%
\endxy
\]
    \caption{The walks~$\omega(\sigma)$ and~$\omega(\sigma')$ when~$\sigma$ dances with~$\sigma'$: case (a).}
    \vspace{1cm}
    \label{fig: dance case a}
\end{figure}

\begin{figure}[p]
\[
\xy
%
(-49,21)="-15";
(-35,7)="-14";
(-28,14)="-13";
(-14,14)="-12";
(-7,7)="-11";
(0,18)*+{\omega(\sigma')};
(7,7)="11";
(14,14)="12";
(28,14)="13";
(35,7)="14";
(49,21)="15";
%
{\ar@{-} "-15";"-14"};
{\ar "-13";"-14"};
{\ar@{~}^{\sigma'_1} "-13";"-12"};
{\ar^\alpha "-12";"-11"};
{\ar@{~}^\xi "-11";"11"};
{\ar_\beta "12";"11"};
{\ar@{~}^{\sigma'_2} "12";"13"};
{\ar "13";"14"};
{\ar@{-} "14";"15"};
%
%
(-49,-7)="-5";
(-35,-21)="-4";
(-28,-14)="-3";
(-14,-14)="-2";
(-7,-7)="-1";
(0,-18)*+{\omega(\sigma)};
(7,-7)="1";
(14,-14)="2";
(28,-14)="3";
(35,-21)="4";
(49,-7)="5";
%
{\ar@{-} "-5";"-4"};
{\ar "-3";"-4"};
{\ar@{~} "-3";"-2"};
{\ar "-1";"-2"};
{\ar@{~}^\xi "-1";"1"};
{\ar "1";"2"};
{\ar@{~} "2";"3"};
{\ar "3";"4"};
{\ar@{-} "4";"5"};
%
{\ar@/_.3pc/@{-} (8,-5);(8,-16)};
{\ar@/^.3pc/@{-} (27,-5);(27,-16)};
%
{\ar@/^.3pc/@{-} (-8,-5);(-8,-16)};
{\ar@/_.3pc/@{-} (-27,-5);(-27,-16)};
%
\endxy
\]
    \caption{The walks~$\omega(\sigma)$ and~$\omega(\sigma')$ when~$\sigma$ dances with~$\sigma'$: case (b).}
    \vspace{1cm}
    \label{fig: dance case b}
\end{figure}

\begin{figure}[p]
\[
\xy
%
(-42,25)="-15";
(-33,16)="-14";
(-28,21)="-13";
(-14,21)="-12";
(-7,14)*+{\bullet}="-11";
(0,25)*+{\omega(\sigma')};
(7,14)*+{\bullet}="11";
(14,7)="12";
(25,18)="13";
(30,23)="14";
%
{\ar@{-} "-15";"-14"};
{\ar "-13";"-14"};
{\ar@{~}^{\sigma'_1} "-13";"-12"};
{\ar^\alpha "-12";"-11"};
{\ar@{~}_\xi "-11";"11"};
{\ar_\beta "11";"12"};
{\ar@{-} "12";"13"};
{\ar_{\beta_s\blossom} "14";"13"};
%
(-40,-9)="-5";
(-30,-19)="-4";
(-25,-14)="-3";
(-14,-14)="-2";
(-7,-7)*+{\bullet}="-1";
(0,-17)*+{\omega(\sigma)};
(7,-7)*+{\bullet}="1";
(14,-14)="2";
(25,-3)="3";
(30,-8)="4";
(37,-8)="5";
(42,-13)="6";
(55,0)="7";
%
{\ar@{-} "-5";"-4"};
{\ar "-3";"-4"};
{\ar@{~} "-3";"-2"};
{\ar "-1";"-2"};
{\ar@{~}^\xi "-1";"1"};
{\ar^\beta "1";"2"};
{\ar@{-} "2";"3"};
{\ar "3";"4"};
{\ar@{~} "4";"5"};
{\ar "5";"6"};
{\ar@{-} "6";"7"};
%
{\ar@/^.3pc/@{-} (-9,-7);(-9,-15)};
{\ar@/_.3pc/@{-} (-24,-7);(-24,-15)};
%
{\ar@/_.3pc/@{-} (26,-2);(26,-10)};
{\ar@/^.3pc/@{-} (36,-2);(36,-10)};
%
\endxy
\]
    \caption{The walks~$\omega(\sigma)$ and~$\omega(\sigma')$ when~$\sigma$ dances with~$\sigma'$: case (c).}
    \label{fig: dance case c}
\end{figure}

We conclude this section with the observation which motivated this paper.

\begin{theorem}
\label{thm:nkc/sttiltc}
For any gentle quiver~$\bar Q = (Q,I)$, the maps
\[
\strings_{\ge-1}^\pm(\bar Q) \xrightleftharpoons[\quad\mbox{$\sigma$}\;\quad]{\mbox{$\omega$}} \bendingWalks^\pm(\bar Q)
\]
induce
\begin{itemize}
\item isomorphisms of simplicial complexes between the support $\tau$-tilting complex~$\tTC$ and the non-kissing complex~$\RNKC$,
\item isomorphisms of oriented graphs between the graph of left mutations in~$\tTC$ and the graph of increasing flips in~$\RNKC$.
\end{itemize}
\end{theorem}

\begin{proof}
The theorem is a direct consequence of Lemma~\ref{lem: attract or dance vs kiss}, except for the fact that increasing flips correspond to left mutations.
We use the notation of Proposition~\ref{prop:flip} and Figure~\ref{fig:flip}: let $F$ and~$F'$ be two adjacent facets such that the flip of~$F$ to~$F'$ is increasing, let $\omega$ and~$\omega'$ are the walks such that~$F \ssm \{\omega\} = F' \ssm \{\omega'\}$, let~$\{\alpha, \beta\} = \distinguishedArrows{\omega}{F}$ and~$\{\alpha', \beta'\} = \distinguishedArrows{\omega'}{F'}$, let~$\xi = \distinguishedString{\omega}{F} = \distinguishedString{\omega'}{F'}$, and let~$\mu = \distinguishedWalk{\alpha'}{F} = \distinguishedWalk{\beta}{F'}$ and~$\nu = \distinguishedWalk{\beta'}{F} = \distinguishedWalk{\alpha}{F'}$.
We consider the four associated strings~$\sigma(\omega), \sigma(\omega'), \sigma(\mu)$ and~$\sigma(\nu)$.
Note that~$\mu$ could be a straight walk, in which case we let~$\sigma(\mu)$ be~$\varnothing$ so that~$M \big( \sigma(\mu) \big) = 0$, and similarly for~$\nu$.
Since the statement is trivially satisfied when~$\omega'$ is a deep walk, we may assume that it is not the case.
We claim that the representation~$M \big( \sigma(\omega') \big)$ is a quotient of~$M \big( \sigma(\mu) \big) \oplus M \big( \sigma(\nu) \big)$, which implies the statement by~\cite[Def.--Prop.~2.28]{AdachiIyamaReiten}.
First note that the distinguished string~$\xi$ is also a substring of~$\omega$ (use~$\alpha$ and~$\beta$).
We distinguish five cases, depending on which of the distinguished arrows~$\alpha'$ and~$\beta'$ belongs to some cohook in~$\omega'$.
Assuming first that~$\alpha', \beta'$ both belong to~$\sigma(\omega')$, then there is a short exact sequence~$0\rightarrow M \big( \sigma(\omega) \big) \rightarrow M \big( \sigma(\mu) \big) \oplus M \big( \sigma(\nu) \big) \rightarrow M \big( \sigma(\omega') \big) \rightarrow 0$.
Assume next that~$\alpha'$ belongs to some (left) cohook for~$\omega'$, but that~$\beta'$ belongs to~$\sigma(\omega')$.
This implies that~$\nu$ is not a straight walk and that~$\sigma(\omega')$ is a substring on top of~$\sigma(\nu)$, thus giving a sujection~$M \big( \sigma(\nu) \big) \rightarrow M \big( \sigma(\omega') \big)$.
The symmetric case gives a surjection~$M \big( \sigma(\mu) \big) \rightarrow M \big( \sigma(\omega') \big)$.
Assume that the distinguished arrows~$\alpha', \beta'$ both belong to the same cohook.
By symmetry, we may assume that it is a left cohook.
In that case again,~$\nu$ is not a straight walk and~$\sigma(\omega')$ is a substring on top of~$\sigma(\nu)$.
Finally, assuming that~$\alpha'$ belongs to some left cohook, while~$\beta'$ belongs to some right cohook for~$\omega'$, the string~$\sigma(\omega')$ is easily seen to be on top of both strings~$\sigma(\mu)$ and~$\sigma(\nu)$.
\end{proof}

\begin{remark}
\begin{enumerate}
\item Considering walks on the blossoming gentle bound quiver allows to obtain a short exact sequence in~$\rep \bar Q\blossom$ associated with each left mutation:
\[
0\rightarrow M(\omega) \rightarrow M(\mu) \oplus M(\nu) \rightarrow M(\omega') \rightarrow 0,
\]
in the notations of Proposition~\ref{prop:flip} and Figure~\ref{fig:flip}.
We note that these extensions have a flavour very similar to the results of I.~\c{C}anak\c{c}{\i} and S.~Schroll in~\cite{CanakciSchroll}.
In their paper, the middle term of an extension is obtained by resolving a crossing, while here, a kissing is resolved into a crossing.
\item One can check that, in all five cases of the proof above, the morphism $M \big( \sigma(\omega) \big) \rightarrow M \big( \sigma(\mu) \big) \oplus M \big( \sigma(\nu) \big)$ is a left-$T$ approximation with cokernel~$M \big( \sigma(\omega') \big)$, where $T$ is the direct sum of all~$M \big( \sigma(\lambda) \big)$ for $\lambda \in F \ssm \{\omega\}$ not a straight walk nor a deep walk.
 However, this approximation is not injective in general.
\end{enumerate}
\end{remark}

\begin{example}
The map~$\sigma$ of \fref{exm:exmBijectionStringsWalks1} sends the support~$\tau$-tilting complexes of \fref{fig:exmtTC}\,(left) to the non-kissing complexes of~\fref{fig:exmNKC}\,(left).
\end{example}

\subsection{From walks to AR-quivers}

In this section, we remark that, by using walks on $\bar Q\blossom$, it is possible to define combinatorially some translation quiver.
We show that this translation quiver contains enough information to recover the components of the Auslander--Reiten quiver of $\bar Q$ containing the string modules.
Two examples in the representation-finite case are given in Figure~\ref{fig:exmAuslanderReitenQuiver}.

\begin{proposition}\label{proposition: elementary moves and walks}
Let $\sigma\in\strings(\bar Q)$ be a string for $\bar Q$ and let $\sigma' = {}_c\sigma$ if $\sigma$ does not start in a deep or $\sigma' = {}_{h^{-1}}\sigma$ if $\sigma$ starts in a deep.
Then the walk $\omega(\sigma)$ starts in a deep and we have $\omega(\sigma') = {}_c\big(_{h^{-1}}\omega(\sigma)\big)$.
\end{proposition}

\begin{proof}
We first note that any walk in $Q\blossom$ starts either with a blossoming arrow or with the inverse of a blossoming arrow.
As a consequence, any walk in $Q\blossom$ starts in a deep.

We first assume that $\sigma$ does not start in a deep, so that $\sigma'=\,_c\sigma$.
Then $\omega(\sigma)$ is of the form $\alpha_{r+1} \blossom \alpha_r \cdots \alpha_1 \alpha^{-1}\sigma\nu$ where $r\geq -1$, $\alpha_r\cdots\alpha_1\alpha^{-1}$ is a left cohook for $\sigma$ in $\bar Q$, $\alpha_{r+1}\blossom$ is a blossoming arrow, and $\nu$ is a right cohook for $\sigma$ in $\bar Q\blossom$.
Moreover, $\sigma'=\alpha_r\cdots\alpha_1\alpha^{-1}\sigma$ and $\,_{h^{-1}}\omega(\sigma) = \alpha_r\cdots\alpha_1\alpha^{-1}\sigma\nu = \sigma'\nu$.
The result follows.

We now assume that $\sigma$ starts in a deep, so that $\sigma'=\,_{h^{-1}}\sigma$.
Write $\sigma = \mu\sigma'$ where $\mu$ is a hook in $\bar Q$.
Then we have $\omega(\sigma)=(\alpha\blossom)^{-1}\mu\sigma'\nu$ for some cohook $\nu$ in $\bar Q\blossom$ and some blossoming arrow $\alpha\blossom$ and $_{h^{-1}}\omega(\sigma)=\sigma'\nu$.
This implies that $\omega(\sigma') = {}_c\big(_{h^{-1}}\omega(\sigma)\big)$.
\end{proof}

\begin{remark}
Assume that $\bar Q$ is representation-finite.
It follows from Proposition~\ref{proposition: elementary moves and walks} and from its dual that the Auslander--Reiten quiver of $\bar Q$ can be computed by using walks in $\bar Q\blossom$ instead of strings in $\bar Q$.
The computation is made slightly easier by the fact that irreducible arrows always correspond to the same elementary move on the walks (replacing a cohook by a hook); while for strings two different elementary moves appear (adding a hook or removing a cohook).
Two examples of computations are shown in Figure~\ref{fig:exmAuslanderReitenQuiver}.
We note that one can slightly extend the AR-quiver by including straight walks and deep walks.
The translation quiver thus obtained resemble the AR-quiver of an exact category whose projective-injectives are the straight walks, whose non-injective projectives are the peak walks (corresponding to the projective representations of $\bar Q$) and whose non-projective injectives are the deep walks (corresponding to the shifted projective representations of $\bar Q$).
The category obtained by killing the projective-injectives seems to be related to two-term silting complexes since its indecomposable objects are the indecomposable representations of $\bar Q$ and the shifts of the indecomposable projective representations of $\bar Q$.
This remark might deserve further investigation.
We also note that, if $Q$ is of type $A_n$, the translation quiver described above is not the AR-quiver of the corresponding cluster category:
the arrows from shifted projectives to modules do not appear in this translation quiver.
\end{remark}

\captionsetup{width=1.5\textwidth}
\hvFloat[floatPos=h, capWidth=h, capPos=r, capAngle=90, objectAngle=90, capVPos=c, objectPos=c]{figure}
{\includegraphics[scale=.45]{exmAuslanderReitenQuiver}}
{The Auslander-Reiten quiver~$\AR$ for two gentle bound quivers on~$3$ vertices. By Sections~\ref{subsec:stringBandModules} and~\ref{subsec:walks2strings}, the indecomposable $\tau$-rigid or shifted projective representations of~$A = kQ/I$ can be identified either with strings of~$\bar Q$ (left) or with walks on~$\bar Q\blossom$ (right). The additional nodes on the walk picture (right) correspond to straight walks.}
{fig:exmAuslanderReitenQuiver}
\captionsetup{width=\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage
\part{The non-kissing lattice}
\label{part:lattice}

This section focuses on lattice theoretic properties of non-kissing complexes.
Referring to~\ref{sec:recollectionLattice} for proper definitions of the lattice theoretic concepts involved, let us immediately state the main result of this section.

\begin{theorem}
\label{thm:lattice}
If~$\bar Q$ is a gentle bound quiver whose non-kissing complex~$\RNKC$ is finite, then the non-kissing oriented flip graph~$\NKG$ is the Hasse diagram of a congruence-uniform lattice.
\end{theorem}

\begin{example}
Theorem~\ref{thm:lattice} is already known for the dissection and grid bound quivers:
\begin{itemize}
\item For a dissection, it is shown in~\cite{GarverMcConville}.
\item For a subset of~$\Z^2$,  it is the central result of~\cite{McConville}.
\item For oriented paths, the non-kissing lattice is the (type~$A$) Cambrian lattice of N.~Reading~\cite{Reading-CambrianLattices}. This contains in particular the classical Tamari lattice for a directed path.
\end{itemize}
\end{example}

In fact, our proof of Theorem~\ref{thm:lattice} is an adaptation of the proof  developed by T.~McConville in~\cite{McConville}.
Namely, we define a closure operator on subsets of strings whose biclosed sets have a lattice structure~(\ref{sec:biclosedStrings}), define a natural lattice congruence on biclosed sets~(\ref{sec:latticeCongruence}), and show that the Hasse diagram of the lattice quotient is isomorphic to the non-kissing oriented flip graph~(\ref{sec:biclosedSetsToNKF}).
Finally (\ref{sec:nonFriendlyComplex}), we study the join-irreducible elements of~$\NKL$ and the canonical join complex of~$\NKL$ which we call the non-friendly complex as in~\cite{GarverMcConville-grid}.

This section follows the same strategy as that of~\cite{McConville, GarverMcConville-grid} and many arguments are just translated to our context.
The reader will certainly appreciate that the definitions on arbitrary gentle bound quivers become somewhat uniform and do not depend on vertical and horizontal edges as in~\cite{McConville}.
However, there are two difficulties which make the proofs sometimes more technical: on the one hand, strings on arbitrary gentle bound quivers are not naturally oriented and can self-intersect which sometimes creates difficulties; on the other hand, only distinguishable strings correspond to join-irreducible elements in~$\NKL$.

In all this section, we assume that~$\RNKC$ is finite, so that~$\bar Q$ has finitely many strings and walks.
Equivalently, there is a relation of~$I$ in any non-kissing cycle of~$Q$ (oriented~or~not).

\section{Some algebraic notions on lattices}
\label{sec:recollectionLattice}

\subsection{Canonical join- and meet-representations}
\label{subsec:joinIrreducibleRep}

Consider a finite lattice~$(L,\le,\meet,\join)$ with minimal element~$\hat 0$ and maximal element~$\hat 1$.
Denote by~$x \lessdot y$ the \defn{cover relations} in~$L$, \ie $x < y$ such that there is no~$z \in L$ with~$x < z < y$.

\begin{definition}
An element~$x \in L$ is \defn{join-irreducible} (resp.~\defn{meet-irreducible}) if~$x \ne \hat 0$ (resp.~$x \ne \hat 1$) and~$x = y \join z$ (resp.~$x = y \meet z$) implies~$x = y$ or~$x = z$.
In other words, $x$ covers a unique element~$x_\star$ (resp.~is covered by a unique element~$x^\star$).
We denote by~$\JI(L)$ and~$\MI(L)$ the subposets induced by join and meet irreducible elements of~$L$.
\end{definition}

Join- and meet-irreducible elements are building blocks for join- and meet-representations.

\begin{definition}
A \defn{join-representation} of~$x \in L$ is a subset~$J \subseteq L$ such that~$x = \bigJoin J$.
Such a representation is \defn{irredundant} if~$x \ne \bigJoin J'$ for a strict subset~$J' \subsetneq J$.
The irredundant join-representations of an element~$x \in L$ are ordered by containement of the lower ideals of their elements, \ie~$J \le J'$ if and only if for any~$y \in J$ there exists~$y' \in J'$ such that~$y \le y'$ in~$L$.
The \defn{canonical join-representation} of~$x$ is the minimal irredundant join-representation of~$x$ for this order when it exists.
The \defn{canonical meet-representation} is defined dually.
\end{definition}

Note that the canonical join-representation does not always exists.
However, when it exists, its elements are necessarily join-irreducible.
The existence of canonical join- and meet-representations are guarantied by the following condition~\cite[Thm.~2.24]{FreeseNation}.

\begin{definition}
A lattice is \defn{semi-distributive} if
\[
x \join z = y \join z \Longrightarrow x \join z = (x \meet y) \join z
\qquad\text{and}\qquad
x \meet z = y \meet z \Longrightarrow x \meet z = (x \join y) \meet z
\]
for any~$x, y, z \in L$, or equivalently if any element admits canonical join- and meet-representations.
\end{definition}

The following characterization of the canonical join- and meet-representations in a semidistributive lattice was recently established by E.~Barnard~\cite{Barnard}.

\begin{proposition}[{\cite[Lem.~3.3]{Barnard}}]
\label{prop:canonicalJoinRepresentation}
Consider a semi-distributive lattice~$(L,\le,\join,\meet)$. Then
\begin{enumerate}[(i)]
\item For any cover relation~$x \lessdot y$ in~$L$, there exists a unique join-irreducible~$\ji(x \lessdot y) \in \JI(L)$ such that~$x \join \ji(x \lessdot y) = y$ and~$x \meet \ji(x \lessdot y) = \ji(x \lessdot y)_\star$.
\item The canonical join-representation of~$y \in L$ is given by
\[
y = \bigJoin_{\substack{x \in L \\ x \lessdot y}} \ji(x \lessdot y).
\]
\end{enumerate}
A dual statement also holds for canonical meet-representations.
\end{proposition}

Finally, as they are closed by subsets, canonical join- and meet-representations naturally define simplicial complexes.

\begin{definition}
The \defn{canonical join complex} of~$L$ is the simplicial complex on join-irreducible elements of~$L$ whose faces are the canonical join-representations of the elements of~$L$.
The \defn{canonical meet complex} is defined dually.
\end{definition}

Recall that a simplicial complex is \defn{flag} when its minimal non-faces are edges, \ie when it is the clique complex of its graph.
The following statement was proved by E.~Barnard~\cite{Barnard}.

\begin{theorem}[{\cite[Thm.~1.1]{Barnard}}]
The canonical join complex of a semi-distributive lattice~is~flag.
\end{theorem}

\subsection{Lattice congruences}
\label{sec:latticeTheory}

We now remind the reader with the definition of lattice congruences and refer to~\cite{Reading-LatticeCongruences, Reading-CambrianLattices} for further details.

\begin{definition}
An \defn{order congruence} is an equivalence relation~$\equiv$ on a poset~$P$ such that:
\begin{enumerate}[(i)]
\item Every equivalence class under~$\equiv$ is an interval of~$P$.
\item The projection~$\projDown : P \to P$ (resp.~$\projUp : P \to P$), which maps an element of~$P$ to the minimal (resp.~maximal) element of its equivalence class, is order preserving.
\end{enumerate}
The \defn{quotient}~$P/{\equiv}$ is a poset on the equivalence classes of~$\equiv$, where the order relation is defined by~$X \le Y$ in~$P/{\equiv}$ iff there exists representatives~$x \in X$ and~$y \in Y$ such that~$x \le y$ in~$P$. The quotient~$P/{\equiv}$ is isomorphic to the subposet of~$P$ induced by~$\projDown(P)$ (or equivalently by~$\projUp(P)$).

If moreover~$P$ is a finite lattice, then~$\equiv$ is automatically a \defn{lattice congruence}, meaning that it is compatible with meets and joins: for any~$x \equiv x'$ and~$y \equiv y'$, we have~$x \meet y \equiv x' \meet y'$ and~$x \join y \equiv x' \join y'$. The poset quotient~$P/{\equiv}$ then inherits a lattice structure where the meet~$X \meet Y$ (resp.~the join~$X \join Y$) of two congruence classes~$X$ and~$Y$ is the congruence classe of~$x \meet y$ (resp.~of~$x \join y$) for arbitrary representatives~$x \in X$ and~$y \in Y$.
\end{definition}

\begin{example}
A lattice congruence is illustrated on \fref{fig:exmLatticeQuotient}\,(left).
\end{example}

\begin{remark}
\label{rem:sublattice}
For a lattice congruence~$\equiv$ on a lattice~$L$, the subposet of~$L$ induced by~$\projDown(L)$ is automatically a join-sublattice of~$L$, meaning that for any~$x,y \in L$, we have~${\projDown(x) \join \projDown(y) \in \projDown(L)}$.
However, $\projDown(L)$ can fail to be a sublattice of~$L$, since it might happen that~$\projDown(x) \meet \projDown(y) \notin \projDown(L)$.
The dual remark holds for~$\projUp(L)$.
\end{remark}

Note that for any order congruence~$\equiv$ the projection maps~$\projDown$ and~$\projUp$ satisfy~${\projDown(x) \le x \le \projUp(x)}$, ${\projUp \circ \projUp = \projUp \circ \projDown = \projUp}$ and ${\projDown \circ \projDown = \projDown \circ \projUp = \projDown}$, and $\projUp$ and~$\projDown$ are order preserving.
The following lemma shows the reciprocal statement.
It is proved for example in~\cite[Lem.~4.2]{DermenjianHohlwegPilaud}.

\begin{lemma}
\label{lem:conditionsProjectionMaps}
If two maps~$\projUp : P \to P$ and~$\projDown : P \to P$ satisfy
\begin{enumerate}[(i)]
\item
\label{item:conditionsProjectionMapsSandwich}
$\projDown(x) \le x \le \projUp(x)$ for any element~$x \in P$,

\item
\label{item:conditionsProjectionMapsLastWins}
$\projUp \circ \projUp = \projUp \circ \projDown = \projUp$ and $\projDown \circ \projDown = \projDown \circ \projUp = \projDown$,

\item
\label{item:conditionsProjectionMapsOrderPreserving}
$\projUp$ and~$\projDown$ are order preserving,
\end{enumerate}
then the fibers of~$\projUp$ and~$\projDown$ coincide and the relation~$\equiv$ on~$P$ defined by
\[
x \equiv y \iff \projUp(x) = \projUp(y) \iff \projDown(x) = \projDown(y)
\]
is an order congruence on~$P$ with projection maps~$\projUp$ and~$\projDown$.
\end{lemma}

\begin{definition}
Given two lattice congruences~$\equiv_1, \equiv_2$ on a poset~$P$, we say that~$\equiv_1$ \defn{refines}~$\equiv_2$ (or that~$\equiv_2$ \defn{coarsens}~$\equiv_1$) when~$x \equiv_1 y$ implies~$x \equiv_2 y$.
The set of order congruences~$\Cong(P)$ on~$P$ is partially ordered by refinement.
The minimal element of~$\Cong(P)$ is the complete congruence ($x \equiv y$ for all~$x,y \in P$) while the maximal element of~$\Cong(P)$ is the empty congruence ($x \not\equiv y$ for all~$x \ne y \in P$).
\end{definition}

\subsection{Congruence-uniform lattices}
\label{subsec:congruenceUniformLattices}

A lattice~$L$ is \defn{distributive} when~$(x \join y) \meet z = (x \meet z) \join (y \meet z)$ for any~$x,y,z \in L$ (which implies as well the dual equality~$(x \meet y) \join z = (x \join z) \meet (y \join z)$).
Birkhoff's representation theorem for distributive lattices affirms that any distributive lattice can be represented as the lattice of order ideals of its subposet~$\JI(L)$ of join-irreducible elements.

This result plays a particularly relevant role with respect to lattice congruences.
Namely, the refinement poset~$\Cong(L)$ of lattice congruences on~$L$ is known to be a distributive lattice, which is thus represented by the lattice of order ideals of~$\JI(\Cong(L))$.
For any cover relation~$x \lessdot y$ in~$L$, there exists a finest lattice congruence~$\con(x,y)$ which identifies~$x$ and~$y$.
The congruence~$\con(x,y)$ is join-irreducible in~$\Cong(L)$.
In fact, all join-irreducible elements in~$\Cong(L)$ are actually of the form~$\con(x_\star,x)$ for some join irreducible~$x \in \JI(L)$.
In other words, the map~$x \mapsto \con(x_\star,x)$ defines a surjection from the join-irreducibles of~$\JI(L)$ to that of~$\JI(\Cong(L))$.
Dually, the map~${x \mapsto \con(x,x^\star)}$ defines a surjection from the meet-irreducibles of~$\MI(L)$ to that of~$\MI(\Cong(L))$.
In this section, we will be mainly interested in the following family of lattices, for which the join- and meet-irreducibles of~$\Cong(L)$ are understood directly from those of~$L$.

\begin{definition}
A lattice~$L$ is \defn{congruence-uniform} if the maps
\[
\begin{array}{ccccccc}
\JI(L) & \longrightarrow & \JI\big(\Cong(L)\big) &
\multirow{2}{*}{\qquad\text{and}\qquad} & 
\MI(L) & \longrightarrow & \MI\big(\Cong(L)\big) \\
x & \longmapsto & \con(x_\star,x) & & x & \longmapsto & \con(x,x^\star)
\end{array}
\]
are bijections.
\end{definition}

\begin{remark}
For finite lattices, it is known that 
\begin{itemize}
\item Congruence-uniformity implies semi-distributivity.
\item Congruence-uniformity and semi-distributivity are preserved by lattice quotients: if~$\equiv$ is a lattice congruence on a congruence-uniform (resp.~semi-distributive) lattice~$L$, then~$L/{\equiv}$ is also congruence-uniform (resp.~semi-distributive).
\end{itemize}
\end{remark}

\subsection{Closure operators and biclosed sets}

We now consider closure operators and the corresponding closed sets. In all this section, the ground set~$\cS$ is assumed to be finite.

\begin{definition}
\label{def:closureOperator}
A \defn{closure operator} on a finite set~$\cS$ is a map~$S \mapsto \closure{S}$ on subsets of~$\cS$ such that
\[
\closure{\varnothing} = \varnothing,
\qquad
S \subseteq \closure{S},
\qquad
\closure{(\closure{S})} = \closure{S},
\qquad\text{and}\qquad
S \subseteq T \Longrightarrow \closure{S} \subseteq \closure{T},
\]
for any~$S,T \subseteq \cS$.
A subset~$S \subseteq \cS$ is \defn{closed} if~$\closure{S} = S$, \defn{coclosed} if~$\cS \ssm S$ is closed, and \defn{biclosed} if it is both closed and coclosed.
We denote by~$\Bicl{\cS}$ the inclusion poset of biclosed subsets of~$\cS$.
Finally, we denote by~$\coclosure{S} \eqdef \cS \ssm \closure{(\cS \ssm S)}$ the \defn{coclosure} of~$S \subseteq \cS$.
\end{definition}

Note that~$\Bicl{\cS}$ always has minimal element~$\varnothing$ and maximal element~$\cS$.
We omit to mention the closure operator in the notation~$\Bicl{\cS}$ since it will be fixed once and for all.
The following result developed in~\cite[Sect.~5]{McConville} gives a very convenient criterion to show that the inclusion poset of biclosed sets of~$\cS$ is a congruence-uniform lattice.

\begin{theorem}[{\cite[Thm.~5.5]{McConville}}]
\label{thm:characterizationCongruenceUniform}
If~$(\cS, \vartriangleleft)$ is a poset with a closure operator~$S \mapsto \closure{S}$~such~that
\begin{enumerate}[(i)]
\item for all~$S,T \in \Bicl{\cS}$ with~$S \subsetneq T$, there exists~$\tau \in T \ssm S$ such that~$S \cup \{\tau\} \in \Bicl{\cS}$, %(ordered by single-step inclusion),
\item $R \cup \closure{\big((S \cup T) \ssm R\big)} \in \Bicl{\cS}$ for~$R,S,T \in \Bicl{\cS}$ with~$R \subseteq S \cap T$, and
\item if~$\rho,\sigma,\tau \in \cS$ with~$\rho \in \closure{\{\sigma,\tau\}} \ssm \{\sigma,\tau\}$, then~$\sigma \vartriangleleft \rho$ and~$\tau \vartriangleleft \rho$,
\end{enumerate}
then the inclusion poset~$\Bicl{\cS}$ of biclosed sets of~$\cS$ is a congruence-uniform lattice.
\end{theorem}

\begin{remark}
\label{rem:meetJoinBiclosedSets}
Condition~(ii) of Theorem~\ref{thm:characterizationCongruenceUniform} applied to~$R = \varnothing$ implies that
\[
S_1, \dots, S_\ell \in \Bicl{\bar Q} \quad \Longrightarrow \quad \closure{\Big( \bigcup_{i \in [\ell]} S_i \Big)} \in \Bicl{\bar Q}.
\]
In particular the meet and join of biclosed sets~$S_1, \dots, S_\ell \in \Bicl{\bar Q}$ are given by
\[
\bigJoin_{i \in [\ell]} S_i = \closure{\Big( \bigcup_{i \in [\ell]} S_i \Big)}
\qquad\text{and}\qquad
\bigMeet_{i \in [\ell]} S_i = \cS \ssm \closure{\Big( \bigcup_{i \in [\ell]} \cS \ssm S_i \Big)} = \coclosure{\Big( \bigcap_{i \in [\ell]} S_i \Big)}.
\]
\end{remark}

\medskip
Unfortunately, the criterion Theorem~\ref{thm:characterizationCongruenceUniform} does not apply directly when singletons are not closed.
The issue comes from the following observation.

\begin{lemma}
\label{lem:loops}
For any closure operator~$S \mapsto \closure{S}$ on a ground set~$\cS$, any biclosed set~$S \in \Bicl{\cS}$ and any~$\sigma \in \cS$, we have~$\sigma \in S \iff \closure{\{\sigma\}} \subseteq S \iff \closure{\{\sigma\}} \cap S \ne \varnothing$.
\end{lemma}

\begin{proof}
Since~$S$ is closed, we have~$\sigma \in S \Longrightarrow \closure{\{\sigma\}} \subseteq S \Longrightarrow \closure{\{\sigma\}} \cap S \ne \varnothing$.
Since~$S$ is coclosed, we can apply the same argument to the complement of~$S$, and we obtain~$\sigma \notin S \Longrightarrow \closure{\{\sigma\}} \cap S = \varnothing$.
\end{proof}

In particular, the previous lemma implies that if~$\closure{\{\sigma\}} \ne \{\sigma\}$, then $\Bicl{\cS}$ cannot satisfy Condition~(i) of Theorem~\ref{thm:characterizationCongruenceUniform}.

The following statement is an adaptation of Theorem~\ref{thm:characterizationCongruenceUniform} to the case when singletons are not closed.

\begin{theorem}[Adapted from~{\cite[Thm.~5.2 \& Thm.~5.5]{McConville}}]
\label{thm:characterizationCongruenceUniform2}
If~$(\cS, \vartriangleleft)$ is a poset with a closure operator~$S \mapsto \closure{S}$~such~that
\begin{enumerate}[(i)]
\item for each cover relation~$S \subset T$ in~$\Bicl{\cS}$, there is a unique~$\tau \in (T \ssm S)$ such that~${S \cup \closure{\{\tau\}} = T}$,
\item $R \cup \closure{\big((S \cup T) \ssm R\big)} \in \Bicl{\cS}$ for~$R,S,T \in \Bicl{\cS}$ with~$R \subseteq S \cap T$, and
\item if~$\rho,\sigma,\tau \in \cS$ with~$\rho \in \closure{\{\sigma,\tau\}} \ssm \{\sigma,\tau\}$, then~$\sigma \vartriangleleft \rho$ and~$\tau \vartriangleleft \rho$,
\end{enumerate}
then the inclusion poset~$\Bicl{\cS}$ of biclosed sets of~$\cS$ is a congruence-uniform lattice.
\end{theorem}

\begin{proof}
We follow the proofs of~\cite[Thm.~5.2 \& Thm.~5.5]{McConville}. 
Let $R,S,T,U$ be biclosed.
Assume that $S$ and $T$ are distinct and both cover $R$, so that $R = S \wedge T$.
Let $\sigma \in S\ssm R$ and $\tau \in T \ssm R$ be such that $S = R \cup \closure{\{\sigma\}}$ and $T = R \cup \closure{\{\tau\}}$.
The conclusion of the theorem follows from the two points below:
\begin{enumerate}
 \item If $S \wedge U = T \wedge U$, then $(S\vee T) \wedge U = R \wedge U$,
 \item If $V$ is biclosed and such that $S \leq V \lessdot S \vee T$, then $S\vee T = V \cup \closure{\{\tau\}}$.
\end{enumerate}
Point (1) shows that~$\Bicl{\cS}$ is a semi-distributive lattice, while point (2) shows that it admits a CN-labelling, and is thus a congruence-uniform lattice (see~\cite[Thm.~4]{Reading-HyperplaneArrangement}).

In order to prove point (1), we will make use of the following:
\begin{itemize}
 \item[(0)] $S\vee T = R\cup\closure{\{\sigma,\tau\}}$.
\end{itemize}

We now prove the three points above:

\begin{enumerate}
\item We have $R \cup \closure{(\closure{\{\sigma\}} \cup \closure{\{\tau\}} )} =   R \cup \closure{\{\sigma,\tau\}}$.
Condition (ii) thus shows that $R \cup \closure{\{\sigma,\tau\}}$ is biclosed.
It follows that $S\vee T = R \cup \closure{\{\sigma,\tau\}}$.

\item We let $S\wedge U$ equal $T\wedge U$. Assume $R\wedge U < (S\vee T)\wedge U$ and let $\rho \in (S\vee T) \ssm R$ satisfy $(R\wedge U) \cup \closure{\{\rho\}} \leq (S\vee T)\wedge U$ in $\Bicl{\cS}$.
Assume that $\rho\in\closure{\{\sigma\}}$.
Then, $\rho\in S$.
Since $\rho\in U$, we have ${\rho \in S \wedge U = R \wedge U}$, which is absurd.
We thus have $\rho \notin \closure{\{\sigma\}}$.
Since $S$ is coclosed, we have $\closure{\{\rho\}} \subseteq \cS\ssm S$.
In particular, $\sigma \notin \closure{\{\rho\}}$.
Similarly $\tau \notin \closure{\{\rho\}}$.
We deduce that ${\closure{\{\sigma\}} \cup \closure{\{\tau\}} \subseteq \cS\ssm \big( (R\wedge U) \cup \closure{\{\rho\}} \big)}$.
This is absurd because the latter set is closed and $\rho$ lies in~$\closure{( \closure{\{\sigma\}} \cup \closure{\{\tau\}} )}$ by (0).

\item Let $V$ be biclosed such that ${S \leq V \lessdot S \vee T}$.
There is a unique $\rho$ such that ${V \cup \closure{\{\rho\}} = S \vee T}$.
Then $\tau\notin V$ (otherwise $V$ would contain $\sigma$ and $\tau$ and thus $S\vee T$).
We thus have $\tau\in\closure{\{\rho\}}$, and $\closure{\{\tau\}}\subseteq\closure{\{\rho\}}$.
Assume that $\rho\notin\closure{\{\tau\}}$.
Then $\rho$ is not in $R\cup\closure{\{\tau\}}$ which is coclosed.
It follows that~$\closure{\{\rho\}}\subseteq \cS\ssm \left(R\cup\closure{\{\tau\}}\right)$ which is absurd.
We have thus proven that~$V \cup \closure{\{\rho\}} = V \cup \closure{\{\tau\}}$, so that~$\rho=\tau$.
\qedhere
\end{enumerate}
\end{proof}

\section{Biclosed sets of strings}
\label{sec:biclosedStrings}

Following~\cite[Sect.~6]{McConville}, we now define a closure operator on the set~$\strings^\pm(\bar Q)$ of undirected strings of~$\bar Q$.
First, for two oriented strings~$\sigma, \tau \in \strings(\bar Q)$, we define
\[
\sigma \circ \tau \eqdef \set{\sigma \alpha \tau}{\alpha \in Q_1 \text{ and } \sigma \alpha \tau \in \strings(\bar Q)}.
\]
This extends to sets~$S,T \subseteq \strings(\bar Q)$ by
\(
S \circ T \eqdef \bigcup_{\sigma \in S, \tau \in T} \sigma \circ \tau.
\)
In particular, for two undirected strings~$\sigma, \tau \in \strings^\pm(\bar Q)$, we can consider~$\sigma \circ \tau$ as the set of strings of~$\strings^\pm(\bar Q)$ obtained by joining an endpoint of~$\sigma$ to an endpoint of~$\tau$ with any arrow~$\alpha \in Q_1$.
Note that~$\sigma \circ \tau$ is not necessary a singleton: it may contain up to~$4$ strings and can also be empty (\eg when no arrow joins an endpoint of~$\sigma$ to an endpoint of~$\tau$).
For a set~$S$ of undirected strings of~$\strings^\pm(\bar Q)$, we then define
\[
\closure{S} \eqdef \bigcup_{\substack{\ell \in \N \\ \sigma_1, \dots, \sigma_\ell \in S}} \sigma_1 \circ \dots \circ \sigma_\ell.
\]
As there is no ambiguity, we abbreviate the notation~$\Bicl{\strings^\pm(\bar Q)}$ by~$\Bicl{\bar Q}$.

\begin{example}
\fref{fig:exmBiclosed} illustrates the notion of closed, coclosed and biclosed sets of strings.

\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=.45]{exmBiclosed}}
	\caption{Four sets of strings on the gentle bound quiver~$\bar Q\ex$ of \fref{fig:exmBlossomingQuiver}\,(left). The first is neither closed not coclosed, the second is closed but not coclosed, the third is coclosed but not closed, and the fourth is biclosed.}
	\label{fig:exmBiclosed}
\end{figure}
\end{example}

\begin{example}
\fref{fig:exmLatticeQuotient}\,(left) illustrates the inclusion poset of biclosed sets~$\Bicl{\bar Q}$ for a specific gentle bound quiver.
All posets are represented from bottom to top, with their minimal elements at the bottom and their maximal elements on top.
\end{example}

\begin{example}
When~$\bar Q$ is an oriented path with vertices linearly labeled by~$[n]$, a string is determined by its endpoint labels~$i \le j$ and can thus be represented by the pair~$(i,j+1)$.
This maps biclosed sets of strings to inversion sets of permutations of~$\fS_{n+1}$.
\end{example}

\begin{remark}
\label{rem:reverseBiclosed}
With the natural identification between undirected strings of a bound quiver~$\bar Q$ and its reversed bound quiver~$\reversed{\bar Q}$, a subset~$S$ is closed (resp.~coclosed, resp.~biclosed) in~$\strings^\pm(\bar Q)$ if and only if it is closed (resp.~coclosed, resp.~biclosed) in~$\strings^\pm(\reversed{\bar Q})$.
\end{remark}

\enlargethispage{.3cm}
To get used to the definition and to provide more examples of biclosed sets, let us immediately state the following lemma which will be used repeatedly.
Recall from Definition~\ref{def:topBottom} that a substring~$\sigma$ of a string~$\tau$ is a top (resp.~bottom) substring of~$\tau$ if $\tau$ either ends or has an outgoing (resp.~incoming) arrow at each endpoint of~$\sigma$.
The set of top (resp.~bottom) substrings of~$\sigma$ is denoted~$\Sigma_\top(\sigma)$ (resp.~$\Sigma_\bottom(\sigma)$).
Note that~$\tau$ is simultaneously a top and a bottom \mbox{substring of itself}.

\begin{lemma}
\label{lem:exmBiclosed}
For any string~$\sigma \in \strings^\pm(\bar Q)$, the closures~$\closure{\Sigma_\bottom(\sigma)}$ and~$\closure{\Sigma_\top(\sigma)}$ of the set of bottom and top substrings of~$\sigma$ are both biclosed.
Therefore,
\[
\closure{\Big( \bigcup_{i \in [\ell]} \Sigma_\bottom(\sigma_i) \Big)}
\quad\text{and}\quad
\coclosure{\Big( \bigcap_{i \in [\ell]} \closure{\Sigma_\top(\sigma_i)} \Big)}
\]
are both biclosed for any~$\sigma_1, \dots, \sigma_\ell \in \strings^\pm(\bar Q)$.
\end{lemma}

\begin{proof}
The set $\closure{\Sigma_\bottom(\sigma)}$ is closed by definition.
To prove that it is coclosed, consider~${\tau \in \closure{\Sigma_\bottom(\sigma)}}$.
There are substrings~$\tau_1, \dots, \tau_{\ell-1} \in \Sigma_\bottom(\sigma)$, arrows~$\alpha_1, \dots, \alpha_{\ell-1} \in Q_1$ and signs~${\varepsilon_1, \dots, \varepsilon_\ell \in \{-1,1\}}$ such that~$\tau = \tau_1 \alpha_1^{\varepsilon_1} \tau_2 \alpha_2^{\varepsilon_2} \cdots \alpha_{\ell-1}^{\varepsilon_{\ell-1}} \tau_\ell$.
Assume that~$\tau = \tau' \beta^\varepsilon \tau''$ for some strings~$\tau', \tau'' \in \strings(\bar Q)$, an arrow~$\beta \in Q_1$, and a sign~$\varepsilon$.
If~$\beta^\varepsilon$ is one of the arrows~$\alpha_k^{\varepsilon_k}$, then both~$\tau'$ and~$\tau''$ are in~$\closure{\Sigma_\bottom(\sigma)}$.
We can therefore assume that there exists~$k \in [\ell]$ such that~$\beta^\varepsilon$ appears inside the string~$\tau_k$.
Write~$\tau_k = \tau_k' \beta^\varepsilon \tau_k''$.
We distinguish two cases:
\begin{itemize}
\item If~$\varepsilon = -1$, then~$\tau_k'$ is a bottom substring of~$\tau_k$ which is a bottom substring of~$\sigma$, so that~$\tau_k' \in \Sigma_\bottom(\sigma)$ and thus~$\tau' = \tau_1 \alpha_1^{\varepsilon_1} \dots \alpha_{k-1}^{\varepsilon_{k-1}} \tau_k' \in \closure{\Sigma_\bottom(\sigma)}$.
\item Similarly, if~$\varepsilon = 1$, then~$\tau''_k$ is a bottom substring of~$\tau_k$ which is a bottom substring of~$\sigma$, so that~$\tau_k'' \in \Sigma_\bottom(\sigma)$ and thus~$\tau'' = \tau_k'' \alpha_k^{\varepsilon_k} \dots \alpha_{\ell-1}^{\varepsilon_{\ell-1}} \tau_\ell \in \closure{\Sigma_\bottom(\sigma)}$.
\end{itemize}
We conclude that~$\closure{\Sigma_\bottom(\sigma)}$ is coclosed, and thus biclosed.
By Remark~\ref{rem:meetJoinBiclosedSets}, $\closure{\big( \bigcup_{i \in [\ell]} \Sigma_\bottom(\sigma_i) \big)}$ is also biclosed for any~$\sigma_1, \dots, \sigma_\ell \in \strings^\pm(\bar Q)$.
The proof is similar for~$\closure{\Sigma_\top(\sigma)}$ or follows by duality from Remarks~\ref{rem:reverseBlossomingQuiver} and~\ref{rem:reverseBiclosed}.
\end{proof}

The next result is the keystone of this section.

\begin{theorem}
For any gentle bound quiver~$\bar Q$ with finitely many strings, the inclusion poset of biclosed sets~$\Bicl{\bar Q}$ is a congruence-uniform lattice.
\end{theorem}

\begin{proof}
The proof is inspired from that of~\cite[Thm.~6.5]{McConville}.
The main difficulty is that~$\Bicl{\bar Q}$ does not satisfies Condition~(i) of Theorem~\ref{thm:characterizationCongruenceUniform} when~$\bar Q$ has a loop.
For example, for the quiver~$\bar Q$ with a single vertex~$v$, a loop~$\alpha$, and the relation~$\alpha^2 = 0$, the biclosed sets of strings are precisely~$\varnothing$ and~$\{\varepsilon_v, \alpha\}$.
We therefore need the adapted criterion of Theorem~\ref{thm:characterizationCongruenceUniform2}.
For a string~$\sigma \in \strings^\pm(\bar Q)$, the closure~$\closure{\{\sigma\}}$ can be of two types:
\begin{itemize}
\item if there is a loop~$\alpha \in Q_1$ such that~$\sigma \alpha \in \strings^\pm(\bar Q)$, then~$\closure{\{\sigma\}} = \{\sigma, \sigma \alpha \sigma^{-1}\}$,
\item otherwise, $\closure{\{\sigma\}} = \{\sigma\}$.
\end{itemize}
In particular, for any two strings~$\sigma, \tau$, the equality~$\closure{\{\sigma\}}=\closure{\{\tau\}}$ implies $\sigma=\tau$.
We note that $\strings^\pm(\bar Q)$ is partially ordered by:~$\sigma \vartriangleleft \tau$ if and only if~$\sigma$ is a substring of~$\tau$.

\medskip\noindent
{\bf (i)}
Consider a cover relation~$S \subset T$ in~$\Bicl{\bar Q}$.
If~$\tau$ is a minimal length string in~$T \ssm S$, then for any~$\sigma, \sigma' \in \strings^\pm(\bar Q)$ with~$\tau \in \sigma \circ \sigma'$, either~$\sigma \in S$ or~$\sigma' \in S$.
Consider now a maximal length string~$\tau$ in~$T \ssm S$ such that for any~$\sigma, \sigma' \in \strings^\pm(\bar Q)$ with~$\tau \in \sigma \circ \sigma'$, either~$\sigma \in S$ or~$\sigma' \in S$.
We claim that~$S \cup \closure{\{\tau\}} \in \Bicl{\bar Q}$.
Observe first that~$S \cup \closure{\{\tau\}}$ is coclosed by the property defining~$\tau$.
Assume by means of contradiction that~$S \cup \closure{\{\tau\}}$ is not closed.
Since~$S$ and~$\closure{\{\tau\}}$ are both closed, it implies that there exists~$\sigma \in S$ such that~$\sigma \circ \tau \not\subseteq S$.
Consider a string~$\sigma \in S$ of minimal length such that~$\sigma \circ \tau \not\subseteq S$.
Let~$\rho \in (\sigma \circ \tau) \ssm S$.
Since~$S \cup \{\tau\} \subseteq T$ and~$T$ is closed, we have~$\rho \in T$.
By maximality of~$\tau$, we thus obtain that there exist~$\sigma', \tau' \in \strings^\pm(\bar Q) \ssm S$ such that~$\rho \in \sigma' \circ \tau'$.
Up to exchanging~$\sigma'$ and~$\tau'$, we have $\sigma \subseteq \sigma'$ and~$\tau \supseteq \tau'$ or \viceversa.
We distinguish these~two~cases:
\begin{itemize}
\item Either there exists a string~$\zeta$ such that~$\sigma' \in \sigma \circ \zeta$ and~$\tau \in \zeta \circ \tau'$. By definition of~$\tau$, we obtain that~$\zeta \in S$. Since~$\sigma, \zeta \in S$ while~$\sigma' \notin S$, this contradicts the closedness of~$S$.
\item Or there exists a string~$\zeta$ such that~$\sigma \in \sigma' \circ \zeta$ and~$\tau' \in \zeta \circ \tau$. We have~$\zeta \notin S$ (otherwise~${\tau, \zeta \in S}$ and~$\tau' \notin S$ would contradict the closedness of~$S$). We obtain a string~$\zeta \in S$ with~$\zeta \circ \tau \not\subseteq S$ and shorter than~$\sigma$, thus contradicting the minimality~of~$\sigma$.
\end{itemize}
Since we reach a contradiction in both cases, we conclude that~$S \cup \closure{\{\tau\}}$ is biclosed.
Finally, since $T$ covers~$S$ in~$\Bicl{\bar Q}$, we obtain that~$S \cup \closure{\{\tau\}} = T$.
The uniqueness is immediate since~$\closure{\{\tau\}} = T \ssm S$ determines~$\tau$ as observed above.
This concludes the proof of~(i).

\medskip\noindent
{\bf (ii)}
We proceed by induction on~$|\strings^\pm(\bar Q) \ssm R|$. The property clearly holds if~${R = S = T = \strings^\pm(\bar Q)}$. Consider thus~$R,S,T \in \Bicl{\bar Q}$ such that the property holds for any~$R' \supsetneq R$. The result is immediate when~$S \subseteq T$ (and similarly when~$S \supseteq T$) since~$R \cup \closure{((S \cup T) \ssm R)} = T \in \Bicl{\bar Q}$ in this case. Assume thus that~$S \ssm T \ne \varnothing$ and~$T \ssm S \ne \varnothing$. By~(i), since~$R \subsetneq S$ and~$R \subsetneq T$, there exist~$\sigma \in S \ssm R$ and~$\tau \in T \ssm R$ such that~$R \cup \closure{\{\sigma\}}$ and~$R \cup \closure{\{\tau\}}$ are biclosed. We claim that~$X \eqdef R \cup \closure{\{\sigma,\tau\}}$ is biclosed:
\begin{description}
\item[closed] Since~$R \cup \closure{\{\sigma\}}$ and~$R \cup \closure{\{\tau\}}$ are closed, we have~$\rho \circ \zeta \subseteq R$ for any~$\rho \in R$~and~${\zeta \in \{\sigma,\tau\}}$. An immediate induction thus shows that~$\rho \circ \zeta_1 \circ \dots \circ \zeta_\ell \subseteq R$ for any~$\zeta_1, \dots, \zeta_\ell \in \{\sigma, \tau\}$. Therefore, $R \circ \zeta \subseteq R$ for any~$\zeta \in \closure{\{\sigma,\tau\}}$. This implies that~$X$ is closed.
\item[coclosed] Assume by means of contradiction that~$X$ is not coclosed. Then there exists~$\sigma', \tau' \in \strings^\pm(\bar Q) \ssm X$ such that~$X \cap (\sigma' \circ \tau') \ne \varnothing$. Since~$R \cup \closure{\{\sigma\}}$ and~$R \cup \closure{\{\tau\}}$ are coclosed, we can assume that~$(\sigma \circ \tau) \cap (\sigma' \circ \tau') \ne \varnothing$. Therefore, up to exchanging~$\sigma'$ and~$\tau'$, we have either~$\sigma \subseteq \sigma'$ and~$\tau \supseteq \tau'$, or~$\sigma \supseteq \sigma'$ and~$\tau \subseteq \tau'$. Say for example that the former holds. Then there exists~$\theta \in \strings^\pm(\bar Q)$ such that~$\sigma' \in \sigma \circ \theta$ and~$\tau \in \theta \circ \tau'$. This implies that~$\theta \notin R$ (because~$R \cup \closure{\{\sigma\}}$ is closed) and that~$\theta \in R$ (because~$R \cup \closure{\{\tau\}}$ is coclosed and~$\theta \subsetneq \tau$), a contradiction.
\end{description}
We will now use the biclosed set~$X = R \cup \closure{\{\sigma, \tau\}}$ to prove that the property holds for~$T$.
We first apply our induction hypothesis to~$R' = R \cup \{\sigma\}$, $S' = S$ and~$T' = X$. We obtain that
\[
(R \cup \{\sigma\}) \cup \closure{\big( ( S \cup X ) \ssm (R \cup \{\sigma\}) \big)}
\]
is biclosed. However, we have
\[
S \cup X \subseteq (R \cup \{\sigma\}) \cup \closure{\big( ( S \cup X ) \ssm (R \cup \{\sigma\}) \big)} \subseteq \closure{(S \cup X)}
\]
Since~$\closure{(S \cup X)}$ is the smallest closed set containing~$S \cup X$, we obtain that
\[
(R \cup \{\sigma\}) \cup \closure{\big( ( S \cup X ) \ssm (R \cup \{\sigma\}) \big)} = \closure{(S \cup X)}.
\]
Applying the induction hypothesis to~$R' = R \cup \{\tau\}$, $S' = X$ and~$T' = T$, we obtain similarly that
\[
(R \cup \{\tau\}) \cup \closure{\big( ( X \cup T ) \ssm (R \cup \{\tau\}) \big)} = \closure{(X \cup T)}.
\]
Applying our induction hypothesis to~$R' = X$, $S' = \closure{(S \cup X)}$ and~$T' = \closure{(X \cup T)}$, we obtain that
\[
X \cup \closure{\big( \big( \closure{(S \cup X)} \cup \closure{(X \cup T)} \big) \ssm X \big)}
\]
is biclosed. Since~$\closure{\big( \big( \closure{(S \cup X)} \cup \closure{(X \cup T)} \big) \ssm X \big)}$ contains~$S \cup T$ and is closed, it also contains~$\closure{(S \cup T)}$.
Moreover,
\begin{align*}
X \cup \closure{\big( \big( \closure{(S \cup X)} \cup \closure{(X \cup T)} \big) \ssm X \big)}
& \subseteq X \cup \closure{\big( \closure{\big( (S \cup T \cup X) \ssm R\big)} \ssm X \big)} \\
& \subseteq R \cup \closure{\big( \closure{\big( (S \cup T \cup X) \ssm R\big)} \ssm R \big)} \\
& = R \cup \closure{\big( (S \cup T \cup X) \ssm R \big)} \\
& = R \cup \closure{\big( (S \cup T) \ssm R \big)} \\
& \subseteq \closure{(S \cup T)}.
\end{align*}
Therefore, all these sets coincide and~$R \cup \closure{\big( (S \cup T) \ssm R \big)}$ is biclosed, concluding the proof of~(ii).

\medskip\noindent
{\bf (iii)}
Consider~$\sigma, \tau \in \strings^\pm(\bar Q)$.
Any string~$\rho \in \closure{\{\sigma, \tau\}} \ssm \{\sigma, \tau\}$ is obtained by concatenations of copies of~$\sigma$ and~$\tau$ with arrows of~$Q_1$.
We thus immediately obtain that~$\sigma$ and~$\tau$ are substrings of~$\rho$.
\end{proof}

\section{Lattice congruence on biclosed sets}
\label{sec:latticeCongruence}

We now define a lattice congruence on biclosed sets of strings.
Our definition is borrowed from~\cite[Sect.~7]{McConville}.

\begin{definition}
\label{def:downUpProjections}
For a biclosed set~$S \in \Bicl{\bar Q}$, define
%\begin{itemize}
%\item $\projDown(S)$ to be the collection of strings of~$\strings^\pm(\bar Q)$ whose bottom substrings all belong to~$S$,
%\item $\projUp(S)$ to be the collection of strings of~$\strings^\pm(\bar Q)$ with a top substring contained in~$S$.
%\end{itemize}
\[
\projDown(S) \eqdef \set{\sigma \in \strings^\pm(\bar Q)}{\Sigma_\bottom(\sigma) \subseteq S}
\qquad\text{and}\qquad
\projUp(S) \eqdef \set{\sigma \in \strings^\pm(\bar Q)}{\Sigma_\top(\sigma) \cap S \ne \varnothing}.
\]
\end{definition}

\begin{example}
The down and up projections~$\projDown$ and~$\projUp$ are illustrated on \fref{fig:exmProjections}.

\begin{figure}[t]
	\capstart
	\centerline{
	\begin{overpic}[scale=.45]{exmProjections}
			\put(30,6){$\longleftarrow$}
			\put(31,8){$\projDown$}
			\put(68,6){$\longrightarrow$}
			\put(69,8){$\projUp$}
			\put(12,-3){$\projDown(S\ex)$}
			\put(50,-3){$S\ex$}
			\put(85,-3){$\projUp(S\ex)$}
	\end{overpic}
	}
	\vspace{.3cm}
	\caption{A biclosed set of strings~$S\ex \in \Bicl{\bar Q\ex}$ (middle) and its images~$\projDown(S\ex)$ (left) and~$\projUp(S\ex)$ (right) by the down and up projections of Definition~\ref{def:downUpProjections}. For space reasons, $\projUp(S\ex)$ is only represented partially: the remaining strings are obtained by adding independently the two dotted arrows to all strings containing their left endpoint.}
	\label{fig:exmProjections}
\end{figure}
\end{example}

Following Remarks~\ref{rem:reverseBlossomingQuiver}, \ref{rem:reverseNKC}, and~\ref{rem:reverseBiclosed}, we start with a simple observation.

\begin{lemma}
\label{rem:reversedProjections}
For any biclosed set~$S \in \Bicl{\bar Q}$,
\[
\strings^\pm(\bar Q) \ssm \projUp(S) = \projDown \big( \strings^\pm(\reversed{\bar Q}) \ssm S \big).
\]
\end{lemma}

\begin{proof}
On the one hand, $\strings^\pm(\bar Q) \ssm \projUp(S)$ is the set of strings of~$\strings^\pm(\bar Q)$ with no top substrings contained in~$S$, \ie whose top substrings are all in~$\strings^\pm(\bar Q) \ssm S$.
On the other hand, ${\projDown(\strings^\pm(\reversed{\bar Q}) \ssm S)}$ is the set of strings of~$\strings^\pm(\reversed{\bar Q})$ whose bottom substrings are all in~$\strings^\pm(\reversed{\bar Q}) \ssm S$.
Since reversing all arrows preserves the strings but exchanges top with bottom substrings, we conclude that the two sets coincide. 
\end{proof}

\begin{lemma}
For any biclosed set~$S \in \Bicl{\bar Q}$, the sets~$\projDown(S)$ and~$\projUp(S)$ are biclosed.
\end{lemma}

\begin{proof}
Let~$\rho, \sigma, \tau \in \strings^\pm(\bar Q)$ such that~$\rho \in \sigma \circ \tau$.
Assume first that~$\sigma, \tau \in \projDown(S)$.
Consider a bottom substring~$\rho'$ of~$\rho$.
We distinguish two cases:
\begin{itemize}
\item If~$\rho'$ is a substring of~$\sigma$ or~$\tau$, then it is a bottom substring and thus belongs to~$S$.
\item Otherwise, $\rho' \in \sigma' \circ \tau'$ for some substrings~$\sigma'$ of~$\sigma$ and~$\tau'$ of~$\tau$. These substrings are again bottom substrings so that~$\sigma' \in S$ and~$\tau' \in S$, which implies that~$\rho' \in S$ since~$S$ is closed.
\end{itemize}
In both cases, we showed that any bottom substring~$\rho'$ of~$\rho$ belongs to~$S$, so that~$\rho \in \projDown(S)$ and thus~$\projDown(S)$ is closed.

Assume now that~$\rho \in \projDown(S)$.
Since~$\rho \in \sigma \circ \tau$, either~$\sigma$ or~$\tau$ is a bottom substring of~$\rho$, say~$\sigma$ without loss of generality.
Any bottom substring of~$\sigma$ is then a bottom substring of~$\rho$ and thus belongs to~$S$ since~$\rho \in \projDown(S)$.
We conclude that~$\sigma \in \projDown(S)$ which proves that~$\projDown(S)$ is coclosed.

We thus proved that~$\projDown(S)$ is biclosed.
The proof is similar for~$\projUp(S)$ or follows by duality from Remarks~\ref{rem:reverseBlossomingQuiver} and~\ref{rem:reverseBiclosed} and Lemma~\ref{rem:reversedProjections}.
\end{proof}

\begin{proposition}
\label{prop:latticeCongruence}
The two maps~$\projDown : \Bicl{\bar Q} \to \Bicl{\bar Q}$ and~$\projUp : \Bicl{\bar Q} \to \Bicl{\bar Q}$ satisfy
\begin{enumerate}[(i)]
\item
$\projDown(S) \subseteq S \subseteq \projUp(S)$ for any element~$S \in \Bicl{\bar Q}$,

\item
$\projDown \circ \projDown = \projDown \circ \projUp = \projDown$ and $\projUp \circ \projUp = \projUp \circ \projDown = \projUp$,

\item
$\projDown$ and~$\projUp$ are order preserving.
\end{enumerate}
Therefore, the fibers of~$\projUp$ and~$\projDown$ coincide and the relation~$\equiv$ on~$\Bicl{\bar Q}$ defined by
\[
S \equiv T \iff \projDown(S) = \projDown(T) \iff \projUp(S) = \projUp(T)
\]
is an order congruence on~$\Bicl{\bar Q}$.
\end{proposition}

\begin{proof}
For~(i), we just observe that any string~$\tau$ is a top and a bottom substring of itself.

For~(iii), it follows from the definition that~$S \subseteq T$ implies~$\projDown(S) \subseteq \projDown(T)$ and~$\projUp(S) \subseteq \projUp(T)$.

For~(ii), we already obtain from~(i) and~(iii) that $\projDown(\projDown(S)) \subseteq \projDown(S)$ and~$\projDown(\projUp(S)) \supseteq \projDown(S)$.
We then observe that if~$\rho, \sigma, \tau \in \strings^\pm(\bar Q)$ are such that $\rho$ is a bottom substring of~$\sigma$ and~$\sigma$ is a bottom substring of~$\tau$, then~$\rho$ is a bottom substring of~$\tau$.
This shows that~$\projDown(\projDown(S)) \supseteq \projDown(S)$.
Finally, we prove that~$\projDown(\projUp(S)) \subseteq \projDown(S)$.
By means of contradiction, assume that there exists~${\tau \in \projDown(\projUp(S)) \ssm \projDown(S)}$.
Since~$\tau \notin \projDown(S)$, there exists a bottom substring~$\sigma$ of~$\tau$ which is not in~$S$.
We can assume that~$\sigma$ is an inclusion minimal such substring of~$\tau$.
Since~$\tau \in \projDown(\projUp(S))$, we have~$\sigma \in \projUp(S)$, so that there exists a top substring~$\rho$ of~$\sigma$ which belongs to~$S$.
The substring~$\rho$ decomposes~$\sigma$ into~$\sigma = \sigma' \circ \rho \circ \sigma''$, where~$\sigma'$ and~$\sigma''$ are bottom substrings of~$\sigma$, and thus of~$\tau$.
By minimality of~$\sigma$, we have~$\sigma' \in S$ and~$\sigma'' \in S$.
Since~$S$ is closed, we obtain that~$\sigma \in \sigma' \circ \rho \circ \sigma'' \subseteq S$, a contradiction.
We therefore proved that~$\projDown \circ \projDown = \projDown \circ \projUp = \projDown$.
Using the symmetry presented in Lemma~\ref{rem:reversedProjections}, this implies as well that~$\projUp \circ \projUp = \projUp \circ \projDown = \projUp$.
\end{proof}

\begin{example}
\fref{fig:exmLatticeQuotient}\,(left) illustrates this lattice congruence on~$\Bicl{\bar Q}$ for a specific gentle bound quiver.
Congruence classes are represented by blue rectangles.

\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[width=1.1\textwidth]{exmLatticeQuotient}}
	\caption{The inclusion lattice of biclosed sets~$\Bicl{\bar Q}$ with congruence classes of~$\equiv$ in blue (left), and the corresponding lattice of increasing flips on facets of~$\NKC$ (right).}
	\label{fig:exmLatticeQuotient}
\end{figure}
\end{example}

To conclude this section, we show that the examples of biclosed sets~$S$ seen in Lemma~\ref{lem:exmBiclosed} are fixed by~$\projDown$ (resp.~$\projUp$).
In other words, they correspond to certain bottom (resp.~top) elements of the congruence classes of~$\equiv$.
We will see in Section~\ref{sec:biclosedSetsToNKF} that all bottom (resp.~top) elements of $\equiv$-classes are in fact of this form, and in Section~\ref{sec:nonFriendlyComplex} that one can in fact restrict to distinguishable~strings.

\begin{lemma}
\label{lem:fixProjDown}
For any string~$\sigma \in \strings^\pm(\bar Q)$, the biclosed set~$\closure{\Sigma_\bottom(\sigma)}$ is fixed by~$\projDown$ while~$\closure{\Sigma_\top(\sigma)}$ is fixed by~$\projUp$.
Therefore,
\[
\projDown \bigg( \closure{\Big( \bigcup_{i \in [\ell]} \Sigma_\bottom(\sigma_i) \Big)} \bigg) = \closure{\Big( \bigcup_{i \in [\ell]} \Sigma_\bottom(\sigma_i) \Big)}
\;\;\text{and}\;\;
\projUp \bigg( \coclosure{\Big( \bigcap_{i \in [\ell]} \closure{\Sigma_\top(\sigma_i)} \Big)} \bigg) = \coclosure{\Big( \bigcap_{i \in [\ell]} \closure{\Sigma_\top(\sigma_i)} \Big)}
\]
for any~$\sigma_1, \dots, \sigma_\ell \in \strings^\pm(\bar Q)$.
\end{lemma}

\begin{proof}
Let~$\tau \in \closure{\Sigma_\bottom(\sigma)}$ and~$\rho \in \Sigma_\bottom(\tau)$.
By definition, there exist strings~${\tau_1, \dots, \tau_\ell \in \Sigma_\bottom(\sigma)}$, arrows~$\alpha_1, \dots, \alpha_{\ell-1} \in Q_1$ and signs~$\varepsilon_1, \dots, \varepsilon_{\ell-1} \in \{-1,1\}$ such that~$\tau = \tau_1 \alpha_1^{\varepsilon_1} \dots \alpha_{\ell-1}^{\varepsilon_{\ell-1}} \tau_\ell$.
Since~${\rho \in \Sigma_\bottom(\tau)}$, there exist indices~$1 \le i < j \le \ell$ and substrings~$\tau_i' \in \Sigma_\bottom(\tau_i)$ and~${\tau_j' \in \Sigma_\bottom(\tau_j)}$ such that ${\rho = \tau_i' \alpha_i^{\varepsilon_i} \tau_{i+1} \dots \tau_{j-1} \alpha_{j-1}^{\varepsilon_{j-1}} \tau_j'}$.
We thus obtain~$\rho \in \closure{\Sigma_\bottom(\sigma)}$ so that~${\Sigma_\bottom(\tau) \subseteq \closure{\Sigma_\bottom(\sigma)}}$.
This shows that~$\closure{\Sigma_\bottom(\sigma)} \subseteq \projDown(\closure{\Sigma_\bottom(\sigma)})$ and thus the equality by Proposition~\ref{prop:latticeCongruence}\,(i).

Consider now~$\sigma_1, \dots, \sigma_\ell \in \strings^\pm(\bar Q)$.
We have
\[
\projDown \bigg( \bigJoin_{i\in [\ell]} \closure{\Sigma_\bottom(\sigma_i)} \bigg) = \bigJoin_{i \in [\ell]} \projDown \big( \closure{\Sigma_\bottom(\sigma_i)} \big) = \bigJoin_{i \in [\ell]} \closure{\Sigma_\bottom(\sigma_i)},
\]
so that
\[
\projDown \bigg( \closure{\Big( \bigcup_{i \in [\ell]} \Sigma_\bottom(\sigma_i) \Big)} \bigg) = \closure{\Big( \bigcup_{i \in [\ell]} \Sigma_\bottom(\sigma_i) \Big)}.
\]
The proof is similar for~$\closure{\Sigma_\top(\sigma)}$ or follows by duality from Remark~\ref{rem:reverseBlossomingQuiver} and Lemma~\ref{rem:reversedProjections}.
\end{proof}

\section{Biclosed sets of strings versus non-kissing facets}
\label{sec:biclosedSetsToNKF}

The goal of this section is to show that the non-kissing oriented flip graph~$\NKG$ is isomorphic to the Hasse diagram of the lattice quotient of the lattice of biclosed sets~$\Bicl{\bar Q}$ by the lattice congruence~$\equiv$.
For this, we first need to define inverse bijections between congruence classes of biclosed sets of~$\Bicl{\bar Q}$ and non-kissing facets of~$\NKC$.

\subsection{From biclosed sets of strings to non-kissing facets}

We first define a map~$\eta$ from biclosed sets in~$\Bicl{\bar Q}$ to subsets of walks of~$\walks^\pm(\bar Q)$.
Although slightly more technical to cover the general situation of gentle bound quivers, our definition is directly inspired by~\cite[Sect.~8]{McConville}.

\begin{definition}
\label{def:fromBiclToNKC}
For~$S \in \Bicl{\bar Q}$ and~$\alpha \in Q_1\blossom$, let
\(
{\omega(\alpha,S) \eqdef \alpha_{-\ell}^{\varepsilon_{-\ell}} \cdots \alpha_{-1}^{\varepsilon_{-1}} \cdot \alpha \cdot \alpha_1^{\varepsilon_1} \cdots \alpha_r^{\varepsilon_r}}
\)
be the directed walk containing~$\alpha$ defined by
%\[
%\varepsilon_i = 
%\begin{cases}
%	1 & \text{if } \alpha_1^{\varepsilon_1} \cdots \alpha_{i-1}^{\varepsilon_{i-1}} \in S \\
%	-1 & \text{otherwise}
%\end{cases}
%\]
%for all~$i \in [m]$ and
%\[
%\varepsilon_{-i} = 
%\begin{cases}
%	1 & \text{if } \alpha_{-i+1}^{\varepsilon_{-i+1}} \cdots \alpha_{-1}^{\varepsilon_{-1}} \in S \\
%	-1 & \text{otherwise}
%\end{cases}
%\]
%for all~$i \in [\ell]$.
\begin{itemize}
\item $\varepsilon_i = -1$ if the string~$\alpha_1^{\varepsilon_1} \cdots \alpha_{i-1}^{\varepsilon_{i-1}}$ belongs to~$S$, and~$\varepsilon_i = 1$ otherwise, for all~$i \in [r]$, and
\item $\varepsilon_{-i} = 1$ if the string~$\alpha_{-i+1}^{\varepsilon_{-i+1}} \cdots \alpha_{-1}^{\varepsilon_{-1}}$ belongs to~$S$, and~$\varepsilon_i = -1$ otherwise, for all~$i \in [\ell]$.
\end{itemize}
\end{definition}

\begin{remark}
Observe that~$\omega(\alpha,S)$ is well-defined and unique for any~$S \in \Bicl{\bar Q}$ and~$\alpha \in Q_1$.
Indeed, one can start from the string~$\alpha$ and let it grow in both directions according to the local rules of Definition~\ref{def:fromBiclToNKC} until it reaches some blossom vertices of~$\bar Q\blossom$.
Note that~$\ell = 0$ (resp.~$r = 0$) when~$\alpha$ is an incoming (resp.~outgoing) blossom arrow.
Note also that for~$i = 1$, we consider $\alpha_1^{\varepsilon_1} \dots \alpha_{i-1}^{\varepsilon_{i-1}}$ to be~$t(\alpha)$ and similarly~$\alpha_{-i+1}^{\varepsilon_{-i+1}} \dots \alpha_{-1}^{\varepsilon_{-1}}$ to be~$s(\alpha)$.
\end{remark}

\begin{example}
The map~$\omega$ is illustrated on \fref{fig:exmSurjection}.
\end{example}

\begin{lemma}
\label{lem:distinctDirectedWalks}
As directed walks, $\omega(\alpha,S) \ne \omega(\beta,S)$ for~$\alpha \ne \beta \in Q_1\blossom$.
\end{lemma}

\begin{proof}
Assume that~$\alpha \ne \beta \in Q_1\blossom$ are such that~$\omega \eqdef \omega(\alpha,S) = \omega(\beta,S)$.
We can assume without loss of generality that~$\alpha$ appears before~$\beta$ along~$\omega$.
Let~$\sigma$ denote the substring of~$\omega$ between~$\alpha$ and~$\beta$.
We obtain that~$\sigma \in S$ since~$\alpha$ is incoming at~$s(\sigma)$, and that~$\sigma \notin S$ since~$\beta$ is outgoing at~$t(\sigma)$, a contradiction.
\end{proof}

Recall from Definition~\ref{def:substrings} that a string~$\sigma \in \strings(\bar Q)$ is a \defn{top substring} (resp.~\defn{bottom substring}) of a walk~$\omega \in \walks(\bar Q)$ if the arrows of~$\omega \ssm \sigma$ incident to the endpoints of~$\sigma$ are both outgoing (resp.~incoming).

\begin{lemma}
\label{lem:positiveNegativeOrientation}
For any~$S \in \Bicl{\bar Q}$ and~$\alpha \in Q_1$, all bottom (resp.~top) substrings of~$\omega(\alpha,S)$ belong to~$S$ (resp.~to the complement of~$S$).
\end{lemma}

\begin{proof}
Write~$\omega(\alpha,S) = \alpha_{-\ell}^{\varepsilon_{-\ell}} \cdots \alpha_{-1}^{\varepsilon_{-1}} \alpha \alpha_1^{\varepsilon_1} \cdots \alpha_r^{\varepsilon_r}$ and consider a substring~$\sigma = \alpha_i^{\varepsilon_i} \cdots \alpha_j^{\varepsilon_j}$ ($i < j$).
Assume for instance that~$\sigma$ is a bottom substring of~$\omega(\alpha,S)$, \ie that~$\varepsilon_{i-1} = 1$ while~$\varepsilon_{j+1} = -1$.
We distinguished three cases:
\begin{itemize}
\item If~$j < 0$, then~$\alpha_i^{\varepsilon_i} \cdots \alpha_{-1}^{\varepsilon_{-1}} \in S$ (since~$\varepsilon_{i-1} = 1$) while~$\alpha_{j+2}^{\varepsilon_{j+2}} \cdots \alpha_{-1}^{\varepsilon_{-1}} \notin S$ (since~$\varepsilon_{j+1} = -1$).
\item If~$i < 0 < j$, then~$\alpha_i^{\varepsilon_i} \cdots \alpha_{-1}^{\varepsilon_{-1}} \in S$  (since~$\varepsilon_{i-1} = 1$) and~$\alpha_1^{\varepsilon_1} \cdots \alpha_j^{\varepsilon_j} \in S$ (since~${\varepsilon_{j+1} = -1}$).
\item If~$0 < i$, then~$\alpha_1^{\varepsilon_1} \cdots \alpha_{i-2}^{\varepsilon_{i-2}} \notin S$ (since~$\varepsilon_{i-1} = 1$) while~$\alpha_1^{\varepsilon_1} \cdots \alpha_j^{\varepsilon_j} \in S$ (since~$\varepsilon_{j+1} = -1$).
\end{itemize}
In all cases, we obtain that~$\sigma = \alpha_i^{\varepsilon_i} \cdots \alpha_j^{\varepsilon_j}$ must belong to~$S$ since~$S$ is biclosed.
The case of top substrings is symmetric, or can be deduced from the case of bottom substrings by Lemma~\ref{rem:reversedProjections}.
\end{proof}

\begin{corollary}
\label{coro:surjectionNonKissingWalks}
For any~$\alpha, \beta \in Q_1\blossom$, the walks~$\omega(\alpha,S)$ and~$\omega(\beta,S)$ (or its inverse) are non-kissing.
In particular, $\omega(\alpha,S)$ is not self-kissing.
\end{corollary}

\begin{proof}
Assume that~$\omega(\alpha,S)$ kisses~$\omega(\beta,S)$ along~$\sigma$, which is thus a maximal substring of~$\omega(\alpha,S)$ and~$\omega(\beta,S)$ (or its inverse).
By Lemma~\ref{lem:positiveNegativeOrientation}, we have~$\sigma \notin S$ since~$\sigma$ is a top substring of~$\omega(\alpha,S)$, while~$\sigma \in S$ since~$\sigma$ is a bottom substring of~$\omega(\beta,S)$, a contradiction.
\end{proof}

\begin{corollary}
\label{coro:eta}
The set~$\set{\omega(\alpha,S)}{\alpha \in Q_1\blossom}$ contains~$2|Q_0| - |Q_1|$ straight walks and~$|Q_0|$ pairs of inverse directed walks.
\end{corollary}

\begin{proof}
Denote by~$s$ the number of straight walks, by~$B$ the number of pairs of inverse bending walks and by~$b$ the remaining bending walks in the set~$\set{\omega(\alpha,S)}{\alpha \in Q_1\blossom}$.
Since this set contains~${|Q_1\blossom| = 4|Q_0| - |Q_1|}$ distinct directed walks by Lemma~\ref{lem:distinctDirectedWalks}, we have~$s + 2B + b = 4|Q_0| - |Q_1|$ and~$s \le 2|Q_0| - |Q_1|$.
Moreover, since all these walks are not self-kissing and pairwise non-kissing by Corollary~\ref{coro:surjectionNonKissingWalks}, we obtain that~$B + b \le |Q_0|$.
Therefore, Corollary~\ref{coro:pure} ensures that ${B = (s + 2B + b) - (s + B + b) \ge |Q_0|}$.
We conclude that~$B = |Q_0|$ and thus~$s = 2|Q_0| - |Q_1|$.
\end{proof}

In other words, beside the straight walks, we can group the walks of~$\set{\omega(\alpha,S)}{\alpha \in Q_1\blossom}$ into pairs of inverse walks.
This leads to the definition of the following map.

\begin{definition}
\label{def:eta}
We denote by~$\eta : \Bicl{\bar Q} \to 2^{\walks^\pm(\bar Q)}$ the map defined by
\[
\eta(S) \eqdef \set{\omega(\alpha,S)}{\alpha \in Q_1\blossom}_{ / \, (\omega \sim \omega^{-1})},
\]
where the quotient means that we consider the walks of~$\eta(S)$ as undirected.
\end{definition}

\begin{example}
Observe that~$\eta(\varnothing) = F_\deep$ and that~$\eta\big(\strings^\pm(\bar Q)\big) = F_\peak$.
\end{example}

\begin{example}
The map~$\eta$ is illustrated on \fref{fig:exmSurjection}\,(left) for the gentle bound quiver~$\bar Q\ex$ of \fref{fig:exmBlossomingQuiver}\,(left).

\begin{figure}[t]
	\capstart
	\centerline{
	\begin{overpic}[scale=.45]{exmSurjection}
			\put(28,8){$\longrightarrow$}
			\put(29,10){$\eta$}
			\put(69,8){$\longrightarrow$}
			\put(70,10){$\zeta$}
			\put(13,-3){$S\ex$}
			\put(46,-3){$\eta(S\ex)$}
			\put(77,-3){$\zeta(\eta(S\ex)) = \projDown(S\ex)$}
	\end{overpic}
	}
	\vspace{.3cm}
	\caption{The maps~$\eta$ of Definition~\ref{def:eta} from biclosed sets to non-kissing facets (left) and $\zeta$ of Definition~\ref{def:zeta} from non-kissing facets to biclosed sets (right).}
	\label{fig:exmSurjection}
\end{figure}
\end{example}

\begin{example}
\fref{fig:exmLatticeQuotient} shows the complete map from the biclosed sets of~$\Bicl{\bar Q}$ to the non-kissing facets of~$\NKC$ for a specific gentle bound quiver.
\end{example}

The following result recasts Corollaries~\ref{coro:surjectionNonKissingWalks} and~\ref{coro:eta} in terms of the map~$\eta$ of Definition~\ref{def:eta}.

\begin{proposition}
For any~$S \in \Bicl{\bar Q}$, the collection of undirected walks~$\eta(S)$ is a non-kissing facet of~$\NKC$.
\end{proposition}

We now identify the relation between an arrow~$\alpha \in Q_1\blossom$ and the walk~$\omega(\alpha,S)$ in the facet~$\eta(S)$.

\begin{lemma}
\label{lem:distinguishedWalkEta}
For any~$S \in \Bicl{\bar Q}$ and~$\alpha \in Q_1\blossom$, the walk~$\omega(\alpha,S)$ is the distinguished walk of the non-kissing facet~$\eta(S)$ at~$\alpha$:
\[
\omega(\alpha,S) = \distinguishedWalk{\alpha}{\eta(S)}.
\]
\end{lemma}

\begin{proof}
Let~$\alpha \ne \beta \in Q_1\blossom$ and assume that~$\alpha$ belongs to~$\omega(\beta,S)$.
If~$\alpha$ and~$\beta$ are opposite along~$\omega(\beta,S)$, then~$\omega(\beta,S)$ is not straight, thus there exists~$\beta' \in Q_1\blossom$ such that~${\omega(\beta,S) = \omega(\beta',S)^{-1}}$ by Corollary~\ref{coro:eta}.
We can thus assume that~$\alpha$ and~$\beta$ are both in the same direction as~$\omega(\beta,S)$.
Assume also for instance that~$\alpha$ appears before~$\beta$ along~$\omega(\beta,S)$, and let~$\rho$ denote the substring of~$\omega(\beta,S)$ between~$\alpha$ and~$\beta$.
By definition of~$\omega(\beta,S)$, we have~$\rho \in S$ which implies that~$\beta \notin \omega(\alpha,S)$.
Decompose~$\rho$ into~$\rho = \sigma \gamma^\varepsilon \tau$ for some strings~$\sigma, \tau \in \strings^\pm(\bar Q)$, arrow~$\gamma \in Q_1$ and sign~$\varepsilon \in \{-1,1\}$ such that~$\omega(\alpha,S)$ contains~$\sigma$ but not~$\sigma \gamma^\varepsilon$.
If~$\varepsilon = -1$, then~$\sigma \notin S$ and~$\tau \notin S$, while~$\rho \in S$ which contradicts that~$S$ is coclosed.
We conclude that~$\varepsilon = 1$ so that~$\omega(\beta,S) \prec_\alpha \omega(\alpha,S)$.
The other situation ($\alpha$ appears after~$\beta$ along~$\omega(\beta,S)$) is symmetric.
\end{proof}

\subsection{From non-kissing facets to biclosed sets of strings}

We now define a map~$\zeta$ from non-kissing facets of~$\NKC$ to sets of strings.
It is again similar to~\cite[Sect.~8]{McConville}.

\begin{definition}
\label{def:zeta}
Recall from Definition~\ref{def:substrings} that~$\Sigma_\bottom(\omega)$ denotes the set of bottom substrings of a walk~$\omega \in \walks^\pm(\bar Q)$ (\ie substrings~$\sigma \in \strings^\pm(\bar Q)$ of~$\omega$ such that the arrows of~$\omega \ssm \sigma$ incident to the endpoints of~$\sigma$ are both incoming).
For a non-kissing facet~$F \in \NKC$, define
\[
\zeta(F) \eqdef \closure{\Big( \bigcup_{\omega \in F} \Sigma_\bottom(\omega) \Big)}
\]
\end{definition}

\begin{example}
The map~$\zeta$ is illustrated on \fref{fig:exmSurjection}\,(right)  for the gentle bound quiver~$\bar Q\ex$ of \fref{fig:exmBlossomingQuiver}\,(left).
\end{example}

\begin{proposition}
For any non-kissing facet~$F \in \NKC$, the set of strings~$\zeta(F)$ is biclosed.
\end{proposition}

\begin{proof}
Observe first that for a walk~$\omega \in \walks^\pm(\bar Q)$, either~$\omega$ is a peak walk and it has no bottom substring, or we have~$\closure{\Sigma_\bottom(\omega)} = \closure{\Sigma_\bottom(\sigma)}$ where~$\sigma$ is the inclusion maximal bottom substring of~$\omega$.
It follows that~$\closure{\Sigma_\bottom(\omega)}$ is biclosed by Lemma~\ref{lem:exmBiclosed}.
Therefore, according to Remark~\ref{rem:meetJoinBiclosedSets},
\[
\zeta(F) = \closure{\Big( \bigcup_{\omega \in F} \Sigma_\bottom(\omega) \Big)} = \closure{\Big( \bigcup_{\omega \in F} \closure{\Sigma_\bottom(\omega)} \Big)} \in \Bicl{\bar Q}. \qedhere
\]
\end{proof}

Observe moreover that~$\projDown \big( \zeta(F) \big) = \zeta(F)$ for any non-kissing facet~$F \in \NKC$ by Lemma~\ref{lem:fixProjDown}.

\subsection{Projection map}

\enlargethispage{.4cm}
We have defined in the previous sections two functions
\[
\Bicl{\bar Q} \xrightleftharpoons[\quad\mbox{$\zeta$}\;\quad]{\mbox{$\eta$}} \NKC
\]
between biclosed sets of strings of~$\bar Q$ and non-kissing facets of~$\NKC$.
We now show that~$\eta$ is surjective and that~$\zeta$ provides a section of~$\eta$.

\begin{proposition}
\label{prop:surjection}
For any non-kissing facet~$F \in \NKC$, we have~$\eta \big( \zeta(F) \big) = F$.
\end{proposition}

\begin{proof}
Fix~$\alpha \in Q_1\blossom$ and let~$\omega \eqdef \distinguishedWalk{\alpha}{F}$ (resp.~$\omega' \eqdef \distinguishedWalk{\alpha}{\eta(\zeta(F))}$) denote the distinguished walk of~$F$ (resp.~$\eta(\zeta(F))$) at~$\alpha$.
Assume for the sake of contradiction that~$\omega \ne \omega'$.
Orient~$\omega$ and~$\omega'$ in the same direction as~$\alpha$ and assume for example that~$\omega$ and~$\omega'$ split after~$\alpha$ (if not, they split before~$\alpha$ and the argument is symmetric).
Let~$\sigma$ be the maximal common substring of~$\omega$ and~$\omega'$ after~$\alpha$.
Recall from Lemma~\ref{lem:distinguishedWalkEta} that~$\omega' = \omega(\alpha, \zeta(F))$ is the walk constructed by the procedure described in Definition~\ref{def:fromBiclToNKC} starting from~$\alpha$ in~$\zeta(F)$.
We distinguish two cases:
\begin{itemize}
\item Assume first that~$\omega \ssm \sigma$ has an incoming arrow at~$t(\sigma)$. Then~$\sigma$ is a bottom substring of~$\omega$, thus belongs to~$\zeta(F)$. This would imply that~$\omega' \ssm \sigma$ also has an incoming arrow at~$t(\sigma)$, thus contradicting the maximality of~$\sigma$ (even in the case that~$\sigma$ is a vertex).
\item Assume now that~$\omega \ssm \sigma$ has an outgoing arrow at~$t(\sigma)$. Since~$\omega$ and~$\omega'$ split at~$t(\sigma)$, this forces~$\omega' \ssm \sigma$ to have an incoming arrow at~$t(\sigma)$. Therefore, $\sigma \in \zeta(F)$. Thus, there exist bottom substrings~$\sigma_1, \dots, \sigma_\ell$ of walks~$\omega_1, \dots, \omega_\ell$ of~$F$, arrows~${\alpha_1, \dots, \alpha_{\ell-1} \in Q_1}$, and signs~$\varepsilon_1, \dots, \varepsilon_{\ell-1} \in \{-1,1\}$ such that~${\sigma = \sigma_1 \alpha_1^{\varepsilon_1} \cdots \alpha_{\ell-1}^{\varepsilon_{\ell-1}} \sigma_\ell}$. Note that~$\omega_1 = \omega$ and thus~$\varepsilon_1 = -1$, as otherwise, we would have~$\omega \prec_\alpha \omega_1$, contradicting the definition of~$\omega$. Let~$k \in [\ell]$ be minimal such that~$\sigma_1 \alpha_1^{\varepsilon_1} \dots \alpha_{k-1}^{\varepsilon_{k-1}} \sigma_k$ is not a bottom substring of~$\omega$ (note that, by assumption, $\sigma$ itself is not a bottom substring of~$\omega$, so that~$k$ is well defined). We thus have~$\varepsilon_{k-1} = -1$ while~$\varepsilon_k = 1$. This implies that~$\omega \ssm \sigma_k$ has two outgoing arrows at the endpoints of~$\sigma_k$, while~$\omega_k \ssm \sigma_k$ has two incoming arrows at the endpoints of~$\sigma_k$. This implies that~$\omega$ and~$\omega_k$ are kissing, contradicting the assumption that they both belong to the non-kissing facet~$F$ of~$\NKC$.
\end{itemize}
As we obtain a contradiction in both cases, we conclude that~$\omega = \omega'$, \ie $\distinguishedWalk{\alpha}{F} = \distinguishedWalk{\alpha}{\eta(\zeta(F))}$.
Since this holds for any arrow~$\alpha \in Q_1\blossom$ and any walk has at least one distinguished arrow, we conclude that~$F = \eta \big( \zeta(F) \big)$.
\end{proof}

\begin{proposition}
\label{prop:section}
For any biclosed set of strings~$S \in \Bicl{\bar Q}$, we have~$\zeta \big( \eta(S) \big) = \projDown(S)$.
\end{proposition}

\begin{proof}
Let~$S \in \Bicl{\bar Q}$ be a biclosed set of strings.
We first prove that~$\projDown(S) \subseteq \zeta \big( \eta(S) \big)$ by induction on the length of the strings in~$\projDown(S)$.
For this, consider a string~$\sigma \in \projDown(S)$ (by definition, all bottom substrings of~$\sigma$ belong to~$S$).
Orient~$\sigma$ in an arbitrary direction, and let~$\alpha \in Q_1\blossom$ be the incoming arrow at~$s(\alpha)$ such that~$\alpha \sigma \in \strings(\bar Q\blossom)$.
Let~$\omega \eqdef \omega(\alpha,S) = \distinguishedWalk{\alpha}{\eta(S)}$ be the walk of~$\eta(S)$ defined form~$\alpha$ (see Definition~\ref{def:fromBiclToNKC}), and let~$\tau$ be the maximal common substring of~$\sigma$ and~$\omega$.
We distinguish two cases:
\begin{itemize}
\item If~$\sigma = \tau$, then~$\omega \ssm \sigma$ has an incoming arrow at~$t(\sigma)$ (by Definition~\ref{def:fromBiclToNKC}). Therefore, $\sigma \in \Sigma_\bottom \big( \omega \big) \subseteq \zeta \big( \eta(S) \big)$.
\item Otherwise, we write~$\sigma = \tau \beta^\varepsilon \tau'$. If~$\varepsilon = -1$, $\tau$ is a bottom substring of~$\sigma$, and thus belong to~$S$, so that Definition~\ref{def:fromBiclToNKC} forces~$\omega$ to use~$\beta^{-1}$ as well, contradicting the maximality of~$\tau$. Therefore, $\sigma = \tau \beta \tau'$. It follows that the walk~$\omega$ has an incoming arrow at~$t(\tau)$, so that~$\tau \in \Sigma_\bottom(\omega) \subseteq \zeta(\eta(S))$. Moreover, $\tau'$ is a bottom substring of~$\sigma$, so that~$\tau' \in \projDown(S)$, which in turns implies by induction hypothesis that~$\tau' \in \zeta(\eta(S))$. Since~$\tau, \tau' \in \zeta(\eta(S))$ and~$\zeta(\eta(S))$ is closed, we conclude that~$\sigma \in \zeta(\eta(S))$.
\end{itemize}

\medskip
Conversely, we now prove the reverse inclusion~$\zeta \big( \eta(S) \big) \subseteq \projDown(S)$.
We showed in Lemma~\ref{lem:fixProjDown} that ${\zeta \big( \eta(S) \big) = \projDown \big( \zeta \big( \eta(S) \big) \big)}$. 
Moreover, as observed in Lemma~\ref{lem:positiveNegativeOrientation}, ${\Sigma_\bottom(\omega) \subseteq S}$ for any~$\omega \in \eta(S)$, so that~$\zeta \big( \eta(S) \big) \subseteq S$.
Since~$\projDown$ is order-preserving, we obtain~${\zeta \big( \eta(S) \big) = \projDown \big( \zeta \big( \eta(S) \big) \big) \subseteq \projDown (S)}$.
\end{proof}

\begin{example}
The maps~$\eta$ and~$\zeta$ are illustrated on \fref{fig:exmSurjection}\,(right).
Compare~$\zeta(\eta(S\ex))$ on \fref{fig:exmSurjection}\,(right) with the down projection~$\projDown(S\ex)$ on \fref{fig:exmProjections}\,(left).
\end{example}

\begin{corollary}
\label{coro:fibers}
$\eta(R) = \eta(S) \iff \projDown(R) = \projDown(S)$ for any biclosed sets~$R,S$. In other words, the fibers of~$\eta$ are precisely the equivalence classes of the lattice congruence of Proposition~\ref{prop:latticeCongruence}.
\end{corollary}

\begin{proof}
If~$\eta(R) = \eta(S)$, then by Proposition~\ref{prop:section}, we have~$\projDown(R) = \zeta(\eta(R)) = \zeta(\eta(S)) = \projDown(S)$.
Reciprocally, if~$\projDown(R) = \projDown(S)$, then by Propositions~\ref{prop:surjection} and~\ref{prop:section}, we have~$\eta(R) = \eta \circ \zeta \circ \eta(R) = \eta(\projDown(R)) = \eta(\projDown(S)) = \eta \circ \zeta \circ \eta(S) = \eta(S)$.
\end{proof}

\begin{corollary}\label{cor: interval biclosed}
For any non-kissing facet~$F \in \NKC$, the fiber~$\eta^{-1}(F)$ is the interval of~$\Bicl{\bar Q}$
\[
\eta^{-1}(F) = \bigg[ \closure{ \Big( \bigcup_{\omega \in F} \Sigma_\bottom(\omega) \Big) }, \coclosure{ \Big( \bigcup_{\omega \in F} \closure{\Sigma_\top(\omega)} \Big) } \bigg].
\]
\end{corollary}

\begin{remark}\label{rem: Bongartz}
 We note that Corollary~\ref{cor: interval biclosed} gives a combinatorial description of Bongartz (co)com\-pletions.
 This allows to reduce the algebraic computations on representations of $\bar Q$ to much easier computations involving walks on $\bar Q\blossom$.
\end{remark}

\subsection{Oriented graph isomorphisms}

To conclude our interpretation of the non-kissing oriented flip graph~$\NKG$ in terms of lattice quotients of biclosed sets, we still need to show that~$\NKG$ is the Hasse diagram of~$\Bicl{\bar Q}/{\equiv}$.
This is the purpose of the next statement similar to~\cite[Claim~8.10]{McConville}.

\begin{proposition}
\label{prop:covers}
For any non-kissing facet~$F' \in \RNKC$ and~$\sigma \in \zeta(F')$, there exists an increasing flip~$F \to F'$ supported by~$\sigma$ if and only if~$\zeta(F') \ssm \{\sigma\}$ is biclosed.
\end{proposition}

\begin{proof}
Throughout the proof, we denote~$S \eqdef \zeta(F') \ssm \{\sigma\}$ and~$S' \eqdef \zeta(F')$.
Consider an increasing flip~$F \to F'$ with~$F \ssm \{\omega\} = F' \ssm \{\omega'\}$ and~$\sigma = \distinguishedString{w}{F} = \distinguishedString{w'}{F'}$.
We prove that~$S$ is biclosed:
\begin{description}
\item[closed] Otherwise, there exist bottom substrings~$\sigma_1, \dots, \sigma_\ell$ of walks~$\omega_1, \dots, \omega_\ell$ of~$F'$, arrows~$\alpha_1, \dots, \alpha_{\ell-1} \in Q_1$ and signs~$\varepsilon_1, \dots, \varepsilon_{\ell-1} \in \{-1,1\}$ such that~$\sigma = \sigma_1 \alpha_1^{\varepsilon_1} \dots \alpha_{\ell-1}^{\varepsilon_{\ell-1}} \sigma_\ell$.
Assume that there is~$k \in [\ell-1]$ such that~$\varepsilon_k = 1$ and choose~$k$ minimal with that property.
Then~$\omega_k \ne \omega'$ and~$\omega$ has two outgoing arrows while~$\omega_k$ has two incoming arrows at the endpoints of~$\sigma_k$, so that~$\sigma_k \in \Sigma_\top(\omega) \cap \Sigma_\bottom(\omega_k)$, contradicting the non-kissingness of~$F$.
We obtain a similar contradiction assuming that there is~$k \in [\ell-1]$ such that~$\varepsilon_k = -1$ and choosing~$k$ maximal with that property.
This forces~$\ell = 1$, so that~$\sigma \in S$, a contradiction.

\item[coclosed] Otherwise, by coclosedness of~$S'$, we can assume that there is a string~${\tau \in \strings(\bar Q) \ssm S'}$, an arrow~$\alpha \in Q_1$ and a sign~$\varepsilon \in \{-1,1\}$ such that~$\sigma \alpha^\varepsilon \tau \in S'$ (the case~${\tau \alpha^\varepsilon \sigma \in S'}$ is symmetric).
Thus, there exist bottom substrings~$\sigma_1, \dots, \sigma_\ell$ of walks~$\omega_1, \dots, \omega_\ell$ of~$F'$, arrows~$\alpha_1, \dots, \alpha_{\ell-1} \in Q_1$ and signs~$\varepsilon_1, \dots, \varepsilon_{\ell-1} \in \{-1,1\}$ such that~$\sigma \alpha^\varepsilon \tau = \sigma_1 \alpha_1^{\varepsilon_1} \dots \alpha_{\ell-1}^{\varepsilon_{\ell-1}} \sigma_\ell$.
Since~$\tau \notin S'$, there is~$k \in [\ell]$ such that~$\alpha^\varepsilon$ belongs to~$\sigma_k$ and we write~$\sigma_k = \sigma'_k \alpha^\varepsilon \sigma''_k$.
Since~$\{\omega, \omega_1, \dots, \omega_k\}$ are non-kissing, we obtain that~$\varepsilon_1, \dots, \varepsilon_{k-1} = -1$, which in turn implies that~$\varepsilon = 1$ (otherwise~$\omega$ would kiss~$\omega_k$).
Since~$\varepsilon = 1$, we have~${\sigma''_k \in \Sigma_\bottom(\sigma_k) \subseteq \Sigma_\bottom(\omega_k)}$.
We thus obtain that~$\tau = \sigma''_k \alpha_k^{\varepsilon_k} \dots \alpha_{\ell-1}^{\varepsilon_{\ell-1}} \sigma_\ell \in S'$, a contradiction.
\end{description}

\medskip
Conversely, consider a string~$\sigma \in S' \eqdef \zeta(F')$ such that~$S \eqdef \zeta(F') \ssm \{\sigma\}$ is biclosed, and consider the facet~$F \eqdef \eta(S)$.
Let~$\alpha, \beta$ (resp.~$\alpha', \beta'$) denote the two outgoing (resp.~incoming) arrows at the endpoints of~$\sigma$ such that~$\alpha^{-1}\sigma\beta \in \strings(\bar Q\blossom)$ (resp.~$\alpha'\sigma\beta'^{-1} \in \strings(\bar Q\blossom)$).
Since~$S$ and~$S'$ only differ by~$\sigma$, the facets~$F = \eta(S)$ and~$F' = \eta(S') = \eta(S \cup \{\sigma\})$ can \apriori{} differ by $4$ directed walks by definition of the map~$\eta$: namely, the walks~$\omega(\alpha, S)$, $\omega(\alpha', S)$, $\omega(\beta, S)$ and~$\omega(\beta', S)$ of~$F$ may or may not be in~$F'$ and conversely the walks~$\omega(\alpha, S')$, $ \omega(\alpha', S')$, $\omega(\beta, S')$ and~$\omega(\beta', S')$ of~$F'$ may or may not be in~$F$.
We claim that
\begin{itemize}
\item $\omega(\alpha', S') = \omega(\beta', S')^{-1}$ is a bending walk~$\omega'$ of~$F' \ssm F$,
\item $\omega(\alpha', S) = \omega(\beta, S')$ and~$\omega(\beta', S) = \omega(\alpha, S')$.
\end{itemize}
This claim implies (by Corollary~\ref{coro:pure}) that~$\omega'$ is the single undirected walk of~$F' \ssm F$, and its distinguished arrows are~$\alpha'$ and~$\beta'$ (by Lemma~\ref{lem:distinguishedWalkEta}).
Therefore the non-kissing facets~$F$ and~$F'$ are adjacent and the flip~$F \to F'$ is increasing and supported by~$\sigma$.

To conclude, we just need to prove our claim.
Since~$\sigma \in S'$ and~$S = S' \ssm \{\sigma\}$ is coclosed, there is a walk~$\omega' \in F'$ such that~$\sigma \in \Sigma_\bottom(\omega')$.
Assume that~$\omega'$ is distinct from~$\lambda \eqdef \distinguishedWalk{\alpha'}{F'}$.
Note that~$\omega'$ and~$\lambda$ share the arrow~$\alpha'$, and thus its target vertex~$u \eqdef t(\alpha')$.
Let~$v$ denote the last common vertex of~$\omega'$ and~$\lambda$ after~$\alpha$, and let~$\tau \eqdef \omega'[u,v] = \lambda[u,v]$ denote their common substring between these two vertices.
Since~$\lambda \eqdef \distinguishedWalk{\alpha'}{F'}$, we know that~$\omega'$ (resp.~$\lambda$) leaves~$\tau$ with an outgoing (resp.~incoming) arrow at~$v$.
In particular, $\sigma \ne \tau$ and~$\tau \in \Sigma_\bottom(\lambda) \ssm \{\sigma\} \subseteq S$.
We distinguish two cases:
\begin{description}
\item[$\sigma \supset \tau$] Since~$\omega'$ leaves~$\tau$ with an outgoing arrow at~$v$, we have~$\sigma \ssm \tau \in \Sigma_\bottom(\omega') \ssm \{\sigma\} \subseteq S$. Therefore, we have~$\sigma \in \tau \circ (\sigma \ssm \tau)$ and~$\sigma \notin S$ while~$\tau \in S$ and~$\sigma \ssm \tau \in S$. This contradicts the assumption that~$S$ is closed.
\item[$\sigma \subset \tau$] Since~$\sigma \notin S$ while~$\tau \in S$ and~$S$ is coclosed, we have~$\tau \ssm \sigma \in S$. Therefore there exist bottom substrings~$\sigma_1, \dots, \sigma_\ell$ of walks~$\omega_1, \dots, \omega_\ell$ of~$F'$, arrows~$\alpha_1, \dots, \alpha_{\ell-1} \in Q_1$ and signs~$\varepsilon_1, \dots, \varepsilon_{\ell-1} \in \{-1,1\}$ such that~$\tau \ssm \sigma = \sigma_1 \alpha_1^{\varepsilon_1} \dots \alpha_{\ell-1}^{\varepsilon_{\ell-1}} \sigma_\ell$. Define~$\varepsilon_\ell = 1$ and let~$k \in [\ell]$ be minimal such that~$\varepsilon_k = 1$. Since~$\tau \ssm \sigma$ is a top substring of~$\omega'$, this implies that~$\omega_k$ kisses~$\omega'$. This contradicts the fact that~$F'$ is a non-kissing facet.
\end{description}
Since both cases are impossible, we conclude that~$\omega' = \distinguishedWalk{\alpha'}{F'} = \omega(\alpha', S')$ (by Lemma~\ref{lem:distinguishedWalkEta}).
By symmetry, we obtain that~$\omega' = \omega(\alpha', S') = \omega(\beta', S')$.
Finally, this implies that all bottom (resp.~top) subsegments of~$\sigma$ are contained in~$S'$ (resp.~in the complement of~$S'$).
We conclude by Definition~\ref{def:fromBiclToNKC} that~$\omega(\alpha', S) = \omega(\beta, S')$ and~$\omega(\beta', S) = \omega(\alpha, S')$.
\end{proof}

To conclude, we need a statement from~\cite{Reading-HopfAlgebras} which characterizes the cover relations in a lattice congruence.

\begin{proposition}[{\cite[Prop.~2.2]{Reading-HopfAlgebras}}]
\label{prop:characterizationCoversLatticeQuotient}
Consider a lattice congruence~$\equiv$ on a lattice~$L$ and two congruence classes~$X, Y \in L/{\equiv}$.
Then~$X$ covers~$Y$ in~$L/{\equiv}$ if and only if the minimal element of~$X$ covers some element of~$Y$ in~$L$.
\end{proposition}

This concludes our proof of Theorem~\ref{thm:lattice}, that we can now restate more precisely as follows.

\begin{corollary}
\label{coro:finalLatticeQuotient}
If~$\bar Q$ is a gentle bound quiver whose non-kissing complex~$\RNKC$ is finite, then the non-kissing oriented flip graph~$\NKG$ is the Hasse diagram of the lattice quotient~$\Bicl{\bar Q}/{\equiv}$ of the congruence-uniform lattice of biclosed sets of strings by the lattice congruence~$\equiv$.
\end{corollary}

\begin{proof}
Proposition~\ref{prop:latticeCongruence} affirms that the maps~$\projDown$ and~$\projUp$ of Definition~\ref{def:downUpProjections} define a lattice congruence~$\equiv$.
Corollary~\ref{coro:fibers} ensures that the congruence classes of~$\equiv$ are the fibers of~$\eta$.
Finally, Propositions~\ref{prop:covers} and~\ref{prop:characterizationCoversLatticeQuotient} ensure that the cover relations of~$\Bicl{\bar Q}/{\equiv}$ are precisely the increasing flips of~$\NKG$.
\end{proof}

\begin{example}
Corollary~\ref{coro:finalLatticeQuotient} is illustrated on \fref{fig:exmLatticeQuotient}, which shows a specific lattice quotient and the corresponding increasing flip graph.
\end{example}

\begin{definition}
We call \defn{non-kissing lattice} and denote by~$\NKL$ the transitive closure of the non-kissing oriented flip graph~$\NKG$.
\end{definition}

\subsection{Sublattice}

As observed in Remark~\ref{rem:sublattice}, the subposet of~$\Bicl{\bar Q}$ induced by~$\projDown \big( \Bicl{\bar Q} \big)$ is a join-sublattice of~$\Bicl{\bar Q}$ but could fail to be a sublattice.
It turns out that there is sufficiently symmetry in the construction to ensures that it is indeed a sublattice.
A similar result was stated for grid bound quivers in~\cite[Lem.~4.5]{GarverMcConville-grid} and for dissection bound quivers in~\cite[Thm.~4.11]{GarverMcConville}.
See \fref{fig:exmSublattice} for an illustration.

\begin{proposition}
\label{prop:sublattice}
The non-kissing lattice~$\NKL$ is isomorphic to the sublattice of~$\Bicl{\bar Q}$ induced by~$\projDown \big( \Bicl{\bar Q} \big)$ (or dually by~$\projUp \big( \Bicl{\bar Q} \big)$). More precisely,
\begin{enumerate}[(i)]
\item $\zeta(F \meet F') = \zeta(F) \meet \zeta(F')$ and~$\zeta(F \join F') = \zeta(F) \join \zeta(F')$ for any non-kissing facets~${F, F' \in \NKC}$,
\item $\eta(S \meet S') = \eta(S) \meet \eta(S')$ and~$\eta(S \join S') = \eta(S) \join \eta(S')$ for any biclosed sets~$S, S' \in \projDown \big( \Bicl{\bar Q} \big)$.
\end{enumerate}
\end{proposition}

\begin{proof}
This follows from the reversing operation discussed in Remarks~\ref{rem:reverseFlipGraph}, \ref{rem:reverseBiclosed} and Lemma~\ref{rem:reversedProjections}.
Indeed, consider~$R, S \in \Bicl{\bar Q}$.
By Lemma~\ref{rem:reversedProjections}, we have
\begin{align*}
\projDown(R) \meet \projDown(S) 
& = \big( \strings^\pm(\bar Q) \ssm \projUp\big( \strings^\pm(\reversed{\bar Q}) \ssm R \big) \big) \meet \big( \strings^\pm(\bar Q) \ssm \projUp\big( \strings^\pm(\reversed{\bar Q}) \ssm S \big) \big) \\
& = \strings^\pm(\bar Q) \ssm \big(  \big( \projUp\big( \strings^\pm(\reversed{\bar Q}) \ssm R \big) \join \big( \projUp\big( \strings^\pm(\reversed{\bar Q}) \ssm S \big) \big) \\
& = \strings^\pm(\bar Q) \ssm \projUp(T) = \projDown\big( \strings^\pm(\reversed{\bar Q}) \ssm T \big)
\end{align*}
for some~$T \in \Bicl{\reversed{\bar Q}} = \Bicl{\bar Q}$.
Therefore, $\projDown(R) \meet \projDown(S) \in \projDown \big( \Bicl{\bar Q} \big)$.
\end{proof}

\begin{example}
\fref{fig:exmSublattice} illustrates Proposition~\ref{prop:sublattice} for a specific gentle bound quiver.

\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[width=1.1\textwidth]{exmSublattice}}
	\caption{The inclusion lattice of biclosed sets~$\Bicl{\bar Q}$ with congruence classes of~$\equiv$ in blue (left), the sublattice of~$\Bicl{\bar Q}$ induced by~$\projDown \big( \Bicl{\bar Q} \big)$ (middle left) and by~$\projUp \big( \Bicl{\bar Q} \big)$ (middle right), and the corresponding lattice of increasing flips on facets of~$\NKC$ (right).}
	\label{fig:exmSublattice}
\end{figure}
\end{example}

\section{Canonical join-representations in~$\NKL$ and the non-friendly complex}
\label{sec:nonFriendlyComplex}

As we have established that the non-kissing lattice~$\NKL$ is congruence-uniform, and thus semi-distributive, it is natural to study its canonical join complex.
Our first step is a bijective understanding of the join-irreducible elements of~$\NKL$.
They correspond to the distinguishable strings of~$\bar Q$, for which we first need an explicit characterization.

\subsection{Distinguishable strings}
\label{subsec:distinguishableStrings}

Recall Definition~\ref{def:distinguishedSubstring} for distinguishable chords.
We now have all tools to describe the distinguishable strings in a gentle bound quiver~$\bar Q$.
Our goal in this section is to prove the following statement.

\begin{proposition}
\label{prop:characterizationDistinguishableStrings}
A string~$\sigma \in \strings^\pm(\bar Q)$ is distinguishable if and only if $\Sigma_\bottom(\sigma) \cap \Sigma_\top(\sigma) = \{\sigma\}$.
\end{proposition}

\begin{proof}
Assume first that~$\sigma$ is distinguishable and consider~$\tau \in \Sigma_\bottom(\sigma) \cap \Sigma_\top(\sigma)$.
Let~$\tau_\bottom$ (resp.~$\tau_\top$) denote the bottom (resp.~top) copy of~$\tau$ seen as a substring of~$\sigma$.
If~$\tau \ne \sigma$, then $\tau_\bottom$ and~$\tau_\top$ are distinct as substrings of~$\sigma$ but coincide as strings of~$\bar Q$.
We distinguish two cases:
\begin{itemize}
\item If~$s(\tau_\bottom) = s(\sigma)$ and~$t(\tau_\top) = t(\sigma)$, then the two endpoints of~$\sigma$ coincide (otherwise, $\NKC$ would not be finite) so that $\sigma$ is not distinguishable (otherwise, the same arrow would be distinguished twice along a path).
\item Otherwise, we can assume for example that~$\tau_\top$ does not share an endpoint with~$\sigma$. Then for any walk~$\omega$ such that~$\sigma \in \Sigma_\bottom(\omega)$, we have~$\tau \in \Sigma_\bottom(\omega) \cap \Sigma_\top(\omega)$ so that~$\omega$ is self-kissing. It follows that~$\sigma$ is not distinguishable.
\end{itemize}
We conclude that if~$\sigma$ is distinguishable, then~$\Sigma_\bottom(\sigma) \cap \Sigma_\top(\sigma) = \{\sigma\}$.
%
The converse statement will follow from the next two lemmas.
\end{proof}

\begin{remark}
It follows from Propositions~\ref{prop:characterizationDistinguishableStrings} and~\ref{prop:morphismsStringModules} that a string~$\sigma$ is distinguishable if and only if~$\Hom{A} \big( M(\sigma), M(\sigma) \big) = k$.
Modules~$M$ such that~$\Hom{A}(M, M) = k$ are called \defn{bricks}.
\end{remark}

\begin{lemma}
\label{lem:sigmaBottomCapSigmaTop}
For any~$\sigma, \tau \in \strings^\pm(\bar Q)$, any string in~$\closure{\Sigma_\bottom(\sigma)} \cap \Sigma_\top(\tau)$ has at least one substring in~$\Sigma_\bottom(\sigma) \cap \Sigma_\top(\tau)$. In particular, we have
\begin{align*}
\Sigma_\bottom(\sigma) \cap \Sigma_\top(\sigma) = \{\sigma\} & \quad \Longrightarrow \quad \closure{\Sigma_\bottom(\sigma)} \cap \Sigma_\top(\sigma) = \{\sigma\} \\
\text{and}\qquad
\Sigma_\bottom(\sigma) \cap \Sigma_\top(\tau) = \varnothing & \quad \Longrightarrow \quad \closure{\Sigma_\bottom(\sigma)} \cap \Sigma_\top(\tau) = \varnothing.
\end{align*}
\end{lemma}

\begin{proof}
Let~$\rho \in \closure{\Sigma_\bottom(\sigma)} \cap \Sigma_\top(\tau)$.
As~$\rho \in \closure{\Sigma_\bottom(\sigma)}$, there exists substrings~$\rho_1, \dots, \rho_\ell \in \Sigma_\bottom(\sigma)$, arrows~$\alpha_1, \dots, \alpha_{\ell-1} \in Q_1$ and signs~$\varepsilon_1, \dots, \varepsilon_{\ell-1} \in \{-1,1\}$ such that~$\rho = \rho_1 \alpha_1^{\varepsilon_1} \dots \alpha_{\ell-1}^{\varepsilon_{\ell-1}} \rho_\ell$.
Assume that there exists~$k \in [\ell-1]$ such that~$\varepsilon_k = 1$ and choose~$k$ minimal for this property (the proof is similar if there exists~$k \in [\ell-1]$ such that~$\varepsilon_k = -1$).
If~$k > 1$, then~$\varepsilon_{k-1} = -1$ while~$\varepsilon_k = 1$ so that~$\rho_k \in \Sigma_\top(\tau)$.
If~$k = 1$, then~$\rho_1$ starts at the endpoint of~$\rho$ and finishes with an outgoing arrow, so that~$\rho_1$ is a top substring of~$\rho$ which is a top substring of~$\tau$, and thus~$\rho_1 \in \Sigma_\top(\tau)$.
In both cases, we found a substring of~$\rho$ in~$\Sigma_\bottom(\sigma) \cap \Sigma_\top(\tau)$.
\end{proof}

\begin{lemma}
\label{lem:bijectionDistinguishableStringsWalks}
Let~$\sigma \in \strings^\pm(\bar Q)$ be such that~$\Sigma_\bottom(\sigma) \cap \Sigma_\top(\sigma) = \{\sigma\}$.
Let~$\alpha', \beta'$ be the two incoming arrows at the endpoint of~$\sigma$ such that~$\alpha'\sigma\beta'^{-1} \in \strings(\bar Q\blossom)$.
Then the oriented walks~$\omega \big( \alpha', \closure{\Sigma_\bottom(\sigma)} \big)$ and~$\omega \big( \beta', \closure{\Sigma_\bottom(\sigma)} \big)$ both contain~$\sigma$ and are reverse to each other. Therefore the corresponding unoriented walk of~$\eta \big( \closure{\Sigma_\bottom(\sigma)} \big)$ has distinguished string~$\sigma$.
\end{lemma}

\begin{proof}
Denote for short~$S \eqdef \closure{\Sigma_\bottom(\sigma)}$ and~$F \eqdef \eta(S)$ the corresponding non-kissing facet. Note that~$F$ is well-defined since~$S$ is biclosed by Lemma~\ref{lem:exmBiclosed}.

We first prove that~$\omega(\alpha',S)$ and~$\omega(\beta',S)$ both contain~$\alpha' \sigma \beta'^{-1}$.
For this, write~$\sigma = \alpha_1^{\varepsilon_1} \dots \alpha_\ell^{\varepsilon_\ell}$ for some arrows~$\alpha_1, \dots, \alpha_\ell \in Q_1$ and signs~$\varepsilon_1, \dots, \varepsilon_\ell \in \{-1, 1\}$.
Define~$\sigma_i \eqdef \alpha_1^{\varepsilon_1} \dots \alpha_i^{\varepsilon_i}$ for~$i \in [\ell]$.
We prove by induction that~$\omega(\alpha',S)$ contains~$\sigma_i$.
Indeed, the base case ($i = 0$) is clear, so assume that it holds for~$i \in [\ell-1]$.
We have two situations:
\begin{itemize}
\item If~$\varepsilon_{i+1} = -1$, then~$\sigma_i \in \Sigma_\bottom(\sigma) \subseteq S$ so that~$\omega(\alpha',S)$ contains~$\alpha_{i+1}^{-1}$ and thus~$\sigma_{i+1}$.
\item If~$\varepsilon_{i+1} = 1$, then~$\sigma_i \in \Sigma_\top(\sigma)$. Since~$S \cap \Sigma_\top(\sigma) = \{\sigma\}$ by Lemma~\ref{lem:sigmaBottomCapSigmaTop}, we obtain that~$\sigma_i \notin S$ so that~$\omega(\alpha',S)$ contains~$\alpha_{i+1}$ and thus~$\sigma_{i+1}$.
\end{itemize}
Finally, since~$\sigma \in S$, we obtain that~$\omega(\alpha',S)$ contains~$\alpha' \sigma \beta'^{-1}$.
By symmetry, we thus obtained that~$\omega(\alpha',S)$ and~$\omega(\beta',S)$ both contain~$\alpha' \sigma \beta'^{-1}$.

To conclude, assume that~$\omega(\alpha',S)$ and~$\omega(\beta',S)$ are not reverse to each other, and let~$\tau$ be a maximal common substring of them containing~$\alpha' \sigma \beta'^{-1}$.
Write~$\tau = \tau' \alpha' \sigma \beta'^{-1} \tau''$ and assume for example that~$t(\tau'')$ is not a blossom.
Since~$\tau'' \in S \iff \sigma \beta^{-1} \tau'' \in S$, the two walks~$\omega(\alpha',S)$ and~$\omega(\beta',S)$ should have the same behavior at~$t(\tau'')$, contradicting the maximality of~$\tau$.
\end{proof}

In fact, Lemma~\ref{lem:bijectionDistinguishableStringsWalks} even provides a bijection from distinguishable strings to walks which are not self-kissing and not in the peak facet.
We will prove that this map is bijective in Proposition~\ref{prop:bijectionDistinguishableStringsWalks}.
Before that, we need the following statement.

\begin{lemma}
\label{lem:bijectionWalksDistinguishableStrings}
For any bending walk~$\omega \in \NKWalks^\pm(\bar Q)$ which is not self-kissing and not in the peak facet, the unique inclusion minimal string in~$\set{\sigma \in \Sigma_\bottom(\omega)}{\closure{\Sigma_\bottom(\omega)} = \closure{\Sigma_\bottom(\sigma)}}$ is distinguishable.
\end{lemma}

\begin{proof}
Let~$X \eqdef \set{\sigma \in \Sigma_\bottom(\omega)}{\closure{\Sigma_\bottom(\omega)} = \closure{\Sigma_\bottom(\sigma)}}$.
Since~$\omega$ is not in the peak facet, it has at least one bottom substring.
It follows that~$X$ is non-empty since it contains the inclusion maximal bottom substring of~$\omega$.
Consider now any inclusion minimal string~$\sigma$ in~$X$ (there could be several).

Assume that~$\sigma$ is not distinguishable.
By Lemma~\ref{lem:bijectionDistinguishableStringsWalks}, there exists~${\tau \in \Sigma_\bottom(\sigma) \cap \Sigma_\top(\sigma)}$ distinct from~$\sigma$.
Since~$\sigma$ is a bottom substring of a non-self-kissing walk~$\omega$, the substring~$\tau$ must be a prefix or a suffix of~$\sigma$, say for example a prefix.
We write~$\sigma = \tau \alpha^\varepsilon \rho$ for an arrow~$\alpha \in Q_1$, a sign~$\varepsilon \in \{-1,1\}$ and a substring~$\rho$ of~$\sigma$.
If~$\varepsilon = -1$, then~$\tau$ would be a top and a bottom substring of~$\omega$, a contradiction.
Therefore~$\varepsilon = 1$ so that we have~$\tau \in \Sigma_\bottom(\rho)$ and thus~$\sigma \in \closure{\Sigma_\bottom(\rho)}$, hence~$\closure{\Sigma_\bottom(\rho)} = \closure{\Sigma_\bottom(\sigma)} = \closure{\Sigma_\bottom(\omega)}$, which would contradict the minimality of~$\sigma$.

Finally, observe that~$\sigma$ is the unique descent of~$\eta \big( \closure{\Sigma_\bottom(\sigma)} \big) = \eta \big( \closure{\Sigma_\bottom(\omega)} \big)$ as will be established in Lemma~\ref{lem:jiJI}.
\end{proof}

We gather the constructions of Lemmas~\ref{lem:bijectionDistinguishableStringsWalks} and~\ref{lem:bijectionWalksDistinguishableStrings} in the following definition.

\begin{definition}
\label{def:bijectionWalksDistinguishableStrings}
For a distinguishable string~$\sigma \in \distinguishableStrings^\pm(\bar Q)$, we denote by $\omega_\bottom(\sigma) \in \NKWalks^\pm(\bar Q)$ the undirected walk constructed in Lemma~\ref{lem:bijectionDistinguishableStringsWalks}, meaning that~$\omega_\bottom(\sigma) = \{\omega(\alpha',S), \omega(\beta',S)\}$ where~$S = \closure{\Sigma_\bottom(\sigma)}$ and~$\alpha', \beta'$ are such that~$\alpha'\sigma\beta'^{-1} \in \strings(\bar Q\blossom)$.

Conversely, for a non-self-kissing walk~$\omega \in \NKWalks^\pm(\bar Q)$ not in the peak facet, we denote by~$\sigma_\bottom(\omega)$ the inclusion minimal string in~$\set{\sigma \in \Sigma_\bottom(\omega)}{\closure{\Sigma_\bottom(\omega)} = \closure{\Sigma_\bottom(\sigma)}}$.
\end{definition}

\begin{proposition}
\label{prop:bijectionDistinguishableStringsWalks}
The maps~$\omega_\bottom$ and~$\sigma_\bottom$ are inverse bijections between the distinguishable strings of~$\bar Q$ and the bending walks of~$\walks^\pm(\bar Q)$ not in the peak facet~$F_\peak$.
\end{proposition}

\begin{proof}
The maps~$\omega_\bottom$ and~$\sigma_\bottom$ are well-defined by Lemmas~\ref{lem:bijectionDistinguishableStringsWalks} and~\ref{lem:bijectionWalksDistinguishableStrings}.
To see that they are inverse bijections, observe that for any~$\sigma \in \distinguishableStrings^\pm(\bar Q)$, we have\[
\closure{ \Sigma_\bottom \big( \sigma_\bottom \big( \omega_\bottom(\sigma) \big) \big)}
= \closure{\Sigma_\bottom \big( \omega_\bottom(\sigma) \big)}
= \closure{\Sigma_\bottom(\sigma)}.
\]
Indeed, the first equality follows from the definition of~$\sigma_\bottom$, while the second one is derived from~$\sigma \in \Sigma_\bottom \big( \omega_\bottom(\sigma) \big)$ and~$\omega_\bottom(\sigma) \in \eta \big( \closure{\Sigma_\bottom(\sigma)} \big)$.
Therefore, we obtain that~$\sigma_\bottom \big( \omega_\bottom(\sigma) \big) = \sigma$ is the unique descent of
\[
\eta \big( \closure{ \Sigma_\bottom \big( \sigma_\bottom \big( \omega_\bottom(\sigma) \big) \big)} \big) = \eta \big( \closure{\Sigma_\bottom(\sigma)} \big)
\]
as will be established in Lemma~\ref{lem:jiJI}.
\end{proof}

\begin{remark}
\label{rem:bijectionDistinguishableStringsWalks}
One can define dually the maps~$\sigma_\top$ and~$\omega_\top$, which provide inverse bijections between distinguishable strings of~$\bar Q$ and the bending walks of~$\walks^\pm(\bar Q)$ not in the deep facet~$F_\deep$.
We will use both~$\sigma_\bottom$ and~$\sigma_\top$ in Section~\ref{subsec:zonotope}.
\end{remark}

\begin{example}
\fref{fig:exmBijectionStringsWalks2} illustrates the maps~$\sigma_\top = \omega_\top^{-1}$ and $\sigma_\bottom = \omega_\bottom^{-1}$ for two quivers on $3$ vertices.

\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=.4]{exmBijectionStringsWalks2}}
	\caption{The bijections~$\sigma_\top = \omega_\top^{-1}$ (top) and $\sigma_\bottom = \omega_\bottom^{-1}$ (bottom) for two specific quivers.}
	\label{fig:exmBijectionStringsWalks2}
\end{figure}
\end{example}

\begin{remark}
Assume that all strings of~$\bar Q$ are distinguishable, as happens for instance in grid and dissection quivers.
Then~$\omega_\bottom(\sigma)$ (resp.~$\omega_\top(\sigma)$) is obtained by adding a hook (resp.~a cohook) at each endpoint of~$\sigma$ while $\sigma_\bottom(\omega)$ (resp.~$\sigma_\top(\omega)$) is obtained by deleting a hook (resp.~a cohook) at each blossom of~$\omega$.
With the notations of Section~\ref{subsec:ARtranslationStringModules},
\[
\omega_\bottom(\sigma) = {}_h\sigma_h
\qquad\text{and}\qquad
\omega_\top(\sigma) = {}_c\sigma_c.
\]
In other words, when all strings of~$\bar Q$ are distinguishable, the bijections~$\omega_\bottom$ and~$\sigma_\bottom$ where already considered in Lemma~\ref{lem:bijections-STTC-NKC}.
As illustrated in \fref{fig:exmBijectionStringsWalks2}\,(right), the bijections of Lemma~\ref{lem:bijections-STTC-NKC} and Definition~\ref{def:bijectionWalksDistinguishableStrings} no longer coincide in general when not all strings are distinguishable.
\end{remark}

\subsection{Join-irreducibles in~$\NKL$}

In order to describe the canonical join-representations in the next section, we now completely describe the join-irreducible elements in~$\NKL$.
We first consider the following join-irreducible elements of~$\Bicl{\bar Q}$.

\begin{lemma}
\label{lem:exmBiclosedJI}
For any distinguishable string~$\sigma \in \strings^\pm(\bar Q)$, the biclosed set~$\closure{\Sigma_\bottom(\sigma)}$ is join-irreducible in~$\Bicl{\bar Q}$.
\end{lemma}

\begin{proof}
We have seen in Lemma~\ref{lem:exmBiclosed} that~$\closure{\Sigma_\bottom(\sigma)}$ is biclosed.
Assume that~$\closure{\Sigma_\bottom(\sigma)} = S \join T$ for some~$S,T \in \Bicl{\bar Q}$.
Recall from Remark~\ref{rem:meetJoinBiclosedSets} that~$S \join T = \closure{(S \cup T)}$.

Assume first that~$\sigma \notin S \cup T$.
Since~$\sigma \in \Sigma_\bottom(\sigma) \subseteq \closure{\Sigma_\bottom(\sigma)} = S \join T = \closure{(S \cup T)}$, there exists strings~$\sigma_1, \dots, \sigma_\ell \in \closure{\Sigma_\bottom(\sigma)} \ssm \{\sigma\}$, arrows~$\alpha_1, \dots, \alpha_{\ell-1} \in Q_1$ and signs~$\varepsilon_1, \dots, \varepsilon_{\ell-1} \in \{-1,1\}$ such that~$\sigma = \sigma_1 \alpha_1^{\varepsilon_1} \dots \alpha_{\ell-1}^{\varepsilon_{\ell-1}} \sigma_\ell$.
Assume that there exists~$k \in [\ell-1]$ such that~$\varepsilon_k = 1$ and choose~$k$ maximal for this property.
Then~$\sigma_{k-1} \in \closure{\Sigma_\bottom(\sigma)} \cap \Sigma_\top(\sigma) = \{\sigma\}$ by Proposition~\ref{prop:characterizationDistinguishableStrings} and Lemma~\ref{lem:sigmaBottomCapSigmaTop}.
We obtain a similar contradiction if there exists~$k \in [\ell-1]$ such that~$\varepsilon_k = -1$.
We thus obtain that~$\sigma \in S \cup T$ and we can thus assume by symmetry that~$\sigma \in S$.

Assume now that there exists~$\tau \in \Sigma_\bottom(\sigma) \ssm S$.
Since~$\tau \ne \sigma$, we can write either~$\sigma = \sigma' \alpha \tau \beta^{-1} \sigma''$ or~$\sigma = \tau \beta^{-1} \sigma''$ or~$\sigma = \sigma' \alpha \tau$ for some arrows~$\alpha, \beta \in Q_1$ and strings~$\sigma', \sigma'' \in \Sigma_\top(\sigma)$.
Assume for example the first situation, the other two are similar.
Since~$\sigma$ is distinguishable and~${\sigma', \sigma'' \in \Sigma_\top(\sigma)}$, Lemma~\ref{lem:sigmaBottomCapSigmaTop} ensures that~$\sigma'$ and~$\sigma''$ do not belong to~$\closure{\Sigma_\bottom(\sigma)}$ and thus to~$S$.
We thus obtain that~$\sigma \in \sigma' \circ \tau \circ \sigma''$ with~$\sigma \in S$ while~$\sigma', \tau, \sigma \notin S$ which contradicts the coclosedness of~$S$.

We conclude that~$\Sigma_\bottom(\sigma) \subseteq S$. Since~$S$ is closed, we thus obtain that~$S = \closure{\Sigma_\bottom(\sigma)}$, which proves that~$\closure{\Sigma_\bottom(\sigma)}$ is join-irreducible.
\end{proof}

Recall the notion of descent from Definition~\ref{def:increasingFlip}.

\begin{lemma}
\label{lem:jiJI}
Any distinguishable string~$\sigma \in \distinguishableStrings^\pm(\bar Q)$ is the unique descent of the non-kissing facet~$\eta \big( \closure{\Sigma_\bottom(\sigma)} \big)$. In other words, $\eta \big( \closure{\Sigma_\bottom(\sigma)} \big)$ is join-irreducible in the non-kissing lattice~$\NKL$.
\end{lemma}

\begin{proof}
Assume that~$\eta \big( \closure{\Sigma_\bottom(\sigma)} \big) = F \join G$ for some non-kissing facets~$F, G \in \NKC$.
By Lemma~\ref{lem:fixProjDown} and Propositions~\ref{prop:section} and~\ref{prop:sublattice}, we have
\[
\closure{\Sigma_\bottom(\sigma)} = \projDown \big( \closure{\Sigma_\bottom(\sigma)} \big) = \zeta \big( \eta \big( \closure{\Sigma_\bottom(\sigma)} \big) \big) = \zeta(F \join G) = \zeta(F) \join \zeta(G).
\]
Since~$\closure{\Sigma_\bottom(\sigma)}$ is join-irreducible in~$\Bicl{\bar Q}$ by Lemma~\ref{lem:exmBiclosedJI}, we can assume that~$\closure{\Sigma_\bottom(\sigma)} = \zeta(F)$ so that~$\eta \big( \closure{\Sigma_\bottom(\sigma)} \big) = \eta(\zeta(F)) = F$ by Proposition~\ref{prop:surjection}.
Thus, $\eta \big( \closure{\Sigma_\bottom(\sigma)} \big) \in \JI \big( \NKL \big)$.
\end{proof}

This motivates the definition of the following map~$\ji : \distinguishableStrings^\pm(\bar Q) \to \JI \big( \NKL \big)$.

\begin{definition}
For a distinguishable string~$\sigma \in \distinguishableStrings^\pm(\bar Q)$, we define the non-kissing facet
\[
\ji(\sigma) \eqdef \eta \big( \closure{\Sigma_\bottom(\sigma)} \big) \in \JI \big( \NKL \big).
\]
\end{definition}

\begin{proposition}
\label{prop:bijectionDistinguishableStringsJI}
The map~$\ji : \sigma \mapsto \ji(\sigma)$ defines a bijection between the distinguishable strings of~$\distinguishableStrings^\pm(\bar Q)$ and the join-irreducible elements of the non-kissing lattice~$\NKL$.
\end{proposition}

\begin{proof}
To see that~$\ji$ is injective, observe that~$\sigma$ is the unique descent of~$\ji(\sigma)$ since~$\ji(\sigma)$ is join-irreducible.
%
To see that~$\ji$ is surjective, consider a join-irreducible~$F$ in~$\NKL$.
By Propositions~\ref{prop:surjection} and~\ref{prop:sublattice}, we have
\[
F = \eta \big( \zeta(F) \big) = \eta \Big( \bigJoin_{\omega \in F} \closure{\Sigma_\bottom(\omega)} \Big) = \bigJoin_{\omega \in F} \eta \big( \closure{\Sigma_\bottom(\omega)} \big).
\]
Since~$F$ is join-irreducible, we obtain that there exists~$\omega \in F$ such that~$F = \eta \big( \closure{\Sigma_\bottom(\omega)} \big)$.
By Lemma~\ref{lem:bijectionWalksDistinguishableStrings}, there exists a distinguishable string~$\sigma = \sigma_\bottom(\omega)$ such that~$\closure{\Sigma_\bottom(\omega)} = \closure{\Sigma_\bottom(\sigma)}$.
We conclude that~$F = \eta \big( \closure{\Sigma_\bottom(\sigma)} \big)$ so that~$\ji$ is surjective.
\end{proof}

\begin{example}
On \fref{fig:exmLatticeQuotient}, observe that the bottom elements in the congruence classes corresponding to join-irreducible facets of~$\NKL$ are precisely the sets of bottom substrings of the $5$ strings of~$\bar Q$.
\end{example}

\subsection{Canonical join-representations in~$\NKL$}

Extending similar results on grid bound quivers~\cite{GarverMcConville-grid} and on dissection bound quivers~\cite{GarverMcConville}, we now consider canonical join-represen\-tations in~$\NKL$.
To apply Proposition~\ref{prop:canonicalJoinRepresentation}, we first need to understand the join-irreducible corresponding to each cover relation that appears in  Proposition~\ref{prop:canonicalJoinRepresentation}\,(i).

\begin{lemma}
Let~$F \to F'$ be an increasing flip in~$\NKG$ supported by~$\sigma$. Then
\[
F \join \ji(\sigma) = F'
\qquad\text{and}\qquad
F \meet \ji(\sigma) = \ji(\sigma)_\star,
\]
where~$\ji(\sigma)_\star$ denotes the only non-kissing facet covered by the join-irreducible facet~$\ji(\sigma)$.
\end{lemma}

\begin{proof}
Applying Proposition~\ref{prop:covers} to the increasing flip~$F \to F'$ supported by~$\sigma$, we have
\[
\zeta \big( \ji(\sigma) \big) = \closure{\Sigma_\bottom(\sigma)} \subseteq \zeta(F')
\qquad\text{and}\qquad
\zeta(F) = \zeta(F') \ssm \{\sigma\}.
\]
%
We thus obtain that~$\ji(\sigma) \le F'$ so that~$F \ne F \join \ji(\sigma) \le F'$. Since~$F$ covers~$F'$ in~$\NKL$, we obtain the first equality
\(
F \join \ji(\sigma) = F'.
\)
%
Moreover, since~$\zeta \big( \ji(\sigma) \big) \subseteq \zeta(F')$ and~$\zeta(F) = \zeta(F') \ssm \{\sigma\}$, %we have
\[
\zeta(F) \meet \zeta \big( \ji(\sigma) \big) = \big( \zeta(F') \ssm \{\sigma\} \big) \cap \zeta \big( \ji(\sigma) \big) = \zeta \big( \ji(\sigma) \big) \ssm \{\sigma\} = \zeta \big( \ji(\sigma)_\star \big).
\]
where the last equality follows from Proposition~\ref{prop:covers} for the increasing flip~$\ji(\sigma)_\star \to \ji(\sigma)$ supported by~$\sigma$.
Therefore, we obtain from Propositions~\ref{prop:surjection} and~\ref{prop:sublattice} that
\[
\ji(\sigma)_\star
= \eta \big( \zeta(\sigma)_\star \big)
= \eta \big( \zeta(F) \meet \zeta \big( \ji(\sigma) \big) \big)
= \eta \big( \zeta(F) \big) \meet \eta \big( \zeta \big( \ji(\sigma) \big) \big)
= F \meet \ji(\sigma).
\qedhere
\]
\end{proof}

Together with Proposition~\ref{prop:canonicalJoinRepresentation}, this statement immediately implies the following description of the join-representation of any facet in~$\NKL$.

\begin{corollary}
\label{coro:joinRepresentations}
The canonical join-representation of a non-kissing facet~$F \in \NKC$ is
\[
F = \bigJoin_{\sigma \in \descents(F)} \ji(\sigma).
\]
\end{corollary}

\begin{remark}
Dually, the map~$\sigma \mapsto \mi(\sigma) \eqdef \eta \big( \closure{\Sigma_\top(\sigma)} \big)$ defines a bijection between the distinguishable strings of~$\distinguishableStrings^\pm(\bar Q)$ and the meet-irreducible elements of the non-kissing lattice~$\NKL$, and the canonical meet-representation of any non-kissing facet~$F \in \NKC$ is $F = \bigMeet_{\sigma \in \ascents(F)} \mi(\sigma)$.
\end{remark}

\subsection{The non-friendly complex}
\label{subsec:nonFriendlyComplex}

\enlargethispage{.4cm}
To conclude, we want to understand the canonical join complex of the non-kissing lattice~$\NKL$.
In view of Corollary~\ref{coro:joinRepresentations}, this amounts to understanding which sets of strings are descent sets of non-kissing facets of~$\NKC$.
We start with a seemingly unrelated definition extending that of~\cite[Sect.~3.4]{GarverMcConville-grid}.

\begin{definition}\label{def: friendly}
Two strings~$\sigma, \tau \in \strings^\pm(\bar Q)$ are \defn{non-friendly} if
\[
\Sigma_\top(\sigma) \cap \Sigma_\bottom(\tau) = \varnothing = \Sigma_\bottom(\sigma) \cap \Sigma_\top(\tau).
\]
The \defn{non-friendly complex}~$\NFC$ is the simplicial complex of pairwise non-friendly subsets of distinguishable strings~of~$\bar Q$.
\end{definition}

\begin{example}
The non-friendly complexes of two gentle bound quivers with~$3$ vertices are illustrated on \fref{fig:exmNFC}.
%
\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=.4]{exmNFC}}
	\caption{The non-friendly complex~$\NFC$ for two specific quivers.}
	\label{fig:exmNFC}
\end{figure}
\end{example}

\begin{example}
When~$\bar Q$ is a path on~$n$ vertices, oriented from left to right, then the non-friendly subsets of strings of~$\strings^\pm(\bar Q)$ are in bijection with non-crossing partitions of~$[n+1]$.
The bijection is illustrated in \fref{fig:exmNCP}.
%
\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=.4]{exmNCP}}
	\caption{The bijection between pairwise non-friendly set of strings of an oriented path on $n$ vertices and non-crossing partitions of~$[n+1]$.}
	\label{fig:exmNCP}
\end{figure}
\end{example}

\begin{theorem}
The following assertions are equivalent for a subset~$\Sigma$ of~$\distinguishableStrings^\pm(\bar Q)$:
\begin{enumerate}[(i)]
\item $\Sigma$ is pairwise non-friendly.
\item $\ji(\Sigma) \eqdef \set{\ji(\sigma)}{\sigma \in \Sigma}$ is the canonical join-representation of an element in~$\NKL$.
\item $\Sigma$ is the descent set of a non-kissing facet~$F \in \NKC$.
\end{enumerate}
Thus, the canonical join complex of~$\NKL$ is isomorphic to the non-friendly complex~$\NFC$.
\end{theorem}

\begin{proof}
We first prove~(i)$\iff$(ii), following exactly the same lines as the proof of~\cite[Thm.~4.9]{GarverMcConville-grid}.
Since both the non-friendly complex~$\NFC$ and the canonical join complex of~$\NKL$ are flag simplicial complexes, we just need to check the property for~$|\Sigma| \in \{1,2\}$.
The case $|\Sigma| = 1$ is Proposition~\ref{prop:bijectionDistinguishableStringsJI}.
Consider now the situation~$\Sigma = \{\sigma, \tau\}$.
Since~$\ji(\sigma) = \eta \big( \closure{\Sigma_\bottom(\sigma)} \big)$ and~$\eta$ is a surjective lattice homomorphism, $\ji(\sigma) \join \ji(\tau)$ is a canonical join representation in~$\NKL$ if and only if~$\Sigma_\bottom(\sigma) \join \Sigma_\bottom(\tau)$ is a canonical join-representation in~$\Bicl{\bar Q}$.
We thus just need to prove that the latter is equivalent to~$\sigma$ and~$\tau$ being non-friendly.

Assume first that~$\sigma$ and~$\tau$ are friendly and let for example~$\rho \in \Sigma_\top(\sigma) \cap \Sigma_\bottom(\tau)$.
Then~$\sigma$ decomposes into~$\sigma = \sigma' \alpha^{-1} \rho \beta \sigma''$, or~$\sigma = \rho \beta \sigma''$, or~$\sigma = \sigma' \alpha^{-1} \rho$ for some~$\sigma', \sigma'' \in \Sigma_\bottom(\sigma)$.
Assume for example the first situation, the other two are similar.
Since~$\rho \in \Sigma_\bottom(\tau)$ and~$\sigma', \sigma'' \in \Sigma_\bottom(\sigma)$, we have
\[
\closure{\Sigma_\bottom(\rho)} \subseteq \closure{\Sigma_\bottom(\tau)},
\qquad
\closure{\Sigma_\bottom(\sigma')} \subseteq \closure{\Sigma_\bottom(\sigma)}
\qquad\text{and}\qquad
\closure{\Sigma_\bottom(\sigma'')} \subseteq \closure{\Sigma_\bottom(\sigma)}.
\]
Therefore
\begin{align*}
\closure{\Sigma_\bottom(\sigma)} \join \closure{\Sigma_\bottom(\tau)}
& \subseteq \big( \closure{\Sigma_\bottom(\sigma')} \join \closure{\Sigma_\bottom(\rho)} \join \closure{\Sigma_\bottom(\sigma'')} \big) \join \closure{\Sigma_\bottom(\tau)} \\
& = \closure{\Sigma_\bottom(\sigma')} \join \closure{\Sigma_\bottom(\sigma'')} \join \closure{\Sigma_\bottom(\tau)} \\
& \subseteq \closure{\Sigma_\bottom(\sigma)} \join \closure{\Sigma_\bottom(\tau)}
\end{align*}
We thus obtain that
\[
\closure{\Sigma_\bottom(\sigma)} \join \closure{\Sigma_\bottom(\tau)} = \closure{\Sigma_\bottom(\sigma')} \join \closure{\Sigma_\bottom(\sigma'')} \join \closure{\Sigma_\bottom(\tau)}.
\]
Since~$\closure{\Sigma_\bottom(\sigma')} \subsetneq \closure{\Sigma_\bottom(\sigma)}$ and~$\closure{\Sigma_\bottom(\sigma'')} \subsetneq \closure{\Sigma_\bottom(\sigma)}$, we have obtained a smaller join-represen\-tation of~$\closure{\Sigma_\bottom(\sigma)} \join \closure{\Sigma_\bottom(\tau)}$. Therefore,~$\closure{\Sigma_\bottom(\sigma)} \join \closure{\Sigma_\bottom(\tau)}$ is not its canonical join-representation.

Conversely, assume that~$\closure{\Sigma_\bottom(\sigma)} \join \closure{\Sigma_\bottom(\tau)}$ is not its canonical join-representation, and let~${R \subseteq \distinguishableStrings^\pm(\sigma)}$ be such that
\[
\closure{\Sigma_\bottom(\sigma)} \join \closure{\Sigma_\bottom(\tau)} = \bigJoin_{\rho \in R} \closure{\Sigma_\bottom(\rho)}
\]
is the canonical join representation of~$\closure{\Sigma_\bottom(\sigma)} \join \closure{\Sigma_\bottom(\tau)}$.
Assume that there is no~$\rho \in R$ such that~$\sigma \in \Sigma_\bottom(\rho)$.
Since~$\sigma \in \closure{\Sigma_\bottom(\sigma)} \join \closure{\Sigma_\bottom(\tau)}$, we know that there exist strings~$\rho_1, \dots, \rho_\ell \in R$, substrings~$\xi_1 \in \Sigma_\bottom(\rho_1), \dots, \xi_\ell \in \Sigma_\bottom(\rho_\ell)$, arrows~$\alpha_1, \dots, \alpha_{\ell_1} \in Q_1$ and signs~${\varepsilon_1, \dots, \varepsilon_{\ell-1} \in \{-1,1\}}$ such that~$\sigma = \xi_1 \alpha_1^{\varepsilon_1} \dots \alpha_{\ell-1}^{\varepsilon_{\ell-1}} \xi_\ell$.
Assume that there is~$k \in [\ell-1]$ such that~$\varepsilon_k = 1$ and consider the prefix~$\xi \eqdef \xi_1 \alpha_1^{\varepsilon_1} \dots \alpha_{k-1}^{\varepsilon_{k-1}} \xi_k$ of~$\sigma$ (the proof for the other case is symmetric considering a suffix).
Since~$\xi \in \closure{\Sigma_\bottom(\sigma)} \join \closure{\Sigma_\bottom(\tau)}$, there exist strings~$\zeta_1, \dots, \zeta_m \in \Sigma_\bottom(\sigma) \cup \Sigma_\bottom(\tau)$, arrows~$\beta_1, \dots, \beta_{m-1} \in Q_1$ and signs~$\delta_1, \dots, \delta_{m-1} \in \{-1,1\}$ such that~$\xi = \zeta_1 \beta_1^{\delta_1} \dots \beta_{m-1}^{\delta_{m-1}} \zeta_m$.
Since~$\varepsilon_k = 1$, we have~$\zeta_m \notin \Sigma_\bottom(\sigma)$ so that~$\zeta_m \in \Sigma_\bottom(\tau)$.
Let~$n \in [m]$ be minimal such that~$\zeta \eqdef \zeta_n \beta_n^{\delta_n} \dots \beta_{m-1}^{\varepsilon_{m-1}} \zeta_m \in \closure{\Sigma_\bottom(\tau)}$.
We distinguish two cases:
\begin{itemize}
\item If~$n = 1$, then~$\zeta \in \Sigma_\top(\sigma)$ since~$\varepsilon_k = 1$.
\item If~$n > 1$, then~$\zeta_{n-1} \notin \Sigma_\bottom(\tau)$ (by minimality of~$n$), so that~$\zeta_{n-1} \in \Sigma_\bottom(\sigma)$, and we get~$\delta_{n-1} = -1$. Since~$\varepsilon_k = 1$, we thus obtain that~$\zeta \in \Sigma_\top(\sigma)$.
\end{itemize}
In both cases, we conclude that~$\zeta \in \Sigma_\top(\sigma) \cap \closure{\Sigma_\bottom(\tau)}$, so that~$\sigma$ and~$\tau$ are friendly along~$\zeta$ by Lemma~\ref{lem:sigmaBottomCapSigmaTop}.
This concludes the proof of~(i)$\iff$(ii). Finally, the equivalence (ii)$\iff$(iii) is proved by Corollary~\ref{coro:joinRepresentations}.
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage
\part{The non-kissing associahedron}
\label{part:geometry}

In this section, we provide geometric realizations of the non-kissing complex~$\RNKC$ when it is finite.
Inspired by similar constructions of~\cite{MannevillePilaud-accordion} for dissection bound quivers and~\cite{GarverMcConville} for grid bound quivers, we first construct a complete simplicial fan~$\gvectorFan$ realizing~$\RNKC$~(\ref{subsec:gvectorFan}).
We then prove that~$\gvectorFan$ is the normal fan of a polytope~$\Asso$~(\ref{subsec:associahedron}) and that the graph of this polytope oriented in a suitable direction is the Hasse diagram of the non-kissing lattice~$\NKL$~(\ref{subsec:geomLattice}).
We then discuss the existence of a zonotope~$\Zono$ which could play the same role for~$\Asso$ as the classical permutahedron plays for the classical associahedron~(\ref{subsec:zonotope}).
Finally, we discuss certain transformations of the quiver~$Q$ that correspond to natural projections of~$\Asso$~(\ref{subsec:projections}).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Recollections on polyhedral geometry}
\label{sec:polyhedralGeometry}

We briefly recall basic definitions and properties of polyhedral fans and polytopes, and refer to~\cite{Ziegler-polytopes} for a classical textbook on this topic.

\begin{definition}
A \defn{polyhedral cone} is a subset of~$\R^n$ defined equivalently as the positive span of finitely many vectors or as the intersection of finitely many closed linear halfspaces.
Throughout the paper, we write~$\R_{\ge0}\b{R}$ for the positive span of a set~$\b{R}$ of vectors of~$\R^n$.
The \defn{faces} of a cone~$C$ are the intersections of~$C$ with the supporting hyperplanes of~$C$.
The $1$-dimensional (resp.~codimension~$1$) faces of~$C$ are called~\defn{rays} (resp.~\defn{facets}) of~$C$.
A cone is \defn{simplicial} if it is generated by a set of independent vectors.
\end{definition}

\begin{definition}
A \defn{polyhedral fan} is a collection~$\Fan$ of polyhedral cones such that
\begin{itemize}
\item if~$C \in \Fan$ and~$F$ is a face of~$C$, then~$F \in \Fan$,
\item the intersection of any two cones of~$\Fan$ is a face of both.
\end{itemize}
A fan is \defn{simplicial} if all its cones are, and \defn{complete} if the union of its cones covers the ambient space~$\R^n$.
\end{definition}

The following statement characterizes complete simplicial fans.
A formal proof can be found \eg in~\cite[Coro.~4.5.20]{DeLoeraRambauSantos}.

\begin{proposition}
\label{prop:characterizationFan}
Consider a pseudomanifold~$\Delta$ on a finite vertex set~$V$ and a set of vectors $\big( \b{r}(v) \big)_{v \in V}$ of~$\R^n$.
For~$\triangle \in \Delta$, define the cone~$\b{r}(\triangle) \eqdef \bigset{\b{r}(v)}{v \in \triangle}$.
Then the collection of cones~${\bigset{\R_{\ge 0}\b{r}(\triangle)}{\triangle \in \Delta}}$ forms a complete simplicial fan if and only if
\begin{enumerate}
\item there exists a facet~$\triangle$ of~$\Delta$ such that~$\b{r}(\triangle)$ is a basis of~$\R^n$ and such that the open cones~$\R_{> 0}\b{r}(\triangle)$ and~$\R_{> 0}\b{r}(\triangle')$ are disjoint for any facet~$\triangle'$ of~$\Delta$ distinct from~$\triangle$;
\item for two adjacent facets~$\triangle, \triangle'$ of~$\Delta$ with~$\triangle \ssm \{v\} = \triangle' \ssm \{v'\}$, there is a linear dependence
\[
\alpha \, \b{r}(v) + \alpha' \, \b{r}(v') + \sum_{w \in \triangle \cap \triangle'} \beta_w \, \b{r}(w) = 0
\]
on~$\b{r}(\triangle \cup \triangle')$ where the coefficients~$\alpha$ and~$\alpha'$ have the same sign.
(When these conditions hold, these coefficients do not vanish and the linear dependence is unique up to rescaling.)
\end{enumerate}
\end{proposition}

\begin{definition}
A \defn{polytope} is a subset~$P$ of~$\R^n$ defined equivalently as the convex hull of finitely many points or as a bounded intersection of finitely many closed affine halfspaces.
The \defn{faces} of~$P$ are the intersections of~$P$ with its supporting hyperplanes.
The dimension~$0$ (resp.~dimension~$1$, resp.~codimension~$1$) faces of~$P$ are called \defn{vertices} (resp.~\defn{edges}, resp.~\defn{facets}) of~$P$.
\end{definition}

\begin{definition}
The (outer) \defn{normal cone} of a face~$F$ of~$P$ is the cone generated by the outer normal vectors of the facets of~$P$ containing~$F$.
The (outer) \defn{normal fan} of~$P$ is the collection of the (outer) normal cones of all its faces.
We say that a complete polyhedral fan in~$\R^n$ is \defn{polytopal} when it is the normal fan of a polytope of~$\R^n$.
\end{definition}

The following statement provides a characterization of polytopality of complete simplicial fans.
It is a reformulation of regularity of triangulations of vector configurations, introduced in the theory of secondary polytopes~\cite{GelfandKapranovZelevinsky}, see also~\cite{DeLoeraRambauSantos}.
We present here a convenient formulation from~\cite[Lem.~2.1]{ChapotonFominZelevinsky}.

\begin{proposition}
\label{prop:characterizationPolytopalFan}
Consider a pseudomanifold~$\Delta$ with vertex set~$V$ and a set of vectors~$\big( \b{r}(v) \big)_{v \in V}$ of~$\R^n$ such that~$\Fan \eqdef \bigset{\R_{\ge 0}\b{r}(\triangle)}{\triangle \in \Delta}$ is a complete simplicial fan in~$\R^n$.
Then the following are equivalent:
\begin{enumerate}
\item $\Fan$ is the normal fan of a simple polytope in~$\R^n$;
\item There exists a map~$h: V \to \R_{> 0}$ such that for any two adjacent facets~$\triangle, \triangle'$ of~$\Delta$ with~$\triangle \ssm \{v\} = \triangle' \ssm \{v'\}$, we have
\[
\alpha \, h(v) + \alpha' \, h(v') + \sum_{w \in \triangle \cap \triangle'} \beta_{w} \, h(w) > 0,
\]
where
\[
\alpha \, \b{r}(v) + \alpha' \, \b{r}(v') + \sum_{w \in \triangle \cap \triangle'} \beta_{w} \, \b{r}(w) = 0
\]
is the unique (up to rescaling) linear dependence with~$\alpha, \alpha' > 0$ between the rays of~${\b{r}(\triangle \cup \triangle')}$.
\end{enumerate}
Under these conditions, $\Fan$ is the normal fan of the polytope defined by
\[
\bigset{\b{x} \in \R^n}{\dotprod{\b{r}(v)}{\b{x}} \le h(v) \text{ for all } v \in V}.
\]
\end{proposition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Non-kissing geometry}
\label{sec:associahedron}

\subsection{$\b{g}$-vectors and $\b{c}$-vectors}
\label{subsec:gcvectors}

Let~$(\b{e}_v)_{v \in Q_0}$ be the standard basis of~$\R^{Q_0}$.
We first define an analog of the characteristic vector for multisets.

\begin{definition}
For a multiset~$V \eqdef \{v_1, \dots, v_m\}$ of vertices of~$Q_0$, we denote by~$\multiplicityVector_V \in \R^{Q_0}$ the \defn{multiplicity vector} of~$V$ defined~by
\[
\multiplicityVector_V \eqdef \sum_{i \in [m]} \b{e}_{v_i} = \sum_{v \in Q_0} |\set{i \in [m]}{v_i = v}| \, \b{e}_v.
\]
For a string~$\sigma \in \strings^\pm(\bar Q)$, we define~$\multiplicityVector_\sigma \eqdef \multiplicityVector_{V(\sigma)}$ where~$V(\sigma)$ is the multiset of vertices of~$\sigma$. 
\end{definition}

We now define two families of vectors that will play a crucial role in the geometric construction.

\begin{definition}\label{def: g-vectors for walks}
For a walk~$\omega \in \NKWalks^\pm(\bar Q)$, we denote by~$\peaks{\omega}$ (resp.~by~$\deeps{\omega}$) the multiset of vertices of~$Q_0$ corresponding to the peaks (resp.~deeps) of~$\omega$.
The \defn{$\b{g}$-vector} of a walk~$\omega$ is the vector~${\gvector{\omega} \in \R^{Q_0}}$ defined by
\[
\gvector{\omega} \eqdef \multiplicityVector_{\peaks{\omega}} - \multiplicityVector_{\deeps{\omega}}.
\]
For a set~$\Omega$ of walks, we let~$\gvectors{\Omega} \eqdef \set{\gvector{\omega}}{\omega \in \Omega}$.
Observe that~$\gvector{\omega} = 0$ for a straight walk~$\omega$.
\end{definition}

\begin{example}
The $\b{g}$-vector of the plain blue walk on \fref{fig:exmFacet}\,(left) is~$(0,-1,0,0,1,0)$ (see \fref{fig:exmBlossomingQuiver} for the labeling order of the vertices of the quiver~$Q\ex$).
See \fref{fig:gcvectors} for more examples of $\b{g}$-vectors.
\end{example}

\begin{remark}\label{rem: g-vectors coincide}
One easily checks that if $\sigma$ is a string for a gentle bound quiver $\bar Q$, and $\omega(\sigma)$ the associated walk in the blossoming bound quiver $\bar Q\blossom$ as in Lemma~\ref{lem:bijections-STTC-NKC}, then $\gvector{\sigma}=\gvector{\omega(\sigma)}$.
\end{remark}

\begin{definition}\label{def: c-vectors}
Consider a bending walk~$\omega$ in a non-kissing facet~$F \in \RNKC$.
Recall from Proposition~\ref{prop:distinguishedArrows} that the walk~$\omega$ carries two distinguished arrows~$\distinguishedArrows{\omega}{F}$ surrounding its distinguished string~$\distinguishedString{\omega}{F}$ (see \fref{fig:gcvectors}).
Define
\[
\distinguishedSign{\omega}{F} \eqdef 
\begin{cases}
\phantom{-}1 & \text{if~$\distinguishedString{\omega}{F}$ is a top substring of~$\omega$ (\ie the arrows~$\distinguishedArrows{\omega}{F}$ point outside),} \\
-1 & \text{if~$\distinguishedString{\omega}{F}$ is a bottom substring of~$\omega$ (\ie if the arrows~$\distinguishedArrows{\omega}{F}$ point inside).}
\end{cases}
\]
The \defn{$\b{c}$-vector} of a walk~$\omega$ of~$F$ is the vector~${\cvector{\omega}{F} \in \R^{Q_0}}$ defined by
\[
\cvector{\omega}{F} \eqdef \distinguishedSign{\omega}{F} \, \multiplicityVector_{\distinguishedString{\omega}{F}}.
\]
We let~$\cvectors{F} \eqdef \set{\cvector{\omega}{F}}{\omega \in F}$ be the set of $\b{c}$-vectors of a non-kissing facet~$F \in \RNKC$, and~$\allcvectors \eqdef \bigcup_F \cvectors{F}$ be the set of all $\b{c}$-vectors of all non-kissing facets~${F \in \RNKC}$.
\end{definition}

\begin{example}
In the facet~$F\ex$ of \fref{fig:exmFacet}\,(right), the $\b{c}$-vector of the blue walk is~$(0,-1,0,0,0,0)$ while the $\b{c}$-vector of the yellow path is~$(0,1,0,1,1,0)$ (see \fref{fig:exmBlossomingQuiver} for the labeling order of the vertices of the quiver~$Q\ex$ and \fref{fig:gcvectors}\,(left) to see the distinguished arrows in the facet~$F\ex$).
See \fref{fig:gcvectors} for more examples of $\b{c}$-vectors.

\begin{figure}[t]
	\capstart
	\centerline{$\raisebox{-1.5cm}{\begin{overpic}[scale=.7]{exmVectors}\put(60,4){$F\ex$}\end{overpic}}$ \qquad \input{gcmatrices}}
	\caption{The $\b{g}$- and $\b{c}$-matrices of the facet~$F\ex$. Their columns correspond to the $\b{g}$- and $\b{c}$-vectors of the different walks of~$F\ex$. See \fref{fig:exmBlossomingQuiver} for the labeling order of the vertices of the quiver~$Q\ex$. Note that~$\gvectors{F\ex} \cdot \cvectors{F\ex}^T = \one$.}
	\label{fig:gcvectors}
\end{figure}
\end{example}

\begin{example}
\label{exm:gcvectors}
The $\b{g}$- and $\b{c}$-vectors of the peak and deep facets~$F_\peak$ and~$F_\deep$ are given by
\begin{gather*}
\gvector{v_\peak} = \b{e}_v, \quad 
\gvector{v_\deep} = -\b{e}_v, \quad
\cvector{v_\peak}{F_\peak} = \b{e}_v, \quad\text{and}\quad
\cvector{v_\deep}{F_\deep} = -\b{e}_v.
\end{gather*}
\end{example}

\begin{remark}
\label{rem:signCoherence}
The definitions of $\b{g}$- and $\b{c}$-vectors immediately imply the \defn{sign-coherence property}: for any non-kissing facet~$F \in \RNKC$,
\begin{itemize}
\item for any~$\omega \in F$, all coordinates of the $\b{c}$-vector~$\cvector{\omega}{F}$ have the same sign,
\item for~$v \in Q_0$, the~$v$th coordinates of all $\b{g}$-vectors~$\gvector{\omega}$ for~$\omega \in F$ have the same sign (otherwise, the corresponding walks would kiss at~$v$).
\end{itemize}
In particular, a $\b{c}$-vector is called \defn{positive} when all its coordinates are non-negative and \defn{negative} when all its coordinates are non-positive.
\end{remark}

\begin{remark}
\label{rem:setcvectors}
There is a subtle relation between $\b{c}$-vectors and strings. Indeed, $\b{c}$-vectors are multiplicity vectors of the vertex multisets of some strings of~$\bar Q$, but
\begin{itemize}
\item not all strings are distinguishable (see Definition~\ref{def:distinguishedSubstring} and Proposition~\ref{prop:characterizationDistinguishableStrings}), and
\item distinct distinguishable strings may have identical vertex multisets.
\end{itemize}
\end{remark}

The $\b{g}$- and $\b{c}$-vectors have been designed so that the following statement holds, as illustrated in \fref{fig:gcvectors}.

\begin{proposition}
\label{prop:gvectorscvectorsDualBases}
For any non-kissing facet~$F \in \RNKC$, the set of $\b{g}$-vectors~$\gvectors{F}$ and the set of $\b{c}$-vectors~$\cvectors{F}$ form dual bases. 
\end{proposition}

\begin{proof}
Consider two walks~$\mu, \nu \in F$.
By definition, the $\b{g}$-vector~$\gvector{\mu}$ counts the corners of~$\omega$, while the $\b{c}$-vector~$\cvector{\nu}{F}$ counts, up to a sign, the vertices on the distinguished string~$\distinguishedString{\nu}{F}$. 
To compute the scalar product~$\dotprod{\gvector{\mu}}{\cvector{\nu}{F}}$, we thus need to understand which corners of~$\mu$ lie on the distinguished string~$\distinguishedString{\nu}{F}$.

Assume first that~$\mu = \nu$. If the distinguished arrows~$\distinguishedArrows{\omega}{F}$ point outside, then~$\cvector{\mu}{F}$ is positive and there is one more peak than deeps on the distinguished string~$\distinguishedString{\mu}{F}$.
Otherwise, ${\cvector{\mu}{F}}$ is negative and there is one more deep than peaks on the distinguished string~$\distinguishedString{\mu}{F}$.
In both cases, we obtain~$\dotprod{\gvector{\mu}}{\cvector{\mu}{F}} = 1$.

Assume now that~$\mu \ne \nu$.
Consider a maximal common substring~$\sigma$ in the intersection of~$\mu$ with~$\nu$.
Since they have opposite directions, the distinguished arrows of~$\nu$ cannot both belong to~$\sigma$.
Therefore, the distinguished string~$\distinguishedString{\nu}{F}$ covers either the whole string~$\sigma$, or nothing, or an initial or final substring of~$\sigma$.
Moreover, the arrows of~$\mu$ incident to but not in~$\distinguishedString{\nu}{F}$ have the same direction along~$\mu$.
Therefore, the distinguished string~$\distinguishedString{\nu}{F}$ contains as many peaks as deeps of~$\mu$ in~$\sigma$.
We thus showed that~$\sigma$ does not contributes to~$\dotprod{\gvector{\mu}}{\cvector{\nu}{F}}$.
Summing the contribution of all common substrings of~$\mu$ and~$\nu$, we obtain that~$\dotprod{\gvector{\mu}}{\cvector{\nu}{F}} = 0$ when~$\mu \ne \nu$.
We conclude that~$\gvectors{F}$ and~$\cvectors{F}$ are dual bases.
\end{proof}

\subsection{The $\b{g}$-vector fan}
\label{subsec:gvectorFan}

We now restrict our attention to a gentle bound quiver~$\bar Q$ with a finite non-kissing complex~$\RNKC$.
We present a fan realization of~$\RNKC$ inspired by similar statements of T.~Manneville and V.~Pilaud in~\cite{MannevillePilaud-accordion} for dissection bound quivers and by A.~Garver and T.~McConville in~\cite{GarverMcConville-grid} for grid bound quivers.
As illustrated in \fref{fig:all2}, this construction actually provides fan realizations of all non-kissing complexes (finite or not).
Our elementary argument proves the finite case, the general case can be proven using~\cite{DehyKeller, DemonetIyamaJasso} (see~Remark~\ref{rem:linDep}).

\begin{theorem}
\label{thm:gvectorFan}
For a gentle bound quiver~$\bar Q$ with finite non-kissing complex~$\RNKC$, the collection of cones
\[
\gvectorFan \eqdef \bigset{\R_{\ge0} \gvectors{F}}{F \text{ non-kissing face of } \RNKC}
\]
forms a complete simplicial fan, that we call the \defn{$\b{g}$-vector fan} of~$\bar Q$.
\end{theorem}

\begin{proof}
We use the characterization of complete simplicial fans of Proposition~\ref{prop:characterizationFan}.
By Remark~\ref{rem:signCoherence}, the cone~$\R_{\ge0} \gvectors{F_\peak}$ is the only cone of~$\gvectorFan$ intersecting the interior of the positive orthant~$(\R_{\ge0})^{Q_0}$.
Consider now two adjacent non-kissing facets~$F,F' \in \RNKC$.
Let~$\omega \in F$ and~$\omega' \in F'$ be such that~${F \ssm \{\omega\} = F' \ssm \{\omega'\}}$, and let~$\mu$ and~$\nu$ be the two other walks involved in the flip as defined in Proposition~\ref{prop:flip} (see \fref{fig:flip}).
Note that a vertex~$v \in Q_0$ is a peak of none of (resp.~one of, resp.~both) the walks~$\omega, \omega'$ if and only if it is a peak of none of (resp.~one of, resp.~both) the walks~$\mu, \nu$.
The same holds for deeps.
We thus have the linear~dependence
\[
\gvector{\omega} + \gvector{\omega'} = \gvector{\mu} + \gvector{\nu}
\]
among the $\b{g}$-vectors involved in the flip.
Note that this equality holds even when~$\mu$ and~$\nu$ coincide, or when~$\mu$ or~$\nu$ are straight walks (in which case their $\b{g}$-vector vanishes).
This shows that~$\gvectorFan$ satisfies the two conditions of Proposition~\ref{prop:characterizationFan}, and thus shows that $\gvectorFan$ is a fan.
\end{proof}

\begin{remark}
The linear dependence~$\gvector{\omega} + \gvector{\omega'} = \gvector{\mu} + \gvector{\nu}$ relating the $\b{g}$-vectors of two adjacent non-kissing facets~$F,F' \in \RNKC$ shows that~${\det \big( \gvector{F} \big) = - \det \big( \gvector{F'} \big)}$.
Since the initial cone~$\R_{\ge0} \gvectors{F_\peak}$ is generated by the coordinate vectors (see Example~\ref{exm:gcvectors}), we obtain that~$\det \big( \gvector{F} \big) = \pm 1$ for all non-kissing facets~$F \in \RNKC$, so that the $\b{g}$-vector fan~$\gvectorFan$ is~\defn{smooth}.
\end{remark}

\begin{remark}
\label{rem:cvectorFan}
Call \defn{$\b{c}$-vector fan} the fan~$\cvectorFan$ defined by the arrangement of the hyperplanes orthogonal to the $\b{c}$-vectors of~$\allcvectors$.
Be aware that contrarily to the $\b{g}$-vector fan whose rays are the $\b{g}$-vectors, the $\b{c}$-vectors are not the rays but the normal vectors of the hyperplanes of the $\b{c}$-vector fan.
By Proposition~\ref{prop:gvectorscvectorsDualBases}, any non-maximal cone of~$\gvectorFan$ is supported by an hyperplane orthogonal to a $\b{c}$-vector of~$\allcvectors$.
The $\b{g}$-vector fan~$\gvectorFan$ thus coarsens the $\b{c}$-vector~fan~$\cvectorFan$.
\end{remark}

\begin{example}
To illustrate Theorem~\ref{thm:gvectorFan} and Remark~\ref{rem:cvectorFan}, we have represented in \fref{fig:exmFans} the $\b{c}$-vector fan~$\cvectorFan$ and the $\b{g}$-vector fan~$\gvectorFan$ for two specific gentle bound quivers.
We use the classical projection to represent~$3$-dimensional fans: the fan is intersected with the unit sphere and stereographically projected to the plane from the pole in direction~$(1,1,1)$.
More generally, \fref{fig:allFans3} gathers the $\b{c}$-vector fan~$\cvectorFan$ and the $\b{g}$-vector fan~$\gvectorFan$ for all possible connected simple gentle bound quivers with~$3$ vertices such that the non-kissing complex~$\RNKC$ is finite (\ie where there is a relation in any cycle, oriented or not).
See also \fref{fig:all2} for the $\b{g}$-vector fans of all connected gentle bound quivers on $2$ vertices.

\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[width=1.1\textwidth]{exmFans}}
	\caption{Stereographic projections of the $\b{c}$-vector fans~$\cvectorFan$ (red, left) and the $\b{g}$-vector fans~$\gvectorFan$ (blue, middle) for two specific quivers. The~$3$-dimensional fan is intersected with the unit sphere and stereographically projected to the plane from the pole in direction~$(1,1,1)$. Note that the $\b{g}$-vector fan is supported by the $\b{c}$-vector fan (right).}
	\label{fig:exmFans}
\end{figure}
\end{example}

\begin{example}
For the dissection and grid bound quivers introduced in Section~\ref{subsec:dissectionGridQuivers}, the $\b{g}$-vector fans already appeared in earlier works:
\begin{itemize}
\item For a dissection~$D$, the $\b{g}$-vector fan~$\gvectorFan[\bar Q(D)]$ was constructed in~\cite{MannevillePilaud-accordion}.
\item For a connected subset~$L$ of~$\Z^2$, the $\b{g}$-vector fan~$\gvectorFan[\bar Q(L)]$ was constructed in~\cite{GarverMcConville-grid}. We note however that our proof, quite different from that of~\cite{GarverMcConville-grid}, will be decisive to obtain polytopal realizations in the next section.
\item For oriented paths, $\b{g}$-vector fans are known as type~$A$ Cambrian fans, constructed by N.~Reading and D.~Speyer~\cite{ReadingSpeyer} in connection with type~$A$ cluster algebras~\cite{FominZelevinsky-ClusterAlgebrasI, FominZelevinsky-ClusterAlgebrasII}.
\end{itemize}
Note that the topmost quiver of \fref{fig:exmFans} is both a dissection and a grid bound quiver, so that its $\b{g}$-vector fan was constructed independently in~\cite{MannevillePilaud-accordion} and~\cite{GarverMcConville-grid}.
\end{example}

\begin{remark}
\label{rem:linDep}
\enlargethispage{.1cm}
Theorem~\ref{thm:gvectorFan} extends to any finite-dimensional algebra~$A$. More precisely:
\begin{itemize}
\item As pointed out to us by L.~Demonet, a similar linear dependence holds for a mutation in the support $\tau$-tilting complex of any finite-dimensional algebra~$A$.
Indeed, the~$\b{g}$-vector of a~$\tau$-rigid pair can be identified with the class of the corresponding $2$-term complex in the Grothendieck group of the bounded homotopy category of finitely generated projective modules over~$A$.
The existence of an exchange triangle $X \rightarrow \bigoplus_{i \in [k]} Y_i \rightarrow X' \rightarrow X[1]$ (see~\cite{AiharaIyama}) immediately gives the equality~$[X] + [X'] = \sum_{i \in [k]} [Y_i]$ in the Grothendieck group, yielding the claimed linear dependence among~$\b{g}$-vectors.
\item By Proposition~\ref{prop:characterizationFan}, this suffices to prove Theorem~\ref{thm:gvectorFan} for any finite-dimensional algebra~$A$ with finite support $\tau$-tilting complex. 
\item This simple argument fails when the support $\tau$-tilting complex is infinite. However, the set~$\gvectorFan$ is still a simplicial fan (not necessarily complete). This can be proven using the (much harder) result~\cite{DehyKeller, DemonetIyamaJasso} that $\tau$-rigid objects are determined by their~$\b{g}$-vectors.
\end{itemize}
\end{remark}

\subsection{The non-kissing associahedron}
\label{subsec:associahedron}

%We now restrict our attention to gentle bound quivers~$\bar Q$ with finite non-kissing complexes~$\RNKC$, \ie such that there is a relation of~$I$ in any cycle of~$Q$, oriented or not.
%We then construct a polytopal realization of the $\b{g}$-vector fan~$\gvectorFan$.
We still consider a gentle bound quiver~$\bar Q$ with finite non-kissing complex~$\RNKC$.
We now construct a polytopal realization of the $\b{g}$-vector fan~$\gvectorFan$.

\begin{definition}\label{def: kissing number}
For two walks~$\omega, \omega' \in \NKWalks^\pm(\bar Q)$, denote by~$\kn(\omega,\omega')$ the number of kisses of~$\omega$ to~$\omega'$.
Note that kisses are counted with multiplicities if~$\omega$ or~$\omega'$ pass twice through the same substring.
The \defn{kissing number} of~$\omega$ and~$\omega'$ is~$\KN(\omega,\omega') \eqdef \kn(\omega,\omega') + \kn(\omega',\omega)$.
Since~$\RNKC$ is finite, we can define the \defn{kissing number} of a walk~$\omega$ on~$\bar Q$ as
\[
\KN(\omega) \eqdef \sum_{\omega'} \KN(\omega,\omega'),
\]
where the sum runs over all walks~$\omega'$ of~$\NKWalks^\pm(\bar Q)$.
\end{definition}

\begin{remark}\label{rem:KNvsTau}
Let~$\omega : \strings_{\ge -1}^\pm(\bar Q) \to \bendingWalks^\pm(\bar Q)$ be the bijection of Lemma~\ref{lem:bijections-STTC-NKC}.
Then one easily checks using Proposition~\ref{prop:morphismsStringModules} that when~$\NKC$ is finite, we have for any~$\sigma \in \strings_{\ge -1}^\pm(\bar Q)$
\[
\KN \big( \omega(\sigma) \big) = \sum_{\rho} \dim \Hom{A} \big( M(\sigma), \tau M(\rho) \big) + \dim \Hom{A} \big( M(\rho), \tau M(\sigma) \big),
\]
where the sum runs over all other strings~$\rho$ of~$\strings_{\ge -1}^\pm(\bar Q)$.
\end{remark}

\begin{lemma}
\label{lem:submodular}
For any adjacent non-kissing facets~$F,F' \in \RNKC$, the values of the kissing number~$\KN$ on the walks~$\omega, \omega', \mu, \nu$ defined in Proposition~\ref{prop:flip} (see \fref{fig:flip}) satisfy the inequality
\[
\KN(\omega) + \KN(\omega') > \KN(\mu) + \KN(\nu).
\]
\end{lemma}

\begin{proof}
Observe in \fref{fig:flip}\,(right) that for any walk~$\lambda$, a kiss of~$\lambda$ with one of (resp.~both) the walks~$\mu$ and~$\nu$ is as well a kiss with one of (resp.~both) the walks~$\omega$ and~$\omega'$.
In other words, $\KN(\lambda, \omega) + \KN(\lambda, \omega') \ge \KN(\lambda, \mu) + \KN(\lambda, \nu)$.
Moreover, the walks~$\omega$ and~$\omega'$ kiss each other but do not kiss~$\mu$ and~$\nu$.
We conclude that~$\KN(\omega) + \KN(\omega') \ge \KN(\mu) + \KN(\nu) + 2$.
\end{proof}

\begin{definition}
Let~$\bar Q$ be a gentle bound quiver with finite non-kissing complex~$\RNKC$.
Define
\begin{enumerate}[(i)]
\item for each non-kissing facet~${F \in \RNKC}$, a point
\[
\point{F} \eqdef \sum_{\omega \in F} \KN(\omega) \, \cvector{\omega}{F},
\]
\item for each walk~${\omega \in \NKWalks^\pm(\bar Q)}$, a halfspace
\[
\HS{\omega} \eqdef \set{\b{x} \in \R^{Q_0}}{\dotprod{\gvector{\omega}}{\b{x}} \le \KN(\omega)}.
\]
\end{enumerate}
\end{definition}

\begin{theorem}
\label{thm:associahedron}
For a gentle bound quiver~$\bar Q$ with finite non-kissing complex~$\RNKC$, the $\b{g}$-vector fan~$\gvectorFan$ is the normal fan of the \defn{$\bar Q$-associahedron}~$\Asso$ defined equivalently~as
\begin{enumerate}[(i)]
\item the convex hull of the points~$\point{F}$ for all non-kissing facets~${F \in \RNKC}$, or
\item the intersection of the halfspaces~$\HS{\omega}$ for all walks~${\omega \in \NKWalks^\pm(\bar Q)}$.
\end{enumerate}
\end{theorem}

\begin{proof}
Consider two adjacent non-kissing facets~$F,F'$ and define the walks~$\omega, \omega', \mu, \nu$ as in Proposition~\ref{prop:flip} (see \fref{fig:flip}).
We have seen in the proof of Theorem~\ref{thm:gvectorFan} that the linear dependence between the $\b{g}$-vectors of~$F \cup F'$ is~$\gvector{\omega} + \gvector{\omega'} = \gvector{\mu} + \gvector{\nu}$.
Moreover, according to Lemma~\ref{lem:submodular}, the kissing number satisfies~$\KN(\omega) + \KN(\omega') > \KN(\mu) + \KN(\nu)$.
Applying the characterization of Proposition~\ref{prop:characterizationPolytopalFan}, we thus immediately obtain that the $\b{g}$-vector fan~$\gvectorFan$ is the normal fan of the polytope defined as the intersection of the halfspaces~$\HS{\omega}$ for all walks~$\omega$ on~$\bar Q$.

Finally, to show the vertex description, we just need to observe that, for any non-kissing facet~$F \in \RNKC$, the point~$\point{F}$ is the intersection of the hyperplanes~$\Hyp{\omega}$ for all~$\omega \in F$.
Indeed, since~$\gvectors{F}$ and~$\cvectors{F}$ form dual bases by Proposition~\ref{prop:gvectorscvectorsDualBases}, we have for any~$\omega \in F$:
\[
\dotprod{\gvector{\omega}}{\point{F}} = \sum_{\mu \in F} \KN(\mu) \, \dotprod{\gvector{\omega}}{\cvector{\mu}{F}} = \sum_{\mu \in F} \KN(\mu) \, \delta_{\omega = \mu} \; = \; \KN(\omega).
\qedhere
\]
\end{proof}

\begin{example}
To illustrate Theorem~\ref{thm:associahedron}, we have represented in \fref{fig:exmAssociahedra}\,(middle) the associahedron~$\Asso$ for two specific gentle bound quivers.
More generally, \fref{fig:allAssociahedra3}\,(middle) gathers the associahedron~$\Asso$ for all possible connected simple gentle bound quivers with~$3$ vertices such that the non-kissing complex~$\RNKC$ is finite (\ie where there is a relation in any cycle, oriented or not).
Their normal fans are represented in \fref{fig:allFans3}\,(middle).
See also \fref{fig:all2} for the associahedra of all connected gentle bound quivers on $2$ vertices.

\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[width=1.1\textwidth]{exmAssociahedra}}
	\caption{The zonotope~$\Zono$ (red, left) and the associahedron~$\Asso$ (blue, middle) for two specific quivers. Observe that the facet defining inequalities of~$\Asso$ are not necessarily facet defining inequalities of~$\Zono$ (right).}
	\label{fig:exmAssociahedra}
\end{figure}
\end{example}

\begin{example}
The dissection and grid bound quivers introduced in Section~\ref{subsec:dissectionGridQuivers} give particularly relevant examples:
\begin{itemize}
\item For a dissection~$D$, the $\bar Q(D)$-associahedron of the dissection bound quiver~$\bar Q(D)$ was previously constructed in~\cite{MannevillePilaud-accordion} as a projection of a well-chosen associahedron.
For example, the top line of \fref{fig:exmAssociahedra} already appeared in~\cite{MannevillePilaud-accordion}.
\item In contrast, the non-kissing associahedron was not known for a grid bound quiver. Our construction thus answers a question of A.~Garver and T.~McConville~\cite{GarverMcConville-grid} concerning the polytopality of the $\b{g}$-vector fan~$\gvectorFan[\bar Q(L)]$ for a subset~$L$ of~$\Z^2$. Note that alternative polytopal realizations for the grid-associahedra were constructed in~\cite{SantosStumpWelker} using the dual of a nice triangulation of an order polytope and in~\cite[Sect.~4]{McConville} by a sequence of suspensions and edge subdivisions.
\item For oriented paths, the non-kissing associahedra are classical associahedra, constructed by J.-L.~Loday~\cite{Loday} and C.~Hohlweg and C.~Lange~\cite{HohlwegLange} and revisited in~\cite{HohlwegLangeThomas, Stella, PilaudSantos-brickPolytope, LangePilaud, HohlwegPilaudStella} (among others).
\end{itemize}
\end{example}

\begin{remark}
\label{rem:polytope}
As in Remark~\ref{rem:linDep}, Theorem~\ref{thm:associahedron} in fact holds over any~$\tau$-tilting finite algebra~$A$.
The kissing number has to be replaced by the dimension of some Hom-space, as in Remark~\ref{rem:KNvsTau}.
More precisely, consider the functions
\[
\KN_\ell(X) = \sum_Y \dim \Hom{} \big( X, Y[1] \big)
\qquad\text{and}\qquad
\KN_r(X) = \sum_Y \dim \Hom{} \big( Y, X[1] \big),
\]
where the sums run over all indecomposable $2$-term presilting complexes.
An exchange triangle $X \rightarrow \bigoplus_{i \in [k]} Y_i \rightarrow X' \rightarrow X[1]$ (see~\cite{AiharaIyama}) then gives rise to
\begin{itemize}
\item a linear dependence~$[X] + [X'] = \sum_{i \in [k]} [Y_i]$ in the Grothendieck group (see Remark~\ref{rem:linDep}),
\item an inequality of the form~$\KN(X) + \KN(X') > \sum_{i \in [k]} \KN(Y_i)$ for~$\KN \in \{\KN_\ell, \KN_r\}$.
\end{itemize}
The proof is then similar to that of Theorem~\ref{thm:associahedron} and leads to the same results using either~$\KN_\ell$, $\KN_r$, or more symmetrically their sum~$\KN_\ell + \KN_r$.
Compare to Remark~\ref{rem:KNvsTau}.
\end{remark}

\subsection{Non-kissing associahedron and lattice}
\label{subsec:geomLattice}

The following observation is an immediate consequence of the fact that the normal fan of the $\bar Q$-associahedron~$\Asso$ is the $\b{g}$-vector fan~$\gvectorFan$.

\begin{lemma}
Consider two adjacent non-kissing facets~$F,F'$ and let~$\omega, \omega', \mu$ and~$\nu$ denote the walks involved in the flip as defined in Proposition~\ref{prop:flip} (see \fref{fig:flip}).
Then the difference~${\point{F'} - \point{F}}$ is a strictly negative multiple of~$\cvector{\omega}{F} = -\cvector{\omega'}{F'}$.
More precisely,
\[
\point{F'} - \point{F} = \big( \KN(\mu) + \KN(\nu) - \KN(\omega) - \KN(\omega') \big) \, \cvector{\omega}{F}.
\]
\end{lemma}

\begin{proof}
One can translate Remark~\ref{rem:changeDistinguishedArrows} in terms of $\b{c}$-vectors as follows:
\begin{itemize}
\item For~$\omega$ and~$\omega'$, we have $\cvector{\omega}{F} = -\cvector{\omega'}{F'}$.
\item For~$\mu$ and~$\nu$, two different situations can happen:
\begin{itemize}
\item If~$\mu = \nu$, then it is a bending walk and~$\cvector{\mu}{F'} = \cvector{\mu}{F} + 2\,\cvector{\omega}{F}$.
\item Otherwise, whenever $\mu$ and~$\nu$ are bending walks, we have
\[
\cvector{\mu}{F'} = \cvector{\mu}{F} + \cvector{\omega}{F}
\quad\text{and}\quad
\cvector{\nu}{F'} = \cvector{\nu}{F} + \cvector{\omega}{F}.
\]
\end{itemize}
\item Finally, $\cvector{\lambda}{F} = \cvector{\lambda}{F'}$ for all walks~$\lambda \in (F \cap F') \ssm \{\mu,\nu\}$
\end{itemize}
The formula thus immediately follows from the definition of~$\point{F}$.
Finally, Lemma~\ref{lem:submodular} asserts that~${\KN(\omega) + \KN(\omega') > \KN(\mu) + \KN(\nu)}$, which shows that~${\point{F'} - \point{F}}$ is a strictly negative multiple of~$\cvector{\omega}{F} = -\cvector{\omega'}{F'}$.
\end{proof}

\begin{proposition}
When oriented in the linear direction~$-\one \eqdef (-1, \dots, -1) \in \R^{Q_0}$, the graph of the $\bar Q$-associahedron~$\Asso$ is (isomorphic to) the increasing flip graph~$\NKG$.
\end{proposition}

\begin{proof}
For any two adjacent non-kissing facets~$F,F'$ with~$F \ssm \{\omega\} = F' \ssm \{\omega'\}$, the scalar product
\[
\dotprod{-\one}{\point{F'} - \point{F}} = \big( \KN(\mu) + \KN(\nu) - \KN(\omega) - \KN(\omega') \big) \dotprod{-\one}{\cvector{\omega}{F}}
\]
has the same sign as~$\cvector{\omega}{F}$.
However, the flip~$F \to F'$ is increasing if and only if the \mbox{$\b{c}$-vector}~$\cvector{\omega}{F}$ is positive.
This concludes the proof.
\end{proof}

\subsection{Zonotope}
\label{subsec:zonotope}

We have seen in Remark~\ref{rem:cvectorFan} that the $\b{c}$-vector fan~$\cvectorFan$ coarsens the $\b{g}$-vector fan~$\gvectorFan$.
The goal of this short section is to discuss the possibility to visualize this property at the level of polytopes.
The prototypes are the associahedra of C.~Hohlweg and C.~Lange which can be obtained by deleting inequalities in the facet description of the permtahedron~\cite{HohlwegLange}.
We are interested in a similar behavior for arbitrary gentle bound quivers.

We still consider only gentle bound quivers~$\bar Q$ with finite non-kissing complexes~$\RNKC$.
In particular, there are only finitely many strings, so that the following Minkowski sum is \mbox{well-defined}.

\begin{definition}
The \defn{$\bar Q$-zonotope} is the Minkowski sum
\[
\Zono \eqdef \sum_{\sigma \in \distinguishableStrings^\pm(\bar Q)} [-\multiplicityVector_\sigma, \multiplicityVector_\sigma] \; = \sum_{\b{c} \in \allcvectors} \big|\set{\sigma \in \distinguishableStrings^\pm(\bar Q)}{\b{c} = \pm \multiplicityVector_\sigma} \big| \, \b{c}
\]
where~$\distinguishableStrings^\pm(\bar Q)$ still denotes the set of distinguishable strings~of~$\bar Q$ (see Definition~\ref{def:distinguishedSubstring}), $\multiplicityVector_\sigma$ is the multiplicity vector of the multiset of vertices of~$\sigma$, and~$\allcvectors$ is the set of all $\b{c}$-vectors.
\end{definition}

\begin{example}
\fref{fig:exmAssociahedra}\,(left) illustrates the zonotope~$\Zono$ for two specific gentle bound quivers.
More generally, \fref{fig:allAssociahedra3}\,(top) gathers the zonotopes~$\Zono$ for all possible connected simple gentle bound quivers with~$3$ vertices such that the non-kissing complex~$\RNKC$ is finite.
Their normal fans are represented in \fref{fig:allFans3}\,(top).
See also \fref{fig:all2} for the zonotopes of all connected gentle bound quivers on $2$ vertices.
\end{example}

\begin{remark}
Since~$\allcvectors = \set{\pm \multiplicityVector_\sigma}{\sigma \in \distinguishableStrings^\pm(\bar Q)}$, the normal fan of the zonotope~$\Zono$ is by construction the $\b{c}$-vector fan~$\cvectorFan$.
In particular, the graph of~$\Zono$, oriented in the direction~$-\one$ is the poset of regions of the $\b{c}$-vector fan~$\cvectorFan$ from the positive orthant as defined by A.~Bj\"orner, P.~Edelman and G.~Ziegler in~\cite{BjornerEdelmanZiegler}.
In particular, when~$\cvectorFan$ is simplicial, the oriented graph of~$\Zono$ is the Hasse diagram of a lattice.
However, the $\b{c}$-vector fan is not simplicial in general, as illustrated by Figures~\ref{fig:exmAssociahedra} and~\ref{fig:allAssociahedra3}.
In fact, the oriented graph of~$\Zono$ is not always the Hasse diagram of a lattice, as observed in~\cite[Rem.~6.2]{McConville} (the first counter-example is given by a square quiver).
The lattice of biclosed sets~$\Bicl{\bar Q}$ was designed in~\cite{McConville} to play the role of this missing lattice structure on~$\Zono$.
\end{remark}

\begin{example}
\label{exm:permutahedron}
When~$\bar Q$ is a type~$A$ quiver, the $\bar Q$-zonotope~$\Zono$ is the Minkowski sum of all characteristic vectors of intervals (\ie all type~$A_n$ roots), thus yielding the classical permutahedron.
In this situation, the $\bar Q$-associahedron~$\Asso$ is thus obtained by deleting inequalities in the facet description of the $\bar Q$-zonotope~$\Zono$.
See~\cite{Loday, HohlwegLange, LangePilaud} for details.
\end{example}

\begin{example}
For a dissection quiver~$\bar Q = \bar Q(D)$, T.~Manneville and V.~Pilaud proved in~\cite{MannevillePilaud-accordion} that the $\bar Q$-associahedron~$\Asso$ is obtained by deleting inequalities in the facet description of the $\bar Q$-zonotope~$\Zono$.
\end{example}

Figures~\ref{fig:exmAssociahedra}, \ref{fig:all2} and~\ref{fig:allAssociahedra3} already illustrate that this property might fail for arbitrary gentle bound quivers.
It would be interesting to characterize those quivers for which it holds.

\begin{question}
For which gentle bound quivers~$\bar Q$ are all inequalities of the $\bar Q$-associahedron~$\Asso$ also inequalities of the $\bar Q$-zonotope~$\Zono$?
\end{question}

Although we cannot provide a general answer to this question, we want to exhibit a sufficient (but certainly not necessary) condition for this property.
We need the following definition.

\begin{definition}
We say that two walks~$\omega, \omega'$ of~$\bar Q$ are \defn{mutually kissing} if~$\omega$ kisses~$\omega'$ and~$\omega'$ kisses~$\omega$, that is, $\kn(\omega,\omega') \, \kn(\omega',\omega) > 0$.
\end{definition}

\begin{proposition}
\label{prop:zonotope}
If~$\bar Q$ is a gentle bound quiver with a finite non-kissing complex and no two mutually kissing walks, then all facet inequalities of the $\bar Q$-associahedron~$\Asso$ are also facet inequalities of the $\bar Q$-zonotope~$\Zono$.
In other words, the $\bar Q$-associahedron~$\Asso$ is obtained by deleting inequalities in the facet description of the $\bar Q$-zonotope~$\Zono$.
\end{proposition}

\begin{proof}
Consider a bending walk~$\omega \in \bendingWalks^\pm(\bar Q)$ and the corresponding facet inequality of~$\Asso$ given by~${\dotprod{\gvector{\omega}}{\b{x}} \le \KN(\omega)}$.
We want to show that~$\dotprod{\gvector{\omega}}{\b{x}} \le \KN(\omega)$ is also a facet inequality of~$\Zono$.
For this, we associate to each bending walk~$\omega'$ a negative $\b{c}$-vector~$\b{c}^-(\omega')$ and a positive $\b{c}$-vector~$\b{c}^+(\omega')$ defined by
\[
\b{c}^-(\omega') \eqdef
\begin{cases}
-\multiplicityVector_{\sigma_\bottom(\omega')} & \text{if } \omega' \notin F_\peak \\
\b{0} & \text{otherwise}
\end{cases}
\qquad\text{and}\qquad
\b{c}^+(\omega') \eqdef 
\begin{cases}
\multiplicityVector_{\sigma_\top(\omega')} & \text{if } \omega' \notin F_\deep \\
\b{0} & \text{otherwise}
\end{cases}
\]
where~$\sigma_\bottom(\omega')$ and~$\sigma_\top(\omega')$ are the distinguishable strings defined in Definition~\ref{def:bijectionWalksDistinguishableStrings} and Remark~\ref{rem:bijectionDistinguishableStringsWalks}.
By Proposition~\ref{prop:bijectionDistinguishableStringsWalks}, the $\bar Q$-zonotope~$\Zono$ can be rewritten as the Minkowski sum of these $\b{c}$-vectors:
\[
\Zono \eqdef \sum_{\sigma \in \distinguishableStrings^\pm(\bar Q)} [-\multiplicityVector_\sigma, \multiplicityVector_\sigma] = \sum_{\omega' \in \bendingWalks^\pm(\bar Q)} \big( [\b{0}, \b{c}^-(\omega')] + [\b{0}, \b{c}^+(\omega')] \big).
\]
Therefore, the facet inequality of~$\Zono$ corresponding to the normal vector~$\gvector{\omega}$ is given~by
\[
\dotprod{\gvector{\omega}}{\b{x}} \le \sum_{\omega' \in \bendingWalks^\pm(\bar Q)} \max(\dotprod{\gvector{\omega}}{\b{c}^-(\omega')},0) + \max(\dotprod{\gvector{\omega}}{\b{c}^+(\omega')},0) \\
\]

Consider now a bending walk~$\omega' \in \bendingWalks^\pm(\bar Q)$.
We want to understand when~$\dotprod{\gvector{\omega}}{\b{c}^+(\omega')} > 0$ (the case~$\dotprod{\gvector{\omega}}{\b{c}^-(\omega')} > 0$ is similar).
If~$\dotprod{\gvector{\omega}}{\b{c}^+(\omega')} > 0$, then the walks~$\omega$ and~$\omega'$ share common vertices.
Let~$\tau$ be a maximal common substring of~$\omega$ and~$\omega'$.
If~$\omega$ enters and leaves~$\tau$ in the same direction, then it has as many peaks as deeps along~$\tau$, so that~$\dotprod{\gvector{\omega}}{\multiplicityVector_{\tau}} = 0$.
In contrast, if~$\omega$ enters and leaves~$\tau$ with two outgoing (resp.~incoming) arrows, then~$\omega$ has one more peak than deep (resp.~one more deep than peak) along~$\tau$, so that~$\dotprod{\gvector{\omega}}{\multiplicityVector_{\tau}} = 1$ (resp.~$-1$).
Observe now that if~$\tau$ is not included in~$\sigma \eqdef \sigma_\top(\omega')$, then~$\omega$ must enter and leave the substring~$\tau \ssm \sigma$ with incoming arrows so that~$\dotprod{\gvector{\omega}}{\multiplicityVector_{\tau \ssm \sigma}} = 0$.
We conclude that~$\tau$ contributes~$0$ (resp.~$1$, resp.~$-1$) to~$\dotprod{\gvector{\omega}}{\b{c}^+(\omega)}$ when~$\omega$ and~$\omega'$ are crossing (resp.~when~$\omega$ kisses~$\omega'$, resp.~when~$\omega'$ kisses~$\omega$) at~$\tau$.
Since~$\omega$ and~$\omega'$ are not mutually kissing, all maximal common substrings of~$\omega$ and~$\omega'$ contribute with the same sign.
Therefore, we have~$\max(\dotprod{\gvector{\omega}}{\b{c}^+(\omega)}, 0) = \kn(w,w')$.
We obtain similarly that~$\max(\dotprod{\gvector{\omega}}{\b{c}^-(\omega)}, 0) = \kn(w',w)$, so that 
\[
\max(\dotprod{\gvector{\omega}}{\b{c}^-(\omega')},0) + \max(\dotprod{\gvector{\omega}}{\b{c}^+(\omega')},0) = \kn(w,w') + \kn(w',w) = \KN(\omega,\omega')
\]
and therefore the maximum of~$\dotprod{\gvector{\omega}}{\b{x}}$ over~$\Zono$ is given by
\[
\sum_{\substack{\omega' \in \bendingWalks^\pm(\bar Q)}} \KN(\omega,\omega') = \KN(\omega).
\qedhere
\]
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Coordinate sections and projections}
\label{subsec:projections}

We conclude the paper with a natural operation on quivers that illustrates a recent result of~\cite{PilaudPlamondonStella}.
%Motivated by an observation of~\cite[Sect.~4]{MannevillePilaud-accordion}, we define a natural operation on quivers which will correspond to coordinate hyperplane sections of the $\b{g}$-vector fan and coordinate projections of the non-kissing associahedron.
Intuitively, we blind a strict subset of the vertices of a gentle bound quiver, meaning that we forbid peaks and deeps at these blinded vertices.
More formally, this corresponds to the following operation.

\begin{definition}
Consider a gentle bound quiver~$\bar Q = (Q,I)$ and a vertex~$v \in Q_0$.
Denote by~$K_v \eqdef \set{\alpha\beta}{\alpha, \beta \in Q_1 \text{ with } t(\alpha) = s(\beta)}$ the set of paths of length~$2$ with middle vertex~$v$ and let~$I_v \eqdef K_v \cap I$ and~$J_v \eqdef K_v \ssm I$.
We denote by~$\bar Q\blinkers{v} = (Q\blinkers{v}, I\blinkers{v})$ the bound quiver where
\begin{gather*}
(Q\blinkers{v})_0 = Q_0 \ssm \{v\},
\qquad\qquad
(Q\blinkers{v})_1 = \set{\alpha \in Q_1}{s(\alpha) \ne v \ne t(\alpha) } \cup J_v,
\\
I\blinkers{v} = \set{\sigma \in I \ssm I_v}{s(\sigma) \ne v \ne t(\sigma)} \cup \set{\alpha\beta\gamma}{\alpha\beta \in I \text{ and } \beta\gamma \in J_v \; \text{ or } \; \alpha\beta \in J_v \text{ and } \beta\gamma \in I}.
\end{gather*}
We say that~$\bar Q\blinkers{v}$ is obtained by \defn{blinding}~$v$ in~$\bar Q$.
Finally, for a subset~$V = \{v_1, \dots, v_\ell\}$ of~$Q_0$, we let~$\bar Q\blinkers{V} \eqdef ((\bar Q\blinkers{v_1})\blinkers{v_2} \dots )\blinkers{v_\ell}$.
\end{definition}

\begin{remark}
The reader is invited to check that
\begin{itemize}
\item the blinded quiver~$Q\blinkers{v}$ is still a gentle bound quiver.
\item blinding commutes with blossoming: $(Q\blinkers{v})\blossom = (Q\blossom)\blinkers{v}$.
\item blinding commutes with reversing: $\reversed{(Q\blinkers{v})} = (\reversed{Q})\blinkers{v}$.
\item $\bar Q\blinkers{V}$ is independent of the ordering of~$V$.
\end{itemize}
\end{remark}

\begin{proposition}
\label{prop:projection}
Consider a gentle bound quiver~$\bar Q$, a subset~$V \subsetneq Q_0$, and the quiver~$\bar Q\blinkers{V}$.~Then
\begin{enumerate}[(i)]
\item The path algebra~$A\blinkers{V}$ of the blinded quiver~$\bar Q\blinkers{V}$ is the subalgebra of the path algebra~$A$ of~$\bar Q$ given by~$A\blinkers{V} = (1-\varepsilon_V) \cdot A \cdot (1-\varepsilon_V)$, where~$\varepsilon_V \eqdef \sum_{v \in V} \varepsilon_v$.
\item The non-kissing complex~$\NKC[\bar Q\blinkers{V}]$ is isomorphic to the subcomplex of the non-kissing complex~$\NKC[\bar Q]$ induced by walks with no corner at a vertex of~$V$.
\item The $\b{g}$-vector fan~$\gvectorFan[\bar Q\blinkers{V}]$ is the section~$\set{C \in \gvectorFan}{C \subseteq V^\perp}$ of the $\b{g}$-vector fan~$\gvectorFan$ by the coordinate plane~$V^\perp \eqdef \set{\b{x} \in \R^{Q_0}}{\dotprod{\b{e}_v}{\b{x}} = 0 \text{ for all } v \in V}$.
\item When~$\NKC$ is finite, the normal fan of the projection of the non-kissing associahedron~$\Asso$ to the coordinate plane~$V^\perp$ is the $\b{g}$-vector fan~$\gvectorFan[\bar Q\blinkers{V}]$.
\end{enumerate}
\end{proposition}

\begin{proof}%[Proof (sketch)]
For~(i), observe that the paths in~$\bar Q\blinkers{V}$ correspond to the paths in~$\bar Q$ that do not start or end at a vertex of~$V$ (the correspondence consists in grouping blocks of consecutive letters~$\alpha\beta$ for which~$t(\alpha) = s(\beta) \in V$).

For~(ii), we just need to observe that a walk~$\omega$ of~$\bar Q$ with no corner at a vertex of~$V$ corresponds to a walk~$\omega\blinkers{V}$ of~$\bar Q\blinkers{V}$ (the correspondence consists again in grouping blocks of consecutive letters~$\alpha\beta$ for which~$t(\alpha) = s(\beta) \in V$).
This correspondence clearly sends non-kissing walks to non-kissing walks, and thus induces an isomorphism between the subcomplex of the non-kissing complex~$\NKC[\bar Q]$ induced by walks with no corner at a vertex of~$V$ and the non-kissing complex~$\NKC[\bar Q\blinkers{V}]$.

Moreover, this correspondence sends peaks (resp.~deeps) of~$\omega$ to peaks (resp.~deeps) of~$\omega\blinkers{V}$.
Since the $v$-th coordinate of the $\b{g}$-vector of a walk~$\omega$ is the number of peaks minus the number of deeps of~$\omega$ at~$v$, we obtain that
\[
\gvector{\omega} \in V^\perp
\qquad\text{and}\qquad
\pi_V \big( \gvector{\omega} \big) = \gvector{\omega\blinkers{V}}
\]
for a walk of~$\bar Q$ with no corner at a vertex of~$V$, where~$\pi_V$ denotes the coordinate projection on the hyperplane~$V^\perp$.
%This ensures that the $\b{g}$-vector fan~$\gvectorFan[\bar Q\blinkers{V}]$ is the section of~$\gvectorFan$ by~$V^\perp$.
This shows~(iii).

Finally, (iv) immediately follows from~(iii) since the normal fan of a projection of a polytope~$P$ on a subspace~$V$ is the section of the normal fan of~$P$ by the subspace~$V$ \cite[Lemma~7.11]{Ziegler-polytopes}.
\end{proof}

\begin{example}
To illustrate Proposition~\ref{prop:projection}, we have represented in \fref{fig:exmKillVertices} all possible coordinate projections of the non-kissing associahedra~$\Asso$ for two specific gentle bound quivers.

\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[width=1.2\textwidth]{exmKillVertices}}
	\caption{All possible coordinate projections of the non-kissing associahedra~$\Asso$ for two specific gentle bound quivers.}
	\label{fig:exmKillVertices}
\end{figure}
\end{example}

\begin{example}
Consider a triangulation~$T$ of a convex polygon and a dissection~$D$ whose edges are included in~$T$.
Then the dissection bound quiver~$\bar Q(D)$ coincides with the blinded bound quiver~$\bar Q(T)\blinkers{V}$ where~$V$ are the vertices of~$\bar Q(T)$ corresponding to the diagonals of~$T$ not in~$D$.
In particular, the $\b{g}$-vector fan of any dissection bound quiver~$\bar Q(D)$ is a section of the $\b{g}$-vector fan of a type~$A$ quiver, and is realized by a projection of the associahedron of~\cite{HohlwegPilaudStella}.
See~\cite{PilaudPlamondonStella}.
\end{example}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\captionsetup{width=1.5\textwidth}
\hvFloat[floatPos=p, capWidth=h, capPos=r, capAngle=90, objectAngle=90, capVPos=c, objectPos=c]{figure}
{\begin{minipage}{23.2cm}\vspace*{-1cm}\includegraphics[scale=.25]{all2}\end{minipage}}
{
For all connected gentle bound quivers~$\bar Q$ on $2$ vertices: the support $\tau$-tilting complex~$\tTC$, its dual graph~$\tTC^*$, the reduced non-kissing complex~$\RNKC$, the non-kissing oriented flip graph~$\NKG$, the $\b{c}$-vector fan~$\cvectorFan$ and the $\b{g}$-vector fan~$\gvectorFan$, and the $\bar Q$-zonotope~$\Zono$ and the $\bar Q$-associahedron~$\Asso$ (when~$\NKC$ is finite).
}
{fig:all2}
\captionsetup{width=\textwidth}

\captionsetup{width=1.5\textwidth}
\hvFloat[floatPos=p, capWidth=h, capPos=r, capAngle=90, objectAngle=90, capVPos=c, objectPos=c]{figure}
{\includegraphics[scale=.27]{allFans3}}
{Stereographic projections of the $\b{c}$-vector fan~$\cvectorFan$ (red, top) and the $\b{g}$-vector fan~$\gvectorFan$ (blue, middle) for all connected simple gentle bound quivers~$\bar Q$ on~$3$ vertices with finite non-kissing complex~$\RNKC$. Note that the $\b{g}$-vector fan is supported by the $\b{c}$-vector fan (bottom). The~$3$-dimensional fans are intersected with the unit sphere and stereographically projected to the plane from the pole in direction~$(1,1,1)$. The first three fans are $\b{g}$-vector fans of type~$A$ cluster algebras, the fourth is a fan realization of an accordion complex from~\cite{MannevillePilaud-accordion} or of a non-kissing grid complex from~\cite{GarverMcConville-grid}, the last three are new.}
{fig:allFans3}
\captionsetup{width=\textwidth}

\captionsetup{width=1.5\textwidth}
\hvFloat[floatPos=p, capWidth=h, capPos=r, capAngle=90, objectAngle=90, capVPos=c, objectPos=c]{figure}
{\includegraphics[scale=.27]{allAssociahedra3}}
{The $\bar Q$-zonotope~$\Zono$ (red, top) and the $\bar Q$-associahedron~$\Asso$ (blue, middle) for all connected simple gentle bound quivers~$\bar Q$ on~$3$ vertices with finite non-kissing complex~$\RNKC$. Observe that the facet defining inequalities of~$\Asso$ are not necessarily facet defining inequalities of~$\Zono$ (bottom). Note that the labels on the quivers have been chosen so that all these polytopes are nicely oriented in the same basis, although the different polytopes are rescaled with independent scaling factors to fit a similar space in the figure. The first is J.-L.~Loday's associahedron~\cite{Loday}, the second is an associahedron of C.~Hohlweg and C.~Lange~\cite{HohlwegLange}, the third is an associahedron recently constructed in~\cite{HohlwegPilaudStella}, the fourth is an accordiohedron of~\cite{MannevillePilaud-accordion}, the last three are new.}
{fig:allAssociahedra3}
\captionsetup{width=\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\addtocontents{toc}{\vspace{.3cm}}
\section*{Acknowledgements}

We benefited form various discussions and several useful comments on a preliminary version of this paper.
We are particularly grateful to F.~Chapoton for initially pointing us in the direction of this paper, to A.~Garver and T.~McConville for important inputs on Part~\ref{part:lattice} (including pointing out to us the need of Theorem~\ref{thm:characterizationCongruenceUniform2}), to T.~Manneville and S.~Stella for their help on Part~\ref{part:geometry}, to L.~Demonet for the observation of Remarks~\ref{rem:linDep} and~\ref{rem:polytope}, and to S.~Schroll for her valuable comments on Part~\ref{part:algebra}.
We also thank T.~Br\"ustle, O.~Iyama, N.~Reading, H.~Thomas for discussions on their ongoing projects mentioned in the introduction.
This work was carried out while the first author was visiting Paris 7. He would like to thank his colleagues there, and especially \mbox{P.~Le Meur}, for a stimulating atmosphere.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliographystyle{alpha}
\bibliography{nonKissingComplex}
\label{sec:biblio}

\end{document}

%\para{Blossoming strings in a string bound quiver}

%A \defn{blossoming string}~$\sigma\blossom$ in a quiver~$\bar Q$ is a string~$\sigma = \alpha_1^{\varepsilon_1} \cdots \alpha_\ell^{\varepsilon_\ell}$ in~$\bar Q$ together with a pair of signs~$\varepsilon_0$ and~$\varepsilon_{\ell+1}$ such that
%\begin{itemize}
%\item if~$\ell > 0$, then~${\alpha_0^{\varepsilon_0} \sigma \notin \strings(\bar Q)}$ for all~$\alpha_0 \in Q_1$ and~${\sigma \alpha_{\ell+1}^{\varepsilon_{\ell+1}} \in \strings(\bar Q)}$ for all~$\alpha_{\ell+1} \in Q_1$,
%\item if~$\sigma = \varepsilon_v$, then~$\alpha_0\alpha_1 \notin I$ for all~$\alpha_0, \alpha_1 \in Q_1$ such that~$s(\alpha_0) = t(\alpha_1) = v$.
%\end{itemize}
%In other words, one can think of a blossoming string as a string with an additional blossom at each endpoint, such that no arrow of~$\bar Q$ in the same direction as the blossoms could have been composed with~$\sigma$.
%
%%A \defn{blossoming} string (resp.~gentle) quiver is a string (resp.~gentle) quiver~$(Q\blossom,I)$ with a distinguished subset~$B$ of~$Q_0$, called \defn{blossoms}, such that each vertex of~$Q_0 \ssm B$ has precisely two incoming and two outgoing arrows, while each vertex of~$B$ has exactly one incident arrow either incoming or outgoing.

%\para{The non-kissing complex of a string bound quiver}

%Consider two blossoming strings~$\sigma\blossom = (\varepsilon_0, \alpha_1^{\varepsilon_1} \cdots \alpha_\ell^{\varepsilon_\ell}, \varepsilon_{l+1})$ and~$\bar\sigma\blossom = (\bar\varepsilon_0, \bar\alpha_1^{\bar\varepsilon_1} \cdots \bar\alpha_{\bar\ell}^{\bar\varepsilon_{\bar\ell}}, \bar\varepsilon_{l+1})$. We say that~$\sigma\blossom$ kisses~$\bar\sigma\blossom$ if there exists~$i < j$ and~$\bar i < \bar j$ such that...

### 2018-07-03 draft/accordionComplexSurfaces.tex
first surfaces
Properties of the complexes and countercurrent order.

@@
 
+\section{Properties of the non-crossing and non-kissing complexes}
+
+\subsection{The countercurrent order}
+The countercurrent order was introduced in \cite{PaluPilaudPlamondon} for gentle algebras.  We now adapt it to locally gentle algebras.
+
+\begin{definition}
+A \defn{marked walk}~$\omega_\star$ is a walk~$\omega$ together with a marked occurence of an arrow~$\alpha^{\pm}$ in~$\omega$.
+In the case where~$\omega$ is an infinite straight walk (so~$\omega$ is a cycle which repeats infinitely on both sides), we consider that all marked occurences of an arrow~$\alpha^\pm$ are equal.
+Otherwise, if~$\omega$ contains several occurrences of~$\alpha^\pm$, only one occurrence is marked.
+\end{definition}
+
+\begin{definition}
+Consider an arrow~$\alpha \in Q\blossom_1$ and any two distinct non-kissing walks~$\mu_\star, \nu_\star$ marked at an occurrence of~$\alpha^\pm$.
+Let~$\sigma$ denote their maximal common substring containing that occurrence of~$\alpha$.
+Since~$\mu_\star \ne \nu_\star$, their common substring~$\sigma$ is strict, so that~$\mu_\star$ and~$\nu_\star$ split at least at one endpoint of~$\sigma$.
+We define the \defn{countercurrent order at~$\alpha$} by~$\mu_\star \prec_\alpha \nu_\star$ when~$\mu_\star$ enters and/or exits~$\sigma$ in the direction pointed by~$\alpha$, while~$\nu_\star$ enters and/or exits~$\sigma$ in the direction opposite to~$\alpha$.
+\end{definition}
+\pierreguy{I need to modify these two definitions.}
+
+\subsection{Purity of the non-crossing and non-kissing complexes}
+
+A simplicial complex is \defn{pure of dimension~$d$} if all its maximal faces have dimension~$d$.
+
+\begin{proposition}
+\label{prop:purity}
+ The the non-kissing complex~$\NKC$ and the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$ are pure of dimension~$|Q_0| + \Delta$, where~$\Delta$ is the number of blossoming vertices of~$Q\blossom$ divided by two.
+\end{proposition}
+
+Note that Proposition \ref{prop:purity} was proved for~$\NKC$ in \cite[Corollary 2.27]{PaluPilaudPlamondon} in the case where~$kQ/I$ is finite-dimensional.
+Note also that, by Theorem \ref{thm:complexesCoincide} above,~$\NKC$ and~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$ coincide, so it suffices to prove the Proposition for one of them.
+
+\begin{lemma}
+\label{lemm:facetsAreFinite}
+Any face of~$\NKC$ and~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$ is contained in a finite maximal face.
+\end{lemma}
+\begin{proof}
+ We provide two proofs of the lemma.  One is combinatorial and applies to~$\NKC$, and the other is geometric and applies to~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$.
+
+ {\it Combinatorial proof.}
+ \pierreguy{Yann has the combinatorial proof.}
+
+ {\it Geometric proof.} Let~$F$ be a face of the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$.
+ Its elements are pairwise compatible~$\dissection$-accordions on the surface~$\surface(\bar Q)$.
+ Thus~$F$ can be viewed as a partial tagged triangulation of~$\surface(\bar Q)$, by letting the~$\dissection$-accordions circling a puncture in (say) clockwise order be seen as ``notched'' arcs to said puncture, and the ones circling it in counter-clockwise orientation be ``un-notched'' arcs.
+ It is known (see, for instance, \cite{FominShapiroThurston}) that any such partial tagged triangulation can be embedded into a full triangulation, and that triangulations contain a finite number of arcs.
+ Thus~$F$ is finite, and is contained in a finite maximal face.
+\end{proof}
+
+\subsection{Thinness of the non-crossing and non-kissing complexes, mutation}
+
 \section{Representation-theoretic interpretation}

### 2018-07-03 draft/accordionComplexSurfaces.tex
work on definition construction surface

--- 2018-07-03 draft/accordionComplexSurfaces.tex
@@
 \centerline{
-\begin{tikzpicture}[scale=2, thick]
-	\node (s) at (-1,0) {$s(\alpha)$};
-	\node (t) at (1,0) {$t(\alpha)$};
-	\node (v) at (0,1) {$\green v(\alpha)$};
-	\node (vd) at (0,-1) {$\red v\dual(\alpha)$};
-	\draw[color=black, ->] (s) -> (t) node[midway, above] {$\alpha$};
+\begin{tikzpicture}[
+	scale=2,
+	thick,
+	decoration={markings, mark=at position 0.5 with {\arrow{>}}},
+	roundNode/.style={circle, fill=black, inner sep=2pt, outer sep=2pt}
+	]
+	\node[roundNode, label=left:{$s(\alpha)$}] (s) at (-1,0) {};
+	\node[roundNode, label=right:{$t(\alpha)$}] (t) at (1,0) {};
+	\node[roundNode, fill=green, label=above:{$\green v(\alpha)$}] (v) at (0,1) {};
+	\node[roundNode, fill=red, label=below:{$\red v\dual(\alpha)$}] (vd) at (0,-1) {};
+	\draw[color=black, postaction={decorate}] (s) -> (t) node[midway, above] {$\alpha$};
 	\pic [draw, angle radius=.7cm] {angle = s--t--vd};
 	\pic [draw, angle radius=.7cm] {angle = vd--s--t};
-	\draw[color=green, ->] (v) -> (s) node[midway, above left] {$\green \Enrs{\alpha}$};
-	\draw[color=green, ->] (v) -> (t) node[midway, above right] {$\green \Enrt{\alpha}$};
-	\draw[color=red, ->] (vd) -> (s) node[midway, below left] {$\red \Ers{\alpha}$};
-	\draw[color=red, ->] (vd) -> (t) node[midway, below right] {$\red \Ert{\alpha}$};
+	\draw[color=green, postaction={decorate}] (v) -> (s) node[midway, above left] {$\green \Enrs{\alpha}$};
+	\draw[color=green, postaction={decorate}] (v) -> (t) node[midway, above right] {$\green \Enrt{\alpha}$};
+	\draw[color=red, postaction={decorate}] (vd) -> (s) node[midway, below left] {$\red \Ers{\alpha}$};
+	\draw[color=red, postaction={decorate}] (vd) -> (t) node[midway, below right] {$\red \Ert{\alpha}$};
 \end{tikzpicture}
@@
 \end{enumerate}
+The orientations on the edges are only use to perform the identifications and can be immediately forgotten.
 \end{definition}
 
-\begin{example}
-\vincent{TODO.}
-\end{example}
-
+This construction is illustrated on \fref{fig:examplesSurfaces}.
+%
+\begin{figure}[t]
+	\capstart
+	\centerline{\includegraphics[scale=.7]{examplesSurfaces}}
+	\caption{The surface~$\surface_{\bar Q}$ for two quivers~$\bar Q$ of \fref{fig:quivers}.}
+	\label{fig:examplesSurfaces}
+\end{figure}
+%
 Definition~\ref{def:surfaceQuiver} constructs an orientable surface~$\surface(\bar Q)$ with boundaries.
-This surface is actually endowed with two disjoint sets~$V_{\bar Q}$ and~${V_{\bar Q}}\dual$ of marked points and two dual dissections~$\dissection_{\bar Q}$ and~${\dissection_{\bar Q}}\dual$ defined as follows.
+Note that we could equivalently construct the surface~$\surface_{\bar Q}$ as follows:
+\begin{itemize}
+\item 
+\item
+\end{itemize}
+\vincent{TODO}
+The advantage of Definition~\ref{def:surfaceQuiver} is that it automatically endows with two disjoint sets~$V_{\bar Q}$ and~${V_{\bar Q}}\dual$ of marked points and two dual dissections~$\dissection_{\bar Q}$ and~${\dissection_{\bar Q}}\dual$ defined as follows.
 
@@
 \begin{itemize}
-\item $V_{\bar Q}$ has one vertex for each straight walk in~$\bar Q$,
+\item $V_{\bar Q}$ has one vertex for each straight walk in~$\bar Q$.
 \item $\dissection_{\bar Q}$ has one arc for each vertex~$p \in \bar Q_0$, obtained by concataining the sides~$\Enrt{\alpha} = \Enrs{\beta}$ and~$\Enrt{\alpha'} = \Enrs{\beta'}$ where~$p = t(\alpha) = s(\beta) = t(\alpha') = s(\beta')$, $\alpha\beta \notin I$ and~$\alpha'\beta' \notin I$.
+\item 
 \end{itemize}
+\vincent{TODO}
 A similar remark holds dually for~${V_{\bar Q}}\dual$ and~${\dissection_{\bar Q}}\dual$.
+Finally, observe that we could also have constructed the surface
 \end{remark}

### 2018-07-03 draft/accordionComplexSurfaces.tex

@@
 	\centerline{\includegraphics[scale=.7]{examplesSurfaces}}
-	\caption{The surface~$\surface_{\bar Q}$ for two quivers~$\bar Q$ of \fref{fig:quivers}.}
+	\caption{The surface~$\surface_{\bar Q}$ for the first four quivers~$\bar Q$ of \fref{fig:quivers}.
+The boundaries of the surfaces are shaded (the second surface has no boundary, it is just a sphere).}
 	\label{fig:examplesSurfaces}
@@
 \begin{itemize}
-\item 
-\item
+\item consider one $(\ell+1)$-gon~$P_\omega$ for each straight walk~$\omega$ of length~$\ell$ in~$\bar Q$ or in~$\bar Q\koszul$ (just closing~$\omega$ with an additional edge connecting~$t(\omega)$ to~$s(\omega)$),
+\item for each arrow~$\alpha \in Q_1\blossom$, consider the only straight walks~$\omega$ of~$\bar Q$ and~$\omega\koszul$ of~$\bar Q\koszul$ containing~$\alpha$, and glue the polygons~$P_\omega$ and~$P_{\omega\koszul}$ along their edges corresponding to~$\alpha$.
 \end{itemize}
-\vincent{TODO}
 The advantage of Definition~\ref{def:surfaceQuiver} is that it automatically endows with two disjoint sets~$V_{\bar Q}$ and~${V_{\bar Q}}\dual$ of marked points and two dual dissections~$\dissection_{\bar Q}$ and~${\dissection_{\bar Q}}\dual$ defined as follows.
@@
 \item $\dissection_{\bar Q}$ has one arc for each vertex~$p \in \bar Q_0$, obtained by concataining the sides~$\Enrt{\alpha} = \Enrs{\beta}$ and~$\Enrt{\alpha'} = \Enrs{\beta'}$ where~$p = t(\alpha) = s(\beta) = t(\alpha') = s(\beta')$, $\alpha\beta \notin I$ and~$\alpha'\beta' \notin I$.
-\item 
+\item $\dissection_{\bar Q}$ has one $\ell$-cell for each straight walk of length~$\ell$ in~$\bar Q\koszul$.
 \end{itemize}
-\vincent{TODO}
 A similar remark holds dually for~${V_{\bar Q}}\dual$ and~${\dissection_{\bar Q}}\dual$.
-Finally, observe that we could also have constructed the surface
 \end{remark}

### 2018-07-03 draft/accordionComplexSurfaces.tex
More about the countercurrent order.

--- 2018-07-03 draft/accordionComplexSurfaces.tex
@@
 \begin{definition}
-Consider an arrow~$\alpha \in Q\blossom_1$ and any two distinct non-kissing walks~$\mu_\star, \nu_\star$ marked at an occurrence of~$\alpha^\pm$.
-Let~$\sigma$ denote their maximal common substring containing that occurrence of~$\alpha$.
-Since~$\mu_\star \ne \nu_\star$, their common substring~$\sigma$ is strict, so that~$\mu_\star$ and~$\nu_\star$ split at least at one endpoint of~$\sigma$.
-We define the \defn{countercurrent order at~$\alpha$} by~$\mu_\star \prec_\alpha \nu_\star$ when~$\mu_\star$ enters and/or exits~$\sigma$ in the direction pointed by~$\alpha$, while~$\nu_\star$ enters and/or exits~$\sigma$ in the direction opposite to~$\alpha$.
+For any arrow~$\alpha \in Q\blossom_1$ and any two distinct non-kissing walks~$\mu_\star, \nu_\star$ marked at an occurrence of~$\alpha^\pm$,
+let~$\sigma$ denote their maximal common substring containing that occurrence of~$\alpha$.
+Since~$\mu_\star \ne \nu_\star$, this common substring~$\sigma$ is strict, so~$\mu_\star$ and~$\nu_\star$ split at one endpoint of~$\sigma$.
+The \defn{countercurrent order at~$\alpha$} is defined by~$\mu_\star \prec_\alpha \nu_\star$ when~$\mu_\star$ enters and/or exits~$\sigma$ in the direction pointed by~$\alpha$, while~$\nu_\star$ enters and/or exits~$\sigma$ in the direction opposite to~$\alpha$.
 \end{definition}
-\pierreguy{I need to modify these two definitions.}
+\pierreguy{Add a picture here?}
+
+\begin{remark}
+\label{rema:countercurrentOrderOnSurface}
+Using Theorem \ref{thm:complexesCoincide}, we can translate the definition of the countercurrent order~$\prec_\alpha$ to the language of~$\dissection$-accordions.
+An arrow~$\alpha$ in~$\bar Q\blossom$ corresponds to an angle at a point $v$ between two arcs of~$\dissection$.
+Two distinct non-kissing walks~$\mu_\star, \nu_\star$ marked at~$\alpha$ in~$\bar Q$ correspond to two distinct non-crossing~$\dissection$-accordions~$\gamma$ and~$\delta$ passing in front of this angle.
+Then~$\gamma \prec_\alpha \delta$ if~$\gamma$ passes closer to~$v$ than~$\delta$ does.
+\pierreguy{Should we prove this?}
+\pierreguy{Add picture.}
+\end{remark}
+
+For any face~$F$ of~$\NKC$ and any arrow~$\alpha\in Q_1\blossom$, we denote by~$F_\alpha$ the set of walks of~$F$ marked at an occurence of~$\alpha^\pm$.
+
+\begin{lemma}
+\label{lemm:countercurrentOrderIsTotal}
+For any face~$F$ of~$\NKC$ and any arrow~$\alpha\in Q_1\blossom$, the countercurrent order~$\prec_\alpha$ defines a total order on~$F_{\alpha}$.
+\end{lemma}
+\begin{proof}
+ The proof of \cite[Lemma 2.21]{PaluPilaudPlamondon} applies here.
+\end{proof}
+
+\begin{lemma}
+\label{lemm:facesHaveMaximalElement}
+For any face~$F$ of~$\NKC$ and any arrow~$\alpha\in Q_1\blossom$, the set~$F_\alpha$ admits a maximal element for the countercurrent order~$\prec_\alpha$.
+\end{lemma}
+\begin{proof}
+ We provide two proofs of the lemma.
+One is combinatorial and applies to~$\NKC$, and the other is geometric and applies to~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$, using the isomorphism of Theorem \ref{thm:complexesCoincide} and Remark \ref{rema:countercurrentOrderOnSurface}.
+
+ {\it Combinatorial proof.}
+ \pierreguy{Yann has the combinatorial proof.}
+
+ {\it Geometric proof.} Let~$F$ be a face of the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$.
+\end{proof}
 

### 2018-07-03 firstPaper/nonKissingComplex.tex

@@
 Observe that this straight walk is always the minimal marked walk of~$F_\alpha$ for the order~$\prec_\alpha$, since it always agrees with the direction of~$\alpha$.
-On the other hand, we can consider the maximal marked walk of~$F_\alpha$ for the order~$\prec_\alpha$.
+On the other hand, \textcolor{red}{ the proposition below shows that} we can consider the maximal marked walk of~$F_\alpha$ for the order~$\prec_\alpha$.
 Intuitively, it is the most countercurrent walk passing through~$\alpha$ with respect to the direction of~$\alpha$.
+\begin{proposition}\label{prop: nk facets are finite}
+\textcolor{red}{The facets of the non-kissing complex have finite cardinality.}
+\end{proposition}
+
+\begin{proof}\textcolor{red}{
+Let~$F$ be a non-kissing facet.
+Since the quiver~$Q$ has a finite number of arrows, it is enough to prove that each~$F_\alpha$ is finite.
+Assume, by means of contradiction, that there is some~$\alpha\in Q_1$ with~$F_\alpha$ infinite.
+Call ``junction'' a marked occurrence of an arrow~$\beta$ in some~$\omega_\star, \omega'_\star\in F_\alpha$, such that~$\omega$ and~$\omega'$ coincide from their marked occurrence of~$\alpha$ up to~$\beta$ and differ after~$\beta$.
+Since~$F_\alpha$ is infinite, there is an infinite number of junctions.
+Since~$Q_1$ is finite, there are two junctions with the same underlying arrow~$\beta$ and such that either~$\alpha$ points towards both junctions or~$\alpha$ points to the direction opposite to both junctions.
+This shows that there exist three marked walks~$\nu_\star\prec_\alpha \mu_\star\prec_\alpha \lambda_\star\in F_\alpha$ such that~$\lambda, \mu$ and $\nu$ coincide from their marked occurrence of~$\alpha$ up to some marked occurrence~$\beta_1$ of~$\beta$, after which~$\lambda$ differs from~$\mu$ and~$\nu$ but~$\mu$ and~$\nu$ coincide up to some other occurrence~$\beta_2$ of~$\beta$, and then differ (see Figure~\ref{fig: nk facets are finite}).
+Let~$\sigma$ be the longest common substring of~$\lambda$ and~$\nu$ containing~$\beta_1$ and~$\beta_2$ respectively.
+If~$\sigma$ is on top of~$\nu$, then it is at the bottom of~$\lambda$, and~$\lambda$ kisses~$\nu$, which is absurd.
+Otherwise, the subword~$\sigma$ of~$\mu$ containing~$\beta_2$ is at the bottom of~$\mu$ while the subword~$\sigma$ of~$\mu$ containing~$\beta_1$ is at the top of~$\mu$.
+Hence,~$\mu$ kisses itself, which is absurd.}
+\end{proof}
 

### 2018-07-03 draft/accordionComplexSurfaces.tex
two more surfaces
Minor changes

@@
 \end{figure}
+\begin{figure}[t]
+	\capstart
+	\centerline{\includegraphics[scale=.7]{examplesSurfaces2}}
+	\caption{The surface~$\surface_{\bar Q}$ for the last two quivers~$\bar Q$ of \fref{fig:quivers}.
+The boundaries of the surfaces are shaded.
+The first surface is a cylinder, the second one is a torus with a hole.}
+	\label{fig:examplesSurfaces2}
+\end{figure}
 %
@@
 
- {\it Geometric proof.} Let~$F$ be a face of the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$.
+ {\it Geometric proof.} View~$F$ as a face of the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$.
+ The arrow~$\alpha$ then corresponds to an angle in~$\dissection$.
+
+ The result is trivial if the set~$F_\alpha$ is finite; assume, therefore, that it is infinite.
+
 \end{proof}

### 2018-07-03 draft/accordionComplexSurfaces.tex
Very minor change

@@
 \label{def:walk}
-A \defn{walk} of a locally gentle quiver~$\bar Q$ is a maximal string of its blossoming quiver~$\bar Q \blossom$, meaning that at each end it either reaches a blossom vertex of~$\bar Q \blossom$ or enters an infinite cycle.
+A \defn{walk} of a locally gentle quiver~$\bar Q$ is a maximal string of its blossoming quiver~$\bar Q \blossom$, meaning that at each end it either reaches a blossom vertex of~$\bar Q \blossom$ or enters an infinite oriented cycle.
 We denote by~$\walks(\bar Q)$ the set of all walks on~$\bar Q$.

### 2018-07-03 draft/accordionComplexSurfaces.tex
demo nKC incomplète

--- 2018-07-03 draft/accordionComplexSurfaces.tex
@@
 \end{alignat*}
-placed as follows:
+placed as foll:qows:
 
@@
 \begin{definition}
-For any arrow~$\alpha \in Q\blossom_1$ and any two distinct non-kissing walks~$\mu_\star, \nu_\star$ marked at an occurrence of~$\alpha^\pm$,
-let~$\sigma$ denote their maximal common substring containing that occurrence of~$\alpha$.
-Since~$\mu_\star \ne \nu_\star$, this common substring~$\sigma$ is strict, so~$\mu_\star$ and~$\nu_\star$ split at one endpoint of~$\sigma$.
-The \defn{countercurrent order at~$\alpha$} is defined by~$\mu_\star \prec_\alpha \nu_\star$ when~$\mu_\star$ enters and/or exits~$\sigma$ in the direction pointed by~$\alpha$, while~$\nu_\star$ enters and/or exits~$\sigma$ in the direction opposite to~$\alpha$.
+Consider an arrow~$\alpha \in Q\blossom_1$ and any two distinct non-kissing walks~$\mu_\star, \nu_\star$ marked at an occurrence of~$\alpha^\pm$.
+Let~$\sigma$ denote their maximal common substring containing that occurrence of~$\alpha$.
+Since~$\mu_\star \ne \nu_\star$, their common substring~$\sigma$ is strict, so that~$\mu_\star$ and~$\nu_\star$ split at least at one endpoint of~$\sigma$.
+We define the \defn{countercurrent order at~$\alpha$} by~$\mu_\star \prec_\alpha \nu_\star$ when~$\mu_\star$ enters and/or exits~$\sigma$ in the direction pointed by~$\alpha$, while~$\nu_\star$ enters and/or exits~$\sigma$ in the direction opposite to~$\alpha$.
 \end{definition}
-\pierreguy{Add a picture here?}
-
-\begin{remark}
-\label{rema:countercurrentOrderOnSurface}
-Using Theorem \ref{thm:complexesCoincide}, we can translate the definition of the countercurrent order~$\prec_\alpha$ to the language of~$\dissection$-accordions.
-An arrow~$\alpha$ in~$\bar Q\blossom$ corresponds to an angle at a point $v$ between two arcs of~$\dissection$.
-Two distinct non-kissing walks~$\mu_\star, \nu_\star$ marked at~$\alpha$ in~$\bar Q$ correspond to two distinct non-crossing~$\dissection$-accordions~$\gamma$ and~$\delta$ passing in front of this angle.
-Then~$\gamma \prec_\alpha \delta$ if~$\gamma$ passes closer to~$v$ than~$\delta$ does.
-\pierreguy{Should we prove this?}
-\pierreguy{Add picture.}
-\end{remark}
-
-For any face~$F$ of~$\NKC$ and any arrow~$\alpha\in Q_1\blossom$, we denote by~$F_\alpha$ the set of walks of~$F$ marked at an occurence of~$\alpha^\pm$.
-
-\begin{lemma}
-\label{lemm:countercurrentOrderIsTotal}
-For any face~$F$ of~$\NKC$ and any arrow~$\alpha\in Q_1\blossom$, the countercurrent order~$\prec_\alpha$ defines a total order on~$F_{\alpha}$.
-\end{lemma}
-\begin{proof}
- The proof of \cite[Lemma 2.21]{PaluPilaudPlamondon} applies here.
-\end{proof}
-
-\begin{lemma}
-\label{lemm:facesHaveMaximalElement}
-For any face~$F$ of~$\NKC$ and any arrow~$\alpha\in Q_1\blossom$, the set~$F_\alpha$ admits a maximal element for the countercurrent order~$\prec_\alpha$.
-\end{lemma}
-\begin{proof}
- We provide two proofs of the lemma.
-One is combinatorial and applies to~$\NKC$, and the other is geometric and applies to~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$, using the isomorphism of Theorem \ref{thm:complexesCoincide} and Remark \ref{rema:countercurrentOrderOnSurface}.
-
- {\it Combinatorial proof.}
- \pierreguy{Yann has the combinatorial proof.}
-
- {\it Geometric proof.} Let~$F$ be a face of the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$.
-\end{proof}
+\pierreguy{I need to modify these two definitions.}
 

### 2018-07-03 firstPaper/nonKissingComplex.tex
demo nKC incomplète

@@
 \begin{proposition}\label{prop: nk facets are finite}
-\textcolor{red}{The facets of the non-kissing complex have finite cardinality.}
+\textcolor{red}{The faces of the non-kissing complex have finite cardinality.}
 \end{proposition}
@@
 \begin{proof}\textcolor{red}{
-Let~$F$ be a non-kissing facet.
+Let~$F$ be a non-kissing face.
 Since the quiver~$Q$ has a finite number of arrows, it is enough to prove that each~$F_\alpha$ is finite.
@@
 This shows that there exist three marked walks~$\nu_\star\prec_\alpha \mu_\star\prec_\alpha \lambda_\star\in F_\alpha$ such that~$\lambda, \mu$ and $\nu$ coincide from their marked occurrence of~$\alpha$ up to some marked occurrence~$\beta_1$ of~$\beta$, after which~$\lambda$ differs from~$\mu$ and~$\nu$ but~$\mu$ and~$\nu$ coincide up to some other occurrence~$\beta_2$ of~$\beta$, and then differ (see Figure~\ref{fig: nk facets are finite}).
-Let~$\sigma$ be the longest common substring of~$\lambda$ and~$\nu$ containing~$\beta_1$ and~$\beta_2$ respectively.
+Let~$\sigma_1$ and~$\sigma_2$ be the longest common substrings of~$\lambda$ and~$\nu$ containing~$\beta_1$ and~$\beta_2$ respectively.
+Note that, since~$\nu$ is finite,~$\sigma_2$ cannot contain~$\beta_1$; in particular,~$\sigma_2$ is contained in~$\mu$.
 If~$\sigma$ is on top of~$\nu$, then it is at the bottom of~$\lambda$, and~$\lambda$ kisses~$\nu$, which is absurd.
-Otherwise, the subword~$\sigma$ of~$\mu$ containing~$\beta_2$ is at the bottom of~$\mu$ while the subword~$\sigma$ of~$\mu$ containing~$\beta_1$ is at the top of~$\mu$.
-Hence,~$\mu$ kisses itself, which is absurd.}
+Otherwise, the subword~$\sigma$ of~$\mu$ containing~$\beta_2$ is at the bottom of~$\mu$ and $\lambda$ constains a substring of the form~$\gamma^{-1}\sigma_1$, where~$\gamma$ is an arrow of~$Q$.
+If~$\mu$ entirely contains~$\gamma^{-1}\sigma_1$, then~$\sigma_1$ is at the top of~$\mu$.
+Hence,~$\mu$ kisses itself, which is absurd.
+Therefore,~$\gamma^{-1}\sigma_1$ is not entirely contained in~$\mu$.}
 \end{proof}

### 2018-07-04 draft/accordionComplexSurfaces.tex
double cycle, double path

--- 2018-07-03 draft/accordionComplexSurfaces.tex
@@
 \begin{tikzpicture}[
-	scale=2,
+	scale=1.5,
 	thick,
 	decoration={markings, mark=at position 0.5 with {\arrow{>}}},
-	roundNode/.style={circle, fill=black, inner sep=2pt, outer sep=2pt}
+	roundNode/.style={circle, fill=black, inner sep=2pt, outer sep=1.5pt}
 	]
-	\node[roundNode, label=left:{$s(\alpha)$}] (s) at (-1,0) {};
-	\node[roundNode, label=right:{$t(\alpha)$}] (t) at (1,0) {};
-	\node[roundNode, fill=green, label=above:{$\green v(\alpha)$}] (v) at (0,1) {};
-	\node[roundNode, fill=red, label=below:{$\red v\dual(\alpha)$}] (vd) at (0,-1) {};
+	\node[roundNode, label={[label distance=-3pt]left:{$s(\alpha)$}}] (s) at (-1,0) {};
+	\node[roundNode, label={[label distance=-3pt]right:{$t(\alpha)$}}] (t) at (1,0) {};
+	\node[roundNode, fill=green, label={[label distance=-3pt]above:{$\green v(\alpha)$}}] (v) at (0,1) {};
+	\node[roundNode, fill=red, label={[label distance=-3pt]below:{$\red v\dual(\alpha)$}}] (vd) at (0,-1) {};
 	\draw[color=black, postaction={decorate}] (s) -> (t) node[midway, above] {$\alpha$};
@@
 	\pic [draw, angle radius=.7cm] {angle = vd--s--t};
-	\draw[color=green, postaction={decorate}] (v) -> (s) node[midway, above left] {$\green \Enrs{\alpha}$};
-	\draw[color=green, postaction={decorate}] (v) -> (t) node[midway, above right] {$\green \Enrt{\alpha}$};
-	\draw[color=red, postaction={decorate}] (vd) -> (s) node[midway, below left] {$\red \Ers{\alpha}$};
-	\draw[color=red, postaction={decorate}] (vd) -> (t) node[midway, below right] {$\red \Ert{\alpha}$};
+	\draw[color=green, postaction={decorate}] (v) -> (s) node[midway, above left, outer sep=-3pt] {$\green \Enrs{\alpha}$};
+	\draw[color=green, postaction={decorate}] (v) -> (t) node[midway, above right, outer sep=-3pt] {$\green \Enrt{\alpha}$};
+	\draw[color=red, postaction={decorate}] (vd) -> (s) node[midway, below left, outer sep=-3pt] {$\red \Ers{\alpha}$};
+	\draw[color=red, postaction={decorate}] (vd) -> (t) node[midway, below right, outer sep=-3pt] {$\red \Ert{\alpha}$};
 \end{tikzpicture}
@@
 
-\begin{example}
+\begin{example}[Double cycle]
+\label{exm:doubleCycle}
 Consider the following family of locally gentle quivers:
-\vincent{TODO}
+\vincent{TODO double cycle}
+\end{example}
+
+\begin{example}[Double path]
+\label{exm:doublePath}
+Consider the following family of locally gentle quivers:
+\vincent{TODO double path}
 \end{example}

### 2018-07-04 draft/accordionComplexSurfaces.tex
Remark on number of boundary components and genus.

@@
 \begin{remark}
-Observe that
+The following observations are useful for the computation of examples.
 \begin{itemize}
-\item $V_{\bar Q}$ has one vertex for each straight walk in~$\bar Q$.
-\item $\dissection_{\bar Q}$ has one arc for each vertex~$p \in \bar Q_0$, obtained by concataining the sides~$\Enrt{\alpha} = \Enrs{\beta}$ and~$\Enrt{\alpha'} = \Enrs{\beta'}$ where~$p = t(\alpha) = s(\beta) = t(\alpha') = s(\beta')$, $\alpha\beta \notin I$ and~$\alpha'\beta' \notin I$.
-\item $\dissection_{\bar Q}$ has one $\ell$-cell for each straight walk of length~$\ell$ in~$\bar Q\koszul$.
+\item The set~$V_{\bar Q}$ has one vertex for each straight walk in~$\bar Q$ (equivalently, for each maximal path in~$\bar Q$).
+      Finite straight walks yield vertices on the boundary, while infinite cyclic straight walks yield punctures.
+\item The dissection~$\dissection_{\bar Q}$ has one arc for each vertex~$p \in \bar Q_0$, obtained by concataining the sides~$\Enrt{\alpha} = \Enrs{\beta}$ and~$\Enrt{\alpha'} = \Enrs{\beta'}$ where~$p = t(\alpha) = s(\beta) = t(\alpha') = s(\beta')$, $\alpha\beta \notin I$ and~$\alpha'\beta' \notin I$.
+\item The dissection~$\dissection_{\bar Q}$ has one $\ell$-cell for each straight walk of length~$\ell$ in~$\bar Q\koszul$.
+\item The number of boundray components of~$\surface(\bar Q)$ can be computed as follows.
+      There are two natural perfect matchings whose vertices are the blossoming vertices of~$\bar Q$: one is obtained by putting an edge between two vertices~$v_1$ and~$v_2$ whenever there is a straight walk of~$\bar Q$ relating them, and the other is obtained by doing the same for~$\bar Q \koszul$.
+      Let~$G$ be the superposition of these two perfect matchings.
+      Then the number of boundary components of~$\surface(\bar Q)$ is the number of connected components of~$G$.
+\item The genus of the surface~$\surface(\bar Q)$ is
+      \[
+       g = \frac{|Q_1| - |Q_0| - b + 2}{2},
+      \]
+      where~$b$ is the number of boundary components (see above for a way to compute~$b$).
+      Indeed, ~$g=\frac{2-\chi(\surface(\bar Q))}{2}$, where~$\chi(\surface(\bar Q))$ is the Euler characteristic of~$\surface(\bar Q)$.
+      The dissection~$\dissection$ provides a cellular decomposition of~$\surface(\bar Q)$ on which we fill the boundary components with disks.  
+      The number of faces of this cellular decomposition is~$b$, its number of edges is~$|Q_0|$ and its number of vertices is the number of finite straight walks in~$\bar Q$, which is equal to~$2|Q_0| - |Q_1|$.
+      The above formula for~$g$ follows.
+
 \end{itemize}
@@
 \label{prop:purity}
- The the non-kissing complex~$\NKC$ and the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$ are pure of dimension~$|Q_0| + \Delta$, where~$\Delta$ is the number of blossoming vertices of~$Q\blossom$ divided by two.
+ The the non-kissing complex~$\NKC$ and the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$ are pure of dimension~$3|Q_0| - |Q_1|$.
 \end{proposition}

### 2018-07-04 draft/accordionComplexSurfaces.tex
modifications pictures

--- 2018-07-04 draft/accordionComplexSurfaces.tex
@@
 	\capstart
-	\centerline{\includegraphics[scale=.4]{quivers}}
+	\centerline{\includegraphics[scale=.6]{quivers}}
 	\caption{Some locally gentle quivers and their blossoming quivers. Initial vertices are solid and labeled while blossom vertices are hollow, and initial arcs are bold while blossom arcs are thin.}
@@
 	\capstart
-	\centerline{\includegraphics[scale=.4]{koszulQuivers}}
+	\centerline{\includegraphics[scale=.6]{koszulQuivers}}
 	\caption{The Koszul duals of the (blossoming) quivers of \fref{fig:quivers}.}
@@
 	\centerline{\includegraphics[scale=.7]{examplesSurfaces}}
-	\caption{The surface~$\surface_{\bar Q}$ for the first four quivers~$\bar Q$ of \fref{fig:quivers}.
-The boundaries of the surfaces are shaded (the second surface has no boundary, it is just a sphere).}
+	\caption{The surface~$\surface_{\bar Q}$ for the quivers~$\bar Q$ of \fref{fig:quivers}.
+The boundaries of the surfaces are shaded, and the glue symbols indicate how to identify some edges to get the desired surfaces.
+The first two surfaces are disks, the third is a sphere, the fourth is a cylinder, and the fifth is a punctured torus.}
 	\label{fig:examplesSurfaces}
 \end{figure}
-\begin{figure}[t]
-	\capstart
-	\centerline{\includegraphics[scale=.7]{examplesSurfaces2}}
-	\caption{The surface~$\surface_{\bar Q}$ for the last two quivers~$\bar Q$ of \fref{fig:quivers}.
+
+%\begin{figure}[t]
+%	\capstart
+%	\centerline{\includegraphics[scale=.7]{examplesSurfaces2}}
+%	\caption{The surface~$\surface_{\bar Q}$ for the last two quivers~$\bar Q$ of \fref{fig:quivers}.
 The boundaries of the surfaces are shaded.
 The first surface is a cylinder, the second one is a torus with a hole.}
-	\label{fig:examplesSurfaces2}
-\end{figure}
+%	\label{fig:examplesSurfaces2}
+%\end{figure}
 %
@@
 
-\begin{example}[Double cycle]
+\begin{example}[Cambrian paths]
+\label{exm:CambrianPath}
+\end{example}
+
+\begin{example}[Double cycles]
 \label{exm:doubleCycle}
@@
 
-\begin{example}[Double path]
+\begin{example}[Double paths]
 \label{exm:doublePath}

### 2018-07-04 draft/accordionComplexSurfaces.tex
Structure of proof of finiteness of faces.

@@
 \label{lemm:facesHaveMaximalElement}
-For any face~$F$ of~$\NKC$ and any arrow~$\alpha\in Q_1\blossom$, the set~$F_\alpha$ admits a maximal element for the countercurrent order~$\prec_\alpha$.
+For any finite face~$F$ of~$\NKC$ and any arrow~$\alpha\in Q_1\blossom$, the set~$F_\alpha$ admits a maximal element for the countercurrent order~$\prec_\alpha$.
 \end{lemma}
@@
 
+\begin{lemma}
+\label{lemm:facesAreBounded}
+There is a bound on the number of elements of a finite face of~$\NKC$.
+\end{lemma}
+
+\begin{lemma}
+\label{lemm:facetsAreFinite}
+Any face of~$\NKC$ and~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$ is contained in a finite maximal face.
+\end{lemma}
+\begin{proof}
+ We provide two proofs of the lemma.  One is combinatorial and applies to~$\NKC$, and the other is geometric and applies to~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$.
+
+ {\it Combinatorial proof.}
+ This is an immediate consequence of Lemma \ref{lemm:facesAreBounded}.
+
+ {\it Geometric proof.} Let~$F$ be a face of the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$.
+ Its elements are pairwise compatible~$\dissection$-accordions on the surface~$\surface(\bar Q)$.
+ Thus~$F$ can be viewed as a partial tagged triangulation of~$\surface(\bar Q)$, by letting the~$\dissection$-accordions circling a puncture in (say) clockwise order be seen as ``notched'' arcs to said puncture, and the ones circling it in counter-clockwise orientation be ``un-notched'' arcs.
+ It is known (see, for instance, \cite{FominShapiroThurston}) that any such partial tagged triangulation can be embedded into a full triangulation, and that triangulations contain a finite number of arcs.
+ Thus~$F$ is finite, and is contained in a finite maximal face.
+\end{proof}
+
 \subsection{Purity of the non-crossing and non-kissing complexes}
@@
 A simplicial complex is \defn{pure of dimension~$d$} if all its maximal faces have dimension~$d$.
+The aim of this section is to prove the following purity result.
 
@@
 
-\begin{lemma}
-\label{lemm:facetsAreFinite}
-Any face of~$\NKC$ and~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$ is contained in a finite maximal face.
-\end{lemma}
+The following definition from \cite[Definition 2.23]{PaluPilaudPlamondon} extends to the setting locally gentle algebras.
+
+\begin{definition}
+\label{defi:distinguishedWalksAndArrows}
+Let~$\alpha \in Q\blossom_1$ be an arrow and let~$F$ be a face of~$\NKC$ containing the straight walk passing through~$\alpha$.
+Consider the marked walk~$\omega_\star \eqdef \max_{\prec_\alpha} F_\alpha$ (which exists by Lemma \ref{lemm:facesHaveMaximalElement}),
+and let~$\omega$ be the walk obtained by forgetting the marked arrow in~$\omega_\star$. 
+We say that~$\omega$ is the \defn{distinguished walk} of~$F$ at~$\alpha$ and that~$\alpha$ is a \defn{distinguished arrow} on~$\omega \in F$.
+We will use the notation
+\[
+\distinguishedWalk{\alpha}{F} \eqdef \max\nolimits_{\prec_\alpha} F_\alpha
+\qquad\text{and}\qquad
+\distinguishedArrows{\omega}{F} \eqdef \set{\alpha \in \omega}{\distinguishedWalk{\alpha}{F} = \omega}.
+\]
+\end{definition}
+
+The following result extends \cite[Proposition 2.26]{PaluPilaudPlamondon} to the case of locally gentle algebras.
+
+\begin{proposition}
+\label{prop:numberOfDistinguishedArrows}
+Let~$F$ be a facet of~$\NKC$.
+\begin{itemize}
+ \item Each bending walk of~$F$ has exactly two distinguished arrows.
+ \item Each finite straight walk of~$F$ has exactly one distinguished arrows.
+ \item Each infinite straight walk of~$F$ has exactly zero distinguished arrows.
+\end{itemize}
+\end{proposition}
 \begin{proof}
- We provide two proofs of the lemma.  One is combinatorial and applies to~$\NKC$, and the other is geometric and applies to~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$.
-
- {\it Combinatorial proof.}
- \pierreguy{Yann has the combinatorial proof.}
-
- {\it Geometric proof.} Let~$F$ be a face of the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$.
- Its elements are pairwise compatible~$\dissection$-accordions on the surface~$\surface(\bar Q)$.
- Thus~$F$ can be viewed as a partial tagged triangulation of~$\surface(\bar Q)$, by letting the~$\dissection$-accordions circling a puncture in (say) clockwise order be seen as ``notched'' arcs to said puncture, and the ones circling it in counter-clockwise orientation be ``un-notched'' arcs.
- It is known (see, for instance, \cite{FominShapiroThurston}) that any such partial tagged triangulation can be embedded into a full triangulation, and that triangulations contain a finite number of arcs.
- Thus~$F$ is finite, and is contained in a finite maximal face.
+ \pierreguy{Vincent has the proof of this proposition.}
 \end{proof}
 
+We can now prove the purity result.
+
+{\it Proof of Proposition \ref{prop:purity}.}
+\pierreguy{TO DO}
+
 \subsection{Thinness of the non-crossing and non-kissing complexes, mutation}
+
+A simplicial complex is \defn{thin} if each of its codimension~$1$ faces is contained in exaclty two facets.
+We state the following results, which generalize \cite[Proposition 2.31 and Corollary 2.33]{PaluPilaudPlamondon}, whose proofs apply withouth change.
+
+\begin{proposition}
+\label{prop:flip}
+Let~$F$ be a non-kissing facet in~$\NKC$ and let~$\omega \in F$ be a bending walk.
+Let~$\alpha$ and~$\beta$ be the distinguished arrows of~$\omega$ (see Proposition \ref{prop:numberOfDistinguishedArrows}), and~$\sigma$ be the distinguished substring of~$\omega$, which splits~$\omega$ into~$\omega = \rho \sigma \tau$.
+Let~$\alpha'$ and~$\beta'$ be the other two arrows of~$Q_1\blossom$ incident to the endpoints of~$\sigma$ and such that~$\alpha'\alpha \in I$ or~$\alpha\alpha' \in I$, and $\beta'\beta \in I$ or~$\beta\beta' \in I$.
+Let~$\mu \eqdef \distinguishedWalk{\alpha'}{F \ssm \{\omega\}}$ and~$\nu \eqdef \distinguishedWalk{\beta'}{F \ssm \{\omega\}}$ be the distinguished walks of~$F \ssm \{\omega\}$ at~$\alpha'$ and~$\beta'$ respectively.
+Then
+\begin{enumerate}[(i)]
+\item The walk~$\mu$ splits into~$\mu = \rho' \sigma \tau$ and the walk~$\nu$ splits into~$\nu = \rho \sigma \tau'$.
+\item The walk~$\omega' \eqdef \rho' \sigma \tau'$ is kissing~$\omega$ but no other~walk~of~$F$.
+Moreover, $\omega'$ is the only other (undirected) walk besides~$\omega$ which is not kissing any other walk of~$F \ssm \{\omega\}$.
+\end{enumerate}
+\end{proposition}
+
+\begin{corollary}
+The non-kissing complex~$\RNKC$ is thin and is a pseudomanifold without boundary.
+\end{corollary}
 

### 2018-07-04 draft/accordionComplexSurfaces.tex
reorder examples
Structure of proof of finiteness of faces, bis.

@@
 \item The dissection~$\dissection_{\bar Q}$ has one $\ell$-cell for each straight walk of length~$\ell$ in~$\bar Q\koszul$.
-\item The number of boundray components of~$\surface(\bar Q)$ can be computed as follows.
+\item The number of boundary components of~$\surface(\bar Q)$ can be computed as follows.
       There are two natural perfect matchings whose vertices are the blossoming vertices of~$\bar Q$: one is obtained by putting an edge between two vertices~$v_1$ and~$v_2$ whenever there is a straight walk of~$\bar Q$ relating them, and the other is obtained by doing the same for~$\bar Q \koszul$.
@@
       The above formula for~$g$ follows.
-
 \end{itemize}
@@
 \label{exm:CambrianPath}
+\end{example}
+
+\begin{example}[Reversed paths]
+\label{exm:doublePath}
+Consider the following family of locally gentle quivers:
+\vincent{TODO double path}
+\end{example}
+
+\begin{example}[Double paths]
+\label{exm:doublePath}
+Consider the following family of locally gentle quivers:
+\vincent{TODO double path}
 \end{example}
@@
 \vincent{TODO double cycle}
-\end{example}
-
-\begin{example}[Double paths]
-\label{exm:doublePath}
-Consider the following family of locally gentle quivers:
-\vincent{TODO double path}
 \end{example}
@@
 \end{lemma}
+\begin{proof}
+ We provide two proofs of the lemma.  One is combinatorial and applies to~$\NKC$, and the other is geometric and applies to~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$.
+
+ {\it Combinatorial proof.}
+ \pierreguy{Yann has the combinatorial proof.}
+
+ {\it Geometric proof.} Let~$F$ be a face of the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$.
+ Its elements are pairwise compatible~$\dissection$-accordions on the surface~$\surface(\bar Q)$.
+ Thus~$F$ can be viewed as a partial tagged triangulation of~$\surface(\bar Q)$, by letting the~$\dissection$-accordions circling a puncture in (say) clockwise order be seen as ``notched'' arcs to said puncture, and the ones circling it in counter-clockwise orientation be ``un-notched'' arcs.
+ It is known (see, for instance, \cite{FominShapiroThurston}) that any such partial tagged triangulation can be embedded into a full triangulation, and that triangulations contain a finite number of arcs.
+ Thus~$F$ is finite, and is contained in a finite maximal face.
+\end{proof}
 
@@
 \begin{proof}
- We provide two proofs of the lemma.  One is combinatorial and applies to~$\NKC$, and the other is geometric and applies to~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$.
-
- {\it Combinatorial proof.}
  This is an immediate consequence of Lemma \ref{lemm:facesAreBounded}.
-
- {\it Geometric proof.} Let~$F$ be a face of the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$.
- Its elements are pairwise compatible~$\dissection$-accordions on the surface~$\surface(\bar Q)$.
- Thus~$F$ can be viewed as a partial tagged triangulation of~$\surface(\bar Q)$, by letting the~$\dissection$-accordions circling a puncture in (say) clockwise order be seen as ``notched'' arcs to said puncture, and the ones circling it in counter-clockwise orientation be ``un-notched'' arcs.
- It is known (see, for instance, \cite{FominShapiroThurston}) that any such partial tagged triangulation can be embedded into a full triangulation, and that triangulations contain a finite number of arcs.
- Thus~$F$ is finite, and is contained in a finite maximal face.
 \end{proof}

### 2018-07-04 firstPaper/nonKissingComplex.tex
nk facets are finite

--- 2018-07-03 firstPaper/nonKissingComplex.tex
@@
 Observe that this straight walk is always the minimal marked walk of~$F_\alpha$ for the order~$\prec_\alpha$, since it always agrees with the direction of~$\alpha$.
-On the other hand, we can consider the maximal marked walk of~$F_\alpha$ for the order~$\prec_\alpha$.
+On the other hand, Proposition~\ref{prop: nk facets are finite}, below, shows that we can consider the maximal marked walk of~$F_\alpha$ for the order~$\prec_\alpha$.
 Intuitively, it is the most countercurrent walk passing through~$\alpha$ with respect to the direction of~$\alpha$.
+
+\begin{lemma}\label{lemma: distinguished arrows exists}
+Let~$F$ be a finite face of~$\NKC$, let~$\omega$ be a walk in~$F$, and let~$\alpha$ be an arrow on~$\omega$.
+Then, there is an arrow~$\beta$ oriented in the same direction as~$\alpha$ in~$\omega$ such that~$\omega$ (marked at~$\beta$) is maximal in~$F$ for~$\prec_\beta$.
+\end{lemma}
+
+\begin{proof}
+If~$\omega$ is not maximal in~$F$ for~$\prec_\alpha$, consider~${\mu \eqdef \min_{\prec_\alpha} \set{\nu \in F_\alpha}{\omega \prec_\alpha \nu}}$.
+Let~$\sigma$ denote the maximal common substring of~$\omega$ and~$\mu$ containing~$\alpha$.
+Since~$\omega$ and~$\mu$ are distinct, they split at an endpoint of~$\sigma$.
+At this endpoint, the arrow~$\beta$ of~$\omega$ not in~$\sigma$ points in the same direction as~$\alpha$ since~$\omega \prec_\alpha \mu$.
+Let~$\lambda$ be maximal in~$F$ for~$\prec_\beta$.
+If~$\lambda \ne \omega$, then~$\lambda$ either kisses~$\mu$ or contradicts the minimality of~$\mu$ among the walks~$\set{\nu \in F_\alpha}{\omega \prec_\alpha \nu}$.
+See \fref{fig:pure}\,(right) for an illustration.
+We conclude that~$\lambda = \omega$ has a distinguished arrow~$\beta$ in the direction of~$\alpha$.
+\end{proof}
+
+\begin{proposition}\label{prop: nk facets are finite}
+The faces of the non-kissing complex have finite cardinality.
+\end{proposition}
+
+\begin{proof}
+By Lemma~\ref{lemma: distinguished arrows exists}, the cardinality of any finite non-kissing face is bounded by~$|Q_1\blossom|$.
+Thus, any collection of~$|Q_1\blossom|+1$ walks contains a kiss and all non-kissing faces are finite.
+% Let~$F$ be a non-kissing face.
+% Since the quiver~$Q$ has a finite number of arrows, it is enough to prove that each~$F_\alpha$ is finite.
+% Assume, by means of contradiction, that there is some~$\alpha\in Q_1$ with~$F_\alpha$ infinite.
+% Call ``junction'' a marked occurrence of an arrow~$\beta$ in some~$\omega_\star, \omega'_\star\in F_\alpha$, such that~$\omega$ and~$\omega'$ coincide from their marked occurrence of~$\alpha$ up to~$\beta$ and differ after~$\beta$.
+% Since~$F_\alpha$ is infinite, there is an infinite number of junctions.
+% Since~$Q_1$ is finite, there are two junctions with the same underlying arrow~$\beta$ and such that either~$\alpha$ points towards both junctions or~$\alpha$ points to the direction opposite to both junctions.
+% This shows that there exist three marked walks~$\nu_\star\prec_\alpha \mu_\star\prec_\alpha \lambda_\star\in F_\alpha$ such that~$\lambda, \mu$ and $\nu$ coincide from their marked occurrence of~$\alpha$ up to some marked occurrence~$\beta_1$ of~$\beta$, after which~$\lambda$ differs from~$\mu$ and~$\nu$ but~$\mu$ and~$\nu$ coincide up to some other occurrence~$\beta_2$ of~$\beta$, and then differ (see Figure~\ref{fig: nk facets are finite}).
+% Let~$\sigma_1$ and~$\sigma_2$ be the longest common substrings of~$\lambda$ and~$\nu$ containing~$\beta_1$ and~$\beta_2$ respectively.
+% Note that, since~$\nu$ is finite,~$\sigma_2$ cannot contain~$\beta_1$; in particular,~$\sigma_2$ is contained in~$\mu$.
+% If~$\sigma$ is on top of~$\nu$, then it is at the bottom of~$\lambda$, and~$\lambda$ kisses~$\nu$, which is absurd.
+% Otherwise, the subword~$\sigma$ of~$\mu$ containing~$\beta_2$ is at the bottom of~$\mu$ and $\lambda$ constains a substring of the form~$\gamma^{-1}\sigma_1$, where~$\gamma$ is an arrow of~$Q$.
+% If~$\mu$ entirely contains~$\gamma^{-1}\sigma_1$, then~$\sigma_1$ is at the top of~$\mu$.
+% Hence,~$\mu$ kisses itself, which is absurd.
+% Therefore,~$\gamma^{-1}\sigma_1$ is not entirely contained in~$\mu$.
+\end{proof}
 
@@
 \begin{proof}
-We first prove that each walk of~$F$ contains at most one distinguished arrow in each direction.
+In view of Lemma~\ref{lemma: distinguished arrows exists}, it remains to prove that each walk of~$F$ contains at most one distinguished arrow in each direction.
 Assume that a walk~$\omega$ has two distinguished arrows~$\alpha, \beta$ pointing in the same direction.
@@
 \end{figure}
-
-\smallskip
-We now prove that for any arrow~$\alpha$ on a walk~$\omega$ in a face~$F$ of~$\NKC$, there is a distinguished arrow on~$\omega \in F$ in the direction of~$\alpha$.
-If~$\omega$ is not the distinguished walk of~$F$ at~$\alpha$, consider~${\mu \eqdef \min_{\prec_\alpha} \set{\nu \in F_\alpha}{\omega \prec_\alpha \nu}}$.
-Let~$\sigma$ denote the maximal common substring of~$\omega$ and~$\mu$ containing~$\alpha$.
-Since~$\omega$ and~$\mu$ are distinct, they split at an endpoint of~$\sigma$.
-At this endpoint, the arrow~$\beta$ of~$\omega$ not in~$\sigma$ points in the same direction as~$\alpha$ since~$\omega \prec_\alpha \mu$.
-Let~$\lambda$ be the distinguished walk of~$F$ at~$\beta$.
-If~$\lambda \ne \omega$, then~$\lambda$ either kisses~$\mu$ or contradicts the minimality of~$\mu$ among the walks~$\set{\nu \in F_\alpha}{\omega \prec_\alpha \nu}$.
-See \fref{fig:pure}\,(right) for an illustration.
-We conclude that~$\lambda = \omega$ has a distinguished arrow~$\beta$ in the direction of~$\alpha$.
 \end{proof}

### 2018-07-04 draft/accordionComplexSurfaces.tex

@@
  {\it Geometric proof.} View~$F$ as a face of the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$.
- The arrow~$\alpha$ then corresponds to an angle in~$\dissection$.
-
- The result is trivial if the set~$F_\alpha$ is finite; assume, therefore, that it is infinite.
+ The arrow~$\alpha$ then corresponds to an angle in~$\dissection$ at a vertex~$v$.
+
+ For any curve~$\gamma$ in~$F$, even though~$\gamma$ may pass through the above angle infinitely many times, there is one instance that is furthest from the angle:
+ indeed, if ~$\gamma$ passes infinitely many times through~$\alpha$, then~$v$ is a puncture and~$\gamma$ circles infinitely towards it.
+ But then~$\gamma$ passes through~$\alpha$ only finitely many times before it starts circling~$v$ (in either direction), and one of these times is the furthest from~$v$.
+
+ Therefore, for every curve~$\gamma\in F$, there is a maximal occurence of~$\alpha$ in~$\gamma$.
+ Since~$F$ is finite, the set of these maximal occurences is finite, so it admits a maximal element.  
+ This element is the maximal element of~$F_\alpha$.
 
@@
 \begin{proof}
- This is an immediate consequence of Lemma \ref{lemm:facesAreBounded}.
+ If~$\NKC$ admits an infinite face, then all subsets of this face are also faces, so~$\NKC$ admits faces of arbitrary finite cardinality.
+ This contradicts Lemma \ref{lemm:facesAreBounded}.
 \end{proof}

### 2018-07-04 draft/accordionComplexSurfaces.tex
:q
double paths

--- 2018-07-04 draft/accordionComplexSurfaces.tex
@@
 
-%\begin{figure}[t]
-%	\capstart
-%	\centerline{\includegraphics[scale=.7]{examplesSurfaces2}}
-%	\caption{The surface~$\surface_{\bar Q}$ for the last two quivers~$\bar Q$ of \fref{fig:quivers}.
-The boundaries of the surfaces are shaded.
-The first surface is a cylinder, the second one is a torus with a hole.}
-%	\label{fig:examplesSurfaces2}
-%\end{figure}
-%
 Definition~\ref{def:surfaceQuiver} constructs an orientable surface~$\surface(\bar Q)$ with boundaries.
@@
 \label{exm:doublePath}
-Consider the following family of locally gentle quivers:
-\vincent{TODO double path}
+Consider the family ``double paths'' quivers indicated in \fref{fig:doublePathsQuivers}.
+
+\begin{figure}[h]
+	\capstart
+	\centerline{\includegraphics[scale=.4]{doublePathsQuivers}}
+	\caption{The double paths quivers with~$1, 2, 3, 4$ vertices.}
+	\label{fig:doublePathsQuivers}
+\end{figure}
+
+\begin{figure}[h]
+	\capstart
+	\centerline{\includegraphics[scale=.7]{doublePathsSurfaces}}
+	\caption{The surface~$\surface_{\bar Q}$ for the double paths with~$1, 2, 3, 4$ vertices.}
+	\label{fig:doublePathsSurfaces}
+\end{figure}
+
 \end{example}
@@
 \end{lemma}
+
+\begin{lemma}
+\label{lemm:facetsAreFinite}
+Any face of~$\NKC$ and~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$ is contained in a finite maximal face.
+\end{lemma}
 \begin{proof}
@@
  {\it Combinatorial proof.}
- \pierreguy{Yann has the combinatorial proof.}
+ This is an immediate consequence of Lemma \ref{lemm:facesAreBounded}.
 
@@
  Thus~$F$ is finite, and is contained in a finite maximal face.
-\end{proof}
-
-\begin{lemma}
-\label{lemm:facetsAreFinite}
-Any face of~$\NKC$ and~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$ is contained in a finite maximal face.
-\end{lemma}
-\begin{proof}
- This is an immediate consequence of Lemma \ref{lemm:facesAreBounded}.
 \end{proof}

### 2018-07-04 draft/accordionComplexSurfaces.tex
max for finite facets

--- 2018-07-04 draft/accordionComplexSurfaces.tex
@@
 \end{alignat*}
-placed as foll:qows:
+placed as follows:
 
@@
 \subsection{The countercurrent order}
-The countercurrent order was introduced in \cite{PaluPilaudPlamondon} for gentle algebras.  We now adapt it to locally gentle algebras.
+The countercurrent order was introduced in~\cite{McConville} for grids and defined in \cite{PaluPilaudPlamondon} for gentle algebras.
+We now adapt it to locally gentle algebras.
 
@@
 \label{lemm:facesHaveMaximalElement}
-For any finite face~$F$ of~$\NKC$ and any arrow~$\alpha\in Q_1\blossom$, the set~$F_\alpha$ admits a maximal element for the countercurrent order~$\prec_\alpha$.
+For any finite face~$F$ of~$\NKC$ and any arrow~$\alpha\in Q_1\blossom$, the set~$F_\alpha$ is either empty or admits a maximal element for the countercurrent order~$\prec_\alpha$.
 \end{lemma}
@@
  {\it Combinatorial proof.}
- \pierreguy{Yann has the combinatorial proof.}
+ Note that even though~$F$ is finite, the set of marked walks~$F_\alpha$ might be infinite if~$\alpha$ belongs to an oriented cycle of~$Q$.
+ Assume that~$F_\alpha$ is non-empty, and infinite.
+ Any walk that contains an infinite number of copies of~$\alpha$ can be written in the form~$\omega=\sigma c^\infty$ where~$\sigma$ is a (possibly infinite) substring and~$c$ is an oriented cycle containing~$\alpha$.
+ Then~$\omega$ marked at the first occurrence of~$\alpha$ in~$c^\infty$ is greater than~$\omega$ marked at any other occurrence of~$\alpha$ in~$c^\infty$.
+ We can thus safely remove all copies of~$\omega$ marked at an occurrence of~$\alpha$ in~$c^\infty$ but the first one.
+ After applying this procedure a finite number of times,~$F_\alpha$ becomes finite, and the claim follows.
 

### 2018-07-04 draft/accordionComplexSurfaces.tex
Bijection locally gentle vs dissected surfaces.

--- 2018-07-04 draft/accordionComplexSurfaces.tex
@@
 Definition~\ref{def:surfaceQuiver} constructs an orientable surface~$\surface(\bar Q)$ with boundaries.
-Note that we could equivalently construct the surface~$\surface_{\bar Q}$ as follows:
+
+\begin{remark}
+We could equivalently construct the surface~$\surface_{\bar Q}$ as follows:
 \begin{itemize}
@@
 \end{itemize}
+\end{remark}
+
 The advantage of Definition~\ref{def:surfaceQuiver} is that it automatically endows with two disjoint sets~$V_{\bar Q}$ and~${V_{\bar Q}}\dual$ of marked points and two dual dissections~$\dissection_{\bar Q}$ and~${\dissection_{\bar Q}}\dual$ defined as follows.
@@
 \end{definition}
+
+\begin{proposition}
+\label{prop:dissectionsAreCellular}
+Let~$\bar Q$ be a locally gentle bound quiver.
+Then the dissections~$\dissection_{\bar Q}$ and~$\dissection_{\bar Q}\dual$ are cellular and dual to each other.
+\end{proposition}
+\begin{proof}
+
+\end{proof}
+
+\begin{theorem}
+\label{thm:bijectionLocallyGentleAndSurfaces}
+ Up to isomorphism, the constructions of Definitions \ref{def:quiverDualDissections} and \ref{def:surfaceQuiver} are inverse to each other.
+ They induce a bijection between the set of isomorphism classes of locally gentle algebras and the set of homeomorphism classes of marked surfaces with a pair of dual cellular dissections.
+\end{theorem}
 

### 2018-07-04 draft/accordionComplexSurfaces.tex

--- 2018-07-04 draft/accordionComplexSurfaces.tex
@@
 
-%\begin{figure}[t]
-%	\capstart
-%	\centerline{\includegraphics[scale=.7]{examplesSurfaces2}}
-%	\caption{The surface~$\surface_{\bar Q}$ for the last two quivers~$\bar Q$ of \fref{fig:quivers}.
-The boundaries of the surfaces are shaded.
-The first surface is a cylinder, the second one is a torus with a hole.}
-%	\label{fig:examplesSurfaces2}
-%\end{figure}
-%
 Definition~\ref{def:surfaceQuiver} constructs an orientable surface~$\surface(\bar Q)$ with boundaries.
-Note that we could equivalently construct the surface~$\surface_{\bar Q}$ as follows:
+
+\begin{remark}
+We could equivalently construct the surface~$\surface_{\bar Q}$ as follows:
 \begin{itemize}

### 2018-07-04 draft/accordionComplexSurfaces.tex
Dissections are cellular and dual to each other.

@@
 \begin{proof}
-
+In the construction of~$\surface(\bar Q)$, if two arrows~$\alpha$ and~$\beta$ of~$\bar Q \blossom$ are such that~$t(\alpha) = s(\beta)$ and~$\alpha\beta\in I\blossom$, then the vertices~$v(\alpha)$ and~$v(\beta)$ are identified on the surface.
+Thus, any two arrows of a given path contribute the same vertex of~$V_{\bar Q}$, so~$V_{\bar Q}$ is in bijection with the set of maximal paths in~$\bar Q\blossom$.
+
+Let~$v\in V_{\bar Q}$.  If~$v$ corresponds to a finite maximal path of~$\bar Q\blossom$, then the situation around~$v$ is as follows:
+\pierreguy{Picture No. 1 here.}
+
+If~$v$ corresponds to an infinite maximal path, then the situation around~$v$ is as follows:
+\pierreguy{Picture No. 2 here.}
+
+In both cases, we see that~$v$ is enclosed in a polygon of~$\dissection_{\bar Q}\dual$.  This shows that~$\dissection_{\bar Q}\dual$ is a cellular dissection of~$\surface(\bar Q)$.
+Dually, one shows that~$\dissection_{\bar Q}$ is also a cellular dissection.
+
+Moreover, by construction, each edge of~$\dissection_{\bar Q}$ which is not on the boundary of~$\surface(\bar Q)$ crosses exactly one edge of~$\dissection_{\bar Q}\dual$, and vice versa.
+This shows that~$\dissection_{\bar Q}$ and~$\dissection_{\bar Q}\dual$ aare dual to each other.
 \end{proof}
@@
 \end{theorem}
+\pierreguy{How much detail for a proof? Or is it clear?}
 
@@
 \pierreguy{Should we prove this?}
-\pierreguy{Add picture.}
+\pierreguy{Add picture No.3.}
 \end{remark}

### 2018-07-04 draft/accordionComplexSurfaces.tex
figures accordions and slaloms

--- 2018-07-04 draft/accordionComplexSurfaces.tex
@@
 
+\begin{figure}[t]
+	\capstart
+	\centerline{\includegraphics[scale=.7]{accordions}}
+	\caption{Some accordions.}
+	\label{fig:accordions}
+\end{figure}
+
 \begin{remark}
@@
 \end{definition}
+
+\begin{figure}[t]
+	\capstart
+	\centerline{\includegraphics[scale=.7]{slaloms}}
+	\caption{Some slaloms.}
+	\label{fig:slaloms}
+\end{figure}
 
@@
 
-This construction is illustrated on \fref{fig:examplesSurfaces}.
+This construction is illustrated on \fref{fig:surfaces}.
 %
@@
 	\capstart
-	\centerline{\includegraphics[scale=.7]{examplesSurfaces}}
+	\centerline{\includegraphics[scale=.7]{surfaces}}
 	\caption{The surface~$\surface_{\bar Q}$ for the quivers~$\bar Q$ of \fref{fig:quivers}.
@@
 The first two surfaces are disks, the third is a sphere, the fourth is a cylinder, and the fifth is a punctured torus.}
-	\label{fig:examplesSurfaces}
+	\label{fig:surfaces}
 \end{figure}
 
-%\begin{figure}[t]
-%	\capstart
-%	\centerline{\includegraphics[scale=.7]{examplesSurfaces2}}
-%	\caption{The surface~$\surface_{\bar Q}$ for the last two quivers~$\bar Q$ of \fref{fig:quivers}.
-The boundaries of the surfaces are shaded.
-The first surface is a cylinder, the second one is a torus with a hole.}
-%	\label{fig:examplesSurfaces2}
-%\end{figure}
-%
 Definition~\ref{def:surfaceQuiver} constructs an orientable surface~$\surface(\bar Q)$ with boundaries.
-
-\begin{remark}
-We could equivalently construct the surface~$\surface_{\bar Q}$ as follows:
+Note that we could equivalently construct the surface~$\surface_{\bar Q}$ as follows:
 \begin{itemize}
@@
 \end{itemize}
-\end{remark}
-
 The advantage of Definition~\ref{def:surfaceQuiver} is that it automatically endows with two disjoint sets~$V_{\bar Q}$ and~${V_{\bar Q}}\dual$ of marked points and two dual dissections~$\dissection_{\bar Q}$ and~${\dissection_{\bar Q}}\dual$ defined as follows.
@@
 \end{definition}
-
-\begin{proposition}
-\label{prop:dissectionsAreCellular}
-Let~$\bar Q$ be a locally gentle bound quiver.
-Then the dissections~$\dissection_{\bar Q}$ and~$\dissection_{\bar Q}\dual$ are cellular and dual to each other.
-\end{proposition}
-\begin{proof}
-
-\end{proof}
-
-\begin{theorem}
-\label{thm:bijectionLocallyGentleAndSurfaces}
- Up to isomorphism, the constructions of Definitions \ref{def:quiverDualDissections} and \ref{def:surfaceQuiver} are inverse to each other.
- They induce a bijection between the set of isomorphism classes of locally gentle algebras and the set of homeomorphism classes of marked surfaces with a pair of dual cellular dissections.
-\end{theorem}
 
@@
 
+\begin{proposition}
+\label{prop:dualityKoszul2}
+For any gentle bound quiver~$\bar Q$ with Koszul dual~$\bar Q\koszul$, the surfaces~$\surface_{\bar Q}$ and~$\surface_{\bar Q\koszul}$ coincide, but~$\dissection_{\bar Q\koszul} = {\dissection_{\bar Q}}\dual$ and~${\dissection_{\bar Q\koszul}}\dual = \dissection_{\bar Q}$.
+\end{proposition}
+
 \begin{example}[Cambrian paths]
@@
 \end{example}
-
-\begin{proposition}
-\label{prop:dualityKoszul2}
-For any gentle bound quiver~$\bar Q$ with Koszul dual~$\bar Q\koszul$, the surfaces~$\surface_{\bar Q}$ and~$\surface_{\bar Q\koszul}$ coincide, but~$\dissection_{\bar Q\koszul} = {\dissection_{\bar Q}}\dual$ and~${\dissection_{\bar Q\koszul}}\dual = \dissection_{\bar Q}$.
-\end{proposition}
 

### 2018-07-04 draft/accordionComplexSurfaces.tex
Dissections are cellular and dual to each other.

--- 2018-07-04 draft/accordionComplexSurfaces.tex
@@
 
-It is not hard to see that~$\bar Q_{\dissection} = (Q_{\dissection}, I_{\dissection})$ is a locally gentle bound quiver,
-and that the vertices corresponding to boundary edges of~$\dissection$ are blossoming vertices.
-\pierreguy{Be more precise on the ``are blossiming vertices'' part of this sentence.}
+\begin{lemma}
+\label{lemm:quiverOfDissectionIsLocallyGentle}
+The bound quiver~$\bar Q_{\dissection} = (Q_{\dissection}, I_{\dissection})$ is a locally gentle bound quiver
+\end{lemma}
+\begin{proof}
+Each arc~$a$ has two endpoints, and at each endpoint there is at most one arc coming immediately after~$a$ in the clockwise order, and at most one coming immediately before.
+Thus, in~$Q_{\dissection}$, there are at most two arrows leaving~$a$ and at most two arriving in~$a$.
+Among these arrows, those arising from the same endpoint of~$a$ will be composable, and those arising from different endpoints will yield relations.
+Thus $\bar Q_{\dissection}$ is locally gentle.
+\end{proof}
+
+%Moreover, the vertices corresponding to boundary edges of~$\dissection$ are blossoming vertices.
+%\pierreguy{Be more precise on the ``are blossiming vertices'' part of this sentence.}
 \vincent{Explain also that we can get the blossoming quiver using the blossom points.}
@@
 
-\subsection{The surface of a quiver}
+\subsection{The surface of a locally gentle bound quiver}
 

### 2018-07-04 draft/accordionComplexSurfaces.tex
figures dissections

--- 2018-07-04 draft/accordionComplexSurfaces.tex
@@
 
-\begin{example}
-Two examples of dual cellular dissections on a surface are represented in \fref{fig:dissections}.
-\end{example}
+Some examples of dual cellular dissections on different surfaces are represented in \fref{fig:dissections}.
+
+\begin{figure}[t]
+	\capstart
+	\centerline{\includegraphics[scale=.7]{dissections}}
+	\caption{Some pairs of dual dissections on different surfaces.}
+	\label{fig:dissections}
+\end{figure}
 
@@
 The first two surfaces are disks, the third is a sphere, the fourth is a cylinder, and the fifth is a punctured torus.}
-	\label{fig:examplesSurfaces}
+	\label{fig:surfaces}
 \end{figure}

### 2018-07-04 draft/accordionComplexSurfaces.tex
figures quivers of dissections
Curves and walks.

@@
 \newcommand{\bottom}{\mathrm{bot}} % bottom
+\newcommand{\walk}{\operatorname{\omega}} % walk (of a curve)
 
@@
 \newcommandx{\RNCC}[1][1={\dissection, \dissection\dual}]{\mathcal{C}_{\mathrm{nc}}(#1)} % non-crossing complex
+\newcommand{\curveof}{\operatorname{\gamma}} % curve (of a walk)
 
@@
 
-Some examples of dual cellular dissections on different surfaces are represented in \fref{fig:dissections}.
-
-\begin{figure}[t]
-	\capstart
-	\centerline{\includegraphics[scale=.7]{dissections}}
-	\caption{Some pairs of dual dissections on different surfaces.}
-	\label{fig:dissections}
-\end{figure}
+\begin{example}
+Two examples of dual cellular dissections on a surface are represented in \fref{fig:dissections}.
+\end{example}
 
@@
 
-\subsection{Non-crossing and non-kissing complexe coincide}
+\subsection{Non-crossing and non-kissing complexes coincide}
+
+Let~$\bar Q$ be a locally gentle bound quiver.
+
+\begin{definition}
+\label{def:curveOfAWalk}
+Let~$\omega$ be a (possibly infinite) walk on~$\bar Q$. 
+Define a curve~$\curveof(\omega)$
+\end{definition}
 

### 2018-07-04 draft/accordionComplexSurfaces.tex

@@
 
+\begin{figure}[t]
+	\capstart
+	\centerline{\includegraphics[scale=.7]{quiversDissections1}}
+	\centerline{\includegraphics[scale=.7]{quiversDissections2}}
+	\caption{The quivers associated to the dissections of \fref{fig:dissections}. As stated in Proposition~\ref{prop:dualityKoszul1}, dual dissections give rise to koszul dual quivers.}
+	\label{fig:quiversDissections}
+\end{figure}
+
 %Moreover, the vertices corresponding to boundary edges of~$\dissection$ are blossoming vertices.
@@
 \vincent{Explain also that we can get the blossoming quiver using the blossom points.}
-
-\begin{example}
- An example on the annulus...
-\end{example}
 

### 2018-07-04 draft/accordionComplexSurfaces.tex
4.0 technical lemma

--- 2018-07-04 draft/accordionComplexSurfaces.tex
@@
 
-\begin{figure}[t]
-	\capstart
-	\centerline{\includegraphics[scale=.7]{accordions}}
-	\caption{Some accordions.}
-	\label{fig:accordions}
-\end{figure}
-
 \begin{remark}
@@
 \end{definition}
-
-\begin{figure}[t]
-	\capstart
-	\centerline{\includegraphics[scale=.7]{slaloms}}
-	\caption{Some slaloms.}
-	\label{fig:slaloms}
-\end{figure}
 
@@
 
-\begin{lemma}
-\label{lemm:quiverOfDissectionIsLocallyGentle}
-The bound quiver~$\bar Q_{\dissection} = (Q_{\dissection}, I_{\dissection})$ is a locally gentle bound quiver
-\end{lemma}
-\begin{proof}
-Each arc~$a$ has two endpoints, and at each endpoint there is at most one arc coming immediately after~$a$ in the clockwise order, and at most one coming immediately before.
-Thus, in~$Q_{\dissection}$, there are at most two arrows leaving~$a$ and at most two arriving in~$a$.
-Among these arrows, those arising from the same endpoint of~$a$ will be composable, and those arising from different endpoints will yield relations.
-Thus $\bar Q_{\dissection}$ is locally gentle.
-\end{proof}
-
-%Moreover, the vertices corresponding to boundary edges of~$\dissection$ are blossoming vertices.
-%\pierreguy{Be more precise on the ``are blossiming vertices'' part of this sentence.}
+It is not hard to see that~$\bar Q_{\dissection} = (Q_{\dissection}, I_{\dissection})$ is a locally gentle bound quiver,
+and that the vertices corresponding to boundary edges of~$\dissection$ are blossoming vertices.
+\pierreguy{Be more precise on the ``are blossiming vertices'' part of this sentence.}
 \vincent{Explain also that we can get the blossoming quiver using the blossom points.}
@@
 
-\subsection{The surface of a locally gentle bound quiver}
+\subsection{The surface of a quiver}
 
@@
 
-This construction is illustrated on \fref{fig:surfaces}.
+This construction is illustrated on \fref{fig:examplesSurfaces}.
 %
@@
 	\capstart
-	\centerline{\includegraphics[scale=.7]{surfaces}}
+	\centerline{\includegraphics[scale=.7]{examplesSurfaces}}
 	\caption{The surface~$\surface_{\bar Q}$ for the quivers~$\bar Q$ of \fref{fig:quivers}.
@@
 The first two surfaces are disks, the third is a sphere, the fourth is a cylinder, and the fifth is a punctured torus.}
-	\label{fig:surfaces}
+	\label{fig:examplesSurfaces}
 \end{figure}
@@
 Definition~\ref{def:surfaceQuiver} constructs an orientable surface~$\surface(\bar Q)$ with boundaries.
-
-\begin{remark}
-We could equivalently construct the surface~$\surface_{\bar Q}$ as follows:
+Note that we could equivalently construct the surface~$\surface_{\bar Q}$ as follows:
 \begin{itemize}
@@
 \end{definition}
-
-\begin{proposition}
-\label{prop:dissectionsAreCellular}
-Let~$\bar Q$ be a locally gentle bound quiver.
-Then the dissections~$\dissection_{\bar Q}$ and~$\dissection_{\bar Q}\dual$ are cellular and dual to each other.
-\end{proposition}
-\begin{proof}
-In the construction of~$\surface(\bar Q)$, if two arrows~$\alpha$ and~$\beta$ of~$\bar Q \blossom$ are such that~$t(\alpha) = s(\beta)$ and~$\alpha\beta\in I\blossom$, then the vertices~$v(\alpha)$ and~$v(\beta)$ are identified on the surface.
-Thus, any two arrows of a given path contribute the same vertex of~$V_{\bar Q}$, so~$V_{\bar Q}$ is in bijection with the set of maximal paths in~$\bar Q\blossom$.
-
-Let~$v\in V_{\bar Q}$.  If~$v$ corresponds to a finite maximal path of~$\bar Q\blossom$, then the situation around~$v$ is as follows:
-\pierreguy{Picture No. 1 here.}
-
-If~$v$ corresponds to an infinite maximal path, then the situation around~$v$ is as follows:
-\pierreguy{Picture No. 2 here.}
-
-In both cases, we see that~$v$ is enclosed in a polygon of~$\dissection_{\bar Q}\dual$.  This shows that~$\dissection_{\bar Q}\dual$ is a cellular dissection of~$\surface(\bar Q)$.
-Dually, one shows that~$\dissection_{\bar Q}$ is also a cellular dissection.
-
-Moreover, by construction, each edge of~$\dissection_{\bar Q}$ which is not on the boundary of~$\surface(\bar Q)$ crosses exactly one edge of~$\dissection_{\bar Q}\dual$, and vice versa.
-This shows that~$\dissection_{\bar Q}$ and~$\dissection_{\bar Q}\dual$ aare dual to each other.
-\end{proof}
-
-\begin{theorem}
-\label{thm:bijectionLocallyGentleAndSurfaces}
- Up to isomorphism, the constructions of Definitions \ref{def:quiverDualDissections} and \ref{def:surfaceQuiver} are inverse to each other.
- They induce a bijection between the set of isomorphism classes of locally gentle algebras and the set of homeomorphism classes of marked surfaces with a pair of dual cellular dissections.
-\end{theorem}
-\pierreguy{How much detail for a proof? Or is it clear?}
 
@@
 
-\begin{proposition}
-\label{prop:dualityKoszul2}
-For any gentle bound quiver~$\bar Q$ with Koszul dual~$\bar Q\koszul$, the surfaces~$\surface_{\bar Q}$ and~$\surface_{\bar Q\koszul}$ coincide, but~$\dissection_{\bar Q\koszul} = {\dissection_{\bar Q}}\dual$ and~${\dissection_{\bar Q\koszul}}\dual = \dissection_{\bar Q}$.
-\end{proposition}
-
 \begin{example}[Cambrian paths]
@@
 
+\begin{proposition}
+\label{prop:dualityKoszul2}
+For any gentle bound quiver~$\bar Q$ with Koszul dual~$\bar Q\koszul$, the surfaces~$\surface_{\bar Q}$ and~$\surface_{\bar Q\koszul}$ coincide, but~$\dissection_{\bar Q\koszul} = {\dissection_{\bar Q}}\dual$ and~${\dissection_{\bar Q\koszul}}\dual = \dissection_{\bar Q}$.
+\end{proposition}
+
 \subsection{Non-crossing and non-kissing complexe coincide}
@@
 \section{Properties of the non-crossing and non-kissing complexes}
+
+\subsection{Some technical properties of non-kissing walks}
+
+\begin{lemma}
+ Let~$\omega$ be a non-kissing walk that contains an oriented cycle~$c$.
+ Then~$\omega$ is of the form~$\sigma c^\infty$ or~$c^\infty\sigma$, for some substring~$\sigma$.
+\end{lemma}
+
+\begin{proof}
+ Let~$c=\alpha_1\cdots\alpha_r$ be an oriented cycle in some walk~$\omega$.
+ Assume that~$\omega$ is not of form~$\sigma c^\infty$ or~$c^\infty\sigma$.
+ Then, up to cyclic reordering of the arrows in~$c$, it contains a substring of the form~$\beta^\pm c^l \alpha_1\cdots\alpha_j\gamma^\pm$, for some arrows~$\beta,\gamma$ not in~$c$, some~$l\geq 1$, and some~$j<r$.
+ Since~$\bar Q$ is locally gentle, this substring is~$\beta^{-1} c^l \alpha_1\cdots\alpha_j\gamma^{-1}$.
+ Hence, the walk~$\omega$ contains the two substrings~$\beta^{-1}\alpha_1\cdots\alpha_j\alpha_{j+1}$ and~$\alpha_r\alpha_1\cdots\alpha_j\gamma^{-1}$, and thus self-kisses.
+\end{proof}
 
@@
 \pierreguy{Should we prove this?}
-\pierreguy{Add picture No.3.}
+\pierreguy{Add picture.}
 \end{remark}
@@
  This element is the maximal element of~$F_\alpha$.
-
 \end{proof}
@@
  {\it Combinatorial proof.}
- \pierreguy{Yann has the combinatorial proof.}
 

### 2018-07-04 draft/accordionComplexSurfaces.tex

--- 2018-07-04 draft/accordionComplexSurfaces.tex
@@
 \newcommand{\bottom}{\mathrm{bot}} % bottom
-\newcommand{\walk}{\operatorname{\omega}} % walk (of a curve)
 
@@
 \newcommandx{\RNCC}[1][1={\dissection, \dissection\dual}]{\mathcal{C}_{\mathrm{nc}}(#1)} % non-crossing complex
-\newcommand{\curveof}{\operatorname{\gamma}} % curve (of a walk)
 
@@
 
-\subsection{Non-crossing and non-kissing complexes coincide}
-
-Let~$\bar Q$ be a locally gentle bound quiver.
-
-\begin{definition}
-\label{def:curveOfAWalk}
-Let~$\omega$ be a (possibly infinite) walk on~$\bar Q$. 
-Define a curve~$\curveof(\omega)$
-\end{definition}
+\subsection{Non-crossing and non-kissing complexe coincide}
 

### 2018-07-04 draft/accordionComplexSurfaces.tex
figures PG

--- 2018-07-04 draft/accordionComplexSurfaces.tex
@@
 	\centerline{\includegraphics[scale=.7]{quiversDissections1}}
+	\medskip
 	\centerline{\includegraphics[scale=.7]{quiversDissections2}}
@@
 Let~$v\in V_{\bar Q}$.  If~$v$ corresponds to a finite maximal path of~$\bar Q\blossom$, then the situation around~$v$ is as follows:
-\pierreguy{Picture No. 1 here.}
+
+\begin{figure}[h]
+	\capstart
+	\centerline{\includegraphics[scale=.7]{halfStar} \qquad \includegraphics[scale=.7]{star}}
+	\caption{.}
+	\label{fig:stars}
+\end{figure}
 
 If~$v$ corresponds to an infinite maximal path, then the situation around~$v$ is as follows:
-\pierreguy{Picture No. 2 here.}
+
+\vincent{Change formulation here to have the pictures on the same line.}
 
@@
 \pierreguy{Should we prove this?}
-\pierreguy{Add picture No.3.}
+%
+\begin{figure}[h]
+	\capstart
+	\centerline{\includegraphics[scale=.7]{orderCurves}}
+	\caption{The order~$\prec_\alpha$ is given by the order in which the curve cross the angle corresponding to~$\alpha$.}
+	\label{fig:orderCurves}
+\end{figure}
 \end{remark}

### 2018-07-04 draft/accordionComplexSurfaces.tex
Walks are exactly accordions.

@@
 
-\begin{figure}[t]
-	\capstart
-	\centerline{\includegraphics[scale=.7]{quiversDissections1}}
-	\medskip
-	\centerline{\includegraphics[scale=.7]{quiversDissections2}}
-	\caption{The quivers associated to the dissections of \fref{fig:dissections}. As stated in Proposition~\ref{prop:dualityKoszul1}, dual dissections give rise to koszul dual quivers.}
-	\label{fig:quiversDissections}
-\end{figure}
-
 %Moreover, the vertices corresponding to boundary edges of~$\dissection$ are blossoming vertices.
@@
 \vincent{Explain also that we can get the blossoming quiver using the blossom points.}
+
+\begin{example}
+ An example on the annulus...
+\end{example}
 
@@
 Let~$v\in V_{\bar Q}$.  If~$v$ corresponds to a finite maximal path of~$\bar Q\blossom$, then the situation around~$v$ is as follows:
-
-\begin{figure}[h]
-	\capstart
-	\centerline{\includegraphics[scale=.7]{halfStar} \qquad \includegraphics[scale=.7]{star}}
-	\caption{.}
-	\label{fig:stars}
-\end{figure}
+\pierreguy{Picture No. 1 here.}
 
 If~$v$ corresponds to an infinite maximal path, then the situation around~$v$ is as follows:
-
-\vincent{Change formulation here to have the pictures on the same line.}
+\pierreguy{Picture No. 2 here.}
 
@@
 
-\subsection{Non-crossing and non-kissing complexe coincide}
+\subsection{Non-crossing and non-kissing complexes coincide}
+
+Let~$\bar Q$ be a locally gentle bound quiver.
+For each arc of the dissection~$\dissection_{\bar Q}$ on~$\surface(\bar Q)$, we fix a point on the interior of this arc, which we call its ``middle point''.
+To each walk on~$\bar Q$, we will now associate a~$\dissection_{\bar Q}$-accordion.
+
+\begin{definition}
+\label{def:curveOfAnArrow}
+For any arrow~$\alpha$ on $\bar Q\blossom$, let~$\curveof(\alpha)$ be the curve on~$\surface(\bar Q)$ which goes from the middle point of the arc corresponding to $s(\alpha)$ to the middle point of the arc corresponding to $t(\alpha)$ by following the angle corresponding to~$\alpha$.
+Define~$\curveof(\alpha^{-1})$ to be~$\curveof(\alpha)^{-1}$.
+\end{definition}
+
+\begin{definition}
+\label{def:curveOfAWalk}
+Let~$\omega = \ldots \alpha_{i-1}^{\varepsilon_{i-1}}\alpha_{i}^{\varepsilon_i}\alpha_{i+1}^{\varepsilon_{i+1}}$ be a (possibly infinite) walk on~$\bar Q$. 
+Define the curve~$\curveof(\omega)$ to be the concatenation of the curves~$\curveof(\alpha_i{\varepsilon_{i}})$ of Definition \ref{def:curveOfAnArrow}.
+\end{definition}
+
+In practice, we will represent~$\curveof(\omega)$ by a curve which intersects itself only transversaly, and such that if it circles infinitely around a puncture, then it spirals towards it.
 
 \begin{lemma}
+\label{lemm:curveOfAWalkIsAccordion}
+Let~$\omega$ be a walk on~$\bar Q$.  Then~$\curveof(\omega)$ is a~$\dissection_{\bar Q}$-accordion.
+\end{lemma}
+\begin{proof}
+ This is because~$\curveof(\omega)$ follows angles in~$\dissection_{\bar Q}$ by definition.
+\end{proof}
+
+\begin{lemma}
+\label{lemm:accordionsAreCurvesOfWalks}
+Let~$\gamma$ be a~$\dissection_{\bar Q}$-accordion.  There exists a unique undirected walk~$\walk(\gamma)$ such that we have~$\curveof(\walk(\gamma)) = \gamma$.
+\end{lemma}
+\begin{proof}
+ \pierreguy{TO DO}
+\end{proof}
+
+The above implies the following.
+
+\begin{proposition}
 \label{lem:walks=arcs}
-Walks of~$\bar Q$ are precisely~$\dissection$-accordions.
-\end{lemma}
+The maps~$\curveof(-)$ and~$\walk(-)$ induce mutually inverse bijections between the set of undirected walks on~$\bar Q$ and the set of~$\dissection_{\bar Q}$-accordions on~$\surface(\bar Q)$.
+\end{proposition}
 
@@
 \pierreguy{Should we prove this?}
-%
-\begin{figure}[h]
-	\capstart
-	\centerline{\includegraphics[scale=.7]{orderCurves}}
-	\caption{The order~$\prec_\alpha$ is given by the order in which the curve cross the angle corresponding to~$\alpha$.}
-	\label{fig:orderCurves}
-\end{figure}
+\pierreguy{Add picture No.3.}
 \end{remark}

### 2018-07-04 draft/accordionComplexSurfaces.tex

@@
 
+\begin{figure}[t]
+	\capstart
+	\centerline{\includegraphics[scale=.7]{quiversDissections1}}
+	\medskip
+	\centerline{\includegraphics[scale=.7]{quiversDissections2}}
+	\caption{The quivers associated to the dissections of \fref{fig:dissections}. As stated in Proposition~\ref{prop:dualityKoszul1}, dual dissections give rise to koszul dual quivers.}
+	\label{fig:quiversDissections}
+\end{figure}
+
 %Moreover, the vertices corresponding to boundary edges of~$\dissection$ are blossoming vertices.
@@
 
+\subsection{Some technical properties of non-kissing walks}
+
+\begin{lemma}
+ Let~$\omega$ be a non-kissing walk that contains an oriented cycle~$c$.
+ Then~$\omega$ is of the form~$\sigma c^\infty$ or~$c^\infty\sigma$, for some substring~$\sigma$.
+\end{lemma}
+
+\begin{proof}
+ Let~$c=\alpha_1\cdots\alpha_r$ be an oriented cycle in some walk~$\omega$.
+ Assume that~$\omega$ is not of form~$\sigma c^\infty$ or~$c^\infty\sigma$.
+ Then, up to cyclic reordering of the arrows in~$c$, it contains a substring of the form~$\beta^\pm c^l \alpha_1\cdots\alpha_j\gamma^\pm$, for some arrows~$\beta,\gamma$ not in~$c$, some~$l\geq 1$, and some~$j<r$.
+ Since~$\bar Q$ is locally gentle, this substring is~$\beta^{-1} c^l \alpha_1\cdots\alpha_j\gamma^{-1}$.
+ Hence, the walk~$\omega$ contains the two substrings~$\beta^{-1}\alpha_1\cdots\alpha_j\alpha_{j+1}$ and~$\alpha_r\alpha_1\cdots\alpha_j\gamma^{-1}$, and thus self-kisses.
+\end{proof}
+
 \subsection{The countercurrent order}

### 2018-07-04 draft/accordionComplexSurfaces.tex
Added caption of a figure.

@@
 
-Let~$v\in V_{\bar Q}$.  If~$v$ corresponds to a finite maximal path of~$\bar Q\blossom$, then the situation around~$v$ is as follows:
+Let~$v\in V_{\bar Q}$. The situation around~$v$ is as follows, depending on whether~$v$ corresponds to a finite or infinite maximal path of~$\bar Q\blossom$,:
 
@@
 	\centerline{\includegraphics[scale=.7]{halfStar} \qquad \includegraphics[scale=.7]{star}}
-	\caption{.}
+	\caption{The situation around~$v$ (green vertex). On the left,~$v$ corresponds to a finite maximal path of~$\bar Q$, while on the right,~$v$ corresponds to an infinite one.}
 	\label{fig:stars}
@@
 
-If~$v$ corresponds to an infinite maximal path, then the situation around~$v$ is as follows:
-
-\vincent{Change formulation here to have the pictures on the same line.}
-
 In both cases, we see that~$v$ is enclosed in a polygon of~$\dissection_{\bar Q}\dual$.  This shows that~$\dissection_{\bar Q}\dual$ is a cellular dissection of~$\surface(\bar Q)$.
@@
 Moreover, by construction, each edge of~$\dissection_{\bar Q}$ which is not on the boundary of~$\surface(\bar Q)$ crosses exactly one edge of~$\dissection_{\bar Q}\dual$, and vice versa.
-This shows that~$\dissection_{\bar Q}$ and~$\dissection_{\bar Q}\dual$ aare dual to each other.
+This shows that~$\dissection_{\bar Q}$ and~$\dissection_{\bar Q}\dual$ are dual to each other.
 \end{proof}
@@
 	\centerline{\includegraphics[scale=.7]{orderCurves}}
-	\caption{The order~$\prec_\alpha$ is given by the order in which the curve cross the angle corresponding to~$\alpha$.}
+	\caption{The order~$\prec_\alpha$ is given by the order in which the curves cross the angle corresponding to~$\alpha$.}
 	\label{fig:orderCurves}

### 2018-07-04 draft/accordionComplexSurfaces.tex
existence of distinguished arrows

--- 2018-07-04 draft/accordionComplexSurfaces.tex
@@
 \begin{proof}
-\vincent{Todo. I have the impression here that we need cellular embeddings.}
+\yann{I have to merge two cases}
 Let~$\alpha$ be a~$\dissection$-accordion.
@@
 	\centerline{\includegraphics[scale=.7]{quiversDissections1}}
-	\medskip
 	\centerline{\includegraphics[scale=.7]{quiversDissections2}}
@@
 
-\subsection{Non-crossing and non-kissing complexes coincide}
-
-Let~$\bar Q$ be a locally gentle bound quiver.
-For each arc of the dissection~$\dissection_{\bar Q}$ on~$\surface(\bar Q)$, we fix a point on the interior of this arc, which we call its ``middle point''.
-To each walk on~$\bar Q$, we will now associate a~$\dissection_{\bar Q}$-accordion.
-
-\begin{definition}
-\label{def:curveOfAnArrow}
-For any arrow~$\alpha$ on $\bar Q\blossom$, let~$\curveof(\alpha)$ be the curve on~$\surface(\bar Q)$ which goes from the middle point of the arc corresponding to $s(\alpha)$ to the middle point of the arc corresponding to $t(\alpha)$ by following the angle corresponding to~$\alpha$.
-Define~$\curveof(\alpha^{-1})$ to be~$\curveof(\alpha)^{-1}$.
-\end{definition}
-
-\begin{definition}
-\label{def:curveOfAWalk}
-Let~$\omega = \ldots \alpha_{i-1}^{\varepsilon_{i-1}}\alpha_{i}^{\varepsilon_i}\alpha_{i+1}^{\varepsilon_{i+1}}$ be a (possibly infinite) walk on~$\bar Q$. 
-Define the curve~$\curveof(\omega)$ to be the concatenation of the curves~$\curveof(\alpha_i{\varepsilon_{i}})$ of Definition \ref{def:curveOfAnArrow}.
-\end{definition}
-
-In practice, we will represent~$\curveof(\omega)$ by a curve which intersects itself only transversaly, and such that if it circles infinitely around a puncture, then it spirals towards it.
+\subsection{Non-crossing and non-kissing complexe coincide}
 
 \begin{lemma}
-\label{lemm:curveOfAWalkIsAccordion}
-Let~$\omega$ be a walk on~$\bar Q$.  Then~$\curveof(\omega)$ is a~$\dissection_{\bar Q}$-accordion.
+\label{lem:walks=arcs}
+Walks of~$\bar Q$ are precisely~$\dissection$-accordions.
 \end{lemma}
-\begin{proof}
- This is because~$\curveof(\omega)$ follows angles in~$\dissection_{\bar Q}$ by definition.
-\end{proof}
-
-\begin{lemma}
-\label{lemm:accordionsAreCurvesOfWalks}
-Let~$\gamma$ be a~$\dissection_{\bar Q}$-accordion.  There exists a unique undirected walk~$\walk(\gamma)$ such that we have~$\curveof(\walk(\gamma)) = \gamma$.
-\end{lemma}
-\begin{proof}
- \pierreguy{TO DO}
-\end{proof}
-
-The above implies the following.
-
-\begin{proposition}
-\label{lem:walks=arcs}
-The maps~$\curveof(-)$ and~$\walk(-)$ induce mutually inverse bijections between the set of undirected walks on~$\bar Q$ and the set of~$\dissection_{\bar Q}$-accordions on~$\surface(\bar Q)$.
-\end{proposition}
 
@@
 
-\begin{lemma}
+\begin{lemma}\label{lem:nkCycles}
  Let~$\omega$ be a non-kissing walk that contains an oriented cycle~$c$.
@@
  This element is the maximal element of~$F_\alpha$.
+\end{proof}
+
+\begin{lemma}\label{lem:ExistenceOfDistinguishedArrows}
+Let~$F$ be a finite face of~$\NKC$, let~$\omega$ be a walk in~$F$, and let~$\alpha$ be an arrow on~$\omega$.
+Assume that~$\omega$ is not an infinite straight walk.
+Then, there is an arrow~$\beta$ oriented in the same direction as~$\alpha$ in~$\omega$ such that~$\omega$ (marked at~$\beta$) is maximal in~$F$ for~$\prec_\beta$.
+\end{lemma}
+
+\begin{proof}
+Let~$\omega$ be a walk in some non-kissing facet~$F$, marked at an arrow~$\alpha$.
+If~$\omega$ is not maximal at~$\alpha$, there is a walk~$\mu_0\in F$ such that~$\omega\prec_\alpha \mu_0$.
+Let~$\sigma_0$ be the maximal common substring of~$\omega$ and~$\mu_0$ containing~$\alpha$.
+Since~$\omega$ and $\mu_0$ are different, they split at some endpoint of~$\sigma_0$.
+At this endpoint, the arrow~$\beta$ of~$\omega$ not in~$\sigma_0$ points in the same direction as~$\alpha$ since~$\omega \prec_\alpha \mu_0$.
+If~$\omega$ is maximal at~$\beta$ in~$F$, we are done.
+Otherwise, let~$\mu_1$ be maximal in~$F$ for~$\prec_\beta$.
+Since~$\mu_1$ does not kiss with~$\mu_0$, and~$\omega\prec_\beta\mu_1$,~$\mu_1$ contains~$\sigma_0$.
+Let~$\sigma_1$ be the maximal common substring of~$\omega$ and~$\mu_1$ containing~$\beta$.
+As remarked above,~$\sigma_1$ contains~$\sigma_0$.
+Since~$\omega$ is not maximal at~$\beta$, the walks~$\omega$ and~$\mu_1$ split at some endpoint of~$\sigma_1$.
+By Lemma\ref{lem:nkCycles}, Iterating this procedure eventually stops ($\mu_j=\omega$ for some $j$) unless~$\omega$ is an infinite straight walk.
 \end{proof}

### 2018-07-04 draft/accordionComplexSurfaces.tex

--- 2018-07-04 draft/accordionComplexSurfaces.tex
@@
 
+\begin{lemma}\label{lem:ExistenceOfDistinguishedArrows}
+Let~$F$ be a finite face of~$\NKC$, let~$\omega$ be a walk in~$F$, and let~$\alpha$ be an arrow on~$\omega$.
+Assume that~$\omega$ is not an infinite straight walk.
+Then, there is an arrow~$\beta$ oriented in the same direction as~$\alpha$ in~$\omega$ such that~$\omega$ (marked at~$\beta$) is maximal in~$F$ for~$\prec_\beta$.
+\end{lemma}
+
+\begin{proof}
+Let~$\omega$ be a walk in some non-kissing facet~$F$, marked at an arrow~$\alpha$.
+If~$\omega$ is not maximal at~$\alpha$, there is a walk~$\mu_0\in F$ such that~$\omega\prec_\alpha \mu_0$.
+Let~$\sigma_0$ be the maximal common substring of~$\omega$ and~$\mu_0$ containing~$\alpha$.
+Since~$\omega$ and $\mu_0$ are different, they split at some endpoint of~$\sigma_0$.
+At this endpoint, the arrow~$\beta$ of~$\omega$ not in~$\sigma_0$ points in the same direction as~$\alpha$ since~$\omega \prec_\alpha \mu_0$.
+If~$\omega$ is maximal at~$\beta$ in~$F$, we are done.
+Otherwise, let~$\mu_1$ be maximal in~$F$ for~$\prec_\beta$.
+Since~$\mu_1$ does not kiss with~$\mu_0$, and~$\omega\prec_\beta\mu_1$,~$\mu_1$ contains~$\sigma_0$.
+Let~$\sigma_1$ be the maximal common substring of~$\omega$ and~$\mu_1$ containing~$\beta$.
+As remarked above,~$\sigma_1$ contains~$\sigma_0$.
+Since~$\omega$ is not maximal at~$\beta$, the walks~$\omega$ and~$\mu_1$ split at some endpoint of~$\sigma_1$.
+By Lemma\ref{lem:nkCycles}, Iterating this procedure eventually stops ($\mu_j=\omega$ for some $j$) unless~$\omega$ is an infinite straight walk.
+\end{proof}
+
 \begin{lemma}

### 2018-07-04 draft/accordionComplexSurfaces.tex
relabel theorems according to sections
Minor changes.

--- 2018-07-04 draft/accordionComplexSurfaces.tex
@@
 \label{def:curveOfAWalk}
-Let~$\omega = \ldots \alpha_{i-1}^{\varepsilon_{i-1}}\alpha_{i}^{\varepsilon_i}\alpha_{i+1}^{\varepsilon_{i+1}}$ be a (possibly infinite) walk on~$\bar Q$. 
+Let~$\omega = \ldots \alpha_{i-1}^{\varepsilon_{i-1}}\alpha_{i}^{\varepsilon_i}\alpha_{i+1}^{\varepsilon_{i+1}} \ldots$ be a (possibly infinite) walk on~$\bar Q$. 
 Define the curve~$\curveof(\omega)$ to be the concatenation of the curves~$\curveof(\alpha_i{\varepsilon_{i}})$ of Definition \ref{def:curveOfAnArrow}.
@@
 \begin{proposition}
-\label{lem:walks=arcs}
+\label{prop:walks=arcs}
 The maps~$\curveof(-)$ and~$\walk(-)$ induce mutually inverse bijections between the set of undirected walks on~$\bar Q$ and the set of~$\dissection_{\bar Q}$-accordions on~$\surface(\bar Q)$.

### 2018-07-04 draft/accordionComplexSurfaces.tex
reverse problem merge

@@
 % theorems
-\newtheorem{theorem}{Theorem}[]
+\newtheorem{theorem}{Theorem}[section]
 \newtheorem{corollary}[theorem]{Corollary}
@@
 \label{def:curveOfAWalk}
-Let~$\omega = \ldots \alpha_{i-1}^{\varepsilon_{i-1}}\alpha_{i}^{\varepsilon_i}\alpha_{i+1}^{\varepsilon_{i+1}} \ldots$ be a (possibly infinite) walk on~$\bar Q$. 
+Let~$\omega = \ldots \alpha_{i-1}^{\varepsilon_{i-1}}\alpha_{i}^{\varepsilon_i}\alpha_{i+1}^{\varepsilon_{i+1}}$ be a (possibly infinite) walk on~$\bar Q$. 
 Define the curve~$\curveof(\omega)$ to be the concatenation of the curves~$\curveof(\alpha_i{\varepsilon_{i}})$ of Definition \ref{def:curveOfAnArrow}.
@@
 \begin{proposition}
-\label{prop:walks=arcs}
+\label{lem:walks=arcs}
 The maps~$\curveof(-)$ and~$\walk(-)$ induce mutually inverse bijections between the set of undirected walks on~$\bar Q$ and the set of~$\dissection_{\bar Q}$-accordions on~$\surface(\bar Q)$.
@@
 
+\vincent{Orient the flip graph. Connection to the lattice of torsion classes?}
+
 \section{Representation-theoretic interpretation}

### 2018-07-04 draft/accordionComplexSurfaces.tex
C_nk is pure.

--- 2018-07-04 draft/accordionComplexSurfaces.tex
@@
 \begin{corollary}
-The non-kissing complex~$\RNKC$ is thin and is a pseudomanifold without boundary.
+The non-kissing complex~$\RNKC$ is pure of dimension~$|Q_0|$.  Moreover, it is thin and is a pseudomanifold without boundary.
 \end{corollary}
+
+\vincent{Orient the flip graph. Connection to the lattice of torsion classes?}
 

### 2018-07-04 draft/accordionComplexSurfaces.tex
nk-facets are finite

--- 2018-07-04 draft/accordionComplexSurfaces.tex
@@
 % theorems
-\newtheorem{theorem}{Theorem}[section]
+\newtheorem{theorem}{Theorem}[]
 \newtheorem{corollary}[theorem]{Corollary}
@@
 \begin{proof}
- We provide two proofs of the lemma.  One is combinatorial and applies to~$\NKC$, and the other is geometric and applies to~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$.
-
- {\it Combinatorial proof.}
+ We provide two proofs of the lemma.
+ One is combinatorial and applies to~$\NKC$, and the other is geometric and applies to~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$.
+
+ {\it Combinatorial proof.} By Lemma~\ref{lem:ExistenceOfDistinguishedArrows}, the number of walks in a finite face of~$\NKC$ is bounded by~$|Q_1\blossom|+s_\infty$, where~$s_\infty$ is the number of infinite straight walks (i.e.
+the number of oriented cycles in~$Q$).
 
@@
 
-\vincent{Orient the flip graph. Connection to the lattice of torsion classes?}
-
 \section{Representation-theoretic interpretation}

### 2018-07-04 draft/accordionComplexSurfaces.tex
cleaning captions figures

--- 2018-07-04 draft/accordionComplexSurfaces.tex
@@
 
-\begin{theorem}[{\cite[Cor.~2.27 \& Cor.~2.33]{PaluPilaudPlamondon}}\footnote{As the main objective of~\cite[Cor.~2.27 \& Cor.~2.33]{PaluPilaudPlamondon} was a combinatorial model for support $\tau$-tilting complexes of gentle algebras, we did require that the ideal~$I$ was admissible so that~$kQ/I$ was finite dimensional.
-However, the same proof directly applies in the generality of this paper.}]
-The reduced non-kissing complex~$\RNKC$ is pure of dimension~$|Q_0|$ (\ie all maximal faces have dimension~$|Q_0|$) and thin (\ie all codimension~$1$ faces are contained in exactly two facets).
-\end{theorem}
-
-This result follows from the existence of flips in non-kissing facets.
-This operation is illustrated in \fref{fig:flip}.
-
-\begin{figure}[t]
-	\capstart
-	\centerline{\includegraphics[scale=1]{flip}}
-	\caption{A schematic representation of flips in the non-kissing complex.
-The flip exchanges the walk~$\omega = \rho \sigma \tau$ in the facet~$F$ (left) with the walk~$\omega' = \rho' \sigma \tau'$ in the facet~$F'$ (middle), using the walks~$\mu = \rho' \sigma \tau$ and~$\nu = \rho \sigma \tau'$.
-The walk~$\omega'$ kisses~$\omega$ but no other walk of~$F$ (right).}
-	\label{fig:flip}
-\end{figure}
+%\begin{theorem}[{\cite[Cor.~2.27 \& Cor.~2.33]{PaluPilaudPlamondon}}]
+%The reduced non-kissing complex~$\RNKC$ is pure of dimension~$|Q_0|$ (\ie all maximal faces have dimension~$|Q_0|$) and thin (\ie all codimension~$1$ faces are contained in exactly two facets).
+%\end{theorem}
+%
+%This result follows from the existence of flips in non-kissing facets.
+%This operation is illustrated in \fref{fig:flip}.
 
@@
 
+Some examples of dual cellular dissections on different surfaces are represented in \fref{fig:dissections}.
+%
+\begin{figure}[t]
+	\capstart
+	\centerline{\includegraphics[scale=.7]{dissections}}
+	\caption{Some pairs~$(\dissection, \dissection\dual)$ of dual dissections on different surfaces.
+The boundaries of the surfaces are shaded, and the glue symbols indicate how to identify some edges to get the desired surfaces.
+The first two surfaces are disks, the third is a sphere, the fourth is a cylinder, and the fifth is a punctured torus.
+The dissection~$\dissection$ is in green while its dual dissection~$\dissection\dual$ is in red.}
+	\label{fig:dissections}
+\end{figure}
+%
 Note that contrarily to the usual conventions, the dual vertex~$f\dual$ of a face~$f$ of~$\dissection$ is not always in the interior of the face~$f$.
@@
 
-Some examples of dual cellular dissections on different surfaces are represented in \fref{fig:dissections}.
-
-\begin{figure}[t]
-	\capstart
-	\centerline{\includegraphics[scale=.7]{dissections}}
-	\caption{Some pairs of dual dissections on different surfaces.}
-	\label{fig:dissections}
-\end{figure}
-
-\begin{definition}
-Interior points, blossom points.
-Half-arcs.
-
-We consider a set~$B$ of points on the boundary of the surface~$\surface$ such that~$B$ and~$M \cup M\dual$ alternate along the boundary of~$\surface$.
+\begin{definition}
+%Interior points, blossom points.
+%Half-arcs.
+We consider a set~$B$ of points on the boundary of the surface~$\surface$ such that~$B$ and~$V \cup V\dual$ alternate along the boundary of~$\surface$.
 The points of~$B$ are called the \defn{blossom points}.
+See \eg Figures~\ref{fig:accordions} and~\ref{fig:slaloms}.
 \end{definition}
@@
 We say that a $B$-curve is \defn{external} if it is homotopic to a boundary arc of~$\surface \ssm B$, and \defn{internal} otherwise.
-Note that no $B$-curve can cross an external $B$-arc.
+Note that no $B$-curve can cross an external $B$-curve.
 Consider two dual cellular dissections~$\dissection$ and~$\dissection\dual$ of~$\bar\surface$.
@@
 
+\fref{fig:accordions} illustrates some $\dissection$-accordions for the dissections~$\dissection$ of \fref{fig:dissections}.
+
 \begin{figure}[t]
@@
 	\centerline{\includegraphics[scale=.7]{accordions}}
-	\caption{Some accordions.}
+	\caption{Some $\dissection$-accordions (in blue) for the dissections~$\dissection$ of \fref{fig:dissections} (in green).}
 	\label{fig:accordions}
@@
 
+\fref{fig:slaloms} illustrates some $\dissection\dual$-slaloms for the dual dissections~$\dissection\dual$ of \fref{fig:dissections}.
+
 \begin{figure}[t]
@@
 	\centerline{\includegraphics[scale=.7]{slaloms}}
-	\caption{Some slaloms.}
+	\caption{Some $\dissection\dual$-slaloms (in blue) for the dual dissections~$\dissection\dual$ of \fref{fig:dissections} (in red).}
 	\label{fig:slaloms}
@@
 %\end{remark}
+
+The following statement is illustrated by Figures~\ref{fig:accordions} and~\ref{fig:slaloms}.
 
@@
 
-\begin{remark}
-To clearly visualize Proposition~\ref{prop:accordionsSlaloms}, we follow the convention to draw the $\dissection$-accordions (resp.~$\dissection\dual$-slaloms) so that they intersect the arcs of~$\dissection$ (resp.~of~$\dissection\dual$) only at the intersection points of the arcs of~$\dissection$ with the arcs of~$\dissection\dual$.
-\vincent{That is interior points}
-\end{remark}
+%\begin{remark}
+%To clearly visualize Proposition~\ref{prop:accordionsSlaloms}, we follow the convention to draw the $\dissection$-accordions (resp.~$\dissection\dual$-slaloms) so that they intersect the arcs of~$\dissection$ (resp.~of~$\dissection\dual$) only at the intersection points of the arcs of~$\dissection$ with the arcs of~$\dissection\dual$.
+%\end{remark}
 
@@
 Interestingly, via the correspondence between pairs of dual cellular dissections and locally gentle bound quivers, the duality between the dissections~$\dissection$ and~$\dissection\dual$ translates to the Koszul duality between the locally gentle algebras of~$\bar Q$ and~$\bar Q\dual$.
-
-\vincent{This section is just sketched at the moment.}
 
@@
 	\centerline{\includegraphics[scale=.7]{surfaces}}
-	\caption{The surface~$\surface_{\bar Q}$ for the quivers~$\bar Q$ of \fref{fig:quivers}.
-The boundaries of the surfaces are shaded, and the glue symbols indicate how to identify some edges to get the desired surfaces.
-The first two surfaces are disks, the third is a sphere, the fourth is a cylinder, and the fifth is a punctured torus.}
+	\caption{The surface~$\surface_{\bar Q}$ for the quivers~$\bar Q$ of \fref{fig:quivers}.}
 	\label{fig:surfaces}
@@
 \begin{example}[Reversed paths]
-\label{exm:doublePath}
+\label{exm:reversedPath}
 Consider the following family of locally gentle quivers:
@@
 
+\begin{figure}[t]
+	\capstart
+	\centerline{\includegraphics[scale=1]{flip}}
+	\caption{A schematic representation of flips in the non-kissing complex.
+The flip exchanges the walk~$\omega = \rho \sigma \tau$ in the facet~$F$ (left) with the walk~$\omega' = \rho' \sigma \tau'$ in the facet~$F'$ (middle), using the walks~$\mu = \rho' \sigma \tau$ and~$\nu = \rho \sigma \tau'$.
+The walk~$\omega'$ kisses~$\omega$ but no other walk of~$F$ (right).}
+	\label{fig:flip}
+\end{figure}
+
 \begin{corollary}
-The non-kissing complex~$\RNKC$ is pure of dimension~$|Q_0|$.  Moreover, it is thin and is a pseudomanifold without boundary.
+The non-kissing complex~$\RNKC$ is thin and is a pseudomanifold without boundary.
 \end{corollary}

### 2018-07-04 draft/accordionComplexSurfaces.tex

@@
 \begin{corollary}
-The non-kissing complex~$\RNKC$ is thin and is a pseudomanifold without boundary.
+The non-kissing complex~$\RNKC$ is pure of dimension~$|Q_0|$.  Moreover, it is thin and is a pseudomanifold without boundary.
 \end{corollary}

### 2018-07-04 draft/accordionComplexSurfaces.tex
minor updates

--- 2018-07-04 draft/accordionComplexSurfaces.tex
@@
 Let~$\omega = \ldots \alpha_{i-1}^{\varepsilon_{i-1}}\alpha_{i}^{\varepsilon_i}\alpha_{i+1}^{\varepsilon_{i+1}} \ldots$ be a (possibly infinite) walk on~$\bar Q$. 
-Define the curve~$\curveof(\omega)$ to be the concatenation of the curves~$\curveof(\alpha_i{\varepsilon_{i}})$ of Definition \ref{def:curveOfAnArrow}.
+Define the curve~$\curveof(\omega)$ to be the concatenation of the curves~$\curveof(\alpha_i^{\varepsilon_{i}})$ of Definition \ref{def:curveOfAnArrow}.
 \end{definition}
@@
  \pierreguy{Vincent has the proof of this proposition.}
+ The first two dots in this proposition are proven in Lemma~\ref{lem:ExistenceOfDistinguishedArrows}.
 \end{proof}

### 2018-07-04 draft/accordionComplexSurfaces.tex
cleaning captions figures
Non-kissing = non-crossing (except for figures).

@@
 \label{lem:nonKissing=nonCrossing}
-Non-kissing walks = non-crossing $\dissection$-accordion curves.
+Let~$\omega_1$ and~$\omega_2$ be walks on~$\bar Q$.
+Then~$\omega_1$ and~$\omega_2$ are non-kissing if and only if the~$\dissection_{\bar Q}$-accordions~$\curveof(\omega_1)$ and~$\curveof(\omega_2)$ are non-crossing on~$\surface(\bar Q)$.
 \end{lemma}
+\begin{proof}
+ \pierreguy{Picture No.4}
+\end{proof}
 
@@
 \end{theorem}
+\begin{proof}
+ The first point is a consequence of Proposition \ref{prop:walks=arcs}, Lemma \ref{lem:nonKissing=nonCrossing} and Proposition \ref{prop:accordionsSlaloms}.
+ The second point is a consequence of Theorem \ref{thm:bijectionLocallyGentleAndSurfaces} and of the first point.
+\end{proof}
 

### 2018-07-04 draft/accordionComplexSurfaces.tex
typos

@@
 \usepackage{todonotes}
-\newcommand{\yann}[1]{\textbf{#1 --- Y.}} % {\todo[color=red!30]{#1 \\ \hfill --- Y.}}
+\newcommand{\yann}[1]{\todo[color=red!30]{#1 --- Y.}}
 \newcommand{\vincent}[1]{\todo[color=blue!30]{#1 \\ \hfill --- V.}}
@@
 
-\begin{lemma}
-\label{lemm:quiverOfDissectionIsLocallyGentle}
-The bound quiver~$\bar Q_{\dissection} = (Q_{\dissection}, I_{\dissection})$ is a locally gentle bound quiver
-\end{lemma}
-\begin{proof}
-Each arc~$a$ has two endpoints, and at each endpoint there is at most one arc coming immediately after~$a$ in the clockwise order, and at most one coming immediately before.
-Thus, in~$Q_{\dissection}$, there are at most two arrows leaving~$a$ and at most two arriving in~$a$.
-Among these arrows, those arising from the same endpoint of~$a$ will be composable, and those arising from different endpoints will yield relations.
-Thus $\bar Q_{\dissection}$ is locally gentle.
-\end{proof}
+%Moreover, the vertices corresponding to boundary edges of~$\dissection$ are blossoming vertices.
+%\pierreguy{Be more precise on the ``are blossiming vertices'' part of this sentence.}
+\vincent{Explain also that we can get the blossoming quiver using the blossom points.}
+
+\fref{fig:quiversDissections} illustrates this construction for the dissections of \fref{fig:dissections}.
 
@@
 
-%Moreover, the vertices corresponding to boundary edges of~$\dissection$ are blossoming vertices.
-%\pierreguy{Be more precise on the ``are blossiming vertices'' part of this sentence.}
-\vincent{Explain also that we can get the blossoming quiver using the blossom points.}
+\begin{lemma}
+\label{lemm:quiverOfDissectionIsLocallyGentle}
+The bound quiver~$\bar Q_{\dissection} = (Q_{\dissection}, I_{\dissection})$ is a locally gentle bound quiver
+\end{lemma}
+\begin{proof}
+Each arc~$a$ has two endpoints, and at each endpoint there is at most one arc coming immediately after~$a$ in the clockwise order, and at most one coming immediately before.
+Thus, in~$Q_{\dissection}$, there are at most two arrows leaving~$a$ and at most two arriving in~$a$.
+Among these arrows, those arising from the same endpoint of~$a$ will be composable, and those arising from different endpoints will yield relations.
+Thus $\bar Q_{\dissection}$ is locally gentle.
+\end{proof}
 
@@
 
-This construction is illustrated on \fref{fig:surfaces}.
-%
+Definition~\ref{def:surfaceQuiver} constructs an orientable surface~$\surface(\bar Q)$ with boundaries.
+\fref{fig:surfaces} illustrates this construction for the quivers of \fref{fig:quivers}.
+
 \begin{figure}[t]
@@
 \end{figure}
-
-Definition~\ref{def:surfaceQuiver} constructs an orientable surface~$\surface(\bar Q)$ with boundaries.
 
@@
 Since~$\omega$ is not maximal at~$\beta$, the walks~$\omega$ and~$\mu_1$ split at some endpoint of~$\sigma_1$.
-By Lemma\ref{lem:nkCycles}, Iterating this procedure eventually stops ($\mu_j=\omega$ for some $j$) unless~$\omega$ is an infinite straight walk.
+By Lemma~\ref{lem:nkCycles}, iterating this procedure eventually stops ($\mu_j=\omega$ for some $j$) unless~$\omega$ is an infinite straight walk.
 \end{proof}

### 2018-07-04 draft/accordionComplexSurfaces.tex
small reorganisation
example double paths

--- 2018-07-04 draft/accordionComplexSurfaces.tex
@@
 
-Definition~\ref{def:surfaceQuiver} constructs an orientable surface~$\surface(\bar Q)$ with boundaries.
-
 \begin{remark}
@@
 \begin{remark}
+\label{rem:propertiesSurface}
 The following observations are useful for the computation of examples.
@@
 \item The dissection~$\dissection_{\bar Q}$ has one $\ell$-cell for each straight walk of length~$\ell$ in~$\bar Q\koszul$.
+\item A similar remark holds dually for~${V_{\bar Q}}\dual$ and~${\dissection_{\bar Q}}\dual$.
 \item The number of boundary components of~$\surface(\bar Q)$ can be computed as follows.
-      There are two natural perfect matchings whose vertices are the blossoming vertices of~$\bar Q$: one is obtained by putting an edge between two vertices~$v_1$ and~$v_2$ whenever there is a straight walk of~$\bar Q$ relating them, and the other is obtained by doing the same for~$\bar Q \koszul$.
+      There are two natural perfect matchings whose vertices are the blossoming vertices of~$\bar Q$: one is obtained by joining the endpoints of each finite straight walk of~$\bar Q$, and the other is obtained similarly from~$\bar Q \koszul$.
       Let~$G$ be the superposition of these two perfect matchings.
-      Then the number of boundary components of~$\surface(\bar Q)$ is the number of connected components of~$G$.
+      Then the number~$b$ of boundary components of~$\surface(\bar Q)$ is the number of connected components of~$G$.
 \item The genus of the surface~$\surface(\bar Q)$ is
@@
 \end{itemize}
-A similar remark holds dually for~${V_{\bar Q}}\dual$ and~${\dissection_{\bar Q}}\dual$.
 \end{remark}
@@
 \label{exm:doublePath}
-Consider the family ``double paths'' quivers indicated in \fref{fig:doublePathsQuivers}.
+Consider the family of ``double paths quivers'' indicated in \fref{fig:doublePathsQuivers}.
 
@@
 	\capstart
-	\centerline{\includegraphics[scale=.4]{doublePathsQuivers}}
+	\centerline{\includegraphics[scale=.45]{doublePathsQuivers}}
 	\caption{The double paths quivers with~$1, 2, 3, 4$ vertices.}
@@
 \end{figure}
+
+The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}) look like~\raisebox{-.1cm}{\includegraphics[scale=.3]{doublePathsPModd}} when~$|Q_0|$ is odd and~\raisebox{-.1cm}{\includegraphics[scale=.3]{doublePathsPMeven}} when~$|Q_0|$ is even.
+Therefore, the corresponding surfaces have $1$ boundary component and genus~$(|Q_0|-1)/2$ when~$|Q_0|$ is odd, and $2$ boundary components and genus~$|Q_0|/2$ when~$|Q_0|$ is even.
 

### 2018-07-04 draft/accordionComplexSurfaces.tex

@@
 Since~$\omega$ is not maximal at~$\beta$, the walks~$\omega$ and~$\mu_1$ split at some endpoint of~$\sigma_1$.
-By Lemma\ref{lem:nkCycles}, Iterating this procedure eventually stops ($\mu_j=\omega$ for some $j$) unless~$\omega$ is an infinite straight walk.
-\end{proof}
+By Lemma~\ref{lem:nkCycles}, iterating this procedure eventually stops ($\mu_j=\omega$ for some $j$) unless~$\omega$ is an infinite straight walk.
+\end{proof}
+
+\subsection{Purity of the non-crossing and non-kissing complexes}
+
+A simplicial complex is \defn{pure of dimension~$d$} if all its maximal faces have dimension~$d$.
+The aim of this section is to prove the following purity result.
+
+\begin{proposition}
+\label{prop:purity}
+ The the non-kissing complex~$\NKC$ and the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$ are pure of dimension~$3|Q_0| - |Q_1|$.
+\end{proposition}
+
+Note that Proposition \ref{prop:purity} was proved for~$\NKC$ in \cite[Corollary 2.27]{PaluPilaudPlamondon} in the case where~$kQ/I$ is finite-dimensional.
+Note also that, by Theorem \ref{thm:complexesCoincide} above,~$\NKC$ and~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$ coincide, so it suffices to prove the Proposition for one of them.
 
@@
 \end{proof}
-
-\subsection{Purity of the non-crossing and non-kissing complexes}
-
-A simplicial complex is \defn{pure of dimension~$d$} if all its maximal faces have dimension~$d$.
-The aim of this section is to prove the following purity result.
-
-\begin{proposition}
-\label{prop:purity}
- The the non-kissing complex~$\NKC$ and the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$ are pure of dimension~$3|Q_0| - |Q_1|$.
-\end{proposition}
-
-Note that Proposition \ref{prop:purity} was proved for~$\NKC$ in \cite[Corollary 2.27]{PaluPilaudPlamondon} in the case where~$kQ/I$ is finite-dimensional.
-Note also that, by Theorem \ref{thm:complexesCoincide} above,~$\NKC$ and~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$ coincide, so it suffices to prove the Proposition for one of them.
 

### 2018-07-04 draft/accordionComplexSurfaces.tex
Burned section 5.
Fixed minor things.

@@
 
-\vincent{Should we introduce Koszul duality here and say what it does on quivers?}
-
 \subsection{Strings and walks}
@@
 \textbf{All throughout the paper, all dissections are considered cellular.}
-The case of non-cellular dissections will be discussed in Section~\ref{sec:nonCellularDissections}.
 \end{convention}
@@
 
-\section{Representation-theoretic interpretation}
-
-\subsection{$\dissection$-accordions and string modules}
-
-\subsection{$\dissection\dual$-slaloms and minimal projective presentations}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-07-04 draft/accordionComplexSurfaces.tex
figure order

--- 2018-07-04 draft/accordionComplexSurfaces.tex
@@
 We say that~$\omega$ \defn{kisses}~$\omega'$ if~$\Sigma_\top(\omega) \cap \Sigma_\bottom(\omega') \ne \varnothing$.
-See \fref{fig:kissingCrossing}.
+See \fref{fig:kissing}.
 % \ie if there exist a common substring~$\sigma \in \strings^\pm(\bar Q)$ of~$\omega$ and~$\omega'$ such that the arrows of~$\omega$ incident to~$\sigma$ are both outgoing while the arrows of~$\omega'$ incident to~$\sigma$ are both incoming.
@@
 	\capstart
-	\centerline{\includegraphics[scale=1]{kissingCrossing}}
-	\caption{A schematic representation of two kissing walks (left) and two crossing walks~(right): $\omega$~kisses~$\omega'$ (left) while~$\mu$~crosses~$\nu$ (right).
-For the crossing walks, we have~$\mu \prec_\gamma \nu$ while~$\nu \prec_\delta \mu$.}
-	\label{fig:kissingCrossing}
+	\centerline{\includegraphics[scale=1]{kissing}}
+	\caption{A schematic representation of two kissing walks: $\omega$~kisses~$\omega'$.}
+	\label{fig:kissing}
 \end{figure}
@@
 \begin{remark}
-A quick disclaimer about accordion complexes and slalom complexes of arbitrary dissections.
+A quick disclaimer about accordion complexes and slalom complexes of arbitrary cellular dissections.
 As stated in Proposition~\ref{prop:conditionsDualDissections}, a dissection~$\dissection$ with a face containing more than one boundary edge does not admit a dual cellular dissection~$\dissection\dual$.
@@
 See \cite[Prop.~2.4]{MannevillePilaud-accordion} for a detailed statement in the case of the disk.
-\vincent{A retravailler}
 \end{remark}
@@
 	\capstart
-	\centerline{\includegraphics[scale=.7]{orderCurves}}
-	\caption{The order~$\prec_\alpha$ is given by the order in which the curves cross the angle corresponding to~$\alpha$.}
+	\centerline{\includegraphics[scale=1]{orderCurves}}
+	\caption{The order~$\prec_\alpha$ on marked walks is the order in which the corresponding curves cross the angle corresponding to~$\alpha$.}
 	\label{fig:orderCurves}
@@
 \end{remark}
+
+%\begin{figure}
+%	\capstart
+%	\centerline{\includegraphics[scale=1]{kissing}}
+%	\caption{A schematic representation of two kissing walks (left) and two crossing walks~(right): $\omega$~kisses~$\omega'$ (left) while~$\mu$~crosses~$\nu$ (right).
+For the crossing walks, we have~$\mu \prec_\gamma \nu$ while~$\nu \prec_\delta \mu$.}
+%	\label{fig:kissing}
+%\end{figure}
 

### 2018-07-04 draft/accordionComplexSurfaces.tex
Introduction.

@@
 
-\section{Non-kissing complex}
+\section{Introduction}
+
+BLAH BLAH BLAH
+
+The two main objects of our study will be locally gentle algebras and dissections of surfaces.
+Our first main result is that these two classes of objects are essentially the same.
+
+\begin{theorem*}[\ref{thm:bijectionLocallyGentleAndSurfaces}]
+ There is an explicit bijection between the set of isomorphism classes of locally gentle bound quivers and the set of homeomorphism classes of oriented marked surfaces with boundary and a pair of dual cellular dissections.
+\end{theorem*}
+
+On the algebraic side, we extend the study of walks from the gentle to the locally gentle case, and define a notion of compatibility called non-kissing (see Section \ref{sec:nonKissingComplex}).
+On the geometric side, we extend the study of dissections, accordions and slaloms from the case of the disk to the case of an arbitrary surface, and define a notion of compatibility called non-crossing (see Section \ref{sec:accordionSlalomNonCrossingComplexes}).
+The combinatorial information contained in these notions is encoded in simplicial complexes: the non-kissing complex~$\NKC$ and the non-crossing complex~$\NCC$.
+
+\begin{theorem*}[\ref{thm:complexesCoincide}]
+ The complexes~$\NKC$ and~$\NCC$ are isomorphic.
+\end{theorem*}
+
+Finally, we show that these complexes have very nice combinatorial properties.
+
+\begin{theorem*}[\ref{prop:purity} and \ref{coro:thin}]
+ The complexes~$\NKC$ and~$\NCC$ are pure and thin.  Their dimension is computed, and mutation is explicitly described.
+\end{theorem*}
+
+Consequences on the representation theory of locally gentle algebras will be investigated in a future project.
+
+\section{Non-kissing complex}\label{sec:nonKissingComplex}
 
@@
 
-\section{Accordion complex, slalom complex, and non-crossing complex}
+\section{Accordion complex, slalom complex, and non-crossing complex}\label{sec:accordionSlalomNonCrossingComplexes}
 
@@
 \begin{corollary}
+\label{coro:thin}
 The non-kissing complex~$\RNKC$ is pure of dimension~$|Q_0|$.  Moreover, it is thin and is a pseudomanifold without boundary.

### 2018-07-04 draft/accordionComplexSurfaces.tex
example reversed paths

--- 2018-07-04 draft/accordionComplexSurfaces.tex
@@
 \item A similar remark holds dually for~${V_{\bar Q}}\dual$ and~${\dissection_{\bar Q}}\dual$.
-\item The number of boundary components of~$\surface(\bar Q)$ can be computed as follows.
+\item The number~$p$ of punctures of~$\surface(\bar Q)$ is the number of infinite straight walks in~$\bar Q$ and in~$\bar Q\koszul$.
+\item The number~$b$ of boundary components of~$\surface(\bar Q)$ can be computed as follows.
       There are two natural perfect matchings whose vertices are the blossoming vertices of~$\bar Q$: one is obtained by joining the endpoints of each finite straight walk of~$\bar Q$, and the other is obtained similarly from~$\bar Q \koszul$.
@@
       \[
-       g = \frac{|Q_1| - |Q_0| - b + 2}{2},
+       g = \frac{|Q_1| - |Q_0| - b - p + 2}{2},
       \]
-      where~$b$ is the number of boundary components (see above for a way to compute~$b$).
-      Indeed, ~$g=\frac{2-\chi(\surface(\bar Q))}{2}$, where~$\chi(\surface(\bar Q))$ is the Euler characteristic of~$\surface(\bar Q)$.
-      The dissection~$\dissection$ provides a cellular decomposition of~$\surface(\bar Q)$ on which we fill the boundary components with disks.  
+      where~$b$ is the number of boundary components (see above for a way to compute~$b$) and~$p$ the number of punctures (\ie infinite straight walks in~$\bar Q$ and in~$\bar Q\koszul$).
+      Indeed, $2g = 2-\chi(\surface(\bar Q))$, where~$\chi(\surface(\bar Q))$ is the Euler characteristic of~$\surface(\bar Q)$.
+      The dissection~$\dissection$ provides a cellular decomposition of~$\surface(\bar Q)$ on which we fill the boundary components and the punctures with disks.  
       The number of faces of this cellular decomposition is~$b$, its number of edges is~$|Q_0|$ and its number of vertices is the number of finite straight walks in~$\bar Q$, which is equal to~$2|Q_0| - |Q_1|$.
@@
 
-\begin{example}[Reversed paths]
+\begin{example}
 \label{exm:reversedPath}
-Consider the following family of locally gentle quivers:
-\vincent{TODO double path}
+Consider the family of ``reversed paths quivers'' indicated in \fref{fig:reversedPathsQuivers}.
+
+\begin{figure}[h]
+	\capstart
+	\centerline{\includegraphics[scale=.45]{reversedPathsQuivers}}
+	\caption{The reversed paths quivers with~$1, 2, 3, 4$ vertices.}
+	\label{fig:reversedPathsQuivers}
+\end{figure}
+
+The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}) look like~\raisebox{-.1cm}{\includegraphics[scale=.3]{reversedPathsPM}}.
+Moreover, $\bar Q$ has no infinite straight walk, while~$\bar Q\koszul$ has~$|Q_0|-1$ infinite straight walks.
+Therefore, the corresponding surfaces have $1$ boundary component and genus~$0$.
+The first few corresponding surfaces are represented in \fref{fig:reversedPathsSurfaces}.
+
+\begin{figure}[h]
+	\capstart
+	\centerline{\includegraphics[scale=.4]{reversedPathsSurfaces}}
+	\caption{The surface~$\surface_{\bar Q}$ for the reversed paths with~$1, 2, 3, 4$ vertices.}
+	\label{fig:reversedPathsSurfaces}
+\end{figure}
+
 \end{example}
 
-\begin{example}[Double paths]
+\begin{example}
 \label{exm:doublePath}
@@
 The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}) look like~\raisebox{-.1cm}{\includegraphics[scale=.3]{doublePathsPModd}} when~$|Q_0|$ is odd and~\raisebox{-.1cm}{\includegraphics[scale=.3]{doublePathsPMeven}} when~$|Q_0|$ is even.
-Therefore, the corresponding surfaces have $1$ boundary component and genus~$(|Q_0|-1)/2$ when~$|Q_0|$ is odd, and $2$ boundary components and genus~$|Q_0|/2$ when~$|Q_0|$ is even.
+Moreover, $\bar Q$ and~$\bar Q\koszul$ have no infinite straight walks.
+Therefore, the corresponding surfaces have no punctures and
+\begin{itemize}
+\item $1$ boundary component and genus~$(|Q_0|-1)/2$ when~$|Q_0|$ is odd, and 
+\item $2$ boundary components and genus~$|Q_0|/2$ when~$|Q_0|$ is even.
+\end{itemize}
+The first few corresponding surfaces are represented in \fref{fig:doublePathsSurfaces}.
 
@@
 
+\vincent{Add a description and a schematic representation of the flip in the accordion complex and in the slalom complex.}
+
 \begin{corollary}

### 2018-07-04 draft/accordionComplexSurfaces.tex
Introduction bis.

@@
 \section{Introduction}
-
-BLAH BLAH BLAH
-
-The two main objects of our study will be locally gentle algebras and dissections of surfaces.
+The aim of this paper is to prove that two combinatorial objects, called the \emph{non-kissing complex} and the \emph{non-crossing complex}, are isomorphic.
+Both complexes appeared in different works in specific cases: the non-kissing complex of a grid appeared in \cite{McConville}, while the non-crossing complex of a disk appeared in \cite{GarverMcConville}.
+It was shown in \cite{PaluPilaudPlamondon} that these complexes are special cases of a more general simplicial complex, defined for any gentle algebra (see also \cite{}).
+
+In order to unify these two objects, we are lead to introduce two generalizations.
+On the algebraic side, the non-kissing complex is extended from the class of gentle algebras to that of locally gentle algebras (which are an infinite-dimensional version of gentle algebras).
+On the geometric side, we construct the non-crossing complex of an arbitrary oriented punctured surface endowed with a pair of dual dissections.
+
+The two main objects of our study will thus be locally gentle algebras and dissections of surfaces.
 Our first main result is that these two classes of objects are essentially the same.
@@
 \begin{theorem*}[\ref{thm:bijectionLocallyGentleAndSurfaces}]
- There is an explicit bijection between the set of isomorphism classes of locally gentle bound quivers and the set of homeomorphism classes of oriented marked surfaces with boundary and a pair of dual cellular dissections.
+ There is an explicit bijection between the set of isomorphism classes of locally gentle bound quivers and the set of homeomorphism classes of oriented punctured marked surfaces with boundary and a pair of dual cellular dissections.
 \end{theorem*}
@@
 Consequences on the representation theory of locally gentle algebras will be investigated in a future project.
+
+Gentle algebras were...
+
+Dissections algebras were...
+
+Algebras and dissections have lived together before... (mention clusters)
 

### 2018-07-04 draft/accordionComplexSurfaces.tex
Acknowledgements.

@@
 Both complexes appeared in different works in specific cases: the non-kissing complex of a grid appeared in \cite{McConville}, while the non-crossing complex of a disk appeared in \cite{GarverMcConville}.
-It was shown in \cite{PaluPilaudPlamondon} that these complexes are special cases of a more general simplicial complex, defined for any gentle algebra (see also \cite{}).
+It was shown in \cite{PaluPilaudPlamondon} that these complexes are special cases of a more general simplicial complex, defined for any gentle algebra (see also \cite{BrustleDouvilleMousavandThomasYildirim}).
 
@@
 Algebras and dissections have lived together before... (mention clusters)
+
+\section*{Acknowledgements}
+We thank Sibylle Schroll for discussions on geometric models for gentle algebras.
 

### 2018-07-04 draft/accordionComplexSurfaces.tex
Introduction ter.

@@
 
-Finally, we show that these complexes have very nice combinatorial properties.
+Finally, we show in Section \ref{sec:propertiesOfComplexes} that these complexes are combinatorially very well-behaved.
 
@@
 
-\section{Properties of the non-crossing and non-kissing complexes}
+\section{Properties of the non-crossing and non-kissing complexes}\label{sec:propertiesOfComplexes}
 

### 2018-07-04 draft/accordionComplexSurfaces.tex
start example double cycles

--- 2018-07-04 draft/accordionComplexSurfaces.tex
@@
 \section{Introduction}
-The aim of this paper is to prove that two combinatorial objects, called the \emph{non-kissing complex} and the \emph{non-crossing complex}, are isomorphic.
-Both complexes appeared in different works in specific cases: the non-kissing complex of a grid appeared in \cite{McConville}, while the non-crossing complex of a disk appeared in \cite{GarverMcConville}.
-It was shown in \cite{PaluPilaudPlamondon} that these complexes are special cases of a more general simplicial complex, defined for any gentle algebra (see also \cite{}).
-
-In order to unify these two objects, we are lead to introduce two generalizations.
-On the algebraic side, the non-kissing complex is extended from the class of gentle algebras to that of locally gentle algebras (which are an infinite-dimensional version of gentle algebras).
-On the geometric side, we construct the non-crossing complex of an arbitrary oriented punctured surface endowed with a pair of dual dissections.
-
-The two main objects of our study will thus be locally gentle algebras and dissections of surfaces.
+
+BLAH BLAH BLAH
+
+The two main objects of our study will be locally gentle algebras and dissections of surfaces.
 Our first main result is that these two classes of objects are essentially the same.
@@
 \begin{theorem*}[\ref{thm:bijectionLocallyGentleAndSurfaces}]
- There is an explicit bijection between the set of isomorphism classes of locally gentle bound quivers and the set of homeomorphism classes of oriented punctured marked surfaces with boundary and a pair of dual cellular dissections.
+ There is an explicit bijection between the set of isomorphism classes of locally gentle bound quivers and the set of homeomorphism classes of oriented marked surfaces with boundary and a pair of dual cellular dissections.
 \end{theorem*}
@@
 Consequences on the representation theory of locally gentle algebras will be investigated in a future project.
-
-Gentle algebras were...
-
-Dissections algebras were...
-
-Algebras and dissections have lived together before... (mention clusters)
 
@@
 \label{exm:CambrianPath}
+\vincent{TODO: Cambrian paths}
 \end{example}
@@
 \label{exm:reversedPath}
-Consider the family of ``reversed paths quivers'' indicated in \fref{fig:reversedPathsQuivers}.
+Consider the family of \defn{reversed path quivers} indicated in \fref{fig:reversedPathsQuivers}.
 
@@
 	\centerline{\includegraphics[scale=.45]{reversedPathsQuivers}}
-	\caption{The reversed paths quivers with~$1, 2, 3, 4$ vertices.}
+	\caption{The reversed path quivers with~$1, 2, 3, 4$ vertices.}
 	\label{fig:reversedPathsQuivers}
@@
 	\capstart
-	\centerline{\includegraphics[scale=.4]{reversedPathsSurfaces}}
-	\caption{The surface~$\surface_{\bar Q}$ for the reversed paths with~$1, 2, 3, 4$ vertices.}
+	\centerline{\includegraphics[scale=.7]{reversedPathsSurfaces3}}
+	\caption{The surface~$\surface_{\bar Q}$ for the reversed path quivers with~$1, 2, 3$ vertices.}
 	\label{fig:reversedPathsSurfaces}
@@
 \label{exm:doublePath}
-Consider the family of ``double paths quivers'' indicated in \fref{fig:doublePathsQuivers}.
+Consider the family of \defn{double path quivers} indicated in \fref{fig:doublePathsQuivers}.
 
@@
 	\centerline{\includegraphics[scale=.45]{doublePathsQuivers}}
-	\caption{The double paths quivers with~$1, 2, 3, 4$ vertices.}
+	\caption{The double path quivers with~$1, 2, 3, 4$ vertices.}
 	\label{fig:doublePathsQuivers}
@@
 	\centerline{\includegraphics[scale=.7]{doublePathsSurfaces}}
-	\caption{The surface~$\surface_{\bar Q}$ for the double paths with~$1, 2, 3, 4$ vertices.}
+	\caption{The surface~$\surface_{\bar Q}$ for the double path quivers with~$1, 2, 3, 4$ vertices.}
 	\label{fig:doublePathsSurfaces}
@@
 
-\begin{example}[Double cycles]
+\begin{example}
 \label{exm:doubleCycle}
-Consider the following family of locally gentle quivers:
-\vincent{TODO double cycle}
+Consider the family of \defn{double cycle quivers} indicated in \fref{fig:doubleCyclesQuivers}.
+
+\begin{figure}[h]
+	\capstart
+	\centerline{\includegraphics[scale=.45]{doubleCyclesQuivers}}
+	\caption{The double cycle quivers with~$1, 2, 3, 4, 5$ vertices.}
+	\label{fig:doubleCyclesQuivers}
+\end{figure}
+
 \end{example}

### 2018-07-04 draft/accordionComplexSurfaces.tex
Fixed referenced Thm 4.22.
comments to do

@@
 
-Possible titles, depending on what we want to insist on:
-\begin{enumerate}
-\item Accordion / slalom / non-kissing / support $\tau$-tilting complexes all coincide for gentle algebras
-\item Non-kissing and non-crossing complexes for gentle algebras
-\item Combinatorial models for support $\tau$-tilting on gentle algebras: accordion, slalom and non-kissing complexes
-\end{enumerate}
+\yann{Abstract to do.}
 
@@
 Algebras and dissections have lived together before... (mention clusters)
+\pierreguy{Finish introduction.}
 
@@
 \section{Non-kissing complex}\label{sec:nonKissingComplex}
+
+\vincent{Connection.}
 
@@
 \subsection{Strings and walks}
+
+\vincent{Connection.}
 
@@
 \subsection{Non-kissing complex}
+
+\vincent{Connection.}
 
@@
 
+\vincent{Connection.}
+
 \subsection{Dual dissections of a surface}
+
+\vincent{Connection.}
 
@@
 \begin{proof}
-\yann{I have to merge two cases}
+\vincent{Careful: arcs / curves.}
 Let~$\alpha$ be a~$\dissection$-accordion.
@@
 
-Case 4: If~$\alpha$ stays inside a blue cell, then it rolls around a~$\dissection\dual$ puncture.
+Case 4: If~$\alpha$ stays inside a $\dissection$-cell, then it rolls around a~$\dissection\dual$ puncture.
 There is a~$\dissection\dual$-arc~$\beta$ ending in that puncture. When~$\alpha$ crosses~$\beta$, the puncture stays on the same side of~$\alpha$, hence~$\alpha$ is not a~$\dissection\dual$-slalom.
@@
 
+\pierreguy{reference OPS}
+
 \begin{figure}[t]
@@
 We now associate a surface to a locally gentle bound quiver.
+\pierreguy{reference OPS}
 
@@
 
+\vincent{Connection.}
+
 \begin{theorem}
@@
 \end{theorem}
-\pierreguy{How much detail for a proof? Or is it clear?}
 
@@
 
+\vincent{TODO: surfaces double cycles.}
 \end{example}
+
+\pierreguy{Remark on the comparison with the surface of OPS}
 
@@
 \end{lemma}
+
 \begin{proof}
@@
  \pierreguy{TO DO}
+ \vincent{figure}
 \end{proof}
@@
 \end{lemma}
+
 \begin{proof}
  \pierreguy{Picture No.4}
+ \vincent{figure}
 \end{proof}
@@
 \end{theorem}
+
 \begin{proof}
@@
 
+The following definition is illustrated in \fref{fig:orderCurves}.
+
 \begin{definition}
@@
 \end{definition}
-\pierreguy{Add a picture here?}
 
@@
 Then~$\gamma \prec_\alpha \delta$ if~$\gamma$ passes closer to~$v$ than~$\delta$ does.
-\pierreguy{Should we prove this?}
 %
@@
 	\centerline{\includegraphics[scale=1]{orderCurves}}
-	\caption{The order~$\prec_\alpha$ on marked walks is the order in which the corresponding curves cross the angle corresponding to~$\alpha$.}
+	\caption{The order~$\mu \prec_\alpha \nu$ on marked walks is the order in which the corresponding curves~$\curveof(\mu)$ and~$\curveof(\nu)$ cross the angle corresponding to~$\alpha$.}
 	\label{fig:orderCurves}
@@
 
-The following definition from \cite[Definition 2.23]{PaluPilaudPlamondon} extends to the setting locally gentle algebras.
+The following definition from \cite[Definition 2.23]{PaluPilaudPlamondon} extends to the setting of locally gentle algebras.
 
@@
 \begin{proof}
- \pierreguy{Vincent has the proof of this proposition.}
+ \vincent{Vincent has the proof of this proposition.}
  The first two dots in this proposition are proven in Lemma~\ref{lem:ExistenceOfDistinguishedArrows}.
@@
 
-{\it Proof of Proposition \ref{prop:purity}.}
-\pierreguy{TO DO}
+\begin{proof}[Proof of Proposition \ref{prop:purity}.]
+\vincent{TO DO}
+\end{proof}
 
@@
 
+\section{$\b{g}$-, $\b{c}$- and $\b{d}$-vectors}
+
+\vincent{To do on the walks, on the accordions and on the slaloms.}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-07-04 draft/accordionComplexSurfaces.tex
References to OPS, Remark to this effect, and fixed a typo in the computation of the genus of the surface.

@@
 
-\pierreguy{reference OPS}
-
 \begin{figure}[t]
@@
 \end{figure}
+
+The following proposition appears implicitly in \cite{OpperPlamondonSchroll}.
 
@@
 We now associate a surface to a locally gentle bound quiver.
-\pierreguy{reference OPS}
+This construction is directly inspired by the one found in \cite{OpperPlamondonSchroll} (see Remark \ref{rem:comparisonWithOPS} for a comparison of the two constructions).
 
@@
       The dissection~$\dissection$ provides a cellular decomposition of~$\surface(\bar Q)$ on which we fill the boundary components and the punctures with disks.  
-      The number of faces of this cellular decomposition is~$b$, its number of edges is~$|Q_0|$ and its number of vertices is the number of finite straight walks in~$\bar Q$, which is equal to~$2|Q_0| - |Q_1|$.
+      The number of faces of this cellular decomposition is~$b+p$, its number of edges is~$|Q_0|$ and its number of vertices is the number of finite straight walks in~$\bar Q$, which is equal to~$2|Q_0| - |Q_1|$.
       The above formula for~$g$ follows.
@@
 \end{example}
+
+\begin{remark}
+\label{rem:comparisonWithOPS}
+The construction of the surface given in Definition \ref{def:surfaceQuiver} yields the same surface as the one constructed in \cite{OpperPlamondonSchroll}.
+A notable difference is that in \cite{OpperPlamondonSchroll}, only~$\dissection_{\bar Q}$ is given, and~$\dissection_{\bar Q}\dual$ is deduced (it is called the dual lamination).
+Another minor difference is that the construction in \cite{OpperPlamondonSchroll} is written only for gentle algebras, while here it is generalized to locally gentle algebras.
+
+The major difference with \cite{OpperPlamondonSchroll} is the application of the surface of a (locally) gentle algebra: 
+there, it is used as a model for the derived category of the gentle algebra (graded arcs correspond to indecomposable objects in that category),
+while here, it will be used as a model for walks in~$\bar Q$ ($\dissection_{\bar Q}$-accordions will correspond to walks in~$\bar{Q}$, see Proposition \ref{prop:walks=arcs}).
+\end{remark}
 
@@
 \label{thm:complexesCoincide}
+$\phantom{x}$
 \begin{itemize}

### 2018-07-05 draft/accordionComplexSurfaces.tex
abstract

--- 2018-07-04 draft/accordionComplexSurfaces.tex
@@
 \begin{abstract}
-We consider three combinatorial models for the support $\tau$-tilting complex of a locally gentle bound quiver: the accordion complex, the slalom complex, and the non-kissing complex.
-We unify these models in the same picture.
+Starting from a locally gentle bound quiver, we define on the one hand a simplicial complex, called the non-kissing complex.
+On the other hand, we construct a punctured, marked, oriented surface with boundary, endowed with a pair of dual dissections.
+From those geometric data, we define two simplicial complexes: the accordion complex, and the slalom complex, generalising work of A. Garver and T. McConville in the case of a disk.
+We show that all three simplicial complexes are isomorphic.
+We also construct inverse bijections between the set of isomorphism classes of locally gentle bound quivers and the set of homeomorphism classes of punctured, marked, oriented surfaces with boundary, endowed with a pair of dual dissections.
 \end{abstract}
@@
 \maketitle
-
-\yann{Abstract to do.}
 
@@
 %We consider a \defn{bound quiver}~$\bar Q = (Q,I)$, formed by a quiver~$Q$ and an admissible ideal~$I$ of the path algebra~$kQ$, so that the quotient algebra~$kQ/I$ is finite dimensional.
-We consider a \defn{bound quiver}~$\bar Q = (Q,I)$, formed by a quiver~$Q$ and an ideal~$I$ of the path algebra~$kQ$ such that $I$ is generated by linear combinations of paths of length at least two.
+We consider a \defn{bound quiver}~$\bar Q = (Q,I)$, formed by a finite quiver~$Q$ and an ideal~$I$ of the path algebra~$kQ$ such that $I$ is generated by linear combinations of paths of length at least two.
 Note that we \textbf{do not require} that the quotient algebra~$kQ/I$ be finite dimensional.
@@
 The algebra~$kQ/I$ is called a \defn{locally gentle algebra}.
-A \defn{gentle bound quiver} is a locally bound quiver~$\bar Q$ such that the algebra $kQ/I$ is finite-dimensional; the algebra is then called a \defn{gentle algebra}.
+A \defn{gentle bound quiver} is a locally gentle bound quiver~$\bar Q$ such that the algebra $kQ/I$ is finite-dimensional; the algebra is then called a \defn{gentle algebra}.
 \end{definition}

### 2018-07-05 draft/accordionComplexSurfaces.tex
connections between parts

--- 2018-07-04 draft/accordionComplexSurfaces.tex
@@
 
-\vincent{Connection.}
+We first quickly review the definition of the non-kissing complex of a gentle bound quiver following the presentation of~\cite{PaluPilaudPlamondon} and slightly extend it to locally gentle bound quivers.
 
@@
 	\centerline{\includegraphics[scale=.6]{quivers}}
-	\caption{Some locally gentle quivers and their blossoming quivers. Initial vertices are solid and labeled while blossom vertices are hollow, and initial arcs are bold while blossom arcs are thin.}
+	\caption{Some locally gentle quivers (top) and their blossoming quivers (bottom).
+Initial vertices are solid and labeled while blossom vertices are hollow, and initial arcs are bold while blossom arcs are thin.}
 	\label{fig:quivers}
@@
 
-\vincent{Connection.}
+The non-kissing complex is constructed using the combinatorics of strings and walks in the quiver~$\bar Q$, whose definitions are now briefly recalled.
 
@@
 
-\vincent{Connection.}
+We can now define the non-kissing complex of a locally gentle bound quiver following~\cite{PaluPilaudPlamondon}.
+We start with the kissing relation for walks.
 
@@
 We denote by~$\NKWalks(\bar Q)$ the walks on~$\bar Q$ which are not self-kissing and by~$\NKWalks^\pm(\bar Q) \eqdef \set{\{\omega, \omega^{-1}\}}{\omega \in \NKWalks(\bar Q)}$ their undirected version.
-\end{definition}
-
+%
 \begin{figure}
@@
 \end{figure}
+%
+\end{definition}
 
@@
 
-\vincent{Connection.}
+We now temporarily switch topic and present the accordion complex and the slalom complex of a pair of dual dissections of an orientable surface.
+The latter is directly inspired from the case of a disk treated in~\cite{GarverMcConville}, while the former is obtained by duality as was already observed in the case of a disk in~\cite{MannevillePilaud-accordion}.
+In the general case of arbitrary orientable surfaces, the correspondence between accordions and slaloms requires a little more attention and is treated in Section~\ref{subsec:accordionsVSSlaloms}.
 
@@
 
-\vincent{Connection.}
+Before defining accordions and slaloms, we need a strong notion of pairs of dual dissections of an orientable surface.
+We first review classical definitions of curves, arcs and dissections of a surface adapting it to our setting.
 
@@
 
-\subsection{Accordion complex, slalom complex, and non-crossing complex}
+\subsection{Accordion complex and slalom complex}
+
 Let~$\bar\surface = (\surface, V \sqcup V\dual)$ be a surface with two disjoint sets~$V$ and~$V\dual$ of marked points, and let~$B$ be the corresponding blossom points.
@@
 
+\subsection{Accordions versus slaloms and the non-crossing complex}
+\label{subsec:accordionsVSSlaloms}
+
 The following statement is illustrated by Figures~\ref{fig:accordions} and~\ref{fig:slaloms}.
@@
  \item the set of vertices of~$Q_{\dissection}$ is the set or edges of $\dissection$;
- \item there is an arrow from~$a$ to~$b$ for each common endpoint~$v$ of~$a$ and~$b$ such that~$b$ comes immediately after~$a$ in the clockwise order around~$v$;
+ \item there is an arrow from~$a$ to~$b$ for each common endpoint~$v$ of~$a$ and~$b$ such that~$b$ comes immediately after~$a$ in the counterclockwise order around~$v$;
  \item the ideal~$I_{\dissection}$ is generated by the paths of length two in~$Q_{\dissection}$ obtained by composing arrows which correspond to triples of consecutive edges in a face of~$\dissection$.
@@
 
-%Moreover, the vertices corresponding to boundary edges of~$\dissection$ are blossoming vertices.
-%\pierreguy{Be more precise on the ``are blossiming vertices'' part of this sentence.}
-\vincent{Explain also that we can get the blossoming quiver using the blossom points.}
+\begin{remark}
+The blossoming quiver~$\bar Q_\dissection\blossom$ of the quiver~$\bar Q_\dissection$ is obtained with the same procedure by considering additional blossom vertices along the boundary of the surface.
+See \fref{fig:quiversDissections}.
+\end{remark}
 
@@
 
-\vincent{Connection.}
+The following statement immediately follows from the definitions and was probably already observed by the reader on \fref{fig:surfaces}.
 

### 2018-07-05 draft/accordionComplexSurfaces.tex
figures kissing=crossing

@@
 \section{Introduction}
+
 The aim of this paper is to prove that two combinatorial objects, called the \emph{non-kissing complex} and the \emph{non-crossing complex}, are isomorphic.
@@
  \pierreguy{TO DO}
- \vincent{figure}
 \end{proof}
@@
 \begin{proof}
- \pierreguy{Picture No.4}
- \vincent{figure}
+See \fref{fig:kissings} and \fref{fig:kissingVSCrossing}.
+\pierreguy{Complete this proof using the pictures.}
+
+\begin{figure}[h]
+	\capstart
+	\centerline{\includegraphics[scale=1]{kissings}}
+	\caption{Two representations of a pair of kissing walks.}
+	\label{fig:kissings}
+\end{figure}
+
+\begin{figure}[h]
+	\capstart
+	\centerline{\includegraphics[scale=1]{kissingVSCrossing}}
+	\caption{Kissing walks on the quiver~$\bar Q$ correspond to crossing curves on the surface~$\surface_{\bar Q}$.}
+	\label{fig:kissingVSCrossing}
+\end{figure}
+
 \end{proof}
@@
 \subsection{The countercurrent order}
+
 The countercurrent order was introduced in~\cite{McConville} for grids and defined in \cite{PaluPilaudPlamondon} for gentle algebras.

### 2018-07-05 draft/accordionComplexSurfaces.tex
example double cycles

@@
 
-\vincent{TODO: surfaces double cycles.}
+The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}) are empty since there is no blossom vertices.
+Moreover, $\bar Q$ has~$1$ infinite straight walk when~$|Q_0|$ is odd and~$2$ when~$|Q_0|$ is even, and~$\bar Q\koszul$ always has~$2$ infinite straight walks.
+Therefore, the corresponding surfaces have no boundary component and
+\begin{itemize}
+\item $3$ punctures and genus~$(|Q_0|-1)/2$ when~$|Q_0|$ is odd, and 
+\item $4$ punctures and genus~$(|Q_0|-2)/2$ when~$|Q_0|$ is even.
+\end{itemize}
+The first few corresponding surfaces are represented in \fref{fig:doubleCyclesSurfaces}.
+
+\begin{figure}[h]
+	\capstart
+	\centerline{\includegraphics[scale=.7]{doubleCyclesSurfaces}}
+	\caption{The surface~$\surface_{\bar Q}$ for the double cycle quivers with~$3, 4, 5$ vertices.}
+	\label{fig:doubleCyclesSurfaces}
+\end{figure}
+
 \end{example}

### 2018-07-05 draft/accordionComplexSurfaces.tex
proof purity

@@
 \newcommand{\defn}[1]{\textsl{\darkblue #1}} % emphasis of a definition
-\newcommand{\para}[1]{\medskip\noindent\textbf{#1.}} % paragraph
+\newcommand{\para}[1]{\medskip\noindent\textit{#1.}} % paragraph
 \renewcommand{\topfraction}{1} % possibility to have one page of pictures
@@
 We thank Sibylle Schroll for discussions on geometric models for gentle algebras.
+We are also grateful to Salvatore Stella for discussions on accordion complexes of dissections of surfaces.
 
@@
 \end{figure}
+
+\begin{remark}
+\label{rem:sizeBlossomingQuiver}
+Note that the blossoming quiver has~$2|Q_0|-|Q_1|$ incoming blossoms and~$2|Q_0|-|Q_1|$ outgoing blossoms.
+Therefore, it has $|Q_0\blossom| = |Q_0| + 2(2|Q_0|-|Q_1|) = 5|Q_0|-2|Q_1|$ vertices and~$|Q_1\blossom| = |Q_1| + 2(2|Q_0|-|Q_1|) = 4|Q_0|-|Q_1|$ arrows.
+\end{remark}
 
@@
 A quick disclaimer about accordion complexes and slalom complexes of arbitrary cellular dissections.
-As stated in Proposition~\ref{prop:conditionsDualDissections}, a dissection~$\dissection$ with a face containing more than one boundary edge does not admit a dual cellular dissection~$\dissection\dual$.
+As stated in Proposition~\ref{prop:conditionsDualDissections}, a cellular dissection~$\dissection$ with a face containing more than one boundary edge does not admit a dual cellular dissection~$\dissection\dual$.
 This prevents to use the definitions given in this section.
@@
 
+This section explores combinatorial properties of the non-crossing and non-kissing complexes, showing in particular that these complexes are pure and thin.
+The proof follows ideas of~\cite{McConville, GarverMcConville} already reinterpreted for non-kissing complexes of gentle algebras in~\cite{PaluPilaudPlamondon}.
+However, the setting of locally gentle algebras studied in this paper requires a little more care.
+
 \subsection{Some technical properties of non-kissing walks}
 
-\begin{lemma}\label{lem:nkCycles}
+We first gather two technical lemmas on properties of oriented cycles of the quiver~$\bar Q$.
+Note that oriented cycles were forbidden in the setting of gentle algebras studied in~\cite{PaluPilaudPlamondon}.
+
+\begin{lemma}
+\label{lem:nkCycles}
 Let~$\omega$ be a non-kissing walk that contains an oriented cycle~$c$.
@@
 Hence, the walk~$\omega$ contains the two substrings~$\beta^{-1}\alpha_1\cdots\alpha_j\alpha_{j+1}$ and~$\alpha_r\alpha_1\cdots\alpha_j\gamma^{-1}$, and thus self-kisses.
-\end{proof}
+\vincent{Should we also give here a geometric argument?}
+\end{proof}
+
+\begin{lemma}
+\label{lem:walksThroughcycles}
+For any oriented cycle~$c$ in~$\bar Q$, any maximal non-kissing face contains a walk of the form~$\sigma c^\infty$ or~$c^\infty\sigma$, for some substring~$\sigma$ distinct from~$c^\infty$.
+\end{lemma}
+
+\begin{proof}
+We provide two proofs of the lemma.
+One is combinatorial and applies to~$\NKC$, and the other is geometric and applies to~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$.
+
+\para{Combinatorial proof}
+Consider a maximal non-kissing face~$F \in \NKC$.
+We first argue that $F$ contains a walk distinct from~$c^\infty$ containing at least one arrow of~$c$.
+\vincent{TODO}
+
+\para{Geometric proof}
+
+\end{proof}
+
+\vincent{Should we also give here a geometric argument? Pierre-Guy, could you add that?}
 
@@
 \begin{proof}
- The proof of \cite[Lemma 2.21]{PaluPilaudPlamondon} applies here.
+ The proof of \cite[Lem.~2.21]{PaluPilaudPlamondon} applies here.
 \end{proof}
@@
 
- {\it Combinatorial proof.}
+ \para{Combinatorial proof}
  Note that even though~$F$ is finite, the set of marked walks~$F_\alpha$ might be infinite if~$\alpha$ belongs to an oriented cycle of~$Q$.
@@
 
- {\it Geometric proof.} View~$F$ as a face of the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$.
+ \para{Geometric proof}
+ View~$F$ as a face of the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$.
  The arrow~$\alpha$ then corresponds to an angle in~$\dissection$ at a vertex~$v$.
@@
 \begin{lemma}\label{lem:ExistenceOfDistinguishedArrows}
-Let~$F$ be a finite face of~$\NKC$, let~$\omega$ be a walk in~$F$, and let~$\alpha$ be an arrow on~$\omega$.
+Let~$F$ be a finite non-kissing face of~$\NKC$, let~$\omega$ be a walk in~$F$, and let~$\alpha$ be an arrow on~$\omega$.
 Assume that~$\omega$ is not an infinite straight walk.
@@
 \label{prop:purity}
- The the non-kissing complex~$\NKC$ and the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$ are pure of dimension~$3|Q_0| - |Q_1|$.
+The non-kissing complex~$\NKC$ and the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$ are pure of dimension~$3|Q_0| - |Q_1|$.
+\vincent{This is wrong. We need to count the infinite straight walks. I propose the next statement instead.}
 \end{proposition}
 
-Note that Proposition \ref{prop:purity} was proved for~$\NKC$ in \cite[Corollary 2.27]{PaluPilaudPlamondon} in the case where~$kQ/I$ is finite-dimensional.
+\begin{proposition}
+\label{prop:purity}
+The reduced non-kissing complex~$\RNKC$ and the reduced non-crossing complex~$\RNCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$ are pure of dimension~$|Q_0|$.
+The non-kissing complex~$\NKC$ and the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$ are pure of dimension~$3|Q_0| - |Q_1| + p$ where~$p$ is the number of oriented cycles in~$\bar Q$ or equivalently the number of punctures in~$\surface_{\bar Q}$.
+\end{proposition}
+
+Note that Proposition \ref{prop:purity} was proved for~$\NKC$ in \cite[Cor.~2.27]{PaluPilaudPlamondon} in the case where~$kQ/I$ is finite-dimensional.
 Note also that, by Theorem \ref{thm:complexesCoincide} above,~$\NKC$ and~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$ coincide, so it suffices to prove the Proposition for one of them.
@@
 
- {\it Combinatorial proof.} By Lemma~\ref{lem:ExistenceOfDistinguishedArrows}, the number of walks in a finite face of~$\NKC$ is bounded by~$|Q_1\blossom|+s_\infty$, where~$s_\infty$ is the number of infinite straight walks (i.e.
+ \para{Combinatorial proof}
+ By Lemma~\ref{lem:ExistenceOfDistinguishedArrows}, the number of walks in a finite face of~$\NKC$ is bounded by~$|Q_1\blossom|+s_\infty$, where~$s_\infty$ is the number of infinite straight walks (i.e.
 the number of oriented cycles in~$Q$).
 
- {\it Geometric proof.} Let~$F$ be a face of the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$.
+ \para{Geometric proof}
+ Let~$F$ be a face of the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$.
  Its elements are pairwise compatible~$\dissection$-accordions on the surface~$\surface(\bar Q)$.
@@
 
-The following definition from \cite[Definition 2.23]{PaluPilaudPlamondon} extends to the setting of locally gentle algebras.
+The following definition from \cite[Def.~2.23]{PaluPilaudPlamondon} extends to the setting of locally gentle algebras.
 
@@
 
-The following result extends \cite[Proposition 2.26]{PaluPilaudPlamondon} to the case of locally gentle algebras.
+The following result extends \cite[Prop.~2.26]{PaluPilaudPlamondon} to the case of locally gentle algebras.
 
@@
 \label{prop:numberOfDistinguishedArrows}
-Let~$F$ be a facet of~$\NKC$.
-\begin{itemize}
- \item Each bending walk of~$F$ has exactly two distinguished arrows.
- \item Each finite straight walk of~$F$ has exactly one distinguished arrows.
- \item Each infinite straight walk of~$F$ has exactly zero distinguished arrows.
+In a non-kissing facet~$F$ of~$\NKC$,
+\begin{itemize}
+ \item each bending walk of~$F$ has exactly two distinguished arrows,
+ \item each finite straight walk of~$F$ has exactly one distinguished arrow,
+ \item each infinite straight walk of~$F$ has no distinguished arrows.
 \end{itemize}
 \end{proposition}
-\begin{proof}
- \vincent{Vincent has the proof of this proposition.}
- The first two dots in this proposition are proven in Lemma~\ref{lem:ExistenceOfDistinguishedArrows}.
+
+\begin{proof}
+The proof of \cite[Prop.~2.26]{PaluPilaudPlamondon} applies here to show that each walk in the non-kissing facet~$F$ has at most one distinguished arrow in each direction.
+Lemma~\ref{lem:ExistenceOfDistinguishedArrows} therefore shows the first two points.
+Finally, Lemma~\ref{lem:walksThroughcycles} shows the last point.
 \end{proof}
@@
 \begin{proof}[Proof of Proposition \ref{prop:purity}.]
-\vincent{TO DO}
+The proof follows that of~\cite[Cor.~2.27]{PaluPilaudPlamondon}.
+Let~$b$ denote the number of bending walks, $s$ the number of finite straight walks, and $p$ the number of infinite straight walks in a non-kissing facet~$F$ of~$\NKC$.
+Since each finite straight walk uses two blossom arrows, we have~$s = 2|Q_0|-|Q_1|$ (see Remark~\ref{rem:sizeBlossomingQuiver}).
+Moreover, the infinite straight walks are just the oriented cycles in~$\bar Q$.
+Using Proposition~\ref{prop:numberOfDistinguishedArrows}, we obtain by double-counting that
+\[
+2 * b + 1 * s + 0 * c= |Q_1\blossom| = 4|Q_0|-|Q_1|
+\]
+from which we derive that~$b = |Q_0|$ and~$b+s+c = 3|Q_0|-|Q_1|+p$.
 \end{proof}
@@
 A simplicial complex is \defn{thin} if each of its codimension~$1$ faces is contained in exaclty two facets.
-We state the following results, which generalize \cite[Proposition 2.31 and Corollary 2.33]{PaluPilaudPlamondon}, whose proofs apply withouth change.
+We state the following results, which generalize \cite[Prop.~2.31 \& Cor.~2.33]{PaluPilaudPlamondon}, whose proofs apply withouth change.
 

### 2018-07-05 draft/accordionComplexSurfaces.tex
reorganization Section 5: New section 5.2 devoted to show that the faces are finite

@@
 
-\subsection{Some technical properties of non-kissing walks}
-
-We first gather two technical lemmas on properties of oriented cycles of the quiver~$\bar Q$.
-Note that oriented cycles were forbidden in the setting of gentle algebras studied in~\cite{PaluPilaudPlamondon}.
-
-\begin{lemma}
-\label{lem:nkCycles}
-Let~$\omega$ be a non-kissing walk that contains an oriented cycle~$c$.
-Then~$\omega$ is of the form~$\sigma c^\infty$ or~$c^\infty\sigma$, for some substring~$\sigma$.
-\end{lemma}
-
-\begin{proof}
-Let~$c=\alpha_1\cdots\alpha_r$ be an oriented cycle in some walk~$\omega$.
-Assume that~$\omega$ is not of form~$\sigma c^\infty$ or~$c^\infty\sigma$.
-Then, up to cyclic reordering of the arrows in~$c$, it contains a substring of the form~$\beta^\pm c^l \alpha_1\cdots\alpha_j\gamma^\pm$, for some arrows~$\beta,\gamma$ not in~$c$, some~$l\geq 1$, and some~$j<r$.
-Since~$\bar Q$ is locally gentle, this substring is~$\beta^{-1} c^l \alpha_1\cdots\alpha_j\gamma^{-1}$.
-Hence, the walk~$\omega$ contains the two substrings~$\beta^{-1}\alpha_1\cdots\alpha_j\alpha_{j+1}$ and~$\alpha_r\alpha_1\cdots\alpha_j\gamma^{-1}$, and thus self-kisses.
-\vincent{Should we also give here a geometric argument?}
-\end{proof}
-
-\begin{lemma}
-\label{lem:walksThroughcycles}
-For any oriented cycle~$c$ in~$\bar Q$, any maximal non-kissing face contains a walk of the form~$\sigma c^\infty$ or~$c^\infty\sigma$, for some substring~$\sigma$ distinct from~$c^\infty$.
-\end{lemma}
-
-\begin{proof}
-We provide two proofs of the lemma.
-One is combinatorial and applies to~$\NKC$, and the other is geometric and applies to~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$.
-
-\para{Combinatorial proof}
-Consider a maximal non-kissing face~$F \in \NKC$.
-We first argue that $F$ contains a walk distinct from~$c^\infty$ containing at least one arrow of~$c$.
-\vincent{TODO}
-
-\para{Geometric proof}
-
-\end{proof}
-
-\vincent{Should we also give here a geometric argument? Pierre-Guy, could you add that?}
-
 \subsection{The countercurrent order}
@@
 \label{lemm:facesHaveMaximalElement}
-For any finite face~$F$ of~$\NKC$ and any arrow~$\alpha\in Q_1\blossom$, the set~$F_\alpha$ is either empty or admits a maximal element for the countercurrent order~$\prec_\alpha$.
+For any finite non-kissing face~$F$ of~$\NKC$ and any arrow~$\alpha\in Q_1\blossom$, the set~$F_\alpha$ is either empty or admits a maximal element for the countercurrent order~$\prec_\alpha$.
 \end{lemma}
@@
  This element is the maximal element of~$F_\alpha$.
+\end{proof}
+
+\subsection{The non-crossing and non-kissing complexes have no infinite faces}
+
+We now pause to prove the following statement.
+
+\begin{lemma}
+\label{lem:facetsAreFinite}
+Any face of~$\NKC$ and~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$ is finite, thus contained in a finite maximal face.
+\end{lemma}
+
+Since Theorem \ref{thm:complexesCoincide} ensures that~$\NKC$ and~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$ coincide, we only prove the statement for the non-kissing complex.
+The proof requires the following intermediate results.
+
+\begin{lemma}
+\label{lem:nkCycles}
+Let~$\omega$ be a non-kissing walk that contains an oriented cycle~$c$.
+Then~$\omega$ is of the form~$\sigma c^\infty$ or~$c^\infty\sigma$, for some substring~$\sigma$.
+\end{lemma}
+
+\begin{proof}
+Let~$c=\alpha_1\cdots\alpha_r$ be an oriented cycle in some walk~$\omega$.
+Assume that~$\omega$ is not of form~$\sigma c^\infty$ or~$c^\infty\sigma$.
+Then, up to cyclic reordering of the arrows in~$c$, it contains a substring of the form~$\beta^\pm c^l \alpha_1\cdots\alpha_j\gamma^\pm$, for some arrows~$\beta,\gamma$ not in~$c$, some~$l\geq 1$, and some~$j<r$.
+Since~$\bar Q$ is locally gentle, this substring is~$\beta^{-1} c^l \alpha_1\cdots\alpha_j\gamma^{-1}$.
+Hence, the walk~$\omega$ contains the two substrings~$\beta^{-1}\alpha_1\cdots\alpha_j\alpha_{j+1}$ and~$\alpha_r\alpha_1\cdots\alpha_j\gamma^{-1}$, and thus self-kisses.
+\vincent{Should we also give here a geometric argument?}
 \end{proof}
@@
 
-\subsection{Purity of the non-crossing and non-kissing complexes}
-
-A simplicial complex is \defn{pure of dimension~$d$} if all its maximal faces have dimension~$d$.
-The aim of this section is to prove the following purity result.
-
-\begin{proposition}
-\label{prop:purity}
-The non-kissing complex~$\NKC$ and the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$ are pure of dimension~$3|Q_0| - |Q_1|$.
-\vincent{This is wrong. We need to count the infinite straight walks. I propose the next statement instead.}
-\end{proposition}
-
-\begin{proposition}
-\label{prop:purity}
-The reduced non-kissing complex~$\RNKC$ and the reduced non-crossing complex~$\RNCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$ are pure of dimension~$|Q_0|$.
-The non-kissing complex~$\NKC$ and the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$ are pure of dimension~$3|Q_0| - |Q_1| + p$ where~$p$ is the number of oriented cycles in~$\bar Q$ or equivalently the number of punctures in~$\surface_{\bar Q}$.
-\end{proposition}
-
-Note that Proposition \ref{prop:purity} was proved for~$\NKC$ in \cite[Cor.~2.27]{PaluPilaudPlamondon} in the case where~$kQ/I$ is finite-dimensional.
-Note also that, by Theorem \ref{thm:complexesCoincide} above,~$\NKC$ and~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$ coincide, so it suffices to prove the Proposition for one of them.
-
 \begin{lemma}
@@
 
-\begin{lemma}
-\label{lemm:facetsAreFinite}
-Any face of~$\NKC$ and~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$ is contained in a finite maximal face.
-\end{lemma}
-\begin{proof}
+\begin{proof}[Proof of Lemma~\ref{lem:facetsAreFinite}]
  If~$\NKC$ admits an infinite face, then all subsets of this face are also faces, so~$\NKC$ admits faces of arbitrary finite cardinality.
@@
 
+\subsection{Purity of the non-crossing and non-kissing complexes}
+
+A simplicial complex is \defn{pure of dimension~$d$} if all its maximal faces have dimension~$d$.
+The aim of this section is to prove the following purity result.
+
+\begin{proposition}
+\label{prop:purity}
+The non-kissing complex~$\NKC$ and the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$ are pure of dimension~$3|Q_0| - |Q_1|$.
+\vincent{This is wrong. We need to count the infinite straight walks. I propose the next statement instead.}
+\end{proposition}
+
+\begin{proposition}
+\label{prop:purity}
+The reduced non-kissing complex~$\RNKC$ and the reduced non-crossing complex~$\RNCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$ are pure of dimension~$|Q_0|$.
+The non-kissing complex~$\NKC$ and the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$ are pure of dimension~$3|Q_0| - |Q_1| + p$ where~$p$ is the number of oriented cycles in~$\bar Q$ or equivalently the number of punctures in~$\surface_{\bar Q}$.
+\end{proposition}
+
+Note that Proposition \ref{prop:purity} was proved for~$\NKC$ in \cite[Cor.~2.27]{PaluPilaudPlamondon} in the case where~$kQ/I$ is finite-dimensional.
+Note also that, by Theorem \ref{thm:complexesCoincide} above,~$\NKC$ and~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$ coincide, so it suffices to prove the Proposition for one of them.
 The following definition from \cite[Def.~2.23]{PaluPilaudPlamondon} extends to the setting of locally gentle algebras.
@@
 Let~$\alpha \in Q\blossom_1$ be an arrow and let~$F$ be a face of~$\NKC$ containing the straight walk passing through~$\alpha$.
-Consider the marked walk~$\omega_\star \eqdef \max_{\prec_\alpha} F_\alpha$ (which exists by Lemma \ref{lemm:facesHaveMaximalElement}),
+Consider the marked walk~$\omega_\star \eqdef \max_{\prec_\alpha} F_\alpha$ (which exists by Lemmas \ref{lemm:facesHaveMaximalElement} and~\ref{lem:facetsAreFinite}),
 and let~$\omega$ be the walk obtained by forgetting the marked arrow in~$\omega_\star$. 
@@
 \end{definition}
+
+We use this definition to prove the following statement.
+
+\begin{lemma}
+\label{lem:walksThroughcycles}
+For any oriented cycle~$c$ in~$\bar Q$, any maximal non-kissing face contains a walk of the form~$\sigma c^\infty$ or~$c^\infty\sigma$, for some substring~$\sigma$ distinct from~$c^\infty$.
+\end{lemma}
+
+\begin{proof}
+We provide two proofs of the lemma.
+One is combinatorial and applies to~$\NKC$, and the other is geometric and applies to~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$.
+
+\para{Combinatorial proof}
+Consider a maximal non-kissing face~$F \in \NKC$.
+We first argue that $F$ contains a walk distinct from~$c^\infty$ containing at least one arrow of~$c$.
+\vincent{TODO}
+
+\para{Geometric proof}
+\vincent{Should we also give here a geometric argument? Pierre-Guy, could you add that?}
+
+\end{proof}
 

### 2018-07-05 draft/accordionComplexSurfaces.tex
combinatorial proof Lemma 5.13

@@
 \para{Combinatorial proof}
-Consider a maximal non-kissing face~$F \in \NKC$.
-We first argue that $F$ contains a walk distinct from~$c^\infty$ containing at least one arrow of~$c$.
-\vincent{TODO}
+Consider a maximal non-kissing face~$F \in \NKC$ and an arrow~$\alpha$ in~$c$.
+Let~$\beta, \gamma \in Q_1\blossom$ be such that~$t(\alpha) = s(\beta) = s(\gamma)$ and~$\alpha\beta \notin I$ while~$\alpha\gamma \in I$ (in other words, $\beta$ is the next arrow along~$c$ after~$\alpha$ and~$\gamma$ is the other outgoing arrow at~$t(\alpha)$).
+Consider the walk~$\mu \eqdef \distinguishedWalk{\gamma}{F}$ and decompose it as~$\mu = \mu_1 \gamma \mu_2$ according to this occurence of~$\gamma$ on~$\mu$.
+Consider the walk~$\nu \eqdef \mu_2^{-1} \gamma^{-1} c^\infty$.
+If~$\nu$ is contained in~$F$, then we have found a walk of the desired form (remember that walks are considered as undirected).
+Otherwise, there exists a walk~$\lambda$ of~$F$ preventing~$\nu$ to belong to~$F$.
+Let~$\sigma$ be a common substring of~$\nu$ and~$\lambda$ where they kiss.
+Since~$\lambda$ must be compatible with~$\mu$ and with the straight walk~$c^\infty$, the substring~$\sigma$ must contain~$t(\alpha) = s(\beta)$.
+If~$\lambda$ contains neither~$\alpha$ nor~$\beta$, then it contains~$\gamma$ and enters $\nu$ at~$s(\gamma)$.
+Since $\lambda$ kisses~$\nu$, it also enters~$\mu_2$, contradicting the maximality of~$\mu$ for~$\prec_\gamma$.
+Therefore, $\lambda$ contains either~$\alpha$ or~$\beta$.
+We have thus found a bended walk~$\lambda \in F$ containing an arrow~$\alpha$ or~$\beta$ of~$c$, say~$\alpha$.
+We can now moreover assume that~$\lambda = \distinguishedWalk{\alpha}{F}$.
+If~$\lambda$ starts or ends by~$c^\infty$, then we have found a walk of the desired form.
+Otherwise, decompose this walk as~$\lambda = \lambda_1 \alpha \lambda_2$ and consider the walk~$\omega = \lambda_1 c^\infty$.
+We claim that~$\omega$ belongs to~$F$.
+Otherwise, there exists a walk~$\rho$ preventing~$\omega$ to belong to~$F$.
+Let~$\tau$ be a common substring of~$\omega$ and~$\rho$ where they kiss.
+Since~$\omega$ must be compatible with~$\lambda$ and with the straight walk~$c^\infty$, the substring~$\tau$ must strictly contain the substring of~$\lambda$ along the cycle~$c$.
+It follows that $\rho$ leaves~$\omega$ when it is on the cycle~$c$, thus with an incoming arrow, contradicting the maximality of~$\lambda$ for~$\prec_\alpha$.
 

### 2018-07-09 draft/accordionComplexSurfaces.tex
References to OPS.

@@
 \end{figure}
+
+The following proposition appears in \cite[Proposition 1.25]{OpperPlamondonSchroll}.
 
@@
 
-\pierreguy{Remark on the comparison with the surface of OPS}
+\begin{remark}
+\label{rem:comparisonWithOPS}
+The construction of the surface given in Definition \ref{def:surfaceQuiver} yields the same surface as the one constructed in \cite{OpperPlamondonSchroll}.
+A notable difference is that in \cite{OpperPlamondonSchroll}, only~$\dissection_{\bar Q}$ is given, and~$\dissection_{\bar Q}\dual$ is deduced (it is called the dual lamination).
+Another minor difference is that the construction in \cite{OpperPlamondonSchroll} is written only for gentle algebras, while here it is generalized to locally gentle algebras.
+
+The major difference with \cite{OpperPlamondonSchroll} is the application of the surface of a (locally) gentle algebra: 
+there, it is used as a model for the derived category of the gentle algebra (graded arcs correspond to indecomposable objects in that category),
+while here, it will be used as a model for walks in~$\bar Q$ ($\dissection_{\bar Q}$-accordions will correspond to walks in~$\bar{Q}$, see Proposition \ref{prop:walks=arcs}).
+\end{remark}
 

### 2018-07-09 draft/accordionComplexSurfaces.tex
Added some proofs.

@@
 \begin{proof}
- \pierreguy{TO DO}
+We can assume that~$\gamma$ intersects itself and the arcs of~$\dissection_{\bar Q}$ transversaly and minimally, in the sense that~$\gamma$ does not cross an arc twice in succession in opposite directions.
+Then~$\gamma$ is completely determined by its sequence of intersection points with the arcs of~$\dissection_{\bar Q}$, since the dissection is cellular.
+Two successive intersection points in this sequence define an angle between two arcs of~$\dissection_{\bar Q}$, which correspoinds to an arrow in~$\bar Q$.
+Thus the sequence of intersection points defines a walk~$\walk(\gamma)$ on~$\bar Q$.
+By construction, we have that~$\curveof(\walk(\gamma)) = \gamma$.
+
+Is also follows from construction above and from Definition~\ref{def:curveOfAWalk} that~$\walk(\curveof(\omega)) = \omega$ for any walk~$\omega$.
+This finishes the proof.
 \end{proof}
@@
 \begin{proof}
-See \fref{fig:kissings} and \fref{fig:kissingVSCrossing}.
-\pierreguy{Complete this proof using the pictures.}
+A kiss between two walks~$\omega$ and~$\omega'$ is depicted on \fref{fig:kissings}.
 
@@
 \end{figure}
+The left hand side of the picture is as in \fref{fig:kissing}, and the right hand side is simply a different representation of it.
+On the surface~$\surface(\bar Q)$, the dual dissections~$\dissection$ and~$\dissection\dual$ are as on \fref{fig:kissingVSCrossing} (on the right hand side).
 
@@
 \end{figure}
+
+The curves~$\curveof(\omega)$ and~$\curveof(\omega')$ on the surface follow~$\omega$ and~$\omega'$ on the picture.
+It is then clear that~$\omega$ and~$\omega'$ kiss if and only if~$\curveof(\omega)$ and~$\curveof(\omega')$ cross.
 
@@
 \vincent{This is wrong. We need to count the infinite straight walks. I propose the next statement instead.}
+\pierreguy{I agree.}
 \end{proposition}

### 2018-07-09 draft/accordionComplexSurfaces.tex
Added a geometric proof.

@@
 \para{Geometric proof}
+The statement of the lemma translates on~$\surface(\bar Q)$ as follows: for any facet~$F$ of the non-crossing complex~$\NCC$ and any puncture of the dissection~$\dissection_{\bar Q}$, there exists a curve in~$F$ which goes to the puncture.
+Assume that there is a puncture with no curves of~$F$ going to it.
+Construct a curve~$\gamma$ as follows:~$\gamma$ first unwinds from the puncture, then~$\gamma$ leaves the local picture around the puncture by turning aroune another marked point (marked~$X$ on the picture below).
+
+\pierreguy{Pic No 7 here.}
+Two situations occur.
+
+Firstly, if there are no curves of~$F$ closer to~$X$ than~$\gamma$, then~$\gamma$ can circle around~$X$ until it reaches the boundary (if~$X$ is on the boundary) or infinitely (if~$X$ is a puncture).
+Then~$\gamma$ is a~$\dissection_{\bar Q}$-accordion which crosses none of those in~$F$, contradicting the maximality of~$F$.
+
+Secondly, if there is a curve of~$F$ closer to~$X$ than~$\gamma$, then let~$\delta$ be the one furthest from~$X$ ($\delta$ exists by Lemma \ref{lemm:facesHaveMaximalElement}).
+From there, let~$\gamma$ follow~$\delta$ on the surface until it either reaches the boundary or circles infinitely around a puncture.  
+Then~$\gamma$ is compatible with all curves in~$F$, a contradiction.
+
+Thus~$F$ contains a curve going to the puncture.
 \vincent{Should we also give here a geometric argument? Pierre-Guy, could you add that?}
+\pierreguy{Done; I will need two pictures, please, Vincent.}
 

### 2018-07-09 draft/accordionComplexSurfaces.tex
Added a picture.
More pictures and a geometric proof.

@@
 Hence, the walk~$\omega$ contains the two substrings~$\beta^{-1}\alpha_1\cdots\alpha_j\alpha_{j+1}$ and~$\alpha_r\alpha_1\cdots\alpha_j\gamma^{-1}$, and thus self-kisses.
+
+\para{Geometric proof}
+An oriented cycle~$c$ corresponds to a puncture in~$\dissection_{\bar Q}$.
+Let~$\gamma = \curveof(\omega)$.  The fact that~$\omega$ contains~$c$ translates to the fact that~$\gamma$ makes a full circle around the correponding puncture.
+\pierreguy{Pic No 8 here.}
+
+\includegraphics{pgFigNo8.pdf}
+
+Once this cycle is completed, since~$\gamma$ cannot cross itself, it has to continue cycling infinitely around the puncture.  This proves the claim.
 \vincent{Should we also give here a geometric argument?}
@@
 
+\includegraphics{pgFigNo7.pdf}
 \pierreguy{Pic No 7 here.}
@@
 \vincent{Should we also give here a geometric argument? Pierre-Guy, could you add that?}
-\pierreguy{Done; I will need two pictures, please, Vincent.}
+\pierreguy{Done; I will need a picture, please, Vincent.}
 

### 2018-07-09 draft/accordionComplexSurfaces.tex
figures PG
abstract + infinite strings + primitive cycles

--- 2018-07-09 draft/accordionComplexSurfaces.tex
@@
 From those geometric data, we define two simplicial complexes: the accordion complex, and the slalom complex, generalising work of A. Garver and T. McConville in the case of a disk.
-We show that all three simplicial complexes are isomorphic.
+We show that all three simplicial complexes are isomorphic; that they are pure and thin.
+In particular, there is a notion of mutation on their facets, akin to $\tau$-tilting mutation.
 We also construct inverse bijections between the set of isomorphism classes of locally gentle bound quivers and the set of homeomorphism classes of punctured, marked, oriented surfaces with boundary, endowed with a pair of dual dissections.
@@
 We thank Sibylle Schroll for discussions on geometric models for gentle algebras.
-We are also grateful to Salvatore Stella for discussions on accordion complexes of dissections of surfaces.
+We are also grateful to Salvatore Stella for discussions on accordion complexes of dissections of surfaces, and to William Crawley-Boevey and Henning Krause for discussions on the representation theory of infinite dimensional algebras.
 
@@
 \label{def:gentleQuiver}
-A \defn{locally gentle bound quiver}~$\bar Q \eqdef (Q,I)$ is a bound quiver such that
+A \defn{locally gentle bound quiver}~$\bar Q \eqdef (Q,I)$ is a (finite) bound quiver such that
 \begin{itemize}
@@
 Let~$\bar Q = (Q,I)$ be a locally gentle bound quiver.
-A \defn{string} for~$\bar Q$ is a word of the form
+A \defn{finite string} for~$\bar Q$ is a word of the form
 \(
@@
 For each vertex~$v \in Q_0$, there is also a \defn{string of length zero}, denoted by~$\varepsilon_v$, that starts and ends at~$v$.
+We note that there is only one string of length 
 %We denote by~$\strings(\bar Q)$ the set of strings on~$\bar Q$.
 %We usually denote strings by~$\rho, \sigma, \tau$.
-We often implicitly identify the two inverse strings~$\rho$ and~$\rho^{-1}$, and we let~$\strings^\pm(\bar Q) \eqdef \set{\{\rho, \rho^{-1}\}}{\rho \in \strings(\bar Q)}$ denote the collection of all \defn{undirected strings} of~$\bar Q$.
 
@@
 \begin{definition}
+ An oriented cycle~$c$ in~$Q$ such that~$c$ and~$c^2$ do not belong to the ideal of relations~$I$ is called \defn{primitive} if it cannot be written as an $n$-th power ($n>1$) of a cycle.
+\end{definition}
+
+\begin{notation}
+If~$c$ is an oriented cycle in~$Q$ such that~$c$ and~$c^2$ do not belong to the ideal of relations~$I$, we write:
+\begin{itemize}
+ \item $^\infty c$ for the infinite word:~$\cdots c c c$;
+ \item $c^\infty$ for the word:~$c c c\cdots$;
+ \item $^{-\infty} c$ for the infinite word:~$\cdots c^{-1} c^{-1} c^{-1}$;
+ \item $c^{-\infty}$ for the word:~$c^{-1} c^{-1} c^{-1}\cdots$ and
+ \item $^\infty c^\infty$ for the word:~$^\infty c c^\infty$.
+\end{itemize}
+\end{notation}
+
+We note that~$(c^\infty)^{-1} =\,^{-\infty}c$ and similarly~$(^\infty c)^{-1} = c^{-\infty}$.
+
+\begin{definition}
+An \defn{eventually cyclic string} for~$\bar Q$ is a word~$\rho$ of the form~$^{\pm\infty}c_1\sigma c_2^{\pm\infty}$, where $c_1,c_2$ are oriented cycles in~$\bar Q$ (possibly of length zero), $c_1, c_1^2, c_2, c_2^2\notin I$, and~$\sigma$ is a finite string.
+In case~$\rho=\,^{\pm\infty}c_1\sigma c_2^{\infty}$, it is called \defn{eventually direct}, and \defn{eventually inverse} if~$\rho=\,^{\pm\infty}c_1\sigma c_2^{-\infty}$.
+\end{definition}
+
+\begin{remark}
+ The terminology in the previous definition is borrowed from~\ref{Crawley-Boevey}.
+ Note however that our choice of convention differs from \emph{loc. cit.}, resulting in exchanging ``inverse'' and ``direct''.
+\end{remark}
+
+\begin{definition}
+ A \defn{string} for~$\bar Q$ is a word which is either a finite string or an eventually cyclic infinite string.
+ We often implicitly identify the two inverse strings~$\rho$ and~$\rho^{-1}$, and we let~$\strings^\pm(\bar Q) \eqdef \set{\{\rho, \rho^{-1}\}}{\rho \in \strings(\bar Q)}$ denote the collection of all \defn{undirected strings} of~$\bar Q$.
+\end{definition}
+
+\begin{definition}
 \label{def:walk}
-A \defn{walk} of a locally gentle quiver~$\bar Q$ is a maximal string of its blossoming quiver~$\bar Q \blossom$, meaning that at each end it either reaches a blossom vertex of~$\bar Q \blossom$ or enters an infinite oriented cycle.
+A \defn{walk} of a locally gentle quiver~$\bar Q$ is a maximal string of its blossoming quiver~$\bar Q \blossom$ (meaning that at each end it either reaches a blossom vertex of~$\bar Q \blossom$ or enters an infinite oriented cycle).
 We denote by~$\walks(\bar Q)$ the set of all walks on~$\bar Q$.
@@
 \label{def:substrings}
-A \defn{substring} of a walk~$\omega = \alpha_1^{\varepsilon_1} \dots \alpha_\ell^{\varepsilon_\ell} \in \walks(\bar Q)$ is a string~$\sigma = \alpha_i^{\varepsilon_i} \dots \alpha_j^{\varepsilon_j}$ of~$\strings(\bar Q)$ for some~$1 < i \le j < \ell$.
-Note that 
-\begin{itemize}
-\item the endpoints of~$\sigma$ are not allowed to be the blossom endpoints of~$\omega$,
-\item the position of~$\sigma$ as a factor of~$\omega$ matters (the same string at a different position is considered a different substring),
-\item the string~$\varepsilon_v$ is a substring of~$\omega$ for each occurence of~$v$ as a vertex of~$\omega$.
-\end{itemize}
-The substring~$\sigma = \alpha_i^{\varepsilon_i} \dots \alpha_j^{\varepsilon_j}$ is \defn{at the bottom} (resp.~\defn{on top}) of the walk~$\omega = \alpha_1^{\varepsilon_1} \dots \alpha_\ell^{\varepsilon_\ell}$ if~$\varepsilon_{i-1} = 1$ and~$\varepsilon_{j+1} = -1$ (resp.~if~$\varepsilon_{i-1} = -1$ and~$\varepsilon_{j+1} = 1$), that is, the two arrows of~$\omega$ incident to the endpoints of~$\sigma$ point towards~$\sigma$ (resp.~outwards from~$\sigma$).
+A \defn{substring} of a walk~$\omega =\cdots \alpha_{-r}^{\varepsilon_{-r}}\cdots\alpha_0^{\varepsilon_0} \alpha_1^{\varepsilon_1} \cdots \alpha_\ell^{\varepsilon_\ell}\cdots \in \walks(\bar Q)$ is a string~$\sigma = \alpha_i^{\varepsilon_i} \dots \alpha_j^{\varepsilon_j}$ of~$\strings(\bar Q)$ for some~$i \le j \in \mathbb{Z}\cup\{\pm\infty\}$, where moreover
+\begin{itemize}
+\item the endpoints of~$\sigma$ are not allowed to be the possible blossom endpoints of~$\omega$,
+\item the position of~$\sigma$ as a factor of~$\omega$ matters (the same string at a different position is considered a different substring).
+\end{itemize}
+Note that the string~$\varepsilon_v$ is a substring of~$\omega$ for each occurence of~$v$ as a vertex of~$\omega$.
+The substring~$\sigma = \alpha_i^{\varepsilon_i} \dots \alpha_j^{\varepsilon_j}$ is \defn{at the bottom} (resp.~\defn{on top}) of the walk~$\omega = \alpha_1^{\varepsilon_1} \dots \alpha_\ell^{\varepsilon_\ell}$ if~$i=-\infty$ or~$\varepsilon_{i-1} = 1$ and~$j=+\infty$ or~$\varepsilon_{j+1} = -1$ (resp.~if~$i=-\infty$ or~$\varepsilon_{i-1} = -1$ and~$i=-\infty$ or~$\varepsilon_{j+1} = 1$), that is, the (at most) two arrows of~$\omega$ incident to the endpoints of~$\sigma$ point towards~$\sigma$ (resp.~outwards from~$\sigma$).
 We let~$\Sigma(\omega)$ be the set of substrings of~$\omega$ and~$\Sigma_\bottom(\omega)$ and~$\Sigma_\top(\omega)$ be the sets of bottom and top substrings of~$\omega$ respectively.
@@
 Let~$\omega,\omega' \in \walks^\pm(\bar Q)$ be two undirected walks on~$\bar Q$.
-We say that~$\omega$ \defn{kisses}~$\omega'$ if~$\Sigma_\top(\omega) \cap \Sigma_\bottom(\omega') \ne \varnothing$.
+We say that~$\omega$ \defn{kisses}~$\omega'$ if~$\Sigma_\top(\omega) \cap \Sigma_\bottom(\omega')$ contains a \emph{finite} substring.
 See \fref{fig:kissing}.
@@
 We say that~$\omega$ and~$\omega'$ are \defn{kissing} if~$\omega$ kisses~$\omega'$ or~$\omega'$ kisses~$\omega$ (or both).
-Note that we authorize the situation where~$\sigma$ is reduced to a vertex~$v$, meaning that~$v$ is a peak of~$\omega$ and a deep of~$\omega'$.
+Note that we authorize the situation where the commmon finite substring is reduced to a vertex~$v$, meaning that~$v$ is a peak of~$\omega$ and a deep of~$\omega'$.
 Observe also that~$\omega$ can kiss~$\omega'$ several times, that~$\omega$ and~$\omega'$ can mutually kiss, and that~$\omega$ can kiss itself.
@@
 \end{figure}
-
-The following proposition appears in \cite[Proposition 1.25]{OpperPlamondonSchroll}.
 
@@
 We now associate a surface to a locally gentle bound quiver.
-This construction is directly inspired by the one found in \cite{OpperPlamondonSchroll} (see Remark \ref{rem:comparisonWithOPS} for a comparison of the two constructions).
+\pierreguy{reference OPS}
 
@@
 \item The set~$V_{\bar Q}$ has one vertex for each straight walk in~$\bar Q$ (equivalently, for each maximal path in~$\bar Q$).
-      Finite straight walks yield vertices on the boundary, while infinite cyclic straight walks yield punctures.
+      Finite straight walks yield vertices on the boundary, while infinite cyclic straight walks in~$\bar Q$ and in~$\bar Q\koszul$ yield punctures.
 \item The dissection~$\dissection_{\bar Q}$ has one arc for each vertex~$p \in \bar Q_0$, obtained by concataining the sides~$\Enrt{\alpha} = \Enrs{\beta}$ and~$\Enrt{\alpha'} = \Enrs{\beta'}$ where~$p = t(\alpha) = s(\beta) = t(\alpha') = s(\beta')$, $\alpha\beta \notin I$ and~$\alpha'\beta' \notin I$.
@@
 
-\begin{remark}
-\label{rem:comparisonWithOPS}
-The construction of the surface given in Definition \ref{def:surfaceQuiver} yields the same surface as the one constructed in \cite{OpperPlamondonSchroll}.
-A notable difference is that in \cite{OpperPlamondonSchroll}, only~$\dissection_{\bar Q}$ is given, and~$\dissection_{\bar Q}\dual$ is deduced (it is called the dual lamination).
-Another minor difference is that the construction in \cite{OpperPlamondonSchroll} is written only for gentle algebras, while here it is generalized to locally gentle algebras.
-
-The major difference with \cite{OpperPlamondonSchroll} is the application of the surface of a (locally) gentle algebra: 
-there, it is used as a model for the derived category of the gentle algebra (graded arcs correspond to indecomposable objects in that category),
-while here, it will be used as a model for walks in~$\bar Q$ ($\dissection_{\bar Q}$-accordions will correspond to walks in~$\bar{Q}$, see Proposition \ref{prop:walks=arcs}).
-\end{remark}
+\pierreguy{Remark on the comparison with the surface of OPS}
 
@@
 \begin{proof}
-We can assume that~$\gamma$ intersects itself and the arcs of~$\dissection_{\bar Q}$ transversaly and minimally, in the sense that~$\gamma$ does not cross an arc twice in succession in opposite directions.
-Then~$\gamma$ is completely determined by its sequence of intersection points with the arcs of~$\dissection_{\bar Q}$, since the dissection is cellular.
-Two successive intersection points in this sequence define an angle between two arcs of~$\dissection_{\bar Q}$, which correspoinds to an arrow in~$\bar Q$.
-Thus the sequence of intersection points defines a walk~$\walk(\gamma)$ on~$\bar Q$.
-By construction, we have that~$\curveof(\walk(\gamma)) = \gamma$.
-
-Is also follows from construction above and from Definition~\ref{def:curveOfAWalk} that~$\walk(\curveof(\omega)) = \omega$ for any walk~$\omega$.
-This finishes the proof.
+ \pierreguy{TO DO}
 \end{proof}
@@
 \begin{proof}
-A kiss between two walks~$\omega$ and~$\omega'$ is depicted on \fref{fig:kissings}.
+See \fref{fig:kissings} and \fref{fig:kissingVSCrossing}.
+\pierreguy{Complete this proof using the pictures.}
 
@@
 \end{figure}
-The left hand side of the picture is as in \fref{fig:kissing}, and the right hand side is simply a different representation of it.
-On the surface~$\surface(\bar Q)$, the dual dissections~$\dissection$ and~$\dissection\dual$ are as on \fref{fig:kissingVSCrossing} (on the right hand side).
 
@@
 \end{figure}
-
-The curves~$\curveof(\omega)$ and~$\curveof(\omega')$ on the surface follow~$\omega$ and~$\omega'$ on the picture.
-It is then clear that~$\omega$ and~$\omega'$ kiss if and only if~$\curveof(\omega)$ and~$\curveof(\omega')$ cross.
 
@@
  Assume that~$F_\alpha$ is non-empty, and infinite.
- Any walk that contains an infinite number of copies of~$\alpha$ can be written in the form~$\omega=\sigma c^\infty$ where~$\sigma$ is a (possibly infinite) substring and~$c$ is an oriented cycle containing~$\alpha$.
- Then~$\omega$ marked at the first occurrence of~$\alpha$ in~$c^\infty$ is greater than~$\omega$ marked at any other occurrence of~$\alpha$ in~$c^\infty$.
- We can thus safely remove all copies of~$\omega$ marked at an occurrence of~$\alpha$ in~$c^\infty$ but the first one.
+ Any walk that contains an infinite number of copies of~$\alpha$ can be written in the form~$\omega=\sigma c^{\pm\infty}$ where~$\sigma$ is a (possibly infinite) substring and~$c$ is an oriented cycle containing~$\alpha$ such that~$c, c^2\notin I$.
+ Then~$\omega$ marked at the first occurrence of~$\alpha$ in~$c^{\pm\infty}$ is greater than~$\omega$ marked at any other occurrence of~$\alpha$ in~$c^{\pm\infty}$.
+ We can thus safely remove all copies of~$\omega$ marked at an occurrence of~$\alpha$ in~$c^{\pm\infty}$ but the first one.
  After applying this procedure a finite number of times,~$F_\alpha$ becomes finite, and the claim follows.
@@
 \label{lem:nkCycles}
-Let~$\omega$ be a non-kissing walk that contains an oriented cycle~$c$.
-Then~$\omega$ is of the form~$\sigma c^\infty$ or~$c^\infty\sigma$, for some substring~$\sigma$.
+Let~$\omega$ be a non-kissing walk that contains a non-trivial oriented cycle~$c$ with~$c, c^2\notin I$.
+Then~$\omega$ is of the form~$\sigma c^{\pm\infty}$, for some (possibly infinite) substring~$\sigma$.
 \end{lemma}
@@
 \begin{proof}
-Let~$c=\alpha_1\cdots\alpha_r$ be an oriented cycle in some walk~$\omega$.
-Assume that~$\omega$ is not of form~$\sigma c^\infty$ or~$c^\infty\sigma$.
+Let~$c=\alpha_1\cdots\alpha_r$ be a non-trivial oriented cycle in some walk~$\omega$, with~$c, c^2\notin I$.
+Assume that~$\omega$ is not of form~$\sigma c^{\pm\infty}$.
 Then, up to cyclic reordering of the arrows in~$c$, it contains a substring of the form~$\beta^\pm c^l \alpha_1\cdots\alpha_j\gamma^\pm$, for some arrows~$\beta,\gamma$ not in~$c$, some~$l\geq 1$, and some~$j<r$.
@@
  By Lemma~\ref{lem:ExistenceOfDistinguishedArrows}, the number of walks in a finite face of~$\NKC$ is bounded by~$|Q_1\blossom|+s_\infty$, where~$s_\infty$ is the number of infinite straight walks (i.e.
-the number of oriented cycles in~$Q$).
+the number of primitive oriented cycles in~$Q$).
 
@@
 \vincent{This is wrong. We need to count the infinite straight walks. I propose the next statement instead.}
-\pierreguy{I agree.}
 \end{proposition}
@@
 The reduced non-kissing complex~$\RNKC$ and the reduced non-crossing complex~$\RNCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$ are pure of dimension~$|Q_0|$.
-The non-kissing complex~$\NKC$ and the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$ are pure of dimension~$3|Q_0| - |Q_1| + p$ where~$p$ is the number of oriented cycles in~$\bar Q$ or equivalently the number of punctures in~$\surface_{\bar Q}$.
+The non-kissing complex~$\NKC$ and the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$ are pure of dimension~$3|Q_0| - |Q_1| + p$ where~$p$ is the number of primitive oriented cycles in~$\bar Q$ or equivalently the number of punctures in~$V_Q$ in~$\surface_{\bar Q}$.
 \end{proposition}
@@
 \label{lem:walksThroughcycles}
-For any oriented cycle~$c$ in~$\bar Q$, any maximal non-kissing face contains a walk of the form~$\sigma c^\infty$ or~$c^\infty\sigma$, for some substring~$\sigma$ distinct from~$c^\infty$.
+For any oriented cycle~$c$ in~$Q$ with~$c, c^2\notin I$, any maximal non-kissing face contains a walk of the form~$\sigma c^{\varepsilon\infty}$, for some~$\varepsilon\in\{\pm1\}$ and some substring~$\sigma$ distinct from~$^{\varepsilon\infty}c$.
 \end{lemma}
@@
 We can now moreover assume that~$\lambda = \distinguishedWalk{\alpha}{F}$.
-If~$\lambda$ starts or ends by~$c^\infty$, then we have found a walk of the desired form.
+If~$\lambda$ starts by~$^\infty c$, or ends by~$c^\infty$, then we have found a walk of the desired form.
 Otherwise, decompose this walk as~$\lambda = \lambda_1 \alpha \lambda_2$ and consider the walk~$\omega = \lambda_1 c^\infty$.
@@
 Since each finite straight walk uses two blossom arrows, we have~$s = 2|Q_0|-|Q_1|$ (see Remark~\ref{rem:sizeBlossomingQuiver}).
-Moreover, the infinite straight walks are just the oriented cycles in~$\bar Q$.
+Moreover, the infinite straight walks are just the primitive oriented cycles in~$\bar Q$.
+
 Using Proposition~\ref{prop:numberOfDistinguishedArrows}, we obtain by double-counting that

### 2018-07-09 draft/accordionComplexSurfaces.tex

@@
 
+The curves~$\curveof(\omega)$ and~$\curveof(\omega')$ on the surface follow~$\omega$ and~$\omega'$ on the picture.
+It is then clear that~$\omega$ and~$\omega'$ kiss if and only if~$\curveof(\omega)$ and~$\curveof(\omega')$ cross. 
 \end{proof}
@@
 The aim of this section is to prove the following purity result.
-
-\begin{proposition}
-\label{prop:purity}
-The non-kissing complex~$\NKC$ and the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$ are pure of dimension~$3|Q_0| - |Q_1|$.
-\vincent{This is wrong. We need to count the infinite straight walks. I propose the next statement instead.}
-\end{proposition}
 
@@
 \para{Geometric proof}
+The statement of the lemma translates on~$\surface(\bar Q)$ as follows: for any facet~$F$ of the non-crossing complex~$\NCC$ and any puncture of the dissection~$\dissection_{\bar Q}$, there exists a curve in~$F$ which goes to the puncture.
+Assume that there is a puncture with no curves of~$F$ going to it.
+Construct a curve~$\gamma$ as follows:~$\gamma$ first unwinds from the puncture, then~$\gamma$ leaves the local picture around the puncture by turning aroune another marked point (marked~$X$ on the picture below).
+
+\includegraphics{pgFigNo7.pdf}
+\pierreguy{Pic No 7 here.}
+Two situations occur.
+
+Firstly, if there are no curves of~$F$ closer to~$X$ than~$\gamma$, then~$\gamma$ can circle around~$X$ until it reaches the boundary (if~$X$ is on the boundary) or infinitely (if~$X$ is a puncture).
+Then~$\gamma$ is a~$\dissection_{\bar Q}$-accordion which crosses none of those in~$F$, contradicting the maximality of~$F$.
+
+Secondly, if there is a curve of~$F$ closer to~$X$ than~$\gamma$, then let~$\delta$ be the one furthest from~$X$ ($\delta$ exists by Lemma \ref{lemm:facesHaveMaximalElement}).
+From there, let~$\gamma$ follow~$\delta$ on the surface until it either reaches the boundary or circles infinitely around a puncture.  
+Then~$\gamma$ is compatible with all curves in~$F$, a contradiction.
+
+Thus~$F$ contains a curve going to the puncture.
 \vincent{Should we also give here a geometric argument? Pierre-Guy, could you add that?}
+\pierreguy{Done; I will need a picture, please, Vincent.}
 

### 2018-07-10 draft/accordionComplexSurfaces.tex
Some pictures.
beginning of g-vectors in Orsay

@@
 
-\includegraphics{pgFigNo8.pdf}
+\includegraphics{infiniteCurve2.pdf}
 
@@
 
-\includegraphics{pgFigNo7.pdf}
+\includegraphics{infiniteCurve1.pdf}
+
 \pierreguy{Pic No 7 here.}
@@
 
+In this section, we recall some results from Section 4.2 of~\cite{PaluPilaudPlamondon} that immediately generalise to the case of locally gentle algebras.
+We show that our geometric model using accordions is well-adapted to computing~$\b{c}$-vectors, while slaloms can naturally be interpreted as~$\b{g}$- vectors.
+The duality between~$\b{g}$-vectors and~$\b{c}$-vectors then follows from the duality between the two dissections~$\dissection_Q$ and~$\dissection\dual_Q$.
+\yann{check the lattest assertion}
+
+\subsection{$\b{g}$-vectors and $\b{c}$-vectors}
+\label{subsec:gcvectors}
+
+Let~$\bar Q = (Q,I)$ be a locally gentle bound quiver, and let~$(\b{e}_v)_{v \in Q_0}$ be the standard basis of~$\R^{Q_0}$.
+
+\begin{definition}
+For a multiset~$V \eqdef \{v_1, \dots, v_m\}$ of vertices of~$Q_0$, we denote by~$\multiplicityVector_V \in \R^{Q_0}$ the \defn{multiplicity vector} of~$V$ defined~by
+\[
+\multiplicityVector_V \eqdef \sum_{i \in [m]} \b{e}_{v_i} = \sum_{v \in Q_0} |\set{i \in [m]}{v_i = v}| \, \b{e}_v.
+\]
+For a string~$\sigma \in \strings^\pm(\bar Q)$, we define~$\multiplicityVector_\sigma \eqdef \multiplicityVector_{V(\sigma)}$ where~$V(\sigma)$ is the multiset of vertices of~$\sigma$. 
+\end{definition}
+
+We now recall two definitions from~\cite{PaluPilaudPlamondon}, that still make sense for locally gentle algebras.
+
+\begin{definition}\label{def: g-vectors for walks}
+For a walk~$\omega \in \NKWalks^\pm(\bar Q)$, we denote by~$\peaks{\omega}$ (resp.~by~$\deeps{\omega}$) the multiset of vertices of~$Q_0$ corresponding to the peaks (resp.~deeps) of~$\omega$.
+The \defn{$\b{g}$-vector} of a walk~$\omega$ is the vector~${\gvector{\omega} \in \R^{Q_0}}$ defined by
+\[
+\gvector{\omega} \eqdef \multiplicityVector_{\peaks{\omega}} - \multiplicityVector_{\deeps{\omega}}.
+\]
+For a set~$\Omega$ of walks, we let~$\gvectors{\Omega} \eqdef \set{\gvector{\omega}}{\omega \in \Omega}$.
+Observe that~$\gvector{\omega} = 0$ for a straight walk~$\omega$, and that, since for any walk~$\omega$, the strings $\omega$ and $\omega^{-1}$ are eventually direct or inverse, the coordinates of~$\gvector{\omega}$ are finite.
+\end{definition}
+
+\begin{remark}
+Let~$\omega$ be a walk in~$\NKWalks^\pm(\bar Q)$, and let$\sigma$ be the string obtained from~$\omega$ by deleting a left and a right co-hook when possible.
+The the~$\b{g}$-vector of the walk~$\omega$ coincide with the~$\b{g}$-vector of the (finitely generated) string module associated with the string~$\sigma$.
+\end{remark}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-07-10 draft/accordionComplexSurfaces.tex
Captions of figures.

@@
 An oriented cycle~$c$ corresponds to a puncture in~$\dissection_{\bar Q}$.
-Let~$\gamma = \curveof(\omega)$.  The fact that~$\omega$ contains~$c$ translates to the fact that~$\gamma$ makes a full circle around the correponding puncture.
-\pierreguy{Pic No 8 here.}
-
-\includegraphics{infiniteCurve2.pdf}
+Let~$\gamma = \curveof(\omega)$.  The fact that~$\omega$ contains~$c$ translates to the fact that~$\gamma$ makes one full circle around the correponding puncture.
+
+\begin{figure}[h]
+	\capstart
+	\centerline{\includegraphics[scale=1]{infiniteCurve2.pdf}}
+	\caption{The arc~$\gamma$ makes at least one full circle around the puncture.}
+	\label{fig:aroundPuncture1}
+\end{figure}
 
@@
 Assume that there is a puncture with no curves of~$F$ going to it.
-Construct a curve~$\gamma$ as follows:~$\gamma$ first unwinds from the puncture, then~$\gamma$ leaves the local picture around the puncture by turning aroune another marked point (marked~$X$ on the picture below).
-
-\includegraphics{infiniteCurve1.pdf}
-
-\pierreguy{Pic No 7 here.}
-Two situations occur.
+Construct a curve~$\gamma$ as follows:~$\gamma$ first unwinds from the puncture, then~$\gamma$ leaves the local picture around the puncture by turning around another marked point (marked~$X$ on the picture below).
+
+\begin{figure}[h]
+	\capstart
+	\centerline{\includegraphics[scale=1]{infiniteCurve1.pdf}}
+	\caption{The arc~$\gamma$ leaving the puncture.}
+	\label{fig:aroundPuncture2}
+\end{figure}
+
+Two situations can occur.
 

### 2018-07-10 draft/accordionComplexSurfaces.tex
brouillon g-vectors

--- 2018-07-10 draft/accordionComplexSurfaces.tex
@@
 We show that our geometric model using accordions is well-adapted to computing~$\b{c}$-vectors, while slaloms can naturally be interpreted as~$\b{g}$- vectors.
-The duality between~$\b{g}$-vectors and~$\b{c}$-vectors then follows from the duality between the two dissections~$\dissection_Q$ and~$\dissection\dual_Q$.
+The duality between~$\b{g}$-vectors and~$\b{c}$-vectors then follows from the duality between the two dissections~$\dissection_{\bar Q}$ and~$\dissection\dual_{\bar Q}$.
 \yann{check the lattest assertion}
@@
 \begin{remark}
-Let~$\omega$ be a walk in~$\NKWalks^\pm(\bar Q)$, and let$\sigma$ be the string obtained from~$\omega$ by deleting a left and a right co-hook when possible.
-The the~$\b{g}$-vector of the walk~$\omega$ coincide with the~$\b{g}$-vector of the (finitely generated) string module associated with the string~$\sigma$.
+Let~$\omega$ be a walk in~$\NKWalks^\pm(\bar Q)$, and let $\sigma$ be the string obtained from~$\omega$ by deleting a left and a right co-hook when possible.
+Then the~$\b{g}$-vector of the walk~$\omega$ coincide with the~$\b{g}$-vector of the (finitely generated) string module associated with the string~$\sigma$.
 \end{remark}
+
+\begin{definition}\label{def: c-vectors for walks}
+Let~$\omega$ be a walk in a non-kissing facet~$F \in \RNKC$.
+Define
+\[
+\distinguishedSign{\omega}{F} \eqdef 
+\begin{cases}
+\phantom{-}1 & \text{if~$\distinguishedString{\omega}{F}$ is a top substring of~$\omega$ (\ie the arrows~$\distinguishedArrows{\omega}{F}$ point outside),} \\
+-1 & \text{if~$\distinguishedString{\omega}{F}$ is a bottom substring of~$\omega$ (\ie if the arrows~$\distinguishedArrows{\omega}{F}$ point inside).}
+\end{cases}
+\]
+The \defn{$\b{c}$-vector} of a walk~$\omega$ of~$F$ is the vector~${\cvector{\omega}{F} \in \R^{Q_0}}$ defined by
+\[
+\cvector{\omega}{F} \eqdef \distinguishedSign{\omega}{F} \, \multiplicityVector_{\distinguishedString{\omega}{F}}.
+\]
+We let~$\cvectors{F} \eqdef \set{\cvector{\omega}{F}}{\omega \in F}$ be the set of $\b{c}$-vectors of a non-kissing facet~$F \in \RNKC$, and~$\allcvectors \eqdef \bigcup_F \cvectors{F}$ be the set of all $\b{c}$-vectors of all non-kissing facets~${F \in \RNKC}$.
+\end{definition}
+
+\begin{remark}
+\label{rem:signCoherence}
+The definitions of $\b{g}$- and $\b{c}$-vectors immediately imply the \defn{sign-coherence property}: for any non-kissing facet~$F \in \RNKC$,
+\begin{itemize}
+\item for any~$\omega \in F$, all coordinates of the $\b{c}$-vector~$\cvector{\omega}{F}$ have the same sign,
+\item for~$v \in Q_0$, the~$v$th coordinates of all $\b{g}$-vectors~$\gvector{\omega}$ for~$\omega \in F$ have the same sign (otherwise, the corresponding walks would kiss at~$v$).
+\end{itemize}
+In particular, a $\b{c}$-vector is called \defn{positive} when all its coordinates are non-negative and \defn{negative} when all its coordinates are non-positive.
+\end{remark}
+
+\begin{proposition}
+\label{prop:gvectorscvectorsDualBases}
+For any non-kissing facet~$F \in \RNKC$, the set of $\b{g}$-vectors~$\gvectors{F}$ and the set of $\b{c}$-vectors~$\cvectors{F}$ form dual bases. 
+\end{proposition}
+
+\begin{proof}
+Noting that the distinguished string of a walk in a given non-kissing facet is always a finite substring, the proof of~\cite[Proposition 4.16]{PaluPilaudPlamondon} applies \emph{verbatim}.
+\end{proof}
+
+Recall that there is a fixed bijection between the vertices of~$Q$, the arc in the dissection~$\dissection_{\bar Q}$ and the arcs in the dual dissection~$\dissection^\dual_{\bar Q}$.
+
+\begin{definition}\label{def: c-vectors for accordions}
+Let~$\alpha$ be a~$\dissection_{\bar Q}$-accordion in a non-crossing facet~$F$ of~$\RNCC$.
+The distinguished curve of~$\alpha$ in~$F$ is the part of~$\alpha$ which lies strictly between the two angles of~$\dissection_{\bar Q}$ where~$\alpha$ is maximal (see Remark~\ref{rema:countercurrentOrderOnSurface}).
+The~$\b{c}$-vector of~$\alpha$ in~$F$ is the vector in~$\R^{Q_0}$ counting the number of crossings between the dinstinguished curve of~$\alpha$ in~$F$ and the arcs of the dissection~$\dissection_{\bar Q}$.
+\end{definition}
+
+\begin{definition}\label{def: g-vectors for slaloms}
+Let~$\alpha$ be a~$\dissection\dual_{\bar Q}$-slalom.
+The~$\b{g}$-vector of~$\alpha$ is the vector in~$\R^{Q_0}$ counting the number of times that~$\alpha$ positively crosses each arc of~$\dissection\dual_{\bar Q}$ minus the number of times it crosses each arc negatively.
+Here, a crossing is positive when~$\alpha$ leaves a face~$f^\dual$ to enter a face~$g^\dual$ with the vertex~$f$ being to its right (and thus with~$g$ being to its left).
+Otherwise, the crossing is negative.
+\end{definition}
+
+\yann{Ajouter une phrase pour mettre en avant cette proposition}
+
+\begin{proposition}\label{prop: geometric interpretation of g- and c-vectors}
+ Let~$\omega$ be a non-kissing walk in~$\bar Q$, and let~$\alpha$ be the corresponding curve on~$\surface(\bar Q)$, as in Definition~\ref{def:curveOfAWalk}.
+ Recall from Lemma~\ref{lemm:curveOfAWalkIsAccordion} and Proposition~\ref{prop:accordionsSlaloms} that~$\alpha$ is both a~$\dissection_{\bar Q}$-accordion and a~$\dissection^\dual_{\bar Q}$-slalom.
+ Let~$F$ be a non-kissing facet to which~$\omega$ belong.
+ We also write~$F$ for the corresponding non-crossing facet in the slalom complex.
+ Then:
+ \begin{enumerate}
+  \item The~$\b{g}$-vectors of the walk~$\omega$ and the accordion~$\alpha$ coincide.
+  \item The~$\b{c}$-vectors of the walk~$\omega$ in~$F$ and the slalom~$\alpha$ in~$F$ concide.
+ \end{enumerate}
+\end{proposition}
+
+\begin{proof}
+Definitions~\ref{def: c-vectors for accordions} and~\ref{def: g-vectors for slaloms} are immediate translations in terms of curves on the surface~$\surface(\bar Q)$ of Definitions~\ref{def: c-vectors for walks} and~\ref{def: g-vectors for walks} respectively.
+\end{proof}
+
+\begin{remark}
+Proposition~\ref{prop: geometric interpretation of g- and c-vectors} gives a new proof of Proposition~\ref{prop:gvectorscvectorsDualBases}: \yann{To Do}
+\end{remark}
+
+\begin{definition}
+The \defn{$\b{g}$-vector fan} of~$\bar Q$ is the collection of cones
+\[
+\gvectorFan \eqdef \bigset{\R_{\ge0} \gvectors{F}}{F \text{ non-kissing face of } \RNKC}.
+\]
+\end{definition}
+
+\yann{Th 4.17 and Th 4.27 of [PPP1] seem to apply as such here. Vincent?}
+Theorem 4.17 and Theorem 4.27 of~\cite{PaluPilaudPlamondon} hold for locally gentle algebras, with the same proofs:
+
+\begin{theorem}
+Let~$\bar Q$ be a locally gentle bound quiver. Then: 
+\begin{enumerate}
+ \item the~$\b{g}$-vector fan of~$\bar Q$ is a complete simplicial fan;
+ \item If moreover~$\NKC$ is finite, then $\gvectorFan$ is the normal fan of the~$\bar Q$-associahedron.
+\end{enumerate}
+\end{theorem}
 

### 2018-07-10 draft/accordionComplexSurfaces.tex
remove ^ before \dual

@@
 
-Recall that there is a fixed bijection between the vertices of~$Q$, the arc in the dissection~$\dissection_{\bar Q}$ and the arcs in the dual dissection~$\dissection^\dual_{\bar Q}$.
+Recall that there is a fixed bijection between the vertices of~$Q$, the arc in the dissection~$\dissection_{\bar Q}$ and the arcs in the dual dissection~$\dissection\dual_{\bar Q}$.
 
@@
 The~$\b{g}$-vector of~$\alpha$ is the vector in~$\R^{Q_0}$ counting the number of times that~$\alpha$ positively crosses each arc of~$\dissection\dual_{\bar Q}$ minus the number of times it crosses each arc negatively.
-Here, a crossing is positive when~$\alpha$ leaves a face~$f^\dual$ to enter a face~$g^\dual$ with the vertex~$f$ being to its right (and thus with~$g$ being to its left).
+Here, a crossing is positive when~$\alpha$ leaves a face~$f\dual$ to enter a face~$g\dual$ with the vertex~$f$ being to its right (and thus with~$g$ being to its left).
 Otherwise, the crossing is negative.
@@
  Let~$\omega$ be a non-kissing walk in~$\bar Q$, and let~$\alpha$ be the corresponding curve on~$\surface(\bar Q)$, as in Definition~\ref{def:curveOfAWalk}.
- Recall from Lemma~\ref{lemm:curveOfAWalkIsAccordion} and Proposition~\ref{prop:accordionsSlaloms} that~$\alpha$ is both a~$\dissection_{\bar Q}$-accordion and a~$\dissection^\dual_{\bar Q}$-slalom.
+ Recall from Lemma~\ref{lemm:curveOfAWalkIsAccordion} and Proposition~\ref{prop:accordionsSlaloms} that~$\alpha$ is both a~$\dissection_{\bar Q}$-accordion and a~$\dissection\dual_{\bar Q}$-slalom.
  Let~$F$ be a non-kissing facet to which~$\omega$ belong.

### 2018-07-10 draft/accordionComplexSurfaces.tex
infinite words

@@
 \begin{itemize}
- \item $^\infty c$ for the infinite word:~$\cdots c c c$;
- \item $c^\infty$ for the word:~$c c c\cdots$;
- \item $^{-\infty} c$ for the infinite word:~$\cdots c^{-1} c^{-1} c^{-1}$;
- \item $c^{-\infty}$ for the word:~$c^{-1} c^{-1} c^{-1}\cdots$ and
- \item $^\infty c^\infty$ for the word:~$^\infty c c^\infty$.
-\end{itemize}
+ \item ${}^\infty c$ for the infinite word~$\cdots c c c$,
+ \item $c^\infty$ for the infinite word~$c c c\cdots$,
+% \item $^{-\infty} c$ for the infinite word~$\cdots c^{-1} c^{-1} c^{-1}$,
+% \item $c^{-\infty}$ for the infinite word~$c^{-1} c^{-1} c^{-1}\cdots$, and
+ \item $^\infty c^\infty$ for the bi-infinite word~$^\infty c c^\infty$.
+\end{itemize}
+We also define~${}^{-\infty}c \eqdef (c^\infty)^{-1}$ and similarly~$c^{-\infty} \eqdef (^\infty c)^{-1}$.
 \end{notation}
 
-We note that~$(c^\infty)^{-1} =\,^{-\infty}c$ and similarly~$(^\infty c)^{-1} = c^{-\infty}$.
-
 \begin{definition}
 An \defn{eventually cyclic string} for~$\bar Q$ is a word~$\rho$ of the form~$^{\pm\infty}c_1\sigma c_2^{\pm\infty}$, where $c_1,c_2$ are oriented cycles in~$\bar Q$ (possibly of length zero), $c_1, c_1^2, c_2, c_2^2\notin I$, and~$\sigma$ is a finite string.
+\vincent{We also want $c_1\sigma \notin I$ or $c_1^{-1} \notin I$ depending on what we have...}
 In case~$\rho=\,^{\pm\infty}c_1\sigma c_2^{\infty}$, it is called \defn{eventually direct}, and \defn{eventually inverse} if~$\rho=\,^{\pm\infty}c_1\sigma c_2^{-\infty}$.
@@
 \begin{remark}
- The terminology in the previous definition is borrowed from~\ref{Crawley-Boevey}.
+ The terminology in the previous definition is borrowed from~\cite{Crawley-Boevey}.
  Note however that our choice of convention differs from \emph{loc. cit.}, resulting in exchanging ``inverse'' and ``direct''.

### 2018-07-10 draft/accordionComplexSurfaces.tex
strings

@@
 The non-kissing complex is constructed using the combinatorics of strings and walks in the quiver~$\bar Q$, whose definitions are now briefly recalled.
+The terminology in the following definitions is borrowed from~\cite{ButlerRingel, Crawley-Boevey}.
 
@@
 For each vertex~$v \in Q_0$, there is also a \defn{string of length zero}, denoted by~$\varepsilon_v$, that starts and ends at~$v$.
-We note that there is only one string of length 
 %We denote by~$\strings(\bar Q)$ the set of strings on~$\bar Q$.
 %We usually denote strings by~$\rho, \sigma, \tau$.
-
 %We call \defn{negative simple string} a formal word of length zero of the form $-v$, where $v$ is any vertex of $Q_0$. We denote by
@@
 \end{itemize}
-We also define~${}^{-\infty}c \eqdef (c^\infty)^{-1}$ and similarly~$c^{-\infty} \eqdef (^\infty c)^{-1}$.
+We also define~${}^{-\infty}c \eqdef {}^{\infty}(c^{-1}) = (c^\infty)^{-1}$ and similarly~$c^{-\infty} \eqdef (c^{-1})^\infty = (^\infty c)^{-1}$.
 \end{notation}
@@
 \begin{definition}
-An \defn{eventually cyclic string} for~$\bar Q$ is a word~$\rho$ of the form~$^{\pm\infty}c_1\sigma c_2^{\pm\infty}$, where $c_1,c_2$ are oriented cycles in~$\bar Q$ (possibly of length zero), $c_1, c_1^2, c_2, c_2^2\notin I$, and~$\sigma$ is a finite string.
-\vincent{We also want $c_1\sigma \notin I$ or $c_1^{-1} \notin I$ depending on what we have...}
-In case~$\rho=\,^{\pm\infty}c_1\sigma c_2^{\infty}$, it is called \defn{eventually direct}, and \defn{eventually inverse} if~$\rho=\,^{\pm\infty}c_1\sigma c_2^{-\infty}$.
-\end{definition}
-
-\begin{remark}
- The terminology in the previous definition is borrowed from~\cite{Crawley-Boevey}.
- Note however that our choice of convention differs from \emph{loc. cit.}, resulting in exchanging ``inverse'' and ``direct''.
-\end{remark}
+An \defn{eventually cyclic string} for~$\bar Q$ is a word~$\rho$ of the form~${}^\infty(c_1^{\varepsilon_1})\sigma (c_2^{\varepsilon_2})^\infty$, where $c_1, c_2$ are oriented cycles in~$\bar Q$ (possibly of length zero) and $\varepsilon_1, \varepsilon_2$ are signs in~$\{\pm 1\}$ such that $c_1^{2\varepsilon_1} \sigma c_2^{2\varepsilon_2}$ is a finite chord.
+%In case~$\rho=\,^{\pm\infty}c_1\sigma c_2^{\infty}$, it is called \defn{eventually direct}, and \defn{eventually inverse} if~$\rho=\,^{\pm\infty}c_1\sigma c_2^{-\infty}$.
+\end{definition}
 
@@
 A \defn{string} for~$\bar Q$ is a word which is either a finite string or an eventually cyclic infinite string.
+We denote by~$\strings(\bar Q)$ the set of strings on~$\bar Q$.
 We often implicitly identify the two inverse strings~$\rho$ and~$\rho^{-1}$, and we let~$\strings^\pm(\bar Q) \eqdef \set{\{\rho, \rho^{-1}\}}{\rho \in \strings(\bar Q)}$ denote the collection of all \defn{undirected strings} of~$\bar Q$.

### 2018-07-10 draft/accordionComplexSurfaces.tex
definition substring

@@
 
+\begin{notation}
+To avoid distinguishing between finite, infinite and bi-infinite words, we denote strings as products~$\rho = \prod_{i < \ell < j} \alpha_\ell$ where~$i < j \in \Z \cup \{\pm \infty\}$ and~$\alpha_\ell \in Q_0$.
+\end{notation}
+
 \begin{definition}
@@
 \label{def:substrings}
-A \defn{substring} of a walk~$\omega =\cdots \alpha_{-r}^{\varepsilon_{-r}}\cdots\alpha_0^{\varepsilon_0} \alpha_1^{\varepsilon_1} \cdots \alpha_\ell^{\varepsilon_\ell}\cdots \in \walks(\bar Q)$ is a string~$\sigma = \alpha_i^{\varepsilon_i} \dots \alpha_j^{\varepsilon_j}$ of~$\strings(\bar Q)$ for some~$i \le j \in \mathbb{Z}\cup\{\pm\infty\}$, where moreover
+A \defn{substring} of a walk~$\omega = \prod_{i < \ell < j} \alpha_\ell^{\varepsilon_\ell} \in \walks(\bar Q)$ is a string~$\sigma = \prod_{i' < \ell < j'} \alpha_\ell^{\varepsilon_\ell}$ of~$\strings(\bar Q)$ for some~$i \le i' < j' \le j$, where the inequality~$i \le i'$ (resp.~$j' \le j$) is strict when~$i \ne -\infty$ (resp.~$j \ne \infty$).
+In other words, $\sigma$ is a factor of~$\omega$ such that
 \begin{itemize}
@@
 Note that the string~$\varepsilon_v$ is a substring of~$\omega$ for each occurence of~$v$ as a vertex of~$\omega$.
-The substring~$\sigma = \alpha_i^{\varepsilon_i} \dots \alpha_j^{\varepsilon_j}$ is \defn{at the bottom} (resp.~\defn{on top}) of the walk~$\omega = \alpha_1^{\varepsilon_1} \dots \alpha_\ell^{\varepsilon_\ell}$ if~$i=-\infty$ or~$\varepsilon_{i-1} = 1$ and~$j=+\infty$ or~$\varepsilon_{j+1} = -1$ (resp.~if~$i=-\infty$ or~$\varepsilon_{i-1} = -1$ and~$i=-\infty$ or~$\varepsilon_{j+1} = 1$), that is, the (at most) two arrows of~$\omega$ incident to the endpoints of~$\sigma$ point towards~$\sigma$ (resp.~outwards from~$\sigma$).
+\end{definition}
+
+\begin{definition}
+\label{def:topBottom}
+The substring~$\sigma = \alpha_i^{\varepsilon_i} \dots \alpha_j^{\varepsilon_j}$ is \defn{at the bottom} (resp.~\defn{on top}) of the walk~$\omega = \cdots \alpha_1^{\varepsilon_1} \dots \alpha_\ell^{\varepsilon_\ell} \cdots $ if~$i=-\infty$ or~$\varepsilon_{i-1} = 1$ and~$j=+\infty$ or~$\varepsilon_{j+1} = -1$ (resp.~if~$i=-\infty$ or~$\varepsilon_{i-1} = -1$ and~$j=\infty$ or~$\varepsilon_{j+1} = 1$), that is, the (at most) two arrows of~$\omega$ incident to the endpoints of~$\sigma$ point towards~$\sigma$ (resp.~outwards from~$\sigma$).
 We let~$\Sigma(\omega)$ be the set of substrings of~$\omega$ and~$\Sigma_\bottom(\omega)$ and~$\Sigma_\top(\omega)$ be the sets of bottom and top substrings of~$\omega$ respectively.

### 2018-07-10 draft/accordionComplexSurfaces.tex
typos

--- 2018-07-10 draft/accordionComplexSurfaces.tex
@@
 The~$\b{g}$-vector of~$\alpha$ is the vector in~$\R^{Q_0}$ counting the number of times that~$\alpha$ positively crosses each arc of~$\dissection\dual_{\bar Q}$ minus the number of times it crosses each arc negatively.
-Here, a crossing is positive when~$\alpha$ leaves a face~$f\dual$ to enter a face~$g\dual$ with the vertex~$f$ being to its right (and thus with~$g$ being to its left).
+Here, a crossing is positive when~$\alpha$ leaves a face~$u\dual$ to enter a face~$v\dual$ with the vertex~$u$ being to its right (and thus with~$v$ being to its left).
 Otherwise, the crossing is negative.

### 2018-07-10 draft/accordionComplexSurfaces.tex
definition top/bottom

--- 2018-07-10 draft/accordionComplexSurfaces.tex
@@
 Note that the string~$\varepsilon_v$ is a substring of~$\omega$ for each occurence of~$v$ as a vertex of~$\omega$.
+We denote by~$\Sigma(\omega)$ the set of substrings of~$\omega$.
+We use the same notation for undirected walks (of course, substrings of an undirected walk are undirected).
 \end{definition}
@@
 \label{def:topBottom}
-The substring~$\sigma = \alpha_i^{\varepsilon_i} \dots \alpha_j^{\varepsilon_j}$ is \defn{at the bottom} (resp.~\defn{on top}) of the walk~$\omega = \cdots \alpha_1^{\varepsilon_1} \dots \alpha_\ell^{\varepsilon_\ell} \cdots $ if~$i=-\infty$ or~$\varepsilon_{i-1} = 1$ and~$j=+\infty$ or~$\varepsilon_{j+1} = -1$ (resp.~if~$i=-\infty$ or~$\varepsilon_{i-1} = -1$ and~$j=\infty$ or~$\varepsilon_{j+1} = 1$), that is, the (at most) two arrows of~$\omega$ incident to the endpoints of~$\sigma$ point towards~$\sigma$ (resp.~outwards from~$\sigma$).
-We let~$\Sigma(\omega)$ be the set of substrings of~$\omega$ and~$\Sigma_\bottom(\omega)$ and~$\Sigma_\top(\omega)$ be the sets of bottom and top substrings of~$\omega$ respectively.
-We use the same notations for undirected walks (of course, substrings of an undirected walk are undirected).
+The substring~$\sigma = \prod_{i' < \ell < j'} \alpha_\ell^{\varepsilon_\ell}$ is \defn{at the bottom} (resp.~\defn{on top}) of the walk~$\omega = \prod_{i < \ell < j} \alpha_\ell^{\varepsilon_\ell}$ if~$i'=-\infty$ or~$\varepsilon_{i'-1} = 1$ and~$j'=+\infty$ or~$\varepsilon_{j'+1} = -1$ (resp.~if~$i'=-\infty$ or~$\varepsilon_{i'-1} = -1$ and~$j'=\infty$ or~$\varepsilon_{j'+1} = 1$).
+In other words the (at most) two arrows of~$\omega$ incident to the endpoints of~$\sigma$ point towards~$\sigma$ (resp.~outwards from~$\sigma$).
+We denote by~$\Sigma_\bottom(\omega)$ and~$\Sigma_\top(\omega)$ the sets of bottom and top substrings of~$\omega$ respectively.
+We use the same notations for undirected walks.
 \end{definition}

### 2018-07-10 draft/accordionComplexSurfaces.tex
typos

@@
 We show that our geometric model using accordions is well-adapted to computing~$\b{c}$-vectors, while slaloms can naturally be interpreted as~$\b{g}$- vectors.
-The duality between~$\b{g}$-vectors and~$\b{c}$-vectors then follows from the duality between the two dissections~$\dissection_{\bar Q}$ and~$\dissection\dual_{\bar Q}$.
-\yann{check the lattest assertion}
 
@@
 
-\begin{remark}
-Proposition~\ref{prop: geometric interpretation of g- and c-vectors} gives a new proof of Proposition~\ref{prop:gvectorscvectorsDualBases}: \yann{To Do}
-\end{remark}
-
 \begin{definition}

### 2018-07-10 draft/accordionComplexSurfaces.tex
Introduction.

@@
 \section{Introduction}
-
+\pierreguy{Should we talk of g,c,d-vectors in the abstract?}
 The aim of this paper is to prove that two combinatorial objects, called the \emph{non-kissing complex} and the \emph{non-crossing complex}, are isomorphic.
@@
 
-Gentle algebras were...
-
-Dissections algebras were...
-
-Algebras and dissections have lived together before... (mention clusters)
+Gentle algebras are a class of finite-dimensional associative algebras over a field defined by generators and relations.
+Their representation theory was first systematically investigated in \cite{ButlerRingel}, and they have been thouroughly studied since.
+Locally gentle algebras are obtained by dropping the requirement that gentle algebras be finite-dimensional.
+It turns out that their representations theory is also well-behaved \cite{Crawley-Boevey} and that these algebras are Koszul \cite{BessenrodtHolm}.
+Recently, the $\tau$-tilting theory \cite{AdachiIyamaReiten} of gentle algebra has been studied in \cite{PaluPilaudPlamondon, BrustleDouvilleMousavandThomasYildirim}.
+
+Dissections of surfaces, on the other hand, are certain collections of pairwise non-intersecting curves on an orientable surface.
+They have been defined in studied in \cite{Baryshnikov, Chapoton-quadrangulations, GarverMcConville, MannevillePilaud-accordion} in the case where the surface is an unpunctured disk.
+
+The idea of associating a finite-dimensional algebra to a dissection (or a triangulation) of a surface seems to take its roots in the theory of cluster algebras and cluster categories.
+This was first done for triangulations of polygons in \cite{CalderoChapotonSchiffler}, and then for any orientable surface with boundary in \cite{ABCP, Labardini}.  
+The algebra of a dissection as we shall use it in this paper has appeared in \cite{DavidRoeslerSchiffler}.
+In most of the above cases, the algebras obtained are gentle algebras.
+It has also been shown in \cite{BaurSimoes} that any gentle algebra is obtained from a dissection of a surface, and that the module category of the algebra can be interpreted by using curves on the surface.
+In the case where the surface is a polygon, the $\tau$-tilting theory of the algebra of a dissection has been studied in \cite{PilaudPlamondonStella}.
+
+Conversely, the construction of a surface associated to a gentle algebra has appeared in \cite{OpperPlamondonSchroll}.
+We give a different construction of the same surface in this paper; we note that this surface is usually different than the one found in \cite{BaurSimoes}.
+Remarkably, gentle algebras and surfaces were linked recently in \cite{HaidenKatzarkovKontsevich}, where the Fukaya category of the surface is shown to be equivalent to the bounded derived category of the associated gentle algebra.
+
 \pierreguy{Finish introduction.}
@@
 The non-kissing complex is constructed using the combinatorics of strings and walks in the quiver~$\bar Q$, whose definitions are now briefly recalled.
-The terminology in the following definitions is borrowed from~\cite{ButlerRingel, Crawley-Boevey}.
 
@@
 For each vertex~$v \in Q_0$, there is also a \defn{string of length zero}, denoted by~$\varepsilon_v$, that starts and ends at~$v$.
+We note that there is only one string of length 
 %We denote by~$\strings(\bar Q)$ the set of strings on~$\bar Q$.
 %We usually denote strings by~$\rho, \sigma, \tau$.
+
 %We call \defn{negative simple string} a formal word of length zero of the form $-v$, where $v$ is any vertex of $Q_0$. We denote by
@@
 \begin{itemize}
- \item ${}^\infty c$ for the infinite word~$\cdots c c c$,
- \item $c^\infty$ for the infinite word~$c c c\cdots$,
-% \item $^{-\infty} c$ for the infinite word~$\cdots c^{-1} c^{-1} c^{-1}$,
-% \item $c^{-\infty}$ for the infinite word~$c^{-1} c^{-1} c^{-1}\cdots$, and
- \item $^\infty c^\infty$ for the bi-infinite word~$^\infty c c^\infty$.
-\end{itemize}
-We also define~${}^{-\infty}c \eqdef {}^{\infty}(c^{-1}) = (c^\infty)^{-1}$ and similarly~$c^{-\infty} \eqdef (c^{-1})^\infty = (^\infty c)^{-1}$.
+ \item $^\infty c$ for the infinite word:~$\cdots c c c$;
+ \item $c^\infty$ for the word:~$c c c\cdots$;
+ \item $^{-\infty} c$ for the infinite word:~$\cdots c^{-1} c^{-1} c^{-1}$;
+ \item $c^{-\infty}$ for the word:~$c^{-1} c^{-1} c^{-1}\cdots$ and
+ \item $^\infty c^\infty$ for the word:~$^\infty c c^\infty$.
+\end{itemize}
 \end{notation}
 
-\begin{definition}
-An \defn{eventually cyclic string} for~$\bar Q$ is a word~$\rho$ of the form~${}^\infty(c_1^{\varepsilon_1})\sigma (c_2^{\varepsilon_2})^\infty$, where $c_1, c_2$ are oriented cycles in~$\bar Q$ (possibly of length zero) and $\varepsilon_1, \varepsilon_2$ are signs in~$\{\pm 1\}$ such that $c_1^{2\varepsilon_1} \sigma c_2^{2\varepsilon_2}$ is a finite chord.
-%In case~$\rho=\,^{\pm\infty}c_1\sigma c_2^{\infty}$, it is called \defn{eventually direct}, and \defn{eventually inverse} if~$\rho=\,^{\pm\infty}c_1\sigma c_2^{-\infty}$.
-\end{definition}
+We note that~$(c^\infty)^{-1} =\,^{-\infty}c$ and similarly~$(^\infty c)^{-1} = c^{-\infty}$.
+
+\begin{definition}
+An \defn{eventually cyclic string} for~$\bar Q$ is a word~$\rho$ of the form~$^{\pm\infty}c_1\sigma c_2^{\pm\infty}$, where $c_1,c_2$ are oriented cycles in~$\bar Q$ (possibly of length zero), $c_1, c_1^2, c_2, c_2^2\notin I$, and~$\sigma$ is a finite string.
+In case~$\rho=\,^{\pm\infty}c_1\sigma c_2^{\infty}$, it is called \defn{eventually direct}, and \defn{eventually inverse} if~$\rho=\,^{\pm\infty}c_1\sigma c_2^{-\infty}$.
+\end{definition}
+
+\begin{remark}
+ The terminology in the previous definition is borrowed from~\ref{Crawley-Boevey}.
+ Note however that our choice of convention differs from \emph{loc. cit.}, resulting in exchanging ``inverse'' and ``direct''.
+\end{remark}
 
@@
  A \defn{string} for~$\bar Q$ is a word which is either a finite string or an eventually cyclic infinite string.
-We denote by~$\strings(\bar Q)$ the set of strings on~$\bar Q$.
  We often implicitly identify the two inverse strings~$\rho$ and~$\rho^{-1}$, and we let~$\strings^\pm(\bar Q) \eqdef \set{\{\rho, \rho^{-1}\}}{\rho \in \strings(\bar Q)}$ denote the collection of all \defn{undirected strings} of~$\bar Q$.
 \end{definition}
-
-\begin{notation}
-To avoid distinguishing between finite, infinite and bi-infinite words, we denote strings as products~$\rho = \prod_{i < \ell < j} \alpha_\ell$ where~$i < j \in \Z \cup \{\pm \infty\}$ and~$\alpha_\ell \in Q_0$.
-\end{notation}
 
@@
 \label{def:substrings}
-A \defn{substring} of a walk~$\omega = \prod_{i < \ell < j} \alpha_\ell^{\varepsilon_\ell} \in \walks(\bar Q)$ is a string~$\sigma = \prod_{i' < \ell < j'} \alpha_\ell^{\varepsilon_\ell}$ of~$\strings(\bar Q)$ for some~$i \le i' < j' \le j$, where the inequality~$i \le i'$ (resp.~$j' \le j$) is strict when~$i \ne -\infty$ (resp.~$j \ne \infty$).
-In other words, $\sigma$ is a factor of~$\omega$ such that
+A \defn{substring} of a walk~$\omega =\cdots \alpha_{-r}^{\varepsilon_{-r}}\cdots\alpha_0^{\varepsilon_0} \alpha_1^{\varepsilon_1} \cdots \alpha_\ell^{\varepsilon_\ell}\cdots \in \walks(\bar Q)$ is a string~$\sigma = \alpha_i^{\varepsilon_i} \dots \alpha_j^{\varepsilon_j}$ of~$\strings(\bar Q)$ for some~$i \le j \in \mathbb{Z}\cup\{\pm\infty\}$, where moreover
 \begin{itemize}
@@
 Note that the string~$\varepsilon_v$ is a substring of~$\omega$ for each occurence of~$v$ as a vertex of~$\omega$.
-We denote by~$\Sigma(\omega)$ the set of substrings of~$\omega$.
-We use the same notation for undirected walks (of course, substrings of an undirected walk are undirected).
-\end{definition}
-
-\begin{definition}
-\label{def:topBottom}
-The substring~$\sigma = \prod_{i' < \ell < j'} \alpha_\ell^{\varepsilon_\ell}$ is \defn{at the bottom} (resp.~\defn{on top}) of the walk~$\omega = \prod_{i < \ell < j} \alpha_\ell^{\varepsilon_\ell}$ if~$i'=-\infty$ or~$\varepsilon_{i'-1} = 1$ and~$j'=+\infty$ or~$\varepsilon_{j'+1} = -1$ (resp.~if~$i'=-\infty$ or~$\varepsilon_{i'-1} = -1$ and~$j'=\infty$ or~$\varepsilon_{j'+1} = 1$).
-In other words the (at most) two arrows of~$\omega$ incident to the endpoints of~$\sigma$ point towards~$\sigma$ (resp.~outwards from~$\sigma$).
-We denote by~$\Sigma_\bottom(\omega)$ and~$\Sigma_\top(\omega)$ the sets of bottom and top substrings of~$\omega$ respectively.
-We use the same notations for undirected walks.
+The substring~$\sigma = \alpha_i^{\varepsilon_i} \dots \alpha_j^{\varepsilon_j}$ is \defn{at the bottom} (resp.~\defn{on top}) of the walk~$\omega = \alpha_1^{\varepsilon_1} \dots \alpha_\ell^{\varepsilon_\ell}$ if~$i=-\infty$ or~$\varepsilon_{i-1} = 1$ and~$j=+\infty$ or~$\varepsilon_{j+1} = -1$ (resp.~if~$i=-\infty$ or~$\varepsilon_{i-1} = -1$ and~$i=-\infty$ or~$\varepsilon_{j+1} = 1$), that is, the (at most) two arrows of~$\omega$ incident to the endpoints of~$\sigma$ point towards~$\sigma$ (resp.~outwards from~$\sigma$).
+We let~$\Sigma(\omega)$ be the set of substrings of~$\omega$ and~$\Sigma_\bottom(\omega)$ and~$\Sigma_\top(\omega)$ be the sets of bottom and top substrings of~$\omega$ respectively.
+We use the same notations for undirected walks (of course, substrings of an undirected walk are undirected).
 \end{definition}
@@
 We show that our geometric model using accordions is well-adapted to computing~$\b{c}$-vectors, while slaloms can naturally be interpreted as~$\b{g}$- vectors.
+The duality between~$\b{g}$-vectors and~$\b{c}$-vectors then follows from the duality between the two dissections~$\dissection_Q$ and~$\dissection\dual_Q$.
+\yann{check the lattest assertion}
 
@@
 \begin{remark}
-Let~$\omega$ be a walk in~$\NKWalks^\pm(\bar Q)$, and let $\sigma$ be the string obtained from~$\omega$ by deleting a left and a right co-hook when possible.
-Then the~$\b{g}$-vector of the walk~$\omega$ coincide with the~$\b{g}$-vector of the (finitely generated) string module associated with the string~$\sigma$.
+Let~$\omega$ be a walk in~$\NKWalks^\pm(\bar Q)$, and let$\sigma$ be the string obtained from~$\omega$ by deleting a left and a right co-hook when possible.
+The the~$\b{g}$-vector of the walk~$\omega$ coincide with the~$\b{g}$-vector of the (finitely generated) string module associated with the string~$\sigma$.
 \end{remark}
-
-\begin{definition}\label{def: c-vectors for walks}
-Let~$\omega$ be a walk in a non-kissing facet~$F \in \RNKC$.
-Define
-\[
-\distinguishedSign{\omega}{F} \eqdef 
-\begin{cases}
-\phantom{-}1 & \text{if~$\distinguishedString{\omega}{F}$ is a top substring of~$\omega$ (\ie the arrows~$\distinguishedArrows{\omega}{F}$ point outside),} \\
--1 & \text{if~$\distinguishedString{\omega}{F}$ is a bottom substring of~$\omega$ (\ie if the arrows~$\distinguishedArrows{\omega}{F}$ point inside).}
-\end{cases}
-\]
-The \defn{$\b{c}$-vector} of a walk~$\omega$ of~$F$ is the vector~${\cvector{\omega}{F} \in \R^{Q_0}}$ defined by
-\[
-\cvector{\omega}{F} \eqdef \distinguishedSign{\omega}{F} \, \multiplicityVector_{\distinguishedString{\omega}{F}}.
-\]
-We let~$\cvectors{F} \eqdef \set{\cvector{\omega}{F}}{\omega \in F}$ be the set of $\b{c}$-vectors of a non-kissing facet~$F \in \RNKC$, and~$\allcvectors \eqdef \bigcup_F \cvectors{F}$ be the set of all $\b{c}$-vectors of all non-kissing facets~${F \in \RNKC}$.
-\end{definition}
-
-\begin{remark}
-\label{rem:signCoherence}
-The definitions of $\b{g}$- and $\b{c}$-vectors immediately imply the \defn{sign-coherence property}: for any non-kissing facet~$F \in \RNKC$,
-\begin{itemize}
-\item for any~$\omega \in F$, all coordinates of the $\b{c}$-vector~$\cvector{\omega}{F}$ have the same sign,
-\item for~$v \in Q_0$, the~$v$th coordinates of all $\b{g}$-vectors~$\gvector{\omega}$ for~$\omega \in F$ have the same sign (otherwise, the corresponding walks would kiss at~$v$).
-\end{itemize}
-In particular, a $\b{c}$-vector is called \defn{positive} when all its coordinates are non-negative and \defn{negative} when all its coordinates are non-positive.
-\end{remark}
-
-\begin{proposition}
-\label{prop:gvectorscvectorsDualBases}
-For any non-kissing facet~$F \in \RNKC$, the set of $\b{g}$-vectors~$\gvectors{F}$ and the set of $\b{c}$-vectors~$\cvectors{F}$ form dual bases. 
-\end{proposition}
-
-\begin{proof}
-Noting that the distinguished string of a walk in a given non-kissing facet is always a finite substring, the proof of~\cite[Proposition 4.16]{PaluPilaudPlamondon} applies \emph{verbatim}.
-\end{proof}
-
-Recall that there is a fixed bijection between the vertices of~$Q$, the arc in the dissection~$\dissection_{\bar Q}$ and the arcs in the dual dissection~$\dissection\dual_{\bar Q}$.
-
-\begin{definition}\label{def: c-vectors for accordions}
-Let~$\alpha$ be a~$\dissection_{\bar Q}$-accordion in a non-crossing facet~$F$ of~$\RNCC$.
-The distinguished curve of~$\alpha$ in~$F$ is the part of~$\alpha$ which lies strictly between the two angles of~$\dissection_{\bar Q}$ where~$\alpha$ is maximal (see Remark~\ref{rema:countercurrentOrderOnSurface}).
-The~$\b{c}$-vector of~$\alpha$ in~$F$ is the vector in~$\R^{Q_0}$ counting the number of crossings between the dinstinguished curve of~$\alpha$ in~$F$ and the arcs of the dissection~$\dissection_{\bar Q}$.
-\end{definition}
-
-\begin{definition}\label{def: g-vectors for slaloms}
-Let~$\alpha$ be a~$\dissection\dual_{\bar Q}$-slalom.
-The~$\b{g}$-vector of~$\alpha$ is the vector in~$\R^{Q_0}$ counting the number of times that~$\alpha$ positively crosses each arc of~$\dissection\dual_{\bar Q}$ minus the number of times it crosses each arc negatively.
-Here, a crossing is positive when~$\alpha$ leaves a face~$u\dual$ to enter a face~$v\dual$ with the vertex~$u$ being to its right (and thus with~$v$ being to its left).
-Otherwise, the crossing is negative.
-\end{definition}
-
-\yann{Ajouter une phrase pour mettre en avant cette proposition}
-
-\begin{proposition}\label{prop: geometric interpretation of g- and c-vectors}
- Let~$\omega$ be a non-kissing walk in~$\bar Q$, and let~$\alpha$ be the corresponding curve on~$\surface(\bar Q)$, as in Definition~\ref{def:curveOfAWalk}.
- Recall from Lemma~\ref{lemm:curveOfAWalkIsAccordion} and Proposition~\ref{prop:accordionsSlaloms} that~$\alpha$ is both a~$\dissection_{\bar Q}$-accordion and a~$\dissection\dual_{\bar Q}$-slalom.
- Let~$F$ be a non-kissing facet to which~$\omega$ belong.
- We also write~$F$ for the corresponding non-crossing facet in the slalom complex.
- Then:
- \begin{enumerate}
-  \item The~$\b{g}$-vectors of the walk~$\omega$ and the accordion~$\alpha$ coincide.
-  \item The~$\b{c}$-vectors of the walk~$\omega$ in~$F$ and the slalom~$\alpha$ in~$F$ concide.
- \end{enumerate}
-\end{proposition}
-
-\begin{proof}
-Definitions~\ref{def: c-vectors for accordions} and~\ref{def: g-vectors for slaloms} are immediate translations in terms of curves on the surface~$\surface(\bar Q)$ of Definitions~\ref{def: c-vectors for walks} and~\ref{def: g-vectors for walks} respectively.
-\end{proof}
-
-\begin{definition}
-The \defn{$\b{g}$-vector fan} of~$\bar Q$ is the collection of cones
-\[
-\gvectorFan \eqdef \bigset{\R_{\ge0} \gvectors{F}}{F \text{ non-kissing face of } \RNKC}.
-\]
-\end{definition}
-
-\yann{Th 4.17 and Th 4.27 of [PPP1] seem to apply as such here. Vincent?}
-Theorem 4.17 and Theorem 4.27 of~\cite{PaluPilaudPlamondon} hold for locally gentle algebras, with the same proofs:
-
-\begin{theorem}
-Let~$\bar Q$ be a locally gentle bound quiver. Then: 
-\begin{enumerate}
- \item the~$\b{g}$-vector fan of~$\bar Q$ is a complete simplicial fan;
- \item If moreover~$\NKC$ is finite, then $\gvectorFan$ is the normal fan of the~$\bar Q$-associahedron.
-\end{enumerate}
-\end{theorem}
 

### 2018-07-10 draft/accordionComplexSurfaces.tex
example Cambrian

--- 2018-07-10 draft/accordionComplexSurfaces.tex
@@
 \label{exm:CambrianPath}
-\vincent{TODO: Cambrian paths}
+Consider a \defn{Cambrian quiver}, that is any orientation of a line with no relations (\aka type~$A$ quiver).
+Two such quivers are represented in \fref{fig:CambrianPathsQuivers}.
+Note that we can choose to position the blossom vertices in such a way that for any arrow~$\beta$, the arrows~$\alpha$ and~$\gamma$ such that~$\alpha\beta \in I$ and~$\beta\gamma \in I$ are on the right of~$\beta$.
+
+\begin{figure}[h]
+	\capstart
+	\centerline{\includegraphics[scale=.45]{CambrianPathsQuivers}}
+	\caption{Two Cambrian quivers on~$5$ vertices.}
+	\label{fig:CambrianPathsQuivers}
+\end{figure}
+
+The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}) form a cycle with green and red arrows alternating.
+Moreover, $\bar Q$ and~$\bar Q\koszul$ have no infinite straight walks.
+Since~$|Q_1| = |Q_0|-1$, the corresponding surfaces have $1$ boundary component and genus~$0$.
+Two examples are represented in \fref{fig:reversedPathsSurfaces}.
+Note that the dissection~$\dissection_{\bar Q}$ is a triangulation with no internal triangles, and the orientation of~$\bar Q$ indicates how to glue these triangles.
+For instance, the Cambrian quiver completely oriented in one direction yields a fan triangulation, were all internal arcs are incident to the same vertex, as in \fref{fig:reversedPathsSurfaces}\,(left).
+
+\begin{figure}[h]
+	\capstart
+	\centerline{\includegraphics[scale=.7]{CambrianPathsSurfaces}}
+	\caption{The surface~$\surface_{\bar Q}$ for two Cambrian paths on~$5$ vertices.}
+	\label{fig:CambrianPathsSurfaces}
+\end{figure}
 \end{example}
@@
 Moreover, $\bar Q$ has no infinite straight walk, while~$\bar Q\koszul$ has~$|Q_0|-1$ infinite straight walks.
-Therefore, the corresponding surfaces have $1$ boundary component and genus~$0$.
+Since~$|Q_1| = 2|Q_0|-2$, the corresponding surfaces have $1$ boundary component and genus~$0$.
 The first few corresponding surfaces are represented in \fref{fig:reversedPathsSurfaces}.
@@
 \end{figure}
-
 \end{example}
@@
 Moreover, $\bar Q$ and~$\bar Q\koszul$ have no infinite straight walks.
-Therefore, the corresponding surfaces have no punctures and
+Since~$|Q_1| = 2|Q_0|-2$, the corresponding surfaces have no punctures and
 \begin{itemize}
 \item $1$ boundary component and genus~$(|Q_0|-1)/2$ when~$|Q_0|$ is odd, and 
-\item $2$ boundary components and genus~$|Q_0|/2$ when~$|Q_0|$ is even.
+\item $2$ boundary components and genus~$(|Q_0|-2)/2$ when~$|Q_0|$ is even.
 \end{itemize}
@@
 Moreover, $\bar Q$ has~$1$ infinite straight walk when~$|Q_0|$ is odd and~$2$ when~$|Q_0|$ is even, and~$\bar Q\koszul$ always has~$2$ infinite straight walks.
-Therefore, the corresponding surfaces have no boundary component and
+Since~$|Q_1| = 2|Q_0|$, the corresponding surfaces have no boundary component and
 \begin{itemize}
@@
 \begin{proof}
+We provide two proofs of the lemma.
+One is combinatorial and applies to~$\NKC$, and the other is geometric and applies to~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$.
+
+\para{Combinatorial proof}
 Let~$c=\alpha_1\cdots\alpha_r$ be a non-trivial oriented cycle in some walk~$\omega$, with~$c, c^2\notin I$.
@@
 Once this cycle is completed, since~$\gamma$ cannot cross itself, it has to continue cycling infinitely around the puncture.  This proves the claim.
-\vincent{Should we also give here a geometric argument?}
 \end{proof}
@@
 Thus~$F$ contains a curve going to the puncture.
-\vincent{Should we also give here a geometric argument? Pierre-Guy, could you add that?}
-\pierreguy{Done; I will need a picture, please, Vincent.}
-
 \end{proof}
@@
 \begin{definition}
+\vincent{Mettre la def dans les thm}
 The \defn{$\b{g}$-vector fan} of~$\bar Q$ is the collection of cones

### 2018-07-10 draft/accordionComplexSurfaces.tex
Intro + reference before definition of accordions.

--- 2018-07-10 draft/accordionComplexSurfaces.tex
@@
 Conversely, the construction of a surface associated to a gentle algebra has appeared in \cite{OpperPlamondonSchroll}.
-We give a different construction of the same surface in this paper; we note that this surface is usually different than the one found in \cite{BaurSimoes}.
+We give a different construction of the same surface in this paper, which is obtained by ``glueing'' quadrilaterals to the arrows of the blossoming quiver (as defined in \cite{PaluPilaudPlamondon}, and called ``framed quiver'' in \cite{BrustleDouvilleMousavandThomasYildirim}).
+Our construction has the advantage that it easily yields the two dual dissections of the surface at the same time (the dissection and dual lamination of \cite{OpperPlamondonSchroll}).
+We note that this surface is usually different than the one found in \cite{BaurSimoes}.
 Remarkably, gentle algebras and surfaces were linked recently in \cite{HaidenKatzarkovKontsevich}, where the Fukaya category of the surface is shown to be equivalent to the bounded derived category of the associated gentle algebra.
@@
 %Note that the edges of~$f$ may be on the boundary of the surface.
+
+The following definition generalises the one from \cite{MannevillePilaud-accordion} for the case where~$\bar \surface$ is a disk.  It appears in \cite{BaurSimoes} under the name ``permissible arc''.
+\pierreguy{Is it ok to cite like this?}
 

### 2018-07-10 draft/accordionComplexSurfaces.tex
start changing sect 6

--- 2018-07-10 draft/accordionComplexSurfaces.tex
@@
 
-\section{$\b{g}$-, $\b{c}$- and $\b{d}$-vectors}
+\section{$\b{g}$-vectors, $\b{c}$-vectors, and $\b{d}$-vectors}
 
@@
 
-In this section, we recall some results from Section 4.2 of~\cite{PaluPilaudPlamondon} that immediately generalise to the case of locally gentle algebras.
-We show that our geometric model using accordions is well-adapted to computing~$\b{c}$-vectors, while slaloms can naturally be interpreted as~$\b{g}$- vectors.
-
-\subsection{$\b{g}$-vectors and $\b{c}$-vectors}
-\label{subsec:gcvectors}
+In this section, we define of three relevant families of vectors associated to walks in the non-kissing complex of a locally gentle quiver~$\bar Q$.
+The $\b{g}$- and $\b{c}$-vectors were already considered for gentle algebras in~\cite[Sect.~4.2]{PaluPilaudPlamondon}, and their definition immediately generalizes to the case of locally gentle algebras.
+Our objective is just to provide interpretations of these vectors in terms of the surface~$\surface_{\bar Q}$.
+We show that our geometric model using accordions is well-adapted to computing~$\b{c}$-vectors, while slaloms can naturally be interpreted as~$\b{g}$-vectors.
+
+\subsection{$\b{g}$-vectors, $\b{c}$-vectors, and $\b{d}$-vectors for walks}
+\label{subsec:gcdVectorsWalks}
 
@@
 
-\begin{definition}\label{def: g-vectors for walks}
+\begin{definition}
+\label{def:gVectorsWalks}
 For a walk~$\omega \in \NKWalks^\pm(\bar Q)$, we denote by~$\peaks{\omega}$ (resp.~by~$\deeps{\omega}$) the multiset of vertices of~$Q_0$ corresponding to the peaks (resp.~deeps) of~$\omega$.
@@
 For a set~$\Omega$ of walks, we let~$\gvectors{\Omega} \eqdef \set{\gvector{\omega}}{\omega \in \Omega}$.
-Observe that~$\gvector{\omega} = 0$ for a straight walk~$\omega$, and that, since for any walk~$\omega$, the strings $\omega$ and $\omega^{-1}$ are eventually direct or inverse, the coordinates of~$\gvector{\omega}$ are finite.
-\end{definition}
-
-\begin{remark}
-Let~$\omega$ be a walk in~$\NKWalks^\pm(\bar Q)$, and let $\sigma$ be the string obtained from~$\omega$ by deleting a left and a right co-hook when possible.
-Then the~$\b{g}$-vector of the walk~$\omega$ coincide with the~$\b{g}$-vector of the (finitely generated) string module associated with the string~$\sigma$.
-\end{remark}
-
-\begin{definition}\label{def: c-vectors for walks}
+Observe that~$\gvector{\omega} = 0$ for a straight walk~$\omega$, and that, since for any infinite walk~$\omega$ is eventually cyclic, the coordinates of~$\gvector{\omega}$ are finite.
+\end{definition}
+
+%\begin{remark}
+%\vincent{I vote for deleting this remark. This goes to the next paper. The present paper should have no algebra}
+%Let~$\omega$ be a walk in~$\NKWalks^\pm(\bar Q)$, and let $\sigma$ be the string obtained from~$\omega$ by deleting a left and a right co-hook when possible.
+%Then the~$\b{g}$-vector of the walk~$\omega$ coincide with the~$\b{g}$-vector of the (finitely generated) string module associated with the string~$\sigma$.
+%\end{remark}
+
+\begin{definition}
+\label{def:cVectorsWalks}
 Let~$\omega$ be a walk in a non-kissing facet~$F \in \RNKC$.
@@
 
-\begin{remark}
-\label{rem:signCoherence}
-The definitions of $\b{g}$- and $\b{c}$-vectors immediately imply the \defn{sign-coherence property}: for any non-kissing facet~$F \in \RNKC$,
-\begin{itemize}
-\item for any~$\omega \in F$, all coordinates of the $\b{c}$-vector~$\cvector{\omega}{F}$ have the same sign,
-\item for~$v \in Q_0$, the~$v$th coordinates of all $\b{g}$-vectors~$\gvector{\omega}$ for~$\omega \in F$ have the same sign (otherwise, the corresponding walks would kiss at~$v$).
-\end{itemize}
-In particular, a $\b{c}$-vector is called \defn{positive} when all its coordinates are non-negative and \defn{negative} when all its coordinates are non-positive.
-\end{remark}
-
-\begin{proposition}
-\label{prop:gvectorscvectorsDualBases}
-For any non-kissing facet~$F \in \RNKC$, the set of $\b{g}$-vectors~$\gvectors{F}$ and the set of $\b{c}$-vectors~$\cvectors{F}$ form dual bases. 
-\end{proposition}
-
-\begin{proof}
-Noting that the distinguished string of a walk in a given non-kissing facet is always a finite substring, the proof of~\cite[Proposition 4.16]{PaluPilaudPlamondon} applies \emph{verbatim}.
-\end{proof}
+\begin{definition}
+\label{def:dVectorsWalks}
+\vincent{TOTO: d-vectors}
+\end{definition}
+
+\begin{example}
+\label{exm:gcdVectorsWalks}
+\vincent{TODO: exm g- c- and d-vectors}
+\end{example}
+
+\subsection{$\b{g}$-vectors, $\b{c}$-vectors, and~$\b{d}$-vectors on the surface}
+\label{subsec:gcdVectorsSurface}
 
@@
 \begin{proof}
-Definitions~\ref{def: c-vectors for accordions} and~\ref{def: g-vectors for slaloms} are immediate translations in terms of curves on the surface~$\surface(\bar Q)$ of Definitions~\ref{def: c-vectors for walks} and~\ref{def: g-vectors for walks} respectively.
+Definitions~\ref{def: c-vectors for accordions} and~\ref{def: g-vectors for slaloms} are immediate translations in terms of curves on the surface~$\surface(\bar Q)$ of Definitions~\ref{def:cVectorsWalks} and~\ref{def:gVectorsWalks} respectively.
+\end{proof}
+
+\subsection{Geometric properties of these vectors}
+\label{subsec:geometricProperties}
+
+\begin{remark}
+\label{rem:signCoherence}
+The definitions of $\b{g}$- and $\b{c}$-vectors immediately imply the \defn{sign-coherence property}: for any non-kissing facet~$F \in \RNKC$,
+\begin{itemize}
+\item for any~$\omega \in F$, all coordinates of the $\b{c}$-vector~$\cvector{\omega}{F}$ have the same sign,
+\item for~$v \in Q_0$, the~$v$th coordinates of all $\b{g}$-vectors~$\gvector{\omega}$ for~$\omega \in F$ have the same sign (otherwise, the corresponding walks would kiss at~$v$).
+\end{itemize}
+In particular, a $\b{c}$-vector is called \defn{positive} when all its coordinates are non-negative and \defn{negative} when all its coordinates are non-positive.
+\end{remark}
+
+\begin{proposition}
+\label{prop:gvectorscvectorsDualBases}
+For any non-kissing facet~$F \in \RNKC$, the set of $\b{g}$-vectors~$\gvectors{F}$ and the set of $\b{c}$-vectors~$\cvectors{F}$ form dual bases. 
+\end{proposition}
+
+\begin{proof}
+Noting that the distinguished string of a walk in a given non-kissing facet is always a finite substring, the proof of~\cite[Proposition 4.16]{PaluPilaudPlamondon} applies \emph{verbatim}.
 \end{proof}

### 2018-07-10 draft/accordionComplexSurfaces.tex
Section g- c- d-vectors

@@
 \newcommand{\curveof}{\operatorname{\gamma}} % curve (of a walk)
+\newcommand{\arcof}{\operatorname{\alpha}} % arc of a vertex
+\newcommand{\dualarcof}{\operatorname{\alpha}\dual} % dual arc of a vertex
+\newcommand{\SSS}{\reflectbox{$\mathsf{Z}$}} % S
+\newcommand{\ZZZ}{\mathsf{Z}} % Z
 
@@
 % GEOMETRY
+% d-vectors
+\newcommand{\dvector}[1]{\mathbf{d}(#1)} % d-vector of the path #1
+\newcommand{\dvectors}[1]{\mathbf{d}(#1)} % d-vectors of the paths #1
+\newcommandx{\dvectorFan}[1][1=\bar Q]{\mathcal{F}^\mathbf{d}(#1)} % d-vector fan
 % g-vectors
@@
 The following observations are useful for the computation of examples.
-\begin{itemize}
+\begin{enumerate}[(i)]
 \item The set~$V_{\bar Q}$ has one vertex for each straight walk in~$\bar Q$ (equivalently, for each maximal path in~$\bar Q$).
       Finite straight walks yield vertices on the boundary, while infinite cyclic straight walks in~$\bar Q$ and in~$\bar Q\koszul$ yield punctures.
-\item The dissection~$\dissection_{\bar Q}$ has one arc for each vertex~$p \in \bar Q_0$, obtained by concataining the sides~$\Enrt{\alpha} = \Enrs{\beta}$ and~$\Enrt{\alpha'} = \Enrs{\beta'}$ where~$p = t(\alpha) = s(\beta) = t(\alpha') = s(\beta')$, $\alpha\beta \notin I$ and~$\alpha'\beta' \notin I$.
+\item \label{item:arcs}
+      The dissection~$\dissection_{\bar Q}$ has one arc for each vertex~$p \in \bar Q_0$, obtained by concataining the sides~$\Enrt{\alpha} = \Enrs{\beta}$ and~$\Enrt{\alpha'} = \Enrs{\beta'}$ where~$p = t(\alpha) = s(\beta) = t(\alpha') = s(\beta')$, $\alpha\beta \notin I$ and~$\alpha'\beta' \notin I$.
 \item The dissection~$\dissection_{\bar Q}$ has one $\ell$-cell for each straight walk of length~$\ell$ in~$\bar Q\koszul$.
@@
 \item The number~$p$ of punctures of~$\surface(\bar Q)$ is the number of infinite straight walks in~$\bar Q$ and in~$\bar Q\koszul$.
-\item The number~$b$ of boundary components of~$\surface(\bar Q)$ can be computed as follows.
+\item \label{item:boundary}
+      The number~$b$ of boundary components of~$\surface(\bar Q)$ can be computed as follows.
       There are two natural perfect matchings whose vertices are the blossoming vertices of~$\bar Q$: one is obtained by joining the endpoints of each finite straight walk of~$\bar Q$, and the other is obtained similarly from~$\bar Q \koszul$.
@@
       The above formula for~$g$ follows.
-\end{itemize}
+\end{enumerate}
 \end{remark}
@@
 
-The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}) form a cycle with green and red arrows alternating.
+We now apply Remark~\ref{rem:propertiesSurface} to understand the corresponding surfaces.
+The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}\,(\ref{item:boundary})) form a cycle with green and red arrows alternating.
 Moreover, $\bar Q$ and~$\bar Q\koszul$ have no infinite straight walks.
-Since~$|Q_1| = |Q_0|-1$, the corresponding surfaces have $1$ boundary component and genus~$0$.
+Since~$|Q_1| = |Q_0|-1$, the corresponding surfaces have $1$ boundary component, no puncture and genus~$0$.
 Two examples are represented in \fref{fig:reversedPathsSurfaces}.
@@
 
-The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}) look like~\raisebox{-.1cm}{\includegraphics[scale=.3]{reversedPathsPM}}.
+We now apply Remark~\ref{rem:propertiesSurface} to understand the corresponding surfaces.
+The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}\,(\ref{item:boundary})) look like~\raisebox{-.1cm}{\includegraphics[scale=.3]{reversedPathsPM}}.
 Moreover, $\bar Q$ has no infinite straight walk, while~$\bar Q\koszul$ has~$|Q_0|-1$ infinite straight walks.
@@
 
-The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}) look like~\raisebox{-.1cm}{\includegraphics[scale=.3]{doublePathsPModd}} when~$|Q_0|$ is odd and~\raisebox{-.1cm}{\includegraphics[scale=.3]{doublePathsPMeven}} when~$|Q_0|$ is even.
+We now apply Remark~\ref{rem:propertiesSurface} to understand the corresponding surfaces.
+The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}\,(\ref{item:boundary})) look like~\raisebox{-.1cm}{\includegraphics[scale=.3]{doublePathsPModd}} when~$|Q_0|$ is odd and~\raisebox{-.1cm}{\includegraphics[scale=.3]{doublePathsPMeven}} when~$|Q_0|$ is even.
 Moreover, $\bar Q$ and~$\bar Q\koszul$ have no infinite straight walks.
@@
 
-The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}) are empty since there is no blossom vertices.
+We now apply Remark~\ref{rem:propertiesSurface} to understand the corresponding surfaces.
+The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}\,(\ref{item:boundary})) are empty since there is no blossom vertices.
 Moreover, $\bar Q$ has~$1$ infinite straight walk when~$|Q_0|$ is odd and~$2$ when~$|Q_0|$ is even, and~$\bar Q\koszul$ always has~$2$ infinite straight walks.
@@
 \label{def:curveOfAWalk}
-Let~$\omega = \ldots \alpha_{i-1}^{\varepsilon_{i-1}}\alpha_{i}^{\varepsilon_i}\alpha_{i+1}^{\varepsilon_{i+1}} \ldots$ be a (possibly infinite) walk on~$\bar Q$. 
-Define the curve~$\curveof(\omega)$ to be the concatenation of the curves~$\curveof(\alpha_i^{\varepsilon_{i}})$ of Definition \ref{def:curveOfAnArrow}.
+Let~$\omega = \prod_{i < \ell < j} \alpha_\ell^{\varepsilon_\ell}$ be a (possibly infinite) walk on~$\bar Q$. 
+Define the curve~$\curveof(\omega)$ to be the concatenation of the curves~$\curveof(\alpha_\ell^{\varepsilon_\ell})$ of Definition \ref{def:curveOfAnArrow}.
 \end{definition}
@@
 
+\begin{example}
+\label{exm:peakDeepFacets}
+\vincent{TODO: Describe here the peak and deep facets in terms of the surface.}
+\end{example}
+
 \section{Properties of the non-crossing and non-kissing complexes}\label{sec:propertiesOfComplexes}
@@
 \begin{remark}
-\label{rema:countercurrentOrderOnSurface}
-Using Theorem \ref{thm:complexesCoincide}, we can translate the definition of the countercurrent order~$\prec_\alpha$ to the language of~$\dissection$-accordions.
-An arrow~$\alpha$ in~$\bar Q\blossom$ corresponds to an angle at a point $v$ between two arcs of~$\dissection$.
-Two distinct non-kissing walks~$\mu_\star, \nu_\star$ marked at~$\alpha$ in~$\bar Q$ correspond to two distinct non-crossing~$\dissection$-accordions~$\gamma$ and~$\delta$ passing in front of this angle.
-Then~$\gamma \prec_\alpha \delta$ if~$\gamma$ passes closer to~$v$ than~$\delta$ does.
+\label{rem:countercurrentOrderOnSurface}
+Using Theorem \ref{thm:complexesCoincide}, we can translate the definition of the countercurrent order~$\prec_\alpha$ to the language of~$\dissection$-accordions (resp.~of~$\dissection\dual$-slaloms).
+An arrow~$\alpha$ in~$\bar Q\blossom$ corresponds to an angle at a point~$v$ between two arcs of~$\dissection$ (resp.~at a point~$v\dual$ between two arcs of~$\dissection\dual$).
+Two distinct non-kissing walks~$\mu_\star, \nu_\star$ marked at~$\alpha$ in~$\bar Q$ correspond to two distinct non-crossing~$\dissection$-accordions (resp.~$\dissection\dual$-slaloms)~$\gamma$ and~$\delta$ passing in front of this angle.
+Then~$\gamma \prec_\alpha \delta$ if~$\gamma$ passes closer (resp.~farther) to~$v$ than~$\delta$ does.
 %
@@
 	\centerline{\includegraphics[scale=1]{orderCurves}}
-	\caption{The order~$\mu \prec_\alpha \nu$ on marked walks is the order in which the corresponding curves~$\curveof(\mu)$ and~$\curveof(\nu)$ cross the angle corresponding to~$\alpha$.}
+	\caption{The order~$\mu \prec_\alpha \nu$ on marked walks is the order in which the corresponding curves~$\curveof(\mu)$ and~$\curveof(\nu)$ cross the angles of~$\dissection$ and~$\dissection\dual$ corresponding to~$\alpha$.}
 	\label{fig:orderCurves}
@@
  We provide two proofs of the lemma.
-One is combinatorial and applies to~$\NKC$, and the other is geometric and applies to~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$, using the isomorphism of Theorem \ref{thm:complexesCoincide} and Remark \ref{rema:countercurrentOrderOnSurface}.
+One is combinatorial and applies to~$\NKC$, and the other is geometric and applies to~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$, using the isomorphism of Theorem \ref{thm:complexesCoincide} and Remark \ref{rem:countercurrentOrderOnSurface}.
 
@@
 	\capstart
-	\centerline{\includegraphics[scale=1]{infiniteCurve2.pdf}}
+	\centerline{\includegraphics[scale=.7]{infiniteCurve2.pdf}}
 	\caption{The arc~$\gamma$ makes at least one full circle around the puncture.}
@@
 	\capstart
-	\centerline{\includegraphics[scale=1]{infiniteCurve1.pdf}}
+	\centerline{\includegraphics[scale=.7]{infiniteCurve1.pdf}}
 	\caption{The arc~$\gamma$ leaving the puncture.}
@@
 
-\vincent{To do on the walks, on the accordions and on the slaloms.}
-
-In this section, we define of three relevant families of vectors associated to walks in the non-kissing complex of a locally gentle quiver~$\bar Q$.
-The $\b{g}$- and $\b{c}$-vectors were already considered for gentle algebras in~\cite[Sect.~4.2]{PaluPilaudPlamondon}, and their definition immediately generalizes to the case of locally gentle algebras.
+In this section, we define three relevant families of vectors associated to walks in the non-kissing complex of a locally gentle quiver~$\bar Q$.
+In contrast to the $\b{d}$-vectors, the $\b{g}$- and $\b{c}$-vectors were already considered in the non-kissing complex of a gentle quiver~\cite[Sect.~4.2]{PaluPilaudPlamondon}, and their definition immediately generalizes to the case of locally gentle algebras.
+All these vectors have algebraic motivations that we prefer to omit in the present paper to remain focus on the two-sided combinatorics of the non-kissing and non-crossing models.
 Our objective is just to provide interpretations of these vectors in terms of the surface~$\surface_{\bar Q}$.
-We show that our geometric model using accordions is well-adapted to computing~$\b{c}$-vectors, while slaloms can naturally be interpreted as~$\b{g}$-vectors.
+% We show that our geometric model using accordions is well-adapted to computing~$\b{c}$-vectors, while slaloms can naturally be interpreted as~$\b{g}$-vectors.
 
@@
 
+We now introduce yet another algebraically motivated family of vectors that was omitted in~\cite{PaluPilaudPlamondon}.
+We first need to introduce the kissing number.
+
+\begin{definition}
+\label{def:kissingNumber}
+For two walks~$\omega, \omega' \in \NKWalks^\pm(\bar Q)$, denote by~$\kn(\omega,\omega')$ the number of kisses of~$\omega$ to~$\omega'$.
+Note that kisses are counted with multiplicities if~$\omega$ or~$\omega'$ pass twice through the same substring.
+Observe also that~$\kn(\omega,\omega')$ is finite since any infinite walk is eventually cyclic.
+The \defn{kissing number} of~$\omega$ and~$\omega'$ is~$\KN(\omega,\omega') \eqdef \kn(\omega,\omega') + \kn(\omega',\omega)$.
+%Since~$\RNKC$ is finite, we can define the \defn{kissing number} of a walk~$\omega$ on~$\bar Q$ as
+%\[
+%\KN(\omega) \eqdef \sum_{\omega'} \KN(\omega,\omega'),
+%\]
+%where the sum runs over all walks~$\omega'$ of~$\NKWalks^\pm(\bar Q)$.
+\end{definition}
+
 \begin{definition}
 \label{def:dVectorsWalks}
-\vincent{TOTO: d-vectors}
+The \defn{$\b{d}$-vector} of a walk~$\omega$ is the vector~$\dvector{\omega} \in \R^{Q_0}$ defined by
+\[
+\dvector{\omega} \eqdef 
+\begin{cases}
+- \b{e}_v & \text{if $\omega$ is the deep walk~$v_\deep$ with a unique deep at~$v$,} \\
+\displaystyle \sum_{v \in Q_0} \kn(v_\deep, \omega) \, \b{e}_v & \text{otherwise.}
+\end{cases}
+\]
+For a set~$\Omega$ of walks, we let~$\dvectors{\Omega} \eqdef \set{\dvector{\omega}}{\omega \in \Omega}$.
 \end{definition}
@@
 
-Recall that there is a fixed bijection between the vertices of~$Q$, the arc in the dissection~$\dissection_{\bar Q}$ and the arcs in the dual dissection~$\dissection\dual_{\bar Q}$.
-
-\begin{definition}\label{def: c-vectors for accordions}
-Let~$\alpha$ be a~$\dissection_{\bar Q}$-accordion in a non-crossing facet~$F$ of~$\RNCC$.
-The distinguished curve of~$\alpha$ in~$F$ is the part of~$\alpha$ which lies strictly between the two angles of~$\dissection_{\bar Q}$ where~$\alpha$ is maximal (see Remark~\ref{rema:countercurrentOrderOnSurface}).
-The~$\b{c}$-vector of~$\alpha$ in~$F$ is the vector in~$\R^{Q_0}$ counting the number of crossings between the dinstinguished curve of~$\alpha$ in~$F$ and the arcs of the dissection~$\dissection_{\bar Q}$.
-\end{definition}
-
-\begin{definition}\label{def: g-vectors for slaloms}
-Let~$\alpha$ be a~$\dissection\dual_{\bar Q}$-slalom.
-The~$\b{g}$-vector of~$\alpha$ is the vector in~$\R^{Q_0}$ counting the number of times that~$\alpha$ positively crosses each arc of~$\dissection\dual_{\bar Q}$ minus the number of times it crosses each arc negatively.
-Here, a crossing is positive when~$\alpha$ leaves a face~$u\dual$ to enter a face~$v\dual$ with the vertex~$u$ being to its right (and thus with~$v$ being to its left).
-Otherwise, the crossing is negative.
-\end{definition}
-
-\yann{Ajouter une phrase pour mettre en avant cette proposition}
-
-\begin{proposition}\label{prop: geometric interpretation of g- and c-vectors}
- Let~$\omega$ be a non-kissing walk in~$\bar Q$, and let~$\alpha$ be the corresponding curve on~$\surface(\bar Q)$, as in Definition~\ref{def:curveOfAWalk}.
- Recall from Lemma~\ref{lemm:curveOfAWalkIsAccordion} and Proposition~\ref{prop:accordionsSlaloms} that~$\alpha$ is both a~$\dissection_{\bar Q}$-accordion and a~$\dissection\dual_{\bar Q}$-slalom.
- Let~$F$ be a non-kissing facet to which~$\omega$ belong.
- We also write~$F$ for the corresponding non-crossing facet in the slalom complex.
- Then:
- \begin{enumerate}
-  \item The~$\b{g}$-vectors of the walk~$\omega$ and the accordion~$\alpha$ coincide.
-  \item The~$\b{c}$-vectors of the walk~$\omega$ in~$F$ and the slalom~$\alpha$ in~$F$ concide.
+Our objective is now to interpret the three families of vectors of Section~\ref{subsec:gcdVectorsWalks} in terms of accordions and slaloms on the surface.
+According to Remark~\ref{rem:propertiesSurface}\,(\ref{item:arcs}), each vertex~$p$ of~$Q$ corresponds to an arc~$\arcof(p)$ in the dissection~$\dissection_{\bar Q}$ and  to an arc~$\dualarcof(p) = \arcof(p)\dual$ in the dual dissection~${\dissection_{\bar Q}}\dual$.
+Recall moreover from Lemma~\ref{lemm:curveOfAWalkIsAccordion} and Proposition~\ref{prop:accordionsSlaloms} that each non-kissing walk~$\omega$ in~$\bar Q$ corresponds to a curve~$\curveof(\omega)$ that is both a $\dissection$-accordion and a $\dissection\dual$-slalom.
+The following three statements translate the definitions of $\b{g}$-, $\b{c}$- and $\b{d}$-vectors on the surface.
+The proofs are left to the reader.
+We note that these interpretations were already used in~\cite{MannevillePilaud-accordion, GarverMcConville} when the surface is a disk.
+
+\begin{proposition}
+\label{prop:gVectorsSurface}
+For a walk~$\omega \in \NKWalks^\pm(\bar Q)$ and a vertex~$p \in Q_0$, the $p$th entry of the $\b{g}$-vector~$\gvector{\omega}$ is given~by
+\begin{enumerate}[(i)]
+\item The number of times that the $\dissection$-accordion~$\curveof(\omega)$ positively crosses the arc~$\arcof(p)$ of~$\dissection$ minus the number of times it negatively crosses the arc~$\arcof(p)$ of~$\dissection$.
+Here, the crossing is positive (resp.~negative) if the two angles of~$\dissection$ crossed by~$\curveof(\alpha)$ just before and after~$\arcof(p)$ form a~$\SSS$ (resp.~as a~$\ZZZ$).
+\item The number of times that the $\dissection\dual$-slalom~$\curveof(\omega)$ positively crosses the arc~$\dualarcof(p)$ of~$\dissection\dual$ minus the number of times it negatively crosses the arc~$\dualarcof(p)$ of~$\dissection\dual$.
+Here, the crossing is positive when~$\curveof(\omega)$ leaves a face~$u\dual$ to enter a face~$v\dual$ with the vertex~$u$ being to its right (and thus with~$v$ being to its left), and the crossing is negative otherwise.
 \end{enumerate}
@@
 
-\begin{proof}
-Definitions~\ref{def: c-vectors for accordions} and~\ref{def: g-vectors for slaloms} are immediate translations in terms of curves on the surface~$\surface(\bar Q)$ of Definitions~\ref{def:cVectorsWalks} and~\ref{def:gVectorsWalks} respectively.
-\end{proof}
+\begin{proposition}
+\label{prop:cVectorsSurface}
+Consider a walk~$\omega \in \NKWalks^\pm(\bar Q)$ in a non-kissing facet~$F \in \RNKC$
+Call \defn{distinguished subcurve} of~$\curveof(\omega)$ in~$\curveof(F)$ the part of~$\curveof(\omega)$ which lies strictly between the two angles of~$\dissection$ (or of~$\dissection\dual$) where~$\curveof(\omega)$ is maximal (see Remark~\ref{rem:countercurrentOrderOnSurface}).
+For a vertex~$p \in Q_0$, the $p$th entry of the $\b{c}$-vector~$\cvector{\omega}{F}$ is given by
+\begin{enumerate}[(i)]
+\item the number of crossings between the distinguished subcurve of~$\curveof(\omega)$ in~$\curveof(F)$ and the arc~$\arcof(v)$ of the dissection~$\dissection$,
+\item the number of times the distinguished subcurve of~$\curveof(\omega)$ in~$\curveof(F)$ follows the arc~$\dualarcof(v)$ of the dual dissection~$\dissection\dual$.
+Here, we say that a curve~$\delta$ follows~$\dualarcof(v)$ if~$\dualarcof(v)$ lies on the boundary opposite to~$u$ of a face~$u\dual$ of~$\dissection\dual$ crossed by~$\delta$.
+\end{enumerate}
+\end{proposition}
+
+\begin{remark}
+Observe that although we gave interpretations for the $\b{g}$- and~$\b{c}$-vectors both in terms of accordions and slaloms, we consider that the slaloms naturally correspond to~$\b{g}$-vectors, while the accordions are more suited for~$\b{c}$-vectors.
+\end{remark}
+
+\begin{proposition}
+\label{prop:dVectorsSurface}
+Denote by~$X_\deep$ the deep facet of the non-crossing complex as described in Example~\ref{exm:peakDeepFacets}.
+For a walk~$\omega \in \NKWalks^\pm(\bar Q)$ and a vertex~$p \in Q_0$, the $p$th entry of the $\b{d}$-vector~$\dvector{\omega}$ is the number of crossings of the curve~$\gamma(\omega)$ with the arc of~$X_\deep$ corresponding to~$p$.
+\end{proposition}
+
+%\begin{proposition}
+%\label{prop:gcdVectorsSurface}
+%For any walk~$\omega$ in any non-kissing facet~$F \in \NKC$,
+%\begin{itemize}
+%\item the~$\b{d}$-vectors of the walk~$\omega$, of the $\dissection$-accordion~$\curveof(\omega)$, and of the $\dissection\dual$-slalom~$\curveof(\omega)$ coincide,
+%\item the~$\b{g}$-vectors of the walk~$\omega$, of the $\dissection$-accordion~$\curveof(\omega)$, and of the $\dissection\dual$-slalom~$\curveof(\omega)$ coincide,
+%\item the~$\b{c}$-vectors of the walk~$\omega$ in~$F$, of the $\dissection$-accordion~$\curveof(\omega)$ in~$\curveof(F)$ and of the $\dissection\dual$-slalom~$\curveof(\omega)$ in~$\curveof(F)$ concide.
+%\end{itemize}
+%\end{proposition}
+%
+%\begin{proof}
+%Definitions~\ref{def:cVectorsAccordions} and~\ref{def:gVectorsSlaloms} are immediate translations in terms of curves on the surface~$\surface(\bar Q)$ of Definitions~\ref{def:cVectorsWalks} and~\ref{def:gVectorsWalks} respectively.
+%\end{proof}
 
@@
 
-\begin{remark}
+We now gather some statements about $\b{g}$-, $\b{c}$-, and~$\b{d}$-vectors, essentially borrowed from~\cite[Part.~4]{PaluPilaudPlamondon}.
+
+\begin{proposition}
 \label{rem:signCoherence}
-The definitions of $\b{g}$- and $\b{c}$-vectors immediately imply the \defn{sign-coherence property}: for any non-kissing facet~$F \in \RNKC$,
-\begin{itemize}
+The $\b{g}$-, $\b{c}$-, and~$\b{d}$-vectors have the \defn{sign-coherence property}: for any non-kissing facet~$F \in \RNKC$,
+\begin{itemize}
+\item for~$v \in Q_0$, the~$v$th coordinates of all $\b{g}$-vectors~$\gvector{\omega}$ for~$\omega \in F$ have the same sign,
 \item for any~$\omega \in F$, all coordinates of the $\b{c}$-vector~$\cvector{\omega}{F}$ have the same sign,
-\item for~$v \in Q_0$, the~$v$th coordinates of all $\b{g}$-vectors~$\gvector{\omega}$ for~$\omega \in F$ have the same sign (otherwise, the corresponding walks would kiss at~$v$).
-\end{itemize}
-In particular, a $\b{c}$-vector is called \defn{positive} when all its coordinates are non-negative and \defn{negative} when all its coordinates are non-positive.
-\end{remark}
+\item for any~$\omega \in F$, all coordinates of the $\b{d}$-vector~$\dvector{\omega}$ have the same sign.
+\end{itemize}
+%In particular, a $\b{c}$-vector is called \defn{positive} when all its coordinates are non-negative and \defn{negative} when all its coordinates are non-positive.
+\end{proposition}
+
+\begin{proof}
+For the $\b{g}$-vectors, observe that two walks~$\omega$ and~$\omega'$ whose $\b{g}$-vectors~$\gvector{\omega}$ and~$\gvector{\omega}$ have opposite signs on their~$v$th coordinate automatically kiss at~$v$.
+For $\b{c}$- and $\b{d}$-vectors, the statement is immediate from the definition.
+\end{proof}
 
@@
 
-\begin{definition}
-\vincent{Mettre la def dans les thm}
-The \defn{$\b{g}$-vector fan} of~$\bar Q$ is the collection of cones
+Finally, we borrow the following geometric statement from~\cite{PaluPilaudPlamondon}.
+We refer to \cite{Ziegler-polytopes} for basic notions on polyhedral geometry (polytopes and normal fans).
+
+\begin{theorem}
+Let~$\bar Q$ be a locally gentle bound quiver such that~$\NKC$ is finite. The collection of cones
 \[
@@
 \]
-\end{definition}
-
-\yann{Th 4.17 and Th 4.27 of [PPP1] seem to apply as such here. Vincent?}
-Theorem 4.17 and Theorem 4.27 of~\cite{PaluPilaudPlamondon} hold for locally gentle algebras, with the same proofs:
-
-\begin{theorem}
-Let~$\bar Q$ be a locally gentle bound quiver. Then: 
-\begin{enumerate}
- \item the~$\b{g}$-vector fan of~$\bar Q$ is a complete simplicial fan;
- \item If moreover~$\NKC$ is finite, then $\gvectorFan$ is the normal fan of the~$\bar Q$-associahedron.
-\end{enumerate}
+is a complete simplicial fan, called the \defn{$\b{g}$-vector fan} of~$\bar Q$.
+Moreover, $\gvectorFan$ is the normal fan of the \defn{$\bar Q$-associahedron} defined equivalently as
+\begin{itemize}
+\item the convex hull of the points~$\point{F} \eqdef \sum_{\omega \in F} \KN(\omega) \, \cvector{\omega}{F}$ for all facets~${F \in \RNKC}$,~or
+\item the intersection of the halfspaces~$\HS{\omega} \eqdef \bigset{\b{x} \in \R^{Q_0}}{\dotprod{\gvector{\omega}}{\b{x}} \le \KN(\omega)}$ for all walks~$\omega$ on~$\bar Q$,
+\end{itemize}
+where $\KN(\omega) \eqdef \sum_{\omega'} \KN(\omega,\omega')$ is the (finite) sum of the kissing numbers of Definition~\ref{def:kissingNumber}.
 \end{theorem}
+
+\begin{proof}
+The proof is identical to that of Theorem 4.17 and Theorem 4.27 of~\cite{PaluPilaudPlamondon}.
+\end{proof}
 

### 2018-07-10 draft/accordionComplexSurfaces.tex
minor changes

@@
 
+The following definition generalizes the one from~\cite{GarverMcConville} for the case where~$\bar\surface$ is a disk.
+
 \begin{definition}
@@
 \label{thm:complexesCoincide}
-$\phantom{x}$
-\begin{itemize}
-\item For any locally gentle bound quiver~$\bar Q$, the non-kissing complex~$\NKC$ is isomorphic to the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$, therefore to the accordion complex~$\AC[\dissection_{\bar Q}]$ and to the slalom complex~$\SC[{\dissection_{\bar Q}}\dual]$.
-\item For any pair of dual cellular dissections~$\dissection, \dissection\dual$ of an oriented surface, the non-crossing complex~$\NCC$ is isomorphic to the non-kissing complex~$\NKC[\bar Q_{\dissection, \dissection\dual}]$.
+The non-kissing and non-crossing complexes are isomorphic:
+\begin{itemize}
+\item for any locally gentle bound quiver~$\bar Q$, the non-kissing complex~$\NKC$ is isomorphic to the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$,% therefore to the accordion complex~$\AC[\dissection_{\bar Q}]$ and to the slalom complex~$\SC[{\dissection_{\bar Q}}\dual]$.
+\item for any pair of dual cellular dissections~$\dissection, \dissection\dual$ of an oriented surface, the non-crossing complex~$\NCC$ is isomorphic to the non-kissing complex~$\NKC[\bar Q_{\dissection, \dissection\dual}]$.
 \end{itemize}

### 2018-07-10 draft/accordionComplexSurfaces.tex
comments

@@
 \pierreguy{Should we talk of g,c,d-vectors in the abstract?}
+\vincent{No. I would say that this does not need to be emphasized.}
 The aim of this paper is to prove that two combinatorial objects, called the \emph{non-kissing complex} and the \emph{non-crossing complex}, are isomorphic.
@@
 
-\pierreguy{Finish introduction.}
-
 \section*{Acknowledgements}
@@
 The non-kissing complex is constructed using the combinatorics of strings and walks in the quiver~$\bar Q$, whose definitions are now briefly recalled.
-The terminology in the following definitions is borrowed from~\cite{ButlerRingel, Crawley-Boevey}.
+The terminology and notations in the following definitions is borrowed from~\cite{ButlerRingel, Crawley-Boevey}.
 

### 2018-07-11 draft/accordionComplexSurfaces.tex
work out definitions of AC and SC

@@
 We often implicitly identify the two inverse strings~$\rho$ and~$\rho^{-1}$, and we let~$\strings^\pm(\bar Q) \eqdef \set{\{\rho, \rho^{-1}\}}{\rho \in \strings(\bar Q)}$ denote the collection of all \defn{undirected strings} of~$\bar Q$.
+\vincent{Can we delete this notation.}
 \end{definition}
@@
 As for strings, we implicitly identify the two inverse walks~$\omega$ and~$\omega^{-1}$, and we let~$\walks^\pm(\bar Q) \eqdef \set{\{\omega, \omega^{-1}\}}{\omega \in \walks(\bar Q)}$ denote the set of \defn{undirected walks} of~$\bar Q$.
+\vincent{Can we delete this notation.}
 \end{definition}
@@
 A walk~$\omega$ is \defn{straight} if it has no corner (\ie if~$\omega$ or~$\omega^{-1}$ is a path in~$\bar Q\blossom$), and \defn{bending} otherwise.
-Let $\straightWalks(\bar Q)$ and~$\bendingWalks(\bar Q)$ denote the sets of straight and bending walks of~$\bar Q$ and let~$\straightWalks^\pm(\bar Q) \eqdef \set{\{\omega, \omega^{-1}\}}{\omega \in \straightWalks(\bar Q)}$ and~$\bendingWalks^\pm(\bar Q) \eqdef \set{\{\omega, \omega^{-1}\}}{\omega \in \bendingWalks(\bar Q)}$.
+%Let $\straightWalks(\bar Q)$ and~$\bendingWalks(\bar Q)$ denote the sets of straight and bending walks of~$\bar Q$ and let~$\straightWalks^\pm(\bar Q) \eqdef \set{\{\omega, \omega^{-1}\}}{\omega \in \straightWalks(\bar Q)}$ and~$\bendingWalks^\pm(\bar Q) \eqdef \set{\{\omega, \omega^{-1}\}}{\omega \in \bendingWalks(\bar Q)}$.
 A \defn{peak walk} (resp.~\defn{deep walk}) is a walk with a unique corner (in other words, it switches orientation only once), which is a peak (resp.~deep).
@@
 We denote by~$\NKWalks(\bar Q)$ the walks on~$\bar Q$ which are not self-kissing and by~$\NKWalks^\pm(\bar Q) \eqdef \set{\{\omega, \omega^{-1}\}}{\omega \in \NKWalks(\bar Q)}$ their undirected version.
+\vincent{Can we delete this notation.}
 %
@@
 In contrast, no straight walk can kiss another walk by definition, so that they appear in all facets of~$\NKC$.
-We thus consider the \defn{reduced non-kissing complex}~$\RNKC$ to be the deletion of all straight walks from~$\NKC$.
+The \defn{reduced non-kissing complex}~$\RNKC$ is the simplicial complex whose faces are the collections of pairwise non-crossing bended walks of~$\bar Q$.
 \end{definition}
@@
 \label{def:accordionComplex}
-The \defn{$\dissection$-accordion complex}~$\AC$ is the simplicial complex of pairwise non-crossing $\dissection$-accordions.
-The \defn{reduced $\dissection$-accordion complex}~$\RAC$ is the simplicial complex of pairwise non-crossing internal $\dissection$-accordions.
+The \defn{$\dissection$-accordion complex}~$\AC$ is the simplicial complex whose faces are the collections of pairwise non-crossing $\dissection$-accordions.
+Note that self-crossing accordions never appear in~$\AC$ by definition.
+In contrast, no external accordion can cross another accordion, so that they appear in all facets of~$\AC$. 
+The \defn{reduced $\dissection$-accordion complex}~$\RAC$ is the simplicial complex whose faces are the collections of pairwise non-crossing internal $\dissection$-accordions.
 \end{definition}
@@
 \label{def:slalomComplex}
-The \defn{$\dissection\dual$-slalom complex}~$\SC$ is the simplicial complex of pairwise non-crossing $\dissection$-slaloms.
-The \defn{reduced $\dissection\dual$-slalom complex}~$\RAC$ is the simplicial complex of pairwise non-crossing internal $\dissection\dual$-slaloms.
+The \defn{$\dissection\dual$-slalom complex}~$\SC$ is the simplicial complex whose faces are the collections of pairwise non-crossing $\dissection\dual$-slaloms.
+Note that self-crossing slalom never appear in~$\SC$ by definition.
+In contrast, no external slalom can cross another slalom, so that they appear in all facets of~$\SC$. 
+The \defn{reduced $\dissection\dual$-slalom complex}~$\RSC$ is the simplicial complex whose faces are the collections of pairwise non-crossing internal $\dissection\dual$-slaloms.
 \end{definition}

### 2018-07-11 draft/accordionComplexSurfaces.tex
minor changes intro

@@
 The aim of this paper is to prove that two combinatorial objects, called the \emph{non-kissing complex} and the \emph{non-crossing complex}, are isomorphic.
-Both complexes appeared in different works in specific cases: the non-kissing complex of a grid appeared in \cite{McConville}, while the non-crossing complex of a disk appeared in \cite{GarverMcConville}.
-It was shown in \cite{PaluPilaudPlamondon} that these complexes are special cases of a more general simplicial complex, defined for any gentle algebra (see also \cite{BrustleDouvilleMousavandThomasYildirim}).
+Both complexes appeared in different works in specific cases: the non-kissing complex of a grid appeared in \cite{McConville}, while the non-crossing complex of a disk appeared in \cite{GarverMcConville, MannevillePilaud-accordion}.
+It was shown in \cite{PaluPilaudPlamondon} that these complexes are special cases of a more general simplicial complex, defined for any gentle algebra (see also~\cite{BrustleDouvilleMousavandThomasYildirim}).
 
@@
 \begin{theorem*}[\ref{thm:bijectionLocallyGentleAndSurfaces}]
- There is an explicit bijection between the set of isomorphism classes of locally gentle bound quivers and the set of homeomorphism classes of oriented punctured marked surfaces with boundary and a pair of dual cellular dissections.
+ There is an explicit bijection between the set of isomorphism classes of locally gentle bound quivers and the set of homeomorphism classes of oriented punctured marked surfaces with boundary endowed with a pair of dual cellular dissections.
 \end{theorem*}
 
-On the algebraic side, we extend the study of walks from the gentle to the locally gentle case, and define a notion of compatibility called non-kissing (see Section \ref{sec:nonKissingComplex}).
-On the geometric side, we extend the study of dissections, accordions and slaloms from the case of the disk to the case of an arbitrary surface, and define a notion of compatibility called non-crossing (see Section \ref{sec:accordionSlalomNonCrossingComplexes}).
+On the algebraic side, we extend the study of walks from the gentle case~\cite{McConville, PaluPilaudPlamondon} to the locally gentle case, and define a notion of compatibility called non-kissing (see Section \ref{sec:nonKissingComplex}).
+On the geometric side, we extend the study of dissections, accordions and slaloms from the case of the disk~\cite{GarverMcConville, MannevillePilaud-accordion} to the case of an arbitrary surface, and define a notion of compatibility called non-crossing (see Section \ref{sec:accordionSlalomNonCrossingComplexes}).
 The combinatorial information contained in these notions is encoded in simplicial complexes: the non-kissing complex~$\NKC$ and the non-crossing complex~$\NCC$.
@@
 
+\vincent{Maybe a sentence here to say that we now review historical / motivation / bibliographic facts.}
 Gentle algebras are a class of finite-dimensional associative algebras over a field defined by generators and relations.
@@
 Dissections of surfaces, on the other hand, are certain collections of pairwise non-intersecting curves on an orientable surface.
-They have been defined in studied in \cite{Baryshnikov, Chapoton-quadrangulations, GarverMcConville, MannevillePilaud-accordion} in the case where the surface is an unpunctured disk.
+They have been defined and studied in \cite{Baryshnikov, Chapoton-quadrangulations, GarverMcConville, MannevillePilaud-accordion} in the case where the surface is an unpunctured disk.
 
@@
 In the case where the surface is a polygon, the $\tau$-tilting theory of the algebra of a dissection has been studied in \cite{PilaudPlamondonStella}.
+\vincent{Should we also mention cluster algebras from surfaces in this paragraph?}
 
@@
 \section*{Acknowledgements}
-We thank Sibylle Schroll for discussions on geometric models for gentle algebras.
-We are also grateful to Salvatore Stella for discussions on accordion complexes of dissections of surfaces, and to William Crawley-Boevey and Henning Krause for discussions on the representation theory of infinite dimensional algebras.
+We thank Sibylle Schroll for discussions on geometric models for gentle algebras, Salvatore Stella for discussions on accordion complexes of dissections of surfaces, and William Crawley-Boevey and Henning Krause for discussions on the representation theory of infinite dimensional algebras.
 
@@
 
-We first quickly review the definition of the non-kissing complex of a gentle bound quiver following the presentation of~\cite{PaluPilaudPlamondon} and slightly extend it to locally gentle bound quivers.
+We first quickly review the definition of the non-kissing complex of a gentle bound quiver following the presentation of~\cite{PaluPilaudPlamondon} and extend it to locally gentle bound quivers.
 

### 2018-07-11 draft/accordionComplexSurfaces.tex
proofreading Sections 1,2,3

--- 2018-07-11 draft/accordionComplexSurfaces.tex
@@
 \newcommand{\curveof}{\operatorname{\gamma}} % curve (of a walk)
-\newcommand{\arcof}{\operatorname{\alpha}} % arc of a vertex
-\newcommand{\dualarcof}{\operatorname{\alpha}\dual} % dual arc of a vertex
+\newcommand{\arcof}{\operatorname{\varepsilon}} % arc of a vertex
+\newcommand{\dualarcof}{\operatorname{\varepsilon}\dual} % dual arc of a vertex
 \newcommand{\SSS}{\reflectbox{$\mathsf{Z}$}} % S
@@
 \vincent{No. I would say that this does not need to be emphasized.}
-The aim of this paper is to prove that two combinatorial objects, called the \emph{non-kissing complex} and the \emph{non-crossing complex}, are isomorphic.
+The aim of this paper is to prove that two combinatorial objects, called the ``non-kissing complex'' and the ``non-crossing complex'', are isomorphic.
 Both complexes appeared in different works in specific cases: the non-kissing complex of a grid appeared in \cite{McConville}, while the non-crossing complex of a disk appeared in \cite{GarverMcConville, MannevillePilaud-accordion}.
@@
 Note that we \textbf{do not require} that the quotient algebra~$kQ/I$ be finite dimensional.
-
-\begin{definition}[\cite{ButlerRingel}]
+The following definition is adapted from~\cite{ButlerRingel}.
+
+\begin{definition}%[\cite{ButlerRingel}]
 \label{def:gentleQuiver}
-A \defn{locally gentle bound quiver}~$\bar Q \eqdef (Q,I)$ is a (finite) bound quiver such that
-\begin{itemize}
+A \defn{locally gentle bound quiver}~$\bar Q \eqdef (Q,I)$ is a (finite) bound quiver~where
+\begin{enumerate}[(i)]
 \item each vertex~$v \in Q_0$ has at most two incoming and two outgoing arrows,
@@
 \item for any arrow~$\beta \in Q_1$, there is at most one arrow~$\alpha \in Q_1$ such that~$t(\alpha) = s(\beta)$ and~${\alpha\beta\notin I}$ (resp.~$\alpha\beta \in I$) and at most one arrow~$\gamma \in Q_1$ such that~$t(\beta) = s(\gamma)$~and~${\beta\gamma\notin I}$~(resp.~${\beta\gamma \in I}$).
-\end{itemize}
+\end{enumerate}
 The algebra~$kQ/I$ is called a \defn{locally gentle algebra}.
@@
 
-\begin{definition}[\cite{PaluPilaudPlamondon}]
+\begin{definition}%[\cite{PaluPilaudPlamondon}]
 \label{def:blossomingQuiver}
@@
 Let~$\bar Q = (Q,I)$ be a locally gentle bound quiver.
-A \defn{finite string} for~$\bar Q$ is a word of the form
+A \defn{finite string} in~$\bar Q$ is a word of the form
 \(
@@
 \begin{definition}
- An oriented cycle~$c$ in~$Q$ such that~$c$ and~$c^2$ do not belong to the ideal of relations~$I$ is called \defn{primitive} if it cannot be written as an $n$-th power ($n>1$) of a cycle.
+ An oriented cycle~$c$ in~$Q$ such that~$c$ and~$c^2$ do not belong to the ideal of relations~$I$ is called \defn{primitive} if it cannot be written as an $n$th power ($n>1$) of a cycle.
 \end{definition}
@@
 \begin{itemize}
+\item $c^\infty$ for the infinite word~$c c c\cdots$,
 \item ${}^\infty c$ for the infinite word~$\cdots c c c$,
- \item $c^\infty$ for the infinite word~$c c c\cdots$,
 % \item $^{-\infty} c$ for the infinite word~$\cdots c^{-1} c^{-1} c^{-1}$,
@@
 \begin{definition}
-An \defn{eventually cyclic string} for~$\bar Q$ is a word~$\rho$ of the form~${}^\infty(c_1^{\varepsilon_1})\sigma (c_2^{\varepsilon_2})^\infty$, where $c_1, c_2$ are oriented cycles in~$\bar Q$ (possibly of length zero) and $\varepsilon_1, \varepsilon_2$ are signs in~$\{\pm 1\}$ such that $c_1^{2\varepsilon_1} \sigma c_2^{2\varepsilon_2}$ is a finite chord.
+An \defn{eventually cyclic string} for~$\bar Q$ is a word~$\rho$ of the form~${}^\infty(c_1^{\varepsilon_1})\sigma (c_2^{\varepsilon_2})^\infty$, where $c_1, c_2$ are oriented cycles in~$\bar Q$ (possibly of length zero) and $\varepsilon_1, \varepsilon_2$ are signs in~$\{\pm 1\}$ such that $c_1^{2\varepsilon_1} \sigma c_2^{2\varepsilon_2}$ is a finite string in~$\bar Q$.
 %In case~$\rho=\,^{\pm\infty}c_1\sigma c_2^{\infty}$, it is called \defn{eventually direct}, and \defn{eventually inverse} if~$\rho=\,^{\pm\infty}c_1\sigma c_2^{-\infty}$.
@@
 \label{def:topBottom}
-The substring~$\sigma = \prod_{i' < \ell < j'} \alpha_\ell^{\varepsilon_\ell}$ is \defn{at the bottom} (resp.~\defn{on top}) of the walk~$\omega = \prod_{i < \ell < j} \alpha_\ell^{\varepsilon_\ell}$ if~$i'=-\infty$ or~$\varepsilon_{i'-1} = 1$ and~$j'=+\infty$ or~$\varepsilon_{j'+1} = -1$ (resp.~if~$i'=-\infty$ or~$\varepsilon_{i'-1} = -1$ and~$j'=\infty$ or~$\varepsilon_{j'+1} = 1$).
+We say that the substring~$\sigma = \prod_{i' < \ell < j'} \alpha_\ell^{\varepsilon_\ell}$ is \defn{at the bottom} (resp.~\defn{on top}) of the walk~$\omega = \prod_{i < \ell < j} \alpha_\ell^{\varepsilon_\ell}$ if~$i'=-\infty$ or~$\varepsilon_{i'-1} = 1$ and~$j'=+\infty$ or~$\varepsilon_{j'+1} = -1$ (resp.~if~$i'=-\infty$ or~$\varepsilon_{i'-1} = -1$ and~$j'=\infty$ or~$\varepsilon_{j'+1} = 1$).
 In other words the (at most) two arrows of~$\omega$ incident to the endpoints of~$\sigma$ point towards~$\sigma$ (resp.~outwards from~$\sigma$).
 We denote by~$\Sigma_\bottom(\omega)$ and~$\Sigma_\top(\omega)$ the sets of bottom and top substrings of~$\omega$ respectively.
-We use the same notations for undirected walks.
+We use the same notations for undirected~walks.
 \end{definition}
@@
 
-We can now define the non-kissing complex of a locally gentle bound quiver following~\cite{PaluPilaudPlamondon}.
+We can now define the non-kissing complex of a locally gentle bound quiver following~\cite{McConville, PaluPilaudPlamondon}.
 We start with the kissing relation for walks.
 
-\begin{definition}
+\begin{definition}%[\cite{McConville, PaluPilaudPlamondon}]
 \label{def:kiss}
@@
 %
-\begin{figure}
+\begin{figure}[h]
 	\capstart
@@
 
-\begin{definition}
+\begin{definition}%[\cite{McConville, PaluPilaudPlamondon}]
 \label{def:nKc}
@@
 In contrast, no straight walk can kiss another walk by definition, so that they appear in all facets of~$\NKC$.
-The \defn{reduced non-kissing complex}~$\RNKC$ is the simplicial complex whose faces are the collections of pairwise non-crossing bended walks of~$\bar Q$.
+The \defn{reduced non-kissing complex}~$\RNKC$ is the simplicial complex whose faces are the collections of pairwise non-kissing bended walks of~$\bar Q$.
 \end{definition}
@@
 \item a \defn{$V$-arc} on~$\bar\surface$ is a curve on~$\surface$ connecting two points of~$V$ and whose interior is disjoint from~$M$ and the boundary of~$\surface$.
-\item a \defn{$V$-curve} on~$\bar\surface$ is a curve on~$\surface$ which at each end either reaches a point of~$V$ or infinitely circles around and finally reaches a puncture of~$M$.
+\item a \defn{$V$-curve} on~$\bar\surface$ is a curve on~$\surface$ which at each end either reaches a point of~$V$ or infinitely circles around and finally reaches a puncture of~$M$, and whose interior is disjoint from~$M$ and the boundary of~$\surface$.
 \end{itemize}
@@
 We denote by~$\vertices(\dissection)$, $\edges(\dissection)$ and~$\faces(\dissection)$ the sets of vertices, edges and faces of~$\dissection$ respectively.
-The dissection~$\dissection$ is \defn{cellular} if all its faces are disks.
+The dissection~$\dissection$ is \defn{cellular} if all its faces are topological disks.
 For~$V \subseteq M$, a \defn{$V$-dissection} is a dissection with only $V$-arcs.
@@
 Consider a marked surface~$\bar\surface = (\surface, V \sqcup V\dual)$, where~$V$ and~$V\dual$ are two disjoint sets of marked points so that the points of~$V$ and~$V\dual$ that are on the boundary of~$\surface$ alternate.
-A cellular $V$-dissection~$\dissection$ of~$\bar\surface$ and a cellular $V\dual$-dissection~$\dissection\dual$ of~$\bar\surface$ are \defn{dual cellular dissections} if there are pairs of mutually inverse bijections~$V\dual \leftrightarrow \faces(\dissection)$ and~$V \leftrightarrow \faces(\dissection\dual)$, denoted~$\dual$ in both directions, such that~$\dissection$ has an edge joining its vertices~$u,v \in V$ and separating its faces~$f,g \in  \faces(\dissection)$ if and only if~$\dissection\dual$ has an edge joining its vertices~$f\dual, g\dual \in V\dual$ and separating its faces~$u\dual, v\dual \in \faces(\dissection\dual)$.
+A cellular $V$-dissection~$\dissection$ of~$\bar\surface$ and a cellular $V\dual$-dissection~$\dissection\dual$ of~$\bar\surface$ are \defn{dual cellular dissections} if there are pairs of mutually inverse bijections~$V\dual \leftrightarrow \faces(\dissection)$ and~$V \leftrightarrow \faces(\dissection\dual)$, both denoted~$\dual$ in both directions, such that~$\dissection$ has an edge joining its vertices~$u,v \in V$ and separating its faces~$f,g \in  \faces(\dissection)$ if and only if~$\dissection\dual$ has an edge joining its vertices~$f\dual, g\dual \in V\dual$ and separating its faces~$u\dual, v\dual \in \faces(\dissection\dual)$.
 \end{definition}
@@
 	\centerline{\includegraphics[scale=.7]{dissections}}
-	\caption{Some pairs~$(\dissection, \dissection\dual)$ of dual dissections on different surfaces.
+	\caption{Some pairs~$(\dissection, \dissection\dual)$ of dual cellular dissections on different surfaces.
 The boundaries of the surfaces are shaded, and the glue symbols indicate how to identify some edges to get the desired surfaces.
 The first two surfaces are disks, the third is a sphere, the fourth is a cylinder, and the fifth is a punctured torus.
-The dissection~$\dissection$ is in green while its dual dissection~$\dissection\dual$ is in red.}
+The dissection~$\dissection$ is in green while its dual dissection~$\dissection\dual$ is~in~red.}
 	\label{fig:dissections}
@@
 \item there exists a cellular $V\dual$-dissection~$\dissection\dual$ of~$\bar\surface$ such that~$\dissection$ and~$\dissection\dual$ are dual cellular dissections,
-\item each face of~$\dissection$ contains exactly one point of~$V\dual$.
+\item each face of~$\dissection$ contains exactly one point of~$V\dual$ (in particular, at most one boundary edge).
 \end{enumerate}
@@
 The points of~$B$ are called the \defn{blossom points}.
-See \eg Figures~\ref{fig:accordions} and~\ref{fig:slaloms}.
+See \eg Figures~\ref{fig:accordions} and~\ref{fig:slaloms} where the blossom points appear as white hollow vertices.
 \end{definition}
@@
 \begin{itemize}
-\item it enters crossing an edge~$e_1$ and leaves crossing an edge~$e_2$ (in other words, $\alpha$ is not allowed to circle around~$f\dual$ when~$f\dual$ is a puncture),
-\item the two edges~$e_1$ and~$e_2$ of~$f$ crossed by~$\alpha$ are consecutive on the boundary of~$f$,
-\item $\alpha$, $e_1$ and~$e_2$ bound a disk inside~$f$ that does not contain~$f\dual{}$.
+\item it enters crossing an edge~$a$ of~$f$ and leaves crossing an edge~$b$ of~$f$ (in other words, $\alpha$ is not allowed to circle around~$f\dual$ when~$f\dual$ is a puncture),
+\item the two edges~$a$ and~$b$ of~$f$ crossed by~$\alpha$ are consecutive along the boundary of~$f$,
+\item $\alpha$, $a$ and~$b$ bound a disk inside~$f$ that does not contain~$f\dual{}$.
 \end{itemize}
@@
 \begin{itemize}
-\item the edges of~$e_1$ and~$e_2$ of~$f$ crossed by~$\alpha$ might coincide, see ...
-\item the second condition is automatically satisfied if~$f\dual$ is not a puncture.
+\item the edges of~$a$ and~$b$ of~$f$ crossed by~$\alpha$ might coincide, see ...
+\item the second condition is automatically satisfied if~$f\dual$ is not a puncture, \ie when it lies on the boundary of~$\surface$.
 \end{itemize}
@@
 Here, we consider that~$f\dual$ lies on the right (resp.~left) of~$\alpha$ when~$\alpha$ circles clockwise (resp.~counterclockwise) around~$f\dual$.
-By convention, we also consider that the punctures of~$V$ are $\dissection\dual$-slaloms.
+By convention, we also consider that the punctures of~$V$ are $\dissection\dual$-slaloms that are considered as external slaloms.
 \end{definition}
@@
 
+\begin{example}
+\vincent{Example with the disk}
+\end{example}
+
 \subsection{Accordions versus slaloms and the non-crossing complex}
@@
 Let~$\alpha$ be a~$\dissection$-accordion.
-Let~$\beta$,~$\gamma$,~$\delta$ be three consecutive arcs of~$\dissection$ crossed by~$\gamma$.
-Let~$m\in\dissection$ be the common endpoint of~$\beta$ and $\gamma$ given by Definition~\ref{def:accordion} and let~$n\in\dissection$ be the common endpoint of~$\gamma$ and~$\delta$.
-If $m=n$, then the segment of~$\alpha$ between~$\beta$ and~$\delta$ stays in the same face of~$\dissection\dual$.
-Otherwise, when crossing~$\gamma$, the accordion~$\alpha$ leaves the face~$m\dual$ of $\dissection\dual$ and enters the face~$n\dual$.
-In the surface obtained by glueing the two cells~$m\dual$ and~$n\dual$ along~$\gamma\dual$, the marked points~$m$ and~$n$ are separated by~$\alpha$.
+Let~$a$,~$b$,~$c$ be three consecutive edges of~$\dissection$ crossed by~$\alpha$.
+Let~$u \in \dissection$ be the common endpoint of~$a$ and $b$ given by Definition~\ref{def:accordion} and let~$v \in \dissection$ be the common endpoint of~$b$ and~$c$.
+If $u = v$, then the segment of~$\alpha$ between~$a$ and~$c$ stays in the same face of~$\dissection\dual$.
+Otherwise, when crossing~$b$, the accordion~$\alpha$ leaves the face~$u\dual$ of $\dissection\dual$ and enters the face~$v\dual$.
+In the surface obtained by glueing the two cells~$u\dual$ and~$v\dual$ along~$b\dual$, the marked points~$u$ and~$v$ are separated by~$\alpha$.
 Conversely, assume that~$\alpha$ is an arc of~$(\surface, B)$ which is not a $\dissection$-accordion.
@@
 
-Case 1: The arc~$\alpha$ consecutively crosses two arcs~$\beta$ and~$\gamma$ of~$\dissection$ that do not share a common endpoint.
-Let~$f$ be the face of~$\dissection$ that contain the segment of~$\alpha$ between~$\beta$ and~$\gamma$.
+Case 1: The arc~$\alpha$ consecutively crosses two arcs~$a$ and~$b$ of~$\dissection$ that do not share a common endpoint.
+Let~$f$ be the face of~$\dissection$ that contains the segment of~$\alpha$ between~$a$ and~$b$.
 Consider the connected component of~$f\setminus\alpha$ that do not contain~$f\dual$.
-The boundaty of this component contains an arc~$\delta\in\dissection\setminus\{\beta\}$ that share a common endpoint with~$\beta$.
-Let~$m,n$ be the endpoints of~$\delta$.
-Then~$\alpha$ cuts the cells $m\dual,n\dual$ glued along~$\delta\dual$ into two connected component, one containing both endpoints of~$\delta$.
-
-Case 2: The arc~$\alpha$ consecutively crosses two arcs~$\beta$ and~$\gamma$ of~$\dissection$ that share a unique common endpoint, but the region delimited by~$\alpha$,~$\beta$ and~$\gamma$ is not a disk.
-Since the dissection~$\dissection$ is cellular, that region has to contain some marked point~$m\in\dissection\dual$.
-One conclude that~$\alpha$ is not a~$\dissection\dual$-slalom similarly as in the first case, by considering the component of~$m\dual\setminus\alpha$ that do not contain~$m$.
-
-Case 3: The arc~$\alpha$ consecutively crosses two arcs~$\beta$ and~$\gamma$ of~$\dissection$ that share two different endpoints, and none of the two regions delimited by~$\alpha$,~$\beta$ and~$\gamma$ is a disk.
+The boundary of this component contains an arc~$c \in \dissection \setminus \{a\}$ that share a common endpoint with~$a$.
+Let~$u,v$ be the endpoints of~$c$.
+Then~$\alpha$ cuts the cells $u\dual,v\dual$ glued along~$c\dual$ into two connected component, one containing both endpoints of~$\delta$.
+
+Case 2: The arc~$\alpha$ consecutively crosses two arcs~$a$ and~$b$ of~$\dissection$ that share a unique common endpoint, but the region delimited by~$\alpha$,~$a$ and~$b$ is not a disk.
+Since the dissection~$\dissection$ is cellular, that region has to contain some marked point~$u \in \dissection\dual$.
+One conclude that~$\alpha$ is not a~$\dissection\dual$-slalom similarly as in the first case, by considering the component of~$u\dual \setminus \alpha$ that do not contain~$u$.
+
+Case 3: The arc~$\alpha$ consecutively crosses two arcs~$a$ and~$b$ of~$\dissection$ that share two different endpoints, and none of the two regions delimited by~$\alpha$,~$a$ and~$b$ is a disk.
 Since the dissection~$\dissection$ is cellular, both regions have to contain a puncture.
@@
 Case 4: If~$\alpha$ stays inside a $\dissection$-cell, then it rolls around a~$\dissection\dual$ puncture.
-There is a~$\dissection\dual$-arc~$\beta$ ending in that puncture. When~$\alpha$ crosses~$\beta$, the puncture stays on the same side of~$\alpha$, hence~$\alpha$ is not a~$\dissection\dual$-slalom.
+There is a~$\dissection\dual$-arc~$a$ ending in that puncture. When~$\alpha$ crosses~$a$, the puncture stays on the same side of~$\alpha$, hence~$\alpha$ is not a~$\dissection\dual$-slalom.
 \end{proof}
@@
 	\centerline{\includegraphics[scale=.7]{quiversDissections2}}
-	\caption{The quivers associated to the dissections of \fref{fig:dissections}. As stated in Proposition~\ref{prop:dualityKoszul1}, dual dissections give rise to koszul dual quivers.}
+	\caption{The quivers associated to the dissections of \fref{fig:dissections}. As stated in Proposition~\ref{prop:dualityKoszul1}, dual dissections give rise to Koszul dual quivers.}
 	\label{fig:quiversDissections}
@@
 
-The advantage of Definition~\ref{def:surfaceQuiver} is that it automatically endows with two disjoint sets~$V_{\bar Q}$ and~${V_{\bar Q}}\dual$ of marked points and two dual dissections~$\dissection_{\bar Q}$ and~${\dissection_{\bar Q}}\dual$ defined as follows.
+The advantage of Definition~\ref{def:surfaceQuiver} is that it automatically endows with two disjoint sets~$V_{\bar Q}$ and~${V_{\bar Q}}\dual$ of marked points and two dual cellular dissections~$\dissection_{\bar Q}$ and~${\dissection_{\bar Q}}\dual$ defined as follows.
 
@@
       The number~$b$ of boundary components of~$\surface(\bar Q)$ can be computed as follows.
-      There are two natural perfect matchings whose vertices are the blossoming vertices of~$\bar Q$: one is obtained by joining the endpoints of each finite straight walk of~$\bar Q$, and the other is obtained similarly from~$\bar Q \koszul$.
+      There are two natural perfect matchings whose vertices are the blossom vertices of~$\bar Q$: one is obtained by joining the endpoints of each finite straight walk of~$\bar Q$, and the other is obtained similarly from~$\bar Q \koszul$.
       Let~$G$ be the superposition of these two perfect matchings.
@@
 Our objective is now to interpret the three families of vectors of Section~\ref{subsec:gcdVectorsWalks} in terms of accordions and slaloms on the surface.
-According to Remark~\ref{rem:propertiesSurface}\,(\ref{item:arcs}), each vertex~$p$ of~$Q$ corresponds to an arc~$\arcof(p)$ in the dissection~$\dissection_{\bar Q}$ and  to an arc~$\dualarcof(p) = \arcof(p)\dual$ in the dual dissection~${\dissection_{\bar Q}}\dual$.
+According to Remark~\ref{rem:propertiesSurface}\,(\ref{item:arcs}), each vertex~$p$ of~$Q$ corresponds to an edge~$\arcof(p)$ in the dissection~$\dissection_{\bar Q}$ and  to an edge~$\dualarcof(p) = \arcof(p)\dual$ in the dual dissection~${\dissection_{\bar Q}}\dual$.
 Recall moreover from Lemma~\ref{lemm:curveOfAWalkIsAccordion} and Proposition~\ref{prop:accordionsSlaloms} that each non-kissing walk~$\omega$ in~$\bar Q$ corresponds to a curve~$\curveof(\omega)$ that is both a $\dissection$-accordion and a $\dissection\dual$-slalom.
@@
 \begin{enumerate}[(i)]
-\item The number of times that the $\dissection$-accordion~$\curveof(\omega)$ positively crosses the arc~$\arcof(p)$ of~$\dissection$ minus the number of times it negatively crosses the arc~$\arcof(p)$ of~$\dissection$.
+\item The number of times that the $\dissection$-accordion~$\curveof(\omega)$ positively crosses the edge~$\arcof(p)$ of~$\dissection$ minus the number of times it negatively crosses the edge~$\arcof(p)$ of~$\dissection$.
 Here, the crossing is positive (resp.~negative) if the two angles of~$\dissection$ crossed by~$\curveof(\alpha)$ just before and after~$\arcof(p)$ form a~$\SSS$ (resp.~as a~$\ZZZ$).
-\item The number of times that the $\dissection\dual$-slalom~$\curveof(\omega)$ positively crosses the arc~$\dualarcof(p)$ of~$\dissection\dual$ minus the number of times it negatively crosses the arc~$\dualarcof(p)$ of~$\dissection\dual$.
+\item The number of times that the $\dissection\dual$-slalom~$\curveof(\omega)$ positively crosses the edge~$\dualarcof(p)$ of~$\dissection\dual$ minus the number of times it negatively crosses the edge~$\dualarcof(p)$ of~$\dissection\dual$.
 Here, the crossing is positive when~$\curveof(\omega)$ leaves a face~$u\dual$ to enter a face~$v\dual$ with the vertex~$u$ being to its right (and thus with~$v$ being to its left), and the crossing is negative otherwise.
@@
 \begin{enumerate}[(i)]
-\item the number of crossings between the distinguished subcurve of~$\curveof(\omega)$ in~$\curveof(F)$ and the arc~$\arcof(v)$ of the dissection~$\dissection$,
-\item the number of times the distinguished subcurve of~$\curveof(\omega)$ in~$\curveof(F)$ follows the arc~$\dualarcof(v)$ of the dual dissection~$\dissection\dual$.
+\item the number of crossings between the distinguished subcurve of~$\curveof(\omega)$ in~$\curveof(F)$ and the edge~$\arcof(v)$ of the dissection~$\dissection$,
+\item the number of times the distinguished subcurve of~$\curveof(\omega)$ in~$\curveof(F)$ follows the edge~$\dualarcof(v)$ of the dual dissection~$\dissection\dual$.
 Here, we say that a curve~$\delta$ follows~$\dualarcof(v)$ if~$\dualarcof(v)$ lies on the boundary opposite to~$u$ of a face~$u\dual$ of~$\dissection\dual$ crossed by~$\delta$.
@@
 Denote by~$X_\deep$ the deep facet of the non-crossing complex as described in Example~\ref{exm:peakDeepFacets}.
-For a walk~$\omega \in \NKWalks^\pm(\bar Q)$ and a vertex~$p \in Q_0$, the $p$th entry of the $\b{d}$-vector~$\dvector{\omega}$ is the number of crossings of the curve~$\gamma(\omega)$ with the arc of~$X_\deep$ corresponding to~$p$.
+For a walk~$\omega \in \NKWalks^\pm(\bar Q)$ and a vertex~$p \in Q_0$, the $p$th entry of the $\b{d}$-vector~$\dvector{\omega}$ is the number of crossings of the curve~$\gamma(\omega)$ with the edge of~$X_\deep$ corresponding to~$p$.
 \end{proposition}

### 2018-07-11 draft/accordionComplexSurfaces.tex
Changes to the intro.

--- 2018-07-11 draft/accordionComplexSurfaces.tex
@@
 \section{Introduction}
-\pierreguy{Should we talk of g,c,d-vectors in the abstract?}
-\vincent{No. I would say that this does not need to be emphasized.}
 The aim of this paper is to prove that two combinatorial objects, called the \emph{non-kissing complex} and the \emph{non-crossing complex}, are isomorphic.
@@
 \end{theorem*}
+We end in Section \ref{sec:vectors} with a discussion of~$\b{g}$-vectors,~$\b{c}$-vectors and~$\b{d}$-vectors associated to walks and curves.
 
@@
 
-\vincent{Maybe a sentence here to say that we now review historical / motivation / bibliographic facts.}
+Let us review the algebraic and geometric objects which appear in this paper.
+
 Gentle algebras are a class of finite-dimensional associative algebras over a field defined by generators and relations.
@@
 It has also been shown in \cite{BaurSimoes} that any gentle algebra is obtained from a dissection of a surface, and that the module category of the algebra can be interpreted by using curves on the surface.
-In the case where the surface is a polygon, the $\tau$-tilting theory of the algebra of a dissection has been studied in \cite{PilaudPlamondonStella}.
+In the case where the surface is a polygon, the $\tau$-tilting theory of the algebra of a dissection has been studied in \cite{PaluPilaudPlamondon, PilaudPlamondonStella}.
 \vincent{Should we also mention cluster algebras from surfaces in this paragraph?}
+\pierreguy{Not sure.}
 
@@
 Our construction has the advantage that it easily yields the two dual dissections of the surface at the same time (the dissection and dual lamination of \cite{OpperPlamondonSchroll}).
-We note that this surface is usually different than the one found in \cite{BaurSimoes}.
+We note that our dissections are always cellularr, while those found in \cite{BaurSimoes} can be arbitrary.
 Remarkably, gentle algebras and surfaces were linked recently in \cite{HaidenKatzarkovKontsevich}, where the Fukaya category of the surface is shown to be equivalent to the bounded derived category of the associated gentle algebra.
@@
 \section{$\b{g}$-vectors, $\b{c}$-vectors, and $\b{d}$-vectors}
+\label{sec:vectors}
 

### 2018-07-11 draft/accordionComplexSurfaces.tex
discussion example disk

--- 2018-07-11 draft/accordionComplexSurfaces.tex
@@
 
-\begin{example}
-\vincent{Example with the disk}
-\end{example}
-
 \subsection{Accordions versus slaloms and the non-crossing complex}
@@
 \begin{proof}
-\vincent{Careful: arcs / curves.}
 Let~$\alpha$ be a~$\dissection$-accordion.
@@
 In the surface obtained by glueing the two cells~$u\dual$ and~$v\dual$ along~$b\dual$, the marked points~$u$ and~$v$ are separated by~$\alpha$.
-Conversely, assume that~$\alpha$ is an arc of~$(\surface, B)$ which is not a $\dissection$-accordion.
+Conversely, assume that~$\alpha$ is an curve of~$(\surface, B)$ which is not a $\dissection$-accordion.
 We are in one of the following cases.
 
-Case 1: The arc~$\alpha$ consecutively crosses two arcs~$a$ and~$b$ of~$\dissection$ that do not share a common endpoint.
+Case 1: The curve~$\alpha$ consecutively crosses two edges~$a$ and~$b$ of~$\dissection$ that do not share a common endpoint.
 Let~$f$ be the face of~$\dissection$ that contains the segment of~$\alpha$ between~$a$ and~$b$.
 Consider the connected component of~$f\setminus\alpha$ that do not contain~$f\dual$.
-The boundary of this component contains an arc~$c \in \dissection \setminus \{a\}$ that share a common endpoint with~$a$.
+The boundary of this component contains an edge~$c \in \dissection \setminus \{a\}$ that share a common endpoint with~$a$.
 Let~$u,v$ be the endpoints of~$c$.
@@
 
-Case 2: The arc~$\alpha$ consecutively crosses two arcs~$a$ and~$b$ of~$\dissection$ that share a unique common endpoint, but the region delimited by~$\alpha$,~$a$ and~$b$ is not a disk.
+Case 2: The curve~$\alpha$ consecutively crosses two edges~$a$ and~$b$ of~$\dissection$ that share a unique common endpoint, but the region delimited by~$\alpha$,~$a$ and~$b$ is not a disk.
 Since the dissection~$\dissection$ is cellular, that region has to contain some marked point~$u \in \dissection\dual$.
@@
 
-Case 3: The arc~$\alpha$ consecutively crosses two arcs~$a$ and~$b$ of~$\dissection$ that share two different endpoints, and none of the two regions delimited by~$\alpha$,~$a$ and~$b$ is a disk.
+Case 3: The curve~$\alpha$ consecutively crosses two edges~$a$ and~$b$ of~$\dissection$ that share two different endpoints, and none of the two regions delimited by~$\alpha$,~$a$ and~$b$ is a disk.
 Since the dissection~$\dissection$ is cellular, both regions have to contain a puncture.
@@
 Case 4: If~$\alpha$ stays inside a $\dissection$-cell, then it rolls around a~$\dissection\dual$ puncture.
-There is a~$\dissection\dual$-arc~$a$ ending in that puncture. When~$\alpha$ crosses~$a$, the puncture stays on the same side of~$\alpha$, hence~$\alpha$ is not a~$\dissection\dual$-slalom.
+There is a~$\dissection\dual$-edge~$a$ ending in that puncture. When~$\alpha$ crosses~$a$, the puncture stays on the same side of~$\alpha$, hence~$\alpha$ is not a~$\dissection\dual$-slalom.
 \end{proof}
@@
 \end{remark}
+
+\begin{example}
+When the dissection~$\dissection$ is a classical dissection of a polygon (with no puncture) where each cell has at most one boundary edge, the dual dissection~$\dissection\dual$ is a tree.
+The non-kissing complex in his situation was treated in detail in~\cite{GarverMcConville, MannevillePilaud-accordion}.
+Note that even when the surface~$\surface$ is a disk, we authorize here both~$\dissection$ and~$\dissection\dual$ to have interior faces and punctures.
+\end{example}
 

### 2018-07-11 draft/accordionComplexSurfaces.tex

@@
 \section{Introduction}
-\pierreguy{Should we talk of g,c,d-vectors in the abstract?}
-\vincent{No. I would say that this does not need to be emphasized.}
-The aim of this paper is to prove that two combinatorial objects, called the ``non-kissing complex'' and the ``non-crossing complex'', are isomorphic.
+The aim of this paper is to prove that two combinatorial objects, called the \emph{non-kissing complex} and the \emph{non-crossing complex}, are isomorphic.
 Both complexes appeared in different works in specific cases: the non-kissing complex of a grid appeared in \cite{McConville}, while the non-crossing complex of a disk appeared in \cite{GarverMcConville, MannevillePilaud-accordion}.

### 2018-07-11 draft/accordionComplexSurfaces.tex
Minor change
changes phone

--- 2018-07-11 draft/accordionComplexSurfaces.tex
@@
 In contrast, no straight walk can kiss another walk by definition, so that they appear in all facets of~$\NKC$.
-The \defn{reduced non-kissing complex}~$\RNKC$ is the simplicial complex whose faces are the collections of pairwise non-kissing bended walks of~$\bar Q$.
+The \defn{reduced non-kissing complex}~$\RNKC$ is the simplicial complex whose faces are the collections of pairwise non-kissing bending walks of~$\bar Q$.
 \end{definition}
@@
 The following definition generalises the one from \cite{MannevillePilaud-accordion} for the case where~$\bar \surface$ is a disk.  It appears in \cite{BaurSimoes} under the name ``permissible arc''.
-\pierreguy{Is it ok to cite like this?}
 
@@
 
-In this section, we show that non-kissing complexes and non-crossing complexes actually coincide.
+In this section, we show that non-kissing and non-crossing complexes actually coincide.
 Namely, any pair of dual cellular dissections~$(\dissection, \dissection\dual)$ defines a locally gentle bound quiver~$\bar Q_{\dissection, \dissection\dual}$ such that the non-crossing complex~$\NCC$ is isomorphic to the non-kissing complex~$\NKC[\bar Q_{\dissection, \dissection\dual}]$.
@@
 In fact, we show that the accordion, slalom, and non-kissing complexes can all be pictured in a unique way on the surface.
-Interestingly, via the correspondence between pairs of dual cellular dissections and locally gentle bound quivers, the duality between the dissections~$\dissection$ and~$\dissection\dual$ translates to the Koszul duality between the locally gentle algebras of~$\bar Q$ and~$\bar Q\dual$.
+Interestingly, via the correspondence between pairs of dual cellular dissections and locally gentle bound quivers, the duality between the dissections~$\dissection$ and~$\dissection\dual$ translates to the Koszul duality between the locally gentle algebras of~$\bar Q$ and~$\bar Q\koszul$.
 
@@
 
-\begin{remark}
-The blossoming quiver~$\bar Q_\dissection\blossom$ of the quiver~$\bar Q_\dissection$ is obtained with the same procedure by considering additional blossom vertices along the boundary of the surface.
-See \fref{fig:quiversDissections}.
-\end{remark}
-
 \fref{fig:quiversDissections} illustrates this construction for the dissections of \fref{fig:dissections}.
@@
 \end{figure}
+
+\begin{remark}
+The blossoming quiver~$\bar Q_\dissection\blossom$ of the quiver~$\bar Q_\dissection$ is obtained with the same procedure by considering additional blossom vertices along the boundary of the surface.
+See \fref{fig:quiversDissections}.
+\end{remark}
 
@@
 \begin{proof}
- The duality gives a bijection~$v\in (Q_\dissection)_0\mapsto v\dual\in (Q_{\dissection\dual})_0$, and induces a bijection~$\alpha\in (Q_\dissection)_1\mapsto \alpha\dual\in (Q_{\dissection\dual})_1$ with~$s(\alpha\dual)=s(\alpha)\dual$ and~$t(\alpha\dual)=t(\alpha)\dual$.
+The duality provides a bijection~$v\in (Q_\dissection)_0\mapsto v\dual\in (Q_{\dissection\dual})_0$, and thus induces a bijection~${\alpha \in (Q_\dissection)_1 \mapsto \alpha\dual \in (Q_{\dissection\dual})_1}$ with~$s(\alpha\dual)=s(\alpha)\dual$ and~$t(\alpha\dual)=t(\alpha)\dual$.
  Moreover, for any two composable arrows~$\alpha,\beta\in(Q_\dissection)_0$, we have~$\alpha\beta\in I_\dissection$ if and only if~$s(\alpha),t(\alpha),t(\beta)$ are three consecutive edges of a~$\dissection$-cell~$f$, if and only if~$s(\alpha)\dual,t(\alpha)\dual,t(\beta)\dual$ are three consecutive arcs in~$\dissection\dual$ ending in~$f\dual$, if and only if~$\beta\dual\alpha\dual\notin I_{\dissection\dual}$.
@@
 We now associate a surface to a locally gentle bound quiver.
-This construction is directly inspired by the one found in \cite{OpperPlamondonSchroll} (see Remark \ref{rem:comparisonWithOPS} for a comparison of the two constructions).
+This construction yields the same surface as the one constructed in \cite{OpperPlamondonSchroll} (see Remark \ref{rem:comparisonWithOPS} for a comparison of the two constructions).
 
@@
 \label{def:surfaceQuiver}
-The surface~$\surface(\bar Q)$ of a locally gentle bound quiver~$\bar Q = (Q,I)$ is the surface obtained from the blossoming quiver~$\bar Q\blossom$ as follows:
+The surface~$\surface_{\bar Q}$ of a locally gentle bound quiver~$\bar Q = (Q,I)$ is the surface obtained from the blossoming quiver~$\bar Q\blossom$ as follows:
 \begin{enumerate}[(i)]
@@
 
-Definition~\ref{def:surfaceQuiver} constructs an orientable surface~$\surface(\bar Q)$ with boundaries.
+Definition~\ref{def:surfaceQuiver} constructs an orientable surface~$\surface_{\bar Q}$ with boundaries.
 \fref{fig:surfaces} illustrates this construction for the quivers of \fref{fig:quivers}.
@@
 
-The advantage of Definition~\ref{def:surfaceQuiver} is that it automatically endows with two disjoint sets~$V_{\bar Q}$ and~${V_{\bar Q}}\dual$ of marked points and two dual cellular dissections~$\dissection_{\bar Q}$ and~${\dissection_{\bar Q}}\dual$ defined as follows.
+The advantage of Definition~\ref{def:surfaceQuiver} is that it automatically endows~$\surface_{\bar Q}$ with two disjoint sets~$V_{\bar Q}$ and~${V_{\bar Q}}\dual$ of marked points and two dual cellular dissections~$\dissection_{\bar Q}$ and~${\dissection_{\bar Q}}\dual$ defined as follows.
 
@@
 \label{def:dissectionQuiver}
-The surface~$\surface(\bar Q)$ is endowed with
+The surface~$\surface_{\bar Q}$ is endowed with
 \begin{itemize}
@@
 \begin{proof}
-In the construction of~$\surface(\bar Q)$, if two arrows~$\alpha$ and~$\beta$ of~$\bar Q \blossom$ are such that~$t(\alpha) = s(\beta)$ and~$\alpha\beta\in I\blossom$, then the vertices~$v(\alpha)$ and~$v(\beta)$ are identified on the surface.
+In the construction of~$\surface_{\bar Q}$, if two arrows~$\alpha$ and~$\beta$ of~$\bar Q \blossom$ are such that~${t(\alpha) = s(\beta)}$ and~${\alpha\beta \in I\blossom}$, then the vertices~$v(\alpha)$ and~$v(\beta)$ are identified on the surface.
 Thus, any two arrows of a given path contribute the same vertex of~$V_{\bar Q}$, so~$V_{\bar Q}$ is in bijection with the set of maximal paths in~$\bar Q\blossom$.
@@
 
-In both cases, we see that~$v$ is enclosed in a polygon of~$\dissection_{\bar Q}\dual$.  This shows that~$\dissection_{\bar Q}\dual$ is a cellular dissection of~$\surface(\bar Q)$.
+In both cases, we see that~$v$ is enclosed in a polygon of~$\dissection_{\bar Q}\dual$.  This shows that~$\dissection_{\bar Q}\dual$ is a cellular dissection of~$\surface_{\bar Q}$.
 Dually, one shows that~$\dissection_{\bar Q}$ is also a cellular dissection.
 
-Moreover, by construction, each edge of~$\dissection_{\bar Q}$ which is not on the boundary of~$\surface(\bar Q)$ crosses exactly one edge of~$\dissection_{\bar Q}\dual$, and vice versa.
+Moreover, by construction, each edge of~$\dissection_{\bar Q}$ which is not on the boundary of~$\surface_{\bar Q}$ crosses exactly one edge of~$\dissection_{\bar Q}\dual$, and vice versa.
 This shows that~$\dissection_{\bar Q}$ and~$\dissection_{\bar Q}\dual$ are dual to each other.
@@
 \item A similar remark holds dually for~${V_{\bar Q}}\dual$ and~${\dissection_{\bar Q}}\dual$.
-\item The number~$p$ of punctures of~$\surface(\bar Q)$ is the number of infinite straight walks in~$\bar Q$ and in~$\bar Q\koszul$.
+\item The number~$p$ of punctures of~$\surface_{\bar Q}$ is the number of infinite straight walks in~$\bar Q$ and in~$\bar Q\koszul$.
 \item \label{item:boundary}
-      The number~$b$ of boundary components of~$\surface(\bar Q)$ can be computed as follows.
+      The number~$b$ of boundary components of~$\surface_{\bar Q}$ can be computed as follows.
       There are two natural perfect matchings whose vertices are the blossom vertices of~$\bar Q$: one is obtained by joining the endpoints of each finite straight walk of~$\bar Q$, and the other is obtained similarly from~$\bar Q \koszul$.
       Let~$G$ be the superposition of these two perfect matchings.
-      Then the number~$b$ of boundary components of~$\surface(\bar Q)$ is the number of connected components of~$G$.
-\item The genus of the surface~$\surface(\bar Q)$ is
+      Then the number~$b$ of boundary components of~$\surface_{\bar Q}$ is the number of connected components of~$G$.
+\item The genus of the surface~$\surface_{\bar Q}$ is
       \[
@@
       where~$b$ is the number of boundary components (see above for a way to compute~$b$) and~$p$ the number of punctures (\ie infinite straight walks in~$\bar Q$ and in~$\bar Q\koszul$).
-      Indeed, $2g = 2-\chi(\surface(\bar Q))$, where~$\chi(\surface(\bar Q))$ is the Euler characteristic of~$\surface(\bar Q)$.
-      The dissection~$\dissection$ provides a cellular decomposition of~$\surface(\bar Q)$ on which we fill the boundary components and the punctures with disks.  
+      Indeed, $2g = 2-\chi(\surface_{\bar Q})$, where~$\chi(\surface_{\bar Q})$ is the Euler characteristic of~$\surface_{\bar Q}$.
+      The dissection~$\dissection$ provides a cellular decomposition of~$\surface_{\bar Q}$ on which we fill the boundary components and the punctures with disks.  
       The number of faces of this cellular decomposition is~$b$, its number of edges is~$|Q_0|$ and its number of vertices is the number of finite straight walks in~$\bar Q$, which is equal to~$2|Q_0| - |Q_1|$.
@@
 \end{proposition}
+
+\begin{remark}
+\label{rem:comparisonWithOPS}
+The construction of the surface given in Definition \ref{def:surfaceQuiver} yields the same surface as the one constructed in \cite{OpperPlamondonSchroll}.
+A notable difference is that in \cite{OpperPlamondonSchroll}, only~$\dissection_{\bar Q}$ is given, and~$\dissection_{\bar Q}\dual$ is deduced (it is called the dual lamination).
+Another minor difference is that the construction in \cite{OpperPlamondonSchroll} is written only for gentle algebras, while here it is generalized to locally gentle algebras.
+
+The major difference with \cite{OpperPlamondonSchroll} is the application of the surface of a (locally) gentle algebra: 
+there, it is used as a model for the derived category of the gentle algebra (graded arcs correspond to indecomposable objects in that category),
+while here, it will be used as a model for walks in~$\bar Q$ ($\dissection_{\bar Q}$-accordions will correspond to walks in~$\bar{Q}$, see Proposition \ref{prop:walks=arcs}).
+\end{remark}
+
+We conclude this section with four families of examples.
 
@@
 
-\begin{remark}
-\label{rem:comparisonWithOPS}
-The construction of the surface given in Definition \ref{def:surfaceQuiver} yields the same surface as the one constructed in \cite{OpperPlamondonSchroll}.
-A notable difference is that in \cite{OpperPlamondonSchroll}, only~$\dissection_{\bar Q}$ is given, and~$\dissection_{\bar Q}\dual$ is deduced (it is called the dual lamination).
-Another minor difference is that the construction in \cite{OpperPlamondonSchroll} is written only for gentle algebras, while here it is generalized to locally gentle algebras.
-
-The major difference with \cite{OpperPlamondonSchroll} is the application of the surface of a (locally) gentle algebra: 
-there, it is used as a model for the derived category of the gentle algebra (graded arcs correspond to indecomposable objects in that category),
-while here, it will be used as a model for walks in~$\bar Q$ ($\dissection_{\bar Q}$-accordions will correspond to walks in~$\bar{Q}$, see Proposition \ref{prop:walks=arcs}).
-\end{remark}
-
 \subsection{Non-crossing and non-kissing complexes coincide}
@@
 Let~$\bar Q$ be a locally gentle bound quiver.
-For each arc of the dissection~$\dissection_{\bar Q}$ on~$\surface(\bar Q)$, we fix a point on the interior of this arc, which we call its ``middle point''.
+For each arc of the dissection~$\dissection_{\bar Q}$ on~$\surface_{\bar Q}$, we fix a point on the interior of this arc, which we call its ``middle point''.
 To each walk on~$\bar Q$, we will now associate a~$\dissection_{\bar Q}$-accordion.
@@
 \label{def:curveOfAnArrow}
-For any arrow~$\alpha$ on $\bar Q\blossom$, let~$\curveof(\alpha)$ be the curve on~$\surface(\bar Q)$ which goes from the middle point of the arc corresponding to $s(\alpha)$ to the middle point of the arc corresponding to $t(\alpha)$ by following the angle corresponding to~$\alpha$.
+For any arrow~$\alpha$ on $\bar Q\blossom$, let~$\curveof(\alpha)$ be the curve on~$\surface_{\bar Q}$ which goes from the middle point of the arc corresponding to $s(\alpha)$ to the middle point of the arc corresponding to $t(\alpha)$ by following the angle corresponding to~$\alpha$.
 Define~$\curveof(\alpha^{-1})$ to be~$\curveof(\alpha)^{-1}$.
@@
 \label{prop:walks=arcs}
-The maps~$\curveof(-)$ and~$\walk(-)$ induce mutually inverse bijections between the set of undirected walks on~$\bar Q$ and the set of~$\dissection_{\bar Q}$-accordions on~$\surface(\bar Q)$.
+The maps~$\curveof(-)$ and~$\walk(-)$ induce mutually inverse bijections between the set of undirected walks on~$\bar Q$ and the set of~$\dissection_{\bar Q}$-accordions on~$\surface_{\bar Q}$.
 \end{proposition}
@@
 Let~$\omega_1$ and~$\omega_2$ be walks on~$\bar Q$.
-Then~$\omega_1$ and~$\omega_2$ are non-kissing if and only if the~$\dissection_{\bar Q}$-accordions~$\curveof(\omega_1)$ and~$\curveof(\omega_2)$ are non-crossing on~$\surface(\bar Q)$.
+Then~$\omega_1$ and~$\omega_2$ are non-kissing if and only if the~$\dissection_{\bar Q}$-accordions~$\curveof(\omega_1)$ and~$\curveof(\omega_2)$ are non-crossing on~$\surface_{\bar Q}$.
 \end{lemma}
@@
 The left hand side of the picture is as in \fref{fig:kissing}, and the right hand side is simply a different representation of it.
-On the surface~$\surface(\bar Q)$, the dual dissections~$\dissection$ and~$\dissection\dual$ are as on \fref{fig:kissingVSCrossing} (on the right hand side).
+On the surface~$\surface_{\bar Q}$, the dual dissections~$\dissection$ and~$\dissection\dual$ are as on \fref{fig:kissingVSCrossing} (on the right hand side).
 
@@
 
+\begin{remark}
+Note that our construction of the surface~$\surface_{\bar Q}$ implies that the vertices of~$\bar Q$ are naturally identified with the intersection points of the dual edges~$a \in \dissection_{\bar Q}$ and~$a\dual \in {\dissection_{\bar Q}}\dual$.
+If we force all $\dissection$-accordions (or $\dissection\dual$-slaloms) to cross the edges of~$\dissection$ and~$\dissection\dual$ only at these intersection points, then an $\dissection$-accordion (or $\dissection\dual$-slalom) is really seen a walk on~$\bar Q$.
+\end{remark}
+
+We conclude with an important example of facets of the non-kissing and non-crossing complexes.
+
 \begin{example}
 \label{exm:peakDeepFacets}
+
 \vincent{TODO: Describe here the peak and deep facets in terms of the surface.}
@@
  Let~$F$ be a face of the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$.
- Its elements are pairwise compatible~$\dissection$-accordions on the surface~$\surface(\bar Q)$.
- Thus~$F$ can be viewed as a partial tagged triangulation of~$\surface(\bar Q)$, by letting the~$\dissection$-accordions circling a puncture in (say) clockwise order be seen as ``notched'' arcs to said puncture, and the ones circling it in counter-clockwise orientation be ``un-notched'' arcs.
+ Its elements are pairwise compatible~$\dissection$-accordions on the surface~$\surface_{\bar Q}$.
+ Thus~$F$ can be viewed as a partial tagged triangulation of~$\surface_{\bar Q}$, by letting the~$\dissection$-accordions circling a puncture in (say) clockwise order be seen as ``notched'' arcs to said puncture, and the ones circling it in counter-clockwise orientation be ``un-notched'' arcs.
  It is known (see, for instance, \cite{FominShapiroThurston}) that any such partial tagged triangulation can be embedded into a full triangulation, and that triangulations contain a finite number of arcs.
@@
 Therefore, $\lambda$ contains either~$\alpha$ or~$\beta$.
-We have thus found a bended walk~$\lambda \in F$ containing an arrow~$\alpha$ or~$\beta$ of~$c$, say~$\alpha$.
+We have thus found a bending walk~$\lambda \in F$ containing an arrow~$\alpha$ or~$\beta$ of~$c$, say~$\alpha$.
 We can now moreover assume that~$\lambda = \distinguishedWalk{\alpha}{F}$.
@@
 \para{Geometric proof}
-The statement of the lemma translates on~$\surface(\bar Q)$ as follows: for any facet~$F$ of the non-crossing complex~$\NCC$ and any puncture of the dissection~$\dissection_{\bar Q}$, there exists a curve in~$F$ which goes to the puncture.
+The statement of the lemma translates on~$\surface_{\bar Q}$ as follows: for any facet~$F$ of the non-crossing complex~$\NCC$ and any puncture of the dissection~$\dissection_{\bar Q}$, there exists a curve in~$F$ which goes to the puncture.
 Assume that there is a puncture with no curves of~$F$ going to it.
@@
 %\begin{proof}
-%Definitions~\ref{def:cVectorsAccordions} and~\ref{def:gVectorsSlaloms} are immediate translations in terms of curves on the surface~$\surface(\bar Q)$ of Definitions~\ref{def:cVectorsWalks} and~\ref{def:gVectorsWalks} respectively.
+%Definitions~\ref{def:cVectorsAccordions} and~\ref{def:gVectorsSlaloms} are immediate translations in terms of curves on the surface~$\surface_{\bar Q}$ of Definitions~\ref{def:cVectorsWalks} and~\ref{def:gVectorsWalks} respectively.
 %\end{proof}

### 2018-07-11 draft/accordionComplexSurfaces.tex
Change ref BS

@@
       The dissection~$\dissection$ provides a cellular decomposition of~$\surface_{\bar Q}$ on which we fill the boundary components and the punctures with disks.  
-      The number of faces of this cellular decomposition is~$b$, its number of edges is~$|Q_0|$ and its number of vertices is the number of finite straight walks in~$\bar Q$, which is equal to~$2|Q_0| - |Q_1|$.
+      The number of faces of this cellular decomposition is~$b+p$, its number of edges is~$|Q_0|$ and its number of vertices is the number of finite straight walks in~$\bar Q$, which is equal to~$2|Q_0| - |Q_1|$.
       The above formula for~$g$ follows.

### 2018-07-11 draft/accordionComplexSurfaces.tex
modifications figures + deleting some notations

@@
 % walks
-\newcommand{\strings}{\mathcal{S}} % strings
+%\newcommand{\strings}{\mathcal{S}} % strings
 \newcommand{\distinguishableStrings}{\mathcal{S}_\mathrm{dist}} % distinguishable strings
 \newcommand{\lfStrings}{\underline{\mathcal{S}}} % loop-free strings
-\newcommand{\walks}{\mathcal{W}} % walks
-\newcommand{\straightWalks}{\mathcal{W}_\mathrm{str}} % straight walks
-\newcommand{\bendingWalks}{\mathcal{W}_\mathrm{bend}} % bending walks
-\newcommand{\NKWalks}{\mathcal{W}_\mathrm{nk}} % non-kissing walks
+%\newcommand{\walks}{\mathcal{W}} % walks
+%\newcommand{\straightWalks}{\mathcal{W}_\mathrm{str}} % straight walks
+%\newcommand{\bendingWalks}{\mathcal{W}_\mathrm{bend}} % bending walks
+%\newcommand{\NKWalks}{\mathcal{W}_\mathrm{nk}} % non-kissing walks
 \newcommand{\peaks}[1]{\mathsf{peaks}(#1)} % peaks
@@
 \end{theorem*}
+
 We end in Section \ref{sec:vectors} with a discussion of~$\b{g}$-vectors,~$\b{c}$-vectors and~$\b{d}$-vectors associated to walks and curves.
-
 Consequences on the representation theory of locally gentle algebras will be investigated in a future project.
 
-Let us review the algebraic and geometric objects which appear in this paper.
+Finally, let us briefly review the algebraic and geometric objects which appear in this paper.
 
@@
 In the case where the surface is a polygon, the $\tau$-tilting theory of the algebra of a dissection has been studied in \cite{PaluPilaudPlamondon, PilaudPlamondonStella}.
-\vincent{Should we also mention cluster algebras from surfaces in this paragraph?}
-\pierreguy{Not sure.}
 
@@
 Our construction has the advantage that it easily yields the two dual dissections of the surface at the same time (the dissection and dual lamination of \cite{OpperPlamondonSchroll}).
-We note that our dissections are always cellularr, while those found in \cite{BaurSimoes} can be arbitrary.
+We note that our dissections are always cellular, while those found in \cite{BaurSimoes} can be arbitrary.
 Remarkably, gentle algebras and surfaces were linked recently in \cite{HaidenKatzarkovKontsevich}, where the Fukaya category of the surface is shown to be equivalent to the bounded derived category of the associated gentle algebra.
@@
 A \defn{string} for~$\bar Q$ is a word which is either a finite string or an eventually cyclic infinite string.
-We denote by~$\strings(\bar Q)$ the set of strings on~$\bar Q$.
-We often implicitly identify the two inverse strings~$\rho$ and~$\rho^{-1}$, and we let~$\strings^\pm(\bar Q) \eqdef \set{\{\rho, \rho^{-1}\}}{\rho \in \strings(\bar Q)}$ denote the collection of all \defn{undirected strings} of~$\bar Q$.
-\vincent{Can we delete this notation.}
+%We denote by~$\strings(\bar Q)$ the set of strings on~$\bar Q$.
+We often implicitly identify the two inverse strings~$\rho$ and~$\rho^{-1}$, and call it an \defn{undirected string} of~$\bar Q$.
+%we let~$\strings^\pm(\bar Q) \eqdef \set{\{\rho, \rho^{-1}\}}{\rho \in \strings(\bar Q)}$ denote the collection of all \defn{undirected strings} of~$\bar Q$.
 \end{definition}
@@
 A \defn{walk} of a locally gentle quiver~$\bar Q$ is a maximal string of its blossoming quiver~$\bar Q \blossom$ (meaning that at each end it either reaches a blossom vertex of~$\bar Q \blossom$ or enters an infinite oriented cycle).
-We denote by~$\walks(\bar Q)$ the set of all walks on~$\bar Q$.
-As for strings, we implicitly identify the two inverse walks~$\omega$ and~$\omega^{-1}$, and we let~$\walks^\pm(\bar Q) \eqdef \set{\{\omega, \omega^{-1}\}}{\omega \in \walks(\bar Q)}$ denote the set of \defn{undirected walks} of~$\bar Q$.
-\vincent{Can we delete this notation.}
+%We denote by~$\walks(\bar Q)$ the set of all walks on~$\bar Q$.
+As for strings, we implicitly identify the two inverse walks~$\omega$ and~$\omega^{-1}$, and call it an \defn{undirected walk} of~$\bar Q$.
+%we let~$\walks^\pm(\bar Q) \eqdef \set{\{\omega, \omega^{-1}\}}{\omega \in \walks(\bar Q)}$ denote the set of \defn{undirected walks} of~$\bar Q$.
 \end{definition}
@@
 \label{def:substrings}
-A \defn{substring} of a walk~$\omega = \prod_{i < \ell < j} \alpha_\ell^{\varepsilon_\ell} \in \walks(\bar Q)$ is a string~$\sigma = \prod_{i' < \ell < j'} \alpha_\ell^{\varepsilon_\ell}$ of~$\strings(\bar Q)$ for some~$i \le i' < j' \le j$, where the inequality~$i \le i'$ (resp.~$j' \le j$) is strict when~$i \ne -\infty$ (resp.~$j \ne \infty$).
+A \defn{substring} of a walk~$\omega = \prod_{i < \ell < j} \alpha_\ell^{\varepsilon_\ell}$ of~$\bar Q$ is a string~$\sigma = \prod_{i' < \ell < j'} \alpha_\ell^{\varepsilon_\ell}$ of~$\bar Q$ for some~$i \le i' < j' \le j$, where the inequality~$i \le i'$ (resp.~$j' \le j$) is strict when~$i \ne -\infty$ (resp.~$j \ne \infty$).
 In other words, $\sigma$ is a factor of~$\omega$ such that
@@
 \label{def:kiss}
-Let~$\omega,\omega' \in \walks^\pm(\bar Q)$ be two undirected walks on~$\bar Q$.
-We say that~$\omega$ \defn{kisses}~$\omega'$ if~$\Sigma_\top(\omega) \cap \Sigma_\bottom(\omega')$ contains a \emph{finite} substring.
+Let~$\omega$ and~$\omega'$ be two undirected walks on~$\bar Q$.
+We say that~$\omega$ \defn{kisses}~$\omega'$ if ${\Sigma_\top(\omega) \cap \Sigma_\bottom(\omega')}$ contains a \emph{finite} substring.
 See \fref{fig:kissing}.
@@
 Observe also that~$\omega$ can kiss~$\omega'$ several times, that~$\omega$ and~$\omega'$ can mutually kiss, and that~$\omega$ can kiss itself.
-We denote by~$\NKWalks(\bar Q)$ the walks on~$\bar Q$ which are not self-kissing and by~$\NKWalks^\pm(\bar Q) \eqdef \set{\{\omega, \omega^{-1}\}}{\omega \in \NKWalks(\bar Q)}$ their undirected version.
-\vincent{Can we delete this notation.}
+%We denote by~$\NKWalks(\bar Q)$ the walks on~$\bar Q$ which are not self-kissing and by~$\NKWalks^\pm(\bar Q) \eqdef \set{\{\omega, \omega^{-1}\}}{\omega \in \NKWalks(\bar Q)}$ their undirected version.
 %
@@
 \label{def:nKc}
-The \defn{non-kissing complex} of~$\bar Q$ is the simplicial complex~$\NKC$ whose faces are the collections of pairwise non-kissing walks of~$\NKWalks^\pm(\bar Q)$.
+The \defn{non-kissing complex} of~$\bar Q$ is the simplicial complex~$\NKC$ whose faces are the collections of pairwise non-kissing walks of~$\bar Q$.
 Note that self-kissing walks never appear in~$\NKC$ by definition.
@@
 
-The following definition generalises the one from \cite{MannevillePilaud-accordion} for the case where~$\bar \surface$ is a disk.  It appears in \cite{BaurSimoes} under the name ``permissible arc''.
+The following definition generalises the one from \cite{MannevillePilaud-accordion} for the case where~$\bar \surface$ is a disk.
+A very similar definition appears in \cite{BaurSimoes} in a slightly different context under the name ``permissible arc''.
 
@@
 	\centerline{\includegraphics[scale=.7]{halfStar} \qquad \includegraphics[scale=.7]{star}}
-	\caption{The situation around~$v$ (green vertex). On the left,~$v$ corresponds to a finite maximal path of~$\bar Q$, while on the right,~$v$ corresponds to an infinite one.}
+	\caption{Two possible situations around~$v$: on the left,~$v$ corresponds to a finite maximal path of~$\bar Q$, while on the right,~$v$ corresponds to an infinite one.}
 	\label{fig:stars}
@@
 Two distinct non-kissing walks~$\mu_\star, \nu_\star$ marked at~$\alpha$ in~$\bar Q$ correspond to two distinct non-crossing~$\dissection$-accordions (resp.~$\dissection\dual$-slaloms)~$\gamma$ and~$\delta$ passing in front of this angle.
-Then~$\gamma \prec_\alpha \delta$ if~$\gamma$ passes closer (resp.~farther) to~$v$ than~$\delta$ does.
+Then~$\gamma \prec_\alpha \delta$ if~$\gamma$ passes closer to~$v$ (resp.~farther to~$v\dual$) than~$\delta$ does.
+These interpretations of~$\prec_\alpha$ on the surface where already considered in the case of the disk in~\cite{GarverMcConville, MannevillePilaud-accordion}.
 %
@@
 Assume that there is a puncture with no curves of~$F$ going to it.
-Construct a curve~$\gamma$ as follows:~$\gamma$ first unwinds from the puncture, then~$\gamma$ leaves the local picture around the puncture by turning around another marked point (marked~$X$ on the picture below).
+Construct a curve~$\gamma$ as follows:~$\gamma$ first unwinds from the puncture, then~$\gamma$ leaves the local picture around the puncture by turning around another marked point (marked~$u$ on the picture below).
 
@@
 
-Two situations can occur.
-
-Firstly, if there are no curves of~$F$ closer to~$X$ than~$\gamma$, then~$\gamma$ can circle around~$X$ until it reaches the boundary (if~$X$ is on the boundary) or infinitely (if~$X$ is a puncture).
+Two situations can occur:
+\begin{itemize}
+\item Firstly, if there are no curves of~$F$ closer to~$u$ than~$\gamma$, then~$\gamma$ can circle around~$u$ until it reaches the boundary (if~$u$ is on the boundary) or infinitely (if~$u$ is a puncture).
 Then~$\gamma$ is a~$\dissection_{\bar Q}$-accordion which crosses none of those in~$F$, contradicting the maximality of~$F$.
-
-Secondly, if there is a curve of~$F$ closer to~$X$ than~$\gamma$, then let~$\delta$ be the one furthest from~$X$ ($\delta$ exists by Lemma \ref{lemm:facesHaveMaximalElement}).
+\item Secondly, if there is a curve of~$F$ closer to~$u$ than~$\gamma$, then let~$\delta$ be the one furthest from~$u$ ($\delta$ exists by Lemma \ref{lemm:facesHaveMaximalElement}).
 From there, let~$\gamma$ follow~$\delta$ on the surface until it either reaches the boundary or circles infinitely around a puncture.  
 Then~$\gamma$ is compatible with all curves in~$F$, a contradiction.
-
+\end{itemize}
 Thus~$F$ contains a curve going to the puncture.
@@
 \]
-For a string~$\sigma \in \strings^\pm(\bar Q)$, we define~$\multiplicityVector_\sigma \eqdef \multiplicityVector_{V(\sigma)}$ where~$V(\sigma)$ is the multiset of vertices of~$\sigma$. 
+For a string~$\sigma$ of~$\bar Q$, we define~$\multiplicityVector_\sigma \eqdef \multiplicityVector_{V(\sigma)}$ where~$V(\sigma)$ is the multiset of vertices of~$\sigma$. 
 \end{definition}
@@
 \label{def:gVectorsWalks}
-For a walk~$\omega \in \NKWalks^\pm(\bar Q)$, we denote by~$\peaks{\omega}$ (resp.~by~$\deeps{\omega}$) the multiset of vertices of~$Q_0$ corresponding to the peaks (resp.~deeps) of~$\omega$.
+For a walk~$\omega$ of~$\bar Q$, we denote by~$\peaks{\omega}$ (resp.~by~$\deeps{\omega}$) the multiset of vertices of~$Q_0$ corresponding to the peaks (resp.~deeps) of~$\omega$.
 The \defn{$\b{g}$-vector} of a walk~$\omega$ is the vector~${\gvector{\omega} \in \R^{Q_0}}$ defined by
@@
 \label{def:kissingNumber}
-For two walks~$\omega, \omega' \in \NKWalks^\pm(\bar Q)$, denote by~$\kn(\omega,\omega')$ the number of kisses of~$\omega$ to~$\omega'$.
+For two walks~$\omega$ and~$\omega'$ of~$\bar Q$, denote by~$\kn(\omega,\omega')$ the number of kisses of~$\omega$ to~$\omega'$.
 Note that kisses are counted with multiplicities if~$\omega$ or~$\omega'$ pass twice through the same substring.
@@
 \label{prop:gVectorsSurface}
-For a walk~$\omega \in \NKWalks^\pm(\bar Q)$ and a vertex~$p \in Q_0$, the $p$th entry of the $\b{g}$-vector~$\gvector{\omega}$ is given~by
+For a walk~$\omega$ of~$\bar Q$ and a vertex~$p \in Q_0$, the $p$th entry of the $\b{g}$-vector~$\gvector{\omega}$ is given~by
 \begin{enumerate}[(i)]
@@
 \label{prop:cVectorsSurface}
-Consider a walk~$\omega \in \NKWalks^\pm(\bar Q)$ in a non-kissing facet~$F \in \RNKC$
+Consider a walk~$\omega$ of~$\bar Q$ in a non-kissing facet~$F \in \RNKC$
 Call \defn{distinguished subcurve} of~$\curveof(\omega)$ in~$\curveof(F)$ the part of~$\curveof(\omega)$ which lies strictly between the two angles of~$\dissection$ (or of~$\dissection\dual$) where~$\curveof(\omega)$ is maximal (see Remark~\ref{rem:countercurrentOrderOnSurface}).
@@
 Denote by~$X_\deep$ the deep facet of the non-crossing complex as described in Example~\ref{exm:peakDeepFacets}.
-For a walk~$\omega \in \NKWalks^\pm(\bar Q)$ and a vertex~$p \in Q_0$, the $p$th entry of the $\b{d}$-vector~$\dvector{\omega}$ is the number of crossings of the curve~$\gamma(\omega)$ with the edge of~$X_\deep$ corresponding to~$p$.
+For a walk~$\omega$ of~$\bar Q$ and a vertex~$p \in Q_0$, the $p$th entry of the $\b{d}$-vector~$\dvector{\omega}$ is the number of crossings of the curve~$\gamma(\omega)$ with the edge of~$X_\deep$ corresponding to~$p$.
 \end{proposition}

### 2018-07-11 draft/accordionComplexSurfaces.tex
Example 4.26

@@
 \usepackage[T1]{fontenc}
-\usepackage{enumerate, amsmath, amsfonts, amssymb, amsthm, mathrsfs, wasysym, graphics, graphicx, xcolor, url, hyperref, hypcap, xargs, multicol, pdflscape, multirow, hvfloat, array, ae, aecompl, pifont, mathtools, a4wide}
+\usepackage{enumerate, amsmath, amsfonts, amssymb, amsthm, mathrsfs, wasysym, graphics, graphicx, xcolor, url, hyperref, hypcap, xargs, multicol, pdflscape, multirow, hvfloat, array, ae, aecompl, pifont, mathtools, a4wide, float}
 \usepackage{marginnote}
@@
 \newcommand{\blossom}{^\text{\ding{96}}} % blossom
-\newcommand{\blinkers}[1]{_{\LEFTCIRCLE \!\! #1 \!\! \RIGHTCIRCLE}} % blossom
-\newcommand{\indeg}{\mathrm{indeg}} % in-degree
-\newcommand{\outdeg}{\mathrm{outdeg}} % out-degree
+%\newcommand{\blinkers}[1]{_{\LEFTCIRCLE \!\! #1 \!\! \RIGHTCIRCLE}} % blossom
+%\newcommand{\indeg}{\mathrm{indeg}} % in-degree
+%\newcommand{\outdeg}{\mathrm{outdeg}} % out-degree
 %\newcommand{\tai}{\mathsf{tai}} % target incompatible
@@
 %\newcommand{\strings}{\mathcal{S}} % strings
-\newcommand{\distinguishableStrings}{\mathcal{S}_\mathrm{dist}} % distinguishable strings
-\newcommand{\lfStrings}{\underline{\mathcal{S}}} % loop-free strings
+%\newcommand{\distinguishableStrings}{\mathcal{S}_\mathrm{dist}} % distinguishable strings
+%\newcommand{\lfStrings}{\underline{\mathcal{S}}} % loop-free strings
 %\newcommand{\walks}{\mathcal{W}} % walks
@@
 \newcommand{\curveof}{\operatorname{\gamma}} % curve (of a walk)
-\newcommand{\arcof}{\operatorname{\varepsilon}} % arc of a vertex
-\newcommand{\dualarcof}{\operatorname{\varepsilon}\dual} % dual arc of a vertex
+\newcommand{\edgeof}{\operatorname{\varepsilon}} % arc of a vertex
+\newcommand{\dualedgeof}{\operatorname{\varepsilon}\dual} % dual arc of a vertex
 \newcommand{\SSS}{\reflectbox{$\mathsf{Z}$}} % S
 \newcommand{\ZZZ}{\mathsf{Z}} % Z
+\newcommand{\vnext}{n} % next point on the boundary of the surface
+\newcommand{\vprevious}{p} % previous point on the boundary of the surface
 
@@
 \begin{definition}
-\label{def:straightBended}
+\label{def:straightBending}
 A \defn{peak} (resp.~\defn{deep}) of a walk~$\omega$ is a substring of~$\omega$ of length zero which is on top (resp.~at the bottom of~$\omega$).
@@
 \item \label{item:arcs}
-      The dissection~$\dissection_{\bar Q}$ has one arc for each vertex~$p \in \bar Q_0$, obtained by concataining the sides~$\Enrt{\alpha} = \Enrs{\beta}$ and~$\Enrt{\alpha'} = \Enrs{\beta'}$ where~$p = t(\alpha) = s(\beta) = t(\alpha') = s(\beta')$, $\alpha\beta \notin I$ and~$\alpha'\beta' \notin I$.
+      The dissection~$\dissection_{\bar Q}$ has one edge for each vertex~$p \in \bar Q_0$, obtained by concataining the sides~$\Enrt{\alpha} = \Enrs{\beta}$ and~$\Enrt{\alpha'} = \Enrs{\beta'}$ where~$p = t(\alpha) = s(\beta) = t(\alpha') = s(\beta')$, $\alpha\beta \notin I$ and~$\alpha'\beta' \notin I$.
+We denote by~$\edgeof(p)$ the edge of~$\dissection_{\bar Q}$ corresponding to~$p$.
 \item The dissection~$\dissection_{\bar Q}$ has one $\ell$-cell for each straight walk of length~$\ell$ in~$\bar Q\koszul$.
@@
 
-We now apply Remark~\ref{rem:propertiesSurface} to understand the corresponding surfaces.
+We apply Remark~\ref{rem:propertiesSurface} to understand the corresponding surfaces.
 The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}\,(\ref{item:boundary})) form a cycle with green and red arrows alternating.
@@
 
-We now apply Remark~\ref{rem:propertiesSurface} to understand the corresponding surfaces.
+We apply Remark~\ref{rem:propertiesSurface} to understand the corresponding surfaces.
 The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}\,(\ref{item:boundary})) look like~\raisebox{-.1cm}{\includegraphics[scale=.3]{reversedPathsPM}}.
@@
 
-We now apply Remark~\ref{rem:propertiesSurface} to understand the corresponding surfaces.
+\enlargethispage{.2cm}
+We apply Remark~\ref{rem:propertiesSurface} to understand the corresponding surfaces.
 The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}\,(\ref{item:boundary})) look like~\raisebox{-.1cm}{\includegraphics[scale=.3]{doublePathsPModd}} when~$|Q_0|$ is odd and~\raisebox{-.1cm}{\includegraphics[scale=.3]{doublePathsPMeven}} when~$|Q_0|$ is even.
@@
 
-\begin{figure}[h]
+\begin{figure}[H]
 	\capstart
@@
 
-We now apply Remark~\ref{rem:propertiesSurface} to understand the corresponding surfaces.
+We apply Remark~\ref{rem:propertiesSurface} to understand the corresponding surfaces.
 The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}\,(\ref{item:boundary})) are empty since there is no blossom vertices.
@@
 \label{exm:peakDeepFacets}
-
-\vincent{TODO: Describe here the peak and deep facets in terms of the surface.}
+We have seen in Definition~\ref{def:straightBending} that each vertex~$p$ of~$Q$ gives rise to a \defn{peak walk}~$p_\peak$ (resp.~\defn{deep walk}~$p_\deep$) with a single peak (resp.~deep) at~$v$ and no other corner.
+The set of all such walks forms the \defn{peak facet}~$\set{p_\peak}{p \in Q_0}$ (resp.~the \defn{deep facet}~$\set{p_\deep}{p \in Q_0}$) of the non-kissing complex~$\NKC$.
+As an example of Theorem~\ref{thm:complexesCoincide}, let us now describe the corresponding non-crossing facets of~$\NCC[\surface_{\bar Q}]$.
+
+For a vertex~$v \in V$ on the boundary of~$\surface$, we denote by~$\vprevious(v)$ (resp.~$\vnext(v)$) the blossom vertex previous (resp.~next) to~$v$ on the clockwise order around the boundary of~$\surface$.
+For an edge~$a$ of~$\dissection$, we denote by~$\vprevious(a)$ (resp.~$\vnext(a)$) the curve obtained by moving each endpoint~$v$ of~$a$ as follows:
+\begin{itemize}
+\item if~$v$ is on the boundary of~$\surface$, then move (continuously) $v$ along the boundary of~$\surface$ until it reaches~$\vprevious(v)$ (resp.~$\vnext(v)$),
+\item if~$v$ is a puncture, then rotate around~$v$ in counterclockwise direction (resp.~clockwise direction).
+\end{itemize}
+Examples are illustrated in \fref{fig:peakDeep}.
+%
+\begin{figure}[h]
+	\capstart
+	\centerline{\includegraphics[scale=.7]{peakDeep}}
+	\caption{The curves~$\vprevious(a)$ (left) and $\vnext(a)$ (right) associated to an edge~$a$ of~$\dissection$ for three different dissections.}
+	\label{fig:peakDeep}
+\end{figure}
+
+We invite the reader to check that~$\curveof(p_\peak) = \vprevious(\edgeof(p))$ (resp.~$\curveof(p_\deep) = \vnext(\edgeof(p))$), where~$\edgeof(p)$ denotes the edge of~$\dissection$ corresponding to~$p \in Q_0$ (see Remark~\ref{rem:propertiesSurface}).
+Therefore, the peak facet (resp.~the deep facet) can be thought of as the dissection~$\dissection$ slightly rotated clockwise (resp.~counterclockwise) on the surface~$\surface$.
 \end{example}
@@
 Our objective is now to interpret the three families of vectors of Section~\ref{subsec:gcdVectorsWalks} in terms of accordions and slaloms on the surface.
-According to Remark~\ref{rem:propertiesSurface}\,(\ref{item:arcs}), each vertex~$p$ of~$Q$ corresponds to an edge~$\arcof(p)$ in the dissection~$\dissection_{\bar Q}$ and  to an edge~$\dualarcof(p) = \arcof(p)\dual$ in the dual dissection~${\dissection_{\bar Q}}\dual$.
+According to Remark~\ref{rem:propertiesSurface}\,(\ref{item:arcs}), each vertex~$p$ of~$Q$ corresponds to an edge~$\edgeof(p)$ in the dissection~$\dissection_{\bar Q}$ and  to an edge~$\dualedgeof(p) = \edgeof(p)\dual$ in the dual dissection~${\dissection_{\bar Q}}\dual$.
 Recall moreover from Lemma~\ref{lemm:curveOfAWalkIsAccordion} and Proposition~\ref{prop:accordionsSlaloms} that each non-kissing walk~$\omega$ in~$\bar Q$ corresponds to a curve~$\curveof(\omega)$ that is both a $\dissection$-accordion and a $\dissection\dual$-slalom.
@@
 \begin{enumerate}[(i)]
-\item The number of times that the $\dissection$-accordion~$\curveof(\omega)$ positively crosses the edge~$\arcof(p)$ of~$\dissection$ minus the number of times it negatively crosses the edge~$\arcof(p)$ of~$\dissection$.
-Here, the crossing is positive (resp.~negative) if the two angles of~$\dissection$ crossed by~$\curveof(\alpha)$ just before and after~$\arcof(p)$ form a~$\SSS$ (resp.~as a~$\ZZZ$).
-\item The number of times that the $\dissection\dual$-slalom~$\curveof(\omega)$ positively crosses the edge~$\dualarcof(p)$ of~$\dissection\dual$ minus the number of times it negatively crosses the edge~$\dualarcof(p)$ of~$\dissection\dual$.
+\item The number of times that the $\dissection$-accordion~$\curveof(\omega)$ positively crosses the edge~$\edgeof(p)$ of~$\dissection$ minus the number of times it negatively crosses the edge~$\edgeof(p)$ of~$\dissection$.
+Here, the crossing is positive (resp.~negative) if the two angles of~$\dissection$ crossed by~$\curveof(\alpha)$ just before and after~$\edgeof(p)$ form a~$\SSS$ (resp.~as a~$\ZZZ$).
+\item The number of times that the $\dissection\dual$-slalom~$\curveof(\omega)$ positively crosses the edge~$\dualedgeof(p)$ of~$\dissection\dual$ minus the number of times it negatively crosses the edge~$\dualedgeof(p)$ of~$\dissection\dual$.
 Here, the crossing is positive when~$\curveof(\omega)$ leaves a face~$u\dual$ to enter a face~$v\dual$ with the vertex~$u$ being to its right (and thus with~$v$ being to its left), and the crossing is negative otherwise.
@@
 \begin{enumerate}[(i)]
-\item the number of crossings between the distinguished subcurve of~$\curveof(\omega)$ in~$\curveof(F)$ and the edge~$\arcof(v)$ of the dissection~$\dissection$,
-\item the number of times the distinguished subcurve of~$\curveof(\omega)$ in~$\curveof(F)$ follows the edge~$\dualarcof(v)$ of the dual dissection~$\dissection\dual$.
-Here, we say that a curve~$\delta$ follows~$\dualarcof(v)$ if~$\dualarcof(v)$ lies on the boundary opposite to~$u$ of a face~$u\dual$ of~$\dissection\dual$ crossed by~$\delta$.
+\item the number of crossings between the distinguished subcurve of~$\curveof(\omega)$ in~$\curveof(F)$ and the edge~$\edgeof(v)$ of the dissection~$\dissection$,
+\item the number of times the distinguished subcurve of~$\curveof(\omega)$ in~$\curveof(F)$ follows the edge~$\dualedgeof(v)$ of the dual dissection~$\dissection\dual$.
+Here, we say that a curve~$\delta$ follows~$\dualedgeof(v)$ if~$\dualedgeof(v)$ lies on the boundary opposite to~$u$ of a face~$u\dual$ of~$\dissection\dual$ crossed by~$\delta$.
 \end{enumerate}

### 2018-07-11 draft/accordionComplexSurfaces.tex
problem notations

@@
 \newcommand{\ZZZ}{\mathsf{Z}} % Z
-\newcommand{\vnext}{n} % next point on the boundary of the surface
-\newcommand{\vprevious}{p} % previous point on the boundary of the surface
+\newcommand{\vnext}[1]{#1_{\operatorname{next}}} % next point on the boundary of the surface
+\newcommand{\vprevious}[1]{#1_{\operatorname{prev}}} % previous point on the boundary of the surface
 
@@
 
-For a vertex~$v \in V$ on the boundary of~$\surface$, we denote by~$\vprevious(v)$ (resp.~$\vnext(v)$) the blossom vertex previous (resp.~next) to~$v$ on the clockwise order around the boundary of~$\surface$.
-For an edge~$a$ of~$\dissection$, we denote by~$\vprevious(a)$ (resp.~$\vnext(a)$) the curve obtained by moving each endpoint~$v$ of~$a$ as follows:
-\begin{itemize}
-\item if~$v$ is on the boundary of~$\surface$, then move (continuously) $v$ along the boundary of~$\surface$ until it reaches~$\vprevious(v)$ (resp.~$\vnext(v)$),
+For a vertex~$v \in V$ on the boundary of~$\surface$, we denote by~$\vprevious{v}$ (resp.~$\vnext{v}$) the blossom vertex previous (resp.~next) to~$v$ on the clockwise order around the boundary of~$\surface$.
+For an edge~$a$ of~$\dissection$, we denote by~$\vprevious{a}$ (resp.~$\vnext{a}$) the curve obtained by moving each endpoint~$v$ of~$a$ as follows:
+\begin{itemize}
+\item if~$v$ is on the boundary of~$\surface$, then move (continuously) $v$ along the boundary of~$\surface$ until it reaches~$\vprevious{v}$ (resp.~$\vnext{v}$),
 \item if~$v$ is a puncture, then rotate around~$v$ in counterclockwise direction (resp.~clockwise direction).
@@
 	\centerline{\includegraphics[scale=.7]{peakDeep}}
-	\caption{The curves~$\vprevious(a)$ (left) and $\vnext(a)$ (right) associated to an edge~$a$ of~$\dissection$ for three different dissections.}
+	\caption{The curves~$\vprevious{a}$ (left) and $\vnext{a}$ (right) associated to an edge~$a$ of~$\dissection$ for three different dissections.}
 	\label{fig:peakDeep}
@@
 
-We invite the reader to check that~$\curveof(p_\peak) = \vprevious(\edgeof(p))$ (resp.~$\curveof(p_\deep) = \vnext(\edgeof(p))$), where~$\edgeof(p)$ denotes the edge of~$\dissection$ corresponding to~$p \in Q_0$ (see Remark~\ref{rem:propertiesSurface}).
+We invite the reader to check that~$\curveof(p_\peak) = \vprevious{\edgeof(p)}$ (resp.~$\curveof(p_\deep) = \vnext{\edgeof(p)}$), where~$\edgeof(p)$ denotes the edge of~$\dissection$ corresponding to~$p \in Q_0$ (see Remark~\ref{rem:propertiesSurface}).
 Therefore, the peak facet (resp.~the deep facet) can be thought of as the dissection~$\dissection$ slightly rotated clockwise (resp.~counterclockwise) on the surface~$\surface$.

### 2018-07-11 draft/accordionComplexSurfaces.tex
Example 6.6

@@
 \usepackage[T1]{fontenc}
-\usepackage{enumerate, amsmath, amsfonts, amssymb, amsthm, mathrsfs, wasysym, graphics, graphicx, xcolor, url, hyperref, hypcap, xargs, multicol, pdflscape, multirow, hvfloat, array, ae, aecompl, pifont, mathtools, a4wide, float}
+\usepackage{enumerate, amsmath, amsfonts, amssymb, amsthm, mathrsfs, wasysym, graphics, graphicx, xcolor, url, hyperref, hypcap, xargs, multicol, pdflscape, multirow, hvfloat, array, ae, aecompl, pifont, mathtools, a4wide, float, blkarray}
 \usepackage{marginnote}
@@
 \newcommand{\pa}{_{\textrm{pa}}} % path
+\newcommand*\circled[1]{\tikz[baseline=(char.base)]{\node[shape=circle,draw,inner sep=1pt, scale=.7] (char) {#1};}}
 
@@
 \label{exm:gcdVectorsWalks}
-\vincent{TODO: exm g- c- and d-vectors}
+For instance, the $\b{g}$-, $\b{c}$-, and $\b{d}$-matrices of the facet illustrated in \fref{} are given by
+\[
+\gvectors{F} = 
+\begin{blockarray}{ccc}
+	{\color{blue} \bullet} & {\color{purple} \bullet} & \\[-.1cm]
+	\begin{block}{[cc]c}
+	1 & 0 & \!\!\!\circled{1} \\
+	-1\!\! & \!\!-1 & \!\!\!\circled{2} \\
+	\end{block}
+\end{blockarray}
+\qquad\qquad
+\cvectors{F} = 
+\begin{blockarray}{ccc}
+	{\color{blue} \bullet} & {\color{purple} \bullet} & \\[-.1cm]
+	\begin{block}{[cc]c}
+	1 & \!\!-1 & \!\!\!\circled{1} \\
+	0 & \!\!-1 & \!\!\!\circled{2} \\
+	\end{block}
+\end{blockarray}
+\qquad\qquad
+\dvectors{F} = 
+\begin{blockarray}{ccc}
+	{\color{blue} \bullet} & {\color{purple} \bullet} & \\[-.1cm]
+	\begin{block}{[cc]c}
+	0 & 1 & \!\!\!\circled{1} \\
+	1 & 1 & \!\!\!\circled{2} \\
+	\end{block}
+\end{blockarray}
+\]
+(\ie columns are the $\b{g}$-, $\b{c}$-, $\b{d}$-vectors of the elements of the facet).
+
+\begin{figure}[t]
+	\capstart
+	\centerline{\includegraphics[scale=.7]{gcdVectors}}
+	\caption{A non-kissing facet (left), an accordion facet (middle) and a slalom facet (right) that correspond via the bijections of Theorem~\ref{thm:complexesCoincide} and Proposition~\ref{prop:accordionsSlaloms}.
+Their~$\b{g}$-, $\b{c}$-, and $\b{d}$-matrices of this facet are given in Example~\ref{exm:gcdVectorsWalks}.}
+	\label{fig:gcdVectors}
+\end{figure}
 \end{example}
@@
 
+\begin{example}
+For instance, one can check that~$\gvectors{F} \cdot \transpose{\cvectors{F}} = 1$ in Example~\ref{exm:gcdVectorsWalks}.
+\end{example}
+
 Finally, we borrow the following geometric statement from~\cite{PaluPilaudPlamondon}.
@@
 
+\vincent{Should we add an example? One of the pictures of~\cite{PaluPilaudPlamondon}?}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-07-11 draft/accordionComplexSurfaces.tex
typos

--- 2018-07-11 draft/accordionComplexSurfaces.tex
@@
 \usepackage[T1]{fontenc}
-\usepackage{enumerate, amsmath, amsfonts, amssymb, amsthm, mathrsfs, wasysym, graphics, graphicx, xcolor, url, hyperref, hypcap, xargs, multicol, pdflscape, multirow, hvfloat, array, ae, aecompl, pifont, mathtools, a4wide, float}
+\usepackage{enumerate, amsmath, amsfonts, amssymb, amsthm, mathrsfs, wasysym, graphics, graphicx, xcolor, url, hyperref, hypcap, xargs, multicol, pdflscape, multirow, hvfloat, array, ae, aecompl, pifont, mathtools, a4wide}
 \usepackage{marginnote}
@@
 \newcommand{\blossom}{^\text{\ding{96}}} % blossom
-%\newcommand{\blinkers}[1]{_{\LEFTCIRCLE \!\! #1 \!\! \RIGHTCIRCLE}} % blossom
-%\newcommand{\indeg}{\mathrm{indeg}} % in-degree
-%\newcommand{\outdeg}{\mathrm{outdeg}} % out-degree
+\newcommand{\blinkers}[1]{_{\LEFTCIRCLE \!\! #1 \!\! \RIGHTCIRCLE}} % blossom
+\newcommand{\indeg}{\mathrm{indeg}} % in-degree
+\newcommand{\outdeg}{\mathrm{outdeg}} % out-degree
 %\newcommand{\tai}{\mathsf{tai}} % target incompatible
@@
 % walks
-%\newcommand{\strings}{\mathcal{S}} % strings
-%\newcommand{\distinguishableStrings}{\mathcal{S}_\mathrm{dist}} % distinguishable strings
-%\newcommand{\lfStrings}{\underline{\mathcal{S}}} % loop-free strings
-%\newcommand{\walks}{\mathcal{W}} % walks
-%\newcommand{\straightWalks}{\mathcal{W}_\mathrm{str}} % straight walks
-%\newcommand{\bendingWalks}{\mathcal{W}_\mathrm{bend}} % bending walks
-%\newcommand{\NKWalks}{\mathcal{W}_\mathrm{nk}} % non-kissing walks
+\newcommand{\strings}{\mathcal{S}} % strings
+\newcommand{\distinguishableStrings}{\mathcal{S}_\mathrm{dist}} % distinguishable strings
+\newcommand{\lfStrings}{\underline{\mathcal{S}}} % loop-free strings
+\newcommand{\walks}{\mathcal{W}} % walks
+\newcommand{\straightWalks}{\mathcal{W}_\mathrm{str}} % straight walks
+\newcommand{\bendingWalks}{\mathcal{W}_\mathrm{bend}} % bending walks
+\newcommand{\NKWalks}{\mathcal{W}_\mathrm{nk}} % non-kissing walks
 \newcommand{\peaks}[1]{\mathsf{peaks}(#1)} % peaks
@@
 \newcommand{\curveof}{\operatorname{\gamma}} % curve (of a walk)
-\newcommand{\edgeof}{\operatorname{\varepsilon}} % arc of a vertex
-\newcommand{\dualedgeof}{\operatorname{\varepsilon}\dual} % dual arc of a vertex
+\newcommand{\arcof}{\operatorname{\varepsilon}} % arc of a vertex
+\newcommand{\dualarcof}{\operatorname{\varepsilon}\dual} % dual arc of a vertex
 \newcommand{\SSS}{\reflectbox{$\mathsf{Z}$}} % S
 \newcommand{\ZZZ}{\mathsf{Z}} % Z
-\newcommand{\vnext}{n} % next point on the boundary of the surface
-\newcommand{\vprevious}{p} % previous point on the boundary of the surface
 
@@
 \end{theorem*}
-
 We end in Section \ref{sec:vectors} with a discussion of~$\b{g}$-vectors,~$\b{c}$-vectors and~$\b{d}$-vectors associated to walks and curves.
+
 Consequences on the representation theory of locally gentle algebras will be investigated in a future project.
 
-Finally, let us briefly review the algebraic and geometric objects which appear in this paper.
+Let us review the algebraic and geometric objects which appear in this paper.
 
@@
 In the case where the surface is a polygon, the $\tau$-tilting theory of the algebra of a dissection has been studied in \cite{PaluPilaudPlamondon, PilaudPlamondonStella}.
+\vincent{Should we also mention cluster algebras from surfaces in this paragraph?}
+\pierreguy{Not sure.}
 
@@
 Our construction has the advantage that it easily yields the two dual dissections of the surface at the same time (the dissection and dual lamination of \cite{OpperPlamondonSchroll}).
-We note that our dissections are always cellular, while those found in \cite{BaurSimoes} can be arbitrary.
+We note that our dissections are always cellularr, while those found in \cite{BaurSimoes} can be arbitrary.
 Remarkably, gentle algebras and surfaces were linked recently in \cite{HaidenKatzarkovKontsevich}, where the Fukaya category of the surface is shown to be equivalent to the bounded derived category of the associated gentle algebra.
@@
 A \defn{string} for~$\bar Q$ is a word which is either a finite string or an eventually cyclic infinite string.
-%We denote by~$\strings(\bar Q)$ the set of strings on~$\bar Q$.
-We often implicitly identify the two inverse strings~$\rho$ and~$\rho^{-1}$, and call it an \defn{undirected string} of~$\bar Q$.
-%we let~$\strings^\pm(\bar Q) \eqdef \set{\{\rho, \rho^{-1}\}}{\rho \in \strings(\bar Q)}$ denote the collection of all \defn{undirected strings} of~$\bar Q$.
+We denote by~$\strings(\bar Q)$ the set of strings on~$\bar Q$.
+We often implicitly identify the two inverse strings~$\rho$ and~$\rho^{-1}$, and we let~$\strings^\pm(\bar Q) \eqdef \set{\{\rho, \rho^{-1}\}}{\rho \in \strings(\bar Q)}$ denote the collection of all \defn{undirected strings} of~$\bar Q$.
+\vincent{Can we delete this notation.}
 \end{definition}
@@
 A \defn{walk} of a locally gentle quiver~$\bar Q$ is a maximal string of its blossoming quiver~$\bar Q \blossom$ (meaning that at each end it either reaches a blossom vertex of~$\bar Q \blossom$ or enters an infinite oriented cycle).
-%We denote by~$\walks(\bar Q)$ the set of all walks on~$\bar Q$.
-As for strings, we implicitly identify the two inverse walks~$\omega$ and~$\omega^{-1}$, and call it an \defn{undirected walk} of~$\bar Q$.
-%we let~$\walks^\pm(\bar Q) \eqdef \set{\{\omega, \omega^{-1}\}}{\omega \in \walks(\bar Q)}$ denote the set of \defn{undirected walks} of~$\bar Q$.
+We denote by~$\walks(\bar Q)$ the set of all walks on~$\bar Q$.
+As for strings, we implicitly identify the two inverse walks~$\omega$ and~$\omega^{-1}$, and we let~$\walks^\pm(\bar Q) \eqdef \set{\{\omega, \omega^{-1}\}}{\omega \in \walks(\bar Q)}$ denote the set of \defn{undirected walks} of~$\bar Q$.
+\vincent{Can we delete this notation.}
 \end{definition}
@@
 \label{def:substrings}
-A \defn{substring} of a walk~$\omega = \prod_{i < \ell < j} \alpha_\ell^{\varepsilon_\ell}$ of~$\bar Q$ is a string~$\sigma = \prod_{i' < \ell < j'} \alpha_\ell^{\varepsilon_\ell}$ of~$\bar Q$ for some~$i \le i' < j' \le j$, where the inequality~$i \le i'$ (resp.~$j' \le j$) is strict when~$i \ne -\infty$ (resp.~$j \ne \infty$).
+A \defn{substring} of a walk~$\omega = \prod_{i < \ell < j} \alpha_\ell^{\varepsilon_\ell} \in \walks(\bar Q)$ is a string~$\sigma = \prod_{i' < \ell < j'} \alpha_\ell^{\varepsilon_\ell}$ of~$\strings(\bar Q)$ for some~$i \le i' < j' \le j$, where the inequality~$i \le i'$ (resp.~$j' \le j$) is strict when~$i \ne -\infty$ (resp.~$j \ne \infty$).
 In other words, $\sigma$ is a factor of~$\omega$ such that
@@
 \begin{definition}
-\label{def:straightBending}
+\label{def:straightBended}
 A \defn{peak} (resp.~\defn{deep}) of a walk~$\omega$ is a substring of~$\omega$ of length zero which is on top (resp.~at the bottom of~$\omega$).
@@
 \label{def:kiss}
-Let~$\omega$ and~$\omega'$ be two undirected walks on~$\bar Q$.
-We say that~$\omega$ \defn{kisses}~$\omega'$ if ${\Sigma_\top(\omega) \cap \Sigma_\bottom(\omega')}$ contains a \emph{finite} substring.
+Let~$\omega,\omega' \in \walks^\pm(\bar Q)$ be two undirected walks on~$\bar Q$.
+We say that~$\omega$ \defn{kisses}~$\omega'$ if~$\Sigma_\top(\omega) \cap \Sigma_\bottom(\omega')$ contains a \emph{finite} substring.
 See \fref{fig:kissing}.
@@
 Observe also that~$\omega$ can kiss~$\omega'$ several times, that~$\omega$ and~$\omega'$ can mutually kiss, and that~$\omega$ can kiss itself.
-%We denote by~$\NKWalks(\bar Q)$ the walks on~$\bar Q$ which are not self-kissing and by~$\NKWalks^\pm(\bar Q) \eqdef \set{\{\omega, \omega^{-1}\}}{\omega \in \NKWalks(\bar Q)}$ their undirected version.
+We denote by~$\NKWalks(\bar Q)$ the walks on~$\bar Q$ which are not self-kissing and by~$\NKWalks^\pm(\bar Q) \eqdef \set{\{\omega, \omega^{-1}\}}{\omega \in \NKWalks(\bar Q)}$ their undirected version.
+\vincent{Can we delete this notation.}
 %
@@
 \label{def:nKc}
-The \defn{non-kissing complex} of~$\bar Q$ is the simplicial complex~$\NKC$ whose faces are the collections of pairwise non-kissing walks of~$\bar Q$.
+The \defn{non-kissing complex} of~$\bar Q$ is the simplicial complex~$\NKC$ whose faces are the collections of pairwise non-kissing walks of~$\NKWalks^\pm(\bar Q)$.
 Note that self-kissing walks never appear in~$\NKC$ by definition.
@@
 	\centerline{\includegraphics[scale=.7]{halfStar} \qquad \includegraphics[scale=.7]{star}}
-	\caption{Two possible situations around~$v$: on the left,~$v$ corresponds to a finite maximal path of~$\bar Q$, while on the right,~$v$ corresponds to an infinite one.}
+	\caption{The situation around~$v$ (green vertex). On the left,~$v$ corresponds to a finite maximal path of~$\bar Q$, while on the right,~$v$ corresponds to an infinite one.}
 	\label{fig:stars}
@@
 \item \label{item:arcs}
-      The dissection~$\dissection_{\bar Q}$ has one edge for each vertex~$p \in \bar Q_0$, obtained by concataining the sides~$\Enrt{\alpha} = \Enrs{\beta}$ and~$\Enrt{\alpha'} = \Enrs{\beta'}$ where~$p = t(\alpha) = s(\beta) = t(\alpha') = s(\beta')$, $\alpha\beta \notin I$ and~$\alpha'\beta' \notin I$.
-We denote by~$\edgeof(p)$ the edge of~$\dissection_{\bar Q}$ corresponding to~$p$.
+      The dissection~$\dissection_{\bar Q}$ has one arc for each vertex~$p \in \bar Q_0$, obtained by concataining the sides~$\Enrt{\alpha} = \Enrs{\beta}$ and~$\Enrt{\alpha'} = \Enrs{\beta'}$ where~$p = t(\alpha) = s(\beta) = t(\alpha') = s(\beta')$, $\alpha\beta \notin I$ and~$\alpha'\beta' \notin I$.
 \item The dissection~$\dissection_{\bar Q}$ has one $\ell$-cell for each straight walk of length~$\ell$ in~$\bar Q\koszul$.
@@
 
-We apply Remark~\ref{rem:propertiesSurface} to understand the corresponding surfaces.
+We now apply Remark~\ref{rem:propertiesSurface} to understand the corresponding surfaces.
 The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}\,(\ref{item:boundary})) form a cycle with green and red arrows alternating.
@@
 
-We apply Remark~\ref{rem:propertiesSurface} to understand the corresponding surfaces.
+We now apply Remark~\ref{rem:propertiesSurface} to understand the corresponding surfaces.
 The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}\,(\ref{item:boundary})) look like~\raisebox{-.1cm}{\includegraphics[scale=.3]{reversedPathsPM}}.
@@
 
-\enlargethispage{.2cm}
-We apply Remark~\ref{rem:propertiesSurface} to understand the corresponding surfaces.
+We now apply Remark~\ref{rem:propertiesSurface} to understand the corresponding surfaces.
 The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}\,(\ref{item:boundary})) look like~\raisebox{-.1cm}{\includegraphics[scale=.3]{doublePathsPModd}} when~$|Q_0|$ is odd and~\raisebox{-.1cm}{\includegraphics[scale=.3]{doublePathsPMeven}} when~$|Q_0|$ is even.
@@
 
-\begin{figure}[H]
+\begin{figure}[h]
 	\capstart
@@
 
-We apply Remark~\ref{rem:propertiesSurface} to understand the corresponding surfaces.
+We now apply Remark~\ref{rem:propertiesSurface} to understand the corresponding surfaces.
 The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}\,(\ref{item:boundary})) are empty since there is no blossom vertices.
@@
 Note that our construction of the surface~$\surface_{\bar Q}$ implies that the vertices of~$\bar Q$ are naturally identified with the intersection points of the dual edges~$a \in \dissection_{\bar Q}$ and~$a\dual \in {\dissection_{\bar Q}}\dual$.
-If we force all $\dissection$-accordions (or $\dissection\dual$-slaloms) to cross the edges of~$\dissection$ and~$\dissection\dual$ only at these intersection points, then an $\dissection$-accordion (or $\dissection\dual$-slalom) is really seen a walk on~$\bar Q$.
+If we force all $\dissection$-accordions (or $\dissection\dual$-slaloms) to cross the edges of~$\dissection$ and~$\dissection\dual$ only at these intersection points, then a $\dissection$-accordion (or $\dissection\dual$-slalom) is really seen as a walk on~$\bar Q$.
 \end{remark}
@@
 \label{exm:peakDeepFacets}
-We have seen in Definition~\ref{def:straightBending} that each vertex~$p$ of~$Q$ gives rise to a \defn{peak walk}~$p_\peak$ (resp.~\defn{deep walk}~$p_\deep$) with a single peak (resp.~deep) at~$v$ and no other corner.
-The set of all such walks forms the \defn{peak facet}~$\set{p_\peak}{p \in Q_0}$ (resp.~the \defn{deep facet}~$\set{p_\deep}{p \in Q_0}$) of the non-kissing complex~$\NKC$.
-As an example of Theorem~\ref{thm:complexesCoincide}, let us now describe the corresponding non-crossing facets of~$\NCC[\surface_{\bar Q}]$.
-
-For a vertex~$v \in V$ on the boundary of~$\surface$, we denote by~$\vprevious(v)$ (resp.~$\vnext(v)$) the blossom vertex previous (resp.~next) to~$v$ on the clockwise order around the boundary of~$\surface$.
-For an edge~$a$ of~$\dissection$, we denote by~$\vprevious(a)$ (resp.~$\vnext(a)$) the curve obtained by moving each endpoint~$v$ of~$a$ as follows:
-\begin{itemize}
-\item if~$v$ is on the boundary of~$\surface$, then move (continuously) $v$ along the boundary of~$\surface$ until it reaches~$\vprevious(v)$ (resp.~$\vnext(v)$),
-\item if~$v$ is a puncture, then rotate around~$v$ in counterclockwise direction (resp.~clockwise direction).
-\end{itemize}
-Examples are illustrated in \fref{fig:peakDeep}.
-%
-\begin{figure}[h]
-	\capstart
-	\centerline{\includegraphics[scale=.7]{peakDeep}}
-	\caption{The curves~$\vprevious(a)$ (left) and $\vnext(a)$ (right) associated to an edge~$a$ of~$\dissection$ for three different dissections.}
-	\label{fig:peakDeep}
-\end{figure}
-
-We invite the reader to check that~$\curveof(p_\peak) = \vprevious(\edgeof(p))$ (resp.~$\curveof(p_\deep) = \vnext(\edgeof(p))$), where~$\edgeof(p)$ denotes the edge of~$\dissection$ corresponding to~$p \in Q_0$ (see Remark~\ref{rem:propertiesSurface}).
-Therefore, the peak facet (resp.~the deep facet) can be thought of as the dissection~$\dissection$ slightly rotated clockwise (resp.~counterclockwise) on the surface~$\surface$.
+
+\vincent{TODO: Describe here the peak and deep facets in terms of the surface.}
 \end{example}
@@
 Two distinct non-kissing walks~$\mu_\star, \nu_\star$ marked at~$\alpha$ in~$\bar Q$ correspond to two distinct non-crossing~$\dissection$-accordions (resp.~$\dissection\dual$-slaloms)~$\gamma$ and~$\delta$ passing in front of this angle.
-Then~$\gamma \prec_\alpha \delta$ if~$\gamma$ passes closer to~$v$ (resp.~farther to~$v\dual$) than~$\delta$ does.
-These interpretations of~$\prec_\alpha$ on the surface where already considered in the case of the disk in~\cite{GarverMcConville, MannevillePilaud-accordion}.
+Then~$\gamma \prec_\alpha \delta$ if~$\gamma$ passes closer (resp.~farther) to~$v$ than~$\delta$ does.
 %
@@
 Assume that there is a puncture with no curves of~$F$ going to it.
-Construct a curve~$\gamma$ as follows:~$\gamma$ first unwinds from the puncture, then~$\gamma$ leaves the local picture around the puncture by turning around another marked point (marked~$u$ on the picture below).
+Construct a curve~$\gamma$ as follows:~$\gamma$ first unwinds from the puncture, then~$\gamma$ leaves the local picture around the puncture by turning around another marked point (marked~$X$ on the picture below).
 
@@
 
-Two situations can occur:
-\begin{itemize}
-\item Firstly, if there are no curves of~$F$ closer to~$u$ than~$\gamma$, then~$\gamma$ can circle around~$u$ until it reaches the boundary (if~$u$ is on the boundary) or infinitely (if~$u$ is a puncture).
+Two situations can occur.
+
+Firstly, if there are no curves of~$F$ closer to~$X$ than~$\gamma$, then~$\gamma$ can circle around~$X$ until it reaches the boundary (if~$X$ is on the boundary) or infinitely (if~$X$ is a puncture).
 Then~$\gamma$ is a~$\dissection_{\bar Q}$-accordion which crosses none of those in~$F$, contradicting the maximality of~$F$.
-\item Secondly, if there is a curve of~$F$ closer to~$u$ than~$\gamma$, then let~$\delta$ be the one furthest from~$u$ ($\delta$ exists by Lemma \ref{lemm:facesHaveMaximalElement}).
+
+Secondly, if there is a curve of~$F$ closer to~$X$ than~$\gamma$, then let~$\delta$ be the one furthest from~$X$ ($\delta$ exists by Lemma \ref{lemm:facesHaveMaximalElement}).
 From there, let~$\gamma$ follow~$\delta$ on the surface until it either reaches the boundary or circles infinitely around a puncture.  
 Then~$\gamma$ is compatible with all curves in~$F$, a contradiction.
-\end{itemize}
+
 Thus~$F$ contains a curve going to the puncture.
@@
 \]
-For a string~$\sigma$ of~$\bar Q$, we define~$\multiplicityVector_\sigma \eqdef \multiplicityVector_{V(\sigma)}$ where~$V(\sigma)$ is the multiset of vertices of~$\sigma$. 
+For a string~$\sigma \in \strings^\pm(\bar Q)$, we define~$\multiplicityVector_\sigma \eqdef \multiplicityVector_{V(\sigma)}$ where~$V(\sigma)$ is the multiset of vertices of~$\sigma$. 
 \end{definition}
@@
 \label{def:gVectorsWalks}
-For a walk~$\omega$ of~$\bar Q$, we denote by~$\peaks{\omega}$ (resp.~by~$\deeps{\omega}$) the multiset of vertices of~$Q_0$ corresponding to the peaks (resp.~deeps) of~$\omega$.
+For a walk~$\omega \in \NKWalks^\pm(\bar Q)$, we denote by~$\peaks{\omega}$ (resp.~by~$\deeps{\omega}$) the multiset of vertices of~$Q_0$ corresponding to the peaks (resp.~deeps) of~$\omega$.
 The \defn{$\b{g}$-vector} of a walk~$\omega$ is the vector~${\gvector{\omega} \in \R^{Q_0}}$ defined by
@@
 \label{def:kissingNumber}
-For two walks~$\omega$ and~$\omega'$ of~$\bar Q$, denote by~$\kn(\omega,\omega')$ the number of kisses of~$\omega$ to~$\omega'$.
+For two walks~$\omega, \omega' \in \NKWalks^\pm(\bar Q)$, denote by~$\kn(\omega,\omega')$ the number of kisses of~$\omega$ to~$\omega'$.
 Note that kisses are counted with multiplicities if~$\omega$ or~$\omega'$ pass twice through the same substring.
@@
 Our objective is now to interpret the three families of vectors of Section~\ref{subsec:gcdVectorsWalks} in terms of accordions and slaloms on the surface.
-According to Remark~\ref{rem:propertiesSurface}\,(\ref{item:arcs}), each vertex~$p$ of~$Q$ corresponds to an edge~$\edgeof(p)$ in the dissection~$\dissection_{\bar Q}$ and  to an edge~$\dualedgeof(p) = \edgeof(p)\dual$ in the dual dissection~${\dissection_{\bar Q}}\dual$.
+According to Remark~\ref{rem:propertiesSurface}\,(\ref{item:arcs}), each vertex~$p$ of~$Q$ corresponds to an edge~$\arcof(p)$ in the dissection~$\dissection_{\bar Q}$ and  to an edge~$\dualarcof(p) = \arcof(p)\dual$ in the dual dissection~${\dissection_{\bar Q}}\dual$.
 Recall moreover from Lemma~\ref{lemm:curveOfAWalkIsAccordion} and Proposition~\ref{prop:accordionsSlaloms} that each non-kissing walk~$\omega$ in~$\bar Q$ corresponds to a curve~$\curveof(\omega)$ that is both a $\dissection$-accordion and a $\dissection\dual$-slalom.
@@
 \label{prop:gVectorsSurface}
-For a walk~$\omega$ of~$\bar Q$ and a vertex~$p \in Q_0$, the $p$th entry of the $\b{g}$-vector~$\gvector{\omega}$ is given~by
+For a walk~$\omega \in \NKWalks^\pm(\bar Q)$ and a vertex~$p \in Q_0$, the $p$th entry of the $\b{g}$-vector~$\gvector{\omega}$ is given~by
 \begin{enumerate}[(i)]
-\item The number of times that the $\dissection$-accordion~$\curveof(\omega)$ positively crosses the edge~$\edgeof(p)$ of~$\dissection$ minus the number of times it negatively crosses the edge~$\edgeof(p)$ of~$\dissection$.
-Here, the crossing is positive (resp.~negative) if the two angles of~$\dissection$ crossed by~$\curveof(\alpha)$ just before and after~$\edgeof(p)$ form a~$\SSS$ (resp.~as a~$\ZZZ$).
-\item The number of times that the $\dissection\dual$-slalom~$\curveof(\omega)$ positively crosses the edge~$\dualedgeof(p)$ of~$\dissection\dual$ minus the number of times it negatively crosses the edge~$\dualedgeof(p)$ of~$\dissection\dual$.
+\item The number of times that the $\dissection$-accordion~$\curveof(\omega)$ positively crosses the edge~$\arcof(p)$ of~$\dissection$ minus the number of times it negatively crosses the edge~$\arcof(p)$ of~$\dissection$.
+Here, the crossing is positive (resp.~negative) if the two angles of~$\dissection$ crossed by~$\curveof(\alpha)$ just before and after~$\arcof(p)$ form a~$\SSS$ (resp.~as a~$\ZZZ$).
+\item The number of times that the $\dissection\dual$-slalom~$\curveof(\omega)$ positively crosses the edge~$\dualarcof(p)$ of~$\dissection\dual$ minus the number of times it negatively crosses the edge~$\dualarcof(p)$ of~$\dissection\dual$.
 Here, the crossing is positive when~$\curveof(\omega)$ leaves a face~$u\dual$ to enter a face~$v\dual$ with the vertex~$u$ being to its right (and thus with~$v$ being to its left), and the crossing is negative otherwise.
@@
 \label{prop:cVectorsSurface}
-Consider a walk~$\omega$ of~$\bar Q$ in a non-kissing facet~$F \in \RNKC$
+Consider a walk~$\omega \in \NKWalks^\pm(\bar Q)$ in a non-kissing facet~$F \in \RNKC$
 Call \defn{distinguished subcurve} of~$\curveof(\omega)$ in~$\curveof(F)$ the part of~$\curveof(\omega)$ which lies strictly between the two angles of~$\dissection$ (or of~$\dissection\dual$) where~$\curveof(\omega)$ is maximal (see Remark~\ref{rem:countercurrentOrderOnSurface}).
@@
 \begin{enumerate}[(i)]
-\item the number of crossings between the distinguished subcurve of~$\curveof(\omega)$ in~$\curveof(F)$ and the edge~$\edgeof(v)$ of the dissection~$\dissection$,
-\item the number of times the distinguished subcurve of~$\curveof(\omega)$ in~$\curveof(F)$ follows the edge~$\dualedgeof(v)$ of the dual dissection~$\dissection\dual$.
-Here, we say that a curve~$\delta$ follows~$\dualedgeof(v)$ if~$\dualedgeof(v)$ lies on the boundary opposite to~$u$ of a face~$u\dual$ of~$\dissection\dual$ crossed by~$\delta$.
+\item the number of crossings between the distinguished subcurve of~$\curveof(\omega)$ in~$\curveof(F)$ and the edge~$\arcof(v)$ of the dissection~$\dissection$,
+\item the number of times the distinguished subcurve of~$\curveof(\omega)$ in~$\curveof(F)$ follows the edge~$\dualarcof(v)$ of the dual dissection~$\dissection\dual$.
+Here, we say that a curve~$\delta$ follows~$\dualarcof(v)$ if~$\dualarcof(v)$ lies on the boundary opposite to~$u$ of a face~$u\dual$ of~$\dissection\dual$ crossed by~$\delta$.
 \end{enumerate}
@@
 Denote by~$X_\deep$ the deep facet of the non-crossing complex as described in Example~\ref{exm:peakDeepFacets}.
-For a walk~$\omega$ of~$\bar Q$ and a vertex~$p \in Q_0$, the $p$th entry of the $\b{d}$-vector~$\dvector{\omega}$ is the number of crossings of the curve~$\gamma(\omega)$ with the edge of~$X_\deep$ corresponding to~$p$.
+For a walk~$\omega \in \NKWalks^\pm(\bar Q)$ and a vertex~$p \in Q_0$, the $p$th entry of the $\b{d}$-vector~$\dvector{\omega}$ is the number of crossings of the curve~$\gamma(\omega)$ with the edge of~$X_\deep$ corresponding to~$p$.
 \end{proposition}

### 2018-07-11 draft/accordionComplexSurfaces.tex
One sentence added.
typos
change name

--- 2018-07-11 draft/accordionComplexSurfaces.tex
@@
 The left hand side of the picture is as in \fref{fig:kissing}, and the right hand side is simply a different representation of it.
-On the surface~$\surface_{\bar Q}$, the dual dissections~$\dissection$ and~$\dissection\dual$ are as on \fref{fig:kissingVSCrossing} (on the right hand side).
+On the surface~$\surface_{\bar Q}$, the dual dissections~$\dissection$ and~$\dissection\dual$ are as on \fref{fig:kissingVSCrossing} (right).
 
@@
 
-For a vertex~$v \in V$ on the boundary of~$\surface$, we denote by~$\vprevious{v}$ (resp.~$\vnext{v}$) the blossom vertex previous (resp.~next) to~$v$ on the clockwise order around the boundary of~$\surface$.
+For a vertex~$v \in V$ on the boundary of~$\surface$, we denote by~$\vprevious{v}$ (resp.~$\vnext{v}$) the blossom vertex previous (resp.~next) to~$v$ on the counterclockwise order around the boundary of~$\surface$.
 For an edge~$a$ of~$\dissection$, we denote by~$\vprevious{a}$ (resp.~$\vnext{a}$) the curve obtained by moving each endpoint~$v$ of~$a$ as follows:
@@
 	\begin{block}{[cc]c}
-	0 & 1 & \!\!\!\circled{1} \\
-	1 & 1 & \!\!\!\circled{2} \\
+	1 & 0 & \!\!\!\circled{1} \\
+	0 & 0 & \!\!\!\circled{2} \\
 	\end{block}
@@
 	\caption{A non-kissing facet (left), an accordion facet (middle) and a slalom facet (right) that correspond via the bijections of Theorem~\ref{thm:complexesCoincide} and Proposition~\ref{prop:accordionsSlaloms}.
-Their~$\b{g}$-, $\b{c}$-, and $\b{d}$-matrices of this facet are given in Example~\ref{exm:gcdVectorsWalks}.}
+The~$\b{g}$-, $\b{c}$-, and $\b{d}$-matrices of this facet are given in Example~\ref{exm:gcdVectorsWalks}.}
 	\label{fig:gcdVectors}

### 2018-07-11 draft/accordionComplexSurfaces.tex
missing crossref
illustration last thm

@@
 
-We conclude this section with four families of examples.
+We conclude this section with four families of examples that illustrate the computation of~$\surface_{\bar Q}$.
 
@@
 \label{exm:gcdVectorsWalks}
-For instance, the $\b{g}$-, $\b{c}$-, and $\b{d}$-matrices of the facet illustrated in \fref{} are given by
+For instance, the $\b{g}$-, $\b{c}$-, and $\b{d}$-matrices of the facet illustrated in \fref{fig:gcdVectors} are given by
 \[
@@
 \begin{theorem}
+\label{thm:fanAssociahedron}
 Let~$\bar Q$ be a locally gentle bound quiver such that~$\NKC$ is finite. The collection of cones
@@
 
-\vincent{Should we add an example? One of the pictures of~\cite{PaluPilaudPlamondon}?}
+We have borrowed \fref{fig:fanAssociahedron} from~\cite{PaluPilaudPlamondon} to illustrate Theorem~\ref{thm:fanAssociahedron}.
+
+\begin{figure}[t]
+	\capstart
+	\centerline{\includegraphics[scale=.5]{fanAssociahedron1}}
+	\centerline{\includegraphics[scale=.5]{fanAssociahedron2}}
+	\caption{The $\b{g}$-vector fan~$\gvectorFan$ (left) and the $\bar Q$-associahedron~$\Asso$ (right) of two gentle quivers. Illustration borrowed from~\cite{PaluPilaudPlamondon}.}
+	\label{fig:fanAssociahedron}
+\end{figure}
 

### 2018-07-11 draft/accordionComplexSurfaces.tex
minor modif abstract

@@
 From those geometric data, we define two simplicial complexes: the accordion complex, and the slalom complex, generalising work of A. Garver and T. McConville in the case of a disk.
-We show that all three simplicial complexes are isomorphic; that they are pure and thin.
+We show that all three simplicial complexes are isomorphic, and that they are pure and thin.
 In particular, there is a notion of mutation on their facets, akin to $\tau$-tilting mutation.
-We also construct inverse bijections between the set of isomorphism classes of locally gentle bound quivers and the set of homeomorphism classes of punctured, marked, oriented surfaces with boundary, endowed with a pair of dual dissections.
+Along the way, we also construct inverse bijections between the set of isomorphism classes of locally gentle bound quivers and the set of homeomorphism classes of punctured, marked, oriented surfaces with boundary, endowed with a pair of dual dissections.
 \end{abstract}

### 2018-07-11 draft/accordionComplexSurfaces.tex
Proposition flip of accordions.

--- 2018-07-11 draft/accordionComplexSurfaces.tex
@@
 The left hand side of the picture is as in \fref{fig:kissing}, and the right hand side is simply a different representation of it.
-On the surface~$\surface_{\bar Q}$, the dual dissections~$\dissection$ and~$\dissection\dual$ are as on \fref{fig:kissingVSCrossing} (right).
+On the surface~$\surface_{\bar Q}$, the dual dissections~$\dissection$ and~$\dissection\dual$ are as on \fref{fig:kissingVSCrossing} (on the right hand side).
 
@@
 
-For a vertex~$v \in V$ on the boundary of~$\surface$, we denote by~$\vprevious{v}$ (resp.~$\vnext{v}$) the blossom vertex previous (resp.~next) to~$v$ on the counterclockwise order around the boundary of~$\surface$.
+For a vertex~$v \in V$ on the boundary of~$\surface$, we denote by~$\vprevious{v}$ (resp.~$\vnext{v}$) the blossom vertex previous (resp.~next) to~$v$ on the clockwise order around the boundary of~$\surface$.
 For an edge~$a$ of~$\dissection$, we denote by~$\vprevious{a}$ (resp.~$\vnext{a}$) the curve obtained by moving each endpoint~$v$ of~$a$ as follows:
@@
 \end{proposition}
+The walk~$\omega'$ of Proposition \ref{prop:flip} is the \defn{flip} of \defn{mutation} of~$F$ at~$\omega$.
 
@@
 \end{corollary}
+
+The mutation of non-kissing facets translates on~$\surface(\bar Q)$ as follows.
+
+\begin{proposition}
+\label{prop:mutationAccordions}
+Let~$F$ be a facet of the non-crossing complex~$\NCC$, and let~$\gamma \in F$.
+Then~$F$ forms a~$B$-dissection of the surface, and~$\gamma$ lies in at least one of the two configutations~$\ZZZ$ and~$\SSS$ with the other curves of the dissection (where the endpoints may be punctures).
+\begin{itemize}
+ \item 
+\end{itemize}
+
+\end{proposition}
 
@@
 	\begin{block}{[cc]c}
-	1 & 0 & \!\!\!\circled{1} \\
-	0 & 0 & \!\!\!\circled{2} \\
+	0 & 1 & \!\!\!\circled{1} \\
+	1 & 1 & \!\!\!\circled{2} \\
 	\end{block}
@@
 	\caption{A non-kissing facet (left), an accordion facet (middle) and a slalom facet (right) that correspond via the bijections of Theorem~\ref{thm:complexesCoincide} and Proposition~\ref{prop:accordionsSlaloms}.
-The~$\b{g}$-, $\b{c}$-, and $\b{d}$-matrices of this facet are given in Example~\ref{exm:gcdVectorsWalks}.}
+Their~$\b{g}$-, $\b{c}$-, and $\b{d}$-matrices of this facet are given in Example~\ref{exm:gcdVectorsWalks}.}
 	\label{fig:gcdVectors}

### 2018-07-11 draft/accordionComplexSurfaces.tex
typos

--- 2018-07-11 draft/accordionComplexSurfaces.tex
@@
 \newcommand{\dualedgeof}{\operatorname{\varepsilon}\dual} % dual arc of a vertex
-\newcommand{\SSS}{\reflectbox{$\mathsf{Z}$}} % S
-\newcommand{\ZZZ}{\mathsf{Z}} % Z
+\newcommand{\SSS}{\reflectbox{$\mathsf{Z}$}} % S deZ or Sed?
+\newcommand{\ZZZ}{\mathsf{Z}} % Z Zed
 \newcommand{\vnext}[1]{#1_{\operatorname{next}}} % next point on the boundary of the surface
@@
 \end{proposition}
-The walk~$\omega'$ of Proposition \ref{prop:flip} is the \defn{flip} of \defn{mutation} of~$F$ at~$\omega$.
 
@@
 \end{corollary}
-
-The mutation of non-kissing facets translates on~$\surface(\bar Q)$ as follows.
-
-\begin{proposition}
-\label{prop:mutationAccordions}
-Let~$F$ be a facet of the non-crossing complex~$\NCC$, and let~$\gamma \in F$.
-Then~$F$ forms a~$B$-dissection of the surface, and~$\gamma$ lies in at least one of the two configutations~$\ZZZ$ and~$\SSS$ with the other curves of the dissection (where the endpoints may be punctures).
-\begin{itemize}
- \item 
-\end{itemize}
-
-\end{proposition}
 

### 2018-07-11 draft/accordionComplexSurfaces.tex
Proposition flip of accordions.

--- 2018-07-11 draft/accordionComplexSurfaces.tex
@@
 The walk~$\omega'$ of Proposition \ref{prop:flip} is the \defn{flip} of \defn{mutation} of~$F$ at~$\omega$.
+The flip is \defn{positive} if~$\sigma$ is on top of~$\omega$, and \defn{negative} otherwise.
 
@@
 \label{prop:mutationAccordions}
-Let~$F$ be a facet of the non-crossing complex~$\NCC$, and let~$\gamma \in F$.
-Then~$F$ forms a~$B$-dissection of the surface, and~$\gamma$ lies in at least one of the two configutations~$\ZZZ$ and~$\SSS$ with the other curves of the dissection (where the endpoints may be punctures).
-\begin{itemize}
- \item 
-\end{itemize}
-
+Let~$F$ be a facet of the non-crossing complex~$\NCC$, and let~$\gamma \in F$.  We represent all curves on the universal cover of~$\surface(\bar Q)$.
+Then~$F$ forms a~$B$-dissection of the surface, and~$\gamma$ lies in at least one of two configutations~$\ZZZ$ and~$\SSS$ with the other curves of the dissection (where the endpoints may go to infinity if punctures are involved).
+\begin{itemize}
+ \item Exactly one of the curves obtained by changing the~$\SSS$ to a~$\ZZZ$ and conversely by moving the endpoints of~$\gamma$ along the top and bottom curves is a~$\dissection$-accordion.
+ \item This~$\dissection$-accordion yields the flip or mutation of~$F$ at~$\gamma$.
+ \item If the flip is positive, then the~$\SSS$ is turned into a~$\ZZZ$.  If the flip is negative, then the~$\ZZZ$ is turned in to an~$\SSS$.
+\end{itemize}
 \end{proposition}
+\begin{proof}
+ Let~$\omega = \walk(\gamma)$.
+Using the notation of Proposition \ref{prop:flip}, the local configuration around~$\omega$ (as in Figure \ref{fig:flip}) translates on the (universal cover of the) surface~$\surface(\bar Q)$ as follows.
+ \pierreguy{1 picture here.}
+
+ We see that the only two~$\dissection$-accordions found between~$\mu$ and~$\curveof(\omega)$ are~$\mu$ and~$\curveof(\omega)$ themselves.  The same holds by replacing~$\mu$ with~$\nu$.
+ Thus~$\mu, \nu$ and~$\curveof(\omega)$ lie in an~$\SSS$ or a~$\ZZZ$.
+
+ We see that~$\curveof(\omega')$ is then obtained as claimed.  Positivity or negativity of the flip translates from the picture in a similar way. 
+\end{proof}
 

### 2018-07-11 draft/accordionComplexSurfaces.tex
Minor changes

--- 2018-07-11 draft/accordionComplexSurfaces.tex
@@
 \end{proposition}
-The walk~$\omega'$ of Proposition \ref{prop:flip} is the \defn{flip} of \defn{mutation} of~$F$ at~$\omega$.
+The walk~$\omega'$ of Proposition \ref{prop:flip} is the \defn{flip} or \defn{mutation} of~$F$ at~$\omega$.
 The flip is \defn{positive} if~$\sigma$ is on top of~$\omega$, and \defn{negative} otherwise.
@@
 
-\vincent{Add a description and a schematic representation of the flip in the accordion complex and in the slalom complex.}
-
 \begin{corollary}
@@
 \end{proof}
-
-\vincent{Orient the flip graph. Connection to the lattice of torsion classes?}
 

### 2018-07-11 draft/accordionComplexSurfaces.tex
last figure

@@
 %This result follows from the existence of flips in non-kissing facets.
-%This operation is illustrated in \fref{fig:flip}.
+%This operation is illustrated in \fref{fig:flip1}.
 
@@
 We have seen in Definition~\ref{def:straightBending} that each vertex~$p$ of~$Q$ gives rise to a \defn{peak walk}~$p_\peak$ (resp.~\defn{deep walk}~$p_\deep$) with a single peak (resp.~deep) at~$v$ and no other corner.
-The set of all such walks forms the \defn{peak facet}~$\set{p_\peak}{p \in Q_0}$ (resp.~the \defn{deep facet}~$\set{p_\deep}{p \in Q_0}$) of the non-kissing complex~$\NKC$.
-As an example of Theorem~\ref{thm:complexesCoincide}, let us now describe the corresponding non-crossing facets of~$\NCC[\surface_{\bar Q}]$.
-
-For a vertex~$v \in V$ on the boundary of~$\surface$, we denote by~$\vprevious{v}$ (resp.~$\vnext{v}$) the blossom vertex previous (resp.~next) to~$v$ on the counterclockwise order around the boundary of~$\surface$.
+The set of all such walks forms the \defn{peak facet}~$\set{p_\peak}{p \in Q_0}$ (resp.~the \defn{deep facet}~$\set{p_\deep}{p \in Q_0}$) of the non-kissing complex~$\RNKC$.
+As an example of Theorem~\ref{thm:complexesCoincide}, let us now describe the corresponding non-crossing facets of~$\RNCC[\surface_{\bar Q}]$.
+
+For a vertex~$v \in V$ on the boundary of~$\surface$, we denote by~$\vprevious{v}$ (resp.~$\vnext{v}$) the blossom vertex previous (resp.~next) to~$v$ when walking along  the boundary of~$\surface$ while keeping it on the right.
 For an edge~$a$ of~$\dissection$, we denote by~$\vprevious{a}$ (resp.~$\vnext{a}$) the curve obtained by moving each endpoint~$v$ of~$a$ as follows:
@@
 \item if~$v$ is on the boundary of~$\surface$, then move (continuously) $v$ along the boundary of~$\surface$ until it reaches~$\vprevious{v}$ (resp.~$\vnext{v}$),
-\item if~$v$ is a puncture, then rotate around~$v$ in counterclockwise direction (resp.~clockwise direction).
+\item if~$v$ is a puncture, then rotate around~$v$ in counterclockwise (resp.~clockwise) direction.
 \end{itemize}
@@
 	\capstart
-	\centerline{\includegraphics[scale=1]{flip}}
+	\centerline{\includegraphics[scale=1]{flip1}}
 	\caption{A schematic representation of flips in the non-kissing complex.
@@
 The walk~$\omega'$ kisses~$\omega$ but no other walk of~$F$ (right).}
-	\label{fig:flip}
+	\label{fig:flip1}
 \end{figure}
@@
 \end{proposition}
+
 \begin{proof}
 Let~$\omega = \walk(\gamma)$.
-Using the notation of Proposition \ref{prop:flip}, the local configuration around~$\omega$ (as in Figure \ref{fig:flip}) translates on the (universal cover of the) surface~$\surface(\bar Q)$ as follows.
- \pierreguy{1 picture here.}
+Using the notation of Proposition \ref{prop:flip}, the local configuration around~$\omega$ (as in Figure \ref{fig:flip1}) translates on the (universal cover of the) surface~$\surface(\bar Q)$ as follows.
+
+\begin{figure}[h]
+	\capstart
+	\centerline{\includegraphics[scale=1]{flip2}}
+	\caption{A schematic representation of flips in the non-crossing complex.
+The flip exchanges the curve~$\omega$ in the facet~$F$ (left) with the curve~$\omega'$ in the facet~$F'$ (middle), using the curves~$\mu$ and~$\nu$.
+The curve~$\omega'$ crosses~$\omega$ but no other curve of~$F$ (right).}
+	\label{fig:flip2}
+\end{figure}
 
@@
 	1 & 0 & \!\!\!\circled{1} \\
-	0 & 0 & \!\!\!\circled{2} \\
+	0 & -1 & \!\!\!\circled{2} \\
 	\end{block}
@@
 	\centerline{\includegraphics[scale=.7]{gcdVectors}}
-	\caption{A non-kissing facet (left), an accordion facet (middle) and a slalom facet (right) that correspond via the bijections of Theorem~\ref{thm:complexesCoincide} and Proposition~\ref{prop:accordionsSlaloms}.
+	\caption{A non-kissing facet of~$\RNKC$ (left), an accordion facet~$\RAC$ (middle) and a slalom facet~$\RSC$ (right) that correspond via the bijections of Theorem~\ref{thm:complexesCoincide} and Proposition~\ref{prop:accordionsSlaloms}.
 The~$\b{g}$-, $\b{c}$-, and $\b{d}$-matrices of this facet are given in Example~\ref{exm:gcdVectorsWalks}.}

### 2018-07-11 draft/accordionComplexSurfaces.tex
path algebra

--- 2018-07-11 draft/accordionComplexSurfaces.tex
@@
 %We consider a \defn{bound quiver}~$\bar Q = (Q,I)$, formed by a quiver~$Q$ and an admissible ideal~$I$ of the path algebra~$kQ$, so that the quotient algebra~$kQ/I$ is finite dimensional.
-We consider a \defn{bound quiver}~$\bar Q = (Q,I)$, formed by a finite quiver~$Q$ and an ideal~$I$ of the path algebra~$kQ$ such that $I$ is generated by linear combinations of paths of length at least two.
+We consider a \defn{bound quiver}~$\bar Q = (Q,I)$, formed by a finite quiver~$Q$ and an ideal~$I$ of the path algebra~$kQ$ (the~$k$-vector space generated by all paths in~$Q$, including vertices as paths of length zero, with multiplication induced by concatenation of paths) such that~$I$ is generated by linear combinations of paths of length at least two.
 Note that we \textbf{do not require} that the quotient algebra~$kQ/I$ be finite dimensional.

### 2018-07-11 draft/accordionComplexSurfaces.tex
Curves in minimal position: references.
relecture section 2

@@
 The \defn{blossoming quiver} of a locally gentle bound quiver~$\bar Q$ is the complete locally gentle bound quiver~$\bar Q\blossom$ whose pruned subquiver is~$\bar Q$.
-The vertices of~$Q\blossom_0 \ssm Q_0$ are called \defn{blossom vertices}, and the arrows~$Q\blossom_1 \ssm Q_1$ are called \defn{blossom arrows}.
+The vertices of~$Q\blossom_0 \ssm Q_0$ are called \defn{blossom vertices}, and the arrows in~$Q\blossom_1 \ssm Q_1$ are called \defn{blossom arrows}.
 \end{definition}
@@
 \label{rem:sizeBlossomingQuiver}
-Note that the blossoming quiver has~$2|Q_0|-|Q_1|$ incoming blossoms and~$2|Q_0|-|Q_1|$ outgoing blossoms.
+Note that~$\bar Q\blossom$ has~$2|Q_0|-|Q_1|$ incoming blossom arrows and~$2|Q_0|-|Q_1|$ outgoing blossom arrows.
 Therefore, it has $|Q_0\blossom| = |Q_0| + 2(2|Q_0|-|Q_1|) = 5|Q_0|-2|Q_1|$ vertices and~$|Q_1\blossom| = |Q_1| + 2(2|Q_0|-|Q_1|) = 4|Q_0|-|Q_1|$ arrows.
@@
 \label{def:topBottom}
-We say that the substring~$\sigma = \prod_{i' < \ell < j'} \alpha_\ell^{\varepsilon_\ell}$ is \defn{at the bottom} (resp.~\defn{on top}) of the walk~$\omega = \prod_{i < \ell < j} \alpha_\ell^{\varepsilon_\ell}$ if~$i'=-\infty$ or~$\varepsilon_{i'-1} = 1$ and~$j'=+\infty$ or~$\varepsilon_{j'+1} = -1$ (resp.~if~$i'=-\infty$ or~$\varepsilon_{i'-1} = -1$ and~$j'=\infty$ or~$\varepsilon_{j'+1} = 1$).
+We say that the substring~$\sigma = \prod_{i' < \ell < j'} \alpha_\ell^{\varepsilon_\ell}$ is \defn{at the bottom} (resp.~\defn{on top}) of the walk~$\omega = \prod_{i < \ell < j} \alpha_\ell^{\varepsilon_\ell}$ if~$i'=-\infty$ or~$\varepsilon_{i'} = 1$ and~$j'=+\infty$ or~$\varepsilon_{j'} = -1$ (resp.~if~$i'=-\infty$ or~$\varepsilon_{i'} = -1$ and~$j'=\infty$ or~$\varepsilon_{j'} = 1$).
 In other words the (at most) two arrows of~$\omega$ incident to the endpoints of~$\sigma$ point towards~$\sigma$ (resp.~outwards from~$\sigma$).
@@
 
-We can now define the non-kissing complex of a locally gentle bound quiver following~\cite{McConville, PaluPilaudPlamondon}.
+We can now define the non-kissing complex of a locally gentle bound quiver following~\cite{McConville, PaluPilaudPlamondon} (see also~\cite{BrustleDouvilleMousavandThomasYildirim}).
 We start with the kissing relation for walks.

### 2018-07-11 draft/accordionComplexSurfaces.tex
Example cycle quivers

--- 2018-07-11 draft/accordionComplexSurfaces.tex
@@
 %We consider a \defn{bound quiver}~$\bar Q = (Q,I)$, formed by a quiver~$Q$ and an admissible ideal~$I$ of the path algebra~$kQ$, so that the quotient algebra~$kQ/I$ is finite dimensional.
-We consider a \defn{bound quiver}~$\bar Q = (Q,I)$, formed by a finite quiver~$Q$ and an ideal~$I$ of the path algebra~$kQ$ (the~$k$-vector space generated by all paths in~$Q$, including vertices as paths of length zero, with multiplication induced by concatenation of paths) such that~$I$ is generated by linear combinations of paths of length at least two.
+We consider a \defn{bound quiver}~$\bar Q = (Q,I)$, formed by a finite quiver~$Q$ and an ideal~$I$ of the path algebra~$kQ$ such that $I$ is generated by linear combinations of paths of length at least two.
 Note that we \textbf{do not require} that the quotient algebra~$kQ/I$ be finite dimensional.
@@
 
-We conclude this section with four families of examples that illustrate the computation of~$\surface_{\bar Q}$.
+We conclude this section with five families of examples that illustrate the computation of~$\surface_{\bar Q}$.
 
@@
 Moreover, $\bar Q$ and~$\bar Q\koszul$ have no infinite straight walks.
-Since~$|Q_1| = |Q_0|-1$, the corresponding surfaces have $1$ boundary component, no puncture and genus~$0$.
+Since~$|Q_1| = |Q_0|-1$, the corresponding surfaces are disks ($1$ boundary component, no puncture and genus~$0$).
 Two examples are represented in \fref{fig:reversedPathsSurfaces}.
@@
 	\label{fig:doublePathsSurfaces}
+\end{figure}
+\end{example}
+
+\begin{example}
+\label{exm:cycle}
+Consider the family of \defn{cycle quivers} indicated in \fref{fig:doubleCyclesQuivers}.
+
+\begin{figure}[H]
+	\capstart
+	\centerline{\includegraphics[scale=.45]{cyclesQuivers}}
+	\caption{The cycle quivers with~$1, 2, 3, 4, 5$ vertices.}
+	\label{fig:cyclesQuivers}
+\end{figure}
+
+We apply Remark~\ref{rem:propertiesSurface} to understand the corresponding surfaces.
+The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}\,(\ref{item:boundary})) form a cycle with green and red arrows alternating.
+Moreover, $\bar Q$ has~$1$ infinite straight walk, while~$\bar Q\koszul$ has none.
+Since~$|Q_1| = |Q_0|$, the corresponding surfaces are punctured disks ($1$ boundary component, $1$ puncture and genus~$0$).
+The first few corresponding surfaces are represented in \fref{fig:doubleCyclesSurfaces} (see Figures~\ref{fig:surfaces} and~\ref{fig:reversedPathsSurfaces} for the cycles with $1$ or~$2$ vertices).
+
+\begin{figure}[h]
+	\capstart
+	\centerline{\includegraphics[scale=.7]{cyclesSurfacesBis}}
+	\caption{The surface~$\surface_{\bar Q}$ for the cycle quivers with~$3, 4, 5$ vertices.}
+	\label{fig:doubleCyclesSurfaces}
 \end{figure}

### 2018-07-11 draft/accordionComplexSurfaces.tex

--- 2018-07-11 draft/accordionComplexSurfaces.tex
@@
 We will always assume that collections of arcs on a surface are in minimal position, in the sense that they cross each other transversaly, and the number of crossings is minimal.
-This is always possible up to homotopy. \pierreguy{Reference?}
+It is pointed out in \cite{Thurston} that the results in \cite{FreedmanHassScott} and \cite{Neumann-Coto} imply that this assumption can always be satisfied (up to homotopy).
 \end{definition}

### 2018-07-11 draft/accordionComplexSurfaces.tex
minor mistake picture

@@
 
-We can now define the non-kissing complex of a locally gentle bound quiver following~\cite{McConville, PaluPilaudPlamondon} (see also~\cite{BrustleDouvilleMousavandThomasYildirim}).
+We can now define the non-kissing complex of a locally gentle bound quiver following~\cite{McConville, PaluPilaudPlamondon, BrustleDouvilleMousavandThomasYildirim}.
 We start with the kissing relation for walks.

### 2018-07-11 draft/accordionComplexSurfaces.tex
fan and polytope

@@
 
-We have borrowed \fref{fig:fanAssociahedron} from~\cite{PaluPilaudPlamondon} to illustrate Theorem~\ref{thm:fanAssociahedron}.
-
-\begin{figure}[t]
+\fref{fig:fanAssociahedron} illustrates Theorem~\ref{thm:fanAssociahedron}.
+
+\begin{figure}[p]
 	\capstart
 	\centerline{\includegraphics[scale=.5]{fanAssociahedron1}}
+	\vspace{.5cm}
 	\centerline{\includegraphics[scale=.5]{fanAssociahedron2}}
-	\caption{The $\b{g}$-vector fan~$\gvectorFan$ (left) and the $\bar Q$-associahedron~$\Asso$ (right) of two gentle quivers. Illustration borrowed from~\cite{PaluPilaudPlamondon}.}
+	\vspace{.5cm}
+	\centerline{\includegraphics[scale=.5]{fanAssociahedron3}}
+	\caption{The $\b{g}$-vector fan~$\gvectorFan$ (left) and the $\bar Q$-associahedron~$\Asso$ (right) of three locally gentle quivers.
+The first two are gentle and the illustration is borrowed from~\cite{PaluPilaudPlamondon}.
+The last is locally gentle but not gentle.}
 	\label{fig:fanAssociahedron}

### 2018-07-11 draft/accordionComplexSurfaces.tex
figure Yann

@@
 \newcommand{\dualedgeof}{\operatorname{\varepsilon}\dual} % dual arc of a vertex
-\newcommand{\SSS}{\reflectbox{$\mathsf{Z}$}} % S deZ or Sed?
-\newcommand{\ZZZ}{\mathsf{Z}} % Z Zed
+\DeclareRobustCommand{\SSS}{\reflectbox{$\mathsf{Z}$}} % S
+\DeclareRobustCommand{\ZZZ}{\mathsf{Z}} % Z
 \newcommand{\vnext}[1]{#1_{\operatorname{next}}} % next point on the boundary of the surface
@@
 The walk~$\omega'$ of Proposition \ref{prop:flip} is the \defn{flip} or \defn{mutation} of~$F$ at~$\omega$.
-The flip is \defn{positive} if~$\sigma$ is on top of~$\omega$, and \defn{negative} otherwise.
+The flip is \defn{increasing} if~$\sigma$ is on top of~$\omega$, and \defn{decreasing} otherwise.
 
@@
 Then~$F$ forms a~$B$-dissection of the surface, and~$\gamma$ lies in at least one of two configutations~$\ZZZ$ and~$\SSS$ with the other curves of the dissection (where the endpoints may go to infinity if punctures are involved).
+See \fref{fig:flip3}.
 \begin{itemize}
@@
 \item This~$\dissection$-accordion yields the flip or mutation of~$F$ at~$\gamma$.
-\item If the flip is positive, then the~$\SSS$ is turned into a~$\ZZZ$.  If the flip is negative, then the~$\ZZZ$ is turned in to an~$\SSS$.
-\end{itemize}
+\item If the flip is increasing, then the~$\SSS$ is turned into a~$\ZZZ$.  If the flip is decreasing, then the~$\ZZZ$ is turned in to an~$\SSS$.
+\end{itemize}
+%
+\begin{figure}[h]
+	\capstart
+	\centerline{\includegraphics[scale=1]{flip3}}
+	\caption{A flip turns a~$\ZZZ$ (formed by~$\mu$, $\omega$ and~$\nu$) to a~$\SSS$ (formed by~$\mu$, $\omega'$ and~$\nu$). The two curves~$\omega$ and~$\omega'$ are crossing.}
+	\label{fig:flip3}
+\end{figure}
 \end{proposition}

### 2018-07-12 draft/accordionComplexSurfaces.tex
relecture section 3

@@
 \begin{itemize}
-\item the edges of~$a$ and~$b$ of~$f$ crossed by~$\alpha$ might coincide, see ...
-\item the second condition is automatically satisfied if~$f\dual$ is not a puncture, \ie when it lies on the boundary of~$\surface$.
+\item the edges of~$a$ and~$b$ of~$f$ crossed by~$\alpha$ might coincide, see the second example in Figure~\ref{fig:accordions}.
+\item the first condition is automatically satisfied if~$f\dual$ is not a puncture, \ie when it lies on the boundary of~$\surface$.
 \end{itemize}
@@
 The \defn{$\dissection\dual$-slalom complex}~$\SC$ is the simplicial complex whose faces are the collections of pairwise non-crossing $\dissection\dual$-slaloms.
-Note that self-crossing slalom never appear in~$\SC$ by definition.
+Note that self-crossing slaloms never appear in~$\SC$ by definition.
 In contrast, no external slalom can cross another slalom, so that they appear in all facets of~$\SC$. 
@@
 Let~$f$ be the face of~$\dissection$ that contains the segment of~$\alpha$ between~$a$ and~$b$.
-Consider the connected component of~$f\setminus\alpha$ that do not contain~$f\dual$.
+Consider the connected component of~$f\setminus\alpha$ that does not contain~$f\dual$.
 The boundary of this component contains an edge~$c \in \dissection \setminus \{a\}$ that share a common endpoint with~$a$.
 Let~$u,v$ be the endpoints of~$c$.
-Then~$\alpha$ cuts the cells $u\dual,v\dual$ glued along~$c\dual$ into two connected component, one containing both endpoints of~$\delta$.
+Then~$\alpha$ cuts the cells $u\dual,v\dual$ glued along~$c\dual$ into two connected components, one containing both endpoints of~$\delta$.
 
@@
 Since the dissection~$\dissection$ is cellular, that region has to contain some marked point~$u \in \dissection\dual$.
-One conclude that~$\alpha$ is not a~$\dissection\dual$-slalom similarly as in the first case, by considering the component of~$u\dual \setminus \alpha$ that do not contain~$u$.
+One conclude that~$\alpha$ is not a~$\dissection\dual$-slalom similarly as in the first case, by considering the component of~$u\dual \setminus \alpha$ that does not contain~$u$.
 
@@
 \begin{example}
-When the dissection~$\dissection$ is a classical dissection of a polygon (with no puncture) where each cell has at most one boundary edge, the dual dissection~$\dissection\dual$ is a tree.
+When the dissection~$\dissection$ is a classical dissection of a polygon (with no punctures) where each cell has at most one boundary edge, the dual dissection~$\dissection\dual$ is a tree.
 The non-kissing complex in his situation was treated in detail in~\cite{GarverMcConville, MannevillePilaud-accordion}.
@@
 This prevents to use the definitions given in this section.
-Although its accordion complex (resp.~slalom complex) could still be defined as in~\cite{MannevillePilaud-accordion} (resp.~\cite{GarverMcConville}) for the disk, the resulting complexes would be join of smaller accordion complexes (resp.~slalom complexes) defined in this paper.
+Although its accordion complex (resp.~slalom complex) could still be defined as in~\cite{MannevillePilaud-accordion} (resp.~\cite{GarverMcConville}) for the disk, the resulting complexes would be joins of smaller accordion complexes (resp.~slalom complexes) defined in this paper.
 See \cite[Prop.~2.4]{MannevillePilaud-accordion} for a detailed statement in the case of the disk.

### 2018-07-12 draft/accordionComplexSurfaces.tex
relecture section 4

@@
 Namely, any pair of dual cellular dissections~$(\dissection, \dissection\dual)$ defines a locally gentle bound quiver~$\bar Q_{\dissection, \dissection\dual}$ such that the non-crossing complex~$\NCC$ is isomorphic to the non-kissing complex~$\NKC[\bar Q_{\dissection, \dissection\dual}]$.
-Conversely, any locally gentle bound quiver~$\bar Q$ gives rise to a surface~$\surface_{\bar Q}$ equipped with a pair of dual cellular dissections~$\dissection_{\bar Q}$ and~${\dissection_{\bar Q}}\dual$ such that the non-kissing complex~$\NKC$ is isomorphic to the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$.
+Conversely, any locally gentle bound quiver~$\bar Q$ gives rise to a surface~$\surface_{\bar Q}$ equipped with a pair of dual cellular dissections~$\dissection_{\bar Q}$ and~${\dissection\dual_{\bar Q}}$ such that the non-kissing complex~$\NKC$ is isomorphic to the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection\dual_{\bar Q}}]$.
 In fact, we show that the accordion, slalom, and non-kissing complexes can all be pictured in a unique way on the surface.
-Interestingly, via the correspondence between pairs of dual cellular dissections and locally gentle bound quivers, the duality between the dissections~$\dissection$ and~$\dissection\dual$ translates to the Koszul duality between the locally gentle algebras of~$\bar Q$ and~$\bar Q\koszul$.
+Interestingly, via the correspondence between pairs of dual cellular dissections and locally gentle bound quivers, the duality between the dissections~$\dissection$ and~$\dissection\dual$ translates into the Koszul duality between the locally gentle algebras of~$\bar Q$ and~$\bar Q\koszul$.
 
@@
 \begin{itemize}
- \item the set of vertices of~$Q_{\dissection}$ is the set or edges of $\dissection$;
+ \item the set of vertices of~$Q_{\dissection}$ is the set of edges of $\dissection$;
  \item there is an arrow from~$a$ to~$b$ for each common endpoint~$v$ of~$a$ and~$b$ such that~$b$ comes immediately after~$a$ in the counterclockwise order around~$v$;
@@
 	\centerline{\includegraphics[scale=.7]{quiversDissections2}}
-	\caption{The quivers associated to the dissections of \fref{fig:dissections}. As stated in Proposition~\ref{prop:dualityKoszul1}, dual dissections give rise to Koszul dual quivers.}
+	\caption{The quivers associated to the dissections of \fref{fig:dissections}. As stated in Proposition~\ref{prop:dualityKoszul1}, dual dissections give rise to Koszul dual bound quivers.}
 	\label{fig:quiversDissections}
@@
 \begin{proof}
-Each arc~$a$ has two endpoints, and at each endpoint there is at most one arc coming immediately after~$a$ in the clockwise order, and at most one coming immediately before.
+Each arc~$a$ has two endpoints, and at each endpoint there is at most one arc coming immediately after~$a$ in the clockwise order, and at most one coming immediately before~$a$.
 Thus, in~$Q_{\dissection}$, there are at most two arrows leaving~$a$ and at most two arriving in~$a$.
@@
 
-The advantage of Definition~\ref{def:surfaceQuiver} is that it automatically endows~$\surface_{\bar Q}$ with two disjoint sets~$V_{\bar Q}$ and~${V_{\bar Q}}\dual$ of marked points and two dual cellular dissections~$\dissection_{\bar Q}$ and~${\dissection_{\bar Q}}\dual$ defined as follows.
+The advantage of Definition~\ref{def:surfaceQuiver} is that it automatically endows~$\surface_{\bar Q}$ with two disjoint sets~$V_{\bar Q}$ and~${V\dual_{\bar Q}}$ of marked points and two dual cellular dissections~$\dissection_{\bar Q}$ and~${\dissection\dual_{\bar Q}}$ defined as follows.
 
@@
 \end{itemize}
-The set~${V_{\bar Q}}\dual$ and the ${V_{\bar Q}}\dual$-dissection~${\dissection_{\bar Q}}\dual$ are defined dually.
+The set~${V\dual_{\bar Q}}$ and the ${V\dual_{\bar Q}}$-dissection~${\dissection\dual_{\bar Q}}$ are defined dually.
 \end{definition}
@@
 Let~$\bar Q$ be a locally gentle bound quiver.
-Then the dissections~$\dissection_{\bar Q}$ and~$\dissection_{\bar Q}\dual$ are cellular and dual to each other.
+Then the dissections~$\dissection_{\bar Q}$ and~$\dissection\dual_{\bar Q}$ are cellular and dual to each other.
 \end{proposition}
@@
 \item \label{item:arcs}
-      The dissection~$\dissection_{\bar Q}$ has one edge for each vertex~$p \in \bar Q_0$, obtained by concataining the sides~$\Enrt{\alpha} = \Enrs{\beta}$ and~$\Enrt{\alpha'} = \Enrs{\beta'}$ where~$p = t(\alpha) = s(\beta) = t(\alpha') = s(\beta')$, $\alpha\beta \notin I$ and~$\alpha'\beta' \notin I$.
-We denote by~$\edgeof(p)$ the edge of~$\dissection_{\bar Q}$ corresponding to~$p$.
+      The dissection~$\dissection_{\bar Q}$ has one edge for each vertex~$v \in \bar Q_0$, obtained by concatenation of the sides~$\Enrt{\alpha} = \Enrs{\beta}$ and~$\Enrt{\alpha'} = \Enrs{\beta'}$ where~$v = t(\alpha) = s(\beta) = t(\alpha') = s(\beta')$, $\alpha\beta \notin I$ and~$\alpha'\beta' \notin I$.
+We denote by~$\edgeof(v)$ the edge of~$\dissection_{\bar Q}$ corresponding to~$v$.
 \item The dissection~$\dissection_{\bar Q}$ has one $\ell$-cell for each straight walk of length~$\ell$ in~$\bar Q\koszul$.
-\item A similar remark holds dually for~${V_{\bar Q}}\dual$ and~${\dissection_{\bar Q}}\dual$.
+\item A similar remark holds dually for~${V\dual_{\bar Q}}$ and~${\dissection\dual_{\bar Q}}$.
 \item The number~$p$ of punctures of~$\surface_{\bar Q}$ is the number of infinite straight walks in~$\bar Q$ and in~$\bar Q\koszul$.
@@
 \label{prop:dualityKoszul2}
-For any gentle bound quiver~$\bar Q$ with Koszul dual~$\bar Q\koszul$, the surfaces~$\surface_{\bar Q}$ and~$\surface_{\bar Q\koszul}$ coincide, but~$\dissection_{\bar Q\koszul} = {\dissection_{\bar Q}}\dual$ and~${\dissection_{\bar Q\koszul}}\dual = \dissection_{\bar Q}$.
+For any gentle bound quiver~$\bar Q$ with Koszul dual~$\bar Q\koszul$, the surfaces~$\surface_{\bar Q}$ and~$\surface_{\bar Q\koszul}$ coincide, but~$\dissection_{\bar Q\koszul} = {\dissection\dual_{\bar Q}}$ and~${\dissection\dual_{\bar Q\koszul}} = \dissection_{\bar Q}$.
 \end{proposition}
@@
 The construction of the surface given in Definition \ref{def:surfaceQuiver} yields the same surface as the one constructed in \cite{OpperPlamondonSchroll}.
-A notable difference is that in \cite{OpperPlamondonSchroll}, only~$\dissection_{\bar Q}$ is given, and~$\dissection_{\bar Q}\dual$ is deduced (it is called the dual lamination).
+A notable difference is that in \cite{OpperPlamondonSchroll}, only~$\dissection_{\bar Q}$ is given, and~$\dissection\dual_{\bar Q}$ is deduced (it is called the dual lamination).
 Another minor difference is that the construction in \cite{OpperPlamondonSchroll} is written only for gentle algebras, while here it is generalized to locally gentle algebras.
@@
 Note that the dissection~$\dissection_{\bar Q}$ is a triangulation with no internal triangles, and the orientation of~$\bar Q$ indicates how to glue these triangles.
-For instance, the Cambrian quiver completely oriented in one direction yields a fan triangulation, were all internal arcs are incident to the same vertex, as in \fref{fig:reversedPathsSurfaces}\,(left).
+For instance, the Cambrian quiver completely oriented in one direction yields a fan triangulation, were all internal arcs are incident to the same vertex, as in \fref{fig:CambrianPathsSurfaces}\,(left).
 
@@
 \label{exm:cycle}
-Consider the family of \defn{cycle quivers} indicated in \fref{fig:doubleCyclesQuivers}.
+Consider the family of \defn{cycle quivers} indicated in \fref{fig:cyclesQuivers}.
 
@@
 Since~$|Q_1| = |Q_0|$, the corresponding surfaces are punctured disks ($1$ boundary component, $1$ puncture and genus~$0$).
-The first few corresponding surfaces are represented in \fref{fig:doubleCyclesSurfaces} (see Figures~\ref{fig:surfaces} and~\ref{fig:reversedPathsSurfaces} for the cycles with $1$ or~$2$ vertices).
+The first few corresponding surfaces are represented in \fref{fig:cyclesSurfacesBis} (see Figures~\ref{fig:surfaces} and~\ref{fig:reversedPathsSurfaces} for the cycles with $1$ or~$2$ vertices, recalling that~$\bar Q$ and~$\bar Q\koszul$ yield the same surface).
 
@@
 	\caption{The surface~$\surface_{\bar Q}$ for the cycle quivers with~$3, 4, 5$ vertices.}
-	\label{fig:doubleCyclesSurfaces}
+	\label{fig:cyclesSurfacesBis}
 \end{figure}
@@
 Then~$\gamma$ is completely determined by its sequence of intersection points with the arcs of~$\dissection_{\bar Q}$, since the dissection is cellular.
-Two successive intersection points in this sequence define an angle between two arcs of~$\dissection_{\bar Q}$, which correspoinds to an arrow in~$\bar Q$.
+Two successive intersection points in this sequence define an angle between two arcs of~$\dissection_{\bar Q}$, which corresponds to an arrow in~$\bar Q$.
 Thus the sequence of intersection points defines a walk~$\walk(\gamma)$ on~$\bar Q$.
@@
 \begin{itemize}
-\item for any locally gentle bound quiver~$\bar Q$, the non-kissing complex~$\NKC$ is isomorphic to the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$,% therefore to the accordion complex~$\AC[\dissection_{\bar Q}]$ and to the slalom complex~$\SC[{\dissection_{\bar Q}}\dual]$.
+\item for any locally gentle bound quiver~$\bar Q$, the non-kissing complex~$\NKC$ is isomorphic to the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection\dual_{\bar Q}}]$,% therefore to the accordion complex~$\AC[\dissection_{\bar Q}]$ and to the slalom complex~$\SC[{\dissection_{\bar Q}}\dual]$.
 \item for any pair of dual cellular dissections~$\dissection, \dissection\dual$ of an oriented surface, the non-crossing complex~$\NCC$ is isomorphic to the non-kissing complex~$\NKC[\bar Q_{\dissection, \dissection\dual}]$.
@@
 \begin{remark}
-Note that our construction of the surface~$\surface_{\bar Q}$ implies that the vertices of~$\bar Q$ are naturally identified with the intersection points of the dual edges~$a \in \dissection_{\bar Q}$ and~$a\dual \in {\dissection_{\bar Q}}\dual$.
+Note that our construction of the surface~$\surface_{\bar Q}$ implies that the vertices of~$\bar Q$ are naturally identified with the intersection points of the dual edges~$a \in \dissection_{\bar Q}$ and~$a\dual \in {\dissection\dual_{\bar Q}}$.
 If we force all $\dissection$-accordions (or $\dissection\dual$-slaloms) to cross the edges of~$\dissection$ and~$\dissection\dual$ only at these intersection points, then a $\dissection$-accordion (or $\dissection\dual$-slalom) is really seen as a walk on~$\bar Q$.
@@
 \label{exm:peakDeepFacets}
-We have seen in Definition~\ref{def:straightBending} that each vertex~$p$ of~$Q$ gives rise to a \defn{peak walk}~$p_\peak$ (resp.~\defn{deep walk}~$p_\deep$) with a single peak (resp.~deep) at~$v$ and no other corner.
-The set of all such walks forms the \defn{peak facet}~$\set{p_\peak}{p \in Q_0}$ (resp.~the \defn{deep facet}~$\set{p_\deep}{p \in Q_0}$) of the non-kissing complex~$\RNKC$.
+We have seen in Definition~\ref{def:straightBending} that each vertex~$v$ of~$Q$ gives rise to a \defn{peak walk}~$v_\peak$ (resp.~\defn{deep walk}~$v_\deep$) with a single peak (resp.~deep) at~$v$ and no other corner.
+The set of all such walks forms the \defn{peak facet}~$\set{v_\peak}{v \in Q_0}$ (resp.~the \defn{deep facet}~$\set{v_\deep}{v \in Q_0}$) of the non-kissing complex~$\RNKC$.
 As an example of Theorem~\ref{thm:complexesCoincide}, let us now describe the corresponding non-crossing facets of~$\RNCC[\surface_{\bar Q}]$.
@@
 
-We invite the reader to check that~$\curveof(p_\peak) = \vprevious{\edgeof(p)}$ (resp.~$\curveof(p_\deep) = \vnext{\edgeof(p)}$), where~$\edgeof(p)$ denotes the edge of~$\dissection$ corresponding to~$p \in Q_0$ (see Remark~\ref{rem:propertiesSurface}).
+We invite the reader to check that~$\curveof(v_\peak) = \vprevious{\edgeof(v)}$ (resp.~$\curveof(v_\deep) = \vnext{\edgeof(v)}$), where~$\edgeof(v)$ denotes the edge of~$\dissection$ corresponding to~$v \in Q_0$ (see Remark~\ref{rem:propertiesSurface}).
 Therefore, the peak facet (resp.~the deep facet) can be thought of as the dissection~$\dissection$ slightly rotated clockwise (resp.~counterclockwise) on the surface~$\surface$.

### 2018-07-12 draft/accordionComplexSurfaces.tex
Typoes Section 3.

--- 2018-07-12 draft/accordionComplexSurfaces.tex
@@
 The boundaries of the surfaces are shaded, and the glue symbols indicate how to identify some edges to get the desired surfaces.
-The first two surfaces are disks, the third is a sphere, the fourth is a cylinder, and the fifth is a punctured torus.
+The first two surfaces are disks, the third is a sphere without boundary, the fourth is a cylinder, and the fifth is a punctured torus.
 The dissection~$\dissection$ is in green while its dual dissection~$\dissection\dual$ is~in~red.}
@@
 When the dissection~$\dissection$ is a classical dissection of a polygon (with no punctures) where each cell has at most one boundary edge, the dual dissection~$\dissection\dual$ is a tree.
-The non-kissing complex in his situation was treated in detail in~\cite{GarverMcConville, MannevillePilaud-accordion}.
+The non-kissing complex in this situation was treated in detail in~\cite{GarverMcConville, MannevillePilaud-accordion}.
 Note that even when the surface~$\surface$ is a disk, we authorize here both~$\dissection$ and~$\dissection\dual$ to have interior faces and punctures.
@@
 As stated in Proposition~\ref{prop:conditionsDualDissections}, a cellular dissection~$\dissection$ with a face containing more than one boundary edge does not admit a dual cellular dissection~$\dissection\dual$.
-This prevents to use the definitions given in this section.
-Although its accordion complex (resp.~slalom complex) could still be defined as in~\cite{MannevillePilaud-accordion} (resp.~\cite{GarverMcConville}) for the disk, the resulting complexes would be joins of smaller accordion complexes (resp.~slalom complexes) defined in this paper.
+This prevents the use of the definitions given in this section.
+Although the accordion complex (resp.~slalom complex) could still be defined as in~\cite{MannevillePilaud-accordion} (resp.~\cite{GarverMcConville}) for the disk, the resulting complexes would be joins of smaller accordion complexes (resp.~slalom complexes) defined in this paper.
 See \cite[Prop.~2.4]{MannevillePilaud-accordion} for a detailed statement in the case of the disk.

### 2018-07-12 draft/accordionComplexSurfaces.tex
Typoes Section 4.

@@
 In this section, we show that non-kissing and non-crossing complexes actually coincide.
-Namely, any pair of dual cellular dissections~$(\dissection, \dissection\dual)$ defines a locally gentle bound quiver~$\bar Q_{\dissection, \dissection\dual}$ such that the non-crossing complex~$\NCC$ is isomorphic to the non-kissing complex~$\NKC[\bar Q_{\dissection, \dissection\dual}]$.
+Namely, any pair of dual cellular dissections~$(\dissection, \dissection\dual)$ defines a locally gentle bound quiver~$\bar Q_{\dissection}$ such that the non-crossing complex~$\NCC$ is isomorphic to the non-kissing complex~$\NKC[\bar Q_{\dissection}]$.
 Conversely, any locally gentle bound quiver~$\bar Q$ gives rise to a surface~$\surface_{\bar Q}$ equipped with a pair of dual cellular dissections~$\dissection_{\bar Q}$ and~${\dissection\dual_{\bar Q}}$ such that the non-kissing complex~$\NKC$ is isomorphic to the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection\dual_{\bar Q}}]$.
@@
 \label{lemm:quiverOfDissectionIsLocallyGentle}
-The bound quiver~$\bar Q_{\dissection} = (Q_{\dissection}, I_{\dissection})$ is a locally gentle bound quiver
+The bound quiver~$\bar Q_{\dissection} = (Q_{\dissection}, I_{\dissection})$ is a locally gentle bound quiver.
 \end{lemma}
@@
 It is seen in \cite{BessenrodtHolm} that the (ungraded version of the) Koszul dual of a locally gentle algebra~$kQ/I$ is isomorphic to~$kQ\koszul/I\koszul$.
-Note that~$\bar Q\koszul$ is gentle, and that Koszul duality is an involution and commutes with blossoming:~$(\bar Q\koszul)\koszul = \bar Q$ and~$(\bar Q\koszul)\blossom = (\bar Q\blossom)\koszul$.
+Note that~$\bar Q\koszul$ is locally gentle, and that Koszul duality is an involution and commutes with blossoming:~$(\bar Q\koszul)\koszul = \bar Q$ and~$(\bar Q\koszul)\blossom = (\bar Q\blossom)\koszul$.
 Examples are represented on \fref{fig:koszulQuivers}.
@@
 \item for any locally gentle bound quiver~$\bar Q$, the non-kissing complex~$\NKC$ is isomorphic to the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection\dual_{\bar Q}}]$,% therefore to the accordion complex~$\AC[\dissection_{\bar Q}]$ and to the slalom complex~$\SC[{\dissection_{\bar Q}}\dual]$.
-\item for any pair of dual cellular dissections~$\dissection, \dissection\dual$ of an oriented surface, the non-crossing complex~$\NCC$ is isomorphic to the non-kissing complex~$\NKC[\bar Q_{\dissection, \dissection\dual}]$.
+\item for any pair of dual cellular dissections~$\dissection, \dissection\dual$ of an oriented surface, the non-crossing complex~$\NCC$ is isomorphic to the non-kissing complex~$\NKC[\bar Q_{\dissection}]$.
 \end{itemize}

### 2018-07-12 draft/accordionComplexSurfaces.tex
Typoes Section 6.

@@
 
-We now recall two definitions from~\cite{PaluPilaudPlamondon}, that still make sense for locally gentle algebras.
+We now recall two definitions from~\cite{PaluPilaudPlamondon} that still make sense for locally gentle algebras.
 
@@
 For a set~$\Omega$ of walks, we let~$\gvectors{\Omega} \eqdef \set{\gvector{\omega}}{\omega \in \Omega}$.
-Observe that~$\gvector{\omega} = 0$ for a straight walk~$\omega$, and that, since for any infinite walk~$\omega$ is eventually cyclic, the coordinates of~$\gvector{\omega}$ are finite.
+Observe that~$\gvector{\omega} = 0$ for a straight walk~$\omega$, and that, since any infinite walk~$\omega$ is eventually cyclic, the coordinates of~$\gvector{\omega}$ are finite.
 \end{definition}
@@
 
-We now introduce yet another algebraically motivated family of vectors that was omitted in~\cite{PaluPilaudPlamondon}.
+We now introduce another algebraically motivated family of vectors that was omitted in~\cite{PaluPilaudPlamondon}.
 We first need to introduce the kissing number.
@@
 \label{prop:cVectorsSurface}
-Consider a walk~$\omega$ of~$\bar Q$ in a non-kissing facet~$F \in \RNKC$
+Consider a walk~$\omega$ of~$\bar Q$ in a non-kissing facet~$F \in \RNKC$.
 Call \defn{distinguished subcurve} of~$\curveof(\omega)$ in~$\curveof(F)$ the part of~$\curveof(\omega)$ which lies strictly between the two angles of~$\dissection$ (or of~$\dissection\dual$) where~$\curveof(\omega)$ is maximal (see Remark~\ref{rem:countercurrentOrderOnSurface}).

### 2018-07-12 draft/accordionComplexSurfaces.tex
relecture section 5

--- 2018-07-12 draft/accordionComplexSurfaces.tex
@@
 The boundaries of the surfaces are shaded, and the glue symbols indicate how to identify some edges to get the desired surfaces.
-The first two surfaces are disks, the third is a sphere without boundary, the fourth is a cylinder, and the fifth is a punctured torus.
+The first two surfaces are disks, the third is a sphere, the fourth is a cylinder, and the fifth is a punctured torus.
 The dissection~$\dissection$ is in green while its dual dissection~$\dissection\dual$ is~in~red.}
@@
 When the dissection~$\dissection$ is a classical dissection of a polygon (with no punctures) where each cell has at most one boundary edge, the dual dissection~$\dissection\dual$ is a tree.
-The non-kissing complex in this situation was treated in detail in~\cite{GarverMcConville, MannevillePilaud-accordion}.
+The non-kissing complex in his situation was treated in detail in~\cite{GarverMcConville, MannevillePilaud-accordion}.
 Note that even when the surface~$\surface$ is a disk, we authorize here both~$\dissection$ and~$\dissection\dual$ to have interior faces and punctures.
@@
 As stated in Proposition~\ref{prop:conditionsDualDissections}, a cellular dissection~$\dissection$ with a face containing more than one boundary edge does not admit a dual cellular dissection~$\dissection\dual$.
-This prevents the use of the definitions given in this section.
-Although the accordion complex (resp.~slalom complex) could still be defined as in~\cite{MannevillePilaud-accordion} (resp.~\cite{GarverMcConville}) for the disk, the resulting complexes would be joins of smaller accordion complexes (resp.~slalom complexes) defined in this paper.
+This prevents to use the definitions given in this section.
+Although its accordion complex (resp.~slalom complex) could still be defined as in~\cite{MannevillePilaud-accordion} (resp.~\cite{GarverMcConville}) for the disk, the resulting complexes would be joins of smaller accordion complexes (resp.~slalom complexes) defined in this paper.
 See \cite[Prop.~2.4]{MannevillePilaud-accordion} for a detailed statement in the case of the disk.
@@
 \begin{itemize}
-\item for any locally gentle bound quiver~$\bar Q$, the non-kissing complex~$\NKC$ is isomorphic to the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection\dual_{\bar Q}}]$,% therefore to the accordion complex~$\AC[\dissection_{\bar Q}]$ and to the slalom complex~$\SC[{\dissection_{\bar Q}}\dual]$.
+\item for any locally gentle bound quiver~$\bar Q$, the non-kissing complex~$\NKC$ is isomorphic to the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection\dual_{\bar Q}}]$,% therefore to the accordion complex~$\AC[\dissection_{\bar Q}]$ and to the slalom complex~$\SC[{\dissection\dual_{\bar Q}}]$.
 \item for any pair of dual cellular dissections~$\dissection, \dissection\dual$ of an oriented surface, the non-crossing complex~$\NCC$ is isomorphic to the non-kissing complex~$\NKC[\bar Q_{\dissection, \dissection\dual}]$.
@@
 
-\begin{definition}
+\begin{definition}\label{def:orderForWalks}
 For any arrow~$\alpha \in Q\blossom_1$ and any two distinct non-kissing walks~$\mu_\star, \nu_\star$ marked at an occurrence of~$\alpha^\pm$,
@@
 \end{definition}
+
+\begin{remark}
+ We note that, since the walks~$\mu$ and~$\nu$ are non-kissing, if~$\mu_\star$ leaves~$\sigma$ on both sides, then is enters and exits~$\sigma$ in the same direction, so that Definition~\ref{def:orderForWalks} is coherent.
+\end{remark}
 
@@
 
+\begin{notation}
+\label{notation:Falpha}
  For any face~$F$ of~$\NKC$ and any arrow~$\alpha\in Q_1\blossom$, we denote by~$F_\alpha$ the set of walks of~$F$ marked at an occurence of~$\alpha^\pm$.
+\end{notation}
 
@@
  We provide two proofs of the lemma.
-One is combinatorial and applies to~$\NKC$, and the other is geometric and applies to~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$, using the isomorphism of Theorem \ref{thm:complexesCoincide} and Remark \ref{rem:countercurrentOrderOnSurface}.
+One is combinatorial and applies to~$\NKC$, and the other is geometric and applies to~$\NCC[\dissection_{\bar Q}, {\dissection\dual_{\bar Q}}]$, using the isomorphism of Theorem \ref{thm:complexesCoincide} and Remark \ref{rem:countercurrentOrderOnSurface}.
 
@@
  \para{Geometric proof}
- View~$F$ as a face of the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$.
+ View~$F$ as a face of the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection\dual_{\bar Q}}]$.
  The arrow~$\alpha$ then corresponds to an angle in~$\dissection$ at a vertex~$v$.
@@
 
-\begin{lemma}
-\label{lem:facetsAreFinite}
-Any face of~$\NKC$ and~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$ is finite, thus contained in a finite maximal face.
-\end{lemma}
-
-Since Theorem \ref{thm:complexesCoincide} ensures that~$\NKC$ and~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$ coincide, we only prove the statement for the non-kissing complex.
+\begin{proposition}
+\label{prop:facetsAreFinite}
+Any face of~$\NKC$ and~$\NCC[\dissection_{\bar Q}, {\dissection\dual_{\bar Q}}]$ is finite, thus contained in a finite maximal face.
+\end{proposition}
+
+Even though Theorem \ref{thm:complexesCoincide} ensures that~$\NKC$ and~$\NCC[\dissection_{\bar Q}, {\dissection\dual_{\bar Q}}]$ coincide, we provide two proofs.
+One is combinatorial and applies to~$\NKC$, and the other is geometric and applies to~$\NCC[\dissection_{\bar Q}, {\dissection\dual_{\bar Q}}]$.
 The proof requires the following intermediate results.
@@
 \begin{proof}
-We provide two proofs of the lemma.
-One is combinatorial and applies to~$\NKC$, and the other is geometric and applies to~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$.
 
@@
 Let~$c=\alpha_1\cdots\alpha_r$ be a non-trivial oriented cycle in some walk~$\omega$, with~$c, c^2\notin I$.
-Assume that~$\omega$ is not of form~$\sigma c^{\pm\infty}$.
+Assume that~$\omega$ is not of the form~$\sigma c^{\pm\infty}$.
 Then, up to cyclic reordering of the arrows in~$c$, it contains a substring of the form~$\beta^\pm c^l \alpha_1\cdots\alpha_j\gamma^\pm$, for some arrows~$\beta,\gamma$ not in~$c$, some~$l\geq 1$, and some~$j<r$.
@@
 \begin{proof}
- We provide two proofs of the lemma.
- One is combinatorial and applies to~$\NKC$, and the other is geometric and applies to~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$.
 
@@
  \para{Geometric proof}
- Let~$F$ be a face of the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$.
+ Let~$F$ be a face of the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection\dual_{\bar Q}}]$.
  Its elements are pairwise compatible~$\dissection$-accordions on the surface~$\surface_{\bar Q}$.
@@
 
-\begin{proof}[Proof of Lemma~\ref{lem:facetsAreFinite}]
- If~$\NKC$ admits an infinite face, then all subsets of this face are also faces, so~$\NKC$ admits faces of arbitrary finite cardinality.
+\begin{proof}[Proof of Lemma~\ref{prop:facetsAreFinite}]
+ If~$\NKC$, respectively~$\NCC$, admits an infinite face, then all subsets of this face are also faces, so~$\NKC$, respectively~$\NCC$, admits faces of arbitrary finite cardinality.
  This contradicts Lemma \ref{lemm:facesAreBounded}.
@@
 \label{prop:purity}
-The reduced non-kissing complex~$\RNKC$ and the reduced non-crossing complex~$\RNCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$ are pure of dimension~$|Q_0|$.
-The non-kissing complex~$\NKC$ and the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$ are pure of dimension~$3|Q_0| - |Q_1| + p$ where~$p$ is the number of primitive oriented cycles in~$\bar Q$ or equivalently the number of punctures in~$V_Q$ in~$\surface_{\bar Q}$.
+The reduced non-kissing complex~$\RNKC$ and the reduced non-crossing complex~$\RNCC[\dissection_{\bar Q}, {\dissection\dual_{\bar Q}}]$ are pure of dimension~$|Q_0|$.
+The non-kissing complex~$\NKC$ and the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection\dual_{\bar Q}}]$ are pure of dimension~$3|Q_0| - |Q_1| + s_\infty$ where~$s_\infty$ is the number of primitive oriented cycles in~$\bar Q$ or equivalently the number of punctures in~$V_Q$ in~$\surface_{\bar Q}$.
 \end{proposition}
@@
 Note that Proposition \ref{prop:purity} was proved for~$\NKC$ in \cite[Cor.~2.27]{PaluPilaudPlamondon} in the case where~$kQ/I$ is finite-dimensional.
-Note also that, by Theorem \ref{thm:complexesCoincide} above,~$\NKC$ and~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$ coincide, so it suffices to prove the Proposition for one of them.
+Note also that, by Theorem \ref{thm:complexesCoincide} above,~$\NKC$ and~$\NCC[\dissection_{\bar Q}, {\dissection\dual_{\bar Q}}]$ coincide, so it suffices to prove the Proposition for one of them.
 The following definition from \cite[Def.~2.23]{PaluPilaudPlamondon} extends to the setting of locally gentle algebras.
@@
 Let~$\alpha \in Q\blossom_1$ be an arrow and let~$F$ be a face of~$\NKC$ containing the straight walk passing through~$\alpha$.
-Consider the marked walk~$\omega_\star \eqdef \max_{\prec_\alpha} F_\alpha$ (which exists by Lemmas \ref{lemm:facesHaveMaximalElement} and~\ref{lem:facetsAreFinite}),
+Consider the marked walk~$\omega_\star \eqdef \max_{\prec_\alpha} F_\alpha$ (which exists by Lemmas \ref{lemm:facesHaveMaximalElement} and~\ref{prop:facetsAreFinite}),
 and let~$\omega$ be the walk obtained by forgetting the marked arrow in~$\omega_\star$. 
@@
 \label{lem:walksThroughcycles}
-For any oriented cycle~$c$ in~$Q$ with~$c, c^2\notin I$, any maximal non-kissing face contains a walk of the form~$\sigma c^{\varepsilon\infty}$, for some~$\varepsilon\in\{\pm1\}$ and some substring~$\sigma$ distinct from~$^{\varepsilon\infty}c$.
+For any oriented cycle~$c$ in~$Q$ with~$c, c^2\notin I$, any maximal non-kissing face contains a walk of the form~$\sigma c^{\varepsilon\infty}$, for some~$\varepsilon\in\{\pm1\}$ and some substring~$\sigma$ distinct from~$^{\varepsilon\infty}c$ (i.e.
+the walk is not an infinite straight walk).
 \end{lemma}
@@
 We provide two proofs of the lemma.
-One is combinatorial and applies to~$\NKC$, and the other is geometric and applies to~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$.
+One is combinatorial and applies to~$\NKC$, and the other is geometric and applies to~$\NCC[\dissection_{\bar Q}, {\dissection\dual_{\bar Q}}]$.
 
@@
 If~$\nu$ is contained in~$F$, then we have found a walk of the desired form (remember that walks are considered as undirected).
-Otherwise, there exists a walk~$\lambda$ of~$F$ preventing~$\nu$ to belong to~$F$.
+Otherwise, there exists a walk~$\lambda$ of~$F$ preventing~$\nu$ from belonging to~$F$.
 Let~$\sigma$ be a common substring of~$\nu$ and~$\lambda$ where they kiss.
@@
 We claim that~$\omega$ belongs to~$F$.
-Otherwise, there exists a walk~$\rho$ preventing~$\omega$ to belong to~$F$.
+Otherwise, there exists a walk~$\rho$ preventing~$\omega$ from belonging to~$F$.
 Let~$\tau$ be a common substring of~$\omega$ and~$\rho$ where they kiss.
@@
 The proof follows that of~\cite[Cor.~2.27]{PaluPilaudPlamondon}.
-Let~$b$ denote the number of bending walks, $s$ the number of finite straight walks, and $p$ the number of infinite straight walks in a non-kissing facet~$F$ of~$\NKC$.
+Let~$b$ denote the number of bending walks, $s$ the number of finite straight walks, and $s_\infty$ the number of infinite straight walks in a non-kissing facet~$F$ of~$\NKC$.
 Since each finite straight walk uses two blossom arrows, we have~$s = 2|Q_0|-|Q_1|$ (see Remark~\ref{rem:sizeBlossomingQuiver}).
@@
 \[
-2 * b + 1 * s + 0 * c= |Q_1\blossom| = 4|Q_0|-|Q_1|
+2 * b + 1 * s + 0 * s_\infty= |Q_1\blossom| = 4|Q_0|-|Q_1|
 \]
-from which we derive that~$b = |Q_0|$ and~$b+s+c = 3|Q_0|-|Q_1|+p$.
+from which we derive that~$b = |Q_0|$ and~$b+s+c = 3|Q_0|-|Q_1|+s_\infty$.
 \end{proof}
@@
 A simplicial complex is \defn{thin} if each of its codimension~$1$ faces is contained in exaclty two facets.
-We state the following results, which generalize \cite[Prop.~2.31 \& Cor.~2.33]{PaluPilaudPlamondon}, whose proofs apply withouth change.
+We state the following results, which generalize \cite[Prop.~2.31 \& Cor.~2.33]{PaluPilaudPlamondon}, whose proofs apply without change.
 
@@
 \begin{itemize}
-\item Exactly one of the curves obtained by changing the~$\SSS$ to a~$\ZZZ$ and conversely by moving the endpoints of~$\gamma$ along the top and bottom curves is a~$\dissection$-accordion.
+\item Exactly one of the curves obtained by changing the~$\SSS$ to a~$\ZZZ$ (and conversely) by moving the endpoints of~$\gamma$ along the top and bottom curves is a~$\dissection$-accordion.
 \item This~$\dissection$-accordion yields the flip or mutation of~$F$ at~$\gamma$.
-\item If the flip is increasing, then the~$\SSS$ is turned into a~$\ZZZ$.  If the flip is decreasing, then the~$\ZZZ$ is turned in to an~$\SSS$.
+\item If the flip is increasing, then the~$\ZZZ$ is turned into a~$\SSS$.  If the flip is decreasing, then the~$\SSS$ is turned in to a~$\ZZZ$.
 \end{itemize}
@@
 We see that the only two~$\dissection$-accordions found between~$\mu$ and~$\curveof(\omega)$ are~$\mu$ and~$\curveof(\omega)$ themselves.  The same holds by replacing~$\mu$ with~$\nu$.
-Thus~$\mu, \nu$ and~$\curveof(\omega)$ lie in an~$\SSS$ or a~$\ZZZ$.
-
-We see that~$\curveof(\omega')$ is then obtained as claimed.  Positivity or negativity of the flip translates from the picture in a similar way. 
+Thus~$\mu, \nu$ and~$\curveof(\omega)$ lie in a~$\SSS$ or a~$\ZZZ$.
+
+We see that~$\curveof(\omega')$ is then obtained as claimed. The direction of the flip translates from the picture in a similar way.
 \end{proof}
@@
 Our objective is now to interpret the three families of vectors of Section~\ref{subsec:gcdVectorsWalks} in terms of accordions and slaloms on the surface.
-According to Remark~\ref{rem:propertiesSurface}\,(\ref{item:arcs}), each vertex~$p$ of~$Q$ corresponds to an edge~$\edgeof(p)$ in the dissection~$\dissection_{\bar Q}$ and  to an edge~$\dualedgeof(p) = \edgeof(p)\dual$ in the dual dissection~${\dissection_{\bar Q}}\dual$.
+According to Remark~\ref{rem:propertiesSurface}\,(\ref{item:arcs}), each vertex~$p$ of~$Q$ corresponds to an edge~$\edgeof(p)$ in the dissection~$\dissection_{\bar Q}$ and  to an edge~$\dualedgeof(p) = \edgeof(p)\dual$ in the dual dissection~${\dissection\dual_{\bar Q}}$.
 Recall moreover from Lemma~\ref{lemm:curveOfAWalkIsAccordion} and Proposition~\ref{prop:accordionsSlaloms} that each non-kissing walk~$\omega$ in~$\bar Q$ corresponds to a curve~$\curveof(\omega)$ that is both a $\dissection$-accordion and a $\dissection\dual$-slalom.

### 2018-07-12 draft/accordionComplexSurfaces.tex

@@
 \item for any pair of dual cellular dissections~$\dissection, \dissection\dual$ of an oriented surface, the non-crossing complex~$\NCC$ is isomorphic to the non-kissing complex~$\NKC[\bar Q_{\dissection, \dissection\dual}]$.
+
 \end{itemize}

### 2018-07-12 firstPaper/corrections/replyToReferee.txt
Reply to referee on first paper.

We thank the referee for their helpful comments.  We have tried to implement them
all.  Below are our replies to each comment.

* In the introduction, and in the introductory paragraphs of several sections
  the authors are sometimes quite abrupt and discuss notions that have not been
  introduced yet. For example examples this happens in
  - page 1, line 2: non-kissing paths
  - page 43: $\mathcal{L}_{nk}(\overline{Q})$
  Could this notions be introduces, at least vaguely, before using them?

  Reply:

* page 1 paragraph 1: ``The interest in'' rather then ``The interest for''

  Reply:

* page 2 par 3: ``description of flips''

  Reply:

* par: 3 ``remarquable'' is French

  Reply:

* page 3: the footnotes refer to the table on next page; they are quite
  confusing here.

  Reply:

* page 6, last line: while the meaning of $I^{rev}$ is clear this has not been
  introduced formally.

  Reply:

* Figure 1: all other figures in the paper are not separated into sub figures by
  lines as this one is

  Reply:

* Def 1.12: say ``The algebra ... associated to a gentle bound quiver is called''
  or something similar.

  Reply:

* page 15 above 1.1.7: all of a sudden there is a shorthand for band modules
  that was not introduced

  Reply:

* page 15 bottom: this formula looks quite ugly, can you remove the text from
  it by defining the two sets first? Even better can you replace the formula 
  with a sentence?

  Reply:

* page 17: the name ``dance'' suggests a symmetric notion but it is not. If
  there in no better name available it should at least be stated clearly that
  this is not a symmetric notion.

  Reply:

* page 24 intro: ``the operation of flip''

  Reply:

* Example 2.2 and many more occurrences: Through the paper there is a recurring
  example and the authors decided to name it by $Q_{exm}$ et similia.
  This makes it look like it is some sort of notation when it is not. I would
  suggest to remove this convention and to just refer to it as the recurring
  example or the example in figure 15.

  Reply:

* Just below: ``See Figure 15'' is not needed here

  Reply:

* bottom of page 24 what is a non-kissing cycle? Do you mean not self-kissing?

  Reply:

* Figure 17: $Q_{pa}$ as above why is an example given a notation-like name?

  Reply:

* Figure 18: crossing walks have not been introduced

  Reply:

* remark 2.20: the first bullet point ``should'' should the ``then'' you are
  stating a fact not an hope

  Reply:

* proof of 2.21: ``follow'' is not really clear here

  Reply:

* def 2.36: is any flip either increasing or decreasing?

  Reply:

* def 3.4: do you mean ``any strict subset''?

  Reply:

* def 3.16 and others: $\mathcal{S}$ and $S$ are not easily distinguishable

  Reply:

* Proof of theorem 3.20: the numberings do not correspond to each other

  Reply:

* page 49 previous to last paragraph: ``ordered by:'' should be ``ordered by''

  Reply:

* Example 3.36: Figure 34 does not illustrate $\omega$

  Reply:

* Example 3.44: It appears to me that the map, which is not explicit, is on the
  quotient of $Bic$

  Reply:

* pages 59,60,64,65,68,73 and probably more: the text goes outside the margin

  Reply:

* remark 3.72: do you mean ``Figure 36 (bottom)''?

  Reply:

A note about notation. This article uses a quite creative notation set. For
example the blossoming quiver has a little flower as exponent and the operation
of blinding is represented by two half circle to suggest blinkers. I am not sure
I am happy about these choices but I do not have better suggestions to offer.

  Reply:

### 2018-07-12 draft/accordionComplexSurfaces.tex
Typoes Section 5.
relecture section 6 debut

@@
 	\centerline{\includegraphics[scale=1]{flip3}}
-	\caption{A flip turns a~$\ZZZ$ (formed by~$\mu$, $\omega$ and~$\nu$) to a~$\SSS$ (formed by~$\mu$, $\omega'$ and~$\nu$). The two curves~$\omega$ and~$\omega'$ are crossing.}
+	\caption{An increasing flip turns a~$\ZZZ$ (formed by~$\mu$, $\omega$ and~$\nu$) to a~$\SSS$ (formed by~$\mu$, $\omega'$ and~$\nu$). The two curves~$\omega$ and~$\omega'$ are crossing.}
 	\label{fig:flip3}
@@
 In contrast to the $\b{d}$-vectors, the $\b{g}$- and $\b{c}$-vectors were already considered in the non-kissing complex of a gentle quiver~\cite[Sect.~4.2]{PaluPilaudPlamondon}, and their definition immediately generalizes to the case of locally gentle algebras.
-All these vectors have algebraic motivations that we prefer to omit in the present paper to remain focus on the two-sided combinatorics of the non-kissing and non-crossing models.
-Our objective is just to provide interpretations of these vectors in terms of the surface~$\surface_{\bar Q}$.
+All these vectors have algebraic motivations that we prefer to omit in the present paper to remain focused on the two-sided combinatorics of the non-kissing and non-crossing models.
+Our objective is to provide interpretations of these vectors in terms of the surface~$\surface_{\bar Q}$.
 % We show that our geometric model using accordions is well-adapted to computing~$\b{c}$-vectors, while slaloms can naturally be interpreted as~$\b{g}$-vectors.
@@
 \begin{definition}
-For a multiset~$V \eqdef \{v_1, \dots, v_m\}$ of vertices of~$Q_0$, we denote by~$\multiplicityVector_V \in \R^{Q_0}$ the \defn{multiplicity vector} of~$V$ defined~by
+Let~$V \eqdef \{v_1, \dots, v_m\}$ be a multiset of vertices of~$Q_0$. We denote by~$\multiplicityVector_V \in \R^{Q_0}$ the \defn{multiplicity vector} of~$V$, defined~by:
 \[
@@
 \label{def:gVectorsWalks}
-For a walk~$\omega$ of~$\bar Q$, we denote by~$\peaks{\omega}$ (resp.~by~$\deeps{\omega}$) the multiset of vertices of~$Q_0$ corresponding to the peaks (resp.~deeps) of~$\omega$.
-The \defn{$\b{g}$-vector} of a walk~$\omega$ is the vector~${\gvector{\omega} \in \R^{Q_0}}$ defined by
+For any walk~$\omega$ of~$\bar Q$, we let~$\peaks{\omega}$ (resp.~by~$\deeps{\omega}$) be the multiset of vertices of~$Q_0$ corresponding to the peaks (resp.~deeps) of~$\omega$.
+The \defn{$\b{g}$-vector} of the walk~$\omega$ is the vector~${\gvector{\omega} \in \R^{Q_0}}$ defined as follows:
 \[
@@
 For a set~$\Omega$ of walks, we let~$\gvectors{\Omega} \eqdef \set{\gvector{\omega}}{\omega \in \Omega}$.
-Observe that~$\gvector{\omega} = 0$ for a straight walk~$\omega$, and that, since any infinite walk~$\omega$ is eventually cyclic, the coordinates of~$\gvector{\omega}$ are finite.
+Observe that, if~$\omega$ is a straight walk, then~$\gvector{\omega} = 0$, and that, since any infinite walk~$\omega$ is eventually cyclic, the coordinates of~$\gvector{\omega}$ are finite.
 \end{definition}
@@
 \label{def:cVectorsWalks}
-Let~$\omega$ be a walk in a non-kissing facet~$F \in \RNKC$.
+Let~$F \in \RNKC$ be a non-kissing facet and $\omega$ be a walk in~$F$.
 Define
@@
 \begin{cases}
-\phantom{-}1 & \text{if~$\distinguishedString{\omega}{F}$ is a top substring of~$\omega$ (\ie the arrows~$\distinguishedArrows{\omega}{F}$ point outside),} \\
--1 & \text{if~$\distinguishedString{\omega}{F}$ is a bottom substring of~$\omega$ (\ie if the arrows~$\distinguishedArrows{\omega}{F}$ point inside).}
+\phantom{-}1 & \text{if~$\distinguishedString{\omega}{F}$ is a top substring of~$\omega$ (\ie if the distinguished arrows point outside),} \\
+-1 & \text{if~$\distinguishedString{\omega}{F}$ is a bottom substring of~$\omega$ (\ie if the distinguished arrows point inside).}
 \end{cases}
@@
 - \b{e}_v & \text{if $\omega$ is the deep walk~$v_\deep$ with a unique deep at~$v$,} \\
-\displaystyle \sum_{v \in Q_0} \kn(v_\deep, \omega) \, \b{e}_v & \text{otherwise.}
+\displaystyle \sum_{v \in Q_0} \kn(\omega, v_\deep) \, \b{e}_v & \text{otherwise.}
 \end{cases}

### 2018-07-12 firstPaper/corrections/replyToReferee.txt
One reply.
reply to referee (b)

@@
 We thank the referee for their helpful comments.  We have tried to implement them
-all.  Below are our replies to each comment.
+all.  Below are our replies to each comment.  We have also made a few additional
+changes, which we first list.
+
+(a) In Notation 1.50, the equalities were wrong and have been corrected.
+
+(b) We have added some details (in a new Proposition 2.24) explaining why the non-kissing facets are finite.
+In doing so, we had to slightly reorganise Subsection 2.2.2 (new Lemma 2.23 was previously part of the proof of Proposition (renumbered) 2.28)
 

### 2018-07-12 draft/accordionComplexSurfaces.tex
relecture section 6 fin

@@
 \label{def:kissingNumber}
-For two walks~$\omega$ and~$\omega'$ of~$\bar Q$, denote by~$\kn(\omega,\omega')$ the number of kisses of~$\omega$ to~$\omega'$.
+For two walks~$\omega$ and~$\omega'$ of~$\bar Q$, denote by~$\kn(\omega,\omega')$ the number of times that~$\omega$ kisses $\omega'$.
 Note that kisses are counted with multiplicities if~$\omega$ or~$\omega'$ pass twice through the same substring.
@@
 \begin{blockarray}{ccc}
-	{\color{blue} \bullet} & {\color{purple} \bullet} & \\[-.1cm]
+	{\color{blue} \bullet} & {\color{violet} \bullet} & \\[-.1cm]
 	\begin{block}{[cc]c}
@@
 \label{prop:gVectorsSurface}
-For a walk~$\omega$ of~$\bar Q$ and a vertex~$p \in Q_0$, the $p$th entry of the $\b{g}$-vector~$\gvector{\omega}$ is given~by
+For a walk~$\omega$ of~$\bar Q$ and a vertex~$p \in Q_0$, the $p$-th entry of the $\b{g}$-vector~$\gvector{\omega}$ is given~by:
 \begin{enumerate}[(i)]
@@
 Here, the crossing is positive (resp.~negative) if the two angles of~$\dissection$ crossed by~$\curveof(\alpha)$ just before and after~$\edgeof(p)$ form a~$\SSS$ (resp.~as a~$\ZZZ$).
+We note that some crossings are neither positive nor negative.
 \item The number of times that the $\dissection\dual$-slalom~$\curveof(\omega)$ positively crosses the edge~$\dualedgeof(p)$ of~$\dissection\dual$ minus the number of times it negatively crosses the edge~$\dualedgeof(p)$ of~$\dissection\dual$.
 Here, the crossing is positive when~$\curveof(\omega)$ leaves a face~$u\dual$ to enter a face~$v\dual$ with the vertex~$u$ being to its right (and thus with~$v$ being to its left), and the crossing is negative otherwise.
+We note that, in this case, each crossing is either positive or negative.
 \end{enumerate}
@@
 Call \defn{distinguished subcurve} of~$\curveof(\omega)$ in~$\curveof(F)$ the part of~$\curveof(\omega)$ which lies strictly between the two angles of~$\dissection$ (or of~$\dissection\dual$) where~$\curveof(\omega)$ is maximal (see Remark~\ref{rem:countercurrentOrderOnSurface}).
-For a vertex~$p \in Q_0$, the $p$th entry of the $\b{c}$-vector~$\cvector{\omega}{F}$ is given by
+For a vertex~$v \in Q_0$, the $v$-th entry of the $\b{c}$-vector~$\cvector{\omega}{F}$ is given by
 \begin{enumerate}[(i)]
@@
 Denote by~$X_\deep$ the deep facet of the non-crossing complex as described in Example~\ref{exm:peakDeepFacets}.
-For a walk~$\omega$ of~$\bar Q$ and a vertex~$p \in Q_0$, the $p$th entry of the $\b{d}$-vector~$\dvector{\omega}$ is the number of crossings of the curve~$\gamma(\omega)$ with the edge of~$X_\deep$ corresponding to~$p$.
+For a walk~$\omega$ of~$\bar Q$ and a vertex~$v \in Q_0$, the $v$-th entry of the $\b{d}$-vector~$\dvector{\omega}$ is the number of crossings of the curve~$\gamma(\omega)$ with the edge of~$X_\deep$ corresponding to~$v$.
 \end{proposition}
@@
 \begin{proof}
-For the $\b{g}$-vectors, observe that two walks~$\omega$ and~$\omega'$ whose $\b{g}$-vectors~$\gvector{\omega}$ and~$\gvector{\omega}$ have opposite signs on their~$v$th coordinate automatically kiss at~$v$.
+For the $\b{g}$-vectors, observe that two walks~$\omega$ and~$\omega'$ whose $\b{g}$-vectors~$\gvector{\omega}$ and~$\gvector{\omega}$ have opposite signs on their~$v$-th coordinate automatically kiss at~$v$.
 For $\b{c}$- and $\b{d}$-vectors, the statement is immediate from the definition.

### 2018-07-12 draft/accordionComplexSurfaces.tex
placement Q

@@
 \usepackage[T1]{fontenc}
-\usepackage{enumerate, amsmath, amsfonts, amssymb, amsthm, mathrsfs, wasysym, graphics, graphicx, xcolor, url, hyperref, hypcap, xargs, multicol, pdflscape, multirow, hvfloat, array, ae, aecompl, pifont, mathtools, a4wide, float, blkarray}
+\usepackage{enumerate, amsmath, amsfonts, amssymb, amsthm, mathrsfs, wasysym, graphics, graphicx, xcolor, url, hyperref, hypcap, xargs, multicol, pdflscape, multirow, hvfloat, array, ae, aecompl, pifont, mathtools, a4wide, float, blkarray, chemmacros}
 \usepackage{marginnote}
@@
 \begin{definition}
- An oriented cycle~$c$ in~$Q$ such that~$c$ and~$c^2$ do not belong to the ideal of relations~$I$ is called \defn{primitive} if it cannot be written as an $n$th power ($n>1$) of a cycle.
+ An oriented cycle~$c$ in~$Q$ such that~$c$ and~$c^2$ do not belong to the ideal of relations~$I$ is called \defn{primitive} if it cannot be written as an $n$-th power ($n>1$) of a cycle.
 \end{definition}
@@
 Namely, any pair of dual cellular dissections~$(\dissection, \dissection\dual)$ defines a locally gentle bound quiver~$\bar Q_{\dissection}$ such that the non-crossing complex~$\NCC$ is isomorphic to the non-kissing complex~$\NKC[\bar Q_{\dissection}]$.
-Conversely, any locally gentle bound quiver~$\bar Q$ gives rise to a surface~$\surface_{\bar Q}$ equipped with a pair of dual cellular dissections~$\dissection_{\bar Q}$ and~${\dissection\dual_{\bar Q}}$ such that the non-kissing complex~$\NKC$ is isomorphic to the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection\dual_{\bar Q}}]$.
+Conversely, any locally gentle bound quiver~$\bar Q$ gives rise to a surface~$\surface_{\bar Q}$ equipped with a pair of dual cellular dissections~$\dissection_{\bar Q}$ and~${\dissection\dual}\!\!_{\bar Q}$ such that the non-kissing complex~$\NKC$ is isomorphic to the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection\dual_{\bar Q}}]$.
 In fact, we show that the accordion, slalom, and non-kissing complexes can all be pictured in a unique way on the surface.
@@
 Call \defn{distinguished subcurve} of~$\curveof(\omega)$ in~$\curveof(F)$ the part of~$\curveof(\omega)$ which lies strictly between the two angles of~$\dissection$ (or of~$\dissection\dual$) where~$\curveof(\omega)$ is maximal (see Remark~\ref{rem:countercurrentOrderOnSurface}).
-For a vertex~$v \in Q_0$, the $v$-th entry of the $\b{c}$-vector~$\cvector{\omega}{F}$ is given by
+For a vertex~$v \in Q_0$, the $v$-th entry of the $\b{c}$-vector~$\cvector{\omega}{F}$ is given by:
 \begin{enumerate}[(i)]
@@
 \begin{itemize}
-\item for~$v \in Q_0$, the~$v$th coordinates of all $\b{g}$-vectors~$\gvector{\omega}$ for~$\omega \in F$ have the same sign,
+\item for~$v \in Q_0$, the~$v$-th coordinates of all $\b{g}$-vectors~$\gvector{\omega}$ for~$\omega \in F$ have the same sign,
 \item for any~$\omega \in F$, all coordinates of the $\b{c}$-vector~$\cvector{\omega}{F}$ have the same sign,

### 2018-07-12 draft/accordionComplexSurfaces.tex
accordions on the universal cover

@@
 \end{itemize}
-By convention, we also consider that the punctures of~$V\dual$ are $\dissection$-accordions.
+By convention, we also consider that the punctures of~$V\dual$ are $\dissection$-accordions; 
+if we were working on the universal cover of the surface, the~$\dissection$-accordion associated to a puncture would be the infinite line crossing all (infinitely many) arcs attached to the puncture.
 \end{definition}

### 2018-07-12 draft/accordionComplexSurfaces.tex
first corrections

--- 2018-07-12 draft/accordionComplexSurfaces.tex
@@
 A locally gentle bound quiver~$\bar Q$ is \defn{complete} if any vertex~$v \in Q_0$ is incident to either one ($v$ is a leaf) or four arrows ($v$ is an internal vertex).
-The \defn{pruned subquiver} of a quiver $\bar Q$ is the locally gentle quiver obtained by deleting all leaves of~$\bar Q$ (degree one vertices) and their incident arrows.
+The \defn{pruned subquiver} of a quiver~$\bar Q$ is the locally gentle quiver obtained by deleting all leaves of~$\bar Q$ (degree one vertices) and their incident arrows.
 The \defn{blossoming quiver} of a locally gentle bound quiver~$\bar Q$ is the complete locally gentle bound quiver~$\bar Q\blossom$ whose pruned subquiver is~$\bar Q$.
@@
 
+In other words, $\bar Q\blossom$ is obtained from~$\bar Q$ by adding blossom arrow and blossom vertices at each incomplete vertex of~$\bar Q$ and by completing~$I$ accordingly.
 Examples are represented on \fref{fig:quivers}.
@@
 where
-	\begin{itemize}
+	\begin{enumerate}[(i)]
 	\item $\alpha_i \in Q_1$ and~$\varepsilon_i \in \{-1,1\}$ for all~$i \in [\ell]$,
@@
 	\item $\rho$ is reduced, in the sense that no factor~$\alpha\alpha^{-1}$ or~$\alpha^{-1}\alpha$ appears in~$\rho$, for~$\alpha \in Q_1$.
-	\end{itemize}
+	\end{enumerate}
 The integer~$\ell$ is called the \defn{length} of the string~$\rho$.
@@
 \begin{definition}
- An oriented cycle~$c$ in~$Q$ such that~$c$ and~$c^2$ do not belong to the ideal of relations~$I$ is called \defn{primitive} if it cannot be written as an $n$th power ($n>1$) of a cycle.
+ An oriented cycle~$c$ in~$Q$ such that~$c, c^2 \notin I$ is called \defn{primitive} if it cannot be written as an $n$-th power ($n>1$) of a cycle.
 \end{definition}
@@
 \begin{notation}
-If~$c$ is an oriented cycle in~$Q$ such that~$c$ and~$c^2$ do not belong to the ideal of relations~$I$, we write:
+If~$c$ is an oriented cycle in~$Q$ such that~$c, c^2 \notin I$, we write:
 \begin{itemize}
@@
 \begin{notation}
-To avoid distinguishing between finite, infinite and bi-infinite words, we denote strings as products~$\rho = \prod_{i < \ell < j} \alpha_\ell$ where~$i < j \in \Z \cup \{\pm \infty\}$ and~$\alpha_\ell \in Q_0$.
+To avoid distinguishing between finite, infinite and bi-infinite words, we denote strings as products~$\rho = \prod_{i < \ell < j} \alpha_\ell$ where~$i < j \in \Z \cup \{\pm \infty\}$ and~$\alpha_\ell \in Q_0$ for all~$i < \ell < j$.
 \end{notation}
@@
 For~$V \subset \surface$,
-\begin{itemize}
+\begin{enumerate}[(i)]
 \item a \defn{$V$-arc} on~$\bar\surface$ is a curve on~$\surface$ connecting two points of~$V$ and whose interior is disjoint from~$M$ and the boundary of~$\surface$.
 \item a \defn{$V$-curve} on~$\bar\surface$ is a curve on~$\surface$ which at each end either reaches a point of~$V$ or infinitely circles around and finally reaches a puncture of~$M$, and whose interior is disjoint from~$M$ and the boundary of~$\surface$.
-\end{itemize}
+\end{enumerate}
 As usual, curves and arcs are considered up to homotopy relative to their endpoints in~$\surface \ssm M$, and curves homotopic to a boundary are not allowed.
@@
 	\caption{Some pairs~$(\dissection, \dissection\dual)$ of dual cellular dissections on different surfaces.
+The dissection~$\dissection$ is in green while its dual dissection~$\dissection\dual$ is~in~red.
 The boundaries of the surfaces are shaded, and the glue symbols indicate how to identify some edges to get the desired surfaces.
-The first two surfaces are disks, the third is a sphere without boundary, the fourth is a cylinder, and the fifth is a punctured torus.
-The dissection~$\dissection$ is in green while its dual dissection~$\dissection\dual$ is~in~red.}
+The first two surfaces are disks, the third is a sphere without boundary, the fourth is a cylinder, and the fifth is a torus with one boundary component.}
 	\label{fig:dissections}
@@
 \begin{itemize}
-\item if a face~$f$ has no edge on the boundary of~$\surface$, its dual vertex~$f\dual$ lies in the interior~of~$f$,
+\item if a face~$f$ has no edge on the boundary of~$\surface$, its dual vertex~$f\dual$ lies in the interior~of~$f$ and is a puncture of~$\bar\surface$,
 \item if a face~$f$ has an edge on the boundary of~$\surface$, then it has exactly one such edge and its dual vertex~$f\dual$ lies on this edge.
@@
 Namely, any pair of dual cellular dissections~$(\dissection, \dissection\dual)$ defines a locally gentle bound quiver~$\bar Q_{\dissection}$ such that the non-crossing complex~$\NCC$ is isomorphic to the non-kissing complex~$\NKC[\bar Q_{\dissection}]$.
-Conversely, any locally gentle bound quiver~$\bar Q$ gives rise to a surface~$\surface_{\bar Q}$ equipped with a pair of dual cellular dissections~$\dissection_{\bar Q}$ and~${\dissection\dual_{\bar Q}}$ such that the non-kissing complex~$\NKC$ is isomorphic to the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection\dual_{\bar Q}}]$.
+Conversely, any locally gentle bound quiver~$\bar Q$ gives rise to a surface~$\surface_{\bar Q}$ equipped with a pair of dual cellular dissections~$\dissection_{\bar Q}$ and~${{\dissection\dual}\!\!_{\bar Q}}$ such that the non-kissing complex~$\NKC$ is isomorphic to the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection\dual\!\!_{\bar Q}}]$.
 In fact, we show that the accordion, slalom, and non-kissing complexes can all be pictured in a unique way on the surface.
@@
 
-The advantage of Definition~\ref{def:surfaceQuiver} is that it automatically endows~$\surface_{\bar Q}$ with two disjoint sets~$V_{\bar Q}$ and~${V\dual_{\bar Q}}$ of marked points and two dual cellular dissections~$\dissection_{\bar Q}$ and~${\dissection\dual_{\bar Q}}$ defined as follows.
+The advantage of Definition~\ref{def:surfaceQuiver} is that it automatically endows~$\surface_{\bar Q}$ with two disjoint sets~$V_{\bar Q}$ and~${V\dual_{\bar Q}}$ of marked points and two dual cellular dissections~$\dissection_{\bar Q}$ and~${\dissection\dual\!\!_{\bar Q}}$ defined as follows.
 
@@
 \end{itemize}
-The set~${V\dual_{\bar Q}}$ and the ${V\dual_{\bar Q}}$-dissection~${\dissection\dual_{\bar Q}}$ are defined dually.
+The set~${V\dual_{\bar Q}}$ and the ${V\dual_{\bar Q}}$-dissection~${\dissection\dual\!\!_{\bar Q}}$ are defined dually.
 \end{definition}
@@
 Let~$\bar Q$ be a locally gentle bound quiver.
-Then the dissections~$\dissection_{\bar Q}$ and~$\dissection\dual_{\bar Q}$ are cellular and dual to each other.
+Then the dissections~$\dissection_{\bar Q}$ and~$\dissection\dual\!\!_{\bar Q}$ are cellular and dual to each other.
 \end{proposition}
@@
 \item The dissection~$\dissection_{\bar Q}$ has one $\ell$-cell for each straight walk of length~$\ell$ in~$\bar Q\koszul$.
-\item A similar remark holds dually for~${V\dual_{\bar Q}}$ and~${\dissection\dual_{\bar Q}}$.
+\item A similar remark holds dually for~${V\dual_{\bar Q}}$ and~${\dissection\dual\!\!_{\bar Q}}$.
 \item The number~$p$ of punctures of~$\surface_{\bar Q}$ is the number of infinite straight walks in~$\bar Q$ and in~$\bar Q\koszul$.
@@
 \label{prop:dualityKoszul2}
-For any gentle bound quiver~$\bar Q$ with Koszul dual~$\bar Q\koszul$, the surfaces~$\surface_{\bar Q}$ and~$\surface_{\bar Q\koszul}$ coincide, but~$\dissection_{\bar Q\koszul} = {\dissection\dual_{\bar Q}}$ and~${\dissection\dual_{\bar Q\koszul}} = \dissection_{\bar Q}$.
+For any gentle bound quiver~$\bar Q$ with Koszul dual~$\bar Q\koszul$, the surfaces~$\surface_{\bar Q}$ and~$\surface_{\bar Q\koszul}$ coincide, but~$\dissection_{\bar Q\koszul} = {\dissection\dual\!\!_{\bar Q}}$ and~${\dissection\dual\!\!_{\bar Q\koszul}} = \dissection_{\bar Q}$.
 \end{proposition}
@@
 The construction of the surface given in Definition \ref{def:surfaceQuiver} yields the same surface as the one constructed in \cite{OpperPlamondonSchroll}.
-A notable difference is that in \cite{OpperPlamondonSchroll}, only~$\dissection_{\bar Q}$ is given, and~$\dissection\dual_{\bar Q}$ is deduced (it is called the dual lamination).
+A notable difference is that in \cite{OpperPlamondonSchroll}, only~$\dissection_{\bar Q}$ is given, and~$\dissection\dual\!\!_{\bar Q}$ is deduced (it is called the dual lamination).
 Another minor difference is that the construction in \cite{OpperPlamondonSchroll} is written only for gentle algebras, while here it is generalized to locally gentle algebras.
@@
 \begin{itemize}
-\item for any locally gentle bound quiver~$\bar Q$, the non-kissing complex~$\NKC$ is isomorphic to the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection\dual_{\bar Q}}]$,% therefore to the accordion complex~$\AC[\dissection_{\bar Q}]$ and to the slalom complex~$\SC[{\dissection\dual_{\bar Q}}]$.
+\item for any locally gentle bound quiver~$\bar Q$, the non-kissing complex~$\NKC$ is isomorphic to the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection\dual\!\!_{\bar Q}}]$,% therefore to the accordion complex~$\AC[\dissection_{\bar Q}]$ and to the slalom complex~$\SC[{\dissection\dual\!\!_{\bar Q}}]$.
 \item for any pair of dual cellular dissections~$\dissection, \dissection\dual$ of an oriented surface, the non-crossing complex~$\NCC$ is isomorphic to the non-kissing complex~$\NKC[\bar Q_{\dissection, \dissection\dual}]$.
@@
 \begin{remark}
-Note that our construction of the surface~$\surface_{\bar Q}$ implies that the vertices of~$\bar Q$ are naturally identified with the intersection points of the dual edges~$a \in \dissection_{\bar Q}$ and~$a\dual \in {\dissection\dual_{\bar Q}}$.
+Note that our construction of the surface~$\surface_{\bar Q}$ implies that the vertices of~$\bar Q$ are naturally identified with the intersection points of the dual edges~$a \in \dissection_{\bar Q}$ and~$a\dual \in {\dissection\dual\!\!_{\bar Q}}$.
 If we force all $\dissection$-accordions (or $\dissection\dual$-slaloms) to cross the edges of~$\dissection$ and~$\dissection\dual$ only at these intersection points, then a $\dissection$-accordion (or $\dissection\dual$-slalom) is really seen as a walk on~$\bar Q$.
@@
  We provide two proofs of the lemma.
-One is combinatorial and applies to~$\NKC$, and the other is geometric and applies to~$\NCC[\dissection_{\bar Q}, {\dissection\dual_{\bar Q}}]$, using the isomorphism of Theorem \ref{thm:complexesCoincide} and Remark \ref{rem:countercurrentOrderOnSurface}.
+One is combinatorial and applies to~$\NKC$, and the other is geometric and applies to~$\NCC[\dissection_{\bar Q}, {\dissection\dual\!\!_{\bar Q}}]$, using the isomorphism of Theorem \ref{thm:complexesCoincide} and Remark \ref{rem:countercurrentOrderOnSurface}.
 
@@
  \para{Geometric proof}
- View~$F$ as a face of the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection\dual_{\bar Q}}]$.
+ View~$F$ as a face of the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection\dual\!\!_{\bar Q}}]$.
  The arrow~$\alpha$ then corresponds to an angle in~$\dissection$ at a vertex~$v$.
@@
 \label{prop:facetsAreFinite}
-Any face of~$\NKC$ and~$\NCC[\dissection_{\bar Q}, {\dissection\dual_{\bar Q}}]$ is finite, thus contained in a finite maximal face.
+Any face of~$\NKC$ and~$\NCC[\dissection_{\bar Q}, {\dissection\dual\!\!_{\bar Q}}]$ is finite, thus contained in a finite maximal face.
 \end{proposition}
 
-Even though Theorem \ref{thm:complexesCoincide} ensures that~$\NKC$ and~$\NCC[\dissection_{\bar Q}, {\dissection\dual_{\bar Q}}]$ coincide, we provide two proofs.
-One is combinatorial and applies to~$\NKC$, and the other is geometric and applies to~$\NCC[\dissection_{\bar Q}, {\dissection\dual_{\bar Q}}]$.
+Even though Theorem \ref{thm:complexesCoincide} ensures that~$\NKC$ and~$\NCC[\dissection_{\bar Q}, {\dissection\dual\!\!_{\bar Q}}]$ coincide, we provide two proofs.
+One is combinatorial and applies to~$\NKC$, and the other is geometric and applies to~$\NCC[\dissection_{\bar Q}, {\dissection\dual\!\!_{\bar Q}}]$.
 The proof requires the following intermediate results.
@@
  \para{Geometric proof}
- Let~$F$ be a face of the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection\dual_{\bar Q}}]$.
+ Let~$F$ be a face of the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection\dual\!\!_{\bar Q}}]$.
  Its elements are pairwise compatible~$\dissection$-accordions on the surface~$\surface_{\bar Q}$.
@@
 \label{prop:purity}
-The reduced non-kissing complex~$\RNKC$ and the reduced non-crossing complex~$\RNCC[\dissection_{\bar Q}, {\dissection\dual_{\bar Q}}]$ are pure of dimension~$|Q_0|$.
-The non-kissing complex~$\NKC$ and the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection\dual_{\bar Q}}]$ are pure of dimension~$3|Q_0| - |Q_1| + s_\infty$ where~$s_\infty$ is the number of primitive oriented cycles in~$\bar Q$ or equivalently the number of punctures in~$V_Q$ in~$\surface_{\bar Q}$.
+The reduced non-kissing complex~$\RNKC$ and the reduced non-crossing complex~$\RNCC[\dissection_{\bar Q}, {\dissection\dual\!\!_{\bar Q}}]$ are pure of dimension~$|Q_0|$.
+The non-kissing complex~$\NKC$ and the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection\dual\!\!_{\bar Q}}]$ are pure of dimension~$3|Q_0| - |Q_1| + s_\infty$ where~$s_\infty$ is the number of primitive oriented cycles in~$\bar Q$ or equivalently the number of punctures in~$V_Q$ in~$\surface_{\bar Q}$.
 \end{proposition}
@@
 Note that Proposition \ref{prop:purity} was proved for~$\NKC$ in \cite[Cor.~2.27]{PaluPilaudPlamondon} in the case where~$kQ/I$ is finite-dimensional.
-Note also that, by Theorem \ref{thm:complexesCoincide} above,~$\NKC$ and~$\NCC[\dissection_{\bar Q}, {\dissection\dual_{\bar Q}}]$ coincide, so it suffices to prove the Proposition for one of them.
+Note also that, by Theorem \ref{thm:complexesCoincide} above,~$\NKC$ and~$\NCC[\dissection_{\bar Q}, {\dissection\dual\!\!_{\bar Q}}]$ coincide, so it suffices to prove the Proposition for one of them.
 The following definition from \cite[Def.~2.23]{PaluPilaudPlamondon} extends to the setting of locally gentle algebras.
@@
 We provide two proofs of the lemma.
-One is combinatorial and applies to~$\NKC$, and the other is geometric and applies to~$\NCC[\dissection_{\bar Q}, {\dissection\dual_{\bar Q}}]$.
+One is combinatorial and applies to~$\NKC$, and the other is geometric and applies to~$\NCC[\dissection_{\bar Q}, {\dissection\dual\!\!_{\bar Q}}]$.
 
@@
 Our objective is now to interpret the three families of vectors of Section~\ref{subsec:gcdVectorsWalks} in terms of accordions and slaloms on the surface.
-According to Remark~\ref{rem:propertiesSurface}\,(\ref{item:arcs}), each vertex~$p$ of~$Q$ corresponds to an edge~$\edgeof(p)$ in the dissection~$\dissection_{\bar Q}$ and  to an edge~$\dualedgeof(p) = \edgeof(p)\dual$ in the dual dissection~${\dissection\dual_{\bar Q}}$.
+According to Remark~\ref{rem:propertiesSurface}\,(\ref{item:arcs}), each vertex~$p$ of~$Q$ corresponds to an edge~$\edgeof(p)$ in the dissection~$\dissection_{\bar Q}$ and  to an edge~$\dualedgeof(p) = \edgeof(p)\dual$ in the dual dissection~${\dissection\dual\!\!_{\bar Q}}$.
 Recall moreover from Lemma~\ref{lemm:curveOfAWalkIsAccordion} and Proposition~\ref{prop:accordionsSlaloms} that each non-kissing walk~$\omega$ in~$\bar Q$ corresponds to a curve~$\curveof(\omega)$ that is both a $\dissection$-accordion and a $\dissection\dual$-slalom.

### 2018-07-12 draft/accordionComplexSurfaces.tex
test

--- 2018-07-12 draft/accordionComplexSurfaces.tex
@@
 \usepackage[T1]{fontenc}
-\usepackage{enumerate, amsmath, amsfonts, amssymb, amsthm, mathrsfs, wasysym, graphics, graphicx, xcolor, url, hyperref, hypcap, xargs, multicol, pdflscape, multirow, hvfloat, array, ae, aecompl, pifont, mathtools, a4wide, float, blkarray, chemmacros}
+\usepackage{enumerate, amsmath, amsfonts, amssymb, amsthm, mathrsfs, wasysym, graphics, graphicx, xcolor, url, hyperref, hypcap, xargs, multicol, pdflscape, multirow, hvfloat, array, ae, aecompl, pifont, mathtools, a4wide, float, blkarray}
 \usepackage{marginnote}
@@
 \end{itemize}
-By convention, we also consider that the punctures of~$V\dual$ are $\dissection$-accordions; 
-if we were working on the universal cover of the surface, the~$\dissection$-accordion associated to a puncture would be the infinite line crossing all (infinitely many) arcs attached to the puncture.
+By convention, we also consider that the punctures of~$V\dual$ are $\dissection$-accordions.
 \end{definition}

### 2018-07-12 draft/accordionComplexSurfaces.tex

--- 2018-07-12 draft/accordionComplexSurfaces.tex
@@
 Gentle algebras are a class of finite-dimensional associative algebras over a field defined by generators and relations.
-Their representation theory was first systematically investigated in \cite{ButlerRingel}, and they have been thouroughly studied since.
+Their representation theory was first systematically investigated in~\cite{ButlerRingel}, and they have been thouroughly studied since.
 Locally gentle algebras are obtained by dropping the requirement that gentle algebras be finite-dimensional.
@@
 
-Let~$\bar\surface = (\surface, V \sqcup V\dual)$ be a surface with two disjoint sets~$V$ and~$V\dual$ of marked points, and let~$B$ be the corresponding blossom points.
+Let~$\bar\surface = (\surface, V \sqcup V\dual)$ be a surface with two disjoint sets~$V$ and~$V\dual$ of marked points, and let~$B$ be the corresponding blossom points on the boundary of~$\surface$.
 %
@@
 The following definition generalises the one from \cite{MannevillePilaud-accordion} for the case where~$\bar \surface$ is a disk.
-A very similar definition appears in \cite{BaurSimoes} in a slightly different context under the name ``permissible arc''.
+A very similar definition appears in \cite{BaurSimoes} in a slightly different context under the name ``permissible~arc''.
 
@@
 A \defn{$\dissection$-accordion} is a $B$-curve~$\alpha$ of~$\bar\surface$ such that whenever~$\alpha$ meets a face~$f$~of~$\dissection$,
-\begin{itemize}
+\begin{enumerate}[(i)]
 \item it enters crossing an edge~$a$ of~$f$ and leaves crossing an edge~$b$ of~$f$ (in other words, $\alpha$ is not allowed to circle around~$f\dual$ when~$f\dual$ is a puncture),
@@
 \item $\alpha$, $a$ and~$b$ bound a disk inside~$f$ that does not contain~$f\dual{}$.
-\end{itemize}
-By convention, we also consider that the punctures of~$V\dual$ are $\dissection$-accordions.
+\end{enumerate}
+By convention, we also consider that the punctures of~$V$ are $\dissection$-accordions that are considered external.
+If we were working on the universal cover of the surface, the~$\dissection$-accordion associated to a puncture would be the infinite line crossing all (infinitely many) arcs attached to the puncture.
 \end{definition}
@@
 Here, we consider that~$f\dual$ lies on the right (resp.~left) of~$\alpha$ when~$\alpha$ circles clockwise (resp.~counterclockwise) around~$f\dual$.
-By convention, we also consider that the punctures of~$V$ are $\dissection\dual$-slaloms that are considered as external slaloms.
+By convention, we also consider that the punctures of~$V$ are $\dissection\dual$-slaloms that are considered external.
+If we were working on the universal cover of the surface, the~$\dissection$-accordion associated to a puncture would be the infinite line crossing all (infinitely many) arcs attached to the puncture.
 \end{definition}
@@
 \label{def:noncrossingComplex}
-We call \defn{non-crossing complex} of the pair of dual cellular dissections~$(\dissection, \dissection\dual)$ the simplicial complex~$\NCC = \AC = \SC$.
-Similarly, the \defn{reduced non-crossing complex} of~$(\dissection, \dissection\dual)$ is~$\RNCC = \RAC = \RSC$.
+We call \defn{non-crossing complex} of the pair of dual cellular dissections~$(\dissection, \dissection\dual)$ the simplicial complex~$\NCC \eqdef \AC = \SC$.
+Similarly, the \defn{reduced non-crossing complex} of~$(\dissection, \dissection\dual)$ is~$\RNCC \eqdef \RAC = \RSC$.
 \end{definition}
@@
 When the dissection~$\dissection$ is a classical dissection of a polygon (with no punctures) where each cell has at most one boundary edge, the dual dissection~$\dissection\dual$ is a tree.
-The non-kissing complex in this situation was treated in detail in~\cite{GarverMcConville, MannevillePilaud-accordion}.
-Note that even when the surface~$\surface$ is a disk, we authorize here both~$\dissection$ and~$\dissection\dual$ to have interior faces and punctures.
+The non-crossing complex in this situation was treated in detail in~\cite{GarverMcConville, MannevillePilaud-accordion}.
+Note that even when the surface~$\surface$ is a disk, we authorize in the present paper both~$\dissection$ and~$\dissection\dual$ to have interior faces and punctures.
 \end{example}
@@
 In this section, we show that non-kissing and non-crossing complexes actually coincide.
-Namely, any pair of dual cellular dissections~$(\dissection, \dissection\dual)$ defines a locally gentle bound quiver~$\bar Q_{\dissection}$ such that the non-crossing complex~$\NCC$ is isomorphic to the non-kissing complex~$\NKC[\bar Q_{\dissection}]$.
-Conversely, any locally gentle bound quiver~$\bar Q$ gives rise to a surface~$\surface_{\bar Q}$ equipped with a pair of dual cellular dissections~$\dissection_{\bar Q}$ and~${{\dissection\dual}\!\!_{\bar Q}}$ such that the non-kissing complex~$\NKC$ is isomorphic to the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection\dual\!\!_{\bar Q}}]$.
+Namely, any pair of dual cellular dissections~$(\dissection, \dissection\dual)$ defines a locally gentle bound quiver~$\bar Q_{\dissection}$ (see Section~\ref{subsec:D2Q}) such that the non-crossing complex~$\NCC$ is isomorphic to the non-kissing complex~$\NKC[\bar Q_{\dissection}]$.
+Conversely, any locally gentle bound quiver~$\bar Q$ gives rise to a surface~$\surface_{\bar Q}$ equipped with a pair of dual cellular dissections~$\dissection_{\bar Q}$ and~${{\dissection\dual}\!\!_{\bar Q}}$ (see Section~\ref{subsec:Q2D}) such that the non-kissing complex~$\NKC$ is isomorphic to the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection\dual\!\!_{\bar Q}}]$.
 In fact, we show that the accordion, slalom, and non-kissing complexes can all be pictured in a unique way on the surface.
 Interestingly, via the correspondence between pairs of dual cellular dissections and locally gentle bound quivers, the duality between the dissections~$\dissection$ and~$\dissection\dual$ translates into the Koszul duality between the locally gentle algebras of~$\bar Q$ and~$\bar Q\koszul$.
+Many examples are treated in Section~\ref{subsec:Q2D}.
 
 \subsection{The bound quiver of a dissection}
+\label{subsec:D2Q}
 
@@
 The bound quiver of the dissection~$\dissection$ is the bound quiver $\bar Q_{\dissection} = (Q_{\dissection}, I_{\dissection})$ defined as follows:
-\begin{itemize}
+\begin{enumerate}[(i)]
  \item the set of vertices of~$Q_{\dissection}$ is the set of edges of $\dissection$;
@@
  \item the ideal~$I_{\dissection}$ is generated by the paths of length two in~$Q_{\dissection}$ obtained by composing arrows which correspond to triples of consecutive edges in a face of~$\dissection$.
-\end{itemize}
+\end{enumerate}
 The bound quiver of the dissection~$\dissection\dual$ is the bound quiver $\bar Q_{\dissection\dual} = (Q_{\dissection\dual}, I_{\dissection\dual})$ defined by replacing~$\dissection$ by~$\dissection\dual$ in the above.
@@
 \begin{proof}
-Each arc~$a$ has two endpoints, and at each endpoint there is at most one arc coming immediately after~$a$ in the clockwise order, and at most one coming immediately before~$a$.
+Each edge~$a$ of~$\dissection$ has two endpoints, and at each endpoint there is at most one edge of~$\dissection$ coming immediately after~$a$ in the clockwise order, and at most one edge of~$\dissection$ coming immediately before~$a$.
 Thus, in~$Q_{\dissection}$, there are at most two arrows leaving~$a$ and at most two arriving in~$a$.
@@
 The \defn{Koszul dual} of a locally gentle bound quiver~$\bar Q = (Q,I)$ is the bound quiver~$\bar Q\koszul = (Q\koszul, I\koszul)$ defined as follows:
-\begin{itemize}
+\begin{enumerate}[(i)]
  \item the quiver~$Q\koszul$ is equal to the opposite quiver of~$Q$, that is, the quiver obtained from~$Q$ by reversing all arrows;
  \item the ideal~$I\koszul$ is generated by the opposites of the paths of length two in~$Q$ that do not appear in~$I$.
-\end{itemize}
+\end{enumerate}
 \end{definition}
@@
 \begin{proof}
-The duality provides a bijection~$v\in (Q_\dissection)_0\mapsto v\dual\in (Q_{\dissection\dual})_0$, and thus induces a bijection~${\alpha \in (Q_\dissection)_1 \mapsto \alpha\dual \in (Q_{\dissection\dual})_1}$ with~$s(\alpha\dual)=s(\alpha)\dual$ and~$t(\alpha\dual)=t(\alpha)\dual$.
+The duality provides a bijection~$v\in (Q_\dissection)_0\mapsto v\dual\in (Q_{\dissection\dual})_0$, and also induces a bijection~${\alpha \in (Q_\dissection)_1 \mapsto \alpha\dual \in (Q_{\dissection\dual})_1}$ with~$s(\alpha\dual) = t(\alpha)\dual$ and~$t(\alpha\dual) = s(\alpha)\dual$.
  Moreover, for any two composable arrows~$\alpha,\beta\in(Q_\dissection)_0$, we have~$\alpha\beta\in I_\dissection$ if and only if~$s(\alpha),t(\alpha),t(\beta)$ are three consecutive edges of a~$\dissection$-cell~$f$, if and only if~$s(\alpha)\dual,t(\alpha)\dual,t(\beta)\dual$ are three consecutive arcs in~$\dissection\dual$ ending in~$f\dual$, if and only if~$\beta\dual\alpha\dual\notin I_{\dissection\dual}$.
@@
 \subsection{The surface of a locally gentle bound quiver}
+\label{subsec:Q2D}
 
@@
 \end{enumerate}
-The orientations on the edges are only use to perform the identifications and can be immediately forgotten.
+The orientations on the edges are only used to perform the identifications and can be immediately forgotten.
 \end{definition}
@@
 
-The advantage of Definition~\ref{def:surfaceQuiver} is that it automatically endows~$\surface_{\bar Q}$ with two disjoint sets~$V_{\bar Q}$ and~${V\dual_{\bar Q}}$ of marked points and two dual cellular dissections~$\dissection_{\bar Q}$ and~${\dissection\dual\!\!_{\bar Q}}$ defined as follows.
+The advantage of Definition~\ref{def:surfaceQuiver} is that it automatically endows~$\surface_{\bar Q}$ with two disjoint sets~$V_{\bar Q}$ and~${{V\dual}\!\!_{\bar Q}}$ of marked points and two dual cellular dissections~$\dissection_{\bar Q}$ and~${\dissection\dual\!\!_{\bar Q}}$ defined as follows.
 
@@
 \end{itemize}
-The set~${V\dual_{\bar Q}}$ and the ${V\dual_{\bar Q}}$-dissection~${\dissection\dual\!\!_{\bar Q}}$ are defined dually.
+The set~${{V\dual}\!\!_{\bar Q}}$ and the ${{V\dual}\!\!_{\bar Q}}$-dissection~${\dissection\dual\!\!_{\bar Q}}$ are defined dually.
 \end{definition}
@@
 
-Let~$v\in V_{\bar Q}$. The situation around~$v$ is as follows, depending on whether~$v$ corresponds to a finite or infinite maximal path of~$\bar Q\blossom$,:
+Let~$v\in V_{\bar Q}$. The situation around~$v$ is as follows, depending on whether~$v$ corresponds to a finite or infinite maximal path of~$\bar Q\blossom$:
 
@@
 \label{thm:bijectionLocallyGentleAndSurfaces}
- Up to isomorphism, the constructions of Definitions \ref{def:quiverDualDissections} and \ref{def:surfaceQuiver} are inverse to each other.
- They induce a bijection between the set of isomorphism classes of locally gentle algebras and the set of homeomorphism classes of marked surfaces with a pair of dual cellular dissections.
+Up to isomorphism, the constructions of Definitions \ref{def:quiverDualDissections} and \ref{def:surfaceQuiver} are inverse~to~each other.
+They induce a bijection between the set of isomorphism classes of locally gentle bound quivers and the set of homeomorphism classes of marked surfaces with a pair of dual cellular dissections.
 \end{theorem}
@@
 \item The set~$V_{\bar Q}$ has one vertex for each straight walk in~$\bar Q$ (equivalently, for each maximal path in~$\bar Q$).
-      Finite straight walks yield vertices on the boundary, while infinite cyclic straight walks in~$\bar Q$ and in~$\bar Q\koszul$ yield punctures.
+      Finite straight walks yield vertices on the boundary of~$\surface_{\bar Q}$, while infinite cyclic straight walks in~$\bar Q$ yield punctures~$\surface_{\bar Q}$ in~$V_{\bar Q}$.
+      We denote by~$p$ the number of infinite cyclic straight walks in~$\bar Q$.
 \item \label{item:arcs}
@@
 \item The dissection~$\dissection_{\bar Q}$ has one $\ell$-cell for each straight walk of length~$\ell$ in~$\bar Q\koszul$.
-\item A similar remark holds dually for~${V\dual_{\bar Q}}$ and~${\dissection\dual\!\!_{\bar Q}}$.
-\item The number~$p$ of punctures of~$\surface_{\bar Q}$ is the number of infinite straight walks in~$\bar Q$ and in~$\bar Q\koszul$.
+\item Similar statements hold dually for~${{V\dual}\!\!_{\bar Q}}$ and~${\dissection\dual\!\!_{\bar Q}}$.
+\item The number of punctures of~$\surface_{\bar Q}$ is the number~$p + p\dual$ of infinite straight walks in~$\bar Q$ and in~$\bar Q\koszul$.
 \item \label{item:boundary}
@@
       \[
-       g = \frac{|Q_1| - |Q_0| - b - p + 2}{2},
+       g = \frac{|Q_1| - |Q_0| - b - p - p\dual + 2}{2},
       \]

### 2018-07-12 draft/accordionComplexSurfaces.tex
surface

@@
 \item The dissection~$\dissection_{\bar Q}$ has one $\ell$-cell for each straight walk of length~$\ell$ in~$\bar Q\koszul$.
-\item Similar statements hold dually for~${{V\dual}\!\!_{\bar Q}}$ and~${\dissection\dual\!\!_{\bar Q}}$.
+\item Similar statements hold dually for~${{V\dual}\!\!_{\bar Q}}$ and~${\dissection\dual\!\!_{\bar Q}}$, and the notations~$p\dual$ and~$\dualedgeof(v)$ are defined similarly.
 \item The number of punctures of~$\surface_{\bar Q}$ is the number~$p + p\dual$ of infinite straight walks in~$\bar Q$ and in~$\bar Q\koszul$.
@@
       where~$b$ is the number of boundary components (see above for a way to compute~$b$) and~$p$ the number of punctures (\ie infinite straight walks in~$\bar Q$ and in~$\bar Q\koszul$).
-      Indeed, $2g = 2-\chi(\surface_{\bar Q})$, where~$\chi(\surface_{\bar Q})$ is the Euler characteristic of~$\surface_{\bar Q}$.
-      The dissection~$\dissection$ provides a cellular decomposition of~$\surface_{\bar Q}$ on which we fill the boundary components and the punctures with disks.  
-      The number of faces of this cellular decomposition is~$b+p$, its number of edges is~$|Q_0|$ and its number of vertices is the number of finite straight walks in~$\bar Q$, which is equal to~$2|Q_0| - |Q_1|$.
+      Indeed, ${2g = 2-\chi(\surface_{\bar Q})}$, where~$\chi(\surface_{\bar Q})$ is the Euler characteristic of~$\surface_{\bar Q}$.
+      The dissection~$\dissection$ provides a cellular decomposition of~$\surface_{\bar Q}$ on which we fill the boundary components with disks.  
+      The number of faces of this cellular decomposition is~$b + p\dual$, its number of edges is~$|Q_0|$ and its number of vertices is the number of straight walks in~$\bar Q$, which is equal to~$2|Q_0| - |Q_1| + p$.
       The above formula for~$g$ follows.
@@
 
-\begin{example}[Cambrian paths]
+\begin{example}
 \label{exm:CambrianPath}

### 2018-07-12 draft/accordionComplexSurfaces.tex
remark 4.28

@@
 \begin{definition}
+\label{def:crossingCurves}
 Two curves or arcs \defn{cross} when they intersect in~their~interior.
 We will always assume that collections of arcs on a surface are in minimal position, in the sense that they cross each other transversaly, and the number of crossings is minimal.
-It is pointed out in \cite{Thurston} that the results in \cite{FreedmanHassScott} and \cite{Neumann-Coto} imply that this assumption can always be satisfied (up to homotopy).
+It is pointed out in \cite{Thurston} that the results in~\cite{FreedmanHassScott} and~\cite{Neumann-Coto} imply that this assumption can always be satisfied (up to homotopy).
 \end{definition}
@@
 Let~$\bar Q$ be a locally gentle bound quiver.
-For each arc of the dissection~$\dissection_{\bar Q}$ on~$\surface_{\bar Q}$, we fix a point on the interior of this arc, which we call its ``middle point''.
+For each arc of the dissection~$\dissection_{\bar Q}$ on~$\surface_{\bar Q}$, we fix a point on the interior of this arc, which we call its ``middle point'' (this is the black vertex on the pictures).
 To each walk on~$\bar Q$, we will now associate a~$\dissection_{\bar Q}$-accordion.
@@
 \end{lemma}
+
 \begin{proof}
-We can assume that~$\gamma$ intersects itself and the arcs of~$\dissection_{\bar Q}$ transversaly and minimally, in the sense that~$\gamma$ does not cross an arc twice in succession in opposite directions.
+We can assume that~$\gamma$ intersects itself and the arcs of~$\dissection_{\bar Q}$ transversaly and minimally, in the sense that~$\gamma$ does not cross an arc twice in succession in opposite directions (see Definition~\ref{def:crossingCurves}).
 Then~$\gamma$ is completely determined by its sequence of intersection points with the arcs of~$\dissection_{\bar Q}$, since the dissection is cellular.
@@
 By construction, we have that~$\curveof(\walk(\gamma)) = \gamma$.
-
-Is also follows from construction above and from Definition~\ref{def:curveOfAWalk} that~$\walk(\curveof(\omega)) = \omega$ for any walk~$\omega$.
+Is also follows from the construction above and from Definition~\ref{def:curveOfAWalk} that~$\walk(\curveof(\omega)) = \omega$ for any walk~$\omega$.
 This finishes the proof.
@@
 \end{example}
+
+\begin{remark}
+According to Proposition~\ref{prop:dualityKoszul2} and Theorem~\ref{thm:complexesCoincide}, the simplicial complexes~$\NKC[\bar Q\koszul]$ and~$\NCC[{\dissection\dual\!\!_{\bar Q}}, \dissection_{\bar Q}]$ are isomorphic.
+It would be interesting to find the precise link between~$\NKC[\bar Q\koszul]$ and~$\NKC[\bar Q\koszul]$.
+\end{remark}
 

### 2018-07-12 secondPaper/accordionComplexSurfaces.tex

--- 2018-07-12 draft/accordionComplexSurfaces.tex
@@
 According to Proposition~\ref{prop:dualityKoszul2} and Theorem~\ref{thm:complexesCoincide}, the simplicial complexes~$\NKC[\bar Q\koszul]$ and~$\NCC[{\dissection\dual\!\!_{\bar Q}}, \dissection_{\bar Q}]$ are isomorphic.
-It would be interesting to find the precise link between~$\NKC[\bar Q\koszul]$ and~$\NKC[\bar Q\koszul]$.
+It would be interesting to find the precise link between~$\NKC$ and~$\NKC[\bar Q\koszul]$.
 \end{remark}
@@
 
-The following definition is illustrated in \fref{fig:orderCurves}.
-
-\begin{definition}\label{def:orderForWalks}
+The following definition is illustrated in \fref{fig:orderCurves}\,(left).
+
+\begin{definition}
+\label{def:orderForWalks}
 For any arrow~$\alpha \in Q\blossom_1$ and any two distinct non-kissing walks~$\mu_\star, \nu_\star$ marked at an occurrence of~$\alpha^\pm$,
@@
 Two distinct non-kissing walks~$\mu_\star, \nu_\star$ marked at~$\alpha$ in~$\bar Q$ correspond to two distinct non-crossing~$\dissection$-accordions (resp.~$\dissection\dual$-slaloms)~$\gamma$ and~$\delta$ passing in front of this angle.
-Then~$\gamma \prec_\alpha \delta$ if~$\gamma$ passes closer to~$v$ (resp.~farther to~$v\dual$) than~$\delta$ does.
+Then~$\gamma \prec_\alpha \delta$ if~$\gamma$ passes closer to~$v$ (resp.~further to~$v\dual$) than~$\delta$ does.
 These interpretations of~$\prec_\alpha$ on the surface where already considered in the case of the disk in~\cite{GarverMcConville, MannevillePilaud-accordion}.
@@
 
-\begin{proof}
-
-\para{Combinatorial proof}
+\begin{proof}[Combinatorial proof]
 Let~$c=\alpha_1\cdots\alpha_r$ be a non-trivial oriented cycle in some walk~$\omega$, with~$c, c^2\notin I$.
@@
 \end{lemma}
-\begin{proof}
-
- \para{Combinatorial proof}
- By Lemma~\ref{lem:ExistenceOfDistinguishedArrows}, the number of walks in a finite face of~$\NKC$ is bounded by~$|Q_1\blossom|+s_\infty$, where~$s_\infty$ is the number of infinite straight walks (i.e.
+
+\begin{proof}[Combinatorial proof]
+By Lemma~\ref{lem:ExistenceOfDistinguishedArrows}, the number of walks in a finite face of~$\NKC$ is bounded by~$|Q_1\blossom|+p$, where~$p$ is the number of infinite straight walks (i.e.
 the number of primitive oriented cycles in~$Q$).
@@
 Its elements are pairwise compatible~$\dissection$-accordions on the surface~$\surface_{\bar Q}$.
- Thus~$F$ can be viewed as a partial tagged triangulation of~$\surface_{\bar Q}$, by letting the~$\dissection$-accordions circling a puncture in (say) clockwise order be seen as ``notched'' arcs to said puncture, and the ones circling it in counter-clockwise orientation be ``un-notched'' arcs.
+Thus~$F$ can be viewed as a partial tagged triangulation of~$\surface_{\bar Q}$, by letting the~$\dissection$-accordions circling a puncture in (say) clockwise order be seen as ``notched'' arcs to said puncture, and the ones circling it in counterclockwise orientation be ``un-notched'' arcs.
 It is known (see, for instance, \cite{FominShapiroThurston}) that any such partial tagged triangulation can be embedded into a full triangulation, and that triangulations contain a finite number of arcs.
@@
 
-\begin{proof}[Proof of Lemma~\ref{prop:facetsAreFinite}]
+\begin{proof}[Proof of Proposition~\ref{prop:facetsAreFinite}]
  If~$\NKC$, respectively~$\NCC$, admits an infinite face, then all subsets of this face are also faces, so~$\NKC$, respectively~$\NCC$, admits faces of arbitrary finite cardinality.
@@
 The reduced non-kissing complex~$\RNKC$ and the reduced non-crossing complex~$\RNCC[\dissection_{\bar Q}, {\dissection\dual\!\!_{\bar Q}}]$ are pure of dimension~$|Q_0|$.
-The non-kissing complex~$\NKC$ and the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection\dual\!\!_{\bar Q}}]$ are pure of dimension~$3|Q_0| - |Q_1| + s_\infty$ where~$s_\infty$ is the number of primitive oriented cycles in~$\bar Q$ or equivalently the number of punctures in~$V_Q$ in~$\surface_{\bar Q}$.
+The non-kissing complex~$\NKC$ and the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection\dual\!\!_{\bar Q}}]$ are pure of dimension~$3|Q_0| - |Q_1| + p$ where~$p$ is the number of primitive oriented cycles in~$\bar Q$ or equivalently the number of punctures in~$V_{\bar Q}$.
 \end{proposition}
@@
 Note that Proposition \ref{prop:purity} was proved for~$\NKC$ in \cite[Cor.~2.27]{PaluPilaudPlamondon} in the case where~$kQ/I$ is finite-dimensional.
-Note also that, by Theorem \ref{thm:complexesCoincide} above,~$\NKC$ and~$\NCC[\dissection_{\bar Q}, {\dissection\dual\!\!_{\bar Q}}]$ coincide, so it suffices to prove the Proposition for one of them.
+Note also that, by Theorem \ref{thm:complexesCoincide} above,~$\NKC$ and~$\NCC[\dissection_{\bar Q}, {\dissection\dual\!\!_{\bar Q}}]$ coincide, so it suffices to prove the statement for one of them.
 The following definition from \cite[Def.~2.23]{PaluPilaudPlamondon} extends to the setting of locally gentle algebras.
@@
 Let~$\alpha \in Q\blossom_1$ be an arrow and let~$F$ be a face of~$\NKC$ containing the straight walk passing through~$\alpha$.
-Consider the marked walk~$\omega_\star \eqdef \max_{\prec_\alpha} F_\alpha$ (which exists by Lemmas \ref{lemm:facesHaveMaximalElement} and~\ref{prop:facetsAreFinite}),
+Consider the marked walk~$\omega_\star \eqdef \max_{\prec_\alpha} F_\alpha$ (which exists by Lemma~\ref{lemm:facesHaveMaximalElement} and Proposition~\ref{prop:facetsAreFinite}),
 and let~$\omega$ be the walk obtained by forgetting the marked arrow in~$\omega_\star$. 
@@
 
-\begin{proof}
-We provide two proofs of the lemma.
-One is combinatorial and applies to~$\NKC$, and the other is geometric and applies to~$\NCC[\dissection_{\bar Q}, {\dissection\dual\!\!_{\bar Q}}]$.
-
-\para{Combinatorial proof}
+\begin{proof}[Combinatorial proof]
 Consider a maximal non-kissing face~$F \in \NKC$ and an arrow~$\alpha$ in~$c$.
@@
 Let~$\sigma$ be a common substring of~$\nu$ and~$\lambda$ where they kiss.
-Since~$\lambda$ must be compatible with~$\mu$ and with the straight walk~$c^\infty$, the substring~$\sigma$ must contain~$t(\alpha) = s(\beta)$.
+Since~$\lambda$ must be compatible with~$\mu$ and with the straight walk~$c^\infty$, the substring~$\sigma$ must contain~${t(\alpha) = s(\beta)}$.
 If~$\lambda$ contains neither~$\alpha$ nor~$\beta$, then it contains~$\gamma$ and enters $\nu$ at~$s(\gamma)$.
@@
 The proof follows that of~\cite[Cor.~2.27]{PaluPilaudPlamondon}.
-Let~$b$ denote the number of bending walks, $s$ the number of finite straight walks, and $s_\infty$ the number of infinite straight walks in a non-kissing facet~$F$ of~$\NKC$.
+Let~$b$ denote the number of bending walks, $s$ the number of finite straight walks, and $p$ the number of infinite straight walks in a non-kissing facet~$F$ of~$\NKC$.
 Since each finite straight walk uses two blossom arrows, we have~$s = 2|Q_0|-|Q_1|$ (see Remark~\ref{rem:sizeBlossomingQuiver}).
@@
 \[
-2 * b + 1 * s + 0 * s_\infty= |Q_1\blossom| = 4|Q_0|-|Q_1|
+2 * b + 1 * s + 0 * p= |Q_1\blossom| = 4|Q_0|-|Q_1|
 \]
-from which we derive that~$b = |Q_0|$ and~$b+s+c = 3|Q_0|-|Q_1|+s_\infty$.
+from which we derive that~$b = |Q_0|$ and~$b+s+p = 3|Q_0|-|Q_1|+p$.
 \end{proof}
@@
 \label{coro:thin}
-The non-kissing complex~$\RNKC$ is pure of dimension~$|Q_0|$.  Moreover, it is thin and is a pseudomanifold without boundary.
+The non-kissing complex~$\RNKC$ is thin and is thus a pseudomanifold without boundary.
 \end{corollary}
@@
 Let~$\omega = \walk(\gamma)$.
-Using the notation of Proposition \ref{prop:flip}, the local configuration around~$\omega$ (as in Figure \ref{fig:flip1}) translates on the (universal cover of the) surface~$\surface(\bar Q)$ as follows.
-
+Using the notation of Proposition \ref{prop:flip}, the local configuration around~$\omega$ (as in Figures~\ref{fig:flip1} and~\ref{fig:flip2}) translates on the (universal cover of the) surface~$\surface(\bar Q)$ as follows.
+%
 \begin{figure}[h]
@@
 \end{figure}
-
-We see that the only two~$\dissection$-accordions found between~$\mu$ and~$\curveof(\omega)$ are~$\mu$ and~$\curveof(\omega)$ themselves.  The same holds by replacing~$\mu$ with~$\nu$.
+%
+We see that the only two~$\dissection$-accordions found between~$\mu$ and~$\curveof(\omega)$ are~$\mu$ and~$\curveof(\omega)$ themselves.
+The same holds by replacing~$\mu$ with~$\nu$.
 Thus~$\mu, \nu$ and~$\curveof(\omega)$ lie in a~$\SSS$ or a~$\ZZZ$.
-
+%
 We see that~$\curveof(\omega')$ is then obtained as claimed. The direction of the flip translates from the picture in a similar way.
@@
 Call \defn{distinguished subcurve} of~$\curveof(\omega)$ in~$\curveof(F)$ the part of~$\curveof(\omega)$ which lies strictly between the two angles of~$\dissection$ (or of~$\dissection\dual$) where~$\curveof(\omega)$ is maximal (see Remark~\ref{rem:countercurrentOrderOnSurface}).
-For a vertex~$v \in Q_0$, the $v$-th entry of the $\b{c}$-vector~$\cvector{\omega}{F}$ is given by:
+For a vertex~$v \in Q_0$, the $v$-th entry of the $\b{c}$-vector~$\cvector{\omega}{F}$ is up to the sign given by:
 \begin{enumerate}[(i)]

### 2018-07-12 firstPaper/firstPaperLong/figures/blossomingQuiver.tex

\begin{tikzpicture}
	  \node(T1) at (0,0) {
		\begin{tikzpicture}
    	\node[inner sep = 1pt] (a) at (1,3) {$\bullet$};
    	\node[inner sep = 1pt] (b) at (1,1) {$\bullet$};
    	\node[inner sep = 1pt] (c) at (2,2) {$\bullet$};
    	\node[inner sep = 1pt] (d) at (3,3) {$\bullet$};
    	\node[inner sep = 1pt] (e) at (4,2) {$\bullet$};
    	\node[inner sep = 1pt] (f) at (5,3) {$\bullet$};
    	\node[inner sep = 1pt] (g) at (5,1) {$\bullet$};
    	\node[inner sep = 1pt] (h) at (6,2) {$\bullet$};
    	\node[inner sep = 1pt] (i) at (7,3) {$\bullet$};
        \path [->, ultra thick] (a) edge (c);
        \path [->, ultra thick] (d) edge (c);
        \path [->, ultra thick] (d) edge (e);
        \path [->, ultra thick] (f) edge (e);
        \path [->, ultra thick] (f) edge (h);
        \path [->, ultra thick] (i) edge (h);
        \path [->, ultra thick] (c) edge (b);
        \path [->, ultra thick] (e) edge (g);
    	\draw pic[draw, angle eccentricity=1.2, angle radius=.4cm, ultra thick]{angle=a--c--b};
    	\draw pic[draw, angle eccentricity=1.2, angle radius=.4cm, ultra thick]{angle=g--e--f};
	  \end{tikzpicture}};
	  \node(T2) at (7.5,0) {
		\begin{tikzpicture}
    	\node[inner sep = 1pt] (a) at (1,3) {$\bullet$};
    	\node[inner sep = 1pt] (b) at (1,1) {$\bullet$};
    	\node[inner sep = 1pt] (c) at (2,2) {$\bullet$};
    	\node[inner sep = 1pt] (d) at (3,3) {$\bullet$};
    	\node[inner sep = 1pt] (e) at (4,2) {$\bullet$};
    	\node[inner sep = 1pt] (f) at (5,3) {$\bullet$};
    	\node[inner sep = 1pt] (g) at (5,1) {$\bullet$};
    	\node[inner sep = 1pt] (h) at (6,2) {$\bullet$};
    	\node[inner sep = 1pt] (i) at (7,3) {$\bullet$};
    	\node (x1) at (.2,3.8) {};
    	\node (x2) at (.2,2.2) {};
    	\node (x3) at (.2,1.8) {};
    	\node (x4) at (.2,.2) {};
    	\node (x5) at (1.8,.2) {};
    	\node (x6) at (2.8,1.2) {};
    	\node (x7) at (3.2,1.2) {};
    	\node (x8) at (4.2,.2) {};
    	\node (x9) at (5.8,.2) {};
    	\node (x10) at (5.5,1.5) {};
    	\node (x11) at (5.5,1.5) {};
    	\node (x12) at (6.8,1.2) {};
    	\node (x13) at (7.8,2.2) {};
    	\node (x14) at (7.8,3.8) {};
    	\node (x15) at (6.2,3.8) {};
    	\node (x16) at (5.8,3.8) {};
    	\node (x17) at (4.2,3.8) {};
    	\node (x18) at (3.8,3.8) {};
    	\node (x19) at (2.2,3.8) {};
    	\node (x20) at (1.8,3.8) {};
        \path [->, ultra thick] (a) edge (c);
        \path [->, ultra thick] (d) edge (c);
        \path [->, ultra thick] (d) edge (e);
        \path [->, ultra thick] (f) edge (e);
        \path [->, ultra thick] (f) edge (h);
        \path [->, ultra thick] (i) edge (h);
        \path [->, ultra thick] (c) edge (b);
        \path [->, ultra thick] (e) edge (g);
        \path [->] (x1) edge (a);
        \path [->] (a) edge (x2);
        \path [->] (x3) edge (b);
        \path [->] (b) edge (x4);
        \path [->] (b) edge (x5);
        \path [->] (c) edge (x6);
        \path [->] (e) edge (x7);
        \path [->] (g) edge (x8);
        \path [->] (g) edge (x9);
        \path [->] (x10) edge (g);
        \path [->] (h) edge (x11);
        \path [->] (h) edge (x12);
        \path [->] (i) edge (x13);
        \path [->] (x14) edge (i);
        \path [->] (x15) edge (i);
        \path [->] (x16) edge (f);
        \path [->] (x17) edge (f);
        \path [->] (x18) edge (d);
        \path [->] (x19) edge (d);
        \path [->] (x20) edge (a);
    	\draw pic[draw, angle eccentricity=1.2, angle radius=.4cm, ultra thick]{angle=a--c--b};
    	\draw pic[draw, angle eccentricity=1.2, angle radius=.4cm, ultra thick]{angle=g--e--f};
    	\draw pic[draw, angle eccentricity=1.2, angle radius=.4cm]{angle=x1--a--x2};
    	\draw pic[draw, angle eccentricity=1.2, angle radius=.4cm]{angle=x3--b--x4};
    	\draw pic[draw, angle eccentricity=1.2, angle radius=.4cm]{angle=x5--b--c};
    	\draw pic[draw, angle eccentricity=1.2, angle radius=.4cm]{angle=x6--c--d};
    	\draw pic[draw, angle eccentricity=1.2, angle radius=.4cm]{angle=d--e--x7};
    	\draw pic[draw, angle eccentricity=1.2, angle radius=.4cm]{angle=e--g--x8};
    	\draw pic[draw, angle eccentricity=1.2, angle radius=.4cm]{angle=x9--g--x10};
    	\draw pic[draw, angle eccentricity=1.2, angle radius=.4cm]{angle=f--h--x11};
    	\draw pic[draw, angle eccentricity=1.2, angle radius=.4cm]{angle=x12--h--i};
    	\draw pic[draw, angle eccentricity=1.2, angle radius=.4cm]{angle=x13--i--x14};
    	\draw pic[draw, angle eccentricity=1.2, angle radius=.4cm]{angle=x15--i--h};
    	\draw pic[draw, angle eccentricity=1.2, angle radius=.4cm]{angle=h--f--x16};
    	\draw pic[draw, angle eccentricity=1.2, angle radius=.4cm]{angle=x17--f--e};
    	\draw pic[draw, angle eccentricity=1.2, angle radius=.4cm]{angle=e--d--x18};
    	\draw pic[draw, angle eccentricity=1.2, angle radius=.4cm]{angle=x19--d--c};
    	\draw pic[draw, angle eccentricity=1.2, angle radius=.4cm]{angle=c--a--x20};
	  \end{tikzpicture}};
\end{tikzpicture}

### 2018-07-12 firstPaper/firstPaperLong/figures/gcmatrices.tex

\(
\begin{blockarray}{ccccccc}
	& {\color{red} \bullet} & {\color{orange} \bullet} & {\color{yellow} \bullet} & {\color{green} \bullet} & {\color{blue} \bullet} & {\color{violet} \bullet} \\
	\begin{block}{c(cccccc)}
	1 & 0 & 0 & 0 & 0 & 0 & \!\!-1\\
	2 & 0 & 0 & 0 & 0 & \!\!-1\!\! & 0 \\
	3 & 0 & 1 & 0 & 1 & 0 & 0 \\
	4 & 0 & 0 & 0 & \!\!-1\!\! & 0 & 0 \\
	5 & 0 & 0 & 1 & 1 & 1 & 0 \\
	6 & 1 & 0 & 0 & 0 & 0 & 0 \\
	\end{block}
	& & & \multicolumn{2}{c}{$\gvectors{F\ex}$} & &
\end{blockarray}
%
\qquad
%
\begin{blockarray}{ccccccc}
	& {\color{red} \bullet} & {\color{orange} \bullet} & {\color{yellow} \bullet} & {\color{green} \bullet} & {\color{blue} \bullet} & {\color{violet} \bullet} \\
	\begin{block}{c(cccccc)}
	1 & 0 & 0 & 0 & 0 & 0 & \!\!-1 \\
	2 & 0 & 0 & 1 & 0 & \!\!-1\!\! & 0 \\
	3 & 0 & 1 & 0 & 0 & 0 & 0 \\
	4 & 0 & 1 & 1 & \!\!-1\!\! & 0 & 0 \\
	5 & 0 & 0 & 1 & 0 & 0 & 0 \\
	6 & 1 & 0 & 0 & 0 & 0 & 0 \\
	\end{block}
	& & & \multicolumn{2}{c}{$\cvectors{F\ex}$} & &
\end{blockarray}
\)

### 2018-07-12 firstPaper/firstPaperLong/nonKissingComplex.tex

--- 2018-07-03 firstPaper/nonKissingComplex.tex
@@
-\documentclass{amsart}
+\documentclass{memo-l}
 
 \usepackage[T1]{fontenc}
-\usepackage{enumerate, amsmath, amsfonts, amssymb, amsthm, mathrsfs, wasysym, graphics, graphicx, xcolor, url, hyperref, hypcap, xargs, multicol, overpic, pdflscape, multirow, hvfloat, minibox, accents, array, xifthen, ae, aecompl, blkarray, pifont, mathtools, a4wide}
+\usepackage{enumerate, amsmath, amsfonts, amssymb, amsthm, mathrsfs, wasysym, graphics, graphicx, xcolor, url, hyperref, hypcap,  shuffle, xargs, multicol, overpic, pdflscape, multirow, hvfloat, minibox, accents, array, xifthen, ae, aecompl, blkarray, pifont, mathtools}
 \usepackage{marginnote}
@@
 % formating the table of contents
+\setcounter{tocdepth}{4}
 \makeatletter
-\def\l@section{\@tocline{1}{2pt}{0pc}{}{}}
+\def\l@section{\@tocline{1}{7pt}{0pc}{}{}}
 \makeatother
@@
 
-\title{Non-kissing complexes and tau-tilting for gentle algebras}
+\begin{document}
+
+\frontmatter
+
+\title[Non-kissing complexes and tau-tilting for gentle algebras]{Non-kissing complexes and tau-tilting \\ for gentle algebras}
 %\title[Non-kissing complexes and tau-tilting for gentle algebras]{Non-kissing complexes and tau-tilting for gentle algebras \\ {\rm Preliminary version --- please do not distribute}}
 
-\thanks{The three authors were partially supported by the French ANR grant SC3A~(15\,CE40\,0004\,01).}
+\thanks{}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{document}
+\date{\today}
+
+\subjclass[2010]{16G10, 16G20, 05E10, 05E45, 06B10, 52B11}
+%    Recognition of the 2010 edition of the Mathematics Subject
+%    Classification requires a version of amsbook.cls from July 2009
+%    or later.  If "2010" is not recognized, please upgrade.
+
+\keywords{Representations of gentle algebras --- Support $\tau$-tilting theory --- Tamari lattice --- Associahedron}
+
+\renewcommand{\leftmark}{\sc Non-kissing complexes and tau-tilting for gentle algebras}
+\renewcommand{\rightmark}{\sc \authors}
 
@@
 
-%\vspace*{.3cm}
-
 \maketitle
 
-\vspace*{.3cm}
 \tableofcontents
 
-\vspace*{-.9cm}
-\enlargethispage{.4cm}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\addtocontents{toc}{\vspace{.3cm}}
+\section*{Acknowledgements}
+
+We benefited form various discussions and several useful comments on a preliminary version of this paper.
+We are particularly grateful to F.~Chapoton for initially pointing us in the direction of this paper, to A.~Garver and T.~McConville for important inputs on Part~\ref{part:lattice} (including pointing out to us the need of Theorem~\ref{thm:characterizationCongruenceUniform2}), to T.~Manneville and S.~Stella for their help on Part~\ref{part:geometry}, to L.~Demonet for the observation of Remarks~\ref{rem:linDep} and~\ref{rem:polytope}, and to S.~Schroll for her valuable comments on Part~\ref{part:algebra}.
+We also thank T.~Br\"ustle, O.~Iyama, N.~Reading, H.~Thomas for discussions on their ongoing projects mentioned in the introduction.
+This work was carried out while the first author was visiting Paris 7. He would like to thank his colleagues there, and especially \mbox{P.~Le Meur}, for a stimulating atmosphere.
+
+The three authors were partially supported by the French ANR grant SC3A: Surfaces, Categorification and Combinatorics of Cluster Algebras~(15\,CE40\,0004\,01).
 
@@
 
-\newpage
+\mainmatter
+
 \section*{Introduction}
@@
 The algebras that occur are certain gentle algebras, a special case of the well-studied string algebras of M.~C.~R.~Butler and C.~Ringel~\cite{ButlerRingel}.
-On the other hand, we extend the notion of non-kissing complex and show that the support $\tau$-tilting complex of any gentle algebra can be interpreted as an extended non-kissing complex.
+On the other hand, we extend the notion of non-kissing complex and show that the support \mbox{$\tau$-tilting} complex of any gentle algebra can be interpreted as an extended non-kissing complex.
 More precisely, starting from any gentle bound quiver~$\bar Q = (Q,I)$, we attach additional incoming and outgoing arrows, called blossoms, to make each initial vertex \mbox{$4$-valent}.
@@
 
-\begin{table}
-	\capstart{}
-    \centerline{
+\captionsetup{width=1.4\textwidth}
+\hvFloat[floatPos=p, capWidth=h, capPos=r, capAngle=90, objectAngle=90, capVPos=c, objectPos=c]{table}
+{
+	\hspace{1cm}
 	\begin{tabular}{|c|c|c|}
@@
     \end{tabular}
+	\hspace{1cm}
 }
-    \caption{Dictionary between algebraic notions on the support $\tau$-tilting complex and combinatorial notions on the non-kissing complex.}
-    \label{table:dictionary}    
-\end{table}
+{Dictionary between algebraic notions on the support $\tau$-tilting complex and combinatorial notions on the non-kissing complex.}
+{table:dictionary}
+\captionsetup{width=\textwidth}
+
+%\begin{table}
+%	\capstart{}
+%    \centerline{
+%    \begin{tabular}{|c|c|c|}
+%    \hline
+%    String modules on~$\bar Q$ &
+%    Walks on~$\bar Q\blossom$  &
+%    Reference
+%    \\ \hline \hline
+%    almost positive strings (Def.~\ref{def:stringsBands}) &
+%    bending walks (Def.~\ref{def:straightBended}) &
+%    Fig.~\ref{exm:exmBijectionStringsWalks1} \& \ref{fig:exmAuslanderReitenQuiver}
+%    \\ \hline
+%    ?\footnotemark[1] &
+%    straight walks (Def.~\ref{def:straightBended}) &
+%    Fig.~\ref{exm:exmBijectionStringsWalks1} \& \ref{fig:exmAuslanderReitenQuiver}
+%    \\ \hline
+%    \multiLinesBox{$P(v)$ and $P(v)[1]$ \\ $A=kQ/I$ and~$A[1]$ \\ ~} &
+%    \multiLinesBox{$v_\peak$ and $v_\deep$ \\ $F_\peak$ and~$F_\deep$ \\ (Exm.~\ref{example: Fdeep Fpeak} and Def.~\ref{def: deep walk})} &
+%    Lem.~\ref{lem:bijections-STTC-NKC}
+%    \\ \hline
+%    ?\footnotemark[2] &
+%    countercurrent order~$\prec_\alpha$ &
+%    ---
+%    \\ \hline
+%    $\tau$-compatibility (Def.~\ref{def: tau-compatibility}) &
+%    non-kissing (Def.~\ref{def: kissing}) &
+%    Thm.~\ref{thm:nkc/sttiltc}
+%    \\ \hline
+%    support~$\tau$-tilting object (Def.~\ref{def: tau-rigid and stautilt}) &
+%    maximal non-kissing collection of walks &
+%    Thm.~\ref{thm:nkc/sttiltc}
+%    \\ \hline
+%    support~$\tau$-tilting complex~$\tTC$ (Def.~\ref{def: stautilt complex}) &
+%    reduced non-kissing complex~$\RNKC$ (Def.~\ref{def: nKc}) &
+%    Thm.~\ref{thm:nkc/sttiltc}
+%    \\ \hline
+%    \multiLinesBox{(left) mutation of support \\ $\tau$-tilting objects (Thm.~\ref{thm: mutation of stautilts}~\cite{AdachiIyamaReiten})} &
+%    \multiLinesBox{(increasing) flip \\ (Prop.~\ref{prop:flip} and Def.~\ref{def:flip} \& \ref{def:increasingFlip})} &
+%    Thm.~\ref{thm:nkc/sttiltc}
+%    \\ \hline
+%    lattice of torsion classes &
+%    non-kissing lattice~$\NKL$ (Thm.~\ref{thm:lattice}) &
+%    Thm.~\ref{thm:nkc/sttiltc}
+%    \\ \hline
+%    bricks &
+%    \multiLinesBox{distinguishable strings (Def.~\ref{def:distinguishedSubstring})} &
+%    Prop.~\ref{prop:characterizationDistinguishableStrings}
+%    \\ \hline
+%    collections of pairwise Hom-orthogonal bricks &
+%    non-friendly complex (Def.~\ref{def: friendly}) &
+%    Prop.~\ref{prop:characterizationDistinguishableStrings}
+%    \\ \hline
+%    \multiLinesBox{bijection between indecomposable~$\tau$-rigid representations and bricks (Thm. 6.1 in~\cite{DemonetIyamaJasso})} &
+%    \multiLinesBox{bijection between non-kissing walks that are not peak walks and distinguishable strings (Prop.~\ref{prop:bijectionDistinguishableStringsWalks})} &
+%    \multiLinesBox{Conjectural \\ cf.~Prop.~\ref{prop:bijectionDistinguishableStringsJI}}[2cm]
+%    \\ \hline
+%    \multiLinesBox{Bongartz cocompletion of a~$\tau$-rigid indecomposable representation $N=M(\rho)$ whose associated brick is~$M(\sigma)$. Moreover $\sigma = \distinguishedWalk{\omega(\rho)}{F}$} &
+%    \multiLinesBox{$F=\eta\left(\closure{\Sigma_\bottom(\sigma)}\right)$, where $\sigma$ is a distinguishable string} &
+%    Rem.~\ref{rem: Bongartz}
+%    \\ \hline
+%    Bongartz completion &
+%    $\eta\left(\closure{\Sigma_\top(\sigma)}\right)$ &
+%    Rem.~\ref{rem: Bongartz}
+%    \\ \hline
+%    $\b{g}$-vector or index of a module (Def.~\ref{definition: g-vector of representation}) &
+%    $\b{g}$-vector of a walk (Def.~\ref{def: g-vectors for walks}) &
+%    Rem.~\ref{rem: g-vectors coincide}
+%    \\ \hline
+%    $\dim \Hom{A} \big( M(\sigma), \tau M(\sigma') \big)$ (Sec.~\ref{subsec:tautilting}) &
+%    kissing number~$\kappa \big( \omega(\sigma), \omega(\sigma') \big)$ (Def.~\ref{def: kissing number}) &
+%    Rem.~\ref{rem:KNvsTau}
+%    \\ \hline
+%    \end{tabular}
+%    }
+%    \caption{Dictionary between algebraic notions on the support $\tau$-tilting complex and combinatorial notions on the non-kissing complex.}
+%    \label{table:dictionary}    
+%\end{table}
 
@@
 When the quiver is a directed path, this increasing flip graph is the Hasse diagram of the classical Tamari lattice.
-In general, when $\bar Q$ is $\tau$-tilting finite, the transitive closure of the increasing flip graph is isomorphic to the lattice of torsion classes, and we therefore call it the non-kissing lattice.
+In general, when $\bar Q$ is \mbox{$\tau$-tilting} finite, the transitive closure of the increasing flip graph is isomorphic to the lattice of torsion classes, and we therefore call it the non-kissing lattice.
 Our main lattice-theoretic result is the following extension of a remarquable result of T.~McConville~\cite{McConville}.
@@
 
-\enlargethispage{.4cm}
 Particular instances of gentle bound quivers enable us to connect previous results and to answer open conjectures from previous works:
@@
 Their work is more oriented on the algebraic aspects of this connection.
-\item Our paper is largely inspired from the paper of T.~McConville~\cite{McConville} and a preliminary version of the recent preprint of A.~Garver and T.~McConville~\cite{GarverMcConville-grid}.
+\item Our paper is largely inspired from the paper of T.~McConville~\cite{McConville} and a preliminary version of the preprint of A.~Garver and T.~McConville~\cite{GarverMcConville-grid}.
 Although we follow the same construction for the $\b{g}$-vector fan (but in the general context of gentle bound quivers), our proof is independent and instrumental in the construction of the non-kissing associahedron.
@@
 
+\enlargethispage{-.3cm}
 In this section, we first fix our notations (\ref{subsec:pathAlgebra}) on quivers, path algebras, their representations, and their support $\tau$-tilting complexes (\ref{subsec:tautilting}).
@@
 We start by recalling standard notions on quivers, paths, and path algebras.
-We refer to the textbooks of I.~Assem, D.~Simson and A.~Skowro\'nski~\cite{AssemSimsonSkowronski} and R.~Schiffler~\cite{Schiffler} for more details.
+We refer the reader to the textbooks of I.~Assem, D.~Simson and A.~Skowro\'nski~\cite{AssemSimsonSkowronski} and R.~Schiffler~\cite{Schiffler} for more details.
 
@@
 The \defn{arrow ideal} of~$kQ$ is the ideal~$R \eqdef \bigoplus_{\ell \ge 1} kQ_\ell$ generated by the arrows of~$Q$.
-A two-sided ideal~$I$ of~$kQ$ is \defn{admissible} if there exists~$m \ge 2$ such that~$R^m \subseteq I \subseteq R^2$ (the condition~$R^m \subseteq I$ ensures that~$kQ/I$ is finite dimensional, and the condition~$I \subseteq R^2$ ensures that~$Q$ can be recovered form~$kQ/I$).
+A two-sided ideal~$I$ of~$kQ$ is \defn{admissible} if there exists~$m \ge 2$ such that~${R^m \subseteq I \subseteq R^2}$ (the condition~$R^m \subseteq I$ ensures that~$kQ/I$ is finite dimensional, and the condition~$I \subseteq R^2$ ensures that~$Q$ can be recovered form~$kQ/I$).
 The pair~$\bar Q \eqdef (Q,I)$ is then called a \defn{bound quiver} and the quotient~$kQ/I$ is a \defn{bound quiver algebra} and is finite dimensional.
 
-Two quivers~$Q = (Q_0, Q_1, s, t)$ and~$Q' = (Q_0', Q_1', s', t')$ are said to be \defn{isomorphic} if there exists $\phi \eqdef (\phi_0, \phi_1)$ where~$\phi_0 : Q_0 \to Q_0'$ and~$\phi_1 : Q_1 \to Q_1'$ are bijections such that~${s'(\phi_1(\alpha)) = \phi_0(s(\alpha))}$ and~${t'(\phi_1(\alpha)) = \phi_0(t(\alpha))}$ for all~$\alpha \in Q_1$.
-The bijection~$\phi_1 : Q_1 \to Q_1'$ naturally extends to a bijection on paths by~$\phi_1(\alpha_1 \cdots \alpha_\ell) = \phi_1(\alpha_1) \cdots \phi_1(\alpha_\ell)$, and thus to a morphism~$\phi_1 : kQ \to kQ'$ of path algebras by linearity.
+Two quivers~$Q = (Q_0, Q_1, s, t)$ and~$Q' = (Q_0', Q_1', s', t')$ are \defn{isomorphic} if there exists $\phi \eqdef (\phi_0, \phi_1)$ where~$\phi_0 : Q_0 \to Q_0'$ and~$\phi_1 : Q_1 \to Q_1'$ are bijections such that~${s'(\phi_1(\alpha)) = \phi_0(s(\alpha))}$ and~${t'(\phi_1(\alpha)) = \phi_0(t(\alpha))}$ for all~${\alpha \in Q_1}$.
+The bijection ${\phi_1 : Q_1 \to Q_1'}$ extends to a bijection on paths by~${\phi_1(\alpha_1 \cdots \alpha_\ell) = \phi_1(\alpha_1) \cdots \phi_1(\alpha_\ell)}$, and thus to a morphism~$\phi_1 : kQ \to kQ'$ of path algebras by linearity.
 We say that two bound quivers~$\bar Q = (Q,I)$ and~$\bar Q' = (Q',I')$ are \defn{isomorphic} if there there is an isomorphism~$\phi = (\phi_0, \phi_1)$ between the quivers~$Q$ and~$Q'$ such that~$\phi_1(I) = I'$.
@@
 \item $M_v$ is a~$k$-vector space for all~$v\in Q_0$, and
-\item $M_\alpha: M_{s(\alpha)} \to M_{t(\alpha)}$ is a linear map for all~$\alpha \in Q_1$, such that~$M_\pi \eqdef M_{\alpha_\ell} \circ \dots \circ M_{\alpha_1} = 0$ for any path~$\pi = \alpha_1 \dots \alpha_\ell$ in~$I$.
+\item $M_\alpha: M_{s(\alpha)} \to M_{t(\alpha)}$ is a linear map for all~$\alpha \in Q_1$, such that \[M_\pi \eqdef M_{\alpha_\ell} \circ \dots \circ M_{\alpha_1} = 0\]  for any path~$\pi = \alpha_1 \dots \alpha_\ell$ in~$I$.
 \end{itemize}
@@
 be a minimal projective presentation.
-Applying the \defn{Nakayama functor}~$\nu = D\circ \Hom{kQ/I}(-, kQ/I)$, where~$D = \Hom{k}(-, k)$ is the standard vector space duality, one gets a morphism between injective representations
+Applying the \defn{Nakayama functor} defined by~${\nu = D\circ \Hom{kQ/I}(-, kQ/I)}$, where~$D = \Hom{k}(-, k)$ is the standard vector space duality, one gets a morphism between injective representations
 \[
@@
 \begin{definition}
+Using the notations introduced above,
  \begin{enumerate}
-  \item Using the above notation, the \defn{Auslander-Reiten translation}~$\tau M$ of~$M$ is defined to be the kernel of~$\nu f^M$.
-  \item \cite{AdachiIyamaReiten} A representation~$M$ is \defn{$\tau$-rigid} if~$\Hom{\bar Q}(M, \tau M) = 0$.
+  \item the \defn{Auslander-Reiten translation}~$\tau M$ of~$M$ is defined to be the kernel of~$\nu f^M$,
+  \item a representation~$M$ is \defn{$\tau$-rigid} if~$\Hom{\bar Q}(M, \tau M) = 0$ \cite{AdachiIyamaReiten}.
  \end{enumerate}
@@
 
-\begin{definition}
+\begin{definition}[\cite{AdachiIyamaReiten}]
 \label{def: tau-rigid and stautilt}
-With this notation, and following \cite{AdachiIyamaReiten}, we say that~$M\oplus P[1]$ is
+With this notation, we say that~$M\oplus P[1]$ is
 \begin{enumerate}
@@
 \begin{definition}\label{def: stautilt complex}
-Let~$\bar Q = (Q,I)$ be a bound quiver and $A = kQ/I$ be its bound algebra.
+Let~$\bar Q = (Q,I)$ be a bound quiver and let~$A = kQ/I$.
 \begin{itemize}
@@
 A \defn{string bound quiver}~$\bar Q \eqdef (Q,I)$ is a bound quiver such that
-\begin{itemize}
+\begin{enumerate}[(i)]
 \item each vertex~$v \in Q_0$ has at most two incoming and two outgoing arrows,
 \item the ideal~$I$ is generated by paths,
-\item for any arrow~$\beta \in Q_1$, there is at most one arrow~$\alpha \in Q_1$ such that~$t(\alpha) = s(\beta)$ and~$\alpha\beta\notin I$,
-\item for any arrow~$\beta \in Q_1$, there is at most one arrow~$\gamma \in Q_1$ such that~$t(\beta) = s(\gamma)$ and~$\beta\gamma\notin I$.
-\end{itemize}
+\item for any~$\beta \in Q_1$, there is at most one~$\alpha \in Q_1$ such that~$t(\alpha) = s(\beta)$ and~$\alpha\beta\notin I$,
+\item for any~$\beta \in Q_1$, there is at most one~$\gamma \in Q_1$ such that~$t(\beta) = s(\gamma)$ and~$\beta\gamma\notin I$.
+\end{enumerate}
 The algebra~$kQ/I$ is called a \defn{string algebra}.
@@
 
-\begin{figure}[b]
+\begin{figure}[h]
 	\capstart
 	\centerline{
-		\begin{tabular}{c@{\quad}|@{\quad}c@{\quad}|@{\quad}c@{\quad}|@{\quad}c}
+		\begin{tabular}{c@{\qquad}|@{\qquad}c}
 			$Q = \vcenter{\hbox{\includegraphics[scale=.5]{exmQuiver1}}}$ &
-			$Q = \vcenter{\hbox{\includegraphics[scale=.5]{exmQuiver2}}}$ &
+			$Q = \vcenter{\hbox{\includegraphics[scale=.5]{exmQuiver2}}}$ \\[1.1cm]
+			$I = (\alpha\beta, \gamma\delta)$ & 
+			$I = (\alpha\beta, \gamma\delta, \alpha\delta)$ \\ \\ \hline \\
 			$Q = \vcenter{\hbox{\includegraphics[scale=.5]{exmQuiver3}}}$ &
-			$Q = \vcenter{\hbox{\includegraphics[scale=.5]{exmQuiver4}}}$ \\[1.1cm]
-			$I = (\alpha\beta, \gamma\delta)$ & 
-			$I = (\alpha\beta, \gamma\delta, \alpha\delta)$ & 
+			$Q = \vcenter{\hbox{\includegraphics[scale=.5]{exmQuiver4}}}$ \\[.5cm]
 			$I = (\alpha\beta, \beta\gamma, \beta^5)$ & 
@@
 	}
-	\caption{Four string bound quivers. The leftmost and rightmost are gentle bound quivers.}
+	\caption{Four string bound quivers. The top left and bottom right are gentle bound quivers.}
 	\label{fig:exmQuiver}
@@
 A \defn{gentle bound quiver}~$\bar Q \eqdef (Q,I)$ is a string bound quiver such that
-\begin{itemize}
+\begin{enumerate}[(i)]
 \item $I$ is generated by paths of length exactly two,
-\item for any arrow~$\beta \in Q_1$, there is at most one arrow~$\alpha \in Q_1$ such that~$t(\alpha) = s(\beta)$ and~$\alpha\beta \in I$,
-\item for any arrow~$\beta \in Q_1$, there is at most one arrow~$\gamma \in Q_1$ such that~$t(\beta) = s(\gamma)$ and~$\beta\gamma \in I$.
-\end{itemize}
+\item for any~$\beta \in Q_1$, there is at most one~$\alpha \in Q_1$ such that~$t(\alpha) = s(\beta)$ and~$\alpha\beta \in I$,
+\item for any~$\beta \in Q_1$, there is at most one~$\gamma \in Q_1$ such that~$t(\beta) = s(\gamma)$ and~$\beta\gamma \in I$.
+\end{enumerate}
 The algebra~$kQ/I$ is called a \defn{gentle algebra}.
@@
 	\item $t(\alpha_i^{\varepsilon_i}) = s(\alpha_{i+1}^{\varepsilon_{i+1}})$ for all~$i \in [\ell-1]$,
-	\item there is no path~$\pi \in I$ such that~$\pi$ or~$\pi^{-1}$ appears as a factor of~$\rho$, and
+	\item there is no path~$\pi \in I$ such that~$\pi$ or~$\pi^{-1}$ appears as a factor of~$\rho$,
 	\item $\rho$ is reduced, in the sense that no factor~$\alpha\alpha^{-1}$ or~$\alpha^{-1}\alpha$ appears in~$\rho$, for~$\alpha \in Q_1$.
@@
 
-\item We call \defn{negative simple string} a formal word of length zero of the form $-v$, where $v$ is any vertex of $Q_0$. We denote by
+\item We call \defn{negative simple string} a formal word of length zero of the form~$-v$, where $v$ is any vertex of $Q_0$. We let
 \(
@@
 \)
-the set of \defn{almost positive unoriented strings}.
+be the set of \defn{almost positive unoriented strings}.
 Note that~$\varepsilon_v$ and~$-v$ are different almost positive strings.
@@
 \label{exm:drawingString}
-For the algebra defined in Example~\ref{exm:aStringAlgebra}, the string~$\rho = \gamma\beta^{-1}\alpha^{-1}\gamma\beta^{-1}\alpha^{-1}\gamma\delta$ is drawn as follows:
+For the algebra of Example~\ref{exm:aStringAlgebra}, we represent the string ${\rho = \gamma\beta^{-1}\alpha^{-1}\gamma\beta^{-1}\alpha^{-1}\gamma\delta}$ as follows:
 \[
@@
 
-\begin{figure}[t]
+\begin{figure}[h]
 	\capstart
@@
 \label{rem:reverseStrings}
-Note that reversing the quiver preserves the set of strings and their substrings but exchanges top with bottom:
+Reversing the quiver preserves the set of strings and their substrings but exchanges top with bottom:
 $\Sigma(\reversed{\rho}) = \Sigma(\reversed{\rho})$ but~$\Sigma_\bottom(\reversed{\rho}) = \Sigma_\top(\rho)$ and~$\Sigma_\top(\reversed{\rho}) = \Sigma_\bottom(\rho)$.
@@
 \begin{example}
-For the algebra given in Example~\ref{exm:aStringAlgebra}, let~$\rho = \gamma\beta^{-1}\alpha^{-1}\gamma\beta^{-1}\alpha^{-1}\gamma\delta$.
+For the algebra of Example~\ref{exm:aStringAlgebra}, let~$\rho = \gamma\beta^{-1}\alpha^{-1}\gamma\beta^{-1}\alpha^{-1}\gamma\delta$.
 Then~$M(\rho)$ is given by
@@
 
-It follows from the definition that the band modules~$M(\varpi, \lambda, d)$ and~$M(\varpi^{-1}, \lambda^{-1}, d)$ are isomorphic.
+It immediately follows from the definition that the band modules~$M(\varpi, \lambda, d)$ and~$M(\varpi^{-1}, \lambda^{-1}, d)$ are isomorphic.
 Moreover, if~$\varpi$ and~$\varpi'$ are two bands that are \defn{cyclically equivalent}, in the sense that one is obtained from the other by cyclically permuting the arrows that constitute it, then we also have that~$M(\varpi, \lambda, d)$ and~$M(\varpi', \lambda, d)$ are isomorphic.
@@
     \item A string module is never isomorphic to a band module.
-    \item Two string modules~$M(\rho)$ and~$M(\rho')$ are isomorphic if and only if~$\rho' = \rho^{\pm 1}$.
+    \item Two string modules~$M(\rho)$ and~$M(\rho')$ are isomorphic if and only if~${\rho' = \rho^{\pm 1}}$.
     \item Two band modules~$M(\varpi,\lambda, d)$ and~$M(\varpi', \lambda', d')$ are isomorphic if and only if~$d=d'$, and  
@@
 
-    \item Dually, let~$\rho$ be a string that does not end on a peak.  Define $\rho_h \eqdef (_h ( \rho )^{-1} )^{-1}$ to be the string obtained by \defn{adding a hook at the end of~$\rho$}.
+    \item Dually, let~$\rho$ be a string that does not end on a peak. Let $\rho_h \eqdef (_h ( \rho )^{-1} )^{-1}$ be the string obtained by \defn{adding a hook at the end of~$\rho$}.
 
@@
 
-    \item Dually, let~$\rho$ be a string that does not end in a deep.  Define $\rho_c \eqdef (_c ( \rho )^{-1} )^{-1}$ to be the string obtained by \defn{adding a cohook at the end of~$\rho$}.
+    \item Dually, let~$\rho$ be a string that does not end in a deep. Let $\rho_c \eqdef (_c ( \rho )^{-1} )^{-1}$ be the string obtained by \defn{adding a cohook at the end of~$\rho$}.
 
@@
 
-    \item Dually, if~$\rho$ ends on a peak and is not the inverse of a path in~$\bar Q$, then define the string obtained by \defn{removing a cohook at the end of~$\rho$} as~${\rho_{c^{-1}} \eqdef (_{c^{-1}} (\rho^{-1}) )^{-1}}$.
+    \item Dually, if~$\rho$ ends on a peak and is not the inverse of a path in~$\bar Q$, then the string obtained by \defn{removing a cohook at the end of~$\rho$} is~${\rho_{c^{-1}} \eqdef (_{c^{-1}} (\rho^{-1}) )^{-1}}$.
 
@@
 
-    \item Dually, if~$\rho$ ends in a deep and is not a path in~$\bar Q$, then define the string obtained by \defn{removing a hook at the end of~$\rho$} as~${\rho_{h^{-1}} \eqdef (_{h^{-1}} (\rho^{-1}) )^{-1}}$.
+    \item Dually, if~$\rho$ ends in a deep and is not a path in~$\bar Q$, then the string obtained by \defn{removing a hook at the end of~$\rho$} is~${\rho_{h^{-1}} \eqdef (_{h^{-1}} (\rho^{-1}) )^{-1}}$.
 
@@
 starts and ends on a peak, and also ends in a deep. Moreover, we have
-\[
-_{c^{-1}}\rho = \;\vcenter{\hbox{\includegraphics[scale=0.3]{exmString5}}}
-\qquad
-_{h^{-1}}\rho = \;\vcenter{\hbox{\includegraphics[scale=0.3]{exmString6}}}
-\qquad
-\rho_{c^{-1}} = \;\vcenter{\hbox{\includegraphics[scale=0.3]{exmString7}}}
-\]
+\begin{align*}
+_{c^{-1}}\rho & = \;\vcenter{\hbox{\includegraphics[scale=0.3]{exmString5}}}
+\\[.3cm]
+_{h^{-1}}\rho & = \;\vcenter{\hbox{\includegraphics[scale=0.3]{exmString6}}}
+\\
+\rho_{c^{-1}} & = \;\vcenter{\hbox{\includegraphics[scale=0.3]{exmString7}}}
+\end{align*}
 \end{example}
@@
 Then the dimension of the $k$-vector space~$\Hom{A} \big( M(\rho), M(\rho') \big)$ is equal to
-
-\smallskip
-\centerline{
-\(
-\sum\limits_{\xi \text{ string}}  (\#\textrm{ of substrings equal to~$\xi$ on top of~$\rho$}) \cdot  (\#\textrm{ of substrings equal to~$\xi$ or~$\xi^{-1}$ at the bottom of~$\rho'$}).
-\)
-}
+\[
+\sum\limits_{\xi \text{ string}} \begin{array}{l} (\#\textrm{ of substrings equal to~$\xi$ on top of~$\rho$}) \; \cdot \\ \hspace{2cm}(\#\textrm{ of substrings equal to~$\xi$ or~$\xi^{-1}$ at the bottom of~$\rho'$}).\end{array}
+\]
 \end{proposition}
@@
  $\bigoplus_{v\in Q_0} \Z [P(v)] \cong \Z^{Q_0}$.  Thus, in the notation of Definition \ref{definition: g-vector of representation},
- if we put $P_0^M = \bigoplus_{v\in Q_0}P(v)^{\oplus a_v}$ and $P_1^M = \bigoplus_{v\in Q_0}P(v)^{\oplus b_v}$, 
+ if $P_0^M = \bigoplus_{v\in Q_0}P(v)^{\oplus a_v}$ and $P_1^M = \bigoplus_{v\in Q_0}P(v)^{\oplus b_v}$, 
  then
@@
 \begin{corollary}
- The $\b{g}$-vector of a string module $M(\rho)$ is given by $\b{g}(M) = \b{a} - \b{b} - \b{r}$, where
+ The $\b{g}$-vector of a string module $M(\rho)$ is $\b{g}(M) = \b{a} - \b{b} - \b{r}$, where
  \begin{itemize}
@@
 \begin{enumerate}
-  \item If $\rho$ is a string for $\bar Q$, we define its \defn{$\b{g}$-vector} as $\b{g}(\rho) \eqdef \b{g} \big( M(\rho) \big)$.
-  \item If $-v$ is a negative simple string for $\bar Q$, we define its \defn{$\b{g}$-vector} as $\b{g}(-v) \eqdef \b{g} \big( P(v)[1] \big) = -\b{e}_v$.
+  \item If $\rho$ is a string for $\bar Q$, we define its \defn{$\b{g}$-vector} as 
+  \[
+  \b{g}(\rho) \eqdef \b{g} \big( M(\rho) \big).
+  \]
+  \item If $-v$ is a negative simple string for $\bar Q$, we define its \defn{$\b{g}$-vector} as
+  \[
+  \b{g}(-v) \eqdef \b{g} \big( P(v)[1] \big) = -\b{e}_v.
+  \]
 \end{enumerate}
@@
 Consider a string bound quiver~$\bar Q = (Q,I)$ and its string algebra~${A = kQ/I}$.
-We now provide a combinatorial criterion for $\tau$-compatibility of string modules over~$A$.
+We now give a combinatorial criterion for $\tau$-compatibility of string modules over~$A$.
 
@@
 \end{itemize}
-\begin{figure}[t]
- 	\capstart
-% 	\centerline{
-\[
-\xy
-%
-(28,7)*+{v}="14";
-(42,7)="16";
-(49,7)*+{\rho'}="17";
-%
-(0,0)*+{\rho}="0";
-(7,0)="1";
-(21,0)*+{u}="3";
-%
-(28,-7)*+{\bullet}="-4";
-(42,-7)="-6";
-%
-{\ar@{~} "1";"3"};
-{\ar "3";"-4"};
-{\ar@{~} "-4";"-6"};
-%
-{\ar@{~} "14";"16"};
-%
-{\ar@{..>}_{\alpha} "14";"3"};
-%
-{\ar@/_.3pc/@{-} (23,0);(23,-9)};
-{\ar@/^.3pc/@{-} (44,0);(44,-9)};
-%
-\endxy
-\]
-% 		    }
-	\caption{The string~$\rho$ attracts~$\rho'$, as in Definition~\ref{definition: dance and attract} (i).}
-	\label{fig:def-attracts}
-\end{figure}
-
-\begin{figure}[t]
- 	\capstart
-\[
-\xy
-%
-(-35,14)*+{\rho'};
-(-28,14)="-14";
-(-14,14)*+{\bullet}="-12";
-(-7,7)*+{\bullet}="-11";
-(7,7)*+{\bullet}="11";
-(14,14)*+{\bullet}="12";
-(28,14)="14";
-%
-(0,0)*+{\xi};
-%
-(-35,-14)*+{\rho};
-(-28,-14)="-4";
-(-14,-14)*+{\bullet}="-2";
-(-7,-7)*+{\bullet}="-1";
-(7,-7)*+{\bullet}="1";
-(14,-14)*+{\bullet}="2";
-(28,-14)="4";
-%
-{\ar@{~} "-14";"-12"};
-{\ar "-12";"-11"};
-{\ar@{~} "-11";"11"};
-{\ar "12";"11"};
-{\ar@{~} "12";"14"};
-%
-{\ar@/_.3pc/@{-} (-30,15);(-30,6)};
-{\ar@/^.3pc/@{-} (-9,15);(-9,6)};
-%
-{\ar@/^.3pc/@{-} (30,15);(30,6)};
-{\ar@/_.3pc/@{-} (9,15);(9,6)};
-%
-{\ar@/^.3pc/@{-} (-30,-15);(-30,-6)};
-{\ar@/_.3pc/@{-} (-9,-15);(-9,-6)};
-%
-{\ar@/_.3pc/@{-} (30,-15);(30,-6)};
-{\ar@/^.3pc/@{-} (9,-15);(9,-6)};
-%
-{\ar@{~} "-4";"-2"};
-{\ar "-1";"-2"};
-{\ar@{~} "-1";"1"};
-{\ar "1";"2"};
-{\ar@{~} "2";"4"};
-%
-\endxy
-\]
-	\caption{The string~$\rho$ dances with~$\rho'$, as in Definition~\ref{definition: dance and attract} (ii).}
-	\label{fig:def-dances}
-\end{figure}
-
-\begin{figure}[t]
- 	\capstart
-\[
-\xy
-%
-(-35,14)*+{\rho'};
-(-28,14)="-14";
-(-14,14)*+{\bullet}="-12";
-(-7,7)*+{\bullet}="-11";
-(7,7)*+{\bullet}="11";
-%
-(-14,7)*+{\textcolor{blue}{\bullet}}="a";
-(-7,0)*+{\textcolor{blue}{\bullet}}="b";
-(7,0)*+{\textcolor{blue}{\bullet}}="c";
-(14,-7)*+{\textcolor{blue}{\bullet}}="d";
-%
-(-35,-14)*+{\rho};
-(-28,-14)="-4";
-(-14,-14)*+{\bullet}="-2";
-(-7,-7)*+{\bullet}="-1";
-(7,-7)*+{\bullet}="1";
-(14,-14)*+{\bullet}="2";
-(28,-14)="4";
-%
-{\ar@{~} "-14";"-12"};
-{\ar^\alpha "-12";"-11"};
-{\ar@{~} "-11";"11"};
-%
-{\ar@/^.3pc/@{-} (-30,-15);(-30,-6)};
-{\ar@/_.3pc/@{-} (-9,-15);(-9,-6)};
-%
-{\ar@{~} "-4";"-2"};
-{\ar "-1";"-2"};
-{\ar@{~} "-1";"1"};
-{\ar_\beta "1";"2"};
-{\ar@{~} "2";"4"};
-%
-{\textcolor{blue}{\ar_\alpha "a";"b"}};
-{\textcolor{blue}{\ar@{~} "b";"c"}};
-{\textcolor{blue}{\ar^\beta "c";"d"}};
-%
-\endxy
-\]
-	\caption{The swinging arms condition, as in Definition~\ref{definition: dance and attract} (ii).}
-	\label{fig: swinging arms}
-\end{figure}
 \end{definition}
@@
 
-\begin{proposition}
-\label{proposition: attract or dance and tau compatibility}
-Let~$\rho$ and~$\rho'$ be two almost positive strings for the string algebra~$A$ and let~$M(\rho)$ and~$M(\rho')$ be the associated string modules.
-Then~$\Hom{A} \big( M(\rho), \tau M(\rho') \big) \ne 0$ if and only if~$\rho$ attracts~$\rho'$ or dances with~$\rho'$.
-\end{proposition}
-
-\begin{proof}
-The case where $\rho$ or~$\rho'$ is a negative simple string directly follows from Definition~\ref{def:negativeSimpleDance} and Notation~\ref{not:explanationNegativeSimpleDance}.
-We therefore assume that~$\rho$ and~$\rho'$ are positive strings.
-We let~$\rho''$ be the string corresponding to~$\tau M(\rho')$ obtained from~$\rho'$ by the rules of Theorem~\ref{theorem: tau for strings}.
-
-Assume first that~$\rho$ attracts~$\rho'$ (Figure~\ref{fig:rho attracts rho'}), and let~$\alpha$ be as in Definition~\ref{definition: dance and attract}.
-Since~$\rho'$ does not start in a deep,~$\rho''$ starts at some substring~$\alpha_1\cdots\alpha_r$, where~$\alpha_r\cdots\alpha_1\alpha^{-1}$ is the cohook at the start of~$\rho'$.
-Let~$0\leq k\leq r$ be maximal such that~$\alpha_k\cdots\alpha_1$ is a substring (possibly a vertex if $k=0$) of~$\rho$ ending in~$u$, where~$u$ is as in Definition~\ref{definition: dance and attract}.
-By definition of a cohook,~$\alpha_k\cdots\alpha_1$ has to be on top of~$\rho$, and is at the bottom of~$\rho''$.
-By Proposition~\ref{prop:morphismsStringModules}, this implies the existence of a non-zero morphism from~$M(\rho)$ to~$M(\rho'') = \tau M(\rho')$.
-
-\begin{figure}[h]
+\begin{figure}[t]
+ 	\capstart
+% 	\centerline{
 \[
@@
 %
-(7,14)="peak";
-%
-(0,7)*+{\rho''}="10";
 (28,7)*+{v}="14";
 (42,7)="16";
-%
+(49,7)*+{\rho'}="17";
+%
+(0,0)*+{\rho}="0";
+(7,0)="1";
 (21,0)*+{u}="3";
 %
-(0,-7)*+{\rho}="-0";
-(7,-7)="-1";
-(21,-7)*+{u}="-3";
-%
-(28,-14)*+{\bullet}="-14";
-(42,-14)="-16";
-%
-{\ar@{~} "-1";"-3"};
-{\ar "-3";"-14"};
-{\ar@{~} "-14";"-16"};
+(28,-7)*+{\bullet}="-4";
+(42,-7)="-6";
+%
+{\ar@{~} "1";"3"};
+{\ar "3";"-4"};
+{\ar@{~} "-4";"-6"};
 %
@@
 %
-{\ar^{\alpha} "14";"3"};
-{\ar@{-} "peak";"3"};
-%
-{\ar@/_.3pc/@{-} (23,9);(23,0)};
-{\ar@/^.3pc/@{-} (44,9);(44,0)};
-%
-{\ar@/_.3pc/@{-} (23,-7);(23,-16)};
-{\ar@/^.3pc/@{-} (44,-7);(44,-16)};
+{\ar@{..>}_{\alpha} "14";"3"};
+%
+{\ar@/_.3pc/@{-} (23,0);(23,-9)};
+{\ar@/^.3pc/@{-} (44,0);(44,-9)};
 %
@@
 \]
-    \caption{If the string~$\rho$ attracts~$\rho'$, then~$\rho''$ is of the form given above.}
-    \vspace{-.5cm}
-    \label{fig:rho attracts rho'}
+% 		    }
+	\caption{The string~$\rho$ attracts~$\rho'$, as in Definition~\ref{definition: dance and attract} (i).}
+	\label{fig:def-attracts}
 \end{figure}
 
-Assume now that~$\rho$ dances with~$\rho'$, and let~$\xi$ be as in Definition~\ref{definition: dance and attract}.
-We distinguish four cases:
-
-\begin{enumerate}[(a)]
-\item If~$\rho'=\xi$ (see Figure~\ref{fig:dance case a}).
-Then~$\rho'$ does not start and does not end in a deep so that ${\rho''= \alpha_r\cdots\alpha_1\alpha^{-1}\rho'\beta\beta_1^{-1}\cdots\beta_s^{-1}}$, where~$\alpha_r\cdots\alpha_1\alpha^{-1}$ and~$\beta\beta_1^{-1}\cdots\beta_s^{-1}$ are cohooks for~$\rho'$.
- By assumption, ~$\alpha^{-1}\rho'\beta$ is a substring of~$\rho$.
-Let~$0\leq i\leq r$ and~$0\leq j\leq s$ be maximal such that~$\alpha_i\cdots\alpha_1\alpha^{-1}\rho'\beta\beta_1^{-1}\cdots\beta_j^{-1}~$ is a substring of~$\rho$.
- This substring is on top of~$\rho$ and at the bottom of~$\rho''$, which shows that~$\Hom{A} \big( M(\rho), \tau M(\rho') \big) \ne 0$ by Proposition~\ref{prop:morphismsStringModules}.
-
-\begin{figure}[h]
- 	\capstart
-\[
-\xy
-%
-(7,14)="lpeak";
-(63,14)="rpeak";
-%
-(0,7)*+{\rho''}="10";
-(28,7)="14";
-(42,7)="16";
-%
-(21,0)="3";
-(49,0)="7";
-%
-{\ar@{~}^{\rho'} "14";"16"};
-%
-{\ar^{\alpha} "14";"3"};
-{\ar@{-} "lpeak";"3"};
-%
-{\ar_{\beta} "16";"7"};
-{\ar@{-} "rpeak";"7"};
-%
-\endxy
-\]
-    \caption{The string~$\rho''$, when~$\rho$ dances with~$\rho'$ and~$\rho'=\xi$ as in case (a).}
-    \vspace{-.5cm}
-    \label{fig:dance case a}
-\end{figure}
-
-\item If there are arrows~$\alpha, \beta$ such that~$\alpha\xi\beta^{-1}$ is a substring of~$\rho'$ (see Figure~\ref{fig:dance case b}).
- Then~$\rho''$ contains~$(\alpha)\xi(\beta^{-1})$ where the brackets have to be understood as follows:~$\rho''$ either contains~$\xi\beta^{-1}$ or ends in~$\xi$ and either contains~$\alpha\xi$ or starts at~$\xi$.
- In any case,~$\xi$ is at the bottom of~$\rho''$.
-Since~$\xi$ is at the top of~$\rho$ by assumption, we have~$\Hom{A} \big( M(\rho), \tau M(\rho') \big)\neq 0$ by Proposition~\ref{prop:morphismsStringModules}.
-
-\begin{figure}[h]
+\begin{figure}[t]
  	\capstart
@@
 %
+(0,0)*+{\xi};
+%
+(-35,-14)*+{\rho};
+(-28,-14)="-4";
+(-14,-14)*+{\bullet}="-2";
+(-7,-7)*+{\bullet}="-1";
+(7,-7)*+{\bullet}="1";
+(14,-14)*+{\bullet}="2";
+(28,-14)="4";
+%
+{\ar@{~} "-14";"-12"};
+{\ar "-12";"-11"};
+{\ar@{~} "-11";"11"};
+{\ar "12";"11"};
+{\ar@{~} "12";"14"};
+%
+{\ar@/_.3pc/@{-} (-30,15);(-30,6)};
+{\ar@/^.3pc/@{-} (-9,15);(-9,6)};
+%
+{\ar@/^.3pc/@{-} (30,15);(30,6)};
+{\ar@/_.3pc/@{-} (9,15);(9,6)};
+%
+{\ar@/^.3pc/@{-} (-30,-15);(-30,-6)};
+{\ar@/_.3pc/@{-} (-9,-15);(-9,-6)};
+%
+{\ar@/_.3pc/@{-} (30,-15);(30,-6)};
+{\ar@/^.3pc/@{-} (9,-15);(9,-6)};
+%
+{\ar@{~} "-4";"-2"};
+{\ar "-1";"-2"};
+{\ar@{~} "-1";"1"};
+{\ar "1";"2"};
+{\ar@{~} "2";"4"};
+%
+\endxy
+\]
+	\caption{The string~$\rho$ dances with~$\rho'$, as in Definition~\ref{definition: dance and attract} (ii).}
+	\label{fig:def-dances}
+\end{figure}
+
+\begin{figure}[t]
+ 	\capstart
+\[
+\xy
+%
+(-35,14)*+{\rho'};
+(-28,14)="-14";
+(-14,14)*+{\bullet}="-12";
+(-7,7)*+{\bullet}="-11";
+(7,7)*+{\bullet}="11";
+%
+(-14,7)*+{\textcolor{blue}{\bullet}}="a";
+(-7,0)*+{\textcolor{blue}{\bullet}}="b";
+(7,0)*+{\textcolor{blue}{\bullet}}="c";
+(14,-7)*+{\textcolor{blue}{\bullet}}="d";
+%
+(-35,-14)*+{\rho};
+(-28,-14)="-4";
+(-14,-14)*+{\bullet}="-2";
+(-7,-7)*+{\bullet}="-1";
+(7,-7)*+{\bullet}="1";
+(14,-14)*+{\bullet}="2";
+(28,-14)="4";
+%
+{\ar@{~} "-14";"-12"};
+{\ar^\alpha "-12";"-11"};
+{\ar@{~} "-11";"11"};
+%
+{\ar@/^.3pc/@{-} (-30,-15);(-30,-6)};
+{\ar@/_.3pc/@{-} (-9,-15);(-9,-6)};
+%
+{\ar@{~} "-4";"-2"};
+{\ar "-1";"-2"};
+{\ar@{~} "-1";"1"};
+{\ar_\beta "1";"2"};
+{\ar@{~} "2";"4"};
+%
+{\textcolor{blue}{\ar_\alpha "a";"b"}};
+{\textcolor{blue}{\ar@{~} "b";"c"}};
+{\textcolor{blue}{\ar^\beta "c";"d"}};
+%
+\endxy
+\]
+	\caption{The swinging arms condition, as in Definition~\ref{definition: dance and attract} (ii).}
+	\label{fig: swinging arms}
+\end{figure}
+
+\enlargethispage{.5cm}
+
+\begin{proposition}
+\label{proposition: attract or dance and tau compatibility}
+Let~$\rho$ and~$\rho'$ be two almost positive strings for the string algebra~$A$ and let~$M(\rho)$ and~$M(\rho')$ be the associated string modules.
+Then \[\Hom{A} \big( M(\rho), \tau M(\rho') \big) \ne 0\] if and only if~$\rho$ attracts~$\rho'$ or dances with~$\rho'$.
+\end{proposition}
+
+\begin{proof}
+The case where $\rho$ or~$\rho'$ is a negative simple string directly follows from Definition~\ref{def:negativeSimpleDance} and Notation~\ref{not:explanationNegativeSimpleDance}.
+We therefore assume that~$\rho$ and~$\rho'$ are positive strings.
+We let~$\rho''$ be the string corresponding to~$\tau M(\rho')$ obtained from~$\rho'$ by the rules of Theorem~\ref{theorem: tau for strings}.
+
+Assume first that~$\rho$ attracts~$\rho'$ (Figure~\ref{fig:rho attracts rho'}), and let~$\alpha$ be as in Definition~\ref{definition: dance and attract}.
+Since~$\rho'$ does not start in a deep,~$\rho''$ starts at a substring~$\alpha_1\cdots\alpha_r$, where~$\alpha_r\cdots\alpha_1\alpha^{-1}$ is the cohook at the start of~$\rho'$.
+Let~$0\leq k\leq r$ be maximal such that~$\alpha_k\cdots\alpha_1$ is a substring (possibly a vertex if $k=0$) of~$\rho$ ending in~$u$, where~$u$ is as in Definition~\ref{definition: dance and attract}.
+By definition of a cohook,~$\alpha_k\cdots\alpha_1$ has to be on top of~$\rho$, and is at the bottom of~$\rho''$.
+By Proposition~\ref{prop:morphismsStringModules}, this implies the existence of a non-zero morphism from~$M(\rho)$ to~$M(\rho'') = \tau M(\rho')$.
+
+\begin{figure}[h]
+\[
+\xy
+%
+(7,14)="peak";
+%
+(0,7)*+{\rho''}="10";
+(28,7)*+{v}="14";
+(42,7)="16";
+%
+(21,0)*+{u}="3";
+%
+(0,-7)*+{\rho}="-0";
+(7,-7)="-1";
+(21,-7)*+{u}="-3";
+%
+(28,-14)*+{\bullet}="-14";
+(42,-14)="-16";
+%
+{\ar@{~} "-1";"-3"};
+{\ar "-3";"-14"};
+{\ar@{~} "-14";"-16"};
+%
+{\ar@{~} "14";"16"};
+%
+{\ar^{\alpha} "14";"3"};
+{\ar@{-} "peak";"3"};
+%
+{\ar@/_.3pc/@{-} (23,9);(23,0)};
+{\ar@/^.3pc/@{-} (44,9);(44,0)};
+%
+{\ar@/_.3pc/@{-} (23,-7);(23,-16)};
+{\ar@/^.3pc/@{-} (44,-7);(44,-16)};
+%
+\endxy
+\]
+    \caption{If the string~$\rho$ attracts~$\rho'$, then~$\rho''$ is of the form given above.}
+    \vspace{-.5cm}
+    \label{fig:rho attracts rho'}
+\end{figure}
+
+Assume now that~$\rho$ dances with~$\rho'$, and let~$\xi$ be as in Definition~\ref{definition: dance and attract}.
+We distinguish four cases:
+
+\begin{enumerate}[(a)]
+\item If~$\rho'=\xi$ (see Figure~\ref{fig:dance case a}).
+Then~$\rho'$ does not start and does not end in a deep so that ${\rho''= \alpha_r\cdots\alpha_1\alpha^{-1}\rho'\beta\beta_1^{-1}\cdots\beta_s^{-1}}$, where~$\alpha_r\cdots\alpha_1\alpha^{-1}$ and~$\beta\beta_1^{-1}\cdots\beta_s^{-1}$ are cohooks for~$\rho'$.
+ By assumption, ~$\alpha^{-1}\rho'\beta$ is a substring of~$\rho$.
+Let~$0\leq i\leq r$ and~$0\leq j\leq s$ be maximal such that~$\alpha_i\cdots\alpha_1\alpha^{-1}\rho'\beta\beta_1^{-1}\cdots\beta_j^{-1}~$ is a substring of~$\rho$.
+ This substring is on top of~$\rho$ and at the bottom of~$\rho''$, which shows that~$\Hom{A} \big( M(\rho), \tau M(\rho') \big) \ne 0$ by Proposition~\ref{prop:morphismsStringModules}.
+
+\begin{figure}[h]
+ 	\capstart
+\[
+\xy
+%
+(7,14)="lpeak";
+(63,14)="rpeak";
+%
+(0,7)*+{\rho''}="10";
+(28,7)="14";
+(42,7)="16";
+%
+(21,0)="3";
+(49,0)="7";
+%
+{\ar@{~}^{\rho'} "14";"16"};
+%
+{\ar^{\alpha} "14";"3"};
+{\ar@{-} "lpeak";"3"};
+%
+{\ar_{\beta} "16";"7"};
+{\ar@{-} "rpeak";"7"};
+%
+\endxy
+\]
+    \caption{The string~$\rho''$, when~$\rho$ dances with~$\rho'$ and~$\rho'=\xi$ as in case (a).}
+    \vspace{-.5cm}
+    \label{fig:dance case a}
+\end{figure}
+
+\item If there are arrows~$\alpha, \beta$ such that~$\alpha\xi\beta^{-1}$ is a substring of~$\rho'$ (see Figure~\ref{fig:dance case b}).
+ Then~$\rho''$ contains~$(\alpha)\xi(\beta^{-1})$ where the brackets have to be understood as follows:~$\rho''$ either contains~$\xi\beta^{-1}$ or ends in~$\xi$ and either contains~$\alpha\xi$ or starts at~$\xi$.
+ In any case,~$\xi$ is at the bottom of~$\rho''$.
+Since~$\xi$ is at the top of~$\rho$ by assumption, we have~$\Hom{A} \big( M(\rho), \tau M(\rho') \big)\neq 0$ by Proposition~\ref{prop:morphismsStringModules}.
+
+\begin{figure}[h]
+ 	\capstart
+\[
+\xy
+%
+(-35,14)*+{\rho'};
+(-28,14)="-14";
+(-14,14)*+{\bullet}="-12";
+(-7,7)*+{\bullet}="-11";
+(7,7)*+{\bullet}="11";
+(14,14)*+{\bullet}="12";
+(28,14)="14";
+%
 {\ar@{~} "-14";"-12"};
@@
 \]
-    \caption{When~$\rho$ dances with~$\rho'$ and~$\rho'$ contains a substring~$\alpha\xi\beta^{-1}$ as in case (b).}
+    \caption{When~$\rho$ dances with~$\rho'$ and~$\rho'$ contains a substring~$\alpha\xi\beta^{-1}$ as in case~(b).}
     \vspace{-.5cm}
@@
 
-\item If~$\rho'$ is of the form~$\sigma\alpha\xi$, then~$(\rho')^{-1}$ is as in case (c), so that~$\Hom{A} \big( M(\rho), \tau M(\rho') \big) \ne 0$.
+\item If~$\rho'$ is of the form~$\sigma\alpha\xi$, then~$(\rho')^{-1}$ is as in (c), and~$\Hom{A} \big( M(\rho), \tau M(\rho') \big) \ne 0$.
 \end{enumerate}
@@
     \caption{When~$\Hom{A} \big( M(\rho), \tau M(\rho') \big) \ne 0$, case (a).}
+    \vspace{-.5cm}
     \label{fig:not tau compatible case a}
@@
     \caption{Case (c1): the string~$\nu$ intersects exactly one cohook.}
+    \vspace{-.5cm}
     \label{fig: not tau compatible case c1}
-    \vspace{-.3cm}
 \end{figure}
@@
     \caption{Case (c2): the string~$\nu$ intersects two cohooks.}
+    \vspace{-.5cm}
     \label{fig: not tau compatible case c2}
@@
 %
-\vspace*{-1.2cm}
 \qedhere
@@
     \caption{A substring~$\xi$ at the bottom of~$\rho''$ which is also a substring of~$\rho$.}
+    \vspace{-.5cm}
     \label{fig: xi equals nu}
-    \vspace{-.3cm}
 \end{figure}
@@
 
-\begin{figure}[h]
+%\captionsetup{width=1.1\textwidth}
+%\hvFloat[floatPos=p, capWidth=h, capPos=r, capAngle=90, objectAngle=90, capVPos=c, objectPos=c]{figure}
+%{\begin{minipage}{cm}\vspace*{-1.5cm}\includegraphics[scale=.5]{exmtTC}\end{minipage}}
+%{The support $\tau$-tilting complex~$\tTC$ (left) and its dual graph (right).
+The string module~$M(\rho)$ is represented by the string~$\rho$ of~$\bar Q$ and the preprojective module~$P(v)[1]$ is represented by a hollow vertex at~$v$.}
+%{fig:exmtTC}
+%\captionsetup{width=\textwidth}
+
+\begin{figure}[p]
 	\capstart
@@
 A gentle bound quiver~$\bar Q\ex$ and its blossoming gentle bound quiver~$\bar Q\ex\blossom$ are represented in \fref{fig:exmBlossomingQuiver}.
-\vspace*{-.4cm}
-
-\begin{figure}[h]
+\end{example}
+
+The following lemma is immediate and left to the reader.
+See \fref{fig:exmBlossomingQuiver}.
+
+\begin{lemma}
+The number of vertices and arrows of the blossoming quiver~$Q\blossom$ are given by
+\[
+|Q\blossom_0| = |Q_0| + 2\Delta = 5|Q_0|-2|Q_1|
+\qquad\text{while}\qquad
+|Q\blossom_1| = |Q_1| + 2\Delta = 4|Q_0|-|Q_1|,
+\]
+where
+\[
+\Delta \eqdef 2|Q_0| - |Q_1| = \frac{1}{2} \sum_{v \in Q_0} \big( 4-\deg(v) \big) = \sum_{v \in Q_0} \big( 2-\indeg(v) \big) = \sum_{v \in Q_0} \big( 2-\outdeg(v) \big)
+\]
+is the number of incoming (or equivalently outgoing) blossom arrows of~$\bar Q\blossom$.
+\end{lemma}
+
+\begin{figure}[t]
 	\capstart
-	\centerline{\includegraphics[scale=.7]{exmBlossomingQuiver}}
+	\centerline{\includegraphics[scale=.6]{exmBlossomingQuiver}}
 	\caption{A gentle bound quiver~$\bar Q\ex$~(left) and its blossoming gentle bound quiver~$\bar Q\blossom\ex$~(right). Blossom vertices are white and blossom edges are thin.}
@@
 \end{figure}
-\end{example}
-
-The following lemma is immediate and left to the reader.
-See \fref{fig:exmBlossomingQuiver} for an example.
-
-\begin{lemma}
-The number of vertices and arrows of the blossoming quiver~$Q\blossom$ are given by
-\[
-|Q\blossom_0| = |Q_0| + 2\Delta = 5|Q_0|-2|Q_1|
-\qquad\text{while}\qquad
-|Q\blossom_1| = |Q_1| + 2\Delta = 4|Q_0|-|Q_1|,
-\]
-where
-\[
-\Delta \eqdef 2|Q_0| - |Q_1| = \frac{1}{2} \sum_{v \in Q_0} \big( 4-\deg(v) \big) = \sum_{v \in Q_0} \big( 2-\indeg(v) \big) = \sum_{v \in Q_0} \big( 2-\outdeg(v) \big)
-\]
-is the number of incoming (or equivalently outgoing) blossom arrows of~$\bar Q\blossom$.
-\end{lemma}
 
@@
 \begin{example}
-\fref{fig:exmFacet} shows many examples of walks on the gentle quiver~$\bar Q\ex$ of \fref{fig:exmBlossomingQuiver}.
+\fref{fig:exmFacet} shows examples of walks on the gentle quiver~$\bar Q\ex$ of \fref{fig:exmBlossomingQuiver}.
 \end{example}
@@
 
-\begin{definition}
-\label{def: deep walk}
+\begin{definition}\label{def: deep walk}
 A \defn{peak walk} (resp.~\defn{deep walk}) is a walk that switches orientation only once, at a peak (resp.~deep).
@@
 \label{rem:reverseBlossomingQuiver}
-Observe that blossoming and reversing commute:~$(\reversed{\bar Q})\blossom = \reversed{(\bar Q\blossom)}$.
+Note that blossoming and reversing commute:~$(\reversed{\bar Q})\blossom = \reversed{(\bar Q\blossom)}$.
 In particular, the undirected walks in~$\bar Q$ coincide with the undirected walks in~$\reversed{\bar Q}$.
-However, bottom and top substrings are reversed: $\Sigma_\bottom(\reversed{\omega}) = \reversed{\big( \Sigma_\top(\omega) \big)}$ and~$\Sigma_\top(\reversed{\omega}) = \reversed{\big( \Sigma_\bottom(\omega) \big)}$.
+However, bottom and top substrings are reversed: $\Sigma_\bottom(\reversed{\omega}) = \reversed{\big( \Sigma_\top(\omega) \big)}$ and $\Sigma_\top(\reversed{\omega}) = \reversed{\big( \Sigma_\bottom(\omega) \big)}$.
 \end{remark}
@@
 
-\begin{figure}[b]
+\begin{figure}[t]
 	\capstart
@@
 
-\enlargethispage{.2cm}
 Throughout the paper, we will illustrate our results with two specific families of gentle bound quivers:
@@
 \para{Grid quivers}
-The following is motivated by the works of T.~K.~Petersen, P.~Pylyavskyy and D.~Speyer for staircase shapes~\cite{PetersenPylyavskyySpeyer}, of F.~Santos, C.~Stump and V.~Welker on Grassmann associahedra~\cite{SantosStumpWelker}, and of T.~McConville~\cite{McConville} and A.~Garver and T.~McConville~\cite{GarverMcConville-grid} for arbitrary grid bound quivers.
+The following is motivated by the works of T.~K.~Petersen, P.~Pylya\-vskyy and D.~Speyer for staircase shapes~\cite{PetersenPylyavskyySpeyer}, of F.~Santos, C.~Stump and V.~Welker on Grassmann associahedra~\cite{SantosStumpWelker}, and of T.~McConville~\cite{McConville} and A.~Garver and T.~McConville~\cite{GarverMcConville-grid} for arbitrary grid bound quivers.
 Consider a connected subset~$L$ of the integer grid~$\Z^2$.
@@
 	\capstart
-	\centerline{\includegraphics[scale=1.4]{exmBijectionAssociahedron}}
-	\caption{An oriented path~$\bar Q\pa$ is simultaneously a triangulation and a grid bound quiver (left).
-A facet of the reduced non-kissing complex~$\RNKC[\bar Q\pa]$ can be seen equivalently as a triangulation or as a collection of non-kissing south-east paths (right).}
+	\centerline{\includegraphics[scale=1.5]{exmBijectionAssociahedron}}
+	\caption{An oriented path~$\bar Q\pa$ is simultaneously a triangulation and a grid bound quiver (top).
+A facet of the reduced non-kissing complex~$\RNKC[\bar Q\pa]$ can be seen as a triangulation or as a collection of non-kissing south-east paths (bottom).}
 	\label{fig:exmBijectionAssociahedron}
@@
 Let~$\omega,\omega' \in \walks^\pm(\bar Q)$ be two undirected walks on~$\bar Q$.
-We say that~$\omega$ \defn{kisses}~$\omega'$ if~$\Sigma_\top(\omega) \cap \Sigma_\bottom(\omega') \ne \varnothing$, \ie if there exist a common substring~$\sigma \in \strings^\pm(\bar Q)$ of~$\omega$ and~$\omega'$ such that the arrows of~$\omega$ incident to~$\sigma$ are both outgoing while the arrows of~$\omega'$ incident to~$\sigma$ are both incoming.
+We say that~$\omega$ \defn{kisses}~$\omega'$ if~$\Sigma_\top(\omega) \cap \Sigma_\bottom(\omega') \ne \varnothing$, \ie if there exist a common substring~${\sigma \in \strings^\pm(\bar Q)}$ of~$\omega$ and~$\omega'$ such that the arrows of~$\omega$ incident to~$\sigma$ are both outgoing while the arrows of~$\omega'$ incident to~$\sigma$ are both incoming.
 We say that~$\omega$ and~$\omega'$ are \defn{kissing} if~$\omega$ kisses~$\omega'$ or~$\omega'$ kisses~$\omega$ (or both).
@@
 Observe also that~$\omega$ can kiss~$\omega'$ several times, that~$\omega$ and~$\omega'$ can mutually kiss, and that~$\omega$ can kiss itself.
-We denote by~$\NKWalks(\bar Q)$ the walks on~$\bar Q$ which are not self-kissing and by~$\NKWalks^\pm(\bar Q) \eqdef \set{\{\omega, \omega^{-1}\}}{\omega \in \NKWalks(\bar Q)}$ their undirected version.
+We let~$\NKWalks(\bar Q)$ be the set of walks on~$\bar Q$ which are not self-kissing and~$\NKWalks^\pm(\bar Q) \eqdef \set{\{\omega, \omega^{-1}\}}{\omega \in \NKWalks(\bar Q)}$ their undirected version.
 
@@
 \begin{example}
-\fref{fig:exmFacet}~(left) provides examples of kissing and non-kissing walks.
+\fref{fig:exmFacet}~(left) gives examples of kissing and non-kissing walks.
 %
@@
 	\capstart
-	\centerline{\includegraphics[scale=.7]{exmFacet}}
+	\centerline{\includegraphics[scale=.6]{exmFacet}}
 	\caption{(Left) Three walks on the quiver~$\bar Q\ex$ of \fref{fig:exmBlossomingQuiver}: the dotted red and orange walks are non-kissing, but both kiss the plain blue walk.
@@
 \begin{example}
-On the schematic illustration of \fref{fig:kissingCrossing}\,(right), the walks~$\mu$ and~$\nu$ are non-kissing and for the walks~$\mu_\star, \nu_\star$ marked at~$\gamma$ (resp.~at~$\delta$), we have~$\mu_\star \prec_\gamma \nu_\star$ (resp.~$\nu_\star \prec_\delta \mu_\star$).
+On the schematic illustration of \fref{fig:kissingCrossing}\,(right), the walks~$\mu$ and~$\nu$ are non-kissing and denoting by~$\mu_\star, \nu_\star$ the walks marked at~$\gamma$ (resp.~at~$\delta$), we have~${\mu_\star \prec_\gamma \nu_\star}$ (resp.~$\nu_\star \prec_\delta \mu_\star$).
 \end{example}
@@
 \item is well-defined: if both endpoints of~$\sigma$ are in~$Q_0$, $\mu_\star$ (resp.~$\nu_\star$) should enter and exit~$\sigma$ in the same direction since~$\mu_\star$ and~$\nu_\star$ are non-kissing;
-\item is independent of the orientation of~$\mu_\star$ and~$\nu_\star$:~${\mu_\star \prec_\alpha \nu_\star \!\iff\!
-(\mu_\star)^{-1} \prec_\alpha \nu_\star \!\iff\!
-\mu_\star \prec_\alpha (\nu_\star)^{-1}}$; we thus also consider~$\prec_\alpha$ as a relation on undirected marked walks;
+\item is independent of the orientation of~$\mu_\star$ and~$\nu_\star$:~$\mu_\star \prec_\alpha \nu_\star$ iff $(\mu_\star)^{-1} \prec_\alpha \nu_\star$ iff $\mu_\star \prec_\alpha (\nu_\star)^{-1}$; we thus also consider~$\prec_\alpha$ as a relation on undirected marked walks;
 \item depends on which occurrence of~$\alpha$ is marked on~$\mu$ and~$\nu$.
@@
 Observe that this straight walk is always the minimal marked walk of~$F_\alpha$ for the order~$\prec_\alpha$, since it always agrees with the direction of~$\alpha$.
-On the other hand, \textcolor{red}{ the proposition below shows that} we can consider the maximal marked walk of~$F_\alpha$ for the order~$\prec_\alpha$.
+On the other hand, we can consider the maximal marked walk of~$F_\alpha$ for the order~$\prec_\alpha$.
 Intuitively, it is the most countercurrent walk passing through~$\alpha$ with respect to the direction of~$\alpha$.
-\begin{proposition}\label{prop: nk facets are finite}
-\textcolor{red}{The facets of the non-kissing complex have finite cardinality.}
-\end{proposition}
-
-\begin{proof}\textcolor{red}{
-Let~$F$ be a non-kissing facet.
-Since the quiver~$Q$ has a finite number of arrows, it is enough to prove that each~$F_\alpha$ is finite.
-Assume, by means of contradiction, that there is some~$\alpha\in Q_1$ with~$F_\alpha$ infinite.
-Call ``junction'' a marked occurrence of an arrow~$\beta$ in some~$\omega_\star, \omega'_\star\in F_\alpha$, such that~$\omega$ and~$\omega'$ coincide from their marked occurrence of~$\alpha$ up to~$\beta$ and differ after~$\beta$.
-Since~$F_\alpha$ is infinite, there is an infinite number of junctions.
-Since~$Q_1$ is finite, there are two junctions with the same underlying arrow~$\beta$ and such that either~$\alpha$ points towards both junctions or~$\alpha$ points to the direction opposite to both junctions.
-This shows that there exist three marked walks~$\nu_\star\prec_\alpha \mu_\star\prec_\alpha \lambda_\star\in F_\alpha$ such that~$\lambda, \mu$ and $\nu$ coincide from their marked occurrence of~$\alpha$ up to some marked occurrence~$\beta_1$ of~$\beta$, after which~$\lambda$ differs from~$\mu$ and~$\nu$ but~$\mu$ and~$\nu$ coincide up to some other occurrence~$\beta_2$ of~$\beta$, and then differ (see Figure~\ref{fig: nk facets are finite}).
-Let~$\sigma$ be the longest common substring of~$\lambda$ and~$\nu$ containing~$\beta_1$ and~$\beta_2$ respectively.
-If~$\sigma$ is on top of~$\nu$, then it is at the bottom of~$\lambda$, and~$\lambda$ kisses~$\nu$, which is absurd.
-Otherwise, the subword~$\sigma$ of~$\mu$ containing~$\beta_2$ is at the bottom of~$\mu$ while the subword~$\sigma$ of~$\mu$ containing~$\beta_1$ is at the top of~$\mu$.
-Hence,~$\mu$ kisses itself, which is absurd.}
-\end{proof}
 
 \begin{definition}
-For an arrow~$\alpha \in Q\blossom_1$ and a non-kissing face~$F \in \NKC$ containing the straight walk passing through~$\alpha$, consider the marked walk~$\omega_\star \eqdef \max_{\prec_\alpha} F_\alpha$ and let~$\omega$ be the walk obtained by forgetting the mark in~$\omega_\star$.
+For an arrow~$\alpha \in Q\blossom_1$ and a non-kissing face~$F \in \NKC$ containing the straight walk passing through~$\alpha$, let~$\omega_\star \eqdef \max_{\prec_\alpha} F_\alpha$ and let~$\omega$ be the walk obtained by forgetting the mark in~$\omega_\star$.
 We say that~$\omega$ is the \defn{distinguished walk} of~$F$ at~$\alpha$ and that~$\alpha$ is a \defn{distinguished arrow} on~$\omega \in F$.
@@
 \begin{example}
-For any~$v \in Q_0$, the distinguished arrows of the peak walk~$v_\peak$ in the peak facet~$F_\peak$ are the two outgoing arrows at~$v$, and the distinguished arrows of the deep walk~$v_\deep$ in the deep facet~$F_\deep$ are the two incoming arrows at~$v$.
+For any~$v \in Q_0$, the distinguished arrows of the peak walk~$v_\peak$ in the peak facet~$F_\peak$ are the two outgoing arrows at~$v$, and the distinguished arrows of the deep walk~$v_\deep$ in the deep facet~$F_\deep$ are the two incoming arrows~at~$v$.
 \end{example}
@@
 \label{prop:distinguishedArrows}
-For any non-kissing facet~$F \in \NKC$, each bending (resp.~straight) walk of~$F$ contains precisely~$2$ (resp.~$1$) distinguished arrows in~$F$ pointing in opposite directions (resp.~in the direction~of~the~walk).
+For any non-kissing facet~$F \in \NKC$, each bending (resp.
+straight) walk of~$F$ contains precisely~$2$ (resp.~$1$) distinguished arrows in~$F$ pointing in opposite directions (resp.~in the direction~of~the~walk).
 \end{proposition}
@@
 \label{coro:pure}
-The non-kissing complex~$\NKC$ is pure of dimension~$|Q_0| + \Delta = 3|Q_0|-|Q_1|$. The reduced non-kissing complex~$\RNKC$ is pure of dimension~$|Q_0|$.
+The non-kissing complex~$\NKC$ is pure of dimension $|Q_0| + \Delta = 3|Q_0|-|Q_1|$. The reduced non-kissing complex~$\RNKC$ is pure of dimension~$|Q_0|$.
 \end{corollary}
@@
 2b+s = |Q\blossom_1| = 4|Q_0|-|Q_1|,
-\qquad\text{thus}\qquad
+\quad\text{thus}\quad
 b = |Q_0|
-\qquad\text{and}\qquad
+\quad\text{and}\quad
 b+s = 3|Q_0|-|Q_1|.
@@
 %For any~$v \in Q_1$, the distinguished string of the peak walk~$v_\peak$ in the peak facet~$F_\peak$ is~$v$ and the distinguished string of the peak walk~$v_\peak$ in the peak facet~$F_\peak$ is~$v$.
-For any~$v \in Q_1$, we have~$\distinguishedString{v_\peak}{F_\peak} = \distinguishedString{v_\deep}{F_\deep} = \varepsilon_v$.
+For any~$v \in Q_1$, we have~${\distinguishedString{v_\peak}{F_\peak} = \distinguishedString{v_\deep}{F_\deep} = \varepsilon_v}$.
 \end{example}
@@
 
-\begin{figure}[t]
-	\capstart
-	\centerline{\includegraphics[scale=.7]{exmFlip}}
-	\caption{The flip of the orange walk~$\omega$ in the facet~$F\ex$ of \fref{fig:exmFacet}.
-The other two walks~$\mu, \nu$ of~$F\ex$ involved in the flip are the yellow and green walks.
-The distinguished arrows on each walk of~$F\ex$ are marked with triple arrows.}
-	\label{fig:exmFlip}
-\end{figure}
-
 We now show that the non-kissing complex~$\RNKC$ is \defn{thin}, \ie that any codimension~$1$ non-kissing face of~$\RNKC$ is contained in exactly two non-kissing facets of~$\RNKC$.
@@
 \label{prop:flip}
-Consider a non-kissing facet~$F \in \NKC$ and a bending walk~$\omega \in F$.
+Consider a non-kissing facet~$F \in \NKC$ and a bending walk ${\omega \in F}$.
 Let~$\alpha$ and~$\beta$ be the distinguished arrows of~$\omega$, and~$\sigma$ be the distinguished substring of~$\omega$, which splits~$\omega$ into~$\omega = \rho \sigma \tau$.
@@
 \end{proposition}
+
+\begin{figure}[b]
+	\capstart
+	\centerline{\includegraphics[scale=1]{flip}}
+	\caption{A schematic representation of flips in the non-kissing complex (see Proposition~\ref{prop:flip}).
+The flip exchanges the walk~$\omega = \rho \sigma \tau$ in the facet~$F$ (left) with the walk~$\omega' = \rho' \sigma \tau'$ in the facet~$F'$ (middle), using the walks~$\mu = \rho' \sigma \tau = \distinguishedWalk{\alpha'}{F \ssm \{\omega\}}$ and~$\nu = \rho \sigma \tau' = \distinguishedWalk{\beta'}{F \ssm \{\omega\}}$.
+The walk~$\omega'$ kisses~$\omega$ but no other walk of~$F$~(right).}
+	\label{fig:flip}
+\end{figure}
 
@@
 \[
+\qquad\qquad
 \omega = \distinguishedWalk{\alpha}{F} = \distinguishedWalk{\beta}{F}
-\qquad\text{and}\qquad
+\quad\text{and}\quad
 \omega' = \distinguishedWalk{\alpha'}{F'} = \distinguishedWalk{\beta'}{F'}.
@@
 \[
+\qquad\qquad
 \mu = \nu = \distinguishedWalk{\alpha}{F \ssm \{\omega\}} = \distinguishedWalk{\beta'}{F} = \distinguishedWalk{\beta}{F'}.
@@
 \[
+\qquad\qquad\qquad
 \mu = \distinguishedWalk{\alpha'}{F} = \distinguishedWalk{\beta}{F'}
-\qquad\text{and}\qquad
+\quad\text{and}\quad
 \nu = \distinguishedWalk{\alpha}{F'} = \distinguishedWalk{\beta'}{F}.
@@
 The non-kissing facet~$F' \eqdef F \symdif \{\omega, \omega'\}$ is obtained from~$F$ by the \defn{flip} of~$\omega$.
-We say that the flip is \defn{supported} by the common substring~$\sigma = \distinguishedString{\omega}{F} = \distinguishedString{\omega'}{F'}$ of~$\omega$ and~$\omega'$.
+We say that the flip is \defn{supported} by the common substring $\sigma = \distinguishedString{\omega}{F} = \distinguishedString{\omega'}{F'}$ of~$\omega$ and~$\omega'$.
 The facets~$F$ and~$F'$ are \defn{adjacent facets}.
@@
 
-\begin{figure}[t]
+\begin{figure}[h]
 	\capstart
-	\centerline{\includegraphics[scale=1]{flip}}
-	\caption{A schematic representation of flips in the non-kissing complex (see Proposition~\ref{prop:flip}).
-The flip exchanges the walk~$\omega = \rho \sigma \tau$ in the facet~$F$ (left) with the walk~$\omega' = \rho' \sigma \tau'$ in the facet~$F'$ (middle), using the walks~$\mu = \rho' \sigma \tau = \distinguishedWalk{\alpha'}{F \ssm \{\omega\}}$ and~$\nu = \rho \sigma \tau' = \distinguishedWalk{\beta'}{F \ssm \{\omega\}}$.
-The walk~$\omega'$ kisses~$\omega$ but no other walk of~$F$ (right).}
-	\label{fig:flip}
+	\centerline{\includegraphics[scale=.6]{exmFlip}}
+	\caption{The flip of the orange walk~$\omega$ in the facet~$F\ex$ of \fref{fig:exmFacet}.
+The other two walks~$\mu, \nu$ of~$F\ex$ involved in the flip are the yellow and green walks.
+The distinguished arrows on each walk of~$F\ex$ are marked with triple arrows.}
+	\label{fig:exmFlip}
 \end{figure}
@@
 \label{def:increasingFlip}
-\enlargethispage{.3cm}
 If the common substring~$\sigma$ of~$\omega$ and~$\omega'$ is on top of~$\omega$ and at the bottom of~$\omega'$, then we say that the flip~$F \to F'$ is \defn{increasing} and that the common substring~$\sigma$ is an \defn{ascent} of~$F$ and a \defn{descent} of~$F'$.
-We denote by~$\ascents(F) \subseteq \strings^\pm(\bar Q)$ and $\descents(F) \subseteq \strings^\pm(\bar Q)$ the sets of ascents and descents of~$F$ respectively.
+We denote by ${\ascents(F) \subseteq \strings^\pm(\bar Q)}$ and $\descents(F) \subseteq \strings^\pm(\bar Q)$ the sets of ascents and descents of~$F$ respectively.
 %In the opposite situation, the flip is \defn{decreasing} and~$\sigma$ is a descent of~$F$ and an ascent of~$F'$.
@@
 \label{rem:reverseFlipGraph}
-Reversing all arrows reverses the orientation of the flips: $\NKG[\reversed{\bar Q}] = \reversed{\NKG[\bar Q]}$.
+Reversing all arrows reverses the orientation of the flips: \[\NKG[\reversed{\bar Q}] = \reversed{\NKG[\bar Q]}.\]
 \end{remark}
@@
 	\capstart
-	\centerline{\includegraphics[scale=.4]{exmBijectionStringsWalks1}}
+	\centerline{\includegraphics[scale=.5]{exmBijectionStringsWalks1}}
 	\caption{The inverse bijections~$\sigma$ and~$\omega$ for two specific quivers.}
@@
 
-\begin{enumerate}[(a)]
-\item If~$\xi=\sigma'$, then~$\sigma = \sigma_1\alpha^{-1}\xi\beta\sigma_2$ for some substrings~$\sigma_1,\sigma_2$ and arrows~$\alpha,\beta\in Q_1$.
-As a consequence,~$\omega(\sigma')$ is of the form~$\alpha_r\cdots\alpha_1\alpha^{-1}\sigma'\beta\beta_1^{-1}\cdots\beta_s^{-1}$ for some~$r,s\geq 1$, and cohooks~$\alpha_r\cdots\alpha_1\alpha^{-1}$ and~$\beta\beta_1^{-1}\cdots\beta_s^{-1}$ where~$\alpha_r,\beta_s$ are blossoming.
-There exist~$0\leq i\leq r$ and~$0\leq j\leq s$ such that~$\alpha_i\cdots\alpha_1\alpha^{-1}\xi\beta\beta_1^{-1}\cdots\beta_j^{-1}$ is a substring on top of~$\omega(\sigma)$ (see Figure~\ref{fig: dance case a}).
-Since it is at the bottom of~$\omega(\sigma')$, the walk~$\omega(\sigma)$ kisses~$\omega(\sigma')$.
-
-\item If~$\sigma'$ is of the form~$\sigma'_1\alpha\xi\beta^{-1}\sigma'_2$, then~$\omega(\sigma')$ contains~$\alpha\xi\beta^{-1}$ as a substring.
-Moreover,~$\xi$ being on top of~$\sigma$,~$\omega(\sigma)$ contains some substring of the form~$\gamma^{-1}\xi\delta$.
-This shows that~$\omega(\sigma)$ kisses~$\omega(\sigma')$.
-
-\item If~$\sigma'=\sigma'_1\alpha\xi$ for some substring~$\sigma'_1$ and some arrow~$\alpha$, then~$\sigma$ is of the form~$\sigma=(\sigma_1\gamma^{-1})\xi\beta\sigma_2$, where~$\alpha\xi\beta$ is a string for~$\bar Q$.
-It follows that~$\omega(\sigma)$ kisses~$\omega(\sigma')$ along some substring~$\xi\beta\beta_1^{-1}\cdots\beta_j^{-1}$ (see Figure~\ref{fig: dance case c}), where~$\beta\beta_1^{-1}\cdots\beta_j^{-1}\cdots\beta_s^{-1}$ is a cohook for~$\sigma\blossom$ and~${j>0}$.
-\end{enumerate}
-
-We now assume that $\omega(\sigma)$ kisses $\omega(\sigma')$.
-Let $\xi$ be a substring which is strictly on top of $\omega(\sigma)$ and strictly at the bottom of $\omega(\sigma')$.
-Note that this implies that $\xi$ is also on top of $\sigma$ (but not necessarily strictly on top).
-It is possible to show that $\sigma$ attracts or dances with $\sigma'$ by using the same method as in the proof of Proposition~\ref{proposition: attract or dance and tau compatibility}.
-However, we choose an alternative proof, showing instead that $\Hom{A} \big( M(\sigma), \tau M(\sigma') \big) \ne 0$, which implies the result by Proposition~\ref{proposition: attract or dance and tau compatibility}.
-Write $\omega(\sigma')=\alpha_r \cdots \alpha_1 \alpha^{-1} \sigma' \beta \beta_1^{-1} \cdots \beta_s^{-1}$ where $r,s\geq 0$, and where if $r\geq 1$, $\alpha_r$ is a blossoming arrow and $\alpha_1,\cdots,\alpha_{r-1},\alpha\in Q_1$ while if $r=0$ $\alpha$ is a blossoming arrow; and similarly for $\beta\beta_1^{-1}\cdots\beta_s^{-1}$.
-
-Assume first that $r$ and $s$ are positive.
-Then $\tau M(\sigma')$ is given by the string $\sigma''=\alpha_{r-1} \cdots \alpha_1 \alpha^{-1} \sigma' \beta \beta_1^{-1} \cdots \beta_{s-1}^{-1}$.
-Thus, $\xi$ is at the bottom of $\sigma''$ and $\Hom{A} \big( M(\sigma), \tau M(\sigma') \big) \neq 0$.
-
-Assume that exactly one of $r,s$ equals $0$.
-By symmetry, we may assume that $r=0$, which is equivalent to $\sigma'$ starting in a deep.
-Since $\xi$ is strictly at the bottom of $\alpha^{-1}\sigma'\beta\beta_1^{-1}\cdots\beta_s^{-1}$, it is also strictly at the bottom of $\sigma'\beta\beta_1^{-1}\cdots\beta_s^{-1}$ (see Figure~\ref{fig: r=0}).
-This implies that $\xi$ is at the bottom of $_{h^{-1}}(\sigma'\beta\beta_1^{-1}\cdots\beta_{s-1}^{-1})$, so that $\Hom{A} \big( M(\sigma), \tau M(\sigma') \big) \ne 0$.
-
-\begin{figure}[h]
- 	\capstart
-\[
-\xy
-%
-(-33,16)="-14";
-(-28,21)="-13";
-(-14,21)="-12";
-(-7,14)*+{\bullet}="-11";
-(0,25)*+{\omega(\sigma')};
-(7,14)*+{\bullet}="11";
-(14,7)="12";
-(25,18)="13";
-(30,23)="14";
-%
-{\ar@{~} "-13";"-12"};
-{\ar^{\gamma} "-12";"-11"};
-{\ar@{~}^{\text{ beginning of }\xi} "-11";"11"};
-{\ar_\beta "11";"12"};
-{\ar@{-} "12";"13"};
-{\ar_{\beta_s\blossom} "14";"13"};
-%
-\endxy
-\]
-    \caption{The walk $\omega(\sigma')$ when $r=0$ and $s>0$. The arrow $\gamma$ ``protects'' $\xi$ from being deleted when removing a left hook for $\sigma'$.}
-    \label{fig: r=0}
-\end{figure}
-
-Finally, assume that $r=0$ and $s=0$.
-In that case, $\xi$ is strictly at the bottom of $\sigma'$.
-It is thus at the bottom of $_{h^{-1}}(\sigma')_{h^{-1}}$ and this gives a non-zero morphism in $\Hom{A} \big( M(\sigma), \tau M(\sigma') \big)$.
-\end{proof}
-
-\begin{figure}[p]
+\begin{figure}[t]
 \[
@@
     \caption{The walks~$\omega(\sigma)$ and~$\omega(\sigma')$ when~$\sigma$ dances with~$\sigma'$: case (a).}
-    \vspace{1cm}
+    \vspace{.1cm}
     \label{fig: dance case a}
@@
 
-\begin{figure}[p]
+\begin{figure}[t]
 \[
@@
     \caption{The walks~$\omega(\sigma)$ and~$\omega(\sigma')$ when~$\sigma$ dances with~$\sigma'$: case (b).}
-    \vspace{1cm}
+    \vspace{.1cm}
     \label{fig: dance case b}
@@
 
+\begin{enumerate}[(a)]
+\item If~$\xi=\sigma'$, then~$\sigma = \sigma_1\alpha^{-1}\xi\beta\sigma_2$ for some substrings~$\sigma_1,\sigma_2$ and arrows~${\alpha,\beta\in Q_1}$.
+As a consequence,~$\omega(\sigma')$ is of the form~$\alpha_r\cdots\alpha_1\alpha^{-1}\sigma'\beta\beta_1^{-1}\cdots\beta_s^{-1}$ for~${r,s\geq 1}$, and cohooks~$\alpha_r\cdots\alpha_1\alpha^{-1}$ and~$\beta\beta_1^{-1}\cdots\beta_s^{-1}$ where~$\alpha_r,\beta_s$ are blossoming.
+There exist~$0\leq i\leq r$ and~$0\leq j\leq s$ such that~$\alpha_i\cdots\alpha_1\alpha^{-1}\xi\beta\beta_1^{-1}\cdots\beta_j^{-1}$ is a substring on top of~$\omega(\sigma)$ (see Figure~\ref{fig: dance case a}).
+Since it is at the bottom of~$\omega(\sigma')$, the walk~$\omega(\sigma)$ kisses~$\omega(\sigma')$.
+
+\item If~$\sigma'$ is of the form~$\sigma'_1\alpha\xi\beta^{-1}\sigma'_2$, then~$\omega(\sigma')$ contains~$\alpha\xi\beta^{-1}$ as a substring.
+Moreover,~$\xi$ being on top of~$\sigma$,~$\omega(\sigma)$ contains some substring of the form~$\gamma^{-1}\xi\delta$.
+This shows that~$\omega(\sigma)$ kisses~$\omega(\sigma')$.
+
+\item If~$\sigma'=\sigma'_1\alpha\xi$ for some substring~$\sigma'_1$ and some arrow~$\alpha$, then~$\sigma$ is of the form~$\sigma=(\sigma_1\gamma^{-1})\xi\beta\sigma_2$, where~$\alpha\xi\beta$ is a string for~$\bar Q$.
+It follows that~$\omega(\sigma)$ kisses~$\omega(\sigma')$ along some substring~$\xi\beta\beta_1^{-1}\cdots\beta_j^{-1}$ (see Figure~\ref{fig: dance case c}), where~$\beta\beta_1^{-1}\cdots\beta_j^{-1}\cdots\beta_s^{-1}$ is a cohook for~$\sigma\blossom$ and~${j>0}$.
+\end{enumerate}
+
+We now assume that $\omega(\sigma)$ kisses $\omega(\sigma')$.
+Let $\xi$ be a substring which is strictly on top of $\omega(\sigma)$ and strictly at the bottom of $\omega(\sigma')$.
+Note that this implies that $\xi$ is also on top of $\sigma$ (but not necessarily strictly on top).
+It is possible to show that $\sigma$ attracts or dances with $\sigma'$ by using the same method as in the proof of Proposition~\ref{proposition: attract or dance and tau compatibility}.
+However, we choose an alternative proof, showing instead that $\Hom{A} \big( M(\sigma), \tau M(\sigma') \big) \ne 0$, which implies the result by Proposition~\ref{proposition: attract or dance and tau compatibility}.
+Write $\omega(\sigma')=\alpha_r \cdots \alpha_1 \alpha^{-1} \sigma' \beta \beta_1^{-1} \cdots \beta_s^{-1}$ where $r,s\geq 0$, and where if $r\geq 1$, $\alpha_r$ is a blossoming arrow and $\alpha_1,\cdots,\alpha_{r-1},\alpha\in Q_1$ while if $r=0$ $\alpha$ is a blossoming arrow; and similarly for $\beta\beta_1^{-1}\cdots\beta_s^{-1}$.
+
+Assume first that $r$ and $s$ are positive.
+Then $\tau M(\sigma')$ is given by the string $\sigma''=\alpha_{r-1} \cdots \alpha_1 \alpha^{-1} \sigma' \beta \beta_1^{-1} \cdots \beta_{s-1}^{-1}$.
+Thus, $\xi$ is at the bottom of $\sigma''$ and we have $\Hom{A} \big( M(\sigma), \tau M(\sigma') \big) \neq 0$.
+
+Assume that exactly one of $r,s$ equals $0$.
+By symmetry, we may assume that $r=0$, which is equivalent to $\sigma'$ starting in a deep.
+Since $\xi$ is strictly at the bottom of $\alpha^{-1}\sigma'\beta\beta_1^{-1}\cdots\beta_s^{-1}$, it is also strictly at the bottom of $\sigma'\beta\beta_1^{-1}\cdots\beta_s^{-1}$ (see Figure~\ref{fig: r=0}).
+This implies that $\xi$ is at the bottom of $_{h^{-1}}(\sigma'\beta\beta_1^{-1}\cdots\beta_{s-1}^{-1})$, so that $\Hom{A} \big( M(\sigma), \tau M(\sigma') \big) \ne 0$.
+
+\begin{figure}[h]
+ 	\capstart
+\[
+\xy
+%
+(-33,16)="-14";
+(-28,21)="-13";
+(-14,21)="-12";
+(-7,14)*+{\bullet}="-11";
+(0,25)*+{\omega(\sigma')};
+(7,14)*+{\bullet}="11";
+(14,7)="12";
+(25,18)="13";
+(30,23)="14";
+%
+{\ar@{~} "-13";"-12"};
+{\ar^{\gamma} "-12";"-11"};
+{\ar@{~}^{\text{ beginning of }\xi} "-11";"11"};
+{\ar_\beta "11";"12"};
+{\ar@{-} "12";"13"};
+{\ar_{\beta_s\blossom} "14";"13"};
+%
+\endxy
+\]
+    \caption{The walk $\omega(\sigma')$ when $r=0$ and $s>0$. The arrow $\gamma$ ``protects'' $\xi$ from being deleted when removing a left hook for $\sigma'$.}
+    \label{fig: r=0}
+\end{figure}
+
+Finally, assume that $r=0$ and $s=0$.
+In that case, $\xi$ is strictly at the bottom of $\sigma'$.
+It is thus at the bottom of $_{h^{-1}}(\sigma')_{h^{-1}}$ and this gives a non-zero morphism in $\Hom{A} \big( M(\sigma), \tau M(\sigma') \big)$.
+\end{proof}
+
+\enlargethispage{.5cm}
 We conclude this section with the observation which motivated this paper.
@@
 \item isomorphisms of simplicial complexes between the support $\tau$-tilting complex~$\tTC$ and the non-kissing complex~$\RNKC$,
-\item isomorphisms of oriented graphs between the graph of left mutations in~$\tTC$ and the graph of increasing flips in~$\RNKC$.
+\item isomorphisms of oriented graphs between the graph of left mutations in $\tTC$ and the graph of increasing flips in~$\RNKC$.
 \end{itemize}
@@
 Since the statement is trivially satisfied when~$\omega'$ is a deep walk, we may assume that it is not the case.
-We claim that the representation~$M \big( \sigma(\omega') \big)$ is a quotient of~$M \big( \sigma(\mu) \big) \oplus M \big( \sigma(\nu) \big)$, which implies the statement by~\cite[Def.--Prop.~2.28]{AdachiIyamaReiten}.
+We claim that the representation~$M \big( \sigma(\omega') \big)$ is a quotient of~${M \big( \sigma(\mu) \big) \oplus M \big( \sigma(\nu) \big)}$, which implies the statement by~\mbox{\cite[Def.--Prop.~2.28]{AdachiIyamaReiten}}.
 First note that the distinguished string~$\xi$ is also a substring of~$\omega$ (use~$\alpha$ and~$\beta$).
 We distinguish five cases, depending on which of the distinguished arrows~$\alpha'$ and~$\beta'$ belongs to some cohook in~$\omega'$.
-Assuming first that~$\alpha', \beta'$ both belong to~$\sigma(\omega')$, then there is a short exact sequence~$0\rightarrow M \big( \sigma(\omega) \big) \rightarrow M \big( \sigma(\mu) \big) \oplus M \big( \sigma(\nu) \big) \rightarrow M \big( \sigma(\omega') \big) \rightarrow 0$.
+Assuming first that~$\alpha', \beta'$ both belong to~$\sigma(\omega')$, there is a short exact sequence~$0\rightarrow M \big( \sigma(\omega) \big) \rightarrow M \big( \sigma(\mu) \big) \oplus M \big( \sigma(\nu) \big) \rightarrow M \big( \sigma(\omega') \big) \rightarrow 0$.
 Assume next that~$\alpha'$ belongs to some (left) cohook for~$\omega'$, but that~$\beta'$ belongs to~$\sigma(\omega')$.
@@
 \captionsetup{width=1.5\textwidth}
-\hvFloat[floatPos=h, capWidth=h, capPos=r, capAngle=90, objectAngle=90, capVPos=c, objectPos=c]{figure}
-{\includegraphics[scale=.45]{exmAuslanderReitenQuiver}}
+\hvFloat[floatPos=p, capWidth=h, capPos=r, capAngle=90, objectAngle=90, capVPos=c, objectPos=c]{figure}
+{\begin{minipage}{22cm}\vspace*{-1cm}\includegraphics[scale=.45]{exmAuslanderReitenQuiver}\end{minipage}}
 {The Auslander-Reiten quiver~$\AR$ for two gentle bound quivers on~$3$ vertices.
@@
 
-Consider a finite lattice~$(L,\le,\meet,\join)$ with minimal element~$\hat 0$ and maximal element~$\hat 1$.
+We consider a finite lattice $(L,\le,\meet,\join)$ with minimal element~$\hat 0$ and maximal element~$\hat 1$.
 Denote by~$x \lessdot y$ the \defn{cover relations} in~$L$, \ie $x < y$ such that there is no~$z \in L$ with~$x < z < y$.
@@
 \begin{definition}
-A \defn{join-representation} of~$x \in L$ is a subset~$J \subseteq L$ such that~$x = \bigJoin J$.
+A \defn{join-representation} of~$x \in L$ is a subset~$J \subseteq L$ such that~${x = \bigJoin J}$.
 Such a representation is \defn{irredundant} if~$x \ne \bigJoin J'$ for a strict subset~$J' \subsetneq J$.
@@
 x \join z = y \join z \Longrightarrow x \join z = (x \meet y) \join z
-\qquad\text{and}\qquad
+\quad\text{and}\quad
 x \meet z = y \meet z \Longrightarrow x \meet z = (x \join y) \meet z
@@
 \label{prop:canonicalJoinRepresentation}
-Consider a semi-distributive lattice~$(L,\le,\join,\meet)$. Then
+Let~$(L,\le,\join,\meet)$ be semi-distributive.
 \begin{enumerate}[(i)]
-\item For any cover relation~$x \lessdot y$ in~$L$, there exists a unique join-irreducible~$\ji(x \lessdot y) \in \JI(L)$ such that~$x \join \ji(x \lessdot y) = y$ and~$x \meet \ji(x \lessdot y) = \ji(x \lessdot y)_\star$.
+\item For any cover relation~$x \lessdot y$ in~$L$, there exists a unique join-irreducible ${\ji(x \lessdot y)}$ in $\JI(L)$ such that~$x \join \ji(x \lessdot y) = y$ and~$x \meet \ji(x \lessdot y) = \ji(x \lessdot y)_\star$.
 \item The canonical join-representation of~$y \in L$ is given by
@@
 \label{rem:sublattice}
-For a lattice congruence~$\equiv$ on a lattice~$L$, the subposet of~$L$ induced by~$\projDown(L)$ is automatically a join-sublattice of~$L$, meaning that for any~$x,y \in L$, we have~${\projDown(x) \join \projDown(y) \in \projDown(L)}$.
+For a lattice congruence~$\equiv$ on a lattice~$L$, the subposet of~$L$ induced by~$\projDown(L)$ is automatically a join-sublattice of~$L$, meaning that for any~${x,y \in L}$, we have~${\projDown(x) \join \projDown(y) \in \projDown(L)}$.
 However, $\projDown(L)$ can fail to be a sublattice of~$L$, since it might happen that~$\projDown(x) \meet \projDown(y) \notin \projDown(L)$.
@@
 
-A lattice~$L$ is \defn{distributive} when~$(x \join y) \meet z = (x \meet z) \join (y \meet z)$ for any~$x,y,z \in L$ (which implies as well the dual equality~$(x \meet y) \join z = (x \join z) \meet (y \join z)$).
+A lattice~$L$ is \defn{distributive} when, for any~$x,y,z \in L$,
+\[
+(x \join y) \meet z = (x \meet z) \join (y \meet z)
+\]
+(which implies as well the dual equality~$(x \meet y) \join z = (x \join z) \meet (y \join z)$).
 Birkhoff's representation theorem for distributive lattices affirms that any distributive lattice can be represented as the lattice of order ideals of its subposet~$\JI(L)$ of join-irreducible elements.
@@
 \begin{enumerate}[(i)]
-\item for all~$S,T \in \Bicl{\cS}$ with~$S \subsetneq T$, there exists~$\tau \in T \ssm S$ such that~$S \cup \{\tau\} \in \Bicl{\cS}$, %(ordered by single-step inclusion),
+\item for all~$S,T \in \Bicl{\cS}$ with~$S \subsetneq T$, there is~$\tau \in T \ssm S$ such that~${S \cup \{\tau\} \in \Bicl{\cS}}$, %(ordered by single-step inclusion),
 \item $R \cup \closure{\big((S \cup T) \ssm R\big)} \in \Bicl{\cS}$ for~$R,S,T \in \Bicl{\cS}$ with~$R \subseteq S \cap T$, and
@@
 \begin{example}
-\fref{fig:exmLatticeQuotient}\,(left) illustrates the inclusion poset of biclosed sets~$\Bicl{\bar Q}$ for a specific gentle bound quiver.
+\fref{fig:exmLatticeQuotient}\,(left) shows the inclusion poset of biclosed sets~$\Bicl{\bar Q}$ for a specific gentle bound quiver.
 All posets are represented from bottom to top, with their minimal elements at the bottom and their maximal elements on top.
@@
 
-\enlargethispage{.3cm}
 To get used to the definition and to provide more examples of biclosed sets, let us immediately state the following lemma which will be used repeatedly.
@@
 To prove that it is coclosed, consider~${\tau \in \closure{\Sigma_\bottom(\sigma)}}$.
-There are substrings~$\tau_1, \dots, \tau_{\ell-1} \in \Sigma_\bottom(\sigma)$, arrows~$\alpha_1, \dots, \alpha_{\ell-1} \in Q_1$ and signs~${\varepsilon_1, \dots, \varepsilon_\ell \in \{-1,1\}}$ such that~$\tau = \tau_1 \alpha_1^{\varepsilon_1} \tau_2 \alpha_2^{\varepsilon_2} \cdots \alpha_{\ell-1}^{\varepsilon_{\ell-1}} \tau_\ell$.
+There are substrings~$\tau_1, \dots, \tau_{\ell-1} \in \Sigma_\bottom(\sigma)$, arrows $\alpha_1, \dots, \alpha_{\ell-1} \in Q_1$ and signs~${\varepsilon_1, \dots, \varepsilon_\ell \in \{-1,1\}}$ such that~$\tau = \tau_1 \alpha_1^{\varepsilon_1} \tau_2 \alpha_2^{\varepsilon_2} \cdots \alpha_{\ell-1}^{\varepsilon_{\ell-1}} \tau_\ell$.
 Assume that~$\tau = \tau' \beta^\varepsilon \tau''$ for some strings~$\tau', \tau'' \in \strings(\bar Q)$, an arrow~$\beta \in Q_1$, and a sign~$\varepsilon$.
@@
 \item If~$\varepsilon = -1$, then~$\tau_k'$ is a bottom substring of~$\tau_k$ which is a bottom substring of~$\sigma$, so that~$\tau_k' \in \Sigma_\bottom(\sigma)$ and thus~$\tau' = \tau_1 \alpha_1^{\varepsilon_1} \dots \alpha_{k-1}^{\varepsilon_{k-1}} \tau_k' \in \closure{\Sigma_\bottom(\sigma)}$.
-\item Similarly, if~$\varepsilon = 1$, then~$\tau''_k$ is a bottom substring of~$\tau_k$ which is a bottom substring of~$\sigma$, so that~$\tau_k'' \in \Sigma_\bottom(\sigma)$ and thus~$\tau'' = \tau_k'' \alpha_k^{\varepsilon_k} \dots \alpha_{\ell-1}^{\varepsilon_{\ell-1}} \tau_\ell \in \closure{\Sigma_\bottom(\sigma)}$.
+\item Similarly, if~$\varepsilon = 1$, then~$\tau''_k$ is a bottom substring of~$\tau_k$ which is a bottom substring of~$\sigma$, so that~$\tau_k'' \in \Sigma_\bottom(\sigma)$ and~${\tau'' = \tau_k'' \alpha_k^{\varepsilon_k} \dots \alpha_{\ell-1}^{\varepsilon_{\ell-1}} \tau_\ell \in \closure{\Sigma_\bottom(\sigma)}}$.
 \end{itemize}
 We conclude that~$\closure{\Sigma_\bottom(\sigma)}$ is coclosed, and thus biclosed.
-By Remark~\ref{rem:meetJoinBiclosedSets}, $\closure{\big( \bigcup_{i \in [\ell]} \Sigma_\bottom(\sigma_i) \big)}$ is also biclosed for any~$\sigma_1, \dots, \sigma_\ell \in \strings^\pm(\bar Q)$.
+By Remark~\ref{rem:meetJoinBiclosedSets}, the set $\closure{\big( \bigcup_{i \in [\ell]} \Sigma_\bottom(\sigma_i) \big)}$ is also biclosed for any~$\sigma_1, \dots, \sigma_\ell \in \strings^\pm(\bar Q)$.
 The proof is similar for~$\closure{\Sigma_\top(\sigma)}$ or follows by duality from Remarks~\ref{rem:reverseBlossomingQuiver} and~\ref{rem:reverseBiclosed}.
@@
 We proceed by induction on~$|\strings^\pm(\bar Q) \ssm R|$.
-The property clearly holds if~${R = S = T = \strings^\pm(\bar Q)}$.
+The property clearly holds when $R = S = T = \strings^\pm(\bar Q)$.
 Consider thus~$R,S,T \in \Bicl{\bar Q}$ such that the property holds for any~$R' \supsetneq R$.
@@
 \item[closed] Since~$R \cup \closure{\{\sigma\}}$ and~$R \cup \closure{\{\tau\}}$ are closed, we have~$\rho \circ \zeta \subseteq R$ for any~$\rho \in R$~and~${\zeta \in \{\sigma,\tau\}}$.
-An immediate induction thus shows that~$\rho \circ \zeta_1 \circ \dots \circ \zeta_\ell \subseteq R$ for any~$\zeta_1, \dots, \zeta_\ell \in \{\sigma, \tau\}$.
+An immediate induction therefore shows that $\rho \circ \zeta_1 \circ \dots \circ \zeta_\ell \subseteq R$ for any~$\zeta_1, \dots, \zeta_\ell \in \{\sigma, \tau\}$.
 Therefore, $R \circ \zeta \subseteq R$ for any~$\zeta \in \closure{\{\sigma,\tau\}}$.
@@
 %\end{itemize}
-\[
-\projDown(S) \eqdef \set{\sigma \in \strings^\pm(\bar Q)}{\Sigma_\bottom(\sigma) \subseteq S}
-\qquad\text{and}\qquad
-\projUp(S) \eqdef \set{\sigma \in \strings^\pm(\bar Q)}{\Sigma_\top(\sigma) \cap S \ne \varnothing}.
-\]
+\begin{align*}
+\projDown(S) & \eqdef \set{\sigma \in \strings^\pm(\bar Q)}{\Sigma_\bottom(\sigma) \subseteq S} \\
+\text{and}\quad
+\projUp(S) & \eqdef \set{\sigma \in \strings^\pm(\bar Q)}{\Sigma_\top(\sigma) \cap S \ne \varnothing}.
+\end{align*}
 \end{definition}
@@
 \begin{proof}
+\enlargethispage{.3cm}
 On the one hand, $\strings^\pm(\bar Q) \ssm \projUp(S)$ is the set of strings of~$\strings^\pm(\bar Q)$ with no top substrings contained in~$S$, \ie whose top substrings are all in~$\strings^\pm(\bar Q) \ssm S$.
 On the other hand, ${\projDown(\strings^\pm(\reversed{\bar Q}) \ssm S)}$ is the set of strings of~$\strings^\pm(\reversed{\bar Q})$ whose bottom substrings are all in~$\strings^\pm(\reversed{\bar Q}) \ssm S$.
-Since reversing all arrows preserves the strings but exchanges top with bottom substrings, we conclude that the two sets coincide. 
+Since reversing all arrows preserves the strings but exchanges top with bottom substrings, we obtain that the two sets coincide. 
 \end{proof}
@@
 \end{itemize}
-In both cases, we showed that any bottom substring~$\rho'$ of~$\rho$ belongs to~$S$, so that~$\rho \in \projDown(S)$ and thus~$\projDown(S)$ is closed.
+In both cases, we showed that any bottom substring~$\rho'$ of~$\rho$ belongs to~$S$, so that~${\rho \in \projDown(S)}$ and thus~$\projDown(S)$ is closed.
 
@@
 \label{prop:latticeCongruence}
-The two maps~$\projDown : \Bicl{\bar Q} \to \Bicl{\bar Q}$ and~$\projUp : \Bicl{\bar Q} \to \Bicl{\bar Q}$ satisfy
+The two maps~$\projDown, \projUp : \Bicl{\bar Q} \to \Bicl{\bar Q}$ satisfy
 \begin{enumerate}[(i)]
@@
 
-For~(ii), we already obtain from~(i) and~(iii) that $\projDown(\projDown(S)) \subseteq \projDown(S)$ and~$\projDown(\projUp(S)) \supseteq \projDown(S)$.
+For~(ii), we already obtain from~(i) and~(iii) that $\projDown(\projDown(S)) \subseteq \projDown(S)$ and $\projDown(\projUp(S)) \supseteq \projDown(S)$.
 We then observe that if~$\rho, \sigma, \tau \in \strings^\pm(\bar Q)$ are such that $\rho$ is a bottom substring of~$\sigma$ and~$\sigma$ is a bottom substring of~$\tau$, then~$\rho$ is a bottom substring of~$\tau$.
 This shows that~$\projDown(\projDown(S)) \supseteq \projDown(S)$.
-Finally, we prove that~$\projDown(\projUp(S)) \subseteq \projDown(S)$.
+Finally, we prove that~${\projDown(\projUp(S)) \subseteq \projDown(S)}$.
 By means of contradiction, assume that there exists~${\tau \in \projDown(\projUp(S)) \ssm \projDown(S)}$.
-Since~$\tau \notin \projDown(S)$, there exists a bottom substring~$\sigma$ of~$\tau$ which is not in~$S$.
+Since $\tau \notin \projDown(S)$, there exists a bottom substring~$\sigma$ of~$\tau$ which is not in~$S$.
 We can assume that~$\sigma$ is an inclusion minimal such substring of~$\tau$.
@@
 
-\begin{figure}[t]
-	\capstart
-	\centerline{\includegraphics[width=1.1\textwidth]{exmLatticeQuotient}}
-	\caption{The inclusion lattice of biclosed sets~$\Bicl{\bar Q}$ with congruence classes of~$\equiv$ in blue (left), and the corresponding lattice of increasing flips on facets of~$\NKC$ (right).}
-	\label{fig:exmLatticeQuotient}
-\end{figure}
+\captionsetup{width=1.5\textwidth}
+\hvFloat[floatPos=p, capWidth=h, capPos=r, capAngle=90, objectAngle=90, capVPos=c, objectPos=c]{figure}
+{\includegraphics[scale=.65]{exmLatticeQuotient}}
+{The inclusion lattice of biclosed sets~$\Bicl{\bar Q}$ with congruence classes of~$\equiv$ in blue (left), and the corresponding lattice of increasing flips on facets of~$\NKC$ (right).}
+{fig:exmLatticeQuotient}
+\captionsetup{width=\textwidth}
+
+%\begin{figure}[t]
+%	\capstart
+%	\centerline{\includegraphics[width=1.1\textwidth]{exmLatticeQuotient}}
+%	\caption{The inclusion lattice of biclosed sets~$\Bicl{\bar Q}$ with congruence classes of~$\equiv$ in blue (left), and the corresponding lattice of increasing flips on facets of~$\NKC$ (right).}
+%	\label{fig:exmLatticeQuotient}
+%\end{figure}
 \end{example}
@@
 Therefore,
-\[
-\projDown \bigg( \closure{\Big( \bigcup_{i \in [\ell]} \Sigma_\bottom(\sigma_i) \Big)} \bigg) = \closure{\Big( \bigcup_{i \in [\ell]} \Sigma_\bottom(\sigma_i) \Big)}
-\;\;\text{and}\;\;
-\projUp \bigg( \coclosure{\Big( \bigcap_{i \in [\ell]} \closure{\Sigma_\top(\sigma_i)} \Big)} \bigg) = \coclosure{\Big( \bigcap_{i \in [\ell]} \closure{\Sigma_\top(\sigma_i)} \Big)}
-\]
+\begin{align*}
+& \projDown \bigg( \closure{\Big( \bigcup_{i \in [\ell]} \Sigma_\bottom(\sigma_i) \Big)} \bigg) = \closure{\Big( \bigcup_{i \in [\ell]} \Sigma_\bottom(\sigma_i) \Big)} \\
+\text{and} \qquad
+& \projUp \bigg( \coclosure{\Big( \bigcap_{i \in [\ell]} \closure{\Sigma_\top(\sigma_i)} \Big)} \bigg) = \coclosure{\Big( \bigcap_{i \in [\ell]} \closure{\Sigma_\top(\sigma_i)} \Big)}
+\end{align*}
 for any~$\sigma_1, \dots, \sigma_\ell \in \strings^\pm(\bar Q)$.
@@
 Let~$\tau \in \closure{\Sigma_\bottom(\sigma)}$ and~$\rho \in \Sigma_\bottom(\tau)$.
-By definition, there exist strings~${\tau_1, \dots, \tau_\ell \in \Sigma_\bottom(\sigma)}$, arrows~$\alpha_1, \dots, \alpha_{\ell-1} \in Q_1$ and signs~$\varepsilon_1, \dots, \varepsilon_{\ell-1} \in \{-1,1\}$ such that~$\tau = \tau_1 \alpha_1^{\varepsilon_1} \dots \alpha_{\ell-1}^{\varepsilon_{\ell-1}} \tau_\ell$.
+By definition, there exist strings ${\tau_1, \dots, \tau_\ell \in \Sigma_\bottom(\sigma)}$, arrows~$\alpha_1, \dots, \alpha_{\ell-1} \in Q_1$ and signs~$\varepsilon_1, \dots, \varepsilon_{\ell-1} \in \{-1,1\}$ such that~$\tau = \tau_1 \alpha_1^{\varepsilon_1} \dots \alpha_{\ell-1}^{\varepsilon_{\ell-1}} \tau_\ell$.
 Since~${\rho \in \Sigma_\bottom(\tau)}$, there exist indices~$1 \le i < j \le \ell$ and substrings~$\tau_i' \in \Sigma_\bottom(\tau_i)$ and~${\tau_j' \in \Sigma_\bottom(\tau_j)}$ such that ${\rho = \tau_i' \alpha_i^{\varepsilon_i} \tau_{i+1} \dots \tau_{j-1} \alpha_{j-1}^{\varepsilon_{j-1}} \tau_j'}$.
-We thus obtain~$\rho \in \closure{\Sigma_\bottom(\sigma)}$ so that~${\Sigma_\bottom(\tau) \subseteq \closure{\Sigma_\bottom(\sigma)}}$.
-This shows that~$\closure{\Sigma_\bottom(\sigma)} \subseteq \projDown(\closure{\Sigma_\bottom(\sigma)})$ and thus the equality by Proposition~\ref{prop:latticeCongruence}\,(i).
+We thus obtain that~$\rho \in \closure{\Sigma_\bottom(\sigma)}$ so that~${\Sigma_\bottom(\tau) \subseteq \closure{\Sigma_\bottom(\sigma)}}$.
+This shows that $\closure{\Sigma_\bottom(\sigma)} \subseteq \projDown(\closure{\Sigma_\bottom(\sigma)})$ and thus the equality by Proposition~\ref{prop:latticeCongruence}\,(i).
 
@@
 
+\enlargethispage{.1cm}
 We first define a map~$\eta$ from biclosed sets in~$\Bicl{\bar Q}$ to subsets of walks of~$\walks^\pm(\bar Q)$.
@@
 For~$S \in \Bicl{\bar Q}$ and~$\alpha \in Q_1\blossom$, let
-\(
+\[
 {\omega(\alpha,S) \eqdef \alpha_{-\ell}^{\varepsilon_{-\ell}} \cdots \alpha_{-1}^{\varepsilon_{-1}} \cdot \alpha \cdot \alpha_1^{\varepsilon_1} \cdots \alpha_r^{\varepsilon_r}}
-\)
+\]
 be the directed walk containing~$\alpha$ defined by
@@
 \begin{itemize}
-\item $\varepsilon_i = -1$ if the string~$\alpha_1^{\varepsilon_1} \cdots \alpha_{i-1}^{\varepsilon_{i-1}}$ belongs to~$S$, and~$\varepsilon_i = 1$ otherwise, for all~$i \in [r]$, and
-\item $\varepsilon_{-i} = 1$ if the string~$\alpha_{-i+1}^{\varepsilon_{-i+1}} \cdots \alpha_{-1}^{\varepsilon_{-1}}$ belongs to~$S$, and~$\varepsilon_i = -1$ otherwise, for all~$i \in [\ell]$.
+\item $\varepsilon_i = -1$ if~$\alpha_1^{\varepsilon_1} \cdots \alpha_{i-1}^{\varepsilon_{i-1}} \in S$, and~$\varepsilon_i = 1$ otherwise, for all~$i \in [r]$, and
+\item $\varepsilon_{-i} = 1$ if~$\alpha_{-i+1}^{\varepsilon_{-i+1}} \cdots \alpha_{-1}^{\varepsilon_{-1}} \in S$, and~$\varepsilon_i = -1$ otherwise, for all~$i \in [\ell]$.
 \end{itemize}
@@
 \begin{remark}
-Observe that~$\omega(\alpha,S)$ is well-defined and unique for any~$S \in \Bicl{\bar Q}$ and~$\alpha \in Q_1$.
+Note that~$\omega(\alpha,S)$ is well-defined and unique for any~${S \in \Bicl{\bar Q}}$ and~$\alpha \in Q_1$.
 Indeed, one can start from the string~$\alpha$ and let it grow in both directions according to the local rules of Definition~\ref{def:fromBiclToNKC} until it reaches some blossom vertices of~$\bar Q\blossom$.
@@
 \begin{proof}
-Write~$\omega(\alpha,S) = \alpha_{-\ell}^{\varepsilon_{-\ell}} \cdots \alpha_{-1}^{\varepsilon_{-1}} \alpha \alpha_1^{\varepsilon_1} \cdots \alpha_r^{\varepsilon_r}$ and consider a substring~$\sigma = \alpha_i^{\varepsilon_i} \cdots \alpha_j^{\varepsilon_j}$ ($i < j$).
+Write~$\omega(\alpha,S) = \alpha_{-\ell}^{\varepsilon_{-\ell}} \cdots \alpha_{-1}^{\varepsilon_{-1}} \alpha \alpha_1^{\varepsilon_1} \cdots \alpha_r^{\varepsilon_r}$ and consider a substring ${\sigma = \alpha_i^{\varepsilon_i} \cdots \alpha_j^{\varepsilon_j}}$ ($i < j$).
 Assume for instance that~$\sigma$ is a bottom substring of~$\omega(\alpha,S)$, \ie that~$\varepsilon_{i-1} = 1$ while~$\varepsilon_{j+1} = -1$.
@@
 \begin{proof}
-Denote by~$s$ the number of straight walks, by~$B$ the number of pairs of inverse bending walks and by~$b$ the remaining bending walks in the set~$\set{\omega(\alpha,S)}{\alpha \in Q_1\blossom}$.
+Denote by~$s$ the number of straight walks, by~$B$ the number of pairs of inverse bending walks and by~$b$ the remaining bending walks in~$\set{\omega(\alpha,S)}{\alpha \in Q_1\blossom}$.
 Since this set contains~${|Q_1\blossom| = 4|Q_0| - |Q_1|}$ distinct directed walks by Lemma~\ref{lem:distinctDirectedWalks}, we have~$s + 2B + b = 4|Q_0| - |Q_1|$ and~$s \le 2|Q_0| - |Q_1|$.
-Moreover, since all these walks are not self-kissing and pairwise non-kissing by Corollary~\ref{coro:surjectionNonKissingWalks}, we obtain that~$B + b \le |Q_0|$.
+Moreover, since all these walks are not self-kissing and pairwise non-kissing by Corollary~\ref{coro:surjectionNonKissingWalks}, we get~${B + b \le |Q_0|}$.
 Therefore, Corollary~\ref{coro:pure} ensures that ${B = (s + 2B + b) - (s + B + b) \ge |Q_0|}$.
@@
 
-In other words, beside the straight walks, we can group the walks of~$\set{\omega(\alpha,S)}{\alpha \in Q_1\blossom}$ into pairs of inverse walks.
+In other words, beside the straight walks, we can group the walks in the set $\set{\omega(\alpha,S)}{\alpha \in Q_1\blossom}$ into pairs of inverse walks.
 This leads to the definition of the following map.
@@
 
-\enlargethispage{.4cm}
 We have defined in the previous sections two functions
@@
 \label{prop:surjection}
-For any non-kissing facet~$F \in \NKC$, we have~$\eta \big( \zeta(F) \big) = F$.
+For any non-kissing facet~$F \in \NKC$, we have~${\eta \big( \zeta(F) \big) \! = F}$.
 \end{proposition}
@@
 Since~$\omega$ and~$\omega'$ split at~$t(\sigma)$, this forces~$\omega' \ssm \sigma$ to have an incoming arrow at~$t(\sigma)$.
-Therefore, $\sigma \in \zeta(F)$.
-Thus, there exist bottom substrings~$\sigma_1, \dots, \sigma_\ell$ of walks~$\omega_1, \dots, \omega_\ell$ of~$F$, arrows~${\alpha_1, \dots, \alpha_{\ell-1} \in Q_1}$, and signs~$\varepsilon_1, \dots, \varepsilon_{\ell-1} \in \{-1,1\}$ such that~${\sigma = \sigma_1 \alpha_1^{\varepsilon_1} \cdots \alpha_{\ell-1}^{\varepsilon_{\ell-1}} \sigma_\ell}$.
+Thus,~${\sigma \in \zeta(F)}$.
+Therefore, there exist bottom substrings~$\sigma_1, \dots, \sigma_\ell$ of walks~$\omega_1, \dots, \omega_\ell$ of~$F$, arrows~${\alpha_1, \dots, \alpha_{\ell-1} \in Q_1}$, and signs~$\varepsilon_1, \dots, \varepsilon_{\ell-1} \in \{-1,1\}$ such that~${\sigma = \sigma_1 \alpha_1^{\varepsilon_1} \cdots \alpha_{\ell-1}^{\varepsilon_{\ell-1}} \sigma_\ell}$.
 Note that~$\omega_1 = \omega$ and thus~$\varepsilon_1 = -1$, as otherwise, we would have~$\omega \prec_\alpha \omega_1$, contradicting the definition of~$\omega$.
@@
 \end{itemize}
-As we obtain a contradiction in both cases, we conclude that~$\omega = \omega'$, \ie $\distinguishedWalk{\alpha}{F} = \distinguishedWalk{\alpha}{\eta(\zeta(F))}$.
+As we obtain a contradiction in both cases, we conclude that~$\omega = \omega'$, \ie that ${\distinguishedWalk{\alpha}{F} = \distinguishedWalk{\alpha}{\eta(\zeta(F))}}$.
 Since this holds for any arrow~$\alpha \in Q_1\blossom$ and any walk has at least one distinguished arrow, we conclude that~$F = \eta \big( \zeta(F) \big)$.
@@
 \label{prop:section}
-For any biclosed set of strings~$S \in \Bicl{\bar Q}$, we have~$\zeta \big( \eta(S) \big) = \projDown(S)$.
+For any biclosed set~$S \in \Bicl{\bar Q}$, we have~$\zeta \big( \eta(S) \big) = \projDown(S)$.
 \end{proposition}
@@
 Let~$S \in \Bicl{\bar Q}$ be a biclosed set of strings.
-We first prove that~$\projDown(S) \subseteq \zeta \big( \eta(S) \big)$ by induction on the length of the strings in~$\projDown(S)$.
+We first prove that ${\projDown(S) \subseteq \zeta \big( \eta(S) \big)}$ by induction on the length of the strings in~$\projDown(S)$.
 For this, consider a string~$\sigma \in \projDown(S)$ (by definition, all bottom substrings of~$\sigma$ belong to~$S$).
@@
 \begin{proof}
-If~$\eta(R) = \eta(S)$, then by Proposition~\ref{prop:section}, we have~$\projDown(R) = \zeta(\eta(R)) = \zeta(\eta(S)) = \projDown(S)$.
-Reciprocally, if~$\projDown(R) = \projDown(S)$, then by Propositions~\ref{prop:surjection} and~\ref{prop:section}, we have~$\eta(R) = \eta \circ \zeta \circ \eta(R) = \eta(\projDown(R)) = \eta(\projDown(S)) = \eta \circ \zeta \circ \eta(S) = \eta(S)$.
+If~$\eta(R) = \eta(S)$, then by Proposition~\ref{prop:section}, we have
+\[
+\projDown(R) = \zeta(\eta(R)) = \zeta(\eta(S)) = \projDown(S)
+\]
+Reciprocally, if~$\projDown(R) = \projDown(S)$, then by Propositions~\ref{prop:surjection} and~\ref{prop:section}, we have
+\[
+\eta(R) = \eta \circ \zeta \circ \eta(R) = \eta(\projDown(R)) = \eta(\projDown(S)) = \eta \circ \zeta \circ \eta(S) = \eta(S).
+\qedhere
+\]
 \end{proof}
@@
 \begin{proof}
+\enlargethispage{.3cm}
 Throughout the proof, we denote~$S \eqdef \zeta(F') \ssm \{\sigma\}$ and~$S' \eqdef \zeta(F')$.
-Consider an increasing flip~$F \to F'$ with~$F \ssm \{\omega\} = F' \ssm \{\omega'\}$ and~$\sigma = \distinguishedString{w}{F} = \distinguishedString{w'}{F'}$.
+Consider an increasing flip~$F \to F'$ with~$F \ssm \{\omega\} = F' \ssm \{\omega'\}$ and supported by~$\sigma = \distinguishedString{w}{F} = \distinguishedString{w'}{F'}$.
 We prove that~$S$ is biclosed:
@@
 \item[closed] Otherwise, there exist bottom substrings~$\sigma_1, \dots, \sigma_\ell$ of walks~$\omega_1, \dots, \omega_\ell$ of~$F'$, arrows~$\alpha_1, \dots, \alpha_{\ell-1} \in Q_1$ and signs~$\varepsilon_1, \dots, \varepsilon_{\ell-1} \in \{-1,1\}$ such that~$\sigma = \sigma_1 \alpha_1^{\varepsilon_1} \dots \alpha_{\ell-1}^{\varepsilon_{\ell-1}} \sigma_\ell$.
-Assume that there is~$k \in [\ell-1]$ such that~$\varepsilon_k = 1$ and choose~$k$ minimal with that property.
+Assume that there is~$k \in [\ell-1]$ such that~${\varepsilon_k = 1}$ and choose~$k$ minimal with that property.
 Then~$\omega_k \ne \omega'$ and~$\omega$ has two outgoing arrows while~$\omega_k$ has two incoming arrows at the endpoints of~$\sigma_k$, so that~$\sigma_k \in \Sigma_\top(\omega) \cap \Sigma_\bottom(\omega_k)$, contradicting the non-kissingness of~$F$.
@@
 \item[coclosed] Otherwise, by coclosedness of~$S'$, we can assume that there is a string~${\tau \in \strings(\bar Q) \ssm S'}$, an arrow~$\alpha \in Q_1$ and a sign~$\varepsilon \in \{-1,1\}$ such that~$\sigma \alpha^\varepsilon \tau \in S'$ (the case~${\tau \alpha^\varepsilon \sigma \in S'}$ is symmetric).
-Thus, there exist bottom substrings~$\sigma_1, \dots, \sigma_\ell$ of walks~$\omega_1, \dots, \omega_\ell$ of~$F'$, arrows~$\alpha_1, \dots, \alpha_{\ell-1} \in Q_1$ and signs~$\varepsilon_1, \dots, \varepsilon_{\ell-1} \in \{-1,1\}$ such that~$\sigma \alpha^\varepsilon \tau = \sigma_1 \alpha_1^{\varepsilon_1} \dots \alpha_{\ell-1}^{\varepsilon_{\ell-1}} \sigma_\ell$.
-Since~$\tau \notin S'$, there is~$k \in [\ell]$ such that~$\alpha^\varepsilon$ belongs to~$\sigma_k$ and we write~$\sigma_k = \sigma'_k \alpha^\varepsilon \sigma''_k$.
+Thus, there are bottom substrings~$\sigma_1, \dots, \sigma_\ell$ of walks~$\omega_1, \dots, \omega_\ell$ of~$F'$, arrows~${\alpha_1, \dots, \alpha_{\ell-1} \in Q_1}$ and signs~$\varepsilon_1, \dots, \varepsilon_{\ell-1} \in \{-1,1\}$ such that~$\sigma \alpha^\varepsilon \tau = \sigma_1 \alpha_1^{\varepsilon_1} \dots \alpha_{\ell-1}^{\varepsilon_{\ell-1}} \sigma_\ell$.
+Since~$\tau \notin S'$, there exists~$k \in [\ell]$ such that~$\alpha^\varepsilon$ belongs to~$\sigma_k$ and we write~$\sigma_k = \sigma'_k \alpha^\varepsilon \sigma''_k$.
 Since~$\{\omega, \omega_1, \dots, \omega_k\}$ are non-kissing, we obtain that~$\varepsilon_1, \dots, \varepsilon_{k-1} = -1$, which in turn implies that~$\varepsilon = 1$ (otherwise~$\omega$ would kiss~$\omega_k$).
@@
 \begin{description}
-\item[$\sigma \supset \tau$] Since~$\omega'$ leaves~$\tau$ with an outgoing arrow at~$v$, we have~$\sigma \ssm \tau \in \Sigma_\bottom(\omega') \ssm \{\sigma\} \subseteq S$.
+\item[$\sigma \supset \tau$] Since~$\omega'$ leaves~$\tau$ with an outgoing arrow at vertex~$v$, we obtain that ${\sigma \ssm \tau \in \Sigma_\bottom(\omega') \ssm \{\sigma\} \subseteq S}$.
 Therefore, we have~$\sigma \in \tau \circ (\sigma \ssm \tau)$ and~$\sigma \notin S$ while~$\tau \in S$ and~$\sigma \ssm \tau \in S$.
@@
 
-This concludes our proof of Theorem~\ref{thm:lattice}, that we can now restate more precisely as follows.
+This concludes our proof of Theorem~\ref{thm:lattice}, which we can restate more precisely.
 
@@
 
-\begin{figure}[t]
+%\captionsetup{width=1.5\textwidth}
+%\hvFloat[floatPos=p, capWidth=h, capPos=r, capAngle=90, objectAngle=90, capVPos=c, objectPos=c]{figure}
+%{\includegraphics[scale=.35]{exmSublattice}}
+%{The inclusion lattice of biclosed sets~$\Bicl{\bar Q}$ with congruence classes of~$\equiv$ in blue (left), the sublattice of~$\Bicl{\bar Q}$ induced by~$\projDown \big( \Bicl{\bar Q} \big)$ (middle left) and by~$\projUp \big( \Bicl{\bar Q} \big)$ (middle right), and the corresponding lattice of increasing flips on facets of~$\NKC$ (right).}
+%{fig:exmSublattice}
+%\captionsetup{width=\textwidth}
+
+\begin{figure}[p]
 	\capstart
-	\centerline{\includegraphics[width=1.1\textwidth]{exmSublattice}}
-	\caption{The inclusion lattice of biclosed sets~$\Bicl{\bar Q}$ with congruence classes of~$\equiv$ in blue (left), the sublattice of~$\Bicl{\bar Q}$ induced by~$\projDown \big( \Bicl{\bar Q} \big)$ (middle left) and by~$\projUp \big( \Bicl{\bar Q} \big)$ (middle right), and the corresponding lattice of increasing flips on facets of~$\NKC$ (right).}
+	\centerline{\includegraphics[width=1.3\textwidth]{exmSublatticeVertical}}
+	\caption{The inclusion lattice of biclosed sets~$\Bicl{\bar Q}$ with congruence classes of~$\equiv$ in blue (top), the sublattice of~$\Bicl{\bar Q}$ induced by~$\projDown \big( \Bicl{\bar Q} \big)$ (middle left) and by~$\projUp \big( \Bicl{\bar Q} \big)$ (middle right), and the corresponding lattice of increasing flips on facets of~$\NKC$ (bottom).}
 	\label{fig:exmSublattice}
@@
 
-\section{Canonical join-representations in~$\NKL$ and the non-friendly complex}
+\section[Canonical join-representations and non-friendly complex]{Canonical join-representations in~$\NKL$ \\ and the non-friendly complex}
 \label{sec:nonFriendlyComplex}
@@
 \label{prop:characterizationDistinguishableStrings}
-A string~$\sigma \in \strings^\pm(\bar Q)$ is distinguishable if and only if $\Sigma_\bottom(\sigma) \cap \Sigma_\top(\sigma) = \{\sigma\}$.
+A string~$\sigma \in \strings^\pm(\bar Q)$ is distinguishable if and only if
+\[
+\Sigma_\bottom(\sigma) \cap \Sigma_\top(\sigma) = \{\sigma\}.
+\]
 \end{proposition}
@@
 \begin{proof}
-Assume first that~$\sigma$ is distinguishable and consider~$\tau \in \Sigma_\bottom(\sigma) \cap \Sigma_\top(\sigma)$.
+Assume first that~$\sigma$ is distinguishable and let~$\tau \in \Sigma_\bottom(\sigma) \cap \Sigma_\top(\sigma)$.
 Let~$\tau_\bottom$ (resp.~$\tau_\top$) denote the bottom (resp.~top) copy of~$\tau$ seen as a substring of~$\sigma$.
@@
 \item Otherwise, we can assume for example that~$\tau_\top$ does not share an endpoint with~$\sigma$.
-Then for any walk~$\omega$ such that~$\sigma \in \Sigma_\bottom(\omega)$, we have~$\tau \in \Sigma_\bottom(\omega) \cap \Sigma_\top(\omega)$ so that~$\omega$ is self-kissing.
+Then for any walk~$\omega$ such that~$\sigma \in \Sigma_\bottom(\omega)$, we have ${\tau \in \Sigma_\bottom(\omega) \cap \Sigma_\top(\omega)}$ so that~$\omega$ is self-kissing.
 It follows that~$\sigma$ is not distinguishable.
@@
 It follows from Propositions~\ref{prop:characterizationDistinguishableStrings} and~\ref{prop:morphismsStringModules} that a string~$\sigma$ is distinguishable if and only if~$\Hom{A} \big( M(\sigma), M(\sigma) \big) = k$.
-Modules~$M$ such that~$\Hom{A}(M, M) = k$ are called \defn{bricks}.
+Modules~$M$ such that ${\Hom{A}(M, M) = k}$ are called \defn{bricks}.
 \end{remark}
@@
 Let~$\rho \in \closure{\Sigma_\bottom(\sigma)} \cap \Sigma_\top(\tau)$.
-As~$\rho \in \closure{\Sigma_\bottom(\sigma)}$, there exists substrings~$\rho_1, \dots, \rho_\ell \in \Sigma_\bottom(\sigma)$, arrows~$\alpha_1, \dots, \alpha_{\ell-1} \in Q_1$ and signs~$\varepsilon_1, \dots, \varepsilon_{\ell-1} \in \{-1,1\}$ such that~$\rho = \rho_1 \alpha_1^{\varepsilon_1} \dots \alpha_{\ell-1}^{\varepsilon_{\ell-1}} \rho_\ell$.
+As~$\rho \in \closure{\Sigma_\bottom(\sigma)}$, there exists substrings $\rho_1, \dots, \rho_\ell \in \Sigma_\bottom(\sigma)$, arrows~$\alpha_1, \dots, \alpha_{\ell-1} \in Q_1$ and signs~${\varepsilon_1, \dots, \varepsilon_{\ell-1} \in \{-1,1\}}$ such that~$\rho = \rho_1 \alpha_1^{\varepsilon_1} \dots \alpha_{\ell-1}^{\varepsilon_{\ell-1}} \rho_\ell$.
 Assume that there exists~$k \in [\ell-1]$ such that~$\varepsilon_k = 1$ and choose~$k$ minimal for this property (the proof is similar if there exists~$k \in [\ell-1]$ such that~$\varepsilon_k = -1$).
@@
 To conclude, assume that~$\omega(\alpha',S)$ and~$\omega(\beta',S)$ are not reverse to each other, and let~$\tau$ be a maximal common substring of them containing~$\alpha' \sigma \beta'^{-1}$.
-Write~$\tau = \tau' \alpha' \sigma \beta'^{-1} \tau''$ and assume for example that~$t(\tau'')$ is not a blossom.
-Since~$\tau'' \in S \iff \sigma \beta^{-1} \tau'' \in S$, the two walks~$\omega(\alpha',S)$ and~$\omega(\beta',S)$ should have the same behavior at~$t(\tau'')$, contradicting the maximality of~$\tau$.
+Write ${\tau = \tau' \alpha' \sigma \beta'^{-1} \tau''}$ and assume for example that~$t(\tau'')$ is not a blossom.
+Since ${\tau'' \in S}$ if and only if~${\sigma \beta^{-1} \tau'' \in S}$, the two walks~$\omega(\alpha',S)$ and~$\omega(\beta',S)$ should have the same behavior at~$t(\tau'')$, contradicting the maximality of~$\tau$.
 \end{proof}
@@
 \label{lem:bijectionWalksDistinguishableStrings}
-For any bending walk~$\omega \in \NKWalks^\pm(\bar Q)$ which is not self-kissing and not in the peak facet, the unique inclusion minimal string in~$\set{\sigma \in \Sigma_\bottom(\omega)}{\closure{\Sigma_\bottom(\omega)} = \closure{\Sigma_\bottom(\sigma)}}$ is distinguishable.
+For any bending walk~$\omega \in \NKWalks^\pm(\bar Q)$ which is not self-kissing and not in the peak facet, the unique inclusion minimal string in \[\set{\sigma \in \Sigma_\bottom(\omega)}{\closure{\Sigma_\bottom(\omega)} = \closure{\Sigma_\bottom(\sigma)}}\] is distinguishable.
 \end{lemma}
@@
 Assume that~$\sigma$ is not distinguishable.
-By Lemma~\ref{lem:bijectionDistinguishableStringsWalks}, there exists~${\tau \in \Sigma_\bottom(\sigma) \cap \Sigma_\top(\sigma)}$ distinct from~$\sigma$.
+By Lemma~\ref{lem:bijectionDistinguishableStringsWalks}, there exists a string ${\tau \in \Sigma_\bottom(\sigma) \cap \Sigma_\top(\sigma)}$ distinct from~$\sigma$.
 Since~$\sigma$ is a bottom substring of a non-self-kissing walk~$\omega$, the substring~$\tau$ must be a prefix or a suffix of~$\sigma$, say for example a prefix.
@@
 \label{def:bijectionWalksDistinguishableStrings}
-For a distinguishable string~$\sigma \in \distinguishableStrings^\pm(\bar Q)$, we denote by $\omega_\bottom(\sigma) \in \NKWalks^\pm(\bar Q)$ the undirected walk constructed in Lemma~\ref{lem:bijectionDistinguishableStringsWalks}, meaning that~$\omega_\bottom(\sigma) = \{\omega(\alpha',S), \omega(\beta',S)\}$ where~$S = \closure{\Sigma_\bottom(\sigma)}$ and~$\alpha', \beta'$ are such that~$\alpha'\sigma\beta'^{-1} \in \strings(\bar Q\blossom)$.
+For a distinguishable string~$\sigma \in \distinguishableStrings^\pm(\bar Q)$, we denote by $\omega_\bottom(\sigma) \in \NKWalks^\pm(\bar Q)$ the undirected walk constructed in Lemma~\ref{lem:bijectionDistinguishableStringsWalks}, meaning that ${\omega_\bottom(\sigma) = \{\omega(\alpha',S), \omega(\beta',S)\}}$ where~$S = \closure{\Sigma_\bottom(\sigma)}$ and~$\alpha', \beta' \in Q\blossom_1$ are such that ${\alpha'\sigma\beta'^{-1} \in \strings(\bar Q\blossom)}$.
 
@@
 	\capstart
-	\centerline{\includegraphics[scale=.4]{exmBijectionStringsWalks2}}
+	\centerline{\includegraphics[scale=.5]{exmBijectionStringsWalks2}}
 	\caption{The bijections~$\sigma_\top = \omega_\top^{-1}$ (top) and $\sigma_\bottom = \omega_\bottom^{-1}$ (bottom) for two specific quivers.}
@@
 We have seen in Lemma~\ref{lem:exmBiclosed} that~$\closure{\Sigma_\bottom(\sigma)}$ is biclosed.
-Assume that~$\closure{\Sigma_\bottom(\sigma)} = S \join T$ for some~$S,T \in \Bicl{\bar Q}$.
-Recall from Remark~\ref{rem:meetJoinBiclosedSets} that~$S \join T = \closure{(S \cup T)}$.
+Assume that $\closure{\Sigma_\bottom(\sigma)} = S \join T$ for some~$S,T \in \Bicl{\bar Q}$.
+Recall from Remark~\ref{rem:meetJoinBiclosedSets} that we have~${S \join T = \closure{(S \cup T)}}$.
 
 Assume first that~$\sigma \notin S \cup T$.
-Since~$\sigma \in \Sigma_\bottom(\sigma) \subseteq \closure{\Sigma_\bottom(\sigma)} = S \join T = \closure{(S \cup T)}$, there exists strings~$\sigma_1, \dots, \sigma_\ell \in \closure{\Sigma_\bottom(\sigma)} \ssm \{\sigma\}$, arrows~$\alpha_1, \dots, \alpha_{\ell-1} \in Q_1$ and signs~$\varepsilon_1, \dots, \varepsilon_{\ell-1} \in \{-1,1\}$ such that~$\sigma = \sigma_1 \alpha_1^{\varepsilon_1} \dots \alpha_{\ell-1}^{\varepsilon_{\ell-1}} \sigma_\ell$.
+Since~${\sigma \in \Sigma_\bottom(\sigma) \subseteq \closure{\Sigma_\bottom(\sigma)} = S \join T = \closure{(S \cup T)}}$, there exists strings~$\sigma_1, \dots, \sigma_\ell \in \closure{\Sigma_\bottom(\sigma)} \ssm \{\sigma\}$, arrows~$\alpha_1, \dots, \alpha_{\ell-1} \in Q_1$ and signs~$\varepsilon_1, \dots, \varepsilon_{\ell-1} \in \{-1,1\}$ such that~$\sigma = \sigma_1 \alpha_1^{\varepsilon_1} \dots \alpha_{\ell-1}^{\varepsilon_{\ell-1}} \sigma_\ell$.
 Assume that there exists~$k \in [\ell-1]$ such that~$\varepsilon_k = 1$ and choose~$k$ maximal for this property.
@@
 We conclude that~$\Sigma_\bottom(\sigma) \subseteq S$.
-Since~$S$ is closed, we thus obtain that~$S = \closure{\Sigma_\bottom(\sigma)}$, which proves that~$\closure{\Sigma_\bottom(\sigma)}$ is join-irreducible.
+Since~$S$ is closed, we thus obtain ${S = \closure{\Sigma_\bottom(\sigma)}}$, which proves that~$\closure{\Sigma_\bottom(\sigma)}$ is join-irreducible.
 \end{proof}
@@
 \begin{proof}
-Assume that~$\eta \big( \closure{\Sigma_\bottom(\sigma)} \big) = F \join G$ for some non-kissing facets~$F, G \in \NKC$.
+Assume that~$\eta \big( \closure{\Sigma_\bottom(\sigma)} \big) = F \join G$ for some non-kissing facets ${F, G}$ of~$\NKC$.
 By Lemma~\ref{lem:fixProjDown} and Propositions~\ref{prop:section} and~\ref{prop:sublattice}, we have
@@
 \]
-Since~$\closure{\Sigma_\bottom(\sigma)}$ is join-irreducible in~$\Bicl{\bar Q}$ by Lemma~\ref{lem:exmBiclosedJI}, we can assume that~$\closure{\Sigma_\bottom(\sigma)} = \zeta(F)$ so that~$\eta \big( \closure{\Sigma_\bottom(\sigma)} \big) = \eta(\zeta(F)) = F$ by Proposition~\ref{prop:surjection}.
+Since~$\closure{\Sigma_\bottom(\sigma)}$ is join-irreducible in~$\Bicl{\bar Q}$ by Lemma~\ref{lem:exmBiclosedJI}, we can assume that ${\closure{\Sigma_\bottom(\sigma)} = \zeta(F)}$ so that~$\eta \big( \closure{\Sigma_\bottom(\sigma)} \big) = \eta(\zeta(F)) = F$ by Proposition~\ref{prop:surjection}.
 Thus, $\eta \big( \closure{\Sigma_\bottom(\sigma)} \big) \in \JI \big( \NKL \big)$.
@@
 \]
-Since~$F$ is join-irreducible, we obtain that there exists~$\omega \in F$ such that~$F = \eta \big( \closure{\Sigma_\bottom(\omega)} \big)$.
-By Lemma~\ref{lem:bijectionWalksDistinguishableStrings}, there exists a distinguishable string~$\sigma = \sigma_\bottom(\omega)$ such that~$\closure{\Sigma_\bottom(\omega)} = \closure{\Sigma_\bottom(\sigma)}$.
+Since~$F$ is join-irreducible, we obtain that there is~$\omega \in F$ such that~${F = \eta \big( \closure{\Sigma_\bottom(\omega)} \big)}$.
+By Lemma~\ref{lem:bijectionWalksDistinguishableStrings}, we obtain that there exists a distinguishable string~$\sigma = \sigma_\bottom(\omega)$ such that ${\closure{\Sigma_\bottom(\omega)} = \closure{\Sigma_\bottom(\sigma)}}$.
 We conclude that~$F = \eta \big( \closure{\Sigma_\bottom(\sigma)} \big)$ so that~$\ji$ is surjective.
@@
 \]
-where~$\ji(\sigma)_\star$ denotes the only non-kissing facet covered by the join-irreducible facet~$\ji(\sigma)$.
+where~$\ji(\sigma)_\star$ denotes the only non-kissing facet covered by the join-irreducible~$\ji(\sigma)$.
 \end{lemma}
@@
 %
-We thus obtain that~$\ji(\sigma) \le F'$ so that~$F \ne F \join \ji(\sigma) \le F'$. Since~$F$ covers~$F'$ in~$\NKL$, we obtain the first equality
+We thus obtain that~$\ji(\sigma) \le F'$ so that~$F \ne F \join \ji(\sigma) \le F'$. Since~$F$ covers~$F'$ in~$\NKL$, we get the first equality
 \(
@@
 %
-Moreover, since~$\zeta \big( \ji(\sigma) \big) \subseteq \zeta(F')$ and~$\zeta(F) = \zeta(F') \ssm \{\sigma\}$, %we have
+Moreover, since~${\zeta \big( \ji(\sigma) \big) \subseteq \zeta(F')}$ and~$\zeta(F) = \zeta(F') \ssm \{\sigma\}$, %we have
 \[
@@
 \]
-where the last equality follows from Proposition~\ref{prop:covers} for the increasing flip~$\ji(\sigma)_\star \to \ji(\sigma)$ supported by~$\sigma$.
+where the last equality follows from Proposition~\ref{prop:covers} applied to the increasing flip~${\ji(\sigma)_\star \to \ji(\sigma)}$ supported by~$\sigma$.
 Therefore, we obtain from Propositions~\ref{prop:surjection} and~\ref{prop:sublattice} that
@@
 \label{coro:joinRepresentations}
-The canonical join-representation of a non-kissing facet~$F \in \NKC$ is
+The canonical join-representation of a non-kissing facet~$F$ of~$\NKC$ is
 \[
@@
 
-\enlargethispage{.4cm}
 To conclude, we want to understand the canonical join complex of the non-kissing lattice~$\NKL$.
@@
 	\capstart
-	\centerline{\includegraphics[scale=.4]{exmNCP}}
+	\centerline{\includegraphics[scale=.35]{exmNCP}}
 	\caption{The bijection between pairwise non-friendly set of strings of an oriented path on $n$ vertices and non-crossing partitions of~$[n+1]$.}
@@
 
-Assume first that~$\sigma$ and~$\tau$ are friendly and let for example~$\rho \in \Sigma_\top(\sigma) \cap \Sigma_\bottom(\tau)$.
+Assume first that~$\sigma$ and~$\tau$ are friendly and let for example ${\rho \in \Sigma_\top(\sigma) \cap \Sigma_\bottom(\tau)}$.
 Then~$\sigma$ decomposes into~$\sigma = \sigma' \alpha^{-1} \rho \beta \sigma''$, or~$\sigma = \rho \beta \sigma''$, or~$\sigma = \sigma' \alpha^{-1} \rho$ for some~$\sigma', \sigma'' \in \Sigma_\bottom(\sigma)$.
@@
 
-Conversely, assume that~$\closure{\Sigma_\bottom(\sigma)} \join \closure{\Sigma_\bottom(\tau)}$ is not its canonical join-representation, and let~${R \subseteq \distinguishableStrings^\pm(\sigma)}$ be such that
+Conversely, assume that~$\closure{\Sigma_\bottom(\sigma)} \join \closure{\Sigma_\bottom(\tau)}$ is not its canonical join-representa\-tion, and let~${R \subseteq \distinguishableStrings^\pm(\sigma)}$ be such that
 \[
@@
 Assume that there is no~$\rho \in R$ such that~$\sigma \in \Sigma_\bottom(\rho)$.
-Since~$\sigma \in \closure{\Sigma_\bottom(\sigma)} \join \closure{\Sigma_\bottom(\tau)}$, we know that there exist strings~$\rho_1, \dots, \rho_\ell \in R$, substrings~$\xi_1 \in \Sigma_\bottom(\rho_1), \dots, \xi_\ell \in \Sigma_\bottom(\rho_\ell)$, arrows~$\alpha_1, \dots, \alpha_{\ell_1} \in Q_1$ and signs~${\varepsilon_1, \dots, \varepsilon_{\ell-1} \in \{-1,1\}}$ such that~$\sigma = \xi_1 \alpha_1^{\varepsilon_1} \dots \alpha_{\ell-1}^{\varepsilon_{\ell-1}} \xi_\ell$.
-Assume that there is~$k \in [\ell-1]$ such that~$\varepsilon_k = 1$ and consider the prefix~$\xi \eqdef \xi_1 \alpha_1^{\varepsilon_1} \dots \alpha_{k-1}^{\varepsilon_{k-1}} \xi_k$ of~$\sigma$ (the proof for the other case is symmetric considering a suffix).
-Since~$\xi \in \closure{\Sigma_\bottom(\sigma)} \join \closure{\Sigma_\bottom(\tau)}$, there exist strings~$\zeta_1, \dots, \zeta_m \in \Sigma_\bottom(\sigma) \cup \Sigma_\bottom(\tau)$, arrows~$\beta_1, \dots, \beta_{m-1} \in Q_1$ and signs~$\delta_1, \dots, \delta_{m-1} \in \{-1,1\}$ such that~$\xi = \zeta_1 \beta_1^{\delta_1} \dots \beta_{m-1}^{\delta_{m-1}} \zeta_m$.
-Since~$\varepsilon_k = 1$, we have~$\zeta_m \notin \Sigma_\bottom(\sigma)$ so that~$\zeta_m \in \Sigma_\bottom(\tau)$.
+Since~$\sigma \in \closure{\Sigma_\bottom(\sigma)} \join \closure{\Sigma_\bottom(\tau)}$, we know that there exist strings~$\rho_1, \dots, \rho_\ell \in R$, substrings~$\xi_1 \in \Sigma_\bottom(\rho_1), \dots, \xi_\ell \in \Sigma_\bottom(\rho_\ell)$, arrows $\alpha_1, \dots, \alpha_{\ell_1} \in Q_1$ and signs~${\varepsilon_1, \dots, \varepsilon_{\ell-1} \in \{-1,1\}}$ such that~$\sigma = \xi_1 \alpha_1^{\varepsilon_1} \dots \alpha_{\ell-1}^{\varepsilon_{\ell-1}} \xi_\ell$.
+Assume that there exists~$k \in [\ell-1]$ such that~$\varepsilon_k = 1$ and consider the prefix $\xi \eqdef \xi_1 \alpha_1^{\varepsilon_1} \dots \alpha_{k-1}^{\varepsilon_{k-1}} \xi_k$ of~$\sigma$ (the proof for the other case is symmetric considering a suffix).
+Since~$\xi \in \closure{\Sigma_\bottom(\sigma)} \join \closure{\Sigma_\bottom(\tau)}$, there are strings $\zeta_1, \dots, \zeta_m \in \Sigma_\bottom(\sigma) \cup \Sigma_\bottom(\tau)$, arrows~$\beta_1, \dots, \beta_{m-1} \in Q_1$ and signs~$\delta_1, \dots, \delta_{m-1} \in \{-1,1\}$ such that~$\xi = \zeta_1 \beta_1^{\delta_1} \dots \beta_{m-1}^{\delta_{m-1}} \zeta_m$.
+Since~$\varepsilon_k = 1$, we have~$\zeta_m \notin \Sigma_\bottom(\sigma)$ so that ${\zeta_m \in \Sigma_\bottom(\tau)}$.
 Let~$n \in [m]$ be minimal such that~$\zeta \eqdef \zeta_n \beta_n^{\delta_n} \dots \beta_{m-1}^{\varepsilon_{m-1}} \zeta_m \in \closure{\Sigma_\bottom(\tau)}$.
@@
 
-In this section, we provide geometric realizations of the non-kissing complex~$\RNKC$ when it is finite.
+This section provides geometric realizations of the non-kissing complex~$\RNKC$ when it is finite.
 Inspired by similar constructions of~\cite{MannevillePilaud-accordion} for dissection bound quivers and~\cite{GarverMcConville} for grid bound quivers, we first construct a complete simplicial fan~$\gvectorFan$ realizing~$\RNKC$~(\ref{subsec:gvectorFan}).
@@
 \begin{definition}
-A \defn{polyhedral fan} is a collection~$\Fan$ of polyhedral cones such that
+A \defn{polyhedral fan} is a collection~$\Fan$ of polyhedral cones such~that
 \begin{itemize}
@@
 \begin{example}
-The $\b{g}$-vector of the plain blue walk on \fref{fig:exmFacet}\,(left) is~$(0,-1,0,0,1,0)$ (see \fref{fig:exmBlossomingQuiver} for the labeling order of the vertices of the quiver~$Q\ex$).
+The $\b{g}$-vector of the plain blue walk on \fref{fig:exmFacet}\,(left) is given by $(0,-1,0,0,1,0)$ (see \fref{fig:exmBlossomingQuiver} for the labeling order of the vertices of the quiver~$Q\ex$).
 See \fref{fig:gcvectors} for more examples of $\b{g}$-vectors.
@@
 \begin{definition}\label{def: c-vectors}
-Consider a bending walk~$\omega$ in a non-kissing facet~$F \in \RNKC$.
-Recall from Proposition~\ref{prop:distinguishedArrows} that the walk~$\omega$ carries two distinguished arrows~$\distinguishedArrows{\omega}{F}$ surrounding its distinguished string~$\distinguishedString{\omega}{F}$ (see \fref{fig:gcvectors}).
+Consider a bending walk~$\omega$ in a non-kissing facet~${F \in \RNKC}$.
+Recall from Proposition~\ref{prop:distinguishedArrows} that the walk~$\omega$ carries two distinguished arrows $\distinguishedArrows{\omega}{F}$ surrounding its distinguished string~$\distinguishedString{\omega}{F}$ (see \fref{fig:gcvectors}).
 Define
@@
 \begin{cases}
-\phantom{-}1 & \text{if~$\distinguishedString{\omega}{F}$ is a top substring of~$\omega$ (\ie the arrows~$\distinguishedArrows{\omega}{F}$ point outside),} \\
--1 & \text{if~$\distinguishedString{\omega}{F}$ is a bottom substring of~$\omega$ (\ie if the arrows~$\distinguishedArrows{\omega}{F}$ point inside).}
+\phantom{-}1 & \text{if~$\distinguishedString{\omega}{F}$ is a top substring of~$\omega$,} \\% (\ie the arrows~$\distinguishedArrows{\omega}{F}$ point outside),} \\
+-1 & \text{if~$\distinguishedString{\omega}{F}$ is a bottom substring of~$\omega$.} % (\ie if the arrows~$\distinguishedArrows{\omega}{F}$ point inside).}
 \end{cases}
@@
 \]
-We let~$\cvectors{F} \eqdef \set{\cvector{\omega}{F}}{\omega \in F}$ be the set of $\b{c}$-vectors of a non-kissing facet~$F \in \RNKC$, and~$\allcvectors \eqdef \bigcup_F \cvectors{F}$ be the set of all $\b{c}$-vectors of all non-kissing facets~${F \in \RNKC}$.
+We let~$\cvectors{F} \eqdef \set{\cvector{\omega}{F}}{\omega \in F}$ denote the set of $\b{c}$-vectors of a non-kissing facet~${F \in \RNKC}$, and~$\allcvectors \eqdef \bigcup_F \cvectors{F}$ be the set of all $\b{c}$-vectors of all non-kissing facets~${F \in \RNKC}$.
 \end{definition}
@@
 	\capstart
-	\centerline{$\raisebox{-1.5cm}{\begin{overpic}[scale=.7]{exmVectors}\put(60,4){$F\ex$}\end{overpic}}$ \qquad \input{gcmatrices}}
+	\centerline{$\raisebox{-1.5cm}{\begin{overpic}[scale=.6]{exmVectors}\put(60,4){$F\ex$}\end{overpic}}$ \qquad \input{gcmatrices}}
 	\caption{The $\b{g}$- and $\b{c}$-matrices of the facet~$F\ex$.
@@
 The $\b{g}$- and $\b{c}$-vectors of the peak and deep facets~$F_\peak$ and~$F_\deep$ are given by
-\begin{gather*}
-\gvector{v_\peak} = \b{e}_v, \quad 
-\gvector{v_\deep} = -\b{e}_v, \quad
-\cvector{v_\peak}{F_\peak} = \b{e}_v, \quad\text{and}\quad
-\cvector{v_\deep}{F_\deep} = -\b{e}_v.
-\end{gather*}
+\begin{align*}
+&\gvector{v_\peak} = \b{e}_v, \\ 
+&\gvector{v_\deep} = -\b{e}_v, \\
+&\cvector{v_\peak}{F_\peak} = \b{e}_v, \\
+\quad\text{and}\quad
+&\cvector{v_\deep}{F_\deep} = -\b{e}_v.
+\end{align*}
 \end{example}
@@
 \label{prop:gvectorscvectorsDualBases}
-For any non-kissing facet~$F \in \RNKC$, the set of $\b{g}$-vectors~$\gvectors{F}$ and the set of $\b{c}$-vectors~$\cvectors{F}$ form dual bases. 
+For a non-kissing facet~$F \in \RNKC$, the set of $\b{g}$-vectors~$\gvectors{F}$ and the set of $\b{c}$-vectors~$\cvectors{F}$ form dual bases. 
 \end{proposition}
@@
 Otherwise, ${\cvector{\mu}{F}}$ is negative and there is one more deep than peaks on the distinguished string~$\distinguishedString{\mu}{F}$.
-In both cases, we obtain~$\dotprod{\gvector{\mu}}{\cvector{\mu}{F}} = 1$.
+In both cases, we obtain that $\dotprod{\gvector{\mu}}{\cvector{\mu}{F}} = 1$.
 
@@
 We thus showed that~$\sigma$ does not contributes to~$\dotprod{\gvector{\mu}}{\cvector{\nu}{F}}$.
-Summing the contribution of all common substrings of~$\mu$ and~$\nu$, we obtain that~$\dotprod{\gvector{\mu}}{\cvector{\nu}{F}} = 0$ when~$\mu \ne \nu$.
+Summing the contribution of all common substrings of~$\mu$ and~$\nu$, we therefore obtain that~$\dotprod{\gvector{\mu}}{\cvector{\nu}{F}} = 0$ when~$\mu \ne \nu$.
 We conclude that~$\gvectors{F}$ and~$\cvectors{F}$ are dual bases.
@@
 \begin{remark}
-The linear dependence~$\gvector{\omega} + \gvector{\omega'} = \gvector{\mu} + \gvector{\nu}$ relating the $\b{g}$-vectors of two adjacent non-kissing facets~$F,F' \in \RNKC$ shows that~${\det \big( \gvector{F} \big) = - \det \big( \gvector{F'} \big)}$.
+The linear dependence \[\gvector{\omega} + \gvector{\omega'} = \gvector{\mu} + \gvector{\nu}\] relating the $\b{g}$-vectors of two adjacent non-kissing facets~$F,F' \in \RNKC$ shows that ${\det \big( \gvector{F} \big) = - \det \big( \gvector{F'} \big)}$.
 Since the initial cone~$\R_{\ge0} \gvectors{F_\peak}$ is generated by the coordinate vectors (see Example~\ref{exm:gcvectors}), we obtain that~$\det \big( \gvector{F} \big) = \pm 1$ for all non-kissing facets~$F \in \RNKC$, so that the $\b{g}$-vector fan~$\gvectorFan$ is~\defn{smooth}.
@@
 
-\begin{figure}[t]
-	\capstart
-	\centerline{\includegraphics[width=1.1\textwidth]{exmFans}}
-	\caption{Stereographic projections of the $\b{c}$-vector fans~$\cvectorFan$ (red, left) and the $\b{g}$-vector fans~$\gvectorFan$ (blue, middle) for two specific quivers.
+\captionsetup{width=1.5\textwidth}
+\hvFloat[floatPos=p, capWidth=h, capPos=r, capAngle=90, objectAngle=90, capVPos=c, objectPos=c]{figure}
+{\includegraphics[scale=.5]{exmFans}}
+{Stereographic projections of the $\b{c}$-vector fans~$\cvectorFan$ (red, left) and the $\b{g}$-vector fans~$\gvectorFan$ (blue, middle) for two specific quivers.
 The~$3$-dimensional fan is intersected with the unit sphere and stereographically projected to the plane from the pole in direction~$(1,1,1)$.
 Note that the $\b{g}$-vector fan is supported by the $\b{c}$-vector fan (right).}
-	\label{fig:exmFans}
-\end{figure}
+{fig:exmFans}
+\captionsetup{width=\textwidth}
+
+%\begin{figure}[t]
+%	\capstart
+%	\centerline{\includegraphics[width=1.1\textwidth]{exmFans}}
+%	\caption{Stereographic projections of the $\b{c}$-vector fans~$\cvectorFan$ (red, left) and the $\b{g}$-vector fans~$\gvectorFan$ (blue, middle) for two specific quivers.
+The~$3$-dimensional fan is intersected with the unit sphere and stereographically projected to the plane from the pole in direction~$(1,1,1)$.
+Note that the $\b{g}$-vector fan is supported by the $\b{c}$-vector fan (right).}
+%	\label{fig:exmFans}
+%\end{figure}
 \end{example}
@@
 \end{itemize}
-Note that the topmost quiver of \fref{fig:exmFans} is both a dissection and a grid bound quiver, so that its $\b{g}$-vector fan was constructed independently in~\cite{MannevillePilaud-accordion} and~\cite{GarverMcConville-grid}.
+Note that the topmost quiver of \fref{fig:exmFans} is both a dissection and a grid bound quiver, and its $\b{g}$-vector fan was constructed independently in~\cite{MannevillePilaud-accordion} and~\cite{GarverMcConville-grid}.
 \end{example}
@@
 \label{rem:linDep}
-\enlargethispage{.1cm}
 Theorem~\ref{thm:gvectorFan} extends to any finite-dimensional algebra~$A$. More precisely:
@@
 Indeed, the~$\b{g}$-vector of a~$\tau$-rigid pair can be identified with the class of the corresponding $2$-term complex in the Grothendieck group of the bounded homotopy category of finitely generated projective modules over~$A$.
-The existence of an exchange triangle $X \rightarrow \bigoplus_{i \in [k]} Y_i \rightarrow X' \rightarrow X[1]$ (see~\cite{AiharaIyama}) immediately gives the equality~$[X] + [X'] = \sum_{i \in [k]} [Y_i]$ in the Grothendieck group, yielding the claimed linear dependence among~$\b{g}$-vectors.
+The existence of an exchange triangle ${X \rightarrow \bigoplus_{i \in [k]} Y_i \rightarrow X' \rightarrow X[1]}$ (see~\cite{AiharaIyama}) immediately gives the equality~$[X] + [X'] = \sum_{i \in [k]} [Y_i]$ in the Grothendieck group, yielding the claimed linear dependence among~$\b{g}$-vectors.
 \item By Proposition~\ref{prop:characterizationFan}, this suffices to prove Theorem~\ref{thm:gvectorFan} for any finite-dimensional algebra~$A$ with finite support $\tau$-tilting complex. 
@@
 \begin{proof}
-Consider two adjacent non-kissing facets~$F,F'$ and define the walks~$\omega, \omega', \mu, \nu$ as in Proposition~\ref{prop:flip} (see \fref{fig:flip}).
+Consider two adjacent non-kissing facets~$F,F'$ and define the walks ${\omega, \omega', \mu, \nu}$ as in Proposition~\ref{prop:flip} (see \fref{fig:flip}).
 We have seen in the proof of Theorem~\ref{thm:gvectorFan} that the linear dependence between the $\b{g}$-vectors of~$F \cup F'$ is~$\gvector{\omega} + \gvector{\omega'} = \gvector{\mu} + \gvector{\nu}$.
@@
 \begin{example}
-To illustrate Theorem~\ref{thm:associahedron}, we have represented in \fref{fig:exmAssociahedra}\,(middle) the associahedron~$\Asso$ for two specific gentle bound quivers.
+To illustrate Theorem~\ref{thm:associahedron}, we have represented the associahedron~$\Asso$ for two specific gentle bound quivers in \fref{fig:exmAssociahedra}\,(middle).
 More generally, \fref{fig:allAssociahedra3}\,(middle) gathers the associahedron~$\Asso$ for all possible connected simple gentle bound quivers with~$3$ vertices such that the non-kissing complex~$\RNKC$ is finite (\ie where there is a relation in any cycle, oriented or not).
@@
 
-\begin{figure}[t]
-	\capstart
-	\centerline{\includegraphics[width=1.1\textwidth]{exmAssociahedra}}
-	\caption{The zonotope~$\Zono$ (red, left) and the associahedron~$\Asso$ (blue, middle) for two specific quivers.
+\captionsetup{width=1.5\textwidth}
+\hvFloat[floatPos=p, capWidth=h, capPos=r, capAngle=90, objectAngle=90, capVPos=c, objectPos=c]{figure}
+{\includegraphics[scale=.5]{exmAssociahedra}}
+{The zonotope~$\Zono$ (red, left) and the associahedron~$\Asso$ (blue, middle) for two specific quivers.
 Observe that the facet defining inequalities of~$\Asso$ are not necessarily facet defining inequalities of~$\Zono$ (right).}
-	\label{fig:exmAssociahedra}
-\end{figure}
+{fig:exmAssociahedra}
+\captionsetup{width=\textwidth}
+
+%\begin{figure}[t]
+%	\capstart
+%	\centerline{\includegraphics[width=1.1\textwidth]{exmAssociahedra}}
+%	\caption{The zonotope~$\Zono$ (red, left) and the associahedron~$\Asso$ (blue, middle) for two specific quivers.
+Observe that the facet defining inequalities of~$\Asso$ are not necessarily facet defining inequalities of~$\Zono$ (right).}
+%	\label{fig:exmAssociahedra}
+%\end{figure}
 \end{example}
@@
 \begin{itemize}
-\item For a dissection~$D$, the $\bar Q(D)$-associahedron of the dissection bound quiver~$\bar Q(D)$ was previously constructed in~\cite{MannevillePilaud-accordion} as a projection of a well-chosen associahedron.
+\item For a dissection~$D$, the $\bar Q(D)$-associahedron of the dissection bound quiver $\bar Q(D)$ was previously constructed in~\cite{MannevillePilaud-accordion} as a projection of a well-chosen associahedron.
 For example, the top line of \fref{fig:exmAssociahedra} already appeared in~\cite{MannevillePilaud-accordion}.
@@
 An exchange triangle $X \rightarrow \bigoplus_{i \in [k]} Y_i \rightarrow X' \rightarrow X[1]$ (see~\cite{AiharaIyama}) then gives rise to
-\begin{itemize}
+\begin{enumerate}[(i)]
 \item a linear dependence~$[X] + [X'] = \sum_{i \in [k]} [Y_i]$ in the Grothendieck group (see Remark~\ref{rem:linDep}),
-\item an inequality of the form~$\KN(X) + \KN(X') > \sum_{i \in [k]} \KN(Y_i)$ for~$\KN \in \{\KN_\ell, \KN_r\}$.
-\end{itemize}
+\item an inequality of the form~$\KN(X) + \KN(X') > \sum_{i \in [k]} \KN(Y_i)$ for~${\KN \in \{\KN_\ell, \KN_r\}}$.
+\end{enumerate}
 The proof is then similar to that of Theorem~\ref{thm:associahedron} and leads to the same results using either~$\KN_\ell$, $\KN_r$, or more symmetrically their sum~$\KN_\ell + \KN_r$.
@@
 
-The following observation is an immediate consequence of the fact that the normal fan of the $\bar Q$-associahedron~$\Asso$ is the $\b{g}$-vector fan~$\gvectorFan$.
+\enlargethispage{-.1cm}
+The following observation is an immediate consequence of the fact that the normal fan of the $\bar Q$-associahedron $\Asso$ is the $\b{g}$-vector fan~$\gvectorFan$.
 
 \begin{lemma}
-Consider two adjacent non-kissing facets~$F,F'$ and let~$\omega, \omega', \mu$ and~$\nu$ denote the walks involved in the flip as defined in Proposition~\ref{prop:flip} (see \fref{fig:flip}).
+Consider two adjacent non-kissing facets~$F,F'$ and let~$\omega, \omega', \mu$ and~$\nu$ denote the walks involved in the flip as defined in Proposition~\ref{prop:flip} (see also \fref{fig:flip}).
 Then the difference~${\point{F'} - \point{F}}$ is a strictly negative multiple of~$\cvector{\omega}{F} = -\cvector{\omega'}{F'}$.
@@
 \begin{itemize}
-\item If~$\mu = \nu$, then it is a bending walk and~$\cvector{\mu}{F'} = \cvector{\mu}{F} + 2\,\cvector{\omega}{F}$.
+\item If~$\mu = \nu$, then it is a bending walk and~
+\[
+\cvector{\mu}{F'} = \cvector{\mu}{F} + 2\,\cvector{\omega}{F}.
+\]
 \item Otherwise, whenever $\mu$ and~$\nu$ are bending walks, we have
@@
 \end{itemize}
-The formula thus immediately follows from the definition of~$\point{F}$.
+The formula thus follows from the definition of~$\point{F}$.
 Finally, Lemma~\ref{lem:submodular} asserts that~${\KN(\omega) + \KN(\omega') > \KN(\mu) + \KN(\nu)}$, which shows that~${\point{F'} - \point{F}}$ is a strictly negative multiple of~$\cvector{\omega}{F} = -\cvector{\omega'}{F'}$.
@@
 \begin{proposition}
-When oriented in the linear direction~$-\one \eqdef (-1, \dots, -1) \in \R^{Q_0}$, the graph of the $\bar Q$-associahedron~$\Asso$ is (isomorphic to) the increasing flip graph~$\NKG$.
+When oriented in the direction~${-\one \eqdef (-1, \dots, -1) \in \R^{Q_0}}$, the graph of the $\bar Q$-associahedron~$\Asso$ is (isomorphic to) the increasing flip graph~$\NKG$.
 \end{proposition}
@@
 \fref{fig:exmAssociahedra}\,(left) illustrates the zonotope~$\Zono$ for two specific gentle bound quivers.
-More generally, \fref{fig:allAssociahedra3}\,(top) gathers the zonotopes~$\Zono$ for all possible connected simple gentle bound quivers with~$3$ vertices such that the non-kissing complex~$\RNKC$ is finite.
+More generally, \fref{fig:allAssociahedra3}\,(top) gathers the zonotopes $\Zono$ for all possible connected simple gentle bound quivers with~$3$ vertices such that the non-kissing complex~$\RNKC$ is finite.
 Their normal fans are represented in \fref{fig:allFans3}\,(top).
@@
 When~$\bar Q$ is a type~$A$ quiver, the $\bar Q$-zonotope~$\Zono$ is the Minkowski sum of all characteristic vectors of intervals (\ie all type~$A_n$ roots), thus yielding the classical permutahedron.
-In this situation, the $\bar Q$-associahedron~$\Asso$ is thus obtained by deleting inequalities in the facet description of the $\bar Q$-zonotope~$\Zono$.
+In this situation, the $\bar Q$-associahedron~$\Asso$ is thus obtained by deleting inequalities in the facet description of the $\bar Q$-zonotope $\Zono$.
 See~\cite{Loday, HohlwegLange, LangePilaud} for details.
@@
 \label{prop:zonotope}
-If~$\bar Q$ is a gentle bound quiver with a finite non-kissing complex and no two mutually kissing walks, then all facet inequalities of the $\bar Q$-associahedron~$\Asso$ are also facet inequalities of the $\bar Q$-zonotope~$\Zono$.
+If~$\bar Q$ is a gentle bound quiver with a finite non-kissing complex and no two mutually kissing walks, then all facet inequalities of the $\bar Q$-associahedron $\Asso$ are also facet inequalities of the $\bar Q$-zonotope~$\Zono$.
 In other words, the $\bar Q$-associahedron~$\Asso$ is obtained by deleting inequalities in the facet description of the $\bar Q$-zonotope~$\Zono$.
@@
 Consider a bending walk~$\omega \in \bendingWalks^\pm(\bar Q)$ and the corresponding facet inequality of~$\Asso$ given by~${\dotprod{\gvector{\omega}}{\b{x}} \le \KN(\omega)}$.
-We want to show that~$\dotprod{\gvector{\omega}}{\b{x}} \le \KN(\omega)$ is also a facet inequality of~$\Zono$.
+We just want to show that $\dotprod{\gvector{\omega}}{\b{x}} \le \KN(\omega)$ is also a facet inequality of~$\Zono$.
 For this, we associate to each bending walk~$\omega'$ a negative $\b{c}$-vector~$\b{c}^-(\omega')$ and a positive $\b{c}$-vector~$\b{c}^+(\omega')$ defined by
@@
 \end{cases}
-\qquad\text{and}\qquad
+\quad\text{and}\quad
 \b{c}^+(\omega') \eqdef 
@@
 Consider now a bending walk~$\omega' \in \bendingWalks^\pm(\bar Q)$.
-We want to understand when~$\dotprod{\gvector{\omega}}{\b{c}^+(\omega')} > 0$ (the case~$\dotprod{\gvector{\omega}}{\b{c}^-(\omega')} > 0$ is similar).
-If~$\dotprod{\gvector{\omega}}{\b{c}^+(\omega')} > 0$, then the walks~$\omega$ and~$\omega'$ share common vertices.
+We want to understand when $\dotprod{\gvector{\omega}}{\b{c}^+(\omega')} > 0$ (the other case~$\dotprod{\gvector{\omega}}{\b{c}^-(\omega')} > 0$ is similar).
+If we have $\dotprod{\gvector{\omega}}{\b{c}^+(\omega')} > 0$, then the walks~$\omega$ and~$\omega'$ share common vertices.
 Let~$\tau$ be a maximal common substring of~$\omega$ and~$\omega'$.
@@
 Therefore, we have~$\max(\dotprod{\gvector{\omega}}{\b{c}^+(\omega)}, 0) = \kn(w,w')$.
-We obtain similarly that~$\max(\dotprod{\gvector{\omega}}{\b{c}^-(\omega)}, 0) = \kn(w',w)$, so that 
-\[
-\max(\dotprod{\gvector{\omega}}{\b{c}^-(\omega')},0) + \max(\dotprod{\gvector{\omega}}{\b{c}^+(\omega')},0) = \kn(w,w') + \kn(w',w) = \KN(\omega,\omega')
+We obtain similarly that $\max(\dotprod{\gvector{\omega}}{\b{c}^-(\omega)}, 0) = \kn(w',w)$, so that 
+\[
+\max(\dotprod{\gvector{\omega}}{\b{c}^-(\omega')},0) + \max(\dotprod{\gvector{\omega}}{\b{c}^+(\omega')},0) = \KN(\omega,\omega')
 \]
@@
 
+\enlargethispage{-.2cm}
 We conclude the paper with a natural operation on quivers that illustrates a recent result of~\cite{PilaudPlamondonStella}.
@@
 \begin{definition}
-Consider a gentle bound quiver~$\bar Q = (Q,I)$ and a vertex~$v \in Q_0$.
+Consider a gentle bound quiver~$\bar Q = (Q,I)$ and a vertex~${v \in Q_0}$.
 Denote by~$K_v \eqdef \set{\alpha\beta}{\alpha, \beta \in Q_1 \text{ with } t(\alpha) = s(\beta)}$ the set of paths of length~$2$ with middle vertex~$v$ and let~$I_v \eqdef K_v \cap I$ and~$J_v \eqdef K_v \ssm I$.
 We denote by~$\bar Q\blinkers{v} = (Q\blinkers{v}, I\blinkers{v})$ the bound quiver where
-\begin{gather*}
-(Q\blinkers{v})_0 = Q_0 \ssm \{v\},
-\qquad\qquad
-(Q\blinkers{v})_1 = \set{\alpha \in Q_1}{s(\alpha) \ne v \ne t(\alpha) } \cup J_v,
-\\
-I\blinkers{v} = \set{\sigma \in I \ssm I_v}{s(\sigma) \ne v \ne t(\sigma)} \cup \set{\alpha\beta\gamma}{\alpha\beta \in I \text{ and } \beta\gamma \in J_v \; \text{ or } \; \alpha\beta \in J_v \text{ and } \beta\gamma \in I}.
-\end{gather*}
-We say that~$\bar Q\blinkers{v}$ is obtained by \defn{blinding}~$v$ in~$\bar Q$.
-Finally, for a subset~$V = \{v_1, \dots, v_\ell\}$ of~$Q_0$, we let~$\bar Q\blinkers{V} \eqdef ((\bar Q\blinkers{v_1})\blinkers{v_2} \dots )\blinkers{v_\ell}$.
+\begin{align*}
+(Q\blinkers{v})_0 = & Q_0 \ssm \{v\}, \\
+(Q \blinkers{v})_1 = & \set{\alpha \in Q_1}{s(\alpha) \ne v \ne t(\alpha) } \cup J_v, \\
+I\blinkers{v} = & \set{\sigma \in I \ssm I_v}{s(\sigma) \ne v \ne t(\sigma)} \\
+& \cup \set{\alpha\beta\gamma}{\alpha\beta \in I \text{ and } \beta\gamma \in J_v \; \text{ or } \; \alpha\beta \in J_v \text{ and } \beta\gamma \in I}.
+\end{align*}
+We say that~$\bar Q\blinkers{v}$ is obtained by \defn{blinding} vertex~$v$ in~$\bar Q$.
+Finally, for a subset $V = \{v_1, \dots, v_\ell\}$ of~$Q_0$, we let~$\bar Q\blinkers{V} \eqdef ((\bar Q\blinkers{v_1})\blinkers{v_2} \dots )\blinkers{v_\ell}$.
 \end{definition}
@@
 \item The non-kissing complex~$\NKC[\bar Q\blinkers{V}]$ is isomorphic to the subcomplex of the non-kissing complex~$\NKC[\bar Q]$ induced by walks with no corner at a vertex of~$V$.
-\item The $\b{g}$-vector fan~$\gvectorFan[\bar Q\blinkers{V}]$ is the section~$\set{C \in \gvectorFan}{C \subseteq V^\perp}$ of the $\b{g}$-vector fan~$\gvectorFan$ by the coordinate plane~$V^\perp \eqdef \set{\b{x} \in \R^{Q_0}}{\dotprod{\b{e}_v}{\b{x}} = 0 \text{ for all } v \in V}$.
+\item The $\b{g}$-vector fan~$\gvectorFan[\bar Q\blinkers{V}]$ is the section~$\set{C \in \gvectorFan}{C \subseteq V^\perp}$ of the $\b{g}$-vector fan~$\gvectorFan$ by the  plane~$V^\perp \eqdef \set{\b{x} \in \R^{Q_0}}{\dotprod{\b{e}_v}{\b{x}} = 0 \text{ for all } v \in V}$.
 \item When~$\NKC$ is finite, the normal fan of the projection of the non-kissing associahedron~$\Asso$ to the coordinate plane~$V^\perp$ is the $\b{g}$-vector fan~$\gvectorFan[\bar Q\blinkers{V}]$.
@@
 
-Moreover, this correspondence sends peaks (resp.~deeps) of~$\omega$ to peaks (resp.~deeps) of~$\omega\blinkers{V}$.
+Moreover, this correspondence sends peaks (resp.~deeps) of~$\omega$ to peaks (resp. deeps) of~$\omega\blinkers{V}$.
 Since the $v$-th coordinate of the $\b{g}$-vector of a walk~$\omega$ is the number of peaks minus the number of deeps of~$\omega$ at~$v$, we obtain that
@@
 
-\begin{figure}[t]
-	\capstart
-	\centerline{\includegraphics[width=1.2\textwidth]{exmKillVertices}}
-	\caption{All possible coordinate projections of the non-kissing associahedra~$\Asso$ for two specific gentle bound quivers.}
-	\label{fig:exmKillVertices}
-\end{figure}
+\captionsetup{width=1.5\textwidth}
+\hvFloat[floatPos=p, capWidth=h, capPos=r, capAngle=90, objectAngle=90, capVPos=c, objectPos=c]{figure}
+{\includegraphics[scale=.34]{exmKillVertices}}
+{All possible coordinate projections of the non-kissing associahedra~$\Asso$ for two specific gentle bound quivers.}
+{fig:exmKillVertices}
+\captionsetup{width=\textwidth}
+
+%\begin{figure}[t]
+%	\capstart
+%	\centerline{\includegraphics[width=1.2\textwidth]{exmKillVertices}}
+%	\caption{All possible coordinate projections of the non-kissing associahedra~$\Asso$ for two specific gentle bound quivers.}
+%	\label{fig:exmKillVertices}
+%\end{figure}
 \end{example}
@@
 
-\addtocontents{toc}{\vspace{.3cm}}
-\section*{Acknowledgements}
-
-We benefited form various discussions and several useful comments on a preliminary version of this paper.
-We are particularly grateful to F.~Chapoton for initially pointing us in the direction of this paper, to A.~Garver and T.~McConville for important inputs on Part~\ref{part:lattice} (including pointing out to us the need of Theorem~\ref{thm:characterizationCongruenceUniform2}), to T.~Manneville and S.~Stella for their help on Part~\ref{part:geometry}, to L.~Demonet for the observation of Remarks~\ref{rem:linDep} and~\ref{rem:polytope}, and to S.~Schroll for her valuable comments on Part~\ref{part:algebra}.
-We also thank T.~Br\"ustle, O.~Iyama, N.~Reading, H.~Thomas for discussions on their ongoing projects mentioned in the introduction.
-This work was carried out while the first author was visiting Paris 7. He would like to thank his colleagues there, and especially \mbox{P.~Le Meur}, for a stimulating atmosphere.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\backmatter
 
@@
 \label{sec:biblio}
+
+\printindex
 

### 2018-07-12 secondPaper/accordionComplexSurfaces.tex
last changes

@@
 
-\thanks{YP, VP and PGP were partially supported by the French ANR grant SC3A~(15\,CE40\,0004\,01).}
+\thanks{YP, VP and PGP were partially supported by the French ANR grant SC3A~(15\,CE40\,0004\,01). VP was partially supported by the French ANR grant CAPPS~(17\,CE40\,0018).}
 
@@
 	\caption{Some locally gentle quivers (top) and their blossoming quivers (bottom).
-Initial vertices are solid and labeled while blossom vertices are hollow, and initial arcs are bold while blossom arcs are thin.}
+Initial vertices are solid and labeled while blossom vertices are hollow, and initial arrows are bold while blossom arrows are thin.}
 	\label{fig:quivers}
@@
 Note that~$\bar Q\blossom$ has~$2|Q_0|-|Q_1|$ incoming blossom arrows and~$2|Q_0|-|Q_1|$ outgoing blossom arrows.
-Therefore, it has $|Q_0\blossom| = |Q_0| + 2(2|Q_0|-|Q_1|) = 5|Q_0|-2|Q_1|$ vertices and~$|Q_1\blossom| = |Q_1| + 2(2|Q_0|-|Q_1|) = 4|Q_0|-|Q_1|$ arrows.
+Therefore, it has $|Q_0\blossom| = |Q_0| + 2(2|Q_0|-|Q_1|) = 5|Q_0|-2|Q_1|$ vertices and~${|Q_1\blossom| = |Q_1| + 2(2|Q_0|-|Q_1|) = 4|Q_0|-|Q_1|}$ arrows.
 \end{remark}
@@
 The terminology and notations in the following definitions is borrowed from~\cite{ButlerRingel, Crawley-Boevey}.
+
+For any arrow~$\alpha$ of~$Q$, define a formal inverse~$\alpha^{-1}$ with the properties that~${s(\alpha^{-1}) = t(\alpha)}$, $t(\alpha^{-1}) = s(\alpha)$, $\alpha^{-1}\alpha = \varepsilon_{t(\alpha)}$ and~$\alpha\alpha^{-1} = \varepsilon_{s(\alpha)}$, where~$\varepsilon_v$ is the path of length zero starting and ending at the vertex~$v \in Q_0$.
+% Furthermore, let~$(\alpha^{-1})^{-1}=\alpha$; thus~$(-)^{-1}$ is an involution on the set of arrows and formal inverses of arrows of~$Q$.
+We extend this involution to the set of all paths involving arrows or their formal inverses by further setting~$(\varepsilon_v)^{-1} = \varepsilon_v$ for all vertices~$v \in Q_0$.
 
@@
 The duality provides a bijection~$v\in (Q_\dissection)_0\mapsto v\dual\in (Q_{\dissection\dual})_0$, and also induces a bijection~${\alpha \in (Q_\dissection)_1 \mapsto \alpha\dual \in (Q_{\dissection\dual})_1}$ with~$s(\alpha\dual) = t(\alpha)\dual$ and~$t(\alpha\dual) = s(\alpha)\dual$.
- Moreover, for any two composable arrows~$\alpha,\beta\in(Q_\dissection)_0$, we have~$\alpha\beta\in I_\dissection$ if and only if~$s(\alpha),t(\alpha),t(\beta)$ are three consecutive edges of a~$\dissection$-cell~$f$, if and only if~$s(\alpha)\dual,t(\alpha)\dual,t(\beta)\dual$ are three consecutive arcs in~$\dissection\dual$ ending in~$f\dual$, if and only if~$\beta\dual\alpha\dual\notin I_{\dissection\dual}$.
+ Moreover, for any two composable arrows~$\alpha,\beta\in(Q_\dissection)_0$, we have~$\alpha\beta\in I_\dissection$ if and only if~$s(\alpha),t(\alpha),t(\beta)$ are three consecutive edges of a~$\dissection$-cell~$f$, if and only if~$s(\alpha)\dual,t(\alpha)\dual,t(\beta)\dual$ are three consecutive edges in~$\dissection\dual$ ending in~$f\dual$, if and only if~$\beta\dual\alpha\dual\notin I_{\dissection\dual}$.
 \end{proof}
@@
       We denote by~$p$ the number of infinite cyclic straight walks in~$\bar Q$.
-\item \label{item:arcs}
+\item \label{item:edges}
       The dissection~$\dissection_{\bar Q}$ has one edge for each vertex~$v \in \bar Q_0$, obtained by concatenation of the sides~$\Enrt{\alpha} = \Enrs{\beta}$ and~$\Enrt{\alpha'} = \Enrs{\beta'}$ where~$v = t(\alpha) = s(\beta) = t(\alpha') = s(\beta')$, $\alpha\beta \notin I$ and~$\alpha'\beta' \notin I$.
@@
 
-The major difference with \cite{OpperPlamondonSchroll} is the application of the surface of a (locally) gentle algebra: 
-there, it is used as a model for the derived category of the gentle algebra (graded arcs correspond to indecomposable objects in that category),
-while here, it will be used as a model for walks in~$\bar Q$ ($\dissection_{\bar Q}$-accordions will correspond to walks in~$\bar{Q}$, see Proposition \ref{prop:walks=arcs}).
+The major difference with \cite{OpperPlamondonSchroll} is the application of the surface of a (locally) gentle algebra: there, it is used as a model for the derived category of the gentle algebra (graded arcs correspond to indecomposable objects in that category), while here, it will be used as a model for walks in~$\bar Q$ ($\dissection_{\bar Q}$-accordions will correspond to walks in~$\bar{Q}$, see Proposition \ref{prop:walks=arcs}).
 \end{remark}
@@
 We apply Remark~\ref{rem:propertiesSurface} to understand the corresponding surfaces.
-The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}\,(\ref{item:boundary})) form a cycle with green and red arrows alternating.
+The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}\,\eqref{item:boundary}) form a cycle with green and red arrows alternating.
 Moreover, $\bar Q$ and~$\bar Q\koszul$ have no infinite straight walks.
@@
 We apply Remark~\ref{rem:propertiesSurface} to understand the corresponding surfaces.
-The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}\,(\ref{item:boundary})) look like~\raisebox{-.1cm}{\includegraphics[scale=.3]{reversedPathsPM}}.
+The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}\,\eqref{item:boundary}) look like~\raisebox{-.1cm}{\includegraphics[scale=.3]{reversedPathsPM}}.
 Moreover, $\bar Q$ has no infinite straight walk, while~$\bar Q\koszul$ has~$|Q_0|-1$ infinite straight walks.
@@
 We apply Remark~\ref{rem:propertiesSurface} to understand the corresponding surfaces.
-The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}\,(\ref{item:boundary})) look like~\raisebox{-.1cm}{\includegraphics[scale=.3]{doublePathsPModd}} when~$|Q_0|$ is odd and~\raisebox{-.1cm}{\includegraphics[scale=.3]{doublePathsPMeven}} when~$|Q_0|$ is even.
+The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}\,\eqref{item:boundary}) look like~\raisebox{-.1cm}{\includegraphics[scale=.3]{doublePathsPModd}} when~$|Q_0|$ is odd and~\raisebox{-.1cm}{\includegraphics[scale=.3]{doublePathsPMeven}} when~$|Q_0|$ is even.
 Moreover, $\bar Q$ and~$\bar Q\koszul$ have no infinite straight walks.
@@
 We apply Remark~\ref{rem:propertiesSurface} to understand the corresponding surfaces.
-The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}\,(\ref{item:boundary})) form a cycle with green and red arrows alternating.
+The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}\,\eqref{item:boundary}) form a cycle with green and red arrows alternating.
 Moreover, $\bar Q$ has~$1$ infinite straight walk, while~$\bar Q\koszul$ has none.
 Since~$|Q_1| = |Q_0|$, the corresponding surfaces are punctured disks ($1$ boundary component, $1$ puncture and genus~$0$).
-The first few corresponding surfaces are represented in \fref{fig:cyclesSurfacesBis} (see Figures~\ref{fig:surfaces} and~\ref{fig:reversedPathsSurfaces} for the cycles with $1$ or~$2$ vertices, recalling that~$\bar Q$ and~$\bar Q\koszul$ yield the same surface).
+The first few corresponding surfaces are represented in \fref{fig:cyclesSurfaces} (see Figures~\ref{fig:surfaces} and~\ref{fig:reversedPathsSurfaces} for the cycles with $1$ or~$2$ vertices, recalling that~$\bar Q$ and~$\bar Q\koszul$ yield the same surface).
 
@@
 	\caption{The surface~$\surface_{\bar Q}$ for the cycle quivers with~$3, 4, 5$ vertices.}
-	\label{fig:cyclesSurfacesBis}
+	\label{fig:cyclesSurfaces}
 \end{figure}
@@
 We apply Remark~\ref{rem:propertiesSurface} to understand the corresponding surfaces.
-The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}\,(\ref{item:boundary})) are empty since there is no blossom vertices.
+The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}\,\eqref{item:boundary}) are empty since there are no blossom vertices.
 Moreover, $\bar Q$ has~$1$ infinite straight walk when~$|Q_0|$ is odd and~$2$ when~$|Q_0|$ is even, and~$\bar Q\koszul$ always has~$2$ infinite straight walks.
@@
 Let~$\bar Q$ be a locally gentle bound quiver.
-For each arc of the dissection~$\dissection_{\bar Q}$ on~$\surface_{\bar Q}$, we fix a point on the interior of this arc, which we call its ``middle point'' (this is the black vertex on the pictures).
+For each edge of the dissection~$\dissection_{\bar Q}$ on~$\surface_{\bar Q}$, we fix a point on the interior of this edge, which we call its ``middle point'' (this is the black vertex on the pictures).
 To each walk on~$\bar Q$, we will now associate a~$\dissection_{\bar Q}$-accordion.
@@
 \label{def:curveOfAnArrow}
-For any arrow~$\alpha$ on $\bar Q\blossom$, let~$\curveof(\alpha)$ be the curve on~$\surface_{\bar Q}$ which goes from the middle point of the arc corresponding to $s(\alpha)$ to the middle point of the arc corresponding to $t(\alpha)$ by following the angle corresponding to~$\alpha$.
+For any arrow~$\alpha$ on $\bar Q\blossom$, let~$\curveof(\alpha)$ be the curve on~$\surface_{\bar Q}$ which goes from the middle point of the edge of~$\dissection$ corresponding to $s(\alpha)$ to the middle point of the edge of~$\dissection$ corresponding to $t(\alpha)$ by following the angle corresponding to~$\alpha$.
 Define~$\curveof(\alpha^{-1})$ to be~$\curveof(\alpha)^{-1}$.
@@
 \begin{proof}
-We can assume that~$\gamma$ intersects itself and the arcs of~$\dissection_{\bar Q}$ transversaly and minimally, in the sense that~$\gamma$ does not cross an arc twice in succession in opposite directions (see Definition~\ref{def:crossingCurves}).
-Then~$\gamma$ is completely determined by its sequence of intersection points with the arcs of~$\dissection_{\bar Q}$, since the dissection is cellular.
-Two successive intersection points in this sequence define an angle between two arcs of~$\dissection_{\bar Q}$, which corresponds to an arrow in~$\bar Q$.
+We can assume that~$\gamma$ intersects itself and the edges of~$\dissection_{\bar Q}$ transversaly and minimally, in the sense that~$\gamma$ does not cross an edge twice in succession in opposite directions (see Definition~\ref{def:crossingCurves}).
+Then~$\gamma$ is completely determined by its sequence of intersection points with the edges of~$\dissection_{\bar Q}$, since the dissection is cellular.
+Two successive intersection points in this sequence define an angle between two edges of~$\dissection_{\bar Q}$, which corresponds to an arrow in~$\bar Q$.
 Thus the sequence of intersection points defines a walk~$\walk(\gamma)$ on~$\bar Q$.
@@
 \label{lem:nonKissing=nonCrossing}
-Let~$\omega_1$ and~$\omega_2$ be walks on~$\bar Q$.
-Then~$\omega_1$ and~$\omega_2$ are non-kissing if and only if the~$\dissection_{\bar Q}$-accordions~$\curveof(\omega_1)$ and~$\curveof(\omega_2)$ are non-crossing on~$\surface_{\bar Q}$.
+Two undirected walks~$\omega_1$ and~$\omega_2$ on~$\bar Q$ are non-kissing if and only if the corresponding $\dissection_{\bar Q}$-accordions~$\curveof(\omega_1)$ and~$\curveof(\omega_2)$ are non-crossing on~$\surface_{\bar Q}$.
 \end{lemma}
@@
 \begin{remark}
-Note that our construction of the surface~$\surface_{\bar Q}$ implies that the vertices of~$\bar Q$ are naturally identified with the intersection points of the dual edges~$a \in \dissection_{\bar Q}$ and~$a\dual \in {\dissection\dual\!\!_{\bar Q}}$.
-If we force all $\dissection$-accordions (or $\dissection\dual$-slaloms) to cross the edges of~$\dissection$ and~$\dissection\dual$ only at these intersection points, then a $\dissection$-accordion (or $\dissection\dual$-slalom) is really seen as a walk on~$\bar Q$.
+Note that our construction of the surface~$\surface_{\bar Q}$ implies that the quiver~$\bar Q$ is naturally embedded on~$\surface_{\bar Q}$.
+If we force all $\dissection$-accordions (or $\dissection\dual$-slaloms) to follow the arrows of~$\bar Q$, then a $\dissection$-accordion (or $\dissection\dual$-slalom) is really seen as a walk on~$\bar Q$.
 \end{remark}
@@
 The set of all such walks forms the \defn{peak facet}~$\set{v_\peak}{v \in Q_0}$ (resp.~the \defn{deep facet}~$\set{v_\deep}{v \in Q_0}$) of the non-kissing complex~$\RNKC$.
-As an example of Theorem~\ref{thm:complexesCoincide}, let us now describe the corresponding non-crossing facets of~$\RNCC[\surface_{\bar Q}]$.
+As an example of Theorem~\ref{thm:complexesCoincide}, let us now describe the corresponding non-crossing facets of~$\RNCC[\dissection_{\bar Q}, {{\dissection\dual}\!\!_{\bar Q}}]$.
 
@@
 
-We invite the reader to check that~$\curveof(v_\peak) = \vprevious{\edgeof(v)}$ (resp.~$\curveof(v_\deep) = \vnext{\edgeof(v)}$), where~$\edgeof(v)$ denotes the edge of~$\dissection$ corresponding to~$v \in Q_0$ (see Remark~\ref{rem:propertiesSurface}).
-Therefore, the peak facet (resp.~the deep facet) can be thought of as the dissection~$\dissection$ slightly rotated clockwise (resp.~counterclockwise) on the surface~$\surface$.
+We invite the reader to check that~$\curveof(v_\peak) = \vprevious{\edgeof(v)}$ (resp.~$\curveof(v_\deep) = \vnext{\edgeof(v)}$), where~$\edgeof(v)$ denotes the edge of~$\dissection_{\bar Q}$ corresponding to~$v \in Q_0$ (see Remark~\ref{rem:propertiesSurface}\,\eqref{item:edges}).
+Therefore, the peak facet (resp.~the deep facet) can be thought of as the dissection~$\dissection_{\bar Q}$ slightly rotated clockwise (resp.~counterclockwise) on the surface~$\surface_{\bar Q}$.
 \end{example}
@@
 Using Theorem \ref{thm:complexesCoincide}, we can translate the definition of the countercurrent order~$\prec_\alpha$ to the language of~$\dissection$-accordions (resp.~of~$\dissection\dual$-slaloms).
-An arrow~$\alpha$ in~$\bar Q\blossom$ corresponds to an angle at a point~$v$ between two arcs of~$\dissection$ (resp.~at a point~$v\dual$ between two arcs of~$\dissection\dual$).
+An arrow~$\alpha$ in~$\bar Q\blossom$ corresponds to an angle at a point~$v$ between two edges of~$\dissection$ (resp.~at a point~$v\dual$ between two edges of~$\dissection\dual$).
 Two distinct non-kissing walks~$\mu_\star, \nu_\star$ marked at~$\alpha$ in~$\bar Q$ correspond to two distinct non-crossing~$\dissection$-accordions (resp.~$\dissection\dual$-slaloms)~$\gamma$ and~$\delta$ passing in front of this angle.
@@
 The arrow~$\alpha$ then corresponds to an angle in~$\dissection$ at a vertex~$v$.  
-
- For any curve~$\gamma$ in~$F$, even though~$\gamma$ may pass through the above angle infinitely many times, there is one instance that is furthest from the angle:
- indeed, if ~$\gamma$ passes infinitely many times through~$\alpha$, then~$v$ is a puncture and~$\gamma$ circles infinitely towards it.
+% 
+For any curve~$\gamma$ in~$F$, even though~$\gamma$ may pass through the above angle infinitely many times, there is one instance that is furthest from the angle: indeed, if ~$\gamma$ passes infinitely many times through~$\alpha$, then~$v$ is a puncture and~$\gamma$ circles infinitely towards it.
 But then~$\gamma$ passes through~$\alpha$ only finitely many times before it starts circling~$v$ (in either direction), and one of these times is the furthest from~$v$.
-
+%  
 Therefore, for every curve~$\gamma\in F$, there is a maximal occurence of~$\alpha$ in~$\gamma$.
@@
 \begin{definition}
-\label{defi:distinguishedWalksAndArrows}
+\label{def:distinguishedWalksAndArrows}
 Let~$\alpha \in Q\blossom_1$ be an arrow and let~$F$ be a face of~$\NKC$ containing the straight walk passing through~$\alpha$.
@@
 
-Let~$\bar Q = (Q,I)$ be a locally gentle bound quiver, and let~$(\b{e}_v)_{v \in Q_0}$ be the standard basis of~$\R^{Q_0}$.
-
-\begin{definition}
-Let~$V \eqdef \{v_1, \dots, v_m\}$ be a multiset of vertices of~$Q_0$. We denote by~$\multiplicityVector_V \in \R^{Q_0}$ the \defn{multiplicity vector} of~$V$, defined~by:
+Let~$\bar Q = (Q,I)$ be a locally gentle bound quiver, and let~$(\b{e}_v)_{v \in Q_0}$ denote the standard basis of~$\R^{Q_0}$.
+
+\begin{definition}
+For a multiset~$V \eqdef \{v_1, \dots, v_m\}$ of vertices of~$Q_0$, we denote by~$\multiplicityVector_V \in \R^{Q_0}$ the \defn{multiplicity vector} of~$V$, defined~by
 \[
@@
 For any walk~$\omega$ of~$\bar Q$, we let~$\peaks{\omega}$ (resp.~by~$\deeps{\omega}$) be the multiset of vertices of~$Q_0$ corresponding to the peaks (resp.~deeps) of~$\omega$.
-The \defn{$\b{g}$-vector} of the walk~$\omega$ is the vector~${\gvector{\omega} \in \R^{Q_0}}$ defined as follows:
+The \defn{$\b{g}$-vector} of the walk~$\omega$ is the vector~${\gvector{\omega} \in \R^{Q_0}}$ defined by
 \[
@@
 For a set~$\Omega$ of walks, we let~$\gvectors{\Omega} \eqdef \set{\gvector{\omega}}{\omega \in \Omega}$.
-Observe that, if~$\omega$ is a straight walk, then~$\gvector{\omega} = 0$, and that, since any infinite walk~$\omega$ is eventually cyclic, the coordinates of~$\gvector{\omega}$ are finite.
+Observe that, if~$\omega$ is a straight walk, then~$\gvector{\omega} = 0$. Moreover, since any infinite walk~$\omega$ is eventually cyclic, the coordinates of~$\gvector{\omega}$ are always finite.
 \end{definition}
@@
 \begin{cases}
-\phantom{-}1 & \text{if~$\distinguishedString{\omega}{F}$ is a top substring of~$\omega$ (\ie if the distinguished arrows point outside),} \\
--1 & \text{if~$\distinguishedString{\omega}{F}$ is a bottom substring of~$\omega$ (\ie if the distinguished arrows point inside).}
+\phantom{-}1 & \text{if~$\distinguishedString{\omega}{F}$ is a top substring of~$\omega$ (\ie if~$\distinguishedArrows{\omega}{F}$ point outside),} \\
+-1 & \text{if~$\distinguishedString{\omega}{F}$ is a bottom substring of~$\omega$ (\ie if~$\distinguishedArrows{\omega}{F}$ point inside),}
 \end{cases}
 \]
+where~$\distinguishedString{\omega}{F}$ and~$\distinguishedArrows{\omega}{F}$ are the distinguished arrows of~$\omega$ in~$F$ (see Definition~\ref{def:distinguishedWalksAndArrows}).
 The \defn{$\b{c}$-vector} of a walk~$\omega$ of~$F$ is the vector~${\cvector{\omega}{F} \in \R^{Q_0}}$ defined by
@@
 Our objective is now to interpret the three families of vectors of Section~\ref{subsec:gcdVectorsWalks} in terms of accordions and slaloms on the surface.
-According to Remark~\ref{rem:propertiesSurface}\,(\ref{item:arcs}), each vertex~$p$ of~$Q$ corresponds to an edge~$\edgeof(p)$ in the dissection~$\dissection_{\bar Q}$ and  to an edge~$\dualedgeof(p) = \edgeof(p)\dual$ in the dual dissection~${\dissection\dual\!\!_{\bar Q}}$.
+According to Remark~\ref{rem:propertiesSurface}\,\eqref{item:edges}, each vertex~$p$ of~$Q$ corresponds to an edge~$\edgeof(p)$ in the dissection~$\dissection_{\bar Q}$ and  to an edge~$\dualedgeof(p) = \edgeof(p)\dual$ in the dual dissection~${\dissection\dual\!\!_{\bar Q}}$.
 Recall moreover from Lemma~\ref{lemm:curveOfAWalkIsAccordion} and Proposition~\ref{prop:accordionsSlaloms} that each non-kissing walk~$\omega$ in~$\bar Q$ corresponds to a curve~$\curveof(\omega)$ that is both a $\dissection$-accordion and a $\dissection\dual$-slalom.
@@
 We note that these interpretations were already used in~\cite{MannevillePilaud-accordion, GarverMcConville} when the surface is a disk.
+When~$\dissection$ is a triangulation of~$\surface$, these interpretations coincide with those given in terms of triangulations and laminations for cluster algebras from surfaces by S.~Fomin and D.~Thurston~\cite{FominThurston}.
 
@@
 \item The number of times that the $\dissection$-accordion~$\curveof(\omega)$ positively crosses the edge~$\edgeof(p)$ of~$\dissection$ minus the number of times it negatively crosses the edge~$\edgeof(p)$ of~$\dissection$.
-Here, the crossing is positive (resp.~negative) if the two angles of~$\dissection$ crossed by~$\curveof(\alpha)$ just before and after~$\edgeof(p)$ form a~$\SSS$ (resp.~as a~$\ZZZ$).
+Here, the crossing is positive (resp.~negative) if the two angles of~$\dissection$ crossed by~$\curveof(\alpha)$ just before and after~$\edgeof(p)$ form a~$\SSS$ (resp.~a~$\ZZZ$).
 We note that some crossings are neither positive nor negative.
@@
 \label{prop:dVectorsSurface}
-Denote by~$X_\deep$ the deep facet of the non-crossing complex as described in Example~\ref{exm:peakDeepFacets}.
-For a walk~$\omega$ of~$\bar Q$ and a vertex~$v \in Q_0$, the $v$-th entry of the $\b{d}$-vector~$\dvector{\omega}$ is the number of crossings of the curve~$\gamma(\omega)$ with the edge of~$X_\deep$ corresponding to~$v$.
+Denote by~$X_\deep \eqdef \set{\curveof(v_\peak)}{v \in Q_0}$ the deep facet of the non-crossing complex obtained by slightly rotating~$\dissection_{\bar Q}$ counterclockwise as described in Example~\ref{exm:peakDeepFacets}.
+For a walk~$\omega$ of~$\bar Q$ and a vertex~$v \in Q_0$, the $v$-th entry of the $\b{d}$-vector~$\dvector{\omega}$ is either~$-1$ if~$\omega = v_\peak$ or the number of crossings of the curve~$\gamma(\omega)$ with the edge~$\curveof(v_\peak)$ of~$X_\deep$ corresponding to~$v$.
 \end{proposition}
@@
 \begin{proof}
-For the $\b{g}$-vectors, observe that two walks~$\omega$ and~$\omega'$ whose $\b{g}$-vectors~$\gvector{\omega}$ and~$\gvector{\omega}$ have opposite signs on their~$v$-th coordinate automatically kiss at~$v$.
+For the $\b{g}$-vectors, observe that two walks~$\omega$ and~$\omega'$ whose $\b{g}$-vectors~$\gvector{\omega}$ and~$\gvector{\omega'}$ have opposite signs on their~$v$-th coordinate automatically kiss at~$v$.
 For $\b{c}$- and $\b{d}$-vectors, the statement is immediate from the definition.

### 2018-07-12 firstPaper/firstPaperLong/nonKissingComplex.tex

@@
 
-The interest for non-kissing complexes is motivated by relevant instances arising from particular shapes.
+The interest in non-kissing complexes is motivated by relevant instances arising from particular shapes.
 As already observed in~\cite[Sect.~10]{McConville}, when the shape is a ribbon, the non-kissing complex is an associahedron (the simplicial complex of dissections of a polygon), and the non-kissing lattice is a type~$A$ Cambrian lattice of N.~Reading~\cite{Reading-CambrianLattices}.
@@
 On the combinatorial side, we provide a purely combinatorial proof that the non-kissing complex over a gentle bound quiver is a pseudomanifold.
-This involves in particular a precise description of the flip inspired from~\cite[Sect.~3]{McConville}.
+This involves in particular a precise description of flips inspired from~\cite[Sect.~3]{McConville}.
 
@@
 In general, when $\bar Q$ is \mbox{$\tau$-tilting} finite, the transitive closure of the increasing flip graph is isomorphic to the lattice of torsion classes, and we therefore call it the non-kissing lattice.
-Our main lattice-theoretic result is the following extension of a remarquable result of T.~McConville~\cite{McConville}.
+Our main lattice-theoretic result is the following extension of a remarkable result of T.~McConville~\cite{McConville}.
 
@@
 \end{enumerate}
-The algebra~$kQ/I$ is called a \defn{string algebra}.
+The algebra~$kQ/I$ associated to a gentle bound quiver~$\bar Q$ is called a \defn{string algebra}.
 \end{definition}
@@
 \\[.3cm]
-Finally, both the Auslander-Reiten translation~$\tau$ and its inverse~$\tau^{-1}$ preserve the band modules: for a band~$\varpi$ of~$\bar Q$, we have~$\tau \big( M(\varpi) \big) = M(\varpi) = \tau^{-1} \big( M(\varpi) \big)$.
+Finally, both the Auslander-Reiten translation~$\tau$ and its inverse~$\tau^{-1}$ preserve the band modules: for a band~$\varpi$ of~$\bar Q$, we have~$\tau \big( M(\varpi, \lambda, d) \big) = M(\varpi, \lambda, d)$ and $\tau^{-1} \big( M(\varpi, \lambda, d) \big)=M(\varpi, \lambda, d)$.
 \end{theorem}

### 2018-07-12 firstPaper/firstPaperShort/nonKissingComplex.tex

--- 2018-07-04 firstPaper/nonKissingComplex.tex
@@
 In general, when $\bar Q$ is $\tau$-tilting finite, the transitive closure of the increasing flip graph is isomorphic to the lattice of torsion classes, and we therefore call it the non-kissing lattice.
-Our main lattice-theoretic result is the following extension of a remarquable result of T.~McConville~\cite{McConville}.
+Our main lattice-theoretic result is the following extension of a remarkable result of T.~McConville~\cite{McConville}.
 
@@
 \end{itemize}
-The algebra~$kQ/I$ is called a \defn{string algebra}.
+The algebra~$kQ/I$ associated to a gentle bound quiver~$\bar Q$ is called a \defn{string algebra}.
 \end{definition}
@@
 \begin{itemize}
-\item $\Hom{A} (M, \tau P[1]) = 0$ for any representation or shifted projective~$M$,
-\item $\Hom{A} (P[1], \tau M) = \Hom{A} (P,M)$ for any representation~$M$.
+\item $\Hom{A} (M, \tau P[1]) = \Hom{A} (P,M)$ for any representation or shifted projective~$M$,
+\item $\Hom{A} (P[1], \tau M) = 0$ for any representation~$M$.
 \end{itemize}
@@
 \[
-\Hom{A} (M, \tau N) \cong \Hom{K^b(\operatorname{proj} A)}(P_M, P_N[1]),
+\Hom{A} (M, \tau N) \cong \Hom{K^b(\operatorname{proj} A)}(P_N, P_M[1]),
 \]

### 2018-07-12 secondPaper/accordionComplexSurfaces.tex
I hate the word quiver

--- 2018-07-12 secondPaper/accordionComplexSurfaces.tex
@@
 \begin{enumerate}[(i)]
-\item each vertex~$v \in Q_0$ has at most two incoming and two outgoing arrows,
+\item each vertex~$a \in Q_0$ has at most two incoming and two outgoing arrows,
 \item the ideal~$I$ is generated by paths of length exactly two,
@@
 \label{def:blossomingQuiver}
-A locally gentle bound quiver~$\bar Q$ is \defn{complete} if any vertex~$v \in Q_0$ is incident to either one ($v$ is a leaf) or four arrows ($v$ is an internal vertex).
+A locally gentle bound quiver~$\bar Q$ is \defn{complete} if any vertex~$a \in Q_0$ is incident to either one ($a$ is a leaf) or four arrows ($a$ is an internal vertex).
 The \defn{pruned subquiver} of a quiver~$\bar Q$ is the locally gentle quiver obtained by deleting all leaves of~$\bar Q$ (degree one vertices) and their incident arrows.
@@
 We let~$s(\rho) \eqdef s(\alpha_1^{\varepsilon_1})$ and~$t(\rho) \eqdef t(\alpha_\ell^{\varepsilon_\ell})$ denote the source and target of~$\rho$.
-For each vertex~$v \in Q_0$, there is also a \defn{string of length zero}, denoted by~$\varepsilon_v$, that starts and ends at~$v$.
+For each vertex~$a \in Q_0$, there is also a \defn{string of length zero}, denoted by~$\varepsilon_a$, that starts and ends at~$a$.
 %We denote by~$\strings(\bar Q)$ the set of strings on~$\bar Q$.
 %We usually denote strings by~$\rho, \sigma, \tau$.
-%We call \defn{negative simple string} a formal word of length zero of the form $-v$, where $v$ is any vertex of $Q_0$. We denote by
+%We call \defn{negative simple string} a formal word of length zero of the form $-a$, where $a$ is any vertex of $Q_0$. We denote by
 %\(
-%\strings^\pm_{\ge -1}(\bar Q) \eqdef \strings^\pm(\bar Q) \sqcup \set{-v}{v \in Q_0}
+%\strings^\pm_{\ge -1}(\bar Q) \eqdef \strings^\pm(\bar Q) \sqcup \set{-a}{a \in Q_0}
 %\)
 %the set of \defn{almost positive unoriented strings}.
-%Note that~$\varepsilon_v$ and~$-v$ are different almost positive strings.
+%Note that~$\varepsilon_a$ and~$-a$ are different almost positive strings.
 %\end{enumerate}
@@
 \end{itemize}
-Note that the string~$\varepsilon_v$ is a substring of~$\omega$ for each occurence of~$v$ as a vertex of~$\omega$.
+Note that the string~$\varepsilon_a$ is a substring of~$\omega$ for each occurence of~$a$ as a vertex of~$\omega$.
 We denote by~$\Sigma(\omega)$ the set of substrings of~$\omega$.
@@
 A \defn{peak walk} (resp.~\defn{deep walk}) is a walk with a unique corner (in other words, it switches orientation only once), which is a peak (resp.~deep).
-For~$v \in Q_0$, we denote by~$v_\peak$ the peak walk with peak at~$v$ and by~$v_\deep$ the deep walk with deep~at~$v$.
+For~$a \in Q_0$, we denote by~$a_\peak$ the peak walk with peak at~$a$ and by~$a_\deep$ the deep walk with deep~at~$a$.
 \end{definition}
@@
 We say that~$\omega$ and~$\omega'$ are \defn{kissing} if~$\omega$ kisses~$\omega'$ or~$\omega'$ kisses~$\omega$ (or both).
-Note that we authorize the situation where the commmon finite substring is reduced to a vertex~$v$, meaning that~$v$ is a peak of~$\omega$ and a deep of~$\omega'$.
+Note that we authorize the situation where the commmon finite substring is reduced to a vertex~$a$, meaning that~$a$ is a peak of~$\omega$ and a deep of~$\omega'$.
 Observe also that~$\omega$ can kiss~$\omega'$ several times, that~$\omega$ and~$\omega'$ can mutually kiss, and that~$\omega$ can kiss itself.
@@
 \begin{proof}
-The duality provides a bijection~$v\in (Q_\dissection)_0\mapsto v\dual\in (Q_{\dissection\dual})_0$, and also induces a bijection~${\alpha \in (Q_\dissection)_1 \mapsto \alpha\dual \in (Q_{\dissection\dual})_1}$ with~$s(\alpha\dual) = t(\alpha)\dual$ and~$t(\alpha\dual) = s(\alpha)\dual$.
+The duality provides a bijection~$a\in (Q_\dissection)_0\mapsto a\dual\in (Q_{\dissection\dual})_0$, and also induces a bijection~${\alpha \in (Q_\dissection)_1 \mapsto \alpha\dual \in (Q_{\dissection\dual})_1}$ with~$s(\alpha\dual) = t(\alpha)\dual$ and~$t(\alpha\dual) = s(\alpha)\dual$.
  Moreover, for any two composable arrows~$\alpha,\beta\in(Q_\dissection)_0$, we have~$\alpha\beta\in I_\dissection$ if and only if~$s(\alpha),t(\alpha),t(\beta)$ are three consecutive edges of a~$\dissection$-cell~$f$, if and only if~$s(\alpha)\dual,t(\alpha)\dual,t(\beta)\dual$ are three consecutive arcs in~$\dissection\dual$ ending in~$f\dual$, if and only if~$\beta\dual\alpha\dual\notin I_{\dissection\dual}$.
@@
 \item \label{item:arcs}
-      The dissection~$\dissection_{\bar Q}$ has one edge for each vertex~$v \in \bar Q_0$, obtained by concatenation of the sides~$\Enrt{\alpha} = \Enrs{\beta}$ and~$\Enrt{\alpha'} = \Enrs{\beta'}$ where~$v = t(\alpha) = s(\beta) = t(\alpha') = s(\beta')$, $\alpha\beta \notin I$ and~$\alpha'\beta' \notin I$.
-We denote by~$\edgeof(v)$ the edge of~$\dissection_{\bar Q}$ corresponding to~$v$.
+      The dissection~$\dissection_{\bar Q}$ has one edge for each vertex~$a \in \bar Q_0$, obtained by concatenation of the sides~$\Enrt{\alpha} = \Enrs{\beta}$ and~$\Enrt{\alpha'} = \Enrs{\beta'}$ where~$a = t(\alpha) = s(\beta) = t(\alpha') = s(\beta')$, $\alpha\beta \notin I$ and~$\alpha'\beta' \notin I$.
+We denote by~$\edgeof(a)$ the edge of~$\dissection_{\bar Q}$ corresponding to~$a$.
 \item The dissection~$\dissection_{\bar Q}$ has one $\ell$-cell for each straight walk of length~$\ell$ in~$\bar Q\koszul$.
-\item Similar statements hold dually for~${{V\dual}\!\!_{\bar Q}}$ and~${\dissection\dual\!\!_{\bar Q}}$, and the notations~$p\dual$ and~$\dualedgeof(v)$ are defined similarly.
+\item Similar statements hold dually for~${{V\dual}\!\!_{\bar Q}}$ and~${\dissection\dual\!\!_{\bar Q}}$, and the notations~$p\dual$ and~$\dualedgeof(a)$ are defined similarly.
 \item The number of punctures of~$\surface_{\bar Q}$ is the number~$p + p\dual$ of infinite straight walks in~$\bar Q$ and in~$\bar Q\koszul$.
@@
 \label{exm:peakDeepFacets}
-We have seen in Definition~\ref{def:straightBending} that each vertex~$v$ of~$Q$ gives rise to a \defn{peak walk}~$v_\peak$ (resp.~\defn{deep walk}~$v_\deep$) with a single peak (resp.~deep) at~$v$ and no other corner.
-The set of all such walks forms the \defn{peak facet}~$\set{v_\peak}{v \in Q_0}$ (resp.~the \defn{deep facet}~$\set{v_\deep}{v \in Q_0}$) of the non-kissing complex~$\RNKC$.
+We have seen in Definition~\ref{def:straightBending} that each vertex~$a$ of~$Q$ gives rise to a \defn{peak walk}~$a_\peak$ (resp.~\defn{deep walk}~$a_\deep$) with a single peak (resp.~deep) at~$a$ and no other corner.
+The set of all such walks forms the \defn{peak facet}~$\set{a_\peak}{a \in Q_0}$ (resp.~the \defn{deep facet}~$\set{a_\deep}{a \in Q_0}$) of the non-kissing complex~$\RNKC$.
 As an example of Theorem~\ref{thm:complexesCoincide}, let us now describe the corresponding non-crossing facets of~$\RNCC[\surface_{\bar Q}]$.
@@
 
-We invite the reader to check that~$\curveof(v_\peak) = \vprevious{\edgeof(v)}$ (resp.~$\curveof(v_\deep) = \vnext{\edgeof(v)}$), where~$\edgeof(v)$ denotes the edge of~$\dissection$ corresponding to~$v \in Q_0$ (see Remark~\ref{rem:propertiesSurface}).
+We invite the reader to check that~$\curveof(a_\peak) = \vprevious{\edgeof(a)}$ (resp.~$\curveof(a_\deep) = \vnext{\edgeof(a)}$), where~$\edgeof(a)$ denotes the edge of~$\dissection$ corresponding to~$a \in Q_0$ (see Remark~\ref{rem:propertiesSurface}).
 Therefore, the peak facet (resp.~the deep facet) can be thought of as the dissection~$\dissection$ slightly rotated clockwise (resp.~counterclockwise) on the surface~$\surface$.
@@
 Using Theorem \ref{thm:complexesCoincide}, we can translate the definition of the countercurrent order~$\prec_\alpha$ to the language of~$\dissection$-accordions (resp.~of~$\dissection\dual$-slaloms).
-An arrow~$\alpha$ in~$\bar Q\blossom$ corresponds to an angle at a point~$v$ between two arcs of~$\dissection$ (resp.~at a point~$v\dual$ between two arcs of~$\dissection\dual$).
+An arrow~$\alpha$ in~$\bar Q\blossom$ corresponds to an angle at a point~$v$ between two arcs of~$\dissection$ (resp.~at a point~$f\dual$,~$v\in f$, between two arcs of~$\dissection\dual$).
 Two distinct non-kissing walks~$\mu_\star, \nu_\star$ marked at~$\alpha$ in~$\bar Q$ correspond to two distinct non-crossing~$\dissection$-accordions (resp.~$\dissection\dual$-slaloms)~$\gamma$ and~$\delta$ passing in front of this angle.
-Then~$\gamma \prec_\alpha \delta$ if~$\gamma$ passes closer to~$v$ (resp.~further to~$v\dual$) than~$\delta$ does.
+Then~$\gamma \prec_\alpha \delta$ if~$\gamma$ passes closer to~$v$ (resp.~further to~$f\dual$) than~$\delta$ does.
 These interpretations of~$\prec_\alpha$ on the surface where already considered in the case of the disk in~\cite{GarverMcConville, MannevillePilaud-accordion}.
@@
 
-Let~$\bar Q = (Q,I)$ be a locally gentle bound quiver, and let~$(\b{e}_v)_{v \in Q_0}$ be the standard basis of~$\R^{Q_0}$.
-
-\begin{definition}
-Let~$V \eqdef \{v_1, \dots, v_m\}$ be a multiset of vertices of~$Q_0$. We denote by~$\multiplicityVector_V \in \R^{Q_0}$ the \defn{multiplicity vector} of~$V$, defined~by:
+Let~$\bar Q = (Q,I)$ be a locally gentle bound quiver, and let~$(\b{e}_a)_{a \in Q_0}$ be the standard basis of~$\R^{Q_0}$.
+
+\begin{definition}
+Let~$V \eqdef \{a_1, \dots, a_m\}$ be a multiset of vertices of~$Q_0$. We denote by~$\multiplicityVector_V \in \R^{Q_0}$ the \defn{multiplicity vector} of~$V$, defined~by:
 \[
-\multiplicityVector_V \eqdef \sum_{i \in [m]} \b{e}_{v_i} = \sum_{v \in Q_0} |\set{i \in [m]}{v_i = v}| \, \b{e}_v.
+\multiplicityVector_V \eqdef \sum_{i \in [m]} \b{e}_{a_i} = \sum_{a \in Q_0} |\set{i \in [m]}{a_i = a}| \, \b{e}_a.
 \]
@@
 \begin{cases}
-- \b{e}_v & \text{if $\omega$ is the deep walk~$v_\deep$ with a unique deep at~$v$,} \\
-\displaystyle \sum_{v \in Q_0} \kn(\omega, v_\deep) \, \b{e}_v & \text{otherwise.}
+- \b{e}_a & \text{if $\omega$ is the deep walk~$a_\deep$ with a unique deep at~$a$,} \\
+\displaystyle \sum_{a \in Q_0} \kn(\omega, a_\deep) \, \b{e}_a & \text{otherwise.}
 \end{cases}
@@
 Our objective is now to interpret the three families of vectors of Section~\ref{subsec:gcdVectorsWalks} in terms of accordions and slaloms on the surface.
-According to Remark~\ref{rem:propertiesSurface}\,(\ref{item:arcs}), each vertex~$p$ of~$Q$ corresponds to an edge~$\edgeof(p)$ in the dissection~$\dissection_{\bar Q}$ and  to an edge~$\dualedgeof(p) = \edgeof(p)\dual$ in the dual dissection~${\dissection\dual\!\!_{\bar Q}}$.
+According to Remark~\ref{rem:propertiesSurface}\,(\ref{item:arcs}), each vertex~$a$ of~$Q$ corresponds to an edge~$\edgeof(a)$ in the dissection~$\dissection_{\bar Q}$ and  to an edge~$\dualedgeof(a) = \edgeof(a)\dual$ in the dual dissection~${\dissection\dual\!\!_{\bar Q}}$.
 Recall moreover from Lemma~\ref{lemm:curveOfAWalkIsAccordion} and Proposition~\ref{prop:accordionsSlaloms} that each non-kissing walk~$\omega$ in~$\bar Q$ corresponds to a curve~$\curveof(\omega)$ that is both a $\dissection$-accordion and a $\dissection\dual$-slalom.
@@
 \label{prop:gVectorsSurface}
-For a walk~$\omega$ of~$\bar Q$ and a vertex~$p \in Q_0$, the $p$-th entry of the $\b{g}$-vector~$\gvector{\omega}$ is given~by:
+For a walk~$\omega$ of~$\bar Q$ and a vertex~$a \in Q_0$, the $a$-th entry of the $\b{g}$-vector~$\gvector{\omega}$ is given~by:
 \begin{enumerate}[(i)]
-\item The number of times that the $\dissection$-accordion~$\curveof(\omega)$ positively crosses the edge~$\edgeof(p)$ of~$\dissection$ minus the number of times it negatively crosses the edge~$\edgeof(p)$ of~$\dissection$.
-Here, the crossing is positive (resp.~negative) if the two angles of~$\dissection$ crossed by~$\curveof(\alpha)$ just before and after~$\edgeof(p)$ form a~$\SSS$ (resp.~as a~$\ZZZ$).
+\item The number of times that the $\dissection$-accordion~$\curveof(\omega)$ positively crosses the edge~$\edgeof(a)$ of~$\dissection$ minus the number of times it negatively crosses the edge~$\edgeof(a)$ of~$\dissection$.
+Here, the crossing is positive (resp.~negative) if the two angles of~$\dissection$ crossed by~$\curveof(\alpha)$ just before and after~$\edgeof(a)$ form a~$\SSS$ (resp.~as a~$\ZZZ$).
 We note that some crossings are neither positive nor negative.
-\item The number of times that the $\dissection\dual$-slalom~$\curveof(\omega)$ positively crosses the edge~$\dualedgeof(p)$ of~$\dissection\dual$ minus the number of times it negatively crosses the edge~$\dualedgeof(p)$ of~$\dissection\dual$.
+\item The number of times that the $\dissection\dual$-slalom~$\curveof(\omega)$ positively crosses the edge~$\dualedgeof(a)$ of~$\dissection\dual$ minus the number of times it negatively crosses the edge~$\dualedgeof(a)$ of~$\dissection\dual$.
 Here, the crossing is positive when~$\curveof(\omega)$ leaves a face~$u\dual$ to enter a face~$v\dual$ with the vertex~$u$ being to its right (and thus with~$v$ being to its left), and the crossing is negative otherwise.
@@
 Call \defn{distinguished subcurve} of~$\curveof(\omega)$ in~$\curveof(F)$ the part of~$\curveof(\omega)$ which lies strictly between the two angles of~$\dissection$ (or of~$\dissection\dual$) where~$\curveof(\omega)$ is maximal (see Remark~\ref{rem:countercurrentOrderOnSurface}).
-For a vertex~$v \in Q_0$, the $v$-th entry of the $\b{c}$-vector~$\cvector{\omega}{F}$ is up to the sign given by:
+For a vertex~$a \in Q_0$, the $a$-th entry of the $\b{c}$-vector~$\cvector{\omega}{F}$ is up to the sign given by:
 \begin{enumerate}[(i)]
-\item the number of crossings between the distinguished subcurve of~$\curveof(\omega)$ in~$\curveof(F)$ and the edge~$\edgeof(v)$ of the dissection~$\dissection$,
-\item the number of times the distinguished subcurve of~$\curveof(\omega)$ in~$\curveof(F)$ follows the edge~$\dualedgeof(v)$ of the dual dissection~$\dissection\dual$.
-Here, we say that a curve~$\delta$ follows~$\dualedgeof(v)$ if~$\dualedgeof(v)$ lies on the boundary opposite to~$u$ of a face~$u\dual$ of~$\dissection\dual$ crossed by~$\delta$.
+\item the number of crossings between the distinguished subcurve of~$\curveof(\omega)$ in~$\curveof(F)$ and the edge~$\edgeof(a)$ of the dissection~$\dissection$,
+\item the number of times the distinguished subcurve of~$\curveof(\omega)$ in~$\curveof(F)$ follows the edge~$\dualedgeof(a)$ of the dual dissection~$\dissection\dual$.
+Here, we say that a curve~$\delta$ follows~$\dualedgeof(a)$ if~$\dualedgeof(a)$ lies on the boundary opposite to~$u$ of a face~$u\dual$ of~$\dissection\dual$ crossed by~$\delta$.
 \end{enumerate}
@@
 Denote by~$X_\deep$ the deep facet of the non-crossing complex as described in Example~\ref{exm:peakDeepFacets}.
-For a walk~$\omega$ of~$\bar Q$ and a vertex~$v \in Q_0$, the $v$-th entry of the $\b{d}$-vector~$\dvector{\omega}$ is the number of crossings of the curve~$\gamma(\omega)$ with the edge of~$X_\deep$ corresponding to~$v$.
+For a walk~$\omega$ of~$\bar Q$ and a vertex~$a \in Q_0$, the $a$-th entry of the $\b{d}$-vector~$\dvector{\omega}$ is the number of crossings of the curve~$\gamma(\omega)$ with the edge of~$X_\deep$ corresponding to~$a$.
 \end{proposition}
@@
 \begin{itemize}
-\item for~$v \in Q_0$, the~$v$-th coordinates of all $\b{g}$-vectors~$\gvector{\omega}$ for~$\omega \in F$ have the same sign,
+\item for~$a \in Q_0$, the~$a$-th coordinates of all $\b{g}$-vectors~$\gvector{\omega}$ for~$\omega \in F$ have the same sign,
 \item for any~$\omega \in F$, all coordinates of the $\b{c}$-vector~$\cvector{\omega}{F}$ have the same sign,
@@
 \begin{proof}
-For the $\b{g}$-vectors, observe that two walks~$\omega$ and~$\omega'$ whose $\b{g}$-vectors~$\gvector{\omega}$ and~$\gvector{\omega}$ have opposite signs on their~$v$-th coordinate automatically kiss at~$v$.
+For the $\b{g}$-vectors, observe that two walks~$\omega$ and~$\omega'$ whose $\b{g}$-vectors~$\gvector{\omega}$ and~$\gvector{\omega}$ have opposite signs on their~$a$-th coordinate automatically kiss at~$a$.
 For $\b{c}$- and $\b{d}$-vectors, the statement is immediate from the definition.

### 2018-07-12 firstPaper/firstPaperLong/nonKissingComplex.tex
Changes to first paper.

@@
 	\end{enumerate}
-\item[(ii)] \defn{dance} with~$\rho'$ (or~$(\rho')^{-1}$) if there is some common substring~$\xi$ on top of~$\rho$ and at the bottom of~$\rho'$ satisfying the swinging arms condition explained thereafter.
+\item[(ii)] \defn{reaches} for~$\rho'$ (or~$(\rho')^{-1}$) if there is some common substring~$\xi$ on top of~$\rho$ and at the bottom of~$\rho'$ satisfying the swinging arms condition explained thereafter.
 In this definition only, we call \defn{left and right arms} of~$\rho$ (resp.~$\rho'$) the (at most) two arrows in the string~$\rho$ (resp.~$\rho'$) incident with~$\xi$.
@@
 Let $\sigma$ be a string in $\strings^\pm(\bar Q)$ and let~$v$ be a vertex of~$\bar Q$.
-We say that the negative simple string $-v$ dances with the string $\sigma$ if~$v$ is a vertex of~$\sigma$.
-On the other hand, no almost positive string dances with the negative simple string~$-v$.
+We say that the negative simple string $-v$ reaches for the string $\sigma$ if~$v$ is a vertex of~$\sigma$.
+On the other hand, no almost positive string reaches for the negative simple string~$-v$.
 \end{definition}
@@
 \]
-	\caption{The string~$\rho$ dances with~$\rho'$, as in Definition~\ref{definition: dance and attract} (ii).}
+	\caption{The string~$\rho$ reaches for~$\rho'$, as in Definition~\ref{definition: dance and attract} (ii).}
 	\label{fig:def-dances}
@@
 Let~$\rho$ and~$\rho'$ be two almost positive strings for the string algebra~$A$ and let~$M(\rho)$ and~$M(\rho')$ be the associated string modules.
-Then \[\Hom{A} \big( M(\rho), \tau M(\rho') \big) \ne 0\] if and only if~$\rho$ attracts~$\rho'$ or dances with~$\rho'$.
+Then \[\Hom{A} \big( M(\rho), \tau M(\rho') \big) \ne 0\] if and only if~$\rho$ attracts~$\rho'$ or reaches for~$\rho'$.
 \end{proposition}
@@
 
-Assume now that~$\rho$ dances with~$\rho'$, and let~$\xi$ be as in Definition~\ref{definition: dance and attract}.
+Assume now that~$\rho$ reaches for~$\rho'$, and let~$\xi$ be as in Definition~\ref{definition: dance and attract}.
 We distinguish four cases:
@@
 \]
-    \caption{The string~$\rho''$, when~$\rho$ dances with~$\rho'$ and~$\rho'=\xi$ as in case (a).}
+    \caption{The string~$\rho''$, when~$\rho$ reaches for~$\rho'$ and~$\rho'=\xi$ as in case (a).}
     \vspace{-.5cm}
@@
 \]
-    \caption{When~$\rho$ dances with~$\rho'$ and~$\rho'$ contains a substring~$\alpha\xi\beta^{-1}$ as in case~(b).}
+    \caption{When~$\rho$ reaches for~$\rho'$ and~$\rho'$ contains a substring~$\alpha\xi\beta^{-1}$ as in case~(b).}
     \vspace{-.5cm}
@@
 \]
-    \caption{When~$\rho$ dances with~$\rho'$ and~$\rho'=\xi\beta^{-1}\sigma$ as in case (c).}
+    \caption{When~$\rho$ reaches for~$\rho'$ and~$\rho'=\xi\beta^{-1}\sigma$ as in case (c).}
     \vspace{-.5cm}
@@
 \end{enumerate}
-This concludes the proof that~$\Hom{A} \big( M(\rho), \tau M(\rho') \big) \ne 0$ when~$\rho$ attracts~$\rho'$ or dances with~$\rho'$.
+This concludes the proof that~$\Hom{A} \big( M(\rho), \tau M(\rho') \big) \ne 0$ when~$\rho$ attracts~$\rho'$ or reaches for~$\rho'$.
 
@@
 
-\item If~$\xi=\nu$. By Lemma~\ref{lemma: xi equals nu} below and the fact that~$\xi$ is on top of~$\rho$, we have that~$\rho$ dances with~$\rho'$.
+\item If~$\xi=\nu$. By Lemma~\ref{lemma: xi equals nu} below and the fact that~$\xi$ is on top of~$\rho$, we have that~$\rho$ reaches for~$\rho'$.
 
@@
 Since~$\nu$ is on top of~$\rho$, we have~$\rho=\rho_1\alpha^{-1}\xi(\beta\rho_2)$ for some substrings~$\rho_1,\rho_2$ and some arrow~$\beta$.
-This shows that~$\rho$ dances with~$\rho'$ (we note that the swinging arms condition is satisfied).
+This shows that~$\rho$ reaches for~$\rho'$ (we note that the swinging arms condition is satisfied).
 
@@
 Moreover,~$\nu$ is at the bottom of~$\rho''$ so that it contains~$\alpha^{-1}\xi\beta$.
-The string~$\rho$ also contains~$\alpha^{-1}\xi\beta$ and therefore dances with~$\xi=\rho'$.
+The string~$\rho$ also contains~$\alpha^{-1}\xi\beta$ and therefore reaches for~$\xi=\rho'$.
 
@@
 \label{coro: stautilt complex from strings}
-The support $\tau$-tilting complex of~$\bar Q$ is isomorphic to the clique complex of the graph whose vertices are the unoriented strings of~$\bar Q$ and whose edges link two strings which do not attract nor dance with each other.
+The support $\tau$-tilting complex of~$\bar Q$ is isomorphic to the clique complex of the graph whose vertices are the unoriented strings of~$\bar Q$ and whose edges link two strings which do not attract nor reach for each other.
 \end{corollary}
@@
 Let~$\sigma$ and~$\sigma'$ be two strings for the gentle bound quiver~$\bar Q$.
-Then~$\sigma$ attracts~$\sigma'$ or dances with~$\sigma'$ if and only if~$\omega(\sigma)$ kisses~$\omega(\sigma')$.
+Then~$\sigma$ attracts~$\sigma'$ or reaches for~$\sigma'$ if and only if~$\omega(\sigma)$ kisses~$\omega(\sigma')$.
 \end{lemma}
@@
 
-Assume that~$\sigma$ dances with~$\sigma'$, and let~$\xi$ be the substring on top of~$\sigma$ and at the bottom of~$\sigma'$, as in Definition~\ref{definition: dance and attract}\,(ii).
+Assume that~$\sigma$ reaches for~$\sigma'$, and let~$\xi$ be the substring on top of~$\sigma$ and at the bottom of~$\sigma'$, as in Definition~\ref{definition: dance and attract}\,(ii).
 We distinguish three cases:
@@
 \]
-    \caption{The walks~$\omega(\sigma)$ and~$\omega(\sigma')$ when~$\sigma$ dances with~$\sigma'$: case (a).}
+    \caption{The walks~$\omega(\sigma)$ and~$\omega(\sigma')$ when~$\sigma$ reaches for~$\sigma'$: case (a).}
     \vspace{.1cm}
@@
 \]
-    \caption{The walks~$\omega(\sigma)$ and~$\omega(\sigma')$ when~$\sigma$ dances with~$\sigma'$: case (b).}
+    \caption{The walks~$\omega(\sigma)$ and~$\omega(\sigma')$ when~$\sigma$ reaches for~$\sigma'$: case (b).}
     \vspace{.1cm}
@@
 \]
-    \caption{The walks~$\omega(\sigma)$ and~$\omega(\sigma')$ when~$\sigma$ dances with~$\sigma'$: case (c).}
+    \caption{The walks~$\omega(\sigma)$ and~$\omega(\sigma')$ when~$\sigma$ reaches for~$\sigma'$: case (c).}
     \label{fig: dance case c}
@@
 Note that this implies that $\xi$ is also on top of $\sigma$ (but not necessarily strictly on top).
-It is possible to show that $\sigma$ attracts or dances with $\sigma'$ by using the same method as in the proof of Proposition~\ref{proposition: attract or dance and tau compatibility}.
+It is possible to show that $\sigma$ attracts or reaches for $\sigma'$ by using the same method as in the proof of Proposition~\ref{proposition: attract or dance and tau compatibility}.
 However, we choose an alternative proof, showing instead that $\Hom{A} \big( M(\sigma), \tau M(\sigma') \big) \ne 0$, which implies the result by Proposition~\ref{proposition: attract or dance and tau compatibility}.

### 2018-07-12 firstPaper/firstPaperShort/nonKissingComplex.tex
Changes to first paper.

@@
 	\end{enumerate}
-\item[(ii)] \defn{dance} with~$\rho'$ (or~$(\rho')^{-1}$) if there is some common substring~$\xi$ on top of~$\rho$ and at the bottom of~$\rho'$ satisfying the swinging arms condition explained thereafter.
+\item[(ii)] \defn{reach} for~$\rho'$ (or~$(\rho')^{-1}$) if there is some common substring~$\xi$ on top of~$\rho$ and at the bottom of~$\rho'$ satisfying the swinging arms condition explained thereafter.
 In this definition only, we call \defn{left and right arms} of~$\rho$ (resp.~$\rho'$) the (at most) two arrows in the string~$\rho$ (resp.~$\rho'$) incident with~$\xi$.
@@
 Let~$\rho$ and~$\rho'$ be two almost positive strings for the string algebra~$A$ and let~$M(\rho)$ and~$M(\rho')$ be the associated string modules.
-Then~$\Hom{A} \big( M(\rho), \tau M(\rho') \big) \ne 0$ if and only if~$\rho$ attracts~$\rho'$ or dances with~$\rho'$.
+Then~$\Hom{A} \big( M(\rho), \tau M(\rho') \big) \ne 0$ if and only if~$\rho$ attracts~$\rho'$ or reaches for~$\rho'$.
 \end{proposition}
@@
 \]
-    \caption{When~$\rho$ dances with~$\rho'$ and~$\rho'$ contains a substring~$\alpha\xi\beta^{-1}$ as in case (b).}
+    \caption{When~$\rho$ reaches for~$\rho'$ and~$\rho'$ contains a substring~$\alpha\xi\beta^{-1}$ as in case (b).}
     \vspace{-.5cm}
@@
 \]
-    \caption{The walks~$\omega(\sigma)$ and~$\omega(\sigma')$ when~$\sigma$ dances with~$\sigma'$: case (a).}
+    \caption{The walks~$\omega(\sigma)$ and~$\omega(\sigma')$ when~$\sigma$ reaches for~$\sigma'$: case (a).}
     \vspace{1cm}
@@
 \]
-    \caption{The walks~$\omega(\sigma)$ and~$\omega(\sigma')$ when~$\sigma$ dances with~$\sigma'$: case (b).}
+    \caption{The walks~$\omega(\sigma)$ and~$\omega(\sigma')$ when~$\sigma$ reaches for~$\sigma'$: case (b).}
     \vspace{1cm}

### 2018-07-12 secondPaper/accordionComplexSurfaces.tex

--- 2018-07-12 secondPaper/accordionComplexSurfaces.tex
@@
 \begin{proof}
-The duality provides a bijection~$v\in (Q_\dissection)_0\mapsto v\dual\in (Q_{\dissection\dual})_0$, and also induces a bijection~${\alpha \in (Q_\dissection)_1 \mapsto \alpha\dual \in (Q_{\dissection\dual})_1}$ with~$s(\alpha\dual) = t(\alpha)\dual$ and~$t(\alpha\dual) = s(\alpha)\dual$.
- Moreover, for any two composable arrows~$\alpha,\beta\in(Q_\dissection)_0$, we have~$\alpha\beta\in I_\dissection$ if and only if~$s(\alpha),t(\alpha),t(\beta)$ are three consecutive edges of a~$\dissection$-cell~$f$, if and only if~$s(\alpha)\dual,t(\alpha)\dual,t(\beta)\dual$ are three consecutive edges in~$\dissection\dual$ ending in~$f\dual$, if and only if~$\beta\dual\alpha\dual\notin I_{\dissection\dual}$.
+The duality provides a bijection~$a\in (Q_\dissection)_0\mapsto a\dual\in (Q_{\dissection\dual})_0$, and also induces a bijection~${\alpha \in (Q_\dissection)_1 \mapsto \alpha\dual \in (Q_{\dissection\dual})_1}$ with~$s(\alpha\dual) = t(\alpha)\dual$ and~$t(\alpha\dual) = s(\alpha)\dual$.
+ Moreover, for any two composable arrows~$\alpha,\beta\in(Q_\dissection)_0$, we have~$\alpha\beta\in I_\dissection$ if and only if~$s(\alpha),t(\alpha),t(\beta)$ are three consecutive edges of a~$\dissection$-cell~$f$, if and only if~$s(\alpha)\dual,t(\alpha)\dual,t(\beta)\dual$ are three consecutive arcs in~$\dissection\dual$ ending in~$f\dual$, if and only if~$\beta\dual\alpha\dual\notin I_{\dissection\dual}$.
 \end{proof}
@@
 \item \label{item:edges}
-      The dissection~$\dissection_{\bar Q}$ has one edge for each vertex~$v \in \bar Q_0$, obtained by concatenation of the sides~$\Enrt{\alpha} = \Enrs{\beta}$ and~$\Enrt{\alpha'} = \Enrs{\beta'}$ where~$v = t(\alpha) = s(\beta) = t(\alpha') = s(\beta')$, $\alpha\beta \notin I$ and~$\alpha'\beta' \notin I$.
-We denote by~$\edgeof(v)$ the edge of~$\dissection_{\bar Q}$ corresponding to~$v$.
+      The dissection~$\dissection_{\bar Q}$ has one edge for each vertex~$a \in \bar Q_0$, obtained by concatenation of the sides~$\Enrt{\alpha} = \Enrs{\beta}$ and~$\Enrt{\alpha'} = \Enrs{\beta'}$ where~$a = t(\alpha) = s(\beta) = t(\alpha') = s(\beta')$, $\alpha\beta \notin I$ and~$\alpha'\beta' \notin I$.
+We denote by~$\edgeof(a)$ the edge of~$\dissection_{\bar Q}$ corresponding to~$a$.
 \item The dissection~$\dissection_{\bar Q}$ has one $\ell$-cell for each straight walk of length~$\ell$ in~$\bar Q\koszul$.
-\item Similar statements hold dually for~${{V\dual}\!\!_{\bar Q}}$ and~${\dissection\dual\!\!_{\bar Q}}$, and the notations~$p\dual$ and~$\dualedgeof(v)$ are defined similarly.
+\item Similar statements hold dually for~${{V\dual}\!\!_{\bar Q}}$ and~${\dissection\dual\!\!_{\bar Q}}$, and the notations~$p\dual$ and~$\dualedgeof(a)$ are defined similarly.
 \item The number of punctures of~$\surface_{\bar Q}$ is the number~$p + p\dual$ of infinite straight walks in~$\bar Q$ and in~$\bar Q\koszul$.
@@
 \label{exm:peakDeepFacets}
-We have seen in Definition~\ref{def:straightBending} that each vertex~$v$ of~$Q$ gives rise to a \defn{peak walk}~$v_\peak$ (resp.~\defn{deep walk}~$v_\deep$) with a single peak (resp.~deep) at~$v$ and no other corner.
-The set of all such walks forms the \defn{peak facet}~$\set{v_\peak}{v \in Q_0}$ (resp.~the \defn{deep facet}~$\set{v_\deep}{v \in Q_0}$) of the non-kissing complex~$\RNKC$.
+We have seen in Definition~\ref{def:straightBending} that each vertex~$a$ of~$Q$ gives rise to a \defn{peak walk}~$a_\peak$ (resp.~\defn{deep walk}~$a_\deep$) with a single peak (resp.~deep) at~$a$ and no other corner.
+The set of all such walks forms the \defn{peak facet}~$\set{a_\peak}{a \in Q_0}$ (resp.~the \defn{deep facet}~$\set{a_\deep}{a \in Q_0}$) of the non-kissing complex~$\RNKC$.
 As an example of Theorem~\ref{thm:complexesCoincide}, let us now describe the corresponding non-crossing facets of~$\RNCC[\dissection_{\bar Q}, {{\dissection\dual}\!\!_{\bar Q}}]$.
@@
 
-We invite the reader to check that~$\curveof(v_\peak) = \vprevious{\edgeof(v)}$ (resp.~$\curveof(v_\deep) = \vnext{\edgeof(v)}$), where~$\edgeof(v)$ denotes the edge of~$\dissection_{\bar Q}$ corresponding to~$v \in Q_0$ (see Remark~\ref{rem:propertiesSurface}\,\eqref{item:edges}).
+We invite the reader to check that~$\curveof(a_\peak) = \vprevious{\edgeof(a)}$ (resp.~$\curveof(a_\deep) = \vnext{\edgeof(a)}$), where~$\edgeof(a)$ denotes the edge of~$\dissection_{\bar Q}$ corresponding to~$a \in Q_0$ (see Remark~\ref{rem:propertiesSurface}\,\eqref{item:edges}).
 Therefore, the peak facet (resp.~the deep facet) can be thought of as the dissection~$\dissection_{\bar Q}$ slightly rotated clockwise (resp.~counterclockwise) on the surface~$\surface_{\bar Q}$.
@@
 Using Theorem \ref{thm:complexesCoincide}, we can translate the definition of the countercurrent order~$\prec_\alpha$ to the language of~$\dissection$-accordions (resp.~of~$\dissection\dual$-slaloms).
-An arrow~$\alpha$ in~$\bar Q\blossom$ corresponds to an angle at a point~$v$ between two edges of~$\dissection$ (resp.~at a point~$v\dual$ between two edges of~$\dissection\dual$).
+An arrow~$\alpha$ in~$\bar Q\blossom$ corresponds to an angle at a point~$v$ between two arcs of~$\dissection$ (resp.~at a point~$f\dual$,~$v\in f$, between two edges of~$\dissection\dual$).
 Two distinct non-kissing walks~$\mu_\star, \nu_\star$ marked at~$\alpha$ in~$\bar Q$ correspond to two distinct non-crossing~$\dissection$-accordions (resp.~$\dissection\dual$-slaloms)~$\gamma$ and~$\delta$ passing in front of this angle.
-Then~$\gamma \prec_\alpha \delta$ if~$\gamma$ passes closer to~$v$ (resp.~further to~$v\dual$) than~$\delta$ does.
+Then~$\gamma \prec_\alpha \delta$ if~$\gamma$ passes closer to~$v$ (resp.~further to~$f\dual$) than~$\delta$ does.
 These interpretations of~$\prec_\alpha$ on the surface where already considered in the case of the disk in~\cite{GarverMcConville, MannevillePilaud-accordion}.
@@
 
-Let~$\bar Q = (Q,I)$ be a locally gentle bound quiver, and let~$(\b{e}_v)_{v \in Q_0}$ denote the standard basis of~$\R^{Q_0}$.
-
-\begin{definition}
-For a multiset~$V \eqdef \{v_1, \dots, v_m\}$ of vertices of~$Q_0$, we denote by~$\multiplicityVector_V \in \R^{Q_0}$ the \defn{multiplicity vector} of~$V$, defined~by
+Let~$\bar Q = (Q,I)$ be a locally gentle bound quiver, and let~$(\b{e}_a)_{a \in Q_0}$ denote the standard basis of~$\R^{Q_0}$.
+
+\begin{definition}
+Let~$V \eqdef \{a_1, \dots, a_m\}$ be a multiset of vertices of~$Q_0$. We denote by~$\multiplicityVector_V \in \R^{Q_0}$ the \defn{multiplicity vector} of~$V$, defined~by:
 \[
-\multiplicityVector_V \eqdef \sum_{i \in [m]} \b{e}_{v_i} = \sum_{v \in Q_0} |\set{i \in [m]}{v_i = v}| \, \b{e}_v.
+\multiplicityVector_V \eqdef \sum_{i \in [m]} \b{e}_{a_i} = \sum_{a \in Q_0} |\set{i \in [m]}{a_i = a}| \, \b{e}_a.
 \]
@@
 Our objective is now to interpret the three families of vectors of Section~\ref{subsec:gcdVectorsWalks} in terms of accordions and slaloms on the surface.
-According to Remark~\ref{rem:propertiesSurface}\,\eqref{item:edges}, each vertex~$p$ of~$Q$ corresponds to an edge~$\edgeof(p)$ in the dissection~$\dissection_{\bar Q}$ and  to an edge~$\dualedgeof(p) = \edgeof(p)\dual$ in the dual dissection~${\dissection\dual\!\!_{\bar Q}}$.
+According to Remark~\ref{rem:propertiesSurface}\,(\eqref{item:edges}), each vertex~$a$ of~$Q$ corresponds to an edge~$\edgeof(a)$ in the dissection~$\dissection_{\bar Q}$ and  to an edge~$\dualedgeof(a) = \edgeof(a)\dual$ in the dual dissection~${\dissection\dual\!\!_{\bar Q}}$.
 Recall moreover from Lemma~\ref{lemm:curveOfAWalkIsAccordion} and Proposition~\ref{prop:accordionsSlaloms} that each non-kissing walk~$\omega$ in~$\bar Q$ corresponds to a curve~$\curveof(\omega)$ that is both a $\dissection$-accordion and a $\dissection\dual$-slalom.
@@
 \label{prop:gVectorsSurface}
-For a walk~$\omega$ of~$\bar Q$ and a vertex~$p \in Q_0$, the $p$-th entry of the $\b{g}$-vector~$\gvector{\omega}$ is given~by:
+For a walk~$\omega$ of~$\bar Q$ and a vertex~$a \in Q_0$, the $a$-th entry of the $\b{g}$-vector~$\gvector{\omega}$ is given~by:
 \begin{enumerate}[(i)]
-\item The number of times that the $\dissection$-accordion~$\curveof(\omega)$ positively crosses the edge~$\edgeof(p)$ of~$\dissection$ minus the number of times it negatively crosses the edge~$\edgeof(p)$ of~$\dissection$.
-Here, the crossing is positive (resp.~negative) if the two angles of~$\dissection$ crossed by~$\curveof(\alpha)$ just before and after~$\edgeof(p)$ form a~$\SSS$ (resp.~a~$\ZZZ$).
+\item The number of times that the $\dissection$-accordion~$\curveof(\omega)$ positively crosses the edge~$\edgeof(a)$ of~$\dissection$ minus the number of times it negatively crosses the edge~$\edgeof(a)$ of~$\dissection$.
+Here, the crossing is positive (resp.~negative) if the two angles of~$\dissection$ crossed by~$\curveof(\alpha)$ just before and after~$\edgeof(a)$ form a~$\SSS$ (resp.~as a~$\ZZZ$).
 We note that some crossings are neither positive nor negative.
-\item The number of times that the $\dissection\dual$-slalom~$\curveof(\omega)$ positively crosses the edge~$\dualedgeof(p)$ of~$\dissection\dual$ minus the number of times it negatively crosses the edge~$\dualedgeof(p)$ of~$\dissection\dual$.
+\item The number of times that the $\dissection\dual$-slalom~$\curveof(\omega)$ positively crosses the edge~$\dualedgeof(a)$ of~$\dissection\dual$ minus the number of times it negatively crosses the edge~$\dualedgeof(a)$ of~$\dissection\dual$.
 Here, the crossing is positive when~$\curveof(\omega)$ leaves a face~$u\dual$ to enter a face~$v\dual$ with the vertex~$u$ being to its right (and thus with~$v$ being to its left), and the crossing is negative otherwise.
@@
 \label{prop:dVectorsSurface}
-Denote by~$X_\deep \eqdef \set{\curveof(v_\peak)}{v \in Q_0}$ the deep facet of the non-crossing complex obtained by slightly rotating~$\dissection_{\bar Q}$ counterclockwise as described in Example~\ref{exm:peakDeepFacets}.
-For a walk~$\omega$ of~$\bar Q$ and a vertex~$v \in Q_0$, the $v$-th entry of the $\b{d}$-vector~$\dvector{\omega}$ is either~$-1$ if~$\omega = v_\peak$ or the number of crossings of the curve~$\gamma(\omega)$ with the edge~$\curveof(v_\peak)$ of~$X_\deep$ corresponding to~$v$.
+Denote by~$X_\deep \eqdef \set{\curveof(a_\peak)}{a \in Q_0}$ the deep facet of the non-crossing complex obtained by slightly rotating~$\dissection_{\bar Q}$ counterclockwise as described in Example~\ref{exm:peakDeepFacets}.
+For a walk~$\omega$ of~$\bar Q$ and a vertex~$a \in Q_0$, the $a$-th entry of the $\b{d}$-vector~$\dvector{\omega}$ is either~$-1$ if~$\omega = a_\peak$ or the number of crossings of the curve~$\gamma(\omega)$ with the edge~$\curveof(a_\peak)$ of~$X_\deep$ corresponding to~$a$.
 \end{proposition}
@@
 \begin{proof}
-For the $\b{g}$-vectors, observe that two walks~$\omega$ and~$\omega'$ whose $\b{g}$-vectors~$\gvector{\omega}$ and~$\gvector{\omega'}$ have opposite signs on their~$v$-th coordinate automatically kiss at~$v$.
+For the $\b{g}$-vectors, observe that two walks~$\omega$ and~$\omega'$ whose $\b{g}$-vectors~$\gvector{\omega}$ and~$\gvector{\omega}$ have opposite signs on their~$a$-th coordinate automatically kiss at~$a$.
 For $\b{c}$- and $\b{d}$-vectors, the statement is immediate from the definition.

### 2018-07-12 secondPaper/accordionComplexSurfaces.tex
v\dual to f\dual
final micro changes

@@
 
+\enlargethispage{.2cm}
 We first quickly review the definition of the non-kissing complex of a gentle bound quiver following the presentation of~\cite{PaluPilaudPlamondon} and extend it to locally gentle bound quivers.
@@
 
+\enlargethispage{.1cm}
 We now temporarily switch topic and present the accordion complex and the slalom complex of a pair of dual dissections of an orientable surface.
@@
 
+\enlargethispage{.1cm}
 Let~$\bar\surface = (\surface, V \sqcup V\dual)$ be a surface with two disjoint sets~$V$ and~$V\dual$ of marked points, and let~$B$ be the corresponding blossom points on the boundary of~$\surface$.
@@
 
+\enlargethispage{.3cm}
 The following definition generalizes the one from~\cite{GarverMcConville} for the case where~$\bar\surface$ is a disk.
@@
 Consider the connected component of~$f\setminus\alpha$ that does not contain~$f\dual$.
-The boundary of this component contains an edge~$c \in \dissection \setminus \{a\}$ that share a common endpoint with~$a$.
-Let~$u,v$ be the endpoints of~$c$.
-Then~$\alpha$ cuts the cells $u\dual,v\dual$ glued along~$c\dual$ into two connected components, one containing both endpoints of~$\delta$.
+The boundary of this component contains an edge~$c \in \dissection \setminus \{a\}$ that shares a common endpoint with~$a$.
+Let~$u,v$ be the endpoints~of~$c$.
+Then~$\alpha$ cuts the cells $u\dual,v\dual$ glued along~$c\dual$ into two connected components, one containing both~endpoints~of~$\delta$.
 
@@
 The duality provides a bijection~$a\in (Q_\dissection)_0\mapsto a\dual\in (Q_{\dissection\dual})_0$, and also induces a bijection~${\alpha \in (Q_\dissection)_1 \mapsto \alpha\dual \in (Q_{\dissection\dual})_1}$ with~$s(\alpha\dual) = t(\alpha)\dual$ and~$t(\alpha\dual) = s(\alpha)\dual$.
- Moreover, for any two composable arrows~$\alpha,\beta\in(Q_\dissection)_0$, we have~$\alpha\beta\in I_\dissection$ if and only if~$s(\alpha),t(\alpha),t(\beta)$ are three consecutive edges of a~$\dissection$-cell~$f$, if and only if~$s(\alpha)\dual,t(\alpha)\dual,t(\beta)\dual$ are three consecutive arcs in~$\dissection\dual$ ending in~$f\dual$, if and only if~$\beta\dual\alpha\dual\notin I_{\dissection\dual}$.
+Moreover, for any two composable arrows~$\alpha,\beta\in(Q_\dissection)_0$, we have~$\alpha\beta\in I_\dissection$ if and only if~$s(\alpha),t(\alpha),t(\beta)$ are three consecutive edges of a~$\dissection$-cell~$f$, if and only if~$s(\alpha)\dual,t(\alpha)\dual,t(\beta)\dual$ are three consecutive edges in~$\dissection\dual$ ending in~$f\dual$, if and only if~$\beta\dual\alpha\dual\notin I_{\dissection\dual}$.
 \end{proof}
@@
 & \Enrs{\alpha} = [v(\alpha), s(\alpha)] \qquad & \Enrt{\alpha} = [v(\alpha), t(\alpha)] \qquad & \text{(colored green)} \\
-\text{and} \qquad & \Ers{\alpha} = [v\dual(\alpha), s(\alpha)] \qquad & \Ert{\alpha} = [v\dual(\alpha), t(\alpha)] \qquad & \text{(colored red)}
+\text{and} \qquad & \Ers{\alpha} = [f\dual(\alpha), s(\alpha)] \qquad & \Ert{\alpha} = [f\dual(\alpha), t(\alpha)] \qquad & \text{(colored red)}
 \end{alignat*}
@@
 	\node[roundNode, fill=green, label={[label distance=-3pt]above:{$\green v(\alpha)$}}] (v) at (0,1) {};
-	\node[roundNode, fill=red, label={[label distance=-3pt]below:{$\red v\dual(\alpha)$}}] (vd) at (0,-1) {};
+	\node[roundNode, fill=red, label={[label distance=-3pt]below:{$\red f\dual(\alpha)$}}] (vd) at (0,-1) {};
 	\draw[color=black, postaction={decorate}] (s) -> (t) node[midway, above] {$\alpha$};
@@
 
+\enlargethispage{-.4cm}
 The advantage of Definition~\ref{def:surfaceQuiver} is that it automatically endows~$\surface_{\bar Q}$ with two disjoint sets~$V_{\bar Q}$ and~${{V\dual}\!\!_{\bar Q}}$ of marked points and two dual cellular dissections~$\dissection_{\bar Q}$ and~${\dissection\dual\!\!_{\bar Q}}$ defined as follows.
@@
 
-\enlargethispage{.2cm}
 We apply Remark~\ref{rem:propertiesSurface} to understand the corresponding surfaces.
@@
 
-For a vertex~$v \in V$ on the boundary of~$\surface$, we denote by~$\vprevious{v}$ (resp.~$\vnext{v}$) the blossom vertex previous (resp.~next) to~$v$ when walking along  the boundary of~$\surface$ while keeping it on the right.
+%For a vertex~$v \in V$ on the boundary of~$\surface$, we denote by~$\vprevious{v}$ (resp.~$\vnext{v}$) the blossom vertex previous (resp.~next) to~$v$ when walking along  the boundary of~$\surface$ while keeping it on the right.
 For an edge~$a$ of~$\dissection$, we denote by~$\vprevious{a}$ (resp.~$\vnext{a}$) the curve obtained by moving each endpoint~$v$ of~$a$ as follows:
 \begin{itemize}
-\item if~$v$ is on the boundary of~$\surface$, then move (continuously) $v$ along the boundary of~$\surface$ until it reaches~$\vprevious{v}$ (resp.~$\vnext{v}$),
+\item if~$v$ is on the boundary of~$\surface$, then move (continuously) $v$ until it reaches the following blossom vertex along the boundary of~$\surface$ while keeping the boundary of~$\surface$ on the right,
 \item if~$v$ is a puncture, then rotate around~$v$ in counterclockwise (resp.~clockwise) direction.
@@
 \begin{remark}
- We note that, since the walks~$\mu$ and~$\nu$ are non-kissing, if~$\mu_\star$ leaves~$\sigma$ on both sides, then is enters and exits~$\sigma$ in the same direction, so that Definition~\ref{def:orderForWalks} is coherent.
+Since the walks~$\mu$ and~$\nu$ are non-kissing, if~$\mu_\star$ leaves~$\sigma$ on both sides, then is enters and exits~$\sigma$ in the same direction, so that Definition~\ref{def:orderForWalks} is coherent.
 \end{remark}
@@
 Using Theorem \ref{thm:complexesCoincide}, we can translate the definition of the countercurrent order~$\prec_\alpha$ to the language of~$\dissection$-accordions (resp.~of~$\dissection\dual$-slaloms).
-An arrow~$\alpha$ in~$\bar Q\blossom$ corresponds to an angle at a point~$v$ between two arcs of~$\dissection$ (resp.~at a point~$f\dual$,~$v\in f$, between two edges of~$\dissection\dual$).
+An arrow~$\alpha$ in~$\bar Q\blossom$ corresponds to an angle at a point~$v$ between two edges of~$\dissection$ (resp.~at a point~$f\dual$ between two edges of~$\dissection\dual$).
 Two distinct non-kissing walks~$\mu_\star, \nu_\star$ marked at~$\alpha$ in~$\bar Q$ correspond to two distinct non-crossing~$\dissection$-accordions (resp.~$\dissection\dual$-slaloms)~$\gamma$ and~$\delta$ passing in front of this angle.
@@
 \begin{proof}[Combinatorial proof]
-By Lemma~\ref{lem:ExistenceOfDistinguishedArrows}, the number of walks in a finite face of~$\NKC$ is bounded by~$|Q_1\blossom|+p$, where~$p$ is the number of infinite straight walks (i.e.
-the number of primitive oriented cycles in~$Q$).
+By Lemma~\ref{lem:ExistenceOfDistinguishedArrows}, the number of walks in a finite face of~$\NKC$ is bounded by~$|Q_1\blossom|+p$, where~$p$ is the number of infinite straight walks (\ie the number of primitive oriented cycles in~$Q$).
 
@@
 
-Note that Proposition \ref{prop:purity} was proved for~$\NKC$ in \cite[Cor.~2.27]{PaluPilaudPlamondon} in the case where~$kQ/I$ is finite-dimensional.
+Note that Proposition \ref{prop:purity} was proved for~$\NKC$ in \cite[Cor.~2.29]{PaluPilaudPlamondon} in the case where~$kQ/I$ is finite-dimensional.
 Note also that, by Theorem \ref{thm:complexesCoincide} above,~$\NKC$ and~$\NCC[\dissection_{\bar Q}, {\dissection\dual\!\!_{\bar Q}}]$ coincide, so it suffices to prove the statement for one of them.
-The following definition from \cite[Def.~2.23]{PaluPilaudPlamondon} extends to the setting of locally gentle algebras.
+The following definition from \cite[Def.~2.25]{PaluPilaudPlamondon} extends to the setting of locally gentle algebras.
 
@@
 \label{lem:walksThroughcycles}
-For any oriented cycle~$c$ in~$Q$ with~$c, c^2\notin I$, any maximal non-kissing face contains a walk of the form~$\sigma c^{\varepsilon\infty}$, for some~$\varepsilon\in\{\pm1\}$ and some substring~$\sigma$ distinct from~$^{\varepsilon\infty}c$ (i.e.
-the walk is not an infinite straight walk).
+For any oriented cycle~$c$ in~$Q$ with~$c, c^2\notin I$, any maximal non-kissing face contains a walk of the form~$\sigma c^{\varepsilon\infty}$, for some~$\varepsilon\in\{\pm1\}$ and some substring~$\sigma$ distinct from~$^{\varepsilon\infty}c$ (\ie the walk is not an infinite straight walk).
 \end{lemma}
@@
 
-The following result extends \cite[Prop.~2.26]{PaluPilaudPlamondon} to the case of locally gentle algebras.
+The following result extends \cite[Prop.~2.28]{PaluPilaudPlamondon} to the case of locally gentle algebras.
 
@@
 \begin{proof}
-The proof of \cite[Prop.~2.26]{PaluPilaudPlamondon} applies here to show that each walk in the non-kissing facet~$F$ has at most one distinguished arrow in each direction.
+The proof of \cite[Prop.~2.28]{PaluPilaudPlamondon} applies here to show that each walk in the non-kissing facet~$F$ has at most one distinguished arrow in each direction.
 Lemma~\ref{lem:ExistenceOfDistinguishedArrows} therefore shows the first two points.
@@
 \begin{proof}[Proof of Proposition \ref{prop:purity}.]
-The proof follows that of~\cite[Cor.~2.27]{PaluPilaudPlamondon}.
+The proof follows that of~\cite[Cor.~2.29]{PaluPilaudPlamondon}.
 Let~$b$ denote the number of bending walks, $s$ the number of finite straight walks, and $p$ the number of infinite straight walks in a non-kissing facet~$F$ of~$\NKC$.
@@
 A simplicial complex is \defn{thin} if each of its codimension~$1$ faces is contained in exaclty two facets.
-We state the following results, which generalize \cite[Prop.~2.31 \& Cor.~2.33]{PaluPilaudPlamondon}, whose proofs apply without change.
+We state the following results, which generalize \cite[Prop.~2.33 \& Cor.~2.35]{PaluPilaudPlamondon}, whose proofs apply without change.
 
@@
 \begin{definition}
-Let~$V \eqdef \{a_1, \dots, a_m\}$ be a multiset of vertices of~$Q_0$. We denote by~$\multiplicityVector_V \in \R^{Q_0}$ the \defn{multiplicity vector} of~$V$, defined~by:
+For a multiset~$V \eqdef \{a_1, \dots, a_m\}$ of vertices of~$Q_0$, we denote by~$\multiplicityVector_V \in \R^{Q_0}$ the \defn{multiplicity vector} of~$V$, defined by
 \[
@@
 \item The number of times that the $\dissection$-accordion~$\curveof(\omega)$ positively crosses the edge~$\edgeof(a)$ of~$\dissection$ minus the number of times it negatively crosses the edge~$\edgeof(a)$ of~$\dissection$.
-Here, the crossing is positive (resp.~negative) if the two angles of~$\dissection$ crossed by~$\curveof(\alpha)$ just before and after~$\edgeof(a)$ form a~$\SSS$ (resp.~as a~$\ZZZ$).
+Here, the crossing is positive (resp.~negative) if the two angles of~$\dissection$ crossed by~$\curveof(\alpha)$ just before and after~$\edgeof(a)$ form a~$\SSS$ (resp.~a~$\ZZZ$).
 We note that some crossings are neither positive nor negative.
@@
 \begin{proof}
-For the $\b{g}$-vectors, observe that two walks~$\omega$ and~$\omega'$ whose $\b{g}$-vectors~$\gvector{\omega}$ and~$\gvector{\omega}$ have opposite signs on their~$a$-th coordinate automatically kiss at~$a$.
+For the $\b{g}$-vectors, observe that two walks~$\omega$ and~$\omega'$ whose $\b{g}$-vectors~$\gvector{\omega}$ and~$\gvector{\omega'}$ have opposite signs on their~$a$-th coordinate automatically kiss at~$a$.
 For $\b{c}$- and $\b{d}$-vectors, the statement is immediate from the definition.

### 2018-07-12 secondPaper/accordionComplexSurfaces.tex
cleaning tex file

@@
 \usepackage[all]{xy}
-%\usepackage[bottom]{footmisc}
 \usepackage{tikz}
@@
 \renewcommand{\bottomfraction}{1} % possibility to have one page of pictures
-%\renewcommand\labelitemi{$\diamond$} % redefine itemize default symbol
 \newcommand{\ex}{_{\textrm{exm}}} % examples
@@
 \newcommand{\blossom}{^\text{\ding{96}}} % blossom
-%\newcommand{\blinkers}[1]{_{\LEFTCIRCLE \!\! #1 \!\! \RIGHTCIRCLE}} % blossom
-%\newcommand{\indeg}{\mathrm{indeg}} % in-degree
-%\newcommand{\outdeg}{\mathrm{outdeg}} % out-degree
-%\newcommand{\tai}{\mathsf{tai}} % target incompatible
-%\newcommand{\tac}{\mathsf{tac}} % target compatible
-%\newcommand{\soi}{\mathsf{soi}} % source incompatible
-%\newcommand{\soc}{\mathsf{soc}} % source compatible
-%\newcommand{\cso}{\mathsf{cso}} % cosource
-%\newcommand{\cta}{\mathsf{cta}} % cotarget
 \newcommand{\Enrs}[1]{E_{nr}^{s}(#1)}
@@
 % walks
-%\newcommand{\strings}{\mathcal{S}} % strings
-%\newcommand{\distinguishableStrings}{\mathcal{S}_\mathrm{dist}} % distinguishable strings
-%\newcommand{\lfStrings}{\underline{\mathcal{S}}} % loop-free strings
-%\newcommand{\walks}{\mathcal{W}} % walks
-%\newcommand{\straightWalks}{\mathcal{W}_\mathrm{str}} % straight walks
-%\newcommand{\bendingWalks}{\mathcal{W}_\mathrm{bend}} % bending walks
-%\newcommand{\NKWalks}{\mathcal{W}_\mathrm{nk}} % non-kissing walks
 \newcommand{\peaks}[1]{\mathsf{peaks}(#1)} % peaks
@@
 
-%\vspace*{.3cm}
-
 \maketitle
@@
 
-%We consider a \defn{bound quiver}~$\bar Q = (Q,I)$, formed by a quiver~$Q$ and an admissible ideal~$I$ of the path algebra~$kQ$, so that the quotient algebra~$kQ/I$ is finite dimensional.
 We consider a \defn{bound quiver}~$\bar Q = (Q,I)$, formed by a finite quiver~$Q$ and an ideal~$I$ of the path algebra~$kQ$ (the~$k$-vector space generated by all paths in~$Q$, including vertices as paths of length zero, with multiplication induced by concatenation of paths) such that~$I$ is generated by linear combinations of paths of length at least two.
@@
 
-\begin{definition}%[\cite{ButlerRingel}]
+\begin{definition}
 \label{def:gentleQuiver}
@@
 
-\begin{definition}%[\cite{PaluPilaudPlamondon}]
+\begin{definition}
 \label{def:blossomingQuiver}
@@
 For any arrow~$\alpha$ of~$Q$, define a formal inverse~$\alpha^{-1}$ with the properties that~${s(\alpha^{-1}) = t(\alpha)}$, $t(\alpha^{-1}) = s(\alpha)$, $\alpha^{-1}\alpha = \varepsilon_{t(\alpha)}$ and~$\alpha\alpha^{-1} = \varepsilon_{s(\alpha)}$, where~$\varepsilon_v$ is the path of length zero starting and ending at the vertex~$v \in Q_0$.
-% Furthermore, let~$(\alpha^{-1})^{-1}=\alpha$; thus~$(-)^{-1}$ is an involution on the set of arrows and formal inverses of arrows of~$Q$.
-We extend this involution to the set of all paths involving arrows or their formal inverses by further setting~$(\varepsilon_v)^{-1} = \varepsilon_v$ for all vertices~$v \in Q_0$.
 
@@
 For each vertex~$a \in Q_0$, there is also a \defn{string of length zero}, denoted by~$\varepsilon_a$, that starts and ends at~$a$.
-%We denote by~$\strings(\bar Q)$ the set of strings on~$\bar Q$.
-%We usually denote strings by~$\rho, \sigma, \tau$.
-%We call \defn{negative simple string} a formal word of length zero of the form $-a$, where $a$ is any vertex of $Q_0$. We denote by
-%\(
-%\strings^\pm_{\ge -1}(\bar Q) \eqdef \strings^\pm(\bar Q) \sqcup \set{-a}{a \in Q_0}
-%\)
-%the set of \defn{almost positive unoriented strings}.
-%Note that~$\varepsilon_a$ and~$-a$ are different almost positive strings.
-%\end{enumerate}
 \end{definition}
@@
 \item ${}^\infty c$ for the infinite word~$\cdots c c c$,
-% \item $^{-\infty} c$ for the infinite word~$\cdots c^{-1} c^{-1} c^{-1}$,
-% \item $c^{-\infty}$ for the infinite word~$c^{-1} c^{-1} c^{-1}\cdots$, and
 \item $^\infty c^\infty$ for the bi-infinite word~$^\infty c c^\infty$.
@@
 An \defn{eventually cyclic string} for~$\bar Q$ is a word~$\rho$ of the form~${}^\infty(c_1^{\varepsilon_1})\sigma (c_2^{\varepsilon_2})^\infty$, where $c_1, c_2$ are oriented cycles in~$\bar Q$ (possibly of length zero) and $\varepsilon_1, \varepsilon_2$ are signs in~$\{\pm 1\}$ such that $c_1^{2\varepsilon_1} \sigma c_2^{2\varepsilon_2}$ is a finite string in~$\bar Q$.
-%In case~$\rho=\,^{\pm\infty}c_1\sigma c_2^{\infty}$, it is called \defn{eventually direct}, and \defn{eventually inverse} if~$\rho=\,^{\pm\infty}c_1\sigma c_2^{-\infty}$.
 \end{definition}
@@
 A \defn{string} for~$\bar Q$ is a word which is either a finite string or an eventually cyclic infinite string.
-%We denote by~$\strings(\bar Q)$ the set of strings on~$\bar Q$.
 We often implicitly identify the two inverse strings~$\rho$ and~$\rho^{-1}$, and call it an \defn{undirected string} of~$\bar Q$.
-%we let~$\strings^\pm(\bar Q) \eqdef \set{\{\rho, \rho^{-1}\}}{\rho \in \strings(\bar Q)}$ denote the collection of all \defn{undirected strings} of~$\bar Q$.
 \end{definition}
@@
 A \defn{walk} of a locally gentle quiver~$\bar Q$ is a maximal string of its blossoming quiver~$\bar Q \blossom$ (meaning that at each end it either reaches a blossom vertex of~$\bar Q \blossom$ or enters an infinite oriented cycle).
-%We denote by~$\walks(\bar Q)$ the set of all walks on~$\bar Q$.
 As for strings, we implicitly identify the two inverse walks~$\omega$ and~$\omega^{-1}$, and call it an \defn{undirected walk} of~$\bar Q$.
-%we let~$\walks^\pm(\bar Q) \eqdef \set{\{\omega, \omega^{-1}\}}{\omega \in \walks(\bar Q)}$ denote the set of \defn{undirected walks} of~$\bar Q$.
 \end{definition}
@@
 A walk~$\omega$ is \defn{straight} if it has no corner (\ie if~$\omega$ or~$\omega^{-1}$ is a path in~$\bar Q\blossom$), and \defn{bending} otherwise.
-%Let $\straightWalks(\bar Q)$ and~$\bendingWalks(\bar Q)$ denote the sets of straight and bending walks of~$\bar Q$ and let~$\straightWalks^\pm(\bar Q) \eqdef \set{\{\omega, \omega^{-1}\}}{\omega \in \straightWalks(\bar Q)}$ and~$\bendingWalks^\pm(\bar Q) \eqdef \set{\{\omega, \omega^{-1}\}}{\omega \in \bendingWalks(\bar Q)}$.
 A \defn{peak walk} (resp.~\defn{deep walk}) is a walk with a unique corner (in other words, it switches orientation only once), which is a peak (resp.~deep).
@@
 
-\begin{definition}%[\cite{McConville, PaluPilaudPlamondon}]
+\begin{definition}
 \label{def:kiss}
@@
 See \fref{fig:kissing}.
-% \ie if there exist a common substring~$\sigma \in \strings^\pm(\bar Q)$ of~$\omega$ and~$\omega'$ such that the arrows of~$\omega$ incident to~$\sigma$ are both outgoing while the arrows of~$\omega'$ incident to~$\sigma$ are both incoming.
 We say that~$\omega$ and~$\omega'$ are \defn{kissing} if~$\omega$ kisses~$\omega'$ or~$\omega'$ kisses~$\omega$ (or both).
@@
 Observe also that~$\omega$ can kiss~$\omega'$ several times, that~$\omega$ and~$\omega'$ can mutually kiss, and that~$\omega$ can kiss itself.
-%We denote by~$\NKWalks(\bar Q)$ the walks on~$\bar Q$ which are not self-kissing and by~$\NKWalks^\pm(\bar Q) \eqdef \set{\{\omega, \omega^{-1}\}}{\omega \in \NKWalks(\bar Q)}$ their undirected version.
 %
@@
 
-\begin{definition}%[\cite{McConville, PaluPilaudPlamondon}]
+\begin{definition}
 \label{def:nKc}
@@
 \end{definition}
-
-%\begin{theorem}[{\cite[Cor.~2.27 \& Cor.~2.33]{PaluPilaudPlamondon}}]
-%The reduced non-kissing complex~$\RNKC$ is pure of dimension~$|Q_0|$ (\ie all maximal faces have dimension~$|Q_0|$) and thin (\ie all codimension~$1$ faces are contained in exactly two facets).
-%\end{theorem}
-%
-%This result follows from the existence of flips in non-kissing facets.
-%This operation is illustrated in \fref{fig:flip1}.
 
@@
 We mimick the proof of~\cite[Prop.~1.12]{OpperPlamondonSchroll}.
-%Assume first that~$\dissection$ and~$\dissection\dual$ are dual cellular dissections.
-If a face~$f$ of~$\dissection$ had two boundary arcs~$a, b$, then it would contain two points of~$M\dual$, one on~$a$ and one on~$b$.
-%Conversely, if each face of~$\dissection$ has at most one boundary arc, we construct the set of points~$M\dual$ with one point on each boundary arc of~$\surface$ and one point in the interior of each interior face of~$\dissection$.
-Clearly, $M\dual$ has one point~$f\dual$ in each face~$f$ of~$\dissection$.
-We then construct half-arcs of~$\dissection\dual$ in each face~$f$ of~$\dissection$ by joining the dual point~$f\dual$ to the middle of each boundary arc of~$f$ that is not a boundary arc of~$\surface$.
-For each arc~$a$ of~$\dissection$, the half-arcs incident to the middle of~$a$ in the two faces of~$\dissection$ containing~$a$ form the dual arc~$a\dual$ of~$a$.
-All these dual arcs do not cross (as the half-arcs do not cross in each face of~$\dissection$) and form the dual cellular dissection~$\dissection\dual$ of~$\dissection$.
-%More details can be found in~\cite{OpperPlamondonSchroll}.
 The direct implication is immediate by definition.
@@
 
-%\begin{remark}
-%In Proposition~\ref{prop:conditionsDualDissections}, note that although the set~$M\dual$ of dual marked points is unique, the dual dissection~$\dissection\dual$ is not when~$\dissection$ is not cellular.
-%\end{remark}
-
-\begin{definition}
-%Interior points, blossom points.
-%Half-arcs.
+\begin{definition}
 We consider a set~$B$ of points on the boundary of the surface~$\surface$ such that~$B$ and~$V \cup V\dual$ alternate along the boundary of~$\surface$.
@@
 Let~$\bar\surface = (\surface, V \sqcup V\dual)$ be a surface with two disjoint sets~$V$ and~$V\dual$ of marked points, and let~$B$ be the corresponding blossom points on the boundary of~$\surface$.
-%
-%\begin{definition}
-%A \defn{$B$-curve} is a curve on~$\surface$ which at each end either reaches a point of~$B$ or infinitely circles around and finally reaches a puncture of~$V \sqcup V\dual$.
-%Curves are considered up to homotopy relative to their endpoints in~$\surface \ssm (B \sqcup V \sqcup V\dual)$, and curves homotopic to a boundary are not allowed.
-%\end{definition}
-%
-%Let~$I$ denote the interior points and $B$ the blossom points.
 We say that a $B$-curve is \defn{external} if it is homotopic to a boundary arc of~$\surface \ssm B$, and \defn{internal} otherwise.
@@
 Consider two dual cellular dissections~$\dissection$ and~$\dissection\dual$ of~$\bar\surface$.
-
-%With this assumption, each segment of a~$B$-arc that lies in a face~$f$ of the dissection~$\dissection$ has two intersection points (called crossings) with the edges of~$f$.
-%Note that the edges of~$f$ may be on the boundary of the surface.
 
@@
 
-%\begin{remark}
-%Note that the $\dissection$-accordions do not depend on~$\dissection\dual$, only on~$\dissection$ (and~$M\dual$ which is determined by~$\dissection$ by Proposition~\ref{prop:conditionsDualDissections}).
-%Similarly, the $\dissection\dual$-slaloms do not depend on~$\dissection$.
-%\end{remark}
-
 \subsection{Accordions versus slaloms and the non-crossing complex}
@@
 \end{definition}
-
-%\begin{remark}
-%To clearly visualize Proposition~\ref{prop:accordionsSlaloms}, we follow the convention to draw the $\dissection$-accordions (resp.~$\dissection\dual$-slaloms) so that they intersect the arcs of~$\dissection$ (resp.~of~$\dissection\dual$) only at the intersection points of the arcs of~$\dissection$ with the arcs of~$\dissection\dual$.
-%\end{remark}
 
@@
 Note that the dissection~$\dissection_{\bar Q}$ is a triangulation with no internal triangles, and the orientation of~$\bar Q$ indicates how to glue these triangles.
-For instance, the Cambrian quiver completely oriented in one direction yields a fan triangulation, were all internal arcs are incident to the same vertex, as in \fref{fig:CambrianPathsSurfaces}\,(left).
+For instance, the Cambrian quiver completely oriented in one direction yields a fan triangulation, were all internal edges are incident to the same vertex, as in \fref{fig:CambrianPathsSurfaces}\,(left).
 
@@
 \begin{itemize}
-\item for any locally gentle bound quiver~$\bar Q$, the non-kissing complex~$\NKC$ is isomorphic to the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection\dual\!\!_{\bar Q}}]$,% therefore to the accordion complex~$\AC[\dissection_{\bar Q}]$ and to the slalom complex~$\SC[{\dissection\dual\!\!_{\bar Q}}]$.
+\item for any locally gentle bound quiver~$\bar Q$, the non-kissing complex~$\NKC$ is isomorphic to the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection\dual\!\!_{\bar Q}}]$,
 \item for any pair of dual cellular dissections~$\dissection, \dissection\dual$ of an oriented surface, the non-crossing complex~$\NCC$ is isomorphic to the non-kissing complex~$\NKC[\bar Q_{\dissection, \dissection\dual}]$.
@@
 
-%For a vertex~$v \in V$ on the boundary of~$\surface$, we denote by~$\vprevious{v}$ (resp.~$\vnext{v}$) the blossom vertex previous (resp.~next) to~$v$ when walking along  the boundary of~$\surface$ while keeping it on the right.
 For an edge~$a$ of~$\dissection$, we denote by~$\vprevious{a}$ (resp.~$\vnext{a}$) the curve obtained by moving each endpoint~$v$ of~$a$ as follows:
@@
 \end{remark}
-
-%\begin{figure}
-%	\capstart
-%	\centerline{\includegraphics[scale=1]{kissing}}
-%	\caption{A schematic representation of two kissing walks (left) and two crossing walks~(right): $\omega$~kisses~$\omega'$ (left) while~$\mu$~crosses~$\nu$ (right).
-For the crossing walks, we have~$\mu \prec_\gamma \nu$ while~$\nu \prec_\delta \mu$.}
-%	\label{fig:kissing}
-%\end{figure}
 
@@
 	\centerline{\includegraphics[scale=.7]{infiniteCurve2.pdf}}
-	\caption{The arc~$\gamma$ makes at least one full circle around the puncture.}
+	\caption{The curve~$\gamma$ makes at least one full circle around the puncture.}
 	\label{fig:aroundPuncture1}
@@
 	\centerline{\includegraphics[scale=.7]{infiniteCurve1.pdf}}
-	\caption{The arc~$\gamma$ leaving the puncture.}
+	\caption{The curve~$\gamma$ leaving the puncture.}
 	\label{fig:aroundPuncture2}
@@
 Our objective is to provide interpretations of these vectors in terms of the surface~$\surface_{\bar Q}$.
-% We show that our geometric model using accordions is well-adapted to computing~$\b{c}$-vectors, while slaloms can naturally be interpreted as~$\b{g}$-vectors.
 
@@
 \end{definition}
-
-%\begin{remark}
-%\vincent{I vote for deleting this remark. This goes to the next paper. The present paper should have no algebra}
-%Let~$\omega$ be a walk in~$\NKWalks^\pm(\bar Q)$, and let $\sigma$ be the string obtained from~$\omega$ by deleting a left and a right co-hook when possible.
-%Then the~$\b{g}$-vector of the walk~$\omega$ coincide with the~$\b{g}$-vector of the (finitely generated) string module associated with the string~$\sigma$.
-%\end{remark}
 
@@
 The \defn{kissing number} of~$\omega$ and~$\omega'$ is~$\KN(\omega,\omega') \eqdef \kn(\omega,\omega') + \kn(\omega',\omega)$.
-%Since~$\RNKC$ is finite, we can define the \defn{kissing number} of a walk~$\omega$ on~$\bar Q$ as
-%\[
-%\KN(\omega) \eqdef \sum_{\omega'} \KN(\omega,\omega'),
-%\]
-%where the sum runs over all walks~$\omega'$ of~$\NKWalks^\pm(\bar Q)$.
 \end{definition}
@@
 
-%\begin{proposition}
-%\label{prop:gcdVectorsSurface}
-%For any walk~$\omega$ in any non-kissing facet~$F \in \NKC$,
-%\begin{itemize}
-%\item the~$\b{d}$-vectors of the walk~$\omega$, of the $\dissection$-accordion~$\curveof(\omega)$, and of the $\dissection\dual$-slalom~$\curveof(\omega)$ coincide,
-%\item the~$\b{g}$-vectors of the walk~$\omega$, of the $\dissection$-accordion~$\curveof(\omega)$, and of the $\dissection\dual$-slalom~$\curveof(\omega)$ coincide,
-%\item the~$\b{c}$-vectors of the walk~$\omega$ in~$F$, of the $\dissection$-accordion~$\curveof(\omega)$ in~$\curveof(F)$ and of the $\dissection\dual$-slalom~$\curveof(\omega)$ in~$\curveof(F)$ concide.
-%\end{itemize}
-%\end{proposition}
-%
-%\begin{proof}
-%Definitions~\ref{def:cVectorsAccordions} and~\ref{def:gVectorsSlaloms} are immediate translations in terms of curves on the surface~$\surface_{\bar Q}$ of Definitions~\ref{def:cVectorsWalks} and~\ref{def:gVectorsWalks} respectively.
-%\end{proof}
-
 \subsection{Geometric properties of these vectors}
@@
 \end{itemize}
-%In particular, a $\b{c}$-vector is called \defn{positive} when all its coordinates are non-negative and \defn{negative} when all its coordinates are non-positive.
 \end{proposition}

### 2018-07-13 firstPaper/firstPaperLong/nonKissingComplex.tex
MAJ (a) et (b) firstPaperLong

@@
 Observe that this straight walk is always the minimal marked walk of~$F_\alpha$ for the order~$\prec_\alpha$, since it always agrees with the direction of~$\alpha$.
-On the other hand, we can consider the maximal marked walk of~$F_\alpha$ for the order~$\prec_\alpha$.
+On the other hand, Proposition~\ref{prop: nk facets are finite}, below, shows that we can consider the maximal marked walk of~$F_\alpha$ for the order~$\prec_\alpha$.
 Intuitively, it is the most countercurrent walk passing through~$\alpha$ with respect to the direction of~$\alpha$.
+\begin{lemma}\label{lemma: distinguished arrows exists}
+Let~$F$ be a finite face of~$\NKC$, let~$\omega$ be a walk in~$F$, and let~$\alpha$ be an arrow on~$\omega$.
+Then, there is an arrow~$\beta$ oriented in the same direction as~$\alpha$ in~$\omega$ such that~$\omega$ (marked at~$\beta$) is maximal in~$F$ for~$\prec_\beta$.
+\end{lemma}
+
+\begin{proof}
+If~$\omega$ is not maximal in~$F$ for~$\prec_\alpha$, consider~${\mu \eqdef \min_{\prec_\alpha} \set{\nu \in F_\alpha}{\omega \prec_\alpha \nu}}$.
+Let~$\sigma$ denote the maximal common substring of~$\omega$ and~$\mu$ containing~$\alpha$.
+Since~$\omega$ and~$\mu$ are distinct, they split at an endpoint of~$\sigma$.
+At this endpoint, the arrow~$\beta$ of~$\omega$ not in~$\sigma$ points in the same direction as~$\alpha$ since~$\omega \prec_\alpha \mu$.
+Let~$\lambda$ be maximal in~$F$ for~$\prec_\beta$.
+If~$\lambda \ne \omega$, then~$\lambda$ either kisses~$\mu$ or contradicts the minimality of~$\mu$ among the walks~$\set{\nu \in F_\alpha}{\omega \prec_\alpha \nu}$.
+See \fref{fig:pure}\,(right) for an illustration.
+We conclude that~$\lambda = \omega$ has a distinguished arrow~$\beta$ in the direction of~$\alpha$.
+\end{proof}
+
+\begin{proposition}\label{prop: nk facets are finite}
+The faces of the non-kissing complex have finite cardinality.
+\end{proposition}
+
+\begin{proof}
+By Lemma~\ref{lemma: distinguished arrows exists}, the cardinality of any finite non-kissing face is bounded by~$|Q_1\blossom|$.
+Thus, any collection of~$|Q_1\blossom|+1$ walks contains a kiss and all non-kissing faces are finite.
+% Let~$F$ be a non-kissing face.
+% Since the quiver~$Q$ has a finite number of arrows, it is enough to prove that each~$F_\alpha$ is finite.
+% Assume, by means of contradiction, that there is some~$\alpha\in Q_1$ with~$F_\alpha$ infinite.
+% Call ``junction'' a marked occurrence of an arrow~$\beta$ in some~$\omega_\star, \omega'_\star\in F_\alpha$, such that~$\omega$ and~$\omega'$ coincide from their marked occurrence of~$\alpha$ up to~$\beta$ and differ after~$\beta$.
+% Since~$F_\alpha$ is infinite, there is an infinite number of junctions.
+% Since~$Q_1$ is finite, there are two junctions with the same underlying arrow~$\beta$ and such that either~$\alpha$ points towards both junctions or~$\alpha$ points to the direction opposite to both junctions.
+% This shows that there exist three marked walks~$\nu_\star\prec_\alpha \mu_\star\prec_\alpha \lambda_\star\in F_\alpha$ such that~$\lambda, \mu$ and $\nu$ coincide from their marked occurrence of~$\alpha$ up to some marked occurrence~$\beta_1$ of~$\beta$, after which~$\lambda$ differs from~$\mu$ and~$\nu$ but~$\mu$ and~$\nu$ coincide up to some other occurrence~$\beta_2$ of~$\beta$, and then differ (see Figure~\ref{fig: nk facets are finite}).
+% Let~$\sigma_1$ and~$\sigma_2$ be the longest common substrings of~$\lambda$ and~$\nu$ containing~$\beta_1$ and~$\beta_2$ respectively.
+% Note that, since~$\nu$ is finite,~$\sigma_2$ cannot contain~$\beta_1$; in particular,~$\sigma_2$ is contained in~$\mu$.
+% If~$\sigma$ is on top of~$\nu$, then it is at the bottom of~$\lambda$, and~$\lambda$ kisses~$\nu$, which is absurd.
+% Otherwise, the subword~$\sigma$ of~$\mu$ containing~$\beta_2$ is at the bottom of~$\mu$ and $\lambda$ constains a substring of the form~$\gamma^{-1}\sigma_1$, where~$\gamma$ is an arrow of~$Q$.
+% If~$\mu$ entirely contains~$\gamma^{-1}\sigma_1$, then~$\sigma_1$ is at the top of~$\mu$.
+% Hence,~$\mu$ kisses itself, which is absurd.
+% Therefore,~$\gamma^{-1}\sigma_1$ is not entirely contained in~$\mu$.
+\end{proof}
 

### 2018-07-13 firstPaper/firstPaperLong/nonKissingComplex.tex
Some referee's changes to first paper.

--- 2018-07-12 firstPaper/firstPaperLong/nonKissingComplex.tex
@@
 Let~$\rho$ and~$\rho'$ be two strings for a string algebra~$A$.
-Then the dimension of the $k$-vector space~$\Hom{A} \big( M(\rho), M(\rho') \big)$ is equal to
-\[
-\sum\limits_{\xi \text{ string}} \begin{array}{l} (\#\textrm{ of substrings equal to~$\xi$ on top of~$\rho$}) \; \cdot \\ \hspace{2cm}(\#\textrm{ of substrings equal to~$\xi$ or~$\xi^{-1}$ at the bottom of~$\rho'$}).\end{array}
-\]
+Then the dimension of the $k$-vector space~$\Hom{A} \big( M(\rho), M(\rho') \big)$ is equal to the number of pairs~$(\sigma, \sigma')$, where~$\sigma$ and~$\sigma'$ are substrings of~$\rho$ and~$\rho'$, respectively, such that there is an equality of strings~$\sigma' = \sigma^{\pm 1}$.
+
+% \[
+% \sum\limits_{\xi \text{ string}} \begin{array}{l} (\#\textrm{ of substrings equal to~$\xi$ on top of~$\rho$}) \; \cdot \\ \hspace{2cm}(\#\textrm{ of substrings equal to~$\xi$ or~$\xi^{-1}$ at the bottom of~$\rho'$}).\end{array}
+% \]
 \end{proposition}
@@
 The following lemma is immediate and left to the reader.
-See \fref{fig:exmBlossomingQuiver}.
+% See \fref{fig:exmBlossomingQuiver}.
 
@@
 \begin{itemize}
-\item is well-defined: if both endpoints of~$\sigma$ are in~$Q_0$, $\mu_\star$ (resp.~$\nu_\star$) should enter and exit~$\sigma$ in the same direction since~$\mu_\star$ and~$\nu_\star$ are non-kissing;
+\item is well-defined: if both endpoints of~$\sigma$ are in~$Q_0$, then $\mu_\star$ (resp.~$\nu_\star$) enters and exits~$\sigma$ in the same direction since~$\mu_\star$ and~$\nu_\star$ are non-kissing;
 \item is independent of the orientation of~$\mu_\star$ and~$\nu_\star$:~$\mu_\star \prec_\alpha \nu_\star$ iff $(\mu_\star)^{-1} \prec_\alpha \nu_\star$ iff $\mu_\star \prec_\alpha (\nu_\star)^{-1}$; we thus also consider~$\prec_\alpha$ as a relation on undirected marked walks;
@@
 \begin{itemize}
-\item either~$\nu_\star$ contains~$v$, then it must follow~$\mu_\star$ (otherwise~$\nu_\star \prec_\alpha \mu_\star$), so that~$\lambda_\star \prec_\alpha \nu_\star$.
+\item either~$\nu_\star$ contains~$v$, then it must leave~$v$ via the same arrow as~$\mu_\star$ (otherwise~$\nu_\star \prec_\alpha \mu_\star$), so that~$\lambda_\star \prec_\alpha \nu_\star$.
 \item or~$\nu_\star$ does not contain~$v$, then~$\nu_\star$ and~$\mu_\star$ split at a vertex~$w$ between~$\alpha$ and~$v$.
@@
 A \defn{join-representation} of~$x \in L$ is a subset~$J \subseteq L$ such that~${x = \bigJoin J}$.
-Such a representation is \defn{irredundant} if~$x \ne \bigJoin J'$ for a strict subset~$J' \subsetneq J$.
+Such a representation is \defn{irredundant} if~$x \ne \bigJoin J'$ for any strict subset~$J' \subsetneq J$.
 The irredundant join-representations of an element~$x \in L$ are ordered by containement of the lower ideals of their elements, \ie~$J \le J'$ if and only if for any~$y \in J$ there exists~$y' \in J'$ such that~$y \le y'$ in~$L$.

### 2018-07-13 firstPaper/firstPaperShort/nonKissingComplex.tex
Some referee's changes to first paper.

@@
 Let~$\rho$ and~$\rho'$ be two strings for a string algebra~$A$.
-Then the dimension of the $k$-vector space~$\Hom{A} \big( M(\rho), M(\rho') \big)$ is equal to
-
-\smallskip
-\centerline{
-\(
-\sum\limits_{\xi \text{ string}}  (\#\textrm{ of substrings equal to~$\xi$ on top of~$\rho$}) \cdot  (\#\textrm{ of substrings equal to~$\xi$ or~$\xi^{-1}$ at the bottom of~$\rho'$}).
-\)
-}
+Then the dimension of the $k$-vector space~$\Hom{A} \big( M(\rho), M(\rho') \big)$ is equal to the number of pairs~$(\sigma, \sigma')$, where~$\sigma$ and~$\sigma'$ are substrings of~$\rho$ and~$\rho'$, respectively, such that there is an equality of strings~$\sigma' = \sigma^{\pm 1}$.
+
+% \smallskip
+% \centerline{
+% \(
+% \sum\limits_{\xi \text{ string}}  (\#\textrm{ of substrings equal to~$\xi$ on top of~$\rho$}) \cdot  (\#\textrm{ of substrings equal to~$\xi$ or~$\xi^{-1}$ at the bottom of~$\rho'$}).
+% \)
+% }
 \end{proposition}
@@
 The following lemma is immediate and left to the reader.
-See \fref{fig:exmBlossomingQuiver} for an example.
+% See \fref{fig:exmBlossomingQuiver} for an example.
 
@@
 \begin{itemize}
-\item is well-defined: if both endpoints of~$\sigma$ are in~$Q_0$, $\mu_\star$ (resp.~$\nu_\star$) should enter and exit~$\sigma$ in the same direction since~$\mu_\star$ and~$\nu_\star$ are non-kissing;
+\item is well-defined: if both endpoints of~$\sigma$ are in~$Q_0$, then $\mu_\star$ (resp.~$\nu_\star$) enters and exits~$\sigma$ in the same direction since~$\mu_\star$ and~$\nu_\star$ are non-kissing;
 \item is independent of the orientation of~$\mu_\star$ and~$\nu_\star$:~${\mu_\star \prec_\alpha \nu_\star \!\iff\!
@@
 A \defn{join-representation} of~$x \in L$ is a subset~$J \subseteq L$ such that~$x = \bigJoin J$.
-Such a representation is \defn{irredundant} if~$x \ne \bigJoin J'$ for a strict subset~$J' \subsetneq J$.
+Such a representation is \defn{irredundant} if~$x \ne \bigJoin J'$ for any strict subset~$J' \subsetneq J$.
 The irredundant join-representations of an element~$x \in L$ are ordered by containement of the lower ideals of their elements, \ie~$J \le J'$ if and only if for any~$y \in J$ there exists~$y' \in J'$ such that~$y \le y'$ in~$L$.

### 2018-07-13 firstPaper/corrections/replyToReferee.txt
Changes to first paper.
Some referee's changes to first paper.
Some more referee's changes to first paper.

@@
 
-(b) We have added some details (in a new Proposition 2.24) explaining why the non-kissing facets are finite.
-In doing so, we had to slightly reorganise Subsection 2.2.2 (new Lemma 2.23 was previously part of the proof of Proposition (renumbered) 2.28)
+(b) We have added some details (in a new Proposition 2.24) explaining why the 
+    non-kissing facets are finite. In doing so, we had to slightly reorganise 
+    Subsection 2.2.2 (new Lemma 2.23 was previously part of the proof of 
+    Proposition (renumbered) 2.28).
 
@@
 
-  Reply:
+  Reply: Done.
 
@@
 
-  Reply:
+  Reply: Corrected.
 
@@
 
-  Reply:
+  Reply: The formula has been replaced by a sentence.
 
@@
 
-  Reply:
+  Reply: We have replaced "dances with" with "reaches for".
 
@@
 
-  Reply:
+  Reply: Removed.
 
@@
 
-  Reply:
+  Reply: We have replaced "crossing" by "non-kissing and having a common substring".  
+         The term "crossing walks" appeared nowhere else in the paper.
 
@@
 
-  Reply:
+  Reply: Fixed.
 
@@
 
-  Reply:
+  Reply: Clarified.
 
@@
 
-  Reply:
+  Reply: Yes, fixed.
 
@@
 
-  Reply:
+  Reply: While we agree that the notation set is non-conventional, we believe
+         that it fits well with our chosen terminology.  We thus respectfully 
+         propose to keep the notation as it is.

### 2018-07-13 firstPaper/firstPaperLong/nonKissingComplex.tex
Some more referee's changes to first paper.

@@
 }
-{Dictionary between algebraic notions on the support $\tau$-tilting complex and combinatorial notions on the non-kissing complex.}
+{Dictionary between algebraic notions on the support $\tau$-tilting complex and combinatorial notions on the non-kissing complex.
+ \footnotetext[1]{The straight walks should morally correspond to some projective-injective objects in an exact category.
+We plan to further investigate the situation depicted in Figure~\ref{fig:exmAuslanderReitenQuiver}.}
+ \footnotetext[2]{We do not know of an algebraic interpretation of the countercurrent order yet. We nonetheless included it in the table above since we think it might be of interest to find one.}
+}
 {table:dictionary}
+
 \captionsetup{width=\textwidth}
@@
 
-\footnotetext[1]{The straight walks should morally correspond to some projective-injective objects in an exact category.
+% \footnotetext[1]{The straight walks should morally correspond to some projective-injective objects in an exact category.
 We plan to further investigate the situation depicted in Figure~\ref{fig:exmAuslanderReitenQuiver}.}
-\footnotetext[2]{We do not know of an algebraic interpretation of the countercurrent order yet. We nonetheless included it in the table above since we think it might be of interest to find one.}
+% \footnotetext[2]{We do not know of an algebraic interpretation of the countercurrent order yet. We nonetheless included it in the table above since we think it might be of interest to find one.}
 
@@
 	\centerline{\includegraphics[scale=1]{kissingCrossing}}
-	\caption{A schematic representation of two kissing walks (left) and two crossing walks~(right): $\omega$~kisses~$\omega'$ (left) while~$\mu$~crosses~$\nu$ (right).
-For the crossing walks, we have~$\mu \prec_\gamma \nu$ while~$\nu \prec_\delta \mu$.}
+	\caption{A schematic representation of two kissing walks (left) and two non-kissing walks~(right) having a common substring: $\omega$~kisses~$\omega'$ (left) while~$\mu$~does not kiss~$\nu$ (right).
+On the right, we have~$\mu \prec_\gamma \nu$ and~$\nu \prec_\delta \mu$.}
 	\label{fig:kissingCrossing}
@@
 \begin{description}
-\item[closed] Otherwise, there exist bottom substrings~$\sigma_1, \dots, \sigma_\ell$ of walks~$\omega_1, \dots, \omega_\ell$ of~$F'$, arrows~$\alpha_1, \dots, \alpha_{\ell-1} \in Q_1$ and signs~$\varepsilon_1, \dots, \varepsilon_{\ell-1} \in \{-1,1\}$ such that~$\sigma = \sigma_1 \alpha_1^{\varepsilon_1} \dots \alpha_{\ell-1}^{\varepsilon_{\ell-1}} \sigma_\ell$.
+\item[closed] Otherwise, there exist bottom substrings~$\sigma_1, \dots, \sigma_\ell$ of respective walks~$\omega_1, \dots, \omega_\ell$ of~$F'$, arrows~$\alpha_1, \dots, \alpha_{\ell-1} \in Q_1$ and signs~$\varepsilon_1, \dots, \varepsilon_{\ell-1} \in \{-1,1\}$ such that~$\sigma = \sigma_1 \alpha_1^{\varepsilon_1} \dots \alpha_{\ell-1}^{\varepsilon_{\ell-1}} \sigma_\ell$.
 Assume that there is~$k \in [\ell-1]$ such that~${\varepsilon_k = 1}$ and choose~$k$ minimal with that property.
@@
 \label{coro:finalLatticeQuotient}
-If~$\bar Q$ is a gentle bound quiver whose non-kissing complex~$\RNKC$ is finite, then the non-kissing oriented flip graph~$\NKG$ is the Hasse diagram of the lattice quotient~$\Bicl{\bar Q}/{\equiv}$ of the congruence-uniform lattice of biclosed sets of strings by the lattice congruence~$\equiv$.
+If~$\bar Q$ is a gentle bound quiver such that the non-kissing complex~$\RNKC$ is finite, then the non-kissing oriented flip graph~$\NKG$ is the Hasse diagram of the lattice quotient~$\Bicl{\bar Q}/{\equiv}$ of the congruence-uniform lattice of biclosed sets of strings by the lattice congruence~$\equiv$.
 \end{corollary}
@@
 
-Conversely, for a non-self-kissing walk~$\omega \in \NKWalks^\pm(\bar Q)$ not in the peak facet, we denote by~$\sigma_\bottom(\omega)$ the inclusion minimal string in~$\set{\sigma \in \Sigma_\bottom(\omega)}{\closure{\Sigma_\bottom(\omega)} = \closure{\Sigma_\bottom(\sigma)}}$.
+Conversely, for a non-self-kissing walk~$\omega \in \NKWalks^\pm(\bar Q)$ not in the peak facet, the inclusion minimal string in the set~$\set{\sigma \in \Sigma_\bottom(\omega)}{\closure{\Sigma_\bottom(\omega)} = \closure{\Sigma_\bottom(\sigma)}}$ is denoted by~$\sigma_\bottom(\omega)$.
 \end{definition}
@@
 In order to describe the canonical join-representations in the next section, we now completely describe the join-irreducible elements in~$\NKL$.
-We first consider the following join-irreducible elements of~$\Bicl{\bar Q}$.
+Let us first consider the following join-irreducible elements of~$\Bicl{\bar Q}$.
 
@@
 \label{lem:exmBiclosedJI}
-For any distinguishable string~$\sigma \in \strings^\pm(\bar Q)$, the biclosed set~$\closure{\Sigma_\bottom(\sigma)}$ is join-irreducible in~$\Bicl{\bar Q}$.
+Let~$\sigma \in \strings^\pm(\bar Q)$ be a distinguishable string. Then the biclosed set~$\closure{\Sigma_\bottom(\sigma)}$ is join-irreducible in~$\Bicl{\bar Q}$.
 \end{lemma}
@@
 \item $\Sigma$ is pairwise non-friendly.
-\item $\ji(\Sigma) \eqdef \set{\ji(\sigma)}{\sigma \in \Sigma}$ is the canonical join-representation of an element in~$\NKL$.
+\item the set~$\ji(\Sigma) \eqdef \set{\ji(\sigma)}{\sigma \in \Sigma}$ is the canonical join-representation of an element in~$\NKL$.
 \item $\Sigma$ is the descent set of a non-kissing facet~$F \in \NKC$.
@@
 \label{prop:gvectorscvectorsDualBases}
-For a non-kissing facet~$F \in \RNKC$, the set of $\b{g}$-vectors~$\gvectors{F}$ and the set of $\b{c}$-vectors~$\cvectors{F}$ form dual bases. 
+For a non-kissing facet~$F \in \RNKC$, the set~$\gvectors{F}$ of~$\b{g}$-vectors and the set~$\cvectors{F}$ of~$\b{c}$-vectors form dual bases. 
 \end{proposition}

### 2018-07-13 firstPaper/firstPaperShort/nonKissingComplex.tex
Some more referee's changes to first paper.

@@
 \end{theorem*}
-
+\footnotetext[1]{The straight walks should morally correspond to some projective-injective objects in an exact category.
+We plan to further investigate the situation depicted in Figure~\ref{fig:exmAuslanderReitenQuiver}.}
+\footnotetext[2]{We do not know of an algebraic interpretation of the countercurrent order yet. We nonetheless included it in the table above since we think it might be of interest to find one.}
 \noindent

### 2018-07-13 firstPaper/firstPaperLong/nonKissingComplex.tex
footnotes in Table 1

@@
 	\hspace{1cm}
+	\begin{minipage}{18cm}
+	\vspace*{-1cm}
+	\noindent
+	\renewcommand{\arraystretch}{1.2}
 	\begin{tabular}{|c|c|c|}
@@
     \end{tabular}
+	\renewcommand{\arraystretch}{1}
+	\\[.2cm]
+	\footnotemark[1]\footnotesize{The straight walks should morally correspond to some projective-injective objects in an exact category.
+We plan to further investigate the situation depicted in Figure~\ref{fig:exmAuslanderReitenQuiver}.} \\
+	\footnotemark[2]\footnotesize{We do not know of an algebraic interpretation of the countercurrent order yet.
+We nonetheless included it in the table above since we think it might be of interest to find one.}
+	\vspace*{.5cm}
+	\end{minipage}
 	\hspace{1cm}
@@
 {Dictionary between algebraic notions on the support $\tau$-tilting complex and combinatorial notions on the non-kissing complex.
- \footnotetext[1]{The straight walks should morally correspond to some projective-injective objects in an exact category.
-We plan to further investigate the situation depicted in Figure~\ref{fig:exmAuslanderReitenQuiver}.}
- \footnotetext[2]{We do not know of an algebraic interpretation of the countercurrent order yet. We nonetheless included it in the table above since we think it might be of interest to find one.}
 }

### 2018-07-13 firstPaper/corrections/replyToReferee.txt
separation figures
corrections

--- 2018-07-12 firstPaper/corrections/replyToReferee.txt
@@
 
-  Reply:
+  Reply: page 43: We have added a reference to the definition.
 
@@
 
-  Reply:
+  Reply: Done
 
@@
 
-  Reply:
+  Reply: We have removed all appearances of _{exm}, and replaced them by references to the relevant figures.
 
@@
 
-  Reply:
+  Reply: That was a mistake. Thank you for spotting it! We meant non-oriented cycle.
 
@@
 
-  Reply:
+  Reply: $Q_pa$ is now replaced by the more traditional $\overrightarrow{A_n}$.
 
@@
 
-  Reply:
+  Reply: Yes. This has now been made axplicit and we have added the definition of decreasing.
 
@@
 
-  Reply:
+  Reply: The numberings have been corrected.
 

### 2018-07-13 firstPaper/firstPaperLong/nonKissingComplex.tex
separation figures
corrections

--- 2018-07-13 firstPaper/firstPaperLong/nonKissingComplex.tex
@@
 %\renewcommand\labelitemi{$\diamond$} % redefine itemize default symbol
-\newcommand{\ex}{_{\textrm{exm}}} % examples
-\newcommand{\pa}{_{\textrm{pa}}} % path
+\newcommand{\exmAn}{\overrightarrow{A_n}} % path
 
@@
 Let~$\rho$ and~$\rho'$ be two strings for a string algebra~$A$.
-Then the dimension of the $k$-vector space~$\Hom{A} \big( M(\rho), M(\rho') \big)$ is equal to the number of pairs~$(\sigma, \sigma')$, where~$\sigma$ and~$\sigma'$ are substrings of~$\rho$ and~$\rho'$, respectively, such that there is an equality of strings~$\sigma' = \sigma^{\pm 1}$.
-
-% \[
-% \sum\limits_{\xi \text{ string}} \begin{array}{l} (\#\textrm{ of substrings equal to~$\xi$ on top of~$\rho$}) \; \cdot \\ \hspace{2cm}(\#\textrm{ of substrings equal to~$\xi$ or~$\xi^{-1}$ at the bottom of~$\rho'$}).\end{array}
-% \]
+Then the dimension of the $k$-vector space~$\Hom{A} \big( M(\rho), M(\rho') \big)$ is equal to
+\[
+\sum\limits_{\xi \text{ string}} \begin{array}{l} (\#\textrm{ of substrings equal to~$\xi$ on top of~$\rho$}) \; \cdot \\ \hspace{2cm}(\#\textrm{ of substrings equal to~$\xi$ or~$\xi^{-1}$ at the bottom of~$\rho'$}).\end{array}
+\]
 \end{proposition}
@@
 This section focuses on the non-kissing complex of a gentle bound quiver, defined as the clique complex of a non-kissing relation among walks in a blossoming version of the quiver~(\ref{sec:blossomingQuivers}).
-We prove combinatorially that this complex is a pseudomanifold~(\ref{sec:nonKissingComplex}), introducing along the way the definitions of distinguished walks, arrows and substrings~(\ref{subsec:distinguished}) and the operation of flips~(\ref{subsec:flips}) that will be fundamental tools all throughout the paper.
+We prove combinatorially that this complex is a pseudomanifold~(\ref{sec:nonKissingComplex}), introducing along the way the definitions of distinguished walks, arrows and substrings~(\ref{subsec:distinguished}) and the operation of flip~(\ref{subsec:flips}) that will be fundamental tools all throughout the paper.
 We then prove the motivating result of this paper, namely that the support $\tau$-tilting complex is isomorphic to the non-kissing complex for any gentle bound quiver~(\ref{sec:nkcvsttc}).
@@
 \begin{example}
-A gentle bound quiver~$\bar Q\ex$ and its blossoming gentle bound quiver~$\bar Q\ex\blossom$ are represented in \fref{fig:exmBlossomingQuiver}.
+A gentle bound quiver~$\bar Q$ and its blossoming gentle bound quiver~$\bar Q\blossom$ are represented in \fref{fig:exmBlossomingQuiver}.
 \end{example}
@@
 The following lemma is immediate and left to the reader.
-% See \fref{fig:exmBlossomingQuiver}.
+See \fref{fig:exmBlossomingQuiver}.
 
@@
 	\centerline{\includegraphics[scale=.6]{exmBlossomingQuiver}}
-	\caption{A gentle bound quiver~$\bar Q\ex$~(left) and its blossoming gentle bound quiver~$\bar Q\blossom\ex$~(right). Blossom vertices are white and blossom edges are thin.}
+	\caption{A gentle bound quiver~$\bar Q$~(left) and its blossoming gentle bound quiver~$\bar Q\blossom$~(right). Blossom vertices are white and blossom edges are thin.}
 	\label{fig:exmBlossomingQuiver}
@@
 We denote by~$\walks(\bar Q)$ the set of all walks on~$\bar Q$.
-Note that~$\walks(\bar Q)$ is finite if and only if~$\bar Q$ has a relation in any non-kissing cycle.
+Note that~$\walks(\bar Q)$ is finite if and only if~$\bar Q$ has a relation in any (not necessarily oriented) cycle.
 As for strings, we often implicitly identify the two inverse walks~$\omega$ and~$\omega^{-1}$, and we let~$\walks^\pm(\bar Q) \eqdef \set{\{\omega, \omega^{-1}\}}{\omega \in \walks(\bar Q)}$ denote the set of undirected~walks.
@@
 \begin{example}
-\fref{fig:exmFacet} shows examples of walks on the gentle quiver~$\bar Q\ex$ of \fref{fig:exmBlossomingQuiver}.
+\fref{fig:exmFacet} shows examples of walks on the gentle quiver~$\bar Q$ of \fref{fig:exmBlossomingQuiver}.
 \end{example}
@@
 	\centerline{\includegraphics[scale=1.5]{exmBijectionAssociahedron}}
-	\caption{An oriented path~$\bar Q\pa$ is simultaneously a triangulation and a grid bound quiver (top).
-A facet of the reduced non-kissing complex~$\RNKC[\bar Q\pa]$ can be seen as a triangulation or as a collection of non-kissing south-east paths (bottom).}
+	\caption{An oriented path~$\exmAn$ is simultaneously a triangulation and a grid bound quiver (top).
+A facet of the reduced non-kissing complex~$\RNKC[\exmAn]$ can be seen as a triangulation or as a collection of non-kissing south-east paths (bottom).}
 	\label{fig:exmBijectionAssociahedron}
@@
 	\centerline{\includegraphics[scale=.6]{exmFacet}}
-	\caption{(Left) Three walks on the quiver~$\bar Q\ex$ of \fref{fig:exmBlossomingQuiver}: the dotted red and orange walks are non-kissing, but both kiss the plain blue walk.
-(Right) A maximal collection~$F\ex$ of pairwise non-kissing walks on the quiver~$\bar Q\ex$: the thin light blue walks are straight, the others~are~bending.}
+	\caption{(Left) Three walks on the quiver~$\bar Q$ of \fref{fig:exmBlossomingQuiver}: the dotted red and orange walks are non-kissing, but both kiss the plain blue walk.
+(Right) A maximal collection~$F$ of pairwise non-kissing walks on the quiver~$\bar Q$: the thin light blue walks are straight, the others~are~bending.}
 	\label{fig:exmFacet}
@@
 \begin{example}
-\fref{fig:exmFacet}\,(right) shows a facet~$F\ex$ of the non-kissing complex~$\NKC[\bar Q\ex]$ for the quiver~$\bar Q\ex$ of \fref{fig:exmBlossomingQuiver}.
+\fref{fig:exmFacet}\,(right) shows a facet~$F$ of the non-kissing complex~$\NKC[\bar Q]$ for the quiver~$\bar Q$ of \fref{fig:exmBlossomingQuiver}.
 The reduced non-kissing complexes of all connected gentle bound quivers with~$2$ vertices are illustrated on \fref{fig:all2}.
@@
 \begin{itemize}
-\item is well-defined: if both endpoints of~$\sigma$ are in~$Q_0$, then $\mu_\star$ (resp.~$\nu_\star$) enters and exits~$\sigma$ in the same direction since~$\mu_\star$ and~$\nu_\star$ are non-kissing;
+\item is well-defined: if both endpoints of~$\sigma$ are in~$Q_0$, $\mu_\star$ (resp.~$\nu_\star$) should enter and exit~$\sigma$ in the same direction since~$\mu_\star$ and~$\nu_\star$ are non-kissing;
 \item is independent of the orientation of~$\mu_\star$ and~$\nu_\star$:~$\mu_\star \prec_\alpha \nu_\star$ iff $(\mu_\star)^{-1} \prec_\alpha \nu_\star$ iff $\mu_\star \prec_\alpha (\nu_\star)^{-1}$; we thus also consider~$\prec_\alpha$ as a relation on undirected marked walks;
@@
 \begin{itemize}
-\item either~$\nu_\star$ contains~$v$, then it must leave~$v$ via the same arrow as~$\mu_\star$ (otherwise~$\nu_\star \prec_\alpha \mu_\star$), so that~$\lambda_\star \prec_\alpha \nu_\star$.
+\item either~$\nu_\star$ contains~$v$, then it must follow~$\mu_\star$ (otherwise~$\nu_\star \prec_\alpha \mu_\star$), so that~$\lambda_\star \prec_\alpha \nu_\star$.
 \item or~$\nu_\star$ does not contain~$v$, then~$\nu_\star$ and~$\mu_\star$ split at a vertex~$w$ between~$\alpha$ and~$v$.
@@
 	\centerline{\includegraphics[scale=.6]{exmFlip}}
-	\caption{The flip of the orange walk~$\omega$ in the facet~$F\ex$ of \fref{fig:exmFacet}.
-The other two walks~$\mu, \nu$ of~$F\ex$ involved in the flip are the yellow and green walks.
-The distinguished arrows on each walk of~$F\ex$ are marked with triple arrows.}
+	\caption{The flip of the orange walk~$\omega$ in the facet~$F$ of \fref{fig:exmFacet}.
+The other two walks~$\mu, \nu$ of~$F$ involved in the flip are the yellow and green walks.
+The distinguished arrows on each walk of~$F$ are marked with triple arrows.}
 	\label{fig:exmFlip}
@@
 We denote by ${\ascents(F) \subseteq \strings^\pm(\bar Q)}$ and $\descents(F) \subseteq \strings^\pm(\bar Q)$ the sets of ascents and descents of~$F$ respectively.
-%In the opposite situation, the flip is \defn{decreasing} and~$\sigma$ is a descent of~$F$ and an ascent of~$F'$.
+Otherwise,~$\sigma$ is a descent of~$F$ and an ascent of~$F'$ and the flip is called \defn{decreasing}.
 \end{definition}
@@
 Oriented flip graphs were studied carefully in~\cite{GarverMcConville, MannevillePilaud-accordion, McConville} for the dissection and grid bound quivers introduced in Section~\ref{subsec:dissectionGridQuivers}.
-Note that when the quiver is an oriented path~$\bar Q\pa$, a flip in a facet of the non-kissing complex~$\NKC[\bar Q\pa]$ corresponds to the classical flip of a diagonal in the corresponding triangulation (see \fref{fig:exmBijectionAssociahedron}).
+Note that when the quiver is an oriented path~$\exmAn$, a flip in a facet of the non-kissing complex~$\NKC[\exmAn]$ corresponds to the classical flip of a diagonal in the corresponding triangulation (see \fref{fig:exmBijectionAssociahedron}).
 Moreover, the flip is increasing if and only if the slope of the diagonal increases along the flip.
@@
 Namely, we define a closure operator on subsets of strings whose biclosed sets have a lattice structure~(\ref{sec:biclosedStrings}), define a natural lattice congruence on biclosed sets~(\ref{sec:latticeCongruence}), and show that the Hasse diagram of the lattice quotient is isomorphic to the non-kissing oriented flip graph~(\ref{sec:biclosedSetsToNKF}).
-Finally (\ref{sec:nonFriendlyComplex}), we study the join-irreducible elements of~$\NKL$ and the canonical join complex of~$\NKL$ which we call the non-friendly complex as in~\cite{GarverMcConville-grid}.
+Finally (\ref{sec:nonFriendlyComplex}), we study the join-irreducible elements of the non-kissing lattice~$\NKL$ (Definition~\ref{def:NKL}) and the canonical join complex of~$\NKL$ which we call the non-friendly complex as in~\cite{GarverMcConville-grid}.
 
@@
 A \defn{join-representation} of~$x \in L$ is a subset~$J \subseteq L$ such that~${x = \bigJoin J}$.
-Such a representation is \defn{irredundant} if~$x \ne \bigJoin J'$ for any strict subset~$J' \subsetneq J$.
+Such a representation is \defn{irredundant} if~$x \ne \bigJoin J'$ for a strict subset~$J' \subsetneq J$.
 The irredundant join-representations of an element~$x \in L$ are ordered by containement of the lower ideals of their elements, \ie~$J \le J'$ if and only if for any~$y \in J$ there exists~$y' \in J'$ such that~$y \le y'$ in~$L$.
@@
 
-\begin{enumerate}
+\begin{enumerate}[(i)]
 \item We have $R \cup \closure{(\closure{\{\sigma\}} \cup \closure{\{\tau\}} )} =   R \cup \closure{\{\sigma,\tau\}}$.
@@
 	\centerline{\includegraphics[scale=.45]{exmBiclosed}}
-	\caption{Four sets of strings on the gentle bound quiver~$\bar Q\ex$ of \fref{fig:exmBlossomingQuiver}\,(left).
+	\caption{Four sets of strings on the gentle bound quiver of \fref{fig:exmBlossomingQuiver}\,(left).
 The first is neither closed not coclosed, the second is closed but not coclosed, the third is coclosed but not closed, and the fourth is biclosed.}
@@
 In particular, for any two strings~$\sigma, \tau$, the equality~$\closure{\{\sigma\}}=\closure{\{\tau\}}$ implies $\sigma=\tau$.
-We note that $\strings^\pm(\bar Q)$ is partially ordered by:~$\sigma \vartriangleleft \tau$ if and only if~$\sigma$ is a substring of~$\tau$.
+We note that $\strings^\pm(\bar Q)$ is partially ordered by~$\sigma \vartriangleleft \tau$ if and only if~$\sigma$ is a substring of~$\tau$.
 
@@
 			\put(69,8){$\projUp$}
-			\put(12,-3){$\projDown(S\ex)$}
-			\put(50,-3){$S\ex$}
-			\put(85,-3){$\projUp(S\ex)$}
+			\put(12,-3){$\projDown(S)$}
+			\put(50,-3){$S$}
+			\put(85,-3){$\projUp(S)$}
 	\end{overpic}
@@
 	\vspace{.3cm}
-	\caption{A biclosed set of strings~$S\ex \in \Bicl{\bar Q\ex}$ (middle) and its images~$\projDown(S\ex)$ (left) and~$\projUp(S\ex)$ (right) by the down and up projections of Definition~\ref{def:downUpProjections}.
-For space reasons, $\projUp(S\ex)$ is only represented partially: the remaining strings are obtained by adding independently the two dotted arrows to all strings containing their left endpoint.}
+	\caption{A biclosed set of strings~$S \in \Bicl{\bar Q}$ (middle), where~$\bar Q$ is the bound quiver of \fref{fig:exmBlossomingQuiver}, and its images~$\projDown(S)$ (left) and~$\projUp(S)$ (right) by the down and up projections of Definition~\ref{def:downUpProjections}.
+For space reasons, $\projUp(S)$ is only represented partially: the remaining strings are obtained by adding independently the two dotted arrows to all strings containing their left endpoint.}
 	\label{fig:exmProjections}
@@
 \begin{example}
-The map~$\eta$ is illustrated on \fref{fig:exmSurjection}\,(left) for the gentle bound quiver~$\bar Q\ex$ of \fref{fig:exmBlossomingQuiver}\,(left).
+The map~$\eta$ is illustrated on \fref{fig:exmSurjection}\,(left) for the gentle bound quiver of \fref{fig:exmBlossomingQuiver}\,(left).
 
@@
 			\put(70,10){$\zeta$}
-			\put(13,-3){$S\ex$}
-			\put(46,-3){$\eta(S\ex)$}
-			\put(77,-3){$\zeta(\eta(S\ex)) = \projDown(S\ex)$}
+			\put(13,-3){$S$}
+			\put(46,-3){$\eta(S)$}
+			\put(77,-3){$\zeta(\eta(S)) = \projDown(S)$}
 	\end{overpic}
@@
 \begin{example}
-The map~$\zeta$ is illustrated on \fref{fig:exmSurjection}\,(right)  for the gentle bound quiver~$\bar Q\ex$ of \fref{fig:exmBlossomingQuiver}\,(left).
+The map~$\zeta$ is illustrated on \fref{fig:exmSurjection}\,(right)  for the gentle bound quiver of \fref{fig:exmBlossomingQuiver}\,(left).
 \end{example}
@@
 The maps~$\eta$ and~$\zeta$ are illustrated on \fref{fig:exmSurjection}\,(right).
-Compare~$\zeta(\eta(S\ex))$ on \fref{fig:exmSurjection}\,(right) with the down projection~$\projDown(S\ex)$ on \fref{fig:exmProjections}\,(left).
+Compare~$\zeta(\eta(S))$ on \fref{fig:exmSurjection}\,(right) with the down projection~$\projDown(S)$ on \fref{fig:exmProjections}\,(left).
 \end{example}
@@
 
-\begin{definition}
+\begin{definition}\label{def:NKL}
 We call \defn{non-kissing lattice} and denote by~$\NKL$ the transitive closure of the non-kissing oriented flip graph~$\NKG$.
@@
 \begin{example}
-The $\b{g}$-vector of the plain blue walk on \fref{fig:exmFacet}\,(left) is given by $(0,-1,0,0,1,0)$ (see \fref{fig:exmBlossomingQuiver} for the labeling order of the vertices of the quiver~$Q\ex$).
+The $\b{g}$-vector of the plain blue walk on \fref{fig:exmFacet}\,(left) is given by $(0,-1,0,0,1,0)$ (see \fref{fig:exmBlossomingQuiver} for the labeling order of the vertices of the quiver~$Q$).
 See \fref{fig:gcvectors} for more examples of $\b{g}$-vectors.
@@
 \begin{example}
-In the facet~$F\ex$ of \fref{fig:exmFacet}\,(right), the $\b{c}$-vector of the blue walk is~$(0,-1,0,0,0,0)$ while the $\b{c}$-vector of the yellow path is~$(0,1,0,1,1,0)$ (see \fref{fig:exmBlossomingQuiver} for the labeling order of the vertices of the quiver~$Q\ex$ and \fref{fig:gcvectors}\,(left) to see the distinguished arrows in the facet~$F\ex$).
+In the facet~$F$ of \fref{fig:exmFacet}\,(right), the $\b{c}$-vector of the blue walk is~$(0,-1,0,0,0,0)$ while the $\b{c}$-vector of the yellow path is~$(0,1,0,1,1,0)$ (see \fref{fig:exmBlossomingQuiver} for the labeling order of the vertices of the quiver~$Q$ and \fref{fig:gcvectors}\,(left) to see the distinguished arrows in the facet~$F$).
 See \fref{fig:gcvectors} for more examples of $\b{c}$-vectors.
@@
 	\capstart
-	\centerline{$\raisebox{-1.5cm}{\begin{overpic}[scale=.6]{exmVectors}\put(60,4){$F\ex$}\end{overpic}}$ \qquad \input{gcmatrices}}
-	\caption{The $\b{g}$- and $\b{c}$-matrices of the facet~$F\ex$.
-Their columns correspond to the $\b{g}$- and $\b{c}$-vectors of the different walks of~$F\ex$.
-See \fref{fig:exmBlossomingQuiver} for the labeling order of the vertices of the quiver~$Q\ex$.
-Note that~$\gvectors{F\ex} \cdot \cvectors{F\ex}^T = \one$.}
+	\centerline{$\raisebox{-1.5cm}{\begin{overpic}[scale=.6]{exmVectors}\put(60,4){$F$}\end{overpic}}$ \qquad \input{gcmatrices}}
+	\caption{The $\b{g}$- and $\b{c}$-matrices of the facet~$F$ of \fref{fig:exmFacet}.
+Their columns correspond to the $\b{g}$- and $\b{c}$-vectors of the different walks of~$F$.
+See \fref{fig:exmBlossomingQuiver} for the labeling order of the vertices of the quiver~$Q$.
+Note that~$\gvectors{F} \cdot \cvectors{F}^T = \one$.}
 	\label{fig:gcvectors}

### 2018-07-13 firstPaper/firstPaperShort/nonKissingComplex.tex
footnotes in Table 1
corrections

--- 2018-07-12 firstPaper/firstPaperShort/nonKissingComplex.tex
@@
 \begin{example}
-A gentle bound quiver~$\bar Q\ex$ and its blossoming gentle bound quiver~$\bar Q\ex\blossom$ are represented in \fref{fig:exmBlossomingQuiver}.
+A gentle bound quiver~$\bar Q$ and its blossoming gentle bound quiver~$\bar Q\blossom$ are represented in \fref{fig:exmBlossomingQuiver}.
 \vspace*{-.4cm}
@@
 	\centerline{\includegraphics[scale=.7]{exmBlossomingQuiver}}
-	\caption{A gentle bound quiver~$\bar Q\ex$~(left) and its blossoming gentle bound quiver~$\bar Q\blossom\ex$~(right). Blossom vertices are white and blossom edges are thin.}
+	\caption{A gentle bound quiver~$\bar Q$~(left) and its blossoming gentle bound quiver~$\bar Q\blossom$~(right). Blossom vertices are white and blossom edges are thin.}
 	\label{fig:exmBlossomingQuiver}
@@
 \begin{example}
-\fref{fig:exmFacet} shows many examples of walks on the gentle quiver~$\bar Q\ex$ of \fref{fig:exmBlossomingQuiver}.
+\fref{fig:exmFacet} shows many examples of walks on the gentle quiver of \fref{fig:exmBlossomingQuiver}.
 \end{example}
@@
 	\centerline{\includegraphics[scale=1.4]{exmBijectionAssociahedron}}
-	\caption{An oriented path~$\bar Q\pa$ is simultaneously a triangulation and a grid bound quiver (left).
-A facet of the reduced non-kissing complex~$\RNKC[\bar Q\pa]$ can be seen equivalently as a triangulation or as a collection of non-kissing south-east paths (right).}
+	\caption{An oriented path~$\exmAn$ is simultaneously a triangulation and a grid bound quiver (left).
+A facet of the reduced non-kissing complex~$\RNKC[\exmAn]$ can be seen equivalently as a triangulation or as a collection of non-kissing south-east paths (right).}
 	\label{fig:exmBijectionAssociahedron}
@@
 	\centerline{\includegraphics[scale=.7]{exmFacet}}
-	\caption{(Left) Three walks on the quiver~$\bar Q\ex$ of \fref{fig:exmBlossomingQuiver}: the dotted red and orange walks are non-kissing, but both kiss the plain blue walk.
-(Right) A maximal collection~$F\ex$ of pairwise non-kissing walks on the quiver~$\bar Q\ex$: the thin light blue walks are straight, the others~are~bending.}
+	\caption{(Left) Three walks on the bound quiver~$\bar Q$ of \fref{fig:exmBlossomingQuiver}: the dotted red and orange walks are non-kissing, but both kiss the plain blue walk.
+(Right) A maximal collection~$F$ of pairwise non-kissing walks on~$\bar Q$: the thin light blue walks are straight, the others~are~bending.}
 	\label{fig:exmFacet}
@@
 \begin{example}
-\fref{fig:exmFacet}\,(right) shows a facet~$F\ex$ of the non-kissing complex~$\NKC[\bar Q\ex]$ for the quiver~$\bar Q\ex$ of \fref{fig:exmBlossomingQuiver}.
+\fref{fig:exmFacet}\,(right) shows a facet~$F$ of the non-kissing complex~$\NKC[\bar Q]$ for the bound quiver~$\bar Q$ of \fref{fig:exmBlossomingQuiver}.
 The reduced non-kissing complexes of all connected gentle bound quivers with~$2$ vertices are illustrated on \fref{fig:all2}.
@@
 	\centerline{\includegraphics[scale=.7]{exmFlip}}
-	\caption{The flip of the orange walk~$\omega$ in the facet~$F\ex$ of \fref{fig:exmFacet}.
-The other two walks~$\mu, \nu$ of~$F\ex$ involved in the flip are the yellow and green walks.
-The distinguished arrows on each walk of~$F\ex$ are marked with triple arrows.}
+	\caption{The flip of the orange walk~$\omega$ in the facet~$F$ of \fref{fig:exmFacet}.
+The other two walks~$\mu, \nu$ of~$F$ involved in the flip are the yellow and green walks.
+The distinguished arrows on each walk of~$F$ are marked with triple arrows.}
 	\label{fig:exmFlip}
@@
 	\centerline{\includegraphics[scale=.45]{exmBiclosed}}
-	\caption{Four sets of strings on the gentle bound quiver~$\bar Q\ex$ of \fref{fig:exmBlossomingQuiver}\,(left).
+	\caption{Four sets of strings on the gentle bound quiver~$\bar Q$ of \fref{fig:exmBlossomingQuiver}\,(left).
 The first is neither closed not coclosed, the second is closed but not coclosed, the third is coclosed but not closed, and the fourth is biclosed.}
@@
 	\vspace{.3cm}
-	\caption{A biclosed set of strings~$S\ex \in \Bicl{\bar Q\ex}$ (middle) and its images~$\projDown(S\ex)$ (left) and~$\projUp(S\ex)$ (right) by the down and up projections of Definition~\ref{def:downUpProjections}.
-For space reasons, $\projUp(S\ex)$ is only represented partially: the remaining strings are obtained by adding independently the two dotted arrows to all strings containing their left endpoint.}
+	\caption{A biclosed set of strings~$S \in \Bicl{\bar Q\}$ (middle), where~$\bar Q$ is the bound quiver of~\fref{fig:exmBlossomingQuiver}, and its images~$\projDown(S)$ (left) and~$\projUp(S)$ (right) by the down and up projections of Definition~\ref{def:downUpProjections}.
+For space reasons, $\projUp(S)$ is only represented partially: the remaining strings are obtained by adding independently the two dotted arrows to all strings containing their left endpoint.}
 	\label{fig:exmProjections}
@@
 \begin{example}
-The map~$\eta$ is illustrated on \fref{fig:exmSurjection}\,(left) for the gentle bound quiver~$\bar Q\ex$ of \fref{fig:exmBlossomingQuiver}\,(left).
+The map~$\eta$ is illustrated on \fref{fig:exmSurjection}\,(left) for the gentle bound quiver~$\bar Q$ of \fref{fig:exmBlossomingQuiver}\,(left).
 
@@
 \begin{example}
-The map~$\zeta$ is illustrated on \fref{fig:exmSurjection}\,(right)  for the gentle bound quiver~$\bar Q\ex$ of \fref{fig:exmBlossomingQuiver}\,(left).
+The map~$\zeta$ is illustrated on \fref{fig:exmSurjection}\,(right)  for the gentle bound quiver~$\bar Q$ of \fref{fig:exmBlossomingQuiver}\,(left).
 \end{example}
@@
 \begin{example}
-The $\b{g}$-vector of the plain blue walk on \fref{fig:exmFacet}\,(left) is~$(0,-1,0,0,1,0)$ (see \fref{fig:exmBlossomingQuiver} for the labeling order of the vertices of the quiver~$Q\ex$).
+The $\b{g}$-vector of the plain blue walk on \fref{fig:exmFacet}\,(left) is~$(0,-1,0,0,1,0)$ (see \fref{fig:exmBlossomingQuiver} for the labeling order of the vertices of the quiver~$Q$).
 See \fref{fig:gcvectors} for more examples of $\b{g}$-vectors.
@@
 	\capstart
-	\centerline{$\raisebox{-1.5cm}{\begin{overpic}[scale=.7]{exmVectors}\put(60,4){$F\ex$}\end{overpic}}$ \qquad \input{gcmatrices}}
-	\caption{The $\b{g}$- and $\b{c}$-matrices of the facet~$F\ex$.
-Their columns correspond to the $\b{g}$- and $\b{c}$-vectors of the different walks of~$F\ex$.
-See \fref{fig:exmBlossomingQuiver} for the labeling order of the vertices of the quiver~$Q\ex$.
-Note that~$\gvectors{F\ex} \cdot \cvectors{F\ex}^T = \one$.}
+	\centerline{$\raisebox{-1.5cm}{\begin{overpic}[scale=.7]{exmVectors}\put(60,4){$F$}\end{overpic}}$ \qquad \input{gcmatrices}}
+	\caption{The $\b{g}$- and $\b{c}$-matrices of the facet~$F$ of \fref{fig:exmFacet}.
+Their columns correspond to the $\b{g}$- and $\b{c}$-vectors of the different walks of~$F$.
+See \fref{fig:exmBlossomingQuiver} for the labeling order of the vertices of the quiver~$Q$.
+Note that~$\gvectors{F} \cdot \cvectors{F}^T = \one$.}
 	\label{fig:gcvectors}

### 2018-07-13 firstPaper/firstPaperLong/nonKissingComplex.tex

--- 2018-07-13 firstPaper/firstPaperLong/nonKissingComplex.tex
@@
 	\centerline{
-		\begin{tabular}{c@{\qquad}|@{\qquad}c}
+		\begin{tabular}{c@{\qquad}@{\qquad}c}
 			$Q = \vcenter{\hbox{\includegraphics[scale=.5]{exmQuiver1}}}$ &
@@
 			$I = (\alpha\beta, \gamma\delta)$ & 
-			$I = (\alpha\beta, \gamma\delta, \alpha\delta)$ \\ \\ \hline \\
+			$I = (\alpha\beta, \gamma\delta, \alpha\delta)$ \\ \\
 			$Q = \vcenter{\hbox{\includegraphics[scale=.5]{exmQuiver3}}}$ &

### 2018-07-13 firstPaper/firstPaperShort/nonKissingComplex.tex

@@
 	\centerline{
-		\begin{tabular}{c@{\quad}|@{\quad}c@{\quad}|@{\quad}c@{\quad}|@{\quad}c}
+		\begin{tabular}{c@{\quad}@{\quad}c@{\quad}@{\quad}c@{\quad}@{\quad}c}
 			$Q = \vcenter{\hbox{\includegraphics[scale=.5]{exmQuiver1}}}$ &

### 2018-07-13 firstPaper/firstPaperLong/nonKissingComplex.tex
first 20 pages of overfullboxes

--- 2018-07-13 firstPaper/firstPaperLong/nonKissingComplex.tex
@@
-\documentclass{memo-l}
+\documentclass[draft]{memo-l}
 
@@
 A \defn{path} in~$Q$ is a sequence~$\pi = \alpha_1 \dots \alpha_\ell$ of~$Q_1$ such that~$t(\alpha_k) = s(\alpha_{k+1})$ for all~${k \in [\ell-1]}$ (note that we compose arrows from left to right).
-The \defn{source} (resp.~\defn{target}) of~$\pi$ is~$s(\pi) \eqdef s(\alpha_1)$ (resp.~$t(\pi) \eqdef t(\alpha_\ell)$), and the \defn{length} of~$\pi$ is~$\ell(\pi) \eqdef \ell$.
+Its \defn{source} (resp.~\defn{target}) is~$s(\pi) \eqdef s(\alpha_1)$ (resp.~$t(\pi) \eqdef t(\alpha_\ell)$), and its \defn{length} is~$\ell(\pi) \eqdef \ell$.
 Note that for each vertex~$v \in Q_0$, we also consider the \defn{path~$\varepsilon_v$ of length zero} with source and target~$s(\varepsilon_v) = t(\varepsilon_v) = v$.
@@
 
-For a quiver~$Q = (Q_0, Q_1, s, t)$, define its \defn{reversed quiver} by~$\reversed{Q} \eqdef (Q_0, Q_1, t, s)$.
+For a quiver~$Q = (Q_0, Q_1, s, t)$, define its \defn{reversed quiver}~$\reversed{Q} \eqdef (Q_0, Q_1, t, s)$.
 For a path~$\pi$ on~$Q$, define its \defn{reversed path} on~$\reversed{Q}$ by~$\reversed{(\alpha_1 \cdots \alpha_\ell)} = \alpha_\ell \cdots \alpha_1$, and extend it by linearity to a morphism~$kQ \to k\reversed{Q}$ of path algebras.
@@
     \item A string module is never isomorphic to a band module.
-    \item Two string modules~$M(\rho)$ and~$M(\rho')$ are isomorphic if and only if~${\rho' = \rho^{\pm 1}}$.
+    \item Two string modules~$M(\rho), M(\rho')$ are isomorphic if and only if~${\rho' = \rho^{\pm 1}}$.
     \item Two band modules~$M(\varpi,\lambda, d)$ and~$M(\varpi', \lambda', d')$ are isomorphic if and only if~$d=d'$, and  
@@
   \begin{itemize}
-    \item \defn{starts} (resp.~\defn{ends}) \defn{on a peak} if there is no arrow~$\alpha$ such that~$\alpha \rho$ (resp.~$\rho\alpha^{-1}$) is a string,
+    \item \defn{starts} (resp.~\defn{ends}) \defn{on a peak} if there is no arrow~$\alpha$ such that~$\alpha \rho$ (resp.\,$\rho\alpha^{-1}$) is a string,
     \item \defn{starts} (resp.~\defn{ends}) \defn{in a deep} if there is no arrow~$\alpha$ such that~$\alpha^{-1} \rho$ (resp.~$\rho \alpha$) is a string.
@@
 \begin{example}
-In the quiver of Example~\ref{exm:aStringAlgebra}, the string~$\rho = \gamma\beta^{-1}\alpha^{-1}\gamma\beta^{-1}\alpha^{-1}\gamma\delta$ of Example~\ref{exm:drawingString} does not start on a deep, and we have
+The string~$\rho = \gamma\beta^{-1}\alpha^{-1}\gamma\beta^{-1}\alpha^{-1}\gamma\delta$ of Example~\ref{exm:drawingString} in the quiver of Example~\ref{exm:aStringAlgebra} does not start on a deep, and we have
 \[
@@
 
-    \item Dually, if~$\rho$ ends on a peak and is not the inverse of a path in~$\bar Q$, then the string obtained by \defn{removing a cohook at the end of~$\rho$} is~${\rho_{c^{-1}} \eqdef (_{c^{-1}} (\rho^{-1}) )^{-1}}$.
+    \item Dually, if~$\rho$ ends on a peak and is not the inverse of a path in~$\bar Q$, then the string obtained by \defn{removing a cohook at the end of~$\rho$} is~${\rho_{c^{-1}} \!
+\eqdef (_{c^{-1}} \!
+(\rho^{-1}) )^{-1}}$.
 
@@
 Consider a string algebra~$A = kQ/I$.
-The Auslander-Reiten translation transforms string modules to string modules: for a string~$\rho$ of~$\bar Q$, we have~${\tau \big( M(\rho) \big) = M(\rho')}$, where the string~$\rho'$ is obtained by following the table below.
+Then the Auslander-Reiten translation transforms string modules to string modules: for a string~$\rho$ of~$\bar Q$, we have~${\tau \big( M(\rho) \big) = M(\rho')}$, where the string~$\rho'$ is obtained by following the table below.
 \\[.3cm]
@@
  $\bigoplus_{v\in Q_0} \Z [P(v)] \cong \Z^{Q_0}$.  Thus, in the notation of Definition \ref{definition: g-vector of representation},
- if $P_0^M = \bigoplus_{v\in Q_0}P(v)^{\oplus a_v}$ and $P_1^M = \bigoplus_{v\in Q_0}P(v)^{\oplus b_v}$, 
+ if $P_0^M = \bigoplus_{v\in Q_0} \! P(v)^{\oplus a_v}$ and $P_1^M = \bigoplus_{v\in Q_0} \! P(v)^{\oplus b_v}$, 
  then
@@
   		\(
-         \b{r} = \begin{cases}
+         \b{r} = \! \begin{cases}
                    0 & \textrm{if $\rho$ starts and ends in a deep,} \\
-                   \b{e}_{t(\alpha)}   & \textrm{if $\rho$ ends in a deep and $\alpha^{-1}\rho$ is a string, with $\alpha\in Q_1$,} \\
+                   \b{e}_{t(\alpha)}   & \textrm{if $\rho$ ends in a deep and $\alpha^{-1}\rho$ is a string with $\alpha\in Q_1$,} \\
                    \b{e}_{t(\beta)}    & \textrm{if $\rho$ starts in a deep and $\rho\beta$ is a string, with $\beta\in Q_1$,} \\
-                   \b{e}_{t(\alpha)} + \b{e}_{t(\beta)}  & \textrm{if $\alpha^{-1}\rho\beta$ is a string, with $\alpha, \beta\in Q_1$,}
+                   \b{e}_{t(\alpha)} + \b{e}_{t(\beta)} \!\!\! & \textrm{if $\alpha^{-1}\rho\beta$ is a string, with $\alpha, \beta\in Q_1$,}
                   \end{cases}
@@
 Assume first that~$\rho$ attracts~$\rho'$ (Figure~\ref{fig:rho attracts rho'}), and let~$\alpha$ be as in Definition~\ref{definition: dance and attract}.
-Since~$\rho'$ does not start in a deep,~$\rho''$ starts at a substring~$\alpha_1\cdots\alpha_r$, where~$\alpha_r\cdots\alpha_1\alpha^{-1}$ is the cohook at the start of~$\rho'$.
+As~$\rho'$ does not start in a deep,~$\rho''$ starts at a substring~$\alpha_1\cdots\alpha_r$, where~$\alpha_r\cdots\alpha_1\alpha^{-1}$ is the cohook at the start of~$\rho'$.
 Let~$0\leq k\leq r$ be maximal such that~$\alpha_k\cdots\alpha_1$ is a substring (possibly a vertex if $k=0$) of~$\rho$ ending in~$u$, where~$u$ is as in Definition~\ref{definition: dance and attract}.

### 2018-07-13 firstPaper/firstPaperLong/nonKissingComplex.tex
RobustCommand
compil

@@
-\documentclass[draft]{memo-l}
+\documentclass{memo-l}
 
@@
 %\renewcommand\labelitemi{$\diamond$} % redefine itemize default symbol
-\newcommand{\exmAn}{\overrightarrow{A_n}} % path
+\DeclareRobustCommand{\exmAn}{\overrightarrow{A_n}} % path
 
@@
 \begin{remark}
-The criterion of Proposition \ref{proposition: attract or dance and tau compatibility} for $\tau$-compatibility between string modules can be compared with a similar criterion obtained recently in \cite{CanakciPauksztelloSchroll} for the existence of extensions between two string modules.
-The similarity between the two criteria is explained by the Auslander--Reiten formula asserting that $\Ext{}^1(N,M)$ is a quotient of the space $\Hom{}(M,\tau N)$ (see \cite[Theorem IV.2.13]{AssemSimsonSkowronski}).
+The criterion of Proposition \ref{proposition: attract or dance and tau compatibility} for $\tau$-compatibility between string modules can be compared with a very similar criterion obtained recently in \cite{CanakciPauksztelloSchroll} for the existence of extensions between two string modules.
+The similarity between the two criteria is explained by the Auslander--Reiten formula asserting that $\Ext{}^1(N,M)$ is a quotient of the space $\Hom{}(M,\tau N)$ (see \cite[Thm.~IV.2.13]{AssemSimsonSkowronski}).
 \end{remark}

### 2018-07-13 firstPaper/firstPaperLong/nonKissingComplex.tex
all overfullboxes

@@
 \begin{definition}\label{def: nKc}
-The \defn{non-kissing complex} of~$\bar Q$ is the simplicial complex~$\NKC$ whose faces are the collections of pairwise non-kissing walks of~$\NKWalks^\pm(\bar Q)$.
+The \defn{non-kissing complex} of~$\bar Q$ is the simplicial complex $\NKC$ whose faces are the collections of pairwise non-kissing walks of~$\NKWalks^\pm(\bar Q)$.
 Note that self-kissing walks never appear in~$\NKC$ by definition.
@@
 \begin{proof}
-If~$\omega$ is not maximal in~$F$ for~$\prec_\alpha$, consider~${\mu \eqdef \min_{\prec_\alpha} \set{\nu \in F_\alpha}{\omega \prec_\alpha \nu}}$.
+If~$\omega$ is not maximal in~$F$ for~$\prec_\alpha$, let~${\mu \eqdef \min_{\prec_\alpha} \set{\nu \in F_\alpha}{\omega \prec_\alpha \nu}}$.
 Let~$\sigma$ denote the maximal common substring of~$\omega$ and~$\mu$ containing~$\alpha$.
@@
 \begin{proof}
-By Lemma~\ref{lemma: distinguished arrows exists}, the cardinality of any finite non-kissing face is bounded by~$|Q_1\blossom|$.
+By Lemma~\ref{lemma: distinguished arrows exists}, the cardinality of any finite non-kissing face of~$\NKC$ is bounded by~$|Q_1\blossom|$.
 Thus, any collection of~$|Q_1\blossom|+1$ walks contains a kiss and all non-kissing faces are finite.
@@
 \begin{example}
-Distinguished arrows and walks are illustrated on \fref{fig:exmFlip}\,(left).
+\fref{fig:exmFlip}\,(left) illustrates distinguished arrows and walks.
 \end{example}
@@
 %For any~$v \in Q_1$, the distinguished string of the peak walk~$v_\peak$ in the peak facet~$F_\peak$ is~$v$ and the distinguished string of the peak walk~$v_\peak$ in the peak facet~$F_\peak$ is~$v$.
-For any~$v \in Q_1$, we have~${\distinguishedString{v_\peak}{F_\peak} = \distinguishedString{v_\deep}{F_\deep} = \varepsilon_v}$.
+For~$v \in Q_1$, we have~${\distinguishedString{v_\peak}{F_\peak} = \distinguishedString{v_\deep}{F_\deep} = \varepsilon_v}$.
 \end{example}
@@
 
-We now show that the non-kissing complex~$\RNKC$ is \defn{thin}, \ie that any codimension~$1$ non-kissing face of~$\RNKC$ is contained in exactly two non-kissing facets of~$\RNKC$.
+We now prove that the non-kissing complex~$\RNKC$ is \defn{thin}, \ie that any codimension~$1$ non-kissing face of~$\RNKC$ is contained in exactly two non-kissing facets of~$\RNKC$.
 Here again, it is more convenient to work with the unreduced non-kissing complex~$\NKC$.
@@
 To prove that it is coclosed, consider~${\tau \in \closure{\Sigma_\bottom(\sigma)}}$.
-There are substrings~$\tau_1, \dots, \tau_{\ell-1} \in \Sigma_\bottom(\sigma)$, arrows $\alpha_1, \dots, \alpha_{\ell-1} \in Q_1$ and signs~${\varepsilon_1, \dots, \varepsilon_\ell \in \{-1,1\}}$ such that~$\tau = \tau_1 \alpha_1^{\varepsilon_1} \tau_2 \alpha_2^{\varepsilon_2} \cdots \alpha_{\ell-1}^{\varepsilon_{\ell-1}} \tau_\ell$.
+There are substrings~$\tau_1, \dots, \tau_{\ell-1} \in \Sigma_\bottom(\sigma)$, arrows $\alpha_1, \dots, \alpha_{\ell-1} \in Q_1$ and signs~${\varepsilon_1, \dots, \varepsilon_\ell \in \{-1,1\}}$ such that~$\tau = \tau_1 \alpha_1^{\varepsilon_1} \cdots \alpha_{\ell-1}^{\varepsilon_{\ell-1}} \tau_\ell$.
 Assume that~$\tau = \tau' \beta^\varepsilon \tau''$ for some strings~$\tau', \tau'' \in \strings(\bar Q)$, an arrow~$\beta \in Q_1$, and a sign~$\varepsilon$.
@@
 \item If~$\varepsilon = -1$, then~$\tau_k'$ is a bottom substring of~$\tau_k$ which is a bottom substring of~$\sigma$, so that~$\tau_k' \in \Sigma_\bottom(\sigma)$ and thus~$\tau' = \tau_1 \alpha_1^{\varepsilon_1} \dots \alpha_{k-1}^{\varepsilon_{k-1}} \tau_k' \in \closure{\Sigma_\bottom(\sigma)}$.
-\item Similarly, if~$\varepsilon = 1$, then~$\tau''_k$ is a bottom substring of~$\tau_k$ which is a bottom substring of~$\sigma$, so that~$\tau_k'' \in \Sigma_\bottom(\sigma)$ and~${\tau'' = \tau_k'' \alpha_k^{\varepsilon_k} \dots \alpha_{\ell-1}^{\varepsilon_{\ell-1}} \tau_\ell \in \closure{\Sigma_\bottom(\sigma)}}$.
+\item Similarly, if~$\varepsilon = 1$, then~$\tau''_k$ is a bottom substring of~$\tau_k$ which is a bottom substring of~$\sigma$, thus~$\tau_k'' \in \Sigma_\bottom(\sigma)$ and~${\tau'' = \tau_k'' \alpha_k^{\varepsilon_k} \dots \alpha_{\ell-1}^{\varepsilon_{\ell-1}} \tau_\ell \in \closure{\Sigma_\bottom(\sigma)}}$.
 \end{itemize}
@@
 
-The goal of this section is to show that the non-kissing oriented flip graph~$\NKG$ is isomorphic to the Hasse diagram of the lattice quotient of the lattice of biclosed sets~$\Bicl{\bar Q}$ by the lattice congruence~$\equiv$.
+The objective of this section is to show that the non-kissing oriented flip graph~$\NKG$ is isomorphic to the Hasse diagram of the lattice quotient of the lattice of biclosed sets~$\Bicl{\bar Q}$ by the lattice congruence~$\equiv$.
 For this, we first need to define inverse bijections between congruence classes of biclosed sets of~$\Bicl{\bar Q}$ and non-kissing facets of~$\NKC$.
@@
 \begin{proposition}
-For any non-kissing facet~$F \in \NKC$, the set of strings~$\zeta(F)$ is biclosed.
+The set of strings $\zeta(F)$ is biclosed for any non-kissing facet~$F \in \NKC$.
 \end{proposition}
@@
 \label{prop:surjection}
-For any non-kissing facet~$F \in \NKC$, we have~${\eta \big( \zeta(F) \big) \! = F}$.
+We have~${\eta \big( \zeta(F) \big) \! = \! F}$ for any non-kissing facet~$F \! \in \! \NKC$.
 \end{proposition}
@@
 Since~$\omega$ and~$\omega'$ split at~$t(\sigma)$, this forces~$\omega' \ssm \sigma$ to have an incoming arrow at~$t(\sigma)$.
-Thus,~${\sigma \in \zeta(F)}$.
+Thus,~${\sigma \!
+\in \!
+\zeta(F)}$.
 Therefore, there exist bottom substrings~$\sigma_1, \dots, \sigma_\ell$ of walks~$\omega_1, \dots, \omega_\ell$ of~$F$, arrows~${\alpha_1, \dots, \alpha_{\ell-1} \in Q_1}$, and signs~$\varepsilon_1, \dots, \varepsilon_{\ell-1} \in \{-1,1\}$ such that~${\sigma = \sigma_1 \alpha_1^{\varepsilon_1} \cdots \alpha_{\ell-1}^{\varepsilon_{\ell-1}} \sigma_\ell}$.
@@
 Assume first that~$\sigma \notin S \cup T$.
-Since~${\sigma \in \Sigma_\bottom(\sigma) \subseteq \closure{\Sigma_\bottom(\sigma)} = S \join T = \closure{(S \cup T)}}$, there exists strings~$\sigma_1, \dots, \sigma_\ell \in \closure{\Sigma_\bottom(\sigma)} \ssm \{\sigma\}$, arrows~$\alpha_1, \dots, \alpha_{\ell-1} \in Q_1$ and signs~$\varepsilon_1, \dots, \varepsilon_{\ell-1} \in \{-1,1\}$ such that~$\sigma = \sigma_1 \alpha_1^{\varepsilon_1} \dots \alpha_{\ell-1}^{\varepsilon_{\ell-1}} \sigma_\ell$.
+As~${\sigma \in \Sigma_\bottom(\sigma) \subseteq \closure{\Sigma_\bottom(\sigma)} = S \join T = \closure{(S \cup T)}}$, there exists strings~$\sigma_1, \dots, \sigma_\ell \in \closure{\Sigma_\bottom(\sigma)} \ssm \{\sigma\}$, arrows~$\alpha_1, \dots, \alpha_{\ell-1} \in Q_1$ and signs~$\varepsilon_1, \dots, \varepsilon_{\ell-1} \in \{-1,1\}$ such that~$\sigma = \sigma_1 \alpha_1^{\varepsilon_1} \dots \alpha_{\ell-1}^{\varepsilon_{\ell-1}} \sigma_\ell$.
 Assume that there exists~$k \in [\ell-1]$ such that~$\varepsilon_k = 1$ and choose~$k$ maximal for this property.
@@
 \]
-Since~$F$ is join-irreducible, we obtain that there is~$\omega \in F$ such that~${F = \eta \big( \closure{\Sigma_\bottom(\omega)} \big)}$.
+As~$F$ is join-irreducible, we obtain that there is~$\omega \in F$ such that~${F = \eta \big( \closure{\Sigma_\bottom(\omega)} \big)}$.
 By Lemma~\ref{lem:bijectionWalksDistinguishableStrings}, we obtain that there exists a distinguishable string~$\sigma = \sigma_\bottom(\omega)$ such that ${\closure{\Sigma_\bottom(\omega)} = \closure{\Sigma_\bottom(\sigma)}}$.
@@
 \begin{theorem}
-The following assertions are equivalent for a subset~$\Sigma$ of~$\distinguishableStrings^\pm(\bar Q)$:
+The following assertions are equivalent for a~$\Sigma \subseteq \distinguishableStrings^\pm(\bar Q)$:
 \begin{enumerate}[(i)]
@@
 \closure{\Sigma_\bottom(\rho)} \subseteq \closure{\Sigma_\bottom(\tau)},
-\qquad
+\quad
 \closure{\Sigma_\bottom(\sigma')} \subseteq \closure{\Sigma_\bottom(\sigma)}
-\qquad\text{and}\qquad
+\quad\text{and}\quad
 \closure{\Sigma_\bottom(\sigma'')} \subseteq \closure{\Sigma_\bottom(\sigma)}.
@@
 \item $\Fan$ is the normal fan of a simple polytope in~$\R^n$;
-\item There exists a map~$h: V \to \R_{> 0}$ such that for any two adjacent facets~$\triangle, \triangle'$ of~$\Delta$ with~$\triangle \ssm \{v\} = \triangle' \ssm \{v'\}$, we have
+\item There exists a map~$h: V \to \R_{> 0}$ such that for any two adjacent facets~$\triangle$ and~$\triangle'$ of~$\Delta$ with~$\triangle \ssm \{v\} = \triangle' \ssm \{v'\}$, we have
 \[
@@
 \begin{definition}\label{def: g-vectors for walks}
-For a walk~$\omega \in \NKWalks^\pm(\bar Q)$, we denote by~$\peaks{\omega}$ (resp.~by~$\deeps{\omega}$) the multiset of vertices of~$Q_0$ corresponding to the peaks (resp.~deeps) of~$\omega$.
+For a walk~$\omega \in \NKWalks^\pm(\bar Q)$, we let~$\peaks{\omega}$ (resp.~$\deeps{\omega}$) denote the multiset of vertices of~$Q_0$ corresponding to the peaks (resp.~deeps) of~$\omega$.
 The \defn{$\b{g}$-vector} of a walk~$\omega$ is the vector~${\gvector{\omega} \in \R^{Q_0}}$ defined by
@@
 \label{exm:gcvectors}
-The $\b{g}$- and $\b{c}$-vectors of the peak and deep facets~$F_\peak$ and~$F_\deep$ are given by
+The $\b{g}$- and $\b{c}$-vectors of the peak facet~$F_\peak$ and the deep facet~$F_\deep$ are given by
 \begin{align*}
@@
 There is a subtle relation between $\b{c}$-vectors and strings. Indeed, $\b{c}$-vectors are multiplicity vectors of the vertex multisets of some strings of~$\bar Q$, but
-\begin{itemize}
-\item not all strings are distinguishable (see Definition~\ref{def:distinguishedSubstring} and Proposition~\ref{prop:characterizationDistinguishableStrings}), and
+\begin{enumerate}[(i)]
+\item not all strings are distinguishable (see Definition~\ref{def:distinguishedSubstring} and Proposition~\ref{prop:characterizationDistinguishableStrings}),
 \item distinct distinguishable strings may have identical vertex multisets.
-\end{itemize}
+\end{enumerate}
 \end{remark}
@@
 Theorem~\ref{thm:gvectorFan} extends to any finite-dimensional algebra~$A$. More precisely:
-\begin{itemize}
+\begin{enumerate}[(i)]
 \item As pointed out to us by L.~Demonet, a similar linear dependence holds for a mutation in the support $\tau$-tilting complex of any finite-dimensional algebra~$A$.
@@
 The existence of an exchange triangle ${X \rightarrow \bigoplus_{i \in [k]} Y_i \rightarrow X' \rightarrow X[1]}$ (see~\cite{AiharaIyama}) immediately gives the equality~$[X] + [X'] = \sum_{i \in [k]} [Y_i]$ in the Grothendieck group, yielding the claimed linear dependence among~$\b{g}$-vectors.
-\item By Proposition~\ref{prop:characterizationFan}, this suffices to prove Theorem~\ref{thm:gvectorFan} for any finite-dimensional algebra~$A$ with finite support $\tau$-tilting complex. 
+\item By Proposition~\ref{prop:characterizationFan}, this suffices to prove Theorem~\ref{thm:gvectorFan} for any finite-dimensio\-nal algebra~$A$ with finite support $\tau$-tilting complex. 
 \item This simple argument fails when the support $\tau$-tilting complex is infinite.
@@
 This can be proven using the (much harder) result~\cite{DehyKeller, DemonetIyamaJasso} that $\tau$-rigid objects are determined by their~$\b{g}$-vectors.
-\end{itemize}
+\end{enumerate}
 \end{remark}
@@
 \label{thm:associahedron}
-For a gentle bound quiver~$\bar Q$ with finite non-kissing complex~$\RNKC$, the $\b{g}$-vector fan~$\gvectorFan$ is the normal fan of the \defn{$\bar Q$-associahedron}~$\Asso$ defined equivalently~as
+For a gentle bound quiver~$\bar Q$ whose non-kissing complex~$\RNKC$ is finite, the $\b{g}$-vector fan~$\gvectorFan$ is the normal fan of the \defn{$\bar Q$-associahedron}~$\Asso$ defined equivalently~as
 \begin{enumerate}[(i)]
@@
 For example, the top line of \fref{fig:exmAssociahedra} already appeared in~\cite{MannevillePilaud-accordion}.
-\item In contrast, the non-kissing associahedron was not known for a grid bound quiver.
+\item In contrast, the non-kissing associahedron was not known for an arbitrary grid bound quiver.
 Our construction thus answers a question of A.~Garver and T.~McConville~\cite{GarverMcConville-grid} concerning the polytopality of the $\b{g}$-vector fan~$\gvectorFan[\bar Q(L)]$ for a subset~$L$ of~$\Z^2$.
@@
 \item a linear dependence~$[X] + [X'] = \sum_{i \in [k]} [Y_i]$ in the Grothendieck group (see Remark~\ref{rem:linDep}),
-\item an inequality of the form~$\KN(X) + \KN(X') > \sum_{i \in [k]} \KN(Y_i)$ for~${\KN \in \{\KN_\ell, \KN_r\}}$.
+\item an inequality of the form~$\KN(X) + \KN(X') > \sum_{i \in [k]} \KN(Y_i)$ for~${\KN \! \in \! \{\KN_\ell, \KN_r\}}$.
 \end{enumerate}
@@
 \label{exm:permutahedron}
-When~$\bar Q$ is a type~$A$ quiver, the $\bar Q$-zonotope~$\Zono$ is the Minkowski sum of all characteristic vectors of intervals (\ie all type~$A_n$ roots), thus yielding the classical permutahedron.
+When~$\bar Q$ is a type~$A$ quiver, the $\bar Q$-zonotope~$\Zono$ is the Minkowski sum of all characteristic vectors of intervals (\ie all type~$A_n$ positive roots), thus yielding the classical permutahedron.
 In this situation, the $\bar Q$-associahedron~$\Asso$ is thus obtained by deleting inequalities in the facet description of the $\bar Q$-zonotope $\Zono$.

### 2018-07-13 firstPaper/firstPaperLong/nonKissingComplex.tex
modifs referee first paper + BC18 second paper

--- 2018-07-13 firstPaper/firstPaperLong/nonKissingComplex.tex
@@
 
-The non-kissing complex is a simplicial complex of pairwise non-kissing paths in a fixed shape of a grid.
+The non-kissing complex is the simplicial complex of a compatibility relation, called non-kissing, on paths in a fixed shape of a grid.
 It was introduced by T.~K.~Petersen, P.~Pylyavskyy and D.~Speyer in~\cite{PetersenPylyavskyySpeyer} for a staircase shape, studied by F.~Santos, C.~Stump and V.~Welker~\cite{SantosStumpWelker} for rectangular shapes, and extended by T.~McConville in~\cite{McConville} for arbitrary shapes.
@@
 A \defn{path} in~$Q$ is a sequence~$\pi = \alpha_1 \dots \alpha_\ell$ of~$Q_1$ such that~$t(\alpha_k) = s(\alpha_{k+1})$ for all~${k \in [\ell-1]}$ (note that we compose arrows from left to right).
-Its \defn{source} (resp.~\defn{target}) is~$s(\pi) \eqdef s(\alpha_1)$ (resp.~$t(\pi) \eqdef t(\alpha_\ell)$), and its \defn{length} is~$\ell(\pi) \eqdef \ell$.
+The \defn{source} (resp.~\defn{target}) of~$\pi$ is~$s(\pi) \eqdef s(\alpha_1)$ (resp.~$t(\pi) \eqdef t(\alpha_\ell)$), and the \defn{length} of~$\pi$ is~$\ell(\pi) \eqdef \ell$.
 Note that for each vertex~$v \in Q_0$, we also consider the \defn{path~$\varepsilon_v$ of length zero} with source and target~$s(\varepsilon_v) = t(\varepsilon_v) = v$.
@@
 
-For a quiver~$Q = (Q_0, Q_1, s, t)$, define its \defn{reversed quiver}~$\reversed{Q} \eqdef (Q_0, Q_1, t, s)$.
+For a quiver~$Q = (Q_0, Q_1, s, t)$, define its \defn{reversed quiver} by~$\reversed{Q} \eqdef (Q_0, Q_1, t, s)$.
 For a path~$\pi$ on~$Q$, define its \defn{reversed path} on~$\reversed{Q}$ by~$\reversed{(\alpha_1 \cdots \alpha_\ell)} = \alpha_\ell \cdots \alpha_1$, and extend it by linearity to a morphism~$kQ \to k\reversed{Q}$ of path algebras.
+We denote by~$\reversed{I}$ the direct image of~$I$ under this morphism.
 The \defn{reversed bound quiver} of a bound quiver~$\bar Q = (Q,I)$ is the bound quiver~$\reversed{\bar Q} \eqdef (\reversed{Q},\reversed{I})$.
@@
     \item A string module is never isomorphic to a band module.
-    \item Two string modules~$M(\rho), M(\rho')$ are isomorphic if and only if~${\rho' = \rho^{\pm 1}}$.
+    \item Two string modules~$M(\rho)$ and~$M(\rho')$ are isomorphic if and only if~${\rho' = \rho^{\pm 1}}$.
     \item Two band modules~$M(\varpi,\lambda, d)$ and~$M(\varpi', \lambda', d')$ are isomorphic if and only if~$d=d'$, and  
@@
   \begin{itemize}
-    \item \defn{starts} (resp.~\defn{ends}) \defn{on a peak} if there is no arrow~$\alpha$ such that~$\alpha \rho$ (resp.\,$\rho\alpha^{-1}$) is a string,
+    \item \defn{starts} (resp.~\defn{ends}) \defn{on a peak} if there is no arrow~$\alpha$ such that~$\alpha \rho$ (resp.~$\rho\alpha^{-1}$) is a string,
     \item \defn{starts} (resp.~\defn{ends}) \defn{in a deep} if there is no arrow~$\alpha$ such that~$\alpha^{-1} \rho$ (resp.~$\rho \alpha$) is a string.
@@
 \begin{example}
-The string~$\rho = \gamma\beta^{-1}\alpha^{-1}\gamma\beta^{-1}\alpha^{-1}\gamma\delta$ of Example~\ref{exm:drawingString} in the quiver of Example~\ref{exm:aStringAlgebra} does not start on a deep, and we have
+In the quiver of Example~\ref{exm:aStringAlgebra}, the string~$\rho = \gamma\beta^{-1}\alpha^{-1}\gamma\beta^{-1}\alpha^{-1}\gamma\delta$ of Example~\ref{exm:drawingString} does not start on a deep, and we have
 \[
@@
 
-    \item Dually, if~$\rho$ ends on a peak and is not the inverse of a path in~$\bar Q$, then the string obtained by \defn{removing a cohook at the end of~$\rho$} is~${\rho_{c^{-1}} \!
-\eqdef (_{c^{-1}} \!
-(\rho^{-1}) )^{-1}}$.
+    \item Dually, if~$\rho$ ends on a peak and is not the inverse of a path in~$\bar Q$, then the string obtained by \defn{removing a cohook at the end of~$\rho$} is~${\rho_{c^{-1}} \eqdef (_{c^{-1}} (\rho^{-1}) )^{-1}}$.
 
@@
 Consider a string algebra~$A = kQ/I$.
-Then the Auslander-Reiten translation transforms string modules to string modules: for a string~$\rho$ of~$\bar Q$, we have~${\tau \big( M(\rho) \big) = M(\rho')}$, where the string~$\rho'$ is obtained by following the table below.
+The Auslander-Reiten translation transforms string modules to string modules: for a string~$\rho$ of~$\bar Q$, we have~${\tau \big( M(\rho) \big) = M(\rho')}$, where the string~$\rho'$ is obtained by following the table below.
 \\[.3cm]
@@
  $\bigoplus_{v\in Q_0} \Z [P(v)] \cong \Z^{Q_0}$.  Thus, in the notation of Definition \ref{definition: g-vector of representation},
- if $P_0^M = \bigoplus_{v\in Q_0} \! P(v)^{\oplus a_v}$ and $P_1^M = \bigoplus_{v\in Q_0} \! P(v)^{\oplus b_v}$, 
+ if $P_0^M = \bigoplus_{v\in Q_0}P(v)^{\oplus a_v}$ and $P_1^M = \bigoplus_{v\in Q_0}P(v)^{\oplus b_v}$, 
  then
@@
   		\(
-         \b{r} = \! \begin{cases}
+         \b{r} = \begin{cases}
                    0 & \textrm{if $\rho$ starts and ends in a deep,} \\
-                   \b{e}_{t(\alpha)}   & \textrm{if $\rho$ ends in a deep and $\alpha^{-1}\rho$ is a string with $\alpha\in Q_1$,} \\
+                   \b{e}_{t(\alpha)}   & \textrm{if $\rho$ ends in a deep and $\alpha^{-1}\rho$ is a string, with $\alpha\in Q_1$,} \\
                    \b{e}_{t(\beta)}    & \textrm{if $\rho$ starts in a deep and $\rho\beta$ is a string, with $\beta\in Q_1$,} \\
-                   \b{e}_{t(\alpha)} + \b{e}_{t(\beta)} \!\!\! & \textrm{if $\alpha^{-1}\rho\beta$ is a string, with $\alpha, \beta\in Q_1$,}
+                   \b{e}_{t(\alpha)} + \b{e}_{t(\beta)}  & \textrm{if $\alpha^{-1}\rho\beta$ is a string, with $\alpha, \beta\in Q_1$,}
                   \end{cases}
@@
 Assume first that~$\rho$ attracts~$\rho'$ (Figure~\ref{fig:rho attracts rho'}), and let~$\alpha$ be as in Definition~\ref{definition: dance and attract}.
-As~$\rho'$ does not start in a deep,~$\rho''$ starts at a substring~$\alpha_1\cdots\alpha_r$, where~$\alpha_r\cdots\alpha_1\alpha^{-1}$ is the cohook at the start of~$\rho'$.
+Since~$\rho'$ does not start in a deep,~$\rho''$ starts at a substring~$\alpha_1\cdots\alpha_r$, where~$\alpha_r\cdots\alpha_1\alpha^{-1}$ is the cohook at the start of~$\rho'$.
 Let~$0\leq k\leq r$ be maximal such that~$\alpha_k\cdots\alpha_1$ is a substring (possibly a vertex if $k=0$) of~$\rho$ ending in~$u$, where~$u$ is as in Definition~\ref{definition: dance and attract}.

### 2018-07-13 firstPaper/firstPaperShort/nonKissingComplex.tex
modifs referee first paper + BC18 second paper

@@
 For a path~$\pi$ on~$Q$, define its \defn{reversed path} on~$\reversed{Q}$ by~$\reversed{(\alpha_1 \cdots \alpha_\ell)} = \alpha_\ell \cdots \alpha_1$, and extend it by linearity to a morphism~$kQ \to k\reversed{Q}$ of path algebras.
+We denote by~$\reversed{I}$ the direct image of~$I$ under this morphism.
 The \defn{reversed bound quiver} of a bound quiver~$\bar Q = (Q,I)$ is the bound quiver~$\reversed{\bar Q} \eqdef (\reversed{Q},\reversed{I})$.

### 2018-07-13 secondPaper/accordionComplexSurfaces.tex
minor modifs
generaliZing
modifs referee first paper + BC18 second paper

@@
 On the other hand, we construct a punctured, marked, oriented surface with boundary, endowed with a pair of dual dissections.
-From those geometric data, we define two simplicial complexes: the accordion complex, and the slalom complex, generalising work of A. Garver and T. McConville in the case of a disk.
+From those geometric data, we define two simplicial complexes: the accordion complex, and the slalom complex, generalizing work of A. Garver and T. McConville in the case of a disk.
 We show that all three simplicial complexes are isomorphic, and that they are pure and thin.
@@
 In most of the above cases, the algebras obtained are gentle algebras.
-It has also been shown in \cite{BaurSimoes} that any gentle algebra is obtained from a dissection of a surface, and that the module category of the algebra can be interpreted by using curves on the surface.
+It has also been shown in \cite{BaurCoelhoSimoes} that any gentle algebra is obtained from a dissection of a surface, and that the module category of the algebra can be interpreted by using curves on the surface.
 In the case where the surface is a polygon, the $\tau$-tilting theory of the algebra of a dissection has been studied in \cite{PaluPilaudPlamondon, PilaudPlamondonStella}.
@@
 Our construction has the advantage that it easily yields the two dual dissections of the surface at the same time (the dissection and dual lamination of \cite{OpperPlamondonSchroll}).
-We note that our dissections are always cellular, while those found in \cite{BaurSimoes} can be arbitrary.
+We note that our dissections are always cellular, while those found in \cite{BaurCoelhoSimoes} can be arbitrary.
 Remarkably, gentle algebras and surfaces were linked recently in \cite{HaidenKatzarkovKontsevich}, where the Fukaya category of the surface is shown to be equivalent to the bounded derived category of the associated gentle algebra.
@@
 The following definition generalises the one from \cite{MannevillePilaud-accordion} for the case where~$\bar \surface$ is a disk.
-A very similar definition appears in \cite{BaurSimoes} in a slightly different context under the name ``permissible~arc''.
+A very similar definition appears in \cite{BaurCoelhoSimoes} in a slightly different context under the name ``permissible~arc''.
 
@@
 \end{proposition}
+
 \begin{proof}
@@
 \item for any pair of dual cellular dissections~$\dissection, \dissection\dual$ of an oriented surface, the non-crossing complex~$\NCC$ is isomorphic to the non-kissing complex~$\NKC[\bar Q_{\dissection, \dissection\dual}]$.
-
 \end{itemize}

### 2018-07-13 firstPaper/firstPaperLong/nonKissingComplex.tex
problems compilation

--- 2018-07-13 firstPaper/firstPaperLong/nonKissingComplex.tex
@@
     \\ \hline
-    \multiLinesBox{(left) mutation of support \\ $\tau$-tilting objects (Thm.~\ref{thm: mutation of stautilts}~\cite{AdachiIyamaReiten})} &
+    \multiLinesBox{(left) mutation of support \\ $\tau$-tilting objects (Thm.~\ref{thm:mutationstautilts}~\cite{AdachiIyamaReiten})} &
     \multiLinesBox{(increasing) flip \\ (Prop.~\ref{prop:flip} and Def.~\ref{def:flip} \& \ref{def:increasingFlip})} &
@@
 %    \\ \hline
-%    \multiLinesBox{(left) mutation of support \\ $\tau$-tilting objects (Thm.~\ref{thm: mutation of stautilts}~\cite{AdachiIyamaReiten})} &
+%    \multiLinesBox{(left) mutation of support \\ $\tau$-tilting objects (Thm.~\ref{thm:mutationstautilts}~\cite{AdachiIyamaReiten})} &
 %    \multiLinesBox{(increasing) flip \\ (Prop.~\ref{prop:flip} and Def.~\ref{def:flip} \& \ref{def:increasingFlip})} &
@@
 
-\begin{theorem}[\cite{AdachiIyamaReiten}]\label{thm: mutation of stautilts}
+\begin{theorem}[\cite{AdachiIyamaReiten}]\label{thm:mutationstautilts}
 Let~$N = \bigoplus_{i \in [n]} N_i$ be a support~$\tau$-tilting object, where each~$N_i$ is either an indecomposable representation or a shifted indecomposable projective representation.
@@
 
-\item If~$\xi=\nu$. By Lemma~\ref{lemma: xi equals nu} below and the fact that~$\xi$ is on top of~$\rho$, we have that~$\rho$ reaches for~$\rho'$.
+\item If~$\xi=\nu$. By Lemma~\ref{lem:xiEqualsNu} below and the fact that~$\xi$ is on top of~$\rho$, we have that~$\rho$ reaches for~$\rho'$.
 
@@
 Moreover, there is some~$0\leq i\leq r$ such that~$\nu=\alpha_i\cdots\alpha_1\alpha^{-1}\xi$.
-The proof of Lemma~\ref{lemma: xi equals nu} shows that~$\rho'$ is of the form~$\xi\beta^{-1}\sigma'$.
+The proof of Lemma~\ref{lem:xiEqualsNu} shows that~$\rho'$ is of the form~$\xi\beta^{-1}\sigma'$.
 Since~$\nu$ is on top of~$\rho$, we have~$\rho=\rho_1\alpha^{-1}\xi(\beta\rho_2)$ for some substrings~$\rho_1,\rho_2$ and some arrow~$\beta$.
@@
 
-\begin{lemma}\label{lemma: xi equals nu}
+\begin{lemma}\label{lem:xiEqualsNu}
 Let~$\rho'$ be a string for~$A$ and~$\rho''$ be the string obtained when computing~$\tau M(\rho')$ as in Theorem~\ref{theorem: tau for strings}.
@@
 Observe that this straight walk is always the minimal marked walk of~$F_\alpha$ for the order~$\prec_\alpha$, since it always agrees with the direction of~$\alpha$.
-On the other hand, Proposition~\ref{prop: nk facets are finite}, below, shows that we can consider the maximal marked walk of~$F_\alpha$ for the order~$\prec_\alpha$.
+On the other hand, Proposition~\ref{prop:nkFacetsAreFinite}, below, shows that we can consider the maximal marked walk of~$F_\alpha$ for the order~$\prec_\alpha$.
 Intuitively, it is the most countercurrent walk passing through~$\alpha$ with respect to the direction of~$\alpha$.
-\begin{lemma}\label{lemma: distinguished arrows exists}
+
+\begin{lemma}
+\label{lem:distArrowExist}
 Let~$F$ be a finite face of~$\NKC$, let~$\omega$ be a walk in~$F$, and let~$\alpha$ be an arrow on~$\omega$.
@@
 
-\begin{proposition}\label{prop: nk facets are finite}
+\begin{proposition}\label{prop:nkFacetsAreFinite}
 The faces of the non-kissing complex have finite cardinality.
@@
 \begin{proof}
-By Lemma~\ref{lemma: distinguished arrows exists}, the cardinality of any finite non-kissing face of~$\NKC$ is bounded by~$|Q_1\blossom|$.
+By Lemma~\ref{lem:distArrowExist}, the cardinality of any finite non-kissing face of~$\NKC$ is bounded by~$|Q_1\blossom|$.
 Thus, any collection of~$|Q_1\blossom|+1$ walks contains a kiss and all non-kissing faces are finite.
@@
 \begin{proof}
-In view of Lemma~\ref{lemma: distinguished arrows exists}, it remains to prove that each walk of~$F$ contains at most one distinguished arrow in each direction.
+In view of Lemma~\ref{lem:distArrowExist}, it remains to prove that each walk of~$F$ contains at most one distinguished arrow in each direction.
 Assume that a walk~$\omega$ has two distinguished arrows~$\alpha, \beta$ pointing in the same direction.
@@
 	\centerline{\includegraphics[scale=1]{pure}}
-	\caption{A schematic illustration of the proof of Proposition~\ref{prop:distinguishedArrows}:~$\omega$ cannot have two distinguished arrows~$\alpha, \beta$ in the same direction (left), and for each arrow~$\alpha$ on~$\omega$, there is a distinguished arrow on~$\omega$ in the direction of~$\alpha$ (right).
+	\caption{A schematic illustration of the proofs of Lemma~\ref{lem:distArrowExist} and Proposition~\ref{prop:distinguishedArrows}: for each arrow~$\alpha$ on~$\omega$, there is a distinguished arrow on~$\omega$ in the direction of~$\alpha$ (left), and~$\omega$ cannot have two distinguished arrows~$\alpha, \beta$ in the same direction (right).
 See the proof of Proposition~\ref{prop:distinguishedArrows} for a detailed description.}
@@
 
-\begin{lemma}\label{lem: attract or dance vs kiss}
+\begin{lemma}\label{lem:attractDanceKiss}
 Let~$\sigma$ and~$\sigma'$ be two strings for the gentle bound quiver~$\bar Q$.
@@
 
-\enlargethispage{.5cm}
 We conclude this section with the observation which motivated this paper.
@@
 \begin{proof}
-The theorem is a direct consequence of Lemma~\ref{lem: attract or dance vs kiss}, except for the fact that increasing flips correspond to left mutations.
+The theorem is a direct consequence of Lemma~\ref{lem:attractDanceKiss}, except for the fact that increasing flips correspond to left mutations.
 We use the notation of Proposition~\ref{prop:flip} and Figure~\ref{fig:flip}: let $F$ and~$F'$ be two adjacent facets such that the flip of~$F$ to~$F'$ is increasing, let $\omega$ and~$\omega'$ are the walks such that~$F \ssm \{\omega\} = F' \ssm \{\omega'\}$, let~$\{\alpha, \beta\} = \distinguishedArrows{\omega}{F}$ and~$\{\alpha', \beta'\} = \distinguishedArrows{\omega'}{F'}$, let~$\xi = \distinguishedString{\omega}{F} = \distinguishedString{\omega'}{F'}$, and let~$\mu = \distinguishedWalk{\alpha'}{F} = \distinguishedWalk{\beta}{F'}$ and~$\nu = \distinguishedWalk{\beta'}{F} = \distinguishedWalk{\alpha}{F'}$.

### 2018-07-13 firstPaper/firstPaperShort/nonKissingComplex.tex
problems compilation

--- 2018-07-13 firstPaper/firstPaperShort/nonKissingComplex.tex
@@
 Observe that this straight walk is always the minimal marked walk of~$F_\alpha$ for the order~$\prec_\alpha$, since it always agrees with the direction of~$\alpha$.
-On the other hand, Proposition~\ref{prop: nk facets are finite}, below, shows that we can consider the maximal marked walk of~$F_\alpha$ for the order~$\prec_\alpha$.
+On the other hand, Proposition~\ref{prop:nkFacetsAreFinite}, below, shows that we can consider the maximal marked walk of~$F_\alpha$ for the order~$\prec_\alpha$.
 Intuitively, it is the most countercurrent walk passing through~$\alpha$ with respect to the direction of~$\alpha$.
 
-\begin{lemma}\label{lemma: distinguished arrows exists}
+\begin{lemma}\label{lem:distArrowExist}
 Let~$F$ be a finite face of~$\NKC$, let~$\omega$ be a walk in~$F$, and let~$\alpha$ be an arrow on~$\omega$.
@@
 \begin{proof}
-By Lemma~\ref{lemma: distinguished arrows exists}, the cardinality of any finite non-kissing face is bounded by~$|Q_1\blossom|$.
+By Lemma~\ref{lem:distArrowExist}, the cardinality of any finite non-kissing face is bounded by~$|Q_1\blossom|$.
 Thus, any collection of~$|Q_1\blossom|+1$ walks contains a kiss and all non-kissing faces are finite.
@@
 	\vspace{.3cm}
-	\caption{A biclosed set of strings~$S \in \Bicl{\bar Q\}$ (middle), where~$\bar Q$ is the bound quiver of~\fref{fig:exmBlossomingQuiver}, and its images~$\projDown(S)$ (left) and~$\projUp(S)$ (right) by the down and up projections of Definition~\ref{def:downUpProjections}.
+	\caption{A biclosed set of strings~$S \in \Bicl{\bar Q}$ (middle), where~$\bar Q$ is the bound quiver of~\fref{fig:exmBlossomingQuiver}, and its images~$\projDown(S)$ (left) and~$\projUp(S)$ (right) by the down and up projections of Definition~\ref{def:downUpProjections}.
 For space reasons, $\projUp(S)$ is only represented partially: the remaining strings are obtained by adding independently the two dotted arrows to all strings containing their left endpoint.}

### 2018-07-13 firstPaper/firstPaperLong/nonKissingComplex.tex
update Fig 21 and references

@@
 If~$\lambda \ne \omega$, then~$\lambda$ either kisses~$\mu$ or contradicts the minimality of~$\mu$ among the walks~$\set{\nu \in F_\alpha}{\omega \prec_\alpha \nu}$.
-See \fref{fig:pure}\,(right) for an illustration.
+See \fref{fig:pure}\,(left) for an illustration.
 We conclude that~$\lambda = \omega$ has a distinguished arrow~$\beta$ in the direction of~$\alpha$.
@@
 Let~$\mu \eqdef \omega[\,\cdot\,, v] \, \nu[v, \cdot\,]$ be the walk connecting~$s(\omega)$ to~$t(\nu)$ via~$v$, using the prefix of~$\omega$ ending at~$v$ followed by the suffix of~$\nu$ starting at~$v$.
-All these notations are illustrated in \fref{fig:pure}\,(left).
+All these notations are illustrated in \fref{fig:pure}\,(right).
 We claim that~$\mu$ is non-kissing with any walk of~$F$, contradicting the maximality~of~$F$.
@@
 %Note that the maximal common substring~$\tau$ of~$\omega$ and~$\lambda$ containing~$v$ is non-empty (otherwise~$\lambda$ would kiss~$\omega$ or~$\nu$) and contains strictly~$\sigma$ (otherwise~$\lambda$ would kiss~$\nu$).
-We now distinguish two cases (see \fref{fig:pure}\,(left)):
+We now distinguish two cases (see \fref{fig:pure}\,(right)):
 \begin{enumerate}[(i)]

### 2018-07-13 firstPaper/firstPaperLong/nonKissingComplex.tex
horizontal spacing

@@
 
+\enlargethispage{-.8cm}
 The non-kissing complex is a simplicial complex of pairwise non-kissing paths in a fixed shape of a grid.
@@
 
+\bigskip
 \begin{theorem*}
@@
 
+\newpage
+\enlargethispage{-.3cm}
 In short, to any walk in $\bar Q \blossom$ corresponds a representation of $\bar Q$, and this correspondence takes non-kissing walks to $\tau$-compatible representations.
@@
 \begin{example}
-\fref{fig:exmFacet}~(left) gives examples of kissing and non-kissing walks.
+\fref{fig:exmFacet}~(left) illustrates kissing and non-kissing walks.
 %
@@
 We obtained a contradiction in all cases, which shows that~$\mu$ is non-kissing with any other walk~of~$F$.
-
+%
 \begin{figure}[t]
@@
 \label{coro:pure}
-The non-kissing complex~$\NKC$ is pure of dimension $|Q_0| + \Delta = 3|Q_0|-|Q_1|$. The reduced non-kissing complex~$\RNKC$ is pure of dimension~$|Q_0|$.
+The non-kissing complex~$\NKC$ is pure and its dimension is ${|Q_0| + \Delta = 3|Q_0|-|Q_1|}$.
+The reduced non-kissing complex~$\RNKC$ is pure and its dimension is $|Q_0|$.
 \end{corollary}
@@
 
+\enlargethispage{.3cm}
 Since each bending walk in a non-kissing facet of~$\RNKC$ has two distinguished arrows, we can consider the substring they surround.
@@
 
-\begin{figure}[b]
+\begin{proof}
+%
+\begin{figure}[ht]
 	\capstart
@@
 \end{figure}
-
-\begin{proof}
+%
 Let~$v$ (resp.~$w$) be the endpoint of~$\sigma$ incident to~$\alpha$ and~$\alpha'$ (resp.~to~$\beta$ and~$\beta'$).
@@
 
-\begin{figure}[h]
+\begin{figure}[t]
 	\capstart
@@
 If the common substring~$\sigma$ of~$\omega$ and~$\omega'$ is on top of~$\omega$ and at the bottom of~$\omega'$, then we say that the flip~$F \to F'$ is \defn{increasing} and that the common substring~$\sigma$ is an \defn{ascent} of~$F$ and a \defn{descent} of~$F'$.
-We denote by ${\ascents(F) \subseteq \strings^\pm(\bar Q)}$ and $\descents(F) \subseteq \strings^\pm(\bar Q)$ the sets of ascents and descents of~$F$ respectively.
+We let~${\ascents(F) \subseteq \strings^\pm(\bar Q)}$ and $\descents(F) \subseteq \strings^\pm(\bar Q)$ denote the sets of ascents and descents of~$F$ respectively.
 Otherwise,~$\sigma$ is a descent of~$F$ and an ascent of~$F'$ and the flip is called \defn{decreasing}.
@@
 
+\enlargethispage{-.3cm}
 In this section, we start the dictionary of Table~\ref{table:dictionary} between algebraic notions on the support $\tau$-tilting complex of a gentle algebra and the combinatorial notions on the non-kissing complex of its blossoming quiver.
@@
 
-\begin{figure}[t]
+\begin{figure}[p]
 \[
@@
     \caption{The walks~$\omega(\sigma)$ and~$\omega(\sigma')$ when~$\sigma$ reaches for~$\sigma'$: case (a).}
-    \vspace{.1cm}
+    \vspace{.8cm}
     \label{fig: dance case a}
@@
     \caption{The walks~$\omega(\sigma)$ and~$\omega(\sigma')$ when~$\sigma$ reaches for~$\sigma'$: case (b).}
-    \vspace{.1cm}
+    \vspace{.8cm}
     \label{fig: dance case b}
@@
 
+\enlargethispage{-.4cm}
 The $\b{g}$- and $\b{c}$-vectors have been designed so that the following statement holds, as illustrated in \fref{fig:gcvectors}.
@@
 %We then construct a polytopal realization of the $\b{g}$-vector fan~$\gvectorFan$.
+\enlargethispage{-.4cm}
 We still consider a gentle bound quiver~$\bar Q$ with finite non-kissing complex~$\RNKC$.

### 2018-07-13 firstPaper/firstPaperLong/nonKissingComplex.tex

@@
 \enlargethispage{-.8cm}
-The non-kissing complex is a simplicial complex of pairwise non-kissing paths in a fixed shape of a grid.
+The non-kissing complex is the simplicial complex of a compatibility relation, called non-kissing, on paths in a fixed shape of a grid.
 It was introduced by T.~K.~Petersen, P.~Pylyavskyy and D.~Speyer in~\cite{PetersenPylyavskyySpeyer} for a staircase shape, studied by F.~Santos, C.~Stump and V.~Welker~\cite{SantosStumpWelker} for rectangular shapes, and extended by T.~McConville in~\cite{McConville} for arbitrary shapes.

### 2018-07-13 firstPaper/firstPaperLong/nonKissingComplex.tex
misplaced correction

@@
 \end{enumerate}
-The algebra~$kQ/I$ associated to a gentle bound quiver~$\bar Q$ is called a \defn{string algebra}.
+The algebra~$kQ/I$ associated to a string bound quiver~$\bar Q$ is called a \defn{string algebra}.
 \end{definition}
@@
 \end{enumerate}
-The algebra~$kQ/I$ is called a \defn{gentle algebra}.
+The algebra~$kQ/I$ associated to a gentle bound quiver~$\bar Q$ is called a \defn{gentle algebra}.
 \end{definition}

### 2018-07-13 firstPaper/firstPaperShort/nonKissingComplex.tex
misplaced correction

@@
 \end{itemize}
-The algebra~$kQ/I$ associated to a gentle bound quiver~$\bar Q$ is called a \defn{string algebra}.
+The algebra~$kQ/I$ associated to a string bound quiver~$\bar Q$ is called a \defn{string algebra}.
 \end{definition}
@@
 \end{itemize}
-The algebra~$kQ/I$ is called a \defn{gentle algebra}.
+The algebra~$kQ/I$ associated to a gentle bound quiver~$\bar Q$ is called a \defn{gentle algebra}.
 \end{definition}

### 2018-07-13 firstPaper/corrections/replyToReferee.txt
all overfullboxes
modifs referee first paper + BC18 second paper
some more corrections

@@
 
-  Reply: page 43: We have added a reference to the definition.
+  Reply: 
+page 1: Modified to: The non-kissing complex is the simplicial complex of a compatibility relation, called non-kissing, on paths in a fixed shape of a grid.
+page 43: We have added a reference to the definition.
 
@@
 
-  Reply:
+  Reply: We have added a definition.
 
@@
 
-  Reply: Done
+  Reply: Done.
 
@@
 
-  Reply: Yes. This has now been made axplicit and we have added the definition of decreasing.
+  Reply: Yes. This has now been made explicit and we have added the definition of decreasing.
 
@@
 
-  Reply: Fixed.
+  Reply: Fixed. We have checked that there are no text in the margin besides pictures and tables.
 
@@
 
-  Reply:
+  Reply: Indeed.
 

### 2018-07-13 firstPaper/firstPaperLong/nonKissingComplex.tex
some more corrections

@@
 In other words, when all strings of~$\bar Q$ are distinguishable, the bijections~$\omega_\bottom$ and~$\sigma_\bottom$ where already considered in Lemma~\ref{lem:bijections-STTC-NKC}.
-As illustrated in \fref{fig:exmBijectionStringsWalks2}\,(right), the bijections of Lemma~\ref{lem:bijections-STTC-NKC} and Definition~\ref{def:bijectionWalksDistinguishableStrings} no longer coincide in general when not all strings are distinguishable.
+As illustrated in \fref{fig:exmBijectionStringsWalks2}\,(bottom), the bijections of Lemma~\ref{lem:bijections-STTC-NKC} and Definition~\ref{def:bijectionWalksDistinguishableStrings} no longer coincide in general when not all strings are distinguishable.
 \end{remark}

### 2018-07-13 firstPaper/firstPaperLong/nonKissingComplex.tex
pdf differences

@@
 
-\enlargethispage{-.3cm}
 In this section, we first fix our notations (\ref{subsec:pathAlgebra}) on quivers, path algebras, their representations, and their support $\tau$-tilting complexes (\ref{subsec:tautilting}).

### 2018-07-13 firstPaper/firstPaperLong/nonKissingComplex.tex
minor changes

@@
 \label{lem:exmBiclosedJI}
-Let~$\sigma \in \strings^\pm(\bar Q)$ be a distinguishable string. Then the biclosed set~$\closure{\Sigma_\bottom(\sigma)}$ is join-irreducible in~$\Bicl{\bar Q}$.
+For any distinguishable string~$\sigma \! \in \! \strings^\pm(\bar Q)$ the biclosed set~$\closure{\Sigma_\bottom(\sigma)}$ is join-irreducible in~$\Bicl{\bar Q}$.
 \end{lemma}
@@
 \begin{enumerate}[(i)]
-\item $\Sigma$ is pairwise non-friendly.
+\item the set~$\Sigma$ is pairwise non-friendly.
 \item the set~$\ji(\Sigma) \eqdef \set{\ji(\sigma)}{\sigma \in \Sigma}$ is the canonical join-representation of an element in~$\NKL$.
-\item $\Sigma$ is the descent set of a non-kissing facet~$F \in \NKC$.
+\item the set~$\Sigma$ is the descent set of a non-kissing facet~$F \in \NKC$.
 \end{enumerate}

### 2018-07-13 firstPaper/firstPaperShort/nonKissingComplex.tex
minor changes

@@
     \centerline{
+    \renewcommand{\arraystretch}{1.2}
     \begin{tabular}{|c|c|c|}
@@
     \end{tabular}
+	\renewcommand{\arraystretch}{1}
     }
@@
 The criterion of Proposition \ref{proposition: attract or dance and tau compatibility} for $\tau$-compatibility between string modules can be compared with a similar criterion obtained recently in \cite{CanakciPauksztelloSchroll} for the existence of extensions between two string modules.
-The similarity between the two criteria is explained by the Auslander--Reiten formula asserting that $\Ext{}^1(N,M)$ is a quotient of the space $\Hom{}(M,\tau N)$ (see \cite[Theorem IV.2.13]{AssemSimsonSkowronski}).
+The similarity between the two criteria is explained by the Auslander--Reiten formula asserting that $\Ext{}^1(N,M)$ is a quotient of the space $\Hom{}(M,\tau N)$ (see \cite[Thm.~IV.2.13]{AssemSimsonSkowronski}).
 \end{remark}
@@
 %In the opposite situation, the flip is \defn{decreasing} and~$\sigma$ is a descent of~$F$ and an ascent of~$F'$.
+Otherwise,~$\sigma$ is a descent of~$F$ and an ascent of~$F'$ and the flip is called \defn{decreasing}.
 \end{definition}

### 2018-07-13 firstPaper/firstPaperLong/nonKissingComplex.tex
dim Hom top/bot added

--- 2018-07-13 firstPaper/firstPaperLong/nonKissingComplex.tex
@@
 Let~$\rho$ and~$\rho'$ be two strings for a string algebra~$A$.
-Then the dimension of the $k$-vector space~$\Hom{A} \big( M(\rho), M(\rho') \big)$ is equal to the number of pairs~$(\sigma, \sigma')$, where~$\sigma$ and~$\sigma'$ are substrings of~$\rho$ and~$\rho'$, respectively, such that there is an equality of strings~$\sigma' = \sigma^{\pm 1}$.
+Then the dimension of the $k$-vector space~$\Hom{A} \big( M(\rho), M(\rho') \big)$ is equal to the number of pairs~$(\sigma, \sigma')$, where~$\sigma$ and~$\sigma'$ are substrings of~$\rho$ and~$\rho'$, respectively, such that~$\sigma$ is on top of~$\rho$,~$\sigma'$ is at the bottom of~$\rho'$ and there is an equality of strings~$\sigma' = \sigma^{\pm 1}$.
 

### 2018-07-13 firstPaper/firstPaperLong/nonKissingComplex.tex
aknowledgments

@@
 %\renewcommand\labelitemi{$\diamond$} % redefine itemize default symbol
-\DeclareRobustCommand{\exmAn}{\overrightarrow{A_n}} % path
 
@@
 This work was carried out while the first author was visiting Paris 7. He would like to thank his colleagues there, and especially \mbox{P.~Le Meur}, for a stimulating atmosphere.
+Finally, we thank an anonymous referee for useful suggestions on the presentation of this work.
 
@@
 	\centerline{\includegraphics[scale=1.5]{exmBijectionAssociahedron}}
-	\caption{An oriented path~$\exmAn$ is simultaneously a triangulation and a grid bound quiver (top).
-A facet of the reduced non-kissing complex~$\RNKC[\exmAn]$ can be seen as a triangulation or as a collection of non-kissing south-east paths (bottom).}
+	\caption{An oriented path~$\bar Q$ is simultaneously a triangulation and a grid bound quiver (top).
+A facet of the reduced non-kissing complex~$\RNKC$ can be seen as a triangulation or as a collection of non-kissing south-east paths (bottom).}
 	\label{fig:exmBijectionAssociahedron}
@@
 Oriented flip graphs were studied carefully in~\cite{GarverMcConville, MannevillePilaud-accordion, McConville} for the dissection and grid bound quivers introduced in Section~\ref{subsec:dissectionGridQuivers}.
-Note that when the quiver is an oriented path~$\exmAn$, a flip in a facet of the non-kissing complex~$\NKC[\exmAn]$ corresponds to the classical flip of a diagonal in the corresponding triangulation (see \fref{fig:exmBijectionAssociahedron}).
+Note that when the quiver is an oriented path~$\bar Q$, a flip in a facet of the non-kissing complex~$\NKC$ corresponds to the classical flip of a diagonal in the corresponding triangulation (see \fref{fig:exmBijectionAssociahedron}).
 Moreover, the flip is increasing if and only if the slope of the diagonal increases along the flip.

### 2018-07-13 secondPaper/accordionComplexSurfaces.tex

@@
 We note that our dissections are always cellular, while those found in \cite{BaurCoelhoSimoes} can be arbitrary.
-Remarkably, gentle algebras and surfaces were linked recently in \cite{HaidenKatzarkovKontsevich}, where the Fukaya category of the surface is shown to be equivalent to the bounded derived category of the associated gentle algebra.
+Remarkably, gentle algebras and surfaces were linked recently in \cite{HaidenKatzarkovKontsevich, LekiliPolishchuk}, where the Fukaya category of the surface is shown to be equivalent to the bounded derived category of the associated gentle algebra.
 

### 2018-07-13 firstPaper/firstPaperLong/nonKissingComplex.tex
mathbb{S}
delete exm 3.36
Exm 3.43

@@
 \newcommand{\cC}{\mathcal{C}} % collection
-\newcommand{\cS}{\mathcal{S}} % ground set
+\newcommand{\cS}{\mathbb{S}} % ground set
 \newcommand{\uR}{\underline{R}} % underline set
@@
 
-\begin{example}
-The map~$\omega$ is illustrated on \fref{fig:exmSurjection}.
-\end{example}
+%\begin{example}
+%The map~$\omega$ is illustrated on \fref{fig:exmSurjection}.
+%\end{example}
 
@@
 \begin{example}
-\fref{fig:exmLatticeQuotient} shows the complete map from the biclosed sets of~$\Bicl{\bar Q}$ to the non-kissing facets of~$\NKC$ for a specific gentle bound quiver.
-\end{example}
-
+\fref{fig:exmLatticeQuotient} shows the complete map~$\eta$ from the biclosed sets of~$\Bicl{\bar Q}$ to the non-kissing facets of~$\NKC$ for a specific gentle bound quiver.
+Instead of drawing the image~$\eta(S)$ for each biclosed set~$S \in \Bicl{\bar Q}$, we have grouped in blue boxes the fibers of~$\eta$.
+\end{example}
+
+\enlargethispage{.2cm}
 The following result recasts Corollaries~\ref{coro:surjectionNonKissingWalks} and~\ref{coro:eta} in terms of the map~$\eta$ of Definition~\ref{def:eta}.

### 2018-07-13 firstPaper/firstPaperShort/nonKissingComplex.tex
aknowledgments
Exm 3.43

@@
 \fref{fig:exmLatticeQuotient} shows the complete map from the biclosed sets of~$\Bicl{\bar Q}$ to the non-kissing facets of~$\NKC$ for a specific gentle bound quiver.
-\end{example}
-
+Instead of drawing the image~$\eta(S)$ for each biclosed set~$S \in \Bicl{\bar Q}$, we have grouped in blue boxes the fibers of~$\eta$.
+\end{example}
+
+\enlargethispage{.2cm}
 The following result recasts Corollaries~\ref{coro:surjectionNonKissingWalks} and~\ref{coro:eta} in terms of the map~$\eta$ of Definition~\ref{def:eta}.

### 2018-07-13 firstPaper/corrections/replyToReferee.txt
delete exm 3.36
Exm 3.43
answer referee
Very minor change

@@
 
-  Reply:
+  Reply: We changed it with $\mathbb{S}$ which seems more different.
 
@@
 
-  Reply:
+  Reply: We have deleted this example.
 
@@
 
-  Reply:
+  Reply: We have made the sentence of Example 3.44 more precise.
 
@@
 
-  Reply: While we agree that the notation set is non-conventional, we believe
+  Reply: While we agree that the notation set is unconventional, we believe
          that it fits well with our chosen terminology.  We thus respectfully 

### 2018-09-07 firstPaper/firstPaperShort/nonKissingComplex.tex
update figure

@@
 
-\enlargethispage{.2cm}
+\enlargethispage{.8cm}
 Throughout the paper, we will illustrate our results with two specific families of gentle bound quivers:
@@
 
+\enlargethispage{.2cm}
 We now define and study first elementary properties of the non-kissing complex of a quiver.
@@
 \end{enumerate}
-We obtained a contradiction in all cases, which shows that~$\mu$ is non-kissing with any other walk~of~$F$.
-
+We get a contradiction in all cases, therefore~$\mu$ is non-kissing with any other walk~of~$F$.
+%
 \begin{figure}[t]
@@
 
+\enlargethispage{.3cm}
 Using material from Part~\ref{part:lattice}, we will characterize distinguishable strings of~$\bar Q$ in Section~\ref{subsec:distinguishableStrings}.
-
-\medskip
 We close this section by a technical lemma about distinguished arrows, which will be helpful to understand the different possible situations in Proposition~\ref{prop:flip}.
@@
 Assume first that $r$ and $s$ are positive.
-Then $\tau M(\sigma')$ is given by the string $\sigma''=\alpha_{r-1} \cdots \alpha_1 \alpha^{-1} \sigma' \beta \beta_1^{-1} \cdots \beta_{s-1}^{-1}$.
+Then $\tau M(\sigma')$ is given by the string $\sigma''=\alpha_{r-1} \cdots \alpha_1 \alpha^{-1} \sigma'$ $\beta \beta_1^{-1} \cdots \beta_{s-1}^{-1}$.
 Thus, $\xi$ is at the bottom of $\sigma''$ and $\Hom{A} \big( M(\sigma), \tau M(\sigma') \big) \neq 0$.

### 2018-09-07 secondPaper/accordionComplexSurfaces.tex
update figure

--- 2018-07-13 secondPaper/accordionComplexSurfaces.tex
@@
 Our construction has the advantage that it easily yields the two dual dissections of the surface at the same time (the dissection and dual lamination of \cite{OpperPlamondonSchroll}).
-We note that our dissections are always cellular, while those found in \cite{BaurCoelhoSimoes} can be arbitrary.
-Remarkably, gentle algebras and surfaces were linked recently in \cite{HaidenKatzarkovKontsevich}, where the Fukaya category of the surface is shown to be equivalent to the bounded derived category of the associated gentle algebra.
+Note that our dissections are always cellular, while those in \cite{BaurCoelhoSimoes} can be arbitrary.
+Remarkably, gentle algebras and surfaces were linked recently in \cite{HaidenKatzarkovKontsevich, LekiliPolishchuk}, where the Fukaya category of the surface is shown to be equivalent to the bounded derived category of the associated gentle~algebra.
 
@@
 
-The following definition generalises the one from \cite{MannevillePilaud-accordion} for the case where~$\bar \surface$ is a disk.
-A very similar definition appears in \cite{BaurCoelhoSimoes} in a slightly different context under the name ``permissible~arc''.
+The following definition generalises the one of \cite{MannevillePilaud-accordion} for the case where~$\bar \surface$ is a disk.
+A~very similar definition appears in \cite{BaurCoelhoSimoes} in a slightly different context under the \mbox{name ``permissible~arc''}.
 

### 2018-09-07 firstPaper/firstPaperLong/nonKissingComplex.tex
minor modif Proposition 3.68

@@
 
-Conversely, for a non-self-kissing walk~$\omega \in \NKWalks^\pm(\bar Q)$ not in the peak facet, the inclusion minimal string in the set~$\set{\sigma \in \Sigma_\bottom(\omega)}{\closure{\Sigma_\bottom(\omega)} = \closure{\Sigma_\bottom(\sigma)}}$ is denoted by~$\sigma_\bottom(\omega)$.
+Conversely, for a bending non-self-kissing walk~$\omega \in \NKWalks^\pm(\bar Q)$ not in the peak facet, the inclusion minimal string in the set~$\set{\sigma \in \Sigma_\bottom(\omega)}{\closure{\Sigma_\bottom(\omega)} = \closure{\Sigma_\bottom(\sigma)}}$ is denoted by~$\sigma_\bottom(\omega)$.
 \end{definition}
@@
 \label{prop:bijectionDistinguishableStringsWalks}
-The maps~$\omega_\bottom$ and~$\sigma_\bottom$ are inverse bijections between the distinguishable strings of~$\bar Q$ and the bending walks of~$\walks^\pm(\bar Q)$ not in the peak facet~$F_\peak$.
+The maps~$\omega_\bottom$ and~$\sigma_\bottom$ are inverse bijections between the distinguishable strings of~$\bar Q$ and the bending non-self-kissing walks of~$\NKWalks^\pm(\bar Q)$ not in the peak facet~$F_\peak$.
 \end{proposition}

### 2018-09-07 firstPaper/firstPaperShort/nonKissingComplex.tex
minor modif Proposition 3.68

@@
 
-Conversely, for a non-self-kissing walk~$\omega \in \NKWalks^\pm(\bar Q)$ not in the peak facet, we denote by~$\sigma_\bottom(\omega)$ the inclusion minimal string in~$\set{\sigma \in \Sigma_\bottom(\omega)}{\closure{\Sigma_\bottom(\omega)} = \closure{\Sigma_\bottom(\sigma)}}$.
+Conversely, for a bending non-self-kissing walk~$\omega \in \NKWalks^\pm(\bar Q)$ not in the peak facet, we denote by~$\sigma_\bottom(\omega)$ the inclusion minimal string in~$\set{\sigma \in \Sigma_\bottom(\omega)}{\closure{\Sigma_\bottom(\omega)} = \closure{\Sigma_\bottom(\sigma)}}$.
 \end{definition}

### 2018-09-24 secondPaper/accordionComplexSurfaces.tex
minor mistakes

@@
 \label{def:slalom}
-A \defn{$\dissection\dual$-slalom} is a $B$-curve~$\alpha$ of~$\bar\surface$ such that, whenever~$\alpha$ crosses an edge~$a$ of~$\dissection$ contained in two faces~$f,g$ of~$\dissection$, the marked points~$f\dual$ and~$g\dual$ lie on opposite sides of~$\alpha$ in the union of~$f$ and~$g$ glued along~$a$.
-Here, we consider that~$f\dual$ lies on the right (resp.~left) of~$\alpha$ when~$\alpha$ circles clockwise (resp.~counterclockwise) around~$f\dual$.
+A \defn{$\dissection\dual$-slalom} is a $B$-curve~$\alpha$ of~$\bar\surface$ such that, whenever~$\alpha$ crosses an edge~$a\dual$ of~$\dissection\dual$ contained in two faces~$f\dual, g\dual$ of~$\dissection\dual$, the marked points~$f$ and~$g$ lie on opposite sides of~$\alpha$ in the union of~$f\dual$ and~$g\dual$ glued along~$a\dual$.
+Here, we consider that~$f$ lies on the right (resp.~left) of~$\alpha$ when~$\alpha$ circles clockwise (resp.~counterclockwise) around~$f$.
 By convention, we also consider that the punctures of~$V$ are $\dissection\dual$-slaloms that are considered external.
-If we were working on the universal cover of the surface, the~$\dissection$-accordion associated to a puncture would be the infinite line crossing all (infinitely many) arcs attached to the puncture.
+If we were working on the universal cover of the surface, the~$\dissection\dual$-slalom associated to a puncture would be an infinite line never crossing any arc of~$\dissection\dual$.
 \end{definition}

### 2018-09-24 thridPaper/draft/typeConeAssociahedra.tex
third paper

\documentclass{amsart}

\usepackage[T1]{fontenc}
\usepackage{enumerate, amsmath, amsfonts, amssymb, amsthm, mathrsfs, wasysym, graphics, graphicx, xcolor, url, hyperref, hypcap, xargs, multicol, pdflscape, multirow, hvfloat, array, ae, aecompl, pifont, mathtools, a4wide, float, blkarray}
\usepackage[noabbrev,capitalise]{cleveref}
\usepackage{marginnote}
\hypersetup{colorlinks=true, citecolor=darkblue, linkcolor=darkblue}
\usepackage[all]{xy}
\usepackage{tikz}
\usepackage{tkz-graph}
\usetikzlibrary{trees, decorations, decorations.markings, shapes, arrows, matrix, calc, fit, intersections, patterns, angles}
\graphicspath{{figures/}}
\makeatletter\def\input@path{{figures/}}\makeatother
\usepackage{caption}
\captionsetup{width=\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% theorems
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem*{theorem*}{Theorem}%[section]

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{question}[theorem]{Question}
\newtheorem{notation}[theorem]{Notation}
\newtheorem{assumption}[theorem]{Assumption}
\newtheorem{convention}[theorem]{Convention}

\crefname{equation}{Equation}{Equations}

% math special letters
\newcommand{\R}{\mathbb{R}} % reals
\newcommand{\N}{\mathbb{N}} % naturals
\newcommand{\Z}{\mathbb{Z}} % integers
\newcommand{\C}{\mathbb{C}} % complex
\newcommand{\I}{\mathbb{I}} % set of integers
\newcommand{\HH}{\mathbb{H}} % hyperplane
\newcommand{\K}{k} % field
\newcommand{\fA}{\mathfrak{A}} % alternating group
\newcommand{\fS}{\mathfrak{S}} % symmetric group
\newcommand{\cA}{\mathcal{A}} % algebra
\newcommand{\cC}{\mathcal{C}} % collection
\newcommand{\cS}{\mathcal{S}} % ground set
\newcommand{\uR}{\underline{R}} % underline set
\newcommand{\uS}{\underline{S}} % underline set
\newcommand{\uT}{\underline{T}} % underline set
\newcommand{\oS}{\overline{S}} % overline set
\newcommand{\ucS}{\underline{\cS}} % underline ground set
\renewcommand{\b}[1]{{\boldsymbol{#1}}} % bold letters
\newcommand{\h}{\widehat} % hat letters

% math commands
\newcommand{\set}[2]{\left\{ #1 \;\middle|\; #2 \right\}} % set notation
\newcommand{\bigset}[2]{\big\{ #1 \;\big|\; #2 \big\}} % big set notation
\newcommand{\Bigset}[2]{\Big\{ #1 \;\Big|\; #2 \Big\}} % Big set notation
\newcommand{\setangle}[2]{\left\langle #1 \;\middle|\; #2 \right\rangle} % set notation
\newcommand{\ssm}{\smallsetminus} % small set minus
\newcommand{\dotprod}[2]{\left\langle \, #1 \; \middle| \; #2 \, \right\rangle} % dot product
\newcommand{\symdif}{\,\triangle\,} % symmetric difference
\newcommand{\one}{{1\!\!1}} % the all one vector
\newcommand{\eqdef}{\mbox{\,\raisebox{0.2ex}{\scriptsize\ensuremath{\mathrm:}}\ensuremath{=}\,}} % :=
\newcommand{\defeq}{\mbox{~\ensuremath{=}\raisebox{0.2ex}{\scriptsize\ensuremath{\mathrm:}} }} % =:
\newcommand{\simplex}{\triangle} % simplex
\renewcommand{\implies}{\Rightarrow} % imply sign
\newcommand{\transpose}[1]{{#1}^t} % transpose matrix

% operators
\DeclareMathOperator{\conv}{conv} % convex hull
\DeclareMathOperator{\vect}{vect} % linear span
\DeclareMathOperator{\cone}{cone} % cone hull
\DeclareMathOperator{\inv}{inv} % inversions
\DeclareMathOperator{\ascents}{asc} % ascents
\DeclareMathOperator{\descents}{des} % descents

% others
\newcommand{\ie}{\textit{i.e.}~} % id est
\newcommand{\eg}{\textit{e.g.}~} % exempli gratia
\newcommand{\Eg}{\textit{E.g.}~} % exempli gratia
\newcommand{\apriori}{\textit{a priori}} % a priori
\newcommand{\viceversa}{\textit{vice versa}} % vice versa
\newcommand{\versus}{\textit{vs.}~} % versus
\newcommand{\aka}{\textit{a.k.a.}~} % also known as
\newcommand{\perse}{\textit{per se}} % per se
\newcommand{\ordinal}{\textsuperscript{th}} % th for ordinals
\newcommand{\ordinalst}{\textsuperscript{st}} % st for ordinals
\definecolor{darkblue}{rgb}{0,0,0.7} % darkblue color
\definecolor{green}{RGB}{57,181,74} % green color
\definecolor{violet}{RGB}{147,39,143} % violet color
\newcommand{\red}{\color{red}} % red command
\newcommand{\green}{\color{green}} % green command
\newcommand{\darkblue}{\color{darkblue}} % darkblue command
\newcommand{\defn}[1]{\textsl{\darkblue #1}} % emphasis of a definition
\newcommand{\para}[1]{\medskip\noindent\textit{#1.}} % paragraph
\renewcommand{\topfraction}{1} % possibility to have one page of pictures
\renewcommand{\bottomfraction}{1} % possibility to have one page of pictures
\newcommand{\ex}{_{\textrm{exm}}} % examples
\newcommand{\pa}{_{\textrm{pa}}} % path
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{\node[shape=circle,draw,inner sep=1pt, scale=.7] (char) {#1};}}

% marginal comments
\usepackage{todonotes}
\newcommand{\arnau}[1]{\todo[color=orange!30]{#1 --- A.}}
\newcommand{\yann}[1]{\todo[color=red!30]{#1 --- Y.}}
\newcommand{\vincent}[1]{\todo[color=blue!30]{#1 \\ \hfill --- V.}}
\newcommand{\pierreguy}[1]{\todo[color=green!30]{#1 \\ \hfill --- PG.}}

% polytopes
\newcommandx{\Asso}[2][1=\bar Q,2={}]{\mathsf{Asso}^{#2}(#1)} % associahedron
\newcommandx{\Zono}[2][1=\bar Q,2={}]{\mathsf{Zono}^{#2}(#1)} % zonotope
\newcommand{\Fan}{\mathcal{F}} % fan
\newcommand{\multiplicityVector}{\b{m}} % multiplicity vector

% Type cone
\newcommand{\typeCone}{\mathbb{TC}} % type cone
\newcommand{\compatibilityDegree}[2]{(#1\,\|\,#2)} % compatibility degree
\newcommandx{\coefficient}[3][1={\ray[s]}, 2=\ray, 3=\ray']{\alpha_{#2,#3}(#1)} % coefficient in linear dependence

% Graph associahedra
\newcommand{\ground}{\mathrm{V}} % ground set
\newcommandx{\graphG}[1][1=G]{\mathrm{#1}} % graph
\newcommandx{\tube}[1][1=t]{\mathsf{#1}} % tube
\newcommandx{\tubes}{\mathcal{T}} % all tubes
\newcommandx{\tubing}[1][1=T]{\mathsf{#1}} % tubing
\newcommand{\connectedComponents}{\kappa} % connected components
\newcommand{\nestedComplex}{\mathcal{N}} % nested complex
\newcommand{\nestedFan}{\mathcal{F}} % nested fan
\newcommand{\nonDisconnecting}{\mathrm{nd}} % non-disconnecting vertices

% SPECIFIC NON-KISSING COMPLEX

% COMBINATORICS
% quiver
\newcommand{\blossom}{^\text{\ding{96}}} % blossom

% walks
\newcommand{\peaks}[1]{\mathsf{peaks}(#1)} % peaks
\newcommand{\deeps}[1]{\mathsf{deeps}(#1)} % deeps
\newcommand{\distinguishedWalk}[2]{\mathsf{dw}(#1,#2)} % distinguished walk
\newcommand{\distinguishedArrows}[2]{\mathsf{da}(#1,#2)} % distinguished arrows
\newcommand{\distinguishedString}[2]{\mathsf{ds}(#1,#2)} % distinguished string
\newcommand{\distinguishedSign}[2]{\varepsilon(#1,#2)} % distinguished sign

% non-kissing complex, lattice, flip graph
\newcommand{\kn}{\kappa} % kissing number
\newcommand{\KN}{\textsc{kn}} % Kissing Number
\newcommandx{\NKC}[1][1=\bar Q]{\mathcal{K}_{\mathrm{nk}}(#1)} % non-kissing complex
\newcommandx{\RNKC}[1][1=\bar Q]{\mathcal{C}_{\mathrm{nk}}(#1)} % non-kissing complex
\newcommandx{\NKL}[1][1=\bar Q]{\mathcal{L}_{\mathrm{nk}}(#1)} % non-kissing lattice
\newcommandx{\NKG}[1][1=\bar Q]{\mathcal{G}_{\mathrm{nk}}(#1)} % non-kissing flip graph
\newcommandx{\NFC}[1][1=\bar Q]{\mathcal{C}_{\mathrm{nf}}(#1)} % non-friendly complex
\newcommand{\peak}{\mathrm{peak}} % bottom dissection
\newcommand{\deep}{\mathrm{deep}} % top dissection
\newcommand{\reversed}[1]{#1^{\mathrm{rev}}} % reverse all arrows
\renewcommand{\top}{\mathrm{top}} % top
\newcommand{\bottom}{\mathrm{bot}} % bottom
\newcommand{\walk}{\operatorname{\omega}} % walk (of a curve)

% accordion and slalom complexes
\newcommand{\surface}{\mathcal{S}} % an orientable surface
\newcommand{\dual}{^*} % duality
\newcommand{\dissection}{\mathrm{D}} % dissection of a marked surface
\newcommand{\vertices}{\mathcal{V}} % vertices of a dissection
\newcommand{\edges}{\mathcal{E}} % edges of a dissection
\newcommand{\faces}{\mathcal{F}} % faces of a dissection
\renewcommandx{\AC}[1][1=\dissection]{\mathcal{K}_{\mathrm{acc}}(#1)} % accordion complex
\newcommandx{\RAC}[1][1=\dissection]{\mathcal{C}_{\mathrm{acc}}(#1)} % reduced accordion complex
\newcommandx{\SC}[1][1=\dissection\dual]{\mathcal{K}_{\mathrm{sla}}(#1)} % slalom complex
\newcommandx{\RSC}[1][1=\dissection\dual]{\mathcal{C}_{\mathrm{sla}}(#1)} % reduced slalom complex
\newcommandx{\NCC}[1][1={\dissection, \dissection\dual}]{\mathcal{K}_{\mathrm{nc}}(#1)} % non-crossing complex
\newcommandx{\RNCC}[1][1={\dissection, \dissection\dual}]{\mathcal{C}_{\mathrm{nc}}(#1)} % non-crossing complex
\newcommand{\curveof}{\operatorname{\gamma}} % curve (of a walk)
\newcommand{\edgeof}{\operatorname{\varepsilon}} % arc of a vertex
\newcommand{\dualedgeof}{\operatorname{\varepsilon}\dual} % dual arc of a vertex
\DeclareRobustCommand{\SSS}{\reflectbox{$\mathsf{Z}$}} % S
\DeclareRobustCommand{\ZZZ}{\mathsf{Z}} % Z
\newcommand{\vnext}[1]{#1_{\operatorname{next}}} % next point on the boundary of the surface
\newcommand{\vprevious}[1]{#1_{\operatorname{prev}}} % previous point on the boundary of the surface

% lattices
\newcommand{\meet}{\wedge} % meet
\newcommand{\join}{\vee} % join
\newcommand{\bigMeet}{\bigwedge} % meet
\newcommand{\bigJoin}{\bigvee} % join
\newcommand{\closure}[1]{#1^{\mathrm{cl}}} % closure operator
\newcommand{\coclosure}[1]{#1^{\mathrm{cocl}}} % coclosure operator
\newcommand{\uclosure}[1]{#1^{\underline{\mathrm{cl}}}} % loop free closure operator
\newcommand{\Bicl}[1]{\mathsf{Bic}(#1)} % biclosed sets
\newcommand{\projDown}{\pi_\downarrow} % down projection map
\newcommand{\projUp}{\pi^\uparrow} % up projection map
\newcommand{\JI}{\mathsf{JI}} % join-irreducible
\newcommand{\MI}{\mathsf{MI}} % meet-irreducible
\newcommand{\Cong}{\mathsf{Cong}} % congruence lattice
\newcommand{\con}{\mathrm{con}} % congruence contracting a cover relation
\newcommand{\ji}{\mathsf{ji}} % join irreducible
\newcommand{\mi}{\mathsf{mi}} % meet irreducible

% GEOMETRY
% d-vectors
\newcommand{\dvector}[1]{\mathbf{d}(#1)} % d-vector of the path #1
\newcommand{\dvectors}[1]{\mathbf{d}(#1)} % d-vectors of the paths #1
\newcommandx{\dvectorFan}[1][1=\bar Q]{\mathcal{F}^\mathbf{d}(#1)} % d-vector fan
% g-vectors
\newcommand{\gvector}[1]{\mathbf{g}(#1)} % g-vector of the path #1
\newcommand{\gvectors}[1]{\mathbf{g}(#1)} % g-vectors of the paths #1
\newcommandx{\gvectorFan}[1][1=\bar Q]{\mathcal{F}^\mathbf{g}(#1)} % g-vector fan
% c-vectors
\newcommand{\cvector}[2]{\mathbf{c}(#1 \in #2)} % c-vector of the path #1 in the facet #2
\newcommand{\cvectors}[1]{\mathbf{c}(#1)} % c-vectors of the paths #1
\newcommandx{\allcvectors}[1][1=\bar Q]{\mathbf{C}(#1)} % all c-vectors with respect to the initial cluster #1
\newcommandx{\cvectorFan}[1][1=\bar Q]{\mathcal{F}^\mathbf{c}(#1)} % fan of hyperplanes orthogonal to all c-vectors
% points, hyperplanes, half-spaces
\newcommand{\point}[1]{\mathbf{p}(#1)} % vertex of the grid associahedron corresponding to the cluster #1
\newcommandx{\ray}[1][1=r]{\mathbf{#1}} % ray
\newcommandx{\rays}[1][1=R]{\mathbf{#1}} % rays
\newcommand{\hs}{\mathbf{H}^{\le}} % half space
\newcommand{\HS}[1]{\mathbf{H}^{\le}(#1)} % half space
\newcommand{\hyp}{\mathbf{H}^{=}} % hyperplane
\newcommand{\Hyp}[1]{\mathbf{H}^{=}(#1)} % hyperplane
\newcommand{\fix}[1]{\mathrm{Fix}(#1)} % fix space

% ALGEBRA
\newcommand{\Hom}[1]{\operatorname{{\rm Hom}}_{#1}}
\newcommand{\Ext}[1]{\operatorname{{\rm Ext}}_{#1}}
\newcommandx{\AR}[1][1=\bar Q]{\mathrm{AR}(#1)} % Auslander-Reiten quiver
\newcommandx{\tTC}[1][1=\bar Q]{\mathcal{K}^{\textrm{s$\tau$-tilt}}(#1)} % tau-tilting complex
\newcommand{\rep}{\operatorname{{\rm rep}}}
\newcommand{\proj}{\operatorname{{\rm proj}}}
\newcommand{\koszul}{^!} % duality

%% formating the part command
%\makeatletter
%\def\part{\@startsection{part}{1}%
%\z@{.7\linespacing\@plus\linespacing}{.8\linespacing}%
%{\LARGE\sffamily\centering}}
%\@addtoreset{section}{part}
%\makeatother
%\renewcommand{\thesection}{\arabic{part}.\arabic{section}}

% formating the table of contents
\makeatletter
\def\l@section{\@tocline{1}{2pt}{0pc}{}{}}
\makeatother
\let\oldtocpart=\tocpart
\renewcommand{\tocpart}[2]{\bf\large\oldtocpart{#1}{#2}}
\let\oldtocsection=\tocsection
\renewcommand{\tocsection}[2]{\bf\oldtocsection{#1}{#2}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Type cones of $\b{g}$-vector fans}

\thanks{YP, VP and PGP were partially supported by the French ANR grant SC3A~(15\,CE40\,0004\,01). AP and VP were partially supported by the French ANR grant CAPPS~(17\,CE40\,0018).}

\author{Arnau Padrol}
\address[Arnau Padrol]{IMJ - Paris Rive Gauche, Sorbonne Universit\'e}
\email{arnau.padrol@imj-prg.fr.}
\urladdr{\url{https://webusers.imj-prg.fr/~arnau.padrol/}}

\author{Yann Palu}
\address[Yann Palu]{LAMFA, Universit\'e Picardie Jules Verne, Amiens}
\email{yann.palu@u-picardie.fr}
\urladdr{\url{http://www.lamfa.u-picardie.fr/palu/}}

\author{Vincent Pilaud}
\address[Vincent Pilaud]{CNRS \& LIX, \'Ecole Polytechnique, Palaiseau}
\email{vincent.pilaud@lix.polytechnique.fr}
\urladdr{\url{http://www.lix.polytechnique.fr/~pilaud/}}

\author{Pierre-Guy Plamondon}
\address[Pierre-Guy Plamondon]{Laboratoire de Math\'ematiques d'Orsay, Universit\'e Paris-Sud, CNRS, Universit\'e Paris-Saclay}
\email{pierre-guy.plamondon@math.u-psud.fr}
\urladdr{\url{https://www.math.u-psud.fr/~plamondon/}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{abstract}
We investigate the type cone of the $\b{g}$-vector fans for different generalizations of the associahedron (hopefully generalized associahedra, gentle associahedra, graph associahedra, and maybe quotientopes and brick polytopes).
The objective is to determine which are the exchangeable pairs of objects that describe the type cone.
When the type cone happens to be simplicial, we derive simple descriptions of all polytopal realizations of the $\b{g}$-vector fan.
\end{abstract}

\maketitle

We explain recent results of~\cite{BazierMatteDouvilleMousavandThomasYildirim}. Some advantages of our approach are:
\begin{itemize}
\item We manage to extend their results to other families of $\b{g}$-vector fans: first to all $\b{g}$-vector fans of finite type cluster algebras acyclic or not (whose polytopality was only proved recently in~\cite{HohlwegPilaudStella}), then to all $\b{g}$-vector fans of the $\tau$-tilting finite gentle algebras (whose polytopality was proved recently in~\cite{PaluPilaudPlamondon}), and finally to the nested fans of graph associahedra (whose polytopality was studied in~\cite{CarrDevadoss, Devadoss, Postnikov, FeichtnerSturmfels, Zelevinsky}).
\item We have a simpler proof, only based on the transformation between the classical descriptions of a polytope of the form~$\set{\b{x} \in \R^n}{\b{G}\b{x} \le \b{h}}$ and~$\set{\b{z} \in \R^N}{\b{K}\b{z} = \b{K}\b{h} \text{ and } \b{z} \ge 0}$ (this transformation is standard in optimization). In particular, we do not need to consider only rational polytopes and pass to the limit to deal with all real descriptions.
\item We observe that we obtain all realizations of the $\b{g}$-vector fans of the considered families.
\end{itemize}

\section{Polytopal realizations and type cone of a simplicial fan}

\subsection{Polytopes and fans}

We briefly recall basic definitions and properties of polyhedral fans and polytopes, and refer to~\cite{Ziegler-polytopes} for a classical textbook on this topic.

A hyperplane~$H \subset \R^d$ is a \defn{supporting hyperplane} of a set~$X \subset \R^d$ if~$H \cap X \ne \varnothing$ and~$X$ is contained in one of the two closed half-spaces of~$\R^d$ defined by~$H$.

We denote by~$\R_{\ge0}\rays \eqdef \set{\sum_{\ray \in \rays} \lambda_{\ray} \, \ray}{\lambda_{\ray} \in \R_{\ge0}}$ the \defn{positive span} of a set~$\rays$ of vectors of~$\R^d$.
A \defn{polyhedral cone} is a subset of~$\R^d$ defined equivalently as the positive span of finitely many vectors or as the intersection of finitely many closed linear halfspaces.
The \defn{faces} of a cone~$C$ are the intersections of~$C$ with the supporting hyperplanes of~$C$.
The $1$-dimensional (resp.~codimension~$1$) faces of~$C$ are called~\defn{rays} (resp.~\defn{facets}) of~$C$.
A cone is \defn{simplicial} if it is generated by a set of independent vectors.

A \defn{polyhedral fan} is a collection~$\Fan$ of polyhedral cones such that
\begin{itemize}
\item if~$C \in \Fan$ and~$F$ is a face of~$C$, then~$F \in \Fan$,
\item the intersection of any two cones of~$\Fan$ is a face of both.
\end{itemize}
A fan is \defn{simplicial} if all its cones are, \defn{complete} if the union of its cones covers the ambient space~$\R^d$, and \defn{essential} if it contains the cone~$\{\b{0}\}$.
% For two fans~$\Fan, \Fan[G]$ in~$\R^d$, we say that~$\Fan$ \defn{refines}~$\Fan[G]$ (and that~$\Fan[G]$ \defn{coarsens}~$\Fan$) if every cone of~$\Fan$ is contained in a cone of~$\Fan[G]$.

A \defn{polytope} is a subset~$P$ of~$\R^d$ defined equivalently as the convex hull of finitely many points or as a bounded intersection of finitely many closed affine halfspaces.
The \defn{dimension}~$\dim(P)$ is the dimension of the affine hull of~$P$.
The \defn{faces} of~$P$ are the intersections of~$P$ with its supporting hyperplanes.
The dimension~$0$ (resp.~dimension~$1$, resp.~codimension~$1$) faces are called \defn{vertices} (resp.~\defn{edges}, resp.~\defn{facets}) of~$P$.
A polytope is \defn{simple} if its supporting hyperplanes are in general position, meaning that each vertex is incident to $\dim(P)$ facets (or equivalently to $\dim(P)$ edges).

The (outer) \defn{normal cone} of a face~$F$ of~$P$ is the cone generated by the outer normal vectors of the facets of~$P$ containing~$F$.
In other words, it is the cone of vectors~$\b{c}$ such that the linear form~${\b{x} \mapsto \dotprod{\b{c}}{\b{x}}}$ on~$P$ is maximized by all points of the face~$F$.
The (outer) \defn{normal fan} of~$P$ is the collection of the (outer) normal cones of all its faces.
We say that a complete polyhedral fan~$\Fan$ in~$\R^d$ is \defn{polytopal} when it is the normal fan of a polytope~$P$ of~$\R^d$, and that~$P$ is a \defn{polytopal realization} of~$\Fan$.

\subsection{Type cone}

Fix an essential complete simplicial fan~$\Fan$ in~$\R^n$. Let~$\b{G}$ the $N \times n$-matrix whose rows are the rays of~$\Fan$ and let~$\b{K}$ be a $(N-n) \times N$-matrix that spans the left kernel of~$\b{G}$ (\ie $\b{K}\b{G} = 0$). For any height vector~$\b{h} \in \R^N$, we define the polytope
\[
P_\b{h} \eqdef \set{\b{x} \in \R^n}{\b{G}\b{x} \le \b{h}}.
\]
We say that $h$ is \defn{$\Fan$-admissible} if $P_\b{h}$ is a polytopal realization of~$\Fan$.
The following classical statement characterizes the $\Fan$-admissible height vectors.
It is a reformulation of regularity of triangulations of vector configurations, introduced in the theory of secondary polytopes~\cite{GelfandKapranovZelevinsky}, see also~\cite{DeLoeraRambauSantos}.
We present here a convenient formulation from~\cite[Lem.~2.1]{ChapotonFominZelevinsky}.

\begin{proposition}
\label{prop:characterizationPolytopalFan}
Then the following are equivalent for any height vector~$h \in \R^N$:
\begin{enumerate}
\item The fan~$\Fan$ is the normal fan of the polytope~$P_\b{h} \eqdef \set{\b{x} \in \R^n}{\b{G}\b{x} \le \b{h}}$.
\item For any two adjacent cones~$\R \rays$ and~$\R \rays'$ of~$\Fan$ with~$\rays \ssm \{\ray\} = \rays' \ssm \{\ray'\}$, we have
\[
\alpha \, h_{\ray} + \alpha' \, h_{\ray'} + \sum_{\ray[s] \in \rays \cap \rays'} \beta_{\ray[s]} \, h_{\ray[s]} > 0,
\]
where
\[
\alpha \, \ray + \alpha' \, \ray' + \sum_{\ray[s] \in \rays \cap \rays'} \beta_{\ray[s]} \, \ray[s] = 0
\]
is the unique (up to rescaling) linear dependence with~$\alpha, \alpha' > 0$ between the rays of~$\rays \cup \rays'$.
\end{enumerate}
\end{proposition}

\begin{notation}
For any two adjacent cones~$\R\rays$ and~$\R\rays'$ of~$\Fan$ with~$\rays \ssm \{\ray\} = \rays' \ssm \{\ray'\}$, we denote by~$\coefficient[{\ray[s]}][\rays][\rays']$ the coefficient of~$\ray[s]$ in the unique linear dependence between the rays of~$\rays \cup \rays'$, \ie such that
\[
\sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \ray[s] = 0.
\]
These coefficients are \apriori{} defined up to rescaling, but we additionally fix the rescaling so that~${\coefficient[\ray][\rays][\rays'] + \coefficient[\ray'][\rays][\rays'] = 1}$.
\end{notation}

In this paper, we are interested in the set of all possible realizations of~$\Fan$. This was studied by P.~McMullen in~\cite{McMullen-typeCone}.

\begin{definition}
The \defn{type cone} of~$\Fan$ is the cone~$\typeCone(\Fan)$ of all $\Fan$-admissible height vectors~$\b{h}$:
\begin{align*}
\typeCone(\Fan) & \eqdef \set{\b{h} \in \R^N}{\Fan \text{ is the normal fan of } P_\b{h}} \\
& = \Bigset{\b{h} \in \R^N}{\sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} > 0 \text{ for any adjacent cones~$\R\rays, \R\rays'$ of~$\Fan$}}.
\end{align*}
\end{definition}

Note that the type cone is an open cone and contains a linearity subspace of dimension~$n$ (it is invariant by translation in~$\b{G} \R^n$). We could thus intersect~$\typeCone(\Fan)$ by the kernel of~$\b{G}$, or consider the projection~$\b{K}\typeCone(\Fan)$.

\begin{definition}
An \defn{extremal adjacent pair} of~$\Fan$ is a pair of adjacent cones~$\{\R\rays, \R\rays'\}$ of~$\Fan$ such that the corresponding inequality $\sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} > 0$ in the definition of the type cone~$\typeCone(\Fan)$ actually defines a facet of~$\typeCone(\Fan)$.
\end{definition}

In other words, extremal adjacent pairs define the extremal rays of the polar of the type cone~$\typeCone(\Fan)$.
Understanding the extremal adjacent pairs of~$\Fan$ enables to describe its type cone~$\typeCone(\Fan)$ and thus all its polytopal realizations.

\subsection{Coherent fans}

Two rays~$\ray$ and~$\ray'$ of~$\Fan$ are called \defn{compatible} if there are both contained in a cone of~$\Fan$ and \defn{exchangeable} if there are two adjacent cones~$\R\rays$ and~$\R\rays'$ of~$\Fan$ with ${\rays \ssm \{\ray\} = \rays' \ssm \{\ray'\}}$.
If~$\rays(\Fan)$ denotes the set of rays of~$\Fan$, a \defn{compatibility degree} for~$\Fan$ is a function~$\compatibilityDegree{-}{-}: \rays(\Fan) \times \rays(\Fan) \to \R$ such that
\begin{itemize}
\item $\compatibilityDegree{\ray}{\ray'} = -1$ if~$\ray = \ray'$ and is non-negative otherwise,
\item $\compatibilityDegree{\ray}{\ray'} = 0$ if ~$\ray$ and~$\ray'$ are compatible,
\item $\compatibilityDegree{\ray}{\ray'} > 0$ if~$\ray \ne \ray'$ are incompatible,
\item $\compatibilityDegree{\ray}{\ray'} = 1 = \compatibilityDegree{\ray'}{\ray}$ if and only if~$\ray$ and~$\ray'$ are exchangeable.
\end{itemize}

We say that the fan~$\Fan$ is \defn{coherent} if for any two exchangeable rays~$\ray, \ray'$ of~$\Fan$, the linear dependence
\vincent{Not sure of the choice of the name.}
\[
\sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \ray[s] = 0.
\]
does not depend on the pair~$\{\rays, \rays'\}$ of adjacent cones of~$\Fan$ with $\rays \ssm \{\ray\} = \rays' \ssm \{\ray'\}$, but only on the pair of rays~$\ray, \ray'$.
This implies in particular that the rays~$\ray[s]$ for which~$\coefficient[{\ray[s]}][\rays][\rays'] \ne 0$ belong to~$\rays \cup \rays'$ for any pair~$\{\rays, \rays'\}$ of adjacent cones of~$\Fan$ with $\rays \ssm \{\ray\} = \rays' \ssm \{\ray'\}$. These rays are thus called \defn{forced rays} for the exchangeable pair~$\{\ray, \ray'\}$.

When~$\Fan$ is coherent, we change the notation~$\coefficient[{\ray[s]}][\rays][\rays']$ to~$\coefficient$ and we obtain that the type cone of~$\Fan$ is expressed as
\[
\typeCone(\Fan) = \Bigset{\b{h} \in \R^N}{\sum_{\ray[s] \in \rays \cup \rays'} \coefficient \, \b{h}_{\ray[s]} > 0 \text{ for any exchangeable rays~$\ray, \ray'$ of~$\Fan$}}.
\]

\begin{definition}
In a coherent fan~$\Fan$, an \defn{extremal exchangeable pair} is a pair of exchangeable rays~$\{\ray,\ray'\}$ such that the corresponding inequality~${\sum_{\ray[s] \in \rays \cup \rays'} \coefficient \, \b{h}_{\ray[s]} > 0}$ defines a facet of the type cone~$\typeCone(\Fan)$.
\end{definition}

In this paper, we will only consider coherent fans, and our objective will be to describe their extremal exchangeable pairs.

\subsection{Alternative polytopal realizations}

In this section, we provide alternative polytopal realizations of the fan~$\Fan$.
We also discuss the behavior of these realizations in the situation when the type cone~$\typeCone(\Fan)$ is simplicial.

We still consider an essential complete simplicial fan~$\Fan$ in~$\R^n$, the $N \times n$-matrix~$\b{G}$ whose rows are the rays of~$\Fan$, and the $(N-n) \times N$-matrix~$\b{K}$ which spans the left kernel of~$\b{G}$.

\begin{proposition}
\label{prop:alternativePolytopalRealization}
The affine map~$\Psi: \R^n \to \R^N$ defined by~$\Psi(\b{x}) = \b{h} - G\b{x}$ sends the polytope
\[
P_\b{h} \eqdef \set{\b{x} \in \R^n}{\b{G}\b{x} \le \b{h}}
\]
to the polytope
\[
Q_\b{h} \eqdef \set{\b{z} \in \R^N}{\b{K}\b{z} = \b{K}\b{h} \text{ and } \b{z} \ge 0}.
\]
\end{proposition}

\begin{proof}
For~$\b{x}$ in~$P_\b{h}$, we have $\Psi(\b{x}) \ge 0$ by definition and~$\b{K}\Psi(\b{x}) = \b{K}\b{h} - \b{K}\b{G}\b{x} = \b{K}\b{h}$ since~$\b{K}$ is the left kernel of~$\b{G}$. Therefore~$\Psi(\b{x}) \in Q_\b{h}$.
Moreover, the map~$\Psi : P_\b{h} \to Q_\b{h}$ is:
\begin{itemize}
\item injective: Indeed, $\Psi(\b{x}) = \Psi(\b{x}')$ implies~$\b{G}(\b{x} - \b{x}') = 0$ and~$\b{G}$ has full rank since~$\Fan$ is essential and complete.
\item surjective: Indeed, for~$\b{z} \in Q_\b{h}$, we have~$\b{K}(\b{h}-\b{z}) = 0$ so that~$\b{h}-\b{z}$ belongs to the right kernel of~$\b{K}$ which is the image of~$\b{G}$. Therefore, there exists~$\b{x} \in \R^n$ such that~$\b{h}-\b{z} = \b{G}\b{x}$. Therefore, $\b{z} = \Psi(\b{x}$ and~$\b{x} \in P_\b{h}$ since~$\b{h} - \b{G}\b{x} = \b{z} \ge 0$.\qedhere
\end{itemize}
\end{proof}

\begin{corollary}
Assume that the type cone~$\typeCone(\Fan)$ is simplicial and let~$\b{K}$ be the $(N-n) \times N$-matrix whose rows are the outer normal vectors of the facets of~$\typeCone(\Fan)$. Then the polytope
\[
R_\b{\ell} \eqdef \set{\b{z} \in \R^N}{K\b{z} = \b{\ell} \text{ and } \b{z} \ge 0}
\]
is a realization of the fan~$\Fan$ for any positive vector~$\b{\ell} \in \R_{>0}^{N-n}$.
Moreover, the polytopes~$R_\b{\ell}$ for~$\b{\ell} \in \R_{>0}^{N-n}$ describe all polytopal realizations of~$\Fan$.
\end{corollary}

\begin{proof}
Let~$\b{\ell} \in \R_{>0}^{N-n}$.
Since~$\b{K}$ has full rank there exists~$\b{h} \in \R^N$ such that~$\b{K}\b{h} = \b{\ell}$.
Since~$\b{K}\b{h} \ge 0$ and the rows of~$\b{K}$ are precisely all outer normal vectors of the facets of the type cone~$\typeCone(\Fan)$, we obtain that~$\b{h}$ belongs to~$\typeCone(\Fan)$.
Since $R_\b{\ell} = Q_\b{h} \sim P_\b{h}$ by \cref{prop:alternativePolytopalRealization}, we conclude that~$R_\b{\ell}$ is a polytopal realization of~$\Fan$.
Since~$\typeCone(\Fan)$ is simplicial, we have~$\b{K}\typeCone(\Fan) = \R_{>0}^{N-n}$, so that we obtain all polytopal realizations of~$\Fan$ this way.
\end{proof}

\section{Applications to different generalizations of the associahedron}

\subsection{Generalized associahedra}

The acyclic and simply-laced case was treated in~\cite{BazierMatteDouvilleMousavandThomasYildirim}.
Computer experiments indicate that the type cone is always simplicial for any seed (acyclic or not) in any finite type cluster algebra.
While the case of acyclic seeds can be handled by representation theory~\cite{BazierMatteDouvilleMousavandThomasYildirim}, we have no proof at the moment for cyclic seeds.

One important observation is that it seems there is ``one extremal exchangeable pair for each positive root'' (or equivalently each positive $c$-vector), meaning that for each positive root~$\beta \in \Phi^+$, there is precisely one extremal exchangeable pair~$\{x,x'\}$ of cluster variables for which the flip of~$x$ to~$x'$ (for any pair of clusters~$\{X,X'\}$ with~$X \ssm \{x\} = X' \ssm \{x'\}$) is in the direction of~$\beta$.
The goal is thus to determine for each positive root which exchangeable pair is extremal.

\subsection{Gentle associahedra}

We are already missing a criterion for exchangeable pairs of walks. See \cite[Sect.~9]{BrustleDouvilleMousavandThomasYildirim}.
It seems that two exchangeable pairs are always kissing along a single distinguishable string.
We need to prove that to see that the non-kissing fan is coherent (because for a pair of exchangeable walks, I can completely reconstruct the $\b{g}$-vector dependence of the flip if I know there distinguished substring).
Note however that
\begin{itemize}
\item exchangeable pairs might kiss along additional non-distinguishable strings (example: just a loop),
\item non-exchangeable walks might kiss along a single distinguishable string (example: see the cyclic triangle in~\cite{PaluPilaudPlamondon}).
\end{itemize}

\bigskip
We have some conjectures on what the extremal exchangeable pairs should be.
One clear (but a bit empty) result is that extremal exchangeable pairs correspond in the Auslander-Reiten quiver to rectangles whose four vertices are non-self-kissing and that cannot be tiled with smaller such rectangles.

\subsection{Graph associahedra}

Let~$\graphG$ be a graph with vertex set~$\ground$.
Let~$\connectedComponents(\graphG)$ denote the set of connected components of~$\graphG$ and define~$n \eqdef |\ground|-|\connectedComponents(\graphG)|$.
A \defn{tube} of~$\graphG$ is a non-empty connected induced subgraph of~$\graphG$.
The set of tubes of~$\graphG$ is denoted by~$\tubes(\graphG)$.
The inclusion maximal tubes of~$\graphG$ are its connected components~$\connectedComponents(\graphG)$, and all other tubes are called \defn{proper}.
Two tubes~$\tube, \tube'$ of~$\graphG$ are \defn{compatible} if they are either nested (\ie $\tube \subseteq \tube'$ or~$\tube' \subseteq \tube$), or disjoint and non-adjacent (\ie $\tube \cup \tube'$ is not a tube of~$\graphG$).
A \defn{tubing} on~$\graphG$ is a set~$\tubing$ of pairwise compatible proper tubes of~$\graphG$.
The collection of all tubings on~$\graphG$ is a simplicial complex, called \defn{nested complex} of~$\graphG$ and denoted by~$\nestedComplex(\graphG)$.

Let~$(\b{e}_v)_{v \in \ground}$ be the canonical basis of~$\R^\ground$, let~${\HH \eqdef \bigset{\b{x} \in \R^\ground}{\sum_{w \in W} x_w = 0 \text{ for all } W \in \connectedComponents(\graphG)}}$ and~$\pi : \R^\ground \to \HH$ denote the orthogonal projection on~$\HH$.
Let~$\gvector{\tube} \eqdef \pi \big( \sum_{v \in \tube} \b{e}_v \big)$ denote the projection of the characteristic vector of a tube~$\tube$ of~$\graphG$, and define~$\gvectors{\tubing} \eqdef \set{\gvector{\tube}}{\tube \in \tubing}$ for a tubing~$\tubing$ on~$\graphG$.
Note that~$\gvector{\graphG} = 0$ by definition.
These vectors support a complete simplicial fan realization of the nested complex:

\begin{theorem}[\cite{CarrDevadoss, Postnikov, FeichtnerSturmfels, Zelevinsky}]
\label{theo:gFan}
For any graph~$\graphG$, the collection of cones
\[
\nestedFan(\graphG) \eqdef \set{\R_{\ge 0} \, \gvectors{\tubing}}{\tubing \text{ tubing on } \graphG}
\]
is a complete simplicial fan of~$\HH$, called \defn{nested fan} of~$\graphG$, which realizes the nested complex~$\nestedComplex(\graphG)$.
\end{theorem}

It is proved in~\cite{CarrDevadoss, Devadoss, Postnikov, FeichtnerSturmfels, Zelevinsky} that the nested fan comes from a polytope.

\begin{theorem}[\cite{CarrDevadoss, Devadoss, Postnikov, FeichtnerSturmfels, Zelevinsky}]
\label{theo:graphAssociahedron}
For any graph~$\graphG$, the nested fan~$\nestedFan(\graphG)$ is the normal fan of the graph associahedron~$\Asso[\graphG]$.
\end{theorem}

The following statement follows from~\cite{MannevillePilaud-compatibilityFans, Zelevinsky}.

\begin{proposition}
\label{prop:exchangeablePairsGA}
Let~$\tube, \tube'$ be two tubes of~$\graphG$. Then
\begin{enumerate}[(i)]
\item The tubes~$\tube$ and~$\tube'$ are exchangeable if and only if $\tube'$ has a unique neighbor~$v$ in~$\tube \ssm \tube'$ and $\tube$ has a unique neighbor~$v'$ in~$\tube' \ssm \tube$.
\item For any maximal tubings~$\tubing, \tubing$ on~$\graphG$ with $\tubing \ssm \{\tube\} = \tubing' \ssm \{\tube'\}$, both~$\tubing \cup \connectedComponents(\graphG)$ and~$\tubing' \cup \connectedComponents(\graphG)$ contain the tube~$\tube \cup \tube'$ and the connected components of~$\tube \cap \tube'$.
\item For any maximal tubings~$\tubing, \tubing$ on~$\graphG$ with $\tubing \ssm \{\tube\} = \tubing' \ssm \{\tube'\}$, the linear dependence between the $\b{g}$-vectors of~$\tubing \cup \tubing'$ is given by
\[
\gvector{\tube} + \gvector{\tube'} = \gvector{\tube \cup \tube'} + \sum_{\tube[s] \in \connectedComponents(\tube \cap \tube')} \gvector{\tube[s]}.
\]
In other words, the nested fan of~$\graphG$ is coherent.
\item For any maximal tubings~$\tubing, \tubing$ on~$\graphG$ with $\tubing \ssm \{\tube\} = \tubing' \ssm \{\tube'\}$, the $\b{c}$-vector orthogonal to all $\b{g}$-vectors~$\gvector{\tube[s]}$ for~$\tube[s] \in \tubing \cap \tubing'$ is~$\b{e}_v - \b{e}_{v'}$.
\end{enumerate}
\end{proposition}

\begin{proof}
Points~(i) and~(ii) was proved in~\cite{MannevillePilaud-compatibilityFans}. Point~(iii) follows from the fact that
\[
\sum_{v \in \tube} \b{e}_v + \sum_{v \in \tube'} \b{e}_v = \sum_{v \in \tube \cup \tube'} \b{e}_v + \sum_{v \in \tube \cap \tube'} \b{e}_v = \sum_{v \in \tube \cup \tube'} \b{e}_v + \sum_{\substack{\tube[s] \in \connectedComponents(\tube \cap \tube') \\ v \in \tube[s]}} \b{e}_v.
\]
Finally, any tube~$\tube[s] \in \tubing \cap \tubing'$ that contains~$v$ or~$v'$ actually contains both (to be compatible with~$\tube$ and~$\tube'$). Therefore, $\gvector{\tube[s]}$ is orthogonal to~$\b{e}_v - \b{e}_{v'}$ for any tube~$\tube[s] \in \tubing \cap \tubing'$.
\end{proof}

We are now ready to describe the type cone of the nested fan~$\nestedFan(\graphG)$.
We start with the case of the path.
Recall that the tubes of the path are the intervals of~$[n]$ and that two intervals~$[i,j]$ and~$[i',j']$ of~$[n]$ are exchangeable if either~${i < i' \le j+1 < j'+1}$ or~${i' < i \le j'+1 < j+1}$.

\begin{proposition}
\label{prop:extremalExchangeablePairsA}
Two intervals~$[i,j]$ and~$[i',j']$ of~$[n]$ form an extremal exchangeable pair for the nested fan the path if and only if~$i = i'+1$ and~$j = j'+1$, or the opposite.
\end{proposition}

\begin{proof}
Let~$(\b{f}_{[i,j]})_{1 \le i \le j \le n}$ denote the canonical basis of~$\R^N$.
Consider two exchangeable tubes~$[i,j]$ and~$[i',j']$ with~$i < i' \le j+1 < j'+1$.
By \cref{prop:exchangeablePairsGA}\,(iii), the linear dependence between the corresponding $\b{g}$-vectors is given by
\[
\gvector{[i,j]} + \gvector{[i',j']} = \gvector{[i,j']} + \gvector{[i',j]}
\]
Therefore, the outer normal vector of the corresponding inequality of the type cone~$\typeCone(\nestedFan(\graphG))$ is given by
\[
\b{n}(i,j,i',j') \eqdef \b{f}_{[i,j]} + \b{f}_{[i',j']} - \b{f}_{[i,j']} - \b{f}_{[i',j]}
\]
Denoting
\[
\b{m}(k,\ell) \eqdef \b{n}(k,\ell-1,k+1,\ell) = \b{f}_{[k, \ell-1]} + \b{f}_{[k+1, \ell]} - \b{f}_{[k, \ell]} - \b{f}_{[k+1, \ell-1]},
\]
we obtain that
\[
\b{n}(i,j,i',j') = \sum_{\substack{k \in {[i,i'[} \\ \ell \in {]j,j']}}} \b{m}(k,\ell).
\]
Indeed, on the right hand side, the basis vector~$\b{f}_{[k,\ell]}$ appears with a positive sign in~$\b{m}(k,{\ell+1})$ for~$(k,\ell) \in {[i,i'[} \times {[j,j'[}$ and in~$\b{m}(k-1, \ell)$ for~$(k,\ell) \in {]i,i']} \times {]j,j']}$, and with a negative sign in~$\b{m}(k,\ell)$ for~$(k,\ell) \in {[i,i'[} \times {]j,j']}$ and in~$\b{m}(k-1,\ell+1)$ for~$(k,\ell) \in {]i,i']} \times {[j,j'[}$.
Therefore, these contributions all vanish except when~$[k, \ell]$ is one of the tubes~$[i,j]$, $[i',j']$, $[i,j']$ or~$[i',j]$.
%For any~$i \le k < i'$ and~$j < \ell \le j'$, the exchange relation between the tubes~$[k, \ell-1]$ and~$[k+1, \ell]$ is given by
%\begin{equation}
%\label{eq:exch2}
%\tag{$\mathrm{ER}_k^\ell$}
%\gvector{[k, \ell-1]} + \gvector{[k+1, \ell]} = \gvector{[k, \ell]} + \gvector{[k+1, \ell-1]}.
%\end{equation}
%Summing the exchange relations~\eqref{eq:exch2} over all pairs~$(k,\ell) \in {[i,i'[} \times {]j,j']}$, we obtain after simplifications the exchange relation~\eqref{eq:exch1}.
%Indeed, the $\b{g}$-vector of each tube~$[k, \ell]$ appears on the left hand sides of the exchange relations~($\mathrm{ER}_k^{\ell+1}$) for~$(k,\ell) \in {[i,i'[} \times {[j,j'[}$ and ($\mathrm{ER}_{k-1}^\ell$) for~$(k,\ell) \in {]i,i']} \times {]j,j']}$ and on the right hand sides of the exchange relations~($\mathrm{ER}_k^\ell$) for~$(k,\ell) \in {[i,i'[} \times {]j,j']}$ and~($\mathrm{ER}_{k-1}^{\ell+1}$) for~$(k,\ell) \in {]i,i']} \times {[j,j'[}$.
%Therefore, these contributions all vanish except when~$[k, \ell]$ is one of the tubes~$[i,j]$, $[i',j']$, $[i,j']$ or~$[i',j]$.
This shows that any exchange relation is a positive linear combination of the exchange relations corresponding to all pairs of tubes~$[i,j]$ and~$[i',j']$ of~$[n]$ such that~$i = i'+1$ and~$j = j'+1$.

We now need to show that all these exchangeable pairs are extremal.
Assume that~$\b{m}(k,\ell)$ can be written as the linear combination
\begin{equation}
\label{eq:linComb}
\b{m}(k,\ell) = \sum \lambda(i,j,i',j') \, \b{n}(i,j,i',j'),
\end{equation}
where~$\lambda(i,j,i',j') \ge 0$ for all exchangeable pairs~$\{[i,j], [i',j']\}$.
Note that~$\sum \lambda(i,j,i',j') > 1$ since the coefficient of~$\b{f}_{[k,\ell]}$ in~$\b{m}(k,\ell)$ is~$-1$.
Consider the linear form~$\Phi: \R^N \to \R$ defined by~$\Phi(\b{f}_{[i,j]}) = -(j-i)^2$.
A quick computation shows that
\[
\Phi(\b{n}(i,j,i',j')) = 2(i'-i)(j'-j).
\]
Applying~$\Phi$ to \cref{eq:linComb}, we obtain
\[
1 = \sum \lambda(i,j,i',j')(i'-i)(j'-j).
\]
Since~$\sum \lambda(i,j,i',j') > 1$ we obtain that~$\lambda(k,\ell-1,k+1,\ell-1) = 1$ and~$\lambda(i,j,i',j') = 0$ for all other exchangeable pairs~$\{[i,j], [i',j']\}$.
\end{proof}

\cref{prop:extremalExchangeablePairsA} extends to arbitrary graphs as follows.
% We denote by~$X \symdif Y$ the symmetric difference of two sets~$X$ and~$Y$.

\begin{proposition}
\label{prop:extremalExchangeablePairsGA}
%A pair~$\{\tube, \tube'\}$ of exchangeable tubes of~$\graphG$ is extremal if and only if~$|\tube \symdif \tube'| = 2$.
Two tubes~$\tube$ and~$\tube'$ of~$\graphG$ form an extremal exchangeable pair for the nested fan of~$\graphG$ if and only if~${\tube \ssm \{v\} = \tube' \ssm \{v'\}}$ for some neighbor~$v$ of~$\tube'$ and some neighbor~$v'$ of~$\tube$.
\end{proposition}

\begin{proof}
Consider an exchangeable pair~$\{\tube, \tube'\}$ of tubes of~$\graphG$ and let~$p = |\tube \cup \tube'|$.
By \cref{prop:exchangeablePairsGA}, $\tube'$ has a unique neighbor~$v$ in~$\tube \ssm \tube'$ and $\tube$ has a unique neighbor~$v'$ in~$\tube' \ssm \tube$.
Therefore, $\tube \ssm \tube'$ and~$\tube' \ssm \tube$ are both connected.
We can thus label the elements of~$\tube \cup \tube'$ by~$\{v_1, \dots, v_p\}$ such that~$\{v_i, \dots, v_j\}$ induces a tube~$\tube_{k,\ell}$ of~$\graphG$ for any~$1 \le k \le \ell \le p$. 
The map~$[k,\ell] \mapsto \tube_{k,\ell}$ is thus an injection from the tubes of the path~$\graphG[P]_p$ to that of~$\graphG$ that fulfills
\begin{itemize}
\item $\tube_{k,\ell-1} \ssm \{v_k\} = \tube_{k+1,\ell} \ssm \{v_\ell\}$ for any~$1 \le k \le \ell \le p$, and
\item $\gvector{\tube_{k,\ell}} = M\gvector{[k,\ell]}$ for any~$1 \le k \le \ell \le p$, where~$M$ is the matrix sending~$\b{e}_m$ to~$\b{e}_{v_m}$.
\end{itemize}
Therefore, this map transports the linear combinations of \cref{prop:extremalExchangeablePairsA}.
We conclude that the exchange relation corresponding to the exchangeable pair~$\{\tube, \tube'\}$ is a positive linear combination of the exchange relations corresponding to the pairs~$\{\tube_{k,\ell-1}, \tube_{k+1,\ell}\}$ for all~${(k,\ell) \in {[1, p-|\tube'|+1[} \times {]|\tube|, p]}}$.

We now need to show that all these pairs are extremal.
\vincent{TODO}
\end{proof}

\begin{corollary}
For any $\b{c}$-vector supports at least one extremal exchangeable pair.
\end{corollary}

\begin{proof}
Consider a $\b{c}$-vector~$\b{e}_v - \b{e}_{v'}$ for two distinct vertices~$v, v'$ in a common connected component of~$\graphG$. Let~$\tube[s]$ be a path from~$v$ to~$v'$ in~$\graphG$ and let~$\tube \eqdef \tube[s] \cup \{v\}$ and~$\tube' \eqdef \tube[s] \cup \{v'\}$. Then $\{\tube, \tube'\}$ is an extremal exchangeable pair with $\b{c}$-vector~$\b{e}_v - \b{e}_{v'}$.
\end{proof}

\begin{corollary}
Consider a graph~$\graphG$ on~$\ground$ with tubes~$\tubes(\graphG)$ and a height vector~$\b{h} \in \R^{\tubes(\graphG)}$ such that~$\b{h}_{\graphG} = 0$ and
\[
\b{h}_{\tube} + \b{h}_{\tube'} = \b{h}_{\tube \cup \tube'} + \sum_{\tube[s] \in \connectedComponents(\tube \cap \tube')} \b{h}_{\tube[s]}
\]
for any pair of tubes~$\{\tube, \tube'\}$ of~$\graphG$ with~$\tube \ssm \{v\} = \tube' \ssm \{v'\}$ where~$v$ is a neighbor of~$\tube'$ and~$v'$ is a neighbor of~$\tube$.
Then the nested fan~$\nestedFan(\graphG)$ is the normal fan of the graph associahedron
\[
\set{\b{x} \in \R^\ground}{\dotprod{\gvector{\tube}}{\b{x}} \le \b{h}_{\tube} \text{ for any tube } \tube \in \tubes(\graphG)}.
\]
\end{corollary}

We now compute the number of extremal exchangeable pairs of the nested fan.
For a tube~$\tube$ of~$\graphG$, we denote by~$\nonDisconnecting(\tube)$ the number of non-disconnecting vertices of~$\tube$.
In other words, it is the number of tubes covered by~$\tube$ in the inclusion poset of all tubes of~$\graphG$.

\begin{proposition}
\label{prop:numberExtremalExchangeablePairsGA}
The nested fan~$\nestedFan(\graphG)$ has~$\sum_{\tube \in \tubes(\graphG)} \binom{\nonDisconnecting(\tube)}{2}$ extremal exchangeable pairs.
\end{proposition}

\begin{proof}
By \cref{prop:extremalExchangeablePairsGA}, extremal exchangeable pairs are in bijection with triples~$(\tube, \tube[s], \tube[s'])$ of tubes of~$\graphG$ where~$\tube[s]$ and~$\tube[s']$ are distinct tubes covered by~$\tube$ in the inclusion poset of all tubes of~$\graphG$.
The result immediately follows.
\end{proof}

The formula of \cref{prop:numberExtremalExchangeablePairsGA} can be made more explicit for specific families of graph associahedra

\begin{proposition}
The number of extreme exchangeable pairs of the nested fan~$\nestedFan(\graphG)$ is:
\begin{itemize}
\item $2^{n-2}\binom{n}{2}$ for the permutahedron (complete graph associahedron),
\item $\binom{n}{2}$ for the associahedron (path associahedron),
\item $3\binom{n}{2} - n$ for the cyclohedron (cycle associahedron),
\item $n-1+2^{n-3}\binom{n-1}{2}$ for the stellohedron (star associahedron).
\end{itemize}
\end{proposition}

\begin{proof}
For the permutahedron, choose any two vertices~$v,v'$, and complete them into a tube by selecting any subset of the~$n-2$ remaining vertices.
For the associahedron, choose any two vertices~$v,v'$, and complete them into a tube by taking the path between them.
For the cyclohedron, choose the two vertices~$v,v'$, and complete them into a tube by taking either all the cycle, or one of the two paths between~$v$ and~$v'$ (this gives three options in general, but only two when~$v,v'$ are neighbors).
For the stellohedron, choose either~$v$ as the center of the star and~$v'$ as one of the $n-1$ leaves, or $v$~and~$v'$ as leaves of the star and complete them into a tube by taking the center and any subset of the $n-3$ remaining leaves.
\end{proof}

%\begin{example}
%The formula of \cref{prop:numberExtremalExchangeablePairsGA} can be made more explicit for specific families of graph associahedra:
%\begin{itemize}
%\item the permutahedron (complete graph associahedron) has~$2^{n-2}\binom{n}{2}$ extreme exchangeable pairs (choose the two vertices~$v,v'$, and complete them into a tube by selecting any subset of the~$n-2$ remaining vertices),
%\item the associahedron (path associahedron) has~$\binom{n}{2}$ extreme exchangeable pairs (choose the two vertices~$v,v'$, and complete them into a tube by taking the path between them),
%\item the cyclohedron (cycle associahedron) has~$3\binom{n}{2} - n$ extreme exchangeable pairs (choose the two vertices~$v,v'$, and complete them into a tube by taking either all the cycle, or one of the two paths between~$v$ and~$v'$; this gives three options in general, but only two when~$v,v'$ are neighbors),
%\item the stellohedron (star associahedron) has $n-1+2^{n-3}\binom{n-1}{2}$ extreme exchangeable pairs (choose either~$v$ as the center of the star and~$v'$ as one of the $n-1$ leaves, or $v$~and~$v'$ as leaves of the star and complete them into a tube by taking the center and any subset of the $n-3$ remaining leaves).
%\end{itemize}
%\end{example}

To conclude on graph associahedra, we characterize the graphs~$\graphG$ whose nested fan has a simplicial type cone.

\begin{proposition}
The type cone~$\typeCone(\nestedFan(\graphG))$ is simplicial if and only if~$\graphG$ is a path.
\end{proposition}

\begin{proof}
Note that any tube~$\tube$ with~$|\tube| \ge 2$ has two non-disconnecting vertices when it is a path, and at least three non-disconnecting vertices otherwise (the leaves of an arbitrary spanning tree of~$\tube$).
Therefore, each tube of~$\tubes(\graphG)$ which is not a singleton contributes to at least one extremal exchangeable pairs.
We conclude that the number of extremal exchangeable pairs is at least:
\[
|\tubes(\graphG)| - |V| = |\tubes(\graphG) \ssm \{\graphG\}| - (|V|-1) = N - n,
\]
with equality if and only if all tubes of~$\graphG$ are paths, \ie if and only if~$\graphG$ is a path.
\end{proof}

\subsection{Quotientopes}

Be careful that the quotient fans are not simplicial.

\subsection{Brick polytopes}

Be careful that the brick fans are not simplicial.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliographystyle{alpha}
\bibliography{typeConeAssociahedra}
\label{sec:biblio}

\end{document}

### 2018-09-28 secondPaper/accordionComplexSurfaces.tex
typos + added reference Schroer

@@
 
-Gentle algebras are a class of finite-dimensional associative algebras over a field defined by generators and relations.
+Gentle algebras are a class of finite-dimensional associative algebras over a field, defined by generators and relations.
 Their representation theory was first systematically investigated in~\cite{ButlerRingel}, and they have been thouroughly studied since.
 Locally gentle algebras are obtained by dropping the requirement that gentle algebras be finite-dimensional.
-It turns out that their representations theory is also well-behaved \cite{Crawley-Boevey} and that these algebras are Koszul \cite{BessenrodtHolm}.
-Recently, the $\tau$-tilting theory \cite{AdachiIyamaReiten} of gentle algebra has been studied in \cite{PaluPilaudPlamondon, BrustleDouvilleMousavandThomasYildirim}.
+It turns out that their representation theory is also well-behaved \cite{Crawley-Boevey} and that these algebras are Koszul \cite{BessenrodtHolm}.
+Recently, the $\tau$-tilting theory \cite{AdachiIyamaReiten} of gentle algebras has been studied in \cite{PaluPilaudPlamondon, BrustleDouvilleMousavandThomasYildirim}.
 
@@
 Note that we \textbf{do not require} that the quotient algebra~$kQ/I$ be finite dimensional.
-The following definition is adapted from~\cite{ButlerRingel}.
+The following definition is adapted from~\cite{ButlerRingel}. We note that it is customary to consider non-finite dimensional gentle algebras in the literature, see e.g.~\cite{Schoer}.
 
@@
 
-In other words, $\bar Q\blossom$ is obtained from~$\bar Q$ by adding blossom arrow and blossom vertices at each incomplete vertex of~$\bar Q$ and by completing~$I$ accordingly.
+In other words, $\bar Q\blossom$ is obtained from~$\bar Q$ by adding blossom arrows and blossom vertices at each incomplete vertex of~$\bar Q$ and by completing~$I$ accordingly.
 Examples are represented on \fref{fig:quivers}.
@@
 
+\begin{example}
+Considering our choice of conventions, we represent the string ${\rho = \gamma\beta^{-1}\alpha^{-1}\gamma\beta^{-1}\alpha^{-1}\gamma\delta}$ as follows:
+\[
+\rho = \;\vcenter{\hbox{\includegraphics[scale=0.3]{exmString1}}}
+\]
+\end{example}
+
 \begin{notation}
-To avoid distinguishing between finite, infinite and bi-infinite words, we denote strings as products~$\rho = \prod_{i < \ell < j} \alpha_\ell$ where~$i < j \in \Z \cup \{\pm \infty\}$ and~$\alpha_\ell \in Q_0$ for all~$i < \ell < j$.
+To avoid distinguishing between finite, infinite and bi-infinite words, we denote strings as products~$\rho = \prod_{i < \ell < j} \alpha_\ell^{\epsilon_\ell}$ where~$i < j \in \Z \cup \{\pm \infty\}$, $\epsilon_\ell\in\{\pm 1\}$ and~$\alpha_\ell \in Q_1$ for all~$i < \ell < j$.
 \end{notation}
@@
 A \defn{peak walk} (resp.~\defn{deep walk}) is a walk with a unique corner (in other words, it switches orientation only once), which is a peak (resp.~deep).
-For~$a \in Q_0$, we denote by~$a_\peak$ the peak walk with peak at~$a$ and by~$a_\deep$ the deep walk with deep~at~$a$.
+For~$a \in Q_0$, we denote by~$a_\peak$ the peak walk with peak at~$a$ and by~$a_\deep$ the deep walk with deep~at~$a$ (note that those are indeed unique by gentleness).
 \end{definition}
@@
 \begin{itemize}
-\item if a face~$f$ has no edge on the boundary of~$\surface$, its dual vertex~$f\dual$ lies in the interior~of~$f$ and is a puncture of~$\bar\surface$,
+\item if a face~$f$ has no edges on the boundary of~$\surface$, its dual vertex~$f\dual$ lies in the interior~of~$f$ and is a puncture of~$\bar\surface$,
 \item if a face~$f$ has an edge on the boundary of~$\surface$, then it has exactly one such edge and its dual vertex~$f\dual$ lies on this edge.
@@
 Let~$u,v$ be the endpoints~of~$c$.
-Then~$\alpha$ cuts the cells $u\dual,v\dual$ glued along~$c\dual$ into two connected components, one containing both~endpoints~of~$\delta$.
+Then~$\alpha$ cuts the cells $u\dual,v\dual$ glued along~$c\dual$ into two connected components, one containing both~endpoints~of~$c$.
 
@@
 \begin{enumerate}[(i)]
-\item for each arrow~$\alpha \in Q_1\blossom$, consider a lozange~$L(\alpha)$ with four (oriented) sides
+\item for each arrow~$\alpha \in Q_1\blossom$, consider a lozenge~$L(\alpha)$ with four (oriented) sides
 \begin{alignat*}{2}
@@
 \end{itemize}
-The set~${{V\dual}\!\!_{\bar Q}}$ and the ${{V\dual}\!\!_{\bar Q}}$-dissection~${\dissection\dual\!\!_{\bar Q}}$ are defined dually.
+The set~${{V\dual}\!\!_{\bar Q}}$ and the ${{V\dual}\!\!_{\bar Q}}$-dissection~${\dissection\dual\!\!_{\bar Q}}$ are defined similarly by using $f\dual(\alpha)$, $\Ers{\alpha}$ and $\Ert{\alpha}$.
 \end{definition}
@@
 In the construction of~$\surface_{\bar Q}$, if two arrows~$\alpha$ and~$\beta$ of~$\bar Q \blossom$ are such that~${t(\alpha) = s(\beta)}$ and~${\alpha\beta \in I\blossom}$, then the vertices~$v(\alpha)$ and~$v(\beta)$ are identified on the surface.
-Thus, any two arrows of a given path contribute the same vertex of~$V_{\bar Q}$, so~$V_{\bar Q}$ is in bijection with the set of maximal paths in~$\bar Q\blossom$.
+Thus, any two arrows of a given path contribute to the same vertex of~$V_{\bar Q}$, so~$V_{\bar Q}$ is in bijection with the set of maximal paths in~$\bar Q\blossom$.
 
@@
 \item The set~$V_{\bar Q}$ has one vertex for each straight walk in~$\bar Q$ (equivalently, for each maximal path in~$\bar Q$).
-      Finite straight walks yield vertices on the boundary of~$\surface_{\bar Q}$, while infinite cyclic straight walks in~$\bar Q$ yield punctures~$\surface_{\bar Q}$ in~$V_{\bar Q}$.
+      Finite straight walks yield vertices on the boundary of~$\surface_{\bar Q}$, while infinite cyclic straight walks in~$\bar Q$ yield punctures of~$\surface_{\bar Q}$ in~$V_{\bar Q}$.
       We denote by~$p$ the number of infinite cyclic straight walks in~$\bar Q$.
@@
       \]
-      where~$b$ is the number of boundary components (see above for a way to compute~$b$) and~$p$ the number of punctures (\ie infinite straight walks in~$\bar Q$ and in~$\bar Q\koszul$).
+      where~$b$ is the number of boundary components (see above for a way to compute~$b$) and~$p + p\dual$ the number of punctures (\ie infinite straight walks in~$\bar Q$ and in~$\bar Q\koszul$).
       Indeed, ${2g = 2-\chi(\surface_{\bar Q})}$, where~$\chi(\surface_{\bar Q})$ is the Euler characteristic of~$\surface_{\bar Q}$.
@@
 Since~$|Q_1| = |Q_0|-1$, the corresponding surfaces are disks ($1$ boundary component, no puncture and genus~$0$).
-Two examples are represented in \fref{fig:reversedPathsSurfaces}.
+Two examples are represented in \fref{fig:CambrianPathsSurfaces}.
 Note that the dissection~$\dissection_{\bar Q}$ is a triangulation with no internal triangles, and the orientation of~$\bar Q$ indicates how to glue these triangles.
@@
 An oriented cycle~$c$ corresponds to a puncture in~$\dissection_{\bar Q}$.
-Let~$\gamma = \curveof(\omega)$.  The fact that~$\omega$ contains~$c$ translates to the fact that~$\gamma$ makes one full circle around the correponding puncture.
+Let~$\gamma = \curveof(\omega)$.  The fact that~$\omega$ contains~$c$ translates to the fact that~$\gamma$ makes one full circle around the corresponding puncture.
 
@@
 \begin{proof}[Proof of Proposition~\ref{prop:facetsAreFinite}]
-If~$\NKC$, respectively~$\NCC$, admits an infinite face, then all subsets of this face are also faces, so~$\NKC$, respectively~$\NCC$, admits faces of arbitrary finite cardinality.
+If~$\NKC$, respectively~$\NCC$, admits an infinite face, then all subsets of this face are also faces, so~$\NKC$, respectively~$\NCC$, admits faces of arbitrarily large finite cardinality.
 This contradicts Lemma \ref{lemm:facesAreBounded}.
@@
 
-A simplicial complex is \defn{thin} if each of its codimension~$1$ faces is contained in exaclty two facets.
+A simplicial complex is \defn{thin} if each of its codimension~$1$ face is contained in exaclty two facets.
 We state the following results, which generalize \cite[Prop.~2.33 \& Cor.~2.35]{PaluPilaudPlamondon}, whose proofs apply without change.
@@
 \end{proposition}
-The walk~$\omega'$ of Proposition \ref{prop:flip} is the \defn{flip} or \defn{mutation} of~$F$ at~$\omega$.
+The facet obtained from~$F$ by replacing the walk~$\omega$ by the walk~$\omega'$ of Proposition \ref{prop:flip} is the \defn{flip} or \defn{mutation} of~$F$ at~$\omega$.
 The flip is \defn{increasing} if~$\sigma$ is on top of~$\omega$, and \defn{decreasing} otherwise.
@@
 \label{coro:thin}
-The non-kissing complex~$\RNKC$ is thin and is thus a pseudomanifold without boundary.
+The reduced non-kissing complex~$\RNKC$ is thin and is thus a pseudomanifold without boundary.
 \end{corollary}
@@
 \]
-where~$\distinguishedString{\omega}{F}$ and~$\distinguishedArrows{\omega}{F}$ are the distinguished arrows of~$\omega$ in~$F$ (see Definition~\ref{def:distinguishedWalksAndArrows}).
+where~$\distinguishedString{\omega}{F}$ is the distinguished string and~$\distinguishedArrows{\omega}{F}$ are the distinguished arrows of~$\omega$ in~$F$ (see Definition~\ref{def:distinguishedWalksAndArrows}).
 The \defn{$\b{c}$-vector} of a walk~$\omega$ of~$F$ is the vector~${\cvector{\omega}{F} \in \R^{Q_0}}$ defined by
@@
 Our objective is now to interpret the three families of vectors of Section~\ref{subsec:gcdVectorsWalks} in terms of accordions and slaloms on the surface.
-According to Remark~\ref{rem:propertiesSurface}\,(\eqref{item:edges}), each vertex~$a$ of~$Q$ corresponds to an edge~$\edgeof(a)$ in the dissection~$\dissection_{\bar Q}$ and  to an edge~$\dualedgeof(a) = \edgeof(a)\dual$ in the dual dissection~${\dissection\dual\!\!_{\bar Q}}$.
+According to Remark~\ref{rem:propertiesSurface}\,\eqref{item:edges}, each vertex~$a$ of~$Q$ corresponds to an edge~$\edgeof(a)$ in the dissection~$\dissection_{\bar Q}$ and  to an edge~$\dualedgeof(a) = \edgeof(a)\dual$ in the dual dissection~${\dissection\dual\!\!_{\bar Q}}$.
 Recall moreover from Lemma~\ref{lemm:curveOfAWalkIsAccordion} and Proposition~\ref{prop:accordionsSlaloms} that each non-kissing walk~$\omega$ in~$\bar Q$ corresponds to a curve~$\curveof(\omega)$ that is both a $\dissection$-accordion and a $\dissection\dual$-slalom.
@@
 Call \defn{distinguished subcurve} of~$\curveof(\omega)$ in~$\curveof(F)$ the part of~$\curveof(\omega)$ which lies strictly between the two angles of~$\dissection$ (or of~$\dissection\dual$) where~$\curveof(\omega)$ is maximal (see Remark~\ref{rem:countercurrentOrderOnSurface}).
-For a vertex~$a \in Q_0$, the $a$-th entry of the $\b{c}$-vector~$\cvector{\omega}{F}$ is up to the sign given by:
+For a vertex~$a \in Q_0$, the $a$-th entry of the $\b{c}$-vector~$\cvector{\omega}{F}$ is, up to the sign, given by:
 \begin{enumerate}[(i)]
@@
 \label{prop:dVectorsSurface}
-Denote by~$X_\deep \eqdef \set{\curveof(a_\peak)}{a \in Q_0}$ the deep facet of the non-crossing complex obtained by slightly rotating~$\dissection_{\bar Q}$ counterclockwise as described in Example~\ref{exm:peakDeepFacets}.
-For a walk~$\omega$ of~$\bar Q$ and a vertex~$a \in Q_0$, the $a$-th entry of the $\b{d}$-vector~$\dvector{\omega}$ is either~$-1$ if~$\omega = a_\peak$ or the number of crossings of the curve~$\gamma(\omega)$ with the edge~$\curveof(a_\peak)$ of~$X_\deep$ corresponding to~$a$.
+Denote by~$X_\deep \eqdef \set{\curveof(a_\deep)}{a \in Q_0}$ the deep facet of the non-crossing complex obtained by slightly rotating~$\dissection_{\bar Q}$ counterclockwise as described in Example~\ref{exm:peakDeepFacets}.
+For a walk~$\omega$ of~$\bar Q$ and a vertex~$a \in Q_0$, the $a$-th entry of the $\b{d}$-vector~$\dvector{\omega}$ is either~$-1$ if~$\omega = a_\peak$ or the number of crossings of the curve~$\gamma(\omega)$ with the edge~$\curveof(a_\deep)$ of~$X_\deep$ corresponding to~$a$.
 \end{proposition}

### 2018-10-05 secondPaper/accordionComplexSurfaces.tex
Schroer
corrections second paper and more on type cones

@@
 
+\vspace*{-1cm}
 \maketitle
+\vspace{-.5cm}
 
@@
 
-\enlargethispage{.2cm}
+\enlargethispage{.4cm}
 We first quickly review the definition of the non-kissing complex of a gentle bound quiver following the presentation of~\cite{PaluPilaudPlamondon} and extend it to locally gentle bound quivers.
@@
 Note that we \textbf{do not require} that the quotient algebra~$kQ/I$ be finite dimensional.
-The following definition is adapted from~\cite{ButlerRingel}. We note that it is customary to consider non-finite dimensional gentle algebras in the literature, see e.g.~\cite{Schoer}.
+The following definition is adapted from~\cite{ButlerRingel}. We note that it is customary to consider non-finite dimensional gentle algebras in the literature, see e.g.~\cite{Schroer}.
 
@@
 \begin{example}
-Considering our choice of conventions, we represent the string ${\rho = \gamma\beta^{-1}\alpha^{-1}\gamma\beta^{-1}\alpha^{-1}\gamma\delta}$ as follows:
+With our choice of conventions, we represent the string ${\gamma\beta^{-1}\alpha^{-1}\gamma\beta^{-1}\alpha^{-1}\gamma\delta}$ by
 \[
-\rho = \;\vcenter{\hbox{\includegraphics[scale=0.3]{exmString1}}}
+\;\vcenter{\hbox{\includegraphics[scale=0.3]{exmString1}}}
 \]
@@
 \begin{notation}
-To avoid distinguishing between finite, infinite and bi-infinite words, we denote strings as products~$\rho = \prod_{i < \ell < j} \alpha_\ell^{\epsilon_\ell}$ where~$i < j \in \Z \cup \{\pm \infty\}$, $\epsilon_\ell\in\{\pm 1\}$ and~$\alpha_\ell \in Q_1$ for all~$i < \ell < j$.
+To avoid distinguishing between finite, infinite and bi-infinite words, we denote strings as products~$\rho = \prod_{i < \ell < j} \alpha_\ell^{\varepsilon_\ell}$ where~$i < j \in \Z \cup \{\pm \infty\}$, $\varepsilon_\ell\in\{\pm 1\}$ and~$\alpha_\ell \in Q_1$ for all~$i < \ell < j$.
 \end{notation}
@@
 
-A simplicial complex is \defn{thin} if each of its codimension~$1$ face is contained in exaclty two facets.
+A simplicial complex is \defn{thin} if each codimension~$1$ face is contained in exactly two facets.
 We state the following results, which generalize \cite[Prop.~2.33 \& Cor.~2.35]{PaluPilaudPlamondon}, whose proofs apply without change.

### 2018-10-05 thridPaper/draft/typeConeAssociahedra.tex
corrections second paper and more on type cones

@@
 
-One important observation is that it seems there is ``one extremal exchangeable pair for each positive root'' (or equivalently each positive $c$-vector), meaning that for each positive root~$\beta \in \Phi^+$, there is precisely one extremal exchangeable pair~$\{x,x'\}$ of cluster variables for which the flip of~$x$ to~$x'$ (for any pair of clusters~$\{X,X'\}$ with~$X \ssm \{x\} = X' \ssm \{x'\}$) is in the direction of~$\beta$.
+One important observation is that it seems there is one extremal exchangeable pair for each positive $c$-vector, meaning that for each positive $c$-vector~$\beta$, there is precisely one extremal exchangeable pair~$\{x,x'\}$ of cluster variables for which the flip of~$x$ to~$x'$ (for any pair of clusters~$\{X,X'\}$ with~$X \ssm \{x\} = X' \ssm \{x'\}$) is in the direction of~$\beta$.
 The goal is thus to determine for each positive root which exchangeable pair is extremal.
+This should be done using the Auslander-Reiten quiver to construct two cluster variables from a $c$-vector (see the next paragraph for the idea).
 
@@
 Note however that
-\begin{itemize}
+\begin{enumerate}
 \item exchangeable pairs might kiss along additional non-distinguishable strings (example: just a loop),
 \item non-exchangeable walks might kiss along a single distinguishable string (example: see the cyclic triangle in~\cite{PaluPilaudPlamondon}).
-\end{itemize}
+\end{enumerate}
 
-\bigskip
 We have some conjectures on what the extremal exchangeable pairs should be.
 One clear (but a bit empty) result is that extremal exchangeable pairs correspond in the Auslander-Reiten quiver to rectangles whose four vertices are non-self-kissing and that cannot be tiled with smaller such rectangles.
+
+We checked on some (but probably not enough) small gentle quivers the following properties:
+\begin{enumerate}
+\item Any $c$-vector (\ie distinguishable string) is the direction of at least one extremal exchangeable pair.
+\item Consider a distinguishable string~$\sigma$.
+Let~$\omega$ (resp.~$\omega'$) be the walk obtained from~$\sigma$ by adding two hooks (resp.~two cohooks) at the endpoints of~$\sigma$.
+If the walks~$\omega$ and~$\omega'$ are non-self-kissing and exchangeable, then they form the unique extremal exchangeable pair directed by~$\sigma$.
+These extremal exchangeable pairs correspond to meshes of the Auslander-Reiten quiver.
+\item Otherwise, $\sigma$ is the direction to one or more extremal exchangeable pairs obtained by moving further in the Auslander-Reiten quiver (this is really unclear at the moment).
+\end{enumerate}
 

### 2018-10-08 secondPaper/accordionComplexSurfaces.tex
spacing

@@
 
-\vspace*{-1cm}
+\vspace*{-1.3cm}
 \maketitle
-\vspace{-.5cm}
+\vspace{-.7cm}
 
 \section{Introduction}
+
+\enlargethispage{.1cm}
 The aim of this paper is to prove that two combinatorial objects, called the \emph{non-kissing complex} and the \emph{non-crossing complex}, are isomorphic.
@@
 
-\enlargethispage{.4cm}
 We first quickly review the definition of the non-kissing complex of a gentle bound quiver following the presentation of~\cite{PaluPilaudPlamondon} and extend it to locally gentle bound quivers.
@@
 The algebra~$kQ/I$ is called a \defn{locally gentle algebra}.
-A \defn{gentle bound quiver} is a locally gentle bound quiver~$\bar Q$ such that the algebra $kQ/I$ is finite-dimensional; the algebra is then called a \defn{gentle algebra}.
+A \defn{gentle bound quiver} is a locally gentle bound quiver~$\bar Q$ such that the algebra $kQ/I$ is finite-dimensional; $kQ/I$ is then a \defn{gentle algebra}.
 \end{definition}
@@
 
+\begin{example}
+With our choice of conventions, we represent the string ${\gamma\beta^{-1}\alpha^{-1}\gamma\beta^{-1}\alpha^{-1}\gamma\delta}$ by
+\[
+\;\vcenter{\hbox{\includegraphics[scale=0.3]{exmString1}}}
+\]
+\end{example}
+
 \begin{definition}
@@
 
-\begin{example}
-With our choice of conventions, we represent the string ${\gamma\beta^{-1}\alpha^{-1}\gamma\beta^{-1}\alpha^{-1}\gamma\delta}$ by
-\[
-\;\vcenter{\hbox{\includegraphics[scale=0.3]{exmString1}}}
-\]
-\end{example}
-
 \begin{notation}
-To avoid distinguishing between finite, infinite and bi-infinite words, we denote strings as products~$\rho = \prod_{i < \ell < j} \alpha_\ell^{\varepsilon_\ell}$ where~$i < j \in \Z \cup \{\pm \infty\}$, $\varepsilon_\ell\in\{\pm 1\}$ and~$\alpha_\ell \in Q_1$ for all~$i < \ell < j$.
+To avoid distinguishing between finite and (bi-)infinite words, we denote strings as products~$\rho = \prod_{i < \ell < j} \alpha_\ell^{\varepsilon_\ell}$ where~$i < j \in \Z \cup \{\pm \infty\}$, $\varepsilon_\ell\in\{\pm 1\}$ and~$\alpha_\ell \in Q_1$ for all~$i < \ell < j$.
 \end{notation}
@@
 
-\enlargethispage{.1cm}
 We now temporarily switch topic and present the accordion complex and the slalom complex of a pair of dual dissections of an orientable surface.
@@
 
+\enlargethispage{.1cm}
 Before defining accordions and slaloms, we need a strong notion of pairs of dual dissections of an orientable surface.

### 2018-10-12 thirdPaper/draft/typeConeAssociahedra.tex
Sections 2.2.1 and 2.2.2

--- 2018-10-05 thridPaper/draft/typeConeAssociahedra.tex
@@
 \usepackage[noabbrev,capitalise]{cleveref}
+\usepackage[normalem]{ulem}
 \usepackage{marginnote}
@@
 \newcommand{\red}{\color{red}} % red command
+\newcommand{\blue}{\color{blue}} % blue command
+\newcommand{\orange}{\color{orange}} % orange command
 \newcommand{\green}{\color{green}} % green command
@@
 \newcommand{\defn}[1]{\textsl{\darkblue #1}} % emphasis of a definition
-\newcommand{\para}[1]{\medskip\noindent\textit{#1.}} % paragraph
+\newcommand{\para}[1]{\medskip\noindent\uline{\textit{#1.}}} % paragraph
 \renewcommand{\topfraction}{1} % possibility to have one page of pictures
@@
 
-% polytopes
-\newcommandx{\Asso}[2][1=\bar Q,2={}]{\mathsf{Asso}^{#2}(#1)} % associahedron
-\newcommandx{\Zono}[2][1=\bar Q,2={}]{\mathsf{Zono}^{#2}(#1)} % zonotope
+% geometry
+\newcommandx{\Asso}[2][1=n,2={}]{\mathsf{Asso}^{#2}(#1)} % associahedron
+\newcommandx{\Zono}[2][1=n,2={}]{\mathsf{Zono}^{#2}(#1)} % zonotope
 \newcommand{\Fan}{\mathcal{F}} % fan
 \newcommand{\multiplicityVector}{\b{m}} % multiplicity vector
+\newcommandx{\ray}[1][1=r]{\b{#1}} % ray
+\newcommandx{\rays}[1][1=R]{\b{#1}} % rays
+\newcommand{\gvector}[1]{\b{g}(#1)} % g-vector of the path #1
+\newcommand{\gvectors}[1]{\b{g}(#1)} % g-vectors of the paths #1
+\newcommandx{\gvectorFan}[1][1=\quiver]{\mathcal{F}(#1)} % g-vector fan
 
@@
 
+% Gentle associahedra
+\newcommand{\quiver}{\bar Q} % quiver
+\newcommand{\blossom}{^\text{\ding{96}}} % blossom
+\newcommandx{\strings}[1][1=\quiver]{\mathcal{S}(#1)} % strings
+\newcommandx{\distinguishableStrings}[1][1=\quiver]{\mathcal{S}_\mathrm{dist}(#1)} % distinguishable strings
+\newcommandx{\walks}[1][1=\quiver]{\mathcal{W}(#1)} % walks
+\newcommandx{\properWalks}[1][1=\quiver]{\mathcal{W}_\mathrm{prop}(#1)} % proper walks
+\renewcommand{\top}{\mathrm{top}} % top
+\newcommand{\bottom}{\mathrm{bot}} % bottom
+\newcommandx{\NKC}[1][1=\quiver]{\mathcal{NK}(#1)} % non-kissing complex
+\newcommandx{\RNKC}[1][1=\quiver]{\mathcal{RNK}(#1)} % reduced non-kissing complex
+\newcommand{\peaks}[1]{\mathsf{peaks}(#1)} % peaks
+\newcommand{\deeps}[1]{\mathsf{deeps}(#1)} % deeps
+\newcommand{\KN}{\textsc{kn}} % Kissing Number
+\newcommand{\hL}{\text{\rotatebox[origin=c]{180}{\checked}}}
+\newcommand{\hR}{\text{\rotatebox[origin=c]{180}{\reflectbox{\checked}}}}
+\newcommand{\cL}{\text{\reflectbox{\checked}}}
+\newcommand{\cR}{\text{\checked}}
+\newcommand{\hh}[1]{\hL#1\hR} % hook - hook
+\newcommand{\cc}[1]{\cL#1\cR} % cohook - cohook
+\newcommand{\hc}[1]{\hL#1\cR} % hook - cohook
+\newcommand{\ch}[1]{\cL#1\hR} % cohook - hook
+
 % Graph associahedra
-\newcommand{\ground}{\mathrm{V}} % ground set
-\newcommandx{\graphG}[1][1=G]{\mathrm{#1}} % graph
+\newcommand{\ground}{V} % ground set
+\newcommandx{\graphG}[1][1=G]{#1} % graph
 \newcommandx{\tube}[1][1=t]{\mathsf{#1}} % tube
@@
 \newcommand{\nestedComplex}{\mathcal{N}} % nested complex
-\newcommand{\nestedFan}{\mathcal{F}} % nested fan
 \newcommand{\nonDisconnecting}{\mathrm{nd}} % non-disconnecting vertices
+\newcommand{\neighbors}{\mathrm{ne}} % neighbors
 
-% SPECIFIC NON-KISSING COMPLEX
-
-% COMBINATORICS
-% quiver
-\newcommand{\blossom}{^\text{\ding{96}}} % blossom
-
-% walks
-\newcommand{\peaks}[1]{\mathsf{peaks}(#1)} % peaks
-\newcommand{\deeps}[1]{\mathsf{deeps}(#1)} % deeps
-\newcommand{\distinguishedWalk}[2]{\mathsf{dw}(#1,#2)} % distinguished walk
-\newcommand{\distinguishedArrows}[2]{\mathsf{da}(#1,#2)} % distinguished arrows
-\newcommand{\distinguishedString}[2]{\mathsf{ds}(#1,#2)} % distinguished string
-\newcommand{\distinguishedSign}[2]{\varepsilon(#1,#2)} % distinguished sign
-
-% non-kissing complex, lattice, flip graph
-\newcommand{\kn}{\kappa} % kissing number
-\newcommand{\KN}{\textsc{kn}} % Kissing Number
-\newcommandx{\NKC}[1][1=\bar Q]{\mathcal{K}_{\mathrm{nk}}(#1)} % non-kissing complex
-\newcommandx{\RNKC}[1][1=\bar Q]{\mathcal{C}_{\mathrm{nk}}(#1)} % non-kissing complex
-\newcommandx{\NKL}[1][1=\bar Q]{\mathcal{L}_{\mathrm{nk}}(#1)} % non-kissing lattice
-\newcommandx{\NKG}[1][1=\bar Q]{\mathcal{G}_{\mathrm{nk}}(#1)} % non-kissing flip graph
-\newcommandx{\NFC}[1][1=\bar Q]{\mathcal{C}_{\mathrm{nf}}(#1)} % non-friendly complex
-\newcommand{\peak}{\mathrm{peak}} % bottom dissection
-\newcommand{\deep}{\mathrm{deep}} % top dissection
-\newcommand{\reversed}[1]{#1^{\mathrm{rev}}} % reverse all arrows
-\renewcommand{\top}{\mathrm{top}} % top
-\newcommand{\bottom}{\mathrm{bot}} % bottom
-\newcommand{\walk}{\operatorname{\omega}} % walk (of a curve)
-
-% accordion and slalom complexes
-\newcommand{\surface}{\mathcal{S}} % an orientable surface
-\newcommand{\dual}{^*} % duality
-\newcommand{\dissection}{\mathrm{D}} % dissection of a marked surface
-\newcommand{\vertices}{\mathcal{V}} % vertices of a dissection
-\newcommand{\edges}{\mathcal{E}} % edges of a dissection
-\newcommand{\faces}{\mathcal{F}} % faces of a dissection
-\renewcommandx{\AC}[1][1=\dissection]{\mathcal{K}_{\mathrm{acc}}(#1)} % accordion complex
-\newcommandx{\RAC}[1][1=\dissection]{\mathcal{C}_{\mathrm{acc}}(#1)} % reduced accordion complex
-\newcommandx{\SC}[1][1=\dissection\dual]{\mathcal{K}_{\mathrm{sla}}(#1)} % slalom complex
-\newcommandx{\RSC}[1][1=\dissection\dual]{\mathcal{C}_{\mathrm{sla}}(#1)} % reduced slalom complex
-\newcommandx{\NCC}[1][1={\dissection, \dissection\dual}]{\mathcal{K}_{\mathrm{nc}}(#1)} % non-crossing complex
-\newcommandx{\RNCC}[1][1={\dissection, \dissection\dual}]{\mathcal{C}_{\mathrm{nc}}(#1)} % non-crossing complex
-\newcommand{\curveof}{\operatorname{\gamma}} % curve (of a walk)
-\newcommand{\edgeof}{\operatorname{\varepsilon}} % arc of a vertex
-\newcommand{\dualedgeof}{\operatorname{\varepsilon}\dual} % dual arc of a vertex
-\DeclareRobustCommand{\SSS}{\reflectbox{$\mathsf{Z}$}} % S
-\DeclareRobustCommand{\ZZZ}{\mathsf{Z}} % Z
-\newcommand{\vnext}[1]{#1_{\operatorname{next}}} % next point on the boundary of the surface
-\newcommand{\vprevious}[1]{#1_{\operatorname{prev}}} % previous point on the boundary of the surface
-
-% lattices
-\newcommand{\meet}{\wedge} % meet
-\newcommand{\join}{\vee} % join
-\newcommand{\bigMeet}{\bigwedge} % meet
-\newcommand{\bigJoin}{\bigvee} % join
-\newcommand{\closure}[1]{#1^{\mathrm{cl}}} % closure operator
-\newcommand{\coclosure}[1]{#1^{\mathrm{cocl}}} % coclosure operator
-\newcommand{\uclosure}[1]{#1^{\underline{\mathrm{cl}}}} % loop free closure operator
-\newcommand{\Bicl}[1]{\mathsf{Bic}(#1)} % biclosed sets
-\newcommand{\projDown}{\pi_\downarrow} % down projection map
-\newcommand{\projUp}{\pi^\uparrow} % up projection map
-\newcommand{\JI}{\mathsf{JI}} % join-irreducible
-\newcommand{\MI}{\mathsf{MI}} % meet-irreducible
-\newcommand{\Cong}{\mathsf{Cong}} % congruence lattice
-\newcommand{\con}{\mathrm{con}} % congruence contracting a cover relation
-\newcommand{\ji}{\mathsf{ji}} % join irreducible
-\newcommand{\mi}{\mathsf{mi}} % meet irreducible
-
-% GEOMETRY
-% d-vectors
-\newcommand{\dvector}[1]{\mathbf{d}(#1)} % d-vector of the path #1
-\newcommand{\dvectors}[1]{\mathbf{d}(#1)} % d-vectors of the paths #1
-\newcommandx{\dvectorFan}[1][1=\bar Q]{\mathcal{F}^\mathbf{d}(#1)} % d-vector fan
-% g-vectors
-\newcommand{\gvector}[1]{\mathbf{g}(#1)} % g-vector of the path #1
-\newcommand{\gvectors}[1]{\mathbf{g}(#1)} % g-vectors of the paths #1
-\newcommandx{\gvectorFan}[1][1=\bar Q]{\mathcal{F}^\mathbf{g}(#1)} % g-vector fan
-% c-vectors
-\newcommand{\cvector}[2]{\mathbf{c}(#1 \in #2)} % c-vector of the path #1 in the facet #2
-\newcommand{\cvectors}[1]{\mathbf{c}(#1)} % c-vectors of the paths #1
-\newcommandx{\allcvectors}[1][1=\bar Q]{\mathbf{C}(#1)} % all c-vectors with respect to the initial cluster #1
-\newcommandx{\cvectorFan}[1][1=\bar Q]{\mathcal{F}^\mathbf{c}(#1)} % fan of hyperplanes orthogonal to all c-vectors
-% points, hyperplanes, half-spaces
-\newcommand{\point}[1]{\mathbf{p}(#1)} % vertex of the grid associahedron corresponding to the cluster #1
-\newcommandx{\ray}[1][1=r]{\mathbf{#1}} % ray
-\newcommandx{\rays}[1][1=R]{\mathbf{#1}} % rays
-\newcommand{\hs}{\mathbf{H}^{\le}} % half space
-\newcommand{\HS}[1]{\mathbf{H}^{\le}(#1)} % half space
-\newcommand{\hyp}{\mathbf{H}^{=}} % hyperplane
-\newcommand{\Hyp}[1]{\mathbf{H}^{=}(#1)} % hyperplane
-\newcommand{\fix}[1]{\mathrm{Fix}(#1)} % fix space
-
-% ALGEBRA
-\newcommand{\Hom}[1]{\operatorname{{\rm Hom}}_{#1}}
-\newcommand{\Ext}[1]{\operatorname{{\rm Ext}}_{#1}}
-\newcommandx{\AR}[1][1=\bar Q]{\mathrm{AR}(#1)} % Auslander-Reiten quiver
-\newcommandx{\tTC}[1][1=\bar Q]{\mathcal{K}^{\textrm{s$\tau$-tilt}}(#1)} % tau-tilting complex
-\newcommand{\rep}{\operatorname{{\rm rep}}}
-\newcommand{\proj}{\operatorname{{\rm proj}}}
-\newcommand{\koszul}{^!} % duality
+%% SPECIFIC NON-KISSING COMPLEX
+%
+%% COMBINATORICS
+%% quiver
+%
+%% walks
+%\newcommand{\peaks}[1]{\mathsf{peaks}(#1)} % peaks
+%\newcommand{\deeps}[1]{\mathsf{deeps}(#1)} % deeps
+%\newcommand{\distinguishedWalk}[2]{\mathsf{dw}(#1,#2)} % distinguished walk
+%\newcommand{\distinguishedArrows}[2]{\mathsf{da}(#1,#2)} % distinguished arrows
+%\newcommand{\distinguishedString}[2]{\mathsf{ds}(#1,#2)} % distinguished string
+%\newcommand{\distinguishedSign}[2]{\varepsilon(#1,#2)} % distinguished sign
+%
+%% non-kissing complex, lattice, flip graph
+%\newcommand{\kn}{\kappa} % kissing number
+%\newcommand{\KN}{\textsc{kn}} % Kissing Number
+%\newcommandx{\NKC}[1][1=\quiver]{\mathcal{K}_{\mathrm{nk}}(#1)} % non-kissing complex
+%\newcommandx{\RNKC}[1][1=\quiver]{\mathcal{C}_{\mathrm{nk}}(#1)} % non-kissing complex
+%\newcommandx{\NKL}[1][1=\quiver]{\mathcal{L}_{\mathrm{nk}}(#1)} % non-kissing lattice
+%\newcommandx{\NKG}[1][1=\quiver]{\mathcal{G}_{\mathrm{nk}}(#1)} % non-kissing flip graph
+%\newcommandx{\NFC}[1][1=\quiver]{\mathcal{C}_{\mathrm{nf}}(#1)} % non-friendly complex
+%\newcommand{\peak}{\mathrm{peak}} % bottom dissection
+%\newcommand{\deep}{\mathrm{deep}} % top dissection
+%\newcommand{\reversed}[1]{#1^{\mathrm{rev}}} % reverse all arrows
+%\renewcommand{\top}{\mathrm{top}} % top
+%\newcommand{\bottom}{\mathrm{bot}} % bottom
+%\newcommand{\walk}{\operatorname{\omega}} % walk (of a curve)
+%
+%% accordion and slalom complexes
+%\newcommand{\surface}{\mathcal{S}} % an orientable surface
+%\newcommand{\dual}{^*} % duality
+%\newcommand{\dissection}{\mathrm{D}} % dissection of a marked surface
+%\newcommand{\vertices}{\mathcal{V}} % vertices of a dissection
+%\newcommand{\edges}{\mathcal{E}} % edges of a dissection
+%\newcommand{\faces}{\mathcal{F}} % faces of a dissection
+%\renewcommandx{\AC}[1][1=\dissection]{\mathcal{K}_{\mathrm{acc}}(#1)} % accordion complex
+%\newcommandx{\RAC}[1][1=\dissection]{\mathcal{C}_{\mathrm{acc}}(#1)} % reduced accordion complex
+%\newcommandx{\SC}[1][1=\dissection\dual]{\mathcal{K}_{\mathrm{sla}}(#1)} % slalom complex
+%\newcommandx{\RSC}[1][1=\dissection\dual]{\mathcal{C}_{\mathrm{sla}}(#1)} % reduced slalom complex
+%\newcommandx{\NCC}[1][1={\dissection, \dissection\dual}]{\mathcal{K}_{\mathrm{nc}}(#1)} % non-crossing complex
+%\newcommandx{\RNCC}[1][1={\dissection, \dissection\dual}]{\mathcal{C}_{\mathrm{nc}}(#1)} % non-crossing complex
+%\newcommand{\curveof}{\operatorname{\gamma}} % curve (of a walk)
+%\newcommand{\edgeof}{\operatorname{\varepsilon}} % arc of a vertex
+%\newcommand{\dualedgeof}{\operatorname{\varepsilon}\dual} % dual arc of a vertex
+%\DeclareRobustCommand{\SSS}{\reflectbox{$\mathsf{Z}$}} % S
+%\DeclareRobustCommand{\ZZZ}{\mathsf{Z}} % Z
+%\newcommand{\vnext}[1]{#1_{\operatorname{next}}} % next point on the boundary of the surface
+%\newcommand{\vprevious}[1]{#1_{\operatorname{prev}}} % previous point on the boundary of the surface
+%
+%% lattices
+%\newcommand{\meet}{\wedge} % meet
+%\newcommand{\join}{\vee} % join
+%\newcommand{\bigMeet}{\bigwedge} % meet
+%\newcommand{\bigJoin}{\bigvee} % join
+%\newcommand{\closure}[1]{#1^{\mathrm{cl}}} % closure operator
+%\newcommand{\coclosure}[1]{#1^{\mathrm{cocl}}} % coclosure operator
+%\newcommand{\uclosure}[1]{#1^{\underline{\mathrm{cl}}}} % loop free closure operator
+%\newcommand{\Bicl}[1]{\mathsf{Bic}(#1)} % biclosed sets
+%\newcommand{\projDown}{\pi_\downarrow} % down projection map
+%\newcommand{\projUp}{\pi^\uparrow} % up projection map
+%\newcommand{\JI}{\mathsf{JI}} % join-irreducible
+%\newcommand{\MI}{\mathsf{MI}} % meet-irreducible
+%\newcommand{\Cong}{\mathsf{Cong}} % congruence lattice
+%\newcommand{\con}{\mathrm{con}} % congruence contracting a cover relation
+%\newcommand{\ji}{\mathsf{ji}} % join irreducible
+%\newcommand{\mi}{\mathsf{mi}} % meet irreducible
+%
+%% GEOMETRY
+%% d-vectors
+%\newcommand{\dvector}[1]{\mathbf{d}(#1)} % d-vector of the path #1
+%\newcommand{\dvectors}[1]{\mathbf{d}(#1)} % d-vectors of the paths #1
+%\newcommandx{\dvectorFan}[1][1=\quiver]{\mathcal{F}^\mathbf{d}(#1)} % d-vector fan
+%% g-vectors
+%\newcommand{\gvector}[1]{\mathbf{g}(#1)} % g-vector of the path #1
+%\newcommand{\gvectors}[1]{\mathbf{g}(#1)} % g-vectors of the paths #1
+%\newcommandx{\gvectorFan}[1][1=\quiver]{\mathcal{F}^\mathbf{g}(#1)} % g-vector fan
+%% c-vectors
+%\newcommand{\cvector}[2]{\mathbf{c}(#1 \in #2)} % c-vector of the path #1 in the facet #2
+%\newcommand{\cvectors}[1]{\mathbf{c}(#1)} % c-vectors of the paths #1
+%\newcommandx{\allcvectors}[1][1=\quiver]{\mathbf{C}(#1)} % all c-vectors with respect to the initial cluster #1
+%\newcommandx{\cvectorFan}[1][1=\quiver]{\mathcal{F}^\mathbf{c}(#1)} % fan of hyperplanes orthogonal to all c-vectors
+%% points, hyperplanes, half-spaces
+%\newcommand{\point}[1]{\mathbf{p}(#1)} % vertex of the grid associahedron corresponding to the cluster #1
+%\newcommandx{\ray}[1][1=r]{\mathbf{#1}} % ray
+%\newcommandx{\rays}[1][1=R]{\mathbf{#1}} % rays
+%\newcommand{\hs}{\mathbf{H}^{\le}} % half space
+%\newcommand{\HS}[1]{\mathbf{H}^{\le}(#1)} % half space
+%\newcommand{\hyp}{\mathbf{H}^{=}} % hyperplane
+%\newcommand{\Hyp}[1]{\mathbf{H}^{=}(#1)} % hyperplane
+%\newcommand{\fix}[1]{\mathrm{Fix}(#1)} % fix space
+%
+%% ALGEBRA
+%\newcommand{\Hom}[1]{\operatorname{{\rm Hom}}_{#1}}
+%\newcommand{\Ext}[1]{\operatorname{{\rm Ext}}_{#1}}
+%\newcommandx{\AR}[1][1=\quiver]{\mathrm{AR}(#1)} % Auslander-Reiten quiver
+%\newcommandx{\tTC}[1][1=\quiver]{\mathcal{K}^{\textrm{s$\tau$-tilt}}(#1)} % tau-tilting complex
+%\newcommand{\rep}{\operatorname{{\rm rep}}}
+%\newcommand{\proj}{\operatorname{{\rm proj}}}
+%\newcommand{\koszul}{^!} % duality
 
@@
 \]
-These coefficients are \apriori{} defined up to rescaling, but we additionally fix the rescaling so that~${\coefficient[\ray][\rays][\rays'] + \coefficient[\ray'][\rays][\rays'] = 1}$.
+These coefficients are \apriori{} defined up to rescaling, but we additionally fix the rescaling so that~${\coefficient[\ray][\rays][\rays'] + \coefficient[\ray'][\rays][\rays'] = 2}$ (this convention is arbitrary, but will be convenient in \cref{sec:applications}).
 \end{notation}
@@
 
+\begin{remark}
+\label{rem:dimTypeCone}
+Since the type cone is an open~$N$ dimensional cone with a linearity subspace of dimension~$n$, it has at least~$N-n$ facets.
+We say that the type cone is \defn{simplicial} when it has precisely $N-n$ facets.
+\end{remark}
+
 \subsection{Coherent fans}
@@
 \end{itemize}
+\vincent{The definition of compatibility degree is not really useful here.}
 
+\begin{definition}
+\label{def:coherent}
 We say that the fan~$\Fan$ is \defn{coherent} if for any two exchangeable rays~$\ray, \ray'$ of~$\Fan$, the linear dependence
@@
 These rays are thus called \defn{forced rays} for the exchangeable pair~$\{\ray, \ray'\}$.
+\end{definition}
 
@@
 Therefore, there exists~$\b{x} \in \R^n$ such that~$\b{h}-\b{z} = \b{G}\b{x}$.
-Therefore, $\b{z} = \Psi(\b{x}$ and~$\b{x} \in P_\b{h}$ since~$\b{h} - \b{G}\b{x} = \b{z} \ge 0$.\qedhere
+Therefore, $\b{z} = \Psi(\b{x})$ and~$\b{x} \in P_\b{h}$ since~$\b{h} - \b{G}\b{x} = \b{z} \ge 0$.\qedhere
 \end{itemize}
@@
 \begin{corollary}
+\label{coro:simplicialTypeCone}
 Assume that the type cone~$\typeCone(\Fan)$ is simplicial and let~$\b{K}$ be the $(N-n) \times N$-matrix whose rows are the outer normal vectors of the facets of~$\typeCone(\Fan)$. Then the polytope
@@
 \section{Applications to different generalizations of the associahedron}
+\label{sec:applications}
+
+Introduction on the associahedron. Loday's associahedron. \\
+Three proofs that the type cone of Loday's associahedron~\cite{Loday} is simplicial and therefore explicit description of all realizations as follows:...\\
+Explain the parallel with $\b{g}$-vectors, $\b{c}$-vectors, etc.
+\vincent{TODO}
 
@@
 
+Gentle associahedra were constructed by Y.~Palu, V.~Pilaud and P.-G.~Plamondon~\cite{PaluPilaudPlamondon} in the context of support $\tau$-tilting for gentle algebras.
+For a given $\tau$-tilting finite gentle quiver~$\quiver$ (defined in the next section), the $\quiver$-associahedron~$\Asso[\quiver]$ is a simple polytope which encodes certain representations of~$\quiver$ and their $\tau$-tilting relations.
+Combinatorially, the $\quiver$-associahedron is a polytopal realization of the non-kissing complex of~$\quiver$, defined as the simplicial complex of all collections of walks on the blossoming quiver~$\quiver\blossom$ which are pairwise non-kissing.
+The non-kissing complex encompasses two families of simplicial complexes studied independently in the literature: on the one hand the grid associahedra introduced by T.~K.~Petersen, P.~Pylyavskyy and D.~Speyer in~\cite{PetersenPylyavskyySpeyer} for a staircase shape, studied by F.~Santos, C.~Stump and V.~Welker~\cite{SantosStumpWelker} for rectangular shapes, and extended by T.~McConville in~\cite{McConville} for arbitrary grid shapes; and on the other hand the Stokes polytopes and accordion associahedra studied b Y.~Baryshnikov~\cite{Baryshnikov}, F.~Chapoton~\cite{Chapoton-quadrangulations}, A.~Garver and T.~McConville~\cite{GarverMcConville} and T.~Manneville and V.~Pilaud~\cite{MannevillePilaud-accordion}.
+These two families naturally extend the classical associahedron, obtained from a line quiver.
+Non-kissing complexes are geometrically realized by polytopes called gentle associahedra, whose normal fan is called the non-kissing fan: its rays correspond to walks in the quiver and its cones are generated by the non-kissing walks.
+In this section, we describe the type cone of the non-kissing fan of a quiver~$\quiver$ with no self-kissing walks.
+
+\subsubsection{Non-kissing complex and non-kissing fan of a gentle quiver}
+
+We present the definitions and properties of the non-kissing complex of a gentle quiver, following the presentation of~\cite{PaluPilaudPlamondon}.
+
+\para{Gentle quivers}
+%
+Consider a \defn{bound quiver}~${\quiver = (Q,I)}$, formed by a finite quiver~$Q = (Q_0, Q_1, s, t)$ and an ideal~$I$ of the path algebra~$kQ$ (the~$k$-vector space generated by all paths in~$Q$, including vertices as paths of length zero, with multiplication induced by concatenation of paths) such that~$I$ is generated by linear combinations of paths of length at least two, and $I$ contains all sufficiently large paths.
+See~\cite{AssemSimsonSkowronski} for background.
+
+Following M.~Butler and C.~Ringel~\cite{ButlerRingel}, we say that~$\quiver$ is a \defn{gentle bound quiver} when
+\begin{enumerate}[(i)]
+\item each vertex~$a \in Q_0$ has at most two incoming and two outgoing arrows,
+\item the ideal~$I$ is generated by paths of length exactly two,
+\item for any arrow~$\beta \in Q_1$, there is at most one arrow~$\alpha \in Q_1$ such that~$t(\alpha) = s(\beta)$ and~${\alpha\beta\notin I}$ (resp.~$\alpha\beta \in I$) and at most one arrow~$\gamma \in Q_1$ such that~$t(\beta) = s(\gamma)$~and~${\beta\gamma\notin I}$~(resp.~${\beta\gamma \in I}$).
+\end{enumerate}
+The algebra~$kQ/I$ is called a \defn{gentle algebra}.
+
+The \defn{blossoming quiver}~$\quiver\blossom$ of a gentle quiver is the gentle quiver obtained by completing all vertices of~$\quiver$ with additional incoming or outgoing \defn{blossoms} such that all vertices of~$\quiver$ become $4$-valent.
+%
+%A gentle bound quiver~$\quiver$ is \defn{complete} if any vertex~$a \in Q_0$ is incident to either one ($a$ is a leaf) or four arrows ($a$ is an internal vertex).
+%The \defn{pruned subquiver} of a quiver~$\quiver$ is the locally gentle quiver obtained by deleting all leaves of~$\quiver$ (degree one vertices) and their incident arrows.
+%The \defn{blossoming quiver} of a locally gentle bound quiver~$\quiver$ is the complete locally gentle bound quiver~$\quiver\blossom$ whose pruned subquiver is~$\quiver$.
+%The vertices of~$Q\blossom_0 \ssm Q_0$ are called \defn{blossom vertices}, and the arrows in~$Q\blossom_1 \ssm Q_1$ are called \defn{blossom arrows}.
+%
+We now always assume that~$\quiver$ is a gentle quiver with blossoming quiver~$\quiver\blossom$.
+
+\para{Strings and walks}
+%
+A \defn{string} in~$\quiver = (Q,I)$ is a word of the form
+\(
+\rho = \alpha_1^{\varepsilon_1}\alpha_2^{\varepsilon_2}\cdots \alpha_\ell^{\varepsilon_\ell},
+\)
+where
+	\begin{enumerate}[(i)]
+	\item $\alpha_i \in Q_1$ and~$\varepsilon_i \in \{-1,1\}$ for all~$i \in [\ell]$,
+	\item $t(\alpha_i^{\varepsilon_i}) = s(\alpha_{i+1}^{\varepsilon_{i+1}})$ for all~$i \in [\ell-1]$,
+	\item there is no path~$\pi \in I$ such that~$\pi$ or~$\pi^{-1}$ appears as a factor of~$\rho$, and
+	\item $\rho$ is reduced, in the sense that no factor~$\alpha\alpha^{-1}$ or~$\alpha^{-1}\alpha$ appears in~$\rho$, for~$\alpha \in Q_1$.
+	\end{enumerate}
+%We say that~$\sigma$ is \defn{straight} if~$\varepsilon_1 = \dots = \varepsilon_\ell$.
+The integer~$\ell$ is called the \defn{length} of the string~$\rho$.
+%We let~$s(\rho) \eqdef s(\alpha_1^{\varepsilon_1})$ and~$t(\rho) \eqdef t(\alpha_\ell^{\varepsilon_\ell})$ denote the source and target of~$\rho$.
+For each vertex~$a \in Q_0$, there is also a \defn{string of length zero}, denoted by~$\varepsilon_a$, that starts and ends at~$a$.
+We often implicitly identify the two inverse strings~$\rho$ and~$\rho^{-1}$, and call it an \defn{undirected string} of~$\quiver$.
+Let~$\strings$ denote the set of strings of~$\quiver$.
+
+A \defn{walk} of~$\quiver$ is a maximal maximal string of its blossoming quiver~$\quiver\blossom$ (meaning that each endpoint is a blossom).
+As for strings, we implicitly identify the two inverse walks~$\omega$ and~$\omega^{-1}$, and call it an \defn{undirected walk} of~$\quiver$.
+Let~$\walks$ denote the set of walks of~$\quiver$.
+
+A \defn{substring} of a walk~$\omega = \alpha_1^{\varepsilon_1} \cdots \alpha_\ell^{\varepsilon_\ell}$ of~$\quiver$ is a string~$\sigma = \alpha_{i+1}^{\varepsilon_{i+1}} \cdots \alpha_{j-1}^{\varepsilon_{j-1}}$ of~$\quiver$ for some indices~$1 \le i < j \le \ell$.
+Note that by definition,
+\begin{itemize}
+\item the endpoints of~$\sigma$ are not allowed to blossom endpoints of~$\omega$,
+\item the position of~$\sigma$ as a factor of~$\omega$ matters (the same string at a different position is considered a different substring).
+\item the string~$\varepsilon_a$ is a substring of~$\omega$ for each occurence of~$a$ as a vertex of~$\omega$ (take~$j = i+1$).
+\end{itemize}
+We denote by~$\Sigma(\omega)$ the set of substrings of~$\omega$.
+We say that the substring~$\sigma = \alpha_{i+1}^{\varepsilon_{i+1}} \cdots \alpha_{j-1}^{\varepsilon_{j-1}}$ is \defn{at the bottom} (resp.~\defn{on top}) of the walk~$\omega = \alpha_1^{\varepsilon_1} \cdots \alpha_\ell^{\varepsilon_\ell}$ if~$\varepsilon_i = 1$ and~$\varepsilon_j = -1$ (resp.~if~$\varepsilon_i = -1$ and~$\varepsilon_j = 1$).
+In other words the two arrows of~$\omega$ incident to the endpoints of~$\sigma$ point towards~$\sigma$ (resp.~outwards from~$\sigma$).
+We denote by~$\Sigma_\bottom(\omega)$ and~$\Sigma_\top(\omega)$ the sets of bottom and top substrings of~$\omega$ respectively.
+We use the same notation for undirected walks (of course, substrings of an undirected walk are undirected).
+
+A \defn{peak} (resp.~\defn{deep}) of a walk~$\omega$ is a substring of~$\omega$ of length zero which is on top (resp.~at the bottom of~$\omega$).
+A walk~$\omega$ is \defn{straight} if it has no peak or deep (\ie if~$\omega$ or~$\omega^{-1}$ is a path in~$\bar Q\blossom$), and \defn{bending} otherwise.
+We denote by~$\peaks{\omega}$ (resp.~$\deeps{\omega}$) the multisets of vertices of peaks (resp.~deeps) of~$\omega$.
+
+\para{Non-kissing complex}
+%
+Let~$\omega$ and~$\omega'$ be two undirected walks on~$\quiver$.
+We say that~$\omega$ \defn{kisses}~$\omega'$ if ${\Sigma_\top(\omega) \cap \Sigma_\bottom(\omega')} \ne \varnothing$.
+In other words, $\omega$ and~$\omega'$ share a common substring~$\sigma$, and both arrows of~$\omega$ (resp.~of~$\omega'$) not in~$\sigma$ are outgoing (resp.~incoming) at the endpoints of~$\sigma$.
+%See \fref{fig:kissing}.
+We say that~$\omega$ and~$\omega'$ are \defn{kissing} if~$\omega$ kisses~$\omega'$ or~$\omega'$ kisses~$\omega$ (or both).
+Note that we authorize the situation where the common finite substring is reduced to a vertex~$a$, that~$\omega$ can kiss~$\omega'$ several times, that~$\omega$ and~$\omega'$ can mutually kiss, and that~$\omega$ can kiss itself.
+We say that a walk is \defn{proper} if it is not straight nor self-kissing.
+We denote by~$\properWalks$ the set of all proper walks of~$\quiver$.
+
+%\begin{figure}[h]
+%	\capstart
+%	\centerline{\includegraphics[scale=1]{kissing}}
+%	\caption{A schematic representation of two kissing walks: $\omega$~kisses~$\omega'$.}
+%	\label{fig:kissing}
+%\end{figure}
+%
+The (reduced) \defn{non-kissing complex} of~$\quiver$ is the simplicial complex~$\NKC$ whose faces are the collections of pairwise non-kissing proper walks of~$\quiver$.
+As shown in~\cite[Thm.~2.46]{PaluPilaudPlamondon}, this simplicial complex is a combinatorial model for the support $\tau$-tilting complex on $\tau$-rigid modules over~$kQ/I$.
+The quiver~$\quiver$ is called \defn{$\tau$-tilting finite} or \defn{non-kissing finite} when this complex is finite (in other words, $\quiver$ has finitely may non-kissing walks).
+
+\para{Non-kissing fan and gentle associahedron}
+%
+Let~$(\b{e}_v)_{v \in Q_0}$ denote the canonical basis of~$\R^{Q_0}$.
+For a multiset~$V = \{\!\{v_1, \dots, v_k\}\!\}$ of~$Q_0$, we denote by $\multiplicityVector_V \eqdef \sum_{i \in [k]} \b{e}_{v_i}$.
+The \defn{$\b{g}$-vector} of a walk~$\omega$ is the vector~$\gvector{\omega} \in \R^{Q_0}$ defined by~$\gvector{\omega} \eqdef \multiplicityVector_{\peaks{\omega}} - \multiplicityVector_{\deeps{\omega}}$.
+Note that by definition, the $\gvector{\omega} = 0$ for a straight walk~$\omega$.
+We also define~$\gvectors{F} \eqdef \set{\gvector{\omega}}{\omega \in F}$ for a face~$F$ of~$\NKC$.
+These vectors support a complete simplicial fan realization of the non-kissing complex complex.
+Examples are illustrated in \cref{fig:nonkissingFans}.
+
+\begin{figure}[h]
+	\capstart
+	\centerline{\includegraphics[scale=.45]{nonkissingFans}}
+	\caption{Two non-kissing fans.
+As the fans are $3$-dimensional, we intersect them with the sphere and stereographically project them from the direction~$(-1,-1,-1)$.
+Illustration from~\cite{PaluPilaudPlamondon}.}
+	\label{fig:nonkissingFans}
+\end{figure}
+
+\begin{theorem}[{\cite[Thm.~4.17]{PaluPilaudPlamondon}}]
+For any non-kissing finite gentle quiver~$\quiver$, the set of cones
+\[
+\gvectorFan[\quiver] \eqdef \set{\R_{\ge 0} \, \gvectors{F}}{F \text{ non-kissing face of } \NKC}
+\]
+is a complete simplicial fan of~$\R^{Q_0}$, called \defn{non-kissing fan} of~$\quiver$, which realizes the non-kissing complex~$\NKC$.
+\end{theorem}
+
+It is proved in~\cite[Thm.~4.27]{PaluPilaudPlamondon} that the non-kissing fan comes from a polytope.
+For a walk~$\omega$, denote by~$\KN(\omega)$ the sum over all other walks~$\omega'$ of the number of kisses between~$\omega$~and~$\omega'$.
+
+\begin{theorem}[{\cite[Thm.~4.27]{PaluPilaudPlamondon}}]
+For any non-kissing finite gentle quiver~$\quiver$, the non-kissing fan~$\gvectorFan[\quiver]$ is the normal fan of the gentle associahedron~$\Asso[\quiver]$, defined as the intersection of the half-spaces~$\set{\b{x} \in \R^{Q_0}}{\dotprod{\gvector{\omega}}{\b{x}} \le \KN(\omega)}$ for all walks~$\omega \in \properWalks$.
+\end{theorem}
+
+\para{Flips in the non-kissing fan}
+%
+Although we lack a characterization of the exchangeable pairs of the non-kissing complex (see \cref{rem:exchangeablePairsNKC}, we can still describe the linear dependence among the $\b{g}$-vectors involved in a flip.
+The following statement is partially proved in~\cite[Thm.~4.17]{PaluPilaudPlamondon}.
+
+\begin{proposition}
+\label{prop:exchangeablePairsNKC}
+Let~$\omega, \omega'$ be two exchangeable walks on~$\quiver$. Then
+\begin{enumerate}[(i)]
+\item For any non-kissing facet~$F, F'$ of~$\NKC$ with~$F \ssm \{\omega\} = f' \ssm \{\omega'\}$, there exists a unique maximal common substring~$\sigma$ of~$\omega$ and~$\omega'$ that decomposes~$\omega = \rho \sigma \tau$ and~$\omega' = \rho' \sigma \tau'$ such that the facets~$F$ and~$F'$ both contain the walks~$\mu \eqdef \rho' \sigma \tau$ and~$\nu \eqdef \rho \sigma \tau'$.
+\item The substring~$\sigma$ and thus the walks~$\mu$ and~$\nu$ actually depend on the exchangeable walks~$\omega$ and~$\omega'$, not on the adjacent non-kissing facet~$F $ and~$F'$.
+\item Moreover, the linear dependence between the $\b{g}$-vectors of~$F \cup F'$ is given by
+\[
+\gvector{\omega} + \gvector{\omega'} = \gvector{\mu} + \gvector{\nu}.
+\]
+In other words, the non-kissing fan of~$\quiver$ is coherent.
+\item The $\b{c}$-vector orthogonal to all $\b{g}$-vectors~$\gvector{\lambda}$ for~$\lambda \in F \cap F'$ is the multiplicity vector~$\multiplicityVector_{\sigma}$ of the vertices of the substring~$\sigma$ of~$\omega$ and~$\omega'$.
+\end{enumerate}
+\end{proposition}
+
+\begin{proof}
+Points~(i), (iii) and~(iv) where shown in~\cite[Prop.~2.33, Thm.~4.17 \& Prop~4.16]{PaluPilaudPlamondon}.
+\vincent{Point~(ii) to prove.}
+\end{proof}
+
+In \cref{prop:exchangeablePairsNKC}, the string~$\sigma$ is called the \defn{distinguished} substring of~$\omega$ and~$\omega'$.
+We say that a string~$\sigma$ is \defn{distinguishable} if it is the distinguished string of an exchangeable pair.
+Note that an equivalent definition of distinguishable strings is given in~\cite[Def.~2.30]{PaluPilaudPlamondon}.
+We denote by~$\distinguishableStrings$ the set of distinguishable strings of~$\quiver$.
+
+\begin{remark}
+\label{rem:exchangeablePairsNKC}
+In view of \cref{prop:exchangeablePairsNKC}, it is tempting to look for a characterization of the exchangeable pairs~$\omega, \omega'$ using the kisses between~$\omega$ and~$\omega'$.
+However, as illustrated in \cref{fig:nonkissingFans}\,(right), note that
+\begin{itemize}
+\item two exchangeable walks may kiss along more than one string, but only one is the distinguished string,
+\item two non-exchangeable walks can kiss along more than one distinguishable string,
+\item two walks that kiss along a single distinguishable string are not always exchangeable,
+\item not all strings are distinguishable.
+\end{itemize}
+\vincent{More explicit. TODO}
+\end{remark}
+
+The following result will also be essential in our discussion.
+
+\begin{proposition}[{\cite[3.68]{PaluPilaudPlamondon}}]
+\label{prop:bijectionStringsWalks}
+The number of distinguishable strings~$\distinguishableStrings$ and proper walks~$\properWalks$ of the quiver~$\quiver$ are related by
+\[
+|\distinguishableStrings| + |Q_0| = |\properWalks|.
+\]
+\end{proposition}
+
+We are now ready to describe the type cone of the non-kissing fan~$\gvectorFan[\quiver]$.
+We first treat the case when~$\quiver$ has no self-kissing walks, which includes the case of the classical associahedron.
+We show that the type cone is then simplicial which gives another proof of \cref{thm:simplicialTypeConeAsso} and \cref{coro:descriptionAllAsso}.
+
+\subsubsection{Simplicial type cones for self-kissing free quivers}
+
+In this section, we focus on the following family of gentle quivers, which was also considered in~\cite[Sect.~4]{}.
+
+\begin{proposition}
+\label{prop:noSelfKissing}
+The following conditions are equivalent for a gentle quiver~$\quiver$.
+\begin{enumerate}[(i)]
+\item any (non necessarily oriented) cycle of~$\quiver$ contains at least two relations in~$I$,
+\item any string of~$\quiver$ is distinguishable,
+\item no walk on~$\quiver$ is self-kissing.
+\end{enumerate}
+\end{proposition}
+
+The quivers of this family is particularly well-behaved: they avoid all pathologies of \cref{rem:exchangeablePairsNKC} and we will prove that the type cone of their non-kissing fan happens to be simplicial.
+Note that this family already contains a lot of relevant examples, including:
+\begin{itemize}
+\item classical associahedra
+\item grid associahedra
+\item dissection associahedra
+\end{itemize}
+\vincent{More explicit. TODO}
+
+%For a string~$\sigma$ of~$\quiver$, we denote by $\sigma\hR$ (resp.~$\hL\sigma$, resp.~$\sigma\cR$, resp.~$\cL\sigma$) the unique string of~$\quiver\blossom$ of the form $\sigma\hR = \sigma \alpha_1^{-1} \alpha_2 \dots \alpha_\ell$ (resp.~$\hL\sigma = \alpha_\ell^{-1} \dots \alpha_2^{-1} \alpha_1 \sigma$, resp.~$\sigma\cR = \sigma \alpha_1 \alpha_2^{-1} \dots \alpha_\ell^{-1}$, resp.~$\cL\sigma = \alpha_\ell \dots \alpha_2 \alpha_1^{-1} \sigma$) with~$\ell \ge 1$ and~$\alpha_1, \dots, \alpha_\ell \in Q_1$ and such that~$t(\alpha_\ell)$ (resp.~$s(\alpha_\ell)$, resp.~$s(\alpha_\ell)$, resp.~$t(\alpha_\ell)$) is a blossom of~$\quiver\blossom$.
+For a string~$\sigma$ of~$\quiver$, we denote by $\sigma\hR$ (resp.~$\sigma\cR$) the unique string of the blossoming quiver~$\quiver\blossom$ of the form $\sigma\hR = \sigma \alpha_1^{-1} \alpha_2 \dots \alpha_\ell$ (resp.~$\sigma\cR = \sigma \alpha_1 \alpha_2^{-1} \dots \alpha_\ell^{-1}$) with~$\ell \ge 1$ and~${\alpha_1, \dots, \alpha_\ell \in Q_1}$ and such that~$t(\alpha_\ell)$ (resp.~$s(\alpha_\ell)$) is a blossom of~$\quiver\blossom$.
+These notations are motivated by the representation of strings used in~\cite{ButlerRingel, PaluPilaudPlamondon}, and the terminology usually says that~$\sigma\hR$ (resp.~$\sigma\cR$) is obtained by adding a \defn{hook} (resp.~\defn{cohook}) to~$\sigma$.
+We define similarly~$\hL\sigma$ (resp.~$\cL\sigma$).
+The walk~$\hL(\sigma\hR) = (\hL\sigma)\hR$ of~$\quiver$ is simply be denoted~$\hh{\sigma}$, and we define similarly~$\cc{\sigma}$, $\hc{\sigma}$ and~$\ch{\sigma}$.
+
+%For a string~$\sigma$ of~$\quiver$, we denote by~$\hh{\sigma}$, $\cc{\sigma}$, $\hc{\sigma}$ and~$\ch{\sigma}$ the unique walks on~$\quiver$ of the~form
+%\begin{alignat*}{3}
+%\hh{\sigma} & = \alpha_k^{-1} \dots \alpha_2^{-1} \alpha_1 \sigma \beta_1^{-1} \beta_2 \dots \beta_\ell
+%\qquad\qquad
+%& \cc{\sigma} & = \alpha_k \dots \alpha_2 \alpha_1^{-1} \sigma \beta_1 \beta_2^{-1} \dots \beta_\ell^{-1}
+%\\
+%\hc{\sigma} & = \alpha_k^{-1} \dots \alpha_2^{-1} \alpha_1 \sigma \beta_1 \beta_2^{-1} \dots \beta_\ell^{-1}
+%\qquad\qquad
+%& \ch{\sigma} & = \alpha_k \dots \alpha_2 \alpha_1^{-1} \sigma \beta_1^{-1} \beta_2 \dots \beta_\ell.
+%\end{alignat*}
+%%\begin{itemize}
+%%\item by~$\hh{\sigma}$ the unique walk on~$\quiver$ of the form~$\hh{\sigma} = \alpha_k^{-1} \dots \alpha_2^{-1} \alpha_1 \sigma \beta_1^{-1} \beta_2 \dots \beta_\ell$,
+%%\item by~$\cc{\sigma}$ the unique walk on~$\quiver$ of the form~$\cc{\sigma} = \alpha_k \dots \alpha_2 \alpha_1^{-1} \sigma \beta_1 \beta_2^{-1} \dots \beta_\ell^{-1}$.
+%%\item by~$\hc{\sigma}$ the unique walk on~$\quiver$ of the form~$\hc{\sigma} = \alpha_k^{-1} \dots \alpha_2^{-1} \alpha_1 \sigma \beta_1 \beta_2^{-1} \dots \beta_\ell^{-1}$.
+%%\item by~$\ch{\sigma}$ the unique walk on~$\quiver$ of the form~$\ch{\sigma} = \alpha_k \dots \alpha_2 \alpha_1^{-1} \sigma \beta_1^{-1} \beta_2 \dots \beta_\ell$.
+%%\end{itemize}
+%with~$k,\ell \ge 1$ and~$\alpha_1, \dots, \alpha_k, \beta_1, \dots, \beta_\ell \in Q_1$.
+%The following statement ensures that in a gentle quiver with no self-kissing walk, the walks~$\hh{\sigma}$ and~$\cc{\sigma}$ are exchangeable with distinguished substring~$\sigma$.
+
+\begin{proposition}
+For any gentle quiver~$\quiver$ with no self-kissing walk and any string~$\sigma \in \strings$, the walks~$\cc{\sigma}$ and~$\hh{\sigma}$ are exchangeable with distinguished substring~$\sigma$.
+\end{proposition}
+
+\begin{proof}
+We just need to prove that there exists a ridge~$R$ of~$\NKC$ containing both~$\hc{\sigma}$ and~$\ch{\sigma}$ and such that~$R \cup \{\cc{\sigma}\}$ and~$R \cup \{\hh{\sigma}\}$ are adjacent facets of~$\NKC$.
+\vincent{TODO}
+\end{proof}
+
+The following statement describes the type cone of the non-kissing fan of a gentle quiver with no self-kissing walks.
+
+\begin{proposition}
+\label{prop:extremalExchangeablePairsNKC}
+For any gentle quiver~$\quiver$ with no self-kissing walk, the extremal exchangeable pairs for the non-kissing fan of~$\quiver$ are precisely the pairs~$\{\cc{\sigma}, \hh{\sigma}\}$ for all strings~$\sigma \in \strings$.
+\end{proposition}
+
+\begin{proof}
+Let~$(\b{f}_\omega)_{\omega \in \walks}$ be the canonical basis of~$\R^{\walks}$.
+Consider two exchangeable walks~$\omega$ and~$\omega'$ with distinguished substring~$\sigma \in \Sigma_\top(\omega) \cap \Sigma_\bottom(\omega')$.
+Decompose~$\omega = \rho \sigma \tau$ and~$\omega' = \rho' \sigma \tau'$ and define~$\mu \eqdef \rho' \sigma \tau$ and~$\nu \eqdef \rho \sigma \tau'$ as in \cref{prop:exchangeablePairsNKC}\,(i).
+\cref{prop:exchangeablePairsNKC}\,(iii) ensures that the linear dependence between the corresponding $\b{g}$-vectors is given by
+\[
+\gvector{\omega} + \gvector{\omega'} = \gvector{\mu} + \gvector{\nu}.
+\]
+Therefore, the outer normal vector of the corresponding inequality of the type cone~$\typeCone(\gvectorFan[\quiver])$ is
+\[
+\b{n}(\omega, \omega') \eqdef \b{f}_\omega + \b{f}_{\omega'} - \b{f}_\mu - \b{f}_\nu.
+\]
+We claim that this normal vector is always a positive linear combination of the normal vectors~$\b{m}(\sigma) \eqdef \b{n}(\cc{\sigma}, \hh{\sigma}) = \b{f}_{\cc{\sigma}} + \b{f}_{\hh{\sigma}} - \b{f}_{\hc{\sigma}} - \b{f}_{\ch{\sigma}}$ for all string~$\sigma \in \strings$.
+Our proof works by descending induction on the length~$\lambda(\omega,\omega') \eqdef \ell(\sigma)$ of the common substring of~$\omega$ and~$\omega'$.
+If~$\lambda(\omega, \omega')$ is big enough, then the walk~$\omega$ (resp.~$\omega'$) is just obtained by adding two outgoing (resp.~incoming) blossoms at the end of~$\sigma$, thus $\omega = \cc{\sigma}$ (resp.~$\omega' = \hh{\sigma}$), and there is nothing to prove.
+Assume now that~$\omega \ne \hh{\sigma}$ (the situations where~$\omega' \ne \cc{\sigma}$ or~$\omega \ne \rho \sigma \hR$ are symmetric).
+%Assume now that~$\omega \ne \hh{\sigma}$, for instance that~$\omega \ne \hL \sigma \tau$ (the situations where~$\omega' \ne \cc{\sigma}$ or~$\omega \ne \rho \sigma \hR$ are symmetric).
+%Let~$\xi \eqdef \hL \sigma \tau$ and $\zeta \eqdef \hL \sigma \tau'$.
+%These notations are summarized in \cref{fig:proofExtremalExchangeablePairsNKC}.
+If~$\rho \ne \cL$, observe that
+\begin{itemize}
+\item $\omega$ and~$\cL \sigma \tau'$ are exchangeable with~$\b{n}(\omega, \cL \sigma \tau') = \b{f}_\omega + \b{f}_{\cL \sigma \tau'} - \b{f}_{\cL \sigma \tau} - \b{f}_\nu$, and
+\item $\cL \sigma \tau$ and~$\omega'$ are exchangeable with~$\b{n}(\cL \sigma \tau, \omega') = \b{f}_{\cL \sigma \tau} + \b{f}_{\omega'} - \b{f}_{\cL \sigma \tau'} - \b{f}_\mu$.
+\end{itemize}
+We derive that
+\[
+\b{n}(\omega, \omega') = \b{n}(\omega, \cL \sigma \tau') + \b{n}(\cL \sigma \tau, \omega').
+\]
+Observe moreover that since~$\omega$ has outgoing arrows at the endpoints of~$\sigma$, the common substring of~$\omega$ and~$\cL \sigma \tau'$ strictly contains~$\sigma$ so that $\lambda(\omega, \cL \sigma \tau') > \lambda(\omega, \omega')$.
+By induction, $\b{n}(\omega, \cL \sigma \tau')$ is thus a positive linear combination of~$\b{m}(\sigma)$ for~$\sigma \in \strings$.
+%
+By symmetry, we obtain the four equalities
+\[
+\b{n}(\omega, \omega') = 
+\begin{cases}
+\b{n}(\omega, \cL \sigma \tau') + \b{n}(\cL \sigma \tau, \omega') & \text{if } \rho \ne \cL, \\
+\b{n}(\omega, \rho' \sigma \cR) + \b{n}(\rho \sigma \cR, \omega') & \text{if } \tau \ne \cR, \\
+\b{n}(\omega, \hL \sigma \tau') + \b{n}(\hL \sigma \tau, \omega') & \text{if } \rho' \ne \hL, \\
+\b{n}(\omega, \rho' \sigma \hR) + \b{n}(\rho \sigma \hR, \omega') & \text{if } \tau' \ne \hR.
+\end{cases}
+\]
+These four equalities are illustrated on \cref{fig:fourEqualities}.
+%
+\begin{figure}[t]
+	\capstart
+%	\centerline{\includegraphics[scale=1.2]{fourEqualities}}
+	\centerline{
+	\begin{tabular}{c@{\qquad}c}
+		\includegraphics[scale=1.2]{fourEqualities1} & \includegraphics[scale=1.2]{fourEqualities2} \\
+		$\b{n}({\red \omega}, {\orange \omega'}) = \b{n}({\red \omega}, {\blue \cL \sigma \tau'}) + \b{n}({\green \cL \sigma \tau}, {\orange \omega'})$ & $\b{n}({\red \omega}, {\orange \omega'}) = \b{n}({\red \omega}, {\blue \rho' \sigma \cR}) + \b{n}({\green \rho \sigma \cR}, {\orange \omega'})$ \\[.4cm]
+		\includegraphics[scale=1.2]{fourEqualities3} & \includegraphics[scale=1.2]{fourEqualities4} \\
+		$\b{n}({\red \omega}, {\orange \omega'}) = \b{n}({\red \omega}, {\blue \hL \sigma \tau'}) + \b{n}({\green \hL \sigma \tau}, {\orange \omega'})$ & $\b{n}({\red \omega}, {\orange \omega'}) = \b{n}({\red \omega}, {\blue \rho' \sigma \hR}) + \b{n}({\green \rho \sigma \hR}, {\orange \omega'})$ \\
+	\end{tabular}
+	}
+	\caption{Schematic representation of te four equalities in the proof of \cref{prop:extremalExchangeablePairsNKC}.}
+	\label{fig:fourEqualities}
+\end{figure}
+%
+Moreover~$\b{n}(\omega, \cL \sigma \tau')$, $\b{n}(\cL \sigma \tau, \hL \sigma \cR)$, $\b{n}(\cL \sigma \hR, \hL \sigma \tau')$ and~$\b{n}(\hL \sigma \tau, \omega')$ are all positive combinations of~$\b{m}(\sigma)$ for~$\sigma \in \strings$ by induction hypothesis.
+%
+Applying these equalities one after the other, we obtain
+\[
+\renewcommand{\arraystretch}{1.3}
+\begin{array}[t]{l@{\;\;}l@{\;}l@{\;}l@{\;}l@{\;}l@{\;}l@{\;}l@{\;}l@{\;}l}
+  & \b{n}(\omega, \omega') & & \hfill\raisebox{-.1cm}{\text{\tiny{Equality 1}}} & & & & & & \\
+\cline{2-4}
+= & \b{n}(\omega, \cL \sigma \tau') & + & \b{n}(\cL \sigma \tau, \omega') & & & & & & \hfill\raisebox{-.1cm}{\text{\tiny{Equality 2}}} \\
+\cline{4-10}
+= & \b{n}(\omega, \cL \sigma \tau') & + & \b{n}(\cL \sigma \tau, \hL \sigma \tau') & & \hfill\raisebox{-.1cm}{\text{\tiny{Equality 3}}} & & & + & \b{n}(\hL \sigma \tau, \omega') \\
+\cline{4-6}
+= & \b{n}(\omega, \cL \sigma \tau') & + & \b{n}(\cL \sigma \tau, \hL \sigma \cR) & + & \b{n}(\cL \sigma \cR, \hL \sigma \tau') & & \hfill\raisebox{-.1cm}{\text{\tiny{Equality 4}}} & + & \b{n}(\hL \sigma \tau, \omega') \\
+\cline{6-8}
+= & \b{n}(\omega, \cL \sigma \tau') & + & \b{n}(\cL \sigma \tau, \hL \sigma \cR) & + & \b{n}(\cL \sigma \cR, \hL \sigma \hR) & + & \b{n}(\cL \sigma \hR, \hL \sigma \tau') & + & \b{n}(\hL \sigma \tau, \omega') \\
+= & \b{n}(\omega, \cL \sigma \tau') & + & \b{n}(\cL \sigma \tau, \hL \sigma \cR) & + & \multicolumn{1}{c}{\b{m}(\sigma)} & + & \b{n}(\cL \sigma \hR, \hL \sigma \tau') & + & \b{n}(\hL \sigma \tau, \omega')
+\end{array}
+\renewcommand{\arraystretch}{1}
+\]
+where we fix the convention~$\b{n}(\lambda, \lambda) = 0$ in case~$\rho = \hL$, $\rho' = \cL$, $\tau = \hR$ or~$\tau' = \cR$.
+%
+We conclude that~$\b{n}(\omega, \omega')$ is a positive combination of~$\b{m}(\sigma)$ for~$\sigma \in \strings$, since~$\b{n}(\omega, \cL \sigma \tau')$, $\b{n}(\cL \sigma \tau, \hL \sigma \cR)$, $\b{n}(\cL \sigma \hR, \hL \sigma \tau')$ and~$\b{n}(\hL \sigma \tau, \omega')$ are.
+This shows that all extremal exchangeable pairs are of the form~$\{\cc{\sigma}, \hh{\sigma}\}$ for~$\sigma \in \strings$.
+
+Conversely, we know from \cref{rem:dimTypeCone} that there are at least~$|\walks|-|Q_0|$ extremal exchangeable pairs.
+Since this~$|\strings| = |\distinguishableStrings| = |\walks| - |Q_0|$ by~\cref{prop:bijectionStringsWalks}, we conclude that all exchangeable pairs~$\{\cc{\sigma}, \hh{\sigma}\}$ for~$\sigma \in \strings$ are extremal.
+\end{proof}
+
+Combining \cref{coro:simplicialTypeCone}, \cref{prop:bijectionStringsWalks} and \cref{prop:extremalExchangeablePairsNKC}, we derive the following description of all polytopal realizations of the non-kissing fan.
+
+\begin{corollary}
+For any gentle quiver~$\quiver$ with no self-kissing walk and any~$\b{\ell} \in \R_{>0}^{\strings}$, the polytope
+\[
+R_\b{\ell}(\quiver) \eqdef \bigset{\b{z} \in \R^{\walks}}{\b{z} \ge 0 \text{ and } \b{z}_{\cc{\sigma}} + \b{z}_{\hh{\sigma}} - \b{z}_{\hc{\sigma}} - \b{z}_{\ch{\sigma}} = \ell_\sigma \text{ for all } \sigma \in \strings}
+\]
+is a realization of the non-kissing fan~$\gvectorFan[\quiver]$.
+Moreover, the polytopes~$R_\b{\ell}(\quiver)$ for~$\b{\ell} \in \R_{>0}^{\strings}$ describe all polytopal realizations of~$\gvectorFan[\quiver]$.
+\end{corollary}
+
+\begin{proof}
+\cref{prop:extremalExchangeablePairsNKC} asserts that the type cone~$\typeCone(\gvectorFan[\quiver])$ has one facet for each string of~$\quiver$.
+Since all strings are distinguishable by \cref{prop:noSelfKissing}, the number of facets of~$\typeCone(\gvectorFan[\quiver])$ is $|\strings| = |\distinguishableStrings| = |\walks| - |Q_0|$ by~\cref{prop:bijectionStringsWalks}, so that~$\typeCone(\gvectorFan[\quiver])$ is simplicial.
+We then conclude by a simple application of \cref{coro:simplicialTypeCone}.
+\end{proof}
+
+We also obtain from \cref{prop:extremalExchangeablePairsNKC} the following surprising property.
+
+\begin{corollary}
+Any $\b{c}$-vector supports exactly one extremal exchangeable pair.
+\end{corollary}
+
+\begin{remark}
+\label{rem:meshARquiver}
+Although not needed in the proof of \cref{prop:extremalExchangeablePairsNKC}, we note that the extremal exchangeable pairs~$\{\cc{\sigma}, \hh{\sigma}\}$ and their linear dependences~${\gvector{\cc{\sigma}} + \gvector{\hh{\sigma}} - \gvector{\hc{\sigma}} - \gvector{\ch{\sigma}}}$ precisely correspond to the meshes of the Auslander-Reiten quiver of~$\quiver$.
+\end{remark}
+
+\subsubsection{Towards the general case}
+
 We are already missing a criterion for exchangeable pairs of walks. See \cite[Sect.~9]{BrustleDouvilleMousavandThomasYildirim}.
-It seems that two exchangeable pairs are always kissing along a single distinguishable string.
+It seems that two exchangeable walks are always kissing along a single distinguishable string.
 We need to prove that to see that the non-kissing fan is coherent (because for a pair of exchangeable walks, I can completely reconstruct the $\b{g}$-vector dependence of the flip if I know there distinguished substring).
@@
 \item non-exchangeable walks might kiss along a single distinguishable string (example: see the cyclic triangle in~\cite{PaluPilaudPlamondon}).
+\item non-exchangeable walks might kiss along two or more distinguishable strings (example: see the cyclic triangle in~\cite{PaluPilaudPlamondon}).
 \end{enumerate}
+
+%In view of these two points, the following conjecture seems plausible.
+%
+%\begin{conjecture}
+%Two walks~$\omega$ and~$\omega'$ are exchangeable if and only if
+%\begin{itemize}
+%\item they kiss along a single distinguishable string~$\sigma$ (note that they might also kiss along other strings as long as they are not distinguishable),
+%\item decomposing~$\omega = \rho \sigma \tau$ and~$\omega' = \rho' \sigma \tau'$ according to their common distinguishable string, the two walks~$\mu \eqdef \rho' \sigma \tau$ and~$\nu \eqdef \rho \sigma \tau'$ are non-self-kissing.
+%\end{itemize}
+%Recall that with these notations, for any flip exchanging~$\omega$ and~$\omega'$, we have the linear dependence
+%\[
+%\gvector{\omega} + \gvector{\omega'} = \gvector{\mu} + \gvector{\nu}.
+%\]
+%\end{conjecture}
 
@@
 
+\begin{figure}[t]
+	\capstart
+	\centerline{\includegraphics[scale=.6]{fan}}
+	\caption{The shards corresponding to the facets of the type cone. Is there a geometric meaning?}
+	\label{fig:fanShards}
+\end{figure}
+
 \subsection{Graph associahedra}
 
+Graph associahedra were defined by M.~Carr and S.~Devadoss~\cite{CarrDevadoss} in connection to C.~De Concini and C.~Procesi's wonderful arrangements~\cite{DeConciniProcesi}.
+For a given graph~$\graphG$, the $\graphG$-associahedron~$\Asso[\graphG]$ is a simple polytope whose combinatorial structure encodes the connected subgraphs of~$\graphG$ and their nested structure.
+More precisely, the $\graphG$-associahedron is a polytopal realization of the nested complex of~$\graphG$, defined as the simplicial complex of all collections of tubes (connected induced subgraphs) of~$\graphG$ which are pairwise compatible (either nested, or disjoint and non-adjacent).
+As illustrated in~\cref{fig:specialGraphAssociahedra}, the graph associahedra of certain special families of graphs coincide with well-known families of polytopes: complete graph associahedra are permutahedra, path associahedra are classical associahedra, cycle associahedra are cyclohedra, and star associahedra are stellohedra.
+The graph associahedra were extended to the \defn{nestohedra}, which are simple polytopes realizing the nested complex of arbitrary building sets~\cite{Postnikov, FeichtnerSturmfels}.
+Graph associahedra and nestohedra have been geometrically realized in different ways: by successive truncations of faces of the standard simplex~\cite{CarrDevadoss}, as Minkowski sums of faces of the standard simplex~\cite{Postnikov, FeichtnerSturmfels}, or from their normal fans by exhibiting explicit inequality descriptions~\cite{Devadoss, Zelevinsky}.
+For a given graph~$\graphG$, the resulting polytopes all have the same normal fan, called nested fan of~$\graphG$: its rays are the characteristic vectors of the tubes, and its cones are generated by characteristic vectors of compatible tubes.
+In this section, we describe the type cone of the nested fan of any graph~$\graphG$.
+
+\begin{figure}[t]
+	\capstart
+	\centerline{
+		\begin{tabular}{c@{\;}c@{\;}c@{\;}c}
+    		permutahedron &
+    		associahedron &
+    		cyclohedron &
+    		stellohedron \\
+    		\includegraphics[scale=.6]{permutahedron} &
+    		\includegraphics[scale=.6]{associahedron} &
+    		\includegraphics[scale=.6]{cyclohedron} &
+    		\includegraphics[scale=.6]{stellohedron} \\
+    		\includegraphics[scale=.6]{permutahedronTubings} &
+    		\includegraphics[scale=.6]{associahedronTubings} &
+    		\includegraphics[scale=.6]{cyclohedronTubings} &
+    		\includegraphics[scale=.6]{stellohedronTubings} \\[.1cm]
+    		complete graph &
+    		path &
+    		cycle &
+    		star
+		\end{tabular}
+	}
+	\caption{Some classical families of polytopes as graph associahedra. Illustration from~\cite{MannevillePilaud-compatibilityFans}.}
+	\label{fig:specialGraphAssociahedra}
+\end{figure}
+
+\subsubsection{Nested complex and nested fan of a graph}
+
+We present the definitions and properties of the nested complex of a graph, following ideas from~\cite{CarrDevadoss, Postnikov, FeichtnerSturmfels, Zelevinsky}.
+
+\para{Nested complex}
+%
 Let~$\graphG$ be a graph with vertex set~$\ground$.
@@
 A \defn{tubing} on~$\graphG$ is a set~$\tubing$ of pairwise compatible proper tubes of~$\graphG$.
-The collection of all tubings on~$\graphG$ is a simplicial complex, called \defn{nested complex} of~$\graphG$ and denoted by~$\nestedComplex(\graphG)$.
+The \defn{nested complex} of~$\graphG$ is the simplicial complex~$\nestedComplex(\graphG)$ of all tubings on~$\graphG$.
 
-Let~$(\b{e}_v)_{v \in \ground}$ be the canonical basis of~$\R^\ground$, let~${\HH \eqdef \bigset{\b{x} \in \R^\ground}{\sum_{w \in W} x_w = 0 \text{ for all } W \in \connectedComponents(\graphG)}}$ and~$\pi : \R^\ground \to \HH$ denote the orthogonal projection on~$\HH$.
-Let~$\gvector{\tube} \eqdef \pi \big( \sum_{v \in \tube} \b{e}_v \big)$ denote the projection of the characteristic vector of a tube~$\tube$ of~$\graphG$, and define~$\gvectors{\tubing} \eqdef \set{\gvector{\tube}}{\tube \in \tubing}$ for a tubing~$\tubing$ on~$\graphG$.
-Note that~$\gvector{\graphG} = 0$ by definition.
-These vectors support a complete simplicial fan realization of the nested complex:
+\para{Nested fan and graph associahedron}
+%
+Let~$(\b{e}_v)_{v \in \ground}$ be the canonical basis of~$\R^\ground$.
+We consider the hyperplane~${\HH \eqdef \bigset{\b{x} \in \R^\ground}{\sum_{w \in W} x_w = 0 \text{ for all } W \in \connectedComponents(\graphG)}}$ and let~$\pi : \R^\ground \to \HH$ denote the orthogonal projection on~$\HH$.
+The \defn{$\b{g}$-vector} of a tube~$\tube$ of~$\graphG$ is the projection~$\gvector{\tube} \eqdef \pi \big( \sum_{v \in \tube} \b{e}_v \big)$ of the characteristic vector of~$\tube$.
+Note that by definition,~$\gvector{\graphG} = 0$.
+We also define~$\gvectors{\tubing} \eqdef \set{\gvector{\tube}}{\tube \in \tubing}$ for a tubing~$\tubing$ on~$\graphG$.
+These vectors support a complete simplicial fan realization of the nested complex.
+Examples are illustrated in \cref{fig:nestedFans}.
+
+\begin{figure}[h]
+	\capstart
+	\centerline{\includegraphics[scale=.55]{nestedFans}}
+	\caption{Two nested fans. As the fans are $3$-dimensional, we intersect them with the sphere and stereographically project them from the direction~$(-1,-1,-1)$.}
+	\label{fig:nestedFans}
+\end{figure}
 
 \begin{theorem}[\cite{CarrDevadoss, Postnikov, FeichtnerSturmfels, Zelevinsky}]
-\label{theo:gFan}
-For any graph~$\graphG$, the collection of cones
+For any graph~$\graphG$, the set of cones
 \[
-\nestedFan(\graphG) \eqdef \set{\R_{\ge 0} \, \gvectors{\tubing}}{\tubing \text{ tubing on } \graphG}
+\gvectorFan[\graphG] \eqdef \set{\R_{\ge 0} \, \gvectors{\tubing}}{\tubing \text{ tubing on } \graphG}
 \]
@@
 It is proved in~\cite{CarrDevadoss, Devadoss, Postnikov, FeichtnerSturmfels, Zelevinsky} that the nested fan comes from a polytope.
+For any subset~$U \subseteq \ground$, denote by~$\triangle_U \eqdef \conv\set{\b{e}_u}{u \in U}$ the face of the standard simplex~$\triangle_\ground$ corresponding to~$U$.
 
 \begin{theorem}[\cite{CarrDevadoss, Devadoss, Postnikov, FeichtnerSturmfels, Zelevinsky}]
-\label{theo:graphAssociahedron}
-For any graph~$\graphG$, the nested fan~$\nestedFan(\graphG)$ is the normal fan of the graph associahedron~$\Asso[\graphG]$.
+For any graph~$\graphG$, the nested fan~$\gvectorFan[\graphG]$ is the normal fan of the graph associahedron~$\Asso[\graphG]$, defined as the Minkowski sum~$\sum_{\tube \in \tubes(\graphG)} \triangle_{\tube}$ of the faces of the standard simplex corresponding to all tubes of~$\graphG$.
 \end{theorem}
 
+\para{Flips in the nested fan}
+%
 The following statement follows from~\cite{MannevillePilaud-compatibilityFans, Zelevinsky}.
@@
 \item For any maximal tubings~$\tubing, \tubing$ on~$\graphG$ with $\tubing \ssm \{\tube\} = \tubing' \ssm \{\tube'\}$, both~$\tubing \cup \connectedComponents(\graphG)$ and~$\tubing' \cup \connectedComponents(\graphG)$ contain the tube~$\tube \cup \tube'$ and the connected components of~$\tube \cap \tube'$.
-\item For any maximal tubings~$\tubing, \tubing$ on~$\graphG$ with $\tubing \ssm \{\tube\} = \tubing' \ssm \{\tube'\}$, the linear dependence between the $\b{g}$-vectors of~$\tubing \cup \tubing'$ is given by
+\item The linear dependence between the $\b{g}$-vectors of~$\tubing \cup \tubing'$ is given by
 \[
@@
 In other words, the nested fan of~$\graphG$ is coherent.
-\item For any maximal tubings~$\tubing, \tubing$ on~$\graphG$ with $\tubing \ssm \{\tube\} = \tubing' \ssm \{\tube'\}$, the $\b{c}$-vector orthogonal to all $\b{g}$-vectors~$\gvector{\tube[s]}$ for~$\tube[s] \in \tubing \cap \tubing'$ is~$\b{e}_v - \b{e}_{v'}$.
+\item The $\b{c}$-vector orthogonal to all $\b{g}$-vectors~$\gvector{\tube[s]}$ for~$\tube[s] \in \tubing \cap \tubing'$ is~$\b{e}_v - \b{e}_{v'}$.
 \end{enumerate}
@@
 \]
-Finally, any tube~$\tube[s] \in \tubing \cap \tubing'$ that contains~$v$ or~$v'$ actually contains both (to be compatible with~$\tube$ and~$\tube'$).
+Finally for~(iv), any tube~$\tube[s] \in \tubing \cap \tubing'$ that contains~$v$ or~$v'$ actually contains both (to be compatible with~$\tube$ and~$\tube'$).
 Therefore, $\gvector{\tube[s]}$ is orthogonal to~$\b{e}_v - \b{e}_{v'}$ for any tube~$\tube[s] \in \tubing \cap \tubing'$.
@@
 
-We are now ready to describe the type cone of the nested fan~$\nestedFan(\graphG)$.
+We are now ready to describe the type cone of the nested fan~$\gvectorFan[\graphG]$.
+We first treat the case when~$G$ is a path so that the $\graphG$-associahedron is a classical associahedron.
+We show that the type cone is then simplicial which gives another proof of \cref{thm:simplicialTypeConeAsso} and \cref{coro:descriptionAllAsso}.
+
+\subsubsection{Simplicial type cones for path associahedra}
+
 We start with the case of the path.
@@
 \label{prop:extremalExchangeablePairsA}
-Two intervals~$[i,j]$ and~$[i',j']$ of~$[n]$ form an extremal exchangeable pair for the nested fan the path if and only if~$i = i'+1$ and~$j = j'+1$, or the opposite.
+%The extremal exchangeable pairs for the nested fan of the path are precisely the pairs of intervals~$\{[i,j], [i+1,j+1]\}$ for~$1 \le i \le j \le n-1$.
+Two intervals~$[i,j]$ and~$[i',j']$ of~$[n]$ form an extremal exchangeable pair for the nested fan of the path if and only if~$i = i'+1$ and~$j = j'+1$, or the opposite.
 \end{proposition}
@@
 \begin{proof}
-Let~$(\b{f}_{[i,j]})_{1 \le i \le j \le n}$ denote the canonical basis of~$\R^N$.
-Consider two exchangeable tubes~$[i,j]$ and~$[i',j']$ with~$i < i' \le j+1 < j'+1$.
+Let~$(\b{f}_{[i,j]})_{1 \le i \le j \le n}$ be the canonical basis of~$\R^{\binom{n+1}{2}}$.
+Consider two exchangeable tubes~$[i,j]$ and~$[i',j']$ with~${i < i' \le j+1 < j'+1}$.
 By \cref{prop:exchangeablePairsGA}\,(iii), the linear dependence between the corresponding $\b{g}$-vectors is given by
@@
 \]
-Therefore, the outer normal vector of the corresponding inequality of the type cone~$\typeCone(\nestedFan(\graphG))$ is given by
+Therefore, the outer normal vector of the corresponding inequality of the type cone~$\typeCone(\gvectorFan[\graphG])$ is
 \[
@@
 where~$\lambda(i,j,i',j') \ge 0$ for all exchangeable pairs~$\{[i,j], [i',j']\}$.
-Note that~$\sum \lambda(i,j,i',j') > 1$ since the coefficient of~$\b{f}_{[k,\ell]}$ in~$\b{m}(k,\ell)$ is~$-1$.
+Note that~$\sum \lambda(i,j,i',j') \ge 1$ since the coefficient of~$\b{f}_{[k,\ell]}$ in~$\b{m}(k,\ell)$ is~$-1$.
 Consider the linear form~$\Phi: \R^N \to \R$ defined by~$\Phi(\b{f}_{[i,j]}) = -(j-i)^2$.
@@
 \]
-Since~$\sum \lambda(i,j,i',j') > 1$ we obtain that~$\lambda(k,\ell-1,k+1,\ell-1) = 1$ and~$\lambda(i,j,i',j') = 0$ for all other exchangeable pairs~$\{[i,j], [i',j']\}$.
+Since~$\sum \lambda(i,j,i',j') \ge 1$ we obtain that~$\lambda(k,\ell-1,k+1,\ell) = 1$ and~$\lambda(i,j,i',j') = 0$ for all other exchangeable pairs~$\{[i,j], [i',j']\}$.
 \end{proof}
 
-\cref{prop:extremalExchangeablePairsA} extends to arbitrary graphs as follows.
+\subsubsection{General case}
+
+We now consider an arbitrary graph~$\graphG$ and describe the type cone of its nested fan.
+\cref{prop:extremalExchangeablePairsA} extends as follows.
 % We denote by~$X \symdif Y$ the symmetric difference of two sets~$X$ and~$Y$.
@@
 
+The following statement reformulates \cref{prop:extremalExchangeablePairsGA}.
+
 \begin{corollary}
-For any $\b{c}$-vector supports at least one extremal exchangeable pair.
+\label{coro:extremalExchangeablePairsGA}
+The extremal exchangeable pairs for the nested fan of~$\graphG$ are equivalently
+\begin{enumerate}[(i)]
+\item the pairs of tubes~$\tube[r] \cup \{v\}$ and~$\tube[r] \cup \{v'\}$ for any tube~$\tube[r] \in \tubes(\graphG)$ and distinct neighbors~$v,v'$ of~$\tube[r]$,
+\item the pairs of tubes~$\tube[s] \ssm \{v'\}$ and~$\tube[s] \ssm \{v\}$ for any tube~$\tube[s] \in \tubes(\graphG)$ and distinct non-disconnecting vertices~$v,v'$ of~$\tube[s]$,
+\end{enumerate}
 \end{corollary}
 
-\begin{proof}
-Consider a $\b{c}$-vector~$\b{e}_v - \b{e}_{v'}$ for two distinct vertices~$v, v'$ in a common connected component of~$\graphG$.
-Let~$\tube[s]$ be a path from~$v$ to~$v'$ in~$\graphG$ and let~$\tube \eqdef \tube[s] \cup \{v\}$ and~$\tube' \eqdef \tube[s] \cup \{v'\}$.
-Then $\{\tube, \tube'\}$ is an extremal exchangeable pair with $\b{c}$-vector~$\b{e}_v - \b{e}_{v'}$.
-\end{proof}
+We derive from \cref{prop:extremalExchangeablePairsGA} and \cref{coro:extremalExchangeablePairsGA} all polytopal realizations of the nested fan, which we can explicitly express using one of the following two equivalent conditions.
+
+%\begin{corollary}
+%Consider a graph~$\graphG$ on~$\ground$ with tubes~$\tubes(\graphG)$ and a height vector~$\b{h} \in \R^{\tubes(\graphG)}$ such that~$\b{h}_{\graphG} = 0$ and
+%\[
+%\b{h}_{\tube} + \b{h}_{\tube'} > \b{h}_{\tube \cup \tube'} + \sum_{\tube[s] \in \connectedComponents(\tube \cap \tube')} \b{h}_{\tube[s]}
+%\]
+%for any pair of tubes~$\{\tube, \tube'\}$ of~$\graphG$ with~$\tube \ssm \{v\} = \tube' \ssm \{v'\}$ where~$v$ is a neighbor of~$\tube'$ and~$v'$ is a neighbor of~$\tube$.
+%Then the nested fan~$\gvectorFan[\graphG]$ is the normal fan of the graph associahedron
+%\[
+%\set{\b{x} \in \R^\ground}{\dotprod{\gvector{\tube}}{\b{x}} \le \b{h}_{\tube} \text{ for any tube } \tube \in \tubes(\graphG)}.
+%\]
+%\end{corollary}
 
 \begin{corollary}
-Consider a graph~$\graphG$ on~$\ground$ with tubes~$\tubes(\graphG)$ and a height vector~$\b{h} \in \R^{\tubes(\graphG)}$ such that~$\b{h}_{\graphG} = 0$ and
-\[
-\b{h}_{\tube} + \b{h}_{\tube'} = \b{h}_{\tube \cup \tube'} + \sum_{\tube[s] \in \connectedComponents(\tube \cap \tube')} \b{h}_{\tube[s]}
-\]
-for any pair of tubes~$\{\tube, \tube'\}$ of~$\graphG$ with~$\tube \ssm \{v\} = \tube' \ssm \{v'\}$ where~$v$ is a neighbor of~$\tube'$ and~$v'$ is a neighbor of~$\tube$.
-Then the nested fan~$\nestedFan(\graphG)$ is the normal fan of the graph associahedron
+Consider a graph~$\graphG$ on~$\ground$ with tubes~$\tubes(\graphG)$ and a height vector~$\b{h} \in \R^{\tubes(\graphG)}$ such that~$\b{h}_{\varnothing} = \b{h}_{\graphG} = 0$ and satisfying one of the two following equivalent conditions:
+\begin{enumerate}[(i)]
+\item $\b{h}_{\tube[r] \cup \{v\}} + \b{h}_{\tube[r] \cup \{v'\}} > \b{h}_{\tube[r] \cup \{v, v'\}} + \b{h}_{\tube[r]}$ for any tube~$\tube[r] \in \tubes(\graphG)$ and distinct neighbors~$v,v'$ of~$\tube[r]$,
+\item $\b{h}_{\tube[s] \ssm \{v'\}} + \b{h}_{\tube[s] \ssm \{v\}} > \b{h}_{\tube[s]} + \b{h}_{\tube[s] \ssm \{v, v'\}}$ for any tube~$\tube[s] \in \tubes(\graphG)$ and distinct non-disconnecting vertices~$v,v'$ of~$\tube[s]$.
+\end{enumerate}
+Then the nested fan~$\gvectorFan[\graphG]$ is the normal fan of the graph associahedron
 \[
@@
 
-We now compute the number of extremal exchangeable pairs of the nested fan.
-For a tube~$\tube$ of~$\graphG$, we denote by~$\nonDisconnecting(\tube)$ the number of non-disconnecting vertices of~$\tube$.
-In other words, it is the number of tubes covered by~$\tube$ in the inclusion poset of all tubes of~$\graphG$.
+We also obtain from \cref{prop:extremalExchangeablePairsGA} the following surprising property.
+
+\begin{corollary}
+Any $\b{c}$-vector supports at least one extremal exchangeable pair.
+\end{corollary}
+
+\begin{proof}
+Consider a $\b{c}$-vector~$\b{e}_v - \b{e}_{v'}$ for two distinct vertices~$v, v'$ in a common connected component of~$\graphG$.
+Let~$\tube[r]$ be a path from~$v$ to~$v'$ in~$\graphG$ and let~$\tube \eqdef \tube[r] \cup \{v\}$ and~$\tube' \eqdef \tube[r] \cup \{v'\}$.
+Then $\{\tube, \tube'\}$ is an extremal exchangeable pair with $\b{c}$-vector~$\b{e}_v - \b{e}_{v'}$.
+\end{proof}
+
+We derive from~\cref{coro:extremalExchangeablePairsGA} the number of extremal exchangeable pairs of the nested fan.
+For a tube~$\tube$ of~$\graphG$, we denote by~$\neighbors(\tube)$ the number of neighbors of~$\tube$ and by~$\nonDisconnecting(\tube)$ the number of non-disconnecting vertices of~$\tube$.
+In other words, it $\neighbors(\tube)$ (resp.~$\nonDisconnecting(\tube)$) is the number of tubes covering~$\tube$ (resp.~covered by~$\tube$) in the inclusion poset of all tubes of~$\graphG$.
+
+\begin{corollary}
+\label{coro:numberExtremalExchangeablePairsGA}
+The nested fan~$\gvectorFan[\graphG]$ has~$\!\!\!\!
+\sum\limits_{\tube[r] \in \tubes(\graphG)} \!\!
+\binom{\neighbors(\tube[r])}{2} = \!\!\!\!
+\sum\limits_{\tube[s] \in \tubes(\graphG)} \!\!
+\binom{\nonDisconnecting(\tube[s])}{2}$ extremal exchangeable pairs.
+\end{corollary}
+
+%\begin{proof}
+%By \cref{prop:extremalExchangeablePairsGA}, extremal exchangeable pairs are in bijection with quadruples~$(\tube[r], \tube[t], \tube[t'], \tube[s])$ of tubes of~$\graphG$ where~$\tube[t]$ and~$\tube[t']$ are distinct tubes covering~$\tube[r]$ and covered by~$\tube[s]$ in the inclusion poset of all tubes of~$\graphG$.
+%The result immediately follows.
+%\end{proof}
+
+The formula of \cref{coro:numberExtremalExchangeablePairsGA} can be made more explicit for specific families of graph associahedra discussed in the introduction and illustrated in \cref{fig:specialGraphAssociahedra}.
 
 \begin{proposition}
-\label{prop:numberExtremalExchangeablePairsGA}
-The nested fan~$\nestedFan(\graphG)$ has~$\sum_{\tube \in \tubes(\graphG)} \binom{\nonDisconnecting(\tube)}{2}$ extremal exchangeable pairs.
-\end{proposition}
-
-\begin{proof}
-By \cref{prop:extremalExchangeablePairsGA}, extremal exchangeable pairs are in bijection with triples~$(\tube, \tube[s], \tube[s'])$ of tubes of~$\graphG$ where~$\tube[s]$ and~$\tube[s']$ are distinct tubes covered by~$\tube$ in the inclusion poset of all tubes of~$\graphG$.
-The result immediately follows.
-\end{proof}
-
-The formula of \cref{prop:numberExtremalExchangeablePairsGA} can be made more explicit for specific families of graph associahedra
-
-\begin{proposition}
-The number of extreme exchangeable pairs of the nested fan~$\nestedFan(\graphG)$ is:
+The number of extreme exchangeable pairs of the nested fan~$\gvectorFan[\graphG]$ is:
 \begin{itemize}
@@
 %\begin{example}
-%The formula of \cref{prop:numberExtremalExchangeablePairsGA} can be made more explicit for specific families of graph associahedra:
+%The formula of \cref{coro:numberExtremalExchangeablePairsGA} can be made more explicit for specific families of graph associahedra:
 %\begin{itemize}
@@
 \begin{proposition}
-The type cone~$\typeCone(\nestedFan(\graphG))$ is simplicial if and only if~$\graphG$ is a path.
+The type cone~$\typeCone(\gvectorFan[\graphG])$ is simplicial if and only if~$\graphG$ is a path.
 \end{proposition}

### 2018-10-12 thirdPaper/draft/typeConeAssociahedra.tex
minor corrections

@@
 Combinatorially, the $\quiver$-associahedron is a polytopal realization of the non-kissing complex of~$\quiver$, defined as the simplicial complex of all collections of walks on the blossoming quiver~$\quiver\blossom$ which are pairwise non-kissing.
-The non-kissing complex encompasses two families of simplicial complexes studied independently in the literature: on the one hand the grid associahedra introduced by T.~K.~Petersen, P.~Pylyavskyy and D.~Speyer in~\cite{PetersenPylyavskyySpeyer} for a staircase shape, studied by F.~Santos, C.~Stump and V.~Welker~\cite{SantosStumpWelker} for rectangular shapes, and extended by T.~McConville in~\cite{McConville} for arbitrary grid shapes; and on the other hand the Stokes polytopes and accordion associahedra studied b Y.~Baryshnikov~\cite{Baryshnikov}, F.~Chapoton~\cite{Chapoton-quadrangulations}, A.~Garver and T.~McConville~\cite{GarverMcConville} and T.~Manneville and V.~Pilaud~\cite{MannevillePilaud-accordion}.
+The non-kissing complex encompasses two families of simplicial complexes studied independently in the literature: on the one hand the grid associahedra introduced by T.~K.~Petersen, P.~Pylyavskyy and D.~Speyer in~\cite{PetersenPylyavskyySpeyer} for a staircase shape, studied by F.~Santos, C.~Stump and V.~Welker~\cite{SantosStumpWelker} for rectangular shapes, and extended by T.~McConville in~\cite{McConville} for arbitrary grid shapes; and on the other hand the Stokes polytopes and accordion associahedra studied by Y.~Baryshnikov~\cite{Baryshnikov}, F.~Chapoton~\cite{Chapoton-quadrangulations}, A.~Garver and T.~McConville~\cite{GarverMcConville} and T.~Manneville and V.~Pilaud~\cite{MannevillePilaud-accordion}.
 These two families naturally extend the classical associahedron, obtained from a line quiver.
@@
 %
-Although we lack a characterization of the exchangeable pairs of the non-kissing complex (see \cref{rem:exchangeablePairsNKC}, we can still describe the linear dependence among the $\b{g}$-vectors involved in a flip.
+Although we lack a characterization of the exchangeable pairs of the non-kissing complex (see \cref{rem:exchangeablePairsNKC}), we can still describe the linear dependence among the $\b{g}$-vectors involved in a flip.
 The following statement is partially proved in~\cite[Thm.~4.17]{PaluPilaudPlamondon}.
@@
 
+\para{Numerology}
+%
 The following result will also be essential in our discussion.
@@
 
+\para{Two families of examples: grid and dissection quivers}
+%
+We conclude this recollections on non-kissing complexes by two families of examples.
+\vincent{TODO}
+
+\bigskip
 We are now ready to describe the type cone of the non-kissing fan~$\gvectorFan[\quiver]$.
-We first treat the case when~$\quiver$ has no self-kissing walks, which includes the case of the classical associahedron.
+We first treat the case when~$\quiver$ has no self-kissing walks, which includes both grid and dissection quivers, thus in particular the case of the classical associahedron.
 We show that the type cone is then simplicial which gives another proof of \cref{thm:simplicialTypeConeAsso} and \cref{coro:descriptionAllAsso}.

### 2018-10-26 thirdPaper/draft/typeConeAssociahedra.tex
unique exchange relation property

@@
 \begin{itemize}
-\item We manage to extend their results to other families of $\b{g}$-vector fans: first to all $\b{g}$-vector fans of finite type cluster algebras acyclic or not (whose polytopality was only proved recently in~\cite{HohlwegPilaudStella}), then to all $\b{g}$-vector fans of the $\tau$-tilting finite gentle algebras (whose polytopality was proved recently in~\cite{PaluPilaudPlamondon}), and finally to the nested fans of graph associahedra (whose polytopality was studied in~\cite{CarrDevadoss, Devadoss, Postnikov, FeichtnerSturmfels, Zelevinsky}).
+\item We manage to extend their results to other families of $\b{g}$-vector fans: first to all $\b{g}$-vector fans of finite type cluster algebras acyclic or not (whose polytopality was only proved recently in~\cite{HohlwegPilaudStella}), then to all $\b{g}$-vector fans of the $\tau$-tilting finite gentle algebras (whose polytopality was proved recently in~\cite{PaluPilaudPlamondon-nonkissing}), and finally to the nested fans of graph associahedra (whose polytopality was studied in~\cite{CarrDevadoss, Devadoss, Postnikov, FeichtnerSturmfels, Zelevinsky}).
 \item We have a simpler proof, only based on the transformation between the classical descriptions of a polytope of the form~$\set{\b{x} \in \R^n}{\b{G}\b{x} \le \b{h}}$ and~$\set{\b{z} \in \R^N}{\b{K}\b{z} = \b{K}\b{h} \text{ and } \b{z} \ge 0}$ (this transformation is standard in optimization).
@@
 \begin{definition}
-\label{def:coherent}
-We say that the fan~$\Fan$ is \defn{coherent} if for any two exchangeable rays~$\ray, \ray'$ of~$\Fan$, the linear dependence
-\vincent{Not sure of the choice of the name.}
+\label{def:uerp}
+We say that two exchangeable rays~$\ray, \ray'$ of~$\Fan$ admit a \defn{unique exchange relation} when the linear dependence
 \[
@@
 These rays are thus called \defn{forced rays} for the exchangeable pair~$\{\ray, \ray'\}$.
+
+We say that the fan~$\Fan$ has the \defn{unique exchange property} if any two exchangeable rays~$\ray, \ray'$ of~$\Fan$ admit a unique exchange relation
 \end{definition}
 
-When~$\Fan$ is coherent, we change the notation~$\coefficient[{\ray[s]}][\rays][\rays']$ to~$\coefficient$ and we obtain that the type cone of~$\Fan$ is expressed as
+When~$\Fan$ has the unique exchange relation property, we change the notation~$\coefficient[{\ray[s]}][\rays][\rays']$ to~$\coefficient$ and we obtain that the type cone of~$\Fan$ is expressed as
 \[
@@
 \begin{definition}
-In a coherent fan~$\Fan$, an \defn{extremal exchangeable pair} is a pair of exchangeable rays~$\{\ray,\ray'\}$ such that the corresponding inequality~${\sum_{\ray[s] \in \rays \cup \rays'} \coefficient \, \b{h}_{\ray[s]} > 0}$ defines a facet of the type cone~$\typeCone(\Fan)$.
+In a fan~$\Fan$ with the unique exchange relation property, an \defn{extremal exchangeable pair} is a pair of exchangeable rays~$\{\ray,\ray'\}$ such that the corresponding inequality~${\sum_{\ray[s] \in \rays \cup \rays'} \coefficient \, \b{h}_{\ray[s]} > 0}$ defines a facet of the type cone~$\typeCone(\Fan)$.
 \end{definition}
 
-In this paper, we will only consider coherent fans, and our objective will be to describe their extremal exchangeable pairs.
+In this paper, we will only consider fans with the unique exchange relation property, and our objective will be to describe their extremal exchangeable pairs.
 
@@
 
-Gentle associahedra were constructed by Y.~Palu, V.~Pilaud and P.-G.~Plamondon~\cite{PaluPilaudPlamondon} in the context of support $\tau$-tilting for gentle algebras.
+Gentle associahedra were constructed by Y.~Palu, V.~Pilaud and P.-G.~Plamondon~\cite{PaluPilaudPlamondon-nonkissing} in the context of support $\tau$-tilting for gentle algebras.
 For a given $\tau$-tilting finite gentle quiver~$\quiver$ (defined in the next section), the $\quiver$-associahedron~$\Asso[\quiver]$ is a simple polytope which encodes certain representations of~$\quiver$ and their $\tau$-tilting relations.
@@
 
-We present the definitions and properties of the non-kissing complex of a gentle quiver, following the presentation of~\cite{PaluPilaudPlamondon}.
+We present the definitions and properties of the non-kissing complex of a gentle quiver, following the presentation of~\cite{PaluPilaudPlamondon-nonkissing}.
 
@@
 The (reduced) \defn{non-kissing complex} of~$\quiver$ is the simplicial complex~$\NKC$ whose faces are the collections of pairwise non-kissing proper walks of~$\quiver$.
-As shown in~\cite[Thm.~2.46]{PaluPilaudPlamondon}, this simplicial complex is a combinatorial model for the support $\tau$-tilting complex on $\tau$-rigid modules over~$kQ/I$.
+As shown in~\cite[Thm.~2.46]{PaluPilaudPlamondon-nonkissing}, this simplicial complex is a combinatorial model for the support $\tau$-tilting complex on $\tau$-rigid modules over~$kQ/I$.
 The quiver~$\quiver$ is called \defn{$\tau$-tilting finite} or \defn{non-kissing finite} when this complex is finite (in other words, $\quiver$ has finitely may non-kissing walks).
@@
 As the fans are $3$-dimensional, we intersect them with the sphere and stereographically project them from the direction~$(-1,-1,-1)$.
-Illustration from~\cite{PaluPilaudPlamondon}.}
+Illustration from~\cite{PaluPilaudPlamondon-nonkissing}.}
 	\label{fig:nonkissingFans}
@@
 
-\begin{theorem}[{\cite[Thm.~4.17]{PaluPilaudPlamondon}}]
+\begin{theorem}[{\cite[Thm.~4.17]{PaluPilaudPlamondon-nonkissing}}]
 For any non-kissing finite gentle quiver~$\quiver$, the set of cones
@@
 
-It is proved in~\cite[Thm.~4.27]{PaluPilaudPlamondon} that the non-kissing fan comes from a polytope.
+It is proved in~\cite[Thm.~4.27]{PaluPilaudPlamondon-nonkissing} that the non-kissing fan comes from a polytope.
 For a walk~$\omega$, denote by~$\KN(\omega)$ the sum over all other walks~$\omega'$ of the number of kisses between~$\omega$~and~$\omega'$.
 
-\begin{theorem}[{\cite[Thm.~4.27]{PaluPilaudPlamondon}}]
+\begin{theorem}[{\cite[Thm.~4.27]{PaluPilaudPlamondon-nonkissing}}]
 For any non-kissing finite gentle quiver~$\quiver$, the non-kissing fan~$\gvectorFan[\quiver]$ is the normal fan of the gentle associahedron~$\Asso[\quiver]$, defined as the intersection of the half-spaces~$\set{\b{x} \in \R^{Q_0}}{\dotprod{\gvector{\omega}}{\b{x}} \le \KN(\omega)}$ for all walks~$\omega \in \properWalks$.
@@
 Although we lack a characterization of the exchangeable pairs of the non-kissing complex (see \cref{rem:exchangeablePairsNKC}), we can still describe the linear dependence among the $\b{g}$-vectors involved in a flip.
-The following statement is partially proved in~\cite[Thm.~4.17]{PaluPilaudPlamondon}.
+The following statement is partially proved in~\cite[Thm.~4.17]{PaluPilaudPlamondon-nonkissing}.
 
@@
 \]
-In other words, the non-kissing fan of~$\quiver$ is coherent.
+In other words, the non-kissing fan of~$\quiver$ has the unique exchange relation property.
 \item The $\b{c}$-vector orthogonal to all $\b{g}$-vectors~$\gvector{\lambda}$ for~$\lambda \in F \cap F'$ is the multiplicity vector~$\multiplicityVector_{\sigma}$ of the vertices of the substring~$\sigma$ of~$\omega$ and~$\omega'$.
@@
 \begin{proof}
-Points~(i), (iii) and~(iv) where shown in~\cite[Prop.~2.33, Thm.~4.17 \& Prop~4.16]{PaluPilaudPlamondon}.
+Points~(i), (iii) and~(iv) where shown in~\cite[Prop.~2.33, Thm.~4.17 \& Prop~4.16]{PaluPilaudPlamondon-nonkissing}.
 \vincent{Point~(ii) to prove.}
@@
 We say that a string~$\sigma$ is \defn{distinguishable} if it is the distinguished string of an exchangeable pair.
-Note that an equivalent definition of distinguishable strings is given in~\cite[Def.~2.30]{PaluPilaudPlamondon}.
+Note that an equivalent definition of distinguishable strings is given in~\cite[Def.~2.30]{PaluPilaudPlamondon-nonkissing}.
 We denote by~$\distinguishableStrings$ the set of distinguishable strings of~$\quiver$.
@@
 
-\begin{proposition}[{\cite[3.68]{PaluPilaudPlamondon}}]
+\begin{proposition}[{\cite[3.68]{PaluPilaudPlamondon-nonkissing}}]
 \label{prop:bijectionStringsWalks}
@@
 For a string~$\sigma$ of~$\quiver$, we denote by $\sigma\hR$ (resp.~$\sigma\cR$) the unique string of the blossoming quiver~$\quiver\blossom$ of the form $\sigma\hR = \sigma \alpha_1^{-1} \alpha_2 \dots \alpha_\ell$ (resp.~$\sigma\cR = \sigma \alpha_1 \alpha_2^{-1} \dots \alpha_\ell^{-1}$) with~$\ell \ge 1$ and~${\alpha_1, \dots, \alpha_\ell \in Q_1}$ and such that~$t(\alpha_\ell)$ (resp.~$s(\alpha_\ell)$) is a blossom of~$\quiver\blossom$.
-These notations are motivated by the representation of strings used in~\cite{ButlerRingel, PaluPilaudPlamondon}, and the terminology usually says that~$\sigma\hR$ (resp.~$\sigma\cR$) is obtained by adding a \defn{hook} (resp.~\defn{cohook}) to~$\sigma$.
+These notations are motivated by the representation of strings used in~\cite{ButlerRingel, PaluPilaudPlamondon-nonkissing}, and the terminology usually says that~$\sigma\hR$ (resp.~$\sigma\cR$) is obtained by adding a \defn{hook} (resp.~\defn{cohook}) to~$\sigma$.
 We define similarly~$\hL\sigma$ (resp.~$\cL\sigma$).
@@
 It seems that two exchangeable walks are always kissing along a single distinguishable string.
-We need to prove that to see that the non-kissing fan is coherent (because for a pair of exchangeable walks, I can completely reconstruct the $\b{g}$-vector dependence of the flip if I know there distinguished substring).
+We need to prove that to see that the non-kissing fan has the unique exchange relation property (because for a pair of exchangeable walks, I can completely reconstruct the $\b{g}$-vector dependence of the flip if I know there distinguished substring).
 Note however that
@@
 \item exchangeable pairs might kiss along additional non-distinguishable strings (example: just a loop),
-\item non-exchangeable walks might kiss along a single distinguishable string (example: see the cyclic triangle in~\cite{PaluPilaudPlamondon}).
-\item non-exchangeable walks might kiss along two or more distinguishable strings (example: see the cyclic triangle in~\cite{PaluPilaudPlamondon}).
+\item non-exchangeable walks might kiss along a single distinguishable string (example: see the cyclic triangle in~\cite{PaluPilaudPlamondon-nonkissing}).
+\item non-exchangeable walks might kiss along two or more distinguishable strings (example: see the cyclic triangle in~\cite{PaluPilaudPlamondon-nonkissing}).
 \end{enumerate}
@@
 \]
-In other words, the nested fan of~$\graphG$ is coherent.
+In other words, the nested fan of~$\graphG$ has the unique exchange relation property.
 \item The $\b{c}$-vector orthogonal to all $\b{g}$-vectors~$\gvector{\tube[s]}$ for~$\tube[s] \in \tubing \cap \tubing'$ is~$\b{e}_v - \b{e}_{v'}$.

### 2018-11-05 secondPaper/FPSAC/figures/lozenge.tex
FPSAC

--- 2018-10-08 secondPaper/accordionComplexSurfaces.tex
@@
-\documentclass{amsart}
-
-\usepackage[T1]{fontenc}
-\usepackage{enumerate, amsmath, amsfonts, amssymb, amsthm, mathrsfs, wasysym, graphics, graphicx, xcolor, url, hyperref, hypcap, xargs, multicol, pdflscape, multirow, hvfloat, array, ae, aecompl, pifont, mathtools, a4wide, float, blkarray}
-\usepackage{marginnote}
-\hypersetup{colorlinks=true, citecolor=darkblue, linkcolor=darkblue}
-\usepackage[all]{xy}
-\usepackage{tikz}
-\usepackage{tkz-graph}
-\usetikzlibrary{trees, decorations, decorations.markings, shapes, arrows, matrix, calc, fit, intersections, patterns, angles}
-\graphicspath{{figures/}}
-\makeatletter\def\input@path{{figures/}}\makeatother
-\usepackage{caption}
-\captionsetup{width=\textwidth}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% theorems
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{corollary}[theorem]{Corollary}
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{conjecture}[theorem]{Conjecture}
-\newtheorem*{theorem*}{Theorem}%[section]
-
-\theoremstyle{definition}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem{example}[theorem]{Example}
-\newtheorem{remark}[theorem]{Remark}
-\newtheorem{question}[theorem]{Question}
-\newtheorem{notation}[theorem]{Notation}
-\newtheorem{assumption}[theorem]{Assumption}
-\newtheorem{convention}[theorem]{Convention}
-
-% math special letters
-\newcommand{\R}{\mathbb{R}} % reals
-\newcommand{\N}{\mathbb{N}} % naturals
-\newcommand{\Z}{\mathbb{Z}} % integers
-\newcommand{\C}{\mathbb{C}} % complex
-\newcommand{\I}{\mathbb{I}} % set of integers
-\newcommand{\HH}{\mathbb{H}} % hyperplane
-\newcommand{\K}{k} % field
-\newcommand{\fA}{\mathfrak{A}} % alternating group
-\newcommand{\fS}{\mathfrak{S}} % symmetric group
-\newcommand{\cA}{\mathcal{A}} % algebra
-\newcommand{\cC}{\mathcal{C}} % collection
-\newcommand{\cS}{\mathcal{S}} % ground set
-\newcommand{\uR}{\underline{R}} % underline set
-\newcommand{\uS}{\underline{S}} % underline set
-\newcommand{\uT}{\underline{T}} % underline set
-\newcommand{\oS}{\overline{S}} % overline set
-\newcommand{\ucS}{\underline{\cS}} % underline ground set
-\renewcommand{\b}[1]{\mathbf{#1}} % bold letters
-\newcommand{\h}{\widehat} % hat letters
-
-% math commands
-\newcommand{\set}[2]{\left\{ #1 \;\middle|\; #2 \right\}} % set notation
-\newcommand{\bigset}[2]{\big\{ #1 \;\big|\; #2 \big\}} % big set notation
-\newcommand{\Bigset}[2]{\Big\{ #1 \;\Big|\; #2 \Big\}} % Big set notation
-\newcommand{\setangle}[2]{\left\langle #1 \;\middle|\; #2 \right\rangle} % set notation
-\newcommand{\ssm}{\smallsetminus} % small set minus
-\newcommand{\dotprod}[2]{\left\langle \, #1 \; \middle| \; #2 \, \right\rangle} % dot product
-\newcommand{\symdif}{\,\triangle\,} % symmetric difference
-\newcommand{\one}{{1\!\!1}} % the all one vector
-\newcommand{\eqdef}{\mbox{\,\raisebox{0.2ex}{\scriptsize\ensuremath{\mathrm:}}\ensuremath{=}\,}} % :=
-\newcommand{\defeq}{\mbox{~\ensuremath{=}\raisebox{0.2ex}{\scriptsize\ensuremath{\mathrm:}} }} % =:
-\newcommand{\simplex}{\triangle} % simplex
-\renewcommand{\implies}{\Rightarrow} % imply sign
-\newcommand{\transpose}[1]{{#1}^t} % transpose matrix
-
-% operators
-\DeclareMathOperator{\conv}{conv} % convex hull
-\DeclareMathOperator{\vect}{vect} % linear span
-\DeclareMathOperator{\cone}{cone} % cone hull
-\DeclareMathOperator{\inv}{inv} % inversions
-\DeclareMathOperator{\ascents}{asc} % ascents
-\DeclareMathOperator{\descents}{des} % descents
-
-% others
-\newcommand{\fref}[1]{Figure~\ref{#1}} % reference figures
-\newcommand{\ie}{\textit{i.e.}~} % id est
-\newcommand{\eg}{\textit{e.g.}~} % exempli gratia
-\newcommand{\Eg}{\textit{E.g.}~} % exempli gratia
-\newcommand{\apriori}{\textit{a priori}} % a priori
-\newcommand{\viceversa}{\textit{vice versa}} % vice versa
-\newcommand{\versus}{\textit{vs.}~} % versus
-\newcommand{\aka}{\textit{a.k.a.}~} % also known as
-\newcommand{\perse}{\textit{per se}} % per se
-\newcommand{\ordinal}{\textsuperscript{th}} % th for ordinals
-\newcommand{\ordinalst}{\textsuperscript{st}} % st for ordinals
-\definecolor{darkblue}{rgb}{0,0,0.7} % darkblue color
-\definecolor{green}{RGB}{57,181,74} % green color
-\definecolor{violet}{RGB}{147,39,143} % violet color
-\newcommand{\red}{\color{red}} % red command
-\newcommand{\green}{\color{green}} % green command
-\newcommand{\darkblue}{\color{darkblue}} % darkblue command
-\newcommand{\defn}[1]{\textsl{\darkblue #1}} % emphasis of a definition
-\newcommand{\para}[1]{\medskip\noindent\textit{#1.}} % paragraph
-\renewcommand{\topfraction}{1} % possibility to have one page of pictures
-\renewcommand{\bottomfraction}{1} % possibility to have one page of pictures
-\newcommand{\ex}{_{\textrm{exm}}} % examples
-\newcommand{\pa}{_{\textrm{pa}}} % path
-\newcommand*\circled[1]{\tikz[baseline=(char.base)]{\node[shape=circle,draw,inner sep=1pt, scale=.7] (char) {#1};}}
-
-% marginal comments
-\usepackage{todonotes}
-\newcommand{\yann}[1]{\todo[color=red!30]{#1 --- Y.}}
-\newcommand{\vincent}[1]{\todo[color=blue!30]{#1 \\ \hfill --- V.}}
-\newcommand{\pierreguy}[1]{\todo[color=green!30]{#1 \\ \hfill --- PG.}}
-
-% SPECIFIC NON-KISSING COMPLEX
-
-% COMBINATORICS
-% quiver
-\newcommand{\blossom}{^\text{\ding{96}}} % blossom
-\newcommand{\Enrs}[1]{E_{nr}^{s}(#1)}
-\newcommand{\Ers}[1]{E_{r}^{s}(#1)}
-\newcommand{\Enrt}[1]{E_{nr}^{t}(#1)}
-\newcommand{\Ert}[1]{E_{r}^{t}(#1)}
-
-% walks
-\newcommand{\peaks}[1]{\mathsf{peaks}(#1)} % peaks
-\newcommand{\deeps}[1]{\mathsf{deeps}(#1)} % deeps
-\newcommand{\distinguishedWalk}[2]{\mathsf{dw}(#1,#2)} % distinguished walk
-\newcommand{\distinguishedArrows}[2]{\mathsf{da}(#1,#2)} % distinguished arrows
-\newcommand{\distinguishedString}[2]{\mathsf{ds}(#1,#2)} % distinguished string
-\newcommand{\distinguishedSign}[2]{\varepsilon(#1,#2)} % distinguished sign
-
-% non-kissing complex, lattice, flip graph
-\newcommand{\kn}{\kappa} % kissing number
-\newcommand{\KN}{\textsc{kn}} % Kissing Number
-\newcommandx{\NKC}[1][1=\bar Q]{\mathcal{K}_{\mathrm{nk}}(#1)} % non-kissing complex
-\newcommandx{\RNKC}[1][1=\bar Q]{\mathcal{C}_{\mathrm{nk}}(#1)} % non-kissing complex
-\newcommandx{\NKL}[1][1=\bar Q]{\mathcal{L}_{\mathrm{nk}}(#1)} % non-kissing lattice
-\newcommandx{\NKG}[1][1=\bar Q]{\mathcal{G}_{\mathrm{nk}}(#1)} % non-kissing flip graph
-\newcommandx{\NFC}[1][1=\bar Q]{\mathcal{C}_{\mathrm{nf}}(#1)} % non-friendly complex
-\newcommand{\peak}{\mathrm{peak}} % bottom dissection
-\newcommand{\deep}{\mathrm{deep}} % top dissection
-\newcommand{\reversed}[1]{#1^{\mathrm{rev}}} % reverse all arrows
-\renewcommand{\top}{\mathrm{top}} % top
-\newcommand{\bottom}{\mathrm{bot}} % bottom
-\newcommand{\walk}{\operatorname{\omega}} % walk (of a curve)
-
-% accordion and slalom complexes
-\newcommand{\surface}{\mathcal{S}} % an orientable surface
-\newcommand{\dual}{^*} % duality
-\newcommand{\dissection}{\mathrm{D}} % dissection of a marked surface
-\newcommand{\vertices}{\mathcal{V}} % vertices of a dissection
-\newcommand{\edges}{\mathcal{E}} % edges of a dissection
-\newcommand{\faces}{\mathcal{F}} % faces of a dissection
-\renewcommandx{\AC}[1][1=\dissection]{\mathcal{K}_{\mathrm{acc}}(#1)} % accordion complex
-\newcommandx{\RAC}[1][1=\dissection]{\mathcal{C}_{\mathrm{acc}}(#1)} % reduced accordion complex
-\newcommandx{\SC}[1][1=\dissection\dual]{\mathcal{K}_{\mathrm{sla}}(#1)} % slalom complex
-\newcommandx{\RSC}[1][1=\dissection\dual]{\mathcal{C}_{\mathrm{sla}}(#1)} % reduced slalom complex
-\newcommandx{\NCC}[1][1={\dissection, \dissection\dual}]{\mathcal{K}_{\mathrm{nc}}(#1)} % non-crossing complex
-\newcommandx{\RNCC}[1][1={\dissection, \dissection\dual}]{\mathcal{C}_{\mathrm{nc}}(#1)} % non-crossing complex
-\newcommand{\curveof}{\operatorname{\gamma}} % curve (of a walk)
-\newcommand{\edgeof}{\operatorname{\varepsilon}} % arc of a vertex
-\newcommand{\dualedgeof}{\operatorname{\varepsilon}\dual} % dual arc of a vertex
-\DeclareRobustCommand{\SSS}{\reflectbox{$\mathsf{Z}$}} % S
-\DeclareRobustCommand{\ZZZ}{\mathsf{Z}} % Z
-\newcommand{\vnext}[1]{#1_{\operatorname{next}}} % next point on the boundary of the surface
-\newcommand{\vprevious}[1]{#1_{\operatorname{prev}}} % previous point on the boundary of the surface
-
-% lattices
-\newcommand{\meet}{\wedge} % meet
-\newcommand{\join}{\vee} % join
-\newcommand{\bigMeet}{\bigwedge} % meet
-\newcommand{\bigJoin}{\bigvee} % join
-\newcommand{\closure}[1]{#1^{\mathrm{cl}}} % closure operator
-\newcommand{\coclosure}[1]{#1^{\mathrm{cocl}}} % coclosure operator
-\newcommand{\uclosure}[1]{#1^{\underline{\mathrm{cl}}}} % loop free closure operator
-\newcommand{\Bicl}[1]{\mathsf{Bic}(#1)} % biclosed sets
-\newcommand{\projDown}{\pi_\downarrow} % down projection map
-\newcommand{\projUp}{\pi^\uparrow} % up projection map
-\newcommand{\JI}{\mathsf{JI}} % join-irreducible
-\newcommand{\MI}{\mathsf{MI}} % meet-irreducible
-\newcommand{\Cong}{\mathsf{Cong}} % congruence lattice
-\newcommand{\con}{\mathrm{con}} % congruence contracting a cover relation
-\newcommand{\ji}{\mathsf{ji}} % join irreducible
-\newcommand{\mi}{\mathsf{mi}} % meet irreducible
-
-% GEOMETRY
-% d-vectors
-\newcommand{\dvector}[1]{\mathbf{d}(#1)} % d-vector of the path #1
-\newcommand{\dvectors}[1]{\mathbf{d}(#1)} % d-vectors of the paths #1
-\newcommandx{\dvectorFan}[1][1=\bar Q]{\mathcal{F}^\mathbf{d}(#1)} % d-vector fan
-% g-vectors
-\newcommand{\gvector}[1]{\mathbf{g}(#1)} % g-vector of the path #1
-\newcommand{\gvectors}[1]{\mathbf{g}(#1)} % g-vectors of the paths #1
-\newcommandx{\gvectorFan}[1][1=\bar Q]{\mathcal{F}^\mathbf{g}(#1)} % g-vector fan
-% c-vectors
-\newcommand{\cvector}[2]{\mathbf{c}(#1 \in #2)} % c-vector of the path #1 in the facet #2
-\newcommand{\cvectors}[1]{\mathbf{c}(#1)} % c-vectors of the paths #1
-\newcommandx{\allcvectors}[1][1=\bar Q]{\mathbf{C}(#1)} % all c-vectors with respect to the initial cluster #1
-\newcommandx{\cvectorFan}[1][1=\bar Q]{\mathcal{F}^\mathbf{c}(#1)} % fan of hyperplanes orthogonal to all c-vectors
-% points, hyperplanes, half-spaces
-\newcommand{\point}[1]{\mathbf{p}(#1)} % vertex of the grid associahedron corresponding to the cluster #1
-\newcommand{\ray}{\mathbf{r}} % ray
-\newcommand{\rays}{\mathbf{R}} % rays
-\newcommand{\hs}{\mathbf{H}^{\le}} % half space
-\newcommand{\HS}[1]{\mathbf{H}^{\le}(#1)} % half space
-\newcommand{\hyp}{\mathbf{H}^{=}} % hyperplane
-\newcommand{\Hyp}[1]{\mathbf{H}^{=}(#1)} % hyperplane
-\newcommand{\fix}[1]{\mathrm{Fix}(#1)} % fix space
-% polytopes
-\newcommandx{\Asso}[2][1=\bar Q,2={}]{\mathsf{Asso}^{#2}(#1)} % associahedron
-\newcommandx{\Zono}[2][1=\bar Q,2={}]{\mathsf{Zono}^{#2}(#1)} % zonotope
-\newcommand{\Fan}{\mathcal{F}} % fan
-\newcommand{\multiplicityVector}{\b{m}} % multiplicity vector
-
-% ALGEBRA
-\newcommand{\Hom}[1]{\operatorname{{\rm Hom}}_{#1}}
-\newcommand{\Ext}[1]{\operatorname{{\rm Ext}}_{#1}}
-\newcommandx{\AR}[1][1=\bar Q]{\mathrm{AR}(#1)} % Auslander-Reiten quiver
-\newcommandx{\tTC}[1][1=\bar Q]{\mathcal{K}^{\textrm{s$\tau$-tilt}}(#1)} % tau-tilting complex
-\newcommand{\rep}{\operatorname{{\rm rep}}}
-\newcommand{\proj}{\operatorname{{\rm proj}}}
-\newcommand{\koszul}{^!} % duality
-
-%% formating the part command
-%\makeatletter
-%\def\part{\@startsection{part}{1}%
-%\z@{.7\linespacing\@plus\linespacing}{.8\linespacing}%
-%{\LARGE\sffamily\centering}}
-%\@addtoreset{section}{part}
-%\makeatother
-%\renewcommand{\thesection}{\arabic{part}.\arabic{section}}
-
-% formating the table of contents
-\makeatletter
-\def\l@section{\@tocline{1}{2pt}{0pc}{}{}}
-\makeatother
-\let\oldtocpart=\tocpart
-\renewcommand{\tocpart}[2]{\bf\large\oldtocpart{#1}{#2}}
-\let\oldtocsection=\tocsection
-\renewcommand{\tocsection}[2]{\bf\oldtocsection{#1}{#2}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\title[Non-kissing and non-crossing complexes for locally gentle algebras]{Non-kissing and non-crossing complexes \\ for locally gentle algebras}
-
-\thanks{YP, VP and PGP were partially supported by the French ANR grant SC3A~(15\,CE40\,0004\,01). VP was partially supported by the French ANR grant CAPPS~(17\,CE40\,0018).}
-
-\author{Yann Palu}
-\address[Yann Palu]{LAMFA, Universit\'e Picardie Jules Verne, Amiens}
-\email{yann.palu@u-picardie.fr}
-\urladdr{\url{http://www.lamfa.u-picardie.fr/palu/}}
-
-\author{Vincent Pilaud}
-\address[Vincent Pilaud]{CNRS \& LIX, \'Ecole Polytechnique, Palaiseau}
-\email{vincent.pilaud@lix.polytechnique.fr}
-\urladdr{\url{http://www.lix.polytechnique.fr/~pilaud/}}
-
-\author{Pierre-Guy Plamondon}
-\address[Pierre-Guy Plamondon]{Laboratoire de Math\'ematiques d'Orsay, Universit\'e Paris-Sud, CNRS, Universit\'e Paris-Saclay}
-\email{pierre-guy.plamondon@math.u-psud.fr}
-\urladdr{\url{https://www.math.u-psud.fr/~plamondon/}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{document}
-
-\begin{abstract}
-Starting from a locally gentle bound quiver, we define on the one hand a simplicial complex, called the non-kissing complex.
-On the other hand, we construct a punctured, marked, oriented surface with boundary, endowed with a pair of dual dissections.
-From those geometric data, we define two simplicial complexes: the accordion complex, and the slalom complex, generalizing work of A. Garver and T. McConville in the case of a disk.
-We show that all three simplicial complexes are isomorphic, and that they are pure and thin.
-In particular, there is a notion of mutation on their facets, akin to $\tau$-tilting mutation.
-Along the way, we also construct inverse bijections between the set of isomorphism classes of locally gentle bound quivers and the set of homeomorphism classes of punctured, marked, oriented surfaces with boundary, endowed with a pair of dual dissections.
-\end{abstract}
-
-\vspace*{-1.3cm}
-\maketitle
-\vspace{-.7cm}
-
-\section{Introduction}
-
-\enlargethispage{.1cm}
-The aim of this paper is to prove that two combinatorial objects, called the \emph{non-kissing complex} and the \emph{non-crossing complex}, are isomorphic.
-Both complexes appeared in different works in specific cases: the non-kissing complex of a grid appeared in \cite{McConville}, while the non-crossing complex of a disk appeared in \cite{GarverMcConville, MannevillePilaud-accordion}.
-It was shown in \cite{PaluPilaudPlamondon} that these complexes are special cases of a more general simplicial complex, defined for any gentle algebra (see also~\cite{BrustleDouvilleMousavandThomasYildirim}).
-
-In order to unify these two objects, we are lead to introduce two generalizations.
-On the algebraic side, the non-kissing complex is extended from the class of gentle algebras to that of locally gentle algebras (which are an infinite-dimensional version of gentle algebras).
-On the geometric side, we construct the non-crossing complex of an arbitrary oriented punctured surface endowed with a pair of dual dissections.
-
-The two main objects of our study will thus be locally gentle algebras and dissections of surfaces.
-Our first main result is that these two classes of objects are essentially the same.
-
-\begin{theorem*}[\ref{thm:bijectionLocallyGentleAndSurfaces}]
-There is an explicit bijection between the set of isomorphism classes of locally gentle bound quivers and the set of homeomorphism classes of oriented punctured marked surfaces with boundary endowed with a pair of dual cellular dissections.
-\end{theorem*}
-
-On the algebraic side, we extend the study of walks from the gentle case~\cite{McConville, PaluPilaudPlamondon} to the locally gentle case, and define a notion of compatibility called non-kissing (see Section \ref{sec:nonKissingComplex}).
-On the geometric side, we extend the study of dissections, accordions and slaloms from the case of the disk~\cite{GarverMcConville, MannevillePilaud-accordion} to the case of an arbitrary surface, and define a notion of compatibility called non-crossing (see Section \ref{sec:accordionSlalomNonCrossingComplexes}).
-The combinatorial information contained in these notions is encoded in simplicial complexes: the non-kissing complex~$\NKC$ and the non-crossing complex~$\NCC$.
-
-\begin{theorem*}[\ref{thm:complexesCoincide}]
-The complexes~$\NKC$ and~$\NCC$ are isomorphic.
-\end{theorem*}
-
-Finally, we show in Section \ref{sec:propertiesOfComplexes} that these complexes are combinatorially very well-behaved.
-
-\begin{theorem*}[\ref{prop:purity} and \ref{coro:thin}]
-The complexes~$\NKC$ and~$\NCC$ are pure and thin.  Their dimension is computed, and mutation is explicitly described.
-\end{theorem*}
-
-We end in Section \ref{sec:vectors} with a discussion of~$\b{g}$-vectors,~$\b{c}$-vectors and~$\b{d}$-vectors associated to walks and curves.
-Consequences on the representation theory of locally gentle algebras will be investigated in a future project.
-
-Finally, let us briefly review the algebraic and geometric objects which appear in this paper.
-
-Gentle algebras are a class of finite-dimensional associative algebras over a field, defined by generators and relations.
-Their representation theory was first systematically investigated in~\cite{ButlerRingel}, and they have been thouroughly studied since.
-Locally gentle algebras are obtained by dropping the requirement that gentle algebras be finite-dimensional.
-It turns out that their representation theory is also well-behaved \cite{Crawley-Boevey} and that these algebras are Koszul \cite{BessenrodtHolm}.
-Recently, the $\tau$-tilting theory \cite{AdachiIyamaReiten} of gentle algebras has been studied in \cite{PaluPilaudPlamondon, BrustleDouvilleMousavandThomasYildirim}.
-
-Dissections of surfaces, on the other hand, are certain collections of pairwise non-intersecting curves on an orientable surface.
-They have been defined and studied in \cite{Baryshnikov, Chapoton-quadrangulations, GarverMcConville, MannevillePilaud-accordion} in the case where the surface is an unpunctured disk.
-
-The idea of associating a finite-dimensional algebra to a dissection (or a triangulation) of a surface seems to take its roots in the theory of cluster algebras and cluster categories.
-This was first done for triangulations of polygons in \cite{CalderoChapotonSchiffler}, and then for any orientable surface with boundary in \cite{ABCP, Labardini}.  
-The algebra of a dissection as we shall use it in this paper has appeared in \cite{DavidRoeslerSchiffler}.
-In most of the above cases, the algebras obtained are gentle algebras.
-It has also been shown in \cite{BaurCoelhoSimoes} that any gentle algebra is obtained from a dissection of a surface, and that the module category of the algebra can be interpreted by using curves on the surface.
-In the case where the surface is a polygon, the $\tau$-tilting theory of the algebra of a dissection has been studied in \cite{PaluPilaudPlamondon, PilaudPlamondonStella}.
-
-Conversely, the construction of a surface associated to a gentle algebra has appeared in \cite{OpperPlamondonSchroll}.
-We give a different construction of the same surface in this paper, which is obtained by ``glueing'' quadrilaterals to the arrows of the blossoming quiver (as defined in \cite{PaluPilaudPlamondon}, and called ``framed quiver'' in \cite{BrustleDouvilleMousavandThomasYildirim}).
-Our construction has the advantage that it easily yields the two dual dissections of the surface at the same time (the dissection and dual lamination of \cite{OpperPlamondonSchroll}).
-Note that our dissections are always cellular, while those in \cite{BaurCoelhoSimoes} can be arbitrary.
-Remarkably, gentle algebras and surfaces were linked recently in \cite{HaidenKatzarkovKontsevich, LekiliPolishchuk}, where the Fukaya category of the surface is shown to be equivalent to the bounded derived category of the associated gentle~algebra.
-
-\section*{Acknowledgements}
-We thank Sibylle Schroll for discussions on geometric models for gentle algebras, Salvatore Stella for discussions on accordion complexes of dissections of surfaces, and William Crawley-Boevey and Henning Krause for discussions on the representation theory of infinite dimensional algebras.
-
-\section{Non-kissing complex}\label{sec:nonKissingComplex}
-
-We first quickly review the definition of the non-kissing complex of a gentle bound quiver following the presentation of~\cite{PaluPilaudPlamondon} and extend it to locally gentle bound quivers.
-
-\subsection{Locally gentle bound quivers and their blossoming quivers}
-
-We consider a \defn{bound quiver}~$\bar Q = (Q,I)$, formed by a finite quiver~$Q$ and an ideal~$I$ of the path algebra~$kQ$ (the~$k$-vector space generated by all paths in~$Q$, including vertices as paths of length zero, with multiplication induced by concatenation of paths) such that~$I$ is generated by linear combinations of paths of length at least two.
-Note that we \textbf{do not require} that the quotient algebra~$kQ/I$ be finite dimensional.
-The following definition is adapted from~\cite{ButlerRingel}. We note that it is customary to consider non-finite dimensional gentle algebras in the literature, see e.g.~\cite{Schroer}.
-
-\begin{definition}
-\label{def:gentleQuiver}
-A \defn{locally gentle bound quiver}~$\bar Q \eqdef (Q,I)$ is a (finite) bound quiver~where
-\begin{enumerate}[(i)]
-\item each vertex~$a \in Q_0$ has at most two incoming and two outgoing arrows,
-\item the ideal~$I$ is generated by paths of length exactly two,
-\item for any arrow~$\beta \in Q_1$, there is at most one arrow~$\alpha \in Q_1$ such that~$t(\alpha) = s(\beta)$ and~${\alpha\beta\notin I}$ (resp.~$\alpha\beta \in I$) and at most one arrow~$\gamma \in Q_1$ such that~$t(\beta) = s(\gamma)$~and~${\beta\gamma\notin I}$~(resp.~${\beta\gamma \in I}$).
-\end{enumerate}
-The algebra~$kQ/I$ is called a \defn{locally gentle algebra}.
-A \defn{gentle bound quiver} is a locally gentle bound quiver~$\bar Q$ such that the algebra $kQ/I$ is finite-dimensional; $kQ/I$ is then a \defn{gentle algebra}.
-\end{definition}
-
-\begin{definition}
-\label{def:blossomingQuiver}
-A locally gentle bound quiver~$\bar Q$ is \defn{complete} if any vertex~$a \in Q_0$ is incident to either one ($a$ is a leaf) or four arrows ($a$ is an internal vertex).
-The \defn{pruned subquiver} of a quiver~$\bar Q$ is the locally gentle quiver obtained by deleting all leaves of~$\bar Q$ (degree one vertices) and their incident arrows.
-The \defn{blossoming quiver} of a locally gentle bound quiver~$\bar Q$ is the complete locally gentle bound quiver~$\bar Q\blossom$ whose pruned subquiver is~$\bar Q$.
-The vertices of~$Q\blossom_0 \ssm Q_0$ are called \defn{blossom vertices}, and the arrows in~$Q\blossom_1 \ssm Q_1$ are called \defn{blossom arrows}.
-\end{definition}
-
-In other words, $\bar Q\blossom$ is obtained from~$\bar Q$ by adding blossom arrows and blossom vertices at each incomplete vertex of~$\bar Q$ and by completing~$I$ accordingly.
-Examples are represented on \fref{fig:quivers}.
-
-\begin{figure}[t]
-	\capstart
-	\centerline{\includegraphics[scale=.6]{quivers}}
-	\caption{Some locally gentle quivers (top) and their blossoming quivers (bottom).
-Initial vertices are solid and labeled while blossom vertices are hollow, and initial arrows are bold while blossom arrows are thin.}
-	\label{fig:quivers}
-\end{figure}
-
-\begin{remark}
-\label{rem:sizeBlossomingQuiver}
-Note that~$\bar Q\blossom$ has~$2|Q_0|-|Q_1|$ incoming blossom arrows and~$2|Q_0|-|Q_1|$ outgoing blossom arrows.
-Therefore, it has $|Q_0\blossom| = |Q_0| + 2(2|Q_0|-|Q_1|) = 5|Q_0|-2|Q_1|$ vertices and~${|Q_1\blossom| = |Q_1| + 2(2|Q_0|-|Q_1|) = 4|Q_0|-|Q_1|}$ arrows.
-\end{remark}
-
-\subsection{Strings and walks}
-
-The non-kissing complex is constructed using the combinatorics of strings and walks in the quiver~$\bar Q$, whose definitions are now briefly recalled.
-The terminology and notations in the following definitions is borrowed from~\cite{ButlerRingel, Crawley-Boevey}.
-
-For any arrow~$\alpha$ of~$Q$, define a formal inverse~$\alpha^{-1}$ with the properties that~${s(\alpha^{-1}) = t(\alpha)}$, $t(\alpha^{-1}) = s(\alpha)$, $\alpha^{-1}\alpha = \varepsilon_{t(\alpha)}$ and~$\alpha\alpha^{-1} = \varepsilon_{s(\alpha)}$, where~$\varepsilon_v$ is the path of length zero starting and ending at the vertex~$v \in Q_0$.
-
-\begin{definition}
-\label{def:string}
-Let~$\bar Q = (Q,I)$ be a locally gentle bound quiver.
-A \defn{finite string} in~$\bar Q$ is a word of the form
-\(
-\rho = \alpha_1^{\varepsilon_1}\alpha_2^{\varepsilon_2}\cdots \alpha_\ell^{\varepsilon_\ell},
-\)
-where
-	\begin{enumerate}[(i)]
-	\item $\alpha_i \in Q_1$ and~$\varepsilon_i \in \{-1,1\}$ for all~$i \in [\ell]$,
-	\item $t(\alpha_i^{\varepsilon_i}) = s(\alpha_{i+1}^{\varepsilon_{i+1}})$ for all~$i \in [\ell-1]$,
-	\item there is no path~$\pi \in I$ such that~$\pi$ or~$\pi^{-1}$ appears as a factor of~$\rho$, and
-	\item $\rho$ is reduced, in the sense that no factor~$\alpha\alpha^{-1}$ or~$\alpha^{-1}\alpha$ appears in~$\rho$, for~$\alpha \in Q_1$.
-	\end{enumerate}
-The integer~$\ell$ is called the \defn{length} of the string~$\rho$.
-We let~$s(\rho) \eqdef s(\alpha_1^{\varepsilon_1})$ and~$t(\rho) \eqdef t(\alpha_\ell^{\varepsilon_\ell})$ denote the source and target of~$\rho$.
-For each vertex~$a \in Q_0$, there is also a \defn{string of length zero}, denoted by~$\varepsilon_a$, that starts and ends at~$a$.
-\end{definition}
-
-\begin{example}
-With our choice of conventions, we represent the string ${\gamma\beta^{-1}\alpha^{-1}\gamma\beta^{-1}\alpha^{-1}\gamma\delta}$ by
-\[
-\;\vcenter{\hbox{\includegraphics[scale=0.3]{exmString1}}}
-\]
-\end{example}
-
-\begin{definition}
-An oriented cycle~$c$ in~$Q$ such that~$c, c^2 \notin I$ is called \defn{primitive} if it cannot be written as an $n$-th power ($n>1$) of a cycle.
-\end{definition}
-
-\begin{notation}
-If~$c$ is an oriented cycle in~$Q$ such that~$c, c^2 \notin I$, we write:
-\begin{itemize}
-\item $c^\infty$ for the infinite word~$c c c\cdots$,
-\item ${}^\infty c$ for the infinite word~$\cdots c c c$,
-\item $^\infty c^\infty$ for the bi-infinite word~$^\infty c c^\infty$.
-\end{itemize}
-We also define~${}^{-\infty}c \eqdef {}^{\infty}(c^{-1}) = (c^\infty)^{-1}$ and similarly~$c^{-\infty} \eqdef (c^{-1})^\infty = (^\infty c)^{-1}$.
-\end{notation}
-
-\begin{definition}
-An \defn{eventually cyclic string} for~$\bar Q$ is a word~$\rho$ of the form~${}^\infty(c_1^{\varepsilon_1})\sigma (c_2^{\varepsilon_2})^\infty$, where $c_1, c_2$ are oriented cycles in~$\bar Q$ (possibly of length zero) and $\varepsilon_1, \varepsilon_2$ are signs in~$\{\pm 1\}$ such that $c_1^{2\varepsilon_1} \sigma c_2^{2\varepsilon_2}$ is a finite string in~$\bar Q$.
-\end{definition}
-
-\begin{definition}
-A \defn{string} for~$\bar Q$ is a word which is either a finite string or an eventually cyclic infinite string.
-We often implicitly identify the two inverse strings~$\rho$ and~$\rho^{-1}$, and call it an \defn{undirected string} of~$\bar Q$.
-\end{definition}
-
-\begin{notation}
-To avoid distinguishing between finite and (bi-)infinite words, we denote strings as products~$\rho = \prod_{i < \ell < j} \alpha_\ell^{\varepsilon_\ell}$ where~$i < j \in \Z \cup \{\pm \infty\}$, $\varepsilon_\ell\in\{\pm 1\}$ and~$\alpha_\ell \in Q_1$ for all~$i < \ell < j$.
-\end{notation}
-
-\begin{definition}
-\label{def:walk}
-A \defn{walk} of a locally gentle quiver~$\bar Q$ is a maximal string of its blossoming quiver~$\bar Q \blossom$ (meaning that at each end it either reaches a blossom vertex of~$\bar Q \blossom$ or enters an infinite oriented cycle).
-As for strings, we implicitly identify the two inverse walks~$\omega$ and~$\omega^{-1}$, and call it an \defn{undirected walk} of~$\bar Q$.
-\end{definition}
-
-\begin{definition}
-\label{def:substrings}
-A \defn{substring} of a walk~$\omega = \prod_{i < \ell < j} \alpha_\ell^{\varepsilon_\ell}$ of~$\bar Q$ is a string~$\sigma = \prod_{i' < \ell < j'} \alpha_\ell^{\varepsilon_\ell}$ of~$\bar Q$ for some~$i \le i' < j' \le j$, where the inequality~$i \le i'$ (resp.~$j' \le j$) is strict when~$i \ne -\infty$ (resp.~$j \ne \infty$).
-In other words, $\sigma$ is a factor of~$\omega$ such that
-\begin{itemize}
-\item the endpoints of~$\sigma$ are not allowed to be the possible blossom endpoints of~$\omega$,
-\item the position of~$\sigma$ as a factor of~$\omega$ matters (the same string at a different position is considered a different substring).
-\end{itemize}
-Note that the string~$\varepsilon_a$ is a substring of~$\omega$ for each occurence of~$a$ as a vertex of~$\omega$.
-We denote by~$\Sigma(\omega)$ the set of substrings of~$\omega$.
-We use the same notation for undirected walks (of course, substrings of an undirected walk are undirected).
-\end{definition}
-
-\begin{definition}
-\label{def:topBottom}
-We say that the substring~$\sigma = \prod_{i' < \ell < j'} \alpha_\ell^{\varepsilon_\ell}$ is \defn{at the bottom} (resp.~\defn{on top}) of the walk~$\omega = \prod_{i < \ell < j} \alpha_\ell^{\varepsilon_\ell}$ if~$i'=-\infty$ or~$\varepsilon_{i'} = 1$ and~$j'=+\infty$ or~$\varepsilon_{j'} = -1$ (resp.~if~$i'=-\infty$ or~$\varepsilon_{i'} = -1$ and~$j'=\infty$ or~$\varepsilon_{j'} = 1$).
-In other words the (at most) two arrows of~$\omega$ incident to the endpoints of~$\sigma$ point towards~$\sigma$ (resp.~outwards from~$\sigma$).
-We denote by~$\Sigma_\bottom(\omega)$ and~$\Sigma_\top(\omega)$ the sets of bottom and top substrings of~$\omega$ respectively.
-We use the same notations for undirected~walks.
-\end{definition}
-
-\begin{definition}
-\label{def:straightBending}
-A \defn{peak} (resp.~\defn{deep}) of a walk~$\omega$ is a substring of~$\omega$ of length zero which is on top (resp.~at the bottom of~$\omega$).
-A \defn{corner} is either a peak or a deep (in other words, it is a vertex of~$\omega$ where the arrows change direction).
-A walk~$\omega$ is \defn{straight} if it has no corner (\ie if~$\omega$ or~$\omega^{-1}$ is a path in~$\bar Q\blossom$), and \defn{bending} otherwise.
-A \defn{peak walk} (resp.~\defn{deep walk}) is a walk with a unique corner (in other words, it switches orientation only once), which is a peak (resp.~deep).
-For~$a \in Q_0$, we denote by~$a_\peak$ the peak walk with peak at~$a$ and by~$a_\deep$ the deep walk with deep~at~$a$ (note that those are indeed unique by gentleness).
-\end{definition}
-
-\subsection{Non-kissing complex}
-
-We can now define the non-kissing complex of a locally gentle bound quiver following~\cite{McConville, PaluPilaudPlamondon, BrustleDouvilleMousavandThomasYildirim}.
-We start with the kissing relation for walks.
-
-\begin{definition}
-\label{def:kiss}
-Let~$\omega$ and~$\omega'$ be two undirected walks on~$\bar Q$.
-We say that~$\omega$ \defn{kisses}~$\omega'$ if ${\Sigma_\top(\omega) \cap \Sigma_\bottom(\omega')}$ contains a \emph{finite} substring.
-See \fref{fig:kissing}.
-We say that~$\omega$ and~$\omega'$ are \defn{kissing} if~$\omega$ kisses~$\omega'$ or~$\omega'$ kisses~$\omega$ (or both).
-Note that we authorize the situation where the commmon finite substring is reduced to a vertex~$a$, meaning that~$a$ is a peak of~$\omega$ and a deep of~$\omega'$.
-Observe also that~$\omega$ can kiss~$\omega'$ several times, that~$\omega$ and~$\omega'$ can mutually kiss, and that~$\omega$ can kiss itself.
-%
-\begin{figure}[h]
-	\capstart
-	\centerline{\includegraphics[scale=1]{kissing}}
-	\caption{A schematic representation of two kissing walks: $\omega$~kisses~$\omega'$.}
-	\label{fig:kissing}
-\end{figure}
-%
-\end{definition}
-
-\begin{definition}
-\label{def:nKc}
-The \defn{non-kissing complex} of~$\bar Q$ is the simplicial complex~$\NKC$ whose faces are the collections of pairwise non-kissing walks of~$\bar Q$.
-Note that self-kissing walks never appear in~$\NKC$ by definition.
-In contrast, no straight walk can kiss another walk by definition, so that they appear in all facets of~$\NKC$.
-The \defn{reduced non-kissing complex}~$\RNKC$ is the simplicial complex whose faces are the collections of pairwise non-kissing bending walks of~$\bar Q$.
-\end{definition}
-
-\section{Accordion complex, slalom complex, and non-crossing complex}\label{sec:accordionSlalomNonCrossingComplexes}
-
-We now temporarily switch topic and present the accordion complex and the slalom complex of a pair of dual dissections of an orientable surface.
-The latter is directly inspired from the case of a disk treated in~\cite{GarverMcConville}, while the former is obtained by duality as was already observed in the case of a disk in~\cite{MannevillePilaud-accordion}.
-In the general case of arbitrary orientable surfaces, the correspondence between accordions and slaloms requires a little more attention and is treated in Section~\ref{subsec:accordionsVSSlaloms}.
-
-\subsection{Dual dissections of a surface}
-
-\enlargethispage{.1cm}
-Before defining accordions and slaloms, we need a strong notion of pairs of dual dissections of an orientable surface.
-We first review classical definitions of curves, arcs and dissections of a surface adapting it to our setting.
-
-\begin{definition}
-A \defn{marked surface}~$\bar\surface \eqdef (\surface, M)$ is an orientable surface~$\surface$ with boundaries, together with a set~$M$ of marked points which can be on the boundary of~$\surface$ or not.
-For~$V \subset \surface$,
-\begin{enumerate}[(i)]
-\item a \defn{$V$-arc} on~$\bar\surface$ is a curve on~$\surface$ connecting two points of~$V$ and whose interior is disjoint from~$M$ and the boundary of~$\surface$.
-\item a \defn{$V$-curve} on~$\bar\surface$ is a curve on~$\surface$ which at each end either reaches a point of~$V$ or infinitely circles around and finally reaches a puncture of~$M$, and whose interior is disjoint from~$M$ and the boundary of~$\surface$.
-\end{enumerate}
-As usual, curves and arcs are considered up to homotopy relative to their endpoints in~$\surface \ssm M$, and curves homotopic to a boundary are not allowed.
-\end{definition}
-
-\begin{definition}
-\label{def:crossingCurves}
-Two curves or arcs \defn{cross} when they intersect in~their~interior.
-We will always assume that collections of arcs on a surface are in minimal position, in the sense that they cross each other transversaly, and the number of crossings is minimal.
-It is pointed out in \cite{Thurston} that the results in~\cite{FreedmanHassScott} and~\cite{Neumann-Coto} imply that this assumption can always be satisfied (up to homotopy).
-\end{definition}
-
-\begin{definition}
-A \defn{dissection} of~$\bar\surface$ is a collection~$\dissection$ of pairwise non-crossing arcs on~$\bar\surface$.
-The \defn{edges} of~$\dissection$ are its arcs together with the boundary arcs of~$\bar\surface$.
-The \defn{faces} of~$\dissection$ are the connected components of the complement of the union of the edges of~$\dissection$ in the surface~$\surface$.
-We denote by~$\vertices(\dissection)$, $\edges(\dissection)$ and~$\faces(\dissection)$ the sets of vertices, edges and faces of~$\dissection$ respectively.
-The dissection~$\dissection$ is \defn{cellular} if all its faces are topological disks.
-For~$V \subseteq M$, a \defn{$V$-dissection} is a dissection with only $V$-arcs.
-\end{definition}
-
-\begin{convention}
-\textbf{All throughout the paper, all dissections are considered cellular.}
-\end{convention}
-
-\begin{definition}
-Consider a marked surface~$\bar\surface = (\surface, V \sqcup V\dual)$, where~$V$ and~$V\dual$ are two disjoint sets of marked points so that the points of~$V$ and~$V\dual$ that are on the boundary of~$\surface$ alternate.
-A cellular $V$-dissection~$\dissection$ of~$\bar\surface$ and a cellular $V\dual$-dissection~$\dissection\dual$ of~$\bar\surface$ are \defn{dual cellular dissections} if there are pairs of mutually inverse bijections~$V\dual \leftrightarrow \faces(\dissection)$ and~$V \leftrightarrow \faces(\dissection\dual)$, both denoted~$\dual$ in both directions, such that~$\dissection$ has an edge joining its vertices~$u,v \in V$ and separating its faces~$f,g \in  \faces(\dissection)$ if and only if~$\dissection\dual$ has an edge joining its vertices~$f\dual, g\dual \in V\dual$ and separating its faces~$u\dual, v\dual \in \faces(\dissection\dual)$.
-\end{definition}
-
-Some examples of dual cellular dissections on different surfaces are represented in \fref{fig:dissections}.
-%
-\begin{figure}[t]
-	\capstart
-	\centerline{\includegraphics[scale=.7]{dissections}}
-	\caption{Some pairs~$(\dissection, \dissection\dual)$ of dual cellular dissections on different surfaces.
-The dissection~$\dissection$ is in green while its dual dissection~$\dissection\dual$ is~in~red.
-The boundaries of the surfaces are shaded, and the glue symbols indicate how to identify some edges to get the desired surfaces.
-The first two surfaces are disks, the third is a sphere without boundary, the fourth is a cylinder, and the fifth is a torus with one boundary component.}
-	\label{fig:dissections}
-\end{figure}
-%
-Note that contrarily to the usual conventions, the dual vertex~$f\dual$ of a face~$f$ of~$\dissection$ is not always in the interior of the face~$f$.
-More precisely, there are two situations:
-\begin{itemize}
-\item if a face~$f$ has no edges on the boundary of~$\surface$, its dual vertex~$f\dual$ lies in the interior~of~$f$ and is a puncture of~$\bar\surface$,
-\item if a face~$f$ has an edge on the boundary of~$\surface$, then it has exactly one such edge and its dual vertex~$f\dual$ lies on this edge.
-\end{itemize}
-In fact, the second point forces the following characterization of the cellular dissections that admit a dual cellular dissection.
-
-\begin{proposition}
-\label{prop:conditionsDualDissections}
-For a cellular $V$-dissection~$\dissection$ of a marked surface~$\bar\surface = (\surface, V \sqcup V\dual)$, the following assertions are equivalent:
-\begin{enumerate}[(i)]
-\item there exists a cellular $V\dual$-dissection~$\dissection\dual$ of~$\bar\surface$ such that~$\dissection$ and~$\dissection\dual$ are dual cellular dissections,
-\item each face of~$\dissection$ contains exactly one point of~$V\dual$ (in particular, at most one boundary edge).
-\end{enumerate}
-Moreover, the cellular dissection~$\dissection\dual$ is uniquely determined.
-\end{proposition}
-
-\begin{proof}
-We mimick the proof of~\cite[Prop.~1.12]{OpperPlamondonSchroll}.
-The direct implication is immediate by definition.
-Assume conversely that each face~$f$ of~$\dissection$ contains exactly one point~$f\dual$ of~$V\dual$.
-We construct half-edges of~$\dissection\dual$ in each face~$f$ of~$\dissection$ by joining the dual point~$f\dual$ to the middle of each boundary edge of~$f$ that is not a boundary edge of~$\surface$.
-For each edge~$a$ of~$\dissection$, the half-edges incident to the middle of~$a$ in the two faces of~$\dissection$ containing~$a$ form the dual edge~$a\dual$ of~$a$.
-All these dual edges do not cross (as the half-edges do not cross in each face of~$\dissection$) and form the dual cellular dissection~$\dissection\dual$~of~$\dissection$.
-\end{proof}
-
-\begin{definition}
-We consider a set~$B$ of points on the boundary of the surface~$\surface$ such that~$B$ and~$V \cup V\dual$ alternate along the boundary of~$\surface$.
-The points of~$B$ are called the \defn{blossom points}.
-See \eg Figures~\ref{fig:accordions} and~\ref{fig:slaloms} where the blossom points appear as white hollow vertices.
-\end{definition}
-
-\subsection{Accordion complex and slalom complex}
-
-\enlargethispage{.1cm}
-Let~$\bar\surface = (\surface, V \sqcup V\dual)$ be a surface with two disjoint sets~$V$ and~$V\dual$ of marked points, and let~$B$ be the corresponding blossom points on the boundary of~$\surface$.
-We say that a $B$-curve is \defn{external} if it is homotopic to a boundary arc of~$\surface \ssm B$, and \defn{internal} otherwise.
-Note that no $B$-curve can cross an external $B$-curve.
-Consider two dual cellular dissections~$\dissection$ and~$\dissection\dual$ of~$\bar\surface$.
-
-The following definition generalises the one of \cite{MannevillePilaud-accordion} for the case where~$\bar \surface$ is a disk.
-A~very similar definition appears in \cite{BaurCoelhoSimoes} in a slightly different context under the \mbox{name ``permissible~arc''}.
-
-\begin{definition}
-\label{def:accordion}
-A \defn{$\dissection$-accordion} is a $B$-curve~$\alpha$ of~$\bar\surface$ such that whenever~$\alpha$ meets a face~$f$~of~$\dissection$,
-\begin{enumerate}[(i)]
-\item it enters crossing an edge~$a$ of~$f$ and leaves crossing an edge~$b$ of~$f$ (in other words, $\alpha$ is not allowed to circle around~$f\dual$ when~$f\dual$ is a puncture),
-\item the two edges~$a$ and~$b$ of~$f$ crossed by~$\alpha$ are consecutive along the boundary of~$f$,
-\item $\alpha$, $a$ and~$b$ bound a disk inside~$f$ that does not contain~$f\dual{}$.
-\end{enumerate}
-By convention, we also consider that the punctures of~$V$ are $\dissection$-accordions that are considered external.
-If we were working on the universal cover of the surface, the~$\dissection$-accordion associated to a puncture would be the infinite line crossing all (infinitely many) arcs attached to the puncture.
-\end{definition}
-
-\fref{fig:accordions} illustrates some $\dissection$-accordions for the dissections~$\dissection$ of \fref{fig:dissections}.
-
-\begin{figure}[t]
-	\capstart
-	\centerline{\includegraphics[scale=.7]{accordions}}
-	\caption{Some $\dissection$-accordions (in blue) for the dissections~$\dissection$ of \fref{fig:dissections} (in green).}
-	\label{fig:accordions}
-\end{figure}
-
-\begin{remark}
-In Definition~\ref{def:accordion}, observe that
-\begin{itemize}
-\item the edges of~$a$ and~$b$ of~$f$ crossed by~$\alpha$ might coincide, see the second example in Figure~\ref{fig:accordions}.
-\item the first condition is automatically satisfied if~$f\dual$ is not a puncture, \ie when it lies on the boundary of~$\surface$.
-\end{itemize}
-\end{remark}
-
-\begin{definition}
-\label{def:accordionComplex}
-The \defn{$\dissection$-accordion complex}~$\AC$ is the simplicial complex whose faces are the collections of pairwise non-crossing $\dissection$-accordions.
-Note that self-crossing accordions never appear in~$\AC$ by definition.
-In contrast, no external accordion can cross another accordion, so that they appear in all facets of~$\AC$. 
-The \defn{reduced $\dissection$-accordion complex}~$\RAC$ is the simplicial complex whose faces are the collections of pairwise non-crossing internal $\dissection$-accordions.
-\end{definition}
-
-\enlargethispage{.3cm}
-The following definition generalizes the one from~\cite{GarverMcConville} for the case where~$\bar\surface$ is a disk.
-
-\begin{definition}
-\label{def:slalom}
-A \defn{$\dissection\dual$-slalom} is a $B$-curve~$\alpha$ of~$\bar\surface$ such that, whenever~$\alpha$ crosses an edge~$a\dual$ of~$\dissection\dual$ contained in two faces~$f\dual, g\dual$ of~$\dissection\dual$, the marked points~$f$ and~$g$ lie on opposite sides of~$\alpha$ in the union of~$f\dual$ and~$g\dual$ glued along~$a\dual$.
-Here, we consider that~$f$ lies on the right (resp.~left) of~$\alpha$ when~$\alpha$ circles clockwise (resp.~counterclockwise) around~$f$.
-By convention, we also consider that the punctures of~$V$ are $\dissection\dual$-slaloms that are considered external.
-If we were working on the universal cover of the surface, the~$\dissection\dual$-slalom associated to a puncture would be an infinite line never crossing any arc of~$\dissection\dual$.
-\end{definition}
-
-\fref{fig:slaloms} illustrates some $\dissection\dual$-slaloms for the dual dissections~$\dissection\dual$ of \fref{fig:dissections}.
-
-\begin{figure}[t]
-	\capstart
-	\centerline{\includegraphics[scale=.7]{slaloms}}
-	\caption{Some $\dissection\dual$-slaloms (in blue) for the dual dissections~$\dissection\dual$ of \fref{fig:dissections} (in red).}
-	\label{fig:slaloms}
-\end{figure}
-
-\begin{definition}
-\label{def:slalomComplex}
-The \defn{$\dissection\dual$-slalom complex}~$\SC$ is the simplicial complex whose faces are the collections of pairwise non-crossing $\dissection\dual$-slaloms.
-Note that self-crossing slaloms never appear in~$\SC$ by definition.
-In contrast, no external slalom can cross another slalom, so that they appear in all facets of~$\SC$. 
-The \defn{reduced $\dissection\dual$-slalom complex}~$\RSC$ is the simplicial complex whose faces are the collections of pairwise non-crossing internal $\dissection\dual$-slaloms.
-\end{definition}
-
-\subsection{Accordions versus slaloms and the non-crossing complex}
-\label{subsec:accordionsVSSlaloms}
-
-The following statement is illustrated by Figures~\ref{fig:accordions} and~\ref{fig:slaloms}.
-
-\begin{proposition}
-\label{prop:accordionsSlaloms}
-For two dual cellular dissections~$\dissection$ and~$\dissection\dual$, the $\dissection$-accordions are precisely the $\dissection\dual$-slaloms and the (reduced) $\dissection$-accordion complex coincides with the (reduced) $\dissection\dual$-slalom complex.
-\end{proposition}
-
-\begin{proof}
-Let~$\alpha$ be a~$\dissection$-accordion.
-Let~$a$,~$b$,~$c$ be three consecutive edges of~$\dissection$ crossed by~$\alpha$.
-Let~$u \in \dissection$ be the common endpoint of~$a$ and $b$ given by Definition~\ref{def:accordion} and let~$v \in \dissection$ be the common endpoint of~$b$ and~$c$.
-If $u = v$, then the segment of~$\alpha$ between~$a$ and~$c$ stays in the same face of~$\dissection\dual$.
-Otherwise, when crossing~$b$, the accordion~$\alpha$ leaves the face~$u\dual$ of $\dissection\dual$ and enters the face~$v\dual$.
-In the surface obtained by glueing the two cells~$u\dual$ and~$v\dual$ along~$b\dual$, the marked points~$u$ and~$v$ are separated by~$\alpha$.
-Conversely, assume that~$\alpha$ is an curve of~$(\surface, B)$ which is not a $\dissection$-accordion.
-We are in one of the following cases.
-
-Case 1: The curve~$\alpha$ consecutively crosses two edges~$a$ and~$b$ of~$\dissection$ that do not share a common endpoint.
-Let~$f$ be the face of~$\dissection$ that contains the segment of~$\alpha$ between~$a$ and~$b$.
-Consider the connected component of~$f\setminus\alpha$ that does not contain~$f\dual$.
-The boundary of this component contains an edge~$c \in \dissection \setminus \{a\}$ that shares a common endpoint with~$a$.
-Let~$u,v$ be the endpoints~of~$c$.
-Then~$\alpha$ cuts the cells $u\dual,v\dual$ glued along~$c\dual$ into two connected components, one containing both~endpoints~of~$c$.
-
-Case 2: The curve~$\alpha$ consecutively crosses two edges~$a$ and~$b$ of~$\dissection$ that share a unique common endpoint, but the region delimited by~$\alpha$,~$a$ and~$b$ is not a disk.
-Since the dissection~$\dissection$ is cellular, that region has to contain some marked point~$u \in \dissection\dual$.
-One conclude that~$\alpha$ is not a~$\dissection\dual$-slalom similarly as in the first case, by considering the component of~$u\dual \setminus \alpha$ that does not contain~$u$.
-
-Case 3: The curve~$\alpha$ consecutively crosses two edges~$a$ and~$b$ of~$\dissection$ that share two different endpoints, and none of the two regions delimited by~$\alpha$,~$a$ and~$b$ is a disk.
-Since the dissection~$\dissection$ is cellular, both regions have to contain a puncture.
-This contradicts the assumption that the dissections~$\dissection$ and~$\dissection\dual$ are dual to each other.
-
-Case 4: If~$\alpha$ stays inside a $\dissection$-cell, then it rolls around a~$\dissection\dual$ puncture.
-There is a~$\dissection\dual$-edge~$a$ ending in that puncture. When~$\alpha$ crosses~$a$, the puncture stays on the same side of~$\alpha$, hence~$\alpha$ is not a~$\dissection\dual$-slalom.
-\end{proof}
-
-\begin{definition}
-\label{def:noncrossingComplex}
-We call \defn{non-crossing complex} of the pair of dual cellular dissections~$(\dissection, \dissection\dual)$ the simplicial complex~$\NCC \eqdef \AC = \SC$.
-Similarly, the \defn{reduced non-crossing complex} of~$(\dissection, \dissection\dual)$ is~$\RNCC \eqdef \RAC = \RSC$.
-\end{definition}
-
-\begin{remark}
-The $\dissection$-slaloms and the $\dissection\dual$-accordions are defined dually and also coincide.
-\end{remark}
-
-\begin{example}
-When the dissection~$\dissection$ is a classical dissection of a polygon (with no punctures) where each cell has at most one boundary edge, the dual dissection~$\dissection\dual$ is a tree.
-The non-crossing complex in this situation was treated in detail in~\cite{GarverMcConville, MannevillePilaud-accordion}.
-Note that even when the surface~$\surface$ is a disk, we authorize in the present paper both~$\dissection$ and~$\dissection\dual$ to have interior faces and punctures.
-\end{example}
-
-\begin{remark}
-A quick disclaimer about accordion complexes and slalom complexes of arbitrary cellular dissections.
-As stated in Proposition~\ref{prop:conditionsDualDissections}, a cellular dissection~$\dissection$ with a face containing more than one boundary edge does not admit a dual cellular dissection~$\dissection\dual$.
-This prevents the use of the definitions given in this section.
-Although the accordion complex (resp.~slalom complex) could still be defined as in~\cite{MannevillePilaud-accordion} (resp.~\cite{GarverMcConville}) for the disk, the resulting complexes would be joins of smaller accordion complexes (resp.~slalom complexes) defined in this paper.
-See \cite[Prop.~2.4]{MannevillePilaud-accordion} for a detailed statement in the case of the disk.
-\end{remark}
-
-\section{Non-kissing versus non-crossing}
-
-In this section, we show that non-kissing and non-crossing complexes actually coincide.
-Namely, any pair of dual cellular dissections~$(\dissection, \dissection\dual)$ defines a locally gentle bound quiver~$\bar Q_{\dissection}$ (see Section~\ref{subsec:D2Q}) such that the non-crossing complex~$\NCC$ is isomorphic to the non-kissing complex~$\NKC[\bar Q_{\dissection}]$.
-Conversely, any locally gentle bound quiver~$\bar Q$ gives rise to a surface~$\surface_{\bar Q}$ equipped with a pair of dual cellular dissections~$\dissection_{\bar Q}$ and~${{\dissection\dual}\!\!_{\bar Q}}$ (see Section~\ref{subsec:Q2D}) such that the non-kissing complex~$\NKC$ is isomorphic to the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection\dual\!\!_{\bar Q}}]$.
-In fact, we show that the accordion, slalom, and non-kissing complexes can all be pictured in a unique way on the surface.
-Interestingly, via the correspondence between pairs of dual cellular dissections and locally gentle bound quivers, the duality between the dissections~$\dissection$ and~$\dissection\dual$ translates into the Koszul duality between the locally gentle algebras of~$\bar Q$ and~$\bar Q\koszul$.
-Many examples are treated in Section~\ref{subsec:Q2D}.
-
-\subsection{The bound quiver of a dissection}
-\label{subsec:D2Q}
-
-Let~$\dissection$ and~$\dissection\dual$ be two dual cellular dissections of a marked surface~$(\surface, V\sqcup V\dual)$.
-Let $B$ be the set of blossom points.
-
-\begin{definition}
-\label{def:quiverDualDissections}
-The bound quiver of the dissection~$\dissection$ is the bound quiver $\bar Q_{\dissection} = (Q_{\dissection}, I_{\dissection})$ defined as follows:
-\begin{enumerate}[(i)]
-\item the set of vertices of~$Q_{\dissection}$ is the set of edges of $\dissection$;
-\item there is an arrow from~$a$ to~$b$ for each common endpoint~$v$ of~$a$ and~$b$ such that~$b$ comes immediately after~$a$ in the counterclockwise order around~$v$;
-\item the ideal~$I_{\dissection}$ is generated by the paths of length two in~$Q_{\dissection}$ obtained by composing arrows which correspond to triples of consecutive edges in a face of~$\dissection$.
-\end{enumerate}
-The bound quiver of the dissection~$\dissection\dual$ is the bound quiver $\bar Q_{\dissection\dual} = (Q_{\dissection\dual}, I_{\dissection\dual})$ defined by replacing~$\dissection$ by~$\dissection\dual$ in the above.
-\end{definition}
-
-\fref{fig:quiversDissections} illustrates this construction for the dissections of \fref{fig:dissections}.
-
-\begin{figure}[t]
-	\capstart
-	\centerline{\includegraphics[scale=.7]{quiversDissections1}}
-	\medskip
-	\centerline{\includegraphics[scale=.7]{quiversDissections2}}
-	\caption{The quivers associated to the dissections of \fref{fig:dissections}. As stated in Proposition~\ref{prop:dualityKoszul1}, dual dissections give rise to Koszul dual bound quivers.}
-	\label{fig:quiversDissections}
-\end{figure}
-
-\begin{remark}
-The blossoming quiver~$\bar Q_\dissection\blossom$ of the quiver~$\bar Q_\dissection$ is obtained with the same procedure by considering additional blossom vertices along the boundary of the surface.
-See \fref{fig:quiversDissections}.
-\end{remark}
-
-\begin{lemma}
-\label{lemm:quiverOfDissectionIsLocallyGentle}
-The bound quiver~$\bar Q_{\dissection} = (Q_{\dissection}, I_{\dissection})$ is a locally gentle bound quiver.
-\end{lemma}
-
-\begin{proof}
-Each edge~$a$ of~$\dissection$ has two endpoints, and at each endpoint there is at most one edge of~$\dissection$ coming immediately after~$a$ in the clockwise order, and at most one edge of~$\dissection$ coming immediately before~$a$.
-Thus, in~$Q_{\dissection}$, there are at most two arrows leaving~$a$ and at most two arriving in~$a$.
-Among these arrows, those arising from the same endpoint of~$a$ will be composable, and those arising from different endpoints will yield relations.
-Thus $\bar Q_{\dissection}$ is locally gentle.
-\end{proof}
-
-\begin{definition}
-\label{defi:koszulDual}
-The \defn{Koszul dual} of a locally gentle bound quiver~$\bar Q = (Q,I)$ is the bound quiver~$\bar Q\koszul = (Q\koszul, I\koszul)$ defined as follows:
-\begin{enumerate}[(i)]
-\item the quiver~$Q\koszul$ is equal to the opposite quiver of~$Q$, that is, the quiver obtained from~$Q$ by reversing all arrows;
-\item the ideal~$I\koszul$ is generated by the opposites of the paths of length two in~$Q$ that do not appear in~$I$.
-\end{enumerate}
-\end{definition}
-It is seen in \cite{BessenrodtHolm} that the (ungraded version of the) Koszul dual of a locally gentle algebra~$kQ/I$ is isomorphic to~$kQ\koszul/I\koszul$.
-Note that~$\bar Q\koszul$ is locally gentle, and that Koszul duality is an involution and commutes with blossoming:~$(\bar Q\koszul)\koszul = \bar Q$ and~$(\bar Q\koszul)\blossom = (\bar Q\blossom)\koszul$.
-Examples are represented on \fref{fig:koszulQuivers}.
-
-\begin{figure}[t]
-	\capstart
-	\centerline{\includegraphics[scale=.6]{koszulQuivers}}
-	\caption{The Koszul duals of the (blossoming) quivers of \fref{fig:quivers}.}
-	\label{fig:koszulQuivers}
-\end{figure}
-
-The following proposition appears in \cite[Proposition 1.25]{OpperPlamondonSchroll}.
-
-\begin{proposition}
-\label{prop:dualityKoszul1}
-Let~$\dissection$ and~$\dissection\dual$ be two dual cellular dissections of a marked surface~$(\surface, V\sqcup V\dual)$.
-The bound quivers~$\bar Q_{\dissection}$ and~$\bar Q_{\dissection\dual}$ are Koszul dual to each other.
-\end{proposition}
-
-\begin{proof}
-The duality provides a bijection~$a\in (Q_\dissection)_0\mapsto a\dual\in (Q_{\dissection\dual})_0$, and also induces a bijection~${\alpha \in (Q_\dissection)_1 \mapsto \alpha\dual \in (Q_{\dissection\dual})_1}$ with~$s(\alpha\dual) = t(\alpha)\dual$ and~$t(\alpha\dual) = s(\alpha)\dual$.
-Moreover, for any two composable arrows~$\alpha,\beta\in(Q_\dissection)_0$, we have~$\alpha\beta\in I_\dissection$ if and only if~$s(\alpha),t(\alpha),t(\beta)$ are three consecutive edges of a~$\dissection$-cell~$f$, if and only if~$s(\alpha)\dual,t(\alpha)\dual,t(\beta)\dual$ are three consecutive edges in~$\dissection\dual$ ending in~$f\dual$, if and only if~$\beta\dual\alpha\dual\notin I_{\dissection\dual}$.
-\end{proof}
-
-\subsection{The surface of a locally gentle bound quiver}
-\label{subsec:Q2D}
-
-We now associate a surface to a locally gentle bound quiver.
-This construction yields the same surface as the one constructed in \cite{OpperPlamondonSchroll} (see Remark \ref{rem:comparisonWithOPS} for a comparison of the two constructions).
-
-\begin{definition}
-\label{def:surfaceQuiver}
-The surface~$\surface_{\bar Q}$ of a locally gentle bound quiver~$\bar Q = (Q,I)$ is the surface obtained from the blossoming quiver~$\bar Q\blossom$ as follows:
-\begin{enumerate}[(i)]
-\item for each arrow~$\alpha \in Q_1\blossom$, consider a lozenge~$L(\alpha)$ with four (oriented) sides
-\begin{alignat*}{2}
-& \Enrs{\alpha} = [v(\alpha), s(\alpha)] \qquad & \Enrt{\alpha} = [v(\alpha), t(\alpha)] \qquad & \text{(colored green)} \\
-\text{and} \qquad & \Ers{\alpha} = [f\dual(\alpha), s(\alpha)] \qquad & \Ert{\alpha} = [f\dual(\alpha), t(\alpha)] \qquad & \text{(colored red)}
-\end{alignat*}
-placed as follows:
-
-\centerline{
 \begin{tikzpicture}[
@@
 \end{tikzpicture}
-}
-
-\item for any~$\alpha, \beta \in Q_1\blossom$ with~$t(\alpha) = s(\beta)$, proceed to the following identifications:
-    \begin{itemize}
-    \item if~$\alpha\beta \in I$, then glue~$\Ert{\alpha}$ with~$\Ers{\beta}$,
-    \item if~$\alpha\beta \notin I$, then glue~$\Enrt{\alpha}$ with~$\Enrs{\beta}$.
-    \end{itemize}
-\end{enumerate}
-The orientations on the edges are only used to perform the identifications and can be immediately forgotten.
-\end{definition}
-
-Definition~\ref{def:surfaceQuiver} constructs an orientable surface~$\surface_{\bar Q}$ with boundaries.
-\fref{fig:surfaces} illustrates this construction for the quivers of \fref{fig:quivers}.
-
-\begin{figure}[t]
-	\capstart
-	\centerline{\includegraphics[scale=.7]{surfaces}}
-	\caption{The surface~$\surface_{\bar Q}$ for the quivers~$\bar Q$ of \fref{fig:quivers}.}
-	\label{fig:surfaces}
-\end{figure}
-
-\begin{remark}
-We could equivalently construct the surface~$\surface_{\bar Q}$ as follows:
-\begin{itemize}
-\item consider one $(\ell+1)$-gon~$P_\omega$ for each straight walk~$\omega$ of length~$\ell$ in~$\bar Q$ or in~$\bar Q\koszul$ (just closing~$\omega$ with an additional edge connecting~$t(\omega)$ to~$s(\omega)$),
-\item for each arrow~$\alpha \in Q_1\blossom$, consider the only straight walks~$\omega$ of~$\bar Q$ and~$\omega\koszul$ of~$\bar Q\koszul$ containing~$\alpha$, and glue the polygons~$P_\omega$ and~$P_{\omega\koszul}$ along their edges corresponding to~$\alpha$.
-\end{itemize}
-\end{remark}
-
-\enlargethispage{-.4cm}
-The advantage of Definition~\ref{def:surfaceQuiver} is that it automatically endows~$\surface_{\bar Q}$ with two disjoint sets~$V_{\bar Q}$ and~${{V\dual}\!\!_{\bar Q}}$ of marked points and two dual cellular dissections~$\dissection_{\bar Q}$ and~${\dissection\dual\!\!_{\bar Q}}$ defined as follows.
-
-\begin{definition}
-\label{def:dissectionQuiver}
-The surface~$\surface_{\bar Q}$ is endowed with
-\begin{itemize}
-\item the set~$V_{\bar Q}$ of points~$v(\alpha)$ for~$\alpha \in Q_1\blossom$ after the identifications given by~(ii),
-\item the $V_{\bar Q}$-dissection~$\dissection_{\bar Q}$ given by all sides~$\Enrs{\alpha}$ and~$\Enrt{\alpha}$ for~$\alpha \in Q_1\blossom$ after the identifications given by~(ii).
-\end{itemize}
-The set~${{V\dual}\!\!_{\bar Q}}$ and the ${{V\dual}\!\!_{\bar Q}}$-dissection~${\dissection\dual\!\!_{\bar Q}}$ are defined similarly by using $f\dual(\alpha)$, $\Ers{\alpha}$ and $\Ert{\alpha}$.
-\end{definition}
-
-\begin{proposition}
-\label{prop:dissectionsAreCellular}
-Let~$\bar Q$ be a locally gentle bound quiver.
-Then the dissections~$\dissection_{\bar Q}$ and~$\dissection\dual\!\!_{\bar Q}$ are cellular and dual to each other.
-\end{proposition}
-
-\begin{proof}
-In the construction of~$\surface_{\bar Q}$, if two arrows~$\alpha$ and~$\beta$ of~$\bar Q \blossom$ are such that~${t(\alpha) = s(\beta)}$ and~${\alpha\beta \in I\blossom}$, then the vertices~$v(\alpha)$ and~$v(\beta)$ are identified on the surface.
-Thus, any two arrows of a given path contribute to the same vertex of~$V_{\bar Q}$, so~$V_{\bar Q}$ is in bijection with the set of maximal paths in~$\bar Q\blossom$.
-
-Let~$v\in V_{\bar Q}$. The situation around~$v$ is as follows, depending on whether~$v$ corresponds to a finite or infinite maximal path of~$\bar Q\blossom$:
-
-\begin{figure}[h]
-	\capstart
-	\centerline{\includegraphics[scale=.7]{halfStar} \qquad \includegraphics[scale=.7]{star}}
-	\caption{Two possible situations around~$v$: on the left,~$v$ corresponds to a finite maximal path of~$\bar Q$, while on the right,~$v$ corresponds to an infinite one.}
-	\label{fig:stars}
-\end{figure}
-
-In both cases, we see that~$v$ is enclosed in a polygon of~$\dissection_{\bar Q}\dual$.  This shows that~$\dissection_{\bar Q}\dual$ is a cellular dissection of~$\surface_{\bar Q}$.
-Dually, one shows that~$\dissection_{\bar Q}$ is also a cellular dissection.
-
-Moreover, by construction, each edge of~$\dissection_{\bar Q}$ which is not on the boundary of~$\surface_{\bar Q}$ crosses exactly one edge of~$\dissection_{\bar Q}\dual$, and vice versa.
-This shows that~$\dissection_{\bar Q}$ and~$\dissection_{\bar Q}\dual$ are dual to each other.
-\end{proof}
-
-The following statement immediately follows from the definitions and was probably already observed by the reader on \fref{fig:surfaces}.
-
-\begin{theorem}
-\label{thm:bijectionLocallyGentleAndSurfaces}
-Up to isomorphism, the constructions of Definitions \ref{def:quiverDualDissections} and \ref{def:surfaceQuiver} are inverse~to~each other.
-They induce a bijection between the set of isomorphism classes of locally gentle bound quivers and the set of homeomorphism classes of marked surfaces with a pair of dual cellular dissections.
-\end{theorem}
-
-\begin{remark}
-\label{rem:propertiesSurface}
-The following observations are useful for the computation of examples.
-\begin{enumerate}[(i)]
-\item The set~$V_{\bar Q}$ has one vertex for each straight walk in~$\bar Q$ (equivalently, for each maximal path in~$\bar Q$).
-      Finite straight walks yield vertices on the boundary of~$\surface_{\bar Q}$, while infinite cyclic straight walks in~$\bar Q$ yield punctures of~$\surface_{\bar Q}$ in~$V_{\bar Q}$.
-      We denote by~$p$ the number of infinite cyclic straight walks in~$\bar Q$.
-\item \label{item:edges}
-      The dissection~$\dissection_{\bar Q}$ has one edge for each vertex~$a \in \bar Q_0$, obtained by concatenation of the sides~$\Enrt{\alpha} = \Enrs{\beta}$ and~$\Enrt{\alpha'} = \Enrs{\beta'}$ where~$a = t(\alpha) = s(\beta) = t(\alpha') = s(\beta')$, $\alpha\beta \notin I$ and~$\alpha'\beta' \notin I$.
-We denote by~$\edgeof(a)$ the edge of~$\dissection_{\bar Q}$ corresponding to~$a$.
-\item The dissection~$\dissection_{\bar Q}$ has one $\ell$-cell for each straight walk of length~$\ell$ in~$\bar Q\koszul$.
-\item Similar statements hold dually for~${{V\dual}\!\!_{\bar Q}}$ and~${\dissection\dual\!\!_{\bar Q}}$, and the notations~$p\dual$ and~$\dualedgeof(a)$ are defined similarly.
-\item The number of punctures of~$\surface_{\bar Q}$ is the number~$p + p\dual$ of infinite straight walks in~$\bar Q$ and in~$\bar Q\koszul$.
-\item \label{item:boundary}
-      The number~$b$ of boundary components of~$\surface_{\bar Q}$ can be computed as follows.
-      There are two natural perfect matchings whose vertices are the blossom vertices of~$\bar Q$: one is obtained by joining the endpoints of each finite straight walk of~$\bar Q$, and the other is obtained similarly from~$\bar Q \koszul$.
-      Let~$G$ be the superposition of these two perfect matchings.
-      Then the number~$b$ of boundary components of~$\surface_{\bar Q}$ is the number of connected components of~$G$.
-\item The genus of the surface~$\surface_{\bar Q}$ is
-      \[
-       g = \frac{|Q_1| - |Q_0| - b - p - p\dual + 2}{2},
-      \]
-      where~$b$ is the number of boundary components (see above for a way to compute~$b$) and~$p + p\dual$ the number of punctures (\ie infinite straight walks in~$\bar Q$ and in~$\bar Q\koszul$).
-      Indeed, ${2g = 2-\chi(\surface_{\bar Q})}$, where~$\chi(\surface_{\bar Q})$ is the Euler characteristic of~$\surface_{\bar Q}$.
-      The dissection~$\dissection$ provides a cellular decomposition of~$\surface_{\bar Q}$ on which we fill the boundary components with disks.  
-      The number of faces of this cellular decomposition is~$b + p\dual$, its number of edges is~$|Q_0|$ and its number of vertices is the number of straight walks in~$\bar Q$, which is equal to~$2|Q_0| - |Q_1| + p$.
-      The above formula for~$g$ follows.
-\end{enumerate}
-\end{remark}
-
-\begin{proposition}
-\label{prop:dualityKoszul2}
-For any gentle bound quiver~$\bar Q$ with Koszul dual~$\bar Q\koszul$, the surfaces~$\surface_{\bar Q}$ and~$\surface_{\bar Q\koszul}$ coincide, but~$\dissection_{\bar Q\koszul} = {\dissection\dual\!\!_{\bar Q}}$ and~${\dissection\dual\!\!_{\bar Q\koszul}} = \dissection_{\bar Q}$.
-\end{proposition}
-
-\begin{remark}
-\label{rem:comparisonWithOPS}
-The construction of the surface given in Definition \ref{def:surfaceQuiver} yields the same surface as the one constructed in \cite{OpperPlamondonSchroll}.
-A notable difference is that in \cite{OpperPlamondonSchroll}, only~$\dissection_{\bar Q}$ is given, and~$\dissection\dual\!\!_{\bar Q}$ is deduced (it is called the dual lamination).
-Another minor difference is that the construction in \cite{OpperPlamondonSchroll} is written only for gentle algebras, while here it is generalized to locally gentle algebras.
-
-The major difference with \cite{OpperPlamondonSchroll} is the application of the surface of a (locally) gentle algebra: there, it is used as a model for the derived category of the gentle algebra (graded arcs correspond to indecomposable objects in that category), while here, it will be used as a model for walks in~$\bar Q$ ($\dissection_{\bar Q}$-accordions will correspond to walks in~$\bar{Q}$, see Proposition \ref{prop:walks=arcs}).
-\end{remark}
-
-We conclude this section with five families of examples that illustrate the computation of~$\surface_{\bar Q}$.
-
-\begin{example}
-\label{exm:CambrianPath}
-Consider a \defn{Cambrian quiver}, that is any orientation of a line with no relations (\aka type~$A$ quiver).
-Two such quivers are represented in \fref{fig:CambrianPathsQuivers}.
-Note that we can choose to position the blossom vertices in such a way that for any arrow~$\beta$, the arrows~$\alpha$ and~$\gamma$ such that~$\alpha\beta \in I$ and~$\beta\gamma \in I$ are on the right of~$\beta$.
-
-\begin{figure}[h]
-	\capstart
-	\centerline{\includegraphics[scale=.45]{CambrianPathsQuivers}}
-	\caption{Two Cambrian quivers on~$5$ vertices.}
-	\label{fig:CambrianPathsQuivers}
-\end{figure}
-
-We apply Remark~\ref{rem:propertiesSurface} to understand the corresponding surfaces.
-The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}\,\eqref{item:boundary}) form a cycle with green and red arrows alternating.
-Moreover, $\bar Q$ and~$\bar Q\koszul$ have no infinite straight walks.
-Since~$|Q_1| = |Q_0|-1$, the corresponding surfaces are disks ($1$ boundary component, no puncture and genus~$0$).
-Two examples are represented in \fref{fig:CambrianPathsSurfaces}.
-Note that the dissection~$\dissection_{\bar Q}$ is a triangulation with no internal triangles, and the orientation of~$\bar Q$ indicates how to glue these triangles.
-For instance, the Cambrian quiver completely oriented in one direction yields a fan triangulation, were all internal edges are incident to the same vertex, as in \fref{fig:CambrianPathsSurfaces}\,(left).
-
-\begin{figure}[h]
-	\capstart
-	\centerline{\includegraphics[scale=.7]{CambrianPathsSurfaces}}
-	\caption{The surface~$\surface_{\bar Q}$ for two Cambrian paths on~$5$ vertices.}
-	\label{fig:CambrianPathsSurfaces}
-\end{figure}
-\end{example}
-
-\begin{example}
-\label{exm:reversedPath}
-Consider the family of \defn{reversed path quivers} indicated in \fref{fig:reversedPathsQuivers}.
-
-\begin{figure}[h]
-	\capstart
-	\centerline{\includegraphics[scale=.45]{reversedPathsQuivers}}
-	\caption{The reversed path quivers with~$1, 2, 3, 4$ vertices.}
-	\label{fig:reversedPathsQuivers}
-\end{figure}
-
-We apply Remark~\ref{rem:propertiesSurface} to understand the corresponding surfaces.
-The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}\,\eqref{item:boundary}) look like~\raisebox{-.1cm}{\includegraphics[scale=.3]{reversedPathsPM}}.
-Moreover, $\bar Q$ has no infinite straight walk, while~$\bar Q\koszul$ has~$|Q_0|-1$ infinite straight walks.
-Since~$|Q_1| = 2|Q_0|-2$, the corresponding surfaces have $1$ boundary component and genus~$0$.
-The first few corresponding surfaces are represented in \fref{fig:reversedPathsSurfaces}.
-
-\begin{figure}[h]
-	\capstart
-	\centerline{\includegraphics[scale=.7]{reversedPathsSurfaces3}}
-	\caption{The surface~$\surface_{\bar Q}$ for the reversed path quivers with~$1, 2, 3$ vertices.}
-	\label{fig:reversedPathsSurfaces}
-\end{figure}
-\end{example}
-
-\begin{example}
-\label{exm:doublePath}
-Consider the family of \defn{double path quivers} indicated in \fref{fig:doublePathsQuivers}.
-
-\begin{figure}[h]
-	\capstart
-	\centerline{\includegraphics[scale=.45]{doublePathsQuivers}}
-	\caption{The double path quivers with~$1, 2, 3, 4$ vertices.}
-	\label{fig:doublePathsQuivers}
-\end{figure}
-
-We apply Remark~\ref{rem:propertiesSurface} to understand the corresponding surfaces.
-The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}\,\eqref{item:boundary}) look like~\raisebox{-.1cm}{\includegraphics[scale=.3]{doublePathsPModd}} when~$|Q_0|$ is odd and~\raisebox{-.1cm}{\includegraphics[scale=.3]{doublePathsPMeven}} when~$|Q_0|$ is even.
-Moreover, $\bar Q$ and~$\bar Q\koszul$ have no infinite straight walks.
-Since~$|Q_1| = 2|Q_0|-2$, the corresponding surfaces have no punctures and
-\begin{itemize}
-\item $1$ boundary component and genus~$(|Q_0|-1)/2$ when~$|Q_0|$ is odd, and 
-\item $2$ boundary components and genus~$(|Q_0|-2)/2$ when~$|Q_0|$ is even.
-\end{itemize}
-The first few corresponding surfaces are represented in \fref{fig:doublePathsSurfaces}.
-
-\begin{figure}[H]
-	\capstart
-	\centerline{\includegraphics[scale=.7]{doublePathsSurfaces}}
-	\caption{The surface~$\surface_{\bar Q}$ for the double path quivers with~$1, 2, 3, 4$ vertices.}
-	\label{fig:doublePathsSurfaces}
-\end{figure}
-\end{example}
-
-\begin{example}
-\label{exm:cycle}
-Consider the family of \defn{cycle quivers} indicated in \fref{fig:cyclesQuivers}.
-
-\begin{figure}[H]
-	\capstart
-	\centerline{\includegraphics[scale=.45]{cyclesQuivers}}
-	\caption{The cycle quivers with~$1, 2, 3, 4, 5$ vertices.}
-	\label{fig:cyclesQuivers}
-\end{figure}
-
-We apply Remark~\ref{rem:propertiesSurface} to understand the corresponding surfaces.
-The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}\,\eqref{item:boundary}) form a cycle with green and red arrows alternating.
-Moreover, $\bar Q$ has~$1$ infinite straight walk, while~$\bar Q\koszul$ has none.
-Since~$|Q_1| = |Q_0|$, the corresponding surfaces are punctured disks ($1$ boundary component, $1$ puncture and genus~$0$).
-The first few corresponding surfaces are represented in \fref{fig:cyclesSurfaces} (see Figures~\ref{fig:surfaces} and~\ref{fig:reversedPathsSurfaces} for the cycles with $1$ or~$2$ vertices, recalling that~$\bar Q$ and~$\bar Q\koszul$ yield the same surface).
-
-\begin{figure}[h]
-	\capstart
-	\centerline{\includegraphics[scale=.7]{cyclesSurfacesBis}}
-	\caption{The surface~$\surface_{\bar Q}$ for the cycle quivers with~$3, 4, 5$ vertices.}
-	\label{fig:cyclesSurfaces}
-\end{figure}
-\end{example}
-
-\begin{example}
-\label{exm:doubleCycle}
-Consider the family of \defn{double cycle quivers} indicated in \fref{fig:doubleCyclesQuivers}.
-
-\begin{figure}[H]
-	\capstart
-	\centerline{\includegraphics[scale=.45]{doubleCyclesQuivers}}
-	\caption{The double cycle quivers with~$1, 2, 3, 4, 5$ vertices.}
-	\label{fig:doubleCyclesQuivers}
-\end{figure}
-
-We apply Remark~\ref{rem:propertiesSurface} to understand the corresponding surfaces.
-The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}\,\eqref{item:boundary}) are empty since there are no blossom vertices.
-Moreover, $\bar Q$ has~$1$ infinite straight walk when~$|Q_0|$ is odd and~$2$ when~$|Q_0|$ is even, and~$\bar Q\koszul$ always has~$2$ infinite straight walks.
-Since~$|Q_1| = 2|Q_0|$, the corresponding surfaces have no boundary component and
-\begin{itemize}
-\item $3$ punctures and genus~$(|Q_0|-1)/2$ when~$|Q_0|$ is odd, and 
-\item $4$ punctures and genus~$(|Q_0|-2)/2$ when~$|Q_0|$ is even.
-\end{itemize}
-The first few corresponding surfaces are represented in \fref{fig:doubleCyclesSurfaces}.
-
-\begin{figure}[h]
-	\capstart
-	\centerline{\includegraphics[scale=.7]{doubleCyclesSurfaces}}
-	\caption{The surface~$\surface_{\bar Q}$ for the double cycle quivers with~$3, 4, 5$ vertices.}
-	\label{fig:doubleCyclesSurfaces}
-\end{figure}
-\end{example}
-
-\subsection{Non-crossing and non-kissing complexes coincide}
-
-Let~$\bar Q$ be a locally gentle bound quiver.
-For each edge of the dissection~$\dissection_{\bar Q}$ on~$\surface_{\bar Q}$, we fix a point on the interior of this edge, which we call its ``middle point'' (this is the black vertex on the pictures).
-To each walk on~$\bar Q$, we will now associate a~$\dissection_{\bar Q}$-accordion.
-
-\begin{definition}
-\label{def:curveOfAnArrow}
-For any arrow~$\alpha$ on $\bar Q\blossom$, let~$\curveof(\alpha)$ be the curve on~$\surface_{\bar Q}$ which goes from the middle point of the edge of~$\dissection$ corresponding to $s(\alpha)$ to the middle point of the edge of~$\dissection$ corresponding to $t(\alpha)$ by following the angle corresponding to~$\alpha$.
-Define~$\curveof(\alpha^{-1})$ to be~$\curveof(\alpha)^{-1}$.
-\end{definition}
-
-\begin{definition}
-\label{def:curveOfAWalk}
-Let~$\omega = \prod_{i < \ell < j} \alpha_\ell^{\varepsilon_\ell}$ be a (possibly infinite) walk on~$\bar Q$. 
-Define the curve~$\curveof(\omega)$ to be the concatenation of the curves~$\curveof(\alpha_\ell^{\varepsilon_\ell})$ of Definition \ref{def:curveOfAnArrow}.
-\end{definition}
-
-In practice, we will represent~$\curveof(\omega)$ by a curve which intersects itself only transversaly, and such that if it circles infinitely around a puncture, then it spirals towards it.
-
-\begin{lemma}
-\label{lemm:curveOfAWalkIsAccordion}
-Let~$\omega$ be a walk on~$\bar Q$.  Then~$\curveof(\omega)$ is a~$\dissection_{\bar Q}$-accordion.
-\end{lemma}
-
-\begin{proof}
-This is because~$\curveof(\omega)$ follows angles in~$\dissection_{\bar Q}$ by definition.
-\end{proof}
-
-\begin{lemma}
-\label{lemm:accordionsAreCurvesOfWalks}
-Let~$\gamma$ be a~$\dissection_{\bar Q}$-accordion.  There exists a unique undirected walk~$\walk(\gamma)$ such that we have~$\curveof(\walk(\gamma)) = \gamma$.
-\end{lemma}
-
-\begin{proof}
-We can assume that~$\gamma$ intersects itself and the edges of~$\dissection_{\bar Q}$ transversaly and minimally, in the sense that~$\gamma$ does not cross an edge twice in succession in opposite directions (see Definition~\ref{def:crossingCurves}).
-Then~$\gamma$ is completely determined by its sequence of intersection points with the edges of~$\dissection_{\bar Q}$, since the dissection is cellular.
-Two successive intersection points in this sequence define an angle between two edges of~$\dissection_{\bar Q}$, which corresponds to an arrow in~$\bar Q$.
-Thus the sequence of intersection points defines a walk~$\walk(\gamma)$ on~$\bar Q$.
-By construction, we have that~$\curveof(\walk(\gamma)) = \gamma$.
-Is also follows from the construction above and from Definition~\ref{def:curveOfAWalk} that~$\walk(\curveof(\omega)) = \omega$ for any walk~$\omega$.
-This finishes the proof.
-\end{proof}
-
-The above implies the following.
-
-\begin{proposition}
-\label{prop:walks=arcs}
-The maps~$\curveof(-)$ and~$\walk(-)$ induce mutually inverse bijections between the set of undirected walks on~$\bar Q$ and the set of~$\dissection_{\bar Q}$-accordions on~$\surface_{\bar Q}$.
-\end{proposition}
-
-\begin{lemma}
-\label{lem:nonKissing=nonCrossing}
-Two undirected walks~$\omega_1$ and~$\omega_2$ on~$\bar Q$ are non-kissing if and only if the corresponding $\dissection_{\bar Q}$-accordions~$\curveof(\omega_1)$ and~$\curveof(\omega_2)$ are non-crossing on~$\surface_{\bar Q}$.
-\end{lemma}
-
-\begin{proof}
-A kiss between two walks~$\omega$ and~$\omega'$ is depicted on \fref{fig:kissings}.
-
-\begin{figure}[h]
-	\capstart
-	\centerline{\includegraphics[scale=1]{kissings}}
-	\caption{Two representations of a pair of kissing walks.}
-	\label{fig:kissings}
-\end{figure}
-The left hand side of the picture is as in \fref{fig:kissing}, and the right hand side is simply a different representation of it.
-On the surface~$\surface_{\bar Q}$, the dual dissections~$\dissection$ and~$\dissection\dual$ are as on \fref{fig:kissingVSCrossing} (right).
-
-\begin{figure}[h]
-	\capstart
-	\centerline{\includegraphics[scale=1]{kissingVSCrossing}}
-	\caption{Kissing walks on the quiver~$\bar Q$ correspond to crossing curves on the surface~$\surface_{\bar Q}$.}
-	\label{fig:kissingVSCrossing}
-\end{figure}
-
-The curves~$\curveof(\omega)$ and~$\curveof(\omega')$ on the surface follow~$\omega$ and~$\omega'$ on the picture.
-It is then clear that~$\omega$ and~$\omega'$ kiss if and only if~$\curveof(\omega)$ and~$\curveof(\omega')$ cross. 
-\end{proof}
-
-\begin{theorem}
-\label{thm:complexesCoincide}
-The non-kissing and non-crossing complexes are isomorphic:
-\begin{itemize}
-\item for any locally gentle bound quiver~$\bar Q$, the non-kissing complex~$\NKC$ is isomorphic to the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection\dual\!\!_{\bar Q}}]$,
-\item for any pair of dual cellular dissections~$\dissection, \dissection\dual$ of an oriented surface, the non-crossing complex~$\NCC$ is isomorphic to the non-kissing complex~$\NKC[\bar Q_{\dissection, \dissection\dual}]$.
-\end{itemize}
-\end{theorem}
-
-\begin{proof}
-The first point is a consequence of Proposition \ref{prop:walks=arcs}, Lemma \ref{lem:nonKissing=nonCrossing} and Proposition \ref{prop:accordionsSlaloms}.
-The second point is a consequence of Theorem \ref{thm:bijectionLocallyGentleAndSurfaces} and of the first point.
-\end{proof}
-
-\begin{remark}
-Note that our construction of the surface~$\surface_{\bar Q}$ implies that the quiver~$\bar Q$ is naturally embedded on~$\surface_{\bar Q}$.
-If we force all $\dissection$-accordions (or $\dissection\dual$-slaloms) to follow the arrows of~$\bar Q$, then a $\dissection$-accordion (or $\dissection\dual$-slalom) is really seen as a walk on~$\bar Q$.
-\end{remark}
-
-We conclude with an important example of facets of the non-kissing and non-crossing complexes.
-
-\begin{example}
-\label{exm:peakDeepFacets}
-We have seen in Definition~\ref{def:straightBending} that each vertex~$a$ of~$Q$ gives rise to a \defn{peak walk}~$a_\peak$ (resp.~\defn{deep walk}~$a_\deep$) with a single peak (resp.~deep) at~$a$ and no other corner.
-The set of all such walks forms the \defn{peak facet}~$\set{a_\peak}{a \in Q_0}$ (resp.~the \defn{deep facet}~$\set{a_\deep}{a \in Q_0}$) of the non-kissing complex~$\RNKC$.
-As an example of Theorem~\ref{thm:complexesCoincide}, let us now describe the corresponding non-crossing facets of~$\RNCC[\dissection_{\bar Q}, {{\dissection\dual}\!\!_{\bar Q}}]$.
-
-For an edge~$a$ of~$\dissection$, we denote by~$\vprevious{a}$ (resp.~$\vnext{a}$) the curve obtained by moving each endpoint~$v$ of~$a$ as follows:
-\begin{itemize}
-\item if~$v$ is on the boundary of~$\surface$, then move (continuously) $v$ until it reaches the following blossom vertex along the boundary of~$\surface$ while keeping the boundary of~$\surface$ on the right,
-\item if~$v$ is a puncture, then rotate around~$v$ in counterclockwise (resp.~clockwise) direction.
-\end{itemize}
-Examples are illustrated in \fref{fig:peakDeep}.
-%
-\begin{figure}[h]
-	\capstart
-	\centerline{\includegraphics[scale=.7]{peakDeep}}
-	\caption{The curves~$\vprevious{a}$ (left) and $\vnext{a}$ (right) associated to an edge~$a$ of~$\dissection$ for three different dissections.}
-	\label{fig:peakDeep}
-\end{figure}
-
-We invite the reader to check that~$\curveof(a_\peak) = \vprevious{\edgeof(a)}$ (resp.~$\curveof(a_\deep) = \vnext{\edgeof(a)}$), where~$\edgeof(a)$ denotes the edge of~$\dissection_{\bar Q}$ corresponding to~$a \in Q_0$ (see Remark~\ref{rem:propertiesSurface}\,\eqref{item:edges}).
-Therefore, the peak facet (resp.~the deep facet) can be thought of as the dissection~$\dissection_{\bar Q}$ slightly rotated clockwise (resp.~counterclockwise) on the surface~$\surface_{\bar Q}$.
-\end{example}
-
-\begin{remark}
-According to Proposition~\ref{prop:dualityKoszul2} and Theorem~\ref{thm:complexesCoincide}, the simplicial complexes~$\NKC[\bar Q\koszul]$ and~$\NCC[{\dissection\dual\!\!_{\bar Q}}, \dissection_{\bar Q}]$ are isomorphic.
-It would be interesting to find the precise link between~$\NKC$ and~$\NKC[\bar Q\koszul]$.
-\end{remark}
-
-\section{Properties of the non-crossing and non-kissing complexes}\label{sec:propertiesOfComplexes}
-
-This section explores combinatorial properties of the non-crossing and non-kissing complexes, showing in particular that these complexes are pure and thin.
-The proof follows ideas of~\cite{McConville, GarverMcConville} already reinterpreted for non-kissing complexes of gentle algebras in~\cite{PaluPilaudPlamondon}.
-However, the setting of locally gentle algebras studied in this paper requires a little more care.
-
-\subsection{The countercurrent order}
-
-The countercurrent order was introduced in~\cite{McConville} for grids and defined in \cite{PaluPilaudPlamondon} for gentle algebras.
-We now adapt it to locally gentle algebras.
-
-\begin{definition}
-A \defn{marked walk}~$\omega_\star$ is a walk~$\omega$ together with a marked occurence of an arrow~$\alpha^{\pm}$ in~$\omega$.
-In the case where~$\omega$ is an infinite straight walk (so~$\omega$ is a cycle which repeats infinitely on both sides), we consider that all marked occurences of an arrow~$\alpha^\pm$ are equal.
-Otherwise, if~$\omega$ contains several occurrences of~$\alpha^\pm$, only one occurrence is marked.
-\end{definition}
-
-The following definition is illustrated in \fref{fig:orderCurves}\,(left).
-
-\begin{definition}
-\label{def:orderForWalks}
-For any arrow~$\alpha \in Q\blossom_1$ and any two distinct non-kissing walks~$\mu_\star, \nu_\star$ marked at an occurrence of~$\alpha^\pm$,
-let~$\sigma$ denote their maximal common substring containing that occurrence of~$\alpha$.
-Since~$\mu_\star \ne \nu_\star$, this common substring~$\sigma$ is strict, so~$\mu_\star$ and~$\nu_\star$ split at one endpoint of~$\sigma$.
-The \defn{countercurrent order at~$\alpha$} is defined by~$\mu_\star \prec_\alpha \nu_\star$ when~$\mu_\star$ enters and/or exits~$\sigma$ in the direction pointed by~$\alpha$, while~$\nu_\star$ enters and/or exits~$\sigma$ in the direction opposite to~$\alpha$.
-\end{definition}
-
-\begin{remark}
-Since the walks~$\mu$ and~$\nu$ are non-kissing, if~$\mu_\star$ leaves~$\sigma$ on both sides, then is enters and exits~$\sigma$ in the same direction, so that Definition~\ref{def:orderForWalks} is coherent.
-\end{remark}
-
-\begin{remark}
-\label{rem:countercurrentOrderOnSurface}
-Using Theorem \ref{thm:complexesCoincide}, we can translate the definition of the countercurrent order~$\prec_\alpha$ to the language of~$\dissection$-accordions (resp.~of~$\dissection\dual$-slaloms).
-An arrow~$\alpha$ in~$\bar Q\blossom$ corresponds to an angle at a point~$v$ between two edges of~$\dissection$ (resp.~at a point~$f\dual$ between two edges of~$\dissection\dual$).
-Two distinct non-kissing walks~$\mu_\star, \nu_\star$ marked at~$\alpha$ in~$\bar Q$ correspond to two distinct non-crossing~$\dissection$-accordions (resp.~$\dissection\dual$-slaloms)~$\gamma$ and~$\delta$ passing in front of this angle.
-Then~$\gamma \prec_\alpha \delta$ if~$\gamma$ passes closer to~$v$ (resp.~further to~$f\dual$) than~$\delta$ does.
-These interpretations of~$\prec_\alpha$ on the surface where already considered in the case of the disk in~\cite{GarverMcConville, MannevillePilaud-accordion}.
-%
-\begin{figure}[h]
-	\capstart
-	\centerline{\includegraphics[scale=1]{orderCurves}}
-	\caption{The order~$\mu \prec_\alpha \nu$ on marked walks is the order in which the corresponding curves~$\curveof(\mu)$ and~$\curveof(\nu)$ cross the angles of~$\dissection$ and~$\dissection\dual$ corresponding to~$\alpha$.}
-	\label{fig:orderCurves}
-\end{figure}
-\end{remark}
-
-\begin{notation}
-\label{notation:Falpha}
-For any face~$F$ of~$\NKC$ and any arrow~$\alpha\in Q_1\blossom$, we denote by~$F_\alpha$ the set of walks of~$F$ marked at an occurence of~$\alpha^\pm$.
-\end{notation}
-
-\begin{lemma}
-\label{lemm:countercurrentOrderIsTotal}
-For any face~$F$ of~$\NKC$ and any arrow~$\alpha\in Q_1\blossom$, the countercurrent order~$\prec_\alpha$ defines a total order on~$F_{\alpha}$.
-\end{lemma}
-
-\begin{proof}
-The proof of \cite[Lem.~2.21]{PaluPilaudPlamondon} applies here.
-\end{proof}
-
-\begin{lemma}
-\label{lemm:facesHaveMaximalElement}
-For any finite non-kissing face~$F$ of~$\NKC$ and any arrow~$\alpha\in Q_1\blossom$, the set~$F_\alpha$ is either empty or admits a maximal element for the countercurrent order~$\prec_\alpha$.
-\end{lemma}
-
-\begin{proof}
-We provide two proofs of the lemma.
-One is combinatorial and applies to~$\NKC$, and the other is geometric and applies to~$\NCC[\dissection_{\bar Q}, {\dissection\dual\!\!_{\bar Q}}]$, using the isomorphism of Theorem \ref{thm:complexesCoincide} and Remark \ref{rem:countercurrentOrderOnSurface}.
-
-\para{Combinatorial proof}
-Note that even though~$F$ is finite, the set of marked walks~$F_\alpha$ might be infinite if~$\alpha$ belongs to an oriented cycle of~$Q$.
-Assume that~$F_\alpha$ is non-empty, and infinite.
-Any walk that contains an infinite number of copies of~$\alpha$ can be written in the form~$\omega=\sigma c^{\pm\infty}$ where~$\sigma$ is a (possibly infinite) substring and~$c$ is an oriented cycle containing~$\alpha$ such that~$c, c^2\notin I$.
-Then~$\omega$ marked at the first occurrence of~$\alpha$ in~$c^{\pm\infty}$ is greater than~$\omega$ marked at any other occurrence of~$\alpha$ in~$c^{\pm\infty}$.
-We can thus safely remove all copies of~$\omega$ marked at an occurrence of~$\alpha$ in~$c^{\pm\infty}$ but the first one.
-After applying this procedure a finite number of times,~$F_\alpha$ becomes finite, and the claim follows.
-
-\para{Geometric proof}
-View~$F$ as a face of the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection\dual\!\!_{\bar Q}}]$.
-The arrow~$\alpha$ then corresponds to an angle in~$\dissection$ at a vertex~$v$.  
-% 
-For any curve~$\gamma$ in~$F$, even though~$\gamma$ may pass through the above angle infinitely many times, there is one instance that is furthest from the angle: indeed, if ~$\gamma$ passes infinitely many times through~$\alpha$, then~$v$ is a puncture and~$\gamma$ circles infinitely towards it.
-But then~$\gamma$ passes through~$\alpha$ only finitely many times before it starts circling~$v$ (in either direction), and one of these times is the furthest from~$v$.
-%  
-Therefore, for every curve~$\gamma\in F$, there is a maximal occurence of~$\alpha$ in~$\gamma$.
-Since~$F$ is finite, the set of these maximal occurences is finite, so it admits a maximal element.  
-This element is the maximal element of~$F_\alpha$.
-\end{proof}
-
-\subsection{The non-crossing and non-kissing complexes have no infinite faces}
-
-We now pause to prove the following statement.
-
-\begin{proposition}
-\label{prop:facetsAreFinite}
-Any face of~$\NKC$ and~$\NCC[\dissection_{\bar Q}, {\dissection\dual\!\!_{\bar Q}}]$ is finite, thus contained in a finite maximal face.
-\end{proposition}
-
-Even though Theorem \ref{thm:complexesCoincide} ensures that~$\NKC$ and~$\NCC[\dissection_{\bar Q}, {\dissection\dual\!\!_{\bar Q}}]$ coincide, we provide two proofs.
-One is combinatorial and applies to~$\NKC$, and the other is geometric and applies to~$\NCC[\dissection_{\bar Q}, {\dissection\dual\!\!_{\bar Q}}]$.
-The proof requires the following intermediate results.
-
-\begin{lemma}
-\label{lem:nkCycles}
-Let~$\omega$ be a non-kissing walk that contains a non-trivial oriented cycle~$c$ with~$c, c^2\notin I$.
-Then~$\omega$ is of the form~$\sigma c^{\pm\infty}$, for some (possibly infinite) substring~$\sigma$.
-\end{lemma}
-
-\begin{proof}[Combinatorial proof]
-Let~$c=\alpha_1\cdots\alpha_r$ be a non-trivial oriented cycle in some walk~$\omega$, with~$c, c^2\notin I$.
-Assume that~$\omega$ is not of the form~$\sigma c^{\pm\infty}$.
-Then, up to cyclic reordering of the arrows in~$c$, it contains a substring of the form~$\beta^\pm c^l \alpha_1\cdots\alpha_j\gamma^\pm$, for some arrows~$\beta,\gamma$ not in~$c$, some~$l\geq 1$, and some~$j<r$.
-Since~$\bar Q$ is locally gentle, this substring is~$\beta^{-1} c^l \alpha_1\cdots\alpha_j\gamma^{-1}$.
-Hence, the walk~$\omega$ contains the two substrings~$\beta^{-1}\alpha_1\cdots\alpha_j\alpha_{j+1}$ and~$\alpha_r\alpha_1\cdots\alpha_j\gamma^{-1}$, and thus self-kisses.
-
-\para{Geometric proof}
-An oriented cycle~$c$ corresponds to a puncture in~$\dissection_{\bar Q}$.
-Let~$\gamma = \curveof(\omega)$.  The fact that~$\omega$ contains~$c$ translates to the fact that~$\gamma$ makes one full circle around the corresponding puncture.
-
-\begin{figure}[h]
-	\capstart
-	\centerline{\includegraphics[scale=.7]{infiniteCurve2.pdf}}
-	\caption{The curve~$\gamma$ makes at least one full circle around the puncture.}
-	\label{fig:aroundPuncture1}
-\end{figure}
-
-Once this cycle is completed, since~$\gamma$ cannot cross itself, it has to continue cycling infinitely around the puncture.  This proves the claim.
-\end{proof}
-
-\begin{lemma}\label{lem:ExistenceOfDistinguishedArrows}
-Let~$F$ be a finite non-kissing face of~$\NKC$, let~$\omega$ be a walk in~$F$, and let~$\alpha$ be an arrow on~$\omega$.
-Assume that~$\omega$ is not an infinite straight walk.
-Then, there is an arrow~$\beta$ oriented in the same direction as~$\alpha$ in~$\omega$ such that~$\omega$ (marked at~$\beta$) is maximal in~$F$ for~$\prec_\beta$.
-\end{lemma}
-
-\begin{proof}
-Let~$\omega$ be a walk in some non-kissing facet~$F$, marked at an arrow~$\alpha$.
-If~$\omega$ is not maximal at~$\alpha$, there is a walk~$\mu_0\in F$ such that~$\omega\prec_\alpha \mu_0$.
-Let~$\sigma_0$ be the maximal common substring of~$\omega$ and~$\mu_0$ containing~$\alpha$.
-Since~$\omega$ and $\mu_0$ are different, they split at some endpoint of~$\sigma_0$.
-At this endpoint, the arrow~$\beta$ of~$\omega$ not in~$\sigma_0$ points in the same direction as~$\alpha$ since~$\omega \prec_\alpha \mu_0$.
-If~$\omega$ is maximal at~$\beta$ in~$F$, we are done.
-Otherwise, let~$\mu_1$ be maximal in~$F$ for~$\prec_\beta$.
-Since~$\mu_1$ does not kiss with~$\mu_0$, and~$\omega\prec_\beta\mu_1$,~$\mu_1$ contains~$\sigma_0$.
-Let~$\sigma_1$ be the maximal common substring of~$\omega$ and~$\mu_1$ containing~$\beta$.
-As remarked above,~$\sigma_1$ contains~$\sigma_0$.
-Since~$\omega$ is not maximal at~$\beta$, the walks~$\omega$ and~$\mu_1$ split at some endpoint of~$\sigma_1$.
-By Lemma~\ref{lem:nkCycles}, iterating this procedure eventually stops ($\mu_j=\omega$ for some $j$) unless~$\omega$ is an infinite straight walk.
-\end{proof}
-
-\begin{lemma}
-\label{lemm:facesAreBounded}
-There is a bound on the number of elements of a finite face of~$\NKC$.
-\end{lemma}
-
-\begin{proof}[Combinatorial proof]
-By Lemma~\ref{lem:ExistenceOfDistinguishedArrows}, the number of walks in a finite face of~$\NKC$ is bounded by~$|Q_1\blossom|+p$, where~$p$ is the number of infinite straight walks (\ie the number of primitive oriented cycles in~$Q$).
-
-\para{Geometric proof}
-Let~$F$ be a face of the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection\dual\!\!_{\bar Q}}]$.
-Its elements are pairwise compatible~$\dissection$-accordions on the surface~$\surface_{\bar Q}$.
-Thus~$F$ can be viewed as a partial tagged triangulation of~$\surface_{\bar Q}$, by letting the~$\dissection$-accordions circling a puncture in (say) clockwise order be seen as ``notched'' arcs to said puncture, and the ones circling it in counterclockwise orientation be ``un-notched'' arcs.
-It is known (see, for instance, \cite{FominShapiroThurston}) that any such partial tagged triangulation can be embedded into a full triangulation, and that triangulations contain a finite number of arcs.
-Thus~$F$ is finite, and is contained in a finite maximal face.
-\end{proof}
-
-\begin{proof}[Proof of Proposition~\ref{prop:facetsAreFinite}]
-If~$\NKC$, respectively~$\NCC$, admits an infinite face, then all subsets of this face are also faces, so~$\NKC$, respectively~$\NCC$, admits faces of arbitrarily large finite cardinality.
-This contradicts Lemma \ref{lemm:facesAreBounded}.
-\end{proof}
-
-\subsection{Purity of the non-crossing and non-kissing complexes}
-
-A simplicial complex is \defn{pure of dimension~$d$} if all its maximal faces have dimension~$d$.
-The aim of this section is to prove the following purity result.
-
-\begin{proposition}
-\label{prop:purity}
-The reduced non-kissing complex~$\RNKC$ and the reduced non-crossing complex~$\RNCC[\dissection_{\bar Q}, {\dissection\dual\!\!_{\bar Q}}]$ are pure of dimension~$|Q_0|$.
-The non-kissing complex~$\NKC$ and the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection\dual\!\!_{\bar Q}}]$ are pure of dimension~$3|Q_0| - |Q_1| + p$ where~$p$ is the number of primitive oriented cycles in~$\bar Q$ or equivalently the number of punctures in~$V_{\bar Q}$.
-\end{proposition}
-
-Note that Proposition \ref{prop:purity} was proved for~$\NKC$ in \cite[Cor.~2.29]{PaluPilaudPlamondon} in the case where~$kQ/I$ is finite-dimensional.
-Note also that, by Theorem \ref{thm:complexesCoincide} above,~$\NKC$ and~$\NCC[\dissection_{\bar Q}, {\dissection\dual\!\!_{\bar Q}}]$ coincide, so it suffices to prove the statement for one of them.
-The following definition from \cite[Def.~2.25]{PaluPilaudPlamondon} extends to the setting of locally gentle algebras.
-
-\begin{definition}
-\label{def:distinguishedWalksAndArrows}
-Let~$\alpha \in Q\blossom_1$ be an arrow and let~$F$ be a face of~$\NKC$ containing the straight walk passing through~$\alpha$.
-Consider the marked walk~$\omega_\star \eqdef \max_{\prec_\alpha} F_\alpha$ (which exists by Lemma~\ref{lemm:facesHaveMaximalElement} and Proposition~\ref{prop:facetsAreFinite}),
-and let~$\omega$ be the walk obtained by forgetting the marked arrow in~$\omega_\star$. 
-We say that~$\omega$ is the \defn{distinguished walk} of~$F$ at~$\alpha$ and that~$\alpha$ is a \defn{distinguished arrow} on~$\omega \in F$.
-We will use the notation
-\[
-\distinguishedWalk{\alpha}{F} \eqdef \max\nolimits_{\prec_\alpha} F_\alpha
-\qquad\text{and}\qquad
-\distinguishedArrows{\omega}{F} \eqdef \set{\alpha \in \omega}{\distinguishedWalk{\alpha}{F} = \omega}.
-\]
-\end{definition}
-
-We use this definition to prove the following statement.
-
-\begin{lemma}
-\label{lem:walksThroughcycles}
-For any oriented cycle~$c$ in~$Q$ with~$c, c^2\notin I$, any maximal non-kissing face contains a walk of the form~$\sigma c^{\varepsilon\infty}$, for some~$\varepsilon\in\{\pm1\}$ and some substring~$\sigma$ distinct from~$^{\varepsilon\infty}c$ (\ie the walk is not an infinite straight walk).
-\end{lemma}
-
-\begin{proof}[Combinatorial proof]
-Consider a maximal non-kissing face~$F \in \NKC$ and an arrow~$\alpha$ in~$c$.
-Let~$\beta, \gamma \in Q_1\blossom$ be such that~$t(\alpha) = s(\beta) = s(\gamma)$ and~$\alpha\beta \notin I$ while~$\alpha\gamma \in I$ (in other words, $\beta$ is the next arrow along~$c$ after~$\alpha$ and~$\gamma$ is the other outgoing arrow at~$t(\alpha)$).
-Consider the walk~$\mu \eqdef \distinguishedWalk{\gamma}{F}$ and decompose it as~$\mu = \mu_1 \gamma \mu_2$ according to this occurence of~$\gamma$ on~$\mu$.
-Consider the walk~$\nu \eqdef \mu_2^{-1} \gamma^{-1} c^\infty$.
-If~$\nu$ is contained in~$F$, then we have found a walk of the desired form (remember that walks are considered as undirected).
-Otherwise, there exists a walk~$\lambda$ of~$F$ preventing~$\nu$ from belonging to~$F$.
-Let~$\sigma$ be a common substring of~$\nu$ and~$\lambda$ where they kiss.
-Since~$\lambda$ must be compatible with~$\mu$ and with the straight walk~$c^\infty$, the substring~$\sigma$ must contain~${t(\alpha) = s(\beta)}$.
-If~$\lambda$ contains neither~$\alpha$ nor~$\beta$, then it contains~$\gamma$ and enters $\nu$ at~$s(\gamma)$.
-Since $\lambda$ kisses~$\nu$, it also enters~$\mu_2$, contradicting the maximality of~$\mu$ for~$\prec_\gamma$.
-Therefore, $\lambda$ contains either~$\alpha$ or~$\beta$.
-We have thus found a bending walk~$\lambda \in F$ containing an arrow~$\alpha$ or~$\beta$ of~$c$, say~$\alpha$.
-We can now moreover assume that~$\lambda = \distinguishedWalk{\alpha}{F}$.
-If~$\lambda$ starts by~$^\infty c$, or ends by~$c^\infty$, then we have found a walk of the desired form.
-Otherwise, decompose this walk as~$\lambda = \lambda_1 \alpha \lambda_2$ and consider the walk~$\omega = \lambda_1 c^\infty$.
-We claim that~$\omega$ belongs to~$F$.
-Otherwise, there exists a walk~$\rho$ preventing~$\omega$ from belonging to~$F$.
-Let~$\tau$ be a common substring of~$\omega$ and~$\rho$ where they kiss.
-Since~$\omega$ must be compatible with~$\lambda$ and with the straight walk~$c^\infty$, the substring~$\tau$ must strictly contain the substring of~$\lambda$ along the cycle~$c$.
-It follows that $\rho$ leaves~$\omega$ when it is on the cycle~$c$, thus with an incoming arrow, contradicting the maximality of~$\lambda$ for~$\prec_\alpha$.
-
-\para{Geometric proof}
-The statement of the lemma translates on~$\surface_{\bar Q}$ as follows: for any facet~$F$ of the non-crossing complex~$\NCC$ and any puncture of the dissection~$\dissection_{\bar Q}$, there exists a curve in~$F$ which goes to the puncture.
-Assume that there is a puncture with no curves of~$F$ going to it.
-Construct a curve~$\gamma$ as follows:~$\gamma$ first unwinds from the puncture, then~$\gamma$ leaves the local picture around the puncture by turning around another marked point (marked~$u$ on the picture below).
-
-\begin{figure}[h]
-	\capstart
-	\centerline{\includegraphics[scale=.7]{infiniteCurve1.pdf}}
-	\caption{The curve~$\gamma$ leaving the puncture.}
-	\label{fig:aroundPuncture2}
-\end{figure}
-
-Two situations can occur:
-\begin{itemize}
-\item Firstly, if there are no curves of~$F$ closer to~$u$ than~$\gamma$, then~$\gamma$ can circle around~$u$ until it reaches the boundary (if~$u$ is on the boundary) or infinitely (if~$u$ is a puncture).
-Then~$\gamma$ is a~$\dissection_{\bar Q}$-accordion which crosses none of those in~$F$, contradicting the maximality of~$F$.
-\item Secondly, if there is a curve of~$F$ closer to~$u$ than~$\gamma$, then let~$\delta$ be the one furthest from~$u$ ($\delta$ exists by Lemma \ref{lemm:facesHaveMaximalElement}).
-From there, let~$\gamma$ follow~$\delta$ on the surface until it either reaches the boundary or circles infinitely around a puncture.  
-Then~$\gamma$ is compatible with all curves in~$F$, a contradiction.
-\end{itemize}
-Thus~$F$ contains a curve going to the puncture.
-\end{proof}
-
-The following result extends \cite[Prop.~2.28]{PaluPilaudPlamondon} to the case of locally gentle algebras.
-
-\begin{proposition}
-\label{prop:numberOfDistinguishedArrows}
-In a non-kissing facet~$F$ of~$\NKC$,
-\begin{itemize}
-\item each bending walk of~$F$ has exactly two distinguished arrows,
-\item each finite straight walk of~$F$ has exactly one distinguished arrow,
-\item each infinite straight walk of~$F$ has no distinguished arrows.
-\end{itemize}
-\end{proposition}
-
-\begin{proof}
-The proof of \cite[Prop.~2.28]{PaluPilaudPlamondon} applies here to show that each walk in the non-kissing facet~$F$ has at most one distinguished arrow in each direction.
-Lemma~\ref{lem:ExistenceOfDistinguishedArrows} therefore shows the first two points.
-Finally, Lemma~\ref{lem:walksThroughcycles} shows the last point.
-\end{proof}
-
-We can now prove the purity result.
-
-\begin{proof}[Proof of Proposition \ref{prop:purity}.]
-The proof follows that of~\cite[Cor.~2.29]{PaluPilaudPlamondon}.
-Let~$b$ denote the number of bending walks, $s$ the number of finite straight walks, and $p$ the number of infinite straight walks in a non-kissing facet~$F$ of~$\NKC$.
-Since each finite straight walk uses two blossom arrows, we have~$s = 2|Q_0|-|Q_1|$ (see Remark~\ref{rem:sizeBlossomingQuiver}).
-Moreover, the infinite straight walks are just the primitive oriented cycles in~$\bar Q$.
-
-Using Proposition~\ref{prop:numberOfDistinguishedArrows}, we obtain by double-counting that
-\[
-2 * b + 1 * s + 0 * p= |Q_1\blossom| = 4|Q_0|-|Q_1|
-\]
-from which we derive that~$b = |Q_0|$ and~$b+s+p = 3|Q_0|-|Q_1|+p$.
-\end{proof}
-
-\subsection{Thinness of the non-crossing and non-kissing complexes, mutation}
-
-A simplicial complex is \defn{thin} if each codimension~$1$ face is contained in exactly two facets.
-We state the following results, which generalize \cite[Prop.~2.33 \& Cor.~2.35]{PaluPilaudPlamondon}, whose proofs apply without change.
-
-\begin{proposition}
-\label{prop:flip}
-Let~$F$ be a non-kissing facet in~$\NKC$ and let~$\omega \in F$ be a bending walk.
-Let~$\alpha$ and~$\beta$ be the distinguished arrows of~$\omega$ (see Proposition \ref{prop:numberOfDistinguishedArrows}), and~$\sigma$ be the distinguished substring of~$\omega$, which splits~$\omega$ into~$\omega = \rho \sigma \tau$.
-Let~$\alpha'$ and~$\beta'$ be the other two arrows of~$Q_1\blossom$ incident to the endpoints of~$\sigma$ and such that~$\alpha'\alpha \in I$ or~$\alpha\alpha' \in I$, and $\beta'\beta \in I$ or~$\beta\beta' \in I$.
-Let~$\mu \eqdef \distinguishedWalk{\alpha'}{F \ssm \{\omega\}}$ and~$\nu \eqdef \distinguishedWalk{\beta'}{F \ssm \{\omega\}}$ be the distinguished walks of~$F \ssm \{\omega\}$ at~$\alpha'$ and~$\beta'$ respectively.
-Then
-\begin{enumerate}[(i)]
-\item The walk~$\mu$ splits into~$\mu = \rho' \sigma \tau$ and the walk~$\nu$ splits into~$\nu = \rho \sigma \tau'$.
-\item The walk~$\omega' \eqdef \rho' \sigma \tau'$ is kissing~$\omega$ but no other~walk~of~$F$.
-Moreover, $\omega'$ is the only other (undirected) walk besides~$\omega$ which is not kissing any other walk of~$F \ssm \{\omega\}$.
-\end{enumerate}
-\end{proposition}
-The facet obtained from~$F$ by replacing the walk~$\omega$ by the walk~$\omega'$ of Proposition \ref{prop:flip} is the \defn{flip} or \defn{mutation} of~$F$ at~$\omega$.
-The flip is \defn{increasing} if~$\sigma$ is on top of~$\omega$, and \defn{decreasing} otherwise.
-
-\begin{figure}[t]
-	\capstart
-	\centerline{\includegraphics[scale=1]{flip1}}
-	\caption{A schematic representation of flips in the non-kissing complex.
-The flip exchanges the walk~$\omega = \rho \sigma \tau$ in the facet~$F$ (left) with the walk~$\omega' = \rho' \sigma \tau'$ in the facet~$F'$ (middle), using the walks~$\mu = \rho' \sigma \tau$ and~$\nu = \rho \sigma \tau'$.
-The walk~$\omega'$ kisses~$\omega$ but no other walk of~$F$ (right).}
-	\label{fig:flip1}
-\end{figure}
-
-\begin{corollary}
-\label{coro:thin}
-The reduced non-kissing complex~$\RNKC$ is thin and is thus a pseudomanifold without boundary.
-\end{corollary}
-
-The mutation of non-kissing facets translates on~$\surface(\bar Q)$ as follows.
-
-\begin{proposition}
-\label{prop:mutationAccordions}
-Let~$F$ be a facet of the non-crossing complex~$\NCC$, and let~$\gamma \in F$.  We represent all curves on the universal cover of~$\surface(\bar Q)$.
-Then~$F$ forms a~$B$-dissection of the surface, and~$\gamma$ lies in at least one of two configutations~$\ZZZ$ and~$\SSS$ with the other curves of the dissection (where the endpoints may go to infinity if punctures are involved).
-See \fref{fig:flip3}.
-\begin{itemize}
-\item Exactly one of the curves obtained by changing the~$\SSS$ to a~$\ZZZ$ (and conversely) by moving the endpoints of~$\gamma$ along the top and bottom curves is a~$\dissection$-accordion.
-\item This~$\dissection$-accordion yields the flip or mutation of~$F$ at~$\gamma$.
-\item If the flip is increasing, then the~$\ZZZ$ is turned into a~$\SSS$.  If the flip is decreasing, then the~$\SSS$ is turned in to a~$\ZZZ$.
-\end{itemize}
-%
-\begin{figure}[h]
-	\capstart
-	\centerline{\includegraphics[scale=1]{flip3}}
-	\caption{An increasing flip turns a~$\ZZZ$ (formed by~$\mu$, $\omega$ and~$\nu$) to a~$\SSS$ (formed by~$\mu$, $\omega'$ and~$\nu$). The two curves~$\omega$ and~$\omega'$ are crossing.}
-	\label{fig:flip3}
-\end{figure}
-\end{proposition}
-
-\begin{proof}
-Let~$\omega = \walk(\gamma)$.
-Using the notation of Proposition \ref{prop:flip}, the local configuration around~$\omega$ (as in Figures~\ref{fig:flip1} and~\ref{fig:flip2}) translates on the (universal cover of the) surface~$\surface(\bar Q)$ as follows.
-%
-\begin{figure}[h]
-	\capstart
-	\centerline{\includegraphics[scale=1]{flip2}}
-	\caption{A schematic representation of flips in the non-crossing complex.
-The flip exchanges the curve~$\omega$ in the facet~$F$ (left) with the curve~$\omega'$ in the facet~$F'$ (middle), using the curves~$\mu$ and~$\nu$.
-The curve~$\omega'$ crosses~$\omega$ but no other curve of~$F$ (right).}
-	\label{fig:flip2}
-\end{figure}
-%
-We see that the only two~$\dissection$-accordions found between~$\mu$ and~$\curveof(\omega)$ are~$\mu$ and~$\curveof(\omega)$ themselves.
-The same holds by replacing~$\mu$ with~$\nu$.
-Thus~$\mu, \nu$ and~$\curveof(\omega)$ lie in a~$\SSS$ or a~$\ZZZ$.
-%
-We see that~$\curveof(\omega')$ is then obtained as claimed. The direction of the flip translates from the picture in a similar way.
-\end{proof}
-
-\section{$\b{g}$-vectors, $\b{c}$-vectors, and $\b{d}$-vectors}
-\label{sec:vectors}
-
-In this section, we define three relevant families of vectors associated to walks in the non-kissing complex of a locally gentle quiver~$\bar Q$.
-In contrast to the $\b{d}$-vectors, the $\b{g}$- and $\b{c}$-vectors were already considered in the non-kissing complex of a gentle quiver~\cite[Sect.~4.2]{PaluPilaudPlamondon}, and their definition immediately generalizes to the case of locally gentle algebras.
-All these vectors have algebraic motivations that we prefer to omit in the present paper to remain focused on the two-sided combinatorics of the non-kissing and non-crossing models.
-Our objective is to provide interpretations of these vectors in terms of the surface~$\surface_{\bar Q}$.
-
-\subsection{$\b{g}$-vectors, $\b{c}$-vectors, and $\b{d}$-vectors for walks}
-\label{subsec:gcdVectorsWalks}
-
-Let~$\bar Q = (Q,I)$ be a locally gentle bound quiver, and let~$(\b{e}_a)_{a \in Q_0}$ denote the standard basis of~$\R^{Q_0}$.
-
-\begin{definition}
-For a multiset~$V \eqdef \{a_1, \dots, a_m\}$ of vertices of~$Q_0$, we denote by~$\multiplicityVector_V \in \R^{Q_0}$ the \defn{multiplicity vector} of~$V$, defined by
-\[
-\multiplicityVector_V \eqdef \sum_{i \in [m]} \b{e}_{a_i} = \sum_{a \in Q_0} |\set{i \in [m]}{a_i = a}| \, \b{e}_a.
-\]
-For a string~$\sigma$ of~$\bar Q$, we define~$\multiplicityVector_\sigma \eqdef \multiplicityVector_{V(\sigma)}$ where~$V(\sigma)$ is the multiset of vertices of~$\sigma$. 
-\end{definition}
-
-We now recall two definitions from~\cite{PaluPilaudPlamondon} that still make sense for locally gentle algebras.
-
-\begin{definition}
-\label{def:gVectorsWalks}
-For any walk~$\omega$ of~$\bar Q$, we let~$\peaks{\omega}$ (resp.~by~$\deeps{\omega}$) be the multiset of vertices of~$Q_0$ corresponding to the peaks (resp.~deeps) of~$\omega$.
-The \defn{$\b{g}$-vector} of the walk~$\omega$ is the vector~${\gvector{\omega} \in \R^{Q_0}}$ defined by
-\[
-\gvector{\omega} \eqdef \multiplicityVector_{\peaks{\omega}} - \multiplicityVector_{\deeps{\omega}}.
-\]
-For a set~$\Omega$ of walks, we let~$\gvectors{\Omega} \eqdef \set{\gvector{\omega}}{\omega \in \Omega}$.
-Observe that, if~$\omega$ is a straight walk, then~$\gvector{\omega} = 0$. Moreover, since any infinite walk~$\omega$ is eventually cyclic, the coordinates of~$\gvector{\omega}$ are always finite.
-\end{definition}
-
-\begin{definition}
-\label{def:cVectorsWalks}
-Let~$F \in \RNKC$ be a non-kissing facet and $\omega$ be a walk in~$F$.
-Define
-\[
-\distinguishedSign{\omega}{F} \eqdef 
-\begin{cases}
-\phantom{-}1 & \text{if~$\distinguishedString{\omega}{F}$ is a top substring of~$\omega$ (\ie if~$\distinguishedArrows{\omega}{F}$ point outside),} \\
--1 & \text{if~$\distinguishedString{\omega}{F}$ is a bottom substring of~$\omega$ (\ie if~$\distinguishedArrows{\omega}{F}$ point inside),}
-\end{cases}
-\]
-where~$\distinguishedString{\omega}{F}$ is the distinguished string and~$\distinguishedArrows{\omega}{F}$ are the distinguished arrows of~$\omega$ in~$F$ (see Definition~\ref{def:distinguishedWalksAndArrows}).
-The \defn{$\b{c}$-vector} of a walk~$\omega$ of~$F$ is the vector~${\cvector{\omega}{F} \in \R^{Q_0}}$ defined by
-\[
-\cvector{\omega}{F} \eqdef \distinguishedSign{\omega}{F} \, \multiplicityVector_{\distinguishedString{\omega}{F}}.
-\]
-We let~$\cvectors{F} \eqdef \set{\cvector{\omega}{F}}{\omega \in F}$ be the set of $\b{c}$-vectors of a non-kissing facet~$F \in \RNKC$, and~$\allcvectors \eqdef \bigcup_F \cvectors{F}$ be the set of all $\b{c}$-vectors of all non-kissing facets~${F \in \RNKC}$.
-\end{definition}
-
-We now introduce another algebraically motivated family of vectors that was omitted in~\cite{PaluPilaudPlamondon}.
-We first need to introduce the kissing number.
-
-\begin{definition}
-\label{def:kissingNumber}
-For two walks~$\omega$ and~$\omega'$ of~$\bar Q$, denote by~$\kn(\omega,\omega')$ the number of times that~$\omega$ kisses $\omega'$.
-Note that kisses are counted with multiplicities if~$\omega$ or~$\omega'$ pass twice through the same substring.
-Observe also that~$\kn(\omega,\omega')$ is finite since any infinite walk is eventually cyclic.
-The \defn{kissing number} of~$\omega$ and~$\omega'$ is~$\KN(\omega,\omega') \eqdef \kn(\omega,\omega') + \kn(\omega',\omega)$.
-\end{definition}
-
-\begin{definition}
-\label{def:dVectorsWalks}
-The \defn{$\b{d}$-vector} of a walk~$\omega$ is the vector~$\dvector{\omega} \in \R^{Q_0}$ defined by
-\[
-\dvector{\omega} \eqdef 
-\begin{cases}
-- \b{e}_a & \text{if $\omega$ is the deep walk~$a_\deep$ with a unique deep at~$a$,} \\
-\displaystyle \sum_{a \in Q_0} \kn(\omega, a_\deep) \, \b{e}_a & \text{otherwise.}
-\end{cases}
-\]
-For a set~$\Omega$ of walks, we let~$\dvectors{\Omega} \eqdef \set{\dvector{\omega}}{\omega \in \Omega}$.
-\end{definition}
-
-\begin{example}
-\label{exm:gcdVectorsWalks}
-For instance, the $\b{g}$-, $\b{c}$-, and $\b{d}$-matrices of the facet illustrated in \fref{fig:gcdVectors} are given by
-\[
-\gvectors{F} = 
-\begin{blockarray}{ccc}
-	{\color{blue} \bullet} & {\color{violet} \bullet} & \\[-.1cm]
-	\begin{block}{[cc]c}
-	1 & 0 & \!\!\!\circled{1} \\
-	-1\!\! & \!\!-1 & \!\!\!\circled{2} \\
-	\end{block}
-\end{blockarray}
-\qquad\qquad
-\cvectors{F} = 
-\begin{blockarray}{ccc}
-	{\color{blue} \bullet} & {\color{violet} \bullet} & \\[-.1cm]
-	\begin{block}{[cc]c}
-	1 & \!\!-1 & \!\!\!\circled{1} \\
-	0 & \!\!-1 & \!\!\!\circled{2} \\
-	\end{block}
-\end{blockarray}
-\qquad\qquad
-\dvectors{F} = 
-\begin{blockarray}{ccc}
-	{\color{blue} \bullet} & {\color{violet} \bullet} & \\[-.1cm]
-	\begin{block}{[cc]c}
-	1 & 0 & \!\!\!\circled{1} \\
-	0 & -1 & \!\!\!\circled{2} \\
-	\end{block}
-\end{blockarray}
-\]
-(\ie columns are the $\b{g}$-, $\b{c}$-, $\b{d}$-vectors of the elements of the facet).
-
-\begin{figure}[t]
-	\capstart
-	\centerline{\includegraphics[scale=.7]{gcdVectors}}
-	\caption{A non-kissing facet of~$\RNKC$ (left), an accordion facet~$\RAC$ (middle) and a slalom facet~$\RSC$ (right) that correspond via the bijections of Theorem~\ref{thm:complexesCoincide} and Proposition~\ref{prop:accordionsSlaloms}.
-The~$\b{g}$-, $\b{c}$-, and $\b{d}$-matrices of this facet are given in Example~\ref{exm:gcdVectorsWalks}.}
-	\label{fig:gcdVectors}
-\end{figure}
-\end{example}
-
-\subsection{$\b{g}$-vectors, $\b{c}$-vectors, and~$\b{d}$-vectors on the surface}
-\label{subsec:gcdVectorsSurface}
-
-Our objective is now to interpret the three families of vectors of Section~\ref{subsec:gcdVectorsWalks} in terms of accordions and slaloms on the surface.
-According to Remark~\ref{rem:propertiesSurface}\,\eqref{item:edges}, each vertex~$a$ of~$Q$ corresponds to an edge~$\edgeof(a)$ in the dissection~$\dissection_{\bar Q}$ and  to an edge~$\dualedgeof(a) = \edgeof(a)\dual$ in the dual dissection~${\dissection\dual\!\!_{\bar Q}}$.
-Recall moreover from Lemma~\ref{lemm:curveOfAWalkIsAccordion} and Proposition~\ref{prop:accordionsSlaloms} that each non-kissing walk~$\omega$ in~$\bar Q$ corresponds to a curve~$\curveof(\omega)$ that is both a $\dissection$-accordion and a $\dissection\dual$-slalom.
-The following three statements translate the definitions of $\b{g}$-, $\b{c}$- and $\b{d}$-vectors on the surface.
-The proofs are left to the reader.
-We note that these interpretations were already used in~\cite{MannevillePilaud-accordion, GarverMcConville} when the surface is a disk.
-When~$\dissection$ is a triangulation of~$\surface$, these interpretations coincide with those given in terms of triangulations and laminations for cluster algebras from surfaces by S.~Fomin and D.~Thurston~\cite{FominThurston}.
-
-\begin{proposition}
-\label{prop:gVectorsSurface}
-For a walk~$\omega$ of~$\bar Q$ and a vertex~$a \in Q_0$, the $a$-th entry of the $\b{g}$-vector~$\gvector{\omega}$ is given~by:
-\begin{enumerate}[(i)]
-\item The number of times that the $\dissection$-accordion~$\curveof(\omega)$ positively crosses the edge~$\edgeof(a)$ of~$\dissection$ minus the number of times it negatively crosses the edge~$\edgeof(a)$ of~$\dissection$.
-Here, the crossing is positive (resp.~negative) if the two angles of~$\dissection$ crossed by~$\curveof(\alpha)$ just before and after~$\edgeof(a)$ form a~$\SSS$ (resp.~a~$\ZZZ$).
-We note that some crossings are neither positive nor negative.
-\item The number of times that the $\dissection\dual$-slalom~$\curveof(\omega)$ positively crosses the edge~$\dualedgeof(a)$ of~$\dissection\dual$ minus the number of times it negatively crosses the edge~$\dualedgeof(a)$ of~$\dissection\dual$.
-Here, the crossing is positive when~$\curveof(\omega)$ leaves a face~$u\dual$ to enter a face~$v\dual$ with the vertex~$u$ being to its right (and thus with~$v$ being to its left), and the crossing is negative otherwise.
-We note that, in this case, each crossing is either positive or negative.
-\end{enumerate}
-\end{proposition}
-
-\begin{proposition}
-\label{prop:cVectorsSurface}
-Consider a walk~$\omega$ of~$\bar Q$ in a non-kissing facet~$F \in \RNKC$.
-Call \defn{distinguished subcurve} of~$\curveof(\omega)$ in~$\curveof(F)$ the part of~$\curveof(\omega)$ which lies strictly between the two angles of~$\dissection$ (or of~$\dissection\dual$) where~$\curveof(\omega)$ is maximal (see Remark~\ref{rem:countercurrentOrderOnSurface}).
-For a vertex~$a \in Q_0$, the $a$-th entry of the $\b{c}$-vector~$\cvector{\omega}{F}$ is, up to the sign, given by:
-\begin{enumerate}[(i)]
-\item the number of crossings between the distinguished subcurve of~$\curveof(\omega)$ in~$\curveof(F)$ and the edge~$\edgeof(a)$ of the dissection~$\dissection$,
-\item the number of times the distinguished subcurve of~$\curveof(\omega)$ in~$\curveof(F)$ follows the edge~$\dualedgeof(a)$ of the dual dissection~$\dissection\dual$.
-Here, we say that a curve~$\delta$ follows~$\dualedgeof(a)$ if~$\dualedgeof(a)$ lies on the boundary opposite to~$u$ of a face~$u\dual$ of~$\dissection\dual$ crossed by~$\delta$.
-\end{enumerate}
-\end{proposition}
-
-\begin{remark}
-Observe that although we gave interpretations for the $\b{g}$- and~$\b{c}$-vectors both in terms of accordions and slaloms, we consider that the slaloms naturally correspond to~$\b{g}$-vectors, while the accordions are more suited for~$\b{c}$-vectors.
-\end{remark}
-
-\begin{proposition}
-\label{prop:dVectorsSurface}
-Denote by~$X_\deep \eqdef \set{\curveof(a_\deep)}{a \in Q_0}$ the deep facet of the non-crossing complex obtained by slightly rotating~$\dissection_{\bar Q}$ counterclockwise as described in Example~\ref{exm:peakDeepFacets}.
-For a walk~$\omega$ of~$\bar Q$ and a vertex~$a \in Q_0$, the $a$-th entry of the $\b{d}$-vector~$\dvector{\omega}$ is either~$-1$ if~$\omega = a_\peak$ or the number of crossings of the curve~$\gamma(\omega)$ with the edge~$\curveof(a_\deep)$ of~$X_\deep$ corresponding to~$a$.
-\end{proposition}
-
-\subsection{Geometric properties of these vectors}
-\label{subsec:geometricProperties}
-
-We now gather some statements about $\b{g}$-, $\b{c}$-, and~$\b{d}$-vectors, essentially borrowed from~\cite[Part.~4]{PaluPilaudPlamondon}.
-
-\begin{proposition}
-\label{rem:signCoherence}
-The $\b{g}$-, $\b{c}$-, and~$\b{d}$-vectors have the \defn{sign-coherence property}: for any non-kissing facet~$F \in \RNKC$,
-\begin{itemize}
-\item for~$a \in Q_0$, the~$a$-th coordinates of all $\b{g}$-vectors~$\gvector{\omega}$ for~$\omega \in F$ have the same sign,
-\item for any~$\omega \in F$, all coordinates of the $\b{c}$-vector~$\cvector{\omega}{F}$ have the same sign,
-\item for any~$\omega \in F$, all coordinates of the $\b{d}$-vector~$\dvector{\omega}$ have the same sign.
-\end{itemize}
-\end{proposition}
-
-\begin{proof}
-For the $\b{g}$-vectors, observe that two walks~$\omega$ and~$\omega'$ whose $\b{g}$-vectors~$\gvector{\omega}$ and~$\gvector{\omega'}$ have opposite signs on their~$a$-th coordinate automatically kiss at~$a$.
-For $\b{c}$- and $\b{d}$-vectors, the statement is immediate from the definition.
-\end{proof}
-
-\begin{proposition}
-\label{prop:gvectorscvectorsDualBases}
-For any non-kissing facet~$F \in \RNKC$, the set of $\b{g}$-vectors~$\gvectors{F}$ and the set of $\b{c}$-vectors~$\cvectors{F}$ form dual bases. 
-\end{proposition}
-
-\begin{proof}
-Noting that the distinguished string of a walk in a given non-kissing facet is always a finite substring, the proof of~\cite[Proposition 4.16]{PaluPilaudPlamondon} applies \emph{verbatim}.
-\end{proof}
-
-\begin{example}
-For instance, one can check that~$\gvectors{F} \cdot \transpose{\cvectors{F}} = 1$ in Example~\ref{exm:gcdVectorsWalks}.
-\end{example}
-
-Finally, we borrow the following geometric statement from~\cite{PaluPilaudPlamondon}.
-We refer to \cite{Ziegler-polytopes} for basic notions on polyhedral geometry (polytopes and normal fans).
-
-\begin{theorem}
-\label{thm:fanAssociahedron}
-Let~$\bar Q$ be a locally gentle bound quiver such that~$\NKC$ is finite. The collection of cones
-\[
-\gvectorFan \eqdef \bigset{\R_{\ge0} \gvectors{F}}{F \text{ non-kissing face of } \RNKC}.
-\]
-is a complete simplicial fan, called the \defn{$\b{g}$-vector fan} of~$\bar Q$.
-Moreover, $\gvectorFan$ is the normal fan of the \defn{$\bar Q$-associahedron} defined equivalently as
-\begin{itemize}
-\item the convex hull of the points~$\point{F} \eqdef \sum_{\omega \in F} \KN(\omega) \, \cvector{\omega}{F}$ for all facets~${F \in \RNKC}$,~or
-\item the intersection of the halfspaces~$\HS{\omega} \eqdef \bigset{\b{x} \in \R^{Q_0}}{\dotprod{\gvector{\omega}}{\b{x}} \le \KN(\omega)}$ for all walks~$\omega$ on~$\bar Q$,
-\end{itemize}
-where $\KN(\omega) \eqdef \sum_{\omega'} \KN(\omega,\omega')$ is the (finite) sum of the kissing numbers of Definition~\ref{def:kissingNumber}.
-\end{theorem}
-
-\begin{proof}
-The proof is identical to that of Theorem 4.17 and Theorem 4.27 of~\cite{PaluPilaudPlamondon}.
-\end{proof}
-
-\fref{fig:fanAssociahedron} illustrates Theorem~\ref{thm:fanAssociahedron}.
-
-\begin{figure}[p]
-	\capstart
-	\centerline{\includegraphics[scale=.5]{fanAssociahedron1}}
-	\vspace{.5cm}
-	\centerline{\includegraphics[scale=.5]{fanAssociahedron2}}
-	\vspace{.5cm}
-	\centerline{\includegraphics[scale=.5]{fanAssociahedron3}}
-	\caption{The $\b{g}$-vector fan~$\gvectorFan$ (left) and the $\bar Q$-associahedron~$\Asso$ (right) of three locally gentle quivers.
-The first two are gentle and the illustration is borrowed from~\cite{PaluPilaudPlamondon}.
-The last is locally gentle but not gentle.}
-	\label{fig:fanAssociahedron}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\bibliographystyle{alpha}
-\bibliography{accordionComplexSurfaces}
-\label{sec:biblio}
-
-\end{document}

### 2018-11-05 secondPaper/FPSAC/nonkissing-noncrossing-FPSAC.tex
FPSAC

%% if you are submitting an initial manuscript then you should have submission as an option here
%% if you are submitting a revised manuscript then you should have revision as an option here
%% otherwise options taken by the article class will be accepted
\documentclass[submission]{FPSAC2019}
%% but DO NOT pass any options (or change anything else anywhere) which alters page size / layout / font size etc

%% note that the class file already loads {amsmath, amsthm, amssymb}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{notation}[theorem]{Notation}
\newtheorem{convention}[theorem]{Convention}
\newtheorem*{theorem*}{Theorem}%[section]

\usepackage{paralist}
\usepackage{xargs}
\usepackage{ulem}\normalem
\usepackage{pifont}
\usepackage{picins/picins}
\usepackage{tikz}
\usepackage{tkz-graph}
\usetikzlibrary{trees, decorations, decorations.markings, shapes, arrows, matrix, calc, fit, intersections, patterns, angles}

\graphicspath{{figures/}}

%%%%% AUTHOR'S COMMANDS %%%%%

% special letters
\newcommand{\R}{\mathbb{R}} % reals
\newcommand{\N}{\mathbb{N}} % naturals
\newcommand{\Z}{\mathbb{Z}} % integers
\newcommand{\C}{\mathbb{C}} % complex

% math commands
\newcommand{\set}[2]{\left\{ #1 \;\middle|\; #2 \right\}} % set notation
\newcommand{\bigset}[2]{\big\{ #1 \;|\; #2 \big\}} % big set notation
\newcommand{\biggset}[2]{\bigg\{ #1 \;\bigg|\; #2 \bigg\}} % bigg set notation
\newcommand{\ssm}{\smallsetminus} % small set minus
\newcommand{\dotprod}[2]{\langle \, #1 \; | \; #2 \, \rangle} % dot product
\newcommand{\symdif}{\,\triangle\,} % symmetric difference
\newcommand{\one}{{1\!\!1}} % the all one vector
\newcommand{\eqdef}{\mbox{\,\raisebox{0.2ex}{\scriptsize\ensuremath{\mathrm:}}\ensuremath{=}\,}} % :=
\newcommand{\defeq}{\mbox{~\ensuremath{=}\raisebox{0.2ex}{\scriptsize\ensuremath{\mathrm:}} }} % =:

% others
\newcommand{\ie}{\textit{i.e.}~} % id est
\newcommand{\eg}{\textit{e.g.}~} % exempli gratia
\newcommand{\Eg}{\textit{E.g.}~} % Exempli gratia
\newcommand{\viceversa}{\textit{vice versa}} % exempli gratia
\newcommand{\red}{\color{red}} % red command
\newcommand{\blue}{\color{blue}} % blue command
\definecolor{green}{RGB}{57,181,74} % green color
\newcommand{\green}{\color{green}} % green command
\newcommand{\defn}[1]{\uline{\textit{#1}}} % emphasis of a definition
\newcommand{\fref}[1]{Fig.\,\ref{#1}} % reference to figure

% COMBINATORICS
% quiver
\newcommand{\blossom}{^\text{\ding{96}}} % blossom
\newcommand{\Enrs}[1]{E_{nr}^{s}(#1)}
\newcommand{\Ers}[1]{E_{r}^{s}(#1)}
\newcommand{\Enrt}[1]{E_{nr}^{t}(#1)}
\newcommand{\Ert}[1]{E_{r}^{t}(#1)}

% walks
\newcommand{\peaks}[1]{\mathsf{peaks}(#1)} % peaks
\newcommand{\deeps}[1]{\mathsf{deeps}(#1)} % deeps
\newcommand{\distinguishedWalk}[2]{\mathsf{dw}(#1,#2)} % distinguished walk
\newcommand{\distinguishedArrows}[2]{\mathsf{da}(#1,#2)} % distinguished arrows
\newcommand{\distinguishedString}[2]{\mathsf{ds}(#1,#2)} % distinguished string
\newcommand{\distinguishedSign}[2]{\varepsilon(#1,#2)} % distinguished sign

% non-kissing complex, lattice, flip graph
\newcommand{\kn}{\kappa} % kissing number
\newcommand{\KN}{\textsc{kn}} % Kissing Number
\newcommandx{\NKC}[1][1=\bar Q]{\mathcal{K}_{\mathrm{nk}}(#1)} % non-kissing complex
\newcommandx{\RNKC}[1][1=\bar Q]{\mathcal{C}_{\mathrm{nk}}(#1)} % non-kissing complex
\newcommandx{\NKL}[1][1=\bar Q]{\mathcal{L}_{\mathrm{nk}}(#1)} % non-kissing lattice
\newcommandx{\NKG}[1][1=\bar Q]{\mathcal{G}_{\mathrm{nk}}(#1)} % non-kissing flip graph
\newcommandx{\NFC}[1][1=\bar Q]{\mathcal{C}_{\mathrm{nf}}(#1)} % non-friendly complex
\newcommand{\peak}{\mathrm{peak}} % bottom dissection
\newcommand{\deep}{\mathrm{deep}} % top dissection
\newcommand{\reversed}[1]{#1^{\mathrm{rev}}} % reverse all arrows
\renewcommand{\top}{\mathrm{top}} % top
\newcommand{\bottom}{\mathrm{bot}} % bottom
\newcommand{\walk}{\omega} % walk (of a curve)

% accordion and slalom complexes
\newcommand{\surface}{\mathcal{S}} % an orientable surface
\newcommand{\dual}{^*} % duality
\newcommand{\dissection}{\mathrm{D}} % dissection of a marked surface
\newcommand{\vertices}{\mathcal{V}} % vertices of a dissection
\newcommand{\edges}{\mathcal{E}} % edges of a dissection
\newcommand{\faces}{\mathcal{F}} % faces of a dissection
\newcommandx{\AC}[1][1=\dissection]{\mathcal{K}_{\mathrm{acc}}(#1)} % accordion complex
\newcommandx{\RAC}[1][1=\dissection]{\mathcal{C}_{\mathrm{acc}}(#1)} % reduced accordion complex
\newcommandx{\SC}[1][1=\dissection\dual]{\mathcal{K}_{\mathrm{sla}}(#1)} % slalom complex
\newcommandx{\RSC}[1][1=\dissection\dual]{\mathcal{C}_{\mathrm{sla}}(#1)} % reduced slalom complex
\newcommandx{\NCC}[1][1={\dissection, \dissection\dual}]{\mathcal{K}_{\mathrm{nc}}(#1)} % non-crossing complex
\newcommandx{\RNCC}[1][1={\dissection, \dissection\dual}]{\mathcal{C}_{\mathrm{nc}}(#1)} % non-crossing complex
\newcommand{\curveof}{\gamma} % curve (of a walk)
\newcommand{\edgeof}{\varepsilon} % arc of a vertex
\newcommand{\dualedgeof}{\varepsilon\dual} % dual arc of a vertex
\DeclareRobustCommand{\SSS}{\reflectbox{$\mathsf{Z}$}} % S
\DeclareRobustCommand{\ZZZ}{\mathsf{Z}} % Z
\newcommand{\koszul}{^!} % duality

%%%%% END AUTHOR'S COMMANDS %%%%%

%% define your title in the usual way
\title{Non-kissing versus non-crossing}

%% define your authors in the usual way
%% use \addressmark{1}, \addressmark{2} etc for the institutions, and use \thanks{} for contact details
\author{
	Yann Palu\thanks{\href{mailto:yann.palu@u-picardie.fr}{yann.palu@u-picardie.fr}. Supp. by ANR SC3A~15\,CE40\,0004\,01.}\addressmark{1},
	\stepcounter{footnote}
	Vincent Pilaud\thanks{\href{mailto:vincent.pilaud@lix.polytechnique.fr}{vincent.pilaud@lix.polytechnique.fr}. Supp. by ANR SC3A~15\,CE40\,0004\,01 and CAPPS~17\,CE40\,0018.}\addressmark{2},
	\and
	Pierre-Guy Plamondon\thanks{\href{mailto:pierre-guy.plamondon@math.u-psud.fr}{pierre-guy.plamondon@math.u-psud.fr}. Supp. by ANR SC3A~15\,CE40\,0004\,01.}\addressmark{3}
}

%% then use \addressmark to match authors to institutions here
\address{
	\addressmark{1} LAMFA, Universit\'e Picardie Jules Verne, Amiens \\
	\addressmark{2} CNRS \& LIX, \'Ecole Polytechnique, Palaiseau, France \\
	\addressmark{3} Laboratoire de Math\'ematiques d'Orsay, Universit\'e Paris-Sud, CNRS, Universit\'e Paris-Saclay
}

%% put the date of submission here
\received{\today}

%% leave this blank until submitting a revised version
%\revised{}

%% put your English abstract here, or comment this out if you don't have one yet
%% please don't use custom commands in your abstract / resume, as these will be displayed online
%% likewise for citations -- please don't use \cite, and instead write out your citation as something like (author year)
\abstract{
Starting from a locally gentle bound quiver, we define on the one hand a simplicial complex, called the non-kissing complex.
On the other hand, we construct a punctured, marked, oriented surface with boundary, endowed with a pair of dual dissections.
From those geometric data, we define two simplicial complexes: the accordion complex, and the slalom complex, generalizing work of A.~Garver and T.~McConville in the case of a disk.
We show that all three complexes are isomorphic.
%, and that they are pure and thin.
%In particular, there is a notion of mutation on their facets, akin to $\tau$-tilting mutation.
%Along the way, we also construct inverse bijections between the set of isomorphism classes of locally gentle bound quivers and the set of homeomorphism classes of punctured, marked, oriented surfaces with boundary, endowed with a pair of dual dissections.
}

%% put your French abstract here, or comment this out if you don't have one
\resumetitle{Résumé}
\resume{
Étant donné un carquois localement aimable, nous définissons d'une part un complexe simplicial appelé complexe platonique. D'autre part, nous construisons une surface orientable à bord pointée et marquée, munie d'une paire de dissections duales. À partir de cette donnée géométrique, nous définissons deux autres complexes simpliciaux : le complexe d'accordéons et le complexe des slaloms qui généralisent les travaux de A.~Garver et T.~McConville dans le cas du disque. Nous montrons que ces trois complexes sont isomorphes.
}

%% put your keywords here, or comment this out if you don't have them yet
\keywords{Gentle algebras, non-kissing complex, non-crossing complex}

%% you can include your bibliography however you want, but using an external .bib file is STRONGLY RECOMMENDED and will make the editor's life much easier
%% regardless of how you do it, please use numerical citations, ie. [xx, yy] in the text

%% this sample uses biblatex, which (among other things) takes care of URLs in a more flexible way than bibtex
%% but you can use bibtex if you want
\usepackage[backend=bibtex, firstinits=true, maxbibnames=99]{biblatex}
\DeclareFieldFormat[article,inbook,incollection,inproceedings,patent,thesis,unpublished]{title}{\textit{#1}\isdot}
\renewbibmacro{in:}{}
\addbibresource{nonkissing-noncrossing-FPSAC.bib}
%% note the \printbibliography command at the end of the file which goes with these biblatex commands

\begin{document}

\maketitle
%% note that you DO NOT have to put your abstract here -- it is generated by \maketitle and the \abstract and \resume commands above

\section{Introduction}

This extended abstract reports on~\cite{PaluPilaudPlamondon-surfaces}, where more details and proofs are available.~It aims to show that two combinatorial objects, called the \emph{non-kissing complex} and the \emph{non-crossing complex}, are isomorphic.
Both complexes appeared in different works in specific cases: the non-kissing complex of a grid appeared in \cite{McConville}, while the non-crossing complex of a disk appeared in \cite{GarverMcConville, MannevillePilaud-accordion}.
It was shown in \cite{PaluPilaudPlamondon} that these complexes are special cases of a more general simplicial complex, defined for any gentle algebra (see~also~\cite{BrustleDouvilleMousavandThomasYildirim}).

In order to unify these two objects, we are lead to introduce two generalizations.
On the algebraic side, the non-kissing complex is extended from the class of gentle algebras to that of locally gentle algebras (which are an infinite-dimensional version of gentle algebras).
On the geometric side, we construct the non-crossing complex of an arbitrary oriented punctured surface endowed with a pair of dual dissections.

The two main objects of our study will thus be locally gentle algebras and dissections of surfaces.
Our first result is that these two classes of objects are essentially the~same.

\begin{theorem*}[\ref{thm:bijectionLocallyGentleAndSurfaces}]
There is an explicit bijection between the set of isomorphism classes of locally gentle bound quivers and the set of homeomorphism classes of oriented punctured marked surfaces with boundary endowed with a pair of dual cellular dissections.
\end{theorem*}

On the algebraic side, we extend the study of walks from the gentle case~\cite{McConville, PaluPilaudPlamondon} to the locally gentle case, and define a notion of compatibility called non-kissing (see Sect.\,\ref{sec:nonKissingComplex}).
On the geometric side, we extend the study of dissections, accordions and slaloms from the case of the disk~\cite{GarverMcConville, MannevillePilaud-accordion} to the case of an arbitrary surface, and define a notion of compatibility called non-crossing (see Sect.\,\ref{sec:accordionSlalomNonCrossingComplexes}).
The combinatorial information contained in these notions is encoded in simplicial complexes: the non-kissing complex~$\NKC$ and the non-crossing complex~$\NCC$.
Our second result is the following.

\begin{theorem*}[\ref{thm:complexesCoincide}]
The complexes~$\NKC$ and~$\NCC$ are isomorphic.
\end{theorem*}

%Finally, we show in Section \ref{sec:propertiesOfComplexes} that these complexes are combinatorially very well-behaved.
%
%\begin{theorem}[\ref{prop:purity} and \ref{coro:thin}]
%The complexes~$\NKC$ and~$\NCC$ are pure and thin.  Their dimension is computed, and mutation is explicitly described.
%\end{theorem}
%
%We end in Section \ref{sec:vectors} with a discussion of~$\b{g}$-vectors,~$\b{c}$-vectors and~$\b{d}$-vectors associated to walks and curves.
%Consequences on the representation theory of locally gentle algebras will be investigated in a future project.

Let us briefly review the algebraic and geometric objects which appear in this paper.
%
Gentle algebras are a class of finite-dimensional associative algebras over a field, defined by generators and relations.
Their representation theory was first systematically investigated in~\cite{ButlerRingel}, and they have been thouroughly studied since.
Locally gentle algebras are obtained by dropping the requirement that gentle algebras be finite-dimensional.
It turns out that their representation theory is also well-behaved \cite{Crawley-Boevey} and that these algebras are Koszul \cite{BessenrodtHolm}.
The $\tau$-tilting theory \cite{AdachiIyamaReiten} of gentle algebras was recently studied~in~\mbox{\cite{PaluPilaudPlamondon, BrustleDouvilleMousavandThomasYildirim}}.

Dissections of surfaces, on the other hand, are certain collections of pairwise non-intersecting curves on an orientable surface.
They have been defined and studied in \cite{Chapoton-quadrangulations, GarverMcConville, MannevillePilaud-accordion} in the case where the surface is an unpunctured disk.

The idea of associating a finite-dimensional algebra to a dissection (or a triangulation) of a surface seems to take its roots in the theory of cluster algebras and cluster categories.
This was first done for triangulations of polygons in \cite{CalderoChapotonSchiffler}, and then for any orientable surface with boundary in \cite{ABCP, Labardini}.  
The algebra of a dissection as we shall use it in this paper has appeared in \cite{DavidRoeslerSchiffler}.
In most of the above cases, the algebras obtained are gentle algebras.
It has also been shown in \cite{BaurCoelhoSimoes} that any gentle algebra is obtained from a dissection of a surface, and that the module category of the algebra can be interpreted by using curves on the surface.
In the case where the surface is a polygon, the $\tau$-tilting theory of the algebra of a dissection has been studied in \cite{PaluPilaudPlamondon}.%, PilaudPlamondonStella}.

Conversely, the construction of a surface associated to a gentle algebra has appeared in \cite{OpperPlamondonSchroll}.
We give a different construction of the same surface in this paper, which is obtained by ``glueing'' quadrilaterals to the arrows of the blossoming quiver (as defined in \cite{PaluPilaudPlamondon}, and called ``fringed quiver'' in \cite{BrustleDouvilleMousavandThomasYildirim}).
Our construction has the advantage that it easily yields the two dual dissections of the surface at the same time (the dissection and dual lamination of \cite{OpperPlamondonSchroll}).
Note that our dissections are always cellular, while those in \cite{BaurCoelhoSimoes} can be arbitrary.
%Remarkably, gentle algebras and surfaces were linked recently in \cite{HaidenKatzarkovKontsevich, LekiliPolishchuk}, where the Fukaya category of the surface is shown to be equivalent to the bounded derived category of the associated gentle~algebra.

\newpage
\section{Non-kissing complex}
\label{sec:nonKissingComplex}

%We first quickly review the definition of the non-kissing complex of a gentle bound quiver following the presentation of~\cite{PaluPilaudPlamondon} and extend it to locally gentle bound quivers.

\subsection{Locally gentle bound quivers and their blossoming quivers}

We consider a \defn{bound quiver}~$\bar Q = (Q,I)$, formed by a finite quiver~$Q = (Q_0, Q_1, s, t)$ and an ideal~$I$ of the path algebra~$kQ$ (the~$k$-vector space generated by all paths in~$Q$, including vertices as paths of length zero, with multiplication induced by concatenation of paths) such that~$I$ is generated by linear combinations of paths of length at least two.
Note that we \textbf{do not require} that the quotient algebra~$kQ/I$ be finite dimensional.
The following definition is adapted from~\cite{ButlerRingel}. We note that it is customary to consider non-finite dimensional gentle algebras in the literature, see e.g.~\cite{Schroer}.

\begin{definition}
\label{def:gentleQuiver}
A \defn{locally gentle bound quiver}~$\bar Q \eqdef (Q,I)$ is a (finite) bound quiver~where
\begin{compactenum}[(i)]
\item each vertex~$a \in Q_0$ has at most two incoming and two outgoing arrows,
\item the ideal~$I$ is generated by paths of length exactly two,
\item for any arrow~$\beta \in Q_1$, there is at most one arrow~$\alpha \in Q_1$ with~$t(\alpha) = s(\beta)$ and~${\alpha\beta\notin I}$ (resp.~$\alpha\beta \in I$) and at most one arrow~$\gamma \in Q_1$ with~$t(\beta) = s(\gamma)$~and~${\beta\gamma\notin I}$~(resp.~${\beta\gamma \in I}$).
\end{compactenum}
The algebra~$kQ/I$ is called a \defn{locally gentle algebra}.
A \defn{gentle bound quiver} is a locally gentle bound quiver~$\bar Q$ such that the algebra $kQ/I$ is finite-dimensional; $kQ/I$ is then a \defn{gentle algebra}.
\end{definition}

\begin{definition}
\label{def:blossomingQuiver}
A locally gentle bound quiver~$\bar Q$ is \defn{complete} if any vertex~$a \in Q_0$ is incident to either one ($a$ is a leaf) or four arrows ($a$ is an internal vertex).
The \defn{pruned subquiver} of a quiver~$\bar Q$ is the locally gentle quiver obtained by deleting all leaves of~$\bar Q$ (degree one vertices) and their incident arrows.
The \defn{blossoming quiver} of a locally gentle bound quiver~$\bar Q$ is the complete locally gentle bound quiver~$\bar Q\blossom$ whose pruned subquiver is~$\bar Q$.
The vertices of~$Q\blossom_0 \ssm Q_0$ are called \defn{blossom vertices}, and the arrows in~$Q\blossom_1 \ssm Q_1$ are called \defn{blossom arrows}. See \fref{fig:quivers}.
%
\begin{figure}[b]
	\centerline{\includegraphics[scale=.6]{quivers}}
	\caption{Some locally gentle quivers (top) and their blossoming quivers (bottom).} %Initial vertices are solid and labeled while blossom vertices are hollow, and initial arrows are bold while blossom arrows are thin.}
	\label{fig:quivers}
\end{figure}
\end{definition}

%In other words, $\bar Q\blossom$ is obtained from~$\bar Q$ by adding blossom arrows and blossom vertices at each incomplete vertex of~$\bar Q$ and by completing~$I$ accordingly.
%Examples are represented on \fref{fig:quivers}.

\begin{remark}
\label{rem:sizeBlossomingQuiver}
Note that~$\bar Q\blossom$ has~$2|Q_0|-|Q_1|$ incoming blossom arrows and~$2|Q_0|-|Q_1|$ outgoing blossom arrows.
Therefore, it has $|Q_0\blossom| = |Q_0| + 2(2|Q_0|-|Q_1|) = 5|Q_0|-2|Q_1|$ vertices and~${|Q_1\blossom| = |Q_1| + 2(2|Q_0|-|Q_1|) = 4|Q_0|-|Q_1|}$ arrows.
\end{remark}

\subsection{Strings and walks}

The non-kissing complex is constructed using the combinatorics of strings and walks in the quiver~$\bar Q$, whose definitions are now briefly recalled.
The terminology and notations in the following definitions is borrowed from~\cite{ButlerRingel, Crawley-Boevey}.

For any arrow~$\alpha$ of~$Q$, define a formal inverse~$\alpha^{-1}$ with the properties that~${s(\alpha^{-1}) = t(\alpha)}$, $t(\alpha^{-1}) = s(\alpha)$, $\alpha^{-1}\alpha = \varepsilon_{t(\alpha)}$ and~$\alpha\alpha^{-1} = \varepsilon_{s(\alpha)}$, where~$\varepsilon_v$ is the path of length zero starting and ending at the vertex~$v \in Q_0$.

\begin{definition}
\label{def:string}
Let~$\bar Q = (Q,I)$ be a locally gentle bound quiver.
A \defn{finite string} in~$\bar Q$ is a word of the form
\(
\rho = \alpha_1^{\varepsilon_1}\alpha_2^{\varepsilon_2}\cdots \alpha_\ell^{\varepsilon_\ell},
\)
where
	\begin{compactenum}[(i)]
	\item $\alpha_i \in Q_1$ and~$\varepsilon_i \in \{-1,1\}$ for all~$i \in [\ell]$,
	\item $t(\alpha_i^{\varepsilon_i}) = s(\alpha_{i+1}^{\varepsilon_{i+1}})$ for all~$i \in [\ell-1]$,
	\item there is no path~$\pi \in I$ such that~$\pi$ or~$\pi^{-1}$ appears as a factor of~$\rho$, and
	\item $\rho$ is reduced, in the sense that no factor~$\alpha\alpha^{-1}$ or~$\alpha^{-1}\alpha$ appears in~$\rho$, for~$\alpha \in Q_1$.
	\end{compactenum}
The integer~$\ell$ is called the \defn{length} of the string~$\rho$.
We let~$s(\rho) \eqdef s(\alpha_1^{\varepsilon_1})$ and~$t(\rho) \eqdef t(\alpha_\ell^{\varepsilon_\ell})$ denote the source and target of~$\rho$.
For each vertex~$a \in Q_0$, there is also a \defn{string of length zero}, denoted by~$\varepsilon_a$, that starts and ends at~$a$.
\end{definition}

%\begin{example}
%With our choice of conventions, we represent the string ${\gamma\beta^{-1}\alpha^{-1}\gamma\beta^{-1}\alpha^{-1}\gamma\delta}$ by
%\[
%\;\vcenter{\hbox{\includegraphics[scale=0.3]{exmString1}}}
%\]
%\end{example}

%\begin{definition}
%An oriented cycle~$c$ in~$Q$ such that~$c, c^2 \notin I$ is called \defn{primitive} if it cannot be written as an $n$-th power ($n>1$) of a cycle.
%\end{definition}

If~$c$ is an oriented cycle in~$Q$ such that~$c, c^2 \notin I$, we write $c^\infty$ for the infinite word~$c c c\cdots$, ${}^\infty c$ for the infinite word~$\cdots c c c$, and $^\infty c^\infty$ for the bi-infinite word~$^\infty c c^\infty$.
We also define~${}^{-\infty}c \eqdef {}^{\infty}(c^{-1}) = (c^\infty)^{-1}$ and similarly~$c^{-\infty} \eqdef (c^{-1})^\infty = (^\infty c)^{-1}$.

\begin{definition}
An \defn{eventually cyclic string} for~$\bar Q$ is a word~$\rho$ of the form~${}^\infty(c_1^{\varepsilon_1})\sigma (c_2^{\varepsilon_2})^\infty$, where $c_1, c_2$ are oriented cycles in~$\bar Q$ (possibly of length zero) and $\varepsilon_1, \varepsilon_2$ are signs in~$\{\pm 1\}$ such that $c_1^{2\varepsilon_1} \sigma c_2^{2\varepsilon_2}$ is a finite string in~$\bar Q$.
\end{definition}

\begin{definition}
A \defn{string} for~$\bar Q$ is a word which is either a finite string or an eventually cyclic infinite string.
We often implicitly identify the strings~$\rho$ and~$\rho^{-1}$, and call it an \defn{undirected string}.
\end{definition}

To avoid distinguishing between finite and (bi-)infinite words, we denote strings as pro\-ducts~$\rho = \prod_{i < \ell < j} \alpha_\ell^{\varepsilon_\ell}$ where~$i < j \in \Z \cup \{\pm \infty\}$, $\varepsilon_\ell\in\{\pm 1\}$ and~$\alpha_\ell \in Q_1$~for~all~${i < \ell < j}$.

\begin{definition}
\label{def:walk}
A \defn{walk} of a locally gentle quiver~$\bar Q$ is a maximal string of its blossoming quiver~$\bar Q \blossom$ (meaning that at each end it either reaches a blossom vertex of~$\bar Q \blossom$ or enters an infinite oriented cycle).
We implicitly identify the walks~$\omega$ and~$\omega^{-1}$, and call it an \defn{undirected walk}.
\end{definition}

\begin{definition}
\label{def:substrings}
A \defn{substring} of a walk~$\omega = \prod_{i < \ell < j} \alpha_\ell^{\varepsilon_\ell}$ of~$\bar Q$ is a string~$\sigma = \prod_{i' < \ell < j'} \alpha_\ell^{\varepsilon_\ell}$ of~$\bar Q$ for some~$i \le i' < j' \le j$, where the inequality~$i \le i'$ (resp.~$j' \le j$) is strict when~$i \ne -\infty$ (resp.~$j \ne \infty$). In other words, $\sigma$ is a factor of~$\omega$ such that
\begin{compactitem}
\item the endpoints of~$\sigma$ are not allowed to be the possible blossom endpoints of~$\omega$,
\item the position of~$\sigma$ as a factor of~$\omega$ matters.
\end{compactitem}
Note that the string~$\varepsilon_a$ is a substring of~$\omega$ for each occurence of~$a$ as a vertex of~$\omega$.
We denote by~$\Sigma(\omega)$ the set of substrings of~$\omega$.
We use the same notation for undirected walks. % (of course, substrings of an undirected walk are undirected).
\end{definition}

\begin{definition}
\label{def:topBottom}
We say that the substring~$\sigma = \prod_{i' < \ell < j'} \alpha_\ell^{\varepsilon_\ell}$ is \defn{at the bottom} (resp.~\defn{on top}) of the walk~$\omega = \prod_{i < \ell < j} \alpha_\ell^{\varepsilon_\ell}$ if~$i'=-\infty$ or~$\varepsilon_{i'} = 1$ and~$j'=+\infty$ or~$\varepsilon_{j'} = -1$ (resp.~if~${i'=-\infty}$ or~${\varepsilon_{i'} = -1}$ and~$j'=\infty$ or~$\varepsilon_{j'} = 1$).
In other words the (at most) two arrows of~$\omega$ incident to the endpoints of~$\sigma$ point towards~$\sigma$ (resp.~outwards from~$\sigma$).
We denote by~$\Sigma_\bottom(\omega)$ and~$\Sigma_\top(\omega)$ the sets of bottom and top substrings of~$\omega$.
We use the same notations for undirected~walks.
\end{definition}

\begin{definition}
\label{def:straightBending}
%A \defn{peak} (resp.~\defn{deep}) of a walk~$\omega$ is a substring of~$\omega$ of length zero which is on top (resp.~at the bottom of~$\omega$).
%A \defn{corner} is either a peak or a deep (in other words, it is a vertex of~$\omega$ where the arrows change direction).
A walk~$\omega$ is \defn{straight} if~$\omega$ or~$\omega^{-1}$ is a path in~$\bar Q\blossom$, and \defn{bending} otherwise.
%A \defn{peak walk} (resp.~\defn{deep walk}) is a walk with a unique corner, which is a peak (resp.~deep). For~$a \in Q_0$, we denote by~$a_\peak$ the peak walk with peak at~$a$ and by~$a_\deep$ the deep walk with deep~at~$a$ (note that those are indeed unique by gentleness).
\end{definition}

\subsection{Non-kissing complex}

We can now define the non-kissing complex of a locally gentle bound quiver following~\cite{McConville, PaluPilaudPlamondon, BrustleDouvilleMousavandThomasYildirim}.
We start with the kissing relation for walks.

\parpic(5cm,2cm)(-2pt, 65pt)[r][b]{\includegraphics[scale=1.2]{kissing}}
\begin{definition}
\label{def:kiss}
Let~$\omega$ and~$\omega'$ be two undirected walks on~$\bar Q$.
We say that~$\omega$ \defn{kisses}~$\omega'$ if ${\Sigma_\top(\omega) \cap \Sigma_\bottom(\omega')}$ contains a \emph{finite} substring.
%See \fref{fig:kissing}.
We say that~$\omega$ and~$\omega'$ are \defn{kissing} if~$\omega$ kisses~$\omega'$ or~$\omega'$ kisses~$\omega$ (or both).
We authorize the situation where the common finite substring is reduced to a vertex~$a$, meaning that~$a$ is a peak of~$\omega$ and a deep of~$\omega'$.
Note also that~$\omega$ can kiss~$\omega'$ several times, that~$\omega$ and~$\omega'$ can mutually kiss, and that~$\omega$ can kiss itself.
%
%\begin{figure}[h]
%	\centerline{\includegraphics[scale=1]{kissing}}
%	\caption{A schematic representation of two kissing walks: $\omega$~kisses~$\omega'$.}
%	\label{fig:kissing}
%\end{figure}
%
\end{definition}

\begin{definition}
\label{def:nKc}
The \defn{non-kissing complex} of~$\bar Q$ is the simplicial complex~$\NKC$ whose faces are the sets of pairwise non-kissing walks of~$\bar Q$.
Note that self-kissing walks are forbidden.
%Note that self-kissing walks never appear in~$\NKC$ by definition.
%In contrast, no straight walk can kiss another walk by definition, so that they appear in all facets of~$\NKC$.
%The \defn{reduced non-kissing complex}~$\RNKC$ is the simplicial complex whose faces are the collections of pairwise non-kissing bending walks of~$\bar Q$.
\end{definition}

\section{Accordions, slaloms, and non-crossing complex}\label{sec:accordionSlalomNonCrossingComplexes}

%We now temporarily switch topic and present the accordion complex and the slalom complex of a pair of dual dissections of an orientable surface.
%The latter is directly inspired from the case of a disk treated in~\cite{GarverMcConville}, while the former is obtained by duality as was already observed in the case of a disk in~\cite{MannevillePilaud-accordion}.
%In the general case of arbitrary orientable surfaces, the correspondence between accordions and slaloms requires a little more attention and is treated in Sect.~\ref{subsec:accordionsVSSlaloms}.

\subsection{Dual dissections of a surface}

Before defining accordions and slaloms, we need a strong notion of pairs of dual dissections of an orientable surface.
We first review classical definitions of curves, arcs and dissections of a surface adapting it to our setting.

\begin{definition}
A \defn{marked surface}~$\bar\surface \eqdef (\surface, M)$ is an orientable surface~$\surface$ with boundaries, together with a set~$M$ of marked points which can be on the boundary of~$\surface$ or not.
For~$V \subset \surface$,
\begin{compactenum}[(i)]
\item a \defn{$V$-arc} on~$\bar\surface$ is a curve on~$\surface$ connecting two points of~$V$ and whose interior is disjoint from~$M$ and the boundary of~$\surface$.
\item a \defn{$V$-curve} on~$\bar\surface$ is a curve on~$\surface$ which at each end either reaches a point of~$V$ or infinitely circles around and finally reaches a puncture of~$M$, and whose interior is disjoint from~$M$ and the boundary of~$\surface$.
\end{compactenum}
As usual, curves and arcs are considered up to homotopy relative to their endpoints in~$\surface \ssm M$, and curves homotopic to a boundary are not allowed.
\end{definition}

\begin{definition}
\label{def:crossingCurves}
Two curves or arcs \defn{cross} when they intersect in~their~interior.
We will always assume that collections of arcs on a surface are in minimal position, in the sense that they cross each other transversaly, and the number of crossings is minimal.
%It is pointed out in \cite{Thurston} that this assumption can always be satisfied (up to homotopy).
\end{definition}

\begin{definition}
A \defn{dissection} of~$\bar\surface$ is a collection~$\dissection$ of pairwise non-crossing arcs on~$\bar\surface$.
The \defn{edges} of~$\dissection$ are its arcs together with the boundary arcs of~$\bar\surface$.
The \defn{faces} of~$\dissection$ are the connected components of the complement of the union of the edges of~$\dissection$ in the surface~$\surface$.
We denote by~$\vertices(\dissection)$, $\edges(\dissection)$ and~$\faces(\dissection)$ the sets of vertices, edges and faces of~$\dissection$ respectively.
The dissection~$\dissection$ is \defn{cellular} if all its faces are topological disks.
For~$V \subseteq M$, a \defn{$V$-dissection} is a dissection with only $V$-arcs.
\end{definition}

\begin{convention}
\textbf{All throughout the paper, all dissections are considered cellular.}
\end{convention}

\begin{definition}
Consider a marked surface~$\bar\surface = (\surface, V \sqcup V\dual)$, where~$V$ and~$V\dual$ are two disjoint sets of marked points so that the points of~$V$ and~$V\dual$ that are on the boundary of~$\surface$ alternate.
A cellular $V$-dissection~$\dissection$ of~$\bar\surface$ and a cellular $V\dual$-dissection~$\dissection\dual$ of~$\bar\surface$ are \defn{dual cellular dissections} if there are pairs of mutually inverse bijections~$V\dual \leftrightarrow \faces(\dissection)$ and~$V \leftrightarrow \faces(\dissection\dual)$, both denoted~$\dual$ in both directions, such that~$\dissection$ has an edge joining its vertices~$u,v \in V$ and separating its faces~$f,g \in  \faces(\dissection)$ if and only if~$\dissection\dual$ has an edge joining its vertices~$f\dual, g\dual \in V\dual$ and separating its faces~$u\dual, v\dual \in \faces(\dissection\dual)$.
\end{definition}

Some examples of dual cellular dissections on different surfaces are represented in \fref{fig:dissections}.
%
\begin{figure}[t]
	\centerline{\includegraphics[scale=.7]{dissections}}
	\caption{Some pairs~$(\dissection, \dissection\dual)$ of dual cellular dissections on different surfaces. The dissection~$\dissection$ is in green while its dual dissection~$\dissection\dual$ is~in~red. The boundaries of the surfaces are shaded, and the glue symbols indicate how to identify edges.}
	\label{fig:dissections}
\end{figure}
%
Note that contrarily to the usual conventions, the dual vertex~$f\dual$ of a face~$f$ of~$\dissection$ is not always in the interior of the face~$f$.
More precisely, each face~$f$ has either no or exactly one edge on the boundary of~$\surface$. Its dual vertex~$f\dual$ then lies in the interior~of~$f$ and is a puncture of~$\bar\surface$ in the former case, and on the boundary edge of~$f$ in the latter~case.

%More precisely, there are two situations:
%\begin{compactitem}
%\item if a face~$f$ has no edges on the boundary of~$\surface$, its dual vertex~$f\dual$ lies in the interior~of~$f$ and is a puncture of~$\bar\surface$,
%\item if a face~$f$ has an edge on the boundary of~$\surface$, then it has exactly one such edge and its dual vertex~$f\dual$ lies on this edge.
%\end{compactitem}
%In fact, the second point forces the following characterization of the cellular dissections that admit a dual cellular dissection.
%
%\begin{proposition}
%\label{prop:conditionsDualDissections}
%For a cellular $V$-dissection~$\dissection$ of a marked surface~$\bar\surface = (\surface, V \sqcup V\dual)$, the following assertions are equivalent:
%\begin{compactenum}[(i)]
%\item there exists a cellular $V\dual$-dissection~$\dissection\dual$ of~$\bar\surface$ such that~$\dissection$ and~$\dissection\dual$ are dual cellular dissections,
%\item each face of~$\dissection$ contains exactly one point of~$V\dual$ (in particular, at most one boundary edge).
%\end{compactenum}
%Moreover, the cellular dissection~$\dissection\dual$ is uniquely determined.
%\end{proposition}
%
%\begin{proof}
%We mimick the proof of~\cite[Prop.~1.12]{OpperPlamondonSchroll}.
%The direct implication is immediate by definition.
%Assume conversely that each face~$f$ of~$\dissection$ contains exactly one point~$f\dual$ of~$V\dual$.
%We construct half-edges of~$\dissection\dual$ in each face~$f$ of~$\dissection$ by joining the dual point~$f\dual$ to the middle of each boundary edge of~$f$ that is not a boundary edge of~$\surface$.
%For each edge~$a$ of~$\dissection$, the half-edges incident to the middle of~$a$ in the two faces of~$\dissection$ containing~$a$ form the dual edge~$a\dual$ of~$a$.
%All these dual edges do not cross (as the half-edges do not cross in each face of~$\dissection$) and form the dual cellular dissection~$\dissection\dual$~of~$\dissection$.
%\end{proof}

\begin{definition}
We consider a set~$B$ of points on the boundary of the surface~$\surface$ such that~$B$ and~$V \cup V\dual$ alternate along the boundary of~$\surface$.
The points of~$B$ are called the \defn{blossom points}.
See \eg Figs.\,\ref{fig:accordions} \&~\ref{fig:slaloms} where the blossom points appear as white hollow vertices.
\end{definition}

\subsection{Accordion complex and slalom complex}

Let~$\bar\surface = (\surface, V \sqcup V\dual)$ be a surface with two disjoint sets~$V$ and~$V\dual$ of marked points, and let~$B$ be the corresponding blossom points on the boundary of~$\surface$.
%We say that a $B$-curve is \defn{external} if it is homotopic to a boundary arc of~$\surface \ssm B$, and \defn{internal} otherwise.
%Note that no $B$-curve can cross an external $B$-curve.
Consider two dual cellular dissections~$\dissection$ and~$\dissection\dual$ of~$\bar\surface$.
%
The next definition generalises the one of \cite{MannevillePilaud-accordion} for the case where~$\bar \surface$ is a disk. % A~very similar definition appears in \cite{BaurCoelhoSimoes} in a slightly different context under the \mbox{name ``permissible~arc''}.

\begin{definition}
\label{def:accordion}
A \defn{$\dissection$-accordion} is a $B$-curve~$\alpha$ of~$\bar\surface$ such that whenever~$\alpha$ meets a face~$f$~of~$\dissection$,
\begin{compactenum}[(i)]
\item it enters crossing an edge~$a$ of~$f$ and leaves crossing an edge~$b$ of~$f$ (in other words, $\alpha$ is not allowed to circle around~$f\dual$ when~$f\dual$ is a puncture),
\item the two edges~$a$ and~$b$ of~$f$ crossed by~$\alpha$ are consecutive along the boundary of~$f$,
\item $\alpha$, $a$ and~$b$ bound a disk inside~$f$ that does not contain~$f\dual{}$.
\end{compactenum}
By convention, we also consider that the punctures of~$V$ are $\dissection$-accordions.
%By convention, we also consider that the punctures of~$V$ are external $\dissection$-accordions.
%If we were working on the universal cover of the surface, the~$\dissection$-accordion associated to a puncture would be the infinite line crossing all (infinitely many) arcs attached to the puncture.
\end{definition}

\fref{fig:accordions} illustrates some $\dissection$-accordions for the dissections~$\dissection$ of \fref{fig:dissections}.

\begin{figure}[h]
	\centerline{\includegraphics[scale=.7]{accordions}}
	\caption{Some $\dissection$-accordions (in blue) for the dissections~$\dissection$ of \fref{fig:dissections} (in green).}
	\label{fig:accordions}
\end{figure}

\begin{remark}
In Def.\,\ref{def:accordion}, observe that
\begin{compactitem}
\item the edges of~$a$ and~$b$ of~$f$ crossed by~$\alpha$ might coincide, see the second example in \fref{fig:accordions}.
\item the first condition is automatically satisfied if~$f\dual$ is not a puncture. %, \ie when it lies on the boundary of~$\surface$.
\end{compactitem}
\end{remark}

\begin{definition}
\label{def:accordionComplex}
The \defn{$\dissection$-accordion complex}~$\AC$ is the simplicial complex whose faces are the sets of pairwise non-crossing $\dissection$-accordions.
Note that self-crossing accordions are~forbidden.
%Note that self-crossing accordions never appear in~$\AC$ by definition.
%In contrast, no external accordion can cross another accordion, so that they appear in all facets of~$\AC$. 
%The \defn{reduced $\dissection$-accordion complex}~$\RAC$ is the simplicial complex whose faces are the collections of pairwise non-crossing internal $\dissection$-accordions.
\end{definition}

The following definition generalizes the one from~\cite{GarverMcConville} for the case where~$\bar\surface$ is a disk.

\begin{definition}
\label{def:slalom}
A \defn{$\dissection\dual$-slalom} is a $B$-curve~$\alpha$ of~$\bar\surface$ such that, whenever~$\alpha$ crosses an edge~$a\dual$ of~$\dissection\dual$ contained in two faces~$f\dual, g\dual$ of~$\dissection\dual$, the marked points~$f$ and~$g$ lie on opposite sides of~$\alpha$ in the union of~$f\dual$ and~$g\dual$ glued along~$a\dual$.
Here, we consider that~$f$ lies on the right (resp.~left) of~$\alpha$ when~$\alpha$ circles clockwise (resp.~counterclockwise) around~$f$.
By convention, we also consider that the punctures of~$V$ are $\dissection\dual$-slaloms.
%By convention, we also consider that the punctures of~$V$ are external $\dissection\dual$-slaloms.
%If we were working on the universal cover of the surface, the~$\dissection\dual$-slalom associated to a puncture would be an infinite line never crossing any arc of~$\dissection\dual$.
\end{definition}

\fref{fig:slaloms} illustrates some $\dissection\dual$-slaloms for the dual dissections~$\dissection\dual$ of \fref{fig:dissections}.

\begin{figure}[h]
	\centerline{\includegraphics[scale=.7]{slaloms}}
	\caption{Some $\dissection\dual$-slaloms (in blue) for the dual dissections~$\dissection\dual$ of \fref{fig:dissections} (in red).}
	\label{fig:slaloms}
\end{figure}

\begin{definition}
\label{def:slalomComplex}
The \defn{$\dissection\dual$-slalom complex}~$\SC$ is the simplicial complex whose faces are the sets of pairwise non-crossing $\dissection\dual$-slaloms.
Note that self-crossing slaloms are forbidden.
%Note that self-crossing slaloms never appear in~$\SC$ by definition.
%In contrast, no external slalom can cross another slalom, so that they appear in all facets of~$\SC$. 
%The \defn{reduced $\dissection\dual$-slalom complex}~$\RSC$ is the simplicial complex whose faces are the collections of pairwise non-crossing internal $\dissection\dual$-slaloms.
\end{definition}

\subsection{Accordions versus slaloms and the non-crossing complex}
\label{subsec:accordionsVSSlaloms}

%The following statement is illustrated by Figures~\ref{fig:accordions} and~\ref{fig:slaloms}.

\begin{proposition}
\label{prop:accordionsSlaloms}
For two dual cellular dissections~$\dissection$ and~$\dissection\dual$, the $\dissection$-accordions are precisely the $\dissection\dual$-slaloms and the $\dissection$-accordion complex coincides with the $\dissection\dual$-slalom complex.
See Figs.\,\ref{fig:accordions} \& \ref{fig:slaloms}.
\end{proposition}

%\begin{proof}
%Let~$\alpha$ be a~$\dissection$-accordion.
%Let~$a$,~$b$,~$c$ be three consecutive edges of~$\dissection$ crossed by~$\alpha$.
%Let~$u \in \dissection$ be the common endpoint of~$a$ and $b$ given by Definition~\ref{def:accordion} and let~$v \in \dissection$ be the common endpoint of~$b$ and~$c$.
%If $u = v$, then the segment of~$\alpha$ between~$a$ and~$c$ stays in the same face of~$\dissection\dual$.
%Otherwise, when crossing~$b$, the accordion~$\alpha$ leaves the face~$u\dual$ of $\dissection\dual$ and enters the face~$v\dual$.
%In the surface obtained by glueing the two cells~$u\dual$ and~$v\dual$ along~$b\dual$, the marked points~$u$ and~$v$ are separated by~$\alpha$.
%Conversely, assume that~$\alpha$ is an curve of~$(\surface, B)$ which is not a $\dissection$-accordion.
%We are in one of the following cases.
%
%Case 1: The curve~$\alpha$ consecutively crosses two edges~$a$ and~$b$ of~$\dissection$ that do not share a common endpoint.
%Let~$f$ be the face of~$\dissection$ that contains the segment of~$\alpha$ between~$a$ and~$b$.
%Consider the connected component of~$f\setminus\alpha$ that does not contain~$f\dual$.
%The boundary of this component contains an edge~$c \in \dissection \setminus \{a\}$ that shares a common endpoint with~$a$.
%Let~$u,v$ be the endpoints~of~$c$.
%Then~$\alpha$ cuts the cells $u\dual,v\dual$ glued along~$c\dual$ into two connected components, one containing both~endpoints~of~$c$.
%
%Case 2: The curve~$\alpha$ consecutively crosses two edges~$a$ and~$b$ of~$\dissection$ that share a unique common endpoint, but the region delimited by~$\alpha$,~$a$ and~$b$ is not a disk.
%Since the dissection~$\dissection$ is cellular, that region has to contain some marked point~$u \in \dissection\dual$.
%One conclude that~$\alpha$ is not a~$\dissection\dual$-slalom similarly as in the first case, by considering the component of~$u\dual \setminus \alpha$ that does not contain~$u$.
%
%Case 3: The curve~$\alpha$ consecutively crosses two edges~$a$ and~$b$ of~$\dissection$ that share two different endpoints, and none of the two regions delimited by~$\alpha$,~$a$ and~$b$ is a disk.
%Since the dissection~$\dissection$ is cellular, both regions have to contain a puncture.
%This contradicts the assumption that the dissections~$\dissection$ and~$\dissection\dual$ are dual to each other.
%
%Case 4: If~$\alpha$ stays inside a $\dissection$-cell, then it rolls around a~$\dissection\dual$ puncture.
%There is a~$\dissection\dual$-edge~$a$ ending in that puncture. When~$\alpha$ crosses~$a$, the puncture stays on the same side of~$\alpha$, hence~$\alpha$ is not a~$\dissection\dual$-slalom.
%\end{proof}

\begin{definition}
\label{def:noncrossingComplex}
The \defn{non-crossing complex} of the pair of dual cellular dissections~$(\dissection, \dissection\dual)$ is the simplicial complex~$\NCC \eqdef \AC = \SC$.
%The \defn{reduced non-crossing complex} of~$(\dissection, \dissection\dual)$ is~$\RNCC \eqdef \RAC = \RSC$.
\end{definition}

%\begin{remark}
%The $\dissection$-slaloms and the $\dissection\dual$-accordions are defined dually and also coincide.
%\end{remark}

%\begin{example}
%When the dissection~$\dissection$ is a classical dissection of a polygon (with no punctures) where each cell has at most one boundary edge, the dual dissection~$\dissection\dual$ is a tree.
%The non-crossing complex in this situation was treated in detail in~\cite{GarverMcConville, MannevillePilaud-accordion}.
%Note that even when the surface~$\surface$ is a disk, we authorize in the present paper both~$\dissection$ and~$\dissection\dual$ to have interior faces and punctures.
%\end{example}

%\begin{remark}
%A quick disclaimer about accordion complexes and slalom complexes of arbitrary cellular dissections.
%As stated in Proposition~\ref{prop:conditionsDualDissections}, a cellular dissection~$\dissection$ with a face containing more than one boundary edge does not admit a dual cellular dissection~$\dissection\dual$.
%This prevents the use of the definitions given in this section.
%Although the accordion complex (resp.~slalom complex) could still be defined as in~\cite{MannevillePilaud-accordion} (resp.~\cite{GarverMcConville}) for the disk, the resulting complexes would be joins of smaller accordion complexes (resp.~slalom complexes) defined in this paper.
%See \cite[Prop.~2.4]{MannevillePilaud-accordion} for a detailed statement in the case of the disk.
%\end{remark}

\section{Non-kissing versus non-crossing}

%In this section, we show that non-kissing and non-crossing complexes actually coincide.
%Namely, any pair of dual cellular dissections~$(\dissection, \dissection\dual)$ defines a locally gentle bound quiver~$\bar Q_{\dissection}$ (see Section~\ref{subsec:D2Q}) such that the non-crossing complex~$\NCC$ is isomorphic to the non-kissing complex~$\NKC[\bar Q_{\dissection}]$.
%Conversely, any locally gentle bound quiver~$\bar Q$ gives rise to a surface~$\surface_{\bar Q}$ equipped with a pair of dual cellular dissections~$\dissection_{\bar Q}$ and~${{\dissection\dual}\!\!_{\bar Q}}$ (see Section~\ref{subsec:Q2D}) such that the non-kissing complex~$\NKC$ is isomorphic to the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection\dual\!\!_{\bar Q}}]$.
%In fact, we show that the accordion, slalom, and non-kissing complexes can all be pictured in a unique way on the surface.
%Interestingly, via the correspondence between pairs of dual cellular dissections and locally gentle bound quivers, the duality between the dissections~$\dissection$ and~$\dissection\dual$ translates into the Koszul duality between the locally gentle algebras of~$\bar Q$ and~$\bar Q\koszul$.
%Many examples are treated in Section~\ref{subsec:Q2D}.

\subsection{The bound quiver of a dissection}
\label{subsec:D2Q}

We first associate a quiver to a pair of dual dissections~$(\dissection,\dissection\dual)$.% of a marked surface~$(\surface, V\sqcup V\dual)$.
%Let~$\dissection$ and~$\dissection\dual$ be two dual cellular dissections of a marked surface~$(\surface, V\sqcup V\dual)$.
%Let $B$ be the set of blossom points.

\begin{definition}
\label{def:quiverDualDissections}
The quiver of the dissection~$\dissection$ is the quiver $\bar Q_{\dissection} = (Q_{\dissection}, I_{\dissection})$ defined~by:
\begin{compactenum}[(i)]
\item the set of vertices of~$Q_{\dissection}$ is the set of edges of $\dissection$;
\item there is an arrow from~$a$ to~$b$ for each common endpoint~$v$ of~$a$ and~$b$ such that~$b$ comes immediately after~$a$ in the counterclockwise order around~$v$;
\item the ideal~$I_{\dissection}$ is generated by the paths of length two in~$Q_{\dissection}$ obtained by composing arrows which correspond to triples of consecutive edges in a face of~$\dissection$.
\end{compactenum}
The bound quiver of the dissection~$\dissection\dual$ is the bound quiver $\bar Q_{\dissection\dual} = (Q_{\dissection\dual}, I_{\dissection\dual})$ defined by replacing~$\dissection$ by~$\dissection\dual$ in the above.
See \fref{fig:quiversDissections}.
%
\begin{figure}[h]
	\centerline{\includegraphics[scale=.7]{quiversDissections1}}
	\medskip
	\centerline{\includegraphics[scale=.7]{quiversDissections2}}
	\caption{The quivers associated to the dissections of \fref{fig:dissections}.}% As stated in Proposition~\ref{prop:dualityKoszul1}, dual dissections give rise to Koszul dual bound quivers.}
	\label{fig:quiversDissections}
\end{figure}
\end{definition}

%\fref{fig:quiversDissections} illustrates this construction for the dissections of \fref{fig:dissections}.

\begin{remark}
The blossoming quiver~$\bar Q_\dissection\blossom$ of the quiver~$\bar Q_\dissection$ is obtained with the same procedure by considering additional blossom vertices along the boundary of the surface. See \fref{fig:quiversDissections}.
\end{remark}

\begin{lemma}
\label{lemm:quiverOfDissectionIsLocallyGentle}
The bound quiver~$\bar Q_{\dissection} = (Q_{\dissection}, I_{\dissection})$ is a locally gentle bound quiver.
\end{lemma}

%\begin{proof}
%Each edge~$a$ of~$\dissection$ has two endpoints, and at each endpoint there is at most one edge of~$\dissection$ coming immediately after~$a$ in the clockwise order, and at most one edge of~$\dissection$ coming immediately before~$a$.
%Thus, in~$Q_{\dissection}$, there are at most two arrows leaving~$a$ and at most two arriving in~$a$.
%Among these arrows, those arising from the same endpoint of~$a$ will be composable, and those arising from different endpoints will yield relations.
%Thus $\bar Q_{\dissection}$ is locally gentle.
%\end{proof}

\begin{definition}
\label{defi:koszulDual}
The \defn{Koszul dual} of a locally gentle bound quiver~$\bar Q = (Q,I)$~is the bound quiver~$\bar Q\koszul = (Q\koszul, I\koszul)$ defined as follows:
\begin{compactenum}[(i)]
\item the quiver~$Q\koszul$ is equal to the opposite quiver of~$Q$ (obtained from~$Q$ by reversing all arrows);
\item the ideal~$I\koszul$ is generated by the opposites of the paths of length two in~$Q$ that are not in~$I$.
\end{compactenum}
\end{definition}

%It is seen in \cite{BessenrodtHolm} that the (ungraded version of the) Koszul dual of a locally gentle algebra~$kQ/I$ is isomorphic to~$kQ\koszul/I\koszul$.
%Note that~$\bar Q\koszul$ is locally gentle, and that Koszul duality is an involution and commutes with blossoming:~$(\bar Q\koszul)\koszul = \bar Q$ and~$(\bar Q\koszul)\blossom = (\bar Q\blossom)\koszul$.
%%Examples are represented on \fref{fig:koszulQuivers}.
%%
%%\begin{figure}[t]
%%	\centerline{\includegraphics[scale=.6]{koszulQuivers}}
%%	\caption{The Koszul duals of the (blossoming) quivers of \fref{fig:quivers}.}
%%	\label{fig:koszulQuivers}
%%\end{figure}
%
%The following proposition appears in \cite[Proposition 1.25]{OpperPlamondonSchroll}.

\begin{proposition}[{\cite[Prop.\,1.25]{OpperPlamondonSchroll}}]
\label{prop:dualityKoszul1}
Let~$\dissection$ and~$\dissection\dual$ be two dual cellular dissections of a marked surface~$(\surface, V\sqcup V\dual)$.
The bound quivers~$\bar Q_{\dissection}$ and~$\bar Q_{\dissection\dual}$ are Koszul dual to each other.
See \fref{fig:quiversDissections}.
\end{proposition}

%\begin{proof}
%The duality provides a bijection~$a\in (Q_\dissection)_0\mapsto a\dual\in (Q_{\dissection\dual})_0$, and also induces a bijection~${\alpha \in (Q_\dissection)_1 \mapsto \alpha\dual \in (Q_{\dissection\dual})_1}$ with~$s(\alpha\dual) = t(\alpha)\dual$ and~$t(\alpha\dual) = s(\alpha)\dual$.
%Moreover, for any two composable arrows~$\alpha,\beta\in(Q_\dissection)_0$, we have~$\alpha\beta\in I_\dissection$ if and only if~$s(\alpha),t(\alpha),t(\beta)$ are three consecutive edges of a~$\dissection$-cell~$f$, if and only if~$s(\alpha)\dual,t(\alpha)\dual,t(\beta)\dual$ are three consecutive edges in~$\dissection\dual$ ending in~$f\dual$, if and only if~$\beta\dual\alpha\dual\notin I_{\dissection\dual}$.
%\end{proof}

\subsection{The surface of a locally gentle bound quiver}
\label{subsec:Q2D}

We now associate a surface to a locally gentle bound quiver.
This construction yields the same surface as the one constructed in \cite{OpperPlamondonSchroll}. % (see Rem.\,\ref{rem:comparisonWithOPS} for a comparison).

\begin{definition}
\label{def:surfaceQuiver}
The surface~$\surface_{\bar Q}$ of a locally gentle bound quiver~$\bar Q = (Q,I)$ is the surface obtained from the blossoming quiver~$\bar Q\blossom$ as follows:
\begin{enumerate}[(i)]
\parpic(5cm,2cm)(-2pt, 115pt)[r][b]{\input{figures/lozenge.tex}}
\item for each arrow~$\alpha \in Q_1\blossom$, consider a lozenge~$L(\alpha)$ with sides
%\begin{alignat*}{2}
\(
\begin{array}{llll}
\qquad & \Enrs{\alpha} = [v(\alpha), s(\alpha)] \quad & \Enrt{\alpha} = [v(\alpha), t(\alpha)] \quad & \text{(green)} \\
\qquad & \Ers{\alpha} = [f\dual(\alpha), s(\alpha)] \quad & \Ert{\alpha} = [f\dual(\alpha), t(\alpha)] \quad & \text{(red)}
\end{array}
\)
%\end{alignat*}

\item for any~$\alpha, \beta \in Q_1\blossom$ with~$t(\alpha) = s(\beta)$, identify:
    \begin{compactitem}
    \item $\Ert{\alpha}$ with~$\Ers{\beta}$ if~$\alpha\beta \in I$,
    \item $\Enrt{\alpha}$ with~$\Enrs{\beta}$ if~$\alpha\beta \notin I$.
    \end{compactitem}
\end{enumerate}
The orientations on the edges are only used for identifications and can be immediately forgotten.
\end{definition}

Def.\,\ref{def:surfaceQuiver} constructs an orientable surface~$\surface_{\bar Q}$ with boundaries.
\fref{fig:surfaces} illustrates this construction for the quivers of \fref{fig:quivers}.

\begin{figure}[h]
	\centerline{\includegraphics[scale=.7]{surfaces}}
	\caption{The surface~$\surface_{\bar Q}$ for the quivers~$\bar Q$ of \fref{fig:quivers}.}
	\label{fig:surfaces}
\end{figure}

%\begin{remark}
%We could equivalently construct the surface~$\surface_{\bar Q}$ as follows:
%\begin{itemize}
%\item consider one $(\ell+1)$-gon~$P_\omega$ for each straight walk~$\omega$ of length~$\ell$ in~$\bar Q$ or in~$\bar Q\koszul$ (just closing~$\omega$ with an additional edge connecting~$t(\omega)$ to~$s(\omega)$),
%\item for each arrow~$\alpha \in Q_1\blossom$, consider the only straight walks~$\omega$ of~$\bar Q$ and~$\omega\koszul$ of~$\bar Q\koszul$ containing~$\alpha$, and glue the polygons~$P_\omega$ and~$P_{\omega\koszul}$ along their edges corresponding to~$\alpha$.
%\end{itemize}
%\end{remark}
%
%The advantage of Definition~\ref{def:surfaceQuiver} is that it automatically endows~$\surface_{\bar Q}$ with two disjoint sets~$V_{\bar Q}$ and~${{V\dual}\!\!_{\bar Q}}$ of marked points and two dual cellular dissections~$\dissection_{\bar Q}$ and~${\dissection\dual\!\!_{\bar Q}}$ defined as follows.

\begin{definition}
\label{def:dissectionQuiver}
The surface~$\surface_{\bar Q}$ is endowed with
\begin{compactitem}
\item the set~$V_{\bar Q}$ of points~$v(\alpha)$ for~$\alpha \in Q_1\blossom$ after the identifications given by~(ii),
\item the $V_{\bar Q}$-dissection~$\dissection_{\bar Q}$ given by all sides~$\Enrs{\alpha}$ and~$\Enrt{\alpha}$ for~$\alpha \in Q_1\blossom$ after the identifications given by~(ii).
\end{compactitem}
The set~${{V\dual}\!\!_{\bar Q}}$ and the ${{V\dual}\!\!_{\bar Q}}$-dissection~${\dissection\dual\!\!_{\bar Q}}$ are defined similarly by using $f\dual(\alpha)$, $\Ers{\alpha}$ and $\Ert{\alpha}$.
\end{definition}

\begin{proposition}
\label{prop:dissectionsAreCellular}
Let~$\bar Q$ be a locally gentle bound quiver.
Then the dissections~$\dissection_{\bar Q}$ and~$\dissection\dual\!\!_{\bar Q}$ are cellular and dual to each other.
\end{proposition}

%\begin{proof}
%In the construction of~$\surface_{\bar Q}$, if two arrows~$\alpha$ and~$\beta$ of~$\bar Q \blossom$ are such that~${t(\alpha) = s(\beta)}$ and~${\alpha\beta \in I\blossom}$, then the vertices~$v(\alpha)$ and~$v(\beta)$ are identified on the surface.
%Thus, any two arrows of a given path contribute to the same vertex of~$V_{\bar Q}$, so~$V_{\bar Q}$ is in bijection with the set of maximal paths in~$\bar Q\blossom$.
%
%Let~$v\in V_{\bar Q}$. The situation around~$v$ is as follows, depending on whether~$v$ corresponds to a finite or infinite maximal path of~$\bar Q\blossom$:
%
%\begin{figure}[h]
%	\centerline{\includegraphics[scale=.7]{halfStar} \qquad \includegraphics[scale=.7]{star}}
%	\caption{Two possible situations around~$v$: on the left,~$v$ corresponds to a finite maximal path of~$\bar Q$, while on the right,~$v$ corresponds to an infinite one.}
%	\label{fig:stars}
%\end{figure}
%
%In both cases, we see that~$v$ is enclosed in a polygon of~$\dissection_{\bar Q}\dual$.  This shows that~$\dissection_{\bar Q}\dual$ is a cellular dissection of~$\surface_{\bar Q}$.
%Dually, one shows that~$\dissection_{\bar Q}$ is also a cellular dissection.
%
%Moreover, by construction, each edge of~$\dissection_{\bar Q}$ which is not on the boundary of~$\surface_{\bar Q}$ crosses exactly one edge of~$\dissection_{\bar Q}\dual$, and vice versa.
%This shows that~$\dissection_{\bar Q}$ and~$\dissection_{\bar Q}\dual$ are dual to each other.
%\end{proof}

%The following statement immediately follows from the definitions and was probably already observed by the reader on \fref{fig:surfaces}.

\begin{theorem}
\label{thm:bijectionLocallyGentleAndSurfaces}
Up to isomorphism, the constructions of Defs.\,\ref{def:quiverDualDissections} \& \ref{def:surfaceQuiver} are inverse~to~each other.
They induce a bijection between the set of isomorphism classes of locally gentle bound quivers and the set of homeomorphism classes of marked surfaces with a pair of dual cellular dissections.
\end{theorem}

\begin{remark}
\label{rem:propertiesSurface}
The following observations are useful for the computation of examples.
\begin{compactenum}[(i)]
\item The set~$V_{\bar Q}$ has one vertex for each straight walk in~$\bar Q$ (equivalently, for each maximal path in~$\bar Q$).
      Finite straight walks yield vertices on the boundary of~$\surface_{\bar Q}$, while infinite cyclic straight walks in~$\bar Q$ yield punctures of~$\surface_{\bar Q}$ in~$V_{\bar Q}$.
      We denote by~$p$ the number of infinite cyclic straight walks in~$\bar Q$.
\item \label{item:edges}
      The dissection~$\dissection_{\bar Q}$ has one edge for each vertex~$a \in \bar Q_0$, obtained by concatenation of the sides~$\Enrt{\alpha} = \Enrs{\beta}$ and~$\Enrt{\alpha'} = \Enrs{\beta'}$ where~$a = t(\alpha) = s(\beta) = t(\alpha') = s(\beta')$, $\alpha\beta \notin I$ and~$\alpha'\beta' \notin I$. We denote by~$\edgeof(a)$ the edge of~$\dissection_{\bar Q}$ corresponding to~$a$.
\item The dissection~$\dissection_{\bar Q}$ has one $\ell$-cell for each straight walk of length~$\ell$ in~$\bar Q\koszul$.
\item Similar statements hold dually for~${{V\dual}\!\!_{\bar Q}}$ and~${\dissection\dual\!\!_{\bar Q}}$, and we define~$p\dual$ and~$\dualedgeof(a)$ similarly.
\item The number of punctures of~$\surface_{\bar Q}$ is the number~$p + p\dual$ of infinite straight walks in~$\bar Q$ and~$\bar Q\koszul$.
\item \label{item:boundary}
      The number~$b$ of boundary components of~$\surface_{\bar Q}$ can be computed as follows.
      There are two natural perfect matchings whose vertices are the blossom vertices of~$\bar Q$: one is obtained by joining the endpoints of each finite straight walk of~$\bar Q$, and the other is obtained similarly from~$\bar Q \koszul$.
      Let~$G$ be the superposition of these two perfect matchings.
      Then the number~$b$ of boundary components of~$\surface_{\bar Q}$ is the number of connected components of~$G$.
\item The genus of the surface~$\surface_{\bar Q}$ is
      \(
       g = (|Q_1| - |Q_0| - b - p - p\dual + 2)/2,
      \)
      where~$b$ is the number of boundary components (see above for a way to compute~$b$) and~$p + p\dual$ the number of punctures (\ie infinite straight walks in~$\bar Q$ and in~$\bar Q\koszul$).
%      Indeed, ${2g = 2-\chi(\surface_{\bar Q})}$, where~$\chi(\surface_{\bar Q})$ is the Euler characteristic of~$\surface_{\bar Q}$.
%      The dissection~$\dissection$ provides a cellular decomposition of~$\surface_{\bar Q}$ on which we fill the boundary components with disks.  
%      The number of faces of this cellular decomposition is~$b + p\dual$, its number of edges is~$|Q_0|$ and its number of vertices is the number of straight walks in~$\bar Q$, which is equal to~$2|Q_0| - |Q_1| + p$.
%      The above formula for~$g$ follows.
\end{compactenum}
\end{remark}

\begin{proposition}
\label{prop:dualityKoszul2}
For any gentle bound quiver~$\bar Q$ with Koszul dual~$\bar Q\koszul$, the surfaces~$\surface_{\bar Q}$ and~$\surface_{\bar Q\koszul}$ coincide, but~$\dissection_{\bar Q\koszul} = {\dissection\dual\!\!_{\bar Q}}$ and~${\dissection\dual\!\!_{\bar Q\koszul}} = \dissection_{\bar Q}$.
\end{proposition}

\begin{example}
\label{exm:cycle}
Consider the family of \defn{cycle quivers} indicated in \fref{fig:cyclesSurfaces}.
%Consider the family of \defn{cycle quivers} indicated in \fref{fig:cyclesQuivers}.
%%
%\begin{figure}[h]
%	\centerline{\includegraphics[scale=.45]{cyclesQuivers}}
%	\caption{The cycle quivers with~$1, 2, 3, 4, 5$ vertices.}
%	\label{fig:cyclesQuivers}
%\end{figure}
%%
We apply Rem.\,\ref{rem:propertiesSurface} to understand the corresponding surfaces.
The corresponding perfect matchings (see Rem.\,\ref{rem:propertiesSurface}\,\eqref{item:boundary}) form a cycle with green and red arrows alternating.
Moreover, $\bar Q$ has~$1$ infinite straight walk, while~$\bar Q\koszul$ has none.
Since~$|Q_1| = |Q_0|$, the corresponding surfaces are punctured disks ($1$ boundary component, $1$ puncture and genus~$0$).
See \fref{fig:cyclesSurfaces}.
%The first few corresponding surfaces are represented in \fref{fig:cyclesSurfaces} (see Figures~\ref{fig:surfaces} and~\ref{fig:reversedPathsSurfaces} for the cycles with $1$ or~$2$ vertices, recalling that~$\bar Q$ and~$\bar Q\koszul$ yield the same surface).

\begin{figure}[t]
	\centerline{\includegraphics[scale=.7]{cyclesSurfacesBis}}
	\caption{The surface~$\surface_{\bar Q}$ for the cycle quivers with~$3, 4, 5$ vertices.}
	\label{fig:cyclesSurfaces}
\end{figure}
\end{example}

%\begin{remark}
%\label{rem:comparisonWithOPS}
%The construction of the surface given in Definition \ref{def:surfaceQuiver} yields the same surface as the one constructed in \cite{OpperPlamondonSchroll}.
%A notable difference is that in \cite{OpperPlamondonSchroll}, only~$\dissection_{\bar Q}$ is given, and~$\dissection\dual\!\!_{\bar Q}$ is deduced (it is called the dual lamination).
%Another minor difference is that the construction in \cite{OpperPlamondonSchroll} is written only for gentle algebras, while here it is generalized to locally gentle algebras.
%
%The major difference with \cite{OpperPlamondonSchroll} is the application of the surface of a (locally) gentle algebra: there, it is used as a model for the derived category of the gentle algebra (graded arcs correspond to indecomposable objects in that category), while here, it will be used as a model for walks in~$\bar Q$. % ($\dissection_{\bar Q}$-accordions will correspond to walks in~$\bar{Q}$, see Prop.\,\ref{prop:walks=arcs}).
%\end{remark}

\subsection{Non-crossing and non-kissing complexes coincide}

Let~$\bar Q$ be a locally gentle bound quiver.
For each edge of the dissection~$\dissection_{\bar Q}$ on~$\surface_{\bar Q}$, we fix a point on the interior of this edge, which we call its ``middle point'' (this is the black vertex on the pictures).
To each walk on~$\bar Q$, we will now associate a~$\dissection_{\bar Q}$-accordion.

\begin{definition}
\label{def:curveOfAnArrow}
For any arrow~$\alpha$ on $\bar Q\blossom$, let~$\curveof(\alpha)$ be the curve on~$\surface_{\bar Q}$ which goes from the middle point of the edge of~$\dissection$ corresponding to $s(\alpha)$ to the middle point of the edge of~$\dissection$ corresponding to $t(\alpha)$ by following the angle corresponding to~$\alpha$.
Define~$\curveof(\alpha^{-1})$ to be~$\curveof(\alpha)^{-1}$.
\end{definition}

\begin{definition}
\label{def:curveOfAWalk}
Let~$\omega = \prod_{i < \ell < j} \alpha_\ell^{\varepsilon_\ell}$ be a (possibly infinite) walk on~$\bar Q$. 
Define the curve~$\curveof(\omega)$ to be the concatenation of the curves~$\curveof(\alpha_\ell^{\varepsilon_\ell})$ of Def.\,\ref{def:curveOfAnArrow}.
\end{definition}

In practice, we will represent~$\curveof(\omega)$ by a curve which intersects itself only transversaly, and such that if it circles infinitely around a puncture, then it spirals towards it.

\begin{lemma}
\label{lemm:curveOfAWalkIsAccordion}
Let~$\omega$ be a walk on~$\bar Q$.  Then~$\curveof(\omega)$ is a~$\dissection_{\bar Q}$-accordion.
\end{lemma}

%\begin{proof}
%This is because~$\curveof(\omega)$ follows angles in~$\dissection_{\bar Q}$ by definition.
%\end{proof}

\begin{lemma}
\label{lemm:accordionsAreCurvesOfWalks}
Let~$\gamma$ be a~$\dissection_{\bar Q}$-accordion.  There exists a unique undirected walk~$\walk(\gamma)$ such that we have~$\curveof(\walk(\gamma)) = \gamma$.
\end{lemma}

%\begin{proof}
%We can assume that~$\gamma$ intersects itself and the edges of~$\dissection_{\bar Q}$ transversaly and minimally, in the sense that~$\gamma$ does not cross an edge twice in succession in opposite directions (see Definition~\ref{def:crossingCurves}).
%Then~$\gamma$ is completely determined by its sequence of intersection points with the edges of~$\dissection_{\bar Q}$, since the dissection is cellular.
%Two successive intersection points in this sequence define an angle between two edges of~$\dissection_{\bar Q}$, which corresponds to an arrow in~$\bar Q$.
%Thus the sequence of intersection points defines a walk~$\walk(\gamma)$ on~$\bar Q$.
%By construction, we have that~$\curveof(\walk(\gamma)) = \gamma$.
%Is also follows from the construction above and from Definition~\ref{def:curveOfAWalk} that~$\walk(\curveof(\omega)) = \omega$ for any walk~$\omega$.
%This finishes the proof.
%\end{proof}
%
%The above implies the following.

\begin{proposition}
\label{prop:walks=arcs}
The maps~$\curveof(-)$ and~$\walk(-)$ induce mutually inverse bijections between the set of undirected walks on~$\bar Q$ and the set of~$\dissection_{\bar Q}$-accordions on~$\surface_{\bar Q}$.
\end{proposition}

\begin{lemma}
\label{lem:nonKissing=nonCrossing}
Two undirected walks~$\omega_1$ and~$\omega_2$ on~$\bar Q$ are non-kissing if and only if the corresponding $\dissection_{\bar Q}$-accordions~$\curveof(\omega_1)$ and~$\curveof(\omega_2)$ are non-crossing on~$\surface_{\bar Q}$.
\end{lemma}

%\begin{proof}
%A kiss between two walks~$\omega$ and~$\omega'$ is depicted on \fref{fig:kissings}.
%
%\begin{figure}[h]
%	\capstart
%	\centerline{\includegraphics[scale=1]{kissings}}
%	\caption{Two representations of a pair of kissing walks.}
%	\label{fig:kissings}
%\end{figure}
%The left hand side of the picture is as in \fref{fig:kissing}, and the right hand side is simply a different representation of it.
%On the surface~$\surface_{\bar Q}$, the dual dissections~$\dissection$ and~$\dissection\dual$ are as on \fref{fig:kissingVSCrossing} (right).
%
%\begin{figure}[h]
%	\capstart
%	\centerline{\includegraphics[scale=1]{kissingVSCrossing}}
%	\caption{Kissing walks on the quiver~$\bar Q$ correspond to crossing curves on the surface~$\surface_{\bar Q}$.}
%	\label{fig:kissingVSCrossing}
%\end{figure}
%
%The curves~$\curveof(\omega)$ and~$\curveof(\omega')$ on the surface follow~$\omega$ and~$\omega'$ on the picture.
%It is then clear that~$\omega$ and~$\omega'$ kiss if and only if~$\curveof(\omega)$ and~$\curveof(\omega')$ cross. 
%\end{proof}

\begin{theorem}
\label{thm:complexesCoincide}
The non-kissing complex and the non-crossing complex are isomorphic.
%The non-kissing complex~$\NKC$ and the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection\dual\!\!_{\bar Q}}]$ are isomorphic.
%\begin{compactitem}
%\item for any locally gentle bound quiver~$\bar Q$, the non-kissing complex~$\NKC$ is isomorphic to the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection\dual\!\!_{\bar Q}}]$,
%\item for any pair of dual cellular dissections~$\dissection, \dissection\dual$ of an oriented surface, the non-crossing complex~$\NCC$ is isomorphic to the non-kissing complex~$\NKC[\bar Q_{\dissection, \dissection\dual}]$.
%\end{compactitem}
\end{theorem}

%\begin{proof}
%The first point is a consequence of Proposition \ref{prop:walks=arcs}, Lemma \ref{lem:nonKissing=nonCrossing} and Proposition \ref{prop:accordionsSlaloms}.
%The second point is a consequence of Theorem \ref{thm:bijectionLocallyGentleAndSurfaces} and of the first point.
%\end{proof}

%\begin{remark}
%Note that our construction of the surface~$\surface_{\bar Q}$ implies that the quiver~$\bar Q$ is naturally embedded on~$\surface_{\bar Q}$.
%If we force all $\dissection$-accordions (or $\dissection\dual$-slaloms) to follow the arrows of~$\bar Q$, then a $\dissection$-accordion (or $\dissection\dual$-slalom) is really seen as a walk on~$\bar Q$.
%\end{remark}

%\newpage
%% if you use biblatex then this generates the bibliography
%% if you use some other method then remove this and do it your own way
\printbibliography

\end{document}

### 2018-11-05 secondPaper/draft/accordionComplexSurfaces.tex
FPSAC

--- 2018-10-08 secondPaper/accordionComplexSurfaces.tex
@@
 We say that~$\omega$ and~$\omega'$ are \defn{kissing} if~$\omega$ kisses~$\omega'$ or~$\omega'$ kisses~$\omega$ (or both).
-Note that we authorize the situation where the commmon finite substring is reduced to a vertex~$a$, meaning that~$a$ is a peak of~$\omega$ and a deep of~$\omega'$.
+Note that we authorize the situation where the common finite substring is reduced to a vertex~$a$, meaning that~$a$ is a peak of~$\omega$ and a deep of~$\omega'$.
 Observe also that~$\omega$ can kiss~$\omega'$ several times, that~$\omega$ and~$\omega'$ can mutually kiss, and that~$\omega$ can kiss itself.

### 2018-11-05 secondPaper/draft/accordionComplexSurfaces.tex
typo

@@
 \usepackage[T1]{fontenc}
-\usepackage{enumerate, amsmath, amsfonts, amssymb, amsthm, mathrsfs, wasysym, graphics, graphicx, xcolor, url, hyperref, hypcap, xargs, multicol, pdflscape, multirow, hvfloat, array, ae, aecompl, pifont, mathtools, a4wide, float, blkarray}
+\usepackage{enumerate, amsmath, amsfonts, amssymb, amsthm, mathrsfs, graphics, graphicx, xcolor, url, hyperref, hypcap, xargs, multicol, pdflscape, multirow, hvfloat, array, ae, aecompl, pifont, mathtools, a4wide, float, blkarray}
 \usepackage{marginnote}
@@
 \newcommand{\faces}{\mathcal{F}} % faces of a dissection
-\renewcommandx{\AC}[1][1=\dissection]{\mathcal{K}_{\mathrm{acc}}(#1)} % accordion complex
+\newcommandx{\AC}[1][1=\dissection]{\mathcal{K}_{\mathrm{acc}}(#1)} % accordion complex
 \newcommandx{\RAC}[1][1=\dissection]{\mathcal{C}_{\mathrm{acc}}(#1)} % reduced accordion complex
@@
 On the other hand, we construct a punctured, marked, oriented surface with boundary, endowed with a pair of dual dissections.
-From those geometric data, we define two simplicial complexes: the accordion complex, and the slalom complex, generalizing work of A. Garver and T. McConville in the case of a disk.
+From those geometric data, we define two simplicial complexes: the accordion complex, and the slalom complex, generalizing work of A.~Garver and T.~McConville in the case of a disk.
 We show that all three simplicial complexes are isomorphic, and that they are pure and thin.
@@
 
-In order to unify these two objects, we are lead to introduce two generalizations.
+In order to unify these two objects, we are led to introduce two generalizations.
 On the algebraic side, the non-kissing complex is extended from the class of gentle algebras to that of locally gentle algebras (which are an infinite-dimensional version of gentle algebras).
@@
 Conversely, the construction of a surface associated to a gentle algebra has appeared in \cite{OpperPlamondonSchroll}.
-We give a different construction of the same surface in this paper, which is obtained by ``glueing'' quadrilaterals to the arrows of the blossoming quiver (as defined in \cite{PaluPilaudPlamondon}, and called ``framed quiver'' in \cite{BrustleDouvilleMousavandThomasYildirim}).
+We give a different construction of the same surface in this paper, which is obtained by ``glueing'' quadrilaterals to the arrows of the blossoming quiver (as defined in \cite{PaluPilaudPlamondon}, and called ``fringed quiver'' in \cite{BrustleDouvilleMousavandThomasYildirim}).
 Our construction has the advantage that it easily yields the two dual dissections of the surface at the same time (the dissection and dual lamination of \cite{OpperPlamondonSchroll}).

### 2018-11-05 secondPaper/FPSAC/nonkissing-noncrossing-FPSAC.tex
delete ref 12

@@
 The idea of associating a finite-dimensional algebra to a dissection (or a triangulation) of a surface seems to take its roots in the theory of cluster algebras and cluster categories.
-This was first done for triangulations of polygons in \cite{CalderoChapotonSchiffler}, and then for any orientable surface with boundary in \cite{ABCP, Labardini}.  
+This was first done for triangulations of polygons in \cite{CalderoChapotonSchiffler}, and then for any orientable surface with boundary in \cite{ABCP}.  
 The algebra of a dissection as we shall use it in this paper has appeared in \cite{DavidRoeslerSchiffler}.
@@
 
-\newpage
 \section{Non-kissing complex}

### 2018-11-08 secondPaper/FPSAC/nonkissing-noncrossing-FPSAC.tex
PEPS Pierre-Guy
corrections mineures

@@
 	\and
-	Pierre-Guy Plamondon\thanks{\href{mailto:pierre-guy.plamondon@math.u-psud.fr}{pierre-guy.plamondon@math.u-psud.fr}. Supp. by ANR SC3A~15\,CE40\,0004\,01.}\addressmark{3}
+	Pierre-Guy Plamondon\thanks{\href{mailto:pierre-guy.plamondon@math.u-psud.fr}{pierre-guy.plamondon@math.u-psud.fr}. Supp. by ANR SC3A~15\,CE40\,0004\,01 and a PEPS JCJC.}\addressmark{3}
 }
@@
 
-This extended abstract reports on~\cite{PaluPilaudPlamondon-surfaces}, where more details and proofs are available.~It aims to show that two combinatorial objects, called the \emph{non-kissing complex} and the \emph{non-crossing complex}, are isomorphic.
+This extended abstract reports on~\cite{PaluPilaudPlamondon-surfaces}, where more details and proofs are available.~It shows that two combinatorial objects, the \emph{non-kissing complex} and the \mbox{\emph{non-crossing complex}}, are isomorphic.
 Both complexes appeared in different works in specific cases: the non-kissing complex of a grid appeared in \cite{McConville}, while the non-crossing complex of a disk appeared in \cite{GarverMcConville, MannevillePilaud-accordion}.

### 2019-02-01 thirdPaper/draft/typeConeAssociahedra.tex
Created section 3

@@
 \newcommand{\vincent}[1]{\todo[color=blue!30]{#1 \\ \hfill --- V.}}
-\newcommand{\pierreguy}[1]{\todo[color=green!30]{#1 \\ \hfill --- PG.}}
+\newcommand{\pg}[1]{\todo[color=green!30]{#1 \\ \hfill --- PG.}}
 
@@
 \newcommand{\neighbors}{\mathrm{ne}} % neighbors
+
+% PG et Yann
+\newcommand{\field}{\mathbb{K}}
+\newcommand{\cat}{\mathcal{C}}
+\newcommand{\Hom}[1]{\operatorname{Hom}_{#1}}
+\newcommand{\susp}{\Sigma}
+\newcommand{\add}{\operatorname{add}}
+\newcommand{\MOD}{\operatorname{mod}}
+\newcommand{\End}[1]{\operatorname{End}_{#1}}
+\newcommand{\spl}{\operatorname{sp}}
+\newcommand{\Ksp}{K_0^{\spl}}
+\newcommand{\Kg}{K_0^{\b{g}}}
+\newcommand{\ind}{\operatorname{ind}}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Relations for~$\b{g}$-vectors in~$2$-Calabi--Yau triangulated categories}
+Let~$\field$ be a field.
+Let~$\cat$ be a~$\field$-linear triangulated category with suspension functor~$\susp$.
+We fix a collection~$\ind(\cat)$ of representatives of isomorphism classes of indecomposable objects of~$\cat$.
+We will assume the following:
+\begin{itemize}
+ \item $\cat$ is essentially small (in particular,~$\ind(\cat)$ is a set);
+ \item $\cat$ is~$\Hom{}$-finite: for each pair of objects~$X$ and~$Y$, the~$\field$-vector space~$\cat(X,Y)$ is finite-dimensional;
+ \item $\cat$ is Krull--Schmidt: the endomorphism algebra of any indecomposable object is local;
+ \item $\cat$ is~$2$-Calabi--Yau: for each pair of objects~$X$ and~$Y$, there is an isomorphism of bifunctors
+ \[
+  \cat(X,\susp Y) \to D\cat(Y,\susp X)
+ \]
+ where~$D=\Hom{\field}(-,\field)$ is the usual duality of vector spaces;
+ \item $\cat$ contains a basic cluster-tilting object~$T=\bigoplus_{i=1}^n T_i$:
+ \[
+  \textrm{for any object~$X$,} \quad \cat(T, \susp X) = 0 \quad \textrm{if and only if} \quad X\in \add(T),
+ \]
+ where~$\add(T)$ is the smallest additive full subcategory of~$\cat$ containing the~$T_i$'s and closed under isomorphisms.
+\end{itemize}
+
+We need to introduce some notations before stating the main result of this section.  Let~$\Lambda:= \End{\cat}(T)$, and let~$F$ be the functor
+\[
+ F=\cat(T,-):\cat \xrightarrow{} \MOD \Lambda.
+\]
+\begin{proposition}[]\pg{Add references to BMR and KR}
+ The functor~$F$ induces an equivalence of~$\field$-linear categories
+ \[
+  F:\cat/(\susp T) \xrightarrow{} \MOD \Lambda,
+ \]
+ where~$(\susp T)$ is the ideal of morphisms factoring through an object of~$\add(\susp T)$ and~$\MOD \Lambda$ is the category of finite-dimensional right~$\Lambda$-modules.
+This equivalence induces further equivalences between~$\add(T)$ and the category of projective modules, and between~$\add(\susp^2 T)$ and that of injective modules.
+\end{proposition}
+
+For categories with a cluster-tilting objects, the~$2$-Calabi--Yau condition implies other duality results which we shall need.
+
+\begin{proposition}[]\pg{Cite Palu}
+ For any pair of objects~$X$ and~$Y$ in~$\cat$, there is an isomorphism of bifunctors
+ \[
+  (\susp T)\cat(X, \susp Y) \xrightarrow{\cong} \cat(Y, \susp X)/(\susp T),
+ \]
+ where~$(\susp T)\cat(X, \susp Y)$ is the space of morphisms from~$X$ to~$Y$ factoring through~$(\susp T)$.
+\end{proposition}
+
+\begin{remark}
+ Although the field~$\field$ is assumed to be algebraically closed in~\cite{} \pg{Cite Palu}, this assumption is not needed in the proof, and the result is valid over any field.
+\end{remark}
+
+Finally, we need the existence of almost-split triangles in~$\cat$.  Recall that a triangle
+\[
+ X\xrightarrow{f} Y \xrightarrow{g} Z \xrightarrow{h} \susp X
+\]
+in~$\cat$ is \defn{almost-split} if~$X$ and~$Z$ are indecomposable,~$h$ is non-zero, and any non-section~$X\to X'$ factors through~$f$  (or equivalently, any non-retraction~$Z'\to Z$ factors through~$g$).
+We say that a triangulated category \defn{has almost-split triangles} if there is an almost-split triangle as above for any indecomposable object~$X$.
+
+\begin{proposition}[]\pg{Cite Happel}
+ Any triangulated category admitting a Serre functor has almost-split triangles.  In particular, any~$2$-Calabi--Yau triangulated category has almost-split triangles.
+\end{proposition}
+
+\begin{definition}
+ \begin{enumerate}
+  \item Let~$\Ksp(\cat)$ be the \defn{split Grothendieck group} of~$\cat$, that is, the free abelian group generated by symbols~$[X]$, where~$[X]$ denotes the isomorphism class of~$X$ in~$\cat$, modulo the following relations: for any objects~$Y$ and~$Z$, we let~$[Y\oplus Z] = [Y] + [Z]$.
+
+  \item Let~$\Kg(\cat)$ be the quotient of~$\Ksp(\cat)$ by the relations~$[X]+[Z]-[Y]$ for all triangles
+  \[
+   X\xrightarrow{} Y \xrightarrow{} Z \xrightarrow{h} \susp X
+  \]
+  with~$h\in (\susp T)$.  Denote by~$\b g:\Ksp(\cat) \to \Kg(\cat)$ the canonical projection.
+
+ \end{enumerate}
+
+\end{definition}
+In particular,~$\Ksp(\cat)$ is isomorphic to a free abelian group over the set~$\ind(\cat)$.
+The choice of the notation for~$\Kg(\cat)$ is motivated by the next section \pg{Add ref}, where we study relations between~$\b g$-vectors.
+
+\begin{definition}
+ For any two objects~$X$ and~$Y$ of~$\cat$, define
+ \[
+  \langle X, Y \rangle := \dim_{\field} \Hom{\Lambda}(FX,FY).
+ \]
+ This defines a bilinear form
+ \[
+  \langle -,-\rangle : \Ksp(\cat) \times \Ksp(\cat) \xrightarrow{} \Z.
+ \]
+\end{definition}
+
+\begin{notation}
+\begin{enumerate}
+ \item For any indecomposable object~$X$ of~$\cat$, let
+ \[
+  X \to E \to \susp^{-1} X \to \susp X
+ \]
+ be an almost split triangle (unique up to isomorphism).  We let
+ \[
+  \ell_X := [X] + [\susp^{-1} X]  - [E] \in \Ksp(\cat).
+ \]
+
+ \item For any indecomposable object~$Y$ of~$\cat$, let
+ \[
+  \susp Y \to E' \to  Y \to \susp^2 Y
+ \]
+ be an almost split triangle (unique up to isomorphism).  We let
+ \[
+  r_Y := [Y] + [\susp Y]  - [E'] \in \Ksp(\cat).
+ \]
+\end{enumerate}
+
+We can finally state the main theorem of this section. \pg{recall Auslander}
+
+\begin{theorem}
+ Let~$\cat$ be a category satisying the hypotheses of \ref{} \pg{add ref}.
+Then~$\cat$ has only finitely many isomorphism classes of indecomposable objects if and only if the set~\[L:=\big\{\ell_X \ | \ X\in \ind(\cat)\setminus \add(\susp T) \big\}\] generates the kernel of~$\b g:\Ksp(\cat) \to \Kg(\cat)$.
+ In this case, the set~$L$ is a basis of the kernel of~$\b g$, and \pg{add formula}.
+\end{theorem}
+
+\end{notation}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2019-02-01 thirdPaper/draft/typeConeAssociahedra.tex
More on Section 3

@@
 \newcommand{\ind}{\operatorname{ind}}
+\newcommand{\coker}{\operatorname{coker}}
+\newcommand{\CC}{\phi}
 
@@
 \section{Relations for~$\b{g}$-vectors in~$2$-Calabi--Yau triangulated categories}
+%%%%%
+\subsection{Setting}
 Let~$\field$ be a field.
@@
 
+%%%%
+\subsection{Statement of the theorem}
 We need to introduce some notations before stating the main result of this section.  Let~$\Lambda:= \End{\cat}(T)$, and let~$F$ be the functor
@@
 \end{enumerate}
+\end{notation}
 
@@
 
-\begin{theorem}
+\begin{theorem}\label{theo::relations-g-vecteurs}
  Let~$\cat$ be a category satisying the hypotheses of \ref{} \pg{add ref}.
 Then~$\cat$ has only finitely many isomorphism classes of indecomposable objects if and only if the set~\[L:=\big\{\ell_X \ | \ X\in \ind(\cat)\setminus \add(\susp T) \big\}\] generates the kernel of~$\b g:\Ksp(\cat) \to \Kg(\cat)$.
- In this case, the set~$L$ is a basis of the kernel of~$\b g$, and \pg{add formula}.
+ In this case, the set~$L$ is a basis of the kernel of~$\b g$, and \pg{add formula}, for any $x\in \ker(\b g)$, we have that
+ \[
+  x= \sum_{A\in \ind(\cat) \setminus \add(\susp T)} \frac{\langle x, A \rangle}{\langle \ell_A, A \rangle} \ell_A.
+ \]
 \end{theorem}
 
-\end{notation}
+\begin{corollary}
+ Assume that~$\ind(\cat)$ is finite.
+Let~$X\xrightarrow{} E \xrightarrow{} Y \xrightarrow{h} \susp X$ be a triangle with~$h\in (\susp T)$.
+Then the element~$x=[X]+[Y]-[E]$ of the kernel of~$\b g$ is a non-negative linear combination of the~$\ell_A$, with~$A\in \ind(\cat)\setminus \add(\susp T)$.
+\end{corollary}
+\begin{proof}
+ We know that~$x=\sum_{A\in \ind(\cat)\setminus \add(\susp T)} \frac{\langle x, [A] \rangle}{\langle \ell_A, [A] \rangle} \ell_A$; since~$\langle \ell_A, [A] \rangle$ is positive by Lemma~\ref{lemm::bilinear-form}, we only need to show that each~$\langle x, [A] \rangle$ is non-negative.
+ The functor~$F=\cat(T,-)$ induces an exact sequence
+ \[
+  FX \to FE \to FY \to 0,
+ \]
+ which in turn induces an exact sequence
+ \[
+  0\to \Hom{\Lambda}(FY, FA) \to \Hom{\Lambda}(FE, FA) \xrightarrow{f} \Hom{\Lambda}(FX, FA) \to \coker(f) \to 0.
+ \]
+ Therefore~$\langle x, [A] \rangle = \dim_{\field} \coker(f) \geq 0$.
+\end{proof}
+
+%%%%
+\subsection{Proof of Theorem \ref{theo::relations-g-vecteurs}}
+
+\begin{lemma}
+ If~$X$ or~$Y$ lie in~$\add(\susp T)$, then~$\langle X, Y \rangle = 0$.
+\end{lemma}
+\begin{proof}
+ This is because~$F\susp T = 0$.
+\end{proof}
+
+\begin{lemma}\label{lemm::almost-split}
+ Let~$X\xrightarrow{} Y \xrightarrow{} \susp^{-1} X \xrightarrow{h} \susp X$ be an almost-split triangle.  Then~$X\notin \add(\susp T)$ if and only if~$h\in (\susp T)$.
+\end{lemma}
+\begin{proof}
+ If~$X\in \add(\susp T)$, then~$h$ cannot be in~$(\susp T)$, otherwise it would be zero since~$\cat(T, \susp T) =0$.
+
+ Assume now that~$X\notin \add(\susp T)$.  Let~$\field_X$ be the residue field of the algebra~$\End{\cat}(X)$. 
+ By definition of an almost-split triangle,~$h$ is in the socle of the right~$\End{\cat}(X)$-module~$\cat(\susp^{-1} X, \susp X)$.
+Moreover, this socle is a one-dimensional~$\field_X$-vector space; indeed, the~$2$-Calabi--Yau condition gives an isomorphism
+ \[
+  \cat(\susp^{-1} X, \susp X) \cong D\cat(X, X).
+ \]
+ Thus the socle of the right module~$\cat(\susp^{-1} X, \susp X)$ has the same~$\field_X$ dimension as the top of the left module~$\cat(X,X)$.
+Since~$X$ is indecomposable,~$\cat(X,X)$ is local, and its top is one-dimensional over~$\field_X$.
+
+ Now,~$(\susp T)\cat(\susp^{-1} X, \susp X)$ is a sub-module of~$\cat(\susp^{-1} X, \susp X)$.
+Therefore, if~$(\susp T)\cat(\susp^{-1} X, \susp X)$ is non-zero, then it contains the one-dimensional socle of~$\cat(\susp^{-1} X, \susp X)$, and thus contains~$h$.
+ By \cite{} \pg{cite Palu},
+ \[
+  (\susp T)\cat(\susp^{-1} X, \susp X) \cong D\cat(X, X)/(\susp T). 
+ \]
+The identity morphism of~$X$ is not in~$(\susp T)$, since~$X$ is not in~$\add(\susp T)$.
+Thus the right-hand side is non-zero, and so neither is the left-hand side.
+By the above, this implies that~$h\in (\susp T)\cat(\susp^{-1} X, \susp X)$, which finishes the proof.
+\end{proof}
+
+\begin{lemma}\label{lemm::bilinear-form}
+Let~$A$ and~$B$ be two indecomposable objects of~$\cat$. \pg{introduce general notation for redisue field}
+\begin{enumerate}
+ \item If~$A \notin \add(\susp T)$, then
+ \[
+  \langle \ell_A, B \rangle = \begin{cases}
+                               0 & \textrm{if~$A\ncong B$;} \\
+                               \dim_{\field}\field_A & \textrm{if~$A\cong B$.}
+                              \end{cases}
+ \]
+
+ \item If~$B \notin \add(\susp T)$, then
+ \[
+  \langle A, r_B \rangle = \begin{cases}
+                               0 & \textrm{if~$A\ncong B$;} \\
+                               \dim_{\field}\field_B & \textrm{if~$A\cong B$.}
+                              \end{cases}
+ \]
+\end{enumerate} 
+\end{lemma}
+\begin{proof}
+ We only prove the first assertion; the second one is proved dually.  Assume that~$A\notin\add(\susp T)$.  Let
+ \[
+  A \xrightarrow{f} E \xrightarrow{} \susp^{-1} A \xrightarrow{h} \susp A
+ \]
+ be an almost-split triangle.  By Lemma~\ref{lemm::almost-split}, the morphism~$h$ is in~$(\susp T)$.  Applying the functor~$F=\cat(T,-)$, we get an exact sequence
+ \[
+  FA\xrightarrow{Ff} FE \xrightarrow{} F\susp^{-1} A \xrightarrow{} 0.
+ \]
+ Applying now the functor~$\Hom{\Lambda}(-, FB)$, we get an exact sequence
+ \[
+  0 \xrightarrow{} \Hom{\Lambda}(F\susp^{-1} A, FB) \xrightarrow{} \Hom{\Lambda}(FE, FB) \xrightarrow{Ff^*} \Hom{\Lambda}(FA, FB) \xrightarrow{} \coker(Ff^*) \xrightarrow{} 0
+ \]
+ If~$B\ncong A$, then the definition of an almost-split triangle implies that~$Ff^*$ is surjective.
+\pg{add an exact sequence here; image of Ffstar is non-invertible elements} Thus~$\coker(Ff^*) = 0$, and by additivity of the dimension in exact sequences, we get that~$\langle \ell_A, B \rangle =0$.
+
+ If~$B\cong A$, then~$\coker(Ff^*)$ is isomorphic to the residue field of~$\End{\Lambda}(FA)$, which is isomorphic to the residue field~$\field_A$ of~$A$.
+\end{proof}
+
+\pg{TO DO}
+
+%%%%
+\subsection{Application to~$\b g$-vectors}
+
+We recall the following results and definition from \cite{} \pg{cite DK and Palu}.
+
+\begin{proposition}
+ Let~$X$ be an object of~$\cat$. Then there exists a triangle
+ \[
+  T_1^X \to T^0_X \to X \to \susp T_1^X
+ \]
+ with~$T_1^X$ and~$T_0^X$ in~$\add(T)$.
+
+\end{proposition}
+
+\begin{definition}
+ The \defn{index} of an object~$X$ is the element
+ \[
+  \ind_T(X) := [T_0^X] - [T_1^X] \in \Ksp(\add(T)).
+ \]
+\end{definition}
+
+The notion of index is very close to the definition of the map~$\b g:\Ksp(\cat)\to \Kg(\cat)$ of Definition~\ref{} \pg{ref}.  The link is given by the following result.
+
+\begin{proposition}[]\pg{cite Palu}
+ Let~$X\xrightarrow{} Y \xrightarrow{} Z \xrightarrow{h} \susp X$ be a triangle.
+ Then
+ \[
+  \ind_T(X) + \ind_T(Z) - \ind_T(Y) = 0
+ \]
+ if and only if~$h\in (\susp T)$.
+\end{proposition}
+
+\begin{corollary}
+ There is an isomorphism~$\phi:\Kg(\cat) \to \Ksp(\add(T))$ such that~$\ind_T = \phi\circ \b g$.  In particular,~$\Kg(\cat)$ is a free abelian group generated by the~$[T_i]$.
+\end{corollary}
+
+\begin{theorem}[]\pg{cite???}
+ Let~$\cat$ be the cluster category of a valued quiver of Dynkin type~$A,B,C,D,E,F$ or~$G$.
+Let~$T$ be a basic cluster-tilting object in~$\cat$, and let~$Q$ be the valued Gabriel quiver of~$\End{\cat}(T)$.
+Then there is a bijection
+ \[
+  \CC: \ind(\cat) \xrightarrow{} \{\textrm{cluster variables in the cluster algebra of~$Q$}\},
+ \]
+ which has the follwing properties.
+ \begin{itemize}
+  \item For any~$X,Y\in \ind(\cat)$, $\CC(X)$ and~$\CC(Y)$ are compatible if and only if~$\cat(X, \susp Y) = 0$.
+  \item For any~$X\in \ind(\cat)$, the~$\b g$-vector of~$\CC(X)$ is~$\b g([X])$, where we identify~$\Z^n$ and~$\Kg(\cat)$ via the isomorphism sending~$(a_1, \ldots, a_n)$ to~$\sum_{i=1}^n a_i [T_i]$.
+  \item For any~$X,Y\in \ind(\cat)$, $\CC(X)$ and~$\CC(Y)$ are exchangeable if and only if~$\dim_{\field_X}\cat(X, \susp Y) = \dim_{\field_Y}\cat(X, \susp Y) = 1$.
+ \end{itemize}
+\end{theorem}
+
+The cluster category also contains enough information to detect positive mutations.
+
+\begin{proposition}
+ Let~$X,Y\in \ind(\cat)$ be such that~$\dim_{\field_X}\cat(X, \susp Y) = \dim_{\field_Y}\cat(X, \susp Y) = 1$.  Let 
+ \[
+  X\xrightarrow{} E \xrightarrow{} Y \xrightarrow{h} \susp X \quad \textrm{and} \quad Y\xrightarrow{} E' \xrightarrow{} X \xrightarrow{h'} \susp Y
+ \]
+ be triangles with~$h$ and~$h'$ non-zero (these triangles are unique up to isomorphism).
+Then~$\CC(Y)$ is obtained by performing a positive mutation on~$\CC(X)$ in some seed if and only if~$h\in (\susp T)$.
+ \begin{proof}
+  \pg{TO DO, Vincent: definition of positive mutation?}
+ \end{proof}
+\end{proposition}
 

### 2019-02-04 thirdPaper/draft/typeConeAssociahedra.tex
More changes to section 3

@@
 %%%%%
-\subsection{Setting}
+\subsection{Setting}\label{sect::setting}
 Let~$\field$ be a field.
@@
 \begin{theorem}\label{theo::relations-g-vecteurs}
- Let~$\cat$ be a category satisying the hypotheses of \ref{} \pg{add ref}.
+ Let~$\cat$ be a category satisying the hypotheses of Section \ref{sect::setting}.
 Then~$\cat$ has only finitely many isomorphism classes of indecomposable objects if and only if the set~\[L:=\big\{\ell_X \ | \ X\in \ind(\cat)\setminus \add(\susp T) \big\}\] generates the kernel of~$\b g:\Ksp(\cat) \to \Kg(\cat)$.
- In this case, the set~$L$ is a basis of the kernel of~$\b g$, and \pg{add formula}, for any $x\in \ker(\b g)$, we have that
+ In this case, the set~$L$ is a basis of the kernel of~$\b g$, and for any $x\in \ker(\b g)$, we have that
  \[
@@
 
-\begin{lemma}
+\begin{lemma}\label{lemm::bilinear-form-suspention-T}
  If~$X$ or~$Y$ lie in~$\add(\susp T)$, then~$\langle X, Y \rangle = 0$.
@@
  If~$B\cong A$, then~$\coker(Ff^*)$ is isomorphic to the residue field of~$\End{\Lambda}(FA)$, which is isomorphic to the residue field~$\field_A$ of~$A$.
+\end{proof}
+
+\begin{lemma}\label{lemm::coefficients}
+ Let~$x\in \Ksp(\cat)$, and write~\[x=\sum_{A\in \ind(\cat)} \lambda_A [A].\]  Then for any~$A\in\ind(\cat)\setminus \add(\susp T)$, we have that
+ \[
+  \lambda_A = \langle \ell_A, x \rangle = \langle x, r_A \rangle.
+ \]
+\end{lemma}
+\begin{proof}
+ Let~$B\in \ind(\cat) \setminus \add(\susp T)$.  Applying Lemma~\ref{lemm::bilinear-form}, we get that
+ \[
+  \langle \ell_B, x \rangle = \langle \ell_B, \sum_{A\in \ind(\cat)} \lambda_A [A] \rangle = \sum_{A\in \ind{\cat}} \lambda_A \langle \ell_B, [A] \rangle = \lambda_A.
+ \]
+ The equality~$\lambda_A = \langle x, r_A\rangle$ is proved in a similar way.
+\end{proof}
+
+\begin{corollary}\label{lemm::test-susp-T}
+ Let~$x\in \Ksp(\cat)$.  Then the following are equivalent.
+ \begin{enumerate}
+  \item $x\in \Ksp(\add(\susp T))$;
+  \item $\langle x, [A]\rangle = 0$ for all~$A\in \ind(\cat)$;
+  \item $\langle [A], x \rangle = 0$ for all~$A\in \ind(\cat)$.
+ \end{enumerate}
+\end{corollary}
+\begin{proof}
+ We will only proof that (1) is equivalent to (2); the proof that (1) is equivalent to (3) is similar.
+
+ Assume that (2) holds.  Then, by Lemma~\ref{lemm::coefficients}, we have that
+ \[
+  x = \sum_{A\in \ind(\cat)\setminus \add(\susp T)} \langle \ell_A, x \rangle + \sum_{i=1}^n \lambda_{\susp T_i} [\susp T_i] = \sum_{i=1}^n \lambda_{\susp T_i} [\susp T_i].
+ \]
+ Thus~$x\in \Ksp(\add(\susp T))$, and (1) holds.
+
+ Assume now that (1) holds.  Then~$\langle x, [A]\rangle = 0$ for any~$A$ by Lemma~\ref{lemm::bilinear-form-suspention-T}.  Thus (2) holds.
+\end{proof}
+
+\begin{proposition}\label{prop::free-set}
+ \begin{enumerate}
+  \item The set~$\{[\ell_A] \ | \ A\in \ind(\cat) \setminus \add(\susp T) \} \cup \{[\susp T_i] \ | \ i=1, \ldots, n\}$ is free in~$\Ksp(\cat)$.
+  \item The set~$\{[r_A] \ | \ A\in \ind(\cat) \setminus \add(\susp T) \} \cup \{[\susp T_i] \ | \ i=1, \ldots, n\}$ is free in~$\Ksp(\cat)$.
+ \end{enumerate}
+\end{proposition}
+\begin{proof}
+ We only prove (1); the proof of (2) is similar.  Assume that~
+ \[
+  x= \sum_{A\in \ind(\cat) \setminus \add(\susp T)} \lambda_A \ell_A + \sum_{i=1}^n \lambda_i [\susp T_i] = 0.
+ \]
+ Then~$\langle x, [A] \rangle = 0$ for all~$A\in\ind(\cat) \setminus \add(\susp T)$.  But~$\langle x, [A] \rangle = \lambda_A$ by Lemma~\ref{lemm::bilinear-form}.  Thus~
+ \[
+  x = \sum_{i=1}^n \lambda_i [\susp T_i] = 0.
+ \]
+ But the~$[\susp T_i]$ are linearly independent in~$\Ksp(\cat)$.  Thus~$\lambda_i = 0$ for all~$i\in \{1, \ldots, n\}$.  This finishes the proof.
+\end{proof}
+
+\begin{proposition}
+ Assume that~$\ind(\cat)$ is finite.  Then the set~$\{[\ell_A] \ | \ A\in \ind(\cat) \setminus \add(\susp T) \}$ is a basis of the kernel of~$\b g$.  Moreover, for any~$x\in \ker \b g$, we have that
+ \[
+  x= \sum_{A\in \ind(\cat) \setminus \add(\susp T)} \frac{\langle x, A \rangle}{\langle \ell_A, A \rangle} \ell_A.
+ \]
+\end{proposition}
+\begin{proof}
+By Proposition~\ref{prop::free-set}, the set is free.  Let~$x\in \ker \b g$.  Consider the element
+\[
+ z = x- \sum_{A\in \ind(\cat) \setminus \add(\susp T)} \frac{\langle x, A \rangle}{\langle \ell_A, A \rangle} \ell_A.
+\]
+Then for any~$B\in \ind{\cat}$, we have that
+\[
+ \langle  z, [B] \rangle = \Big\langle x- \sum_{A\in \ind(\cat) \setminus \add(\susp T)} \frac{\langle x, A \rangle}{\langle \ell_A, A \rangle} \ell_A, [B] \Big\rangle = \langle x, [B] \rangle - \langle x, [B] \rangle = 0,
+\]
+where the second equality is obtained by using Lemma~\ref{lemm::bilinear-form}.
+By Lemma~\ref{lemm::test-susp-T}, this implies that~$z\in \Ksp(\add(\susp T))$.
+Since~$z\in \ker(\b g)$ and since~$\b g$ is injective on~$\Ksp(\add (\susp T))$, we get that~$z=0$.
+This finishes the proof.
+\pg{We need a lemma saying that g is injective on K(add(susp T))}
+\end{proof}
+
+All that remains is to prove the converse in the statement of Theorem~\ref{theo::relations-g-vecteurs}.
+
+\begin{proposition}
+ Assume that the set~$\{[\ell_A] \ | \ A\in \ind(\cat) \setminus \add(\susp T) \}$ is a basis of the kernel of~$\b g$. Then~$\ind(\cat)$ is finite.
+\end{proposition}
+\begin{proof}
+
 \end{proof}

### 2019-02-04 thirdPaper/draft/typeConeAssociahedra.tex
Completed first draft of Section 3 and added references.

@@
 \]
-\begin{proposition}[]\pg{Add references to BMR and KR}
+\begin{proposition}[\cite{BuanMarshReiten, KellerReiten}]
  The functor~$F$ induces an equivalence of~$\field$-linear categories
@@
 
-\begin{proposition}[]\pg{Cite Palu}
+\begin{proposition}[\cite{Palu}]
  For any pair of objects~$X$ and~$Y$ in~$\cat$, there is an isomorphism of bifunctors
@@
 \begin{remark}
- Although the field~$\field$ is assumed to be algebraically closed in~\cite{} \pg{Cite Palu}, this assumption is not needed in the proof, and the result is valid over any field.
+ Although the field~$\field$ is assumed to be algebraically closed in~\cite{Palu}, this assumption is not needed in the proof, and the result is valid over any field.
 \end{remark}
@@
 
-\begin{definition}
+\begin{definition}\label{defi::grothendieck-group}
  \begin{enumerate}
@@
 In particular,~$\Ksp(\cat)$ is isomorphic to a free abelian group over the set~$\ind(\cat)$.
-The choice of the notation for~$\Kg(\cat)$ is motivated by the next section \pg{Add ref}, where we study relations between~$\b g$-vectors.
+The choice of the notation for~$\Kg(\cat)$ is motivated by Section~\ref{sect::applications-g-vectors}, where we study relations between~$\b g$-vectors.
 
@@
 Therefore, if~$(\susp T)\cat(\susp^{-1} X, \susp X)$ is non-zero, then it contains the one-dimensional socle of~$\cat(\susp^{-1} X, \susp X)$, and thus contains~$h$.
- By \cite{} \pg{cite Palu},
+ By \cite{Palu},
  \[
@@
 
+\begin{corollary}
+ If~$\ind(\cat)$ is finite, then the set~\[\{[\ell_A] \ | \ A\in \ind(\cat) \setminus \add(\susp T) \} \cup \{[\susp T_i] \ | \ i=1, \ldots, n\}\] is a basis of~$\Ksp(\cat)$.
+\end{corollary}
+\begin{proof}
+ By Proposition~\ref{prop::free-set}, the set is free.  It suffices to prove that it generates~$\Ksp(\cat)$.  Let~$x\in \Ksp(\cat)$.  Consider
+ \[
+  z = x - \sum_{A\in \ind{\cat}} \frac{\langle x, A \rangle}{\langle \ell_A, A\rangle} \ell_A.
+ \]
+ Then for any~$B\in \ind(\cat)$, we have that~$\langle z, [B] \rangle = 0$.  By Lemma~\ref{lemm::test-susp-T}, this implies that~$z\in \Ksp(\add(\susp T))$, and finishes the proof.
+\end{proof}
+
 All that remains is to prove the converse in the statement of Theorem~\ref{theo::relations-g-vecteurs}.
@@
 \begin{proof}
-
-\end{proof}
-
-\pg{TO DO}
+ Let~$x\in \ker \b g$, and write~$x = \sum_{[A]\in \ind(\cat)} \lambda_A[A]$, where the sum has finite support.  For any~$B$ not in the support of the sum, we have that~$\langle x, [B] \rangle = 0$.
+
+ Now,~$[T]+[\susp T]$ is in the kernel of~$\b g$, but~$\langle [T] + [\susp T], [B] \rangle = \langle [T], [B] \rangle = 0$ if and only if~$B\in \add(\susp T)$.  Thus~$\ind(\cat)$ has to be finite.
+\end{proof}
 
 %%%%
-\subsection{Application to~$\b g$-vectors}
-
-We recall the following results and definition from \cite{} \pg{cite DK and Palu}.
+\subsection{Application to~$\b g$-vectors}\label{sect::applications-g-vectors}
+
+We recall the following results and definition from \cite{DehyKeller,Palu}.
 
@@
 
-The notion of index is very close to the definition of the map~$\b g:\Ksp(\cat)\to \Kg(\cat)$ of Definition~\ref{} \pg{ref}.  The link is given by the following result.
-
-\begin{proposition}[]\pg{cite Palu}
+The notion of index is very close to the definition of the map~$\b g:\Ksp(\cat)\to \Kg(\cat)$ of Definition~\ref{defi::grothendieck-group}.  The link is given by the following result.
+
+\begin{proposition}[\cite{Palu}]
  Let~$X\xrightarrow{} Y \xrightarrow{} Z \xrightarrow{h} \susp X$ be a triangle.

### 2019-02-04 thirdPaper/draft/typeConeAssociahedra.tex
associahedron

--- 2019-02-01 thirdPaper/draft/typeConeAssociahedra.tex
@@
 \newcommand{\vincent}[1]{\todo[color=blue!30]{#1 \\ \hfill --- V.}}
-\newcommand{\pg}[1]{\todo[color=green!30]{#1 \\ \hfill --- PG.}}
+\newcommand{\pierreguy}[1]{\todo[color=green!30]{#1 \\ \hfill --- PG.}}
 
@@
 \newcommand{\neighbors}{\mathrm{ne}} % neighbors
-
-% PG et Yann
-\newcommand{\field}{\mathbb{K}}
-\newcommand{\cat}{\mathcal{C}}
-\newcommand{\Hom}[1]{\operatorname{Hom}_{#1}}
-\newcommand{\susp}{\Sigma}
-\newcommand{\add}{\operatorname{add}}
-\newcommand{\MOD}{\operatorname{mod}}
-\newcommand{\End}[1]{\operatorname{End}_{#1}}
-\newcommand{\spl}{\operatorname{sp}}
-\newcommand{\Ksp}{K_0^{\spl}}
-\newcommand{\Kg}{K_0^{\b{g}}}
-\newcommand{\ind}{\operatorname{ind}}
-\newcommand{\coker}{\operatorname{coker}}
-\newcommand{\CC}{\phi}
 
@@
 \label{prop:alternativePolytopalRealization}
+\vincent{See \cite[Coro.~9.5.7]{DeLoeraRambauSantos}}
 The affine map~$\Psi: \R^n \to \R^N$ defined by~$\Psi(\b{x}) = \b{h} - G\b{x}$ sends the polytope
@@
 
+\subsection{Faces of the type cone and Minkowski sums}
+
+\begin{lemma}
+\label{lem:MinkowskiSum}
+For~$\b{h}, \b{h}' \! \in \R^N$, the polytope~$P_{\b{h} + \b{h'}}$ is the Minkowski sum of the polytopes~$P_\b{h}$~and~$P_{\b{h}'}$.
+\end{lemma}
+
+\begin{proof}
+This follows from the definition of~$P_\b{h}$ and of Minkowski sums:
+\begin{align*}
+P_\b{h} + P_{\b{h}'} & = \set{\b{x} + \b{x}'}{\b{x} \in P_\b{h} \text{ and } \b{x}' \in P_{\b{h}'}} = \set{\b{x} + \b{x}'}{\b{G}\b{x} \le \b{h} \text{ and } \b{G}\b{x}' \le \b{h}'} \\
+& = \set{\b{y} \in \R^n}{\b{G}\b{y} \le \b{h} + \b{h}'} = P_{\b{h} + \b{h}'}.
+\qedhere
+\end{align*}
+\end{proof}
+
+\cref{lem:MinkowskiSum} ensures that convex combinations in the type cone correspond to Minkowski combinations of polytopes.
+This provides natural Minkowski summands for all polytopal realizations of~$\Fan$.
+
+\begin{corollary}
+Any polytope in~$\typeCone(\Fan)$ is the Minkowski sum of at most~$N-n$ polytopes corresponding to the rays of~$\b{K}\typeCone(\Fan)$.
+\end{corollary}
+
 \section{Applications to different generalizations of the associahedron}
@@
 
-Introduction on the associahedron. Loday's associahedron. \\
-Three proofs that the type cone of Loday's associahedron~\cite{Loday} is simplicial and therefore explicit description of all realizations as follows:...\\
-Explain the parallel with $\b{g}$-vectors, $\b{c}$-vectors, etc.
-\vincent{TODO}
+In this section, we study the type cones of complete simplicial fans arising as normal fans of three families of generalizations of the associahedron: the generalized associahedra of finite type cluster algebras~\cite{FominZelevinsky-ClusterAlgebrasI, FominZelevinsky-ClusterAlgebrasII, FominZelevinsky-ClusterAlgebrasIV, HohlwegLangeThomas}, the gentle associahedra~\cite{PaluPilaudPlamondon-nonkissing}, and the graph associahedra~\cite{CarrDevadoss, Postnikov, FeichtnerSturmfels, Zelevinsky}.
+All these families contain the classical associahedra~$\Asso[n]$ constructed in~\cite{ShniderSternberg, Loday}.
+We first describe these associahedra and their type cones as they are the prototypes of our constructions.
+
+\subsection{Classical associahedra}
+
+We quickly recall the combinatorics and the geometric construction of~\cite{ShniderSternberg, Loday} for the associahedron~$\Asso[n]$.
+The face lattice of~$\Asso[n]$ is the reverse inclusion lattice of dissections (\ie pairwise non-crossing subsets of diagonals) of a convex~$(n+3)$-gon.
+In particular, its vertices correspond to triangulations of the $(n+3)$-gon and its facets correspond to internal diagonals of the $(n+3)$-gon.
+Equivalently, its vertices correspond to rooted binary trees with $(n+1)$ internal nodes, and its facets correspond to proper intervals of~$[n+1]$ (\ie intervals distinct from~$\varnothing$ and~$[n+1]$).
+These bijections become clear when the convex $(n+3)$-gon is drawn with its vertices on a concave curve labeled by~$0, \dots, n+2$.
+The following statement provides three equivalent geometric constructions of~$\Asso[n]$.
+
+\begin{proposition}
+The associahedron~$\Asso[n]$ can be described equivalently as:
+\begin{itemize}
+\item the convex hull of the points~$L(T) \in \R^{n+1}$ for all rooted binary trees~$T$ with~$n+1$ internal nodes, where the $i$th coordinate of~$L(T)$ is the product of the number of leaves in the left subtree by the number of leaves in the right subtree of the $i$th node of~$T$ in inorder~\cite{Loday},
+\item the intersection of the hyperplane~$\bigset{\b{x} \in \R^{n+1}}{\sum_{\ell \in [n+1]} x_\ell = \binom{n+2}{2}}$ with the halfspaces $\bigset{\b{x} \in \R^{n+1}}{\sum_{i \le \ell \le j} x_\ell \ge \binom{j-i+2}{2}}$ for all proper intervals~$[i,j]$ of~$[n+1]$,~\cite{ShniderSternberg},
+\item the Minkowski sum of the faces~$\simplex_{[i,j]}$ of the standard $n$-dimensional simplex~$\simplex$ corresponding to all proper intervals~$[i,j]$ of~$[n+1]$,~\cite{Postnikov}.
+\end{itemize}
+\end{proposition}
+
+We now focus on the normal fan~$\gvectorFan[n]$ of~$\Asso[n]$.
+Since~$\Asso[n]$ leaves in a hyperplane of~$\R^{n+1}$, so does its normal fan.
+Let~$\HH \eqdef \bigset{\b{x} \in \R^{n+1}}{\sum_{\ell \in [n+1]} x_\ell = 0}$ and~$\pi : \R^{n+1} \to \HH$ denote the orthogonal projection.
+
+\begin{proposition}
+In the normal fan~$\gvectorFan[n]$ of~$\Asso[n]$, 
+\begin{itemize}
+\item the normal vector of the facet corresponding to an internal diagonal~$(a,b)$ of the $(n+3)$-gon is the vector~$\gvector{a,b} \eqdef \pi\big( \sum_{a < \ell < b} \b{e}_\ell \big) = (n+1) \sum_{a < \ell < b} \b{e}_\ell - (j-i+1) \sum_{1 \le \ell \le n+1} \b{e}_\ell$.
+\item the normal cone of the vertex corresponding to a rooted binary tree~$T$ is the incidence cone~$\bigset{\b{x} \in \HH}{x_i \le x_j \text{ for all edges $i \to j$ in $T$}}$.
+\end{itemize}
+\end{proposition}
+
+Let us also recall the linear dependencies in this fan and observe that it has the unique exchange property.
+From now on, we use the convention that~$\gvector{a,b} = 0$ when~$(a,b)$ is a boundary edge of the $(n+3)$-gon.
+
+\begin{proposition}
+\label{prop:exchangeablePairsAsso}
+%Consider two exchangeable proper intervals~$[i,j]$ and~$[\ell,k]$ of~$[n+1]$, corresponding to two crossing diagonals~$(i-1,j+1)$ and~$(k-1,\ell+1)$ of the $(n+3)$-gon with~$0 \le i-1 < k-1 < j+1 < \ell+1 \le n+2$.
+Consider two crossing diagonals~$(a,b)$ and~$(a',b')$, and any two triangulations~$T, T'$ such that~$T \ssm \{(a,b)\} = T' \ssm \{(a',b')\}$.
+Then both triangulations~$T$ and~$T'$ contain the square $aa'bb'$, and the linear dependence between the $\b{g}$-vectors of~$T \cup T'$ is given by
+\[
+\gvector{a,b} + \gvector{a',b'} = \gvector{a,b'} + \gvector{a',b}.
+\]
+In particular, the fan~$\gvectorFan[n]$ has the unique exchange property.
+\end{proposition}
+
+From these linear dependencies, we obtain that the type cone of the fan~$\gvectorFan[n]$.
+
+\begin{corollary}
+Let~$n \in \N$ and~$X(n) \eqdef \set{(a,b)}{0 \le a < b \le n+2}$. Then the type cone of the normal fan~$\gvectorFan[n]$ of~$\Asso[n]$ is given by
+\[
+\typeCone(\gvectorFan[n]) = \set{\b{h} \in \R^{X(n)}}{\begin{array}{l} \b{h}_{(0,n+2)} = 0, \qquad\text{and}\qquad \b{h}_{(a,a+1)} = 0 \text{ for all } 0 \le a \le n+1 \\ \b{h}_{(a,b)} + \b{h}_{(a',b')} > \b{h}_{(a,b')} + \b{h}_{(a',b)} \text{ for all } 0 \le a < a' < b < b' \le n+2 \end{array}}.
+\]
+\end{corollary}
+
+We now describe the facets of this type cone~$\typeCone(\gvectorFan[n])$.
+
+\begin{proposition}
+\label{prop:extremalExchangeablePairsAsso}
+Two internal diagonals~$(a,b)$ and~$(a',b')$ of the~$(n+3)$-gon form an extremal exchangeable pair for the fan~$\gvectorFan[n]$ if and only if~$a = a'+1$ and~$b = b'+1$, or the opposite.
+\end{proposition}
+
+\begin{proof}
+Let~$(\b{f}_{(a,b)})_{0 \le a < b \le n+2}$ be the canonical basis of~$\R^{\binom{n+3}{2}}$.
+Consider two crossing internal diagonals~$(a,b)$ and~$(a',b')$ with~$0 \le a < a' < b < b' \le n+2$.
+By \cref{prop:exchangeablePairsAsso}, the linear dependence between the corresponding $\b{g}$-vectors is given by
+\[
+\gvector{a,b} + \gvector{a',b'} = \gvector{a,b'} + \gvector{a',b}.
+\]
+Therefore, the outer normal vector of the corresponding inequality of the type cone~$\typeCone(\gvectorFan[n])$ is
+\[
+\b{n}(a,b,a',b') \eqdef \b{f}_{(a,b)} + \b{f}_{(a',b')} - \b{f}_{(a,b')} - \b{f}_{(a',b)}.
+\]
+Denoting
+\[
+\b{m}(c,d) \eqdef \b{n}(c,d-1,c+1,d) = \b{f}_{(c,d-1)} + \b{f}_{(c+1,d)} - \b{f}_{(c,d)} - \b{f}_{(c+1,d-1)},
+\]
+we obtain that
+\[
+\b{n}(a,b,a',b') = \sum_{\substack{c \in {[a,a'[} \\ d \in {]b,b']}}} \b{m}(c,d).
+\]
+Indeed, on the right hand side, the basis vector~$\b{f}_{(c,d)}$ appears with a positive sign in~$\b{m}(c,d+1)$ for~$(c,d) \in {[a,a'[} \times {[b,b'[}$ and in~$\b{m}(c-1,d)$ for~$(c,d) \in {]a,a']} \times {]b,b']}$, and with a negative sign in~$\b{m}(c,d)$ for~$(c,d) \in {[a,a'[} \times {]b,b']}$ and in~$\b{m}(c-1,d+1)$ for~$(c,d) \in {]a,a']} \times {[b,b'[}$.
+Therefore, these contributions all vanish except when~$(c,d)$ is one of the diagonals~$(a,b)$, $(a',b')$, $(a,b')$ or~$(a',b)$.
+This shows that any exchange relation is a positive linear combination of the exchange relations corresponding to all pairs of diagonals~$(a,b)$ and~$(a',b')$ of the~$(n+3)$-gon such that~$a = a'+1$ and~$b = b'+1$ or the opposite.
+
+Conversely, since~$\gvectorFan[n]$ has dimension~$n$ and~$n(n+3)/2$ rays (corresponding to the internal diagonals of the $(n+3)$-gon), we know from \cref{rem:dimTypeCone} that there are at least~$n(n+1)/2$ extremal exchangeable pairs.
+We thus conclude that all exchangeable pairs of diagonals~$\{(a,b-1), (a+1,b)\}$ for~$1 \le a < b-2 \le n$ are extremal.
+\end{proof}
+
+The following statement follows from the end of the previous proof.
+
+\begin{corollary}
+\label{coro:simplicialTypeConeAsso}
+The type cone~$\typeCone(\gvectorFan[n])$ is simplicial.
+\end{corollary}
+
+Combining \cref{coro:simplicialTypeCone}, \cref{coro:simplicialTypeConeAsso} and \cref{prop:extremalExchangeablePairsAsso}, we derive the following description of all polytopal realizations of the fan~$\gvectorFan[n]$, thus recovering all associahedra of~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan}.
+We note that the arguments used in~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} were quite different from the present approach.
+
+\begin{corollary}[{\cite[Sect.~3.2]{ArkaniHamedBaiHeYan}}]
+For~$n \in \N$, define~$X(n) \eqdef \set{(a,b)}{0 \le a < b \le n+2}$ and~$Y(n) \eqdef \set{(a,b)}{0 \le a < b-2 \le n}$.
+Then for any~$\b{\ell} \in \R_{>0}^{Y(n)}$, the polytope
+\[
+R_\b{\ell}(n) \eqdef \set{\b{z} \in \R^{X(n)}}{\begin{array}{l} \b{z} \ge 0, \quad \b{z}_{(0,n+2)} = 0 \quad\text{and}\quad \b{z}_{(a,a+1)} = 0 \text{ for all } 0 \le a \le n+1 \\ \b{z}_{(a,b-1)} + \b{z}_{(a+1,b)} - \b{z}_{(a,b)} - \b{z}_{(a+1,b-1)} = \b{\ell}_{(a,b)} \text{ for all } (a,b) \in Y(n) \end{array}}
+%\bigset{\b{z} \in \R^{X(n)}}{\b{z} \ge 0, \; \b{z}_{1,n+1} = 0 \text{ and } \b{z}_{i,j} + \b{z}_{i+1,j+1} - \b{z}_{i,j+1} - \b{z}_{i+1,j} = \b{\ell}_{i,j} \text{ for } (i,j) \in X(n-1)}
+\]
+is an $n$-dimensional associahedron.
+\end{corollary}
 
@@
 A \defn{peak} (resp.~\defn{deep}) of a walk~$\omega$ is a substring of~$\omega$ of length zero which is on top (resp.~at the bottom of~$\omega$).
-A walk~$\omega$ is \defn{straight} if it has no peak or deep (\ie if~$\omega$ or~$\omega^{-1}$ is a path in~$\bar Q\blossom$), and \defn{bending} otherwise.
+A walk~$\omega$ is \defn{straight} if it has no peak or deep (\ie if~$\omega$ or~$\omega^{-1}$ is a path in~$\quiver\blossom$), and \defn{bending} otherwise.
 We denote by~$\peaks{\omega}$ (resp.~$\deeps{\omega}$) the multisets of vertices of peaks (resp.~deeps) of~$\omega$.
@@
 \end{remark}
+
+\begin{corollary}
+For any non-kissing finite gentle quiver~$\quiver$, the type cone of the non-kissing fan~$\gvectorFan[\quiver]$ is given by
+\[
+\typeCone(\gvectorFan[\quiver]) = \set{\b{h} \in \R^{\walks}}{\begin{array}{l} \b{h}_\omega = 0 \text{ for any improper walk } \omega \\ \b{h}_\omega + \b{h}_{\omega'} > \b{h}_\mu + \b{h}_\nu \text{ for any exchangeable walks } \omega, \omega' \end{array}}.
+\]
+\end{corollary}
 
@@
 
-Conversely, we know from \cref{rem:dimTypeCone} that there are at least~$|\walks|-|Q_0|$ extremal exchangeable pairs.
-Since this~$|\strings| = |\distinguishableStrings| = |\walks| - |Q_0|$ by~\cref{prop:bijectionStringsWalks}, we conclude that all exchangeable pairs~$\{\cc{\sigma}, \hh{\sigma}\}$ for~$\sigma \in \strings$ are extremal.
+Conversely, we know from \cref{rem:dimTypeCone} that there are at least~$|\properWalks|-|Q_0|$ extremal exchangeable pairs.
+Since this~$|\strings| = |\distinguishableStrings| = |\properWalks| - |Q_0|$ by~\cref{prop:bijectionStringsWalks}, we conclude that all exchangeable pairs~$\{\cc{\sigma}, \hh{\sigma}\}$ for~$\sigma \in \strings$ are extremal.
 \end{proof}
 
-Combining \cref{coro:simplicialTypeCone}, \cref{prop:bijectionStringsWalks} and \cref{prop:extremalExchangeablePairsNKC}, we derive the following description of all polytopal realizations of the non-kissing fan.
+The following statement now follows from \cref{prop:bijectionStringsWalks,prop:extremalExchangeablePairsNKC}.
+
+\begin{corollary}
+\label{coro:simplicialTypeConeNKC}
+For any gentle quiver~$\quiver$ with no self-kissing walk, the type cone~$\typeCone(\gvectorFan[\quiver])$ of the non-kissing fan~$\quiver$ is simplicial.
+\end{corollary}
+
+Combining \cref{coro:simplicialTypeCone}, \cref{coro:simplicialTypeConeNKC} and \cref{prop:extremalExchangeablePairsNKC}, we derive the following description of all polytopal realizations of the non-kissing fan~$\gvectorFan[\quiver]$ of a quiver~$\quiver$ with no self-kissing~walk.
 
@@
 \[
-R_\b{\ell}(\quiver) \eqdef \bigset{\b{z} \in \R^{\walks}}{\b{z} \ge 0 \text{ and } \b{z}_{\cc{\sigma}} + \b{z}_{\hh{\sigma}} - \b{z}_{\hc{\sigma}} - \b{z}_{\ch{\sigma}} = \ell_\sigma \text{ for all } \sigma \in \strings}
+R_\b{\ell}(\quiver) \eqdef \set{\b{z} \in \R^{\walks}}{\begin{array}{l} \b{z} \ge 0 \qquad\text{and}\qquad \b{z}_\omega = 0 \text{ for any improper walk } \omega \\ \b{z}_{\cc{\sigma}} + \b{z}_{\hh{\sigma}} - \b{z}_{\hc{\sigma}} - \b{z}_{\ch{\sigma}} = \b{\ell}_\sigma \text{ for all } \sigma \in \strings\end{array}}
 \]
@@
 \cref{prop:extremalExchangeablePairsNKC} asserts that the type cone~$\typeCone(\gvectorFan[\quiver])$ has one facet for each string of~$\quiver$.
-Since all strings are distinguishable by \cref{prop:noSelfKissing}, the number of facets of~$\typeCone(\gvectorFan[\quiver])$ is $|\strings| = |\distinguishableStrings| = |\walks| - |Q_0|$ by~\cref{prop:bijectionStringsWalks}, so that~$\typeCone(\gvectorFan[\quiver])$ is simplicial.
+Since all strings are distinguishable by \cref{prop:noSelfKissing}, the number of facets of~$\typeCone(\gvectorFan[\quiver])$ is $|\strings| = |\distinguishableStrings| = |\properWalks| - |Q_0|$ by~\cref{prop:bijectionStringsWalks}, so that~$\typeCone(\gvectorFan[\quiver])$ is simplicial.
 We then conclude by a simple application of \cref{coro:simplicialTypeCone}.
@@
 \label{rem:meshARquiver}
-Although not needed in the proof of \cref{prop:extremalExchangeablePairsNKC}, we note that the extremal exchangeable pairs~$\{\cc{\sigma}, \hh{\sigma}\}$ and their linear dependences~${\gvector{\cc{\sigma}} + \gvector{\hh{\sigma}} - \gvector{\hc{\sigma}} - \gvector{\ch{\sigma}}}$ precisely correspond to the meshes of the Auslander-Reiten quiver of~$\quiver$.
+Although not needed in the proof of \cref{prop:extremalExchangeablePairsNKC}, we note that the extremal exchangeable pairs~$\{\cc{\sigma}, \hh{\sigma}\}$ and their linear dependencies~${\gvector{\cc{\sigma}} + \gvector{\hh{\sigma}} - \gvector{\hc{\sigma}} - \gvector{\ch{\sigma}}}$ precisely correspond to the meshes of the Auslander-Reiten quiver of~$\quiver$.
 \end{remark}
@@
 It seems that two exchangeable walks are always kissing along a single distinguishable string.
-We need to prove that to see that the non-kissing fan has the unique exchange relation property (because for a pair of exchangeable walks, I can completely reconstruct the $\b{g}$-vector dependence of the flip if I know there distinguished substring).
+We need to prove that to see that the non-kissing fan has the unique exchange relation property (because for a pair of exchangeable walks, I can completely reconstruct the $\b{g}$-vector dependence of the flip if I know their distinguished substring).
 Note however that
@@
 Let~$\connectedComponents(\graphG)$ denote the set of connected components of~$\graphG$ and define~$n \eqdef |\ground|-|\connectedComponents(\graphG)|$.
-A \defn{tube} of~$\graphG$ is a non-empty connected induced subgraph of~$\graphG$.
+A \defn{tube} of~$\graphG$ is a connected induced subgraph of~$\graphG$.
 The set of tubes of~$\graphG$ is denoted by~$\tubes(\graphG)$.
-The inclusion maximal tubes of~$\graphG$ are its connected components~$\connectedComponents(\graphG)$, and all other tubes are called \defn{proper}.
+The inclusion maximal tubes of~$\graphG$ are its connected components~$\connectedComponents(\graphG)$.
+The tubes which are neither empty nor maximal are called \defn{proper}.
 Two tubes~$\tube, \tube'$ of~$\graphG$ are \defn{compatible} if they are either nested (\ie $\tube \subseteq \tube'$ or~$\tube' \subseteq \tube$), or disjoint and non-adjacent (\ie $\tube \cup \tube'$ is not a tube of~$\graphG$).
@@
 
-We start with the case of the path.
-Recall that the tubes of the path are the intervals of~$[n]$ and that two intervals~$[i,j]$ and~$[i',j']$ of~$[n]$ are exchangeable if either~${i < i' \le j+1 < j'+1}$ or~${i' < i \le j'+1 < j+1}$.
+We start with the case of the path on~$n+1$ vertices.
+Recall that the tubes of the path are the intervals of~$[n+1]$ and that two intervals~$[i,j]$ and~$[i',j']$ of~$[n+1]$ are exchangeable if either~${i < i' \le j+1 < j'+1}$ or~${i' < i \le j'+1 < j+1}$.
 
@@
 %The extremal exchangeable pairs for the nested fan of the path are precisely the pairs of intervals~$\{[i,j], [i+1,j+1]\}$ for~$1 \le i \le j \le n-1$.
-Two intervals~$[i,j]$ and~$[i',j']$ of~$[n]$ form an extremal exchangeable pair for the nested fan of the path if and only if~$i = i'+1$ and~$j = j'+1$, or the opposite.
+Two intervals~$[i,j]$ and~$[i',j']$ of~$[n+1]$ form an extremal exchangeable pair for the nested fan of the path if and only if~$i = i'+1$ and~$j = j'+1$, or the opposite.
 \end{proposition}
@@
 \[
-\gvector{[i,j]} + \gvector{[i',j']} = \gvector{[i,j']} + \gvector{[i',j]}
+\gvector{[i,j]} + \gvector{[i',j']} = \gvector{[i,j']} + \gvector{[i',j]}.
 \]
@@
 \[
-\b{n}(i,j,i',j') \eqdef \b{f}_{[i,j]} + \b{f}_{[i',j']} - \b{f}_{[i,j']} - \b{f}_{[i',j]}
+\b{n}(i,j,i',j') \eqdef \b{f}_{[i,j]} + \b{f}_{[i',j']} - \b{f}_{[i,j']} - \b{f}_{[i',j]}.
 \]
@@
 %Therefore, these contributions all vanish except when~$[k, \ell]$ is one of the tubes~$[i,j]$, $[i',j']$, $[i,j']$ or~$[i',j]$.
-This shows that any exchange relation is a positive linear combination of the exchange relations corresponding to all pairs of tubes~$[i,j]$ and~$[i',j']$ of~$[n]$ such that~$i = i'+1$ and~$j = j'+1$.
+This shows that any exchange relation is a positive linear combination of the exchange relations corresponding to all pairs of tubes~$[i,j]$ and~$[i',j']$ of~$[n+1]$ such that~$i = i'+1$ and~$j = j'+1$.
 
@@
 \[
-|\tubes(\graphG)| - |V| = |\tubes(\graphG) \ssm \{\graphG\}| - (|V|-1) = N - n,
+|\tubes(\graphG)| - |V| = |\tubes(\graphG) \ssm \{\varnothing, \graphG\}| - (|V|-1) = N - n,
 \]
@@
 \end{proof}
-
-\subsection{Quotientopes}
-
-Be careful that the quotient fans are not simplicial.
-
-\subsection{Brick polytopes}
-
-Be careful that the brick fans are not simplicial.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Relations for~$\b{g}$-vectors in~$2$-Calabi--Yau triangulated categories}
-%%%%%
-\subsection{Setting}
-Let~$\field$ be a field.
-Let~$\cat$ be a~$\field$-linear triangulated category with suspension functor~$\susp$.
-We fix a collection~$\ind(\cat)$ of representatives of isomorphism classes of indecomposable objects of~$\cat$.
-We will assume the following:
-\begin{itemize}
- \item $\cat$ is essentially small (in particular,~$\ind(\cat)$ is a set);
- \item $\cat$ is~$\Hom{}$-finite: for each pair of objects~$X$ and~$Y$, the~$\field$-vector space~$\cat(X,Y)$ is finite-dimensional;
- \item $\cat$ is Krull--Schmidt: the endomorphism algebra of any indecomposable object is local;
- \item $\cat$ is~$2$-Calabi--Yau: for each pair of objects~$X$ and~$Y$, there is an isomorphism of bifunctors
- \[
-  \cat(X,\susp Y) \to D\cat(Y,\susp X)
- \]
- where~$D=\Hom{\field}(-,\field)$ is the usual duality of vector spaces;
- \item $\cat$ contains a basic cluster-tilting object~$T=\bigoplus_{i=1}^n T_i$:
- \[
-  \textrm{for any object~$X$,} \quad \cat(T, \susp X) = 0 \quad \textrm{if and only if} \quad X\in \add(T),
- \]
- where~$\add(T)$ is the smallest additive full subcategory of~$\cat$ containing the~$T_i$'s and closed under isomorphisms.
-\end{itemize}
-
-%%%%
-\subsection{Statement of the theorem}
-We need to introduce some notations before stating the main result of this section.  Let~$\Lambda:= \End{\cat}(T)$, and let~$F$ be the functor
-\[
- F=\cat(T,-):\cat \xrightarrow{} \MOD \Lambda.
-\]
-\begin{proposition}[]\pg{Add references to BMR and KR}
- The functor~$F$ induces an equivalence of~$\field$-linear categories
- \[
-  F:\cat/(\susp T) \xrightarrow{} \MOD \Lambda,
- \]
- where~$(\susp T)$ is the ideal of morphisms factoring through an object of~$\add(\susp T)$ and~$\MOD \Lambda$ is the category of finite-dimensional right~$\Lambda$-modules.
-This equivalence induces further equivalences between~$\add(T)$ and the category of projective modules, and between~$\add(\susp^2 T)$ and that of injective modules.
-\end{proposition}
-
-For categories with a cluster-tilting objects, the~$2$-Calabi--Yau condition implies other duality results which we shall need.
-
-\begin{proposition}[]\pg{Cite Palu}
- For any pair of objects~$X$ and~$Y$ in~$\cat$, there is an isomorphism of bifunctors
- \[
-  (\susp T)\cat(X, \susp Y) \xrightarrow{\cong} \cat(Y, \susp X)/(\susp T),
- \]
- where~$(\susp T)\cat(X, \susp Y)$ is the space of morphisms from~$X$ to~$Y$ factoring through~$(\susp T)$.
-\end{proposition}
-
-\begin{remark}
- Although the field~$\field$ is assumed to be algebraically closed in~\cite{} \pg{Cite Palu}, this assumption is not needed in the proof, and the result is valid over any field.
-\end{remark}
-
-Finally, we need the existence of almost-split triangles in~$\cat$.  Recall that a triangle
-\[
- X\xrightarrow{f} Y \xrightarrow{g} Z \xrightarrow{h} \susp X
-\]
-in~$\cat$ is \defn{almost-split} if~$X$ and~$Z$ are indecomposable,~$h$ is non-zero, and any non-section~$X\to X'$ factors through~$f$  (or equivalently, any non-retraction~$Z'\to Z$ factors through~$g$).
-We say that a triangulated category \defn{has almost-split triangles} if there is an almost-split triangle as above for any indecomposable object~$X$.
-
-\begin{proposition}[]\pg{Cite Happel}
- Any triangulated category admitting a Serre functor has almost-split triangles.  In particular, any~$2$-Calabi--Yau triangulated category has almost-split triangles.
-\end{proposition}
-
-\begin{definition}
- \begin{enumerate}
-  \item Let~$\Ksp(\cat)$ be the \defn{split Grothendieck group} of~$\cat$, that is, the free abelian group generated by symbols~$[X]$, where~$[X]$ denotes the isomorphism class of~$X$ in~$\cat$, modulo the following relations: for any objects~$Y$ and~$Z$, we let~$[Y\oplus Z] = [Y] + [Z]$.
-
-  \item Let~$\Kg(\cat)$ be the quotient of~$\Ksp(\cat)$ by the relations~$[X]+[Z]-[Y]$ for all triangles
-  \[
-   X\xrightarrow{} Y \xrightarrow{} Z \xrightarrow{h} \susp X
-  \]
-  with~$h\in (\susp T)$.  Denote by~$\b g:\Ksp(\cat) \to \Kg(\cat)$ the canonical projection.
-
- \end{enumerate}
-
-\end{definition}
-In particular,~$\Ksp(\cat)$ is isomorphic to a free abelian group over the set~$\ind(\cat)$.
-The choice of the notation for~$\Kg(\cat)$ is motivated by the next section \pg{Add ref}, where we study relations between~$\b g$-vectors.
-
-\begin{definition}
- For any two objects~$X$ and~$Y$ of~$\cat$, define
- \[
-  \langle X, Y \rangle := \dim_{\field} \Hom{\Lambda}(FX,FY).
- \]
- This defines a bilinear form
- \[
-  \langle -,-\rangle : \Ksp(\cat) \times \Ksp(\cat) \xrightarrow{} \Z.
- \]
-\end{definition}
-
-\begin{notation}
-\begin{enumerate}
- \item For any indecomposable object~$X$ of~$\cat$, let
- \[
-  X \to E \to \susp^{-1} X \to \susp X
- \]
- be an almost split triangle (unique up to isomorphism).  We let
- \[
-  \ell_X := [X] + [\susp^{-1} X]  - [E] \in \Ksp(\cat).
- \]
-
- \item For any indecomposable object~$Y$ of~$\cat$, let
- \[
-  \susp Y \to E' \to  Y \to \susp^2 Y
- \]
- be an almost split triangle (unique up to isomorphism).  We let
- \[
-  r_Y := [Y] + [\susp Y]  - [E'] \in \Ksp(\cat).
- \]
-\end{enumerate}
-\end{notation}
-
-We can finally state the main theorem of this section. \pg{recall Auslander}
-
-\begin{theorem}\label{theo::relations-g-vecteurs}
- Let~$\cat$ be a category satisying the hypotheses of \ref{} \pg{add ref}.
-Then~$\cat$ has only finitely many isomorphism classes of indecomposable objects if and only if the set~\[L:=\big\{\ell_X \ | \ X\in \ind(\cat)\setminus \add(\susp T) \big\}\] generates the kernel of~$\b g:\Ksp(\cat) \to \Kg(\cat)$.
- In this case, the set~$L$ is a basis of the kernel of~$\b g$, and \pg{add formula}, for any $x\in \ker(\b g)$, we have that
- \[
-  x= \sum_{A\in \ind(\cat) \setminus \add(\susp T)} \frac{\langle x, A \rangle}{\langle \ell_A, A \rangle} \ell_A.
- \]
-\end{theorem}
-
-\begin{corollary}
- Assume that~$\ind(\cat)$ is finite.
-Let~$X\xrightarrow{} E \xrightarrow{} Y \xrightarrow{h} \susp X$ be a triangle with~$h\in (\susp T)$.
-Then the element~$x=[X]+[Y]-[E]$ of the kernel of~$\b g$ is a non-negative linear combination of the~$\ell_A$, with~$A\in \ind(\cat)\setminus \add(\susp T)$.
-\end{corollary}
-\begin{proof}
- We know that~$x=\sum_{A\in \ind(\cat)\setminus \add(\susp T)} \frac{\langle x, [A] \rangle}{\langle \ell_A, [A] \rangle} \ell_A$; since~$\langle \ell_A, [A] \rangle$ is positive by Lemma~\ref{lemm::bilinear-form}, we only need to show that each~$\langle x, [A] \rangle$ is non-negative.
- The functor~$F=\cat(T,-)$ induces an exact sequence
- \[
-  FX \to FE \to FY \to 0,
- \]
- which in turn induces an exact sequence
- \[
-  0\to \Hom{\Lambda}(FY, FA) \to \Hom{\Lambda}(FE, FA) \xrightarrow{f} \Hom{\Lambda}(FX, FA) \to \coker(f) \to 0.
- \]
- Therefore~$\langle x, [A] \rangle = \dim_{\field} \coker(f) \geq 0$.
-\end{proof}
-
-%%%%
-\subsection{Proof of Theorem \ref{theo::relations-g-vecteurs}}
-
-\begin{lemma}
- If~$X$ or~$Y$ lie in~$\add(\susp T)$, then~$\langle X, Y \rangle = 0$.
-\end{lemma}
-\begin{proof}
- This is because~$F\susp T = 0$.
-\end{proof}
-
-\begin{lemma}\label{lemm::almost-split}
- Let~$X\xrightarrow{} Y \xrightarrow{} \susp^{-1} X \xrightarrow{h} \susp X$ be an almost-split triangle.  Then~$X\notin \add(\susp T)$ if and only if~$h\in (\susp T)$.
-\end{lemma}
-\begin{proof}
- If~$X\in \add(\susp T)$, then~$h$ cannot be in~$(\susp T)$, otherwise it would be zero since~$\cat(T, \susp T) =0$.
-
- Assume now that~$X\notin \add(\susp T)$.  Let~$\field_X$ be the residue field of the algebra~$\End{\cat}(X)$. 
- By definition of an almost-split triangle,~$h$ is in the socle of the right~$\End{\cat}(X)$-module~$\cat(\susp^{-1} X, \susp X)$.
-Moreover, this socle is a one-dimensional~$\field_X$-vector space; indeed, the~$2$-Calabi--Yau condition gives an isomorphism
- \[
-  \cat(\susp^{-1} X, \susp X) \cong D\cat(X, X).
- \]
- Thus the socle of the right module~$\cat(\susp^{-1} X, \susp X)$ has the same~$\field_X$ dimension as the top of the left module~$\cat(X,X)$.
-Since~$X$ is indecomposable,~$\cat(X,X)$ is local, and its top is one-dimensional over~$\field_X$.
-
- Now,~$(\susp T)\cat(\susp^{-1} X, \susp X)$ is a sub-module of~$\cat(\susp^{-1} X, \susp X)$.
-Therefore, if~$(\susp T)\cat(\susp^{-1} X, \susp X)$ is non-zero, then it contains the one-dimensional socle of~$\cat(\susp^{-1} X, \susp X)$, and thus contains~$h$.
- By \cite{} \pg{cite Palu},
- \[
-  (\susp T)\cat(\susp^{-1} X, \susp X) \cong D\cat(X, X)/(\susp T). 
- \]
-The identity morphism of~$X$ is not in~$(\susp T)$, since~$X$ is not in~$\add(\susp T)$.
-Thus the right-hand side is non-zero, and so neither is the left-hand side.
-By the above, this implies that~$h\in (\susp T)\cat(\susp^{-1} X, \susp X)$, which finishes the proof.
-\end{proof}
-
-\begin{lemma}\label{lemm::bilinear-form}
-Let~$A$ and~$B$ be two indecomposable objects of~$\cat$. \pg{introduce general notation for redisue field}
-\begin{enumerate}
- \item If~$A \notin \add(\susp T)$, then
- \[
-  \langle \ell_A, B \rangle = \begin{cases}
-                               0 & \textrm{if~$A\ncong B$;} \\
-                               \dim_{\field}\field_A & \textrm{if~$A\cong B$.}
-                              \end{cases}
- \]
-
- \item If~$B \notin \add(\susp T)$, then
- \[
-  \langle A, r_B \rangle = \begin{cases}
-                               0 & \textrm{if~$A\ncong B$;} \\
-                               \dim_{\field}\field_B & \textrm{if~$A\cong B$.}
-                              \end{cases}
- \]
-\end{enumerate} 
-\end{lemma}
-\begin{proof}
- We only prove the first assertion; the second one is proved dually.  Assume that~$A\notin\add(\susp T)$.  Let
- \[
-  A \xrightarrow{f} E \xrightarrow{} \susp^{-1} A \xrightarrow{h} \susp A
- \]
- be an almost-split triangle.  By Lemma~\ref{lemm::almost-split}, the morphism~$h$ is in~$(\susp T)$.  Applying the functor~$F=\cat(T,-)$, we get an exact sequence
- \[
-  FA\xrightarrow{Ff} FE \xrightarrow{} F\susp^{-1} A \xrightarrow{} 0.
- \]
- Applying now the functor~$\Hom{\Lambda}(-, FB)$, we get an exact sequence
- \[
-  0 \xrightarrow{} \Hom{\Lambda}(F\susp^{-1} A, FB) \xrightarrow{} \Hom{\Lambda}(FE, FB) \xrightarrow{Ff^*} \Hom{\Lambda}(FA, FB) \xrightarrow{} \coker(Ff^*) \xrightarrow{} 0
- \]
- If~$B\ncong A$, then the definition of an almost-split triangle implies that~$Ff^*$ is surjective.
-\pg{add an exact sequence here; image of Ffstar is non-invertible elements} Thus~$\coker(Ff^*) = 0$, and by additivity of the dimension in exact sequences, we get that~$\langle \ell_A, B \rangle =0$.
-
- If~$B\cong A$, then~$\coker(Ff^*)$ is isomorphic to the residue field of~$\End{\Lambda}(FA)$, which is isomorphic to the residue field~$\field_A$ of~$A$.
-\end{proof}
-
-\pg{TO DO}
-
-%%%%
-\subsection{Application to~$\b g$-vectors}
-
-We recall the following results and definition from \cite{} \pg{cite DK and Palu}.
-
-\begin{proposition}
- Let~$X$ be an object of~$\cat$. Then there exists a triangle
- \[
-  T_1^X \to T^0_X \to X \to \susp T_1^X
- \]
- with~$T_1^X$ and~$T_0^X$ in~$\add(T)$.
-
-\end{proposition}
-
-\begin{definition}
- The \defn{index} of an object~$X$ is the element
- \[
-  \ind_T(X) := [T_0^X] - [T_1^X] \in \Ksp(\add(T)).
- \]
-\end{definition}
-
-The notion of index is very close to the definition of the map~$\b g:\Ksp(\cat)\to \Kg(\cat)$ of Definition~\ref{} \pg{ref}.  The link is given by the following result.
-
-\begin{proposition}[]\pg{cite Palu}
- Let~$X\xrightarrow{} Y \xrightarrow{} Z \xrightarrow{h} \susp X$ be a triangle.
- Then
- \[
-  \ind_T(X) + \ind_T(Z) - \ind_T(Y) = 0
- \]
- if and only if~$h\in (\susp T)$.
-\end{proposition}
-
-\begin{corollary}
- There is an isomorphism~$\phi:\Kg(\cat) \to \Ksp(\add(T))$ such that~$\ind_T = \phi\circ \b g$.  In particular,~$\Kg(\cat)$ is a free abelian group generated by the~$[T_i]$.
-\end{corollary}
-
-\begin{theorem}[]\pg{cite???}
- Let~$\cat$ be the cluster category of a valued quiver of Dynkin type~$A,B,C,D,E,F$ or~$G$.
-Let~$T$ be a basic cluster-tilting object in~$\cat$, and let~$Q$ be the valued Gabriel quiver of~$\End{\cat}(T)$.
-Then there is a bijection
- \[
-  \CC: \ind(\cat) \xrightarrow{} \{\textrm{cluster variables in the cluster algebra of~$Q$}\},
- \]
- which has the follwing properties.
- \begin{itemize}
-  \item For any~$X,Y\in \ind(\cat)$, $\CC(X)$ and~$\CC(Y)$ are compatible if and only if~$\cat(X, \susp Y) = 0$.
-  \item For any~$X\in \ind(\cat)$, the~$\b g$-vector of~$\CC(X)$ is~$\b g([X])$, where we identify~$\Z^n$ and~$\Kg(\cat)$ via the isomorphism sending~$(a_1, \ldots, a_n)$ to~$\sum_{i=1}^n a_i [T_i]$.
-  \item For any~$X,Y\in \ind(\cat)$, $\CC(X)$ and~$\CC(Y)$ are exchangeable if and only if~$\dim_{\field_X}\cat(X, \susp Y) = \dim_{\field_Y}\cat(X, \susp Y) = 1$.
- \end{itemize}
-\end{theorem}
-
-The cluster category also contains enough information to detect positive mutations.
-
-\begin{proposition}
- Let~$X,Y\in \ind(\cat)$ be such that~$\dim_{\field_X}\cat(X, \susp Y) = \dim_{\field_Y}\cat(X, \susp Y) = 1$.  Let 
- \[
-  X\xrightarrow{} E \xrightarrow{} Y \xrightarrow{h} \susp X \quad \textrm{and} \quad Y\xrightarrow{} E' \xrightarrow{} X \xrightarrow{h'} \susp Y
- \]
- be triangles with~$h$ and~$h'$ non-zero (these triangles are unique up to isomorphism).
-Then~$\CC(Y)$ is obtained by performing a positive mutation on~$\CC(X)$ in some seed if and only if~$h\in (\susp T)$.
- \begin{proof}
-  \pg{TO DO, Vincent: definition of positive mutation?}
- \end{proof}
-\end{proposition}
 

### 2019-02-04 thirdPaper/draft/typeConeAssociahedra.tex

--- 2019-02-04 thirdPaper/draft/typeConeAssociahedra.tex
@@
 
-Conversely, we know from \cref{rem:dimTypeCone} that there are at least~$|\walks|-|Q_0|$ extremal exchangeable pairs.
-Since this~$|\strings| = |\distinguishableStrings| = |\walks| - |Q_0|$ by~\cref{prop:bijectionStringsWalks}, we conclude that all exchangeable pairs~$\{\cc{\sigma}, \hh{\sigma}\}$ for~$\sigma \in \strings$ are extremal.
-\end{proof}
-
-Combining \cref{coro:simplicialTypeCone}, \cref{prop:bijectionStringsWalks} and \cref{prop:extremalExchangeablePairsNKC}, we derive the following description of all polytopal realizations of the non-kissing fan.
+Conversely, we know from \cref{rem:dimTypeCone} that there are at least~$|\properWalks|-|Q_0|$ extremal exchangeable pairs.
+Since this~$|\strings| = |\distinguishableStrings| = |\properWalks| - |Q_0|$ by~\cref{prop:bijectionStringsWalks}, we conclude that all exchangeable pairs~$\{\cc{\sigma}, \hh{\sigma}\}$ for~$\sigma \in \strings$ are extremal.
+\end{proof}
+
+The following statement now follows from \cref{prop:bijectionStringsWalks,prop:extremalExchangeablePairsNKC}.
+
+\begin{corollary}
+\label{coro:simplicialTypeConeNKC}
+For any gentle quiver~$\quiver$ with no self-kissing walk, the type cone~$\typeCone(\gvectorFan[\quiver])$ of the non-kissing fan~$\quiver$ is simplicial.
+\end{corollary}
+
+Combining \cref{coro:simplicialTypeCone}, \cref{coro:simplicialTypeConeNKC} and \cref{prop:extremalExchangeablePairsNKC}, we derive the following description of all polytopal realizations of the non-kissing fan~$\gvectorFan[\quiver]$ of a quiver~$\quiver$ with no self-kissing~walk.
 
@@
 \end{proof}
-
-\subsection{Quotientopes}
-
-Be careful that the quotient fans are not simplicial.
-
-\subsection{Brick polytopes}
-
-Be careful that the brick fans are not simplicial.
 

### 2019-02-05 thirdPaper/draft/typeConeAssociahedra.tex
Created new section

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Relations for~$\b{g}$-vectors in~$2$-Calabi--Yau triangulated categories}
+\section{Relations for~$\b{g}$-vectors in finite type cluster algebras via~$2$-Calabi--Yau triangulated categories}
 %%%%%
@@
 %%%%
-\subsection{Application to~$\b g$-vectors}\label{sect::applications-g-vectors}
+\subsection{Application to~$\b g$-vectors of cluster algebras of finite type}\label{sect::applications-g-vectors}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Relations for~$\b{g}$-vectors in brick algebras via extriangulated categories}
+
+%%%%
+\subsection{Setting}
+
+%%%%
+\subsection{Statement of the theorem}
+
+%%%%
+\subsection{Proof of Theorem~\ref{}}
+
+%%%%
+\subsection{Application to~$\b g$-vectors of brick algebras}
+
+%%%%
+\subsection{Examples}
+
+%%
+\subsubsection{A brick algebra}
+
+%%
+\subsubsection{A quotient of a Frobenius category}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2019-02-05 thirdPaper/draft/typeConeAssociahedra.tex
draft introduction cluster algebras

--- 2019-02-04 thirdPaper/draft/typeConeAssociahedra.tex
@@
 \newcommand{\R}{\mathbb{R}} % reals
+\newcommand{\Q}{\mathbb{Q}} % rationals
 \newcommand{\N}{\mathbb{N}} % naturals
@@
 \newcommand{\dotprod}[2]{\left\langle \, #1 \; \middle| \; #2 \, \right\rangle} % dot product
+\newcommand{\bigdotprod}[2]{\big\langle \, #1 \; \big| \; #2 \, \big\rangle} % dot product
 \newcommand{\symdif}{\,\triangle\,} % symmetric difference
@@
 \renewcommand{\implies}{\Rightarrow} % imply sign
-\newcommand{\transpose}[1]{{#1}^t} % transpose matrix
+\newcommand{\transpose}[1]{{#1}^T} % transpose matrix
 
@@
 \newcommandx{\gvectorFan}[1][1=\quiver]{\mathcal{F}(#1)} % g-vector fan
+\newcommand{\cvector}[3]{\mathbf{c}(#1, #3 \in #2)} % c-vector of the cluster variable #3 in the cluster #2 with respect to the initial cluster #1
+\newcommand{\cvectors}[2]{\mathbf{c}(#1, #2)} % c-vectors of the cluster #2 with respect to the initial cluster #1
 
@@
 \newcommandx{\coefficient}[3][1={\ray[s]}, 2=\ray, 3=\ray']{\alpha_{#2,#3}(#1)} % coefficient in linear dependence
+
+% Cluster algebras
+\newcommand{\Trop}[1]{\mathbb{P}_{#1}} % tropical semifield
+\newcommand{\positiveExponents}[1]{\left\{#1\right\}_+} % positive exponents in tropical semifield
+\newcommand{\negativeExponents}[1]{\left\{#1\right\}_-} % negative exponents in tropical semifield
+\newcommand{\seed}{\Sigma} % a cluster
+\newcommand{\cluster}{\mathrm{X}} % a cluster
+\newcommandx{\clusters}{\mathcal{X}} % all clusters
+\newcommand{\coefficients}{\mathrm{P}} % a coefficients tuple
+\newcommandx{\clusterAlgebra}[2][1=\B_\circ, 2=\coefficients_\circ]{\mathcal{A}\!\left(#1,#2\right)} % cluster algebra
+\newcommandx{\principalClusterAlgebra}[1][1=\B_\circ]{\mathcal{A}_{\mathrm{pr}}\left(#1\right)} % principal coefficients cluster algebra
+\newcommandx{\coefficientFreeClusterAlgebra}[1][1=\B_\circ]{\mathcal{A}_{\mathrm{fr}}(#1)} % coefficient free cluster algebra
+\newcommandx{\clusterComplex}[1][1=\B_\circ]{\Delta(#1)} % cluster complex
+\newcommand{\B}{\mathrm{B}} % b-matrix
+\newcommand{\A}[1]{\mathrm{A}({#1})} % b-matrix
+\newcommand{\D}{\mathrm{D}} % symmetrizer
+\newcommand{\simpleRoot}{\alpha} % simple root
+\newcommand{\fundamentalWeight}{\omega} % fundamental weights
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Polytopal realizations and type cone of a simplicial fan}
+
+%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%
+
 \subsection{Type cone}
@@
 \end{remark}
+
+%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%
+
 \subsection{Alternative polytopal realizations}
@@
 
+%%%%%%%%%%%
+
 \subsection{Faces of the type cone and Minkowski sums}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Applications to different generalizations of the associahedron}
@@
 We first describe these associahedra and their type cones as they are the prototypes of our constructions.
+
+%%%%%%%%%%%
 
@@
 %Consider two exchangeable proper intervals~$[i,j]$ and~$[\ell,k]$ of~$[n+1]$, corresponding to two crossing diagonals~$(i-1,j+1)$ and~$(k-1,\ell+1)$ of the $(n+3)$-gon with~$0 \le i-1 < k-1 < j+1 < \ell+1 \le n+2$.
-Consider two crossing diagonals~$(a,b)$ and~$(a',b')$, and any two triangulations~$T, T'$ such that~$T \ssm \{(a,b)\} = T' \ssm \{(a',b')\}$.
+Let~$(a,b)$ and~$(a',b')$ be two crossing diagonals with~${0 \le a < a' < b < b' \le n+2}$, and let~$T$ and~$T'$ be any two triangulations such that~$T \ssm \{(a,b)\} = T' \ssm \{(a',b')\}$.
 Then both triangulations~$T$ and~$T'$ contain the square $aa'bb'$, and the linear dependence between the $\b{g}$-vectors of~$T \cup T'$ is given by
@@
 
+%%%%%%%%%%%
+
 \subsection{Generalized associahedra}
 
+We now extend the results of the previous section to the $\b{g}$-vector fan of any finite type cluster algebra with respect to any seed (acyclic or not).
+Cluster algebras were introduced by S.~Fomin and A.~Zelevinsky~\cite{FominZelevinsky-ClusterAlgebrasI} with motivation coming from total positivity and canonical bases.
+Here, we will focus on finite type cluster algebras~\cite{FominZelevinsky-ClusterAlgebrasII} and more specifically on properties of their $\b{g}$-vectors~\cite{FominZelevinsky-ClusterAlgebrasIV}.
+These $\b{g}$-vectors support a complete simplicial fan, which is known to be the normal fan of a polytope called generalized associahedron.
+These polytopal realizations were first constructed for bipartite initial seeds by F.~Chapoton, S.~Fomin and A.~Zelevinsky~\cite{ChapotonFominZelevinsky} using the $\b{d}$-vector fans of~\cite{FominZelevinsky-YSystems}, then for acyclic initial seeds by C.~Hohlweg, C.~Lange and H.~Thomas~\cite{HohlwegLangeThomas} using Cambrian lattices and fans of N.~Reading and D.~Speyer~\cite{Reading-CambrianLattices, ReadingSpeyer}, and revisited by S.~Stella~\cite{Stella}, and by V.~Pilaud and C.~Stump~\cite{PilaudStump-brickPolytope} via brick polytopes, and finally for arbitrary initial seeds by C.~Hohlweg, V.~Pilaud and S.~Stella~\cite{HohlwegPilaudStella}.
+
+\para{Cluster algebras}
+%
+Let~$\Q(x_1, \dots, x_n, p_1, \dots, p_m)$ be the field of rational expressions in~$n+m$ variables with rational coefficients, and~$\Trop{m}$ denote its abelian multiplicative subgroup generated by~$\{p_i\}_{i \in [m]}$.
+For~$p = \prod\limits_{i \in [m]} p_i^{a_i} \in \Trop{m}$, define
+\(
+\positiveExponents{p} \eqdef \prod\limits_{i \in [m]} p_i^{\max(a_i,0)}
+\)
+and
+\(
+\negativeExponents{p} \eqdef \prod\limits_{i \in [m]} p_i^{-\min(a_i,0)}
+\).
+%so that~$p = \positiveExponents{p} \negativeExponents{p}^{-1}$.
+
+\medskip
+A \defn{seed}~$\seed$ is a triple~$(\B, \coefficients, \cluster)$ where
+\begin{itemize}
+\item the \defn{exchange matrix}~$\B$ is an integer~$n \times n$ skew-symmetrizable matrix, \ie such that there exists a diagonal matrix~$\D$ with~$-\B\D = (\B\D)^T$,
+\item the \defn{coefficient tuple}~$\coefficients$ is any subset of~$n$ elements of~$\Trop{m}$,
+\item the \defn{cluster}~$\cluster$ is a set of~$n$ \defn{cluster variables} in~$\Q(x_1, \dots, x_n, p_1, \dots, p_m)$ algebraically independent over~$\Q(p_1, \dots, p_m)$.
+\end{itemize}
+To simplify our notations, we use the convention to label~$\B = (b_{xy})_{x,y \in \cluster}$ and~$\coefficients = \{p_x\}_{x \in \cluster}$ by the cluster variables of~$\cluster$.
+
+For a seed~$\seed = (\B, \coefficients, \cluster)$ and a cluster variable~$x \in \seed$, the \defn{mutation} in direction~$x$ creates a new seed~$\mu_x(\seed) = \seed' = (\B', \coefficients', \cluster')$ where:
+\begin{itemize}
+\item the new cluster $\cluster'$ is obtained from $\cluster$ by replacing $x$ with the cluster variable $x'$ defined by the following \defn{exchange relation}:
+\[
+x x' = \positiveExponents{p_x} \prod_{{y \in \cluster, \; b_{xy}  > 0}} y^{b_{xy}} + \negativeExponents{p_x} \prod_{{y \in \cluster, \; b_{xy}  <0}} y^{-b_{xy}}
+\]
+and leaving the remaining cluster variables unchanged so that $\cluster \ssm \{x\} = \cluster' \ssm \{x'\}$.
+
+\item the row (resp.~column) of~$\B'$ indexed by~$x'$ is the negative of the row (resp.~column) of~$\B$ indexed by~$x$, while all other entries satisfy
+\(
+b'_{yz} = b_{yz} + \frac{1}{2}\big(|b_{yx}| b_{xz} + b_{yx}|b_{xz}|\big),
+\)
+
+\item the elements of the new coefficient tuple $\coefficients'$ are 
+\[
+p'_y =
+\begin{cases}
+	p_x^{-1}  & \text{if } y = x', \\
+	p_y\negativeExponents{p_x}^{b_{xy}}  & \text{if } y \neq x' \text{ and } b_{xy} \leq 0, \\
+	p_y\positiveExponents{p_x}^{b_{xy}}  & \text{if } y \neq x' \text{ and } b_{xy} > 0,
+\end{cases}
+\]
+\end{itemize}
+An important point is that mutations are involutions: $\mu_{x'} \big( \mu_{x}(\seed) \big) = \seed$.
+We say that two seeds are \defn{mutationally equivalent} when they can be obtained from each other by a sequence of mutations (we also use the same terminology for exchange matrices).
+%We consider an \defn{initial seed} $\seed_\circ = (\B_\circ, \coefficients_\circ, \cluster_\circ)$ whose cluster variables are supposed to be~$x_1, \dots, x_n$.
+
+\begin{definition}[{\cite[Definition~2.11]{FominZelevinsky-ClusterAlgebrasIV}}]
+The (geometric type) \defn{cluster algebra} $\clusterAlgebra$ is the $\Z\Trop{m}$-subring of~$\Q(x_1, \dots, x_n, p_1, \dots, p_m)$ generated by all the cluster variables in all the seeds mutationally equivalent to an initial seed~$\seed_\circ = (\B_\circ, \coefficients_\circ, \cluster_\circ)$ with cluster variables~$\cluster_\circ = \{x_1, \dots, x_n\}$.
+\end{definition}
+
+The \defn{cluster complex} of~$\clusterAlgebra$ is the simplicial complex whose vertices are the cluster variables of~$\clusterAlgebra$ and whose facets are the clusters of~$\clusterAlgebra$.
+
+\para{Finite type}
+%
+In this paper, we only consider \defn{finite type} cluster algebras, \ie those having only finitely many cluster variables.
+It turns out that these finite type cluster algebras were classified by S.~Fomin and A.~Zelevinsky~\cite{FominZelevinsky-ClusterAlgebrasII} using the Cartan-killing classification for crystallographic root systems.
+Define the \defn{Cartan companion} of an exchange matrix $\B$ as the matrix~$\A{\B}$ given by~$a_{xy} = 2$ if~$x = y$ and~$a_{xy} = -|b_{xy}|$ otherwise.
+
+\begin{theorem}[{\cite[Theorem~1.4]{FominZelevinsky-ClusterAlgebrasII}}]
+\label{thm:finiteTypeClassification}
+The cluster algebra~$\clusterAlgebra$ is of finite type if and only~if $\B_\circ$ is mutationally equivalent to a matrix~$\B$ whose Cartan companion~$\A{\B}$ is a Cartan matrix of finite type.
+Moreover the type of $\A{\B}$ is determined~by~$B_\circ$.
+\end{theorem}
+
+A finite type exchange matrix~$\B_\circ$ is \defn{acyclic} if~$\A{\B_\circ}$ is already a Cartan matrix, and \defn{cyclic} otherwise.
+An acyclic exchange matrix~$\B_\circ$ is \defn{bipartite} if each row of~$\B_\circ$ consists either of non-positive or non-negative entries.
+We use the same terminology for the seed~$\seed_\circ$.
+
+From now on, we fix a finite type cluster algebra~$\clusterAlgebra$ and we consider the root system of type~$\A{\B_\circ}$ (again, this root system is finite only when the initial seed~$\B_\circ$ is acyclic).
+We use the following classical bases of the underlying vector spaces:
+\begin{itemize}
+\item the simple roots~$\{\simpleRoot_x\}_{x \in \cluster_\circ}$ and the fundamental weights~$\{\fundamentalWeight_x\}_{x \in \cluster_\circ}$ are two bases of the same vector space~$V$ related by the Cartan matrix~$\A{\B_\circ}$,
+\item the simple coroots~$\{\simpleRoot^\vee_x\}_{x \in \cluster_\circ}$ and the fundamental coweights~$\{\fundamentalWeight^\vee_x\}_{x \in \cluster_\circ}$ are two basis of the dual space~$V^\vee$ related by the transpose of the Cartan matrix~$\transpose{\A{\B_\circ}}$,
+\end{itemize}
+and the basis of simple roots is dual to the basis of fundamental coweights, while the basis of fundamental weights is dual to the basis of simple coroots.
+
+The cluster complex of a finite cluster algebra~$\clusterAlgebra$ is independent of the choice of coefficients and of the choice of the initial seed (as long at it remains in the same mutation class), and therefore only depends on the cluster type of~$\clusterAlgebra$ (\ie the Cartan type of~$\A(\B)$ in \cref{thm:finiteTypeClassification}).
+Moreover, for~$\B_\circ^\vee \eqdef -\transpose{\B_\circ}$, then the map sending a cluster variable~$x$ in a seed~$\seed$ of~$\clusterAlgebra$ to the cluster variable~$x^\vee$ in the seed~$\seed^\vee$ of~$\principalClusterAlgebra[\B_\circ^\vee]$ obtained by the same sequence of mutations defines a natural isomorphism between the cluster complexes of~$\clusterAlgebra$ and~$\clusterAlgebra[\B_\circ^\vee]$.
+
+\para{Principal coefficients and $\b{g}$- and $\b{c}$-vectors}
+%
+We now consider principal coefficients to define the $\b{g}$- and $\b{c}$-vectors.
+
+\begin{definition}[{\cite[Definition~3.1]{FominZelevinsky-ClusterAlgebrasIV}}]
+The cluster algebra with \defn{principal coefficients} at~$\B_\circ$ is the cluster algebra~$\principalClusterAlgebra \eqdef \clusterAlgebra[\B_\circ][\coefficients_\circ]$ in~$\Q(x_1, \dots, x_n, p_1, \dots, p_n)$, where~$\coefficients_\circ = \{p_x\}_{x \in \cluster_\circ}$ are precisely the generators~$p_1, \dots, p_n$ of~$\Trop{n}$ relabeled by~$\cluster_\circ$.
+\end{definition}
+
+Cluster algebras with principal coefficients are $\Z^n$-graded (in the basis~$\{\omega_x\}_{x \in \cluster_\circ}$ of~$V$).
+The degree function~$\deg(\B_\circ,\cdot)$ on $\principalClusterAlgebra$ is obtained by setting
+\(
+\deg(\B_\circ,  x) \eqdef \fundamentalWeight_x
+\)
+and
+\(
+\deg(\B_\circ, p_x) \eqdef \sum_{y \in \cluster_\circ} -b_{yx} \fundamentalWeight_y
+\)
+for any $x\in\cluster_\circ$.
+This assignment makes all exchange relations and all cluster variables in~$\principalClusterAlgebra$ homogeneous~\cite{FominZelevinsky-ClusterAlgebrasIV} and it justifies the definition of the following family of integer vectors associated to cluster variables.
+
+\begin{definition}[\cite{FominZelevinsky-ClusterAlgebrasIV}]
+The \defn{$\b{g}$-vector}~$\gvector{\B_\circ}{x}$ of a cluster variable~$x \in \principalClusterAlgebra$ is its degree.
+We denote by $\gvectors{\B_\circ}{\seed} \eqdef \set{\gvector{\B_\circ}{x}}{x \in \seed}$ the set of $\b{g}$-vectors of the cluster variable in the seed~$\seed$ of~$\principalClusterAlgebra$.
+\end{definition}
+
+The next definition gives another family of integer vectors, introduced implicitly in~\cite{FominZelevinsky-ClusterAlgebrasIV}, that are relevant in the structure of~$\principalClusterAlgebra$.
+
+\begin{definition}
+Given a seed~$\seed$ in~$\principalClusterAlgebra$, the \defn{$\b{c}$-vector} of a cluster variable $x \in \seed$ is the vector
+\(
+\cvector{\B_\circ}{\seed}{x} \eqdef \sum_{y \in \cluster_\circ} c_{yx} \, \simpleRoot_y
+\)
+of exponents of~$p_x = \prod_{y \in \cluster_\circ} (p_y)^{c_{yx}}$.
+We denote by~$\cvectors{\B_\circ}{\seed} \eqdef \set{\cvector{\B_\circ}{\seed}{x}}{x \in \seed}$ the set of $\b{c}$-vectors of a seed~$\seed$.
+\end{definition}
+
+These two families of vectors are connected via the isomorphism~$x \mapsto x^\vee$ between the cluster complexes of~$\principalClusterAlgebra$ and~$\principalClusterAlgebra[\B_\circ^\vee]$ described above.
+
+\begin{theorem}[{\cite[Theorem~1.2]{NakanishiZelevinsky}}]
+\label{thm:duality}
+For any seed~$\seed$ of~$\principalClusterAlgebra$, let $\seed^\vee$ be its dual in $\principalClusterAlgebra[\B_\circ^\vee]$.
+Then the set of $\b{g}$-vectors~$\gvector{\B_\circ}{\seed}$ and the set of $\b{c}$-vectors~$\cvectors{\B_\circ^\vee}{\seed^\vee}$ form dual bases, that is
+\(
+{\bigdotprod{\gvector{\B_\circ}{x}}{\cvector{\B_\circ^\vee}{\seed^\vee}{y^\vee}} = \delta_{x=y}}
+\)
+for any two cluster variables~$x,y \in \seed$.
+\end{theorem}
+
+\para{The $\b{g}$-vector fan}
+%
+The following statement is well known.
+\vincent{Explain}
+
+\begin{theorem}
+\label{thm:gvectorFan}
+For any finite type exchange matrix~$\B_\circ$, the collection of cones \\[.1cm]
+\centerline{
+$\gvectorFan[\B_\circ] \eqdef \bigset{\R_{\ge0} \gvectors{\B_\circ}{\seed}}{\seed \text{ seed of } \principalClusterAlgebra},$
+} \\[.1cm]
+together with all their faces, forms a complete simplicial fan, called the \defn{$\b{g}$-vector fan} of~$\B_\circ$.
+\end{theorem}
+
+Moreover, this fan is known to be polytopal.
+
+\begin{theorem}[{\cite[Thm.~26]{HohlwegPilaudStella}}]
+\label{thm:gvectorFan}
+For any finite type exchange matrix~$\B_\circ$, the $\b{g}$-vector fan~$\gvectorFan[\B_\circ]$ is the normal fan of the polytope defined by...
+\vincent{TODO}
+\end{theorem}
+
+\para{Flips in the $\b{g}$-vector fan}
+
+\newpage
 The acyclic and simply-laced case was treated in~\cite{BazierMatteDouvilleMousavandThomasYildirim}.
@@
 This should be done using the Auslander-Reiten quiver to construct two cluster variables from a $c$-vector (see the next paragraph for the idea).
+
+%%%%%%%%%%%
 
@@
 Examples are illustrated in \cref{fig:nonkissingFans}.
+\vincent{Define $\b{c}$-vectors}
 
@@
 For any non-kissing finite gentle quiver~$\quiver$, the non-kissing fan~$\gvectorFan[\quiver]$ is the normal fan of the gentle associahedron~$\Asso[\quiver]$, defined as the intersection of the half-spaces~$\set{\b{x} \in \R^{Q_0}}{\dotprod{\gvector{\omega}}{\b{x}} \le \KN(\omega)}$ for all walks~$\omega \in \properWalks$.
+\vincent{Give the vertex description using $c$-vectors}
 \end{theorem}
@@
 For any gentle quiver~$\quiver$ with no self-kissing walk and any string~$\sigma \in \strings$, the walks~$\cc{\sigma}$ and~$\hh{\sigma}$ are exchangeable with distinguished substring~$\sigma$.
+\vincent{This is FALSE...}
 \end{proposition}
@@
 \end{figure}
+
+%%%%%%%%%%%
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Relations for~$\b{g}$-vectors in~$2$-Calabi--Yau triangulated categories}
-%%%%%
+
+%%%%%%%%%%%
+
 \subsection{Setting}\label{sect::setting}
@@
 
-%%%%
+%%%%%%%%%%%
+
 \subsection{Statement of the theorem}
@@
 
-%%%%
+%%%%%%%%%%%
+
 \subsection{Proof of Theorem \ref{theo::relations-g-vecteurs}}
@@
 
-%%%%
+%%%%%%%%%%%
+
 \subsection{Application to~$\b g$-vectors}\label{sect::applications-g-vectors}

### 2019-02-05 thirdPaper/draft/typeConeAssociahedra.tex

@@
 
-%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Relations for~$\b{g}$-vectors in finite type cluster algebras via~$2$-Calabi--Yau triangulated categories}
 
@@
 
+\subsection{Application to~$\b g$-vectors of cluster algebras of finite type}\label{sect::applications-g-vectors}
+
 We recall the following results and definition from \cite{DehyKeller,Palu}.

### 2019-02-08 thirdPaper/draft/typeConeAssociahedra.tex
Messed around with section 5.

@@
 \newcommand{\CC}{\phi}
+\newcommand{\proj}{\operatorname{proj}}
 
@@
 
+\begin{remark}
+ Examples of categories satisfying the above properties are
+ \begin{itemize}
+  \item $2$-Calabi--Yau triangulaged categories admitting a cluster-tilting object (see Section~\ref{sect::2CYTriangulated});
+  \item $2$-Calabi--Yau Frobenius exact categories (see Section~\ref{sect::2CYexact});
+  \item for any Artin algebra~$\Lambda$, the category~$K^{[-1,0]}(\proj \Lambda)$ of complexes of finitely generated projective~$\Lambda$-modules concentrated in degrees~$-1$ and~$0$, with morphisms considered up to homotopy (see Section~\ref{sect::Kbproj}).
+ \end{itemize}
+
+\end{remark}
+
 %%%%
@@
 %%%%
-\subsection{Application to~$\b g$-vectors of brick algebras}
+\subsection{Application to certain categories}
+
+%%
+\subsubsection{$2$-Calabi--Yau triangulated categories}\label{sect::2CYTriangulated}
+
+%%
+\subsubsection{$2$-Calabi--Yau Frobenius exact categories}\label{sect::2CYexact}
+
+%%
+\subsubsection{$2$-term complexes of projective modules}
+
+%%
+\subsubsection{Objects presented by a rigid object}
 
@@
 %%
-\subsubsection{A brick algebra}
+\subsubsection{Associative algebras}\label{sect::Kbproj}
 

### 2019-02-08 thirdPaper/draft/typeConeAssociahedra.tex
improve cluster algebras

--- 2019-02-05 thirdPaper/draft/typeConeAssociahedra.tex
@@
 \newcommandx{\rays}[1][1=R]{\b{#1}} % rays
-\newcommand{\gvector}[1]{\b{g}(#1)} % g-vector of the path #1
-\newcommand{\gvectors}[1]{\b{g}(#1)} % g-vectors of the paths #1
+\newcommand{\gvector}[1]{\b{g}(#1)} % g-vector of #1
+\newcommand{\gvectorFull}[2]{\b{g}_{#1}(#2)} % g-vector of #2 wrt #1
+\newcommand{\gvectors}[1]{\b{g}(#1)} % g-vectors of #1
+\newcommand{\gvectorsFull}[2]{\b{g}_{#1}(#2)} % g-vectors of #2 wrt #1
 \newcommandx{\gvectorFan}[1][1=\quiver]{\mathcal{F}(#1)} % g-vector fan
-\newcommand{\cvector}[3]{\mathbf{c}(#1, #3 \in #2)} % c-vector of the cluster variable #3 in the cluster #2 with respect to the initial cluster #1
-\newcommand{\cvectors}[2]{\mathbf{c}(#1, #2)} % c-vectors of the cluster #2 with respect to the initial cluster #1
+\newcommand{\cvector}[2]{\mathbf{c}(#2 \in #1)} % c-vector of the cluster variable #2 in the cluster #1
+\newcommand{\cvectorFull}[3]{\mathbf{c}_{#1}(#3 \in #2)} % c-vector of the cluster variable #3 in the cluster #2 with respect to the initial cluster #1
+\newcommand{\cvectors}[1]{\mathbf{c}(#1)} % c-vectors of the cluster #1
+\newcommand{\cvectorsFull}[2]{\mathbf{c}_{#1}(#2)} % c-vectors of the cluster #2 with respect to the initial cluster #1
 
@@
 \newcommand{\coefficients}{\mathrm{P}} % a coefficients tuple
+\newcommandx{\variables}[1][1=\clusterAlgebra]{\mathcal{V}(#1)} % all variables
 \newcommandx{\clusterAlgebra}[2][1=\B_\circ, 2=\coefficients_\circ]{\mathcal{A}\!\left(#1,#2\right)} % cluster algebra
@@
 
+\subsubsection{Cluster algebras and $\b{g}$-vector fans}
+
+We present some definitions and properties of finite type cluster algebras and their $\b{g}$-vector fans, following the presentation of~\cite{HohlwegPilaudStella}.
+
 \para{Cluster algebras}
@@
 \begin{definition}[\cite{FominZelevinsky-ClusterAlgebrasIV}]
-The \defn{$\b{g}$-vector}~$\gvector{\B_\circ}{x}$ of a cluster variable~$x \in \principalClusterAlgebra$ is its degree.
-We denote by $\gvectors{\B_\circ}{\seed} \eqdef \set{\gvector{\B_\circ}{x}}{x \in \seed}$ the set of $\b{g}$-vectors of the cluster variable in the seed~$\seed$ of~$\principalClusterAlgebra$.
+The \defn{$\b{g}$-vector}~$\gvector{x} = \gvectorFull{\B_\circ}(x)$ of a cluster variable~$x \in \principalClusterAlgebra$ is its degree.
+We denote by $\gvectors{\seed} = \gvectorFull{\B_\circ}(\seed) \eqdef \set{\gvectorFull{\B_\circ}(x)}{x \in \seed}$ the set of $\b{g}$-vectors of the cluster variable in the seed~$\seed$ of~$\principalClusterAlgebra$.
 \end{definition}
@@
 \(
-\cvector{\B_\circ}{\seed}{x} \eqdef \sum_{y \in \cluster_\circ} c_{yx} \, \simpleRoot_y
+\cvector{\seed}{x} = \cvectorFull{\B_\circ}{\seed}{x} \eqdef \sum_{y \in \cluster_\circ} c_{yx} \, \simpleRoot_y
 \)
 of exponents of~$p_x = \prod_{y \in \cluster_\circ} (p_y)^{c_{yx}}$.
-We denote by~$\cvectors{\B_\circ}{\seed} \eqdef \set{\cvector{\B_\circ}{\seed}{x}}{x \in \seed}$ the set of $\b{c}$-vectors of a seed~$\seed$.
+We denote by~$\cvectors{\seed} = \cvectorsFull{\B_\circ}{\seed} \eqdef \set{\cvectorFull{\B_\circ}{\seed}{x}}{x \in \seed}$ the set of $\b{c}$-vectors of a seed~$\seed$.
 \end{definition}
@@
 For any seed~$\seed$ of~$\principalClusterAlgebra$, let $\seed^\vee$ be its dual in $\principalClusterAlgebra[\B_\circ^\vee]$.
-Then the set of $\b{g}$-vectors~$\gvector{\B_\circ}{\seed}$ and the set of $\b{c}$-vectors~$\cvectors{\B_\circ^\vee}{\seed^\vee}$ form dual bases, that is
+Then the set of $\b{g}$-vectors~$\gvectorFull{\B_\circ}{\seed}$ and the set of $\b{c}$-vectors~$\cvectorsFull{\B_\circ^\vee}{\seed^\vee}$ form dual bases, that is
 \(
-{\bigdotprod{\gvector{\B_\circ}{x}}{\cvector{\B_\circ^\vee}{\seed^\vee}{y^\vee}} = \delta_{x=y}}
+{\bigdotprod{\gvectorFull{\B_\circ}{x}}{\cvectorFull{\B_\circ^\vee}{\seed^\vee}{y^\vee}} = \delta_{x=y}}
 \)
@@
 
-\para{The $\b{g}$-vector fan}
+\para{The $\b{g}$-vector fan and generalized associahedron}
 %
@@
 Moreover, this fan is known to be polytopal.
+More precisely, consider a vector~$\b{h} \in \R^{\variables}$ such that
+\[
+\b{h}_x + \b{h}_{x'} > \max \Big( \sum_{{y \in \cluster \cap \cluster', \; b_{xy} < 0}} -b_{xy} \, \b{h}_y \;,  \sum_{{y \in \cluster \cap \cluster', \; b_{xy} > 0}} b_{xy} \, \b{h}_y \Big).
+\]
+for any adjacent seeds~$(\B, \coefficients, \cluster)$ and~$(\B', \coefficients', \cluster')$ with~$\cluster \ssm \{x\} = \cluster' \ssm \{x'\}$.
+Such a vector~$\b{h}$ exists, see the discussion in~\cite[Prop.~28]{HohlwegPilaudStella}.
 
@@
 \label{thm:gvectorFan}
-For any finite type exchange matrix~$\B_\circ$, the $\b{g}$-vector fan~$\gvectorFan[\B_\circ]$ is the normal fan of the polytope defined by...
-\vincent{TODO}
+For any finite type exchange matrix~$\B_\circ$, the $\b{g}$-vector fan~$\gvectorFan[\B_\circ]$ is the normal fan of the \defn{$\B_\circ$-associahedron}~$\Asso{\B_\circ, \b{h}}$ defined equivalently as
+\begin{enumerate}[(i)]
+\item the convex hull of the points~$\sum_{x \in \seed} \b{h}_x \, \cvectorFull{\B_\circ^\vee}{\seed^\vee}{x^\vee}$ for all seeds~$\seed$ of~$\principalClusterAlgebra$, or
+\item the intersection of the halfspaces~$\set{\b{v} \in V^\vee}{\dotprod{\gvectorFull{\B_\circ}{x}}{\b{v}} \le \b{h}_x}$ for all cluster variables~$x$ of~$\principalClusterAlgebra$.
+\end{enumerate}
 \end{theorem}
@@
 \vincent{More explicit. TODO}
+\vincent{Do we still have these problems when the gentle algebra is brick and/or without oriented $2$-cycle?}
 \end{remark}

### 2019-02-08 thirdPaper/draft/typeConeAssociahedra.tex
improve Section 2

@@
 \newcommand{\gvector}[1]{\b{g}(#1)} % g-vector of #1
-\newcommand{\gvectorFull}[2]{\b{g}_{#1}(#2)} % g-vector of #2 wrt #1
+\newcommand{\gvectorFull}[2]{\b{g}(#1,#2)} % g-vector of #2 wrt #1
 \newcommand{\gvectors}[1]{\b{g}(#1)} % g-vectors of #1
-\newcommand{\gvectorsFull}[2]{\b{g}_{#1}(#2)} % g-vectors of #2 wrt #1
+\newcommand{\gvectorsFull}[2]{\b{g}(#1,#2)} % g-vectors of #2 wrt #1
 \newcommandx{\gvectorFan}[1][1=\quiver]{\mathcal{F}(#1)} % g-vector fan
 \newcommand{\cvector}[2]{\mathbf{c}(#2 \in #1)} % c-vector of the cluster variable #2 in the cluster #1
-\newcommand{\cvectorFull}[3]{\mathbf{c}_{#1}(#3 \in #2)} % c-vector of the cluster variable #3 in the cluster #2 with respect to the initial cluster #1
+\newcommand{\cvectorFull}[3]{\mathbf{c}(#1,#3 \in #2)} % c-vector of the cluster variable #3 in the cluster #2 with respect to the initial cluster #1
 \newcommand{\cvectors}[1]{\mathbf{c}(#1)} % c-vectors of the cluster #1
-\newcommand{\cvectorsFull}[2]{\mathbf{c}_{#1}(#2)} % c-vectors of the cluster #2 with respect to the initial cluster #1
+\newcommand{\cvectorsFull}[2]{\mathbf{c}(#1,#2)} % c-vectors of the cluster #2 with respect to the initial cluster #1
 
@@
 \newcommand{\ch}[1]{\cL#1\hR} % cohook - hook
+\newcommand{\distinguishedString}[2]{\mathsf{ds}(#1,#2)} % distinguished string
+\newcommand{\distinguishedSign}[2]{\varepsilon(#1,#2)} % distinguished sign
 
@@
 
+\tableofcontents
+
 We explain recent results of~\cite{BazierMatteDouvilleMousavandThomasYildirim}. Some advantages of our approach are:
@@
 \item The fan~$\Fan$ is the normal fan of the polytope~$P_\b{h} \eqdef \set{\b{x} \in \R^n}{\b{G}\b{x} \le \b{h}}$.
-\item For any two adjacent cones~$\R \rays$ and~$\R \rays'$ of~$\Fan$ with~$\rays \ssm \{\ray\} = \rays' \ssm \{\ray'\}$, we have
+\item For any two adjacent maximal cones~$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$ of~$\Fan$ with~$\rays \ssm \{\ray\} = \rays' \ssm \{\ray'\}$,
 \[
@@
 \begin{notation}
-For any two adjacent cones~$\R\rays$ and~$\R\rays'$ of~$\Fan$ with~$\rays \ssm \{\ray\} = \rays' \ssm \{\ray'\}$, we denote by~$\coefficient[{\ray[s]}][\rays][\rays']$ the coefficient of~$\ray[s]$ in the unique linear dependence between the rays of~$\rays \cup \rays'$, \ie such that
+For any two adjacent cones~$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$ of~$\Fan$ with~$\rays \ssm \{\ray\} = \rays' \ssm \{\ray'\}$, we denote by~$\coefficient[{\ray[s]}][\rays][\rays']$ the coefficient of~$\ray[s]$ in the unique linear dependence between the rays of~$\rays \cup \rays'$, \ie such that
 \[
@@
 \typeCone(\Fan) & \eqdef \set{\b{h} \in \R^N}{\Fan \text{ is the normal fan of } P_\b{h}} \\
-& = \Bigset{\b{h} \in \R^N}{\sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} > 0 \text{ for any adjacent cones~$\R\rays, \R\rays'$ of~$\Fan$}}.
+& = \Bigset{\b{h} \in \R^N}{\sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} > 0 \text{ for any adjacent maximal cones~$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$ of~$\Fan$}}.
 \end{align*}
@@
 \begin{definition}
-An \defn{extremal adjacent pair} of~$\Fan$ is a pair of adjacent cones~$\{\R\rays, \R\rays'\}$ of~$\Fan$ such that the corresponding inequality $\sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} > 0$ in the definition of the type cone~$\typeCone(\Fan)$ actually defines a facet of~$\typeCone(\Fan)$.
+An \defn{extremal adjacent pair} of~$\Fan$ is a pair of adjacent maximal cones~$\{\R_{\ge0}\rays, \R_{\ge0}\rays'\}$ of~$\Fan$ such that the corresponding inequality $\sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} > 0$ in the definition of the type cone~$\typeCone(\Fan)$ actually defines a facet of~$\typeCone(\Fan)$.
 \end{definition}
@@
 
-Two rays~$\ray$ and~$\ray'$ of~$\Fan$ are called \defn{compatible} if there are both contained in a cone of~$\Fan$ and \defn{exchangeable} if there are two adjacent cones~$\R\rays$ and~$\R\rays'$ of~$\Fan$ with ${\rays \ssm \{\ray\} = \rays' \ssm \{\ray'\}}$.
+Two rays~$\ray$ and~$\ray'$ of~$\Fan$ are called \defn{compatible} if there are both contained in a cone of~$\Fan$ and \defn{exchangeable} if there are two adjacent maximal cones~$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$ of~$\Fan$ with ${\rays \ssm \{\ray\} = \rays' \ssm \{\ray'\}}$.
 If~$\rays(\Fan)$ denotes the set of rays of~$\Fan$, a \defn{compatibility degree} for~$\Fan$ is a function~$\compatibilityDegree{-}{-}: \rays(\Fan) \times \rays(\Fan) \to \R$ such that
@@
 \]
-does not depend on the pair~$\{\rays, \rays'\}$ of adjacent cones of~$\Fan$ with $\rays \ssm \{\ray\} = \rays' \ssm \{\ray'\}$, but only on the pair of rays~$\ray, \ray'$.
+does not depend on the pair~$\{\rays, \rays'\}$ of adjacent maximal cones of~$\Fan$ with $\rays \ssm \{\ray\} = \rays' \ssm \{\ray'\}$, but only on the pair of rays~$\ray, \ray'$.
 This implies in particular that the rays~$\ray[s]$ for which~$\coefficient[{\ray[s]}][\rays][\rays'] \ne 0$ belong to~$\rays \cup \rays'$ for any pair~$\{\rays, \rays'\}$ of adjacent cones of~$\Fan$ with $\rays \ssm \{\ray\} = \rays' \ssm \{\ray'\}$.
@@
 
-\section{Applications to different generalizations of the associahedron}
+\section{Applications to three generalizations of the associahedron}
 \label{sec:applications}
 
-In this section, we study the type cones of complete simplicial fans arising as normal fans of three families of generalizations of the associahedron: the generalized associahedra of finite type cluster algebras~\cite{FominZelevinsky-ClusterAlgebrasI, FominZelevinsky-ClusterAlgebrasII, FominZelevinsky-ClusterAlgebrasIV, HohlwegLangeThomas}, the gentle associahedra~\cite{PaluPilaudPlamondon-nonkissing}, and the graph associahedra~\cite{CarrDevadoss, Postnikov, FeichtnerSturmfels, Zelevinsky}.
+In this section, we study the type cones of complete simplicial fans arising as normal fans of three families of generalizations of the associahedron: the generalized associahedra of finite type cluster algebras~\cite{FominZelevinsky-ClusterAlgebrasI, FominZelevinsky-ClusterAlgebrasII, FominZelevinsky-ClusterAlgebrasIV, HohlwegLangeThomas, HohlwegPilaudStella}, the gentle associahedra~\cite{PaluPilaudPlamondon-nonkissing}, and the graph associahedra~\cite{CarrDevadoss, Postnikov, FeichtnerSturmfels, Zelevinsky}.
 All these families contain the classical associahedra~$\Asso[n]$ constructed in~\cite{ShniderSternberg, Loday}.
@@
 
-From these linear dependencies, we obtain that the type cone of the fan~$\gvectorFan[n]$.
+From these linear dependencies, we obtain a redundant description of the type cone of the fan~$\gvectorFan[n]$.
 
@@
 
-\subsection{Generalized associahedra}
-
-We now extend the results of the previous section to the $\b{g}$-vector fan of any finite type cluster algebra with respect to any seed (acyclic or not).
+\subsection{Finite type cluster complexes and generalized associahedra}
+
+%We now extend the results of the previous section to the $\b{g}$-vector fan of any finite type cluster algebra with respect to any seed (acyclic or not).
 Cluster algebras were introduced by S.~Fomin and A.~Zelevinsky~\cite{FominZelevinsky-ClusterAlgebrasI} with motivation coming from total positivity and canonical bases.
@@
 These polytopal realizations were first constructed for bipartite initial seeds by F.~Chapoton, S.~Fomin and A.~Zelevinsky~\cite{ChapotonFominZelevinsky} using the $\b{d}$-vector fans of~\cite{FominZelevinsky-YSystems}, then for acyclic initial seeds by C.~Hohlweg, C.~Lange and H.~Thomas~\cite{HohlwegLangeThomas} using Cambrian lattices and fans of N.~Reading and D.~Speyer~\cite{Reading-CambrianLattices, ReadingSpeyer}, and revisited by S.~Stella~\cite{Stella}, and by V.~Pilaud and C.~Stump~\cite{PilaudStump-brickPolytope} via brick polytopes, and finally for arbitrary initial seeds by C.~Hohlweg, V.~Pilaud and S.~Stella~\cite{HohlwegPilaudStella}.
+More recently in~\cite{BazierMatteDouvilleMousavandThomasYildirim}, V.~Bazier-Matte, G.~Douville, K.~Mousavand, H.~Thomas and E.~Yildirim extended the construction of associahedra of~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} to acyclic seeds of simply laced finite type cluster algebras.
+Here, we extend the construction of~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} to any finite type (simply laced or not) cluster algebra with respect to any seed (acyclic or not) by showing that the type cone of the $\b{g}$-vector fan of any finite type cluster algebra is simplicial.
 
@@
 
-\begin{definition}[{\cite[Definition~2.11]{FominZelevinsky-ClusterAlgebrasIV}}]
+\begin{definition}[{\cite[Def.~2.11]{FominZelevinsky-ClusterAlgebrasIV}}]
 The (geometric type) \defn{cluster algebra} $\clusterAlgebra$ is the $\Z\Trop{m}$-subring of~$\Q(x_1, \dots, x_n, p_1, \dots, p_m)$ generated by all the cluster variables in all the seeds mutationally equivalent to an initial seed~$\seed_\circ = (\B_\circ, \coefficients_\circ, \cluster_\circ)$ with cluster variables~$\cluster_\circ = \{x_1, \dots, x_n\}$.
@@
 
-\begin{definition}[{\cite[Definition~3.1]{FominZelevinsky-ClusterAlgebrasIV}}]
+\begin{definition}[{\cite[Def.~3.1]{FominZelevinsky-ClusterAlgebrasIV}}]
 The cluster algebra with \defn{principal coefficients} at~$\B_\circ$ is the cluster algebra~$\principalClusterAlgebra \eqdef \clusterAlgebra[\B_\circ][\coefficients_\circ]$ in~$\Q(x_1, \dots, x_n, p_1, \dots, p_n)$, where~$\coefficients_\circ = \{p_x\}_{x \in \cluster_\circ}$ are precisely the generators~$p_1, \dots, p_n$ of~$\Trop{n}$ relabeled by~$\cluster_\circ$.
@@
 
-Cluster algebras with principal coefficients are $\Z^n$-graded (in the basis~$\{\omega_x\}_{x \in \cluster_\circ}$ of~$V$).
-The degree function~$\deg(\B_\circ,\cdot)$ on $\principalClusterAlgebra$ is obtained by setting
+Principal coefficients cluster algebras are $\Z^n$-graded (in the fundamental weight basis~$\{\omega_x\}_{x \in \cluster_\circ}$ of~$V$) for the degree function~$\deg(\B_\circ,\cdot)$ on $\principalClusterAlgebra$ is obtained by setting
 \(
@@
 for any $x\in\cluster_\circ$.
-This assignment makes all exchange relations and all cluster variables in~$\principalClusterAlgebra$ homogeneous~\cite{FominZelevinsky-ClusterAlgebrasIV} and it justifies the definition of the following family of integer vectors associated to cluster variables.
+%This assignment makes all exchange relations and all cluster variables in~$\principalClusterAlgebra$ homogeneous~\cite{FominZelevinsky-ClusterAlgebrasIV} and it justifies the definition of the following family of integer vectors associated to cluster variables.
 
 \begin{definition}[\cite{FominZelevinsky-ClusterAlgebrasIV}]
-The \defn{$\b{g}$-vector}~$\gvector{x} = \gvectorFull{\B_\circ}(x)$ of a cluster variable~$x \in \principalClusterAlgebra$ is its degree.
-We denote by $\gvectors{\seed} = \gvectorFull{\B_\circ}(\seed) \eqdef \set{\gvectorFull{\B_\circ}(x)}{x \in \seed}$ the set of $\b{g}$-vectors of the cluster variable in the seed~$\seed$ of~$\principalClusterAlgebra$.
+The \defn{$\b{g}$-vector}~$\gvector{x} = \gvectorFull{\B_\circ}{x}$ of a cluster variable~$x \in \principalClusterAlgebra$ is its degree.
+We denote by $\gvectors{\seed} = \gvectorFull{\B_\circ}{\seed} \eqdef \set{\gvectorFull{\B_\circ}{x}}{x \in \seed}$ the set of $\b{g}$-vectors of a seed~$\seed$.
 \end{definition}
@@
 \begin{definition}
-Given a seed~$\seed$ in~$\principalClusterAlgebra$, the \defn{$\b{c}$-vector} of a cluster variable $x \in \seed$ is the vector
+The \defn{$\b{c}$-vector} of a cluster variable $x$ in a seed~$\seed$ of~$\principalClusterAlgebra$ is the vector
 \(
@@
 
-\begin{theorem}[{\cite[Theorem~1.2]{NakanishiZelevinsky}}]
+\begin{theorem}[{\cite[Thm~1.2]{NakanishiZelevinsky}}]
 \label{thm:duality}
@@
 \label{thm:gvectorFan}
-For any finite type exchange matrix~$\B_\circ$, the $\b{g}$-vector fan~$\gvectorFan[\B_\circ]$ is the normal fan of the \defn{$\B_\circ$-associahedron}~$\Asso{\B_\circ, \b{h}}$ defined equivalently as
+For any finite type exchange matrix~$\B_\circ$, the $\b{g}$-vector fan~$\gvectorFan[\B_\circ]$ is the normal fan of the \defn{$\B_\circ$-associahedron}~$\Asso[\B_\circ, \b{h}]$ defined equivalently as
 \begin{enumerate}[(i)]
@@
 \newpage
-The acyclic and simply-laced case was treated in~\cite{BazierMatteDouvilleMousavandThomasYildirim}.
-Computer experiments indicate that the type cone is always simplicial for any seed (acyclic or not) in any finite type cluster algebra.
-While the case of acyclic seeds can be handled by representation theory~\cite{BazierMatteDouvilleMousavandThomasYildirim}, we have no proof at the moment for cyclic seeds.
-
+
+\begin{remark}
 One important observation is that it seems there is one extremal exchangeable pair for each positive $c$-vector, meaning that for each positive $c$-vector~$\beta$, there is precisely one extremal exchangeable pair~$\{x,x'\}$ of cluster variables for which the flip of~$x$ to~$x'$ (for any pair of clusters~$\{X,X'\}$ with~$X \ssm \{x\} = X' \ssm \{x'\}$) is in the direction of~$\beta$.
@@
 This should be done using the Auslander-Reiten quiver to construct two cluster variables from a $c$-vector (see the next paragraph for the idea).
+\end{remark}
+
+\newpage
 
@@
 
-\subsection{Gentle associahedra}
+\subsection{Non-kissing complexes and gentle associahedra}
 
@@
 
-\para{Non-kissing fan and gentle associahedron}
-%
+\para{$\b{g}$- and $\b{c}$-vectors}
+%
+We now define two families of vectors associated to walks in the non-kissing complex.
 Let~$(\b{e}_v)_{v \in Q_0}$ denote the canonical basis of~$\R^{Q_0}$.
 For a multiset~$V = \{\!\{v_1, \dots, v_k\}\!\}$ of~$Q_0$, we denote by $\multiplicityVector_V \eqdef \sum_{i \in [k]} \b{e}_{v_i}$.
-The \defn{$\b{g}$-vector} of a walk~$\omega$ is the vector~$\gvector{\omega} \in \R^{Q_0}$ defined by~$\gvector{\omega} \eqdef \multiplicityVector_{\peaks{\omega}} - \multiplicityVector_{\deeps{\omega}}$.
+
+\begin{definition}[{\cite[Def.~{4.8}]{PaluPilaudPlamondon-nonkissing}}]
+The \defn{$\b{g}$-vector} of a walk~$\omega$ is~$\gvector{\omega} \eqdef \multiplicityVector_{\peaks{\omega}} - \multiplicityVector_{\deeps{\omega}}$.
+We denote by~$\gvectors{F} \eqdef \set{\gvector{\omega}}{\omega \in F}$ the set of $\b{g}$-vectors of a facet~$F$.
+\end{definition}
+
 Note that by definition, the $\gvector{\omega} = 0$ for a straight walk~$\omega$.
-We also define~$\gvectors{F} \eqdef \set{\gvector{\omega}}{\omega \in F}$ for a face~$F$ of~$\NKC$.
-These vectors support a complete simplicial fan realization of the non-kissing complex complex.
+
+To define the other family of vectors, we need to recall the notion of distinguished substring of a walk defined in~\cite[Def.~2.25]{PaluPilaudPlamondon-nonkissing}.
+Consider an arrow~$\alpha \in Q_1$ contained in two distinct walks~$\omega, \omega'$ of a non-kissing facet~$F \in \NKC$, and let~$\sigma$ denote the common substring of~$\omega$ and~$\omega'$.
+We write~$\omega \prec_\alpha \omega'$ if $\omega$ enters and/or exits~$\sigma$ with arrows in the direction pointed by~$\alpha$, while $\omega'$ enters and/or exits~$\sigma$ with arrows in the direction opposite to~$\alpha$.
+The \defn{distinguished walk} of the non-kissing facet~$F \in \NKC$ at the arrow~$\alpha$ is the maximum walk of~$F$ for~$\prec_\alpha$.
+The \defn{distinguished arrows} of the walk~$\omega$ in the non-kissing facet~$F \in \NKC$ are the arrow where~$\omega$ is the distinguished walk.
+It is shown in~\cite[Prop.~2.28]{PaluPilaudPlamondon-nonkissing} that each bending walk in a non-kissing facet has precisely two distinguished arrows, pointing in opposite directions.
+The \defn{distinguished substring}~$\distinguishedString{\omega}{F}$ of the walk~$\omega$ in the non-kissing facet~$F \in \NKC$ is the substring located between its two distinguished arrows.
+
+\begin{definition}[{\cite[Def.~{4.11}]{PaluPilaudPlamondon-nonkissing}}]
+The \defn{$\b{c}$-vector} of a walk~$\omega$ in a non-kissing facet~${F \in \NKC}$ is~${\cvector{F}{\omega} \eqdef \distinguishedSign{\omega}{F} \, \multiplicityVector_{\distinguishedString{\omega}{F}}}$, where~$\distinguishedSign{\omega}{F} \in \{-1,1\}$ is positive if~${\distinguishedString{\omega}{F} \in \Sigma_\top(\omega)}$ and negative if~${\distinguishedString{\omega}{F} \in \Sigma_\bottom(\omega)}$.
+We denote by~$\cvectors{F} \eqdef \set{\cvector{F}{\omega}}{\omega \in F}$ the set of $\b{c}$-vectors~of~a~facet~$F$.
+\end{definition}
+
+The $\b{g}$- and $\b{c}$-vectors also form dual bases.
+
+\begin{proposition}
+\label{prop:gvectorscvectorsDualBases}
+For any non-kissing facet~$F \in \NKC$, the set of $\b{g}$-vectors~$\gvectors{F}$ and the set of $\b{c}$-vectors~$\cvectors{F}$ form dual bases, that is
+\(
+{\bigdotprod{\gvector{\omega}}{\cvector{F}{\omega'}} = \delta_{\omega=\omega'}}
+\)
+for any two walks~$\omega, \omega' \in F$.
+\end{proposition}
+
+\para{Non-kissing fan and gentle associahedron}
+%
+The $\b{g}$-vectors support a complete simplicial fan realization of the non-kissing complex complex.
 Examples are illustrated in \cref{fig:nonkissingFans}.
-\vincent{Define $\b{c}$-vectors}
 
@@
 \begin{theorem}[{\cite[Thm.~4.27]{PaluPilaudPlamondon-nonkissing}}]
-For any non-kissing finite gentle quiver~$\quiver$, the non-kissing fan~$\gvectorFan[\quiver]$ is the normal fan of the gentle associahedron~$\Asso[\quiver]$, defined as the intersection of the half-spaces~$\set{\b{x} \in \R^{Q_0}}{\dotprod{\gvector{\omega}}{\b{x}} \le \KN(\omega)}$ for all walks~$\omega \in \properWalks$.
-\vincent{Give the vertex description using $c$-vectors}
+For any non-kissing finite gentle quiver~$\quiver$, the non-kissing fan~$\gvectorFan[\quiver]$ is the normal fan of the \defn{gentle associahedron}~$\Asso[\quiver]$ defined equivalently as:
+\begin{enumerate}[(i)]
+\item the convex hull of the points~$\sum_{\omega \in F} \KN(\omega) \, \cvector{F}{\omega}$ for all facets~${F \in \NKC}$,~or
+\item the intersection of the halfspaces~$\bigset{\b{x} \in \R^{Q_0}}{\dotprod{\gvector{\omega}}{\b{x}} \le \KN(\omega)}$ for all walks~$\omega$ on~$\bar Q$.
+\end{enumerate}
 \end{theorem}
@@
 We denote by~$\distinguishableStrings$ the set of distinguishable strings of~$\quiver$.
+\vincent{Clean that}
 
@@
 
-\subsection{Graph associahedra}
+\subsection{Graphical nested complexes and graph associahedra}
 

### 2019-02-08 thirdPaper/draft/typeConeAssociahedra.tex
figure cluster fans

@@
 \usepackage[T1]{fontenc}
-\usepackage{enumerate, amsmath, amsfonts, amssymb, amsthm, mathrsfs, wasysym, graphics, graphicx, xcolor, url, hyperref, hypcap, xargs, multicol, pdflscape, multirow, hvfloat, array, ae, aecompl, pifont, mathtools, a4wide, float, blkarray}
+\usepackage{enumerate, amsmath, amsfonts, amssymb, amsthm, mathrsfs, wasysym, graphics, graphicx, xcolor, url, hyperref, hypcap, xargs, multicol, pdflscape, multirow, hvfloat, array, ae, aecompl, pifont, mathtools, a4wide, float, blkarray, overpic}
 \usepackage[noabbrev,capitalise]{cleveref}
@@
 \vincent{Explain}
+Examples are illustrated in \cref{fig:clusterFans}.
+
+\begin{figure}[h]
+	\capstart
+	%\centerline{\includegraphics[scale=.45]{clusterFans}}
+	\centerline{
+	\begin{overpic}[scale=.45]{clusterFans}
+	\put(-19,30){$\left[\begin{array}{@{}c@{\;}c@{\;}c@{}} 0 & -1 & 1 \\ 1 & 0 & -1 \\ -1 & 1 & 0 \end{array}\right]$}
+	\put(98,30){$\left[\begin{array}{@{}c@{\;}c@{\;}c@{}} 0 & -1 & 2 \\ 1 & 0 & -2 \\ -1 & 1 & 0 \end{array}\right]$}
+	\end{overpic}
+	}
+  \caption{Two $\b{g}$-vector fans~$\gvectorFan[\B_\circ]$ for the type~$A_3$~(left) and type~$C_3$~(right) cyclic initial exchange matrices.
+As the fans are $3$-dimensional, we intersect them with the sphere and stereographically project them from the direction~$(-1,-1,-1)$.
+Illustration from~\cite{HohlwegPilaudStella}.}
+	\label{fig:clusterFans}
+\end{figure}
 

### 2019-02-08 thirdPaper/draft/typeConeAssociahedra.tex
Removed empty Section 3, added intro to new section 3

--- 2019-02-08 thirdPaper/draft/typeConeAssociahedra.tex
@@
 \newcommandx{\rays}[1][1=R]{\b{#1}} % rays
-\newcommand{\gvector}[1]{\b{g}(#1)} % g-vector of #1
-\newcommand{\gvectorFull}[2]{\b{g}_{#1}(#2)} % g-vector of #2 wrt #1
-\newcommand{\gvectors}[1]{\b{g}(#1)} % g-vectors of #1
-\newcommand{\gvectorsFull}[2]{\b{g}_{#1}(#2)} % g-vectors of #2 wrt #1
+\newcommand{\gvector}[1]{\b{g}(#1)} % g-vector of the path #1
+\newcommand{\gvectors}[1]{\b{g}(#1)} % g-vectors of the paths #1
 \newcommandx{\gvectorFan}[1][1=\quiver]{\mathcal{F}(#1)} % g-vector fan
-\newcommand{\cvector}[2]{\mathbf{c}(#2 \in #1)} % c-vector of the cluster variable #2 in the cluster #1
-\newcommand{\cvectorFull}[3]{\mathbf{c}_{#1}(#3 \in #2)} % c-vector of the cluster variable #3 in the cluster #2 with respect to the initial cluster #1
-\newcommand{\cvectors}[1]{\mathbf{c}(#1)} % c-vectors of the cluster #1
-\newcommand{\cvectorsFull}[2]{\mathbf{c}_{#1}(#2)} % c-vectors of the cluster #2 with respect to the initial cluster #1
+\newcommand{\cvector}[3]{\mathbf{c}(#1, #3 \in #2)} % c-vector of the cluster variable #3 in the cluster #2 with respect to the initial cluster #1
+\newcommand{\cvectors}[2]{\mathbf{c}(#1, #2)} % c-vectors of the cluster #2 with respect to the initial cluster #1
 
@@
 \newcommand{\coefficients}{\mathrm{P}} % a coefficients tuple
-\newcommandx{\variables}[1][1=\clusterAlgebra]{\mathcal{V}(#1)} % all variables
 \newcommandx{\clusterAlgebra}[2][1=\B_\circ, 2=\coefficients_\circ]{\mathcal{A}\!\left(#1,#2\right)} % cluster algebra
@@
 
-\subsubsection{Cluster algebras and $\b{g}$-vector fans}
-
-We present some definitions and properties of finite type cluster algebras and their $\b{g}$-vector fans, following the presentation of~\cite{HohlwegPilaudStella}.
-
 \para{Cluster algebras}
@@
 \begin{definition}[\cite{FominZelevinsky-ClusterAlgebrasIV}]
-The \defn{$\b{g}$-vector}~$\gvector{x} = \gvectorFull{\B_\circ}(x)$ of a cluster variable~$x \in \principalClusterAlgebra$ is its degree.
-We denote by $\gvectors{\seed} = \gvectorFull{\B_\circ}(\seed) \eqdef \set{\gvectorFull{\B_\circ}(x)}{x \in \seed}$ the set of $\b{g}$-vectors of the cluster variable in the seed~$\seed$ of~$\principalClusterAlgebra$.
+The \defn{$\b{g}$-vector}~$\gvector{\B_\circ}{x}$ of a cluster variable~$x \in \principalClusterAlgebra$ is its degree.
+We denote by $\gvectors{\B_\circ}{\seed} \eqdef \set{\gvector{\B_\circ}{x}}{x \in \seed}$ the set of $\b{g}$-vectors of the cluster variable in the seed~$\seed$ of~$\principalClusterAlgebra$.
 \end{definition}
@@
 \(
-\cvector{\seed}{x} = \cvectorFull{\B_\circ}{\seed}{x} \eqdef \sum_{y \in \cluster_\circ} c_{yx} \, \simpleRoot_y
+\cvector{\B_\circ}{\seed}{x} \eqdef \sum_{y \in \cluster_\circ} c_{yx} \, \simpleRoot_y
 \)
 of exponents of~$p_x = \prod_{y \in \cluster_\circ} (p_y)^{c_{yx}}$.
-We denote by~$\cvectors{\seed} = \cvectorsFull{\B_\circ}{\seed} \eqdef \set{\cvectorFull{\B_\circ}{\seed}{x}}{x \in \seed}$ the set of $\b{c}$-vectors of a seed~$\seed$.
+We denote by~$\cvectors{\B_\circ}{\seed} \eqdef \set{\cvector{\B_\circ}{\seed}{x}}{x \in \seed}$ the set of $\b{c}$-vectors of a seed~$\seed$.
 \end{definition}
@@
 For any seed~$\seed$ of~$\principalClusterAlgebra$, let $\seed^\vee$ be its dual in $\principalClusterAlgebra[\B_\circ^\vee]$.
-Then the set of $\b{g}$-vectors~$\gvectorFull{\B_\circ}{\seed}$ and the set of $\b{c}$-vectors~$\cvectorsFull{\B_\circ^\vee}{\seed^\vee}$ form dual bases, that is
+Then the set of $\b{g}$-vectors~$\gvector{\B_\circ}{\seed}$ and the set of $\b{c}$-vectors~$\cvectors{\B_\circ^\vee}{\seed^\vee}$ form dual bases, that is
 \(
-{\bigdotprod{\gvectorFull{\B_\circ}{x}}{\cvectorFull{\B_\circ^\vee}{\seed^\vee}{y^\vee}} = \delta_{x=y}}
+{\bigdotprod{\gvector{\B_\circ}{x}}{\cvector{\B_\circ^\vee}{\seed^\vee}{y^\vee}} = \delta_{x=y}}
 \)
@@
 
-\para{The $\b{g}$-vector fan and generalized associahedron}
+\para{The $\b{g}$-vector fan}
 %
@@
 Moreover, this fan is known to be polytopal.
-More precisely, consider a vector~$\b{h} \in \R^{\variables}$ such that
-\[
-\b{h}_x + \b{h}_{x'} > \max \Big( \sum_{{y \in \cluster \cap \cluster', \; b_{xy} < 0}} -b_{xy} \, \b{h}_y \;,  \sum_{{y \in \cluster \cap \cluster', \; b_{xy} > 0}} b_{xy} \, \b{h}_y \Big).
-\]
-for any adjacent seeds~$(\B, \coefficients, \cluster)$ and~$(\B', \coefficients', \cluster')$ with~$\cluster \ssm \{x\} = \cluster' \ssm \{x'\}$.
-Such a vector~$\b{h}$ exists, see the discussion in~\cite[Prop.~28]{HohlwegPilaudStella}.
 
@@
 \label{thm:gvectorFan}
-For any finite type exchange matrix~$\B_\circ$, the $\b{g}$-vector fan~$\gvectorFan[\B_\circ]$ is the normal fan of the \defn{$\B_\circ$-associahedron}~$\Asso{\B_\circ, \b{h}}$ defined equivalently as
-\begin{enumerate}[(i)]
-\item the convex hull of the points~$\sum_{x \in \seed} \b{h}_x \, \cvectorFull{\B_\circ^\vee}{\seed^\vee}{x^\vee}$ for all seeds~$\seed$ of~$\principalClusterAlgebra$, or
-\item the intersection of the halfspaces~$\set{\b{v} \in V^\vee}{\dotprod{\gvectorFull{\B_\circ}{x}}{\b{v}} \le \b{h}_x}$ for all cluster variables~$x$ of~$\principalClusterAlgebra$.
-\end{enumerate}
+For any finite type exchange matrix~$\B_\circ$, the $\b{g}$-vector fan~$\gvectorFan[\B_\circ]$ is the normal fan of the polytope defined by...
+\vincent{TODO}
 \end{theorem}
@@
 \vincent{More explicit. TODO}
-\vincent{Do we still have these problems when the gentle algebra is brick and/or without oriented $2$-cycle?}
 \end{remark}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Relations for~$\b{g}$-vectors in~$2$-Calabi--Yau triangulated categories}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section{Relations for~$\b{g}$-vectors in finite type cluster algebras via~$2$-Calabi--Yau triangulated categories}
+
+In~\cite{Auslander1984}, M.~Auslander showed that the relations in the Grothendieck group of an Artin algebra are generated by the ones given by almost-split sequences precisely when the algebra is of finite representation type.
+Inspired by this result, we will show that a similar statement holds (Theorem~\ref{theo::relations-g-vecteurs}) for the~$\b g$-vectors (or indices) of objects in a~$2$-Calabi--Yau triangulated category.
 
@@
 %%
-\subsubsection{$2$-term complexes of projective modules}
+\subsubsection{$2$-term complexes of projective modules}\label{sect::Kbproj}
 
@@
 %%
-\subsubsection{Associative algebras}\label{sect::Kbproj}
+\subsubsection{Associative algebras}
 

### 2019-02-08 thirdPaper/draft/typeConeAssociahedra.tex
Minor changes

--- 2019-02-08 thirdPaper/draft/typeConeAssociahedra.tex
@@
 \begin{enumerate}[(i)]
-\item For any non-kissing facet~$F, F'$ of~$\NKC$ with~$F \ssm \{\omega\} = f' \ssm \{\omega'\}$, there exists a unique maximal common substring~$\sigma$ of~$\omega$ and~$\omega'$ that decomposes~$\omega = \rho \sigma \tau$ and~$\omega' = \rho' \sigma \tau'$ such that the facets~$F$ and~$F'$ both contain the walks~$\mu \eqdef \rho' \sigma \tau$ and~$\nu \eqdef \rho \sigma \tau'$.
-\item The substring~$\sigma$ and thus the walks~$\mu$ and~$\nu$ actually depend on the exchangeable walks~$\omega$ and~$\omega'$, not on the adjacent non-kissing facet~$F $ and~$F'$.
+\item For any non-kissing facet~$F, F'$ of~$\NKC$ with~$F \ssm \{\omega\} = F' \ssm \{\omega'\}$, there exists a unique maximal common substring~$\sigma$ of~$\omega$ and~$\omega'$ that decomposes~$\omega = \rho \sigma \tau$ and~$\omega' = \rho' \sigma \tau'$ such that the facets~$F$ and~$F'$ both contain the walks~$\mu \eqdef \rho' \sigma \tau$ and~$\nu \eqdef \rho \sigma \tau'$.
+\item The substring~$\sigma$ and thus the walks~$\mu$ and~$\nu$ only depend on the exchangeable walks~$\omega$ and~$\omega'$, not on the adjacent non-kissing facets~$F $ and~$F'$.
+\yann{This needs more assumptions.  Move to another proposition.}
 \item Moreover, the linear dependence between the $\b{g}$-vectors of~$F \cup F'$ is given by
@@
 
-The quivers of this family is particularly well-behaved: they avoid all pathologies of \cref{rem:exchangeablePairsNKC} and we will prove that the type cone of their non-kissing fan happens to be simplicial.
+The quivers of this family are particularly well-behaved: they avoid all pathologies of \cref{rem:exchangeablePairsNKC} and we will prove that the type cone of their non-kissing fan happens to be simplicial.\pg{Need to exclude two-cycles, else false.}
 Note that this family already contains a lot of relevant examples, including:
@@
 If the walks~$\omega$ and~$\omega'$ are non-self-kissing and exchangeable, then they form the unique extremal exchangeable pair directed by~$\sigma$.
-These extremal exchangeable pairs correspond to meshes of the Auslander-Reiten quiver.
+These extremal exchangeable pairs correspond to meshes of the Auslander-Reiten quiver.\pg{The conjecture is the word ``unique''.}
 \item Otherwise, $\sigma$ is the direction to one or more extremal exchangeable pairs obtained by moving further in the Auslander-Reiten quiver (this is really unclear at the moment).
@@
  \[
-  X\xrightarrow{} E \xrightarrow{} Y \xrightarrow{h} \susp X \quad \textrm{and} \quad Y\xrightarrow{} E' \xrightarrow{} X \xrightarrow{h'} \susp Y
- \]
- be triangles with~$h$ and~$h'$ non-zero (these triangles are unique up to isomorphism).
-Then~$\CC(Y)$ is obtained by performing a positive mutation on~$\CC(X)$ in some seed if and only if~$h\in (\susp T)$.
+  X\xrightarrow{} E \xrightarrow{} Y \xrightarrow{h} \susp X 
+ \]
+ be triangle with~$h$ non-zero (this triangle is unique up to isomorphism).  Then~$\CC(Y)$ is obtained by performing a positive mutation on~$\CC(X)$ in some seed if and only if~$h\in (\susp T)$.
  \begin{proof}

### 2019-02-08 thirdPaper/draft/typeConeAssociahedra.tex
Started Section 4.4.3

@@
 \subsubsection{$2$-term complexes of projective modules}\label{sect::Kbproj}
+Let~$\Lambda$ be an Artin algebra.
+Then the homotopy category~$K^b(\proj \Lambda)$ is a triangulated category, and its full subcategory~$K^{[-1,0]}(\proj \Lambda)$ of complexes concentrated in degrees~$-1$ and~$0$ is closed under extensions.
+Therefore, it is an extriangulated category.
+
+We know from~\cite{} that the indecomposable objects of~$K^{[-1,0]}(\proj \Lambda)$ are in natural bijection with the indecomposable~$\Lambda$-modules and with the shifted indecomposable projective~$\Lambda$-modules.
+Thus is has finitely many isomorphism classes of indecomposable objects if and only if~$\Lambda$ is representation-finite.
+This gives a setting in which to apply Theorem~\ref{}.
+
+\pg{Add introducing paragraph}
+
+\begin{theorem}
+ Let~$\Lambda$ be a brick algebra.
+Then the almost-split conflations of~$K^{[-1,0]}(\proj \Lambda)$ are mutation conflations if and only if for any indecomposable~$\Lambda$-module~$M$, the space~$\Hom{\Lambda}(M, \tau^2 M)$ vanishes.
+\end{theorem}
+\begin{proof}
+ \pg{TO DO}
+\end{proof}
 

### 2019-02-11 thirdPaper/draft/typeConeAssociahedra.tex
Corrected some mistakes in Section 3.

@@
 
+Before we can prove Theorem~\ref{theo::relations-g-vecteurs}, we need to recall the following results and definition from \cite{DehyKeller,Palu}.
+
+\begin{proposition}
+ Let~$X$ be an object of~$\cat$. Then there exists a triangle
+ \[
+  T_1^X \to T^0_X \to X \to \susp T_1^X
+ \]
+ with~$T_1^X$ and~$T_0^X$ in~$\add(T)$.
+
+\end{proposition}
+
+\begin{definition}
+ The \defn{index} of an object~$X$ is the element
+ \[
+  \ind_T(X) := [T_0^X] - [T_1^X] \in \Ksp(\add(T)).
+ \]
+\end{definition}
+
+The notion of index is very close to the definition of the map~$\b g:\Ksp(\cat)\to \Kg(\cat)$ of Definition~\ref{defi::grothendieck-group}.  The link is given by the following result.
+
+\begin{proposition}[\cite{Palu}]
+ Let~$X\xrightarrow{} Y \xrightarrow{} Z \xrightarrow{h} \susp X$ be a triangle.
+ Then
+ \[
+  \ind_T(X) + \ind_T(Z) - \ind_T(Y) = 0
+ \]
+ if and only if~$h\in (\susp T)$.
+\end{proposition}
+
+\begin{corollary}\label{coro::grothendieck-g-vectors}
+ There is an isomorphism~$\phi:\Kg(\cat) \to \Ksp(\add(T))$ such that~$\ind_T = \phi\circ \b g$.  In particular,~$\Kg(\cat)$ is a free abelian group generated by the~$[T_i]$.
+\end{corollary}
+
+We can now begin the proof of Theorem~\ref{theo::relations-g-vecteurs}
+
 \begin{lemma}\label{lemm::bilinear-form-suspention-T}
@@
  \[
-  \lambda_A = \langle \ell_A, x \rangle = \langle x, r_A \rangle.
+  \lambda_A = \frac{\langle \ell_A, x \rangle}{\langle \ell_A, A \rangle} = \frac{\langle x, r_A \rangle}{\langle A, r_A \rangle}.
  \]
@@
  \[
-  \langle \ell_B, x \rangle = \langle \ell_B, \sum_{A\in \ind(\cat)} \lambda_A [A] \rangle = \sum_{A\in \ind{\cat}} \lambda_A \langle \ell_B, [A] \rangle = \lambda_A.
- \]
- The equality~$\lambda_A = \langle x, r_A\rangle$ is proved in a similar way.
+  \langle \ell_B, x \rangle = \langle \ell_B, \sum_{A\in \ind(\cat)} \lambda_A [A] \rangle = \sum_{A\in \ind{\cat}} \lambda_A \langle \ell_B, [A] \rangle = \lambda_B \langle \ell_B, [B] \rangle.
+ \]
+ The equality~$\lambda_A = \frac{\langle x, r_A \rangle}{\langle A, r_A \rangle}$ is proved in a similar way.
 \end{proof}
@@
  \[
-  x = \sum_{A\in \ind(\cat)\setminus \add(\susp T)} \langle \ell_A, x \rangle + \sum_{i=1}^n \lambda_{\susp T_i} [\susp T_i] = \sum_{i=1}^n \lambda_{\susp T_i} [\susp T_i].
+  x = \sum_{A\in \ind(\cat)\setminus \add(\susp T)} \frac{\langle \ell_A, x \rangle}{\langle \ell_A, A \rangle}[A] + \sum_{i=1}^n \lambda_{\susp T_i} [\susp T_i] = \sum_{i=1}^n \lambda_{\susp T_i} [\susp T_i].
  \]
@@
 By Lemma~\ref{lemm::test-susp-T}, this implies that~$z\in \Ksp(\add(\susp T))$.
-Since~$z\in \ker(\b g)$ and since~$\b g$ is injective on~$\Ksp(\add (\susp T))$, we get that~$z=0$.
+Since~$z\in \ker(\b g)$ and since~$\b g$ is injective on~$\Ksp(\add (\susp T))$ by Corollary~\ref{coro::grothendieck-g-vectors}, we get that~$z=0$.
 This finishes the proof.
-\pg{We need a lemma saying that g is injective on K(add(susp T))}
 \end{proof}
@@
 \subsection{Application to~$\b g$-vectors of cluster algebras of finite type}\label{sect::applications-g-vectors}
-
-We recall the following results and definition from \cite{DehyKeller,Palu}.
-
-\begin{proposition}
- Let~$X$ be an object of~$\cat$. Then there exists a triangle
- \[
-  T_1^X \to T^0_X \to X \to \susp T_1^X
- \]
- with~$T_1^X$ and~$T_0^X$ in~$\add(T)$.
-
-\end{proposition}
-
-\begin{definition}
- The \defn{index} of an object~$X$ is the element
- \[
-  \ind_T(X) := [T_0^X] - [T_1^X] \in \Ksp(\add(T)).
- \]
-\end{definition}
-
-The notion of index is very close to the definition of the map~$\b g:\Ksp(\cat)\to \Kg(\cat)$ of Definition~\ref{defi::grothendieck-group}.  The link is given by the following result.
-
-\begin{proposition}[\cite{Palu}]
- Let~$X\xrightarrow{} Y \xrightarrow{} Z \xrightarrow{h} \susp X$ be a triangle.
- Then
- \[
-  \ind_T(X) + \ind_T(Z) - \ind_T(Y) = 0
- \]
- if and only if~$h\in (\susp T)$.
-\end{proposition}
-
-\begin{corollary}
- There is an isomorphism~$\phi:\Kg(\cat) \to \Ksp(\add(T))$ such that~$\ind_T = \phi\circ \b g$.  In particular,~$\Kg(\cat)$ is a free abelian group generated by the~$[T_i]$.
-\end{corollary}
 

### 2019-02-11 thirdPaper/draft/typeConeAssociahedra.tex
More with Section 3

@@
 \]
-\begin{proposition}[\cite{BuanMarshReiten, KellerReiten}]
+\begin{proposition}[\cite{BuanMarshReiten, KellerReiten}]\label{prop::functor-F}
  The functor~$F$ induces an equivalence of~$\field$-linear categories
@@
 
-\begin{proposition}[]\pg{Cite Happel}
+\begin{proposition}[Proposition I.2.3 of~\cite{ReitenVandenbergh}]
  Any triangulated category admitting a Serre functor has almost-split triangles.  In particular, any~$2$-Calabi--Yau triangulated category has almost-split triangles.
@@
 
-We can finally state the main theorem of this section. \pg{recall Auslander}
+We can finally state the main theorem of this section, which is an analogue of the main result of~\cite{Auslander1984}.
 
@@
  \]
- Applying now the functor~$\Hom{\Lambda}(-, FB)$, we get an exact sequence
- \[
-  0 \xrightarrow{} \Hom{\Lambda}(F\susp^{-1} A, FB) \xrightarrow{} \Hom{\Lambda}(FE, FB) \xrightarrow{Ff^*} \Hom{\Lambda}(FA, FB) \xrightarrow{} \coker(Ff^*) \xrightarrow{} 0
- \]
- If~$B\ncong A$, then the definition of an almost-split triangle implies that~$Ff^*$ is surjective.
-\pg{add an exact sequence here; image of Ffstar is non-invertible elements} Thus~$\coker(Ff^*) = 0$, and by additivity of the dimension in exact sequences, we get that~$\langle \ell_A, B \rangle =0$.
-
- If~$B\cong A$, then~$\coker(Ff^*)$ is isomorphic to the residue field of~$\End{\Lambda}(FA)$, which is isomorphic to the residue field~$\field_A$ of~$A$.
+ Applying now the functors~$\cat(-, B)$ and~$\Hom{\Lambda}(-, FB)$, we get a commutative diagram whose rows are exact sequences and whose vertical maps are surjective by Proposition~\ref{prop::functor-F}.
+ \[
+  \xymatrix{ & \cat(\susp^{-1} A, B)\ar[r]\ar@{->>}[d] & \cat(E, B)\ar[r]^{f^*}\ar@{->>}[d] & \cat(A,B)\ar[r]\ar@{->>}[d] & \coker(f^*)\ar[r]\ar@{->>}[d] & 0 \\
+  0 \ar[r] & \Hom{\Lambda}(F\susp^{-1} A, FB)\ar[r] & \Hom{\Lambda}(FE, FB)\ar[r]^{Ff^*} & \Hom{\Lambda}(FA, FB)\ar[r] & \coker(Ff^*)\ar[r] & 0.
+  }
+ \]
+
+ If~$B\ncong A$, then the definition of an almost-split triangle implies that~$f^*$ is surjective.
+Thus~$\coker(f^*)=0$, so that~$\coker(Ff^*) = 0$, and by additivity of the dimension in exact sequences, we get that~$\langle \ell_A, B \rangle =0$.
+
+ If~$B\cong A$, then~$\coker(f^*)$ is isomorphic to the residue field~$\field_A$ of~$\cat(A,A)$.
+Since~$A$ is not in~$\add(\susp T)$, the ideal of endomorphisms of~$A$ factoring through an object of~$\add(\susp T)$ is contained in the maximal ideal of~$\cat(A,A)$.
+Therefore, the rightmost morphism in the commutative diagram is an isomorphism, so~$\coker(Ff^*)$ is isomorphic to~$\field_A$.
 \end{proof}

### 2019-02-11 thirdPaper/draft/typeConeAssociahedra.tex
problems files
restore all my changes

@@
 \newcommandx{\rays}[1][1=R]{\b{#1}} % rays
-\newcommand{\gvector}[1]{\b{g}(#1)} % g-vector of the path #1
-\newcommand{\gvectors}[1]{\b{g}(#1)} % g-vectors of the paths #1
+\newcommand{\gvector}[1]{\b{g}(#1)} % g-vector of #1
+\newcommand{\gvectorFull}[2]{\b{g}(#1,#2)} % g-vector of #2 wrt #1
+\newcommand{\gvectors}[1]{\b{g}(#1)} % g-vectors of #1
+\newcommand{\gvectorsFull}[2]{\b{g}(#1,#2)} % g-vectors of #2 wrt #1
 \newcommandx{\gvectorFan}[1][1=\quiver]{\mathcal{F}(#1)} % g-vector fan
-\newcommand{\cvector}[3]{\mathbf{c}(#1, #3 \in #2)} % c-vector of the cluster variable #3 in the cluster #2 with respect to the initial cluster #1
-\newcommand{\cvectors}[2]{\mathbf{c}(#1, #2)} % c-vectors of the cluster #2 with respect to the initial cluster #1
+\newcommand{\cvector}[2]{\mathbf{c}(#2 \in #1)} % c-vector of the cluster variable #2 in the cluster #1
+\newcommand{\cvectorFull}[3]{\mathbf{c}(#1,#3 \in #2)} % c-vector of the cluster variable #3 in the cluster #2 with respect to the initial cluster #1
+\newcommand{\cvectors}[1]{\mathbf{c}(#1)} % c-vectors of the cluster #1
+\newcommand{\cvectorsFull}[2]{\mathbf{c}(#1,#2)} % c-vectors of the cluster #2 with respect to the initial cluster #1
 
@@
 These polytopal realizations were first constructed for bipartite initial seeds by F.~Chapoton, S.~Fomin and A.~Zelevinsky~\cite{ChapotonFominZelevinsky} using the $\b{d}$-vector fans of~\cite{FominZelevinsky-YSystems}, then for acyclic initial seeds by C.~Hohlweg, C.~Lange and H.~Thomas~\cite{HohlwegLangeThomas} using Cambrian lattices and fans of N.~Reading and D.~Speyer~\cite{Reading-CambrianLattices, ReadingSpeyer}, and revisited by S.~Stella~\cite{Stella}, and by V.~Pilaud and C.~Stump~\cite{PilaudStump-brickPolytope} via brick polytopes, and finally for arbitrary initial seeds by C.~Hohlweg, V.~Pilaud and S.~Stella~\cite{HohlwegPilaudStella}.
+More recently in~\cite{BazierMatteDouvilleMousavandThomasYildirim}, V.~Bazier-Matte, G.~Douville, K.~Mousavand, H.~Thomas and E.~Yildirim extended the construction of associahedra of~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} to acyclic seeds of simply laced finite type cluster algebras.
+Here, we extend the construction of~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} to any finite type (simply laced or not) cluster algebra with respect to any seed (acyclic or not) by showing that the type cone of the $\b{g}$-vector fan of any finite type cluster algebra is simplicial.
+
+\subsubsection{Cluster algebras and $\b{g}$-vector fans}
+
+We present some definitions and properties of finite type cluster algebras and their $\b{g}$-vector fans, following the presentation of~\cite{HohlwegPilaudStella}.
 
@@
 for any $x\in\cluster_\circ$.
-This assignment makes all exchange relations and all cluster variables in~$\principalClusterAlgebra$ homogeneous~\cite{FominZelevinsky-ClusterAlgebrasIV} and it justifies the definition of the following family of integer vectors associated to cluster variables.
+%This assignment makes all exchange relations and all cluster variables in~$\principalClusterAlgebra$ homogeneous~\cite{FominZelevinsky-ClusterAlgebrasIV} and it justifies the definition of the following family of integer vectors associated to cluster variables.
 
 \begin{definition}[\cite{FominZelevinsky-ClusterAlgebrasIV}]
-The \defn{$\b{g}$-vector}~$\gvector{\B_\circ}{x}$ of a cluster variable~$x \in \principalClusterAlgebra$ is its degree.
-We denote by $\gvectors{\B_\circ}{\seed} \eqdef \set{\gvector{\B_\circ}{x}}{x \in \seed}$ the set of $\b{g}$-vectors of the cluster variable in the seed~$\seed$ of~$\principalClusterAlgebra$.
+The \defn{$\b{g}$-vector}~$\gvector{x} = \gvectorFull{\B_\circ}{x}$ of a cluster variable~$x \in \principalClusterAlgebra$ is its degree.
+We denote by $\gvectors{\seed} = \gvectorFull{\B_\circ}{\seed} \eqdef \set{\gvectorFull{\B_\circ}{x}}{x \in \seed}$ the set of $\b{g}$-vectors of a seed~$\seed$.
 \end{definition}
@@
 \begin{definition}
-Given a seed~$\seed$ in~$\principalClusterAlgebra$, the \defn{$\b{c}$-vector} of a cluster variable $x \in \seed$ is the vector
+The \defn{$\b{c}$-vector} of a cluster variable $x$ in a seed~$\seed$ of~$\principalClusterAlgebra$ is the vector
 \(
-\cvector{\B_\circ}{\seed}{x} \eqdef \sum_{y \in \cluster_\circ} c_{yx} \, \simpleRoot_y
+\cvector{\seed}{x} = \cvectorFull{\B_\circ}{\seed}{x} \eqdef \sum_{y \in \cluster_\circ} c_{yx} \, \simpleRoot_y
 \)
 of exponents of~$p_x = \prod_{y \in \cluster_\circ} (p_y)^{c_{yx}}$.
-We denote by~$\cvectors{\B_\circ}{\seed} \eqdef \set{\cvector{\B_\circ}{\seed}{x}}{x \in \seed}$ the set of $\b{c}$-vectors of a seed~$\seed$.
+We denote by~$\cvectors{\seed} = \cvectorsFull{\B_\circ}{\seed} \eqdef \set{\cvectorFull{\B_\circ}{\seed}{x}}{x \in \seed}$ the set of $\b{c}$-vectors of a seed~$\seed$.
 \end{definition}
@@
 
-\begin{theorem}[{\cite[Theorem~1.2]{NakanishiZelevinsky}}]
+\begin{theorem}[{\cite[Thm~1.2]{NakanishiZelevinsky}}]
 \label{thm:duality}
 For any seed~$\seed$ of~$\principalClusterAlgebra$, let $\seed^\vee$ be its dual in $\principalClusterAlgebra[\B_\circ^\vee]$.
-Then the set of $\b{g}$-vectors~$\gvector{\B_\circ}{\seed}$ and the set of $\b{c}$-vectors~$\cvectors{\B_\circ^\vee}{\seed^\vee}$ form dual bases, that is
+Then the set of $\b{g}$-vectors~$\gvectorFull{\B_\circ}{\seed}$ and the set of $\b{c}$-vectors~$\cvectorsFull{\B_\circ^\vee}{\seed^\vee}$ form dual bases, that is
 \(
-{\bigdotprod{\gvector{\B_\circ}{x}}{\cvector{\B_\circ^\vee}{\seed^\vee}{y^\vee}} = \delta_{x=y}}
+{\bigdotprod{\gvectorFull{\B_\circ}{x}}{\cvectorFull{\B_\circ^\vee}{\seed^\vee}{y^\vee}} = \delta_{x=y}}
 \)
@@
 \label{thm:gvectorFan}
-For any finite type exchange matrix~$\B_\circ$, the $\b{g}$-vector fan~$\gvectorFan[\B_\circ]$ is the normal fan of the polytope defined by...
-\vincent{TODO}
+For any finite type exchange matrix~$\B_\circ$, the $\b{g}$-vector fan~$\gvectorFan[\B_\circ]$ is the normal fan of the \defn{$\B_\circ$-associahedron}~$\Asso[\B_\circ, \b{h}]$ defined equivalently as
+\begin{enumerate}[(i)]
+\item the convex hull of the points~$\sum_{x \in \seed} \b{h}_x \, \cvectorFull{\B_\circ^\vee}{\seed^\vee}{x^\vee}$ for all seeds~$\seed$ of~$\principalClusterAlgebra$, or
+\item the intersection of the halfspaces~$\set{\b{v} \in V^\vee}{\dotprod{\gvectorFull{\B_\circ}{x}}{\b{v}} \le \b{h}_x}$ for all cluster variables~$x$ of~$\principalClusterAlgebra$.
+\end{enumerate}
 \end{theorem}
@@
 \begin{enumerate}[(i)]
-\item For any non-kissing facet~$F, F'$ of~$\NKC$ with~$F \ssm \{\omega\} = F' \ssm \{\omega'\}$, there exists a unique maximal common substring~$\sigma$ of~$\omega$ and~$\omega'$ that decomposes~$\omega = \rho \sigma \tau$ and~$\omega' = \rho' \sigma \tau'$ such that the facets~$F$ and~$F'$ both contain the walks~$\mu \eqdef \rho' \sigma \tau$ and~$\nu \eqdef \rho \sigma \tau'$.
-\item The substring~$\sigma$ and thus the walks~$\mu$ and~$\nu$ only depend on the exchangeable walks~$\omega$ and~$\omega'$, not on the adjacent non-kissing facets~$F $ and~$F'$.
-\yann{This needs more assumptions.  Move to another proposition.}
+\item For any non-kissing facet~$F, F'$ of~$\NKC$ with~$F \ssm \{\omega\} = f' \ssm \{\omega'\}$, there exists a unique maximal common substring~$\sigma$ of~$\omega$ and~$\omega'$ that decomposes~$\omega = \rho \sigma \tau$ and~$\omega' = \rho' \sigma \tau'$ such that the facets~$F$ and~$F'$ both contain the walks~$\mu \eqdef \rho' \sigma \tau$ and~$\nu \eqdef \rho \sigma \tau'$.
+\item The substring~$\sigma$ and thus the walks~$\mu$ and~$\nu$ actually depend on the exchangeable walks~$\omega$ and~$\omega'$, not on the adjacent non-kissing facet~$F $ and~$F'$.
 \item Moreover, the linear dependence between the $\b{g}$-vectors of~$F \cup F'$ is given by
@@
 
-The quivers of this family are particularly well-behaved: they avoid all pathologies of \cref{rem:exchangeablePairsNKC} and we will prove that the type cone of their non-kissing fan happens to be simplicial.\pg{Need to exclude two-cycles, else false.}
+The quivers of this family is particularly well-behaved: they avoid all pathologies of \cref{rem:exchangeablePairsNKC} and we will prove that the type cone of their non-kissing fan happens to be simplicial.
 Note that this family already contains a lot of relevant examples, including:
@@
 If the walks~$\omega$ and~$\omega'$ are non-self-kissing and exchangeable, then they form the unique extremal exchangeable pair directed by~$\sigma$.
-These extremal exchangeable pairs correspond to meshes of the Auslander-Reiten quiver.\pg{The conjecture is the word ``unique''.}
+These extremal exchangeable pairs correspond to meshes of the Auslander-Reiten quiver.
 \item Otherwise, $\sigma$ is the direction to one or more extremal exchangeable pairs obtained by moving further in the Auslander-Reiten quiver (this is really unclear at the moment).

### 2019-02-11 thirdPaper/draft/typeConeAssociahedra.tex
statements extricats

--- 2019-02-11 thirdPaper/draft/typeConeAssociahedra.tex
@@
 
+% extriangulated
+\newcommand{\tc}{\mathcal{T}}
+\newcommand{\ec}{\mathcal{E}}
+\newcommand{\infl}{\rightarrowtail}
+\newcommand{\defl}{\twoheadrightarrow}
+\newcommand{\Modt}{\operatorname{Mod}\tc}
+\newcommand{\modt}{\MOD\tc}
+\newcommand{\kzero}[1]{K_0(#1)}
+
 %% SPECIFIC NON-KISSING COMPLEX
@@
 \]
-\begin{proposition}[\cite{BuanMarshReiten, KellerReiten}]\label{prop::functor-F}
+\begin{proposition}[\cite{BuanMarshReiten, KellerReiten}]\label{prop::BMR-KR}
  The functor~$F$ induces an equivalence of~$\field$-linear categories
@@
 
-\begin{proposition}[Proposition I.2.3 of~\cite{ReitenVandenbergh}]
+\begin{proposition}[]\pg{Cite Happel}
  Any triangulated category admitting a Serre functor has almost-split triangles.  In particular, any~$2$-Calabi--Yau triangulated category has almost-split triangles.
@@
 
-\begin{definition}
+\begin{definition}\label{defi::bilinear form}
  For any two objects~$X$ and~$Y$ of~$\cat$, define
@@
 
-\begin{notation}
+\begin{notation}\label{notation::ell_X}
 \begin{enumerate}
@@
 
-We can finally state the main theorem of this section, which is an analogue of the main result of~\cite{Auslander1984}.
+We can finally state the main theorem of this section. \pg{recall Auslander}
 
@@
 
-Before we can prove Theorem~\ref{theo::relations-g-vecteurs}, we need to recall the following results and definition from \cite{DehyKeller,Palu}.
-
-\begin{proposition}
- Let~$X$ be an object of~$\cat$. Then there exists a triangle
- \[
-  T_1^X \to T^0_X \to X \to \susp T_1^X
- \]
- with~$T_1^X$ and~$T_0^X$ in~$\add(T)$.
-
-\end{proposition}
-
-\begin{definition}
- The \defn{index} of an object~$X$ is the element
- \[
-  \ind_T(X) := [T_0^X] - [T_1^X] \in \Ksp(\add(T)).
- \]
-\end{definition}
-
-The notion of index is very close to the definition of the map~$\b g:\Ksp(\cat)\to \Kg(\cat)$ of Definition~\ref{defi::grothendieck-group}.  The link is given by the following result.
-
-\begin{proposition}[\cite{Palu}]
- Let~$X\xrightarrow{} Y \xrightarrow{} Z \xrightarrow{h} \susp X$ be a triangle.
- Then
- \[
-  \ind_T(X) + \ind_T(Z) - \ind_T(Y) = 0
- \]
- if and only if~$h\in (\susp T)$.
-\end{proposition}
-
-\begin{corollary}\label{coro::grothendieck-g-vectors}
- There is an isomorphism~$\phi:\Kg(\cat) \to \Ksp(\add(T))$ such that~$\ind_T = \phi\circ \b g$.  In particular,~$\Kg(\cat)$ is a free abelian group generated by the~$[T_i]$.
-\end{corollary}
-
-We can now begin the proof of Theorem~\ref{theo::relations-g-vecteurs}
-
 \begin{lemma}\label{lemm::bilinear-form-suspention-T}
@@
  \]
- Applying now the functors~$\cat(-, B)$ and~$\Hom{\Lambda}(-, FB)$, we get a commutative diagram whose rows are exact sequences and whose vertical maps are surjective by Proposition~\ref{prop::functor-F}.
- \[
-  \xymatrix{ & \cat(\susp^{-1} A, B)\ar[r]\ar@{->>}[d] & \cat(E, B)\ar[r]^{f^*}\ar@{->>}[d] & \cat(A,B)\ar[r]\ar@{->>}[d] & \coker(f^*)\ar[r]\ar@{->>}[d] & 0 \\
-  0 \ar[r] & \Hom{\Lambda}(F\susp^{-1} A, FB)\ar[r] & \Hom{\Lambda}(FE, FB)\ar[r]^{Ff^*} & \Hom{\Lambda}(FA, FB)\ar[r] & \coker(Ff^*)\ar[r] & 0.
-  }
- \]
-
- If~$B\ncong A$, then the definition of an almost-split triangle implies that~$f^*$ is surjective.
-Thus~$\coker(f^*)=0$, so that~$\coker(Ff^*) = 0$, and by additivity of the dimension in exact sequences, we get that~$\langle \ell_A, B \rangle =0$.
-
- If~$B\cong A$, then~$\coker(f^*)$ is isomorphic to the residue field~$\field_A$ of~$\cat(A,A)$.
-Since~$A$ is not in~$\add(\susp T)$, the ideal of endomorphisms of~$A$ factoring through an object of~$\add(\susp T)$ is contained in the maximal ideal of~$\cat(A,A)$.
-Therefore, the rightmost morphism in the commutative diagram is an isomorphism, so~$\coker(Ff^*)$ is isomorphic to~$\field_A$.
+ Applying now the functor~$\Hom{\Lambda}(-, FB)$, we get an exact sequence
+ \[
+  0 \xrightarrow{} \Hom{\Lambda}(F\susp^{-1} A, FB) \xrightarrow{} \Hom{\Lambda}(FE, FB) \xrightarrow{Ff^*} \Hom{\Lambda}(FA, FB) \xrightarrow{} \coker(Ff^*) \xrightarrow{} 0
+ \]
+ If~$B\ncong A$, then the definition of an almost-split triangle implies that~$Ff^*$ is surjective.
+\pg{add an exact sequence here; image of Ffstar is non-invertible elements} Thus~$\coker(Ff^*) = 0$, and by additivity of the dimension in exact sequences, we get that~$\langle \ell_A, B \rangle =0$.
+
+ If~$B\cong A$, then~$\coker(Ff^*)$ is isomorphic to the residue field of~$\End{\Lambda}(FA)$, which is isomorphic to the residue field~$\field_A$ of~$A$.
 \end{proof}
@@
  \[
-  \lambda_A = \frac{\langle \ell_A, x \rangle}{\langle \ell_A, A \rangle} = \frac{\langle x, r_A \rangle}{\langle A, r_A \rangle}.
+  \lambda_A = \langle \ell_A, x \rangle = \langle x, r_A \rangle.
  \]
@@
  \[
-  \langle \ell_B, x \rangle = \langle \ell_B, \sum_{A\in \ind(\cat)} \lambda_A [A] \rangle = \sum_{A\in \ind{\cat}} \lambda_A \langle \ell_B, [A] \rangle = \lambda_B \langle \ell_B, [B] \rangle.
- \]
- The equality~$\lambda_A = \frac{\langle x, r_A \rangle}{\langle A, r_A \rangle}$ is proved in a similar way.
+  \langle \ell_B, x \rangle = \langle \ell_B, \sum_{A\in \ind(\cat)} \lambda_A [A] \rangle = \sum_{A\in \ind{\cat}} \lambda_A \langle \ell_B, [A] \rangle = \lambda_A.
+ \]
+ The equality~$\lambda_A = \langle x, r_A\rangle$ is proved in a similar way.
 \end{proof}
@@
  \[
-  x = \sum_{A\in \ind(\cat)\setminus \add(\susp T)} \frac{\langle \ell_A, x \rangle}{\langle \ell_A, A \rangle}[A] + \sum_{i=1}^n \lambda_{\susp T_i} [\susp T_i] = \sum_{i=1}^n \lambda_{\susp T_i} [\susp T_i].
+  x = \sum_{A\in \ind(\cat)\setminus \add(\susp T)} \langle \ell_A, x \rangle + \sum_{i=1}^n \lambda_{\susp T_i} [\susp T_i] = \sum_{i=1}^n \lambda_{\susp T_i} [\susp T_i].
  \]
@@
 By Lemma~\ref{lemm::test-susp-T}, this implies that~$z\in \Ksp(\add(\susp T))$.
-Since~$z\in \ker(\b g)$ and since~$\b g$ is injective on~$\Ksp(\add (\susp T))$ by Corollary~\ref{coro::grothendieck-g-vectors}, we get that~$z=0$.
+Since~$z\in \ker(\b g)$ and since~$\b g$ is injective on~$\Ksp(\add (\susp T))$, we get that~$z=0$.
 This finishes the proof.
+\pg{We need a lemma saying that g is injective on K(add(susp T))}
 \end{proof}
@@
 \subsection{Application to~$\b g$-vectors of cluster algebras of finite type}\label{sect::applications-g-vectors}
+
+We recall the following results and definition from \cite{DehyKeller,Palu}.
+
+\begin{proposition}
+ Let~$X$ be an object of~$\cat$. Then there exists a triangle
+ \[
+  T_1^X \to T^0_X \to X \to \susp T_1^X
+ \]
+ with~$T_1^X$ and~$T_0^X$ in~$\add(T)$.
+
+\end{proposition}
+
+\begin{definition}
+ The \defn{index} of an object~$X$ is the element
+ \[
+  \ind_T(X) := [T_0^X] - [T_1^X] \in \Ksp(\add(T)).
+ \]
+\end{definition}
+
+The notion of index is very close to the definition of the map~$\b g:\Ksp(\cat)\to \Kg(\cat)$ of Definition~\ref{defi::grothendieck-group}.  The link is given by the following result.
+
+\begin{proposition}[\cite{Palu}]
+ Let~$X\xrightarrow{} Y \xrightarrow{} Z \xrightarrow{h} \susp X$ be a triangle.
+ Then
+ \[
+  \ind_T(X) + \ind_T(Z) - \ind_T(Y) = 0
+ \]
+ if and only if~$h\in (\susp T)$.
+\end{proposition}
+
+\begin{corollary}
+ There is an isomorphism~$\phi:\Kg(\cat) \to \Ksp(\add(T))$ such that~$\ind_T = \phi\circ \b g$.  In particular,~$\Kg(\cat)$ is a free abelian group generated by the~$[T_i]$.
+\end{corollary}
 
@@
 %%%%
-\subsection{Setting}
+\subsection{Setting}\label{setting::extricat}
+
+In this section, we let~$\cat$ be a Krull--Schmidt, extriangulated category with a fixed full subcategory~$\tc$ satisfying the following three properties:
+\begin{enumerate}
+ \item Every~$T\in\tc$ is projective in~$\cat$;
+ \item For each~$T\in\tc$, the morphism~$T\to 0$ is an inflation for the extriangulated structure of~$\cat$;
+ \item For each~$X\in\cat$, there is an extriangle~$T_1^X\infl T_0^X \defl X \overset{\delta_X}{\dashrightarrow}$ in~$\cat$ with~$T_0^X, T_1^X$ in~$\tc$.
+\end{enumerate}
 
 \begin{remark}
- Examples of categories satisfying the above properties are
+ Examples of categories satisfying the properties above are
  \begin{itemize}
-  \item $2$-Calabi--Yau triangulaged categories admitting a cluster-tilting object (see Section~\ref{sect::2CYTriangulated});
+  \item $2$-Calabi--Yau triangulated categories admitting a cluster-tilting object (see Section~\ref{sect::2CYTriangulated});
   \item $2$-Calabi--Yau Frobenius exact categories (see Section~\ref{sect::2CYexact});
-  \item for any Artin algebra~$\Lambda$, the category~$K^{[-1,0]}(\proj \Lambda)$ of complexes of finitely generated projective~$\Lambda$-modules concentrated in degrees~$-1$ and~$0$, with morphisms considered up to homotopy (see Section~\ref{sect::Kbproj}).
+  \item for any Artin algebra~$\Lambda$, the category~$K^{[-1,0]}(\proj \Lambda)$ of complexes of finitely generated projective~$\Lambda$-modules concentrated in degrees~$-1$ and~$0$, with morphisms considered up to homotopy (see Section~\ref{sect::Kbproj});
+  \item more generally, extriangulated categories~$\cat$ constructed as follows: if~$\tc$ is a rigid subcategory of an extriangulated category~$\ec$, we let~$\cat$ be the full subcategory of~$\ec$ whose objects satisfy condition (3), equipped with the extriangulated structure obtained from that of~$\ec$ by considering those extriangles in~$\ec$ all whose terms belong to~$\cat$ and whose deflation is~$\tc$-epi (see Section~\ref{sect::Rigid}).
  \end{itemize}
-
 \end{remark}
 
+\yann{Rappels sur les categories extriangulees}
 %%%%
+\subsection{Statement of preliminary results on extriangulated categories}
+\label{subsection: prelim on extricats}
+
+We let~$\cat$ be as in Setting~\ref{setting::extricat}.
+
+\begin{notation}
+For any indecomposable object~$T\in\tc$, we fix an extriangle~$T\infl 0 \defl \susp T \dashrightarrow$.
+Extending by additivity, this defines (uniquely up to isomorphism) an object~$\susp T$, for each object~$T\in\tc$.
+\end{notation}
+
+\begin{remark}
+ As will be proven below [REF], this notation extends to an equivalence of categories from the category~$\tc$ of projective objects in~$\cat$ to the category~$\susp\tc$ of injective objects in~$\cat$.
+\end{remark}
+
+\begin{notation}
+We let~$\Modt$ denote the category of functors from~$\tc$ to Abelian groups, and~$\modt$ its full subcategory of functors that are finitely presented, i.e.
+cokernels of morphisms between representable functors.
+We let~$F:\cat\to\Modt$ be the functor defined on objects by sending~$X\in\cat$ to~$\cat(-,X)|_\tc$.
+\end{notation}
+
+\begin{lemma}
+For any~$X\in\cat$, the functor~$FX$ is finitely presented.
+We thus have a functor
+\[
+F:\cat\to\modt.
+\]
+\end{lemma}
+
+Proposition~\ref{prop::KRextricat} below extends similar results from [REF]\yann{ref: BMR, KR ,KZ, IY...} (see also Proposition~\ref{prop::BMR-KR}) to the setting under consideration.
+We note that the proof requires minor modifications.
+
+\begin{proposition}\label{prop::KRextricat}
+The functor~$F$ induces an equivalence of categories
+\[
+F: \cat/(\susp\tc) \to \modt
+\]
+where~$(\susp\tc)$ is the ideal of morphisms factoring through an object of the form~$\susp T$, for some~$T\in\tc$.
+% This equivalence induces further equivalences between~$\tc$ and the category of projectives, and between~$\tau\susp\tc$ and that of injectives.
+\end{proposition}
+
+\begin{remark}
+Because the category~$\cat$ does not have weak kernels in general, the category~$\modt$ might not be abelian.
+However, in all our applications, the subcategory~$\tc$ is of the form~$\add(T)$ for some object~$T$.
+In that case,~$\modt$ is equivalent to~$\MOD\End{\cat}(T)$ and thus abelian.
+\end{remark}
+
+\yann{Applying $X\mapsto\mathbb{E}(-,X)|_{\susp\tc}$ might solve this issue?}
+
+\begin{definition}
+We let~$\kzero{\cat}$ denote the Grothendieck group of~$\cat$, that is, the quotient of the free abelian group generated by symbols~$[X]$, for each $X\in\cat$, by the relations~$[X]-[Y]+[Z]$, for each conflation~$X\infl Y\defl Z$ in~$\cat$.
+\end{definition}
+
+\begin{remark}
+Since~$\tc$ is extension-closed in~$\cat$, it inherits an extriangulated structure.
+Because~$\tc$ is made of projective objects in~$\cat$, its extriangulated structure splits and we have~$\kzero{\tc}\cong\Ksp(\tc)$.
+\end{remark}
+
+The notion of index from \yann{ref RVdB, DK, P, also studied in ....} generalises to our current setting.
+
+\begin{definition}
+For any object~$X\in\cat$, fix some extriangle
+\[
+T_1^X \infl T_0^X \defl X \overset{\delta_X}{\dashrightarrow}
+\]
+and define
+\[
+\ind_\tc X = [T_0^X]-[T_1^X]\in\kzero{\tc}.
+\]
+\end{definition}
+
+\begin{proposition}
+ The assignment~$X\mapsto\ind_\tc X$ is well-defined and induces an isomorphism
+\[
+\ind_\tc : \kzero{\cat} \overset{\cong}{\longrightarrow} \kzero{\tc}
+\]
+of abelian groups.
+\end{proposition}
+
 \subsection{Statement of the theorem}
 
+Let~$\cat$ be as in Setting~\ref{setting::extricat}.
+
+\begin{remark}
+Assume moreover that~$\cat$ is $\field$-linear and Ext-finite.
+By the preliminary results of Section~\ref{subsection: prelim on extricats}, we can apply~\cite[Proposition 4.2]{IyamaNakaokaPalu} to obtain that~$\modt$ is Hom-finite.
+In particular, if $\tc=\add T$, then $\End{\cat}(T)$ is a finite-dimensional~$\field$-algebra.
+It thus also follows that Definition~\ref{defi::bilinear form} still makes sense in this more general settup: For any~$X,Y\in\cat$,
+\[
+\langle X,Y\rangle := \dim_\field \Hom{\tc}(FX,FY) = \dim_\field \cat/(\susp\tc)(X,Y).
+\]
+\end{remark}
+
+When this makes sense, we make use of Notation~\ref{notation::ell_X}: if
+\[
+X \infl E \defl Y \dashrightarrow
+\]
+is an almost-split sequence (see~\cite{IyamaNakaokaPalu} for a definition in this setting), we let
+\[
+ \ell_X := [X]+[Y]-[E]\in\Ksp(\cat).
+\]
+
+\begin{theorem}\label{theorem::extricats}
+Assume that~$\cat$ is a~$\field$-linear, Ext-finite, Krull--Schmidt, extriangulated category with Auslander--Reiten--Serre duality.
+Assume that~$T$ is a projective object of~$\cat$ such that any~$X\in\cat$ admits an extriangle~$T_1^X\infl T_0^X\defl X\dashrightarrow$ with~$T_0^X, T_1^X\in\add(T)$, and for any~$T'\in\add(T)$ the morphism~$T'\to 0$ is an inflation.
+Then~$\cat$ has only finitely many isomorphism classes of indecomposable objects if and only if the set
+\[
+ L:=\left\{\ell_X \ | \ X\in \ind(\cat)\setminus \add(\susp T) \right\}
+\]
+generates the kernel of the canonical projection~$\b g:\Ksp(\cat) \to \kzero{\cat}$. 
+In this case, the set~$L$ is a basis of the kernel of~$\b g$, and for any $x\in \ker(\b g)$, we have that
+ \[
+  x= \sum_{A\in \ind(\cat) \setminus \add(\susp T)} \frac{\langle x, A \rangle}{\langle \ell_A, A \rangle} \ell_A.
+ \]
+\end{theorem}
+
+\begin{corollary}
+Assume that~$\ind(\cat)$ is finite.
+Let~$X\infl E\defl Y\dashrightarrow$ be any extriangle.
+Then the element~$x=[X]+[Y]-[E]$ of the kernel of~$\b g$ is a non-negative linear combination of the~$\ell_A$, with~$A\in\ind(\cat)\setminus\add(\susp T)$.
+\end{corollary}
+
 %%%%
-\subsection{Proof of Theorem~\ref{}}
+\subsection{Proof of Theorem~\ref{theorem::extricats}}
 
@@
 %%
-\subsubsection{Objects presented by a rigid object}
+\subsubsection{Objects presented by a rigid object}\label{sect::Rigid}
 

### 2019-02-11 thirdPaper/draft/typeConeAssociahedra.tex

--- 2019-02-11 thirdPaper/draft/typeConeAssociahedra.tex
@@
 \]
+
 \begin{proposition}[\cite{BuanMarshReiten, KellerReiten}]\label{prop::functor-F}
+
 The functor~$F$ induces an equivalence of~$\field$-linear categories

### 2019-02-11 thirdPaper/draft/typeConeAssociahedra.tex
beginning of proof extricats

@@
 \newcommand{\kzero}[1]{K_0(#1)}
+\newcommand{\eps}{\varepsilon}
 
@@
 
-In this section, we let~$\cat$ be a Krull--Schmidt, extriangulated category with a fixed full subcategory~$\tc$ satisfying the following three properties:
+In this section, we let~$\cat$ be a Krull--Schmidt, extriangulated category with a fixed full additive \yann{additive contains strictly full + stable under taking summands} subcategory~$\tc$ satisfying the following three properties:
 \begin{enumerate}
@@
 \begin{notation}
-We let~$\Modt$ denote the category of functors from~$\tc$ to Abelian groups, and~$\modt$ its full subcategory of functors that are finitely presented, i.e.
+We let~$\Modt$ denote the category of additive functors from~$\tc$ to Abelian groups, and~$\modt$ its full subcategory of functors that are finitely presented, i.e.
 cokernels of morphisms between representable functors.
@@
 
-Proposition~\ref{prop::KRextricat} below extends similar results from [REF]\yann{ref: BMR, KR ,KZ, IY...} (see also Proposition~\ref{prop::BMR-KR}) to the setting under consideration.
+Proposition~\ref{prop::KRextricat} below extends similar results from [REF]\yann{ref: BMR, KR ,KZ, IY...} (see also Proposition~\ref{prop::functor-F}) to the setting under consideration.
 We note that the proof requires minor modifications.
@@
 
+We let~$\cat$ and~$\tc$ be as in Setting~\ref{setting::extricat}.
+We will make it explicit when more assumptions are needed.
+
+We start by stating some immediate implications of the existence of conflations~$T\infl 0 \defl \susp T$, for~$T\in\tc$.
+
+\begin{lemma}
+The following holds:
+\begin{enumerate}[{\rm (a)}]
+ \item An object belongs to~$\tc$ if and only if it is projective in~$\cat$.
+ \item For any~$T,T'\in\tc$, we have~$\cat(T,\susp T')=0$.
+ \item For any~$X\in\cat$ and~$T\in\tc$,~$\cat(X,\susp T)\cong\mathbb{E}(X,T)$.
+ \item For any~$X\in\cat$ and~$T\in\tc$,~$\cat(T,X)\cong\mathbb{E}(\susp T,X)$.
+ \item The full subcategory~$\susp\tc$ is rigid in~$\cat$.
+\end{enumerate}
+\end{lemma}
+
+\begin{proof}
+(a) If~$X$ is projective in~$\cat$, then the deflation~$T_0^X\defl X$ splits and~$X$ is a summand of~$T_0^X$.
+
+(b) This follows from the fact that~$T$ is projective and~$0\defl\susp T'$ is a deflation.
+
+(c) and (d) are obtained from the long exact sequences associated with the extriangle~$T\infl 0\defl \susp T\dashrightarrow$.
+
+(e) For any~$T,T'\in\tc$, we have~$\mathbb{E}(\susp T,\susp T') \cong \cat(T,\susp T')=0$.
+\end{proof}
+
+\begin{lemma}\label{lemma::shifts of extriangles}
+Let~$X\in\cat$ and let
+\[
+T_1^X\overset{f_X}{\infl} T_0^X\overset{g_X}{\defl} X \overset{\delta_X}{\dashrightarrow}, \ \ \ T_0^X\infl 0\defl \susp T_0^X\overset{\delta_0}{\dashrightarrow}, \ \ \ T_1^X\infl 0\defl \susp T_1^X\overset{\delta_1}{\dashrightarrow}
+\]
+be extriangles with~$T_0^X,T_1^X\in\tc$.
+Then there are extriangles
+\[
+T_0^X\overset{g_X}{\infl} X \overset{h_X}{\defl} \susp T_1^X \overset{(f_X)_\ast\delta_1}{\dashrightarrow}, \ \ \ X \overset{h_X}{\infl} \susp T_1^X \overset{\susp f_X}{\defl} \susp T_0^X \overset{(g_X)_\ast\delta_0}{\dashrightarrow}
+\]
+where~$h_X$ is the unique morphism in~$\cat(X,\susp T_1^X)$ satisfying~$(h_X)^\ast\delta_1=\delta_X$ and~$\susp f_X$ is the unique morphism in~$\cat(\susp T_1^X,\susp T_0^X)$ satisfying~$(\susp f_X)^\ast\delta_0 = (f_X)_\ast\delta_1$.
+\end{lemma}
+
+\begin{proof}
+The first extriangle is obtained by applying the dual of~\cite[Proposition 3.15]{NakaokaPalu} to~$\delta_X$ and~$\delta_1$, and the second one is obtained similarly from~$\delta_0$ and ~$(f_X)_\ast \delta_1$.
+\end{proof}
+
+\begin{remark}
+For any~$T\in\ind(\tc)$, fix an extriangle~$T\infl 0\defl\susp T\overset{\eps_T}{\dashrightarrow}$, and extend those choices to the all of~$\tc$ by additivity.
+As noticed in Lemma~\ref{lemma::shifts of extriangles}, for any morphism~$T\overset{f}{\to}T'$ in~$\tc$, there is a unique morphism~$\susp f\in\cat(\susp T,\susp T')$ such that~$f_\ast\eps_T=(\susp f)^\ast\eps_{T'}$, as illustrated below:
+\[
+\xy
+(-12,6)*+{T}="0";
+(0,6)*+{0}="2";
+(12,6)*+{\susp T}="4";
+(24,6)*+{}="6";
+%
+(-12,-6)*+{T'}="10";
+(0,-6)*+{0}="12";
+(12,-6)*+{\susp T'}="14";
+(24,-6)*+{}="16";
+%
+{\ar "0";"2"};
+{\ar "2";"4"};
+{\ar@{-->}^{\eps_T} "4";"6"};
+%
+{\ar_{f} "0";"10"};
+{\ar "2";"12"};
+{\ar^{\susp f} "4";"14"};
+%
+{\ar "10";"12"};
+{\ar "12";"14"};
+{\ar@{-->}_{\eps_{T'}} "14";"16"};
+\endxy
+\]
+which gives an equivalence of additive categories
+\[
+ \susp: \tc \to \susp\tc
+\]
+where~$\susp\tc$ is the full subcategory of~$\cat$ whose objects are of the form~$\susp T$, for some~$T\in\tc$.
+\end{remark}
+
 %%%%

### 2019-02-11 thirdPaper/draft/typeConeAssociahedra.tex
minor changes g-vectors

--- 2019-02-11 thirdPaper/draft/typeConeAssociahedra.tex
@@
 \newcommand{\coefficients}{\mathrm{P}} % a coefficients tuple
-\newcommandx{\variables}[1][1=\clusterAlgebra]{\mathcal{V}(#1)} % all variables
+\newcommandx{\variables}[2][1=\B_\circ, 2 = \coefficients_\circ]{\mathcal{V}(#1,#2)} % all variables
 \newcommandx{\clusterAlgebra}[2][1=\B_\circ, 2=\coefficients_\circ]{\mathcal{A}\!\left(#1,#2\right)} % cluster algebra
@@
 \begin{proposition}
+\label{prop:associahedronLoday}
 The associahedron~$\Asso[n]$ can be described equivalently as:
@@
 \begin{proposition}
+\label{prop:normalFanLoday}
 In the normal fan~$\gvectorFan[n]$ of~$\Asso[n]$, 
@@
 \begin{corollary}
+\label{coro:typeConeAsso}
 Let~$n \in \N$ and~$X(n) \eqdef \set{(a,b)}{0 \le a < b \le n+2}$. Then the type cone of the normal fan~$\gvectorFan[n]$ of~$\Asso[n]$ is given by
@@
 %We consider an \defn{initial seed} $\seed_\circ = (\B_\circ, \coefficients_\circ, \cluster_\circ)$ whose cluster variables are supposed to be~$x_1, \dots, x_n$.
+We denote by~$\variables$ the collection of all cluster variables in the seeds mutationally equivalent to an initial seed~$\seed_\circ = (\B_\circ, \coefficients_\circ, \cluster_\circ)$ with cluster variables~$\cluster_\circ = \{x_1, \dots, x_n\}$.
 
 \begin{definition}[{\cite[Def.~2.11]{FominZelevinsky-ClusterAlgebrasIV}}]
-The (geometric type) \defn{cluster algebra} $\clusterAlgebra$ is the $\Z\Trop{m}$-subring of~$\Q(x_1, \dots, x_n, p_1, \dots, p_m)$ generated by all the cluster variables in all the seeds mutationally equivalent to an initial seed~$\seed_\circ = (\B_\circ, \coefficients_\circ, \cluster_\circ)$ with cluster variables~$\cluster_\circ = \{x_1, \dots, x_n\}$.
+The (geometric type) \defn{cluster algebra} $\clusterAlgebra$ is the $\Z\Trop{m}$-subring of~$\Q(x_1, \dots, x_n, p_1, \dots, p_m)$ generated by~$\variables$.
+% all the cluster variables in all the seeds mutationally equivalent to an initial seed~$\seed_\circ = (\B_\circ, \coefficients_\circ, \cluster_\circ)$ with cluster variables~$\cluster_\circ = \{x_1, \dots, x_n\}$.
 \end{definition}
@@
 \begin{theorem}[{\cite[Thm~1.2]{NakanishiZelevinsky}}]
-\label{thm:duality}
+\label{prop:gvectorscvectorsDualBasesCA}
 For any seed~$\seed$ of~$\principalClusterAlgebra$, let $\seed^\vee$ be its dual in $\principalClusterAlgebra[\B_\circ^\vee]$.
@@
 \begin{theorem}
-\label{thm:gvectorFan}
+\label{thm:gvectorFanCA}
 For any finite type exchange matrix~$\B_\circ$, the collection of cones \\[.1cm]
 \centerline{
-$\gvectorFan[\B_\circ] \eqdef \bigset{\R_{\ge0} \gvectors{\B_\circ}{\seed}}{\seed \text{ seed of } \principalClusterAlgebra},$
+$\gvectorFan[\B_\circ] \eqdef \bigset{\R_{\ge0} \, \gvectorsFull{\B_\circ}{\seed}}{\seed \text{ seed of } \principalClusterAlgebra},$
 } \\[.1cm]
@@
 \begin{theorem}[{\cite[Thm.~26]{HohlwegPilaudStella}}]
-\label{thm:gvectorFan}
+\label{thm:generalizedAsso}
 For any finite type exchange matrix~$\B_\circ$, the $\b{g}$-vector fan~$\gvectorFan[\B_\circ]$ is the normal fan of the \defn{$\B_\circ$-associahedron}~$\Asso[\B_\circ, \b{h}]$ defined equivalently as
@@
 \para{Flips in the $\b{g}$-vector fan}
+%
+We now discuss the linear dependences between $\b{g}$-vectors of adjacent clusters.
+The following proposition was stated in~\cite[Lem.~19]{HohlwegPilaudStella}.
+
+\begin{lemma}
+\label{lem:linearDependencegvectorsCA}
+For any finite type~exchange matrix~$\B_\circ$ and any adjacent seeds~${(\B, \coefficients, \cluster)}$ and~${(\B', \coefficients', \cluster')}$ in $\principalClusterAlgebra$ with~$\cluster \ssm \{x\} = \cluster' \ssm \{x'\}$, the $\b{g}$-vectors of~$\cluster \cup \cluster'$ with respect to~$\B_\circ$ satisfy precisely one of the following two linear dependences
+\[
+\gvectorFull{\B_\circ}{x} + \gvectorFull{\B_\circ}{x'} = \sum_{\substack{y \in \cluster \cap \cluster' \\ b_{xy} < 0}} -b_{xy} \, \gvectorFull{\B_\circ}{y}
+\quad\text{or}\quad
+\gvectorFull{\B_\circ}{x} + \gvectorFull{\B_\circ}{x'} = \sum_{\substack{y \in \cluster \cap \cluster' \\ b_{xy} > 0}} b_{xy} \, \gvectorFull{\B_\circ}{y}.
+\]
+\end{lemma}
+
+Note that this statement is unfortunately less precise than \cref{prop:exchangeablePairsAsso}.
+Indeed, which of the two possible linear dependences is satisfied by the $\b{g}$-vectors of~$\cluster \cup \cluster'$ depends on the initial exchange matrix~$\B_\circ$.
+%In particular, the geometry of the $\b{g}$-vector fan~$\gvectorFan$ changes as $\B_\circ$ varies within a given mutation class.
+However, it already ensures that the type cone~$\typeCone(\gvectorFan[\B_\circ])$ of the $\b{g}$-vector fan contains the polyhedral cone of~$\b{h} \in \R^{\variables}$ such that
+\(
+\b{h}_x + \b{h}_{x'} > \sum_{{y \in \cluster \cap \cluster', \; b_{xy} < 0}} -b_{xy}
+\)
+and
+\(
+% \quad\text{and}\quad
+\b{h}_x + \b{h}_{x'} > \sum_{{y \in \cluster \cap \cluster', \; b_{xy} > 0}} b_{xy} \, \b{h}_y
+\)
+for any seeds~$(\B, \coefficients, \cluster)$ and~$(\B', \coefficients', \cluster')$ with~${\cluster \ssm \{x\} = \cluster' \ssm \{x'\}}$.
+This is precisely where the vector~$\b{h}$ was chosen to ensure a realization in \cref{thm:generalizedAsso}.
 
@@
 \begin{proposition}
-\label{prop:gvectorscvectorsDualBases}
+\label{prop:gvectorscvectorsDualBasesGentle}
 For any non-kissing facet~$F \in \NKC$, the set of $\b{g}$-vectors~$\gvectors{F}$ and the set of $\b{c}$-vectors~$\cvectors{F}$ form dual bases, that is
@@
 \begin{theorem}[{\cite[Thm.~4.17]{PaluPilaudPlamondon-nonkissing}}]
+\label{thm:nonkissingAsso}
 For any non-kissing finite gentle quiver~$\quiver$, the set of cones

### 2019-02-11 thirdPaper/draft/typeConeAssociahedra.tex
Added examples.

@@
 \usepackage{tikz}
+\usepackage{tikz-cd}
 \usepackage{tkz-graph}
@@
 
-\begin{theorem}
+\begin{theorem}\label{theo::brick-algebra-condition}
  Let~$\Lambda$ be a brick algebra.
@@
 \subsubsection{Associative algebras}
+\begin{example}[A gentle algebra]
+ Consider the algebra~$\Lambda$ given the the path algebra of the quiver
+ \[
+  \begin{tikzcd}
+   1 \arrow[r, "\alpha"] & 2\arrow[r, "\beta"] & 3\arrow[r, "\gamma"] & 4
+  \end{tikzcd}
+ \]
+ modulo the relation~$\gamma\beta\alpha = 0$.  The Auslander--Reiten quiver of the extriangulated category~$K^{[-1, 0]}(\proj\Lambda)$ is depicted below.
+ \[
+ \hspace*{-1cm}
+ {\tiny
+  \begin{tikzcd}
+    &&&& (0\to P_4)\arrow[ddr] && (P_2\to 0)\arrow[ddr] && \\
+    && (0\to P_3)\arrow[dr] && (P_1\to 0)\arrow[dr] &&&& \\
+    & (0\to P_2)\arrow[dr]\arrow[ur] && (P_1\to P_3)\arrow[uur]\arrow[ur]\arrow[dr] && (P_2\to P_4)\arrow[uur]\arrow[dr] && (P_3\to 0)\arrow[dr] & \\
+    (0\to P_1) \arrow[ur] && (P_1\to P_2)\arrow[ur] && (P_2\to P_3)\arrow[ur]  && (P_3\to P_4)\arrow[ur] && (P_4\to 0)
+  \end{tikzcd}
+ }
+ \]
+ The Auslander--Reiten of the module category is obtained by taking the quotient by the ideal generated by the shifted projective modules.
+ \[
+ \hspace*{-1cm}
+ {\footnotesize
+  \begin{tikzcd}
+    &&&& \begin{matrix} 4\\3\\2 \end{matrix}\arrow[ddr] && \\
+    && \begin{matrix} 3\\2\\1 \end{matrix}\arrow[dr] &&&& \\
+    & \begin{matrix} 2\\1 \end{matrix}\arrow[dr]\arrow[ur] && \begin{matrix} 3\\2 \end{matrix}\arrow[uur]\arrow[dr] && \begin{matrix} 4\\3 \end{matrix}\arrow[dr] & \\
+    \begin{matrix} 1 \end{matrix} \arrow[ur] && \begin{matrix} 2 \end{matrix}\arrow[ur] && \begin{matrix} 3 \end{matrix}\arrow[ur] && \begin{matrix}4 \end{matrix}
+  \end{tikzcd}
+ }
+ \]
+ The conditions of Theorem~\ref{theo::brick-algebra-condition} are satisfied.
+
+\end{example}
+
+\begin{example}[Preprojective algebra of type~$A_3$]
+ Let~$\Lambda$ be the preprojective algebra of type~$A_3$: it is the path algebra of the quiver
+ \[
+ \begin{tikzcd}
+  1\arrow[r, shift left = 2pt, "\alpha"] & 2\arrow[l, shift left = 2pt, "\bar \alpha"] \arrow[r, shift left = 2pt, "\beta"]& 3\arrow[l, shift left = 2pt, "\bar \beta"]
+ \end{tikzcd}
+ \] 
+ modulo the relations~$\alpha \bar \alpha = 0$, $\bar \beta \beta = 0$ and~$\bar \alpha \alpha + \beta \bar \beta = 0$. 
+ The Auslander--Reiten quiver of the extriangulated category~$K^{[-1,0]}(\proj \Lambda)$ is depicted below.  Note that it is periodic.
+
+ \[
+  \hspace*{-2cm}
+ {\tiny
+  \begin{tikzcd}
+   (P_1 \to P_3)\arrow[dr] && (P_3\to P_2)\arrow[r]\arrow[dr] & (0\to P_3)\arrow[r]& (P_1\to P_3)\arrow[r]\arrow[dr] & (P_1\to 0)\arrow[r] & (P_2\to P_1)\arrow[dr]&& (P_1\to P_2) \\
+   (0\to P_2)\ar[r] & (P_2\to P_2)\arrow[ur]\arrow[dr]\arrow[r] & (P_2\to 0)\arrow[r] & (P_1\oplus P_3\to P_2)\arrow[ur]\arrow[dr] && (P_2\to P_1\oplus P_3)\arrow[ur]\arrow[dr]\arrow[r] & (0\to P_2)\arrow[r] & (P_2\to P_2)\arrow[ur]\arrow[dr]\arrow[r] & (P_2\to 0) \\
+   (P_2\to P_1)\arrow[ur] && (P_1\to P_2)\arrow[ur]\arrow[r] & (0\to P_1)\arrow[r] & (P_3\to P_1)\arrow[r]\arrow[ur] & (P_3\to 0)\arrow[r] & (P_2\to P_3)\arrow[ur] && (P_3\to P_2)
+  \end{tikzcd}
+  }
+ \]
+
+ The Auslander--Reiten quiver of the module category~$\MOD(\Lambda)$ can be obtained by applying the functor~$\Hom{}(\Lambda, -)$.
+
+ \[
+  \hspace*{-2cm}
+ {\footnotesize
+  \begin{tikzcd}
+   \begin{matrix} 3 \end{matrix}\arrow[dr] && \begin{matrix} 2 \\ 1 \end{matrix}\arrow[r]\arrow[dr] & \begin{matrix} 3 \\ 2 \\ 1 \end{matrix}\arrow[r]& \begin{matrix} 3 \\ 2 \end{matrix}\arrow[dr] && \begin{matrix} 1 \end{matrix}\arrow[dr]&& \begin{matrix} 2 \\ 3 \end{matrix} \\
+   \begin{matrix} 2 \\ 13 \\ 2 \end{matrix}\ar[r] & \begin{matrix} 2\\ 13 \end{matrix}\arrow[ur]\arrow[dr] && \begin{matrix} 2 \end{matrix}\arrow[ur]\arrow[dr] && \begin{matrix} 13\\2 \end{matrix}\arrow[ur]\arrow[dr]\arrow[r] & \begin{matrix} 2\\13\\2 \end{matrix}\arrow[r] & \begin{matrix} 2\\13 \end{matrix}\arrow[ur]\arrow[dr] &  \\
+   \begin{matrix} 1 \end{matrix}\arrow[ur] && \begin{matrix} 2\\3 \end{matrix}\arrow[ur]\arrow[r] & \begin{matrix} 1\\2\\3 \end{matrix}\arrow[r] & \begin{matrix} 1\\2 \end{matrix}\arrow[ur] && \begin{matrix} 3\\1 \end{matrix}\arrow[ur] && \begin{matrix} 2\\1 \end{matrix}
+  \end{tikzcd}
+  }
+ \]
+
+One can check directly that the condition of Theorem~\ref{theo::brick-algebra-condition} is not satisfied. 
+\end{example}
 

### 2019-02-12 thirdPaper/draft/typeConeAssociahedra.tex
a bit more on extricats - cannot compile, may have introduced errors

@@
 \captionsetup{width=\textwidth}
+
+\tikzlibrary{matrix,quotes,arrows.meta}
 
@@
 
-\begin{remark}
+\begin{remark}\label{remark::equivalence Sigma}
 For any~$T\in\ind(\tc)$, fix an extriangle~$T\infl 0\defl\susp T\overset{\eps_T}{\dashrightarrow}$, and extend those choices to the all of~$\tc$ by additivity.
@@
 \]
-which gives an equivalence of additive categories
+This gives an equivalence of additive categories
 \[
@@
 \]
-where~$\susp\tc$ is the full subcategory of~$\cat$ whose objects are of the form~$\susp T$, for some~$T\in\tc$.
+where~$\susp\tc$ is the full subcategory of~$\cat$ whose objects are isomorphic to objects of the form~$\susp T$, for some~$T\in\tc$.
 \end{remark}
+
+\begin{lemma}\label{lemma:: mphs in T are inflations}
+Every morphism in~$\tc$ is an inflation.
+\end{lemma}
+
+\begin{proof}
+Let~$T_1 \overset{t}{\to} T_0$ be a morphism in~$\tc$.
+Using the notation of Remark~\ref{remark::equivalence Sigma}, there is an extriangle~$T_1\infl 0\defl \susp T_1 \overset{\eps_{T_1}}{\dashrightarrow}$.
+Consider the extriangle~$T_0\overset{g}{\infl} X \overset{h}{\defl} \susp T_1 \overset{t_\ast\eps_{T_1}}{\dashrightarrow}$.
+By~\cite[Proposition 3.17]{NakaokaPalu}, there is a commutative diagram of extriangles
+\[
+\xy
+(-7,7)*+{T_1}="2";
+(7,7)*+{0}="4";
+(21,7)*+{\susp T_1}="6";
+(28,7)*+{}="8";
+%
+(-7,-7)*+{T_0}="12";
+(7,-7)*+{X}="14";
+(21,-7)*+{\susp T_1}="16";
+(28,-7)*+{}="18";
+%
+(-7,-21)*+{X}="22";
+(7,-21)*+{X}="24";
+%
+(-7,-28)*+{}="32";
+(7,-28)*+{}="34";
+%
+{\ar@{>->} "2";"4"};
+{\ar@{->>} "4";"6"};
+{\ar@{-->}^{\eps_{T_1}} "6";"8"};
+%
+{\ar@{>->}_{t'} "2";"12"};
+{\ar "4";"14"};
+{\ar@{=} "6";"16"};
+%
+{\ar^{g} "12";"14"};
+{\ar^{h} "14";"16"};
+{\ar@{-->}^{t_\ast\aps_{T_1}} "16";"18"};
+%
+{\ar_{g} "12";"22"};
+{\ar^{1} "14";"24"};
+%
+{\ar@{=} "22";"24"};
+%
+{\ar@{-->}^{h^\ast\eps_{T_1}} "22";"32"};
+{\ar@{-->} "24";"34"};
+%
+{\ar@{}|\circlearrowright "2";"14"};
+{\ar@{}|\circlearrowright "4";"16"};
+{\ar@{}|\circlearrowright "12";"24"};
+\endxy
+\]
+satisfying~$(t')_\ast\eps_{T_1}=t_\ast\eps_{T_1}$.
+We thus have~$t'=t$.
+\end{proof}
+
+\begin{remark}
+ It follows from the proof of Lemma~\ref{lemma:: mphs in T are inflations} that conditions (1), (2), (3) in Setting~\ref{setting::extricat} are equivalent to conditions (1), (2), (3'), where
+\[
+{\rm (3')} \ \ \ \cat = \tc\ast\susp\tc.
+\]
+\end{remark}
+
+\begin{proof}[Proof of Proposition~\ref{prop::KRextricat}]
+
+\end{proof}
+
+\begin{corollary}
+The objects in~$\susp\tc$ are precisely the injective objects in~$\cat$.
+\end{corollary}
 
@@
  \]
- The Auslander--Reiten of the module category is obtained by taking the quotient by the ideal generated by the shifted projective modules.
+ The Auslander--Reiten quiver of the module category is obtained by taking the quotient by the ideal generated by the shifted projective modules.
  \[

### 2019-02-12 thirdPaper/draft/typeConeAssociahedra.tex
typos
Replaces \aps by \eps
improvements Section 2.2

--- 2019-02-11 thirdPaper/draft/typeConeAssociahedra.tex
@@
 All these families contain the classical associahedra~$\Asso[n]$ constructed in~\cite{ShniderSternberg, Loday}.
-We first describe these associahedra and their type cones as they are the prototypes of our constructions.
 
@@
 \subsection{Classical associahedra}
+
+We first describe the associahedra of~\cite{ShniderSternberg, Loday} and their type cones as they are the prototypes of our constructions.
+
+\subsubsection{Associahedra and their normal fans}
 
@@
 
-From these linear dependencies, we obtain a redundant description of the type cone of the fan~$\gvectorFan[n]$.
+\subsubsection{Type cones of associahedra}
+
+From the linear dependencies of \cref{prop:exchangeablePairsAsso}, we obtain a redundant description of the type cone of the fan~$\gvectorFan[n]$.
 
@@
 
-For a seed~$\seed = (\B, \coefficients, \cluster)$ and a cluster variable~$x \in \seed$, the \defn{mutation} in direction~$x$ creates a new seed~$\mu_x(\seed) = \seed' = (\B', \coefficients', \cluster')$ where:
+For a seed~$\seed = (\B, \coefficients, \cluster)$ and a cluster variable~$x \in \cluster$, the \defn{mutation} in direction~$x$ creates a new seed~$\mu_x(\seed) = \seed' = (\B', \coefficients', \cluster')$ where:
 \begin{itemize}
@@
 %
-In this paper, we only consider \defn{finite type} cluster algebras, \ie those having only finitely many cluster variables.
+In this paper, we only consider \defn{finite type} cluster algebras, \ie those with a finite number~$N$ of cluster variables.
 It turns out that these finite type cluster algebras were classified by S.~Fomin and A.~Zelevinsky~\cite{FominZelevinsky-ClusterAlgebrasII} using the Cartan-killing classification for crystallographic root systems.
@@
 
-\para{Flips in the $\b{g}$-vector fan}
-%
-We now discuss the linear dependences between $\b{g}$-vectors of adjacent clusters.
+\para{Mutations in the $\b{g}$-vector fan}
+%
+We now discuss the linear dependences between $\b{g}$-vectors of adjacent seeds.
 The following proposition was stated in~\cite[Lem.~19]{HohlwegPilaudStella}.
@@
 
-Note that this statement is unfortunately less precise than \cref{prop:exchangeablePairsAsso}.
-Indeed, which of the two possible linear dependences is satisfied by the $\b{g}$-vectors of~$\cluster \cup \cluster'$ depends on the initial exchange matrix~$\B_\circ$.
-%In particular, the geometry of the $\b{g}$-vector fan~$\gvectorFan$ changes as $\B_\circ$ varies within a given mutation class.
-However, it already ensures that the type cone~$\typeCone(\gvectorFan[\B_\circ])$ of the $\b{g}$-vector fan contains the polyhedral cone of~$\b{h} \in \R^{\variables}$ such that
+Note that \cref{lem:linearDependencegvectorsCA} implies \cref{thm:generalizedAsso} since it ensures that the type cone~$\typeCone(\gvectorFan[\B_\circ])$ of the $\b{g}$-vector fan contains the cone of~${\b{h} \in \R^{\variables}}$ such that
 \(
@@
 for any seeds~$(\B, \coefficients, \cluster)$ and~$(\B', \coefficients', \cluster')$ with~${\cluster \ssm \{x\} = \cluster' \ssm \{x'\}}$.
-This is precisely where the vector~$\b{h}$ was chosen to ensure a realization in \cref{thm:generalizedAsso}.
+
+Unfortunately, \cref{lem:linearDependencegvectorsCA} is less precise than \cref{prop:exchangeablePairsAsso}.
+Indeed, which of the two possible linear dependences is satisfied by the $\b{g}$-vectors of~$\cluster \cup \cluster'$ depends on the initial exchange matrix~$\B_\circ$.
+We will prove however that it is independent of the seeds containing~$x$ and~$x'$.
+
+\begin{proposition}
+\label{prop:uniqueExchangePropertyCA}
+For any finite type exchange matrix~$\B_\circ$, the $\b{g}$-vector fan has the unique exchange relation property.
+\end{proposition}
+
+\subsubsection{Type cone of $\b{g}$-vector fans}
+
+The linear dependences of \cref{lem:linearDependencegvectorsCA} provide a redundant description of the type cone of the $\b{g}$-vector fan~$\gvectorFan[\B_\circ]$.
+We denote by~$\b{n}(\B_\circ, x, x')$ the normal vector of the inequality of the type cone corresponding to two exchangeable cluster variable~$x$ to~$x'$ (it is well defined by \cref{prop:uniqueExchangePropertyCA}.
+In other words, depending on which of the two linear dependences of \cref{lem:linearDependencegvectorsCA} holds, we have
+\[
+\b{n}(\B_\circ, x, x') \eqdef \b{f}_x + \b{f}_{x'} - \sum_{\substack{y \in \cluster \cap \cluster' \\ b_{xy} < 0}} -b_{xy} \, \b{f}_y
+\qquad\text{or}\qquad
+\b{n}(\B_\circ, x, x') \eqdef \b{f}_x + \b{f}_{x'} - \sum_{\substack{y \in \cluster \cap \cluster' \\ b_{xy} > 0}} b_{xy} \, \b{f}_y,
+\]
+where~$(\b{f}_x)_{x \in \variables}$ denotes the canonical basis of~$\R^{\variables}$.
+We obtain the following statement.
+
+\begin{corollary}
+\label{coro:typeConeCA}
+For any finite type exchange matrix~$\B_\circ$, the type cone of the $\b{g}$-vector fan~$\gvectorFan[\B_\circ]$ is given by
+\[
+\typeCone(\gvectorFan[\B_\circ]) = \set{\b{h} \in \R^{\variables}}{\dotprod{\b{n}(\B_\circ, x, x')}{\b{h}} > 0 \text{ for all exchangeable cluster variables } x, x'}.
+\]
+\end{corollary}
+
+In order to describe the facets of this type cone, we need the following special mutations.
+
+\begin{definition}
+Consider a seed~$(\B, \coefficients, \cluster)$ and a cluster variable~$x \in \cluster$.
+The mutation of~$\seed$ in direction~$x$ is a \defn{mesh mutation} if the entries~$b_{xy}$ for~$y \in X$ are all non-negative, or all non-positive.
+\end{definition}
+
+For instance, in the initial seed~$(\B_\circ, \coefficients_\circ, \cluster_\circ)$, the mutation in the direction of any variable~${x_\circ \in \cluster_\circ}$ is a mesh.
+% and the corresponding $\b{g}$-vector linear dependence is~$\gvectorFull{\B_\circ}{x_\circ} + \gvectorFull{\B_\circ}{x_\circ'} = 0$.
+%%, so that~$\b{n}(\B_\circ, x_\circ, x_\circ') = \b{f}_{x_\circ} + \b{f}_{x_\circ'}$. 
+We call these meshes \defn{initial}.
+The following statement describes the other meshes.
+
+\begin{lemma}
+\label{lem:bijectionMeshMutations}
+There is precisely one non-initial mesh directed by each positive $\b{c}$-vector of the cluster algebra. Therefore, the number of non-initial meshes is~$N-n$.
+\end{lemma}
+
+%The linear dependence among the $\b{g}$-vectors of an initial mesh is just~$\gvectorFull{\B_\circ}{x_\circ} + \gvectorFull{\B_\circ}{x_\circ'} = 0$.
+The following statement describes the linear dependence in any other mesh mutation.
+
+\begin{lemma}
+Consider two adjacent seeds~${(\B, \coefficients, \cluster)}$ and~${(\B', \coefficients', \cluster')}$ with~$\cluster \ssm \{x\} = \cluster' \ssm \{x'\}$ such that the entries~$b_{xy}$ for~$y \in X$ are all non-positive or all non-negative.
+If either~$x$ or~$x'$ is an initial cluster variable, then
+\[
+\gvectorFull{\B_\circ}{x} + \gvectorFull{\B_\circ}{x'} = 0.
+\]
+Otherwise, the $\b{g}$-vectors of~$\cluster \cup \cluster'$ with respect to~$\B_\circ$ satisfy the linear dependence
+\[
+\gvectorFull{\B_\circ}{x} + \gvectorFull{\B_\circ}{x'} = \sum_{y \in \cluster \cap \cluster'} |b_{xy}| \, \gvectorFull{\B_\circ}{y}.
+\]
+%\[
+%\b{n}(\B_\circ, x, x') = \b{f}_x + \b{f}_{x'} - \sum_{y \in \cluster \cap \cluster'} |b_{xy}| \, \b{f}_y
+%\]
+\end{lemma}
+
+Our main result states that the linear dependences between the $\b{g}$-vectors of any mutation can be decomposed into positive combinations of linear dependences arising from meshes.
+
+\begin{proposition}
+\label{prop:extremalExchangeablePairsCA}
+\end{proposition}
+
+Our next statement follws from~\cref{prop:extremalExchangeablePairsCA,lem:bijectionMeshMutations}.
+
+\begin{corollary}
+\label{coro:simplicialTypeConeCA}
+The type cone~$\typeCone(\gvectorFan[n])$ is simplicial.
+\end{corollary}
+
+Combining \cref{coro:simplicialTypeCone,coro:simplicialTypeConeCA,prop:extremalExchangeablePairsCA}, we derive the following description of all polytopal realizations of the $\b{g}$-vector fan~$\gvectorFan[\B_\circ]$.
+This result was stated in~\cite{BazierMatteDouvilleMousavandThomasYildirim} in the special situation of acyclic seeds in simply-laced types.
+
+\begin{theorem}
+For any finite type exchange matrix~$\B_\circ$, and for any~$\b{\ell} \in \R_{>0}^{N-n}$, the polytope
+\[
+R_{\b{\ell}}(\B_\circ) \eqdef \set{\b{z} \in \R^{\variables}}{...}
+\]
+is a generalized associahedron, whose normal fan is the $\b{g}$-vector fan~$\gvectorFan[\B_\circ]$.
+\end{theorem}
 

### 2019-02-12 thirdPaper/draft/typeConeAssociahedra.tex

@@
 \captionsetup{width=\textwidth}
+
+%\tikzlibrary{matrix,quotes,arrows.meta}
 
@@
 \]
-where~$\susp\tc$ is the full subcategory of~$\cat$ whose objects are of the form~$\susp T$, for some~$T\in\tc$.
+where~$\susp\tc$ is the full subcategory of~$\cat$ whose objects are isomorphic to objects of the form~$\susp T$, for some~$T\in\tc$.
 \end{remark}
+
+\begin{lemma}\label{lemma:: mphs in T are inflations}
+Every morphism in~$\tc$ is an inflation.
+\end{lemma}
+
+\begin{proof}
+Let~$T_1 \overset{t}{\to} T_0$ be a morphism in~$\tc$.
+Using the notation of Remark~\ref{remark::equivalence Sigma}, there is an extriangle~$T_1\infl 0\defl \susp T_1 \overset{\eps_{T_1}}{\dashrightarrow}$.
+Consider the extriangle~$T_0\overset{g}{\infl} X \overset{h}{\defl} \susp T_1 \overset{t_\ast\eps_{T_1}}{\dashrightarrow}$.
+By~\cite[Proposition 3.17]{NakaokaPalu}, there is a commutative diagram of extriangles
+\[
+\xy
+(-7,7)*+{T_1}="2";
+(7,7)*+{0}="4";
+(21,7)*+{\susp T_1}="6";
+(28,7)*+{}="8";
+%
+(-7,-7)*+{T_0}="12";
+(7,-7)*+{X}="14";
+(21,-7)*+{\susp T_1}="16";
+(28,-7)*+{}="18";
+%
+(-7,-21)*+{X}="22";
+(7,-21)*+{X}="24";
+%
+(-7,-28)*+{}="32";
+(7,-28)*+{}="34";
+%
+{\ar@{>->} "2";"4"};
+{\ar@{->>} "4";"6"};
+{\ar@{-->}^{\eps_{T_1}} "6";"8"};
+%
+{\ar@{>->}_{t'} "2";"12"};
+{\ar "4";"14"};
+{\ar@{=} "6";"16"};
+%
+{\ar^{g} "12";"14"};
+{\ar^{h} "14";"16"};
+{\ar@{-->}^{t_\ast\eps_{T_1}} "16";"18"};
+%
+{\ar_{g} "12";"22"};
+{\ar^{1} "14";"24"};
+%
+{\ar@{=} "22";"24"};
+%
+{\ar@{-->}^{h^\ast\eps_{T_1}} "22";"32"};
+{\ar@{-->} "24";"34"};
+%
+{\ar@{}|\circlearrowright "2";"14"};
+{\ar@{}|\circlearrowright "4";"16"};
+{\ar@{}|\circlearrowright "12";"24"};
+\endxy
+\]
+satisfying~$(t')_\ast\eps_{T_1}=t_\ast\eps_{T_1}$.
+We thus have~$t'=t$.
+\end{proof}
+
+\begin{remark}
+ It follows from the proof of Lemma~\ref{lemma:: mphs in T are inflations} that conditions (1), (2), (3) in Setting~\ref{setting::extricat} are equivalent to conditions (1), (2), (3'), where
+\[
+{\rm (3')} \ \ \ \cat = \tc\ast\susp\tc.
+\]
+\end{remark}
+
+\begin{proof}[Proof of Proposition~\ref{prop::KRextricat}]
+
+\end{proof}
+
+\begin{corollary}
+The objects in~$\susp\tc$ are precisely the injective objects in~$\cat$.
+\end{corollary}
 
@@
 \subsubsection{Associative algebras}
+\begin{example}[A gentle algebra]
+ Consider the algebra~$\Lambda$ given the the path algebra of the quiver
+ \[
+  \begin{tikzcd}
+   1 \arrow[r, "\alpha"] & 2\arrow[r, "\beta"] & 3\arrow[r, "\gamma"] & 4
+  \end{tikzcd}
+ \]
+ modulo the relation~$\gamma\beta\alpha = 0$.  The Auslander--Reiten quiver of the extriangulated category~$K^{[-1, 0]}(\proj\Lambda)$ is depicted below.
+ \[
+ \hspace*{-1cm}
+ {\tiny
+  \begin{tikzcd}
+    &&&& (0\to P_4)\arrow[ddr] && (P_2\to 0)\arrow[ddr] && \\
+    && (0\to P_3)\arrow[dr] && (P_1\to 0)\arrow[dr] &&&& \\
+    & (0\to P_2)\arrow[dr]\arrow[ur] && (P_1\to P_3)\arrow[uur]\arrow[ur]\arrow[dr] && (P_2\to P_4)\arrow[uur]\arrow[dr] && (P_3\to 0)\arrow[dr] & \\
+    (0\to P_1) \arrow[ur] && (P_1\to P_2)\arrow[ur] && (P_2\to P_3)\arrow[ur]  && (P_3\to P_4)\arrow[ur] && (P_4\to 0)
+  \end{tikzcd}
+ }
+ \]
+ The Auslander--Reiten quiver of the module category is obtained by taking the quotient by the ideal generated by the shifted projective modules.
+ \[
+ \hspace*{-1cm}
+ {\footnotesize
+  \begin{tikzcd}
+    &&&& \begin{matrix} 4\\3\\2 \end{matrix}\arrow[ddr] && \\
+    && \begin{matrix} 3\\2\\1 \end{matrix}\arrow[dr] &&&& \\
+    & \begin{matrix} 2\\1 \end{matrix}\arrow[dr]\arrow[ur] && \begin{matrix} 3\\2 \end{matrix}\arrow[uur]\arrow[dr] && \begin{matrix} 4\\3 \end{matrix}\arrow[dr] & \\
+    \begin{matrix} 1 \end{matrix} \arrow[ur] && \begin{matrix} 2 \end{matrix}\arrow[ur] && \begin{matrix} 3 \end{matrix}\arrow[ur] && \begin{matrix}4 \end{matrix}
+  \end{tikzcd}
+ }
+ \]
+ The conditions of Theorem~\ref{theo::brick-algebra-condition} are satisfied.
+
+\end{example}
+
+\begin{example}[Preprojective algebra of type~$A_3$]
+ Let~$\Lambda$ be the preprojective algebra of type~$A_3$: it is the path algebra of the quiver
+ \[
+ \begin{tikzcd}
+  1\arrow[r, shift left = 2pt, "\alpha"] & 2\arrow[l, shift left = 2pt, "\bar \alpha"] \arrow[r, shift left = 2pt, "\beta"]& 3\arrow[l, shift left = 2pt, "\bar \beta"]
+ \end{tikzcd}
+ \] 
+ modulo the relations~$\alpha \bar \alpha = 0$, $\bar \beta \beta = 0$ and~$\bar \alpha \alpha + \beta \bar \beta = 0$. 
+ The Auslander--Reiten quiver of the extriangulated category~$K^{[-1,0]}(\proj \Lambda)$ is depicted below.  Note that it is periodic.
+
+ \[
+  \hspace*{-2cm}
+ {\tiny
+  \begin{tikzcd}
+   (P_1 \to P_3)\arrow[dr] && (P_3\to P_2)\arrow[r]\arrow[dr] & (0\to P_3)\arrow[r]& (P_1\to P_3)\arrow[r]\arrow[dr] & (P_1\to 0)\arrow[r] & (P_2\to P_1)\arrow[dr]&& (P_1\to P_2) \\
+   (0\to P_2)\ar[r] & (P_2\to P_2)\arrow[ur]\arrow[dr]\arrow[r] & (P_2\to 0)\arrow[r] & (P_1\oplus P_3\to P_2)\arrow[ur]\arrow[dr] && (P_2\to P_1\oplus P_3)\arrow[ur]\arrow[dr]\arrow[r] & (0\to P_2)\arrow[r] & (P_2\to P_2)\arrow[ur]\arrow[dr]\arrow[r] & (P_2\to 0) \\
+   (P_2\to P_1)\arrow[ur] && (P_1\to P_2)\arrow[ur]\arrow[r] & (0\to P_1)\arrow[r] & (P_3\to P_1)\arrow[r]\arrow[ur] & (P_3\to 0)\arrow[r] & (P_2\to P_3)\arrow[ur] && (P_3\to P_2)
+  \end{tikzcd}
+  }
+ \]
+
+ The Auslander--Reiten quiver of the module category~$\MOD(\Lambda)$ can be obtained by applying the functor~$\Hom{}(\Lambda, -)$.
+
+ \[
+  \hspace*{-2cm}
+ {\footnotesize
+  \begin{tikzcd}
+   \begin{matrix} 3 \end{matrix}\arrow[dr] && \begin{matrix} 2 \\ 1 \end{matrix}\arrow[r]\arrow[dr] & \begin{matrix} 3 \\ 2 \\ 1 \end{matrix}\arrow[r]& \begin{matrix} 3 \\ 2 \end{matrix}\arrow[dr] && \begin{matrix} 1 \end{matrix}\arrow[dr]&& \begin{matrix} 2 \\ 3 \end{matrix} \\
+   \begin{matrix} 2 \\ 13 \\ 2 \end{matrix}\ar[r] & \begin{matrix} 2\\ 13 \end{matrix}\arrow[ur]\arrow[dr] && \begin{matrix} 2 \end{matrix}\arrow[ur]\arrow[dr] && \begin{matrix} 13\\2 \end{matrix}\arrow[ur]\arrow[dr]\arrow[r] & \begin{matrix} 2\\13\\2 \end{matrix}\arrow[r] & \begin{matrix} 2\\13 \end{matrix}\arrow[ur]\arrow[dr] &  \\
+   \begin{matrix} 1 \end{matrix}\arrow[ur] && \begin{matrix} 2\\3 \end{matrix}\arrow[ur]\arrow[r] & \begin{matrix} 1\\2\\3 \end{matrix}\arrow[r] & \begin{matrix} 1\\2 \end{matrix}\arrow[ur] && \begin{matrix} 3\\1 \end{matrix}\arrow[ur] && \begin{matrix} 2\\1 \end{matrix}
+  \end{tikzcd}
+  }
+ \]
+
+One can check directly that the condition of Theorem~\ref{theo::brick-algebra-condition} is not satisfied. 
+\end{example}
 

### 2019-02-15 secondPaper/FPSAC/nonkissing-noncrossing-FPSAC.tex

@@
 
-\begin{theorem*}[\ref{thm:bijectionLocallyGentleAndSurfaces}]
+\begin{theorem*}[see Thm.~\ref{thm:bijectionLocallyGentleAndSurfaces}]
 There is an explicit bijection between the set of isomorphism classes of locally gentle bound quivers and the set of homeomorphism classes of oriented punctured marked surfaces with boundary endowed with a pair of dual cellular dissections.
@@
 
-\begin{theorem*}[\ref{thm:complexesCoincide}]
+\begin{theorem*}[see Thm.~\ref{thm:complexesCoincide}]
 The complexes~$\NKC$ and~$\NCC$ are isomorphic.
@@
 We say that~$\omega$ and~$\omega'$ are \defn{kissing} if~$\omega$ kisses~$\omega'$ or~$\omega'$ kisses~$\omega$ (or both).
-We authorize the situation where the common finite substring is reduced to a vertex~$a$, meaning that~$a$ is a peak of~$\omega$ and a deep of~$\omega'$.
+We allow the situation where the common finite substring is reduced to a vertex~$a$, meaning that~$a$ is a peak of~$\omega$ and a deep of~$\omega'$.
 Note also that~$\omega$ can kiss~$\omega'$ several times, that~$\omega$ and~$\omega'$ can mutually kiss, and that~$\omega$ can kiss itself.
@@
 The \defn{non-kissing complex} of~$\bar Q$ is the simplicial complex~$\NKC$ whose faces are the sets of pairwise non-kissing walks of~$\bar Q$.
-Note that self-kissing walks are forbidden.
+Note that self-kissing walks are excluded from the vertex set of this complex.
 %Note that self-kissing walks never appear in~$\NKC$ by definition.
@@
 The \defn{$\dissection$-accordion complex}~$\AC$ is the simplicial complex whose faces are the sets of pairwise non-crossing $\dissection$-accordions.
-Note that self-crossing accordions are~forbidden.
+Note that self-crossing accordions are~excluded from the vertex set of this complex.
 %Note that self-crossing accordions never appear in~$\AC$ by definition.

### 2019-02-15 thirdPaper/draft/typeConeAssociahedra.tex
Very minor corrections.
modified setting for extricat: removed KS

@@
 \section{Relations for~$\b{g}$-vectors in brick algebras via extriangulated categories}
-
+\label{sect::extricats}
 %%%%
@@
 
-In this section, we let~$\cat$ be a Krull--Schmidt, extriangulated category with a fixed full additive \yann{additive contains strictly full + stable under taking summands} subcategory~$\tc$ satisfying the following three properties:
+\noindent {\bf Setting for Section~\ref{sect::prelim on extricats}}
+In that section, we let~$\cat$ be an extriangulated category with a fixed full additive \yann{additive contains strictly full + stable under taking summands} subcategory~$\tc$ satisfying the following three properties:
 \begin{enumerate}
@@
 \end{enumerate}
+
+\noindent {\bf Setting for Section~\ref{sect::Statment extricats}}
+We that section, we keep the previous setting, but assume moreover that~$\cat$ is Krull--Schmidt, Ext-finite, and has Auslander--Reiten--Serre duality.
 
@@
 \subsection{Statement of preliminary results on extriangulated categories}
-\label{subsection: prelim on extricats}
+\label{sect::prelim on extricats}
+
+So as to be able to state the main theorem of Section~\ref{sect::extricats}, we need a few results on extriangulated categories.
+However, all proofs are postpone to Section~\ref{sect::proofs extricats}.
 
@@
 \subsection{Statement of the theorem}
+\label{sect::Statment extricats}
 
@@
 \subsection{Proof of Theorem~\ref{theorem::extricats}}
+\label{sect::proofs extricats}
 

### 2019-02-15 thirdPaper/draft/typeConeAssociahedra.tex
corrected setting

@@
 \noindent {\bf Setting for Section~\ref{sect::Statment extricats}}
-We that section, we keep the previous setting, but assume moreover that~$\cat$ is Krull--Schmidt, Ext-finite, and has Auslander--Reiten--Serre duality.
+In that section, we keep the previous setting, but assume moreover that~$\cat$ is Krull--Schmidt, $\field$-linear, Ext-finite, and has Auslander--Reiten--Serre duality, and that the subcategory~$\tc$ is of the form~$\add T$, where~$T=T_1\oplus\cdots\oplus T_n$ is a basic object.
 
@@
 We know from~\cite{} that the indecomposable objects of~$K^{[-1,0]}(\proj \Lambda)$ are in natural bijection with the indecomposable~$\Lambda$-modules and with the shifted indecomposable projective~$\Lambda$-modules.
-Thus is has finitely many isomorphism classes of indecomposable objects if and only if~$\Lambda$ is representation-finite.
+Thus it has finitely many isomorphism classes of indecomposable objects if and only if~$\Lambda$ is representation-finite.
 This gives a setting in which to apply Theorem~\ref{}.

### 2019-02-15 thirdPaper/draft/typeConeAssociahedra.tex
notation

@@
 Assume that~$\cat$ is a~$\field$-linear, Ext-finite, Krull--Schmidt, extriangulated category with Auslander--Reiten--Serre duality.
-Assume that~$T$ is a projective object of~$\cat$ such that any~$X\in\cat$ admits an extriangle~$T_1^X\infl T_0^X\defl X\dashrightarrow$ with~$T_0^X, T_1^X\in\add(T)$, and for any~$T'\in\add(T)$ the morphism~$T'\to 0$ is an inflation.
+Assume that~$T$ is a projective object of~$\cat$ such that any~$X\in\cat$ admits an extriangle~$T_1^X\infl T_0^X\defl X\dashrightarrow$ with~$T_0^X, T_1^X\in\add(T)$, and the morphism~$T\to 0$ is an inflation.
+Fix a conflation~$T\to 0 \to \susp T$.
 Then~$\cat$ has only finitely many isomorphism classes of indecomposable objects if and only if the set

### 2019-02-15 thirdPaper/draft/typeConeAssociahedra.tex
notation
rk

@@
 
+\vspace{.4cm}
 \noindent {\bf Setting for Section~\ref{sect::prelim on extricats}}
@@
 \begin{notation}
-For any indecomposable object~$T\in\tc$, we fix an extriangle~$T\infl 0 \defl \susp T \dashrightarrow$.
-Extending by additivity, this defines (uniquely up to isomorphism) an object~$\susp T$, for each object~$T\in\tc$.
+For any object~$T\in\tc$, we fix an extriangle~$T\infl 0 \defl \susp T \dashrightarrow$.
+% Extending by additivity, this defines (uniquely up to isomorphism) an object~$\susp T$, for each object~$T\in\tc$.
 \end{notation}

### 2019-02-16 thirdPaper/draft/typeConeAssociahedra.tex
More on section 4.5.3.

@@
 \subsubsection{$2$-term complexes of projective modules}\label{sect::Kbproj}
-Let~$\Lambda$ be an Artin algebra.
-Then the homotopy category~$K^b(\proj \Lambda)$ is a triangulated category, and its full subcategory~$K^{[-1,0]}(\proj \Lambda)$ of complexes concentrated in degrees~$-1$ and~$0$ is closed under extensions.
-Therefore, it is an extriangulated category.
-
-We know from~\cite{} that the indecomposable objects of~$K^{[-1,0]}(\proj \Lambda)$ are in natural bijection with the indecomposable~$\Lambda$-modules and with the shifted indecomposable projective~$\Lambda$-modules.
-Thus it has finitely many isomorphism classes of indecomposable objects if and only if~$\Lambda$ is representation-finite.
-This gives a setting in which to apply Theorem~\ref{}.
-
-\pg{Add introducing paragraph}
+Let~$\Lambda$ be a finite-dimensional algebra over a field~$\field$.
+Then the homotopy category~$K^b(\proj \Lambda)$ is a triangulated category, and we consider its full subcategory~$K^{[-1,0]}(\proj \Lambda)$ of complexes concentrated in degrees~$-1$ and~$0$.
+
+\begin{proposition}\label{prop::2kbproj-is-extriangulated}
+ Let~$\Lambda$ be any Artin algebra.
+Then the category~$K^{[-1,0]}(\proj \Lambda)$ is an extriangulated category satisfying the assumptions (1) to (3) of Section~\ref{setting::extricat}, wiht~$\tc = \add(\Lambda)$.
+If, moreover,~$\Lambda$ is finite-dimensional over a field~$\field$, then~$K^{[-1,0]}(\proj \Lambda)$ satisfies all assumptions of Section~\ref{setting::extricat}.
+\end{proposition}
+\begin{proof}
+ The category~$K^{[-1,0]}(\proj \Lambda)$ is closed under extensions in~$K^b(\proj \Lambda)$, so it is an extriangulated category whose conflations are induced by triangles in~$K^b(\proj\Lambda)$ by~\cite[Remark 2.18]{NakaokaPalu}.
+Now, the object~$\Lambda$ is projective in~$K^{[-1,0]}(\proj \Lambda)$, since if~$X\infl Y\defl Z$ is a conflation, then we get a long exact sequence
+ \[
+  \Hom{K^b}(\Lambda,Y)\to \Hom{K^b}(\Lambda,Z) \to  \Hom{K^b}(\Lambda, \susp X),
+ \]
+ and the last term vanishes, since~$\susp X$ is a complex concentrated in degrees~$-2$ and~$-1$, while~$\Lambda$ is in degree~$0$.  This proves that~$\Lambda$ is projective.
+
+ The morphism~$\Lambda \to 0$ is an inflation, since~$\Lambda\infl 0 \defl \susp \Lambda$ is a conflation.
+Moreover, if~$X= P_1\xrightarrow{f}P_0$ is an object of~$K^{[-1,0]}(\proj\Lambda)$, then it lies in a conflation~$P_1\stackrel{f}{\infl} P_0 \defl X$ by definition.
+We have proved that properties~(1) t0 (3) of Section~\ref{setting::extricat} are satisfied.
+
+ Finally, assume that~$\Lambda$ is finite-dimensional over a field~$\field$.
+Then~$K^{[-1,0]}(\proj\Lambda)$ is Krull--Schmidt,~$\field$-linear and Ext-finite, since this is true for~$K^b(\proj\Lambda)$ for any finite-dimensional algebra~$\Lambda$.
+Moreover, it has Auslander--Reiten--Serre duality by~\cite[Proposition 6.1]{IyamaNakaokaPalu}.
+\end{proof}
+
+Proposition~\ref{prop::2kbproj-is-extriangulated} gives a setting in which to apply Theorem~\ref{}.
 
 \begin{theorem}\label{theo::brick-algebra-condition}
- Let~$\Lambda$ be a brick algebra.
+ Let~$\Lambda$ be a brick algebra which is finite-dimensional over a field~$\field$\pg{True for any Artin algebra?}.
 Then the almost-split conflations of~$K^{[-1,0]}(\proj \Lambda)$ are mutation conflations if and only if for any indecomposable~$\Lambda$-module~$M$, the space~$\Hom{\Lambda}(M, \tau^2 M)$ vanishes.
 \end{theorem}
-\begin{proof}
- \pg{TO DO}
+
+\begin{lemma}\label{lemm::AR-conflations-and-sequences}
+ Let~$\Lambda$ be any Artin algebra.
+Let~$X\infl Y\defl Z$ be an almost-split conflation in~$K^{[-1,0]}(\proj \Lambda)$ such that~$Z$ is not in~$\add(\susp \Lambda)$.
+Denote by~$F$ the functor~$\Hom{K^b}(\Lambda, -):K^{[-1,0]}(\proj \Lambda) \to \MOD \Lambda$.
+Then there is an almost-split sequence
+ \[
+  0\to FX\to FY \to FZ \to 0
+ \]
+ in~$\MOD\Lambda$.
+\end{lemma}
+\begin{proof}
+
+\end{proof}
+
+\begin{lemma}\label{lemm::if-AR-sequences-are-mutation}
+ Let~$\Lambda$ be an Artin algebra.
+Assume that for any almost-split conflation~$\tau X \infl E \defl X$ of~$K^{[-1,0]}(\proj\Lambda)$, we have that~$\Hom{K^b}(X, \susp E) = \Hom{K^b}(E, \susp X) = 0$ and~$\Hom{K^b}(\tau X, \susp E) = \Hom{K^b}(E, \susp \tau X) = 0$.
+Then for any indecomposable~$\Lambda$-module~$M$, we have that~$\Hom{\Lambda}(M, \tau^2 M)$ vanishes.
+\end{lemma}
+\begin{proof}
+
 \end{proof}

### 2019-02-21 thirdPaper/draft/typeConeAssociahedra.tex
cleaning

@@
 \subsection{Statement of the theorem}
-We need to introduce some notations before stating the main result of this section.  Let~$\Lambda:= \End{\cat}(T)$, and let~$F$ be the functor
-\[
- F=\cat(T,-):\cat \xrightarrow{} \MOD \Lambda.
+We need to introduce some notations before stating the main result of this section.  Let~$\Lambda\eqdef \End{\cat}(T)$, and let~$F$ be the functor
+\[
+F = \cat(T,-): \cat \xrightarrow{} \MOD \Lambda.
 \]
@@
  \[
-  \langle X, Y \rangle := \dim_{\field} \Hom{\Lambda}(FX,FY).
+  \langle X, Y \rangle \eqdef \dim_{\field} \Hom{\Lambda}(FX,FY).
  \]
@@
  \[
-  \ell_X := [X] + [\susp^{-1} X]  - [E] \in \Ksp(\cat).
+  \ell_X \eqdef [X] + [\susp^{-1} X]  - [E] \in \Ksp(\cat).
  \]
@@
  \[
-  r_Y := [Y] + [\susp Y]  - [E'] \in \Ksp(\cat).
+  r_Y \eqdef [Y] + [\susp Y]  - [E'] \in \Ksp(\cat).
  \]
@@
 \begin{theorem}\label{theo::relations-g-vecteurs}
- Let~$\cat$ be a category satisying the hypotheses of Section \ref{sect::setting}.
-Then~$\cat$ has only finitely many isomorphism classes of indecomposable objects if and only if the set~\[L:=\big\{\ell_X \ | \ X\in \ind(\cat)\setminus \add(\susp T) \big\}\] generates the kernel of~$\b g:\Ksp(\cat) \to \Kg(\cat)$.
+ Let~$\cat$ be a category satisying the hypotheses of Section \ref{sect::setting}.  Then~$\cat$ has only finitely many isomorphism classes of indecomposable objects if and only if the set
+ \[
+ L \eqdef \bigset{\ell_X}{X\in \ind(\cat) \ssm \add(\susp T)}
+ \]
+ generates the kernel of~$\b g:\Ksp(\cat) \to \Kg(\cat)$. 
  In this case, the set~$L$ is a basis of the kernel of~$\b g$, and for any $x\in \ker(\b g)$, we have that
  \[
-  x= \sum_{A\in \ind(\cat) \setminus \add(\susp T)} \frac{\langle x, A \rangle}{\langle \ell_A, A \rangle} \ell_A.
+  x= \sum_{A\in \ind(\cat) \ssm \add(\susp T)} \frac{\langle x, A \rangle}{\langle \ell_A, A \rangle} \ell_A.
  \]
@@
 Let~$X\xrightarrow{} E \xrightarrow{} Y \xrightarrow{h} \susp X$ be a triangle with~$h\in (\susp T)$.
-Then the element~$x=[X]+[Y]-[E]$ of the kernel of~$\b g$ is a non-negative linear combination of the~$\ell_A$, with~$A\in \ind(\cat)\setminus \add(\susp T)$.
+Then the element~$x=[X]+[Y]-[E]$ of the kernel of~$\b g$ is a non-negative linear combination of the~$\ell_A$, with~$A\in \ind(\cat)\ssm \add(\susp T)$.
 \end{corollary}
 \begin{proof}
- We know that~$x=\sum_{A\in \ind(\cat)\setminus \add(\susp T)} \frac{\langle x, [A] \rangle}{\langle \ell_A, [A] \rangle} \ell_A$; since~$\langle \ell_A, [A] \rangle$ is positive by Lemma~\ref{lemm::bilinear-form}, we only need to show that each~$\langle x, [A] \rangle$ is non-negative.
+ We know that~$x=\sum_{A\in \ind(\cat) \ssm \add(\susp T)} \frac{\langle x, [A] \rangle}{\langle \ell_A, [A] \rangle} \ell_A$; since~$\langle \ell_A, [A] \rangle$ is positive by Lemma~\ref{lemm::bilinear-form}, we only need to show that each~$\langle x, [A] \rangle$ is non-negative.
  The functor~$F=\cat(T,-)$ induces an exact sequence
@@
  \[
-  \ind_T(X) := [T_0^X] - [T_1^X] \in \Ksp(\add(T)).
+  \ind_T(X) \eqdef [T_0^X] - [T_1^X] \in \Ksp(\add(T)).
  \]
@@
 \begin{lemma}\label{lemm::coefficients}
- Let~$x\in \Ksp(\cat)$, and write~\[x=\sum_{A\in \ind(\cat)} \lambda_A [A].\]  Then for any~$A\in\ind(\cat)\setminus \add(\susp T)$, we have that
+ Let~$x\in \Ksp(\cat)$, and write~\[x=\sum_{A\in \ind(\cat)} \lambda_A [A].\]  Then for any~$A\in\ind(\cat) \ssm \add(\susp T)$, we have that
  \[
@@
 \begin{proof}
- Let~$B\in \ind(\cat) \setminus \add(\susp T)$.  Applying Lemma~\ref{lemm::bilinear-form}, we get that
+ Let~$B\in \ind(\cat) \ssm \add(\susp T)$.  Applying Lemma~\ref{lemm::bilinear-form}, we get that
  \[
@@
  \[
-  x = \sum_{A\in \ind(\cat)\setminus \add(\susp T)} \frac{\langle \ell_A, x \rangle}{\langle \ell_A, A \rangle}[A] + \sum_{i=1}^n \lambda_{\susp T_i} [\susp T_i] = \sum_{i=1}^n \lambda_{\susp T_i} [\susp T_i].
+  x = \sum_{A\in \ind(\cat) \ssm \add(\susp T)} \frac{\langle \ell_A, x \rangle}{\langle \ell_A, A \rangle}[A] + \sum_{i=1}^n \lambda_{\susp T_i} [\susp T_i] = \sum_{i=1}^n \lambda_{\susp T_i} [\susp T_i].
  \]
@@
  \begin{enumerate}
-  \item The set~$\{[\ell_A] \ | \ A\in \ind(\cat) \setminus \add(\susp T) \} \cup \{[\susp T_i] \ | \ i=1, \ldots, n\}$ is free in~$\Ksp(\cat)$.
-  \item The set~$\{[r_A] \ | \ A\in \ind(\cat) \setminus \add(\susp T) \} \cup \{[\susp T_i] \ | \ i=1, \ldots, n\}$ is free in~$\Ksp(\cat)$.
+  \item The set~$\set{[\ell_A]}{A\in \ind(\cat) \ssm \add(\susp T)} \cup \set{[\susp T_i]}{i=1, \dots, n}$ is free in~$\Ksp(\cat)$.
+  \item The set~$\set{[r_A]}{A\in \ind(\cat) \ssm \add(\susp T)} \cup \set{[\susp T_i]}{i=1, \dots, n}$ is free in~$\Ksp(\cat)$.
  \end{enumerate}
@@
  \[
-  x= \sum_{A\in \ind(\cat) \setminus \add(\susp T)} \lambda_A \ell_A + \sum_{i=1}^n \lambda_i [\susp T_i] = 0.
- \]
- Then~$\langle x, [A] \rangle = 0$ for all~$A\in\ind(\cat) \setminus \add(\susp T)$.  But~$\langle x, [A] \rangle = \lambda_A$ by Lemma~\ref{lemm::bilinear-form}.  Thus~
+  x= \sum_{A\in \ind(\cat) \ssm \add(\susp T)} \lambda_A \ell_A + \sum_{i=1}^n \lambda_i [\susp T_i] = 0.
+ \]
+ Then~$\langle x, [A] \rangle = 0$ for all~$A\in\ind(\cat) \ssm \add(\susp T)$.  But~$\langle x, [A] \rangle = \lambda_A$ by Lemma~\ref{lemm::bilinear-form}.  Thus~
  \[
@@
 \begin{proposition}
- Assume that~$\ind(\cat)$ is finite.  Then the set~$\{[\ell_A] \ | \ A\in \ind(\cat) \setminus \add(\susp T) \}$ is a basis of the kernel of~$\b g$.  Moreover, for any~$x\in \ker \b g$, we have that
- \[
-  x= \sum_{A\in \ind(\cat) \setminus \add(\susp T)} \frac{\langle x, A \rangle}{\langle \ell_A, A \rangle} \ell_A.
+ Assume that~$\ind(\cat)$ is finite.  Then the set~$\set{[\ell_A]}{A\in \ind(\cat) \ssm \add(\susp T)}$ is a basis of the kernel of~$\b g$.  Moreover, for any~$x\in \ker \b g$, we have that
+ \[
+  x= \sum_{A\in \ind(\cat) \ssm \add(\susp T)} \frac{\langle x, A \rangle}{\langle \ell_A, A \rangle} \ell_A.
  \]
@@
 \[
- z = x- \sum_{A\in \ind(\cat) \setminus \add(\susp T)} \frac{\langle x, A \rangle}{\langle \ell_A, A \rangle} \ell_A.
+ z = x- \sum_{A\in \ind(\cat) \ssm \add(\susp T)} \frac{\langle x, A \rangle}{\langle \ell_A, A \rangle} \ell_A.
 \]
@@
 \[
- \langle  z, [B] \rangle = \Big\langle x- \sum_{A\in \ind(\cat) \setminus \add(\susp T)} \frac{\langle x, A \rangle}{\langle \ell_A, A \rangle} \ell_A, [B] \Big\rangle = \langle x, [B] \rangle - \langle x, [B] \rangle = 0,
+ \langle  z, [B] \rangle = \Big\langle x- \sum_{A\in \ind(\cat) \ssm \add(\susp T)} \frac{\langle x, A \rangle}{\langle \ell_A, A \rangle} \ell_A, [B] \Big\rangle = \langle x, [B] \rangle - \langle x, [B] \rangle = 0,
 \]
@@
 \begin{corollary}
- If~$\ind(\cat)$ is finite, then the set~\[\{[\ell_A] \ | \ A\in \ind(\cat) \setminus \add(\susp T) \} \cup \{[\susp T_i] \ | \ i=1, \ldots, n\}\] is a basis of~$\Ksp(\cat)$.
+ If~$\ind(\cat)$ is finite, then the set
+ \[
+ \set{[\ell_A]}{A\in \ind(\cat) \ssm \add(\susp T)} \cup \set{[\susp T_i]}{i=1, \ldots, n}
+ \]
+ is a basis of~$\Ksp(\cat)$.
 \end{corollary}
@@
 \begin{proposition}
- Assume that the set~$\{[\ell_A] \ | \ A\in \ind(\cat) \setminus \add(\susp T) \}$ is a basis of the kernel of~$\b g$. Then~$\ind(\cat)$ is finite.
+ Assume that the set~$\set{[\ell_A]}{A\in \ind(\cat) \ssm \add(\susp T)}$ is a basis of the kernel of~$\b g$. Then~$\ind(\cat)$ is finite.
 \end{proposition}
@@
 \[
-\langle X,Y\rangle := \dim_\field \Hom{\tc}(FX,FY) = \dim_\field \cat/(\susp\tc)(X,Y).
+\langle X,Y\rangle \eqdef \dim_\field \Hom{\tc}(FX,FY) = \dim_\field \cat/(\susp\tc)(X,Y).
 \]
@@
 \[
- \ell_X := [X]+[Y]-[E]\in\Ksp(\cat).
+ \ell_X \eqdef [X]+[Y]-[E]\in\Ksp(\cat).
 \]
@@
 \[
- L:=\left\{\ell_X \ | \ X\in \ind(\cat)\setminus \add(\susp T) \right\}
+L \eqdef \bigset{\ell_X}{X\in \ind(\cat) \ssm \add(\susp T)}
 \]
@@
  \[
-  x= \sum_{A\in \ind(\cat) \setminus \add(\susp T)} \frac{\langle x, A \rangle}{\langle \ell_A, A \rangle} \ell_A.
+  x= \sum_{A\in \ind(\cat) \ssm \add(\susp T)} \frac{\langle x, A \rangle}{\langle \ell_A, A \rangle} \ell_A.
  \]
@@
 Let~$X\infl E\defl Y\dashrightarrow$ be any extriangle.
-Then the element~$x=[X]+[Y]-[E]$ of the kernel of~$\b g$ is a non-negative linear combination of the~$\ell_A$, with~$A\in\ind(\cat)\setminus\add(\susp T)$.
+Then the element~$x=[X]+[Y]-[E]$ of the kernel of~$\b g$ is a non-negative linear combination of the~$\ell_A$, with~$A\in\ind(\cat)\ssm \add(\susp T)$.
 \end{corollary}

### 2019-02-21 thirdPaper/draft/typeConeAssociahedra.tex
improve section 2

@@
 \newcommandx{\clusterAlgebra}[2][1=\B_\circ, 2=\coefficients_\circ]{\mathcal{A}\!\left(#1,#2\right)} % cluster algebra
-\newcommandx{\principalClusterAlgebra}[1][1=\B_\circ]{\mathcal{A}_{\mathrm{pr}}\left(#1\right)} % principal coefficients cluster algebra
+\newcommandx{\principalClusterAlgebra}[1][1=\B_\circ]{\mathcal{A}\left(#1\right)} % principal coefficients cluster algebra
+\newcommandx{\principalVariables}[1][1=\B_\circ]{\mathcal{V}(#1)} % all variables, principal case
 \newcommandx{\coefficientFreeClusterAlgebra}[1][1=\B_\circ]{\mathcal{A}_{\mathrm{fr}}(#1)} % coefficient free cluster algebra
@@
 \newcommand{\fundamentalWeight}{\omega} % fundamental weights
+\newcommandx{\meshes}[1][1=\B_\circ]{\mathcal{M}\!\left(#1\right)} % meshes
 
@@
 
-\subsection{Coherent fans}
+\subsection{Unique exchange property}
+\label{subsec:uniqueExchangeProperty}
 
@@
 
-\begin{proposition}
-\label{prop:associahedronLoday}
+\begin{theorem}
+\label{thm:associahedronLoday}
 The associahedron~$\Asso[n]$ can be described equivalently as:
@@
 \item the convex hull of the points~$L(T) \in \R^{n+1}$ for all rooted binary trees~$T$ with~$n+1$ internal nodes, where the $i$th coordinate of~$L(T)$ is the product of the number of leaves in the left subtree by the number of leaves in the right subtree of the $i$th node of~$T$ in inorder~\cite{Loday},
-\item the intersection of the hyperplane~$\bigset{\b{x} \in \R^{n+1}}{\sum_{\ell \in [n+1]} x_\ell = \binom{n+2}{2}}$ with the halfspaces $\bigset{\b{x} \in \R^{n+1}}{\sum_{i \le \ell \le j} x_\ell \ge \binom{j-i+2}{2}}$ for all proper intervals~$[i,j]$ of~$[n+1]$,~\cite{ShniderSternberg},
+\item the intersection of the hyperplane~$\bigset{\b{x} \in \R^{n+1}}{\sum_{\ell \in [n+1]} x_\ell = \binom{n+2}{2}}$ with the halfspaces $\bigset{\b{x} \in \R^{n+1}}{\sum_{a < \ell < b} x_\ell \ge \binom{b-a+2}{2}}$ for all internal diagonal~$(a,b)$ of \mbox{the $(n+3)$-gon~\cite{ShniderSternberg}},
 \item the Minkowski sum of the faces~$\simplex_{[i,j]}$ of the standard $n$-dimensional simplex~$\simplex$ corresponding to all proper intervals~$[i,j]$ of~$[n+1]$,~\cite{Postnikov}.
 \end{itemize}
-\end{proposition}
+\end{theorem}
 
@@
 
-\begin{proposition}
-\label{prop:normalFanLoday}
+\begin{theorem}
+\label{thm:normalFanLoday}
 In the normal fan~$\gvectorFan[n]$ of~$\Asso[n]$, 
 \begin{itemize}
-\item the normal vector of the facet corresponding to an internal diagonal~$(a,b)$ of the $(n+3)$-gon is the vector~$\gvector{a,b} \eqdef \pi\big( \sum_{a < \ell < b} \b{e}_\ell \big) = (n+1) \sum_{a < \ell < b} \b{e}_\ell - (j-i+1) \sum_{1 \le \ell \le n+1} \b{e}_\ell$.
+\item the normal vector of the facet corresponding to an internal diagonal~$(a,b)$ of the $(n+3)$-gon is the vector~$\gvector{a,b} \eqdef \pi\big( \sum_{a < \ell < b} \b{e}_\ell \big) = (n+1) \sum_{a < \ell < b} \b{e}_\ell - (b-a+1) \sum_{1 \le \ell \le n+1} \b{e}_\ell$.
 \item the normal cone of the vertex corresponding to a rooted binary tree~$T$ is the incidence cone~$\bigset{\b{x} \in \HH}{x_i \le x_j \text{ for all edges $i \to j$ in $T$}}$.
 \end{itemize}
-\end{proposition}
-
-Let us also recall the linear dependencies in this fan and observe that it has the unique exchange property.
+\end{theorem}
+
+Let us also recall the linear dependencies in this fan and observe that it has the unique exchange property discussed in \cref{subsec:uniqueExchangeProperty}.
 From now on, we use the convention that~$\gvector{a,b} = 0$ when~$(a,b)$ is a boundary edge of the $(n+3)$-gon.
@@
 
-The following statement follows from the end of the previous proof.
+Our next statement follows from the end of the previous proof.
 
@@
 More recently in~\cite{BazierMatteDouvilleMousavandThomasYildirim}, V.~Bazier-Matte, G.~Douville, K.~Mousavand, H.~Thomas and E.~Yildirim extended the construction of associahedra of~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} to acyclic seeds of simply laced finite type cluster algebras.
-Here, we extend the construction of~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} to any finite type (simply laced or not) cluster algebra with respect to any seed (acyclic or not) by showing that the type cone of the $\b{g}$-vector fan of any finite type cluster algebra is simplicial.
+Here, we extend the construction of~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} to any finite type (simply laced or not) cluster algebra with respect to any seed (acyclic or not) by providing a direct proof that the type cone of the $\b{g}$-vector fan of any finite type cluster algebra is simplicial.
 
@@
 	p_y\negativeExponents{p_x}^{b_{xy}}  & \text{if } y \neq x' \text{ and } b_{xy} \leq 0, \\
-	p_y\positiveExponents{p_x}^{b_{xy}}  & \text{if } y \neq x' \text{ and } b_{xy} > 0,
+	p_y\positiveExponents{p_x}^{b_{xy}}  & \text{if } y \neq x' \text{ and } b_{xy} > 0.
 \end{cases}
@@
 We denote by~$\variables$ the collection of all cluster variables in the seeds mutationally equivalent to an initial seed~$\seed_\circ = (\B_\circ, \coefficients_\circ, \cluster_\circ)$ with cluster variables~$\cluster_\circ = \{x_1, \dots, x_n\}$.
-
-\begin{definition}[{\cite[Def.~2.11]{FominZelevinsky-ClusterAlgebrasIV}}]
-The (geometric type) \defn{cluster algebra} $\clusterAlgebra$ is the $\Z\Trop{m}$-subring of~$\Q(x_1, \dots, x_n, p_1, \dots, p_m)$ generated by~$\variables$.
-% all the cluster variables in all the seeds mutationally equivalent to an initial seed~$\seed_\circ = (\B_\circ, \coefficients_\circ, \cluster_\circ)$ with cluster variables~$\cluster_\circ = \{x_1, \dots, x_n\}$.
-\end{definition}
-
+The (geometric type) \defn{cluster algebra} $\clusterAlgebra$ is the $\Z\Trop{m}$-subring of~$\Q(x_1, \dots, x_n, p_1, \dots, p_m)$ generated by the cluster variables in~$\variables$.
 The \defn{cluster complex} of~$\clusterAlgebra$ is the simplicial complex whose vertices are the cluster variables of~$\clusterAlgebra$ and whose facets are the clusters of~$\clusterAlgebra$.
@@
 
-The cluster complex of a finite cluster algebra~$\clusterAlgebra$ is independent of the choice of coefficients and of the choice of the initial seed (as long at it remains in the same mutation class), and therefore only depends on the cluster type of~$\clusterAlgebra$ (\ie the Cartan type of~$\A(\B)$ in \cref{thm:finiteTypeClassification}).
-Moreover, for~$\B_\circ^\vee \eqdef -\transpose{\B_\circ}$, then the map sending a cluster variable~$x$ in a seed~$\seed$ of~$\clusterAlgebra$ to the cluster variable~$x^\vee$ in the seed~$\seed^\vee$ of~$\principalClusterAlgebra[\B_\circ^\vee]$ obtained by the same sequence of mutations defines a natural isomorphism between the cluster complexes of~$\clusterAlgebra$ and~$\clusterAlgebra[\B_\circ^\vee]$.
+The cluster complex of a finite type cluster algebra~$\clusterAlgebra$ is independent of the choice of coefficients and of the choice of the initial seed (as long at it remains in the same mutation class), and therefore only depends on the cluster type of~$\clusterAlgebra$ (\ie the Cartan type of~$\A{\B}$ in \cref{thm:finiteTypeClassification}).
+Moreover, for~$\B_\circ^\vee \eqdef -\transpose{\B_\circ}$, then the map sending a cluster variable~$x$ in a seed~$\seed$ of~$\clusterAlgebra$ to the cluster variable~$x^\vee$ in the seed~$\seed^\vee$ of~$\clusterAlgebra[\B_\circ^\vee]$ obtained by the same sequence of mutations defines a natural isomorphism between the cluster complexes of~$\clusterAlgebra$ and~$\clusterAlgebra[\B_\circ^\vee]$.
 
@@
 We now consider principal coefficients to define the $\b{g}$- and $\b{c}$-vectors.
-
-\begin{definition}[{\cite[Def.~3.1]{FominZelevinsky-ClusterAlgebrasIV}}]
-The cluster algebra with \defn{principal coefficients} at~$\B_\circ$ is the cluster algebra~$\principalClusterAlgebra \eqdef \clusterAlgebra[\B_\circ][\coefficients_\circ]$ in~$\Q(x_1, \dots, x_n, p_1, \dots, p_n)$, where~$\coefficients_\circ = \{p_x\}_{x \in \cluster_\circ}$ are precisely the generators~$p_1, \dots, p_n$ of~$\Trop{n}$ relabeled by~$\cluster_\circ$.
-\end{definition}
-
+As defined in~\cite[Def.~3.1]{FominZelevinsky-ClusterAlgebrasIV}, the cluster algebra with \defn{principal coefficients} at~$\B_\circ$ is the cluster algebra~$\clusterAlgebra[\B_\circ][\coefficients_\circ]$ in~$\Q(x_1, \dots, x_n, p_1, \dots, p_n)$, where~$\coefficients_\circ = \{p_x\}_{x \in \cluster_\circ}$ are precisely the generators~$p_1, \dots, p_n$ of~$\Trop{n}$ relabeled by~$\cluster_\circ$.
+For simplicity, we drop the mention of the coefficients for principal cluster algebras in the notations for seeds~$\seed = (\B, \cluster)$, for cluster algebras~$\principalClusterAlgebra$ and for variables~$\principalVariables$.
 Principal coefficients cluster algebras are $\Z^n$-graded (in the fundamental weight basis~$\{\omega_x\}_{x \in \cluster_\circ}$ of~$V$) for the degree function~$\deg(\B_\circ,\cdot)$ on $\principalClusterAlgebra$ is obtained by setting
@@
 %
-The following statement is well known.
-\vincent{Explain}
+The following statement is well known and admits several possible proofs as discussed in~\cite[Sect.~4]{HohlwegPilaudStella}.
 Examples are illustrated in \cref{fig:clusterFans}.
@@
 Moreover, this fan is known to be polytopal.
-More precisely, consider a vector~$\b{h} \in \R^{\variables}$ such that
+More precisely, consider a vector~$\b{h} \in \R^{\principalVariables}$ such that
 \[
@@
 \]
-for any adjacent seeds~$(\B, \coefficients, \cluster)$ and~$(\B', \coefficients', \cluster')$ with~$\cluster \ssm \{x\} = \cluster' \ssm \{x'\}$.
+for any adjacent seeds~$(\B, \cluster)$ and~$(\B', \cluster')$ with~$\cluster \ssm \{x\} = \cluster' \ssm \{x'\}$.
 Such a vector~$\b{h}$ exists, see the discussion in~\cite[Prop.~28]{HohlwegPilaudStella}.
@@
 \label{lem:linearDependencegvectorsCA}
-For any finite type~exchange matrix~$\B_\circ$ and any adjacent seeds~${(\B, \coefficients, \cluster)}$ and~${(\B', \coefficients', \cluster')}$ in $\principalClusterAlgebra$ with~$\cluster \ssm \{x\} = \cluster' \ssm \{x'\}$, the $\b{g}$-vectors of~$\cluster \cup \cluster'$ with respect to~$\B_\circ$ satisfy precisely one of the following two linear dependences
+For any finite type~exchange matrix~$\B_\circ$ and any adjacent seeds~${(\B, \cluster)}$ and~${(\B', \cluster')}$ in $\principalClusterAlgebra$ with~$\cluster \ssm \{x\} = \cluster' \ssm \{x'\}$, the $\b{g}$-vectors of~$\cluster \cup \cluster'$ with respect to~$\B_\circ$ satisfy precisely one of the following two linear dependences
 \[
@@
 
-Note that \cref{lem:linearDependencegvectorsCA} implies \cref{thm:generalizedAsso} since it ensures that the type cone~$\typeCone(\gvectorFan[\B_\circ])$ of the $\b{g}$-vector fan contains the cone of~${\b{h} \in \R^{\variables}}$ such that
+Note that \cref{lem:linearDependencegvectorsCA} implies \cref{thm:generalizedAsso} since it ensures that the type cone~$\typeCone(\gvectorFan[\B_\circ])$ of the $\b{g}$-vector fan contains the cone of~${\b{h} \in \R^{\principalVariables}}$ such that
 \(
@@
 \)
-for any seeds~$(\B, \coefficients, \cluster)$ and~$(\B', \coefficients', \cluster')$ with~${\cluster \ssm \{x\} = \cluster' \ssm \{x'\}}$.
+for any seeds~$(\B, \cluster)$ and~$(\B', \cluster')$ with~${\cluster \ssm \{x\} = \cluster' \ssm \{x'\}}$.
 
@@
 The linear dependences of \cref{lem:linearDependencegvectorsCA} provide a redundant description of the type cone of the $\b{g}$-vector fan~$\gvectorFan[\B_\circ]$.
-We denote by~$\b{n}(\B_\circ, x, x')$ the normal vector of the inequality of the type cone corresponding to two exchangeable cluster variable~$x$ to~$x'$ (it is well defined by \cref{prop:uniqueExchangePropertyCA}.
+We denote by~$\b{n}(\B_\circ, x, x')$ the normal vector of the inequality of the type cone corresponding to two exchangeable cluster variable~$x$ to~$x'$ (it is well defined by \cref{prop:uniqueExchangePropertyCA}).
 In other words, depending on which of the two linear dependences of \cref{lem:linearDependencegvectorsCA} holds, we have
@@
 \]
-where~$(\b{f}_x)_{x \in \variables}$ denotes the canonical basis of~$\R^{\variables}$.
+where~$(\b{f}_x)_{x \in \principalVariables}$ denotes the canonical basis of~$\R^{\principalVariables}$.
 We obtain the following statement.
@@
 \[
-\typeCone(\gvectorFan[\B_\circ]) = \set{\b{h} \in \R^{\variables}}{\dotprod{\b{n}(\B_\circ, x, x')}{\b{h}} > 0 \text{ for all exchangeable cluster variables } x, x'}.
+\typeCone(\gvectorFan[\B_\circ]) = \set{\b{h} \in \R^{\principalVariables}}{\dotprod{\b{n}(\B_\circ, x, x')}{\b{h}} > 0 \text{ for all exchangeable cluster variables } x, x'}.
 \]
@@
 \begin{definition}
-Consider a seed~$(\B, \coefficients, \cluster)$ and a cluster variable~$x \in \cluster$.
-The mutation of~$\seed$ in direction~$x$ is a \defn{mesh mutation} if the entries~$b_{xy}$ for~$y \in X$ are all non-negative, or all non-positive.
+Consider a seed~$(\B, \cluster)$ and a cluster variable~$x \in \cluster$.
+The mutation of~$\seed$ in direction~$x$ is a \defn{mesh mutation} if the entries~$b_{xy}$ for~$y \in \cluster$ are all non-negative, or all non-positive.
 \end{definition}
 
-For instance, in the initial seed~$(\B_\circ, \coefficients_\circ, \cluster_\circ)$, the mutation in the direction of any variable~${x_\circ \in \cluster_\circ}$ is a mesh.
-% and the corresponding $\b{g}$-vector linear dependence is~$\gvectorFull{\B_\circ}{x_\circ} + \gvectorFull{\B_\circ}{x_\circ'} = 0$.
-%%, so that~$\b{n}(\B_\circ, x_\circ, x_\circ') = \b{f}_{x_\circ} + \b{f}_{x_\circ'}$. 
+For instance, in the initial seed~$(\B_\circ, \cluster_\circ)$, the mutation in the direction of any variable~${x_\circ \in \cluster_\circ}$ is a mesh.
 We call these meshes \defn{initial}.
+We denote by~$\meshes$ the set of all pairs~$(x,x')$ where~$x$ and~$x'$ are two non-initial cluster variables of~$\principalClusterAlgebra$ which are exchangeable via a mesh mutation.
 The following statement describes the other meshes.
@@
 \label{lem:bijectionMeshMutations}
-There is precisely one non-initial mesh directed by each positive $\b{c}$-vector of the cluster algebra. Therefore, the number of non-initial meshes is~$N-n$.
+There is precisely one non-initial mesh directed by each positive $\b{c}$-vector of the cluster algebra~$\principalClusterAlgebra$. Therefore~$|\principalVariables| = |\meshes| + n$.
 \end{lemma}
 
-%The linear dependence among the $\b{g}$-vectors of an initial mesh is just~$\gvectorFull{\B_\circ}{x_\circ} + \gvectorFull{\B_\circ}{x_\circ'} = 0$.
-The following statement describes the linear dependence in any other mesh mutation.
+The following statement describes the linear dependence in the mesh mutations.
 
 \begin{lemma}
-Consider two adjacent seeds~${(\B, \coefficients, \cluster)}$ and~${(\B', \coefficients', \cluster')}$ with~$\cluster \ssm \{x\} = \cluster' \ssm \{x'\}$ such that the entries~$b_{xy}$ for~$y \in X$ are all non-positive or all non-negative.
+\label{lem:dependenceMesh}
+Consider two adjacent seeds~${(\B, \cluster)}$ and~${(\B', \cluster')}$ with~$\cluster \ssm \{x\} = \cluster' \ssm \{x'\}$ such that the entries~$b_{xy}$ for~$y \in \cluster$ are all non-positive or all non-negative.
 If either~$x$ or~$x'$ is an initial cluster variable, then
@@
 
+For~$(x,x') \in \meshes$ and~$y \in \principalVariables$, we denote by~$\alpha_{x,x',y}$ the coefficient of~$\gvectorFull{\B_\circ}{y}$ in the linear dependence between the $\b{g}$-vectors~$\gvectorFull{\B_\circ}{x}$ and~$\gvectorFull{\B_\circ}{x'}$.
+In other words, according to \cref{lem:dependenceMesh}, if~${(\B, \cluster)}$ and~${(\B', \cluster')}$ are two adjacent seeds with~$\cluster \ssm \{x\} = \cluster' \ssm \{x'\}$, we have~$\alpha_{x,x',y} = |b_{xy}|$ for~$y \in \cluster \cap \cluster'$ and~$\alpha_{x,x',y} = 0$ otherwise.
+
 Our main result states that the linear dependences between the $\b{g}$-vectors of any mutation can be decomposed into positive combinations of linear dependences arising from meshes.
@@
 \label{prop:extremalExchangeablePairsCA}
-\end{proposition}
-
-Our next statement follws from~\cref{prop:extremalExchangeablePairsCA,lem:bijectionMeshMutations}.
+For any finite type exchange matrix~$\B_\circ$ (acyclic or not), the non-initial mesh mutations precisely correspond to the extremal exchangeable pairs of the $\b{g}$-vector fan~$\gvectorFan[\B_\circ]$.
+\end{proposition}
+
+This statement will be proved in full generality in \cref{???}.
+We proved it in \cref{prop:extremalExchangeablePairsAsso} for acyclic initial seeds in type~$A$. To provide an intuition of the result, we sketch here a proof for arbitrary initial seeds in type~$A$.
+
+\begin{proof}[Sketch of \cref{prop:extremalExchangeablePairsCA} in type~$A$]
+We need to prove that the normal vector~$\b{n}(\B_\circ, y, y')$ for any exchangeable pair~$\{y,y'\}$ is a positive linear combination of the vectors~$\b{n}(\B_\circ, x, x')$ for non-initial meshes.
+\vincent{Do we really want to do that?}
+\end{proof}
+
+Our next statement follows from~\cref{prop:extremalExchangeablePairsCA,lem:bijectionMeshMutations}.
 
@@
 This result was stated in~\cite{BazierMatteDouvilleMousavandThomasYildirim} in the special situation of acyclic seeds in simply-laced types.
+Note that our proof is quite different from~\cite{BazierMatteDouvilleMousavandThomasYildirim} as it relies on our type cone approach.
 
 \begin{theorem}
-For any finite type exchange matrix~$\B_\circ$, and for any~$\b{\ell} \in \R_{>0}^{N-n}$, the polytope
-\[
-R_{\b{\ell}}(\B_\circ) \eqdef \set{\b{z} \in \R^{\variables}}{...}
+For any finite type exchange matrix~$\B_\circ$, and for any~$\b{\ell} \in \R_{>0}^{\meshes}$, the polytope
+\[
+R_{\b{\ell}}(\B_\circ) \eqdef \Bigset{\b{z} \in \R^{\principalVariables}}{\b{z} \ge 0 \text{ and } \b{z}_x + \b{z}_{x'} = \sum_{y \in \principalVariables} \alpha_{x,x',y} \, \b{z}_{y} \text{ for all } (x,x') \in \meshes}
 \]
@@
 \end{theorem}
-
-\newpage
-
-\begin{remark}
-One important observation is that it seems there is one extremal exchangeable pair for each positive $c$-vector, meaning that for each positive $c$-vector~$\beta$, there is precisely one extremal exchangeable pair~$\{x,x'\}$ of cluster variables for which the flip of~$x$ to~$x'$ (for any pair of clusters~$\{X,X'\}$ with~$X \ssm \{x\} = X' \ssm \{x'\}$) is in the direction of~$\beta$.
-The goal is thus to determine for each positive root which exchangeable pair is extremal.
-This should be done using the Auslander-Reiten quiver to construct two cluster variables from a $c$-vector (see the next paragraph for the idea).
-\end{remark}
-
-\newpage
 

### 2019-02-26 thirdPaper/draft/typeConeAssociahedra.tex
merge

--- 2019-02-16 thirdPaper/draft/typeConeAssociahedra.tex
@@
 \captionsetup{width=\textwidth}
-
-%\tikzlibrary{matrix,quotes,arrows.meta}
 
@@
 
-\begin{lemma}
+\begin{lemma}\label{lemma::first consequences}
 The following holds:
@@
 (21,7)*+{\susp T_1}="6";
-(28,7)*+{}="8";
+(32,7)*+{}="8";
 %
@@
 (21,-7)*+{\susp T_1}="16";
-(28,-7)*+{}="18";
+(32,-7)*+{}="18";
 %
@@
 %
-(-7,-28)*+{}="32";
-(7,-28)*+{}="34";
+(-7,-32)*+{}="32";
+(7,-32)*+{}="34";
 %
@@
 \end{corollary}
+
+\begin{proof}
+First note that any injective object belongs to~$\susp \tc$, by Lemma~\ref{lemma::shifts of extriangles}.
+Let us prove that the converse holds.
+Let~$\susp T \infl X \overset{f}{\defl} Y\overset{\delta}{\dashrightarrow}$ be an extriangle with~$T\in\tc$.
+Since~$\cat(-,\susp T)|_\tc = 0$ and~$f$ is~$\tc$-epic, the morphism~$\cat(-,f)_\tc$ is an isomorphism in~$\modt$.
+By Proposition~\ref{prop::KRextricat}, there are morphisms~$Y\overset{s}{\to} X$,~$Y\xrightarrow{h}\susp T'$,~$\susp T'\xrightarrow{t} Y$, for some~$T'\in\tc$ satisfying
+\[
+fs = id_Y + th.
+\]
+By Lemma~\ref{lemma::first consequences} (e),~$\susp\tc$ is a rigid subcategory so that~$t^\ast\delta=0$.
+Equivalently, there is a morphism~$\susp T'\xrightarrow{k} X$ such that~$t=fk$.
+We thus have~$f(s-kh)=id_Y$, showing that the extriangle splits.
+\end{proof}
 

### 2019-02-26 thirdPaper/draft/typeConeAssociahedra.tex
index extricat

@@
 In particular, if $\tc=\add T$, then $\End{\cat}(T)$ is a finite-dimensional~$\field$-algebra.
-It thus also follows that Definition~\ref{defi::bilinear form} still makes sense in this more general settup: For any~$X,Y\in\cat$,
+It thus also follows that Definition~\ref{defi::bilinear form} still makes sense in this more general setup: For any~$X,Y\in\cat$,
 \[
@@
 \begin{remark}\label{remark::equivalence Sigma}
-For any~$T\in\ind(\tc)$, fix an extriangle~$T\infl 0\defl\susp T\overset{\eps_T}{\dashrightarrow}$, and extend those choices to the all of~$\tc$ by additivity.
+For any~$T\in\tc$, fix an extriangle~$T\infl 0\defl\susp T\overset{\eps_T}{\dashrightarrow}$.
 As noticed in Lemma~\ref{lemma::shifts of extriangles}, for any morphism~$T\overset{f}{\to}T'$ in~$\tc$, there is a unique morphism~$\susp f\in\cat(\susp T,\susp T')$ such that~$f_\ast\eps_T=(\susp f)^\ast\eps_{T'}$, as illustrated below:
@@
 \begin{lemma}\label{lemma:: mphs in T are inflations}
-Every morphism in~$\tc$ is an inflation.
+Every morphism with domain in~$\tc$ is an inflation.
 \end{lemma}
@@
 \begin{proof}
-Let~$T_1 \overset{t}{\to} T_0$ be a morphism in~$\tc$.
-Using the notation of Remark~\ref{remark::equivalence Sigma}, there is an extriangle~$T_1\infl 0\defl \susp T_1 \overset{\eps_{T_1}}{\dashrightarrow}$.
-Consider the extriangle~$T_0\overset{g}{\infl} X \overset{h}{\defl} \susp T_1 \overset{t_\ast\eps_{T_1}}{\dashrightarrow}$.
+Let~$T \overset{t}{\to} X$ be a morphism with $T\in \tc$.
+Using the notation of Remark~\ref{remark::equivalence Sigma}, there is an extriangle~$T\infl 0\defl \susp T \overset{\eps_T}{\dashrightarrow}$.
+Consider the extriangle~$X\overset{g}{\infl} Y \overset{h}{\defl} \susp T \overset{t_\ast\eps_T}{\dashrightarrow}$.
 By~\cite[Proposition 3.17]{NakaokaPalu}, there is a commutative diagram of extriangles
@@
 \xy
-(-7,7)*+{T_1}="2";
+(-7,7)*+{T}="2";
 (7,7)*+{0}="4";
-(21,7)*+{\susp T_1}="6";
+(21,7)*+{\susp T}="6";
 (32,7)*+{}="8";
 %
-(-7,-7)*+{T_0}="12";
-(7,-7)*+{X}="14";
-(21,-7)*+{\susp T_1}="16";
+(-7,-7)*+{X}="12";
+(7,-7)*+{Y}="14";
+(21,-7)*+{\susp T}="16";
 (32,-7)*+{}="18";
 %
-(-7,-21)*+{X}="22";
-(7,-21)*+{X}="24";
+(-7,-21)*+{Y}="22";
+(7,-21)*+{Y}="24";
 %
@@
 %
-{\ar@{>->} "2";"4"};
-{\ar@{->>} "4";"6"};
-{\ar@{-->}^{\eps_{T_1}} "6";"8"};
-%
-{\ar@{>->}_{t'} "2";"12"};
+{\ar@{->} "2";"4"};
+{\ar@{->} "4";"6"};
+{\ar@{-->}^{\eps_T} "6";"8"};
+%
+{\ar@{->}_{t'} "2";"12"};
 {\ar "4";"14"};
@@
 {\ar^{h} "14";"16"};
-{\ar@{-->}^{t_\ast\eps_{T_1}} "16";"18"};
+{\ar@{-->}^{t_\ast\eps_T} "16";"18"};
 %
@@
 %
-{\ar@{-->}^{h^\ast\eps_{T_1}} "22";"32"};
+{\ar@{-->}^{h^\ast\eps_T} "22";"32"};
 {\ar@{-->} "24";"34"};
@@
 \]
-satisfying~$(t')_\ast\eps_{T_1}=t_\ast\eps_{T_1}$.
+satisfying~$(t')_\ast\eps_T=t_\ast\eps_T$.
 We thus have~$t'=t$.
@@
 \begin{proof}[Proof of Proposition~\ref{prop::KRextricat}]
-
+Recall that~$F:\cat\to\modt$ denotes the functor sending an object~$X$ to the module~$\cat(-,X)|_\tc$.
+By Lemma~\ref{lemma::first consequences} (e), the ideal~$(\susp\tc)$ of morphisms factoring through an object in~$\susp\tc$ is included in the kernel of~$F$.
+Conversely, let~$X\xrightarrow{f}Y$ be such that~$Ff=0$.
+By Lemma~\ref{lemma::shifts of extriangles}, there is a conflation~$T_0\overset{g}{\infl} X\overset{h}{\defl} \susp T_1$ with~$T_0,T_1\in\tc$.
+By assumption, the composition~$f\circ g$ vanishes, which implies that~$f$ factors through~$\susp T_1$.
+The functor~$F$ thus induces a faithful functor, still denoted~$F$, from~$\cat/(\susp\tc)$ to~$\modt$.
+It is well-known (see for instance~\cite[Lemma 3.1]{AssemSimsonSkowronski}) that~$F$ restricts to an equivalence of categories~$\tc\to\proj\tc$.
+Because~$\tc$ consists of projective objects in~$\cat$, the image under~$F$ of every conflation is a right exact sequence.
+The fact that~$F$ is full and dense can thus be proven as in the case of triangulated categories, by using Lemma~\ref{lemma:: mphs in T are inflations}.
 \end{proof}
@@
 Let~$\susp T \infl X \overset{f}{\defl} Y\overset{\delta}{\dashrightarrow}$ be an extriangle with~$T\in\tc$.
-Since~$\cat(-,\susp T)|_\tc = 0$ and~$f$ is~$\tc$-epic, the morphism~$\cat(-,f)_\tc$ is an isomorphism in~$\modt$.
+Since~$\cat(-,\susp T)|_\tc = 0$ and~$f$ is~$\tc$-epic, the morphism~$\cat(-,f)|_\tc$ is an isomorphism in~$\modt$.
 By Proposition~\ref{prop::KRextricat}, there are morphisms~$Y\overset{s}{\to} X$,~$Y\xrightarrow{h}\susp T'$,~$\susp T'\xrightarrow{t} Y$, for some~$T'\in\tc$ satisfying
@@
 \]
-By Lemma~\ref{lemma::first consequences} (e),~$\susp\tc$ is a rigid subcategory so that~$t^\ast\delta=0$.
+By Lemma~\ref{lemma::first consequences} (e)~$\susp\tc$ is a rigid subcategory, so that~$t^\ast\delta=0$.
 Equivalently, there is a morphism~$\susp T'\xrightarrow{k} X$ such that~$t=fk$.
 We thus have~$f(s-kh)=id_Y$, showing that the extriangle splits.
+\end{proof}
+
+\begin{lemma}
+ The index is well-defined.
+More precisely, for any object~$X\in\cat$ and any two conflations~$T_1\overset{f}{\infl} T_0 \overset{g}{\defl} X$,~$T'_1\overset{f'}{\infl} T'_0 \overset{g'}{\defl} X$ with~$T_0,T_1,T'_0,T'_1\in\tc$, we have~$[T_0]-[T_1]=[T'_0]-[T'_1]$ in~$\kzero{\tc}$.
+\end{lemma}
+
+\begin{proof}
+Applying~\cite[Proposition 3.15]{NakaokaPalu} gives a commutative diagram made of conflations
+\[
+\xy
+%
+(-7,21)*+{T_1}="-12";
+(7,21)*+{T_1}="-14";
+%
+(-21,7)*+{T'_1}="0";
+(-7,7)*+{Y}="2";
+(7,7)*+{T_0}="4";
+%
+(-21,-7)*+{T'_1}="10";
+(-7,-7)*+{T'_0}="12";
+(7,-7)*+{X}="14";
+%
+{\ar@{=} "-12";"-14"};
+%
+{\ar "-12";"2"};
+{\ar "-14";"4"};
+%
+{\ar "0";"2"};
+{\ar "2";"4"};
+%
+{\ar@{=} "0";"10"};
+{\ar "2";"12"};
+{\ar "4";"14"};
+%
+{\ar "10";"12"};
+{\ar "12";"14"};
+%
+{\ar@{}|\circlearrowright "-12";"4"};
+{\ar@{}|\circlearrowright "0";"12"};
+{\ar@{}|\circlearrowright "2";"14"};
+\endxy
+\]
+Since the objects in~$\tc$ are projective, the two conflations with middle term~$Y$ split and there are isomorphisms~$T'_1\oplus T_0 \cong Y \cong T_1\oplus T'_0$.
+The equality~$[T'_1]+[T_0]=[T_1]+[T'_0]$ thus holds in~$\kzero{\tc}$.
+\end{proof}
+
+\begin{lemma}
+ The index descends to~$\kzero{\cat}$: For any conflation~$X\infl Y\defl Z$ in~$\cat$, we have~$\ind_\tc Y = \ind_\tc X + \ind_\tc Z$ in~$\kzero{\tc}$.
+\end{lemma}
+
+\begin{proof}
+Let~$X\infl Y\defl Z$ be a conflation in~$\cat$.
+Fix conflations~$T_1^X \infl T_0^X \defl X$,~$T_1^Z\infl T_0^Z \defl Z$ with~$T_0^X, T_1^X, T_0^Z, T_1^Z\in\tc$.
+By~\cite[Proposition 3.15]{NakaokaPalu} and axiom (ET4)$^{\mathrm{op}}$, there are commutative diagrams of conflations
+\[
+\xy
+%
+(-7,21)*+{T^Z_1}="-12";
+(7,21)*+{T^Z_1}="-14";
+%
+(-21,7)*+{X}="0";
+(-7,7)*+{X\oplus T^Z_0}="2";
+(7,7)*+{T^Z_0}="4";
+%
+(-21,-7)*+{X}="10";
+(-7,-7)*+{Y}="12";
+(7,-7)*+{Z}="14";
+%
+{\ar@{=} "-12";"-14"};
+%
+{\ar "-12";"2"};
+{\ar "-14";"4"};
+%
+{\ar "0";"2"};
+{\ar "2";"4"};
+%
+{\ar@{=} "0";"10"};
+{\ar "2";"12"};
+{\ar "4";"14"};
+%
+{\ar "10";"12"};
+{\ar "12";"14"};
+%
+{\ar@{}|\circlearrowright "-12";"4"};
+{\ar@{}|\circlearrowright "0";"12"};
+{\ar@{}|\circlearrowright "2";"14"};
+\endxy
+\ \ \ \
+\xy
+(-21,7)*+{T^X_1}="0";
+(-7,7)*+{B}="2";
+(7,7)*+{T^Z_1}="4";
+%
+(-21,-7)*+{T^X_1}="10";
+(-7,-7)*+{T^X_0\oplus T^Z_0}="12";
+(7,-7)*+{X\oplus T^Z_0}="14";
+%
+(-7,-21)*+{Y}="22";
+(7,-21)*+{Y}="24";
+%
+%
+{\ar "0";"2"};
+{\ar "2";"4"};
+%
+{\ar@{=} "0";"10"};
+{\ar "2";"12"};
+{\ar "4";"14"};
+%
+{\ar "10";"12"};
+{\ar "12";"14"};
+%
+{\ar "12";"22"};
+{\ar "14";"24"};
+%
+{\ar@{=} "22";"24"};
+%
+{\ar@{}|\circlearrowright "0";"12"};
+{\ar@{}|\circlearrowright "2";"14"};
+{\ar@{}|\circlearrowright "12";"24"};
+\endxy
+\]
+where we have used the fact that~$T_0^Z$ is projective in~$\cat$.
+Moreover, the conflation with middle term~$B$ splits, which implies that~$B$ is isomorphic to~$T_1^X\oplus T_1^Z$.
 \end{proof}
@@
 Moreover, if~$X= P_1\xrightarrow{f}P_0$ is an object of~$K^{[-1,0]}(\proj\Lambda)$, then it lies in a conflation~$P_1\stackrel{f}{\infl} P_0 \defl X$ by definition.
-We have proved that properties~(1) t0 (3) of Section~\ref{setting::extricat} are satisfied.
+We have proved that properties~(1) to (3) of Section~\ref{setting::extricat} are satisfied.
 

### 2019-02-27 thirdPaper/draft/typeConeAssociahedra.tex
end proof index extricat

@@
 
-\begin{proposition}
+\begin{proposition}\label{prop::index iso extricat}
  The assignment~$X\mapsto\ind_\tc X$ is well-defined and induces an isomorphism
@@
 
-\begin{lemma}
+\begin{lemma}\label{lemma::index well-defined extricat}
  The index is well-defined.
@@
 
-\begin{lemma}
+\begin{remark}
+We note that Lemma~\ref{lemma::index well-defined extricat} only requires the subcategory~$\tc$ to be rigid, and not made of projective objects.
+However, this stronger assumption is used in the proof of Lemma~\ref{lemma::index kzero extricat} below.
+\end{remark}
+
+\begin{lemma}\label{lemma::index kzero extricat}
  The index descends to~$\kzero{\cat}$: For any conflation~$X\infl Y\defl Z$ in~$\cat$, we have~$\ind_\tc Y = \ind_\tc X + \ind_\tc Z$ in~$\kzero{\tc}$.
@@
 (-7,21)*+{T^Z_1}="-12";
-(7,21)*+{T^Z_1}="-14";
-%
-(-21,7)*+{X}="0";
+(10,21)*+{T^Z_1}="-14";
+%
+(-24,7)*+{X}="0";
 (-7,7)*+{X\oplus T^Z_0}="2";
-(7,7)*+{T^Z_0}="4";
-%
-(-21,-7)*+{X}="10";
+(10,7)*+{T^Z_0}="4";
+%
+(-24,-7)*+{X}="10";
 (-7,-7)*+{Y}="12";
-(7,-7)*+{Z}="14";
+(10,-7)*+{Z}="14";
 %
@@
 \endxy
-\ \ \ \
+\ \ \ \ \ \ \ \
 \xy
-(-21,7)*+{T^X_1}="0";
-(-7,7)*+{B}="2";
-(7,7)*+{T^Z_1}="4";
-%
-(-21,-7)*+{T^X_1}="10";
-(-7,-7)*+{T^X_0\oplus T^Z_0}="12";
-(7,-7)*+{X\oplus T^Z_0}="14";
-%
-(-7,-21)*+{Y}="22";
-(7,-21)*+{Y}="24";
+(-24,21)*+{T^X_1}="0";
+(-7,21)*+{B}="2";
+(14,21)*+{T^Z_1}="4";
+%
+(-24,7)*+{T^X_1}="10";
+(-7,7)*+{T^X_0\oplus T^Z_0}="12";
+(14,7)*+{X\oplus T^Z_0}="14";
+%
+(-7,-7)*+{Y}="22";
+(14,-7)*+{Y}="24";
 %
@@
 Moreover, the conflation with middle term~$B$ splits, which implies that~$B$ is isomorphic to~$T_1^X\oplus T_1^Z$.
+\end{proof}
+
+\begin{proof}[Proof of Proposition~\ref{prop::index iso extricat}]
+ By Lemma~\ref{lemma::index well-defined extricat} and Lemma~\ref{lemma::index kzero extricat}, the index induces an well-defined morphism of abelian groups~$\ind_\tc:\kzero{\cat}\to\kzero{\tc}$.
+ It remains to prove that it is an isomorphism.
+ Let~$\pi:\kzero{\tc}\to\kzero{\cat}$ send a class~$[T]\in\kzero{\tc}$ to the class~$[T]\in\kzero{\cat}$.
+ The existence, for any~$T\in\tc$, of a conflation~$0\infl T\defl T$ shows that~$\pi$ is right inverse to~$\ind_\tc$.
+ To see that it is also a left inverse, note that if~$T_1\infl T_0\defl X$ is a conflation in~$\cat$, then the equality~$[X]=[T_0]-[T_1]$ holds in~$\kzero{\cat}$.
 \end{proof}

### 2019-02-28 thirdPaper/draft/typeConeAssociahedra.tex
minor modifs
objects presented

@@
 
-\begin{corollary}
+\begin{corollary}\label{corollary::meshes positively generate extricats}
 Assume that~$\ind(\cat)$ is finite.
@@
 
+\begin{proof}[Proof of Theorem~\ref{theorem::extricats}]\yann{PG: Est-ce que cela te semble suffisant, ou veux-tu que j'ajoute des d\'etails ? }
+ The proof is know similar to the proof of Theorem~\ref{theo::relations-g-vecteurs}, by using Proposition~\ref{prop::KRextricat} instead of Proposition~\ref{prop::functor-F}, Proposition~\ref{prop::index iso extricat} instead of Corollary~\ref{coro::grothendieck-g-vectors}, and the fact that~$\tc$ is made of projective objects instead of Lemma~\ref{lemm::almost-split}.
+\end{proof}
+
+\begin{proof}[Proof of Corollary~\ref{corollary::meshes positively generate extricats}]
+\yann{TO DO}
+\end{proof}
+
 %%%%
@@
 \subsubsection{Objects presented by a rigid object}\label{sect::Rigid}
+
+We know describe a setup satisfying the assumptions of Section~\ref{sect::setting} that, at the same time, subsumes all examples given so far, while being easily checked in practice.\yann{A reformuler...}
+
+Let~$(\ec,\mathbb{E},\mathfrak{s})$ be an extriangulated category (for example, a small exact category or a triangulated category), and let~$\tc$ be an essentially small \yann{Cette hypoth\`ese n'appara\^it pas dans [HLN], mais me semble n\'ecessaire...} subcategory of~$\ec$.
+
+For any~$X,Y\in\ec$, let~$\mathbb{E}_\tc(X,Y)$ be the subset of~$\mathbb{E}(X,Y)$ consisting of those~$\delta$ that satisfy~$f^\ast\delta = 0$, for any~$T\in\tc$ and any~$T\xrightarrow{f}X$.
+It is easily seen that~$\mathbb{E}_\tc$ is an additive subfunctor of~$\mathbb{E}$.
+Consider $(\ec,\mathbb{E}_\tc,\mathfrak{s}_\tc)$ endowed with the resctriction of the additive realisation~$\mathfrak{s}$.
+Since the deflations in~$(\ec,\mathbb{E}_\tc,\mathfrak{s}_\tc)$ are precisely the deflations in~$(\ec,\mathbb{E},\mathfrak{s})$ that are~$\tc$-epic, they are closed under composition.
+We can thus apply~\cite[Proposition 3.14]{HerschendLiuNakaoka} to obtain that~$(\ec,\mathbb{E}_\tc,\mathfrak{s}_\tc)$ is an extriangulated category.
+With that relative structure, the objects in~$\tc$ become projective.
+Define~$\cat$ to be the full subcategory of~$\ec$ whose objects~$X$ admit an~$\mathfrak{s}_\tc$-conflation~$T_1\infl T_0\defl X$.
+
+\begin{lemma}
+ The full subcategory~$\cat$ is extension-closed in~$(\ec,\mathbb{E}_\tc,\mathfrak{s}_\tc)$, and thus inherits an extriangulated structure.
+\end{lemma}
+
+\begin{proof}
+ This follows from the proof of Lemma~\ref{lemma::index kzero extricat}.
+\end{proof}
+
+\begin{proposition}
+
+\end{proposition}
 

### 2019-03-04 thirdPaper/draft/typeConeAssociahedra.tex
minor changes
modifs sect 2.3

@@
 
-%% SPECIFIC NON-KISSING COMPLEX
-%
-%% COMBINATORICS
-%% quiver
-%
-%% walks
-%\newcommand{\peaks}[1]{\mathsf{peaks}(#1)} % peaks
-%\newcommand{\deeps}[1]{\mathsf{deeps}(#1)} % deeps
-%\newcommand{\distinguishedWalk}[2]{\mathsf{dw}(#1,#2)} % distinguished walk
-%\newcommand{\distinguishedArrows}[2]{\mathsf{da}(#1,#2)} % distinguished arrows
-%\newcommand{\distinguishedString}[2]{\mathsf{ds}(#1,#2)} % distinguished string
-%\newcommand{\distinguishedSign}[2]{\varepsilon(#1,#2)} % distinguished sign
-%
-%% non-kissing complex, lattice, flip graph
-%\newcommand{\kn}{\kappa} % kissing number
-%\newcommand{\KN}{\textsc{kn}} % Kissing Number
-%\newcommandx{\NKC}[1][1=\quiver]{\mathcal{K}_{\mathrm{nk}}(#1)} % non-kissing complex
-%\newcommandx{\RNKC}[1][1=\quiver]{\mathcal{C}_{\mathrm{nk}}(#1)} % non-kissing complex
-%\newcommandx{\NKL}[1][1=\quiver]{\mathcal{L}_{\mathrm{nk}}(#1)} % non-kissing lattice
-%\newcommandx{\NKG}[1][1=\quiver]{\mathcal{G}_{\mathrm{nk}}(#1)} % non-kissing flip graph
-%\newcommandx{\NFC}[1][1=\quiver]{\mathcal{C}_{\mathrm{nf}}(#1)} % non-friendly complex
-%\newcommand{\peak}{\mathrm{peak}} % bottom dissection
-%\newcommand{\deep}{\mathrm{deep}} % top dissection
-%\newcommand{\reversed}[1]{#1^{\mathrm{rev}}} % reverse all arrows
-%\renewcommand{\top}{\mathrm{top}} % top
-%\newcommand{\bottom}{\mathrm{bot}} % bottom
-%\newcommand{\walk}{\operatorname{\omega}} % walk (of a curve)
-%
-%% accordion and slalom complexes
-%\newcommand{\surface}{\mathcal{S}} % an orientable surface
-%\newcommand{\dual}{^*} % duality
-%\newcommand{\dissection}{\mathrm{D}} % dissection of a marked surface
-%\newcommand{\vertices}{\mathcal{V}} % vertices of a dissection
-%\newcommand{\edges}{\mathcal{E}} % edges of a dissection
-%\newcommand{\faces}{\mathcal{F}} % faces of a dissection
-%\renewcommandx{\AC}[1][1=\dissection]{\mathcal{K}_{\mathrm{acc}}(#1)} % accordion complex
-%\newcommandx{\RAC}[1][1=\dissection]{\mathcal{C}_{\mathrm{acc}}(#1)} % reduced accordion complex
-%\newcommandx{\SC}[1][1=\dissection\dual]{\mathcal{K}_{\mathrm{sla}}(#1)} % slalom complex
-%\newcommandx{\RSC}[1][1=\dissection\dual]{\mathcal{C}_{\mathrm{sla}}(#1)} % reduced slalom complex
-%\newcommandx{\NCC}[1][1={\dissection, \dissection\dual}]{\mathcal{K}_{\mathrm{nc}}(#1)} % non-crossing complex
-%\newcommandx{\RNCC}[1][1={\dissection, \dissection\dual}]{\mathcal{C}_{\mathrm{nc}}(#1)} % non-crossing complex
-%\newcommand{\curveof}{\operatorname{\gamma}} % curve (of a walk)
-%\newcommand{\edgeof}{\operatorname{\varepsilon}} % arc of a vertex
-%\newcommand{\dualedgeof}{\operatorname{\varepsilon}\dual} % dual arc of a vertex
-%\DeclareRobustCommand{\SSS}{\reflectbox{$\mathsf{Z}$}} % S
-%\DeclareRobustCommand{\ZZZ}{\mathsf{Z}} % Z
-%\newcommand{\vnext}[1]{#1_{\operatorname{next}}} % next point on the boundary of the surface
-%\newcommand{\vprevious}[1]{#1_{\operatorname{prev}}} % previous point on the boundary of the surface
-%
-%% lattices
-%\newcommand{\meet}{\wedge} % meet
-%\newcommand{\join}{\vee} % join
-%\newcommand{\bigMeet}{\bigwedge} % meet
-%\newcommand{\bigJoin}{\bigvee} % join
-%\newcommand{\closure}[1]{#1^{\mathrm{cl}}} % closure operator
-%\newcommand{\coclosure}[1]{#1^{\mathrm{cocl}}} % coclosure operator
-%\newcommand{\uclosure}[1]{#1^{\underline{\mathrm{cl}}}} % loop free closure operator
-%\newcommand{\Bicl}[1]{\mathsf{Bic}(#1)} % biclosed sets
-%\newcommand{\projDown}{\pi_\downarrow} % down projection map
-%\newcommand{\projUp}{\pi^\uparrow} % up projection map
-%\newcommand{\JI}{\mathsf{JI}} % join-irreducible
-%\newcommand{\MI}{\mathsf{MI}} % meet-irreducible
-%\newcommand{\Cong}{\mathsf{Cong}} % congruence lattice
-%\newcommand{\con}{\mathrm{con}} % congruence contracting a cover relation
-%\newcommand{\ji}{\mathsf{ji}} % join irreducible
-%\newcommand{\mi}{\mathsf{mi}} % meet irreducible
-%
-%% GEOMETRY
-%% d-vectors
-%\newcommand{\dvector}[1]{\mathbf{d}(#1)} % d-vector of the path #1
-%\newcommand{\dvectors}[1]{\mathbf{d}(#1)} % d-vectors of the paths #1
-%\newcommandx{\dvectorFan}[1][1=\quiver]{\mathcal{F}^\mathbf{d}(#1)} % d-vector fan
-%% g-vectors
-%\newcommand{\gvector}[1]{\mathbf{g}(#1)} % g-vector of the path #1
-%\newcommand{\gvectors}[1]{\mathbf{g}(#1)} % g-vectors of the paths #1
-%\newcommandx{\gvectorFan}[1][1=\quiver]{\mathcal{F}^\mathbf{g}(#1)} % g-vector fan
-%% c-vectors
-%\newcommand{\cvector}[2]{\mathbf{c}(#1 \in #2)} % c-vector of the path #1 in the facet #2
-%\newcommand{\cvectors}[1]{\mathbf{c}(#1)} % c-vectors of the paths #1
-%\newcommandx{\allcvectors}[1][1=\quiver]{\mathbf{C}(#1)} % all c-vectors with respect to the initial cluster #1
-%\newcommandx{\cvectorFan}[1][1=\quiver]{\mathcal{F}^\mathbf{c}(#1)} % fan of hyperplanes orthogonal to all c-vectors
-%% points, hyperplanes, half-spaces
-%\newcommand{\point}[1]{\mathbf{p}(#1)} % vertex of the grid associahedron corresponding to the cluster #1
-%\newcommandx{\ray}[1][1=r]{\mathbf{#1}} % ray
-%\newcommandx{\rays}[1][1=R]{\mathbf{#1}} % rays
-%\newcommand{\hs}{\mathbf{H}^{\le}} % half space
-%\newcommand{\HS}[1]{\mathbf{H}^{\le}(#1)} % half space
-%\newcommand{\hyp}{\mathbf{H}^{=}} % hyperplane
-%\newcommand{\Hyp}[1]{\mathbf{H}^{=}(#1)} % hyperplane
-%\newcommand{\fix}[1]{\mathrm{Fix}(#1)} % fix space
-%
-%% ALGEBRA
-%\newcommand{\Hom}[1]{\operatorname{{\rm Hom}}_{#1}}
-%\newcommand{\Ext}[1]{\operatorname{{\rm Ext}}_{#1}}
-%\newcommandx{\AR}[1][1=\quiver]{\mathrm{AR}(#1)} % Auslander-Reiten quiver
-%\newcommandx{\tTC}[1][1=\quiver]{\mathcal{K}^{\textrm{s$\tau$-tilt}}(#1)} % tau-tilting complex
-%\newcommand{\rep}{\operatorname{{\rm rep}}}
-%\newcommand{\proj}{\operatorname{{\rm proj}}}
-%\newcommand{\koszul}{^!} % duality
-
-%% formating the part command
-%\makeatletter
-%\def\part{\@startsection{part}{1}%
-%\z@{.7\linespacing\@plus\linespacing}{.8\linespacing}%
-%{\LARGE\sffamily\centering}}
-%\@addtoreset{section}{part}
-%\makeatother
-%\renewcommand{\thesection}{\arabic{part}.\arabic{section}}
-
 % formating the table of contents
@@
 \typeCone(\Fan) & \eqdef \set{\b{h} \in \R^N}{\Fan \text{ is the normal fan of } P_\b{h}} \\
-& = \Bigset{\b{h} \in \R^N}{\sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} > 0 \text{ for any adjacent maximal cones~$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$ of~$\Fan$}}.
+& = \Bigset{\b{h} \in \R^N}{\sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} > 0 \; \begin{array}{l} \text{for any adjacent maximal} \\ \text{cones~$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$ of~$\Fan$} \end{array}}.
 \end{align*}
@@
 \[
-\typeCone(\Fan) = \Bigset{\b{h} \in \R^N}{\sum_{\ray[s] \in \rays \cup \rays'} \coefficient \, \b{h}_{\ray[s]} > 0 \text{ for any exchangeable rays~$\ray, \ray'$ of~$\Fan$}}.
+\typeCone(\Fan) = \Bigset{\b{h} \in \R^N}{\sum_{\ray[s] \in \rays \cup \rays'} \coefficient \, \b{h}_{\ray[s]} > 0 \text{ for any exchangeable rays~$\ray$ and~$\ray'$ of~$\Fan$}}.
 \]
@@
 \).
-%so that~$p = \positiveExponents{p} \negativeExponents{p}^{-1}$.
 
@@
 \(
-% \quad\text{and}\quad
 \b{h}_x + \b{h}_{x'} > \sum_{{y \in \cluster \cap \cluster', \; b_{xy} > 0}} b_{xy} \, \b{h}_y
@@
 \]
-%\[
-%\b{n}(\B_\circ, x, x') = \b{f}_x + \b{f}_{x'} - \sum_{y \in \cluster \cap \cluster'} |b_{xy}| \, \b{f}_y
-%\]
 \end{lemma}
@@
 \subsubsection{Non-kissing complex and non-kissing fan of a gentle quiver}
+\label{subsubsec:nonkissingComplex}
 
@@
 The \defn{distinguished substring}~$\distinguishedString{\omega}{F}$ of the walk~$\omega$ in the non-kissing facet~$F \in \NKC$ is the substring located between its two distinguished arrows.
+We say that a string~$\sigma$ is \defn{distinguishable} if it is the distinguished string of a walk in a non-kissing facet, and we denote by~$\distinguishableStrings$ the set of distinguishable strings of~$\quiver$.
 
@@
 \begin{theorem}[{\cite[Thm.~4.17]{PaluPilaudPlamondon-nonkissing}}]
-\label{thm:nonkissingAsso}
+\label{thm:nonkissingFan}
 For any non-kissing finite gentle quiver~$\quiver$, the set of cones
@@
 \begin{theorem}[{\cite[Thm.~4.27]{PaluPilaudPlamondon-nonkissing}}]
+\label{thm:nonkissingAsso}
 For any non-kissing finite gentle quiver~$\quiver$, the non-kissing fan~$\gvectorFan[\quiver]$ is the normal fan of the \defn{gentle associahedron}~$\Asso[\quiver]$ defined equivalently as:
@@
 
-In \cref{prop:exchangeablePairsNKC}, the string~$\sigma$ is called the \defn{distinguished} substring of~$\omega$ and~$\omega'$.
-We say that a string~$\sigma$ is \defn{distinguishable} if it is the distinguished string of an exchangeable pair.
-Note that an equivalent definition of distinguishable strings is given in~\cite[Def.~2.30]{PaluPilaudPlamondon-nonkissing}.
-We denote by~$\distinguishableStrings$ the set of distinguishable strings of~$\quiver$.
-\vincent{Clean that}
-
 \begin{remark}
@@
 In view of \cref{prop:exchangeablePairsNKC}, it is tempting to look for a characterization of the exchangeable pairs~$\omega, \omega'$ using the kisses between~$\omega$ and~$\omega'$.
+This question was discussed in \cite[Sect.~9]{BrustleDouvilleMousavandThomasYildirim}.
 However, as illustrated in \cref{fig:nonkissingFans}\,(right), note that
 \begin{itemize}
-\item two exchangeable walks may kiss along more than one string, but only one is the distinguished string,
+\item two exchangeable walks may kiss along more than one string (only one is distinguished),
 \item two non-exchangeable walks can kiss along more than one distinguishable string,
@@
 \end{itemize}
-\vincent{More explicit. TODO}
+In \cref{subsubsec:simplicialTypeConeNKC}, we will restrict to a situation that avoids all these patologies.
 \vincent{Do we still have these problems when the gentle algebra is brick and/or without oriented $2$-cycle?}
 \end{remark}
-
-\begin{corollary}
-For any non-kissing finite gentle quiver~$\quiver$, the type cone of the non-kissing fan~$\gvectorFan[\quiver]$ is given by
-\[
-\typeCone(\gvectorFan[\quiver]) = \set{\b{h} \in \R^{\walks}}{\begin{array}{l} \b{h}_\omega = 0 \text{ for any improper walk } \omega \\ \b{h}_\omega + \b{h}_{\omega'} > \b{h}_\mu + \b{h}_\nu \text{ for any exchangeable walks } \omega, \omega' \end{array}}.
-\]
-\end{corollary}
 
@@
 %
-We conclude this recollections on non-kissing complexes by two families of examples.
-\vincent{TODO}
-
-\bigskip
-We are now ready to describe the type cone of the non-kissing fan~$\gvectorFan[\quiver]$.
-We first treat the case when~$\quiver$ has no self-kissing walks, which includes both grid and dissection quivers, thus in particular the case of the classical associahedron.
-We show that the type cone is then simplicial which gives another proof of \cref{thm:simplicialTypeConeAsso} and \cref{coro:descriptionAllAsso}.
-
-\subsubsection{Simplicial type cones for self-kissing free quivers}
-
-In this section, we focus on the following family of gentle quivers, which was also considered in~\cite[Sect.~4]{}.
+We conclude this recollections on non-kissing complexes by two families of examples:
+\begin{enumerate}[(1)]
+\item \textbf{Grid quivers}: Consider the infinite grid quiver~$\quiver_{Z^2}$, whose vertices are all integer points of~$\Z^2$, whose arrows connect between~$(i,j) \longrightarrow (i,j+1)$ and~$(i,j) \longrightarrow (i+1,j)$ for any~$(i,j) \in \Z^2$, and whose relations forbid~$(i-1,j) \longrightarrow (i,j) \longrightarrow (i,j+1)$ and~$(i,j-1) \longrightarrow (i,j) \longrightarrow (i+1,j)$ for any~$(i,j) \in \Z^2$.
+A \defn{gentle grid quiver} is any subquiver~$\quiver_A$ of~$\quiver_{Z^2}$ induced by a finite subset~$A \subset \Z^2$ of the integer grid.
+The non-kissing complex of gentle grid quivers were introduced in~\cite{McConville} with motivation coming from~\cite{PetersenPylyavskyySpeyer} and~\cite{SantosStumpWelker}.
+
+\smallskip
+\item \textbf{Dissection quivers}: Consider a dissection~$D$ of a convex polygon~$P$ (that is a crossing-free set of diagonals of~$P$) and its \defn{gentle dissection quiver}~$\quiver_D$, whose vertices are the internal diagonals of~$D$, whose arrows connect pairs of consecutive internal diagonals along the boundary of a face of~$D$, and whose relations correspond to triples of consecutive internal diagonals along the boundary of a face of~$D$.
+The non-kissing complex of~$\quiver_D$ the corresponds to non-crossing sets of accordions of~$D$, where an accordion is a segment connecting the middles of two boundary edges of~$P$ and crossing a connected set of diagonals of~$D$.
+This accordion complex was studied in~\cite{GarverMcConville} and~\cite{MannevillePilaud-accordion} with motivation coming from~\cite{Baryshnikov}, and~\cite{Chapoton-quadrangulations}.
+\end{enumerate}
+
+\vincent{Example picture?}
+
+\smallskip
+These two families of non-kissing complexes are well-behaved as they avoid all pathologies of \cref{rem:exchangeablePairsNKC}.
+However, they still provide good examples of non-kissing complexes.
+In particular, both families contain the classical associahedron.
+Namely, the gentle associahedron~$\Asso[\quiver]$ is the classical associahedron of~\cite{ShniderSternberg, Loday} presented in \cref{thm:associahedronLoday} when~${\quiver = \quiver_A}$ for the path~${A = \set{(0,j)}{j \in [n]}}$ or equivalently~$\quiver = \quiver_D$ for the fan triangulation~$D$ (where all internal diagonals incident to the same point).
+More generally, $\Asso[\quiver]$ is an associahedron of~\cite{HohlwegLange} when~$\quiver = \quiver_A$ for a ribbon~$A$ or equivalently~$\quiver = \quiver_D$ for a triangulation~$D$.
+
+Note that, it was shown in~\cite{PaluPilaudPlamondon-surfaces} that the accordion complexes can be extended to dissections of arbitrary orientable surfaces with marked points and then provide a geometric model for all non-kissing complexes of gentle quivers.
+
+\subsubsection{Type cones of non-kissing fans}
+
+We now discuss the type cones of the non-kissing fans defined in \cref{thm:nonkissingFan}. We obtain from \cref{prop:exchangeablePairsNKC} the following redundant description.
+
+\begin{corollary}
+For any non-kissing finite gentle quiver~$\quiver$, the type cone of the non-kissing fan~$\gvectorFan[\quiver]$ is given by
+\[
+\typeCone(\gvectorFan[\quiver]) = \set{\b{h} \in \R^{\walks}}{\begin{array}{l} \b{h}_\omega = 0 \text{ for any improper walk } \omega \\ \b{h}_\omega + \b{h}_{\omega'} > \b{h}_\mu + \b{h}_\nu \text{ for any exchangeable walks } \omega, \omega' \end{array}},
+\]
+where the walks~$\mu$ and~$\nu$ for two exchangeable walks~$\omega, \omega'$ are defined in \cref{prop:exchangeablePairsNKC}.
+\end{corollary}
+
+\begin{example}
+\label{exm:typeConeNKC}
+Consider the gentle quivers of \cref{fig:typeConeNKC}.
+\vincent{Todo}
+\end{example}
+
+As illustrated in \cref{exm:typeConeNKC}, the type cone of the non-kissing fan is not simplicial and we do not always understand its extremal exchangeable pairs.
+In the next section section, we will explore a special family of gentle quivers for which we can completely describe the type cone.
+The combination of this special family with computer experiments in the general case support the following conjecture.
+
+\begin{conjecture}
+Consider a distinguishable string~$\sigma \in \distinguishableStrings$, and let~$\omega$ (resp.~$\omega'$) be the walk obtained from~$\sigma$ by adding two hooks (resp.~two cohooks) at the endpoints of~$\sigma$.
+Then
+\begin{enumerate}
+\item The $\b{c}$-vector~$\multiplicityVector_\sigma$ is the direction of at least one extremal exchangeable pair.
+\item If the walks~$\omega$ and~$\omega'$ are non-self-kissing and exchangeable, then they form the unique extremal exchangeable pair directed by~$\sigma$.
+These extremal exchangeable pairs correspond to meshes of the Auslander-Reiten quiver.
+\end{enumerate}
+\end{conjecture}
+
+\subsubsection{Simplicial type cones for self-kissing-free and $2$-cycle-free quivers}
+\label{subsubsec:simplicialTypeConeNKC}
+
+In this section, we focus on the following family of gentle quivers, which was also considered in~\cite[Sect.~4]{GarverMcConvilleMousavand}.
 
@@
 
-The quivers of this family are particularly well-behaved: they avoid all pathologies of \cref{rem:exchangeablePairsNKC} and we will prove that the type cone of their non-kissing fan happens to be simplicial.\pg{Need to exclude two-cycles, else false.}
-Note that this family already contains a lot of relevant examples, including:
+We say that a gentle quiver~$\quiver$ is \defn{simple} when
 \begin{itemize}
-\item classical associahedra
-\item grid associahedra
-\item dissection associahedra
+\item it satisfies the three equivalent conditions of \cref{prop:noSelfKissing},
+\item it contains no cycle of length~$2$.
 \end{itemize}
-\vincent{More explicit. TODO}
-
-%For a string~$\sigma$ of~$\quiver$, we denote by $\sigma\hR$ (resp.~$\hL\sigma$, resp.~$\sigma\cR$, resp.~$\cL\sigma$) the unique string of~$\quiver\blossom$ of the form $\sigma\hR = \sigma \alpha_1^{-1} \alpha_2 \dots \alpha_\ell$ (resp.~$\hL\sigma = \alpha_\ell^{-1} \dots \alpha_2^{-1} \alpha_1 \sigma$, resp.~$\sigma\cR = \sigma \alpha_1 \alpha_2^{-1} \dots \alpha_\ell^{-1}$, resp.~$\cL\sigma = \alpha_\ell \dots \alpha_2 \alpha_1^{-1} \sigma$) with~$\ell \ge 1$ and~$\alpha_1, \dots, \alpha_\ell \in Q_1$ and such that~$t(\alpha_\ell)$ (resp.~$s(\alpha_\ell)$, resp.~$s(\alpha_\ell)$, resp.~$t(\alpha_\ell)$) is a blossom of~$\quiver\blossom$.
+Note that this family already contains a lot of relevant examples, including the grid and dissection quivers discussed in \cref{subsubsec:nonkissingComplex}.
+In particular, the classical associahedron is the gentle associahedron of a simple gentle quiver.
+We will see in~\cref{coro:simplicialTypeConeNKC} that the type cone of the non-kissing fan~$\gvectorFan[\quiver]$ of a simple gentle quiver~$\quiver$ happens to be simplicial, and we will derive in~\cref{coro:allPolytopalRealizationsNKC} a simple description of all polytopal realizations of~$\gvectorFan[\quiver]$.
+
 For a string~$\sigma$ of~$\quiver$, we denote by $\sigma\hR$ (resp.~$\sigma\cR$) the unique string of the blossoming quiver~$\quiver\blossom$ of the form $\sigma\hR = \sigma \alpha_1^{-1} \alpha_2 \dots \alpha_\ell$ (resp.~$\sigma\cR = \sigma \alpha_1 \alpha_2^{-1} \dots \alpha_\ell^{-1}$) with~$\ell \ge 1$ and~${\alpha_1, \dots, \alpha_\ell \in Q_1}$ and such that~$t(\alpha_\ell)$ (resp.~$s(\alpha_\ell)$) is a blossom of~$\quiver\blossom$.
@@
 
-%For a string~$\sigma$ of~$\quiver$, we denote by~$\hh{\sigma}$, $\cc{\sigma}$, $\hc{\sigma}$ and~$\ch{\sigma}$ the unique walks on~$\quiver$ of the~form
-%\begin{alignat*}{3}
-%\hh{\sigma} & = \alpha_k^{-1} \dots \alpha_2^{-1} \alpha_1 \sigma \beta_1^{-1} \beta_2 \dots \beta_\ell
-%\qquad\qquad
-%& \cc{\sigma} & = \alpha_k \dots \alpha_2 \alpha_1^{-1} \sigma \beta_1 \beta_2^{-1} \dots \beta_\ell^{-1}
-%\\
-%\hc{\sigma} & = \alpha_k^{-1} \dots \alpha_2^{-1} \alpha_1 \sigma \beta_1 \beta_2^{-1} \dots \beta_\ell^{-1}
-%\qquad\qquad
-%& \ch{\sigma} & = \alpha_k \dots \alpha_2 \alpha_1^{-1} \sigma \beta_1^{-1} \beta_2 \dots \beta_\ell.
-%\end{alignat*}
-%%\begin{itemize}
-%%\item by~$\hh{\sigma}$ the unique walk on~$\quiver$ of the form~$\hh{\sigma} = \alpha_k^{-1} \dots \alpha_2^{-1} \alpha_1 \sigma \beta_1^{-1} \beta_2 \dots \beta_\ell$,
-%%\item by~$\cc{\sigma}$ the unique walk on~$\quiver$ of the form~$\cc{\sigma} = \alpha_k \dots \alpha_2 \alpha_1^{-1} \sigma \beta_1 \beta_2^{-1} \dots \beta_\ell^{-1}$.
-%%\item by~$\hc{\sigma}$ the unique walk on~$\quiver$ of the form~$\hc{\sigma} = \alpha_k^{-1} \dots \alpha_2^{-1} \alpha_1 \sigma \beta_1 \beta_2^{-1} \dots \beta_\ell^{-1}$.
-%%\item by~$\ch{\sigma}$ the unique walk on~$\quiver$ of the form~$\ch{\sigma} = \alpha_k \dots \alpha_2 \alpha_1^{-1} \sigma \beta_1^{-1} \beta_2 \dots \beta_\ell$.
-%%\end{itemize}
-%with~$k,\ell \ge 1$ and~$\alpha_1, \dots, \alpha_k, \beta_1, \dots, \beta_\ell \in Q_1$.
-%The following statement ensures that in a gentle quiver with no self-kissing walk, the walks~$\hh{\sigma}$ and~$\cc{\sigma}$ are exchangeable with distinguished substring~$\sigma$.
-
 \begin{proposition}
-For any gentle quiver~$\quiver$ with no self-kissing walk and any string~$\sigma \in \strings$, the walks~$\cc{\sigma}$ and~$\hh{\sigma}$ are exchangeable with distinguished substring~$\sigma$.
-\vincent{This is FALSE...}
+For any simple gentle quiver~$\quiver$ and any string~$\sigma \in \strings$, the walks~$\cc{\sigma}$ and~$\hh{\sigma}$ are exchangeable with distinguished substring~$\sigma$.
 \end{proposition}
@@
 \label{prop:extremalExchangeablePairsNKC}
-For any gentle quiver~$\quiver$ with no self-kissing walk, the extremal exchangeable pairs for the non-kissing fan of~$\quiver$ are precisely the pairs~$\{\cc{\sigma}, \hh{\sigma}\}$ for all strings~$\sigma \in \strings$.
+For any simple gentle quiver~$\quiver$, the extremal exchangeable pairs for the non-kissing fan of~$\quiver$ are precisely the pairs~$\{\cc{\sigma}, \hh{\sigma}\}$ for all strings~$\sigma \in \strings$.
 \end{proposition}
@@
 \label{coro:simplicialTypeConeNKC}
-For any gentle quiver~$\quiver$ with no self-kissing walk, the type cone~$\typeCone(\gvectorFan[\quiver])$ of the non-kissing fan~$\quiver$ is simplicial.
+For any simple gentle quiver~$\quiver$, the type cone~$\typeCone(\gvectorFan[\quiver])$ of the non-kissing fan~$\quiver$ is simplicial.
 \end{corollary}
@@
 \begin{corollary}
-For any gentle quiver~$\quiver$ with no self-kissing walk and any~$\b{\ell} \in \R_{>0}^{\strings}$, the polytope
+\label{coro:allPolytopalRealizationsNKC}
+For any simple gentle quiver~$\quiver$ and any~$\b{\ell} \in \R_{>0}^{\strings}$, the polytope
 \[
@@
 \end{remark}
-
-\subsubsection{Towards the general case}
-
-We are already missing a criterion for exchangeable pairs of walks. See \cite[Sect.~9]{BrustleDouvilleMousavandThomasYildirim}.
-It seems that two exchangeable walks are always kissing along a single distinguishable string.
-We need to prove that to see that the non-kissing fan has the unique exchange relation property (because for a pair of exchangeable walks, I can completely reconstruct the $\b{g}$-vector dependence of the flip if I know their distinguished substring).
-Note however that
-\begin{enumerate}
-\item exchangeable pairs might kiss along additional non-distinguishable strings (example: just a loop),
-\item non-exchangeable walks might kiss along a single distinguishable string (example: see the cyclic triangle in~\cite{PaluPilaudPlamondon-nonkissing}).
-\item non-exchangeable walks might kiss along two or more distinguishable strings (example: see the cyclic triangle in~\cite{PaluPilaudPlamondon-nonkissing}).
-\end{enumerate}
-
-%In view of these two points, the following conjecture seems plausible.
-%
-%\begin{conjecture}
-%Two walks~$\omega$ and~$\omega'$ are exchangeable if and only if
-%\begin{itemize}
-%\item they kiss along a single distinguishable string~$\sigma$ (note that they might also kiss along other strings as long as they are not distinguishable),
-%\item decomposing~$\omega = \rho \sigma \tau$ and~$\omega' = \rho' \sigma \tau'$ according to their common distinguishable string, the two walks~$\mu \eqdef \rho' \sigma \tau$ and~$\nu \eqdef \rho \sigma \tau'$ are non-self-kissing.
-%\end{itemize}
-%Recall that with these notations, for any flip exchanging~$\omega$ and~$\omega'$, we have the linear dependence
-%\[
-%\gvector{\omega} + \gvector{\omega'} = \gvector{\mu} + \gvector{\nu}.
-%\]
-%\end{conjecture}
-
-We have some conjectures on what the extremal exchangeable pairs should be.
-One clear (but a bit empty) result is that extremal exchangeable pairs correspond in the Auslander-Reiten quiver to rectangles whose four vertices are non-self-kissing and that cannot be tiled with smaller such rectangles.
-
-We checked on some (but probably not enough) small gentle quivers the following properties:
-\begin{enumerate}
-\item Any $c$-vector (\ie distinguishable string) is the direction of at least one extremal exchangeable pair.
-\item Consider a distinguishable string~$\sigma$.
-Let~$\omega$ (resp.~$\omega'$) be the walk obtained from~$\sigma$ by adding two hooks (resp.~two cohooks) at the endpoints of~$\sigma$.
-If the walks~$\omega$ and~$\omega'$ are non-self-kissing and exchangeable, then they form the unique extremal exchangeable pair directed by~$\sigma$.
-These extremal exchangeable pairs correspond to meshes of the Auslander-Reiten quiver.\pg{The conjecture is the word ``unique''.}
-\item Otherwise, $\sigma$ is the direction to one or more extremal exchangeable pairs obtained by moving further in the Auslander-Reiten quiver (this is really unclear at the moment).
-\end{enumerate}
-
-\begin{figure}[t]
-	\capstart
-	\centerline{\includegraphics[scale=.6]{fan}}
-	\caption{The shards corresponding to the facets of the type cone. Is there a geometric meaning?}
-	\label{fig:fanShards}
-\end{figure}
 
@@
 \begin{proposition}
-
-\end{proposition}
+Assume that
+Then the extriangulated category~$\cat$ satisfies the assumptions (1) to (3) of Section~\ref{sect::setting}.
+\end{proposition}
+
+\begin{proof}
+For any~$T\in\tc$ the existence of an extriangle~$0\infl T\defl T\overset{0}{\dashrightarrow}$ shows that~$\tc$ is a full subcategory of~$\cat$.
+
+\end{proof}
 

### 2019-03-07 thirdPaper/draft/typeConeAssociahedra.tex
added assumptions in Proposition 4.30

@@
 \begin{proof}[Proof of Theorem~\ref{theorem::extricats}]\yann{PG: Est-ce que cela te semble suffisant, ou veux-tu que j'ajoute des d\'etails ? }
- The proof is know similar to the proof of Theorem~\ref{theo::relations-g-vecteurs}, by using Proposition~\ref{prop::KRextricat} instead of Proposition~\ref{prop::functor-F}, Proposition~\ref{prop::index iso extricat} instead of Corollary~\ref{coro::grothendieck-g-vectors}, and the fact that~$\tc$ is made of projective objects instead of Lemma~\ref{lemm::almost-split}.
+ The proof is now similar to the proof of Theorem~\ref{theo::relations-g-vecteurs}, by using Proposition~\ref{prop::KRextricat} instead of Proposition~\ref{prop::functor-F}, Proposition~\ref{prop::index iso extricat} instead of Corollary~\ref{coro::grothendieck-g-vectors}, and the fact that~$\tc$ is made of projective objects instead of Lemma~\ref{lemm::almost-split}.
 \end{proof}
@@
 %%
-\subsubsection{Objects presented by a rigid object}\label{sect::Rigid}
-
-We know describe a setup satisfying the assumptions of Section~\ref{sect::setting} that, at the same time, subsumes all examples given so far, while being easily checked in practice.\yann{A reformuler...}
+\subsubsection{Objects presented by a subcategory}\label{sect::prT}
+
+We know describe a setup satisfying the assumptions of Section~\ref{setting::extricat} that, at the same time, subsumes all examples given so far, while being easily checked in practice.\yann{A reformuler...}
 
@@
 
-\begin{lemma}
+\begin{lemma}\label{lemma:: prT is extriangulated}
  The full subcategory~$\cat$ is extension-closed in~$(\ec,\mathbb{E}_\tc,\mathfrak{s}_\tc)$, and thus inherits an extriangulated structure.
@@
 
-\begin{proposition}
-Assume that
-Then the extriangulated category~$\cat$ satisfies the assumptions (1) to (3) of Section~\ref{sect::setting}.
+\begin{notation}
+ Write~$\tc^\perp$ for the full subcategory of~$\ec$ whose objects are those objects~$X\in\ec$ that satisfy~$\ec(T,X)=0$, for any~$T\in\tc$.
+\end{notation}
+
+\begin{proposition}\label{prop::prT}
+Assume that, for any~$T\in\tc$, there is an~$\mathfrak{s}$-conflation~$T\infl 0\defl X_T$ in~$\ec$ with~$X_T\in\tc^\perp$.
+Then the extriangulated category~$\cat$ satisfies the assumptions (1) to (3) of Section~\ref{setting::extricat}.
 \end{proposition}
@@
 For any~$T\in\tc$ the existence of an extriangle~$0\infl T\defl T\overset{0}{\dashrightarrow}$ shows that~$\tc$ is a full subcategory of~$\cat$.
-
-\end{proof}
+By Lemma~\ref{lemma:: prT is extriangulated}, the category~$\cat$ is extriangulated and, by definition of this extriangulated structure, the objects in~$\tc$ are projective in~$\cat$.
+Assumption (3) is satisfied by the definition of~$\cat$, and assumption (2) is equivalent to that of the proposition.
+\end{proof}
+
+\begin{remark}
+ The categories considered in Sections~\ref{sect::2CYTriangulated},~\ref{sect::2CYexact} and~\ref{sect::Kbproj} all fall into the setting of Proposition~\ref{prop::prT}.
+\end{remark}
 

### 2019-03-29 thirdPaper/draft/typeConeAssociahedra.tex

@@
   \item for any Artin algebra~$\Lambda$, the category~$K^{[-1,0]}(\proj \Lambda)$ of complexes of finitely generated projective~$\Lambda$-modules concentrated in degrees~$-1$ and~$0$, with morphisms considered up to homotopy (see Section~\ref{sect::Kbproj});
-  \item more generally, extriangulated categories~$\cat$ constructed as follows: if~$\tc$ is a rigid subcategory of an extriangulated category~$\ec$, we let~$\cat$ be the full subcategory of~$\ec$ whose objects satisfy condition (3), equipped with the extriangulated structure obtained from that of~$\ec$ by considering those extriangles in~$\ec$ all whose terms belong to~$\cat$ and whose deflation is~$\tc$-epi (see Section~\ref{sect::Rigid}).
+  \item more generally, extriangulated categories~$\cat$ constructed as follows: if~$\tc$ is a rigid subcategory of an extriangulated category~$\ec$, we let~$\cat$ be the full subcategory of~$\ec$ whose objects satisfy condition (3), equipped with the extriangulated structure obtained from that of~$\ec$ by considering those extriangles in~$\ec$ all whose terms belong to~$\cat$ and whose deflation is~$\tc$-epi (see Section~\ref{sect::prT}).
  \end{itemize}
@@
 
-Proposition~\ref{prop::KRextricat} below extends similar results from [REF]\yann{ref: BMR, KR ,KZ, IY...} (see also Proposition~\ref{prop::functor-F}) to the setting under consideration.
+Proposition~\ref{prop::KRextricat} below extends similar results from~\cite{BuanMarshReiten,KellerReiten,KoenigZhu,IyamaYoshino} (see also Proposition~\ref{prop::functor-F}) to the setting under consideration.
 We note that the proof requires minor modifications.
@@
 
-The notion of index from \yann{ref RVdB, DK, P, also studied in ....} generalises to our current setting.
+The notion of index from~\cite{DehyKeller,Palu} \yann{ref RVdB ou BB ou ?, also studied in ....} generalises to our current setting.
 
@@
 %%%%
-\subsection{Proof of Theorem~\ref{theorem::extricats}}
+\subsection{Proofs of preliminary results and of Theorem~\ref{theorem::extricats}}
 \label{sect::proofs extricats}
 
-We let~$\cat$ and~$\tc$ be as in Setting~\ref{setting::extricat}.
+We let~$\cat$ and~$\tc$ satisfy the assumptions (1), (2) and (3) of Setting~\ref{setting::extricat}.
 We will make it explicit when more assumptions are needed.

### 2019-04-01 thirdPaper/draft/typeConeAssociahedra.tex
minor editing

@@
 	}
-	\caption{Schematic representation of te four equalities in the proof of \cref{prop:extremalExchangeablePairsNKC}.}
+	\caption{Schematic representation of the four equalities in the proof of \cref{prop:extremalExchangeablePairsNKC}.}
 	\label{fig:fourEqualities}
@@
 Assume that~$\cat$ is a~$\field$-linear, Ext-finite, Krull--Schmidt, extriangulated category with Auslander--Reiten--Serre duality.
-Assume that~$T$ is a projective object of~$\cat$ such that any~$X\in\cat$ admits an extriangle~$T_1^X\infl T_0^X\defl X\dashrightarrow$ with~$T_0^X, T_1^X\in\add(T)$, and the morphism~$T\to 0$ is an inflation.
+Assume that~$T$ is a projective object of~$\cat$ such that any~$X\in\cat$ admits a conflation~$T_1^X\infl T_0^X\defl X$ with~$T_0^X, T_1^X\in\add(T)$, and the morphism~$T\to 0$ is an inflation.
 Fix a conflation~$T\to 0 \to \susp T$.
@@
 
+\begin{corollary}
+ Generalised cluster categories with infinite dimensional Hom-spaces ?
+\end{corollary}
+
 %%%%

### 2019-04-01 thirdPaper/draft/typeConeAssociahedra.tex
improvements Sec 2

--- 2019-03-29 thirdPaper/draft/typeConeAssociahedra.tex
@@
 \newcommandx{\tube}[1][1=t]{\mathsf{#1}} % tube
-\newcommandx{\tubes}{\mathcal{T}} % all tubes
+\newcommandx{\tubes}[1][1=\graphG]{\mathcal{T}(#1)} % all tubes
 \newcommandx{\tubing}[1][1=T]{\mathsf{#1}} % tubing
@@
 
-\subsubsection{Type cone of $\b{g}$-vector fans}
+\subsubsection{Type cone of finite type $\b{g}$-vector fans}
 
@@
 \end{corollary}
+
+\begin{example}
+%sage: B = Matrix([[0,-1,1],[1,0,-1],[-1,1,0]])
+%sage: CA = ClusterAlgebra(B)
+%
+%sage: CA.explore_to_depth(infinity)
+%sage: gvectors = CA.cluster_fan().rays()
+%sage: for gvector in gvectors:
+%....:     print gvector, CA.cluster_variable(gvector)
+%....:     
+%N(1, 0, 0) x0
+%N(0, 0, 1) x2
+%N(1, -1, 0) (x0 + x2)/x1
+%N(0, 0, -1) (x0 + x1 + x2)/(x1*x2)
+%N(-1, 0, 1) (x1 + x2)/x0
+%N(0, -1, 0) (x0 + x1 + x2)/(x0*x1)
+%N(-1, 0, 0) (x0 + x1 + x2)/(x0*x2)
+%N(0, 1, 0) x1
+%N(0, 1, -1) (x0 + x1)/x2
+%
+%sage: TCCA = type_cone_CA(CA)
+%sage: TCCA
+%A 9-dimensional polyhedron in QQ^9 defined as the convex hull of 1 vertex, 6 rays, 3 lines
+%sage: TCCA.inequalities()
+%(An inequality (-1, 0, 1, -1, 0, 0, 0, 0, 1) x + 0 >= 0,
+% An inequality (1, 0, -1, 0, 0, 1, 0, 0, 0) x + 0 >= 0,
+% An inequality (0, -1, 1, 0, 1, -1, 0, 0, 0) x + 0 >= 0,
+% An inequality (0, 1, 0, 0, -1, 0, 1, 0, 0) x + 0 >= 0,
+% An inequality (0, 0, 0, 1, 0, 0, 0, 1, -1) x + 0 >= 0,
+% An inequality (0, 0, 0, 0, 1, 0, -1, -1, 1) x + 0 >= 0)
+
+%sage: B = Matrix([[0,-1,2],[1,0,-2],[-1,1,0]])
+%sage: CA = ClusterAlgebra(B)
+%
+%sage: CA.explore_to_depth(infinity)
+%sage: gvectors = CA.cluster_fan().rays()
+%sage: for gvector in gvectors:
+%....:     print gvector, CA.cluster_variable(gvector)
+%....:     
+%N(-1, 1, 0) (x0^2 + x1^2 + x1*x2)/(x0*x2)
+%N(0, 2, -1) (x0^2 + x1^2)/x2
+%N(1, 0, 0) x0
+%N(0, 0, 1) x2
+%N(-2, 0, 1) (x0^2 + x1^2 + 2*x1*x2 + x2^2)/(x0^2*x2)
+%N(1, -1, 0) (x0 + x2)/x1
+%N(0, 0, -1) (x0^2 + x1^2 + 2*x0*x2 + x2^2)/(x1^2*x2)
+%N(-1, 0, 1) (x1 + x2)/x0
+%N(0, -1, 0) (x0 + x1 + x2)/(x0*x1)
+%N(-1, 0, 0) (x0^2 + x1^2 + x0*x2 + x1*x2)/(x0*x1*x2)
+%N(0, 1, 0) x1
+%N(0, 1, -1) (x0^2 + x1^2 + x0*x2)/(x1*x2)
+%
+%sage: TCCA = type_cone_CA(CA)
+%sage: TCCA
+%A 12-dimensional polyhedron in QQ^12 defined as the convex hull of 1 vertex, 9 rays, 3 lines
+%sage: TCCA.lines()
+%(A line in the direction (0, 0, 1, 2, 0, 0, -2, 1, -1, -1, 1, -1),
+% A line in the direction (1, 2, 0, 0, 0, -1, 0, 0, -1, 0, 1, 1),
+% A line in the direction (0, 1, 0, -1, -1, 0, 1, -1, 0, 0, 0, 1))
+%sage: TCCA.inequalities()
+%(An inequality (-2, 1, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0) x + 0 >= 0,
+% An inequality (-1, 0, 0, 0, 0, 0, 0, 0, 0, 1, 1, 0) x + 0 >= 0,
+% An inequality (1, 0, 0, 0, -1, 0, 0, 1, 0, 0, -1, 0) x + 0 >= 0,
+% An inequality (0, 0, -1, 0, 0, 1, -1, 0, 0, 0, 0, 1) x + 0 >= 0,
+% An inequality (1, -1, 0, 0, 0, 0, 0, 0, 0, -1, 0, 1) x + 0 >= 0,
+% An inequality (0, 0, 0, -1, 0, 1, 0, 1, -1, 0, 0, 0) x + 0 >= 0,
+% An inequality (0, 1, 0, 0, 0, 0, 1, 0, 0, 0, 0, -2) x + 0 >= 0,
+% An inequality (0, 0, 1, 0, 0, -1, 0, 0, 1, 0, 0, 0) x + 0 >= 0,
+% An inequality (0, 0, 0, 1, 1, 0, 0, -2, 0, 0, 0, 0) x + 0 >= 0)
+\vincent{todo}
+\end{example}
 
@@
 The \defn{$\b{g}$-vector} of a walk~$\omega$ is~$\gvector{\omega} \eqdef \multiplicityVector_{\peaks{\omega}} - \multiplicityVector_{\deeps{\omega}}$.
-We denote by~$\gvectors{F} \eqdef \set{\gvector{\omega}}{\omega \in F}$ the set of $\b{g}$-vectors of a facet~$F$.
+We set~$\gvectors{F} \eqdef \set{\gvector{\omega}}{\omega \in F}$ for a non-kissing facet~$F \in \NKC$.
 \end{definition}
@@
 The \defn{$\b{c}$-vector} of a walk~$\omega$ in a non-kissing facet~${F \in \NKC}$ is~${\cvector{F}{\omega} \eqdef \distinguishedSign{\omega}{F} \, \multiplicityVector_{\distinguishedString{\omega}{F}}}$, where~$\distinguishedSign{\omega}{F} \in \{-1,1\}$ is positive if~${\distinguishedString{\omega}{F} \in \Sigma_\top(\omega)}$ and negative if~${\distinguishedString{\omega}{F} \in \Sigma_\bottom(\omega)}$.
-We denote by~$\cvectors{F} \eqdef \set{\cvector{F}{\omega}}{\omega \in F}$ the set of $\b{c}$-vectors~of~a~facet~$F$.
+We set~$\cvectors{F} \eqdef \set{\cvector{F}{\omega}}{\omega \in F}$ for a non-kissing facet~$F \in \NKC$.
 \end{definition}
@@
 \item \textbf{Dissection quivers}: Consider a dissection~$D$ of a convex polygon~$P$ (that is a crossing-free set of diagonals of~$P$) and its \defn{gentle dissection quiver}~$\quiver_D$, whose vertices are the internal diagonals of~$D$, whose arrows connect pairs of consecutive internal diagonals along the boundary of a face of~$D$, and whose relations correspond to triples of consecutive internal diagonals along the boundary of a face of~$D$.
-The non-kissing complex of~$\quiver_D$ the corresponds to non-crossing sets of accordions of~$D$, where an accordion is a segment connecting the middles of two boundary edges of~$P$ and crossing a connected set of diagonals of~$D$.
+The non-kissing complex of~$\quiver_D$ then corresponds to non-crossing sets of accordions of~$D$, where an accordion is a segment connecting the middles of two boundary edges of~$P$ and crossing a connected set of diagonals of~$D$.
 This accordion complex was studied in~\cite{GarverMcConville} and~\cite{MannevillePilaud-accordion} with motivation coming from~\cite{Baryshnikov}, and~\cite{Chapoton-quadrangulations}.
@@
 \label{exm:typeConeNKC}
-Consider the gentle quivers of \cref{fig:typeConeNKC}.
+Consider the gentle quivers of \cref{fig:nonkissingFans}.
+%sage: Q = GentleQuiver({'e1':{'e2':['a']}, 'e2':{'e3':['b']}}, [('a','b')])
+%
+%sage: Q.non_kissing_fan().rays()
+%N( 1,  0,  0),
+%N( 0,  0,  1),
+%N( 1, -1,  0),
+%N( 0,  0, -1),
+%N( 0, -1,  0),
+%N(-1,  0,  0),
+%N( 0,  1,  0),
+%N( 0,  1, -1)
+%in 3-d lattice N
+%
+%sage: TCNKC = type_cone_NKC(Q)
+%sage: TCNKC
+%A 8-dimensional polyhedron in QQ^8 defined as the convex hull of 1 vertex, 5 rays, 3 lines
+%sage: TCNKC.inequalities()
+%(An inequality (-1, 0, 1, -1, 0, 0, 0, 1) x + 0 >= 0,
+% An inequality (1, 0, -1, 0, 1, 0, 0, 0) x + 0 >= 0,
+% An inequality (0, 1, 0, 0, 0, 0, -1, 1) x + 0 >= 0,
+% An inequality (0, 0, 1, 0, -1, 1, 0, 0) x + 0 >= 0,
+% An inequality (0, 0, 0, 1, 0, 0, 1, -1) x + 0 >= 0)
+%sage: TCNKC.lines()
+%(A line in the direction (0, 0, 1, 0, 1, 0, -1, -1),
+% A line in the direction (1, 0, 0, 0, -1, -1, 1, 1),
+% A line in the direction (0, 1, 0, -1, 0, 0, 0, -1))
+
+%sage: Q = GentleQuiver({'e1':{'e2':['a']}, 'e2':{'e3':['b']}, 'e3':{'e1':['c']}}, [('b','c')])
+%
+%sage: Q.non_kissing_fan().rays()
+%N( 1,  0,  0),
+%N( 0,  0,  1),
+%N( 1,  0, -1),
+%N( 1, -1,  0),
+%N( 0,  0, -1),
+%N(-1,  0,  1),
+%N( 0, -1,  0),
+%N( 0, -1,  1),
+%N(-1,  0,  0),
+%N( 0,  1,  0),
+%N( 0,  1, -1)
+%in 3-d lattice N
+%
+%sage: TCNKC = type_cone_NKC(Q)
+%sage: TCNKC
+%A 11-dimensional polyhedron in QQ^11 defined as the convex hull of 1 vertex, 9 rays, 3 lines
+%sage: TCNKC.inequalities()
+%(An inequality (0, 0, 0, 1, 0, 1, 0, -1, 0, 0, 0) x + 0 >= 0,
+% An inequality (-1, 0, 1, 0, 0, 0, 0, 0, 0, 1, -1) x + 0 >= 0,
+% An inequality (1, 0, -1, 0, 1, 0, 0, 0, 0, 0, 0) x + 0 >= 0,
+% An inequality (1, -1, 0, -1, 0, 0, 0, 1, 0, 0, 0) x + 0 >= 0,
+% An inequality (0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 1) x + 0 >= 0,
+% An inequality (0, 1, 0, 0, 0, 0, 1, -1, 0, 0, 0) x + 0 >= 0,
+% An inequality (0, 0, 0, 0, 0, -1, -1, 1, 1, 0, 0) x + 0 >= 0,
+% An inequality (0, 0, 1, -1, -1, 0, 1, 0, 0, 0, 0) x + 0 >= 0,
+% An inequality (0, 0, 0, 0, 0, 1, 0, 0, -1, -1, 1) x + 0 >= 0)
+%sage: TCNKC.lines()
+%(A line in the direction (0, 0, 0, 1, 0, 0, 1, 1, 0, -1, -1),
+% A line in the direction (1, 0, 1, 1, 0, -1, 0, 0, -1, 0, 0),
+% A line in the direction (1, 1, 0, 1, -1, 0, 0, 1, -1, 0, -1))
 \vincent{Todo}
@@
 
-In this section, we focus on the following family of gentle quivers, which was also considered in~\cite[Sect.~4]{GarverMcConvilleMousavand}.
+The following family of gentle quivers was considered in~\cite[Sect.~4]{GarverMcConvilleMousavand}.
 
@@
 
+In this section, we need to restrict even further the family of gentle quivers we consider.
+
+\begin{definition}
 We say that a gentle quiver~$\quiver$ is \defn{simple} when
@@
 \end{itemize}
+\end{definition}
+
 Note that this family already contains a lot of relevant examples, including the grid and dissection quivers discussed in \cref{subsubsec:nonkissingComplex}.
@@
 A \defn{tube} of~$\graphG$ is a connected induced subgraph of~$\graphG$.
-The set of tubes of~$\graphG$ is denoted by~$\tubes(\graphG)$.
+The set of tubes of~$\graphG$ is denoted by~$\tubes$.
 The inclusion maximal tubes of~$\graphG$ are its connected components~$\connectedComponents(\graphG)$.
@@
 We consider the hyperplane~${\HH \eqdef \bigset{\b{x} \in \R^\ground}{\sum_{w \in W} x_w = 0 \text{ for all } W \in \connectedComponents(\graphG)}}$ and let~$\pi : \R^\ground \to \HH$ denote the orthogonal projection on~$\HH$.
+
+\begin{definition}
 The \defn{$\b{g}$-vector} of a tube~$\tube$ of~$\graphG$ is the projection~$\gvector{\tube} \eqdef \pi \big( \sum_{v \in \tube} \b{e}_v \big)$ of the characteristic vector of~$\tube$.
-Note that by definition,~$\gvector{\graphG} = 0$.
-We also define~$\gvectors{\tubing} \eqdef \set{\gvector{\tube}}{\tube \in \tubing}$ for a tubing~$\tubing$ on~$\graphG$.
+We set~$\gvectors{\tubing} \eqdef \set{\gvector{\tube}}{\tube \in \tubing}$ for a tubing~$\tubing$ on~$\graphG$.
+\end{definition}
+
+Note that by definition, $\gvector(\varnothing) = 0$ and $\gvector{W} = 0$ for all connected components~$W \in \connectedComponents(\graphG)$.
 These vectors support a complete simplicial fan realization of the nested complex.
@@
 
-\begin{figure}[h]
+\begin{figure}[b]
 	\capstart
@@
 \begin{theorem}[\cite{CarrDevadoss, Postnikov, FeichtnerSturmfels, Zelevinsky}]
+\label{thm:nestedFan}
 For any graph~$\graphG$, the set of cones
@@
 \begin{theorem}[\cite{CarrDevadoss, Devadoss, Postnikov, FeichtnerSturmfels, Zelevinsky}]
-For any graph~$\graphG$, the nested fan~$\gvectorFan[\graphG]$ is the normal fan of the graph associahedron~$\Asso[\graphG]$, defined as the Minkowski sum~$\sum_{\tube \in \tubes(\graphG)} \triangle_{\tube}$ of the faces of the standard simplex corresponding to all tubes of~$\graphG$.
+For any graph~$\graphG$, the nested fan~$\gvectorFan[\graphG]$ is the normal fan of the graph associahedron~$\Asso[\graphG]$, defined as the Minkowski sum~$\sum_{\tube \in \tubes} \triangle_{\tube}$ of the faces of the standard simplex corresponding to all tubes of~$\graphG$.
 \end{theorem}
@@
 
-We are now ready to describe the type cone of the nested fan~$\gvectorFan[\graphG]$.
-We first treat the case when~$G$ is a path so that the $\graphG$-associahedron is a classical associahedron.
-We show that the type cone is then simplicial which gives another proof of \cref{thm:simplicialTypeConeAsso} and \cref{coro:descriptionAllAsso}.
-
-\subsubsection{Simplicial type cones for path associahedra}
-
-We start with the case of the path on~$n+1$ vertices.
-Recall that the tubes of the path are the intervals of~$[n+1]$ and that two intervals~$[i,j]$ and~$[i',j']$ of~$[n+1]$ are exchangeable if either~${i < i' \le j+1 < j'+1}$ or~${i' < i \le j'+1 < j+1}$.
+\subsubsection{Type cones of graphical nested fans}
+
+We now discuss the type cones of the graphical nested fans defined in \cref{thm:nestedFan}.
+We first obtain from \cref{prop:exchangeablePairsGA} the following redundant description.
+
+\begin{corollary}
+For any graph~$\graphG$, the type cone of the nested fan~$\gvectorFan[\graphG]$ is given by
+\[
+\typeCone(\gvectorFan[\graphG]) = \set{\b{h} \in \R^{\tubes}}{\begin{array}{l} \b{h}_{\tube} = 0 \text{ for any improper tube } \tube \\ \b{h}_{\tube} + \b{h}_{\tube'} > \b{h}_{\tube \cup \tube'} + \sum_{\tube[s] \in \connectedComponents(\tube \cap \tube')} \b{h}_{\tube[s]} \text{ for any exchangeable tubes } \tube, \tube' \end{array}}.
+\]
+\end{corollary}
+
+\begin{example}
+\label{exm:typeConeGA}
+\vincent{Todo}
+\end{example}
+
+In the remaining of this section, we describe the facet defining inequalities of the type cone of the graphical nested fans.
+Observe first that we have already indirectly described this type cone when the graph is a path in \cref{prop:extremalExchangeablePairsAsso}.
+Recall that on the path with~$n+1$ vertices, the tubes of the path are the intervals of~$[n+1]$ and that two intervals~$[i,j]$ and~$[i',j']$ of~$[n+1]$ are exchangeable if either~${i < i' \le j+1 < j'+1}$ or~${i' < i \le j'+1 < j+1}$.
 
@@
 \end{proposition}
-
-\begin{proof}
-Let~$(\b{f}_{[i,j]})_{1 \le i \le j \le n}$ be the canonical basis of~$\R^{\binom{n+1}{2}}$.
-Consider two exchangeable tubes~$[i,j]$ and~$[i',j']$ with~${i < i' \le j+1 < j'+1}$.
-By \cref{prop:exchangeablePairsGA}\,(iii), the linear dependence between the corresponding $\b{g}$-vectors is given by
-\[
-\gvector{[i,j]} + \gvector{[i',j']} = \gvector{[i,j']} + \gvector{[i',j]}.
-\]
-Therefore, the outer normal vector of the corresponding inequality of the type cone~$\typeCone(\gvectorFan[\graphG])$ is
-\[
-\b{n}(i,j,i',j') \eqdef \b{f}_{[i,j]} + \b{f}_{[i',j']} - \b{f}_{[i,j']} - \b{f}_{[i',j]}.
-\]
-Denoting
-\[
-\b{m}(k,\ell) \eqdef \b{n}(k,\ell-1,k+1,\ell) = \b{f}_{[k, \ell-1]} + \b{f}_{[k+1, \ell]} - \b{f}_{[k, \ell]} - \b{f}_{[k+1, \ell-1]},
-\]
-we obtain that
-\[
-\b{n}(i,j,i',j') = \sum_{\substack{k \in {[i,i'[} \\ \ell \in {]j,j']}}} \b{m}(k,\ell).
-\]
-Indeed, on the right hand side, the basis vector~$\b{f}_{[k,\ell]}$ appears with a positive sign in~$\b{m}(k,{\ell+1})$ for~$(k,\ell) \in {[i,i'[} \times {[j,j'[}$ and in~$\b{m}(k-1, \ell)$ for~$(k,\ell) \in {]i,i']} \times {]j,j']}$, and with a negative sign in~$\b{m}(k,\ell)$ for~$(k,\ell) \in {[i,i'[} \times {]j,j']}$ and in~$\b{m}(k-1,\ell+1)$ for~$(k,\ell) \in {]i,i']} \times {[j,j'[}$.
-Therefore, these contributions all vanish except when~$[k, \ell]$ is one of the tubes~$[i,j]$, $[i',j']$, $[i,j']$ or~$[i',j]$.
-%For any~$i \le k < i'$ and~$j < \ell \le j'$, the exchange relation between the tubes~$[k, \ell-1]$ and~$[k+1, \ell]$ is given by
-%\begin{equation}
-%\label{eq:exch2}
-%\tag{$\mathrm{ER}_k^\ell$}
-%\gvector{[k, \ell-1]} + \gvector{[k+1, \ell]} = \gvector{[k, \ell]} + \gvector{[k+1, \ell-1]}.
-%\end{equation}
-%Summing the exchange relations~\eqref{eq:exch2} over all pairs~$(k,\ell) \in {[i,i'[} \times {]j,j']}$, we obtain after simplifications the exchange relation~\eqref{eq:exch1}.
-%Indeed, the $\b{g}$-vector of each tube~$[k, \ell]$ appears on the left hand sides of the exchange relations~($\mathrm{ER}_k^{\ell+1}$) for~$(k,\ell) \in {[i,i'[} \times {[j,j'[}$ and ($\mathrm{ER}_{k-1}^\ell$) for~$(k,\ell) \in {]i,i']} \times {]j,j']}$ and on the right hand sides of the exchange relations~($\mathrm{ER}_k^\ell$) for~$(k,\ell) \in {[i,i'[} \times {]j,j']}$ and~($\mathrm{ER}_{k-1}^{\ell+1}$) for~$(k,\ell) \in {]i,i']} \times {[j,j'[}$.
-%Therefore, these contributions all vanish except when~$[k, \ell]$ is one of the tubes~$[i,j]$, $[i',j']$, $[i,j']$ or~$[i',j]$.
-This shows that any exchange relation is a positive linear combination of the exchange relations corresponding to all pairs of tubes~$[i,j]$ and~$[i',j']$ of~$[n+1]$ such that~$i = i'+1$ and~$j = j'+1$.
-
-We now need to show that all these exchangeable pairs are extremal.
-Assume that~$\b{m}(k,\ell)$ can be written as the linear combination
-\begin{equation}
-\label{eq:linComb}
-\b{m}(k,\ell) = \sum \lambda(i,j,i',j') \, \b{n}(i,j,i',j'),
-\end{equation}
-where~$\lambda(i,j,i',j') \ge 0$ for all exchangeable pairs~$\{[i,j], [i',j']\}$.
-Note that~$\sum \lambda(i,j,i',j') \ge 1$ since the coefficient of~$\b{f}_{[k,\ell]}$ in~$\b{m}(k,\ell)$ is~$-1$.
-Consider the linear form~$\Phi: \R^N \to \R$ defined by~$\Phi(\b{f}_{[i,j]}) = -(j-i)^2$.
-A quick computation shows that
-\[
-\Phi(\b{n}(i,j,i',j')) = 2(i'-i)(j'-j).
-\]
-Applying~$\Phi$ to \cref{eq:linComb}, we obtain
-\[
-1 = \sum \lambda(i,j,i',j')(i'-i)(j'-j).
-\]
-Since~$\sum \lambda(i,j,i',j') \ge 1$ we obtain that~$\lambda(k,\ell-1,k+1,\ell) = 1$ and~$\lambda(i,j,i',j') = 0$ for all other exchangeable pairs~$\{[i,j], [i',j']\}$.
-\end{proof}
-
-\subsubsection{General case}
 
@@
 \begin{enumerate}[(i)]
-\item the pairs of tubes~$\tube[r] \cup \{v\}$ and~$\tube[r] \cup \{v'\}$ for any tube~$\tube[r] \in \tubes(\graphG)$ and distinct neighbors~$v,v'$ of~$\tube[r]$,
-\item the pairs of tubes~$\tube[s] \ssm \{v'\}$ and~$\tube[s] \ssm \{v\}$ for any tube~$\tube[s] \in \tubes(\graphG)$ and distinct non-disconnecting vertices~$v,v'$ of~$\tube[s]$,
+\item the pairs of tubes~$\tube[r] \cup \{v\}$ and~$\tube[r] \cup \{v'\}$ for any tube~$\tube[r] \in \tubes$ and distinct neighbors~$v,v'$ of~$\tube[r]$,
+\item the pairs of tubes~$\tube[s] \ssm \{v'\}$ and~$\tube[s] \ssm \{v\}$ for any tube~$\tube[s] \in \tubes$ and distinct non-disconnecting vertices~$v,v'$ of~$\tube[s]$,
 \end{enumerate}
@@
 %\begin{corollary}
-%Consider a graph~$\graphG$ on~$\ground$ with tubes~$\tubes(\graphG)$ and a height vector~$\b{h} \in \R^{\tubes(\graphG)}$ such that~$\b{h}_{\graphG} = 0$ and
+%Consider a graph~$\graphG$ on~$\ground$ with tubes~$\tubes$ and a height vector~$\b{h} \in \R^{\tubes}$ such that~$\b{h}_{\graphG} = 0$ and
 %\[
@@
 %\[
-%\set{\b{x} \in \R^\ground}{\dotprod{\gvector{\tube}}{\b{x}} \le \b{h}_{\tube} \text{ for any tube } \tube \in \tubes(\graphG)}.
+%\set{\b{x} \in \R^\ground}{\dotprod{\gvector{\tube}}{\b{x}} \le \b{h}_{\tube} \text{ for any tube } \tube \in \tubes}.
 %\]
@@
 \begin{corollary}
-Consider a graph~$\graphG$ on~$\ground$ with tubes~$\tubes(\graphG)$ and a height vector~$\b{h} \in \R^{\tubes(\graphG)}$ such that~$\b{h}_{\varnothing} = \b{h}_{\graphG} = 0$ and satisfying one of the two following equivalent conditions:
+Consider a graph~$\graphG$ on~$\ground$ with tubes~$\tubes$ and a height vector~$\b{h} \in \R^{\tubes}$ such that~$\b{h}_{\varnothing} = \b{h}_{\graphG} = 0$ and satisfying one of the two following equivalent conditions:
 \begin{enumerate}[(i)]
-\item $\b{h}_{\tube[r] \cup \{v\}} + \b{h}_{\tube[r] \cup \{v'\}} > \b{h}_{\tube[r] \cup \{v, v'\}} + \b{h}_{\tube[r]}$ for any tube~$\tube[r] \in \tubes(\graphG)$ and distinct neighbors~$v,v'$ of~$\tube[r]$,
-\item $\b{h}_{\tube[s] \ssm \{v'\}} + \b{h}_{\tube[s] \ssm \{v\}} > \b{h}_{\tube[s]} + \b{h}_{\tube[s] \ssm \{v, v'\}}$ for any tube~$\tube[s] \in \tubes(\graphG)$ and distinct non-disconnecting vertices~$v,v'$ of~$\tube[s]$.
+\item $\b{h}_{\tube[r] \cup \{v\}} + \b{h}_{\tube[r] \cup \{v'\}} > \b{h}_{\tube[r] \cup \{v, v'\}} + \b{h}_{\tube[r]}$ for any tube~$\tube[r] \in \tubes$ and distinct neighbors~$v,v'$ of~$\tube[r]$,
+\item $\b{h}_{\tube[s] \ssm \{v'\}} + \b{h}_{\tube[s] \ssm \{v\}} > \b{h}_{\tube[s]} + \b{h}_{\tube[s] \ssm \{v, v'\}}$ for any tube~$\tube[s] \in \tubes$ and distinct non-disconnecting vertices~$v,v'$ of~$\tube[s]$.
 \end{enumerate}
@@
 \[
-\set{\b{x} \in \R^\ground}{\dotprod{\gvector{\tube}}{\b{x}} \le \b{h}_{\tube} \text{ for any tube } \tube \in \tubes(\graphG)}.
+\set{\b{x} \in \R^\ground}{\dotprod{\gvector{\tube}}{\b{x}} \le \b{h}_{\tube} \text{ for any tube } \tube \in \tubes}.
 \]
@@
 The nested fan~$\gvectorFan[\graphG]$ has~$\!\!\!\!
-\sum\limits_{\tube[r] \in \tubes(\graphG)} \!\!
+\sum\limits_{\tube[r] \in \tubes} \!\!
 \binom{\neighbors(\tube[r])}{2} = \!\!\!\!
-\sum\limits_{\tube[s] \in \tubes(\graphG)} \!\!
+\sum\limits_{\tube[s] \in \tubes} \!\!
 \binom{\nonDisconnecting(\tube[s])}{2}$ extremal exchangeable pairs.
@@
 Note that any tube~$\tube$ with~$|\tube| \ge 2$ has two non-disconnecting vertices when it is a path, and at least three non-disconnecting vertices otherwise (the leaves of an arbitrary spanning tree of~$\tube$).
-Therefore, each tube of~$\tubes(\graphG)$ which is not a singleton contributes to at least one extremal exchangeable pairs.
+Therefore, each tube of~$\tubes$ which is not a singleton contributes to at least one extremal exchangeable pairs.
 We conclude that the number of extremal exchangeable pairs is at least:
 \[
-|\tubes(\graphG)| - |V| = |\tubes(\graphG) \ssm \{\varnothing, \graphG\}| - (|V|-1) = N - n,
+|\tubes| - |V| = |\tubes \ssm \{\varnothing, \graphG\}| - (|V|-1) = N - n,
 \]

### 2019-04-01 thirdPaper/draft/typeConeAssociahedra.tex
improvements + table

@@
 Here, we will focus on finite type cluster algebras~\cite{FominZelevinsky-ClusterAlgebrasII} and more specifically on properties of their $\b{g}$-vectors~\cite{FominZelevinsky-ClusterAlgebrasIV}.
-These $\b{g}$-vectors support a complete simplicial fan, which is known to be the normal fan of a polytope called generalized associahedron.
+These $\b{g}$-vectors support a complete simplicial fan, which is called \defn{$\b{g}$-vector fan} or \defn{cluster fan}.
+It is known to be the normal fan of a polytope called generalized associahedron.
 These polytopal realizations were first constructed for bipartite initial seeds by F.~Chapoton, S.~Fomin and A.~Zelevinsky~\cite{ChapotonFominZelevinsky} using the $\b{d}$-vector fans of~\cite{FominZelevinsky-YSystems}, then for acyclic initial seeds by C.~Hohlweg, C.~Lange and H.~Thomas~\cite{HohlwegLangeThomas} using Cambrian lattices and fans of N.~Reading and D.~Speyer~\cite{Reading-CambrianLattices, ReadingSpeyer}, and revisited by S.~Stella~\cite{Stella}, and by V.~Pilaud and C.~Stump~\cite{PilaudStump-brickPolytope} via brick polytopes, and finally for arbitrary initial seeds by C.~Hohlweg, V.~Pilaud and S.~Stella~\cite{HohlwegPilaudStella}.
 More recently in~\cite{BazierMatteDouvilleMousavandThomasYildirim}, V.~Bazier-Matte, G.~Douville, K.~Mousavand, H.~Thomas and E.~Yildirim extended the construction of associahedra of~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} to acyclic seeds of simply laced finite type cluster algebras.
-Here, we extend the construction of~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} to any finite type (simply laced or not) cluster algebra with respect to any seed (acyclic or not) by providing a direct proof that the type cone of the $\b{g}$-vector fan of any finite type cluster algebra is simplicial.
-
-\subsubsection{Cluster algebras and $\b{g}$-vector fans}
-
-We present some definitions and properties of finite type cluster algebras and their $\b{g}$-vector fans, following the presentation of~\cite{HohlwegPilaudStella}.
+Here, we extend the construction of~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} to any finite type (simply laced or not) cluster algebra with respect to any seed (acyclic or not) by providing a direct proof that the type cone of the cluster fan of any finite type cluster algebra is simplicial.
+
+\subsubsection{Cluster algebras and cluster fans}
+
+We present some definitions and properties of finite type cluster algebras and their cluster fans, following the presentation of~\cite{HohlwegPilaudStella}.
 
@@
 
-\para{The $\b{g}$-vector fan and generalized associahedron}
+\para{Cluster fan and generalized associahedron}
 %
@@
 	}
-	\caption{Two $\b{g}$-vector fans~$\gvectorFan[\B_\circ]$ for the type~$A_3$~(left) and type~$C_3$~(right) cyclic initial exchange matrices.
+	\caption{Two cluster fans~$\gvectorFan[\B_\circ]$ for the type~$A_3$~(left) and type~$C_3$~(right) cyclic initial exchange matrices.
 As the fans are $3$-dimensional, we intersect them with the sphere and stereographically project them from the direction~$(-1,-1,-1)$.
@@
 } \\[.1cm]
-together with all their faces, forms a complete simplicial fan, called the \defn{$\b{g}$-vector fan} of~$\B_\circ$.
+together with all their faces, forms a complete simplicial fan, called the \defn{$\b{g}$-vector fan} or \defn{cluster fan} of~$\B_\circ$.
 \end{theorem}
@@
 \label{thm:generalizedAsso}
-For any finite type exchange matrix~$\B_\circ$, the $\b{g}$-vector fan~$\gvectorFan[\B_\circ]$ is the normal fan of the \defn{$\B_\circ$-associahedron}~$\Asso[\B_\circ, \b{h}]$ defined equivalently as
+For any finite type exchange matrix~$\B_\circ$, the cluster fan~$\gvectorFan[\B_\circ]$ is the normal fan of the \defn{$\B_\circ$-associahedron}~$\Asso[\B_\circ, \b{h}]$ defined equivalently as
 \begin{enumerate}[(i)]
@@
 
-\para{Mutations in the $\b{g}$-vector fan}
+\para{Mutations in the cluster fan}
 %
@@
 
-Note that \cref{lem:linearDependencegvectorsCA} implies \cref{thm:generalizedAsso} since it ensures that the type cone~$\typeCone(\gvectorFan[\B_\circ])$ of the $\b{g}$-vector fan contains the cone of~${\b{h} \in \R^{\principalVariables}}$ such that
+Note that \cref{lem:linearDependencegvectorsCA} implies \cref{thm:generalizedAsso} since it ensures that the type cone~$\typeCone(\gvectorFan[\B_\circ])$ of the cluster fan contains the cone of~${\b{h} \in \R^{\principalVariables}}$ such that
 \(
@@
 \label{prop:uniqueExchangePropertyCA}
-For any finite type exchange matrix~$\B_\circ$, the $\b{g}$-vector fan has the unique exchange relation property.
+For any finite type exchange matrix~$\B_\circ$, the cluster fan has the unique exchange relation property.
 \end{proposition}
 
-\subsubsection{Type cone of finite type $\b{g}$-vector fans}
-
-The linear dependences of \cref{lem:linearDependencegvectorsCA} provide a redundant description of the type cone of the $\b{g}$-vector fan~$\gvectorFan[\B_\circ]$.
+\subsubsection{Type cone of finite type cluster fans}
+
+The linear dependences of \cref{lem:linearDependencegvectorsCA} provide a redundant description of the type cone of the cluster fan~$\gvectorFan[\B_\circ]$.
 We denote by~$\b{n}(\B_\circ, x, x')$ the normal vector of the inequality of the type cone corresponding to two exchangeable cluster variable~$x$ to~$x'$ (it is well defined by \cref{prop:uniqueExchangePropertyCA}).
@@
 \label{coro:typeConeCA}
-For any finite type exchange matrix~$\B_\circ$, the type cone of the $\b{g}$-vector fan~$\gvectorFan[\B_\circ]$ is given by
+For any finite type exchange matrix~$\B_\circ$, the type cone of the cluster fan~$\gvectorFan[\B_\circ]$ is given by
 \[
@@
 \begin{example}
+Consider the initial $B$-matrices~$\B_\circ$ whose cluster fans are illustrated in \cref{fig:clusterFans}.
+\newcommand{\compactVector}[3]{\begin{bmatrix} #1 \\[-.1cm] #2 \\[-.1cm] #3 \end{bmatrix}}
+
+\[
+\begin{array}{c|ccccccccc}
+\text{variables} & \rotatebox{70}{$x_1$} & \rotatebox{70}{$x_2$} & \rotatebox{70}{$x_3$} & \rotatebox{70}{$\frac{x_2 + x_3}{x_1}$} & \rotatebox{70}{$\frac{x_1 + x_3}{x_2}$} & \rotatebox{70}{$\frac{x_1 + x_2}{x_3}$} & \rotatebox{70}{$\frac{x_1 + x_2 + x_3}{x_2 x_3}$} & \rotatebox{70}{$\frac{x_1 + x_2 + x_3}{x_1 x_3}$} & \rotatebox{70}{$\frac{x_1 + x_2 + x_3}{x_1 x_2}$} \\[.3cm]
+\text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{-1}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{0}{1}{-1} & \compactVector{0}{0}{-1} & \compactVector{-1}{0}{0} & \compactVector{0}{-1}{0} \\[.5cm]
+\text{lines}		& 0 & 0 & 1 & 1 & 0 & -1 & -1 & 0 & 0 \\
+					& 0 & -1 & 0 & 0 & 1 & -1 & 0 & 0 & 1 \\
+					& 1 & 1 & 0 & -1 & 0 & 1 & 0 & -1 & -1 \\[.2cm]
+\text{inequalities} & -1 & 0 & 0 & 0 & 1 & 1 & -1 & 0 & 0 \\
+ 					& 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 1 \\
+ 					& 0 & 0 & -1 & 1 & 1 & 0 & 0 & 0 & -1 \\
+ 					& 0 & 0 & 1 & -1 & 0 & 0 & 0 & 1 & 0 \\
+ 					& 0 & 1 & 0 & 0 & 0 & -1 & 1 & 0 & 0 \\
+ 					& 0 & -1 & 0 & 1 & 0 & 1 & 0 & -1 & 0
+\end{array}
+\]
+
 %sage: B = Matrix([[0,-1,1],[1,0,-1],[-1,1,0]])
@@
 %A 9-dimensional polyhedron in QQ^9 defined as the convex hull of 1 vertex, 6 rays, 3 lines
+%sage: TCCA.lines()
+%(A line in the direction (0, 1, 0, -1, 1, 0, 0, 0, -1),
+% A line in the direction (0, 0, 1, 0, 0, 1, 0, -1, -1),
+% A line in the direction (1, 0, 0, 0, -1, -1, -1, 1, 1))
 %sage: TCCA.inequalities()
@@
 % An inequality (0, 0, 0, 0, 1, 0, -1, -1, 1) x + 0 >= 0)
+
+\centerline{$
+\begin{array}{c|c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;}c@{\;}c@{\;}c@{}c@{}c@{}c}
+\text{variables} & \rotatebox{70}{$x_1$} & \rotatebox{70}{$x_2$} & \rotatebox{70}{$x_3$} & \rotatebox{70}{$\frac{x_2 + x_3}{x_1}$} & \rotatebox{70}{$\frac{x_1 + x_3}{x_2}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2}{x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + x_1 x_3}{x_2 x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + x_2 x_3}{x_1 x_3}$} & \rotatebox{70}{$\frac{x_1 + x_2 + x_3}{x_1 x_2}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + 2 x_1 x_3 + x_3^2}{x_2^2 x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + 2 x_2 x_3 + x_3^2}{x_1^2 x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + x_1 x_3 + x_2 x_3}{x_1 x_2 x_3}$} \\[.3cm]
+\text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{-1}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{0}{2}{-1} & \compactVector{0}{1}{-1} & \compactVector{-1}{1}{0} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} & \compactVector{-2}{0}{1} & \compactVector{-1}{0}{0}  \\[.5cm]
+\text{lines}		& 1 & 1 & 2 & 1 & 0 & 0 & -1 & 0 & -1 & -2 & 0 & -1 \\
+					& 0 & 1 & 0 & 0 & -1 & 2 & 1 & 1 & -1 & 0 & 0 & 0 \\
+					& 0 & 0 & -1 & -1 & 0 & 1 & 1 & 0 & 0 & 1 & -1 & 0 \\[.2cm]
+\text{inequalities} & 0 & 0 & 0 & 0 & 0 & 1 & 0 & -2 & 0 & 0 & 1 & 0 \\
+					& 0 & 1 & 0 & 0 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 1 \\
+					& 0 & -1 & 0 & 1 & 0 & 0 & 0 & 1 & 0 & 0 & -1 & 0 \\
+					& -1 & 0 & 0 & 0 & 1 & 0 & 1 & 0 & 0 & -1 & 0 & 0 \\
+					& 0 & 0 & 0 & 0 & 0 & -1 & 1 & 1 & 0 & 0 & 0 & -1 \\
+					& 0 & 0 & -1 & 1 & 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 \\
+					& 0 & 0 & 0 & 0 & 0 & 1 & -2 & 0 & 0 & 1 & 0 & 0 \\
+					& 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 1 & 0 & 0 & 0 \\
+					& 0 & 0 & 1 & -2 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0
+\end{array}
+$}
 
@@
 \label{prop:extremalExchangeablePairsCA}
-For any finite type exchange matrix~$\B_\circ$ (acyclic or not), the non-initial mesh mutations precisely correspond to the extremal exchangeable pairs of the $\b{g}$-vector fan~$\gvectorFan[\B_\circ]$.
+For any finite type exchange matrix~$\B_\circ$ (acyclic or not), the non-initial mesh mutations precisely correspond to the extremal exchangeable pairs of the cluster fan~$\gvectorFan[\B_\circ]$.
 \end{proposition}
@@
 
-Combining \cref{coro:simplicialTypeCone,coro:simplicialTypeConeCA,prop:extremalExchangeablePairsCA}, we derive the following description of all polytopal realizations of the $\b{g}$-vector fan~$\gvectorFan[\B_\circ]$.
+Combining \cref{coro:simplicialTypeCone,coro:simplicialTypeConeCA,prop:extremalExchangeablePairsCA}, we derive the following description of all polytopal realizations of the cluster fan~$\gvectorFan[\B_\circ]$.
 This result was stated in~\cite{BazierMatteDouvilleMousavandThomasYildirim} in the special situation of acyclic seeds in simply-laced types.
@@
 \]
-is a generalized associahedron, whose normal fan is the $\b{g}$-vector fan~$\gvectorFan[\B_\circ]$.
+is a generalized associahedron, whose normal fan is the cluster fan~$\gvectorFan[\B_\circ]$.
 \end{theorem}
@@
 \label{exm:typeConeNKC}
-Consider the gentle quivers of \cref{fig:nonkissingFans}.
+Consider the gentle quivers whose non-kissing fans are illustrated in \cref{fig:nonkissingFans}.
 %sage: Q = GentleQuiver({'e1':{'e2':['a']}, 'e2':{'e3':['b']}}, [('a','b')])

### 2019-04-01 thirdPaper/draft/typeConeAssociahedra.tex
more tables

@@
 \usetikzlibrary{trees, decorations, decorations.markings, shapes, arrows, matrix, calc, fit, intersections, patterns, angles}
-\graphicspath{{figures/}}
+\graphicspath{{figures/}{figures/walks/}{figures/tubes}}
 \makeatletter\def\input@path{{figures/}}\makeatother
@@
 \newcommand*\circled[1]{\tikz[baseline=(char.base)]{\node[shape=circle,draw,inner sep=1pt, scale=.7] (char) {#1};}}
+\newcommand{\compactVector}[3]{\begin{bmatrix} #1 \\[-.1cm] #2 \\[-.1cm] #3 \end{bmatrix}}
 
@@
 \begin{example}
-Consider the initial $B$-matrices~$\B_\circ$ whose cluster fans are illustrated in \cref{fig:clusterFans}.
-\newcommand{\compactVector}[3]{\begin{bmatrix} #1 \\[-.1cm] #2 \\[-.1cm] #3 \end{bmatrix}}
-
-\[
-\begin{array}{c|ccccccccc}
-\text{variables} & \rotatebox{70}{$x_1$} & \rotatebox{70}{$x_2$} & \rotatebox{70}{$x_3$} & \rotatebox{70}{$\frac{x_2 + x_3}{x_1}$} & \rotatebox{70}{$\frac{x_1 + x_3}{x_2}$} & \rotatebox{70}{$\frac{x_1 + x_2}{x_3}$} & \rotatebox{70}{$\frac{x_1 + x_2 + x_3}{x_2 x_3}$} & \rotatebox{70}{$\frac{x_1 + x_2 + x_3}{x_1 x_3}$} & \rotatebox{70}{$\frac{x_1 + x_2 + x_3}{x_1 x_2}$} \\[.3cm]
-\text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{-1}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{0}{1}{-1} & \compactVector{0}{0}{-1} & \compactVector{-1}{0}{0} & \compactVector{0}{-1}{0} \\[.5cm]
+Consider the cluster fans illustrated in \cref{fig:clusterFans}.
+The type cone of the left one lives in~$\R^9$, has a linearity space of dimension~$3$ (a basis is given below) and $6$ facet defining inequalities (given below).
+
+\[
+\begin{array}{r|ccccccccc}
+\text{variables} & \rotatebox{70}{$x_1$} & \rotatebox{70}{$x_2$} & \rotatebox{70}{$x_3$} & \rotatebox{70}{$\frac{x_2 + x_3}{x_1}$} & \rotatebox{70}{$\frac{x_1 + x_3}{x_2}$} & \rotatebox{70}{$\frac{x_1 + x_2}{x_3}$} & \rotatebox{70}{$\frac{x_1 + x_2 + x_3}{x_2 x_3}$} & \rotatebox{70}{$\frac{x_1 + x_2 + x_3}{x_1 x_3}$} & \rotatebox{70}{$\frac{x_1 + x_2 + x_3}{x_1 x_2}$} \\[.2cm]
+\text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{-1}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{0}{1}{-1} & \compactVector{0}{0}{-1} & \compactVector{-1}{0}{0} & \compactVector{0}{-1}{0} \\[.6cm]
 \text{lines}		& 0 & 0 & 1 & 1 & 0 & -1 & -1 & 0 & 0 \\
@@
 
-\centerline{$
-\begin{array}{c|c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;}c@{\;}c@{\;}c@{}c@{}c@{}c}
-\text{variables} & \rotatebox{70}{$x_1$} & \rotatebox{70}{$x_2$} & \rotatebox{70}{$x_3$} & \rotatebox{70}{$\frac{x_2 + x_3}{x_1}$} & \rotatebox{70}{$\frac{x_1 + x_3}{x_2}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2}{x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + x_1 x_3}{x_2 x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + x_2 x_3}{x_1 x_3}$} & \rotatebox{70}{$\frac{x_1 + x_2 + x_3}{x_1 x_2}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + 2 x_1 x_3 + x_3^2}{x_2^2 x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + 2 x_2 x_3 + x_3^2}{x_1^2 x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + x_1 x_3 + x_2 x_3}{x_1 x_2 x_3}$} \\[.3cm]
-\text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{-1}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{0}{2}{-1} & \compactVector{0}{1}{-1} & \compactVector{-1}{1}{0} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} & \compactVector{-2}{0}{1} & \compactVector{-1}{0}{0}  \\[.5cm]
+\bigskip
+\noindent
+The type cone of the right one lives in~$\R^12$, has a linearity space of dimension~$3$ (a basis is given below) and $9$ facet defining inequalities (given below).
+
+\[
+\begin{array}{r|c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;}c@{\;}c@{\;}c@{}c@{}c@{}c}
+\text{variables} & \rotatebox{70}{$x_1$} & \rotatebox{70}{$x_2$} & \rotatebox{70}{$x_3$} & \rotatebox{70}{$\frac{x_2 + x_3}{x_1}$} & \rotatebox{70}{$\frac{x_1 + x_3}{x_2}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2}{x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + x_1 x_3}{x_2 x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + x_2 x_3}{x_1 x_3}$} & \rotatebox{70}{$\frac{x_1 + x_2 + x_3}{x_1 x_2}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + 2 x_1 x_3 + x_3^2}{x_2^2 x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + 2 x_2 x_3 + x_3^2}{x_1^2 x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + x_1 x_3 + x_2 x_3}{x_1 x_2 x_3}$} \\[.2cm]
+\text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{-1}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{0}{2}{-1} & \compactVector{0}{1}{-1} & \compactVector{-1}{1}{0} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} & \compactVector{-2}{0}{1} & \compactVector{-1}{0}{0}  \\[.6cm]
 \text{lines}		& 1 & 1 & 2 & 1 & 0 & 0 & -1 & 0 & -1 & -2 & 0 & -1 \\
@@
 \end{array}
-$}
+\]
 
@@
 \label{exm:typeConeNKC}
-Consider the gentle quivers whose non-kissing fans are illustrated in \cref{fig:nonkissingFans}.
+Consider the non-kissing fans illustrated in \cref{fig:nonkissingFans}.
+The type cone of the left one lives in~$\R^9$, has a linearity space of dimension~$3$ (a basis is given below) and $6$ facet defining inequalities (given below).
+
+\[
+\begin{array}{r|cccccccc}
+\text{walks} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA1}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA2}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA3}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA4}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA5}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA6}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA7}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA8}} \\[.6cm]
+\text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{0}{1}{-1} & \compactVector{-1}{0}{0} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} \\[.6cm]
+\text{lines}		& 0 & -1 & 0 & 1 & -1 & 0 & 1 & 0 \\
+					& 1 & 1 & 0 & 0 & 1 & -1 & -1 & 0 \\
+					& 0 & 0 & 1 & 0 & -1 & 0 & 0 & -1 \\[.2cm]
+\text{inequalities} & -1 & 0 & 0 & 1 & 1 & 0 & 0 & -1 \\
+					& 1 & 0 & 0 & -1 & 0 & 0 & 1 & 0 \\
+					& 0 & -1 & 1 & 0 & 1 & 0 & 0 & 0 \\
+					& 0 & 0 & 0 & 1 & 0 & 1 & -1 & 0 \\
+					& 0 & 1 & 0 & 0 & -1 & 0 & 0 & 1
+\end{array}
+\]
+
 %sage: Q = GentleQuiver({'e1':{'e2':['a']}, 'e2':{'e3':['b']}}, [('a','b')])
@@
 %A 8-dimensional polyhedron in QQ^8 defined as the convex hull of 1 vertex, 5 rays, 3 lines
+%sage: TCNKC.lines()
+%(A line in the direction (0, 0, 1, 0, 1, 0, -1, -1),
+% A line in the direction (1, 0, 0, 0, -1, -1, 1, 1),
+% A line in the direction (0, 1, 0, -1, 0, 0, 0, -1))
 %sage: TCNKC.inequalities()
@@
 % An inequality (0, 0, 0, 1, 0, 0, 1, -1) x + 0 >= 0)
-%sage: TCNKC.lines()
-%(A line in the direction (0, 0, 1, 0, 1, 0, -1, -1),
-% A line in the direction (1, 0, 0, 0, -1, -1, 1, 1),
-% A line in the direction (0, 1, 0, -1, 0, 0, 0, -1))
+
+\bigskip
+\noindent
+The type cone of the right one lives in~$\R^11$, has a linearity space of dimension~$3$ (a basis is given below) and $9$ facet defining inequalities (given below). In particular, it is not simplicial.
+
+\[
+\begin{array}{r|c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c}
+\text{walks} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB1}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB2}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB3}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB4}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB5}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB6}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB7}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB8}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB9}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB10}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB11}} \\[.6cm]
+\text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{1}{0}{-1} & \compactVector{0}{-1}{1} & \compactVector{0}{1}{-1} & \compactVector{-1}{0}{1} & \compactVector{-1}{0}{0} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} \\[.6cm]
+\text{lines}		& 0 & -1 & 0 & 1 & 0 & 1 & -1 & 0 & 0 & 1 & 0 \\
+					& 1 & 0 & 0 & 1 & 1 & 0 & 0 & -1 & -1 & 0 & 0 \\
+					& 1 & 0 & 1 & 1 & 0 & 1 & -1 & 0 & -1 & 0 & -1 \\[.2cm]
+\text{inequalities} & 0 & 0 & 0 & 1 & 0 & -1 & 0 & 1 & 0 & 0 & 0 \\
+					& -1 & 1 & 0 & 0 & 1 & 0 & -1 & 0 & 0 & 0 & 0 \\
+					& 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 0 & 0 & 1 \\
+					& 1 & 0 & -1 & -1 & 0 & 1 & 0 & 0 & 0 & 0 & 0 \\
+					& 0 & 0 & 0 & 1 & -1 & 0 & 1 & 0 & 0 & 0 & 0 \\
+					& 0 & 0 & 1 & 0 & 0 & -1 & 0 & 0 & 0 & 1 & 0 \\
+					& 0 & 0 & 0 & 0 & 0 & 1 & 0 & -1 & 1 & -1 & 0 \\
+					& 0 & 0 & 0 & -1 & 1 & 0 & 0 & 0 & 0 & 1 & -1 \\
+					& 0 & -1 & 0 & 0 & 0 & 0 & 1 & 1 & -1 & 0 & 0
+\end{array}
+\]
 
@@
 %sage: Q.non_kissing_fan().rays()
-%N( 1,  0,  0),
-%N( 0,  0,  1),
-%N( 1,  0, -1),
-%N( 1, -1,  0),
-%N( 0,  0, -1),
-%N(-1,  0,  1),
-%N( 0, -1,  0),
-%N( 0, -1,  1),
-%N(-1,  0,  0),
-%N( 0,  1,  0),
-%N( 0,  1, -1)
+%N( 1,  0,  0),0
+%N( 0,  0,  1),1
+%N( 1,  0, -1),2
+%N( 1, -1,  0),3
+%N( 0,  0, -1),4
+%N(-1,  0,  1),5
+%N( 0, -1,  0),6
+%N( 0, -1,  1),7
+%N(-1,  0,  0),8
+%N( 0,  1,  0),9
+%N( 0,  1, -1)10
 %in 3-d lattice N
@@
 %A 11-dimensional polyhedron in QQ^11 defined as the convex hull of 1 vertex, 9 rays, 3 lines
+%sage: TCNKC.lines()
+%(A line in the direction (0, 0, 0, 1, 0, 0, 1, 1, 0, -1, -1),
+% A line in the direction (1, 0, 1, 1, 0, -1, 0, 0, -1, 0, 0),
+% A line in the direction (1, 1, 0, 1, -1, 0, 0, 1, -1, 0, -1))
 %sage: TCNKC.inequalities()
@@
 % An inequality (0, 0, 0, 0, 0, 1, 0, 0, -1, -1, 1) x + 0 >= 0)
-%sage: TCNKC.lines()
-%(A line in the direction (0, 0, 0, 1, 0, 0, 1, 1, 0, -1, -1),
-% A line in the direction (1, 0, 1, 1, 0, -1, 0, 0, -1, 0, 0),
-% A line in the direction (1, 1, 0, 1, -1, 0, 0, 1, -1, 0, -1))
 \vincent{Todo}

### 2019-04-01 thirdPaper/draft/typeConeAssociahedra.tex
more tables

@@
 \usetikzlibrary{trees, decorations, decorations.markings, shapes, arrows, matrix, calc, fit, intersections, patterns, angles}
-\graphicspath{{figures/}{figures/walks/}{figures/tubes}}
+\graphicspath{{figures/}{figures/walks/}{figures/tubes/}}
 \makeatletter\def\input@path{{figures/}}\makeatother
@@
 Consider the cluster fans illustrated in \cref{fig:clusterFans}.
-The type cone of the left one lives in~$\R^9$, has a linearity space of dimension~$3$ (a basis is given below) and $6$ facet defining inequalities (given below).
+The type cone of the left fan lives in~$\R^9$, has a linearity space of dimension~$3$ (a basis is given below) and $6$ facet defining inequalities (given below).
 
@@
  					& 0 & 1 & 0 & 0 & 0 & -1 & 1 & 0 & 0 \\
- 					& 0 & -1 & 0 & 1 & 0 & 1 & 0 & -1 & 0
+ 					& 0 & -1 & 0 & 1 & 0 & 1 & 0 & -1 & 0 \\[.2cm]
 \end{array}
@@
 
-\bigskip
 \noindent
-The type cone of the right one lives in~$\R^12$, has a linearity space of dimension~$3$ (a basis is given below) and $9$ facet defining inequalities (given below).
+The type cone of the right fan lives in~$\R^{12}$, has a linearity space of dimension~$3$ (a basis is given below) and $9$ facet defining inequalities (given below).
 
@@
 					& 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 1 & 0 & 0 & 0 \\
-					& 0 & 0 & 1 & -2 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0
+					& 0 & 0 & 1 & -2 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 \\[.2cm]
 \end{array}
@@
 % An inequality (0, 0, 0, 1, 1, 0, 0, -2, 0, 0, 0, 0) x + 0 >= 0)
-\vincent{todo}
 \end{example}
@@
 Consider the non-kissing fans illustrated in \cref{fig:nonkissingFans}.
-The type cone of the left one lives in~$\R^9$, has a linearity space of dimension~$3$ (a basis is given below) and $6$ facet defining inequalities (given below).
+The type cone of the left fan lives in~$\R^9$, has a linearity space of dimension~$3$ (a basis is given below) and $6$ facet defining inequalities (given below).
 
@@
 					& 0 & 0 & 0 & 1 & 0 & 1 & -1 & 0 \\
-					& 0 & 1 & 0 & 0 & -1 & 0 & 0 & 1
+					& 0 & 1 & 0 & 0 & -1 & 0 & 0 & 1 \\[.2cm]
 \end{array}
@@
 
-\bigskip
 \noindent
-The type cone of the right one lives in~$\R^11$, has a linearity space of dimension~$3$ (a basis is given below) and $9$ facet defining inequalities (given below). In particular, it is not simplicial.
+The type cone of the right fan lives in~$\R^{11}$, has a linearity space of dimension~$3$ (a basis is given below) and $9$ facet defining inequalities (given below).
+In particular, it is not simplicial.
 
@@
 					& 0 & 0 & 0 & -1 & 1 & 0 & 0 & 0 & 0 & 1 & -1 \\
-					& 0 & -1 & 0 & 0 & 0 & 0 & 1 & 1 & -1 & 0 & 0
+					& 0 & -1 & 0 & 0 & 0 & 0 & 1 & 1 & -1 & 0 & 0 \\[.2cm]
 \end{array}
@@
 % An inequality (0, 0, 0, 0, 0, 1, 0, 0, -1, -1, 1) x + 0 >= 0)
-\vincent{Todo}
 \end{example}
@@
 \label{exm:typeConeGA}
+Consider the nested fans illustrated in \cref{fig:nestedFans}.
+The type cone of the left fan lives in~$\R^{13}$, has a linearity space of dimension~$3$ (a basis is given below) and $6$ facet defining inequalities (given below).
+In particular, it is not simplicial.
+
+\[
+\begin{array}{r|c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c}
+\text{walks} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA1}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA2}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA3}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA4}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA5}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA6}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA7}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA8}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA9}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA10}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA11}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA12}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA13}}  \\[.6cm]
+\text{$\b{g}$-vectors} & \\ %\compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{1}{0}{-1} & \compactVector{0}{-1}{1} & \compactVector{0}{1}{-1} & \compactVector{-1}{0}{1} & \compactVector{-1}{0}{0} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} \\[.6cm]
+\text{lines}		& 
+					& \\[.2cm]
+\text{inequalities} & \\[.2cm]
+\end{array}
+\]
+
+\noindent
+The type cone of the right fan lives in~$\R^{11}$, has a linearity space of dimension~$3$ (a basis is given below) and $9$ facet defining inequalities (given below).
+In particular, it is not simplicial.
+
+\[
+\begin{array}{r|c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c}
+\text{walks} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB1}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA2}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB3}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB4}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB5}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB6}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB7}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB8}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB9}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB10}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB11}} \\[.6cm]
+\text{$\b{g}$-vectors} & \\ %\compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{1}{0}{-1} & \compactVector{0}{-1}{1} & \compactVector{0}{1}{-1} & \compactVector{-1}{0}{1} & \compactVector{-1}{0}{0} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} \\[.6cm]
+\text{lines}		& 
+					& \\[.2cm]
+\text{inequalities} & \\[.2cm]
+\end{array}
+\]
+
 \vincent{Todo}

### 2019-04-02 thirdPaper/draft/typeConeAssociahedra.tex

@@
 
-\begin{corollary}
+\begin{corollary}\label{corollary::meshes positively generate cluster cats}
  Assume that~$\ind(\cat)$ is finite.
@@
 
-\begin{proof}[Proof of Theorem~\ref{theorem::extricats}]\yann{PG: Est-ce que cela te semble suffisant, ou veux-tu que j'ajoute des d\'etails ? }
+\begin{proof}[Proof of Theorem~\ref{theorem::extricats}]
  The proof is now similar to the proof of Theorem~\ref{theo::relations-g-vecteurs}, by using Proposition~\ref{prop::KRextricat} instead of Proposition~\ref{prop::functor-F}, Proposition~\ref{prop::index iso extricat} instead of Corollary~\ref{coro::grothendieck-g-vectors}, and the fact that~$\tc$ is made of projective objects instead of Lemma~\ref{lemm::almost-split}.
@@
 \begin{proof}[Proof of Corollary~\ref{corollary::meshes positively generate extricats}]
-\yann{TO DO}
+The proof is similar to that of Corollary~\ref{corollary::meshes positively generate cluster cats}.
 \end{proof}
@@
 
-\begin{corollary}
- Generalised cluster categories with infinite dimensional Hom-spaces ?
-\end{corollary}
+% \begin{corollary}
+%  Generalised cluster categories with infinite dimensional Hom-spaces ?
+% \end{corollary}
 

### 2019-04-02 thirdPaper/draft/typeConeAssociahedra.tex
2CY triangulated

@@
 
-\subsection{Statement of the theorem}
+\subsection{Statement of the theorem}\label{subsect::Statement cluster cats}
 We need to introduce some notations before stating the main result of this section.  Let~$\Lambda\eqdef \End{\cat}(T)$, and let~$F$ be the functor
@@
 
+Let~$\cat$ be a triangulated category with shift functor~$\susp$.
+We assume moreover that~$\cat$ is~$\field$-linear, Krull--Schmidt, Hom-finite, 2-Calabi--Yau, with a cluster-tilting object~$T$.
+Then~$\cat$ satisfies all the assumptions of Setting~\ref{setting::extricat} for Section~\ref{sect::Statment extricats} but assumption (1).
+
+We fix this issue by considering a relative extriangulated structure.
+Let~$\mathbb{E}_T$ be the additive sub-bifunctor of~$\cat(-,\susp -)$ formed by those morphisms that factor through~$\add\susp T$.
+Then~$(\cat,\mathbb{E}_T)$ becomes extriangulated by~\cite[Proposition 3.14]{HerschendLiuNakaoka} (this can also be checked directly).
+The extriangles of~$\cat$ are precisely the triangles~$X\overset{f}{\rightarrow}Y\overset{g}{\rightarrow} Z \overset{h}{\dashrightarrow}$, for which the morphism~$h$ factors through~$\add\susp T$.
+By construction, Condition (1) is now satisfied.
+Moreover, the triangles appearing in Conditions (2) and (3) are extriangles for this relative structure, which shows that those two conditions are still satisfied for the extriangulated structure~$(\cat,\mathbb{E}_T)$.
+
+\begin{remark}
+The index of an object~$X$ in the triangulated category~$\cat$, coincide with its class in the Grothendieck group of~$\cat$ for the relative extriangulated structure given by~$\mathbb{E}_T$.
+\end{remark}
+
+\begin{remark}
+ The main results of Section~\ref{subsect::Statement cluster cats} can thus be viewed as specific cases of the results of Section~\ref{sect::extricats}: Theorem~\ref{theo::relations-g-vecteurs} and Corollary~\ref{corollary::meshes positively generate cluster cats} are consequences of Theorem~\ref{theorem::extricats} and Corollary~\ref{corollary::meshes positively generate extricats}.
+\end{remark}
+
 %%

### 2019-04-02 thirdPaper/draft/typeConeAssociahedra.tex
linearity space

@@
 We will prove however that it is independent of the seeds containing~$x$ and~$x'$.
+\vincent{Link to \cref{sec:clusterCategories}.}
 
@@
 \text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{-1}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{0}{1}{-1} & \compactVector{0}{0}{-1} & \compactVector{-1}{0}{0} & \compactVector{0}{-1}{0} \\[.6cm]
-\text{lines}		& 0 & 0 & 1 & 1 & 0 & -1 & -1 & 0 & 0 \\
-					& 0 & -1 & 0 & 0 & 1 & -1 & 0 & 0 & 1 \\
+\text{linearity}	& 0 & 0 & 1 & 1 & 0 & -1 & -1 & 0 & 0 \\
+\text{space}		& 0 & -1 & 0 & 0 & 1 & -1 & 0 & 0 & 1 \\
 					& 1 & 1 & 0 & -1 & 0 & 1 & 0 & -1 & -1 \\[.2cm]
@@
 \text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{-1}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{0}{2}{-1} & \compactVector{0}{1}{-1} & \compactVector{-1}{1}{0} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} & \compactVector{-2}{0}{1} & \compactVector{-1}{0}{0}  \\[.6cm]
-\text{lines}		& 1 & 1 & 2 & 1 & 0 & 0 & -1 & 0 & -1 & -2 & 0 & -1 \\
-					& 0 & 1 & 0 & 0 & -1 & 2 & 1 & 1 & -1 & 0 & 0 & 0 \\
+\text{linearity}	& 1 & 1 & 2 & 1 & 0 & 0 & -1 & 0 & -1 & -2 & 0 & -1 \\
+\text{space}		& 0 & 1 & 0 & 0 & -1 & 2 & 1 & 1 & -1 & 0 & 0 & 0 \\
 					& 0 & 0 & -1 & -1 & 0 & 1 & 1 & 0 & 0 & 1 & -1 & 0 \\[.2cm]
@@
 \begin{definition}
-Consider a seed~$(\B, \cluster)$ and a cluster variable~$x \in \cluster$.
-The mutation of~$\seed$ in direction~$x$ is a \defn{mesh mutation} if the entries~$b_{xy}$ for~$y \in \cluster$ are all non-negative, or all non-positive.
+%Consider a seed~$\seed = (\B, \cluster)$ and a cluster variable~$x \in \cluster$.
+The mutation of a seed~$\seed = (\B, \cluster)$ in the direction of a cluster variable~$x \in \cluster$ is a \defn{mesh mutation} that \defn{starts} (resp.~\defn{ends}) at~$x$ if the entries~$b_{xy}$ for~$y \in \cluster$ are all non-negative (resp.~all non-positive).
+A mesh mutation is \defn{initial} if it starts at a cluster variable of an initial seed.
 \end{definition}
 
-For instance, in the initial seed~$(\B_\circ, \cluster_\circ)$, the mutation in the direction of any variable~${x_\circ \in \cluster_\circ}$ is a mesh.
-We call these meshes \defn{initial}.
-We denote by~$\meshes$ the set of all pairs~$(x,x')$ where~$x$ and~$x'$ are two non-initial cluster variables of~$\principalClusterAlgebra$ which are exchangeable via a mesh mutation.
-The following statement describes the other meshes.
+We denote by~$\meshes$ the set of all pairs~$(x,x')$ where~$x$ and~$x'$ are two cluster variables of~$\principalClusterAlgebra$ which are exchangeable via a non-initial mesh mutation.
 
@@
 \label{lem:dependenceMesh}
-Consider two adjacent seeds~${(\B, \cluster)}$ and~${(\B', \cluster')}$ with~$\cluster \ssm \{x\} = \cluster' \ssm \{x'\}$ such that the entries~$b_{xy}$ for~$y \in \cluster$ are all non-positive or all non-negative.
-If either~$x$ or~$x'$ is an initial cluster variable, then
+Consider two adjacent seeds~${(\B, \cluster)}$ and~${(\B', \cluster')}$ with~$\cluster \ssm \{x\} = \cluster' \ssm \{x'\}$ connected by a mesh mutation.
+If the mesh mutation is initial, then
 \[
@@
 \text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{0}{1}{-1} & \compactVector{-1}{0}{0} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} \\[.6cm]
-\text{lines}		& 0 & -1 & 0 & 1 & -1 & 0 & 1 & 0 \\
-					& 1 & 1 & 0 & 0 & 1 & -1 & -1 & 0 \\
+\text{linearity}	& 0 & -1 & 0 & 1 & -1 & 0 & 1 & 0 \\
+\text{space}		& 1 & 1 & 0 & 0 & 1 & -1 & -1 & 0 \\
 					& 0 & 0 & 1 & 0 & -1 & 0 & 0 & -1 \\[.2cm]
@@
 \text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{1}{0}{-1} & \compactVector{0}{-1}{1} & \compactVector{0}{1}{-1} & \compactVector{-1}{0}{1} & \compactVector{-1}{0}{0} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} \\[.6cm]
-\text{lines}		& 0 & -1 & 0 & 1 & 0 & 1 & -1 & 0 & 0 & 1 & 0 \\
-					& 1 & 0 & 0 & 1 & 1 & 0 & 0 & -1 & -1 & 0 & 0 \\
+\text{linearity}	& 0 & -1 & 0 & 1 & 0 & 1 & -1 & 0 & 0 & 1 & 0 \\
+\text{space}		& 1 & 0 & 0 & 1 & 1 & 0 & 0 & -1 & -1 & 0 & 0 \\
 					& 1 & 0 & 1 & 1 & 0 & 1 & -1 & 0 & -1 & 0 & -1 \\[.2cm]
@@
 \text{$\b{g}$-vectors} & \\ %\compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{1}{0}{-1} & \compactVector{0}{-1}{1} & \compactVector{0}{1}{-1} & \compactVector{-1}{0}{1} & \compactVector{-1}{0}{0} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} \\[.6cm]
-\text{lines}		& 
-					& \\[.2cm]
+\text{linearity}	& 
+\text{space}		& \\[.2cm]
 \text{inequalities} & \\[.2cm]
@@
 \section{Relations for~$\b{g}$-vectors in finite type cluster algebras via~$2$-Calabi--Yau triangulated categories}
+\label{sec:clusterCategories}
 

### 2019-04-02 thirdPaper/draft/typeConeAssociahedra.tex
mesh mutations

@@
 
-\subsection{Statement of the theorem}\label{subsect::Statement cluster cats}
+\subsection{Statement of the theorem}
 We need to introduce some notations before stating the main result of this section.  Let~$\Lambda\eqdef \End{\cat}(T)$, and let~$F$ be the functor
@@
 
-Let~$\cat$ be a triangulated category with shift functor~$\susp$.
-We assume moreover that~$\cat$ is~$\field$-linear, Krull--Schmidt, Hom-finite, 2-Calabi--Yau, with a cluster-tilting object~$T$.
-Then~$\cat$ satisfies all the assumptions of Setting~\ref{setting::extricat} for Section~\ref{sect::Statment extricats} but assumption (1).
-
-We fix this issue by considering a relative extriangulated structure.
-Let~$\mathbb{E}_T$ be the additive sub-bifunctor of~$\cat(-,\susp -)$ formed by those morphisms that factor through~$\add\susp T$.
-Then~$(\cat,\mathbb{E}_T)$ becomes extriangulated by~\cite[Proposition 3.14]{HerschendLiuNakaoka} (this can also be checked directly).
-The extriangles of~$\cat$ are precisely the triangles~$X\overset{f}{\rightarrow}Y\overset{g}{\rightarrow} Z \overset{h}{\dashrightarrow}$, for which the morphism~$h$ factors through~$\add\susp T$.
-By construction, Condition (1) is now satisfied.
-Moreover, the triangles appearing in Conditions (2) and (3) are extriangles for this relative structure, which shows that those two conditions are still satisfied for the extriangulated structure~$(\cat,\mathbb{E}_T)$.
-
-\begin{remark}
-The index of an object~$X$ in the triangulated category~$\cat$, coincide with its class in the Grothendieck group of~$\cat$ for the relative extriangulated structure given by~$\mathbb{E}_T$.
-\end{remark}
-
-\begin{remark}
- The main results of Section~\ref{subsect::Statement cluster cats} can thus be viewed as specific cases of the results of Section~\ref{sect::extricats}: Theorem~\ref{theo::relations-g-vecteurs} and Corollary~\ref{corollary::meshes positively generate cluster cats} are consequences of Theorem~\ref{theorem::extricats} and Corollary~\ref{corollary::meshes positively generate extricats}.
-\end{remark}
-
 %%

### 2019-04-02 thirdPaper/draft/typeConeAssociahedra.tex
mesh mutations

@@
 \(
-\cvector{\seed}{x} = \cvectorFull{\B_\circ}{\seed}{x} \eqdef \sum_{y \in \cluster_\circ} c_{yx} \, \simpleRoot_y
+{\cvector{\seed}{x} = \cvectorFull{\B_\circ}{\seed}{x} \eqdef \sum_{y \in \cluster_\circ} c_{yx} \, \simpleRoot_y}
 \)
 of exponents of~$p_x = \prod_{y \in \cluster_\circ} (p_y)^{c_{yx}}$.
-We denote by~$\cvectors{\seed} = \cvectorsFull{\B_\circ}{\seed} \eqdef \set{\cvectorFull{\B_\circ}{\seed}{x}}{x \in \seed}$ the set of $\b{c}$-vectors of a seed~$\seed$.
+We denote by ${\cvectors{\seed} = \cvectorsFull{\B_\circ}{\seed} \eqdef \set{\cvectorFull{\B_\circ}{\seed}{x}}{x \in \seed}}$ the set of $\b{c}$-vectors of a seed~$\seed$.
 \end{definition}
@@
 A mesh mutation is \defn{initial} if it starts at a cluster variable of an initial seed.
+We denote by~$\meshes$ the set of all pairs~$(x,x')$ where~$x$ and~$x'$ are two cluster variables of~$\principalClusterAlgebra$ which are exchangeable via a non-initial mesh mutation.
 \end{definition}
-
-We denote by~$\meshes$ the set of all pairs~$(x,x')$ where~$x$ and~$x'$ are two cluster variables of~$\principalClusterAlgebra$ which are exchangeable via a non-initial mesh mutation.
 
@@
 \label{lem:bijectionMeshMutations}
-There is precisely one non-initial mesh directed by each positive $\b{c}$-vector of the cluster algebra~$\principalClusterAlgebra$. Therefore~$|\principalVariables| = |\meshes| + n$.
+There is precisely one non-initial mesh directed by each positive $\b{c}$-vector of the cluster algebra~$\principalClusterAlgebra[\B_\circ^\vee]$. Therefore~$|\principalVariables| = |\meshes| + n$.
 \end{lemma}
@@
 
-Our main result states that the linear dependences between the $\b{g}$-vectors of any mutation can be decomposed into positive combinations of linear dependences arising from meshes.
+The following will be shown in \cref{sec:clusterCategories}.
 
 \begin{proposition}
-\label{prop:extremalExchangeablePairsCA}
-For any finite type exchange matrix~$\B_\circ$ (acyclic or not), the non-initial mesh mutations precisely correspond to the extremal exchangeable pairs of the cluster fan~$\gvectorFan[\B_\circ]$.
+\label{prop:meshMutations}
+For any finite type exchange matrix~$\B_\circ$ (acyclic or not, simply-laced or not), the linear dependence between the $\b{g}$-vectors of any mutation can be decomposed into positive combinations of linear dependences between $\b{g}$-vectors of non-initial mesh mutations.
 \end{proposition}
 
-This statement will be proved in full generality in \cref{???}.
-We proved it in \cref{prop:extremalExchangeablePairsAsso} for acyclic initial seeds in type~$A$. To provide an intuition of the result, we sketch here a proof for arbitrary initial seeds in type~$A$.
-
-\begin{proof}[Sketch of \cref{prop:extremalExchangeablePairsCA} in type~$A$]
-We need to prove that the normal vector~$\b{n}(\B_\circ, y, y')$ for any exchangeable pair~$\{y,y'\}$ is a positive linear combination of the vectors~$\b{n}(\B_\circ, x, x')$ for non-initial meshes.
-\vincent{Do we really want to do that?}
-\end{proof}
-
-Our next statement follows from~\cref{prop:extremalExchangeablePairsCA,lem:bijectionMeshMutations}.
+We derive from \cref{prop:meshMutations} the following description of the facets of the type cone of the $\b{g}$-vector fan.
+
+\begin{theorem}
+\label{thm:extremalExchangeablePairsCA}
+For any finite type exchange matrix~$\B_\circ$ (acyclic or not, simply-laced or not), the non-initial mesh mutations precisely correspond to the extremal exchangeable pairs of the cluster fan~$\gvectorFan[\B_\circ]$.
+\end{theorem}
+
+\begin{proof}
+\end{proof}
+
+%This statement will be proved in full generality in \cref{???}.
+%We proved it in \cref{prop:extremalExchangeablePairsAsso} for acyclic initial seeds in type~$A$. To provide an intuition of the result, we sketch here a proof for arbitrary initial seeds in type~$A$.
+%
+%\begin{proof}[Sketch of \cref{thm:extremalExchangeablePairsCA} in type~$A$]
+%We need to prove that the normal vector~$\b{n}(\B_\circ, y, y')$ for any exchangeable pair~$\{y,y'\}$ is a positive linear combination of the vectors~$\b{n}(\B_\circ, x, x')$ for non-initial meshes.
+%\vincent{Do we really want to do that?}
+%\end{proof}
+
+We also obtain from \cref{thm:extremalExchangeablePairsCA} the following surprising property.
+
+\begin{corollary}
+Any $\b{c}$-vector supports exactly one extremal exchangeable pair.
+\end{corollary}
+
+Our next statement follows from~\cref{thm:extremalExchangeablePairsCA,lem:bijectionMeshMutations}.
 
@@
 
-Combining \cref{coro:simplicialTypeCone,coro:simplicialTypeConeCA,prop:extremalExchangeablePairsCA}, we derive the following description of all polytopal realizations of the cluster fan~$\gvectorFan[\B_\circ]$.
+Combining \cref{coro:simplicialTypeCone,coro:simplicialTypeConeCA,thm:extremalExchangeablePairsCA}, we derive the following description of all polytopal realizations of the cluster fan~$\gvectorFan[\B_\circ]$.
 This result was stated in~\cite{BazierMatteDouvilleMousavandThomasYildirim} in the special situation of acyclic seeds in simply-laced types.

### 2019-04-02 thirdPaper/draft/typeConeAssociahedra.tex
added notes on Minkowski sums

--- 2019-04-02 thirdPaper/draft/typeConeAssociahedra.tex
@@
 \usetikzlibrary{trees, decorations, decorations.markings, shapes, arrows, matrix, calc, fit, intersections, patterns, angles}
-\graphicspath{{figures/}{figures/walks/}{figures/tubes/}}
+\graphicspath{{figures/}}
 \makeatletter\def\input@path{{figures/}}\makeatother
@@
 \newcommand*\circled[1]{\tikz[baseline=(char.base)]{\node[shape=circle,draw,inner sep=1pt, scale=.7] (char) {#1};}}
-\newcommand{\compactVector}[3]{\begin{bmatrix} #1 \\[-.1cm] #2 \\[-.1cm] #3 \end{bmatrix}}
 
@@
 
-% Type cone
-\newcommand{\typeCone}{\mathbb{TC}} % type cone
+% Type-cone
+\newcommand{\typeCone}{\mathbb{TC}} % type-cone
+\newcommand{\ctypeCone}{\overline{\mathbb{TC}}} % type-cone
 \newcommand{\compatibilityDegree}[2]{(#1\,\|\,#2)} % compatibility degree
@@
 
-\title{Type cones of $\b{g}$-vector fans}
+\title{Type-cones of $\b{g}$-vector fans}
 
@@
 \begin{abstract}
-We investigate the type cone of the $\b{g}$-vector fans for different generalizations of the associahedron (hopefully generalized associahedra, gentle associahedra, graph associahedra, and maybe quotientopes and brick polytopes).
-The objective is to determine which are the exchangeable pairs of objects that describe the type cone.
-When the type cone happens to be simplicial, we derive simple descriptions of all polytopal realizations of the $\b{g}$-vector fan.
+We investigate the type-cone of the $\b{g}$-vector fans for different generalizations of the associahedron (hopefully generalized associahedra, gentle associahedra, graph associahedra, and maybe quotientopes and brick polytopes).
+The objective is to determine which are the exchangeable pairs of objects that describe the type-cone.
+When the type-cone happens to be simplicial, we derive simple descriptions of all polytopal realizations of the $\b{g}$-vector fan.
 \end{abstract}
@@
 
-\section{Polytopal realizations and type cone of a simplicial fan}
+\section{Polytopal realizations and type-cone of a simplicial fan}
 
@@
 The $1$-dimensional (resp.~codimension~$1$) faces of~$C$ are called~\defn{rays} (resp.~\defn{facets}) of~$C$.
-A cone is \defn{simplicial} if it is generated by a set of independent vectors.
+A cone is \defn{simplicial} if it is generated by a set of linearly independent vectors.
 
@@
 
-\subsection{Type cone}
+\subsection{Type-cone}
 
@@
 \label{prop:characterizationPolytopalFan}
-Then the following are equivalent for any height vector~$h \in \R^N$:
+Let~$\Fan$ be an essential complete simplicial fan in~$\R^n$. Then the following are equivalent for any height vector~$h \in \R^N$:
 \begin{enumerate}
@@
 
-In this paper, we are interested in the set of all possible realizations of~$\Fan$. This was studied by P.~McMullen in~\cite{McMullen-typeCone}.
-
-\begin{definition}
-The \defn{type cone} of~$\Fan$ is the cone~$\typeCone(\Fan)$ of all $\Fan$-admissible height vectors~$\b{h}$:
+In this paper, we are interested in the set of all possible realizations of~$\Fan$ as the normal fan of a polytope~$P_\b{h}$.
+This was studied by P.~McMullen in~\cite{McMullen-typeCone} (see~\cite[Sect.~9.5]{DeLoeraRambauSantos} for a formulation in terms of chambers of triangulations of vector configurations).
+
+\begin{definition}\label{def:typecone}
+The \defn{type-cone} of~$\Fan$ is the cone~$\typeCone(\Fan)$ of all $\Fan$-admissible height vectors~$\b{h}$:
 \begin{align*}
@@
 
-Note that the type cone is an open cone and contains a linearity subspace of dimension~$n$ (it is invariant by translation in~$\b{G} \R^n$).
+Note that the type-cone is an open cone and contains a linearity subspace of dimension~$n$ (it is invariant by translation in~$\b{G} \R^n$).
 We could thus intersect~$\typeCone(\Fan)$ by the kernel of~$\b{G}$, or consider the projection~$\b{K}\typeCone(\Fan)$.
 
+We denote by $\ctypeCone(\Fan)$ the closure of $\typeCone(\Fan)$.
+It is a closed polyhedral cone defined by the inequalities $\sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} \geq 0$ for adjacent maximal cones~$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$.
+
+\begin{remark}
+ \label{rmk:non-simplicial}
+Although we will only treat with simplicial fans, for completeness, note that \cref{prop:characterizationPolytopalFan} and \cref{def:typecone} can be easily adapted to non-simplicial fans.
+If~$\Fan$ is an arbitrary essential complete fan, it suffices to consider consider any simplicial refinement~$\Fan'$, and set some of the strict inequalities of the definition of $\typeCone(\Fan')$ to equality.
+Specifically, for any adjacent maximal cones~$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$ of~$\Fan'$ we impose
+\[
+ \sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} {\left\{\begin{array}{l} =\\ >\end{array}\right\}} 0
+\]
+with `$>$' when $\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$ do not belong to the same maximal cone of $\Fan$; and with `$=$' if $\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$ belong to the same maximal cone of $\Fan$.
+\end{remark}
+
 \begin{definition}
-An \defn{extremal adjacent pair} of~$\Fan$ is a pair of adjacent maximal cones~$\{\R_{\ge0}\rays, \R_{\ge0}\rays'\}$ of~$\Fan$ such that the corresponding inequality $\sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} > 0$ in the definition of the type cone~$\typeCone(\Fan)$ actually defines a facet of~$\typeCone(\Fan)$.
+An \defn{extremal adjacent pair} of~$\Fan$ is a pair of adjacent maximal cones~$\{\R_{\ge0}\rays, \R_{\ge0}\rays'\}$ of~$\Fan$ such that the corresponding inequality $\sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} \geq 0$ in the definition of the type-cone~$\ctypeCone(\Fan)$ actually defines a facet of~$\ctypeCone(\Fan)$.
 \end{definition}
-
-In other words, extremal adjacent pairs define the extremal rays of the polar of the type cone~$\typeCone(\Fan)$.
-Understanding the extremal adjacent pairs of~$\Fan$ enables to describe its type cone~$\typeCone(\Fan)$ and thus all its polytopal realizations.
+\arnau{I changed open to closed here}
+
+In other words, extremal adjacent pairs define the extremal rays of the polar of the closed type-cone~$\ctypeCone(\Fan)$.
+Understanding the extremal adjacent pairs of~$\Fan$ enables to describe its type-cone~$\typeCone(\Fan)$ and thus all its polytopal realizations.
 
@@
 \label{rem:dimTypeCone}
-Since the type cone is an open~$N$ dimensional cone with a linearity subspace of dimension~$n$, it has at least~$N-n$ facets.
-We say that the type cone is \defn{simplicial} when it has precisely $N-n$ facets.
+Since the type-cone is an $N$ dimensional cone with a linearity subspace of dimension~$n$, it has at least~$N-n$ facets.
+We say that the type-cone is \defn{simplicial} when it has precisely $N-n$ facets.
 \end{remark}
@@
 These rays are thus called \defn{forced rays} for the exchangeable pair~$\{\ray, \ray'\}$.
-
-We say that the fan~$\Fan$ has the \defn{unique exchange property} if any two exchangeable rays~$\ray, \ray'$ of~$\Fan$ admit a unique exchange relation
+\arnau{Remove definition of forced rays. Not used anywhere.}
+
+We say that the fan~$\Fan$ has the \defn{unique exchange property} if any two exchangeable rays~$\ray, \ray'$ of~$\Fan$ admit a unique exchange relation.
 \end{definition}
 
-When~$\Fan$ has the unique exchange relation property, we change the notation~$\coefficient[{\ray[s]}][\rays][\rays']$ to~$\coefficient$ and we obtain that the type cone of~$\Fan$ is expressed as
+When~$\Fan$ has the unique exchange relation property, we change the notation~$\coefficient[{\ray[s]}][\rays][\rays']$ to~$\coefficient$ and we obtain that the type-cone of~$\Fan$ is expressed as
 \[
@@
 
+\arnau{Do we have a notation for the set of all rays? I would change the sum over ${\ray[s] \in \rays \cup \rays'}$ to the whole ground set.}
 \begin{definition}
-In a fan~$\Fan$ with the unique exchange relation property, an \defn{extremal exchangeable pair} is a pair of exchangeable rays~$\{\ray,\ray'\}$ such that the corresponding inequality~${\sum_{\ray[s] \in \rays \cup \rays'} \coefficient \, \b{h}_{\ray[s]} > 0}$ defines a facet of the type cone~$\typeCone(\Fan)$.
+In a fan~$\Fan$ with the unique exchange relation property, an \defn{extremal exchangeable pair} is a pair of exchangeable rays~$\{\ray,\ray'\}$ such that the corresponding inequality~${\sum_{\ray[s] \in \rays \cup \rays'} \coefficient \, \b{h}_{\ray[s]} \geq  0}$ defines a facet of the closed type-cone~$\ctypeCone(\Fan)$.
 \end{definition}
+\arnau{I changed open to closed here}
 
@@
 In this section, we provide alternative polytopal realizations of the fan~$\Fan$.
-We also discuss the behavior of these realizations in the situation when the type cone~$\typeCone(\Fan)$ is simplicial.
+We also discuss the behavior of these realizations in the situation when the type-cone~$\typeCone(\Fan)$ is simplicial.
 
@@
 \label{coro:simplicialTypeCone}
-Assume that the type cone~$\typeCone(\Fan)$ is simplicial and let~$\b{K}$ be the $(N-n) \times N$-matrix whose rows are the outer normal vectors of the facets of~$\typeCone(\Fan)$. Then the polytope
+Assume that the type-cone~$\typeCone(\Fan)$ is simplicial and let~$\b{K}$ be the $(N-n) \times N$-matrix whose rows are the outer normal vectors of the facets of~$\typeCone(\Fan)$. Then the polytope
 \[
@@
 Since~$\b{K}$ has full rank there exists~$\b{h} \in \R^N$ such that~$\b{K}\b{h} = \b{\ell}$.
-Since~$\b{K}\b{h} \ge 0$ and the rows of~$\b{K}$ are precisely all outer normal vectors of the facets of the type cone~$\typeCone(\Fan)$, we obtain that~$\b{h}$ belongs to~$\typeCone(\Fan)$.
+Since~$\b{K}\b{h} \ge 0$ and the rows of~$\b{K}$ are precisely all outer normal vectors of the facets of the type-cone~$\typeCone(\Fan)$, we obtain that~$\b{h}$ belongs to~$\typeCone(\Fan)$.
 Since $R_\b{\ell} = Q_\b{h} \sim P_\b{h}$ by \cref{prop:alternativePolytopalRealization}, we conclude that~$R_\b{\ell}$ is a polytopal realization of~$\Fan$.
@@
 
-\subsection{Faces of the type cone and Minkowski sums}
+\subsection{Faces of the type-cone and Minkowski sums}
+Recall that the \defn{Minkowski sum} of two polytopes $P$ and $Q$ is the polytope $P+Q=\set{p+q}{p\in P\text{ and } q\in Q}$.
 
@@
 
-\cref{lem:MinkowskiSum} ensures that convex combinations in the type cone correspond to Minkowski combinations of polytopes.
-This provides natural Minkowski summands for all polytopal realizations of~$\Fan$.
+We say that~$P$ is a \defn{Minkowski summand} of~$R$ if there is a polytope~$Q$ such that $R=P+Q$, and a \defn{weak Minkowski summand} if there is a $\lambda\geq 0$ and a polytope~$Q$ such that $\lambda R=P+Q$.
+\cref{lem:MinkowskiSum} ensures that convex combinations in the type-cone correspond to Minkowski combinations of polytopes.
+Actually, the set of weak Minkowski summands of a polytope $P$ with normal fan~$\Fan$ is isomorphic to the closed type-cone~$\ctypeCone(\Fan)$ modulo linearity (the cone of weak Minkowski summands is studied by Meyer in~\cite{Meyer1974}, to see that it is equivalent to the type-cone and other formulations, see for example the appendix of~\cite{PostnikovReinerWilliams}).
+
+This provides natural Minkowski summands for all polytopal realizations of~$\Fan$: the rays of the type-cone.
+These correspond to indecomposable polytopes~(cf.~\cite{Meyer1974} or \cite{McMullen-typeCone}).
+A polytope $P$ in $\R^n$ is
+  called \defn{indecomposable} if all its weak Minkowski summands are of the form $\lambda P+t$ for some $\lambda\geq 0$ and $t\in\R^n$.
 
 \begin{corollary}
-Any polytope in~$\typeCone(\Fan)$ is the Minkowski sum of at most~$N-n$ polytopes corresponding to the rays of~$\b{K}\typeCone(\Fan)$.
+\arnau{See \cite{Meyer1974} and \cite{McMullen-typeCone}}
+Any polytope in~$\typeCone(\Fan)$ is the Minkowski sum of at most~$N-n$ indecomposable polytopes corresponding to the rays of~$\b{K}\typeCone(\Fan)$.
 \end{corollary}
+
+If $P=Q+R$, then we say that $R$ is the \defn{Minkowski difference} of $P$ and $Q$, which we denote by $R=P-Q$. We will only consider the case where $Q$ is a summand of $P$.
+There are two natural ways this construction generalizes to arbitrary pairs of polyhedra. On the one hand, we have $P-Q=\set{x\in\R^n}{x+Q\subseteq P}$. 
+Notice that $P_\b{h}-P_{\b{h}'}=P_{\b{h} - \b{h'}}$ when $P_{\b{h}'}$ is a Minkowski summand of $P_\b{h}$.
+Considering arbitrary differences of support functions gives rise to  \defn{virtual polyhedra}, which is the Grothendieck group of the semigroup of polytopes with Minkowski sums~\cite{PukhlikovKhovanskii1992}.
+
+\begin{corollary}
+Let $\b{h}_1,\dots, \b{h}_{N-n}\in \ctypeCone(\Fan)$ form a basis of $\ker \b{G}$.
+Then every $P_\b{h}$ with $\b{h}\in \ctypeCone(\Fan)$ has a unique representation (up to translation) as a signed Minkowski sum of dilates of $P_{\b{h}_1},\dots, P_{\b{h}_{N-n}}$.
+\end{corollary}
+\begin{proof}
+ It suffices to express the projection of $\b{h}$ into $\ker\b{G}$ in terms of $\b{h}_1,\dots, \b{h}_{N-n}$, and to separate those terms with positive and negative coefficients to express Minkowski sums and differences.
+\end{proof}
+
+This is used in~\cite{ArdilaBenedettiDoker} to show that every generalized permutahedron can be written uniquelyas a signed Minkowski sum of simplices. 
+\arnau{This has consequences in expressing volume and other valuations! I have to have a look at it.}
+In the particular case when the type-cone is simplicial, then we can get rid of the sums.
+\begin{corollary}
+ If the type-cone~$\typeCone(\Fan)$ of $\Fan$ is simplicial, then the $N-n$ idecomposable polytopes $P_{\b{h}_1},\dots, P_{\b{h}_{N-n}}$ arising from the rays of $\ctypeCone(\Fan)$
+ verify that 
+ \begin{enumerate}[(i)]
+  \item  every $P_\b{h}$ with $\b{h}\in \typeCone(\Fan)$ has a unique representation (up to translation) as a Minkowski sum of positive dilates of $P_{\b{h}_1},\dots, P_{\b{h}_{N-n}}$; and
+ \item  every $P_\b{h}$ with $\b{h}\in \ctypeCone(\Fan)$ has a unique representation (up to translation) as a Minkowski sum of dilates of $P_{\b{h}_1},\dots, P_{\b{h}_{N-n}}$.
+ \end{enumerate}
+
+\end{corollary}
+ Note that such a family of polytopes giving rise to unique positive representations only exists when the type-cone is simplicial.
+
+\arnau{By \cite{McMullen-Valuations} valuations on the polytope $\alpha_1P_{\b{h}_1}+\cdots+\alpha_{N-n}P_{\b{h}_{N-n}}$ (such as volume) are a polynomial on $\alpha_1\dots\alpha_{N-n}$ with coefficients the mixed volumes.
+This also works when the $\alpha$'s are not necessarily positive \cite{ArdilaBenedettiDoker}.
+Does this help in any way?}
 
@@
 
-In this section, we study the type cones of complete simplicial fans arising as normal fans of three families of generalizations of the associahedron: the generalized associahedra of finite type cluster algebras~\cite{FominZelevinsky-ClusterAlgebrasI, FominZelevinsky-ClusterAlgebrasII, FominZelevinsky-ClusterAlgebrasIV, HohlwegLangeThomas, HohlwegPilaudStella}, the gentle associahedra~\cite{PaluPilaudPlamondon-nonkissing}, and the graph associahedra~\cite{CarrDevadoss, Postnikov, FeichtnerSturmfels, Zelevinsky}.
+In this section, we study the type-cones of complete simplicial fans arising as normal fans of three families of generalizations of the associahedron: the generalized associahedra of finite type cluster algebras~\cite{FominZelevinsky-ClusterAlgebrasI, FominZelevinsky-ClusterAlgebrasII, FominZelevinsky-ClusterAlgebrasIV, HohlwegLangeThomas, HohlwegPilaudStella}, the gentle associahedra~\cite{PaluPilaudPlamondon-nonkissing}, and the graph associahedra~\cite{CarrDevadoss, Postnikov, FeichtnerSturmfels, Zelevinsky}.
 All these families contain the classical associahedra~$\Asso[n]$ constructed in~\cite{ShniderSternberg, Loday}.
@@
 
-We first describe the associahedra of~\cite{ShniderSternberg, Loday} and their type cones as they are the prototypes of our constructions.
+We first describe the associahedra of~\cite{ShniderSternberg, Loday} and their type-cones as they are the prototypes of our constructions.
 
@@
 
-\subsubsection{Type cones of associahedra}
-
-From the linear dependencies of \cref{prop:exchangeablePairsAsso}, we obtain a redundant description of the type cone of the fan~$\gvectorFan[n]$.
+\subsubsection{Type-cones of associahedra}
+
+From the linear dependencies of \cref{prop:exchangeablePairsAsso}, we obtain a redundant description of the type-cone of the fan~$\gvectorFan[n]$.
 
@@
 \label{coro:typeConeAsso}
-Let~$n \in \N$ and~$X(n) \eqdef \set{(a,b)}{0 \le a < b \le n+2}$. Then the type cone of the normal fan~$\gvectorFan[n]$ of~$\Asso[n]$ is given by
+Let~$n \in \N$ and~$X(n) \eqdef \set{(a,b)}{0 \le a < b \le n+2}$. Then the type-cone of the normal fan~$\gvectorFan[n]$ of~$\Asso[n]$ is given by
 \[
@@
 
-We now describe the facets of this type cone~$\typeCone(\gvectorFan[n])$.
+We now describe the facets of this type-cone~$\typeCone(\gvectorFan[n])$.
 
@@
 \]
-Therefore, the outer normal vector of the corresponding inequality of the type cone~$\typeCone(\gvectorFan[n])$ is
+Therefore, the outer normal vector of the corresponding inequality of the type-cone~$\typeCone(\gvectorFan[n])$ is
 \[
@@
 \label{coro:simplicialTypeConeAsso}
-The type cone~$\typeCone(\gvectorFan[n])$ is simplicial.
+The type-cone~$\typeCone(\gvectorFan[n])$ is simplicial.
 \end{corollary}
@@
 Here, we will focus on finite type cluster algebras~\cite{FominZelevinsky-ClusterAlgebrasII} and more specifically on properties of their $\b{g}$-vectors~\cite{FominZelevinsky-ClusterAlgebrasIV}.
-These $\b{g}$-vectors support a complete simplicial fan, which is called \defn{$\b{g}$-vector fan} or \defn{cluster fan}.
-It is known to be the normal fan of a polytope called generalized associahedron.
+These $\b{g}$-vectors support a complete simplicial fan, which is known to be the normal fan of a polytope called generalized associahedron.
 These polytopal realizations were first constructed for bipartite initial seeds by F.~Chapoton, S.~Fomin and A.~Zelevinsky~\cite{ChapotonFominZelevinsky} using the $\b{d}$-vector fans of~\cite{FominZelevinsky-YSystems}, then for acyclic initial seeds by C.~Hohlweg, C.~Lange and H.~Thomas~\cite{HohlwegLangeThomas} using Cambrian lattices and fans of N.~Reading and D.~Speyer~\cite{Reading-CambrianLattices, ReadingSpeyer}, and revisited by S.~Stella~\cite{Stella}, and by V.~Pilaud and C.~Stump~\cite{PilaudStump-brickPolytope} via brick polytopes, and finally for arbitrary initial seeds by C.~Hohlweg, V.~Pilaud and S.~Stella~\cite{HohlwegPilaudStella}.
 More recently in~\cite{BazierMatteDouvilleMousavandThomasYildirim}, V.~Bazier-Matte, G.~Douville, K.~Mousavand, H.~Thomas and E.~Yildirim extended the construction of associahedra of~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} to acyclic seeds of simply laced finite type cluster algebras.
-Here, we extend the construction of~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} to any finite type (simply laced or not) cluster algebra with respect to any seed (acyclic or not) by providing a direct proof that the type cone of the cluster fan of any finite type cluster algebra is simplicial.
-
-\subsubsection{Cluster algebras and cluster fans}
-
-We present some definitions and properties of finite type cluster algebras and their cluster fans, following the presentation of~\cite{HohlwegPilaudStella}.
+Here, we extend the construction of~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} to any finite type (simply laced or not) cluster algebra with respect to any seed (acyclic or not) by providing a direct proof that the type-cone of the $\b{g}$-vector fan of any finite type cluster algebra is simplicial.
+
+\subsubsection{Cluster algebras and $\b{g}$-vector fans}
+
+We present some definitions and properties of finite type cluster algebras and their $\b{g}$-vector fans, following the presentation of~\cite{HohlwegPilaudStella}.
 
@@
 
-\para{Cluster fan and generalized associahedron}
+\para{The $\b{g}$-vector fan and generalized associahedron}
 %
@@
 	}
-	\caption{Two cluster fans~$\gvectorFan[\B_\circ]$ for the type~$A_3$~(left) and type~$C_3$~(right) cyclic initial exchange matrices.
+	\caption{Two $\b{g}$-vector fans~$\gvectorFan[\B_\circ]$ for the type~$A_3$~(left) and type~$C_3$~(right) cyclic initial exchange matrices.
 As the fans are $3$-dimensional, we intersect them with the sphere and stereographically project them from the direction~$(-1,-1,-1)$.
@@
 } \\[.1cm]
-together with all their faces, forms a complete simplicial fan, called the \defn{$\b{g}$-vector fan} or \defn{cluster fan} of~$\B_\circ$.
+together with all their faces, forms a complete simplicial fan, called the \defn{$\b{g}$-vector fan} of~$\B_\circ$.
 \end{theorem}
@@
 \label{thm:generalizedAsso}
-For any finite type exchange matrix~$\B_\circ$, the cluster fan~$\gvectorFan[\B_\circ]$ is the normal fan of the \defn{$\B_\circ$-associahedron}~$\Asso[\B_\circ, \b{h}]$ defined equivalently as
+For any finite type exchange matrix~$\B_\circ$, the $\b{g}$-vector fan~$\gvectorFan[\B_\circ]$ is the normal fan of the \defn{$\B_\circ$-associahedron}~$\Asso[\B_\circ, \b{h}]$ defined equivalently as
 \begin{enumerate}[(i)]
@@
 
-\para{Mutations in the cluster fan}
+\para{Mutations in the $\b{g}$-vector fan}
 %
@@
 
-Note that \cref{lem:linearDependencegvectorsCA} implies \cref{thm:generalizedAsso} since it ensures that the type cone~$\typeCone(\gvectorFan[\B_\circ])$ of the cluster fan contains the cone of~${\b{h} \in \R^{\principalVariables}}$ such that
+Note that \cref{lem:linearDependencegvectorsCA} implies \cref{thm:generalizedAsso} since it ensures that the type-cone~$\typeCone(\gvectorFan[\B_\circ])$ of the $\b{g}$-vector fan contains the cone of~${\b{h} \in \R^{\principalVariables}}$ such that
 \(
@@
 We will prove however that it is independent of the seeds containing~$x$ and~$x'$.
-\vincent{Link to \cref{sec:clusterCategories}.}
 
@@
 \label{prop:uniqueExchangePropertyCA}
-For any finite type exchange matrix~$\B_\circ$, the cluster fan has the unique exchange relation property.
+For any finite type exchange matrix~$\B_\circ$, the $\b{g}$-vector fan has the unique exchange relation property.
 \end{proposition}
 
-\subsubsection{Type cone of finite type cluster fans}
-
-The linear dependences of \cref{lem:linearDependencegvectorsCA} provide a redundant description of the type cone of the cluster fan~$\gvectorFan[\B_\circ]$.
-We denote by~$\b{n}(\B_\circ, x, x')$ the normal vector of the inequality of the type cone corresponding to two exchangeable cluster variable~$x$ to~$x'$ (it is well defined by \cref{prop:uniqueExchangePropertyCA}).
+\subsubsection{Type-cone of finite type $\b{g}$-vector fans}
+
+The linear dependences of \cref{lem:linearDependencegvectorsCA} provide a redundant description of the type-cone of the $\b{g}$-vector fan~$\gvectorFan[\B_\circ]$.
+We denote by~$\b{n}(\B_\circ, x, x')$ the normal vector of the inequality of the type-cone corresponding to two exchangeable cluster variable~$x$ to~$x'$ (it is well defined by \cref{prop:uniqueExchangePropertyCA}).
 In other words, depending on which of the two linear dependences of \cref{lem:linearDependencegvectorsCA} holds, we have
@@
 \label{coro:typeConeCA}
-For any finite type exchange matrix~$\B_\circ$, the type cone of the cluster fan~$\gvectorFan[\B_\circ]$ is given by
+For any finite type exchange matrix~$\B_\circ$, the type-cone of the $\b{g}$-vector fan~$\gvectorFan[\B_\circ]$ is given by
 \[
@@
 \begin{example}
-Consider the cluster fans illustrated in \cref{fig:clusterFans}.
-The type cone of the left fan lives in~$\R^9$, has a linearity space of dimension~$3$ (a basis is given below) and $6$ facet defining inequalities (given below).
-
-\[
-\begin{array}{r|ccccccccc}
-\text{variables} & \rotatebox{70}{$x_1$} & \rotatebox{70}{$x_2$} & \rotatebox{70}{$x_3$} & \rotatebox{70}{$\frac{x_2 + x_3}{x_1}$} & \rotatebox{70}{$\frac{x_1 + x_3}{x_2}$} & \rotatebox{70}{$\frac{x_1 + x_2}{x_3}$} & \rotatebox{70}{$\frac{x_1 + x_2 + x_3}{x_2 x_3}$} & \rotatebox{70}{$\frac{x_1 + x_2 + x_3}{x_1 x_3}$} & \rotatebox{70}{$\frac{x_1 + x_2 + x_3}{x_1 x_2}$} \\[.2cm]
-\text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{-1}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{0}{1}{-1} & \compactVector{0}{0}{-1} & \compactVector{-1}{0}{0} & \compactVector{0}{-1}{0} \\[.6cm]
-\text{linearity}	& 0 & 0 & 1 & 1 & 0 & -1 & -1 & 0 & 0 \\
-\text{space}		& 0 & -1 & 0 & 0 & 1 & -1 & 0 & 0 & 1 \\
-					& 1 & 1 & 0 & -1 & 0 & 1 & 0 & -1 & -1 \\[.2cm]
-\text{inequalities} & -1 & 0 & 0 & 0 & 1 & 1 & -1 & 0 & 0 \\
- 					& 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 1 \\
- 					& 0 & 0 & -1 & 1 & 1 & 0 & 0 & 0 & -1 \\
- 					& 0 & 0 & 1 & -1 & 0 & 0 & 0 & 1 & 0 \\
- 					& 0 & 1 & 0 & 0 & 0 & -1 & 1 & 0 & 0 \\
- 					& 0 & -1 & 0 & 1 & 0 & 1 & 0 & -1 & 0 \\[.2cm]
-\end{array}
-\]
-
 %sage: B = Matrix([[0,-1,1],[1,0,-1],[-1,1,0]])
@@
 %A 9-dimensional polyhedron in QQ^9 defined as the convex hull of 1 vertex, 6 rays, 3 lines
-%sage: TCCA.lines()
-%(A line in the direction (0, 1, 0, -1, 1, 0, 0, 0, -1),
-% A line in the direction (0, 0, 1, 0, 0, 1, 0, -1, -1),
-% A line in the direction (1, 0, 0, 0, -1, -1, -1, 1, 1))
 %sage: TCCA.inequalities()
@@
 % An inequality (0, 0, 0, 0, 1, 0, -1, -1, 1) x + 0 >= 0)
-
-\noindent
-The type cone of the right fan lives in~$\R^{12}$, has a linearity space of dimension~$3$ (a basis is given below) and $9$ facet defining inequalities (given below).
-
-\[
-\begin{array}{r|c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;}c@{\;}c@{\;}c@{}c@{}c@{}c}
-\text{variables} & \rotatebox{70}{$x_1$} & \rotatebox{70}{$x_2$} & \rotatebox{70}{$x_3$} & \rotatebox{70}{$\frac{x_2 + x_3}{x_1}$} & \rotatebox{70}{$\frac{x_1 + x_3}{x_2}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2}{x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + x_1 x_3}{x_2 x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + x_2 x_3}{x_1 x_3}$} & \rotatebox{70}{$\frac{x_1 + x_2 + x_3}{x_1 x_2}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + 2 x_1 x_3 + x_3^2}{x_2^2 x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + 2 x_2 x_3 + x_3^2}{x_1^2 x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + x_1 x_3 + x_2 x_3}{x_1 x_2 x_3}$} \\[.2cm]
-\text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{-1}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{0}{2}{-1} & \compactVector{0}{1}{-1} & \compactVector{-1}{1}{0} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} & \compactVector{-2}{0}{1} & \compactVector{-1}{0}{0}  \\[.6cm]
-\text{linearity}	& 1 & 1 & 2 & 1 & 0 & 0 & -1 & 0 & -1 & -2 & 0 & -1 \\
-\text{space}		& 0 & 1 & 0 & 0 & -1 & 2 & 1 & 1 & -1 & 0 & 0 & 0 \\
-					& 0 & 0 & -1 & -1 & 0 & 1 & 1 & 0 & 0 & 1 & -1 & 0 \\[.2cm]
-\text{inequalities} & 0 & 0 & 0 & 0 & 0 & 1 & 0 & -2 & 0 & 0 & 1 & 0 \\
-					& 0 & 1 & 0 & 0 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 1 \\
-					& 0 & -1 & 0 & 1 & 0 & 0 & 0 & 1 & 0 & 0 & -1 & 0 \\
-					& -1 & 0 & 0 & 0 & 1 & 0 & 1 & 0 & 0 & -1 & 0 & 0 \\
-					& 0 & 0 & 0 & 0 & 0 & -1 & 1 & 1 & 0 & 0 & 0 & -1 \\
-					& 0 & 0 & -1 & 1 & 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 \\
-					& 0 & 0 & 0 & 0 & 0 & 1 & -2 & 0 & 0 & 1 & 0 & 0 \\
-					& 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 1 & 0 & 0 & 0 \\
-					& 0 & 0 & 1 & -2 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 \\[.2cm]
-\end{array}
-\]
 
@@
 % An inequality (0, 0, 0, 1, 1, 0, 0, -2, 0, 0, 0, 0) x + 0 >= 0)
+\vincent{todo}
 \end{example}
 
-In order to describe the facets of this type cone, we need the following special mutations.
+In order to describe the facets of this type-cone, we need the following special mutations.
 
 \begin{definition}
-%Consider a seed~$\seed = (\B, \cluster)$ and a cluster variable~$x \in \cluster$.
-The mutation of a seed~$\seed = (\B, \cluster)$ in the direction of a cluster variable~$x \in \cluster$ is a \defn{mesh mutation} that \defn{starts} (resp.~\defn{ends}) at~$x$ if the entries~$b_{xy}$ for~$y \in \cluster$ are all non-negative (resp.~all non-positive).
-A mesh mutation is \defn{initial} if it starts at a cluster variable of an initial seed.
+Consider a seed~$(\B, \cluster)$ and a cluster variable~$x \in \cluster$.
+The mutation of~$\seed$ in direction~$x$ is a \defn{mesh mutation} if the entries~$b_{xy}$ for~$y \in \cluster$ are all non-negative, or all non-positive.
 \end{definition}
 
-We denote by~$\meshes$ the set of all pairs~$(x,x')$ where~$x$ and~$x'$ are two cluster variables of~$\principalClusterAlgebra$ which are exchangeable via a non-initial mesh mutation.
+For instance, in the initial seed~$(\B_\circ, \cluster_\circ)$, the mutation in the direction of any variable~${x_\circ \in \cluster_\circ}$ is a mesh.
+We call these meshes \defn{initial}.
+We denote by~$\meshes$ the set of all pairs~$(x,x')$ where~$x$ and~$x'$ are two non-initial cluster variables of~$\principalClusterAlgebra$ which are exchangeable via a mesh mutation.
+The following statement describes the other meshes.
 
@@
 \label{lem:dependenceMesh}
-Consider two adjacent seeds~${(\B, \cluster)}$ and~${(\B', \cluster')}$ with~$\cluster \ssm \{x\} = \cluster' \ssm \{x'\}$ connected by a mesh mutation.
-If the mesh mutation is initial, then
+Consider two adjacent seeds~${(\B, \cluster)}$ and~${(\B', \cluster')}$ with~$\cluster \ssm \{x\} = \cluster' \ssm \{x'\}$ such that the entries~$b_{xy}$ for~$y \in \cluster$ are all non-positive or all non-negative.
+If either~$x$ or~$x'$ is an initial cluster variable, then
 \[
@@
 \label{prop:extremalExchangeablePairsCA}
-For any finite type exchange matrix~$\B_\circ$ (acyclic or not), the non-initial mesh mutations precisely correspond to the extremal exchangeable pairs of the cluster fan~$\gvectorFan[\B_\circ]$.
+For any finite type exchange matrix~$\B_\circ$ (acyclic or not), the non-initial mesh mutations precisely correspond to the extremal exchangeable pairs of the $\b{g}$-vector fan~$\gvectorFan[\B_\circ]$.
 \end{proposition}
@@
 \label{coro:simplicialTypeConeCA}
-The type cone~$\typeCone(\gvectorFan[n])$ is simplicial.
+The type-cone~$\typeCone(\gvectorFan[n])$ is simplicial.
 \end{corollary}
 
-Combining \cref{coro:simplicialTypeCone,coro:simplicialTypeConeCA,prop:extremalExchangeablePairsCA}, we derive the following description of all polytopal realizations of the cluster fan~$\gvectorFan[\B_\circ]$.
+Combining \cref{coro:simplicialTypeCone,coro:simplicialTypeConeCA,prop:extremalExchangeablePairsCA}, we derive the following description of all polytopal realizations of the $\b{g}$-vector fan~$\gvectorFan[\B_\circ]$.
 This result was stated in~\cite{BazierMatteDouvilleMousavandThomasYildirim} in the special situation of acyclic seeds in simply-laced types.
-Note that our proof is quite different from~\cite{BazierMatteDouvilleMousavandThomasYildirim} as it relies on our type cone approach.
+Note that our proof is quite different from~\cite{BazierMatteDouvilleMousavandThomasYildirim} as it relies on our type-cone approach.
 
@@
 \]
-is a generalized associahedron, whose normal fan is the cluster fan~$\gvectorFan[\B_\circ]$.
+is a generalized associahedron, whose normal fan is the $\b{g}$-vector fan~$\gvectorFan[\B_\circ]$.
 \end{theorem}
@@
 Non-kissing complexes are geometrically realized by polytopes called gentle associahedra, whose normal fan is called the non-kissing fan: its rays correspond to walks in the quiver and its cones are generated by the non-kissing walks.
-In this section, we describe the type cone of the non-kissing fan of a quiver~$\quiver$ with no self-kissing walks.
+In this section, we describe the type-cone of the non-kissing fan of a quiver~$\quiver$ with no self-kissing walks.
 
@@
 
-\subsubsection{Type cones of non-kissing fans}
-
-We now discuss the type cones of the non-kissing fans defined in \cref{thm:nonkissingFan}. We obtain from \cref{prop:exchangeablePairsNKC} the following redundant description.
+\subsubsection{Type-cones of non-kissing fans}
+
+We now discuss the type-cones of the non-kissing fans defined in \cref{thm:nonkissingFan}. We obtain from \cref{prop:exchangeablePairsNKC} the following redundant description.
 
 \begin{corollary}
-For any non-kissing finite gentle quiver~$\quiver$, the type cone of the non-kissing fan~$\gvectorFan[\quiver]$ is given by
+For any non-kissing finite gentle quiver~$\quiver$, the type-cone of the non-kissing fan~$\gvectorFan[\quiver]$ is given by
 \[
@@
 \label{exm:typeConeNKC}
-Consider the non-kissing fans illustrated in \cref{fig:nonkissingFans}.
-The type cone of the left fan lives in~$\R^9$, has a linearity space of dimension~$3$ (a basis is given below) and $6$ facet defining inequalities (given below).
-
-\[
-\begin{array}{r|cccccccc}
-\text{walks} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA1}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA2}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA3}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA4}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA5}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA6}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA7}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA8}} \\[.6cm]
-\text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{0}{1}{-1} & \compactVector{-1}{0}{0} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} \\[.6cm]
-\text{linearity}	& 0 & -1 & 0 & 1 & -1 & 0 & 1 & 0 \\
-\text{space}		& 1 & 1 & 0 & 0 & 1 & -1 & -1 & 0 \\
-					& 0 & 0 & 1 & 0 & -1 & 0 & 0 & -1 \\[.2cm]
-\text{inequalities} & -1 & 0 & 0 & 1 & 1 & 0 & 0 & -1 \\
-					& 1 & 0 & 0 & -1 & 0 & 0 & 1 & 0 \\
-					& 0 & -1 & 1 & 0 & 1 & 0 & 0 & 0 \\
-					& 0 & 0 & 0 & 1 & 0 & 1 & -1 & 0 \\
-					& 0 & 1 & 0 & 0 & -1 & 0 & 0 & 1 \\[.2cm]
-\end{array}
-\]
-
+Consider the gentle quivers of \cref{fig:nonkissingFans}.
 %sage: Q = GentleQuiver({'e1':{'e2':['a']}, 'e2':{'e3':['b']}}, [('a','b')])
@@
 %A 8-dimensional polyhedron in QQ^8 defined as the convex hull of 1 vertex, 5 rays, 3 lines
-%sage: TCNKC.lines()
-%(A line in the direction (0, 0, 1, 0, 1, 0, -1, -1),
-% A line in the direction (1, 0, 0, 0, -1, -1, 1, 1),
-% A line in the direction (0, 1, 0, -1, 0, 0, 0, -1))
 %sage: TCNKC.inequalities()
@@
 % An inequality (0, 0, 0, 1, 0, 0, 1, -1) x + 0 >= 0)
-
-\noindent
-The type cone of the right fan lives in~$\R^{11}$, has a linearity space of dimension~$3$ (a basis is given below) and $9$ facet defining inequalities (given below).
-In particular, it is not simplicial.
-
-\[
-\begin{array}{r|c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c}
-\text{walks} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB1}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB2}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB3}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB4}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB5}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB6}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB7}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB8}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB9}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB10}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB11}} \\[.6cm]
-\text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{1}{0}{-1} & \compactVector{0}{-1}{1} & \compactVector{0}{1}{-1} & \compactVector{-1}{0}{1} & \compactVector{-1}{0}{0} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} \\[.6cm]
-\text{linearity}	& 0 & -1 & 0 & 1 & 0 & 1 & -1 & 0 & 0 & 1 & 0 \\
-\text{space}		& 1 & 0 & 0 & 1 & 1 & 0 & 0 & -1 & -1 & 0 & 0 \\
-					& 1 & 0 & 1 & 1 & 0 & 1 & -1 & 0 & -1 & 0 & -1 \\[.2cm]
-\text{inequalities} & 0 & 0 & 0 & 1 & 0 & -1 & 0 & 1 & 0 & 0 & 0 \\
-					& -1 & 1 & 0 & 0 & 1 & 0 & -1 & 0 & 0 & 0 & 0 \\
-					& 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 0 & 0 & 1 \\
-					& 1 & 0 & -1 & -1 & 0 & 1 & 0 & 0 & 0 & 0 & 0 \\
-					& 0 & 0 & 0 & 1 & -1 & 0 & 1 & 0 & 0 & 0 & 0 \\
-					& 0 & 0 & 1 & 0 & 0 & -1 & 0 & 0 & 0 & 1 & 0 \\
-					& 0 & 0 & 0 & 0 & 0 & 1 & 0 & -1 & 1 & -1 & 0 \\
-					& 0 & 0 & 0 & -1 & 1 & 0 & 0 & 0 & 0 & 1 & -1 \\
-					& 0 & -1 & 0 & 0 & 0 & 0 & 1 & 1 & -1 & 0 & 0 \\[.2cm]
-\end{array}
-\]
+%sage: TCNKC.lines()
+%(A line in the direction (0, 0, 1, 0, 1, 0, -1, -1),
+% A line in the direction (1, 0, 0, 0, -1, -1, 1, 1),
+% A line in the direction (0, 1, 0, -1, 0, 0, 0, -1))
 
@@
 %sage: Q.non_kissing_fan().rays()
-%N( 1,  0,  0),0
-%N( 0,  0,  1),1
-%N( 1,  0, -1),2
-%N( 1, -1,  0),3
-%N( 0,  0, -1),4
-%N(-1,  0,  1),5
-%N( 0, -1,  0),6
-%N( 0, -1,  1),7
-%N(-1,  0,  0),8
-%N( 0,  1,  0),9
-%N( 0,  1, -1)10
+%N( 1,  0,  0),
+%N( 0,  0,  1),
+%N( 1,  0, -1),
+%N( 1, -1,  0),
+%N( 0,  0, -1),
+%N(-1,  0,  1),
+%N( 0, -1,  0),
+%N( 0, -1,  1),
+%N(-1,  0,  0),
+%N( 0,  1,  0),
+%N( 0,  1, -1)
 %in 3-d lattice N
@@
 %A 11-dimensional polyhedron in QQ^11 defined as the convex hull of 1 vertex, 9 rays, 3 lines
-%sage: TCNKC.lines()
-%(A line in the direction (0, 0, 0, 1, 0, 0, 1, 1, 0, -1, -1),
-% A line in the direction (1, 0, 1, 1, 0, -1, 0, 0, -1, 0, 0),
-% A line in the direction (1, 1, 0, 1, -1, 0, 0, 1, -1, 0, -1))
 %sage: TCNKC.inequalities()
@@
 % An inequality (0, 0, 0, 0, 0, 1, 0, 0, -1, -1, 1) x + 0 >= 0)
+%sage: TCNKC.lines()
+%(A line in the direction (0, 0, 0, 1, 0, 0, 1, 1, 0, -1, -1),
+% A line in the direction (1, 0, 1, 1, 0, -1, 0, 0, -1, 0, 0),
+% A line in the direction (1, 1, 0, 1, -1, 0, 0, 1, -1, 0, -1))
+\vincent{Todo}
 \end{example}
 
-As illustrated in \cref{exm:typeConeNKC}, the type cone of the non-kissing fan is not simplicial and we do not always understand its extremal exchangeable pairs.
-In the next section section, we will explore a special family of gentle quivers for which we can completely describe the type cone.
+As illustrated in \cref{exm:typeConeNKC}, the type-cone of the non-kissing fan is not simplicial and we do not always understand its extremal exchangeable pairs.
+In the next section section, we will explore a special family of gentle quivers for which we can completely describe the type-cone.
 The combination of this special family with computer experiments in the general case support the following conjecture.
@@
 
-\subsubsection{Simplicial type cones for self-kissing-free and $2$-cycle-free quivers}
+\subsubsection{Simplicial type-cones for self-kissing-free and $2$-cycle-free quivers}
 \label{subsubsec:simplicialTypeConeNKC}
@@
 In particular, the classical associahedron is the gentle associahedron of a simple gentle quiver.
-We will see in~\cref{coro:simplicialTypeConeNKC} that the type cone of the non-kissing fan~$\gvectorFan[\quiver]$ of a simple gentle quiver~$\quiver$ happens to be simplicial, and we will derive in~\cref{coro:allPolytopalRealizationsNKC} a simple description of all polytopal realizations of~$\gvectorFan[\quiver]$.
+We will see in~\cref{coro:simplicialTypeConeNKC} that the type-cone of the non-kissing fan~$\gvectorFan[\quiver]$ of a simple gentle quiver~$\quiver$ happens to be simplicial, and we will derive in~\cref{coro:allPolytopalRealizationsNKC} a simple description of all polytopal realizations of~$\gvectorFan[\quiver]$.
 
@@
 
-The following statement describes the type cone of the non-kissing fan of a gentle quiver with no self-kissing walks.
+The following statement describes the type-cone of the non-kissing fan of a gentle quiver with no self-kissing walks.
 
@@
 \]
-Therefore, the outer normal vector of the corresponding inequality of the type cone~$\typeCone(\gvectorFan[\quiver])$ is
+Therefore, the outer normal vector of the corresponding inequality of the type-cone~$\typeCone(\gvectorFan[\quiver])$ is
 \[
@@
 \label{coro:simplicialTypeConeNKC}
-For any simple gentle quiver~$\quiver$, the type cone~$\typeCone(\gvectorFan[\quiver])$ of the non-kissing fan~$\quiver$ is simplicial.
+For any simple gentle quiver~$\quiver$, the type-cone~$\typeCone(\gvectorFan[\quiver])$ of the non-kissing fan~$\quiver$ is simplicial.
 \end{corollary}
@@
 \begin{proof}
-\cref{prop:extremalExchangeablePairsNKC} asserts that the type cone~$\typeCone(\gvectorFan[\quiver])$ has one facet for each string of~$\quiver$.
+\cref{prop:extremalExchangeablePairsNKC} asserts that the type-cone~$\typeCone(\gvectorFan[\quiver])$ has one facet for each string of~$\quiver$.
 Since all strings are distinguishable by \cref{prop:noSelfKissing}, the number of facets of~$\typeCone(\gvectorFan[\quiver])$ is $|\strings| = |\distinguishableStrings| = |\properWalks| - |Q_0|$ by~\cref{prop:bijectionStringsWalks}, so that~$\typeCone(\gvectorFan[\quiver])$ is simplicial.
@@
 For a given graph~$\graphG$, the resulting polytopes all have the same normal fan, called nested fan of~$\graphG$: its rays are the characteristic vectors of the tubes, and its cones are generated by characteristic vectors of compatible tubes.
-In this section, we describe the type cone of the nested fan of any graph~$\graphG$.
+In this section, we describe the type-cone of the nested fan of any graph~$\graphG$.
 
@@
 
-\subsubsection{Type cones of graphical nested fans}
-
-We now discuss the type cones of the graphical nested fans defined in \cref{thm:nestedFan}.
+\subsubsection{Type-cones of graphical nested fans}
+
+We now discuss the type-cones of the graphical nested fans defined in \cref{thm:nestedFan}.
 We first obtain from \cref{prop:exchangeablePairsGA} the following redundant description.
@@
 \begin{corollary}
-For any graph~$\graphG$, the type cone of the nested fan~$\gvectorFan[\graphG]$ is given by
+For any graph~$\graphG$, the type-cone of the nested fan~$\gvectorFan[\graphG]$ is given by
 \[
@@
 \label{exm:typeConeGA}
-Consider the nested fans illustrated in \cref{fig:nestedFans}.
-The type cone of the left fan lives in~$\R^{13}$, has a linearity space of dimension~$3$ (a basis is given below) and $6$ facet defining inequalities (given below).
-In particular, it is not simplicial.
-
-\[
-\begin{array}{r|c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c}
-\text{walks} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA1}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA2}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA3}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA4}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA5}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA6}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA7}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA8}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA9}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA10}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA11}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA12}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA13}}  \\[.6cm]
-\text{$\b{g}$-vectors} & \\ %\compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{1}{0}{-1} & \compactVector{0}{-1}{1} & \compactVector{0}{1}{-1} & \compactVector{-1}{0}{1} & \compactVector{-1}{0}{0} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} \\[.6cm]
-\text{linearity}	& 
-\text{space}		& \\[.2cm]
-\text{inequalities} & \\[.2cm]
-\end{array}
-\]
-
-\noindent
-The type cone of the right fan lives in~$\R^{11}$, has a linearity space of dimension~$3$ (a basis is given below) and $9$ facet defining inequalities (given below).
-In particular, it is not simplicial.
-
-\[
-\begin{array}{r|c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c}
-\text{walks} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB1}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA2}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB3}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB4}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB5}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB6}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB7}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB8}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB9}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB10}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB11}} \\[.6cm]
-\text{$\b{g}$-vectors} & \\ %\compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{1}{0}{-1} & \compactVector{0}{-1}{1} & \compactVector{0}{1}{-1} & \compactVector{-1}{0}{1} & \compactVector{-1}{0}{0} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} \\[.6cm]
-\text{linearity}	& 
-\text{space}		& \\[.2cm]
-\text{inequalities} & \\[.2cm]
-\end{array}
-\]
-
 \vincent{Todo}
@@
 
-In the remaining of this section, we describe the facet defining inequalities of the type cone of the graphical nested fans.
-Observe first that we have already indirectly described this type cone when the graph is a path in \cref{prop:extremalExchangeablePairsAsso}.
+In the remaining of this section, we describe the facet defining inequalities of the type-cone of the graphical nested fans.
+Observe first that we have already indirectly described this type-cone when the graph is a path in \cref{prop:extremalExchangeablePairsAsso}.
 Recall that on the path with~$n+1$ vertices, the tubes of the path are the intervals of~$[n+1]$ and that two intervals~$[i,j]$ and~$[i',j']$ of~$[n+1]$ are exchangeable if either~${i < i' \le j+1 < j'+1}$ or~${i' < i \le j'+1 < j+1}$.
@@
 
-We now consider an arbitrary graph~$\graphG$ and describe the type cone of its nested fan.
+We now consider an arbitrary graph~$\graphG$ and describe the type-cone of its nested fan.
 \cref{prop:extremalExchangeablePairsA} extends as follows.
@@
 
-To conclude on graph associahedra, we characterize the graphs~$\graphG$ whose nested fan has a simplicial type cone.
+To conclude on graph associahedra, we characterize the graphs~$\graphG$ whose nested fan has a simplicial type-cone.
 
 \begin{proposition}
-The type cone~$\typeCone(\gvectorFan[\graphG])$ is simplicial if and only if~$\graphG$ is a path.
+The type-cone~$\typeCone(\gvectorFan[\graphG])$ is simplicial if and only if~$\graphG$ is a path.
 \end{proposition}
@@
 \section{Relations for~$\b{g}$-vectors in finite type cluster algebras via~$2$-Calabi--Yau triangulated categories}
-\label{sec:clusterCategories}
 
@@
 
-\begin{corollary}\label{corollary::meshes positively generate cluster cats}
+\begin{corollary}
  Assume that~$\ind(\cat)$ is finite.
@@
 
-\begin{proof}[Proof of Theorem~\ref{theorem::extricats}]
+\begin{proof}[Proof of Theorem~\ref{theorem::extricats}]\yann{PG: Est-ce que cela te semble suffisant, ou veux-tu que j'ajoute des d\'etails ? }
  The proof is now similar to the proof of Theorem~\ref{theo::relations-g-vecteurs}, by using Proposition~\ref{prop::KRextricat} instead of Proposition~\ref{prop::functor-F}, Proposition~\ref{prop::index iso extricat} instead of Corollary~\ref{coro::grothendieck-g-vectors}, and the fact that~$\tc$ is made of projective objects instead of Lemma~\ref{lemm::almost-split}.
@@
 \begin{proof}[Proof of Corollary~\ref{corollary::meshes positively generate extricats}]
-The proof is similar to that of Corollary~\ref{corollary::meshes positively generate cluster cats}.
+\yann{TO DO}
 \end{proof}
@@
 
-% \begin{corollary}
-%  Generalised cluster categories with infinite dimensional Hom-spaces ?
-% \end{corollary}
+\begin{corollary}
+ Generalised cluster categories with infinite dimensional Hom-spaces ?
+\end{corollary}
 

### 2019-04-02 thirdPaper/draft/typeConeAssociahedra.tex
mesh mutations

--- 2019-04-02 thirdPaper/draft/typeConeAssociahedra.tex
@@
 A mesh mutation is \defn{initial} if it starts at a cluster variable of an initial seed.
-We denote by~$\meshes$ the set of all pairs~$(x,x')$ where~$x$ and~$x'$ are two cluster variables of~$\principalClusterAlgebra$ which are exchangeable via a non-initial mesh mutation.
+We denote by~$\meshes$ the set of all pairs~$\{x,x'\}$ where~$x$ and~$x'$ are two cluster variables of~$\principalClusterAlgebra$ which are exchangeable via a non-initial mesh mutation.
 \end{definition}
+\vincent{Link to \cref{sec:clusterCategories}.}
+\vincent{Pictures quivers.}
 
@@
 \begin{proof}
+%Conversely, since~$\gvectorFan[n]$ has dimension~$n$ and~$n(n+3)/2$ rays (corresponding to the internal diagonals of the $(n+3)$-gon), we know from \cref{rem:dimTypeCone} that there are at least~$n(n+1)/2$ extremal exchangeable pairs.
+We thus conclude that all exchangeable pairs of diagonals~$\{(a,b-1), (a+1,b)\}$ for~$1 \le a < b-2 \le n$ are extremal.
+%
+%
+%Our next statement follows from~\cref{thm:extremalExchangeablePairsCA,lem:bijectionMeshMutations}.
 \end{proof}
@@
 
-We also obtain from \cref{thm:extremalExchangeablePairsCA} the following surprising property.
-
-\begin{corollary}
-Any $\b{c}$-vector supports exactly one extremal exchangeable pair.
-\end{corollary}
-
-Our next statement follows from~\cref{thm:extremalExchangeablePairsCA,lem:bijectionMeshMutations}.
+Our next statement follows from the end of the previous proof.
 
@@
 The type cone~$\typeCone(\gvectorFan[n])$ is simplicial.
+\end{corollary}
+
+We also obtain from \cref{thm:extremalExchangeablePairsCA} the following surprising property.
+
+\begin{corollary}
+Any positive dual $\b{c}$-vector supports exactly one extremal exchangeable pair.
 \end{corollary}

### 2019-04-02 thirdPaper/draft/typeConeAssociahedra.tex

--- 2019-04-02 thirdPaper/draft/typeConeAssociahedra.tex
@@
 
-\subsection{Type cone}
-
+\subsection{Type-cone}
+\arnau{McMullen uses a dash between type and cone. Should we do it too?}
 Fix an essential complete simplicial fan~$\Fan$ in~$\R^n$.
@@
 \label{rem:dimTypeCone}
-Since the type cone is an open~$N$ dimensional cone with a linearity subspace of dimension~$n$, it has at least~$N-n$ facets.
-We say that the type cone is \defn{simplicial} when it has precisely $N-n$ facets.
+Since the type-cone is an open~$N$ dimensional cone with a linearity subspace of dimension~$n$, it has at least~$N-n$ facets.
+We say that the type-cone is \defn{simplicial} when it has precisely $N-n$ facets.
 \end{remark}
@@
 
-\cref{lem:MinkowskiSum} ensures that convex combinations in the type cone correspond to Minkowski combinations of polytopes.
-This provides natural Minkowski summands for all polytopal realizations of~$\Fan$.
+We say that~$P$ is a \defn{Minkowski summand} of~$R$ if there is a polytope~$Q$ such that $R=P+Q$, and a \defn{weak Minkowski summand} if there is a $\lambda\geq 0$ and a polytope~$Q$ such that $\lambda R=P+Q$.
+\cref{lem:MinkowskiSum} ensures that convex combinations in the type-cone correspond to Minkowski combinations of polytopes.
+Actually, the set of weak Minkowski summands of a polytope $P$ with normal fan~$\Fan$ is isomorphic to the closed type-cone~$\ctypeCone(\Fan)$ modulo linearity (the cone of weak Minkowski summands is studied by Meyer in~\cite{Meyer1974}, to see that it is equivalent to the type-cone and other formulations, see for example the appendix of~\cite{PostnikovReinerWilliams}).
+
+This provides natural Minkowski summands for all polytopal realizations of~$\Fan$: the rays of the type-cone.
+These correspond to indecomposable polytopes~(cf.~\cite{Meyer1974} or \cite{McMullen-typeCone}).
+A polytope $P$ in $\R^n$ is
+  called \defn{indecomposable} if all its weak Minkowski summands are of the form $\lambda P+t$ for some $\lambda\geq 0$ and $t\in\R^n$.
 
 \begin{corollary}
-Any polytope in~$\typeCone(\Fan)$ is the Minkowski sum of at most~$N-n$ polytopes corresponding to the rays of~$\b{K}\typeCone(\Fan)$.
+\arnau{See \cite{Meyer1974} and \cite{McMullen-typeCone}}
+Any polytope in~$\typeCone(\Fan)$ is the Minkowski sum of at most~$N-n$ indecomposable polytopes corresponding to the rays of~$\b{K}\typeCone(\Fan)$.
 \end{corollary}
+
+If $P=Q+R$, then we say that $R$ is the \defn{Minkowski difference} of $P$ and $Q$, which we denote by $R=P-Q$. We will only consider the case where $Q$ is a summand of $P$.
+There are two natural ways this construction generalizes to arbitrary pairs of polyhedra. On the one hand, we have $P-Q=\set{x\in\R^n}{x+Q\subseteq P}$. 
+Notice that $P_\b{h}-P_{\b{h}'}=P_{\b{h} - \b{h'}}$ when $P_{\b{h}'}$ is a Minkowski summand of $P_\b{h}$.
+Considering arbitrary differences of support functions gives rise to  \defn{virtual polyhedra}, which is the Grothendieck group of the semigroup of polytopes with Minkowski sums~\cite{PukhlikovKhovanskii1992}.
+
+\begin{corollary}
+Let $\b{h}_1,\dots, \b{h}_{N-n}\in \ctypeCone(\Fan)$ form a basis of $\ker \b{G}$.
+Then every $P_\b{h}$ with $\b{h}\in \ctypeCone(\Fan)$ has a unique representation (up to translation) as a signed Minkowski sum of dilates of $P_{\b{h}_1},\dots, P_{\b{h}_{N-n}}$.
+\end{corollary}
+\begin{proof}
+ It suffices to express the projection of $\b{h}$ into $\ker\b{G}$ in terms of $\b{h}_1,\dots, \b{h}_{N-n}$, and to separate those terms with positive and negative coefficients to express Minkowski sums and differences.
+\end{proof}
+
+This is used in~\cite{ArdilaBenedettiDoker} to show that every generalized permutahedron can be written uniquelyas a signed Minkowski sum of simplices. 
+\arnau{This has consequences in expressing volume and other valuations! I have to have a look at it.}
+In the particular case when the type-cone is simplicial, then we can get rid of the Minkowski differences.
+\begin{corollary}
+ If the type-cone~$\typeCone(\Fan)$ of $\Fan$ is simplicial, then the $N-n$ idecomposable polytopes $P_{\b{h}_1},\dots, P_{\b{h}_{N-n}}$ arising from the rays of $\ctypeCone(\Fan)$
+ verify that 
+ \begin{enumerate}[(i)]
+  \item  every $P_\b{h}$ with $\b{h}\in \typeCone(\Fan)$ has a unique representation (up to translation) as a Minkowski sum of positive dilates of $P_{\b{h}_1},\dots, P_{\b{h}_{N-n}}$; and
+ \item  every $P_\b{h}$ with $\b{h}\in \ctypeCone(\Fan)$ has a unique representation (up to translation) as a Minkowski sum of dilates of $P_{\b{h}_1},\dots, P_{\b{h}_{N-n}}$.
+ \end{enumerate}
+
+\end{corollary}
+ Note that such a family of polytopes giving rise to unique positive representations only exists when the type-cone is simplicial.
+
+\arnau{By \cite{McMullen-Valuations} valuations on the polytope $\alpha_1P_{\b{h}_1}+\cdots+\alpha_{N-n}P_{\b{h}_{N-n}}$ (such as volume) are a polynomial on $\alpha_1\dots\alpha_{N-n}$ with coefficients the mixed volumes.
+This also works when the $\alpha$'s are not necessarily positive \cite{ArdilaBenedettiDoker}.
+Does this help in any way?}
 
@@
 % An inequality (0, 0, 0, 1, 0, 0, 1, -1) x + 0 >= 0)
+%sage: TCNKC.lines()
+%(A line in the direction (0, 0, 1, 0, 1, 0, -1, -1),
+% A line in the direction (1, 0, 0, 0, -1, -1, 1, 1),
+% A line in the direction (0, 1, 0, -1, 0, 0, 0, -1))
 
@@
 % An inequality (0, 0, 0, 0, 0, 1, 0, 0, -1, -1, 1) x + 0 >= 0)
+%sage: TCNKC.lines()
+%(A line in the direction (0, 0, 0, 1, 0, 0, 1, 1, 0, -1, -1),
+% A line in the direction (1, 0, 1, 1, 0, -1, 0, 0, -1, 0, 0),
+% A line in the direction (1, 1, 0, 1, -1, 0, 0, 1, -1, 0, -1))
+\vincent{Todo}
 \end{example}

### 2019-04-02 thirdPaper/draft/typeConeAssociahedra.tex
mesh mutations

--- 2019-04-02 thirdPaper/draft/typeConeAssociahedra.tex
@@
 \newcommand{\fundamentalWeight}{\omega} % fundamental weights
-\newcommandx{\meshes}[1][1=\B_\circ]{\mathcal{M}\!\left(#1\right)} % meshes
+\newcommandx{\meshes}[1][1=\B_\circ]{\mathcal{M}(#1)} % meshes
 
@@
 \end{definition}
+
 \vincent{Link to \cref{sec:clusterCategories}.}
@@
 
-For~$(x,x') \in \meshes$ and~$y \in \principalVariables$, we denote by~$\alpha_{x,x',y}$ the coefficient of~$\gvectorFull{\B_\circ}{y}$ in the linear dependence between the $\b{g}$-vectors~$\gvectorFull{\B_\circ}{x}$ and~$\gvectorFull{\B_\circ}{x'}$.
+For~$\{x,x'\} \in \meshes$ and~$y \in \principalVariables$, we denote by~$\alpha_{x,x',y}$ the coefficient of~$\gvectorFull{\B_\circ}{y}$ in the linear dependence between the $\b{g}$-vectors~$\gvectorFull{\B_\circ}{x}$ and~$\gvectorFull{\B_\circ}{x'}$.
 In other words, according to \cref{lem:dependenceMesh}, if~${(\B, \cluster)}$ and~${(\B', \cluster')}$ are two adjacent seeds with~$\cluster \ssm \{x\} = \cluster' \ssm \{x'\}$, we have~$\alpha_{x,x',y} = |b_{xy}|$ for~$y \in \cluster \cap \cluster'$ and~$\alpha_{x,x',y} = 0$ otherwise.
@@
 The following will be shown in \cref{sec:clusterCategories}.
+\vincent{Link to \cref{sec:clusterCategories}.}
 
@@
 \begin{proof}
+It follows from \cref{prop:meshMutations} that ...
 %Conversely, since~$\gvectorFan[n]$ has dimension~$n$ and~$n(n+3)/2$ rays (corresponding to the internal diagonals of the $(n+3)$-gon), we know from \cref{rem:dimTypeCone} that there are at least~$n(n+1)/2$ extremal exchangeable pairs.
@@
 \begin{theorem}
-For any finite type exchange matrix~$\B_\circ$, and for any~$\b{\ell} \in \R_{>0}^{\meshes}$, the polytope
-\[
-R_{\b{\ell}}(\B_\circ) \eqdef \Bigset{\b{z} \in \R^{\principalVariables}}{\b{z} \ge 0 \text{ and } \b{z}_x + \b{z}_{x'} = \sum_{y \in \principalVariables} \alpha_{x,x',y} \, \b{z}_{y} \text{ for all } (x,x') \in \meshes}
+For any finite type exchange matrix~$\B_\circ$ (acyclic or not, simply-laced or not), and for any~$\b{\ell} \in \R_{>0}^{\meshes}$, the polytope
+\[
+R_{\b{\ell}}(\B_\circ) \eqdef \Bigset{\b{z} \in \R^{\principalVariables}}{\b{z} \ge 0 \text{ and } \b{z}_x + \b{z}_{x'} = \sum_{y \in \principalVariables} \alpha_{x,x',y} \, \b{z}_{y} \text{ for all } \{x,x'\} \in \meshes}
 \]

### 2019-04-02 thirdPaper/draft/typeConeAssociahedra.tex
clean 3.4
todo notes

@@
 \vincent{Link to \cref{sec:clusterCategories}.}
+\vincent{\cref{lem:bijectionMeshMutations} might become a conjecture.}
 \vincent{Pictures quivers.}
@@
 
+\vincent{Should we give a type $A$ intuition here?}
 %This statement will be proved in full generality in \cref{???}.
@@
 In this section, we need to restrict even further the family of gentle quivers we consider.
+\vincent{rephrase}
 
 \begin{definition}
-We say that a gentle quiver~$\quiver$ is \defn{simple} when
+A gentle quiver~$\quiver$ is called:
 \begin{itemize}
-\item it satisfies the three equivalent conditions of \cref{prop:noSelfKissing},
-\item it contains no cycle of length~$2$.
+\item \defn{brick}: it satisfies the three equivalent conditions of \cref{prop:noSelfKissing},
+\item \defn{$2$-acyclic}: it contains no cycle of length~$2$.
 \end{itemize}
@@
 Note that this family already contains a lot of relevant examples, including the grid and dissection quivers discussed in \cref{subsubsec:nonkissingComplex}.
-In particular, the classical associahedron is the gentle associahedron of a simple gentle quiver.
-We will see in~\cref{coro:simplicialTypeConeNKC} that the type cone of the non-kissing fan~$\gvectorFan[\quiver]$ of a simple gentle quiver~$\quiver$ happens to be simplicial, and we will derive in~\cref{coro:allPolytopalRealizationsNKC} a simple description of all polytopal realizations of~$\gvectorFan[\quiver]$.
+In particular, the classical associahedron is the gentle associahedron of a brick $2$-acyclic gentle quiver.
+We will see in~\cref{coro:simplicialTypeConeNKC} that the type cone of the non-kissing fan~$\gvectorFan[\quiver]$ of a brick $2$-acyclic gentle quiver~$\quiver$ happens to be simplicial, and we will derive in~\cref{coro:allPolytopalRealizationsNKC} a simple description of all polytopal realizations of~$\gvectorFan[\quiver]$.
 
@@
 \begin{proposition}
-For any simple gentle quiver~$\quiver$ and any string~$\sigma \in \strings$, the walks~$\cc{\sigma}$ and~$\hh{\sigma}$ are exchangeable with distinguished substring~$\sigma$.
+For any brick $2$-acyclic gentle quiver~$\quiver$ and any string~$\sigma \in \strings$, the walks~$\cc{\sigma}$ and~$\hh{\sigma}$ are exchangeable with distinguished substring~$\sigma$.
 \end{proposition}
@@
 \label{prop:extremalExchangeablePairsNKC}
-For any simple gentle quiver~$\quiver$, the extremal exchangeable pairs for the non-kissing fan of~$\quiver$ are precisely the pairs~$\{\cc{\sigma}, \hh{\sigma}\}$ for all strings~$\sigma \in \strings$.
+For any brick $2$-acyclic gentle quiver~$\quiver$, the extremal exchangeable pairs for the non-kissing fan of~$\quiver$ are precisely the pairs~$\{\cc{\sigma}, \hh{\sigma}\}$ for all strings~$\sigma \in \strings$.
 \end{proposition}
@@
 \label{coro:simplicialTypeConeNKC}
-For any simple gentle quiver~$\quiver$, the type cone~$\typeCone(\gvectorFan[\quiver])$ of the non-kissing fan~$\quiver$ is simplicial.
+For any brick $2$-acyclic gentle quiver~$\quiver$, the type cone~$\typeCone(\gvectorFan[\quiver])$ of the non-kissing fan~$\quiver$ is simplicial.
 \end{corollary}
@@
 \label{coro:allPolytopalRealizationsNKC}
-For any simple gentle quiver~$\quiver$ and any~$\b{\ell} \in \R_{>0}^{\strings}$, the polytope
+For any brick $2$-acyclic gentle quiver~$\quiver$ and any~$\b{\ell} \in \R_{>0}^{\strings}$, the polytope
 \[
@@
 \end{remark}
+
+\vincent{All this section is wrong when the quiver is not brick or has a cycle of length~$2$.}
 
@@
 
-\subsection{Application to~$\b g$-vectors}\label{sect::applications-g-vectors}
-
-\subsection{Application to~$\b g$-vectors of cluster algebras of finite type}\label{sect::applications-g-vectors}
+\subsection{Application to~$\b g$-vectors of cluster algebras of finite type}
+\label{sect::applications-g-vectors}
 
@@
 \end{proposition}
+
+\vincent{Here should come the proof of \cref{prop:meshMutations}.}
+
+\vincent{Here should come the proof of \cref{prop:uniqueExchangePropertyCA}.}
 
@@
 \end{corollary}
+
+\vincent{Here should come the proof of \cref{prop:exchangeablePairsNKC}.}
 
@@
 
+\vincent{Here should be explained that the gentle algebra result is a special case of this.}
+
 %%

### 2019-04-02 thirdPaper/draft/typeConeAssociahedra.tex
title

@@
 
+% formating the part command
+\makeatletter
+\def\part{\@startsection{part}{1}%
+\z@{.7\linespacing\@plus\linespacing}{.8\linespacing}%
+{\LARGE\sffamily\centering}}
+\@addtoreset{section}{part}
+\makeatother
+\renewcommand{\thesection}{\arabic{part}.\arabic{section}}
+
 % formating the table of contents
@@
 
-\title{Type cones of $\b{g}$-vector fans}
+\title[Generalized associahedra and minimal relations between $\b{g}$-vectors]{Associahedra for finite type cluster algebras \\ and minimal relations between $\b{g}$-vectors}
 
@@
 \end{itemize}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\part{Type cones of $\b{g}$-vector fans}
 
@@
 \vincent{\cref{lem:bijectionMeshMutations} might become a conjecture.}
-\vincent{Pictures quivers.}
+\vincent{Pictures AR quivers + labeling of meshes reported on the inequalities.}
 
@@
 
-We derive from \cref{prop:meshMutations} the following description of the facets of the type cone of the $\b{g}$-vector fan.
+We derive from \cref{prop:meshMutations} the following description of the facets of the type cone of the cluster fan.
 
@@
 \vincent{Todo}
+\vincent{Pictures AR quivers + labeling of meshes reported on the inequalities.}
 \end{example}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\part{Grothendieck group and relations between $\b{g}$-vectors}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-04-05 thirdPaper/draft/typeConeAssociahedra.tex
improvements examples

@@
 \usepackage[T1]{fontenc}
-\usepackage{enumerate, amsmath, amsfonts, amssymb, amsthm, mathrsfs, wasysym, graphics, graphicx, xcolor, url, hyperref, hypcap, xargs, multicol, pdflscape, multirow, hvfloat, array, ae, aecompl, pifont, mathtools, a4wide, float, blkarray, overpic}
+\usepackage{enumerate, amsmath, amsfonts, amssymb, amsthm, mathrsfs, wasysym, graphics, graphicx, xcolor, url, hyperref, hypcap, xargs, multicol, pdflscape, multirow, hvfloat, array, ae, aecompl, pifont, mathtools, a4wide, float, blkarray, overpic, nicefrac}
 \usepackage[noabbrev,capitalise]{cleveref}
@@
 
-\subsection{Faces of the type-cone and Minkowski sums}
+\subsection{Faces of the type-cone}
+
+%%%%%%%%%%%
+
+\subsection{Minkowski sums}
+
 Recall that the \defn{Minkowski sum} of two polytopes $P$ and $Q$ is the polytope $P+Q=\set{p+q}{p\in P\text{ and } q\in Q}$.
@@
 
-We say that~$P$ is a \defn{Minkowski summand} of~$R$ if there is a polytope~$Q$ such that $R=P+Q$, and a \defn{weak Minkowski summand} if there is a $\lambda\geq 0$ and a polytope~$Q$ such that $\lambda R=P+Q$.
+We say that~$P$ is a \defn{Minkowski summand} of~$R$ if there is a polytope~$Q$ such that $R=P+Q$, and a \defn{weak Minkowski summand} if there is a $\lambda \ge 0$ and a polytope~$Q$ such that ${\lambda R = P + Q}$.
 \cref{lem:MinkowskiSum} ensures that convex combinations in the type-cone correspond to Minkowski combinations of polytopes.
-Actually, the set of weak Minkowski summands of a polytope $P$ with normal fan~$\Fan$ is isomorphic to the closed type-cone~$\ctypeCone(\Fan)$ modulo linearity (the cone of weak Minkowski summands is studied by Meyer in~\cite{Meyer1974}, to see that it is equivalent to the type-cone and other formulations, see for example the appendix of~\cite{PostnikovReinerWilliams}).
+Actually, the set of weak Minkowski summands of a polytope $P$ with normal fan~$\Fan$ is isomorphic to the closed type-cone~$\ctypeCone(\Fan)$ modulo linearity (the cone of weak Minkowski summands is studied by W.~Meyer in~\cite{Meyer}, to see that it is equivalent to the type-cone and other formulations, see for example the appendix of~\cite{PostnikovReinerWilliams}).
 
 This provides natural Minkowski summands for all polytopal realizations of~$\Fan$: the rays of the type-cone.
-These correspond to indecomposable polytopes~(cf.~\cite{Meyer1974} or \cite{McMullen-typeCone}).
-A polytope $P$ in $\R^n$ is
-  called \defn{indecomposable} if all its weak Minkowski summands are of the form $\lambda P+t$ for some $\lambda\geq 0$ and $t\in\R^n$.
+These correspond to indecomposable polytopes, see~\cite{Meyer} or \cite{McMullen-typeCone}.
+A polytope $P$ in $\R^n$ is called \defn{indecomposable} if all its weak Minkowski summands are of the form $\lambda P+t$ for some $\lambda \ge 0$ and $t \in \R^n$.
 
 \begin{corollary}
-\arnau{See \cite{Meyer1974} and \cite{McMullen-typeCone}}
+\arnau{See \cite{Meyer} and \cite{McMullen-typeCone}}
 Any polytope in~$\typeCone(\Fan)$ is the Minkowski sum of at most~$N-n$ indecomposable polytopes corresponding to the rays of~$\b{K}\typeCone(\Fan)$.
@@
 
-If $P=Q+R$, then we say that $R$ is the \defn{Minkowski difference} of $P$ and $Q$, which we denote by $R=P-Q$. We will only consider the case where $Q$ is a summand of $P$.
-There are two natural ways this construction generalizes to arbitrary pairs of polyhedra. On the one hand, we have $P-Q=\set{x\in\R^n}{x+Q\subseteq P}$. 
+If $P = Q + R$, then we say that~$R$ is the \defn{Minkowski difference} of~$P$ and~$Q$, denoted~${R = P - Q}$. Note that this is only defined when~$Q$ is a Minkowski summand of~$P$.
+There are two natural ways this construction generalizes to arbitrary pairs of polyhedra. On the one hand, we have $P - Q = \set{x \in \R^n}{x + Q \subseteq P}$. 
 Notice that $P_\b{h}-P_{\b{h}'}=P_{\b{h} - \b{h'}}$ when $P_{\b{h}'}$ is a Minkowski summand of $P_\b{h}$.
-Considering arbitrary differences of support functions gives rise to  \defn{virtual polyhedra}, which is the Grothendieck group of the semigroup of polytopes with Minkowski sums~\cite{PukhlikovKhovanskii1992}.
+Considering arbitrary differences of support functions gives rise to \defn{virtual polyhedra}, which is the Grothendieck group of the semigroup of polytopes with Minkowski sums~\cite{PukhlikovKhovanskii}.
 
@@
 Let $\b{h}_1,\dots, \b{h}_{N-n}\in \ctypeCone(\Fan)$ form a basis of $\ker \b{G}$.
-Then every $P_\b{h}$ with $\b{h}\in \ctypeCone(\Fan)$ has a unique representation (up to translation) as a signed Minkowski sum of dilates of $P_{\b{h}_1},\dots, P_{\b{h}_{N-n}}$.
+Then for any~$\b{h} \in \ctypeCone(\Fan)$, the polytope~$P_\b{h}$ has a unique representation (up to translation) as a signed Minkowski sum of dilates of $P_{\b{h}_1},\dots, P_{\b{h}_{N-n}}$.
 \end{corollary}
@@
 
-This is used in~\cite{ArdilaBenedettiDoker} to show that every generalized permutahedron can be written uniquelyas a signed Minkowski sum of simplices. 
+This is used in~\cite{ArdilaBenedettiDoker} to show that every generalized permutahedron can be written uniquely as a signed Minkowski sum of simplices. 
 \arnau{This has consequences in expressing volume and other valuations! I have to have a look at it.}
 In the particular case when the type-cone is simplicial, then we can get rid of the Minkowski differences.
+
 \begin{corollary}
- If the type-cone~$\typeCone(\Fan)$ of $\Fan$ is simplicial, then the $N-n$ idecomposable polytopes $P_{\b{h}_1},\dots, P_{\b{h}_{N-n}}$ arising from the rays of $\ctypeCone(\Fan)$
- verify that 
+If the type-cone~$\typeCone(\Fan)$ of $\Fan$ is simplicial, then the $N-n$ idecomposable polytopes $P_{\b{h}_1},\dots, P_{\b{h}_{N-n}}$ arising from the rays of $\ctypeCone(\Fan)$ verify that 
 \begin{enumerate}[(i)]
@@
 \end{enumerate} 
-
 \end{corollary}
+
 Note that such a family of polytopes giving rise to unique positive representations only exists when the type-cone is simplicial.
@@
 Consider the nested fans illustrated in \cref{fig:nestedFans}.
-The type cone of the left fan lives in~$\R^{13}$, has a linearity space of dimension~$3$ (a basis is given below) and $6$ facet defining inequalities (given below).
+The type cone of the left fan lives in~$\R^{13}$, has a linearity space of dimension~$3$ (a basis is given below) and $19$ facet defining inequalities (given below).
 In particular, it is not simplicial.
@@
 \[
-\begin{array}{r|c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c}
+\begin{array}{r|c@{\;\;\;}c@{\;\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;}c@{\;}c@{\;}c@{\;}c@{\;\;}c@{\;\;}c@{\;\;}c}
 \text{walks} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA1}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA2}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA3}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA4}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA5}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA6}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA7}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA8}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA9}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA10}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA11}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA12}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA13}}  \\[.6cm]
-\text{$\b{g}$-vectors} & \\ %\compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{1}{0}{-1} & \compactVector{0}{-1}{1} & \compactVector{0}{1}{-1} & \compactVector{-1}{0}{1} & \compactVector{-1}{0}{0} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} \\[.6cm]
-\text{linearity}	& 
-\text{space}		& \\[.2cm]
-\text{inequalities} & \\[.2cm]
+\text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{0}{2}{-1} & \compactVector{\nicefrac{1}{2}}{-1}{\nicefrac{1}{2}} & \compactVector{1}{-2}{0} & \compactVector{\nicefrac{1}{2}}{0}{\nicefrac{-1}{2}} & \compactVector{-1}{2}{0} & \compactVector{\nicefrac{-1}{2}}{0}{\nicefrac{1}{2}} & \compactVector{-1}{0}{0} & \compactVector{0}{-2}{1} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} \\[.6cm]
+
+\text{linearity}	& 1 & 0 & 0 & 0 & 2 & 1 & 2 & -1 & -2 & -1 & 0 & 0 & 0 \\ 
+\text{space}		& -2 & -1 & 0 & -2 & 0 & 0 & -4 & 0 & 4 & 2 & 2 & 1 & 0 \\
+					& 0 & 0 & -1 & 1 & -2 & 0 & 2 & 0 & -2 & 0 & -1 & 0 & 1 \\[.2cm]
+\text{inequalities} & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & -2 & 1 \\
+					& 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 & 0 & 1 & 0 & -2 & 0 \\
+					& -1 & 2 & 0 & -1 & 0 & 0 & 2 & 0 & 0 & 0 & 0 & 0 & 0 \\
+					& 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 2 & -1 & -1 & 2 & 0 \\
+					& 0 & 0 & 0 & 0 & 0 & -1 & 2 & 0 & 0 & 0 & 0 & 2 & -1 \\
+					& -1 & 2 & -1 & 0 & 2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+					& -1 & 0 & 0 & 0 & 2 & -1 & 2 & 0 & 0 & 0 & 0 & 0 & 0 \\
+					& 0 & 2 & -1 & 0 & 0 & 0 & 0 & -1 & 1 & 0 & 0 & 0 & 0 \\
+					& 0 & 0 & -1 & 0 & 2 & 0 & 0 & 0 & 2 & 0 & -1 & 0 & 0 \\
+					& 0 & 0 & 0 & 0 & 2 & -1 & 0 & 0 & 0 & 0 & -1 & 2 & 0 \\
+					& 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & -2 & 1 & 0 & 0 & 0 \\
+					& 0 & 0 & 1 & 0 & -2 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+					& 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & -2 & 0 & 1 & 0 & 0 \\
+					& 1 & 0 & 0 & 0 & 0 & 0 & -2 & 0 & 0 & 0 & 0 & 0 & 1 \\
+					& 1 & 0 & 0 & 0 & -2 & 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 \\
+					& 1 & -2 & 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 \\
+					& 0 & 0 & 0 & 1 & 0 & 0 & 0 & -1 & 0 & 1 & 0 & 0 & -1 \\
+					& 0 & 0 & 0 & 1 & 0 & 1 & -2 & 0 & 0 & 0 & 0 & 0 & 0 \\
+					& 0 & -2 & 1 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\[.2cm]
 \end{array}
@@
 
+%sage: G = Graph([[1,2,3,4], [[1,2],[1,3],[1,4],[2,3],[3,4]]])
+%sage: M = Matrix([g_vector_GA(G, (1,)), g_vector_GA(G, (1,2)), g_vector_GA(G, (1,2,3)), [1,1,1,1]]).inverse()
+%sage: rays
+%{(1,): (1, 0, 0),
+% (1, 2): (0, 1, 0),
+% (1, 2, 3): (0, 0, 1),
+% (1, 2, 3, 4): (0, 0, 0),
+% (1, 2, 4): (0, 2, -1),
+% (1, 3): (1/2, -1, 1/2),
+% (1, 3, 4): (1, -2, 0),
+% (1, 4): (1/2, 0, -1/2),
+% (2,): (-1, 2, 0),
+% (2, 3): (-1/2, 0, 1/2),
+% (2, 3, 4): (-1, 0, 0),
+% (3,): (0, -2, 1),
+% (3, 4): (0, -1, 0),
+% (4,): (0, 0, -1)}
+
+%sage: NF = Fan([Cone([rays[tuple(tube)] for tube in tubing]) for tubing in maximal_tubings(G)])
+%sage: NF.rays()
+%N( 0, -1,  0),
+%N( 0,  2, -1),
+%N( 1,  0,  0),
+%N(-1,  2,  0),
+%N( 0,  0,  1),
+%N( 1, -2,  0),
+%N( 0, -2,  1),
+%N( 0,  0, -1),
+%N(-1,  0,  1),
+%N( 1,  0, -1),
+%N(-1,  0,  0),
+%N( 0,  1,  0),
+%N( 1, -2,  1)
+%in 3-d lattice N
+
+%sage: TCNF = type_cone(NF)
+%sage: TCNF
+%A 13-dimensional polyhedron in QQ^13 defined as the convex hull of 1 vertex, 25 rays, 3 lines
+%sage: TCNF.lines()
+%(A line in the direction (0, 0, 1, -1, 0, 1, 0, 0, -1, 1, -1, 0, 1),
+% A line in the direction (1, -2, -2, 0, 0, 0, 2, 0, 2, -2, 2, -1, 0),
+% A line in the direction (0, 1, 0, 0, -1, 0, -1, 1, -1, 1, 0, 0, -1))
+%sage: TCNF.inequalities()
+%(An inequality (-2, 0, 0, 0, 0, 0, 1, 1, 0, 0, 0, 0, 0) x + 0 >= 0,
+% An inequality (-2, 0, 0, 0, 0, 1, 0, 0, 0, 0, 1, 0, 0) x + 0 >= 0,
+% An inequality (0, -1, -1, 0, 0, 0, 0, 0, 0, 1, 0, 2, 0) x + 0 >= 0,
+% An inequality (2, 0, 0, 0, 0, 0, -1, 0, 1, 0, -1, 0, 0) x + 0 >= 0,
+% An inequality (2, 0, 0, 0, 0, -1, 0, -1, 0, 1, 0, 0, 0) x + 0 >= 0,
+% An inequality (0, 0, -1, 0, -1, 0, 0, 0, 0, 0, 0, 2, 1) x + 0 >= 0,
+% An inequality (0, 0, -1, 0, 0, -1, 0, 0, 0, 1, 0, 0, 1) x + 0 >= 0,
+% An inequality (0, 0, 0, -1, -1, 0, 0, 0, 1, 0, 0, 2, 0) x + 0 >= 0,
+% An inequality (0, 0, 0, 0, -1, 0, -1, 0, 1, 0, 0, 0, 1) x + 0 >= 0,
+% An inequality (2, 0, 0, 0, 0, -1, -1, 0, 0, 0, 0, 0, 1) x + 0 >= 0,
+% An inequality (0, 0, 0, 0, 1, 0, 0, 0, -1, 0, 1, 0, 0) x + 0 >= 0,
+% An inequality (0, 0, 0, 0, 1, 1, 0, 0, 0, 0, 0, 0, -1) x + 0 >= 0,
+% An inequality (0, 0, 0, 1, 0, 0, 1, 0, -1, 0, 0, 0, 0) x + 0 >= 0,
+% An inequality (0, 0, 1, 0, 0, 0, 0, 1, 0, -1, 0, 0, 0) x + 0 >= 0,
+% An inequality (0, 0, 1, 0, 0, 0, 1, 0, 0, 0, 0, 0, -1) x + 0 >= 0,
+% An inequality (0, 0, 1, 1, 0, 0, 0, 0, 0, 0, 0, -2, 0) x + 0 >= 0,
+% An inequality (0, 1, 0, -1, 0, 0, 0, -1, 0, 0, 1, 0, 0) x + 0 >= 0,
+% An inequality (0, 1, 0, 0, 0, 1, 0, 0, 0, -1, 0, 0, 0) x + 0 >= 0,
+% An inequality (0, 1, 0, 0, 1, 0, 0, 0, 0, 0, 0, -2, 0) x + 0 >= 0)
+%sage: len(TCNF.inequalities())
+%12
+
 \noindent
-The type cone of the right fan lives in~$\R^{11}$, has a linearity space of dimension~$3$ (a basis is given below) and $9$ facet defining inequalities (given below).
+The type cone of the right fan lives in~$\R^{11}$, has a linearity space of dimension~$3$ (a basis is given below) and $12$ facet defining inequalities (given below).
 In particular, it is not simplicial.
@@
 \[
-\begin{array}{r|c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c}
-\text{walks} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB1}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA2}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB3}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB4}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB5}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB6}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB7}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB8}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB9}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB10}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB11}} \\[.6cm]
-\text{$\b{g}$-vectors} & \\ %\compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{1}{0}{-1} & \compactVector{0}{-1}{1} & \compactVector{0}{1}{-1} & \compactVector{-1}{0}{1} & \compactVector{-1}{0}{0} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} \\[.6cm]
-\text{linearity}	& 
-\text{space}		& \\[.2cm]
-\text{inequalities} & \\[.2cm]
+\begin{array}{r|c@{\;\;\;}c@{\;\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;}c@{\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c}
+\text{walks} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB1}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB2}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB3}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB4}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB5}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB6}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB7}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB8}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB9}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB10}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB11}} \\[.6cm]
+\text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{\nicefrac{1}{2}}{-1}{\nicefrac{1}{2}} & \compactVector{1}{-2}{0} & \compactVector{-1}{2}{0} & \compactVector{\nicefrac{-1}{2}}{0}{\nicefrac{1}{2}} & \compactVector{-1}{0}{0} & \compactVector{0}{-2}{1} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} \\[.6cm]
+\text{linearity}	& 0 & 1 & 0 & -4 & -2 & 2 & 0 & 0 & -2 & -1 & 0 \\
+\text{space}		& 1 & 0 & 0 & 2 & 1 & -1 & -2 & -1 & 0 & 0 & 0 \\
+					& 1 & 0 & 1 & 4 & 1 & -1 & 0 & -1 & 1 & 0 & -1 \\[.2cm]
+\text{inequalities} & -1 & 2 & -1 & 2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+					& 1 & -2 & 0 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 \\
+					& 0 & 2 & -1 & 0 & 0 & -1 & 2 & 0 & 0 & 0 & 0 \\
+					& 1 & 0 & 0 & -2 & 0 & 0 & 0 & 0 & 1 & 0 & 0 \\
+					& 0 & 0 & -1 & 2 & 0 & 0 & 2 & 0 & -1 & 0 & 0 \\
+					& 0 & 0 & 0 & 2 & -1 & 0 & 0 & 0 & -1 & 2 & 0 \\
+					& 0 & 0 & 0 & 0 & 0 & 1 & -2 & 0 & 1 & 0 & 0 \\
+					& 0 & 0 & 0 & 0 & 0 & 0 & 2 & -1 & -1 & 2 & 0 \\
+					& 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & -2 & 1 \\
+					& 0 & 0 & 0 & 0 & 1 & 0 & 0 & 1 & 0 & -2 & 0 \\
+					& 0 & 0 & 1 & 0 & 0 & 0 & -2 & 1 & 0 & 0 & 0 \\
+					& 0 & 0 & 1 & -2 & 1 & 0 & 0 & 0 & 0 & 0 & 0 \\[.2cm]
 \end{array}
@@
 
-\vincent{Todo}
+%sage: G = Graph([[1,2,3,4], [[1,2],[1,3],[2,3],[3,4]]])
+%sage: M = Matrix([g_vector_GA(G, (1,)), g_vector_GA(G, (1,2)), g_vector_GA(G, (1,2,3)), [1,1,1,1]]).inverse()
+%sage: rays = {tuple(tube) : (g_vector_GA(G, tube)*M)[:-1] for tube in tubes(G)}
+%sage: rays
+%{(1,): (1, 0, 0),
+% (1, 2): (0, 1, 0),
+% (1, 2, 3): (0, 0, 1),
+% (1, 2, 3, 4): (0, 0, 0),
+% (1, 3): (1/2, -1, 1/2),
+% (1, 3, 4): (1, -2, 0),
+% (2,): (-1, 2, 0),
+% (2, 3): (-1/2, 0, 1/2),
+% (2, 3, 4): (-1, 0, 0),
+% (3,): (0, -2, 1),
+% (3, 4): (0, -1, 0),
+% (4,): (0, 0, -1)}
+
+%sage: NF = Fan([Cone([rays[tuple(tube)] for tube in tubing]) for tubing in maximal_tubings(G)])
+%sage: NF.rays()
+%N( 1,  0,  0),
+%N(-1,  2,  0),
+%N( 0,  0,  1),
+%N( 1, -2,  0),
+%N( 0,  0, -1),
+%N(-1,  0,  1),
+%N( 1, -2,  1),
+%N( 0, -2,  1),
+%N(-1,  0,  0),
+%N( 0,  1,  0),
+%N( 0, -1,  0)
+%in 3-d lattice N
+
+%sage: TCNF = type_cone(NF)
+%sage: TCNF
+%A 11-dimensional polyhedron in QQ^11 defined as the convex hull of 1 vertex, 11 rays, 3 lines
+%sage: TCNF.lines()
+%(A line in the direction (0, 2, 0, -2, 0, 0, -2, -2, 0, 1, -1),
+% A line in the direction (1, -1, 0, 1, 0, -1, 1, 0, -1, 0, 0),
+% A line in the direction (1, -1, 1, 1, -1, 0, 2, 1, -1, 0, 0))
+%sage: TCNF.inequalities()
+%(An inequality (-1, 0, -1, 0, 0, 0, 1, 0, 0, 2, 0) x + 0 >= 0,
+% An inequality (1, 1, 0, 0, 0, 0, 0, 0, 0, -2, 0) x + 0 >= 0,
+% An inequality (0, -1, -1, 0, 0, 1, 0, 0, 0, 2, 0) x + 0 >= 0,
+% An inequality (1, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0) x + 0 >= 0,
+% An inequality (0, 0, -1, 0, 0, 1, 1, -1, 0, 0, 0) x + 0 >= 0,
+% An inequality (0, 0, 0, -1, 0, 0, 1, -1, 0, 0, 2) x + 0 >= 0,
+% An inequality (0, 1, 0, 0, 0, -1, 0, 1, 0, 0, 0) x + 0 >= 0,
+% An inequality (0, 0, 0, 0, 0, 1, 0, -1, -1, 0, 2) x + 0 >= 0,
+% An inequality (0, 0, 0, 0, 1, 0, 0, 1, 0, 0, -2) x + 0 >= 0,
+% An inequality (0, 0, 0, 1, 0, 0, 0, 0, 1, 0, -2) x + 0 >= 0,
+% An inequality (0, 0, 1, 0, 0, -1, 0, 0, 1, 0, 0) x + 0 >= 0,
+% An inequality (0, 0, 1, 1, 0, 0, -1, 0, 0, 0, 0) x + 0 >= 0)
+%sage: len(TCNF.inequalities())
+%12
 \end{example}

### 2019-04-05 thirdPaper/draft/typeConeAssociahedra.tex
AR quivers non-kissing

@@
 \captionsetup{width=\textwidth}
+\usepackage[export]{adjustbox}
 
@@
 
+\vincent{Example type cone}
+
 \subsubsection{Associahedra and their normal fans}
@@
 	%\centerline{\includegraphics[scale=.45]{clusterFans}}
-	\centerline{
+	\begin{adjustbox}{center}
     	\begin{overpic}[scale=.45]{clusterFans}
@@
     	\end{overpic}
-	}
+	\end{adjustbox}
 	\caption{Two cluster fans~$\gvectorFan[\B_\circ]$ for the type~$A_3$~(left) and type~$C_3$~(right) cyclic initial exchange matrices.
@@
 \label{thm:gvectorFanCA}
-For any finite type exchange matrix~$\B_\circ$, the collection of cones \\[.1cm]
-\centerline{
-$\gvectorFan[\B_\circ] \eqdef \bigset{\R_{\ge0} \, \gvectorsFull{\B_\circ}{\seed}}{\seed \text{ seed of } \principalClusterAlgebra},$
-} \\[.1cm]
+For any finite type exchange matrix~$\B_\circ$, the collection of cones
+\[
+\gvectorFan[\B_\circ] \eqdef \bigset{\R_{\ge0} \, \gvectorsFull{\B_\circ}{\seed}}{\seed \text{ seed of } \principalClusterAlgebra},
+\]
 together with all their faces, forms a complete simplicial fan, called the \defn{$\b{g}$-vector fan} or \defn{cluster fan} of~$\B_\circ$.
@@
 \text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{-1}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{0}{1}{-1} & \compactVector{0}{0}{-1} & \compactVector{-1}{0}{0} & \compactVector{0}{-1}{0} \\[.6cm]
-\text{linearity}	& 0 & 0 & 1 & 1 & 0 & -1 & -1 & 0 & 0 \\
-\text{space}		& 0 & -1 & 0 & 0 & 1 & -1 & 0 & 0 & 1 \\
-					& 1 & 1 & 0 & -1 & 0 & 1 & 0 & -1 & -1 \\[.2cm]
-\text{inequalities} & -1 & 0 & 0 & 0 & 1 & 1 & -1 & 0 & 0 \\
- 					& 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 1 \\
- 					& 0 & 0 & -1 & 1 & 1 & 0 & 0 & 0 & -1 \\
+%\text{linearity}	& 0 & 0 & 1 & 1 & 0 & -1 & -1 & 0 & 0 \\
+%\text{space}		& 0 & -1 & 0 & 0 & 1 & -1 & 0 & 0 & 1 \\
+%					& 1 & 1 & 0 & -1 & 0 & 1 & 0 & -1 & -1 \\[.2cm]
+\text{facet}		& -1 & 0 & 0 & 0 & 1 & 1 & -1 & 0 & 0 \\
+\text{defining} 	& 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 1 \\
+\text{inequalities}	& 0 & 0 & -1 & 1 & 1 & 0 & 0 & 0 & -1 \\
  					& 0 & 0 & 1 & -1 & 0 & 0 & 0 & 1 & 0 \\
@@
 \text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{-1}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{0}{2}{-1} & \compactVector{0}{1}{-1} & \compactVector{-1}{1}{0} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} & \compactVector{-2}{0}{1} & \compactVector{-1}{0}{0}  \\[.6cm]
-\text{linearity}	& 1 & 1 & 2 & 1 & 0 & 0 & -1 & 0 & -1 & -2 & 0 & -1 \\
-\text{space}		& 0 & 1 & 0 & 0 & -1 & 2 & 1 & 1 & -1 & 0 & 0 & 0 \\
-					& 0 & 0 & -1 & -1 & 0 & 1 & 1 & 0 & 0 & 1 & -1 & 0 \\[.2cm]
-\text{inequalities} & 0 & 0 & 0 & 0 & 0 & 1 & 0 & -2 & 0 & 0 & 1 & 0 \\
-					& 0 & 1 & 0 & 0 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 1 \\
-					& 0 & -1 & 0 & 1 & 0 & 0 & 0 & 1 & 0 & 0 & -1 & 0 \\
+%\text{linearity}	& 1 & 1 & 2 & 1 & 0 & 0 & -1 & 0 & -1 & -2 & 0 & -1 \\
+%\text{space}		& 0 & 1 & 0 & 0 & -1 & 2 & 1 & 1 & -1 & 0 & 0 & 0 \\
+%					& 0 & 0 & -1 & -1 & 0 & 1 & 1 & 0 & 0 & 1 & -1 & 0 \\[.2cm]
+\text{facet}		& 0 & 0 & 0 & 0 & 0 & 1 & 0 & -2 & 0 & 0 & 1 & 0 \\
+\text{defining}		& 0 & 1 & 0 & 0 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 1 \\
+\text{inequalities}	& 0 & -1 & 0 & 1 & 0 & 0 & 0 & 1 & 0 & 0 & -1 & 0 \\
 					& -1 & 0 & 0 & 0 & 1 & 0 & 1 & 0 & 0 & -1 & 0 & 0 \\
@@
 \[
-\begin{array}{r|cccccccc}
+\begin{array}{r|ccccccccc}
 \text{walks} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA1}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA2}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA3}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA4}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA5}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA6}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA7}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA8}} \\[.6cm]
 \text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{0}{1}{-1} & \compactVector{-1}{0}{0} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} \\[.6cm]
-\text{linearity}	& 0 & -1 & 0 & 1 & -1 & 0 & 1 & 0 \\
-\text{space}		& 1 & 1 & 0 & 0 & 1 & -1 & -1 & 0 \\
-					& 0 & 0 & 1 & 0 & -1 & 0 & 0 & -1 \\[.2cm]
-\text{inequalities} & -1 & 0 & 0 & 1 & 1 & 0 & 0 & -1 \\
-					& 1 & 0 & 0 & -1 & 0 & 0 & 1 & 0 \\
-					& 0 & -1 & 1 & 0 & 1 & 0 & 0 & 0 \\
-					& 0 & 0 & 0 & 1 & 0 & 1 & -1 & 0 \\
-					& 0 & 1 & 0 & 0 & -1 & 0 & 0 & 1 \\[.2cm]
+%\text{linearity}	& 0 & -1 & 0 & 1 & -1 & 0 & 1 & 0 \\
+%\text{space}		& 1 & 1 & 0 & 0 & 1 & -1 & -1 & 0 \\
+%					& 0 & 0 & 1 & 0 & -1 & 0 & 0 & -1 \\[.2cm]
+\text{facet}		& 0 & -1 & 1 & 0 & 1 & 0 & 0 & 0 & \red \circled{A} \\
+\text{defining}		& 0 & 1 & 0 & 0 & -1 & 0 & 0 & 1 & \red \circled{B} \\
+\text{inequalities}	& -1 & 0 & 0 & 1 & 1 & 0 & 0 & -1 & \red \circled{C} \\
+					& 1 & 0 & 0 & -1 & 0 & 0 & 1 & 0 & \red \circled{D} \\
+					& 0 & 0 & 0 & 1 & 0 & 1 & -1 & 0 & \red \circled{E} \\[.2cm]
 \end{array}
@@
 \[
-\begin{array}{r|c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c}
+\begin{array}{r|c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}cc}
 \text{walks} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB1}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB2}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB3}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB4}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB5}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB6}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB7}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB8}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB9}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB10}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB11}} \\[.6cm]
 \text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{1}{0}{-1} & \compactVector{0}{-1}{1} & \compactVector{0}{1}{-1} & \compactVector{-1}{0}{1} & \compactVector{-1}{0}{0} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} \\[.6cm]
-\text{linearity}	& 0 & -1 & 0 & 1 & 0 & 1 & -1 & 0 & 0 & 1 & 0 \\
-\text{space}		& 1 & 0 & 0 & 1 & 1 & 0 & 0 & -1 & -1 & 0 & 0 \\
-					& 1 & 0 & 1 & 1 & 0 & 1 & -1 & 0 & -1 & 0 & -1 \\[.2cm]
-\text{inequalities} & 0 & 0 & 0 & 1 & 0 & -1 & 0 & 1 & 0 & 0 & 0 \\
-					& -1 & 1 & 0 & 0 & 1 & 0 & -1 & 0 & 0 & 0 & 0 \\
-					& 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 0 & 0 & 1 \\
-					& 1 & 0 & -1 & -1 & 0 & 1 & 0 & 0 & 0 & 0 & 0 \\
-					& 0 & 0 & 0 & 1 & -1 & 0 & 1 & 0 & 0 & 0 & 0 \\
-					& 0 & 0 & 1 & 0 & 0 & -1 & 0 & 0 & 0 & 1 & 0 \\
-					& 0 & 0 & 0 & 0 & 0 & 1 & 0 & -1 & 1 & -1 & 0 \\
-					& 0 & 0 & 0 & -1 & 1 & 0 & 0 & 0 & 0 & 1 & -1 \\
-					& 0 & -1 & 0 & 0 & 0 & 0 & 1 & 1 & -1 & 0 & 0 \\[.2cm]
+%\text{linearity}	& 0 & -1 & 0 & 1 & 0 & 1 & -1 & 0 & 0 & 1 & 0 \\
+%\text{space}		& 1 & 0 & 0 & 1 & 1 & 0 & 0 & -1 & -1 & 0 & 0 \\
+%					& 1 & 0 & 1 & 1 & 0 & 1 & -1 & 0 & -1 & 0 & -1 \\[.2cm]
+\text{facet}		& -1 & 1 & 0 & 0 & 1 & 0 & -1 & 0 & 0 & 0 & 0 & \red \circled{A} \\
+\text{defining}		& 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 0 & 0 & 1 & \red \circled{B} \\
+\text{inequalities}	& 0 & 0 & 0 & 1 & -1 & 0 & 1 & 0 & 0 & 0 & 0 & \red \circled{C} \\
+					& 1 & 0 & -1 & -1 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & \red \circled{D} \\
+					& 0 & 0 & 0 & -1 & 1 & 0 & 0 & 0 & 0 & 1 & -1 & \red \circled{E} \\
+					& 0 & 0 & 1 & 0 & 0 & -1 & 0 & 0 & 0 & 1 & 0 & \red \circled{F}\\
+					& 0 & 0 & 0 & 1 & 0 & -1 & 0 & 1 & 0 & 0 & 0 & \red \circled{G} \\
+					& 0 & 0 & 0 & 0 & 0 & 1 & 0 & -1 & 1 & -1 & 0 & \red \circled{H} \\
+					& 0 & -1 & 0 & 0 & 0 & 0 & 1 & 1 & -1 & 0 & 0 & \red \circled{K} \\[.2cm]
 \end{array}
@@
 % A line in the direction (1, 1, 0, 1, -1, 0, 0, 1, -1, 0, -1))
-\vincent{Todo}
-\vincent{Pictures AR quivers + labeling of meshes reported on the inequalities.}
+
+%\begin{figure}
+%\begin{adjustbox}{center}
+%\begin{tikzpicture}
+%	\matrix (m) [matrix of math nodes, row sep=.15cm, column sep=.3cm, nodes={anchor=center, align=center, inner sep=0pt}]{
+%		&&&& \includegraphics[scale=.5]{walkA11} && \\
+%		& \includegraphics[scale=.5]{walkA9} && \includegraphics[scale=.5]{walkA1} & \circled{D} & \includegraphics[scale=.5]{walkA7} & \\
+%		\includegraphics[scale=.5]{walkA3} & \circled{A} & \includegraphics[scale=.5]{walkA5} & \circled{C} & \includegraphics[scale=.5]{walkA4} & \circled{E} & \includegraphics[scale=.5]{walkA6} \\
+%		& \includegraphics[scale=.5]{walkA2} & \circled{B} & \includegraphics[scale=.5]{walkA8} && \includegraphics[scale=.5]{walkA12} & \\
+%		&& \includegraphics[scale=.5]{walkA10} &&&& \\};
+%	\draw[->] (m-3-1) -- (m-2-2);
+%	\draw[->] (m-3-1) -- (m-4-2);
+%	\draw[->] (m-2-2) -- (m-3-3);
+%	\draw[->] (m-4-2) -- (m-3-3);
+%	\draw[->] (m-4-2) -- (m-5-3);
+%	\draw[->] (m-3-3) -- (m-2-4);
+%	\draw[->] (m-3-3) -- (m-4-4);
+%	\draw[->] (m-5-3) -- (m-4-4);
+%	\draw[->] (m-2-4) -- (m-1-5);
+%	\draw[->] (m-2-4) -- (m-3-5);
+%	\draw[->] (m-4-4) -- (m-3-5);
+%	\draw[->] (m-1-5) -- (m-2-6);
+%	\draw[->] (m-3-5) -- (m-2-6);
+%	\draw[->] (m-3-5) -- (m-4-6);
+%	\draw[->] (m-2-6) -- (m-3-7);
+%	\draw[->] (m-4-6) -- (m-3-7);
+%\end{tikzpicture}
+%\quad
+%\begin{tikzpicture}
+%	\matrix (m) [matrix of math nodes, row sep=.3cm, column sep=.1cm, nodes={anchor=center, align=center, inner sep=0pt}]{
+%		&&& \includegraphics[scale=.5]{walkB12} &&& \\
+%		&& \includegraphics[scale=.5]{walkB3} & \circled{D} & \includegraphics[scale=.5]{walkB11} && \\
+%		& \includegraphics[scale=.5]{walkB1} & \circled{B} & \includegraphics[scale=.5]{walkB13} & \circled{F} & \includegraphics[scale=.5]{walkB10} & \\
+%		\includegraphics[scale=.5]{walkB2} & \circled{A} & \includegraphics[scale=.5]{walkB5} & \circled{E} & \includegraphics[scale=.5]{walkB6} & \circled{H} & \includegraphics[scale=.5]{walkB9} \\
+%		& \includegraphics[scale=.5]{walkB7} & \circled{C} & \includegraphics[scale=.5]{walkB4} & \circled{G} & \includegraphics[scale=.5]{walkB8} & \\
+%		&& \includegraphics[scale=.5]{walkB14} && \includegraphics[scale=.5]{walkB15} && \\};
+%	\draw[->] (m-4-1) -- (m-3-2);
+%	\draw[->] (m-4-1) -- (m-5-2);
+%	\draw[->] (m-3-2) -- (m-2-3);
+%	\draw[->] (m-3-2) -- (m-4-3);
+%	\draw[->] (m-5-2) -- (m-4-3);
+%	\draw[->] (m-5-2) -- (m-6-3);
+%	\draw[->] (m-2-3) -- (m-1-4);
+%	\draw[->] (m-2-3) -- (m-3-4);
+%	\draw[->] (m-4-3) -- (m-3-4);
+%	\draw[->] (m-4-3) -- (m-5-4);
+%	\draw[->] (m-6-3) -- (m-5-4);
+%	\draw[->] (m-1-4) -- (m-2-5);
+%	\draw[->] (m-3-4) -- (m-2-5);
+%	\draw[->] (m-3-4) -- (m-4-5);
+%	\draw[->] (m-5-4) -- (m-4-5);
+%	\draw[->] (m-5-4) -- (m-6-5);
+%	\draw[->] (m-2-5) -- (m-3-6);
+%	\draw[->] (m-4-5) -- (m-3-6);
+%	\draw[->] (m-4-5) -- (m-5-6);
+%	\draw[->] (m-6-5) -- (m-5-6);
+%	\draw[->] (m-3-6) -- (m-4-7);
+%	\draw[->] (m-5-6) -- (m-4-7);
+%\end{tikzpicture}
+%\end{adjustbox}
+%\end{figure}
+
+\begin{figure}
+\begin{adjustbox}{center}
+\begin{tikzpicture}
+	\matrix (m) [matrix of math nodes, row sep=.15cm, column sep=.3cm, nodes={anchor=center, align=center, inner sep=0pt}]{
+		&&& \includegraphics[scale=.5]{walkA1} & \node (d) {\red \circled{D}}; & \includegraphics[scale=.5]{walkA7} & \\
+		\includegraphics[scale=.5]{walkA3} & \node (a) {\red \circled{A}}; & \includegraphics[scale=.5]{walkA5} & \node (c) {\red \circled{C}}; & \includegraphics[scale=.5]{walkA4} & \node (e) {\red \circled{E}}; & \includegraphics[scale=.5]{walkA6} \\
+		& \includegraphics[scale=.5]{walkA2} & \node (b) {\red \circled{B}}; & \includegraphics[scale=.5]{walkA8} &&& \\};
+	\draw[->] (m-2-1) -- (m-3-2);
+	\draw[->] (m-3-2) -- (m-2-3);
+	\draw[->] (m-2-3) -- (m-1-4);
+	\draw[->] (m-2-3) -- (m-3-4);
+	\draw[->] (m-1-4) -- (m-2-5);
+	\draw[->] (m-3-4) -- (m-2-5);
+	\draw[->] (m-2-5) -- (m-1-6);
+	\draw[->] (m-1-6) -- (m-2-7);
+	\draw[red] (a) -- (m-2-1);
+	\draw[red] (a) -- (m-2-3);
+	\draw[red] (a) -- (m-3-2);
+	\draw[red] (b) -- (m-3-2);
+	\draw[red] (b) -- (m-3-4);
+	\draw[red] (b) -- (m-2-3);
+	\draw[red] (c) -- (m-2-3);
+	\draw[red] (c) -- (m-2-5);
+	\draw[red] (c) -- (m-1-4);
+	\draw[red] (c) -- (m-3-4);
+	\draw[red] (d) -- (m-1-4);
+	\draw[red] (d) -- (m-1-6);
+	\draw[red] (d) -- (m-2-5);
+	\draw[red] (e) -- (m-2-5);
+	\draw[red] (e) -- (m-2-7);
+	\draw[red] (e) -- (m-1-6);
+\end{tikzpicture}
+\quad
+\begin{tikzpicture}
+	\matrix (m) [matrix of math nodes, row sep=.3cm, column sep=.1cm, nodes={anchor=center, align=center, inner sep=0pt}]{
+		&& \includegraphics[scale=.5]{walkB3} && \includegraphics[scale=.5]{walkB11} && \\
+		& \includegraphics[scale=.5]{walkB1} & \node (b) {\red \circled{B}}; && \node (f) {\red \circled{F}}; & \includegraphics[scale=.5]{walkB10} & \\
+		\includegraphics[scale=.5]{walkB2} & \node (a) {\red \circled{A}}; & \includegraphics[scale=.5]{walkB5} & \node (d) at (-.3,.3) {\red \circled{D}}; \node (e) at (.3,.3) {\red \circled{E}}; & \includegraphics[scale=.5]{walkB6} & \node (h) {\red \circled{H}}; & \includegraphics[scale=.5]{walkB9} \\
+		\node (k1) {\red \circled{K}}; & \includegraphics[scale=.5]{walkB7} & \node (c) {\red \circled{C}}; & \includegraphics[scale=.5]{walkB4} & \node (g) {\red \circled{G}}; & \includegraphics[scale=.5]{walkB8} & \node (k2) {\red \circled{K}}; \\};
+	\draw[->] (m-3-1) -- (m-2-2);
+	\draw[->] (m-3-1) -- (m-4-2);
+	\draw[->] (m-2-2) -- (m-1-3);
+	\draw[->] (m-2-2) -- (m-3-3);
+	\draw[->] (m-4-2) -- (m-3-3);
+	\draw[->] (m-1-3) -- (m-3-5);
+	\draw[->] (m-3-3) -- (m-1-5);
+	\draw[->] (m-3-3) -- (m-4-4);
+	\draw[->] (m-4-4) -- (m-3-5);
+	\draw[->] (m-1-5) -- (m-2-6);
+	\draw[->] (m-3-5) -- (m-2-6);
+	\draw[->] (m-3-5) -- (m-4-6);
+	\draw[->] (m-2-6) -- (m-3-7);
+	\draw[->] (m-4-6) -- (m-3-7);
+	\draw[red] (a) -- (m-3-1);
+	\draw[red] (a) -- (m-3-3);
+	\draw[red] (a) -- (m-2-2);
+	\draw[red] (a) -- (m-4-2);
+	\draw[red] (b) -- (m-2-2);
+	\draw[red] (b) -- (m-1-5);
+	\draw[red] (b) -- (m-3-3);
+	\draw[red] (c) -- (m-4-2);
+	\draw[red] (c) -- (m-4-4);
+	\draw[red] (c) -- (m-3-3);
+	\draw[red] (d) -- (m-2-2);
+	\draw[red] (d) -- (m-3-5.200);
+	\draw[red] (d) -- (m-1-3);
+	\draw[red] (d) -- (m-4-4);
+	\draw[red] (e) -- (m-3-3.340);
+	\draw[red] (e) -- (m-2-6);
+	\draw[red] (e) -- (m-4-4);
+	\draw[red] (e) -- (m-1-5);
+	\draw[red] (f) -- (m-1-3);
+	\draw[red] (f) -- (m-2-6);
+	\draw[red] (f) -- (m-3-5);
+	\draw[red] (g) -- (m-4-4);
+	\draw[red] (g) -- (m-4-6);
+	\draw[red] (g) -- (m-3-5);
+	\draw[red] (h) -- (m-3-5);
+	\draw[red] (h) -- (m-3-7);
+	\draw[red] (h) -- (m-2-6);
+	\draw[red] (h) -- (m-4-6);
+	\draw[red] (k1) -- (m-3-1);
+	\draw[red] (k1) -- (m-4-2);
+	\draw[red, densely dotted] (k1.west) -- ([xshift=-.3cm]k1.west);
+	\draw[red, densely dotted] (k1.south) -- ([yshift=-.3cm]k1.south);
+	\draw[red] (k2) -- (m-4-6);
+	\draw[red] (k2) -- (m-3-7);
+	\draw[red, densely dotted] (k2.east) -- ([xshift=.3cm]k2.east);
+	\draw[red, densely dotted] (k2.south) -- ([yshift=-.3cm]k2.south);
+\end{tikzpicture}
+\end{adjustbox}
+\end{figure}
 \end{example}
@@
 %	\centerline{\includegraphics[scale=1.2]{fourEqualities}}
-	\centerline{
+	\begin{adjustbox}{center}
     	\begin{tabular}{c@{\qquad}c}
@@
     	\end{tabular}
-	}
+	\end{adjustbox}
 	\caption{Schematic representation of the four equalities in the proof of \cref{prop:extremalExchangeablePairsNKC}.}
@@
 	\capstart
-	\centerline{
+	\begin{adjustbox}{center}
 		\begin{tabular}{c@{\;}c@{\;}c@{\;}c}
@@
 		\end{tabular}
-	}
+	\end{adjustbox}
 	\caption{Some classical families of polytopes as graph associahedra. Illustration from~\cite{MannevillePilaud-compatibilityFans}.}
@@
 \text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{0}{2}{-1} & \compactVector{\nicefrac{1}{2}}{-1}{\nicefrac{1}{2}} & \compactVector{1}{-2}{0} & \compactVector{\nicefrac{1}{2}}{0}{\nicefrac{-1}{2}} & \compactVector{-1}{2}{0} & \compactVector{\nicefrac{-1}{2}}{0}{\nicefrac{1}{2}} & \compactVector{-1}{0}{0} & \compactVector{0}{-2}{1} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} \\[.6cm]
-
-\text{linearity}	& 1 & 0 & 0 & 0 & 2 & 1 & 2 & -1 & -2 & -1 & 0 & 0 & 0 \\ 
-\text{space}		& -2 & -1 & 0 & -2 & 0 & 0 & -4 & 0 & 4 & 2 & 2 & 1 & 0 \\
-					& 0 & 0 & -1 & 1 & -2 & 0 & 2 & 0 & -2 & 0 & -1 & 0 & 1 \\[.2cm]
-\text{inequalities} & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & -2 & 1 \\
-					& 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 & 0 & 1 & 0 & -2 & 0 \\
-					& -1 & 2 & 0 & -1 & 0 & 0 & 2 & 0 & 0 & 0 & 0 & 0 & 0 \\
+%\text{linearity}	& 1 & 0 & 0 & 0 & 2 & 1 & 2 & -1 & -2 & -1 & 0 & 0 & 0 \\ 
+%\text{space}		& -2 & -1 & 0 & -2 & 0 & 0 & -4 & 0 & 4 & 2 & 2 & 1 & 0 \\
+%					& 0 & 0 & -1 & 1 & -2 & 0 & 2 & 0 & -2 & 0 & -1 & 0 & 1 \\[.2cm]
+\text{facet}		& 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & -2 & 1 \\
+\text{defining}		& 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 & 0 & 1 & 0 & -2 & 0 \\
+\text{inequalities}	& -1 & 2 & 0 & -1 & 0 & 0 & 2 & 0 & 0 & 0 & 0 & 0 & 0 \\
 					& 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 2 & -1 & -1 & 2 & 0 \\
@@
 \text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{\nicefrac{1}{2}}{-1}{\nicefrac{1}{2}} & \compactVector{1}{-2}{0} & \compactVector{-1}{2}{0} & \compactVector{\nicefrac{-1}{2}}{0}{\nicefrac{1}{2}} & \compactVector{-1}{0}{0} & \compactVector{0}{-2}{1} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} \\[.6cm]
-\text{linearity}	& 0 & 1 & 0 & -4 & -2 & 2 & 0 & 0 & -2 & -1 & 0 \\
-\text{space}		& 1 & 0 & 0 & 2 & 1 & -1 & -2 & -1 & 0 & 0 & 0 \\
-					& 1 & 0 & 1 & 4 & 1 & -1 & 0 & -1 & 1 & 0 & -1 \\[.2cm]
-\text{inequalities} & -1 & 2 & -1 & 2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-					& 1 & -2 & 0 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 \\
-					& 0 & 2 & -1 & 0 & 0 & -1 & 2 & 0 & 0 & 0 & 0 \\
+%\text{linearity}	& 0 & 1 & 0 & -4 & -2 & 2 & 0 & 0 & -2 & -1 & 0 \\
+%\text{space}		& 1 & 0 & 0 & 2 & 1 & -1 & -2 & -1 & 0 & 0 & 0 \\
+%					& 1 & 0 & 1 & 4 & 1 & -1 & 0 & -1 & 1 & 0 & -1 \\[.2cm]
+\text{facet}		& -1 & 2 & -1 & 2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+\text{defining}		& 1 & -2 & 0 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 \\
+\text{inequalities}	& 0 & 2 & -1 & 0 & 0 & -1 & 2 & 0 & 0 & 0 & 0 \\
 					& 1 & 0 & 0 & -2 & 0 & 0 & 0 & 0 & 1 & 0 & 0 \\

### 2019-04-05 thirdPaper/draft/typeConeAssociahedra.tex
AR quivers cluster algebras

@@
 \usetikzlibrary{trees, decorations, decorations.markings, shapes, arrows, matrix, calc, fit, intersections, patterns, angles}
-\graphicspath{{figures/}{figures/walks/}{figures/tubes/}}
+\graphicspath{{figures/}{figures/diagonals/}{figures/walks/}{figures/tubes/}}
 \makeatletter\def\input@path{{figures/}}\makeatother
@@
 \newcommand{\pa}{_{\textrm{pa}}} % path
-\newcommand*\circled[1]{\tikz[baseline=(char.base)]{\node[shape=circle,draw,inner sep=1pt, scale=.7] (char) {#1};}}
+\newcommand*\circled[1]{\tikz[baseline=(char.base)]{\node[shape=circle, draw, inner sep=1.5pt, scale=.7] (char) {#1};}}
 \newcommand{\compactVector}[3]{\begin{bmatrix} #1 \\[-.1cm] #2 \\[-.1cm] #3 \end{bmatrix}}
@@
 \subsection{Classical associahedra}
+\label{subsec:typeConeAsso}
 
@@
 
+\begin{figure}[h]
+	\capstart
+	\centerline{\raisebox{.5cm}{\includegraphics[scale=.45]{lodayFan2}}\hspace{1.5cm}\includegraphics[scale=.45]{lodayFan3}}
+	\caption{The normal fans~$\gvectorFan[2]$ and~$\gvectorFan[3]$ of J.-L.~Loday's associahedra.
+As the rightmost fan is $3$-dimensional, we intersect it with the sphere and stereographically project it from the direction~$(-1,-1,-1)$.}
+	\label{fig:lodayFans}
+\end{figure}
+
+These fans are illustrated in \cref{fig:lodayFans} in dimension~$2$ and~$3$.
 Let us also recall the linear dependencies in this fan and observe that it has the unique exchange property discussed in \cref{subsec:uniqueExchangeProperty}.
@@
 
+\begin{example}
+Consider the fan~$\gvectorFan[2]$ and~$\gvectorFan[3]$ illustrated in \cref{fig:lodayFans}.
+The type cone of~$\gvectorFan[3]$ in~$\R^9$, has a linearity space of dimension~$3$ and $6$ facet defining inequalities (given below).
+
+\[
+\begin{array}{r|cccccccccc}
+\text{diagonals} & \raisebox{-.25cm}{\;\includegraphics[scale=.6]{diagonalB1}}  & \raisebox{-.25cm}{\;\includegraphics[scale=.6]{diagonalB2}} & \raisebox{-.25cm}{\;\includegraphics[scale=.6]{diagonalB3}} & \raisebox{-.25cm}{\;\includegraphics[scale=.6]{diagonalB4}} & \raisebox{-.25cm}{\;\includegraphics[scale=.6]{diagonalB5}} & \raisebox{-.25cm}{\;\includegraphics[scale=.6]{diagonalB6}} & \raisebox{-.25cm}{\;\includegraphics[scale=.6]{diagonalB7}} & \raisebox{-.25cm}{\;\includegraphics[scale=.6]{diagonalB8}} & \raisebox{-.25cm}{\;\includegraphics[scale=.6]{diagonalB9}} \\[.3cm]
+\text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{-1}{1}{0} & \compactVector{0}{-1}{1} & \compactVector{-1}{0}{1} & \compactVector{-1}{0}{0} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} \\[.6cm]
+%\text{linearity}	& 0 & 1 & 0 & 1 & 0 & -1 & 0 & -1 & 0 \\
+%\text{space}		& 0 & 1 & 1 & 1 & 1 & 0 & 0 & -1 & -1 \\
+%					& 1 & 1 & 1 & 0 & 0 & 0 & -1 & -1 & -1 \\
+\text{facet}		& 1 & -1 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & \red \circled{A} \\
+\text{defining} 	& 0 & 1 & -1 & -1 & 1 & 0 & 0 & 0 & 0 & \red \circled{B} \\
+\text{inequalities}	& 0 & 0 & 1 & 0 & -1 & 0 & 1 & 0 & 0 & \red \circled{C} \\
+					& 0 & 0 & 0 & 1 & -1 & 1 & 0 & 0 & 0 & \red \circled{D} \\
+					& 0 & 0 & 0 & 0 & 1 & -1 & -1 & 1 & 0 & \red \circled{E} \\
+					& 0 & 0 & 0 & 0 & 0 & 1 & 0 & -1 & 1 & \red \circled{F} \\[.2cm]
+\end{array}
+\]
+
+%sage: B = Matrix([[0,1,0],[-1,0,1],[0,-1,0]])
+%sage: CA = ClusterAlgebra(B)
+%
+%sage: CA.explore_to_depth(infinity)
+%sage: gvectors = CA.cluster_fan().rays()
+%sage: for gvector in gvectors:
+%....:     print gvector, CA.cluster_variable(gvector)
+%....:     
+%N(-1, 1, 0) (x1 + 1)/x0
+%N(1, 0, 0) x0
+%N(0, 0, 1) x2
+%N(0, -1, 1) (x0 + x2)/x1
+%N(0, 0, -1) (x1 + 1)/x2
+%N(-1, 0, 1) (x1*x2 + x0 + x2)/(x0*x1)
+%N(0, -1, 0) (x0*x1 + x0 + x2)/(x1*x2)
+%N(-1, 0, 0) (x0*x1 + x1*x2 + x0 + x2)/(x0*x1*x2)
+%N(0, 1, 0) x1
+%
+%sage: TCCA = type_cone_CA(CA)
+%sage: TCCA
+%A 9-dimensional polyhedron in QQ^9 defined as the convex hull of 1 vertex, 6 rays, 3 lines
+%sage: TCCA.lines()
+%(A line in the direction (1, 0, 0, -1, 0, 0, -1, 0, 1),
+% A line in the direction (1, 0, 1, 0, -1, 1, -1, 0, 1),
+% A line in the direction (0, 1, 1, 0, -1, 0, -1, -1, 1))
+%sage: TCCA.inequalities()
+%(An inequality (-1, 0, -1, 0, 0, 1, 0, 0, 1) x + 0 >= 0,
+% An inequality (1, 1, 0, 0, 0, 0, 0, 0, -1) x + 0 >= 0,
+% An inequality (1, 0, 0, 1, 0, -1, 0, 0, 0) x + 0 >= 0,
+% An inequality (0, 0, 0, -1, 0, 1, 1, -1, 0) x + 0 >= 0,
+% An inequality (0, 0, 1, 0, 0, -1, 0, 1, 0) x + 0 >= 0,
+% An inequality (0, 0, 0, 1, 1, 0, -1, 0, 0) x + 0 >= 0)
+
+\begin{figure}
+    \begin{adjustbox}{center}
+        \begin{tikzpicture}
+        	\matrix (m) [matrix of math nodes, row sep=.35cm, column sep=.2cm, nodes={anchor=center, align=center, inner sep=0pt}]{
+        		& \;\includegraphics[scale=.6]{diagonalA2} & \node (b) {\red \circled{B}}; & \;\includegraphics[scale=.6]{diagonalA4} & \\
+        		\;\includegraphics[scale=.6]{diagonalA1} & \node (a) {\red \circled{A}}; & \;\includegraphics[scale=.6]{diagonalA3} & \node (c) {\red \circled{C}}; & \;\includegraphics[scale=.6]{diagonalA5} \\};
+        	\draw[->] (m-2-1) -- (m-1-2);
+        	\draw[->] (m-1-2) -- (m-2-3);
+        	\draw[->] (m-2-3) -- (m-1-4);
+        	\draw[->] (m-1-4) -- (m-2-5);
+        	\draw[red] (a) -- (m-2-1);
+        	\draw[red] (a) -- (m-2-3);
+        	\draw[red] (a) -- (m-1-2);
+        	\draw[red] (b) -- (m-1-2);
+        	\draw[red] (b) -- (m-1-4);
+        	\draw[red] (b) -- (m-2-3);
+        	\draw[red] (c) -- (m-2-3);
+        	\draw[red] (c) -- (m-2-5);
+        	\draw[red] (c) -- (m-1-4);
+        \end{tikzpicture}
+        \quad
+        \begin{tikzpicture}
+        	\matrix (m) [matrix of math nodes, row sep=.35cm, column sep=.2cm, nodes={anchor=center, align=center, inner sep=0pt}]{
+        		&& \;\includegraphics[scale=.6]{diagonalB3} & \node (c) {\red \circled{C}}; & \;\includegraphics[scale=.6]{diagonalB7} && \\
+        		& \;\includegraphics[scale=.6]{diagonalB2} & \node (b) {\red \circled{B}}; & \;\includegraphics[scale=.6]{diagonalB5} & \node (e) {\red \circled{E}}; & \;\includegraphics[scale=.6]{diagonalB8} & \\
+        		\;\includegraphics[scale=.6]{diagonalB1} & \node (a) {\red \circled{A}}; & \;\includegraphics[scale=.6]{diagonalB4} & \node (d) {\red \circled{D}}; & \;\includegraphics[scale=.6]{diagonalB6} & \node (f) {\red \circled{F}}; & \;\includegraphics[scale=.6]{diagonalB9} \\};
+        	\draw[->] (m-3-1) -- (m-2-2);
+        	\draw[->] (m-2-2) -- (m-1-3);
+        	\draw[->] (m-2-2) -- (m-3-3);
+        	\draw[->] (m-1-3) -- (m-2-4);
+        	\draw[->] (m-3-3) -- (m-2-4);
+        	\draw[->] (m-2-4) -- (m-1-5);
+        	\draw[->] (m-2-4) -- (m-3-5);
+        	\draw[->] (m-1-5) -- (m-2-6);
+        	\draw[->] (m-3-5) -- (m-2-6);
+        	\draw[->] (m-2-6) -- (m-3-7);
+        	\draw[red] (a) -- (m-3-1);
+        	\draw[red] (a) -- (m-3-3);
+        	\draw[red] (a) -- (m-2-2);
+        	\draw[red] (b) -- (m-2-2);
+        	\draw[red] (b) -- (m-2-4);
+        	\draw[red] (b) -- (m-1-3);
+        	\draw[red] (b) -- (m-3-3);
+        	\draw[red] (c) -- (m-1-3);
+        	\draw[red] (c) -- (m-1-5);
+        	\draw[red] (c) -- (m-2-4);
+        	\draw[red] (d) -- (m-3-3);
+        	\draw[red] (d) -- (m-3-5);
+        	\draw[red] (d) -- (m-2-4);
+        	\draw[red] (e) -- (m-2-4);
+        	\draw[red] (e) -- (m-2-6);
+        	\draw[red] (e) -- (m-1-5);
+        	\draw[red] (e) -- (m-3-5);
+        	\draw[red] (f) -- (m-3-5);
+        	\draw[red] (f) -- (m-3-7);
+        	\draw[red] (f) -- (m-2-6);
+        \end{tikzpicture}
+    \end{adjustbox}
+	\caption{The facet defining inequalities of the type cone~$\typeCone(\gvectorFan[n])$ correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso}.
+See \cref{subsec:typeConeCA,sec:clusterCategories} for a representation theoretic \mbox{interpretation}.}
+\end{figure}
+\end{example}
+
 We now describe the facets of this type cone~$\typeCone(\gvectorFan[n])$.
@@
 \subsection{Finite type cluster complexes and generalized associahedra}
+\label{subsec:typeConeCA}
 
@@
 Consider the cluster fans illustrated in \cref{fig:clusterFans}.
-The type cone of the left fan lives in~$\R^9$, has a linearity space of dimension~$3$ (a basis is given below) and $6$ facet defining inequalities (given below).
-
-\[
-\begin{array}{r|ccccccccc}
+The type cone of the left fan lives in~$\R^9$, has a linearity space of dimension~$3$ and $6$ facet defining inequalities (given below).
+
+\[
+\begin{array}{r|cccccccccc}
 \text{variables} & \rotatebox{70}{$x_1$} & \rotatebox{70}{$x_2$} & \rotatebox{70}{$x_3$} & \rotatebox{70}{$\frac{x_2 + x_3}{x_1}$} & \rotatebox{70}{$\frac{x_1 + x_3}{x_2}$} & \rotatebox{70}{$\frac{x_1 + x_2}{x_3}$} & \rotatebox{70}{$\frac{x_1 + x_2 + x_3}{x_2 x_3}$} & \rotatebox{70}{$\frac{x_1 + x_2 + x_3}{x_1 x_3}$} & \rotatebox{70}{$\frac{x_1 + x_2 + x_3}{x_1 x_2}$} \\[.2cm]
@@
 %					& 1 & 1 & 0 & -1 & 0 & 1 & 0 & -1 & -1 \\[.2cm]
-\text{facet}		& -1 & 0 & 0 & 0 & 1 & 1 & -1 & 0 & 0 \\
-\text{defining} 	& 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 1 \\
-\text{inequalities}	& 0 & 0 & -1 & 1 & 1 & 0 & 0 & 0 & -1 \\
- 					& 0 & 0 & 1 & -1 & 0 & 0 & 0 & 1 & 0 \\
- 					& 0 & 1 & 0 & 0 & 0 & -1 & 1 & 0 & 0 \\
- 					& 0 & -1 & 0 & 1 & 0 & 1 & 0 & -1 & 0 \\[.2cm]
+\text{facet} 		& 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 1 & \red \circled{A} \\
+\text{defining}		& 0 & 0 & -1 & 1 & 1 & 0 & 0 & 0 & -1 & \red \circled{B} \\
+\text{inequalities}	& 0 & 0 & 1 & -1 & 0 & 0 & 0 & 1 & 0 & \red \circled{C} \\
+ 					& 0 & -1 & 0 & 1 & 0 & 1 & 0 & -1 & 0 & \red \circled{D} \\
+ 					& 0 & 1 & 0 & 0 & 0 & -1 & 1 & 0 & 0 & \red \circled{E} \\
+					& -1 & 0 & 0 & 0 & 1 & 1 & -1 & 0 & 0 & \red \circled{F} \\[.2cm]
 \end{array}
@@
 \noindent
-The type cone of the right fan lives in~$\R^{12}$, has a linearity space of dimension~$3$ (a basis is given below) and $9$ facet defining inequalities (given below).
+The type cone of the right fan lives in~$\R^{12}$, has a linearity space of dimension~$3$ and $9$ facet defining inequalities (given below).
 
@@
 % An inequality (0, 0, 0, 1, 1, 0, 0, -2, 0, 0, 0, 0) x + 0 >= 0)
+
+\begin{figure}
+    \begin{adjustbox}{center}
+%        \begin{tikzpicture}
+%        	\matrix (m) [matrix of math nodes, row sep=.35cm, column sep=.2cm, nodes={anchor=center, align=center, inner sep=0pt}]{
+%        		& \;\includegraphics[scale=.6]{diagonalA2} & \node (b) {\red \circled{B}}; & \;\includegraphics[scale=.6]{diagonalA4} & \\
+%        		\;\includegraphics[scale=.6]{diagonalA1} & \node (a) {\red \circled{A}}; & \;\includegraphics[scale=.6]{diagonalA3} & \node (c) {\red \circled{C}}; & \;\includegraphics[scale=.6]{diagonalA5} \\};
+%        	\draw[->] (m-2-1) -- (m-1-2);
+%        	\draw[->] (m-1-2) -- (m-2-3);
+%        	\draw[->] (m-2-3) -- (m-1-4);
+%        	\draw[->] (m-1-4) -- (m-2-5);
+%        	\draw[red] (a) -- (m-2-1);
+%        	\draw[red] (a) -- (m-2-3);
+%        	\draw[red] (a) -- (m-1-2);
+%        	\draw[red] (b) -- (m-1-2);
+%        	\draw[red] (b) -- (m-1-4);
+%        	\draw[red] (b) -- (m-2-3);
+%        	\draw[red] (c) -- (m-2-3);
+%        	\draw[red] (c) -- (m-2-5);
+%        	\draw[red] (c) -- (m-1-4);
+%        \end{tikzpicture}
+%        \quad
+		\newcommand{\fitClusterVariable}[1]{\parbox[c][.7cm][c]{1.5cm}{\centering $#1$}}
+        \begin{tikzpicture}
+        	\matrix (m) [matrix of math nodes, row sep=.4cm, column sep=-.1cm, nodes={anchor=center, align=center, inner sep=0pt}]{
+        		\fitClusterVariable{\phantom{1}} & \node (e1) {\red \circled{E}}; & \fitClusterVariable{\frac{x_1 + x_2 + x_3}{x_2 x_3}} && \fitClusterVariable{x_3} & \node (c) {\red \circled{C}}; & \fitClusterVariable{\frac{x_1 + x_2 + x_3}{x_1 x_3}} && \fitClusterVariable{x_1} & \node (a2) {\red \circled{A}}; & \fitClusterVariable{\phantom{1}} \\
+        		& \fitClusterVariable{\frac{x_1 + x_2}{x_3}} & \node (f1) {\red \circled{F}}; & \fitClusterVariable{\frac{x_1 + x_3}{x_2}} & \node (b) {\red \circled{B}}; & \fitClusterVariable{\frac{x_2 + x_3}{x_1}} & \node (d) {\red \circled{D}}; & \fitClusterVariable{\frac{x_1 + x_2}{x_3}} & \node (f2) {\red \circled{F}}; & \fitClusterVariable{\frac{x_1 + x_3}{x_2}} \\
+        		\fitClusterVariable{\phantom{1}} && \fitClusterVariable{x_1} & \node (a1) {\red \circled{A}}; & \fitClusterVariable{\frac{x_1 + x_2 + x_3}{x_1 x_2}} && \fitClusterVariable{x_2} & \node (e2) {\red \circled{E}}; & \fitClusterVariable{\frac{x_1 + x_2 + x_3}{x_2 x_3}} && \fitClusterVariable{\phantom{1}} \\};
+        	\draw[->] (m-2-2) -- (m-1-3);
+        	\draw[->] (m-2-2) -- (m-3-3);
+        	\draw[->] (m-1-3) -- (m-2-4);
+        	\draw[->] (m-3-3) -- (m-2-4);
+        	\draw[->] (m-2-4) -- (m-1-5);
+        	\draw[->] (m-2-4) -- (m-3-5);
+        	\draw[->] (m-1-5) -- (m-2-6);
+        	\draw[->] (m-3-5) -- (m-2-6);
+        	\draw[->] (m-2-6) -- (m-1-7);
+        	\draw[->] (m-2-6) -- (m-3-7);
+        	\draw[->] (m-1-7) -- (m-2-8);
+        	\draw[->] (m-3-7) -- (m-2-8);
+        	\draw[->] (m-2-8) -- (m-1-9);
+        	\draw[->] (m-2-8) -- (m-3-9);
+        	\draw[->] (m-1-9) -- (m-2-10);
+        	\draw[->] (m-3-9) -- (m-2-10);
+        	\draw[densely dotted, thick] (m-1-1) -- (m-2-2);
+        	\draw[densely dotted, thick] (m-3-1) -- (m-2-2);
+        	\draw[densely dotted, thick] (m-2-10) -- (m-1-11);
+        	\draw[densely dotted, thick] (m-2-10) -- (m-3-11);
+        	\draw[red] (a1) -- (m-3-3);
+        	\draw[red] (a1) -- (m-3-5);
+        	\draw[red] (a1) -- (m-2-4);
+        	\draw[red] (a2) -- (m-1-9);
+        	\draw[red, densely dotted, thick] (a2) -- (m-1-11);
+        	\draw[red] (a2) -- (m-2-10);
+        	\draw[red] (b) -- (m-2-4);
+        	\draw[red] (b) -- (m-2-6);
+        	\draw[red] (b) -- (m-1-5);
+        	\draw[red] (b) -- (m-3-5);
+        	\draw[red] (c) -- (m-1-5);
+        	\draw[red] (c) -- (m-1-7);
+        	\draw[red] (c) -- (m-2-6);
+        	\draw[red] (d) -- (m-2-6);
+        	\draw[red] (d) -- (m-2-8);
+        	\draw[red] (d) -- (m-1-7);
+        	\draw[red] (d) -- (m-3-7);
+        	\draw[red, densely dotted, thick] (e1) -- (m-1-1);
+        	\draw[red] (e1) -- (m-1-3);
+        	\draw[red] (e1) -- (m-2-2);
+        	\draw[red] (e2) -- (m-3-7);
+        	\draw[red] (e2) -- (m-3-9);
+        	\draw[red] (e2) -- (m-2-8);
+        	\draw[red] (f1) -- (m-2-2);
+        	\draw[red] (f1) -- (m-2-4);
+        	\draw[red] (f1) -- (m-1-3);
+        	\draw[red] (f1) -- (m-3-3);
+        	\draw[red] (f2) -- (m-2-8);
+        	\draw[red] (f2) -- (m-2-10);
+        	\draw[red] (f2) -- (m-1-9);
+        	\draw[red] (f2) -- (m-3-9);
+        \end{tikzpicture}
+    \end{adjustbox}
+	\caption{}%The facet defining inequalities of the type cone~$\typeCone(\gvectorFan[])$ correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso}.
+See \cref{subsec:typeConeCA,sec:clusterCategories} for a representation theoretic \mbox{interpretation}.}
+\end{figure}
 \end{example}
@@
 \subsection{Non-kissing complexes and gentle associahedra}
+\label{subsec:typeConeNKC}
 
@@
 Consider the non-kissing fans illustrated in \cref{fig:nonkissingFans}.
-The type cone of the left fan lives in~$\R^9$, has a linearity space of dimension~$3$ (a basis is given below) and $6$ facet defining inequalities (given below).
+The type cone of the left fan lives in~$\R^9$, has a linearity space of dimension~$3$ and $6$ facet defining inequalities (given below).
 
@@
 \noindent
-The type cone of the right fan lives in~$\R^{11}$, has a linearity space of dimension~$3$ (a basis is given below) and $9$ facet defining inequalities (given below).
-In particular, it is not simplicial.
+The type cone of the right fan lives in~$\R^{11}$, has a linearity space of dimension~$3$ and $9$ facet defining inequalities (given below). In particular, it is not simplicial.
 
@@
         	\draw[red] (k1) -- (m-4-2);
-	\draw[red, densely dotted] (k1.west) -- ([xshift=-.3cm]k1.west);
-	\draw[red, densely dotted] (k1.south) -- ([yshift=-.3cm]k1.south);
+        	\draw[red, densely dotted, thick] (k1.west) -- ([xshift=-.3cm]k1.west);
+        	\draw[red, densely dotted, thick] (k1.south) -- ([yshift=-.3cm]k1.south);
         	\draw[red] (k2) -- (m-4-6);
         	\draw[red] (k2) -- (m-3-7);
-	\draw[red, densely dotted] (k2.east) -- ([xshift=.3cm]k2.east);
-	\draw[red, densely dotted] (k2.south) -- ([yshift=-.3cm]k2.south);
+        	\draw[red, densely dotted, thick] (k2.east) -- ([xshift=.3cm]k2.east);
+        	\draw[red, densely dotted, thick] (k2.south) -- ([yshift=-.3cm]k2.south);
         \end{tikzpicture}
     \end{adjustbox}
+	\caption{The facet defining inequalities of the type cone~$\typeCone(\gvectorFan[\quiver])$ represented on the Auslander Reiten quiver of the gentle algebra of~$\quiver$.
+While they correspond to meshes on the left, they are not as clear in the general case as on the right.
+See also \cref{sect::extricats}.}
 \end{figure}
@@
 \subsection{Graphical nested complexes and graph associahedra}
+\label{subsec:typeConeGA}
 
@@
 Consider the nested fans illustrated in \cref{fig:nestedFans}.
-The type cone of the left fan lives in~$\R^{13}$, has a linearity space of dimension~$3$ (a basis is given below) and $19$ facet defining inequalities (given below).
-In particular, it is not simplicial.
+The type cone of the left fan lives in~$\R^{13}$, has a linearity space of dimension~$3$ and $19$ facet defining inequalities (given below). In particular, it is not simplicial.
 
@@
 \begin{array}{r|c@{\;\;\;}c@{\;\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;}c@{\;}c@{\;}c@{\;}c@{\;\;}c@{\;\;}c@{\;\;}c}
-\text{walks} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA1}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA2}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA3}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA4}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA5}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA6}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA7}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA8}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA9}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA10}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA11}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA12}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA13}}  \\[.6cm]
+\text{tubes} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA1}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA2}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA3}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA4}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA5}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA6}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA7}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA8}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA9}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA10}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA11}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA12}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA13}}  \\[.6cm]
 \text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{0}{2}{-1} & \compactVector{\nicefrac{1}{2}}{-1}{\nicefrac{1}{2}} & \compactVector{1}{-2}{0} & \compactVector{\nicefrac{1}{2}}{0}{\nicefrac{-1}{2}} & \compactVector{-1}{2}{0} & \compactVector{\nicefrac{-1}{2}}{0}{\nicefrac{1}{2}} & \compactVector{-1}{0}{0} & \compactVector{0}{-2}{1} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} \\[.6cm]
@@
 
+\vincent{Should only be 1 and -1...}
 \noindent
-The type cone of the right fan lives in~$\R^{11}$, has a linearity space of dimension~$3$ (a basis is given below) and $12$ facet defining inequalities (given below).
-In particular, it is not simplicial.
+The type cone of the right fan lives in~$\R^{11}$, has a linearity space of dimension~$3$ and $12$ facet defining inequalities (given below). In particular, it is not simplicial.
 
@@
 \begin{array}{r|c@{\;\;\;}c@{\;\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;}c@{\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c}
-\text{walks} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB1}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB2}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB3}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB4}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB5}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB6}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB7}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB8}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB9}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB10}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB11}} \\[.6cm]
+\text{tubes} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB1}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB2}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB3}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB4}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB5}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB6}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB7}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB8}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB9}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB10}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB11}} \\[.6cm]
 \text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{\nicefrac{1}{2}}{-1}{\nicefrac{1}{2}} & \compactVector{1}{-2}{0} & \compactVector{-1}{2}{0} & \compactVector{\nicefrac{-1}{2}}{0}{\nicefrac{1}{2}} & \compactVector{-1}{0}{0} & \compactVector{0}{-2}{1} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} \\[.6cm]

### 2019-04-05 thirdPaper/draft/typeConeAssociahedra.tex
type cone associahedra

@@
 \newcommand*\circled[1]{\tikz[baseline=(char.base)]{\node[shape=circle, draw, inner sep=1.5pt, scale=.7] (char) {#1};}}
-\newcommand{\compactVector}[3]{\begin{bmatrix} #1 \\[-.1cm] #2 \\[-.1cm] #3 \end{bmatrix}}
+\newcommand{\compactVectorD}[2]{\begin{bmatrix} #1 \\ #2 \end{bmatrix}}
+\newcommand{\compactVectorT}[3]{\begin{bmatrix} #1 \\[-.1cm] #2 \\[-.1cm] #3 \end{bmatrix}}
 
@@
 Consider the fan~$\gvectorFan[2]$ and~$\gvectorFan[3]$ illustrated in \cref{fig:lodayFans}.
+The type cone of~$\gvectorFan[2]$ in~$\R^5$, has a linearity space of dimension~$2$ and $3$ facet defining inequalities (given below).
+
+\[
+\begin{array}{r|cccccc}
+\text{diagonals} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalA1}}  & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalA2}} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalA3}} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalA4}} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalA5}} \\[.3cm]
+\text{$\b{g}$-vectors} & \compactVectorD{1}{0} & \compactVectorD{0}{1} & \compactVectorD{1}{-1} & \compactVectorD{-1}{0} & \compactVectorD{0}{-1} \\[.6cm]
+\text{facet}		& 1 & -1 & 1 & 0 & 0 & \red \circled{A} \\
+\text{defining} 	& 0 & 1 & -1 & 1 & 0 & \red \circled{B} \\
+\text{inequalities}	& 0 & 0 & 1 & -1 & 1 & \red \circled{C} \\[.2cm]
+\end{array}
+\]
+
+\noindent
 The type cone of~$\gvectorFan[3]$ in~$\R^9$, has a linearity space of dimension~$3$ and $6$ facet defining inequalities (given below).
@@
 \begin{array}{r|cccccccccc}
-\text{diagonals} & \raisebox{-.25cm}{\;\includegraphics[scale=.6]{diagonalB1}}  & \raisebox{-.25cm}{\;\includegraphics[scale=.6]{diagonalB2}} & \raisebox{-.25cm}{\;\includegraphics[scale=.6]{diagonalB3}} & \raisebox{-.25cm}{\;\includegraphics[scale=.6]{diagonalB4}} & \raisebox{-.25cm}{\;\includegraphics[scale=.6]{diagonalB5}} & \raisebox{-.25cm}{\;\includegraphics[scale=.6]{diagonalB6}} & \raisebox{-.25cm}{\;\includegraphics[scale=.6]{diagonalB7}} & \raisebox{-.25cm}{\;\includegraphics[scale=.6]{diagonalB8}} & \raisebox{-.25cm}{\;\includegraphics[scale=.6]{diagonalB9}} \\[.3cm]
-\text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{-1}{1}{0} & \compactVector{0}{-1}{1} & \compactVector{-1}{0}{1} & \compactVector{-1}{0}{0} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} \\[.6cm]
+\text{diagonals} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalB1}}  & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalB2}} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalB3}} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalB4}} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalB5}} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalB6}} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalB7}} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalB8}} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalB9}} \\[.3cm]
+\text{$\b{g}$-vectors} & \compactVectorT{1}{0}{0} & \compactVectorT{0}{1}{0} & \compactVectorT{0}{0}{1} & \compactVectorT{-1}{1}{0} & \compactVectorT{0}{-1}{1} & \compactVectorT{-1}{0}{1} & \compactVectorT{-1}{0}{0} & \compactVectorT{0}{-1}{0} & \compactVectorT{0}{0}{-1} \\[.6cm]
 %\text{linearity}	& 0 & 1 & 0 & 1 & 0 & -1 & 0 & -1 & 0 \\
@@
         	\matrix (m) [matrix of math nodes, row sep=.35cm, column sep=.2cm, nodes={anchor=center, align=center, inner sep=0pt}]{
-        		& \;\includegraphics[scale=.6]{diagonalA2} & \node (b) {\red \circled{B}}; & \;\includegraphics[scale=.6]{diagonalA4} & \\
-        		\;\includegraphics[scale=.6]{diagonalA1} & \node (a) {\red \circled{A}}; & \;\includegraphics[scale=.6]{diagonalA3} & \node (c) {\red \circled{C}}; & \;\includegraphics[scale=.6]{diagonalA5} \\};
+        		& \;\includegraphics[scale=.7]{diagonalA2} & \node (b) {\red \circled{B}}; & \;\includegraphics[scale=.7]{diagonalA4} & \\
+        		\;\includegraphics[scale=.7]{diagonalA1} & \node (a) {\red \circled{A}}; & \;\includegraphics[scale=.7]{diagonalA3} & \node (c) {\red \circled{C}}; & \;\includegraphics[scale=.7]{diagonalA5} \\};
         	\draw[->] (m-2-1) -- (m-1-2);
@@
         	\matrix (m) [matrix of math nodes, row sep=.35cm, column sep=.2cm, nodes={anchor=center, align=center, inner sep=0pt}]{
-        		&& \;\includegraphics[scale=.6]{diagonalB3} & \node (c) {\red \circled{C}}; & \;\includegraphics[scale=.6]{diagonalB7} && \\
-        		& \;\includegraphics[scale=.6]{diagonalB2} & \node (b) {\red \circled{B}}; & \;\includegraphics[scale=.6]{diagonalB5} & \node (e) {\red \circled{E}}; & \;\includegraphics[scale=.6]{diagonalB8} & \\
-        		\;\includegraphics[scale=.6]{diagonalB1} & \node (a) {\red \circled{A}}; & \;\includegraphics[scale=.6]{diagonalB4} & \node (d) {\red \circled{D}}; & \;\includegraphics[scale=.6]{diagonalB6} & \node (f) {\red \circled{F}}; & \;\includegraphics[scale=.6]{diagonalB9} \\};
+        		&& \;\includegraphics[scale=.7]{diagonalB3} & \node (c) {\red \circled{C}}; & \;\includegraphics[scale=.7]{diagonalB7} && \\
+        		& \;\includegraphics[scale=.7]{diagonalB2} & \node (b) {\red \circled{B}}; & \;\includegraphics[scale=.7]{diagonalB5} & \node (e) {\red \circled{E}}; & \;\includegraphics[scale=.7]{diagonalB8} & \\
+        		\;\includegraphics[scale=.7]{diagonalB1} & \node (a) {\red \circled{A}}; & \;\includegraphics[scale=.7]{diagonalB4} & \node (d) {\red \circled{D}}; & \;\includegraphics[scale=.7]{diagonalB6} & \node (f) {\red \circled{F}}; & \;\includegraphics[scale=.7]{diagonalB9} \\};
         	\draw[->] (m-3-1) -- (m-2-2);
@@
 \text{variables} & \rotatebox{70}{$x_1$} & \rotatebox{70}{$x_2$} & \rotatebox{70}{$x_3$} & \rotatebox{70}{$\frac{x_2 + x_3}{x_1}$} & \rotatebox{70}{$\frac{x_1 + x_3}{x_2}$} & \rotatebox{70}{$\frac{x_1 + x_2}{x_3}$} & \rotatebox{70}{$\frac{x_1 + x_2 + x_3}{x_2 x_3}$} & \rotatebox{70}{$\frac{x_1 + x_2 + x_3}{x_1 x_3}$} & \rotatebox{70}{$\frac{x_1 + x_2 + x_3}{x_1 x_2}$} \\[.2cm]
-\text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{-1}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{0}{1}{-1} & \compactVector{0}{0}{-1} & \compactVector{-1}{0}{0} & \compactVector{0}{-1}{0} \\[.6cm]
+\text{$\b{g}$-vectors} & \compactVectorT{1}{0}{0} & \compactVectorT{0}{1}{0} & \compactVectorT{0}{0}{1} & \compactVectorT{-1}{0}{1} & \compactVectorT{1}{-1}{0} & \compactVectorT{0}{1}{-1} & \compactVectorT{0}{0}{-1} & \compactVectorT{-1}{0}{0} & \compactVectorT{0}{-1}{0} \\[.6cm]
 %\text{linearity}	& 0 & 0 & 1 & 1 & 0 & -1 & -1 & 0 & 0 \\
@@
 \text{variables} & \rotatebox{70}{$x_1$} & \rotatebox{70}{$x_2$} & \rotatebox{70}{$x_3$} & \rotatebox{70}{$\frac{x_2 + x_3}{x_1}$} & \rotatebox{70}{$\frac{x_1 + x_3}{x_2}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2}{x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + x_1 x_3}{x_2 x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + x_2 x_3}{x_1 x_3}$} & \rotatebox{70}{$\frac{x_1 + x_2 + x_3}{x_1 x_2}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + 2 x_1 x_3 + x_3^2}{x_2^2 x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + 2 x_2 x_3 + x_3^2}{x_1^2 x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + x_1 x_3 + x_2 x_3}{x_1 x_2 x_3}$} \\[.2cm]
-\text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{-1}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{0}{2}{-1} & \compactVector{0}{1}{-1} & \compactVector{-1}{1}{0} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} & \compactVector{-2}{0}{1} & \compactVector{-1}{0}{0}  \\[.6cm]
+\text{$\b{g}$-vectors} & \compactVectorT{1}{0}{0} & \compactVectorT{0}{1}{0} & \compactVectorT{0}{0}{1} & \compactVectorT{-1}{0}{1} & \compactVectorT{1}{-1}{0} & \compactVectorT{0}{2}{-1} & \compactVectorT{0}{1}{-1} & \compactVectorT{-1}{1}{0} & \compactVectorT{0}{-1}{0} & \compactVectorT{0}{0}{-1} & \compactVectorT{-2}{0}{1} & \compactVectorT{-1}{0}{0}  \\[.6cm]
 %\text{linearity}	& 1 & 1 & 2 & 1 & 0 & 0 & -1 & 0 & -1 & -2 & 0 & -1 \\
@@
 %        	\matrix (m) [matrix of math nodes, row sep=.35cm, column sep=.2cm, nodes={anchor=center, align=center, inner sep=0pt}]{
-%        		& \;\includegraphics[scale=.6]{diagonalA2} & \node (b) {\red \circled{B}}; & \;\includegraphics[scale=.6]{diagonalA4} & \\
-%        		\;\includegraphics[scale=.6]{diagonalA1} & \node (a) {\red \circled{A}}; & \;\includegraphics[scale=.6]{diagonalA3} & \node (c) {\red \circled{C}}; & \;\includegraphics[scale=.6]{diagonalA5} \\};
+%        		& \;\includegraphics[scale=.7]{diagonalA2} & \node (b) {\red \circled{B}}; & \;\includegraphics[scale=.7]{diagonalA4} & \\
+%        		\;\includegraphics[scale=.7]{diagonalA1} & \node (a) {\red \circled{A}}; & \;\includegraphics[scale=.7]{diagonalA3} & \node (c) {\red \circled{C}}; & \;\includegraphics[scale=.7]{diagonalA5} \\};
 %        	\draw[->] (m-2-1) -- (m-1-2);
@@
 \text{walks} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA1}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA2}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA3}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA4}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA5}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA6}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA7}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA8}} \\[.6cm]
-\text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{0}{1}{-1} & \compactVector{-1}{0}{0} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} \\[.6cm]
+\text{$\b{g}$-vectors} & \compactVectorT{1}{0}{0} & \compactVectorT{0}{1}{0} & \compactVectorT{0}{0}{1} & \compactVectorT{1}{-1}{0} & \compactVectorT{0}{1}{-1} & \compactVectorT{-1}{0}{0} & \compactVectorT{0}{-1}{0} & \compactVectorT{0}{0}{-1} \\[.6cm]
 %\text{linearity}	& 0 & -1 & 0 & 1 & -1 & 0 & 1 & 0 \\
@@
 \text{walks} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB1}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB2}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB3}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB4}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB5}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB6}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB7}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB8}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB9}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB10}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB11}} \\[.6cm]
-\text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{1}{0}{-1} & \compactVector{0}{-1}{1} & \compactVector{0}{1}{-1} & \compactVector{-1}{0}{1} & \compactVector{-1}{0}{0} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} \\[.6cm]
+\text{$\b{g}$-vectors} & \compactVectorT{1}{0}{0} & \compactVectorT{0}{1}{0} & \compactVectorT{0}{0}{1} & \compactVectorT{1}{-1}{0} & \compactVectorT{1}{0}{-1} & \compactVectorT{0}{-1}{1} & \compactVectorT{0}{1}{-1} & \compactVectorT{-1}{0}{1} & \compactVectorT{-1}{0}{0} & \compactVectorT{0}{-1}{0} & \compactVectorT{0}{0}{-1} \\[.6cm]
 %\text{linearity}	& 0 & -1 & 0 & 1 & 0 & 1 & -1 & 0 & 0 & 1 & 0 \\
@@
 \text{tubes} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA1}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA2}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA3}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA4}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA5}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA6}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA7}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA8}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA9}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA10}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA11}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA12}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA13}}  \\[.6cm]
-\text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{0}{2}{-1} & \compactVector{\nicefrac{1}{2}}{-1}{\nicefrac{1}{2}} & \compactVector{1}{-2}{0} & \compactVector{\nicefrac{1}{2}}{0}{\nicefrac{-1}{2}} & \compactVector{-1}{2}{0} & \compactVector{\nicefrac{-1}{2}}{0}{\nicefrac{1}{2}} & \compactVector{-1}{0}{0} & \compactVector{0}{-2}{1} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} \\[.6cm]
+\text{$\b{g}$-vectors} & \compactVectorT{1}{0}{0} & \compactVectorT{0}{1}{0} & \compactVectorT{0}{0}{1} & \compactVectorT{0}{2}{-1} & \compactVectorT{\nicefrac{1}{2}}{-1}{\nicefrac{1}{2}} & \compactVectorT{1}{-2}{0} & \compactVectorT{\nicefrac{1}{2}}{0}{\nicefrac{-1}{2}} & \compactVectorT{-1}{2}{0} & \compactVectorT{\nicefrac{-1}{2}}{0}{\nicefrac{1}{2}} & \compactVectorT{-1}{0}{0} & \compactVectorT{0}{-2}{1} & \compactVectorT{0}{-1}{0} & \compactVectorT{0}{0}{-1} \\[.6cm]
 %\text{linearity}	& 1 & 0 & 0 & 0 & 2 & 1 & 2 & -1 & -2 & -1 & 0 & 0 & 0 \\ 
@@
 \text{tubes} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB1}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB2}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB3}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB4}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB5}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB6}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB7}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB8}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB9}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB10}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB11}} \\[.6cm]
-\text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{\nicefrac{1}{2}}{-1}{\nicefrac{1}{2}} & \compactVector{1}{-2}{0} & \compactVector{-1}{2}{0} & \compactVector{\nicefrac{-1}{2}}{0}{\nicefrac{1}{2}} & \compactVector{-1}{0}{0} & \compactVector{0}{-2}{1} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} \\[.6cm]
+\text{$\b{g}$-vectors} & \compactVectorT{1}{0}{0} & \compactVectorT{0}{1}{0} & \compactVectorT{0}{0}{1} & \compactVectorT{\nicefrac{1}{2}}{-1}{\nicefrac{1}{2}} & \compactVectorT{1}{-2}{0} & \compactVectorT{-1}{2}{0} & \compactVectorT{\nicefrac{-1}{2}}{0}{\nicefrac{1}{2}} & \compactVectorT{-1}{0}{0} & \compactVectorT{0}{-2}{1} & \compactVectorT{0}{-1}{0} & \compactVectorT{0}{0}{-1} \\[.6cm]
 %\text{linearity}	& 0 & 1 & 0 & -4 & -2 & 2 & 0 & 0 & -2 & -1 & 0 \\

### 2019-04-06 thirdPaper/draft/typeConeAssociahedra.tex
missing pictures
minor changes

@@
 A fan is \defn{simplicial} if all its cones are, \defn{complete} if the union of its cones covers the ambient space~$\R^d$, and \defn{essential} if it contains the cone~$\{\b{0}\}$.
-% For two fans~$\Fan, \Fan[G]$ in~$\R^d$, we say that~$\Fan$ \defn{refines}~$\Fan[G]$ (and that~$\Fan[G]$ \defn{coarsens}~$\Fan$) if every cone of~$\Fan$ is contained in a cone of~$\Fan[G]$.
+Note that every complete fan is the product of an essential fan with its linearity space.
+For two fans~$\Fan, \Fan'$ in~$\R^d$, we say that~$\Fan$ \defn{refines}~$\Fan'$ (and that~$\Fan'$ \defn{coarsens}~$\Fan$) if every cone of~$\Fan$ is contained in a cone of~$\Fan'$.
 
@@
 Note that the type-cone is an open cone and contains a linearity subspace of dimension~$n$ (it is invariant by translation in~$\b{G} \R^n$). 
-We could thus intersect~$\typeCone(\Fan)$ by the kernel of~$\b{G}$, or consider the projection~$\b{K}\typeCone(\Fan)$.
+% We could thus intersect~$\typeCone(\Fan)$ with the kernel of~$\b{G}$, or consider the projection~$\b{K}\typeCone(\Fan)$.
+It is sometimes useful to get rid of the linearity by considering the projection~$\b{K}\typeCone(\Fan)$.
 
 We denote by $\ctypeCone(\Fan)$ the closure of $\typeCone(\Fan)$.
-It is a closed polyhedral cone defined by the inequalities $\sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} \geq 0$ for adjacent maximal cones~$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$.
+It is the closed polyhedral cone defined by the inequalities $\sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} \geq 0$ for adjacent maximal cones~$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$.
+If $\Fan$ is the normal fan of the polytope~$P$, then $\ctypeCone(\Fan)$ is called the \defn{deformation cone} of $P$ in~\cite{Postnikov}.
 
@@
 Although we will only treat with simplicial fans, for completeness, note that \cref{prop:characterizationPolytopalFan} and \cref{def:typecone} can be easily adapted to non-simplicial fans.
-If~$\Fan$ is an arbitrary essential complete fan, it suffices to consider consider any simplicial refinement~$\Fan'$, and set some of the strict inequalities of the definition of $\typeCone(\Fan')$ to equality.
+If~$\Fan$ is an arbitrary complete fan, it suffices to consider consider any simplicial refinement~$\Fan'$, and set some of the strict inequalities of the definition of $\typeCone(\Fan')$ to equality.
 Specifically, for any adjacent maximal cones~$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$ of~$\Fan'$ we impose
@@
 \label{rem:dimTypeCone}
-Since the type-cone is an open~$N$ dimensional cone with a linearity subspace of dimension~$n$, it has at least~$N-n$ facets.
+Since the type-cone is an~$N$ dimensional cone with a linearity subspace of dimension~$n$, it has at least~$N-n$ facets.
 We say that the type-cone is \defn{simplicial} when it has precisely $N-n$ facets.
@@
 \cref{lem:MinkowskiSum} ensures that convex combinations in the type-cone correspond to Minkowski combinations of polytopes.
-Actually, the set of weak Minkowski summands of a polytope $P$ with normal fan~$\Fan$ is isomorphic to the closed type-cone~$\ctypeCone(\Fan)$ modulo linearity (the cone of weak Minkowski summands is studied by W.~Meyer in~\cite{Meyer}, to see that it is equivalent to the type-cone and other formulations, see for example the appendix of~\cite{PostnikovReinerWilliams}).
-
-This provides natural Minkowski summands for all polytopal realizations of~$\Fan$: the rays of the type-cone.
+Actually, the set of weak Minkowski summands of a polytope $P$ with normal fan~$\Fan$ is isomorphic to the closed type-cone~$\ctypeCone(\Fan)$ modulo linearity (the cone of weak Minkowski summands was studied by W.~Meyer in~\cite{Meyer}, to see that it is equivalent to the type-cone and other formulations, see for example the appendix of~\cite{PostnikovReinerWilliams}).
+
+This provides natural Minkowski summands for all polytopal realizations of~$\Fan$: the rays of the closed 6type-cone.
 These correspond to indecomposable polytopes, see~\cite{Meyer} or \cite{McMullen-typeCone}.
-A polytope $P$ in $\R^n$ is called \defn{indecomposable} if all its weak Minkowski summands are of the form $\lambda P+t$ for some $\lambda \ge 0$ and $t \in \R^n$.
+A polytope $P\subseteq\R^n$ is called \defn{indecomposable} if all its weak Minkowski summands are of the form $\lambda P+t$ for some $\lambda \ge 0$ and $t \in \R^n$.
 

### 2019-04-06 thirdPaper/draft/typeConeAssociahedra.tex
update comments in examples

--- 2019-04-05 thirdPaper/draft/typeConeAssociahedra.tex
@@
 
-\vincent{Example type cone}
-
 \subsubsection{Associahedra and their normal fans}
@@
 Consider the fan~$\gvectorFan[2]$ and~$\gvectorFan[3]$ illustrated in \cref{fig:lodayFans}.
-The type cone of~$\gvectorFan[2]$ in~$\R^5$, has a linearity space of dimension~$2$ and $3$ facet defining inequalities (given below).
+The type cone of~$\gvectorFan[2]$ lives in~$\R^5$ and has a linearity space of dimension~$2$.
+It has $3$ facet defining inequalities (given below), which correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso} and illustrated in \cref{fig:labelFacetDefiningInequalititesAsso}\,(left).
 
@@
 \noindent
-The type cone of~$\gvectorFan[3]$ in~$\R^9$, has a linearity space of dimension~$3$ and $6$ facet defining inequalities (given below).
+The type cone of~$\gvectorFan[2]$ lives in~$\R^9$ and has a linearity space of dimension~$3$.
+It has $6$ facet defining inequalities (given below), which correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso} and illustrated in \cref{fig:labelFacetDefiningInequalititesAsso}\,(left).
 
@@
 See \cref{subsec:typeConeCA,sec:clusterCategories} for a representation theoretic \mbox{interpretation}.}
+	\label{fig:labelFacetDefiningInequalititesAsso}
 \end{figure}
@@
 Consider the cluster fans illustrated in \cref{fig:clusterFans}.
-The type cone of the left fan lives in~$\R^9$, has a linearity space of dimension~$3$ and $6$ facet defining inequalities (given below).
+The type cone of the left fan of \cref{fig:clusterFans} lives in~$\R^9$ and has a linearity space of dimension~$3$.
+It has $6$ facet defining inequalities (given below), which correspond to the mesh mutations of \cref{thm:extremalExchangeablePairsCA} as illustrated in \cref{fig:labelFacetDefiningInequalititesCA}\,(top).
 
@@
 \noindent
-The type cone of the right fan lives in~$\R^{12}$, has a linearity space of dimension~$3$ and $9$ facet defining inequalities (given below).
-
-\[
-\begin{array}{r|c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;}c@{\;}c@{\;}c@{}c@{}c@{}c}
+The type cone of the right fan of \cref{fig:clusterFans} lives in~$\R^{12}$ and has a linearity space of dimension~$3$.
+It has $9$ facet defining inequalities (given below), which correspond to the mesh mutations of \cref{thm:extremalExchangeablePairsCA} as illustrated in \cref{fig:labelFacetDefiningInequalititesCA}\,(bottom).
+
+\[
+\begin{array}{r|c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;}c@{\;}c@{\;}c@{}c@{}c@{}cc}
 \text{variables} & \rotatebox{70}{$x_1$} & \rotatebox{70}{$x_2$} & \rotatebox{70}{$x_3$} & \rotatebox{70}{$\frac{x_2 + x_3}{x_1}$} & \rotatebox{70}{$\frac{x_1 + x_3}{x_2}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2}{x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + x_1 x_3}{x_2 x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + x_2 x_3}{x_1 x_3}$} & \rotatebox{70}{$\frac{x_1 + x_2 + x_3}{x_1 x_2}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + 2 x_1 x_3 + x_3^2}{x_2^2 x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + 2 x_2 x_3 + x_3^2}{x_1^2 x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + x_1 x_3 + x_2 x_3}{x_1 x_2 x_3}$} \\[.2cm]
@@
 %					& 0 & 0 & -1 & -1 & 0 & 1 & 1 & 0 & 0 & 1 & -1 & 0 \\[.2cm]
-\text{facet}		& 0 & 0 & 0 & 0 & 0 & 1 & 0 & -2 & 0 & 0 & 1 & 0 \\
-\text{defining}		& 0 & 1 & 0 & 0 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 1 \\
-\text{inequalities}	& 0 & -1 & 0 & 1 & 0 & 0 & 0 & 1 & 0 & 0 & -1 & 0 \\
-					& -1 & 0 & 0 & 0 & 1 & 0 & 1 & 0 & 0 & -1 & 0 & 0 \\
-					& 0 & 0 & 0 & 0 & 0 & -1 & 1 & 1 & 0 & 0 & 0 & -1 \\
-					& 0 & 0 & -1 & 1 & 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 \\
-					& 0 & 0 & 0 & 0 & 0 & 1 & -2 & 0 & 0 & 1 & 0 & 0 \\
-					& 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 1 & 0 & 0 & 0 \\
-					& 0 & 0 & 1 & -2 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 \\[.2cm]
+\text{facet}		& 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 1 & 0 & 0 & 0 & \red \circled{A} \\
+\text{defining}		& 0 & 0 & -1 & 1 & 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & \red \circled{B} \\
+\text{inequalities}	& 0 & 0 & 1 & -2 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 & \red \circled{C} \\
+					& 0 & -1 & 0 & 1 & 0 & 0 & 0 & 1 & 0 & 0 & -1 & 0 & \red \circled{D} \\
+					& 0 & 0 & 0 & 0 & 0 & 1 & -2 & 0 & 0 & 1 & 0 & 0 & \red \circled{E} \\
+					& 0 & 1 & 0 & 0 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 1 & \red \circled{F} \\
+					& 0 & 0 & 0 & 0 & 0 & -1 & 1 & 1 & 0 & 0 & 0 & -1 & \red \circled{G} \\
+					& 0 & 0 & 0 & 0 & 0 & 1 & 0 & -2 & 0 & 0 & 1 & 0 & \red \circled{H} \\
+					& -1 & 0 & 0 & 0 & 1 & 0 & 1 & 0 & 0 & -1 & 0 & 0 & \red \circled{I} \\[.2cm]
 \end{array}
@@
     \begin{adjustbox}{center}
-%        \begin{tikzpicture}
-%        	\matrix (m) [matrix of math nodes, row sep=.35cm, column sep=.2cm, nodes={anchor=center, align=center, inner sep=0pt}]{
-%        		& \;\includegraphics[scale=.7]{diagonalA2} & \node (b) {\red \circled{B}}; & \;\includegraphics[scale=.7]{diagonalA4} & \\
-%        		\;\includegraphics[scale=.7]{diagonalA1} & \node (a) {\red \circled{A}}; & \;\includegraphics[scale=.7]{diagonalA3} & \node (c) {\red \circled{C}}; & \;\includegraphics[scale=.7]{diagonalA5} \\};
-%        	\draw[->] (m-2-1) -- (m-1-2);
-%        	\draw[->] (m-1-2) -- (m-2-3);
-%        	\draw[->] (m-2-3) -- (m-1-4);
-%        	\draw[->] (m-1-4) -- (m-2-5);
-%        	\draw[red] (a) -- (m-2-1);
-%        	\draw[red] (a) -- (m-2-3);
-%        	\draw[red] (a) -- (m-1-2);
-%        	\draw[red] (b) -- (m-1-2);
-%        	\draw[red] (b) -- (m-1-4);
-%        	\draw[red] (b) -- (m-2-3);
-%        	\draw[red] (c) -- (m-2-3);
-%        	\draw[red] (c) -- (m-2-5);
-%        	\draw[red] (c) -- (m-1-4);
-%        \end{tikzpicture}
-%        \quad
 		\newcommand{\fitClusterVariable}[1]{\parbox[c][.7cm][c]{1.5cm}{\centering $#1$}}
@@
         		\fitClusterVariable{\phantom{1}} && \fitClusterVariable{x_1} & \node (a1) {\red \circled{A}}; & \fitClusterVariable{\frac{x_1 + x_2 + x_3}{x_1 x_2}} && \fitClusterVariable{x_2} & \node (e2) {\red \circled{E}}; & \fitClusterVariable{\frac{x_1 + x_2 + x_3}{x_2 x_3}} && \fitClusterVariable{\phantom{1}} \\};
+        	\draw[densely dotted, thick] (m-1-1) -- (m-2-2);
+        	\draw[densely dotted, thick] (m-3-1) -- (m-2-2);
         	\draw[->] (m-2-2) -- (m-1-3);
@@
         	\draw[->] (m-3-9) -- (m-2-10);
-        	\draw[densely dotted, thick] (m-1-1) -- (m-2-2);
-        	\draw[densely dotted, thick] (m-3-1) -- (m-2-2);
         	\draw[densely dotted, thick] (m-2-10) -- (m-1-11);
@@
     \end{adjustbox}
-	\caption{}%The facet defining inequalities of the type cone~$\typeCone(\gvectorFan[])$ correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso}.
-See \cref{subsec:typeConeCA,sec:clusterCategories} for a representation theoretic \mbox{interpretation}.}
+    %
+    \begin{adjustbox}{center}
+		\newcommand{\fitClusterVariable}[1]{\parbox[c][.7cm][c]{2.3cm}{\centering $#1$}}
+        \begin{tikzpicture}
+        	\matrix (m) [matrix of math nodes, row sep=.4cm, column sep=-.7cm, nodes={anchor=center, align=center, inner sep=0pt}]{
+        		& \fitClusterVariable{\frac{x_1^2 + x_2^2 + 2 x_1 x_3 + x_3^2}{x_2^2 x_3}} && \fitClusterVariable{x_3} & \node (c) {\red \circled{C}}; & \fitClusterVariable{\frac{x_1^2 + x_2^2 + 2 x_2 x_3 + x_3^2}{x_1^2 x_3}} & \node (e) {\red \circled{E}}; & \fitClusterVariable{\frac{x_1^2 + x_2^2}{x_3}} & \node (h) {\red \circled{H}}; & \fitClusterVariable{\frac{x_1^2 + x_2^2 + 2 x_1 x_3 + x_3^2}{x_2^2 x_3}} && \fitClusterVariable{\phantom{1}} \\
+        		\fitClusterVariable{\phantom{1}} & \node (i1) {\red \circled{I}}; & \fitClusterVariable{\frac{x_1 + x_3}{x_2}} & \node (b) {\red \circled{B}}; & \fitClusterVariable{\frac{x_2 + x_3}{x_1}} & \node (d) {\red \circled{D}}; & \fitClusterVariable{\frac{x_1^2 + x_2^2 + x_2 x_3}{x_1 x_3}} & \node (g) {\red \circled{G}}; & \fitClusterVariable{\frac{x_1^2 + x_2^2 + x_1 x_3}{x_2 x_3}} & \node (i2) {\red \circled{I}}; & \fitClusterVariable{\frac{x_1 + x_3}{x_2}} & \\
+        		& \fitClusterVariable{x_1} & \node (a1) {\red \circled{A}}; & \fitClusterVariable{\frac{x_1 + x_2 + x_3}{x_1 x_2}} && \fitClusterVariable{x_2} & \node (f) {\red \circled{F}}; & \fitClusterVariable{\frac{x_1^2 + x_2^2 + x_1 x_3 + x_2 x_3}{x_1 x_2 x_3}} && \fitClusterVariable{x_1} & \node (a2) {\red \circled{A}}; & \fitClusterVariable{\phantom{1}} \\};
+        	\draw[densely dotted, thick] (m-2-1) -- (m-1-2);
+        	\draw[densely dotted, thick] (m-2-1) -- (m-3-2);
+        	\draw[->] (m-1-2) -- (m-2-3);
+        	\draw[->] (m-3-2) -- (m-2-3);
+        	\draw[->] (m-2-3) -- (m-1-4);
+        	\draw[->] (m-2-3) -- (m-3-4);
+        	\draw[->] (m-1-4) -- (m-2-5);
+        	\draw[->] (m-3-4) -- (m-2-5);
+        	\draw[->] (m-2-5) -- (m-1-6);
+        	\draw[->] (m-2-5) -- (m-3-6);
+        	\draw[->] (m-1-6) -- (m-2-7);
+        	\draw[->] (m-3-6) -- (m-2-7);
+        	\draw[->] (m-2-7) -- (m-1-8);
+        	\draw[->] (m-2-7) -- (m-3-8);
+        	\draw[->] (m-1-8) -- (m-2-9);
+        	\draw[->] (m-3-8) -- (m-2-9);
+        	\draw[->] (m-2-9) -- (m-1-10);
+        	\draw[->] (m-2-9) -- (m-3-10);
+        	\draw[->] (m-1-10) -- (m-2-11);
+        	\draw[->] (m-3-10) -- (m-2-11);
+        	\draw[densely dotted, thick] (m-2-11) -- (m-1-12);
+        	\draw[densely dotted, thick] (m-2-11) -- (m-3-12);
+        	\draw[red] (a1) -- (m-3-2);
+        	\draw[red] (a1) -- (m-3-4);
+        	\draw[red] (a1) -- (m-2-3);
+        	\draw[red] (a2) -- (m-3-10);
+        	\draw[red] (a2) -- (m-3-12);
+        	\draw[red] (a2) -- (m-2-11);
+        	\draw[red] (b) -- (m-2-3);
+        	\draw[red] (b) -- (m-2-5);
+        	\draw[red] (b) -- (m-1-4);
+        	\draw[red] (b) -- (m-3-4);
+        	\draw[red] (c) -- (m-1-4);
+        	\draw[red] (c) -- (m-1-6);
+        	\draw[red] (c) -- (m-2-5);
+        	\draw[red] (d) -- (m-2-5);
+        	\draw[red] (d) -- (m-2-7);
+        	\draw[red] (d) -- (m-1-6);
+        	\draw[red] (d) -- (m-3-6);
+        	\draw[red] (e) -- (m-1-6);
+        	\draw[red] (e) -- (m-1-8);
+        	\draw[red] (e) -- (m-2-7);
+        	\draw[red] (f) -- (m-3-6);
+        	\draw[red] (f) -- (m-3-8);
+        	\draw[red] (f) -- (m-2-7);
+        	\draw[red] (g) -- (m-2-7);
+        	\draw[red] (g) -- (m-2-9);
+        	\draw[red] (g) -- (m-1-8);
+        	\draw[red] (g) -- (m-3-8);
+        	\draw[red] (h) -- (m-1-8);
+        	\draw[red] (h) -- (m-1-10);
+        	\draw[red] (h) -- (m-2-9);
+        	\draw[red] (i1) -- (m-2-1);
+        	\draw[red] (i1) -- (m-2-3);
+        	\draw[red] (i1) -- (m-1-2);
+        	\draw[red] (i1) -- (m-3-2);
+        	\draw[red] (i2) -- (m-2-9);
+        	\draw[red] (i2) -- (m-2-11);
+        	\draw[red] (i2) -- (m-1-10);
+        	\draw[red] (i2) -- (m-3-10);
+        \end{tikzpicture}
+    \end{adjustbox}
+	\caption{The facet defining inequalities of the type cone~$\typeCone(\gvectorFan[\B_\circ])$ of the cluster fan correspond to the mesh mutations described in \cref{thm:extremalExchangeablePairsCA}.
+See \cref{sec:clusterCategories} for a representation theoretic \mbox{interpretation}.}
+	\label{fig:labelFacetDefiningInequalititesCA}
 \end{figure}
@@
 \begin{definition}
+\label{def:meshMutation}
 %Consider a seed~$\seed = (\B, \cluster)$ and a cluster variable~$x \in \cluster$.
@@
 A mesh mutation is \defn{initial} if it starts at a cluster variable of an initial seed.
+\vincent{Problem here. In my examples, the condition is to end at an initial cluster variable.}
 We denote by~$\meshes$ the set of all pairs~$\{x,x'\}$ where~$x$ and~$x'$ are two cluster variables of~$\principalClusterAlgebra$ which are exchangeable via a non-initial mesh mutation.
@@
 \vincent{\cref{lem:bijectionMeshMutations} might become a conjecture.}
-\vincent{Pictures AR quivers + labeling of meshes reported on the inequalities.}
 
@@
 Consider the non-kissing fans illustrated in \cref{fig:nonkissingFans}.
-The type cone of the left fan lives in~$\R^9$, has a linearity space of dimension~$3$ and $6$ facet defining inequalities (given below).
+The type cone of the left fan of \cref{fig:nonkissingFans} lives in~$\R^9$ and has a linearity space of dimension~$3$.
+It has $6$ facet defining inequalities (given below), which correspond to the flips described in \cref{prop:interestingExchangeablePairsNKC,prop:extremalExchangeablePairsNKC} and illustrated in \cref{fig:labelFacetDefiningInequalititesNKC}\,(left).
 
@@
 \noindent
-The type cone of the right fan lives in~$\R^{11}$, has a linearity space of dimension~$3$ and $9$ facet defining inequalities (given below). In particular, it is not simplicial.
+The type cone of the right fan of \cref{fig:nonkissingFans} lives in~$\R^{11}$ and has a linearity space of dimension~$3$.
+It has $9$ facet defining inequalities (given below), which correspond to the flips illustrated in \cref{fig:labelFacetDefiningInequalititesNKC}\,(right).
+In particular, it is not simplicial.
 
@@
     \end{adjustbox}
-	\caption{The facet defining inequalities of the type cone~$\typeCone(\gvectorFan[\quiver])$ represented on the Auslander Reiten quiver of the gentle algebra of~$\quiver$.
+	\caption{The facet defining inequalities of the type cone~$\typeCone(\gvectorFan[\quiver])$ of the non-kissing fan, represented on the Auslander Reiten quiver of the gentle algebra of~$\quiver$.
 While they correspond to meshes on the left, they are not as clear in the general case as on the right.
 See also \cref{sect::extricats}.}
+	\label{fig:labelFacetDefiningInequalititesNKC}
 \end{figure}
@@
 \begin{proposition}
+\label{prop:interestingExchangeablePairsNKC}
 For any brick $2$-acyclic gentle quiver~$\quiver$ and any string~$\sigma \in \strings$, the walks~$\cc{\sigma}$ and~$\hh{\sigma}$ are exchangeable with distinguished substring~$\sigma$.

### 2019-04-06 thirdPaper/draft/typeConeAssociahedra.tex
describint faces of type cone

--- 2019-04-06 thirdPaper/draft/typeConeAssociahedra.tex
@@
 
-We denote by $\ctypeCone(\Fan)$ the closure of $\typeCone(\Fan)$.
+We denote by $\ctypeCone(\Fan)$ the closure of $\typeCone(\Fan)$, and call it the \defn{closed type-cone} of~$\Fan$.
 It is the closed polyhedral cone defined by the inequalities $\sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} \geq 0$ for adjacent maximal cones~$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$.
@@
 
-\begin{remark}
- \label{rmk:non-simplicial}
 Although we will only treat with simplicial fans, for completeness, note that \cref{prop:characterizationPolytopalFan} and \cref{def:typecone} can be easily adapted to non-simplicial fans.
-If~$\Fan$ is an arbitrary complete fan, it suffices to consider consider any simplicial refinement~$\Fan'$, and set some of the strict inequalities of the definition of $\typeCone(\Fan')$ to equality.
-Specifically, for any adjacent maximal cones~$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$ of~$\Fan'$ we impose
-\[
- \sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} {\left\{\begin{array}{l} =\\ >\end{array}\right\}} 0
-\]
-with `$>$' when $\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$ do not belong to the same maximal cone of $\Fan$; and with `$=$' if $\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$ belong to the same maximal cone of $\Fan$.
-\end{remark}
+For an arbitrary complete fan, it suffices to consider consider any simplicial refinement, and set some of the strict inequalities of the definition of the type cone to equality.
+\begin{proposition}
+ \label{prop:non-simplicial}
+ Let $\Fan'$ be a complete fan that coarsens the essential complete simplicial fan~$\Fan$.
+ The \defn{type-cone}~$\typeCone(\Fan')$ of all $\Fan'$-admissible height vectors~$\b{h}$ is
+ \begin{align*}
+ \typeCone(\Fan) 
+%  & \eqdef \set{\b{h} \in \R^N}{\Fan \text{ is the normal fan of } P_\b{h}} \\
+& = \left\{\b{h} \in \R^N\;\middle|\;
+\begin{array}{ll}
+ \sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} = 0
+ & \begin{array}{l} \text{for any adjacent maximal cones} \\ \text{$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$ of~$\Fan$ \textbf{belonging}}\\\text{to the same maximal cone of $\Fan'$; and}\end{array}
+\\\\
+\sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} > 0
+ & \begin{array}{l} \text{for any adjacent maximal cones} \\ \text{$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$ of~$\Fan$ \textbf{not belonging}}\\\text{to the same maximal cone of $\Fan'$}\end{array}
+\end{array}
+ \right\}.
+ \end{align*}
+\end{proposition}
+\arnau{should add proof or citation}
 
@@
 
+\begin{theorem}
+ Let $\Fan$ be a polytopal fan. Then the relatively open faces of~$\ctypeCone(\Fan)$ are the type-cones of all (polytopal) coarsenings of~$\Fan$. 
+\end{theorem}
+\begin{proof}
+ Let $\Fan'$ be a simplicial refinement of $\Fan$.
+By~\cref{prop:non-simplicial}, the type-cone of any coarsening of $\Fan$ is a relatively open cell of the hyperplane arrangement defined by adjacent pairs of~$\Fan'$.
+The type-cone of the coarsening is not empty whenever it is polytopal.
+When non-empty, distinct coarsenings give rise to distinct cells (one will have an equation that is a strict inequality in the other).
+And all lie in the closure of~$\typeCone(\Fan)$, since no non-strict inequality is violated.
+
+ For the converse, observe that for $\b{h}\in\ctypeCone(\Fan)$, the normal fan of $P_{\b{h}}$ is the polytopal complete fan obtained by merging all pairs of adjacent maximal cones~$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$ of~$\Fan$ such that $\sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} = 0$.
+\end{proof}
+
+Some observations are in place:
+
+\begin{itemize}
+ \item Note that any extremal adjacent pair $\{\R_{\ge0}\rays, \R_{\ge0}\rays'\}$ of~$\Fan$ gives rise to a facet of $\ctypeCone(\Fan)$, but that this pair might not be unique for this facet.
+There might be several extremal adjacent pairs giving rise to the same facet.
+ This situation arises when, in order to have a polytopal polyhedral fan, more pairs of adjacent cones must be merged.
+ For example, when we have the unique exchange property and there are many pairs of cones separating the same exchangeable pair of rays.
+
+ \item Mergings induced by extremal adjacent pairs are not the only ones that can take place in the boundary of~$\ctypeCone(\Fan)$.
+Indeed, if $\Fan'$ is the coarsening defining a lower-dimensional face~$\typeCone(\Fan')$ of~$\ctypeCone(\Fan)$, then to get $\Fan$ we have to perform all the coarsenings given by facets of~$\ctypeCone(\Fan)$ containing~$\typeCone(\Fan')$.
+But we might have to perform more coarsenings arising from exchangeable pairs  $\{\R_{\ge0}\rays, \R_{\ge0}\rays'\}$ whose inequality is redundant for~$\ctypeCone(\Fan)$ but tight for all points in~$\typeCone(\Fan')$.
+ \item Even if $\Fan$ is essential, not all its polytopal coarsenings need to be.
+Indeed, it can happen that there is a certain polytopal coarsening $\Fan'$ in which all the cells have a common linearity space.
+In this case, $\Fan'$ is the normal fan of a lower dimensional polytope (whose codimension is the dimension of the linearity space of $\Fan'$).
+ For this to happen, it is necessary (but not sufficient) that there is a positive linear dependence between some rays of $\Fan$. 
+\end{itemize}
+
 %%%%%%%%%%%
@@
 We first describe the associahedra of~\cite{ShniderSternberg, Loday} and their type cones as they are the prototypes of our constructions.
-
-\vincent{Example type cone}
 
@@
 \[
-\begin{array}{r|c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;}c@{\;}c@{\;}c@{}c@{}c@{}c}
+\begin{array}{r|c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;}c@{\;}c@{\;}c@{}c@{}c@{}cc}
 \text{variables} & \rotatebox{70}{$x_1$} & \rotatebox{70}{$x_2$} & \rotatebox{70}{$x_3$} & \rotatebox{70}{$\frac{x_2 + x_3}{x_1}$} & \rotatebox{70}{$\frac{x_1 + x_3}{x_2}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2}{x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + x_1 x_3}{x_2 x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + x_2 x_3}{x_1 x_3}$} & \rotatebox{70}{$\frac{x_1 + x_2 + x_3}{x_1 x_2}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + 2 x_1 x_3 + x_3^2}{x_2^2 x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + 2 x_2 x_3 + x_3^2}{x_1^2 x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + x_1 x_3 + x_2 x_3}{x_1 x_2 x_3}$} \\[.2cm]
@@
 \text{facet}		& 0 & 0 & 0 & 0 & 0 & 1 & 0 & -2 & 0 & 0 & 1 & 0 \\
-\text{defining}		& 0 & 1 & 0 & 0 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 1 \\
-\text{inequalities}	& 0 & -1 & 0 & 1 & 0 & 0 & 0 & 1 & 0 & 0 & -1 & 0 \\
+\text{defining}		& 0 & 1 & 0 & 0 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 1 & \red \circled{E2} \\
+\text{inequalities}	& 0 & -1 & 0 & 1 & 0 & 0 & 0 & 1 & 0 & 0 & -1 & 0 & \red \circled{D} \\
 					& -1 & 0 & 0 & 0 & 1 & 0 & 1 & 0 & 0 & -1 & 0 & 0 \\
-					& 0 & 0 & 0 & 0 & 0 & -1 & 1 & 1 & 0 & 0 & 0 & -1 \\
-					& 0 & 0 & -1 & 1 & 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 \\
-					& 0 & 0 & 0 & 0 & 0 & 1 & -2 & 0 & 0 & 1 & 0 & 0 \\
-					& 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 1 & 0 & 0 & 0 \\
-					& 0 & 0 & 1 & -2 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 \\[.2cm]
+					& 0 & 0 & 0 & 0 & 0 & -1 & 1 & 1 & 0 & 0 & 0 & -1 & \red \circled{F2} \\
+					& 0 & 0 & -1 & 1 & 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & \red \circled{B} \\
+					& 0 & 0 & 0 & 0 & 0 & 1 & -2 & 0 & 0 & 1 & 0 & 0 & \red \circled{E3} \\
+					& 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 1 & 0 & 0 & 0 & \red \circled{A1} \\
+					& 0 & 0 & 1 & -2 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 & \red \circled{C} \\[.2cm]
 \end{array}
@@
         	\draw[red] (f2) -- (m-3-9);
+        \end{tikzpicture}
+    \end{adjustbox}
+    %
+    \begin{adjustbox}{center}
+		\newcommand{\fitClusterVariable}[1]{\parbox[c][.7cm][c]{2.3cm}{\centering $#1$}}
+        \begin{tikzpicture}
+        	\matrix (m) [matrix of math nodes, row sep=.4cm, column sep=-.7cm, nodes={anchor=center, align=center, inner sep=0pt}]{
+        		& \fitClusterVariable{\frac{x_1^2 + x_2^2 + 2 x_1 x_3 + x_3^2}{x_2^2 x_3}} && \fitClusterVariable{x_3} & \node (c) {\red \circled{C}}; & \fitClusterVariable{\frac{x_1^2 + x_2^2 + 2 x_2 x_3 + x_3^2}{x_1^2 x_3}} & \node (e) {\red \circled{E}}; & \fitClusterVariable{\frac{x_1^2 + x_2^2}{x_3}} & \node (h) {\red \circled{H}}; & \fitClusterVariable{\frac{x_1^2 + x_2^2 + 2 x_1 x_3 + x_3^2}{x_2^2 x_3}} && \fitClusterVariable{\phantom{1}} \\
+        		\fitClusterVariable{\phantom{1}} & \node (i1) {\red \circled{I}}; & \fitClusterVariable{\frac{x_1 + x_3}{x_2}} & \node (b) {\red \circled{B}}; & \fitClusterVariable{\frac{x_2 + x_3}{x_1}} & \node (d) {\red \circled{D}}; & \fitClusterVariable{\frac{x_1^2 + x_2^2 + x_2 x_3}{x_1 x_3}} & \node (g) {\red \circled{G}}; & \fitClusterVariable{\frac{x_1^2 + x_2^2 + x_1 x_3}{x_2 x_3}} & \node (i2) {\red \circled{I}}; & \fitClusterVariable{\frac{x_1 + x_3}{x_2}} & \\
+        		& \fitClusterVariable{x_1} & \node (a1) {\red \circled{A}}; & \fitClusterVariable{\frac{x_1 + x_2 + x_3}{x_1 x_2}} && \fitClusterVariable{x_2} & \node (f) {\red \circled{F}}; & \fitClusterVariable{\frac{x_1^2 + x_2^2 + x_1 x_3 + x_2 x_3}{x_1 x_2 x_3}} && \fitClusterVariable{x_1} & \node (a2) {\red \circled{A}}; & \fitClusterVariable{\phantom{1}} \\};
+        	\draw[densely dotted, thick] (m-2-1) -- (m-1-2);
+        	\draw[densely dotted, thick] (m-2-1) -- (m-3-2);
+        	\draw[->] (m-1-2) -- (m-2-3);
+        	\draw[->] (m-3-2) -- (m-2-3);
+        	\draw[->] (m-2-3) -- (m-1-4);
+        	\draw[->] (m-2-3) -- (m-3-4);
+        	\draw[->] (m-1-4) -- (m-2-5);
+        	\draw[->] (m-3-4) -- (m-2-5);
+        	\draw[->] (m-2-5) -- (m-1-6);
+        	\draw[->] (m-2-5) -- (m-3-6);
+        	\draw[->] (m-1-6) -- (m-2-7);
+        	\draw[->] (m-3-6) -- (m-2-7);
+        	\draw[->] (m-2-7) -- (m-1-8);
+        	\draw[->] (m-2-7) -- (m-3-8);
+        	\draw[->] (m-1-8) -- (m-2-9);
+        	\draw[->] (m-3-8) -- (m-2-9);
+        	\draw[->] (m-2-9) -- (m-1-10);
+        	\draw[->] (m-2-9) -- (m-3-10);
+        	\draw[->] (m-1-10) -- (m-2-11);
+        	\draw[->] (m-3-10) -- (m-2-11);
+        	\draw[densely dotted, thick] (m-2-11) -- (m-1-12);
+        	\draw[densely dotted, thick] (m-2-11) -- (m-3-12);
+        	\draw[red] (a1) -- (m-3-2);
+        	\draw[red] (a1) -- (m-3-4);
+        	\draw[red] (a1) -- (m-2-3);
+        	\draw[red] (a2) -- (m-3-10);
+        	\draw[red] (a2) -- (m-3-12);
+        	\draw[red] (a2) -- (m-2-11);
+        	\draw[red] (b) -- (m-2-3);
+        	\draw[red] (b) -- (m-2-5);
+        	\draw[red] (b) -- (m-1-4);
+        	\draw[red] (b) -- (m-3-4);
+        	\draw[red] (c) -- (m-1-4);
+        	\draw[red] (c) -- (m-1-6);
+        	\draw[red] (c) -- (m-2-5);
+        	\draw[red] (d) -- (m-2-5);
+        	\draw[red] (d) -- (m-2-7);
+        	\draw[red] (d) -- (m-1-6);
+        	\draw[red] (d) -- (m-3-6);
+        	\draw[red] (e) -- (m-1-6);
+        	\draw[red] (e) -- (m-1-8);
+        	\draw[red] (e) -- (m-2-7);
+        	\draw[red] (f) -- (m-3-6);
+        	\draw[red] (f) -- (m-3-8);
+        	\draw[red] (f) -- (m-2-7);
+        	\draw[red] (g) -- (m-2-7);
+        	\draw[red] (g) -- (m-2-9);
+        	\draw[red] (g) -- (m-1-8);
+        	\draw[red] (g) -- (m-3-8);
+        	\draw[red] (h) -- (m-1-8);
+        	\draw[red] (h) -- (m-1-10);
+        	\draw[red] (h) -- (m-2-9);
+        	\draw[red] (i1) -- (m-2-1);
+        	\draw[red] (i1) -- (m-2-3);
+        	\draw[red] (i1) -- (m-1-2);
+        	\draw[red] (i1) -- (m-3-2);
+        	\draw[red] (i2) -- (m-2-9);
+        	\draw[red] (i2) -- (m-2-11);
+        	\draw[red] (i2) -- (m-1-10);
+        	\draw[red] (i2) -- (m-3-10);
         \end{tikzpicture}

### 2019-04-06 thirdPaper/draft/typeConeAssociahedra.tex

@@
 \noindent
-The type cone of the right fan lives in~$\R^{12}$, has a linearity space of dimension~$3$ and $9$ facet defining inequalities (given below).
+The type cone of the right fan of \cref{fig:clusterFans} lives in~$\R^{12}$ and has a linearity space of dimension~$3$.
+It has $9$ facet defining inequalities (given below), which correspond to the mesh mutations of \cref{thm:extremalExchangeablePairsCA} as illustrated in \cref{fig:labelFacetDefiningInequalititesCA}\,(bottom).
 
@@
 %					& 0 & 0 & -1 & -1 & 0 & 1 & 1 & 0 & 0 & 1 & -1 & 0 \\[.2cm]
-\text{facet}		& 0 & 0 & 0 & 0 & 0 & 1 & 0 & -2 & 0 & 0 & 1 & 0 \\
-\text{defining}		& 0 & 1 & 0 & 0 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 1 & \red \circled{E2} \\
-\text{inequalities}	& 0 & -1 & 0 & 1 & 0 & 0 & 0 & 1 & 0 & 0 & -1 & 0 & \red \circled{D} \\
-					& -1 & 0 & 0 & 0 & 1 & 0 & 1 & 0 & 0 & -1 & 0 & 0 \\
-					& 0 & 0 & 0 & 0 & 0 & -1 & 1 & 1 & 0 & 0 & 0 & -1 & \red \circled{F2} \\
-					& 0 & 0 & -1 & 1 & 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & \red \circled{B} \\
-					& 0 & 0 & 0 & 0 & 0 & 1 & -2 & 0 & 0 & 1 & 0 & 0 & \red \circled{E3} \\
-					& 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 1 & 0 & 0 & 0 & \red \circled{A1} \\
-					& 0 & 0 & 1 & -2 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 & \red \circled{C} \\[.2cm]
+\text{facet}		& 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 1 & 0 & 0 & 0 & \red \circled{A} \\
+\text{defining}		& 0 & 0 & -1 & 1 & 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & \red \circled{B} \\
+\text{inequalities}	& 0 & 0 & 1 & -2 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 & \red \circled{C} \\
+					& 0 & -1 & 0 & 1 & 0 & 0 & 0 & 1 & 0 & 0 & -1 & 0 & \red \circled{D} \\
+					& 0 & 0 & 0 & 0 & 0 & 1 & -2 & 0 & 0 & 1 & 0 & 0 & \red \circled{E} \\
+					& 0 & 1 & 0 & 0 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 1 & \red \circled{F} \\
+					& 0 & 0 & 0 & 0 & 0 & -1 & 1 & 1 & 0 & 0 & 0 & -1 & \red \circled{G} \\
+					& 0 & 0 & 0 & 0 & 0 & 1 & 0 & -2 & 0 & 0 & 1 & 0 & \red \circled{H} \\
+					& -1 & 0 & 0 & 0 & 1 & 0 & 1 & 0 & 0 & -1 & 0 & 0 & \red \circled{I} \\[.2cm]
 \end{array}
@@
     \end{adjustbox}
-	\caption{}%The facet defining inequalities of the type cone~$\typeCone(\gvectorFan[])$ correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso}.
-See \cref{subsec:typeConeCA,sec:clusterCategories} for a representation theoretic \mbox{interpretation}.}
+	\caption{The facet defining inequalities of the type cone~$\typeCone(\gvectorFan[\B_\circ])$ of the cluster fan correspond to the mesh mutations described in \cref{thm:extremalExchangeablePairsCA}.
+See \cref{sec:clusterCategories} for a representation theoretic \mbox{interpretation}.}
+	\label{fig:labelFacetDefiningInequalititesCA}
 \end{figure}

### 2019-04-08 thirdPaper/draft/typeConeAssociahedra.tex
added example of type cone

@@
 Although we will only treat with simplicial fans, for completeness, note that \cref{prop:characterizationPolytopalFan} and \cref{def:typecone} can be easily adapted to non-simplicial fans.
-For an arbitrary complete fan, it suffices to consider consider any simplicial refinement, and set some of the strict inequalities of the definition of the type cone to equality.
+To describe the type-cone of an arbitrary complete fan, it suffices to consider consider any simplicial refinement, and to set some of the strict inequalities of the definition of the type cone to equality.
 \begin{proposition}
@@
 When non-empty, distinct coarsenings give rise to distinct cells (one will have an equation that is a strict inequality in the other).
-And all lie in the closure of~$\typeCone(\Fan)$, since no non-strict inequality is violated.
+And all lie in the closure of~$\typeCone(\Fan)$, since they are al in the closure of all the defining half-spaces.
 
@@
 There might be several extremal adjacent pairs giving rise to the same facet.
- This situation arises when, in order to have a polytopal polyhedral fan, more pairs of adjacent cones must be merged.
- For example, when we have the unique exchange property and there are many pairs of cones separating the same exchangeable pair of rays.
+This happens often when we have the unique exchange property and there are many pairs of cones separating the same exchangeable pair of rays.
 
@@
 But we might have to perform more coarsenings arising from exchangeable pairs  $\{\R_{\ge0}\rays, \R_{\ge0}\rays'\}$ whose inequality is redundant for~$\ctypeCone(\Fan)$ but tight for all points in~$\typeCone(\Fan')$.
+This situation arises when, in order to have a polytopal polyhedral fan, more pairs of adjacent cones must be merged.
  \item Even if $\Fan$ is essential, not all its polytopal coarsenings need to be.
@@
 \end{itemize}
+
+\begin{example}\label{ex:typecone}
+Consider the $2$-dimensional fan~$\Fan$ depicted in \cref{fig:typecone} (left) (we will encounter this fan again in \cref{ex:LodayFans}).
+It has five rays $v_1,\dots,v_5$ and five maximal cones $a,\dots, e$.
+Its type-cone lies in~$\R^5$, but has a $2$-dimensional linearity space.
+It suffices to study $\b{K}\ctypeCone(\Fan)$ which is an essential simplicial cone in~$\R^3$.
+One can further reduce the dimension by intersecting with a transversal hyperplane, to get a $2$-dimensional representation.
+This is the triangle that is depicted in \cref{fig:typecone} (right).
+The five pairs of adjacent maximal cones give rise to five defining inequalities for $\ctypeCone(\Fan)$, although only three are non-redundant.
+If $H_{ij}$ is the hyperplane supporting the inequality given by the two adjacent maximal cones~$i$ and~$j$, then only $H_{ab}$, $H_{cd}$ and $H_{bc}$ support facets of the type-cone.
+The relative interior of the three facets of~$\ctypeCone(\Fan)$ are the type-cones of three coarsenings of~$\Fan$, obtained by merging certain adjacent maximal cones (those that are extremal).
+One of the rays generating~$\b{K}\ctypeCone(\Fan)$ corresponds to a $2$-dimensional simplex, and its normal fan is obtained by merging two pairs of extremal adjacent maximal cones.
+The two remaining rays lie not only in the hyperplanes~$H_{ij}$ defining the facets it belongs to, but also one extra such hyperplane.
+Its normal fan has only two cones, one arising as a merging of three cones and one arising as a merging of two cones.
+These fans are not essential, they have a one-dimensional linearity.
+Hence, the corresponding polytopes are not full-dimensional, they are of codimension~$1$.
+
+\begin{figure}[htpb]
+	\capstart
+	\centerline{{\includegraphics[width=.3\linewidth]{typeconeFan}}\hspace{1.5cm}\includegraphics[width=.4\linewidth]{typecone}}
+	\caption{A complete $2$-dimensional fan~$\Fan$ with five rays $v_1,\dots,v_5$ and five maximal cones $a,\dots, e$.
+We depict the intersection of $\b{K}\ctypeCone(F)$ with a hyperplane to get a $2$-dimensional slice.
+On top of each face of $\ctypeCone(F)$, and example of polytope with the corresponding normal fan is depicted.}
+	\label{fig:typecone}
+\end{figure}
+
+\end{example}
 
@@
 
-Note that such a family of polytopes giving rise to unique positive representations only exists when the type-cone is simplicial.
+Note that such a family of polytopes giving rise to unique positive representations only exists when the type-cone is simplicial (both unicity and positivity only happen when the type-cone is simplicial).
+
+In the case of \cref{ex:typecone}, we get that any polytope in $\ctypeCone(\Fan)$ is a positive Minkowski combination of a triangle and two of its edges. This is the normal fan of 
+Loday's $2$-dimensional associahedron, and the realization as a Minkowski sum of faces of a simplex was given by Postnikov in~\cite{Postnikov}.
 
@@
 
-\begin{example}
+\begin{example}\label{ex:LodayFans}
 Consider the fan~$\gvectorFan[2]$ and~$\gvectorFan[3]$ illustrated in \cref{fig:lodayFans}.

### 2019-04-08 thirdPaper/draft/typeConeAssociahedra.tex
start intro

--- 2019-04-06 thirdPaper/draft/typeConeAssociahedra.tex
@@
 \newcommand{\K}{k} % field
-\newcommand{\fA}{\mathfrak{A}} % alternating group
-\newcommand{\fS}{\mathfrak{S}} % symmetric group
-\newcommand{\cA}{\mathcal{A}} % algebra
-\newcommand{\cC}{\mathcal{C}} % collection
-\newcommand{\cS}{\mathcal{S}} % ground set
-\newcommand{\uR}{\underline{R}} % underline set
-\newcommand{\uS}{\underline{S}} % underline set
-\newcommand{\uT}{\underline{T}} % underline set
-\newcommand{\oS}{\overline{S}} % overline set
-\newcommand{\ucS}{\underline{\cS}} % underline ground set
+\newcommand{\f}[1]{{\mathfrak{#1}}} % mathfrak letters
+\renewcommand{\c}[1]{{\mathcal{#1}}} % call letters
 \renewcommand{\b}[1]{{\boldsymbol{#1}}} % bold letters
@@
 
-We explain recent results of~\cite{BazierMatteDouvilleMousavandThomasYildirim}. Some advantages of our approach are:
-\begin{itemize}
-\item We manage to extend their results to other families of $\b{g}$-vector fans: first to all $\b{g}$-vector fans of finite type cluster algebras acyclic or not (whose polytopality was only proved recently in~\cite{HohlwegPilaudStella}), then to all $\b{g}$-vector fans of the $\tau$-tilting finite gentle algebras (whose polytopality was proved recently in~\cite{PaluPilaudPlamondon-nonkissing}), and finally to the nested fans of graph associahedra (whose polytopality was studied in~\cite{CarrDevadoss, Devadoss, Postnikov, FeichtnerSturmfels, Zelevinsky}).
-\item We have a simpler proof, only based on the transformation between the classical descriptions of a polytope of the form~$\set{\b{x} \in \R^n}{\b{G}\b{x} \le \b{h}}$ and~$\set{\b{z} \in \R^N}{\b{K}\b{z} = \b{K}\b{h} \text{ and } \b{z} \ge 0}$ (this transformation is standard in optimization).
+\newpage
+
+The associahedron is a ``mythical polytope'' \cite{Haiman} whose facial structure encodes Catalan families: its vertices correspond to parenthesizations of a non-associative product, triangulations of a convex polygon, or binary trees; its edges correspond to applications of the associativity rule, diagonal flips, or edge rotations; and in general its faces correspond to partial parenthesizations, diagonal dissections, or Schr\"oder trees.
+Its combinatorial and topological structure was introduced in early works of D.~Tamari~\cite{Tamari} and J.~Stasheff~\cite{Stasheff}, and a first polytopal model was realized by J.~Milnor for the PhD defense of the latter.
+The first systematic polytopal realizations were constructed by M.~Haiman~\cite{Haiman} and C.~Lee~\cite{Lee}.
+Since then, the associahedron has been largely ``demystified'' with several polytopal constructions...
+%~\cite{Loday, HohlwegLange, LangePilaud}.
+%See~\cite{CeballosSantosZiegler} for a survey on these constructions.
+% and generalizations to secondary and fiber polytopes~\cite{GelfandKapranovZelevinsky, BilleraFillimanSturmfels}, to pseudotriangulation polytopes~\cite{RoteSantosStreinu-polytope}, to graph associahedra and nestohedra~\cite{CarrDevadoss, Devadoss, Postnikov, FeichtnerSturmfels, Zelevinsky, Pilaud-removahedra}, to cluster complexes and generalized associahedra~\cite{FominZelevinsky-YSystems, FominZelevinsky-ClusterAlgebrasI, FominZelevinsky-ClusterAlgebrasII, ChapotonFominZelevinsky, HohlwegLangeThomas, Stella, Hohlweg, HohlwegPilaudStella}, to brick polytopes~\cite{PilaudSantos-brickPolytope, PilaudStump-brickPolytope}, to quotientopes~\cite{Reading-latticeCongruences, Reading-CambrianLattices, PilaudSantos-quotientopes}, etc.
+
+The associahedron appears as a fundamental structure in several mathematical theories, such as moduli spaces and topology~\cite{Stasheff, Keller-AinfinityAlgebras}, operads and rewriting theory~\cite{}, combinatorial Hopf algebras~\cite{LodayRonco, ChatelPilaud, Pilaud-brickAlgebra}, diagonal harmonics~\cite{}, mathematical physics~\cite{ArkaniHamedBaiHeYan}, etc.
+Another striking illustration of the ubiquity of the associahedron lies in the theory of cluster algebras introduced by S.~Fomin and A.~Zelevinsky in~\cite{FominZelevinsky-ClusterAlgebrasI} with motivation coming from total positivity and canonical bases.
+Cluster algebras are commutative rings generated by variables obtained from an initial seed by the discrete dynamical process of seed mutations.
+Finite type cluster algebras, whose mutation graph is finite, were classified in~\cite{FominZelevinsky-ClusterAlgebrasII} using the Cartan-Killing classification for crystallographic root systems.
+Finite type cluster complexes were geometrically realized first by F.~Chapoton, S.~Fomin and A.~Zelevinsky~\cite{ChapotonFominZelevinsky} based on the $\b{d}$-vector fans~\cite{FominZelevinsky-YSystems, FominZelevinsky-ClusterAlgebrasII}, then by~C.~Hohlweg, C.~Lange and H.~Thomas~\cite{HohlwegLangeThomas} based on the Cambrian fans~\cite{Reading-CambrianLattices, ReadingSpeyer}, and finally by C.~Hohlweg, V.~Pilaud and S.~Stella~\cite{HohlwegPilaudStella} based on the $\b{g}$-vector fans~\cite{FominZelevinsky-ClusterAlgebrasIV} with respect to an arbitrary initial seed.
+The resulting polytopes are known as generalized associahedra, and the classical associahedra corresponds to the cluster algebras of type~$A$.
+
+This paper focuses on a recent construction of the associahedron that appeared in mathematical physics.
+Motivated by the prediction of the behavior of scattering particules, N.~Arkani-Hamed, Y.~Bai, S.~He, and G.~Yan recently described in~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} the kinetic associahedron.
+It is a class of polytopal realizations of the classical associahedron obtained as sections of a high-dimensional positive orthant with well-chosen affine subspaces.
+This construction provides a large degree of freedom in the choice of the parameters defining these affine subspaces and produces all polytopes whose normal fan is affinely equivalent to that of J.-L.~Loday's associahedron~\cite{Loday} (see \cref{subsec:typeConeAsso}).
+These realizations were then extended by V.~Bazier-Matte, G.~Douville, K.~Mousavand, H.~Thomas and E.~Yildirim~\cite{BazierMatteDouvilleMousavandThomasYildirim} in the context of finite type cluster algebras using tools from representation theory of quivers.
+More precisely, they fix a finite type cluster algebra~$\c{A}$ and consider the real euclidean space~$\R^\c{V}$ indexed by the set~$\c{V}$ of cluster variables of~$\c{A}$.
+Starting from an acyclic initial seed~$\seed_\circ$, they consider a certain set~$\c{M}$ of mesh relations and compute the corresponding linear relations between the $\b{g}$-vectors, interpreted as linear spaces in~$\R^\c{V}$.
+Finally, they perturb these mesh linear spaces by a collection~$\b{\ell} \in \R^{\c{M}}$ of positive constants and intersect the resulting perturbed affine mesh relations with the positive orthant of~$\R^\c{V}$ (see \cref{subsec:typeConeCA}).
+They show that the resulting polytope is always a generalized associahedron, and that its normal fan is the $\b{g}$-vector fan of~$\c{A}$ with respect to the initial acyclic seed~$\seed_\circ$.
+A by-product of their construction is that the space of all polytopal realizations of the $\b{g}$-vector fan of~$\c{A}$ with respect to the initial acyclic seed~$\seed_\circ$ is a simplicial cone.
+
+In this paper, we revisit, extend and explore further this construction using a different approach.
+Given a complete simplicial fan~$\Fan$, we consider its space~$\typeCone(\Fan)$ of polytopal realizations, called type-cone of~$\Fan$ in~\cite{McMullen-typeCone}.
+This type-cone is known to be a polyhedral cone defined by a collection of inequalities corresponding to the linear dependences among the rays of~$\Fan$ contained in pairs of adjacent maximal cones of~$\Fan$.
+Our approach is based on a simple but crucial observation: if the type-cone~$\typeCone(\Fan)$ is a simplicial cone, then all polytopal realizations of~$\Fan$ can be described as sections of a high dimensional positive orthant with a collection of affine subspaces corresponding to the facets of~$\typeCone(\Fan)$ (see \cref{coro:simplicialTypeCone}).
+To prove that the type-cone~$\typeCone(\Fan)$ is simplicial, we just need to identify which pairs of adjacent maximal cones of~$\Fan$ correspond to the facets of~$\typeCone(\Fan)$ and to show that the corresponding linear dependences among their rays positively span the linear dependence among the rays of any pair of adjacent maximal cones of~$\Fan$.
+
+%
+%
+%Their proof, based on representation theory of quivers, is subtle: on the one hand, only simply-laced types are explicitly treated and the remaining finite type are argued by folding; on the other hand, the technique requires to work with rational perturbations~$\b{\ell}$ and to conclude for arbitrary real perturbations by an approximation argument.
+
+%Is the realization space connected?
+
+%We explain recent results of~\cite{BazierMatteDouvilleMousavandThomasYildirim}. Some advantages of our approach are:
+%\begin{itemize}
+%\item We manage to extend their results to other families of $\b{g}$-vector fans: first to all $\b{g}$-vector fans of finite type cluster algebras acyclic or not (whose polytopality was only proved recently in~\cite{HohlwegPilaudStella}), then to all $\b{g}$-vector fans of the $\tau$-tilting finite gentle algebras (whose polytopality was proved recently in~\cite{PaluPilaudPlamondon-nonkissing}), and finally to the nested fans of graph associahedra (whose polytopality was studied in~\cite{CarrDevadoss, Devadoss, Postnikov, FeichtnerSturmfels, Zelevinsky}).
+%\item We have a simpler proof, only based on the transformation between the classical descriptions of a polytope of the form~$\set{\b{x} \in \R^n}{\b{G}\b{x} \le \b{h}}$ and~$\set{\b{z} \in \R^N}{\b{K}\b{z} = \b{K}\b{h} \text{ and } \b{z} \ge 0}$ (this transformation is standard in optimization).
 In particular, we do not need to consider only rational polytopes and pass to the limit to deal with all real descriptions.
-\item We observe that we obtain all realizations of the $\b{g}$-vector fans of the considered families.
-\end{itemize}
+%\item We observe that we obtain all realizations of the $\b{g}$-vector fans of the considered families.
+%\end{itemize}
 
@@
 Although we will only treat with simplicial fans, for completeness, note that \cref{prop:characterizationPolytopalFan} and \cref{def:typecone} can be easily adapted to non-simplicial fans.
-For an arbitrary complete fan, it suffices to consider consider any simplicial refinement, and set some of the strict inequalities of the definition of the type cone to equality.
+For an arbitrary complete fan, it suffices to consider any simplicial refinement, and set some of the strict inequalities of the definition of the type cone to equality.
 \begin{proposition}
@@
 Let~$\HH \eqdef \bigset{\b{x} \in \R^{n+1}}{\sum_{\ell \in [n+1]} x_\ell = 0}$ and~$\pi : \R^{n+1} \to \HH$ denote the orthogonal projection.
+The following fans are illustrated in \cref{fig:lodayFans} in dimension~$2$ and~$3$.
 
@@
 
-These fans are illustrated in \cref{fig:lodayFans} in dimension~$2$ and~$3$.
 Let us also recall the linear dependencies in this fan and observe that it has the unique exchange property discussed in \cref{subsec:uniqueExchangeProperty}.
@@
 \begin{example}
+\label{exm:typeConeAsso}
 Consider the fan~$\gvectorFan[2]$ and~$\gvectorFan[3]$ illustrated in \cref{fig:lodayFans}.
@@
 \noindent
+In all our tables, we just record the coefficients of the inequalities, which are then easily reconstructed.
+For instance, the inequality~$\red \circled{A}$ above is given by~$\b{h}_{\includegraphics[scale=.3]{diagonalA1}} + \b{h}_{\includegraphics[scale=.3]{diagonalA3}} > \b{h}_{\includegraphics[scale=.3]{diagonalA2}}$.
+
 The type cone of~$\gvectorFan[2]$ lives in~$\R^9$ and has a linearity space of dimension~$3$.
@@
 \text{$\b{g}$-vectors} & \compactVectorT{1}{0}{0} & \compactVectorT{0}{1}{0} & \compactVectorT{0}{0}{1} & \compactVectorT{-1}{1}{0} & \compactVectorT{0}{-1}{1} & \compactVectorT{-1}{0}{1} & \compactVectorT{-1}{0}{0} & \compactVectorT{0}{-1}{0} & \compactVectorT{0}{0}{-1} \\[.6cm]
-%\text{linearity}	& 0 & 1 & 0 & 1 & 0 & -1 & 0 & -1 & 0 \\
-%\text{space}		& 0 & 1 & 1 & 1 & 1 & 0 & 0 & -1 & -1 \\
-%					& 1 & 1 & 1 & 0 & 0 & 0 & -1 & -1 & -1 \\
 \text{facet}		& 1 & -1 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & \red \circled{A} \\
@@
 
-\begin{figure}
+\begin{figure}[h]
     \begin{adjustbox}{center}
@@
 
-We now describe the facets of this type cone~$\typeCone(\gvectorFan[n])$.
+Motivated by \cref{exm:typeConeAsso}, we now describe the facets of this type cone~$\typeCone(\gvectorFan[n])$.
 
@@
 \begin{corollary}[{\cite[Sect.~3.2]{ArkaniHamedBaiHeYan}}]
+\label{coro:allPolytopalRealizationsAsso}
 For~$n \in \N$, define~$X(n) \eqdef \set{(a,b)}{0 \le a < b \le n+2}$ and~$Y(n) \eqdef \set{(a,b)}{0 \le a < b-2 \le n}$.
@@
 \]
-is an $n$-dimensional associahedron.
+is an $n$-dimensional associahedron, whose normal fan is~$\gvectorFan[n]$.
+Moreover, the polytopes~$R_\b{\ell}(n)$ for~$\b{\ell} \in \R_{>0}^{Y(n)}$ describe all polytopal realizations of the fan~$\gvectorFan[n]$.
 \end{corollary}
+
+\vincent{Describe the rays of the type cone. They are the Minkowski basis.}
 
@@
 These polytopal realizations were first constructed for bipartite initial seeds by F.~Chapoton, S.~Fomin and A.~Zelevinsky~\cite{ChapotonFominZelevinsky} using the $\b{d}$-vector fans of~\cite{FominZelevinsky-YSystems}, then for acyclic initial seeds by C.~Hohlweg, C.~Lange and H.~Thomas~\cite{HohlwegLangeThomas} using Cambrian lattices and fans of N.~Reading and D.~Speyer~\cite{Reading-CambrianLattices, ReadingSpeyer}, and revisited by S.~Stella~\cite{Stella}, and by V.~Pilaud and C.~Stump~\cite{PilaudStump-brickPolytope} via brick polytopes, and finally for arbitrary initial seeds by C.~Hohlweg, V.~Pilaud and S.~Stella~\cite{HohlwegPilaudStella}.
-More recently in~\cite{BazierMatteDouvilleMousavandThomasYildirim}, V.~Bazier-Matte, G.~Douville, K.~Mousavand, H.~Thomas and E.~Yildirim extended the construction of associahedra of~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} to acyclic seeds of simply laced finite type cluster algebras.
-Here, we extend the construction of~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} to any finite type (simply laced or not) cluster algebra with respect to any seed (acyclic or not) by providing a direct proof that the type cone of the cluster fan of any finite type cluster algebra is simplicial.
+More recently in~\cite{BazierMatteDouvilleMousavandThomasYildirim}, V.~Bazier-Matte, G.~Douville, K.~Mousavand, H.~Thomas and E.~Yildirim extended the construction of associahedra of~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} to acyclic seeds of simply-laced finite type cluster algebras.
+Here, we extend the construction of~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} to any finite type (simply-laced or not) cluster algebra with respect to any seed (acyclic or not) by providing a direct proof that the type cone of the cluster fan of any finite type cluster algebra is simplicial.
 
@@
 \text{$\b{g}$-vectors} & \compactVectorT{1}{0}{0} & \compactVectorT{0}{1}{0} & \compactVectorT{0}{0}{1} & \compactVectorT{-1}{0}{1} & \compactVectorT{1}{-1}{0} & \compactVectorT{0}{1}{-1} & \compactVectorT{0}{0}{-1} & \compactVectorT{-1}{0}{0} & \compactVectorT{0}{-1}{0} \\[.6cm]
-%\text{linearity}	& 0 & 0 & 1 & 1 & 0 & -1 & -1 & 0 & 0 \\
-%\text{space}		& 0 & -1 & 0 & 0 & 1 & -1 & 0 & 0 & 1 \\
-%					& 1 & 1 & 0 & -1 & 0 & 1 & 0 & -1 & -1 \\[.2cm]
 \text{facet} 		& 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 1 & \red \circled{A} \\
@@
 \text{$\b{g}$-vectors} & \compactVectorT{1}{0}{0} & \compactVectorT{0}{1}{0} & \compactVectorT{0}{0}{1} & \compactVectorT{-1}{0}{1} & \compactVectorT{1}{-1}{0} & \compactVectorT{0}{2}{-1} & \compactVectorT{0}{1}{-1} & \compactVectorT{-1}{1}{0} & \compactVectorT{0}{-1}{0} & \compactVectorT{0}{0}{-1} & \compactVectorT{-2}{0}{1} & \compactVectorT{-1}{0}{0}  \\[.6cm]
-%\text{linearity}	& 1 & 1 & 2 & 1 & 0 & 0 & -1 & 0 & -1 & -2 & 0 & -1 \\
-%\text{space}		& 0 & 1 & 0 & 0 & -1 & 2 & 1 & 1 & -1 & 0 & 0 & 0 \\
-%					& 0 & 0 & -1 & -1 & 0 & 1 & 1 & 0 & 0 & 1 & -1 & 0 \\[.2cm]
 \text{facet}		& 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 1 & 0 & 0 & 0 & \red \circled{A} \\
@@
 \begin{proof}
-It follows from \cref{prop:meshMutations} that ...
-%Conversely, since~$\gvectorFan[n]$ has dimension~$n$ and~$n(n+3)/2$ rays (corresponding to the internal diagonals of the $(n+3)$-gon), we know from \cref{rem:dimTypeCone} that there are at least~$n(n+1)/2$ extremal exchangeable pairs.
-We thus conclude that all exchangeable pairs of diagonals~$\{(a,b-1), (a+1,b)\}$ for~$1 \le a < b-2 \le n$ are extremal.
-%
-%
-%Our next statement follows from~\cref{thm:extremalExchangeablePairsCA,lem:bijectionMeshMutations}.
-\end{proof}
-
-\vincent{Should we give a type $A$ intuition here?}
-%This statement will be proved in full generality in \cref{???}.
-%We proved it in \cref{prop:extremalExchangeablePairsAsso} for acyclic initial seeds in type~$A$. To provide an intuition of the result, we sketch here a proof for arbitrary initial seeds in type~$A$.
-%
-%\begin{proof}[Sketch of \cref{thm:extremalExchangeablePairsCA} in type~$A$]
-%We need to prove that the normal vector~$\b{n}(\B_\circ, y, y')$ for any exchangeable pair~$\{y,y'\}$ is a positive linear combination of the vectors~$\b{n}(\B_\circ, x, x')$ for non-initial meshes.
-%\vincent{Do we really want to do that?}
-%\end{proof}
+Since~$\gvectorFan[\B_\circ]$ has dimension~$n$ and~$|\principalVariables|$ rays (corresponding to the cluster variables), we know from \cref{rem:dimTypeCone} that there are at least~$|\principalVariables| - n$ extremal exchangeable pairs.
+Moreover, \cref{prop:meshMutations,lem:bijectionMeshMutations} ensure that there are at most $|\meshes| = |\principalVariables| - n$ extremal exchangeable pairs (corresponding to the non-initial mesh mutations).
+We conclude that all non-initial mesh mutations are extremal exchangeable pairs.
+\end{proof}
 
@@
 \begin{theorem}
+\label{thm:allPolytopalRealizationsCA}
 For any finite type exchange matrix~$\B_\circ$ (acyclic or not, simply-laced or not), and for any~$\b{\ell} \in \R_{>0}^{\meshes}$, the polytope
 \[
-R_{\b{\ell}}(\B_\circ) \eqdef \Bigset{\b{z} \in \R^{\principalVariables}}{\b{z} \ge 0 \text{ and } \b{z}_x + \b{z}_{x'} = \sum_{y \in \principalVariables} \alpha_{x,x',y} \, \b{z}_{y} \text{ for all } \{x,x'\} \in \meshes}
+R_{\b{\ell}}(\B_\circ) \eqdef \Bigset{\b{z} \in \R^{\principalVariables}}{\b{z} \ge 0 \text{ and } \b{z}_x + \b{z}_{x'} - \sum_{y \in \principalVariables} \alpha_{x,x',y} \, \b{z}_{y} = \b{\ell}_{\{x,x'\}} \text{ for all } \{x,x'\} \in \meshes}
 \]
 is a generalized associahedron, whose normal fan is the cluster fan~$\gvectorFan[\B_\circ]$.
+Moreover, the polytopes~$R_\b{\ell}(\B_\circ)$ for~$\b{\ell} \in \R_{>0}^{\meshes}$ describe all polytopal realizations of~$\gvectorFan[\B_\circ]$.
 \end{theorem}
+
+\begin{example}
+To complement \cref{subsec:typeConeAsso}, let us translate to diagonals and triangulations the result of \cref{thm:allPolytopalRealizationsCA} in type~$A$.
+Let~$n \ge 3$.
+Consider a convex $(n+3)$-gon whose vertices are labeled modulo~$n+3$ and whose internal and boundary diagonals are denoted by~$\Delta(n) \eqdef \binom{\Z/(n+3)\Z}{2}$.
+Consider a triangulation~$T$ of this polygon, formed by the $n+3$ boundary edges and $n$ internal diagonals of the $(n+3)$-gon.
+Then for any~$\b{\ell} \in \R_{>0}^{\Delta(n) \ssm T}$, the polytope
+\[
+R_\b{\ell}(T) \eqdef \Bigset{\b{z} \in \R^{\Delta(n)}}{\begin{array}{l} \b{z} \ge 0 \quad\text{ and }\quad \b{z}_{(a,b)} = 0 \text{ for all } (a,b) \in T \quad\text{ and }\quad \\ \b{z}_{(a,b)} + \b{z}_{(a-1,b-1)} - \b{z}_{(a,b-1)} - \b{z}_{(a-1,b)} = \b{\ell}_{(a,b)} \text{ for all } (a,b) \notin T \end{array}}
+\]
+is an associahedron whose normal fan is the $\b{g}$-vector fan~$\gvectorFan[T]$ with respect to the triangulation~$T$.
+Moreover, the polytopes~$R_\b{\ell}(T)$ for~$\b{\ell} \in \R_{>0}^{\Delta(n) \ssm T}$ describe all polytopal realizations of~$\gvectorFan[T]$.
+\end{example}
+
+\vincent{Describe the rays of the type cone. They are the Minkowski basis. Newton polytopes of $F$-polynomials.}
 
@@
 \text{$\b{g}$-vectors} & \compactVectorT{1}{0}{0} & \compactVectorT{0}{1}{0} & \compactVectorT{0}{0}{1} & \compactVectorT{1}{-1}{0} & \compactVectorT{0}{1}{-1} & \compactVectorT{-1}{0}{0} & \compactVectorT{0}{-1}{0} & \compactVectorT{0}{0}{-1} \\[.6cm]
-%\text{linearity}	& 0 & -1 & 0 & 1 & -1 & 0 & 1 & 0 \\
-%\text{space}		& 1 & 1 & 0 & 0 & 1 & -1 & -1 & 0 \\
-%					& 0 & 0 & 1 & 0 & -1 & 0 & 0 & -1 \\[.2cm]
 \text{facet}		& 0 & -1 & 1 & 0 & 1 & 0 & 0 & 0 & \red \circled{A} \\
@@
 \text{$\b{g}$-vectors} & \compactVectorT{1}{0}{0} & \compactVectorT{0}{1}{0} & \compactVectorT{0}{0}{1} & \compactVectorT{1}{-1}{0} & \compactVectorT{1}{0}{-1} & \compactVectorT{0}{-1}{1} & \compactVectorT{0}{1}{-1} & \compactVectorT{-1}{0}{1} & \compactVectorT{-1}{0}{0} & \compactVectorT{0}{-1}{0} & \compactVectorT{0}{0}{-1} \\[.6cm]
-%\text{linearity}	& 0 & -1 & 0 & 1 & 0 & 1 & -1 & 0 & 0 & 1 & 0 \\
-%\text{space}		& 1 & 0 & 0 & 1 & 1 & 0 & 0 & -1 & -1 & 0 & 0 \\
-%					& 1 & 0 & 1 & 1 & 0 & 1 & -1 & 0 & -1 & 0 & -1 \\[.2cm]
 \text{facet}		& -1 & 1 & 0 & 0 & 1 & 0 & -1 & 0 & 0 & 0 & 0 & \red \circled{A} \\
@@
 
-In this section, we need to restrict even further the family of gentle quivers we consider.
-\vincent{rephrase}
+In this section, we will restrict our attention to the following family of quivers.
 
@@
 We just need to prove that there exists a ridge~$R$ of~$\NKC$ containing both~$\hc{\sigma}$ and~$\ch{\sigma}$ and such that~$R \cup \{\cc{\sigma}\}$ and~$R \cup \{\hh{\sigma}\}$ are adjacent facets of~$\NKC$.
+
 \vincent{TODO}
@@
 If~$\lambda(\omega, \omega')$ is big enough, then the walk~$\omega$ (resp.~$\omega'$) is just obtained by adding two outgoing (resp.~incoming) blossoms at the end of~$\sigma$, thus $\omega = \cc{\sigma}$ (resp.~$\omega' = \hh{\sigma}$), and there is nothing to prove.
-Assume now that~$\omega \ne \hh{\sigma}$ (the situations where~$\omega' \ne \cc{\sigma}$ or~$\omega \ne \rho \sigma \hR$ are symmetric).
+Assume now that~$\omega \ne \hh{\sigma}$ (the situation where~$\omega' \ne \cc{\sigma}$ is symmetric).
 %Assume now that~$\omega \ne \hh{\sigma}$, for instance that~$\omega \ne \hL \sigma \tau$ (the situations where~$\omega' \ne \cc{\sigma}$ or~$\omega \ne \rho \sigma \hR$ are symmetric).
@@
 Conversely, we know from \cref{rem:dimTypeCone} that there are at least~$|\properWalks|-|Q_0|$ extremal exchangeable pairs.
-Since this~$|\strings| = |\distinguishableStrings| = |\properWalks| - |Q_0|$ by~\cref{prop:bijectionStringsWalks}, we conclude that all exchangeable pairs~$\{\cc{\sigma}, \hh{\sigma}\}$ for~$\sigma \in \strings$ are extremal.
-\end{proof}
-
-The following statement now follows from \cref{prop:bijectionStringsWalks,prop:extremalExchangeablePairsNKC}.
+Since~$|\strings| = |\distinguishableStrings| = |\properWalks| - |Q_0|$ by~\cref{prop:bijectionStringsWalks}, we conclude that all exchangeable pairs~$\{\cc{\sigma}, \hh{\sigma}\}$ for~$\sigma \in \strings$ are extremal.
+\end{proof}
+
+Our next statement follows from the end of the previous proof.
 
@@
 
-Combining \cref{coro:simplicialTypeCone}, \cref{coro:simplicialTypeConeNKC} and \cref{prop:extremalExchangeablePairsNKC}, we derive the following description of all polytopal realizations of the non-kissing fan~$\gvectorFan[\quiver]$ of a quiver~$\quiver$ with no self-kissing~walk.
+Combining \cref{coro:simplicialTypeCone,coro:simplicialTypeConeNKC,prop:extremalExchangeablePairsNKC}, we derive the following description of all polytopal realizations of the non-kissing fan~$\gvectorFan[\quiver]$ of a brick $2$-acyclic quiver~$\quiver$.
 
@@
 \end{remark}
+
+\vincent{Describe the rays of the type cone. They are the Minkowski basis.}
 
@@
 \[
-\begin{array}{r|c@{\;\;\;}c@{\;\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;}c@{\;}c@{\;}c@{\;}c@{\;\;}c@{\;\;}c@{\;\;}c}
-\text{tubes} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA1}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA2}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA3}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA4}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA5}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA6}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA7}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA8}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA9}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA10}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA11}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA12}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA13}}  \\[.6cm]
-\text{$\b{g}$-vectors} & \compactVectorT{1}{0}{0} & \compactVectorT{0}{1}{0} & \compactVectorT{0}{0}{1} & \compactVectorT{0}{2}{-1} & \compactVectorT{\nicefrac{1}{2}}{-1}{\nicefrac{1}{2}} & \compactVectorT{1}{-2}{0} & \compactVectorT{\nicefrac{1}{2}}{0}{\nicefrac{-1}{2}} & \compactVectorT{-1}{2}{0} & \compactVectorT{\nicefrac{-1}{2}}{0}{\nicefrac{1}{2}} & \compactVectorT{-1}{0}{0} & \compactVectorT{0}{-2}{1} & \compactVectorT{0}{-1}{0} & \compactVectorT{0}{0}{-1} \\[.6cm]
-%\text{linearity}	& 1 & 0 & 0 & 0 & 2 & 1 & 2 & -1 & -2 & -1 & 0 & 0 & 0 \\ 
-%\text{space}		& -2 & -1 & 0 & -2 & 0 & 0 & -4 & 0 & 4 & 2 & 2 & 1 & 0 \\
-%					& 0 & 0 & -1 & 1 & -2 & 0 & 2 & 0 & -2 & 0 & -1 & 0 & 1 \\[.2cm]
-\text{facet}		& 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & -2 & 1 \\
-\text{defining}		& 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 & 0 & 1 & 0 & -2 & 0 \\
-\text{inequalities}	& -1 & 2 & 0 & -1 & 0 & 0 & 2 & 0 & 0 & 0 & 0 & 0 & 0 \\
-					& 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 2 & -1 & -1 & 2 & 0 \\
-					& 0 & 0 & 0 & 0 & 0 & -1 & 2 & 0 & 0 & 0 & 0 & 2 & -1 \\
-					& -1 & 2 & -1 & 0 & 2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-					& -1 & 0 & 0 & 0 & 2 & -1 & 2 & 0 & 0 & 0 & 0 & 0 & 0 \\
-					& 0 & 2 & -1 & 0 & 0 & 0 & 0 & -1 & 1 & 0 & 0 & 0 & 0 \\
-					& 0 & 0 & -1 & 0 & 2 & 0 & 0 & 0 & 2 & 0 & -1 & 0 & 0 \\
-					& 0 & 0 & 0 & 0 & 2 & -1 & 0 & 0 & 0 & 0 & -1 & 2 & 0 \\
-					& 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & -2 & 1 & 0 & 0 & 0 \\
-					& 0 & 0 & 1 & 0 & -2 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-					& 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & -2 & 0 & 1 & 0 & 0 \\
-					& 1 & 0 & 0 & 0 & 0 & 0 & -2 & 0 & 0 & 0 & 0 & 0 & 1 \\
-					& 1 & 0 & 0 & 0 & -2 & 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 \\
-					& 1 & -2 & 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 \\
+\begin{array}{r|c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c}
+\text{tubes} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeA1}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeA2}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeA3}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeA4}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeA5}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeA6}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeA7}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeA8}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeA9}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeA10}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeA11}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeA12}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeA13}}  \\[.6cm]
+\text{$\b{g}$-vectors} & \compactVectorT{1}{0}{0} & \compactVectorT{0}{2}{0} & \compactVectorT{0}{0}{1} & \compactVectorT{0}{2}{-1} & \compactVectorT{1}{-2}{1} & \compactVectorT{1}{-2}{0} & \compactVectorT{1}{0}{-1} & \compactVectorT{-1}{2}{0} & \compactVectorT{-1}{0}{1} & \compactVectorT{-1}{0}{0} & \compactVectorT{0}{-2}{1} & \compactVectorT{0}{-2}{0} & \compactVectorT{0}{0}{-1} \\[.6cm]
+\text{facet}		& 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & -1 & 1 \\
+\text{defining}		& 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 & 0 & 1 & 0 & -1 & 0 \\
+\text{inequalities}	& -1 & 1 & 0 & -1 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 \\
+					& 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & -1 & -1 & 1 & 0 \\
+					& 0 & 0 & 0 & 0 & 0 & -1 & 1 & 0 & 0 & 0 & 0 & 1 & -1 \\
+					& -1 & 1 & -1 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+					& -1 & 0 & 0 & 0 & 1 & -1 & 1 & 0 & 0 & 0 & 0 & 0 & 0 \\
+					& 0 & 1 & -1 & 0 & 0 & 0 & 0 & -1 & 1 & 0 & 0 & 0 & 0 \\
+					& 0 & 0 & -1 & 0 & 1 & 0 & 0 & 0 & 1 & 0 & -1 & 0 & 0 \\
+					& 0 & 0 & 0 & 0 & 1 & -1 & 0 & 0 & 0 & 0 & -1 & 1 & 0 \\
+					& 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & -1 & 1 & 0 & 0 & 0 \\
+					& 0 & 0 & 1 & 0 & -1 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+					& 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & -1 & 0 & 1 & 0 & 0 \\
+					& 1 & 0 & 0 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 0 & 0 & 1 \\
+					& 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 \\
+					& 1 & -1 & 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 \\
 					& 0 & 0 & 0 & 1 & 0 & 0 & 0 & -1 & 0 & 1 & 0 & 0 & -1 \\
-					& 0 & 0 & 0 & 1 & 0 & 1 & -2 & 0 & 0 & 0 & 0 & 0 & 0 \\
-					& 0 & -2 & 1 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\[.2cm]
+					& 0 & 0 & 0 & 1 & 0 & 1 & -1 & 0 & 0 & 0 & 0 & 0 & 0 \\
+					& 0 & -1 & 1 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\[.2cm]
 \end{array}
@@
 %sage: M = Matrix([g_vector_GA(G, (1,)), g_vector_GA(G, (1,2)), g_vector_GA(G, (1,2,3)), [1,1,1,1]]).inverse()
+%sage: rays = {tuple(tube) : (g_vector_GA(G, tube)*M)[:-1] for tube in tubes(G)}
 %sage: rays
@@
 
-\vincent{Should only be 1 and -1...}
+\medskip
 \noindent
@@
 \[
-\begin{array}{r|c@{\;\;\;}c@{\;\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;}c@{\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c}
-\text{tubes} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB1}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB2}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB3}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB4}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB5}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB6}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB7}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB8}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB9}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB10}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB11}} \\[.6cm]
-\text{$\b{g}$-vectors} & \compactVectorT{1}{0}{0} & \compactVectorT{0}{1}{0} & \compactVectorT{0}{0}{1} & \compactVectorT{\nicefrac{1}{2}}{-1}{\nicefrac{1}{2}} & \compactVectorT{1}{-2}{0} & \compactVectorT{-1}{2}{0} & \compactVectorT{\nicefrac{-1}{2}}{0}{\nicefrac{1}{2}} & \compactVectorT{-1}{0}{0} & \compactVectorT{0}{-2}{1} & \compactVectorT{0}{-1}{0} & \compactVectorT{0}{0}{-1} \\[.6cm]
-%\text{linearity}	& 0 & 1 & 0 & -4 & -2 & 2 & 0 & 0 & -2 & -1 & 0 \\
-%\text{space}		& 1 & 0 & 0 & 2 & 1 & -1 & -2 & -1 & 0 & 0 & 0 \\
-%					& 1 & 0 & 1 & 4 & 1 & -1 & 0 & -1 & 1 & 0 & -1 \\[.2cm]
-\text{facet}		& -1 & 2 & -1 & 2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-\text{defining}		& 1 & -2 & 0 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 \\
-\text{inequalities}	& 0 & 2 & -1 & 0 & 0 & -1 & 2 & 0 & 0 & 0 & 0 \\
-					& 1 & 0 & 0 & -2 & 0 & 0 & 0 & 0 & 1 & 0 & 0 \\
-					& 0 & 0 & -1 & 2 & 0 & 0 & 2 & 0 & -1 & 0 & 0 \\
-					& 0 & 0 & 0 & 2 & -1 & 0 & 0 & 0 & -1 & 2 & 0 \\
-					& 0 & 0 & 0 & 0 & 0 & 1 & -2 & 0 & 1 & 0 & 0 \\
-					& 0 & 0 & 0 & 0 & 0 & 0 & 2 & -1 & -1 & 2 & 0 \\
-					& 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & -2 & 1 \\
-					& 0 & 0 & 0 & 0 & 1 & 0 & 0 & 1 & 0 & -2 & 0 \\
-					& 0 & 0 & 1 & 0 & 0 & 0 & -2 & 1 & 0 & 0 & 0 \\
-					& 0 & 0 & 1 & -2 & 1 & 0 & 0 & 0 & 0 & 0 & 0 \\[.2cm]
+\begin{array}{r|c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c}
+\text{tubes} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeB1}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeB2}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeB3}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeB4}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeB5}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeB6}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeB7}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeB8}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeB9}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeB10}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeB11}} \\[.6cm]
+\text{$\b{g}$-vectors} & \compactVectorT{1}{0}{0} & \compactVectorT{0}{2}{0} & \compactVectorT{0}{0}{1} & \compactVectorT{1}{-2}{1} & \compactVectorT{1}{-2}{0} & \compactVectorT{-1}{2}{0} & \compactVectorT{-1}{0}{1} & \compactVectorT{-1}{0}{0} & \compactVectorT{0}{-2}{1} & \compactVectorT{0}{-2}{0} & \compactVectorT{0}{0}{-1} \\[.6cm]
+\text{facet}		& -1 & 1 & -1 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+\text{defining}		& 1 & -1 & 0 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 \\
+\text{inequalities}	& 0 & 1 & -1 & 0 & 0 & -1 & 1 & 0 & 0 & 0 & 0 \\
+					& 1 & 0 & 0 & -1 & 0 & 0 & 0 & 0 & 1 & 0 & 0 \\
+					& 0 & 0 & -1 & 1 & 0 & 0 & 1 & 0 & -1 & 0 & 0 \\
+					& 0 & 0 & 0 & 1 & -1 & 0 & 0 & 0 & -1 & 1 & 0 \\
+					& 0 & 0 & 0 & 0 & 0 & 1 & -1 & 0 & 1 & 0 & 0 \\
+					& 0 & 0 & 0 & 0 & 0 & 0 & 1 & -1 & -1 & 1 & 0 \\
+					& 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & -1 & 1 \\
+					& 0 & 0 & 0 & 0 & 1 & 0 & 0 & 1 & 0 & -1 & 0 \\
+					& 0 & 0 & 1 & 0 & 0 & 0 & -1 & 1 & 0 & 0 & 0 \\
+					& 0 & 0 & 1 & -1 & 1 & 0 & 0 & 0 & 0 & 0 & 0 \\[.2cm]
 \end{array}
@@
 %12
+\medskip
 \end{example}

### 2019-04-08 thirdPaper/draft/typeConeAssociahedra.tex

@@
 Although we will only treat with simplicial fans, for completeness, note that \cref{prop:characterizationPolytopalFan} and \cref{def:typecone} can be easily adapted to non-simplicial fans.
-For an arbitrary complete fan, it suffices to consider any simplicial refinement, and set some of the strict inequalities of the definition of the type cone to equality.
+To describe the type-cone of an arbitrary complete fan, it suffices to consider any simplicial refinement, and to set some of the strict inequalities of the definition of the type cone to equality.
 \begin{proposition}
@@
 \end{itemize}
+
+\begin{example}\label{ex:typecone}
+Consider the $2$-dimensional fan~$\Fan$ depicted in \cref{fig:typecone} (left) (we will encounter this fan again in \cref{exm:typeConeAsso}).
+It has five rays $v_1,\dots,v_5$ and five maximal cones $a,\dots, e$.
+Its type-cone lies in~$\R^5$, but has a $2$-dimensional linearity space.
+It suffices to study $\b{K}\ctypeCone(\Fan)$ which is an essential simplicial cone in~$\R^3$.
+One can further reduce the dimension by intersecting with a transversal hyperplane, to get a $2$-dimensional representation.
+This is the triangle that is depicted in \cref{fig:typecone} (right).
+The five pairs of adjacent maximal cones give rise to five defining inequalities for $\ctypeCone(\Fan)$, although only three are non-redundant.
+If $H_{ij}$ is the hyperplane supporting the inequality given by the two adjacent maximal cones~$i$ and~$j$, then only $H_{ab}$, $H_{cd}$ and $H_{bc}$ support facets of the type-cone.
+The relative interior of the three facets of~$\ctypeCone(\Fan)$ are the type-cones of three coarsenings of~$\Fan$, obtained by merging certain adjacent maximal cones (those that are extremal).
+One of the rays generating~$\b{K}\ctypeCone(\Fan)$ corresponds to a $2$-dimensional simplex, and its normal fan is obtained by merging two pairs of extremal adjacent maximal cones.
+The two remaining rays lie not only in the hyperplanes~$H_{ij}$ defining the facets it belongs to, but also one extra such hyperplane.
+Its normal fan has only two cones, one arising as a merging of three cones and one arising as a merging of two cones.
+These fans are not essential, they have a one-dimensional linearity.
+Hence, the corresponding polytopes are not full-dimensional, they are of codimension~$1$.
+
+\begin{figure}[htpb]
+	\capstart
+	\centerline{{\includegraphics[width=.3\linewidth]{typeconeFan}}\hspace{1.5cm}\includegraphics[width=.4\linewidth]{typecone}}
+	\caption{A complete $2$-dimensional fan~$\Fan$ with five rays $v_1,\dots,v_5$ and five maximal cones $a,\dots, e$.
+We depict the intersection of $\b{K}\ctypeCone(F)$ with a hyperplane to get a $2$-dimensional slice.
+On top of each face of $\ctypeCone(F)$, and example of polytope with the corresponding normal fan is depicted.}
+	\label{fig:typecone}
+\end{figure}
+
+\end{example}
 

### 2019-04-09 thirdPaper/draft/typeConeAssociahedra.tex
type-cone

@@
 
-% Type-cone
-\newcommand{\typeCone}{\mathbb{TC}} % type-cone
-\newcommand{\ctypeCone}{\overline{\mathbb{TC}}} % type-cone
+% Type cone
+\newcommand{\typeCone}{\mathbb{TC}} % type cone
+\newcommand{\ctypeCone}{\overline{\mathbb{TC}}} % type cone
 \newcommand{\compatibilityDegree}[2]{(#1\,\|\,#2)} % compatibility degree
@@
 In this paper, we revisit, extend and explore further this construction using a different approach.
-Given a complete simplicial fan~$\Fan$, we consider its space~$\typeCone(\Fan)$ of polytopal realizations, called type-cone of~$\Fan$ in~\cite{McMullen-typeCone}.
-This type-cone is known to be a polyhedral cone defined by a collection of inequalities corresponding to the linear dependences among the rays of~$\Fan$ contained in pairs of adjacent maximal cones of~$\Fan$.
-Our approach is based on a simple but crucial observation: if the type-cone~$\typeCone(\Fan)$ is a simplicial cone, then all polytopal realizations of~$\Fan$ can be described as sections of a high dimensional positive orthant with a collection of affine subspaces corresponding to the facets of~$\typeCone(\Fan)$ (see \cref{coro:simplicialTypeCone}).
-To prove that the type-cone~$\typeCone(\Fan)$ is simplicial, we just need to identify which pairs of adjacent maximal cones of~$\Fan$ correspond to the facets of~$\typeCone(\Fan)$ and to show that the corresponding linear dependences among their rays positively span the linear dependence among the rays of any pair of adjacent maximal cones of~$\Fan$.
+Given a complete simplicial fan~$\Fan$, we consider its space~$\typeCone(\Fan)$ of polytopal realizations, called type cone of~$\Fan$ in~\cite{McMullen-typeCone}.
+This type cone is known to be a polyhedral cone defined by a collection of inequalities corresponding to the linear dependences among the rays of~$\Fan$ contained in pairs of adjacent maximal cones of~$\Fan$.
+Our approach is based on a simple but crucial observation: if the type cone~$\typeCone(\Fan)$ is a simplicial cone, then all polytopal realizations of~$\Fan$ can be described as sections of a high dimensional positive orthant with a collection of affine subspaces corresponding to the facets of~$\typeCone(\Fan)$ (see \cref{coro:simplicialTypeCone}).
+To prove that the type cone~$\typeCone(\Fan)$ is simplicial, we just need to identify which pairs of adjacent maximal cones of~$\Fan$ correspond to the facets of~$\typeCone(\Fan)$ and to show that the corresponding linear dependences among their rays positively span the linear dependence among the rays of any pair of adjacent maximal cones of~$\Fan$.
 
@@
 
-\subsection{Type-cone}
-\arnau{McMullen uses a dash between type and cone. Should we do it too?}
+\subsection{Type cone}
+
 Fix an essential complete simplicial fan~$\Fan$ in~$\R^n$.
@@
 \begin{definition}\label{def:typecone}
-The \defn{type-cone} of~$\Fan$ is the cone~$\typeCone(\Fan)$ of all $\Fan$-admissible height vectors~$\b{h}$:
+The \defn{type cone} of~$\Fan$ is the cone~$\typeCone(\Fan)$ of all $\Fan$-admissible height vectors~$\b{h}$:
 \begin{align*}
@@
 
-Note that the type-cone is an open cone and contains a linearity subspace of dimension~$n$ (it is invariant by translation in~$\b{G} \R^n$). 
+Note that the type cone is an open cone and contains a linearity subspace of dimension~$n$ (it is invariant by translation in~$\b{G} \R^n$). 
 % We could thus intersect~$\typeCone(\Fan)$ with the kernel of~$\b{G}$, or consider the projection~$\b{K}\typeCone(\Fan)$.
@@
 
-We denote by $\ctypeCone(\Fan)$ the closure of $\typeCone(\Fan)$, and call it the \defn{closed type-cone} of~$\Fan$.
+We denote by $\ctypeCone(\Fan)$ the closure of $\typeCone(\Fan)$, and call it the \defn{closed type cone} of~$\Fan$.
 It is the closed polyhedral cone defined by the inequalities $\sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} \geq 0$ for adjacent maximal cones~$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$.
@@
 Although we will only treat with simplicial fans, for completeness, note that \cref{prop:characterizationPolytopalFan} and \cref{def:typecone} can be easily adapted to non-simplicial fans.
-To describe the type-cone of an arbitrary complete fan, it suffices to consider any simplicial refinement, and to set some of the strict inequalities of the definition of the type cone to equality.
+To describe the type cone of an arbitrary complete fan, it suffices to consider any simplicial refinement, and to set some of the strict inequalities of the definition of the type cone to equality.
 \begin{proposition}
@@
  Let $\Fan'$ be a complete fan that coarsens the essential complete simplicial fan~$\Fan$.
- The \defn{type-cone}~$\typeCone(\Fan')$ of all $\Fan'$-admissible height vectors~$\b{h}$ is
+ The \defn{type cone}~$\typeCone(\Fan')$ of all $\Fan'$-admissible height vectors~$\b{h}$ is
  \begin{align*}
@@
 \begin{definition}
-An \defn{extremal adjacent pair} of~$\Fan$ is a pair of adjacent maximal cones~$\{\R_{\ge0}\rays, \R_{\ge0}\rays'\}$ of~$\Fan$ such that the corresponding inequality $\sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} \geq 0$ in the definition of the type-cone~$\ctypeCone(\Fan)$ actually defines a facet of~$\ctypeCone(\Fan)$.
+An \defn{extremal adjacent pair} of~$\Fan$ is a pair of adjacent maximal cones~$\{\R_{\ge0}\rays, \R_{\ge0}\rays'\}$ of~$\Fan$ such that the corresponding inequality $\sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} \geq 0$ in the definition of the type cone~$\ctypeCone(\Fan)$ actually defines a facet of~$\ctypeCone(\Fan)$.
 \end{definition}
@@
 
-In other words, extremal adjacent pairs define the extremal rays of the polar of the closed type-cone~$\ctypeCone(\Fan)$.
-Understanding the extremal adjacent pairs of~$\Fan$ enables to describe its type-cone~$\typeCone(\Fan)$ and thus all its polytopal realizations.
+In other words, extremal adjacent pairs define the extremal rays of the polar of the closed type cone~$\ctypeCone(\Fan)$.
+Understanding the extremal adjacent pairs of~$\Fan$ enables to describe its type cone~$\typeCone(\Fan)$ and thus all its polytopal realizations.
 
@@
 \label{rem:dimTypeCone}
-Since the type-cone is an~$N$ dimensional cone with a linearity subspace of dimension~$n$, it has at least~$N-n$ facets.
-We say that the type-cone is \defn{simplicial} when it has precisely $N-n$ facets.
+Since the type cone is an~$N$ dimensional cone with a linearity subspace of dimension~$n$, it has at least~$N-n$ facets.
+We say that the type cone is \defn{simplicial} when it has precisely $N-n$ facets.
 \end{remark}
@@
 
-When~$\Fan$ has the unique exchange relation property, we change the notation~$\coefficient[{\ray[s]}][\rays][\rays']$ to~$\coefficient$ and we obtain that the type-cone of~$\Fan$ is expressed as
+When~$\Fan$ has the unique exchange relation property, we change the notation~$\coefficient[{\ray[s]}][\rays][\rays']$ to~$\coefficient$ and we obtain that the type cone of~$\Fan$ is expressed as
 \[
@@
 \begin{definition}
-In a fan~$\Fan$ with the unique exchange relation property, an \defn{extremal exchangeable pair} is a pair of exchangeable rays~$\{\ray,\ray'\}$ such that the corresponding inequality~${\sum_{\ray[s] \in \rays \cup \rays'} \coefficient \, \b{h}_{\ray[s]} \geq  0}$ defines a facet of the closed type-cone~$\ctypeCone(\Fan)$.
+In a fan~$\Fan$ with the unique exchange relation property, an \defn{extremal exchangeable pair} is a pair of exchangeable rays~$\{\ray,\ray'\}$ such that the corresponding inequality~${\sum_{\ray[s] \in \rays \cup \rays'} \coefficient \, \b{h}_{\ray[s]} \geq  0}$ defines a facet of the closed type cone~$\ctypeCone(\Fan)$.
 \end{definition}
@@
 In this section, we provide alternative polytopal realizations of the fan~$\Fan$.
-We also discuss the behavior of these realizations in the situation when the type-cone~$\typeCone(\Fan)$ is simplicial.
+We also discuss the behavior of these realizations in the situation when the type cone~$\typeCone(\Fan)$ is simplicial.
 
@@
 \label{coro:simplicialTypeCone}
-Assume that the type-cone~$\typeCone(\Fan)$ is simplicial and let~$\b{K}$ be the $(N-n) \times N$-matrix whose rows are the outer normal vectors of the facets of~$\typeCone(\Fan)$. Then the polytope
+Assume that the type cone~$\typeCone(\Fan)$ is simplicial and let~$\b{K}$ be the $(N-n) \times N$-matrix whose rows are the outer normal vectors of the facets of~$\typeCone(\Fan)$. Then the polytope
 \[
@@
 Since~$\b{K}$ has full rank there exists~$\b{h} \in \R^N$ such that~$\b{K}\b{h} = \b{\ell}$.
-Since~$\b{K}\b{h} \ge 0$ and the rows of~$\b{K}$ are precisely all outer normal vectors of the facets of the type-cone~$\typeCone(\Fan)$, we obtain that~$\b{h}$ belongs to~$\typeCone(\Fan)$.
+Since~$\b{K}\b{h} \ge 0$ and the rows of~$\b{K}$ are precisely all outer normal vectors of the facets of the type cone~$\typeCone(\Fan)$, we obtain that~$\b{h}$ belongs to~$\typeCone(\Fan)$.
 Since $R_\b{\ell} = Q_\b{h} \sim P_\b{h}$ by \cref{prop:alternativePolytopalRealization}, we conclude that~$R_\b{\ell}$ is a polytopal realization of~$\Fan$.
@@
 
-\subsection{Faces of the type-cone}
+\subsection{Faces of the type cone}
 
 \begin{theorem}
- Let $\Fan$ be a polytopal fan. Then the relatively open faces of~$\ctypeCone(\Fan)$ are the type-cones of all (polytopal) coarsenings of~$\Fan$. 
+ Let $\Fan$ be a polytopal fan. Then the relatively open faces of~$\ctypeCone(\Fan)$ are the type cones of all (polytopal) coarsenings of~$\Fan$. 
 \end{theorem}
@@
  Let $\Fan'$ be a simplicial refinement of $\Fan$.
-By~\cref{prop:non-simplicial}, the type-cone of any coarsening of $\Fan$ is a relatively open cell of the hyperplane arrangement defined by adjacent pairs of~$\Fan'$.
-The type-cone of the coarsening is not empty whenever it is polytopal.
+By~\cref{prop:non-simplicial}, the type cone of any coarsening of $\Fan$ is a relatively open cell of the hyperplane arrangement defined by adjacent pairs of~$\Fan'$.
+The type cone of the coarsening is not empty whenever it is polytopal.
 When non-empty, distinct coarsenings give rise to distinct cells (one will have an equation that is a strict inequality in the other).
@@
 It has five rays $v_1,\dots,v_5$ and five maximal cones $a,\dots, e$.
-Its type-cone lies in~$\R^5$, but has a $2$-dimensional linearity space.
+Its type cone lies in~$\R^5$, but has a $2$-dimensional linearity space.
 It suffices to study $\b{K}\ctypeCone(\Fan)$ which is an essential simplicial cone in~$\R^3$.
@@
 The five pairs of adjacent maximal cones give rise to five defining inequalities for $\ctypeCone(\Fan)$, although only three are non-redundant.
-If $H_{ij}$ is the hyperplane supporting the inequality given by the two adjacent maximal cones~$i$ and~$j$, then only $H_{ab}$, $H_{cd}$ and $H_{bc}$ support facets of the type-cone.
-The relative interior of the three facets of~$\ctypeCone(\Fan)$ are the type-cones of three coarsenings of~$\Fan$, obtained by merging certain adjacent maximal cones (those that are extremal).
+If $H_{ij}$ is the hyperplane supporting the inequality given by the two adjacent maximal cones~$i$ and~$j$, then only $H_{ab}$, $H_{cd}$ and $H_{bc}$ support facets of the type cone.
+The relative interior of the three facets of~$\ctypeCone(\Fan)$ are the type cones of three coarsenings of~$\Fan$, obtained by merging certain adjacent maximal cones (those that are extremal).
 One of the rays generating~$\b{K}\ctypeCone(\Fan)$ corresponds to a $2$-dimensional simplex, and its normal fan is obtained by merging two pairs of extremal adjacent maximal cones.
@@
 We say that~$P$ is a \defn{Minkowski summand} of~$R$ if there is a polytope~$Q$ such that $R=P+Q$, and a \defn{weak Minkowski summand} if there is a $\lambda \ge 0$ and a polytope~$Q$ such that ${\lambda R = P + Q}$.
-\cref{lem:MinkowskiSum} ensures that convex combinations in the type-cone correspond to Minkowski combinations of polytopes.
-Actually, the set of weak Minkowski summands of a polytope $P$ with normal fan~$\Fan$ is isomorphic to the closed type-cone~$\ctypeCone(\Fan)$ modulo linearity (the cone of weak Minkowski summands was studied by W.~Meyer in~\cite{Meyer}, to see that it is equivalent to the type-cone and other formulations, see for example the appendix of~\cite{PostnikovReinerWilliams}).
-
-This provides natural Minkowski summands for all polytopal realizations of~$\Fan$: the rays of the closed 6type-cone.
+\cref{lem:MinkowskiSum} ensures that convex combinations in the type cone correspond to Minkowski combinations of polytopes.
+Actually, the set of weak Minkowski summands of a polytope $P$ with normal fan~$\Fan$ is isomorphic to the closed type cone~$\ctypeCone(\Fan)$ modulo linearity (the cone of weak Minkowski summands was studied by W.~Meyer in~\cite{Meyer}, to see that it is equivalent to the type cone and other formulations, see for example the appendix of~\cite{PostnikovReinerWilliams}).
+
+This provides natural Minkowski summands for all polytopal realizations of~$\Fan$: the rays of the closed 6type cone.
 These correspond to indecomposable polytopes, see~\cite{Meyer} or \cite{McMullen-typeCone}.
@@
 \arnau{This has consequences in expressing volume and other valuations! I have to have a look at it.}
-In the particular case when the type-cone is simplicial, then we can get rid of the Minkowski differences.
+In the particular case when the type cone is simplicial, then we can get rid of the Minkowski differences.
 
 \begin{corollary}
-If the type-cone~$\typeCone(\Fan)$ of $\Fan$ is simplicial, then the $N-n$ idecomposable polytopes $P_{\b{h}_1},\dots, P_{\b{h}_{N-n}}$ arising from the rays of $\ctypeCone(\Fan)$ verify that 
+If the type cone~$\typeCone(\Fan)$ of $\Fan$ is simplicial, then the $N-n$ idecomposable polytopes $P_{\b{h}_1},\dots, P_{\b{h}_{N-n}}$ arising from the rays of $\ctypeCone(\Fan)$ verify that 
 \begin{enumerate}[(i)]
@@
 
-Note that such a family of polytopes giving rise to unique positive representations only exists when the type-cone is simplicial (both unicity and positivity only happen when the type-cone is simplicial).
+Note that such a family of polytopes giving rise to unique positive representations only exists when the type cone is simplicial (both unicity and positivity only happen when the type cone is simplicial).
 

### 2019-04-09 thirdPaper/draft/typeConeAssociahedra.tex
intro CA

@@
 {\LARGE\sffamily\centering}}
-\@addtoreset{section}{part}
+%\@addtoreset{section}{part}
 \makeatother
-\renewcommand{\thesection}{\arabic{part}.\arabic{section}}
+\renewcommand{\thepart}{\Roman{part}}
+%\renewcommand{\thesection}{\arabic{part}.\arabic{section}}
 
@@
 
+\vspace{-.5cm}
+
 \tableofcontents
@@
 \newpage
+
+\section*{Introduction}
 
@@
 Finite type cluster algebras, whose mutation graph is finite, were classified in~\cite{FominZelevinsky-ClusterAlgebrasII} using the Cartan-Killing classification for crystallographic root systems.
-Finite type cluster complexes were geometrically realized first by F.~Chapoton, S.~Fomin and A.~Zelevinsky~\cite{ChapotonFominZelevinsky} based on the $\b{d}$-vector fans~\cite{FominZelevinsky-YSystems, FominZelevinsky-ClusterAlgebrasII}, then by~C.~Hohlweg, C.~Lange and H.~Thomas~\cite{HohlwegLangeThomas} based on the Cambrian fans~\cite{Reading-CambrianLattices, ReadingSpeyer}, and finally by C.~Hohlweg, V.~Pilaud and S.~Stella~\cite{HohlwegPilaudStella} based on the $\b{g}$-vector fans~\cite{FominZelevinsky-ClusterAlgebrasIV} with respect to an arbitrary initial seed.
+Finite type cluster complexes were geometrically realized first by F.~Chapoton, S.~Fomin and A.~Zelevinsky~\cite{ChapotonFominZelevinsky} based on the $\b{d}$-vector fans~\cite{FominZelevinsky-YSystems, FominZelevinsky-ClusterAlgebrasII} of the bipartite initial seed, then by~C.~Hohlweg, C.~Lange and H.~Thomas~\cite{HohlwegLangeThomas} based on the Cambrian fans~\cite{Reading-CambrianLattices, ReadingSpeyer} of acyclic initial seeds, and finally by C.~Hohlweg, V.~Pilaud and S.~Stella~\cite{HohlwegPilaudStella} based on the $\b{g}$-vector fans~\cite{FominZelevinsky-ClusterAlgebrasIV} with respect to an arbitrary initial seed.
 The resulting polytopes are known as generalized associahedra, and the classical associahedra corresponds to the cluster algebras of type~$A$.
 
-This paper focuses on a recent construction of the associahedron that appeared in mathematical physics.
+This paper focuses on a surprising construction of the associahedron that recently appeared in mathematical physics.
 Motivated by the prediction of the behavior of scattering particules, N.~Arkani-Hamed, Y.~Bai, S.~He, and G.~Yan recently described in~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} the kinetic associahedron.
@@
 More precisely, they fix a finite type cluster algebra~$\c{A}$ and consider the real euclidean space~$\R^\c{V}$ indexed by the set~$\c{V}$ of cluster variables of~$\c{A}$.
-Starting from an acyclic initial seed~$\seed_\circ$, they consider a certain set~$\c{M}$ of mesh relations and compute the corresponding linear relations between the $\b{g}$-vectors, interpreted as linear spaces in~$\R^\c{V}$.
-Finally, they perturb these mesh linear spaces by a collection~$\b{\ell} \in \R^{\c{M}}$ of positive constants and intersect the resulting perturbed affine mesh relations with the positive orthant of~$\R^\c{V}$ (see \cref{subsec:typeConeCA}).
+Starting from an acyclic initial seed~$\seed_\circ$, they consider a certain set~$\c{M}$ of mesh mutations and compute the corresponding linear dependences between the $\b{g}$-vectors, that can be interpreted as linear spaces in~$\R^\c{V}$.
+Finally, they perturb these mesh linear spaces by a collection~$\b{\ell} \in \R^{\c{M}}$ of positive parameters and intersect the resulting perturbed mesh affine spaces with the positive orthant of~$\R^\c{V}$ (see \cref{subsec:typeConeCA}).
 They show that the resulting polytope is always a generalized associahedron, and that its normal fan is the $\b{g}$-vector fan of~$\c{A}$ with respect to the initial acyclic seed~$\seed_\circ$.
@@
 
-In this paper, we revisit, extend and explore further this construction using a different approach.
-Given a complete simplicial fan~$\Fan$, we consider its space~$\typeCone(\Fan)$ of polytopal realizations, called type cone of~$\Fan$ in~\cite{McMullen-typeCone}.
-This type cone is known to be a polyhedral cone defined by a collection of inequalities corresponding to the linear dependences among the rays of~$\Fan$ contained in pairs of adjacent maximal cones of~$\Fan$.
-Our approach is based on a simple but crucial observation: if the type cone~$\typeCone(\Fan)$ is a simplicial cone, then all polytopal realizations of~$\Fan$ can be described as sections of a high dimensional positive orthant with a collection of affine subspaces corresponding to the facets of~$\typeCone(\Fan)$ (see \cref{coro:simplicialTypeCone}).
+In this paper, we revisit, extend and explore further this construction using an reversed approach.
+Given a complete simplicial fan~$\Fan$, we consider the space~$\typeCone(\Fan)$ of all its polytopal realizations, called type cone of~$\Fan$ in~\cite{McMullen-typeCone}.
+This type cone is known to be a polyhedral cone defined by a collection of inequalities corresponding to the linear dependences among the rays of~$\Fan$ contained in pairs of adjacent maximal cones of~$\Fan$ (see \cref{def:typeCone}).
+Our approach is based on an elementary but powerful observation: if the type cone~$\typeCone(\Fan)$ is a simplicial cone, then all polytopal realizations of~$\Fan$ can be described as sections of a high dimensional positive orthant with a collection of affine subspaces corresponding to the facets of~$\typeCone(\Fan)$ (see \cref{coro:simplicialTypeCone}).
 To prove that the type cone~$\typeCone(\Fan)$ is simplicial, we just need to identify which pairs of adjacent maximal cones of~$\Fan$ correspond to the facets of~$\typeCone(\Fan)$ and to show that the corresponding linear dependences among their rays positively span the linear dependence among the rays of any pair of adjacent maximal cones of~$\Fan$.
-
-%
-%
-%Their proof, based on representation theory of quivers, is subtle: on the one hand, only simply-laced types are explicitly treated and the remaining finite type are argued by folding; on the other hand, the technique requires to work with rational perturbations~$\b{\ell}$ and to conclude for arbitrary real perturbations by an approximation argument.
+When applied to the $\b{g}$-vector fans of cluster algebras (see \cref{subsec:typeConeCA}), this reversed approach enables us to efficiently revisit and extend the construction of~\cite{BazierMatteDouvilleMousavandThomasYildirim}.
+This new perspective has several advantages:
+\begin{itemize}
+\item Our proof applies to any initial seed, regardless of whether it is acyclic or not (see \cref{exm:typeConeCA,fig:clusterFans,fig:labelFacetDefiningInequalititesCA} for examples in types~$A_3$ and~$C_3$~cyclic).
+In contrast, the proof of~\cite{BazierMatteDouvilleMousavandThomasYildirim} only treat acyclic initial seeds.
+\item Our proof is uniform for all finite type cluster algebras, regardless of whether it is simply-laced or not (see \cref{exm:typeConeCA} for an example in type~$C_3$).
+In contrast, even with the acyclicity restriction, the result of~\cite{BazierMatteDouvilleMousavandThomasYildirim} is first proved in simply-laced cases ($A$, $D$ and~$E$) using representation theory of quivers, and then argued by a folding argument.
+Although not presented in detail, this argument is subtle and technical.
+\item Our proof directly applies to any positive real valued parameters, regardless of whether they are rational or not.
+In contrast, the proof of~\cite{BazierMatteDouvilleMousavandThomasYildirim} naturally applies to rational parameters and then requires to apply an approximation argument.
+\end{itemize}
+These advantages all follow from one essential feature of our reversed approach.
+Namely, it enables to completely separate the algebraic and the geometric aspects of the problem:
+\begin{itemize}
+\item On the algebraic side, we study the relations between the $\b{g}$-vectors of a finite type cluster algebra and we show that the mesh mutations minimally generate these relations.
+For this, we use representation theory in the setting of a~$2$-Calabi--Yau triangulated categories, and we adapt M.~Auslander's proof that the relations in the Grothendieck group of an Artin algebra are generated by the ones given by almost-split sequences precisely when the algebra is of finite representation type~\cite{Auslander1984} (see \cref{}).
+\item On the geometric side, we observe that our algebraic result precisely states that all type cones of $\b{g}$-vector fans of cluster algebras are simplicial and we just use elementary manipulations to show that a fan whose type cone is simplicial is affinely equivalent to the normal fan of sections of a high dimensional positive orthant with well-chosen affine subspaces (see \cref{}).
+\end{itemize}
+These two aspects are interesting for their own right and might be useful in different communities: the geometric side enables to describe all polytopal realizations of a fan with simplicial type cone (which is sometimes easier to check than to find an explicit realization), while the algebraic side provides fundamental new results on the $\b{g}$-vectors and the Grothendieck groups of cluster algebras.
+We have therefore voluntarily split our presentation into two clearly marked parts that can be read independently.
+The geometric side, which uses elementary techniques, is presented in \cref{part:geometry} together with all its polytopal realization consequences.
+The algebraic side, which is our core contribution, is presented in \cref{part:algebra}.
 
@@
 
+% other generalizations would deserve the same study.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \part{Type cones of $\b{g}$-vector fans}
+\label{part:geometry}
 
@@
 
-\begin{definition}\label{def:typecone}
+\begin{definition}
+\label{def:typeCone}
 The \defn{type cone} of~$\Fan$ is the cone~$\typeCone(\Fan)$ of all $\Fan$-admissible height vectors~$\b{h}$:
@@
 
-Although we will only treat with simplicial fans, for completeness, note that \cref{prop:characterizationPolytopalFan} and \cref{def:typecone} can be easily adapted to non-simplicial fans.
+Although we will only treat with simplicial fans, for completeness, note that \cref{prop:characterizationPolytopalFan} and \cref{def:typeCone} can be easily adapted to non-simplicial fans.
 To describe the type cone of an arbitrary complete fan, it suffices to consider any simplicial refinement, and to set some of the strict inequalities of the definition of the type cone to equality.
+
 \begin{proposition}
@@
 
-\begin{example}\label{ex:typecone}
+\begin{example}
+\label{ex:typecone}
 Consider the $2$-dimensional fan~$\Fan$ depicted in \cref{fig:typecone} (left) (we will encounter this fan again in \cref{exm:typeConeAsso}).
@@
 \begin{figure}[h]
+	\capstart
     \begin{adjustbox}{center}
@@
 \begin{example}
+\label{exm:typeConeCA}
 Consider the cluster fans illustrated in \cref{fig:clusterFans}.
@@
 \begin{figure}
+	\capstart
     \begin{adjustbox}{center}
@@
 \part{Grothendieck group and relations between $\b{g}$-vectors}
+\label{part:algebra}
 
@@
 
-\subsection{Setting}\label{sect::setting}
+\subsection{Setting}
+\label{sect::setting}
+
 Let~$\field$ be a field.
@@
 
-\subsection{Statement of the theorem}\label{subsect::Statement cluster cats}
+\subsection{Statement of the theorem}
+\label{subsect::Statement cluster cats}
+
 We need to introduce some notations before stating the main result of this section.  Let~$\Lambda\eqdef \End{\cat}(T)$, and let~$F$ be the functor
@@
 
-\begin{definition}\label{defi::grothendieck-group}
+\begin{definition}
+\label{defi::grothendieck-group}
  \begin{enumerate}
@@
 
-\begin{definition}\label{defi::bilinear form}
+\begin{definition}
+\label{defi::bilinear form}
  For any two objects~$X$ and~$Y$ of~$\cat$, define
@@
 
-\begin{notation}\label{notation::ell_X}
+\begin{notation}
+\label{notation::ell_X}
 \begin{enumerate}
@@
 
-\begin{theorem}\label{theo::relations-g-vecteurs}
+\begin{theorem}
+\label{theo::relations-g-vecteurs}
  Let~$\cat$ be a category satisying the hypotheses of Section \ref{sect::setting}.  Then~$\cat$ has only finitely many isomorphism classes of indecomposable objects if and only if the set
@@
 
-\begin{corollary}\label{corollary::meshes positively generate cluster cats}
+\begin{corollary}
+\label{corollary::meshes positively generate cluster cats}
  Assume that~$\ind(\cat)$ is finite.
@@
 
-\begin{corollary}\label{coro::grothendieck-g-vectors}
+\begin{corollary}
+\label{coro::grothendieck-g-vectors}
  There is an isomorphism~$\phi:\Kg(\cat) \to \Ksp(\add(T))$ such that~$\ind_T = \phi\circ \b g$.  In particular,~$\Kg(\cat)$ is a free abelian group generated by the~$[T_i]$.
@@
 
-\begin{lemma}\label{lemm::bilinear-form-suspention-T}
+\begin{lemma}
+\label{lemm::bilinear-form-suspention-T}
  If~$X$ or~$Y$ lie in~$\add(\susp T)$, then~$\langle X, Y \rangle = 0$.
@@
 
-\begin{lemma}\label{lemm::almost-split}
+\begin{lemma}
+\label{lemm::almost-split}
  Let~$X\xrightarrow{} Y \xrightarrow{} \susp^{-1} X \xrightarrow{h} \susp X$ be an almost-split triangle.  Then~$X\notin \add(\susp T)$ if and only if~$h\in (\susp T)$.
@@
 
-\begin{lemma}\label{lemm::bilinear-form}
+\begin{lemma}
+\label{lemm::bilinear-form}
 Let~$A$ and~$B$ be two indecomposable objects of~$\cat$. \pg{introduce general notation for redisue field}
@@
 
-\begin{lemma}\label{lemm::coefficients}
+\begin{lemma}
+\label{lemm::coefficients}
  Let~$x\in \Ksp(\cat)$, and write~\[x=\sum_{A\in \ind(\cat)} \lambda_A [A].\]  Then for any~$A\in\ind(\cat) \ssm \add(\susp T)$, we have that
@@
 
-\begin{corollary}\label{lemm::test-susp-T}
+\begin{corollary}
+\label{lemm::test-susp-T}
  Let~$x\in \Ksp(\cat)$.  Then the following are equivalent.
@@
 
-\begin{proposition}\label{prop::free-set}
+\begin{proposition}
+\label{prop::free-set}
  \begin{enumerate}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Relations for~$\b{g}$-vectors in brick algebras via extriangulated categories}
 \label{sect::extricats}
+
 %%%%
-\subsection{Setting}\label{setting::extricat}
+
+\subsection{Setting}
+\label{setting::extricat}
 
@@
 
-\begin{proposition}\label{prop::KRextricat}
+\begin{proposition}
+\label{prop::KRextricat}
 The functor~$F$ induces an equivalence of categories
@@
 
-\begin{proposition}\label{prop::index iso extricat}
+\begin{proposition}
+\label{prop::index iso extricat}
  The assignment~$X\mapsto\ind_\tc X$ is well-defined and induces an isomorphism
@@
 
-\begin{theorem}\label{theorem::extricats}
+\begin{theorem}
+\label{theorem::extricats}
 Assume that~$\cat$ is a~$\field$-linear, Ext-finite, Krull--Schmidt, extriangulated category with Auslander--Reiten--Serre duality.
@@
 
-\begin{corollary}\label{corollary::meshes positively generate extricats}
+\begin{corollary}
+\label{corollary::meshes positively generate extricats}
 Assume that~$\ind(\cat)$ is finite.
@@
 
-\begin{lemma}\label{lemma::first consequences}
+\begin{lemma}
+\label{lemma::first consequences}
 The following holds:
@@
 
-\begin{lemma}\label{lemma::shifts of extriangles}
+\begin{lemma}
+\label{lemma::shifts of extriangles}
 Let~$X\in\cat$ and let
@@
 
-\begin{remark}\label{remark::equivalence Sigma}
+\begin{remark}
+\label{remark::equivalence Sigma}
 For any~$T\in\tc$, fix an extriangle~$T\infl 0\defl\susp T\overset{\eps_T}{\dashrightarrow}$.
@@
 
-\begin{lemma}\label{lemma:: mphs in T are inflations}
+\begin{lemma}
+\label{lemma:: mphs in T are inflations}
 Every morphism with domain in~$\tc$ is an inflation.
@@
 
-\begin{lemma}\label{lemma::index well-defined extricat}
+\begin{lemma}
+\label{lemma::index well-defined extricat}
  The index is well-defined.
@@
 
-\begin{lemma}\label{lemma::index kzero extricat}
+\begin{lemma}
+\label{lemma::index kzero extricat}
  The index descends to~$\kzero{\cat}$: For any conflation~$X\infl Y\defl Z$ in~$\cat$, we have~$\ind_\tc Y = \ind_\tc X + \ind_\tc Z$ in~$\kzero{\tc}$.
@@
 %%
-\subsubsection{$2$-Calabi--Yau triangulated categories}\label{sect::2CYTriangulated}
+\subsubsection{$2$-Calabi--Yau triangulated categories}
+\label{sect::2CYTriangulated}
 
@@
 %%
-\subsubsection{$2$-Calabi--Yau Frobenius exact categories}\label{sect::2CYexact}
+\subsubsection{$2$-Calabi--Yau Frobenius exact categories}
+\label{sect::2CYexact}
 
 %%
-\subsubsection{$2$-term complexes of projective modules}\label{sect::Kbproj}
+\subsubsection{$2$-term complexes of projective modules}
+\label{sect::Kbproj}
 Let~$\Lambda$ be a finite-dimensional algebra over a field~$\field$.
@@
 
-\begin{proposition}\label{prop::2kbproj-is-extriangulated}
+\begin{proposition}
+\label{prop::2kbproj-is-extriangulated}
  Let~$\Lambda$ be any Artin algebra.
@@
 
-\begin{theorem}\label{theo::brick-algebra-condition}
+\begin{theorem}
+\label{theo::brick-algebra-condition}
  Let~$\Lambda$ be a brick algebra which is finite-dimensional over a field~$\field$\pg{True for any Artin algebra?}.
@@
 
-\begin{lemma}\label{lemm::AR-conflations-and-sequences}
+\begin{lemma}
+\label{lemm::AR-conflations-and-sequences}
  Let~$\Lambda$ be any Artin algebra.
@@
 
-\begin{lemma}\label{lemm::if-AR-sequences-are-mutation}
+\begin{lemma}
+\label{lemm::if-AR-sequences-are-mutation}
  Let~$\Lambda$ be an Artin algebra.
@@
 %%
-\subsubsection{Objects presented by a subcategory}\label{sect::prT}
+\subsubsection{Objects presented by a subcategory}
+\label{sect::prT}
 
@@
 
-\begin{lemma}\label{lemma:: prT is extriangulated}
+\begin{lemma}
+\label{lemma:: prT is extriangulated}
  The full subcategory~$\cat$ is extension-closed in~$(\ec,\mathbb{E}_\tc,\mathfrak{s}_\tc)$, and thus inherits an extriangulated structure.
@@
 
-\begin{proposition}\label{prop::prT}
+\begin{proposition}
+\label{prop::prT}
 Assume that, for any~$T\in\tc$, there is an~$\mathfrak{s}$-conflation~$T\infl 0\defl X_T$ in~$\ec$ with~$X_T\in\tc^\perp$.

### 2019-04-09 thirdPaper/draft/typeConeAssociahedra.tex
introduction

@@
 
-\vspace{-.5cm}
-
 \tableofcontents
-
-\newpage
 
@@
 The first systematic polytopal realizations were constructed by M.~Haiman~\cite{Haiman} and C.~Lee~\cite{Lee}.
-Since then, the associahedron has been largely ``demystified'' with several polytopal constructions...
-%~\cite{Loday, HohlwegLange, LangePilaud}.
-%See~\cite{CeballosSantosZiegler} for a survey on these constructions.
-% and generalizations to secondary and fiber polytopes~\cite{GelfandKapranovZelevinsky, BilleraFillimanSturmfels}, to pseudotriangulation polytopes~\cite{RoteSantosStreinu-polytope}, to graph associahedra and nestohedra~\cite{CarrDevadoss, Devadoss, Postnikov, FeichtnerSturmfels, Zelevinsky, Pilaud-removahedra}, to cluster complexes and generalized associahedra~\cite{FominZelevinsky-YSystems, FominZelevinsky-ClusterAlgebrasI, FominZelevinsky-ClusterAlgebrasII, ChapotonFominZelevinsky, HohlwegLangeThomas, Stella, Hohlweg, HohlwegPilaudStella}, to brick polytopes~\cite{PilaudSantos-brickPolytope, PilaudStump-brickPolytope}, to quotientopes~\cite{Reading-latticeCongruences, Reading-CambrianLattices, PilaudSantos-quotientopes}, etc.
+Since then, the associahedron has been largely ``demystified'' with several polytopal constructions and generalizations (further references are discussed below).
+Its realizations can be classified into three species: the secondary polytopes~\cite{GelfandKapranovZelevinsky, BilleraFillimanSturmfels}, the $\b{g}$-vectors realizations~\cite{Loday, HohlwegLange, LangePilaud, HohlwegLangeThomas, HohlwegPilaudStella, Postnikov, PilaudSantos-brickPolytope, PilaudStump-brickPolytope} and the $\b{d}$-vector realizations~\cite{ChapotonFominZelevinsky, CeballosSantosZiegler}.
+See~\cite{CeballosSantosZiegler} for a discussion of these realizations and their connections.
 
@@
 
+\medskip
 In this paper, we revisit, extend and explore further this construction using an reversed approach.
@@
 When applied to the $\b{g}$-vector fans of cluster algebras (see \cref{subsec:typeConeCA}), this reversed approach enables us to efficiently revisit and extend the construction of~\cite{BazierMatteDouvilleMousavandThomasYildirim}.
-This new perspective has several advantages:
+This new perspective has several advantages, as our proof uniformly applies to:
+
+\smallskip
 \begin{itemize}
-\item Our proof applies to any initial seed, regardless of whether it is acyclic or not (see \cref{exm:typeConeCA,fig:clusterFans,fig:labelFacetDefiningInequalititesCA} for examples in types~$A_3$ and~$C_3$~cyclic).
+\item \textbf{any initial seed}, regardless of whether it is acyclic or not (see \cref{exm:typeConeCA,fig:clusterFans,fig:labelFacetDefiningInequalititesCA} for examples in types~$A_3$ and~$C_3$~cyclic).
 In contrast, the proof of~\cite{BazierMatteDouvilleMousavandThomasYildirim} only treat acyclic initial seeds.
-\item Our proof is uniform for all finite type cluster algebras, regardless of whether it is simply-laced or not (see \cref{exm:typeConeCA} for an example in type~$C_3$).
+
+\smallskip
+\item \textbf{all finite type cluster algebras}, regardless of whether it is simply-laced or not (see \cref{exm:typeConeCA} for an example in type~$C_3$).
 In contrast, even with the acyclicity restriction, the result of~\cite{BazierMatteDouvilleMousavandThomasYildirim} is first proved in simply-laced cases ($A$, $D$ and~$E$) using representation theory of quivers, and then argued by a folding argument.
 Although not presented in detail, this argument is subtle and technical.
-\item Our proof directly applies to any positive real valued parameters, regardless of whether they are rational or not.
+
+\smallskip
+\item \textbf{any positive real valued parameters}, regardless of whether they are rational or not.
 In contrast, the proof of~\cite{BazierMatteDouvilleMousavandThomasYildirim} naturally applies to rational parameters and then requires to apply an approximation argument.
 \end{itemize}
+
+\smallskip
+\noindent
 These advantages all follow from one essential feature of our reversed approach.
@@
 \begin{itemize}
-\item On the algebraic side, we study the relations between the $\b{g}$-vectors of a finite type cluster algebra and we show that the mesh mutations minimally generate these relations.
-For this, we use representation theory in the setting of a~$2$-Calabi--Yau triangulated categories, and we adapt M.~Auslander's proof that the relations in the Grothendieck group of an Artin algebra are generated by the ones given by almost-split sequences precisely when the algebra is of finite representation type~\cite{Auslander1984} (see \cref{}).
-\item On the geometric side, we observe that our algebraic result precisely states that all type cones of $\b{g}$-vector fans of cluster algebras are simplicial and we just use elementary manipulations to show that a fan whose type cone is simplicial is affinely equivalent to the normal fan of sections of a high dimensional positive orthant with well-chosen affine subspaces (see \cref{}).
+\item On the \textbf{algebraic side}, we study the relations between the $\b{g}$-vectors of a finite type cluster algebra and we show that the mesh mutations minimally generate these relations.
+For this, we use representation theory in the setting of a~$2$-Calabi--Yau triangulated categories, and we adapt M.~Auslander's proof that the relations in the Grothendieck group of an Artin algebra are generated by the ones given by almost-split sequences precisely when the algebra is of finite representation type~\cite{Auslander1984} (see \cref{sec:clusterCategories}).
+
+\smallskip
+\item On the \textbf{geometric side}, we use elementary manipulations to show that a fan whose type cone is simplicial is affinely equivalent to the normal fan of sections of a high dimensional positive orthant with well-chosen affine subspaces (see \cref{sec:typeCone}).
+We then observe that our algebraic result precisely states that all type cones of $\b{g}$-vector fans of cluster algebras are simplicial from which we derive all our geometric consequences (see \cref{sec:applications}).
 \end{itemize}
+
+\smallskip
+\noindent
 These two aspects are interesting for their own right and might be useful in different communities: the geometric side enables to describe all polytopal realizations of a fan with simplicial type cone (which is sometimes easier to check than to find an explicit realization), while the algebraic side provides fundamental new results on the $\b{g}$-vectors and the Grothendieck groups of cluster algebras.
@@
 
-%Is the realization space connected?
-
-%We explain recent results of~\cite{BazierMatteDouvilleMousavandThomasYildirim}. Some advantages of our approach are:
-%\begin{itemize}
-%\item We manage to extend their results to other families of $\b{g}$-vector fans: first to all $\b{g}$-vector fans of finite type cluster algebras acyclic or not (whose polytopality was only proved recently in~\cite{HohlwegPilaudStella}), then to all $\b{g}$-vector fans of the $\tau$-tilting finite gentle algebras (whose polytopality was proved recently in~\cite{PaluPilaudPlamondon-nonkissing}), and finally to the nested fans of graph associahedra (whose polytopality was studied in~\cite{CarrDevadoss, Devadoss, Postnikov, FeichtnerSturmfels, Zelevinsky}).
-%\item We have a simpler proof, only based on the transformation between the classical descriptions of a polytope of the form~$\set{\b{x} \in \R^n}{\b{G}\b{x} \le \b{h}}$ and~$\set{\b{z} \in \R^N}{\b{K}\b{z} = \b{K}\b{h} \text{ and } \b{z} \ge 0}$ (this transformation is standard in optimization).
-In particular, we do not need to consider only rational polytopes and pass to the limit to deal with all real descriptions.
-%\item We observe that we obtain all realizations of the $\b{g}$-vector fans of the considered families.
-%\end{itemize}
-
-% other generalizations would deserve the same study.
+\medskip
+Besides revisiting the construction of~\cite{ArkaniHamedBaiHeYan, BazierMatteDouvilleMousavandThomasYildirim} and extending it to any initial seed (acyclic or not) in any finite type cluster algebra (simply-laced or not), our reversed approach is also successful on $\b{g}$-vector fans of other families of generalizations of the associahedron.
+In the present paper, we explore specifically two families of such generalizations:
+
+\smallskip
+\begin{itemize}
+\item \textbf{Gentle associahedra} were constructed in~\cite{PaluPilaudPlamondon-nonkissing} as polytopal realizations of finite non-kissing complexes of gentle quivers.
+These complexes encompass two families of simplicial complexes studied independently in the literature: on the one hand the grid associahedra introduced by T.~K.~Petersen, P.~Pylyavskyy and D.~Speyer in~\cite{PetersenPylyavskyySpeyer} for a staircase shape, studied by F.~Santos, C.~Stump and V.~Welker~\cite{SantosStumpWelker} for rectangular shapes, and extended by T.~McConville in~\cite{McConville} for arbitrary grid shapes; and on the other hand the Stokes polytopes and accordion associahedra studied by Y.~Baryshnikov~\cite{Baryshnikov}, F.~Chapoton~\cite{Chapoton-quadrangulations}, A.~Garver and T.~McConville~\cite{GarverMcConville} and T.~Manneville and V.~Pilaud~\cite{MannevillePilaud-accordion}.
+It was shown in~\cite{PaluPilaudPlamondon-nonkissing, BrustleDouvilleMousavandThomasYildirim} that the non-kissing complex of a gentle quiver provides a combinatorial model for the support $\tau$-tilting complex~\cite{AdachiIyamaReiten} of the path algebra of the quiver.
+Even for finite non-kissing complexes, it turns out that the type cone of the non-kissing fan is not always simplicial (see \cref{exm:nonSimplicialTypeConeNKC}).
+We prove however that the type cone is always simplicial when the quiver is brick (at least $2$ relations in any cycle) and $2$-acyclic (no cycle of length~$2$).
+Moreover, we precisely describe the facet defining inequalities of the type cone in terms of linear dependences of $\b{g}$-vectors involved in certain mesh relations corresponding to bricks.
+We thus automatically derive a construction similar to~\cite{ArkaniHamedBaiHeYan, BazierMatteDouvilleMousavandThomasYildirim} describing all polytopal realizations of the $\b{g}$-vector fans of these brick $2$-acyclic quivers as sections of a positive orthant by well-chosen affine spaces (see \cref{subsec:typeConeCA}).
+Again, this result just relies on finding which relations minimally generate the relations between the $\b{g}$-vectors in the non-kissing complex.
+We present both a purely combinatorial proof (see \cref{subsec:typeConeCA}) and a purely algebraic proof for arbitrary brick algebras based on extriangulated categories (see \cref{sec:extricats}).
+
+\medskip
+\item \textbf{Graph associahedra} were defined by M.~Carr and S.~Devadoss~\cite{CarrDevadoss} in connection to C.~De Concini and C.~Procesi's wonderful arrangements~\cite{DeConciniProcesi}.
+As illustrated in~\cref{fig:specialGraphAssociahedra}, the graph associahedra of certain special families of graphs coincide with well-known families of polytopes: complete graph associahedra are permutahedra, path associahedra are classical associahedra, cycle associahedra are cyclohedra, and star associahedra are stellohedra.
+The graph associahedra were extended to the \defn{nestohedra}, which are simple polytopes realizing the nested complex of arbitrary building sets~\cite{Postnikov, FeichtnerSturmfels}.
+Graph associahedra and nestohedra have been geometrically realized in different ways: by successive truncations of faces of the standard simplex~\cite{CarrDevadoss}, as Minkowski sums of faces of the standard simplex~\cite{Postnikov, FeichtnerSturmfels}, or from their normal fans by exhibiting explicit inequality descriptions~\cite{Devadoss, Zelevinsky}.
+All these realizations have the same normal fan, called nested fan.
+We study the type cones of these nested fans (see \cref{subsec:typeConeGA}): we describe describe their facet defining inequalities in terms of certain specific pairs of neighboring tubings and count them for the specific families of graph associahedra described earlier.
+For instance the type cone of the permutahedron coincides with the classical submodular functions on~$2^{[n]}$, described by~$2^{n-2} \binom{n}{2}$ inequalities.
+In fact, we observe that the type cone of a graphical nested fan is never simplicial except in the case of the classical associahedron (when the graph is the path).
+Our results describe nevertheless all polytopal realizations of the graphical nested fans.
+\end{itemize}
+
+\smallskip
+Further families of generalizations of the associahedron certainly deserve to be studied with our type cone approach
+We are investigating in particular brick polytopes~\cite{PilaudSantos-brickPolytope, PilaudStump-brickPolytope} and quotientopes~\cite{Reading-latticeCongruences, Reading-CambrianLattices, PilaudSantos-quotientopes}.
+In fact, as already mentioned, it seems sometimes easier to find all polytopal realizations of a fan (by describing its type cone in terms of certain specific pairs of adjacent maximal cones) than to identify one specific explicit realization.
+This is clearly the case when the type cone is simplicial as illustrated by the results of this paper: we naturally obtained all polytopal realizations of the $\b{g}$-vector fans of cluster algebras from cyclic seeds and of gentle algebras whose polytopality was only established very recently~\cite{HohlwegPilaudStella, PaluPilaudPlamondon-nonkissing}.
+We believe that this gives reasonable hope that the polytopality of further fans could in the future be established using our type cone approach.
+Tempting candidates are quotientopes for hyperplane arrangements beyond type~$A$, which are particularly interesting since the coarsenings of a fan essentially correspond to the faces of its type cone (see \cref{subsec:facesTypeCone}).
+
+\medskip
+Last but not least, the type cone approach naturally opens many research questions.
+First, it raised the fundamental problem to describe the minimal relations among $\b{g}$-vectors in $2$-Calabi--Yau and extriangulated categories that we treat in \cref{part:algebra}.
+It is also motivates the study of relevant objects revealed by the type cone dictionary between geometry and algebra:
+
+\smallskip
+\begin{itemize}
+\item The facet defining inequalities of the type cone of~$\Fan$ correspond to very specific pairs of adjacent maximal cones of~$\Fan$ whose corresponding linear dependences minimally generate all such dependences.
+While they correspond to mesh mutations for cluster algebras and brick $2$-acyclic gentle algebras, they are not clear in general (see for instance \cref{fig:labelFacetDefiningInequalititesNKC}\,(right)).
+It would be particularly interesting to fully understand these specific mutations for arbitrary ($\tau$-tilting finite) gentle algebras.
+
+\smallskip
+\item The rays of the type cone of~$\Fan$ correspond to specific polytopes which form a positive Minkowski basis of all realizations of~$\Fan$ (see \cref{subsec:MinkowskiSums}).
+In particular, when the type cone is simplicial, any polytopal realization of~$\Fan$ has a unique representation (up to translation) as a Minkowski sum of positive dilates of the polytopes corresponding to the rays of the type cone.
+For cluster algebras, it follows from~\cite[Sect.~6]{BazierMatteDouvilleMousavandThomasYildirim} that these polytopes are Newton polytopes of the $F$-polynomials.
+It would be interesting to obtain similar algebraic interpretations for the rays of the type cones of the non-kissing fans of gentle algebras.
+\end{itemize}
+
+\smallskip
+\noindent
+Some of these questions are explicitly indicated throughout the paper.
+To conclude, we observe that the associahedra constructed in~\cite{ArkaniHamedBaiHeYan, BazierMatteDouvilleMousavandThomasYildirim} and the present paper describe all polytopal realizations of the $\b{g}$-vector fan, motivating the question to understand the complete realization space of the cluster complex.
 
@@
 
+\newpage
 \part{Type cones of $\b{g}$-vector fans}
@@
 \section{Polytopal realizations and type cone of a simplicial fan}
+\label{sec:typeCone}
 
@@
 \subsection{Faces of the type cone}
+\label{subsec:facesTypeCone}
 
@@
 \subsection{Minkowski sums}
+\label{subsec:MinkowskiSums}
 
@@
 While they correspond to meshes on the left, they are not as clear in the general case as on the right.
-See also \cref{sect::extricats}.}
+See also \cref{sec:extricats}.}
 	\label{fig:labelFacetDefiningInequalititesNKC}
@@
 
+\begin{example}
+\label{exm:nonSimplicialTypeConeNKC}
 \vincent{All this section is wrong when the quiver is not brick or has a cycle of length~$2$.}
+\end{example}
 
@@
 
+\newpage
 \part{Grothendieck group and relations between $\b{g}$-vectors}
@@
 \section{Relations for~$\b{g}$-vectors in brick algebras via extriangulated categories}
-\label{sect::extricats}
+\label{sec:extricats}
+
+\vincent{A short introduction is missing here.}
 
@@
 
-So as to be able to state the main theorem of Section~\ref{sect::extricats}, we need a few results on extriangulated categories.
+So as to be able to state the main theorem of Section~\ref{sec:extricats}, we need a few results on extriangulated categories.
 However, all proofs are postpone to Section~\ref{sect::proofs extricats}.
@@
 \begin{remark}
- The main results of Section~\ref{subsect::Statement cluster cats} can thus be viewed as specific cases of the results of Section~\ref{sect::extricats}: Theorem~\ref{theo::relations-g-vecteurs} and Corollary~\ref{corollary::meshes positively generate cluster cats} are consequences of Theorem~\ref{theorem::extricats} and Corollary~\ref{corollary::meshes positively generate extricats}.
+ The main results of Section~\ref{subsect::Statement cluster cats} can thus be viewed as specific cases of the results of Section~\ref{sec:extricats}: Theorem~\ref{theo::relations-g-vecteurs} and Corollary~\ref{corollary::meshes positively generate cluster cats} are consequences of Theorem~\ref{theorem::extricats} and Corollary~\ref{corollary::meshes positively generate extricats}.
 \end{remark}

### 2019-04-09 thirdPaper/draft/typeConeAssociahedra.tex
abstract

@@
 \begin{abstract}
-We investigate the type cone of the $\b{g}$-vector fans for different generalizations of the associahedron (hopefully generalized associahedra, gentle associahedra, graph associahedra, and maybe quotientopes and brick polytopes).
-The objective is to determine which are the exchangeable pairs of objects that describe the type cone.
-When the type cone happens to be simplicial, we derive simple descriptions of all polytopal realizations of the $\b{g}$-vector fan.
+We show that the mesh mutations are the minimal relations among the $\b{g}$-vectors with respect to any initial seed in any finite type cluster algebra.
+We then use this algebraic result to derive geometric properties of the $\b{g}$-vector fan: we show that the space of all its polytopal realizations is a simplicial cone, and we then observe that this property implies that all its realizations can be described as the intersection of a high dimensional positive orthant with well-chosen affine spaces.
+This explains and extends earlier results of N.~Arkani-Hamed, Y.~Bai, S.~He, and G.~Yan in type~$A$ and of V.~Bazier-Matte, G.~Douville, K.~Mousavand, H.~Thomas and E.~Yildirim for acyclic initial seeds.
+
+Finally, we use a similar approach to study the space of polytopal realizations of the $\b{g}$-vector fans of other generalizations of the associahedron.
+For non-kissing complexes of gentle algebras, we show that the space of realizations of the non-kissing fan is simplicial when the gentle quiver is brick and $2$-acyclic, and we describe in this case its facet defining inequalities in terms of mesh mutations.
+For graphical nested complexes, we show that the space of realizations of the nested fan is simplicial only in the case of the associahedron, and we describe its facet defining inequalities in general.
 \end{abstract}
@@
 
+\newpage
 \tableofcontents
@@
 \smallskip
+\enlargethispage{.3cm}
 Further families of generalizations of the associahedron certainly deserve to be studied with our type cone approach

### 2019-04-09 thirdPaper/draft/typeConeAssociahedra.tex
minor changes/typos

--- 2019-04-09 thirdPaper/draft/typeConeAssociahedra.tex
@@
 \medskip
-In this paper, we revisit, extend and explore further this construction using an reversed approach.
+In this paper, we revisit, extend and explore further this construction using a reversed approach.
 Given a complete simplicial fan~$\Fan$, we consider the space~$\typeCone(\Fan)$ of all its polytopal realizations, called type cone of~$\Fan$ in~\cite{McMullen-typeCone}.
@@
 \noindent
-These two aspects are interesting for their own right and might be useful in different communities: the geometric side enables to describe all polytopal realizations of a fan with simplicial type cone (which is sometimes easier to check than to find an explicit realization), while the algebraic side provides fundamental new results on the $\b{g}$-vectors and the Grothendieck groups of cluster algebras.
+These two aspects are interesting in their own right and might be useful in different communities: the geometric side enables to describe all polytopal realizations of a fan with simplicial type cone (which is sometimes easier to check than to find an explicit realization), while the algebraic side provides fundamental new results on the $\b{g}$-vectors and the Grothendieck groups of cluster algebras.
 We have therefore voluntarily split our presentation into two clearly marked parts that can be read independently.
@@
 \smallskip
-Further families of generalizations of the associahedron certainly deserve to be studied with our type cone approach
+Further families of generalizations of the associahedron certainly deserve to be studied with our type cone approach.
 We are investigating in particular brick polytopes~\cite{PilaudSantos-brickPolytope, PilaudStump-brickPolytope} and quotientopes~\cite{Reading-latticeCongruences, Reading-CambrianLattices, PilaudSantos-quotientopes}.
@@
 Although we will only treat with simplicial fans, for completeness, note that \cref{prop:characterizationPolytopalFan} and \cref{def:typeCone} can be easily adapted to non-simplicial fans.
-To describe the type cone of an arbitrary complete fan, it suffices to consider any simplicial refinement, and to set some of the strict inequalities of the definition of the type cone to equality.
+To describe the type cone of an arbitrary complete fan, it suffices to consider any simplicial refinement, and to set some of the strict inequalities of the definition of the type cone to equality (see~\cite[Prop.~3]{PilaudSantos-quotientopes} for a proof).
 
@@
 \end{proposition}
-\arnau{should add proof or citation}
 
@@
 When non-empty, distinct coarsenings give rise to distinct cells (one will have an equation that is a strict inequality in the other).
-And all lie in the closure of~$\typeCone(\Fan)$, since they are al in the closure of all the defining half-spaces.
+And all lie in the closure of~$\typeCone(\Fan)$, since they are all in the closure of all the defining half-spaces.
+ Thus every coarsening decribes a relatively open face of~$\ctypeCone(\Fan)$.
 
@@
 It suffices to study $\b{K}\ctypeCone(\Fan)$ which is an essential simplicial cone in~$\R^3$.
-One can further reduce the dimension by intersecting with a transversal hyperplane, to get a $2$-dimensional representation.
+One can further reduce the dimension by intersecting with a transversal hyperplane to get a $2$-dimensional representation.
 This is the triangle that is depicted in \cref{fig:typecone} (right).
@@
 One of the rays generating~$\b{K}\ctypeCone(\Fan)$ corresponds to a $2$-dimensional simplex, and its normal fan is obtained by merging two pairs of extremal adjacent maximal cones.
-The two remaining rays lie not only in the hyperplanes~$H_{ij}$ defining the facets it belongs to, but also one extra such hyperplane.
-Its normal fan has only two cones, one arising as a merging of three cones and one arising as a merging of two cones.
+The two remaining rays lie not only in hyperplanes~$H_{ij}$ defining facets of the type cone, but also one extra such hyperplane.
+Their normal fans have only two cones, one arising as a merging of three cones and one arising as a merging of two cones.
 These fans are not essential, they have a one-dimensional linearity.
@@
 	\caption{A complete $2$-dimensional fan~$\Fan$ with five rays $v_1,\dots,v_5$ and five maximal cones $a,\dots, e$.
-We depict the intersection of $\b{K}\ctypeCone(F)$ with a hyperplane to get a $2$-dimensional slice.
+We depict the intersection of $\b{K}\ctypeCone(F)$ with a hyperplane to get a $2$-dimensional section.
 On top of each face of $\ctypeCone(F)$, and example of polytope with the corresponding normal fan is depicted.}
@@
 
-This provides natural Minkowski summands for all polytopal realizations of~$\Fan$: the rays of the closed 6type cone.
+This provides natural Minkowski summands for all polytopal realizations of~$\Fan$: the rays of the closed type cone.
 These correspond to indecomposable polytopes, see~\cite{Meyer} or \cite{McMullen-typeCone}.
@@
 \begin{corollary}
-\arnau{See \cite{Meyer} and \cite{McMullen-typeCone}}
-Any polytope in~$\typeCone(\Fan)$ is the Minkowski sum of at most~$N-n$ indecomposable polytopes corresponding to the rays of~$\b{K}\typeCone(\Fan)$.
+% % \arnau{See \cite{Meyer} and \cite{McMullen-typeCone}}
+Any polytope in~$\ctypeCone(\Fan)$ is the Minkowski sum of at most~$N-n$ indecomposable polytopes corresponding to the rays of~$\b{K}\ctypeCone(\Fan)$.
 \end{corollary}
@@
 \begin{corollary}
-Let $\b{h}_1,\dots, \b{h}_{N-n}\in \ctypeCone(\Fan)$ form a basis of $\ker \b{G}$.
+Let $\b{h}_1,\dots, \b{h}_{N-n}\in \ctypeCone(\Fan)$ form a basis of the left kernel of~$\b{G}$.
 Then for any~$\b{h} \in \ctypeCone(\Fan)$, the polytope~$P_\b{h}$ has a unique representation (up to translation) as a signed Minkowski sum of dilates of $P_{\b{h}_1},\dots, P_{\b{h}_{N-n}}$.
@@
 \begin{proof}
-It suffices to express the projection of $\b{h}$ into $\ker\b{G}$ in terms of $\b{h}_1,\dots, \b{h}_{N-n}$, and to separate those terms with positive and negative coefficients to express Minkowski sums and differences.
+It suffices to express the projection of $\b{h}$ onto the left kernel of~$\b{G}$ in terms of $\b{h}_1,\dots, \b{h}_{N-n}$, and to separate those terms with positive and negative coefficients to express Minkowski sums and differences.
 \end{proof}
@@
 \item  every $P_\b{h}$ with $\b{h}\in \typeCone(\Fan)$ has a unique representation (up to translation) as a Minkowski sum of positive dilates of $P_{\b{h}_1},\dots, P_{\b{h}_{N-n}}$; and
-\item  every $P_\b{h}$ with $\b{h}\in \ctypeCone(\Fan)$ has a unique representation (up to translation) as a Minkowski sum of dilates of $P_{\b{h}_1},\dots, P_{\b{h}_{N-n}}$.
+\item  every $P_\b{h}$ with $\b{h}\in \ctypeCone(\Fan)$ has a unique representation (up to translation) as a Minkowski sum of non-negative dilates of $P_{\b{h}_1},\dots, P_{\b{h}_{N-n}}$.
 \end{enumerate} 
@@
 
-Note that such a family of polytopes giving rise to unique positive representations only exists when the type cone is simplicial (both unicity and positivity only happen when the type cone is simplicial).
+Note that such a family of polytopes giving rise to unique positive/non-negative representations only exists when the type cone is simplicial.
+We get unicity with any basis, but in general we cannot guarantee non-negativity unless we are in the simplicial cone they span.
+If we take all rays of the type cone, we get non-negativity, but the representation is not unique unless the cone is simplicial.
 

### 2019-04-09 thirdPaper/draft/typeConeAssociahedra.tex

@@
 \smallskip
+\enlargethispage{.3cm}
 Further families of generalizations of the associahedron certainly deserve to be studied with our type cone approach.

### 2019-04-09 thirdPaper/draft/typeConeAssociahedra.tex
abstract

--- 2019-04-09 thirdPaper/draft/typeConeAssociahedra.tex
@@
 	\capstart
-	\centerline{{\includegraphics[width=.3\linewidth]{typeconeFan}}\hspace{1.5cm}\includegraphics[width=.4\linewidth]{typecone}}
-	\caption{A complete $2$-dimensional fan~$\Fan$ with five rays $v_1,\dots,v_5$ and five maximal cones $a,\dots, e$.
-We depict the intersection of $\b{K}\ctypeCone(F)$ with a hyperplane to get a $2$-dimensional slice.
-On top of each face of $\ctypeCone(F)$, and example of polytope with the corresponding normal fan is depicted.}
+	\centerline{{\includegraphics[scale=1]{typeconeFan}}\hspace{1.5cm}\includegraphics[width=.4\linewidth]{typecone}}
+	\caption{A complete $2$-dimensional fan~$\Fan$ with five rays $v_1,\dots,v_5$ and five maximal cones~$a,\dots, e$ (left), and the intersection of $\b{K}\ctypeCone(F)$ with a hyperplane to get a $2$-dimensional slice (right).
+On top of each face of $\ctypeCone(F)$, we depict an example of polytope with the corresponding normal fan.}
 	\label{fig:typecone}

### 2019-04-09 thirdPaper/draft/typeConeAssociahedra.tex

--- 2019-04-09 thirdPaper/draft/typeConeAssociahedra.tex
@@
 	\capstart
-	\centerline{{\includegraphics[width=.3\linewidth]{typeconeFan}}\hspace{1.5cm}\includegraphics[width=.4\linewidth]{typecone}}
-	\caption{A complete $2$-dimensional fan~$\Fan$ with five rays $v_1,\dots,v_5$ and five maximal cones $a,\dots, e$.
-We depict the intersection of $\b{K}\ctypeCone(F)$ with a hyperplane to get a $2$-dimensional section.
-On top of each face of $\ctypeCone(F)$, and example of polytope with the corresponding normal fan is depicted.}
+	\centerline{{\includegraphics[scale=1]{typeconeFan}}\hspace{1.5cm}\includegraphics[width=.4\linewidth]{typecone}}
+	\caption{A complete $2$-dimensional fan~$\Fan$ with five rays $v_1,\dots,v_5$ and five maximal cones~$a,\dots, e$ (left), and the intersection of $\b{K}\ctypeCone(F)$ with a hyperplane to get a $2$-dimensional slice (right).
+On top of each face of $\ctypeCone(F)$, we depict an example of polytope with the corresponding normal fan.}
 	\label{fig:typecone}

### 2019-04-09 thirdPaper/draft/typeConeAssociahedra.tex
typo

--- 2019-04-09 thirdPaper/draft/typeConeAssociahedra.tex
@@
 We now focus on the normal fan~$\gvectorFan[n]$ of~$\Asso[n]$.
-Since~$\Asso[n]$ leaves in a hyperplane of~$\R^{n+1}$, so does its normal fan.
+Since~$\Asso[n]$ lives in a hyperplane of~$\R^{n+1}$, so does its normal fan.
 Let~$\HH \eqdef \bigset{\b{x} \in \R^{n+1}}{\sum_{\ell \in [n+1]} x_\ell = 0}$ and~$\pi : \R^{n+1} \to \HH$ denote the orthogonal projection.
@@
 Consider the fan~$\gvectorFan[2]$ and~$\gvectorFan[3]$ illustrated in \cref{fig:lodayFans}.
-The type cone of~$\gvectorFan[2]$ lives in~$\R^5$ and has a linearity space of dimension~$2$.
+The type cone of~$\gvectorFan[2]$ lives in~$\R^5$ and has a linearity space of dimension~$2$ (this is the type cone studied in \cref{ex:typecone}).
 It has $3$ facet defining inequalities (given below), which correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso} and illustrated in \cref{fig:labelFacetDefiningInequalititesAsso}\,(left).

### 2019-04-09 thirdPaper/draft/typeConeAssociahedra.tex
minor modif intro

--- 2019-04-09 thirdPaper/draft/typeConeAssociahedra.tex
@@
 Finally, we use a similar approach to study the space of polytopal realizations of the $\b{g}$-vector fans of other generalizations of the associahedron.
-For non-kissing complexes of gentle algebras, we show that the space of realizations of the non-kissing fan is simplicial when the gentle quiver is brick and $2$-acyclic, and we describe in this case its facet defining inequalities in terms of mesh mutations.
-For graphical nested complexes, we show that the space of realizations of the nested fan is simplicial only in the case of the associahedron, and we describe its facet defining inequalities in general.
+For non-kissing complexes of gentle algebras, we show that the space of realizations of the non-kissing fan is simplicial when the gentle bound quiver is brick and $2$-acyclic, and we describe in this case its facet-defining inequalities in terms of mesh mutations.
+For graphical nested complexes, we show that the space of realizations of the nested fan is simplicial only in the case of the associahedron, and we describe its facet-defining inequalities in general.
+
+Along the way, we prove algebraic results on~$2$-Calabi--Yau triangulated categories, and on extriangulated categories that are of independent interest.
+In particular, we prove, in those two setups, an analogue of a result of M. Auslander on minimal relations for Grothendieck groups.
 \end{abstract}
@@
 \item \textbf{any initial seed}, regardless of whether it is acyclic or not (see \cref{exm:typeConeCA,fig:clusterFans,fig:labelFacetDefiningInequalititesCA} for examples in types~$A_3$ and~$C_3$~cyclic).
-In contrast, the proof of~\cite{BazierMatteDouvilleMousavandThomasYildirim} only treat acyclic initial seeds.
+In contrast, the proof of~\cite{BazierMatteDouvilleMousavandThomasYildirim} only treats acyclic initial seeds.
 
@@
 \item \textbf{all finite type cluster algebras}, regardless of whether it is simply-laced or not (see \cref{exm:typeConeCA} for an example in type~$C_3$).
-In contrast, even with the acyclicity restriction, the result of~\cite{BazierMatteDouvilleMousavandThomasYildirim} is first proved in simply-laced cases ($A$, $D$ and~$E$) using representation theory of quivers, and then argued by a folding argument.
+In contrast, even with the acyclicity restriction, the result of~\cite{BazierMatteDouvilleMousavandThomasYildirim} is first proved in simply-laced cases ($A$, $D$ and~$E$) using representation theory of quivers.
+Extension to the non simply-laced cases is then argued by a folding argument.
 Although not presented in detail, this argument is subtle and technical.
@@
 These advantages all follow from one essential feature of our reversed approach.
-Namely, it enables to completely separate the algebraic and the geometric aspects of the problem:
+Namely, it enables to completely separate the algebraic aspects from the geometric aspects of the problem:
 \begin{itemize}
 \item On the \textbf{algebraic side}, we study the relations between the $\b{g}$-vectors of a finite type cluster algebra and we show that the mesh mutations minimally generate these relations.
-For this, we use representation theory in the setting of a~$2$-Calabi--Yau triangulated categories, and we adapt M.~Auslander's proof that the relations in the Grothendieck group of an Artin algebra are generated by the ones given by almost-split sequences precisely when the algebra is of finite representation type~\cite{Auslander1984} (see \cref{sec:clusterCategories}).
+For this, we use representation theory in the setting of~$2$-Calabi--Yau triangulated categories, and we adapt M.~Auslander's proof that the relations in the Grothendieck group of an Artin algebra are generated by the ones given by almost-split sequences precisely when the algebra is of finite representation type~\cite{Auslander1984} (see \cref{sec:clusterCategories}).
 
@@
 \noindent
-These two aspects are interesting in their own right and might be useful in different communities: the geometric side enables to describe all polytopal realizations of a fan with simplicial type cone (which is sometimes easier to check than to find an explicit realization), while the algebraic side provides fundamental new results on the $\b{g}$-vectors and the Grothendieck groups of cluster algebras.
+These two aspects are interesting in their own right and might be useful in different communities: the geometric side enables to describe all polytopal realizations of a fan with simplicial type cone (which is sometimes easier to check than to find an explicit realization), while the algebraic side provides fundamental new results on the $\b{g}$-vectors of cluster algebras and on (an extriangulated variant of) the Grothendieck groups of~$2$-Calabi--Yau triangulated categories with cluster tilting objects.
 We have therefore voluntarily split our presentation into two clearly marked parts that can be read independently.
-The geometric side, which uses elementary techniques, is presented in \cref{part:geometry} together with all its polytopal realization consequences.
-The algebraic side, which is our core contribution, is presented in \cref{part:algebra}.
+The geometric side, which uses elementary techniques, is presented in \cref{part:geometry} together with all its consequences on polytopal realizations.
+The algebraic side, which is of independent interest, is presented in \cref{part:algebra}.
 
 \medskip
-Besides revisiting the construction of~\cite{ArkaniHamedBaiHeYan, BazierMatteDouvilleMousavandThomasYildirim} and extending it to any initial seed (acyclic or not) in any finite type cluster algebra (simply-laced or not), our reversed approach is also successful on $\b{g}$-vector fans of other families of generalizations of the associahedron.
+Besides revisiting the construction of~\cite{ArkaniHamedBaiHeYan, BazierMatteDouvilleMousavandThomasYildirim} and extending it to any initial seed (acyclic or not) in any finite type cluster algebra (simply-laced or not), our reversed approach is also successful when applied to the $\b{g}$-vector fans of other families of generalizations of the associahedron.
 In the present paper, we explore specifically two families of such generalizations:
@@
 \begin{itemize}
-\item \textbf{Gentle associahedra} were constructed in~\cite{PaluPilaudPlamondon-nonkissing} as polytopal realizations of finite non-kissing complexes of gentle quivers.
+\item \textbf{Gentle associahedra} were constructed in~\cite{PaluPilaudPlamondon-nonkissing} as polytopal realizations of finite non-kissing complexes of gentle bound quivers.
 These complexes encompass two families of simplicial complexes studied independently in the literature: on the one hand the grid associahedra introduced by T.~K.~Petersen, P.~Pylyavskyy and D.~Speyer in~\cite{PetersenPylyavskyySpeyer} for a staircase shape, studied by F.~Santos, C.~Stump and V.~Welker~\cite{SantosStumpWelker} for rectangular shapes, and extended by T.~McConville in~\cite{McConville} for arbitrary grid shapes; and on the other hand the Stokes polytopes and accordion associahedra studied by Y.~Baryshnikov~\cite{Baryshnikov}, F.~Chapoton~\cite{Chapoton-quadrangulations}, A.~Garver and T.~McConville~\cite{GarverMcConville} and T.~Manneville and V.~Pilaud~\cite{MannevillePilaud-accordion}.
-It was shown in~\cite{PaluPilaudPlamondon-nonkissing, BrustleDouvilleMousavandThomasYildirim} that the non-kissing complex of a gentle quiver provides a combinatorial model for the support $\tau$-tilting complex~\cite{AdachiIyamaReiten} of the path algebra of the quiver.
+It was shown in~\cite{PaluPilaudPlamondon-nonkissing, BrustleDouvilleMousavandThomasYildirim} that the non-kissing complex of a gentle bound quiver provides a combinatorial model for the support $\tau$-tilting complex~\cite{AdachiIyamaReiten} of the associated gentle algebra.
 Even for finite non-kissing complexes, it turns out that the type cone of the non-kissing fan is not always simplicial (see \cref{exm:nonSimplicialTypeConeNKC}).
-We prove however that the type cone is always simplicial when the quiver is brick (at least $2$ relations in any cycle) and $2$-acyclic (no cycle of length~$2$).
-Moreover, we precisely describe the facet defining inequalities of the type cone in terms of linear dependences of $\b{g}$-vectors involved in certain mesh relations corresponding to bricks.
-We thus automatically derive a construction similar to~\cite{ArkaniHamedBaiHeYan, BazierMatteDouvilleMousavandThomasYildirim} describing all polytopal realizations of the $\b{g}$-vector fans of these brick $2$-acyclic quivers as sections of a positive orthant by well-chosen affine spaces (see \cref{subsec:typeConeCA}).
-Again, this result just relies on finding which relations minimally generate the relations between the $\b{g}$-vectors in the non-kissing complex.
+We prove however that the type cone is always simplicial when the gentle bound quiver is brick (at least $2$ relations in any cycle) and $2$-acyclic (no oriented cycle of length~$2$).
+Moreover, we precisely describe the facet-defining inequalities of the type cone in terms of linear dependences of $\b{g}$-vectors involved in certain mesh relations.
+We thus automatically derive a construction similar to that of~\cite{ArkaniHamedBaiHeYan, BazierMatteDouvilleMousavandThomasYildirim} describing all polytopal realizations of the $\b{g}$-vector fans of these brick $2$-acyclic bound quivers as sections of a positive orthant by well-chosen affine spaces (see \cref{subsec:typeConeCA}).
+Again, this result mainly relies on finding which relations minimally generate the relations between the $\b{g}$-vectors in the non-kissing complex.
 We present both a purely combinatorial proof (see \cref{subsec:typeConeCA}) and a purely algebraic proof for arbitrary brick algebras based on extriangulated categories (see \cref{sec:extricats}).
@@
 All these realizations have the same normal fan, called nested fan.
-We study the type cones of these nested fans (see \cref{subsec:typeConeGA}): we describe describe their facet defining inequalities in terms of certain specific pairs of neighboring tubings and count them for the specific families of graph associahedra described earlier.
+We study the type cones of these nested fans (see \cref{subsec:typeConeGA}): we describe describe their facet-defining inequalities in terms of certain specific pairs of neighboring tubings and count them for the specific families of graph associahedra described earlier.
 For instance the type cone of the permutahedron coincides with the classical submodular functions on~$2^{[n]}$, described by~$2^{n-2} \binom{n}{2}$ inequalities.
@@
 Last but not least, the type cone approach naturally opens many research questions.
-First, it raised the fundamental problem to describe the minimal relations among $\b{g}$-vectors in $2$-Calabi--Yau and extriangulated categories that we treat in \cref{part:algebra}.
+First, it raised the fundamental problem of describing the minimal relations among $\b{g}$-vectors in $2$-Calabi--Yau and extriangulated categories that we treat in \cref{part:algebra}.
 It is also motivates the study of relevant objects revealed by the type cone dictionary between geometry and algebra:
@@
 \begin{itemize}
-\item The facet defining inequalities of the type cone of~$\Fan$ correspond to very specific pairs of adjacent maximal cones of~$\Fan$ whose corresponding linear dependences minimally generate all such dependences.
+\item The facet-defining inequalities of the type cone of~$\Fan$ correspond to very specific pairs of adjacent maximal cones of~$\Fan$ whose corresponding linear dependences minimally generate all such dependences.
 While they correspond to mesh mutations for cluster algebras and brick $2$-acyclic gentle algebras, they are not clear in general (see for instance \cref{fig:labelFacetDefiningInequalititesNKC}\,(right)).
@@
 The type cone of~$\gvectorFan[2]$ lives in~$\R^5$ and has a linearity space of dimension~$2$.
-It has $3$ facet defining inequalities (given below), which correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso} and illustrated in \cref{fig:labelFacetDefiningInequalititesAsso}\,(left).
+It has $3$ facet-defining inequalities (given below), which correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso} and illustrated in \cref{fig:labelFacetDefiningInequalititesAsso}\,(left).
 
@@
 The type cone of~$\gvectorFan[2]$ lives in~$\R^9$ and has a linearity space of dimension~$3$.
-It has $6$ facet defining inequalities (given below), which correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso} and illustrated in \cref{fig:labelFacetDefiningInequalititesAsso}\,(left).
+It has $6$ facet-defining inequalities (given below), which correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso} and illustrated in \cref{fig:labelFacetDefiningInequalititesAsso}\,(left).
 
@@
     \end{adjustbox}
-	\caption{The facet defining inequalities of the type cone~$\typeCone(\gvectorFan[n])$ correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso}.
+	\caption{The facet-defining inequalities of the type cone~$\typeCone(\gvectorFan[n])$ correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso}.
 See \cref{subsec:typeConeCA,sec:clusterCategories} for a representation theoretic \mbox{interpretation}.}
@@
 The type cone of the left fan of \cref{fig:clusterFans} lives in~$\R^9$ and has a linearity space of dimension~$3$.
-It has $6$ facet defining inequalities (given below), which correspond to the mesh mutations of \cref{thm:extremalExchangeablePairsCA} as illustrated in \cref{fig:labelFacetDefiningInequalititesCA}\,(top).
+It has $6$ facet-defining inequalities (given below), which correspond to the mesh mutations of \cref{thm:extremalExchangeablePairsCA} as illustrated in \cref{fig:labelFacetDefiningInequalititesCA}\,(top).
 
@@
 The type cone of the right fan of \cref{fig:clusterFans} lives in~$\R^{12}$ and has a linearity space of dimension~$3$.
-It has $9$ facet defining inequalities (given below), which correspond to the mesh mutations of \cref{thm:extremalExchangeablePairsCA} as illustrated in \cref{fig:labelFacetDefiningInequalititesCA}\,(bottom).
+It has $9$ facet-defining inequalities (given below), which correspond to the mesh mutations of \cref{thm:extremalExchangeablePairsCA} as illustrated in \cref{fig:labelFacetDefiningInequalititesCA}\,(bottom).
 
@@
     \end{adjustbox}
-	\caption{The facet defining inequalities of the type cone~$\typeCone(\gvectorFan[\B_\circ])$ of the cluster fan correspond to the mesh mutations described in \cref{thm:extremalExchangeablePairsCA}.
+	\caption{The facet-defining inequalities of the type cone~$\typeCone(\gvectorFan[\B_\circ])$ of the cluster fan correspond to the mesh mutations described in \cref{thm:extremalExchangeablePairsCA}.
 See \cref{sec:clusterCategories} for a representation theoretic \mbox{interpretation}.}
@@
 The type cone of the left fan of \cref{fig:nonkissingFans} lives in~$\R^9$ and has a linearity space of dimension~$3$.
-It has $6$ facet defining inequalities (given below), which correspond to the flips described in \cref{prop:interestingExchangeablePairsNKC,prop:extremalExchangeablePairsNKC} and illustrated in \cref{fig:labelFacetDefiningInequalititesNKC}\,(left).
+It has $6$ facet-defining inequalities (given below), which correspond to the flips described in \cref{prop:interestingExchangeablePairsNKC,prop:extremalExchangeablePairsNKC} and illustrated in \cref{fig:labelFacetDefiningInequalititesNKC}\,(left).
 
@@
 The type cone of the right fan of \cref{fig:nonkissingFans} lives in~$\R^{11}$ and has a linearity space of dimension~$3$.
-It has $9$ facet defining inequalities (given below), which correspond to the flips illustrated in \cref{fig:labelFacetDefiningInequalititesNKC}\,(right).
+It has $9$ facet-defining inequalities (given below), which correspond to the flips illustrated in \cref{fig:labelFacetDefiningInequalititesNKC}\,(right).
 In particular, it is not simplicial.
@@
     \end{adjustbox}
-	\caption{The facet defining inequalities of the type cone~$\typeCone(\gvectorFan[\quiver])$ of the non-kissing fan, represented on the Auslander Reiten quiver of the gentle algebra of~$\quiver$.
+	\caption{The facet-defining inequalities of the type cone~$\typeCone(\gvectorFan[\quiver])$ of the non-kissing fan, represented on the Auslander Reiten quiver of the gentle algebra of~$\quiver$.
 While they correspond to meshes on the left, they are not as clear in the general case as on the right.
@@
 Consider the nested fans illustrated in \cref{fig:nestedFans}.
-The type cone of the left fan lives in~$\R^{13}$, has a linearity space of dimension~$3$ and $19$ facet defining inequalities (given below). In particular, it is not simplicial.
+The type cone of the left fan lives in~$\R^{13}$, has a linearity space of dimension~$3$ and $19$ facet-defining inequalities (given below). In particular, it is not simplicial.
 
@@
 \noindent
-The type cone of the right fan lives in~$\R^{11}$, has a linearity space of dimension~$3$ and $12$ facet defining inequalities (given below). In particular, it is not simplicial.
+The type cone of the right fan lives in~$\R^{11}$, has a linearity space of dimension~$3$ and $12$ facet-defining inequalities (given below). In particular, it is not simplicial.
 
@@
 
-In the remaining of this section, we describe the facet defining inequalities of the type cone of the graphical nested fans.
+In the remaining of this section, we describe the facet-defining inequalities of the type cone of the graphical nested fans.
 Observe first that we have already indirectly described this type cone when the graph is a path in \cref{prop:extremalExchangeablePairsAsso}.

### 2019-04-09 thirdPaper/draft/typeConeAssociahedra.tex

@@
 Consider the fan~$\gvectorFan[2]$ and~$\gvectorFan[3]$ illustrated in \cref{fig:lodayFans}.
-The type cone of~$\gvectorFan[2]$ lives in~$\R^5$ and has a linearity space of dimension~$2$.
+The type cone of~$\gvectorFan[2]$ lives in~$\R^5$ and has a linearity space of dimension~$2$ (this is the type cone studied in \cref{ex:typecone}).
 It has $3$ facet-defining inequalities (given below), which correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso} and illustrated in \cref{fig:labelFacetDefiningInequalititesAsso}\,(left).

### 2019-04-09 thirdPaper/draft/typeConeAssociahedra.tex
cleaning Section 1

--- 2019-04-09 thirdPaper/draft/typeConeAssociahedra.tex
@@
 Note that every complete fan is the product of an essential fan with its linearity space.
-For two fans~$\Fan, \Fan'$ in~$\R^d$, we say that~$\Fan$ \defn{refines}~$\Fan'$ (and that~$\Fan'$ \defn{coarsens}~$\Fan$) if every cone of~$\Fan$ is contained in a cone of~$\Fan'$.
+For two fans~$\Fan, \c{G}$ in~$\R^d$, we say that~$\Fan$ \defn{refines}~$\c{G}$ (and that~$\c{G}$ \defn{coarsens}~$\Fan$) if every cone of~$\Fan$ is contained in a cone of~$\c{G}$.
 
@@
 Note that the type cone is an open cone and contains a linearity subspace of dimension~$n$ (it is invariant by translation in~$\b{G} \R^n$). 
-% We could thus intersect~$\typeCone(\Fan)$ with the kernel of~$\b{G}$, or consider the projection~$\b{K}\typeCone(\Fan)$.
-It is sometimes useful to get rid of the linearity by considering the projection~$\b{K}\typeCone(\Fan)$.
+It is sometimes useful to get rid of the linearity space by considering the projection~$\b{K}\typeCone(\Fan)$.
 
@@
 
-Although we will only treat with simplicial fans, for completeness, note that \cref{prop:characterizationPolytopalFan} and \cref{def:typeCone} can be easily adapted to non-simplicial fans.
-To describe the type cone of an arbitrary complete fan, it suffices to consider any simplicial refinement, and to set some of the strict inequalities of the definition of the type cone to equality (see~\cite[Prop.~3]{PilaudSantos-quotientopes} for a proof).
-
-\begin{proposition}
-\label{prop:non-simplicial}
-Let $\Fan'$ be a complete fan that coarsens the essential complete simplicial fan~$\Fan$.
-The \defn{type cone}~$\typeCone(\Fan')$ of all $\Fan'$-admissible height vectors~$\b{h}$ is
-\begin{align*}
-\typeCone(\Fan) 
-%  & \eqdef \set{\b{h} \in \R^N}{\Fan \text{ is the normal fan of } P_\b{h}} \\
-& = \left\{\b{h} \in \R^N\;\middle|\;
-\begin{array}{ll}
-\sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} = 0
-& \begin{array}{l} \text{for any adjacent maximal cones} \\ \text{$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$ of~$\Fan$ \textbf{belonging}}\\\text{to the same maximal cone of $\Fan'$; and}\end{array}
-\\\\
-\sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} > 0
-& \begin{array}{l} \text{for any adjacent maximal cones} \\ \text{$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$ of~$\Fan$ \textbf{not belonging}}\\\text{to the same maximal cone of $\Fan'$}\end{array}
-\end{array}
-\right\}.
-\end{align*}
-\end{proposition}
+\begin{example}
+\label{exm:typeCone}
+\enlargethispage{.5cm}
+Consider the $2$-dimensional fan~$\Fan$ depicted in \cref{fig:typeCone} (left) (we will encounter this fan again in \cref{exm:typeConeCoarsenings,exm:typeConeMinkowskiSum,exm:typeConeAsso}).
+It has five rays labeled~$1, \dots, 5$ and five maximal cones labeled~$a,\dots, e$.
+Its type cone~$\ctypeCone(\Fan)$ lies in~$\R^5$, but has a $2$-dimensional linearity space.
+The five pairs of adjacent maximal cones of~$\Fan$ give rise to following five defining inequalities for~$\ctypeCone(\Fan)$:
+\begin{gather*}
+H^>_{ab}: \; \b{h}_1 + \b{h}_3 - \b{h}_2 > 0
+\qquad
+H^>_{bc}: \; \b{h}_2 + \b{h}_4 - \b{h}_3 > 0
+\qquad
+H^>_{cd}: \; \b{h}_3 + \b{h}_5 - \b{h}_4 > 0
+\\
+H^>_{de}: \; \b{h}_1 + \b{h}_4 > 0
+\qquad
+H^>_{ae}: \; \b{h}_2 + \b{h}_5 > 0,
+\end{gather*}
+where $H^>_{ij}$ denotes the halfspace defined by the inequality corresponding to the two adjacent maximal cones~$i$ and~$j$.
+Note that the inequalities~$H^>_{ae}$ and~$H^>_{de}$ are redundant.
+For example, the height vector~$(\nicefrac{1}{2}, \nicefrac{3}{4}, \nicefrac{5}{4}, 1, \nicefrac{5}{4})$ belongs to the type cone~$\ctypeCone(\Fan)$, and the corresponding polytope is represented in \cref{fig:typeCone} (middle).
+To represent this type cone, it suffices to represent~$\b{K}\ctypeCone(\Fan)$ which is an essential simplicial cone in~$\R^3$.
+One can further reduce the dimension by intersecting with a transversal hyperplane to get a $2$-dimensional representation.
+This is the red triangle depicted in \cref{fig:typeCone} (right).
+
+\begin{figure}[htpb]
+	\capstart
+	\centerline{{\includegraphics[scale=1]{typeConeFan}} \quad {\includegraphics[scale=1]{typeConePolytope}} \quad \raisebox{.5cm}{\includegraphics[scale=.45]{typeCone}}}
+	\caption{A $2$-dimensional fan~$\Fan$ with five rays $1, \dots, 5$ and five maximal cones~$a, \dots, e$ (left), its polytopal realization corresponding to the height vector~$(\nicefrac{1}{2}, \nicefrac{3}{4}, 1, 1, \nicefrac{5}{4})$ (middle), and the intersection of $\b{K}\ctypeCone(\Fan)$ with a hyperplane to get a $2$-dimensional slice (right).}
+	\label{fig:typeCone}
+\end{figure}
+\end{example}
 
@@
 \end{definition}
-\arnau{I changed open to closed here}
 
@@
 Understanding the extremal adjacent pairs of~$\Fan$ enables to describe its type cone~$\typeCone(\Fan)$ and thus all its polytopal realizations.
+For instance in
 
@@
 
+Although we will only deal with simplicial fans, note for completeness that \cref{prop:characterizationPolytopalFan,def:typeCone} can be easily adapted to non-simplicial fans.
+To describe the type cone of an arbitrary complete fan, it suffices to consider any simplicial refinement, and to set some of the strict inequalities of the definition of the type cone to equality (see~\cite[Prop.~3]{PilaudSantos-quotientopes} for a proof).
+
+\begin{proposition}
+\label{prop:non-simplicial}
+Let $\c{G}$ be a complete fan that coarsens the essential complete simplicial fan~$\Fan$.
+The \defn{type cone}~$\typeCone(\c{G})$ of all $\c{G}$-admissible height vectors~$\b{h}$ is
+\begin{align*}
+\typeCone(\c{G}) 
+%  & \eqdef \set{\b{h} \in \R^N}{\Fan \text{ is the normal fan of } P_\b{h}} \\
+& = \left\{\b{h} \in \R^N\;\middle|\;
+\begin{array}{ll}
+\sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} = 0
+& \begin{array}{l} \text{for any adjacent maximal cones} \\ \text{$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$ of~$\Fan$ belonging}\\\text{to \textbf{the same} maximal cone of $\c{G}$,}\end{array}
+\\[.7cm]
+\sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} > 0
+& \begin{array}{l} \text{for any adjacent maximal cones} \\ \text{$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$ of~$\Fan$ belonging}\\\text{to \textbf{distinct} maximal cones of $\c{G}$}\end{array}
+\end{array}
+\right\}.
+\end{align*}
+\end{proposition}
+
 %%%%%%%%%%%
@@
 
-Two rays~$\ray$ and~$\ray'$ of~$\Fan$ are called \defn{compatible} if there are both contained in a cone of~$\Fan$ and \defn{exchangeable} if there are two adjacent maximal cones~$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$ of~$\Fan$ with ${\rays \ssm \{\ray\} = \rays' \ssm \{\ray'\}}$.
-If~$\rays(\Fan)$ denotes the set of rays of~$\Fan$, a \defn{compatibility degree} for~$\Fan$ is a function~$\compatibilityDegree{-}{-}: \rays(\Fan) \times \rays(\Fan) \to \R$ such that
-\begin{itemize}
-\item $\compatibilityDegree{\ray}{\ray'} = -1$ if~$\ray = \ray'$ and is non-negative otherwise,
-\item $\compatibilityDegree{\ray}{\ray'} = 0$ if ~$\ray$ and~$\ray'$ are compatible,
-\item $\compatibilityDegree{\ray}{\ray'} > 0$ if~$\ray \ne \ray'$ are incompatible,
-\item $\compatibilityDegree{\ray}{\ray'} = 1 = \compatibilityDegree{\ray'}{\ray}$ if and only if~$\ray$ and~$\ray'$ are exchangeable.
-\end{itemize}
-\vincent{The definition of compatibility degree is not really useful here.}
+Two rays~$\ray$ and~$\ray'$ of~$\Fan$ are
+% called \defn{compatible} if there are both contained in a cone of~$\Fan$ and 
+\defn{exchangeable} if there are two adjacent maximal cones~$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$ of~$\Fan$ with ${\rays \ssm \{\ray\} = \rays' \ssm \{\ray'\}}$.
+%If~$\rays(\Fan)$ denotes the set of rays of~$\Fan$, a \defn{compatibility degree} for~$\Fan$ is a function~$\compatibilityDegree{-}{-}: \rays(\Fan) \times \rays(\Fan) \to \R$ such that
+%\begin{itemize}
+%\item $\compatibilityDegree{\ray}{\ray'} = -1$ if~$\ray = \ray'$ and is non-negative otherwise,
+%\item $\compatibilityDegree{\ray}{\ray'} = 0$ if ~$\ray$ and~$\ray'$ are compatible,
+%\item $\compatibilityDegree{\ray}{\ray'} > 0$ if~$\ray \ne \ray'$ are incompatible,
+%\item $\compatibilityDegree{\ray}{\ray'} = 1 = \compatibilityDegree{\ray'}{\ray}$ if and only if~$\ray$ and~$\ray'$ are exchangeable.
+%\end{itemize}
 
@@
 This implies in particular that the rays~$\ray[s]$ for which~$\coefficient[{\ray[s]}][\rays][\rays'] \ne 0$ belong to~$\rays \cup \rays'$ for any pair~$\{\rays, \rays'\}$ of adjacent cones of~$\Fan$ with $\rays \ssm \{\ray\} = \rays' \ssm \{\ray'\}$.
-These rays are thus called \defn{forced rays} for the exchangeable pair~$\{\ray, \ray'\}$.
-\arnau{Remove definition of forced rays. Not used anywhere.}
+%These rays are thus called \defn{forced rays} for the exchangeable pair~$\{\ray, \ray'\}$.
 
@@
 \[
-\typeCone(\Fan) = \Bigset{\b{h} \in \R^N}{\sum_{\ray[s] \in \rays \cup \rays'} \coefficient \, \b{h}_{\ray[s]} > 0 \text{ for any exchangeable rays~$\ray$ and~$\ray'$ of~$\Fan$}}.
-\]
-
-\arnau{Do we have a notation for the set of all rays? I would change the sum over ${\ray[s] \in \rays \cup \rays'}$ to the whole ground set.}
+\typeCone(\Fan) = \Bigset{\b{h} \in \R^N}{\sum_{\ray[s]} \coefficient \, \b{h}_{\ray[s]} > 0 \text{ for any exchangeable rays~$\ray$ and~$\ray'$ of~$\Fan$}}.
+\]
+
 \begin{definition}
-In a fan~$\Fan$ with the unique exchange relation property, an \defn{extremal exchangeable pair} is a pair of exchangeable rays~$\{\ray,\ray'\}$ such that the corresponding inequality~${\sum_{\ray[s] \in \rays \cup \rays'} \coefficient \, \b{h}_{\ray[s]} \geq  0}$ defines a facet of the closed type cone~$\ctypeCone(\Fan)$.
+In a fan~$\Fan$ with the unique exchange relation property, an \defn{extremal exchangeable pair} is a pair of exchangeable rays~$\{\ray,\ray'\}$ such that the corresponding inequality~${\sum_{\ray[s]} \coefficient \, \b{h}_{\ray[s]} \geq  0}$ defines a facet of the closed type cone~$\ctypeCone(\Fan)$.
 \end{definition}
-\arnau{I changed open to closed here}
 
@@
 \label{prop:alternativePolytopalRealization}
-\vincent{See \cite[Coro.~9.5.7]{DeLoeraRambauSantos}}
 The affine map~$\Psi: \R^n \to \R^N$ defined by~$\Psi(\b{x}) = \b{h} - G\b{x}$ sends the polytope
@@
 \begin{proof}
+This result is standard and is proved for instance in~\cite[Coro.~9.5.7]{DeLoeraRambauSantos}.
+We include a short argument here for the convenience of the reader.
 For~$\b{x}$ in~$P_\b{h}$, we have $\Psi(\b{x}) \ge 0$ by definition and~$\b{K}\Psi(\b{x}) = \b{K}\b{h} - \b{K}\b{G}\b{x} = \b{K}\b{h}$ since~$\b{K}$ is the left kernel of~$\b{G}$.
@@
 
+We now relate the faces of the closed type cone~$\ctypeCone(\Fan)$ with the coarsenings of the fan~$\Fan$.
+
 \begin{theorem}
- Let $\Fan$ be a polytopal fan. Then the relatively open faces of~$\ctypeCone(\Fan)$ are the type cones of all (polytopal) coarsenings of~$\Fan$. 
+Let $\Fan$ be a polytopal fan. Then the relatively open faces of the closed type cone~$\ctypeCone(\Fan)$ are the type cones of all (polytopal) coarsenings of~$\Fan$. 
 \end{theorem}
+
 \begin{proof}
- Let $\Fan'$ be a simplicial refinement of $\Fan$.
-By~\cref{prop:non-simplicial}, the type cone of any coarsening of $\Fan$ is a relatively open cell of the hyperplane arrangement defined by adjacent pairs of~$\Fan'$.
+Let $\c{G}$ be a simplicial refinement of $\Fan$.
+By~\cref{prop:non-simplicial}, the type cone of any coarsening of $\Fan$ is a relatively open cell of the hyperplane arrangement defined by adjacent pairs of~$\c{G}$.
 The type cone of the coarsening is not empty whenever it is polytopal.
-When non-empty, distinct coarsenings give rise to distinct cells (one will have an equation that is a strict inequality in the other).
-And all lie in the closure of~$\typeCone(\Fan)$, since they are all in the closure of all the defining half-spaces.
- Thus every coarsening decribes a relatively open face of~$\ctypeCone(\Fan)$.
+When non-empty, distinct coarsenings give rise to distinct cells (one will have an equality that is a strict inequality in the other), and all lie in the closure of~$\typeCone(\Fan)$ (since they are all in the closure of all the defining half-spaces).
+Thus every coarsening describes a relatively open face of~$\ctypeCone(\Fan)$.
 
@@
 
+\begin{remark}
 Some observations are in place:
@@
 There might be several extremal adjacent pairs giving rise to the same facet.
-This happens often when we have the unique exchange property and there are many pairs of cones separating the same exchangeable pair of rays.
+This happens often when we have the unique exchange property and there are many pairs of maximal cones separating the same exchangeable rays.
 
 \item Mergings induced by extremal adjacent pairs are not the only ones that can take place in the boundary of~$\ctypeCone(\Fan)$.
-Indeed, if $\Fan'$ is the coarsening defining a lower-dimensional face~$\typeCone(\Fan')$ of~$\ctypeCone(\Fan)$, then to get $\Fan$ we have to perform all the coarsenings given by facets of~$\ctypeCone(\Fan)$ containing~$\typeCone(\Fan')$.
-But we might have to perform more coarsenings arising from exchangeable pairs  $\{\R_{\ge0}\rays, \R_{\ge0}\rays'\}$ whose inequality is redundant for~$\ctypeCone(\Fan)$ but tight for all points in~$\typeCone(\Fan')$.
+Indeed, if $\c{G}$ is the coarsening defining a lower-dimensional face~$\typeCone(\c{G})$ of~$\ctypeCone(\Fan)$, then to get $\Fan$ we have to perform all the coarsenings given by facets of~$\ctypeCone(\Fan)$ containing~$\typeCone(\c{G})$.
+But we might have to perform more coarsenings arising from exchangeable pairs  $\{\R_{\ge0}\rays, \R_{\ge0}\rays'\}$ whose inequality is redundant for~$\ctypeCone(\Fan)$ but tight for all points in~$\typeCone(\c{G})$.
 This situation arises when, in order to have a polytopal polyhedral fan, more pairs of adjacent cones must be merged.
+
 \item Even if $\Fan$ is essential, not all its polytopal coarsenings need to be.
-Indeed, it can happen that there is a certain polytopal coarsening $\Fan'$ in which all the cells have a common linearity space.
-In this case, $\Fan'$ is the normal fan of a lower dimensional polytope (whose codimension is the dimension of the linearity space of $\Fan'$).
+Indeed, it can happen that there is a certain polytopal coarsening $\c{G}$ in which all the cells have a common linearity space.
+In this case, $\c{G}$ is the normal fan of a lower dimensional polytope (whose codimension is the dimension of the linearity space of $\c{G}$).
 For this to happen, it is necessary (but not sufficient) that there is a positive linear dependence between some rays of $\Fan$.
 \end{itemize}
+\end{remark}
 
 \begin{example}
-\label{ex:typecone}
-Consider the $2$-dimensional fan~$\Fan$ depicted in \cref{fig:typecone} (left) (we will encounter this fan again in \cref{exm:typeConeAsso}).
-It has five rays $v_1,\dots,v_5$ and five maximal cones $a,\dots, e$.
-Its type cone lies in~$\R^5$, but has a $2$-dimensional linearity space.
-It suffices to study $\b{K}\ctypeCone(\Fan)$ which is an essential simplicial cone in~$\R^3$.
-One can further reduce the dimension by intersecting with a transversal hyperplane to get a $2$-dimensional representation.
-This is the triangle that is depicted in \cref{fig:typecone} (right).
-The five pairs of adjacent maximal cones give rise to five defining inequalities for $\ctypeCone(\Fan)$, although only three are non-redundant.
-If $H_{ij}$ is the hyperplane supporting the inequality given by the two adjacent maximal cones~$i$ and~$j$, then only $H_{ab}$, $H_{cd}$ and $H_{bc}$ support facets of the type cone.
+\label{exm:typeConeCoarsenings}
+Consider the $2$-dimensional fan~$\Fan$ of \cref{fig:typeCone}\,(left) whose type cone has been described in \cref{exm:typeCone} and represented in \cref{fig:typeCone}\,(right).
 The relative interior of the three facets of~$\ctypeCone(\Fan)$ are the type cones of three coarsenings of~$\Fan$, obtained by merging certain adjacent maximal cones (those that are extremal).
-One of the rays generating~$\b{K}\ctypeCone(\Fan)$ corresponds to a $2$-dimensional simplex, and its normal fan is obtained by merging two pairs of extremal adjacent maximal cones.
-The two remaining rays lie not only in hyperplanes~$H_{ij}$ defining facets of the type cone, but also one extra such hyperplane.
+One of the rays generating~$\b{K}\ctypeCone(\Fan)$ corresponds to a triangle, and its normal fan is obtained by merging two pairs of extremal adjacent maximal cones.
+The two remaining rays lie not only in hyperplanes~$H_{ij}$ defining facets of the type cone, but also in one extra such hyperplane.
 Their normal fans have only two cones, one arising as a merging of three cones and one arising as a merging of two cones.
@@
 	\capstart
-	\centerline{{\includegraphics[scale=1]{typeconeFan}}\hspace{1.5cm}\includegraphics[width=.4\linewidth]{typecone}}
-	\caption{A complete $2$-dimensional fan~$\Fan$ with five rays $v_1,\dots,v_5$ and five maximal cones~$a,\dots, e$ (left), and the intersection of $\b{K}\ctypeCone(F)$ with a hyperplane to get a $2$-dimensional slice (right).
-On top of each face of $\ctypeCone(F)$, we depict an example of polytope with the corresponding normal fan.}
-	\label{fig:typecone}
+	\centerline{\includegraphics[scale=.8]{typeConeCoarsenings}}
+	\caption{The type cone~$\ctypeCone(\Fan)$ of the fan~$\Fan$ of \cref{fig:typeCone}\,(left).
+On top of each face of $\ctypeCone(\Fan)$, we depict an example of polytope with the corresponding normal fan.}
+	\label{fig:typeConeCoarsenings}
 \end{figure}
@@
 
-Recall that the \defn{Minkowski sum} of two polytopes $P$ and $Q$ is the polytope $P+Q=\set{p+q}{p\in P\text{ and } q\in Q}$.
+We now discuss the connection between convex combinations in the type cone and Minkowski sums of polytopes.
+Recall that the \defn{Minkowski sum} of two polytopes~$P$ and~$Q$ is the polytope $P + Q \eqdef \set{p + q}{p \in P\text{ and } q \in Q}$.
 
@@
 These correspond to indecomposable polytopes, see~\cite{Meyer} or \cite{McMullen-typeCone}.
-A polytope $P\subseteq\R^n$ is called \defn{indecomposable} if all its weak Minkowski summands are of the form $\lambda P+t$ for some $\lambda \ge 0$ and $t \in \R^n$.
+A polytope $P \subseteq \R^n$ is called \defn{indecomposable} if all its weak Minkowski summands are of the form $\lambda P+t$ for some $\lambda \ge 0$ and $t \in \R^n$.
 
 \begin{corollary}
-% % \arnau{See \cite{Meyer} and \cite{McMullen-typeCone}}
-Any polytope in~$\ctypeCone(\Fan)$ is the Minkowski sum of at most~$N-n$ indecomposable polytopes corresponding to the rays of~$\b{K}\ctypeCone(\Fan)$.
+Any polytope in~$\ctypeCone(\Fan)$ is the Minkowski sum of at most~$N-n$ indecomposable polytopes corresponding to some rays of~$\b{K}\ctypeCone(\Fan)$.
 \end{corollary}
@@
 There are two natural ways this construction generalizes to arbitrary pairs of polyhedra. On the one hand, we have $P - Q = \set{x \in \R^n}{x + Q \subseteq P}$. 
-Notice that $P_\b{h}-P_{\b{h}'}=P_{\b{h} - \b{h'}}$ when $P_{\b{h}'}$ is a Minkowski summand of $P_\b{h}$.
+Notice that $P_\b{h} - P_{\b{h}'} = P_{\b{h} - \b{h'}}$ when $P_{\b{h}'}$ is a Minkowski summand of $P_\b{h}$.
 Considering arbitrary differences of support functions gives rise to \defn{virtual polyhedra}, which is the Grothendieck group of the semigroup of polytopes with Minkowski sums~\cite{PukhlikovKhovanskii}.
@@
 \begin{corollary}
-Let $\b{h}_1,\dots, \b{h}_{N-n}\in \ctypeCone(\Fan)$ form a basis of the left kernel of~$\b{G}$.
-Then for any~$\b{h} \in \ctypeCone(\Fan)$, the polytope~$P_\b{h}$ has a unique representation (up to translation) as a signed Minkowski sum of dilates of $P_{\b{h}_1},\dots, P_{\b{h}_{N-n}}$.
+Let $\b{h}^{(1)},\dots, \b{h}^{(N-n)}\in \ctypeCone(\Fan)$ form a basis of the left kernel of~$\b{G}$.
+Then for any~$\b{h} \in \ctypeCone(\Fan)$, the polytope~$P_\b{h}$ has a unique representation (up to translation) as a signed Minkowski sum of dilates of $P_{\b{h}^{(1)}}, \dots, P_{\b{h}^{(N-n)}}$.
 \end{corollary}
 \begin{proof}
-It suffices to express the projection of $\b{h}$ onto the left kernel of~$\b{G}$ in terms of $\b{h}_1,\dots, \b{h}_{N-n}$, and to separate those terms with positive and negative coefficients to express Minkowski sums and differences.
+It suffices to express the projection of $\b{h}$ onto the left kernel of~$\b{G}$ in terms of $\b{h}^{(1)}, \dots, \b{h}^{(N-n)}$, and to separate those terms with positive and negative coefficients to express Minkowski sums and differences.
 \end{proof}
@@
 \arnau{This has consequences in expressing volume and other valuations! I have to have a look at it.}
+\arnau{By \cite{McMullen-Valuations} valuations on the polytope $\alpha_1 P_{\b{h}^{(1)}}+\cdots+\alpha_{N-n}P_{\b{h}^{(N-n)}}$ (such as volume) are a polynomial on $\alpha_1\dots\alpha_{N-n}$ with coefficients the mixed volumes.
+This also works when the $\alpha$'s are not necessarily positive \cite{ArdilaBenedettiDoker}.
+Does this help in any way?}
 In the particular case when the type cone is simplicial, then we can get rid of the Minkowski differences.
@@
 \begin{corollary}
-If the type cone~$\typeCone(\Fan)$ of $\Fan$ is simplicial, then the $N-n$ idecomposable polytopes $P_{\b{h}_1},\dots, P_{\b{h}_{N-n}}$ arising from the rays of $\ctypeCone(\Fan)$ verify that 
+If the type cone~$\typeCone(\Fan)$ of $\Fan$ is simplicial, then the $N-n$ idecomposable polytopes $P_{\b{h}^{(1)}}, \dots, P_{\b{h}^{(N-n)}}$ arising from the rays of $\ctypeCone(\Fan)$ verify that 
 \begin{enumerate}[(i)]
-\item  every $P_\b{h}$ with $\b{h}\in \typeCone(\Fan)$ has a unique representation (up to translation) as a Minkowski sum of positive dilates of $P_{\b{h}_1},\dots, P_{\b{h}_{N-n}}$; and
-\item  every $P_\b{h}$ with $\b{h}\in \ctypeCone(\Fan)$ has a unique representation (up to translation) as a Minkowski sum of non-negative dilates of $P_{\b{h}_1},\dots, P_{\b{h}_{N-n}}$.
+\item  every $P_\b{h}$ with $\b{h}\in \typeCone(\Fan)$ has a unique representation (up to translation) as a Minkowski sum of positive dilates of $P_{\b{h}^{(1)}}, \dots, P_{\b{h}^{(N-n)}}$; and
+\item  every $P_\b{h}$ with $\b{h}\in \ctypeCone(\Fan)$ has a unique representation (up to translation) as a Minkowski sum of non-negative dilates of $P_{\b{h}^{(1)}}, \dots, P_{\b{h}^{(N-n)}}$.
 \end{enumerate} 
@@
 
-In the case of \cref{ex:typecone}, we get that any polytope in $\ctypeCone(\Fan)$ is a positive Minkowski combination of a triangle and two of its edges. This is the normal fan of 
-Loday's $2$-dimensional associahedron, and the realization as a Minkowski sum of faces of a simplex was given by Postnikov in~\cite{Postnikov}.
-
-\arnau{By \cite{McMullen-Valuations} valuations on the polytope $\alpha_1P_{\b{h}_1}+\cdots+\alpha_{N-n}P_{\b{h}_{N-n}}$ (such as volume) are a polynomial on $\alpha_1\dots\alpha_{N-n}$ with coefficients the mixed volumes.
-This also works when the $\alpha$'s are not necessarily positive \cite{ArdilaBenedettiDoker}.
-Does this help in any way?}
+\begin{example}
+\label{exm:typeConeMinkowskiSum}
+\enlargethispage{.4cm}
+Consider the $2$-dimensional fan~$\Fan$ of \cref{fig:typeCone}\,(left) whose type cone has been described in \cref{exm:typeCone} and represented in \cref{fig:typeCone}\,(right).
+As illustrated in \cref{fig:typeConeCoarsenings}, the rays of the closed type cone~$\ctypeCone(\Fan)$ are directed by the height vectors~$(1,2,1,2,1)$ (corresponding to a triangle), $(0,1,1,0,1)$ (corresponding to a vertical segment) and~$(1,0,1,1,0)$ (corresponding to a horizontal segment).
+Therefore, any polytope in~$\ctypeCone(\Fan)$ is (up to translation) a positive Minkowski combination of a triangle and two edges.
+\cref{fig:typeConeMinkowskiSum} illustrates this property for the polytope of \cref{fig:typeCone}\,(middle) corresponding to the height vector~$(\nicefrac{1}{2}, \nicefrac{3}{4}, \nicefrac{5}{4}, 1, \nicefrac{5}{4})$.
+Note that~$\Fan$ is the normal fan of J.-L.~Loday's $2$-dimensional associahedron, whose realization as a Minkowski sum of faces of a simplex was given by A.~Postnikov in~\cite{Postnikov}.
+
+\begin{figure}[htpb]
+	\capstart
+	\centerline{
+	\begin{tabular}{c@{\;$=$\;}c@{\,$+$\,}c@{\,$+$\,}c@{\,}l@{\,}l}
+	$(\frac{1}{2}, \frac{3}{4}, \frac{5}{4}, 1, \frac{5}{4})$ & $\frac{1}{6}(1,2,1,2,1)$ & $\frac{3}{4}(0,1,1,0,1)$ & $\frac{1}{2}(1,0,1,1,0)$ & $-\,\frac{1}{6}(1,0,-1,-1,0)$ & $-\,\frac{1}{3}(0,1,1,0,-1)$ \\
+	\raisebox{-0.5\height}{\includegraphics[scale=.5]{typeConePolytope}} & \raisebox{-0.5\height}{\includegraphics[scale=.5]{typeConeMinkowskiSum1}} & \raisebox{-0.5\height}{\includegraphics[scale=.5]{typeConeMinkowskiSum2}} & \raisebox{-0.5\height}{\includegraphics[scale=.5]{typeConeMinkowskiSum3}} & $+$ translation.
+	\end{tabular}
+	}
+	\caption{The polytope of \cref{fig:typeCone}\,(middle) is a Minkowski sum of a triangle and two edges.}
+	\label{fig:typeConeMinkowskiSum}
+\end{figure}
+\end{example}
 
@@
 We now focus on the normal fan~$\gvectorFan[n]$ of~$\Asso[n]$.
-Since~$\Asso[n]$ lives in a hyperplane of~$\R^{n+1}$, so does its normal fan.
+Since~$\Asso[n]$ leaves in a hyperplane of~$\R^{n+1}$, so does its normal fan.
 Let~$\HH \eqdef \bigset{\b{x} \in \R^{n+1}}{\sum_{\ell \in [n+1]} x_\ell = 0}$ and~$\pi : \R^{n+1} \to \HH$ denote the orthogonal projection.
@@
 Consider the fan~$\gvectorFan[2]$ and~$\gvectorFan[3]$ illustrated in \cref{fig:lodayFans}.
-The type cone of~$\gvectorFan[2]$ lives in~$\R^5$ and has a linearity space of dimension~$2$ (this is the type cone studied in \cref{ex:typecone}).
+The type cone of~$\gvectorFan[2]$ lives in~$\R^5$ and has a linearity space of dimension~$2$.
 It has $3$ facet defining inequalities (given below), which correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso} and illustrated in \cref{fig:labelFacetDefiningInequalititesAsso}\,(left).

### 2019-04-09 thirdPaper/draft/typeConeAssociahedra.tex

@@
 Consider the fan~$\gvectorFan[2]$ and~$\gvectorFan[3]$ illustrated in \cref{fig:lodayFans}.
-The type cone of~$\gvectorFan[2]$ lives in~$\R^5$ and has a linearity space of dimension~$2$.
-It has $3$ facet defining inequalities (given below), which correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso} and illustrated in \cref{fig:labelFacetDefiningInequalititesAsso}\,(left).
+The type cone of~$\gvectorFan[2]$ lives in~$\R^5$ and has a linearity space of dimension~$2$ (this is the type cone studied in \cref{ex:typecone}).
+It has $3$ facet-defining inequalities (given below), which correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso} and illustrated in \cref{fig:labelFacetDefiningInequalititesAsso}\,(left).
 

### 2019-04-09 thirdPaper/draft/typeConeAssociahedra.tex
layout

@@
 
+\vspace{2cm}
+\centerline{\includegraphics[scale=.8]{typeConeCoarsenings}}
+
 \newpage
 \tableofcontents
+
+\vspace{-.8cm}
+\enlargethispage{.3cm}
 
@@
 Consider the fan~$\gvectorFan[2]$ and~$\gvectorFan[3]$ illustrated in \cref{fig:lodayFans}.
-The type cone of~$\gvectorFan[2]$ lives in~$\R^5$ and has a linearity space of dimension~$2$ (this is the type cone studied in \cref{ex:typecone}).
+The type cone of~$\gvectorFan[2]$ lives in~$\R^5$ and has a linearity space of dimension~$2$ (this is the type cone studied in \cref{exm:typeCone,exm:typeConeCoarsenings,exm:typeConeMinkowskiSum}).
 It has $3$ facet-defining inequalities (given below), which correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso} and illustrated in \cref{fig:labelFacetDefiningInequalititesAsso}\,(left).
@@
 
+\addtocontents{toc}{\bigskip}
 \bibliographystyle{alpha}

### 2019-04-09 thirdPaper/draft/typeConeAssociahedra.tex
layout

@@
 \begin{itemize}
-\item \textbf{any initial seed}, regardless of whether it is acyclic or not (see \cref{exm:typeConeCA,fig:clusterFans,fig:labelFacetDefiningInequalititesCA} for examples in types~$A_3$ and~$C_3$~cyclic).
+\item \textbf{any initial seed}, regardless of whether it is acyclic or not (see \cref{exm:typeConeCA,fig:clusterFans,fig:labelFacetDefiningInequalititiesCA1,fig:labelFacetDefiningInequalititiesCA2} for examples in types~$A_3$ and~$C_3$~cyclic).
 In contrast, the proof of~\cite{BazierMatteDouvilleMousavandThomasYildirim} only treats acyclic initial seeds.
@@
 \item The facet-defining inequalities of the type cone of~$\Fan$ correspond to very specific pairs of adjacent maximal cones of~$\Fan$ whose corresponding linear dependences minimally generate all such dependences.
-While they correspond to mesh mutations for cluster algebras and brick $2$-acyclic gentle algebras, they are not clear in general (see for instance \cref{fig:labelFacetDefiningInequalititesNKC}\,(right)).
+While they correspond to mesh mutations for cluster algebras and brick $2$-acyclic gentle algebras, they are not clear in general (see for instance \cref{fig:labelFacetDefiningInequalititiesNKC}\,(right)).
 It would be particularly interesting to fully understand these specific mutations for arbitrary ($\tau$-tilting finite) gentle algebras.
@@
 The type cone of~$\gvectorFan[2]$ lives in~$\R^5$ and has a linearity space of dimension~$2$ (this is the type cone studied in \cref{exm:typeCone,exm:typeConeCoarsenings,exm:typeConeMinkowskiSum}).
-It has $3$ facet-defining inequalities (given below), which correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso} and illustrated in \cref{fig:labelFacetDefiningInequalititesAsso}\,(left).
+It has $3$ facet-defining inequalities (given below), which correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso} and illustrated in \cref{fig:labelFacetDefiningInequalititiesAsso}\,(left).
 
@@
 
+\medskip
 \noindent
@@
 The type cone of~$\gvectorFan[2]$ lives in~$\R^9$ and has a linearity space of dimension~$3$.
-It has $6$ facet-defining inequalities (given below), which correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso} and illustrated in \cref{fig:labelFacetDefiningInequalititesAsso}\,(left).
+It has $6$ facet-defining inequalities (given below), which correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso} and illustrated in \cref{fig:labelFacetDefiningInequalititiesAsso}\,(left).
 
@@
 \]
+\medskip
 
@@
 See \cref{subsec:typeConeCA,sec:clusterCategories} for a representation theoretic \mbox{interpretation}.}
-	\label{fig:labelFacetDefiningInequalititesAsso}
+	\label{fig:labelFacetDefiningInequalititiesAsso}
 \end{figure}
@@
 
-Combining \cref{coro:simplicialTypeCone}, \cref{coro:simplicialTypeConeAsso} and \cref{prop:extremalExchangeablePairsAsso}, we derive the following description of all polytopal realizations of the fan~$\gvectorFan[n]$, thus recovering all associahedra of~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan}.
-We note that the arguments used in~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} were quite different from the present approach.
+\enlargethispage{.2cm}
+Combining \cref{coro:simplicialTypeCone}, \cref{coro:simplicialTypeConeAsso} and \cref{prop:extremalExchangeablePairsAsso}, we derive the following description of all polytopal realizations of the fan~$\gvectorFan[n]$, recovering all associahedra of~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan}.
+Note that the arguments of~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} were quite different from the present~approach.
 
@@
 
-\vincent{Describe the rays of the type cone. They are the Minkowski basis.}
+%\vincent{Describe the rays of the type cone. They are the Minkowski basis.}
 
@@
 The type cone of the left fan of \cref{fig:clusterFans} lives in~$\R^9$ and has a linearity space of dimension~$3$.
-It has $6$ facet-defining inequalities (given below), which correspond to the mesh mutations of \cref{thm:extremalExchangeablePairsCA} as illustrated in \cref{fig:labelFacetDefiningInequalititesCA}\,(top).
+It has $6$ facet-defining inequalities (given below), which correspond to the mesh mutations of \cref{thm:extremalExchangeablePairsCA} as illustrated in \cref{fig:labelFacetDefiningInequalititiesCA1}.
 
@@
 
-\noindent
-The type cone of the right fan of \cref{fig:clusterFans} lives in~$\R^{12}$ and has a linearity space of dimension~$3$.
-It has $9$ facet-defining inequalities (given below), which correspond to the mesh mutations of \cref{thm:extremalExchangeablePairsCA} as illustrated in \cref{fig:labelFacetDefiningInequalititesCA}\,(bottom).
-
-\[
-\begin{array}{r|c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;}c@{\;}c@{\;}c@{}c@{}c@{}cc}
-\text{variables} & \rotatebox{70}{$x_1$} & \rotatebox{70}{$x_2$} & \rotatebox{70}{$x_3$} & \rotatebox{70}{$\frac{x_2 + x_3}{x_1}$} & \rotatebox{70}{$\frac{x_1 + x_3}{x_2}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2}{x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + x_1 x_3}{x_2 x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + x_2 x_3}{x_1 x_3}$} & \rotatebox{70}{$\frac{x_1 + x_2 + x_3}{x_1 x_2}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + 2 x_1 x_3 + x_3^2}{x_2^2 x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + 2 x_2 x_3 + x_3^2}{x_1^2 x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + x_1 x_3 + x_2 x_3}{x_1 x_2 x_3}$} \\[.2cm]
-\text{$\b{g}$-vectors} & \compactVectorT{1}{0}{0} & \compactVectorT{0}{1}{0} & \compactVectorT{0}{0}{1} & \compactVectorT{-1}{0}{1} & \compactVectorT{1}{-1}{0} & \compactVectorT{0}{2}{-1} & \compactVectorT{0}{1}{-1} & \compactVectorT{-1}{1}{0} & \compactVectorT{0}{-1}{0} & \compactVectorT{0}{0}{-1} & \compactVectorT{-2}{0}{1} & \compactVectorT{-1}{0}{0}  \\[.6cm]
-\text{facet}		& 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 1 & 0 & 0 & 0 & \red \circled{A} \\
-\text{defining}		& 0 & 0 & -1 & 1 & 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & \red \circled{B} \\
-\text{inequalities}	& 0 & 0 & 1 & -2 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 & \red \circled{C} \\
-					& 0 & -1 & 0 & 1 & 0 & 0 & 0 & 1 & 0 & 0 & -1 & 0 & \red \circled{D} \\
-					& 0 & 0 & 0 & 0 & 0 & 1 & -2 & 0 & 0 & 1 & 0 & 0 & \red \circled{E} \\
-					& 0 & 1 & 0 & 0 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 1 & \red \circled{F} \\
-					& 0 & 0 & 0 & 0 & 0 & -1 & 1 & 1 & 0 & 0 & 0 & -1 & \red \circled{G} \\
-					& 0 & 0 & 0 & 0 & 0 & 1 & 0 & -2 & 0 & 0 & 1 & 0 & \red \circled{H} \\
-					& -1 & 0 & 0 & 0 & 1 & 0 & 1 & 0 & 0 & -1 & 0 & 0 & \red \circled{I} \\[.2cm]
-\end{array}
-\]
-
-%sage: B = Matrix([[0,-1,2],[1,0,-2],[-1,1,0]])
-%sage: CA = ClusterAlgebra(B)
-%
-%sage: CA.explore_to_depth(infinity)
-%sage: gvectors = CA.cluster_fan().rays()
-%sage: for gvector in gvectors:
-%....:     print gvector, CA.cluster_variable(gvector)
-%....:     
-%N(-1, 1, 0) (x0^2 + x1^2 + x1*x2)/(x0*x2)
-%N(0, 2, -1) (x0^2 + x1^2)/x2
-%N(1, 0, 0) x0
-%N(0, 0, 1) x2
-%N(-2, 0, 1) (x0^2 + x1^2 + 2*x1*x2 + x2^2)/(x0^2*x2)
-%N(1, -1, 0) (x0 + x2)/x1
-%N(0, 0, -1) (x0^2 + x1^2 + 2*x0*x2 + x2^2)/(x1^2*x2)
-%N(-1, 0, 1) (x1 + x2)/x0
-%N(0, -1, 0) (x0 + x1 + x2)/(x0*x1)
-%N(-1, 0, 0) (x0^2 + x1^2 + x0*x2 + x1*x2)/(x0*x1*x2)
-%N(0, 1, 0) x1
-%N(0, 1, -1) (x0^2 + x1^2 + x0*x2)/(x1*x2)
-%
-%sage: TCCA = type_cone_CA(CA)
-%sage: TCCA
-%A 12-dimensional polyhedron in QQ^12 defined as the convex hull of 1 vertex, 9 rays, 3 lines
-%sage: TCCA.lines()
-%(A line in the direction (0, 0, 1, 2, 0, 0, -2, 1, -1, -1, 1, -1),
-% A line in the direction (1, 2, 0, 0, 0, -1, 0, 0, -1, 0, 1, 1),
-% A line in the direction (0, 1, 0, -1, -1, 0, 1, -1, 0, 0, 0, 1))
-%sage: TCCA.inequalities()
-%(An inequality (-2, 1, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0) x + 0 >= 0,
-% An inequality (-1, 0, 0, 0, 0, 0, 0, 0, 0, 1, 1, 0) x + 0 >= 0,
-% An inequality (1, 0, 0, 0, -1, 0, 0, 1, 0, 0, -1, 0) x + 0 >= 0,
-% An inequality (0, 0, -1, 0, 0, 1, -1, 0, 0, 0, 0, 1) x + 0 >= 0,
-% An inequality (1, -1, 0, 0, 0, 0, 0, 0, 0, -1, 0, 1) x + 0 >= 0,
-% An inequality (0, 0, 0, -1, 0, 1, 0, 1, -1, 0, 0, 0) x + 0 >= 0,
-% An inequality (0, 1, 0, 0, 0, 0, 1, 0, 0, 0, 0, -2) x + 0 >= 0,
-% An inequality (0, 0, 1, 0, 0, -1, 0, 0, 1, 0, 0, 0) x + 0 >= 0,
-% An inequality (0, 0, 0, 1, 1, 0, 0, -2, 0, 0, 0, 0) x + 0 >= 0)
-
-\begin{figure}
+\begin{figure}[h]
 	\capstart
@@
     \end{adjustbox}
-    %
+	\caption{The facet-defining inequalities of the type cone~$\typeCone(\gvectorFan[\B_\circ])$ of the cluster fan correspond to the mesh mutations described in \cref{thm:extremalExchangeablePairsCA}.
+See \cref{sec:clusterCategories} for a representation theoretic \mbox{interpretation}.}
+	\label{fig:labelFacetDefiningInequalititiesCA1}
+\end{figure}
+
+\noindent
+The type cone of the right fan of \cref{fig:clusterFans} lives in~$\R^{12}$ and has a linearity space of dimension~$3$.
+It has $9$ facet-defining inequalities (given below), which correspond to the mesh mutations of \cref{thm:extremalExchangeablePairsCA} as illustrated in \cref{fig:labelFacetDefiningInequalititiesCA2}.
+
+\[
+\begin{array}{r|c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;}c@{\;}c@{\;}c@{}c@{}c@{}cc}
+\text{variables} & \rotatebox{70}{$x_1$} & \rotatebox{70}{$x_2$} & \rotatebox{70}{$x_3$} & \rotatebox{70}{$\frac{x_2 + x_3}{x_1}$} & \rotatebox{70}{$\frac{x_1 + x_3}{x_2}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2}{x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + x_1 x_3}{x_2 x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + x_2 x_3}{x_1 x_3}$} & \rotatebox{70}{$\frac{x_1 + x_2 + x_3}{x_1 x_2}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + 2 x_1 x_3 + x_3^2}{x_2^2 x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + 2 x_2 x_3 + x_3^2}{x_1^2 x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + x_1 x_3 + x_2 x_3}{x_1 x_2 x_3}$} \\[.2cm]
+\text{$\b{g}$-vectors} & \compactVectorT{1}{0}{0} & \compactVectorT{0}{1}{0} & \compactVectorT{0}{0}{1} & \compactVectorT{-1}{0}{1} & \compactVectorT{1}{-1}{0} & \compactVectorT{0}{2}{-1} & \compactVectorT{0}{1}{-1} & \compactVectorT{-1}{1}{0} & \compactVectorT{0}{-1}{0} & \compactVectorT{0}{0}{-1} & \compactVectorT{-2}{0}{1} & \compactVectorT{-1}{0}{0}  \\[.6cm]
+\text{facet}		& 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 1 & 0 & 0 & 0 & \red \circled{A} \\
+\text{defining}		& 0 & 0 & -1 & 1 & 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & \red \circled{B} \\
+\text{inequalities}	& 0 & 0 & 1 & -2 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 & \red \circled{C} \\
+					& 0 & -1 & 0 & 1 & 0 & 0 & 0 & 1 & 0 & 0 & -1 & 0 & \red \circled{D} \\
+					& 0 & 0 & 0 & 0 & 0 & 1 & -2 & 0 & 0 & 1 & 0 & 0 & \red \circled{E} \\
+					& 0 & 1 & 0 & 0 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 1 & \red \circled{F} \\
+					& 0 & 0 & 0 & 0 & 0 & -1 & 1 & 1 & 0 & 0 & 0 & -1 & \red \circled{G} \\
+					& 0 & 0 & 0 & 0 & 0 & 1 & 0 & -2 & 0 & 0 & 1 & 0 & \red \circled{H} \\
+					& -1 & 0 & 0 & 0 & 1 & 0 & 1 & 0 & 0 & -1 & 0 & 0 & \red \circled{I} \\[.2cm]
+\end{array}
+\]
+
+%sage: B = Matrix([[0,-1,2],[1,0,-2],[-1,1,0]])
+%sage: CA = ClusterAlgebra(B)
+%
+%sage: CA.explore_to_depth(infinity)
+%sage: gvectors = CA.cluster_fan().rays()
+%sage: for gvector in gvectors:
+%....:     print gvector, CA.cluster_variable(gvector)
+%....:     
+%N(-1, 1, 0) (x0^2 + x1^2 + x1*x2)/(x0*x2)
+%N(0, 2, -1) (x0^2 + x1^2)/x2
+%N(1, 0, 0) x0
+%N(0, 0, 1) x2
+%N(-2, 0, 1) (x0^2 + x1^2 + 2*x1*x2 + x2^2)/(x0^2*x2)
+%N(1, -1, 0) (x0 + x2)/x1
+%N(0, 0, -1) (x0^2 + x1^2 + 2*x0*x2 + x2^2)/(x1^2*x2)
+%N(-1, 0, 1) (x1 + x2)/x0
+%N(0, -1, 0) (x0 + x1 + x2)/(x0*x1)
+%N(-1, 0, 0) (x0^2 + x1^2 + x0*x2 + x1*x2)/(x0*x1*x2)
+%N(0, 1, 0) x1
+%N(0, 1, -1) (x0^2 + x1^2 + x0*x2)/(x1*x2)
+%
+%sage: TCCA = type_cone_CA(CA)
+%sage: TCCA
+%A 12-dimensional polyhedron in QQ^12 defined as the convex hull of 1 vertex, 9 rays, 3 lines
+%sage: TCCA.lines()
+%(A line in the direction (0, 0, 1, 2, 0, 0, -2, 1, -1, -1, 1, -1),
+% A line in the direction (1, 2, 0, 0, 0, -1, 0, 0, -1, 0, 1, 1),
+% A line in the direction (0, 1, 0, -1, -1, 0, 1, -1, 0, 0, 0, 1))
+%sage: TCCA.inequalities()
+%(An inequality (-2, 1, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0) x + 0 >= 0,
+% An inequality (-1, 0, 0, 0, 0, 0, 0, 0, 0, 1, 1, 0) x + 0 >= 0,
+% An inequality (1, 0, 0, 0, -1, 0, 0, 1, 0, 0, -1, 0) x + 0 >= 0,
+% An inequality (0, 0, -1, 0, 0, 1, -1, 0, 0, 0, 0, 1) x + 0 >= 0,
+% An inequality (1, -1, 0, 0, 0, 0, 0, 0, 0, -1, 0, 1) x + 0 >= 0,
+% An inequality (0, 0, 0, -1, 0, 1, 0, 1, -1, 0, 0, 0) x + 0 >= 0,
+% An inequality (0, 1, 0, 0, 0, 0, 1, 0, 0, 0, 0, -2) x + 0 >= 0,
+% An inequality (0, 0, 1, 0, 0, -1, 0, 0, 1, 0, 0, 0) x + 0 >= 0,
+% An inequality (0, 0, 0, 1, 1, 0, 0, -2, 0, 0, 0, 0) x + 0 >= 0)
+
+\begin{figure}
+	\capstart
     \begin{adjustbox}{center}
@@
 See \cref{sec:clusterCategories} for a representation theoretic \mbox{interpretation}.}
-	\label{fig:labelFacetDefiningInequalititesCA}
+	\label{fig:labelFacetDefiningInequalititiesCA2}
 \end{figure}
@@
 The type cone of the left fan of \cref{fig:nonkissingFans} lives in~$\R^9$ and has a linearity space of dimension~$3$.
-It has $6$ facet-defining inequalities (given below), which correspond to the flips described in \cref{prop:interestingExchangeablePairsNKC,prop:extremalExchangeablePairsNKC} and illustrated in \cref{fig:labelFacetDefiningInequalititesNKC}\,(left).
+It has $6$ facet-defining inequalities (given below), which correspond to the flips described in \cref{prop:interestingExchangeablePairsNKC,prop:extremalExchangeablePairsNKC} and illustrated in \cref{fig:labelFacetDefiningInequalititiesNKC}\,(left).
 
@@
 The type cone of the right fan of \cref{fig:nonkissingFans} lives in~$\R^{11}$ and has a linearity space of dimension~$3$.
-It has $9$ facet-defining inequalities (given below), which correspond to the flips illustrated in \cref{fig:labelFacetDefiningInequalititesNKC}\,(right).
+It has $9$ facet-defining inequalities (given below), which correspond to the flips illustrated in \cref{fig:labelFacetDefiningInequalititiesNKC}\,(right).
 In particular, it is not simplicial.
@@
 See also \cref{sec:extricats}.}
-	\label{fig:labelFacetDefiningInequalititesNKC}
+	\label{fig:labelFacetDefiningInequalititiesNKC}
 \end{figure}

### 2019-04-10 thirdPaper/draft/typeConeAssociahedra.tex
section 4 intro

@@
 \centerline{\includegraphics[scale=.8]{typeConeCoarsenings}}
+\vspace{.5cm}
+\centerline{The type cone of type~$A_2$.}
 
@@
 Again, this result mainly relies on finding which relations minimally generate the relations between the $\b{g}$-vectors in the non-kissing complex.
-We present both a purely combinatorial proof (see \cref{subsec:typeConeCA}) and a purely algebraic proof for arbitrary brick algebras based on extriangulated categories (see \cref{sec:extricats}).
+We present both a purely combinatorial proof (see \cref{subsec:typeConeCA}) and a purely algebraic proof for (non-necessarily gentle) brick algebras making use of extriangulated categories (see \cref{sec:extricats}).
+Our algebraic proof is based on an analogue of a result of M. Auslander~\cite{Auslander1984} relating to minimal generators of Grothendieck groups.
+Along the way, we need to generalise, for extriangulated categories, several results from cluster-tilting theory on indices~\cite{DehyKeller} and on abelian quotients~\cite{BuanMarshReiten, KellerReiten} that were known for triangulated categories.
+We note however, that our assumptions are not quite the expected ones.
+This is related to the fact that the Grothendieck groups of cluster categories are badly behaved (e.g. the Grothendieck group of a cluster category of type~$A_2$ is trivial):
+so as to overcome this difficulty, we replace the triangulated structure of cluster categories by some relative extriangulated structure, before considering Grothendieck groups.
+This explains why we consider projective objects rather than cluster-tilting objects for extriangulated categories.
 
@@
 
-\begin{figure}[htpb]
-	\capstart
-	\centerline{{\includegraphics[scale=1]{typeConeFan}} \quad {\includegraphics[scale=1]{typeConePolytope}} \quad \raisebox{.5cm}{\includegraphics[scale=.45]{typeCone}}}
-	\caption{A $2$-dimensional fan~$\Fan$ with five rays $1, \dots, 5$ and five maximal cones~$a, \dots, e$ (left), its polytopal realization corresponding to the height vector~$(\nicefrac{1}{2}, \nicefrac{3}{4}, 1, 1, \nicefrac{5}{4})$ (middle), and the intersection of $\b{K}\ctypeCone(\Fan)$ with a hyperplane to get a $2$-dimensional slice (right).}
-	\label{fig:typeCone}
-\end{figure}
+% \begin{figure}[htpb]
+% 	\capstart
+% 	\centerline{{\includegraphics[scale=1]{typeConeFan}} \quad {\includegraphics[scale=1]{typeConePolytope}} \quad \raisebox{.5cm}{\includegraphics[scale=.45]{typeCone}}}
+% 	\caption{A $2$-dimensional fan~$\Fan$ with five rays $1, \dots, 5$ and five maximal cones~$a, \dots, e$ (left), its polytopal realization corresponding to the height vector~$(\nicefrac{1}{2}, \nicefrac{3}{4}, 1, 1, \nicefrac{5}{4})$ (middle), and the intersection of $\b{K}\ctypeCone(\Fan)$ with a hyperplane to get a $2$-dimensional slice (right).}
+% 	\label{fig:typeCone}
+% \end{figure}
 \end{example}

### 2019-04-10 thirdPaper/draft/typeConeAssociahedra.tex
rename figures

--- 2019-04-09 thirdPaper/draft/typeConeAssociahedra.tex
@@
 
-\vspace{-.8cm}
-\enlargethispage{.3cm}
+\vspace{-1cm}
+\enlargethispage{.5cm}
 
@@
 More precisely, they fix a finite type cluster algebra~$\c{A}$ and consider the real euclidean space~$\R^\c{V}$ indexed by the set~$\c{V}$ of cluster variables of~$\c{A}$.
-Starting from an acyclic initial seed~$\seed_\circ$, they consider a certain set~$\c{M}$ of mesh mutations and compute the corresponding linear dependences between the $\b{g}$-vectors, that can be interpreted as linear spaces in~$\R^\c{V}$.
+Starting from an acyclic initial seed~$\seed_\circ$, they consider a set~$\c{M}$ of mesh mutations and compute the corresponding linear dependences between the $\b{g}$-vectors, that can be interpreted as linear spaces in~$\R^\c{V}$.
 Finally, they perturb these mesh linear spaces by a collection~$\b{\ell} \in \R^{\c{M}}$ of positive parameters and intersect the resulting perturbed mesh affine spaces with the positive orthant of~$\R^\c{V}$ (see \cref{subsec:typeConeCA}).
@@
 \medskip
+\enlargethispage{.5cm}
 In this paper, we revisit, extend and explore further this construction using a reversed approach.
@@
 \smallskip
-\begin{itemize}
+\begin{enumerate}[$\quad\bullet$]
 \item \textbf{any initial seed}, regardless of whether it is acyclic or not (see \cref{exm:typeConeCA,fig:clusterFans,fig:labelFacetDefiningInequalititiesCA1,fig:labelFacetDefiningInequalititiesCA2} for examples in types~$A_3$ and~$C_3$~cyclic).
@@
 In contrast, the proof of~\cite{BazierMatteDouvilleMousavandThomasYildirim} naturally applies to rational parameters and then requires to apply an approximation argument.
-\end{itemize}
+\end{enumerate}
 
@@
 \noindent
+\enlargethispage{.3cm}
 These advantages all follow from one essential feature of our reversed approach.
 Namely, it enables to completely separate the algebraic aspects from the geometric aspects of the problem:
-\begin{itemize}
+\begin{enumerate}[$\quad\bullet$]
 \item On the \textbf{algebraic side}, we study the relations between the $\b{g}$-vectors of a finite type cluster algebra and we show that the mesh mutations minimally generate these relations.
@@
 We then observe that our algebraic result precisely states that all type cones of $\b{g}$-vector fans of cluster algebras are simplicial from which we derive all our geometric consequences (see \cref{sec:applications}).
-\end{itemize}
+\end{enumerate}
 
@@
 \smallskip
-\begin{itemize}
+\begin{enumerate}[$\quad\bullet$]
 \item \textbf{Gentle associahedra} were constructed in~\cite{PaluPilaudPlamondon-nonkissing} as polytopal realizations of finite non-kissing complexes of gentle bound quivers.
@@
 Again, this result mainly relies on finding which relations minimally generate the relations between the $\b{g}$-vectors in the non-kissing complex.
-We present both a purely combinatorial proof (see \cref{subsec:typeConeCA}) and a purely algebraic proof for arbitrary brick algebras based on extriangulated categories (see \cref{sec:extricats}).
+We present both a purely combinatorial proof (see \cref{subsec:typeConeCA}) and a purely algebraic proof for (non-necessarily gentle) brick algebras making use of extriangulated categories (see \cref{sec:extricats}).
+Our algebraic proof is based on an analogue of a result of M. Auslander~\cite{Auslander1984} relating to minimal generators of Grothendieck groups.
+Along the way, we need to generalise, for extriangulated categories, several results from cluster-tilting theory on indices~\cite{DehyKeller} and on abelian quotients~\cite{BuanMarshReiten, KellerReiten} that were known for triangulated categories.
+We note however, that our assumptions are not quite the expected ones.
+This is related to the fact that the Grothendieck groups of cluster categories are badly behaved (\eg the Grothendieck group of a cluster category of type~$A_2$ is trivial).
+So as to overcome this difficulty, we replace the triangulated structure of cluster categories by some relative extriangulated structure, before considering Grothendieck groups.
+This explains why we consider projective objects rather than cluster-tilting objects for extriangulated categories.
 
@@
 Our results describe nevertheless all polytopal realizations of the graphical nested fans.
-\end{itemize}
+\end{enumerate}
 
 \smallskip
-\enlargethispage{.3cm}
+\enlargethispage{.5cm}
 Further families of generalizations of the associahedron certainly deserve to be studied with our type cone approach.
@@
 \smallskip
-\begin{itemize}
+\begin{enumerate}[$\quad\bullet$]
 \item The facet-defining inequalities of the type cone of~$\Fan$ correspond to very specific pairs of adjacent maximal cones of~$\Fan$ whose corresponding linear dependences minimally generate all such dependences.
@@
 It would be interesting to obtain similar algebraic interpretations for the rays of the type cones of the non-kissing fans of gentle algebras.
-\end{itemize}
+\end{enumerate}
 

### 2019-04-10 thirdPaper/draft/typeConeAssociahedra.tex
problem convention

@@
 \vspace{-1cm}
-\enlargethispage{.5cm}
+\enlargethispage{.4cm}
 
@@
 \smallskip
-\begin{enumerate}[$\quad\bullet$]
+\begin{itemize}
 \item \textbf{any initial seed}, regardless of whether it is acyclic or not (see \cref{exm:typeConeCA,fig:clusterFans,fig:labelFacetDefiningInequalititiesCA1,fig:labelFacetDefiningInequalititiesCA2} for examples in types~$A_3$ and~$C_3$~cyclic).
@@
 In contrast, the proof of~\cite{BazierMatteDouvilleMousavandThomasYildirim} naturally applies to rational parameters and then requires to apply an approximation argument.
-\end{enumerate}
+\end{itemize}
 
@@
 Namely, it enables to completely separate the algebraic aspects from the geometric aspects of the problem:
-\begin{enumerate}[$\quad\bullet$]
+\begin{itemize}
 \item On the \textbf{algebraic side}, we study the relations between the $\b{g}$-vectors of a finite type cluster algebra and we show that the mesh mutations minimally generate these relations.
@@
 We then observe that our algebraic result precisely states that all type cones of $\b{g}$-vector fans of cluster algebras are simplicial from which we derive all our geometric consequences (see \cref{sec:applications}).
-\end{enumerate}
+\end{itemize}
 
@@
 Besides revisiting the construction of~\cite{ArkaniHamedBaiHeYan, BazierMatteDouvilleMousavandThomasYildirim} and extending it to any initial seed (acyclic or not) in any finite type cluster algebra (simply-laced or not), our reversed approach is also successful when applied to the $\b{g}$-vector fans of other families of generalizations of the associahedron.
-In the present paper, we explore specifically two families of such generalizations:
-
-\smallskip
-\begin{enumerate}[$\quad\bullet$]
-\item \textbf{Gentle associahedra} were constructed in~\cite{PaluPilaudPlamondon-nonkissing} as polytopal realizations of finite non-kissing complexes of gentle bound quivers.
+In the present paper, we explore specifically two families of such generalizations.
+
+\textbf{Gentle associahedra} were constructed in~\cite{PaluPilaudPlamondon-nonkissing} as polytopal realizations of finite non-kissing complexes of gentle bound quivers.
 These complexes encompass two families of simplicial complexes studied independently in the literature: on the one hand the grid associahedra introduced by T.~K.~Petersen, P.~Pylyavskyy and D.~Speyer in~\cite{PetersenPylyavskyySpeyer} for a staircase shape, studied by F.~Santos, C.~Stump and V.~Welker~\cite{SantosStumpWelker} for rectangular shapes, and extended by T.~McConville in~\cite{McConville} for arbitrary grid shapes; and on the other hand the Stokes polytopes and accordion associahedra studied by Y.~Baryshnikov~\cite{Baryshnikov}, F.~Chapoton~\cite{Chapoton-quadrangulations}, A.~Garver and T.~McConville~\cite{GarverMcConville} and T.~Manneville and V.~Pilaud~\cite{MannevillePilaud-accordion}.
@@
 
-\medskip
-\item \textbf{Graph associahedra} were defined by M.~Carr and S.~Devadoss~\cite{CarrDevadoss} in connection to C.~De Concini and C.~Procesi's wonderful arrangements~\cite{DeConciniProcesi}.
+\textbf{Graph associahedra} were defined by M.~Carr and S.~Devadoss~\cite{CarrDevadoss} in connection to C.~De Concini and C.~Procesi's wonderful arrangements~\cite{DeConciniProcesi}.
 As illustrated in~\cref{fig:specialGraphAssociahedra}, the graph associahedra of certain special families of graphs coincide with well-known families of polytopes: complete graph associahedra are permutahedra, path associahedra are classical associahedra, cycle associahedra are cyclohedra, and star associahedra are stellohedra.
@@
 Our results describe nevertheless all polytopal realizations of the graphical nested fans.
-\end{enumerate}
-
-\smallskip
-\enlargethispage{.5cm}
+
 Further families of generalizations of the associahedron certainly deserve to be studied with our type cone approach.
@@
 \medskip
+\enlargethispage{.1cm}
 Last but not least, the type cone approach naturally opens many research questions.
@@
 \newpage
+\addtocontents{toc}{\vspace{-.2cm}}
 \part{Type cones of $\b{g}$-vector fans}
@@
 The mutation of a seed~$\seed = (\B, \cluster)$ in the direction of a cluster variable~$x \in \cluster$ is a \defn{mesh mutation} that \defn{starts} (resp.~\defn{ends}) at~$x$ if the entries~$b_{xy}$ for~$y \in \cluster$ are all non-negative (resp.~all non-positive).
-A mesh mutation is \defn{initial} if it starts at a cluster variable of an initial seed.
-\vincent{Problem here. In my examples, the condition is to end at an initial cluster variable.}
+A mesh mutation is \defn{initial} if it ends at a cluster variable of an initial seed.
 We denote by~$\meshes$ the set of all pairs~$\{x,x'\}$ where~$x$ and~$x'$ are two cluster variables of~$\principalClusterAlgebra$ which are exchangeable via a non-initial mesh mutation.
@@
 
+%%%%%%%%%%%
+
 \subsection{Setting}
@@
 
+\vincent{Careful.
+There is a convention change with \cref{subsec:typeConeCA} and \cref{fig:labelFacetDefiningInequalititiesCA1,fig:labelFacetDefiningInequalititiesCA2}.
+Justify this change by the fact that we followed the convention of~\cite{BazierMatteDouvilleMousavandThomasYildirim} in \cref{subsec:typeConeCA}.}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-%%%%
+%%%%%%%%%%%
 
@@
 \yann{Rappels sur les categories extriangulees}
-%%%%
+
+%%%%%%%%%%%
+
 \subsection{Statement of preliminary results on extriangulated categories}
@@
 \end{proposition}
+
+%%%%%%%%%%%
 
@@
 
-%%%%
+%%%%%%%%%%%
+
+\subsection{Recollections on extriangulated categories}
+
+%%%%%%%%%%%
+
 \subsection{Proofs of preliminary results and of Theorem~\ref{theorem::extricats}}
@@
 
-%%%%
+%%%%%%%%%%%
+
 \subsection{Application to certain categories}
 
-%%
+%%%%%%%%%%%
+
 \subsubsection{$2$-Calabi--Yau triangulated categories}
@@
 
-%%%%
+%%%%%%%%%%%
+
 \subsection{Examples}
@@
 %%
+
 \subsubsection{Associative algebras}
@@
 
-\addtocontents{toc}{\bigskip}
+\addtocontents{toc}{\vspace{.2cm}}
 \bibliographystyle{alpha}

### 2019-04-10 thirdPaper/draft/typeConeAssociahedra.tex
mixed volumes

@@
 \vspace{.5cm}
-\centerline{The type cone of type~$A_2$.}
+\centerline{The type cone of the cluster fan of type~$A_2$.}
 
@@
 
-\vspace{-1cm}
-\enlargethispage{.4cm}
-
+\enlargethispage{-.3cm}
 \section*{Introduction}
@@
 \medskip
-\enlargethispage{.5cm}
 In this paper, we revisit, extend and explore further this construction using a reversed approach.
@@
 \noindent
-\enlargethispage{.3cm}
 These advantages all follow from one essential feature of our reversed approach.
@@
 
-\textbf{Gentle associahedra} were constructed in~\cite{PaluPilaudPlamondon-nonkissing} as polytopal realizations of finite non-kissing complexes of gentle bound quivers.
+\smallskip
+\begin{itemize}
+\item \textbf{Gentle associahedra} were constructed in~\cite{PaluPilaudPlamondon-nonkissing} as polytopal realizations of finite non-kissing complexes of gentle bound quivers.
 These complexes encompass two families of simplicial complexes studied independently in the literature: on the one hand the grid associahedra introduced by T.~K.~Petersen, P.~Pylyavskyy and D.~Speyer in~\cite{PetersenPylyavskyySpeyer} for a staircase shape, studied by F.~Santos, C.~Stump and V.~Welker~\cite{SantosStumpWelker} for rectangular shapes, and extended by T.~McConville in~\cite{McConville} for arbitrary grid shapes; and on the other hand the Stokes polytopes and accordion associahedra studied by Y.~Baryshnikov~\cite{Baryshnikov}, F.~Chapoton~\cite{Chapoton-quadrangulations}, A.~Garver and T.~McConville~\cite{GarverMcConville} and T.~Manneville and V.~Pilaud~\cite{MannevillePilaud-accordion}.
@@
 
-\textbf{Graph associahedra} were defined by M.~Carr and S.~Devadoss~\cite{CarrDevadoss} in connection to C.~De Concini and C.~Procesi's wonderful arrangements~\cite{DeConciniProcesi}.
+\smallskip
+\item \textbf{Graph associahedra} were defined by M.~Carr and S.~Devadoss~\cite{CarrDevadoss} in connection to C.~De Concini and C.~Procesi's wonderful arrangements~\cite{DeConciniProcesi}.
 As illustrated in~\cref{fig:specialGraphAssociahedra}, the graph associahedra of certain special families of graphs coincide with well-known families of polytopes: complete graph associahedra are permutahedra, path associahedra are classical associahedra, cycle associahedra are cyclohedra, and star associahedra are stellohedra.
@@
 Our results describe nevertheless all polytopal realizations of the graphical nested fans.
-
+\end{itemize}
+
+\smallskip
 Further families of generalizations of the associahedron certainly deserve to be studied with our type cone approach.
@@
 \medskip
-\enlargethispage{.1cm}
 Last but not least, the type cone approach naturally opens many research questions.
@@
 \smallskip
-\begin{enumerate}[$\quad\bullet$]
+\begin{itemize}
 \item The facet-defining inequalities of the type cone of~$\Fan$ correspond to very specific pairs of adjacent maximal cones of~$\Fan$ whose corresponding linear dependences minimally generate all such dependences.
@@
 \item The rays of the type cone of~$\Fan$ correspond to specific polytopes which form a positive Minkowski basis of all realizations of~$\Fan$ (see \cref{subsec:MinkowskiSums}).
-In particular, when the type cone is simplicial, any polytopal realization of~$\Fan$ has a unique representation (up to translation) as a Minkowski sum of positive dilates of the polytopes corresponding to the rays of the type cone.
+In particular, when the type cone is simplicial, any polytopal realization of~$\Fan$ has a unique representation (up to translation) as a Minkowski sum of positive dilates of these polytopes.
 For cluster algebras, it follows from~\cite[Sect.~6]{BazierMatteDouvilleMousavandThomasYildirim} that these polytopes are Newton polytopes of the $F$-polynomials.
-It would be interesting to obtain similar algebraic interpretations for the rays of the type cones of the non-kissing fans of gentle algebras.
-\end{enumerate}
+It would be interesting to obtain similar algebraic interpretations for the rays of the type cones of the non-kissing fans of gentle~algebras.
+
+\smallskip
+\item mixed volumes
+\end{itemize}
 
@@
 This is used in~\cite{ArdilaBenedettiDoker} to show that every generalized permutahedron can be written uniquely as a signed Minkowski sum of simplices. 
-\arnau{This has consequences in expressing volume and other valuations! I have to have a look at it.}
-\arnau{By \cite{McMullen-Valuations} valuations on the polytope $\alpha_1 P_{\b{h}^{(1)}}+\cdots+\alpha_{N-n}P_{\b{h}^{(N-n)}}$ (such as volume) are a polynomial on $\alpha_1\dots\alpha_{N-n}$ with coefficients the mixed volumes.
-This also works when the $\alpha$'s are not necessarily positive \cite{ArdilaBenedettiDoker}.
-Does this help in any way?}
 In the particular case when the type cone is simplicial, then we can get rid of the Minkowski differences.

### 2019-04-10 thirdPaper/draft/typeConeAssociahedra.tex
added mixed volume open question

@@
 \smallskip
-\item mixed volumes
+\item Once we get a representation of a polytope~$P$ as a signed Minkowski sum~$P=\sum_{1\leq i\leq k}\alpha_i Q_i$, we get a formula for the volume of $P$ as a multivariate polynomial in $\alpha_1,\dots,\alpha_k$ whose coefficients are the mixed volumes of $Q_1,\dots, Q_k$~\cite{ArdilaBenedettiDoker,McMullen-Valuations}.
+These encode rich combinatorial information when representing generalized permuahedra as positive Minkowski sum of coordinate simplices or hypersimplices~\cite{Postnikov}, and in particular for matroid polytopes~\cite{ArdilaBenedettiDoker}.
+It would be interesting to get such volume formulas for polytopal realizations of $\b{g}$-vector fans of cluster algebras, and combinatorial interpretations for their coefficients.
 \end{itemize}
@@
 It has five rays labeled~$1, \dots, 5$ and five maximal cones labeled~$a,\dots, e$.
-Its type cone~$\ctypeCone(\Fan)$ lies in~$\R^5$, but has a $2$-dimensional linearity space.
-The five pairs of adjacent maximal cones of~$\Fan$ give rise to following five defining inequalities for~$\ctypeCone(\Fan)$:
+Its type cone~$\typeCone(\Fan)$ lies in~$\R^5$, but has a $2$-dimensional linearity space.
+The five pairs of adjacent maximal cones of~$\Fan$ give rise to following five defining inequalities for~$\typeCone(\Fan)$:
 \begin{gather*}
@@
 Note that the inequalities~$H^>_{ae}$ and~$H^>_{de}$ are redundant.
-For example, the height vector~$(\nicefrac{1}{2}, \nicefrac{3}{4}, \nicefrac{5}{4}, 1, \nicefrac{5}{4})$ belongs to the type cone~$\ctypeCone(\Fan)$, and the corresponding polytope is represented in \cref{fig:typeCone} (middle).
-To represent this type cone, it suffices to represent~$\b{K}\ctypeCone(\Fan)$ which is an essential simplicial cone in~$\R^3$.
+For example, the height vector~$(\nicefrac{1}{2}, \nicefrac{3}{4}, \nicefrac{5}{4}, 1, \nicefrac{5}{4})$ belongs to the type cone~$\typeCone(\Fan)$, and the corresponding polytope is represented in \cref{fig:typeCone} (middle).
+To represent this type cone, it suffices to represent~$\b{K}\typeCone(\Fan)$ which is an essential simplicial cone in~$\R^3$.
 One can further reduce the dimension by intersecting with a transversal hyperplane to get a $2$-dimensional representation.
@@
 	\centerline{{\includegraphics[scale=1]{typeConeFan}} \quad {\includegraphics[scale=1]{typeConePolytope}} \quad \raisebox{.5cm}{\includegraphics[scale=.45]{typeCone}}}
-	\caption{A $2$-dimensional fan~$\Fan$ with five rays $1, \dots, 5$ and five maximal cones~$a, \dots, e$ (left), its polytopal realization corresponding to the height vector~$(\nicefrac{1}{2}, \nicefrac{3}{4}, 1, 1, \nicefrac{5}{4})$ (middle), and the intersection of $\b{K}\ctypeCone(\Fan)$ with a hyperplane to get a $2$-dimensional slice (right).}
+	\caption{A $2$-dimensional fan~$\Fan$ with five rays $1, \dots, 5$ and five maximal cones~$a, \dots, e$ (left), its polytopal realization corresponding to the height vector~$(\nicefrac{1}{2}, \nicefrac{3}{4}, 1, 1, \nicefrac{5}{4})$ (middle), and the intersection of $\b{K}\typeCone(\Fan)$ with a hyperplane to get a $2$-dimensional slice (right).}
 	\label{fig:typeCone}
@@
 For instance in 
+\arnau{unfinished sentence}
 

### 2019-04-10 thirdPaper/draft/typeConeAssociahedra.tex
figure dissection + grid

--- 2019-04-10 thirdPaper/draft/typeConeAssociahedra.tex
@@
 
-\enlargethispage{-.3cm}
+\newpage
 \section*{Introduction}
@@
 
-\vincent{Example picture?}
-
-\smallskip
+\begin{figure}[ht]
+	\capstart
+	\centerline{\includegraphics[scale=.8]{dissectionQuiver} \quad \includegraphics[scale=.35]{gridQuiver} \quad \includegraphics[scale=1.2]{bijectionAssociahedronDissection} \quad \includegraphics[scale=1.2]{bijectionAssociahedronGrid}}
+	\caption{}
+	\label{fig:dissectionGridQuivers}
+\end{figure}
+
 These two families of non-kissing complexes are well-behaved as they avoid all pathologies of \cref{rem:exchangeablePairsNKC}.
@@
 
-Note that by definition, $\gvector(\varnothing) = 0$ and $\gvector{W} = 0$ for all connected components~$W \in \connectedComponents(\graphG)$.
+Note that by definition, $\gvector{\varnothing} = 0$ and $\gvector{W} = 0$ for all connected components~$W \in \connectedComponents(\graphG)$.
 These vectors support a complete simplicial fan realization of the nested complex.

### 2019-04-10 thirdPaper/draft/typeConeAssociahedra.tex
missing sentence

@@
 \smallskip
-\item Once we get a representation of a polytope~$P$ as a signed Minkowski sum~$P=\sum_{1\leq i\leq k}\alpha_i Q_i$, we get a formula for the volume of $P$ as a multivariate polynomial in $\alpha_1,\dots,\alpha_k$ whose coefficients are the mixed volumes of $Q_1,\dots, Q_k$~\cite{ArdilaBenedettiDoker,McMullen-Valuations}.
+\item Once we get a representation of a polytope~$P$ as a signed Minkowski sum~$P = \sum_{i \in [k]}\alpha_i Q_i$, we get a formula for the volume of $P$ as a multivariate polynomial in $\alpha_1,\dots,\alpha_k$ whose coefficients are the mixed volumes of $Q_1,\dots, Q_k$~\cite{ArdilaBenedettiDoker,McMullen-Valuations}.
 These encode rich combinatorial information when representing generalized permuahedra as positive Minkowski sum of coordinate simplices or hypersimplices~\cite{Postnikov}, and in particular for matroid polytopes~\cite{ArdilaBenedettiDoker}.
-It would be interesting to get such volume formulas for polytopal realizations of $\b{g}$-vector fans of cluster algebras, and combinatorial interpretations for their coefficients.
+It would be interesting to get such volume formulas for polytopal realizations of $\b{g}$-vector fans of cluster algebras and gentle algebras, and combinatorial interpretations for their coefficients.
 \end{itemize}
@@
 Understanding the extremal adjacent pairs of~$\Fan$ enables to describe its type cone~$\typeCone(\Fan)$ and thus all its polytopal realizations.
-For instance in 
-\arnau{unfinished sentence}
+For instance, for the $2$-dimensional fan of \cref{exm:typeCone}, the extremal adjacent pairs are~$\{a,b\}$, $\{b,c\}$ and~$\{c,d\}$.
 

### 2019-04-10 thirdPaper/draft/typeConeAssociahedra.tex
minor reorganization subsubsections
cleaning sections 1 and 2

@@
 \typeCone(\c{G}) 
-%  & \eqdef \set{\b{h} \in \R^N}{\Fan \text{ is the normal fan of } P_\b{h}} \\
 & = \left\{\b{h} \in \R^N\;\middle|\;
@@
 
-Two rays~$\ray$ and~$\ray'$ of~$\Fan$ are
-% called \defn{compatible} if there are both contained in a cone of~$\Fan$ and 
-\defn{exchangeable} if there are two adjacent maximal cones~$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$ of~$\Fan$ with ${\rays \ssm \{\ray\} = \rays' \ssm \{\ray'\}}$.
-%If~$\rays(\Fan)$ denotes the set of rays of~$\Fan$, a \defn{compatibility degree} for~$\Fan$ is a function~$\compatibilityDegree{-}{-}: \rays(\Fan) \times \rays(\Fan) \to \R$ such that
-%\begin{itemize}
-%\item $\compatibilityDegree{\ray}{\ray'} = -1$ if~$\ray = \ray'$ and is non-negative otherwise,
-%\item $\compatibilityDegree{\ray}{\ray'} = 0$ if ~$\ray$ and~$\ray'$ are compatible,
-%\item $\compatibilityDegree{\ray}{\ray'} > 0$ if~$\ray \ne \ray'$ are incompatible,
-%\item $\compatibilityDegree{\ray}{\ray'} = 1 = \compatibilityDegree{\ray'}{\ray}$ if and only if~$\ray$ and~$\ray'$ are exchangeable.
-%\end{itemize}
+Two rays~$\ray$ and~$\ray'$ of~$\Fan$ are \defn{exchangeable} if there are two adjacent maximal cones~$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$ of~$\Fan$ with ${\rays \ssm \{\ray\} = \rays' \ssm \{\ray'\}}$.
 
@@
 This implies in particular that the rays~$\ray[s]$ for which~$\coefficient[{\ray[s]}][\rays][\rays'] \ne 0$ belong to~$\rays \cup \rays'$ for any pair~$\{\rays, \rays'\}$ of adjacent cones of~$\Fan$ with $\rays \ssm \{\ray\} = \rays' \ssm \{\ray'\}$.
-%These rays are thus called \defn{forced rays} for the exchangeable pair~$\{\ray, \ray'\}$.
 
@@
 
+%%%
+
 \subsubsection{Associahedra and their normal fans}
@@
 \label{prop:exchangeablePairsAsso}
-%Consider two exchangeable proper intervals~$[i,j]$ and~$[\ell,k]$ of~$[n+1]$, corresponding to two crossing diagonals~$(i-1,j+1)$ and~$(k-1,\ell+1)$ of the $(n+3)$-gon with~$0 \le i-1 < k-1 < j+1 < \ell+1 \le n+2$.
 Let~$(a,b)$ and~$(a',b')$ be two crossing diagonals with~${0 \le a < a' < b < b' \le n+2}$, and let~$T$ and~$T'$ be any two triangulations such that~$T \ssm \{(a,b)\} = T' \ssm \{(a',b')\}$.
@@
 \end{proposition}
+
+%%%
 
@@
 R_\b{\ell}(n) \eqdef \set{\b{z} \in \R^{X(n)}}{\begin{array}{l} \b{z} \ge 0, \quad \b{z}_{(0,n+2)} = 0 \quad\text{and}\quad \b{z}_{(a,a+1)} = 0 \text{ for all } 0 \le a \le n+1 \\ \b{z}_{(a,b-1)} + \b{z}_{(a+1,b)} - \b{z}_{(a,b)} - \b{z}_{(a+1,b-1)} = \b{\ell}_{(a,b)} \text{ for all } (a,b) \in Y(n) \end{array}}
-%\bigset{\b{z} \in \R^{X(n)}}{\b{z} \ge 0, \; \b{z}_{1,n+1} = 0 \text{ and } \b{z}_{i,j} + \b{z}_{i+1,j+1} - \b{z}_{i,j+1} - \b{z}_{i+1,j} = \b{\ell}_{i,j} \text{ for } (i,j) \in X(n-1)}
 \]
@@
 
-%We now extend the results of the previous section to the $\b{g}$-vector fan of any finite type cluster algebra with respect to any seed (acyclic or not).
 Cluster algebras were introduced by S.~Fomin and A.~Zelevinsky~\cite{FominZelevinsky-ClusterAlgebrasI} with motivation coming from total positivity and canonical bases.
@@
 Here, we extend the construction of~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} to any finite type (simply-laced or not) cluster algebra with respect to any seed (acyclic or not) by providing a direct proof that the type cone of the cluster fan of any finite type cluster algebra is simplicial.
+
+%%%
 
@@
 
-\[
+\centerline{$
 \begin{array}{r|c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;}c@{\;}c@{\;}c@{}c@{}c@{}cc}
@@
 \end{array}
-\]
+$}
 
@@
 
-\begin{figure}
+\begin{figure}[h]
 	\capstart
@@
 \label{def:meshMutation}
-%Consider a seed~$\seed = (\B, \cluster)$ and a cluster variable~$x \in \cluster$.
 The mutation of a seed~$\seed = (\B, \cluster)$ in the direction of a cluster variable~$x \in \cluster$ is a \defn{mesh mutation} that \defn{starts} (resp.~\defn{ends}) at~$x$ if the entries~$b_{xy}$ for~$y \in \cluster$ are all non-negative (resp.~all non-positive).
@@
 The following will be shown in \cref{sec:clusterCategories}.
-\vincent{Link to \cref{sec:clusterCategories}.}
+\vincent{Precise link to \cref{sec:clusterCategories}.}
 
@@
 
+%%%
+
 \subsubsection{Non-kissing complex and non-kissing fan of a gentle quiver}
@@
 The \defn{blossoming quiver}~$\quiver\blossom$ of a gentle quiver is the gentle quiver obtained by completing all vertices of~$\quiver$ with additional incoming or outgoing \defn{blossoms} such that all vertices of~$\quiver$ become $4$-valent.
-%
-%A gentle bound quiver~$\quiver$ is \defn{complete} if any vertex~$a \in Q_0$ is incident to either one ($a$ is a leaf) or four arrows ($a$ is an internal vertex).
-%The \defn{pruned subquiver} of a quiver~$\quiver$ is the locally gentle quiver obtained by deleting all leaves of~$\quiver$ (degree one vertices) and their incident arrows.
-%The \defn{blossoming quiver} of a locally gentle bound quiver~$\quiver$ is the complete locally gentle bound quiver~$\quiver\blossom$ whose pruned subquiver is~$\quiver$.
-%The vertices of~$Q\blossom_0 \ssm Q_0$ are called \defn{blossom vertices}, and the arrows in~$Q\blossom_1 \ssm Q_1$ are called \defn{blossom arrows}.
-%
 We now always assume that~$\quiver$ is a gentle quiver with blossoming quiver~$\quiver\blossom$.
@@
 	\end{enumerate}
-%We say that~$\sigma$ is \defn{straight} if~$\varepsilon_1 = \dots = \varepsilon_\ell$.
 The integer~$\ell$ is called the \defn{length} of the string~$\rho$.
-%We let~$s(\rho) \eqdef s(\alpha_1^{\varepsilon_1})$ and~$t(\rho) \eqdef t(\alpha_\ell^{\varepsilon_\ell})$ denote the source and target of~$\rho$.
 For each vertex~$a \in Q_0$, there is also a \defn{string of length zero}, denoted by~$\varepsilon_a$, that starts and ends at~$a$.
@@
 
+\begin{figure}[t]
+	\capstart
+	\centerline{\includegraphics[width=\textwidth]{exmNonkissing}}
+	\caption{A blossoming quiver (left), three pairwise kissing walks (middle), and a non-kissing facet (right). Illustration from~\cite{PaluPilaudPlamondon-nonkissing}.}
+	\label{fig:exmNonkissing}
+\end{figure}
+
 \para{Non-kissing complex}
@@
 The quiver~$\quiver$ is called \defn{$\tau$-tilting finite} or \defn{non-kissing finite} when this complex is finite (in other words, $\quiver$ has finitely may non-kissing walks).
+
+\para{Two families of examples: grid and dissection quivers}
+%
+The initial motivation for non-kissing complexes came from two families of examples:
+\begin{enumerate}[(1)]
+\item \textbf{Grid quivers}: Consider the infinite grid quiver~$\quiver_{Z^2}$, whose vertices are all integer points of~$\Z^2$, whose arrows connect between~$(i,j) \longrightarrow (i,j+1)$ and~$(i,j) \longrightarrow (i+1,j)$ for any~$(i,j) \in \Z^2$, and whose relations forbid~$(i-1,j) \longrightarrow (i,j) \longrightarrow (i,j+1)$ and~$(i,j-1) \longrightarrow (i,j) \longrightarrow (i+1,j)$ for any~$(i,j) \in \Z^2$.
+A \defn{gentle grid quiver} is any subquiver~$\quiver_A$ of~$\quiver_{Z^2}$ induced by a finite subset~$A \subset \Z^2$ of the integer grid.
+The non-kissing complex of gentle grid quivers were introduced in~\cite{McConville} with motivation coming from~\cite{PetersenPylyavskyySpeyer} and~\cite{SantosStumpWelker}.
+
+\smallskip
+\item \textbf{Dissection quivers}: Consider a dissection~$D$ of a convex polygon~$P$ (that is a crossing-free set of diagonals of~$P$) and its \defn{gentle dissection quiver}~$\quiver_D$, whose vertices are the internal diagonals of~$D$, whose arrows connect pairs of consecutive internal diagonals along the boundary of a face of~$D$, and whose relations correspond to triples of consecutive internal diagonals along the boundary of a face of~$D$.
+The non-kissing complex of~$\quiver_D$ then corresponds to non-crossing sets of accordions of~$D$, where an accordion is a segment connecting the middles of two boundary edges of~$P$ and crossing a connected set of diagonals of~$D$.
+This accordion complex was studied in~\cite{GarverMcConville} and~\cite{MannevillePilaud-accordion} with motivation coming from~\cite{Baryshnikov}, and~\cite{Chapoton-quadrangulations}.
+\end{enumerate}
+
+\begin{figure}[ht]
+	\capstart
+	\centerline{\includegraphics[scale=.8]{dissectionQuiver} \quad \includegraphics[scale=.35]{gridQuiver} \quad \includegraphics[scale=1.2]{bijectionAssociahedronDissection} \quad \includegraphics[scale=1.2]{bijectionAssociahedronGrid}}
+	\caption{}
+	\label{fig:dissectionGridQuivers}
+\end{figure}
+
+These two families of non-kissing complexes are well-behaved as they avoid all pathologies of \cref{rem:exchangeablePairsNKC}.
+However, they still provide good examples of non-kissing complexes.
+In particular, both families contain the classical associahedron.
+Namely, the gentle associahedron~$\Asso[\quiver]$ is the classical associahedron of~\cite{ShniderSternberg, Loday} presented in \cref{thm:associahedronLoday} when~${\quiver = \quiver_A}$ for the path~${A = \set{(0,j)}{j \in [n]}}$ or equivalently~$\quiver = \quiver_D$ for the fan triangulation~$D$ (where all internal diagonals incident to the same point).
+More generally, $\Asso[\quiver]$ is an associahedron of~\cite{HohlwegLange} when~$\quiver = \quiver_A$ for a ribbon~$A$ or equivalently~$\quiver = \quiver_D$ for a triangulation~$D$.
+See \cref{fig:dissectionGridQuivers}\,(right).
+
+Note that, it was shown in~\cite{PaluPilaudPlamondon-surfaces} that the accordion complexes can be extended to dissections of arbitrary orientable surfaces with marked points and then provide a geometric model for all non-kissing complexes of gentle quivers.
 
@@
 
-\para{Two families of examples: grid and dissection quivers}
-%
-We conclude this recollections on non-kissing complexes by two families of examples:
-\begin{enumerate}[(1)]
-\item \textbf{Grid quivers}: Consider the infinite grid quiver~$\quiver_{Z^2}$, whose vertices are all integer points of~$\Z^2$, whose arrows connect between~$(i,j) \longrightarrow (i,j+1)$ and~$(i,j) \longrightarrow (i+1,j)$ for any~$(i,j) \in \Z^2$, and whose relations forbid~$(i-1,j) \longrightarrow (i,j) \longrightarrow (i,j+1)$ and~$(i,j-1) \longrightarrow (i,j) \longrightarrow (i+1,j)$ for any~$(i,j) \in \Z^2$.
-A \defn{gentle grid quiver} is any subquiver~$\quiver_A$ of~$\quiver_{Z^2}$ induced by a finite subset~$A \subset \Z^2$ of the integer grid.
-The non-kissing complex of gentle grid quivers were introduced in~\cite{McConville} with motivation coming from~\cite{PetersenPylyavskyySpeyer} and~\cite{SantosStumpWelker}.
-
-\smallskip
-\item \textbf{Dissection quivers}: Consider a dissection~$D$ of a convex polygon~$P$ (that is a crossing-free set of diagonals of~$P$) and its \defn{gentle dissection quiver}~$\quiver_D$, whose vertices are the internal diagonals of~$D$, whose arrows connect pairs of consecutive internal diagonals along the boundary of a face of~$D$, and whose relations correspond to triples of consecutive internal diagonals along the boundary of a face of~$D$.
-The non-kissing complex of~$\quiver_D$ then corresponds to non-crossing sets of accordions of~$D$, where an accordion is a segment connecting the middles of two boundary edges of~$P$ and crossing a connected set of diagonals of~$D$.
-This accordion complex was studied in~\cite{GarverMcConville} and~\cite{MannevillePilaud-accordion} with motivation coming from~\cite{Baryshnikov}, and~\cite{Chapoton-quadrangulations}.
-\end{enumerate}
-
-\begin{figure}[ht]
-	\capstart
-	\centerline{\includegraphics[scale=.8]{dissectionQuiver} \quad \includegraphics[scale=.35]{gridQuiver} \quad \includegraphics[scale=1.2]{bijectionAssociahedronDissection} \quad \includegraphics[scale=1.2]{bijectionAssociahedronGrid}}
-	\caption{}
-	\label{fig:dissectionGridQuivers}
-\end{figure}
-
-These two families of non-kissing complexes are well-behaved as they avoid all pathologies of \cref{rem:exchangeablePairsNKC}.
-However, they still provide good examples of non-kissing complexes.
-In particular, both families contain the classical associahedron.
-Namely, the gentle associahedron~$\Asso[\quiver]$ is the classical associahedron of~\cite{ShniderSternberg, Loday} presented in \cref{thm:associahedronLoday} when~${\quiver = \quiver_A}$ for the path~${A = \set{(0,j)}{j \in [n]}}$ or equivalently~$\quiver = \quiver_D$ for the fan triangulation~$D$ (where all internal diagonals incident to the same point).
-More generally, $\Asso[\quiver]$ is an associahedron of~\cite{HohlwegLange} when~$\quiver = \quiver_A$ for a ribbon~$A$ or equivalently~$\quiver = \quiver_D$ for a triangulation~$D$.
-
-Note that, it was shown in~\cite{PaluPilaudPlamondon-surfaces} that the accordion complexes can be extended to dissections of arbitrary orientable surfaces with marked points and then provide a geometric model for all non-kissing complexes of gentle quivers.
+%%%
 
@@
 
+%%%
+
 \subsubsection{Simplicial type cones for self-kissing-free and $2$-cycle-free quivers}
@@
 
+%%%
+
 \subsubsection{Nested complex and nested fan of a graph}
@@
 \end{proof}
+
+%%%
 
@@
 \label{prop:extremalExchangeablePairsA}
-%The extremal exchangeable pairs for the nested fan of the path are precisely the pairs of intervals~$\{[i,j], [i+1,j+1]\}$ for~$1 \le i \le j \le n-1$.
 Two intervals~$[i,j]$ and~$[i',j']$ of~$[n+1]$ form an extremal exchangeable pair for the nested fan of the path if and only if~$i = i'+1$ and~$j = j'+1$, or the opposite.
@@
 \cref{prop:extremalExchangeablePairsA} extends as follows.
-% We denote by~$X \symdif Y$ the symmetric difference of two sets~$X$ and~$Y$.
 
@@
 \label{prop:extremalExchangeablePairsGA}
-%A pair~$\{\tube, \tube'\}$ of exchangeable tubes of~$\graphG$ is extremal if and only if~$|\tube \symdif \tube'| = 2$.
 Two tubes~$\tube$ and~$\tube'$ of~$\graphG$ form an extremal exchangeable pair for the nested fan of~$\graphG$ if and only if~${\tube \ssm \{v\} = \tube' \ssm \{v'\}}$ for some neighbor~$v$ of~$\tube'$ and some neighbor~$v'$ of~$\tube$.
@@
 
-%\begin{corollary}
-%Consider a graph~$\graphG$ on~$\ground$ with tubes~$\tubes$ and a height vector~$\b{h} \in \R^{\tubes}$ such that~$\b{h}_{\graphG} = 0$ and
-%\[
-%\b{h}_{\tube} + \b{h}_{\tube'} > \b{h}_{\tube \cup \tube'} + \sum_{\tube[s] \in \connectedComponents(\tube \cap \tube')} \b{h}_{\tube[s]}
-%\]
-%for any pair of tubes~$\{\tube, \tube'\}$ of~$\graphG$ with~$\tube \ssm \{v\} = \tube' \ssm \{v'\}$ where~$v$ is a neighbor of~$\tube'$ and~$v'$ is a neighbor of~$\tube$.
-%Then the nested fan~$\gvectorFan[\graphG]$ is the normal fan of the graph associahedron
-%\[
-%\set{\b{x} \in \R^\ground}{\dotprod{\gvector{\tube}}{\b{x}} \le \b{h}_{\tube} \text{ for any tube } \tube \in \tubes}.
-%\]
-%\end{corollary}
-
 \begin{corollary}
@@
 \begin{proposition}
-The number of extreme exchangeable pairs of the nested fan~$\gvectorFan[\graphG]$ is:
+The number of extremal exchangeable pairs of the nested fan~$\gvectorFan[\graphG]$ is:
 \begin{itemize}
@@
 \end{proof}
-
-%\begin{example}
-%The formula of \cref{coro:numberExtremalExchangeablePairsGA} can be made more explicit for specific families of graph associahedra:
-%\begin{itemize}
-%\item the permutahedron (complete graph associahedron) has~$2^{n-2}\binom{n}{2}$ extreme exchangeable pairs (choose the two vertices~$v,v'$, and complete them into a tube by selecting any subset of the~$n-2$ remaining vertices),
-%\item the associahedron (path associahedron) has~$\binom{n}{2}$ extreme exchangeable pairs (choose the two vertices~$v,v'$, and complete them into a tube by taking the path between them),
-%\item the cyclohedron (cycle associahedron) has~$3\binom{n}{2} - n$ extreme exchangeable pairs (choose the two vertices~$v,v'$, and complete them into a tube by taking either all the cycle, or one of the two paths between~$v$ and~$v'$; this gives three options in general, but only two when~$v,v'$ are neighbors),
-%\item the stellohedron (star associahedron) has $n-1+2^{n-3}\binom{n-1}{2}$ extreme exchangeable pairs (choose either~$v$ as the center of the star and~$v'$ as one of the $n-1$ leaves, or $v$~and~$v'$ as leaves of the star and complete them into a tube by taking the center and any subset of the $n-3$ remaining leaves).
-%\end{itemize}
-%\end{example}
 
@@
 
-%%%%%%%%%%%
+%%%
 
@@
 
-%%
+%%%
+
 \subsubsection{$2$-Calabi--Yau Frobenius exact categories}
@@
 
-%%
+%%%
+
 \subsubsection{$2$-term complexes of projective modules}
@@
 
-%%
+%%%
+
 \subsubsection{Objects presented by a subcategory}
@@
 
-%%
+%%%
 
@@
 
-%%
+%%%
+
 \subsubsection{A quotient of a Frobenius category}

### 2019-04-10 thirdPaper/draft/typeConeAssociahedra.tex
figure tubes

@@
 While they correspond to mesh mutations for cluster algebras and brick $2$-acyclic gentle algebras, they are not clear in general (see for instance \cref{fig:labelFacetDefiningInequalititiesNKC}\,(right)).
-It would be particularly interesting to fully understand these specific mutations for arbitrary ($\tau$-tilting finite) gentle algebras.
+It would be particularly interesting to fully understand these specific mutations for arbitrary (non-kissing finite) gentle algebras.
 
@@
 
-\vincent{Describe the rays of the type cone. They are the Minkowski basis. Newton polytopes of $F$-polynomials.}
+%\vincent{Describe the rays of the type cone. They are the Minkowski basis. Newton polytopes of $F$-polynomials.}
 
@@
 The \defn{blossoming quiver}~$\quiver\blossom$ of a gentle quiver is the gentle quiver obtained by completing all vertices of~$\quiver$ with additional incoming or outgoing \defn{blossoms} such that all vertices of~$\quiver$ become $4$-valent.
+For instance, \cref{fig:exmNonkissing},(left) shows a blossoming quiver: the vertices of~$\quiver$ appear in black, while the blossom vertices of~$\quiver\blossom$ appear in white.
 We now always assume that~$\quiver$ is a gentle quiver with blossoming quiver~$\quiver\blossom$.
@@
 Note that we authorize the situation where the common finite substring is reduced to a vertex~$a$, that~$\omega$ can kiss~$\omega'$ several times, that~$\omega$ and~$\omega'$ can mutually kiss, and that~$\omega$ can kiss itself.
+For example, \cref{fig:exmNonkissing}\,(middle) shows three walks that are pairwise kissing, and the orange walk is self-kissing (at its self-intersection).
 We say that a walk is \defn{proper} if it is not straight nor self-kissing.
@@
 %\end{figure}
-%
+
 The (reduced) \defn{non-kissing complex} of~$\quiver$ is the simplicial complex~$\NKC$ whose faces are the collections of pairwise non-kissing proper walks of~$\quiver$.
-As shown in~\cite[Thm.~2.46]{PaluPilaudPlamondon-nonkissing}, this simplicial complex is a combinatorial model for the support $\tau$-tilting complex on $\tau$-rigid modules over~$kQ/I$.
+For example, \cref{fig:exmNonkissing}\,(right) represents a non-kissing facet.
+As shown in~\cite[Thm.~2.46]{PaluPilaudPlamondon-nonkissing}, the non-kissing complex is a combinatorial model for the support $\tau$-tilting complex on $\tau$-rigid modules over~$kQ/I$.
 The quiver~$\quiver$ is called \defn{$\tau$-tilting finite} or \defn{non-kissing finite} when this complex is finite (in other words, $\quiver$ has finitely may non-kissing walks).
 
-\para{Two families of examples: grid and dissection quivers}
-%
-The initial motivation for non-kissing complexes came from two families of examples:
+\para{Two families of examples: gentle grid and dissection quivers}
+%
+The initial motivation for non-kissing complexes came from two families of examples, illustrated in \cref{fig:dissectionGridQuivers}:
 \begin{enumerate}[(1)]
@@
 A \defn{gentle grid quiver} is any subquiver~$\quiver_A$ of~$\quiver_{Z^2}$ induced by a finite subset~$A \subset \Z^2$ of the integer grid.
+See \cref{fig:dissectionGridQuivers}.
 The non-kissing complex of gentle grid quivers were introduced in~\cite{McConville} with motivation coming from~\cite{PetersenPylyavskyySpeyer} and~\cite{SantosStumpWelker}.
@@
 \item \textbf{Dissection quivers}: Consider a dissection~$D$ of a convex polygon~$P$ (that is a crossing-free set of diagonals of~$P$) and its \defn{gentle dissection quiver}~$\quiver_D$, whose vertices are the internal diagonals of~$D$, whose arrows connect pairs of consecutive internal diagonals along the boundary of a face of~$D$, and whose relations correspond to triples of consecutive internal diagonals along the boundary of a face of~$D$.
+See \cref{fig:dissectionGridQuivers}.
 The non-kissing complex of~$\quiver_D$ then corresponds to non-crossing sets of accordions of~$D$, where an accordion is a segment connecting the middles of two boundary edges of~$P$ and crossing a connected set of diagonals of~$D$.
@@
 
-\begin{figure}[ht]
+\begin{figure}[t]
 	\capstart
-	\centerline{\includegraphics[scale=.8]{dissectionQuiver} \quad \includegraphics[scale=.35]{gridQuiver} \quad \includegraphics[scale=1.2]{bijectionAssociahedronDissection} \quad \includegraphics[scale=1.2]{bijectionAssociahedronGrid}}
-	\caption{}
+	\centerline{\includegraphics[scale=.35]{gridQuiver} \quad \includegraphics[scale=.8]{dissectionQuiver} \quad \includegraphics[scale=1.2]{bijectionAssociahedronGrid} \quad \includegraphics[scale=1.2]{bijectionAssociahedronDissection}}
+	\caption{A gentle grid quiver (left), a gentle dissection quiver (middle left), and a path quiver which is both the gentle grid quiver of a ribbon (middle right) and the dissection quiver of a triangulation (right).
+Illustration from~\cite{PaluPilaudPlamondon-nonkissing}.}
 	\label{fig:dissectionGridQuivers}
@@
 More generally, $\Asso[\quiver]$ is an associahedron of~\cite{HohlwegLange} when~$\quiver = \quiver_A$ for a ribbon~$A$ or equivalently~$\quiver = \quiver_D$ for a triangulation~$D$.
-See \cref{fig:dissectionGridQuivers}\,(right).
+See \cref{fig:dissectionGridQuivers}.
 
@@
 
+For example, the $\b{g}$-vectors of the blue, green, and yellow walks of \cref{fig:exmNonkissing}\,(right) are respectively~$(0, -1, 0, 0, 1, 0)$, $(0, 0, 1, -1, 1, 0)$ and $(0, 0, 0, 0, 1, 0)$.
 Note that by definition, the $\gvector{\omega} = 0$ for a straight walk~$\omega$.
@@
 It is shown in~\cite[Prop.~2.28]{PaluPilaudPlamondon-nonkissing} that each bending walk in a non-kissing facet has precisely two distinguished arrows, pointing in opposite directions.
+For example, we have marked in \cref{fig:exmNonkissing}\,(right) the two distinguished arrows on each walk by triple arrows.
 The \defn{distinguished substring}~$\distinguishedString{\omega}{F}$ of the walk~$\omega$ in the non-kissing facet~$F \in \NKC$ is the substring located between its two distinguished arrows.
@@
 
-The $\b{g}$- and $\b{c}$-vectors also form dual bases.
+For example, the $\b{g}$-vectors of the blue, green, and yellow walks in the non-kissing facet of \cref{fig:exmNonkissing}\,(right) are respectively~$(0, -1, 0, 0, 0, 0)$, $(0, 0, 0, -1, 0, 0)$ and $(0, 1, 0, 1, 1, 0)$.
+As the reader can observe on the example of \cref{fig:exmNonkissing}\,(right), the $\b{g}$- and $\b{c}$-vectors also form dual bases.
 
@@
 
+\begin{theorem}[{\cite[Thm.~4.17]{PaluPilaudPlamondon-nonkissing}}]
+\label{thm:nonkissingFan}
+For any non-kissing finite gentle quiver~$\quiver$, the set of cones
+\[
+\gvectorFan[\quiver] \eqdef \set{\R_{\ge 0} \, \gvectors{F}}{F \text{ non-kissing face of } \NKC}
+\]
+is a complete simplicial fan of~$\R^{Q_0}$, called \defn{non-kissing fan} of~$\quiver$, which realizes the non-kissing complex~$\NKC$.
+\end{theorem}
+
 \begin{figure}[h]
@@
 \end{figure}
-
-\begin{theorem}[{\cite[Thm.~4.17]{PaluPilaudPlamondon-nonkissing}}]
-\label{thm:nonkissingFan}
-For any non-kissing finite gentle quiver~$\quiver$, the set of cones
-\[
-\gvectorFan[\quiver] \eqdef \set{\R_{\ge 0} \, \gvectors{F}}{F \text{ non-kissing face of } \NKC}
-\]
-is a complete simplicial fan of~$\R^{Q_0}$, called \defn{non-kissing fan} of~$\quiver$, which realizes the non-kissing complex~$\NKC$.
-\end{theorem}
 
@@
 In \cref{subsubsec:simplicialTypeConeNKC}, we will restrict to a situation that avoids all these patologies.
-\vincent{Do we still have these problems when the gentle algebra is brick and/or without oriented $2$-cycle?}
+%\vincent{Do we still have these problems when the gentle algebra is brick and/or without oriented $2$-cycle?}
 \end{remark}
@@
 
-Note that this family already contains a lot of relevant examples, including the grid and dissection quivers discussed in \cref{subsubsec:nonkissingComplex}.
+Note that this family already contains a lot of relevant examples, including the gentle grid and dissection quivers discussed in \cref{subsubsec:nonkissingComplex}.
 In particular, the classical associahedron is the gentle associahedron of a brick $2$-acyclic gentle quiver.
@@
 A \defn{tubing} on~$\graphG$ is a set~$\tubing$ of pairwise compatible proper tubes of~$\graphG$.
-The \defn{nested complex} of~$\graphG$ is the simplicial complex~$\nestedComplex(\graphG)$ of all tubings on~$\graphG$.
+See \cref{fig:exmNested}.
+The \defn{nested complex} of~$\graphG$ is the simplicial complex~$\nestedComplex(\graphG)$ of all tubings~on~$\graphG$.
+
+\begin{figure}[h]
+	\capstart
+	\centerline{\includegraphics[width=\textwidth]{exmNested}}
+	\caption{Some incompatible tubes (left and middle), and a maximal tubing (right).}
+	\label{fig:exmNested}
+\end{figure}
 

### 2019-04-10 thirdPaper/draft/typeConeAssociahedra.tex
proof of Prop 2.41

@@
 
+\enlargethispage{.1cm}
 We now focus on the normal fan~$\gvectorFan[n]$ of~$\Asso[n]$.
@@
 
+\enlargethispage{-.4cm}
 Gentle associahedra were constructed by Y.~Palu, V.~Pilaud and P.-G.~Plamondon~\cite{PaluPilaudPlamondon-nonkissing} in the context of support $\tau$-tilting for gentle algebras.
@@
 We present the definitions and properties of the non-kissing complex of a gentle quiver, following the presentation of~\cite{PaluPilaudPlamondon-nonkissing}.
+See also~\cite{BrustleDouvilleMousavandThomasYildirim} for an alternative presentation.
 
@@
 In other words, $\omega$ and~$\omega'$ share a common substring~$\sigma$, and both arrows of~$\omega$ (resp.~of~$\omega'$) not in~$\sigma$ are outgoing (resp.~incoming) at the endpoints of~$\sigma$.
-%See \fref{fig:kissing}.
+See \cref{fig:kissingCrossing} for a schematic representation and \cref{fig:exmNonkissing}\,(middle) where the three walks are pairwise kissing.
 We say that~$\omega$ and~$\omega'$ are \defn{kissing} if~$\omega$ kisses~$\omega'$ or~$\omega'$ kisses~$\omega$ (or both).
 Note that we authorize the situation where the common finite substring is reduced to a vertex~$a$, that~$\omega$ can kiss~$\omega'$ several times, that~$\omega$ and~$\omega'$ can mutually kiss, and that~$\omega$ can kiss itself.
-For example, \cref{fig:exmNonkissing}\,(middle) shows three walks that are pairwise kissing, and the orange walk is self-kissing (at its self-intersection).
+For example, the orange walk in \cref{fig:exmNonkissing}\,(middle) is self-kissing (at its self-intersection).
 We say that a walk is \defn{proper} if it is not straight nor self-kissing.
@@
 
-%\begin{figure}[h]
-%	\capstart
-%	\centerline{\includegraphics[scale=1]{kissing}}
-%	\caption{A schematic representation of two kissing walks: $\omega$~kisses~$\omega'$.}
-%	\label{fig:kissing}
-%\end{figure}
+\begin{figure}[h]
+	\capstart
+	\centerline{\includegraphics[scale=1]{kissingCrossing}}
+	\caption{A schematic representation of kissing and non-kissing walks.
+The walks $\omega$ and~$\omega'$ kiss (left) while the walks~$\mu$ and~$\nu$ share a common substring but do not kiss (right).
+Illustration from~\cite{PaluPilaudPlamondon-nonkissing}.}
+	\label{fig:kissingCrossing}
+\end{figure}
 
@@
 We write~$\omega \prec_\alpha \omega'$ if $\omega$ enters and/or exits~$\sigma$ with arrows in the direction pointed by~$\alpha$, while $\omega'$ enters and/or exits~$\sigma$ with arrows in the direction opposite to~$\alpha$.
+For example, in \cref{fig:kissingCrossing}, we have~$\mu \prec_\gamma \nu$ but~$\nu \prec_\delta \mu$.
 The \defn{distinguished walk} of the non-kissing facet~$F \in \NKC$ at the arrow~$\alpha$ is the maximum walk of~$F$ for~$\prec_\alpha$.
@@
 %
+\enlargethispage{.2cm}
 The $\b{g}$-vectors support a complete simplicial fan realization of the non-kissing complex complex.
@@
 %
+\enlargethispage{-.4cm}
 Although we lack a characterization of the exchangeable pairs of the non-kissing complex (see \cref{rem:exchangeablePairsNKC}), we can still describe the linear dependence among the $\b{g}$-vectors involved in a flip.
 The following statement is partially proved in~\cite[Thm.~4.17]{PaluPilaudPlamondon-nonkissing}.
+The notations are illustrated in \cref{fig:flip}.
 
@@
 \begin{enumerate}[(i)]
-\item For any non-kissing facet~$F, F'$ of~$\NKC$ with~$F \ssm \{\omega\} = f' \ssm \{\omega'\}$, there exists a unique maximal common substring~$\sigma$ of~$\omega$ and~$\omega'$ that decomposes~$\omega = \rho \sigma \tau$ and~$\omega' = \rho' \sigma \tau'$ such that the facets~$F$ and~$F'$ both contain the walks~$\mu \eqdef \rho' \sigma \tau$ and~$\nu \eqdef \rho \sigma \tau'$.
+\item For any non-kissing facets~$F, F'$ of~$\NKC$ with~$F \ssm \{\omega\} = f' \ssm \{\omega'\}$, the distinguished substrings of~$\omega$ in~$F$ and of~$\omega'$ in~$F'$ coincide to a string~$\sigma$.
+Moreover, if we decompose~$\omega = \rho \sigma \tau$ and~$\omega' = \rho' \sigma \tau'$, then the facets~$F$ and~$F'$ both contain the walks~$\mu \eqdef \rho' \sigma \tau$ and~$\nu \eqdef \rho \sigma \tau'$.
 \item The substring~$\sigma$ and thus the walks~$\mu$ and~$\nu$ actually depend on the exchangeable walks~$\omega$ and~$\omega'$, not on the adjacent non-kissing facet~$F $ and~$F'$.
@@
 \end{enumerate}
+%
+\begin{figure}[t]
+	\capstart
+	\centerline{\includegraphics[scale=1]{flip}}
+	\caption{A schematic representation of a flip. Illustration from~\cite{PaluPilaudPlamondon-nonkissing}.}
+	\label{fig:flip}
+\end{figure}
 \end{proposition}
@@
 \label{exm:typeConeNKC}
+\enlargethispage{.4cm}
 Consider the non-kissing fans illustrated in \cref{fig:nonkissingFans}.
@@
 \begin{proof}
-We just need to prove that there exists a ridge~$R$ of~$\NKC$ containing both~$\hc{\sigma}$ and~$\ch{\sigma}$ and such that~$R \cup \{\cc{\sigma}\}$ and~$R \cup \{\hh{\sigma}\}$ are adjacent facets of~$\NKC$.
-
-\vincent{TODO}
+We fix some notations similar to that of \cref{fig:flip}.
+Let~$\omega \eqdef \cc{\sigma}$, $\omega' \eqdef \hh{\sigma}$, $\mu \eqdef \hc{\sigma}$ and~$\nu \eqdef \ch{\sigma}$.
+%Let~$v,y$ be the two endpoints of~$\sigma$, and let~$u$ (resp.~$w$, resp.~$x$, resp.~$z$) be the only peak of~$\mu$ (resp.~deep of~$\mu$, resp.~peak of~$\nu$, resp.~deep of~$\nu$) that is not a substring of~$\sigma$.
+%Finally, let~$\alpha = v \to w$, $\alpha' = u \to v$, $\beta = y \to z$ and $\beta' = x \to y$.
+See \cref{fig:flip}.
+
+Since~$\quiver$ is brick, these walks are not self-kissing by \cref{prop:noSelfKissing} and since they are bending, they are proper walks.
+We want to show that there are non-kissing facets~$F, F'$ of the non-kissing complex~$\NKC$ containing both~$\mu$ and~$\nu$ and such that~$F \ssm \{\omega\} = F' \ssm \{\omega'\}$.
+
+We first show that~$\mu$ and~$\nu$ are compatible.
+Let~$\tau$ be a maximal common substring of~$\mu$ and~$\nu$.
+If~$\sigma$ and~$\tau$ are not disjoint, then~$\sigma = \tau$ and $\mu$ and~$\nu$ are not kissing at~$\tau$.
+We can therefore assume that $\tau$ appears completely before or completely after~$\sigma$ in both~$\mu$ and~$\nu$.
+We distinguish the different cases:
+\begin{itemize}
+\item If~$\tau$ appears before~$\sigma$ in both~$\mu$ and~$\nu$, then~$\alpha \tau \alpha'$ form a cycle in~$\quiver$.
+If~$\tau$ is reduced to a vertex, then we have a $2$-cycle.
+Otherwise, since~$\alpha\tau$ is a substring of~$\nu$ and~$\alpha'\tau$ is a substring of~$\nu$, the cycle~$\alpha \tau \alpha'$ contains a unique relation~$\alpha'\alpha$.
+This rules out this case under the assumption that~$\quiver$ is brick $2$-acyclic.
+The case when~$\tau$ appears after~$\sigma$ in both~$\mu$ and~$\nu$ is symmetric.
+\item If~$\tau$ appears before~$\sigma$ in~$\mu$ and after~$\sigma$ in~$\nu$, then~$\omega$, $\mu$ and~$\nu$ finish at the same blossom so that~$\mu$ and~$\nu$ are not kissing at~$\tau$.
+The case when~$\tau$ appears after~$\sigma$ in~$\mu$ and before~$\sigma$ in~$\nu$ is identical.
+\end{itemize}
+We conclude that~$\mu$ and~$\nu$ are non-kissing, which also implies that~$\{\mu, \nu, \omega\}$ and~$\{\mu, \nu, \omega'\}$ are non-kissing faces of~$\NKC$.
+We can therefore consider a non-kissing facet~$F$ containing~$\{\mu, \nu, \omega\}$.
+
+We claim that~$\omega$ is distinguished at~$\alpha$ and~$\beta$ in the facet~$F$, that~$\mu$ is distinguished at~$\alpha'$ and that~$\nu$ is distinguished at~$\beta'$.
+Let us just prove that~$\mu$ is distinguished at~$\alpha'$, the other statements being similar.
+Consider any walk~$\lambda$ of~$F$ containing~$\alpha'$, and let~$\tau$ be the maximal common substring of~$\omega$ and~$\lambda$.
+Note that~$\omega$ has the outgoing arrow~$\alpha$ while~$\lambda$ has the incoming arrow~$\alpha'$ at one end of~$\tau$.
+Since~$\omega$ and~$\lambda$ are compatible, it ensures that either~$\tau$ ends at a blossom, or $\lambda$ has an outgoing arrow at the other end of~$\tau$.
+This shows that~$\lambda \prec_{\alpha'} \mu$ since $\lambda$ separates from~$\mu$ with an arrow in the same direction as~$\alpha'$.
+
+Since this precisely coincides with the description of the flip in the non-kissing complex (see \cref{prop:exchangeablePairsNKC}\,(i) or \cite[Prop.~2.31]{PaluPilaudPlamondon-nonkissing} for an alternative presentation), we conclude that the flip of~$\omega$ in~$F$ creates a facet~$F'$ containing~$\omega'$.
+Therefore, $\omega$ and~$\omega'$ are exchangeable with distinguished substring~$\sigma$.
 \end{proof}
@@
 
+\newpage
 \subsection{Graphical nested complexes and graph associahedra}

### 2019-04-10 thirdPaper/draft/typeConeAssociahedra.tex
counter-example if not brick or not 2-cyclic

@@
 %sage: CA = ClusterAlgebra(B)
-%
+
 %sage: CA.explore_to_depth(infinity)
@@
 %N(0, 1, 0) x1
-%
+
 %sage: TCCA = type_cone_CA(CA)
@@
 %N(0, 1, -1) (x0 + x1)/x2
-%
+
 %sage: TCCA = type_cone_CA(CA)
@@
 %N(0, 1, -1) (x0^2 + x1^2 + x0*x2)/(x1*x2)
-%
+
 %sage: TCCA = type_cone_CA(CA)
@@
 %sage: Q = GentleQuiver({'e1':{'e2':['a']}, 'e2':{'e3':['b']}}, [('a','b')])
-%
+
 %sage: Q.non_kissing_fan().rays()
@@
 %in 3-d lattice N
-%
+
 %sage: TCNKC = type_cone_NKC(Q)
@@
 % An inequality (0, 0, 0, 1, 0, 0, 1, -1) x + 0 >= 0)
-%sage: TCNKC.lines()
-%(A line in the direction (0, 0, 1, 0, 1, 0, -1, -1),
-% A line in the direction (1, 0, 0, 0, -1, -1, 1, 1),
-% A line in the direction (0, 1, 0, -1, 0, 0, 0, -1))
 
@@
 %sage: Q = GentleQuiver({'e1':{'e2':['a']}, 'e2':{'e3':['b']}, 'e3':{'e1':['c']}}, [('b','c')])
-%
+
 %sage: Q.non_kissing_fan().rays()
@@
 % An inequality (0, 0, 0, 0, 0, 1, 0, 0, -1, -1, 1) x + 0 >= 0)
-%sage: TCNKC.lines()
-%(A line in the direction (0, 0, 0, 1, 0, 0, 1, 1, 0, -1, -1),
-% A line in the direction (1, 0, 1, 1, 0, -1, 0, 0, -1, 0, 0),
-% A line in the direction (1, 1, 0, 1, -1, 0, 0, 1, -1, 0, -1))
 
@@
 
-\begin{example}
+\begin{remark}
 \label{exm:nonSimplicialTypeConeNKC}
-\vincent{All this section is wrong when the quiver is not brick or has a cycle of length~$2$.}
-\end{example}
+Note that \cref{prop:interestingExchangeablePairsNKC,prop:extremalExchangeablePairsNKC} and therefore~\cref{coro:simplicialTypeConeNKC,coro:allPolytopalRealizationsNKC} fail when the quiver is not brick or not $2$-acyclic.
+The smallest exemples are the $2$-cycles whose non-kissing fans are represented in \cref{fig:nonkissingFans2}.
+
+\begin{figure}[h]
+	\capstart
+	\centerline{\includegraphics[scale=.45]{nonkissingFans2}}
+	\caption{The non-kissing fans of two $2$-cyclic gentle quivers. Illustration from~\cite{PaluPilaudPlamondon-nonkissing}.}
+	\label{fig:nonkissingFans2}
+\end{figure}
+
+The left one is not brick: it has a non-distinguishable string and a self-kissing walk.
+The right one is brick but is not $2$-acyclic.
+
+In both cases, \cref{prop:interestingExchangeablePairsNKC} fails for the string~$\sigma$ of length~$0$ at vertex~$1$ (resp.~$2$) as the resulting walks~$\cc{\sigma}$ and~$\hh{\sigma}$ have $\b{g}$-vectors~$\gvector{\cc{\sigma}} = (1,-1)$ and~$\gvector{\hh{\sigma}} = (-1,1)$ (resp.~$\gvector{\cc{\sigma}} = (-1,1)$ and~$\gvector{\hh{\sigma}} = (1,-1)$), and are therefore not exchangeable.
+\cref{prop:extremalExchangeablePairsNKC} also fails as the type cone has dimension~$4$ and the following~$5$ inequalities:
+
+\[
+\begin{array}{r|cccccc}
+\text{walks} & \raisebox{-.25cm}{\includegraphics[scale=.5]{walkC1}} & \raisebox{-.25cm}{\includegraphics[scale=.5]{walkC2}} & \raisebox{-.25cm}{\includegraphics[scale=.5]{walkC3}} & \raisebox{-.25cm}{\includegraphics[scale=.5]{walkC4}} & \raisebox{-.25cm}{\includegraphics[scale=.5]{walkC5}} & \raisebox{-.25cm}{\includegraphics[scale=.5]{walkC6}} \\[.2cm]
+& \raisebox{-.25cm}{\includegraphics[scale=.5]{walkD1}} & \raisebox{-.25cm}{\includegraphics[scale=.5]{walkD2}} & \raisebox{-.25cm}{\includegraphics[scale=.5]{walkD3}} & \raisebox{-.25cm}{\includegraphics[scale=.5]{walkD4}} & \raisebox{-.25cm}{\includegraphics[scale=.5]{walkD5}} & \raisebox{-.25cm}{\includegraphics[scale=.5]{walkD6}} \\[.6cm]
+\text{$\b{g}$-vectors} & \compactVectorD{1}{0} & \compactVectorD{0}{1} & \compactVectorD{-1}{1} & \compactVectorD{-1}{0} & \compactVectorD{0}{-1} & \compactVectorD{1}{-1} \\[.6cm]
+\text{facet}		& 1 & -1 & 1 & 0 & 0 & 0 \\
+\text{defining}		& 0 & 1 & -1 & 1 & 0 & 0 \\
+\text{inequalities}	& 0 & 0 & 1 & -1 & 1 & 0 \\
+					& 0 & 0 & 0 & 1 & -1 & 1 \\
+					& 1 & 0 & 0 & 0 & 1 & -1 \\[.2cm]
+\end{array}
+\]
+
+\noindent
+(since the fans are the same, the type cones are the same and we therefore present them together)
+
+%sage: Q = GentleQuiver({'e1':{'e2':['a']}, 'e2':{'e1':['b']}}, [('b','a')])
+
+%sage: Q.non_kissing_fan().rays()
+%N( 0,  1),
+%N(-1,  1),
+%N(-1,  0),
+%N( 0, -1),
+%N( 1,  0),
+%N( 1, -1)
+%in 2-d lattice N
+
+%sage: TCNKC = type_cone_NKC(Q)
+%sage: TCNKC
+%A 6-dimensional polyhedron in QQ^6 defined as the convex hull of 1 vertex, 5 rays, 2 lines
+%sage: TCNKC.lines()
+%(A line in the direction (1, 0, -1, -1, 1, 0),
+% A line in the direction (1, 1, 0, -1, 0, -1))
+%sage: TCNKC.inequalities()
+%(An inequality (-1, 1, 0, 0, 1, 0) x + 0 >= 0,
+% An inequality (0, 0, 0, 1, 1, -1) x + 0 >= 0,
+% An inequality (0, 0, 1, -1, 0, 1) x + 0 >= 0,
+% An inequality (0, 1, -1, 1, 0, 0) x + 0 >= 0,
+% An inequality (1, -1, 1, 0, 0, 0) x + 0 >= 0,
+% An inequality (1, 0, 0, 0, -1, 1) x + 0 >= 0)
+
+%sage: Q = GentleQuiver({'e1':{'e2':['a']}, 'e2':{'e1':['b']}}, [('a','b'), ('b','a')])
+
+%sage: Q.non_kissing_fan().rays()
+%N( 0,  1),
+%N(-1,  1),
+%N(-1,  0),
+%N( 0, -1),
+%N( 1,  0),
+%N( 1, -1)
+%in 2-d lattice N
+
+%sage: TCNKC = type_cone_NKC(Q)
+%sage: TCNKC
+%A 6-dimensional polyhedron in QQ^6 defined as the convex hull of 1 vertex, 5 rays, 2 lines
+%sage: TCNKC.lines()
+%(A line in the direction (1, 0, -1, -1, 1, 0),
+% A line in the direction (1, 1, 0, -1, 0, -1))
+%sage: TCNKC.inequalities()
+%(An inequality (-1, 1, 0, 0, 1, 0) x + 0 >= 0,
+% An inequality (0, 0, 0, 1, 1, -1) x + 0 >= 0,
+% An inequality (0, 0, 1, -1, 0, 1) x + 0 >= 0,
+% An inequality (0, 1, -1, 1, 0, 0) x + 0 >= 0,
+% An inequality (1, -1, 1, 0, 0, 0) x + 0 >= 0,
+% An inequality (1, 0, 0, 0, -1, 1) x + 0 >= 0)
+\end{remark}
 
@@
 
-\begin{figure}[t]
+\begin{figure}[b]
 	\capstart

### 2019-04-10 thirdPaper/draft/typeConeAssociahedra.tex
submodular functions

@@
 \]
-We say that $h$ is \defn{$\Fan$-admissible} if $P_\b{h}$ is a polytopal realization of~$\Fan$.
+We say that $\b{h}$ is \defn{$\Fan$-admissible} if $P_\b{h}$ is a polytopal realization of~$\Fan$.
 The following classical statement characterizes the $\Fan$-admissible height vectors.
@@
 \label{prop:characterizationPolytopalFan}
-Let~$\Fan$ be an essential complete simplicial fan in~$\R^n$. Then the following are equivalent for any height vector~$h \in \R^N$:
+Let~$\Fan$ be an essential complete simplicial fan in~$\R^n$. Then the following are equivalent for any height vector~$\b{h} \in \R^N$:
 \begin{enumerate}
@@
 \begin{definition}
+\label{def:brick2acyclic}
 A gentle quiver~$\quiver$ is called:
@@
 The smallest exemples are the $2$-cycles whose non-kissing fans are represented in \cref{fig:nonkissingFans2}.
+The left one is not brick: it has a non-distinguishable string and a self-kissing walk.
+The right one is brick but is not $2$-acyclic.
 
@@
 \end{figure}
-
-The left one is not brick: it has a non-distinguishable string and a self-kissing walk.
-The right one is brick but is not $2$-acyclic.
 
@@
 
+\medskip
 \noindent
-(since the fans are the same, the type cones are the same and we therefore present them together)
+(since the fans are the same, the type cones are the same and we therefore present them together).
+
+Note that both assumptions of \cref{def:brick2acyclic} are needed for \cref{prop:interestingExchangeablePairsNKC,prop:extremalExchangeablePairsNKC}.
+Indeed, these statements fail for the quiver of \cref{fig:nonkissingFans}\,(left) which is $2$-acyclic but not brick and for the quiver of \cref{fig:nonkissingFans2} which is brick but $2$-cyclic.
 
@@
 
-\newpage
 \subsection{Graphical nested complexes and graph associahedra}
@@
 \begin{corollary}
+\label{coro:typeConeGA}
 For any graph~$\graphG$, the type cone of the nested fan~$\gvectorFan[\graphG]$ is given by
@@
 \end{corollary}
+
+\begin{example}
+For the complete graph~$\graphG[K]_n$, all the inequalities of \cref{coro:typeConeGA} actually define facets of~$\typeCone(\gvectorFan[\graphG[K]_n])$.
+The corresponding admissible height vectors are precisely the submodular functions, \ie the functions~$\b{h} : 2^{[n]} \to \R$ such that~$\b{h}_{\varnothing} = 0$ and~$\b{h}_{A} + \b{h}_{B} > \b{h}_{A \cap B} + \b{h}_{A \cup B}$ for any~$A, B \subseteq [n]$.
+This is precisely the description of the generalized permutahedra introduced by A.~Postnikov in~\cite{Postnikov} and E.-M.~Feichtner and B.~Sturmfels in~\cite{FeichtnerSturmfels}.
+\end{example}
 
@@
 
-\[
+\medskip
+\centerline{$
 \begin{array}{r|c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c}

### 2019-04-10 thirdPaper/draft/typeConeAssociahedra.tex
improve pictures

@@
 The first systematic polytopal realizations were constructed by M.~Haiman~\cite{Haiman} and C.~Lee~\cite{Lee}.
-Since then, the associahedron has been largely ``demystified'' with several polytopal constructions and generalizations (further references are discussed below).
+Since then, the associahedron has been largely ``demystified'' with several polytopal constructions and generalizations (some are discussed below).
 Its realizations can be classified into three species: the secondary polytopes~\cite{GelfandKapranovZelevinsky, BilleraFillimanSturmfels}, the $\b{g}$-vectors realizations~\cite{Loday, HohlwegLange, LangePilaud, HohlwegLangeThomas, HohlwegPilaudStella, Postnikov, PilaudSantos-brickPolytope, PilaudStump-brickPolytope} and the $\b{d}$-vector realizations~\cite{ChapotonFominZelevinsky, CeballosSantosZiegler}.

### 2019-04-10 thirdPaper/draft/typeConeAssociahedra.tex
minor modif

@@
 \begin{example}
-For the complete graph~$\graphG[K]_n$, all the inequalities of \cref{coro:typeConeGA} actually define facets of~$\typeCone(\gvectorFan[\graphG[K]_n])$.
-The corresponding admissible height vectors are precisely the submodular functions, \ie the functions~$\b{h} : 2^{[n]} \to \R$ such that~$\b{h}_{\varnothing} = 0$ and~$\b{h}_{A} + \b{h}_{B} > \b{h}_{A \cap B} + \b{h}_{A \cup B}$ for any~$A, B \subseteq [n]$.
+For the complete graph~$\graphG[K]_n$, the admissible height vectors are precisely the submodular functions, \ie the functions~$\b{h} : 2^{[n]} \to \R$ such that~$\b{h}_{\varnothing} = 0$ and~$\b{h}_{A} + \b{h}_{B} > \b{h}_{A \cap B} + \b{h}_{A \cup B}$ for any~$A, B \subseteq [n]$.
 This is precisely the description of the generalized permutahedra introduced by A.~Postnikov in~\cite{Postnikov} and E.-M.~Feichtner and B.~Sturmfels in~\cite{FeichtnerSturmfels}.
@@
 Therefore, $\tube \ssm \tube'$ and~$\tube' \ssm \tube$ are both connected.
-We can thus label the elements of~$\tube \cup \tube'$ by~$\{v_1, \dots, v_p\}$ such that~$\{v_i, \dots, v_j\}$ induces a tube~$\tube_{k,\ell}$ of~$\graphG$ for any~$1 \le k \le \ell \le p$. 
+We can thus label the elements of~$\tube \cup \tube'$ by~$\{v_1, \dots, v_p\}$ such that~$\{v_k, \dots, v_\ell\}$ induces a tube~$\tube_{k,\ell}$ of~$\graphG$ for any~$1 \le k \le \ell \le p$. 
 The map~$[k,\ell] \mapsto \tube_{k,\ell}$ is thus an injection from the tubes of the path~$\graphG[P]_p$ to that of~$\graphG$ that fulfills

### 2019-04-11 thirdPaper/draft/typeConeAssociahedra.tex
proofs of Lemmas 4.28 and 4.29

@@
  Let~$\Lambda$ be any Artin algebra.
-Let~$X\infl Y\defl Z$ be an almost-split conflation in~$K^{[-1,0]}(\proj \Lambda)$ such that~$Z$ is not in~$\add(\susp \Lambda)$.
+Let~$X\overset{a}{\infl} Y \overset{b}{\defl} Z$ be an almost-split conflation in~$K^{[-1,0]}(\proj \Lambda)$ such that~$Z$ is not in~$\add(\susp \Lambda)$.
 Denote by~$F$ the functor~$\Hom{K^b}(\Lambda, -):K^{[-1,0]}(\proj \Lambda) \to \MOD \Lambda$.
@@
 \end{lemma}
+
 \begin{proof}
-
+The almost-split conflation induces an exact sequence
+\[
+F\susp^{-1}Y\to F\susp^{-1}Z \to FX \to FY\to FZ\to F\susp X.
+\]
+Because~$X$ is concentrated in non-positive degrees,~$FX=0$.
+Let us verify that the map~$F\susp^{-1}Y\to F\susp^{-1}Z$ is surjective.
+Let~$\Lambda \xrightarrow{f} \susp^{-1} Z$ be a morphism in~$K^b(\proj \Lambda)$.
+Since~$Y\overset{b}{\to} Z$ is right almost-split, and~$Z$ is indecomposable not in~$\add(\susp\Lambda)$, the morphism~$\susp f$ factors through~$b$.
+This implies the required surjectivity, and we have a short exact sequence
+\[
+ 0 \to FX \xrightarrow{Fa} FY\xrightarrow{Fb} FZ\to 0.
+\]
+Because~$\MOD\Lambda$ and~$K^b(\proj \Lambda)$ are Krull--Schmidt, it is immediate to check that~$Fb$ (resp.~$Fa$) inherits from~$b$ (resp.~$a$) the property of being right (resp. left) almost-split.
+\end{proof}
+
+\begin{lemma}
+\label{lemm::then-AR-seq-are-mutation}
+Let~$\Lambda$ be an Artin algebra, let~$\tau X\infl E\defl X$ be an Auslander--Reiten conflation in~$K^{[-1,0]}(\proj\Lambda)$ and denote~$FX=M$.
+Assume that:\yann{There might be some redundancies in the assumptions}
+\begin{enumerate}
+ \item $X\notin\add(\susp\Lambda)$;
+ \item $M$ and~$\tau M$ are~$\tau$-rigid;
+ \item $\Hom{\Lambda}(M,\tau^2 M)=0$;
+ \item $\tau M$ is a brick.
+\end{enumerate}
+Then~$\tau X\infl E\defl X$ is a mutation conflation.
+\end{lemma}
+
+\begin{proof}
+First note that the results~\cite[Lemmas 3.4 and 3.5]{AdachiIyamaReiten}, even though stated for finite dimensional algebras, hold with the same proofs for any Artin algebra.
+For convenience of the reader, we recall those two results: Let~$Y, Z \in K^{[-1,0]}(\proj\Lambda)$ be indecomposable and not in~$\add(\susp\Lambda)$, and let~$P\in\proj\Lambda$.
+Then~$\Hom{K^b}(Y,\susp Z)=0$ if and only if~$\Hom{\Lambda}(FZ,\tau FY)=0$ and~$\Hom{K^b}(P,Y)=0$ if and only if~$\Hom{\Lambda}(P,FY)=0$.
+
+Note also that Lemma~\ref{lemm::AR-conflations-and-sequences} implies that~$F\tau X$ is isomorphic to $\tau M$.
+
+By assumption,~$X$ is not in~$\add(\susp\Lambda)$.
+The same is true of~$\tau X$ since objects in~$\add(\susp\Lambda)$ are injective in~$K^{[-1,0]}(\proj\Lambda)$ and an Auslander--Reiten conflation does not split.
+It thus follows from~\cite[Lemma 3.4 ]{AdachiIyamaReiten} that~$X$ and~$\tau X$ are rigid in $K^{[-1,0]}(\proj\Lambda)$.
+We have to prove that both~$E\oplus X$ and~$E\oplus\tau X$ are rigid.
+
+\vspace{7pt}
+\noindent (1) $\Hom{K^b}(E,\susp X) = 0$.
+\vspace{4pt}
+
+The Auslander--Reiten conflation induces an exact sequence
+\[
+\Hom{K^b}(X,\susp X) \to \Hom{K^b}(E,\susp X) \to \Hom{K^b}(\tau X,\susp X).
+\]
+As already remarked,~$X$ is rigid so that the left-most term vanishes.
+By assumption
+\[
+\Hom{\Lambda}(FX,\tau F\tau X) = \Hom{\Lambda}(M,\tau^2 M)=0,
+\]
+so that the right-most term also vanishes by~\cite[Lemma 3.4 ]{AdachiIyamaReiten}.
+
+\vspace{7pt}
+\noindent (2) $\Hom{K^b}(\tau X,\susp E) = 0$.
+\vspace{4pt}
+
+Since~$\Lambda$ is projective in~$K^{[-1,0]}(\proj\Lambda)$, the sequence~$\tau M \to FE \to M$ is short exact.
+It induces a sequence
+\[
+\Hom{\Lambda}(M,\tau^2 M) \to \Hom{\Lambda}(FE,\tau^2 M) \to \Hom{\Lambda}(\tau M,\tau^2 M)
+\]
+from which we deduce that~$\Hom{\Lambda}(FE,\tau^2 M)=0$.
+This implies~$\Hom{K^b}(\tau X,\susp E) = 0$ by~\cite[Lemma 3.4 ]{AdachiIyamaReiten}.
+
+\vspace{7pt}
+\noindent (3) $\Hom{K^b}(X,\susp E) = 0$.
+\vspace{4pt}
+
+Let us show that~$\Hom{\Lambda}(FE,\tau M)=0$.
+Let~$FE \xrightarrow{f} \tau M$ be any morphism, and consider the short exact sequence~$0\to \tau M \xrightarrow{a} FE \xrightarrow{b} M \to 0$ induced by the Auslander--Reiten conflation.
+Since~$\tau M$ is a brick, the composition~$fa$ is zero.
+The morphism~$f$ then factors through the cokernel~$b$, which implies~$f=0$ since~$M$ is~$\tau$-rigid.
+
+\vspace{7pt}
+\noindent (4) $\Hom{K^b}(E,\susp E) = 0$.
+\vspace{4pt}
+
+The Auslander--Reiten conflation induces an exact sequence
+\[
+\Hom{K^b}(X,\susp E) \to \Hom{K^b}(E,\susp E) \to \Hom{K^b}(\tau X,\susp E).
+\]
+We can conclude by (2) and (3).
+
+\vspace{7pt}
+\noindent (5) $\Hom{K^b}(E,\susp \tau X) = 0$.
+\vspace{4pt}
+
+We have an exact sequence
+\[
+\Hom{K^b}(E,E) \to \Hom{K^b}(E,X) \to \Hom{K^b}(E,\susp \tau X) \to \Hom{K^b}(E,\susp E).
+\]
+The first map is surjective since~$E\to X$ is right almost split.
+We can conclude by (4).
 \end{proof}

### 2019-04-16 thirdPaper/draft/typeConeAssociahedra.tex
Th 4.27 mutation conflations for Artin algebras

@@
 \newcommand{\proj}{\operatorname{proj}}
+\newcommand{\bsm}{\begin{smallmatrix}}
+\newcommand{\esm}{\end{smallmatrix}}
 
@@
 \label{theo::brick-algebra-condition}
- Let~$\Lambda$ be a brick algebra which is finite-dimensional over a field~$\field$\pg{True for any Artin algebra?}.
-Then the almost-split conflations of~$K^{[-1,0]}(\proj \Lambda)$ are mutation conflations if and only if for any indecomposable~$\Lambda$-module~$M$, the space~$\Hom{\Lambda}(M, \tau^2 M)$ vanishes.
+ Let~$\Lambda$ be an Artin algebra all of whose non-injective indecomposable objects are bricks and all of whose indecomposable objects are~$\tau$-rigid\yann{Are there examples of representation-infinite algebras which satisfy those assumptions?}.
+Then the almost-split conflations of~$K^{[-1,0]}(\proj \Lambda)$ are mutation conflations if and only if for any non-projective indecomposable~$\Lambda$-module~$M$, the space~$\Hom{\Lambda}(M, \tau^2 M)$ vanishes.
 \end{theorem}
+
+\begin{remark}
+Assume that~$\Lambda$ is a finite-dimensional brick algebra which is representation-finite.
+Then~\cite[Theorem 6.2]{DemonetIyamaJasso} implies that the assumptions of Theorem~\ref{theo::brick-algebra-condition} are satisfied.
+\end{remark}
 
@@
 \]
-The first map is surjective since~$E\to X$ is right almost split.
+The first map is surjective since~$E\to X$ is right almost-split.
 We can conclude by (4).
@@
 \begin{lemma}
-\label{lemm::if-AR-sequences-are-mutation}
- Let~$\Lambda$ be an Artin algebra.
+Let~$\Lambda$ be an Artin algebra, and let~$Y\infl E\defl X$ be a conflation in~$K^{[-1,0]}(\proj\Lambda)$. Then:
+\begin{enumerate}
+ \item If~$\Hom{K^b}(Y,\susp E)=0$, we have~$\Hom{\Lambda}(FX,\tau FY)=0$.
+ \item If moreover~$Z\notin\add(\susp\Lambda)$ and the conflation is almost-split, then~$\Hom{\Lambda}(FX,\tau^2 FX)=0$.
+\end{enumerate}
+\end{lemma}
+
+\begin{proof}
+By Lemma~\ref{lemm::AR-conflations-and-sequences}, \emph{(2)} follows from \emph{(1)}.
+Let us prove \emph{(1)}.
+The conflation induces an exact sequence~$\Hom{K^b}(Y,\susp E) \to \Hom{K^b}(Y,\susp X) \to \Hom{K^b}(Y,\susp^2,Y)$.
+The complex~$Y$ being two-term, we have~$\Hom{K^b}(Y,\susp^2,Y)=0$.
+Assuming that~$\Hom{K^b}(Y,\susp E)=0$, we deduce that~$\Hom{K^b}(Y,\susp X)=0$, and hence that~$\Hom{\Lambda}(FX,\tau FY) = 0$ by~\cite[Lemma 3.4]{AdachiIyamaReiten}.
+\end{proof}
+
+\begin{lemma}
+Let~$\Lambda$ be an Artin algebra, and let~$P$ be an indecomposable projective~$\Lambda$-module which is a brick.
+Let~$I$ be indecomposable injective with socle~$P/\operatorname{rad}P$, and~$\alpha$ be the composition~$P\to\operatorname{soc} I \to I$.
+Then, composition with~$\alpha$ induces a surjection~$\Hom{\Lambda}(P,I)\to\Hom{\Lambda}(P,I)$.
+\end{lemma}
+
+\begin{proof}
+{\bf Small gap}
+\end{proof}
+
+\begin{lemma}\label{lemm::initial meshes}
+Let~$\Lambda$ be an Artin algebra, and let~$P$ be an indecomposable projective~$\Lambda$-module which is a brick.
+Let~$I$ be indecomposable injective with socle~$P/\operatorname{rad}P$, and~$\alpha$ be the composition~$P\to\operatorname{soc} I \to I$.
+Complete the morphism~$\alpha$ to a triangle~$P\to Y\to E\to \susp P$ in~$K^{[-1,0]}(\proj\Lambda)$, where~$Y$ is a minimal projective presentation of~$I$.
+Then~$Y\infl E\defl \susp P$ is an Auslander--Reiten conflation in~$K^{[-1,0]}(\proj\Lambda)$, which is also a mutation conflation.
+\end{lemma}
+
+\begin{proof}
+In this proof, we implicitely identify the projective indecomposable~$\Lambda$-module~$P$ with the complex~$P$ concentrated in degree~$0$.
+
+We first show that the conflation is almost-split.
+
+blahblahblah
+
+We now check that the conflation~$Y\infl E\defl\susp P$ is a mutation conflation.
+
+(0) Since~$P$ is concentrated in only one degree, it is rigid in~~$K^{[-1,0]}(\proj\Lambda)$ and so is~$\susp P$.
+Moreover,~$FY=I$ is~$\tau$-rigid, hence~$Y$ is rigid in~$K^{[-1,0]}(\proj\Lambda)$ by~\cite[Lemma 3.4]{AdachiIyamaReiten}.
+
+(1) We have~$\Hom{K^b}(E,\susp^2 P)=0$ since~$E$ is concentrated in degrees~$-1$ and~$0$.
+
+(2) $\Hom{K^b}(Y,\susp E)=0$: There is an exact sequence
+\[
+\Hom{K^b}(Y,\susp Y) \to \Hom{K^b}(Y,\susp E) \to \Hom{K^b}(Y,\susp^2 P),
+\]
+where the first term vanishes by (0) and the last term vanishes since~$Y$ is in degrees~$-1, 0$ while~$\susp^2 P$ is concentrated in degree~$-2$.
+
+(3) $\Hom{K^b}(E,\susp E)=0$: There is an exact sequence
+\[
+ \Hom{K^b}(\susp Y,\susp E) \to \Hom{K^b}(\susp P, \susp E) \to \Hom{K^b}(E,\susp E) \to \Hom{K^b}(Y,\susp E)
+\]
+in which the last term is zero by (2).
+The first morphism is isomorphic to~$\Hom{K^b}(Y,E) \to \Hom{K^b}(P,E)$, which is surjective by the previous lemma.
+
+(4) $\Hom{K^b}(E,\susp Y) = 0$: Consider the exact sequence
+\[
+ \Hom{K^b}(E,E) \to \Hom{K^b}(E,\susp P) \to \Hom{K^b}(E,\susp Y) \to \Hom{K^b}(E,\susp E).
+\]
+Its last term vanishes by (3) and its first morphism is surjective because~$E\to \susp P$ is right almost-split.
+
+(5) $\Hom{K^b}(\susp P,\susp E= 0$:
+Let~$P\xrightarrow{f} E$ be any morphism.
+Since~$P$ is rigid,~$f$ factors through the inflation~$\beta$ in the conflation~$Y\infl E\defl \susp P$, and there is some morphism~$g$ such that~$f=\beta g$.
+By the previous lemma, or by (4), the morphism~$g$ factors through~$\alpha$: there is some~$h$ such that~$g= h \alpha$.
+
+{\bf Small gap:} There is an~$h'$ such that~$h \alpha = \alpha h'$ and we deduce that~$f=\beta h \alpha = \beta \alpha h' = 0$.
+\end{proof}
+
+\begin{proof}[Proof of Theorem~\ref{theo::brick-algebra-condition}]
+ The theorem follows from the slightly more general statements of Lemma~\ref{lemm::then-AR-seq-are-mutation} and Lemma~\ref{lemm::initial meshes}.
+\end{proof}
+
+% \begin{lemma}
+% \label{lemm::if-AR-sequences-are-mutation}
+%  Let~$\Lambda$ be an Artin algebra.
 Assume that for any almost-split conflation~$\tau X \infl E \defl X$ of~$K^{[-1,0]}(\proj\Lambda)$, we have that~$\Hom{K^b}(X, \susp E) = \Hom{K^b}(E, \susp X) = 0$ and~$\Hom{K^b}(\tau X, \susp E) = \Hom{K^b}(E, \susp \tau X) = 0$.
 Then for any indecomposable~$\Lambda$-module~$M$, we have that~$\Hom{\Lambda}(M, \tau^2 M)$ vanishes.
-\end{lemma}
-\begin{proof}
-
-\end{proof}
+% \end{lemma}
+% \begin{proof}
+%  
+% \end{proof}
 
@@
 
-We know describe a setup satisfying the assumptions of Section~\ref{setting::extricat} that, at the same time, subsumes all examples given so far, while being easily checked in practice.\yann{A reformuler...}
+We now describe a setup satisfying the assumptions of Section~\ref{setting::extricat} that, at the same time, subsumes all examples given so far, while being easily checked in practice.\yann{A reformuler...}
 
@@
 One can check directly that the condition of Theorem~\ref{theo::brick-algebra-condition} is not satisfied.
+For example, the module~$\bsm2\\1\esm$ is~$\tau$-rigid since~$\tau(\bsm2\\1\esm) = \bsm3\\1\esm$, while~$\Hom{\Lambda}\left(\bsm2\\1\esm,\tau^2(\bsm2\\1\esm)\right) = \Hom{\Lambda}(\bsm2\\1\esm,\bsm1\\2\esm) \neq 0$.
 \end{example}

### 2019-04-16 thirdPaper/draft/typeConeAssociahedra.tex
definition extricats

@@
 
+The main definitions and first properties on extriangulated categories are recalled after the statements of the main results of this section.
+See Section~\ref{sect::recollections extricats} below.
+The reader that does not want to dwell into details can safely skip Section~\ref{sect::recollections extricats} and focus on any of the first three examples given in Remark~\ref{remark::examples extricats}: triangulated categories, exact categories (that are small or have enough projectives or injectives) and extension-closed subcategories of triangulated categories, such as the category~$K^{[-1,0]}(\proj \Lambda)$, are examples of extriangulated categories.
+
+We indifferently call \emph{conflations}, written~$X\infl Y\defl Z$, or \emph{extriangles}, written~$X\infl Y\defl Z \overset{\delta}{\dashrightarrow}$, the analogues of short exact sequences or triangles in an extriangulated category.
+
 \vspace{.4cm}
@@
 
-\begin{remark}
+\begin{remark}\label{remark::examples extricats}
  Examples of categories satisfying the properties above are
@@
 
-\yann{Rappels sur les categories extriangulees}
-
 %%%%%%%%%%%
@@
 \subsection{Recollections on extriangulated categories}
-
+\label{sect::recollections extricats}
 %%%%%%%%%%%
+
+Extriangulated categories, recently introduced in~\cite{NakaokaPalu}, axiomatize extension-closed subcategories of triangulated categories in a (moderately) similar way that Quillen's exact categories axiomatize extension-closed subcategories of abelian categories.
+They appear in representation theory in relation with cotorsion pairs~\cite{ChangZhouZhu-ClusterSubalgebras,ZhaoHuang-Phantom,LiuNakaoka-Hearts,Liu-LocalizationsHearts}, with Auslander--Reiten theory~\cite{IyamaNakaokaPalu}, with cluster algebras, mutations, or cluster-tilting theory~\cite{ChangZhouZhu-ClusterSubalgebras,Pressland,ZhouZhu-TriangulatedQuotient,LiuZhou-Abelian,LiuZhou-AbelianII}, with Cohen--Macaulay dg-modules in the remarkable~\cite{Jin}.
+We also note the generalization, called~$n$-exangulated categories~\cite{HerschendLiuNakaoka}, to a version suited for higher homological algebra.
+
+An extriangulated category is the data of an additive category~$\cat$, an additive bifunctor~$\mathbb{E}:\cat^\mathrm{op}\times\cat\to \mathit{Ab}$ modelling the~$\operatorname{Ext}^1$-bifunctor, and an additive realization~$\mathfrak{s}$ sending each element~$\delta\in\mathbb{E}(Z,X)$ to some (equivalence classe of) diagram~$X\to Y\to Z$ modelling the short exact sequences or triangles.
+Some axioms, inspired from the case of extension-closed subcategories of triangulated categories have to be satisfied.
+
+More specifically: fix an additive category~$\cat$, and an additive bifunctor~$\mathbb{E}: \cat^\mathrm{op}\times\cat\to\mathit{Ab}$.
+
+\begin{definition}
+For any~$X,Z\in\cat$, an element~$\delta\in\mathbb{E}(Z,X)$ is called an~$\mathbb{E}$-extension.
+A split~$\mathbb{E}$-extension is a zero element~$0\in\mathbb{E}(Z,X)$, for some objects~$X,Z\in\cat$.
+For any two~$\mathbb{E}$-extensions~$\delta\in\mathbb{E}(Z,X)$,~$\delta'\in\mathbb{E}(Z',X')$, the additivity of~$\cat$,~$\mathbb{E}$ permits to define the~$\mathbb{E}$-extension
+\[
+\delta\oplus\delta'\in\mathbb{E}(Z\oplus Z',X\oplus X').
+\]
+\end{definition}
+
+\begin{remark}
+Let~$\delta\in\mathbb{E}(Z,X)$ be an~$\mathbb{E}$-extension.
+By functoriality, any morphisms~$f\in\cat(X,X')$ and~$h\in\cat(Z',Z)$ induce~$\mathbb{E}$-extensions~$\mathbb{E}(Z,f)(\delta)\in\mathbb{E}(Z,X')\ \ \text{and}\ \ \mathbb{E}(h,X)(\delta)\in\mathbb{E}(Z',X)$.
+For short, we write~$f_\ast\delta$ and~$h^\ast\delta$ instead.
+Using those notations, we have, in~$\mathbb{E}(Z',X')$
+\[ \mathbb{E}(h,f)(\delta)=h^\ast f_\ast\delta=f_\ast h^\ast\delta. \]
+\end{remark}
+
+\begin{definition}
+A morphism~$(f,h):\delta\to\delta'$ of~$\mathbb{E}$-extensions~$\delta\in\mathbb{E}(Z,X)$,~$\delta'\in\mathbb{E}(Z',X')$ is a pair of morphisms~$f\in\cat(X,X')$ and~$h\in\cat(Z,Z')$ in~$\cat$, such that~$f_\ast\delta=h^\ast\delta'.$
+\end{definition}
+
+\begin{definition}\label{DefSqEquiv}
+Let~$X,Z\in\cat$ be any two objects. Two sequences of morphisms in~$\cat$
+\[ X \overset{x}{\longrightarrow}Y\overset{y}{\longrightarrow}Z \ \text{ and } \ X\overset{x'}{\longrightarrow}Y'\overset{y'}{\longrightarrow}Z \]
+are said to be equivalent if there exists an isomorphism~$g\in\cat(Y,Y')$ such that the following diagram commutes.
+\[
+\xy
+(-20,0)*+{X}="X";
+(5,0)*+{}="1";
+(0,6)*+{Y}="Y";
+(0,-6)*+{Y'}="Y'";
+(-5,0)*+{}="2";
+(20,0)*+{Z}="Z";
+%
+{\ar^{x} "X";"Y"};
+{\ar^{y} "Y";"Z"};
+{\ar_{x^{\prime}} "X";"Y'"};
+{\ar_{y^{\prime}} "Y'";"Z"};
+%
+{\ar^{g}_{\cong} "Y";"Y'"};
+%
+{\ar@{}|{} "X";"1"};
+{\ar@{}|{} "2";"Z"};
+\endxy
+\]
+The equivalence class of~$X \xrightarrow{x} Y \xrightarrow{y} Z$ is denoted by~$[X \xrightarrow{x} Y \xrightarrow{y} Z]$.
+\end{definition}
+
+\begin{notation}
+For any~$X,Y,Z,A,B,C\in\cat$, and any~$[X \xrightarrow{x} Y \xrightarrow{y} Z]$,~$[A \xrightarrow{a} B \xrightarrow{b} C]$, we let
+\[ 0=[X\overset{\left[\bsm1\\0\esm\right]}{\longrightarrow} X\oplus Y \overset{\left[\bsm0\;1\esm\right]}{\longrightarrow} Y]
+\]
+and
+\[
+[X \xrightarrow{x} Y \xrightarrow{y} Z]\oplus [A \xrightarrow{a} B \xrightarrow{b} C] = [X\oplus A \overset{\left[\bsm x \; 0 \\ 0\; a\esm\right]}{\longrightarrow} Y\oplus B \overset{\left[\bsm y\;0\\0\;b \esm\right]}{\longrightarrow} Z\oplus C].
+\]
+\end{notation}
+
+\begin{definition}
+An additive realization~$\mathfrak{s}$ is a correspondence associating, with~$\mathbb{E}$-extension~$\delta\in\mathbb{E}(Z,X)$, an equivalence class~$\mathfrak{s}(\delta)=[X\xrightarrow{x}Y\xrightarrow{y}Z]$ and satisfying the following condition:
+\begin{itemize}
+\item[$(\ast)$] Let~$\delta\in\mathbb{E}(Z,X)$ and~$\delta'\in\mathbb{E}(Z',X')$ be any pair of~$\mathbb{E}$-extensions, with
+\[\mathfrak{s}(\delta)=[X\xrightarrow{x}Y\xrightarrow{y}Z] \text{ and } \mathfrak{s}(\delta')=[X'\xrightarrow{x'}Y'\xrightarrow{y'}Z'].\]
+Then, for any morphism~$(f,h):\delta\to\delta'$, there exists~$g\in\cat(Y,Y')$ such that the following diagram commutes:
+\[
+\xy
+(-12,6)*+{X}="0";
+(0,6)*+{Y}="2";
+(12,6)*+{Z}="4";
+%
+(-12,-6)*+{X'}="10";
+(0,-6)*+{Y'}="12";
+(12,-6)*+{Z'}="14";
+%
+{\ar^{x} "0";"2"};
+{\ar^{y} "2";"4"};
+%
+{\ar_{f} "0";"10"};
+{\ar^{g} "2";"12"};
+{\ar^{h} "4";"14"};
+%
+{\ar_{x'} "10";"12"};
+{\ar_{y'} "12";"14"};
+%
+{\ar@{}|{} "0";"12"};
+{\ar@{}|{} "2";"14"};
+%
+{\ar@{}|\circlearrowright "0";"12"};
+{\ar@{}|\circlearrowright "2";"14"};
+\endxy
+\]
+\end{itemize}
+
+The sequence~$X\xrightarrow{x}Y\xrightarrow{y}Z$ is said to realize~$\delta$ if~$\mathfrak{s}(\delta)=[X\xrightarrow{x}Y\xrightarrow{y}Z]$, and the triple~$(f,g,h)$ is said to realize~$(f,h)$ if the diagram in~$(\ast)$ commutes.
+\end{definition}
+
+\begin{definition}
+A realization of~$\mathbb{E}$ is called additive if the following conditions are satisfied:
+\begin{enumerate}
+\item For any~$X,Z\in\cat$, the realization of the split~$\mathbb{E}$-extension~$0\in\mathbb{E}(Z,X)$ is given bys~$\mathfrak{s}(0)=0$.
+\item For any two~$\mathbb{E}$-extensions~$\delta\in\mathbb{E}(Z,X)$ and~$\delta'\in\mathbb{E}(Z',X')$, the realization of~$\delta\oplus\delta'$ is given by~$\mathfrak{s}(\delta\oplus\delta')=\mathfrak{s}(\delta)\oplus\mathfrak{s}(\delta')$.
+\end{enumerate}
+\end{definition}
+
+\begin{definition}(\cite[Definition 2.12]{NakaokaPalu})
+A triple~$(\cat,\mathbb{E},\mathfrak{s})$ is called an extriangulated category if the following holds:
+\begin{itemize}
+\item[{\rm (ET1)}] $\mathbb{E}:\cat^{\mathrm{op}}\times\cat\to\mathit{Ab}$ is an additive bifunctor;
+\item[{\rm (ET2)}] $\mathfrak{s}$ is an additive realization of~$\mathbb{E}$;
+\item[{\rm (ET3)}] Let~$\delta\in\mathbb{E}(Z,X)$ and~$\delta'\in\mathbb{E}(Z',X')$ be~$\mathbb{E}$-extensions, respectively realized by~$X\xrightarrow{x}Y\xrightarrow{y}Z$ and~$X'\xrightarrow{x'}Y'\xrightarrow{y'}Z'$.
+Then, for any commutative square
+\[
+\xy
+(-12,6)*+{X}="0";
+(0,6)*+{Y}="2";
+(12,6)*+{Z}="4";
+%
+(-12,-6)*+{X'}="10";
+(0,-6)*+{Y'}="12";
+(12,-6)*+{Z'}="14";
+%
+{\ar^{x} "0";"2"};
+{\ar^{y} "2";"4"};
+%
+{\ar_{f} "0";"10"};
+{\ar^{g} "2";"12"};
+%
+{\ar_{x'} "10";"12"};
+{\ar_{y'} "12";"14"};
+%
+{\ar@{}|{} "0";"12"};
+%
+{\ar@{}|\circlearrowright "0";"12"};
+\endxy 
+\]
+in~$\cat$, there exists a morphism~$(f,h):\delta\to\delta'$ satisfying~$h\circ y=y'\circ g$.
+\item[{\rm (ET3)$^{\mathrm{op}}$}] Dual of {\rm (ET3)}.
+\item[{\rm (ET4)}] Let~$\delta\in\mathbb{E}(Z',X)$ and~$\delta'\in\mathbb{E}(X',Y)$ be~$\mathbb{E}$-extensions realized respectively by
+\[
+X\overset{f}{\longrightarrow}Y\overset{f'}{\longrightarrow}Z'\ \text{ and } \ Y\overset{g}{\longrightarrow}Z\overset{g'}{\longrightarrow}X'.
+\]
+Then there exist an object~$Y'\in\cat$, a commutative diagram in~$\cat$
+\[
+\xy
+(-18,6)*+{X}="0";
+(-6,6)*+{Y}="2";
+(6,6)*+{Z'}="4";
+(18,6)="6";
+%
+(-18,-6)*+{X}="10";
+(-6,-6)*+{Z}="12";
+(6,-6)*+{Y'}="14";
+(18,-6)="16";
+%
+(-6,-18)*+{X'}="22";
+(6,-18)*+{X'}="24";
+%
+(-6,-28)="32";
+(6,-28)="34";
+%
+%
+{\ar^{f} "0";"2"};
+{\ar^{f'} "2";"4"};
+%
+{\ar@{=} "0";"10"};
+{\ar_{g} "2";"12"};
+{\ar^{d} "4";"14"};
+%
+{\ar_{h} "10";"12"};
+{\ar_{h'} "12";"14"};
+%
+{\ar_{g'} "12";"22"};
+{\ar^{e} "14";"24"};
+%
+{\ar@{=} "22";"24"};
+%
+{\ar@{}|{} "0";"12"};
+{\ar@{}|{} "2";"14"};
+{\ar@{}|{} "12";"24"};
+%
+{\ar@{-->}^\delta "4";"6"};
+{\ar@{-->}^{\delta''} "14";"16"};
+{\ar@{-->}^{\delta'} "22";"32"};
+{\ar@{-->}^{f'_\ast \delta'} "24";"34"};
+\endxy
+\]
+and an~$\mathbb{E}$-extension~$\delta''\in\mathbb{E}(Y',X)$ realized by~$X\overset{h}{\longrightarrow}Z\overset{h'}{\longrightarrow}Y'$, which satisfy the following compatibilities.
+  \begin{enumerate}[(i)]
+    \item $Z'\overset{d}{\longrightarrow}Y'\overset{e}{\longrightarrow}X'$ realizes~$f'_\ast\delta'$,
+    \item $d^\ast\delta''=\delta$,
+    \item $f_\ast\delta''=e^\ast\delta'$. 
+  \end{enumerate}
+\item[{\rm (ET4)$^{\mathrm{op}}$}] Dual of {\rm (ET4)}.
+\end{itemize}
+\end{definition}
+
+We use the following terminology.
+\begin{notation}
+Let~$(\cat,\mathbb{E},\mathfrak{s})$ be an extriangulated category.
+\begin{enumerate}
+\item A sequence~$X\xrightarrow{x}Y\xrightarrow{y}Z$ is called a conflation if it realizes some~$\mathbb{E}$-extension in~$\mathbb{E}(Z,X)$.
+In which case the morphism~$X\xrightarrow{x}Y$ is called an inflation, written~$X\infl Y$, and the morphism~$Y\xrightarrow{y}Z$ is called a deflation, witten~$Y\defl Z$.
+\item An extriangle is a diagram~$X\overset{x}{\infl} Y\overset{y}{\defl} Z\overset{\delta}{\dashrightarrow}$ where~$X\overset{x}{\infl} Y\overset{y}{\defl} Z$ is a conflation realizing the~$\mathbb{E}$-extension~$\delta\in\mathbb{E}(Z,X)$.
+\item Similarly, we call morphism of extriangles any diagram
+\[
+\xy
+(-12,6)*+{X}="0";
+(0,6)*+{Y}="2";
+(12,6)*+{Z}="4";
+(24,6)*+{}="6";
+%
+(-12,-6)*+{X'}="10";
+(0,-6)*+{Y'}="12";
+(12,-6)*+{Z'}="14";
+(24,-6)*+{}="16";
+%
+{\ar^{x} "0";"2"};
+{\ar^{y} "2";"4"};
+{\ar@{-->}^{\delta} "4";"6"};
+%
+{\ar_{f} "0";"10"};
+{\ar^{g} "2";"12"};
+{\ar^{h} "4";"14"};
+%
+{\ar_{x'} "10";"12"};
+{\ar_{y'} "12";"14"};
+{\ar@{-->}_{\delta'} "14";"16"};
+%
+{\ar@{}|{} "0";"12"};
+{\ar@{}|{} "2";"14"};
+\endxy
+\]
+where~$(f,h):\delta\to\delta'$ is a morphism of~$\mathbb{E}$-extensions realized by~$(f,g,h)$.
+\end{enumerate}
+\end{notation}
 
@@
 \begin{proof}
-Let~$T \overset{t}{\to} X$ be a morphism with $T\in \tc$.
+Let~$T \overset{t}{\to} X$ be a morphism with~$T\in \tc$.
 Using the notation of Remark~\ref{remark::equivalence Sigma}, there is an extriangle~$T\infl 0\defl \susp T \overset{\eps_T}{\dashrightarrow}$.

### 2019-04-16 thirdPaper/draft/typeConeAssociahedra.tex
properties extricats

@@
 %
-{\ar_{h} "10";"12"};
-{\ar_{h'} "12";"14"};
+{\ar^{h} "10";"12"};
+{\ar^{h'} "12";"14"};
 %
@@
 {\ar@{-->}^{f'_\ast \delta'} "24";"34"};
+%
+{\ar@{}|\circlearrowright "0";"12"};
+{\ar@{}|\circlearrowright "2";"14"};
+{\ar@{}|\circlearrowright "12";"24"};
 \endxy
@@
 \end{notation}
+
+The axioms above ensure that any extriangle induce long-ish exact sequences after application of some covariant or contravariant Hom-functor.
+In particular in any conflation, the inflation is a weak kernel of the deflation, and the deflation is a weak cokernel of the inflation.
+
+\begin{proposition}\emph{(}\cite[Propositions 3.3, 3.11]{NakaokaPalu}\emph{)}
+Assume that $(\cat,\mathbb{E},\mathfrak{s})$ is an extriangulated category, and let $X\xrightarrow{x}Y\xrightarrow{y}Z\overset{\delta}{\dashrightarrow}$ be an extriangle.
+Then the following sequences of natural transformations are exact:
+\[ \cat(Z,-)\overset{-\circ y}{\longrightarrow}\cat(Y,-)\overset{-\circ x}{\longrightarrow}\cat(X,-)\overset{\delta^\sharp}{\longrightarrow}\mathbb{E}(Z,-)\overset{y^\ast}{\longrightarrow}\mathbb{E}(Y,-)\overset{x^\ast}{\longrightarrow}\mathbb{E}(X,-), \]
+\[ \cat(-,X)\overset{x\circ-}{\longrightarrow}\cat(-,Y)\overset{y\circ-}{\longrightarrow}\cat(-,Z)\overset{\delta_\sharp}{\longrightarrow}\mathbb{E}(-,X)\overset{x_\ast}{\longrightarrow}\mathbb{E}(-,Y)\overset{y_\ast}{\longrightarrow}\mathbb{E}(-,Z), \]
+where~$\delta^\sharp(f)=f_\ast\delta$ and~$\delta_\sharp(g)=g^\ast\delta$.
+\end{proposition}
+
+Any variant of the axiom (ET4) that would hold in an extension-closed subcategory of a triangulated category by applying the octahedron axiom also holds in any extriangulated category.
+See~\cite[Section 3.2]{NakaokaPalu} for more details.
+
+\begin{definition}
+An almost-split~$\mathbb{E}$-extension~$\delta\in\mathbb{E}(Z,X)$ is a non-split~$\mathbb{E}$-extension such that:
+\begin{itemize}
+\item[{\rm (AS1)}] $f_\ast\delta=0$ for any non-section $f\in\cat(X,X')$.
+\item[{\rm (AS2)}] $g^\ast\delta=0$ for any non-retraction $g\in\cat(Z',Z)$.
+\end{itemize}
+\end{definition}
+
+\begin{definition}
+A non-zero object $X\in\cat$ is said to be endo-local if $\cat(X,X)$ is local.
+\end{definition}
+
+\begin{proposition}\emph{(}\cite[Proposition 2.5]{IyamaNakaokaPalu}\emph{)}
+For any non-split $\mathbb{E}$-extension $\delta\in\mathbb{E}(Z,X)$, the following holds.
+\begin{enumerate}[{\rm (1)}]
+\item If $\delta$ satisfies {\rm (AS1)}, then $X$ is endo-local.
+\item If $\delta$ satisfies {\rm (AS2)}, then $Z$ is endo-local.
+\end{enumerate}
+\end{proposition}
+
+\begin{definition}
+ An object~$P\in\cat$ is called projective if, for any~$X\in\cat$, we have~$\mathbb{E}(P,X)=0$.
+ Dually, an object~$I\in\cat$ is called injective if for any~$X\in\cat$, we have~$\mathbb{E}(X,I)=0$.
+\end{definition}
+
+\begin{proposition}\emph{(}\cite[Proposition 8.1]{IyamaNakaokaPalu}\emph{)}
+Let~$\Lambda$ be an Artin algebra and let~$K^{[-1,0]}(\proj\Lambda)$ be the full subcategory of the homotopy category~$K^b(\proj\Lambda)$ consisting of complexes concentrated in degrees~$-1$ and~$0$ (using cohomological conventions).
+Then any endo-local non-projective object~$X\in\cat$ permits an almost-split conflation~$\tau X\infl E\defl X$ and any endo-local non-injective object~$Y\in\cat$ permits an almost-split conflation~$Y\infl E'\defl \tau^- Y$.
+\end{proposition}
 

### 2019-04-17 thirdPaper/draft/typeConeAssociahedra.tex
modif small gaps

@@
 
-\begin{lemma}
-Let~$\Lambda$ be an Artin algebra, and let~$P$ be an indecomposable projective~$\Lambda$-module which is a brick.
-Let~$I$ be indecomposable injective with socle~$P/\operatorname{rad}P$, and~$\alpha$ be the composition~$P\to\operatorname{soc} I \to I$.
-Then, composition with~$\alpha$ induces a surjection~$\Hom{\Lambda}(P,I)\to\Hom{\Lambda}(P,I)$.
-\end{lemma}
-
-\begin{proof}
-{\bf Small gap}
-\end{proof}
+% \begin{lemma}
+% Let~$\Lambda$ be an Artin algebra, and let~$P$ be an indecomposable projective~$\Lambda$-module which is a brick.
+% Let~$I$ be indecomposable injective with socle~$P/\operatorname{rad}P$, and~$\alpha$ be the composition~$P\to\operatorname{soc} I \to I$.
+% Then, composition with~$\alpha$ induces a surjection~$\Hom{\Lambda}(P,I)\to\Hom{\Lambda}(P,I)$.
+% \end{lemma}
+% 
+% \begin{proof}
+% {\bf Small gap}
+% \end{proof}
 
 \begin{lemma}\label{lemm::initial meshes}
-Let~$\Lambda$ be an Artin algebra, and let~$P$ be an indecomposable projective~$\Lambda$-module which is a brick.
-Let~$I$ be indecomposable injective with socle~$P/\operatorname{rad}P$, and~$\alpha$ be the composition~$P\to\operatorname{soc} I \to I$.
-Complete the morphism~$\alpha$ to a triangle~$P\to Y\to E\to \susp P$ in~$K^{[-1,0]}(\proj\Lambda)$, where~$Y$ is a minimal projective presentation of~$I$.
-Then~$Y\infl E\defl \susp P$ is an Auslander--Reiten conflation in~$K^{[-1,0]}(\proj\Lambda)$, which is also a mutation conflation.
+Let~$\Lambda$ be an Artin algebra, and let~$P$ be an indecomposable projective~$\Lambda$-module.
+%which is a brick.
+% Let~$I$ be indecomposable injective with socle~$P/\operatorname{rad}P$, and~$\alpha$ be the composition~$P\to\operatorname{soc} I \to I$.
+% Complete the morphism~$\alpha$ to a triangle~$P\to Y\to E\to \susp P$ in~$K^{[-1,0]}(\proj\Lambda)$, where~$Y$ is a minimal projective presentation of~$I$.
+% Then~$Y\infl E\defl \susp P$ is an Auslander--Reiten conflation in~$K^{[-1,0]}(\proj\Lambda)$, which is also a mutation conflation.
+Then the Auslander--Reiten conflation~$Y\infl E\defl \susp P$ in~$K^{[-1,0]}(\proj\Lambda)$ is a mutation conflation.
 \end{lemma}
@@
 
-We first show that the conflation is almost-split.
-
-blahblahblah
-
-We now check that the conflation~$Y\infl E\defl\susp P$ is a mutation conflation.
+% We first show that the conflation is almost-split.
+% 
+% blahblahblah
+
+We check that the conflation~$Y\infl E\defl\susp P$ is a mutation conflation.
 
@@
 By the previous lemma, or by (4), the morphism~$g$ factors through~$\alpha$: there is some~$h$ such that~$g= h \alpha$.
+
+We then have~$f = \beta g = \beta (g-\alpha) = \beta (h-1) \alpha$.
+Since~$Y$ is endo-local, the morphism~$h-1$ is an automorphism.
 

### 2019-04-17 thirdPaper/draft/typeConeAssociahedra.tex
proofs of UERPforCA and meshMutations

@@
 Indeed, which of the two possible linear dependences is satisfied by the $\b{g}$-vectors of~$\cluster \cup \cluster'$ depends on the initial exchange matrix~$\B_\circ$.
-We will prove however that it is independent of the seeds containing~$x$ and~$x'$.
-\vincent{Link to \cref{sec:clusterCategories}.}
+% We will prove however that it is independent of the seeds containing~$x$ and~$x'$.
+% \vincent{Link to \cref{sec:clusterCategories}.}
+However, for cluster algebras of finite type, this linear dependence is independent of the choice of a seed containing~$x$ and~$x'$.
+As explained in Corollary~\ref{corollary:UERPforCAproof}, this statement follows from~\cite[Theorem 7.5]{BuanMarshReinekeReitenTodorov}.
+We state it here for future reference.
+Note that the corresponding statement for cluster variables, instead of~$\b{g}$-vectors, holds by~\cite[Theorem 1.11]{FominZelevinsky-ClusterAlgebrasII}.
 
@@
 
-The following will be shown in \cref{sec:clusterCategories}.
-\vincent{Precise link to \cref{sec:clusterCategories}.}
+The following will be shown in \cref{sec:clusterCategories}, Corollary~\ref{corollary:proof of prop meshMutations}.
 
@@
 
-  \item Let~$\Kg(\cat)$ be the quotient of~$\Ksp(\cat)$ by the relations~$[X]+[Z]-[Y]$ for all triangles
+  \item Let~$\Kg(\cat)$ \yann{I do not like this notation anymore: $\Kg(\cat)$ depends on the choice of a CTO $T$.
+How about $K_0^T(\cat)$, $K_0^{(\susp T)}(\cat)$, $K_0(\cat;T)$, $\Kg(\cat;T)$ or $K_0(\cat;(\susp T))$?} be the quotient of~$\Ksp(\cat)$ by the relations~$[X]+[Z]-[Y]$ for all triangles
   \[
@@
   with~$h\in (\susp T)$.  Denote by~$\b g:\Ksp(\cat) \to \Kg(\cat)$ the canonical projection.
-
  \end{enumerate}
@@
 
+In this section, we apply the results of Section~\ref{subsect::Statement cluster cats} in order to prove Proposition~\ref{prop:uniqueExchangePropertyCA} and Proposition~\ref{prop:meshMutations} of Section~\ref{subsec:typeConeCA}.
+
+We first recall the results on categorification of cluster algebras that we will make use of in the proofs.
 \begin{theorem}[]\pg{cite???}
+\label{thm::categorification}
  Let~$\cat$ be the cluster category of a valued quiver of Dynkin type~$A,B,C,D,E,F$ or~$G$.
@@
  \]
- which has the follwing properties.
+ expressing cluster variables as Laurent polynomials in the variables of the cluster~$\CC(T)$ and which has the follwing properties.
  \begin{itemize}
-  \item For any~$X,Y\in \ind(\cat)$, $\CC(X)$ and~$\CC(Y)$ are compatible if and only if~$\cat(X, \susp Y) = 0$.
-  \item For any~$X\in \ind(\cat)$, the~$\b g$-vector of~$\CC(X)$ is~$\b g([X])$, where we identify~$\Z^n$ and~$\Kg(\cat)$ via the isomorphism sending~$(a_1, \ldots, a_n)$ to~$\sum_{i=1}^n a_i [T_i]$.
-  \item For any~$X,Y\in \ind(\cat)$, $\CC(X)$ and~$\CC(Y)$ are exchangeable if and only if~$\dim_{\field_X}\cat(X, \susp Y) = \dim_{\field_Y}\cat(X, \susp Y) = 1$.
+  \item[(i)] \emph{(}\cite[Proposition 3.2]{BuanMarshReinekeReitenTodorov} and~\cite[]{×} \emph{)} For any~$X,Y\in \ind(\cat)$, $\CC(X)$ and~$\CC(Y)$ are compatible if and only if~$\cat(X, \susp Y) = 0$.
+  \item[(ii)] \emph{(}\cite[Proposition 4.3]{FuKeller} and \emph{)} For any~$X\in \ind(\cat)$, the~$\b g$-vector of~$\CC(X)$ is~$\b g([X])$, where we identify~$\Z^n$ and~$\Kg(\cat)$ via the isomorphism sending~$(a_1, \ldots, a_n)$ to~$\sum_{i=1}^n a_i [T_i]$.
+  \item[(iii)] \emph{(}\cite[Theorem 7.5]{BuanMarshReinekeReitenTodorov} and~\cite[]{×} \emph{)} For any~$X,Y\in \ind(\cat)$, $\CC(X)$ and~$\CC(Y)$ are exchangeable if and only if~$\dim_{\field_X}\cat(X, \susp Y) = \dim_{\field_Y}\cat(X, \susp Y) = 1$.
+  \item[(iv)]\emph{(}\cite[???]{BuanMarshReinekeReitenTodorov} and~\cite[???]{BuanIyamaReitenScott} and ???\emph{)} Let~$T'$ be any basic cluster-tilting object of~$\cat$.
+Then the matrix~$B'$ of the associated seed~$(\CC(T'),B')$ is given by the multiplicities of the middle terms of the exchange triangles.
+More explicitely,
  \end{itemize}
@@
 
-The cluster category also contains enough information to detect positive mutations.
-
-\begin{proposition}
- Let~$X,Y\in \ind(\cat)$ be such that~$\dim_{\field_X}\cat(X, \susp Y) = \dim_{\field_Y}\cat(X, \susp Y) = 1$.  Let 
+%The cluster category also contains enough information to detect positive mutations.
+The following definition is a cluster-tilting version of the positive mutation for~$\tau$-tilting modules, or for~$2$-term silting complexes.
+\begin{definition}
+Let~$x\in\cluster$ be a cluster variable in a given cluster and let~$x'\in \cluster'$ be obtained by mutating~$\cluster$ at~$x$.
+The mutation is said to be a \defn{positive mutation} with respect to some initial cluster~$\cluster_\circ$ if there are~$X,Y\in \ind(\cat)$ such that~$\CC(X)=x$,~$\CC(Y)=x'$,~$\dim_{\field_X}\cat(X, \susp Y) = \dim_{\field_Y}\cat(X, \susp Y) = 1$ and, for any non-split triangle
  \[
@@
  \]
- be triangle with~$h$ non-zero (this triangle is unique up to isomorphism).  Then~$\CC(Y)$ is obtained by performing a positive mutation on~$\CC(X)$ in some seed if and only if~$h\in (\susp T)$.
+(this triangle is unique up to isomorphism) we have~$h\in (\susp T)$, where~$T\in\cat$ is any basic cluster-tilting object such that~$\CC(T)=\cluster_\circ$.
+\end{definition}
+
+\begin{lemma}
+\label{lemma:positive mutation triangles}
+Let~$\mathcal{A}$ be any cluster algebra admitting a categorification by a Hom-finite,~$2$-Calabi--Yau, Krull--Schmidt, triangulated category with cluster-tilting objects.
+Let~$x\in\cluster$ be a cluster cariable in a given cluster and let~$x'\in \cluster'$ be obtained by mutating~$\cluster$ at~$x$.
+Then precisely one of the two mutations~$\mu_x(\cluster)$ and~$\mu_{x'}(\cluster')$ is a positive mutation.
+\end{lemma}
+
 \begin{proof}
-  \pg{TO DO, Vincent: definition of positive mutation?}
+In view of Theorem~\ref{thm::categorification} (iii), it follows from~\cite[Lemma 3.3]{Palu}
 \end{proof}
-\end{proposition}
-
-\vincent{Here should come the proof of \cref{prop:meshMutations}.}
-
-\vincent{Here should come the proof of \cref{prop:uniqueExchangePropertyCA}.}
+
+\begin{corollary}\emph{(Proposition~\ref{prop:meshMutations})}
+\label{corollary:proof of prop meshMutations}
+ For any initial exchange matrix~$\B_\circ$ of mutation type~$A, B, C, D$, $E, F$ or~$G$, the linear dependence between the $\b{g}$-vectors of any mutation can be decomposed into positive combinations of linear dependences between $\b{g}$-vectors of non-initial mesh mutations.
+\end{corollary}
+
+\begin{proof}
+Let~$\cat$ be a cluster category of Dynkin type~$A,B,C,D,E,F$ or~$G$, and let $T\in\cat$ be some basic cluster-tilting object categorifying the given initial exchange matrix$\B_\circ$. 
+By Lemma~\ref{lemma:positive mutation triangles}, we may assume that the mutation under consideration is a positive mutation.
+In view of Theorem~\ref{thm::categorification} (ii) and (iv) it is enough to show that the relation in~$\Kg(\cat)$ given by any triangle~$X\to E\to Y\xrightarrow{h} \susp X$ with~$h\in(\susp T)$ is a positive linear combination of relations coming from Auslander--Reiten triangles with third term not in~$\add(\susp T)$.
+This categorified statement is precisely Corollary~\ref{corollary::meshes positively generate cluster cats}.
+\end{proof}
+
+It also follows form Theorem~\ref{thm::categorification} above that any cluster algebra of finite type has the unique exchange relation property (see Definition~\ref{def:uerp}):
+\begin{corollary}
+\label{corollary:UERPforCAproof}
+\emph{(Proposition~\ref{prop:uniqueExchangePropertyCA})}
+Let~$\B_\circ$ be any finite type exchange matrix, and let~$\mathcal{A}(\B_\circ)$ be the associated cluster algebra without coefficients.
+Then, for any exchangeable cluster variables~$x$ and~$x'$, the linear dependence $\sum_{y \in \cluster \cup \cluster'} \coefficient[{\b{g}_y}][\cluster][\cluster'] \, \b{g}_y = 0$ only depends on the pair~$(x,x')$ and not on the specific choice of clusters~$\cluster$ and~$\cluster'$ containing~$x$ and~$x'$ respectively and such that~$\cluster\setminus\{x\}=\cluster'\setminus\{x'\}$.
+\end{corollary}
+
+\begin{proof}
+By the results in additive categorification of cluster algebras recalled in Theorem~\ref{thm::categorification}, the statement follows from Lemma~\ref{lemma::uerp categorified} below.
+\end{proof}
+
+\begin{lemma}
+\label{lemma::uerp categorified}
+Let~$\cat$ be a cluster category of Dynkin type~$A,B,C,D,E,F$ or~$G$, and let~$X,Y\in \cat$ be such~$\CC(Y)$ is obtained by performing a positive mutation at~$\CC(X)$ in any cluster containing it.
+Then the linear dependence between the~$\b{g}$-vectors given by the positive mutation is
+\[
+\b{g}_{\CC(X)} + \b{g}_{\CC(Y)} = \sum_i\b{g}_{\CC(E_i)}, 
+\]
+where~$X\to \bigoplus_i E_i \to Y \xrightarrow{h} \susp X$ is a non-split triangle and each~$E_i$ is indecomposable.
+\end{lemma}
+
+\begin{proof}
+Let~$T\in\cat$ be a basic cluster tilting object such that~$\CC(T)$ is the initial cluster.
+By LEmma~\ref{lemma:positive mutation triangles}, the morphism~$h$ belongs to the ideal~$(\susp T)$.
+Therefore, the triangle~$X\to \bigoplus_i E_i \to Y \xrightarrow{h} \susp X$ induces the relation~$[X]+[Y]=\sum_i [E_i]$ in~$\Kg(\cat)$.
+Theorem~\ref{thm::categorification} (ii) gives the equality~$\b{g}_{\CC(X)} + \b{g}_{\CC(Y)} = \sum_i\b{g}_{\CC(E_i)}$, where the~$\b{g}$-vectors are computed with respect to the initial seed~$\CC(T)$.
+By Theorem~\ref{thm::categorification} (iii), the middle term of the triangle is uniquely defined, up to isomorphism, by~$X$, and~$Y$, and the triangle is therefore an exchange triangle, with respect to any mutation at~$X$: it does not depend on the choice of a cluster tilting object containing~$X$.
+By Theorem~\ref{thm::categorification} (iv) this equality is one of the two equalities in Lemma~\ref{lem:linearDependencegvectorsCA}.
+\end{proof}
 
@@
 
+\yann{I think that our conventions coincide.
+With the choice of the Hom functor, $\susp T$ is sent to the initial seed so that the AR triangles ending in $\add(\susp T)$ are precisely the meshes ending in an initial variable}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{definition}
-We let~$\kzero{\cat}$ denote the Grothendieck group of~$\cat$, that is, the quotient of the free abelian group generated by symbols~$[X]$, for each $X\in\cat$, by the relations~$[X]-[Y]+[Z]$, for each conflation~$X\infl Y\defl Z$ in~$\cat$.
+We let~$\kzero{\cat}$ denote the \defn{Grothendieck group} of~$\cat$, that is, the quotient of the free abelian group generated by symbols~$[X]$, for each $X\in\cat$, by the relations~$[X]-[Y]+[Z]$, for each conflation~$X\infl Y\defl Z$ in~$\cat$.
 \end{definition}
@@
 \]
-and define
+and define the \defn{index} of~$X$ by
 \[
@@
 \begin{definition}
-For any~$X,Z\in\cat$, an element~$\delta\in\mathbb{E}(Z,X)$ is called an~$\mathbb{E}$-extension.
-A split~$\mathbb{E}$-extension is a zero element~$0\in\mathbb{E}(Z,X)$, for some objects~$X,Z\in\cat$.
+For any~$X,Z\in\cat$, an element~$\delta\in\mathbb{E}(Z,X)$ is called an~\defn{$\mathbb{E}$-extension}.
+A \defn{split}~$\mathbb{E}$-extension is a zero element~$0\in\mathbb{E}(Z,X)$, for some objects~$X,Z\in\cat$.
 For any two~$\mathbb{E}$-extensions~$\delta\in\mathbb{E}(Z,X)$,~$\delta'\in\mathbb{E}(Z',X')$, the additivity of~$\cat$,~$\mathbb{E}$ permits to define the~$\mathbb{E}$-extension
@@
 \begin{definition}
-A morphism~$(f,h):\delta\to\delta'$ of~$\mathbb{E}$-extensions~$\delta\in\mathbb{E}(Z,X)$,~$\delta'\in\mathbb{E}(Z',X')$ is a pair of morphisms~$f\in\cat(X,X')$ and~$h\in\cat(Z,Z')$ in~$\cat$, such that~$f_\ast\delta=h^\ast\delta'.$
+A \defn{morphism}~$(f,h):\delta\to\delta'$ of~$\mathbb{E}$-extensions~$\delta\in\mathbb{E}(Z,X)$,~$\delta'\in\mathbb{E}(Z',X')$ is a pair of morphisms~$f\in\cat(X,X')$ and~$h\in\cat(Z,Z')$ in~$\cat$, such that~$f_\ast\delta=h^\ast\delta'.$
 \end{definition}
@@
 \[ X \overset{x}{\longrightarrow}Y\overset{y}{\longrightarrow}Z \ \text{ and } \ X\overset{x'}{\longrightarrow}Y'\overset{y'}{\longrightarrow}Z \]
-are said to be equivalent if there exists an isomorphism~$g\in\cat(Y,Y')$ such that the following diagram commutes.
+are said to be \defn{equivalent} if there exists an isomorphism~$g\in\cat(Y,Y')$ such that the following diagram commutes.
 \[
@@
 \begin{definition}
-An additive realization~$\mathfrak{s}$ is a correspondence associating, with~$\mathbb{E}$-extension~$\delta\in\mathbb{E}(Z,X)$, an equivalence class~$\mathfrak{s}(\delta)=[X\xrightarrow{x}Y\xrightarrow{y}Z]$ and satisfying the following condition:
+An \defn{additive realization}~$\mathfrak{s}$ is a correspondence associating, with~$\mathbb{E}$-extension~$\delta\in\mathbb{E}(Z,X)$, an equivalence class~$\mathfrak{s}(\delta)=[X\xrightarrow{x}Y\xrightarrow{y}Z]$ and satisfying the following condition:
 \begin{itemize}
@@
 
-The sequence~$X\xrightarrow{x}Y\xrightarrow{y}Z$ is said to realize~$\delta$ if~$\mathfrak{s}(\delta)=[X\xrightarrow{x}Y\xrightarrow{y}Z]$, and the triple~$(f,g,h)$ is said to realize~$(f,h)$ if the diagram in~$(\ast)$ commutes.
+The sequence~$X\xrightarrow{x}Y\xrightarrow{y}Z$ is said to \defn{realize}~$\delta$ if~$\mathfrak{s}(\delta)=[X\xrightarrow{x}Y\xrightarrow{y}Z]$, and the triple~$(f,g,h)$ is said to realize~$(f,h)$ if the diagram in~$(\ast)$ commutes.
 \end{definition}
@@
 \begin{definition}
-A realization of~$\mathbb{E}$ is called additive if the following conditions are satisfied:
+A realization of~$\mathbb{E}$ is called an \defn{additive realization} if the following conditions are satisfied:
 \begin{enumerate}
@@
 \begin{definition}(\cite[Definition 2.12]{NakaokaPalu})
-A triple~$(\cat,\mathbb{E},\mathfrak{s})$ is called an extriangulated category if the following holds:
+A triple~$(\cat,\mathbb{E},\mathfrak{s})$ is called an \defn{extriangulated category} if the following holds:
 \begin{itemize}
@@
 \begin{definition}
-An almost-split~$\mathbb{E}$-extension~$\delta\in\mathbb{E}(Z,X)$ is a non-split~$\mathbb{E}$-extension such that:
+An \defn{almost-split}~$\mathbb{E}$-extension~$\delta\in\mathbb{E}(Z,X)$ is a non-split~$\mathbb{E}$-extension such that:
 \begin{itemize}
@@
 \begin{definition}
-A non-zero object $X\in\cat$ is said to be endo-local if $\cat(X,X)$ is local.
+A non-zero object $X\in\cat$ is said to be \defn{endo-local} if $\cat(X,X)$ is local.
 \end{definition}
@@
 \begin{definition}
- An object~$P\in\cat$ is called projective if, for any~$X\in\cat$, we have~$\mathbb{E}(P,X)=0$.
- Dually, an object~$I\in\cat$ is called injective if for any~$X\in\cat$, we have~$\mathbb{E}(X,I)=0$.
+ An object~$P\in\cat$ is called \defn{projective} if, for any~$X\in\cat$, we have~$\mathbb{E}(P,X)=0$.
+ Dually, an object~$I\in\cat$ is called \defn{injective} if for any~$X\in\cat$, we have~$\mathbb{E}(X,I)=0$.
 \end{definition}

### 2019-04-17 thirdPaper/draft/typeConeAssociahedra.tex
last sentence of introduction modified

@@
 Some of these questions are explicitly indicated throughout the paper.
-To conclude, we observe that the associahedra constructed in~\cite{ArkaniHamedBaiHeYan, BazierMatteDouvilleMousavandThomasYildirim} and the present paper describe all polytopal realizations of the $\b{g}$-vector fan, motivating the question to understand the complete realization space of the cluster complex.
+To conclude, we observe that the associahedra constructed in~\cite{ArkaniHamedBaiHeYan, BazierMatteDouvilleMousavandThomasYildirim} and the present paper describe all polytopal realizations of the $\b{g}$-vector fan.
+This motivates the following question: Is it possible to similarly understand the complete realization space of the cluster complex, including all realizations not having the~$\b{g}$-vector fan as their normal fan?
 

### 2019-04-21 thirdPaper/draft/typeConeAssociahedra.tex
Minor minor changes to intro and abstract.

@@
 Along the way, we prove algebraic results on~$2$-Calabi--Yau triangulated categories, and on extriangulated categories that are of independent interest.
-In particular, we prove, in those two setups, an analogue of a result of M. Auslander on minimal relations for Grothendieck groups.
+In particular, we prove, in those two setups, an analogue of a result of M. Auslander on minimal relations for Grothendieck groups of module categories.
 \end{abstract}
@@
 \section*{Introduction}
-
+\pg{Could we replace ``explains'' with ``sheds a new light on'' in abstract?}
 The associahedron is a ``mythical polytope'' \cite{Haiman} whose facial structure encodes Catalan families: its vertices correspond to parenthesizations of a non-associative product, triangulations of a convex polygon, or binary trees; its edges correspond to applications of the associativity rule, diagonal flips, or edge rotations; and in general its faces correspond to partial parenthesizations, diagonal dissections, or Schr\"oder trees.
 Its combinatorial and topological structure was introduced in early works of D.~Tamari~\cite{Tamari} and J.~Stasheff~\cite{Stasheff}, and a first polytopal model was realized by J.~Milnor for the PhD defense of the latter.
+\pg{Of whose PhD thesis?}
 The first systematic polytopal realizations were constructed by M.~Haiman~\cite{Haiman} and C.~Lee~\cite{Lee}.
@@
 This construction provides a large degree of freedom in the choice of the parameters defining these affine subspaces and produces all polytopes whose normal fan is affinely equivalent to that of J.-L.~Loday's associahedron~\cite{Loday} (see \cref{subsec:typeConeAsso}).
-These realizations were then extended by V.~Bazier-Matte, G.~Douville, K.~Mousavand, H.~Thomas and E.~Yildirim~\cite{BazierMatteDouvilleMousavandThomasYildirim} in the context of finite type cluster algebras using tools from representation theory of quivers.
+These realizations were then extended by V.~Bazier-Matte, G.~Douville, K.~Mousavand, H.~Thomas and E.~Y\i ld\i r\i m~\cite{BazierMatteDouvilleMousavandThomasYildirim} in the context of finite type cluster algebras using tools from representation theory of quivers.
 More precisely, they fix a finite type cluster algebra~$\c{A}$ and consider the real euclidean space~$\R^\c{V}$ indexed by the set~$\c{V}$ of cluster variables of~$\c{A}$.
-Starting from an acyclic initial seed~$\seed_\circ$, they consider a set~$\c{M}$ of mesh mutations and compute the corresponding linear dependences between the $\b{g}$-vectors, that can be interpreted as linear spaces in~$\R^\c{V}$.
+Starting from an acyclic initial seed~$\seed_\circ$, they consider a set~$\c{M}$ of mesh mutations and compute the corresponding linear dependences between the $\b{g}$-vectors, which can be interpreted as linear spaces in~$\R^\c{V}$.
 Finally, they perturb these mesh linear spaces by a collection~$\b{\ell} \in \R^{\c{M}}$ of positive parameters and intersect the resulting perturbed mesh affine spaces with the positive orthant of~$\R^\c{V}$ (see \cref{subsec:typeConeCA}).
@@
 \smallskip
-\item \textbf{any positive real valued parameters}, regardless of whether they are rational or not.
-In contrast, the proof of~\cite{BazierMatteDouvilleMousavandThomasYildirim} naturally applies to rational parameters and then requires to apply an approximation argument.
+\item \textbf{any positive real-valued parameters}, regardless of whether they are rational or not.
+In contrast, the proof of~\cite{BazierMatteDouvilleMousavandThomasYildirim} naturally applies to rational parameters and then requires an approximation argument.
 \end{itemize}
@@
 Our algebraic proof is based on an analogue of a result of M. Auslander~\cite{Auslander1984} relating to minimal generators of Grothendieck groups.
-Along the way, we need to generalise, for extriangulated categories, several results from cluster-tilting theory on indices~\cite{DehyKeller} and on abelian quotients~\cite{BuanMarshReiten, KellerReiten} that were known for triangulated categories.
-We note however, that our assumptions are not quite the expected ones.
+Along the way, we need to generalize, for extriangulated categories, several results from cluster-tilting theory on indices~\cite{DehyKeller} and on abelian quotients~\cite{BuanMarshReiten, KellerReiten} that were known for triangulated categories.
+We note, however, that our assumptions are not quite the expected ones.
 This is related to the fact that the Grothendieck groups of cluster categories are badly behaved (\eg the Grothendieck group of a cluster category of type~$A_2$ is trivial).
@@
 This motivates the following question: Is it possible to similarly understand the complete realization space of the cluster complex, including all realizations not having the~$\b{g}$-vector fan as their normal fan?
+\pg{AWESOME introduction.}
 
@@
 
-(5) $\Hom{K^b}(\susp P,\susp E= 0$:
+(5) $\Hom{K^b}(\susp P,\susp E)= 0$:
 Let~$P\xrightarrow{f} E$ be any morphism.

### 2019-04-21 thirdPaper/draft/typeConeAssociahedra.tex
Minor changes and comments to Section 4.

@@
 \end{theorem}
+\pg{Should define mutation conflations}
 
@@
 Let~$\Lambda$ be an Artin algebra, let~$\tau X\infl E\defl X$ be an Auslander--Reiten conflation in~$K^{[-1,0]}(\proj\Lambda)$ and denote~$FX=M$.
-Assume that:\yann{There might be some redundancies in the assumptions}
+Assume that:\yann{There might be some redundancies in the assumptions}\pg{If so, it's not obvious to me.}
 \begin{enumerate}
@@
 \begin{proof}
-In this proof, we implicitely identify the projective indecomposable~$\Lambda$-module~$P$ with the complex~$P$ concentrated in degree~$0$.
+In this proof, we implicitly identify the projective indecomposable~$\Lambda$-module~$P$ with the complex~$P$ concentrated in degree~$0$.
 
@@
 (0) Since~$P$ is concentrated in only one degree, it is rigid in~~$K^{[-1,0]}(\proj\Lambda)$ and so is~$\susp P$.
-Moreover,~$FY=I$ is~$\tau$-rigid, hence~$Y$ is rigid in~$K^{[-1,0]}(\proj\Lambda)$ by~\cite[Lemma 3.4]{AdachiIyamaReiten}.
+Moreover,~$FY=I$ is~$\tau$-rigid, hence~$Y$ is rigid in~$K^{[-1,0]}(\proj\Lambda)$ by~\cite[Lemma 3.4]{AdachiIyamaReiten}.\pg{Injectives are not necessarily tau-rigid.
+Need that Lambda is a brick algebra?}
 
@@
 Since~$P$ is rigid,~$f$ factors through the inflation~$\beta$ in the conflation~$Y\infl E\defl \susp P$, and there is some morphism~$g$ such that~$f=\beta g$.
-By the previous lemma, or by (4), the morphism~$g$ factors through~$\alpha$: there is some~$h$ such that~$g= h \alpha$.
+By the previous lemma, or by (4), the morphism~$g$ factors through~$\alpha$: there is some~$h$ such that~$g= h \alpha$.\pg{What is alpha?}
 

### 2019-04-21 thirdPaper/draft/typeConeAssociahedra.tex
minor changes intro

@@
 We then use this algebraic result to derive geometric properties of the $\b{g}$-vector fan: we show that the space of all its polytopal realizations is a simplicial cone, and we then observe that this property implies that all its realizations can be described as the intersection of a high dimensional positive orthant with well-chosen affine spaces.
-This explains and extends earlier results of N.~Arkani-Hamed, Y.~Bai, S.~He, and G.~Yan in type~$A$ and of V.~Bazier-Matte, G.~Douville, K.~Mousavand, H.~Thomas and E.~Yildirim for acyclic initial seeds.
+This sheds a new light on and extends earlier results of N.~Arkani-Hamed, Y.~Bai, S.~He, and G.~Yan in type~$A$ and of V.~Bazier-Matte, G.~Douville, K.~Mousavand, H.~Thomas and E.~Y\i ld\i r\i m for acyclic initial seeds.
 
@@
 \section*{Introduction}
-\pg{Could we replace ``explains'' with ``sheds a new light on'' in abstract?}
+
 The associahedron is a ``mythical polytope'' \cite{Haiman} whose facial structure encodes Catalan families: its vertices correspond to parenthesizations of a non-associative product, triangulations of a convex polygon, or binary trees; its edges correspond to applications of the associativity rule, diagonal flips, or edge rotations; and in general its faces correspond to partial parenthesizations, diagonal dissections, or Schr\"oder trees.
-Its combinatorial and topological structure was introduced in early works of D.~Tamari~\cite{Tamari} and J.~Stasheff~\cite{Stasheff}, and a first polytopal model was realized by J.~Milnor for the PhD defense of the latter.
-\pg{Of whose PhD thesis?}
+Its combinatorial and topological structure was introduced in early works of D.~Tamari~\cite{Tamari} and J.~Stasheff~\cite{Stasheff}, and a first polytopal model was realized by J.~Milnor for the PhD defense of J.~Stasheff.
 The first systematic polytopal realizations were constructed by M.~Haiman~\cite{Haiman} and C.~Lee~\cite{Lee}.
@@
 All these realizations have the same normal fan, called nested fan.
-We study the type cones of these nested fans (see \cref{subsec:typeConeGA}): we describe describe their facet-defining inequalities in terms of certain specific pairs of neighboring tubings and count them for the specific families of graph associahedra described earlier.
+We study the type cones of these nested fans (see \cref{subsec:typeConeGA}): we describe their facet-defining inequalities in terms of certain specific pairs of neighboring tubings and count them for the specific families of graph associahedra described earlier.
 For instance the type cone of the permutahedron coincides with the classical submodular functions on~$2^{[n]}$, described by~$2^{n-2} \binom{n}{2}$ inequalities.
@@
 First, it raised the fundamental problem of describing the minimal relations among $\b{g}$-vectors in $2$-Calabi--Yau and extriangulated categories that we treat in \cref{part:algebra}.
-It is also motivates the study of relevant objects revealed by the type cone dictionary between geometry and algebra:
+It also motivates the study of relevant objects revealed by the type cone dictionary between geometry and algebra:
 
@@
 \pg{AWESOME introduction.}
+\vincent{:-)}
 
@@
 These polytopal realizations were first constructed for bipartite initial seeds by F.~Chapoton, S.~Fomin and A.~Zelevinsky~\cite{ChapotonFominZelevinsky} using the $\b{d}$-vector fans of~\cite{FominZelevinsky-YSystems}, then for acyclic initial seeds by C.~Hohlweg, C.~Lange and H.~Thomas~\cite{HohlwegLangeThomas} using Cambrian lattices and fans of N.~Reading and D.~Speyer~\cite{Reading-CambrianLattices, ReadingSpeyer}, and revisited by S.~Stella~\cite{Stella}, and by V.~Pilaud and C.~Stump~\cite{PilaudStump-brickPolytope} via brick polytopes, and finally for arbitrary initial seeds by C.~Hohlweg, V.~Pilaud and S.~Stella~\cite{HohlwegPilaudStella}.
-More recently in~\cite{BazierMatteDouvilleMousavandThomasYildirim}, V.~Bazier-Matte, G.~Douville, K.~Mousavand, H.~Thomas and E.~Yildirim extended the construction of associahedra of~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} to acyclic seeds of simply-laced finite type cluster algebras.
+More recently in~\cite{BazierMatteDouvilleMousavandThomasYildirim}, V.~Bazier-Matte, G.~Douville, K.~Mousavand, H.~Thomas and E.~Y\i ld\i r\i m extended the construction of associahedra of~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} to acyclic seeds of simply-laced finite type cluster algebras.
 Here, we extend the construction of~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} to any finite type (simply-laced or not) cluster algebra with respect to any seed (acyclic or not) by providing a direct proof that the type cone of the cluster fan of any finite type cluster algebra is simplicial.

### 2019-04-22 thirdPaper/draft/typeConeAssociahedra.tex
comments Lemma 4.47

@@
 \begin{lemma}\label{lemm::initial meshes}
-Let~$\Lambda$ be an Artin algebra, and let~$P$ be an indecomposable projective~$\Lambda$-module.
+Let~$\Lambda$ be an Artin algebra whose indecomposable injective modules are~$\tau$-rigid\yann{harmless assumption added}, and let~$P$ be an indecomposable projective~$\Lambda$-module.
 %which is a brick.
@@
 Moreover,~$FY=I$ is~$\tau$-rigid, hence~$Y$ is rigid in~$K^{[-1,0]}(\proj\Lambda)$ by~\cite[Lemma 3.4]{AdachiIyamaReiten}.\pg{Injectives are not necessarily tau-rigid.
-Need that Lambda is a brick algebra?}
+Need that Lambda is a brick algebra?}\yann{You are right, they are $\tau^-$-rigid.
+Not a problem because we assume all indecomposables to be $\tau$-rigid in our theorem.}
 
@@
 Since~$P$ is rigid,~$f$ factors through the inflation~$\beta$ in the conflation~$Y\infl E\defl \susp P$, and there is some morphism~$g$ such that~$f=\beta g$.
-By the previous lemma, or by (4), the morphism~$g$ factors through~$\alpha$: there is some~$h$ such that~$g= h \alpha$.\pg{What is alpha?}
+By the previous lemma, or by (4), the morphism~$g$ factors through~$P \xrightarrow{\alpha} Y$: there is some~$h$ such that~$g= h \alpha$.\pg{What is alpha?}
 

### 2019-04-23 thirdPaper/draft/typeConeAssociahedra.tex
added reference

@@
 Extriangulated categories, recently introduced in~\cite{NakaokaPalu}, axiomatize extension-closed subcategories of triangulated categories in a (moderately) similar way that Quillen's exact categories axiomatize extension-closed subcategories of abelian categories.
-They appear in representation theory in relation with cotorsion pairs~\cite{ChangZhouZhu-ClusterSubalgebras,ZhaoHuang-Phantom,LiuNakaoka-Hearts,Liu-LocalizationsHearts}, with Auslander--Reiten theory~\cite{IyamaNakaokaPalu}, with cluster algebras, mutations, or cluster-tilting theory~\cite{ChangZhouZhu-ClusterSubalgebras,Pressland,ZhouZhu-TriangulatedQuotient,LiuZhou-Abelian,LiuZhou-AbelianII}, with Cohen--Macaulay dg-modules in the remarkable~\cite{Jin}.
+They appear in representation theory in relation with cotorsion pairs~\cite{ChangZhouZhu-ClusterSubalgebras,ZhaoHuang-Phantom,LiuNakaoka-Hearts,Liu-LocalizationsHearts}, with Auslander--Reiten theory~\cite{IyamaNakaokaPalu}, with cluster algebras, mutations, or cluster-tilting theory~\cite{ChangZhouZhu-ClusterSubalgebras,Pressland,ZhouZhu-TriangulatedQuotient,LiuZhou-Abelian,LiuZhou-AbelianII,LiuZhou-Gorenstein}, with Cohen--Macaulay dg-modules in the remarkable~\cite{Jin}.
 We also note the generalization, called~$n$-exangulated categories~\cite{HerschendLiuNakaoka}, to a version suited for higher homological algebra.

### 2019-04-26 thirdPaper/draft/typeConeAssociahedra.tex
Need brick algebra for Lemma 4.7?

@@
   \item Let~$\Kg(\cat)$ \yann{I do not like this notation anymore: $\Kg(\cat)$ depends on the choice of a CTO $T$.
-How about $K_0^T(\cat)$, $K_0^{(\susp T)}(\cat)$, $K_0(\cat;T)$, $\Kg(\cat;T)$ or $K_0(\cat;(\susp T))$?} be the quotient of~$\Ksp(\cat)$ by the relations~$[X]+[Z]-[Y]$ for all triangles
+How about $K_0^T(\cat)$, $K_0^{(\susp T)}(\cat)$, $K_0(\cat;T)$, $\Kg(\cat;T)$ or $K_0(\cat;(\susp T))$?}\pg{Good point.
+I like~$K_0^T(\cat)$ and~$K_0(\cat;T)$.} be the quotient of~$\Ksp(\cat)$ by the relations~$[X]+[Z]-[Y]$ for all triangles
   \[
@@
 \label{theo::brick-algebra-condition}
- Let~$\Lambda$ be an Artin algebra all of whose non-injective indecomposable objects are bricks and all of whose indecomposable objects are~$\tau$-rigid\yann{Are there examples of representation-infinite algebras which satisfy those assumptions?}.
+ Let~$\Lambda$ be an Artin algebra all of whose non-injective indecomposable objects are bricks and all of whose indecomposable objects are~$\tau$-rigid\yann{Are there examples of representation-infinite algebras which satisfy those assumptions?}\pg{Don't think so, but can't find a proof}.
 Then the almost-split conflations of~$K^{[-1,0]}(\proj \Lambda)$ are mutation conflations if and only if for any non-projective indecomposable~$\Lambda$-module~$M$, the space~$\Hom{\Lambda}(M, \tau^2 M)$ vanishes.
@@
 \begin{lemma}\label{lemm::initial meshes}
-Let~$\Lambda$ be an Artin algebra whose indecomposable injective modules are~$\tau$-rigid\yann{harmless assumption added}, and let~$P$ be an indecomposable projective~$\Lambda$-module.
+Let~$\Lambda$ be an Artin algebra whose indecomposable injective modules are~$\tau$-rigid, and let~$P$ be an indecomposable projective~$\Lambda$-module.
 %which is a brick.
@@
 \end{lemma}
+\pg{This seems false for~$\Lambda = k[x]/(x^2)$: AR sequence~$\Lambda\to (\Lambda\to \Lambda) \to \Sigma\Lambda$.  Probably need brick algebra.}
 
@@
 (0) Since~$P$ is concentrated in only one degree, it is rigid in~~$K^{[-1,0]}(\proj\Lambda)$ and so is~$\susp P$.
-Moreover,~$FY=I$ is~$\tau$-rigid, hence~$Y$ is rigid in~$K^{[-1,0]}(\proj\Lambda)$ by~\cite[Lemma 3.4]{AdachiIyamaReiten}.\pg{Injectives are not necessarily tau-rigid.
-Need that Lambda is a brick algebra?}\yann{You are right, they are $\tau^-$-rigid.
-Not a problem because we assume all indecomposables to be $\tau$-rigid in our theorem.}
+Moreover,~$FY=I$ is~$\tau$-rigid, hence~$Y$ is rigid in~$K^{[-1,0]}(\proj\Lambda)$ by~\cite[Lemma 3.4]{AdachiIyamaReiten}.
 
@@
 Since~$P$ is rigid,~$f$ factors through the inflation~$\beta$ in the conflation~$Y\infl E\defl \susp P$, and there is some morphism~$g$ such that~$f=\beta g$.
-By the previous lemma, or by (4), the morphism~$g$ factors through~$P \xrightarrow{\alpha} Y$: there is some~$h$ such that~$g= h \alpha$.\pg{What is alpha?}
+By the previous lemma, or by (4), the morphism~$g$ factors through~$P \xrightarrow{\alpha} Y$: there is some~$h:Y\to Y$ such that~$g= h \alpha$.\pg{Fixable if~$\Lambda$ is brick? Will think more...}
 

### 2019-05-09 thirdPaper/draft/typeConeAssociahedra.tex
located a bug in the graph associahedra proof

@@
 \item Once we get a representation of a polytope~$P$ as a signed Minkowski sum~$P = \sum_{i \in [k]}\alpha_i Q_i$, we get a formula for the volume of $P$ as a multivariate polynomial in $\alpha_1,\dots,\alpha_k$ whose coefficients are the mixed volumes of $Q_1,\dots, Q_k$~\cite{ArdilaBenedettiDoker,McMullen-Valuations}.
-These encode rich combinatorial information when representing generalized permuahedra as positive Minkowski sum of coordinate simplices or hypersimplices~\cite{Postnikov}, and in particular for matroid polytopes~\cite{ArdilaBenedettiDoker}.
+These encode rich combinatorial information when representing generalized permutahedra as positive Minkowski sums of coordinate simplices or hypersimplices~\cite{Postnikov}, and in particular for matroid polytopes~\cite{ArdilaBenedettiDoker}.
 It would be interesting to get such volume formulas for polytopal realizations of $\b{g}$-vector fans of cluster algebras and gentle algebras, and combinatorial interpretations for their coefficients.
@@
 \end{proof}
+
+\arnau{Change $\b{f}_{(a,b)}$ to $\b{h}_{(a,b)}$? (To homogenize with previous sections)}
 
@@
 \item The tubes~$\tube$ and~$\tube'$ are exchangeable if and only if $\tube'$ has a unique neighbor~$v$ in~$\tube \ssm \tube'$ and $\tube$ has a unique neighbor~$v'$ in~$\tube' \ssm \tube$.
-\item For any maximal tubings~$\tubing, \tubing$ on~$\graphG$ with $\tubing \ssm \{\tube\} = \tubing' \ssm \{\tube'\}$, both~$\tubing \cup \connectedComponents(\graphG)$ and~$\tubing' \cup \connectedComponents(\graphG)$ contain the tube~$\tube \cup \tube'$ and the connected components of~$\tube \cap \tube'$.
+\item For any maximal tubings~$\tubing, \tubing'$ on~$\graphG$ with $\tubing \ssm \{\tube\} = \tubing' \ssm \{\tube'\}$, both~$\tubing \cup \connectedComponents(\graphG)$ and~$\tubing' \cup \connectedComponents(\graphG)$ contain the tube~$\tube \cup \tube'$ and the connected components of~$\tube \cap \tube'$.
 \item The linear dependence between the $\b{g}$-vectors of~$\tubing \cup \tubing'$ is given by
@@
 \begin{proof}
-Consider an exchangeable pair~$\{\tube, \tube'\}$ of tubes of~$\graphG$ and let~$p = |\tube \cup \tube'|$.
-By \cref{prop:exchangeablePairsGA}, $\tube'$ has a unique neighbor~$v$ in~$\tube \ssm \tube'$ and $\tube$ has a unique neighbor~$v'$ in~$\tube' \ssm \tube$.
-Therefore, $\tube \ssm \tube'$ and~$\tube' \ssm \tube$ are both connected.
-We can thus label the elements of~$\tube \cup \tube'$ by~$\{v_1, \dots, v_p\}$ such that~$\{v_k, \dots, v_\ell\}$ induces a tube~$\tube_{k,\ell}$ of~$\graphG$ for any~$1 \le k \le \ell \le p$. 
-The map~$[k,\ell] \mapsto \tube_{k,\ell}$ is thus an injection from the tubes of the path~$\graphG[P]_p$ to that of~$\graphG$ that fulfills
-\begin{itemize}
-\item $\tube_{k,\ell-1} \ssm \{v_k\} = \tube_{k+1,\ell} \ssm \{v_\ell\}$ for any~$1 \le k \le \ell \le p$, and
-\item $\gvector{\tube_{k,\ell}} = M\gvector{[k,\ell]}$ for any~$1 \le k \le \ell \le p$, where~$M$ is the matrix sending~$\b{e}_m$ to~$\b{e}_{v_m}$.
-\end{itemize}
-Therefore, this map transports the linear combinations of \cref{prop:extremalExchangeablePairsA}.
-We conclude that the exchange relation corresponding to the exchangeable pair~$\{\tube, \tube'\}$ is a positive linear combination of the exchange relations corresponding to the pairs~$\{\tube_{k,\ell-1}, \tube_{k+1,\ell}\}$ for all~${(k,\ell) \in {[1, p-|\tube'|+1[} \times {]|\tube|, p]}}$.
-
-We now need to show that all these pairs are extremal.
+% Consider an exchangeable pair~$\{\tube, \tube'\}$ of tubes of~$\graphG$ and let~$p = |\tube \cup \tube'|$.
+% By \cref{prop:exchangeablePairsGA}, $\tube'$ has a unique neighbor~$v$ in~$\tube \ssm \tube'$ and $\tube$ has a unique neighbor~$v'$ in~$\tube' \ssm \tube$.
+% Therefore, $\tube \ssm \tube'$ and~$\tube' \ssm \tube$ are both connected.
+% We can thus label the elements of~$\tube \cup \tube'$ by~$\{v_1, \dots, v_p\}$ such that~$\{v_k, \dots, v_\ell\}$ induces a tube~$\tube_{k,\ell}$ of~$\graphG$ for any~$1 \le k \le \ell \le p$. 
+% The map~$[k,\ell] \mapsto \tube_{k,\ell}$ is thus an injection from the tubes of the path~$\graphG[P]_p$ to that of~$\graphG$ that fulfills
+% \begin{itemize}
+% \item $\tube_{k,\ell-1} \ssm \{v_k\} = \tube_{k+1,\ell} \ssm \{v_\ell\}$ for any~$1 \le k \le \ell \le p$, and
+% \item $\gvector{\tube_{k,\ell}} = M\gvector{[k,\ell]}$ for any~$1 \le k \le \ell \le p$, where~$M$ is the matrix sending~$\b{e}_m$ to~$\b{e}_{v_m}$.
+% \end{itemize}
+% Therefore, this map transports the linear combinations of \cref{prop:extremalExchangeablePairsA}.
+% We conclude that the exchange relation corresponding to the exchangeable pair~$\{\tube, \tube'\}$ is a positive linear combination of the exchange relations corresponding to the pairs~$\{\tube_{k,\ell-1}, \tube_{k+1,\ell}\}$ for all~${(k,\ell) \in {[1, p-|\tube'|+1[} \times {]|\tube|, p]}}$.
+% 
+% We now need to show that all these pairs are extremal.
 \vincent{TODO}
+\arnau{The proof had a bug. TODO.}
 \end{proof}
@@
 \label{coro:extremalExchangeablePairsGA}
-The extremal exchangeable pairs for the nested fan of~$\graphG$ are equivalently
-\begin{enumerate}[(i)]
-\item the pairs of tubes~$\tube[r] \cup \{v\}$ and~$\tube[r] \cup \{v'\}$ for any tube~$\tube[r] \in \tubes$ and distinct neighbors~$v,v'$ of~$\tube[r]$,
-\item the pairs of tubes~$\tube[s] \ssm \{v'\}$ and~$\tube[s] \ssm \{v\}$ for any tube~$\tube[s] \in \tubes$ and distinct non-disconnecting vertices~$v,v'$ of~$\tube[s]$,
-\end{enumerate}
+The extremal exchangeable pairs for the nested fan of~$\graphG$ are the pairs of tubes~$\tube[s] \ssm \{v'\}$ and~$\tube[s] \ssm \{v\}$ for any tube~$\tube[s] \in \tubes$ and distinct non-disconnecting vertices~$v,v'$ of~$\tube[s]$.
+% equivalently
+% \begin{enumerate}[(i)]
+% \item the pairs of tubes~$\tube[r] \cup \{v\}$ and~$\tube[r] \cup \{v'\}$ for any tube~$\tube[r] \in \tubes$ and distinct neighbors~$v,v'$ of~$\tube[r]$,
+% \item the pairs of tubes~$\tube[s] \ssm \{v'\}$ and~$\tube[s] \ssm \{v\}$ for any tube~$\tube[s] \in \tubes$ and distinct non-disconnecting vertices~$v,v'$ of~$\tube[s]$,
+% \end{enumerate}
 \end{corollary}
+\arnau{The two conditions were not equivalent. I removed the wrong one.}
 
@@
 \begin{corollary}
-Consider a graph~$\graphG$ on~$\ground$ with tubes~$\tubes$ and a height vector~$\b{h} \in \R^{\tubes}$ such that~$\b{h}_{\varnothing} = \b{h}_{\graphG} = 0$ and satisfying one of the two following equivalent conditions:
-\begin{enumerate}[(i)]
-\item $\b{h}_{\tube[r] \cup \{v\}} + \b{h}_{\tube[r] \cup \{v'\}} > \b{h}_{\tube[r] \cup \{v, v'\}} + \b{h}_{\tube[r]}$ for any tube~$\tube[r] \in \tubes$ and distinct neighbors~$v,v'$ of~$\tube[r]$,
-\item $\b{h}_{\tube[s] \ssm \{v'\}} + \b{h}_{\tube[s] \ssm \{v\}} > \b{h}_{\tube[s]} + \b{h}_{\tube[s] \ssm \{v, v'\}}$ for any tube~$\tube[s] \in \tubes$ and distinct non-disconnecting vertices~$v,v'$ of~$\tube[s]$.
-\end{enumerate}
+Consider a graph~$\graphG$ on~$\ground$ with tubes~$\tubes$ and a height vector~$\b{h} \in \R^{\tubes}$ such that~$\b{h}_{\varnothing} = \b{h}_{\graphG} = 0$ and satisfying 
+ $\b{h}_{\tube[s] \ssm \{v'\}} + \b{h}_{\tube[s] \ssm \{v\}} > \b{h}_{\tube[s]} + \b{h}_{\tube[s] \ssm \{v, v'\}}$ for any tube~$\tube[s] \in \tubes$ and distinct non-disconnecting vertices~$v,v'$ of~$\tube[s]$.
+% one of the two following equivalent conditions:
+% \begin{enumerate}[(i)]
+% \item $\b{h}_{\tube[r] \cup \{v\}} + \b{h}_{\tube[r] \cup \{v'\}} > \b{h}_{\tube[r] \cup \{v, v'\}} + \b{h}_{\tube[r]}$ for any tube~$\tube[r] \in \tubes$ and distinct neighbors~$v,v'$ of~$\tube[r]$,
+% \item $\b{h}_{\tube[s] \ssm \{v'\}} + \b{h}_{\tube[s] \ssm \{v\}} > \b{h}_{\tube[s]} + \b{h}_{\tube[s] \ssm \{v, v'\}}$ for any tube~$\tube[s] \in \tubes$ and distinct non-disconnecting vertices~$v,v'$ of~$\tube[s]$.
+% \end{enumerate}
+
 Then the nested fan~$\gvectorFan[\graphG]$ is the normal fan of the graph associahedron

### 2019-05-10 thirdPaper/draft/typeConeAssociahedra.tex
fixing a bug in graph associahedra, work in progress

@@
 \text{diagonals} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalA1}}  & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalA2}} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalA3}} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalA4}} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalA5}} \\[.3cm]
-\text{$\b{g}$-vectors} & \compactVectorD{1}{0} & \compactVectorD{0}{1} & \compactVectorD{1}{-1} & \compactVectorD{-1}{0} & \compactVectorD{0}{-1} \\[.6cm]
+\text{$\b{g}$-vectors} & \compactVectorD{1}{0} & \compactVectorD{0}{1} & \compactVectorD{-1}{1} & \compactVectorD{-1}{0} & \compactVectorD{0}{-1} \\[.6cm]
 \text{facet}		& 1 & -1 & 1 & 0 & 0 & \red \circled{A} \\
@@
 
+\arnau{I think the coordinates of the g-vector corresponding to {diagonalA3} were wrong, and I swapped them. }
+
+\arnau{When writing the coordinates of the g's, we cannot follow \cref{thm:normalFanLoday}, because we don't say which basis have we chosen for the hyperplane.}
 \medskip
@@
 \begin{proof}
-% Consider an exchangeable pair~$\{\tube, \tube'\}$ of tubes of~$\graphG$ and let~$p = |\tube \cup \tube'|$.
-% By \cref{prop:exchangeablePairsGA}, $\tube'$ has a unique neighbor~$v$ in~$\tube \ssm \tube'$ and $\tube$ has a unique neighbor~$v'$ in~$\tube' \ssm \tube$.
-% Therefore, $\tube \ssm \tube'$ and~$\tube' \ssm \tube$ are both connected.
-% We can thus label the elements of~$\tube \cup \tube'$ by~$\{v_1, \dots, v_p\}$ such that~$\{v_k, \dots, v_\ell\}$ induces a tube~$\tube_{k,\ell}$ of~$\graphG$ for any~$1 \le k \le \ell \le p$. 
-% The map~$[k,\ell] \mapsto \tube_{k,\ell}$ is thus an injection from the tubes of the path~$\graphG[P]_p$ to that of~$\graphG$ that fulfills
-% \begin{itemize}
-% \item $\tube_{k,\ell-1} \ssm \{v_k\} = \tube_{k+1,\ell} \ssm \{v_\ell\}$ for any~$1 \le k \le \ell \le p$, and
-% \item $\gvector{\tube_{k,\ell}} = M\gvector{[k,\ell]}$ for any~$1 \le k \le \ell \le p$, where~$M$ is the matrix sending~$\b{e}_m$ to~$\b{e}_{v_m}$.
-% \end{itemize}
-% Therefore, this map transports the linear combinations of \cref{prop:extremalExchangeablePairsA}.
-% We conclude that the exchange relation corresponding to the exchangeable pair~$\{\tube, \tube'\}$ is a positive linear combination of the exchange relations corresponding to the pairs~$\{\tube_{k,\ell-1}, \tube_{k+1,\ell}\}$ for all~${(k,\ell) \in {[1, p-|\tube'|+1[} \times {]|\tube|, p]}}$.
-% 
-% We now need to show that all these pairs are extremal.
-\vincent{TODO}
-\arnau{The proof had a bug. TODO.}
+Consider an exchangeable pair~$\{\tube, \tube'\}$ of tubes of~$\graphG$.
+The outer normal vector of the corresponding inequality of the type cone is
+\[
+\b{n}(\tube, \tube') \eqdef \b{f}_{\tube} + \b{f}_{\tube'} - \b{f}_{\tube\cup \tube'} - \sum_{\tube[s] \in \connectedComponents(\tube \cap \tube')} \b{f}_{\tube[s]}.
+\]
+
+By \cref{prop:exchangeablePairsGA}, $\tube'$ has a unique neighbor~$v$ in~$\tube \ssm \tube'$ and $\tube$ has a unique neighbor~$v'$ in~$\tube' \ssm \tube$.
+Therefore, $\tube \ssm \tube'$ and~$\tube' \ssm \tube$ are both connected.
+Assume that $\tube \ssm \tube'\neq \{v\}$, and let $w\neq v$ be a non-disconnecting node of $\tube \ssm \tube'$.
+Then $\tilde \tube:=\tube \ssm \{w\}$ and $\tube'$ are exchangeable, and $\tilde \tube':=(\tube \cup \tube')\ssm \{w\}$ and $\tube$ are exchangeable as well.
+We have
+\begin{align*}
+\b{n}(\tilde \tube, \tube')+\b{n}( \tube, \tilde \tube') &=\b{f}_{\tilde \tube} + \b{f}_{\tube'} - \b{f}_{\tilde \tube\cup \tube'} - \sum_{\tube[s] \in \connectedComponents(\tilde \tube \cap \tube')} \b{f}_{\tube[s]}
++ \b{f}_{\tube} + \b{f}_{\tilde \tube'} - \b{f}_{\tube\cup \tilde \tube'} - \sum_{\tube[s] \in \connectedComponents(\tube \cap \tilde \tube')} \b{f}_{\tube[s]} \\
+&= \b{f}_{\tube} + \b{f}_{\tube'} - \b{f}_{\tube\cup \tube'} - \sum_{\tube[s] \in \connectedComponents(\tube \cap \tube')} \b{f}_{\tube[s]} =\b{n}(\tube, \tube'),
+\end{align*}
+as $\tube \cup \tilde \tube'=\tube \cup \tube'$, $\tilde \tube \cap \tube'=\tube \cap \tube'$, $\tilde \tube \cup \tube '=\tilde \tube '$,  and $\tube \cap \tilde \tube '=\tilde \tube$.
+% \[\b{n}(\tube, \tube')=\b{n}(\tilde \tube, \tube')+\b{n}( \tube, \tilde \tube'),\] 
+Therefore $\b{n}(\tube, \tube')$ defines a redundant inequality and $\{\tube, \tube'\}$ is not an extremal exchangeable pair.
+
+We have seen that $\{\tube, \tube'\}$ do not form an extremal pair unless both $\tube\ssm \tube'$ and $\tube'\ssm \tube$ are singletons. We now need to show that all these pairs are extremal.
+
+Assume that~$\tube=\tube[s] \ssm \{v'\}$ and~$\tube'=\tube[s] \ssm \{v\}$ for some tube~$\tube[s] \in \tubes$ and distinct non-disconnecting vertices~$v,v'$ of~$\tube[s]$. 
+To prove that this pair is extremal, consider the vector $\b{z}\in\R^{\tubes}$ with 
+\[\b{z}_{\tube[u]}=\big|\set{\tube[u]'\in \tubes\}}{\tube[u]'\not\subseteq \tube[u]\text{ and } \{v,v'\}\not\subseteq\tube[u]'}\big|\]
+for each tube~$\tube[u]\in\tubes$.
+
+Notice that $\b{z}$ verifies 
+\[\b{z}_{\tube} + \b{z}_{\tube'} - \b{z}_{\tube\cup \tube'} - \sum_{\tube[s] \in \connectedComponents(\tube \cap \tube')} \b{z}_{\tube[s]}= 0\]
+but \[\b{z}_{\tilde \tube} + \b{z}_{\tilde \tube'} - \b{z}_{\tilde \tube\cup \tilde \tube'} - \sum_{\tube[s] \in \connectedComponents(\tilde \tube \cap \tilde \tube')} \b{z}_{\tube[s]}> 0\]
+for any other exchangeable pair~$\{\tilde\tube,\tilde \tube '\}$. 
+\arnau{Verify and write more details}
+
+Thus, $\b{z}$ lies in the relative interior of the facet of the closed type cone defined by~$\{\tube, \tube'\}$, and hence the inequality is not redundant.
 \end{proof}

### 2019-05-15 thirdPaper/draft/typeConeAssociahedra.tex
working on graph associahedra

@@
 
-\begin{proposition}
-\label{prop:extremalExchangeablePairsGA}
-Two tubes~$\tube$ and~$\tube'$ of~$\graphG$ form an extremal exchangeable pair for the nested fan of~$\graphG$ if and only if~${\tube \ssm \{v\} = \tube' \ssm \{v'\}}$ for some neighbor~$v$ of~$\tube'$ and some neighbor~$v'$ of~$\tube$.
-\end{proposition}
+\begin{lemma}
+\label{lem:extremalExchangeablePairsGAonlyif}
+Two tubes~$\tube$ and~$\tube'$ of~$\graphG$ form an extremal exchangeable pair for the nested fan of~$\graphG$ only if~${\tube \ssm \{v\} = \tube' \ssm \{v'\}}$ for some neighbor~$v$ of~$\tube'$ and some neighbor~$v'$ of~$\tube$.
+\end{lemma}
 
@@
 Therefore $\b{n}(\tube, \tube')$ defines a redundant inequality and $\{\tube, \tube'\}$ is not an extremal exchangeable pair.
+\end{proof}
+
+\begin{example}
+Let $\graphG$ be a graph. Consider the vectors $\b{a}, \b{b}, \b{c}\in\R^{\tubes}$ whose entries for $\tube[s]\in\tubes$ are given by 
+$\b{a}_{\tube[s]}=-\big| \set{\tube[u]\in\tubes}{\tube[u]\subseteq \tube[s]}\big| $, $\b{b}_{\tube[s]}=-3^{\big| \tube[s]\big| -2}$, and $\b{c}_{\tube[s]}=-\big| \set{\tube[u]\in\tubes}{\tube[u]\supseteq \tube[s]}\big| $, respectively.
+
+Now, let $\tube$ and~$\tube'$ be tubes such that ${\tube \ssm \{v\} = \tube' \ssm \{v'\}}$ for some neighbor~$v$ of~$\tube'$ and some neighbor~$v'$ of~$\tube$, and let 
+$\b{n}(\tube, \tube')$ be as in~\cref{lem:extremalExchangeablePairsGAonlyif}.
+
+We have
+\[\dotprod{\b{n}(\tube, \tube')}{\b{a}}=\big|\set{\tube[u]\in\tubes}{\tube[u]\subseteq\tube[t]\cup\tube[t']\text{ and }v,v'\in\tube[u]}|,\]
+which is positive since at least $\tube[u]=\tube[t]\cup\tube[t']$ fulfills this condition.
+Hence $\b{a}\in\typeCone(\gvectorFan[\graphG])$.
+This gives Postnikov's realization of the graph associahedron from~\cite{Postnikov}.
+
+Setting $x=|\tube \cap \tube'|$, we get
+\[\dotprod{\b{n}(\tube, \tube')}{\b{b}}=3^{|\tube[t]\cup\tube[t']| -2}- 3^{|\tube[t]| -2}- 3^{|\tube[t']| -2} +\sum_{\tube[s] \in \connectedComponents(\tube \cap \tube')} 3^{|\tube[s]|-2 }\geq 3^{x}- 2\cdot 3^{x-1}>0.\]
+This shows that $\b{b}\in\typeCone(\gvectorFan[\graphG])$, and we recover Devadoss' realization of graph-associahedra~\cite{Devadoss}.
+
+Finally, 
+\[\dotprod{\b{n}(\tube, \tube')}{\b{c}}=\big| \set{(\tube[u], \tube[s])\in\tubes\times \connectedComponents(\tube[t]\cap\tube[t'])}{\tube[s]\subseteq\tube[u]\text{ and }\tube,\tube'\not\subseteq u}\big| +(\big| \connectedComponents(\tube[t]\cap\tube[t'])\big| -1)\big| \set{\tube[u]\in\tubes}{\tube\text{ or }\tube'\subseteq \tube[u]}\big| .\]
+Any connected component of $\tube\cap \tube'$ certifies the positivity of this evaluation, showing that $\b{c}\in\typeCone(\gvectorFan[\graphG])$. This realization of 
+the graph-associahedron is new, to the best of our knowledge. 
+\arnau{Is it worth to add it?}
+\arnau{recheck details}
+
+\end{example}
+
+\begin{proposition}
+\label{prop:extremalExchangeablePairsGA}
+Two tubes~$\tube$ and~$\tube'$ of~$\graphG$ form an extremal exchangeable pair for the nested fan of~$\graphG$ if and only if~${\tube \ssm \{v\} = \tube' \ssm \{v'\}}$ for some neighbor~$v$ of~$\tube'$ and some neighbor~$v'$ of~$\tube$.
+\end{proposition}
+
+\begin{proof}
 
@@
 Assume that~$\tube=\tube[s] \ssm \{v'\}$ and~$\tube'=\tube[s] \ssm \{v\}$ for some tube~$\tube[s] \in \tubes$ and distinct non-disconnecting vertices~$v,v'$ of~$\tube[s]$.
-To prove that this pair is extremal, consider the vector $\b{z}\in\R^{\tubes}$ with 
-\[\b{z}_{\tube[u]}=\big|\set{\tube[u]'\in \tubes\}}{\tube[u]'\not\subseteq \tube[u]\text{ and } \{v,v'\}\not\subseteq\tube[u]'}\big|\]
-for each tube~$\tube[u]\in\tubes$.
-
-Notice that $\b{z}$ verifies 
-\[\b{z}_{\tube} + \b{z}_{\tube'} - \b{z}_{\tube\cup \tube'} - \sum_{\tube[s] \in \connectedComponents(\tube \cap \tube')} \b{z}_{\tube[s]}= 0\]
-but \[\b{z}_{\tilde \tube} + \b{z}_{\tilde \tube'} - \b{z}_{\tilde \tube\cup \tilde \tube'} - \sum_{\tube[s] \in \connectedComponents(\tilde \tube \cap \tilde \tube')} \b{z}_{\tube[s]}> 0\]
-for any other exchangeable pair~$\{\tilde\tube,\tilde \tube '\}$. 
-\arnau{Verify and write more details}
-
-Thus, $\b{z}$ lies in the relative interior of the facet of the closed type cone defined by~$\{\tube, \tube'\}$, and hence the inequality is not redundant.
+To prove that this pair is extremal, we will construct a vector $\b{z}\in\R^{\tubes}$ such that \[\dotprod{\b{n}(\tube, \tube')}{\b{z}}=0,\]
+but \[\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{z}}>0\] for any other pair $\{\tilde \tube, \tilde \tube'\}$ verifying the conditions.
+This will show that $\b{z}$ lies in the relative interior of the facet of the closed type cone defined by~$\{\tube, \tube'\}$, and hence that the inequality is not redundant.
+
+\arnau{TODO! I have a partial construction, but there are still some undesired $\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{z}}=0$}
+
+Define $\alpha(\tube,\tube')=\set{\tube[u]\in\tubes}{\tube[u]\subseteq \tube \cup \tube'\text{ and } v,v'\in \tube[u]}$, and set 
+\[\b{z}_{\tube[s]}=-\big|\set{\tube[u]\in \tubes\ssm \alpha(\tube,\tube')\}}{\tube[u]\subseteq \tube[s]}\big|\]
+for each tube~$\tube[s]\in\tubes$.
+
+Notice that $\dotprod{\b{n}(\tube, \tube')}{\b{z}}=0$, and that 
+\[\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{z}}= \big|\set{\tube[u]\in\tubes}{\tube[u]\subseteq\tube[t]\cup\tube[t']\text{ and }\tilde v,\tilde v'\in\tube[u]}\ssm \alpha(\tube,\tube')|\geq0,\]
+where $\tilde v=\tilde \tube\ssm \tilde \tube'$  and $\tilde v'=\tilde \tube'\ssm \tilde \tube$.
+In particular, if $\tilde \tube\cup \tilde \tube'\notin\alpha(\tube,\tube')$ then $\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{z}}>0$.
+
+\arnau{To finish. How to separate the remaining cases?}
+
 \end{proof}
@@
 We derive from~\cref{coro:extremalExchangeablePairsGA} the number of extremal exchangeable pairs of the nested fan.
-For a tube~$\tube$ of~$\graphG$, we denote by~$\neighbors(\tube)$ the number of neighbors of~$\tube$ and by~$\nonDisconnecting(\tube)$ the number of non-disconnecting vertices of~$\tube$.
-In other words, it $\neighbors(\tube)$ (resp.~$\nonDisconnecting(\tube)$) is the number of tubes covering~$\tube$ (resp.~covered by~$\tube$) in the inclusion poset of all tubes of~$\graphG$.
+For a tube~$\tube$ of~$\graphG$, we denote 
+%by~$\neighbors(\tube)$ the number of neighbors of~$\tube$ and
+ by~$\nonDisconnecting(\tube)$ the number of non-disconnecting vertices of~$\tube$.
+% In other words, it $\neighbors(\tube)$ (resp.~$\nonDisconnecting(\tube)$) is the number of tubes covering~$\tube$ (resp.~covered by~$\tube$) in the inclusion poset of all tubes of~$\graphG$.
+In other words, $\nonDisconnecting(\tube)$ is the number of tubes covered by~$\tube$ in the inclusion poset of all tubes of~$\graphG$.
 
@@
 \label{coro:numberExtremalExchangeablePairsGA}
-The nested fan~$\gvectorFan[\graphG]$ has~$\!\!\!\!
-\sum\limits_{\tube[r] \in \tubes} \!\!
-\binom{\neighbors(\tube[r])}{2} = \!\!\!\!
-\sum\limits_{\tube[s] \in \tubes} \!\!
-\binom{\nonDisconnecting(\tube[s])}{2}$ extremal exchangeable pairs.
+The nested fan~$\gvectorFan[\graphG]$ 
+has~$\!\!\!\! \sum\limits_{\tube[s] \in \tubes} \!\! \binom{\nonDisconnecting(\tube[s])}{2}$ 
+% $\!\!\!\! \sum\limits_{\tube[r] \in \tubes} \!\! \binom{\neighbors(\tube[r])}{2} = \!\!\!\! \sum\limits_{\tube[s] \in \tubes} \!\! \binom{\nonDisconnecting(\tube[s])}{2}$ 
+extremal exchangeable pairs.
 \end{corollary}

### 2019-05-17 thirdPaper/draft/typeConeAssociahedra.tex
fixed missing part of graph associahedra

@@
 
-We have seen that $\{\tube, \tube'\}$ do not form an extremal pair unless both $\tube\ssm \tube'$ and $\tube'\ssm \tube$ are singletons. We now need to show that all these pairs are extremal.
-
-Assume that~$\tube=\tube[s] \ssm \{v'\}$ and~$\tube'=\tube[s] \ssm \{v\}$ for some tube~$\tube[s] \in \tubes$ and distinct non-disconnecting vertices~$v,v'$ of~$\tube[s]$.
-To prove that this pair is extremal, we will construct a vector $\b{z}\in\R^{\tubes}$ such that \[\dotprod{\b{n}(\tube, \tube')}{\b{z}}=0,\]
-but \[\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{z}}>0\] for any other pair $\{\tilde \tube, \tilde \tube'\}$ verifying the conditions.
-This will show that $\b{z}$ lies in the relative interior of the facet of the closed type cone defined by~$\{\tube, \tube'\}$, and hence that the inequality is not redundant.
-
-\arnau{TODO! I have a partial construction, but there are still some undesired $\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{z}}=0$}
-
-Define $\alpha(\tube,\tube')=\set{\tube[u]\in\tubes}{\tube[u]\subseteq \tube \cup \tube'\text{ and } v,v'\in \tube[u]}$, and set 
-\[\b{z}_{\tube[s]}=-\big|\set{\tube[u]\in \tubes\ssm \alpha(\tube,\tube')\}}{\tube[u]\subseteq \tube[s]}\big|\]
+We have seen that an exchangeable pair $\{\tube, \tube'\}$ is not extremal unless both $\tube\ssm \tube'$ and $\tube'\ssm \tube$ are singletons.
+We now need to show that all these pairs are extremal.
+Until we finish the proof, we will call such a pair a \defn{suspected extremal pair}.
+
+Let $\{\tube, \tube'\}$ be a suspected extremal pair.
+To prove that it is extremal, we will construct a vector $\b{w}\in\R^{\tubes}$ such that $\dotprod{\b{n}(\tube, \tube')}{\b{w}}< 0,$
+but $\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{w}}>0$ for any other suspected extremal pair $\{\tilde \tube, \tilde \tube'\}$.
+This will show that the inequality induced by~$\{\tube, \tube'\}$ is not redundant.
+
+Define $\alpha(\tube,\tube')=\set{\tube[u]\in\tubes}{\tube[u]\subseteq \tube \cup \tube'\text{ and } \tube\triangle\tube'\subseteq \tube[u]}$, where $\tube\triangle\tube'$ denotes the symmetric difference, and let $\b{x}\in\R^{\tubes}$ be such that
+\[\b{x}_{\tube[s]}=-\big|\set{\tube[u]\in \tubes\ssm \alpha(\tube,\tube')}{\tube[u]\subseteq \tube[s]}\big|\]
 for each tube~$\tube[s]\in\tubes$.
 
-Notice that $\dotprod{\b{n}(\tube, \tube')}{\b{z}}=0$, and that 
-\[\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{z}}= \big|\set{\tube[u]\in\tubes}{\tube[u]\subseteq\tube[t]\cup\tube[t']\text{ and }\tilde v,\tilde v'\in\tube[u]}\ssm \alpha(\tube,\tube')|\geq0,\]
-where $\tilde v=\tilde \tube\ssm \tilde \tube'$  and $\tilde v'=\tilde \tube'\ssm \tilde \tube$.
-In particular, if $\tilde \tube\cup \tilde \tube'\notin\alpha(\tube,\tube')$ then $\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{z}}>0$.
-
-\arnau{To finish. How to separate the remaining cases?}
+For any suspected extremal pair $\{\tilde \tube, \tilde \tube'\}$ we have
+\[\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{x}}= \big|\alpha(\tilde \tube, \tilde \tube ')\ssm \alpha(\tube,\tube')|\geq0.\]
+Notice that $\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{x}}=0$ if $\alpha(\tilde \tube, \tilde \tube ')\subseteq \alpha(\tube,\tube')$ and
+$\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{x}}\geq 1$ otherwise.
+In particular, if $\{\tilde \tube, \tilde \tube'\}\neq \{\tube, \tube'\}$ then
+$\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{x}}\geq 1$ unless $\tilde \tube\cup \tilde \tube'\subsetneq \tube\cup \tube'$ because 
+ $\tilde \tube\cup \tilde \tube'\in\alpha(\tilde \tube, \tilde \tube ')$, and if $\tilde \tube\cup \tilde \tube'=\tube\cup \tube'$ but $\{\tilde \tube, \tilde \tube'\}\neq \{\tube, \tube'\}$, then either $\tube$ or $\tube'$ will belong to $\alpha(\tilde \tube, \tilde \tube ')$.
+
+Now, define $\b{y}\in\R^{\tubes}$ by \[\b{y}_{\tube[s]}=\begin{cases}
+                             -1&\text{ if }|\tube[s]|\geq |\tube|\\
+                             0&\text{ otherwise.}
+                            \end{cases}\]
+We have $\dotprod{\b{n}(\tube, \tube')}{\b{y}}=-1$.
+For any suspected extremal pair $\{\tilde \tube, \tilde \tube'\}$ we have $\dotprod{\b{n}(\tube, \tube')}{\b{y}}\geq -1$.
+If moreover $\tilde \tube\cup \tilde \tube'\subsetneq \tube\cup \tube'$, then we have $\dotprod{\b{n}(\tube, \tube')}{\b{y}}\geq 0$.
+
+Finally, consider $\b{z}\in\R^{\tubes}$ given by
+\[\b{z}_{\tube[s]}=-\big|\set{\tube[u]\in \alpha(\tube,\tube')}{\tube[u]\subseteq \tube[s]}\big|. \]
+It verifies $\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{z}}\geq0$ for any suspected extremal pair~$\{\tilde \tube, \tilde \tube'\}$, and $\dotprod{\b{n}(\tube, \tube')}{\b{z}}=|\alpha(\tilde \tube, \tilde \tube ')|>0$ if $\alpha(\tilde \tube, \tilde \tube ')\subseteq \alpha(\tube,\tube')$.
+
+For $0<\varepsilon<1$, and $0<\delta<\frac{\varepsilon}{|\alpha(\tube,\tube')|}$, the vector $\b{w}=\b{x}+\varepsilon \b{y}+\delta \b{z}$ fulfills the desired properties.
+Indeed, if $\{\tilde \tube, \tilde \tube'\}\neq \{\tube,\tube '\}$ is a suspected extremal pair with $\alpha(\tilde \tube, \tilde \tube ')\not \subseteq \alpha(\tube,\tube')$, then 
+\[\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{w}}=\underbrace{\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{x}}}_{\geq 1}+\underbrace{\varepsilon \dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{y}}}_{> -1}+\underbrace{\delta \dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{z}}}_{\geq 0}> 0.\]
+ If $\{\tilde \tube, \tilde \tube'\}\neq \{\tube,\tube '\}$ is a suspected extremal pair with $\alpha(\tilde \tube, \tilde \tube ')\subseteq \alpha(\tube,\tube')$, then $\tilde \tube\cup \tilde \tube'\subsetneq \tube\cup \tube'$ and
+\[\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{w}}=\underbrace{\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{x}}}_{=0}+\underbrace{\varepsilon \dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{y}}}_{\geq 0}+\underbrace{\delta \dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{z}}}_{>0}> 0.\]
+However,
+\[\dotprod{\b{n}(\tube, \tube')}{\b{w}}=\underbrace{\dotprod{\b{n}(\tube, \tube')}{\b{x}}}_{=0}+\underbrace{\varepsilon \dotprod{\b{n}(\tube, \tube')}{\b{y}}}_{=-\varepsilon}+\underbrace{\delta \dotprod{\b{n}( \tube,  \tube')}{\b{z}}}_{=\delta|\alpha(\tube ,\tube')|<\varepsilon}< 0.\]
 
@@
 
-We derive from \cref{prop:extremalExchangeablePairsGA} and \cref{coro:extremalExchangeablePairsGA} all polytopal realizations of the nested fan, which we can explicitly express using one of the following two equivalent conditions.
+We derive from \cref{prop:extremalExchangeablePairsGA} and \cref{coro:extremalExchangeablePairsGA} all polytopal realizations of the nested fan, which we can explicitly express.
+% using one of the following two equivalent conditions.
 
@@
 \begin{proof}
-Note that any tube~$\tube$ with~$|\tube| \ge 2$ has two non-disconnecting vertices when it is a path, and at least three non-disconnecting vertices otherwise (the leaves of an arbitrary spanning tree of~$\tube$).
-Therefore, each tube of~$\tubes$ which is not a singleton contributes to at least one extremal exchangeable pairs.
+Note that any tube~$\tube$ with~$|\tube| \ge 2$ has two non-disconnecting vertices when it is a path, and at least three non-disconnecting vertices otherwise (the leaves of an arbitrary spanning tree of~$\tube$, or any vertex if it is a cycle).
+Therefore, each tube of~$\tubes$ which is not a singleton contributes to at least one extremal exchangeable pair.
 We conclude that the number of extremal exchangeable pairs is at least:

### 2019-05-23 thirdPaper/draft/typeConeAssociahedra.tex
defn mutation conflation

@@
 Proposition~\ref{prop::2kbproj-is-extriangulated} gives a setting in which to apply Theorem~\ref{}.
+Before stating our next theorem, we first recall some definitions
+
+\begin{definition}
+Recall that a two-term silting object is a complex~$T$ in~$K^{[-1,0]}(\proj \Lambda)$ such that~$\Hom{K^b}(T,\susp T)=0$ and the number of isomorphism classes of indecomposable summands of~$T$ is the same as that of~$\Lambda$.
+\end{definition}
+
+\begin{remark}
+ The definition given above is only equivalent to the usual definition of a silting object for two-term complexes of projectives.
+\end{remark}
+
+\begin{definition}\label{defn::mutation conflation}
+A conflation $X\infl E\defl Y$ of~$K^{[-1,0]}(\proj \Lambda)$ is called a \defn{mutation conflation} if there are basic, two-term, silting objects $X\oplus R$, $Y\oplus R$ such that the inflation $X\infl E$ is a left ($\add R$)-approximation (i.e.
+any morphism from~$X$ to an object in~$\add R$ factors through~$X\infl E$).
+\end{definition}
 
@@
 \label{theo::brick-algebra-condition}
- Let~$\Lambda$ be an Artin algebra all of whose non-injective indecomposable objects are bricks and all of whose indecomposable objects are~$\tau$-rigid\yann{Are there examples of representation-infinite algebras which satisfy those assumptions?}\pg{Don't think so, but can't find a proof}.
+ Let~$\Lambda$ be an Artin algebra all of whose indecomposable objects are ~$\tau$-rigid bricks.
 Then the almost-split conflations of~$K^{[-1,0]}(\proj \Lambda)$ are mutation conflations if and only if for any non-projective indecomposable~$\Lambda$-module~$M$, the space~$\Hom{\Lambda}(M, \tau^2 M)$ vanishes.
 \end{theorem}
-\pg{Should define mutation conflations}
 
@@
 % Then~$Y\infl E\defl \susp P$ is an Auslander--Reiten conflation in~$K^{[-1,0]}(\proj\Lambda)$, which is also a mutation conflation.
-Then the Auslander--Reiten conflation~$Y\infl E\defl \susp P$ in~$K^{[-1,0]}(\proj\Lambda)$ is a mutation conflation.
+Then the Auslander--Reiten conflation~$Y\infl E\defl \susp P$ in~$K^{[-1,0]}(\proj\Lambda)$ is a mutation conflation if~$FY$ is a brick.
 \end{lemma}
@@
 We then have~$f = \beta g = \beta (g-\alpha) = \beta (h-1) \alpha$.
-Since~$Y$ is endo-local, the morphism~$h-1$ is an automorphism.
+Since~$Y$ is endo-local, the morphism~$h$ or~$h-1$ is an automorphism.
 

### 2019-05-28 thirdPaper/draft/typeConeAssociahedra.tex
corrected proof of Lemma 4.50

@@
 \]
-Because~$X$ is concentrated in non-positive degrees,~$FX=0$.
+Because~$X$ is concentrated in non-positive degrees,~$F\susp X=0$.
 Let us verify that the map~$F\susp^{-1}Y\to F\susp^{-1}Z$ is surjective.
@@
 
-\begin{lemma}
+\begin{lemma}\label{lemm::if AR are mutations}
 Let~$\Lambda$ be an Artin algebra, and let~$Y\infl E\defl X$ be a conflation in~$K^{[-1,0]}(\proj\Lambda)$. Then:
@@
  \item If~$\Hom{K^b}(Y,\susp E)=0$, we have~$\Hom{\Lambda}(FX,\tau FY)=0$.
- \item If moreover~$Z\notin\add(\susp\Lambda)$ and the conflation is almost-split, then~$\Hom{\Lambda}(FX,\tau^2 FX)=0$.
+ \item If moreover~$X\notin\add(\susp\Lambda)$ and the conflation is almost-split, then~$\Hom{\Lambda}(FX,\tau^2 FX)=0$.
 \end{enumerate}
@@
 \end{lemma}
-\pg{This seems false for~$\Lambda = k[x]/(x^2)$: AR sequence~$\Lambda\to (\Lambda\to \Lambda) \to \Sigma\Lambda$.  Probably need brick algebra.}
 
@@
 
-% We first show that the conflation is almost-split.
-% 
-% blahblahblah
-
 We check that the conflation~$Y\infl E\defl\susp P$ is a mutation conflation.
@@
 (0) Since~$P$ is concentrated in only one degree, it is rigid in~~$K^{[-1,0]}(\proj\Lambda)$ and so is~$\susp P$.
-Moreover,~$FY=I$ is~$\tau$-rigid, hence~$Y$ is rigid in~$K^{[-1,0]}(\proj\Lambda)$ by~\cite[Lemma 3.4]{AdachiIyamaReiten}.
+Moreover,~$FY$ is indecomposable and injective.
+By assumption, it is~$\tau$-rigid, hence~$Y$ is rigid in~$K^{[-1,0]}(\proj\Lambda)$ by~\cite[Lemma 3.4]{AdachiIyamaReiten}.
 
@@
 
-(3) $\Hom{K^b}(E,\susp E)=0$: There is an exact sequence
-\[
- \Hom{K^b}(\susp Y,\susp E) \to \Hom{K^b}(\susp P, \susp E) \to \Hom{K^b}(E,\susp E) \to \Hom{K^b}(Y,\susp E)
-\]
-in which the last term is zero by (2).
-The first morphism is isomorphic to~$\Hom{K^b}(Y,E) \to \Hom{K^b}(P,E)$, which is surjective by the previous lemma.
-
-(4) $\Hom{K^b}(E,\susp Y) = 0$: Consider the exact sequence
-\[
- \Hom{K^b}(E,E) \to \Hom{K^b}(E,\susp P) \to \Hom{K^b}(E,\susp Y) \to \Hom{K^b}(E,\susp E).
-\]
-Its last term vanishes by (3) and its first morphism is surjective because~$E\to \susp P$ is right almost-split.
+(3) $\Hom{K^b}(E,\susp Y) = 0$: Consider the exact sequence
+\[
+ \Hom{K^b}(\susp Y,\susp Y) \to \Hom{K^b}(\susp P,\susp Y) \to \Hom{K^b}(E,\susp Y) \to \Hom{K^b}(Y,\susp Y).
+\]
+Its last term vanishes by (0).
+Let us prove that its first morphism is surjective.
+Composition with~$\alpha$ and~$F\alpha$ yields a commutative square
+\[
+\xy
+%
+(-20,7)*+{\Hom{K^b}(Y,Y)}="0";
+(20,7)*+{\Hom{K^b}(P,Y)}="2";
+(-20,-7)*+{\Hom{\Lambda}(FY,FY)}="10";
+(20,-7)*+{\Hom{\Lambda}(FP,FY)}="12";
+%
+{\ar@{->>} "0";"10"};
+{\ar^{\alpha^\ast} "0";"2"};
+{\ar@{->>} "2";"12"};
+{\ar_{(F\alpha)^\ast} "10";"12"};
+%
+{\ar@{}|\circlearrowright "0";"12"};
+\endxy
+\]
+where the vertical maps are surjective.
+Since~$\Lambda$ is rigid and~$Y$ is two-term, we can apply~\cite[Proposition 6.2]{IyamaYoshino} to the triangulated category~$K^b(\proj\Lambda)$ (or Proposition~\ref{prop::KRextricat} to the extriangulated~$K^{[-1,0]}(\proj\Lambda)$).
+As a consequence, the right-most vertical map is bijective.
+Because~$FY$ is a brick,~$\End{\Lambda}(FY)$ is a division ring.
+Moreover,~$FY$ is the indecomposable injective with simple socle the simple top of~$P$, so that the~$\End{\Lambda}(FY)$-module~$\Hom{\Lambda}(FP,FY)$ is one-dimensional over~$\End{\Lambda}(FY)$.
+It follows that the vertical map~$(F\alpha)^\ast$ is either zero or bijective.
+But~$\alpha$ is non-zero with domain in~$\add\Lambda$ so that~$F\alpha$ is non-zero ; and~$(F\alpha)^\ast(1_{FY})=F\alpha$ so that~$(F\alpha)^\ast$ is non-zero.
+By commutativity, this implies the surjectivity of the top vertical morphism~$\alpha^\ast$.
+Since the shift functor is an automorphism, the morphism~$\Hom{K^b}(\susp Y,\susp Y) \to \Hom{K^b}(\susp P,\susp Y)$ is also surjective, and~$\Hom{K^b}(E,\susp Y) = 0$.
+
+(4) $\Hom{K^b}(E,\susp E)=0$: In the exact sequence
+\[
+ \Hom{K^b}(E,\susp Y) \to \Hom{K^b}(E, \susp E) \to \Hom{K^b}(E,\susp^2 P),
+\]
+the first term is zero by (3) and the last term vanishes since~$P$ is concentrated in degree zero.
 
@@
 Let~$P\xrightarrow{f} E$ be any morphism.
+\[
+\xy
+%
+(7,14)*+{P}="P";
+%
+(-21,0)*+{P}="0";
+(-7,0)*+{Y}="2";
+(7,0)*+{E}="4";
+(21,0)*+{\susp P}="6";
+%
+(-21,-14)*+{Y}="Y";
+(-7,-14)*+{E}="E";
+%
+{\ar^f "P";"4"};
+{\ar^0 "P";"6"};
+{\ar@{-->}_g "P";"2"};
+%
+{\ar^\alpha "0";"2"};
+{\ar^\beta "2";"4"};
+{\ar "4";"6"};
+%
+{\ar_g "0";"Y"};
+{\ar@{-->}_h "2";"Y"};
+{\ar_\beta "Y";"E"};
+{\ar_{\beta h\!} "2";"E"};
+{\ar@{-->}^{h'} "4";"E"};
+\endxy
+\]
 Since~$P$ is rigid,~$f$ factors through the inflation~$\beta$ in the conflation~$Y\infl E\defl \susp P$, and there is some morphism~$g$ such that~$f=\beta g$.
-By the previous lemma, or by (4), the morphism~$g$ factors through~$P \xrightarrow{\alpha} Y$: there is some~$h:Y\to Y$ such that~$g= h \alpha$.\pg{Fixable if~$\Lambda$ is brick? Will think more...}
-
+By (3), the morphism~$g$ factors through~$P \xrightarrow{\alpha} Y$: there is some~$h:Y\to Y$ such that~$g= h \alpha$.
 We then have~$f = \beta g = \beta (g-\alpha) = \beta (h-1) \alpha$.
-Since~$Y$ is endo-local, the morphism~$h$ or~$h-1$ is an automorphism.
-
-{\bf Small gap:} There is an~$h'$ such that~$h \alpha = \alpha h'$ and we deduce that~$f=\beta h \alpha = \beta \alpha h' = 0$.
+Since~$Y$ is endo-local, the morphism~$h$ or~$h-1$ is an automorphism, and we may assume that~$h$ is an automorphism.
+The morphism~$\beta h$ is not a section (otherwise~$\beta$ would be a section) and~$\beta$ is left-almost split: there is an endomorphism~$h'$ of~$E$ such that~$\beta h = h'\beta$.
+Therefore, we have~$f=\beta h \alpha = h'\beta\alpha = 0$.
 \end{proof}
@@
 \begin{proof}[Proof of Theorem~\ref{theo::brick-algebra-condition}]
- The theorem follows from the slightly more general statements of Lemma~\ref{lemm::then-AR-seq-are-mutation} and Lemma~\ref{lemm::initial meshes}.
+ The theorem follows from the slightly more general statements of Lemma~\ref{lemm::then-AR-seq-are-mutation},~\ref{lemm::if AR are mutations} and Lemma~\ref{lemm::initial meshes}.
 \end{proof}

### 2019-05-28 thirdPaper/draft/typeConeAssociahedra.tex
added tau-tilting in abstract

@@
 Finally, we use a similar approach to study the space of polytopal realizations of the $\b{g}$-vector fans of other generalizations of the associahedron.
-For non-kissing complexes of gentle algebras, we show that the space of realizations of the non-kissing fan is simplicial when the gentle bound quiver is brick and $2$-acyclic, and we describe in this case its facet-defining inequalities in terms of mesh mutations.
+For non-kissing complexes (a.k.a.
+support~$\tau$-tilting complexes) of gentle algebras, we show that the space of realizations of the non-kissing fan is simplicial when the gentle bound quiver is brick and $2$-acyclic, and we describe in this case its facet-defining inequalities in terms of mesh mutations.
 For graphical nested complexes, we show that the space of realizations of the nested fan is simplicial only in the case of the associahedron, and we describe its facet-defining inequalities in general.

### 2019-06-10 thirdPaper/draft/typeConeAssociahedra.tex
some changes

--- 2019-05-23 thirdPaper/draft/typeConeAssociahedra.tex
@@
 Moreover, if we decompose~$\omega = \rho \sigma \tau$ and~$\omega' = \rho' \sigma \tau'$, then the facets~$F$ and~$F'$ both contain the walks~$\mu \eqdef \rho' \sigma \tau$ and~$\nu \eqdef \rho \sigma \tau'$.
-\item The substring~$\sigma$ and thus the walks~$\mu$ and~$\nu$ actually depend on the exchangeable walks~$\omega$ and~$\omega'$, not on the adjacent non-kissing facet~$F $ and~$F'$.
+\item The substring~$\sigma$ and thus the walks~$\mu$ and~$\nu$ only depend on the exchangeable walks~$\omega$ and~$\omega'$, and not on the adjacent non-kissing facets~$F $ and~$F'$.
 \item Moreover, the linear dependence between the $\b{g}$-vectors of~$F \cup F'$ is given by
@@
 
+The extriangulated category~$K^{[-1,0]}(\proj \Lambda)$ is the setting in which we can finally prove point~(ii) of Proposition~\ref{prop:exchangeablePairsNKC}, using results of~\cite{DemonetIyamaJasso} on~$\b g$-vectors.
+
+\begin{proposition}
+ Let~$\Lambda$ be a finite-dimensional~$\field$-algebra, where~$\field$ is a field.  Let~$X$ and~$Y$ be objects of~$K^{[-1,0]}(\proj \Lambda)$.  Assume that~ 
+ Then~$E$ and~$E'$ are isomorphic.
+\end{proposition}
+\begin{proof}
+ By~\cite[Theorem 6.5]{DemonetIyamaJasso} (based on~\cite[Theorem 2.3]{DehyKeller}), rigid objects in~$K^{[-1,0]}(\proj \Lambda)$ are determined by their~$\b g$-vector.
+The datum of the~$\b g$-vector of an object of~$K^{[-1,0]}(\proj \Lambda)$ is equivalent to that of its class in the Grothendieck group~$K_0(K^{[-1,0]}(\proj \Lambda))$, where~$K^{[-1,0]}(\proj \Lambda)$ is viewed as an extriangulated category (see Proposition~\ref{2kbproj-is-extriangulated}).
+In this Grothendieck group, we have that~$[E] = [E'] = [X]+[Y]$.
+Thus~$E$ and~$E'$ are isomorphic.
+\end{proof}
+
+\begin{corollary}\label{coro::exchangeablePairsNKC}
+ Point~(ii) of Proposition~\ref{prop:exchangeablePairsNKC} holds.
+\end{corollary}
+\begin{proof}
+
+\end{proof}
+
 Proposition~\ref{prop::2kbproj-is-extriangulated} gives a setting in which to apply Theorem~\ref{}.
-Before stating our next theorem, we first recall some definitions
-
-\begin{definition}
-Recall that a two-term silting object is a complex~$T$ in~$K^{[-1,0]}(\proj \Lambda)$ such that~$\Hom{K^b}(T,\susp T)=0$ and the number of isomorphism classes of indecomposable summands of~$T$ is the same as that of~$\Lambda$.
-\end{definition}
-
-\begin{remark}
- The definition given above is only equivalent to the usual definition of a silting object for two-term complexes of projectives.
-\end{remark}
-
-\begin{definition}\label{defn::mutation conflation}
-A conflation $X\infl E\defl Y$ of~$K^{[-1,0]}(\proj \Lambda)$ is called a \defn{mutation conflation} if there are basic, two-term, silting objects $X\oplus R$, $Y\oplus R$ such that the inflation $X\infl E$ is a left ($\add R$)-approximation (i.e.
-any morphism from~$X$ to an object in~$\add R$ factors through~$X\infl E$).
-\end{definition}
 
@@
 \label{theo::brick-algebra-condition}
- Let~$\Lambda$ be an Artin algebra all of whose indecomposable objects are ~$\tau$-rigid bricks.
+ Let~$\Lambda$ be an Artin algebra all of whose non-injective indecomposable objects are bricks and all of whose indecomposable objects are~$\tau$-rigid\yann{Are there examples of representation-infinite algebras which satisfy those assumptions?}\pg{Don't think so, but can't find a proof}.
 Then the almost-split conflations of~$K^{[-1,0]}(\proj \Lambda)$ are mutation conflations if and only if for any non-projective indecomposable~$\Lambda$-module~$M$, the space~$\Hom{\Lambda}(M, \tau^2 M)$ vanishes.
 \end{theorem}
+\pg{Should define mutation conflations}
 
@@
 % Then~$Y\infl E\defl \susp P$ is an Auslander--Reiten conflation in~$K^{[-1,0]}(\proj\Lambda)$, which is also a mutation conflation.
-Then the Auslander--Reiten conflation~$Y\infl E\defl \susp P$ in~$K^{[-1,0]}(\proj\Lambda)$ is a mutation conflation if~$FY$ is a brick.
+Then the Auslander--Reiten conflation~$Y\infl E\defl \susp P$ in~$K^{[-1,0]}(\proj\Lambda)$ is a mutation conflation.
 \end{lemma}
@@
 We then have~$f = \beta g = \beta (g-\alpha) = \beta (h-1) \alpha$.
-Since~$Y$ is endo-local, the morphism~$h$ or~$h-1$ is an automorphism.
+Since~$Y$ is endo-local, the morphism~$h-1$ is an automorphism.
 

### 2019-06-10 thirdPaper/draft/typeConeAssociahedra.tex

--- 2019-05-28 thirdPaper/draft/typeConeAssociahedra.tex
@@
 
+The extriangulated category~$K^{[-1,0]}(\proj \Lambda)$ is the setting in which we can finally prove point~(ii) of Proposition~\ref{prop:exchangeablePairsNKC}, using results of~\cite{DemonetIyamaJasso} on~$\b g$-vectors.
+
+\begin{proposition}
+ Let~$\Lambda$ be a finite-dimensional~$\field$-algebra, where~$\field$ is a field.  Let~$X$ and~$Y$ be objects of~$K^{[-1,0]}(\proj \Lambda)$.  Assume that~ 
+ Then~$E$ and~$E'$ are isomorphic.
+\end{proposition}
+\begin{proof}
+ By~\cite[Theorem 6.5]{DemonetIyamaJasso} (based on~\cite[Theorem 2.3]{DehyKeller}), rigid objects in~$K^{[-1,0]}(\proj \Lambda)$ are determined by their~$\b g$-vector.
+The datum of the~$\b g$-vector of an object of~$K^{[-1,0]}(\proj \Lambda)$ is equivalent to that of its class in the Grothendieck group~$K_0(K^{[-1,0]}(\proj \Lambda))$, where~$K^{[-1,0]}(\proj \Lambda)$ is viewed as an extriangulated category (see Proposition~\ref{2kbproj-is-extriangulated}).
+In this Grothendieck group, we have that~$[E] = [E'] = [X]+[Y]$.
+Thus~$E$ and~$E'$ are isomorphic.
+\end{proof}
+
+\begin{corollary}\label{coro::exchangeablePairsNKC}
+ Point~(ii) of Proposition~\ref{prop:exchangeablePairsNKC} holds.
+\end{corollary}
+\begin{proof}
+
+\end{proof}
+
 Proposition~\ref{prop::2kbproj-is-extriangulated} gives a setting in which to apply Theorem~\ref{}.

### 2019-06-10 thirdPaper/draft/typeConeAssociahedra.tex
changes Parts 1 and 2

--- 2019-05-28 thirdPaper/draft/typeConeAssociahedra.tex
@@
 \newcommandx{\Zono}[2][1=n,2={}]{\mathsf{Zono}^{#2}(#1)} % zonotope
-\newcommand{\Fan}{\mathcal{F}} % fan
+\newcommandx{\Fan}[1][1=F]{\mathcal{#1}} % fan
 \newcommand{\multiplicityVector}{\b{m}} % multiplicity vector
@@
 
-\vspace{2cm}
+\vspace{1.5cm}
 \centerline{\includegraphics[scale=.8]{typeConeCoarsenings}}
@@
 \smallskip
-\item Once we get a representation of a polytope~$P$ as a signed Minkowski sum~$P = \sum_{i \in [k]}\alpha_i Q_i$, we get a formula for the volume of $P$ as a multivariate polynomial in $\alpha_1,\dots,\alpha_k$ whose coefficients are the mixed volumes of $Q_1,\dots, Q_k$~\cite{ArdilaBenedettiDoker,McMullen-Valuations}.
+\item Once we get a representation of a polytope~$P$ as a signed Minkowski sum~$P = \sum_{i \in [k]} \alpha_i Q_i$, we get a formula for the volume of $P$ as a multivariate polynomial in $\alpha_1, \dots, \alpha_k$ whose coefficients are the mixed volumes of $Q_1, \dots, Q_k$~\cite{ArdilaBenedettiDoker, McMullen-Valuations}.
 These encode rich combinatorial information when representing generalized permutahedra as positive Minkowski sums of coordinate simplices or hypersimplices~\cite{Postnikov}, and in particular for matroid polytopes~\cite{ArdilaBenedettiDoker}.
@@
 This motivates the following question: Is it possible to similarly understand the complete realization space of the cluster complex, including all realizations not having the~$\b{g}$-vector fan as their normal fan?
-\pg{AWESOME introduction.}
-\vincent{:-)}
 
@@
 \begin{notation}
-For any two adjacent cones~$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$ of~$\Fan$ with~$\rays \ssm \{\ray\} = \rays' \ssm \{\ray'\}$, we denote by~$\coefficient[{\ray[s]}][\rays][\rays']$ the coefficient of~$\ray[s]$ in the unique linear dependence between the rays of~$\rays \cup \rays'$, \ie such that
+For any adjacent maximal cones~$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$ of~$\Fan$ with ${\rays \ssm \{\ray\} = \rays' \ssm \{\ray'\}}$, we denote by~$\coefficient[{\ray[s]}][\rays][\rays']$ the coefficient of~$\ray[s]$ in the unique linear dependence between the rays of~$\rays \cup \rays'$, \ie such that
 \[
@@
 \label{def:typeCone}
-The \defn{type cone} of~$\Fan$ is the cone~$\typeCone(\Fan)$ of all $\Fan$-admissible height vectors~$\b{h}$:
+The \defn{type cone} of~$\Fan$ is the cone~$\typeCone(\Fan)$ of all $\Fan$-admissible height vectors~$\b{h} \in \R^N$:
 \begin{align*}
@@
 We denote by $\ctypeCone(\Fan)$ the closure of $\typeCone(\Fan)$, and call it the \defn{closed type cone} of~$\Fan$.
-It is the closed polyhedral cone defined by the inequalities $\sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} \geq 0$ for adjacent maximal cones~$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$.
-If $\Fan$ is the normal fan of the polytope~$P$, then $\ctypeCone(\Fan)$ is called the \defn{deformation cone} of $P$ in~\cite{Postnikov}.
+It is the closed polyhedral cone defined by the inequalities $\sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} \ge 0$ for any adjacent maximal cones~$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$.
+If $\Fan$ is the normal fan of the polytope~$P$, then $\ctypeCone(\Fan)$ is called the \defn{deformation cone} of $P$ in~\cite{Postnikov}, see also~\cite{PostnikovReinerWilliams}.
 
@@
 \begin{definition}
-An \defn{extremal adjacent pair} of~$\Fan$ is a pair of adjacent maximal cones~$\{\R_{\ge0}\rays, \R_{\ge0}\rays'\}$ of~$\Fan$ such that the corresponding inequality $\sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} \geq 0$ in the definition of the type cone~$\ctypeCone(\Fan)$ actually defines a facet of~$\ctypeCone(\Fan)$.
+An \defn{extremal adjacent pair} of~$\Fan$ is a pair of adjacent maximal cones~$\{\R_{\ge0}\rays, \R_{\ge0}\rays'\}$ of~$\Fan$ such that the corresponding inequality $\sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} \ge 0$ in the definition of the type cone~$\ctypeCone(\Fan)$ actually defines a facet of~$\ctypeCone(\Fan)$.
 \end{definition}
@@
 \label{rem:dimTypeCone}
-Since the type cone is an~$N$ dimensional cone with a linearity subspace of dimension~$n$, it has at least~$N-n$ facets.
+Since the type cone is an~$N$ dimensional cone with a linearity subspace of dimension~$n$, it has at least~$N-n$ facets (thus~$N-n$ extremal adjacent pairs).
 We say that the type cone is \defn{simplicial} when it has precisely $N-n$ facets.
@@
 \label{prop:non-simplicial}
-Let $\c{G}$ be a complete fan that coarsens the essential complete simplicial fan~$\Fan$.
-The \defn{type cone}~$\typeCone(\c{G})$ of all $\c{G}$-admissible height vectors~$\b{h}$ is
+Let $\Fan$ be a complete fan that coarsens the essential complete simplicial fan~$\Fan[G]$.
+The \defn{type cone}~$\typeCone(\Fan)$ of all $\Fan$-admissible height vectors~$\b{h} \in \R^N$ is
 \begin{align*}
-\typeCone(\c{G}) 
+\typeCone(\Fan) 
 & = \left\{\b{h} \in \R^N\;\middle|\;
@@
 \sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} = 0
-& \begin{array}{l} \text{for any adjacent maximal cones} \\ \text{$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$ of~$\Fan$ belonging}\\\text{to \textbf{the same} maximal cone of $\c{G}$,}\end{array}
+& \begin{array}{l} \text{for any adjacent maximal cones} \\ \text{$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$ of~$\Fan[G]$ belonging}\\\text{to \textbf{the same} maximal cone of $\Fan$,}\end{array}
 \\[.7cm]
 \sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} > 0
-& \begin{array}{l} \text{for any adjacent maximal cones} \\ \text{$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$ of~$\Fan$ belonging}\\\text{to \textbf{distinct} maximal cones of $\c{G}$}\end{array}
+& \begin{array}{l} \text{for any adjacent maximal cones} \\ \text{$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$ of~$\Fan[G]$ belonging}\\\text{to \textbf{distinct} maximal cones of $\Fan$}\end{array}
 \end{array}
@@
 \]
-does not depend on the pair~$\{\rays, \rays'\}$ of adjacent maximal cones of~$\Fan$ with $\rays \ssm \{\ray\} = \rays' \ssm \{\ray'\}$, but only on the pair of rays~$\ray, \ray'$.
-This implies in particular that the rays~$\ray[s]$ for which~$\coefficient[{\ray[s]}][\rays][\rays'] \ne 0$ belong to~$\rays \cup \rays'$ for any pair~$\{\rays, \rays'\}$ of adjacent cones of~$\Fan$ with $\rays \ssm \{\ray\} = \rays' \ssm \{\ray'\}$.
+does not depend on the pair~$\{\rays, \rays'\}$ of adjacent maximal cones of~$\Fan$ with $\rays \ssm \{\ray\} = \rays' \ssm \{\ray'\}$, but only on the pair of rays~$\{\ray, \ray'\}$.
+This implies in particular that the rays~$\ray[s]$ for which~$\coefficient[{\ray[s]}][\rays][\rays'] \ne 0$ belong to~$\rays \cup \rays'$ for any pair~$\{\rays, \rays'\}$ of adjacent maximal cones of~$\Fan$ with $\rays \ssm \{\ray\} = \rays' \ssm \{\ray'\}$.
 
@@
 \begin{definition}
-In a fan~$\Fan$ with the unique exchange relation property, an \defn{extremal exchangeable pair} is a pair of exchangeable rays~$\{\ray,\ray'\}$ such that the corresponding inequality~${\sum_{\ray[s]} \coefficient \, \b{h}_{\ray[s]} \geq  0}$ defines a facet of the closed type cone~$\ctypeCone(\Fan)$.
+In a fan~$\Fan$ with the unique exchange relation property, an \defn{extremal exchangeable pair} is a pair of exchangeable rays~$\{\ray,\ray'\}$ such that the corresponding inequality~${\sum_{\ray[s]} \coefficient \, \b{h}_{\ray[s]} \ge  0}$ defines a facet of the closed type cone~$\ctypeCone(\Fan)$.
 \end{definition}
@@
 
-We still consider an essential complete simplicial fan~$\Fan$ in~$\R^n$, the $N \times n$-matrix~$\b{G}$ whose rows are the rays of~$\Fan$, and the $(N-n) \times N$-matrix~$\b{K}$ which spans the left kernel of~$\b{G}$.
+We still consider an essential complete simplicial fan~$\Fan$ in~$\R^n$, the $N \times n$-matrix~$\b{G}$ whose rows are the rays of~$\Fan$, and the $(N-n) \times N$-matrix~$\b{K}$ which spans the left kernel of~$\b{G}$ (\ie $\b{K}\b{G} = 0$).
 
@@
 \label{coro:simplicialTypeCone}
-Assume that the type cone~$\typeCone(\Fan)$ is simplicial and let~$\b{K}$ be the $(N-n) \times N$-matrix whose rows are the outer normal vectors of the facets of~$\typeCone(\Fan)$. Then the polytope
+Assume that the type cone~$\typeCone(\Fan)$ is simplicial and let~$\b{K}$ be the $(N-n) \times N$-matrix whose rows are the inner normal vectors of the facets of~$\typeCone(\Fan)$. Then the polytope
 \[
@@
 Since~$\b{K}$ has full rank there exists~$\b{h} \in \R^N$ such that~$\b{K}\b{h} = \b{\ell}$.
-Since~$\b{K}\b{h} \ge 0$ and the rows of~$\b{K}$ are precisely all outer normal vectors of the facets of the type cone~$\typeCone(\Fan)$, we obtain that~$\b{h}$ belongs to~$\typeCone(\Fan)$.
+Since~$\b{K}\b{h} \ge 0$ and the rows of~$\b{K}$ are precisely all inner normal vectors of the facets of the type cone~$\typeCone(\Fan)$, we obtain that~$\b{h}$ belongs to~$\typeCone(\Fan)$.
 Since $R_\b{\ell} = Q_\b{h} \sim P_\b{h}$ by \cref{prop:alternativePolytopalRealization}, we conclude that~$R_\b{\ell}$ is a polytopal realization of~$\Fan$.
-Since~$\typeCone(\Fan)$ is simplicial, we have~$\b{K}\typeCone(\Fan) = \R_{>0}^{N-n}$, so that we obtain all polytopal realizations of~$\Fan$ this way.
+Since~$\typeCone(\Fan)$ is simplicial, we have~$\b{K}\typeCone(\Fan) = \R_{>0}^{N-n}$, so that we obtain all polytopal realizations of~$\Fan$ in this way.
 \end{proof}
@@
 
-We say that~$P$ is a \defn{Minkowski summand} of~$R$ if there is a polytope~$Q$ such that $R=P+Q$, and a \defn{weak Minkowski summand} if there is a $\lambda \ge 0$ and a polytope~$Q$ such that ${\lambda R = P + Q}$.
+We say that~$P$ is a \defn{Minkowski summand} of~$R$ if there is a polytope~$Q$ such that $P+Q = R$, and a \defn{weak Minkowski summand} if there is a $\lambda \ge 0$ and a polytope~$Q$ such that ${P + Q = \lambda R}$.
 \cref{lem:MinkowskiSum} ensures that convex combinations in the type cone correspond to Minkowski combinations of polytopes.
@@
 If $P = Q + R$, then we say that~$R$ is the \defn{Minkowski difference} of~$P$ and~$Q$, denoted~${R = P - Q}$. Note that this is only defined when~$Q$ is a Minkowski summand of~$P$.
-There are two natural ways this construction generalizes to arbitrary pairs of polyhedra. On the one hand, we have $P - Q = \set{x \in \R^n}{x + Q \subseteq P}$. 
-Notice that $P_\b{h} - P_{\b{h}'} = P_{\b{h} - \b{h'}}$ when $P_{\b{h}'}$ is a Minkowski summand of $P_\b{h}$.
-Considering arbitrary differences of support functions gives rise to \defn{virtual polyhedra}, which is the Grothendieck group of the semigroup of polytopes with Minkowski sums~\cite{PukhlikovKhovanskii}.
+For instance, we have ${P_\b{h} - P_{\b{h}'} = P_{\b{h} - \b{h'}}}$ when $P_{\b{h}'}$ is a Minkowski summand of $P_\b{h}$.
+There are two natural ways this construction generalizes to arbitrary pairs of polyhedra.
+On the one hand, one can consider that ${P - Q = \set{x \in \R^n}{x + Q \subseteq P}}$.
+On the other hand, considering arbitrary differences of support functions gives rise to \defn{virtual polyhedra}, which is the Grothendieck group of the semigroup of polytopes with Minkowski sums~\cite{PukhlikovKhovanskii}.
 
@@
 \begin{corollary}
-If the type cone~$\typeCone(\Fan)$ of $\Fan$ is simplicial, then the $N-n$ idecomposable polytopes $P_{\b{h}^{(1)}}, \dots, P_{\b{h}^{(N-n)}}$ arising from the rays of $\ctypeCone(\Fan)$ verify that 
-\begin{enumerate}[(i)]
-\item  every $P_\b{h}$ with $\b{h}\in \typeCone(\Fan)$ has a unique representation (up to translation) as a Minkowski sum of positive dilates of $P_{\b{h}^{(1)}}, \dots, P_{\b{h}^{(N-n)}}$; and
-\item  every $P_\b{h}$ with $\b{h}\in \ctypeCone(\Fan)$ has a unique representation (up to translation) as a Minkowski sum of non-negative dilates of $P_{\b{h}^{(1)}}, \dots, P_{\b{h}^{(N-n)}}$.
-\end{enumerate} 
+If the type cone~$\typeCone(\Fan)$ of $\Fan$ is simplicial, then every $P_\b{h}$ with $\b{h}\in \typeCone(\Fan)$ (resp.~with $\b{h}\in \ctypeCone(\Fan)$) has a unique representation, up to translation, as a Minkowski sum of positive (resp.~non-negative) dilates of the $N-n$ indecomposable polytopes $P_{\b{h}^{(1)}}, \dots, P_{\b{h}^{(N-n)}}$ arising from the rays~$\b{h}^{(1)}, \dots, \b{h}^{(N-n)}$ of $\ctypeCone(\Fan)$.
 \end{corollary}
@@
 \label{exm:typeConeMinkowskiSum}
-\enlargethispage{.4cm}
 Consider the $2$-dimensional fan~$\Fan$ of \cref{fig:typeCone}\,(left) whose type cone has been described in \cref{exm:typeCone} and represented in \cref{fig:typeCone}\,(right).
@@
 \item the convex hull of the points~$L(T) \in \R^{n+1}$ for all rooted binary trees~$T$ with~$n+1$ internal nodes, where the $i$th coordinate of~$L(T)$ is the product of the number of leaves in the left subtree by the number of leaves in the right subtree of the $i$th node of~$T$ in inorder~\cite{Loday},
-\item the intersection of the hyperplane~$\bigset{\b{x} \in \R^{n+1}}{\sum_{\ell \in [n+1]} x_\ell = \binom{n+2}{2}}$ with the halfspaces $\bigset{\b{x} \in \R^{n+1}}{\sum_{a < \ell < b} x_\ell \ge \binom{b-a+2}{2}}$ for all internal diagonal~$(a,b)$ of \mbox{the $(n+3)$-gon~\cite{ShniderSternberg}},
-\item the Minkowski sum of the faces~$\simplex_{[i,j]}$ of the standard $n$-dimensional simplex~$\simplex$ corresponding to all proper intervals~$[i,j]$ of~$[n+1]$,~\cite{Postnikov}.
+\item the intersection of the hyperplane~$\bigset{\b{x} \in \R^{n+1}}{\sum_{\ell \in [n+1]} x_\ell = \binom{n+2}{2}}$ with the halfspaces $\bigset{\b{x} \in \R^{n+1}}{\sum_{a < \ell < b} x_\ell \ge \binom{b-a+2}{2}}$ for all internal diagonals~$(a,b)$ of \mbox{the $(n+3)$-gon~\cite{ShniderSternberg}},
+\item the Minkowski sum of the faces~$\simplex_{[i,j]}$ of the standard $n$-dimensional simplex~$\simplex_{[n+1]}$ corresponding to all proper intervals~$[i,j]$ of~$[n+1]$,~\cite{Postnikov}.
 \end{itemize}
@@
 \[
-\typeCone(\gvectorFan[n]) = \set{\b{h} \in \R^{X(n)}}{\begin{array}{l} \b{h}_{(0,n+2)} = 0, \qquad\text{and}\qquad \b{h}_{(a,a+1)} = 0 \text{ for all } 0 \le a \le n+1 \\ \b{h}_{(a,b)} + \b{h}_{(a',b')} > \b{h}_{(a,b')} + \b{h}_{(a',b)} \text{ for all } 0 \le a < a' < b < b' \le n+2 \end{array}}.
+\typeCone \big( \gvectorFan[n] \big) = \set{\b{h} \in \R^{X(n)}}{\begin{array}{@{}l@{}} \b{h}_{(0,n+2)} = 0, \qquad\text{and}\qquad \b{h}_{(a,a+1)} = 0 \text{ for all } 0 \le a \le n+1 \\ \b{h}_{(a,b)} + \b{h}_{(a',b')} > \b{h}_{(a,b')} + \b{h}_{(a',b)} \text{ for all } 0 \le a < a' < b < b' \le n+2 \end{array}} \!.
 \]
@@
 
-\arnau{I think the coordinates of the g-vector corresponding to {diagonalA3} were wrong, and I swapped them. }
-
-\arnau{When writing the coordinates of the g's, we cannot follow \cref{thm:normalFanLoday}, because we don't say which basis have we chosen for the hyperplane.}
 \medskip
@@
 The type cone of~$\gvectorFan[2]$ lives in~$\R^9$ and has a linearity space of dimension~$3$.
-It has $6$ facet-defining inequalities (given below), which correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso} and illustrated in \cref{fig:labelFacetDefiningInequalititiesAsso}\,(left).
+It has $6$ facet-defining inequalities (given below), which correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso} and illustrated in \cref{fig:labelFacetDefiningInequalititiesAsso}\,(right).
 
@@
     \end{adjustbox}
-	\caption{The facet-defining inequalities of the type cone~$\typeCone(\gvectorFan[n])$ correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso}.
+	\caption{The facet-defining inequalities of the type cone~$\typeCone \big( \gvectorFan[n] \big)$ correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso}.
 See \cref{subsec:typeConeCA,sec:clusterCategories} for a representation theoretic \mbox{interpretation}.}
@@
 
-Motivated by \cref{exm:typeConeAsso}, we now describe the facets of this type cone~$\typeCone(\gvectorFan[n])$.
+Motivated by \cref{exm:typeConeAsso}, we now describe the facets of this type cone~$\typeCone \big( \gvectorFan[n] \big)$.
 
@@
 \]
-Therefore, the outer normal vector of the corresponding inequality of the type cone~$\typeCone(\gvectorFan[n])$ is
+Therefore, the inner normal vector of the corresponding inequality of the type cone~$\typeCone \big( \gvectorFan[n] \big)$ is
 \[
@@
 
-\arnau{Change $\b{f}_{(a,b)}$ to $\b{h}_{(a,b)}$? (To homogenize with previous sections)}
-
 Our next statement follows from the end of the previous proof.
@@
 \label{coro:simplicialTypeConeAsso}
-The type cone~$\typeCone(\gvectorFan[n])$ is simplicial.
+The type cone~$\typeCone \big( \gvectorFan[n] \big)$ is simplicial.
 \end{corollary}
@@
 It is known to be the normal fan of a polytope called generalized associahedron.
-These polytopal realizations were first constructed for bipartite initial seeds by F.~Chapoton, S.~Fomin and A.~Zelevinsky~\cite{ChapotonFominZelevinsky} using the $\b{d}$-vector fans of~\cite{FominZelevinsky-YSystems}, then for acyclic initial seeds by C.~Hohlweg, C.~Lange and H.~Thomas~\cite{HohlwegLangeThomas} using Cambrian lattices and fans of N.~Reading and D.~Speyer~\cite{Reading-CambrianLattices, ReadingSpeyer}, and revisited by S.~Stella~\cite{Stella}, and by V.~Pilaud and C.~Stump~\cite{PilaudStump-brickPolytope} via brick polytopes, and finally for arbitrary initial seeds by C.~Hohlweg, V.~Pilaud and S.~Stella~\cite{HohlwegPilaudStella}.
+These polytopal realizations were first constructed for bipartite initial seeds by F.~Chapoton, S.~Fomin and A.~Zelevinsky~\cite{ChapotonFominZelevinsky} using the $\b{d}$-vector fans of~\cite{FominZelevinsky-YSystems}, then for acyclic initial seeds by C.~Hohlweg, C.~Lange and H.~Thomas~\cite{HohlwegLangeThomas} using Cambrian lattices and fans of N.~Reading and D.~Speyer~\cite{Reading-CambrianLattices, ReadingSpeyer}, then revisited by S.~Stella~\cite{Stella}, and by V.~Pilaud and C.~Stump~\cite{PilaudStump-brickPolytope} via brick polytopes, and finally for arbitrary initial seeds by C.~Hohlweg, V.~Pilaud and S.~Stella~\cite{HohlwegPilaudStella}.
 More recently in~\cite{BazierMatteDouvilleMousavandThomasYildirim}, V.~Bazier-Matte, G.~Douville, K.~Mousavand, H.~Thomas and E.~Y\i ld\i r\i m extended the construction of associahedra of~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} to acyclic seeds of simply-laced finite type cluster algebras.
-Here, we extend the construction of~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} to any finite type (simply-laced or not) cluster algebra with respect to any seed (acyclic or not) by providing a direct proof that the type cone of the cluster fan of any finite type cluster algebra is simplicial.
+Here, we extend the construction of~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} to any finite type (simply-laced or not) cluster algebra with respect to any seed (acyclic or not) by providing a direct proof that the type cone of the cluster fan of any finite type cluster algebra with respect to any initial seed is simplicial.
 
@@
 	p_x^{-1}  & \text{if } y = x', \\
-	p_y\negativeExponents{p_x}^{b_{xy}}  & \text{if } y \neq x' \text{ and } b_{xy} \leq 0, \\
-	p_y\positiveExponents{p_x}^{b_{xy}}  & \text{if } y \neq x' \text{ and } b_{xy} > 0.
+	p_y\negativeExponents{p_x}^{b_{xy}}  & \text{if } y \ne x' \text{ and } b_{xy} \leq 0, \\
+	p_y\positiveExponents{p_x}^{b_{xy}}  & \text{if } y \ne x' \text{ and } b_{xy} > 0.
 \end{cases}
@@
 For simplicity, we drop the mention of the coefficients for principal cluster algebras in the notations for seeds~$\seed = (\B, \cluster)$, for cluster algebras~$\principalClusterAlgebra$ and for variables~$\principalVariables$.
-Principal coefficients cluster algebras are $\Z^n$-graded (in the fundamental weight basis~$\{\omega_x\}_{x \in \cluster_\circ}$ of~$V$) for the degree function~$\deg(\B_\circ,\cdot)$ on $\principalClusterAlgebra$ is obtained by setting
+Principal coefficients cluster algebras are $\Z^n$-graded (in the fundamental weight basis~$\{\omega_x\}_{x \in \cluster_\circ}$ of~$V$) for the degree function~$\deg(\B_\circ,\cdot)$ on $\principalClusterAlgebra$ obtained by setting
 \(
@@
 \[
-\gvectorFan[\B_\circ] \eqdef \bigset{\R_{\ge0} \, \gvectorsFull{\B_\circ}{\seed}}{\seed \text{ seed of } \principalClusterAlgebra},
-\]
-together with all their faces, forms a complete simplicial fan, called the \defn{$\b{g}$-vector fan} or \defn{cluster fan} of~$\B_\circ$.
+\bigset{\R_{\ge0} \, \gvectorsFull{\B_\circ}{\seed}}{\seed \text{ seed of } \principalClusterAlgebra},
+\]
+together with all their faces, forms a complete simplicial fan~$\gvectorFan[\B_\circ]$, called the \defn{$\b{g}$-vector fan} or \defn{cluster fan} of~$\B_\circ$.
 \end{theorem}
@@
 We now discuss the linear dependences between $\b{g}$-vectors of adjacent seeds.
-The following proposition was stated in~\cite[Lem.~19]{HohlwegPilaudStella}.
+The following lemma was stated in~\cite[Lem.~19]{HohlwegPilaudStella}.
 
@@
 
-Note that \cref{lem:linearDependencegvectorsCA} implies \cref{thm:generalizedAsso} since it ensures that the type cone~$\typeCone(\gvectorFan[\B_\circ])$ of the cluster fan contains the cone of~${\b{h} \in \R^{\principalVariables}}$ such that
+Note that \cref{lem:linearDependencegvectorsCA} implies \cref{thm:generalizedAsso} since it ensures that the type cone~$\typeCone \big( \gvectorFan[\B_\circ] \big)$~of~the cluster fan contains the cone of height vectors~${\b{h} \in \R^{\principalVariables}}$ such that
 \(
@@
 However, for cluster algebras of finite type, this linear dependence is independent of the choice of a seed containing~$x$ and~$x'$.
-As explained in Corollary~\ref{corollary:UERPforCAproof}, this statement follows from~\cite[Theorem 7.5]{BuanMarshReinekeReitenTodorov}.
+As explained in ~\cref{corollary:UERPforCAproof}, this statement follows from~\cite[Theorem 7.5]{BuanMarshReinekeReitenTodorov}.
 We state it here for future reference.
@@
 \[
-\typeCone(\gvectorFan[\B_\circ]) = \set{\b{h} \in \R^{\principalVariables}}{\dotprod{\b{n}(\B_\circ, x, x')}{\b{h}} > 0 \text{ for all exchangeable cluster variables } x, x'}.
+\typeCone \big( \gvectorFan[\B_\circ] \big) = \set{\b{h} \in \R^{\principalVariables}}{\dotprod{\b{n}(\B_\circ, x, x')}{\b{h}} > 0 \text{ for all exchangeable cluster variables } x, x'}.
 \]
@@
     \end{adjustbox}
-	\caption{The facet-defining inequalities of the type cone~$\typeCone(\gvectorFan[\B_\circ])$ of the cluster fan correspond to the mesh mutations described in \cref{thm:extremalExchangeablePairsCA}.
+	\caption{The facet-defining inequalities of the type cone~$\typeCone \big( \gvectorFan[\B_\circ] \big)$ of the cluster fan correspond to the mesh mutations described in \cref{thm:extremalExchangeablePairsCA}.
 See \cref{sec:clusterCategories} for a representation theoretic \mbox{interpretation}.}
@@
 In other words, according to \cref{lem:dependenceMesh}, if~${(\B, \cluster)}$ and~${(\B', \cluster')}$ are two adjacent seeds with~$\cluster \ssm \{x\} = \cluster' \ssm \{x'\}$, we have~$\alpha_{x,x',y} = |b_{xy}|$ for~$y \in \cluster \cap \cluster'$ and~$\alpha_{x,x',y} = 0$ otherwise.
-
-The following will be shown in \cref{sec:clusterCategories}, Corollary~\ref{corollary:proof of prop meshMutations}.
+The following statement will be shown in \cref{corollary:proof of prop meshMutations}.
 
@@
 \label{coro:simplicialTypeConeCA}
-The type cone~$\typeCone(\gvectorFan[n])$ is simplicial.
+The type cone~$\typeCone \big( \gvectorFan[n] \big)$ is simplicial.
 \end{corollary}
@@
 
-\enlargethispage{-.4cm}
 Gentle associahedra were constructed by Y.~Palu, V.~Pilaud and P.-G.~Plamondon~\cite{PaluPilaudPlamondon-nonkissing} in the context of support $\tau$-tilting for gentle algebras.
@@
 For each vertex~$a \in Q_0$, there is also a \defn{string of length zero}, denoted by~$\varepsilon_a$, that starts and ends at~$a$.
-We often implicitly identify the two inverse strings~$\rho$ and~$\rho^{-1}$, and call it an \defn{undirected string} of~$\quiver$.
+We implicitly identify the two inverse strings~$\rho$ and~$\rho^{-1}$, and call it an \defn{undirected string} of~$\quiver$.
 Let~$\strings$ denote the set of strings of~$\quiver$.
 
-A \defn{walk} of~$\quiver$ is a maximal maximal string of its blossoming quiver~$\quiver\blossom$ (meaning that each endpoint is a blossom).
+A \defn{walk} of~$\quiver$ is a maximal string of its blossoming quiver~$\quiver\blossom$ (meaning that each endpoint is a blossom).
 As for strings, we implicitly identify the two inverse walks~$\omega$ and~$\omega^{-1}$, and call it an \defn{undirected walk} of~$\quiver$.
@@
 \begin{itemize}
-\item the endpoints of~$\sigma$ are not allowed to blossom endpoints of~$\omega$,
+\item the endpoints of~$\sigma$ are not allowed to be blossom endpoints of~$\omega$,
 \item the position of~$\sigma$ as a factor of~$\omega$ matters (the same string at a different position is considered a different substring).
@@
 We say that~$\omega$ \defn{kisses}~$\omega'$ if ${\Sigma_\top(\omega) \cap \Sigma_\bottom(\omega')} \ne \varnothing$.
-In other words, $\omega$ and~$\omega'$ share a common substring~$\sigma$, and both arrows of~$\omega$ (resp.~of~$\omega'$) not in~$\sigma$ are outgoing (resp.~incoming) at the endpoints of~$\sigma$.
+In other words, $\omega$ and~$\omega'$ share a common substring~$\sigma$, and both arrows of~$\omega$ (resp.~of~$\omega'$) incident to the endpoints of~$\sigma$ but not in~$\sigma$ are outgoing (resp.~incoming) at the endpoints of~$\sigma$.
 See \cref{fig:kissingCrossing} for a schematic representation and \cref{fig:exmNonkissing}\,(middle) where the three walks are pairwise kissing.
@@
 
-\para{Two families of examples: gentle grid and dissection quivers}
-%
-The initial motivation for non-kissing complexes came from two families of examples, illustrated in \cref{fig:dissectionGridQuivers}:
-\begin{enumerate}[(1)]
-\item \textbf{Grid quivers}: Consider the infinite grid quiver~$\quiver_{Z^2}$, whose vertices are all integer points of~$\Z^2$, whose arrows connect between~$(i,j) \longrightarrow (i,j+1)$ and~$(i,j) \longrightarrow (i+1,j)$ for any~$(i,j) \in \Z^2$, and whose relations forbid~$(i-1,j) \longrightarrow (i,j) \longrightarrow (i,j+1)$ and~$(i,j-1) \longrightarrow (i,j) \longrightarrow (i+1,j)$ for any~$(i,j) \in \Z^2$.
-A \defn{gentle grid quiver} is any subquiver~$\quiver_A$ of~$\quiver_{Z^2}$ induced by a finite subset~$A \subset \Z^2$ of the integer grid.
-See \cref{fig:dissectionGridQuivers}.
-The non-kissing complex of gentle grid quivers were introduced in~\cite{McConville} with motivation coming from~\cite{PetersenPylyavskyySpeyer} and~\cite{SantosStumpWelker}.
-
-\smallskip
-\item \textbf{Dissection quivers}: Consider a dissection~$D$ of a convex polygon~$P$ (that is a crossing-free set of diagonals of~$P$) and its \defn{gentle dissection quiver}~$\quiver_D$, whose vertices are the internal diagonals of~$D$, whose arrows connect pairs of consecutive internal diagonals along the boundary of a face of~$D$, and whose relations correspond to triples of consecutive internal diagonals along the boundary of a face of~$D$.
-See \cref{fig:dissectionGridQuivers}.
-The non-kissing complex of~$\quiver_D$ then corresponds to non-crossing sets of accordions of~$D$, where an accordion is a segment connecting the middles of two boundary edges of~$P$ and crossing a connected set of diagonals of~$D$.
-This accordion complex was studied in~\cite{GarverMcConville} and~\cite{MannevillePilaud-accordion} with motivation coming from~\cite{Baryshnikov}, and~\cite{Chapoton-quadrangulations}.
-\end{enumerate}
-
-\begin{figure}[h]
-	\capstart
-	\centerline{\includegraphics[scale=.35]{gridQuiver} \quad \includegraphics[scale=.8]{dissectionQuiver} \quad \includegraphics[scale=1.2]{bijectionAssociahedronGrid} \quad \includegraphics[scale=1.2]{bijectionAssociahedronDissection}}
-	\caption{A gentle grid quiver (left), a gentle dissection quiver (middle left), and a path quiver which is both the gentle grid quiver of a ribbon (middle right) and the dissection quiver of a triangulation (right).
-Illustration from~\cite{PaluPilaudPlamondon-nonkissing}.}
-	\label{fig:dissectionGridQuivers}
-\end{figure}
-
-These two families of non-kissing complexes are well-behaved as they avoid all pathologies of \cref{rem:exchangeablePairsNKC}.
-However, they still provide good examples of non-kissing complexes.
-In particular, both families contain the classical associahedron.
-Namely, the gentle associahedron~$\Asso[\quiver]$ is the classical associahedron of~\cite{ShniderSternberg, Loday} presented in \cref{thm:associahedronLoday} when~${\quiver = \quiver_A}$ for the path~${A = \set{(0,j)}{j \in [n]}}$ or equivalently~$\quiver = \quiver_D$ for the fan triangulation~$D$ (where all internal diagonals incident to the same point).
-More generally, $\Asso[\quiver]$ is an associahedron of~\cite{HohlwegLange} when~$\quiver = \quiver_A$ for a ribbon~$A$ or equivalently~$\quiver = \quiver_D$ for a triangulation~$D$.
-See \cref{fig:dissectionGridQuivers}.
-
-Note that, it was shown in~\cite{PaluPilaudPlamondon-surfaces} that the accordion complexes can be extended to dissections of arbitrary orientable surfaces with marked points and then provide a geometric model for all non-kissing complexes of gentle quivers.
-
 \para{$\b{g}$- and $\b{c}$-vectors}
@@
 The \defn{distinguished walk} of the non-kissing facet~$F \in \NKC$ at the arrow~$\alpha$ is the maximum walk of~$F$ for~$\prec_\alpha$.
-The \defn{distinguished arrows} of the walk~$\omega$ in the non-kissing facet~$F \in \NKC$ are the arrow where~$\omega$ is the distinguished walk.
+The \defn{distinguished arrows} of the walk~$\omega$ in the non-kissing facet~$F \in \NKC$ are the arrows where~$\omega$ is the distinguished walk.
 It is shown in~\cite[Prop.~2.28]{PaluPilaudPlamondon-nonkissing} that each bending walk in a non-kissing facet has precisely two distinguished arrows, pointing in opposite directions.
@@
 The \defn{distinguished substring}~$\distinguishedString{\omega}{F}$ of the walk~$\omega$ in the non-kissing facet~$F \in \NKC$ is the substring located between its two distinguished arrows.
-We say that a string~$\sigma$ is \defn{distinguishable} if it is the distinguished string of a walk in a non-kissing facet, and we denote by~$\distinguishableStrings$ the set of distinguishable strings of~$\quiver$.
 
@@
 
+The following result will also be essential in our discussion.
+We say that a string~$\sigma$ is \defn{distinguishable} if it is the distinguished substring of a walk in a non-kissing facet, and we denote by~$\distinguishableStrings$ the set of distinguishable strings of~$\quiver$.
+
+\begin{proposition}[{\cite[3.68]{PaluPilaudPlamondon-nonkissing}}]
+\label{prop:bijectionStringsWalks}
+The number of distinguishable strings~$\distinguishableStrings$ and proper walks~$\properWalks$ of the quiver~$\quiver$ are related by
+\[
+|\distinguishableStrings| + |Q_0| = |\properWalks|.
+\]
+\end{proposition}
+
 \para{Non-kissing fan and gentle associahedron}
 %
-\enlargethispage{.2cm}
-The $\b{g}$-vectors support a complete simplicial fan realization of the non-kissing complex complex.
+\enlargethispage{.1cm}
+The $\b{g}$-vectors support a complete simplicial fan realization of the non-kissing complex~$\NKC$.
 Examples are illustrated in \cref{fig:nonkissingFans}.
@@
 
-\begin{figure}[b]
+\begin{figure}[h]
 	\capstart
@@
 %
-\enlargethispage{-.4cm}
 Although we lack a characterization of the exchangeable pairs of the non-kissing complex (see \cref{rem:exchangeablePairsNKC}), we can still describe the linear dependence among the $\b{g}$-vectors involved in a flip.
@@
 \label{prop:exchangeablePairsNKC}
-Let~$\omega, \omega'$ be two exchangeable walks on~$\quiver$. Then
+Let~$\omega, \omega'$ be two exchangeable walks on~$\quiver$. Then:
 \begin{enumerate}[(i)]
 \item For any non-kissing facets~$F, F'$ of~$\NKC$ with~$F \ssm \{\omega\} = f' \ssm \{\omega'\}$, the distinguished substrings of~$\omega$ in~$F$ and of~$\omega'$ in~$F'$ coincide to a string~$\sigma$.
-Moreover, if we decompose~$\omega = \rho \sigma \tau$ and~$\omega' = \rho' \sigma \tau'$, then the facets~$F$ and~$F'$ both contain the walks~$\mu \eqdef \rho' \sigma \tau$ and~$\nu \eqdef \rho \sigma \tau'$.
+Moreover, if we decompose~${\omega = \rho \sigma \tau}$ and~${\omega' = \rho' \sigma \tau'}$, then the facets~$F$ and~$F'$ both contain the walks~$\mu \eqdef \rho' \sigma \tau$ and~$\nu \eqdef \rho \sigma \tau'$.
 \item The substring~$\sigma$ and thus the walks~$\mu$ and~$\nu$ actually depend on the exchangeable walks~$\omega$ and~$\omega'$, not on the adjacent non-kissing facet~$F $ and~$F'$.
-\item Moreover, the linear dependence between the $\b{g}$-vectors of~$F \cup F'$ is given by
+\item The linear dependence between the $\b{g}$-vectors of~$F \cup F'$ is given by
 \[
@@
 %
-\begin{figure}[t]
+\begin{figure}[b]
 	\capstart
@@
 This question was discussed in \cite[Sect.~9]{BrustleDouvilleMousavandThomasYildirim}.
-However, as illustrated in \cref{fig:nonkissingFans}\,(right), note that
+However, as illustrated for instance in the non-kissing complex of \cref{fig:nonkissingFans}\,(right),
 \begin{itemize}
@@
 
-\para{Numerology}
-%
-The following result will also be essential in our discussion.
-
-\begin{proposition}[{\cite[3.68]{PaluPilaudPlamondon-nonkissing}}]
-\label{prop:bijectionStringsWalks}
-The number of distinguishable strings~$\distinguishableStrings$ and proper walks~$\properWalks$ of the quiver~$\quiver$ are related by
-\[
-|\distinguishableStrings| + |Q_0| = |\properWalks|.
-\]
-\end{proposition}
+\para{Two families of examples: gentle grid and dissection quivers}
+%
+The initial motivation for non-kissing complexes came from two families of examples, illustrated in \cref{fig:dissectionGridQuivers}:
+
+\medskip
+\begin{enumerate}[(1)]
+\item \textbf{Grid quivers}: Consider the infinite grid quiver~$\quiver_{Z^2}$, whose vertices are all integer points of~$\Z^2$, whose arrows are~$(i,j) \longrightarrow (i,j+1)$ and~$(i,j) \longrightarrow (i+1,j)$ for any~$(i,j) \in \Z^2$, and whose relations are~$(i-1,j) \longrightarrow (i,j) \longrightarrow (i,j+1)$ and~$(i,j-1) \longrightarrow (i,j) \longrightarrow (i+1,j)$ for any~$(i,j) \in \Z^2$.
+A \defn{gentle grid quiver} is any subquiver~$\quiver_A$ of~$\quiver_{Z^2}$ induced by a finite subset~$A \subset \Z^2$ of the integer grid.
+See \cref{fig:dissectionGridQuivers}.
+The non-kissing complex of gentle grid quivers were introduced in~\cite{McConville} with motivation coming from~\cite{PetersenPylyavskyySpeyer} and~\cite{SantosStumpWelker}.
+
+\medskip
+\item \textbf{Dissection quivers}: Consider a dissection~$D$ of a convex polygon~$P$ (that is a crossing-free set of diagonals of~$P$) and its \defn{gentle dissection quiver}~$\quiver_D$, whose vertices are the internal diagonals of~$D$, whose arrows connect pairs of consecutive internal diagonals along the boundary of a face of~$D$, and whose relations correspond to triples of consecutive internal diagonals along the boundary of a face of~$D$.
+See \cref{fig:dissectionGridQuivers}.
+The non-kissing complex of~$\quiver_D$ then corresponds to non-crossing sets of accordions of~$D$, where an accordion is a segment connecting the middles of two boundary edges of~$P$ and crossing a connected set of diagonals of~$D$.
+This accordion complex was studied in~\cite{GarverMcConville} and~\cite{MannevillePilaud-accordion} with motivation coming from~\cite{Baryshnikov}, and~\cite{Chapoton-quadrangulations}.
+\end{enumerate}
+
+\begin{figure}[h]
+	\capstart
+	\centerline{\includegraphics[scale=.35]{gridQuiver} \quad \includegraphics[scale=.8]{dissectionQuiver} \quad \includegraphics[scale=1.2]{bijectionAssociahedronGrid} \quad \includegraphics[scale=1.2]{bijectionAssociahedronDissection}}
+	\caption{A gentle grid quiver (left), a gentle dissection quiver (middle left), and a path quiver which is both the gentle grid quiver of a ribbon (middle right) and the dissection quiver of a triangulation (right).
+Illustration from~\cite{PaluPilaudPlamondon-nonkissing}.}
+	\label{fig:dissectionGridQuivers}
+\end{figure}
+
+These two families of non-kissing complexes are well-behaved as they avoid all pathologies of \cref{rem:exchangeablePairsNKC}.
+However, they still provide good examples of non-kissing complexes.
+In particular, both families contain the classical associahedron.
+Namely, the gentle associahedron~$\Asso[\quiver]$ is the classical associahedron of~\cite{ShniderSternberg, Loday} presented in \cref{thm:associahedronLoday} when~${\quiver = \quiver_A}$ for the path~${A = \set{(0,j)}{j \in [n]}}$ or equivalently~$\quiver = \quiver_D$ for the fan triangulation~$D$ (where all internal diagonals are incident to the same point).
+More generally, $\Asso[\quiver]$ is an associahedron of~\cite{HohlwegLange} when~$\quiver = \quiver_A$ for a ribbon~$A$ or equivalently~$\quiver = \quiver_D$ for a triangulation~$D$.
+See \cref{fig:dissectionGridQuivers}.
+
+Note that, it was shown in~\cite{PaluPilaudPlamondon-surfaces} that the accordion complexes can be extended to dissections of arbitrary orientable surfaces with marked points and then provide a geometric model for all non-kissing complexes of gentle quivers.
 
@@
 
+\enlargethispage{-.3cm}
 We now discuss the type cones of the non-kissing fans defined in \cref{thm:nonkissingFan}. We obtain from \cref{prop:exchangeablePairsNKC} the following redundant description.
@@
 \[
-\typeCone(\gvectorFan[\quiver]) = \set{\b{h} \in \R^{\walks}}{\begin{array}{l} \b{h}_\omega = 0 \text{ for any improper walk } \omega \\ \b{h}_\omega + \b{h}_{\omega'} > \b{h}_\mu + \b{h}_\nu \text{ for any exchangeable walks } \omega, \omega' \end{array}},
+\typeCone \big( \gvectorFan[\quiver] \big) = \set{\b{h} \in \R^{\walks}}{\begin{array}{l} \b{h}_\omega = 0 \text{ for any improper walk } \omega \\ \b{h}_\omega + \b{h}_{\omega'} > \b{h}_\mu + \b{h}_\nu \text{ for any exchangeable walks } \omega, \omega' \end{array}},
 \]
@@
 Consider the non-kissing fans illustrated in \cref{fig:nonkissingFans}.
-The type cone of the left fan of \cref{fig:nonkissingFans} lives in~$\R^9$ and has a linearity space of dimension~$3$.
-It has $6$ facet-defining inequalities (given below), which correspond to the flips described in \cref{prop:interestingExchangeablePairsNKC,prop:extremalExchangeablePairsNKC} and illustrated in \cref{fig:labelFacetDefiningInequalititiesNKC}\,(left).
+The type cone of the left fan of \cref{fig:nonkissingFans} lives in~$\R^8$ and has a linearity space of dimension~$3$.
+It has $5$ facet-defining inequalities (given below), which correspond to the flips described in \cref{prop:interestingExchangeablePairsNKC,prop:extremalExchangeablePairsNKC} and illustrated in \cref{fig:labelFacetDefiningInequalititiesNKC}\,(left).
 
@@
     \end{adjustbox}
-	\caption{The facet-defining inequalities of the type cone~$\typeCone(\gvectorFan[\quiver])$ of the non-kissing fan, represented on the Auslander Reiten quiver of the gentle algebra of~$\quiver$.
+	\caption{The facet-defining inequalities of the type cone~$\typeCone \big( \gvectorFan[\quiver] \big)$ of the non-kissing fan, represented on the Auslander Reiten quiver of the gentle algebra of~$\quiver$.
 While they correspond to meshes on the left, they are not as clear in the general case as on the right.
@@
 
-As illustrated in \cref{exm:typeConeNKC}, the type cone of the non-kissing fan is not simplicial and we do not always understand its extremal exchangeable pairs.
+As illustrated in \cref{exm:typeConeNKC}, the type cone of the non-kissing fan is not always simplicial and we do not always understand its extremal exchangeable pairs.
 In the next section section, we will explore a special family of gentle quivers for which we can completely describe the type cone.
-The combination of this special family with computer experiments in the general case support the following conjecture.
+The combination of this special family with computer experiments in the general case supports the following conjecture.
 
@@
 \begin{itemize}
-\item \defn{brick}: it satisfies the three equivalent conditions of \cref{prop:noSelfKissing},
-\item \defn{$2$-acyclic}: it contains no cycle of length~$2$.
+\item \defn{brick} if it satisfies the three equivalent conditions of \cref{prop:noSelfKissing},
+\item \defn{$2$-acyclic} if it contains no cycle of length~$2$.
 \end{itemize}
@@
 
-Note that this family already contains a lot of relevant examples, including the gentle grid and dissection quivers discussed in \cref{subsubsec:nonkissingComplex}.
+Note that the family of brick $2$-acyclic gentle quivers already contains a lot of relevant examples, including the gentle grid and dissection quivers discussed in \cref{subsubsec:nonkissingComplex}.
 In particular, the classical associahedron is the gentle associahedron of a brick $2$-acyclic gentle quiver.
@@
 For a string~$\sigma$ of~$\quiver$, we denote by $\sigma\hR$ (resp.~$\sigma\cR$) the unique string of the blossoming quiver~$\quiver\blossom$ of the form $\sigma\hR = \sigma \alpha_1^{-1} \alpha_2 \dots \alpha_\ell$ (resp.~$\sigma\cR = \sigma \alpha_1 \alpha_2^{-1} \dots \alpha_\ell^{-1}$) with~$\ell \ge 1$ and~${\alpha_1, \dots, \alpha_\ell \in Q_1}$ and such that~$t(\alpha_\ell)$ (resp.~$s(\alpha_\ell)$) is a blossom of~$\quiver\blossom$.
-These notations are motivated by the representation of strings used in~\cite{ButlerRingel, PaluPilaudPlamondon-nonkissing}, and the terminology usually says that~$\sigma\hR$ (resp.~$\sigma\cR$) is obtained by adding a \defn{hook} (resp.~\defn{cohook}) to~$\sigma$.
+These notations are motivated by the representation of strings used in~\cite{ButlerRingel, PaluPilaudPlamondon-nonkissing}, and the terminology usually says that~$\sigma\hR$ (resp.~$\sigma\cR$) is obtained by adding a \defn{hook} (resp.~a \defn{cohook}) to~$\sigma$.
 We define similarly~$\hL\sigma$ (resp.~$\cL\sigma$).
-The walk~$\hL(\sigma\hR) = (\hL\sigma)\hR$ of~$\quiver$ is simply be denoted~$\hh{\sigma}$, and we define similarly~$\cc{\sigma}$, $\hc{\sigma}$ and~$\ch{\sigma}$.
+The walk~$\hL(\sigma\hR) = (\hL\sigma)\hR$ of~$\quiver$ is simply denoted by~$\hh{\sigma}$, and we define similarly~$\cc{\sigma}$, $\hc{\sigma}$ and~$\ch{\sigma}$.
 
@@
 We can therefore assume that $\tau$ appears completely before or completely after~$\sigma$ in both~$\mu$ and~$\nu$.
-We distinguish the different cases:
+We distinguish two different cases:
 \begin{itemize}
-\item If~$\tau$ appears before~$\sigma$ in both~$\mu$ and~$\nu$, then~$\alpha \tau \alpha'$ form a cycle in~$\quiver$.
+\item If~$\tau$ appears before~$\sigma$ in both~$\mu$ and~$\nu$, then~$\alpha \tau \alpha'$ forms a cycle in~$\quiver$.
 If~$\tau$ is reduced to a vertex, then we have a $2$-cycle.
@@
 \item If~$\tau$ appears before~$\sigma$ in~$\mu$ and after~$\sigma$ in~$\nu$, then~$\omega$, $\mu$ and~$\nu$ finish at the same blossom so that~$\mu$ and~$\nu$ are not kissing at~$\tau$.
-The case when~$\tau$ appears after~$\sigma$ in~$\mu$ and before~$\sigma$ in~$\nu$ is identical.
+The case when~$\tau$ appears after~$\sigma$ in~$\mu$ and before~$\sigma$ in~$\nu$ is symmetric.
 \end{itemize}
@@
 
-We claim that~$\omega$ is distinguished at~$\alpha$ and~$\beta$ in the facet~$F$, that~$\mu$ is distinguished at~$\alpha'$ and that~$\nu$ is distinguished at~$\beta'$.
+We claim that~$\omega$ is distinguished at~$\alpha$ and~$\beta$ in~$F$, that~$\mu$ is distinguished at~$\alpha'$ in~$F$ and that~$\nu$ is distinguished at~$\beta'$ in~$F$.
 Let us just prove that~$\mu$ is distinguished at~$\alpha'$, the other statements being similar.
@@
 
-The following statement describes the type cone of the non-kissing fan of a gentle quiver with no self-kissing walks.
+The following statement describes the type cone of the non-kissing fan of a brick $2$-acyclic gentle quiver.
 
@@
 \]
-Therefore, the outer normal vector of the corresponding inequality of the type cone~$\typeCone(\gvectorFan[\quiver])$ is
+Therefore, the inner normal vector of the corresponding inequality of the type cone~$\typeCone \big( \gvectorFan[\quiver] \big)$ is
 \[
@@
 \]
-We claim that this normal vector is always a positive linear combination of the normal vectors~$\b{m}(\sigma) \eqdef \b{n}(\cc{\sigma}, \hh{\sigma}) = \b{f}_{\cc{\sigma}} + \b{f}_{\hh{\sigma}} - \b{f}_{\hc{\sigma}} - \b{f}_{\ch{\sigma}}$ for all string~$\sigma \in \strings$.
+We claim that this normal vector is always a positive linear combination of the normal vectors~$\b{m}(\sigma) \eqdef \b{n}(\cc{\sigma}, \hh{\sigma}) = \b{f}_{\cc{\sigma}} + \b{f}_{\hh{\sigma}} - \b{f}_{\hc{\sigma}} - \b{f}_{\ch{\sigma}}$ for all strings~$\sigma \in \strings$.
 Our proof works by descending induction on the length~$\lambda(\omega,\omega') \eqdef \ell(\sigma)$ of the common substring of~$\omega$ and~$\omega'$.
@@
 \label{coro:simplicialTypeConeNKC}
-For any brick $2$-acyclic gentle quiver~$\quiver$, the type cone~$\typeCone(\gvectorFan[\quiver])$ of the non-kissing fan~$\quiver$ is simplicial.
+For any brick $2$-acyclic gentle quiver~$\quiver$, the type cone~$\typeCone \big( \gvectorFan[\quiver] \big)$ of the non-kissing fan~$\quiver$ is simplicial.
 \end{corollary}
@@
 \end{corollary}
-
-\begin{proof}
-\cref{prop:extremalExchangeablePairsNKC} asserts that the type cone~$\typeCone(\gvectorFan[\quiver])$ has one facet for each string of~$\quiver$.
-Since all strings are distinguishable by \cref{prop:noSelfKissing}, the number of facets of~$\typeCone(\gvectorFan[\quiver])$ is $|\strings| = |\distinguishableStrings| = |\properWalks| - |Q_0|$ by~\cref{prop:bijectionStringsWalks}, so that~$\typeCone(\gvectorFan[\quiver])$ is simplicial.
-We then conclude by a simple application of \cref{coro:simplicialTypeCone}.
-\end{proof}
 
@@
 \label{exm:nonSimplicialTypeConeNKC}
-Note that \cref{prop:interestingExchangeablePairsNKC,prop:extremalExchangeablePairsNKC} and therefore~\cref{coro:simplicialTypeConeNKC,coro:allPolytopalRealizationsNKC} fail when the quiver is not brick or not $2$-acyclic.
+Note that \cref{prop:interestingExchangeablePairsNKC,prop:extremalExchangeablePairsNKC} and therefore~\cref{coro:simplicialTypeConeNKC,coro:allPolytopalRealizationsNKC} fail when the quiver is not brick or $2$-cyclic.
 The smallest exemples are the $2$-cycles whose non-kissing fans are represented in \cref{fig:nonkissingFans2}.
 The left one is not brick: it has a non-distinguishable string and a self-kissing walk.
-The right one is brick but is not $2$-acyclic.
+The right one is brick but is $2$-cyclic.
 
@@
 (since the fans are the same, the type cones are the same and we therefore present them together).
-
-Note that both assumptions of \cref{def:brick2acyclic} are needed for \cref{prop:interestingExchangeablePairsNKC,prop:extremalExchangeablePairsNKC}.
-Indeed, these statements fail for the quiver of \cref{fig:nonkissingFans}\,(left) which is $2$-acyclic but not brick and for the quiver of \cref{fig:nonkissingFans2} which is brick but $2$-cyclic.
+\cref{fig:nonkissingFans}\,(right) gives another example of brick but $2$-cyclic gentle quiver for which \cref{prop:interestingExchangeablePairsNKC,prop:extremalExchangeablePairsNKC} fail.
 
@@
 \begin{theorem}[\cite{CarrDevadoss, Devadoss, Postnikov, FeichtnerSturmfels, Zelevinsky}]
-For any graph~$\graphG$, the nested fan~$\gvectorFan[\graphG]$ is the normal fan of the graph associahedron~$\Asso[\graphG]$, defined as the Minkowski sum~$\sum_{\tube \in \tubes} \triangle_{\tube}$ of the faces of the standard simplex corresponding to all tubes of~$\graphG$.
+For any graph~$\graphG$, the nested fan~$\gvectorFan[\graphG]$ is the normal fan of the graph associahedron~$\Asso[\graphG]$.
+It can be constructed as
+\begin{itemize}
+\item the intersection of~$\HH$ with the hyperplanes~$\dotprod{\gvector{\tube}}{\b{x}} \le 3^{|\tube|-2}$ for all tubes~$\tube \in \tubes$~\cite{Devadoss},
+\item the Minkowski sum~$\sum_{\tube \in \tubes} \triangle_{\tube}$ of the faces of the standard simplex corresponding to all tubes of~$\graphG$~\cite{Postnikov}.
+\end{itemize}
 \end{theorem}
@@
 \[
-\typeCone(\gvectorFan[\graphG]) = \set{\b{h} \in \R^{\tubes}}{\begin{array}{l} \b{h}_{\tube} = 0 \text{ for any improper tube } \tube \\ \b{h}_{\tube} + \b{h}_{\tube'} > \b{h}_{\tube \cup \tube'} + \sum_{\tube[s] \in \connectedComponents(\tube \cap \tube')} \b{h}_{\tube[s]} \text{ for any exchangeable tubes } \tube, \tube' \end{array}}.
+\typeCone \big( \gvectorFan[\graphG] \big) = \set{\b{h} \in \R^{\tubes}}{\begin{array}{l} \b{h}_{\tube} = 0 \text{ for any improper tube } \tube \\ \b{h}_{\tube} + \b{h}_{\tube'} > \b{h}_{\tube \cup \tube'} + \sum_{\tube[s] \in \connectedComponents(\tube \cap \tube')} \b{h}_{\tube[s]} \text{ for any exchangeable tubes } \tube, \tube' \end{array}}.
 \]
@@
 We now consider an arbitrary graph~$\graphG$ and describe the type cone of its nested fan.
-\cref{prop:extremalExchangeablePairsA} extends as follows.
+We give a necessary condition for an exchangeable pair to be extremal in \cref{lem:extremalExchangeablePairsGAonlyif}, exploit it in \cref{exm:constructionsGA}, and prove that it is actually a sufficient condition in \cref{prop:extremalExchangeablePairsGA}
 
@@
 \label{lem:extremalExchangeablePairsGAonlyif}
-Two tubes~$\tube$ and~$\tube'$ of~$\graphG$ form an extremal exchangeable pair for the nested fan of~$\graphG$ only if~${\tube \ssm \{v\} = \tube' \ssm \{v'\}}$ for some neighbor~$v$ of~$\tube'$ and some neighbor~$v'$ of~$\tube$.
+If two tubes~$\tube$ and~$\tube'$ of~$\graphG$ form an extremal exchangeable pair for the nested fan of~$\graphG$, then~${\tube \ssm \{v\} = \tube' \ssm \{v'\}}$ for some neighbor~$v$ of~$\tube'$ and some neighbor~$v'$ of~$\tube$.
 \end{lemma}
@@
 Consider an exchangeable pair~$\{\tube, \tube'\}$ of tubes of~$\graphG$.
-The outer normal vector of the corresponding inequality of the type cone is
+The inner normal vector of the corresponding inequality of the type cone is
 \[
@@
 Therefore, $\tube \ssm \tube'$ and~$\tube' \ssm \tube$ are both connected.
-Assume that $\tube \ssm \tube'\neq \{v\}$, and let $w\neq v$ be a non-disconnecting node of $\tube \ssm \tube'$.
-Then $\tilde \tube:=\tube \ssm \{w\}$ and $\tube'$ are exchangeable, and $\tilde \tube':=(\tube \cup \tube')\ssm \{w\}$ and $\tube$ are exchangeable as well.
-We have
+Assume that $\tube \ssm \tube'\ne \{v\}$, and let $w\ne v$ be a non-disconnecting node of $\tube \ssm \tube'$.
+By \cref{prop:exchangeablePairsGA}, $\tilde \tube \eqdef \tube \ssm \{w\}$ and $\tube'$ are exchangeable, and $\tilde \tube' \eqdef (\tube \cup \tube') \ssm \{w\}$ and $\tube$ are exchangeable as well.
+Moreover, we have
 \begin{align*}
-\b{n}(\tilde \tube, \tube')+\b{n}( \tube, \tilde \tube') &=\b{f}_{\tilde \tube} + \b{f}_{\tube'} - \b{f}_{\tilde \tube\cup \tube'} - \sum_{\tube[s] \in \connectedComponents(\tilde \tube \cap \tube')} \b{f}_{\tube[s]}
-+ \b{f}_{\tube} + \b{f}_{\tilde \tube'} - \b{f}_{\tube\cup \tilde \tube'} - \sum_{\tube[s] \in \connectedComponents(\tube \cap \tilde \tube')} \b{f}_{\tube[s]} \\
-&= \b{f}_{\tube} + \b{f}_{\tube'} - \b{f}_{\tube\cup \tube'} - \sum_{\tube[s] \in \connectedComponents(\tube \cap \tube')} \b{f}_{\tube[s]} =\b{n}(\tube, \tube'),
+\b{n}(\tilde \tube, \tube') + \b{n}( \tube, \tilde \tube')
+& = \Big( \b{f}_{\tilde \tube} + \b{f}_{\tube'} - \b{f}_{\tilde \tube\cup \tube'} - \sum_{\tube[s] \in \connectedComponents(\tilde \tube \cap \tube')} \b{f}_{\tube[s]} \Big)
++ \Big( \b{f}_{\tube} + \b{f}_{\tilde \tube'} - \b{f}_{\tube\cup \tilde \tube'} - \sum_{\tube[s] \in \connectedComponents(\tube \cap \tilde \tube')} \b{f}_{\tube[s]} \Big) \\
+& = \b{f}_{\tube} + \b{f}_{\tube'} - \b{f}_{\tube\cup \tube'} - \sum_{\tube[s] \in \connectedComponents(\tube \cap \tube')} \b{f}_{\tube[s]} =\b{n}(\tube, \tube'),
 \end{align*}
-as $\tube \cup \tilde \tube'=\tube \cup \tube'$, $\tilde \tube \cap \tube'=\tube \cap \tube'$, $\tilde \tube \cup \tube '=\tilde \tube '$,  and $\tube \cap \tilde \tube '=\tilde \tube$.
-% \[\b{n}(\tube, \tube')=\b{n}(\tilde \tube, \tube')+\b{n}( \tube, \tilde \tube'),\] 
+as $\tilde \tube \cup \tube' = \tilde \tube'$, $\tilde \tube \cap \tube' = \tube \cap \tube'$, $\tube \cup \tilde \tube' = \tube \cup \tube'$ and $\connectedComponents(\tube \cap \tilde \tube') = \connectedComponents(\tilde \tube) = \tilde \tube$.
 Therefore $\b{n}(\tube, \tube')$ defines a redundant inequality and $\{\tube, \tube'\}$ is not an extremal exchangeable pair.
+The proof is symmetric if~$\tube' \ssm \tube \ne \{v'\}$.
 \end{proof}
@@
 \begin{example}
-Let $\graphG$ be a graph. Consider the vectors $\b{a}, \b{b}, \b{c}\in\R^{\tubes}$ whose entries for $\tube[s]\in\tubes$ are given by 
-$\b{a}_{\tube[s]}=-\big| \set{\tube[u]\in\tubes}{\tube[u]\subseteq \tube[s]}\big| $, $\b{b}_{\tube[s]}=-3^{\big| \tube[s]\big| -2}$, and $\b{c}_{\tube[s]}=-\big| \set{\tube[u]\in\tubes}{\tube[u]\supseteq \tube[s]}\big| $, respectively.
-
-Now, let $\tube$ and~$\tube'$ be tubes such that ${\tube \ssm \{v\} = \tube' \ssm \{v'\}}$ for some neighbor~$v$ of~$\tube'$ and some neighbor~$v'$ of~$\tube$, and let 
-$\b{n}(\tube, \tube')$ be as in~\cref{lem:extremalExchangeablePairsGAonlyif}.
-
-We have
-\[\dotprod{\b{n}(\tube, \tube')}{\b{a}}=\big|\set{\tube[u]\in\tubes}{\tube[u]\subseteq\tube[t]\cup\tube[t']\text{ and }v,v'\in\tube[u]}|,\]
-which is positive since at least $\tube[u]=\tube[t]\cup\tube[t']$ fulfills this condition.
-Hence $\b{a}\in\typeCone(\gvectorFan[\graphG])$.
-This gives Postnikov's realization of the graph associahedron from~\cite{Postnikov}.
-
-Setting $x=|\tube \cap \tube'|$, we get
-\[\dotprod{\b{n}(\tube, \tube')}{\b{b}}=3^{|\tube[t]\cup\tube[t']| -2}- 3^{|\tube[t]| -2}- 3^{|\tube[t']| -2} +\sum_{\tube[s] \in \connectedComponents(\tube \cap \tube')} 3^{|\tube[s]|-2 }\geq 3^{x}- 2\cdot 3^{x-1}>0.\]
-This shows that $\b{b}\in\typeCone(\gvectorFan[\graphG])$, and we recover Devadoss' realization of graph-associahedra~\cite{Devadoss}.
-
-Finally, 
-\[\dotprod{\b{n}(\tube, \tube')}{\b{c}}=\big| \set{(\tube[u], \tube[s])\in\tubes\times \connectedComponents(\tube[t]\cap\tube[t'])}{\tube[s]\subseteq\tube[u]\text{ and }\tube,\tube'\not\subseteq u}\big| +(\big| \connectedComponents(\tube[t]\cap\tube[t'])\big| -1)\big| \set{\tube[u]\in\tubes}{\tube\text{ or }\tube'\subseteq \tube[u]}\big| .\]
-Any connected component of $\tube\cap \tube'$ certifies the positivity of this evaluation, showing that $\b{c}\in\typeCone(\gvectorFan[\graphG])$. This realization of 
-the graph-associahedron is new, to the best of our knowledge. 
-\arnau{Is it worth to add it?}
-\arnau{recheck details}
-
+\label{exm:constructionsGA}
+We now exploit \cref{lem:extremalExchangeablePairsGAonlyif} to show that certain height functions belong to the type cone of~$\gvectorFan[\graphG]$ and recover the classical constructions of the graph associahedron.
+
+\begin{enumerate}
+\item Consider the height function~$\b{h} \in \R^{\tubes}$ given by~$\b{h}_{\tube} \eqdef -|\bigset{\tube[s] \in \tubes}{\tube[s] \subseteq \tube}|$.
+Then for any tubes~$\tube$ and~$\tube'$ such that ${\tube \ssm \{v\} = \tube' \ssm \{v'\}}$ for some neighbor~$v$ of~$\tube'$ and some neighbor~$v'$ of~$\tube$, we have
+\[
+\qquad\qquad
+\dotprod{\b{n}(\tube, \tube')}{\b{h}} = |\bigset{\tube[s]\in\tubes}{\tube[s] \subseteq \tube[t] \cup \tube' \text{ and } v, v' \in \tube[s]}|,
+\]
+which is positive since at least~$\tube \cup \tube'$ fulfills the condition.
+Thus, $\b{h}$ belongs to the type cone~$\typeCone \big( \gvectorFan[\graphG] \big)$.
+The polytope~$P_\b{h} \eqdef \set{\b{x} \in \R^\ground}{\dotprod{\gvector{\tube}}{\b{x}} \le \b{h}_{\tube} \text{ for any tube } \tube \in \tubes}$ is the graph associahedron constructed by A.~Postnikov's in~\cite{Postnikov}.
+\item Consider now the height function~$\b{h} \in \R^{\tubes}$ given by~$\b{h}_{\tube} \eqdef -3^{|\tube|-2}$.
+Then for any tubes~$\tube$ and~$\tube'$ such that ${\tube \ssm \{v\} = \tube' \ssm \{v'\}}$ for some neighbor~$v$ of~$\tube'$ and some neighbor~$v'$ of~$\tube$, we have
+\[
+\qquad\qquad
+\dotprod{\b{n}(\tube, \tube')}{\b{h}} = - 3^{|\tube|-2} - 3^{|\tube'|-2} + 3^{|\tube \cup \tube'|-2} + \sum_{\tube[s] \in \connectedComponents(\tube \cap \tube')} 3^{|\tube[s]|-2 } \ge - 2 \cdot 3^{|\tube \cup \tube'|-1} + 3^{|\tube \cup \tube'|} > 0.
+\]
+Thus, $\b{h}$ belongs to the type cone~$\typeCone \big( \gvectorFan[\graphG] \big)$.
+The corresponding polytope~$P_\b{h}$ is the graph associahedron constructed by S.~Devadoss's in~\cite{Devadoss}.
+\item Finally, consider the height function~$\b{h} \in \R^{\tubes}$ given by~$\b{h}_{\tube} \eqdef |\bigset{\tube[s] \in \tubes}{\tube[s] \supseteq \tube}|$.
+Then for any tubes~$\tube$ and~$\tube'$ such that ${\tube \ssm \{v\} = \tube' \ssm \{v'\}}$ for some neighbor~$v$ of~$\tube'$ and some neighbor~$v'$ of~$\tube$, we have
+\begin{align*}
+\qquad\qquad
+\dotprod{\b{n}(\tube, \tube')}{\b{h}} = \; & |\bigset{\tube[r] \in \tubes, \tube[s] \in \connectedComponents(\tube \cap \tube')}{\tube[s] \subseteq \tube[r] \text{ and } \tube, \tube' \not\subseteq \tube[r]}| \\
+& + \big( |\connectedComponents(\tube \cap \tube')|-1 \big) \cdot | \bigset{\tube[r] \in \tubes}{\tube \text{ or } \tube'\subseteq \tube[r]}\big|.
+\end{align*}
+Any connected component of~$\tube \cap \tube'$ certifies the positivity of this evaluation, showing that $\b{h}$ belongs to~$\typeCone \big( \gvectorFan[\graphG] \big)$.
+The corresponding realization~$P_\b{h}$ of the graph associahedron is new, to the best of our knowledge.
+\end{enumerate}
 \end{example}
+
+We now show that the condition of \cref{lem:extremalExchangeablePairsGAonlyif} actually characterizes the extremal exchangeable pairs of the nested fan~$\gvectorFan[\graphG]$.
 
@@
 \begin{proof}
-
-We have seen that an exchangeable pair $\{\tube, \tube'\}$ is not extremal unless both $\tube\ssm \tube'$ and $\tube'\ssm \tube$ are singletons.
+By \cref{lem:extremalExchangeablePairsGAonlyif}, an exchangeable pair $\{\tube, \tube'\}$ is not extremal unless both $\tube \ssm \tube'$ and $\tube' \ssm \tube$ are singletons.
 We now need to show that all these pairs are extremal.
@@
 Let $\{\tube, \tube'\}$ be a suspected extremal pair.
-To prove that it is extremal, we will construct a vector $\b{w}\in\R^{\tubes}$ such that $\dotprod{\b{n}(\tube, \tube')}{\b{w}}< 0,$
+To prove that it is extremal, we will construct a vector $\b{w} \in \R^{\tubes}$ such that $\dotprod{\b{n}(\tube, \tube')}{\b{w}}< 0,$
 but $\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{w}}>0$ for any other suspected extremal pair $\{\tilde \tube, \tilde \tube'\}$.
@@
 
-Define $\alpha(\tube,\tube')=\set{\tube[u]\in\tubes}{\tube[u]\subseteq \tube \cup \tube'\text{ and } \tube\triangle\tube'\subseteq \tube[u]}$, where $\tube\triangle\tube'$ denotes the symmetric difference, and let $\b{x}\in\R^{\tubes}$ be such that
-\[\b{x}_{\tube[s]}=-\big|\set{\tube[u]\in \tubes\ssm \alpha(\tube,\tube')}{\tube[u]\subseteq \tube[s]}\big|\]
-for each tube~$\tube[s]\in\tubes$.
+Define $\alpha(\tube,\tube') \eqdef \set{\tube[u] \in \tubes}{\tube[u] \subseteq \tube \cup \tube' \text{ and } \tube \symdif \tube' \subseteq \tube[u]}$, where $\symdif$ denotes the symmetric difference, and let $\b{x} \in \R^{\tubes}$ be such that
+\[
+\b{x}_{\tube[s]} = -|\bigset{\tube[u] \in \tubes \ssm \alpha(\tube, \tube')}{\tube[u] \subseteq \tube[s]}|
+\]
+for each tube~$\tube[s] \in \tubes$.
 
 For any suspected extremal pair $\{\tilde \tube, \tilde \tube'\}$ we have
-\[\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{x}}= \big|\alpha(\tilde \tube, \tilde \tube ')\ssm \alpha(\tube,\tube')|\geq0.\]
-Notice that $\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{x}}=0$ if $\alpha(\tilde \tube, \tilde \tube ')\subseteq \alpha(\tube,\tube')$ and
-$\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{x}}\geq 1$ otherwise.
-In particular, if $\{\tilde \tube, \tilde \tube'\}\neq \{\tube, \tube'\}$ then
-$\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{x}}\geq 1$ unless $\tilde \tube\cup \tilde \tube'\subsetneq \tube\cup \tube'$ because 
- $\tilde \tube\cup \tilde \tube'\in\alpha(\tilde \tube, \tilde \tube ')$, and if $\tilde \tube\cup \tilde \tube'=\tube\cup \tube'$ but $\{\tilde \tube, \tilde \tube'\}\neq \{\tube, \tube'\}$, then either $\tube$ or $\tube'$ will belong to $\alpha(\tilde \tube, \tilde \tube ')$.
-
-Now, define $\b{y}\in\R^{\tubes}$ by \[\b{y}_{\tube[s]}=\begin{cases}
-                             -1&\text{ if }|\tube[s]|\geq |\tube|\\
-                             0&\text{ otherwise.}
-                            \end{cases}\]
-We have $\dotprod{\b{n}(\tube, \tube')}{\b{y}}=-1$.
-For any suspected extremal pair $\{\tilde \tube, \tilde \tube'\}$ we have $\dotprod{\b{n}(\tube, \tube')}{\b{y}}\geq -1$.
-If moreover $\tilde \tube\cup \tilde \tube'\subsetneq \tube\cup \tube'$, then we have $\dotprod{\b{n}(\tube, \tube')}{\b{y}}\geq 0$.
-
-Finally, consider $\b{z}\in\R^{\tubes}$ given by
-\[\b{z}_{\tube[s]}=-\big|\set{\tube[u]\in \alpha(\tube,\tube')}{\tube[u]\subseteq \tube[s]}\big|. \]
-It verifies $\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{z}}\geq0$ for any suspected extremal pair~$\{\tilde \tube, \tilde \tube'\}$, and $\dotprod{\b{n}(\tube, \tube')}{\b{z}}=|\alpha(\tilde \tube, \tilde \tube ')|>0$ if $\alpha(\tilde \tube, \tilde \tube ')\subseteq \alpha(\tube,\tube')$.
-
-For $0<\varepsilon<1$, and $0<\delta<\frac{\varepsilon}{|\alpha(\tube,\tube')|}$, the vector $\b{w}=\b{x}+\varepsilon \b{y}+\delta \b{z}$ fulfills the desired properties.
-Indeed, if $\{\tilde \tube, \tilde \tube'\}\neq \{\tube,\tube '\}$ is a suspected extremal pair with $\alpha(\tilde \tube, \tilde \tube ')\not \subseteq \alpha(\tube,\tube')$, then 
-\[\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{w}}=\underbrace{\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{x}}}_{\geq 1}+\underbrace{\varepsilon \dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{y}}}_{> -1}+\underbrace{\delta \dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{z}}}_{\geq 0}> 0.\]
- If $\{\tilde \tube, \tilde \tube'\}\neq \{\tube,\tube '\}$ is a suspected extremal pair with $\alpha(\tilde \tube, \tilde \tube ')\subseteq \alpha(\tube,\tube')$, then $\tilde \tube\cup \tilde \tube'\subsetneq \tube\cup \tube'$ and
-\[\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{w}}=\underbrace{\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{x}}}_{=0}+\underbrace{\varepsilon \dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{y}}}_{\geq 0}+\underbrace{\delta \dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{z}}}_{>0}> 0.\]
+\[
+\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{x}} = |\alpha(\tilde \tube, \tilde \tube')\ssm \alpha(\tube, \tube')| \ge 0.
+\]
+Notice that $\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{x}} = 0$ if $\alpha(\tilde \tube, \tilde \tube') \subseteq \alpha(\tube,\tube')$ and $\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{x}} \ge 1$ otherwise.
+In particular, if $\{\tilde \tube, \tilde \tube'\} \ne \{\tube, \tube'\}$ then $\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{x}} \ge 1$ unless $\tilde \tube \cup \tilde \tube' \subsetneq \tube \cup \tube'$ because $\tilde \tube \cup \tilde \tube' \in \alpha(\tilde \tube, \tilde \tube')$, and if $\tilde \tube \cup \tilde \tube' = \tube \cup \tube'$ but $\{\tilde \tube, \tilde \tube'\} \ne \{\tube, \tube'\}$, then either $\tube$ or $\tube'$ will belong to $\alpha(\tilde \tube, \tilde \tube')$.
+
+Now, define $\b{y}\in\R^{\tubes}$ by
+\[
+\b{y}_{\tube[s]} \eqdef \begin{cases}
+	-1 & \text{ if } |\tube[s]| \ge |\tube| \\
+	0 & \text{ otherwise.}
+\end{cases}
+\]
+We have $\dotprod{\b{n}(\tube, \tube')}{\b{y}} = -1$.
+For any suspected extremal pair $\{\tilde \tube, \tilde \tube'\}$ we have $\dotprod{\b{n}(\tube, \tube')}{\b{y}}\ge -1$.
+If moreover $\tilde \tube \cup \tilde \tube' \subsetneq \tube \cup \tube'$, then we have $\dotprod{\b{n}(\tube, \tube')}{\b{y}} \ge 0$.
+
+Finally, consider $\b{z} \in \R^{\tubes}$ given by
+\[
+\b{z}_{\tube[s]} = -|\bigset{\tube[u] \in \alpha(\tube, \tube')}{\tube[u] \subseteq \tube[s]}|.
+\]
+It verifies $\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{z}} \ge 0$ for any suspected extremal pair~$\{\tilde \tube, \tilde \tube'\}$, and $\dotprod{\b{n}(\tube, \tube')}{\b{z}} = |\alpha(\tilde \tube, \tilde \tube')| > 0$ if $\alpha(\tilde \tube, \tilde \tube') \subseteq \alpha(\tube, \tube')$.
+
+For $0 < \varepsilon < 1$, and $0 < \delta < \frac{\varepsilon}{|\alpha(\tube, \tube')|}$, the vector $\b{w} \eqdef \b{x} + \varepsilon \b{y} + \delta \b{z}$ fulfills the desired properties.
+Indeed, if $\{\tilde \tube, \tilde \tube'\} \ne \{\tube,\tube'\}$ is a suspected extremal pair with $\alpha(\tilde \tube, \tilde \tube') \not \subseteq \alpha(\tube,\tube')$, then 
+\[
+\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{w}} = \underbrace{\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{x}}}_{\ge 1} + \underbrace{\varepsilon \dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{y}}}_{> -1} + \underbrace{\delta \dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{z}}}_{\ge 0} > 0.
+\]
+If $\{\tilde \tube, \tilde \tube'\} \ne \{\tube,\tube'\}$ is a suspected extremal pair with $\alpha(\tilde \tube, \tilde \tube') \subseteq \alpha(\tube,\tube')$, then $\tilde \tube \cup \tilde \tube' \subsetneq \tube \cup \tube'$ and
+\[
+\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{w}} = \underbrace{\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{x}}}_{= 0} + \underbrace{\varepsilon \dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{y}}}_{\ge 0} + \underbrace{\delta \dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{z}}}_{> 0} > 0.
+\]
 However,
-\[\dotprod{\b{n}(\tube, \tube')}{\b{w}}=\underbrace{\dotprod{\b{n}(\tube, \tube')}{\b{x}}}_{=0}+\underbrace{\varepsilon \dotprod{\b{n}(\tube, \tube')}{\b{y}}}_{=-\varepsilon}+\underbrace{\delta \dotprod{\b{n}( \tube,  \tube')}{\b{z}}}_{=\delta|\alpha(\tube ,\tube')|<\varepsilon}< 0.\]
-
+\[
+\dotprod{\b{n}(\tube, \tube')}{\b{w}} = \underbrace{\dotprod{\b{n}(\tube, \tube')}{\b{x}}}_{= 0} + \underbrace{\varepsilon \dotprod{\b{n}(\tube, \tube')}{\b{y}}}_{= -\varepsilon} + \underbrace{\delta \dotprod{\b{n}( \tube,  \tube')}{\b{z}}}_{= \delta |\alpha(\tube ,\tube')| < \varepsilon} < 0.
+\qedhere
+\]
 \end{proof}
@@
 \label{coro:extremalExchangeablePairsGA}
-The extremal exchangeable pairs for the nested fan of~$\graphG$ are the pairs of tubes~$\tube[s] \ssm \{v'\}$ and~$\tube[s] \ssm \{v\}$ for any tube~$\tube[s] \in \tubes$ and distinct non-disconnecting vertices~$v,v'$ of~$\tube[s]$.
-% equivalently
-% \begin{enumerate}[(i)]
-% \item the pairs of tubes~$\tube[r] \cup \{v\}$ and~$\tube[r] \cup \{v'\}$ for any tube~$\tube[r] \in \tubes$ and distinct neighbors~$v,v'$ of~$\tube[r]$,
-% \item the pairs of tubes~$\tube[s] \ssm \{v'\}$ and~$\tube[s] \ssm \{v\}$ for any tube~$\tube[s] \in \tubes$ and distinct non-disconnecting vertices~$v,v'$ of~$\tube[s]$,
-% \end{enumerate}
+The extremal exchangeable pairs for the nested fan of~$\graphG$ are precisely the pairs of tubes~${\tube[s] \ssm \{v'\}}$ and~${\tube[s] \ssm \{v\}}$ for any tube~$\tube[s] \in \tubes$ and distinct non-disconnecting vertices~$v,v'$~of~$\tube[s]$.
 \end{corollary}
-\arnau{The two conditions were not equivalent. I removed the wrong one.}
 
 We derive from \cref{prop:extremalExchangeablePairsGA} and \cref{coro:extremalExchangeablePairsGA} all polytopal realizations of the nested fan, which we can explicitly express.
-% using one of the following two equivalent conditions.
 
@@
  $\b{h}_{\tube[s] \ssm \{v'\}} + \b{h}_{\tube[s] \ssm \{v\}} > \b{h}_{\tube[s]} + \b{h}_{\tube[s] \ssm \{v, v'\}}$ for any tube~$\tube[s] \in \tubes$ and distinct non-disconnecting vertices~$v,v'$ of~$\tube[s]$.
-% one of the two following equivalent conditions:
-% \begin{enumerate}[(i)]
-% \item $\b{h}_{\tube[r] \cup \{v\}} + \b{h}_{\tube[r] \cup \{v'\}} > \b{h}_{\tube[r] \cup \{v, v'\}} + \b{h}_{\tube[r]}$ for any tube~$\tube[r] \in \tubes$ and distinct neighbors~$v,v'$ of~$\tube[r]$,
-% \item $\b{h}_{\tube[s] \ssm \{v'\}} + \b{h}_{\tube[s] \ssm \{v\}} > \b{h}_{\tube[s]} + \b{h}_{\tube[s] \ssm \{v, v'\}}$ for any tube~$\tube[s] \in \tubes$ and distinct non-disconnecting vertices~$v,v'$ of~$\tube[s]$.
-% \end{enumerate}
-
 Then the nested fan~$\gvectorFan[\graphG]$ is the normal fan of the graph associahedron
@@
 %\begin{proof}
-%By \cref{prop:extremalExchangeablePairsGA}, extremal exchangeable pairs are in bijection with quadruples~$(\tube[r], \tube[t], \tube[t'], \tube[s])$ of tubes of~$\graphG$ where~$\tube[t]$ and~$\tube[t']$ are distinct tubes covering~$\tube[r]$ and covered by~$\tube[s]$ in the inclusion poset of all tubes of~$\graphG$.
+%By \cref{prop:extremalExchangeablePairsGA}, extremal exchangeable pairs are in bijection with quadruples~$(\tube[r], \tube[t], \tube', \tube[s])$ of tubes of~$\graphG$ where~$\tube[t]$ and~$\tube'$ are distinct tubes covering~$\tube[r]$ and covered by~$\tube[s]$ in the inclusion poset of all tubes of~$\graphG$.
 %The result immediately follows.
@@
 \begin{proposition}
-The type cone~$\typeCone(\gvectorFan[\graphG])$ is simplicial if and only if~$\graphG$ is a path.
+The type cone~$\typeCone \big( \gvectorFan[\graphG] \big)$ is simplicial if and only if~$\graphG$ is a path.
 \end{proposition}
@@
  \]
- Therefore~$\langle x, [A] \rangle = \dim_{\field} \coker(f) \geq 0$.
+ Therefore~$\langle x, [A] \rangle = \dim_{\field} \coker(f) \ge 0$.
 \end{proof}
@@
 One can check directly that the condition of Theorem~\ref{theo::brick-algebra-condition} is not satisfied.
-For example, the module~$\bsm2\\1\esm$ is~$\tau$-rigid since~$\tau(\bsm2\\1\esm) = \bsm3\\1\esm$, while~$\Hom{\Lambda}\left(\bsm2\\1\esm,\tau^2(\bsm2\\1\esm)\right) = \Hom{\Lambda}(\bsm2\\1\esm,\bsm1\\2\esm) \neq 0$.
+For example, the module~$\bsm2\\1\esm$ is~$\tau$-rigid since~$\tau(\bsm2\\1\esm) = \bsm3\\1\esm$, while~$\Hom{\Lambda}\left(\bsm2\\1\esm,\tau^2(\bsm2\\1\esm)\right) = \Hom{\Lambda}(\bsm2\\1\esm,\bsm1\\2\esm) \ne 0$.
 \end{example}

### 2019-06-10 thirdPaper/draft/typeConeAssociahedra.tex
citations

@@
 
-\begin{theorem}[{\cite[Theorem~1.4]{FominZelevinsky-ClusterAlgebrasII}}]
+\begin{theorem}[{\cite[Thm.~1.4]{FominZelevinsky-ClusterAlgebrasII}}]
 \label{thm:finiteTypeClassification}
@@
 However, for cluster algebras of finite type, this linear dependence is independent of the choice of a seed containing~$x$ and~$x'$.
-As explained in ~\cref{corollary:UERPforCAproof}, this statement follows from~\cite[Theorem 7.5]{BuanMarshReinekeReitenTodorov}.
+As explained in ~\cref{corollary:UERPforCAproof}, this statement follows from~\cite[Thm.~7.5]{BuanMarshReinekeReitenTodorov}.
 We state it here for future reference.
-Note that the corresponding statement for cluster variables, instead of~$\b{g}$-vectors, holds by~\cite[Theorem 1.11]{FominZelevinsky-ClusterAlgebrasII}.
+Note that the corresponding statement for cluster variables, instead of~$\b{g}$-vectors, holds by~\cite[Thm.~1.11]{FominZelevinsky-ClusterAlgebrasII}.
 
@@
 
-\begin{proposition}[{\cite[3.68]{PaluPilaudPlamondon-nonkissing}}]
+\begin{proposition}[{\cite[Prop.~3.68]{PaluPilaudPlamondon-nonkissing}}]
 \label{prop:bijectionStringsWalks}
@@
  \begin{itemize}
-  \item[(i)] \emph{(}\cite[Proposition 3.2]{BuanMarshReinekeReitenTodorov} and~\cite[]{×} \emph{)} For any~$X,Y\in \ind(\cat)$, $\CC(X)$ and~$\CC(Y)$ are compatible if and only if~$\cat(X, \susp Y) = 0$.
-  \item[(ii)] \emph{(}\cite[Proposition 4.3]{FuKeller} and \emph{)} For any~$X\in \ind(\cat)$, the~$\b g$-vector of~$\CC(X)$ is~$\b g([X])$, where we identify~$\Z^n$ and~$\Kg(\cat)$ via the isomorphism sending~$(a_1, \ldots, a_n)$ to~$\sum_{i=1}^n a_i [T_i]$.
-  \item[(iii)] \emph{(}\cite[Theorem 7.5]{BuanMarshReinekeReitenTodorov} and~\cite[]{×} \emph{)} For any~$X,Y\in \ind(\cat)$, $\CC(X)$ and~$\CC(Y)$ are exchangeable if and only if~$\dim_{\field_X}\cat(X, \susp Y) = \dim_{\field_Y}\cat(X, \susp Y) = 1$.
+  \item[(i)] \emph{(}\cite[Prop.~3.2]{BuanMarshReinekeReitenTodorov} and~\cite[]{???} \emph{)} For any~$X,Y\in \ind(\cat)$, $\CC(X)$ and~$\CC(Y)$ are compatible if and only if~$\cat(X, \susp Y) = 0$.
+  \item[(ii)] \emph{(}\cite[Prop.~4.3]{FuKeller} and \emph{)} For any~$X\in \ind(\cat)$, the~$\b g$-vector of~$\CC(X)$ is~$\b g([X])$, where we identify~$\Z^n$ and~$\Kg(\cat)$ via the isomorphism sending~$(a_1, \ldots, a_n)$ to~$\sum_{i=1}^n a_i [T_i]$.
+  \item[(iii)] \emph{(}\cite[Thm.~7.5]{BuanMarshReinekeReitenTodorov} and~\cite[]{???—} \emph{)} For any~$X,Y\in \ind(\cat)$, $\CC(X)$ and~$\CC(Y)$ are exchangeable if and only if~$\dim_{\field_X}\cat(X, \susp Y) = \dim_{\field_Y}\cat(X, \susp Y) = 1$.
   \item[(iv)]\emph{(}\cite[???]{BuanMarshReinekeReitenTodorov} and~\cite[???]{BuanIyamaReitenScott} and ???\emph{)} Let~$T'$ be any basic cluster-tilting object of~$\cat$.
@@
 \begin{proof}
-In view of Theorem~\ref{thm::categorification} (iii), it follows from~\cite[Lemma 3.3]{Palu}
+In view of Theorem~\ref{thm::categorification} (iii), it follows from~\cite[Lem.~3.3]{Palu}
 \end{proof}
@@
 Assume moreover that~$\cat$ is $\field$-linear and Ext-finite.
-By the preliminary results of Section~\ref{subsection: prelim on extricats}, we can apply~\cite[Proposition 4.2]{IyamaNakaokaPalu} to obtain that~$\modt$ is Hom-finite.
+By the preliminary results of Section~\ref{subsection: prelim on extricats}, we can apply~\cite[Prop.~4.2]{IyamaNakaokaPalu} to obtain that~$\modt$ is Hom-finite.
 In particular, if $\tc=\add T$, then $\End{\cat}(T)$ is a finite-dimensional~$\field$-algebra.
@@
 
-\begin{definition}(\cite[Definition 2.12]{NakaokaPalu})
+\begin{definition}(\cite[Def.~2.12]{NakaokaPalu})
 A triple~$(\cat,\mathbb{E},\mathfrak{s})$ is called an \defn{extriangulated category} if the following holds:
@@
 
-\begin{proposition}\emph{(}\cite[Propositions 3.3, 3.11]{NakaokaPalu}\emph{)}
+\begin{proposition}\emph{(}\cite[Props.~3.3~\&~3.11]{NakaokaPalu}\emph{)}
 Assume that $(\cat,\mathbb{E},\mathfrak{s})$ is an extriangulated category, and let $X\xrightarrow{x}Y\xrightarrow{y}Z\overset{\delta}{\dashrightarrow}$ be an extriangle.
@@
 Any variant of the axiom (ET4) that would hold in an extension-closed subcategory of a triangulated category by applying the octahedron axiom also holds in any extriangulated category.
-See~\cite[Section 3.2]{NakaokaPalu} for more details.
+See~\cite[Sect.~3.2]{NakaokaPalu} for more details.
 
@@
 
-\begin{proposition}\emph{(}\cite[Proposition 2.5]{IyamaNakaokaPalu}\emph{)}
+\begin{proposition}\emph{(}\cite[Prop.~2.5]{IyamaNakaokaPalu}\emph{)}
 For any non-split $\mathbb{E}$-extension $\delta\in\mathbb{E}(Z,X)$, the following holds.
@@
 
-\begin{proposition}\emph{(}\cite[Proposition 8.1]{IyamaNakaokaPalu}\emph{)}
+\begin{proposition}\emph{(}\cite[Prop.~8.1]{IyamaNakaokaPalu}\emph{)}
 Let~$\Lambda$ be an Artin algebra and let~$K^{[-1,0]}(\proj\Lambda)$ be the full subcategory of the homotopy category~$K^b(\proj\Lambda)$ consisting of complexes concentrated in degrees~$-1$ and~$0$ (using cohomological conventions).
@@
 \begin{proof}
-The first extriangle is obtained by applying the dual of~\cite[Proposition 3.15]{NakaokaPalu} to~$\delta_X$ and~$\delta_1$, and the second one is obtained similarly from~$\delta_0$ and ~$(f_X)_\ast \delta_1$.
+The first extriangle is obtained by applying the dual of~\cite[Prop.~3.15]{NakaokaPalu} to~$\delta_X$ and~$\delta_1$, and the second one is obtained similarly from~$\delta_0$ and ~$(f_X)_\ast \delta_1$.
 \end{proof}
@@
 Consider the extriangle~$X\overset{g}{\infl} Y \overset{h}{\defl} \susp T \overset{t_\ast\eps_T}{\dashrightarrow}$.
-By~\cite[Proposition 3.17]{NakaokaPalu}, there is a commutative diagram of extriangles
+By~\cite[Prop.~3.17]{NakaokaPalu}, there is a commutative diagram of extriangles
 \[
@@
 The functor~$F$ thus induces a faithful functor, still denoted~$F$, from~$\cat/(\susp\tc)$ to~$\modt$.
-It is well-known (see for instance~\cite[Lemma 3.1]{AssemSimsonSkowronski}) that~$F$ restricts to an equivalence of categories~$\tc\to\proj\tc$.
+It is well-known (see for instance~\cite[Lem.~3.1]{AssemSimsonSkowronski}) that~$F$ restricts to an equivalence of categories~$\tc\to\proj\tc$.
 Because~$\tc$ consists of projective objects in~$\cat$, the image under~$F$ of every conflation is a right exact sequence.
@@
 \begin{proof}
-Applying~\cite[Proposition 3.15]{NakaokaPalu} gives a commutative diagram made of conflations
+Applying~\cite[Prop.~3.15]{NakaokaPalu} gives a commutative diagram made of conflations
 \[
@@
 Let~$X\infl Y\defl Z$ be a conflation in~$\cat$.
-Fix conflations~$T_1^X \infl T_0^X \defl X$,~$T_1^Z\infl T_0^Z \defl Z$ with~$T_0^X, T_1^X, T_0^Z, T_1^Z\in\tc$.
-By~\cite[Proposition 3.15]{NakaokaPalu} and axiom (ET4)$^{\mathrm{op}}$, there are commutative diagrams of conflations
+Fix conflations~$T_1^XÂ \infl T_0^X \defl X$,~$T_1^Z\infl T_0^Z \defl Z$ with~$T_0^X, T_1^X, T_0^Z, T_1^Z\in\tc$.
+By~\cite[Prop.~3.15]{NakaokaPalu} and axiom (ET4)$^{\mathrm{op}}$, there are commutative diagrams of conflations
 \[
@@
 Let~$\mathbb{E}_T$ be the additive sub-bifunctor of~$\cat(-,\susp -)$ formed by those morphisms that factor through~$\add\susp T$.
-Then~$(\cat,\mathbb{E}_T)$ becomes extriangulated by~\cite[Proposition 3.14]{HerschendLiuNakaoka} (this can also be checked directly).
+Then~$(\cat,\mathbb{E}_T)$ becomes extriangulated by~\cite[Prop.~3.14]{HerschendLiuNakaoka} (this can also be checked directly).
 The extriangles of~$\cat$ are precisely the triangles~$X\overset{f}{\rightarrow}Y\overset{g}{\rightarrow} Z \overset{h}{\dashrightarrow}$, for which the morphism~$h$ factors through~$\add\susp T$.
@@
 \begin{proof}
- The category~$K^{[-1,0]}(\proj \Lambda)$ is closed under extensions in~$K^b(\proj \Lambda)$, so it is an extriangulated category whose conflations are induced by triangles in~$K^b(\proj\Lambda)$ by~\cite[Remark 2.18]{NakaokaPalu}.
+ The category~$K^{[-1,0]}(\proj \Lambda)$ is closed under extensions in~$K^b(\proj \Lambda)$, so it is an extriangulated category whose conflations are induced by triangles in~$K^b(\proj\Lambda)$ by~\cite[Rem.~2.18]{NakaokaPalu}.
 Now, the object~$\Lambda$ is projective in~$K^{[-1,0]}(\proj \Lambda)$, since if~$X\infl Y\defl Z$ is a conflation, then we get a long exact sequence
@@
 Then~$K^{[-1,0]}(\proj\Lambda)$ is Krull--Schmidt,~$\field$-linear and Ext-finite, since this is true for~$K^b(\proj\Lambda)$ for any finite-dimensional algebra~$\Lambda$.
-Moreover, it has Auslander--Reiten--Serre duality by~\cite[Proposition 6.1]{IyamaNakaokaPalu}.
+Moreover, it has Auslander--Reiten--Serre duality by~\cite[Prop.~6.1]{IyamaNakaokaPalu}.
 \end{proof}
@@
 Assume that~$\Lambda$ is a finite-dimensional brick algebra which is representation-finite.
-Then~\cite[Theorem 6.2]{DemonetIyamaJasso} implies that the assumptions of Theorem~\ref{theo::brick-algebra-condition} are satisfied.
+Then~\cite[Thm.~6.2]{DemonetIyamaJasso} implies that the assumptions of Theorem~\ref{theo::brick-algebra-condition} are satisfied.
 \end{remark}
@@
 \begin{proof}
-First note that the results~\cite[Lemmas 3.4 and 3.5]{AdachiIyamaReiten}, even though stated for finite dimensional algebras, hold with the same proofs for any Artin algebra.
+First note that the results~\cite[Lems.~3.4~\&~3.5]{AdachiIyamaReiten}, even though stated for finite dimensional algebras, hold with the same proofs for any Artin algebra.
 For convenience of the reader, we recall those two results: Let~$Y, Z \in K^{[-1,0]}(\proj\Lambda)$ be indecomposable and not in~$\add(\susp\Lambda)$, and let~$P\in\proj\Lambda$.
@@
 The same is true of~$\tau X$ since objects in~$\add(\susp\Lambda)$ are injective in~$K^{[-1,0]}(\proj\Lambda)$ and an Auslander--Reiten conflation does not split.
-It thus follows from~\cite[Lemma 3.4 ]{AdachiIyamaReiten} that~$X$ and~$\tau X$ are rigid in $K^{[-1,0]}(\proj\Lambda)$.
+It thus follows from~\cite[Lem.~3.4 ]{AdachiIyamaReiten} that~$X$ and~$\tau X$ are rigid in $K^{[-1,0]}(\proj\Lambda)$.
 We have to prove that both~$E\oplus X$ and~$E\oplus\tau X$ are rigid.
@@
 \]
-so that the right-most term also vanishes by~\cite[Lemma 3.4 ]{AdachiIyamaReiten}.
+so that the right-most term also vanishes by~\cite[Lem.~3.4 ]{AdachiIyamaReiten}.
 
@@
 from which we deduce that~$\Hom{\Lambda}(FE,\tau^2 M)=0$.
-This implies~$\Hom{K^b}(\tau X,\susp E) = 0$ by~\cite[Lemma 3.4 ]{AdachiIyamaReiten}.
+This implies~$\Hom{K^b}(\tau X,\susp E) = 0$ by~\cite[Lem.~3.4 ]{AdachiIyamaReiten}.
 
@@
 The complex~$Y$ being two-term, we have~$\Hom{K^b}(Y,\susp^2,Y)=0$.
-Assuming that~$\Hom{K^b}(Y,\susp E)=0$, we deduce that~$\Hom{K^b}(Y,\susp X)=0$, and hence that~$\Hom{\Lambda}(FX,\tau FY) = 0$ by~\cite[Lemma 3.4]{AdachiIyamaReiten}.
+Assuming that~$\Hom{K^b}(Y,\susp E)=0$, we deduce that~$\Hom{K^b}(Y,\susp X)=0$, and hence that~$\Hom{\Lambda}(FX,\tau FY) = 0$ by~\cite[Lem.~3.4]{AdachiIyamaReiten}.
 \end{proof}
@@
 Moreover,~$FY$ is indecomposable and injective.
-By assumption, it is~$\tau$-rigid, hence~$Y$ is rigid in~$K^{[-1,0]}(\proj\Lambda)$ by~\cite[Lemma 3.4]{AdachiIyamaReiten}.
+By assumption, it is~$\tau$-rigid, hence~$Y$ is rigid in~$K^{[-1,0]}(\proj\Lambda)$ by~\cite[Lem.~3.4]{AdachiIyamaReiten}.
 
@@
 where the vertical maps are surjective.
-Since~$\Lambda$ is rigid and~$Y$ is two-term, we can apply~\cite[Proposition 6.2]{IyamaYoshino} to the triangulated category~$K^b(\proj\Lambda)$ (or Proposition~\ref{prop::KRextricat} to the extriangulated~$K^{[-1,0]}(\proj\Lambda)$).
+Since~$\Lambda$ is rigid and~$Y$ is two-term, we can apply~\cite[Prop.~6.2]{IyamaYoshino} to the triangulated category~$K^b(\proj\Lambda)$ (or Proposition~\ref{prop::KRextricat} to the extriangulated~$K^{[-1,0]}(\proj\Lambda)$).
 As a consequence, the right-most vertical map is bijective.
@@
 Since the deflations in~$(\ec,\mathbb{E}_\tc,\mathfrak{s}_\tc)$ are precisely the deflations in~$(\ec,\mathbb{E},\mathfrak{s})$ that are~$\tc$-epic, they are closed under composition.
-We can thus apply~\cite[Proposition 3.14]{HerschendLiuNakaoka} to obtain that~$(\ec,\mathbb{E}_\tc,\mathfrak{s}_\tc)$ is an extriangulated category.
+We can thus apply~\cite[Prop.~3.14]{HerschendLiuNakaoka} to obtain that~$(\ec,\mathbb{E}_\tc,\mathfrak{s}_\tc)$ is an extriangulated category.
 With that relative structure, the objects in~$\tc$ become projective.

### 2019-06-10 thirdPaper/draft/typeConeAssociahedra.tex
minor corrections

@@
 \qquad\qquad
-\dotprod{\b{n}(\tube, \tube')}{\b{h}} = |\bigset{\tube[s]\in\tubes}{\tube[s] \subseteq \tube[t] \cup \tube' \text{ and } v, v' \in \tube[s]}|,
-\]
-which is positive since at least~$\tube \cup \tube'$ fulfills the condition.
-Thus, $\b{h}$ belongs to the type cone~$\typeCone \big( \gvectorFan[\graphG] \big)$.
+\dotprod{\b{n}(\tube, \tube')}{\b{h}} = |\bigset{\tube[s]\in\tubes}{\tube \symdif \tube' \subseteq \tube[s] \subseteq \tube \cup \tube'}|,
+\]
+where~$\tube \symdif \tube' = \{v,v'\}$ denotes the symmetric difference.
+This quantity is positive since at least~$\tube \cup \tube'$ fulfills the condition.
+Thus, the height function~$\b{h}$ belongs to the type cone~$\typeCone \big( \gvectorFan[\graphG] \big)$.
 The polytope~$P_\b{h} \eqdef \set{\b{x} \in \R^\ground}{\dotprod{\gvector{\tube}}{\b{x}} \le \b{h}_{\tube} \text{ for any tube } \tube \in \tubes}$ is the graph associahedron constructed by A.~Postnikov's in~\cite{Postnikov}.
@@
 \]
-Thus, $\b{h}$ belongs to the type cone~$\typeCone \big( \gvectorFan[\graphG] \big)$.
+Thus, the height function~$\b{h}$ belongs to the type cone~$\typeCone \big( \gvectorFan[\graphG] \big)$.
 The corresponding polytope~$P_\b{h}$ is the graph associahedron constructed by S.~Devadoss's in~\cite{Devadoss}.
@@
 \qquad\qquad
-\dotprod{\b{n}(\tube, \tube')}{\b{h}} = \; & |\bigset{\tube[r] \in \tubes, \tube[s] \in \connectedComponents(\tube \cap \tube')}{\tube[s] \subseteq \tube[r] \text{ and } \tube, \tube' \not\subseteq \tube[r]}| \\
+\dotprod{\b{n}(\tube, \tube')}{\b{h}} = \; & |\bigset{(\tube[r], \tube[s]) \in \tubes \times \connectedComponents(\tube \cap \tube')}{\tube[s] \subseteq \tube[r] \text{ and } \tube, \tube' \not\subseteq \tube[r]}| \\
 & + \big( |\connectedComponents(\tube \cap \tube')|-1 \big) \cdot | \bigset{\tube[r] \in \tubes}{\tube \text{ or } \tube'\subseteq \tube[r]}\big|.
 \end{align*}
-Any connected component of~$\tube \cap \tube'$ certifies the positivity of this evaluation, showing that $\b{h}$ belongs to~$\typeCone \big( \gvectorFan[\graphG] \big)$.
+Any connected component of~$\tube \cap \tube'$ certifies the positivity of this evaluation, showing that the height function~$\b{h}$ belongs to~$\typeCone \big( \gvectorFan[\graphG] \big)$.
 The corresponding realization~$P_\b{h}$ of the graph associahedron is new, to the best of our knowledge.
@@
 
-Define $\alpha(\tube,\tube') \eqdef \set{\tube[u] \in \tubes}{\tube[u] \subseteq \tube \cup \tube' \text{ and } \tube \symdif \tube' \subseteq \tube[u]}$, where $\symdif$ denotes the symmetric difference, and let $\b{x} \in \R^{\tubes}$ be such that
+Define $\alpha(\tube,\tube') \eqdef \set{\tube[u] \in \tubes}{\tube \symdif \tube' \subseteq \tube[u] \subseteq \tube \cup \tube'}$, where $\symdif$ denotes the symmetric difference, and define $\b{x} \in \R^{\tubes}$ be such that
 \[
@@
 for each tube~$\tube[s] \in \tubes$.
-
 For any suspected extremal pair $\{\tilde \tube, \tilde \tube'\}$ we have
@@
 \[
-\b{y}_{\tube[s]} \eqdef \begin{cases}
-	-1 & \text{ if } |\tube[s]| \ge |\tube| \\
-	0 & \text{ otherwise.}
+\b{y}_{\tube[s]} = \begin{cases}
+	-1 & \text{ if } |\tube[s]| \ge |\tube|, \\
+	0 & \text{ otherwise},
 \end{cases}
 \]
+for each tube~$\tube[s] \in \tubes$.
 We have $\dotprod{\b{n}(\tube, \tube')}{\b{y}} = -1$.
-For any suspected extremal pair $\{\tilde \tube, \tilde \tube'\}$ we have $\dotprod{\b{n}(\tube, \tube')}{\b{y}}\ge -1$.
-If moreover $\tilde \tube \cup \tilde \tube' \subsetneq \tube \cup \tube'$, then we have $\dotprod{\b{n}(\tube, \tube')}{\b{y}} \ge 0$.
+For any suspected extremal pair $\{\tilde \tube, \tilde \tube'\}$ we have $\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{y}} \ge -1$.
+If moreover $\tilde \tube \cup \tilde \tube' \subsetneq \tube \cup \tube'$, then we have $\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{y}} \ge 0$.
 
@@
 \[
-\b{z}_{\tube[s]} = -|\bigset{\tube[u] \in \alpha(\tube, \tube')}{\tube[u] \subseteq \tube[s]}|.
-\]
-It verifies $\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{z}} \ge 0$ for any suspected extremal pair~$\{\tilde \tube, \tilde \tube'\}$, and $\dotprod{\b{n}(\tube, \tube')}{\b{z}} = |\alpha(\tilde \tube, \tilde \tube')| > 0$ if $\alpha(\tilde \tube, \tilde \tube') \subseteq \alpha(\tube, \tube')$.
-
-For $0 < \varepsilon < 1$, and $0 < \delta < \frac{\varepsilon}{|\alpha(\tube, \tube')|}$, the vector $\b{w} \eqdef \b{x} + \varepsilon \b{y} + \delta \b{z}$ fulfills the desired properties.
+\b{z}_{\tube[s]} = -|\bigset{\tube[u] \in \alpha(\tube, \tube')}{\tube[u] \subseteq \tube[s]}|,
+\]
+for each tube~$\tube[s] \in \tubes$.
+It verifies $\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{z}} \ge 0$ for any suspected extremal pair~$\{\tilde \tube, \tilde \tube'\}$, and $\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{z}} = |\alpha(\tilde \tube, \tilde \tube')| > 0$ if $\alpha(\tilde \tube, \tilde \tube') \subseteq \alpha(\tube, \tube')$.
+
+For $0 < \varepsilon < 1$, and $0 < \delta < \frac{\varepsilon}{|\alpha(\tube, \tube')|}$, we claim that the vector $\b{w} \eqdef \b{x} + \varepsilon \b{y} + \delta \b{z}$ fulfills the desired properties.
 Indeed, if $\{\tilde \tube, \tilde \tube'\} \ne \{\tube,\tube'\}$ is a suspected extremal pair with $\alpha(\tilde \tube, \tilde \tube') \not \subseteq \alpha(\tube,\tube')$, then 

### 2019-06-10 thirdPaper/draft/typeConeAssociahedra.tex
More small changes

--- 2019-06-10 thirdPaper/draft/typeConeAssociahedra.tex
@@
 \newcommandx{\Zono}[2][1=n,2={}]{\mathsf{Zono}^{#2}(#1)} % zonotope
-\newcommandx{\Fan}[1][1=F]{\mathcal{#1}} % fan
+\newcommand{\Fan}{\mathcal{F}} % fan
 \newcommand{\multiplicityVector}{\b{m}} % multiplicity vector
@@
 
-\vspace{1.5cm}
+\vspace{2cm}
 \centerline{\includegraphics[scale=.8]{typeConeCoarsenings}}
@@
 \smallskip
-\item Once we get a representation of a polytope~$P$ as a signed Minkowski sum~$P = \sum_{i \in [k]} \alpha_i Q_i$, we get a formula for the volume of $P$ as a multivariate polynomial in $\alpha_1, \dots, \alpha_k$ whose coefficients are the mixed volumes of $Q_1, \dots, Q_k$~\cite{ArdilaBenedettiDoker, McMullen-Valuations}.
+\item Once we get a representation of a polytope~$P$ as a signed Minkowski sum~$P = \sum_{i \in [k]}\alpha_i Q_i$, we get a formula for the volume of $P$ as a multivariate polynomial in $\alpha_1,\dots,\alpha_k$ whose coefficients are the mixed volumes of $Q_1,\dots, Q_k$~\cite{ArdilaBenedettiDoker,McMullen-Valuations}.
 These encode rich combinatorial information when representing generalized permutahedra as positive Minkowski sums of coordinate simplices or hypersimplices~\cite{Postnikov}, and in particular for matroid polytopes~\cite{ArdilaBenedettiDoker}.
@@
 This motivates the following question: Is it possible to similarly understand the complete realization space of the cluster complex, including all realizations not having the~$\b{g}$-vector fan as their normal fan?
+\pg{AWESOME introduction.}
+\vincent{:-)}
 
@@
 \begin{notation}
-For any adjacent maximal cones~$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$ of~$\Fan$ with ${\rays \ssm \{\ray\} = \rays' \ssm \{\ray'\}}$, we denote by~$\coefficient[{\ray[s]}][\rays][\rays']$ the coefficient of~$\ray[s]$ in the unique linear dependence between the rays of~$\rays \cup \rays'$, \ie such that
+For any two adjacent cones~$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$ of~$\Fan$ with~$\rays \ssm \{\ray\} = \rays' \ssm \{\ray'\}$, we denote by~$\coefficient[{\ray[s]}][\rays][\rays']$ the coefficient of~$\ray[s]$ in the unique linear dependence between the rays of~$\rays \cup \rays'$, \ie such that
 \[
@@
 \label{def:typeCone}
-The \defn{type cone} of~$\Fan$ is the cone~$\typeCone(\Fan)$ of all $\Fan$-admissible height vectors~$\b{h} \in \R^N$:
+The \defn{type cone} of~$\Fan$ is the cone~$\typeCone(\Fan)$ of all $\Fan$-admissible height vectors~$\b{h}$:
 \begin{align*}
@@
 We denote by $\ctypeCone(\Fan)$ the closure of $\typeCone(\Fan)$, and call it the \defn{closed type cone} of~$\Fan$.
-It is the closed polyhedral cone defined by the inequalities $\sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} \ge 0$ for any adjacent maximal cones~$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$.
-If $\Fan$ is the normal fan of the polytope~$P$, then $\ctypeCone(\Fan)$ is called the \defn{deformation cone} of $P$ in~\cite{Postnikov}, see also~\cite{PostnikovReinerWilliams}.
+It is the closed polyhedral cone defined by the inequalities $\sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} \geq 0$ for adjacent maximal cones~$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$.
+If $\Fan$ is the normal fan of the polytope~$P$, then $\ctypeCone(\Fan)$ is called the \defn{deformation cone} of $P$ in~\cite{Postnikov}.
 
@@
 \begin{definition}
-An \defn{extremal adjacent pair} of~$\Fan$ is a pair of adjacent maximal cones~$\{\R_{\ge0}\rays, \R_{\ge0}\rays'\}$ of~$\Fan$ such that the corresponding inequality $\sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} \ge 0$ in the definition of the type cone~$\ctypeCone(\Fan)$ actually defines a facet of~$\ctypeCone(\Fan)$.
+An \defn{extremal adjacent pair} of~$\Fan$ is a pair of adjacent maximal cones~$\{\R_{\ge0}\rays, \R_{\ge0}\rays'\}$ of~$\Fan$ such that the corresponding inequality $\sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} \geq 0$ in the definition of the type cone~$\ctypeCone(\Fan)$ actually defines a facet of~$\ctypeCone(\Fan)$.
 \end{definition}
@@
 \label{rem:dimTypeCone}
-Since the type cone is an~$N$ dimensional cone with a linearity subspace of dimension~$n$, it has at least~$N-n$ facets (thus~$N-n$ extremal adjacent pairs).
+Since the type cone is an~$N$ dimensional cone with a linearity subspace of dimension~$n$, it has at least~$N-n$ facets.
 We say that the type cone is \defn{simplicial} when it has precisely $N-n$ facets.
@@
 \label{prop:non-simplicial}
-Let $\Fan$ be a complete fan that coarsens the essential complete simplicial fan~$\Fan[G]$.
-The \defn{type cone}~$\typeCone(\Fan)$ of all $\Fan$-admissible height vectors~$\b{h} \in \R^N$ is
+Let $\c{G}$ be a complete fan that coarsens the essential complete simplicial fan~$\Fan$.
+The \defn{type cone}~$\typeCone(\c{G})$ of all $\c{G}$-admissible height vectors~$\b{h}$ is
 \begin{align*}
-\typeCone(\Fan) 
+\typeCone(\c{G}) 
 & = \left\{\b{h} \in \R^N\;\middle|\;
@@
 \sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} = 0
-& \begin{array}{l} \text{for any adjacent maximal cones} \\ \text{$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$ of~$\Fan[G]$ belonging}\\\text{to \textbf{the same} maximal cone of $\Fan$,}\end{array}
+& \begin{array}{l} \text{for any adjacent maximal cones} \\ \text{$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$ of~$\Fan$ belonging}\\\text{to \textbf{the same} maximal cone of $\c{G}$,}\end{array}
 \\[.7cm]
 \sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} > 0
-& \begin{array}{l} \text{for any adjacent maximal cones} \\ \text{$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$ of~$\Fan[G]$ belonging}\\\text{to \textbf{distinct} maximal cones of $\Fan$}\end{array}
+& \begin{array}{l} \text{for any adjacent maximal cones} \\ \text{$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$ of~$\Fan$ belonging}\\\text{to \textbf{distinct} maximal cones of $\c{G}$}\end{array}
 \end{array}
@@
 \]
-does not depend on the pair~$\{\rays, \rays'\}$ of adjacent maximal cones of~$\Fan$ with $\rays \ssm \{\ray\} = \rays' \ssm \{\ray'\}$, but only on the pair of rays~$\{\ray, \ray'\}$.
-This implies in particular that the rays~$\ray[s]$ for which~$\coefficient[{\ray[s]}][\rays][\rays'] \ne 0$ belong to~$\rays \cup \rays'$ for any pair~$\{\rays, \rays'\}$ of adjacent maximal cones of~$\Fan$ with $\rays \ssm \{\ray\} = \rays' \ssm \{\ray'\}$.
+does not depend on the pair~$\{\rays, \rays'\}$ of adjacent maximal cones of~$\Fan$ with $\rays \ssm \{\ray\} = \rays' \ssm \{\ray'\}$, but only on the pair of rays~$\ray, \ray'$.
+This implies in particular that the rays~$\ray[s]$ for which~$\coefficient[{\ray[s]}][\rays][\rays'] \ne 0$ belong to~$\rays \cup \rays'$ for any pair~$\{\rays, \rays'\}$ of adjacent cones of~$\Fan$ with $\rays \ssm \{\ray\} = \rays' \ssm \{\ray'\}$.
 
@@
 \begin{definition}
-In a fan~$\Fan$ with the unique exchange relation property, an \defn{extremal exchangeable pair} is a pair of exchangeable rays~$\{\ray,\ray'\}$ such that the corresponding inequality~${\sum_{\ray[s]} \coefficient \, \b{h}_{\ray[s]} \ge  0}$ defines a facet of the closed type cone~$\ctypeCone(\Fan)$.
+In a fan~$\Fan$ with the unique exchange relation property, an \defn{extremal exchangeable pair} is a pair of exchangeable rays~$\{\ray,\ray'\}$ such that the corresponding inequality~${\sum_{\ray[s]} \coefficient \, \b{h}_{\ray[s]} \geq  0}$ defines a facet of the closed type cone~$\ctypeCone(\Fan)$.
 \end{definition}
@@
 
-We still consider an essential complete simplicial fan~$\Fan$ in~$\R^n$, the $N \times n$-matrix~$\b{G}$ whose rows are the rays of~$\Fan$, and the $(N-n) \times N$-matrix~$\b{K}$ which spans the left kernel of~$\b{G}$ (\ie $\b{K}\b{G} = 0$).
+We still consider an essential complete simplicial fan~$\Fan$ in~$\R^n$, the $N \times n$-matrix~$\b{G}$ whose rows are the rays of~$\Fan$, and the $(N-n) \times N$-matrix~$\b{K}$ which spans the left kernel of~$\b{G}$.
 
@@
 \label{coro:simplicialTypeCone}
-Assume that the type cone~$\typeCone(\Fan)$ is simplicial and let~$\b{K}$ be the $(N-n) \times N$-matrix whose rows are the inner normal vectors of the facets of~$\typeCone(\Fan)$. Then the polytope
+Assume that the type cone~$\typeCone(\Fan)$ is simplicial and let~$\b{K}$ be the $(N-n) \times N$-matrix whose rows are the outer normal vectors of the facets of~$\typeCone(\Fan)$. Then the polytope
 \[
@@
 Since~$\b{K}$ has full rank there exists~$\b{h} \in \R^N$ such that~$\b{K}\b{h} = \b{\ell}$.
-Since~$\b{K}\b{h} \ge 0$ and the rows of~$\b{K}$ are precisely all inner normal vectors of the facets of the type cone~$\typeCone(\Fan)$, we obtain that~$\b{h}$ belongs to~$\typeCone(\Fan)$.
+Since~$\b{K}\b{h} \ge 0$ and the rows of~$\b{K}$ are precisely all outer normal vectors of the facets of the type cone~$\typeCone(\Fan)$, we obtain that~$\b{h}$ belongs to~$\typeCone(\Fan)$.
 Since $R_\b{\ell} = Q_\b{h} \sim P_\b{h}$ by \cref{prop:alternativePolytopalRealization}, we conclude that~$R_\b{\ell}$ is a polytopal realization of~$\Fan$.
-Since~$\typeCone(\Fan)$ is simplicial, we have~$\b{K}\typeCone(\Fan) = \R_{>0}^{N-n}$, so that we obtain all polytopal realizations of~$\Fan$ in this way.
+Since~$\typeCone(\Fan)$ is simplicial, we have~$\b{K}\typeCone(\Fan) = \R_{>0}^{N-n}$, so that we obtain all polytopal realizations of~$\Fan$ this way.
 \end{proof}
@@
 
-We say that~$P$ is a \defn{Minkowski summand} of~$R$ if there is a polytope~$Q$ such that $P+Q = R$, and a \defn{weak Minkowski summand} if there is a $\lambda \ge 0$ and a polytope~$Q$ such that ${P + Q = \lambda R}$.
+We say that~$P$ is a \defn{Minkowski summand} of~$R$ if there is a polytope~$Q$ such that $R=P+Q$, and a \defn{weak Minkowski summand} if there is a $\lambda \ge 0$ and a polytope~$Q$ such that ${\lambda R = P + Q}$.
 \cref{lem:MinkowskiSum} ensures that convex combinations in the type cone correspond to Minkowski combinations of polytopes.
@@
 If $P = Q + R$, then we say that~$R$ is the \defn{Minkowski difference} of~$P$ and~$Q$, denoted~${R = P - Q}$. Note that this is only defined when~$Q$ is a Minkowski summand of~$P$.
-For instance, we have ${P_\b{h} - P_{\b{h}'} = P_{\b{h} - \b{h'}}}$ when $P_{\b{h}'}$ is a Minkowski summand of $P_\b{h}$.
-There are two natural ways this construction generalizes to arbitrary pairs of polyhedra.
-On the one hand, one can consider that ${P - Q = \set{x \in \R^n}{x + Q \subseteq P}}$.
-On the other hand, considering arbitrary differences of support functions gives rise to \defn{virtual polyhedra}, which is the Grothendieck group of the semigroup of polytopes with Minkowski sums~\cite{PukhlikovKhovanskii}.
+There are two natural ways this construction generalizes to arbitrary pairs of polyhedra. On the one hand, we have $P - Q = \set{x \in \R^n}{x + Q \subseteq P}$. 
+Notice that $P_\b{h} - P_{\b{h}'} = P_{\b{h} - \b{h'}}$ when $P_{\b{h}'}$ is a Minkowski summand of $P_\b{h}$.
+Considering arbitrary differences of support functions gives rise to \defn{virtual polyhedra}, which is the Grothendieck group of the semigroup of polytopes with Minkowski sums~\cite{PukhlikovKhovanskii}.
 
@@
 \begin{corollary}
-If the type cone~$\typeCone(\Fan)$ of $\Fan$ is simplicial, then every $P_\b{h}$ with $\b{h}\in \typeCone(\Fan)$ (resp.~with $\b{h}\in \ctypeCone(\Fan)$) has a unique representation, up to translation, as a Minkowski sum of positive (resp.~non-negative) dilates of the $N-n$ indecomposable polytopes $P_{\b{h}^{(1)}}, \dots, P_{\b{h}^{(N-n)}}$ arising from the rays~$\b{h}^{(1)}, \dots, \b{h}^{(N-n)}$ of $\ctypeCone(\Fan)$.
+If the type cone~$\typeCone(\Fan)$ of $\Fan$ is simplicial, then the $N-n$ idecomposable polytopes $P_{\b{h}^{(1)}}, \dots, P_{\b{h}^{(N-n)}}$ arising from the rays of $\ctypeCone(\Fan)$ verify that 
+\begin{enumerate}[(i)]
+\item  every $P_\b{h}$ with $\b{h}\in \typeCone(\Fan)$ has a unique representation (up to translation) as a Minkowski sum of positive dilates of $P_{\b{h}^{(1)}}, \dots, P_{\b{h}^{(N-n)}}$; and
+\item  every $P_\b{h}$ with $\b{h}\in \ctypeCone(\Fan)$ has a unique representation (up to translation) as a Minkowski sum of non-negative dilates of $P_{\b{h}^{(1)}}, \dots, P_{\b{h}^{(N-n)}}$.
+\end{enumerate} 
 \end{corollary}
@@
 \label{exm:typeConeMinkowskiSum}
+\enlargethispage{.4cm}
 Consider the $2$-dimensional fan~$\Fan$ of \cref{fig:typeCone}\,(left) whose type cone has been described in \cref{exm:typeCone} and represented in \cref{fig:typeCone}\,(right).
@@
 \item the convex hull of the points~$L(T) \in \R^{n+1}$ for all rooted binary trees~$T$ with~$n+1$ internal nodes, where the $i$th coordinate of~$L(T)$ is the product of the number of leaves in the left subtree by the number of leaves in the right subtree of the $i$th node of~$T$ in inorder~\cite{Loday},
-\item the intersection of the hyperplane~$\bigset{\b{x} \in \R^{n+1}}{\sum_{\ell \in [n+1]} x_\ell = \binom{n+2}{2}}$ with the halfspaces $\bigset{\b{x} \in \R^{n+1}}{\sum_{a < \ell < b} x_\ell \ge \binom{b-a+2}{2}}$ for all internal diagonals~$(a,b)$ of \mbox{the $(n+3)$-gon~\cite{ShniderSternberg}},
-\item the Minkowski sum of the faces~$\simplex_{[i,j]}$ of the standard $n$-dimensional simplex~$\simplex_{[n+1]}$ corresponding to all proper intervals~$[i,j]$ of~$[n+1]$,~\cite{Postnikov}.
+\item the intersection of the hyperplane~$\bigset{\b{x} \in \R^{n+1}}{\sum_{\ell \in [n+1]} x_\ell = \binom{n+2}{2}}$ with the halfspaces $\bigset{\b{x} \in \R^{n+1}}{\sum_{a < \ell < b} x_\ell \ge \binom{b-a+2}{2}}$ for all internal diagonal~$(a,b)$ of \mbox{the $(n+3)$-gon~\cite{ShniderSternberg}},
+\item the Minkowski sum of the faces~$\simplex_{[i,j]}$ of the standard $n$-dimensional simplex~$\simplex$ corresponding to all proper intervals~$[i,j]$ of~$[n+1]$,~\cite{Postnikov}.
 \end{itemize}
@@
 \[
-\typeCone \big( \gvectorFan[n] \big) = \set{\b{h} \in \R^{X(n)}}{\begin{array}{@{}l@{}} \b{h}_{(0,n+2)} = 0, \qquad\text{and}\qquad \b{h}_{(a,a+1)} = 0 \text{ for all } 0 \le a \le n+1 \\ \b{h}_{(a,b)} + \b{h}_{(a',b')} > \b{h}_{(a,b')} + \b{h}_{(a',b)} \text{ for all } 0 \le a < a' < b < b' \le n+2 \end{array}} \!.
+\typeCone(\gvectorFan[n]) = \set{\b{h} \in \R^{X(n)}}{\begin{array}{l} \b{h}_{(0,n+2)} = 0, \qquad\text{and}\qquad \b{h}_{(a,a+1)} = 0 \text{ for all } 0 \le a \le n+1 \\ \b{h}_{(a,b)} + \b{h}_{(a',b')} > \b{h}_{(a,b')} + \b{h}_{(a',b)} \text{ for all } 0 \le a < a' < b < b' \le n+2 \end{array}}.
 \]
@@
 The type cone of~$\gvectorFan[2]$ lives in~$\R^9$ and has a linearity space of dimension~$3$.
-It has $6$ facet-defining inequalities (given below), which correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso} and illustrated in \cref{fig:labelFacetDefiningInequalititiesAsso}\,(right).
+It has $6$ facet-defining inequalities (given below), which correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso} and illustrated in \cref{fig:labelFacetDefiningInequalititiesAsso}\,(left).
 
@@
     \end{adjustbox}
-	\caption{The facet-defining inequalities of the type cone~$\typeCone \big( \gvectorFan[n] \big)$ correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso}.
+	\caption{The facet-defining inequalities of the type cone~$\typeCone(\gvectorFan[n])$ correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso}.
 See \cref{subsec:typeConeCA,sec:clusterCategories} for a representation theoretic \mbox{interpretation}.}
@@
 
-Motivated by \cref{exm:typeConeAsso}, we now describe the facets of this type cone~$\typeCone \big( \gvectorFan[n] \big)$.
+Motivated by \cref{exm:typeConeAsso}, we now describe the facets of this type cone~$\typeCone(\gvectorFan[n])$.
 
@@
 \]
-Therefore, the inner normal vector of the corresponding inequality of the type cone~$\typeCone \big( \gvectorFan[n] \big)$ is
+Therefore, the outer normal vector of the corresponding inequality of the type cone~$\typeCone(\gvectorFan[n])$ is
 \[
@@
 
+\arnau{Change $\b{f}_{(a,b)}$ to $\b{h}_{(a,b)}$? (To homogenize with previous sections)}
+
 Our next statement follows from the end of the previous proof.
@@
 \label{coro:simplicialTypeConeAsso}
-The type cone~$\typeCone \big( \gvectorFan[n] \big)$ is simplicial.
+The type cone~$\typeCone(\gvectorFan[n])$ is simplicial.
 \end{corollary}
@@
 It is known to be the normal fan of a polytope called generalized associahedron.
-These polytopal realizations were first constructed for bipartite initial seeds by F.~Chapoton, S.~Fomin and A.~Zelevinsky~\cite{ChapotonFominZelevinsky} using the $\b{d}$-vector fans of~\cite{FominZelevinsky-YSystems}, then for acyclic initial seeds by C.~Hohlweg, C.~Lange and H.~Thomas~\cite{HohlwegLangeThomas} using Cambrian lattices and fans of N.~Reading and D.~Speyer~\cite{Reading-CambrianLattices, ReadingSpeyer}, then revisited by S.~Stella~\cite{Stella}, and by V.~Pilaud and C.~Stump~\cite{PilaudStump-brickPolytope} via brick polytopes, and finally for arbitrary initial seeds by C.~Hohlweg, V.~Pilaud and S.~Stella~\cite{HohlwegPilaudStella}.
+These polytopal realizations were first constructed for bipartite initial seeds by F.~Chapoton, S.~Fomin and A.~Zelevinsky~\cite{ChapotonFominZelevinsky} using the $\b{d}$-vector fans of~\cite{FominZelevinsky-YSystems}, then for acyclic initial seeds by C.~Hohlweg, C.~Lange and H.~Thomas~\cite{HohlwegLangeThomas} using Cambrian lattices and fans of N.~Reading and D.~Speyer~\cite{Reading-CambrianLattices, ReadingSpeyer}, and revisited by S.~Stella~\cite{Stella}, and by V.~Pilaud and C.~Stump~\cite{PilaudStump-brickPolytope} via brick polytopes, and finally for arbitrary initial seeds by C.~Hohlweg, V.~Pilaud and S.~Stella~\cite{HohlwegPilaudStella}.
 More recently in~\cite{BazierMatteDouvilleMousavandThomasYildirim}, V.~Bazier-Matte, G.~Douville, K.~Mousavand, H.~Thomas and E.~Y\i ld\i r\i m extended the construction of associahedra of~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} to acyclic seeds of simply-laced finite type cluster algebras.
-Here, we extend the construction of~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} to any finite type (simply-laced or not) cluster algebra with respect to any seed (acyclic or not) by providing a direct proof that the type cone of the cluster fan of any finite type cluster algebra with respect to any initial seed is simplicial.
+Here, we extend the construction of~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} to any finite type (simply-laced or not) cluster algebra with respect to any seed (acyclic or not) by providing a direct proof that the type cone of the cluster fan of any finite type cluster algebra is simplicial.
 
@@
 	p_x^{-1}  & \text{if } y = x', \\
-	p_y\negativeExponents{p_x}^{b_{xy}}  & \text{if } y \ne x' \text{ and } b_{xy} \leq 0, \\
-	p_y\positiveExponents{p_x}^{b_{xy}}  & \text{if } y \ne x' \text{ and } b_{xy} > 0.
+	p_y\negativeExponents{p_x}^{b_{xy}}  & \text{if } y \neq x' \text{ and } b_{xy} \leq 0, \\
+	p_y\positiveExponents{p_x}^{b_{xy}}  & \text{if } y \neq x' \text{ and } b_{xy} > 0.
 \end{cases}
@@
 For simplicity, we drop the mention of the coefficients for principal cluster algebras in the notations for seeds~$\seed = (\B, \cluster)$, for cluster algebras~$\principalClusterAlgebra$ and for variables~$\principalVariables$.
-Principal coefficients cluster algebras are $\Z^n$-graded (in the fundamental weight basis~$\{\omega_x\}_{x \in \cluster_\circ}$ of~$V$) for the degree function~$\deg(\B_\circ,\cdot)$ on $\principalClusterAlgebra$ obtained by setting
+Principal coefficients cluster algebras are $\Z^n$-graded (in the fundamental weight basis~$\{\omega_x\}_{x \in \cluster_\circ}$ of~$V$) for the degree function~$\deg(\B_\circ,\cdot)$ on $\principalClusterAlgebra$ is obtained by setting
 \(
@@
 \[
-\bigset{\R_{\ge0} \, \gvectorsFull{\B_\circ}{\seed}}{\seed \text{ seed of } \principalClusterAlgebra},
-\]
-together with all their faces, forms a complete simplicial fan~$\gvectorFan[\B_\circ]$, called the \defn{$\b{g}$-vector fan} or \defn{cluster fan} of~$\B_\circ$.
+\gvectorFan[\B_\circ] \eqdef \bigset{\R_{\ge0} \, \gvectorsFull{\B_\circ}{\seed}}{\seed \text{ seed of } \principalClusterAlgebra},
+\]
+together with all their faces, forms a complete simplicial fan, called the \defn{$\b{g}$-vector fan} or \defn{cluster fan} of~$\B_\circ$.
 \end{theorem}
@@
 We now discuss the linear dependences between $\b{g}$-vectors of adjacent seeds.
-The following lemma was stated in~\cite[Lem.~19]{HohlwegPilaudStella}.
+The following proposition was stated in~\cite[Lem.~19]{HohlwegPilaudStella}.
 
@@
 
-Note that \cref{lem:linearDependencegvectorsCA} implies \cref{thm:generalizedAsso} since it ensures that the type cone~$\typeCone \big( \gvectorFan[\B_\circ] \big)$~of~the cluster fan contains the cone of height vectors~${\b{h} \in \R^{\principalVariables}}$ such that
+Note that \cref{lem:linearDependencegvectorsCA} implies \cref{thm:generalizedAsso} since it ensures that the type cone~$\typeCone(\gvectorFan[\B_\circ])$ of the cluster fan contains the cone of~${\b{h} \in \R^{\principalVariables}}$ such that
 \(
@@
 However, for cluster algebras of finite type, this linear dependence is independent of the choice of a seed containing~$x$ and~$x'$.
-As explained in ~\cref{corollary:UERPforCAproof}, this statement follows from~\cite[Theorem 7.5]{BuanMarshReinekeReitenTodorov}.
+As explained in Corollary~\ref{corollary:UERPforCAproof}, this statement follows from~\cite[Theorem 7.5]{BuanMarshReinekeReitenTodorov}.
 We state it here for future reference.
@@
 \[
-\typeCone \big( \gvectorFan[\B_\circ] \big) = \set{\b{h} \in \R^{\principalVariables}}{\dotprod{\b{n}(\B_\circ, x, x')}{\b{h}} > 0 \text{ for all exchangeable cluster variables } x, x'}.
+\typeCone(\gvectorFan[\B_\circ]) = \set{\b{h} \in \R^{\principalVariables}}{\dotprod{\b{n}(\B_\circ, x, x')}{\b{h}} > 0 \text{ for all exchangeable cluster variables } x, x'}.
 \]
@@
     \end{adjustbox}
-	\caption{The facet-defining inequalities of the type cone~$\typeCone \big( \gvectorFan[\B_\circ] \big)$ of the cluster fan correspond to the mesh mutations described in \cref{thm:extremalExchangeablePairsCA}.
+	\caption{The facet-defining inequalities of the type cone~$\typeCone(\gvectorFan[\B_\circ])$ of the cluster fan correspond to the mesh mutations described in \cref{thm:extremalExchangeablePairsCA}.
 See \cref{sec:clusterCategories} for a representation theoretic \mbox{interpretation}.}
@@
 In other words, according to \cref{lem:dependenceMesh}, if~${(\B, \cluster)}$ and~${(\B', \cluster')}$ are two adjacent seeds with~$\cluster \ssm \{x\} = \cluster' \ssm \{x'\}$, we have~$\alpha_{x,x',y} = |b_{xy}|$ for~$y \in \cluster \cap \cluster'$ and~$\alpha_{x,x',y} = 0$ otherwise.
-The following statement will be shown in \cref{corollary:proof of prop meshMutations}.
+
+The following will be shown in \cref{sec:clusterCategories}, Corollary~\ref{corollary:proof of prop meshMutations}.
 
@@
 \label{coro:simplicialTypeConeCA}
-The type cone~$\typeCone \big( \gvectorFan[n] \big)$ is simplicial.
+The type cone~$\typeCone(\gvectorFan[n])$ is simplicial.
 \end{corollary}
@@
 For each vertex~$a \in Q_0$, there is also a \defn{string of length zero}, denoted by~$\varepsilon_a$, that starts and ends at~$a$.
-We implicitly identify the two inverse strings~$\rho$ and~$\rho^{-1}$, and call it an \defn{undirected string} of~$\quiver$.
+We often implicitly identify the two inverse strings~$\rho$ and~$\rho^{-1}$, and call it an \defn{undirected string} of~$\quiver$.
 Let~$\strings$ denote the set of strings of~$\quiver$.
 
-A \defn{walk} of~$\quiver$ is a maximal string of its blossoming quiver~$\quiver\blossom$ (meaning that each endpoint is a blossom).
+A \defn{walk} of~$\quiver$ is a maximal maximal string of its blossoming quiver~$\quiver\blossom$ (meaning that each endpoint is a blossom).
 As for strings, we implicitly identify the two inverse walks~$\omega$ and~$\omega^{-1}$, and call it an \defn{undirected walk} of~$\quiver$.
@@
 \begin{itemize}
-\item the endpoints of~$\sigma$ are not allowed to be blossom endpoints of~$\omega$,
+\item the endpoints of~$\sigma$ are not allowed to blossom endpoints of~$\omega$,
 \item the position of~$\sigma$ as a factor of~$\omega$ matters (the same string at a different position is considered a different substring).
@@
 We say that~$\omega$ \defn{kisses}~$\omega'$ if ${\Sigma_\top(\omega) \cap \Sigma_\bottom(\omega')} \ne \varnothing$.
-In other words, $\omega$ and~$\omega'$ share a common substring~$\sigma$, and both arrows of~$\omega$ (resp.~of~$\omega'$) incident to the endpoints of~$\sigma$ but not in~$\sigma$ are outgoing (resp.~incoming) at the endpoints of~$\sigma$.
+In other words, $\omega$ and~$\omega'$ share a common substring~$\sigma$, and both arrows of~$\omega$ (resp.~of~$\omega'$) not in~$\sigma$ are outgoing (resp.~incoming) at the endpoints of~$\sigma$.
 See \cref{fig:kissingCrossing} for a schematic representation and \cref{fig:exmNonkissing}\,(middle) where the three walks are pairwise kissing.
@@
 
+\para{Two families of examples: gentle grid and dissection quivers}
+%
+The initial motivation for non-kissing complexes came from two families of examples, illustrated in \cref{fig:dissectionGridQuivers}:
+\begin{enumerate}[(1)]
+\item \textbf{Grid quivers}: Consider the infinite grid quiver~$\quiver_{Z^2}$, whose vertices are all integer points of~$\Z^2$, whose arrows connect between~$(i,j) \longrightarrow (i,j+1)$ and~$(i,j) \longrightarrow (i+1,j)$ for any~$(i,j) \in \Z^2$, and whose relations forbid~$(i-1,j) \longrightarrow (i,j) \longrightarrow (i,j+1)$ and~$(i,j-1) \longrightarrow (i,j) \longrightarrow (i+1,j)$ for any~$(i,j) \in \Z^2$.
+A \defn{gentle grid quiver} is any subquiver~$\quiver_A$ of~$\quiver_{Z^2}$ induced by a finite subset~$A \subset \Z^2$ of the integer grid.
+See \cref{fig:dissectionGridQuivers}.
+The non-kissing complex of gentle grid quivers were introduced in~\cite{McConville} with motivation coming from~\cite{PetersenPylyavskyySpeyer} and~\cite{SantosStumpWelker}.
+
+\smallskip
+\item \textbf{Dissection quivers}: Consider a dissection~$D$ of a convex polygon~$P$ (that is a crossing-free set of diagonals of~$P$) and its \defn{gentle dissection quiver}~$\quiver_D$, whose vertices are the internal diagonals of~$D$, whose arrows connect pairs of consecutive internal diagonals along the boundary of a face of~$D$, and whose relations correspond to triples of consecutive internal diagonals along the boundary of a face of~$D$.
+See \cref{fig:dissectionGridQuivers}.
+The non-kissing complex of~$\quiver_D$ then corresponds to non-crossing sets of accordions of~$D$, where an accordion is a segment connecting the middles of two boundary edges of~$P$ and crossing a connected set of diagonals of~$D$.
+This accordion complex was studied in~\cite{GarverMcConville} and~\cite{MannevillePilaud-accordion} with motivation coming from~\cite{Baryshnikov}, and~\cite{Chapoton-quadrangulations}.
+\end{enumerate}
+
+\begin{figure}[h]
+	\capstart
+	\centerline{\includegraphics[scale=.35]{gridQuiver} \quad \includegraphics[scale=.8]{dissectionQuiver} \quad \includegraphics[scale=1.2]{bijectionAssociahedronGrid} \quad \includegraphics[scale=1.2]{bijectionAssociahedronDissection}}
+	\caption{A gentle grid quiver (left), a gentle dissection quiver (middle left), and a path quiver which is both the gentle grid quiver of a ribbon (middle right) and the dissection quiver of a triangulation (right).
+Illustration from~\cite{PaluPilaudPlamondon-nonkissing}.}
+	\label{fig:dissectionGridQuivers}
+\end{figure}
+
+These two families of non-kissing complexes are well-behaved as they avoid all pathologies of \cref{rem:exchangeablePairsNKC}.
+However, they still provide good examples of non-kissing complexes.
+In particular, both families contain the classical associahedron.
+Namely, the gentle associahedron~$\Asso[\quiver]$ is the classical associahedron of~\cite{ShniderSternberg, Loday} presented in \cref{thm:associahedronLoday} when~${\quiver = \quiver_A}$ for the path~${A = \set{(0,j)}{j \in [n]}}$ or equivalently~$\quiver = \quiver_D$ for the fan triangulation~$D$ (where all internal diagonals incident to the same point).
+More generally, $\Asso[\quiver]$ is an associahedron of~\cite{HohlwegLange} when~$\quiver = \quiver_A$ for a ribbon~$A$ or equivalently~$\quiver = \quiver_D$ for a triangulation~$D$.
+See \cref{fig:dissectionGridQuivers}.
+
+Note that, it was shown in~\cite{PaluPilaudPlamondon-surfaces} that the accordion complexes can be extended to dissections of arbitrary orientable surfaces with marked points and then provide a geometric model for all non-kissing complexes of gentle quivers.
+
 \para{$\b{g}$- and $\b{c}$-vectors}
@@
 The \defn{distinguished walk} of the non-kissing facet~$F \in \NKC$ at the arrow~$\alpha$ is the maximum walk of~$F$ for~$\prec_\alpha$.
-The \defn{distinguished arrows} of the walk~$\omega$ in the non-kissing facet~$F \in \NKC$ are the arrows where~$\omega$ is the distinguished walk.
+The \defn{distinguished arrows} of the walk~$\omega$ in the non-kissing facet~$F \in \NKC$ are the arrow where~$\omega$ is the distinguished walk.
 It is shown in~\cite[Prop.~2.28]{PaluPilaudPlamondon-nonkissing} that each bending walk in a non-kissing facet has precisely two distinguished arrows, pointing in opposite directions.
@@
 
-The following result will also be essential in our discussion.
-We say that a string~$\sigma$ is \defn{distinguishable} if it is the distinguished substring of a walk in a non-kissing facet, and we denote by~$\distinguishableStrings$ the set of distinguishable strings of~$\quiver$.
-
-\begin{proposition}[{\cite[3.68]{PaluPilaudPlamondon-nonkissing}}]
-\label{prop:bijectionStringsWalks}
-The number of distinguishable strings~$\distinguishableStrings$ and proper walks~$\properWalks$ of the quiver~$\quiver$ are related by
-\[
-|\distinguishableStrings| + |Q_0| = |\properWalks|.
-\]
-\end{proposition}
-
 \para{Non-kissing fan and gentle associahedron}
 %
-\enlargethispage{.1cm}
-The $\b{g}$-vectors support a complete simplicial fan realization of the non-kissing complex~$\NKC$.
+\enlargethispage{.2cm}
+The $\b{g}$-vectors support a complete simplicial fan realization of the non-kissing complex complex.
 Examples are illustrated in \cref{fig:nonkissingFans}.
@@
 %
+\enlargethispage{-.4cm}
 Although we lack a characterization of the exchangeable pairs of the non-kissing complex (see \cref{rem:exchangeablePairsNKC}), we can still describe the linear dependence among the $\b{g}$-vectors involved in a flip.
@@
 \label{prop:exchangeablePairsNKC}
-Let~$\omega, \omega'$ be two exchangeable walks on~$\quiver$. Then:
+Let~$\omega, \omega'$ be two exchangeable walks on~$\quiver$. Then
 \begin{enumerate}[(i)]
 \item For any non-kissing facets~$F, F'$ of~$\NKC$ with~$F \ssm \{\omega\} = f' \ssm \{\omega'\}$, the distinguished substrings of~$\omega$ in~$F$ and of~$\omega'$ in~$F'$ coincide to a string~$\sigma$.
-Moreover, if we decompose~${\omega = \rho \sigma \tau}$ and~${\omega' = \rho' \sigma \tau'}$, then the facets~$F$ and~$F'$ both contain the walks~$\mu \eqdef \rho' \sigma \tau$ and~$\nu \eqdef \rho \sigma \tau'$.
-\item The substring~$\sigma$ and thus the walks~$\mu$ and~$\nu$ actually depend on the exchangeable walks~$\omega$ and~$\omega'$, not on the adjacent non-kissing facet~$F $ and~$F'$.
-\item The linear dependence between the $\b{g}$-vectors of~$F \cup F'$ is given by
+Moreover, if we decompose~$\omega = \rho \sigma \tau$ and~$\omega' = \rho' \sigma \tau'$, then the facets~$F$ and~$F'$ both contain the walks~$\mu \eqdef \rho' \sigma \tau$ and~$\nu \eqdef \rho \sigma \tau'$.
+\item The substring~$\sigma$ and thus the walks~$\mu$ and~$\nu$ only depend on the exchangeable walks~$\omega$ and~$\omega'$, and not on the adjacent non-kissing facets~$F $ and~$F'$.
+\item Moreover, the linear dependence between the $\b{g}$-vectors of~$F \cup F'$ is given by
 \[
@@
 %
-\begin{figure}[b]
+\begin{figure}[t]
 	\capstart
@@
 This question was discussed in \cite[Sect.~9]{BrustleDouvilleMousavandThomasYildirim}.
-However, as illustrated for instance in the non-kissing complex of \cref{fig:nonkissingFans}\,(right),
+However, as illustrated in \cref{fig:nonkissingFans}\,(right), note that
 \begin{itemize}
@@
 
-\para{Two families of examples: gentle grid and dissection quivers}
-%
-The initial motivation for non-kissing complexes came from two families of examples, illustrated in \cref{fig:dissectionGridQuivers}:
-
-\medskip
-\begin{enumerate}[(1)]
-\item \textbf{Grid quivers}: Consider the infinite grid quiver~$\quiver_{Z^2}$, whose vertices are all integer points of~$\Z^2$, whose arrows are~$(i,j) \longrightarrow (i,j+1)$ and~$(i,j) \longrightarrow (i+1,j)$ for any~$(i,j) \in \Z^2$, and whose relations are~$(i-1,j) \longrightarrow (i,j) \longrightarrow (i,j+1)$ and~$(i,j-1) \longrightarrow (i,j) \longrightarrow (i+1,j)$ for any~$(i,j) \in \Z^2$.
-A \defn{gentle grid quiver} is any subquiver~$\quiver_A$ of~$\quiver_{Z^2}$ induced by a finite subset~$A \subset \Z^2$ of the integer grid.
-See \cref{fig:dissectionGridQuivers}.
-The non-kissing complex of gentle grid quivers were introduced in~\cite{McConville} with motivation coming from~\cite{PetersenPylyavskyySpeyer} and~\cite{SantosStumpWelker}.
-
-\medskip
-\item \textbf{Dissection quivers}: Consider a dissection~$D$ of a convex polygon~$P$ (that is a crossing-free set of diagonals of~$P$) and its \defn{gentle dissection quiver}~$\quiver_D$, whose vertices are the internal diagonals of~$D$, whose arrows connect pairs of consecutive internal diagonals along the boundary of a face of~$D$, and whose relations correspond to triples of consecutive internal diagonals along the boundary of a face of~$D$.
-See \cref{fig:dissectionGridQuivers}.
-The non-kissing complex of~$\quiver_D$ then corresponds to non-crossing sets of accordions of~$D$, where an accordion is a segment connecting the middles of two boundary edges of~$P$ and crossing a connected set of diagonals of~$D$.
-This accordion complex was studied in~\cite{GarverMcConville} and~\cite{MannevillePilaud-accordion} with motivation coming from~\cite{Baryshnikov}, and~\cite{Chapoton-quadrangulations}.
-\end{enumerate}
-
-\begin{figure}[h]
-	\capstart
-	\centerline{\includegraphics[scale=.35]{gridQuiver} \quad \includegraphics[scale=.8]{dissectionQuiver} \quad \includegraphics[scale=1.2]{bijectionAssociahedronGrid} \quad \includegraphics[scale=1.2]{bijectionAssociahedronDissection}}
-	\caption{A gentle grid quiver (left), a gentle dissection quiver (middle left), and a path quiver which is both the gentle grid quiver of a ribbon (middle right) and the dissection quiver of a triangulation (right).
-Illustration from~\cite{PaluPilaudPlamondon-nonkissing}.}
-	\label{fig:dissectionGridQuivers}
-\end{figure}
-
-These two families of non-kissing complexes are well-behaved as they avoid all pathologies of \cref{rem:exchangeablePairsNKC}.
-However, they still provide good examples of non-kissing complexes.
-In particular, both families contain the classical associahedron.
-Namely, the gentle associahedron~$\Asso[\quiver]$ is the classical associahedron of~\cite{ShniderSternberg, Loday} presented in \cref{thm:associahedronLoday} when~${\quiver = \quiver_A}$ for the path~${A = \set{(0,j)}{j \in [n]}}$ or equivalently~$\quiver = \quiver_D$ for the fan triangulation~$D$ (where all internal diagonals are incident to the same point).
-More generally, $\Asso[\quiver]$ is an associahedron of~\cite{HohlwegLange} when~$\quiver = \quiver_A$ for a ribbon~$A$ or equivalently~$\quiver = \quiver_D$ for a triangulation~$D$.
-See \cref{fig:dissectionGridQuivers}.
-
-Note that, it was shown in~\cite{PaluPilaudPlamondon-surfaces} that the accordion complexes can be extended to dissections of arbitrary orientable surfaces with marked points and then provide a geometric model for all non-kissing complexes of gentle quivers.
+\para{Numerology}
+%
+The following result will also be essential in our discussion.
+
+\begin{proposition}[{\cite[3.68]{PaluPilaudPlamondon-nonkissing}}]
+\label{prop:bijectionStringsWalks}
+The number of distinguishable strings~$\distinguishableStrings$ and proper walks~$\properWalks$ of the quiver~$\quiver$ are related by
+\[
+|\distinguishableStrings| + |Q_0| = |\properWalks|.
+\]
+\end{proposition}
 
@@
 
-\enlargethispage{-.3cm}
 We now discuss the type cones of the non-kissing fans defined in \cref{thm:nonkissingFan}. We obtain from \cref{prop:exchangeablePairsNKC} the following redundant description.
@@
 \[
-\typeCone \big( \gvectorFan[\quiver] \big) = \set{\b{h} \in \R^{\walks}}{\begin{array}{l} \b{h}_\omega = 0 \text{ for any improper walk } \omega \\ \b{h}_\omega + \b{h}_{\omega'} > \b{h}_\mu + \b{h}_\nu \text{ for any exchangeable walks } \omega, \omega' \end{array}},
+\typeCone(\gvectorFan[\quiver]) = \set{\b{h} \in \R^{\walks}}{\begin{array}{l} \b{h}_\omega = 0 \text{ for any improper walk } \omega \\ \b{h}_\omega + \b{h}_{\omega'} > \b{h}_\mu + \b{h}_\nu \text{ for any exchangeable walks } \omega, \omega' \end{array}},
 \]
@@
 Consider the non-kissing fans illustrated in \cref{fig:nonkissingFans}.
-The type cone of the left fan of \cref{fig:nonkissingFans} lives in~$\R^8$ and has a linearity space of dimension~$3$.
-It has $5$ facet-defining inequalities (given below), which correspond to the flips described in \cref{prop:interestingExchangeablePairsNKC,prop:extremalExchangeablePairsNKC} and illustrated in \cref{fig:labelFacetDefiningInequalititiesNKC}\,(left).
+The type cone of the left fan of \cref{fig:nonkissingFans} lives in~$\R^9$ and has a linearity space of dimension~$3$.
+It has $6$ facet-defining inequalities (given below), which correspond to the flips described in \cref{prop:interestingExchangeablePairsNKC,prop:extremalExchangeablePairsNKC} and illustrated in \cref{fig:labelFacetDefiningInequalititiesNKC}\,(left).
 
@@
     \end{adjustbox}
-	\caption{The facet-defining inequalities of the type cone~$\typeCone \big( \gvectorFan[\quiver] \big)$ of the non-kissing fan, represented on the Auslander Reiten quiver of the gentle algebra of~$\quiver$.
+	\caption{The facet-defining inequalities of the type cone~$\typeCone(\gvectorFan[\quiver])$ of the non-kissing fan, represented on the Auslander Reiten quiver of the gentle algebra of~$\quiver$.
 While they correspond to meshes on the left, they are not as clear in the general case as on the right.
@@
 
-As illustrated in \cref{exm:typeConeNKC}, the type cone of the non-kissing fan is not always simplicial and we do not always understand its extremal exchangeable pairs.
+As illustrated in \cref{exm:typeConeNKC}, the type cone of the non-kissing fan is not simplicial and we do not always understand its extremal exchangeable pairs.
 In the next section section, we will explore a special family of gentle quivers for which we can completely describe the type cone.
-The combination of this special family with computer experiments in the general case supports the following conjecture.
+The combination of this special family with computer experiments in the general case support the following conjecture.
 
@@
 \begin{itemize}
-\item \defn{brick} if it satisfies the three equivalent conditions of \cref{prop:noSelfKissing},
-\item \defn{$2$-acyclic} if it contains no cycle of length~$2$.
+\item \defn{brick}: it satisfies the three equivalent conditions of \cref{prop:noSelfKissing},
+\item \defn{$2$-acyclic}: it contains no cycle of length~$2$.
 \end{itemize}
@@
 
-Note that the family of brick $2$-acyclic gentle quivers already contains a lot of relevant examples, including the gentle grid and dissection quivers discussed in \cref{subsubsec:nonkissingComplex}.
+Note that this family already contains a lot of relevant examples, including the gentle grid and dissection quivers discussed in \cref{subsubsec:nonkissingComplex}.
 In particular, the classical associahedron is the gentle associahedron of a brick $2$-acyclic gentle quiver.
@@
 For a string~$\sigma$ of~$\quiver$, we denote by $\sigma\hR$ (resp.~$\sigma\cR$) the unique string of the blossoming quiver~$\quiver\blossom$ of the form $\sigma\hR = \sigma \alpha_1^{-1} \alpha_2 \dots \alpha_\ell$ (resp.~$\sigma\cR = \sigma \alpha_1 \alpha_2^{-1} \dots \alpha_\ell^{-1}$) with~$\ell \ge 1$ and~${\alpha_1, \dots, \alpha_\ell \in Q_1}$ and such that~$t(\alpha_\ell)$ (resp.~$s(\alpha_\ell)$) is a blossom of~$\quiver\blossom$.
-These notations are motivated by the representation of strings used in~\cite{ButlerRingel, PaluPilaudPlamondon-nonkissing}, and the terminology usually says that~$\sigma\hR$ (resp.~$\sigma\cR$) is obtained by adding a \defn{hook} (resp.~a \defn{cohook}) to~$\sigma$.
+These notations are motivated by the representation of strings used in~\cite{ButlerRingel, PaluPilaudPlamondon-nonkissing}, and the terminology usually says that~$\sigma\hR$ (resp.~$\sigma\cR$) is obtained by adding a \defn{hook} (resp.~\defn{cohook}) to~$\sigma$.
 We define similarly~$\hL\sigma$ (resp.~$\cL\sigma$).
-The walk~$\hL(\sigma\hR) = (\hL\sigma)\hR$ of~$\quiver$ is simply denoted by~$\hh{\sigma}$, and we define similarly~$\cc{\sigma}$, $\hc{\sigma}$ and~$\ch{\sigma}$.
+The walk~$\hL(\sigma\hR) = (\hL\sigma)\hR$ of~$\quiver$ is simply be denoted~$\hh{\sigma}$, and we define similarly~$\cc{\sigma}$, $\hc{\sigma}$ and~$\ch{\sigma}$.
 
@@
 We can therefore assume that $\tau$ appears completely before or completely after~$\sigma$ in both~$\mu$ and~$\nu$.
-We distinguish two different cases:
+We distinguish the different cases:
 \begin{itemize}
-\item If~$\tau$ appears before~$\sigma$ in both~$\mu$ and~$\nu$, then~$\alpha \tau \alpha'$ forms a cycle in~$\quiver$.
+\item If~$\tau$ appears before~$\sigma$ in both~$\mu$ and~$\nu$, then~$\alpha \tau \alpha'$ form a cycle in~$\quiver$.
 If~$\tau$ is reduced to a vertex, then we have a $2$-cycle.
@@
 \item If~$\tau$ appears before~$\sigma$ in~$\mu$ and after~$\sigma$ in~$\nu$, then~$\omega$, $\mu$ and~$\nu$ finish at the same blossom so that~$\mu$ and~$\nu$ are not kissing at~$\tau$.
-The case when~$\tau$ appears after~$\sigma$ in~$\mu$ and before~$\sigma$ in~$\nu$ is symmetric.
+The case when~$\tau$ appears after~$\sigma$ in~$\mu$ and before~$\sigma$ in~$\nu$ is identical.
 \end{itemize}
@@
 
-We claim that~$\omega$ is distinguished at~$\alpha$ and~$\beta$ in~$F$, that~$\mu$ is distinguished at~$\alpha'$ in~$F$ and that~$\nu$ is distinguished at~$\beta'$ in~$F$.
+We claim that~$\omega$ is distinguished at~$\alpha$ and~$\beta$ in the facet~$F$, that~$\mu$ is distinguished at~$\alpha'$ and that~$\nu$ is distinguished at~$\beta'$.
 Let us just prove that~$\mu$ is distinguished at~$\alpha'$, the other statements being similar.
@@
 
-The following statement describes the type cone of the non-kissing fan of a brick $2$-acyclic gentle quiver.
+The following statement describes the type cone of the non-kissing fan of a gentle quiver with no self-kissing walks.
 
@@
 \]
-Therefore, the inner normal vector of the corresponding inequality of the type cone~$\typeCone \big( \gvectorFan[\quiver] \big)$ is
+Therefore, the outer normal vector of the corresponding inequality of the type cone~$\typeCone(\gvectorFan[\quiver])$ is
 \[
@@
 \]
-We claim that this normal vector is always a positive linear combination of the normal vectors~$\b{m}(\sigma) \eqdef \b{n}(\cc{\sigma}, \hh{\sigma}) = \b{f}_{\cc{\sigma}} + \b{f}_{\hh{\sigma}} - \b{f}_{\hc{\sigma}} - \b{f}_{\ch{\sigma}}$ for all strings~$\sigma \in \strings$.
+We claim that this normal vector is always a positive linear combination of the normal vectors~$\b{m}(\sigma) \eqdef \b{n}(\cc{\sigma}, \hh{\sigma}) = \b{f}_{\cc{\sigma}} + \b{f}_{\hh{\sigma}} - \b{f}_{\hc{\sigma}} - \b{f}_{\ch{\sigma}}$ for all string~$\sigma \in \strings$.
 Our proof works by descending induction on the length~$\lambda(\omega,\omega') \eqdef \ell(\sigma)$ of the common substring of~$\omega$ and~$\omega'$.
@@
 \label{coro:simplicialTypeConeNKC}
-For any brick $2$-acyclic gentle quiver~$\quiver$, the type cone~$\typeCone \big( \gvectorFan[\quiver] \big)$ of the non-kissing fan~$\quiver$ is simplicial.
+For any brick $2$-acyclic gentle quiver~$\quiver$, the type cone~$\typeCone(\gvectorFan[\quiver])$ of the non-kissing fan~$\quiver$ is simplicial.
 \end{corollary}
@@
 \end{corollary}
+
+\begin{proof}
+\cref{prop:extremalExchangeablePairsNKC} asserts that the type cone~$\typeCone(\gvectorFan[\quiver])$ has one facet for each string of~$\quiver$.
+Since all strings are distinguishable by \cref{prop:noSelfKissing}, the number of facets of~$\typeCone(\gvectorFan[\quiver])$ is $|\strings| = |\distinguishableStrings| = |\properWalks| - |Q_0|$ by~\cref{prop:bijectionStringsWalks}, so that~$\typeCone(\gvectorFan[\quiver])$ is simplicial.
+We then conclude by a simple application of \cref{coro:simplicialTypeCone}.
+\end{proof}
 
@@
 \label{exm:nonSimplicialTypeConeNKC}
-Note that \cref{prop:interestingExchangeablePairsNKC,prop:extremalExchangeablePairsNKC} and therefore~\cref{coro:simplicialTypeConeNKC,coro:allPolytopalRealizationsNKC} fail when the quiver is not brick or $2$-cyclic.
+Note that \cref{prop:interestingExchangeablePairsNKC,prop:extremalExchangeablePairsNKC} and therefore~\cref{coro:simplicialTypeConeNKC,coro:allPolytopalRealizationsNKC} fail when the quiver is not brick or not $2$-acyclic.
 The smallest exemples are the $2$-cycles whose non-kissing fans are represented in \cref{fig:nonkissingFans2}.
 The left one is not brick: it has a non-distinguishable string and a self-kissing walk.
-The right one is brick but is $2$-cyclic.
+The right one is brick but is not $2$-acyclic.
 
@@
 (since the fans are the same, the type cones are the same and we therefore present them together).
-\cref{fig:nonkissingFans}\,(right) gives another example of brick but $2$-cyclic gentle quiver for which \cref{prop:interestingExchangeablePairsNKC,prop:extremalExchangeablePairsNKC} fail.
+
+Note that both assumptions of \cref{def:brick2acyclic} are needed for \cref{prop:interestingExchangeablePairsNKC,prop:extremalExchangeablePairsNKC}.
+Indeed, these statements fail for the quiver of \cref{fig:nonkissingFans}\,(left) which is $2$-acyclic but not brick and for the quiver of \cref{fig:nonkissingFans2} which is brick but $2$-cyclic.
 
@@
 \begin{theorem}[\cite{CarrDevadoss, Devadoss, Postnikov, FeichtnerSturmfels, Zelevinsky}]
-For any graph~$\graphG$, the nested fan~$\gvectorFan[\graphG]$ is the normal fan of the graph associahedron~$\Asso[\graphG]$.
-It can be constructed as
-\begin{itemize}
-\item the intersection of~$\HH$ with the hyperplanes~$\dotprod{\gvector{\tube}}{\b{x}} \le 3^{|\tube|-2}$ for all tubes~$\tube \in \tubes$~\cite{Devadoss},
-\item the Minkowski sum~$\sum_{\tube \in \tubes} \triangle_{\tube}$ of the faces of the standard simplex corresponding to all tubes of~$\graphG$~\cite{Postnikov}.
-\end{itemize}
+For any graph~$\graphG$, the nested fan~$\gvectorFan[\graphG]$ is the normal fan of the graph associahedron~$\Asso[\graphG]$, defined as the Minkowski sum~$\sum_{\tube \in \tubes} \triangle_{\tube}$ of the faces of the standard simplex corresponding to all tubes of~$\graphG$.
 \end{theorem}
@@
 \[
-\typeCone \big( \gvectorFan[\graphG] \big) = \set{\b{h} \in \R^{\tubes}}{\begin{array}{l} \b{h}_{\tube} = 0 \text{ for any improper tube } \tube \\ \b{h}_{\tube} + \b{h}_{\tube'} > \b{h}_{\tube \cup \tube'} + \sum_{\tube[s] \in \connectedComponents(\tube \cap \tube')} \b{h}_{\tube[s]} \text{ for any exchangeable tubes } \tube, \tube' \end{array}}.
+\typeCone(\gvectorFan[\graphG]) = \set{\b{h} \in \R^{\tubes}}{\begin{array}{l} \b{h}_{\tube} = 0 \text{ for any improper tube } \tube \\ \b{h}_{\tube} + \b{h}_{\tube'} > \b{h}_{\tube \cup \tube'} + \sum_{\tube[s] \in \connectedComponents(\tube \cap \tube')} \b{h}_{\tube[s]} \text{ for any exchangeable tubes } \tube, \tube' \end{array}}.
 \]
@@
 We now consider an arbitrary graph~$\graphG$ and describe the type cone of its nested fan.
-We give a necessary condition for an exchangeable pair to be extremal in \cref{lem:extremalExchangeablePairsGAonlyif}, exploit it in \cref{exm:constructionsGA}, and prove that it is actually a sufficient condition in \cref{prop:extremalExchangeablePairsGA}
+\cref{prop:extremalExchangeablePairsA} extends as follows.
 
@@
 \label{lem:extremalExchangeablePairsGAonlyif}
-If two tubes~$\tube$ and~$\tube'$ of~$\graphG$ form an extremal exchangeable pair for the nested fan of~$\graphG$, then~${\tube \ssm \{v\} = \tube' \ssm \{v'\}}$ for some neighbor~$v$ of~$\tube'$ and some neighbor~$v'$ of~$\tube$.
+Two tubes~$\tube$ and~$\tube'$ of~$\graphG$ form an extremal exchangeable pair for the nested fan of~$\graphG$ only if~${\tube \ssm \{v\} = \tube' \ssm \{v'\}}$ for some neighbor~$v$ of~$\tube'$ and some neighbor~$v'$ of~$\tube$.
 \end{lemma}
@@
 Consider an exchangeable pair~$\{\tube, \tube'\}$ of tubes of~$\graphG$.
-The inner normal vector of the corresponding inequality of the type cone is
+The outer normal vector of the corresponding inequality of the type cone is
 \[
@@
 Therefore, $\tube \ssm \tube'$ and~$\tube' \ssm \tube$ are both connected.
-Assume that $\tube \ssm \tube'\ne \{v\}$, and let $w\ne v$ be a non-disconnecting node of $\tube \ssm \tube'$.
-By \cref{prop:exchangeablePairsGA}, $\tilde \tube \eqdef \tube \ssm \{w\}$ and $\tube'$ are exchangeable, and $\tilde \tube' \eqdef (\tube \cup \tube') \ssm \{w\}$ and $\tube$ are exchangeable as well.
-Moreover, we have
+Assume that $\tube \ssm \tube'\neq \{v\}$, and let $w\neq v$ be a non-disconnecting node of $\tube \ssm \tube'$.
+Then $\tilde \tube:=\tube \ssm \{w\}$ and $\tube'$ are exchangeable, and $\tilde \tube':=(\tube \cup \tube')\ssm \{w\}$ and $\tube$ are exchangeable as well.
+We have
 \begin{align*}
-\b{n}(\tilde \tube, \tube') + \b{n}( \tube, \tilde \tube')
-& = \Big( \b{f}_{\tilde \tube} + \b{f}_{\tube'} - \b{f}_{\tilde \tube\cup \tube'} - \sum_{\tube[s] \in \connectedComponents(\tilde \tube \cap \tube')} \b{f}_{\tube[s]} \Big)
-+ \Big( \b{f}_{\tube} + \b{f}_{\tilde \tube'} - \b{f}_{\tube\cup \tilde \tube'} - \sum_{\tube[s] \in \connectedComponents(\tube \cap \tilde \tube')} \b{f}_{\tube[s]} \Big) \\
-& = \b{f}_{\tube} + \b{f}_{\tube'} - \b{f}_{\tube\cup \tube'} - \sum_{\tube[s] \in \connectedComponents(\tube \cap \tube')} \b{f}_{\tube[s]} =\b{n}(\tube, \tube'),
+\b{n}(\tilde \tube, \tube')+\b{n}( \tube, \tilde \tube') &=\b{f}_{\tilde \tube} + \b{f}_{\tube'} - \b{f}_{\tilde \tube\cup \tube'} - \sum_{\tube[s] \in \connectedComponents(\tilde \tube \cap \tube')} \b{f}_{\tube[s]}
++ \b{f}_{\tube} + \b{f}_{\tilde \tube'} - \b{f}_{\tube\cup \tilde \tube'} - \sum_{\tube[s] \in \connectedComponents(\tube \cap \tilde \tube')} \b{f}_{\tube[s]} \\
+&= \b{f}_{\tube} + \b{f}_{\tube'} - \b{f}_{\tube\cup \tube'} - \sum_{\tube[s] \in \connectedComponents(\tube \cap \tube')} \b{f}_{\tube[s]} =\b{n}(\tube, \tube'),
 \end{align*}
-as $\tilde \tube \cup \tube' = \tilde \tube'$, $\tilde \tube \cap \tube' = \tube \cap \tube'$, $\tube \cup \tilde \tube' = \tube \cup \tube'$ and $\connectedComponents(\tube \cap \tilde \tube') = \connectedComponents(\tilde \tube) = \tilde \tube$.
+as $\tube \cup \tilde \tube'=\tube \cup \tube'$, $\tilde \tube \cap \tube'=\tube \cap \tube'$, $\tilde \tube \cup \tube '=\tilde \tube '$,  and $\tube \cap \tilde \tube '=\tilde \tube$.
+% \[\b{n}(\tube, \tube')=\b{n}(\tilde \tube, \tube')+\b{n}( \tube, \tilde \tube'),\] 
 Therefore $\b{n}(\tube, \tube')$ defines a redundant inequality and $\{\tube, \tube'\}$ is not an extremal exchangeable pair.
-The proof is symmetric if~$\tube' \ssm \tube \ne \{v'\}$.
 \end{proof}
@@
 \begin{example}
-\label{exm:constructionsGA}
-We now exploit \cref{lem:extremalExchangeablePairsGAonlyif} to show that certain height functions belong to the type cone of~$\gvectorFan[\graphG]$ and recover the classical constructions of the graph associahedron.
-
-\begin{enumerate}
-\item Consider the height function~$\b{h} \in \R^{\tubes}$ given by~$\b{h}_{\tube} \eqdef -|\bigset{\tube[s] \in \tubes}{\tube[s] \subseteq \tube}|$.
-Then for any tubes~$\tube$ and~$\tube'$ such that ${\tube \ssm \{v\} = \tube' \ssm \{v'\}}$ for some neighbor~$v$ of~$\tube'$ and some neighbor~$v'$ of~$\tube$, we have
-\[
-\qquad\qquad
-\dotprod{\b{n}(\tube, \tube')}{\b{h}} = |\bigset{\tube[s]\in\tubes}{\tube[s] \subseteq \tube[t] \cup \tube' \text{ and } v, v' \in \tube[s]}|,
-\]
-which is positive since at least~$\tube \cup \tube'$ fulfills the condition.
-Thus, $\b{h}$ belongs to the type cone~$\typeCone \big( \gvectorFan[\graphG] \big)$.
-The polytope~$P_\b{h} \eqdef \set{\b{x} \in \R^\ground}{\dotprod{\gvector{\tube}}{\b{x}} \le \b{h}_{\tube} \text{ for any tube } \tube \in \tubes}$ is the graph associahedron constructed by A.~Postnikov's in~\cite{Postnikov}.
-\item Consider now the height function~$\b{h} \in \R^{\tubes}$ given by~$\b{h}_{\tube} \eqdef -3^{|\tube|-2}$.
-Then for any tubes~$\tube$ and~$\tube'$ such that ${\tube \ssm \{v\} = \tube' \ssm \{v'\}}$ for some neighbor~$v$ of~$\tube'$ and some neighbor~$v'$ of~$\tube$, we have
-\[
-\qquad\qquad
-\dotprod{\b{n}(\tube, \tube')}{\b{h}} = - 3^{|\tube|-2} - 3^{|\tube'|-2} + 3^{|\tube \cup \tube'|-2} + \sum_{\tube[s] \in \connectedComponents(\tube \cap \tube')} 3^{|\tube[s]|-2 } \ge - 2 \cdot 3^{|\tube \cup \tube'|-1} + 3^{|\tube \cup \tube'|} > 0.
-\]
-Thus, $\b{h}$ belongs to the type cone~$\typeCone \big( \gvectorFan[\graphG] \big)$.
-The corresponding polytope~$P_\b{h}$ is the graph associahedron constructed by S.~Devadoss's in~\cite{Devadoss}.
-\item Finally, consider the height function~$\b{h} \in \R^{\tubes}$ given by~$\b{h}_{\tube} \eqdef |\bigset{\tube[s] \in \tubes}{\tube[s] \supseteq \tube}|$.
-Then for any tubes~$\tube$ and~$\tube'$ such that ${\tube \ssm \{v\} = \tube' \ssm \{v'\}}$ for some neighbor~$v$ of~$\tube'$ and some neighbor~$v'$ of~$\tube$, we have
-\begin{align*}
-\qquad\qquad
-\dotprod{\b{n}(\tube, \tube')}{\b{h}} = \; & |\bigset{\tube[r] \in \tubes, \tube[s] \in \connectedComponents(\tube \cap \tube')}{\tube[s] \subseteq \tube[r] \text{ and } \tube, \tube' \not\subseteq \tube[r]}| \\
-& + \big( |\connectedComponents(\tube \cap \tube')|-1 \big) \cdot | \bigset{\tube[r] \in \tubes}{\tube \text{ or } \tube'\subseteq \tube[r]}\big|.
-\end{align*}
-Any connected component of~$\tube \cap \tube'$ certifies the positivity of this evaluation, showing that $\b{h}$ belongs to~$\typeCone \big( \gvectorFan[\graphG] \big)$.
-The corresponding realization~$P_\b{h}$ of the graph associahedron is new, to the best of our knowledge.
-\end{enumerate}
+Let $\graphG$ be a graph. Consider the vectors $\b{a}, \b{b}, \b{c}\in\R^{\tubes}$ whose entries for $\tube[s]\in\tubes$ are given by 
+$\b{a}_{\tube[s]}=-\big| \set{\tube[u]\in\tubes}{\tube[u]\subseteq \tube[s]}\big| $, $\b{b}_{\tube[s]}=-3^{\big| \tube[s]\big| -2}$, and $\b{c}_{\tube[s]}=-\big| \set{\tube[u]\in\tubes}{\tube[u]\supseteq \tube[s]}\big| $, respectively.
+
+Now, let $\tube$ and~$\tube'$ be tubes such that ${\tube \ssm \{v\} = \tube' \ssm \{v'\}}$ for some neighbor~$v$ of~$\tube'$ and some neighbor~$v'$ of~$\tube$, and let 
+$\b{n}(\tube, \tube')$ be as in~\cref{lem:extremalExchangeablePairsGAonlyif}.
+
+We have
+\[\dotprod{\b{n}(\tube, \tube')}{\b{a}}=\big|\set{\tube[u]\in\tubes}{\tube[u]\subseteq\tube[t]\cup\tube[t']\text{ and }v,v'\in\tube[u]}|,\]
+which is positive since at least $\tube[u]=\tube[t]\cup\tube[t']$ fulfills this condition.
+Hence $\b{a}\in\typeCone(\gvectorFan[\graphG])$.
+This gives Postnikov's realization of the graph associahedron from~\cite{Postnikov}.
+
+Setting $x=|\tube \cap \tube'|$, we get
+\[\dotprod{\b{n}(\tube, \tube')}{\b{b}}=3^{|\tube[t]\cup\tube[t']| -2}- 3^{|\tube[t]| -2}- 3^{|\tube[t']| -2} +\sum_{\tube[s] \in \connectedComponents(\tube \cap \tube')} 3^{|\tube[s]|-2 }\geq 3^{x}- 2\cdot 3^{x-1}>0.\]
+This shows that $\b{b}\in\typeCone(\gvectorFan[\graphG])$, and we recover Devadoss' realization of graph-associahedra~\cite{Devadoss}.
+
+Finally, 
+\[\dotprod{\b{n}(\tube, \tube')}{\b{c}}=\big| \set{(\tube[u], \tube[s])\in\tubes\times \connectedComponents(\tube[t]\cap\tube[t'])}{\tube[s]\subseteq\tube[u]\text{ and }\tube,\tube'\not\subseteq u}\big| +(\big| \connectedComponents(\tube[t]\cap\tube[t'])\big| -1)\big| \set{\tube[u]\in\tubes}{\tube\text{ or }\tube'\subseteq \tube[u]}\big| .\]
+Any connected component of $\tube\cap \tube'$ certifies the positivity of this evaluation, showing that $\b{c}\in\typeCone(\gvectorFan[\graphG])$. This realization of 
+the graph-associahedron is new, to the best of our knowledge. 
+\arnau{Is it worth to add it?}
+\arnau{recheck details}
+
 \end{example}
-
-We now show that the condition of \cref{lem:extremalExchangeablePairsGAonlyif} actually characterizes the extremal exchangeable pairs of the nested fan~$\gvectorFan[\graphG]$.
 
@@
 \begin{proof}
-By \cref{lem:extremalExchangeablePairsGAonlyif}, an exchangeable pair $\{\tube, \tube'\}$ is not extremal unless both $\tube \ssm \tube'$ and $\tube' \ssm \tube$ are singletons.
+
+We have seen that an exchangeable pair $\{\tube, \tube'\}$ is not extremal unless both $\tube\ssm \tube'$ and $\tube'\ssm \tube$ are singletons.
 We now need to show that all these pairs are extremal.
@@
 Let $\{\tube, \tube'\}$ be a suspected extremal pair.
-To prove that it is extremal, we will construct a vector $\b{w} \in \R^{\tubes}$ such that $\dotprod{\b{n}(\tube, \tube')}{\b{w}}< 0,$
+To prove that it is extremal, we will construct a vector $\b{w}\in\R^{\tubes}$ such that $\dotprod{\b{n}(\tube, \tube')}{\b{w}}< 0,$
 but $\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{w}}>0$ for any other suspected extremal pair $\{\tilde \tube, \tilde \tube'\}$.
@@
 
-Define $\alpha(\tube,\tube') \eqdef \set{\tube[u] \in \tubes}{\tube[u] \subseteq \tube \cup \tube' \text{ and } \tube \symdif \tube' \subseteq \tube[u]}$, where $\symdif$ denotes the symmetric difference, and let $\b{x} \in \R^{\tubes}$ be such that
-\[
-\b{x}_{\tube[s]} = -|\bigset{\tube[u] \in \tubes \ssm \alpha(\tube, \tube')}{\tube[u] \subseteq \tube[s]}|
-\]
-for each tube~$\tube[s] \in \tubes$.
+Define $\alpha(\tube,\tube')=\set{\tube[u]\in\tubes}{\tube[u]\subseteq \tube \cup \tube'\text{ and } \tube\triangle\tube'\subseteq \tube[u]}$, where $\tube\triangle\tube'$ denotes the symmetric difference, and let $\b{x}\in\R^{\tubes}$ be such that
+\[\b{x}_{\tube[s]}=-\big|\set{\tube[u]\in \tubes\ssm \alpha(\tube,\tube')}{\tube[u]\subseteq \tube[s]}\big|\]
+for each tube~$\tube[s]\in\tubes$.
 
 For any suspected extremal pair $\{\tilde \tube, \tilde \tube'\}$ we have
-\[
-\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{x}} = |\alpha(\tilde \tube, \tilde \tube')\ssm \alpha(\tube, \tube')| \ge 0.
-\]
-Notice that $\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{x}} = 0$ if $\alpha(\tilde \tube, \tilde \tube') \subseteq \alpha(\tube,\tube')$ and $\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{x}} \ge 1$ otherwise.
-In particular, if $\{\tilde \tube, \tilde \tube'\} \ne \{\tube, \tube'\}$ then $\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{x}} \ge 1$ unless $\tilde \tube \cup \tilde \tube' \subsetneq \tube \cup \tube'$ because $\tilde \tube \cup \tilde \tube' \in \alpha(\tilde \tube, \tilde \tube')$, and if $\tilde \tube \cup \tilde \tube' = \tube \cup \tube'$ but $\{\tilde \tube, \tilde \tube'\} \ne \{\tube, \tube'\}$, then either $\tube$ or $\tube'$ will belong to $\alpha(\tilde \tube, \tilde \tube')$.
-
-Now, define $\b{y}\in\R^{\tubes}$ by
-\[
-\b{y}_{\tube[s]} \eqdef \begin{cases}
-	-1 & \text{ if } |\tube[s]| \ge |\tube| \\
-	0 & \text{ otherwise.}
-\end{cases}
-\]
-We have $\dotprod{\b{n}(\tube, \tube')}{\b{y}} = -1$.
-For any suspected extremal pair $\{\tilde \tube, \tilde \tube'\}$ we have $\dotprod{\b{n}(\tube, \tube')}{\b{y}}\ge -1$.
-If moreover $\tilde \tube \cup \tilde \tube' \subsetneq \tube \cup \tube'$, then we have $\dotprod{\b{n}(\tube, \tube')}{\b{y}} \ge 0$.
-
-Finally, consider $\b{z} \in \R^{\tubes}$ given by
-\[
-\b{z}_{\tube[s]} = -|\bigset{\tube[u] \in \alpha(\tube, \tube')}{\tube[u] \subseteq \tube[s]}|.
-\]
-It verifies $\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{z}} \ge 0$ for any suspected extremal pair~$\{\tilde \tube, \tilde \tube'\}$, and $\dotprod{\b{n}(\tube, \tube')}{\b{z}} = |\alpha(\tilde \tube, \tilde \tube')| > 0$ if $\alpha(\tilde \tube, \tilde \tube') \subseteq \alpha(\tube, \tube')$.
-
-For $0 < \varepsilon < 1$, and $0 < \delta < \frac{\varepsilon}{|\alpha(\tube, \tube')|}$, the vector $\b{w} \eqdef \b{x} + \varepsilon \b{y} + \delta \b{z}$ fulfills the desired properties.
-Indeed, if $\{\tilde \tube, \tilde \tube'\} \ne \{\tube,\tube'\}$ is a suspected extremal pair with $\alpha(\tilde \tube, \tilde \tube') \not \subseteq \alpha(\tube,\tube')$, then 
-\[
-\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{w}} = \underbrace{\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{x}}}_{\ge 1} + \underbrace{\varepsilon \dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{y}}}_{> -1} + \underbrace{\delta \dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{z}}}_{\ge 0} > 0.
-\]
-If $\{\tilde \tube, \tilde \tube'\} \ne \{\tube,\tube'\}$ is a suspected extremal pair with $\alpha(\tilde \tube, \tilde \tube') \subseteq \alpha(\tube,\tube')$, then $\tilde \tube \cup \tilde \tube' \subsetneq \tube \cup \tube'$ and
-\[
-\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{w}} = \underbrace{\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{x}}}_{= 0} + \underbrace{\varepsilon \dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{y}}}_{\ge 0} + \underbrace{\delta \dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{z}}}_{> 0} > 0.
-\]
+\[\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{x}}= \big|\alpha(\tilde \tube, \tilde \tube ')\ssm \alpha(\tube,\tube')|\geq0.\]
+Notice that $\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{x}}=0$ if $\alpha(\tilde \tube, \tilde \tube ')\subseteq \alpha(\tube,\tube')$ and
+$\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{x}}\geq 1$ otherwise.
+In particular, if $\{\tilde \tube, \tilde \tube'\}\neq \{\tube, \tube'\}$ then
+$\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{x}}\geq 1$ unless $\tilde \tube\cup \tilde \tube'\subsetneq \tube\cup \tube'$ because 
+ $\tilde \tube\cup \tilde \tube'\in\alpha(\tilde \tube, \tilde \tube ')$, and if $\tilde \tube\cup \tilde \tube'=\tube\cup \tube'$ but $\{\tilde \tube, \tilde \tube'\}\neq \{\tube, \tube'\}$, then either $\tube$ or $\tube'$ will belong to $\alpha(\tilde \tube, \tilde \tube ')$.
+
+Now, define $\b{y}\in\R^{\tubes}$ by \[\b{y}_{\tube[s]}=\begin{cases}
+                             -1&\text{ if }|\tube[s]|\geq |\tube|\\
+                             0&\text{ otherwise.}
+                            \end{cases}\]
+We have $\dotprod{\b{n}(\tube, \tube')}{\b{y}}=-1$.
+For any suspected extremal pair $\{\tilde \tube, \tilde \tube'\}$ we have $\dotprod{\b{n}(\tube, \tube')}{\b{y}}\geq -1$.
+If moreover $\tilde \tube\cup \tilde \tube'\subsetneq \tube\cup \tube'$, then we have $\dotprod{\b{n}(\tube, \tube')}{\b{y}}\geq 0$.
+
+Finally, consider $\b{z}\in\R^{\tubes}$ given by
+\[\b{z}_{\tube[s]}=-\big|\set{\tube[u]\in \alpha(\tube,\tube')}{\tube[u]\subseteq \tube[s]}\big|. \]
+It verifies $\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{z}}\geq0$ for any suspected extremal pair~$\{\tilde \tube, \tilde \tube'\}$, and $\dotprod{\b{n}(\tube, \tube')}{\b{z}}=|\alpha(\tilde \tube, \tilde \tube ')|>0$ if $\alpha(\tilde \tube, \tilde \tube ')\subseteq \alpha(\tube,\tube')$.
+
+For $0<\varepsilon<1$, and $0<\delta<\frac{\varepsilon}{|\alpha(\tube,\tube')|}$, the vector $\b{w}=\b{x}+\varepsilon \b{y}+\delta \b{z}$ fulfills the desired properties.
+Indeed, if $\{\tilde \tube, \tilde \tube'\}\neq \{\tube,\tube '\}$ is a suspected extremal pair with $\alpha(\tilde \tube, \tilde \tube ')\not \subseteq \alpha(\tube,\tube')$, then 
+\[\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{w}}=\underbrace{\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{x}}}_{\geq 1}+\underbrace{\varepsilon \dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{y}}}_{> -1}+\underbrace{\delta \dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{z}}}_{\geq 0}> 0.\]
+ If $\{\tilde \tube, \tilde \tube'\}\neq \{\tube,\tube '\}$ is a suspected extremal pair with $\alpha(\tilde \tube, \tilde \tube ')\subseteq \alpha(\tube,\tube')$, then $\tilde \tube\cup \tilde \tube'\subsetneq \tube\cup \tube'$ and
+\[\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{w}}=\underbrace{\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{x}}}_{=0}+\underbrace{\varepsilon \dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{y}}}_{\geq 0}+\underbrace{\delta \dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{z}}}_{>0}> 0.\]
 However,
-\[
-\dotprod{\b{n}(\tube, \tube')}{\b{w}} = \underbrace{\dotprod{\b{n}(\tube, \tube')}{\b{x}}}_{= 0} + \underbrace{\varepsilon \dotprod{\b{n}(\tube, \tube')}{\b{y}}}_{= -\varepsilon} + \underbrace{\delta \dotprod{\b{n}( \tube,  \tube')}{\b{z}}}_{= \delta |\alpha(\tube ,\tube')| < \varepsilon} < 0.
-\qedhere
-\]
+\[\dotprod{\b{n}(\tube, \tube')}{\b{w}}=\underbrace{\dotprod{\b{n}(\tube, \tube')}{\b{x}}}_{=0}+\underbrace{\varepsilon \dotprod{\b{n}(\tube, \tube')}{\b{y}}}_{=-\varepsilon}+\underbrace{\delta \dotprod{\b{n}( \tube,  \tube')}{\b{z}}}_{=\delta|\alpha(\tube ,\tube')|<\varepsilon}< 0.\]
+
 \end{proof}
@@
 \label{coro:extremalExchangeablePairsGA}
-The extremal exchangeable pairs for the nested fan of~$\graphG$ are precisely the pairs of tubes~${\tube[s] \ssm \{v'\}}$ and~${\tube[s] \ssm \{v\}}$ for any tube~$\tube[s] \in \tubes$ and distinct non-disconnecting vertices~$v,v'$~of~$\tube[s]$.
+The extremal exchangeable pairs for the nested fan of~$\graphG$ are the pairs of tubes~$\tube[s] \ssm \{v'\}$ and~$\tube[s] \ssm \{v\}$ for any tube~$\tube[s] \in \tubes$ and distinct non-disconnecting vertices~$v,v'$ of~$\tube[s]$.
+% equivalently
+% \begin{enumerate}[(i)]
+% \item the pairs of tubes~$\tube[r] \cup \{v\}$ and~$\tube[r] \cup \{v'\}$ for any tube~$\tube[r] \in \tubes$ and distinct neighbors~$v,v'$ of~$\tube[r]$,
+% \item the pairs of tubes~$\tube[s] \ssm \{v'\}$ and~$\tube[s] \ssm \{v\}$ for any tube~$\tube[s] \in \tubes$ and distinct non-disconnecting vertices~$v,v'$ of~$\tube[s]$,
+% \end{enumerate}
 \end{corollary}
+\arnau{The two conditions were not equivalent. I removed the wrong one.}
 
 We derive from \cref{prop:extremalExchangeablePairsGA} and \cref{coro:extremalExchangeablePairsGA} all polytopal realizations of the nested fan, which we can explicitly express.
+% using one of the following two equivalent conditions.
 
@@
  $\b{h}_{\tube[s] \ssm \{v'\}} + \b{h}_{\tube[s] \ssm \{v\}} > \b{h}_{\tube[s]} + \b{h}_{\tube[s] \ssm \{v, v'\}}$ for any tube~$\tube[s] \in \tubes$ and distinct non-disconnecting vertices~$v,v'$ of~$\tube[s]$.
+% one of the two following equivalent conditions:
+% \begin{enumerate}[(i)]
+% \item $\b{h}_{\tube[r] \cup \{v\}} + \b{h}_{\tube[r] \cup \{v'\}} > \b{h}_{\tube[r] \cup \{v, v'\}} + \b{h}_{\tube[r]}$ for any tube~$\tube[r] \in \tubes$ and distinct neighbors~$v,v'$ of~$\tube[r]$,
+% \item $\b{h}_{\tube[s] \ssm \{v'\}} + \b{h}_{\tube[s] \ssm \{v\}} > \b{h}_{\tube[s]} + \b{h}_{\tube[s] \ssm \{v, v'\}}$ for any tube~$\tube[s] \in \tubes$ and distinct non-disconnecting vertices~$v,v'$ of~$\tube[s]$.
+% \end{enumerate}
+
 Then the nested fan~$\gvectorFan[\graphG]$ is the normal fan of the graph associahedron
@@
 %\begin{proof}
-%By \cref{prop:extremalExchangeablePairsGA}, extremal exchangeable pairs are in bijection with quadruples~$(\tube[r], \tube[t], \tube', \tube[s])$ of tubes of~$\graphG$ where~$\tube[t]$ and~$\tube'$ are distinct tubes covering~$\tube[r]$ and covered by~$\tube[s]$ in the inclusion poset of all tubes of~$\graphG$.
+%By \cref{prop:extremalExchangeablePairsGA}, extremal exchangeable pairs are in bijection with quadruples~$(\tube[r], \tube[t], \tube[t'], \tube[s])$ of tubes of~$\graphG$ where~$\tube[t]$ and~$\tube[t']$ are distinct tubes covering~$\tube[r]$ and covered by~$\tube[s]$ in the inclusion poset of all tubes of~$\graphG$.
 %The result immediately follows.
@@
 \begin{proposition}
-The type cone~$\typeCone \big( \gvectorFan[\graphG] \big)$ is simplicial if and only if~$\graphG$ is a path.
+The type cone~$\typeCone(\gvectorFan[\graphG])$ is simplicial if and only if~$\graphG$ is a path.
 \end{proposition}
@@
  \]
- Therefore~$\langle x, [A] \rangle = \dim_{\field} \coker(f) \ge 0$.
+ Therefore~$\langle x, [A] \rangle = \dim_{\field} \coker(f) \geq 0$.
 \end{proof}
@@
 Moreover, it has Auslander--Reiten--Serre duality by~\cite[Proposition 6.1]{IyamaNakaokaPalu}.
+\end{proof}
+
+The extriangulated category~$K^{[-1,0]}(\proj \Lambda)$ is the setting in which we can finally prove point~(ii) of Proposition~\ref{prop:exchangeablePairsNKC}, using results of~\cite{DemonetIyamaJasso} on~$\b g$-vectors.
+
+\begin{proposition}
+ Let~$\Lambda$ be a finite-dimensional~$\field$-algebra, where~$\field$ is a field.  Let~$X$ and~$Y$ be objects of~$K^{[-1,0]}(\proj \Lambda)$.  Assume that~ \pg{Finish this} 
+ Then~$E$ and~$E'$ are isomorphic.
+\end{proposition}
+\begin{proof}
+ By~\cite[Theorem 6.5]{DemonetIyamaJasso} (based on~\cite[Theorem 2.3]{DehyKeller}), rigid objects in~$K^{[-1,0]}(\proj \Lambda)$ are determined by their~$\b g$-vector.
+The datum of the~$\b g$-vector of an object of~$K^{[-1,0]}(\proj \Lambda)$ is equivalent to that of its class in the Grothendieck group~$K_0(K^{[-1,0]}(\proj \Lambda))$, where~$K^{[-1,0]}(\proj \Lambda)$ is viewed as an extriangulated category (see Proposition~\ref{2kbproj-is-extriangulated}).
+In this Grothendieck group, we have that~$[E] = [E'] = [X]+[Y]$.
+Thus~$E$ and~$E'$ are isomorphic.
+\end{proof}
+
+\begin{corollary}\label{coro::exchangeablePairsNKC}
+ Point~(ii) of Proposition~\ref{prop:exchangeablePairsNKC} holds.
+\end{corollary}
+\begin{proof}
+
 \end{proof}
@@
 One can check directly that the condition of Theorem~\ref{theo::brick-algebra-condition} is not satisfied.
-For example, the module~$\bsm2\\1\esm$ is~$\tau$-rigid since~$\tau(\bsm2\\1\esm) = \bsm3\\1\esm$, while~$\Hom{\Lambda}\left(\bsm2\\1\esm,\tau^2(\bsm2\\1\esm)\right) = \Hom{\Lambda}(\bsm2\\1\esm,\bsm1\\2\esm) \ne 0$.
+For example, the module~$\bsm2\\1\esm$ is~$\tau$-rigid since~$\tau(\bsm2\\1\esm) = \bsm3\\1\esm$, while~$\Hom{\Lambda}\left(\bsm2\\1\esm,\tau^2(\bsm2\\1\esm)\right) = \Hom{\Lambda}(\bsm2\\1\esm,\bsm1\\2\esm) \neq 0$.
 \end{example}

### 2019-06-10 thirdPaper/draft/typeConeAssociahedra.tex

--- 2019-06-10 thirdPaper/draft/typeConeAssociahedra.tex
@@
 \begin{enumerate}[(i)]
+
 \item For any non-kissing facets~$F, F'$ of~$\NKC$ with~$F \ssm \{\omega\} = f' \ssm \{\omega'\}$, the distinguished substrings of~$\omega$ in~$F$ and of~$\omega'$ in~$F'$ coincide to a string~$\sigma$.
 Moreover, if we decompose~${\omega = \rho \sigma \tau}$ and~${\omega' = \rho' \sigma \tau'}$, then the facets~$F$ and~$F'$ both contain the walks~$\mu \eqdef \rho' \sigma \tau$ and~$\nu \eqdef \rho \sigma \tau'$.
-\item The substring~$\sigma$ and thus the walks~$\mu$ and~$\nu$ actually depend on the exchangeable walks~$\omega$ and~$\omega'$, not on the adjacent non-kissing facet~$F $ and~$F'$.
+\item The substring~$\sigma$ and thus the walks~$\mu$ and~$\nu$ only depend on the exchangeable walks~$\omega$ and~$\omega'$, and not on the adjacent non-kissing facet~$F $ and~$F'$.
 \item The linear dependence between the $\b{g}$-vectors of~$F \cup F'$ is given by
@@
 
+The extriangulated category~$K^{[-1,0]}(\proj \Lambda)$ is the setting in which we can finally prove point~(ii) of Proposition~\ref{prop:exchangeablePairsNKC}, using results of~\cite{DemonetIyamaJasso} on~$\b g$-vectors.
+
+\begin{proposition}
+ Let~$\Lambda$ be a finite-dimensional~$\field$-algebra, where~$\field$ is a field.  Let~$X$ and~$Y$ be objects of~$K^{[-1,0]}(\proj \Lambda)$.  Assume that~ \pg{Finish this} 
+ Then~$E$ and~$E'$ are isomorphic.
+\end{proposition}
+\begin{proof}
+ By~\cite[Theorem 6.5]{DemonetIyamaJasso} (based on~\cite[Theorem 2.3]{DehyKeller}), rigid objects in~$K^{[-1,0]}(\proj \Lambda)$ are determined by their~$\b g$-vector.
+The datum of the~$\b g$-vector of an object of~$K^{[-1,0]}(\proj \Lambda)$ is equivalent to that of its class in the Grothendieck group~$K_0(K^{[-1,0]}(\proj \Lambda))$, where~$K^{[-1,0]}(\proj \Lambda)$ is viewed as an extriangulated category (see Proposition~\ref{2kbproj-is-extriangulated}).
+In this Grothendieck group, we have that~$[E] = [E'] = [X]+[Y]$.
+Thus~$E$ and~$E'$ are isomorphic.
+\end{proof}
+
+\begin{corollary}\label{coro::exchangeablePairsNKC}
+ Point~(ii) of Proposition~\ref{prop:exchangeablePairsNKC} holds.
+\end{corollary}
+\begin{proof}
+
+\end{proof}
+
 Proposition~\ref{prop::2kbproj-is-extriangulated} gives a setting in which to apply Theorem~\ref{}.

### 2019-06-10 thirdPaper/draft/typeConeAssociahedra.tex
Corollary 4.43 + minor changes.

@@
 Points~(i), (iii) and~(iv) where shown in~\cite[Prop.~2.33, Thm.~4.17 \& Prop~4.16]{PaluPilaudPlamondon-nonkissing}.
-\vincent{Point~(ii) to prove.}
+We postpone the proof of point~(ii) until Corollary~\ref{coro::exchangeablePairsNKC}.
 \end{proof}
@@
 \begin{proposition}
- Let~$\Lambda$ be a finite-dimensional~$\field$-algebra, where~$\field$ is a field.  Let~$X$ and~$Y$ be objects of~$K^{[-1,0]}(\proj \Lambda)$.  Assume that~ \pg{Finish this} 
- Then~$E$ and~$E'$ are isomorphic.
+\label{prop::exchange conflations are unique}
+ Let~$\Lambda$ be a finite-dimensional~$\field$-algebra, where~$\field$ is a field.
+Let~$X$ and~$Y$ be objects of~$K^{[-1,0]}(\proj \Lambda)$.
+Assume that~$X\infl E\defl Y$ and~$X\infl E'\defl Y$ are two mutation conflations (see Definition~\ref{defn::mutation conflation}.
+ Then~$E$ and~$E'$ are isomorphic. \pg{Is is possible that~$X$ and~$Y$ are permuted in one of the exchange conflations?}
 \end{proposition}
@@
  By~\cite[Theorem 6.5]{DemonetIyamaJasso} (based on~\cite[Theorem 2.3]{DehyKeller}), rigid objects in~$K^{[-1,0]}(\proj \Lambda)$ are determined by their~$\b g$-vector.
-The datum of the~$\b g$-vector of an object of~$K^{[-1,0]}(\proj \Lambda)$ is equivalent to that of its class in the Grothendieck group~$K_0(K^{[-1,0]}(\proj \Lambda))$, where~$K^{[-1,0]}(\proj \Lambda)$ is viewed as an extriangulated category (see Proposition~\ref{2kbproj-is-extriangulated}).
+The datum of the~$\b g$-vector of an object of~$K^{[-1,0]}(\proj \Lambda)$ is equivalent to that of its class in the Grothendieck group~$K_0(K^{[-1,0]}(\proj \Lambda))$, where~$K^{[-1,0]}(\proj \Lambda)$ is viewed as an extriangulated category (see Proposition~\ref{prop::2kbproj-is-extriangulated}).
 In this Grothendieck group, we have that~$[E] = [E'] = [X]+[Y]$.
@@
 \begin{proof}
-
+ Let~$\omega$ and~$\omega'$ be in facets~$F$ and~$F'$ as in the statement of Proposition~\ref{prop:exchangeablePairsNKC}.
+For every walk~$\omega''$, let~$P(\omega'')$ be the object of~$K^{[-1,0]}(\proj \Lambda)$ corresponding to~$\omega''$.
+Then the walks~$\mu$ and~$\nu$ defined in the same statement yield an exchange conflation
+ \[
+  P(\omega) \infl P(\mu) \oplus P(\nu) \defl P(\omega') \quad \textrm{or} \quad P(\omega') \infl P(\mu) \oplus P(\nu) \defl P(\omega).
+ \]
+ Assume that there are other facets~$F_0$ and~$F_0'$ also satisfying the hypotheses of Proposition~\ref{prop:exchangeablePairsNKC}.
+Then they give rise to walks~$\mu'$ and~$\nu'$ and an exchange conflation
+ \[
+  P(\omega) \infl P(\mu') \oplus P(\nu') \defl P(\omega') \quad \textrm{or} \quad P(\omega') \infl P(\mu') \oplus P(\nu') \defl P(\omega).
+ \]
+ By Proposition~\ref{prop::exchange conflations are unique}, we get that~$P(\mu)\oplus P(\nu)$ and~$P(\mu')\oplus P(\nu')$ are isomorphic.
+This implies that~$\{\mu,\nu\}$ and~$\{\mu',\nu'\}$ are the same sets.
+This determines~$\sigma$, and point (ii) of Proposition~\ref{prop:exchangeablePairsNKC} is proved.
 \end{proof}
 
-Proposition~\ref{prop::2kbproj-is-extriangulated} gives a setting in which to apply Theorem~\ref{}.
+% Proposition~\ref{prop::2kbproj-is-extriangulated} gives a setting in which to apply Theorem~\ref{}.
 Before stating our next theorem, we first recall some definitions

### 2019-06-10 thirdPaper/draft/typeConeAssociahedra.tex
Changed order: Coro 4.43 is now Coro 4.46.

@@
 The extriangulated category~$K^{[-1,0]}(\proj \Lambda)$ is the setting in which we can finally prove point~(ii) of Proposition~\ref{prop:exchangeablePairsNKC}, using results of~\cite{DemonetIyamaJasso} on~$\b g$-vectors.
+% Proposition~\ref{prop::2kbproj-is-extriangulated} gives a setting in which to apply Theorem~\ref{}.
+Before doind so, we introduce the notion of mutation conflation for two-term silting objects.
+
+\begin{definition}
+Recall that a two-term silting object is a complex~$T$ in~$K^{[-1,0]}(\proj \Lambda)$ such that~$\Hom{K^b}(T,\susp T)=0$ and the number of isomorphism classes of indecomposable summands of~$T$ is the same as that of~$\Lambda$.
+\end{definition}
+
+\begin{remark}
+ The definition given above is only equivalent to the usual definition of a silting object for two-term complexes of projectives.
+\end{remark}
+
+\begin{definition}\label{defn::mutation conflation}
+A conflation $X\infl E\defl Y$ of~$K^{[-1,0]}(\proj \Lambda)$ is called a \defn{mutation conflation} if there are basic, two-term, silting objects $X\oplus R$, $Y\oplus R$ such that the inflation $X\infl E$ is a left ($\add R$)-approximation (i.e.
+any morphism from~$X$ to an object in~$\add R$ factors through~$X\infl E$).
+\end{definition}
 
@@
 Let~$X$ and~$Y$ be objects of~$K^{[-1,0]}(\proj \Lambda)$.
-Assume that~$X\infl E\defl Y$ and~$X\infl E'\defl Y$ are two mutation conflations (see Definition~\ref{defn::mutation conflation}.
- Then~$E$ and~$E'$ are isomorphic. \pg{Is is possible that~$X$ and~$Y$ are permuted in one of the exchange conflations?}
+Assume that~$X\infl E\defl Y$ and~$X\infl E'\defl Y$ (or~$Y\infl E'\defl X$) are two mutation conflations (see Definition~\ref{defn::mutation conflation}.
+ Then~$E$ and~$E'$ are isomorphic. \pg{Is it possible that~$X$ and~$Y$ are permuted in one of the exchange conflations?}
 \end{proposition}
@@
 
-% Proposition~\ref{prop::2kbproj-is-extriangulated} gives a setting in which to apply Theorem~\ref{}.
-Before stating our next theorem, we first recall some definitions
-
-\begin{definition}
-Recall that a two-term silting object is a complex~$T$ in~$K^{[-1,0]}(\proj \Lambda)$ such that~$\Hom{K^b}(T,\susp T)=0$ and the number of isomorphism classes of indecomposable summands of~$T$ is the same as that of~$\Lambda$.
-\end{definition}
-
-\begin{remark}
- The definition given above is only equivalent to the usual definition of a silting object for two-term complexes of projectives.
-\end{remark}
-
-\begin{definition}\label{defn::mutation conflation}
-A conflation $X\infl E\defl Y$ of~$K^{[-1,0]}(\proj \Lambda)$ is called a \defn{mutation conflation} if there are basic, two-term, silting objects $X\oplus R$, $Y\oplus R$ such that the inflation $X\infl E$ is a left ($\add R$)-approximation (i.e.
-any morphism from~$X$ to an object in~$\add R$ factors through~$X\infl E$).
-\end{definition}
+We now come to the main result of this section.
 

### 2019-06-10 thirdPaper/draft/typeConeAssociahedra.tex
Last example

@@
 
-\begin{example}[Preprojective algebra of type~$A_3$]
+\begin{example}[Preprojective algebra of type~$A_3$]\label{exam::preprojective silting objects}
  Let~$\Lambda$ be the preprojective algebra of type~$A_3$: it is the path algebra of the quiver
@@
 \subsubsection{A quotient of a Frobenius category}
+\begin{example}
+ Consider the preprojective algebra of type~$A_3$, as in Example~\ref{exam::preprojective silting objects}.
+It is a self-injective algebra, so its module category is a Frobenius category.
+Its projective-injective objects are the modules
+ \[
+  \begin{matrix} 1 \\ 2 \\ 3 \end{matrix} \quad , \quad  \begin{matrix} 2 \\ 13 \\ 2 \end{matrix} \quad \textrm{and} \quad \begin{matrix} 3 \\ 2 \\ 1 \end{matrix}.
+ \]
+ Taking the quotient by the ideal generated by all morphisms factoring through direct sums of copies of the second of these objects, we get an extriangulated category whose Auslander--Reiten quiver is given by
+  \[
+  \hspace*{-2cm}
+ {\footnotesize
+  \begin{tikzcd}
+   \begin{matrix} 3 \end{matrix}\arrow[dr] && \begin{matrix} 2 \\ 1 \end{matrix}\arrow[r]\arrow[dr] & \begin{matrix} 3 \\ 2 \\ 1 \end{matrix}\arrow[r]& \begin{matrix} 3 \\ 2 \end{matrix}\arrow[dr] && \begin{matrix} 1 \end{matrix}\arrow[dr]&& \begin{matrix} 2 \\ 3 \end{matrix} \\
+    & \begin{matrix} 2\\ 13 \end{matrix}\arrow[ur]\arrow[dr] && \begin{matrix} 2 \end{matrix}\arrow[ur]\arrow[dr] && \begin{matrix} 13\\2 \end{matrix}\arrow[ur]\arrow[dr] && \begin{matrix} 2\\13 \end{matrix}\arrow[ur]\arrow[dr] &  \\
+   \begin{matrix} 1 \end{matrix}\arrow[ur] && \begin{matrix} 2\\3 \end{matrix}\arrow[ur]\arrow[r] & \begin{matrix} 1\\2\\3 \end{matrix}\arrow[r] & \begin{matrix} 1\\2 \end{matrix}\arrow[ur] && \begin{matrix} 3\\1 \end{matrix}\arrow[ur] && \begin{matrix} 2\\1 \end{matrix}
+  \end{tikzcd}
+  }
+ \]
+\end{example}
 

### 2019-06-11 thirdPaper/draft/typeConeAssociahedra.tex
Improved Prop.4.45 and Coro 4.46.

@@
 % Proposition~\ref{prop::2kbproj-is-extriangulated} gives a setting in which to apply Theorem~\ref{}.
-Before doind so, we introduce the notion of mutation conflation for two-term silting objects.
+Before doing so, we introduce the notion of mutation conflation for two-term silting objects.
 
@@
 any morphism from~$X$ to an object in~$\add R$ factors through~$X\infl E$).
+\pg{To simplify, we should perhaps ask for the approximations to be minimal.}
 \end{definition}
@@
 \label{prop::exchange conflations are unique}
- Let~$\Lambda$ be a finite-dimensional~$\field$-algebra, where~$\field$ is a field.
-Let~$X$ and~$Y$ be objects of~$K^{[-1,0]}(\proj \Lambda)$.
-Assume that~$X\infl E\defl Y$ and~$X\infl E'\defl Y$ (or~$Y\infl E'\defl X$) are two mutation conflations (see Definition~\ref{defn::mutation conflation}.
- Then~$E$ and~$E'$ are isomorphic. \pg{Is it possible that~$X$ and~$Y$ are permuted in one of the exchange conflations?}
+ Let~$\Lambda$ be a finite-dimensional~$\field$-algebra, where~$\field$ is a field.  Let~$X$ and~$Y$ be objects of~$K^{[-1,0]}(\proj \Lambda)$.  
+ \begin{enumerate}
+  \item If there is a mutation conflation (see Definition~\ref{defn::mutation conflation}) of the form~$X\infl E\defl Y$, then there can be no mutation conflation of the form~$Y\infl E'\defl X$.
+
+  \item Assume that~$X\infl E\defl Y$ and~$X\infl E'\defl Y$ are two mutation conflations.  
+ Then~$E$ and~$E'$ are isomorphic. 
+ \end{enumerate} 
 \end{proposition}
 \begin{proof}
+ We first prove~(1).
+Assume that~$X\infl E\defl Y$ and~$Y\infl E'\defl X$ are two mutation conflations.
+Applying the functor~$\Hom{K^b}(\susp^{-1} Y, -)$ to the second sequence, we get an exact sequence of abelian groups
+ \[
+  \Hom{K^b}(\susp^{-1} Y, E') \to \Hom{K^b}(\susp^{-1} Y, X) \Hom{K^b}(\susp^{-1} Y, \susp Y).
+ \]
+ By definition of a mutation conflation, we have that~$\Hom{K^b}(\susp^{-1} Y, E') = 0$.
+Moreover, since~$Y$ is concentrated in homological degrees~$-1$ and~$0$, we get that~$\Hom{K^b}(\susp^{-1} Y, \susp Y) = 0$.
+Therefore,~$\Hom{K^b}(\susp^{-1} Y, X) = 0$.
+ However, since the conflation~$X\infl E\defl Y$ is not split, we have that~$\Hom{K^b}(\susp^{-1} Y, X) \neq 0$, a contradiction.  This proves~(1).
+
+ \smallskip
+
+ We now prove~(2).
+Let~$X\infl E\defl Y$ and~$X\infl E'\defl Y$ be two mutation conflations.
 By~\cite[Theorem 6.5]{DemonetIyamaJasso} (based on~\cite[Theorem 2.3]{DehyKeller}), rigid objects in~$K^{[-1,0]}(\proj \Lambda)$ are determined by their~$\b g$-vector.
@@
 For every walk~$\omega''$, let~$P(\omega'')$ be the object of~$K^{[-1,0]}(\proj \Lambda)$ corresponding to~$\omega''$.
-Then the walks~$\mu$ and~$\nu$ defined in the same statement yield an exchange conflation
+Then the walks~$\mu$ and~$\nu$ defined in the same statement yield a mutation conflation
  \[
@@
  \]
- By Proposition~\ref{prop::exchange conflations are unique}, we get that~$P(\mu)\oplus P(\nu)$ and~$P(\mu')\oplus P(\nu')$ are isomorphic.
-This implies that~$\{\mu,\nu\}$ and~$\{\mu',\nu'\}$ are the same sets.
-This determines~$\sigma$, and point (ii) of Proposition~\ref{prop:exchangeablePairsNKC} is proved.
+ By Proposition~\ref{prop::exchange conflations are unique}, we get that~$P(\mu)\oplus P(\nu)$ and~$P(\mu')\oplus P(\nu')$ are isomorphic, and that the mutation conflations either both have the form~$P(\omega) \infl P(\mu) \oplus P(\nu) \defl P(\omega')$ or both have the form~$P(\omega') \infl P(\mu) \oplus P(\nu) \defl P(\omega)$.
+Without loss of generality, assume that they have the first form.
+
+ In particular, the leftmost morphisms of both mutation conflations are both minimal~$\add(P(\mu) \oplus P(\nu))$-approximations of~$P(\omega)$.
+As such, they are isomorphic as morphisms.
+They determine common substrings of~$\omega$ and~$\mu$ and of~$\omega$ and~$\nu$, which in turn determine~$\sigma$.
+Point (ii) of Proposition~\ref{prop:exchangeablePairsNKC} is proved.
 \end{proof}
@@
  \]
+ \pg{To finish}
 \end{example}

### 2019-06-11 thirdPaper/draft/typeConeAssociahedra.tex
Added margin comments
Added more margin comments

@@
 \vincent{Here should come the proof of \cref{prop:exchangeablePairsNKC}.}
+\pg{It is done in Coro~\ref{coro::exchangeablePairsNKC}.}
 
@@
  \]
- Taking the quotient by the ideal generated by all morphisms factoring through direct sums of copies of the second of these objects, we get an extriangulated category whose Auslander--Reiten quiver is given by
+ Taking the quotient by the ideal generated by all morphisms factoring through direct sums of copies of the second of these objects, we get an extriangulated category~\cite{} whose Auslander--Reiten quiver is given as follows.
   \[
@@
  \]
- \pg{To finish}
+
+ \pg{Not sure why we wanted this example anymore.}
 \end{example}

### 2019-06-11 thirdPaper/draft/typeConeAssociahedra.tex
Added more margin comments

@@
 \begin{remark}
- As will be proven below [REF], this notation extends to an equivalence of categories from the category~$\tc$ of projective objects in~$\cat$ to the category~$\susp\tc$ of injective objects in~$\cat$.
+ As will be proven below [REF]\pg{REF}, this notation extends to an equivalence of categories from the category~$\tc$ of projective objects in~$\cat$ to the category~$\susp\tc$ of injective objects in~$\cat$.
 \end{remark}

### 2019-06-11 thirdPaper/draft/typeConeAssociahedra.tex
minor change

--- 2019-06-11 thirdPaper/draft/typeConeAssociahedra.tex
@@
 \begin{enumerate}[(i)]
-
 \item For any non-kissing facets~$F, F'$ of~$\NKC$ with~$F \ssm \{\omega\} = f' \ssm \{\omega'\}$, the distinguished substrings of~$\omega$ in~$F$ and of~$\omega'$ in~$F'$ coincide to a string~$\sigma$.
 Moreover, if we decompose~${\omega = \rho \sigma \tau}$ and~${\omega' = \rho' \sigma \tau'}$, then the facets~$F$ and~$F'$ both contain the walks~$\mu \eqdef \rho' \sigma \tau$ and~$\nu \eqdef \rho \sigma \tau'$.
-\item The substring~$\sigma$ and thus the walks~$\mu$ and~$\nu$ only depend on the exchangeable walks~$\omega$ and~$\omega'$, and not on the adjacent non-kissing facet~$F $ and~$F'$.
+\item The substring~$\sigma$ and thus the walks~$\mu$ and~$\nu$ actually depend on the exchangeable walks~$\omega$ and~$\omega'$, not on the adjacent non-kissing facet~$F $ and~$F'$.
 \item The linear dependence between the $\b{g}$-vectors of~$F \cup F'$ is given by
@@
 Points~(i), (iii) and~(iv) where shown in~\cite[Prop.~2.33, Thm.~4.17 \& Prop~4.16]{PaluPilaudPlamondon-nonkissing}.
-We postpone the proof of point~(ii) until Corollary~\ref{coro::exchangeablePairsNKC}.
+\vincent{Point~(ii) to prove.}
 \end{proof}
@@
 
-We derive from \cref{prop:extremalExchangeablePairsGA} and \cref{coro:extremalExchangeablePairsGA} all polytopal realizations of the nested fan, which we can explicitly express.
+We derive from \cref{prop:extremalExchangeablePairsGA} and \cref{coro:extremalExchangeablePairsGA} all polytopal realizations of the nested fan.
 
@@
 
-The extriangulated category~$K^{[-1,0]}(\proj \Lambda)$ is the setting in which we can finally prove point~(ii) of Proposition~\ref{prop:exchangeablePairsNKC}, using results of~\cite{DemonetIyamaJasso} on~$\b g$-vectors.
-% Proposition~\ref{prop::2kbproj-is-extriangulated} gives a setting in which to apply Theorem~\ref{}.
-Before doing so, we introduce the notion of mutation conflation for two-term silting objects.
+Proposition~\ref{prop::2kbproj-is-extriangulated} gives a setting in which to apply Theorem~\ref{}.
+Before stating our next theorem, we first recall some definitions
 
@@
 any morphism from~$X$ to an object in~$\add R$ factors through~$X\infl E$).
-\pg{To simplify, we should perhaps ask for the approximations to be minimal.}
 \end{definition}
-
-\begin{proposition}
-\label{prop::exchange conflations are unique}
- Let~$\Lambda$ be a finite-dimensional~$\field$-algebra, where~$\field$ is a field.  Let~$X$ and~$Y$ be objects of~$K^{[-1,0]}(\proj \Lambda)$.  
- \begin{enumerate}
-  \item If there is a mutation conflation (see Definition~\ref{defn::mutation conflation}) of the form~$X\infl E\defl Y$, then there can be no mutation conflation of the form~$Y\infl E'\defl X$.
-
-  \item Assume that~$X\infl E\defl Y$ and~$X\infl E'\defl Y$ are two mutation conflations.  
- Then~$E$ and~$E'$ are isomorphic. 
- \end{enumerate} 
-\end{proposition}
-\begin{proof}
- We first prove~(1).
-Assume that~$X\infl E\defl Y$ and~$Y\infl E'\defl X$ are two mutation conflations.
-Applying the functor~$\Hom{K^b}(\susp^{-1} Y, -)$ to the second sequence, we get an exact sequence of abelian groups
- \[
-  \Hom{K^b}(\susp^{-1} Y, E') \to \Hom{K^b}(\susp^{-1} Y, X) \Hom{K^b}(\susp^{-1} Y, \susp Y).
- \]
- By definition of a mutation conflation, we have that~$\Hom{K^b}(\susp^{-1} Y, E') = 0$.
-Moreover, since~$Y$ is concentrated in homological degrees~$-1$ and~$0$, we get that~$\Hom{K^b}(\susp^{-1} Y, \susp Y) = 0$.
-Therefore,~$\Hom{K^b}(\susp^{-1} Y, X) = 0$.
- However, since the conflation~$X\infl E\defl Y$ is not split, we have that~$\Hom{K^b}(\susp^{-1} Y, X) \neq 0$, a contradiction.  This proves~(1).
-
- \smallskip
-
- We now prove~(2).
-Let~$X\infl E\defl Y$ and~$X\infl E'\defl Y$ be two mutation conflations.
-By~\cite[Theorem 6.5]{DemonetIyamaJasso} (based on~\cite[Theorem 2.3]{DehyKeller}), rigid objects in~$K^{[-1,0]}(\proj \Lambda)$ are determined by their~$\b g$-vector.
-The datum of the~$\b g$-vector of an object of~$K^{[-1,0]}(\proj \Lambda)$ is equivalent to that of its class in the Grothendieck group~$K_0(K^{[-1,0]}(\proj \Lambda))$, where~$K^{[-1,0]}(\proj \Lambda)$ is viewed as an extriangulated category (see Proposition~\ref{prop::2kbproj-is-extriangulated}).
-In this Grothendieck group, we have that~$[E] = [E'] = [X]+[Y]$.
-Thus~$E$ and~$E'$ are isomorphic.
-\end{proof}
-
-\begin{corollary}\label{coro::exchangeablePairsNKC}
- Point~(ii) of Proposition~\ref{prop:exchangeablePairsNKC} holds.
-\end{corollary}
-\begin{proof}
- Let~$\omega$ and~$\omega'$ be in facets~$F$ and~$F'$ as in the statement of Proposition~\ref{prop:exchangeablePairsNKC}.
-For every walk~$\omega''$, let~$P(\omega'')$ be the object of~$K^{[-1,0]}(\proj \Lambda)$ corresponding to~$\omega''$.
-Then the walks~$\mu$ and~$\nu$ defined in the same statement yield a mutation conflation
- \[
-  P(\omega) \infl P(\mu) \oplus P(\nu) \defl P(\omega') \quad \textrm{or} \quad P(\omega') \infl P(\mu) \oplus P(\nu) \defl P(\omega).
- \]
- Assume that there are other facets~$F_0$ and~$F_0'$ also satisfying the hypotheses of Proposition~\ref{prop:exchangeablePairsNKC}.
-Then they give rise to walks~$\mu'$ and~$\nu'$ and an exchange conflation
- \[
-  P(\omega) \infl P(\mu') \oplus P(\nu') \defl P(\omega') \quad \textrm{or} \quad P(\omega') \infl P(\mu') \oplus P(\nu') \defl P(\omega).
- \]
- By Proposition~\ref{prop::exchange conflations are unique}, we get that~$P(\mu)\oplus P(\nu)$ and~$P(\mu')\oplus P(\nu')$ are isomorphic, and that the mutation conflations either both have the form~$P(\omega) \infl P(\mu) \oplus P(\nu) \defl P(\omega')$ or both have the form~$P(\omega') \infl P(\mu) \oplus P(\nu) \defl P(\omega)$.
-Without loss of generality, assume that they have the first form.
-
- In particular, the leftmost morphisms of both mutation conflations are both minimal~$\add(P(\mu) \oplus P(\nu))$-approximations of~$P(\omega)$.
-As such, they are isomorphic as morphisms.
-They determine common substrings of~$\omega$ and~$\mu$ and of~$\omega$ and~$\nu$, which in turn determine~$\sigma$.
-Point (ii) of Proposition~\ref{prop:exchangeablePairsNKC} is proved.
-\end{proof}
-
-We now come to the main result of this section.
 
@@
 
-\begin{example}[Preprojective algebra of type~$A_3$]\label{exam::preprojective silting objects}
+\begin{example}[Preprojective algebra of type~$A_3$]
  Let~$\Lambda$ be the preprojective algebra of type~$A_3$: it is the path algebra of the quiver
@@
 \subsubsection{A quotient of a Frobenius category}
-\begin{example}
- Consider the preprojective algebra of type~$A_3$, as in Example~\ref{exam::preprojective silting objects}.
-It is a self-injective algebra, so its module category is a Frobenius category.
-Its projective-injective objects are the modules
- \[
-  \begin{matrix} 1 \\ 2 \\ 3 \end{matrix} \quad , \quad  \begin{matrix} 2 \\ 13 \\ 2 \end{matrix} \quad \textrm{and} \quad \begin{matrix} 3 \\ 2 \\ 1 \end{matrix}.
- \]
- Taking the quotient by the ideal generated by all morphisms factoring through direct sums of copies of the second of these objects, we get an extriangulated category whose Auslander--Reiten quiver is given by
-  \[
-  \hspace*{-2cm}
- {\footnotesize
-  \begin{tikzcd}
-   \begin{matrix} 3 \end{matrix}\arrow[dr] && \begin{matrix} 2 \\ 1 \end{matrix}\arrow[r]\arrow[dr] & \begin{matrix} 3 \\ 2 \\ 1 \end{matrix}\arrow[r]& \begin{matrix} 3 \\ 2 \end{matrix}\arrow[dr] && \begin{matrix} 1 \end{matrix}\arrow[dr]&& \begin{matrix} 2 \\ 3 \end{matrix} \\
-    & \begin{matrix} 2\\ 13 \end{matrix}\arrow[ur]\arrow[dr] && \begin{matrix} 2 \end{matrix}\arrow[ur]\arrow[dr] && \begin{matrix} 13\\2 \end{matrix}\arrow[ur]\arrow[dr] && \begin{matrix} 2\\13 \end{matrix}\arrow[ur]\arrow[dr] &  \\
-   \begin{matrix} 1 \end{matrix}\arrow[ur] && \begin{matrix} 2\\3 \end{matrix}\arrow[ur]\arrow[r] & \begin{matrix} 1\\2\\3 \end{matrix}\arrow[r] & \begin{matrix} 1\\2 \end{matrix}\arrow[ur] && \begin{matrix} 3\\1 \end{matrix}\arrow[ur] && \begin{matrix} 2\\1 \end{matrix}
-  \end{tikzcd}
-  }
- \]
- \pg{To finish}
-\end{example}
 

### 2019-06-11 thirdPaper/draft/typeConeAssociahedra.tex
minor changes intro

@@
 In this paper, we revisit, extend and explore further this construction using a reversed approach.
-Given a complete simplicial fan~$\Fan$, we consider the space~$\typeCone(\Fan)$ of all its polytopal realizations, called type cone of~$\Fan$ in~\cite{McMullen-typeCone}.
-This type cone is known to be a polyhedral cone defined by a collection of inequalities corresponding to the linear dependences among the rays of~$\Fan$ contained in pairs of adjacent maximal cones of~$\Fan$ (see \cref{def:typeCone}).
-Our approach is based on an elementary but powerful observation: if the type cone~$\typeCone(\Fan)$ is a simplicial cone, then all polytopal realizations of~$\Fan$ can be described as sections of a high dimensional positive orthant with a collection of affine subspaces corresponding to the facets of~$\typeCone(\Fan)$ (see \cref{coro:simplicialTypeCone}).
+Given a complete simplicial fan~$\Fan$, we consider the space~$\typeCone(\Fan)$ of all its polytopal realizations.
+This space was called type cone of~$\Fan$ in~\cite{McMullen-typeCone} and deformation cone of~$\Fan$ in~\cite{Postnikov, PostnikovReinerWilliams}, who studied the case when~$\Fan$ is the braid arrangement leading to the rich theory of generalized permutahedra (recently extended to all finite Coxeter arrangements in~\cite{ACEP-DeformationsCoxeterPermutahedra}).
+The type cone is known to be a polyhedral cone defined by a collection of inequalities corresponding to the linear dependences among the rays of~$\Fan$ contained in pairs of adjacent maximal cones of~$\Fan$ (see \cref{def:typeCone}).
+Our approach is based on an elementary but powerful observation: for any fan~$\Fan$, all polytopal realizations of~$\Fan$ can be described as sections of a high dimensional positive orthant with a collection of affine subspaces parametrized by the type cone~$\typeCone(\Fan)$ (see \cref{prop:alternativePolytopalRealization}); if moreover the type cone~$\typeCone(\Fan)$ is a simplicial cone, it leads to a simple parametrization of all polytopal realizations of~$\Fan$ by a positive orthant (see \cref{coro:simplicialTypeCone}).
 To prove that the type cone~$\typeCone(\Fan)$ is simplicial, we just need to identify which pairs of adjacent maximal cones of~$\Fan$ correspond to the facets of~$\typeCone(\Fan)$ and to show that the corresponding linear dependences among their rays positively span the linear dependence among the rays of any pair of adjacent maximal cones of~$\Fan$.
@@
 
-Define $\alpha(\tube,\tube') \eqdef \set{\tube[u] \in \tubes}{\tube \symdif \tube' \subseteq \tube[u] \subseteq \tube \cup \tube'}$, where $\symdif$ denotes the symmetric difference, and define $\b{x} \in \R^{\tubes}$ be such that
-\[
-\b{x}_{\tube[s]} = -|\bigset{\tube[u] \in \tubes \ssm \alpha(\tube, \tube')}{\tube[u] \subseteq \tube[s]}|
+Define $\alpha(\tube,\tube') \eqdef \set{\tube[r] \in \tubes}{\tube \symdif \tube' \subseteq \tube[r] \subseteq \tube \cup \tube'}$, where $\symdif$ denotes the symmetric difference, and define $\b{x} \in \R^{\tubes}$ be such that
+\[
+\b{x}_{\tube[s]} = -|\bigset{\tube[r] \in \tubes \ssm \alpha(\tube, \tube')}{\tube[r] \subseteq \tube[s]}|
 \]
@@
 \[
-\b{z}_{\tube[s]} = -|\bigset{\tube[u] \in \alpha(\tube, \tube')}{\tube[u] \subseteq \tube[s]}|,
+\b{z}_{\tube[s]} = -|\bigset{\tube[r] \in \alpha(\tube, \tube')}{\tube[r] \subseteq \tube[s]}|,
 \]

### 2019-06-11 thirdPaper/draft/typeConeAssociahedra.tex
minor edits

--- 2019-06-11 thirdPaper/draft/typeConeAssociahedra.tex
@@
 It is a class of polytopal realizations of the classical associahedron obtained as sections of a high-dimensional positive orthant with well-chosen affine subspaces.
-This construction provides a large degree of freedom in the choice of the parameters defining these affine subspaces and produces all polytopes whose normal fan is affinely equivalent to that of J.-L.~Loday's associahedron~\cite{Loday} (see \cref{subsec:typeConeAsso}).
+This construction provides a large degree of freedom in the choice of the parameters defining these affine subspaces, and actually produces all polytopes whose normal fan is affinely equivalent to that of J.-L.~Loday's associahedron~\cite{Loday} (see \cref{subsec:typeConeAsso}).
 These realizations were then extended by V.~Bazier-Matte, G.~Douville, K.~Mousavand, H.~Thomas and E.~Y\i ld\i r\i m~\cite{BazierMatteDouvilleMousavandThomasYildirim} in the context of finite type cluster algebras using tools from representation theory of quivers.
@@
 These complexes encompass two families of simplicial complexes studied independently in the literature: on the one hand the grid associahedra introduced by T.~K.~Petersen, P.~Pylyavskyy and D.~Speyer in~\cite{PetersenPylyavskyySpeyer} for a staircase shape, studied by F.~Santos, C.~Stump and V.~Welker~\cite{SantosStumpWelker} for rectangular shapes, and extended by T.~McConville in~\cite{McConville} for arbitrary grid shapes; and on the other hand the Stokes polytopes and accordion associahedra studied by Y.~Baryshnikov~\cite{Baryshnikov}, F.~Chapoton~\cite{Chapoton-quadrangulations}, A.~Garver and T.~McConville~\cite{GarverMcConville} and T.~Manneville and V.~Pilaud~\cite{MannevillePilaud-accordion}.
+The latter, sometimes called Accordiohedra, have also appeared in the mathematical physics litterature concerning scattering amplitudes~\cite{BLR-StokesPolytopes, Raman-PositiveGeometry}, with realizations inspired by those in~\cite{ArkaniHamedBaiHeYan}.
 It was shown in~\cite{PaluPilaudPlamondon-nonkissing, BrustleDouvilleMousavandThomasYildirim} that the non-kissing complex of a gentle bound quiver provides a combinatorial model for the support $\tau$-tilting complex~\cite{AdachiIyamaReiten} of the associated gentle algebra.
@@
 It is easily seen that~$\mathbb{E}_\tc$ is an additive subfunctor of~$\mathbb{E}$.
-Consider $(\ec,\mathbb{E}_\tc,\mathfrak{s}_\tc)$ endowed with the resctriction of the additive realisation~$\mathfrak{s}$.
+Consider $(\ec,\mathbb{E}_\tc,\mathfrak{s}_\tc)$ endowed with the resctriction of the additive realization~$\mathfrak{s}$.
 Since the deflations in~$(\ec,\mathbb{E}_\tc,\mathfrak{s}_\tc)$ are precisely the deflations in~$(\ec,\mathbb{E},\mathfrak{s})$ that are~$\tc$-epic, they are closed under composition.

### 2019-06-11 thirdPaper/draft/typeConeAssociahedra.tex
minor changes intro

--- 2019-06-11 thirdPaper/draft/typeConeAssociahedra.tex
@@
 The type cone is known to be a polyhedral cone defined by a collection of inequalities corresponding to the linear dependences among the rays of~$\Fan$ contained in pairs of adjacent maximal cones of~$\Fan$ (see \cref{def:typeCone}).
-Our approach is based on an elementary but powerful observation: for any fan~$\Fan$, all polytopal realizations of~$\Fan$ can be described as sections of a high dimensional positive orthant with a collection of affine subspaces parametrized by the type cone~$\typeCone(\Fan)$ (see \cref{prop:alternativePolytopalRealization}); if moreover the type cone~$\typeCone(\Fan)$ is a simplicial cone, it leads to a simple parametrization of all polytopal realizations of~$\Fan$ by a positive orthant (see \cref{coro:simplicialTypeCone}).
+Our approach is based on an elementary but powerful observation: for any fan~$\Fan$, all polytopal realizations of~$\Fan$ can be described as sections of a high dimensional positive orthant with a collection of affine subspaces parametrized by the type cone~$\typeCone(\Fan)$ (see \cref{prop:alternativePolytopalRealization}); if moreover the type cone~$\typeCone(\Fan)$ is a simplicial cone, it leads to a simple parametrization of all polytopal realizations of~$\Fan$ by a positive orthant corresponding to the facets of the type cone~$\typeCone(\Fan)$ (see \cref{coro:simplicialTypeCone}).
 To prove that the type cone~$\typeCone(\Fan)$ is simplicial, we just need to identify which pairs of adjacent maximal cones of~$\Fan$ correspond to the facets of~$\typeCone(\Fan)$ and to show that the corresponding linear dependences among their rays positively span the linear dependence among the rays of any pair of adjacent maximal cones of~$\Fan$.
-When applied to the $\b{g}$-vector fans of cluster algebras (see \cref{subsec:typeConeCA}), this reversed approach enables us to efficiently revisit and extend the construction of~\cite{BazierMatteDouvilleMousavandThomasYildirim}.
-This new perspective has several advantages, as our proof uniformly applies to:
+When applied to the $\b{g}$-vector fans of cluster algebras (see \cref{subsec:typeConeCA}), this reversed approach yields all polytopal realizations of the $\b{g}$-vector fans and thus efficiently revisits and extends the construction of~\cite{BazierMatteDouvilleMousavandThomasYildirim}.
+This new perspective has several advantages, as our proof uniformly~applies~to:
 
@@
 In the present paper, we explore specifically two families of such generalizations.
+\enlargethispage{.2cm}
 
@@
 We present both a purely combinatorial proof (see \cref{subsec:typeConeCA}) and a purely algebraic proof for (non-necessarily gentle) brick algebras making use of extriangulated categories (see \cref{sec:extricats}).
-Our algebraic proof is based on an analogue of a result of M. Auslander~\cite{Auslander1984} relating to minimal generators of Grothendieck groups.
+Our algebraic proof is based on an analogue of a result of M.
+Auslander~\cite{Auslander1984} relating to minimal generators of Grothendieck groups.
 Along the way, we need to generalize, for extriangulated categories, several results from cluster-tilting theory on indices~\cite{DehyKeller} and on abelian quotients~\cite{BuanMarshReiten, KellerReiten} that were known for triangulated categories.

### 2019-06-11 thirdPaper/draft/typeConeAssociahedra.tex

@@
 
-The associahedron appears as a fundamental structure in several mathematical theories, such as moduli spaces and topology~\cite{Stasheff, Keller-AinfinityAlgebras}, operads and rewriting theory~\cite{}, combinatorial Hopf algebras~\cite{LodayRonco, ChatelPilaud, Pilaud-brickAlgebra}, diagonal harmonics~\cite{}, mathematical physics~\cite{ArkaniHamedBaiHeYan}, etc.
+The associahedron appears as a fundamental structure in several mathematical theories, such as moduli spaces and topology~\cite{Stasheff, Keller-AinfinityAlgebras}, operads and rewriting theory~\cite{}, combinatorial Hopf algebras~\cite{LodayRonco, ChatelPilaud, Pilaud-brickAlgebra}, diagonal harmonics~\cite{}, mathematical physics~\cite{ArkaniHamedBaiHeYan, BLR-StokesPolytopes, Raman-PositiveGeometry}, etc.
 Another striking illustration of the ubiquity of the associahedron lies in the theory of cluster algebras introduced by S.~Fomin and A.~Zelevinsky in~\cite{FominZelevinsky-ClusterAlgebrasI} with motivation coming from total positivity and canonical bases.
@@
 In the present paper, we explore specifically two families of such generalizations.
-\enlargethispage{.2cm}
-
-\smallskip
+
 \begin{itemize}
@@
 These complexes encompass two families of simplicial complexes studied independently in the literature: on the one hand the grid associahedra introduced by T.~K.~Petersen, P.~Pylyavskyy and D.~Speyer in~\cite{PetersenPylyavskyySpeyer} for a staircase shape, studied by F.~Santos, C.~Stump and V.~Welker~\cite{SantosStumpWelker} for rectangular shapes, and extended by T.~McConville in~\cite{McConville} for arbitrary grid shapes; and on the other hand the Stokes polytopes and accordion associahedra studied by Y.~Baryshnikov~\cite{Baryshnikov}, F.~Chapoton~\cite{Chapoton-quadrangulations}, A.~Garver and T.~McConville~\cite{GarverMcConville} and T.~Manneville and V.~Pilaud~\cite{MannevillePilaud-accordion}.
+The latter, sometimes called accordiohedra, have also appeared in the mathematical physics litterature concerning scattering amplitudes~\cite{BLR-StokesPolytopes, Raman-PositiveGeometry}, with realizations inspired by those in~\cite{ArkaniHamedBaiHeYan}.
 It was shown in~\cite{PaluPilaudPlamondon-nonkissing, BrustleDouvilleMousavandThomasYildirim} that the non-kissing complex of a gentle bound quiver provides a combinatorial model for the support $\tau$-tilting complex~\cite{AdachiIyamaReiten} of the associated gentle algebra.
@@
 We present both a purely combinatorial proof (see \cref{subsec:typeConeCA}) and a purely algebraic proof for (non-necessarily gentle) brick algebras making use of extriangulated categories (see \cref{sec:extricats}).
-Our algebraic proof is based on an analogue of a result of M.
-Auslander~\cite{Auslander1984} relating to minimal generators of Grothendieck groups.
+Our algebraic proof is based on an analogue of a result of M. Auslander~\cite{Auslander1984} relating to minimal generators of Grothendieck groups.
 Along the way, we need to generalize, for extriangulated categories, several results from cluster-tilting theory on indices~\cite{DehyKeller} and on abelian quotients~\cite{BuanMarshReiten, KellerReiten} that were known for triangulated categories.
@@
 \smallskip
+\enlargethispage{.2cm}
 \item \textbf{Graph associahedra} were defined by M.~Carr and S.~Devadoss~\cite{CarrDevadoss} in connection to C.~De Concini and C.~Procesi's wonderful arrangements~\cite{DeConciniProcesi}.

### 2019-06-11 thirdPaper/draft/typeConeAssociahedra.tex
minor changes intro

@@
 This is clearly the case when the type cone is simplicial as illustrated by the results of this paper: we naturally obtained all polytopal realizations of the $\b{g}$-vector fans of cluster algebras from cyclic seeds and of gentle algebras whose polytopality was only established very recently~\cite{HohlwegPilaudStella, PaluPilaudPlamondon-nonkissing}.
-We believe that this gives reasonable hope that the polytopality of further fans could in the future be established using our type cone approach.
+Even when the type cone is not simplicial, describing the type cone sometimes leads to relevant explicit realizations of the fan, as we illustrate on graph associahedra (see \cref{exm:constructionsGA}).
+We believe that this approach gives reasonable hope that the polytopality of further fans could in the future be established using our type cone approach.
 Tempting candidates are quotientopes for hyperplane arrangements beyond type~$A$, which are particularly interesting since the coarsenings of a fan essentially correspond to the faces of its type cone (see \cref{subsec:facesTypeCone}).

### 2019-06-11 thirdPaper/draft/typeConeAssociahedra.tex
minor changes intro

@@
 
+\smallskip
 \begin{itemize}
@@
 As illustrated in~\cref{fig:specialGraphAssociahedra}, the graph associahedra of certain special families of graphs coincide with well-known families of polytopes: complete graph associahedra are permutahedra, path associahedra are classical associahedra, cycle associahedra are cyclohedra, and star associahedra are stellohedra.
-The graph associahedra were extended to the \defn{nestohedra}, which are simple polytopes realizing the nested complex of arbitrary building sets~\cite{Postnikov, FeichtnerSturmfels}.
+The graph associahedra were extended to the nestohedra, which are simple polytopes realizing the nested complex of arbitrary building sets~\cite{Postnikov, FeichtnerSturmfels}.
 Graph associahedra and nestohedra have been geometrically realized in different ways: by successive truncations of faces of the standard simplex~\cite{CarrDevadoss}, as Minkowski sums of faces of the standard simplex~\cite{Postnikov, FeichtnerSturmfels}, or from their normal fans by exhibiting explicit inequality descriptions~\cite{Devadoss, Zelevinsky}.
@@
 It would be interesting to get such volume formulas for polytopal realizations of $\b{g}$-vector fans of cluster algebras and gentle algebras, and combinatorial interpretations for their coefficients.
+
+\smallskip
+\item The associahedra constructed in~\cite{ArkaniHamedBaiHeYan, BazierMatteDouvilleMousavandThomasYildirim} and the present paper describe all polytopal realizations of the $\b{g}$-vector fan.
+This motivates the following question: Is it possible to similarly understand the complete realization space of the cluster complex, including all realizations not having the~$\b{g}$-vector fan as their normal fan?
 \end{itemize}
@@
 Some of these questions are explicitly indicated throughout the paper.
-To conclude, we observe that the associahedra constructed in~\cite{ArkaniHamedBaiHeYan, BazierMatteDouvilleMousavandThomasYildirim} and the present paper describe all polytopal realizations of the $\b{g}$-vector fan.
-This motivates the following question: Is it possible to similarly understand the complete realization space of the cluster complex, including all realizations not having the~$\b{g}$-vector fan as their normal fan?
+
+\medskip
+To conclude, it is our hope that the present paper will participate to the interactions between combinatorial geometry, representation theory, and mathematical physics in particular through further developments of the amplituhedron program open in~\cite{ArkaniHamedBaiHeYan}.
 

### 2019-06-11 thirdPaper/draft/typeConeAssociahedra.tex
bib

@@
 
-The associahedron appears as a fundamental structure in several mathematical theories, such as moduli spaces and topology~\cite{Stasheff, Keller-AinfinityAlgebras}, operads and rewriting theory~\cite{}, combinatorial Hopf algebras~\cite{LodayRonco, ChatelPilaud, Pilaud-brickAlgebra}, diagonal harmonics~\cite{}, mathematical physics~\cite{ArkaniHamedBaiHeYan, BLR-StokesPolytopes, Raman-PositiveGeometry}, etc.
+The associahedron appears as a fundamental structure in several mathematical theories, such as moduli spaces and topology~\cite{Stasheff, Keller-AinfinityAlgebras}, operads and rewriting theory~\cite{}, combinatorial Hopf algebras~\cite{LodayRonco, ChatelPilaud, Pilaud-brickAlgebra}, diagonal harmonics~\cite{}, mathematical physics~\cite{ArkaniHamedBaiHeYan, BanerjeeLaddhaRaman-StokesPolytopes, Raman-PositiveGeometry}, etc.
 Another striking illustration of the ubiquity of the associahedron lies in the theory of cluster algebras introduced by S.~Fomin and A.~Zelevinsky in~\cite{FominZelevinsky-ClusterAlgebrasI} with motivation coming from total positivity and canonical bases.
@@
 These complexes encompass two families of simplicial complexes studied independently in the literature: on the one hand the grid associahedra introduced by T.~K.~Petersen, P.~Pylyavskyy and D.~Speyer in~\cite{PetersenPylyavskyySpeyer} for a staircase shape, studied by F.~Santos, C.~Stump and V.~Welker~\cite{SantosStumpWelker} for rectangular shapes, and extended by T.~McConville in~\cite{McConville} for arbitrary grid shapes; and on the other hand the Stokes polytopes and accordion associahedra studied by Y.~Baryshnikov~\cite{Baryshnikov}, F.~Chapoton~\cite{Chapoton-quadrangulations}, A.~Garver and T.~McConville~\cite{GarverMcConville} and T.~Manneville and V.~Pilaud~\cite{MannevillePilaud-accordion}.
-The latter, sometimes called accordiohedra, have also appeared in the mathematical physics litterature concerning scattering amplitudes~\cite{BLR-StokesPolytopes, Raman-PositiveGeometry}, with realizations inspired by those in~\cite{ArkaniHamedBaiHeYan}.
+The latter, sometimes called accordiohedra, have also appeared in the mathematical physics litterature concerning scattering amplitudes~\cite{BanerjeeLaddhaRaman-StokesPolytopes, Raman-PositiveGeometry}, with realizations inspired by those in~\cite{ArkaniHamedBaiHeYan}.
 It was shown in~\cite{PaluPilaudPlamondon-nonkissing, BrustleDouvilleMousavandThomasYildirim} that the non-kissing complex of a gentle bound quiver provides a combinatorial model for the support $\tau$-tilting complex~\cite{AdachiIyamaReiten} of the associated gentle algebra.

### 2019-06-11 thirdPaper/draft/typeConeAssociahedra.tex
minor change

@@
 \author{Arnau Padrol}
-\address[Arnau Padrol]{IMJ - Paris Rive Gauche, Sorbonne Universit\'e}
+\address[Arnau Padrol]{Institut de Mathématiques de Jussieu - Paris Rive Gauche, Sorbonne Universit\'e, Paris}
 \email{arnau.padrol@imj-prg.fr.}
@@
 \medskip
-To conclude, it is our hope that the present paper will participate to the interactions between combinatorial geometry, representation theory, and mathematical physics in particular through further developments of the amplituhedron program open in~\cite{ArkaniHamedBaiHeYan}.
+To conclude, it is our hope that the present paper will participate to the interactions between combinatorial geometry, representation theory, and mathematical physics; in particular through further developments of the amplituhedron program, which was open in~\cite{ArkaniHamedTrnka2014Amplituhedron} and has flourished during the last years~\cite{GrassmannianGeometryScatteringAmplitudes}.
+The kinetic associahedron from~\cite{ArkaniHamedBaiHeYan} is one of the last ``positive geometries''~\cite{ArkaniHamedBaiLam2017-PositiveGeometries} that has emerged in the study of scattering amplitudes.
+% \cite{ArkaniHamedBaiHeYan}.7
 

### 2019-06-11 thirdPaper/draft/typeConeAssociahedra.tex
changes biblio + poster

--- 2019-06-11 thirdPaper/draft/typeConeAssociahedra.tex
@@
 \medskip
-To conclude, it is our hope that the present paper will participate to the interactions between combinatorial geometry, representation theory, and mathematical physics in particular through further developments of the amplituhedron program open in~\cite{ArkaniHamedBaiHeYan}.
+To conclude, it is our hope that the present paper will participate to the interactions between combinatorial geometry, representation theory, and mathematical physics; in particular through further developments of the amplituhedron program, which was open in~\cite{ArkaniHamedTrnka-Amplituhedron} and has flourished during the last years~\cite{ArkaniHamedBourjailyCachazoGoncharovPostnikovTrnka-GrassmannianGeometryScatteringAmplitudes}.
+The kinetic associahedron from~\cite{ArkaniHamedBaiHeYan} is one of the last ``positive geometries''~\cite{ArkaniHamedBaiLam-PositiveGeometries} that has emerged in the study of scattering amplitudes.
 

### 2019-06-12 thirdPaper/draft/typeConeAssociahedra.tex
typo

@@
 The linear dependences of \cref{lem:linearDependencegvectorsCA} provide a redundant description of the type cone of the cluster fan~$\gvectorFan[\B_\circ]$.
-We denote by~$\b{n}(\B_\circ, x, x')$ the normal vector of the inequality of the type cone corresponding to two exchangeable cluster variable~$x$ to~$x'$ (it is well defined by \cref{prop:uniqueExchangePropertyCA}).
+We denote by~$\b{n}(\B_\circ, x, x')$ the normal vector of the inequality of the type cone corresponding to two exchangeable cluster variables~$x$ to~$x'$ (it is well defined by \cref{prop:uniqueExchangePropertyCA}).
 In other words, depending on which of the two linear dependences of \cref{lem:linearDependencegvectorsCA} holds, we have

### 2019-06-12 thirdPaper/draft/typeConeAssociahedra.tex
minor changes

--- 2019-06-11 thirdPaper/draft/typeConeAssociahedra.tex
@@
 
-For categories with a cluster-tilting objects, the~$2$-Calabi--Yau condition implies other duality results which we shall need.
+For categories with a cluster-tilting object, the~$2$-Calabi--Yau condition implies other duality results which we shall need.
 
@@
 
-  \item Let~$\Kg(\cat)$ \yann{I do not like this notation anymore: $\Kg(\cat)$ depends on the choice of a CTO $T$.
+  \item Let~$K_0(\cat ; T)$ \yann{I do not like this notation anymore: $K_0(\cat ; T)$ depends on the choice of a CTO $T$.
 How about $K_0^T(\cat)$, $K_0^{(\susp T)}(\cat)$, $K_0(\cat;T)$, $\Kg(\cat;T)$ or $K_0(\cat;(\susp T))$?}\pg{Good point.
@@
   \]
-  with~$h\in (\susp T)$.  Denote by~$\b g:\Ksp(\cat) \to \Kg(\cat)$ the canonical projection.
+  with~$h\in (\susp T)$.  Denote by~$\b g:\Ksp(\cat) \to K_0(\cat ; T)$ the canonical projection.
  \end{enumerate}
@@
 In particular,~$\Ksp(\cat)$ is isomorphic to a free abelian group over the set~$\ind(\cat)$.
-The choice of the notation for~$\Kg(\cat)$ is motivated by Section~\ref{sect::applications-g-vectors}, where we study relations between~$\b g$-vectors.
+Considering the modified group~$K_0(\cat ; T)$ instead of the usual Grothendieck group is motivated by Section~\ref{sect::applications-g-vectors}, where we study relations between~$\b g$-vectors.
 
@@
  \]
- generates the kernel of~$\b g:\Ksp(\cat) \to \Kg(\cat)$. 
+ generates the kernel of~$\b g:\Ksp(\cat) \to K_0(\cat ; T)$. 
  In this case, the set~$L$ is a basis of the kernel of~$\b g$, and for any $x\in \ker(\b g)$, we have that
@@
  \[
-  T_1^X \to T^0_X \to X \to \susp T_1^X
+  T_1^X \to T_0^X \to X \to \susp T_1^X
  \]
@@
 
-The notion of index is very close to the definition of the map~$\b g:\Ksp(\cat)\to \Kg(\cat)$ of Definition~\ref{defi::grothendieck-group}.  The link is given by the following result.
+The notion of index is very close to the definition of the map~$\b g:\Ksp(\cat)\to K_0(\cat ; T)$ of Definition~\ref{defi::grothendieck-group}.  The link is given by the following result.
 
@@
 \label{coro::grothendieck-g-vectors}
- There is an isomorphism~$\phi:\Kg(\cat) \to \Ksp(\add(T))$ such that~$\ind_T = \phi\circ \b g$.  In particular,~$\Kg(\cat)$ is a free abelian group generated by the~$[T_i]$.
+ There is an isomorphism~$\phi:K_0(\cat ; T) \to \Ksp(\add(T))$ such that~$\ind_T = \phi\circ \b g$.  In particular,~$K_0(\cat ; T)$ is a free abelian group generated by the~$[T_i]$.
 \end{corollary}
@@
 \begin{proof}
- We will only proof that (1) is equivalent to (2); the proof that (1) is equivalent to (3) is similar.
+ We will only proove that (1) is equivalent to (2); the proof that (1) is equivalent to (3) is similar.
 
@@
 \begin{proposition}
- Assume that~$\ind(\cat)$ is finite.  Then the set~$\set{[\ell_A]}{A\in \ind(\cat) \ssm \add(\susp T)}$ is a basis of the kernel of~$\b g$.  Moreover, for any~$x\in \ker \b g$, we have that
+ Assume that~$\ind(\cat)$ is finite.
+Then the set~$\set{[\ell_A]}{A\in \ind(\cat) \ssm \add(\susp T)}$ is a basis of the kernel of~$\b g : \Ksp(\cat) \to K_0(\cat ; T)$.
+Moreover, for any~$x\in \ker \b g$, we have that
  \[
@@
   \item[(i)] \emph{(}\cite[Prop.~3.2]{BuanMarshReinekeReitenTodorov} and~\cite[]{???} \emph{)} For any~$X,Y\in \ind(\cat)$, $\CC(X)$ and~$\CC(Y)$ are compatible if and only if~$\cat(X, \susp Y) = 0$.
-  \item[(ii)] \emph{(}\cite[Prop.~4.3]{FuKeller} and \emph{)} For any~$X\in \ind(\cat)$, the~$\b g$-vector of~$\CC(X)$ is~$\b g([X])$, where we identify~$\Z^n$ and~$\Kg(\cat)$ via the isomorphism sending~$(a_1, \ldots, a_n)$ to~$\sum_{i=1}^n a_i [T_i]$.
+  \item[(ii)] \emph{(}\cite[Prop.~4.3]{FuKeller} and \emph{)} For any~$X\in \ind(\cat)$, the~$\b g$-vector of~$\CC(X)$ is~$\b g([X])$, where we identify~$\Z^n$ and~$K_0(\cat ; T)$ via the isomorphism sending~$(a_1, \ldots, a_n)$ to~$\sum_{i=1}^n a_i [T_i]$.
   \item[(iii)] \emph{(}\cite[Thm.~7.5]{BuanMarshReinekeReitenTodorov} and~\cite[]{???—} \emph{)} For any~$X,Y\in \ind(\cat)$, $\CC(X)$ and~$\CC(Y)$ are exchangeable if and only if~$\dim_{\field_X}\cat(X, \susp Y) = \dim_{\field_Y}\cat(X, \susp Y) = 1$.
@@
 Let~$\mathcal{A}$ be any cluster algebra admitting a categorification by a Hom-finite,~$2$-Calabi--Yau, Krull--Schmidt, triangulated category with cluster-tilting objects.
-Let~$x\in\cluster$ be a cluster cariable in a given cluster and let~$x'\in \cluster'$ be obtained by mutating~$\cluster$ at~$x$.
+Let~$x\in\cluster$ be a cluster variable in a given cluster and let~$x'\in \cluster'$ be obtained by mutating~$\cluster$ at~$x$.
 Then precisely one of the two mutations~$\mu_x(\cluster)$ and~$\mu_{x'}(\cluster')$ is a positive mutation.
@@
 \begin{proof}
-Let~$\cat$ be a cluster category of Dynkin type~$A,B,C,D,E,F$ or~$G$, and let $T\in\cat$ be some basic cluster-tilting object categorifying the given initial exchange matrix$\B_\circ$. 
+Let~$\cat$ be a cluster category of Dynkin type~$A,B,C,D,E,F$ or~$G$, and let $T\in\cat$ be some basic cluster-tilting object categorifying the given initial exchange matrix~$\B_\circ$. 
 By Lemma~\ref{lemma:positive mutation triangles}, we may assume that the mutation under consideration is a positive mutation.
-In view of Theorem~\ref{thm::categorification} (ii) and (iv) it is enough to show that the relation in~$\Kg(\cat)$ given by any triangle~$X\to E\to Y\xrightarrow{h} \susp X$ with~$h\in(\susp T)$ is a positive linear combination of relations coming from Auslander--Reiten triangles with third term not in~$\add(\susp T)$.
+In view of Theorem~\ref{thm::categorification} (ii) and (iv) it is enough to show that the relation in~$K_0(\cat ; T)$ given by any triangle~$X\to E\to Y\xrightarrow{h} \susp X$ with~$h\in(\susp T)$ is a positive linear combination of relations coming from Auslander--Reiten triangles with third term not in~$\add(\susp T)$.
 This categorified statement is precisely Corollary~\ref{corollary::meshes positively generate cluster cats}.
@@
 \label{lemma::uerp categorified}
-Let~$\cat$ be a cluster category of Dynkin type~$A,B,C,D,E,F$ or~$G$, and let~$X,Y\in \cat$ be such~$\CC(Y)$ is obtained by performing a positive mutation at~$\CC(X)$ in any cluster containing it.
+Let~$\cat$ be a cluster category of Dynkin type~$A,B,C,D,E,F$ or~$G$, and let~$X,Y\in \cat$ be such~$\CC(Y)$ is obtained by performing a positive mutation at~$\CC(X)$ in some cluster containing it.
 Then the linear dependence between the~$\b{g}$-vectors given by the positive mutation is
@@
 Let~$T\in\cat$ be a basic cluster tilting object such that~$\CC(T)$ is the initial cluster.
-By LEmma~\ref{lemma:positive mutation triangles}, the morphism~$h$ belongs to the ideal~$(\susp T)$.
-Therefore, the triangle~$X\to \bigoplus_i E_i \to Y \xrightarrow{h} \susp X$ induces the relation~$[X]+[Y]=\sum_i [E_i]$ in~$\Kg(\cat)$.
+By Lemma~\ref{lemma:positive mutation triangles}, the morphism~$h$ belongs to the ideal~$(\susp T)$.
+Therefore, the triangle~$X\to \bigoplus_i E_i \to Y \xrightarrow{h} \susp X$ induces the relation~$[X]+[Y]=\sum_i [E_i]$ in~$K_0(\cat ; T)$.
 Theorem~\ref{thm::categorification} (ii) gives the equality~$\b{g}_{\CC(X)} + \b{g}_{\CC(Y)} = \sum_i\b{g}_{\CC(E_i)}$, where the~$\b{g}$-vectors are computed with respect to the initial seed~$\CC(T)$.
@@
 So as to be able to state the main theorem of Section~\ref{sec:extricats}, we need a few results on extriangulated categories.
-However, all proofs are postpone to Section~\ref{sect::proofs extricats}.
+However, all proofs are postponed to Section~\ref{sect::proofs extricats}.
 
@@
 \begin{remark}
- As will be proven below [REF]\pg{REF}, this notation extends to an equivalence of categories from the category~$\tc$ of projective objects in~$\cat$ to the category~$\susp\tc$ of injective objects in~$\cat$.
+ As will be proven below (Remark~\ref{remark::equivalence Sigma} and Corollary~\ref{corollary::Sigma T injectives}), this notation extends to an equivalence of categories from the category~$\tc$ of projective objects in~$\cat$ to the category~$\susp\tc$ of injective objects in~$\cat$.
 \end{remark}
@@
 
-\begin{lemma}
+\begin{lemma}\label{lemma::finitely presented}
 For any~$X\in\cat$, the functor~$FX$ is finitely presented.
@@
 
-\begin{proposition}\emph{(}\cite[Props.~3.3~\&~3.11]{NakaokaPalu}\emph{)}
+\begin{proposition}\label{proposition::extricat long exact sequences}\emph{(}\cite[Props.~3.3~\&~3.11]{NakaokaPalu}\emph{)}
 Assume that $(\cat,\mathbb{E},\mathfrak{s})$ is an extriangulated category, and let $X\xrightarrow{x}Y\xrightarrow{y}Z\overset{\delta}{\dashrightarrow}$ be an extriangle.
@@
 
-(c) and (d) are obtained from the long exact sequences associated with the extriangle~$T\infl 0\defl \susp T\dashrightarrow$.
+(c) and (d) are obtained from the exact sequences of Proposition~\ref{proposition::extricat long exact sequences} associated with the extriangle~$T\infl 0\defl \susp T\dashrightarrow$.
 
@@
 For any~$T\in\tc$, fix an extriangle~$T\infl 0\defl\susp T\overset{\eps_T}{\dashrightarrow}$.
-As noticed in Lemma~\ref{lemma::shifts of extriangles}, for any morphism~$T\overset{f}{\to}T'$ in~$\tc$, there is a unique morphism~$\susp f\in\cat(\susp T,\susp T')$ such that~$f_\ast\eps_T=(\susp f)^\ast\eps_{T'}$, as illustrated below:
+As noticed in Lemma~\ref{lemma::shifts of extriangles}, for any morphism~$T\overset{f}{\to}T'$ in~$\tc$, there is a unique morphism~$\susp f\in\cat(\susp T,\susp T')$ such that~$f_\ast\eps_T=(\susp f)^\ast\eps_{T'}$ (i.e.
+such that~$(f,\susp f)$ is a morphism from~$\eps_T$ to~$\eps_{T'}$), as illustrated below:
 \[
@@
 (21,7)*+{\susp T}="6";
-(32,7)*+{}="8";
+(35,7)*+{}="8";
 %
@@
 (21,-7)*+{\susp T}="16";
-(32,-7)*+{}="18";
+(35,-7)*+{}="18";
 %
@@
 \end{remark}
+
+\begin{proof}[Proof of Lemma~\ref{lemma::finitely presented}]
+ Applying the functor~$F$ to the extriangle~$T_1^X\infl T_0^X\defl X\overset{\delta_X}{\dashrightarrow}$ induces an exact sequence~$FT_1^X \to FT_0^X \to FX \to \mathbb{E}(T,T_1^X)=0$, showing that~$FX$ is finitely presented.
+\end{proof}
 
@@
 
-\begin{corollary}
+\begin{corollary}\label{corollary::Sigma T injectives}
 The objects in~$\susp\tc$ are precisely the injective objects in~$\cat$.
@@
 Let~$\Lambda$ be a finite-dimensional algebra over a field~$\field$.
-Then the homotopy category~$K^b(\proj \Lambda)$ is a triangulated category, and we consider its full subcategory~$K^{[-1,0]}(\proj \Lambda)$ of complexes concentrated in degrees~$-1$ and~$0$.
+Then the homotopy category~$K^b(\proj \Lambda)$ is a triangulated category, and we consider its full subcategory~$K^{[-1,0]}(\proj \Lambda)$ of complexes concentrated in degrees~$-1$ and~$0$ (with cohomological conventions).
 
@@
 \begin{definition}\label{defn::mutation conflation}
-A conflation $X\infl E\defl Y$ of~$K^{[-1,0]}(\proj \Lambda)$ is called a \defn{mutation conflation} if there are basic, two-term, silting objects $X\oplus R$, $Y\oplus R$ such that the inflation $X\infl E$ is a left ($\add R$)-approximation (i.e.
+A conflation $X\infl E\defl Y$ of~$K^{[-1,0]}(\proj \Lambda)$ is called a \defn{mutation conflation} if there are basic, two-term, silting objects $X\oplus R$, $Y\oplus R$, with~$X$ and~$Y$ indecomposable, such that the inflation $X\infl E$ is a left ($\add R$)-approximation (i.e.
 any morphism from~$X$ to an object in~$\add R$ factors through~$X\infl E$).
-\pg{To simplify, we should perhaps ask for the approximations to be minimal.}
+\pg{To simplify, we should perhaps ask for the approximations to be minimal.}\yann{added missing  ``indecomposable'' which fixes this issue}
 \end{definition}
@@
 Denote by~$F$ the functor~$\Hom{K^b}(\Lambda, -):K^{[-1,0]}(\proj \Lambda) \to \MOD \Lambda$.
-Then there is an almost-split sequence
+Then there is an almost-split sequence in~$\MOD\Lambda$:
  \[
@@
  \]
- in~$\MOD\Lambda$.
+
 \end{lemma}

### 2019-06-12 thirdPaper/draft/typeConeAssociahedra.tex
typo

@@
 \item The facet-defining inequalities of the type cone of~$\Fan$ correspond to very specific pairs of adjacent maximal cones of~$\Fan$ whose corresponding linear dependences minimally generate all such dependences.
-While they correspond to mesh mutations for cluster algebras and brick $2$-acyclic gentle algebras, they are not clear in general (see for instance \cref{fig:labelFacetDefiningInequalititiesNKC}\,(right)).
+While they correspond to mesh mutations for cluster algebras and brick $2$-acyclic gentle algebras, they are not understood in general (see for instance \cref{fig:labelFacetDefiningInequalititiesNKC}\,(right)).
 It would be particularly interesting to fully understand these specific mutations for arbitrary (non-kissing finite) gentle algebras.

### 2019-06-13 thirdPaper/draft/typeConeAssociahedra.tex
Got rid of last example, which is not relevant.

@@
 
-\subsubsection{A quotient of a Frobenius category}
-\begin{example}
- Consider the preprojective algebra of type~$A_3$, as in Example~\ref{exam::preprojective silting objects}.
+% \subsubsection{A quotient of a Frobenius category}
+% \begin{example}
+%  Consider the preprojective algebra of type~$A_3$, as in Example~\ref{exam::preprojective silting objects}.
 It is a self-injective algebra, so its module category is a Frobenius category.
 Its projective-injective objects are the modules
- \[
-  \begin{matrix} 1 \\ 2 \\ 3 \end{matrix} \quad , \quad  \begin{matrix} 2 \\ 13 \\ 2 \end{matrix} \quad \textrm{and} \quad \begin{matrix} 3 \\ 2 \\ 1 \end{matrix}.
- \]
- Taking the quotient by the ideal generated by all morphisms factoring through direct sums of copies of the second of these objects, we get an extriangulated category~\cite{} whose Auslander--Reiten quiver is given as follows.
-  \[
-  \hspace*{-2cm}
- {\footnotesize
-  \begin{tikzcd}
-   \begin{matrix} 3 \end{matrix}\arrow[dr] && \begin{matrix} 2 \\ 1 \end{matrix}\arrow[r]\arrow[dr] & \begin{matrix} 3 \\ 2 \\ 1 \end{matrix}\arrow[r]& \begin{matrix} 3 \\ 2 \end{matrix}\arrow[dr] && \begin{matrix} 1 \end{matrix}\arrow[dr]&& \begin{matrix} 2 \\ 3 \end{matrix} \\
-    & \begin{matrix} 2\\ 13 \end{matrix}\arrow[ur]\arrow[dr] && \begin{matrix} 2 \end{matrix}\arrow[ur]\arrow[dr] && \begin{matrix} 13\\2 \end{matrix}\arrow[ur]\arrow[dr] && \begin{matrix} 2\\13 \end{matrix}\arrow[ur]\arrow[dr] &  \\
-   \begin{matrix} 1 \end{matrix}\arrow[ur] && \begin{matrix} 2\\3 \end{matrix}\arrow[ur]\arrow[r] & \begin{matrix} 1\\2\\3 \end{matrix}\arrow[r] & \begin{matrix} 1\\2 \end{matrix}\arrow[ur] && \begin{matrix} 3\\1 \end{matrix}\arrow[ur] && \begin{matrix} 2\\1 \end{matrix}
-  \end{tikzcd}
-  }
- \]
-
- \pg{Not sure why we wanted this example anymore.}
-\end{example}
+%  \[
+%   \begin{matrix} 1 \\ 2 \\ 3 \end{matrix} \quad , \quad  \begin{matrix} 2 \\ 13 \\ 2 \end{matrix} \quad \textrm{and} \quad \begin{matrix} 3 \\ 2 \\ 1 \end{matrix}.
+%  \]
+%  Taking the quotient by the ideal generated by all morphisms factoring through direct sums of copies of the second of these objects, we get an extriangulated category~\cite{} whose Auslander--Reiten quiver is given as follows.
+%   \[
+%   \hspace*{-2cm}
+%  {\footnotesize
+%   \begin{tikzcd}
+%    \begin{matrix} 3 \end{matrix}\arrow[dr] && \begin{matrix} 2 \\ 1 \end{matrix}\arrow[r]\arrow[dr] & \begin{matrix} 3 \\ 2 \\ 1 \end{matrix}\arrow[r]& \begin{matrix} 3 \\ 2 \end{matrix}\arrow[dr] && \begin{matrix} 1 \end{matrix}\arrow[dr]&& \begin{matrix} 2 \\ 3 \end{matrix} \\
+%     & \begin{matrix} 2\\ 13 \end{matrix}\arrow[ur]\arrow[dr] && \begin{matrix} 2 \end{matrix}\arrow[ur]\arrow[dr] && \begin{matrix} 13\\2 \end{matrix}\arrow[ur]\arrow[dr] && \begin{matrix} 2\\13 \end{matrix}\arrow[ur]\arrow[dr] &  \\
+%    \begin{matrix} 1 \end{matrix}\arrow[ur] && \begin{matrix} 2\\3 \end{matrix}\arrow[ur]\arrow[r] & \begin{matrix} 1\\2\\3 \end{matrix}\arrow[r] & \begin{matrix} 1\\2 \end{matrix}\arrow[ur] && \begin{matrix} 3\\1 \end{matrix}\arrow[ur] && \begin{matrix} 2\\1 \end{matrix}
+%   \end{tikzcd}
+%   }
+%  \]
+%  
+%  \pg{Not sure why we wanted this example anymore.}
+% \end{example}
 

### 2019-06-13 thirdPaper/draft/typeConeAssociahedra.tex
Added Remark 4.45

@@
 
-\vincent{Here should come the proof of \cref{prop:exchangeablePairsNKC}.}
-\pg{It is done in Coro~\ref{coro::exchangeablePairsNKC}.}
-
 %%%%%%%%%%%
@@
 any morphism from~$X$ to an object in~$\add R$ factors through~$X\infl E$).
-\pg{To simplify, we should perhaps ask for the approximations to be minimal.}\yann{added missing  ``indecomposable'' which fixes this issue}
 \end{definition}
+\begin{remark}
+In Definition~\ref{defn::mutation conflation}, the requirement that~$X$ and~$Y$ are indecomposable implies the map~$E\defl Y$ is a right~($\add R$)-approximation, and that both approximations are minimal.
+\end{remark}
 
@@
 Let~$\Lambda$ be an Artin algebra, let~$\tau X\infl E\defl X$ be an Auslander--Reiten conflation in~$K^{[-1,0]}(\proj\Lambda)$ and denote~$FX=M$.
-Assume that:\yann{There might be some redundancies in the assumptions}\pg{If so, it's not obvious to me.}
 \begin{enumerate}

### 2019-06-13 thirdPaper/draft/typeConeAssociahedra.tex
Minor changes

@@
 
-  \item Let~$K_0(\cat ; T)$ \yann{I do not like this notation anymore: $K_0(\cat ; T)$ depends on the choice of a CTO $T$.
-How about $K_0^T(\cat)$, $K_0^{(\susp T)}(\cat)$, $K_0(\cat;T)$, $\Kg(\cat;T)$ or $K_0(\cat;(\susp T))$?}\pg{Good point.
-I like~$K_0^T(\cat)$ and~$K_0(\cat;T)$.} be the quotient of~$\Ksp(\cat)$ by the relations~$[X]+[Z]-[Y]$ for all triangles
+  \item Let~$K_0(\cat ; T)$ be the quotient of~$\Ksp(\cat)$ by the relations~$[X]+[Z]-[Y]$ for all triangles
   \[

### 2019-06-13 thirdPaper/draft/typeConeAssociahedra.tex
3-dim

--- 2019-06-13 thirdPaper/draft/typeConeAssociahedra.tex
@@
 The associahedron is a ``mythical polytope'' \cite{Haiman} whose facial structure encodes Catalan families: its vertices correspond to parenthesizations of a non-associative product, triangulations of a convex polygon, or binary trees; its edges correspond to applications of the associativity rule, diagonal flips, or edge rotations; and in general its faces correspond to partial parenthesizations, diagonal dissections, or Schr\"oder trees.
-Its combinatorial and topological structure was introduced in early works of D.~Tamari~\cite{Tamari} and J.~Stasheff~\cite{Stasheff}, and a first polytopal model was realized by J.~Milnor for the PhD defense of J.~Stasheff.
+Its combinatorial and topological structure was introduced in early works of D.~Tamari~\cite{Tamari} and J.~Stasheff~\cite{Stasheff}, and a first $3$-dimensional polytopal model was realized by J.~Milnor for the PhD defense of J.~Stasheff.
 The first systematic polytopal realizations were constructed by M.~Haiman~\cite{Haiman} and C.~Lee~\cite{Lee}.

### 2019-06-13 thirdPaper/draft/typeConeAssociahedra.tex
typographic changes

@@
 \tableofcontents
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \begin{proof}
-Points~(i), (iii) and~(iv) where shown in~\cite[Prop.~2.33, Thm.~4.17 \& Prop~4.16]{PaluPilaudPlamondon-nonkissing}.
-We postpone the proof of point~(ii) until Corollary~\ref{coro::exchangeablePairsNKC}.
+Points~(i), (iii) and~(iv) where shown in~\cite[Prop.~2.33, Thm.~4.17 \& Prop~4.16]{PaluPilaudPlamondon-nonkissing}. We postpone the proof of point~(ii) until \cref{coro::exchangeablePairsNKC}.
 \end{proof}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 In~\cite{Auslander1984}, M.~Auslander showed that the relations in the Grothendieck group of an Artin algebra are generated by the ones given by almost-split sequences precisely when the algebra is of finite representation type.
-Inspired by this result, we will show that a similar statement holds (Theorem~\ref{theo::relations-g-vecteurs}) for the~$\b g$-vectors (or indices) of objects in a~$2$-Calabi--Yau triangulated category.
+Inspired by this result, we will show that a similar statement holds (\cref{theo::relations-g-vecteurs}) for the~$\b{g}$-vectors (or indices) of objects in a~$2$-Calabi--Yau triangulated category.
 
@@
 \]
- where~$D=\Hom{\field}(-,\field)$ is the usual duality of vector spaces;
- \item $\cat$ contains a basic cluster-tilting object~$T=\bigoplus_{i=1}^n T_i$:
+where~$D = \Hom{\field}(-,\field)$ is the usual duality of vector spaces;
+\item $\cat$ contains a basic cluster-tilting object~$T = \bigoplus_{i=1}^n T_i$:
 \[
@@
 
-\begin{proposition}[Proposition I.2.3 of~\cite{ReitenVandenbergh}]
+\begin{proposition}[{\cite[Prop.~I.2.3]{ReitenVandenbergh}}]
 Any triangulated category admitting a Serre functor has almost-split triangles. In particular, any~$2$-Calabi--Yau triangulated category has almost-split triangles.
@@
 \]
-  with~$h\in (\susp T)$.  Denote by~$\b g:\Ksp(\cat) \to K_0(\cat ; T)$ the canonical projection.
+with~$h\in (\susp T)$. Denote by~$\b{g}:\Ksp(\cat) \to K_0(\cat ; T)$ the canonical projection.
 \end{enumerate}
-
 \end{definition}
+
 In particular,~$\Ksp(\cat)$ is isomorphic to a free abelian group over the set~$\ind(\cat)$.
-Considering the modified group~$K_0(\cat ; T)$ instead of the usual Grothendieck group is motivated by Section~\ref{sect::applications-g-vectors}, where we study relations between~$\b g$-vectors.
+Considering the modified group~$K_0(\cat ; T)$ instead of the usual Grothendieck group is motivated by \cref{sect::applications-g-vectors}, where we study relations between~$\b{g}$-vectors.
 
@@
 \label{theo::relations-g-vecteurs}
- Let~$\cat$ be a category satisying the hypotheses of Section \ref{sect::setting}.  Then~$\cat$ has only finitely many isomorphism classes of indecomposable objects if and only if the set
+Let~$\cat$ be a category satisying the hypotheses of \cref{sect::setting}. Then~$\cat$ has only finitely many isomorphism classes of indecomposable objects if and only if the set
 \[
@@
 \]
- generates the kernel of~$\b g:\Ksp(\cat) \to K_0(\cat ; T)$. 
- In this case, the set~$L$ is a basis of the kernel of~$\b g$, and for any $x\in \ker(\b g)$, we have that
+generates the kernel of~$\b{g}:\Ksp(\cat) \to K_0(\cat ; T)$. 
+In this case, the set~$L$ is a basis of the kernel of~$\b{g}$, and for any $x\in \ker(\b{g})$, we have that
 \[
@@
 Let~$X\xrightarrow{} E \xrightarrow{} Y \xrightarrow{h} \susp X$ be a triangle with~$h\in (\susp T)$.
-Then the element~$x=[X]+[Y]-[E]$ of the kernel of~$\b g$ is a non-negative linear combination of the~$\ell_A$, with~$A\in \ind(\cat)\ssm \add(\susp T)$.
+Then the element~$x=[X]+[Y]-[E]$ of the kernel of~$\b{g}$ is a non-negative linear combination of the~$\ell_A$, with~$A\in \ind(\cat)\ssm \add(\susp T)$.
 \end{corollary}
+
 \begin{proof}
- We know that~$x=\sum_{A\in \ind(\cat) \ssm \add(\susp T)} \frac{\langle x, [A] \rangle}{\langle \ell_A, [A] \rangle} \ell_A$; since~$\langle \ell_A, [A] \rangle$ is positive by Lemma~\ref{lemm::bilinear-form}, we only need to show that each~$\langle x, [A] \rangle$ is non-negative.
+We know that~$x=\sum_{A\in \ind(\cat) \ssm \add(\susp T)} \frac{\langle x, [A] \rangle}{\langle \ell_A, [A] \rangle} \ell_A$; since~$\langle \ell_A, [A] \rangle$ is positive by \cref{lemm::bilinear-form}, we only need to show that each~$\langle x, [A] \rangle$ is non-negative.
 The functor~$F=\cat(T,-)$ induces an exact sequence
@@
 
-\subsection{Proof of Theorem \ref{theo::relations-g-vecteurs}}
-
-Before we can prove Theorem~\ref{theo::relations-g-vecteurs}, we need to recall the following results and definition from \cite{DehyKeller,Palu}.
+\subsection{Proof of \cref{theo::relations-g-vecteurs}}
+
+Before we can prove \cref{theo::relations-g-vecteurs}, we need to recall the following results and definition from \cite{DehyKeller,Palu}.
 
@@
 
-The notion of index is very close to the definition of the map~$\b g:\Ksp(\cat)\to K_0(\cat ; T)$ of Definition~\ref{defi::grothendieck-group}.  The link is given by the following result.
+The notion of index is very close to the definition of the map~$\b{g}:\Ksp(\cat)\to K_0(\cat ; T)$ of \cref{defi::grothendieck-group}. The link is given by the following result.
 
@@
 \label{coro::grothendieck-g-vectors}
- There is an isomorphism~$\phi:K_0(\cat ; T) \to \Ksp(\add(T))$ such that~$\ind_T = \phi\circ \b g$.  In particular,~$K_0(\cat ; T)$ is a free abelian group generated by the~$[T_i]$.
+ There is an isomorphism~$\phi:K_0(\cat ; T) \to \Ksp(\add(T))$ such that~$\ind_T = \phi\circ \b{g}$. In particular,~$K_0(\cat ; T)$ is a free abelian group generated by the~$[T_i]$.
 \end{corollary}
 
-We can now begin the proof of Theorem~\ref{theo::relations-g-vecteurs}
+We can now begin the proof of \cref{theo::relations-g-vecteurs}
 
@@
  \]
- be an almost-split triangle.  By Lemma~\ref{lemm::almost-split}, the morphism~$h$ is in~$(\susp T)$.  Applying the functor~$F=\cat(T,-)$, we get an exact sequence
+ be an almost-split triangle. By \cref{lemm::almost-split}, the morphism~$h$ is in~$(\susp T)$. Applying the functor~$F=\cat(T,-)$, we get an exact sequence
  \[
@@
  \]
- Applying now the functors~$\cat(-, B)$ and~$\Hom{\Lambda}(-, FB)$, we get a commutative diagram whose rows are exact sequences and whose vertical maps are surjective by Proposition~\ref{prop::functor-F}.
+ Applying now the functors~$\cat(-, B)$ and~$\Hom{\Lambda}(-, FB)$, we get a commutative diagram whose rows are exact sequences and whose vertical maps are surjective by \cref{prop::functor-F}.
  \[
@@
 \begin{proof}
- Let~$B\in \ind(\cat) \ssm \add(\susp T)$.  Applying Lemma~\ref{lemm::bilinear-form}, we get that
+ Let~$B\in \ind(\cat) \ssm \add(\susp T)$. Applying \cref{lemm::bilinear-form}, we get that
  \[
@@
 
- Assume that (2) holds.  Then, by Lemma~\ref{lemm::coefficients}, we have that
+ Assume that (2) holds. Then, by \cref{lemm::coefficients}, we have that
  \[
@@
 
- Assume now that (1) holds.  Then~$\langle x, [A]\rangle = 0$ for any~$A$ by Lemma~\ref{lemm::bilinear-form-suspention-T}.  Thus (2) holds.
+ Assume now that (1) holds. Then~$\langle x, [A]\rangle = 0$ for any~$A$ by \cref{lemm::bilinear-form-suspention-T}. Thus (2) holds.
 \end{proof}
@@
  \]
- Then~$\langle x, [A] \rangle = 0$ for all~$A\in\ind(\cat) \ssm \add(\susp T)$.  But~$\langle x, [A] \rangle = \lambda_A$ by Lemma~\ref{lemm::bilinear-form}.  Thus~
+ Then~$\langle x, [A] \rangle = 0$ for all~$A\in\ind(\cat) \ssm \add(\susp T)$. But~$\langle x, [A] \rangle = \lambda_A$ by \cref{lemm::bilinear-form}. Thus~
  \[
@@
  Assume that~$\ind(\cat)$ is finite.
-Then the set~$\set{[\ell_A]}{A\in \ind(\cat) \ssm \add(\susp T)}$ is a basis of the kernel of~$\b g : \Ksp(\cat) \to K_0(\cat ; T)$.
-Moreover, for any~$x\in \ker \b g$, we have that
+Then the set~$\set{[\ell_A]}{A\in \ind(\cat) \ssm \add(\susp T)}$ is a basis of the kernel of~$\b{g} : \Ksp(\cat) \to K_0(\cat ; T)$.
+Moreover, for any~$x\in \ker \b{g}$, we have that
  \[
@@
 \begin{proof}
-By Proposition~\ref{prop::free-set}, the set is free.  Let~$x\in \ker \b g$.  Consider the element
+By \cref{prop::free-set}, the set is free. Let~$x\in \ker \b{g}$. Consider the element
 \[
@@
 \]
-where the second equality is obtained by using Lemma~\ref{lemm::bilinear-form}.
-By Lemma~\ref{lemm::test-susp-T}, this implies that~$z\in \Ksp(\add(\susp T))$.
-Since~$z\in \ker(\b g)$ and since~$\b g$ is injective on~$\Ksp(\add (\susp T))$ by Corollary~\ref{coro::grothendieck-g-vectors}, we get that~$z=0$.
+where the second equality is obtained by using \cref{lemm::bilinear-form}.
+By \cref{lemm::test-susp-T}, this implies that~$z\in \Ksp(\add(\susp T))$.
+Since~$z\in \ker(\b{g})$ and since~$\b{g}$ is injective on~$\Ksp(\add (\susp T))$ by \cref{coro::grothendieck-g-vectors}, we get that~$z=0$.
 This finishes the proof.
@@
 \begin{proof}
- By Proposition~\ref{prop::free-set}, the set is free.  It suffices to prove that it generates~$\Ksp(\cat)$.  Let~$x\in \Ksp(\cat)$.  Consider
+ By \cref{prop::free-set}, the set is free. It suffices to prove that it generates~$\Ksp(\cat)$. Let~$x\in \Ksp(\cat)$. Consider
  \[
@@
  \]
- Then for any~$B\in \ind(\cat)$, we have that~$\langle z, [B] \rangle = 0$.  By Lemma~\ref{lemm::test-susp-T}, this implies that~$z\in \Ksp(\add(\susp T))$, and finishes the proof.
+ Then for any~$B\in \ind(\cat)$, we have that~$\langle z, [B] \rangle = 0$. By \cref{lemm::test-susp-T}, this implies that~$z\in \Ksp(\add(\susp T))$, and finishes the proof.
 \end{proof}
 
-All that remains is to prove the converse in the statement of Theorem~\ref{theo::relations-g-vecteurs}.
+All that remains is to prove the converse in the statement of \cref{theo::relations-g-vecteurs}.
 
 \begin{proposition}
- Assume that the set~$\set{[\ell_A]}{A\in \ind(\cat) \ssm \add(\susp T)}$ is a basis of the kernel of~$\b g$. Then~$\ind(\cat)$ is finite.
+ Assume that the set~$\set{[\ell_A]}{A\in \ind(\cat) \ssm \add(\susp T)}$ is a basis of the kernel of~$\b{g}$. Then~$\ind(\cat)$ is finite.
 \end{proposition}
 \begin{proof}
- Let~$x\in \ker \b g$, and write~$x = \sum_{[A]\in \ind(\cat)} \lambda_A[A]$, where the sum has finite support.  For any~$B$ not in the support of the sum, we have that~$\langle x, [B] \rangle = 0$.
-
- Now,~$[T]+[\susp T]$ is in the kernel of~$\b g$, but~$\langle [T] + [\susp T], [B] \rangle = \langle [T], [B] \rangle = 0$ if and only if~$B\in \add(\susp T)$.  Thus~$\ind(\cat)$ has to be finite.
+ Let~$x\in \ker \b{g}$, and write~$x = \sum_{[A]\in \ind(\cat)} \lambda_A[A]$, where the sum has finite support. For any~$B$ not in the support of the sum, we have that~$\langle x, [B] \rangle = 0$.
+
+ Now,~$[T]+[\susp T]$ is in the kernel of~$\b{g}$, but~$\langle [T] + [\susp T], [B] \rangle = \langle [T], [B] \rangle = 0$ if and only if~$B\in \add(\susp T)$. Thus~$\ind(\cat)$ has to be finite.
 \end{proof}
@@
 
-\subsection{Application to~$\b g$-vectors of cluster algebras of finite type}
+\subsection{Application to~$\b{g}$-vectors of cluster algebras of finite type}
 \label{sect::applications-g-vectors}
 
-In this section, we apply the results of Section~\ref{subsect::Statement cluster cats} in order to prove Proposition~\ref{prop:uniqueExchangePropertyCA} and Proposition~\ref{prop:meshMutations} of Section~\ref{subsec:typeConeCA}.
+In this section, we apply the results of \cref{subsect::Statement cluster cats} in order to prove \cref{prop:uniqueExchangePropertyCA} and \cref{prop:meshMutations} of \cref{subsec:typeConeCA}.
 
@@
   \item[(i)] \emph{(}\cite[Prop.~3.2]{BuanMarshReinekeReitenTodorov} and~\cite[]{???} \emph{)} For any~$X,Y\in \ind(\cat)$, $\CC(X)$ and~$\CC(Y)$ are compatible if and only if~$\cat(X, \susp Y) = 0$.
-  \item[(ii)] \emph{(}\cite[Prop.~4.3]{FuKeller} and \emph{)} For any~$X\in \ind(\cat)$, the~$\b g$-vector of~$\CC(X)$ is~$\b g([X])$, where we identify~$\Z^n$ and~$K_0(\cat ; T)$ via the isomorphism sending~$(a_1, \ldots, a_n)$ to~$\sum_{i=1}^n a_i [T_i]$.
+  \item[(ii)] \emph{(}\cite[Prop.~4.3]{FuKeller} and \emph{)} For any~$X\in \ind(\cat)$, the~$\b{g}$-vector of~$\CC(X)$ is~$\b{g}([X])$, where we identify~$\Z^n$ and~$K_0(\cat ; T)$ via the isomorphism sending~$(a_1, \ldots, a_n)$ to~$\sum_{i=1}^n a_i [T_i]$.
   \item[(iii)] \emph{(}\cite[Thm.~7.5]{BuanMarshReinekeReitenTodorov} and~\cite[]{???—} \emph{)} For any~$X,Y\in \ind(\cat)$, $\CC(X)$ and~$\CC(Y)$ are exchangeable if and only if~$\dim_{\field_X}\cat(X, \susp Y) = \dim_{\field_Y}\cat(X, \susp Y) = 1$.
@@
 \begin{proof}
-In view of Theorem~\ref{thm::categorification} (iii), it follows from~\cite[Lem.~3.3]{Palu}
+In view of \cref{thm::categorification} (iii), it follows from~\cite[Lem.~3.3]{Palu}
 \end{proof}
 
-\begin{corollary}\emph{(Proposition~\ref{prop:meshMutations})}
+\begin{corollary}\emph{(\cref{prop:meshMutations})}
 \label{corollary:proof of prop meshMutations}
@@
 Let~$\cat$ be a cluster category of Dynkin type~$A,B,C,D,E,F$ or~$G$, and let $T\in\cat$ be some basic cluster-tilting object categorifying the given initial exchange matrix~$\B_\circ$. 
-By Lemma~\ref{lemma:positive mutation triangles}, we may assume that the mutation under consideration is a positive mutation.
-In view of Theorem~\ref{thm::categorification} (ii) and (iv) it is enough to show that the relation in~$K_0(\cat ; T)$ given by any triangle~$X\to E\to Y\xrightarrow{h} \susp X$ with~$h\in(\susp T)$ is a positive linear combination of relations coming from Auslander--Reiten triangles with third term not in~$\add(\susp T)$.
-This categorified statement is precisely Corollary~\ref{corollary::meshes positively generate cluster cats}.
+By \cref{lemma:positive mutation triangles}, we may assume that the mutation under consideration is a positive mutation.
+In view of \cref{thm::categorification} (ii) and (iv) it is enough to show that the relation in~$K_0(\cat ; T)$ given by any triangle~$X\to E\to Y\xrightarrow{h} \susp X$ with~$h\in(\susp T)$ is a positive linear combination of relations coming from Auslander--Reiten triangles with third term not in~$\add(\susp T)$.
+This categorified statement is precisely \cref{corollary::meshes positively generate cluster cats}.
 \end{proof}
 
-It also follows form Theorem~\ref{thm::categorification} above that any cluster algebra of finite type has the unique exchange relation property (see Definition~\ref{def:uerp}):
+It also follows form \cref{thm::categorification} above that any cluster algebra of finite type has the unique exchange relation property (see \cref{def:uerp}):
 \begin{corollary}
 \label{corollary:UERPforCAproof}
-\emph{(Proposition~\ref{prop:uniqueExchangePropertyCA})}
+\emph{(\cref{prop:uniqueExchangePropertyCA})}
 Let~$\B_\circ$ be any finite type exchange matrix, and let~$\mathcal{A}(\B_\circ)$ be the associated cluster algebra without coefficients.
@@
 \begin{proof}
-By the results in additive categorification of cluster algebras recalled in Theorem~\ref{thm::categorification}, the statement follows from Lemma~\ref{lemma::uerp categorified} below.
+By the results in additive categorification of cluster algebras recalled in \cref{thm::categorification}, the statement follows from \cref{lemma::uerp categorified} below.
 \end{proof}
@@
 Let~$T\in\cat$ be a basic cluster tilting object such that~$\CC(T)$ is the initial cluster.
-By Lemma~\ref{lemma:positive mutation triangles}, the morphism~$h$ belongs to the ideal~$(\susp T)$.
+By \cref{lemma:positive mutation triangles}, the morphism~$h$ belongs to the ideal~$(\susp T)$.
 Therefore, the triangle~$X\to \bigoplus_i E_i \to Y \xrightarrow{h} \susp X$ induces the relation~$[X]+[Y]=\sum_i [E_i]$ in~$K_0(\cat ; T)$.
-Theorem~\ref{thm::categorification} (ii) gives the equality~$\b{g}_{\CC(X)} + \b{g}_{\CC(Y)} = \sum_i\b{g}_{\CC(E_i)}$, where the~$\b{g}$-vectors are computed with respect to the initial seed~$\CC(T)$.
-By Theorem~\ref{thm::categorification} (iii), the middle term of the triangle is uniquely defined, up to isomorphism, by~$X$, and~$Y$, and the triangle is therefore an exchange triangle, with respect to any mutation at~$X$: it does not depend on the choice of a cluster tilting object containing~$X$.
-By Theorem~\ref{thm::categorification} (iv) this equality is one of the two equalities in Lemma~\ref{lem:linearDependencegvectorsCA}.
+\cref{thm::categorification} (ii) gives the equality~$\b{g}_{\CC(X)} + \b{g}_{\CC(Y)} = \sum_i\b{g}_{\CC(E_i)}$, where the~$\b{g}$-vectors are computed with respect to the initial seed~$\CC(T)$.
+By \cref{thm::categorification} (iii), the middle term of the triangle is uniquely defined, up to isomorphism, by~$X$, and~$Y$, and the triangle is therefore an exchange triangle, with respect to any mutation at~$X$: it does not depend on the choice of a cluster tilting object containing~$X$.
+By \cref{thm::categorification} (iv) this equality is one of the two equalities in \cref{lem:linearDependencegvectorsCA}.
 \end{proof}
@@
 With the choice of the Hom functor, $\susp T$ is sent to the initial seed so that the AR triangles ending in $\add(\susp T)$ are precisely the meshes ending in an initial variable}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\vincent{A short introduction is missing here.}
+The main definitions and first properties on extriangulated categories are recalled after the statements of the main results of this section.
+See \cref{sect::recollections extricats} below.
+The reader that does not want to dwell into details can safely skip \cref{sect::recollections extricats} and focus on any of the first three examples given in \cref{remark::examples extricats}: triangulated categories, exact categories (that are small or have enough projectives or injectives) and extension-closed subcategories of triangulated categories, such as the category~$K^{[-1,0]}(\proj \Lambda)$, are examples of extriangulated categories.
 
@@
 
-The main definitions and first properties on extriangulated categories are recalled after the statements of the main results of this section.
-See Section~\ref{sect::recollections extricats} below.
-The reader that does not want to dwell into details can safely skip Section~\ref{sect::recollections extricats} and focus on any of the first three examples given in Remark~\ref{remark::examples extricats}: triangulated categories, exact categories (that are small or have enough projectives or injectives) and extension-closed subcategories of triangulated categories, such as the category~$K^{[-1,0]}(\proj \Lambda)$, are examples of extriangulated categories.
-
 We indifferently call \emph{conflations}, written~$X\infl Y\defl Z$, or \emph{extriangles}, written~$X\infl Y\defl Z \overset{\delta}{\dashrightarrow}$, the analogues of short exact sequences or triangles in an extriangulated category.
@@
 \vspace{.4cm}
-\noindent {\bf Setting for Section~\ref{sect::prelim on extricats}}
+\noindent {\bf Setting for \cref{sect::prelim on extricats}}
 In that section, we let~$\cat$ be an extriangulated category with a fixed full additive \yann{additive contains strictly full + stable under taking summands} subcategory~$\tc$ satisfying the following three properties:
@@
 
-\noindent {\bf Setting for Section~\ref{sect::Statment extricats}}
+\noindent {\bf Setting for \cref{sect::Statment extricats}}
 In that section, we keep the previous setting, but assume moreover that~$\cat$ is Krull--Schmidt, $\field$-linear, Ext-finite, and has Auslander--Reiten--Serre duality, and that the subcategory~$\tc$ is of the form~$\add T$, where~$T=T_1\oplus\cdots\oplus T_n$ is a basic object.
@@
  \begin{itemize}
-  \item $2$-Calabi--Yau triangulated categories admitting a cluster-tilting object (see Section~\ref{sect::2CYTriangulated});
-  \item $2$-Calabi--Yau Frobenius exact categories (see Section~\ref{sect::2CYexact});
-  \item for any Artin algebra~$\Lambda$, the category~$K^{[-1,0]}(\proj \Lambda)$ of complexes of finitely generated projective~$\Lambda$-modules concentrated in degrees~$-1$ and~$0$, with morphisms considered up to homotopy (see Section~\ref{sect::Kbproj});
-  \item more generally, extriangulated categories~$\cat$ constructed as follows: if~$\tc$ is a rigid subcategory of an extriangulated category~$\ec$, we let~$\cat$ be the full subcategory of~$\ec$ whose objects satisfy condition (3), equipped with the extriangulated structure obtained from that of~$\ec$ by considering those extriangles in~$\ec$ all whose terms belong to~$\cat$ and whose deflation is~$\tc$-epi (see Section~\ref{sect::prT}).
+  \item $2$-Calabi--Yau triangulated categories admitting a cluster-tilting object (see \cref{sect::2CYTriangulated});
+  \item $2$-Calabi--Yau Frobenius exact categories (see \cref{sect::2CYexact});
+  \item for any Artin algebra~$\Lambda$, the category~$K^{[-1,0]}(\proj \Lambda)$ of complexes of finitely generated projective~$\Lambda$-modules concentrated in degrees~$-1$ and~$0$, with morphisms considered up to homotopy (see \cref{sect::Kbproj});
+  \item more generally, extriangulated categories~$\cat$ constructed as follows: if~$\tc$ is a rigid subcategory of an extriangulated category~$\ec$, we let~$\cat$ be the full subcategory of~$\ec$ whose objects satisfy condition (3), equipped with the extriangulated structure obtained from that of~$\ec$ by considering those extriangles in~$\ec$ all whose terms belong to~$\cat$ and whose deflation is~$\tc$-epi (see \cref{sect::prT}).
  \end{itemize}
@@
 
-So as to be able to state the main theorem of Section~\ref{sec:extricats}, we need a few results on extriangulated categories.
-However, all proofs are postponed to Section~\ref{sect::proofs extricats}.
-
-We let~$\cat$ be as in Setting~\ref{setting::extricat}.
+So as to be able to state the main theorem of \cref{sec:extricats}, we need a few results on extriangulated categories.
+However, all proofs are postponed to \cref{sect::proofs extricats}.
+
+We let~$\cat$ be as in \cref{setting::extricat}.
 
@@
 \begin{remark}
- As will be proven below (Remark~\ref{remark::equivalence Sigma} and Corollary~\ref{corollary::Sigma T injectives}), this notation extends to an equivalence of categories from the category~$\tc$ of projective objects in~$\cat$ to the category~$\susp\tc$ of injective objects in~$\cat$.
+ As will be proven below (\cref{remark::equivalence Sigma} and \cref{corollary::Sigma T injectives}), this notation extends to an equivalence of categories from the category~$\tc$ of projective objects in~$\cat$ to the category~$\susp\tc$ of injective objects in~$\cat$.
 \end{remark}
@@
 
-Proposition~\ref{prop::KRextricat} below extends similar results from~\cite{BuanMarshReiten,KellerReiten,KoenigZhu,IyamaYoshino} (see also Proposition~\ref{prop::functor-F}) to the setting under consideration.
+\cref{prop::KRextricat} below extends similar results from~\cite{BuanMarshReiten,KellerReiten,KoenigZhu,IyamaYoshino} (see also \cref{prop::functor-F}) to the setting under consideration.
 We note that the proof requires minor modifications.
@@
 
-Let~$\cat$ be as in Setting~\ref{setting::extricat}.
+Let~$\cat$ be as in \cref{setting::extricat}.
 
@@
 Assume moreover that~$\cat$ is $\field$-linear and Ext-finite.
-By the preliminary results of Section~\ref{subsection: prelim on extricats}, we can apply~\cite[Prop.~4.2]{IyamaNakaokaPalu} to obtain that~$\modt$ is Hom-finite.
+By the preliminary results of \cref{sect::recollections extricats}, we can apply~\cite[Prop.~4.2]{IyamaNakaokaPalu} to obtain that~$\modt$ is Hom-finite.
 In particular, if $\tc=\add T$, then $\End{\cat}(T)$ is a finite-dimensional~$\field$-algebra.
-It thus also follows that Definition~\ref{defi::bilinear form} still makes sense in this more general setup: For any~$X,Y\in\cat$,
+It thus also follows that \cref{defi::bilinear form} still makes sense in this more general setup: For any~$X,Y\in\cat$,
 \[
@@
 
-When this makes sense, we make use of Notation~\ref{notation::ell_X}: if
+When this makes sense, we make use of \cref{notation::ell_X}: if
 \[
@@
 \]
-generates the kernel of the canonical projection~$\b g:\Ksp(\cat) \to \kzero{\cat}$. 
-In this case, the set~$L$ is a basis of the kernel of~$\b g$, and for any $x\in \ker(\b g)$, we have that
+generates the kernel of the canonical projection~$\b{g}:\Ksp(\cat) \to \kzero{\cat}$. 
+In this case, the set~$L$ is a basis of the kernel of~$\b{g}$, and for any $x\in \ker(\b{g})$, we have that
  \[
@@
 Let~$X\infl E\defl Y\dashrightarrow$ be any extriangle.
-Then the element~$x=[X]+[Y]-[E]$ of the kernel of~$\b g$ is a non-negative linear combination of the~$\ell_A$, with~$A\in\ind(\cat)\ssm \add(\susp T)$.
+Then the element~$x=[X]+[Y]-[E]$ of the kernel of~$\b{g}$ is a non-negative linear combination of the~$\ell_A$, with~$A\in\ind(\cat)\ssm \add(\susp T)$.
 \end{corollary}
@@
 \label{sect::recollections extricats}
-%%%%%%%%%%%
 
@@
 
-\subsection{Proofs of preliminary results and of Theorem~\ref{theorem::extricats}}
+%%%%%%%%%%%
+
+\subsection{Proofs of preliminary results and of \cref{theorem::extricats}}
 \label{sect::proofs extricats}
 
-We let~$\cat$ and~$\tc$ satisfy the assumptions (1), (2) and (3) of Setting~\ref{setting::extricat}.
+We let~$\cat$ and~$\tc$ satisfy the assumptions (1), (2) and (3) of \cref{setting::extricat}.
 We will make it explicit when more assumptions are needed.
@@
 
-(c) and (d) are obtained from the exact sequences of Proposition~\ref{proposition::extricat long exact sequences} associated with the extriangle~$T\infl 0\defl \susp T\dashrightarrow$.
+(c) and (d) are obtained from the exact sequences of \cref{proposition::extricat long exact sequences} associated with the extriangle~$T\infl 0\defl \susp T\dashrightarrow$.
 
@@
 For any~$T\in\tc$, fix an extriangle~$T\infl 0\defl\susp T\overset{\eps_T}{\dashrightarrow}$.
-As noticed in Lemma~\ref{lemma::shifts of extriangles}, for any morphism~$T\overset{f}{\to}T'$ in~$\tc$, there is a unique morphism~$\susp f\in\cat(\susp T,\susp T')$ such that~$f_\ast\eps_T=(\susp f)^\ast\eps_{T'}$ (i.e.
+As noticed in \cref{lemma::shifts of extriangles}, for any morphism~$T\overset{f}{\to}T'$ in~$\tc$, there is a unique morphism~$\susp f\in\cat(\susp T,\susp T')$ such that~$f_\ast\eps_T=(\susp f)^\ast\eps_{T'}$ (i.e.
 such that~$(f,\susp f)$ is a morphism from~$\eps_T$ to~$\eps_{T'}$), as illustrated below:
@@
 Let~$T \overset{t}{\to} X$ be a morphism with~$T\in \tc$.
-Using the notation of Remark~\ref{remark::equivalence Sigma}, there is an extriangle~$T\infl 0\defl \susp T \overset{\eps_T}{\dashrightarrow}$.
+Using the notation of \cref{remark::equivalence Sigma}, there is an extriangle~$T\infl 0\defl \susp T \overset{\eps_T}{\dashrightarrow}$.
 Consider the extriangle~$X\overset{g}{\infl} Y \overset{h}{\defl} \susp T \overset{t_\ast\eps_T}{\dashrightarrow}$.
@@
 \begin{remark}
- It follows from the proof of Lemma~\ref{lemma:: mphs in T are inflations} that conditions (1), (2), (3) in Setting~\ref{setting::extricat} are equivalent to conditions (1), (2), (3'), where
+ It follows from the proof of \cref{lemma:: mphs in T are inflations} that conditions (1), (2), (3) in \cref{setting::extricat} are equivalent to conditions (1), (2), (3'), where
 \[
@@
 
-\begin{proof}[Proof of Lemma~\ref{lemma::finitely presented}]
+\begin{proof}[Proof of \cref{lemma::finitely presented}]
  Applying the functor~$F$ to the extriangle~$T_1^X\infl T_0^X\defl X\overset{\delta_X}{\dashrightarrow}$ induces an exact sequence~$FT_1^X \to FT_0^X \to FX \to \mathbb{E}(T,T_1^X)=0$, showing that~$FX$ is finitely presented.
@@
 
-\begin{proof}[Proof of Proposition~\ref{prop::KRextricat}]
+\begin{proof}[Proof of \cref{prop::KRextricat}]
 Recall that~$F:\cat\to\modt$ denotes the functor sending an object~$X$ to the module~$\cat(-,X)|_\tc$.
-By Lemma~\ref{lemma::first consequences} (e), the ideal~$(\susp\tc)$ of morphisms factoring through an object in~$\susp\tc$ is included in the kernel of~$F$.
+By \cref{lemma::first consequences} (e), the ideal~$(\susp\tc)$ of morphisms factoring through an object in~$\susp\tc$ is included in the kernel of~$F$.
 Conversely, let~$X\xrightarrow{f}Y$ be such that~$Ff=0$.
-By Lemma~\ref{lemma::shifts of extriangles}, there is a conflation~$T_0\overset{g}{\infl} X\overset{h}{\defl} \susp T_1$ with~$T_0,T_1\in\tc$.
+By \cref{lemma::shifts of extriangles}, there is a conflation~$T_0\overset{g}{\infl} X\overset{h}{\defl} \susp T_1$ with~$T_0,T_1\in\tc$.
 By assumption, the composition~$f\circ g$ vanishes, which implies that~$f$ factors through~$\susp T_1$.
@@
 Because~$\tc$ consists of projective objects in~$\cat$, the image under~$F$ of every conflation is a right exact sequence.
-The fact that~$F$ is full and dense can thus be proven as in the case of triangulated categories, by using Lemma~\ref{lemma:: mphs in T are inflations}.
+The fact that~$F$ is full and dense can thus be proven as in the case of triangulated categories, by using \cref{lemma:: mphs in T are inflations}.
 \end{proof}
@@
 \begin{proof}
-First note that any injective object belongs to~$\susp \tc$, by Lemma~\ref{lemma::shifts of extriangles}.
+First note that any injective object belongs to~$\susp \tc$, by \cref{lemma::shifts of extriangles}.
 Let us prove that the converse holds.
@@
 Since~$\cat(-,\susp T)|_\tc = 0$ and~$f$ is~$\tc$-epic, the morphism~$\cat(-,f)|_\tc$ is an isomorphism in~$\modt$.
-By Proposition~\ref{prop::KRextricat}, there are morphisms~$Y\overset{s}{\to} X$,~$Y\xrightarrow{h}\susp T'$,~$\susp T'\xrightarrow{t} Y$, for some~$T'\in\tc$ satisfying
+By \cref{prop::KRextricat}, there are morphisms~$Y\overset{s}{\to} X$,~$Y\xrightarrow{h}\susp T'$,~$\susp T'\xrightarrow{t} Y$, for some~$T'\in\tc$ satisfying
 \[
@@
 \]
-By Lemma~\ref{lemma::first consequences} (e)~$\susp\tc$ is a rigid subcategory, so that~$t^\ast\delta=0$.
+By \cref{lemma::first consequences} (e)~$\susp\tc$ is a rigid subcategory, so that~$t^\ast\delta=0$.
 Equivalently, there is a morphism~$\susp T'\xrightarrow{k} X$ such that~$t=fk$.
@@
 \begin{remark}
-We note that Lemma~\ref{lemma::index well-defined extricat} only requires the subcategory~$\tc$ to be rigid, and not made of projective objects.
-However, this stronger assumption is used in the proof of Lemma~\ref{lemma::index kzero extricat} below.
+We note that \cref{lemma::index well-defined extricat} only requires the subcategory~$\tc$ to be rigid, and not made of projective objects.
+However, this stronger assumption is used in the proof of \cref{lemma::index kzero extricat} below.
 \end{remark}
@@
 
-\begin{proof}[Proof of Proposition~\ref{prop::index iso extricat}]
- By Lemma~\ref{lemma::index well-defined extricat} and Lemma~\ref{lemma::index kzero extricat}, the index induces an well-defined morphism of abelian groups~$\ind_\tc:\kzero{\cat}\to\kzero{\tc}$.
+\begin{proof}[Proof of \cref{prop::index iso extricat}]
+ By \cref{lemma::index well-defined extricat} and \cref{lemma::index kzero extricat}, the index induces an well-defined morphism of abelian groups~$\ind_\tc:\kzero{\cat}\to\kzero{\tc}$.
  It remains to prove that it is an isomorphism.
@@
 
-\begin{proof}[Proof of Theorem~\ref{theorem::extricats}]
- The proof is now similar to the proof of Theorem~\ref{theo::relations-g-vecteurs}, by using Proposition~\ref{prop::KRextricat} instead of Proposition~\ref{prop::functor-F}, Proposition~\ref{prop::index iso extricat} instead of Corollary~\ref{coro::grothendieck-g-vectors}, and the fact that~$\tc$ is made of projective objects instead of Lemma~\ref{lemm::almost-split}.
+\begin{proof}[Proof of \cref{theorem::extricats}]
+ The proof is now similar to the proof of \cref{theo::relations-g-vecteurs}, by using \cref{prop::KRextricat} instead of \cref{prop::functor-F}, \cref{prop::index iso extricat} instead of \cref{coro::grothendieck-g-vectors}, and the fact that~$\tc$ is made of projective objects instead of \cref{lemm::almost-split}.
 \end{proof}
 
-\begin{proof}[Proof of Corollary~\ref{corollary::meshes positively generate extricats}]
-The proof is similar to that of Corollary~\ref{corollary::meshes positively generate cluster cats}.
+\begin{proof}[Proof of \cref{corollary::meshes positively generate extricats}]
+The proof is similar to that of \cref{corollary::meshes positively generate cluster cats}.
 \end{proof}
@@
 We assume moreover that~$\cat$ is~$\field$-linear, Krull--Schmidt, Hom-finite, 2-Calabi--Yau, with a cluster-tilting object~$T$.
-Then~$\cat$ satisfies all the assumptions of Setting~\ref{setting::extricat} for Section~\ref{sect::Statment extricats} but assumption (1).
+Then~$\cat$ satisfies all the assumptions of \cref{setting::extricat} for \cref{sect::Statment extricats} but assumption (1).
 
@@
 \begin{remark}
- The main results of Section~\ref{subsect::Statement cluster cats} can thus be viewed as specific cases of the results of Section~\ref{sec:extricats}: Theorem~\ref{theo::relations-g-vecteurs} and Corollary~\ref{corollary::meshes positively generate cluster cats} are consequences of Theorem~\ref{theorem::extricats} and Corollary~\ref{corollary::meshes positively generate extricats}.
+ The main results of \cref{subsect::Statement cluster cats} can thus be viewed as specific cases of the results of \cref{sec:extricats}: \cref{theo::relations-g-vecteurs} and \cref{corollary::meshes positively generate cluster cats} are consequences of \cref{theorem::extricats} and \cref{corollary::meshes positively generate extricats}.
 \end{remark}
@@
  Let~$\Lambda$ be any Artin algebra.
-Then the category~$K^{[-1,0]}(\proj \Lambda)$ is an extriangulated category satisfying the assumptions (1) to (3) of Section~\ref{setting::extricat}, wiht~$\tc = \add(\Lambda)$.
-If, moreover,~$\Lambda$ is finite-dimensional over a field~$\field$, then~$K^{[-1,0]}(\proj \Lambda)$ satisfies all assumptions of Section~\ref{setting::extricat}.
+Then the category~$K^{[-1,0]}(\proj \Lambda)$ is an extriangulated category satisfying the assumptions (1) to (3) of \cref{setting::extricat}, wiht~$\tc = \add(\Lambda)$.
+If, moreover,~$\Lambda$ is finite-dimensional over a field~$\field$, then~$K^{[-1,0]}(\proj \Lambda)$ satisfies all assumptions of \cref{setting::extricat}.
 \end{proposition}
@@
 Moreover, if~$X= P_1\xrightarrow{f}P_0$ is an object of~$K^{[-1,0]}(\proj\Lambda)$, then it lies in a conflation~$P_1\stackrel{f}{\infl} P_0 \defl X$ by definition.
-We have proved that properties~(1) to (3) of Section~\ref{setting::extricat} are satisfied.
+We have proved that properties~(1) to (3) of \cref{setting::extricat} are satisfied.
 
@@
 
-The extriangulated category~$K^{[-1,0]}(\proj \Lambda)$ is the setting in which we can finally prove point~(ii) of Proposition~\ref{prop:exchangeablePairsNKC}, using results of~\cite{DemonetIyamaJasso} on~$\b g$-vectors.
-% Proposition~\ref{prop::2kbproj-is-extriangulated} gives a setting in which to apply Theorem~\ref{}.
+The extriangulated category~$K^{[-1,0]}(\proj \Lambda)$ is the setting in which we can finally prove point~(ii) of \cref{prop:exchangeablePairsNKC}, using results of~\cite{DemonetIyamaJasso} on~$\b{g}$-vectors.
+% \cref{prop::2kbproj-is-extriangulated} gives a setting in which to apply \cref{}.
 Before doing so, we introduce the notion of mutation conflation for two-term silting objects.
@@
 \begin{remark}
-In Definition~\ref{defn::mutation conflation}, the requirement that~$X$ and~$Y$ are indecomposable implies the map~$E\defl Y$ is a right~($\add R$)-approximation, and that both approximations are minimal.
+In \cref{defn::mutation conflation}, the requirement that~$X$ and~$Y$ are indecomposable implies the map~$E\defl Y$ is a right~($\add R$)-approximation, and that both approximations are minimal.
 \end{remark}
@@
  \begin{enumerate}
-  \item If there is a mutation conflation (see Definition~\ref{defn::mutation conflation}) of the form~$X\infl E\defl Y$, then there can be no mutation conflation of the form~$Y\infl E'\defl X$.
+  \item If there is a mutation conflation (see \cref{defn::mutation conflation}) of the form~$X\infl E\defl Y$, then there can be no mutation conflation of the form~$Y\infl E'\defl X$.
 
@@
 Let~$X\infl E\defl Y$ and~$X\infl E'\defl Y$ be two mutation conflations.
-By~\cite[Theorem 6.5]{DemonetIyamaJasso} (based on~\cite[Theorem 2.3]{DehyKeller}), rigid objects in~$K^{[-1,0]}(\proj \Lambda)$ are determined by their~$\b g$-vector.
-The datum of the~$\b g$-vector of an object of~$K^{[-1,0]}(\proj \Lambda)$ is equivalent to that of its class in the Grothendieck group~$K_0(K^{[-1,0]}(\proj \Lambda))$, where~$K^{[-1,0]}(\proj \Lambda)$ is viewed as an extriangulated category (see Proposition~\ref{prop::2kbproj-is-extriangulated}).
+By~\cite[Theorem 6.5]{DemonetIyamaJasso} (based on~\cite[Theorem 2.3]{DehyKeller}), rigid objects in~$K^{[-1,0]}(\proj \Lambda)$ are determined by their~$\b{g}$-vector.
+The datum of the~$\b{g}$-vector of an object of~$K^{[-1,0]}(\proj \Lambda)$ is equivalent to that of its class in the Grothendieck group~$K_0(K^{[-1,0]}(\proj \Lambda))$, where~$K^{[-1,0]}(\proj \Lambda)$ is viewed as an extriangulated category (see \cref{prop::2kbproj-is-extriangulated}).
 In this Grothendieck group, we have that~$[E] = [E'] = [X]+[Y]$.
@@
 \begin{corollary}\label{coro::exchangeablePairsNKC}
- Point~(ii) of Proposition~\ref{prop:exchangeablePairsNKC} holds.
+ Point~(ii) of \cref{prop:exchangeablePairsNKC} holds.
 \end{corollary}
 \begin{proof}
- Let~$\omega$ and~$\omega'$ be in facets~$F$ and~$F'$ as in the statement of Proposition~\ref{prop:exchangeablePairsNKC}.
+ Let~$\omega$ and~$\omega'$ be in facets~$F$ and~$F'$ as in the statement of \cref{prop:exchangeablePairsNKC}.
 For every walk~$\omega''$, let~$P(\omega'')$ be the object of~$K^{[-1,0]}(\proj \Lambda)$ corresponding to~$\omega''$.
@@
  \]
- Assume that there are other facets~$F_0$ and~$F_0'$ also satisfying the hypotheses of Proposition~\ref{prop:exchangeablePairsNKC}.
-Then they give rise to walks~$\mu'$ and~$\nu'$ and an exchange conflation
+ Assume that there are other facets~$F_0$ and~$F_0'$ also satisfying the hypotheses of \cref{prop:exchangeablePairsNKC}. Then they give rise to walks~$\mu'$ and~$\nu'$ and an exchange conflation
  \[
@@
  \]
- By Proposition~\ref{prop::exchange conflations are unique}, we get that~$P(\mu)\oplus P(\nu)$ and~$P(\mu')\oplus P(\nu')$ are isomorphic, and that the mutation conflations either both have the form~$P(\omega) \infl P(\mu) \oplus P(\nu) \defl P(\omega')$ or both have the form~$P(\omega') \infl P(\mu) \oplus P(\nu) \defl P(\omega)$.
+ By \cref{prop::exchange conflations are unique}, we get that~$P(\mu)\oplus P(\nu)$ and~$P(\mu')\oplus P(\nu')$ are isomorphic, and that the mutation conflations either both have the form~$P(\omega) \infl P(\mu) \oplus P(\nu) \defl P(\omega')$ or both have the form~$P(\omega') \infl P(\mu) \oplus P(\nu) \defl P(\omega)$.
 Without loss of generality, assume that they have the first form.
@@
 They determine common substrings of~$\omega$ and~$\mu$ and of~$\omega$ and~$\nu$, which in turn determine~$\sigma$.
-Point (ii) of Proposition~\ref{prop:exchangeablePairsNKC} is proved.
+Point (ii) of \cref{prop:exchangeablePairsNKC} is proved.
 \end{proof}
@@
 Assume that~$\Lambda$ is a finite-dimensional brick algebra which is representation-finite.
-Then~\cite[Thm.~6.2]{DemonetIyamaJasso} implies that the assumptions of Theorem~\ref{theo::brick-algebra-condition} are satisfied.
+Then~\cite[Thm.~6.2]{DemonetIyamaJasso} implies that the assumptions of \cref{theo::brick-algebra-condition} are satisfied.
 \end{remark}
@@
 
-Note also that Lemma~\ref{lemm::AR-conflations-and-sequences} implies that~$F\tau X$ is isomorphic to $\tau M$.
+Note also that \cref{lemm::AR-conflations-and-sequences} implies that~$F\tau X$ is isomorphic to $\tau M$.
 
@@
 \begin{proof}
-By Lemma~\ref{lemm::AR-conflations-and-sequences}, \emph{(2)} follows from \emph{(1)}.
+By \cref{lemm::AR-conflations-and-sequences}, \emph{(2)} follows from \emph{(1)}.
 Let us prove \emph{(1)}.
@@
 where the vertical maps are surjective.
-Since~$\Lambda$ is rigid and~$Y$ is two-term, we can apply~\cite[Prop.~6.2]{IyamaYoshino} to the triangulated category~$K^b(\proj\Lambda)$ (or Proposition~\ref{prop::KRextricat} to the extriangulated~$K^{[-1,0]}(\proj\Lambda)$).
+Since~$\Lambda$ is rigid and~$Y$ is two-term, we can apply~\cite[Prop.~6.2]{IyamaYoshino} to the triangulated category~$K^b(\proj\Lambda)$ (or \cref{prop::KRextricat} to the extriangulated~$K^{[-1,0]}(\proj\Lambda)$).
 As a consequence, the right-most vertical map is bijective.
@@
 
-\begin{proof}[Proof of Theorem~\ref{theo::brick-algebra-condition}]
- The theorem follows from the slightly more general statements of Lemma~\ref{lemm::then-AR-seq-are-mutation},~\ref{lemm::if AR are mutations} and Lemma~\ref{lemm::initial meshes}.
+\begin{proof}[Proof of \cref{theo::brick-algebra-condition}]
+ The theorem follows from the slightly more general statements of \cref{lemm::then-AR-seq-are-mutation,lemm::if AR are mutations,lemm::initial meshes}.
 \end{proof}
@@
 
-We now describe a setup satisfying the assumptions of Section~\ref{setting::extricat} that, at the same time, subsumes all examples given so far, while being easily checked in practice.\yann{A reformuler...}
+We now describe a setup satisfying the assumptions of \cref{setting::extricat} that, at the same time, subsumes all examples given so far, while being easily checked in practice.\yann{A reformuler...}
 
@@
 \begin{proof}
- This follows from the proof of Lemma~\ref{lemma::index kzero extricat}.
+ This follows from the proof of \cref{lemma::index kzero extricat}.
 \end{proof}
@@
 Assume that, for any~$T\in\tc$, there is an~$\mathfrak{s}$-conflation~$T\infl 0\defl X_T$ in~$\ec$ with~$X_T\in\tc^\perp$.
-Then the extriangulated category~$\cat$ satisfies the assumptions (1) to (3) of Section~\ref{setting::extricat}.
+Then the extriangulated category~$\cat$ satisfies the assumptions (1) to (3) of \cref{setting::extricat}.
 \end{proposition}
@@
 For any~$T\in\tc$ the existence of an extriangle~$0\infl T\defl T\overset{0}{\dashrightarrow}$ shows that~$\tc$ is a full subcategory of~$\cat$.
-By Lemma~\ref{lemma:: prT is extriangulated}, the category~$\cat$ is extriangulated and, by definition of this extriangulated structure, the objects in~$\tc$ are projective in~$\cat$.
+By \cref{lemma:: prT is extriangulated}, the category~$\cat$ is extriangulated and, by definition of this extriangulated structure, the objects in~$\tc$ are projective in~$\cat$.
 Assumption (3) is satisfied by the definition of~$\cat$, and assumption (2) is equivalent to that of the proposition.
@@
 \begin{remark}
- The categories considered in Sections~\ref{sect::2CYTriangulated},~\ref{sect::2CYexact} and~\ref{sect::Kbproj} all fall into the setting of Proposition~\ref{prop::prT}.
+ The categories considered in \cref{sect::2CYTriangulated,sect::2CYexact,sect::Kbproj} all fall into the setting of \cref{prop::prT}.
 \end{remark}
@@
  \]
- The conditions of Theorem~\ref{theo::brick-algebra-condition} are satisfied.
+ The conditions of \cref{theo::brick-algebra-condition} are satisfied.
 
@@
 
-One can check directly that the condition of Theorem~\ref{theo::brick-algebra-condition} is not satisfied.
+One can check directly that the condition of \cref{theo::brick-algebra-condition} is not satisfied.
 For example, the module~$\bsm2\\1\esm$ is~$\tau$-rigid since~$\tau(\bsm2\\1\esm) = \bsm3\\1\esm$, while~$\Hom{\Lambda}\left(\bsm2\\1\esm,\tau^2(\bsm2\\1\esm)\right) = \Hom{\Lambda}(\bsm2\\1\esm,\bsm1\\2\esm) \ne 0$.
@@
 % \begin{example}
-%  Consider the preprojective algebra of type~$A_3$, as in Example~\ref{exam::preprojective silting objects}.
+%  Consider the preprojective algebra of type~$A_3$, as in \cref{exam::preprojective silting objects}.
 It is a self-injective algebra, so its module category is a Frobenius category.

### 2019-06-13 thirdPaper/draft/typeConeAssociahedra.tex
Changed 2.20 and 2.25.

@@
 \label{lem:bijectionMeshMutations}
-There is precisely one non-initial mesh directed by each positive $\b{c}$-vector of the cluster algebra~$\principalClusterAlgebra[\B_\circ^\vee]$. Therefore~$|\principalVariables| = |\meshes| + n$.
+We have that~$|\principalVariables| = |\meshes| + n$.
 \end{lemma}
+\begin{proof}
+ We postpone the proof until \pg{ref to later}.
+\end{proof}
 
@@
 
-We also obtain from \cref{thm:extremalExchangeablePairsCA} the following surprising property.
-
-\begin{corollary}
+As a follow-up to \cref{thm:extremalExchangeablePairsCA}, we conjecture the following surprising property.
+
+\begin{conjecture}
 Any positive dual $\b{c}$-vector supports exactly one extremal exchangeable pair.
-\end{corollary}
+\end{conjecture}
 

### 2019-06-13 thirdPaper/draft/typeConeAssociahedra.tex
typographic changes

--- 2019-06-13 thirdPaper/draft/typeConeAssociahedra.tex
@@
 
-The associahedron is a ``mythical polytope'' \cite{Haiman} whose facial structure encodes Catalan families: its vertices correspond to parenthesizations of a non-associative product, triangulations of a convex polygon, or binary trees; its edges correspond to applications of the associativity rule, diagonal flips, or edge rotations; and in general its faces correspond to partial parenthesizations, diagonal dissections, or Schr\"oder trees.
+The associahedron is a ``mythical polytope''~\cite{Haiman} whose facial structure encodes Catalan families: its vertices correspond to parenthesizations of a non-associative product, triangulations of a convex polygon, or binary trees; its edges correspond to applications of the associativity rule, diagonal flips, or edge rotations; and in general its faces correspond to partial parenthesizations, diagonal dissections, or Schr\"oder trees.
 Its combinatorial and topological structure was introduced in early works of D.~Tamari~\cite{Tamari} and J.~Stasheff~\cite{Stasheff}, and a first $3$-dimensional polytopal model was realized by J.~Milnor for the PhD defense of J.~Stasheff.
@@
 This provides natural Minkowski summands for all polytopal realizations of~$\Fan$: the rays of the closed type cone.
-These correspond to indecomposable polytopes, see~\cite{Meyer} or \cite{McMullen-typeCone}.
+These correspond to indecomposable polytopes, see~\cite{Meyer} or~\cite{McMullen-typeCone}.
 A polytope $P \subseteq \R^n$ is called \defn{indecomposable} if all its weak Minkowski summands are of the form $\lambda P+t$ for some $\lambda \ge 0$ and $t \in \R^n$.
@@
 In view of \cref{prop:exchangeablePairsNKC}, it is tempting to look for a characterization of the exchangeable pairs~$\omega, \omega'$ using the kisses between~$\omega$ and~$\omega'$.
-This question was discussed in \cite[Sect.~9]{BrustleDouvilleMousavandThomasYildirim}.
+This question was discussed in~\cite[Sect.~9]{BrustleDouvilleMousavandThomasYildirim}.
 However, as illustrated for instance in the non-kissing complex of \cref{fig:nonkissingFans}\,(right),
@@
 
-Since this precisely coincides with the description of the flip in the non-kissing complex (see \cref{prop:exchangeablePairsNKC}\,(i) or \cite[Prop.~2.31]{PaluPilaudPlamondon-nonkissing} for an alternative presentation), we conclude that the flip of~$\omega$ in~$F$ creates a facet~$F'$ containing~$\omega'$.
+Since this precisely coincides with the description of the flip in the non-kissing complex (see \cref{prop:exchangeablePairsNKC}\,(i) or~\cite[Prop.~2.31]{PaluPilaudPlamondon-nonkissing} for an alternative presentation), we conclude that the flip of~$\omega$ in~$F$ creates a facet~$F'$ containing~$\omega'$.
 Therefore, $\omega$ and~$\omega'$ are exchangeable with distinguished substring~$\sigma$.
@@
 
-Before we can prove \cref{theo::relations-g-vecteurs}, we need to recall the following results and definition from \cite{DehyKeller,Palu}.
+Before we can prove \cref{theo::relations-g-vecteurs}, we need to recall the following results and definition from~\cite{DehyKeller,Palu}.
 
@@
 with~$T_1^X$ and~$T_0^X$ in~$\add(T)$.
-
 \end{proposition}
@@
 Therefore, if~$(\susp T)\cat(\susp^{-1} X, \susp X)$ is non-zero, then it contains the one-dimensional socle of~$\cat(\susp^{-1} X, \susp X)$, and thus contains~$h$.
- By \cite{Palu},
+By~\cite{Palu},
 \[
@@
 \[
-  \langle \ell_A, B \rangle = \begin{cases}
+\langle \ell_A, B \rangle = 
+\begin{cases}
 0 & \textrm{if~$A\ncong B$;} \\
@@
 \[
-  \langle A, r_B \rangle = \begin{cases}
+\langle A, r_B \rangle =
+\begin{cases}
 0 & \textrm{if~$A\ncong B$;} \\
@@
 \end{corollary}
+
 \begin{proof}
@@
 
-%The cluster category also contains enough information to detect positive mutations.
 The following definition is a cluster-tilting version of the positive mutation for~$\tau$-tilting modules, or for~$2$-term silting complexes.
@@
 
-\vspace{.4cm}
-\noindent {\bf Setting for \cref{sect::prelim on extricats}}
+\para{Setting for Section~\ref{sect::prelim on extricats}}
 In that section, we let~$\cat$ be an extriangulated category with a fixed full additive \yann{additive contains strictly full + stable under taking summands} subcategory~$\tc$ satisfying the following three properties:
@@
 
-\noindent {\bf Setting for \cref{sect::Statment extricats}}
+\para{Setting for Section~\ref{sect::Statment extricats}}
 In that section, we keep the previous setting, but assume moreover that~$\cat$ is Krull--Schmidt, $\field$-linear, Ext-finite, and has Auslander--Reiten--Serre duality, and that the subcategory~$\tc$ is of the form~$\add T$, where~$T=T_1\oplus\cdots\oplus T_n$ is a basic object.
 
-\begin{remark}\label{remark::examples extricats}
+\begin{remark}
+\label{remark::examples extricats}
 Examples of categories satisfying the properties above are
@@
 
-\begin{lemma}\label{lemma::finitely presented}
+\begin{lemma}
+\label{lemma::finitely presented}
 For any~$X\in\cat$, the functor~$FX$ is finitely presented.
@@
 
-\begin{definition}\label{DefSqEquiv}
+\begin{definition}
+\label{DefSqEquiv}
 Let~$X,Z\in\cat$ be any two objects. Two sequences of morphisms in~$\cat$
@@
 
-\begin{proposition}\label{proposition::extricat long exact sequences}\emph{(}\cite[Props.~3.3~\&~3.11]{NakaokaPalu}\emph{)}
+\begin{proposition}[{\cite[Props.~3.3~\&~3.11]{NakaokaPalu}}]
+\label{proposition::extricat long exact sequences}
 Assume that $(\cat,\mathbb{E},\mathfrak{s})$ is an extriangulated category, and let $X\xrightarrow{x}Y\xrightarrow{y}Z\overset{\delta}{\dashrightarrow}$ be an extriangle.
@@
 
-\begin{proposition}\emph{(}\cite[Prop.~2.5]{IyamaNakaokaPalu}\emph{)}
+\begin{proposition}[{\cite[Prop.~2.5]{IyamaNakaokaPalu}}]
 For any non-split $\mathbb{E}$-extension $\delta\in\mathbb{E}(Z,X)$, the following holds.
@@
 
-\begin{proposition}\emph{(}\cite[Prop.~8.1]{IyamaNakaokaPalu}\emph{)}
+\begin{proposition}[{\cite[Prop.~8.1]{IyamaNakaokaPalu}}]
 Let~$\Lambda$ be an Artin algebra and let~$K^{[-1,0]}(\proj\Lambda)$ be the full subcategory of the homotopy category~$K^b(\proj\Lambda)$ consisting of complexes concentrated in degrees~$-1$ and~$0$ (using cohomological conventions).
@@
 
-\begin{corollary}\label{corollary::Sigma T injectives}
+\begin{corollary}
+\label{corollary::Sigma T injectives}
 The objects in~$\susp\tc$ are precisely the injective objects in~$\cat$.
@@
 
-\begin{definition}\label{defn::mutation conflation}
+\begin{definition}
+\label{defn::mutation conflation}
 A conflation $X\infl E\defl Y$ of~$K^{[-1,0]}(\proj \Lambda)$ is called a \defn{mutation conflation} if there are basic, two-term, silting objects $X\oplus R$, $Y\oplus R$, with~$X$ and~$Y$ indecomposable, such that the inflation $X\infl E$ is a left ($\add R$)-approximation (i.e.
@@
 \smallskip
-
 We now prove~(2).
 Let~$X\infl E\defl Y$ and~$X\infl E'\defl Y$ be two mutation conflations.
-By~\cite[Theorem 6.5]{DemonetIyamaJasso} (based on~\cite[Theorem 2.3]{DehyKeller}), rigid objects in~$K^{[-1,0]}(\proj \Lambda)$ are determined by their~$\b{g}$-vector.
+By~\cite[Thm.~6.5]{DemonetIyamaJasso} (based on~\cite[Thm~2.3]{DehyKeller}), rigid objects in~$K^{[-1,0]}(\proj \Lambda)$ are determined by their~$\b{g}$-vector.
 The datum of the~$\b{g}$-vector of an object of~$K^{[-1,0]}(\proj \Lambda)$ is equivalent to that of its class in the Grothendieck group~$K_0(K^{[-1,0]}(\proj \Lambda))$, where~$K^{[-1,0]}(\proj \Lambda)$ is viewed as an extriangulated category (see \cref{prop::2kbproj-is-extriangulated}).
@@
 
-\begin{corollary}\label{coro::exchangeablePairsNKC}
+\begin{corollary}
+\label{coro::exchangeablePairsNKC}
  Point~(ii) of \cref{prop:exchangeablePairsNKC} holds.
 \end{corollary}
+
 \begin{proof}
@@
 \]
-
 \end{lemma}
@@
 
-\begin{lemma}\label{lemm::if AR are mutations}
+\begin{lemma}
+\label{lemm::if AR are mutations}
 Let~$\Lambda$ be an Artin algebra, and let~$Y\infl E\defl X$ be a conflation in~$K^{[-1,0]}(\proj\Lambda)$. Then:
@@
 
-\begin{lemma}\label{lemm::initial meshes}
+\begin{lemma}
+\label{lemm::initial meshes}
 Let~$\Lambda$ be an Artin algebra whose indecomposable injective modules are~$\tau$-rigid, and let~$P$ be an indecomposable projective~$\Lambda$-module.
@@
 
-% \begin{corollary}
-%  Generalised cluster categories with infinite dimensional Hom-spaces ?
-% \end{corollary}
-
 %%%%%%%%%%%
@@
 \subsubsection{Associative algebras}
+
 \begin{example}[A gentle algebra]
@@
 The conditions of \cref{theo::brick-algebra-condition} are satisfied.
-
 \end{example}

### 2019-06-13 thirdPaper/draft/typeConeAssociahedra.tex
typographic changes

@@
 \begin{corollary}
-Let $\b{h}^{(1)},\dots, \b{h}^{(N-n)}\in \ctypeCone(\Fan)$ form a basis of the left kernel of~$\b{G}$.
+Let $\b{h}^{(1)},\dots, \b{h}^{(N-n)} \in \ctypeCone(\Fan)$ form a basis of the left kernel of~$\b{G}$.
 Then for any~$\b{h} \in \ctypeCone(\Fan)$, the polytope~$P_\b{h}$ has a unique representation (up to translation) as a signed Minkowski sum of dilates of $P_{\b{h}^{(1)}}, \dots, P_{\b{h}^{(N-n)}}$.
@@
 \begin{corollary}
-If the type cone~$\typeCone(\Fan)$ of $\Fan$ is simplicial, then every $P_\b{h}$ with $\b{h}\in \typeCone(\Fan)$ (resp.~with $\b{h}\in \ctypeCone(\Fan)$) has a unique representation, up to translation, as a Minkowski sum of positive (resp.~non-negative) dilates of the $N-n$ indecomposable polytopes $P_{\b{h}^{(1)}}, \dots, P_{\b{h}^{(N-n)}}$ arising from the rays~$\b{h}^{(1)}, \dots, \b{h}^{(N-n)}$ of $\ctypeCone(\Fan)$.
+If the type cone~$\typeCone(\Fan)$ of $\Fan$ is simplicial, then every $P_\b{h}$ with $\b{h} \in \typeCone(\Fan)$ (resp.~with $\b{h} \in \ctypeCone(\Fan)$) has a unique representation, up to translation, as a Minkowski sum of positive (resp.~non-negative) dilates of the $N-n$ indecomposable polytopes $P_{\b{h}^{(1)}}, \dots, P_{\b{h}^{(N-n)}}$ arising from the rays~$\b{h}^{(1)}, \dots, \b{h}^{(N-n)}$ of $\ctypeCone(\Fan)$.
 \end{corollary}
@@
 \[
-\textrm{for any object~$X$,} \quad \cat(T, \susp X) = 0 \quad \textrm{if and only if} \quad X\in \add(T),
+\textrm{for any object~$X$,} \quad \cat(T, \susp X) = 0 \quad \textrm{if and only if} \quad X \in \add(T),
 \]
@@
 \]
-with~$h\in (\susp T)$. Denote by~$\b{g}:\Ksp(\cat) \to K_0(\cat ; T)$ the canonical projection.
+with~$h \in (\susp T)$. Denote by~$\b{g}:\Ksp(\cat) \to K_0(\cat ; T)$ the canonical projection.
 \end{enumerate}
@@
 \[
-L \eqdef \bigset{\ell_X}{X\in \ind(\cat) \ssm \add(\susp T)}
+L \eqdef \bigset{\ell_X}{X \in \ind(\cat) \ssm \add(\susp T)}
 \]
 generates the kernel of~$\b{g}:\Ksp(\cat) \to K_0(\cat ; T)$. 
-In this case, the set~$L$ is a basis of the kernel of~$\b{g}$, and for any $x\in \ker(\b{g})$, we have that
-\[
-x= \sum_{A\in \ind(\cat) \ssm \add(\susp T)} \frac{\langle x, A \rangle}{\langle \ell_A, A \rangle} \ell_A.
+In this case, the set~$L$ is a basis of the kernel of~$\b{g}$, and for any $x \in \ker(\b{g})$, we have that
+\[
+x= \sum_{A \in \ind(\cat) \ssm \add(\susp T)} \frac{\langle x, A \rangle}{\langle \ell_A, A \rangle} \ell_A.
 \]
@@
 Assume that~$\ind(\cat)$ is finite.
-Let~$X\xrightarrow{} E \xrightarrow{} Y \xrightarrow{h} \susp X$ be a triangle with~$h\in (\susp T)$.
-Then the element~$x=[X]+[Y]-[E]$ of the kernel of~$\b{g}$ is a non-negative linear combination of the~$\ell_A$, with~$A\in \ind(\cat)\ssm \add(\susp T)$.
+Let~$X\xrightarrow{} E \xrightarrow{} Y \xrightarrow{h} \susp X$ be a triangle with~$h \in (\susp T)$.
+Then the element~$x=[X]+[Y]-[E]$ of the kernel of~$\b{g}$ is a non-negative linear combination of the~$\ell_A$, with~$A \in \ind(\cat)\ssm \add(\susp T)$.
 \end{corollary}
@@
 \begin{proof}
-We know that~$x=\sum_{A\in \ind(\cat) \ssm \add(\susp T)} \frac{\langle x, [A] \rangle}{\langle \ell_A, [A] \rangle} \ell_A$; since~$\langle \ell_A, [A] \rangle$ is positive by \cref{lemm::bilinear-form}, we only need to show that each~$\langle x, [A] \rangle$ is non-negative.
+We know that~$x=\sum_{A \in \ind(\cat) \ssm \add(\susp T)} \frac{\langle x, [A] \rangle}{\langle \ell_A, [A] \rangle} \ell_A$; since~$\langle \ell_A, [A] \rangle$ is positive by \cref{lemm::bilinear-form}, we only need to show that each~$\langle x, [A] \rangle$ is non-negative.
 The functor~$F=\cat(T,-)$ induces an exact sequence
@@
 \[
-\ind_T(X) \eqdef [T_0^X] - [T_1^X] \in \Ksp(\add(T)).
+\ind_T(X) \eqdef [T_0^X] - [T_1^X] \in \Ksp \big( \add(T) \big).
 \]
@@
 \]
-if and only if~$h\in (\susp T)$.
+if and only if~$h \in (\susp T)$.
 \end{proposition}
@@
 \label{coro::grothendieck-g-vectors}
-There is an isomorphism~$\phi:K_0(\cat ; T) \to \Ksp(\add(T))$ such that~$\ind_T = \phi\circ \b{g}$. In particular,~$K_0(\cat ; T)$ is a free abelian group generated by the~$[T_i]$.
+There is an isomorphism~$\phi:K_0(\cat ; T) \to \Ksp \big( \add(T) \big)$ such that~$\ind_T = \phi\circ \b{g}$. In particular,~$K_0(\cat ; T)$ is a free abelian group generated by the~$[T_i]$.
 \end{corollary}
@@
 \label{lemm::almost-split}
-Let~$X\xrightarrow{} Y \xrightarrow{} \susp^{-1} X \xrightarrow{h} \susp X$ be an almost-split triangle. Then~$X\notin \add(\susp T)$ if and only if~$h\in (\susp T)$.
+Let~$X\xrightarrow{} Y \xrightarrow{} \susp^{-1} X \xrightarrow{h} \susp X$ be an almost-split triangle. Then~$X\notin \add(\susp T)$ if and only if~$h \in (\susp T)$.
 \end{lemma}
@@
 \begin{proof}
-If~$X\in \add(\susp T)$, then~$h$ cannot be in~$(\susp T)$, otherwise it would be zero since~$\cat(T, \susp T) =0$.
+If~$X \in \add(\susp T)$, then~$h$ cannot be in~$(\susp T)$, otherwise it would be zero since~$\cat(T, \susp T) =0$.
 
@@
 Thus the right-hand side is non-zero, and so neither is the left-hand side.
-By the above, this implies that~$h\in (\susp T)\cat(\susp^{-1} X, \susp X)$, which finishes the proof.
+By the above, this implies that~$h \in (\susp T)\cat(\susp^{-1} X, \susp X)$, which finishes the proof.
 \end{proof}
@@
 \label{lemm::coefficients}
-Let~$x\in \Ksp(\cat)$, and write~\[x=\sum_{A\in \ind(\cat)} \lambda_A [A].\]  Then for any~$A\in\ind(\cat) \ssm \add(\susp T)$, we have that
+Let~$x \in \Ksp(\cat)$, and write~\[x=\sum_{A \in \ind(\cat)} \lambda_A [A].\]  Then for any~$A\in\ind(\cat) \ssm \add(\susp T)$, we have that
 \[
@@
 \begin{proof}
-Let~$B\in \ind(\cat) \ssm \add(\susp T)$. Applying \cref{lemm::bilinear-form}, we get that
-\[
-\langle \ell_B, x \rangle = \langle \ell_B, \sum_{A\in \ind(\cat)} \lambda_A [A] \rangle = \sum_{A\in \ind{\cat}} \lambda_A \langle \ell_B, [A] \rangle = \lambda_B \langle \ell_B, [B] \rangle.
+Let~$B \in \ind(\cat) \ssm \add(\susp T)$. Applying \cref{lemm::bilinear-form}, we get that
+\[
+\langle \ell_B, x \rangle = \langle \ell_B, \sum_{A \in \ind(\cat)} \lambda_A [A] \rangle = \sum_{A \in \ind{\cat}} \lambda_A \langle \ell_B, [A] \rangle = \lambda_B \langle \ell_B, [B] \rangle.
 \]
@@
 \label{lemm::test-susp-T}
-Let~$x\in \Ksp(\cat)$. Then the following are equivalent.
+Let~$x \in \Ksp(\cat)$. Then the following are equivalent.
 \begin{enumerate}
-\item $x\in \Ksp(\add(\susp T))$;
-\item $\langle x, [A]\rangle = 0$ for all~$A\in \ind(\cat)$;
-\item $\langle [A], x \rangle = 0$ for all~$A\in \ind(\cat)$.
+\item $x \in \Ksp \big( \add(\susp T) \big)$;
+\item $\langle x, [A]\rangle = 0$ for all~$A \in \ind(\cat)$;
+\item $\langle [A], x \rangle = 0$ for all~$A \in \ind(\cat)$.
 \end{enumerate}
@@
 \[
-x = \sum_{A\in \ind(\cat) \ssm \add(\susp T)} \frac{\langle \ell_A, x \rangle}{\langle \ell_A, A \rangle}[A] + \sum_{i=1}^n \lambda_{\susp T_i} [\susp T_i] = \sum_{i=1}^n \lambda_{\susp T_i} [\susp T_i].
-\]
-Thus~$x\in \Ksp(\add(\susp T))$, and (1) holds.
+x = \sum_{A \in \ind(\cat) \ssm \add(\susp T)} \frac{\langle \ell_A, x \rangle}{\langle \ell_A, A \rangle}[A] + \sum_{i=1}^n \lambda_{\susp T_i} [\susp T_i] = \sum_{i=1}^n \lambda_{\susp T_i} [\susp T_i].
+\]
+Thus~$x \in \Ksp \big( \add(\susp T) \big)$, and (1) holds.
 
@@
 \begin{enumerate}
-\item The set~$\set{[\ell_A]}{A\in \ind(\cat) \ssm \add(\susp T)} \cup \set{[\susp T_i]}{i=1, \dots, n}$ is free in~$\Ksp(\cat)$.
-\item The set~$\set{[r_A]}{A\in \ind(\cat) \ssm \add(\susp T)} \cup \set{[\susp T_i]}{i=1, \dots, n}$ is free in~$\Ksp(\cat)$.
+\item The set~$\set{[\ell_A]}{A \in \ind(\cat) \ssm \add(\susp T)} \cup \set{[\susp T_i]}{i=1, \dots, n}$ is free in~$\Ksp(\cat)$.
+\item The set~$\set{[r_A]}{A \in \ind(\cat) \ssm \add(\susp T)} \cup \set{[\susp T_i]}{i=1, \dots, n}$ is free in~$\Ksp(\cat)$.
 \end{enumerate}
@@
 \[
-x= \sum_{A\in \ind(\cat) \ssm \add(\susp T)} \lambda_A \ell_A + \sum_{i=1}^n \lambda_i [\susp T_i] = 0.
+x= \sum_{A \in \ind(\cat) \ssm \add(\susp T)} \lambda_A \ell_A + \sum_{i=1}^n \lambda_i [\susp T_i] = 0.
 \]
@@
 \]
-But the~$[\susp T_i]$ are linearly independent in~$\Ksp(\cat)$. Thus~$\lambda_i = 0$ for all~$i\in \{1, \ldots, n\}$. This finishes the proof.
+But the~$[\susp T_i]$ are linearly independent in~$\Ksp(\cat)$. Thus~$\lambda_i = 0$ for all~$i \in \{1, \ldots, n\}$. This finishes the proof.
 \end{proof}
@@
 Assume that~$\ind(\cat)$ is finite.
-Then the set~$\set{[\ell_A]}{A\in \ind(\cat) \ssm \add(\susp T)}$ is a basis of the kernel of~$\b{g} : \Ksp(\cat) \to K_0(\cat ; T)$.
-Moreover, for any~$x\in \ker \b{g}$, we have that
-\[
-x= \sum_{A\in \ind(\cat) \ssm \add(\susp T)} \frac{\langle x, A \rangle}{\langle \ell_A, A \rangle} \ell_A.
+Then the set~$\set{[\ell_A]}{A \in \ind(\cat) \ssm \add(\susp T)}$ is a basis of the kernel of~$\b{g} : \Ksp(\cat) \to K_0(\cat ; T)$.
+Moreover, for any~$x \in \ker \b{g}$, we have that
+\[
+x= \sum_{A \in \ind(\cat) \ssm \add(\susp T)} \frac{\langle x, A \rangle}{\langle \ell_A, A \rangle} \ell_A.
 \]
@@
 \begin{proof}
-By \cref{prop::free-set}, the set is free. Let~$x\in \ker \b{g}$. Consider the element
-\[
-z = x- \sum_{A\in \ind(\cat) \ssm \add(\susp T)} \frac{\langle x, A \rangle}{\langle \ell_A, A \rangle} \ell_A.
-\]
-Then for any~$B\in \ind{\cat}$, we have that
-\[
-\langle  z, [B] \rangle = \Big\langle x- \sum_{A\in \ind(\cat) \ssm \add(\susp T)} \frac{\langle x, A \rangle}{\langle \ell_A, A \rangle} \ell_A, [B] \Big\rangle = \langle x, [B] \rangle - \langle x, [B] \rangle = 0,
+By \cref{prop::free-set}, the set is free. Let~$x \in \ker \b{g}$. Consider the element
+\[
+z = x- \sum_{A \in \ind(\cat) \ssm \add(\susp T)} \frac{\langle x, A \rangle}{\langle \ell_A, A \rangle} \ell_A.
+\]
+Then for any~$B \in \ind{\cat}$, we have that
+\[
+\langle  z, [B] \rangle = \Big\langle x- \sum_{A \in \ind(\cat) \ssm \add(\susp T)} \frac{\langle x, A \rangle}{\langle \ell_A, A \rangle} \ell_A, [B] \Big\rangle = \langle x, [B] \rangle - \langle x, [B] \rangle = 0,
 \]
 where the second equality is obtained by using \cref{lemm::bilinear-form}.
-By \cref{lemm::test-susp-T}, this implies that~$z\in \Ksp(\add(\susp T))$.
-Since~$z\in \ker(\b{g})$ and since~$\b{g}$ is injective on~$\Ksp(\add (\susp T))$ by \cref{coro::grothendieck-g-vectors}, we get that~$z=0$.
+By \cref{lemm::test-susp-T}, this implies that~$z \in \Ksp \big( \add(\susp T) \big)$.
+Since~$z \in \ker(\b{g})$ and since~$\b{g}$ is injective on~$\Ksp \big( \add (\susp T) \big)$ by \cref{coro::grothendieck-g-vectors}, we get that~$z=0$.
 This finishes the proof.
@@
 \[
-\set{[\ell_A]}{A\in \ind(\cat) \ssm \add(\susp T)} \cup \set{[\susp T_i]}{i=1, \ldots, n}
+\set{[\ell_A]}{A \in \ind(\cat) \ssm \add(\susp T)} \cup \set{[\susp T_i]}{i=1, \ldots, n}
 \]
@@
 \begin{proof}
-By \cref{prop::free-set}, the set is free. It suffices to prove that it generates~$\Ksp(\cat)$. Let~$x\in \Ksp(\cat)$. Consider
-\[
-z = x - \sum_{A\in \ind{\cat}} \frac{\langle x, A \rangle}{\langle \ell_A, A\rangle} \ell_A.
-\]
-Then for any~$B\in \ind(\cat)$, we have that~$\langle z, [B] \rangle = 0$. By \cref{lemm::test-susp-T}, this implies that~$z\in \Ksp(\add(\susp T))$, and finishes the proof.
+By \cref{prop::free-set}, the set is free. It suffices to prove that it generates~$\Ksp(\cat)$. Let~${x \in \Ksp(\cat)}$. Consider
+\[
+z = x - \sum_{A \in \ind{\cat}} \frac{\langle x, A \rangle}{\langle \ell_A, A\rangle} \ell_A.
+\]
+Then for any~$B \in \ind(\cat)$, we have that~$\langle z, [B] \rangle = 0$. By \cref{lemm::test-susp-T}, this implies that~${z \in \Ksp \big( \add(\susp T) \big)}$, and finishes the proof.
 \end{proof}
@@
 \begin{proposition}
-Assume that the set~$\set{[\ell_A]}{A\in \ind(\cat) \ssm \add(\susp T)}$ is a basis of the kernel of~$\b{g}$. Then~$\ind(\cat)$ is finite.
+Assume that the set~$\set{[\ell_A]}{A \in \ind(\cat) \ssm \add(\susp T)}$ is a basis of the kernel of~$\b{g}$. Then~$\ind(\cat)$ is finite.
 \end{proposition}
@@
 \begin{proof}
-Let~$x\in \ker \b{g}$, and write~$x = \sum_{[A]\in \ind(\cat)} \lambda_A[A]$, where the sum has finite support. For any~$B$ not in the support of the sum, we have that~$\langle x, [B] \rangle = 0$.
-
-Now,~$[T]+[\susp T]$ is in the kernel of~$\b{g}$, but~$\langle [T] + [\susp T], [B] \rangle = \langle [T], [B] \rangle = 0$ if and only if~$B\in \add(\susp T)$. Thus~$\ind(\cat)$ has to be finite.
+Let~$x \in \ker \b{g}$, and write~$x = \sum_{[A] \in \ind(\cat)} \lambda_A[A]$, where the sum has finite support. For any~$B$ not in the support of the sum, we have that~$\langle x, [B] \rangle = 0$.
+
+Now,~$[T]+[\susp T]$ is in the kernel of~$\b{g}$, but~$\langle [T] + [\susp T], [B] \rangle = \langle [T], [B] \rangle = 0$ if and only if~$B \in \add(\susp T)$. Thus~$\ind(\cat)$ has to be finite.
 \end{proof}
@@
 \begin{itemize}
-\item[(i)] \emph{(}\cite[Prop.~3.2]{BuanMarshReinekeReitenTodorov} and~\cite[]{???} \emph{)} For any~$X,Y\in \ind(\cat)$, $\CC(X)$ and~$\CC(Y)$ are compatible if and only if~$\cat(X, \susp Y) = 0$.
-\item[(ii)] \emph{(}\cite[Prop.~4.3]{FuKeller} and \emph{)} For any~$X\in \ind(\cat)$, the~$\b{g}$-vector of~$\CC(X)$ is~$\b{g}([X])$, where we identify~$\Z^n$ and~$K_0(\cat ; T)$ via the isomorphism sending~$(a_1, \ldots, a_n)$ to~$\sum_{i=1}^n a_i [T_i]$.
-\item[(iii)] \emph{(}\cite[Thm.~7.5]{BuanMarshReinekeReitenTodorov} and~\cite[]{???—} \emph{)} For any~$X,Y\in \ind(\cat)$, $\CC(X)$ and~$\CC(Y)$ are exchangeable if and only if~$\dim_{\field_X}\cat(X, \susp Y) = \dim_{\field_Y}\cat(X, \susp Y) = 1$.
+\item[(i)] \emph{(}\cite[Prop.~3.2]{BuanMarshReinekeReitenTodorov} and~\cite[]{???} \emph{)} For any~$X,Y \in \ind(\cat)$, $\CC(X)$ and~$\CC(Y)$ are compatible if and only if~$\cat(X, \susp Y) = 0$.
+\item[(ii)] \emph{(}\cite[Prop.~4.3]{FuKeller} and \emph{)} For any~$X \in \ind(\cat)$, the~$\b{g}$-vector of~$\CC(X)$ is~$\b{g}([X])$, where we identify~$\Z^n$ and~$K_0(\cat ; T)$ via the isomorphism sending~$(a_1, \ldots, a_n)$ to~$\sum_{i=1}^n a_i [T_i]$.
+\item[(iii)] \emph{(}\cite[Thm.~7.5]{BuanMarshReinekeReitenTodorov} and~\cite[]{???—} \emph{)} For any~$X,Y \in \ind(\cat)$, $\CC(X)$ and~$\CC(Y)$ are exchangeable if and only if~$\dim_{\field_X}\cat(X, \susp Y) = \dim_{\field_Y}\cat(X, \susp Y) = 1$.
 \item[(iv)]\emph{(}\cite[???]{BuanMarshReinekeReitenTodorov} and~\cite[???]{BuanIyamaReitenScott} and ???\emph{)} Let~$T'$ be any basic cluster-tilting object of~$\cat$.
@@
 \begin{definition}
-Let~$x\in\cluster$ be a cluster variable in a given cluster and let~$x'\in \cluster'$ be obtained by mutating~$\cluster$ at~$x$.
-The mutation is said to be a \defn{positive mutation} with respect to some initial cluster~$\cluster_\circ$ if there are~$X,Y\in \ind(\cat)$ such that~$\CC(X)=x$,~$\CC(Y)=x'$,~$\dim_{\field_X}\cat(X, \susp Y) = \dim_{\field_Y}\cat(X, \susp Y) = 1$ and, for any non-split triangle
+Let~$x\in\cluster$ be a cluster variable in a given cluster and let~$x' \in \cluster'$ be obtained by mutating~$\cluster$ at~$x$.
+The mutation is said to be a \defn{positive mutation} with respect to some initial cluster~$\cluster_\circ$ if there are~$X,Y \in \ind(\cat)$ such that~$\CC(X)=x$,~$\CC(Y)=x'$,~$\dim_{\field_X}\cat(X, \susp Y) = \dim_{\field_Y}\cat(X, \susp Y) = 1$ and, for any non-split triangle
 \[
@@
 \]
-(this triangle is unique up to isomorphism) we have~$h\in (\susp T)$, where~$T\in\cat$ is any basic cluster-tilting object such that~$\CC(T)=\cluster_\circ$.
+(this triangle is unique up to isomorphism) we have~$h \in (\susp T)$, where~$T\in\cat$ is any basic cluster-tilting object such that~$\CC(T)=\cluster_\circ$.
 \end{definition}
@@
 Let~$\mathcal{A}$ be any cluster algebra admitting a categorification by a Hom-finite,~$2$-Calabi--Yau, Krull--Schmidt, triangulated category with cluster-tilting objects.
-Let~$x\in\cluster$ be a cluster variable in a given cluster and let~$x'\in \cluster'$ be obtained by mutating~$\cluster$ at~$x$.
+Let~$x\in\cluster$ be a cluster variable in a given cluster and let~$x' \in \cluster'$ be obtained by mutating~$\cluster$ at~$x$.
 Then precisely one of the two mutations~$\mu_x(\cluster)$ and~$\mu_{x'}(\cluster')$ is a positive mutation.
@@
 \label{lemma::uerp categorified}
-Let~$\cat$ be a cluster category of Dynkin type~$A,B,C,D,E,F$ or~$G$, and let~$X,Y\in \cat$ be such~$\CC(Y)$ is obtained by performing a positive mutation at~$\CC(X)$ in some cluster containing it.
+Let~$\cat$ be a cluster category of Dynkin type~$A,B,C,D,E,F$ or~$G$, and let~$X,Y \in \cat$ be such~$\CC(Y)$ is obtained by performing a positive mutation at~$\CC(X)$ in some cluster containing it.
 Then the linear dependence between the~$\b{g}$-vectors given by the positive mutation is
@@
 \[
-L \eqdef \bigset{\ell_X}{X\in \ind(\cat) \ssm \add(\susp T)}
+L \eqdef \bigset{\ell_X}{X \in \ind(\cat) \ssm \add(\susp T)}
 \]
 generates the kernel of the canonical projection~$\b{g}:\Ksp(\cat) \to \kzero{\cat}$. 
-In this case, the set~$L$ is a basis of the kernel of~$\b{g}$, and for any $x\in \ker(\b{g})$, we have that
-\[
-x= \sum_{A\in \ind(\cat) \ssm \add(\susp T)} \frac{\langle x, A \rangle}{\langle \ell_A, A \rangle} \ell_A.
+In this case, the set~$L$ is a basis of the kernel of~$\b{g}$, and for any $x \in \ker(\b{g})$, we have that
+\[
+x= \sum_{A \in \ind(\cat) \ssm \add(\susp T)} \frac{\langle x, A \rangle}{\langle \ell_A, A \rangle} \ell_A.
 \]
@@
 \begin{proof}
-Let~$T \overset{t}{\to} X$ be a morphism with~$T\in \tc$.
+Let~$T \overset{t}{\to} X$ be a morphism with~$T \in \tc$.
 Using the notation of \cref{remark::equivalence Sigma}, there is an extriangle~$T\infl 0\defl \susp T \overset{\eps_T}{\dashrightarrow}$.
@@
 By~\cite[Thm.~6.5]{DemonetIyamaJasso} (based on~\cite[Thm~2.3]{DehyKeller}), rigid objects in~$K^{[-1,0]}(\proj \Lambda)$ are determined by their~$\b{g}$-vector.
-The datum of the~$\b{g}$-vector of an object of~$K^{[-1,0]}(\proj \Lambda)$ is equivalent to that of its class in the Grothendieck group~$K_0(K^{[-1,0]}(\proj \Lambda))$, where~$K^{[-1,0]}(\proj \Lambda)$ is viewed as an extriangulated category (see \cref{prop::2kbproj-is-extriangulated}).
+The datum of the~$\b{g}$-vector of an object of~$K^{[-1,0]}(\proj \Lambda)$ is equivalent to that of its class in the Grothendieck group~$K_0 \big( K^{[-1,0]}(\proj \Lambda) \big)$, where~$K^{[-1,0]}(\proj \Lambda)$ is viewed as an extriangulated category (see \cref{prop::2kbproj-is-extriangulated}).
 In this Grothendieck group, we have that~$[E] = [E'] = [X]+[Y]$.
@@
 
-In particular, the leftmost morphisms of both mutation conflations are both minimal~$\add(P(\mu) \oplus P(\nu))$-approximations of~$P(\omega)$.
+In particular, the leftmost morphisms of both mutation conflations are both minimal~$\add \big( P(\mu) \oplus P(\nu) \big)$-approximations of~$P(\omega)$.
 As such, they are isomorphic as morphisms.

### 2019-06-13 thirdPaper/draft/typeConeAssociahedra.tex
Proof of Lemma 2.20

--- 2019-06-13 thirdPaper/draft/typeConeAssociahedra.tex
@@
 
-The associahedron is a ``mythical polytope''~\cite{Haiman} whose facial structure encodes Catalan families: its vertices correspond to parenthesizations of a non-associative product, triangulations of a convex polygon, or binary trees; its edges correspond to applications of the associativity rule, diagonal flips, or edge rotations; and in general its faces correspond to partial parenthesizations, diagonal dissections, or Schr\"oder trees.
+The associahedron is a ``mythical polytope'' \cite{Haiman} whose facial structure encodes Catalan families: its vertices correspond to parenthesizations of a non-associative product, triangulations of a convex polygon, or binary trees; its edges correspond to applications of the associativity rule, diagonal flips, or edge rotations; and in general its faces correspond to partial parenthesizations, diagonal dissections, or Schr\"oder trees.
 Its combinatorial and topological structure was introduced in early works of D.~Tamari~\cite{Tamari} and J.~Stasheff~\cite{Stasheff}, and a first $3$-dimensional polytopal model was realized by J.~Milnor for the PhD defense of J.~Stasheff.
@@
 This provides natural Minkowski summands for all polytopal realizations of~$\Fan$: the rays of the closed type cone.
-These correspond to indecomposable polytopes, see~\cite{Meyer} or~\cite{McMullen-typeCone}.
+These correspond to indecomposable polytopes, see~\cite{Meyer} or \cite{McMullen-typeCone}.
 A polytope $P \subseteq \R^n$ is called \defn{indecomposable} if all its weak Minkowski summands are of the form $\lambda P+t$ for some $\lambda \ge 0$ and $t \in \R^n$.
@@
 \begin{proof}
- We postpone the proof until \pg{ref to later}.
+ We postpone the proof until Corollary~\ref{coro::number of positive meshes}.
 \end{proof}
@@
 In view of \cref{prop:exchangeablePairsNKC}, it is tempting to look for a characterization of the exchangeable pairs~$\omega, \omega'$ using the kisses between~$\omega$ and~$\omega'$.
-This question was discussed in~\cite[Sect.~9]{BrustleDouvilleMousavandThomasYildirim}.
+This question was discussed in \cite[Sect.~9]{BrustleDouvilleMousavandThomasYildirim}.
 However, as illustrated for instance in the non-kissing complex of \cref{fig:nonkissingFans}\,(right),
@@
 
-Since this precisely coincides with the description of the flip in the non-kissing complex (see \cref{prop:exchangeablePairsNKC}\,(i) or~\cite[Prop.~2.31]{PaluPilaudPlamondon-nonkissing} for an alternative presentation), we conclude that the flip of~$\omega$ in~$F$ creates a facet~$F'$ containing~$\omega'$.
+Since this precisely coincides with the description of the flip in the non-kissing complex (see \cref{prop:exchangeablePairsNKC}\,(i) or \cite[Prop.~2.31]{PaluPilaudPlamondon-nonkissing} for an alternative presentation), we conclude that the flip of~$\omega$ in~$F$ creates a facet~$F'$ containing~$\omega'$.
 Therefore, $\omega$ and~$\omega'$ are exchangeable with distinguished substring~$\sigma$.
@@
 
-Before we can prove \cref{theo::relations-g-vecteurs}, we need to recall the following results and definition from~\cite{DehyKeller,Palu}.
+Before we can prove \cref{theo::relations-g-vecteurs}, we need to recall the following results and definition from \cite{DehyKeller,Palu}.
 
@@
  with~$T_1^X$ and~$T_0^X$ in~$\add(T)$.
+
 \end{proposition}
@@
 \end{lemma}
-
 \begin{proof}
@@
 Therefore, if~$(\susp T)\cat(\susp^{-1} X, \susp X)$ is non-zero, then it contains the one-dimensional socle of~$\cat(\susp^{-1} X, \susp X)$, and thus contains~$h$.
-By~\cite{Palu},
+ By \cite{Palu},
  \[
@@
  \[
-\langle \ell_A, B \rangle = 
-\begin{cases}
+  \langle \ell_A, B \rangle = \begin{cases}
                                0 & \textrm{if~$A\ncong B$;} \\
@@
  \[
-\langle A, r_B \rangle =
-\begin{cases}
+  \langle A, r_B \rangle = \begin{cases}
                                0 & \textrm{if~$A\ncong B$;} \\
@@
 \end{corollary}
-
 \begin{proof}
@@
 \end{proposition}
-
 \begin{proof}
@@
 
+%The cluster category also contains enough information to detect positive mutations.
 The following definition is a cluster-tilting version of the positive mutation for~$\tau$-tilting modules, or for~$2$-term silting complexes.
-\begin{definition}
+\begin{definition}\label{defn::positive mutation}
 Let~$x\in\cluster$ be a cluster variable in a given cluster and let~$x'\in \cluster'$ be obtained by mutating~$\cluster$ at~$x$.
-The mutation is said to be a \defn{positive mutation} with respect to some initial cluster~$\cluster_\circ$ if there are~$X,Y\in \ind(\cat)$ such that~$\CC(X)=x$,~$\CC(Y)=x'$,~$\dim_{\field_X}\cat(X, \susp Y) = \dim_{\field_Y}\cat(X, \susp Y) = 1$ and, for any non-split triangle
+The pair~$(x,x')$ is said to be a \defn{positive mutation} with respect to some initial cluster~$\cluster_\circ$ if there are~$X,Y\in \ind(\cat)$ such that~$\CC(X)=x$,~$\CC(Y)=x'$,~$\dim_{\field_X}\cat(X, \susp Y) = \dim_{\field_Y}\cat(X, \susp Y) = 1$ and, for any non-split triangle
  \[
@@
 (this triangle is unique up to isomorphism) we have~$h\in (\susp T)$, where~$T\in\cat$ is any basic cluster-tilting object such that~$\CC(T)=\cluster_\circ$.
+
+The mutation is a \defn{mesh mutation} if the triangle can be chosen to be an almost-split triangle (with no assumption on~$h$).
 \end{definition}
+
+\begin{lemma}\label{lemm::exaclty one mesh mutation}
+ For every non-initial cluster variable, there exists precisely one pair~$(x,x')$ such that there exists a positive mesh mutation changing~$x$ into~$x'$.
+\end{lemma}
+\begin{proof}
+ Up to isomorphism, there is precisely one almost-split triangle of~$\cat$ starting in~$X$, where~$X$ is the object such that~$\phi(X) = x$.
+Thus there is precisely one mesh relation By Lemma~\ref{lemm::almost-split}, the pair~$(x,x')$ is a positive mutation if and only~$X\notin \add(\susp T)$, that is, if and only if~$x$ is not an initial variable.
+\end{proof}
+
+\begin{lemma}\label{lemm::mesh mutations and meshes}
+ The set of positive mesh mutations~$(x,x')$ of Definition~\ref{defn::positive mutation} is in bijection with the set~$\meshes$ from~\ref{defn::positive mutation}.
+\end{lemma}
+\begin{proof}
+ If~$(x,x')$ is a positive mesh mutation, then~$\{x,x'\}$ is in~$\meshes$.  Indeed, if~$X$ and~$X'$ are the the corresponding objects in~$\cat$.  Then there is an almost-split triangle
+ \[
+  X\to E\to X' \to \susp E,
+ \]
+ so that~$X' = \tau^{-1}X$.
+Moreover, there is a slice of the Auslander--Reiten quiver of~$\cat$ containing~$X$ and all indecomposable direct factors of~$E$.
+The direct sum of indecomposable objects in this slice is a cluster-tilting object in which~$X$ is a sink, and mutation at~$X$ gives~$X'$.
+Thus~$\{x,x'\}$ is in~$\meshes$.
+This gives an injective map from the set of positive mutations to~$\meshes$.
+
+ \smallskip
+
+ Next, assume that~$\{x,x'\}\in \meshes$ starts in~$x$.
+Then there is a cluster-tilting object~$T$ in~$\cat$ having~$X$ as a direct factor, and such that~$X$ is a sink in~$T$ and mutation at~$X$ yields~$X'$.
+Since~$X$ is a sink, the mutation triangle starting and ending in~$X$ are
+ \[
+  X\to E\to X' \to \susp X \quad \textrm{and} \quad  X' \to 0 \to X \to \susp X'.
+ \]
+  Therefore~$X' = \susp^{-1}X = \tau^{-1}X$.
+Thus the first triangle is the almost-split triangle starting in~$X$.
+Since the pair~$\{x,x'\}$ is not initial, the mutation is a positive mesh mutation.
+This gives an injective map from~$\meshes$ to the set of positive mutations.
+\end{proof}
+
+\begin{corollary}[Lemma~\ref{lem:bijectionMeshMutations}]
+\label{coro::number of positive meshes}
+ We have that~$|\meshes|$ is the number of non-initial variables.
+\end{corollary}
+\begin{proof}
+ This is a direct consequence of Lemmas~\ref{lemm::exaclty one mesh mutation} and~\ref{lemm::mesh mutations and meshes}.
+\end{proof}
 
@@
 \begin{proof}
-In view of \cref{thm::categorification} (iii), it follows from~\cite[Lem.~3.3]{Palu}
+In view of \cref{thm::categorification} (iii), it follows from~\cite[Lem.~3.3]{Palu}.
 \end{proof}
@@
 
-\para{Setting for Section~\ref{sect::prelim on extricats}}
+\vspace{.4cm}
+\noindent {\bf Setting for \cref{sect::prelim on extricats}}
 In that section, we let~$\cat$ be an extriangulated category with a fixed full additive \yann{additive contains strictly full + stable under taking summands} subcategory~$\tc$ satisfying the following three properties:
@@
 
-\para{Setting for Section~\ref{sect::Statment extricats}}
+\noindent {\bf Setting for \cref{sect::Statment extricats}}
 In that section, we keep the previous setting, but assume moreover that~$\cat$ is Krull--Schmidt, $\field$-linear, Ext-finite, and has Auslander--Reiten--Serre duality, and that the subcategory~$\tc$ is of the form~$\add T$, where~$T=T_1\oplus\cdots\oplus T_n$ is a basic object.
 
-\begin{remark}
-\label{remark::examples extricats}
+\begin{remark}\label{remark::examples extricats}
  Examples of categories satisfying the properties above are
@@
 
-\begin{lemma}
-\label{lemma::finitely presented}
+\begin{lemma}\label{lemma::finitely presented}
 For any~$X\in\cat$, the functor~$FX$ is finitely presented.
@@
 
-\begin{definition}
-\label{DefSqEquiv}
+\begin{definition}\label{DefSqEquiv}
 Let~$X,Z\in\cat$ be any two objects. Two sequences of morphisms in~$\cat$
@@
 
-\begin{proposition}[{\cite[Props.~3.3~\&~3.11]{NakaokaPalu}}]
-\label{proposition::extricat long exact sequences}
+\begin{proposition}\label{proposition::extricat long exact sequences}\emph{(}\cite[Props.~3.3~\&~3.11]{NakaokaPalu}\emph{)}
 Assume that $(\cat,\mathbb{E},\mathfrak{s})$ is an extriangulated category, and let $X\xrightarrow{x}Y\xrightarrow{y}Z\overset{\delta}{\dashrightarrow}$ be an extriangle.
@@
 
-\begin{proposition}[{\cite[Prop.~2.5]{IyamaNakaokaPalu}}]
+\begin{proposition}\emph{(}\cite[Prop.~2.5]{IyamaNakaokaPalu}\emph{)}
 For any non-split $\mathbb{E}$-extension $\delta\in\mathbb{E}(Z,X)$, the following holds.
@@
 
-\begin{proposition}[{\cite[Prop.~8.1]{IyamaNakaokaPalu}}]
+\begin{proposition}\emph{(}\cite[Prop.~8.1]{IyamaNakaokaPalu}\emph{)}
 Let~$\Lambda$ be an Artin algebra and let~$K^{[-1,0]}(\proj\Lambda)$ be the full subcategory of the homotopy category~$K^b(\proj\Lambda)$ consisting of complexes concentrated in degrees~$-1$ and~$0$ (using cohomological conventions).
@@
 
-\begin{corollary}
-\label{corollary::Sigma T injectives}
+\begin{corollary}\label{corollary::Sigma T injectives}
 The objects in~$\susp\tc$ are precisely the injective objects in~$\cat$.
@@
 
-\begin{definition}
-\label{defn::mutation conflation}
+\begin{definition}\label{defn::mutation conflation}
 A conflation $X\infl E\defl Y$ of~$K^{[-1,0]}(\proj \Lambda)$ is called a \defn{mutation conflation} if there are basic, two-term, silting objects $X\oplus R$, $Y\oplus R$, with~$X$ and~$Y$ indecomposable, such that the inflation $X\infl E$ is a left ($\add R$)-approximation (i.e.
@@
  \smallskip
+
  We now prove~(2).
 Let~$X\infl E\defl Y$ and~$X\infl E'\defl Y$ be two mutation conflations.
-By~\cite[Thm.~6.5]{DemonetIyamaJasso} (based on~\cite[Thm~2.3]{DehyKeller}), rigid objects in~$K^{[-1,0]}(\proj \Lambda)$ are determined by their~$\b{g}$-vector.
+By~\cite[Theorem 6.5]{DemonetIyamaJasso} (based on~\cite[Theorem 2.3]{DehyKeller}), rigid objects in~$K^{[-1,0]}(\proj \Lambda)$ are determined by their~$\b{g}$-vector.
 The datum of the~$\b{g}$-vector of an object of~$K^{[-1,0]}(\proj \Lambda)$ is equivalent to that of its class in the Grothendieck group~$K_0(K^{[-1,0]}(\proj \Lambda))$, where~$K^{[-1,0]}(\proj \Lambda)$ is viewed as an extriangulated category (see \cref{prop::2kbproj-is-extriangulated}).
@@
 
-\begin{corollary}
-\label{coro::exchangeablePairsNKC}
+\begin{corollary}\label{coro::exchangeablePairsNKC}
  Point~(ii) of \cref{prop:exchangeablePairsNKC} holds.
 \end{corollary}
-
 \begin{proof}
@@
  \]
+
 \end{lemma}
@@
 
-\begin{lemma}
-\label{lemm::if AR are mutations}
+\begin{lemma}\label{lemm::if AR are mutations}
 Let~$\Lambda$ be an Artin algebra, and let~$Y\infl E\defl X$ be a conflation in~$K^{[-1,0]}(\proj\Lambda)$. Then:
@@
 
-\begin{lemma}
-\label{lemm::initial meshes}
+\begin{lemma}\label{lemm::initial meshes}
 Let~$\Lambda$ be an Artin algebra whose indecomposable injective modules are~$\tau$-rigid, and let~$P$ be an indecomposable projective~$\Lambda$-module.
@@
 
+% \begin{corollary}
+%  Generalised cluster categories with infinite dimensional Hom-spaces ?
+% \end{corollary}
+
 %%%%%%%%%%%
@@
 \subsubsection{Associative algebras}
-
 \begin{example}[A gentle algebra]
@@
  The conditions of \cref{theo::brick-algebra-condition} are satisfied.
+
 \end{example}

### 2019-06-13 thirdPaper/draft/typeConeAssociahedra.tex

--- 2019-06-13 thirdPaper/draft/typeConeAssociahedra.tex
@@
 The following definition is a cluster-tilting version of the positive mutation for~$\tau$-tilting modules, or for~$2$-term silting complexes.
-\begin{definition}
+
+\begin{definition}\label{defn::positive mutation}
 Let~$x\in\cluster$ be a cluster variable in a given cluster and let~$x' \in \cluster'$ be obtained by mutating~$\cluster$ at~$x$.
-The mutation is said to be a \defn{positive mutation} with respect to some initial cluster~$\cluster_\circ$ if there are~$X,Y \in \ind(\cat)$ such that~$\CC(X)=x$,~$\CC(Y)=x'$,~$\dim_{\field_X}\cat(X, \susp Y) = \dim_{\field_Y}\cat(X, \susp Y) = 1$ and, for any non-split triangle
+The pair~$(x,x')$ is said to be a \defn{positive mutation} with respect to some initial cluster~$\cluster_\circ$ if there are~$X,Y\in \ind(\cat)$ such that~$\CC(X)=x$,~$\CC(Y)=x'$,~$\dim_{\field_X}\cat(X, \susp Y) = \dim_{\field_Y}\cat(X, \susp Y) = 1$ and, for any non-split triangle
  \[
@@
  \]
-(this triangle is unique up to isomorphism) we have~$h \in (\susp T)$, where~$T\in\cat$ is any basic cluster-tilting object such that~$\CC(T)=\cluster_\circ$.
+(this triangle is unique up to isomorphism) we have~$h\in (\susp T)$, where~$T\in\cat$ is any basic cluster-tilting object such that~$\CC(T)=\cluster_\circ$.
+
+The mutation is a \defn{mesh mutation} if the triangle can be chosen to be an almost-split triangle (with no assumption on~$h$).
 \end{definition}
+
+\begin{lemma}\label{lemm::exaclty one mesh mutation}
+ For every non-initial cluster variable, there exists precisely one pair~$(x,x')$ such that there exists a positive mesh mutation changing~$x$ into~$x'$.
+\end{lemma}
+\begin{proof}
+ Up to isomorphism, there is precisely one almost-split triangle of~$\cat$ starting in~$X$, where~$X$ is the object such that~$\phi(X) = x$.
+Thus there is precisely one mesh relation By Lemma~\ref{lemm::almost-split}, the pair~$(x,x')$ is a positive mutation if and only~$X\notin \add(\susp T)$, that is, if and only if~$x$ is not an initial variable.
+\end{proof}
+
+\begin{lemma}\label{lemm::mesh mutations and meshes}
+ The set of positive mesh mutations~$(x,x')$ of Definition~\ref{defn::positive mutation} is in bijection with the set~$\meshes$ from~\ref{defn::positive mutation}.
+\end{lemma}
+\begin{proof}
+ If~$(x,x')$ is a positive mesh mutation, then~$\{x,x'\}$ is in~$\meshes$.  Indeed, if~$X$ and~$X'$ are the the corresponding objects in~$\cat$.  Then there is an almost-split triangle
+ \[
+  X\to E\to X' \to \susp E,
+ \]
+ so that~$X' = \tau^{-1}X$.
+Moreover, there is a slice of the Auslander--Reiten quiver of~$\cat$ containing~$X$ and all indecomposable direct factors of~$E$.
+The direct sum of indecomposable objects in this slice is a cluster-tilting object in which~$X$ is a sink, and mutation at~$X$ gives~$X'$.
+Thus~$\{x,x'\}$ is in~$\meshes$.
+This gives an injective map from the set of positive mutations to~$\meshes$.
+
+ \smallskip
+
+ Next, assume that~$\{x,x'\}\in \meshes$ starts in~$x$.
+Then there is a cluster-tilting object~$T$ in~$\cat$ having~$X$ as a direct factor, and such that~$X$ is a sink in~$T$ and mutation at~$X$ yields~$X'$.
+Since~$X$ is a sink, the mutation triangle starting and ending in~$X$ are
+ \[
+  X\to E\to X' \to \susp X \quad \textrm{and} \quad  X' \to 0 \to X \to \susp X'.
+ \]
+  Therefore~$X' = \susp^{-1}X = \tau^{-1}X$.
+Thus the first triangle is the almost-split triangle starting in~$X$.
+Since the pair~$\{x,x'\}$ is not initial, the mutation is a positive mesh mutation.
+This gives an injective map from~$\meshes$ to the set of positive mutations.
+\end{proof}
+
+\begin{corollary}[Lemma~\ref{lem:bijectionMeshMutations}]
+\label{coro::number of positive meshes}
+ We have that~$|\meshes|$ is the number of non-initial variables.
+\end{corollary}
+\begin{proof}
+ This is a direct consequence of Lemmas~\ref{lemm::exaclty one mesh mutation} and~\ref{lemm::mesh mutations and meshes}.
+\end{proof}
 

### 2019-06-13 thirdPaper/draft/typeConeAssociahedra.tex
typographic changes

--- 2019-06-13 thirdPaper/draft/typeConeAssociahedra.tex
@@
 
-\section{Relations for~$\b{g}$-vectors in finite type cluster algebras via~$2$-Calabi--Yau triangulated categories}
+\section{Relations for~$\b{g}$-vectors in finite type cluster algebras \\ via~$2$-Calabi--Yau triangulated categories}
 \label{sec:clusterCategories}
@@
 In~\cite{Auslander1984}, M.~Auslander showed that the relations in the Grothendieck group of an Artin algebra are generated by the ones given by almost-split sequences precisely when the algebra is of finite representation type.
-Inspired by this result, we will show that a similar statement holds (\cref{theo::relations-g-vecteurs}) for the~$\b{g}$-vectors (or indices) of objects in a~$2$-Calabi--Yau triangulated category.
+Inspired by this result, we will show that a similar statement holds (see \cref{theo::relations-g-vecteurs}) for the~$\b{g}$-vectors (or indices) of objects in a~$2$-Calabi--Yau triangulated category.
 
@@
 Thus the right-hand side is non-zero, and so neither is the left-hand side.
-By the above, this implies that~$h \in (\susp T)\cat(\susp^{-1} X, \susp X)$, which finishes the proof.
+By the above, this implies~${h \in (\susp T)\cat(\susp^{-1} X, \susp X)}$, which finishes the proof.
 \end{proof}
@@
 \begin{proof}
-We only prove the first assertion; the second one is proved dually. Assume that~$A\notin\add(\susp T)$. Let
+We only prove the first assertion; the second one is proved dually. Assume that ${A\notin\add(\susp T)}$. Let
 \[
@@
 \]
-be an almost-split triangle. By \cref{lemm::almost-split}, the morphism~$h$ is in~$(\susp T)$. Applying the functor~$F=\cat(T,-)$, we get an exact sequence
+be an almost-split triangle. By \cref{lemm::almost-split}, the morphism~$h$ is in~$(\susp T)$. Applying the functor ${F=\cat(T,-)}$, we get an exact sequence
 \[
@@
 If~$B\ncong A$, then the definition of an almost-split triangle implies that~$f^*$ is surjective.
-Thus~$\coker(f^*)=0$, so that~$\coker(Ff^*) = 0$, and by additivity of the dimension in exact sequences, we get that~$\langle \ell_A, B \rangle =0$.
+Thus $\coker(f^*)=0$, so that~$\coker(Ff^*) = 0$, and by additivity of the dimension in exact sequences, we get that~$\langle \ell_A, B \rangle =0$.
 
@@
 \]
-Then for any~$B \in \ind(\cat)$, we have that~$\langle z, [B] \rangle = 0$. By \cref{lemm::test-susp-T}, this implies that~${z \in \Ksp \big( \add(\susp T) \big)}$, and finishes the proof.
+Then for any~$B \in \ind(\cat)$, we have that~$\langle z, [B] \rangle = 0$. By \cref{lemm::test-susp-T}, this implies that ${z \in \Ksp \big( \add(\susp T) \big)}$, and finishes the proof.
 \end{proof}
@@
 
-Now,~$[T]+[\susp T]$ is in the kernel of~$\b{g}$, but~$\langle [T] + [\susp T], [B] \rangle = \langle [T], [B] \rangle = 0$ if and only if~$B \in \add(\susp T)$. Thus~$\ind(\cat)$ has to be finite.
+Now,~$[T]+[\susp T]$ is in the kernel of~$\b{g}$, but~$\langle [T] + [\susp T], [B] \rangle = \langle [T], [B] \rangle = 0$ if and only if ${B \in \add(\susp T)}$. Thus~$\ind(\cat)$ has to be finite.
 \end{proof}
@@
 By \cref{lemma:positive mutation triangles}, we may assume that the mutation under consideration is a positive mutation.
-In view of \cref{thm::categorification} (ii) and (iv) it is enough to show that the relation in~$K_0(\cat ; T)$ given by any triangle~$X\to E\to Y\xrightarrow{h} \susp X$ with~$h\in(\susp T)$ is a positive linear combination of relations coming from Auslander--Reiten triangles with third term not in~$\add(\susp T)$.
+In view of \cref{thm::categorification} (ii) and (iv) it is enough to show that the relation in~$K_0(\cat ; T)$ given by any triangle ${X\to E\to Y\xrightarrow{h} \susp X}$ with~$h\in(\susp T)$ is a positive linear combination of relations coming from Auslander--Reiten triangles with third term not in~$\add(\susp T)$.
 This categorified statement is precisely \cref{corollary::meshes positively generate cluster cats}.
@@
 Let~$\B_\circ$ be any finite type exchange matrix, and let~$\mathcal{A}(\B_\circ)$ be the associated cluster algebra without coefficients.
-Then, for any exchangeable cluster variables~$x$ and~$x'$, the linear dependence $\sum_{y \in \cluster \cup \cluster'} \coefficient[{\b{g}_y}][\cluster][\cluster'] \, \b{g}_y = 0$ only depends on the pair~$(x,x')$ and not on the specific choice of clusters~$\cluster$ and~$\cluster'$ containing~$x$ and~$x'$ respectively and such that~$\cluster\setminus\{x\}=\cluster'\setminus\{x'\}$.
+Then, for any exchangeable cluster variables~$x$ and~$x'$, the linear dependence $\sum_{y \in \cluster \cup \cluster'} \coefficient[{\b{g}_y}][\cluster][\cluster'] \, \b{g}_y = 0$ only depends on the pair~$(x,x')$ and not on the specific choice of clusters~$\cluster$ and~$\cluster'$ containing~$x$ and~$x'$ respectively and such that~${\cluster\setminus\{x\}=\cluster'\setminus\{x'\}}$.
 \end{corollary}
@@
 Let~$T\in\cat$ be a basic cluster tilting object such that~$\CC(T)$ is the initial cluster.
-By \cref{lemma:positive mutation triangles}, the morphism~$h$ belongs to the ideal~$(\susp T)$.
-Therefore, the triangle~$X\to \bigoplus_i E_i \to Y \xrightarrow{h} \susp X$ induces the relation~$[X]+[Y]=\sum_i [E_i]$ in~$K_0(\cat ; T)$.
+By~\cref{lemma:positive mutation triangles}, the morphism~$h$ belongs to the ideal~$(\susp T)$.
+Therefore, the triangle ${X\to \bigoplus_i E_i \to Y \xrightarrow{h} \susp X}$ induces the relation~$[X]+[Y]=\sum_i [E_i]$ in~$K_0(\cat ; T)$.
 \cref{thm::categorification} (ii) gives the equality~$\b{g}_{\CC(X)} + \b{g}_{\CC(Y)} = \sum_i\b{g}_{\CC(E_i)}$, where the~$\b{g}$-vectors are computed with respect to the initial seed~$\CC(T)$.
@@
 
-We indifferently call \emph{conflations}, written~$X\infl Y\defl Z$, or \emph{extriangles}, written~$X\infl Y\defl Z \overset{\delta}{\dashrightarrow}$, the analogues of short exact sequences or triangles in an extriangulated category.
+We indifferently call \emph{conflations}, written~$X\infl Y\defl Z$, or \emph{extriangles}, written ${X\infl Y\defl Z \overset{\delta}{\dashrightarrow}}$, the analogues of short exact sequences or triangles in an extriangulated category.
 
@@
 A \defn{split}~$\mathbb{E}$-extension is a zero element~$0\in\mathbb{E}(Z,X)$, for some objects~$X,Z\in\cat$.
-For any two~$\mathbb{E}$-extensions~$\delta\in\mathbb{E}(Z,X)$,~$\delta'\in\mathbb{E}(Z',X')$, the additivity of~$\cat$,~$\mathbb{E}$ permits to define the~$\mathbb{E}$-extension
+For any two~$\mathbb{E}$-exten\-sions~${\delta\in\mathbb{E}(Z,X)}$, $\delta'\in\mathbb{E}(Z',X')$, the additivity of~$\cat$,~$\mathbb{E}$ permits to define the~$\mathbb{E}$-extension
 \[
@@
 \begin{definition}
-An \defn{additive realization}~$\mathfrak{s}$ is a correspondence associating, with~$\mathbb{E}$-extension~$\delta\in\mathbb{E}(Z,X)$, an equivalence class~$\mathfrak{s}(\delta)=[X\xrightarrow{x}Y\xrightarrow{y}Z]$ and satisfying the following condition:
+An \defn{additive realization}~$\mathfrak{s}$ is a correspondence associating, with~$\mathbb{E}$-extension ${\delta\in\mathbb{E}(Z,X)}$, an equivalence class~$\mathfrak{s}(\delta)=[X\xrightarrow{x}Y\xrightarrow{y}Z]$ and satisfying the following condition:
 \begin{itemize}
@@
 For any~$T\in\tc$, fix an extriangle~$T\infl 0\defl\susp T\overset{\eps_T}{\dashrightarrow}$.
-As noticed in \cref{lemma::shifts of extriangles}, for any morphism~$T\overset{f}{\to}T'$ in~$\tc$, there is a unique morphism~$\susp f\in\cat(\susp T,\susp T')$ such that~$f_\ast\eps_T=(\susp f)^\ast\eps_{T'}$ (i.e.
+As noticed in \cref{lemma::shifts of extriangles}, for any morphism~$T\overset{f}{\to}T'$ in~$\tc$, there is a unique morphism~$\susp f\in\cat(\susp T,\susp T')$ such that~${f_\ast\eps_T=(\susp f)^\ast\eps_{T'}}$ (i.e.
 such that~$(f,\susp f)$ is a morphism from~$\eps_T$ to~$\eps_{T'}$), as illustrated below:
@@
 
-In particular, the leftmost morphisms of both mutation conflations are both minimal~$\add \big( P(\mu) \oplus P(\nu) \big)$-approximations of~$P(\omega)$.
+In particular, the leftmost morphisms of both mutation conflations are minimal ${\add \big( P(\mu) \oplus P(\nu) \big)}$-approximations of~$P(\omega)$.
 As such, they are isomorphic as morphisms.
@@
 Because~$X$ is concentrated in non-positive degrees,~$F\susp X=0$.
-Let us verify that the map~$F\susp^{-1}Y\to F\susp^{-1}Z$ is surjective.
+Let us verify that the map ${F\susp^{-1}Y\to F\susp^{-1}Z}$ is surjective.
 Let~$\Lambda \xrightarrow{f} \susp^{-1} Z$ be a morphism in~$K^b(\proj \Lambda)$.
@@
 For convenience of the reader, we recall those two results: Let~$Y, Z \in K^{[-1,0]}(\proj\Lambda)$ be indecomposable and not in~$\add(\susp\Lambda)$, and let~$P\in\proj\Lambda$.
-Then~$\Hom{K^b}(Y,\susp Z)=0$ if and only if~$\Hom{\Lambda}(FZ,\tau FY)=0$ and~$\Hom{K^b}(P,Y)=0$ if and only if~$\Hom{\Lambda}(P,FY)=0$.
+Then~$\Hom{K^b}(Y,\susp Z)=0$ if and only if~$\Hom{\Lambda}(FZ,\tau FY)=0$ and~${\Hom{K^b}(P,Y)=0}$ if and only if~$\Hom{\Lambda}(P,FY)=0$.
 
@@
 % Then~$Y\infl E\defl \susp P$ is an Auslander--Reiten conflation in~$K^{[-1,0]}(\proj\Lambda)$, which is also a mutation conflation.
-Then the Auslander--Reiten conflation~$Y\infl E\defl \susp P$ in~$K^{[-1,0]}(\proj\Lambda)$ is a mutation conflation if~$FY$ is a brick.
+Then the Auslander--Reiten conflation~${Y\infl E\defl \susp P}$ in~$K^{[-1,0]}(\proj\Lambda)$ is a mutation conflation if~$FY$ is a brick.
 \end{lemma}
@@
 where the vertical maps are surjective.
-Since~$\Lambda$ is rigid and~$Y$ is two-term, we can apply~\cite[Prop.~6.2]{IyamaYoshino} to the triangulated category~$K^b(\proj\Lambda)$ (or \cref{prop::KRextricat} to the extriangulated~$K^{[-1,0]}(\proj\Lambda)$).
+Since~$\Lambda$ is rigid and~$Y$ is two-term, we can apply~\cite[Prop.~6.2]{IyamaYoshino} to the triangulated category~$K^b(\proj\Lambda)$ (or \cref{prop::KRextricat} to the extriangulated $K^{[-1,0]}(\proj\Lambda)$).
 As a consequence, the right-most vertical map is bijective.
@@
 \]
-modulo the relation~$\gamma\beta\alpha = 0$. The Auslander--Reiten quiver of the extriangulated category~$K^{[-1, 0]}(\proj\Lambda)$ is depicted below.
+modulo the relation~$\gamma\beta\alpha = 0$. The Auslander--Reiten quiver of the extriangulated category $K^{[-1, 0]}(\proj\Lambda)$ is depicted below.
 \[

### 2019-06-13 thirdPaper/draft/typeConeAssociahedra.tex
typographic changes

@@
 
-\begin{lemma}\label{lemm::mesh mutations and meshes}
+\begin{lemma}
+\label{lemm::mesh mutations and meshes}
 The set of positive mesh mutations~$(x,x')$ of Definition~\ref{defn::positive mutation} is in bijection with the set~$\meshes$ from~\ref{defn::positive mutation}.
 \end{lemma}
+
 \begin{proof}
@@
 \smallskip
-
 Next, assume that~$\{x,x'\}\in \meshes$ starts in~$x$.
@@
 Let~$\delta\in\mathbb{E}(Z,X)$ be an~$\mathbb{E}$-extension.
-By functoriality, any morphisms~$f\in\cat(X,X')$ and~$h\in\cat(Z',Z)$ induce~$\mathbb{E}$-extensions~$\mathbb{E}(Z,f)(\delta)\in\mathbb{E}(Z,X')\ \ \text{and}\ \ \mathbb{E}(h,X)(\delta)\in\mathbb{E}(Z',X)$.
+By functoriality, any morphisms~$f\in\cat(X,X')$ and~$h\in\cat(Z',Z)$ induce~$\mathbb{E}$-extensions~$\mathbb{E}(Z,f)(\delta)\in\mathbb{E}(Z,X') \text{ and } \mathbb{E}(h,X)(\delta)\in\mathbb{E}(Z',X)$.
 For short, we write~$f_\ast\delta$ and~$h^\ast\delta$ instead.
 Using those notations, we have, in~$\mathbb{E}(Z',X')$
-\[ \mathbb{E}(h,f)(\delta)=h^\ast f_\ast\delta=f_\ast h^\ast\delta. \]
+\[
+\mathbb{E}(h,f)(\delta)=h^\ast f_\ast\delta=f_\ast h^\ast\delta.
+\]
 \end{remark}
@@
 Let~$X,Z\in\cat$ be any two objects. Two sequences of morphisms in~$\cat$
-\[ X \overset{x}{\longrightarrow}Y\overset{y}{\longrightarrow}Z \ \text{ and } \ X\overset{x'}{\longrightarrow}Y'\overset{y'}{\longrightarrow}Z \]
+\[
+X \overset{x}{\longrightarrow}Y\overset{y}{\longrightarrow}Z \text{ and } X\overset{x'}{\longrightarrow}Y'\overset{y'}{\longrightarrow}Z
+\]
 are said to be \defn{equivalent} if there exists an isomorphism~$g\in\cat(Y,Y')$ such that the following diagram commutes.
@@
 \[
-X\overset{f}{\longrightarrow}Y\overset{f'}{\longrightarrow}Z'\ \text{ and } \ Y\overset{g}{\longrightarrow}Z\overset{g'}{\longrightarrow}X'.
+X\overset{f}{\longrightarrow}Y\overset{f'}{\longrightarrow}Z' \quad\text{and}\quad Y\overset{g}{\longrightarrow}Z\overset{g'}{\longrightarrow}X'.
 \]
@@
 Then the following sequences of natural transformations are exact:
-\[ \cat(Z,-)\overset{-\circ y}{\longrightarrow}\cat(Y,-)\overset{-\circ x}{\longrightarrow}\cat(X,-)\overset{\delta^\sharp}{\longrightarrow}\mathbb{E}(Z,-)\overset{y^\ast}{\longrightarrow}\mathbb{E}(Y,-)\overset{x^\ast}{\longrightarrow}\mathbb{E}(X,-), \]
-\[ \cat(-,X)\overset{x\circ-}{\longrightarrow}\cat(-,Y)\overset{y\circ-}{\longrightarrow}\cat(-,Z)\overset{\delta_\sharp}{\longrightarrow}\mathbb{E}(-,X)\overset{x_\ast}{\longrightarrow}\mathbb{E}(-,Y)\overset{y_\ast}{\longrightarrow}\mathbb{E}(-,Z), \]
+\[
+\cat(Z,-)\overset{-\circ y}{\longrightarrow}\cat(Y,-)\overset{-\circ x}{\longrightarrow}\cat(X,-)\overset{\delta^\sharp}{\longrightarrow}\mathbb{E}(Z,-)\overset{y^\ast}{\longrightarrow}\mathbb{E}(Y,-)\overset{x^\ast}{\longrightarrow}\mathbb{E}(X,-),
+\]
+\[
+\cat(-,X)\overset{x\circ-}{\longrightarrow}\cat(-,Y)\overset{y\circ-}{\longrightarrow}\cat(-,Z)\overset{\delta_\sharp}{\longrightarrow}\mathbb{E}(-,X)\overset{x_\ast}{\longrightarrow}\mathbb{E}(-,Y)\overset{y_\ast}{\longrightarrow}\mathbb{E}(-,Z),
+\]
 where~$\delta^\sharp(f)=f_\ast\delta$ and~$\delta_\sharp(g)=g^\ast\delta$.
@@
 \[
-T_1^X\overset{f_X}{\infl} T_0^X\overset{g_X}{\defl} X \overset{\delta_X}{\dashrightarrow}, \ \ \ T_0^X\infl 0\defl \susp T_0^X\overset{\delta_0}{\dashrightarrow}, \ \ \ T_1^X\infl 0\defl \susp T_1^X\overset{\delta_1}{\dashrightarrow}
+T_1^X\overset{f_X}{\infl} T_0^X\overset{g_X}{\defl} X \overset{\delta_X}{\dashrightarrow}, \quad T_0^X\infl 0\defl \susp T_0^X\overset{\delta_0}{\dashrightarrow}, \quad T_1^X\infl 0\defl \susp T_1^X\overset{\delta_1}{\dashrightarrow}
 \]
@@
 \[
-T_0^X\overset{g_X}{\infl} X \overset{h_X}{\defl} \susp T_1^X \overset{(f_X)_\ast\delta_1}{\dashrightarrow}, \ \ \ X \overset{h_X}{\infl} \susp T_1^X \overset{\susp f_X}{\defl} \susp T_0^X \overset{(g_X)_\ast\delta_0}{\dashrightarrow}
+T_0^X\overset{g_X}{\infl} X \overset{h_X}{\defl} \susp T_1^X \overset{(f_X)_\ast\delta_1}{\dashrightarrow}, \quad X \overset{h_X}{\infl} \susp T_1^X \overset{\susp f_X}{\defl} \susp T_0^X \overset{(g_X)_\ast\delta_0}{\dashrightarrow}
 \]
@@
 \[
-{\rm (3')} \ \ \ \cat = \tc\ast\susp\tc.
+{\rm (3')} \quad \cat = \tc\ast\susp\tc.
 \]
@@
 \endxy
-\ \ \ \ \ \ \ \
+\quad \quad \ \
 \xy

### 2019-06-13 thirdPaper/draft/typeConeAssociahedra.tex
typographic changes

@@
 \begin{enumerate}
-\item The set~$\set{[\ell_A]}{A \in \ind(\cat) \ssm \add(\susp T)} \cup \set{[\susp T_i]}{i=1, \dots, n}$ is free in~$\Ksp(\cat)$.
-\item The set~$\set{[r_A]}{A \in \ind(\cat) \ssm \add(\susp T)} \cup \set{[\susp T_i]}{i=1, \dots, n}$ is free in~$\Ksp(\cat)$.
+\item The set~$\set{[\ell_A]}{A \in \ind(\cat) \ssm \add(\susp T)} \cup \set{[\susp T_i]}{i \in [n]}$ is free in~$\Ksp(\cat)$.
+\item The set~$\set{[r_A]}{A \in \ind(\cat) \ssm \add(\susp T)} \cup \set{[\susp T_i]}{i \in [n]}$ is free in~$\Ksp(\cat)$.
 \end{enumerate}
@@
 \]
-But the~$[\susp T_i]$ are linearly independent in~$\Ksp(\cat)$. Thus~$\lambda_i = 0$ for all~$i \in \{1, \ldots, n\}$. This finishes the proof.
+But the~$[\susp T_i]$ are linearly independent in~$\Ksp(\cat)$. Thus~$\lambda_i = 0$ for all~$i \in [n]$. This finishes the proof.
 \end{proof}
@@
 \[
-\set{[\ell_A]}{A \in \ind(\cat) \ssm \add(\susp T)} \cup \set{[\susp T_i]}{i=1, \ldots, n}
+\set{[\ell_A]}{A \in \ind(\cat) \ssm \add(\susp T)} \cup \set{[\susp T_i]}{i \in [n]}
 \]
@@
 \item[(i)] \emph{(}\cite[Prop.~3.2]{BuanMarshReinekeReitenTodorov} and~\cite[]{???} \emph{)} For any~$X,Y \in \ind(\cat)$, $\CC(X)$ and~$\CC(Y)$ are compatible if and only if~$\cat(X, \susp Y) = 0$.
-\item[(ii)] \emph{(}\cite[Prop.~4.3]{FuKeller} and \emph{)} For any~$X \in \ind(\cat)$, the~$\b{g}$-vector of~$\CC(X)$ is~$\b{g}([X])$, where we identify~$\Z^n$ and~$K_0(\cat ; T)$ via the isomorphism sending~$(a_1, \ldots, a_n)$ to~$\sum_{i=1}^n a_i [T_i]$.
+\item[(ii)] \emph{(}\cite[Prop.~4.3]{FuKeller} and \emph{)} For any~$X \in \ind(\cat)$, the~$\b{g}$-vector of~$\CC(X)$ is~$\b{g}([X])$, where we identify~$\Z^n$ and~$K_0(\cat ; T)$ via the isomorphism sending~$(a_1, \dots, a_n)$ to~$\sum_{i=1}^n a_i [T_i]$.
 \item[(iii)] \emph{(}\cite[Thm.~7.5]{BuanMarshReinekeReitenTodorov} and~\cite[]{???—} \emph{)} For any~$X,Y \in \ind(\cat)$, $\CC(X)$ and~$\CC(Y)$ are exchangeable if and only if~$\dim_{\field_X}\cat(X, \susp Y) = \dim_{\field_Y}\cat(X, \susp Y) = 1$.

### 2019-06-13 thirdPaper/draft/typeConeAssociahedra.tex
minor changes

--- 2019-06-13 thirdPaper/draft/typeConeAssociahedra.tex
@@
 
-\vincent{Link to \cref{sec:clusterCategories}.}
-\vincent{\cref{lem:bijectionMeshMutations} might become a conjecture.}
+The following statement is proved in \cref{coro::number of positive meshes}.
 
@@
 \end{lemma}
-\begin{proof}
- We postpone the proof until Corollary~\ref{coro::number of positive meshes}.
-\end{proof}
-
-The following statement describes the linear dependence in the mesh mutations.
+
+The following statement describes the linear dependence in the mesh mutations. It follows from \cref{lem:linearDependencegvectorsCA,def:meshMutation}.
 
@@
 
-\begin{definition}\label{defn::positive mutation}
+\begin{definition}
+\label{defn::positive mutation}
 Let~$x\in\cluster$ be a cluster variable in a given cluster and let~$x' \in \cluster'$ be obtained by mutating~$\cluster$ at~$x$.
@@
 
-\begin{lemma}\label{lemm::exaclty one mesh mutation}
+\begin{lemma}
+\label{lemm::exaclty one mesh mutation}
 For every non-initial cluster variable, there exists precisely one pair~$(x,x')$ such that there exists a positive mesh mutation changing~$x$ into~$x'$.
 \end{lemma}
+
 \begin{proof}
 Up to isomorphism, there is precisely one almost-split triangle of~$\cat$ starting in~$X$, where~$X$ is the object such that~$\phi(X) = x$.
-Thus there is precisely one mesh relation By Lemma~\ref{lemm::almost-split}, the pair~$(x,x')$ is a positive mutation if and only~$X\notin \add(\susp T)$, that is, if and only if~$x$ is not an initial variable.
+Thus there is precisely one mesh relation By \cref{lemm::almost-split}, the pair~$(x,x')$ is a positive mutation if and only~$X\notin \add(\susp T)$, that is, if and only if~$x$ is not an initial variable.
 \end{proof}
@@
 \label{lemm::mesh mutations and meshes}
-The set of positive mesh mutations~$(x,x')$ of Definition~\ref{defn::positive mutation} is in bijection with the set~$\meshes$ from~\ref{defn::positive mutation}.
+The set of positive mesh mutations~$(x,x')$ of \cref{defn::positive mutation} is in bijection with the set~$\meshes$ of~\cref{defn::positive mutation}.
 \end{lemma}
@@
 
-\begin{corollary}[Lemma~\ref{lem:bijectionMeshMutations}]
+\begin{corollary}[\cref{lem:bijectionMeshMutations}]
 \label{coro::number of positive meshes}
@@
 \end{corollary}
+
 \begin{proof}
- This is a direct consequence of Lemmas~\ref{lemm::exaclty one mesh mutation} and~\ref{lemm::mesh mutations and meshes}.
+This is a direct consequence of \cref{lemm::exaclty one mesh mutation,lemm::mesh mutations and meshes}.
 \end{proof}

### 2019-06-13 thirdPaper/draft/typeConeAssociahedra.tex
references intro

@@
 \newcommand{\f}[1]{{\mathfrak{#1}}} % mathfrak letters
-\renewcommand{\c}[1]{{\mathcal{#1}}} % call letters
+\newcommand{\cal}[1]{{\mathcal{#1}}} % call letters
 \renewcommand{\b}[1]{{\boldsymbol{#1}}} % bold letters
@@
 For non-kissing complexes (a.k.a.
-support~$\tau$-tilting complexes) of gentle algebras, we show that the space of realizations of the non-kissing fan is simplicial when the gentle bound quiver is brick and $2$-acyclic, and we describe in this case its facet-defining inequalities in terms of mesh mutations.
+support $\tau$-tilting complexes) of gentle algebras, we show that the space of realizations of the non-kissing fan is simplicial when the gentle bound quiver is brick and $2$-acyclic, and we describe in this case its facet-defining inequalities in terms of mesh mutations.
 For graphical nested complexes, we show that the space of realizations of the nested fan is simplicial only in the case of the associahedron, and we describe its facet-defining inequalities in general.
@@
 
-The associahedron appears as a fundamental structure in several mathematical theories, such as moduli spaces and topology~\cite{Stasheff, Keller-AinfinityAlgebras}, operads and rewriting theory~\cite{}, combinatorial Hopf algebras~\cite{LodayRonco, ChatelPilaud, Pilaud-brickAlgebra}, diagonal harmonics~\cite{}, mathematical physics~\cite{ArkaniHamedBaiHeYan, BanerjeeLaddhaRaman-StokesPolytopes, Raman-PositiveGeometry}, etc.
+The associahedron appears as a fundamental structure in several mathematical theories, such as moduli spaces and topology~\cite{Stasheff, Keller-AinfinityAlgebras}, operads and rewriting theory~\cite{Street, MasudaThomasTonksVallette}, combinatorial Hopf algebras~\cite{LodayRonco, ChatelPilaud, Pilaud-brickAlgebra}, diagonal harmonics~\cite{BergeronPrevilleRatelle, PrevilleRatelleViennot}, mathematical physics~\cite{ArkaniHamedBaiHeYan, BanerjeeLaddhaRaman-StokesPolytopes, Raman-PositiveGeometry}, etc.
 Another striking illustration of the ubiquity of the associahedron lies in the theory of cluster algebras introduced by S.~Fomin and A.~Zelevinsky in~\cite{FominZelevinsky-ClusterAlgebrasI} with motivation coming from total positivity and canonical bases.
@@
 Finite type cluster complexes were geometrically realized first by F.~Chapoton, S.~Fomin and A.~Zelevinsky~\cite{ChapotonFominZelevinsky} based on the $\b{d}$-vector fans~\cite{FominZelevinsky-YSystems, FominZelevinsky-ClusterAlgebrasII} of the bipartite initial seed, then by~C.~Hohlweg, C.~Lange and H.~Thomas~\cite{HohlwegLangeThomas} based on the Cambrian fans~\cite{Reading-CambrianLattices, ReadingSpeyer} of acyclic initial seeds, and finally by C.~Hohlweg, V.~Pilaud and S.~Stella~\cite{HohlwegPilaudStella} based on the $\b{g}$-vector fans~\cite{FominZelevinsky-ClusterAlgebrasIV} with respect to an arbitrary initial seed.
-The resulting polytopes are known as generalized associahedra, and the classical associahedra corresponds to the cluster algebras of type~$A$.
+The resulting polytopes are known as generalized associahedra, and the classical associahedra corresponds to the cluster algebras~of~type~$A$.
 
@@
 These realizations were then extended by V.~Bazier-Matte, G.~Douville, K.~Mousavand, H.~Thomas and E.~Y\i ld\i r\i m~\cite{BazierMatteDouvilleMousavandThomasYildirim} in the context of finite type cluster algebras using tools from representation theory of quivers.
-More precisely, they fix a finite type cluster algebra~$\c{A}$ and consider the real euclidean space~$\R^\c{V}$ indexed by the set~$\c{V}$ of cluster variables of~$\c{A}$.
-Starting from an acyclic initial seed~$\seed_\circ$, they consider a set~$\c{M}$ of mesh mutations and compute the corresponding linear dependences between the $\b{g}$-vectors, which can be interpreted as linear spaces in~$\R^\c{V}$.
-Finally, they perturb these mesh linear spaces by a collection~$\b{\ell} \in \R^{\c{M}}$ of positive parameters and intersect the resulting perturbed mesh affine spaces with the positive orthant of~$\R^\c{V}$ (see \cref{subsec:typeConeCA}).
-They show that the resulting polytope is always a generalized associahedron, and that its normal fan is the $\b{g}$-vector fan of~$\c{A}$ with respect to the initial acyclic seed~$\seed_\circ$.
-A by-product of their construction is that the space of all polytopal realizations of the $\b{g}$-vector fan of~$\c{A}$ with respect to the initial acyclic seed~$\seed_\circ$ is a simplicial cone.
+More precisely, they fix a finite type cluster algebra~$\cal{A}$ and consider the real euclidean space~$\R^\cal{V}$ indexed by the set~$\cal{V}$ of cluster variables of~$\cal{A}$.
+Starting from an acyclic initial seed~$\seed_\circ$, they consider a set~$\cal{M}$ of mesh mutations and compute the corresponding linear dependences between the $\b{g}$-vectors, which can be interpreted as linear spaces in~$\R^\cal{V}$.
+Finally, they perturb these mesh linear spaces by a collection~$\b{\ell} \in \R^{\cal{M}}$ of positive parameters and intersect the resulting perturbed mesh affine spaces with the positive orthant of~$\R^\cal{V}$ (see \cref{subsec:typeConeCA}).
+They show that the resulting polytope is always a generalized associahedron, and that its normal fan is the $\b{g}$-vector fan of~$\cal{A}$ with respect to the initial acyclic seed~$\seed_\circ$.
+A by-product of their construction is that the space of all polytopal realizations of the $\b{g}$-vector fan of~$\cal{A}$ with respect to the initial acyclic seed~$\seed_\circ$ is a simplicial cone.
 
@@
 \medskip
+\enlargethispage{.1cm}
 Besides revisiting the construction of~\cite{ArkaniHamedBaiHeYan, BazierMatteDouvilleMousavandThomasYildirim} and extending it to any initial seed (acyclic or not) in any finite type cluster algebra (simply-laced or not), our reversed approach is also successful when applied to the $\b{g}$-vector fans of other families of generalizations of the associahedron.
@@
 Note that every complete fan is the product of an essential fan with its linearity space.
-For two fans~$\Fan, \c{G}$ in~$\R^d$, we say that~$\Fan$ \defn{refines}~$\c{G}$ (and that~$\c{G}$ \defn{coarsens}~$\Fan$) if every cone of~$\Fan$ is contained in a cone of~$\c{G}$.
+For two fans~$\Fan, \cal{G}$ in~$\R^d$, we say that~$\Fan$ \defn{refines}~$\cal{G}$ (and that~$\cal{G}$ \defn{coarsens}~$\Fan$) if every cone of~$\Fan$ is contained in a cone of~$\cal{G}$.
 
@@
 \begin{proof}
-Let $\c{G}$ be a simplicial refinement of $\Fan$.
-By~\cref{prop:non-simplicial}, the type cone of any coarsening of $\Fan$ is a relatively open cell of the hyperplane arrangement defined by adjacent pairs of~$\c{G}$.
+Let $\cal{G}$ be a simplicial refinement of $\Fan$.
+By~\cref{prop:non-simplicial}, the type cone of any coarsening of $\Fan$ is a relatively open cell of the hyperplane arrangement defined by adjacent pairs of~$\cal{G}$.
 The type cone of the coarsening is not empty whenever it is polytopal.
@@
 \item Mergings induced by extremal adjacent pairs are not the only ones that can take place in the boundary of~$\ctypeCone(\Fan)$.
-Indeed, if $\c{G}$ is the coarsening defining a lower-dimensional face~$\typeCone(\c{G})$ of~$\ctypeCone(\Fan)$, then to get $\Fan$ we have to perform all the coarsenings given by facets of~$\ctypeCone(\Fan)$ containing~$\typeCone(\c{G})$.
-But we might have to perform more coarsenings arising from exchangeable pairs  $\{\R_{\ge0}\rays, \R_{\ge0}\rays'\}$ whose inequality is redundant for~$\ctypeCone(\Fan)$ but tight for all points in~$\typeCone(\c{G})$.
+Indeed, if $\cal{G}$ is the coarsening defining a lower-dimensional face~$\typeCone(\cal{G})$ of~$\ctypeCone(\Fan)$, then to get $\Fan$ we have to perform all the coarsenings given by facets of~$\ctypeCone(\Fan)$ containing~$\typeCone(\cal{G})$.
+But we might have to perform more coarsenings arising from exchangeable pairs  $\{\R_{\ge0}\rays, \R_{\ge0}\rays'\}$ whose inequality is redundant for~$\ctypeCone(\Fan)$ but tight for all points in~$\typeCone(\cal{G})$.
 This situation arises when, in order to have a polytopal polyhedral fan, more pairs of adjacent cones must be merged.
@@
 \item Even if $\Fan$ is essential, not all its polytopal coarsenings need to be.
-Indeed, it can happen that there is a certain polytopal coarsening $\c{G}$ in which all the cells have a common linearity space.
-In this case, $\c{G}$ is the normal fan of a lower dimensional polytope (whose codimension is the dimension of the linearity space of $\c{G}$).
+Indeed, it can happen that there is a certain polytopal coarsening $\cal{G}$ in which all the cells have a common linearity space.
+In this case, $\cal{G}$ is the normal fan of a lower dimensional polytope (whose codimension is the dimension of the linearity space of $\cal{G}$).
 For this to happen, it is necessary (but not sufficient) that there is a positive linear dependence between some rays of $\Fan$.

### 2019-06-13 thirdPaper/draft/typeConeAssociahedra.tex
ameliorations intro

@@
 
-Finally, we use a similar approach to study the space of polytopal realizations of the $\b{g}$-vector fans of other generalizations of the associahedron.
+Moreover, we use a similar approach to study the space of polytopal realizations of the $\b{g}$-vector fans of other generalizations of the associahedron.
 For non-kissing complexes (a.k.a.
@@
 They show that the resulting polytope is always a generalized associahedron, and that its normal fan is the $\b{g}$-vector fan of~$\cal{A}$ with respect to the initial acyclic seed~$\seed_\circ$.
-A by-product of their construction is that the space of all polytopal realizations of the $\b{g}$-vector fan of~$\cal{A}$ with respect to the initial acyclic seed~$\seed_\circ$ is a simplicial cone.
+An implicit by-product of their construction is that the space of all polytopal realizations of the $\b{g}$-vector fan of~$\cal{A}$ with respect to the initial acyclic seed~$\seed_\circ$ is a simplicial cone.
 
@@
 \noindent
-These two aspects are interesting in their own right and might be useful in different communities: the geometric side enables to describe all polytopal realizations of a fan with simplicial type cone (which is sometimes easier to check than to find an explicit realization), while the algebraic side provides fundamental new results on the $\b{g}$-vectors of cluster algebras and on (an extriangulated variant of) the Grothendieck groups of~$2$-Calabi--Yau triangulated categories with cluster tilting objects.
+These two aspects are interesting in their own right and might be useful in different communities: the geometric side enables to simply describe all polytopal realizations of a fan with simplicial type cone (which is sometimes easier to check than to find an explicit realization), while the algebraic side provides fundamental new results on the $\b{g}$-vectors of cluster algebras and on (an extriangulated variant of) the Grothendieck groups of~$2$-Calabi--Yau triangulated categories with cluster tilting objects.
 We have therefore voluntarily split our presentation into two clearly marked parts that can be read independently.
@@
 These complexes encompass two families of simplicial complexes studied independently in the literature: on the one hand the grid associahedra introduced by T.~K.~Petersen, P.~Pylyavskyy and D.~Speyer in~\cite{PetersenPylyavskyySpeyer} for a staircase shape, studied by F.~Santos, C.~Stump and V.~Welker~\cite{SantosStumpWelker} for rectangular shapes, and extended by T.~McConville in~\cite{McConville} for arbitrary grid shapes; and on the other hand the Stokes polytopes and accordion associahedra studied by Y.~Baryshnikov~\cite{Baryshnikov}, F.~Chapoton~\cite{Chapoton-quadrangulations}, A.~Garver and T.~McConville~\cite{GarverMcConville} and T.~Manneville and V.~Pilaud~\cite{MannevillePilaud-accordion}.
-The latter, sometimes called accordiohedra, have also appeared in the mathematical physics litterature concerning scattering amplitudes~\cite{BanerjeeLaddhaRaman-StokesPolytopes, Raman-PositiveGeometry}, with realizations inspired by those in~\cite{ArkaniHamedBaiHeYan}.
+The latter, sometimes called accordiohedra, have also~recently appeared in the mathematical physics litterature concerning scattering amplitudes~\cite{BanerjeeLaddhaRaman-StokesPolytopes, Raman-PositiveGeometry}, with realizations inspired by those in~\cite{ArkaniHamedBaiHeYan}.
 It was shown in~\cite{PaluPilaudPlamondon-nonkissing, BrustleDouvilleMousavandThomasYildirim} that the non-kissing complex of a gentle bound quiver provides a combinatorial model for the support $\tau$-tilting complex~\cite{AdachiIyamaReiten} of the associated gentle algebra.
@@
 It would be interesting to get such volume formulas for polytopal realizations of $\b{g}$-vector fans of cluster algebras and gentle algebras, and combinatorial interpretations for their coefficients.
-
-\smallskip
-\item The associahedra constructed in~\cite{ArkaniHamedBaiHeYan, BazierMatteDouvilleMousavandThomasYildirim} and the present paper describe all polytopal realizations of the $\b{g}$-vector fan.
-This motivates the following question: Is it possible to similarly understand the complete realization space of the cluster complex, including all realizations not having the~$\b{g}$-vector fan as their normal fan?
 \end{itemize}
@@
 \noindent
-Some of these questions are explicitly indicated throughout the paper.
+Another question related to this paper is to understand the complete realization space of the combinatorics of the associahedra.
+The associahedra constructed in~\cite{ArkaniHamedBaiHeYan, BazierMatteDouvilleMousavandThomasYildirim} and the present paper describe all polytopal realizations of the $\b{g}$-vector fans, but there are other realizations of the combinatorics of the associahedra with different fans.
+Is it possible to similarly understand the complete realization space of the cluster complex, including all realizations not having the~$\b{g}$-vector fan as their normal fan?
 

### 2019-06-13 thirdPaper/draft/typeConeAssociahedra.tex
ameliorations intro

@@
 Finite type cluster complexes were geometrically realized first by F.~Chapoton, S.~Fomin and A.~Zelevinsky~\cite{ChapotonFominZelevinsky} based on the $\b{d}$-vector fans~\cite{FominZelevinsky-YSystems, FominZelevinsky-ClusterAlgebrasII} of the bipartite initial seed, then by~C.~Hohlweg, C.~Lange and H.~Thomas~\cite{HohlwegLangeThomas} based on the Cambrian fans~\cite{Reading-CambrianLattices, ReadingSpeyer} of acyclic initial seeds, and finally by C.~Hohlweg, V.~Pilaud and S.~Stella~\cite{HohlwegPilaudStella} based on the $\b{g}$-vector fans~\cite{FominZelevinsky-ClusterAlgebrasIV} with respect to an arbitrary initial seed.
-The resulting polytopes are known as generalized associahedra, and the classical associahedra corresponds to the cluster algebras~of~type~$A$.
+The resulting polytopes are known as generalized associahedra, and the classical associahedra corresponds to the type~$A$ cluster algebras.
 
@@
 \item \textbf{any initial seed}, regardless of whether it is acyclic or not (see \cref{exm:typeConeCA,fig:clusterFans,fig:labelFacetDefiningInequalititiesCA1,fig:labelFacetDefiningInequalititiesCA2} for examples in types~$A_3$ and~$C_3$~cyclic).
-In contrast, the proof of~\cite{BazierMatteDouvilleMousavandThomasYildirim} only treats acyclic initial seeds.
+In contrast, the proof of~\cite{BazierMatteDouvilleMousavandThomasYildirim} only treats acyclic initial seeds (though, H.~Thomas recently announced that this restriction will disappear in a future version of~\cite{BazierMatteDouvilleMousavandThomasYildirim}).
 

### 2019-06-13 thirdPaper/draft/typeConeAssociahedra.tex
Changes to section 3

--- 2019-06-13 thirdPaper/draft/typeConeAssociahedra.tex
@@
 \newcommand{\f}[1]{{\mathfrak{#1}}} % mathfrak letters
-\newcommand{\cal}[1]{{\mathcal{#1}}} % call letters
+\renewcommand{\c}[1]{{\mathcal{#1}}} % call letters
 \renewcommand{\b}[1]{{\boldsymbol{#1}}} % bold letters
@@
 For non-kissing complexes (a.k.a.
-support $\tau$-tilting complexes) of gentle algebras, we show that the space of realizations of the non-kissing fan is simplicial when the gentle bound quiver is brick and $2$-acyclic, and we describe in this case its facet-defining inequalities in terms of mesh mutations.
+support~$\tau$-tilting complexes) of gentle algebras, we show that the space of realizations of the non-kissing fan is simplicial when the gentle bound quiver is brick and $2$-acyclic, and we describe in this case its facet-defining inequalities in terms of mesh mutations.
 For graphical nested complexes, we show that the space of realizations of the nested fan is simplicial only in the case of the associahedron, and we describe its facet-defining inequalities in general.
@@
 
-The associahedron appears as a fundamental structure in several mathematical theories, such as moduli spaces and topology~\cite{Stasheff, Keller-AinfinityAlgebras}, operads and rewriting theory~\cite{Street, MasudaThomasTonksVallette}, combinatorial Hopf algebras~\cite{LodayRonco, ChatelPilaud, Pilaud-brickAlgebra}, diagonal harmonics~\cite{BergeronPrevilleRatelle, PrevilleRatelleViennot}, mathematical physics~\cite{ArkaniHamedBaiHeYan, BanerjeeLaddhaRaman-StokesPolytopes, Raman-PositiveGeometry}, etc.
+The associahedron appears as a fundamental structure in several mathematical theories, such as moduli spaces and topology~\cite{Stasheff, Keller-AinfinityAlgebras}, operads and rewriting theory~\cite{}, combinatorial Hopf algebras~\cite{LodayRonco, ChatelPilaud, Pilaud-brickAlgebra}, diagonal harmonics~\cite{}, mathematical physics~\cite{ArkaniHamedBaiHeYan, BanerjeeLaddhaRaman-StokesPolytopes, Raman-PositiveGeometry}, etc.
 Another striking illustration of the ubiquity of the associahedron lies in the theory of cluster algebras introduced by S.~Fomin and A.~Zelevinsky in~\cite{FominZelevinsky-ClusterAlgebrasI} with motivation coming from total positivity and canonical bases.
@@
 Finite type cluster complexes were geometrically realized first by F.~Chapoton, S.~Fomin and A.~Zelevinsky~\cite{ChapotonFominZelevinsky} based on the $\b{d}$-vector fans~\cite{FominZelevinsky-YSystems, FominZelevinsky-ClusterAlgebrasII} of the bipartite initial seed, then by~C.~Hohlweg, C.~Lange and H.~Thomas~\cite{HohlwegLangeThomas} based on the Cambrian fans~\cite{Reading-CambrianLattices, ReadingSpeyer} of acyclic initial seeds, and finally by C.~Hohlweg, V.~Pilaud and S.~Stella~\cite{HohlwegPilaudStella} based on the $\b{g}$-vector fans~\cite{FominZelevinsky-ClusterAlgebrasIV} with respect to an arbitrary initial seed.
-The resulting polytopes are known as generalized associahedra, and the classical associahedra corresponds to the cluster algebras~of~type~$A$.
+The resulting polytopes are known as generalized associahedra, and the classical associahedra corresponds to the cluster algebras of type~$A$.
 
@@
 These realizations were then extended by V.~Bazier-Matte, G.~Douville, K.~Mousavand, H.~Thomas and E.~Y\i ld\i r\i m~\cite{BazierMatteDouvilleMousavandThomasYildirim} in the context of finite type cluster algebras using tools from representation theory of quivers.
-More precisely, they fix a finite type cluster algebra~$\cal{A}$ and consider the real euclidean space~$\R^\cal{V}$ indexed by the set~$\cal{V}$ of cluster variables of~$\cal{A}$.
-Starting from an acyclic initial seed~$\seed_\circ$, they consider a set~$\cal{M}$ of mesh mutations and compute the corresponding linear dependences between the $\b{g}$-vectors, which can be interpreted as linear spaces in~$\R^\cal{V}$.
-Finally, they perturb these mesh linear spaces by a collection~$\b{\ell} \in \R^{\cal{M}}$ of positive parameters and intersect the resulting perturbed mesh affine spaces with the positive orthant of~$\R^\cal{V}$ (see \cref{subsec:typeConeCA}).
-They show that the resulting polytope is always a generalized associahedron, and that its normal fan is the $\b{g}$-vector fan of~$\cal{A}$ with respect to the initial acyclic seed~$\seed_\circ$.
-A by-product of their construction is that the space of all polytopal realizations of the $\b{g}$-vector fan of~$\cal{A}$ with respect to the initial acyclic seed~$\seed_\circ$ is a simplicial cone.
+More precisely, they fix a finite type cluster algebra~$\c{A}$ and consider the real euclidean space~$\R^\c{V}$ indexed by the set~$\c{V}$ of cluster variables of~$\c{A}$.
+Starting from an acyclic initial seed~$\seed_\circ$, they consider a set~$\c{M}$ of mesh mutations and compute the corresponding linear dependences between the $\b{g}$-vectors, which can be interpreted as linear spaces in~$\R^\c{V}$.
+Finally, they perturb these mesh linear spaces by a collection~$\b{\ell} \in \R^{\c{M}}$ of positive parameters and intersect the resulting perturbed mesh affine spaces with the positive orthant of~$\R^\c{V}$ (see \cref{subsec:typeConeCA}).
+They show that the resulting polytope is always a generalized associahedron, and that its normal fan is the $\b{g}$-vector fan of~$\c{A}$ with respect to the initial acyclic seed~$\seed_\circ$.
+A by-product of their construction is that the space of all polytopal realizations of the $\b{g}$-vector fan of~$\c{A}$ with respect to the initial acyclic seed~$\seed_\circ$ is a simplicial cone.
 
@@
 \medskip
-\enlargethispage{.1cm}
 Besides revisiting the construction of~\cite{ArkaniHamedBaiHeYan, BazierMatteDouvilleMousavandThomasYildirim} and extending it to any initial seed (acyclic or not) in any finite type cluster algebra (simply-laced or not), our reversed approach is also successful when applied to the $\b{g}$-vector fans of other families of generalizations of the associahedron.
@@
 Note that every complete fan is the product of an essential fan with its linearity space.
-For two fans~$\Fan, \cal{G}$ in~$\R^d$, we say that~$\Fan$ \defn{refines}~$\cal{G}$ (and that~$\cal{G}$ \defn{coarsens}~$\Fan$) if every cone of~$\Fan$ is contained in a cone of~$\cal{G}$.
+For two fans~$\Fan, \c{G}$ in~$\R^d$, we say that~$\Fan$ \defn{refines}~$\c{G}$ (and that~$\c{G}$ \defn{coarsens}~$\Fan$) if every cone of~$\Fan$ is contained in a cone of~$\c{G}$.
 
@@
 \begin{proof}
-Let $\cal{G}$ be a simplicial refinement of $\Fan$.
-By~\cref{prop:non-simplicial}, the type cone of any coarsening of $\Fan$ is a relatively open cell of the hyperplane arrangement defined by adjacent pairs of~$\cal{G}$.
+Let $\c{G}$ be a simplicial refinement of $\Fan$.
+By~\cref{prop:non-simplicial}, the type cone of any coarsening of $\Fan$ is a relatively open cell of the hyperplane arrangement defined by adjacent pairs of~$\c{G}$.
 The type cone of the coarsening is not empty whenever it is polytopal.
@@
 \item Mergings induced by extremal adjacent pairs are not the only ones that can take place in the boundary of~$\ctypeCone(\Fan)$.
-Indeed, if $\cal{G}$ is the coarsening defining a lower-dimensional face~$\typeCone(\cal{G})$ of~$\ctypeCone(\Fan)$, then to get $\Fan$ we have to perform all the coarsenings given by facets of~$\ctypeCone(\Fan)$ containing~$\typeCone(\cal{G})$.
-But we might have to perform more coarsenings arising from exchangeable pairs  $\{\R_{\ge0}\rays, \R_{\ge0}\rays'\}$ whose inequality is redundant for~$\ctypeCone(\Fan)$ but tight for all points in~$\typeCone(\cal{G})$.
+Indeed, if $\c{G}$ is the coarsening defining a lower-dimensional face~$\typeCone(\c{G})$ of~$\ctypeCone(\Fan)$, then to get $\Fan$ we have to perform all the coarsenings given by facets of~$\ctypeCone(\Fan)$ containing~$\typeCone(\c{G})$.
+But we might have to perform more coarsenings arising from exchangeable pairs  $\{\R_{\ge0}\rays, \R_{\ge0}\rays'\}$ whose inequality is redundant for~$\ctypeCone(\Fan)$ but tight for all points in~$\typeCone(\c{G})$.
 This situation arises when, in order to have a polytopal polyhedral fan, more pairs of adjacent cones must be merged.
@@
 \item Even if $\Fan$ is essential, not all its polytopal coarsenings need to be.
-Indeed, it can happen that there is a certain polytopal coarsening $\cal{G}$ in which all the cells have a common linearity space.
-In this case, $\cal{G}$ is the normal fan of a lower dimensional polytope (whose codimension is the dimension of the linearity space of $\cal{G}$).
+Indeed, it can happen that there is a certain polytopal coarsening $\c{G}$ in which all the cells have a common linearity space.
+In this case, $\c{G}$ is the normal fan of a lower dimensional polytope (whose codimension is the dimension of the linearity space of $\c{G}$).
 For this to happen, it is necessary (but not sufficient) that there is a positive linear dependence between some rays of $\Fan$.
@@
 The linear dependences of \cref{lem:linearDependencegvectorsCA} provide a redundant description of the type cone of the cluster fan~$\gvectorFan[\B_\circ]$.
-We denote by~$\b{n}(\B_\circ, x, x')$ the normal vector of the inequality of the type cone corresponding to two exchangeable cluster variables~$x$ to~$x'$ (it is well defined by \cref{prop:uniqueExchangePropertyCA}).
+We denote by~$\b{n}(\B_\circ, x, x')$ the normal vector of the inequality of the type cone corresponding to two exchangeable cluster variable~$x$ to~$x'$ (it is well defined by \cref{prop:uniqueExchangePropertyCA}).
 In other words, depending on which of the two linear dependences of \cref{lem:linearDependencegvectorsCA} holds, we have
@@
 
-The following statement is proved in \cref{coro::number of positive meshes}.
+%\vincent{Link to \cref{sec:clusterCategories}.}
 
@@
 \end{lemma}
-
-The following statement describes the linear dependence in the mesh mutations. It follows from \cref{lem:linearDependencegvectorsCA,def:meshMutation}.
+\begin{proof}
+ We postpone the proof until Corollary~\ref{coro::number of positive meshes}.
+\end{proof}
+
+The following statement describes the linear dependence in the mesh mutations.
 
@@
 
-\section{Relations for~$\b{g}$-vectors in finite type cluster algebras \\ via~$2$-Calabi--Yau triangulated categories}
+\section{Relations for~$\b{g}$-vectors in finite type cluster algebras via~$2$-Calabi--Yau triangulated categories}
 \label{sec:clusterCategories}
@@
 In~\cite{Auslander1984}, M.~Auslander showed that the relations in the Grothendieck group of an Artin algebra are generated by the ones given by almost-split sequences precisely when the algebra is of finite representation type.
-Inspired by this result, we will show that a similar statement holds (see \cref{theo::relations-g-vecteurs}) for the~$\b{g}$-vectors (or indices) of objects in a~$2$-Calabi--Yau triangulated category.
+Inspired by this result, we will show that a similar statement holds (\cref{theo::relations-g-vecteurs}) for the~$\b{g}$-vectors (or indices) of objects in a~$2$-Calabi--Yau triangulated category.
 
@@
 Thus the right-hand side is non-zero, and so neither is the left-hand side.
-By the above, this implies~${h \in (\susp T)\cat(\susp^{-1} X, \susp X)}$, which finishes the proof.
+By the above, this implies that~$h \in (\susp T)\cat(\susp^{-1} X, \susp X)$, which finishes the proof.
 \end{proof}
@@
 \label{lemm::bilinear-form}
-Let~$A$ and~$B$ be two indecomposable objects of~$\cat$. \pg{introduce general notation for redisue field}
+Let~$A$ and~$B$ be two indecomposable objects of~$\cat$. %\pg{introduce general notation for redisue field}
 \begin{enumerate}
@@
 \begin{proof}
-We only prove the first assertion; the second one is proved dually. Assume that ${A\notin\add(\susp T)}$. Let
+We only prove the first assertion; the second one is proved dually. Assume that~$A\notin\add(\susp T)$. Let
 \[
@@
 \]
-be an almost-split triangle. By \cref{lemm::almost-split}, the morphism~$h$ is in~$(\susp T)$. Applying the functor ${F=\cat(T,-)}$, we get an exact sequence
+be an almost-split triangle. By \cref{lemm::almost-split}, the morphism~$h$ is in~$(\susp T)$. Applying the functor~$F=\cat(T,-)$, we get an exact sequence
 \[
@@
 If~$B\ncong A$, then the definition of an almost-split triangle implies that~$f^*$ is surjective.
-Thus $\coker(f^*)=0$, so that~$\coker(Ff^*) = 0$, and by additivity of the dimension in exact sequences, we get that~$\langle \ell_A, B \rangle =0$.
+Thus~$\coker(f^*)=0$, so that~$\coker(Ff^*) = 0$, and by additivity of the dimension in exact sequences, we get that~$\langle \ell_A, B \rangle =0$.
 
@@
 \begin{enumerate}
-\item The set~$\set{[\ell_A]}{A \in \ind(\cat) \ssm \add(\susp T)} \cup \set{[\susp T_i]}{i \in [n]}$ is free in~$\Ksp(\cat)$.
-\item The set~$\set{[r_A]}{A \in \ind(\cat) \ssm \add(\susp T)} \cup \set{[\susp T_i]}{i \in [n]}$ is free in~$\Ksp(\cat)$.
+\item The set~$\set{[\ell_A]}{A \in \ind(\cat) \ssm \add(\susp T)} \cup \set{[\susp T_i]}{i=1, \dots, n}$ is free in~$\Ksp(\cat)$.
+\item The set~$\set{[r_A]}{A \in \ind(\cat) \ssm \add(\susp T)} \cup \set{[\susp T_i]}{i=1, \dots, n}$ is free in~$\Ksp(\cat)$.
 \end{enumerate}
@@
 \]
-But the~$[\susp T_i]$ are linearly independent in~$\Ksp(\cat)$. Thus~$\lambda_i = 0$ for all~$i \in [n]$. This finishes the proof.
+But the~$[\susp T_i]$ are linearly independent in~$\Ksp(\cat)$. Thus~$\lambda_i = 0$ for all~$i \in \{1, \ldots, n\}$. This finishes the proof.
 \end{proof}
@@
 \[
-\set{[\ell_A]}{A \in \ind(\cat) \ssm \add(\susp T)} \cup \set{[\susp T_i]}{i \in [n]}
+\set{[\ell_A]}{A \in \ind(\cat) \ssm \add(\susp T)} \cup \set{[\susp T_i]}{i=1, \ldots, n}
 \]
@@
 \]
-Then for any~$B \in \ind(\cat)$, we have that~$\langle z, [B] \rangle = 0$. By \cref{lemm::test-susp-T}, this implies that ${z \in \Ksp \big( \add(\susp T) \big)}$, and finishes the proof.
+Then for any~$B \in \ind(\cat)$, we have that~$\langle z, [B] \rangle = 0$. By \cref{lemm::test-susp-T}, this implies that~${z \in \Ksp \big( \add(\susp T) \big)}$, and finishes the proof.
 \end{proof}
@@
 
-Now,~$[T]+[\susp T]$ is in the kernel of~$\b{g}$, but~$\langle [T] + [\susp T], [B] \rangle = \langle [T], [B] \rangle = 0$ if and only if ${B \in \add(\susp T)}$. Thus~$\ind(\cat)$ has to be finite.
+Now,~$[T]+[\susp T]$ is in the kernel of~$\b{g}$, but~$\langle [T] + [\susp T], [B] \rangle = \langle [T], [B] \rangle = 0$ if and only if~$B \in \add(\susp T)$. Thus~$\ind(\cat)$ has to be finite.
 \end{proof}
@@
 \item[(i)] \emph{(}\cite[Prop.~3.2]{BuanMarshReinekeReitenTodorov} and~\cite[]{???} \emph{)} For any~$X,Y \in \ind(\cat)$, $\CC(X)$ and~$\CC(Y)$ are compatible if and only if~$\cat(X, \susp Y) = 0$.
-\item[(ii)] \emph{(}\cite[Prop.~4.3]{FuKeller} and \emph{)} For any~$X \in \ind(\cat)$, the~$\b{g}$-vector of~$\CC(X)$ is~$\b{g}([X])$, where we identify~$\Z^n$ and~$K_0(\cat ; T)$ via the isomorphism sending~$(a_1, \dots, a_n)$ to~$\sum_{i=1}^n a_i [T_i]$.
+\item[(ii)] \emph{(}\cite[Prop.~4.3]{FuKeller} and \emph{)} For any~$X \in \ind(\cat)$, the~$\b{g}$-vector of~$\CC(X)$ is~$\b{g}([X])$, where we identify~$\Z^n$ and~$K_0(\cat ; T)$ via the isomorphism sending~$(a_1, \ldots, a_n)$ to~$\sum_{i=1}^n a_i [T_i]$.
 \item[(iii)] \emph{(}\cite[Thm.~7.5]{BuanMarshReinekeReitenTodorov} and~\cite[]{???—} \emph{)} For any~$X,Y \in \ind(\cat)$, $\CC(X)$ and~$\CC(Y)$ are exchangeable if and only if~$\dim_{\field_X}\cat(X, \susp Y) = \dim_{\field_Y}\cat(X, \susp Y) = 1$.
@@
 
-\begin{definition}
-\label{defn::positive mutation}
+\begin{definition}\label{defn::positive mutation}
 Let~$x\in\cluster$ be a cluster variable in a given cluster and let~$x' \in \cluster'$ be obtained by mutating~$\cluster$ at~$x$.
@@
 
-\begin{lemma}
-\label{lemm::exaclty one mesh mutation}
-For every non-initial cluster variable, there exists precisely one pair~$(x,x')$ such that there exists a positive mesh mutation changing~$x$ into~$x'$.
+\begin{lemma}\label{lemm::exaclty one mesh mutation}
+ For every non-initial cluster variable~$x$, there exists precisely one pair~$(x,x')$ such that there exists a positive mesh mutation changing~$x$ into~$x'$.
 \end{lemma}
-
 \begin{proof}
  Up to isomorphism, there is precisely one almost-split triangle of~$\cat$ starting in~$X$, where~$X$ is the object such that~$\phi(X) = x$.
-Thus there is precisely one mesh relation By \cref{lemm::almost-split}, the pair~$(x,x')$ is a positive mutation if and only~$X\notin \add(\susp T)$, that is, if and only if~$x$ is not an initial variable.
-\end{proof}
-
-\begin{lemma}
-\label{lemm::mesh mutations and meshes}
-The set of positive mesh mutations~$(x,x')$ of \cref{defn::positive mutation} is in bijection with the set~$\meshes$ of~\cref{defn::positive mutation}.
+Thus there is precisely one mesh mutation.
+By Lemma~\ref{lemm::almost-split}, the pair~$(x,x')$ is a positive mutation if and only~$X\notin \add(\susp T)$, that is, if and only if~$x$ is not an initial variable.
+\end{proof}
+
+\begin{lemma}\label{lemm::mesh mutations and meshes}
+ The set of positive mesh mutations~$(x,x')$ of Definition~\ref{defn::positive mutation} is in bijection with the set~$\meshes$ from Definition~\ref{def:meshMutation}.
 \end{lemma}
-
 \begin{proof}
-If~$(x,x')$ is a positive mesh mutation, then~$\{x,x'\}$ is in~$\meshes$.  Indeed, if~$X$ and~$X'$ are the the corresponding objects in~$\cat$.  Then there is an almost-split triangle
+ If~$(x,x')$ is a positive mesh mutation, then~$\{x,x'\}$ is in~$\meshes$.  Indeed, if~$X$ and~$X'$ are the corresponding objects in~$\cat$, then there is an almost-split triangle
  \[
@@
 Moreover, there is a slice of the Auslander--Reiten quiver of~$\cat$ containing~$X$ and all indecomposable direct factors of~$E$.
-The direct sum of indecomposable objects in this slice is a cluster-tilting object in which~$X$ is a sink, and mutation at~$X$ gives~$X'$.
+The direct sum of indecomposable objects in this slice is a cluster-tilting object in which~$X$ is a source, and mutation at~$X$ gives~$X'$.
 Thus~$\{x,x'\}$ is in~$\meshes$.
-This gives an injective map from the set of positive mutations to~$\meshes$.
+This gives an injective map from the set of positive mesh mutations to~$\meshes$.
 
  \smallskip
+
  Next, assume that~$\{x,x'\}\in \meshes$ starts in~$x$.
-Then there is a cluster-tilting object~$T$ in~$\cat$ having~$X$ as a direct factor, and such that~$X$ is a sink in~$T$ and mutation at~$X$ yields~$X'$.
-Since~$X$ is a sink, the mutation triangle starting and ending in~$X$ are
+Then there is a cluster-tilting object~$T$ in~$\cat$ having~$X$ as a direct factor, and such that~$X$ is a source in~$T$ and mutation at~$X$ yields~$X'$.
+Since~$X$ is a source, the mutation triangle starting and ending in~$X$ are
  \[
@@
   Therefore~$X' = \susp^{-1}X = \tau^{-1}X$.
-Thus the first triangle is the almost-split triangle starting in~$X$.
-Since the pair~$\{x,x'\}$ is not initial, the mutation is a positive mesh mutation.
+Thus the first triangle is the almost-split triangle starting in~$X$, since the dimension of~$\cat(X',\susp X)$ is~$1$ over~$\field_{X'}$.
+Since the pair~$\{x,x'\}$ is not initial,~$\phi(X')$ is not an initial variable; in other words,~$X'$ is not in~$\add(T)$.
+Therefore,~$X = \tau X' = \susp X'$ is not in~$\add\susp T$, so the mutation is a positive mesh mutation by Lemma~\ref{lemm::almost-split}.
 This gives an injective map from~$\meshes$ to the set of positive mutations.
@@
 
-\begin{corollary}[\cref{lem:bijectionMeshMutations}]
+\begin{corollary}[Lemma~\ref{lem:bijectionMeshMutations}]
 \label{coro::number of positive meshes}
-We have that~$|\meshes|$ is the number of non-initial variables.
+ We have that~$|\meshes|$ is the number of non-initial cluster variables.
 \end{corollary}
-
 \begin{proof}
-This is a direct consequence of \cref{lemm::exaclty one mesh mutation,lemm::mesh mutations and meshes}.
+ This is a direct consequence of Lemmas~\ref{lemm::exaclty one mesh mutation} and~\ref{lemm::mesh mutations and meshes}.
 \end{proof}
@@
 By \cref{lemma:positive mutation triangles}, we may assume that the mutation under consideration is a positive mutation.
-In view of \cref{thm::categorification} (ii) and (iv) it is enough to show that the relation in~$K_0(\cat ; T)$ given by any triangle ${X\to E\to Y\xrightarrow{h} \susp X}$ with~$h\in(\susp T)$ is a positive linear combination of relations coming from Auslander--Reiten triangles with third term not in~$\add(\susp T)$.
+In view of \cref{thm::categorification} (ii) and (iv) it is enough to show that the relation in~$K_0(\cat ; T)$ given by any triangle~$X\to E\to Y\xrightarrow{h} \susp X$ with~$h\in(\susp T)$ is a positive linear combination of relations coming from Auslander--Reiten triangles with third term not in~$\add(\susp T)$.
 This categorified statement is precisely \cref{corollary::meshes positively generate cluster cats}.
@@
 Let~$\B_\circ$ be any finite type exchange matrix, and let~$\mathcal{A}(\B_\circ)$ be the associated cluster algebra without coefficients.
-Then, for any exchangeable cluster variables~$x$ and~$x'$, the linear dependence $\sum_{y \in \cluster \cup \cluster'} \coefficient[{\b{g}_y}][\cluster][\cluster'] \, \b{g}_y = 0$ only depends on the pair~$(x,x')$ and not on the specific choice of clusters~$\cluster$ and~$\cluster'$ containing~$x$ and~$x'$ respectively and such that~${\cluster\setminus\{x\}=\cluster'\setminus\{x'\}}$.
+Then, for any exchangeable cluster variables~$x$ and~$x'$, the linear dependence $\sum_{y \in \cluster \cup \cluster'} \coefficient[{\b{g}_y}][\cluster][\cluster'] \, \b{g}_y = 0$ only depends on the pair~$(x,x')$ and not on the specific choice of clusters~$\cluster$ and~$\cluster'$ containing~$x$ and~$x'$ respectively and such that~$\cluster\setminus\{x\}=\cluster'\setminus\{x'\}$.
 \end{corollary}
@@
 Let~$T\in\cat$ be a basic cluster tilting object such that~$\CC(T)$ is the initial cluster.
-By~\cref{lemma:positive mutation triangles}, the morphism~$h$ belongs to the ideal~$(\susp T)$.
-Therefore, the triangle ${X\to \bigoplus_i E_i \to Y \xrightarrow{h} \susp X}$ induces the relation~$[X]+[Y]=\sum_i [E_i]$ in~$K_0(\cat ; T)$.
+By \cref{lemma:positive mutation triangles}, the morphism~$h$ belongs to the ideal~$(\susp T)$.
+Therefore, the triangle~$X\to \bigoplus_i E_i \to Y \xrightarrow{h} \susp X$ induces the relation~$[X]+[Y]=\sum_i [E_i]$ in~$K_0(\cat ; T)$.
 \cref{thm::categorification} (ii) gives the equality~$\b{g}_{\CC(X)} + \b{g}_{\CC(Y)} = \sum_i\b{g}_{\CC(E_i)}$, where the~$\b{g}$-vectors are computed with respect to the initial seed~$\CC(T)$.
@@
 
-We indifferently call \emph{conflations}, written~$X\infl Y\defl Z$, or \emph{extriangles}, written ${X\infl Y\defl Z \overset{\delta}{\dashrightarrow}}$, the analogues of short exact sequences or triangles in an extriangulated category.
+We indifferently call \emph{conflations}, written~$X\infl Y\defl Z$, or \emph{extriangles}, written~$X\infl Y\defl Z \overset{\delta}{\dashrightarrow}$, the analogues of short exact sequences or triangles in an extriangulated category.
 
@@
 A \defn{split}~$\mathbb{E}$-extension is a zero element~$0\in\mathbb{E}(Z,X)$, for some objects~$X,Z\in\cat$.
-For any two~$\mathbb{E}$-exten\-sions~${\delta\in\mathbb{E}(Z,X)}$, $\delta'\in\mathbb{E}(Z',X')$, the additivity of~$\cat$,~$\mathbb{E}$ permits to define the~$\mathbb{E}$-extension
+For any two~$\mathbb{E}$-extensions~$\delta\in\mathbb{E}(Z,X)$,~$\delta'\in\mathbb{E}(Z',X')$, the additivity of~$\cat$,~$\mathbb{E}$ permits to define the~$\mathbb{E}$-extension
 \[
@@
 Let~$\delta\in\mathbb{E}(Z,X)$ be an~$\mathbb{E}$-extension.
-By functoriality, any morphisms~$f\in\cat(X,X')$ and~$h\in\cat(Z',Z)$ induce~$\mathbb{E}$-extensions~$\mathbb{E}(Z,f)(\delta)\in\mathbb{E}(Z,X') \text{ and } \mathbb{E}(h,X)(\delta)\in\mathbb{E}(Z',X)$.
+By functoriality, any morphisms~$f\in\cat(X,X')$ and~$h\in\cat(Z',Z)$ induce~$\mathbb{E}$-extensions~$\mathbb{E}(Z,f)(\delta)\in\mathbb{E}(Z,X')\ \ \text{and}\ \ \mathbb{E}(h,X)(\delta)\in\mathbb{E}(Z',X)$.
 For short, we write~$f_\ast\delta$ and~$h^\ast\delta$ instead.
 Using those notations, we have, in~$\mathbb{E}(Z',X')$
-\[
-\mathbb{E}(h,f)(\delta)=h^\ast f_\ast\delta=f_\ast h^\ast\delta.
-\]
+\[ \mathbb{E}(h,f)(\delta)=h^\ast f_\ast\delta=f_\ast h^\ast\delta. \]
 \end{remark}
@@
 Let~$X,Z\in\cat$ be any two objects. Two sequences of morphisms in~$\cat$
-\[
-X \overset{x}{\longrightarrow}Y\overset{y}{\longrightarrow}Z \text{ and } X\overset{x'}{\longrightarrow}Y'\overset{y'}{\longrightarrow}Z
-\]
+\[ X \overset{x}{\longrightarrow}Y\overset{y}{\longrightarrow}Z \ \text{ and } \ X\overset{x'}{\longrightarrow}Y'\overset{y'}{\longrightarrow}Z \]
 are said to be \defn{equivalent} if there exists an isomorphism~$g\in\cat(Y,Y')$ such that the following diagram commutes.
@@
 \begin{definition}
-An \defn{additive realization}~$\mathfrak{s}$ is a correspondence associating, with~$\mathbb{E}$-extension ${\delta\in\mathbb{E}(Z,X)}$, an equivalence class~$\mathfrak{s}(\delta)=[X\xrightarrow{x}Y\xrightarrow{y}Z]$ and satisfying the following condition:
+An \defn{additive realization}~$\mathfrak{s}$ is a correspondence associating, with~$\mathbb{E}$-extension~$\delta\in\mathbb{E}(Z,X)$, an equivalence class~$\mathfrak{s}(\delta)=[X\xrightarrow{x}Y\xrightarrow{y}Z]$ and satisfying the following condition:
 \begin{itemize}
@@
 \[
-X\overset{f}{\longrightarrow}Y\overset{f'}{\longrightarrow}Z' \quad\text{and}\quad Y\overset{g}{\longrightarrow}Z\overset{g'}{\longrightarrow}X'.
+X\overset{f}{\longrightarrow}Y\overset{f'}{\longrightarrow}Z'\ \text{ and } \ Y\overset{g}{\longrightarrow}Z\overset{g'}{\longrightarrow}X'.
 \]
@@
 Then the following sequences of natural transformations are exact:
-\[
-\cat(Z,-)\overset{-\circ y}{\longrightarrow}\cat(Y,-)\overset{-\circ x}{\longrightarrow}\cat(X,-)\overset{\delta^\sharp}{\longrightarrow}\mathbb{E}(Z,-)\overset{y^\ast}{\longrightarrow}\mathbb{E}(Y,-)\overset{x^\ast}{\longrightarrow}\mathbb{E}(X,-),
-\]
-\[
-\cat(-,X)\overset{x\circ-}{\longrightarrow}\cat(-,Y)\overset{y\circ-}{\longrightarrow}\cat(-,Z)\overset{\delta_\sharp}{\longrightarrow}\mathbb{E}(-,X)\overset{x_\ast}{\longrightarrow}\mathbb{E}(-,Y)\overset{y_\ast}{\longrightarrow}\mathbb{E}(-,Z),
-\]
+\[ \cat(Z,-)\overset{-\circ y}{\longrightarrow}\cat(Y,-)\overset{-\circ x}{\longrightarrow}\cat(X,-)\overset{\delta^\sharp}{\longrightarrow}\mathbb{E}(Z,-)\overset{y^\ast}{\longrightarrow}\mathbb{E}(Y,-)\overset{x^\ast}{\longrightarrow}\mathbb{E}(X,-), \]
+\[ \cat(-,X)\overset{x\circ-}{\longrightarrow}\cat(-,Y)\overset{y\circ-}{\longrightarrow}\cat(-,Z)\overset{\delta_\sharp}{\longrightarrow}\mathbb{E}(-,X)\overset{x_\ast}{\longrightarrow}\mathbb{E}(-,Y)\overset{y_\ast}{\longrightarrow}\mathbb{E}(-,Z), \]
 where~$\delta^\sharp(f)=f_\ast\delta$ and~$\delta_\sharp(g)=g^\ast\delta$.
@@
 \[
-T_1^X\overset{f_X}{\infl} T_0^X\overset{g_X}{\defl} X \overset{\delta_X}{\dashrightarrow}, \quad T_0^X\infl 0\defl \susp T_0^X\overset{\delta_0}{\dashrightarrow}, \quad T_1^X\infl 0\defl \susp T_1^X\overset{\delta_1}{\dashrightarrow}
+T_1^X\overset{f_X}{\infl} T_0^X\overset{g_X}{\defl} X \overset{\delta_X}{\dashrightarrow}, \ \ \ T_0^X\infl 0\defl \susp T_0^X\overset{\delta_0}{\dashrightarrow}, \ \ \ T_1^X\infl 0\defl \susp T_1^X\overset{\delta_1}{\dashrightarrow}
 \]
@@
 \[
-T_0^X\overset{g_X}{\infl} X \overset{h_X}{\defl} \susp T_1^X \overset{(f_X)_\ast\delta_1}{\dashrightarrow}, \quad X \overset{h_X}{\infl} \susp T_1^X \overset{\susp f_X}{\defl} \susp T_0^X \overset{(g_X)_\ast\delta_0}{\dashrightarrow}
+T_0^X\overset{g_X}{\infl} X \overset{h_X}{\defl} \susp T_1^X \overset{(f_X)_\ast\delta_1}{\dashrightarrow}, \ \ \ X \overset{h_X}{\infl} \susp T_1^X \overset{\susp f_X}{\defl} \susp T_0^X \overset{(g_X)_\ast\delta_0}{\dashrightarrow}
 \]
@@
 For any~$T\in\tc$, fix an extriangle~$T\infl 0\defl\susp T\overset{\eps_T}{\dashrightarrow}$.
-As noticed in \cref{lemma::shifts of extriangles}, for any morphism~$T\overset{f}{\to}T'$ in~$\tc$, there is a unique morphism~$\susp f\in\cat(\susp T,\susp T')$ such that~${f_\ast\eps_T=(\susp f)^\ast\eps_{T'}}$ (i.e.
+As noticed in \cref{lemma::shifts of extriangles}, for any morphism~$T\overset{f}{\to}T'$ in~$\tc$, there is a unique morphism~$\susp f\in\cat(\susp T,\susp T')$ such that~$f_\ast\eps_T=(\susp f)^\ast\eps_{T'}$ (i.e.
 such that~$(f,\susp f)$ is a morphism from~$\eps_T$ to~$\eps_{T'}$), as illustrated below:
@@
 \[
-{\rm (3')} \quad \cat = \tc\ast\susp\tc.
+{\rm (3')} \ \ \ \cat = \tc\ast\susp\tc.
 \]
@@
 \endxy
-\quad \quad \ \
+\ \ \ \ \ \ \ \
 \xy
@@
 
-In particular, the leftmost morphisms of both mutation conflations are minimal ${\add \big( P(\mu) \oplus P(\nu) \big)}$-approximations of~$P(\omega)$.
+In particular, the leftmost morphisms of both mutation conflations are both minimal~$\add \big( P(\mu) \oplus P(\nu) \big)$-approximations of~$P(\omega)$.
 As such, they are isomorphic as morphisms.
@@
 Because~$X$ is concentrated in non-positive degrees,~$F\susp X=0$.
-Let us verify that the map ${F\susp^{-1}Y\to F\susp^{-1}Z}$ is surjective.
+Let us verify that the map~$F\susp^{-1}Y\to F\susp^{-1}Z$ is surjective.
 Let~$\Lambda \xrightarrow{f} \susp^{-1} Z$ be a morphism in~$K^b(\proj \Lambda)$.
@@
 For convenience of the reader, we recall those two results: Let~$Y, Z \in K^{[-1,0]}(\proj\Lambda)$ be indecomposable and not in~$\add(\susp\Lambda)$, and let~$P\in\proj\Lambda$.
-Then~$\Hom{K^b}(Y,\susp Z)=0$ if and only if~$\Hom{\Lambda}(FZ,\tau FY)=0$ and~${\Hom{K^b}(P,Y)=0}$ if and only if~$\Hom{\Lambda}(P,FY)=0$.
+Then~$\Hom{K^b}(Y,\susp Z)=0$ if and only if~$\Hom{\Lambda}(FZ,\tau FY)=0$ and~$\Hom{K^b}(P,Y)=0$ if and only if~$\Hom{\Lambda}(P,FY)=0$.
 
@@
 % Then~$Y\infl E\defl \susp P$ is an Auslander--Reiten conflation in~$K^{[-1,0]}(\proj\Lambda)$, which is also a mutation conflation.
-Then the Auslander--Reiten conflation~${Y\infl E\defl \susp P}$ in~$K^{[-1,0]}(\proj\Lambda)$ is a mutation conflation if~$FY$ is a brick.
+Then the Auslander--Reiten conflation~$Y\infl E\defl \susp P$ in~$K^{[-1,0]}(\proj\Lambda)$ is a mutation conflation if~$FY$ is a brick.
 \end{lemma}
@@
 where the vertical maps are surjective.
-Since~$\Lambda$ is rigid and~$Y$ is two-term, we can apply~\cite[Prop.~6.2]{IyamaYoshino} to the triangulated category~$K^b(\proj\Lambda)$ (or \cref{prop::KRextricat} to the extriangulated $K^{[-1,0]}(\proj\Lambda)$).
+Since~$\Lambda$ is rigid and~$Y$ is two-term, we can apply~\cite[Prop.~6.2]{IyamaYoshino} to the triangulated category~$K^b(\proj\Lambda)$ (or \cref{prop::KRextricat} to the extriangulated~$K^{[-1,0]}(\proj\Lambda)$).
 As a consequence, the right-most vertical map is bijective.
@@
 \]
-modulo the relation~$\gamma\beta\alpha = 0$. The Auslander--Reiten quiver of the extriangulated category $K^{[-1, 0]}(\proj\Lambda)$ is depicted below.
+modulo the relation~$\gamma\beta\alpha = 0$. The Auslander--Reiten quiver of the extriangulated category~$K^{[-1, 0]}(\proj\Lambda)$ is depicted below.
 \[

### 2019-06-13 thirdPaper/draft/typeConeAssociahedra.tex

--- 2019-06-13 thirdPaper/draft/typeConeAssociahedra.tex
@@
 
-\subsubsection{Simplicial type cones for self-kissing-free and $2$-cycle-free quivers}
+\subsubsection{Simplicial type cones for brick and $2$-acyclic gentle bound quivers}
 \label{subsubsec:simplicialTypeConeNKC}
@@
 \begin{proof}
-If~$(x,x')$ is a positive mesh mutation, then~$\{x,x'\}$ is in~$\meshes$.  Indeed, if~$X$ and~$X'$ are the the corresponding objects in~$\cat$.  Then there is an almost-split triangle
+ If~$(x,x')$ is a positive mesh mutation, then~$\{x,x'\}$ is in~$\meshes$.  Indeed, if~$X$ and~$X'$ are the corresponding objects in~$\cat$, then there is an almost-split triangle
  \[
@@
 \label{coro::number of positive meshes}
-We have that~$|\meshes|$ is the number of non-initial variables.
+ We have that~$|\meshes|$ is the number of non-initial cluster variables.
 \end{corollary}

### 2019-06-13 thirdPaper/draft/typeConeAssociahedra.tex
Removed comments

@@
 We first recall the results on categorification of cluster algebras that we will make use of in the proofs.
-\begin{theorem}[]\pg{cite???}
+\begin{theorem}
 \label{thm::categorification}
@@
 \begin{itemize}
-\item[(i)] \emph{(}\cite[Prop.~3.2]{BuanMarshReinekeReitenTodorov} and~\cite[]{???} \emph{)} For any~$X,Y \in \ind(\cat)$, $\CC(X)$ and~$\CC(Y)$ are compatible if and only if~$\cat(X, \susp Y) = 0$.
-\item[(ii)] \emph{(}\cite[Prop.~4.3]{FuKeller} and \emph{)} For any~$X \in \ind(\cat)$, the~$\b{g}$-vector of~$\CC(X)$ is~$\b{g}([X])$, where we identify~$\Z^n$ and~$K_0(\cat ; T)$ via the isomorphism sending~$(a_1, \dots, a_n)$ to~$\sum_{i=1}^n a_i [T_i]$.
-\item[(iii)] \emph{(}\cite[Thm.~7.5]{BuanMarshReinekeReitenTodorov} and~\cite[]{???—} \emph{)} For any~$X,Y \in \ind(\cat)$, $\CC(X)$ and~$\CC(Y)$ are exchangeable if and only if~$\dim_{\field_X}\cat(X, \susp Y) = \dim_{\field_Y}\cat(X, \susp Y) = 1$.
-\item[(iv)]\emph{(}\cite[???]{BuanMarshReinekeReitenTodorov} and~\cite[???]{BuanIyamaReitenScott} and ???\emph{)} Let~$T'$ be any basic cluster-tilting object of~$\cat$.
+\item[(i)] \emph{(}\cite[Prop.~3.2]{BuanMarshReinekeReitenTodorov}\emph{)} For any~$X,Y \in \ind(\cat)$, $\CC(X)$ and~$\CC(Y)$ are compatible if and only if~$\cat(X, \susp Y) = 0$.
+\item[(ii)] \emph{(}\cite[Prop.~4.3]{FuKeller} and \cite[Prop.~2.2]{Palu}, where the proofs also work over an arbitrary base field\emph{)} For any~$X \in \ind(\cat)$, the~$\b{g}$-vector of~$\CC(X)$ is~$\b{g}([X])$, where we identify~$\Z^n$ and~$K_0(\cat ; T)$ via the isomorphism sending~$(a_1, \dots, a_n)$ to~$\sum_{i=1}^n a_i [T_i]$.
+\item[(iii)] \emph{(}\cite[Thm.~7.5]{BuanMarshReinekeReitenTodorov}\emph{)} For any~$X,Y \in \ind(\cat)$, $\CC(X)$ and~$\CC(Y)$ are exchangeable if and only if~$\dim_{\field_X}\cat(X, \susp Y) = \dim_{\field_Y}\cat(X, \susp Y) = 1$.
+\item[(iv)]\emph{(}\cite{BuanIyamaReitenScott} and \cite[Thm.~5.1]{BuanMarshReiten-mutation}, adapted to the cluster categories of species of Dynkin type\emph{)} Let~$T'$ be any basic cluster-tilting object of~$\cat$.
 Then the matrix~$B'$ of the associated seed~$(\CC(T'),B')$ is given by the multiplicities of the middle terms of the exchange triangles.
-More explicitely,
 \end{itemize}
@@
 
-\vincent{Careful.
+% \vincent{Careful.
 There is a convention change with \cref{subsec:typeConeCA} and \cref{fig:labelFacetDefiningInequalititiesCA1,fig:labelFacetDefiningInequalititiesCA2}.
@@
 
-\yann{I think that our conventions coincide.
+% \yann{I think that our conventions coincide.
 With the choice of the Hom functor, $\susp T$ is sent to the initial seed so that the AR triangles ending in $\add(\susp T)$ are precisely the meshes ending in an initial variable}
@@
 \para{Setting for Section~\ref{sect::prelim on extricats}}
-In that section, we let~$\cat$ be an extriangulated category with a fixed full additive \yann{additive contains strictly full + stable under taking summands} subcategory~$\tc$ satisfying the following three properties:
+In that section, we let~$\cat$ be an extriangulated category with a fixed full additive subcategory~$\tc$, stable under isomorphisms, under taking direct summands, and satisfying the following three properties:
 \begin{enumerate}
@@
 
-\yann{Applying $X\mapsto\mathbb{E}(-,X)|_{\susp\tc}$ might solve this issue?}
-
 \begin{definition}
@@
 
-The notion of index from~\cite{DehyKeller,Palu} \yann{ref RVdB ou BB ou ?, also studied in ....} generalises to our current setting.
+The notion of index from~\cite{DehyKeller,Palu} generalises to our current setting.
 
@@
 
-\vincent{Here should be explained that the gentle algebra result is a special case of this.}
+% \vincent{Here should be explained that the gentle algebra result is a special case of this.}
 
@@
 
-We now describe a setup satisfying the assumptions of \cref{setting::extricat} that, at the same time, subsumes all examples given so far, while being easily checked in practice.\yann{A reformuler...}
-
-Let~$(\ec,\mathbb{E},\mathfrak{s})$ be an extriangulated category (for example, a small exact category or a triangulated category), and let~$\tc$ be an essentially small \yann{Cette hypoth\`ese n'appara\^it pas dans [HLN], mais me semble n\'ecessaire...} subcategory of~$\ec$.
+We now describe a setup satisfying the assumptions of \cref{setting::extricat} that, at the same time, subsumes all examples given so far, while being easily checked in practice.
+
+Let~$(\ec,\mathbb{E},\mathfrak{s})$ be an extriangulated category (for example, a small exact category or a triangulated category), and let~$\tc$ be an essentially small subcategory of~$\ec$.
 

### 2019-06-13 thirdPaper/draft/typeConeAssociahedra.tex
Minor change in intro and added reference

@@
 \item \textbf{any initial seed}, regardless of whether it is acyclic or not (see \cref{exm:typeConeCA,fig:clusterFans,fig:labelFacetDefiningInequalititiesCA1,fig:labelFacetDefiningInequalititiesCA2} for examples in types~$A_3$ and~$C_3$~cyclic).
-In contrast, the proof of~\cite{BazierMatteDouvilleMousavandThomasYildirim} only treats acyclic initial seeds (though, H.~Thomas recently announced that this restriction will disappear in a future version of~\cite{BazierMatteDouvilleMousavandThomasYildirim}).
+In contrast, the proof of~\cite{BazierMatteDouvilleMousavandThomasYildirim} only treats acyclic initial seeds (although H.~Thomas announced in a lecture given at RIMS in June 2019 that this restriction will disappear in a future version of~\cite{BazierMatteDouvilleMousavandThomasYildirim}).
 

### 2019-06-13 thirdPaper/draft/typeConeAssociahedra.tex
minor typo changes

@@
 Its realizations can be classified into three species: the secondary polytopes~\cite{GelfandKapranovZelevinsky, BilleraFillimanSturmfels}, the $\b{g}$-vectors realizations~\cite{Loday, HohlwegLange, LangePilaud, HohlwegLangeThomas, HohlwegPilaudStella, Postnikov, PilaudSantos-brickPolytope, PilaudStump-brickPolytope} and the $\b{d}$-vector realizations~\cite{ChapotonFominZelevinsky, CeballosSantosZiegler}.
-See~\cite{CeballosSantosZiegler} for a discussion of these realizations and their connections.
+See~\cite{CeballosSantosZiegler} for a discussion of some of these realizations and their connections.
 
@@
 Starting from an acyclic initial seed~$\seed_\circ$, they consider a set~$\cal{M}$ of mesh mutations and compute the corresponding linear dependences between the $\b{g}$-vectors, which can be interpreted as linear spaces in~$\R^\cal{V}$.
-Finally, they perturb these mesh linear spaces by a collection~$\b{\ell} \in \R^{\cal{M}}$ of positive parameters and intersect the resulting perturbed mesh affine spaces with the positive orthant of~$\R^\cal{V}$ (see \cref{subsec:typeConeCA}).
+Finally, they perturb these mesh linear spaces by a collection~$\b{\ell} \in \R_{>0}^{\cal{M}}$ of positive parameters and intersect the resulting perturbed mesh affine spaces with the positive orthant~$\R_{\ge 0}^\cal{V}$ (see \cref{subsec:typeConeCA}).
 They show that the resulting polytope is always a generalized associahedron, and that its normal fan is the $\b{g}$-vector fan of~$\cal{A}$ with respect to the initial acyclic seed~$\seed_\circ$.
@@
 Given a complete simplicial fan~$\Fan$, we consider the space~$\typeCone(\Fan)$ of all its polytopal realizations.
-This space was called type cone of~$\Fan$ in~\cite{McMullen-typeCone} and deformation cone of~$\Fan$ in~\cite{Postnikov, PostnikovReinerWilliams}, who studied the case when~$\Fan$ is the braid arrangement leading to the rich theory of generalized permutahedra (recently extended to all finite Coxeter arrangements in~\cite{ACEP-DeformationsCoxeterPermutahedra}).
+This space was called type cone in~\cite{McMullen-typeCone} and deformation cone in~\cite{Postnikov, PostnikovReinerWilliams}, who studied the case when~$\Fan$ is the braid arrangement leading to the rich theory of generalized permutahedra (recently extended to all finite Coxeter arrangements in~\cite{ACEP-DeformationsCoxeterPermutahedra}).
 The type cone is known to be a polyhedral cone defined by a collection of inequalities corresponding to the linear dependences among the rays of~$\Fan$ contained in pairs of adjacent maximal cones of~$\Fan$ (see \cref{def:typeCone}).
@@
 
-In this section, we apply the results of \cref{subsect::Statement cluster cats} in order to prove \cref{prop:uniqueExchangePropertyCA} and \cref{prop:meshMutations} of \cref{subsec:typeConeCA}.
-
-We first recall the results on categorification of cluster algebras that we will make use of in the proofs.
+In this section, we apply the results of \cref{subsect::Statement cluster cats} in order to prove \cref{prop:uniqueExchangePropertyCA,prop:meshMutations} of \cref{subsec:typeConeCA}.
+
+We first recall the results on categorification of cluster algebras that we will use in the proofs.
 \begin{theorem}
@@
 \begin{proof}
+\enlargethispage{.3cm}
 If~$(x,x')$ is a positive mesh mutation, then~$\{x,x'\}$ is in~$\meshes$.  Indeed, if~$X$ and~$X'$ are the corresponding objects in~$\cat$, then there is an almost-split triangle
@@
 Since the pair~$\{x,x'\}$ is not initial,~$\phi(X')$ is not an initial variable; in other words,~$X'$ is not in~$\add(T)$.
-Therefore,~$X = \tau X' = \susp X'$ is not in~$\add\susp T$, so the mutation is a positive mesh mutation by Lemma~\ref{lemm::almost-split}.
+Therefore,~$X = \tau X' = \susp X'$ is not in~$\add\susp T$, so the mutation is a positive mesh mutation by \cref{lemm::almost-split}.
 This gives an injective map from~$\meshes$ to the set of positive mutations.
@@
 \label{coro::number of positive meshes}
- We have that~$|\meshes|$ is the number of non-initial cluster variables.
+We have that~$|\meshes|$ is the number~$|\variables[\B_\circ]|-n$ of non-initial cluster variables.
 \end{corollary}
@@
 \begin{proof}
-In view of \cref{thm::categorification} (iii), it follows from~\cite[Lem.~3.3]{Palu}.
+In view of \cref{thm::categorification}\,(iii), it follows from~\cite[Lem.~3.3]{Palu}.
 \end{proof}
@@
 By \cref{lemma:positive mutation triangles}, we may assume that the mutation under consideration is a positive mutation.
-In view of \cref{thm::categorification} (ii) and (iv) it is enough to show that the relation in~$K_0(\cat ; T)$ given by any triangle ${X\to E\to Y\xrightarrow{h} \susp X}$ with~$h\in(\susp T)$ is a positive linear combination of relations coming from Auslander--Reiten triangles with third term not in~$\add(\susp T)$.
+In view of \cref{thm::categorification}\,(ii) and (iv) it is enough to show that the relation in~$K_0(\cat ; T)$ given by any triangle ${X\to E\to Y\xrightarrow{h} \susp X}$ with~$h\in(\susp T)$ is a positive linear combination of relations coming from Auslander--Reiten triangles with third term not in~$\add(\susp T)$.
 This categorified statement is precisely \cref{corollary::meshes positively generate cluster cats}.
@@
 
-It also follows form \cref{thm::categorification} above that any cluster algebra of finite type has the unique exchange relation property (see \cref{def:uerp}):
+It also follows from \cref{thm::categorification} above that any cluster algebra of finite type has the unique exchange relation property (see \cref{def:uerp}).
+
 \begin{corollary}
@@
 Let~$T\in\cat$ be a basic cluster tilting object such that~$\CC(T)$ is the initial cluster.
-By~\cref{lemma:positive mutation triangles}, the morphism~$h$ belongs to the ideal~$(\susp T)$.
+According to~\cref{lemma:positive mutation triangles}, the morphism~$h$ belongs to the ideal~$(\susp T)$.
 Therefore, the triangle ${X\to \bigoplus_i E_i \to Y \xrightarrow{h} \susp X}$ induces the relation~$[X]+[Y]=\sum_i [E_i]$ in~$K_0(\cat ; T)$.
-\cref{thm::categorification} (ii) gives the equality~$\b{g}_{\CC(X)} + \b{g}_{\CC(Y)} = \sum_i\b{g}_{\CC(E_i)}$, where the~$\b{g}$-vectors are computed with respect to the initial seed~$\CC(T)$.
-By \cref{thm::categorification} (iii), the middle term of the triangle is uniquely defined, up to isomorphism, by~$X$, and~$Y$, and the triangle is therefore an exchange triangle, with respect to any mutation at~$X$: it does not depend on the choice of a cluster tilting object containing~$X$.
-By \cref{thm::categorification} (iv) this equality is one of the two equalities in \cref{lem:linearDependencegvectorsCA}.
+\cref{thm::categorification}\,(ii) gives the equality ${\b{g}_{\CC(X)} + \b{g}_{\CC(Y)} = \sum_i\b{g}_{\CC(E_i)}}$, where the~$\b{g}$-vectors are computed with respect to the initial seed~$\CC(T)$.
+By \cref{thm::categorification}\,(iii), the middle term of the triangle is uniquely defined, up to isomorphism, by~$X$, and~$Y$, and the triangle is therefore an exchange triangle, with respect to any mutation at~$X$: it does not depend on the choice of a cluster tilting object containing~$X$.
+By \cref{thm::categorification}\,(iv) this equality is one of the two equalities in \cref{lem:linearDependencegvectorsCA}.
 \end{proof}
@@
 
+\smallskip
 \para{Setting for Section~\ref{sect::prelim on extricats}}
@@
 
+\smallskip
 \para{Setting for Section~\ref{sect::Statment extricats}}
@@
 
-An extriangulated category is the data of an additive category~$\cat$, an additive bifunctor~$\mathbb{E}:\cat^\mathrm{op}\times\cat\to \mathit{Ab}$ modelling the~$\operatorname{Ext}^1$-bifunctor, and an additive realization~$\mathfrak{s}$ sending each element~$\delta\in\mathbb{E}(Z,X)$ to some (equivalence classe of) diagram~$X\to Y\to Z$ modelling the short exact sequences or triangles.
+An extriangulated category is the data of an additive category~$\cat$, of an additive bifunctor ${\mathbb{E}:\cat^\mathrm{op}\times\cat\to \mathit{Ab}}$ modelling the~$\operatorname{Ext}^1$-bifunctor, and of an additive realization~$\mathfrak{s}$ sending each element~$\delta\in\mathbb{E}(Z,X)$ to some (equivalence classe of) diagram~$X\to Y\to Z$ modelling the short exact sequences or triangles.
 Some axioms, inspired from the case of extension-closed subcategories of triangulated categories have to be satisfied.
@@
 For any non-split $\mathbb{E}$-extension $\delta\in\mathbb{E}(Z,X)$, the following holds.
-\begin{enumerate}[{\rm (1)}]
+\begin{enumerate}
 \item If $\delta$ satisfies {\rm (AS1)}, then $X$ is endo-local.
@@
 The following holds:
-\begin{enumerate}[{\rm (a)}]
+\begin{enumerate}[(i)]
 \item An object belongs to~$\tc$ if and only if it is projective in~$\cat$.
@@
 \begin{proof}
-(a) If~$X$ is projective in~$\cat$, then the deflation~$T_0^X\defl X$ splits and~$X$ is a summand of~$T_0^X$.
-
-(b) This follows from the fact that~$T$ is projective and~$0\defl\susp T'$ is a deflation.
-
-(c) and (d) are obtained from the exact sequences of \cref{proposition::extricat long exact sequences} associated with the extriangle~$T\infl 0\defl \susp T\dashrightarrow$.
-
-(e) For any~$T,T'\in\tc$, we have~$\mathbb{E}(\susp T,\susp T') \cong \cat(T,\susp T')=0$.
+\begin{enumerate}[(i)]
+\item If~$X$ is projective in~$\cat$, then the deflation~$T_0^X\defl X$ splits and~$X$ is a summand of~$T_0^X$.
+\item This follows from the fact that~$T$ is projective and~$0\defl\susp T'$ is a deflation.
+\item and (iv) are obtained from the exact sequences of \cref{proposition::extricat long exact sequences} associated with the extriangle~$T\infl 0\defl \susp T\dashrightarrow$.
+\addtocounter{enumi}{1}
+\item For any~$T,T'\in\tc$, we have~$\mathbb{E}(\susp T,\susp T') \cong \cat(T,\susp T')=0$.
+\qedhere
+\end{enumerate}
 \end{proof}
@@
 Recall that~$F:\cat\to\modt$ denotes the functor sending an object~$X$ to the module~$\cat(-,X)|_\tc$.
-By \cref{lemma::first consequences} (e), the ideal~$(\susp\tc)$ of morphisms factoring through an object in~$\susp\tc$ is included in the kernel of~$F$.
+By \cref{lemma::first consequences}\,(v), the ideal~$(\susp\tc)$ of morphisms factoring through an object in~$\susp\tc$ is included in the kernel of~$F$.
 Conversely, let~$X\xrightarrow{f}Y$ be such that~$Ff=0$.
@@
 \]
-By \cref{lemma::first consequences} (e)~$\susp\tc$ is a rigid subcategory, so that~$t^\ast\delta=0$.
+By \cref{lemma::first consequences}\,(v), $\susp\tc$ is a rigid subcategory, so that~$t^\ast\delta=0$.
 Equivalently, there is a morphism~$\susp T'\xrightarrow{k} X$ such that~$t=fk$.
@@
 
+We conclude with a couple of examples for two associative algebras.
+
 %%%
 
-\subsubsection{Associative algebras}
+%\subsubsection{Associative algebras}
 
@@
 % \subsubsection{A quotient of a Frobenius category}
+%
 % \begin{example}
@@
 %  \]
-%  
-%  \pg{Not sure why we wanted this example anymore.}
 % \end{example}
@@
 
+\newpage
 \addtocontents{toc}{\vspace{.2cm}}

### 2019-06-13 thirdPaper/draft/typeConeAssociahedra.tex
HT comments (some of them)

--- 2019-06-13 thirdPaper/draft/typeConeAssociahedra.tex
@@
 This paper focuses on a surprising construction of the associahedron that recently appeared in mathematical physics.
-Motivated by the prediction of the behavior of scattering particules, N.~Arkani-Hamed, Y.~Bai, S.~He, and G.~Yan recently described in~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} the kinetic associahedron.
+Motivated by the prediction of the behavior of scattering particles, N.~Arkani-Hamed, Y.~Bai, S.~He, and G.~Yan recently described in~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} the kinematic associahedron.
 It is a class of polytopal realizations of the classical associahedron obtained as sections of a high-dimensional positive orthant with well-chosen affine subspaces.
@@
 These two aspects are interesting in their own right and might be useful in different communities: the geometric side enables to simply describe all polytopal realizations of a fan with simplicial type cone (which is sometimes easier to check than to find an explicit realization), while the algebraic side provides fundamental new results on the $\b{g}$-vectors of cluster algebras and on (an extriangulated variant of) the Grothendieck groups of~$2$-Calabi--Yau triangulated categories with cluster tilting objects.
-We have therefore voluntarily split our presentation into two clearly marked parts that can be read independently.
+We have therefore deliberately split our presentation into two clearly marked parts that can be read independently.
 The geometric side, which uses elementary techniques, is presented in \cref{part:geometry} together with all its consequences on polytopal realizations.
@@
 \medskip
-To conclude, it is our hope that the present paper will participate to the interactions between combinatorial geometry, representation theory, and mathematical physics; in particular through further developments of the amplituhedron program, which was open in~\cite{ArkaniHamedTrnka-Amplituhedron} and has flourished during the last years~\cite{ArkaniHamedBourjailyCachazoGoncharovPostnikovTrnka-GrassmannianGeometryScatteringAmplitudes}.
-The kinetic associahedron from~\cite{ArkaniHamedBaiHeYan} is one of the last ``positive geometries''~\cite{ArkaniHamedBaiLam-PositiveGeometries} that has emerged in the study of scattering amplitudes.
+To conclude, it is our hope that the present paper will participate to the interactions between combinatorial geometry, representation theory, and mathematical physics; in particular through further developments of the geometric approach to scattering amplitudes that has flourished during the last years~\cite{ArkaniHamedTrnka-Amplituhedron,ArkaniHamedBourjailyCachazoGoncharovPostnikovTrnka-GrassmannianGeometryScatteringAmplitudes}.
+The kinematic associahedron from~\cite{ArkaniHamedBaiHeYan} is one of the most recent ``positive geometries''~\cite{ArkaniHamedBaiLam-PositiveGeometries} that has emerged in the study of scattering amplitudes.
 

### 2019-06-13 thirdPaper/draft/typeConeAssociahedra.tex
reversed approach

@@
 To prove that the type cone~$\typeCone(\Fan)$ is simplicial, we just need to identify which pairs of adjacent maximal cones of~$\Fan$ correspond to the facets of~$\typeCone(\Fan)$ and to show that the corresponding linear dependences among their rays positively span the linear dependence among the rays of any pair of adjacent maximal cones of~$\Fan$.
-When applied to the $\b{g}$-vector fans of cluster algebras (see \cref{subsec:typeConeCA}), this reversed approach yields all polytopal realizations of the $\b{g}$-vector fans and thus efficiently revisits and extends the construction of~\cite{BazierMatteDouvilleMousavandThomasYildirim}.
+When applied to the $\b{g}$-vector fans of cluster algebras (see \cref{subsec:typeConeCA}), the type cone approach yields all polytopal realizations of the $\b{g}$-vector fans and thus efficiently revisits and extends the construction of~\cite{BazierMatteDouvilleMousavandThomasYildirim}.
 This new perspective has several advantages, as our proof uniformly~applies~to:
@@
 \noindent
-These advantages all follow from one essential feature of our reversed approach.
+These advantages all follow from one essential feature of the type cone approach.
 Namely, it enables to completely separate the algebraic aspects from the geometric aspects of the problem:
@@
 \enlargethispage{.1cm}
-Besides revisiting the construction of~\cite{ArkaniHamedBaiHeYan, BazierMatteDouvilleMousavandThomasYildirim} and extending it to any initial seed (acyclic or not) in any finite type cluster algebra (simply-laced or not), our reversed approach is also successful when applied to the $\b{g}$-vector fans of other families of generalizations of the associahedron.
+Besides revisiting the construction of~\cite{ArkaniHamedBaiHeYan, BazierMatteDouvilleMousavandThomasYildirim} and extending it to any initial seed (acyclic or not) in any finite type cluster algebra (simply-laced or not), our type cone approach is also successful when applied to the $\b{g}$-vector fans of other families of generalizations of the associahedron.
 In the present paper, we explore specifically two families of such generalizations.

### 2019-06-13 thirdPaper/draft/typeConeAssociahedra.tex
space

--- 2019-06-13 thirdPaper/draft/typeConeAssociahedra.tex
@@
 Along the way, we prove algebraic results on~$2$-Calabi--Yau triangulated categories, and on extriangulated categories that are of independent interest.
-In particular, we prove, in those two setups, an analogue of a result of M. Auslander on minimal relations for Grothendieck groups of module categories.
+In particular, we prove, in those two setups, an analogue of a result of M.~Auslander on minimal relations for Grothendieck groups of module categories.
 \end{abstract}
@@
 This paper focuses on a surprising construction of the associahedron that recently appeared in mathematical physics.
-Motivated by the prediction of the behavior of scattering particles, N.~Arkani-Hamed, Y.~Bai, S.~He, and G.~Yan recently described in~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} the kinematic associahedron.
+Motivated by the prediction of the behavior of scattering particules, N.~Arkani-Hamed, Y.~Bai, S.~He, and G.~Yan recently described in~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} the kinetic associahedron.
 It is a class of polytopal realizations of the classical associahedron obtained as sections of a high-dimensional positive orthant with well-chosen affine subspaces.
@@
 These two aspects are interesting in their own right and might be useful in different communities: the geometric side enables to simply describe all polytopal realizations of a fan with simplicial type cone (which is sometimes easier to check than to find an explicit realization), while the algebraic side provides fundamental new results on the $\b{g}$-vectors of cluster algebras and on (an extriangulated variant of) the Grothendieck groups of~$2$-Calabi--Yau triangulated categories with cluster tilting objects.
-We have therefore deliberately split our presentation into two clearly marked parts that can be read independently.
+We have therefore voluntarily split our presentation into two clearly marked parts that can be read independently.
 The geometric side, which uses elementary techniques, is presented in \cref{part:geometry} together with all its consequences on polytopal realizations.
@@
 We present both a purely combinatorial proof (see \cref{subsec:typeConeCA}) and a purely algebraic proof for (non-necessarily gentle) brick algebras making use of extriangulated categories (see \cref{sec:extricats}).
-Our algebraic proof is based on an analogue of a result of M. Auslander~\cite{Auslander1984} relating to minimal generators of Grothendieck groups.
+Our algebraic proof is based on an analogue of a result of M.~Auslander~\cite{Auslander1984} relating to minimal generators of Grothendieck groups.
 Along the way, we need to generalize, for extriangulated categories, several results from cluster-tilting theory on indices~\cite{DehyKeller} and on abelian quotients~\cite{BuanMarshReiten, KellerReiten} that were known for triangulated categories.
@@
 \medskip
-To conclude, it is our hope that the present paper will participate to the interactions between combinatorial geometry, representation theory, and mathematical physics; in particular through further developments of the geometric approach to scattering amplitudes that has flourished during the last years~\cite{ArkaniHamedTrnka-Amplituhedron,ArkaniHamedBourjailyCachazoGoncharovPostnikovTrnka-GrassmannianGeometryScatteringAmplitudes}.
-The kinematic associahedron from~\cite{ArkaniHamedBaiHeYan} is one of the most recent ``positive geometries''~\cite{ArkaniHamedBaiLam-PositiveGeometries} that has emerged in the study of scattering amplitudes.
+To conclude, it is our hope that the present paper will participate to the interactions between combinatorial geometry, representation theory, and mathematical physics; in particular through further developments of the amplituhedron program, which was open in~\cite{ArkaniHamedTrnka-Amplituhedron} and has flourished during the last years~\cite{ArkaniHamedBourjailyCachazoGoncharovPostnikovTrnka-GrassmannianGeometryScatteringAmplitudes}.
+The kinetic associahedron from~\cite{ArkaniHamedBaiHeYan} is one of the last ``positive geometries''~\cite{ArkaniHamedBaiLam-PositiveGeometries} that has emerged in the study of scattering amplitudes.
 

### 2019-06-13 thirdPaper/draft/typeConeAssociahedra.tex
layout

@@
 % formating the table of contents
+\setcounter{tocdepth}{4}
 \makeatletter
@@
 \renewcommand{\tocsection}[2]{\bf\oldtocsection{#1}{#2}}
+\let\oldtocsubsubsection=\tocsubsubsection
+\renewcommand{\tocsubsubsection}[2]{\quad\oldtocsubsubsection{#1}{#2}}
 
@@
 They show that the resulting polytope is always a generalized associahedron, and that its normal fan is the $\b{g}$-vector fan of~$\cal{A}$ with respect to the initial acyclic seed~$\seed_\circ$.
-An implicit by-product of their construction is that the space of all polytopal realizations of the $\b{g}$-vector fan of~$\cal{A}$ with respect to the initial acyclic seed~$\seed_\circ$ is a simplicial cone.
+An implicit by-product of their construction is that the space of all polytopal realizations of the $\b{g}$-vector fan of~$\cal{A}$ with respect to the initial acyclic \mbox{seed~$\seed_\circ$ is a simplicial cone}.
 
@@
 \label{rem:exchangeablePairsNKC}
+\enlargethispage{.3cm}
 In view of \cref{prop:exchangeablePairsNKC}, it is tempting to look for a characterization of the exchangeable pairs~$\omega, \omega'$ using the kisses between~$\omega$ and~$\omega'$.
@@
 
-\begin{figure}[t]
-	\capstart
-	\begin{adjustbox}{center}
+\hvFloat[floatPos=p, capWidth=h, capPos=r, capAngle=90, objectAngle=90, capVPos=c, objectPos=c]{figure}
+{
 		\begin{tabular}{c@{\;}c@{\;}c@{\;}c}
@@
 			cyclohedron &
-			stellohedron \\
-			\includegraphics[scale=.6]{permutahedron} &
-			\includegraphics[scale=.6]{associahedron} &
-			\includegraphics[scale=.6]{cyclohedron} &
-			\includegraphics[scale=.6]{stellohedron} \\
-			\includegraphics[scale=.6]{permutahedronTubings} &
-			\includegraphics[scale=.6]{associahedronTubings} &
-			\includegraphics[scale=.6]{cyclohedronTubings} &
-			\includegraphics[scale=.6]{stellohedronTubings} \\[.1cm]
+			stellohedron \\[.2cm]
+			\includegraphics[scale=.93]{permutahedron} &
+			\includegraphics[scale=.93]{associahedron} &
+			\includegraphics[scale=.93]{cyclohedron} &
+			\includegraphics[scale=.93]{stellohedron} \\[.1cm]
+			\includegraphics[scale=.93]{permutahedronTubings} &
+			\includegraphics[scale=.93]{associahedronTubings} &
+			\includegraphics[scale=.93]{cyclohedronTubings} &
+			\includegraphics[scale=.93]{stellohedronTubings} \\[.2cm]
 			complete graph &
@@
 		\end{tabular}
-	\end{adjustbox}
-	\caption{Some classical families of polytopes as graph associahedra. Illustration from~\cite{MannevillePilaud-compatibilityFans}.}
-	\label{fig:specialGraphAssociahedra}
-\end{figure}
+}
+{Some classical families of polytopes as graph associahedra. Illustration from~\cite{MannevillePilaud-compatibilityFans}.}
+{fig:specialGraphAssociahedra}
+
+%\begin{figure}[t]
+%	\capstart
+%	\begin{adjustbox}{center}
+%		\begin{tabular}{c@{\;}c@{\;}c@{\;}c}
+%			permutahedron &
+%			associahedron &
+%			cyclohedron &
+%			stellohedron \\
+%			\includegraphics[scale=.6]{permutahedron} &
+%			\includegraphics[scale=.6]{associahedron} &
+%			\includegraphics[scale=.6]{cyclohedron} &
+%			\includegraphics[scale=.6]{stellohedron} \\
+%			\includegraphics[scale=.6]{permutahedronTubings} &
+%			\includegraphics[scale=.6]{associahedronTubings} &
+%			\includegraphics[scale=.6]{cyclohedronTubings} &
+%			\includegraphics[scale=.6]{stellohedronTubings} \\[.1cm]
+%			complete graph &
+%			path &
+%			cycle &
+%			star
+%		\end{tabular}
+%	\end{adjustbox}
+%	\caption{Some classical families of polytopes as graph associahedra. Illustration from~\cite{MannevillePilaud-compatibilityFans}.}
+%	\label{fig:specialGraphAssociahedra}
+%\end{figure}
 
@@
 
+\clearpage
 \subsubsection{Nested complex and nested fan of a graph}
@@
 Let~$\B_\circ$ be any finite type exchange matrix, and let~$\mathcal{A}(\B_\circ)$ be the associated cluster algebra without coefficients.
-Then, for any exchangeable cluster variables~$x$ and~$x'$, the linear dependence $\sum_{y \in \cluster \cup \cluster'} \coefficient[{\b{g}_y}][\cluster][\cluster'] \, \b{g}_y = 0$ only depends on the pair~$(x,x')$ and not on the specific choice of clusters~$\cluster$ and~$\cluster'$ containing~$x$ and~$x'$ respectively and such that~${\cluster\setminus\{x\}=\cluster'\setminus\{x'\}}$.
+Then, for any exchangeable cluster variables~$x$ and~$x'$, the linear dependence $\sum_{y \in \cluster \cup \cluster'} \coefficient[{\b{g}_y}][\cluster][\cluster'] \, \b{g}_y = 0$ only depends on the pair~$(x,x')$ and not on the specific choice of clusters~$\cluster$ and~$\cluster'$ containing~$x$ and~$x'$ respectively and such that~${\cluster \ssm \{x\} = \cluster' \ssm \{x'\}}$.
 \end{corollary}
@@
 
+\medskip
 The Auslander--Reiten quiver of the module category~$\MOD(\Lambda)$ can be obtained by applying the functor~$\Hom{}(\Lambda, -)$.
@@
 
-One can check directly that the condition of \cref{theo::brick-algebra-condition} is not satisfied.
+\medskip
+One can check directly that the conditions of \cref{theo::brick-algebra-condition} is not satisfied.
 For example, the module~$\bsm2\\1\esm$ is~$\tau$-rigid since~$\tau(\bsm2\\1\esm) = \bsm3\\1\esm$, while~$\Hom{\Lambda}\left(\bsm2\\1\esm,\tau^2(\bsm2\\1\esm)\right) = \Hom{\Lambda}(\bsm2\\1\esm,\bsm1\\2\esm) \ne 0$.

### 2019-06-13 thirdPaper/draft/typeConeAssociahedra.tex
layout

@@
 \makeatletter
-\def\l@section{\@tocline{1}{2pt}{0pc}{}{}}
+\def\l@section{\@tocline{1}{5pt}{0pc}{}{}}
 \makeatother
@@
 \[
+\hspace{-.3cm}
 \xymatrix{ & \cat(\susp^{-1} A, B)\ar[r]\ar@{->>}[d] & \cat(E, B)\ar[r]^{f^*}\ar@{->>}[d] & \cat(A,B)\ar[r]\ar@{->>}[d] & \coker(f^*)\ar[r]\ar@{->>}[d] & 0 \\
@@
 
+\enlargethispage{-.8cm}
 We use the following terminology.
+
 \begin{notation}
@@
 
+\enlargethispage{-.1cm}
 We start by stating some immediate implications of the existence of conflations~$T\infl 0 \defl \susp T$, for~$T\in\tc$.

### 2019-06-14 thirdPaper/draft/typeConeAssociahedra.tex
space fig 17

@@
 			cycle &
-			star
+			star \\[.3cm]
 		\end{tabular}

### 2019-06-14 thirdPaper/draft/typeConeAssociahedra.tex
small reformulation of a phrase

@@
 Another question related to this paper is to understand the complete realization space of the combinatorics of the associahedra.
-The associahedra constructed in~\cite{ArkaniHamedBaiHeYan, BazierMatteDouvilleMousavandThomasYildirim} and the present paper describe all polytopal realizations of the $\b{g}$-vector fans, but there are other realizations of the combinatorics of the associahedra with different fans.
+The associahedra constructed in~\cite{ArkaniHamedBaiHeYan, BazierMatteDouvilleMousavandThomasYildirim} and the present paper describe all polytopal realizations of the $\b{g}$-vector fans, but there are other polytopal realizations of the combinatorial type of the associahedron with different normal fans.
 Is it possible to similarly understand the complete realization space of the cluster complex, including all realizations not having the~$\b{g}$-vector fan as their normal fan?

### 2019-06-16 thirdPaper/draft/typeConeAssociahedra.tex
rem: no X in E
new subsection for 2-term + application to gentle added

@@
 \item The facet-defining inequalities of the type cone of~$\Fan$ correspond to very specific pairs of adjacent maximal cones of~$\Fan$ whose corresponding linear dependences minimally generate all such dependences.
-While they correspond to mesh mutations for cluster algebras and brick $2$-acyclic gentle algebras, they are not understood in general (see for instance \cref{fig:labelFacetDefiningInequalititiesNKC}\,(right)).
+While they correspond to mesh mutations for cluster algebras and $2$-acyclic gentle brick algebras, they are not understood in general (see for instance \cref{fig:labelFacetDefiningInequalititiesNKC}\,(right)).
 It would be particularly interesting to fully understand these specific mutations for arbitrary (non-kissing finite) gentle algebras.
@@
 
-Note that the family of brick $2$-acyclic gentle quivers already contains a lot of relevant examples, including the gentle grid and dissection quivers discussed in \cref{subsubsec:nonkissingComplex}.
-In particular, the classical associahedron is the gentle associahedron of a brick $2$-acyclic gentle quiver.
-We will see in~\cref{coro:simplicialTypeConeNKC} that the type cone of the non-kissing fan~$\gvectorFan[\quiver]$ of a brick $2$-acyclic gentle quiver~$\quiver$ happens to be simplicial, and we will derive in~\cref{coro:allPolytopalRealizationsNKC} a simple description of all polytopal realizations of~$\gvectorFan[\quiver]$.
+Note that the family of brick and $2$-acyclic gentle quivers already contains a lot of relevant examples, including the gentle grid and dissection quivers discussed in \cref{subsubsec:nonkissingComplex}.
+In particular, the classical associahedron is the gentle associahedron of a brick and $2$-acyclic gentle quiver.
+We will see in~\cref{coro:simplicialTypeConeNKC} that the type cone of the non-kissing fan~$\gvectorFan[\quiver]$ of a brick and $2$-acyclic gentle quiver~$\quiver$ happens to be simplicial, and we will derive in~\cref{coro:allPolytopalRealizationsNKC} a simple description of all polytopal realizations of~$\gvectorFan[\quiver]$.
 
@@
 \label{prop:interestingExchangeablePairsNKC}
-For any brick $2$-acyclic gentle quiver~$\quiver$ and any string~$\sigma \in \strings$, the walks~$\cc{\sigma}$ and~$\hh{\sigma}$ are exchangeable with distinguished substring~$\sigma$.
+For any brick and $2$-acyclic gentle quiver~$\quiver$ and any string~$\sigma \in \strings$, the walks~$\cc{\sigma}$ and~$\hh{\sigma}$ are exchangeable with distinguished substring~$\sigma$.
 \end{proposition}
@@
 Otherwise, since~$\alpha\tau$ is a substring of~$\nu$ and~$\alpha'\tau$ is a substring of~$\nu$, the cycle~$\alpha \tau \alpha'$ contains a unique relation~$\alpha'\alpha$.
-This rules out this case under the assumption that~$\quiver$ is brick $2$-acyclic.
+This rules out this case under the assumption that~$\quiver$ is brick and $2$-acyclic.
 The case when~$\tau$ appears after~$\sigma$ in both~$\mu$ and~$\nu$ is symmetric.
@@
 
-The following statement describes the type cone of the non-kissing fan of a brick $2$-acyclic gentle quiver.
+The following statement describes the type cone of the non-kissing fan of a brick and $2$-acyclic gentle quiver.
 
@@
 \label{prop:extremalExchangeablePairsNKC}
-For any brick $2$-acyclic gentle quiver~$\quiver$, the extremal exchangeable pairs for the non-kissing fan of~$\quiver$ are precisely the pairs~$\{\cc{\sigma}, \hh{\sigma}\}$ for all strings~$\sigma \in \strings$.
+For any brick and $2$-acyclic gentle quiver~$\quiver$, the extremal exchangeable pairs for the non-kissing fan of~$\quiver$ are precisely the pairs~$\{\cc{\sigma}, \hh{\sigma}\}$ for all strings~$\sigma \in \strings$.
 \end{proposition}
@@
 \label{coro:simplicialTypeConeNKC}
-For any brick $2$-acyclic gentle quiver~$\quiver$, the type cone~$\typeCone \big( \gvectorFan[\quiver] \big)$ of the non-kissing fan~$\quiver$ is simplicial.
+For any brick and $2$-acyclic gentle quiver~$\quiver$, the type cone~$\typeCone \big( \gvectorFan[\quiver] \big)$ of the non-kissing fan~$\quiver$ is simplicial.
 \end{corollary}
 
-Combining \cref{coro:simplicialTypeCone,coro:simplicialTypeConeNKC,prop:extremalExchangeablePairsNKC}, we derive the following description of all polytopal realizations of the non-kissing fan~$\gvectorFan[\quiver]$ of a brick $2$-acyclic quiver~$\quiver$.
+Combining \cref{coro:simplicialTypeCone,coro:simplicialTypeConeNKC,prop:extremalExchangeablePairsNKC}, we derive the following description of all polytopal realizations of the non-kissing fan~$\gvectorFan[\quiver]$ of a brick and $2$-acyclic quiver~$\quiver$.
 
@@
 \label{coro:allPolytopalRealizationsNKC}
-For any brick $2$-acyclic gentle quiver~$\quiver$ and any~$\b{\ell} \in \R_{>0}^{\strings}$, the polytope
+For any brick and $2$-acyclic gentle quiver~$\quiver$ and any~$\b{\ell} \in \R_{>0}^{\strings}$, the polytope
 \[
@@
 
-\subsection{Application to certain categories}
+\subsection{Application to 2-term complexes of projectives and to gentle algebras}
+\label{sect::Kbproj}
 
@@
 
-\subsubsection{$2$-Calabi--Yau triangulated categories}
-\label{sect::2CYTriangulated}
-
-Let~$\cat$ be a triangulated category with shift functor~$\susp$.
-We assume moreover that~$\cat$ is~$\field$-linear, Krull--Schmidt, Hom-finite, 2-Calabi--Yau, with a cluster-tilting object~$T$.
-Then~$\cat$ satisfies all the assumptions of \cref{setting::extricat} for \cref{sect::Statment extricats} but assumption (1).
-
-We fix this issue by considering a relative extriangulated structure.
-Let~$\mathbb{E}_T$ be the additive sub-bifunctor of~$\cat(-,\susp -)$ formed by those morphisms that factor through~$\add\susp T$.
-Then~$(\cat,\mathbb{E}_T)$ becomes extriangulated by~\cite[Prop.~3.14]{HerschendLiuNakaoka} (this can also be checked directly).
-The extriangles of~$\cat$ are precisely the triangles~$X\overset{f}{\rightarrow}Y\overset{g}{\rightarrow} Z \overset{h}{\dashrightarrow}$, for which the morphism~$h$ factors through~$\add\susp T$.
-By construction, Condition (1) is now satisfied.
-Moreover, the triangles appearing in Conditions (2) and (3) are extriangles for this relative structure, which shows that those two conditions are still satisfied for the extriangulated structure~$(\cat,\mathbb{E}_T)$.
-
-\begin{remark}
-The index of an object~$X$ in the triangulated category~$\cat$, coincide with its class in the Grothendieck group of~$\cat$ for the relative extriangulated structure given by~$\mathbb{E}_T$.
-\end{remark}
-
-\begin{remark}
-The main results of \cref{subsect::Statement cluster cats} can thus be viewed as specific cases of the results of \cref{sec:extricats}: \cref{theo::relations-g-vecteurs} and \cref{corollary::meshes positively generate cluster cats} are consequences of \cref{theorem::extricats} and \cref{corollary::meshes positively generate extricats}.
-\end{remark}
-
-%%%
-
-\subsubsection{$2$-Calabi--Yau Frobenius exact categories}
-\label{sect::2CYexact}
-
-%%%
-
-\subsubsection{$2$-term complexes of projective modules}
-\label{sect::Kbproj}
-Let~$\Lambda$ be a finite-dimensional algebra over a field~$\field$.
+Let~$\Lambda$ be an Artin algebra.
 Then the homotopy category~$K^b(\proj \Lambda)$ is a triangulated category, and we consider its full subcategory~$K^{[-1,0]}(\proj \Lambda)$ of complexes concentrated in degrees~$-1$ and~$0$ (with cohomological conventions).
@@
 \end{remark}
+
+\begin{corollary}\label{coro::silting simplicial}
+ Let~$\Lambda$ be a finite dimensional brick algebra of finite representation type.
+ Assume moreover that, for any indecomposable~$\Lambda$-module~$M$, the space~$\Hom{\Lambda}(M, \tau^2 M)$ vanishes.
+ Then the support~$\tau$-tilting fan of~$\Lambda$ has the unique exchange property and its type cone is simplicial.
+\end{corollary}
+
+As a consequence of Corollary~\ref{coro::silting simplicial}, the method of Part~\ref{part:geometry} apply and give an explicit description of all realizations of the support~$\tau$-tilting fan of~$\Lambda$.
+
+Another consequence is an algebraic proof of Corollary~\ref{coro:simplicialTypeConeNKC}, that we restate below.
+
+\begin{corollary}\label{coro::simplicialTypeConeNKCalgebraic}
+ For any~$2$-acyclic gentle brick algebra, the type cone of its support~$\tau$-tilting fan is simplicial.
+\end{corollary}
+
+The remaining part of this section is devoted to proving Theorem~\ref{theo::brick-algebra-condition} and Corollary~\ref{coro::simplicialTypeConeNKCalgebraic}.
 
@@
 \]
-The first map is surjective since~$E\to X$ is right almost-split.
+The first map is surjective since~$E\to X$ is right almost-split (note that~$E$ cannot contain any summand isomorphic to~$X$).
 We can conclude by (4).
@@
 %%%
+
+\begin{lemma}\label{lemma::characterization Gentle 2-acyclic}
+ Let~$\Lambda$ be a~$2$-acyclic gentle brick algebra.
+ Then, for any indecomposable~$\Lambda$-module~$M$ we have~$\Hom{\Lambda}(M,\tau^2 M)=0$.
+\end{lemma}
+
+\begin{proof}
+ Let~$\Lambda=\field Q / I$ be any gentle algebra of finite representation type, and let~$M$ be an indecomposable~$\Lambda$-module.
+ Write~$\sigma$ for the string corresponding to~$\tau M$.
+ Then the walks (i.e.
+the maximal strings in the blossoming bound quiver of~$(Q,I)$) associated with~$M$ and~$\tau M$ are respectively~$\omega_M = \hh\sigma = p^{-1}\alpha\sigma\beta^{-1}q$ and~$\omega_{\tau M}=\cc\sigma=p'\alpha'^{-1}\sigma\beta'q'^{-1}$, where~$p,p',q,q'$ are paths and~$\alpha,\alpha',\beta,\beta'$ are arrows in the blossoming quiver.
+
+ Assume that~$\Hom{\Lambda}(M,\tau^2 M)\neq0$.
+ By~\cite[]{PaluPilaudPlamondon-nonkissing} or~\cite[]{BrustleDouvilleMousavandThomasYildirim}, the walk~$\omega_M$ kisses the walk~$\omega_{\tau M}$: there is a substring~$\rho$ of~$\omega_M$ and~$\omega_{\tau M}$ that is strictly on top of~$\omega_M$ and strictly at the bottom of~$\omega_{\tau M}$.
+Remark that~$\rho$ cannot start nor end at some endpoint of~$\sigma$ (because~$\rho$ is a top substring of~$\omega_M$).
+
+ If the substring~$\rho$ of~$\omega_M$ is contained in~$\sigma$, by the previous remark it is strictly below~$\sigma$.
+This implies that~$\omega_M$ kisses itself, hence that~$M$ is not~$\tau$-rigid.
+Similarly, if~$\rho$ is contained in~$\sigma$ as a substring of~$\omega_{\tau M}$, then~$\tau M$ is not~$\tau$-rigid.
+In both cases, the brick-$\tau$-rigid correspondence of~\cite{DemonetIyamaJasso} implies that~$\Lambda$ is not a brick algebra.
+
+ Note that~$\rho$ cannot contain~$\sigma$, because~$\sigma$ is the only common substring of~$\omega_M$ and~$\omega_{\tau M}$ that contains~$\sigma$.
+%  We split the remaining of the proof into two cases:
+%  
+%  \noindent {\it Case 1:} As a substring of~$\omega_M$,~$\rho$ contains~$\alpha\in\hL$ and the first letter (i.e. arrow or inverse of an arrow) of~$\sigma$.
+%  
+%  \noindent {\it Case 2:} As a substring of~$\omega_M$,~$\rho$ does not intersect~$\sigma$.
+Assume now that~$\rho$, viewed either as a substring of~$\omega_M$ or of~$\omega_{\tau M}$ is not contained in~$\sigma$.
+Since~$\rho$ is strictly on top of~$\omega_M$, it contains the source of~$\alpha$ or the source of~$\beta$.
+Similarly,~$\rho$ contains the target of~$\alpha'$ or the target of~$\beta'$.
+Because the target of~$\alpha$ is the source of~$\alpha'$ (and the target of~$\beta$ is the source of~$\beta'$), this implies that~$Q$ contains either a non-oriented cycle with at most one relation, in which case~$\Lambda$ is not a brick algebra, or a~$2$-cycle, in which case~$\Lambda$ is not~$2$-acyclic.
+\end{proof}
+
+\begin{proof}[Proof of Corollary~\ref{coro::simplicialTypeConeNKCalgebraic}]
+ The unique exchange property follows from Proposition~\ref{prop::exchange conflations are unique} (2).
+ By Lemma~\ref{lemma::characterization Gentle 2-acyclic}, the assumptions of Theorem~\ref{theo::brick-algebra-condition} are satisfied.
+ We can thus apply Theorem~\ref{theorem::extricats} and its corollary, which shows that there is the same number of extremal exchange pairs of the support~$\tau$-tilting fan (i.e.
+the non-kissing fan) as there are meshes in the Auslander--Reiten quiver of~$\Lambda$.
+ Hence the type cone of the support~$\tau$-tilting fan is simplicial.
+\end{proof}
+
+%%%%%%%%%%%
+
+\subsection{Application to other examples of categories}
+
+%%%
+
+\subsubsection{$2$-Calabi--Yau triangulated categories}
+\label{sect::2CYTriangulated}
+
+Let~$\cat$ be a triangulated category with shift functor~$\susp$.
+We assume moreover that~$\cat$ is~$\field$-linear, Krull--Schmidt, Hom-finite, 2-Calabi--Yau, with a cluster-tilting object~$T$.
+Then~$\cat$ satisfies all the assumptions of \cref{setting::extricat} for \cref{sect::Statment extricats} but, possibly, assumption (1).
+
+We fix this issue by considering a relative extriangulated structure.
+Let~$\mathbb{E}_T$ be the additive sub-bifunctor of~$\cat(-,\susp -)$ formed by those morphisms that factor through~$\add\susp T$.
+Then~$(\cat,\mathbb{E}_T)$ becomes extriangulated by~\cite[Prop.~3.14]{HerschendLiuNakaoka} (this can also be checked directly).
+The extriangles of~$\cat$ are precisely the triangles~$X\overset{f}{\rightarrow}Y\overset{g}{\rightarrow} Z \overset{h}{\dashrightarrow}$, for which the morphism~$h$ factors through~$\add\susp T$.
+By construction, Condition (1) is now satisfied.
+Moreover, the triangles appearing in Conditions (2) and (3) are extriangles for this relative structure, which shows that those two conditions are still satisfied for the extriangulated structure~$(\cat,\mathbb{E}_T)$.
+
+\begin{remark}
+The index of an object~$X$ in the triangulated category~$\cat$, coincide with its class in the Grothendieck group of~$\cat$ for the relative extriangulated structure given by~$\mathbb{E}_T$.
+\end{remark}
+
+\begin{remark}
+The main results of \cref{subsect::Statement cluster cats} can thus be viewed as specific cases of the results of \cref{sec:extricats}: \cref{theo::relations-g-vecteurs} and \cref{corollary::meshes positively generate cluster cats} are consequences of \cref{theorem::extricats} and \cref{corollary::meshes positively generate extricats}.
+\end{remark}
 

### 2019-06-16 thirdPaper/draft/typeConeAssociahedra.tex
acknowledgments

--- 2019-06-14 thirdPaper/draft/typeConeAssociahedra.tex
@@
 
+\addtocontents{toc}{\vspace{.2cm}}
+\section*{Acknowledgments}
+
+We thank H.~Thomas for comments on a preliminary version of the paper and for informing us about the upcoming extended version of~\cite{BazierMatteDouvilleMousavandThomasYildirim}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \newpage
-\addtocontents{toc}{\vspace{.2cm}}
 \bibliographystyle{alpha}

### 2019-06-16 thirdPaper/draft/typeConeAssociahedra.tex
ref to cref

--- 2019-06-16 thirdPaper/draft/typeConeAssociahedra.tex
@@
 Moreover, we precisely describe the facet-defining inequalities of the type cone in terms of linear dependences of $\b{g}$-vectors involved in certain mesh relations.
-We thus automatically derive a construction similar to that of~\cite{ArkaniHamedBaiHeYan, BazierMatteDouvilleMousavandThomasYildirim} describing all polytopal realizations of the $\b{g}$-vector fans of these brick $2$-acyclic bound quivers as sections of a positive orthant by well-chosen affine spaces (see \cref{subsec:typeConeCA}).
+We thus automatically derive a construction similar to that of~\cite{ArkaniHamedBaiHeYan, BazierMatteDouvilleMousavandThomasYildirim} describing all polytopal realizations of the $\b{g}$-vector fans of these brick and $2$-acyclic gentle bound quivers as sections of a positive orthant by well-chosen affine spaces (see \cref{subsec:typeConeCA}).
 Again, this result mainly relies on finding which relations minimally generate the relations between the $\b{g}$-vectors in the non-kissing complex.
@@
 
-As a consequence of Corollary~\ref{coro::silting simplicial}, the method of Part~\ref{part:geometry} apply and give an explicit description of all realizations of the support~$\tau$-tilting fan of~$\Lambda$.
-
-Another consequence is an algebraic proof of Corollary~\ref{coro:simplicialTypeConeNKC}, that we restate below.
+As a consequence of \cref{coro::silting simplicial}, the method of \cref{part:geometry} apply and give an explicit description of all realizations of the support~$\tau$-tilting fan of~$\Lambda$.
+
+Another consequence is an algebraic proof of \cref{coro:simplicialTypeConeNKC}, that we restate below.
 
@@
 
-The remaining part of this section is devoted to proving Theorem~\ref{theo::brick-algebra-condition} and Corollary~\ref{coro::simplicialTypeConeNKCalgebraic}.
+The remaining part of this section is devoted to proving \cref{theo::brick-algebra-condition,coro::simplicialTypeConeNKCalgebraic}.
 
@@
 
-\begin{proof}[Proof of Corollary~\ref{coro::simplicialTypeConeNKCalgebraic}]
- The unique exchange property follows from Proposition~\ref{prop::exchange conflations are unique} (2).
- By Lemma~\ref{lemma::characterization Gentle 2-acyclic}, the assumptions of Theorem~\ref{theo::brick-algebra-condition} are satisfied.
- We can thus apply Theorem~\ref{theorem::extricats} and its corollary, which shows that there is the same number of extremal exchange pairs of the support~$\tau$-tilting fan (i.e.
+\begin{proof}[Proof of \cref{coro::simplicialTypeConeNKCalgebraic}]
+ The unique exchange property follows from \cref{prop::exchange conflations are unique} (2).
+ By \cref{lemma::characterization Gentle 2-acyclic}, the assumptions of \cref{theo::brick-algebra-condition} are satisfied.
+ We can thus apply \cref{theorem::extricats} and its corollary, which shows that there is the same number of extremal exchange pairs of the support~$\tau$-tilting fan (i.e.
 the non-kissing fan) as there are meshes in the Auslander--Reiten quiver of~$\Lambda$.

### 2019-06-16 thirdPaper/draft/typeConeAssociahedra.tex
minor changes + biblio
minor changes

@@
 \item The facet-defining inequalities of the type cone of~$\Fan$ correspond to very specific pairs of adjacent maximal cones of~$\Fan$ whose corresponding linear dependences minimally generate all such dependences.
-While they correspond to mesh mutations for cluster algebras and $2$-acyclic gentle brick algebras, they are not understood in general (see for instance \cref{fig:labelFacetDefiningInequalititiesNKC}\,(right)).
+While they correspond to mesh mutations for cluster algebras and brick and $2$-acyclic gentle algebras, they are not understood in general (see for instance \cref{fig:labelFacetDefiningInequalititiesNKC}\,(right)).
 It would be particularly interesting to fully understand these specific mutations for arbitrary (non-kissing finite) gentle algebras.
@@
 
+\vincent{Connect as well to Yann}
+
 \begin{proposition}
@@
 \end{definition}
+
 \begin{remark}
@@
 \item If there is a mutation conflation (see \cref{defn::mutation conflation}) of the form~$X\infl E\defl Y$, then there can be no mutation conflation of the form~$Y\infl E'\defl X$.
-
 \item Assume that~$X\infl E\defl Y$ and~$X\infl E'\defl Y$ are two mutation conflations. 
@@
 
-\begin{corollary}\label{coro::silting simplicial}
+\begin{corollary}
+\label{coro::silting simplicial}
 Let~$\Lambda$ be a finite dimensional brick algebra of finite representation type.
@@
 
-\begin{corollary}\label{coro::simplicialTypeConeNKCalgebraic}
- For any~$2$-acyclic gentle brick algebra, the type cone of its support~$\tau$-tilting fan is simplicial.
+\begin{corollary}[\cref{coro:simplicialTypeConeNKC}]
+\label{coro::simplicialTypeConeNKCalgebraic}
+For any brick and $2$-acyclic gentle algebra, the type cone of its support~$\tau$-tilting fan is simplicial.
 \end{corollary}
@@
 
-\begin{lemma}\label{lemma::characterization Gentle 2-acyclic}
- Let~$\Lambda$ be a~$2$-acyclic gentle brick algebra.
+\begin{lemma}
+\label{lemma::characterization Gentle 2-acyclic}
+Let~$\Lambda$ be a brick and $2$-acyclic gentle algebra.
 Then, for any indecomposable~$\Lambda$-module~$M$ we have~$\Hom{\Lambda}(M,\tau^2 M)=0$.

### 2019-06-16 thirdPaper/draft/typeConeAssociahedra.tex
minor changes
minor modif + explicit ref

--- 2019-06-16 thirdPaper/draft/typeConeAssociahedra.tex
@@
 Moreover, we precisely describe the facet-defining inequalities of the type cone in terms of linear dependences of $\b{g}$-vectors involved in certain mesh relations.
-We thus automatically derive a construction similar to that of~\cite{ArkaniHamedBaiHeYan, BazierMatteDouvilleMousavandThomasYildirim} describing all polytopal realizations of the $\b{g}$-vector fans of these brick and $2$-acyclic gentle bound quivers as sections of a positive orthant by well-chosen affine spaces (see \cref{subsec:typeConeCA}).
+We thus automatically derive a construction similar to that of~\cite{ArkaniHamedBaiHeYan, BazierMatteDouvilleMousavandThomasYildirim} describing all polytopal realizations of the $\b{g}$-vector fans of these brick $2$-acyclic bound quivers as sections of a positive orthant by well-chosen affine spaces (see \cref{subsec:typeConeCA}).
 Again, this result mainly relies on finding which relations minimally generate the relations between the $\b{g}$-vectors in the non-kissing complex.
@@
 \item $2$-Calabi--Yau triangulated categories admitting a cluster-tilting object (see \cref{sect::2CYTriangulated});
-\item $2$-Calabi--Yau Frobenius exact categories (see \cref{sect::2CYexact});
 \item for any Artin algebra~$\Lambda$, the category~$K^{[-1,0]}(\proj \Lambda)$ of complexes of finitely generated projective~$\Lambda$-modules concentrated in degrees~$-1$ and~$0$, with morphisms considered up to homotopy (see \cref{sect::Kbproj});
-\item more generally, extriangulated categories~$\cat$ constructed as follows: if~$\tc$ is a rigid subcategory of an extriangulated category~$\ec$, we let~$\cat$ be the full subcategory of~$\ec$ whose objects satisfy condition (3), equipped with the extriangulated structure obtained from that of~$\ec$ by considering those extriangles in~$\ec$ all whose terms belong to~$\cat$ and whose deflation is~$\tc$-epi (see \cref{sect::prT}).
+\item more generally, extriangulated categories~$\cat$ constructed as follows: if~$\tc$ is a rigid subcategory of an extriangulated category~$\ec$ (with some assumption ensuring that condition (2) holds) we let~$\cat$ be the full subcategory of~$\ec$ whose objects satisfy condition (3), equipped with the extriangulated structure obtained from that of~$\ec$ by considering those extriangles in~$\ec$ all whose terms belong to~$\cat$ and whose deflation is~$\tc$-epi (see \cref{sect::prT}).
 \end{itemize}
@@
 
-As a consequence of \cref{coro::silting simplicial}, the method of \cref{part:geometry} apply and give an explicit description of all realizations of the support~$\tau$-tilting fan of~$\Lambda$.
-
-Another consequence is an algebraic proof of \cref{coro:simplicialTypeConeNKC}, that we restate below.
+As a consequence of Corollary~\cref{coro::silting simplicial}, the method of Part~\cref{part:geometry} apply and give an explicit description of all realizations of the support~$\tau$-tilting fan of~$\Lambda$.
+
+Another consequence is an algebraic proof of Corollary~\cref{coro:simplicialTypeConeNKC}, that we restate below.
 
@@
 
-The remaining part of this section is devoted to proving \cref{theo::brick-algebra-condition,coro::simplicialTypeConeNKCalgebraic}.
+The remaining part of this section is devoted to proving Theorem~\cref{theo::brick-algebra-condition} and Corollary~\cref{coro::simplicialTypeConeNKCalgebraic}.
 
@@
  Assume that~$\Hom{\Lambda}(M,\tau^2 M)\neq0$.
- By~\cite[]{PaluPilaudPlamondon-nonkissing} or~\cite[]{BrustleDouvilleMousavandThomasYildirim}, the walk~$\omega_M$ kisses the walk~$\omega_{\tau M}$: there is a substring~$\rho$ of~$\omega_M$ and~$\omega_{\tau M}$ that is strictly on top of~$\omega_M$ and strictly at the bottom of~$\omega_{\tau M}$.
+ By~\cite[Theorem 2.46]{PaluPilaudPlamondon-nonkissing} or~\cite[Theorem 5.1]{BrustleDouvilleMousavandThomasYildirim}, the walk~$\omega_M$ kisses the walk~$\omega_{\tau M}$: there is a substring~$\rho$ of~$\omega_M$ and~$\omega_{\tau M}$ that is strictly on top of~$\omega_M$ and strictly at the bottom of~$\omega_{\tau M}$.
 Remark that~$\rho$ cannot start nor end at some endpoint of~$\sigma$ (because~$\rho$ is a top substring of~$\omega_M$).
@@
 
-\begin{proof}[Proof of \cref{coro::simplicialTypeConeNKCalgebraic}]
- The unique exchange property follows from \cref{prop::exchange conflations are unique} (2).
- By \cref{lemma::characterization Gentle 2-acyclic}, the assumptions of \cref{theo::brick-algebra-condition} are satisfied.
- We can thus apply \cref{theorem::extricats} and its corollary, which shows that there is the same number of extremal exchange pairs of the support~$\tau$-tilting fan (i.e.
+\begin{proof}[Proof of Corollary~\cref{coro::simplicialTypeConeNKCalgebraic}]
+ The unique exchange property follows from Proposition~\cref{prop::exchange conflations are unique} (2).
+ By Lemma~\cref{lemma::characterization Gentle 2-acyclic}, the assumptions of Theorem~\cref{theo::brick-algebra-condition} are satisfied.
+ We can thus apply Theorem~\cref{theorem::extricats} and its corollary, which shows that there is the same number of extremal exchange pairs of the support~$\tau$-tilting fan (i.e.
 the non-kissing fan) as there are meshes in the Auslander--Reiten quiver of~$\Lambda$.
@@
 \begin{remark}
- The categories considered in \cref{sect::2CYTriangulated,sect::2CYexact,sect::Kbproj} all fall into the setting of \cref{prop::prT}.
+ The categories considered in \cref{sect::2CYTriangulated,sect::Kbproj} all fall into the setting of \cref{prop::prT}.
 \end{remark}
@@
 
+\newpage
 \addtocontents{toc}{\vspace{.2cm}}
-\section*{Acknowledgments}
-
-We thank H.~Thomas for comments on a preliminary version of the paper and for informing us about the upcoming extended version of~\cite{BazierMatteDouvilleMousavandThomasYildirim}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\newpage
 \bibliographystyle{alpha}

### 2019-06-16 thirdPaper/draft/typeConeAssociahedra.tex

--- 2019-06-16 thirdPaper/draft/typeConeAssociahedra.tex
@@
 Indeed, which of the two possible linear dependences is satisfied by the $\b{g}$-vectors of~$\cluster \cup \cluster'$ depends on the initial exchange matrix~$\B_\circ$.
-% We will prove however that it is independent of the seeds containing~$x$ and~$x'$.
-% \vincent{Link to \cref{sec:clusterCategories}.}
 However, for cluster algebras of finite type, this linear dependence is independent of the choice of a seed containing~$x$ and~$x'$.
@@
 In \cref{subsubsec:simplicialTypeConeNKC}, we will restrict to a situation that avoids all these patologies.
-%\vincent{Do we still have these problems when the gentle algebra is brick and/or without oriented $2$-cycle?}
 \end{remark}
@@
 
-\vincent{Connect as well to Yann}
-
 \begin{proposition}
@@
 Let~$\omega \eqdef \cc{\sigma}$, $\omega' \eqdef \hh{\sigma}$, $\mu \eqdef \hc{\sigma}$ and~$\nu \eqdef \ch{\sigma}$.
-%Let~$v,y$ be the two endpoints of~$\sigma$, and let~$u$ (resp.~$w$, resp.~$x$, resp.~$z$) be the only peak of~$\mu$ (resp.~deep of~$\mu$, resp.~peak of~$\nu$, resp.~deep of~$\nu$) that is not a substring of~$\sigma$.
-%Finally, let~$\alpha = v \to w$, $\alpha' = u \to v$, $\beta = y \to z$ and $\beta' = x \to y$.
 See \cref{fig:flip}.
@@
 The following statement describes the type cone of the non-kissing fan of a brick and $2$-acyclic gentle quiver.
+We provide here an elementary combinatorial proof, a deeper and more general reason is discussed in \cref{coro::simplicialTypeConeNKCalgebraic}.
 
@@
 
-% \vincent{Careful.
-There is a convention change with \cref{subsec:typeConeCA} and \cref{fig:labelFacetDefiningInequalititiesCA1,fig:labelFacetDefiningInequalititiesCA2}.
-Justify this change by the fact that we followed the convention of~\cite{BazierMatteDouvilleMousavandThomasYildirim} in \cref{subsec:typeConeCA}.}
-
-% \yann{I think that our conventions coincide.
-With the choice of the Hom functor, $\susp T$ is sent to the initial seed so that the AR triangles ending in $\add(\susp T)$ are precisely the meshes ending in an initial variable}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-% \vincent{Here should be explained that the gentle algebra result is a special case of this.}
-
 %%%
@@
 Assume that~$\Hom{\Lambda}(M,\tau^2 M)\neq0$.
-By~\cite[]{PaluPilaudPlamondon-nonkissing} or~\cite[]{BrustleDouvilleMousavandThomasYildirim}, the walk~$\omega_M$ kisses the walk~$\omega_{\tau M}$: there is a substring~$\rho$ of~$\omega_M$ and~$\omega_{\tau M}$ that is strictly on top of~$\omega_M$ and strictly at the bottom of~$\omega_{\tau M}$.
+By~\cite[Theorem 2.46]{PaluPilaudPlamondon-nonkissing} or~\cite[Theorem 5.1]{BrustleDouvilleMousavandThomasYildirim}, the walk~$\omega_M$ kisses the walk~$\omega_{\tau M}$: there is a substring~$\rho$ of~$\omega_M$ and~$\omega_{\tau M}$ that is strictly on top of~$\omega_M$ and strictly at the bottom of~$\omega_{\tau M}$.
 Remark that~$\rho$ cannot start nor end at some endpoint of~$\sigma$ (because~$\rho$ is a top substring of~$\omega_M$).

### 2019-06-16 thirdPaper/draft/typeConeAssociahedra.tex
minor change

@@
 The following statement describes the type cone of the non-kissing fan of a brick and $2$-acyclic gentle quiver.
-We provide here an elementary combinatorial proof, a deeper and more general reason is discussed in \cref{coro::simplicialTypeConeNKCalgebraic}.
+We provide here an elementary combinatorial proof, a more general representation theoretic perspective is discussed in \cref{theo::brick-algebra-condition}.
 
@@
 Our next statement follows from the end of the previous proof.
+See also \cref{coro::simplicialTypeConeNKCalgebraic}.
 

### 2019-06-16 thirdPaper/draft/typeConeAssociahedra.tex
subsection 4.7 sentence
minor changes

@@
 \let\oldtocpart=\tocpart
-\renewcommand{\tocpart}[2]{\bf\large\oldtocpart{#1}{#2}}
+\renewcommand{\tocpart}[2]{\sc\large\oldtocpart{#1}{#2}}
 \let\oldtocsection=\tocsection
@@
 \item \textbf{Graph associahedra} were defined by M.~Carr and S.~Devadoss~\cite{CarrDevadoss} in connection to C.~De Concini and C.~Procesi's wonderful arrangements~\cite{DeConciniProcesi}.
-As illustrated in~\cref{fig:specialGraphAssociahedra}, the graph associahedra of certain special families of graphs coincide with well-known families of polytopes: complete graph associahedra are permutahedra, path associahedra are classical associahedra, cycle associahedra are cyclohedra, and star associahedra are stellohedra.
+As illustrated in \cref{fig:specialGraphAssociahedra}, the graph associahedra of certain special families of graphs coincide with well-known families of polytopes: complete graph associahedra are permutahedra, path associahedra are classical associahedra, cycle associahedra are cyclohedra, and star associahedra are stellohedra.
 The graph associahedra were extended to the nestohedra, which are simple polytopes realizing the nested complex of arbitrary building sets~\cite{Postnikov, FeichtnerSturmfels}.
@@
 Let $\cal{G}$ be a simplicial refinement of $\Fan$.
-By~\cref{prop:non-simplicial}, the type cone of any coarsening of $\Fan$ is a relatively open cell of the hyperplane arrangement defined by adjacent pairs of~$\cal{G}$.
+By \cref{prop:non-simplicial}, the type cone of any coarsening of $\Fan$ is a relatively open cell of the hyperplane arrangement defined by adjacent pairs of~$\cal{G}$.
 The type cone of the coarsening is not empty whenever it is polytopal.
@@
 However, for cluster algebras of finite type, this linear dependence is independent of the choice of a seed containing~$x$ and~$x'$.
-As explained in ~\cref{corollary:UERPforCAproof}, this statement follows from~\cite[Thm.~7.5]{BuanMarshReinekeReitenTodorov}.
+As explained in \cref{corollary:UERPforCAproof}, this statement follows from~\cite[Thm.~7.5]{BuanMarshReinekeReitenTodorov}.
 We state it here for future reference.
@@
 In particular, the classical associahedron is the gentle associahedron of a brick and $2$-acyclic gentle quiver.
-We will see in~\cref{coro:simplicialTypeConeNKC} that the type cone of the non-kissing fan~$\gvectorFan[\quiver]$ of a brick and $2$-acyclic gentle quiver~$\quiver$ happens to be simplicial, and we will derive in~\cref{coro:allPolytopalRealizationsNKC} a simple description of all polytopal realizations of~$\gvectorFan[\quiver]$.
+We will see in \cref{coro:simplicialTypeConeNKC} that the type cone of the non-kissing fan~$\gvectorFan[\quiver]$ of a brick and $2$-acyclic gentle quiver~$\quiver$ happens to be simplicial, and we will derive in \cref{coro:allPolytopalRealizationsNKC} a simple description of all polytopal realizations of~$\gvectorFan[\quiver]$.
 
@@
 Conversely, we know from \cref{rem:dimTypeCone} that there are at least~$|\properWalks|-|Q_0|$ extremal exchangeable pairs.
-Since~$|\strings| = |\distinguishableStrings| = |\properWalks| - |Q_0|$ by~\cref{prop:bijectionStringsWalks}, we conclude that all exchangeable pairs~$\{\cc{\sigma}, \hh{\sigma}\}$ for~$\sigma \in \strings$ are extremal.
+Since~$|\strings| = |\distinguishableStrings| = |\properWalks| - |Q_0|$ by \cref{prop:bijectionStringsWalks}, we conclude that all exchangeable pairs~$\{\cc{\sigma}, \hh{\sigma}\}$ for~$\sigma \in \strings$ are extremal.
 \end{proof}
@@
 \label{exm:nonSimplicialTypeConeNKC}
-Note that \cref{prop:interestingExchangeablePairsNKC,prop:extremalExchangeablePairsNKC} and therefore~\cref{coro:simplicialTypeConeNKC,coro:allPolytopalRealizationsNKC} fail when the quiver is not brick or $2$-cyclic.
+Note that \cref{prop:interestingExchangeablePairsNKC,prop:extremalExchangeablePairsNKC} and therefore \cref{coro:simplicialTypeConeNKC,coro:allPolytopalRealizationsNKC} fail when the quiver is not brick or $2$-cyclic.
 The smallest exemples are the $2$-cycles whose non-kissing fans are represented in \cref{fig:nonkissingFans2}.
@@
 More precisely, the $\graphG$-associahedron is a polytopal realization of the nested complex of~$\graphG$, defined as the simplicial complex of all collections of tubes (connected induced subgraphs) of~$\graphG$ which are pairwise compatible (either nested, or disjoint and non-adjacent).
-As illustrated in~\cref{fig:specialGraphAssociahedra}, the graph associahedra of certain special families of graphs coincide with well-known families of polytopes: complete graph associahedra are permutahedra, path associahedra are classical associahedra, cycle associahedra are cyclohedra, and star associahedra are stellohedra.
+As illustrated in \cref{fig:specialGraphAssociahedra}, the graph associahedra of certain special families of graphs coincide with well-known families of polytopes: complete graph associahedra are permutahedra, path associahedra are classical associahedra, cycle associahedra are cyclohedra, and star associahedra are stellohedra.
 The graph associahedra were extended to the \defn{nestohedra}, which are simple polytopes realizing the nested complex of arbitrary building sets~\cite{Postnikov, FeichtnerSturmfels}.
@@
 
-We derive from~\cref{coro:extremalExchangeablePairsGA} the number of extremal exchangeable pairs of the nested fan.
+We derive from \cref{coro:extremalExchangeablePairsGA} the number of extremal exchangeable pairs of the nested fan.
 For a tube~$\tube$ of~$\graphG$, we denote 
@@
 \label{lemm::mesh mutations and meshes}
-The set of positive mesh mutations~$(x,x')$ of \cref{defn::positive mutation} is in bijection with the set~$\meshes$ of~\cref{defn::positive mutation}.
+The set of positive mesh mutations~$(x,x')$ of \cref{defn::positive mutation} is in bijection with the set~$\meshes$ of \cref{defn::positive mutation}.
 \end{lemma}
@@
 Let~$T\in\cat$ be a basic cluster tilting object such that~$\CC(T)$ is the initial cluster.
-According to~\cref{lemma:positive mutation triangles}, the morphism~$h$ belongs to the ideal~$(\susp T)$.
+According to \cref{lemma:positive mutation triangles}, the morphism~$h$ belongs to the ideal~$(\susp T)$.
 Therefore, the triangle ${X\to \bigoplus_i E_i \to Y \xrightarrow{h} \susp X}$ induces the relation~$[X]+[Y]=\sum_i [E_i]$ in~$K_0(\cat ; T)$.
@@
 
-%%%
-
 Let~$\Lambda$ be an Artin algebra.
@@
 As a consequence of \cref{coro::silting simplicial}, the method of \cref{part:geometry} apply and give an explicit description of all realizations of the support~$\tau$-tilting fan of~$\Lambda$.
-
 Another consequence is an algebraic proof of \cref{coro:simplicialTypeConeNKC}, that we restate below.
@@
 \subsection{Application to other examples of categories}
+
+In this section, we give two more examples of families of categories to which \cref{theorem::extricats,corollary::meshes positively generate extricats} apply.
 
@@
 
-\addtocontents{toc}{\vspace{.2cm}}
+\addtocontents{toc}{\vspace{.1cm}}
 \section*{Acknowledgments}

### 2019-06-17 secondPaper/draft/accordionComplexSurfaces.tex
PPP2: comment (ii) of referee.

@@
 \begin{definition}
-An \defn{eventually cyclic string} for~$\bar Q$ is a word~$\rho$ of the form~${}^\infty(c_1^{\varepsilon_1})\sigma (c_2^{\varepsilon_2})^\infty$, where $c_1, c_2$ are oriented cycles in~$\bar Q$ (possibly of length zero) and $\varepsilon_1, \varepsilon_2$ are signs in~$\{\pm 1\}$ such that $c_1^{2\varepsilon_1} \sigma c_2^{2\varepsilon_2}$ is a finite string in~$\bar Q$.
+An \defn{eventually cyclic string} for~$\bar Q$ is a word~$\rho$ of the form~${}^\infty(c_1^{\varepsilon_1})\sigma (c_2^{\varepsilon_2})^\infty$, where $c_1, c_2$ are oriented cycles in~$\bar Q$ (with at most one of them of length zero) and $\varepsilon_1, \varepsilon_2$ are signs in~$\{\pm 1\}$ such that $c_1^{2\varepsilon_1} \sigma c_2^{2\varepsilon_2}$ is a finite string in~$\bar Q$.
 \end{definition}

### 2019-06-17 secondPaper/draft/accordionComplexSurfaces.tex
PPP2: comment (iv) of referee.

@@
 Consider a marked surface~$\bar\surface = (\surface, V \sqcup V\dual)$, where~$V$ and~$V\dual$ are two disjoint sets of marked points so that the points of~$V$ and~$V\dual$ that are on the boundary of~$\surface$ alternate.
-A cellular $V$-dissection~$\dissection$ of~$\bar\surface$ and a cellular $V\dual$-dissection~$\dissection\dual$ of~$\bar\surface$ are \defn{dual cellular dissections} if there are pairs of mutually inverse bijections~$V\dual \leftrightarrow \faces(\dissection)$ and~$V \leftrightarrow \faces(\dissection\dual)$, both denoted~$\dual$ in both directions, such that~$\dissection$ has an edge joining its vertices~$u,v \in V$ and separating its faces~$f,g \in  \faces(\dissection)$ if and only if~$\dissection\dual$ has an edge joining its vertices~$f\dual, g\dual \in V\dual$ and separating its faces~$u\dual, v\dual \in \faces(\dissection\dual)$.
+A cellular $V$-dissection~$\dissection$ of~$\bar\surface$ and a cellular $V\dual$-dissection~$\dissection\dual$ of~$\bar\surface$ are \defn{dual cellular dissections} if there are mutually inverse bijections~$V\dual \leftrightarrow \faces(\dissection)$,~$V \leftrightarrow \faces(\dissection\dual)$, and~$\edges(\dissection) \leftrightarrow \edges(\dissection\dual)$,  all denoted by~$\dual$ in both directions, such that
+\begin{enumerate}
+ \item for each vertex~$v\in V$, the closure of the face~$v\dual$ of~$\dissection\dual$ contains~$v$;
+ \item for each vertex~$w\in V\dual$, the closure of the face~$w\dual$ of~$\dissection$ contains~$w$;
+ \item for each edge~$e\in \edges(\dissection)$, the edges~$e$ and~$e\dual$ intersect exactly once in their interior; moreover,~$e$ intersects (in their interior) no other edge of~$\dissection\dual$, and~$e\dual$ intersects (in their interior) no other edge of~$\dissection$.
+\end{enumerate}
+
+% ~$\dissection$ has an edge joining its vertices~$u,v \in V$ and separating its faces~$f,g \in  \faces(\dissection)$ if and only if~$\dissection\dual$ has an edge joining its vertices~$f\dual, g\dual \in V\dual$ and separating its faces~$u\dual, v\dual \in \faces(\dissection\dual)$.
 \end{definition}

### 2019-06-18 secondPaper/draft/accordionComplexSurfaces.tex
layout

@@
 
-\enlargethispage{.1cm}
 Before defining accordions and slaloms, we need a strong notion of pairs of dual dissections of an orientable surface.
@@
 \end{enumerate}
-
-% ~$\dissection$ has an edge joining its vertices~$u,v \in V$ and separating its faces~$f,g \in  \faces(\dissection)$ if and only if~$\dissection\dual$ has an edge joining its vertices~$f\dual, g\dual \in V\dual$ and separating its faces~$u\dual, v\dual \in \faces(\dissection\dual)$.
 \end{definition}
@@
 
-\enlargethispage{.1cm}
+\enlargethispage{.4cm}
 Let~$\bar\surface = (\surface, V \sqcup V\dual)$ be a surface with two disjoint sets~$V$ and~$V\dual$ of marked points, and let~$B$ be the corresponding blossom points on the boundary of~$\surface$.
@@
 
-\enlargethispage{.3cm}
 The following definition generalizes the one from~\cite{GarverMcConville} for the case where~$\bar\surface$ is a disk.
@@
 
+\enlargethispage{-.2cm}
 In this section, we show that non-kissing and non-crossing complexes actually coincide.
@@
 
+\enlargethispage{-.5cm}
 Definition~\ref{def:surfaceQuiver} constructs an orientable surface~$\surface_{\bar Q}$ with boundaries.
@@
 
-\enlargethispage{-.4cm}
 The advantage of Definition~\ref{def:surfaceQuiver} is that it automatically endows~$\surface_{\bar Q}$ with two disjoint sets~$V_{\bar Q}$ and~${{V\dual}\!\!_{\bar Q}}$ of marked points and two dual cellular dissections~$\dissection_{\bar Q}$ and~${\dissection\dual\!\!_{\bar Q}}$ defined as follows.
@@
 
+\enlargethispage{.4cm}
 We conclude this section with five families of examples that illustrate the computation of~$\surface_{\bar Q}$.
@@
 
+\begin{figure}[h]
+	\capstart
+	\centerline{\includegraphics[scale=.7]{CambrianPathsSurfaces}}
+	\caption{The surface~$\surface_{\bar Q}$ for two Cambrian paths on~$5$ vertices.}
+	\label{fig:CambrianPathsSurfaces}
+\end{figure}
+
 We apply Remark~\ref{rem:propertiesSurface} to understand the corresponding surfaces.
@@
 Two examples are represented in \fref{fig:CambrianPathsSurfaces}.
-Note that the dissection~$\dissection_{\bar Q}$ is a triangulation with no internal triangles, and the orientation of~$\bar Q$ indicates how to glue these triangles.
-For instance, the Cambrian quiver completely oriented in one direction yields a fan triangulation, were all internal edges are incident to the same vertex, as in \fref{fig:CambrianPathsSurfaces}\,(left).
-
-\begin{figure}[h]
-	\capstart
-	\centerline{\includegraphics[scale=.7]{CambrianPathsSurfaces}}
-	\caption{The surface~$\surface_{\bar Q}$ for two Cambrian paths on~$5$ vertices.}
-	\label{fig:CambrianPathsSurfaces}
-\end{figure}
+The dissection~$\dissection_{\bar Q}$ is a triangulation with no internal triangles, and the orientation of~$\bar Q$ indicates how to glue these triangles.
+For instance, the Cambrian quiver completely oriented in one direction yields a fan triangulation, with all internal edges incident to the same vertex, as in \fref{fig:CambrianPathsSurfaces}\,(left).
 \end{example}
@@
 Consider the family of \defn{reversed path quivers} indicated in \fref{fig:reversedPathsQuivers}.
-
-\begin{figure}[h]
-	\capstart
-	\centerline{\includegraphics[scale=.45]{reversedPathsQuivers}}
-	\caption{The reversed path quivers with~$1, 2, 3, 4$ vertices.}
-	\label{fig:reversedPathsQuivers}
-\end{figure}
 
@@
 	\capstart
+	\centerline{\includegraphics[scale=.45]{reversedPathsQuivers}}
+	\caption{The reversed path quivers with~$1, 2, 3, 4$ vertices.}
+	\label{fig:reversedPathsQuivers}
+\end{figure}
+
+\begin{figure}[h]
+	\capstart
 	\centerline{\includegraphics[scale=.7]{reversedPathsSurfaces3}}
@@
 Consider the family of \defn{double path quivers} indicated in \fref{fig:doublePathsQuivers}.
-
-\begin{figure}[h]
-	\capstart
-	\centerline{\includegraphics[scale=.45]{doublePathsQuivers}}
-	\caption{The double path quivers with~$1, 2, 3, 4$ vertices.}
-	\label{fig:doublePathsQuivers}
-\end{figure}
 
@@
 
-\begin{figure}[H]
+\begin{figure}[h]
+	\capstart
+	\centerline{\includegraphics[scale=.45]{doublePathsQuivers}}
+	\caption{The double path quivers with~$1, 2, 3, 4$ vertices.}
+	\label{fig:doublePathsQuivers}
+\end{figure}
+
+\begin{figure}[h]
 	\capstart
@@
 \label{exm:cycle}
+\enlargethispage{1cm}
 Consider the family of \defn{cycle quivers} indicated in \fref{fig:cyclesQuivers}.
-
-\begin{figure}[H]
-	\capstart
-	\centerline{\includegraphics[scale=.45]{cyclesQuivers}}
-	\caption{The cycle quivers with~$1, 2, 3, 4, 5$ vertices.}
-	\label{fig:cyclesQuivers}
-\end{figure}
 
@@
 	\capstart
+	\centerline{\includegraphics[scale=.45]{cyclesQuivers}}
+	\caption{The cycle quivers with~$1, 2, 3, 4, 5$ vertices.}
+	\label{fig:cyclesQuivers}
+\end{figure}
+
+\begin{figure}[h]
+	\capstart
 	\centerline{\includegraphics[scale=.7]{cyclesSurfacesBis}}
@@
 Consider the family of \defn{double cycle quivers} indicated in \fref{fig:doubleCyclesQuivers}.
-
-\begin{figure}[H]
-	\capstart
-	\centerline{\includegraphics[scale=.45]{doubleCyclesQuivers}}
-	\caption{The double cycle quivers with~$1, 2, 3, 4, 5$ vertices.}
-	\label{fig:doubleCyclesQuivers}
-\end{figure}
 
@@
 The first few corresponding surfaces are represented in \fref{fig:doubleCyclesSurfaces}.
+
+\begin{figure}[h]
+	\capstart
+	\centerline{\includegraphics[scale=.45]{doubleCyclesQuivers}}
+	\caption{The double cycle quivers with~$1, 2, 3, 4, 5$ vertices.}
+	\label{fig:doubleCyclesQuivers}
+\end{figure}
 

### 2019-07-01 thirdPaper/draft/typeConeAssociahedra.tex
cleaning tex file
ref to physics accordions?

@@
 \DeclareMathOperator{\cone}{cone} % cone hull
-\DeclareMathOperator{\inv}{inv} % inversions
-\DeclareMathOperator{\ascents}{asc} % ascents
-\DeclareMathOperator{\descents}{des} % descents
 
@@
 
-% PG et Yann
+% Representation theory
 \newcommand{\field}{\mathbb{K}}
@@
 
-% extriangulated
+% Extriangulated categories
 \newcommand{\tc}{\mathcal{T}}
@@
 \newcommand{\eps}{\varepsilon}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \begin{itemize}
-\item \textbf{Gentle associahedra} were constructed in~\cite{PaluPilaudPlamondon-nonkissing} as polytopal realizations of finite non-kissing complexes of gentle bound quivers.
+\item \textbf{Gentle associahedra}\yann{Ref physicien accordions ?} were constructed in~\cite{PaluPilaudPlamondon-nonkissing} as polytopal realizations of finite non-kissing complexes of gentle bound quivers.
 These complexes encompass two families of simplicial complexes studied independently in the literature: on the one hand the grid associahedra introduced by T.~K.~Petersen, P.~Pylyavskyy and D.~Speyer in~\cite{PetersenPylyavskyySpeyer} for a staircase shape, studied by F.~Santos, C.~Stump and V.~Welker~\cite{SantosStumpWelker} for rectangular shapes, and extended by T.~McConville in~\cite{McConville} for arbitrary grid shapes; and on the other hand the Stokes polytopes and accordion associahedra studied by Y.~Baryshnikov~\cite{Baryshnikov}, F.~Chapoton~\cite{Chapoton-quadrangulations}, A.~Garver and T.~McConville~\cite{GarverMcConville} and T.~Manneville and V.~Pilaud~\cite{MannevillePilaud-accordion}.
@@
 
-\medskip
+\medskip\yann{Ref physicien accordions ?}
 To conclude, it is our hope that the present paper will participate to the interactions between combinatorial geometry, representation theory, and mathematical physics; in particular through further developments of the geometric approach to scattering amplitudes that has flourished during the last years~\cite{ArkaniHamedTrnka-Amplituhedron,ArkaniHamedBourjailyCachazoGoncharovPostnikovTrnka-GrassmannianGeometryScatteringAmplitudes}.
@@
 We say that two seeds are \defn{mutationally equivalent} when they can be obtained from each other by a sequence of mutations (we also use the same terminology for exchange matrices).
-%We consider an \defn{initial seed} $\seed_\circ = (\B_\circ, \coefficients_\circ, \cluster_\circ)$ whose cluster variables are supposed to be~$x_1, \dots, x_n$.
 We denote by~$\variables$ the collection of all cluster variables in the seeds mutationally equivalent to an initial seed~$\seed_\circ = (\B_\circ, \coefficients_\circ, \cluster_\circ)$ with cluster variables~$\cluster_\circ = \{x_1, \dots, x_n\}$.
@@
 for any $x\in\cluster_\circ$.
-%This assignment makes all exchange relations and all cluster variables in~$\principalClusterAlgebra$ homogeneous~\cite{FominZelevinsky-ClusterAlgebrasIV} and it justifies the definition of the following family of integer vectors associated to cluster variables.
 
@@
 	\capstart
-	%\centerline{\includegraphics[scale=.45]{clusterFans}}
 	\begin{adjustbox}{center}
@@
 Assume now that~$\omega \ne \hh{\sigma}$ (the situation where~$\omega' \ne \cc{\sigma}$ is symmetric).
-%Assume now that~$\omega \ne \hh{\sigma}$, for instance that~$\omega \ne \hL \sigma \tau$ (the situations where~$\omega' \ne \cc{\sigma}$ or~$\omega \ne \rho \sigma \hR$ are symmetric).
-%Let~$\xi \eqdef \hL \sigma \tau$ and $\zeta \eqdef \hL \sigma \tau'$.
-%These notations are summarized in \cref{fig:proofExtremalExchangeablePairsNKC}.
 If~$\rho \ne \cL$, observe that
@@
 	\capstart
-%	\centerline{\includegraphics[scale=1.2]{fourEqualities}}
 	\begin{adjustbox}{center}
@@
 We derive from \cref{coro:extremalExchangeablePairsGA} the number of extremal exchangeable pairs of the nested fan.
-For a tube~$\tube$ of~$\graphG$, we denote 
-%by~$\neighbors(\tube)$ the number of neighbors of~$\tube$ and
- by~$\nonDisconnecting(\tube)$ the number of non-disconnecting vertices of~$\tube$.
-% In other words, it $\neighbors(\tube)$ (resp.~$\nonDisconnecting(\tube)$) is the number of tubes covering~$\tube$ (resp.~covered by~$\tube$) in the inclusion poset of all tubes of~$\graphG$.
+For a tube~$\tube$ of~$\graphG$, we denote by~$\nonDisconnecting(\tube)$ the number of non-disconnecting vertices of~$\tube$.
 In other words, $\nonDisconnecting(\tube)$ is the number of tubes covered by~$\tube$ in the inclusion poset of all tubes of~$\graphG$.
@@
 \label{coro:numberExtremalExchangeablePairsGA}
-The nested fan~$\gvectorFan[\graphG]$ 
-has~$\!\!\!\! \sum\limits_{\tube[s] \in \tubes} \!\! \binom{\nonDisconnecting(\tube[s])}{2}$ 
-% $\!\!\!\! \sum\limits_{\tube[r] \in \tubes} \!\! \binom{\neighbors(\tube[r])}{2} = \!\!\!\! \sum\limits_{\tube[s] \in \tubes} \!\! \binom{\nonDisconnecting(\tube[s])}{2}$ 
-extremal exchangeable pairs.
+The nested fan~$\gvectorFan[\graphG]$ has~$\!\!\!\! \sum\limits_{\tube[s] \in \tubes} \!\! \binom{\nonDisconnecting(\tube[s])}{2}$ extremal exchangeable pairs.
 \end{corollary}
-
-%\begin{proof}
-%By \cref{prop:extremalExchangeablePairsGA}, extremal exchangeable pairs are in bijection with quadruples~$(\tube[r], \tube[t], \tube', \tube[s])$ of tubes of~$\graphG$ where~$\tube[t]$ and~$\tube'$ are distinct tubes covering~$\tube[r]$ and covered by~$\tube[s]$ in the inclusion poset of all tubes of~$\graphG$.
-%The result immediately follows.
-%\end{proof}
 
@@
 \label{lemm::bilinear-form}
-Let~$A$ and~$B$ be two indecomposable objects of~$\cat$. %\pg{introduce general notation for redisue field}
+Let~$A$ and~$B$ be two indecomposable objects of~$\cat$.
 \begin{enumerate}
@@
 For any object~$T\in\tc$, we fix an extriangle~$T\infl 0 \defl \susp T \dashrightarrow$.
-% Extending by additivity, this defines (uniquely up to isomorphism) an object~$\susp T$, for each object~$T\in\tc$.
 \end{notation}
@@
 
-\cref{prop::KRextricat} below extends similar results from~\cite{BuanMarshReiten,KellerReiten,KoenigZhu,IyamaYoshino} (see also \cref{prop::functor-F}) to the setting under consideration.
+\cref{prop::KRextricat} below extends similar results from~\cite{BuanMarshReiten,KellerReiten,KoenigZhu,IyamaYoshino}\yann{Add reference silting Iyama} (see also \cref{prop::functor-F}) to the setting under consideration.
 We note that the proof requires minor modifications.
@@
 where~$(\susp\tc)$ is the ideal of morphisms factoring through an object of the form~$\susp T$, for some~$T\in\tc$.
-% This equivalence induces further equivalences between~$\tc$ and the category of projectives, and between~$\tau\susp\tc$ and that of injectives.
 \end{proposition}
@@
 The extriangulated category~$K^{[-1,0]}(\proj \Lambda)$ is the setting in which we can finally prove point~(ii) of \cref{prop:exchangeablePairsNKC}, using results of~\cite{DemonetIyamaJasso} on~$\b{g}$-vectors.
-% \cref{prop::2kbproj-is-extriangulated} gives a setting in which to apply \cref{}.
 Before doing so, we introduce the notion of mutation conflation for two-term silting objects.
@@
 \[
-\Hom{K^b}(\susp^{-1} Y, E') \to \Hom{K^b}(\susp^{-1} Y, X) \Hom{K^b}(\susp^{-1} Y, \susp Y).
+\Hom{K^b}(\susp^{-1} Y, E') \to \Hom{K^b}(\susp^{-1} Y, X) \to \Hom{K^b}(\susp^{-1} Y, \susp Y).
 \]
@@
 Let~$\Lambda$ be an Artin algebra whose indecomposable injective modules are~$\tau$-rigid, and let~$P$ be an indecomposable projective~$\Lambda$-module.
-%which is a brick.
-% Let~$I$ be indecomposable injective with socle~$P/\operatorname{rad}P$, and~$\alpha$ be the composition~$P\to\operatorname{soc} I \to I$.
-% Complete the morphism~$\alpha$ to a triangle~$P\to Y\to E\to \susp P$ in~$K^{[-1,0]}(\proj\Lambda)$, where~$Y$ is a minimal projective presentation of~$I$.
-% Then~$Y\infl E\defl \susp P$ is an Auslander--Reiten conflation in~$K^{[-1,0]}(\proj\Lambda)$, which is also a mutation conflation.
 Then the Auslander--Reiten conflation~${Y\infl E\defl \susp P}$ in~$K^{[-1,0]}(\proj\Lambda)$ is a mutation conflation if~$FY$ is a brick.
@@
 
-% \begin{lemma}
-% \label{lemm::if-AR-sequences-are-mutation}
-%  Let~$\Lambda$ be an Artin algebra.
-Assume that for any almost-split conflation~$\tau X \infl E \defl X$ of~$K^{[-1,0]}(\proj\Lambda)$, we have that~$\Hom{K^b}(X, \susp E) = \Hom{K^b}(E, \susp X) = 0$ and~$\Hom{K^b}(\tau X, \susp E) = \Hom{K^b}(E, \susp \tau X) = 0$.
-Then for any indecomposable~$\Lambda$-module~$M$, we have that~$\Hom{\Lambda}(M, \tau^2 M)$ vanishes.
-% \end{lemma}
-% \begin{proof}
-%  
-% \end{proof}
-
 %%%
@@
 Note that~$\rho$ cannot contain~$\sigma$, because~$\sigma$ is the only common substring of~$\omega_M$ and~$\omega_{\tau M}$ that contains~$\sigma$.
-%  We split the remaining of the proof into two cases:
-%  
-%  \noindent {\it Case 1:} As a substring of~$\omega_M$,~$\rho$ contains~$\alpha\in\hL$ and the first letter (i.e. arrow or inverse of an arrow) of~$\sigma$.
-%  
-%  \noindent {\it Case 2:} As a substring of~$\omega_M$,~$\rho$ does not intersect~$\sigma$.
 Assume now that~$\rho$, viewed either as a substring of~$\omega_M$ or of~$\omega_{\tau M}$ is not contained in~$\sigma$.

### 2019-07-02 thirdPaper/draft/typeConeAssociahedra.tex
removed comments

@@
 \begin{itemize}
-\item \textbf{Gentle associahedra}\yann{Ref physicien accordions ?} were constructed in~\cite{PaluPilaudPlamondon-nonkissing} as polytopal realizations of finite non-kissing complexes of gentle bound quivers.
+\item \textbf{Gentle associahedra} were constructed in~\cite{PaluPilaudPlamondon-nonkissing} as polytopal realizations of finite non-kissing complexes of gentle bound quivers.
 These complexes encompass two families of simplicial complexes studied independently in the literature: on the one hand the grid associahedra introduced by T.~K.~Petersen, P.~Pylyavskyy and D.~Speyer in~\cite{PetersenPylyavskyySpeyer} for a staircase shape, studied by F.~Santos, C.~Stump and V.~Welker~\cite{SantosStumpWelker} for rectangular shapes, and extended by T.~McConville in~\cite{McConville} for arbitrary grid shapes; and on the other hand the Stokes polytopes and accordion associahedra studied by Y.~Baryshnikov~\cite{Baryshnikov}, F.~Chapoton~\cite{Chapoton-quadrangulations}, A.~Garver and T.~McConville~\cite{GarverMcConville} and T.~Manneville and V.~Pilaud~\cite{MannevillePilaud-accordion}.
@@
 
-\medskip\yann{Ref physicien accordions ?}
+\medskip
 To conclude, it is our hope that the present paper will participate to the interactions between combinatorial geometry, representation theory, and mathematical physics; in particular through further developments of the geometric approach to scattering amplitudes that has flourished during the last years~\cite{ArkaniHamedTrnka-Amplituhedron,ArkaniHamedBourjailyCachazoGoncharovPostnikovTrnka-GrassmannianGeometryScatteringAmplitudes}.
@@
 
-\cref{prop::KRextricat} below extends similar results from~\cite{BuanMarshReiten,KellerReiten,KoenigZhu,IyamaYoshino}\yann{Add reference silting Iyama} (see also \cref{prop::functor-F}) to the setting under consideration.
+\cref{prop::KRextricat} below extends similar results from~\cite{BuanMarshReiten,KellerReiten,KoenigZhu,IyamaYoshino} (see also \cref{prop::functor-F}) to the setting under consideration.
 We note that the proof requires minor modifications.

### 2019-07-09 thirdPaper/draft/typeConeAssociahedra.tex
began main results

@@
 
+\section*{Main results and logical dependencies}
+
+We give a brief overview of our main results.
+Their logical dependencies are recalled in a schematic diagram at the end of this section.
+
+Let~$\Fan$ be an essential, complete, simplicial, polyhedral fan in~$\R^n$ (all definitions are recalled in \cref{ssec:polytopes and fans}).
+The type cone~$\typeCone(\Fan)$ of~$\Fan$ (\cref{ssec:type cone}), introduced by P. McMullen, is a device that encodes the information about all possible polytopal realizations of~$\Fan$.
+If the simplicial fan~$\Fan$ has the unique exchange relation property (\cref{def:uerp}), then its type cone is easier to describe and study.
+In particular, if moreover the type cone~$\typeCone(\Fan)$ is simplicial (\cref{rem:dimTypeCone}), then all possible polytopal realizations of~$\Fan$ can be described explicitely in~$\R^N_{>0}$, where~$N$ is the number of rays of~$\typeCone(\Fan)$, in terms of~$N-n$ positive real parameters (\cref{coro:simplicialTypeCone}).
+This gives a new point of view on~\cite{ArkaniHamedBaiHeYan,BazierMatteDouvilleMousavandThomasYildirim}, illustrated in \cref{subsec:typeConeAsso} for classical associahedra, that we then apply to two families of~$\b{g}$-vector fans generalizing the~$\b{g}$-vector fans of classical associahedra: The~$\b{g}$-vector fans of cluster algebras of finite type (generalized associahedra), and the~$\b{g}$-vector fans of gentle algebras (non-kissing associahedra, non-crossing associahedra, generalized accordiohedra).
+We also describe the type cone for graph associahedra (\cref{subsec:typeConeGA}), to which our strategy does not apply.
+
+\subsection*{Cluster algebras of finite type} (\cref{subsec:typeConeCA})
+
+We first consider the~$\b{g}$-vector fan~$\Fan(\B_\circ)$ of a skew-symmetrizable cluster algebra of finite type, with respect to any initial exchange matrix of finite type~$\B_\circ$.
+A reformulation of~\cite[Thm 7.5]{BuanMarshReinekeReitenTodorov}
+\medskip
+
+\noindent \ref{prop:uniqueExchangePropertyCA}: The cluster fan~$\Fan(\B_\circ)$ has the unique exchange relation property.
+
+\medskip
+
+We consider the set~$\meshes$ of all pairs~$\{x,x'\}$ related by non-initial mesh mutations (\cref{def:meshMutation}), and we denote by~$\principalVariables$ the set of cluster variables.
+Let~$\{x,x'\}\in\meshes$, and let~$X,X'$ be two clusters such that~$X\setminus\{x\}=X'\setminus\{x'\}$.
+For any~$y\in\principalVariables$, define~$\alpha_{x,x',y}$ to be~$|b_{xy}|$ if~$y\in X\cap X'$ and 0 otherwise.
+By the unique exchange relation property, the~$\alpha_{x,x',y}$'s do not depend on the choice of the clusters~$X,X'$.
+
+\medskip
+
+\noindent \cref{thm:allPolytopalRealizationsCA}: 
+\emph{For any~$\b{\ell} \in \R_{>0}^{\meshes}$, the polytope
+\[
+R_{\b{\ell}}(\B_\circ) \eqdef \Bigset{\b{z} \in \R^{\principalVariables}}{\b{z} \ge 0 \text{ and } \b{z}_x + \b{z}_{x'} - \sum_{y \in \principalVariables} \alpha_{x,x',y} \, \b{z}_{y} = \b{\ell}_{\{x,x'\}} \text{ for all } \{x,x'\} \in \meshes}
+\]
+is a generalized associahedron, whose normal fan is the cluster fan~$\gvectorFan[\B_\circ]$.
+Moreover, the polytopes~$R_\b{\ell}(\B_\circ)$ for~$\b{\ell} \in \R_{>0}^{\meshes}$ describe all polytopal realizations of~$\gvectorFan[\B_\circ]$.}
+
+\subsection*{Gentle algebras}
+
+\subsection*{Cluster categories}
+
+\subsection*{Extriangulated categories}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subsection{Polytopes and fans}
+\label{ssec:polytopes and fans}
 
@@
 \subsection{Type cone}
+\label{ssec:type cone}
 

### 2019-07-09 thirdPaper/draft/typeConeAssociahedra.tex
main results gentle

@@
 
-\subsection*{Cluster algebras of finite type} (\cref{subsec:typeConeCA})
+\medskip
+
+\noindent {\bf Cluster algebras of finite type} (\cref{subsec:typeConeCA})
+
+\medskip
 
 We first consider the~$\b{g}$-vector fan~$\Fan(\B_\circ)$ of a skew-symmetrizable cluster algebra of finite type, with respect to any initial exchange matrix of finite type~$\B_\circ$.
-A reformulation of~\cite[Thm 7.5]{BuanMarshReinekeReitenTodorov}
+A reformulation of~\cite[Thm 7.5]{BuanMarshReinekeReitenTodorov} gives the first step towards applying our type cone strategy.
+
 \medskip
 
-\noindent \ref{prop:uniqueExchangePropertyCA}: The cluster fan~$\Fan(\B_\circ)$ has the unique exchange relation property.
+\noindent \cref{prop:uniqueExchangePropertyCA}: \emph{The cluster fan~$\Fan(\B_\circ)$ has the unique exchange relation property.}
+
+\medskip
+
+The second step follows from our main result in \cref{sec:clusterCategories}, which makes use of representation theory of finite dimensional algebras and additive categorification of cluster algebras.
+
+\medskip
+
+\noindent \cref{coro:simplicialTypeConeCA}: \emph{The type cone~$\typeCone(\Fan(\B_\circ))$ is simplicial.}
 
@@
 For any~$y\in\principalVariables$, define~$\alpha_{x,x',y}$ to be~$|b_{xy}|$ if~$y\in X\cap X'$ and 0 otherwise.
-By the unique exchange relation property, the~$\alpha_{x,x',y}$'s do not depend on the choice of the clusters~$X,X'$.
+By the unique exchange relation property, the~$\alpha_{x,x',y}$'s do not depend on the specific choice of the clusters~$X,X'$.
 
@@
 
-\subsection*{Gentle algebras}
-
-\subsection*{Cluster categories}
-
-\subsection*{Extriangulated categories}
+\bigskip
+
+\noindent {\bf Gentle algebras, non-kissing complex, generalized accordiohedra} (\cref{subsec:typeConeNKC})
+
+\medskip
+
+The same strategy is applied to a class of finite dimensional algebras, called gentle algebras, whose representations are combinatorially well understood.
+We identify two conditions, called brick and 2-acyclicity (\cref{def:brick2acyclic}), that enable us to make use of the type cone approach.
+We note that the~$\tau$-tilting theory of gentle algebras is the algebraic counterpart of the combinatorics of accordions on surfaces~\cite{PaluPilaudPlamondon-nonkissing,BrustleDouvilleMousavandThomasYildirim,PaluPilaudPlamondon-surfaces}.
+
+Let~$\quiver = (Q,I)$ be a gentle bound quiver, and let~$\Fan(\quiver)$ be the fan of its~$\b{g}$-vectors (\cref{subsubsec:nonkissingComplex}), also called its non-kissing fan.
+In \cref{sect::Kbproj}, we make use of representation theory in order to prove:
+
+\medskip
+
+\noindent \cref{prop:exchangeablePairsNKC} (ii): \emph{The non-kissing fan~$\Fan(\quiver)$ has the unique exchange relation property.}
+
+\medskip
+
+\cref{subsubsec:simplicialTypeConeNKC} is dedicated to giving a purely combinatorial proof of:
+
+\medskip
+
+\noindent \cref{coro:simplicialTypeConeNKC}: \emph{Assume that the gentle bound quiver~$\quiver$ is brick and 2-acyclic.
+Then the type cone~$\typeCone(\Fan(\quiver))$ is simplicial.}
+
+\medskip
+
+An alternative algebraic proof, using the main result of \cref{sec:extricats}, is given in \cref{sect::Kbproj}.
+
+Write~$\strings$ for the set of all strings of~$\quiver$, and~$\walks$ for the set of all walks on~$\quiver$ (i.e.
+of all strings of the blossoming bound quiver of~$\quiver$ that join two blossom vertices).
+If~$\sigma$ is a string of~$\quiver$, we make use of the evocative notations~$\cc{\sigma}, \hh{\sigma}, \hc{\sigma}, \ch{\sigma}$ for the walks obtained by adding, in the blossoming bound quiver, hooks or cohooks at each end of~$\sigma$.
+We make use of our type cone approach to deduce:
+
+\medskip
+
+\noindent \cref{coro:allPolytopalRealizationsNKC}: \emph{For any brick and $2$-acyclic gentle quiver~$\quiver$ and any~$\b{\ell} \in \R_{>0}^{\strings}$, the polytope
+\[
+R_\b{\ell}(\quiver) \eqdef \set{\b{z} \in \R^{\walks}}{\begin{array}{l} \b{z} \ge 0 \qquad\text{and}\qquad \b{z}_\omega = 0 \text{ for any improper walk } \omega \\ \b{z}_{\cc{\sigma}} + \b{z}_{\hh{\sigma}} - \b{z}_{\hc{\sigma}} - \b{z}_{\ch{\sigma}} = \b{\ell}_\sigma \text{ for all } \sigma \in \strings\end{array}}
+\]
+is a realization of the non-kissing fan~$\gvectorFan[\quiver]$.
+Moreover, the polytopes~$R_\b{\ell}(\quiver)$ for~$\b{\ell} \in \R_{>0}^{\strings}$ describe all polytopal realizations of~$\gvectorFan[\quiver]$.}
+
+\bigskip
+
+\noindent {\bf Cluster categories}
+
+\medskip
+
+\bigskip
+
+\noindent {\bf Extriangulated categories}
+
+\medskip
 
@@
 \label{coro:simplicialTypeConeNKC}
-For any brick and $2$-acyclic gentle quiver~$\quiver$, the type cone~$\typeCone \big( \gvectorFan[\quiver] \big)$ of the non-kissing fan~$\quiver$ is simplicial.
+For any brick and $2$-acyclic gentle quiver~$\quiver$, the type cone~$\typeCone \big( \gvectorFan[\quiver] \big)$ of the non-kissing fan~$\gvectorFan[\quiver]$ is simplicial.
 \end{corollary}
@@
 
-\begin{corollary}
+\begin{theorem}
 \label{coro:allPolytopalRealizationsNKC}
@@
 Moreover, the polytopes~$R_\b{\ell}(\quiver)$ for~$\b{\ell} \in \R_{>0}^{\strings}$ describe all polytopal realizations of~$\gvectorFan[\quiver]$.
-\end{corollary}
+\end{theorem}
 

### 2019-07-09 thirdPaper/draft/typeConeAssociahedra.tex
uep 2 uerp

@@
 
-\subsection{Unique exchange property}
+\subsection{Unique exchange relation property}
 \label{subsec:uniqueExchangeProperty}
@@
 
-We say that the fan~$\Fan$ has the \defn{unique exchange property} if any two exchangeable rays~$\ray, \ray'$ of~$\Fan$ admit a unique exchange relation.
+We say that the fan~$\Fan$ has the \defn{unique exchange relation property} if any two exchangeable rays~$\ray, \ray'$ of~$\Fan$ admit a unique exchange relation.
 \end{definition}
@@
 There might be several extremal adjacent pairs giving rise to the same facet.
-This happens often when we have the unique exchange property and there are many pairs of maximal cones separating the same exchangeable rays.
+This happens often when we have the unique exchange relation property and there are many pairs of maximal cones separating the same exchangeable rays.
 
@@
 
-Let us also recall the linear dependencies in this fan and observe that it has the unique exchange property discussed in \cref{subsec:uniqueExchangeProperty}.
+Let us also recall the linear dependencies in this fan and observe that it has the unique exchange relation property discussed in \cref{subsec:uniqueExchangeProperty}.
 From now on, we use the convention that~$\gvector{a,b} = 0$ when~$(a,b)$ is a boundary edge of the $(n+3)$-gon.
@@
 \]
-In particular, the fan~$\gvectorFan[n]$ has the unique exchange property.
+In particular, the fan~$\gvectorFan[n]$ has the unique exchange relation property.
 \end{proposition}
@@
 Assume moreover that, for any indecomposable~$\Lambda$-module~$M$, the space~$\Hom{\Lambda}(M, \tau^2 M)$ vanishes.
-Then the support~$\tau$-tilting fan of~$\Lambda$ has the unique exchange property and its type cone is simplicial.
+Then the support~$\tau$-tilting fan of~$\Lambda$ has the unique exchange relation property and its type cone is simplicial.
 \end{corollary}
@@
 \begin{proof}[Proof of \cref{coro::simplicialTypeConeNKCalgebraic}]
-The unique exchange property follows from \cref{prop::exchange conflations are unique} (2).
+The unique exchange relation property follows from \cref{prop::exchange conflations are unique} (2).
 By \cref{lemma::characterization Gentle 2-acyclic}, the assumptions of \cref{theo::brick-algebra-condition} are satisfied.

### 2019-07-09 thirdPaper/draft/typeConeAssociahedra.tex
coro:simplicialTypeConeCA typo
main results part II

@@
 Let~$\quiver = (Q,I)$ be a gentle bound quiver, and let~$\Fan(\quiver)$ be the fan of its~$\b{g}$-vectors (\cref{subsubsec:nonkissingComplex}), also called its non-kissing fan.
-In \cref{sect::Kbproj}, we make use of representation theory in order to prove:
+We prove in \cref{sect::Kbproj}, by making use of representation theory:
 
@@
 
+In \cref{sec:clusterCategories}, we prove an analogue for cluster categories of M. Auslander's result~\cite{Auslander1984}.
+We are mainly motivated by the fact that itt has for a consequence that the type cones of the cluster fans of finite type are simplicial.
+However, this result is of independent interest and sheds new lights on the Grothendieck groups of cluster categories.
+
+Let~$\cat$ be a cluster category with finitely many isomorphism classes of indecomposable objects (see \cref{sect::setting} for the precise and more general setting in which the theorem is proven).
+Let~$\Ksp(\cat)$ be the split Grothendieck group of~$\cat$.
+Fix a cluster-tilting object~$T\in\cat$, and let~$K_0(\cat ; T)$ be the quotient of~$\Ksp(\cat)$ by the relations~$[X]+[Z]-[Y]$ for all triangles
+$
+X\xrightarrow{} Y \xrightarrow{} Z \xrightarrow{h} \susp X
+$
+with~$h \in (\susp T)$.
+Denote by~$\b{g}:\Ksp(\cat) \to K_0(\cat ; T)$ the canonical projection.
+For any indecomposable~$X\in\cat$, write~$\ell_X = [X]+[\susp^{-1}X]-[E]$, where~$E$ is the middle term of an almost split triangle starting at~$X$.
+For any objects~$X,Y\in\cat$, we write~$\langle X, Y \rangle$ for~$\dim_\field\Hom{\Lambda}(FX,FY)$, where~$\Lambda$ is the cluster-tilted algebra~$\End{\cat}(T)$ and~$F$ is the equivalence of categories~$\cat(T,-):\cat/(\susp T) \to \MOD \Lambda$.
+
+\medskip
+
+\noindent Theorem (see \cref{theo::relations-g-vecteurs}): \emph{The set~$L_\cat=\{\ell_X\,|\, X\in\ind(\cat)\setminus\add(\susp T)\}$ is a basis of the kernel of~$\b{g}$ and, for any~$x\in\ker(\b{g})$, we have:}
+\[
+x = \sum_{A \in \ind(\cat) \ssm \add(\susp T)} \frac{\langle x, A \rangle}{\langle \ell_A, A \rangle} \ell_A.
+\]
+
 \bigskip
@@
 \medskip
+
+In \cref{sec:extricats} we prove a more general version of \cref{theo::relations-g-vecteurs} that not only applies to cluster fans, but also to non-kissing fans.
+Once more, our main motivation is to prove that the type cone of the non-kissing fan of a brick and 2-acyclic gentle algebra is simplicial, but the results are of independent interest, and might be useful for studying the type cones of other families of simplicial fans.
+
+Let~$\cat$ be an extriangulated category (\cref{sect::recollections extricats}) with a fixed projective object~$T$ such that the morphism~$T\to 0$ is an inflation and, for each~$X\in\cat$, there is an extriangle~$T_1^X\infl T_0^X\defl X\overset{\delta_X}{\dashrightarrow}$.
+Let~$\susp T$ be the cone of the inflation~$T\infl 0$.
+
+\medskip
+
+\noindent \cref{prop::KRextricat}: \emph{The functor~$\cat(T,-)$ induces an equivalence~$F:\cat/(\susp T) \to \MOD \End{\cat}(T)$.}
+
+\medskip
+
+Our assumptions allow for a well-defined notion of index:~$\ind_T(X)=[T_0^X]-[T_1^X]\in\kzero{\add T}$.
+
+\medskip
+
+\noindent \cref{prop::index iso extricat}: \emph{The index induces an isomorphism of abelian groups from~$\kzero{\cat}$ to~$\kzero{\add T}$.}
+
+\medskip
+
+The previous two statements also hold when~$T$ is an additive subcategory rather than a mere object.
+Assume moreover that~$\cat$ is~$\field$-linear, Ext-finite, Krull--Schmidt and has Auslander--Reiten--Serre duality.
+Then, with notations analoguous to those used for cluster categories above, we obtain the following:
+
+\medskip
+
+\noindent \cref{theorem::extricats}: \emph{The extriangulated category~$\cat$ has only finitely many ismorphism classes of indecomposable objects if and only if the set~$L_\cat$ generates the kernel of the canonical projection~$\b{g}:\Ksp(\cat)\to\kzero{\cat}$.
+In that case~$L_\cat$ is a basis of the kernel of~$\b{g}$ and any~$x\in\ker(\b{g})$ decomposes as}
+\[
+ x = \sum_{A \in \ind(\cat) \ssm \add(\susp T)} \frac{\langle x, A \rangle}{\langle \ell_A, A \rangle} \ell_A.
+\]
 
@@
 \label{coro:simplicialTypeConeCA}
-The type cone~$\typeCone \big( \gvectorFan[n] \big)$ is simplicial.
+The type cone~$\typeCone \big( \gvectorFan[\B_\circ] \big)$ is simplicial.
 \end{corollary}

### 2019-07-09 thirdPaper/draft/typeConeAssociahedra.tex
ask for schematic diagram

@@
 \]
+
+Schematic diagram:\yann{Vincent, Arnau, je suis certain que vous feriez bien mieux que moi. Puis-je vous demander de le représenter ?}
+
+I.1 explains the type cone approach to the problem
+
+This strategy is used in I.2.2 for cluster algebras and in I.2.3 for gentle algebras.
+
+II.3 cluster categories (2-Calabi--Yau triangulated categories) is used in 1.2.2
+
+II.4 generalises II.3, and offers a different proof for I.2.3
 

### 2019-07-09 thirdPaper/draft/typeConeAssociahedra.tex
schematic diagram, a bit more details

@@
 
-II.3 cluster categories (2-Calabi--Yau triangulated categories) is used in 1.2.2
-
-II.4 generalises II.3, and offers a different proof for I.2.3
+II.3 cluster categories (2-Calabi--Yau triangulated categories) is used in 1.2.2 for proving U.E.R.P. and simpliciality of the type cone.
+
+II.4 generalises II.3, is used in I.2.3 for proving the U.E.R.P. and offers a different proof of simpliciality of the type cone .
 

### 2019-07-09 thirdPaper/draft/typeConeAssociahedra.tex
3 typos

@@
 In \cref{sec:clusterCategories}, we prove an analogue for cluster categories of M. Auslander's result~\cite{Auslander1984}.
-We are mainly motivated by the fact that itt has for a consequence that the type cones of the cluster fans of finite type are simplicial.
-However, this result is of independent interest and sheds new lights on the Grothendieck groups of cluster categories.
+We are mainly motivated by the fact that it has for a consequence that the type cones of the cluster fans of finite type are simplicial.
+However, this result is of independent interest and sheds a new light on the Grothendieck groups of cluster categories.
 
@@
 Assume moreover that~$\cat$ is~$\field$-linear, Ext-finite, Krull--Schmidt and has Auslander--Reiten--Serre duality.
-Then, with notations analoguous to those used for cluster categories above, we obtain the following:
+Then, with notations analogous to those used for cluster categories above, we obtain the following:
 

### 2019-07-09 thirdPaper/draft/typeConeAssociahedra.tex
Remark 1.6 is now Definition 1.6

@@
 
-\begin{remark}
+Since the type cone is an~$N$ dimensional cone with a linearity subspace of dimension~$n$, it has at least~$N-n$ facets (thus~$N-n$ extremal adjacent pairs).
+
+\begin{definition}
 \label{rem:dimTypeCone}
-Since the type cone is an~$N$ dimensional cone with a linearity subspace of dimension~$n$, it has at least~$N-n$ facets (thus~$N-n$ extremal adjacent pairs).
-We say that the type cone is \defn{simplicial} when it has precisely $N-n$ facets.
-\end{remark}
+The type cone is \defn{simplicial} if it has precisely $N-n$ facets.
+\end{definition}
 

### 2019-07-09 thirdPaper/draft/typeConeAssociahedra.tex
edditing structure of the paper

--- 2019-07-09 thirdPaper/draft/typeConeAssociahedra.tex
@@
 
-\section*{Main results and logical dependencies}
-
-We give a brief overview of our main results.
-Their logical dependencies are recalled in a schematic diagram at the end of this section.
-
-Let~$\Fan$ be an essential, complete, simplicial, polyhedral fan in~$\R^n$ (all definitions are recalled in \cref{ssec:polytopes and fans}).
-The type cone~$\typeCone(\Fan)$ of~$\Fan$ (\cref{ssec:type cone}), introduced by P. McMullen, is a device that encodes the information about all possible polytopal realizations of~$\Fan$.
-If the simplicial fan~$\Fan$ has the unique exchange relation property (\cref{def:uerp}), then its type cone is easier to describe and study.
-In particular, if moreover the type cone~$\typeCone(\Fan)$ is simplicial (\cref{rem:dimTypeCone}), then all possible polytopal realizations of~$\Fan$ can be described explicitely in~$\R^N_{>0}$, where~$N$ is the number of rays of~$\typeCone(\Fan)$, in terms of~$N-n$ positive real parameters (\cref{coro:simplicialTypeCone}).
-This gives a new point of view on~\cite{ArkaniHamedBaiHeYan,BazierMatteDouvilleMousavandThomasYildirim}, illustrated in \cref{subsec:typeConeAsso} for classical associahedra, that we then apply to two families of~$\b{g}$-vector fans generalizing the~$\b{g}$-vector fans of classical associahedra: The~$\b{g}$-vector fans of cluster algebras of finite type (generalized associahedra), and the~$\b{g}$-vector fans of gentle algebras (non-kissing associahedra, non-crossing associahedra, generalized accordiohedra).
-We also describe the type cone for graph associahedra (\cref{subsec:typeConeGA}), to which our strategy does not apply.
+% \section*{Main results and logical dependencies}
+\subsection*{Structure of the paper: main results and logical dependencies}
+
+We give a brief overview of our main results and the structure of the article.
+In particular, some of the geometric realizations in~\cref{part:geometry} depend on algebraic results whose proof is delayed until~\cref{part:algebra}.
+The goal of this section is to clarify their logical dependencies.
+% Their logical dependencies are recalled in a schematic diagram at the end of this section.
+
+Let~$\Fan$ be an essential complete polyhedral fan in~$\R^n$ (all definitions are recalled in~\cref{ssec:polytopes and fans}).
+The type cone~$\typeCone(\Fan)$ of~$\Fan$ (\cref{ssec:type cone}), introduced by P.
+McMullen~\cite{McMullen-typeCone}, is a polyhedral cone that parametrizes the set of all possible polytopal realizations of~$\Fan$.
+These realizations can be described explicitly as affine sections of the nonnegative orthant~$\R^N_{\geq0}$, where~$N$ is the number of rays of~$\Fan$ (\cref{prop:alternativePolytopalRealization}).
+If $\Fan$ is a simplicial fan and has the unique exchange relation property (\cref{def:uerp}), then its type cone is easier to describe and study.
+And if moreover the type cone~$\typeCone(\Fan)$ is simplicial (\cref{rem:dimTypeCone}), then all possible polytopal realizations of~$\Fan$ can be described explicitely in terms of~$N-n$ positive real parameters (\cref{coro:simplicialTypeCone}).
+This gives a new point of view on~\cite{ArkaniHamedBaiHeYan,BazierMatteDouvilleMousavandThomasYildirim}, illustrated in \cref{subsec:typeConeAsso} for classical associahedra, that we then apply to two families of~$\b{g}$-vector fans generalizing the~$\b{g}$-vector fans of classical associahedra: The~$\b{g}$-vector fans of cluster algebras of finite type (generalized associahedra) in~\cref{subsec:typeConeCA}, and the~$\b{g}$-vector fans of gentle algebras (non-kissing associahedra, non-crossing associahedra, generalized accordiohedra) in~\cref{subsec:typeConeNKC}.
+We also completely describe the facets of the type cone for graph associahedra in~\cref{subsec:typeConeGA}, to which our strategy does not apply, as only the classical associahedron has a simplicial type cone.
 
@@
 We first consider the~$\b{g}$-vector fan~$\Fan(\B_\circ)$ of a skew-symmetrizable cluster algebra of finite type, with respect to any initial exchange matrix of finite type~$\B_\circ$.
-A reformulation of~\cite[Thm 7.5]{BuanMarshReinekeReitenTodorov} gives the first step towards applying our type cone strategy.
-
-\medskip
-
-\noindent \cref{prop:uniqueExchangePropertyCA}: \emph{The cluster fan~$\Fan(\B_\circ)$ has the unique exchange relation property.}
-
-\medskip
-
-The second step follows from our main result in \cref{sec:clusterCategories}, which makes use of representation theory of finite dimensional algebras and additive categorification of cluster algebras.
-
-\medskip
-
-\noindent \cref{coro:simplicialTypeConeCA}: \emph{The type cone~$\typeCone(\Fan(\B_\circ))$ is simplicial.}
-
-\medskip
-
-We consider the set~$\meshes$ of all pairs~$\{x,x'\}$ related by non-initial mesh mutations (\cref{def:meshMutation}), and we denote by~$\principalVariables$ the set of cluster variables.
-Let~$\{x,x'\}\in\meshes$, and let~$X,X'$ be two clusters such that~$X\setminus\{x\}=X'\setminus\{x'\}$.
-For any~$y\in\principalVariables$, define~$\alpha_{x,x',y}$ to be~$|b_{xy}|$ if~$y\in X\cap X'$ and 0 otherwise.
-By the unique exchange relation property, the~$\alpha_{x,x',y}$'s do not depend on the specific choice of the clusters~$X,X'$.
+We provide the following polytopal realizations of~$\Fan(\B_\circ)$:
+% We consider the set~$\meshes$ of all pairs~$\{x,x'\}$ related by non-initial mesh mutations (\cref{def:meshMutation}), and we denote by~$\principalVariables$ the set of cluster variables.
+% Let~$\{x,x'\}\in\meshes$, and let~$X,X'$ be two clusters such that~$X\setminus\{x\}=X'\setminus\{x'\}$.
+% For any~$y\in\principalVariables$, define~$\alpha_{x,x',y}$ to be~$|b_{xy}|$ if~$y\in X\cap X'$ and 0 otherwise.
+% By the unique exchange relation property, the~$\alpha_{x,x',y}$'s do not depend on the specific choice of the clusters~$X,X'$.
 
@@
 
+\medskip
+
+Here, $\meshes$ represents the set of all pairs~$\{x,x'\}$ related by non-initial mesh mutations (\cref{def:meshMutation}), and~$\principalVariables$ the set of cluster variables.
+For $\{x,x'\} \in \meshes$ and $y \in \principalVariables$, the coefficient $\alpha_{x,x',y}$ is defined as follows: $\alpha_{x,x',y}$ is set to be~$|b_{xy}|$ if~$y\in X\cap X'$ and $0$ otherwise, where~$X,X'$ are any two clusters such that~$X\setminus\{x\}=X'\setminus\{x'\}$.
+By the unique exchange relation property, the~$\alpha_{x,x',y}$'s do not depend on the specific choice of the clusters~$X,X'$.
+
+\medskip
+
+Some crucial pieces of the proof of~\cref{thm:allPolytopalRealizationsCA} use cluster categories (2-Calabi--Yau triangulated categories) and are deferred to~\cref{sec:clusterCategories}.
+Namely, a reformulation of~\cite[Thm 7.5]{BuanMarshReinekeReitenTodorov}, proved in~\cref{sec:clusterCategories}, gives the first step towards applying our type cone strategy.
+
+\medskip
+
+\noindent \cref{prop:uniqueExchangePropertyCA}: \emph{The cluster fan~$\Fan(\B_\circ)$ has the unique exchange relation property.}
+
+\medskip
+
+And the second step follows from our main result in \cref{sec:clusterCategories}, which makes use of representation theory of finite dimensional algebras and additive categorification of cluster algebras.
+
+\medskip
+
+\noindent \cref{coro:simplicialTypeConeCA}: \emph{The type cone~$\typeCone(\Fan(\B_\circ))$ is simplicial.}
+
+\medskip
 \bigskip
@@
 \noindent \cref{prop:exchangeablePairsNKC} (ii): \emph{The non-kissing fan~$\Fan(\quiver)$ has the unique exchange relation property.}
-
+\arnau{In the proof of \cref{prop:exchangeablePairsNKC} it says that the UERP follows from PPP17}
 \medskip
@@
 
-Write~$\strings$ for the set of all strings of~$\quiver$, and~$\walks$ for the set of all walks on~$\quiver$ (i.e.
+Combining these pieces, we make use of our type cone approach to deduce:
+
+\medskip
+
+\noindent \cref{coro:allPolytopalRealizationsNKC}: \emph{For any brick and $2$-acyclic gentle quiver~$\quiver$ and any~$\b{\ell} \in \R_{>0}^{\strings}$, the polytope
+\[
+R_\b{\ell}(\quiver) \eqdef \set{\b{z} \in \R^{\walks}}{\begin{array}{l} \b{z} \ge 0 \qquad\text{and}\qquad \b{z}_\omega = 0 \text{ for any improper walk } \omega \\ \b{z}_{\cc{\sigma}} + \b{z}_{\hh{\sigma}} - \b{z}_{\hc{\sigma}} - \b{z}_{\ch{\sigma}} = \b{\ell}_\sigma \text{ for all } \sigma \in \strings\end{array}}
+\]
+is a realization of the non-kissing fan~$\gvectorFan[\quiver]$.
+Moreover, the polytopes~$R_\b{\ell}(\quiver)$ for~$\b{\ell} \in \R_{>0}^{\strings}$ describe all polytopal realizations of~$\gvectorFan[\quiver]$.}
+
+\medskip
+
+Here, $\strings$ is the set of all strings of~$\quiver$, and~$\walks$ the set of all walks on~$\quiver$ (i.e.
 of all strings of the blossoming bound quiver of~$\quiver$ that join two blossom vertices).
 If~$\sigma$ is a string of~$\quiver$, we make use of the evocative notations~$\cc{\sigma}, \hh{\sigma}, \hc{\sigma}, \ch{\sigma}$ for the walks obtained by adding, in the blossoming bound quiver, hooks or cohooks at each end of~$\sigma$.
-We make use of our type cone approach to deduce:
+
+\bigskip
+
+\noindent {\bf Graphical nested complexes} (\cref{subsec:typeConeGA})
 
@@
 
-\noindent \cref{coro:allPolytopalRealizationsNKC}: \emph{For any brick and $2$-acyclic gentle quiver~$\quiver$ and any~$\b{\ell} \in \R_{>0}^{\strings}$, the polytope
-\[
-R_\b{\ell}(\quiver) \eqdef \set{\b{z} \in \R^{\walks}}{\begin{array}{l} \b{z} \ge 0 \qquad\text{and}\qquad \b{z}_\omega = 0 \text{ for any improper walk } \omega \\ \b{z}_{\cc{\sigma}} + \b{z}_{\hh{\sigma}} - \b{z}_{\hc{\sigma}} - \b{z}_{\ch{\sigma}} = \b{\ell}_\sigma \text{ for all } \sigma \in \strings\end{array}}
-\]
-is a realization of the non-kissing fan~$\gvectorFan[\quiver]$.
-Moreover, the polytopes~$R_\b{\ell}(\quiver)$ for~$\b{\ell} \in \R_{>0}^{\strings}$ describe all polytopal realizations of~$\gvectorFan[\quiver]$.}
+Even though graph associahedra do not have simplicial type cones except for the path (\cref{prop:simplicialnestedfan}), we provide a non-redundant characterization of the type cones of graphical nested fans:
+
+\medskip
+
+\noindent \cref{cor:typeconenestedfan}:\emph{
+Consider a graph~$\graphG$ on~$\ground$ with tubes~$\tubes$. 
+Then, for a height vector~$\b{h} \in \R^{\tubes}$, the nested fan~$\gvectorFan[\graphG]$ is the normal fan of the graph associahedron
+\[
+\set{\b{x} \in \R^\ground}{\dotprod{\gvector{\tube}}{\b{x}} \le \b{h}_{\tube} \text{ for any tube } \tube \in \tubes}
+\]
+if and only if~$\b{h}_{\varnothing} = \b{h}_{\graphG} = 0$ and
+ $\b{h}_{\tube[s] \ssm \{v'\}} + \b{h}_{\tube[s] \ssm \{v\}} > \b{h}_{\tube[s]} + \b{h}_{\tube[s] \ssm \{v, v'\}}$ for any tube~$\tube[s] \in \tubes$ and distinct non-disconnecting vertices~$v,v'$ of~$\tube[s]$.
+}
 
@@
 
-In \cref{sec:clusterCategories}, we prove an analogue for cluster categories of M. Auslander's result~\cite{Auslander1984}.
-We are mainly motivated by the fact that itt has for a consequence that the type cones of the cluster fans of finite type are simplicial.
+In \cref{sec:clusterCategories}, we prove an analogue for cluster categories of M.
+Auslander's result~\cite{Auslander1984}.
+\arnau{Which result?
+Is it famous?
+Should we say something like Auslaunder's famous result from...?
+}
+We are mainly motivated by the fact that it has for a consequence that the type cones of the cluster fans of finite type are simplicial.
 However, this result is of independent interest and sheds new lights on the Grothendieck groups of cluster categories.
@@
 
-Schematic diagram:\yann{Vincent, Arnau, je suis certain que vous feriez bien mieux que moi. Puis-je vous demander de le représenter ?}
-
-I.1 explains the type cone approach to the problem
-
-This strategy is used in I.2.2 for cluster algebras and in I.2.3 for gentle algebras.
-
-II.3 cluster categories (2-Calabi--Yau triangulated categories) is used in 1.2.2 for proving U.E.R.P. and simpliciality of the type cone.
-
-II.4 generalises II.3, is used in I.2.3 for proving the U.E.R.P. and offers a different proof of simpliciality of the type cone .
+% Schematic diagram:\yann{Vincent, Arnau, je suis certain que vous feriez bien mieux que moi. Puis-je vous demander de le représenter ?}
+% 
+% I.1 explains the type cone approach to the problem
+% 
+% This strategy is used in I.2.2 for cluster algebras and in I.2.3 for gentle algebras.
+% 
+% II.3 cluster categories (2-Calabi--Yau triangulated categories) is used in 1.2.2 for proving U.E.R.P. and simpliciality of the type cone.
+% 
+% II.4 generalises II.3, is used in I.2.3 for proving the U.E.R.P. and offers a different proof of simpliciality of the type cone .
 
@@
 
-\begin{corollary}
-Consider a graph~$\graphG$ on~$\ground$ with tubes~$\tubes$ and a height vector~$\b{h} \in \R^{\tubes}$ such that~$\b{h}_{\varnothing} = \b{h}_{\graphG} = 0$ and satisfying 
+\begin{corollary}\label{cor:typeconenestedfan}
+Consider a graph~$\graphG$ on~$\ground$ with tubes~$\tubes$. 
+Then, for a height vector~$\b{h} \in \R^{\tubes}$, the nested fan~$\gvectorFan[\graphG]$ is the normal fan of the graph associahedron
+\[
+\set{\b{x} \in \R^\ground}{\dotprod{\gvector{\tube}}{\b{x}} \le \b{h}_{\tube} \text{ for any tube } \tube \in \tubes}
+\]
+if and only if~$\b{h}_{\varnothing} = \b{h}_{\graphG} = 0$ and
  $\b{h}_{\tube[s] \ssm \{v'\}} + \b{h}_{\tube[s] \ssm \{v\}} > \b{h}_{\tube[s]} + \b{h}_{\tube[s] \ssm \{v, v'\}}$ for any tube~$\tube[s] \in \tubes$ and distinct non-disconnecting vertices~$v,v'$ of~$\tube[s]$.
-Then the nested fan~$\gvectorFan[\graphG]$ is the normal fan of the graph associahedron
-\[
-\set{\b{x} \in \R^\ground}{\dotprod{\gvector{\tube}}{\b{x}} \le \b{h}_{\tube} \text{ for any tube } \tube \in \tubes}.
-\]
 \end{corollary}
@@
 
-\begin{proposition}
+\begin{proposition}\label{prop:simplicialnestedfan}
 The type cone~$\typeCone \big( \gvectorFan[\graphG] \big)$ is simplicial if and only if~$\graphG$ is a path.

### 2019-07-09 thirdPaper/draft/typeConeAssociahedra.tex

@@
 
-Even though graph associahedra do not have simplicial type cones except for the path (\cref{prop:simplicialnestedfan}), we provide a non-redundant characterization of the type cones of graphical nested fans:
+Even though graph associahedra do not have simplicial type cones except for the path (\cref{prop:simplicialnestedfan}), we provide a non-redundant characterization of the type cones of all graphical nested fans:
 
@@
 
-% Schematic diagram:\yann{Vincent, Arnau, je suis certain que vous feriez bien mieux que moi. Puis-je vous demander de le représenter ?}
+% Schematic diagram:
+\yann{Vincent, Arnau, je suis certain que vous feriez bien mieux que moi. Puis-je vous demander de le représenter ?}
+\arnau{As tu une idée en tête de comment le réprsenter? Je trouve que ce que t'as écrit est très clair et je ne vois pas comment faire une schema qui le ameillore}
 % 

### 2019-07-09 thirdPaper/draft/typeConeAssociahedra.tex
One typo
Auslander's result

@@
 
-In \cref{sec:clusterCategories}, we prove an analogue for cluster categories of M.
-Auslander's result~\cite{Auslander1984}.
+In \cref{sec:clusterCategories}, we prove an analogue for cluster categories of a result of M.
+Auslander for module categories of Artin algebras~\cite{Auslander1984}.
 \arnau{Which result?
@@
 Should we say something like Auslaunder's famous result from...?
-}
+}\pg{I've reformulated slightly.
+Auslander was extremely prolific :-)}
 We are mainly motivated by the fact that it has for a consequence that the type cones of the cluster fans of finite type are simplicial.

### 2019-07-10 thirdPaper/draft/typeConeAssociahedra.tex
Comment on Proposition 2.34 (ii) in answer to Arnau's comment.
corrected a typo and removed a comment

@@
 \noindent \cref{prop:exchangeablePairsNKC} (ii): \emph{The non-kissing fan~$\Fan(\quiver)$ has the unique exchange relation property.}
-\arnau{In the proof of \cref{prop:exchangeablePairsNKC} it says that the UERP follows from PPP17}
+\arnau{In the proof of \cref{prop:exchangeablePairsNKC} it says that the UERP follows from PPP17}\pg{Not for point (ii), which uses results of Section 4}
 \medskip
@@
 
-In \cref{sec:clusterCategories}, we prove an analogue for cluster categories of a result of M.
-Auslander for module categories of Artin algebras~\cite{Auslander1984}.
-\arnau{Which result?
-Is it famous?
-Should we say something like Auslaunder's famous result from...?
-}\pg{I've reformulated slightly.
-Auslander was extremely prolific :-)}
+In \cref{sec:clusterCategories}, we prove an analogue for cluster categories of a result of M. Auslander for module categories of Artin algebras~\cite{Auslander1984}. 
 We are mainly motivated by the fact that it has for a consequence that the type cones of the cluster fans of finite type are simplicial.
@@
 \yann{Vincent, Arnau, je suis certain que vous feriez bien mieux que moi. Puis-je vous demander de le représenter ?}
-\arnau{As tu une idée en tête de comment le réprsenter? Je trouve que ce que t'as écrit est très clair et je ne vois pas comment faire une schema qui le ameillore}
+\arnau{As tu une idée en tête de comment le répresenter? Je trouve que ce que t'as écrit est très clair et je ne vois pas comment faire une schema qui le ameillore}
 % 
@@
 \begin{proof}
-Points~(i), (iii) and~(iv) where shown in~\cite[Prop.~2.33, Thm.~4.17 \& Prop~4.16]{PaluPilaudPlamondon-nonkissing}. We postpone the proof of point~(ii) until \cref{coro::exchangeablePairsNKC}.
+Points~(i), (iii) and~(iv) were shown in~\cite[Prop.~2.33, Thm.~4.17 \& Prop~4.16]{PaluPilaudPlamondon-nonkissing}. We postpone the proof of point~(ii) until \cref{coro::exchangeablePairsNKC}.
 \end{proof}

### 2019-07-11 thirdPaper/draft/typeConeAssociahedra.tex
corollaire uerp gentle

@@
 Let~$\quiver = (Q,I)$ be a gentle bound quiver, and let~$\Fan(\quiver)$ be the fan of its~$\b{g}$-vectors (\cref{subsubsec:nonkissingComplex}), also called its non-kissing fan.
-We prove in \cref{sect::Kbproj}, by making use of representation theory:
+We prove \cref{prop:exchangeablePairsNKC} (ii) in \cref{sect::Kbproj}, by making use of representation theory, and state here the following consequence:
 
@@
 
-\noindent \cref{prop:exchangeablePairsNKC} (ii): \emph{The non-kissing fan~$\Fan(\quiver)$ has the unique exchange relation property.}
+\noindent \cref{corollary: uerp gentle}: \emph{The non-kissing fan~$\Fan(\quiver)$ has the unique exchange relation property.}
 \arnau{In the proof of \cref{prop:exchangeablePairsNKC} it says that the UERP follows from PPP17}\pg{Not for point (ii), which uses results of Section 4}
@@
 \]
-In other words, the non-kissing fan of~$\quiver$ has the unique exchange relation property.
+% In other words, the non-kissing fan of~$\quiver$ has the unique exchange relation property.
 \item The $\b{c}$-vector orthogonal to all $\b{g}$-vectors~$\gvector{\lambda}$ for~$\lambda \in F \cap F'$ is the multiplicity vector~$\multiplicityVector_{\sigma}$ of the vertices of the substring~$\sigma$ of~$\omega$ and~$\omega'$.
@@
 %
-\begin{figure}[b]
+
+\begin{proof}
+Points~(i), (iii) and~(iv) were shown in~\cite[Prop.~2.33, Thm.~4.17 \& Prop~4.16]{PaluPilaudPlamondon-nonkissing}. We postpone the proof of point~(ii) until \cref{coro::exchangeablePairsNKC}.
+\end{proof}
+
+As a consequence of points $(ii)$ and $(iii)$ in \cref{prop:exchangeablePairsNKC}, we obtain the:
+\begin{corollary}
+\label{corollary: uerp gentle}
+For any non-kissing finite gentle bound quiver~$\quiver$, the non-kissing fan~$\Fan(\quiver)$ has the unique exchange relation property.
+\end{corollary}
+
+\begin{figure}[h]
 	\capstart
@@
 \end{proposition}
-
-\begin{proof}
-Points~(i), (iii) and~(iv) were shown in~\cite[Prop.~2.33, Thm.~4.17 \& Prop~4.16]{PaluPilaudPlamondon-nonkissing}. We postpone the proof of point~(ii) until \cref{coro::exchangeablePairsNKC}.
-\end{proof}
 

### 2019-07-11 thirdPaper/draft/typeConeAssociahedra.tex
schema
Remark 1.6 changed to a Definition

@@
 
+\bigskip
+
+\noindent {\bf Schematic diagram of logical dependencies:}
+
+\medskip
+
+\begin{center}
+\includegraphics[scale=.9]{Schema}
+\end{center}
+
 % Schematic diagram:
-\yann{Vincent, Arnau, je suis certain que vous feriez bien mieux que moi. Puis-je vous demander de le représenter ?}
-\arnau{As tu une idée en tête de comment le répresenter? Je trouve que ce que t'as écrit est très clair et je ne vois pas comment faire une schema qui le ameillore}
+% \yann{Vincent, Arnau, je suis certain que vous feriez bien mieux que moi. Puis-je vous demander de le représenter ?}
+% \arnau{As tu une idée en tête de comment le répresenter? Je trouve que ce que t'as écrit est très clair et je ne vois pas comment faire une schema qui le ameillore}
 % 
@@
 
-\begin{remark}
+Since the type cone is an~$N$-dimensional cone with a linearity subspace of dimension~$n$, it has at least~$N-n$ facets (thus~$N-n$ extremal adjacent pairs).
+
+\begin{definition}
 \label{rem:dimTypeCone}
-Since the type cone is an~$N$ dimensional cone with a linearity subspace of dimension~$n$, it has at least~$N-n$ facets (thus~$N-n$ extremal adjacent pairs).
-We say that the type cone is \defn{simplicial} when it has precisely $N-n$ facets.
-\end{remark}
+The type cone is \defn{simplicial} when it has precisely $N-n$ facets.
+\end{definition}
 

### 2019-07-12 thirdPaper/draft/typeConeAssociahedra.tex
workout latex

@@
 
-% \section*{Main results and logical dependencies}
-\subsection*{Structure of the paper: main results and logical dependencies}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section*{Structure of the paper: main results and logical dependencies}
 
@@
 % Their logical dependencies are recalled in a schematic diagram at the end of this section.
+
+\para{Type cone approach}
+(\cref{sec:typeCone})
 
@@
 
-\medskip
-
-\noindent {\bf Cluster algebras of finite type} (\cref{subsec:typeConeCA})
-
-\medskip
-
+\para{Cluster algebras of finite type}
+(\cref{subsec:typeConeCA})
+
+\noindent
 We first consider the~$\b{g}$-vector fan~$\Fan(\B_\circ)$ of a skew-symmetrizable cluster algebra of finite type, with respect to any initial exchange matrix of finite type~$\B_\circ$.
@@
 
-\medskip
-
-\noindent \cref{thm:allPolytopalRealizationsCA}: 
-\emph{For any~$\b{\ell} \in \R_{>0}^{\meshes}$, the polytope
+\newtheorem*{thm:allPolytopalRealizationsCA}{\cref{thm:allPolytopalRealizationsCA}}
+\begin{thm:allPolytopalRealizationsCA}
+For any~$\b{\ell} \in \R_{>0}^{\meshes}$, the polytope
 \[
@@
 is a generalized associahedron, whose normal fan is the cluster fan~$\gvectorFan[\B_\circ]$.
-Moreover, the polytopes~$R_\b{\ell}(\B_\circ)$ for~$\b{\ell} \in \R_{>0}^{\meshes}$ describe all polytopal realizations of~$\gvectorFan[\B_\circ]$.}
-
-\medskip
+Moreover, the polytopes~$R_\b{\ell}(\B_\circ)$ for~$\b{\ell} \in \R_{>0}^{\meshes}$ describe all polytopal realizations of~$\gvectorFan[\B_\circ]$.
+\end{thm:allPolytopalRealizationsCA}
 
@@
 Some crucial pieces of the proof of~\cref{thm:allPolytopalRealizationsCA} use cluster categories (2-Calabi--Yau triangulated categories) and are deferred to~\cref{sec:clusterCategories}.
-Namely, a reformulation of~\cite[Thm 7.5]{BuanMarshReinekeReitenTodorov}, proved in~\cref{sec:clusterCategories}, gives the first step towards applying our type cone strategy.
-
-\medskip
-
-\noindent \cref{prop:uniqueExchangePropertyCA}: \emph{The cluster fan~$\Fan(\B_\circ)$ has the unique exchange relation property.}
-
-\medskip
+Namely, a reformulation of~\cite[Thm.~7.5]{BuanMarshReinekeReitenTodorov}, proved in~\cref{sec:clusterCategories}, gives the first step towards applying our type cone strategy.
+
+\newtheorem*{prop:uniqueExchangePropertyCA}{\cref{prop:uniqueExchangePropertyCA}}
+\begin{prop:uniqueExchangePropertyCA}
+The cluster fan~$\Fan(\B_\circ)$ has the unique exchange relation property.
+\end{prop:uniqueExchangePropertyCA}
 
@@
 
-\medskip
-
-\noindent \cref{coro:simplicialTypeConeCA}: \emph{The type cone~$\typeCone(\Fan(\B_\circ))$ is simplicial.}
-
-\medskip
-\bigskip
-
-\noindent {\bf Gentle algebras, non-kissing complex, generalized accordiohedra} (\cref{subsec:typeConeNKC})
-
-\medskip
-
+\newtheorem*{coro:simplicialTypeConeCA}{\cref{coro:simplicialTypeConeCA}}
+\begin{coro:simplicialTypeConeCA}
+The type cone~$\typeCone(\Fan(\B_\circ))$ is simplicial.
+\end{coro:simplicialTypeConeCA}
+
+\para{Gentle algebras, non-kissing complex, generalized accordiohedra}
+(\cref{subsec:typeConeNKC})
+
+\noindent
 The same strategy is applied to a class of finite dimensional algebras, called gentle algebras, whose representations are combinatorially well understood.
@@
 Let~$\quiver = (Q,I)$ be a gentle bound quiver, and let~$\Fan(\quiver)$ be the fan of its~$\b{g}$-vectors (\cref{subsubsec:nonkissingComplex}), also called its non-kissing fan.
-We prove \cref{prop:exchangeablePairsNKC} (ii) in \cref{sect::Kbproj}, by making use of representation theory, and state here the following consequence:
-
-\medskip
-
-\noindent \cref{corollary: uerp gentle}: \emph{The non-kissing fan~$\Fan(\quiver)$ has the unique exchange relation property.}
-\arnau{In the proof of \cref{prop:exchangeablePairsNKC} it says that the UERP follows from PPP17}\pg{Not for point (ii), which uses results of Section 4}
-\medskip
-
-\cref{subsubsec:simplicialTypeConeNKC} is dedicated to giving a purely combinatorial proof of:
-
-\medskip
-
-\noindent \cref{coro:simplicialTypeConeNKC}: \emph{Assume that the gentle bound quiver~$\quiver$ is brick and 2-acyclic.
-Then the type cone~$\typeCone(\Fan(\quiver))$ is simplicial.}
-
-\medskip
-
-An alternative algebraic proof, using the main result of \cref{sec:extricats}, is given in \cref{sect::Kbproj}.
-
-Combining these pieces, we make use of our type cone approach to deduce:
-
-\medskip
-
-\noindent \cref{coro:allPolytopalRealizationsNKC}: \emph{For any brick and $2$-acyclic gentle quiver~$\quiver$ and any~$\b{\ell} \in \R_{>0}^{\strings}$, the polytope
+We prove \cref{prop:exchangeablePairsNKC} (ii) in \cref{sec:Kbproj}, by making use of representation theory, and state here the following consequence.
+
+\newtheorem*{corollary: uerp gentle}{\cref{corollary: uerp gentle}}
+\begin{corollary: uerp gentle}
+The non-kissing fan~$\Fan(\quiver)$ has the unique exchange relation property.
+\end{corollary: uerp gentle}
+
+\cref{subsubsec:simplicialTypeConeNKC} is dedicated to giving a purely combinatorial proof of the following statement.
+
+\newtheorem*{coro:simplicialTypeConeNKC}{\cref{coro:simplicialTypeConeNKC}}
+\begin{coro:simplicialTypeConeNKC}
+Assume that the gentle bound quiver~$\quiver$ is brick and 2-acyclic.
+Then the type cone~$\typeCone(\Fan(\quiver))$ is simplicial.
+\end{coro:simplicialTypeConeNKC}
+
+An alternative algebraic proof, using the main result of \cref{sec:extricats}, is given in \cref{sec:Kbproj}.
+
+Combining these pieces, we make use of our type cone approach to deduce the following statement.
+
+\newtheorem*{coro:allPolytopalRealizationsNKC}{\cref{coro:allPolytopalRealizationsNKC}}
+\begin{coro:allPolytopalRealizationsNKC}
+For any brick and $2$-acyclic gentle quiver~$\quiver$ and any~$\b{\ell} \in \R_{>0}^{\strings}$, the polytope
 \[
@@
 is a realization of the non-kissing fan~$\gvectorFan[\quiver]$.
-Moreover, the polytopes~$R_\b{\ell}(\quiver)$ for~$\b{\ell} \in \R_{>0}^{\strings}$ describe all polytopal realizations of~$\gvectorFan[\quiver]$.}
-
-\medskip
+Moreover, the polytopes~$R_\b{\ell}(\quiver)$ for~$\b{\ell} \in \R_{>0}^{\strings}$ describe all polytopal realizations of~$\gvectorFan[\quiver]$.
+\end{coro:allPolytopalRealizationsNKC}
 
@@
 
-\bigskip
-
-\noindent {\bf Graphical nested complexes} (\cref{subsec:typeConeGA})
-
-\medskip
+\para{Graphical nested complexes}
+(\cref{subsec:typeConeGA})
 
@@
 
-\medskip
-
-\noindent \cref{cor:typeconenestedfan}:\emph{
+\newtheorem*{cor:typeconenestedfan}{\cref{cor:typeconenestedfan}}
+\begin{cor:typeconenestedfan}
 Consider a graph~$\graphG$ on~$\ground$ with tubes~$\tubes$. 
@@
  $\b{h}_{\tube[s] \ssm \{v'\}} + \b{h}_{\tube[s] \ssm \{v\}} > \b{h}_{\tube[s]} + \b{h}_{\tube[s] \ssm \{v, v'\}}$ for any tube~$\tube[s] \in \tubes$ and distinct non-disconnecting vertices~$v,v'$ of~$\tube[s]$.
-}
-
-\bigskip
-
-\noindent {\bf Cluster categories}
-
-\medskip
+\end{cor:typeconenestedfan}
+
+\para{Cluster categories}
+(\cref{sec:clusterCategories})
 
@@
 
-Let~$\cat$ be a cluster category with finitely many isomorphism classes of indecomposable objects (see \cref{sect::setting} for the precise and more general setting in which the theorem is proven).
+Let~$\cat$ be a cluster category with finitely many isomorphism classes of indecomposable objects (see \cref{sec:setting} for the precise and more general setting in which the theorem is proven).
 Let~$\Ksp(\cat)$ be the split Grothendieck group of~$\cat$.
@@
 
-\medskip
-
-\noindent Theorem (see \cref{theo::relations-g-vecteurs}): \emph{The set~$L_\cat=\{\ell_X\,|\, X\in\ind(\cat)\setminus\add(\susp T)\}$ is a basis of the kernel of~$\b{g}$ and, for any~$x\in\ker(\b{g})$, we have:}
+\newtheorem*{thm:relations-g-vecteurs}{\cref{thm:relations-g-vecteurs}}
+\begin{thm:relations-g-vecteurs}
+The set~$L_\cat \eqdef \set{\ell_X}{X \in \ind(\cat) \setminus \add(\susp T)}$ is a basis of the kernel of~$\b{g}$ and, for any~$x \in \ker(\b{g})$, we have:
 \[
@@
 \]
-
-\bigskip
-
-\noindent {\bf Extriangulated categories}
-
-\medskip
-
-In \cref{sec:extricats} we prove a more general version of \cref{theo::relations-g-vecteurs} that not only applies to cluster fans, but also to non-kissing fans.
+\end{thm:relations-g-vecteurs}
+
+\para{Extriangulated categories}
+(\cref{sec:extricats})
+
+In \cref{sec:extricats} we prove a more general version of \cref{thm:relations-g-vecteurs} that not only applies to cluster fans, but also to non-kissing fans.
 Once more, our main motivation is to prove that the type cone of the non-kissing fan of a brick and 2-acyclic gentle algebra is simplicial, but the results are of independent interest, and might be useful for studying the type cones of other families of simplicial fans.
 
-Let~$\cat$ be an extriangulated category (\cref{sect::recollections extricats}) with a fixed projective object~$T$ such that the morphism~$T\to 0$ is an inflation and, for each~$X\in\cat$, there is an extriangle~$T_1^X\infl T_0^X\defl X\overset{\delta_X}{\dashrightarrow}$.
+Let~$\cat$ be an extriangulated category (\cref{sec:recollections extricats}) with a fixed projective object~$T$ such that the morphism~$T\to 0$ is an inflation and, for each~$X\in\cat$, there is an extriangle~$T_1^X\infl T_0^X\defl X\overset{\delta_X}{\dashrightarrow}$.
 Let~$\susp T$ be the cone of the inflation~$T\infl 0$.
 
-\medskip
-
-\noindent \cref{prop::KRextricat}: \emph{The functor~$\cat(T,-)$ induces an equivalence~$F:\cat/(\susp T) \to \MOD \End{\cat}(T)$.}
-
-\medskip
+\newtheorem*{prop:KRextricat}{\cref{prop:KRextricat}}
+\begin{prop:KRextricat}
+The functor~$\cat(T,-)$ induces an equivalence~$F:\cat/(\susp T) \to \MOD \End{\cat}(T)$.
+\end{prop:KRextricat}
 
@@
 
-\medskip
-
-\noindent \cref{prop::index iso extricat}: \emph{The index induces an isomorphism of abelian groups from~$\kzero{\cat}$ to~$\kzero{\add T}$.}
-
-\medskip
+\newtheorem*{prop:index iso extricat}{\cref{prop:index iso extricat}}
+\begin{prop:index iso extricat}
+The index induces an isomorphism of abelian groups from~$\kzero{\cat}$ to~$\kzero{\add T}$.
+\end{prop:index iso extricat}
 
@@
 
-\medskip
-
-\noindent \cref{theorem::extricats}: \emph{The extriangulated category~$\cat$ has only finitely many ismorphism classes of indecomposable objects if and only if the set~$L_\cat$ generates the kernel of the canonical projection~$\b{g}:\Ksp(\cat)\to\kzero{\cat}$.
-In that case~$L_\cat$ is a basis of the kernel of~$\b{g}$ and any~$x\in\ker(\b{g})$ decomposes as}
+\newtheorem*{thm:extricats}{\cref{thm:extricats}}
+\begin{thm:extricats}
+The extriangulated category~$\cat$ has only finitely many ismorphism classes of indecomposable objects if and only if the set~$L_\cat$ generates the kernel of the canonical projection~$\b{g}:\Ksp(\cat)\to\kzero{\cat}$.
+In that case~$L_\cat$ is a basis of the kernel of~$\b{g}$ and any~$x\in\ker(\b{g})$ decomposes as
 \[
@@
 \]
-
-\bigskip
-
-\noindent {\bf Schematic diagram of logical dependencies:}
+\end{thm:extricats}
+
+\para{Schematic diagram of logical dependencies}
 
@@
 \end{center}
-
-% Schematic diagram:
-% \yann{Vincent, Arnau, je suis certain que vous feriez bien mieux que moi. Puis-je vous demander de le représenter ?}
-% \arnau{As tu une idée en tête de comment le répresenter? Je trouve que ce que t'as écrit est très clair et je ne vois pas comment faire une schema qui le ameillore}
-% 
-% I.1 explains the type cone approach to the problem
-% 
-% This strategy is used in I.2.2 for cluster algebras and in I.2.3 for gentle algebras.
-% 
-% II.3 cluster categories (2-Calabi--Yau triangulated categories) is used in 1.2.2 for proving U.E.R.P. and simpliciality of the type cone.
-% 
-% II.4 generalises II.3, is used in I.2.3 for proving the U.E.R.P. and offers a different proof of simpliciality of the type cone .
 
@@
 
-The following statement is proved in \cref{coro::number of positive meshes}.
+The following statement is proved in \cref{coro:number of positive meshes}.
 
@@
 \begin{proof}
-Points~(i), (iii) and~(iv) were shown in~\cite[Prop.~2.33, Thm.~4.17 \& Prop~4.16]{PaluPilaudPlamondon-nonkissing}. We postpone the proof of point~(ii) until \cref{coro::exchangeablePairsNKC}.
+Points~(i), (iii) and~(iv) were shown in~\cite[Prop.~2.33, Thm.~4.17 \& Prop~4.16]{PaluPilaudPlamondon-nonkissing}. We postpone the proof of point~(ii) until \cref{coro:exchangeablePairsNKC}.
 \end{proof}
@@
 The following statement describes the type cone of the non-kissing fan of a brick and $2$-acyclic gentle quiver.
-We provide here an elementary combinatorial proof, a more general representation theoretic perspective is discussed in \cref{theo::brick-algebra-condition}.
+We provide here an elementary combinatorial proof, a more general representation theoretic perspective is discussed in \cref{thm:brick-algebra-condition}.
 
@@
 Our next statement follows from the end of the previous proof.
-See also \cref{coro::simplicialTypeConeNKCalgebraic}.
+See also \cref{coro:simplicialTypeConeNKCalgebraic}.
 
@@
 In~\cite{Auslander1984}, M.~Auslander showed that the relations in the Grothendieck group of an Artin algebra are generated by the ones given by almost-split sequences precisely when the algebra is of finite representation type.
-Inspired by this result, we will show that a similar statement holds (see \cref{theo::relations-g-vecteurs}) for the~$\b{g}$-vectors (or indices) of objects in a~$2$-Calabi--Yau triangulated category.
+Inspired by this result, we will show that a similar statement holds (see \cref{thm:relations-g-vecteurs}) for the~$\b{g}$-vectors (or indices) of objects in a~$2$-Calabi--Yau triangulated category.
 
@@
 \subsection{Setting}
-\label{sect::setting}
+\label{sec:setting}
 
@@
 \subsection{Statement of the theorem}
-\label{subsect::Statement cluster cats}
+\label{subsec:Statement cluster cats}
 
@@
 
-\begin{proposition}[\cite{BuanMarshReiten, KellerReiten}]\label{prop::functor-F}
+\begin{proposition}[\cite{BuanMarshReiten, KellerReiten}]\label{prop:functor-F}
 
@@
 \begin{definition}
-\label{defi::grothendieck-group}
+\label{def:grothendieck-group}
 \begin{enumerate}
@@
 In particular,~$\Ksp(\cat)$ is isomorphic to a free abelian group over the set~$\ind(\cat)$.
-Considering the modified group~$K_0(\cat ; T)$ instead of the usual Grothendieck group is motivated by \cref{sect::applications-g-vectors}, where we study relations between~$\b{g}$-vectors.
+Considering the modified group~$K_0(\cat ; T)$ instead of the usual Grothendieck group is motivated by \cref{sec:applications-g-vectors}, where we study relations between~$\b{g}$-vectors.
 
 \begin{definition}
-\label{defi::bilinear form}
+\label{def:bilinear form}
 For any two objects~$X$ and~$Y$ of~$\cat$, define
@@
 \begin{notation}
-\label{notation::ell_X}
+\label{notation:ell_X}
 \begin{enumerate}
@@
 \begin{theorem}
-\label{theo::relations-g-vecteurs}
-Let~$\cat$ be a category satisying the hypotheses of \cref{sect::setting}. Then~$\cat$ has only finitely many isomorphism classes of indecomposable objects if and only if the set
+\label{thm:relations-g-vecteurs}
+Let~$\cat$ be a category satisying the hypotheses of \cref{sec:setting}. Then~$\cat$ has only finitely many isomorphism classes of indecomposable objects if and only if the set
 \[
@@
 \begin{corollary}
-\label{corollary::meshes positively generate cluster cats}
+\label{coro:meshes positively generate cluster cats}
 Assume that~$\ind(\cat)$ is finite.
@@
 \begin{proof}
-We know that~$x=\sum_{A \in \ind(\cat) \ssm \add(\susp T)} \frac{\langle x, [A] \rangle}{\langle \ell_A, [A] \rangle} \ell_A$; since~$\langle \ell_A, [A] \rangle$ is positive by \cref{lemm::bilinear-form}, we only need to show that each~$\langle x, [A] \rangle$ is non-negative.
+We know that~$x=\sum_{A \in \ind(\cat) \ssm \add(\susp T)} \frac{\langle x, [A] \rangle}{\langle \ell_A, [A] \rangle} \ell_A$; since~$\langle \ell_A, [A] \rangle$ is positive by \cref{lem:bilinear-form}, we only need to show that each~$\langle x, [A] \rangle$ is non-negative.
 The functor~$F=\cat(T,-)$ induces an exact sequence
@@
 
-\subsection{Proof of \cref{theo::relations-g-vecteurs}}
-
-Before we can prove \cref{theo::relations-g-vecteurs}, we need to recall the following results and definition from~\cite{DehyKeller,Palu}.
+\subsection{Proof of \cref{thm:relations-g-vecteurs}}
+
+Before we can prove \cref{thm:relations-g-vecteurs}, we need to recall the following results and definition from~\cite{DehyKeller,Palu}.
 
@@
 
-The notion of index is very close to the definition of the map~$\b{g}:\Ksp(\cat)\to K_0(\cat ; T)$ of \cref{defi::grothendieck-group}. The link is given by the following result.
+The notion of index is very close to the definition of the map~$\b{g}:\Ksp(\cat)\to K_0(\cat ; T)$ of \cref{def:grothendieck-group}. The link is given by the following result.
 
@@
 \begin{corollary}
-\label{coro::grothendieck-g-vectors}
+\label{coro:grothendieck-g-vectors}
 There is an isomorphism~$\phi:K_0(\cat ; T) \to \Ksp \big( \add(T) \big)$ such that~$\ind_T = \phi\circ \b{g}$. In particular,~$K_0(\cat ; T)$ is a free abelian group generated by the~$[T_i]$.
@@
 
-We can now begin the proof of \cref{theo::relations-g-vecteurs}
+We can now begin the proof of \cref{thm:relations-g-vecteurs}
 
 \begin{lemma}
-\label{lemm::bilinear-form-suspention-T}
+\label{lem:bilinear-form-suspention-T}
 If~$X$ or~$Y$ lie in~$\add(\susp T)$, then~$\langle X, Y \rangle = 0$.
@@
 \begin{lemma}
-\label{lemm::almost-split}
+\label{lem:almost-split}
 Let~$X\xrightarrow{} Y \xrightarrow{} \susp^{-1} X \xrightarrow{h} \susp X$ be an almost-split triangle. Then~$X\notin \add(\susp T)$ if and only if~$h \in (\susp T)$.
@@
 \begin{lemma}
-\label{lemm::bilinear-form}
+\label{lem:bilinear-form}
 Let~$A$ and~$B$ be two indecomposable objects of~$\cat$.
@@
 \]
-be an almost-split triangle. By \cref{lemm::almost-split}, the morphism~$h$ is in~$(\susp T)$. Applying the functor ${F=\cat(T,-)}$, we get an exact sequence
+be an almost-split triangle. By \cref{lem:almost-split}, the morphism~$h$ is in~$(\susp T)$. Applying the functor ${F=\cat(T,-)}$, we get an exact sequence
 \[
@@
 \]
-Applying now the functors~$\cat(-, B)$ and~$\Hom{\Lambda}(-, FB)$, we get a commutative diagram whose rows are exact sequences and whose vertical maps are surjective by \cref{prop::functor-F}.
+Applying now the functors~$\cat(-, B)$ and~$\Hom{\Lambda}(-, FB)$, we get a commutative diagram whose rows are exact sequences and whose vertical maps are surjective by \cref{prop:functor-F}.
 \[
@@
 \begin{lemma}
-\label{lemm::coefficients}
+\label{lem:coefficients}
 Let~$x \in \Ksp(\cat)$, and write~\[x=\sum_{A \in \ind(\cat)} \lambda_A [A].\]  Then for any~$A\in\ind(\cat) \ssm \add(\susp T)$, we have that
@@
 \begin{proof}
-Let~$B \in \ind(\cat) \ssm \add(\susp T)$. Applying \cref{lemm::bilinear-form}, we get that
+Let~$B \in \ind(\cat) \ssm \add(\susp T)$. Applying \cref{lem:bilinear-form}, we get that
 \[
@@
 \begin{corollary}
-\label{lemm::test-susp-T}
+\label{lem:test-susp-T}
 Let~$x \in \Ksp(\cat)$. Then the following are equivalent.
@@
 
-Assume that (2) holds. Then, by \cref{lemm::coefficients}, we have that
+Assume that (2) holds. Then, by \cref{lem:coefficients}, we have that
 \[
@@
 
-Assume now that (1) holds. Then~$\langle x, [A]\rangle = 0$ for any~$A$ by \cref{lemm::bilinear-form-suspention-T}. Thus (2) holds.
+Assume now that (1) holds. Then~$\langle x, [A]\rangle = 0$ for any~$A$ by \cref{lem:bilinear-form-suspention-T}. Thus (2) holds.
 \end{proof}
@@
 \begin{proposition}
-\label{prop::free-set}
+\label{prop:free-set}
 \begin{enumerate}
@@
 \]
-Then~$\langle x, [A] \rangle = 0$ for all~$A\in\ind(\cat) \ssm \add(\susp T)$. But~$\langle x, [A] \rangle = \lambda_A$ by \cref{lemm::bilinear-form}. Thus~
+Then~$\langle x, [A] \rangle = 0$ for all~$A\in\ind(\cat) \ssm \add(\susp T)$. But~$\langle x, [A] \rangle = \lambda_A$ by \cref{lem:bilinear-form}. Thus~
 \[
@@
 \begin{proof}
-By \cref{prop::free-set}, the set is free. Let~$x \in \ker \b{g}$. Consider the element
+By \cref{prop:free-set}, the set is free. Let~$x \in \ker \b{g}$. Consider the element
 \[
@@
 \]
-where the second equality is obtained by using \cref{lemm::bilinear-form}.
-By \cref{lemm::test-susp-T}, this implies that~$z \in \Ksp \big( \add(\susp T) \big)$.
-Since~$z \in \ker(\b{g})$ and since~$\b{g}$ is injective on~$\Ksp \big( \add (\susp T) \big)$ by \cref{coro::grothendieck-g-vectors}, we get that~$z=0$.
+where the second equality is obtained by using \cref{lem:bilinear-form}.
+By \cref{lem:test-susp-T}, this implies that~$z \in \Ksp \big( \add(\susp T) \big)$.
+Since~$z \in \ker(\b{g})$ and since~$\b{g}$ is injective on~$\Ksp \big( \add (\susp T) \big)$ by \cref{coro:grothendieck-g-vectors}, we get that~$z=0$.
 This finishes the proof.
@@
 \begin{proof}
-By \cref{prop::free-set}, the set is free. It suffices to prove that it generates~$\Ksp(\cat)$. Let~${x \in \Ksp(\cat)}$. Consider
+By \cref{prop:free-set}, the set is free. It suffices to prove that it generates~$\Ksp(\cat)$. Let~${x \in \Ksp(\cat)}$. Consider
 \[
@@
 \]
-Then for any~$B \in \ind(\cat)$, we have that~$\langle z, [B] \rangle = 0$. By \cref{lemm::test-susp-T}, this implies that ${z \in \Ksp \big( \add(\susp T) \big)}$, and finishes the proof.
-\end{proof}
-
-All that remains is to prove the converse in the statement of \cref{theo::relations-g-vecteurs}.
+Then for any~$B \in \ind(\cat)$, we have that~$\langle z, [B] \rangle = 0$. By \cref{lem:test-susp-T}, this implies that ${z \in \Ksp \big( \add(\susp T) \big)}$, and finishes the proof.
+\end{proof}
+
+All that remains is to prove the converse in the statement of \cref{thm:relations-g-vecteurs}.
 
@@
 \subsection{Application to~$\b{g}$-vectors of cluster algebras of finite type}
-\label{sect::applications-g-vectors}
-
-In this section, we apply the results of \cref{subsect::Statement cluster cats} in order to prove \cref{prop:uniqueExchangePropertyCA,prop:meshMutations} of \cref{subsec:typeConeCA}.
+\label{sec:applications-g-vectors}
+
+In this section, we apply the results of \cref{subsec:Statement cluster cats} in order to prove \cref{prop:uniqueExchangePropertyCA,prop:meshMutations} of \cref{subsec:typeConeCA}.
 
@@
 \begin{theorem}
-\label{thm::categorification}
+\label{thm:categorification}
 Let~$\cat$ be the cluster category of a valued quiver of Dynkin type~$A,B,C,D,E,F$ or~$G$.
@@
 \begin{definition}
-\label{defn::positive mutation}
+\label{def:positive mutation}
 Let~$x\in\cluster$ be a cluster variable in a given cluster and let~$x' \in \cluster'$ be obtained by mutating~$\cluster$ at~$x$.
@@
 \begin{lemma}
-\label{lemm::exaclty one mesh mutation}
+\label{lem:exaclty one mesh mutation}
 For every non-initial cluster variable, there exists precisely one pair~$(x,x')$ such that there exists a positive mesh mutation changing~$x$ into~$x'$.
@@
 Up to isomorphism, there is precisely one almost-split triangle of~$\cat$ starting in~$X$, where~$X$ is the object such that~$\phi(X) = x$.
-Thus there is precisely one mesh relation By \cref{lemm::almost-split}, the pair~$(x,x')$ is a positive mutation if and only~$X\notin \add(\susp T)$, that is, if and only if~$x$ is not an initial variable.
+Thus there is precisely one mesh relation By \cref{lem:almost-split}, the pair~$(x,x')$ is a positive mutation if and only~$X\notin \add(\susp T)$, that is, if and only if~$x$ is not an initial variable.
 \end{proof}
@@
 \begin{lemma}
-\label{lemm::mesh mutations and meshes}
-The set of positive mesh mutations~$(x,x')$ of \cref{defn::positive mutation} is in bijection with the set~$\meshes$ of \cref{defn::positive mutation}.
+\label{lem:mesh mutations and meshes}
+The set of positive mesh mutations~$(x,x')$ of \cref{def:positive mutation} is in bijection with the set~$\meshes$ of \cref{def:positive mutation}.
 \end{lemma}
@@
 Since the pair~$\{x,x'\}$ is not initial,~$\phi(X')$ is not an initial variable; in other words,~$X'$ is not in~$\add(T)$.
-Therefore,~$X = \tau X' = \susp X'$ is not in~$\add\susp T$, so the mutation is a positive mesh mutation by \cref{lemm::almost-split}.
+Therefore,~$X = \tau X' = \susp X'$ is not in~$\add\susp T$, so the mutation is a positive mesh mutation by \cref{lem:almost-split}.
 This gives an injective map from~$\meshes$ to the set of positive mutations.
@@
 \begin{corollary}[\cref{lem:bijectionMeshMutations}]
-\label{coro::number of positive meshes}
+\label{coro:number of positive meshes}
 We have that~$|\meshes|$ is the number~$|\variables[\B_\circ]|-n$ of non-initial cluster variables.
@@
 \begin{proof}
-This is a direct consequence of \cref{lemm::exaclty one mesh mutation,lemm::mesh mutations and meshes}.
+This is a direct consequence of \cref{lem:exaclty one mesh mutation,lem:mesh mutations and meshes}.
 \end{proof}
@@
 \begin{proof}
-In view of \cref{thm::categorification}\,(iii), it follows from~\cite[Lem.~3.3]{Palu}.
+In view of \cref{thm:categorification}\,(iii), it follows from~\cite[Lem.~3.3]{Palu}.
 \end{proof}
@@
 By \cref{lemma:positive mutation triangles}, we may assume that the mutation under consideration is a positive mutation.
-In view of \cref{thm::categorification}\,(ii) and (iv) it is enough to show that the relation in~$K_0(\cat ; T)$ given by any triangle ${X\to E\to Y\xrightarrow{h} \susp X}$ with~$h\in(\susp T)$ is a positive linear combination of relations coming from Auslander--Reiten triangles with third term not in~$\add(\susp T)$.
-This categorified statement is precisely \cref{corollary::meshes positively generate cluster cats}.
-\end{proof}
-
-It also follows from \cref{thm::categorification} above that any cluster algebra of finite type has the unique exchange relation property (see \cref{def:uerp}).
+In view of \cref{thm:categorification}\,(ii) and (iv) it is enough to show that the relation in~$K_0(\cat ; T)$ given by any triangle ${X\to E\to Y\xrightarrow{h} \susp X}$ with~$h\in(\susp T)$ is a positive linear combination of relations coming from Auslander--Reiten triangles with third term not in~$\add(\susp T)$.
+This categorified statement is precisely \cref{coro:meshes positively generate cluster cats}.
+\end{proof}
+
+It also follows from \cref{thm:categorification} above that any cluster algebra of finite type has the unique exchange relation property (see \cref{def:uerp}).
 
@@
 \begin{proof}
-By the results in additive categorification of cluster algebras recalled in \cref{thm::categorification}, the statement follows from \cref{lemma::uerp categorified} below.
+By the results in additive categorification of cluster algebras recalled in \cref{thm:categorification}, the statement follows from \cref{lem:uerp categorified} below.
 \end{proof}
@@
 \begin{lemma}
-\label{lemma::uerp categorified}
+\label{lem:uerp categorified}
 Let~$\cat$ be a cluster category of Dynkin type~$A,B,C,D,E,F$ or~$G$, and let~$X,Y \in \cat$ be such~$\CC(Y)$ is obtained by performing a positive mutation at~$\CC(X)$ in some cluster containing it.
@@
 Therefore, the triangle ${X\to \bigoplus_i E_i \to Y \xrightarrow{h} \susp X}$ induces the relation~$[X]+[Y]=\sum_i [E_i]$ in~$K_0(\cat ; T)$.
-\cref{thm::categorification}\,(ii) gives the equality ${\b{g}_{\CC(X)} + \b{g}_{\CC(Y)} = \sum_i\b{g}_{\CC(E_i)}}$, where the~$\b{g}$-vectors are computed with respect to the initial seed~$\CC(T)$.
-By \cref{thm::categorification}\,(iii), the middle term of the triangle is uniquely defined, up to isomorphism, by~$X$, and~$Y$, and the triangle is therefore an exchange triangle, with respect to any mutation at~$X$: it does not depend on the choice of a cluster tilting object containing~$X$.
-By \cref{thm::categorification}\,(iv) this equality is one of the two equalities in \cref{lem:linearDependencegvectorsCA}.
+\cref{thm:categorification}\,(ii) gives the equality ${\b{g}_{\CC(X)} + \b{g}_{\CC(Y)} = \sum_i\b{g}_{\CC(E_i)}}$, where the~$\b{g}$-vectors are computed with respect to the initial seed~$\CC(T)$.
+By \cref{thm:categorification}\,(iii), the middle term of the triangle is uniquely defined, up to isomorphism, by~$X$, and~$Y$, and the triangle is therefore an exchange triangle, with respect to any mutation at~$X$: it does not depend on the choice of a cluster tilting object containing~$X$.
+By \cref{thm:categorification}\,(iv) this equality is one of the two equalities in \cref{lem:linearDependencegvectorsCA}.
 \end{proof}
@@
 The main definitions and first properties on extriangulated categories are recalled after the statements of the main results of this section.
-See \cref{sect::recollections extricats} below.
-The reader that does not want to dwell into details can safely skip \cref{sect::recollections extricats} and focus on any of the first three examples given in \cref{remark::examples extricats}: triangulated categories, exact categories (that are small or have enough projectives or injectives) and extension-closed subcategories of triangulated categories, such as the category~$K^{[-1,0]}(\proj \Lambda)$, are examples of extriangulated categories.
+See \cref{sec:recollections extricats} below.
+The reader that does not want to dwell into details can safely skip \cref{sec:recollections extricats} and focus on any of the first three examples given in \cref{rem:examples extricats}: triangulated categories, exact categories (that are small or have enough projectives or injectives) and extension-closed subcategories of triangulated categories, such as the category~$K^{[-1,0]}(\proj \Lambda)$, are examples of extriangulated categories.
 
@@
 \subsection{Setting}
-\label{setting::extricat}
+\label{setting:extricat}
 
@@
 \smallskip
-\para{Setting for Section~\ref{sect::prelim on extricats}}
+\para{Setting for Section~\ref{sec:prelim on extricats}}
 In that section, we let~$\cat$ be an extriangulated category with a fixed full additive subcategory~$\tc$, stable under isomorphisms, under taking direct summands, and satisfying the following three properties:
@@
 \smallskip
-\para{Setting for Section~\ref{sect::Statment extricats}}
+\para{Setting for Section~\ref{sec:Statment extricats}}
 In that section, we keep the previous setting, but assume moreover that~$\cat$ is Krull--Schmidt, $\field$-linear, Ext-finite, and has Auslander--Reiten--Serre duality, and that the subcategory~$\tc$ is of the form~$\add T$, where~$T=T_1\oplus\cdots\oplus T_n$ is a basic object.
@@
 \begin{remark}
-\label{remark::examples extricats}
+\label{rem:examples extricats}
 Examples of categories satisfying the properties above are
 \begin{itemize}
-\item $2$-Calabi--Yau triangulated categories admitting a cluster-tilting object (see \cref{sect::2CYTriangulated});
-\item for any Artin algebra~$\Lambda$, the category~$K^{[-1,0]}(\proj \Lambda)$ of complexes of finitely generated projective~$\Lambda$-modules concentrated in degrees~$-1$ and~$0$, with morphisms considered up to homotopy (see \cref{sect::Kbproj});
-\item more generally, extriangulated categories~$\cat$ constructed as follows: if~$\tc$ is a rigid subcategory of an extriangulated category~$\ec$ (with some assumption ensuring that condition (2) holds) we let~$\cat$ be the full subcategory of~$\ec$ whose objects satisfy condition (3), equipped with the extriangulated structure obtained from that of~$\ec$ by considering those extriangles in~$\ec$ all whose terms belong to~$\cat$ and whose deflation is~$\tc$-epi (see \cref{sect::prT}).
+\item $2$-Calabi--Yau triangulated categories admitting a cluster-tilting object (see \cref{sec:2CYTriangulated});
+\item for any Artin algebra~$\Lambda$, the category~$K^{[-1,0]}(\proj \Lambda)$ of complexes of finitely generated projective~$\Lambda$-modules concentrated in degrees~$-1$ and~$0$, with morphisms considered up to homotopy (see \cref{sec:Kbproj});
+\item more generally, extriangulated categories~$\cat$ constructed as follows: if~$\tc$ is a rigid subcategory of an extriangulated category~$\ec$ (with some assumption ensuring that condition (2) holds) we let~$\cat$ be the full subcategory of~$\ec$ whose objects satisfy condition (3), equipped with the extriangulated structure obtained from that of~$\ec$ by considering those extriangles in~$\ec$ all whose terms belong to~$\cat$ and whose deflation is~$\tc$-epi (see \cref{sec:prT}).
 \end{itemize}
@@
 \subsection{Statement of preliminary results on extriangulated categories}
-\label{sect::prelim on extricats}
+\label{sec:prelim on extricats}
 
 So as to be able to state the main theorem of \cref{sec:extricats}, we need a few results on extriangulated categories.
-However, all proofs are postponed to \cref{sect::proofs extricats}.
-
-We let~$\cat$ be as in \cref{setting::extricat}.
+However, all proofs are postponed to \cref{sec:proofs extricats}.
+
+We let~$\cat$ be as in \cref{setting:extricat}.
 
@@
 \begin{remark}
-As will be proven below (\cref{remark::equivalence Sigma} and \cref{corollary::Sigma T injectives}), this notation extends to an equivalence of categories from the category~$\tc$ of projective objects in~$\cat$ to the category~$\susp\tc$ of injective objects in~$\cat$.
+As will be proven below (\cref{rem:equivalence Sigma} and \cref{coro:Sigma T injectives}), this notation extends to an equivalence of categories from the category~$\tc$ of projective objects in~$\cat$ to the category~$\susp\tc$ of injective objects in~$\cat$.
 \end{remark}
@@
 \begin{lemma}
-\label{lemma::finitely presented}
+\label{lem:finitely presented}
 For any~$X\in\cat$, the functor~$FX$ is finitely presented.
@@
 
-\cref{prop::KRextricat} below extends similar results from~\cite{BuanMarshReiten,KellerReiten,KoenigZhu,IyamaYoshino} (see also \cref{prop::functor-F}) to the setting under consideration.
+\cref{prop:KRextricat} below extends similar results from~\cite{BuanMarshReiten,KellerReiten,KoenigZhu,IyamaYoshino} (see also \cref{prop:functor-F}) to the setting under consideration.
 We note that the proof requires minor modifications.
@@
 \begin{proposition}
-\label{prop::KRextricat}
+\label{prop:KRextricat}
 The functor~$F$ induces an equivalence of categories
@@
 \begin{proposition}
-\label{prop::index iso extricat}
+\label{prop:index iso extricat}
  The assignment~$X\mapsto\ind_\tc X$ is well-defined and induces an isomorphism
@@
 \subsection{Statement of the theorem}
-\label{sect::Statment extricats}
-
-Let~$\cat$ be as in \cref{setting::extricat}.
+\label{sec:Statment extricats}
+
+Let~$\cat$ be as in \cref{setting:extricat}.
 
@@
 Assume moreover that~$\cat$ is $\field$-linear and Ext-finite.
-By the preliminary results of \cref{sect::recollections extricats}, we can apply~\cite[Prop.~4.2]{IyamaNakaokaPalu} to obtain that~$\modt$ is Hom-finite.
+By the preliminary results of \cref{sec:recollections extricats}, we can apply~\cite[Prop.~4.2]{IyamaNakaokaPalu} to obtain that~$\modt$ is Hom-finite.
 In particular, if $\tc=\add T$, then $\End{\cat}(T)$ is a finite-dimensional~$\field$-algebra.
-It thus also follows that \cref{defi::bilinear form} still makes sense in this more general setup: For any~$X,Y\in\cat$,
+It thus also follows that \cref{def:bilinear form} still makes sense in this more general setup: For any~$X,Y\in\cat$,
 \[
@@
 
-When this makes sense, we make use of \cref{notation::ell_X}: if
+When this makes sense, we make use of \cref{notation:ell_X}: if
 \[
@@
 \begin{theorem}
-\label{theorem::extricats}
+\label{thm:extricats}
 Assume that~$\cat$ is a~$\field$-linear, Ext-finite, Krull--Schmidt, extriangulated category with Auslander--Reiten--Serre duality.
@@
 \begin{corollary}
-\label{corollary::meshes positively generate extricats}
+\label{coro:meshes positively generate extricats}
 Assume that~$\ind(\cat)$ is finite.
@@
 \subsection{Recollections on extriangulated categories}
-\label{sect::recollections extricats}
+\label{sec:recollections extricats}
 
@@
 \begin{proposition}[{\cite[Props.~3.3~\&~3.11]{NakaokaPalu}}]
-\label{proposition::extricat long exact sequences}
+\label{prop:extricat long exact sequences}
 Assume that $(\cat,\mathbb{E},\mathfrak{s})$ is an extriangulated category, and let $X\xrightarrow{x}Y\xrightarrow{y}Z\overset{\delta}{\dashrightarrow}$ be an extriangle.
@@
 
-\subsection{Proofs of preliminary results and of \cref{theorem::extricats}}
-\label{sect::proofs extricats}
-
-We let~$\cat$ and~$\tc$ satisfy the assumptions (1), (2) and (3) of \cref{setting::extricat}.
+\subsection{Proofs of preliminary results and of \cref{thm:extricats}}
+\label{sec:proofs extricats}
+
+We let~$\cat$ and~$\tc$ satisfy the assumptions (1), (2) and (3) of \cref{setting:extricat}.
 We will make it explicit when more assumptions are needed.
@@
 \begin{lemma}
-\label{lemma::first consequences}
+\label{lem:first consequences}
 The following holds:
@@
 \item This follows from the fact that~$T$ is projective and~$0\defl\susp T'$ is a deflation.
-\item and (iv) are obtained from the exact sequences of \cref{proposition::extricat long exact sequences} associated with the extriangle~$T\infl 0\defl \susp T\dashrightarrow$.
+\item and (iv) are obtained from the exact sequences of \cref{prop:extricat long exact sequences} associated with the extriangle~$T\infl 0\defl \susp T\dashrightarrow$.
 \addtocounter{enumi}{1}
@@
 \begin{lemma}
-\label{lemma::shifts of extriangles}
+\label{lem:shifts of extriangles}
 Let~$X\in\cat$ and let
@@
 \begin{remark}
-\label{remark::equivalence Sigma}
+\label{rem:equivalence Sigma}
 For any~$T\in\tc$, fix an extriangle~$T\infl 0\defl\susp T\overset{\eps_T}{\dashrightarrow}$.
-As noticed in \cref{lemma::shifts of extriangles}, for any morphism~$T\overset{f}{\to}T'$ in~$\tc$, there is a unique morphism~$\susp f\in\cat(\susp T,\susp T')$ such that~${f_\ast\eps_T=(\susp f)^\ast\eps_{T'}}$ (i.e.
+As noticed in \cref{lem:shifts of extriangles}, for any morphism~$T\overset{f}{\to}T'$ in~$\tc$, there is a unique morphism~$\susp f\in\cat(\susp T,\susp T')$ such that~${f_\ast\eps_T=(\susp f)^\ast\eps_{T'}}$ (i.e.
 such that~$(f,\susp f)$ is a morphism from~$\eps_T$ to~$\eps_{T'}$), as illustrated below:
@@
 \begin{lemma}
-\label{lemma:: mphs in T are inflations}
+\label{lem: mphs in T are inflations}
 Every morphism with domain in~$\tc$ is an inflation.
@@
 Let~$T \overset{t}{\to} X$ be a morphism with~$T \in \tc$.
-Using the notation of \cref{remark::equivalence Sigma}, there is an extriangle~$T\infl 0\defl \susp T \overset{\eps_T}{\dashrightarrow}$.
+Using the notation of \cref{rem:equivalence Sigma}, there is an extriangle~$T\infl 0\defl \susp T \overset{\eps_T}{\dashrightarrow}$.
 Consider the extriangle~$X\overset{g}{\infl} Y \overset{h}{\defl} \susp T \overset{t_\ast\eps_T}{\dashrightarrow}$.
@@
 \begin{remark}
-It follows from the proof of \cref{lemma:: mphs in T are inflations} that conditions (1), (2), (3) in \cref{setting::extricat} are equivalent to conditions (1), (2), (3'), where
+It follows from the proof of \cref{lem: mphs in T are inflations} that conditions (1), (2), (3) in \cref{setting:extricat} are equivalent to conditions (1), (2), (3'), where
 \[
@@
 
-\begin{proof}[Proof of \cref{lemma::finitely presented}]
+\begin{proof}[Proof of \cref{lem:finitely presented}]
 Applying the functor~$F$ to the extriangle~$T_1^X\infl T_0^X\defl X\overset{\delta_X}{\dashrightarrow}$ induces an exact sequence~$FT_1^X \to FT_0^X \to FX \to \mathbb{E}(T,T_1^X)=0$, showing that~$FX$ is finitely presented.
@@
 
-\begin{proof}[Proof of \cref{prop::KRextricat}]
+\begin{proof}[Proof of \cref{prop:KRextricat}]
 Recall that~$F:\cat\to\modt$ denotes the functor sending an object~$X$ to the module~$\cat(-,X)|_\tc$.
-By \cref{lemma::first consequences}\,(v), the ideal~$(\susp\tc)$ of morphisms factoring through an object in~$\susp\tc$ is included in the kernel of~$F$.
+By \cref{lem:first consequences}\,(v), the ideal~$(\susp\tc)$ of morphisms factoring through an object in~$\susp\tc$ is included in the kernel of~$F$.
 Conversely, let~$X\xrightarrow{f}Y$ be such that~$Ff=0$.
-By \cref{lemma::shifts of extriangles}, there is a conflation~$T_0\overset{g}{\infl} X\overset{h}{\defl} \susp T_1$ with~$T_0,T_1\in\tc$.
+By \cref{lem:shifts of extriangles}, there is a conflation~$T_0\overset{g}{\infl} X\overset{h}{\defl} \susp T_1$ with~$T_0,T_1\in\tc$.
 By assumption, the composition~$f\circ g$ vanishes, which implies that~$f$ factors through~$\susp T_1$.
@@
 Because~$\tc$ consists of projective objects in~$\cat$, the image under~$F$ of every conflation is a right exact sequence.
-The fact that~$F$ is full and dense can thus be proven as in the case of triangulated categories, by using \cref{lemma:: mphs in T are inflations}.
+The fact that~$F$ is full and dense can thus be proven as in the case of triangulated categories, by using \cref{lem: mphs in T are inflations}.
 \end{proof}
@@
 \begin{corollary}
-\label{corollary::Sigma T injectives}
+\label{coro:Sigma T injectives}
 The objects in~$\susp\tc$ are precisely the injective objects in~$\cat$.
@@
 \begin{proof}
-First note that any injective object belongs to~$\susp \tc$, by \cref{lemma::shifts of extriangles}.
+First note that any injective object belongs to~$\susp \tc$, by \cref{lem:shifts of extriangles}.
 Let us prove that the converse holds.
@@
 Since~$\cat(-,\susp T)|_\tc = 0$ and~$f$ is~$\tc$-epic, the morphism~$\cat(-,f)|_\tc$ is an isomorphism in~$\modt$.
-By \cref{prop::KRextricat}, there are morphisms~$Y\overset{s}{\to} X$,~$Y\xrightarrow{h}\susp T'$,~$\susp T'\xrightarrow{t} Y$, for some~$T'\in\tc$ satisfying
+By \cref{prop:KRextricat}, there are morphisms~$Y\overset{s}{\to} X$,~$Y\xrightarrow{h}\susp T'$,~$\susp T'\xrightarrow{t} Y$, for some~$T'\in\tc$ satisfying
 \[
@@
 \]
-By \cref{lemma::first consequences}\,(v), $\susp\tc$ is a rigid subcategory, so that~$t^\ast\delta=0$.
+By \cref{lem:first consequences}\,(v), $\susp\tc$ is a rigid subcategory, so that~$t^\ast\delta=0$.
 Equivalently, there is a morphism~$\susp T'\xrightarrow{k} X$ such that~$t=fk$.
@@
 \begin{lemma}
-\label{lemma::index well-defined extricat}
+\label{lem:index well-defined extricat}
  The index is well-defined.
@@
 \begin{remark}
-We note that \cref{lemma::index well-defined extricat} only requires the subcategory~$\tc$ to be rigid, and not made of projective objects.
-However, this stronger assumption is used in the proof of \cref{lemma::index kzero extricat} below.
+We note that \cref{lem:index well-defined extricat} only requires the subcategory~$\tc$ to be rigid, and not made of projective objects.
+However, this stronger assumption is used in the proof of \cref{lem:index kzero extricat} below.
 \end{remark}
@@
 \begin{lemma}
-\label{lemma::index kzero extricat}
+\label{lem:index kzero extricat}
 The index descends to~$\kzero{\cat}$: For any conflation~$X\infl Y\defl Z$ in~$\cat$, we have~$\ind_\tc Y = \ind_\tc X + \ind_\tc Z$ in~$\kzero{\tc}$.
@@
 
-\begin{proof}[Proof of \cref{prop::index iso extricat}]
-By \cref{lemma::index well-defined extricat} and \cref{lemma::index kzero extricat}, the index induces an well-defined morphism of abelian groups~$\ind_\tc:\kzero{\cat}\to\kzero{\tc}$.
+\begin{proof}[Proof of \cref{prop:index iso extricat}]
+By \cref{lem:index well-defined extricat} and \cref{lem:index kzero extricat}, the index induces an well-defined morphism of abelian groups~$\ind_\tc:\kzero{\cat}\to\kzero{\tc}$.
 It remains to prove that it is an isomorphism.
@@
 
-\begin{proof}[Proof of \cref{theorem::extricats}]
-The proof is now similar to the proof of \cref{theo::relations-g-vecteurs}, by using \cref{prop::KRextricat} instead of \cref{prop::functor-F}, \cref{prop::index iso extricat} instead of \cref{coro::grothendieck-g-vectors}, and the fact that~$\tc$ is made of projective objects instead of \cref{lemm::almost-split}.
-\end{proof}
-
-\begin{proof}[Proof of \cref{corollary::meshes positively generate extricats}]
-The proof is similar to that of \cref{corollary::meshes positively generate cluster cats}.
+\begin{proof}[Proof of \cref{thm:extricats}]
+The proof is now similar to the proof of \cref{thm:relations-g-vecteurs}, by using \cref{prop:KRextricat} instead of \cref{prop:functor-F}, \cref{prop:index iso extricat} instead of \cref{coro:grothendieck-g-vectors}, and the fact that~$\tc$ is made of projective objects instead of \cref{lem:almost-split}.
+\end{proof}
+
+\begin{proof}[Proof of \cref{coro:meshes positively generate extricats}]
+The proof is similar to that of \cref{coro:meshes positively generate cluster cats}.
 \end{proof}
@@
 \subsection{Application to 2-term complexes of projectives and to gentle algebras}
-\label{sect::Kbproj}
+\label{sec:Kbproj}
 
@@
 \begin{proposition}
-\label{prop::2kbproj-is-extriangulated}
+\label{prop:2kbproj-is-extriangulated}
 Let~$\Lambda$ be any Artin algebra.
-Then the category~$K^{[-1,0]}(\proj \Lambda)$ is an extriangulated category satisfying the assumptions (1) to (3) of \cref{setting::extricat}, wiht~$\tc = \add(\Lambda)$.
-If, moreover,~$\Lambda$ is finite-dimensional over a field~$\field$, then~$K^{[-1,0]}(\proj \Lambda)$ satisfies all assumptions of \cref{setting::extricat}.
+Then the category~$K^{[-1,0]}(\proj \Lambda)$ is an extriangulated category satisfying the assumptions (1) to (3) of \cref{setting:extricat}, wiht~$\tc = \add(\Lambda)$.
+If, moreover,~$\Lambda$ is finite-dimensional over a field~$\field$, then~$K^{[-1,0]}(\proj \Lambda)$ satisfies all assumptions of \cref{setting:extricat}.
 \end{proposition}
@@
 Moreover, if~$X= P_1\xrightarrow{f}P_0$ is an object of~$K^{[-1,0]}(\proj\Lambda)$, then it lies in a conflation~$P_1\stackrel{f}{\infl} P_0 \defl X$ by definition.
-We have proved that properties~(1) to (3) of \cref{setting::extricat} are satisfied.
+We have proved that properties~(1) to (3) of \cref{setting:extricat} are satisfied.
 
@@
 \begin{definition}
-\label{defn::mutation conflation}
+\label{def:mutation conflation}
 A conflation $X\infl E\defl Y$ of~$K^{[-1,0]}(\proj \Lambda)$ is called a \defn{mutation conflation} if there are basic, two-term, silting objects $X\oplus R$, $Y\oplus R$, with~$X$ and~$Y$ indecomposable, such that the inflation $X\infl E$ is a left ($\add R$)-approximation (i.e.
@@
 \begin{remark}
-In \cref{defn::mutation conflation}, the requirement that~$X$ and~$Y$ are indecomposable implies the map~$E\defl Y$ is a right~($\add R$)-approximation, and that both approximations are minimal.
+In \cref{def:mutation conflation}, the requirement that~$X$ and~$Y$ are indecomposable implies the map~$E\defl Y$ is a right~($\add R$)-approximation, and that both approximations are minimal.
 \end{remark}
@@
 \begin{proposition}
-\label{prop::exchange conflations are unique}
+\label{prop:exchange conflations are unique}
 Let~$\Lambda$ be a finite-dimensional~$\field$-algebra, where~$\field$ is a field. Let~$X$ and~$Y$ be objects of~$K^{[-1,0]}(\proj \Lambda)$. 
 \begin{enumerate}
-\item If there is a mutation conflation (see \cref{defn::mutation conflation}) of the form~$X\infl E\defl Y$, then there can be no mutation conflation of the form~$Y\infl E'\defl X$.
+\item If there is a mutation conflation (see \cref{def:mutation conflation}) of the form~$X\infl E\defl Y$, then there can be no mutation conflation of the form~$Y\infl E'\defl X$.
 \item Assume that~$X\infl E\defl Y$ and~$X\infl E'\defl Y$ are two mutation conflations. 
@@
 By~\cite[Thm.~6.5]{DemonetIyamaJasso} (based on~\cite[Thm~2.3]{DehyKeller}), rigid objects in~$K^{[-1,0]}(\proj \Lambda)$ are determined by their~$\b{g}$-vector.
-The datum of the~$\b{g}$-vector of an object of~$K^{[-1,0]}(\proj \Lambda)$ is equivalent to that of its class in the Grothendieck group~$K_0 \big( K^{[-1,0]}(\proj \Lambda) \big)$, where~$K^{[-1,0]}(\proj \Lambda)$ is viewed as an extriangulated category (see \cref{prop::2kbproj-is-extriangulated}).
+The datum of the~$\b{g}$-vector of an object of~$K^{[-1,0]}(\proj \Lambda)$ is equivalent to that of its class in the Grothendieck group~$K_0 \big( K^{[-1,0]}(\proj \Lambda) \big)$, where~$K^{[-1,0]}(\proj \Lambda)$ is viewed as an extriangulated category (see \cref{prop:2kbproj-is-extriangulated}).
 In this Grothendieck group, we have that~$[E] = [E'] = [X]+[Y]$.
@@
 \begin{corollary}
-\label{coro::exchangeablePairsNKC}
+\label{coro:exchangeablePairsNKC}
 Point~(ii) of \cref{prop:exchangeablePairsNKC} holds.
@@
 \]
-By \cref{prop::exchange conflations are unique}, we get that~$P(\mu)\oplus P(\nu)$ and~$P(\mu')\oplus P(\nu')$ are isomorphic, and that the mutation conflations either both have the form~$P(\omega) \infl P(\mu) \oplus P(\nu) \defl P(\omega')$ or both have the form~$P(\omega') \infl P(\mu) \oplus P(\nu) \defl P(\omega)$.
+By \cref{prop:exchange conflations are unique}, we get that~$P(\mu)\oplus P(\nu)$ and~$P(\mu')\oplus P(\nu')$ are isomorphic, and that the mutation conflations either both have the form~$P(\omega) \infl P(\mu) \oplus P(\nu) \defl P(\omega')$ or both have the form~$P(\omega') \infl P(\mu) \oplus P(\nu) \defl P(\omega)$.
 Without loss of generality, assume that they have the first form.
@@
 \begin{theorem}
-\label{theo::brick-algebra-condition}
+\label{thm:brick-algebra-condition}
 Let~$\Lambda$ be an Artin algebra all of whose indecomposable objects are ~$\tau$-rigid bricks.
@@
 Assume that~$\Lambda$ is a finite-dimensional brick algebra which is representation-finite.
-Then~\cite[Thm.~6.2]{DemonetIyamaJasso} implies that the assumptions of \cref{theo::brick-algebra-condition} are satisfied.
+Then~\cite[Thm.~6.2]{DemonetIyamaJasso} implies that the assumptions of \cref{thm:brick-algebra-condition} are satisfied.
 \end{remark}
@@
 \begin{corollary}
-\label{coro::silting simplicial}
+\label{coro:silting simplicial}
 Let~$\Lambda$ be a finite dimensional brick algebra of finite representation type.
@@
 
-As a consequence of \cref{coro::silting simplicial}, the method of \cref{part:geometry} apply and give an explicit description of all realizations of the support~$\tau$-tilting fan of~$\Lambda$.
+As a consequence of \cref{coro:silting simplicial}, the method of \cref{part:geometry} apply and give an explicit description of all realizations of the support~$\tau$-tilting fan of~$\Lambda$.
 Another consequence is an algebraic proof of \cref{coro:simplicialTypeConeNKC}, that we restate below.
@@
 \begin{corollary}[\cref{coro:simplicialTypeConeNKC}]
-\label{coro::simplicialTypeConeNKCalgebraic}
+\label{coro:simplicialTypeConeNKCalgebraic}
 For any brick and $2$-acyclic gentle algebra, the type cone of its support~$\tau$-tilting fan is simplicial.
@@
 
-The remaining part of this section is devoted to proving \cref{theo::brick-algebra-condition,coro::simplicialTypeConeNKCalgebraic}.
+The remaining part of this section is devoted to proving \cref{thm:brick-algebra-condition,coro:simplicialTypeConeNKCalgebraic}.
 
 \begin{lemma}
-\label{lemm::AR-conflations-and-sequences}
+\label{lem:AR-conflations-and-sequences}
 Let~$\Lambda$ be any Artin algebra.
@@
 \begin{lemma}
-\label{lemm::then-AR-seq-are-mutation}
+\label{lem:then-AR-seq-are-mutation}
 Let~$\Lambda$ be an Artin algebra, let~$\tau X\infl E\defl X$ be an Auslander--Reiten conflation in~$K^{[-1,0]}(\proj\Lambda)$ and denote~$FX=M$.
@@
 
-Note also that \cref{lemm::AR-conflations-and-sequences} implies that~$F\tau X$ is isomorphic to $\tau M$.
+Note also that \cref{lem:AR-conflations-and-sequences} implies that~$F\tau X$ is isomorphic to $\tau M$.
 
@@
 \begin{lemma}
-\label{lemm::if AR are mutations}
+\label{lem:if AR are mutations}
 Let~$\Lambda$ be an Artin algebra, and let~$Y\infl E\defl X$ be a conflation in~$K^{[-1,0]}(\proj\Lambda)$. Then:
@@
 \begin{proof}
-By \cref{lemm::AR-conflations-and-sequences}, \emph{(2)} follows from \emph{(1)}.
+By \cref{lem:AR-conflations-and-sequences}, \emph{(2)} follows from \emph{(1)}.
 Let us prove \emph{(1)}.
@@
 \begin{lemma}
-\label{lemm::initial meshes}
+\label{lem:initial meshes}
 Let~$\Lambda$ be an Artin algebra whose indecomposable injective modules are~$\tau$-rigid, and let~$P$ be an indecomposable projective~$\Lambda$-module.
@@
 where the vertical maps are surjective.
-Since~$\Lambda$ is rigid and~$Y$ is two-term, we can apply~\cite[Prop.~6.2]{IyamaYoshino} to the triangulated category~$K^b(\proj\Lambda)$ (or \cref{prop::KRextricat} to the extriangulated $K^{[-1,0]}(\proj\Lambda)$).
+Since~$\Lambda$ is rigid and~$Y$ is two-term, we can apply~\cite[Prop.~6.2]{IyamaYoshino} to the triangulated category~$K^b(\proj\Lambda)$ (or \cref{prop:KRextricat} to the extriangulated $K^{[-1,0]}(\proj\Lambda)$).
 As a consequence, the right-most vertical map is bijective.
@@
 
-\begin{proof}[Proof of \cref{theo::brick-algebra-condition}]
-The theorem follows from the slightly more general statements of \cref{lemm::then-AR-seq-are-mutation,lemm::if AR are mutations,lemm::initial meshes}.
+\begin{proof}[Proof of \cref{thm:brick-algebra-condition}]
+The theorem follows from the slightly more general statements of \cref{lem:then-AR-seq-are-mutation,lem:if AR are mutations,lem:initial meshes}.
 \end{proof}
@@
 \begin{lemma}
-\label{lemma::characterization Gentle 2-acyclic}
+\label{lem:characterization Gentle 2-acyclic}
 Let~$\Lambda$ be a brick and $2$-acyclic gentle algebra.
@@
 
-\begin{proof}[Proof of \cref{coro::simplicialTypeConeNKCalgebraic}]
-The unique exchange relation property follows from \cref{prop::exchange conflations are unique} (2).
-By \cref{lemma::characterization Gentle 2-acyclic}, the assumptions of \cref{theo::brick-algebra-condition} are satisfied.
-We can thus apply \cref{theorem::extricats} and its corollary, which shows that there is the same number of extremal exchange pairs of the support~$\tau$-tilting fan (i.e.
+\begin{proof}[Proof of \cref{coro:simplicialTypeConeNKCalgebraic}]
+The unique exchange relation property follows from \cref{prop:exchange conflations are unique} (2).
+By \cref{lem:characterization Gentle 2-acyclic}, the assumptions of \cref{thm:brick-algebra-condition} are satisfied.
+We can thus apply \cref{thm:extricats} and its corollary, which shows that there is the same number of extremal exchange pairs of the support~$\tau$-tilting fan (i.e.
 the non-kissing fan) as there are meshes in the Auslander--Reiten quiver of~$\Lambda$.
@@
 
-In this section, we give two more examples of families of categories to which \cref{theorem::extricats,corollary::meshes positively generate extricats} apply.
+In this section, we give two more examples of families of categories to which \cref{thm:extricats,coro:meshes positively generate extricats} apply.
 
@@
 \subsubsection{$2$-Calabi--Yau triangulated categories}
-\label{sect::2CYTriangulated}
+\label{sec:2CYTriangulated}
 
@@
 We assume moreover that~$\cat$ is~$\field$-linear, Krull--Schmidt, Hom-finite, 2-Calabi--Yau, with a cluster-tilting object~$T$.
-Then~$\cat$ satisfies all the assumptions of \cref{setting::extricat} for \cref{sect::Statment extricats} but, possibly, assumption (1).
+Then~$\cat$ satisfies all the assumptions of \cref{setting:extricat} for \cref{sec:Statment extricats} but, possibly, assumption (1).
 
@@
 \begin{remark}
-The main results of \cref{subsect::Statement cluster cats} can thus be viewed as specific cases of the results of \cref{sec:extricats}: \cref{theo::relations-g-vecteurs} and \cref{corollary::meshes positively generate cluster cats} are consequences of \cref{theorem::extricats} and \cref{corollary::meshes positively generate extricats}.
+The main results of \cref{subsec:Statement cluster cats} can thus be viewed as specific cases of the results of \cref{sec:extricats}: \cref{thm:relations-g-vecteurs} and \cref{coro:meshes positively generate cluster cats} are consequences of \cref{thm:extricats} and \cref{coro:meshes positively generate extricats}.
 \end{remark}
@@
 \subsubsection{Objects presented by a subcategory}
-\label{sect::prT}
-
-We now describe a setup satisfying the assumptions of \cref{setting::extricat} that, at the same time, subsumes all examples given so far, while being easily checked in practice.
+\label{sec:prT}
+
+We now describe a setup satisfying the assumptions of \cref{setting:extricat} that, at the same time, subsumes all examples given so far, while being easily checked in practice.
 
@@
 \begin{lemma}
-\label{lemma:: prT is extriangulated}
+\label{lem: prT is extriangulated}
 The full subcategory~$\cat$ is extension-closed in~$(\ec,\mathbb{E}_\tc,\mathfrak{s}_\tc)$, and thus inherits an extriangulated structure.
@@
 \begin{proof}
-This follows from the proof of \cref{lemma::index kzero extricat}.
+This follows from the proof of \cref{lem:index kzero extricat}.
 \end{proof}
@@
 \begin{proposition}
-\label{prop::prT}
+\label{prop:prT}
 Assume that, for any~$T\in\tc$, there is an~$\mathfrak{s}$-conflation~$T\infl 0\defl X_T$ in~$\ec$ with~$X_T\in\tc^\perp$.
-Then the extriangulated category~$\cat$ satisfies the assumptions (1) to (3) of \cref{setting::extricat}.
+Then the extriangulated category~$\cat$ satisfies the assumptions (1) to (3) of \cref{setting:extricat}.
 \end{proposition}
@@
 For any~$T\in\tc$ the existence of an extriangle~$0\infl T\defl T\overset{0}{\dashrightarrow}$ shows that~$\tc$ is a full subcategory of~$\cat$.
-By \cref{lemma:: prT is extriangulated}, the category~$\cat$ is extriangulated and, by definition of this extriangulated structure, the objects in~$\tc$ are projective in~$\cat$.
+By \cref{lem: prT is extriangulated}, the category~$\cat$ is extriangulated and, by definition of this extriangulated structure, the objects in~$\tc$ are projective in~$\cat$.
 Assumption (3) is satisfied by the definition of~$\cat$, and assumption (2) is equivalent to that of the proposition.
@@
 \begin{remark}
- The categories considered in \cref{sect::2CYTriangulated,sect::Kbproj} all fall into the setting of \cref{prop::prT}.
+ The categories considered in \cref{sec:2CYTriangulated,sec:Kbproj} all fall into the setting of \cref{prop:prT}.
 \end{remark}
@@
 \]
-The conditions of \cref{theo::brick-algebra-condition} are satisfied.
+The conditions of \cref{thm:brick-algebra-condition} are satisfied.
 \end{example}
 
-\begin{example}[Preprojective algebra of type~$A_3$]\label{exam::preprojective silting objects}
+\begin{example}[Preprojective algebra of type~$A_3$]\label{exm:preprojective silting objects}
 Let~$\Lambda$ be the preprojective algebra of type~$A_3$: it is the path algebra of the quiver
@@
 \medskip
-One can check directly that the conditions of \cref{theo::brick-algebra-condition} is not satisfied.
+One can check directly that the conditions of \cref{thm:brick-algebra-condition} is not satisfied.
 For example, the module~$\bsm2\\1\esm$ is~$\tau$-rigid since~$\tau(\bsm2\\1\esm) = \bsm3\\1\esm$, while~$\Hom{\Lambda}\left(\bsm2\\1\esm,\tau^2(\bsm2\\1\esm)\right) = \Hom{\Lambda}(\bsm2\\1\esm,\bsm1\\2\esm) \ne 0$.
@@
 % \begin{example}
-%  Consider the preprojective algebra of type~$A_3$, as in \cref{exam::preprojective silting objects}.
+%  Consider the preprojective algebra of type~$A_3$, as in \cref{exm:preprojective silting objects}.
 It is a self-injective algebra, so its module category is a Frobenius category.

### 2019-07-12 thirdPaper/draft/typeConeAssociahedra.tex
workout presentation

@@
 The goal of this section is to clarify their logical dependencies.
-% Their logical dependencies are recalled in a schematic diagram at the end of this section.
 
@@
 
+\noindent
 Let~$\Fan$ be an essential complete polyhedral fan in~$\R^n$ (all definitions are recalled in~\cref{ssec:polytopes and fans}).
@@
 We provide the following polytopal realizations of~$\Fan(\B_\circ)$:
-% We consider the set~$\meshes$ of all pairs~$\{x,x'\}$ related by non-initial mesh mutations (\cref{def:meshMutation}), and we denote by~$\principalVariables$ the set of cluster variables.
-% Let~$\{x,x'\}\in\meshes$, and let~$X,X'$ be two clusters such that~$X\setminus\{x\}=X'\setminus\{x'\}$.
-% For any~$y\in\principalVariables$, define~$\alpha_{x,x',y}$ to be~$|b_{xy}|$ if~$y\in X\cap X'$ and 0 otherwise.
-% By the unique exchange relation property, the~$\alpha_{x,x',y}$'s do not depend on the specific choice of the clusters~$X,X'$.
 
@@
 Here, $\meshes$ represents the set of all pairs~$\{x,x'\}$ related by non-initial mesh mutations (\cref{def:meshMutation}), and~$\principalVariables$ the set of cluster variables.
-For $\{x,x'\} \in \meshes$ and $y \in \principalVariables$, the coefficient $\alpha_{x,x',y}$ is defined as follows: $\alpha_{x,x',y}$ is set to be~$|b_{xy}|$ if~$y\in X\cap X'$ and $0$ otherwise, where~$X,X'$ are any two clusters such that~$X\setminus\{x\}=X'\setminus\{x'\}$.
+For $\{x,x'\} \in \meshes$ and $y \in \principalVariables$, the coefficient $\alpha_{x,x',y}$ is defined as follows: $\alpha_{x,x',y}$ is set to be~$|b_{xy}|$ if~$y\in X\cap X'$ and $0$ otherwise, where~$X,X'$ are any two clusters such that~$X \ssm \{x\} = X' \ssm \{x'\}$.
 By the unique exchange relation property, the~$\alpha_{x,x',y}$'s do not depend on the specific choice of the clusters~$X,X'$.
@@
 
-\newtheorem*{corollary: uerp gentle}{\cref{corollary: uerp gentle}}
-\begin{corollary: uerp gentle}
+\newtheorem*{prop:exchangeablePairsNKC}{\cref{prop:exchangeablePairsNKC}\,(iv)}
+\begin{prop:exchangeablePairsNKC}
 The non-kissing fan~$\Fan(\quiver)$ has the unique exchange relation property.
-\end{corollary: uerp gentle}
+\end{prop:exchangeablePairsNKC}
 
@@
 
-Combining these pieces, we make use of our type cone approach to deduce the following statement.
+Combining these pieces, we make use of our type cone approach to deduce the following.
 
@@
 
-Even though graph associahedra do not have simplicial type cones except for the path (\cref{prop:simplicialnestedfan}), we provide a non-redundant characterization of the type cones of all graphical nested fans:
-
-\newtheorem*{cor:typeconenestedfan}{\cref{cor:typeconenestedfan}}
-\begin{cor:typeconenestedfan}
+\noindent
+Even though graph associahedra do not have simplicial type cones except for the path (\cref{prop:simplicialnestedfan}), we provide the following non-redundant characterization of the type cones of all graphical nested fans.
+
+\newtheorem*{coro:typeconenestedfan}{\cref{coro:typeconenestedfan}}
+\begin{coro:typeconenestedfan}
 Consider a graph~$\graphG$ on~$\ground$ with tubes~$\tubes$. 
@@
  $\b{h}_{\tube[s] \ssm \{v'\}} + \b{h}_{\tube[s] \ssm \{v\}} > \b{h}_{\tube[s]} + \b{h}_{\tube[s] \ssm \{v, v'\}}$ for any tube~$\tube[s] \in \tubes$ and distinct non-disconnecting vertices~$v,v'$ of~$\tube[s]$.
-\end{cor:typeconenestedfan}
+\end{coro:typeconenestedfan}
 
@@
 
-In \cref{sec:clusterCategories}, we prove an analogue for cluster categories of a result of M. Auslander for module categories of Artin algebras~\cite{Auslander1984}. 
+\noindent
+We prove an analogue for cluster categories of a result of M. Auslander for module categories of Artin algebras~\cite{Auslander1984}. 
 We are mainly motivated by the fact that it has for a consequence that the type cones of the cluster fans of finite type are simplicial.
@@
 \begin{thm:relations-g-vecteurs}
-The set~$L_\cat \eqdef \set{\ell_X}{X \in \ind(\cat) \setminus \add(\susp T)}$ is a basis of the kernel of~$\b{g}$ and, for any~$x \in \ker(\b{g})$, we have:
+The set~$L_\cat \eqdef \set{\ell_X}{X \in \ind(\cat) \ssm \add(\susp T)}$ is a basis of the kernel of~$\b{g}$ and, for any~$x \in \ker(\b{g})$, we have
 \[
@@
 
-In \cref{sec:extricats} we prove a more general version of \cref{thm:relations-g-vecteurs} that not only applies to cluster fans, but also to non-kissing fans.
+\noindent
+We prove a more general version of \cref{thm:relations-g-vecteurs} that not only applies to cluster fans, but also to non-kissing fans.
 Once more, our main motivation is to prove that the type cone of the non-kissing fan of a brick and 2-acyclic gentle algebra is simplicial, but the results are of independent interest, and might be useful for studying the type cones of other families of simplicial fans.
@@
 \begin{thm:extricats}
-The extriangulated category~$\cat$ has only finitely many ismorphism classes of indecomposable objects if and only if the set~$L_\cat$ generates the kernel of the canonical projection~$\b{g}:\Ksp(\cat)\to\kzero{\cat}$.
-In that case~$L_\cat$ is a basis of the kernel of~$\b{g}$ and any~$x\in\ker(\b{g})$ decomposes as
+The extriangulated category~$\cat$ has only finitely many ismorphism classes of indecomposable objects if and only if the set~$L_\cat$ generates the kernel of the canonical projection ${\b{g}:\Ksp(\cat)\to\kzero{\cat}}$.
+In that case~$L_\cat$ is a basis of the kernel of~$\b{g}$ and any~$x\in\ker(\b{g})$ decomposes~as
 \[
@@
 \]
-% In other words, the non-kissing fan of~$\quiver$ has the unique exchange relation property.
+\item The non-kissing fan of~$\quiver$ has the unique exchange relation property.
 \item The $\b{c}$-vector orthogonal to all $\b{g}$-vectors~$\gvector{\lambda}$ for~$\lambda \in F \cap F'$ is the multiplicity vector~$\multiplicityVector_{\sigma}$ of the vertices of the substring~$\sigma$ of~$\omega$ and~$\omega'$.
 \end{enumerate}
-%
-
-\begin{proof}
-Points~(i), (iii) and~(iv) were shown in~\cite[Prop.~2.33, Thm.~4.17 \& Prop~4.16]{PaluPilaudPlamondon-nonkissing}. We postpone the proof of point~(ii) until \cref{coro:exchangeablePairsNKC}.
-\end{proof}
-
-As a consequence of points $(ii)$ and $(iii)$ in \cref{prop:exchangeablePairsNKC}, we obtain the:
-\begin{corollary}
-\label{corollary: uerp gentle}
-For any non-kissing finite gentle bound quiver~$\quiver$, the non-kissing fan~$\Fan(\quiver)$ has the unique exchange relation property.
-\end{corollary}
-
-\begin{figure}[h]
+
+\begin{figure}[b]
 	\capstart
@@
 
+\begin{proof}
+Points~(i), (iii) and~(v) were shown in~\cite[Prop.~2.33, Thm.~4.17 \& Prop~4.16]{PaluPilaudPlamondon-nonkissing}.
+We postpone the proof of point~(ii) until \cref{coro:exchangeablePairsNKC}.
+Finally, point~(iv) follows directly from points~(ii) and~(iii).
+\end{proof}
+
 \begin{remark}
 \label{rem:exchangeablePairsNKC}
-\enlargethispage{.3cm}
+\enlargethispage{.7cm}
 In view of \cref{prop:exchangeablePairsNKC}, it is tempting to look for a characterization of the exchangeable pairs~$\omega, \omega'$ using the kisses between~$\omega$ and~$\omega'$.
@@
 \]
-In other words, the nested fan of~$\graphG$ has the unique exchange relation property.
+\item The nested fan of~$\graphG$ has the unique exchange relation property.
 \item The $\b{c}$-vector orthogonal to all $\b{g}$-vectors~$\gvector{\tube[s]}$ for~$\tube[s] \in \tubing \cap \tubing'$ is~$\b{e}_v - \b{e}_{v'}$.
@@
 \]
-Finally for~(iv), any tube~$\tube[s] \in \tubing \cap \tubing'$ that contains~$v$ or~$v'$ actually contains both (to be compatible with~$\tube$ and~$\tube'$).
+Point~(iv) is obtained by combining~(ii) and~(iii).
+Finally for~(v), any tube~$\tube[s] \in \tubing \cap \tubing'$ that contains~$v$ or~$v'$ actually contains both (to be compatible with~$\tube$ and~$\tube'$).
 Therefore, $\gvector{\tube[s]}$ is orthogonal to~$\b{e}_v - \b{e}_{v'}$ for any tube~$\tube[s] \in \tubing \cap \tubing'$.
@@
 
+\enlargethispage{-.1cm}
 We derive from \cref{prop:extremalExchangeablePairsGA} and \cref{coro:extremalExchangeablePairsGA} all polytopal realizations of the nested fan.
 
-\begin{corollary}\label{cor:typeconenestedfan}
+\begin{corollary}
+\label{coro:typeconenestedfan}
 Consider a graph~$\graphG$ on~$\ground$ with tubes~$\tubes$. 

### 2019-07-12 thirdPaper/draft/typeConeAssociahedra.tex
workout presentation

@@
 McMullen~\cite{McMullen-typeCone}, is a polyhedral cone that parametrizes the set of all possible polytopal realizations of~$\Fan$.
-These realizations can be described explicitly as affine sections of the nonnegative orthant~$\R^N_{\geq0}$, where~$N$ is the number of rays of~$\Fan$ (\cref{prop:alternativePolytopalRealization}).
+These realizations can be described explicitly as affine sections of the non-negative orthant~$\R^N_{\geq0}$, where~$N$ is the number of rays of~$\Fan$ (\cref{prop:alternativePolytopalRealization}).
 If $\Fan$ is a simplicial fan and has the unique exchange relation property (\cref{def:uerp}), then its type cone is easier to describe and study.
 And if moreover the type cone~$\typeCone(\Fan)$ is simplicial (\cref{rem:dimTypeCone}), then all possible polytopal realizations of~$\Fan$ can be described explicitely in terms of~$N-n$ positive real parameters (\cref{coro:simplicialTypeCone}).
-This gives a new point of view on~\cite{ArkaniHamedBaiHeYan,BazierMatteDouvilleMousavandThomasYildirim}, illustrated in \cref{subsec:typeConeAsso} for classical associahedra, that we then apply to two families of~$\b{g}$-vector fans generalizing the~$\b{g}$-vector fans of classical associahedra: The~$\b{g}$-vector fans of cluster algebras of finite type (generalized associahedra) in~\cref{subsec:typeConeCA}, and the~$\b{g}$-vector fans of gentle algebras (non-kissing associahedra, non-crossing associahedra, generalized accordiohedra) in~\cref{subsec:typeConeNKC}.
+This gives a new point of view on~\cite{ArkaniHamedBaiHeYan,BazierMatteDouvilleMousavandThomasYildirim}, illustrated in \cref{subsec:typeConeAsso} for classical associahedra, that we then apply to two families of~$\b{g}$-vector fans generalizing the~$\b{g}$-vector fans of classical associahedra: the~$\b{g}$-vector fans of cluster algebras of finite type (generalized associahedra) in~\cref{subsec:typeConeCA}, and the~$\b{g}$-vector fans of gentle algebras (non-kissing associahedra, non-crossing associahedra, generalized accordiohedra) in~\cref{subsec:typeConeNKC}.
 We also completely describe the facets of the type cone for graph associahedra in~\cref{subsec:typeConeGA}, to which our strategy does not apply, as only the classical associahedron has a simplicial type cone.
@@
 \noindent
-We first consider the~$\b{g}$-vector fan~$\Fan(\B_\circ)$ of a skew-symmetrizable cluster algebra of finite type, with respect to any initial exchange matrix of finite type~$\B_\circ$.
-We provide the following polytopal realizations of~$\Fan(\B_\circ)$:
+We first consider the~$\b{g}$-vector fan~$\Fan(\B_\circ)$ of a skew-symmetrizable cluster algebra of finite type, with respect to any initial exchange matrix~$\B_\circ$ (acyclic or not).
+We provide the following polytopal realizations of~$\Fan(\B_\circ)$.
 
@@
 
-Here, $\meshes$ represents the set of all pairs~$\{x,x'\}$ related by non-initial mesh mutations (\cref{def:meshMutation}), and~$\principalVariables$ the set of cluster variables.
+Here, $\meshes$ denotes the set of all pairs~$\{x,x'\}$ related by non-initial mesh mutations (\cref{def:meshMutation}), and~$\principalVariables$ the set of cluster variables.
 For $\{x,x'\} \in \meshes$ and $y \in \principalVariables$, the coefficient $\alpha_{x,x',y}$ is defined as follows: $\alpha_{x,x',y}$ is set to be~$|b_{xy}|$ if~$y\in X\cap X'$ and $0$ otherwise, where~$X,X'$ are any two clusters such that~$X \ssm \{x\} = X' \ssm \{x'\}$.
-By the unique exchange relation property, the~$\alpha_{x,x',y}$'s do not depend on the specific choice of the clusters~$X,X'$.
+By the unique exchange relation property, the coefficients~$\alpha_{x,x',y}$ do not depend on the specific choice of clusters~$X,X'$.
 
@@
 \begin{coro:simplicialTypeConeCA}
-The type cone~$\typeCone(\Fan(\B_\circ))$ is simplicial.
+The type cone~$\typeCone \big( \Fan(\B_\circ) \big)$ is simplicial.
 \end{coro:simplicialTypeConeCA}
 
-\para{Gentle algebras, non-kissing complex, generalized accordiohedra}
+\para{Gentle algebras, non-kissing complexes, and generalized accordiohedra}
 (\cref{subsec:typeConeNKC})
@@
 
-Let~$\quiver = (Q,I)$ be a gentle bound quiver, and let~$\Fan(\quiver)$ be the fan of its~$\b{g}$-vectors (\cref{subsubsec:nonkissingComplex}), also called its non-kissing fan.
-We prove \cref{prop:exchangeablePairsNKC} (ii) in \cref{sec:Kbproj}, by making use of representation theory, and state here the following consequence.
-
-\newtheorem*{prop:exchangeablePairsNKC}{\cref{prop:exchangeablePairsNKC}\,(iv)}
+Let~$\quiver = (Q,I)$ be a gentle bound quiver, and let~$\Fan(\quiver)$ be the fan of its~$\b{g}$-vectors (\cref{subsubsec:nonkissingComplex}), also called non-kissing fan.
+We provide the following polytopal realizations of~$\Fan(\quiver)$.
+
+\newtheorem*{thm:allPolytopalRealizationsNKC}{\cref{thm:allPolytopalRealizationsNKC}}
+\begin{thm:allPolytopalRealizationsNKC}
+For any brick and $2$-acyclic gentle quiver~$\quiver$ and any~$\b{\ell} \in \R_{>0}^{\strings}$, the polytope
+\[
+R_\b{\ell}(\quiver) \eqdef \set{\b{z} \in \R^{\walks}}{\begin{array}{l} \b{z} \ge 0 \qquad\text{and}\qquad \b{z}_\omega = 0 \text{ for any improper walk } \omega \\ \b{z}_{\cc{\sigma}} + \b{z}_{\hh{\sigma}} - \b{z}_{\hc{\sigma}} - \b{z}_{\ch{\sigma}} = \b{\ell}_\sigma \text{ for all } \sigma \in \strings\end{array}}
+\]
+is a realization of the non-kissing fan~$\gvectorFan[\quiver]$.
+Moreover, the polytopes~$R_\b{\ell}(\quiver)$ for~$\b{\ell} \in \R_{>0}^{\strings}$ describe all polytopal realizations of~$\gvectorFan[\quiver]$.
+\end{thm:allPolytopalRealizationsNKC}
+
+Here, $\strings$ is the set of all strings of~$\quiver$, and~$\walks$ the set of all walks on~$\quiver$ (\ie of all strings of the blossoming bound quiver of~$\quiver$ that join two blossom vertices).
+If~$\sigma$ is a string of~$\quiver$, we make use of the evocative notations~$\cc{\sigma}, \hh{\sigma}, \hc{\sigma}, \ch{\sigma}$ for the walks obtained by adding, in the blossoming bound quiver, hooks or cohooks at each end of~$\sigma$.
+
+\medskip
+
+The two main ingredients are similar to those for cluster algebras.
+As a first step, we obtain the following consequence of \cref{prop:exchangeablePairsNKC} (ii), which is proved in \cref{sec:Kbproj} by representation theory.
+
+\newtheorem*{prop:exchangeablePairsNKC}{\cref{prop:exchangeablePairsNKC}\,{\normalfont (iv)}}
 \begin{prop:exchangeablePairsNKC}
@@
 
-\cref{subsubsec:simplicialTypeConeNKC} is dedicated to giving a purely combinatorial proof of the following statement.
+The second step is the following statement, for which we provide a purely combinatorial proof in \cref{subsubsec:simplicialTypeConeNKC} and an algebraic proof in \cref{sec:Kbproj}, using the main result of \cref{sec:extricats}.
 
@@
 \begin{coro:simplicialTypeConeNKC}
-Assume that the gentle bound quiver~$\quiver$ is brick and 2-acyclic.
-Then the type cone~$\typeCone(\Fan(\quiver))$ is simplicial.
+If the gentle bound quiver~$\quiver$ is brick and 2-acyclic, then the type cone~$\typeCone \big( \Fan(\quiver) \big)$ is simplicial.
 \end{coro:simplicialTypeConeNKC}
-
-An alternative algebraic proof, using the main result of \cref{sec:extricats}, is given in \cref{sec:Kbproj}.
-
-Combining these pieces, we make use of our type cone approach to deduce the following.
-
-\newtheorem*{coro:allPolytopalRealizationsNKC}{\cref{coro:allPolytopalRealizationsNKC}}
-\begin{coro:allPolytopalRealizationsNKC}
-For any brick and $2$-acyclic gentle quiver~$\quiver$ and any~$\b{\ell} \in \R_{>0}^{\strings}$, the polytope
-\[
-R_\b{\ell}(\quiver) \eqdef \set{\b{z} \in \R^{\walks}}{\begin{array}{l} \b{z} \ge 0 \qquad\text{and}\qquad \b{z}_\omega = 0 \text{ for any improper walk } \omega \\ \b{z}_{\cc{\sigma}} + \b{z}_{\hh{\sigma}} - \b{z}_{\hc{\sigma}} - \b{z}_{\ch{\sigma}} = \b{\ell}_\sigma \text{ for all } \sigma \in \strings\end{array}}
-\]
-is a realization of the non-kissing fan~$\gvectorFan[\quiver]$.
-Moreover, the polytopes~$R_\b{\ell}(\quiver)$ for~$\b{\ell} \in \R_{>0}^{\strings}$ describe all polytopal realizations of~$\gvectorFan[\quiver]$.
-\end{coro:allPolytopalRealizationsNKC}
-
-Here, $\strings$ is the set of all strings of~$\quiver$, and~$\walks$ the set of all walks on~$\quiver$ (i.e.
-of all strings of the blossoming bound quiver of~$\quiver$ that join two blossom vertices).
-If~$\sigma$ is a string of~$\quiver$, we make use of the evocative notations~$\cc{\sigma}, \hh{\sigma}, \hc{\sigma}, \ch{\sigma}$ for the walks obtained by adding, in the blossoming bound quiver, hooks or cohooks at each end of~$\sigma$.
 
@@
 Let~$\Ksp(\cat)$ be the split Grothendieck group of~$\cat$.
-Fix a cluster-tilting object~$T\in\cat$, and let~$K_0(\cat ; T)$ be the quotient of~$\Ksp(\cat)$ by the relations~$[X]+[Z]-[Y]$ for all triangles
-$
-X\xrightarrow{} Y \xrightarrow{} Z \xrightarrow{h} \susp X
-$
-with~$h \in (\susp T)$.
+Fix a cluster-tilting object~$T\in\cat$, and let $K_0(\cat ; T)$ be the quotient of~$\Ksp(\cat)$ by the relations~$[X]+[Z]-[Y]$ for all triangles ${X\xrightarrow{} Y \xrightarrow{} Z \xrightarrow{h} \susp X}$ with~$h \in (\susp T)$.
 Denote by~$\b{g}:\Ksp(\cat) \to K_0(\cat ; T)$ the canonical projection.
@@
 Assume moreover that~$\cat$ is~$\field$-linear, Ext-finite, Krull--Schmidt and has Auslander--Reiten--Serre duality.
-Then, with notations analogous to those used for cluster categories above, we obtain the following:
+Then, with notations analogous to those used for cluster categories above, we obtain the following statement.
 
@@
 In particular, the classical associahedron is the gentle associahedron of a brick and $2$-acyclic gentle quiver.
-We will see in \cref{coro:simplicialTypeConeNKC} that the type cone of the non-kissing fan~$\gvectorFan[\quiver]$ of a brick and $2$-acyclic gentle quiver~$\quiver$ happens to be simplicial, and we will derive in \cref{coro:allPolytopalRealizationsNKC} a simple description of all polytopal realizations of~$\gvectorFan[\quiver]$.
+We will see in \cref{coro:simplicialTypeConeNKC} that the type cone of the non-kissing fan~$\gvectorFan[\quiver]$ of a brick and $2$-acyclic gentle quiver~$\quiver$ happens to be simplicial, and we will derive in \cref{thm:allPolytopalRealizationsNKC} a simple description of all polytopal realizations of~$\gvectorFan[\quiver]$.
 
@@
 \begin{theorem}
-\label{coro:allPolytopalRealizationsNKC}
+\label{thm:allPolytopalRealizationsNKC}
 For any brick and $2$-acyclic gentle quiver~$\quiver$ and any~$\b{\ell} \in \R_{>0}^{\strings}$, the polytope
@@
 \label{exm:nonSimplicialTypeConeNKC}
-Note that \cref{prop:interestingExchangeablePairsNKC,prop:extremalExchangeablePairsNKC} and therefore \cref{coro:simplicialTypeConeNKC,coro:allPolytopalRealizationsNKC} fail when the quiver is not brick or $2$-cyclic.
+Note that \cref{prop:interestingExchangeablePairsNKC,prop:extremalExchangeablePairsNKC} and therefore \cref{coro:simplicialTypeConeNKC,thm:allPolytopalRealizationsNKC} fail when the quiver is not brick or $2$-cyclic.
 The smallest exemples are the $2$-cycles whose non-kissing fans are represented in \cref{fig:nonkissingFans2}.
@@
 \begin{notation}
-We let~$\Modt$ denote the category of additive functors from~$\tc$ to Abelian groups, and~$\modt$ its full subcategory of functors that are finitely presented, i.e.
-cokernels of morphisms between representable functors.
+We let~$\Modt$ denote the category of additive functors from~$\tc$ to Abelian groups, and~$\modt$ its full subcategory of functors that are finitely presented, \ie cokernels of morphisms between representable functors.
 We let~$F:\cat\to\Modt$ be the functor defined on objects by sending~$X\in\cat$ to~$\cat(-,X)|_\tc$.
@@
 For any~$T\in\tc$, fix an extriangle~$T\infl 0\defl\susp T\overset{\eps_T}{\dashrightarrow}$.
-As noticed in \cref{lem:shifts of extriangles}, for any morphism~$T\overset{f}{\to}T'$ in~$\tc$, there is a unique morphism~$\susp f\in\cat(\susp T,\susp T')$ such that~${f_\ast\eps_T=(\susp f)^\ast\eps_{T'}}$ (i.e.
-such that~$(f,\susp f)$ is a morphism from~$\eps_T$ to~$\eps_{T'}$), as illustrated below:
+As noticed in \cref{lem:shifts of extriangles}, for any morphism~$T\overset{f}{\to}T'$ in~$\tc$, there is a unique morphism~$\susp f\in\cat(\susp T,\susp T')$ such that~${f_\ast\eps_T=(\susp f)^\ast\eps_{T'}}$ (\ie such that~$(f,\susp f)$ is a morphism from~$\eps_T$ to~$\eps_{T'}$), as illustrated below:
 \[
@@
 \label{def:mutation conflation}
-A conflation $X\infl E\defl Y$ of~$K^{[-1,0]}(\proj \Lambda)$ is called a \defn{mutation conflation} if there are basic, two-term, silting objects $X\oplus R$, $Y\oplus R$, with~$X$ and~$Y$ indecomposable, such that the inflation $X\infl E$ is a left ($\add R$)-approximation (i.e.
-any morphism from~$X$ to an object in~$\add R$ factors through~$X\infl E$).
+A conflation $X\infl E\defl Y$ of~$K^{[-1,0]}(\proj \Lambda)$ is called a \defn{mutation conflation} if there are basic, two-term, silting objects $X\oplus R$, $Y\oplus R$, with~$X$ and~$Y$ indecomposable, such that the inflation $X\infl E$ is a left ($\add R$)-approximation (\ie any morphism from~$X$ to an object in~$\add R$ factors through~$X\infl E$).
 \end{definition}
@@
 Write~$\sigma$ for the string corresponding to~$\tau M$.
-Then the walks (i.e.
-the maximal strings in the blossoming bound quiver of~$(Q,I)$) associated with~$M$ and~$\tau M$ are respectively~$\omega_M = \hh\sigma = p^{-1}\alpha\sigma\beta^{-1}q$ and~$\omega_{\tau M}=\cc\sigma=p'\alpha'^{-1}\sigma\beta'q'^{-1}$, where~$p,p',q,q'$ are paths and~$\alpha,\alpha',\beta,\beta'$ are arrows in the blossoming quiver.
+Then the walks (\ie the maximal strings in the blossoming bound quiver of~$(Q,I)$) associated with~$M$ and~$\tau M$ are respectively~$\omega_M = \hh\sigma = p^{-1}\alpha\sigma\beta^{-1}q$ and~$\omega_{\tau M}=\cc\sigma=p'\alpha'^{-1}\sigma\beta'q'^{-1}$, where~$p,p',q,q'$ are paths and~$\alpha,\alpha',\beta,\beta'$ are arrows in the blossoming quiver.
 
@@
 By \cref{lem:characterization Gentle 2-acyclic}, the assumptions of \cref{thm:brick-algebra-condition} are satisfied.
-We can thus apply \cref{thm:extricats} and its corollary, which shows that there is the same number of extremal exchange pairs of the support~$\tau$-tilting fan (i.e.
-the non-kissing fan) as there are meshes in the Auslander--Reiten quiver of~$\Lambda$.
+We can thus apply \cref{thm:extricats} and its corollary, which shows that there is the same number of extremal exchange pairs of the support~$\tau$-tilting fan (\ie the non-kissing fan) as there are meshes in the Auslander--Reiten quiver of~$\Lambda$.
 Hence the type cone of the support~$\tau$-tilting fan is simplicial.

### 2019-07-14 thirdPaper/draft/typeConeAssociahedra.tex
schema

@@
 \usepackage{tkz-graph}
-\usetikzlibrary{trees, decorations, decorations.markings, shapes, arrows, matrix, calc, fit, intersections, patterns, angles}
+\usetikzlibrary{trees, decorations, decorations.pathmorphing, decorations.markings, decorations.shapes, shapes, arrows, matrix, calc, fit, intersections, patterns, angles}
 \graphicspath{{figures/}{figures/diagonals/}{figures/walks/}{figures/tubes/}}
@@
 
-We give a brief overview of our main results and the structure of the article.
+We now give a more detailed overview of our main results and the structure of the article.
 In particular, some of the geometric realizations in~\cref{part:geometry} depend on algebraic results whose proof is delayed until~\cref{part:algebra}.
@@
 
-\para{Cluster algebras of finite type}
+\para{Cluster algebras of finite type and generalized associahedra}
 (\cref{subsec:typeConeCA})
@@
 The same strategy is applied to a class of finite dimensional algebras, called gentle algebras, whose representations are combinatorially well understood.
+We note that the~$\tau$-tilting theory of gentle algebras is the algebraic counterpart of the combinatorics of accordions on surfaces~\cite{PaluPilaudPlamondon-nonkissing,BrustleDouvilleMousavandThomasYildirim,PaluPilaudPlamondon-surfaces}.
 We identify two conditions, called brick and 2-acyclicity (\cref{def:brick2acyclic}), that enable us to make use of the type cone approach.
-We note that the~$\tau$-tilting theory of gentle algebras is the algebraic counterpart of the combinatorics of accordions on surfaces~\cite{PaluPilaudPlamondon-nonkissing,BrustleDouvilleMousavandThomasYildirim,PaluPilaudPlamondon-surfaces}.
 
@@
 
-\para{Graphical nested complexes}
+\para{Graphical nested complexes and graph associahedra}
 (\cref{subsec:typeConeGA})
@@
 We prove an analogue for cluster categories of a result of M. Auslander for module categories of Artin algebras~\cite{Auslander1984}. 
-We are mainly motivated by the fact that it has for a consequence that the type cones of the cluster fans of finite type are simplicial.
+We are mainly motivated by the fact that it implies that the type cones of the cluster fans of finite type are simplicial.
 However, this result is of independent interest and sheds new lights on the Grothendieck groups of cluster categories.
@@
 \noindent
-We prove a more general version of \cref{thm:relations-g-vecteurs} that not only applies to cluster fans, but also to non-kissing fans.
+We prove a more general version of \cref{thm:relations-g-vecteurs} that applies not only to cluster fans, but also to non-kissing fans.
 Once more, our main motivation is to prove that the type cone of the non-kissing fan of a brick and 2-acyclic gentle algebra is simplicial, but the results are of independent interest, and might be useful for studying the type cones of other families of simplicial fans.
@@
 
+\noindent
+We conclude with a schematic diagram representing the logical dependencies between the different sections of the paper.
+
 \medskip
@@
 \end{center}
+
+\vspace{.5cm}
+\tikzset{
+  double arrow/.style={
+    -latex, line width=3pt, black, % first arrow
+    postaction={draw,line width=2pt, white, shorten <= 1,shorten >= 2}, % second arrow
+  }
+}
+\centerline{
+\begin{tikzpicture}[every node/.style={inner sep=6, outer sep=8}]
+	\node[cloud, cloud puffs=25, cloud ignores aspect, minimum width=5cm, minimum height=1cm, align=center, draw=blue, fill=blue!25] (I1) at (0,1.5) {\ref{part:geometry}.\ref{sec:typeCone} -- Type cone strategy};
+	\node[rectangle, draw=black, fill=black!10, align=center] (I21) at (-6,0) {\ref{part:geometry}.\ref{subsec:typeConeAsso} -- Toy example \\ Classical associahedra};
+	\node[rectangle, draw=orange, fill=orange!10, align=center, text width=5cm] (I22) at (-3,-1.5) {\ref{part:geometry}.\ref{subsec:typeConeCA} -- Cluster algebras \\ \& generalized associahedra};
+	\node[rectangle, draw=green, fill=green!10, align=center, text width=5cm] (I23) at (3,-1.5) {\ref{part:geometry}.\ref{subsec:typeConeNKC} -- Gentle algebras \\ \& generalized accordiohedra};
+	\node[rectangle, draw=red, fill=red!10, align=center, text width=5.4cm] (I24) at (7,0) {\ref{part:geometry}.\ref{subsec:typeConeGA} -- Graphical nested complexes \\ \& graph associahedra};
+	\node[ellipse, draw=orange, fill=orange!10, align=center, text width=4.9cm, inner sep=2, minimum height=1cm] (II1) at (-4.5,-4.2) {\ref{part:algebra}.\ref{sec:clusterCategories} -- Cluster categories};
+	\node[ellipse, draw=green, fill=green!10, align=center, text width=4.9cm, inner sep=0, minimum height=1cm] (II2) at (4.5,-4.2) {\ref{part:algebra}.\ref{sec:extricats} -- Extriangulated categories};
+	\draw[decorate, decoration={shape backgrounds, shape=circle, shape size=2mm, shape evenly spread=8}, draw=blue, fill=blue!25] (I1.180) to [bend right, looseness=1.1] node[label={[shift={(.6,-1.5)}]applied to}]{} (I21.90);
+	\draw[decorate, decoration={shape backgrounds, shape=circle, shape size=2mm, shape evenly spread=8}, draw=blue, fill=blue!25] (I1.240) to [bend right, looseness=.6] node[label={[shift={(.6,-1.5)}]applied to}]{} (I22.90);
+	\draw[decorate, decoration={shape backgrounds, shape=circle, shape size=2mm, shape evenly spread=8}, draw=blue, fill=blue!25] (I1.300) to [bend left, looseness=.6] node[label={[shift={(-.6,-1.5)}]applied to}]{} (I23.90);
+	\draw[decorate, decoration={shape backgrounds, shape=circle, shape size=2mm, shape evenly spread=10}, draw=blue, fill=blue!25] (I1.0) to [bend left, looseness=1.1] (I24.90);
+	\draw[decorate, decoration={markings, mark=at position 0.5 with {\draw [red, ultra thick,-] ++ (-.3,-.3)  -- ( .3, .3); \draw [red, ultra thick,-] ++ (-.3, .3)  -- ( .3,-.3);}}] (I1.0) to [bend left, looseness=1.1] node[label={[shift={(-.4,-1.7)}]not applicable to}]{} (I24.90);
+	\draw[thick, double distance=2pt, -implies] (I22.270)+(0,-1.3) to node[semithick, right, outer sep=0, pos=0.65]{used for} (I22.270)+(0,.15);
+	\draw[thick, double distance=2pt, -implies] (I23.270)+(0,-1.3) to node[semithick, right, outer sep=0, pos=0.65]{used for} (I23.270)+(0,.15);
+	\draw[thick, ->] (II1.0) to node[semithick, above, outer sep=0]{generalizes} (II2.180);
+	\draw let \p{top}=(I1.90), \p{left}=(I21.180), \p{bottom}=(I22.270), \p{right}=(I24.0) in (\x{left}, \y{top}) -- (\x{left}, \y{bottom}) -- (\x{right}, \y{bottom}) -- (\x{right}, \y{top}) -- (\x{left}, \y{top});
+	\draw let \p{top}=([shift={(0,.2)}]II1.90), \p{left}=(I21.180), \p{bottom}=(II1.270), \p{right}=(I24.0) in (\x{left}, \y{top}) -- (\x{left}, \y{bottom}) -- (\x{right}, \y{bottom}) -- (\x{right}, \y{top}) -- (\x{left}, \y{top});
+	\path let \p{top}=(I1.90) in node[rectangle, draw, fill=white, align=left, inner sep=4] (I) at (-6.15, \y{top}) {\ref{part:geometry} -- Discrete geometry};
+	\path let \p{top}=([shift={(0,.2)}]II1.90) in node[rectangle, draw, fill=white, align=left, inner sep=4] (I) at (-5.8, \y{top}) {\ref{part:algebra} -- Representation theory};
+\end{tikzpicture}
+}
 

### 2019-07-14 thirdPaper/draft/typeConeAssociahedra.tex
coro type cone summaary

@@
 If $\Fan$ is a simplicial fan and has the unique exchange relation property (\cref{def:uerp}), then its type cone is easier to describe and study.
-And if moreover the type cone~$\typeCone(\Fan)$ is simplicial (\cref{rem:dimTypeCone}), then all possible polytopal realizations of~$\Fan$ can be described explicitely in terms of~$N-n$ positive real parameters (\cref{coro:simplicialTypeCone}).
+And if moreover the type cone~$\typeCone(\Fan)$ is simplicial (\cref{rem:dimTypeCone}), then all possible polytopal realizations of~$\Fan$ can be described explicitely in terms of~$N-n$ positive real parameters as follows
+
+\newtheorem*{coro:simplicialTypeCone}{\cref{coro:simplicialTypeCone}}
+\begin{coro:simplicialTypeCone}
+\label{coro:simplicialTypeCone}
+Assume that the type cone~$\typeCone(\Fan)$ is simplicial and let~$\b{K}$ be the $(N-n) \times N$-matrix whose rows are the inner normal vectors of the facets of~$\typeCone(\Fan)$. Then the polytope
+\[
+R_\b{\ell} \eqdef \set{\b{z} \in \R^N}{K\b{z} = \b{\ell} \text{ and } \b{z} \ge 0}
+\]
+is a realization of the fan~$\Fan$ for any positive vector~$\b{\ell} \in \R_{>0}^{N-n}$.
+Moreover, the polytopes~$R_\b{\ell}$ for~$\b{\ell} \in \R_{>0}^{N-n}$ describe all polytopal realizations of~$\Fan$.
+\end{coro:simplicialTypeCone}
+
 This gives a new point of view on~\cite{ArkaniHamedBaiHeYan,BazierMatteDouvilleMousavandThomasYildirim}, illustrated in \cref{subsec:typeConeAsso} for classical associahedra, that we then apply to two families of~$\b{g}$-vector fans generalizing the~$\b{g}$-vector fans of classical associahedra: the~$\b{g}$-vector fans of cluster algebras of finite type (generalized associahedra) in~\cref{subsec:typeConeCA}, and the~$\b{g}$-vector fans of gentle algebras (non-kissing associahedra, non-crossing associahedra, generalized accordiohedra) in~\cref{subsec:typeConeNKC}.
@@
 We conclude with a schematic diagram representing the logical dependencies between the different sections of the paper.
-
-\medskip
-
-\begin{center}
-\includegraphics[scale=.9]{Schema}
-\end{center}
 
@@
 }
+
+\medskip
+
+\begin{center}
+\includegraphics[scale=.9]{Schema}
+\end{center}
 

### 2019-07-15 thirdPaper/draft/typeConeAssociahedra.tex
changed cloud to diamond

@@
 In particular, some of the geometric realizations in~\cref{part:geometry} depend on algebraic results whose proof is delayed until~\cref{part:algebra}.
-The goal of this section is to clarify their logical dependencies.
+The goal of this section is to clarify their logical dependencies, summarized in the schematic diagram depicted at the end.
 
@@
 \begin{tikzpicture}[every node/.style={inner sep=6, outer sep=8}]
-	\node[cloud, cloud puffs=25, cloud ignores aspect, minimum width=5cm, minimum height=1cm, align=center, draw=blue, fill=blue!25] (I1) at (0,1.5) {\ref{part:geometry}.\ref{sec:typeCone} -- Type cone strategy};
+% 	\node[cloud, cloud puffs=25, cloud ignores aspect, minimum width=5cm, minimum height=1cm, align=center, draw=blue, fill=blue!25] (I1) at (0,1.5) {\ref{part:geometry}.\ref{sec:typeCone} -- Type cone strategy};
+	\node[diamond,aspect=3, minimum width=5cm, minimum height=1cm, align=center, draw=blue, fill=blue!10] (I1) at (0,1.5) {\ref{part:geometry}.\ref{sec:typeCone} -- Type cone strategy};
 	\node[rectangle, draw=black, fill=black!10, align=center] (I21) at (-6,0) {\ref{part:geometry}.\ref{subsec:typeConeAsso} -- Toy example \\ Classical associahedra};
@@
 	\node[ellipse, draw=green, fill=green!10, align=center, text width=4.9cm, inner sep=0, minimum height=1cm] (II2) at (4.5,-4.2) {\ref{part:algebra}.\ref{sec:extricats} -- Extriangulated categories};
-	\draw[decorate, decoration={shape backgrounds, shape=circle, shape size=2mm, shape evenly spread=8}, draw=blue, fill=blue!25] (I1.180) to [bend right, looseness=1.1] node[label={[shift={(.6,-1.5)}]applied to}]{} (I21.90);
-	\draw[decorate, decoration={shape backgrounds, shape=circle, shape size=2mm, shape evenly spread=8}, draw=blue, fill=blue!25] (I1.240) to [bend right, looseness=.6] node[label={[shift={(.6,-1.5)}]applied to}]{} (I22.90);
-	\draw[decorate, decoration={shape backgrounds, shape=circle, shape size=2mm, shape evenly spread=8}, draw=blue, fill=blue!25] (I1.300) to [bend left, looseness=.6] node[label={[shift={(-.6,-1.5)}]applied to}]{} (I23.90);
-	\draw[decorate, decoration={shape backgrounds, shape=circle, shape size=2mm, shape evenly spread=10}, draw=blue, fill=blue!25] (I1.0) to [bend left, looseness=1.1] (I24.90);
+% 	\draw[decorate, decoration={shape backgrounds, shape=circle, shape size=2mm, shape evenly spread=8}, draw=blue, fill=blue!25] (I1.180) to [bend right, looseness=1.1] node[label={[shift={(.6,-1.5)}]applied to}]{} (I21.90);
+% 	\draw[decorate, decoration={shape backgrounds, shape=circle, shape size=2mm, shape evenly spread=8}, draw=blue, fill=blue!25] (I1.240) to [bend right, looseness=.6] node[label={[shift={(.6,-1.5)}]applied to}]{} (I22.90);
+% 	\draw[decorate, decoration={shape backgrounds, shape=circle, shape size=2mm, shape evenly spread=8}, draw=blue, fill=blue!25] (I1.300) to [bend left, looseness=.6] node[label={[shift={(-.6,-1.5)}]applied to}]{} (I23.90);
+% 	\draw[decorate, decoration={shape backgrounds, shape=circle, shape size=2mm, shape evenly spread=10}, draw=blue, fill=blue!25] (I1.0) to [bend left, looseness=1.1] (I24.90);
+% 	\draw[decorate, decoration={markings, mark=at position 0.5 with {\draw [red, ultra thick,-] ++ (-.3,-.3)  -- ( .3, .3); \draw [red, ultra thick,-] ++ (-.3, .3)  -- ( .3,-.3);}}] (I1.0) to [bend left, looseness=1.1] node[label={[shift={(-.4,-1.7)}]not applicable to}]{} (I24.90);
+	\draw[decorate, decoration={shape backgrounds, shape=dart, shape size=2mm, shape evenly spread=8}, draw=blue, fill=blue!10] (I1.180) to [bend right, looseness=1.1] node[label={[shift={(.6,-1.5)}]applied to}]{} (I21.90);
+	\draw[decorate, decoration={shape backgrounds, shape=dart, shape size=2mm, shape evenly spread=8}, draw=blue, fill=blue!10] (I1.220) to [bend right, looseness=.6] node[label={[shift={(.6,-1.5)}]applied to}]{} (I22.90);
+	\draw[decorate, decoration={shape backgrounds, shape=dart, shape size=2mm, shape evenly spread=8}, draw=blue, fill=blue!10] (I1.320) to [bend left, looseness=.6] node[label={[shift={(-.6,-1.5)}]applied to}]{} (I23.90);
+	\draw[decorate, decoration={shape backgrounds, shape=dart, shape size=2mm, shape evenly spread=10}, draw=blue, fill=blue!10] (I1.0) to [bend left, looseness=1.1] (I24.90);
 	\draw[decorate, decoration={markings, mark=at position 0.5 with {\draw [red, ultra thick,-] ++ (-.3,-.3)  -- ( .3, .3); \draw [red, ultra thick,-] ++ (-.3, .3)  -- ( .3,-.3);}}] (I1.0) to [bend left, looseness=1.1] node[label={[shift={(-.4,-1.7)}]not applicable to}]{} (I24.90);

### 2019-07-15 thirdPaper/draft/typeConeAssociahedra.tex
both pictures + simplicial + Rem 1.6

@@
 \begin{tikzpicture}[every node/.style={inner sep=6, outer sep=8}]
-% 	\node[cloud, cloud puffs=25, cloud ignores aspect, minimum width=5cm, minimum height=1cm, align=center, draw=blue, fill=blue!25] (I1) at (0,1.5) {\ref{part:geometry}.\ref{sec:typeCone} -- Type cone strategy};
-	\node[diamond,aspect=3, minimum width=5cm, minimum height=1cm, align=center, draw=blue, fill=blue!10] (I1) at (0,1.5) {\ref{part:geometry}.\ref{sec:typeCone} -- Type cone strategy};
+	\node[diamond,aspect=3, text width=5cm, minimum height=1cm, align=center, draw=blue, fill=blue!10, inner sep=-2] (I1) at (0,1.5) {\ref{part:geometry}.\ref{sec:typeCone} -- Simplicial type cone strategy};
 	\node[rectangle, draw=black, fill=black!10, align=center] (I21) at (-6,0) {\ref{part:geometry}.\ref{subsec:typeConeAsso} -- Toy example \\ Classical associahedra};
@@
 	\node[ellipse, draw=green, fill=green!10, align=center, text width=4.9cm, inner sep=0, minimum height=1cm] (II2) at (4.5,-4.2) {\ref{part:algebra}.\ref{sec:extricats} -- Extriangulated categories};
-% 	\draw[decorate, decoration={shape backgrounds, shape=circle, shape size=2mm, shape evenly spread=8}, draw=blue, fill=blue!25] (I1.180) to [bend right, looseness=1.1] node[label={[shift={(.6,-1.5)}]applied to}]{} (I21.90);
-% 	\draw[decorate, decoration={shape backgrounds, shape=circle, shape size=2mm, shape evenly spread=8}, draw=blue, fill=blue!25] (I1.240) to [bend right, looseness=.6] node[label={[shift={(.6,-1.5)}]applied to}]{} (I22.90);
-% 	\draw[decorate, decoration={shape backgrounds, shape=circle, shape size=2mm, shape evenly spread=8}, draw=blue, fill=blue!25] (I1.300) to [bend left, looseness=.6] node[label={[shift={(-.6,-1.5)}]applied to}]{} (I23.90);
-% 	\draw[decorate, decoration={shape backgrounds, shape=circle, shape size=2mm, shape evenly spread=10}, draw=blue, fill=blue!25] (I1.0) to [bend left, looseness=1.1] (I24.90);
-% 	\draw[decorate, decoration={markings, mark=at position 0.5 with {\draw [red, ultra thick,-] ++ (-.3,-.3)  -- ( .3, .3); \draw [red, ultra thick,-] ++ (-.3, .3)  -- ( .3,-.3);}}] (I1.0) to [bend left, looseness=1.1] node[label={[shift={(-.4,-1.7)}]not applicable to}]{} (I24.90);
 	\draw[decorate, decoration={shape backgrounds, shape=dart, shape size=2mm, shape evenly spread=8}, draw=blue, fill=blue!10] (I1.180) to [bend right, looseness=1.1] node[label={[shift={(.6,-1.5)}]applied to}]{} (I21.90);
@@
 	\draw[decorate, decoration={shape backgrounds, shape=dart, shape size=2mm, shape evenly spread=10}, draw=blue, fill=blue!10] (I1.0) to [bend left, looseness=1.1] (I24.90);
+	\draw[decorate, decoration={markings, mark=at position 0.5 with {\draw [red, ultra thick,-] ++ (-.3,-.3)  -- ( .3, .3); \draw [red, ultra thick,-] ++ (-.3, .3)  -- ( .3,-.3);}}] (I1.0) to [bend left, looseness=1.1] node[label={[shift={(-.4,-1.7)}]not applicable to}]{} (I24.90);
+	\draw[thick, double distance=2pt, -implies] (I22.270)+(0,-1.3) to node[semithick, right, outer sep=0, pos=0.65]{used for} (I22.270)+(0,.15);
+	\draw[thick, double distance=2pt, -implies] (I23.270)+(0,-1.3) to node[semithick, right, outer sep=0, pos=0.65]{used for} (I23.270)+(0,.15);
+	\draw[thick, ->] (II1.0) to node[semithick, above, outer sep=0]{generalizes} (II2.180);
+	\draw let \p{top}=(I1.90), \p{left}=(I21.180), \p{bottom}=(I22.270), \p{right}=(I24.0) in (\x{left}, \y{top}) -- (\x{left}, \y{bottom}) -- (\x{right}, \y{bottom}) -- (\x{right}, \y{top}) -- (\x{left}, \y{top});
+	\draw let \p{top}=([shift={(0,.2)}]II1.90), \p{left}=(I21.180), \p{bottom}=(II1.270), \p{right}=(I24.0) in (\x{left}, \y{top}) -- (\x{left}, \y{bottom}) -- (\x{right}, \y{bottom}) -- (\x{right}, \y{top}) -- (\x{left}, \y{top});
+	\path let \p{top}=(I1.90) in node[rectangle, draw, fill=white, align=left, inner sep=4] (I) at (-6.15, \y{top}) {\ref{part:geometry} -- Discrete geometry};
+	\path let \p{top}=([shift={(0,.2)}]II1.90) in node[rectangle, draw, fill=white, align=left, inner sep=4] (I) at (-5.8, \y{top}) {\ref{part:algebra} -- Representation theory};
+\end{tikzpicture}
+}
+
+\centerline{
+\begin{tikzpicture}[every node/.style={inner sep=6, outer sep=8}]
+ 	\node[cloud, cloud puffs=25, cloud ignores aspect, text width=5cm, minimum height=1cm, align=center, draw=blue, fill=blue!10, inner sep=3] (I1) at (0,1.5) {\ref{part:geometry}.\ref{sec:typeCone} -- Simplicial type cone strategy};
+	\node[rectangle, draw=black, fill=black!10, align=center] (I21) at (-6,0) {\ref{part:geometry}.\ref{subsec:typeConeAsso} -- Toy example \\ Classical associahedra};
+	\node[rectangle, draw=orange, fill=orange!10, align=center, text width=5cm] (I22) at (-3,-1.5) {\ref{part:geometry}.\ref{subsec:typeConeCA} -- Cluster algebras \\ \& generalized associahedra};
+	\node[rectangle, draw=green, fill=green!10, align=center, text width=5cm] (I23) at (3,-1.5) {\ref{part:geometry}.\ref{subsec:typeConeNKC} -- Gentle algebras \\ \& generalized accordiohedra};
+	\node[rectangle, draw=red, fill=red!10, align=center, text width=5.4cm] (I24) at (7,0) {\ref{part:geometry}.\ref{subsec:typeConeGA} -- Graphical nested complexes \\ \& graph associahedra};
+	\node[ellipse, draw=orange, fill=orange!10, align=center, text width=4.9cm, inner sep=2, minimum height=1cm] (II1) at (-4.5,-4.2) {\ref{part:algebra}.\ref{sec:clusterCategories} -- Cluster categories};
+	\node[ellipse, draw=green, fill=green!10, align=center, text width=4.9cm, inner sep=0, minimum height=1cm] (II2) at (4.5,-4.2) {\ref{part:algebra}.\ref{sec:extricats} -- Extriangulated categories};
+ 	\draw[decorate, decoration={shape backgrounds, shape=circle, shape size=2mm, shape evenly spread=8}, draw=blue, fill=blue!10] (I1.180) to [bend right, looseness=1.1] node[label={[shift={(.6,-1.5)}]applied to}]{} (I21.90);
+ 	\draw[decorate, decoration={shape backgrounds, shape=circle, shape size=2mm, shape evenly spread=8}, draw=blue, fill=blue!10] (I1.240) to [bend right, looseness=.6] node[label={[shift={(.6,-1.5)}]applied to}]{} (I22.90);
+ 	\draw[decorate, decoration={shape backgrounds, shape=circle, shape size=2mm, shape evenly spread=8}, draw=blue, fill=blue!10] (I1.300) to [bend left, looseness=.6] node[label={[shift={(-.6,-1.5)}]applied to}]{} (I23.90);
+ 	\draw[decorate, decoration={shape backgrounds, shape=circle, shape size=2mm, shape evenly spread=10}, draw=blue, fill=blue!10] (I1.0) to [bend left, looseness=1.1] (I24.90);
  	\draw[decorate, decoration={markings, mark=at position 0.5 with {\draw [red, ultra thick,-] ++ (-.3,-.3)  -- ( .3, .3); \draw [red, ultra thick,-] ++ (-.3, .3)  -- ( .3,-.3);}}] (I1.0) to [bend left, looseness=1.1] node[label={[shift={(-.4,-1.7)}]not applicable to}]{} (I24.90);
@@
 
+\begin{remark}
+\label{rem:dimTypeCone}
 Since the type cone is an~$N$-dimensional cone with a linearity subspace of dimension~$n$, it has at least~$N-n$ facets (thus~$N-n$ extremal adjacent pairs).
-
-\begin{definition}
-\label{rem:dimTypeCone}
 The type cone is \defn{simplicial} when it has precisely $N-n$ facets.
-\end{definition}
+\end{remark}
 

### 2019-07-15 thirdPaper/draft/typeConeAssociahedra.tex
minor change margin node tikz

@@
 \begin{tikzpicture}[every node/.style={inner sep=6, outer sep=8}]
- 	\node[cloud, cloud puffs=25, cloud ignores aspect, text width=5cm, minimum height=1cm, align=center, draw=blue, fill=blue!10, inner sep=3] (I1) at (0,1.5) {\ref{part:geometry}.\ref{sec:typeCone} -- Simplicial type cone strategy};
+ 	\node[cloud, cloud puffs=25, cloud ignores aspect, text width=5cm, minimum height=1cm, align=center, draw=blue, fill=blue!10, inner sep=3, outer sep=5] (I1) at (0,1.5) {\ref{part:geometry}.\ref{sec:typeCone} -- Simplicial type cone strategy};
 	\node[rectangle, draw=black, fill=black!10, align=center] (I21) at (-6,0) {\ref{part:geometry}.\ref{subsec:typeConeAsso} -- Toy example \\ Classical associahedra};

### 2019-07-15 thirdPaper/draft/typeConeAssociahedra.tex
Generalizes --> Generalizes to
3 typos

@@
 We now give a more detailed overview of our main results and the structure of the article.
-In particular, some of the geometric realizations in~\cref{part:geometry} depend on algebraic results whose proof is delayed until~\cref{part:algebra}.
+In particular, some of the geometric realizations in~\cref{part:geometry} depend on algebraic results whose proves are delayed until~\cref{part:algebra}.
 The goal of this section is to clarify their logical dependencies, summarized in the schematic diagram depicted at the end.
@@
 The two main ingredients are similar to those for cluster algebras.
-As a first step, we obtain the following consequence of \cref{prop:exchangeablePairsNKC} (ii), which is proved in \cref{sec:Kbproj} by representation theory.
+As a first step, we obtain the following consequence of \cref{prop:exchangeablePairsNKC} (ii), which is proved in \cref{sec:Kbproj} by representation-theoretic methods.
 
@@
 \begin{thm:extricats}
-The extriangulated category~$\cat$ has only finitely many ismorphism classes of indecomposable objects if and only if the set~$L_\cat$ generates the kernel of the canonical projection ${\b{g}:\Ksp(\cat)\to\kzero{\cat}}$.
+The extriangulated category~$\cat$ has only finitely many isomorphism classes of indecomposable objects if and only if the set~$L_\cat$ generates the kernel of the canonical projection ${\b{g}:\Ksp(\cat)\to\kzero{\cat}}$.
 In that case~$L_\cat$ is a basis of the kernel of~$\b{g}$ and any~$x\in\ker(\b{g})$ decomposes~as
@@
 	\draw[thick, double distance=2pt, -implies] (I23.270)+(0,-1.3) to node[semithick, right, outer sep=0, pos=0.65]{used for} (I23.270)+(0,.15);
-	\draw[thick, ->] (II1.0) to node[semithick, above, outer sep=0]{generalizes} (II2.180);
+	\draw[thick, ->] (II1.0) to node[semithick, above, outer sep=0]{generalizes to} (II2.180);
 	\draw let \p{top}=(I1.90), \p{left}=(I21.180), \p{bottom}=(I22.270), \p{right}=(I24.0) in (\x{left}, \y{top}) -- (\x{left}, \y{bottom}) -- (\x{right}, \y{bottom}) -- (\x{right}, \y{top}) -- (\x{left}, \y{top});

### 2019-07-15 thirdPaper/draft/typeConeAssociahedra.tex
choice picture

@@
 	\draw[thick, ->] (II1.0) to node[semithick, above, outer sep=0]{generalizes to} (II2.180);
-	\draw let \p{top}=(I1.90), \p{left}=(I21.180), \p{bottom}=(I22.270), \p{right}=(I24.0) in (\x{left}, \y{top}) -- (\x{left}, \y{bottom}) -- (\x{right}, \y{bottom}) -- (\x{right}, \y{top}) -- (\x{left}, \y{top});
+	\draw let \p{top}=(I1.90), \p{left}=(I21.180), \p{bottom}=([shift={(0,-.15)}]I22.270), \p{right}=(I24.0) in (\x{left}, \y{top}) -- (\x{left}, \y{bottom}) -- (\x{right}, \y{bottom}) -- (\x{right}, \y{top}) -- (\x{left}, \y{top});
 	\draw let \p{top}=([shift={(0,.2)}]II1.90), \p{left}=(I21.180), \p{bottom}=(II1.270), \p{right}=(I24.0) in (\x{left}, \y{top}) -- (\x{left}, \y{bottom}) -- (\x{right}, \y{bottom}) -- (\x{right}, \y{top}) -- (\x{left}, \y{top});
@@
 
-\centerline{
-\begin{tikzpicture}[every node/.style={inner sep=6, outer sep=8}]
- 	\node[cloud, cloud puffs=25, cloud ignores aspect, text width=5cm, minimum height=1cm, align=center, draw=blue, fill=blue!10, inner sep=3, outer sep=5] (I1) at (0,1.5) {\ref{part:geometry}.\ref{sec:typeCone} -- Simplicial type cone strategy};
-	\node[rectangle, draw=black, fill=black!10, align=center] (I21) at (-6,0) {\ref{part:geometry}.\ref{subsec:typeConeAsso} -- Toy example \\ Classical associahedra};
-	\node[rectangle, draw=orange, fill=orange!10, align=center, text width=5cm] (I22) at (-3,-1.5) {\ref{part:geometry}.\ref{subsec:typeConeCA} -- Cluster algebras \\ \& generalized associahedra};
-	\node[rectangle, draw=green, fill=green!10, align=center, text width=5cm] (I23) at (3,-1.5) {\ref{part:geometry}.\ref{subsec:typeConeNKC} -- Gentle algebras \\ \& generalized accordiohedra};
-	\node[rectangle, draw=red, fill=red!10, align=center, text width=5.4cm] (I24) at (7,0) {\ref{part:geometry}.\ref{subsec:typeConeGA} -- Graphical nested complexes \\ \& graph associahedra};
-	\node[ellipse, draw=orange, fill=orange!10, align=center, text width=4.9cm, inner sep=2, minimum height=1cm] (II1) at (-4.5,-4.2) {\ref{part:algebra}.\ref{sec:clusterCategories} -- Cluster categories};
-	\node[ellipse, draw=green, fill=green!10, align=center, text width=4.9cm, inner sep=0, minimum height=1cm] (II2) at (4.5,-4.2) {\ref{part:algebra}.\ref{sec:extricats} -- Extriangulated categories};
- 	\draw[decorate, decoration={shape backgrounds, shape=circle, shape size=2mm, shape evenly spread=8}, draw=blue, fill=blue!10] (I1.180) to [bend right, looseness=1.1] node[label={[shift={(.6,-1.5)}]applied to}]{} (I21.90);
- 	\draw[decorate, decoration={shape backgrounds, shape=circle, shape size=2mm, shape evenly spread=8}, draw=blue, fill=blue!10] (I1.240) to [bend right, looseness=.6] node[label={[shift={(.6,-1.5)}]applied to}]{} (I22.90);
- 	\draw[decorate, decoration={shape backgrounds, shape=circle, shape size=2mm, shape evenly spread=8}, draw=blue, fill=blue!10] (I1.300) to [bend left, looseness=.6] node[label={[shift={(-.6,-1.5)}]applied to}]{} (I23.90);
- 	\draw[decorate, decoration={shape backgrounds, shape=circle, shape size=2mm, shape evenly spread=10}, draw=blue, fill=blue!10] (I1.0) to [bend left, looseness=1.1] (I24.90);
- 	\draw[decorate, decoration={markings, mark=at position 0.5 with {\draw [red, ultra thick,-] ++ (-.3,-.3)  -- ( .3, .3); \draw [red, ultra thick,-] ++ (-.3, .3)  -- ( .3,-.3);}}] (I1.0) to [bend left, looseness=1.1] node[label={[shift={(-.4,-1.7)}]not applicable to}]{} (I24.90);
-	\draw[thick, double distance=2pt, -implies] (I22.270)+(0,-1.3) to node[semithick, right, outer sep=0, pos=0.65]{used for} (I22.270)+(0,.15);
-	\draw[thick, double distance=2pt, -implies] (I23.270)+(0,-1.3) to node[semithick, right, outer sep=0, pos=0.65]{used for} (I23.270)+(0,.15);
-	\draw[thick, ->] (II1.0) to node[semithick, above, outer sep=0]{generalizes to} (II2.180);
-	\draw let \p{top}=(I1.90), \p{left}=(I21.180), \p{bottom}=(I22.270), \p{right}=(I24.0) in (\x{left}, \y{top}) -- (\x{left}, \y{bottom}) -- (\x{right}, \y{bottom}) -- (\x{right}, \y{top}) -- (\x{left}, \y{top});
-	\draw let \p{top}=([shift={(0,.2)}]II1.90), \p{left}=(I21.180), \p{bottom}=(II1.270), \p{right}=(I24.0) in (\x{left}, \y{top}) -- (\x{left}, \y{bottom}) -- (\x{right}, \y{bottom}) -- (\x{right}, \y{top}) -- (\x{left}, \y{top});
-	\path let \p{top}=(I1.90) in node[rectangle, draw, fill=white, align=left, inner sep=4] (I) at (-6.15, \y{top}) {\ref{part:geometry} -- Discrete geometry};
-	\path let \p{top}=([shift={(0,.2)}]II1.90) in node[rectangle, draw, fill=white, align=left, inner sep=4] (I) at (-5.8, \y{top}) {\ref{part:algebra} -- Representation theory};
-\end{tikzpicture}
-}
-
-\medskip
-
-\begin{center}
-\includegraphics[scale=.9]{Schema}
-\end{center}
+%\centerline{
+%\begin{tikzpicture}[every node/.style={inner sep=6, outer sep=8}]
+% 	\node[cloud, cloud puffs=25, cloud ignores aspect, text width=5cm, minimum height=1cm, align=center, draw=blue, fill=blue!10, inner sep=3, outer sep=5] (I1) at (0,1.5) {\ref{part:geometry}.\ref{sec:typeCone} -- Simplicial type cone strategy};
+%	\node[rectangle, draw=black, fill=black!10, align=center] (I21) at (-6,0) {\ref{part:geometry}.\ref{subsec:typeConeAsso} -- Toy example \\ Classical associahedra};
+%	\node[rectangle, draw=orange, fill=orange!10, align=center, text width=5cm] (I22) at (-3,-1.5) {\ref{part:geometry}.\ref{subsec:typeConeCA} -- Cluster algebras \\ \& generalized associahedra};
+%	\node[rectangle, draw=green, fill=green!10, align=center, text width=5cm] (I23) at (3,-1.5) {\ref{part:geometry}.\ref{subsec:typeConeNKC} -- Gentle algebras \\ \& generalized accordiohedra};
+%	\node[rectangle, draw=red, fill=red!10, align=center, text width=5.4cm] (I24) at (7,0) {\ref{part:geometry}.\ref{subsec:typeConeGA} -- Graphical nested complexes \\ \& graph associahedra};
+%	\node[ellipse, draw=orange, fill=orange!10, align=center, text width=4.9cm, inner sep=2, minimum height=1cm] (II1) at (-4.5,-4.2) {\ref{part:algebra}.\ref{sec:clusterCategories} -- Cluster categories};
+%	\node[ellipse, draw=green, fill=green!10, align=center, text width=4.9cm, inner sep=0, minimum height=1cm] (II2) at (4.5,-4.2) {\ref{part:algebra}.\ref{sec:extricats} -- Extriangulated categories};
+% 	\draw[decorate, decoration={shape backgrounds, shape=circle, shape size=2mm, shape evenly spread=8}, draw=blue, fill=blue!10] (I1.180) to [bend right, looseness=1.1] node[label={[shift={(.6,-1.5)}]applied to}]{} (I21.90);
+% 	\draw[decorate, decoration={shape backgrounds, shape=circle, shape size=2mm, shape evenly spread=8}, draw=blue, fill=blue!10] (I1.240) to [bend right, looseness=.6] node[label={[shift={(.6,-1.5)}]applied to}]{} (I22.90);
+% 	\draw[decorate, decoration={shape backgrounds, shape=circle, shape size=2mm, shape evenly spread=8}, draw=blue, fill=blue!10] (I1.300) to [bend left, looseness=.6] node[label={[shift={(-.6,-1.5)}]applied to}]{} (I23.90);
+% 	\draw[decorate, decoration={shape backgrounds, shape=circle, shape size=2mm, shape evenly spread=10}, draw=blue, fill=blue!10] (I1.0) to [bend left, looseness=1.1] (I24.90);
+% 	\draw[decorate, decoration={markings, mark=at position 0.5 with {\draw [red, ultra thick,-] ++ (-.3,-.3)  -- ( .3, .3); \draw [red, ultra thick,-] ++ (-.3, .3)  -- ( .3,-.3);}}] (I1.0) to [bend left, looseness=1.1] node[label={[shift={(-.4,-1.7)}]not applicable to}]{} (I24.90);
+%	\draw[thick, double distance=2pt, -implies] (I22.270)+(0,-1.3) to node[semithick, right, outer sep=0, pos=0.65]{used for} (I22.270)+(0,.15);
+%	\draw[thick, double distance=2pt, -implies] (I23.270)+(0,-1.3) to node[semithick, right, outer sep=0, pos=0.65]{used for} (I23.270)+(0,.15);
+%	\draw[thick, ->] (II1.0) to node[semithick, above, outer sep=0]{generalizes to} (II2.180);
+%	\draw let \p{top}=(I1.90), \p{left}=(I21.180), \p{bottom}=([shift={(0,-.15)}]I22.270), \p{right}=(I24.0) in (\x{left}, \y{top}) -- (\x{left}, \y{bottom}) -- (\x{right}, \y{bottom}) -- (\x{right}, \y{top}) -- (\x{left}, \y{top});
+%	\draw let \p{top}=([shift={(0,.2)}]II1.90), \p{left}=(I21.180), \p{bottom}=(II1.270), \p{right}=(I24.0) in (\x{left}, \y{top}) -- (\x{left}, \y{bottom}) -- (\x{right}, \y{bottom}) -- (\x{right}, \y{top}) -- (\x{left}, \y{top});
+%	\path let \p{top}=(I1.90) in node[rectangle, draw, fill=white, align=left, inner sep=4] (I) at (-6.15, \y{top}) {\ref{part:geometry} -- Discrete geometry};
+%	\path let \p{top}=([shift={(0,.2)}]II1.90) in node[rectangle, draw, fill=white, align=left, inner sep=4] (I) at (-5.8, \y{top}) {\ref{part:algebra} -- Representation theory};
+%\end{tikzpicture}
+%}
+%
+%\medskip
+%
+%\begin{center}
+%\includegraphics[scale=.9]{Schema}
+%\end{center}
 

### 2019-07-16 thirdPaper/draft/typeConeAssociahedra.tex
improper

@@
 \[
-R_\b{\ell}(\quiver) \eqdef \set{\b{z} \in \R^{\walks}}{\begin{array}{l} \b{z} \ge 0 \qquad\text{and}\qquad \b{z}_\omega = 0 \text{ for any improper walk } \omega \\ \b{z}_{\cc{\sigma}} + \b{z}_{\hh{\sigma}} - \b{z}_{\hc{\sigma}} - \b{z}_{\ch{\sigma}} = \b{\ell}_\sigma \text{ for all } \sigma \in \strings\end{array}}
+R_\b{\ell}(\quiver) \eqdef \set{\b{z} \in \R^{\walks}}{\begin{array}{l} \b{z} \ge 0 \qquad\text{and}\qquad \b{z}_\omega = 0 \text{ for any straight or self-kissing walk } \omega \\ \b{z}_{\cc{\sigma}} + \b{z}_{\hh{\sigma}} - \b{z}_{\hc{\sigma}} - \b{z}_{\ch{\sigma}} = \b{\ell}_\sigma \text{ for all } \sigma \in \strings\end{array}}
 \]
@@
 For example, the orange walk in \cref{fig:exmNonkissing}\,(middle) is self-kissing (at its self-intersection).
-We say that a walk is \defn{proper} if it is not straight nor self-kissing.
+We say that a walk is \defn{proper} if it is not straight nor self-kissing, and \defn{improper} otherwise.
 We denote by~$\properWalks$ the set of all proper walks of~$\quiver$.

### 2019-07-16 thirdPaper/draft/typeConeAssociahedra.tex
minor change

--- 2019-07-15 thirdPaper/draft/typeConeAssociahedra.tex
@@
 \[
-R_\b{\ell}(\quiver) \eqdef \set{\b{z} \in \R^{\walks}}{\begin{array}{l} \b{z} \ge 0 \qquad\text{and}\qquad \b{z}_\omega = 0 \text{ for any improper walk } \omega \\ \b{z}_{\cc{\sigma}} + \b{z}_{\hh{\sigma}} - \b{z}_{\hc{\sigma}} - \b{z}_{\ch{\sigma}} = \b{\ell}_\sigma \text{ for all } \sigma \in \strings\end{array}}
+R_\b{\ell}(\quiver) \eqdef \set{\b{z} \in \R^{\walks}}{\begin{array}{@{}l@{}} \b{z} \ge 0, \quad \b{z}_\omega = 0 \text{ for any straight or self-kissing walk } \omega, \\ \text{and } \b{z}_{\cc{\sigma}} + \b{z}_{\hh{\sigma}} - \b{z}_{\hc{\sigma}} - \b{z}_{\ch{\sigma}} = \b{\ell}_\sigma \text{ for all } \sigma \in \strings\end{array}}
 \]

### 2019-07-16 thirdPaper/draft/typeConeAssociahedra.tex
relecture intro

@@
 
-The associahedron appears as a fundamental structure in several mathematical theories, such as moduli spaces and topology~\cite{Stasheff, Keller-AinfinityAlgebras}, operads and rewriting theory~\cite{Street, MasudaThomasTonksVallette}, combinatorial Hopf algebras~\cite{LodayRonco, ChatelPilaud, Pilaud-brickAlgebra}, diagonal harmonics~\cite{BergeronPrevilleRatelle, PrevilleRatelleViennot}, mathematical physics~\cite{ArkaniHamedBaiHeYan, BanerjeeLaddhaRaman-StokesPolytopes, Raman-PositiveGeometry}, etc.
+The associahedron appears as a fundamental structure in several mathematical theories, such as moduli spaces and topology~\cite{Stasheff, Keller-AinfinityAlgebras}, operads and rewriting theory~\cite{Street, MasudaThomasTonksVallette}, combinatorial Hopf algebras~\cite{LodayRonco, ChatelPilaud, Pilaud-brickAlgebra}, diagonal harmonics~\cite{BergeronPrevilleRatelle, PrevilleRatelleViennot}, mathematical physics~\cite{ArkaniHamedBaiHeYan}, etc.
 Another striking illustration of the ubiquity of the associahedron lies in the theory of cluster algebras introduced by S.~Fomin and A.~Zelevinsky in~\cite{FominZelevinsky-ClusterAlgebrasI} with motivation coming from total positivity and canonical bases.
@@
 In fact, we observe that the type cone of a graphical nested fan is never simplicial except in the case of the classical associahedron (when the graph is the path).
-Our results describe nevertheless all polytopal realizations of the graphical nested fans.
+Nevertheless, our results give a non-redundant description of all polytopal realizations of the graphical nested fans.
 \end{itemize}

### 2019-07-30 thirdPaper/draft/typeConeAssociahedra.tex
Added 2010 MSC classes.
Added reference to Haugland at the start of Section 3.

@@
 \thanks{YP, VP and PGP were partially supported by the French ANR grant SC3A~(15\,CE40\,0004\,01). AP and VP were partially supported by the French ANR grant CAPPS~(17\,CE40\,0018).}
+
+\subjclass[2010]{13F60, 16G20, 18E10, 18E30, 52B11 (primary), 52B35, 05E15 (secondary)}
 
@@
 In~\cite{Auslander1984}, M.~Auslander showed that the relations in the Grothendieck group of an Artin algebra are generated by the ones given by almost-split sequences precisely when the algebra is of finite representation type.
-Inspired by this result, we will show that a similar statement holds (see \cref{thm:relations-g-vecteurs}) for the~$\b{g}$-vectors (or indices) of objects in a~$2$-Calabi--Yau triangulated category.
+This result was generalized to $\Hom{}$-finite, Krull--Schmidt triangulated categories with a cogenerator by J.~Haugland in~\cite{Haugland}.
+Inspired by these results, we will show in this Section that a similar statement holds (see \cref{thm:relations-g-vecteurs}) for the~$\b{g}$-vectors (or indices) of objects in a~$2$-Calabi--Yau triangulated category.
+We will further generalize these results in Section~\ref{sec:extricats} to the setting of Ext-finite, Krull-Schmidt, extriangulated categories with Auslander--Reiten--Serre duality admitting projective objects with certain properties.
 

### 2019-09-02 thirdPaper/draft/typeConeAssociahedra.tex
Added reference to Enomoto in beginning of section 3.

@@
 In~\cite{Auslander1984}, M.~Auslander showed that the relations in the Grothendieck group of an Artin algebra are generated by the ones given by almost-split sequences precisely when the algebra is of finite representation type.
-This result was generalized to $\Hom{}$-finite, Krull--Schmidt triangulated categories with a cogenerator by J.~Haugland in~\cite{Haugland}.
+This result was generalized to $\Hom{}$-finite, Krull-Schmidt exact categories with enough projectives by H.~Enomoto in~\cite{Enomoto}, and to $\Hom{}$-finite, Krull--Schmidt triangulated categories with a cogenerator by J.~Haugland in~\cite{Haugland}.
 Inspired by these results, we will show in this Section that a similar statement holds (see \cref{thm:relations-g-vecteurs}) for the~$\b{g}$-vectors (or indices) of objects in a~$2$-Calabi--Yau triangulated category.

### 2019-09-02 thirdPaper/draft/typeConeAssociahedra.tex
typos Lemma 3.25

@@
 \label{lem:exaclty one mesh mutation}
-For every non-initial cluster variable, there exists precisely one pair~$(x,x')$ such that there exists a positive mesh mutation changing~$x$ into~$x'$.
+For every non-initial cluster variable~$x$, there exists precisely one pair~$(x,x')$ such that there exists a positive mesh mutation changing~$x$ into~$x'$.
 \end{lemma}
@@
 Up to isomorphism, there is precisely one almost-split triangle of~$\cat$ starting in~$X$, where~$X$ is the object such that~$\phi(X) = x$.
-Thus there is precisely one mesh relation By \cref{lem:almost-split}, the pair~$(x,x')$ is a positive mutation if and only~$X\notin \add(\susp T)$, that is, if and only if~$x$ is not an initial variable.
+Thus there is precisely one mesh relation starting at~$x$.
+By \cref{lem:almost-split}, the pair~$(x,x')$ is a positive mutation if and only~$X\notin \add(\susp T)$, that is, if and only if~$x$ is not an initial variable.
 \end{proof}

### 2019-09-10 thirdPaper/draft/typeConeAssociahedra.tex
typo

@@
 Fix an essential complete simplicial fan~$\Fan$ in~$\R^n$.
-Let~$\b{G}$ the $N \times n$-matrix whose rows are the rays of~$\Fan$ and let~$\b{K}$ be a $(N-n) \times N$-matrix that spans the left kernel of~$\b{G}$ (\ie $\b{K}\b{G} = 0$).
+Let~$\b{G}$ be the $N \times n$-matrix whose rows are the rays of~$\Fan$ and let~$\b{K}$ be a $(N-n) \times N$-matrix that spans the left kernel of~$\b{G}$ (\ie $\b{K}\b{G} = 0$).
 For any height vector~$\b{h} \in \R^N$, we define the polytope

### 2019-10-24 thirdPaper/draft/typeConeAssociahedra.tex
coefficients cluster algebras

@@
 \[
-R_{\b{\ell}}(\B_\circ) \eqdef \Bigset{\b{z} \in \R^{\principalVariables}}{\b{z} \ge 0 \text{ and } \b{z}_x + \b{z}_{x'} - \sum_{y \in \principalVariables} \alpha_{x,x',y} \, \b{z}_{y} = \b{\ell}_{\{x,x'\}} \text{ for all } \{x,x'\} \in \meshes}
+R_{\b{\ell}}(\B_\circ) \eqdef \Bigset{\b{z} \in \R^{\principalVariables}}{\b{z} \ge 0 \text{ and } \b{z}_x + \b{z}_{x'} - \sum_{y \in \principalVariables} \coefficient[y][x][x'] \, \b{z}_{y} = \b{\ell}_{\{x,x'\}} \text{ for all } \{x,x'\} \in \meshes}
 \]
@@
 Here, $\meshes$ denotes the set of all pairs~$\{x,x'\}$ related by non-initial mesh mutations (\cref{def:meshMutation}), and~$\principalVariables$ the set of cluster variables.
-For $\{x,x'\} \in \meshes$ and $y \in \principalVariables$, the coefficient $\alpha_{x,x',y}$ is defined as follows: $\alpha_{x,x',y}$ is set to be~$|b_{xy}|$ if~$y\in X\cap X'$ and $0$ otherwise, where~$X,X'$ are any two clusters such that~$X \ssm \{x\} = X' \ssm \{x'\}$.
-By the unique exchange relation property, the coefficients~$\alpha_{x,x',y}$ do not depend on the specific choice of clusters~$X,X'$.
+For $\{x,x'\} \in \meshes$ and $y \in \principalVariables$, the coefficient $\coefficient[y][x][x']$ is defined as follows: $\coefficient[y][x][x']$ is set to be~$|b_{xy}|$ if~$y\in X\cap X'$ and $0$ otherwise, where~$X,X'$ are any two clusters such that~$X \ssm \{x\} = X' \ssm \{x'\}$.
+By the unique exchange relation property, the coefficients~$\coefficient[y][x][x']$ do not depend on the specific choice of clusters~$X,X'$.
 
@@
 
-For~$\{x,x'\} \in \meshes$ and~$y \in \principalVariables$, we denote by~$\alpha_{x,x',y}$ the coefficient of~$\gvectorFull{\B_\circ}{y}$ in the linear dependence between the $\b{g}$-vectors~$\gvectorFull{\B_\circ}{x}$ and~$\gvectorFull{\B_\circ}{x'}$.
-In other words, according to \cref{lem:dependenceMesh}, if~${(\B, \cluster)}$ and~${(\B', \cluster')}$ are two adjacent seeds with~$\cluster \ssm \{x\} = \cluster' \ssm \{x'\}$, we have~$\alpha_{x,x',y} = |b_{xy}|$ for~$y \in \cluster \cap \cluster'$ and~$\alpha_{x,x',y} = 0$ otherwise.
+For~$\{x,x'\} \in \meshes$ and~$y \in \principalVariables$, we denote by~$\coefficient[y][x][x']$ the coefficient of~$\gvectorFull{\B_\circ}{y}$ in the linear dependence between the $\b{g}$-vectors~$\gvectorFull{\B_\circ}{x}$ and~$\gvectorFull{\B_\circ}{x'}$.
+In other words, according to \cref{lem:dependenceMesh}, if~${(\B, \cluster)}$ and~${(\B', \cluster')}$ are two adjacent seeds with~$\cluster \ssm \{x\} = \cluster' \ssm \{x'\}$, we have~$\coefficient[y][x][x'] = |b_{xy}|$ for~$y \in \cluster \cap \cluster'$ and~$\coefficient[y][x][x'] = 0$ otherwise.
 The following statement will be shown in \cref{corollary:proof of prop meshMutations}.
@@
 \[
-R_\b{\ell}(T) \eqdef \Bigset{\b{z} \in \R^{\Delta(n)}}{\begin{array}{l} \b{z} \ge 0 \quad\text{ and }\quad \b{z}_{(a,b)} = 0 \text{ for all } (a,b) \in T \quad\text{ and }\quad \\ \b{z}_{(a,b)} + \b{z}_{(a-1,b-1)} - \b{z}_{(a,b-1)} - \b{z}_{(a-1,b)} = \b{\ell}_{(a,b)} \text{ for all } (a,b) \notin T \end{array}}
+R_\b{\ell}(T) \eqdef \Bigset{\b{z} \in \R^{\Delta(n)}}{\begin{array}{l} \b{z} \ge 0 \quad\text{ and }\quad \b{z}_{(a,a+1)} = 0 \text{ for all } a \in \Z/(n+3)\Z \quad\text{ and }\quad \\ \b{z}_{(a,b)} + \b{z}_{(a-1,b-1)} - \b{z}_{(a,b-1)} - \b{z}_{(a-1,b)} = \b{\ell}_{(a,b)} \text{ for all } (a,b) \notin T \end{array}}
 \]

### 2019-10-31 thirdPaper/FPSAC/typeConeAssociahedraFPSAC.tex
FPSAC

%% if you are submitting an initial manuscript then you should have submission as an option here
%% if you are submitting a revised manuscript then you should have revision as an option here
%% otherwise options taken by the article class will be accepted
\documentclass[submission]{FPSAC2020}
%% but DO NOT pass any options (or change anything else anywhere) which alters page size / layout / font size etc

%% note that the class file already loads {amsmath, amsthm, amssymb}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{remark}[theorem]{Remark}

\usepackage{paralist} % special lists
\usepackage{xargs} % commands with optional parameters
\usepackage{ulem}\normalem % special underline
\usepackage{picins/picins}
\graphicspath{{figures/}{figures/diagonals/}{figures/walks/}{figures/tubes/}}
\usepackage{nicefrac}
\usepackage[export]{adjustbox}
\usepackage{tikz}
\usetikzlibrary{matrix}
\makeatletter
\protected\def\tikz@nonactivesemicolon{\ifmmode\mathrel{\mathop\ordinarysemicolon}\else;\fi} 
\makeatother
\usepackage{overpic}
\usepackage{wasysym, pifont}

% math special letters
\newcommand{\R}{\mathbb{R}} % reals
\newcommand{\Q}{\mathbb{Q}} % rationals
\newcommand{\N}{\mathbb{N}} % naturals
\newcommand{\Z}{\mathbb{Z}} % integers
\newcommand{\C}{\mathbb{C}} % complex
\newcommand{\f}[1]{{\mathfrak{#1}}} % mathfrak letters
%\newcommand{\cal}[1]{{\mathcal{#1}}} % call letters
\renewcommand{\b}[1]{{\boldsymbol{#1}}} % bold letters

% math commands
\newcommand{\set}[2]{\left\{ #1 \;\middle|\; #2 \right\}} % set notation
\newcommand{\bigset}[2]{\big\{ #1 \;|\; #2 \big\}} % big set notation
\newcommand{\biggset}[2]{\bigg\{ #1 \;\bigg|\; #2 \bigg\}} % bigg set notation
\newcommand{\Bigset}[2]{\Big\{ #1 \;\Big|\; #2 \Big\}} % Big set notation
\newcommand{\ssm}{\smallsetminus} % small set minus
\newcommand{\dotprod}[2]{\langle \, #1 \; | \; #2 \, \rangle} % dot product
\newcommand{\symdif}{\,\triangle\,} % symmetric difference
\newcommand{\one}{{1\!\!1}} % the all one vector
\newcommand{\eqdef}{\mbox{\,\raisebox{0.2ex}{\scriptsize\ensuremath{\mathrm:}}\ensuremath{=}\,}} % :=
\newcommand{\defeq}{\mbox{~\ensuremath{=}\raisebox{0.2ex}{\scriptsize\ensuremath{\mathrm:}} }} % =:
\newcommand{\interior}[1]{\mathring{#1}} % interior

% others
\newcommand{\ie}{\textit{i.e.}~} % id est
\newcommand{\eg}{\textit{e.g.}~} % exempli gratia
\newcommand{\Eg}{\textit{E.g.}~} % Exempli gratia
\newcommand{\aka}{\textit{a.k.a.}~} % also known as
\newcommand{\viceversa}{\textit{vice versa}} % exempli gratia
\newcommand{\red}{\color{red}} % red command
\newcommand{\blue}{\color{blue}} % blue command
\newcommand{\green}{\color{green}} % green command
\newcommand{\defn}[1]{\uline{\textit{#1}}} % emphasis of a definition
\newcommand{\parabf}[1]{\noindent\textbf{#1}.} % paragraph bf

% type cones
\newcommandx{\Fan}[1][1=F]{\mathcal{#1}} % fan
\newcommandx{\ray}[1][1=r]{\b{#1}} % ray
\newcommandx{\rays}[1][1=R]{\b{#1}} % rays
\newcommand{\gvector}[1]{\b{g}(#1)} % g-vector of #1
\newcommand{\gvectorFull}[2]{\b{g}(#1,#2)} % g-vector of #2 wrt #1
\newcommand{\gvectors}[1]{\b{g}(#1)} % g-vectors of #1
\newcommand{\gvectorsFull}[2]{\b{g}(#1,#2)} % g-vectors of #2 wrt #1
\newcommandx{\gvectorFan}[1][1=\quiver]{\mathcal{F}(#1)} % g-vector fan
\newcommand{\typeCone}{\mathbb{TC}} % type cone
\newcommandx{\coefficient}[3][1={\ray[s]}, 2=\ray, 3=\ray']{\alpha_{#2,#3}(#1)} 
\newcommandx{\Asso}[2][1=n,2={}]{\mathsf{Asso}^{#2}(#1)} % associahedron
\newcommandx{\clusterAlgebra}[1][1=\B_\circ]{\mathcal{A}\!\left(#1\right)} % cluster algebra
\newcommand{\seed}{\Sigma} % a cluster
\newcommand{\cluster}{X} % a cluster
\newcommandx{\clusters}{X} % all clusters
\newcommand{\B}{B} % b-matrix
\newcommandx{\meshes}[1][1=\B_\circ]{\mathcal{M}(#1)} % meshes
\newcommandx{\variables}[1][1=\B_\circ]{\mathcal{V}(#1)} % all variables
\newcommand{\coefficients}{\mathrm{P}} % a coefficients tuple
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{\node[shape=circle, draw, inner sep=1.5pt, scale=.7] (char) {#1};}}
\newcommand{\compactVectorD}[2]{\begin{bmatrix} #1 \\ #2 \end{bmatrix}}
\newcommand{\compactVectorT}[3]{\begin{bmatrix} #1 \\[-.1cm] #2 \\[-.1cm] #3 \end{bmatrix}}
\newcommand{\quiver}{\bar Q} % quiver
\newcommand{\blossom}{^\text{\ding{96}}} % blossom
\newcommandx{\walks}[1][1=\quiver]{\mathcal{W}(#1)} % walks
\newcommandx{\strings}[1][1=\quiver]{\mathcal{S}(#1)} % strings
\newcommand{\hL}{\text{\rotatebox[origin=c]{180}{\checked}}}
\newcommand{\hR}{\text{\rotatebox[origin=c]{180}{\reflectbox{\checked}}}}
\newcommand{\cL}{\text{\reflectbox{\checked}}}
\newcommand{\cR}{\text{\checked}}
\newcommand{\hh}[1]{\hL#1\hR} % hook - hook
\newcommand{\cc}[1]{\cL#1\cR} % cohook - cohook
\newcommand{\hc}[1]{\hL#1\cR} % hook - cohook
\newcommand{\ch}[1]{\cL#1\hR} % cohook - hook
\renewcommand{\top}{\mathrm{top}} % top
\newcommand{\bottom}{\mathrm{bot}} % bottom
\newcommandx{\NKC}[1][1=\quiver]{\mathcal{NK}(#1)} % non-kissing complex
\newcommand{\peaks}[1]{\mathsf{peaks}(#1)} % peaks
\newcommand{\deeps}[1]{\mathsf{deeps}(#1)} % deeps
\newcommand{\multiplicityVector}{\b{m}} % multiplicity vector
\newcommand{\ground}{V} % ground set
\newcommandx{\graphG}[1][1=G]{#1} % graph
\newcommandx{\tube}[1][1=t]{#1} % tube
\newcommandx{\tubes}[1][1=\graphG]{\mathcal{T}(#1)} % all tubes
\newcommandx{\tubing}[1][1=T]{#1} % tubing
\newcommand{\connectedComponents}{\kappa} % connected components
\newcommand{\nestedComplex}{\mathcal{N}} % nested complex
\newcommand{\nonDisconnecting}{\mathrm{nd}} % non-disconnecting vertices

%% define your title in the usual way
\title{On type cones of $\b{g}$-vector fans}

%% define your authors in the usual way
%% use \addressmark{1}, \addressmark{2} etc for the institutions, and use \thanks{} for contact details
\author[Arnau Padrol, Yann Palu, Vincent Pilaud and Pierre-Guy Plamondon]{
	Arnau Padrol\thanks{\href{mailto:arnau.padrol@imj-prg.fr}{arnau.padrol@imj-prg.fr}. Supp. by ANR grant CAPPS~(17\,CE40\,0018).}\addressmark{1},
	\stepcounter{footnote}
	Yann Palu\thanks{\href{mailto:yann.palu@u-picardie.fr}{yann.palu@u-picardie.fr}. Supp. by ANR grant SC3A~(15\,CE40\,0004\,01).}\addressmark{2}, \\
	Vincent Pilaud\thanks{\href{mailto:vincent.pilaud@lix.polytechnique.fr}{vincent.pilaud@lix.polytechnique.fr}. Supp. by ANR SC3A~15\,CE40\,0004\,01 and CAPPS~17\,CE40\,0018.}\addressmark{3}
	\and
	Pierre-Guy Plamondon\thanks{\href{mailto:pierre-guy.plamondon@math.u-psud.fr}{pierre-guy.plamondon@math.u-psud.fr}. Supp. by ANR grant SC3A~(15\,CE40\,0004\,01).}\addressmark{4},
}

%% then use \addressmark to match authors to institutions here
\address{
	\addressmark{1} Institut de Mathématiques de Jussieu - Paris Rive Gauche, Sorbonne Universit\'e, Paris, France \\
	\addressmark{2} LAMFA, Universit\'e Picardie Jules Verne, Amiens, France \\
	\addressmark{3} CNRS \& LIX, \'Ecole Polytechnique, Palaiseau, France \\
	\addressmark{4} Laboratoire de Math\'ematiques d'Orsay, CNRS, Universit\'e Paris-Saclay, France
}

%% put the date of submission here
\received{\today}

%% leave this blank until submitting a revised version
%\revised{}

%% put your English abstract here, or comment this out if you don't have one yet
%% please don't use custom commands in your abstract / resume, as these will be displayed online
%% likewise for citations -- please don't use \cite, and instead write out your citation as something like (author year)
\abstract{
We study the type cone (\ie the space of all polytopal realizations) of $\b{g}$-vector fans of finite type cluster-like complexes (finite type cluster complexes, non-kissing complexes of gentle algebra, and graphical nested complexes). We show that this cone is often simplicial, which explains an elegant ``kinematic'' construction of the associahedron as a section of a high dimensional positive orthant by certain affine subspaces parametrized by a small dimensional positive orthant.
}

%% put your French abstract here, or comment this out if you don't have one
\resume{
Nous \'etudions le type cone (\ie l'espace de toutes les r\'ealisations polytopales) des \'eventails de $\b{g}$-vecteurs de complexes de type amassés (complexes amassés de type fini, complexes platoniques d'alg\`ebres aimables, et complexes emboit\'es graphi\-ques). Nous montrons que ce cone est souvent simplicial, ce qui explique une \'el\'egante construction ``cin\'ematique'' de l'associa\`edre comme section d'un orthant positif de grande dimension par certains sous-espaces affines param\`etrés par un orthant positif de petite dimension.
}

%% put your keywords here, or comment this out if you don't have them yet
\keywords{Fans $\cdot$ cluster algebras $\cdot$ non-kissing complex $\cdot$ graph associahedra}

%% you can include your bibliography however you want, but using an external .bib file is STRONGLY RECOMMENDED and will make the editor's life much easier
%% regardless of how you do it, please use numerical citations, ie. [xx, yy] in the text

%% this sample uses biblatex, which (among other things) takes care of URLs in a more flexible way than bibtex
%% but you can use bibtex if you want
\usepackage[backend=bibtex, firstinits=true, maxbibnames=99]{biblatex}
\DeclareFieldFormat[article,inbook,incollection,inproceedings,patent,thesis,unpublished]{title}{\textit{#1}\isdot}
\renewbibmacro{in:}{}
\addbibresource{typeConeAssociahedraFPSAC.bib}
%% note the \printbibliography command at the end of the file which goes with these biblatex commands

\begin{document}

\maketitle
%% note that you DO NOT have to put your abstract here -- it is generated by \maketitle and the \abstract and \resume commands above

\section{Introduction}

This paper focuses on a surprising construction of the associahedron that recently appeared in mathematical physics.
Motivated by the prediction of the behavior of scattering particles, N.~Arkani-Hamed, Y.~Bai, S.~He, and G.~Yan recently described in~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} the kinematic associahedron.
It is a class of polytopal realizations of the classical associahedron obtained as sections of a high-dimensional positive orthant with well-chosen affine subspaces.
This construction provides a large degree of freedom in the choice of the parameters defining these affine subspaces, and actually produces all polytopes whose normal fan is affinely equivalent to that of J.-L.~Loday's associahedron~\cite{Loday} (see \cref{subsec:associahedra}).
These realizations were then extended by V.~Bazier-Matte, G.~Douville, K.~Mousavand, H.~Thomas and E.~Y\i ld\i r\i m~\cite{BazierMatteDouvilleMousavandThomasYildirim} in the context of finite type cluster algebras (see \cref{subsec:generalizedAssociahedra}) using tools from quiver representation theory.

We revisit, extend and explore further this construction using a reversed approach.
Given a complete simplicial fan~$\Fan$, we consider the space~$\typeCone(\Fan)$ of all its polytopal realizations.
This space was called type cone in~\cite{McMullen-typeCone} and deformation cone in~\cite{Postnikov}, who studied the case when~$\Fan$ is the braid arrangement leading to the rich theory of generalized permutahedra.
The type cone is known to be a polyhedral cone defined by a collection of inequalities corresponding to the linear dependences among the rays of~$\Fan$ contained in pairs of adjacent maximal cones of~$\Fan$ (see \cref{def:typeCone}).
Our approach is based on an elementary but powerful observation: for any fan~$\Fan$, all polytopal realizations of~$\Fan$ can be described as sections of a high dimensional positive orthant with a collection of affine subspaces parametrized by the type cone~$\typeCone(\Fan)$ (see \cref{prop:alternativePolytopalRealization}); if moreover the type cone~$\typeCone(\Fan)$ is a simplicial cone, it leads to a simple parametrization of all polytopal realizations of~$\Fan$ by a positive orthant corresponding to the facets of the type cone~$\typeCone(\Fan)$ (see \cref{coro:simplicialTypeCone}).
To prove that the type cone~$\typeCone(\Fan)$ is simplicial, we just need to identify which pairs of adjacent maximal cones of~$\Fan$ correspond to the facets of~$\typeCone(\Fan)$ and to show that the corresponding linear dependences among their rays positively span the linear dependence among the rays of any pair of adjacent maximal cones of~$\Fan$.
When applied to cluster algebras (see \cref{subsec:generalizedAssociahedra}), this yields all polytopal realizations of the $\b{g}$-vector fans, revisiting and extending results of~\cite{BazierMatteDouvilleMousavandThomasYildirim}.

This new perspective has several advantages, as our proof uniformly applies to \emph{any initial seed} (acyclic or not), \emph{any finite type cluster algebra} (simply-laced or not), and \emph{any positive real-valued parameters} (rational or not). In contrast, note that the result of~\cite{BazierMatteDouvilleMousavandThomasYildirim} is first proved for acyclic initial seeds in simply-laced cluster algebras for integer parameters, and then extended by a technical folding argument to all finite types and by an approximation argument to arbitrary real-valued parameters.
These advantages of the type cone approach all follow from one essential feature: it enables to completely separate the algebraic aspects from the geometric aspects of the problem.

Besides revisiting the construction of~\cite{ArkaniHamedBaiHeYan, BazierMatteDouvilleMousavandThomasYildirim} and extending it to any initial seed, our type cone approach is also successful when applied to the $\b{g}$-vector fans of other families of generalizations of the associahedron.
In the present paper, we explore specifically the non-kissing complexes of gentle algebras introduced in~\cite{PaluPilaudPlamondon-nonkissing} (see \cref{subsec:gentleAssociahedra}) and the graphical nested complexes studied in~\cite{CarrDevadoss, Postnikov, FeichtnerSturmfels, Zelevinsky} (see \cref{subsec:graphAssociahedra}).

Many details and all proofs are omitted in this extended abstract for space reason, but a complete treatment can be found in~\cite{PadrolPaluPilaudPlamondon}.
In particular, the quiver representation theory is an iceberg in this abstract: while useful for intuition and essential for certain proofs (\eg \cref{thm:meshMutations}), it is mostly hidden and only appears in the Auslander-Reiten quivers used to represent the inequalities of the type cones (in \cref{fig:labelFacetDefiningInequalititiesAsso,fig:labelFacetDefiningInequalititiesCA,fig:labelFacetDefiningInequalititiesNKC}).

\section{Type cone of a fan}
\label{sec:typeCone}

Fix an essential complete simplicial fan\footnote{A \defn{polyhedral cone} is the positive span of finitely many vectors or equivalently, the intersection of finitely many closed linear half-spaces. The \defn{faces} of a cone are its intersections with its supporting hyperplanes. A \defn{fan}~$\Fan$ is a set of polyhedral cones such that any face of a cone of~$\Fan$ belongs to~$\Fan$, and any two cones of~$\Fan$ intersect along a face of both. A fan is \defn{essential} if the intersection of its cones is the origin, \defn{complete} if the union of its cones covers~$\R^n$, and \defn{simplicial} if all its cones are generated by dimension many rays.}~$\Fan$ in~$\R^n$. Let~$\b{G}$ the $N \times n$-matrix whose rows are (representative vectors of) the rays of~$\Fan$ and let~$\b{K}$ be a $(N-n) \times N$-matrix that spans the left kernel of~$\b{G}$ (\ie $\b{K}\b{G} = 0$). For any height vector~$\b{h} \in \R^N$, we define the polytope\footnote{A \defn{polytope} is the convex hull of finitely many points or equivalently, a bounded intersection of finitely many closed affine half-spaces.}
\(
P_\b{h} \eqdef \set{\b{x} \in \R^n}{\b{G}\b{x} \le \b{h}}.
\)
Unfortunately, the normal fan\footnote{The \defn{normal cone} of a face~$F$ of a polytope~$P$ is the cone generated by the normal vectors of the facets of~$P$ containing~$F$. The \defn{normal fan} of~$P$ is the set of normal cones of all its faces.} of this polytope~$P_\b{h}$ does not always coincide with the fan~$\Fan$ we started from. The following statement gives a simple characterization of the height vectors~$h$ for which it is the case. It is a reformulation of regularity of triangulations of vector configurations, introduced in the theory of secondary polytopes~\cite{GelfandKapranovZelevinsky}.
We present here a convenient formulation from~\cite{ChapotonFominZelevinsky}.

\begin{proposition}
\label{prop:characterizationPolytopalFan}
Let~$\Fan$ be an essential complete simplicial fan in~$\R^n$. Then the following are equivalent for any height vector~$\b{h} \in \R^N$:
\begin{compactenum}
\item The fan~$\Fan$ is the normal fan of the polytope~$P_\b{h} \eqdef \set{\b{x} \in \R^n}{\b{G}\b{x} \le \b{h}}$.
\item For any two adjacent maximal cones~$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$ of~$\Fan$ with~$\rays \ssm \{\ray\} = \rays' \ssm \{\ray'\}$, we have
\(
{\displaystyle\sum}_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, h_{\ray[s]} > 0,
\)
where
\(
{\displaystyle\sum}_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \ray[s] = 0
\)
is the unique linear dependence among the rays of~$\rays \cup \rays'$ such that~$\coefficient[{\ray[r]}][\rays][\rays'] + \coefficient[{\ray[r]'}][\rays][\rays'] = 2$. 
\end{compactenum}
\end{proposition}

\begin{definition}[\cite{McMullen-typeCone}]
\label{def:typeCone}
The \defn{type cone} of~$\Fan$ is the cone~$\typeCone(\Fan)$ of all polytopal realizations of~$\Fan$:
\begin{align*}
\typeCone(\Fan) & \eqdef \set{\b{h} \in \R^N}{\Fan \text{ is the normal fan of } P_\b{h}} \\
& = \Bigset{\b{h} \in \R^N}{\sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} > 0 \; \begin{array}{l} \text{for any adjacent maximal} \\ \text{cones~$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$ of~$\Fan$} \end{array}}.
\end{align*}
\end{definition}

Note that the type cone is an open cone and contains a linearity subspace of dimension~$n$ (it is invariant by translation in~$\b{G} \R^n$). Therefore, we say that the type cone is \defn{simplicial} when it has precisely $N-n$ facets.

\begin{definition}
An \defn{extremal adjacent pair} of~$\Fan$ is a pair of adjacent maximal cones~$\{\R_{\ge0}\rays, \R_{\ge0}\rays'\}$ of~$\Fan$ such that the corresponding inequality ${\displaystyle\sum}_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} > 0$ in the definition of the type cone~$\typeCone(\Fan)$ actually defines a facet of~$\typeCone(\Fan)$.
In other words, extremal adjacent pairs define the extremal rays of the polar of the closed type cone~$\typeCone(\Fan)$.
\vspace{.2cm}
\end{definition}

\begin{example}
\label{exm:typeCone}
\enlargethispage{.1cm}
Consider the $2$-dimensional fan~$\Fan$ depicted in \cref{fig:typeCone} (left).
% (we will encounter this fan again in \cref{exm:typeConeCoarsenings,exm:typeConeMinkowskiSum,exm:typeConeAsso}).
It has five rays labeled~$1, \dots, 5$ and five maximal cones labeled~$a,\dots, e$.
Its type cone~$\typeCone(\Fan)$ lies in~$\R^5$, but has a $2$-dimensional linearity space.
The five pairs of adjacent maximal cones of~$\Fan$ give rise to following five defining inequalities for~$\typeCone(\Fan)$:
\begin{gather*}
H^>_{ab}: \; \b{h}_1 + \b{h}_3 - \b{h}_2 > 0
\qquad
H^>_{bc}: \; \b{h}_2 + \b{h}_4 - \b{h}_3 > 0
\qquad
H^>_{cd}: \; \b{h}_3 + \b{h}_5 - \b{h}_4 > 0
\\
H^>_{de}: \; \b{h}_1 + \b{h}_4 > 0
\qquad
H^>_{ae}: \; \b{h}_2 + \b{h}_5 > 0,
\end{gather*}
where $H^>_{ij}$ denotes the halfspace defined by the inequality corresponding to the two adjacent maximal cones~$i$ and~$j$.
%Note that the inequalities~$H^>_{ae}$ and~$H^>_{de}$ are redundant, while the other three define facets, so that the extremal adjacent pairs are~$(a,b)$, $(b,c)$ and~$(c,d)$.
For example, the height vector~$(\nicefrac{1}{2}, \nicefrac{3}{4}, \nicefrac{5}{4}, 1, \nicefrac{5}{4})$ belongs to the type cone~$\typeCone(\Fan)$, and the corresponding polytope is represented in \cref{fig:typeCone} (middle).
To represent this type cone, we slice it with a transversal $2$-dimensional affine space. This is the red triangle depicted in \cref{fig:typeCone} (right).

\begin{figure}[t]
	\centerline{{\includegraphics[scale=1]{typeConeFan}} \quad {\includegraphics[scale=1]{typeConePolytope}} \quad \raisebox{.5cm}{\includegraphics[scale=.45]{typeCone}}}
	\caption{A $2$-dimensional fan~$\Fan$ with five rays $1, \dots, 5$ and five maximal cones~$a, \dots, e$ (left), its polytopal realization corresponding to the height vector~$(\nicefrac{1}{2}, \nicefrac{3}{4}, 1, 1, \nicefrac{5}{4})$ (middle), and a $2$-dimensional slice of the type cone~$\typeCone(\Fan)$ (right).}
	\label{fig:typeCone}
\end{figure}
\end{example}

\begin{remark}
All fans considered in \cref{sec:gvectorFans} have the \defn{unique exchange relation property}: the linear dependence ${\displaystyle\sum}_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \ray[s] = 0$ only depends on the exchanged rays~$\ray[r]$ and~$\ray[r]'$, not on the maximal adjacent cones~$\rays$ and~$\rays'$. We then write~$\coefficient[{\ray[s]}][\ray][\ray']$ instead of~$\coefficient[{\ray[s]}][\rays][\rays']$ and we call \defn{extremal adjacent pair} of~$\Fan$ the pairs of exchangeable rays~$\{\ray, \ray'\}$ of~$\Fan$ such that the corresponding inequality ${\displaystyle\sum}_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\ray][\ray'] \, \b{h}_{\ray[s]} > 0$ defines a facet of~$\typeCone(\Fan)$.

\end{remark}

To conclude this section, we consider alternative polytopal realizations of the fan~$\Fan$ and discuss their behavior in the situation when the type cone~$\typeCone(\Fan)$ is simplicial.

\begin{proposition}
\label{prop:alternativePolytopalRealization}
The affine map~$\Psi: \R^n \to \R^N$ defined by~$\Psi(\b{x}) = \b{h} - G\b{x}$ sends the polytope~$P_\b{h} \eqdef \set{\b{x} \in \R^n}{\b{G}\b{x} \le \b{h}}$ to the polytope~$Q_\b{h} \eqdef \set{\b{z} \in \R^N}{\b{K}\b{z} = \b{K}\b{h} \text{ and } \b{z} \ge 0}$.
\end{proposition}

\begin{corollary}
\label{coro:simplicialTypeCone}
Assume that the type cone~$\typeCone(\Fan)$ is simplicial and consider inner normal vectors to its $N-n$ facets. Since all these vectors belong to the left kernel of~$\b{G}$ by \cref{prop:characterizationPolytopalFan}, we can assume that they are the rows of the ${(N-n) \times N}$-matrix~$\b{K}$. Then, for any positive vector~${\b{\ell} \in \R_{>0}^{N-n}}$, the polytope
\(
R_\b{\ell} \eqdef \set{\b{z} \in \R^N}{K\b{z} = \b{\ell} \text{ and } \b{z} \ge 0}
\)
is a realization of the fan~$\Fan$.
Moreover, the polytopes~$R_\b{\ell}$ for~$\b{\ell} \in \R_{>0}^{N-n}$ describe all polytopal realizations of~$\Fan$.
\end{corollary}

\section{Applications to $\b{g}$-vector fans}
\label{sec:gvectorFans}

We now study the type cones of the normal fans of three families generalizing the associahedron constructed in~\cite{Loday}: the generalized associahedra of finite type cluster algebras~\cite{FominZelevinsky-ClusterAlgebrasI, FominZelevinsky-ClusterAlgebrasII, FominZelevinsky-ClusterAlgebrasIV, HohlwegLangeThomas, HohlwegPilaudStella}, the gentle associahedra~\cite{PaluPilaudPlamondon-nonkissing}, and the graph associahedra~\mbox{\cite{CarrDevadoss, Postnikov, FeichtnerSturmfels, Zelevinsky}}.
%All these families contain the classical associahedra~$\Asso[n]$ constructed in~\cite{Loday}.

\subsection{Classical associahedra}
\label{subsec:associahedra}

%We start with the classical associahedron.
A $n$-dimensional \defn{associahedron} is a polytope whose face lattice is the reverse inclusion lattice of dissections (\ie sets of pairwise non-crossing diagonals) of a convex~$(n+3)$-gon.
In particular, its vertices correspond to triangulations of the $(n+3)$-gon and its facets correspond to internal diagonals of the $(n+3)$-gon.
Let~$X(n) \eqdef \set{(a,b)}{0 \le a < b \le n+2}$ (resp.~$Y(n) \eqdef \set{(a,b)}{0 \le a < b-2 \le n}$) denote all (resp.~the internal) diagonals.
The \defn{$\b{g}$-vector} of a diagonal $(a,b) \in X(n)$ is ${\gvector{a,b} \eqdef (n+1) {\displaystyle\sum}_{\,a < \ell < b} \b{e}_\ell - (b-a-1) {\displaystyle\sum}_{\,1 \le \ell \le n+1} \b{e}_\ell}$.
%Note that~$\gvector{a,b} = 0$ if~$(a,b)$ is not internal.
We set~$\gvector{D} \eqdef \set{\gvector{a,b}}{(a,b) \in D}$ for a dissection~$D$.
Recall that:
\begin{compactitem}
\item the set of cones
\(
\gvectorFan[n] \eqdef \bigset{\R_{\ge0} \, \gvectors{D}}{D \text{ dissection of the $(n+3)$-gon}}
\)
forms a complete simplicial fan.
See \cref{fig:lodayFans}\,(left and middle).

\item the fan~$\gvectorFan[n]$ is the normal fan of an associahedron~$\Asso[n]$ constructed \eg in~\cite{Loday}.

\item for any two adjacent triangulations~$T$ and~$T'$ with~${T \ssm \{(a,b)\} = T' \ssm \{(a',b')\}}$ such that~${0 \le a < a' < b < b' \le n+2}$, the linear dependence among the $\b{g}$-vectors of~${T \cup T'}$ is given by
\(
\gvector{a,b} + \gvector{a',b'} = \gvector{a,b'} + \gvector{a',b}.
\)
\end{compactitem}

\smallskip
This provides a redundant description of the type cone of the fan~$\gvectorFan[n]$.

%For~$n \in \N$, we define~$X(n) \eqdef \set{(a,b)}{0 \le a < b \le n+2}$ and $Y(n) \eqdef \set{(a,b)}{0 \le a < b-2 \le n}$.

\begin{corollary}
\label{coro:typeConeAsso}
%Let~$n \in \N$ and~$X(n) \eqdef \set{(a,b)}{0 \le a < b \le n+2}$. 
For any~$n \in \N$, the type cone of the fan~$\gvectorFan[n]$ is given by
\[
\typeCone \big( \gvectorFan[n] \big) = \set{\b{h} \in \R^{X(n)}}{\begin{array}{@{}l@{}} \b{h}_{(0,n+2)} = 0, \qquad\text{and}\qquad \b{h}_{(a,a+1)} = 0 \text{ for all } 0 \le a \le n+1 \\ \b{h}_{(a,b)} \! + \! \b{h}_{(a',b')} \! > \! \b{h}_{(a,b')} \! + \! \b{h}_{(a',b)} \text{ for all } 0 \! \le \! a \! < \! a' \! < \! b \! < \! b' \! \le \! n+2 \end{array}} \!.
\]
\end{corollary}

The next statement, illustrated in \cref{fig:labelFacetDefiningInequalititiesAsso}, gives the facets of the type cone of~$\gvectorFan[n]$.

%\begin{example}
%\label{exm:typeConeAsso}
%The type cone of~$\gvectorFan[2]$ (resp.~$\gvectorFan[3]$) lives in~$\R^5$ (resp.~$\R^9$), has a linearity space of dimension~$2$ (resp.~$3$), and has $3$ (resp.~$6$) facet-defining inequalities described in \cref{prop:extremalExchangeablePairsAsso}.
%We represent these inequalities in red in \cref{fig:labelFacetDefiningInequalititiesAsso}, using incoming and outgoing arrows to distinguish their left and right hand sides.
%For instance, the inequality~$\red \circled{A}$ is given by~$\b{h}_{\includegraphics[scale=.3]{diagonalA1}} + \b{h}_{\includegraphics[scale=.3]{diagonalA3}} > \b{h}_{\includegraphics[scale=.3]{diagonalA2}}$.

%\centerline{
%	\includegraphics[scale=.5]{lodayFan2}
%%	\quad
%%	\includegraphics[scale=.5]{lodayFan3}
%	\quad
%	\begin{tikzpicture}
%		\matrix (m) [matrix of math nodes, row sep=.35cm, column sep=.2cm, nodes={anchor=center, align=center, inner sep=0pt}, ampersand replacement=\&]{
%			\& \;\includegraphics[scale=.7]{diagonalA2} \& \node (b) {\red \circled{B}}; \& \;\includegraphics[scale=.7]{diagonalA4} \& \\
%			\;\includegraphics[scale=.7]{diagonalA1} \& \node (a) {\red \circled{A}}; \& \;\includegraphics[scale=.7]{diagonalA3} \& \node (c) {\red \circled{C}}; \& \;\includegraphics[scale=.7]{diagonalA5} \\};
%		\draw[->] (m-2-1) -- (m-1-2);
%		\draw[->] (m-1-2) -- (m-2-3);
%		\draw[->] (m-2-3) -- (m-1-4);
%		\draw[->] (m-1-4) -- (m-2-5);
%		\draw[red] (a) -- (m-2-1);
%		\draw[red] (a) -- (m-2-3);
%		\draw[red] (a) -- (m-1-2);
%		\draw[red] (b) -- (m-1-2);
%		\draw[red] (b) -- (m-1-4);
%		\draw[red] (b) -- (m-2-3);
%		\draw[red] (c) -- (m-2-3);
%		\draw[red] (c) -- (m-2-5);
%		\draw[red] (c) -- (m-1-4);
%	\end{tikzpicture}
%}
%
%%\begin{center}
%%	\raisebox{-2.9cm}{\includegraphics[scale=.8]{lodayFan2}}
%%	\begin{minipage}{10cm}
%%	\(
%%	\begin{array}{r|cccccc}
%%	\text{diagonals} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalA1}}  & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalA2}} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalA3}} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalA4}} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalA5}} \\[.3cm]
%%	\text{$\b{g}$-vectors} & \compactVectorD{1}{0} & \compactVectorD{0}{1} & \compactVectorD{-1}{1} & \compactVectorD{-1}{0} & \compactVectorD{0}{-1} \\[.6cm]
%%	\text{facet}		& 1 & -1 & 1 & 0 & 0 & \red \circled{A} \\
%%	\text{defining} 	& 0 & 1 & -1 & 1 & 0 & \red \circled{B} \\
%%	\text{inequalities}	& 0 & 0 & 1 & -1 & 1 & \red \circled{C} \\[.2cm]
%%	\end{array}
%%	\)
%%	\\
%%	\hspace*{2.3cm}
%%	\begin{tikzpicture}
%%		\matrix (m) [matrix of math nodes, row sep=.35cm, column sep=.2cm, nodes={anchor=center, align=center, inner sep=0pt}]{
%%			& \;\includegraphics[scale=.7]{diagonalA2} & \node (b) {\red \circled{B}}; & \;\includegraphics[scale=.7]{diagonalA4} & \\
%%			\;\includegraphics[scale=.7]{diagonalA1} & \node (a) {\red \circled{A}}; & \;\includegraphics[scale=.7]{diagonalA3} & \node (c) {\red \circled{C}}; & \;\includegraphics[scale=.7]{diagonalA5} \\};
%%		\draw[->] (m-2-1) -- (m-1-2);
%%		\draw[->] (m-1-2) -- (m-2-3);
%%		\draw[->] (m-2-3) -- (m-1-4);
%%		\draw[->] (m-1-4) -- (m-2-5);
%%		\draw[red] (a) -- (m-2-1);
%%		\draw[red] (a) -- (m-2-3);
%%		\draw[red] (a) -- (m-1-2);
%%		\draw[red] (b) -- (m-1-2);
%%		\draw[red] (b) -- (m-1-4);
%%		\draw[red] (b) -- (m-2-3);
%%		\draw[red] (c) -- (m-2-3);
%%		\draw[red] (c) -- (m-2-5);
%%		\draw[red] (c) -- (m-1-4);
%%	\end{tikzpicture}
%%	\end{minipage}
%%\end{center}
%\end{example}

\begin{proposition}
\label{prop:extremalExchangeablePairsAsso}
Two internal diagonals~$(a,b)$ and~$(a',b')$ of the~$(n+3)$-gon form an extremal exchangeable pair for the fan~$\gvectorFan[n]$ if and only if~$a = a'+1$ and~$b = b'+1$, or the opposite.
\end{proposition}

\begin{corollary}
\label{coro:simplicialTypeConeAsso}
The type cone~$\typeCone \big( \gvectorFan[n] \big)$ is simplicial.
\end{corollary}

Combining \cref{coro:simplicialTypeCone,coro:simplicialTypeConeAsso} and \cref{prop:extremalExchangeablePairsAsso}, we derive the following description of all polytopal realizations of~$\gvectorFan[n]$, recovering all associahedra of~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan}.
%Note that the arguments of~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} were quite different from the present~approach.

\begin{corollary}[{\cite[Sect.~3.2]{ArkaniHamedBaiHeYan}}]
\label{coro:allPolytopalRealizationsAsso}
%Let~$X(n) \eqdef \set{(a,b)}{0 \le a < b \le n+2}$ and $Y(n) \eqdef \set{(a,b)}{0 \le a < b-2 \le n}$.
For any~$n \in \N$ and any~$\b{\ell} \in \R_{>0}^{Y(n)}$, the polytope
\[
R_\b{\ell}(n) \eqdef \set{\b{z} \in \R^{X(n)}}{\begin{array}{@{}l@{}} \b{z} \ge 0, \quad \b{z}_{(0,n+2)} = 0 \quad\text{and}\quad \b{z}_{(a,a+1)} = 0 \text{ for all } 0 \le a \le n+1 \\ \b{z}_{(a,b-1)} + \b{z}_{(a+1,b)} - \b{z}_{(a,b)} - \b{z}_{(a+1,b-1)} = \b{\ell}_{(a,b)} \text{ for all } (a,b) \in Y(n) \end{array}}
\]
is an $n$-dimensional associahedron, whose normal fan is~$\gvectorFan[n]$.
Moreover, the polytopes~$R_\b{\ell}(n)$ for~$\b{\ell} \in \R_{>0}^{Y(n)}$ describe all polytopal realizations of the fan~$\gvectorFan[n]$.
\end{corollary}

\begin{figure}[t]
	\centerline{
	\raisebox{.5cm}{\begin{overpic}[scale=.5]{lodayFan2} \put(0,105){$\boxed{n=2}$} \end{overpic}}
	\hspace{.5cm}
	\begin{overpic}[scale=.5]{lodayFan3} \put(-10,93){$\boxed{n=3}$} \end{overpic}
	\hspace{.5cm}
	\raisebox{.35cm}{\begin{overpic}[scale=.5]{clusterFanA}
		\put(35,33){${\scriptstyle x_1}$}
		\put(47,54){${\scriptstyle x_2}$}
		\put(59,33){${\scriptstyle x_3}$}
		\put(70,37){$\frac{x_2 + x_3}{x_1}$}
		\put(22,18){$\frac{x_1 + x_3}{x_2}$}
		\put(29,62){$\frac{x_1 + x_2}{x_3}$}
		\put(80,57){$\frac{x_1 + x_2 + x_3}{x_1 x_3}$}
		\put(35,-7){$\frac{x_1 + x_2 + x_3}{x_1 x_2}$}
		\put(-10,57){$\frac{x_1 + x_2 + x_3}{x_2 x_3}$}
%		\put(34,49){$x_1$}
%		\put(57,61){$x_2$}
%		\put(57,36){$x_3$}
%		\put(68,33){$\frac{x_2 + x_3}{x_1}$}
%		\put(17,36){$\frac{x_1 + x_3}{x_2}$}
%		\put(44,74){$\frac{x_1 + x_2}{x_3}$}
%		\put(90,49){$\frac{x_1 + x_2 + x_3}{x_1 x_3}$}
%		\put(7,12){$\frac{x_1 + x_2 + x_3}{x_1 x_2}$}
%		\put(7,84){$\frac{x_1 + x_2 + x_3}{x_2 x_3}$}
	\end{overpic}}
	}
	\caption{The fans~$\gvectorFan[2]$, $\gvectorFan[3]$ and~$\gvectorFan[\B_\circ]$. The two right $3$-dimensional fans are intersected with the sphere and stereographically projected from the direction~$(-1,-1,-1)$.}
	\label{fig:lodayFans}
	\vspace*{-.2cm}
\end{figure}

\begin{figure}
	\centerline{
%	\begin{minipage}[b]{9cm}
%	\begin{center}
%	${\red \circled{B}}: \; \b{h}_{\includegraphics[scale=.3]{diagonalA2}} + \b{h}_{\includegraphics[scale=.3]{diagonalA4}} > \b{h}_{\includegraphics[scale=.3]{diagonalA3}}$	
%	\\[.1cm]
%	${\red \circled{A}}: \; \b{h}_{\includegraphics[scale=.3]{diagonalA1}} + \b{h}_{\includegraphics[scale=.3]{diagonalA3}} > \b{h}_{\includegraphics[scale=.3]{diagonalA2}}$
%	\qquad
%	${\red \circled{C}}: \; \b{h}_{\includegraphics[scale=.3]{diagonalA3}} + \b{h}_{\includegraphics[scale=.3]{diagonalA5}} > \b{h}_{\includegraphics[scale=.3]{diagonalA4}}$
%	\\
	\begin{tikzpicture}
		\matrix (m) [matrix of math nodes, row sep=.35cm, column sep=.2cm, nodes={anchor=center, align=center, inner sep=0pt}, ampersand replacement=\&]{
			$\!\!\boxed{n=2}\!\!$ \\
			\& \;\includegraphics[scale=.7]{diagonalA2} \& \node (b) {\red \circled{B}}; \& \;\includegraphics[scale=.7]{diagonalA4} \& \\
			\;\includegraphics[scale=.7]{diagonalA1} \& \node (a) {\red \circled{A}}; \& \;\includegraphics[scale=.7]{diagonalA3} \& \node (c) {\red \circled{C}}; \& \;\includegraphics[scale=.7]{diagonalA5} \\};
		\draw[->] (m-3-1) -- (m-2-2);
		\draw[->] (m-2-2) -- (m-3-3);
		\draw[->] (m-3-3) -- (m-2-4);
		\draw[->] (m-2-4) -- (m-3-5);
		\draw[red, -<] (a) -- (m-3-1);
		\draw[red, -<] (a) -- (m-3-3);
		\draw[red, ->] (a) -- (m-2-2);
		\draw[red, -<] (b) -- (m-2-2);
		\draw[red, -<] (b) -- (m-2-4);
		\draw[red, ->] (b) -- (m-3-3);
		\draw[red, -<] (c) -- (m-3-3);
		\draw[red, -<] (c) -- (m-3-5);
		\draw[red, ->] (c) -- (m-2-4);
	\end{tikzpicture}
%	\end{center}
%	\end{minipage}
%	\hspace{-.5cm}
	\quad
	\begin{tikzpicture}
		\matrix (m) [matrix of math nodes, row sep=.35cm, column sep=.2cm, nodes={anchor=center, align=center, inner sep=0pt}, ampersand replacement=\&]{
			$\!\!\boxed{n=3}\!\!$ \&\& \;\includegraphics[scale=.7]{diagonalB3} \& \node (c) {\red \circled{C}}; \& \;\includegraphics[scale=.7]{diagonalB7} \&\& \\
			\& \;\includegraphics[scale=.7]{diagonalB2} \& \node (b) {\red \circled{B}}; \& \;\includegraphics[scale=.7]{diagonalB5} \& \node (e) {\red \circled{E}}; \& \;\includegraphics[scale=.7]{diagonalB8} \& \\
			\;\includegraphics[scale=.7]{diagonalB1} \& \node (a) {\red \circled{A}}; \& \;\includegraphics[scale=.7]{diagonalB4} \& \node (d) {\red \circled{D}}; \& \;\includegraphics[scale=.7]{diagonalB6} \& \node (f) {\red \circled{F}}; \& \;\includegraphics[scale=.7]{diagonalB9} \\};
		\draw[->] (m-3-1) -- (m-2-2);
		\draw[->] (m-2-2) -- (m-1-3);
		\draw[->] (m-2-2) -- (m-3-3);
		\draw[->] (m-1-3) -- (m-2-4);
		\draw[->] (m-3-3) -- (m-2-4);
		\draw[->] (m-2-4) -- (m-1-5);
		\draw[->] (m-2-4) -- (m-3-5);
		\draw[->] (m-1-5) -- (m-2-6);
		\draw[->] (m-3-5) -- (m-2-6);
		\draw[->] (m-2-6) -- (m-3-7);
		\draw[red, -<] (a) -- (m-3-1);
		\draw[red, -<] (a) -- (m-3-3);
		\draw[red, ->] (a) -- (m-2-2);
		\draw[red, -<] (b) -- (m-2-2);
		\draw[red, -<] (b) -- (m-2-4);
		\draw[red, ->] (b) -- (m-1-3);
		\draw[red, ->] (b) -- (m-3-3);
		\draw[red, -<] (c) -- (m-1-3);
		\draw[red, -<] (c) -- (m-1-5);
		\draw[red, ->] (c) -- (m-2-4);
		\draw[red, -<] (d) -- (m-3-3);
		\draw[red, -<] (d) -- (m-3-5);
		\draw[red, ->] (d) -- (m-2-4);
		\draw[red, -<] (e) -- (m-2-4);
		\draw[red, -<] (e) -- (m-2-6);
		\draw[red, ->] (e) -- (m-1-5);
		\draw[red, ->] (e) -- (m-3-5);
		\draw[red, -<] (f) -- (m-3-5);
		\draw[red, -<] (f) -- (m-3-7);
		\draw[red, ->] (f) -- (m-2-6);
	\end{tikzpicture}
	}
	\caption{Facet-defining inequalities of the type cone~$\typeCone \big( \gvectorFan[n] \big)$. See \cref{prop:extremalExchangeablePairsAsso}. Each circled red letter gives an inequality with left (resp.~right) hand side given by the incoming (resp.~outgoing) arrows. For instance, the inequality~$\red \textcircled{\scriptsize A}$ is~$\b{h}_{\protect\includegraphics[scale=.3]{diagonalA1}} + \b{h}_{\protect\includegraphics[scale=.3]{diagonalA3}} > \b{h}_{\protect\includegraphics[scale=.3]{diagonalA2}}$.}
	\label{fig:labelFacetDefiningInequalititiesAsso}
	\vspace*{-.4cm}
\end{figure}

\subsection{Cluster fan and generalized associahedra}
\label{subsec:generalizedAssociahedra}

We now consider finite type cluster algebras, defined by S.~Fomin and A.~Zelevinsky in~\cite{FominZelevinsky-ClusterAlgebrasI, FominZelevinsky-ClusterAlgebrasII}.
We skip the technical definitions and refer to the original papers for details.
We fix an initial exchange matrix~$\B_\circ$ (acyclic or not) of finite type and denote by~$\clusterAlgebra$ the corresponding cluster algebra with principal coefficients, and by~$\variables$ its cluster variables. We denote by~$\gvectorFull{\B_\circ}{x}$ the \defn{$\b{g}$-vector} of a cluster variable~$x \in \variables$ as defined in~\cite{FominZelevinsky-ClusterAlgebrasIV}, and we set~$\gvectorFull{\B_\circ}{\cluster} \eqdef \set{\gvectorFull{\B_\circ}{x}}{x \in \cluster}$ for a cluster~$\cluster$ of~$\clusterAlgebra$. Recall~that:
\begin{compactenum}
\item the set of cones
\(
\bigset{\R_{\ge0} \, \gvectorsFull{\B_\circ}{\cluster}}{\cluster \text{ cluster of } \clusterAlgebra \!},
\)
together with all their faces, forms a complete simplicial fan~$\gvectorFan[\B_\circ]$, called the \defn{cluster fan} of~$\B_\circ$.
See \cref{fig:lodayFans}.

\item the cluster fan is the normal fan of a polytope~$\Asso[\B_\circ]$, called \defn{generalized associa}\-\defn{hedron}, constructed for bipartite (resp.~acyclic, resp.~arbitrary) initial exchange matrices in~\cite{ChapotonFominZelevinsky} (resp.~\cite{HohlwegLangeThomas}, resp.~\cite{HohlwegPilaudStella}).

\item for any two adjacent seeds~${(\B, \cluster)}$ and~${(\B', \cluster')}$ in $\clusterAlgebra$ with~$\cluster \ssm \{x\} = \cluster' \ssm \{x'\}$, the $\b{g}$-vectors of~$\cluster \cup \cluster'$ with respect to~$\B_\circ$ satisfy one of the two linear dependences
\[
\smash{\gvectorFull{\B_\circ}{x} + \gvectorFull{\B_\circ}{x'} = \!\!\!\! \sum_{\substack{y \in \cluster \cap \cluster' \\ b_{xy} < 0}} \!\!\! -b_{xy} \, \gvectorFull{\B_\circ}{y}
\quad\text{or}\quad
\gvectorFull{\B_\circ}{x} + \gvectorFull{\B_\circ}{x'} = \!\!\!\! \sum_{\substack{y \in \cluster \cap \cluster' \\ b_{xy} > 0}} \!\!\! b_{xy} \, \gvectorFull{\B_\circ}{y}.}
\]
\end{compactenum}

This provides a redundant description of the type cone of the cluster fan~$\gvectorFan[\B_\circ]$.
Denoting by~$\b{n}(\B_\circ, x, x')$ the vector whose coefficients are given by the appropriate linear dependence above, we obtain the following statement.

\begin{corollary}
\label{coro:typeConeCA}
For any finite type exchange matrix~$\B_\circ$, the type cone of~$\gvectorFan[\B_\circ]$ is given by
\[
\typeCone \big( \gvectorFan[\B_\circ] \big) = \bigset{\b{h} \in \R^{\variables}}{\dotprod{\b{n}(\B_\circ, x, x')}{\b{h}} > 0 \text{ for any exchangeable variables } x, x'}.
\]
\end{corollary}

%%\parpic(7cm,6cm)(10pt, 140pt)[r][b]{
%%	\begin{overpic}[scale=.5]{clusterFanA}
%%		\put(34,49){$x_1$}
%%		\put(57,61){$x_2$}
%%		\put(57,36){$x_3$}
%%		\put(68,33){$\frac{x_2 + x_3}{x_1}$}
%%		\put(17,36){$\frac{x_1 + x_3}{x_2}$}
%%		\put(44,74){$\frac{x_1 + x_2}{x_3}$}
%%		\put(90,49){$\frac{x_1 + x_2 + x_3}{x_1 x_3}$}
%%		\put(7,12){$\frac{x_1 + x_2 + x_3}{x_1 x_2}$}
%%		\put(7,84){$\frac{x_1 + x_2 + x_3}{x_2 x_3}$}
%%	\end{overpic}
%%}{
%\begin{example}
%Consider the cluster fan~$\gvectorFan[\B_\circ]$ for the initial exchange matrix of type~$A_3$ cyclic represented on the right.
%%As it is a $3$-dimensional fan, we intersect it with the unit sphere and project the result stereographically from the pole $(-1,-1,-1)$.
%Its type cone lives in~$\R^{9}$ and has a linearity space of dimension~$3$.
%It has $6$ facet-defining inequalities (given below), which correspond to the mesh mutations of \cref{thm:extremalExchangeablePairsCA}.
%
%\begin{figure}[h]
%	\newcommand{\fitClusterVariable}[1]{\parbox[c][.7cm][c]{1.5cm}{\centering $#1$}}
%	\centerline{
%    \begin{tikzpicture}
%    	\matrix (m) [matrix of math nodes, row sep=.4cm, column sep=-.1cm, nodes={anchor=center, align=center, inner sep=0pt}, ampersand replacement=\&]{
%    		\fitClusterVariable{\phantom{1}} \& \node (e1) {\red \circled{E}}; \& \fitClusterVariable{\frac{x_1 + x_2 + x_3}{x_2 x_3}} \&\& \fitClusterVariable{x_3} \& \node (c) {\red \circled{C}}; \& \fitClusterVariable{\frac{x_1 + x_2 + x_3}{x_1 x_3}} \&\& \fitClusterVariable{x_1} \& \node (a2) {\red \circled{A}}; \& \fitClusterVariable{\phantom{1}} \\
%    		\& \fitClusterVariable{\frac{x_1 + x_2}{x_3}} \& \node (f1) {\red \circled{F}}; \& \fitClusterVariable{\frac{x_1 + x_3}{x_2}} \& \node (b) {\red \circled{B}}; \& \fitClusterVariable{\frac{x_2 + x_3}{x_1}} \& \node (d) {\red \circled{D}}; \& \fitClusterVariable{\frac{x_1 + x_2}{x_3}} \& \node (f2) {\red \circled{F}}; \& \fitClusterVariable{\frac{x_1 + x_3}{x_2}} \\
%    		\fitClusterVariable{\phantom{1}} \&\& \fitClusterVariable{x_1} \& \node (a1) {\red \circled{A}}; \& \fitClusterVariable{\frac{x_1 + x_2 + x_3}{x_1 x_2}} \&\& \fitClusterVariable{x_2} \& \node (e2) {\red \circled{E}}; \& \fitClusterVariable{\frac{x_1 + x_2 + x_3}{x_2 x_3}} \&\& \fitClusterVariable{\phantom{1}} \\};
%    	\draw[densely dotted, thick] (m-1-1) -- (m-2-2);
%    	\draw[densely dotted, thick] (m-3-1) -- (m-2-2);
%    	\draw[->] (m-2-2) -- (m-1-3);
%    	\draw[->] (m-2-2) -- (m-3-3);
%    	\draw[->] (m-1-3) -- (m-2-4);
%    	\draw[->] (m-3-3) -- (m-2-4);
%    	\draw[->] (m-2-4) -- (m-1-5);
%    	\draw[->] (m-2-4) -- (m-3-5);
%    	\draw[->] (m-1-5) -- (m-2-6);
%    	\draw[->] (m-3-5) -- (m-2-6);
%    	\draw[->] (m-2-6) -- (m-1-7);
%    	\draw[->] (m-2-6) -- (m-3-7);
%    	\draw[->] (m-1-7) -- (m-2-8);
%    	\draw[->] (m-3-7) -- (m-2-8);
%    	\draw[->] (m-2-8) -- (m-1-9);
%    	\draw[->] (m-2-8) -- (m-3-9);
%    	\draw[->] (m-1-9) -- (m-2-10);
%    	\draw[->] (m-3-9) -- (m-2-10);
%    	\draw[densely dotted, thick] (m-2-10) -- (m-1-11);
%    	\draw[densely dotted, thick] (m-2-10) -- (m-3-11);
%    	\draw[red] (a1) -- (m-3-3);
%    	\draw[red] (a1) -- (m-3-5);
%    	\draw[red] (a1) -- (m-2-4);
%    	\draw[red] (a2) -- (m-1-9);
%    	\draw[red, densely dotted, thick] (a2) -- (m-1-11);
%    	\draw[red] (a2) -- (m-2-10);
%    	\draw[red] (b) -- (m-2-4);
%    	\draw[red] (b) -- (m-2-6);
%    	\draw[red] (b) -- (m-1-5);
%    	\draw[red] (b) -- (m-3-5);
%    	\draw[red] (c) -- (m-1-5);
%    	\draw[red] (c) -- (m-1-7);
%    	\draw[red] (c) -- (m-2-6);
%    	\draw[red] (d) -- (m-2-6);
%    	\draw[red] (d) -- (m-2-8);
%    	\draw[red] (d) -- (m-1-7);
%    	\draw[red] (d) -- (m-3-7);
%    	\draw[red, densely dotted, thick] (e1) -- (m-1-1);
%    	\draw[red] (e1) -- (m-1-3);
%    	\draw[red] (e1) -- (m-2-2);
%    	\draw[red] (e2) -- (m-3-7);
%    	\draw[red] (e2) -- (m-3-9);
%    	\draw[red] (e2) -- (m-2-8);
%    	\draw[red] (f1) -- (m-2-2);
%    	\draw[red] (f1) -- (m-2-4);
%    	\draw[red] (f1) -- (m-1-3);
%    	\draw[red] (f1) -- (m-3-3);
%    	\draw[red] (f2) -- (m-2-8);
%    	\draw[red] (f2) -- (m-2-10);
%    	\draw[red] (f2) -- (m-1-9);
%    	\draw[red] (f2) -- (m-3-9);
%    \end{tikzpicture}
%    }
%	\caption{Facet-defining inequalities of the type cone~$\typeCone \big( \gvectorFan[n] \big)$. See \cref{prop:extremalExchangeablePairsAsso}. See \cref{fig:labelFacetDefiningInequalititiesAsso} for the conventions.}
%	\label{fig:labelFacetDefiningInequalititiesAsso}
%\end{figure}
%
%\end{example}
%%}

To describe the facets of this type cone, we need the following special mutations.

\begin{figure}[b]
	\newcommand{\fitClusterVariable}[1]{\parbox[c][.7cm][c]{1.5cm}{\centering $#1$}}
	\centerline{
    \begin{tikzpicture}
    	\matrix (m) [matrix of math nodes, row sep=.4cm, column sep=-.1cm, nodes={anchor=center, align=center, inner sep=0pt}, ampersand replacement=\&]{
    		\fitClusterVariable{\phantom{1}} \& \node (e1) {\red \circled{E}}; \& \fitClusterVariable{\frac{x_1 + x_2 + x_3}{x_2 x_3}} \&\& \fitClusterVariable{x_3} \& \node (c) {\red \circled{C}}; \& \fitClusterVariable{\frac{x_1 + x_2 + x_3}{x_1 x_3}} \&\& \fitClusterVariable{x_1} \& \node (a2) {\red \circled{A}}; \& \fitClusterVariable{\phantom{1}} \\
    		\& \fitClusterVariable{\frac{x_1 + x_2}{x_3}} \& \node (f1) {\red \circled{F}}; \& \fitClusterVariable{\frac{x_1 + x_3}{x_2}} \& \node (b) {\red \circled{B}}; \& \fitClusterVariable{\frac{x_2 + x_3}{x_1}} \& \node (d) {\red \circled{D}}; \& \fitClusterVariable{\frac{x_1 + x_2}{x_3}} \& \node (f2) {\red \circled{F}}; \& \fitClusterVariable{\frac{x_1 + x_3}{x_2}} \\
    		\fitClusterVariable{\phantom{1}} \&\& \fitClusterVariable{x_1} \& \node (a1) {\red \circled{A}}; \& \fitClusterVariable{\frac{x_1 + x_2 + x_3}{x_1 x_2}} \&\& \fitClusterVariable{x_2} \& \node (e2) {\red \circled{E}}; \& \fitClusterVariable{\frac{x_1 + x_2 + x_3}{x_2 x_3}} \&\& \fitClusterVariable{\phantom{1}} \\};
    	\draw[densely dotted, thick] (m-1-1) -- (m-2-2);
    	\draw[densely dotted, thick] (m-3-1) -- (m-2-2);
    	\draw[->] (m-2-2) -- (m-1-3);
    	\draw[->] (m-2-2) -- (m-3-3);
    	\draw[->] (m-1-3) -- (m-2-4);
    	\draw[->] (m-3-3) -- (m-2-4);
    	\draw[->] (m-2-4) -- (m-1-5);
    	\draw[->] (m-2-4) -- (m-3-5);
    	\draw[->] (m-1-5) -- (m-2-6);
    	\draw[->] (m-3-5) -- (m-2-6);
    	\draw[->] (m-2-6) -- (m-1-7);
    	\draw[->] (m-2-6) -- (m-3-7);
    	\draw[->] (m-1-7) -- (m-2-8);
    	\draw[->] (m-3-7) -- (m-2-8);
    	\draw[->] (m-2-8) -- (m-1-9);
    	\draw[->] (m-2-8) -- (m-3-9);
    	\draw[->] (m-1-9) -- (m-2-10);
    	\draw[->] (m-3-9) -- (m-2-10);
    	\draw[densely dotted, thick] (m-2-10) -- (m-1-11);
    	\draw[densely dotted, thick] (m-2-10) -- (m-3-11);
    	\draw[red, -<] (a1) -- (m-3-3);
    	\draw[red, -<] (a1) -- (m-3-5);
    	\draw[red, ->] (a1) -- (m-2-4);
    	\draw[red, -<] (a2) -- (m-1-9);
    	\draw[red, densely dotted, thick] (a2) -- (m-1-11);
    	\draw[red, ->] (a2) -- (m-2-10);
    	\draw[red, -<] (b) -- (m-2-4);
    	\draw[red, -<] (b) -- (m-2-6);
    	\draw[red, ->] (b) -- (m-1-5);
    	\draw[red, ->] (b) -- (m-3-5);
    	\draw[red, -<] (c) -- (m-1-5);
    	\draw[red, -<] (c) -- (m-1-7);
    	\draw[red, ->] (c) -- (m-2-6);
    	\draw[red, -<] (d) -- (m-2-6);
    	\draw[red, -<] (d) -- (m-2-8);
    	\draw[red, ->] (d) -- (m-1-7);
    	\draw[red, ->] (d) -- (m-3-7);
    	\draw[red, densely dotted, thick] (e1) -- (m-1-1);
    	\draw[red, -<] (e1) -- (m-1-3);
    	\draw[red, ->] (e1) -- (m-2-2);
    	\draw[red, -<] (e2) -- (m-3-7);
    	\draw[red, -<] (e2) -- (m-3-9);
    	\draw[red, ->] (e2) -- (m-2-8);
    	\draw[red, -<] (f1) -- (m-2-2);
    	\draw[red, -<] (f1) -- (m-2-4);
    	\draw[red, ->] (f1) -- (m-1-3);
    	\draw[red, ->] (f1) -- (m-3-3);
    	\draw[red, -<] (f2) -- (m-2-8);
    	\draw[red, -<] (f2) -- (m-2-10);
    	\draw[red, ->] (f2) -- (m-1-9);
    	\draw[red, ->] (f2) -- (m-3-9);
    \end{tikzpicture}
    }
    \vspace{-.1cm}
	\caption{The facet-defining inequalities of the type cone~$\typeCone \big( \gvectorFan[\B_\circ] \big)$ for the cluster fan of \cref{fig:lodayFans}\,(right). See \cref{thm:extremalExchangeablePairsCA}. The conventions are similar as in \cref{fig:labelFacetDefiningInequalititiesAsso}.}
	\label{fig:labelFacetDefiningInequalititiesCA}
\end{figure}

\begin{definition}
\label{def:meshMutation}
The mutation of a seed~$(\B, \cluster)$ in the direction of a cluster variable~$x \in \cluster$ is a \defn{mesh mutation} that \defn{starts} (resp.~\defn{ends}) at~$x$ if the entries~$b_{xy}$ for~$y \in \cluster$ are all non-negative (resp.~all non-positive).
A mesh mutation is \defn{initial} if it ends at a cluster variable of an initial seed.
We denote by~$\meshes$ the set of all pairs~$\{x,x'\}$ where~$x$ and~$x'$ are two cluster variables of~$\clusterAlgebra$ which are exchangeable via a non-initial mesh mutation.
\end{definition}

\begin{lemma}
\label{lem:dependenceMesh}
Consider two adjacent seeds~${(\B, \cluster)}$ and~${(\B', \cluster')}$ with~$\cluster \ssm \{x\} = \cluster' \ssm \{x'\}$ connected by a non-initial mesh mutation.
Then, the $\b{g}$-vectors of~$\cluster \cup \cluster'$ with respect to~$\B_\circ$ satisfy the linear dependence
\(
\gvectorFull{\B_\circ}{x} + \gvectorFull{\B_\circ}{x'} = {\displaystyle\sum}_{y \in \cluster \cap \cluster'} |b_{xy}| \, \gvectorFull{\B_\circ}{y}.
\)
\end{lemma}

For~$\{x,x'\} \in \meshes$ and~$y \in \variables$, we denote by~$\coefficient[y][x][x']$ the coefficient of~$\gvectorFull{\B_\circ}{y}$ in the linear dependence among the $\b{g}$-vectors~$\gvectorFull{\B_\circ}{x}$ and~$\gvectorFull{\B_\circ}{x'}$. In other words, by \cref{lem:dependenceMesh}, if~${(\B, \cluster)}$ and~${(\B', \cluster')}$ are for two adjacent seeds with~${\cluster \ssm \{x\} = \cluster' \ssm \{x'\}}$, we have~$\coefficient[y][x][x'] = |b_{xy}|$ for~$y \in \cluster \cap \cluster'$ and~$\coefficient[y][x][x'] = 0$ otherwise.
The next statement is proved in~\cite[Sect.~3]{PadrolPaluPilaudPlamondon} using techniques from the quiver representation theory.

\begin{theorem}
\label{thm:meshMutations}
For any finite type exchange matrix~$\B_\circ$ (acyclic or not, simply-laced or not), the linear dependence among the $\b{g}$-vectors of any mutation decomposes into positive combinations of linear dependences among $\b{g}$-vectors of non-initial mesh mutations.
\end{theorem}

%We derive from \cref{thm:meshMutations} the following description of the facets of the type cone of the cluster fan.
Using \cref{thm:meshMutations} as a blackbox, we describe the facets of the type cone. See \cref{fig:labelFacetDefiningInequalititiesAsso}. %, and thus all polytopal realizations, of the cluster fans of finite type cluster algebras.

\begin{theorem}
\label{thm:extremalExchangeablePairsCA}
For any finite type exchange matrix~$\B_\circ$, the type cone~$\typeCone \big( \gvectorFan[\B_\circ] \big)$ is simplicial and the non-initial mesh mutations are the extremal adjacent pairs of the cluster fan~$\gvectorFan[\B_\circ]$.
\end{theorem}

Combining \cref{coro:simplicialTypeCone,thm:extremalExchangeablePairsCA}, we derive the following description of all polytopal realizations of the cluster fan~$\gvectorFan[\B_\circ]$.
This result was stated in~\cite{BazierMatteDouvilleMousavandThomasYildirim} in the special situation of acyclic seeds in simply-laced types, with a very different proof.
%Note that our proof is quite different from~\cite{BazierMatteDouvilleMousavandThomasYildirim} as it relies on our type cone approach.

\begin{theorem}
\label{thm:allPolytopalRealizationsCA}
For any finite type exchange matrix~$\B_\circ$, and for any~$\b{\ell} \in \R_{>0}^{\meshes}$, the polytope
\[
\b{R}_{\b{\ell}}(\B_\circ) \eqdef \Bigset{\b{z} \in \R^{\variables}}{\b{z} \ge 0 \text{ and } \b{z}_x + \b{z}_{x'} - \!\!\!\!\! \sum_{y \in \variables} \!\!\!\!\!\coefficient[y][x][x'] \, \b{z}_{y} = \b{\ell}_{\{x,x'\}} \text{ for } \{x,x'\} \in \meshes}
\]
is a generalized associahedron, whose normal fan is the cluster fan~$\gvectorFan[\B_\circ]$.
Moreover, the polytopes~$\b{R}_\b{\ell}(\B_\circ)$ for~$\b{\ell} \in \R_{>0}^{\meshes}$ describe all polytopal realizations of~$\gvectorFan[\B_\circ]$.
\end{theorem}

\subsection{Non-kissing fans and gentle associahedra}
\label{subsec:gentleAssociahedra}

We now consider non-kissing complexes of gentle algebras studied in~\cite{PaluPilaudPlamondon-nonkissing}.
We briefly recall all definitions needed here as they are purely combinatorial.

Fix a \defn{gentle bound quiver}~${\quiver = (Q,I)}$, \ie a finite quiver~$Q$ (with vertices~$Q_0$, arrows~$Q_1$, and source and target maps~$s$ and~$t$) and an ideal~$I$ of the path algebra~$kQ$ such~that
\begin{compactenum}[(i)]
\item each vertex~$a \in Q_0$ has at most two incoming and two outgoing arrows,
\item the ideal~$I$ is generated by paths of length exactly two,
\item for any~$\beta \in Q_1$, there is at most one~$\alpha \in Q_1$ such that~$t(\alpha) = s(\beta)$ and~${\alpha\beta\notin I}$ (resp.~$\alpha\beta \in I$) and at most one~$\gamma \in Q_1$ such that~${t(\beta) = s(\gamma)}$ and~${\beta\gamma\notin I}$~(resp.~${\beta\gamma \in I}$).
\end{compactenum}

The \defn{blossoming quiver}~$\quiver\blossom$ of a gentle quiver~$\quiver$ is the gentle quiver obtained by completing all vertices of~$\quiver$ with additional incoming or outgoing \defn{blossoms} such that all vertices of~$\quiver$ become $4$-valent.
Blossom vertices appear in white in all pictures.

A \defn{string} in~$\quiver$ is a word
\(
\rho = \alpha_1^{\varepsilon_1}\alpha_2^{\varepsilon_2}\cdots \alpha_\ell^{\varepsilon_\ell}
\)
with $\alpha_i \in Q_1$ and~$\varepsilon_i \in \{-1,1\}$ such that $\smash{t(\alpha_i^{\varepsilon_i}) = s(\alpha_{i+1}^{\varepsilon_{i+1}})}$ and containing no factor~$\pi$ or~$\pi^{-1}$ for~$\pi \in I \cup \set{\smash{\alpha\alpha^{-1}}}{\alpha \in Q_1}$.
We implicitly identify the two inverse strings~$\rho$ and~$\rho^{-1}$.
A \defn{walk} of~$\quiver$ is a maximal string of its blossoming quiver~$\quiver\blossom$ (meaning that each endpoint is a blossom).

A \defn{substring} of a walk~$\smash{\omega = \alpha_1^{\varepsilon_1} \cdots \alpha_\ell^{\varepsilon_\ell}}$ of~$\quiver$ is a string~$\smash{\sigma = \alpha_{i+1}^{\varepsilon_{i+1}} \cdots \alpha_{j-1}^{\varepsilon_{j-1}}}$ of~$\quiver$ for some indices~$1 \le i < j \le \ell$.
We say that the substring~$\smash{\sigma = \alpha_{i+1}^{\varepsilon_{i+1}} \cdots \alpha_{j-1}^{\varepsilon_{j-1}}}$ is \defn{at the bottom} (resp.~\defn{on top}) of the walk~$\omega = \alpha_1^{\varepsilon_1} \cdots \alpha_\ell^{\varepsilon_\ell}$ if~$\varepsilon_i = 1$ and~$\varepsilon_j = -1$ (resp.~if~$\varepsilon_i = -1$ and~$\varepsilon_j = 1$).
In other words the two arrows of~$\omega$ incident to the endpoints of~$\sigma$ point towards~$\sigma$ (resp.~outwards from~$\sigma$).
We denote by~$\Sigma_\bottom(\omega)$ and~$\Sigma_\top(\omega)$ the sets of bottom and top substrings of~$\omega$ respectively.

For a walk~$\omega$, we denote by~$\peaks{\omega}$ (resp.~$\deeps{\omega}$) the multiset of \defn{peaks} (resp.~\defn{deeps}) of~$\omega$, \ie vertices which are substrings on the top (resp.~at the bottom) of~$\omega$.
A walk is \defn{straight} if it has no peak nor deep.

\parpic(4.15cm,2cm)(0pt, 55pt)[r][b]{\includegraphics[scale=1]{kissing}}{
Two walks~$\omega, \omega'$ are \defn{kissing} if ${\Sigma_\top(\omega) \cap \Sigma_\bottom(\omega')} \ne \varnothing$  (as illustrated on the right) or the opposite.
%In other words, $\omega$ and~$\omega'$ share a common substring~$\sigma$, and both arrows of~$\omega$ (resp.~of~$\omega'$) incident to the endpoints of~$\sigma$ but not in~$\sigma$ are outgoing (resp.~incoming) at the endpoints of~$\sigma$.
A walk is \defn{proper} if it is not straight nor self-kissing.
The \defn{non-kissing complex} of~$\quiver$ is the simplicial complex~$\NKC$ whose faces are the sets of pairwise non-kissing proper walks of~$\quiver$.
}

For a multiset~$V = \{\!\{v_1, \dots, v_k\}\!\}$ of~$Q_0$, we denote by $\multiplicityVector_V \eqdef \sum_{i \in [k]} \b{e}_{v_i}$, where~$(\b{e}_v)_{v \in Q_0}$ is the canonical basis of~$\R^{Q_0}$.
The \defn{$\b{g}$-vector} of a walk~$\omega$ is~$\gvector{\omega} \eqdef \multiplicityVector_{\peaks{\omega}} - \multiplicityVector_{\deeps{\omega}}$. We set~$\gvectors{F} \eqdef \set{\gvector{\omega}}{\omega \in F}$ for a non-kissing face~$F \in \NKC$.
Recall that:
\begin{compactenum}
\item the set of cones
\(
\gvectorFan[\quiver] \eqdef \bigset{\R_{\ge0} \, \gvectors{F}}{F \text{ non-kissing facet of } \NKC}
\)
forms a complete simplicial fan, called the \defn{non-kissing fan} of~$\quiver$.
See \cref{fig:nonkissingFans}.

\item the non-kissing fan is the normal fan of a polytope~$\Asso[\quiver]$, called \defn{gentle associahedron}, constructed in~\cite{PaluPilaudPlamondon-nonkissing}.

\parpic(4.2cm,2cm)(0pt, 60pt)[r][b]{\includegraphics[scale=1]{flip}}{
\item for any two adjacent non-kissing facets~$F$ and~$F'$ of~$\NKC$ with~$F \! \ssm \! \{\omega\} \! = \! F' \! \ssm \! \{\omega'\}$, the linear dependence among~the $\b{g}$-vectors of~$F \cup F'$ is given by~${\gvector{\omega} + \gvector{\omega'} = \gvector{\mu} + \gvector{\nu}}$, where~$\mu \eqdef \rho' \sigma \tau$ and~$\nu \eqdef \rho \sigma \tau'$ if the walks $\omega = \rho \sigma \tau$ and $\omega' = \rho' \sigma \tau'$ kiss along~$\sigma$ (as illustrated on the right).
}
\end{compactenum}

%\begin{figure}[t]
%	\centerline{\includegraphics[scale=1]{flipHor}}
%	\caption{A flip exchanging two kissing walks~$\omega$ and~$\omega'$.}
%\end{figure}

\smallskip
This provides a redundant description of the type cone of the non-kissing~fan~$\gvectorFan[\quiver]$.
See \cref{fig:labelFacetDefiningInequalititiesNKC} for examples of facet descriptions of these type cones.

\begin{corollary}
The type cone of the non-kissing fan~$\gvectorFan[\quiver]$ is given by
\[
\smash{
\typeCone \big( \gvectorFan[\quiver] \big) = \set{\b{h} \in \R^{\walks}}{\begin{array}{l} \b{h}_\omega = 0 \text{ for any improper walk } \omega \\ \b{h}_\omega + \b{h}_{\omega'} > \b{h}_\mu + \b{h}_\nu \text{ for any exchangeable walks } \omega, \omega' \end{array}},}
\]
where~$\mu \eqdef \rho' \sigma \tau$ and~$\nu \eqdef \rho \sigma \tau'$ if the walks $\omega = \rho \sigma \tau$ and~$\omega' = \rho' \sigma \tau'$ kiss along~$\sigma$.
\end{corollary}

%\begin{example}
%\label{exm:typeConeNKC}
%Consider the type cones of the non-kissing fans illustrated below.

\begin{figure}[t]
	\centerline{\includegraphics[scale=.5]{nonkissingFans}}
	\caption{Two non-kissing fans. As the fans are $3$-dimensional, we intersect them with the sphere and stereographically project them from the direction~$(-1,-1,-1)$. }
	\label{fig:nonkissingFans}
\end{figure}

%\vspace{-.1cm}
%\noindent
%The first lives in~$\R^8$, has a linearity space of dimension~$3$, and~$5$ facet-defining inequalities (given below),  which correspond to the flips described in \cref{prop:interestingExchangeablePairsNKC,prop:extremalExchangeablePairsNKC}.
%
%\begin{center}
%$
%\begin{array}{r|ccccccccc}
%\text{walks} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA1}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA2}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA3}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA4}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA5}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA6}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA7}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA8}} \\[.6cm]
%\text{$\b{g}$-vectors} & \compactVectorT{1}{0}{0} & \compactVectorT{0}{1}{0} & \compactVectorT{0}{0}{1} & \compactVectorT{1}{-1}{0} & \compactVectorT{0}{1}{-1} & \compactVectorT{-1}{0}{0} & \compactVectorT{0}{-1}{0} & \compactVectorT{0}{0}{-1} \\[.6cm]
%\text{facet}		& 0 & -1 & 1 & 0 & 1 & 0 & 0 & 0 & \red \circled{A} \\
%\text{defining}		& 0 & 1 & 0 & 0 & -1 & 0 & 0 & 1 & \red \circled{B} \\
%\text{inequalities}	& -1 & 0 & 0 & 1 & 1 & 0 & 0 & -1 & \red \circled{C} \\
%					& 1 & 0 & 0 & -1 & 0 & 0 & 1 & 0 & \red \circled{D} \\
%					& 0 & 0 & 0 & 1 & 0 & 1 & -1 & 0 & \red \circled{E}
%\end{array}
%$
%\end{center}
%
%\noindent
%The second lives in~$\R^{11}$, has a linearity space of dimension~$3$, and~$9$ facet-defining inequalities.% In particular, it is not simplicial.
%
%\vspace{-.3cm}
%\begin{center}
%$
%\begin{array}{r|c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}cc}
%\text{walks} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB1}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB2}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB3}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB4}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB5}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB6}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB7}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB8}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB9}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB10}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB11}} \\[.6cm]
%\text{$\b{g}$-vectors} & \compactVectorT{1}{0}{0} & \compactVectorT{0}{1}{0} & \compactVectorT{0}{0}{1} & \compactVectorT{1}{-1}{0} & \compactVectorT{1}{0}{-1} & \compactVectorT{0}{-1}{1} & \compactVectorT{0}{1}{-1} & \compactVectorT{-1}{0}{1} & \compactVectorT{-1}{0}{0} & \compactVectorT{0}{-1}{0} & \compactVectorT{0}{0}{-1} \\[.6cm]
%\text{facet}		& -1 & 1 & 0 & 0 & 1 & 0 & -1 & 0 & 0 & 0 & 0 & \red \circled{A} \\
%\text{defining}		& 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 0 & 0 & 1 & \red \circled{B} \\
%\text{inequalities}	& 0 & 0 & 0 & 1 & -1 & 0 & 1 & 0 & 0 & 0 & 0 & \red \circled{C} \\
%					& 1 & 0 & -1 & -1 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & \red \circled{D} \\
%					& 0 & 0 & 0 & -1 & 1 & 0 & 0 & 0 & 0 & 1 & -1 & \red \circled{E} \\
%					& 0 & 0 & 1 & 0 & 0 & -1 & 0 & 0 & 0 & 1 & 0 & \red \circled{F}\\
%					& 0 & 0 & 0 & 1 & 0 & -1 & 0 & 1 & 0 & 0 & 0 & \red \circled{G} \\
%					& 0 & 0 & 0 & 0 & 0 & 1 & 0 & -1 & 1 & -1 & 0 & \red \circled{H} \\
%					& 0 & -1 & 0 & 0 & 0 & 0 & 1 & 1 & -1 & 0 & 0 & \red \circled{K} 
%\end{array}
%$
%\end{center}

\begin{figure}
	\centerline{
	\begin{tikzpicture}
			\matrix (m) [matrix of math nodes, row sep=.15cm, column sep=.3cm, nodes={anchor=center, align=center, inner sep=0pt}, ampersand replacement=\&]{
				\&\&\& \includegraphics[scale=.5]{walkA1} \& \node (d) {\red \circled{D}}; \& \includegraphics[scale=.5]{walkA7} \& \\
				\includegraphics[scale=.5]{walkA3} \& \node (a) {\red \circled{A}}; \& \includegraphics[scale=.5]{walkA5} \& \node (c) {\red \circled{C}}; \& \includegraphics[scale=.5]{walkA4} \& \node (e) {\red \circled{E}}; \& \includegraphics[scale=.5]{walkA6} \\
				\& \includegraphics[scale=.5]{walkA2} \& \node (b) {\red \circled{B}}; \& \includegraphics[scale=.5]{walkA8} \&\&\& \\};
			\draw[->] (m-2-1) -- (m-3-2);
			\draw[->] (m-3-2) -- (m-2-3);
			\draw[->] (m-2-3) -- (m-1-4);
			\draw[->] (m-2-3) -- (m-3-4);
			\draw[->] (m-1-4) -- (m-2-5);
			\draw[->] (m-3-4) -- (m-2-5);
			\draw[->] (m-2-5) -- (m-1-6);
			\draw[->] (m-1-6) -- (m-2-7);
			\draw[red, -<] (a) -- (m-2-1);
			\draw[red, -<] (a) -- (m-2-3);
			\draw[red, ->] (a) -- (m-3-2);
			\draw[red, -<] (b) -- (m-3-2);
			\draw[red, -<] (b) -- (m-3-4);
			\draw[red, ->] (b) -- (m-2-3);
			\draw[red, -<] (c) -- (m-2-3);
			\draw[red, -<] (c) -- (m-2-5);
			\draw[red, ->] (c) -- (m-1-4);
			\draw[red, ->] (c) -- (m-3-4);
			\draw[red, -<] (d) -- (m-1-4);
			\draw[red, -<] (d) -- (m-1-6);
			\draw[red, ->] (d) -- (m-2-5);
			\draw[red, -<] (e) -- (m-2-5);
			\draw[red, -<] (e) -- (m-2-7);
			\draw[red, ->] (e) -- (m-1-6);
		\end{tikzpicture}
		\quad
		\begin{tikzpicture}
			\matrix (m) [matrix of math nodes, row sep=.3cm, column sep=.1cm, nodes={anchor=center, align=center, inner sep=0pt}, ampersand replacement=\&]{
				\&\& \includegraphics[scale=.5]{walkB3} \&\& \includegraphics[scale=.5]{walkB11} \&\& \\
				\& \includegraphics[scale=.5]{walkB1} \& \node (b) {\red \circled{B}}; \&\& \node (f) {\red \circled{F}}; \& \includegraphics[scale=.5]{walkB10} \& \\
				\includegraphics[scale=.5]{walkB2} \& \node (a) {\red \circled{A}}; \& \includegraphics[scale=.5]{walkB5} \& \node (d) at (-.3,.3) {\red \circled{D}}; \node (e) at (.3,.3) {\red \circled{E}}; \& \includegraphics[scale=.5]{walkB6} \& \node (h) {\red \circled{H}}; \& \includegraphics[scale=.5]{walkB9} \\
				\node (k1) {\red \circled{K}}; \& \includegraphics[scale=.5]{walkB7} \& \node (c) {\red \circled{C}}; \& \includegraphics[scale=.5]{walkB4} \& \node (g) {\red \circled{G}}; \& \includegraphics[scale=.5]{walkB8} \& \node (k2) {\red \circled{K}}; \\};
			\draw[->] (m-3-1) -- (m-2-2);
			\draw[->] (m-3-1) -- (m-4-2);
			\draw[->] (m-2-2) -- (m-1-3);
			\draw[->] (m-2-2) -- (m-3-3);
			\draw[->] (m-4-2) -- (m-3-3);
			\draw[->] (m-1-3) -- (m-3-5);
			\draw[->] (m-3-3) -- (m-1-5);
			\draw[->] (m-3-3) -- (m-4-4);
			\draw[->] (m-4-4) -- (m-3-5);
			\draw[->] (m-1-5) -- (m-2-6);
			\draw[->] (m-3-5) -- (m-2-6);
			\draw[->] (m-3-5) -- (m-4-6);
			\draw[->] (m-2-6) -- (m-3-7);
			\draw[->] (m-4-6) -- (m-3-7);
			\draw[red, -<] (a) -- (m-3-1);
			\draw[red, -<] (a) -- (m-3-3);
			\draw[red, ->] (a) -- (m-2-2);
			\draw[red, ->] (a) -- (m-4-2);
			\draw[red, -<] (b) -- (m-2-2);
			\draw[red, -<] (b) -- (m-1-5);
			\draw[red, ->] (b) -- (m-3-3);
			\draw[red, -<] (c) -- (m-4-2);
			\draw[red, -<] (c) -- (m-4-4);
			\draw[red, ->] (c) -- (m-3-3);
			\draw[red, -<] (d) -- (m-2-2);
			\draw[red, -<] (d) -- (m-3-5.200);
			\draw[red, ->] (d) -- (m-1-3);
			\draw[red, ->] (d) -- (m-4-4);
			\draw[red, -<] (e) -- (m-3-3.340);
			\draw[red, -<] (e) -- (m-2-6);
			\draw[red, ->] (e) -- (m-4-4);
			\draw[red, ->] (e) -- (m-1-5);
			\draw[red, -<] (f) -- (m-1-3);
			\draw[red, -<] (f) -- (m-2-6);
			\draw[red, ->] (f) -- (m-3-5);
			\draw[red, -<] (g) -- (m-4-4);
			\draw[red, -<] (g) -- (m-4-6);
			\draw[red, ->] (g) -- (m-3-5);
			\draw[red, -<] (h) -- (m-3-5);
			\draw[red, -<] (h) -- (m-3-7);
			\draw[red, ->] (h) -- (m-2-6);
			\draw[red, ->] (h) -- (m-4-6);
			\draw[red, ->] (k1) -- (m-3-1);
			\draw[red, -<] (k1) -- (m-4-2);
			\draw[red, densely dotted, thick] (k1.west) -- ([xshift=-.3cm]k1.west);
			\draw[red, densely dotted, thick] (k1.south) -- ([yshift=-.3cm]k1.south);
			\draw[red, -<] (k2) -- (m-4-6);
			\draw[red, ->] (k2) -- (m-3-7);
			\draw[red, densely dotted, thick] (k2.east) -- ([xshift=.3cm]k2.east);
			\draw[red, densely dotted, thick] (k2.south) -- ([yshift=-.3cm]k2.south);
	\end{tikzpicture}
	}
	\caption{The facet-defining inequalities of the type cone~$\typeCone \big( \gvectorFan[\quiver] \big)$ for the non-kissing fan of \cref{fig:nonkissingFans}\,(right). The conventions are similar as in \cref{fig:labelFacetDefiningInequalititiesAsso}.}
	\label{fig:labelFacetDefiningInequalititiesNKC}
\end{figure}
%\end{example}

\newpage
%The flips corresponding to the facet-defining inequalities of the type cones of \cref{fig:labelFacetDefiningInequalititiesNKC} are represented on the corresponding Auslander-Reiten quivers.
As illustrated by the second non-kissing fan of \cref{fig:labelFacetDefiningInequalititiesNKC} (which lives in~$\R^{11}$, has a $3$-dimensional linearity space, and has $9$ facets), the type cone~$\typeCone(\gvectorFan[\quiver])$ is not always simplicial.
However, it turns out to be for the following family of quivers.

\begin{definition}
\label{def:brick2acyclic}
A gentle quiver~$\quiver$ is called:
\begin{compactitem}
\item \defn{brick} if any (non necessarily oriented) cycle of~$\quiver$ contains at least two relations in~$I$. %, or equivalently, no walk on~$\quiver$ is self-kissing.
\item \defn{$2$-acyclic} if it contains no cycle of length~$2$.
\end{compactitem}
\end{definition}

For a string~$\sigma$ of~$\quiver$, we denote by $\sigma\hR$ (resp.~$\sigma\cR$) the unique string of the blossoming quiver~$\quiver\blossom$ of the form $\sigma\hR = \sigma \alpha_1^{-1} \alpha_2 \dots \alpha_\ell$ (resp.~$\sigma\cR = \sigma \alpha_1 \alpha_2^{-1} \dots \alpha_\ell^{-1}$) with~$\ell \ge 1$ and~${\alpha_1, \dots, \alpha_\ell \in Q_1}$ and such that~$t(\alpha_\ell)$ (resp.~$s(\alpha_\ell)$) is a blossom of~$\quiver\blossom$.
The terminology usually says that~$\sigma\hR$ (resp.~$\sigma\cR$) is obtained by adding a \defn{hook} (resp.~a \defn{cohook}) to~$\sigma$.
We define similarly~$\hL\sigma$ (resp.~$\cL\sigma$).
The walk~$\hL(\sigma\hR) = (\hL\sigma)\hR$ of~$\quiver$ is simply denoted by~$\hh{\sigma}$, and we define similarly~$\cc{\sigma}$, $\hc{\sigma}$ and~$\ch{\sigma}$.

\begin{proposition}
\label{prop:interestingExchangeablePairsNKC}
For any brick and $2$-acyclic gentle quiver~$\quiver$ and any string~$\sigma \in \strings$, the walks~$\cc{\sigma}$ and~$\hh{\sigma}$ are exchangeable with distinguished substring~$\sigma$.
\end{proposition}

%The following statement describes the type cone of the non-kissing fan of a brick and $2$-acyclic gentle quiver.

\begin{proposition}
\label{prop:extremalExchangeablePairsNKC}
For any brick and $2$-acyclic gentle quiver~$\quiver$, the extremal exchangeable pairs for the non-kissing fan of~$\quiver$ are precisely the pairs~$\{\cc{\sigma}, \hh{\sigma}\}$ for all strings~$\sigma \in \strings$.
\end{proposition}

\begin{corollary}
\label{coro:simplicialTypeConeNKC}
For any brick and $2$-acyclic gentle quiver~$\quiver$, the type cone~$\typeCone \big( \gvectorFan[\quiver] \big)$ of the non-kissing fan~$\gvectorFan[\quiver]$ is simplicial.
\end{corollary}

%Combining \cref{coro:simplicialTypeCone,coro:simplicialTypeConeNKC,prop:extremalExchangeablePairsNKC}, we derive the following description of all polytopal realizations of the non-kissing fan~$\gvectorFan[\quiver]$ of a brick and $2$-acyclic quiver~$\quiver$.

\begin{theorem}
\label{thm:allPolytopalRealizationsNKC}
For any brick and $2$-acyclic gentle quiver~$\quiver$ and any~$\b{\ell} \in \R_{>0}^{\strings}$, the polytope
\[
R_\b{\ell}(\quiver) \eqdef \set{\b{z} \in \R^{\walks}}{\begin{array}{l} \b{z} \ge 0 \qquad\text{and}\qquad \b{z}_\omega = 0 \text{ for any improper walk } \omega \\ \b{z}_{\cc{\sigma}} + \b{z}_{\hh{\sigma}} - \b{z}_{\hc{\sigma}} - \b{z}_{\ch{\sigma}} = \b{\ell}_\sigma \text{ for all } \sigma \in \strings\end{array}}
\]
is a realization of the non-kissing fan~$\gvectorFan[\quiver]$.
Moreover, the polytopes~$R_\b{\ell}(\quiver)$ for~$\b{\ell} \in \R_{>0}^{\strings}$ describe all polytopal realizations of~$\gvectorFan[\quiver]$.
\end{theorem}

\subsection{Nested fans and graph associahedra}
\label{subsec:graphAssociahedra}

We now consider the graph associahedra studied in~\cite{CarrDevadoss, Postnikov, FeichtnerSturmfels, Zelevinsky}.
Again, we briefly recall all definitions needed here as they are purely combinatorial.

Let~$\graphG$ be a graph on~$\ground$.
%Let~$\connectedComponents(\graphG)$ be the set of connected components of~$\graphG$ and let $n \eqdef |\ground|-|\connectedComponents(\graphG)|$.
A \defn{tube} of~$\graphG$ is a connected induced subgraph of~$\graphG$.
Le~$\tubes$ denote the set of tubes of~$\graphG$.
The inclusion maximal tubes of~$\graphG$ are its connected components~$\connectedComponents(\graphG)$.
The tubes which are neither empty nor maximal are called \defn{proper}.
Two tubes~$\tube, \tube'$ of~$\graphG$ are \defn{compatible} if they are either nested (\ie $\tube \subseteq \tube'$ or~$\tube' \subseteq \tube$), or disjoint and non-adjacent (\ie $\tube \cup \tube'$ is not a tube of~$\graphG$).
A \defn{tubing} on~$\graphG$ is a set~$\tubing$ of pairwise compatible proper tubes of~$\graphG$.
%See \cref{fig:exmNested}.
The \defn{nested complex} of~$\graphG$ is the simplicial complex~$\nestedComplex(\graphG)$ of all tubings~on~$\graphG$.

The \defn{$\b{g}$-vector} of a tube~$\tube$ of~$\graphG$ is the projection~$\gvector{\tube}$ of the characteristic vector~$\sum_{v \in \tube} \b{e}_v$ of~$\tube$ orthogonally to~$\sum_{v \in \ground} \b{e}_v$.
We set~$\gvectors{\tubing} \eqdef \set{\gvector{\tube}}{\tube \in \tubing}$ for a tubing~$\tubing$.
%
Recall~that:
\begin{compactenum}
\item the set of cones
\(
\gvectorFan[\graphG] \eqdef \bigset{\R_{\ge0} \, \gvectors{\tubing}}{\tubing \text{ tubing on } \graphG}
\)
forms a complete simplicial fan, called the \defn{nested fan} of~$\graphG$.

\item the nested fan is the normal fan of a polytope~$\Asso[\graphG]$, called \defn{graph associahedron}, constructed in~\cite{CarrDevadoss, Postnikov, FeichtnerSturmfels, Zelevinsky}.
For instance, the permutahedra, associahedra and cyclohedra are graph associahedra of complete graphs, paths, and cycles respectively.
%For instance, the permutahedron is the complete graph associahedron, the associahedron is the path associahedron, and the cyclohedron is the cycle associahedron.

\item for any maximal tubings~$\tubing, \tubing'$ on~$\graphG$ with $\tubing \ssm \{\tube\} = \tubing' \ssm \{\tube'\}$, the linear dependence among the $\b{g}$-vectors of~$\tubing \cup \tubing'$ is given by~$\gvector{\tube} + \gvector{\tube'} = \gvector{\tube \cup \tube'} + \sum_{\tube[s] \in \connectedComponents(\tube \cap \tube')} \gvector{\tube[s]}$, where~$\connectedComponents(\tube \cap \tube')$ denote the set of connected components of~$\tube \cap \tube'$.

\end{compactenum}

\smallskip
This provides a redundant description of the type cone of the nested fan~$\gvectorFan[n]$.

\begin{corollary}
\label{coro:typeConeGA}
For any graph~$\graphG$, the type cone of the nested fan~$\gvectorFan[\graphG]$ is given by
\[
\typeCone \big( \gvectorFan[\graphG] \big) = \set{\b{h} \in \R^{\tubes}}{\begin{array}{l} \b{h}_{\tube} = 0 \text{ for any improper tube } \tube \\ \b{h}_{\tube} + \b{h}_{\tube'} > \b{h}_{\,\tube \cup \tube'} + \!\!\!\smash{\displaystyle\sum_{\tube[s] \in \connectedComponents(\tube \cap \tube')}} \!\!\! \b{h}_{\tube[s]} \text{ for any exchangeable tubes } \tube, \tube' \end{array}}.
\]
\end{corollary}

\medskip
The next statement gives the facets of the type cone of the nested fan~$\gvectorFan[\graphG]$.

\begin{proposition}
\label{prop:extremalExchangeablePairsGA}
Two tubes~$\tube$ and~$\tube'$ of~$\graphG$ form an extremal exchangeable pair for the nested fan of~$\graphG$ if and only if~${\tube \ssm \{v\} = \tube' \ssm \{v'\}}$ for some neighbor~$v$ of~$\tube'$ and some neighbor~$v'$ of~$\tube$.
\end{proposition}

\begin{corollary}
\label{coro:typeconenestedfan}
For a graph~$\graphG$ on~$\ground$ with tubes~$\tubes$ and a height vector~$\b{h} \in \R^{\tubes}$, the nested fan~$\gvectorFan[\graphG]$ is the normal fan of the polytope
\(
\set{\b{x} \in \R^\ground}{\dotprod{\gvector{\tube}}{\b{x}} \le \b{h}_{\tube} \text{ for any tube } \tube \in \tubes}
\)
if and only if~$\b{h}_{\varnothing} = \b{h}_{\graphG} = 0$ and
 $\b{h}_{\tube[s] \ssm \{v'\}} + \b{h}_{\tube[s] \ssm \{v\}} > \b{h}_{\tube[s]} + \b{h}_{\tube[s] \ssm \{v, v'\}}$ for any tube~$\tube[s] \in \tubes$ and distinct non-disconnecting vertices~$v,v'$ of~$\tube[s]$.
\end{corollary}

\begin{corollary}
\label{coro:numberExtremalExchangeablePairsGA}
The nested fan~$\gvectorFan[\graphG]$ has~${\displaystyle\sum}_{\,\tube[s] \in \tubes} \binom{\nonDisconnecting(\tube[s])}{2}$ extremal exchangeable pairs, where~$\nonDisconnecting(\tube[s])$ is the number of non-disconnecting vertices of~$\tube[s]$.
\end{corollary}

%\begin{corollary}
%The type cone~$\typeCone \big( \gvectorFan[\graphG] \big)$ is simplicial if and only if~$\graphG$ is a path.
%\end{corollary}

For instance, the number of extremal exchangeable pairs is $2^{n-2}\binom{n}{2}$ for the permutahedron, $\binom{n}{2}$ for the associahedron, and $3\binom{n}{2} - n$ for the cyclohedron.
In fact, it turns out that the type cone~$\typeCone \big( \gvectorFan[\graphG] \big)$ is simplicial if and only if~$\graphG$ is a path.
%\begin{proposition}
%The number of extremal exchangeable pairs of the nested fan~$\gvectorFan[\graphG]$ is:
%\begin{compactitem}
%\item $2^{n-2}\binom{n}{2}$ for the permutahedron (complete graph associahedron),
%\item $\binom{n}{2}$ for the associahedron (path associahedron),
%\item $3\binom{n}{2} - n$ for the cyclohedron (cycle associahedron),
%\item $n-1+2^{n-3}\binom{n-1}{2}$ for the stellohedron (star associahedron).
%\end{compactitem}
%\end{proposition}

\newpage
%% if you use biblatex then this generates the bibliography
%% if you use some other method then remove this and do it your own way
\printbibliography

\end{document}

### 2019-10-31 thirdPaper/draft/typeConeAssociahedra.tex
FPSAC

@@
 \item the convex hull of the points~$L(T) \in \R^{n+1}$ for all rooted binary trees~$T$ with~$n+1$ internal nodes, where the $i$th coordinate of~$L(T)$ is the product of the number of leaves in the left subtree by the number of leaves in the right subtree of the $i$th node of~$T$ in inorder~\cite{Loday},
-\item the intersection of the hyperplane~$\bigset{\b{x} \in \R^{n+1}}{\sum_{\ell \in [n+1]} x_\ell = \binom{n+2}{2}}$ with the halfspaces $\bigset{\b{x} \in \R^{n+1}}{\sum_{a < \ell < b} x_\ell \ge \binom{b-a+2}{2}}$ for all internal diagonals~$(a,b)$ of \mbox{the $(n+3)$-gon~\cite{ShniderSternberg}},
+\item the intersection of the hyperplane~$\bigset{\b{x} \in \R^{n+1}}{\sum_{\ell \in [n+1]} x_\ell = \binom{n+2}{2}}$ with the halfspaces $\bigset{\b{x} \in \R^{n+1}}{\sum_{a < \ell < b} x_\ell \ge \binom{b-a}{2}}$ for all internal diagonals~$(a,b)$ of \mbox{the $(n+3)$-gon~\cite{ShniderSternberg}},
 \item the Minkowski sum of the faces~$\simplex_{[i,j]}$ of the standard $n$-dimensional simplex~$\simplex_{[n+1]}$ corresponding to all proper intervals~$[i,j]$ of~$[n+1]$,~\cite{Postnikov}.
@@
 \begin{itemize}
-\item the normal vector of the facet corresponding to an internal diagonal~$(a,b)$ of the $(n+3)$-gon is the vector~$\gvector{a,b} \eqdef \pi\big( \sum_{a < \ell < b} \b{e}_\ell \big) = (n+1) \sum_{a < \ell < b} \b{e}_\ell - (b-a+1) \sum_{1 \le \ell \le n+1} \b{e}_\ell$.
+\item the normal vector of the facet corresponding to an internal diagonal~$(a,b)$ of the $(n+3)$-gon is the vector~$\gvector{a,b} \eqdef \pi\big( \sum_{a < \ell < b} \b{e}_\ell \big) = (n+1) \sum_{a < \ell < b} \b{e}_\ell - (b-a-1) \sum_{1 \le \ell \le n+1} \b{e}_\ell$.
 \item the normal cone of the vertex corresponding to a rooted binary tree~$T$ is the incidence cone~$\bigset{\b{x} \in \HH}{x_i \le x_j \text{ for all edges $i \to j$ in $T$}}$.
@@
 
-The type cone of~$\gvectorFan[2]$ lives in~$\R^9$ and has a linearity space of dimension~$3$.
+The type cone of~$\gvectorFan[3]$ lives in~$\R^9$ and has a linearity space of dimension~$3$.
 It has $6$ facet-defining inequalities (given below), which correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso} and illustrated in \cref{fig:labelFacetDefiningInequalititiesAsso}\,(right).
@@
 \enlargethispage{.2cm}
-Combining \cref{coro:simplicialTypeCone}, \cref{coro:simplicialTypeConeAsso} and \cref{prop:extremalExchangeablePairsAsso}, we derive the following description of all polytopal realizations of the fan~$\gvectorFan[n]$, recovering all associahedra of~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan}.
+Combining \cref{coro:simplicialTypeCone,coro:simplicialTypeConeAsso} and \cref{prop:extremalExchangeablePairsAsso}, we derive the following description of all polytopal realizations of the fan~$\gvectorFan[n]$, recovering all associahedra of~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan}.
 Note that the arguments of~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} were quite different from the present~approach.
@@
 
-The \defn{blossoming quiver}~$\quiver\blossom$ of a gentle quiver is the gentle quiver obtained by completing all vertices of~$\quiver$ with additional incoming or outgoing \defn{blossoms} such that all vertices of~$\quiver$ become $4$-valent.
+The \defn{blossoming quiver}~$\quiver\blossom$ of a gentle quiver~$\quiver$ is the gentle quiver obtained by completing all vertices of~$\quiver$ with additional incoming or outgoing \defn{blossoms} such that all vertices of~$\quiver$ become $4$-valent.
 For instance, \cref{fig:exmNonkissing},(left) shows a blossoming quiver: the vertices of~$\quiver$ appear in black, while the blossom vertices of~$\quiver\blossom$ appear in white.
@@
 
-A \defn{peak} (resp.~\defn{deep}) of a walk~$\omega$ is a substring of~$\omega$ of length zero which is on top (resp.~at the bottom of~$\omega$).
+A \defn{peak} (resp.~\defn{deep}) of a walk~$\omega$ is a substring of~$\omega$ of length zero which is on top (resp.~at the bottom) of~$\omega$.
 A walk~$\omega$ is \defn{straight} if it has no peak or deep (\ie if~$\omega$ or~$\omega^{-1}$ is a path in~$\quiver\blossom$), and \defn{bending} otherwise.
@@
 
-\item For any non-kissing facets~$F, F'$ of~$\NKC$ with~$F \ssm \{\omega\} = f' \ssm \{\omega'\}$, the distinguished substrings of~$\omega$ in~$F$ and of~$\omega'$ in~$F'$ coincide to a string~$\sigma$.
+\item For any non-kissing facets~$F, F'$ of~$\NKC$ with~$F \ssm \{\omega\} = F' \ssm \{\omega'\}$, the distinguished substrings of~$\omega$ in~$F$ and of~$\omega'$ in~$F'$ coincide to a string~$\sigma$.
 Moreover, if we decompose~${\omega = \rho \sigma \tau}$ and~${\omega' = \rho' \sigma \tau'}$, then the facets~$F$ and~$F'$ both contain the walks~$\mu \eqdef \rho' \sigma \tau$ and~$\nu \eqdef \rho \sigma \tau'$.

### 2019-11-11 thirdPaper/FPSAC/typeConeAssociahedraFPSAC.tex
keywords
resume
corrections + pictures FPSAC

@@
 	Arnau Padrol\thanks{\href{mailto:arnau.padrol@imj-prg.fr}{arnau.padrol@imj-prg.fr}. Supp. by ANR grant CAPPS~(17\,CE40\,0018).}\addressmark{1},
-	\stepcounter{footnote}
+	\stepcounter{footnote}%
 	Yann Palu\thanks{\href{mailto:yann.palu@u-picardie.fr}{yann.palu@u-picardie.fr}. Supp. by ANR grant SC3A~(15\,CE40\,0004\,01).}\addressmark{2}, \\
@@
 We study the type cone (\ie the space of all polytopal realizations) of $\b{g}$-vector fans of finite type cluster-like complexes (finite type cluster complexes, non-kissing complexes of gentle algebra, and graphical nested complexes).
-We show that this cone is often simplicial, which explains an elegant ``kinematic'' construction of the associahedron as a section of a high dimensional positive orthant by certain affine subspaces parametrized by a small dimensional positive orthant.
+We show that this cone is often simplicial, which explains an elegant ``kinematic'' construction of the associahedron as a section of a high dimensional positive orthant by certain affine subspaces parametrized by a low dimensional positive orthant.
 }
@@
 %% put your French abstract here, or comment this out if you don't have one
+\resumetitle{R\'esum\'e}
 \resume{
 Nous \'etudions le type cone (\ie l'espace de toutes les r\'ealisations polytopales) des \'eventails de $\b{g}$-vecteurs de complexes de type amassés (complexes amassés de type fini, complexes platoniques d'alg\`ebres aimables, et complexes emboit\'es graphi\-ques).
-Nous montrons que ce cone est souvent simplicial, ce qui explique une \'el\'egante construction ``cin\'ematique'' de l'associa\`edre comme section d'un orthant positif de grande dimension par certains sous-espaces affines param\`etrés par un orthant positif de petite dimension.
+Nous montrons que ce cone est souvent simplicial, ce qui explique une \'el\'egante construction ``cin\'ematique'' de l'associa\`edre comme section d'un orthant positif de haute dimension par certains sous-espaces affines param\`etrés par un orthant positif de basse dimension.
 }
@@
 %% put your keywords here, or comment this out if you don't have them yet
-\keywords{Fans $\cdot$ cluster algebras $\cdot$ non-kissing complex $\cdot$ graph associahedra}
+\keywords{Fans $\cdot$ cluster algebras $\cdot$ non-kissing complexes $\cdot$ graph associahedra}
 
@@
 Besides revisiting the construction of~\cite{ArkaniHamedBaiHeYan, BazierMatteDouvilleMousavandThomasYildirim} and extending it to any initial seed, our type cone approach is also successful when applied to the $\b{g}$-vector fans of other families of generalizations of the associahedron.
-In the present paper, we explore specifically the non-kissing complexes of gentle algebras introduced in~\cite{PaluPilaudPlamondon-nonkissing} (see \cref{subsec:gentleAssociahedra}) and the graphical nested complexes studied in~\cite{CarrDevadoss, Postnikov, FeichtnerSturmfels, Zelevinsky} (see \cref{subsec:graphAssociahedra}).
+In the present paper, we explore specifically the non-kissing complexes of gentle algebras introduced in~\cite{PaluPilaudPlamondon-nonkissing} (see \cref{subsec:gentleAssociahedra}) and the graphical nested complexes studied in~\cite{CarrDevadoss, FeichtnerSturmfels, Postnikov, Zelevinsky} (see \cref{subsec:graphAssociahedra}).
 
@@
 A fan is \defn{essential} if the intersection of its cones is the origin, \defn{complete} if the union of its cones covers~$\R^n$, and \defn{simplicial} if all its cones are generated by dimension many rays.}~$\Fan$ in~$\R^n$.
-Let~$\b{G}$ the $N \times n$-matrix whose rows are (representative vectors of) the rays of~$\Fan$ and let~$\b{K}$ be a $(N-n) \times N$-matrix that spans the left kernel of~$\b{G}$ (\ie $\b{K}\b{G} = 0$).
+Let~$\b{G}$ be the $N \times n$-matrix whose rows are (representative vectors of) the rays of~$\Fan$ and let~$\b{K}$ be a $(N-n) \times N$-matrix that spans the left kernel of~$\b{G}$ (\ie $\b{K}\b{G} = 0$).
 For any height vector~$\b{h} \in \R^N$, we define the polytope\footnote{A \defn{polytope} is the convex hull of finitely many points or equivalently, a bounded intersection of finitely many closed affine half-spaces.}
@@
 \end{gather*}
-where $H^>_{ij}$ denotes the halfspace defined by the inequality corresponding to the two adjacent maximal cones~$i$ and~$j$.
+where $H^>_{xy}$ denotes the halfspace defined by the inequality corresponding to the two adjacent maximal cones~$x$ and~$y$.
 %Note that the inequalities~$H^>_{ae}$ and~$H^>_{de}$ are redundant, while the other three define facets, so that the extremal adjacent pairs are~$(a,b)$, $(b,c)$ and~$(c,d)$.
@@
 All fans considered in \cref{sec:gvectorFans} have the \defn{unique exchange relation property}: the linear dependence ${\displaystyle\sum}_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \ray[s] = 0$ only depends on the exchanged rays~$\ray[r]$ and~$\ray[r]'$, not on the maximal adjacent cones~$\rays$ and~$\rays'$.
-We then write~$\coefficient[{\ray[s]}][\ray][\ray']$ instead of~$\coefficient[{\ray[s]}][\rays][\rays']$ and we call \defn{extremal adjacent pair} of~$\Fan$ the pairs of exchangeable rays~$\{\ray, \ray'\}$ of~$\Fan$ such that the corresponding inequality ${\displaystyle\sum}_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\ray][\ray'] \, \b{h}_{\ray[s]} > 0$ defines a facet of~$\typeCone(\Fan)$.
+We then write~$\coefficient[{\ray[s]}][\ray][\ray']$ instead of~$\coefficient[{\ray[s]}][\rays][\rays']$ and we call \defn{extremal exchangeable pairs} of~$\Fan$ the pairs of exchangeable rays~$\{\ray, \ray'\}$ of~$\Fan$ such that the corresponding inequality ${\displaystyle\sum}_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\ray][\ray'] \, \b{h}_{\ray[s]} > 0$ defines a facet of~$\typeCone(\Fan)$.
 
@@
 \label{prop:alternativePolytopalRealization}
-The affine map~$\Psi: \R^n \to \R^N$ defined by~$\Psi(\b{x}) = \b{h} - G\b{x}$ sends the polytope~$P_\b{h} \eqdef \set{\b{x} \in \R^n}{\b{G}\b{x} \le \b{h}}$ to the polytope~$Q_\b{h} \eqdef \set{\b{z} \in \R^N}{\b{K}\b{z} = \b{K}\b{h} \text{ and } \b{z} \ge 0}$.
+The map~$\b{x} \in \R^n \mapsto \b{h} - G\b{x} \in \R^N$ is an affine transformation of the polytope~$P_\b{h} \eqdef \set{\b{x} \in \R^n}{\b{G}\b{x} \le \b{h}}$ to the polytope~$Q_\b{h} \eqdef \set{\b{z} \in \R^N}{\b{K}\b{z} = \b{K}\b{h} \text{ and } \b{z} \ge 0}$.
 \end{proposition}
@@
 
-We now study the type cones of the normal fans of three families generalizing the associahedron constructed in~\cite{Loday}: the generalized associahedra of finite type cluster algebras~\cite{FominZelevinsky-ClusterAlgebrasI, FominZelevinsky-ClusterAlgebrasII, FominZelevinsky-ClusterAlgebrasIV, HohlwegLangeThomas, HohlwegPilaudStella}, the gentle associahedra~\cite{PaluPilaudPlamondon-nonkissing}, and the graph associahedra~\mbox{\cite{CarrDevadoss, Postnikov, FeichtnerSturmfels, Zelevinsky}}.
+We now study the type cones of the normal fans of three families generalizing the associahedron constructed in~\cite{Loday}: the generalized associahedra of finite type cluster algebras~\cite{FominZelevinsky-ClusterAlgebrasI, FominZelevinsky-ClusterAlgebrasII, FominZelevinsky-ClusterAlgebrasIV, HohlwegLangeThomas, HohlwegPilaudStella}, the gentle associahedra~\cite{PaluPilaudPlamondon-nonkissing}, and the graph associahedra~\mbox{\cite{CarrDevadoss, FeichtnerSturmfels, Postnikov, Zelevinsky}}.
 %All these families contain the classical associahedra~$\Asso[n]$ constructed in~\cite{Loday}.
@@
 %We start with the classical associahedron.
-A $n$-dimensional \defn{associahedron} is a polytope whose face lattice is the reverse inclusion lattice of dissections (\ie sets of pairwise non-crossing diagonals) of a convex~$(n+3)$-gon.
+An $n$-dimensional \defn{associahedron} is a polytope whose face lattice is the reverse inclusion lattice of dissections (\ie sets of pairwise non-crossing diagonals) of a convex~$(n+3)$-gon.
 In particular, its vertices correspond to triangulations of the $(n+3)$-gon and its facets correspond to internal diagonals of the $(n+3)$-gon.
 Let~$X(n) \eqdef \set{(a,b)}{0 \le a < b \le n+2}$ (resp.~$Y(n) \eqdef \set{(a,b)}{0 \le a < b-2 \le n}$) denote all (resp.~the internal) diagonals.
-The \defn{$\b{g}$-vector} of a diagonal $(a,b) \in X(n)$ is ${\gvector{a,b} \eqdef (n+1) {\displaystyle\sum}_{\,a < \ell < b} \b{e}_\ell - (b-a-1) {\displaystyle\sum}_{\,1 \le \ell \le n+1} \b{e}_\ell}$.
+The \defn{$\b{g}$-vector} of a diagonal $(a,b) \in X(n)$ is ${\gvector{a,b} \eqdef {\displaystyle\sum}_{\,a < \ell < b} \b{e}_\ell - \frac{b-a-1}{n+1} {\displaystyle\sum}_{\,1 \le \ell \le n+1} \b{e}_\ell}$.
 %Note that~$\gvector{a,b} = 0$ if~$(a,b)$ is not internal.
@@
 	\raisebox{.35cm}{\begin{overpic}[scale=.5]{clusterFanA}
+		\put(75,92){$\boxed{\B_\circ \! = \!\! {\tiny\left[\begin{array}{@{}r@{}r@{}r@{}} 0 & -1 & 1 \\ 1 & 0 & -1 \\ -1 & 1 & 0 \end{array}\right]}}$}
 		\put(35,33){${\scriptstyle x_1}$}
@@
     }
-    \vspace{-.1cm}
+    % \vspace{-.1cm}
 	\caption{The facet-defining inequalities of the type cone~$\typeCone \big( \gvectorFan[\B_\circ] \big)$ for the cluster fan of \cref{fig:lodayFans}\,(right).
 See \cref{thm:extremalExchangeablePairsCA}.
-The conventions are similar as in \cref{fig:labelFacetDefiningInequalititiesAsso}.}
+The conventions are similar to \cref{fig:labelFacetDefiningInequalititiesAsso}.}
 	\label{fig:labelFacetDefiningInequalititiesCA}
@@
 
-For~$\{x,x'\} \in \meshes$ and~$y \in \variables$, we denote by~$\coefficient[y][x][x']$ the coefficient of~$\gvectorFull{\B_\circ}{y}$ in the linear dependence among the $\b{g}$-vectors~$\gvectorFull{\B_\circ}{x}$ and~$\gvectorFull{\B_\circ}{x'}$.
-In other words, by \cref{lem:dependenceMesh}, if~${(\B, \cluster)}$ and~${(\B', \cluster')}$ are for two adjacent seeds with~${\cluster \ssm \{x\} = \cluster' \ssm \{x'\}}$, we have~$\coefficient[y][x][x'] = |b_{xy}|$ for~$y \in \cluster \cap \cluster'$ and~$\coefficient[y][x][x'] = 0$ otherwise.
-The next statement is proved in~\cite[Sect.~3]{PadrolPaluPilaudPlamondon} using techniques from the quiver representation theory.
+For~$\{x,x'\} \in \meshes$ and~$y \in \variables$, we denote by~$\coefficient[y][x][x']$ the coefficient of~$\gvectorFull{\B_\circ}{y}$ in the linear dependence of \cref{lem:dependenceMesh}.
+% among the $\b{g}$-vectors~$\gvectorFull{\B_\circ}{x}$ and~$\gvectorFull{\B_\circ}{x'}$.
+%In other words, by \cref{lem:dependenceMesh}, if~${(\B, \cluster)}$ and~${(\B', \cluster')}$ are two adjacent seeds with~${\cluster \ssm \{x\} = \cluster' \ssm \{x'\}}$, we have~$\coefficient[y][x][x'] = |b_{xy}|$ for~$y \in \cluster \cap \cluster'$ and~$\coefficient[y][x][x'] = 0$ otherwise.
+The next statement is proved in~\cite[Sect.~3]{PadrolPaluPilaudPlamondon} using techniques from quiver representation theory.
 
@@
 Using \cref{thm:meshMutations} as a blackbox, we describe the facets of the type cone.
-See \cref{fig:labelFacetDefiningInequalititiesAsso}.
+See \cref{fig:labelFacetDefiningInequalititiesCA}.
 %, and thus all polytopal realizations, of the cluster fans of finite type cluster algebras.
@@
 \label{thm:extremalExchangeablePairsCA}
-For any finite type exchange matrix~$\B_\circ$, the type cone~$\typeCone \big( \gvectorFan[\B_\circ] \big)$ is simplicial and the non-initial mesh mutations are the extremal adjacent pairs of the cluster fan~$\gvectorFan[\B_\circ]$.
+For any finite type exchange matrix~$\B_\circ$, the type cone~$\typeCone \big( \gvectorFan[\B_\circ] \big)$ is simplicial and the non-initial mesh mutations are the extremal exchangeable pairs of the cluster fan~$\gvectorFan[\B_\circ]$.
 \end{theorem}
@@
 A \defn{substring} of a walk~$\smash{\omega = \alpha_1^{\varepsilon_1} \cdots \alpha_\ell^{\varepsilon_\ell}}$ of~$\quiver$ is a string~$\smash{\sigma = \alpha_{i+1}^{\varepsilon_{i+1}} \cdots \alpha_{j-1}^{\varepsilon_{j-1}}}$ of~$\quiver$ for some indices~$1 \le i < j \le \ell$.
-We say that the substring~$\smash{\sigma = \alpha_{i+1}^{\varepsilon_{i+1}} \cdots \alpha_{j-1}^{\varepsilon_{j-1}}}$ is \defn{at the bottom} (resp.~\defn{on top}) of the walk~$\omega = \alpha_1^{\varepsilon_1} \cdots \alpha_\ell^{\varepsilon_\ell}$ if~$\varepsilon_i = 1$ and~$\varepsilon_j = -1$ (resp.~if~$\varepsilon_i = -1$ and~$\varepsilon_j = 1$).
+The substring~$\smash{\sigma = \alpha_{i+1}^{\varepsilon_{i+1}} \cdots \alpha_{j-1}^{\varepsilon_{j-1}}}$ is \defn{at the bottom} (resp.~\defn{on top}) of the walk~$\omega = \alpha_1^{\varepsilon_1} \cdots \alpha_\ell^{\varepsilon_\ell}$ if~$\varepsilon_i = 1$ and~$\varepsilon_j = -1$ (resp.~if~$\varepsilon_i = -1$ and~$\varepsilon_j = 1$).
 In other words the two arrows of~$\omega$ incident to the endpoints of~$\sigma$ point towards~$\sigma$ (resp.~outwards from~$\sigma$).
-We denote by~$\Sigma_\bottom(\omega)$ and~$\Sigma_\top(\omega)$ the sets of bottom and top substrings of~$\omega$ respectively.
+We denote by~$\Sigma_\bottom(\omega)$ and~$\Sigma_\top(\omega)$ the sets of bottom and top substrings of~$\omega$.
 
@@
 	\caption{The facet-defining inequalities of the type cone~$\typeCone \big( \gvectorFan[\quiver] \big)$ for the non-kissing fan of \cref{fig:nonkissingFans}\,(right).
-The conventions are similar as in \cref{fig:labelFacetDefiningInequalititiesAsso}.}
+The conventions are similar to \cref{fig:labelFacetDefiningInequalititiesAsso}.}
 	\label{fig:labelFacetDefiningInequalititiesNKC}
@@
 \begin{compactitem}
-\item \defn{brick} if any (non necessarily oriented) cycle of~$\quiver$ contains at least two relations in~$I$. %, or equivalently, no walk on~$\quiver$ is self-kissing.
+\item \defn{brick} if any (non necessarily oriented) cycle of~$\quiver$ contains at least two relations in~$I$, %, or equivalently, no walk on~$\quiver$ is self-kissing.
 \item \defn{$2$-acyclic} if it contains no cycle of length~$2$.
@@
 
-We now consider the graph associahedra studied in~\cite{CarrDevadoss, Postnikov, FeichtnerSturmfels, Zelevinsky}.
+We finally consider the graph associahedra studied in~\cite{CarrDevadoss, FeichtnerSturmfels, Postnikov, Zelevinsky}.
 Again, we briefly recall all definitions needed here as they are purely combinatorial.
 
-Let~$\graphG$ be a graph on~$\ground$.
+Let~$\graphG$ be a graph with vertex set~$\ground$.
 %Let~$\connectedComponents(\graphG)$ be the set of connected components of~$\graphG$ and let $n \eqdef |\ground|-|\connectedComponents(\graphG)|$.
 A \defn{tube} of~$\graphG$ is a connected induced subgraph of~$\graphG$.
-Le~$\tubes$ denote the set of tubes of~$\graphG$.
+Let~$\tubes$ denote the set of tubes of~$\graphG$.
 The inclusion maximal tubes of~$\graphG$ are its connected components~$\connectedComponents(\graphG)$.
@@
 
-\item the nested fan is the normal fan of a polytope~$\Asso[\graphG]$, called \defn{graph associahedron}, constructed in~\cite{CarrDevadoss, Postnikov, FeichtnerSturmfels, Zelevinsky}.
+\item the nested fan is the normal fan of a polytope~$\Asso[\graphG]$, called \defn{graph associahedron}, constructed in~\cite{CarrDevadoss, FeichtnerSturmfels, Postnikov, Zelevinsky}.
 For instance, the permutahedra, associahedra and cyclohedra are graph associahedra of complete graphs, paths, and cycles respectively.

### 2020-03-14 thirdPaper/draft/typeConeAssociahedra.tex
correction FPSAC + linearity -> lineality

@@
 A fan is \defn{simplicial} if all its cones are, \defn{complete} if the union of its cones covers the ambient space~$\R^d$, and \defn{essential} if it contains the cone~$\{\b{0}\}$.
-Note that every complete fan is the product of an essential fan with its linearity space.
+Note that every complete fan is the product of an essential fan with its lineality space.
 For two fans~$\Fan, \cal{G}$ in~$\R^d$, we say that~$\Fan$ \defn{refines}~$\cal{G}$ (and that~$\cal{G}$ \defn{coarsens}~$\Fan$) if every cone of~$\Fan$ is contained in a cone of~$\cal{G}$.
@@
 
-Note that the type cone is an open cone and contains a linearity subspace of dimension~$n$ (it is invariant by translation in~$\b{G} \R^n$). 
-It is sometimes useful to get rid of the linearity space by considering the projection~$\b{K}\typeCone(\Fan)$.
+Note that the type cone is an open cone and contains a lineality subspace of dimension~$n$ (it is invariant by translation in~$\b{G} \R^n$). 
+It is sometimes useful to get rid of the lineality space by considering the projection~$\b{K}\typeCone(\Fan)$.
 
@@
 It has five rays labeled~$1, \dots, 5$ and five maximal cones labeled~$a,\dots, e$.
-Its type cone~$\typeCone(\Fan)$ lies in~$\R^5$, but has a $2$-dimensional linearity space.
+Its type cone~$\typeCone(\Fan)$ lies in~$\R^5$, but has a $2$-dimensional lineality space.
 The five pairs of adjacent maximal cones of~$\Fan$ give rise to following five defining inequalities for~$\typeCone(\Fan)$:
@@
 \label{rem:dimTypeCone}
-Since the type cone is an~$N$-dimensional cone with a linearity subspace of dimension~$n$, it has at least~$N-n$ facets (thus~$N-n$ extremal adjacent pairs).
+Since the type cone is an~$N$-dimensional cone with a lineality subspace of dimension~$n$, it has at least~$N-n$ facets (thus~$N-n$ extremal adjacent pairs).
 The type cone is \defn{simplicial} when it has precisely $N-n$ facets.
@@
 \item Even if $\Fan$ is essential, not all its polytopal coarsenings need to be.
-Indeed, it can happen that there is a certain polytopal coarsening $\cal{G}$ in which all the cells have a common linearity space.
-In this case, $\cal{G}$ is the normal fan of a lower dimensional polytope (whose codimension is the dimension of the linearity space of $\cal{G}$).
+Indeed, it can happen that there is a certain polytopal coarsening $\cal{G}$ in which all the cells have a common lineality space.
+In this case, $\cal{G}$ is the normal fan of a lower dimensional polytope (whose codimension is the dimension of the lineality space of $\cal{G}$).
 For this to happen, it is necessary (but not sufficient) that there is a positive linear dependence between some rays of $\Fan$.
@@
 Their normal fans have only two cones, one arising as a merging of three cones and one arising as a merging of two cones.
-These fans are not essential, they have a one-dimensional linearity.
+These fans are not essential, they have a one-dimensional lineality space.
 Hence, the corresponding polytopes are not full-dimensional, they are of codimension~$1$.
@@
 \cref{lem:MinkowskiSum} ensures that convex combinations in the type cone correspond to Minkowski combinations of polytopes.
-Actually, the set of weak Minkowski summands of a polytope $P$ with normal fan~$\Fan$ is isomorphic to the closed type cone~$\ctypeCone(\Fan)$ modulo linearity (the cone of weak Minkowski summands was studied by W.~Meyer in~\cite{Meyer}, to see that it is equivalent to the type cone and other formulations, see for example the appendix of~\cite{PostnikovReinerWilliams}).
+Actually, the set of weak Minkowski summands of a polytope $P$ with normal fan~$\Fan$ is isomorphic to the closed type cone~$\ctypeCone(\Fan)$ modulo lineality (the cone of weak Minkowski summands was studied by W.~Meyer in~\cite{Meyer}, to see that it is equivalent to the type cone and other formulations, see for example the appendix of~\cite{PostnikovReinerWilliams}).
 
@@
 Consider the fan~$\gvectorFan[2]$ and~$\gvectorFan[3]$ illustrated in \cref{fig:lodayFans}.
-The type cone of~$\gvectorFan[2]$ lives in~$\R^5$ and has a linearity space of dimension~$2$ (this is the type cone studied in \cref{exm:typeCone,exm:typeConeCoarsenings,exm:typeConeMinkowskiSum}).
+The type cone of~$\gvectorFan[2]$ lives in~$\R^5$ and has a lineality space of dimension~$2$ (this is the type cone studied in \cref{exm:typeCone,exm:typeConeCoarsenings,exm:typeConeMinkowskiSum}).
 It has $3$ facet-defining inequalities (given below), which correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso} and illustrated in \cref{fig:labelFacetDefiningInequalititiesAsso}\,(left).
@@
 
-The type cone of~$\gvectorFan[3]$ lives in~$\R^9$ and has a linearity space of dimension~$3$.
+The type cone of~$\gvectorFan[3]$ lives in~$\R^9$ and has a lineality space of dimension~$3$.
 It has $6$ facet-defining inequalities (given below), which correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso} and illustrated in \cref{fig:labelFacetDefiningInequalititiesAsso}\,(right).
@@
 Consider the cluster fans illustrated in \cref{fig:clusterFans}.
-The type cone of the left fan of \cref{fig:clusterFans} lives in~$\R^9$ and has a linearity space of dimension~$3$.
+The type cone of the left fan of \cref{fig:clusterFans} lives in~$\R^9$ and has a lineality space of dimension~$3$.
 It has $6$ facet-defining inequalities (given below), which correspond to the mesh mutations of \cref{thm:extremalExchangeablePairsCA} as illustrated in \cref{fig:labelFacetDefiningInequalititiesCA1}.
@@
 \noindent
-The type cone of the right fan of \cref{fig:clusterFans} lives in~$\R^{12}$ and has a linearity space of dimension~$3$.
+The type cone of the right fan of \cref{fig:clusterFans} lives in~$\R^{12}$ and has a lineality space of dimension~$3$.
 It has $9$ facet-defining inequalities (given below), which correspond to the mesh mutations of \cref{thm:extremalExchangeablePairsCA} as illustrated in \cref{fig:labelFacetDefiningInequalititiesCA2}.
@@
 Consider the non-kissing fans illustrated in \cref{fig:nonkissingFans}.
-The type cone of the left fan of \cref{fig:nonkissingFans} lives in~$\R^8$ and has a linearity space of dimension~$3$.
+The type cone of the left fan of \cref{fig:nonkissingFans} lives in~$\R^8$ and has a lineality space of dimension~$3$.
 It has $5$ facet-defining inequalities (given below), which correspond to the flips described in \cref{prop:interestingExchangeablePairsNKC,prop:extremalExchangeablePairsNKC} and illustrated in \cref{fig:labelFacetDefiningInequalititiesNKC}\,(left).
@@
 \noindent
-The type cone of the right fan of \cref{fig:nonkissingFans} lives in~$\R^{11}$ and has a linearity space of dimension~$3$.
+The type cone of the right fan of \cref{fig:nonkissingFans} lives in~$\R^{11}$ and has a lineality space of dimension~$3$.
 It has $9$ facet-defining inequalities (given below), which correspond to the flips illustrated in \cref{fig:labelFacetDefiningInequalititiesNKC}\,(right).
@@
 Consider the nested fans illustrated in \cref{fig:nestedFans}.
-The type cone of the left fan lives in~$\R^{13}$, has a linearity space of dimension~$3$ and $19$ facet-defining inequalities (given below). In particular, it is not simplicial.
+The type cone of the left fan lives in~$\R^{13}$, has a lineality space of dimension~$3$ and $19$ facet-defining inequalities (given below). In particular, it is not simplicial.
 
@@
 \noindent
-The type cone of the right fan lives in~$\R^{11}$, has a linearity space of dimension~$3$ and $12$ facet-defining inequalities (given below). In particular, it is not simplicial.
+The type cone of the right fan lives in~$\R^{11}$, has a lineality space of dimension~$3$ and $12$ facet-defining inequalities (given below). In particular, it is not simplicial.
 

### 2020-04-03 thirdPaper/draft/typeConeAssociahedra.tex
removing graph associahedra

--- 2019-10-24 thirdPaper/draft/typeConeAssociahedra.tex
@@
 
-\subjclass[2010]{13F60, 16G20, 18E10, 18E30, 52B11 (primary), 52B35, 05E15 (secondary)}
-
 \author{Arnau Padrol}
@@
 
-Moreover, we use a similar approach to study the space of polytopal realizations of the $\b{g}$-vector fans of other generalizations of the associahedron.
-For non-kissing complexes (a.k.a.
-support $\tau$-tilting complexes) of gentle algebras, we show that the space of realizations of the non-kissing fan is simplicial when the gentle bound quiver is brick and $2$-acyclic, and we describe in this case its facet-defining inequalities in terms of mesh mutations.
-For graphical nested complexes, we show that the space of realizations of the nested fan is simplicial only in the case of the associahedron, and we describe its facet-defining inequalities in general.
+Moreover, we use a similar approach to study the space of polytopal realizations of the $\b{g}$-vector fans of another generalization of the associahedron: non-kissing complexes (a.k.a.
+support $\tau$-tilting complexes) of gentle algebras.
+We show that the space of realizations of the non-kissing fan is simplicial when the gentle bound quiver is brick and $2$-acyclic, and we describe in this case its facet-defining inequalities in terms of mesh mutations.
 
@@
 \medskip
-\enlargethispage{.1cm}
 Besides revisiting the construction of~\cite{ArkaniHamedBaiHeYan, BazierMatteDouvilleMousavandThomasYildirim} and extending it to any initial seed (acyclic or not) in any finite type cluster algebra (simply-laced or not), our type cone approach is also successful when applied to the $\b{g}$-vector fans of other families of generalizations of the associahedron.
-In the present paper, we explore specifically two families of such generalizations.
-
-\smallskip
-\begin{itemize}
-\item \textbf{Gentle associahedra} were constructed in~\cite{PaluPilaudPlamondon-nonkissing} as polytopal realizations of finite non-kissing complexes of gentle bound quivers.
-These complexes encompass two families of simplicial complexes studied independently in the literature: on the one hand the grid associahedra introduced by T.~K.~Petersen, P.~Pylyavskyy and D.~Speyer in~\cite{PetersenPylyavskyySpeyer} for a staircase shape, studied by F.~Santos, C.~Stump and V.~Welker~\cite{SantosStumpWelker} for rectangular shapes, and extended by T.~McConville in~\cite{McConville} for arbitrary grid shapes; and on the other hand the Stokes polytopes and accordion associahedra studied by Y.~Baryshnikov~\cite{Baryshnikov}, F.~Chapoton~\cite{Chapoton-quadrangulations}, A.~Garver and T.~McConville~\cite{GarverMcConville} and T.~Manneville and V.~Pilaud~\cite{MannevillePilaud-accordion}.
+In the present paper, we explore specifically \textbf{Gentle associahedra}.
+These complexes where constructed in~\cite{PaluPilaudPlamondon-nonkissing} as polytopal realizations of finite non-kissing complexes of gentle bound quivers.
+They encompass two families of simplicial complexes studied independently in the literature: on the one hand the grid associahedra introduced by T.~K.~Petersen, P.~Pylyavskyy and D.~Speyer in~\cite{PetersenPylyavskyySpeyer} for a staircase shape, studied by F.~Santos, C.~Stump and V.~Welker~\cite{SantosStumpWelker} for rectangular shapes, and extended by T.~McConville in~\cite{McConville} for arbitrary grid shapes; and on the other hand the Stokes polytopes and accordion associahedra studied by Y.~Baryshnikov~\cite{Baryshnikov}, F.~Chapoton~\cite{Chapoton-quadrangulations}, A.~Garver and T.~McConville~\cite{GarverMcConville} and T.~Manneville and V.~Pilaud~\cite{MannevillePilaud-accordion}.
 The latter, sometimes called accordiohedra, have also~recently appeared in the mathematical physics litterature concerning scattering amplitudes~\cite{BanerjeeLaddhaRaman-StokesPolytopes, Raman-PositiveGeometry}, with realizations inspired by those in~\cite{ArkaniHamedBaiHeYan}.
@@
 \smallskip
-\enlargethispage{.2cm}
-\item \textbf{Graph associahedra} were defined by M.~Carr and S.~Devadoss~\cite{CarrDevadoss} in connection to C.~De Concini and C.~Procesi's wonderful arrangements~\cite{DeConciniProcesi}.
-As illustrated in \cref{fig:specialGraphAssociahedra}, the graph associahedra of certain special families of graphs coincide with well-known families of polytopes: complete graph associahedra are permutahedra, path associahedra are classical associahedra, cycle associahedra are cyclohedra, and star associahedra are stellohedra.
-The graph associahedra were extended to the nestohedra, which are simple polytopes realizing the nested complex of arbitrary building sets~\cite{Postnikov, FeichtnerSturmfels}.
-Graph associahedra and nestohedra have been geometrically realized in different ways: by successive truncations of faces of the standard simplex~\cite{CarrDevadoss}, as Minkowski sums of faces of the standard simplex~\cite{Postnikov, FeichtnerSturmfels}, or from their normal fans by exhibiting explicit inequality descriptions~\cite{Devadoss, Zelevinsky}.
-All these realizations have the same normal fan, called nested fan.
-We study the type cones of these nested fans (see \cref{subsec:typeConeGA}): we describe their facet-defining inequalities in terms of certain specific pairs of neighboring tubings and count them for the specific families of graph associahedra described earlier.
-For instance the type cone of the permutahedron coincides with the classical submodular functions on~$2^{[n]}$, described by~$2^{n-2} \binom{n}{2}$ inequalities.
-In fact, we observe that the type cone of a graphical nested fan is never simplicial except in the case of the classical associahedron (when the graph is the path).
-Nevertheless, our results give a non-redundant description of all polytopal realizations of the graphical nested fans.
-\end{itemize}
-
-\smallskip
 Further families of generalizations of the associahedron certainly deserve to be studied with our type cone approach.
-We are investigating in particular brick polytopes~\cite{PilaudSantos-brickPolytope, PilaudStump-brickPolytope} and quotientopes~\cite{Reading-latticeCongruences, Reading-CambrianLattices, PilaudSantos-quotientopes}.
+We are investigating in particular graph associahedra~\cite{CarrDevadoss, Postnikov, FeichtnerSturmfels, Zelevinsky}, brick polytopes~\cite{PilaudSantos-brickPolytope, PilaudStump-brickPolytope} and quotientopes~\cite{Reading-latticeCongruences, Reading-CambrianLattices, PilaudSantos-quotientopes}.
 In fact, as already mentioned, it seems sometimes easier to find all polytopal realizations of a fan (by describing its type cone in terms of certain specific pairs of adjacent maximal cones) than to identify one specific explicit realization.
 This is clearly the case when the type cone is simplicial as illustrated by the results of this paper: we naturally obtained all polytopal realizations of the $\b{g}$-vector fans of cluster algebras from cyclic seeds and of gentle algebras whose polytopality was only established very recently~\cite{HohlwegPilaudStella, PaluPilaudPlamondon-nonkissing}.
-Even when the type cone is not simplicial, describing the type cone sometimes leads to relevant explicit realizations of the fan, as we illustrate on graph associahedra (see \cref{exm:constructionsGA}).
+% Even when the type cone is not simplicial, describing the type cone sometimes leads to relevant explicit realizations of the fan, as we illustrate on graph associahedra (see \cref{exm:constructionsGA}).
 We believe that this approach gives reasonable hope that the polytopality of further fans could in the future be established using our type cone approach.
@@
 This gives a new point of view on~\cite{ArkaniHamedBaiHeYan,BazierMatteDouvilleMousavandThomasYildirim}, illustrated in \cref{subsec:typeConeAsso} for classical associahedra, that we then apply to two families of~$\b{g}$-vector fans generalizing the~$\b{g}$-vector fans of classical associahedra: the~$\b{g}$-vector fans of cluster algebras of finite type (generalized associahedra) in~\cref{subsec:typeConeCA}, and the~$\b{g}$-vector fans of gentle algebras (non-kissing associahedra, non-crossing associahedra, generalized accordiohedra) in~\cref{subsec:typeConeNKC}.
-We also completely describe the facets of the type cone for graph associahedra in~\cref{subsec:typeConeGA}, to which our strategy does not apply, as only the classical associahedron has a simplicial type cone.
 
@@
 \[
-R_{\b{\ell}}(\B_\circ) \eqdef \Bigset{\b{z} \in \R^{\principalVariables}}{\b{z} \ge 0 \text{ and } \b{z}_x + \b{z}_{x'} - \sum_{y \in \principalVariables} \coefficient[y][x][x'] \, \b{z}_{y} = \b{\ell}_{\{x,x'\}} \text{ for all } \{x,x'\} \in \meshes}
+R_{\b{\ell}}(\B_\circ) \eqdef \Bigset{\b{z} \in \R^{\principalVariables}}{\b{z} \ge 0 \text{ and } \b{z}_x + \b{z}_{x'} - \sum_{y \in \principalVariables} \alpha_{x,x',y} \, \b{z}_{y} = \b{\ell}_{\{x,x'\}} \text{ for all } \{x,x'\} \in \meshes}
 \]
@@
 Here, $\meshes$ denotes the set of all pairs~$\{x,x'\}$ related by non-initial mesh mutations (\cref{def:meshMutation}), and~$\principalVariables$ the set of cluster variables.
-For $\{x,x'\} \in \meshes$ and $y \in \principalVariables$, the coefficient $\coefficient[y][x][x']$ is defined as follows: $\coefficient[y][x][x']$ is set to be~$|b_{xy}|$ if~$y\in X\cap X'$ and $0$ otherwise, where~$X,X'$ are any two clusters such that~$X \ssm \{x\} = X' \ssm \{x'\}$.
-By the unique exchange relation property, the coefficients~$\coefficient[y][x][x']$ do not depend on the specific choice of clusters~$X,X'$.
+For $\{x,x'\} \in \meshes$ and $y \in \principalVariables$, the coefficient $\alpha_{x,x',y}$ is defined as follows: $\alpha_{x,x',y}$ is set to be~$|b_{xy}|$ if~$y\in X\cap X'$ and $0$ otherwise, where~$X,X'$ are any two clusters such that~$X \ssm \{x\} = X' \ssm \{x'\}$.
+By the unique exchange relation property, the coefficients~$\alpha_{x,x',y}$ do not depend on the specific choice of clusters~$X,X'$.
 
@@
 \end{coro:simplicialTypeConeNKC}
-
-\para{Graphical nested complexes and graph associahedra}
-(\cref{subsec:typeConeGA})
-
-\noindent
-Even though graph associahedra do not have simplicial type cones except for the path (\cref{prop:simplicialnestedfan}), we provide the following non-redundant characterization of the type cones of all graphical nested fans.
-
-\newtheorem*{coro:typeconenestedfan}{\cref{coro:typeconenestedfan}}
-\begin{coro:typeconenestedfan}
-Consider a graph~$\graphG$ on~$\ground$ with tubes~$\tubes$. 
-Then, for a height vector~$\b{h} \in \R^{\tubes}$, the nested fan~$\gvectorFan[\graphG]$ is the normal fan of the graph associahedron
-\[
-\set{\b{x} \in \R^\ground}{\dotprod{\gvector{\tube}}{\b{x}} \le \b{h}_{\tube} \text{ for any tube } \tube \in \tubes}
-\]
-if and only if~$\b{h}_{\varnothing} = \b{h}_{\graphG} = 0$ and
- $\b{h}_{\tube[s] \ssm \{v'\}} + \b{h}_{\tube[s] \ssm \{v\}} > \b{h}_{\tube[s]} + \b{h}_{\tube[s] \ssm \{v, v'\}}$ for any tube~$\tube[s] \in \tubes$ and distinct non-disconnecting vertices~$v,v'$ of~$\tube[s]$.
-\end{coro:typeconenestedfan}
 
@@
 	\node[diamond,aspect=3, text width=5cm, minimum height=1cm, align=center, draw=blue, fill=blue!10, inner sep=-2] (I1) at (0,1.5) {\ref{part:geometry}.\ref{sec:typeCone} -- Simplicial type cone strategy};
-	\node[rectangle, draw=black, fill=black!10, align=center] (I21) at (-6,0) {\ref{part:geometry}.\ref{subsec:typeConeAsso} -- Toy example \\ Classical associahedra};
-	\node[rectangle, draw=orange, fill=orange!10, align=center, text width=5cm] (I22) at (-3,-1.5) {\ref{part:geometry}.\ref{subsec:typeConeCA} -- Cluster algebras \\ \& generalized associahedra};
-	\node[rectangle, draw=green, fill=green!10, align=center, text width=5cm] (I23) at (3,-1.5) {\ref{part:geometry}.\ref{subsec:typeConeNKC} -- Gentle algebras \\ \& generalized accordiohedra};
-	\node[rectangle, draw=red, fill=red!10, align=center, text width=5.4cm] (I24) at (7,0) {\ref{part:geometry}.\ref{subsec:typeConeGA} -- Graphical nested complexes \\ \& graph associahedra};
+	\node[rectangle, draw=black, fill=black!10, align=center] (I21) at (-6,-1.5) {\ref{part:geometry}.\ref{subsec:typeConeAsso} -- Toy example \\ Classical associahedra};
+	\node[rectangle, draw=orange, fill=orange!10, align=center, text width=5cm] (I22) at (0,-1.5) {\ref{part:geometry}.\ref{subsec:typeConeCA} -- Cluster algebras \\ \& generalized associahedra};
+	\node[rectangle, draw=green, fill=green!10, align=center, text width=5cm] (I23) at (6,-1.5) {\ref{part:geometry}.\ref{subsec:typeConeNKC} -- Gentle algebras \\ \& generalized accordiohedra};
+% 	\node[rectangle, draw=red, fill=red!10, align=center, text width=5.4cm] (I24) at (7,0) {\ref{part:geometry}.\ref{subsec:typeConeGA} -- Graphical nested complexes \\ \& graph associahedra};
 	\node[ellipse, draw=orange, fill=orange!10, align=center, text width=4.9cm, inner sep=2, minimum height=1cm] (II1) at (-4.5,-4.2) {\ref{part:algebra}.\ref{sec:clusterCategories} -- Cluster categories};
 	\node[ellipse, draw=green, fill=green!10, align=center, text width=4.9cm, inner sep=0, minimum height=1cm] (II2) at (4.5,-4.2) {\ref{part:algebra}.\ref{sec:extricats} -- Extriangulated categories};
-	\draw[decorate, decoration={shape backgrounds, shape=dart, shape size=2mm, shape evenly spread=8}, draw=blue, fill=blue!10] (I1.180) to [bend right, looseness=1.1] node[label={[shift={(.6,-1.5)}]applied to}]{} (I21.90);
-	\draw[decorate, decoration={shape backgrounds, shape=dart, shape size=2mm, shape evenly spread=8}, draw=blue, fill=blue!10] (I1.220) to [bend right, looseness=.6] node[label={[shift={(.6,-1.5)}]applied to}]{} (I22.90);
-	\draw[decorate, decoration={shape backgrounds, shape=dart, shape size=2mm, shape evenly spread=8}, draw=blue, fill=blue!10] (I1.320) to [bend left, looseness=.6] node[label={[shift={(-.6,-1.5)}]applied to}]{} (I23.90);
-	\draw[decorate, decoration={shape backgrounds, shape=dart, shape size=2mm, shape evenly spread=10}, draw=blue, fill=blue!10] (I1.0) to [bend left, looseness=1.1] (I24.90);
-	\draw[decorate, decoration={markings, mark=at position 0.5 with {\draw [red, ultra thick,-] ++ (-.3,-.3)  -- ( .3, .3); \draw [red, ultra thick,-] ++ (-.3, .3)  -- ( .3,-.3);}}] (I1.0) to [bend left, looseness=1.1] node[label={[shift={(-.4,-1.7)}]not applicable to}]{} (I24.90);
+	\draw[decorate, decoration={shape backgrounds, shape=dart, shape size=2mm, shape evenly spread=8}, draw=blue, fill=blue!10] (I1.180) to [bend right, looseness=1.1] node[label={[shift={(-1.6,-1.5)}]applied to}]{} (I21.90);
+	\draw[decorate, decoration={shape backgrounds, shape=dart, shape size=2mm, shape evenly spread=3}, draw=blue, fill=blue!10] (I1.270) to node[label={[shift={(1,-1.)}]applied to}]{} (I22.90);
+	\draw[decorate, decoration={shape backgrounds, shape=dart, shape size=2mm, shape evenly spread=8}, draw=blue, fill=blue!10] (I1.360) to [bend left, looseness=1.1] node[label={[shift={(1.6,-1.5)}]applied to}]{} (I23.90);
+% 	\draw[decorate, decoration={shape backgrounds, shape=dart, shape size=2mm, shape evenly spread=10}, draw=blue, fill=blue!10] (I1.0) to [bend left, looseness=1.1] (I24.90);
+% 	\draw[decorate, decoration={markings, mark=at position 0.5 with {\draw [red, ultra thick,-] ++ (-.3,-.3)  -- ( .3, .3); \draw [red, ultra thick,-] ++ (-.3, .3)  -- ( .3,-.3);}}] (I1.0) to [bend left, looseness=1.1] node[label={[shift={(-.4,-1.7)}]not applicable to}]{} (I24.90);
 	\draw[thick, double distance=2pt, -implies] (I22.270)+(0,-1.3) to node[semithick, right, outer sep=0, pos=0.65]{used for} (I22.270)+(0,.15);
@@
 	\draw[thick, ->] (II1.0) to node[semithick, above, outer sep=0]{generalizes to} (II2.180);
-	\draw let \p{top}=(I1.90), \p{left}=(I21.180), \p{bottom}=([shift={(0,-.15)}]I22.270), \p{right}=(I24.0) in (\x{left}, \y{top}) -- (\x{left}, \y{bottom}) -- (\x{right}, \y{bottom}) -- (\x{right}, \y{top}) -- (\x{left}, \y{top});
-	\draw let \p{top}=([shift={(0,.2)}]II1.90), \p{left}=(I21.180), \p{bottom}=(II1.270), \p{right}=(I24.0) in (\x{left}, \y{top}) -- (\x{left}, \y{bottom}) -- (\x{right}, \y{bottom}) -- (\x{right}, \y{top}) -- (\x{left}, \y{top});
+	\draw let \p{top}=(I1.90), \p{left}=(I21.180), \p{bottom}=([shift={(0,-.15)}]I22.270), \p{right}=(I23.0) in (\x{left}, \y{top}) -- (\x{left}, \y{bottom}) -- (\x{right}, \y{bottom}) -- (\x{right}, \y{top}) -- (\x{left}, \y{top});
+	\draw let \p{top}=([shift={(0,.2)}]II1.90), \p{left}=(I21.180), \p{bottom}=(II1.270), \p{right}=(I23.0) in (\x{left}, \y{top}) -- (\x{left}, \y{bottom}) -- (\x{right}, \y{bottom}) -- (\x{right}, \y{top}) -- (\x{left}, \y{top});
 	\path let \p{top}=(I1.90) in node[rectangle, draw, fill=white, align=left, inner sep=4] (I) at (-6.15, \y{top}) {\ref{part:geometry} -- Discrete geometry};
@@
 Fix an essential complete simplicial fan~$\Fan$ in~$\R^n$.
-Let~$\b{G}$ be the $N \times n$-matrix whose rows are the rays of~$\Fan$ and let~$\b{K}$ be a $(N-n) \times N$-matrix that spans the left kernel of~$\b{G}$ (\ie $\b{K}\b{G} = 0$).
+Let~$\b{G}$ the $N \times n$-matrix whose rows are the rays of~$\Fan$ and let~$\b{K}$ be a $(N-n) \times N$-matrix that spans the left kernel of~$\b{G}$ (\ie $\b{K}\b{G} = 0$).
 For any height vector~$\b{h} \in \R^N$, we define the polytope
@@
 
-We still consider an essential complete simplicial fan~$\Fan$ in~$\R^n$, the $N \times n$-matrix~$\b{G}$ whose rows are the rays of~$\Fan$, and the $(N-n) \times N$-matrix~$\b{K}$ which spans the left kernel of~$\b{G}$ (\ie $\b{K}\b{G} = 0$).
+We still consider an essential complete simplicial fan~$\Fan$ in~$\R^n$, the $N \times n$-matrix~$\b{G}$ whose rows are the rays of~$\Fan$, and an $(N-n) \times N$-matrix~$\b{K}$ which spans the left kernel of~$\b{G}$ (\ie $\b{K}\b{G} = 0$).
 
@@
 
+Note that~$\b{K}$ is only defined up to linear transformation, as it depends on the choice of a basis of the left kernel of~$\b{G}$.
+Note also that, by construction, the coefficients of the normal vectors of the facets of~$\typeCone(\Fan)$ arise from a linear dependence among the $\b{g}$-vectors, and hence belong to this kernel.
+When~$\typeCone(\Fan)$ is simplicial, its $(N-n)$ facets are necessarily linearly independent, and hence form a basis.
+They provide a particularly interesting choice of~$\b{K}$.
+
 \begin{corollary}
@@
 
-\section{Applications to three generalizations of the associahedron}
+\section{Applications to two generalizations of the associahedron}
 \label{sec:applications}
 
-In this section, we study the type cones of complete simplicial fans arising as normal fans of three families of generalizations of the associahedron: the generalized associahedra of finite type cluster algebras~\cite{FominZelevinsky-ClusterAlgebrasI, FominZelevinsky-ClusterAlgebrasII, FominZelevinsky-ClusterAlgebrasIV, HohlwegLangeThomas, HohlwegPilaudStella}, the gentle associahedra~\cite{PaluPilaudPlamondon-nonkissing}, and the graph associahedra~\cite{CarrDevadoss, Postnikov, FeichtnerSturmfels, Zelevinsky}.
-All these families contain the classical associahedra~$\Asso[n]$ constructed in~\cite{ShniderSternberg, Loday}.
+In this section, we study the type cones of complete simplicial fans arising as normal fans of two families of generalizations of the associahedron: the generalized associahedra of finite type cluster algebras~\cite{FominZelevinsky-ClusterAlgebrasI, FominZelevinsky-ClusterAlgebrasII, FominZelevinsky-ClusterAlgebrasIV, HohlwegLangeThomas, HohlwegPilaudStella} and the gentle associahedra~\cite{PaluPilaudPlamondon-nonkissing}.
+Both families contain the classical associahedra~$\Asso[n]$ constructed in~\cite{ShniderSternberg, Loday}.
 
@@
 It has $6$ facet-defining inequalities (given below), which correspond to the mesh mutations of \cref{thm:extremalExchangeablePairsCA} as illustrated in \cref{fig:labelFacetDefiningInequalititiesCA1}.
+
+\arnau{Vincent, can you please check the coordinates? C.\ Stump thought that two facets had some typo (a $\pm 1$ was in the wrong column)}
 
@@
 
-For~$\{x,x'\} \in \meshes$ and~$y \in \principalVariables$, we denote by~$\coefficient[y][x][x']$ the coefficient of~$\gvectorFull{\B_\circ}{y}$ in the linear dependence between the $\b{g}$-vectors~$\gvectorFull{\B_\circ}{x}$ and~$\gvectorFull{\B_\circ}{x'}$.
-In other words, according to \cref{lem:dependenceMesh}, if~${(\B, \cluster)}$ and~${(\B', \cluster')}$ are two adjacent seeds with~$\cluster \ssm \{x\} = \cluster' \ssm \{x'\}$, we have~$\coefficient[y][x][x'] = |b_{xy}|$ for~$y \in \cluster \cap \cluster'$ and~$\coefficient[y][x][x'] = 0$ otherwise.
+For~$\{x,x'\} \in \meshes$ and~$y \in \principalVariables$, we denote by~$\alpha_{x,x',y}$ the coefficient of~$\gvectorFull{\B_\circ}{y}$ in the linear dependence between the $\b{g}$-vectors~$\gvectorFull{\B_\circ}{x}$ and~$\gvectorFull{\B_\circ}{x'}$.
+In other words, according to \cref{lem:dependenceMesh}, if~${(\B, \cluster)}$ and~${(\B', \cluster')}$ are two adjacent seeds with~$\cluster \ssm \{x\} = \cluster' \ssm \{x'\}$, we have~$\alpha_{x,x',y} = |b_{xy}|$ for~$y \in \cluster \cap \cluster'$ and~$\alpha_{x,x',y} = 0$ otherwise.
 The following statement will be shown in \cref{corollary:proof of prop meshMutations}.
@@
 \[
-R_\b{\ell}(T) \eqdef \Bigset{\b{z} \in \R^{\Delta(n)}}{\begin{array}{l} \b{z} \ge 0 \quad\text{ and }\quad \b{z}_{(a,a+1)} = 0 \text{ for all } a \in \Z/(n+3)\Z \quad\text{ and }\quad \\ \b{z}_{(a,b)} + \b{z}_{(a-1,b-1)} - \b{z}_{(a,b-1)} - \b{z}_{(a-1,b)} = \b{\ell}_{(a,b)} \text{ for all } (a,b) \notin T \end{array}}
+R_\b{\ell}(T) \eqdef \Bigset{\b{z} \in \R^{\Delta(n)}}{\begin{array}{l} \b{z} \ge 0 \quad\text{ and }\quad \b{z}_{(a,b)} = 0 \text{ for all } (a,b) \in T \quad\text{ and }\quad \\ \b{z}_{(a,b)} + \b{z}_{(a-1,b-1)} - \b{z}_{(a,b-1)} - \b{z}_{(a-1,b)} = \b{\ell}_{(a,b)} \text{ for all } (a,b) \notin T \end{array}}
 \]
@@
 
-%%%%%%%%%%%
-
-\subsection{Graphical nested complexes and graph associahedra}
-\label{subsec:typeConeGA}
-
-Graph associahedra were defined by M.~Carr and S.~Devadoss~\cite{CarrDevadoss} in connection to C.~De Concini and C.~Procesi's wonderful arrangements~\cite{DeConciniProcesi}.
-For a given graph~$\graphG$, the $\graphG$-associahedron~$\Asso[\graphG]$ is a simple polytope whose combinatorial structure encodes the connected subgraphs of~$\graphG$ and their nested structure.
-More precisely, the $\graphG$-associahedron is a polytopal realization of the nested complex of~$\graphG$, defined as the simplicial complex of all collections of tubes (connected induced subgraphs) of~$\graphG$ which are pairwise compatible (either nested, or disjoint and non-adjacent).
-As illustrated in \cref{fig:specialGraphAssociahedra}, the graph associahedra of certain special families of graphs coincide with well-known families of polytopes: complete graph associahedra are permutahedra, path associahedra are classical associahedra, cycle associahedra are cyclohedra, and star associahedra are stellohedra.
-The graph associahedra were extended to the \defn{nestohedra}, which are simple polytopes realizing the nested complex of arbitrary building sets~\cite{Postnikov, FeichtnerSturmfels}.
-Graph associahedra and nestohedra have been geometrically realized in different ways: by successive truncations of faces of the standard simplex~\cite{CarrDevadoss}, as Minkowski sums of faces of the standard simplex~\cite{Postnikov, FeichtnerSturmfels}, or from their normal fans by exhibiting explicit inequality descriptions~\cite{Devadoss, Zelevinsky}.
-For a given graph~$\graphG$, the resulting polytopes all have the same normal fan, called nested fan of~$\graphG$: its rays are the characteristic vectors of the tubes, and its cones are generated by characteristic vectors of compatible tubes.
-In this section, we describe the type cone of the nested fan of any graph~$\graphG$.
-
-\hvFloat[floatPos=p, capWidth=h, capPos=r, capAngle=90, objectAngle=90, capVPos=c, objectPos=c]{figure}
-{
-		\begin{tabular}{c@{\;}c@{\;}c@{\;}c}
-			permutahedron &
-			associahedron &
-			cyclohedron &
-			stellohedron \\[.2cm]
-			\includegraphics[scale=.93]{permutahedron} &
-			\includegraphics[scale=.93]{associahedron} &
-			\includegraphics[scale=.93]{cyclohedron} &
-			\includegraphics[scale=.93]{stellohedron} \\[.1cm]
-			\includegraphics[scale=.93]{permutahedronTubings} &
-			\includegraphics[scale=.93]{associahedronTubings} &
-			\includegraphics[scale=.93]{cyclohedronTubings} &
-			\includegraphics[scale=.93]{stellohedronTubings} \\[.2cm]
-			complete graph &
-			path &
-			cycle &
-			star \\[.3cm]
-		\end{tabular}
-}
-{Some classical families of polytopes as graph associahedra. Illustration from~\cite{MannevillePilaud-compatibilityFans}.}
-{fig:specialGraphAssociahedra}
-
-%\begin{figure}[t]
-%	\capstart
-%	\begin{adjustbox}{center}
-%		\begin{tabular}{c@{\;}c@{\;}c@{\;}c}
-%			permutahedron &
-%			associahedron &
-%			cyclohedron &
-%			stellohedron \\
-%			\includegraphics[scale=.6]{permutahedron} &
-%			\includegraphics[scale=.6]{associahedron} &
-%			\includegraphics[scale=.6]{cyclohedron} &
-%			\includegraphics[scale=.6]{stellohedron} \\
-%			\includegraphics[scale=.6]{permutahedronTubings} &
-%			\includegraphics[scale=.6]{associahedronTubings} &
-%			\includegraphics[scale=.6]{cyclohedronTubings} &
-%			\includegraphics[scale=.6]{stellohedronTubings} \\[.1cm]
-%			complete graph &
-%			path &
-%			cycle &
-%			star
-%		\end{tabular}
-%	\end{adjustbox}
-%	\caption{Some classical families of polytopes as graph associahedra. Illustration from~\cite{MannevillePilaud-compatibilityFans}.}
-%	\label{fig:specialGraphAssociahedra}
-%\end{figure}
-
-%%%
-
-\clearpage
-\subsubsection{Nested complex and nested fan of a graph}
-
-We present the definitions and properties of the nested complex of a graph, following ideas from~\cite{CarrDevadoss, Postnikov, FeichtnerSturmfels, Zelevinsky}.
-
-\para{Nested complex}
-%
-Let~$\graphG$ be a graph with vertex set~$\ground$.
-Let~$\connectedComponents(\graphG)$ denote the set of connected components of~$\graphG$ and define~$n \eqdef |\ground|-|\connectedComponents(\graphG)|$.
-A \defn{tube} of~$\graphG$ is a connected induced subgraph of~$\graphG$.
-The set of tubes of~$\graphG$ is denoted by~$\tubes$.
-The inclusion maximal tubes of~$\graphG$ are its connected components~$\connectedComponents(\graphG)$.
-The tubes which are neither empty nor maximal are called \defn{proper}.
-Two tubes~$\tube, \tube'$ of~$\graphG$ are \defn{compatible} if they are either nested (\ie $\tube \subseteq \tube'$ or~$\tube' \subseteq \tube$), or disjoint and non-adjacent (\ie $\tube \cup \tube'$ is not a tube of~$\graphG$).
-A \defn{tubing} on~$\graphG$ is a set~$\tubing$ of pairwise compatible proper tubes of~$\graphG$.
-See \cref{fig:exmNested}.
-The \defn{nested complex} of~$\graphG$ is the simplicial complex~$\nestedComplex(\graphG)$ of all tubings~on~$\graphG$.
-
-\begin{figure}[t]
-	\capstart
-	\centerline{\includegraphics[width=\textwidth]{exmNested}}
-	\caption{Some incompatible tubes (left and middle), and a maximal tubing (right).}
-	\label{fig:exmNested}
-\end{figure}
-
-\para{Nested fan and graph associahedron}
-%
-Let~$(\b{e}_v)_{v \in \ground}$ be the canonical basis of~$\R^\ground$.
-We consider the hyperplane~${\HH \eqdef \bigset{\b{x} \in \R^\ground}{\sum_{w \in W} x_w = 0 \text{ for all } W \in \connectedComponents(\graphG)}}$ and let~$\pi : \R^\ground \to \HH$ denote the orthogonal projection on~$\HH$.
-
-\begin{definition}
-The \defn{$\b{g}$-vector} of a tube~$\tube$ of~$\graphG$ is the projection~$\gvector{\tube} \eqdef \pi \big( \sum_{v \in \tube} \b{e}_v \big)$ of the characteristic vector of~$\tube$.
-We set~$\gvectors{\tubing} \eqdef \set{\gvector{\tube}}{\tube \in \tubing}$ for a tubing~$\tubing$ on~$\graphG$.
-\end{definition}
-
-Note that by definition, $\gvector{\varnothing} = 0$ and $\gvector{W} = 0$ for all connected components~$W \in \connectedComponents(\graphG)$.
-These vectors support a complete simplicial fan realization of the nested complex.
-Examples are illustrated in \cref{fig:nestedFans}.
-
-\begin{figure}[b]
-	\capstart
-	\centerline{\includegraphics[scale=.55]{nestedFans}}
-	\caption{Two nested fans. As the fans are $3$-dimensional, we intersect them with the sphere and stereographically project them from the direction~$(-1,-1,-1)$.}
-	\label{fig:nestedFans}
-\end{figure}
-
-\begin{theorem}[\cite{CarrDevadoss, Postnikov, FeichtnerSturmfels, Zelevinsky}]
-\label{thm:nestedFan}
-For any graph~$\graphG$, the set of cones
-\[
-\gvectorFan[\graphG] \eqdef \set{\R_{\ge 0} \, \gvectors{\tubing}}{\tubing \text{ tubing on } \graphG}
-\]
-is a complete simplicial fan of~$\HH$, called \defn{nested fan} of~$\graphG$, which realizes the nested complex~$\nestedComplex(\graphG)$.
-\end{theorem}
-
-It is proved in~\cite{CarrDevadoss, Devadoss, Postnikov, FeichtnerSturmfels, Zelevinsky} that the nested fan comes from a polytope.
-For any subset~$U \subseteq \ground$, denote by~$\triangle_U \eqdef \conv\set{\b{e}_u}{u \in U}$ the face of the standard simplex~$\triangle_\ground$ corresponding to~$U$.
-
-\begin{theorem}[\cite{CarrDevadoss, Devadoss, Postnikov, FeichtnerSturmfels, Zelevinsky}]
-For any graph~$\graphG$, the nested fan~$\gvectorFan[\graphG]$ is the normal fan of the graph associahedron~$\Asso[\graphG]$.
-It can be constructed as
-\begin{itemize}
-\item the intersection of~$\HH$ with the hyperplanes~$\dotprod{\gvector{\tube}}{\b{x}} \le 3^{|\tube|-2}$ for all tubes~$\tube \in \tubes$~\cite{Devadoss},
-\item the Minkowski sum~$\sum_{\tube \in \tubes} \triangle_{\tube}$ of the faces of the standard simplex corresponding to all tubes of~$\graphG$~\cite{Postnikov}.
-\end{itemize}
-\end{theorem}
-
-\para{Flips in the nested fan}
-%
-The following statement follows from~\cite{MannevillePilaud-compatibilityFans, Zelevinsky}.
-
-\begin{proposition}
-\label{prop:exchangeablePairsGA}
-Let~$\tube, \tube'$ be two tubes of~$\graphG$. Then
-\begin{enumerate}[(i)]
-\item The tubes~$\tube$ and~$\tube'$ are exchangeable if and only if $\tube'$ has a unique neighbor~$v$ in~$\tube \ssm \tube'$ and $\tube$ has a unique neighbor~$v'$ in~$\tube' \ssm \tube$.
-\item For any maximal tubings~$\tubing, \tubing'$ on~$\graphG$ with $\tubing \ssm \{\tube\} = \tubing' \ssm \{\tube'\}$, both~$\tubing \cup \connectedComponents(\graphG)$ and~$\tubing' \cup \connectedComponents(\graphG)$ contain the tube~$\tube \cup \tube'$ and the connected components of~$\tube \cap \tube'$.
-\item The linear dependence between the $\b{g}$-vectors of~$\tubing \cup \tubing'$ is given by
-\[
-\gvector{\tube} + \gvector{\tube'} = \gvector{\tube \cup \tube'} + \sum_{\tube[s] \in \connectedComponents(\tube \cap \tube')} \gvector{\tube[s]}.
-\]
-\item The nested fan of~$\graphG$ has the unique exchange relation property.
-\item The $\b{c}$-vector orthogonal to all $\b{g}$-vectors~$\gvector{\tube[s]}$ for~$\tube[s] \in \tubing \cap \tubing'$ is~$\b{e}_v - \b{e}_{v'}$.
-\end{enumerate}
-\end{proposition}
-
-\begin{proof}
-Points~(i) and~(ii) was proved in~\cite{MannevillePilaud-compatibilityFans}. Point~(iii) follows from the fact that
-\[
-\sum_{v \in \tube} \b{e}_v + \sum_{v \in \tube'} \b{e}_v = \sum_{v \in \tube \cup \tube'} \b{e}_v + \sum_{v \in \tube \cap \tube'} \b{e}_v = \sum_{v \in \tube \cup \tube'} \b{e}_v + \sum_{\substack{\tube[s] \in \connectedComponents(\tube \cap \tube') \\ v \in \tube[s]}} \b{e}_v.
-\]
-Point~(iv) is obtained by combining~(ii) and~(iii).
-Finally for~(v), any tube~$\tube[s] \in \tubing \cap \tubing'$ that contains~$v$ or~$v'$ actually contains both (to be compatible with~$\tube$ and~$\tube'$).
-Therefore, $\gvector{\tube[s]}$ is orthogonal to~$\b{e}_v - \b{e}_{v'}$ for any tube~$\tube[s] \in \tubing \cap \tubing'$.
-\end{proof}
-
-%%%
-
-\subsubsection{Type cones of graphical nested fans}
-
-We now discuss the type cones of the graphical nested fans defined in \cref{thm:nestedFan}.
-We first obtain from \cref{prop:exchangeablePairsGA} the following redundant description.
-
-\begin{corollary}
-\label{coro:typeConeGA}
-For any graph~$\graphG$, the type cone of the nested fan~$\gvectorFan[\graphG]$ is given by
-\[
-\typeCone \big( \gvectorFan[\graphG] \big) = \set{\b{h} \in \R^{\tubes}}{\begin{array}{l} \b{h}_{\tube} = 0 \text{ for any improper tube } \tube \\ \b{h}_{\tube} + \b{h}_{\tube'} > \b{h}_{\tube \cup \tube'} + \sum_{\tube[s] \in \connectedComponents(\tube \cap \tube')} \b{h}_{\tube[s]} \text{ for any exchangeable tubes } \tube, \tube' \end{array}}.
-\]
-\end{corollary}
-
-\begin{example}
-For the complete graph~$\graphG[K]_n$, the admissible height vectors are precisely the submodular functions, \ie the functions~$\b{h} : 2^{[n]} \to \R$ such that~$\b{h}_{\varnothing} = 0$ and~$\b{h}_{A} + \b{h}_{B} > \b{h}_{A \cap B} + \b{h}_{A \cup B}$ for any~$A, B \subseteq [n]$.
-This is precisely the description of the generalized permutahedra introduced by A.~Postnikov in~\cite{Postnikov} and E.-M.~Feichtner and B.~Sturmfels in~\cite{FeichtnerSturmfels}.
-\end{example}
-
-\begin{example}
-\label{exm:typeConeGA}
-Consider the nested fans illustrated in \cref{fig:nestedFans}.
-The type cone of the left fan lives in~$\R^{13}$, has a linearity space of dimension~$3$ and $19$ facet-defining inequalities (given below). In particular, it is not simplicial.
-
-\medskip
-\centerline{$
-\begin{array}{r|c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c}
-\text{tubes} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeA1}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeA2}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeA3}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeA4}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeA5}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeA6}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeA7}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeA8}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeA9}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeA10}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeA11}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeA12}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeA13}}  \\[.6cm]
-\text{$\b{g}$-vectors} & \compactVectorT{1}{0}{0} & \compactVectorT{0}{2}{0} & \compactVectorT{0}{0}{1} & \compactVectorT{0}{2}{-1} & \compactVectorT{1}{-2}{1} & \compactVectorT{1}{-2}{0} & \compactVectorT{1}{0}{-1} & \compactVectorT{-1}{2}{0} & \compactVectorT{-1}{0}{1} & \compactVectorT{-1}{0}{0} & \compactVectorT{0}{-2}{1} & \compactVectorT{0}{-2}{0} & \compactVectorT{0}{0}{-1} \\[.6cm]
-\text{facet}		& 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & -1 & 1 \\
-\text{defining}		& 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 & 0 & 1 & 0 & -1 & 0 \\
-\text{inequalities}	& -1 & 1 & 0 & -1 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 \\
-					& 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & -1 & -1 & 1 & 0 \\
-					& 0 & 0 & 0 & 0 & 0 & -1 & 1 & 0 & 0 & 0 & 0 & 1 & -1 \\
-					& -1 & 1 & -1 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-					& -1 & 0 & 0 & 0 & 1 & -1 & 1 & 0 & 0 & 0 & 0 & 0 & 0 \\
-					& 0 & 1 & -1 & 0 & 0 & 0 & 0 & -1 & 1 & 0 & 0 & 0 & 0 \\
-					& 0 & 0 & -1 & 0 & 1 & 0 & 0 & 0 & 1 & 0 & -1 & 0 & 0 \\
-					& 0 & 0 & 0 & 0 & 1 & -1 & 0 & 0 & 0 & 0 & -1 & 1 & 0 \\
-					& 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & -1 & 1 & 0 & 0 & 0 \\
-					& 0 & 0 & 1 & 0 & -1 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-					& 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & -1 & 0 & 1 & 0 & 0 \\
-					& 1 & 0 & 0 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 0 & 0 & 1 \\
-					& 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 \\
-					& 1 & -1 & 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 \\
-					& 0 & 0 & 0 & 1 & 0 & 0 & 0 & -1 & 0 & 1 & 0 & 0 & -1 \\
-					& 0 & 0 & 0 & 1 & 0 & 1 & -1 & 0 & 0 & 0 & 0 & 0 & 0 \\
-					& 0 & -1 & 1 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\[.2cm]
-\end{array}
-$}
-
-%sage: G = Graph([[1,2,3,4], [[1,2],[1,3],[1,4],[2,3],[3,4]]])
-%sage: M = Matrix([g_vector_GA(G, (1,)), g_vector_GA(G, (1,2)), g_vector_GA(G, (1,2,3)), [1,1,1,1]]).inverse()
-%sage: rays = {tuple(tube) : (g_vector_GA(G, tube)*M)[:-1] for tube in tubes(G)}
-%sage: rays
-%{(1,): (1, 0, 0),
-% (1, 2): (0, 1, 0),
-% (1, 2, 3): (0, 0, 1),
-% (1, 2, 3, 4): (0, 0, 0),
-% (1, 2, 4): (0, 2, -1),
-% (1, 3): (1/2, -1, 1/2),
-% (1, 3, 4): (1, -2, 0),
-% (1, 4): (1/2, 0, -1/2),
-% (2,): (-1, 2, 0),
-% (2, 3): (-1/2, 0, 1/2),
-% (2, 3, 4): (-1, 0, 0),
-% (3,): (0, -2, 1),
-% (3, 4): (0, -1, 0),
-% (4,): (0, 0, -1)}
-
-%sage: NF = Fan([Cone([rays[tuple(tube)] for tube in tubing]) for tubing in maximal_tubings(G)])
-%sage: NF.rays()
-%N( 0, -1,  0),
-%N( 0,  2, -1),
-%N( 1,  0,  0),
-%N(-1,  2,  0),
-%N( 0,  0,  1),
-%N( 1, -2,  0),
-%N( 0, -2,  1),
-%N( 0,  0, -1),
-%N(-1,  0,  1),
-%N( 1,  0, -1),
-%N(-1,  0,  0),
-%N( 0,  1,  0),
-%N( 1, -2,  1)
-%in 3-d lattice N
-
-%sage: TCNF = type_cone(NF)
-%sage: TCNF
-%A 13-dimensional polyhedron in QQ^13 defined as the convex hull of 1 vertex, 25 rays, 3 lines
-%sage: TCNF.lines()
-%(A line in the direction (0, 0, 1, -1, 0, 1, 0, 0, -1, 1, -1, 0, 1),
-% A line in the direction (1, -2, -2, 0, 0, 0, 2, 0, 2, -2, 2, -1, 0),
-% A line in the direction (0, 1, 0, 0, -1, 0, -1, 1, -1, 1, 0, 0, -1))
-%sage: TCNF.inequalities()
-%(An inequality (-2, 0, 0, 0, 0, 0, 1, 1, 0, 0, 0, 0, 0) x + 0 >= 0,
-% An inequality (-2, 0, 0, 0, 0, 1, 0, 0, 0, 0, 1, 0, 0) x + 0 >= 0,
-% An inequality (0, -1, -1, 0, 0, 0, 0, 0, 0, 1, 0, 2, 0) x + 0 >= 0,
-% An inequality (2, 0, 0, 0, 0, 0, -1, 0, 1, 0, -1, 0, 0) x + 0 >= 0,
-% An inequality (2, 0, 0, 0, 0, -1, 0, -1, 0, 1, 0, 0, 0) x + 0 >= 0,
-% An inequality (0, 0, -1, 0, -1, 0, 0, 0, 0, 0, 0, 2, 1) x + 0 >= 0,
-% An inequality (0, 0, -1, 0, 0, -1, 0, 0, 0, 1, 0, 0, 1) x + 0 >= 0,
-% An inequality (0, 0, 0, -1, -1, 0, 0, 0, 1, 0, 0, 2, 0) x + 0 >= 0,
-% An inequality (0, 0, 0, 0, -1, 0, -1, 0, 1, 0, 0, 0, 1) x + 0 >= 0,
-% An inequality (2, 0, 0, 0, 0, -1, -1, 0, 0, 0, 0, 0, 1) x + 0 >= 0,
-% An inequality (0, 0, 0, 0, 1, 0, 0, 0, -1, 0, 1, 0, 0) x + 0 >= 0,
-% An inequality (0, 0, 0, 0, 1, 1, 0, 0, 0, 0, 0, 0, -1) x + 0 >= 0,
-% An inequality (0, 0, 0, 1, 0, 0, 1, 0, -1, 0, 0, 0, 0) x + 0 >= 0,
-% An inequality (0, 0, 1, 0, 0, 0, 0, 1, 0, -1, 0, 0, 0) x + 0 >= 0,
-% An inequality (0, 0, 1, 0, 0, 0, 1, 0, 0, 0, 0, 0, -1) x + 0 >= 0,
-% An inequality (0, 0, 1, 1, 0, 0, 0, 0, 0, 0, 0, -2, 0) x + 0 >= 0,
-% An inequality (0, 1, 0, -1, 0, 0, 0, -1, 0, 0, 1, 0, 0) x + 0 >= 0,
-% An inequality (0, 1, 0, 0, 0, 1, 0, 0, 0, -1, 0, 0, 0) x + 0 >= 0,
-% An inequality (0, 1, 0, 0, 1, 0, 0, 0, 0, 0, 0, -2, 0) x + 0 >= 0)
-%sage: len(TCNF.inequalities())
-%12
-
-\medskip
-\noindent
-The type cone of the right fan lives in~$\R^{11}$, has a linearity space of dimension~$3$ and $12$ facet-defining inequalities (given below). In particular, it is not simplicial.
-
-\[
-\begin{array}{r|c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c}
-\text{tubes} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeB1}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeB2}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeB3}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeB4}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeB5}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeB6}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeB7}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeB8}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeB9}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeB10}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeB11}} \\[.6cm]
-\text{$\b{g}$-vectors} & \compactVectorT{1}{0}{0} & \compactVectorT{0}{2}{0} & \compactVectorT{0}{0}{1} & \compactVectorT{1}{-2}{1} & \compactVectorT{1}{-2}{0} & \compactVectorT{-1}{2}{0} & \compactVectorT{-1}{0}{1} & \compactVectorT{-1}{0}{0} & \compactVectorT{0}{-2}{1} & \compactVectorT{0}{-2}{0} & \compactVectorT{0}{0}{-1} \\[.6cm]
-\text{facet}		& -1 & 1 & -1 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-\text{defining}		& 1 & -1 & 0 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 \\
-\text{inequalities}	& 0 & 1 & -1 & 0 & 0 & -1 & 1 & 0 & 0 & 0 & 0 \\
-					& 1 & 0 & 0 & -1 & 0 & 0 & 0 & 0 & 1 & 0 & 0 \\
-					& 0 & 0 & -1 & 1 & 0 & 0 & 1 & 0 & -1 & 0 & 0 \\
-					& 0 & 0 & 0 & 1 & -1 & 0 & 0 & 0 & -1 & 1 & 0 \\
-					& 0 & 0 & 0 & 0 & 0 & 1 & -1 & 0 & 1 & 0 & 0 \\
-					& 0 & 0 & 0 & 0 & 0 & 0 & 1 & -1 & -1 & 1 & 0 \\
-					& 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & -1 & 1 \\
-					& 0 & 0 & 0 & 0 & 1 & 0 & 0 & 1 & 0 & -1 & 0 \\
-					& 0 & 0 & 1 & 0 & 0 & 0 & -1 & 1 & 0 & 0 & 0 \\
-					& 0 & 0 & 1 & -1 & 1 & 0 & 0 & 0 & 0 & 0 & 0 \\[.2cm]
-\end{array}
-\]
-
-%sage: G = Graph([[1,2,3,4], [[1,2],[1,3],[2,3],[3,4]]])
-%sage: M = Matrix([g_vector_GA(G, (1,)), g_vector_GA(G, (1,2)), g_vector_GA(G, (1,2,3)), [1,1,1,1]]).inverse()
-%sage: rays = {tuple(tube) : (g_vector_GA(G, tube)*M)[:-1] for tube in tubes(G)}
-%sage: rays
-%{(1,): (1, 0, 0),
-% (1, 2): (0, 1, 0),
-% (1, 2, 3): (0, 0, 1),
-% (1, 2, 3, 4): (0, 0, 0),
-% (1, 3): (1/2, -1, 1/2),
-% (1, 3, 4): (1, -2, 0),
-% (2,): (-1, 2, 0),
-% (2, 3): (-1/2, 0, 1/2),
-% (2, 3, 4): (-1, 0, 0),
-% (3,): (0, -2, 1),
-% (3, 4): (0, -1, 0),
-% (4,): (0, 0, -1)}
-
-%sage: NF = Fan([Cone([rays[tuple(tube)] for tube in tubing]) for tubing in maximal_tubings(G)])
-%sage: NF.rays()
-%N( 1,  0,  0),
-%N(-1,  2,  0),
-%N( 0,  0,  1),
-%N( 1, -2,  0),
-%N( 0,  0, -1),
-%N(-1,  0,  1),
-%N( 1, -2,  1),
-%N( 0, -2,  1),
-%N(-1,  0,  0),
-%N( 0,  1,  0),
-%N( 0, -1,  0)
-%in 3-d lattice N
-
-%sage: TCNF = type_cone(NF)
-%sage: TCNF
-%A 11-dimensional polyhedron in QQ^11 defined as the convex hull of 1 vertex, 11 rays, 3 lines
-%sage: TCNF.lines()
-%(A line in the direction (0, 2, 0, -2, 0, 0, -2, -2, 0, 1, -1),
-% A line in the direction (1, -1, 0, 1, 0, -1, 1, 0, -1, 0, 0),
-% A line in the direction (1, -1, 1, 1, -1, 0, 2, 1, -1, 0, 0))
-%sage: TCNF.inequalities()
-%(An inequality (-1, 0, -1, 0, 0, 0, 1, 0, 0, 2, 0) x + 0 >= 0,
-% An inequality (1, 1, 0, 0, 0, 0, 0, 0, 0, -2, 0) x + 0 >= 0,
-% An inequality (0, -1, -1, 0, 0, 1, 0, 0, 0, 2, 0) x + 0 >= 0,
-% An inequality (1, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0) x + 0 >= 0,
-% An inequality (0, 0, -1, 0, 0, 1, 1, -1, 0, 0, 0) x + 0 >= 0,
-% An inequality (0, 0, 0, -1, 0, 0, 1, -1, 0, 0, 2) x + 0 >= 0,
-% An inequality (0, 1, 0, 0, 0, -1, 0, 1, 0, 0, 0) x + 0 >= 0,
-% An inequality (0, 0, 0, 0, 0, 1, 0, -1, -1, 0, 2) x + 0 >= 0,
-% An inequality (0, 0, 0, 0, 1, 0, 0, 1, 0, 0, -2) x + 0 >= 0,
-% An inequality (0, 0, 0, 1, 0, 0, 0, 0, 1, 0, -2) x + 0 >= 0,
-% An inequality (0, 0, 1, 0, 0, -1, 0, 0, 1, 0, 0) x + 0 >= 0,
-% An inequality (0, 0, 1, 1, 0, 0, -1, 0, 0, 0, 0) x + 0 >= 0)
-%sage: len(TCNF.inequalities())
-%12
-\medskip
-\end{example}
-
-In the remaining of this section, we describe the facet-defining inequalities of the type cone of the graphical nested fans.
-Observe first that we have already indirectly described this type cone when the graph is a path in \cref{prop:extremalExchangeablePairsAsso}.
-Recall that on the path with~$n+1$ vertices, the tubes of the path are the intervals of~$[n+1]$ and that two intervals~$[i,j]$ and~$[i',j']$ of~$[n+1]$ are exchangeable if either~${i < i' \le j+1 < j'+1}$ or~${i' < i \le j'+1 < j+1}$.
-
-\begin{proposition}
-\label{prop:extremalExchangeablePairsA}
-Two intervals~$[i,j]$ and~$[i',j']$ of~$[n+1]$ form an extremal exchangeable pair for the nested fan of the path if and only if~$i = i'+1$ and~$j = j'+1$, or the opposite.
-\end{proposition}
-
-We now consider an arbitrary graph~$\graphG$ and describe the type cone of its nested fan.
-We give a necessary condition for an exchangeable pair to be extremal in \cref{lem:extremalExchangeablePairsGAonlyif}, exploit it in \cref{exm:constructionsGA}, and prove that it is actually a sufficient condition in \cref{prop:extremalExchangeablePairsGA}
-
-\begin{lemma}
-\label{lem:extremalExchangeablePairsGAonlyif}
-If two tubes~$\tube$ and~$\tube'$ of~$\graphG$ form an extremal exchangeable pair for the nested fan of~$\graphG$, then~${\tube \ssm \{v\} = \tube' \ssm \{v'\}}$ for some neighbor~$v$ of~$\tube'$ and some neighbor~$v'$ of~$\tube$.
-\end{lemma}
-
-\begin{proof}
-Consider an exchangeable pair~$\{\tube, \tube'\}$ of tubes of~$\graphG$.
-The inner normal vector of the corresponding inequality of the type cone is
-\[
-\b{n}(\tube, \tube') \eqdef \b{f}_{\tube} + \b{f}_{\tube'} - \b{f}_{\tube\cup \tube'} - \sum_{\tube[s] \in \connectedComponents(\tube \cap \tube')} \b{f}_{\tube[s]}.
-\]
-
-By \cref{prop:exchangeablePairsGA}, $\tube'$ has a unique neighbor~$v$ in~$\tube \ssm \tube'$ and $\tube$ has a unique neighbor~$v'$ in~$\tube' \ssm \tube$.
-Therefore, $\tube \ssm \tube'$ and~$\tube' \ssm \tube$ are both connected.
-Assume that $\tube \ssm \tube'\ne \{v\}$, and let $w\ne v$ be a non-disconnecting node of $\tube \ssm \tube'$.
-By \cref{prop:exchangeablePairsGA}, $\tilde \tube \eqdef \tube \ssm \{w\}$ and $\tube'$ are exchangeable, and $\tilde \tube' \eqdef (\tube \cup \tube') \ssm \{w\}$ and $\tube$ are exchangeable as well.
-Moreover, we have
-\begin{align*}
-\b{n}(\tilde \tube, \tube') + \b{n}( \tube, \tilde \tube')
-& = \Big( \b{f}_{\tilde \tube} + \b{f}_{\tube'} - \b{f}_{\tilde \tube\cup \tube'} - \sum_{\tube[s] \in \connectedComponents(\tilde \tube \cap \tube')} \b{f}_{\tube[s]} \Big)
-+ \Big( \b{f}_{\tube} + \b{f}_{\tilde \tube'} - \b{f}_{\tube\cup \tilde \tube'} - \sum_{\tube[s] \in \connectedComponents(\tube \cap \tilde \tube')} \b{f}_{\tube[s]} \Big) \\
-& = \b{f}_{\tube} + \b{f}_{\tube'} - \b{f}_{\tube\cup \tube'} - \sum_{\tube[s] \in \connectedComponents(\tube \cap \tube')} \b{f}_{\tube[s]} =\b{n}(\tube, \tube'),
-\end{align*}
-as $\tilde \tube \cup \tube' = \tilde \tube'$, $\tilde \tube \cap \tube' = \tube \cap \tube'$, $\tube \cup \tilde \tube' = \tube \cup \tube'$ and $\connectedComponents(\tube \cap \tilde \tube') = \connectedComponents(\tilde \tube) = \tilde \tube$.
-Therefore $\b{n}(\tube, \tube')$ defines a redundant inequality and $\{\tube, \tube'\}$ is not an extremal exchangeable pair.
-The proof is symmetric if~$\tube' \ssm \tube \ne \{v'\}$.
-\end{proof}
-
-\begin{example}
-\label{exm:constructionsGA}
-We now exploit \cref{lem:extremalExchangeablePairsGAonlyif} to show that certain height functions belong to the type cone of~$\gvectorFan[\graphG]$ and recover the classical constructions of the graph associahedron.
-
-\begin{enumerate}
-\item Consider the height function~$\b{h} \in \R^{\tubes}$ given by~$\b{h}_{\tube} \eqdef -|\bigset{\tube[s] \in \tubes}{\tube[s] \subseteq \tube}|$.
-Then for any tubes~$\tube$ and~$\tube'$ such that ${\tube \ssm \{v\} = \tube' \ssm \{v'\}}$ for some neighbor~$v$ of~$\tube'$ and some neighbor~$v'$ of~$\tube$, we have
-\[
-\qquad\qquad
-\dotprod{\b{n}(\tube, \tube')}{\b{h}} = |\bigset{\tube[s]\in\tubes}{\tube \symdif \tube' \subseteq \tube[s] \subseteq \tube \cup \tube'}|,
-\]
-where~$\tube \symdif \tube' = \{v,v'\}$ denotes the symmetric difference.
-This quantity is positive since at least~$\tube \cup \tube'$ fulfills the condition.
-Thus, the height function~$\b{h}$ belongs to the type cone~$\typeCone \big( \gvectorFan[\graphG] \big)$.
-The polytope~$P_\b{h} \eqdef \set{\b{x} \in \R^\ground}{\dotprod{\gvector{\tube}}{\b{x}} \le \b{h}_{\tube} \text{ for any tube } \tube \in \tubes}$ is the graph associahedron constructed by A.~Postnikov's in~\cite{Postnikov}.
-\item Consider now the height function~$\b{h} \in \R^{\tubes}$ given by~$\b{h}_{\tube} \eqdef -3^{|\tube|-2}$.
-Then for any tubes~$\tube$ and~$\tube'$ such that ${\tube \ssm \{v\} = \tube' \ssm \{v'\}}$ for some neighbor~$v$ of~$\tube'$ and some neighbor~$v'$ of~$\tube$, we have
-\[
-\qquad\qquad
-\dotprod{\b{n}(\tube, \tube')}{\b{h}} = - 3^{|\tube|-2} - 3^{|\tube'|-2} + 3^{|\tube \cup \tube'|-2} + \sum_{\tube[s] \in \connectedComponents(\tube \cap \tube')} 3^{|\tube[s]|-2 } \ge - 2 \cdot 3^{|\tube \cup \tube'|-1} + 3^{|\tube \cup \tube'|} > 0.
-\]
-Thus, the height function~$\b{h}$ belongs to the type cone~$\typeCone \big( \gvectorFan[\graphG] \big)$.
-The corresponding polytope~$P_\b{h}$ is the graph associahedron constructed by S.~Devadoss's in~\cite{Devadoss}.
-\item Finally, consider the height function~$\b{h} \in \R^{\tubes}$ given by~$\b{h}_{\tube} \eqdef |\bigset{\tube[s] \in \tubes}{\tube[s] \supseteq \tube}|$.
-Then for any tubes~$\tube$ and~$\tube'$ such that ${\tube \ssm \{v\} = \tube' \ssm \{v'\}}$ for some neighbor~$v$ of~$\tube'$ and some neighbor~$v'$ of~$\tube$, we have
-\begin{align*}
-\qquad\qquad
-\dotprod{\b{n}(\tube, \tube')}{\b{h}} = \; & |\bigset{(\tube[r], \tube[s]) \in \tubes \times \connectedComponents(\tube \cap \tube')}{\tube[s] \subseteq \tube[r] \text{ and } \tube, \tube' \not\subseteq \tube[r]}| \\
-& + \big( |\connectedComponents(\tube \cap \tube')|-1 \big) \cdot | \bigset{\tube[r] \in \tubes}{\tube \text{ or } \tube'\subseteq \tube[r]}\big|.
-\end{align*}
-Any connected component of~$\tube \cap \tube'$ certifies the positivity of this evaluation, showing that the height function~$\b{h}$ belongs to~$\typeCone \big( \gvectorFan[\graphG] \big)$.
-The corresponding realization~$P_\b{h}$ of the graph associahedron is new, to the best of our knowledge.
-\end{enumerate}
-\end{example}
-
-We now show that the condition of \cref{lem:extremalExchangeablePairsGAonlyif} actually characterizes the extremal exchangeable pairs of the nested fan~$\gvectorFan[\graphG]$.
-
-\begin{proposition}
-\label{prop:extremalExchangeablePairsGA}
-Two tubes~$\tube$ and~$\tube'$ of~$\graphG$ form an extremal exchangeable pair for the nested fan of~$\graphG$ if and only if~${\tube \ssm \{v\} = \tube' \ssm \{v'\}}$ for some neighbor~$v$ of~$\tube'$ and some neighbor~$v'$ of~$\tube$.
-\end{proposition}
-
-\begin{proof}
-By \cref{lem:extremalExchangeablePairsGAonlyif}, an exchangeable pair $\{\tube, \tube'\}$ is not extremal unless both $\tube \ssm \tube'$ and $\tube' \ssm \tube$ are singletons.
-We now need to show that all these pairs are extremal.
-Until we finish the proof, we will call such a pair a \defn{suspected extremal pair}.
-
-Let $\{\tube, \tube'\}$ be a suspected extremal pair.
-To prove that it is extremal, we will construct a vector $\b{w} \in \R^{\tubes}$ such that $\dotprod{\b{n}(\tube, \tube')}{\b{w}}< 0,$
-but $\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{w}}>0$ for any other suspected extremal pair $\{\tilde \tube, \tilde \tube'\}$.
-This will show that the inequality induced by~$\{\tube, \tube'\}$ is not redundant.
-
-Define $\alpha(\tube,\tube') \eqdef \set{\tube[r] \in \tubes}{\tube \symdif \tube' \subseteq \tube[r] \subseteq \tube \cup \tube'}$, where $\symdif$ denotes the symmetric difference, and define $\b{x} \in \R^{\tubes}$ be such that
-\[
-\b{x}_{\tube[s]} = -|\bigset{\tube[r] \in \tubes \ssm \alpha(\tube, \tube')}{\tube[r] \subseteq \tube[s]}|
-\]
-for each tube~$\tube[s] \in \tubes$.
-For any suspected extremal pair $\{\tilde \tube, \tilde \tube'\}$ we have
-\[
-\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{x}} = |\alpha(\tilde \tube, \tilde \tube')\ssm \alpha(\tube, \tube')| \ge 0.
-\]
-Notice that $\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{x}} = 0$ if $\alpha(\tilde \tube, \tilde \tube') \subseteq \alpha(\tube,\tube')$ and $\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{x}} \ge 1$ otherwise.
-In particular, if $\{\tilde \tube, \tilde \tube'\} \ne \{\tube, \tube'\}$ then $\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{x}} \ge 1$ unless $\tilde \tube \cup \tilde \tube' \subsetneq \tube \cup \tube'$ because $\tilde \tube \cup \tilde \tube' \in \alpha(\tilde \tube, \tilde \tube')$, and if $\tilde \tube \cup \tilde \tube' = \tube \cup \tube'$ but $\{\tilde \tube, \tilde \tube'\} \ne \{\tube, \tube'\}$, then either $\tube$ or $\tube'$ will belong to $\alpha(\tilde \tube, \tilde \tube')$.
-
-Now, define $\b{y}\in\R^{\tubes}$ by
-\[
-\b{y}_{\tube[s]} = \begin{cases}
-	-1 & \text{ if } |\tube[s]| \ge |\tube|, \\
-	0 & \text{ otherwise},
-\end{cases}
-\]
-for each tube~$\tube[s] \in \tubes$.
-We have $\dotprod{\b{n}(\tube, \tube')}{\b{y}} = -1$.
-For any suspected extremal pair $\{\tilde \tube, \tilde \tube'\}$ we have $\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{y}} \ge -1$.
-If moreover $\tilde \tube \cup \tilde \tube' \subsetneq \tube \cup \tube'$, then we have $\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{y}} \ge 0$.
-
-Finally, consider $\b{z} \in \R^{\tubes}$ given by
-\[
-\b{z}_{\tube[s]} = -|\bigset{\tube[r] \in \alpha(\tube, \tube')}{\tube[r] \subseteq \tube[s]}|,
-\]
-for each tube~$\tube[s] \in \tubes$.
-It verifies $\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{z}} \ge 0$ for any suspected extremal pair~$\{\tilde \tube, \tilde \tube'\}$, and $\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{z}} = |\alpha(\tilde \tube, \tilde \tube')| > 0$ if $\alpha(\tilde \tube, \tilde \tube') \subseteq \alpha(\tube, \tube')$.
-
-For $0 < \varepsilon < 1$, and $0 < \delta < \frac{\varepsilon}{|\alpha(\tube, \tube')|}$, we claim that the vector $\b{w} \eqdef \b{x} + \varepsilon \b{y} + \delta \b{z}$ fulfills the desired properties.
-Indeed, if $\{\tilde \tube, \tilde \tube'\} \ne \{\tube,\tube'\}$ is a suspected extremal pair with $\alpha(\tilde \tube, \tilde \tube') \not \subseteq \alpha(\tube,\tube')$, then 
-\[
-\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{w}} = \underbrace{\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{x}}}_{\ge 1} + \underbrace{\varepsilon \dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{y}}}_{> -1} + \underbrace{\delta \dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{z}}}_{\ge 0} > 0.
-\]
-If $\{\tilde \tube, \tilde \tube'\} \ne \{\tube,\tube'\}$ is a suspected extremal pair with $\alpha(\tilde \tube, \tilde \tube') \subseteq \alpha(\tube,\tube')$, then $\tilde \tube \cup \tilde \tube' \subsetneq \tube \cup \tube'$ and
-\[
-\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{w}} = \underbrace{\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{x}}}_{= 0} + \underbrace{\varepsilon \dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{y}}}_{\ge 0} + \underbrace{\delta \dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{z}}}_{> 0} > 0.
-\]
-However,
-\[
-\dotprod{\b{n}(\tube, \tube')}{\b{w}} = \underbrace{\dotprod{\b{n}(\tube, \tube')}{\b{x}}}_{= 0} + \underbrace{\varepsilon \dotprod{\b{n}(\tube, \tube')}{\b{y}}}_{= -\varepsilon} + \underbrace{\delta \dotprod{\b{n}( \tube,  \tube')}{\b{z}}}_{= \delta |\alpha(\tube ,\tube')| < \varepsilon} < 0.
-\qedhere
-\]
-\end{proof}
-
-The following statement reformulates \cref{prop:extremalExchangeablePairsGA}.
-
-\begin{corollary}
-\label{coro:extremalExchangeablePairsGA}
-The extremal exchangeable pairs for the nested fan of~$\graphG$ are precisely the pairs of tubes~${\tube[s] \ssm \{v'\}}$ and~${\tube[s] \ssm \{v\}}$ for any tube~$\tube[s] \in \tubes$ and distinct non-disconnecting vertices~$v,v'$~of~$\tube[s]$.
-\end{corollary}
-
-\enlargethispage{-.1cm}
-We derive from \cref{prop:extremalExchangeablePairsGA} and \cref{coro:extremalExchangeablePairsGA} all polytopal realizations of the nested fan.
-
-\begin{corollary}
-\label{coro:typeconenestedfan}
-Consider a graph~$\graphG$ on~$\ground$ with tubes~$\tubes$. 
-Then, for a height vector~$\b{h} \in \R^{\tubes}$, the nested fan~$\gvectorFan[\graphG]$ is the normal fan of the graph associahedron
-\[
-\set{\b{x} \in \R^\ground}{\dotprod{\gvector{\tube}}{\b{x}} \le \b{h}_{\tube} \text{ for any tube } \tube \in \tubes}
-\]
-if and only if~$\b{h}_{\varnothing} = \b{h}_{\graphG} = 0$ and
- $\b{h}_{\tube[s] \ssm \{v'\}} + \b{h}_{\tube[s] \ssm \{v\}} > \b{h}_{\tube[s]} + \b{h}_{\tube[s] \ssm \{v, v'\}}$ for any tube~$\tube[s] \in \tubes$ and distinct non-disconnecting vertices~$v,v'$ of~$\tube[s]$.
-\end{corollary}
-
-We also obtain from \cref{prop:extremalExchangeablePairsGA} the following surprising property.
-
-\begin{corollary}
-Any $\b{c}$-vector supports at least one extremal exchangeable pair.
-\end{corollary}
-
-\begin{proof}
-Consider a $\b{c}$-vector~$\b{e}_v - \b{e}_{v'}$ for two distinct vertices~$v, v'$ in a common connected component of~$\graphG$.
-Let~$\tube[r]$ be a path from~$v$ to~$v'$ in~$\graphG$ and let~$\tube \eqdef \tube[r] \cup \{v\}$ and~$\tube' \eqdef \tube[r] \cup \{v'\}$.
-Then $\{\tube, \tube'\}$ is an extremal exchangeable pair with $\b{c}$-vector~$\b{e}_v - \b{e}_{v'}$.
-\end{proof}
-
-We derive from \cref{coro:extremalExchangeablePairsGA} the number of extremal exchangeable pairs of the nested fan.
-For a tube~$\tube$ of~$\graphG$, we denote by~$\nonDisconnecting(\tube)$ the number of non-disconnecting vertices of~$\tube$.
-In other words, $\nonDisconnecting(\tube)$ is the number of tubes covered by~$\tube$ in the inclusion poset of all tubes of~$\graphG$.
-
-\begin{corollary}
-\label{coro:numberExtremalExchangeablePairsGA}
-The nested fan~$\gvectorFan[\graphG]$ has~$\!\!\!\! \sum\limits_{\tube[s] \in \tubes} \!\! \binom{\nonDisconnecting(\tube[s])}{2}$ extremal exchangeable pairs.
-\end{corollary}
-
-The formula of \cref{coro:numberExtremalExchangeablePairsGA} can be made more explicit for specific families of graph associahedra discussed in the introduction and illustrated in \cref{fig:specialGraphAssociahedra}.
-
-\begin{proposition}
-The number of extremal exchangeable pairs of the nested fan~$\gvectorFan[\graphG]$ is:
-\begin{itemize}
-\item $2^{n-2}\binom{n}{2}$ for the permutahedron (complete graph associahedron),
-\item $\binom{n}{2}$ for the associahedron (path associahedron),
-\item $3\binom{n}{2} - n$ for the cyclohedron (cycle associahedron),
-\item $n-1+2^{n-3}\binom{n-1}{2}$ for the stellohedron (star associahedron).
-\end{itemize}
-\end{proposition}
-
-\begin{proof}
-For the permutahedron, choose any two vertices~$v,v'$, and complete them into a tube by selecting any subset of the~$n-2$ remaining vertices.
-For the associahedron, choose any two vertices~$v,v'$, and complete them into a tube by taking the path between them.
-For the cyclohedron, choose the two vertices~$v,v'$, and complete them into a tube by taking either all the cycle, or one of the two paths between~$v$ and~$v'$ (this gives three options in general, but only two when~$v,v'$ are neighbors).
-For the stellohedron, choose either~$v$ as the center of the star and~$v'$ as one of the $n-1$ leaves, or $v$~and~$v'$ as leaves of the star and complete them into a tube by taking the center and any subset of the $n-3$ remaining leaves.
-\end{proof}
-
-To conclude on graph associahedra, we characterize the graphs~$\graphG$ whose nested fan has a simplicial type cone.
-
-\begin{proposition}\label{prop:simplicialnestedfan}
-The type cone~$\typeCone \big( \gvectorFan[\graphG] \big)$ is simplicial if and only if~$\graphG$ is a path.
-\end{proposition}
-
-\begin{proof}
-Note that any tube~$\tube$ with~$|\tube| \ge 2$ has two non-disconnecting vertices when it is a path, and at least three non-disconnecting vertices otherwise (the leaves of an arbitrary spanning tree of~$\tube$, or any vertex if it is a cycle).
-Therefore, each tube of~$\tubes$ which is not a singleton contributes to at least one extremal exchangeable pair.
-We conclude that the number of extremal exchangeable pairs is at least:
-\[
-|\tubes| - |V| = |\tubes \ssm \{\varnothing, \graphG\}| - (|V|-1) = N - n,
-\]
-with equality if and only if all tubes of~$\graphG$ are paths, \ie if and only if~$\graphG$ is a path.
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \newpage
@@
 In~\cite{Auslander1984}, M.~Auslander showed that the relations in the Grothendieck group of an Artin algebra are generated by the ones given by almost-split sequences precisely when the algebra is of finite representation type.
-This result was generalized to $\Hom{}$-finite, Krull-Schmidt exact categories with enough projectives by H.~Enomoto in~\cite{Enomoto}, and to $\Hom{}$-finite, Krull--Schmidt triangulated categories with a cogenerator by J.~Haugland in~\cite{Haugland}.
-Inspired by these results, we will show in this Section that a similar statement holds (see \cref{thm:relations-g-vecteurs}) for the~$\b{g}$-vectors (or indices) of objects in a~$2$-Calabi--Yau triangulated category.
-We will further generalize these results in Section~\ref{sec:extricats} to the setting of Ext-finite, Krull-Schmidt, extriangulated categories with Auslander--Reiten--Serre duality admitting projective objects with certain properties.
+Inspired by this result, we will show that a similar statement holds (see \cref{thm:relations-g-vecteurs}) for the~$\b{g}$-vectors (or indices) of objects in a~$2$-Calabi--Yau triangulated category.
 
@@
 \label{lem:exaclty one mesh mutation}
-For every non-initial cluster variable~$x$, there exists precisely one pair~$(x,x')$ such that there exists a positive mesh mutation changing~$x$ into~$x'$.
+For every non-initial cluster variable, there exists precisely one pair~$(x,x')$ such that there exists a positive mesh mutation changing~$x$ into~$x'$.
 \end{lemma}
@@
 Up to isomorphism, there is precisely one almost-split triangle of~$\cat$ starting in~$X$, where~$X$ is the object such that~$\phi(X) = x$.
-Thus there is precisely one mesh relation starting at~$x$.
-By \cref{lem:almost-split}, the pair~$(x,x')$ is a positive mutation if and only~$X\notin \add(\susp T)$, that is, if and only if~$x$ is not an initial variable.
+Thus there is precisely one mesh relation By \cref{lem:almost-split}, the pair~$(x,x')$ is a positive mutation if and only~$X\notin \add(\susp T)$, that is, if and only if~$x$ is not an initial variable.
 \end{proof}

### 2020-04-03 thirdPaper/FPSAC/typeConeAssociahedraFPSAC.tex

@@
 A fan is \defn{essential} if the intersection of its cones is the origin, \defn{complete} if the union of its cones covers~$\R^n$, and \defn{simplicial} if all its cones are generated by dimension many rays.}~$\Fan$ in~$\R^n$.
-Let~$\b{G}$ be the $N \times n$-matrix whose rows are (representative vectors of) the rays of~$\Fan$ and let~$\b{K}$ be a $(N-n) \times N$-matrix that spans the left kernel of~$\b{G}$ (\ie $\b{K}\b{G} = 0$).
+Let~$\b{G}$ be the $N \times n$-matrix whose rows are (representative vectors of) the rays of~$\Fan$.
+% and let~$\b{K}$ be a $(N-n) \times N$-matrix that spans the left kernel of~$\b{G}$ (\ie $\b{K}\b{G} = 0$). 
 For any height vector~$\b{h} \in \R^N$, we define the polytope\footnote{A \defn{polytope} is the convex hull of finitely many points or equivalently, a bounded intersection of finitely many closed affine half-spaces.}
@@
 
-Note that the type cone is an open cone and contains a linearity subspace of dimension~$n$ (it is invariant by translation in~$\b{G} \R^n$).
+Note that the type cone is an open cone and contains a lineality subspace of dimension~$n$ (it is invariant by translation in~$\b{G} \R^n$).
 Therefore, we say that the type cone is \defn{simplicial} when it has precisely $N-n$ facets.
@@
 \begin{definition}
-An \defn{extremal adjacent pair} of~$\Fan$ is a pair of adjacent maximal cones~$\{\R_{\ge0}\rays, \R_{\ge0}\rays'\}$ of~$\Fan$ such that the corresponding inequality ${\displaystyle\sum}_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} > 0$ in the definition of the type cone~$\typeCone(\Fan)$ actually defines a facet of~$\typeCone(\Fan)$.
+An \defn{extremal adjacent pair} of~$\Fan$ is a pair of adjacent maximal cones~$\R_{\ge0}\rays, \R_{\ge0}\rays'$ of~$\Fan$ such that the corresponding inequality ${\displaystyle\sum}_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} > 0$ in the definition of the type cone~$\typeCone(\Fan)$ actually defines a facet of~$\typeCone(\Fan)$.
 In other words, extremal adjacent pairs define the extremal rays of the polar of the closed type cone~$\typeCone(\Fan)$.
@@
 \label{exm:typeCone}
-\enlargethispage{.1cm}
 Consider the $2$-dimensional fan~$\Fan$ depicted in \cref{fig:typeCone} (left).
@@
 It has five rays labeled~$1, \dots, 5$ and five maximal cones labeled~$a,\dots, e$.
-Its type cone~$\typeCone(\Fan)$ lies in~$\R^5$, but has a $2$-dimensional linearity space.
-The five pairs of adjacent maximal cones of~$\Fan$ give rise to following five defining inequalities for~$\typeCone(\Fan)$:
+Its type cone~$\typeCone(\Fan)$ lies in~$\R^5$, but has a $2$-dimensional lineality space, and is defined by the following five inequalities:
 \begin{gather*}
@@
 %Note that the inequalities~$H^>_{ae}$ and~$H^>_{de}$ are redundant, while the other three define facets, so that the extremal adjacent pairs are~$(a,b)$, $(b,c)$ and~$(c,d)$.
-For example, the height vector~$(\nicefrac{1}{2}, \nicefrac{3}{4}, \nicefrac{5}{4}, 1, \nicefrac{5}{4})$ belongs to the type cone~$\typeCone(\Fan)$, and the corresponding polytope is represented in \cref{fig:typeCone} (middle).
-To represent this type cone, we slice it with a transversal $2$-dimensional affine space. This is the red triangle depicted in \cref{fig:typeCone} (right).
+For example, the height vector~$(\nicefrac{1}{2}, \nicefrac{3}{4}, \nicefrac{5}{4}, 1, \nicefrac{5}{4})$ belongs to~$\typeCone(\Fan)$, and the corresponding polytope is represented in \cref{fig:typeCone} (middle).
+To represent $\typeCone(\Fan)$, we slice it with a transversal $2$-dimensional affine space, and obtain the red triangle in \cref{fig:typeCone} (right).
 
@@
 All fans considered in \cref{sec:gvectorFans} have the \defn{unique exchange relation property}: the linear dependence ${\displaystyle\sum}_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \ray[s] = 0$ only depends on the exchanged rays~$\ray[r]$ and~$\ray[r]'$, not on the maximal adjacent cones~$\rays$ and~$\rays'$.
-We then write~$\coefficient[{\ray[s]}][\ray][\ray']$ instead of~$\coefficient[{\ray[s]}][\rays][\rays']$ and we call \defn{extremal exchangeable pairs} of~$\Fan$ the pairs of exchangeable rays~$\{\ray, \ray'\}$ of~$\Fan$ such that the corresponding inequality ${\displaystyle\sum}_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\ray][\ray'] \, \b{h}_{\ray[s]} > 0$ defines a facet of~$\typeCone(\Fan)$.
+We then write~$\coefficient[{\ray[s]}][\ray][\ray']$ instead of~$\coefficient[{\ray[s]}][\rays][\rays']$ and we call \defn{extremal exchangeable pairs} of~$\Fan$ the pairs of exchangeable rays~$\ray, \ray'$ of~$\Fan$ such that the corresponding inequality ${\displaystyle\sum}_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\ray][\ray'] \, \b{h}_{\ray[s]} > 0$ defines a facet of~$\typeCone(\Fan)$.
 
@@
 To conclude this section, we consider alternative polytopal realizations of the fan~$\Fan$ and discuss their behavior in the situation when the type cone~$\typeCone(\Fan)$ is simplicial.
+Fix a $(N-n) \times N$-matrix~$\b{K}$ that spans the left kernel of the $N \times n$-matrix~$\b{G}$ (\ie $\b{K}\b{G} = 0$).
 
@@
 In particular, its vertices correspond to triangulations of the $(n+3)$-gon and its facets correspond to internal diagonals of the $(n+3)$-gon.
-Let~$X(n) \eqdef \set{(a,b)}{0 \le a < b \le n+2}$ (resp.~$Y(n) \eqdef \set{(a,b)}{0 \le a < b-2 \le n}$) denote all (resp.~the internal) diagonals.
+Let~$X(n) \eqdef \set{(a,b)}{0 \le a < b \le n+2}$ denote all diagonals of the $(n+3)$-gon and~$Y(n) \eqdef \set{(a,b)}{0 \le a < b-2 \le n} \subset X(n)$.
 The \defn{$\b{g}$-vector} of a diagonal $(a,b) \in X(n)$ is ${\gvector{a,b} \eqdef {\displaystyle\sum}_{\,a < \ell < b} \b{e}_\ell - \frac{b-a-1}{n+1} {\displaystyle\sum}_{\,1 \le \ell \le n+1} \b{e}_\ell}$.
@@
 
-\item the fan~$\gvectorFan[n]$ is the normal fan of an associahedron~$\Asso[n]$ constructed \eg in~\cite{Loday}.
+\item the fan~$\gvectorFan[n]$ is the normal fan of the associahedron~$\Asso[n]$ constructed \eg in~\cite{Loday}.
 
@@
 \[
-\typeCone \big( \gvectorFan[n] \big) = \set{\b{h} \in \R^{X(n)}}{\begin{array}{@{}l@{}} \b{h}_{(0,n+2)} = 0, \qquad\text{and}\qquad \b{h}_{(a,a+1)} = 0 \text{ for all } 0 \le a \le n+1 \\ \b{h}_{(a,b)} \!
+\typeCone \big( \gvectorFan[n] \big) = \set{\b{h} \in \R^{X(n)} \!}{\begin{array}{@{}l@{}} \b{h}_{(0,n+2)} = 0, \qquad\text{and}\qquad \b{h}_{(a,a+1)} = 0 \text{ for all } 0 \le a \le n+1 \\ \b{h}_{(a,b)} \!
 + \!
@@
 %\label{exm:typeConeAsso}
-%The type cone of~$\gvectorFan[2]$ (resp.~$\gvectorFan[3]$) lives in~$\R^5$ (resp.~$\R^9$), has a linearity space of dimension~$2$ (resp.~$3$), and has $3$ (resp.~$6$) facet-defining inequalities described in \cref{prop:extremalExchangeablePairsAsso}.
+%The type cone of~$\gvectorFan[2]$ (resp.~$\gvectorFan[3]$) lives in~$\R^5$ (resp.~$\R^9$), has a lineality space of dimension~$2$ (resp.~$3$), and has $3$ (resp.~$6$) facet-defining inequalities described in \cref{prop:extremalExchangeablePairsAsso}.
 %We represent these inequalities in red in \cref{fig:labelFacetDefiningInequalititiesAsso}, using incoming and outgoing arrows to distinguish their left and right hand sides.
@@
 \[
-R_\b{\ell}(n) \eqdef \set{\b{z} \in \R^{X(n)}}{\begin{array}{@{}l@{}} \b{z} \ge 0, \quad \b{z}_{(0,n+2)} = 0 \quad\text{and}\quad \b{z}_{(a,a+1)} = 0 \text{ for all } 0 \le a \le n+1 \\ \b{z}_{(a,b-1)} + \b{z}_{(a+1,b)} - \b{z}_{(a,b)} - \b{z}_{(a+1,b-1)} = \b{\ell}_{(a,b)} \text{ for all } (a,b) \in Y(n) \end{array}}
+R_\b{\ell}(n) \eqdef \set{\b{z} \in \R^{X(n)} \!}{\begin{array}{@{}l@{}} \b{z} \ge 0, \quad \b{z}_{(0,n+2)} = 0 \quad\text{and}\quad \b{z}_{(a,a+1)} = 0 \text{ for all } 0 \le a \le n+1 \\ \b{z}_{(a,b-1)} + \b{z}_{(a+1,b)} - \b{z}_{(a,b)} - \b{z}_{(a+1,b-1)} = \b{\ell}_{(a,b)} \text{ for all } (a,b) \in Y(n) \end{array}}
 \]
@@
 
-\item the cluster fan is the normal fan of a polytope~$\Asso[\B_\circ]$, called \defn{generalized associa}\-\defn{hedron}, constructed for bipartite (resp.~acyclic, resp.~arbitrary) initial exchange matrices in~\cite{ChapotonFominZelevinsky} (resp.~\cite{HohlwegLangeThomas}, resp.~\cite{HohlwegPilaudStella}).
+\item the cluster fan~$\gvectorFan[\B_\circ]$ is the normal fan of the \defn{generalized associahedron}~$\Asso[\B_\circ]$, constructed for bipartite (resp.~acyclic, resp.~arbitrary) initial exchange matrices in~\cite{ChapotonFominZelevinsky} (resp.~\cite{HohlwegLangeThomas}, resp.~\cite{HohlwegPilaudStella}).
 
@@
 %%As it is a $3$-dimensional fan, we intersect it with the unit sphere and project the result stereographically from the pole $(-1,-1,-1)$.
-%Its type cone lives in~$\R^{9}$ and has a linearity space of dimension~$3$.
+%Its type cone lives in~$\R^{9}$ and has a lineality space of dimension~$3$.
 %It has $6$ facet-defining inequalities (given below), which correspond to the mesh mutations of \cref{thm:extremalExchangeablePairsCA}.
@@
 \begin{figure}[b]
-	\newcommand{\fitClusterVariable}[1]{\parbox[c][.7cm][c]{1.5cm}{\centering $#1$}}
+	\newcommand{\fitClusterVariable}[1]{\parbox[c][.7cm][c]{1.6cm}{\centering $#1$}}
 	\centerline{
@@
 \[
-\b{R}_{\b{\ell}}(\B_\circ) \eqdef \Bigset{\b{z} \in \R^{\variables}}{\b{z} \ge 0 \text{ and } \b{z}_x + \b{z}_{x'} - \!\!\!\!\!
+\b{R}_{\b{\ell}}(\B_\circ) \eqdef \Bigset{\b{z} \in \R^{\variables}}{\b{z} \ge 0 \text{ and } \b{z}_x + \b{z}_{x'} - \!\!\!\!\!\!
 \sum_{y \in \variables} \!\!\!\!\!\coefficient[y][x][x'] \, \b{z}_{y} = \b{\ell}_{\{x,x'\}} \text{ for } \{x,x'\} \in \meshes}
@@
 \item the ideal~$I$ is generated by paths of length exactly two,
-\item for any~$\beta \in Q_1$, there is at most one~$\alpha \in Q_1$ such that~$t(\alpha) = s(\beta)$ and~${\alpha\beta\notin I}$ (resp.~$\alpha\beta \in I$) and at most one~$\gamma \in Q_1$ such that~${t(\beta) = s(\gamma)}$ and~${\beta\gamma\notin I}$~(resp.~${\beta\gamma \in I}$).
+\item for any~$\beta \in Q_1$, there is at most one~$\alpha \in Q_1$ such that~$t(\alpha) = s(\beta)$ and~${\alpha\beta\notin I}$ (resp.~$\alpha\beta \in \!
+I$) and at most one~$\gamma \in Q_1$ such that~$t(\beta) \!
+= \!
+s(\gamma)$ and~$\beta\gamma \notin \!I$~(resp.~${\beta\gamma \in \!
+I}$).
 \end{compactenum}
@@
 
-\item the non-kissing fan is the normal fan of a polytope~$\Asso[\quiver]$, called \defn{gentle associahedron}, constructed in~\cite{PaluPilaudPlamondon-nonkissing}.
+\item the non-kissing fan~$\gvectorFan[\quiver]$ is the normal fan of the \defn{gentle associahedron}~$\Asso[\quiver]$, constructed in~\cite{PaluPilaudPlamondon-nonkissing}.
 
@@
 \ssm \!
-\{\omega'\}$, the linear dependence among~the $\b{g}$-vectors of~$F \cup F'$ is given by~${\gvector{\omega} + \gvector{\omega'} = \gvector{\mu} + \gvector{\nu}}$, where~$\mu \eqdef \rho' \sigma \tau$ and~$\nu \eqdef \rho \sigma \tau'$ if the walks $\omega = \rho \sigma \tau$ and $\omega' = \rho' \sigma \tau'$ kiss along~$\sigma$ (as illustrated on the right).
+\{\omega'\}$, the linear dependence among~the $\b{g}$-vectors of~$F \cup F'$ is given by~${\gvector{\omega} + \gvector{\omega'} \!
+= \!
+\gvector{\mu} + \gvector{\nu}}$, where~$\mu \eqdef \rho' \sigma \tau$ and~$\nu \eqdef \rho \sigma \tau'$ if the walks $\omega = \rho \sigma \tau$ and $\omega' = \rho' \sigma \tau'$ kiss along~$\sigma$ (as illustrated on the right).
 }
@@
 %\noindent
-%The first lives in~$\R^8$, has a linearity space of dimension~$3$, and~$5$ facet-defining inequalities (given below),  which correspond to the flips described in \cref{prop:interestingExchangeablePairsNKC,prop:extremalExchangeablePairsNKC}.
+%The first lives in~$\R^8$, has a lineality space of dimension~$3$, and~$5$ facet-defining inequalities (given below),  which correspond to the flips described in \cref{prop:interestingExchangeablePairsNKC,prop:extremalExchangeablePairsNKC}.
 %
@@
 %\noindent
-%The second lives in~$\R^{11}$, has a linearity space of dimension~$3$, and~$9$ facet-defining inequalities.% In particular, it is not simplicial.
+%The second lives in~$\R^{11}$, has a lineality space of dimension~$3$, and~$9$ facet-defining inequalities.% In particular, it is not simplicial.
 %
@@
 %The flips corresponding to the facet-defining inequalities of the type cones of \cref{fig:labelFacetDefiningInequalititiesNKC} are represented on the corresponding Auslander-Reiten quivers.
-As illustrated by the second non-kissing fan of \cref{fig:labelFacetDefiningInequalititiesNKC} (which lives in~$\R^{11}$, has a $3$-dimensional linearity space, and has $9$ facets), the type cone~$\typeCone(\gvectorFan[\quiver])$ is not always simplicial.
+As illustrated by the second non-kissing fan of \cref{fig:labelFacetDefiningInequalititiesNKC} (which lives in~$\R^{11}$, has a $3$-dimensional lineality space, and has $9$ facets), the type cone~$\typeCone(\gvectorFan[\quiver])$ is not always simplicial.
 However, it turns out to be for the following family of quivers.
@@
 
-\item the nested fan is the normal fan of a polytope~$\Asso[\graphG]$, called \defn{graph associahedron}, constructed in~\cite{CarrDevadoss, FeichtnerSturmfels, Postnikov, Zelevinsky}.
+\item the nested fan~$\gvectorFan[\graphG]$ is the normal fan of the \defn{graph associahedron}~$\Asso[\graphG]$, constructed in~\cite{CarrDevadoss, FeichtnerSturmfels, Postnikov, Zelevinsky}.
 For instance, the permutahedra, associahedra and cyclohedra are graph associahedra of complete graphs, paths, and cycles respectively.
@@
 \label{coro:numberExtremalExchangeablePairsGA}
-The nested fan~$\gvectorFan[\graphG]$ has~${\displaystyle\sum}_{\,\tube[s] \in \tubes} \binom{\nonDisconnecting(\tube[s])}{2}$ extremal exchangeable pairs, where~$\nonDisconnecting(\tube[s])$ is the number of non-disconnecting vertices of~$\tube[s]$.
+The nested fan~$\gvectorFan[\graphG]$ has~${\displaystyle\sum}_{\,\tube[s] \in \tubes} \binom{\nonDisconnecting(\tube[s])}{2}$ extremal exchangeable pairs, where $\nonDisconnecting(\tube[s])$ is the number of non-disconnecting vertices of~$\tube[s]$.
 \end{corollary}

### 2020-04-03 thirdPaper/draft/typeConeAssociahedra.tex

@@
 
+\subjclass[2010]{13F60, 16G20, 18E10, 18E30, 52B11 (primary), 52B35, 05E15 (secondary)}
+
 \author{Arnau Padrol}
@@
 
-The type cone of~$\gvectorFan[2]$ lives in~$\R^9$ and has a linearity space of dimension~$3$.
+The type cone of~$\gvectorFan[3]$ lives in~$\R^9$ and has a lineality space of dimension~$3$.
 It has $6$ facet-defining inequalities (given below), which correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso} and illustrated in \cref{fig:labelFacetDefiningInequalititiesAsso}\,(right).
@@
 In~\cite{Auslander1984}, M.~Auslander showed that the relations in the Grothendieck group of an Artin algebra are generated by the ones given by almost-split sequences precisely when the algebra is of finite representation type.
-Inspired by this result, we will show that a similar statement holds (see \cref{thm:relations-g-vecteurs}) for the~$\b{g}$-vectors (or indices) of objects in a~$2$-Calabi--Yau triangulated category.
+This result was generalized to $\Hom{}$-finite, Krull-Schmidt exact categories with enough projectives by H.~Enomoto in~\cite{Enomoto}, and to $\Hom{}$-finite, Krull--Schmidt triangulated categories with a cogenerator by J.~Haugland in~\cite{Haugland}.
+Inspired by these results, we will show in this Section that a similar statement holds (see \cref{thm:relations-g-vecteurs}) for the~$\b{g}$-vectors (or indices) of objects in a~$2$-Calabi--Yau triangulated category.
+We will further generalize these results in Section~\ref{sec:extricats} to the setting of Ext-finite, Krull-Schmidt, extriangulated categories with Auslander--Reiten--Serre duality admitting projective objects with certain properties.
 

### 2020-04-04 fourthPaper/draft/typeConeGraphAssociahedra.tex
reshaped schematic diagram and created new paper on graph associahedra

\documentclass{amsart}

\usepackage[T1]{fontenc}
\usepackage{enumerate, amsmath, amsfonts, amssymb, amsthm, mathrsfs, wasysym, graphics, graphicx, xcolor, url, hyperref, hypcap, xargs, multicol, pdflscape, multirow, hvfloat, array, ae, aecompl, pifont, mathtools, a4wide, float, blkarray, overpic, nicefrac}
\usepackage[noabbrev,capitalise]{cleveref}
\usepackage[normalem]{ulem}
\usepackage{marginnote}
\hypersetup{colorlinks=true, citecolor=darkblue, linkcolor=darkblue}
\usepackage[all]{xy}
\usepackage{tikz}
\usepackage{tikz-cd}
\usepackage{tkz-graph}
\usetikzlibrary{trees, decorations, decorations.pathmorphing, decorations.markings, decorations.shapes, shapes, arrows, matrix, calc, fit, intersections, patterns, angles}
\graphicspath{{figures/}{figures/diagonals/}{figures/walks/}{figures/tubes/}}
\makeatletter\def\input@path{{figures/}}\makeatother
\usepackage{caption}
\captionsetup{width=\textwidth}
\usepackage[export]{adjustbox}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% theorems
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem*{theorem*}{Theorem}%[section]

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{question}[theorem]{Question}
\newtheorem{notation}[theorem]{Notation}
\newtheorem{assumption}[theorem]{Assumption}
\newtheorem{convention}[theorem]{Convention}

\crefname{equation}{Equation}{Equations}

% math special letters
\newcommand{\R}{\mathbb{R}} % reals
\newcommand{\Q}{\mathbb{Q}} % rationals
\newcommand{\N}{\mathbb{N}} % naturals
\newcommand{\Z}{\mathbb{Z}} % integers
\newcommand{\C}{\mathbb{C}} % complex
\newcommand{\I}{\mathbb{I}} % set of integers
\newcommand{\HH}{\mathbb{H}} % hyperplane
\newcommand{\K}{k} % field
\newcommand{\f}[1]{{\mathfrak{#1}}} % mathfrak letters
\newcommand{\cal}[1]{{\mathcal{#1}}} % call letters
\renewcommand{\b}[1]{{\boldsymbol{#1}}} % bold letters
\newcommand{\h}{\widehat} % hat letters

% math commands
\newcommand{\set}[2]{\left\{ #1 \;\middle|\; #2 \right\}} % set notation
\newcommand{\bigset}[2]{\big\{ #1 \;\big|\; #2 \big\}} % big set notation
\newcommand{\Bigset}[2]{\Big\{ #1 \;\Big|\; #2 \Big\}} % Big set notation
\newcommand{\setangle}[2]{\left\langle #1 \;\middle|\; #2 \right\rangle} % set notation
\newcommand{\ssm}{\smallsetminus} % small set minus
\newcommand{\dotprod}[2]{\left\langle \, #1 \; \middle| \; #2 \, \right\rangle} % dot product
\newcommand{\bigdotprod}[2]{\big\langle \, #1 \; \big| \; #2 \, \big\rangle} % dot product
\newcommand{\symdif}{\,\triangle\,} % symmetric difference
\newcommand{\one}{{1\!\!1}} % the all one vector
\newcommand{\eqdef}{\mbox{\,\raisebox{0.2ex}{\scriptsize\ensuremath{\mathrm:}}\ensuremath{=}\,}} % :=
\newcommand{\defeq}{\mbox{~\ensuremath{=}\raisebox{0.2ex}{\scriptsize\ensuremath{\mathrm:}} }} % =:
\newcommand{\simplex}{\triangle} % simplex
\renewcommand{\implies}{\Rightarrow} % imply sign
\newcommand{\transpose}[1]{{#1}^T} % transpose matrix

% operators
\DeclareMathOperator{\conv}{conv} % convex hull
\DeclareMathOperator{\vect}{vect} % linear span
\DeclareMathOperator{\cone}{cone} % cone hull

% others
\newcommand{\ie}{\textit{i.e.}~} % id est
\newcommand{\eg}{\textit{e.g.}~} % exempli gratia
\newcommand{\Eg}{\textit{E.g.}~} % exempli gratia
\newcommand{\apriori}{\textit{a priori}} % a priori
\newcommand{\viceversa}{\textit{vice versa}} % vice versa
\newcommand{\versus}{\textit{vs.}~} % versus
\newcommand{\aka}{\textit{a.k.a.}~} % also known as
\newcommand{\perse}{\textit{per se}} % per se
\newcommand{\ordinal}{\textsuperscript{th}} % th for ordinals
\newcommand{\ordinalst}{\textsuperscript{st}} % st for ordinals
\definecolor{darkblue}{rgb}{0,0,0.7} % darkblue color
\definecolor{green}{RGB}{57,181,74} % green color
\definecolor{violet}{RGB}{147,39,143} % violet color
\newcommand{\red}{\color{red}} % red command
\newcommand{\blue}{\color{blue}} % blue command
\newcommand{\orange}{\color{orange}} % orange command
\newcommand{\green}{\color{green}} % green command
\newcommand{\darkblue}{\color{darkblue}} % darkblue command
\newcommand{\defn}[1]{\textsl{\darkblue #1}} % emphasis of a definition
\newcommand{\para}[1]{\medskip\noindent\uline{\textit{#1.}}} % paragraph
\renewcommand{\topfraction}{1} % possibility to have one page of pictures
\renewcommand{\bottomfraction}{1} % possibility to have one page of pictures
\newcommand{\ex}{_{\textrm{exm}}} % examples
\newcommand{\pa}{_{\textrm{pa}}} % path
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{\node[shape=circle, draw, inner sep=1.5pt, scale=.7] (char) {#1};}}
\newcommand{\compactVectorD}[2]{\begin{bmatrix} #1 \\ #2 \end{bmatrix}}
\newcommand{\compactVectorT}[3]{\begin{bmatrix} #1 \\[-.1cm] #2 \\[-.1cm] #3 \end{bmatrix}}

% marginal comments
\usepackage{todonotes}
\newcommand{\arnau}[1]{\todo[color=orange!30]{#1 --- A.}}
\newcommand{\yann}[1]{\todo[color=red!30]{#1 --- Y.}}
\newcommand{\vincent}[1]{\todo[color=blue!30]{#1 \\ \hfill --- V.}}
\newcommand{\pg}[1]{\todo[color=green!30]{#1 \\ \hfill --- PG.}}

% geometry
\newcommandx{\Asso}[2][1=n,2={}]{\mathsf{Asso}^{#2}(#1)} % associahedron
\newcommandx{\Zono}[2][1=n,2={}]{\mathsf{Zono}^{#2}(#1)} % zonotope
\newcommandx{\Fan}[1][1=F]{\mathcal{#1}} % fan
\newcommand{\multiplicityVector}{\b{m}} % multiplicity vector
\newcommandx{\ray}[1][1=r]{\b{#1}} % ray
\newcommandx{\rays}[1][1=R]{\b{#1}} % rays
\newcommand{\gvector}[1]{\b{g}(#1)} % g-vector of #1
\newcommand{\gvectorFull}[2]{\b{g}(#1,#2)} % g-vector of #2 wrt #1
\newcommand{\gvectors}[1]{\b{g}(#1)} % g-vectors of #1
\newcommand{\gvectorsFull}[2]{\b{g}(#1,#2)} % g-vectors of #2 wrt #1
\newcommandx{\gvectorFan}[1][1=\quiver]{\mathcal{F}(#1)} % g-vector fan
\newcommand{\cvector}[2]{\mathbf{c}(#2 \in #1)} % c-vector of the cluster variable #2 in the cluster #1
\newcommand{\cvectorFull}[3]{\mathbf{c}(#1,#3 \in #2)} % c-vector of the cluster variable #3 in the cluster #2 with respect to the initial cluster #1
\newcommand{\cvectors}[1]{\mathbf{c}(#1)} % c-vectors of the cluster #1
\newcommand{\cvectorsFull}[2]{\mathbf{c}(#1,#2)} % c-vectors of the cluster #2 with respect to the initial cluster #1

% Type cone
\newcommand{\typeCone}{\mathbb{TC}} % type cone
\newcommand{\ctypeCone}{\overline{\mathbb{TC}}} % type cone
\newcommand{\compatibilityDegree}[2]{(#1\,\|\,#2)} % compatibility degree
\newcommandx{\coefficient}[3][1={\ray[s]}, 2=\ray, 3=\ray']{\alpha_{#2,#3}(#1)} % coefficient in linear dependence

% Cluster algebras
\newcommand{\Trop}[1]{\mathbb{P}_{#1}} % tropical semifield
\newcommand{\positiveExponents}[1]{\left\{#1\right\}_+} % positive exponents in tropical semifield
\newcommand{\negativeExponents}[1]{\left\{#1\right\}_-} % negative exponents in tropical semifield
\newcommand{\seed}{\Sigma} % a cluster
\newcommand{\cluster}{\mathrm{X}} % a cluster
\newcommandx{\clusters}{\mathcal{X}} % all clusters
\newcommand{\coefficients}{\mathrm{P}} % a coefficients tuple
\newcommandx{\variables}[2][1=\B_\circ, 2 = \coefficients_\circ]{\mathcal{V}(#1,#2)} % all variables
\newcommandx{\clusterAlgebra}[2][1=\B_\circ, 2=\coefficients_\circ]{\mathcal{A}\!\left(#1,#2\right)} % cluster algebra
\newcommandx{\principalClusterAlgebra}[1][1=\B_\circ]{\mathcal{A}\left(#1\right)} % principal coefficients cluster algebra
\newcommandx{\principalVariables}[1][1=\B_\circ]{\mathcal{V}(#1)} % all variables, principal case
\newcommandx{\coefficientFreeClusterAlgebra}[1][1=\B_\circ]{\mathcal{A}_{\mathrm{fr}}(#1)} % coefficient free cluster algebra
\newcommandx{\clusterComplex}[1][1=\B_\circ]{\Delta(#1)} % cluster complex
\newcommand{\B}{\mathrm{B}} % b-matrix
\newcommand{\A}[1]{\mathrm{A}({#1})} % b-matrix
\newcommand{\D}{\mathrm{D}} % symmetrizer
\newcommand{\simpleRoot}{\alpha} % simple root
\newcommand{\fundamentalWeight}{\omega} % fundamental weights
\newcommandx{\meshes}[1][1=\B_\circ]{\mathcal{M}(#1)} % meshes

% Gentle associahedra
\newcommand{\quiver}{\bar Q} % quiver
\newcommand{\blossom}{^\text{\ding{96}}} % blossom
\newcommandx{\strings}[1][1=\quiver]{\mathcal{S}(#1)} % strings
\newcommandx{\distinguishableStrings}[1][1=\quiver]{\mathcal{S}_\mathrm{dist}(#1)} % distinguishable strings
\newcommandx{\walks}[1][1=\quiver]{\mathcal{W}(#1)} % walks
\newcommandx{\properWalks}[1][1=\quiver]{\mathcal{W}_\mathrm{prop}(#1)} % proper walks
\renewcommand{\top}{\mathrm{top}} % top
\newcommand{\bottom}{\mathrm{bot}} % bottom
\newcommandx{\NKC}[1][1=\quiver]{\mathcal{NK}(#1)} % non-kissing complex
\newcommandx{\RNKC}[1][1=\quiver]{\mathcal{RNK}(#1)} % reduced non-kissing complex
\newcommand{\peaks}[1]{\mathsf{peaks}(#1)} % peaks
\newcommand{\deeps}[1]{\mathsf{deeps}(#1)} % deeps
\newcommand{\KN}{\textsc{kn}} % Kissing Number
\newcommand{\hL}{\text{\rotatebox[origin=c]{180}{\checked}}}
\newcommand{\hR}{\text{\rotatebox[origin=c]{180}{\reflectbox{\checked}}}}
\newcommand{\cL}{\text{\reflectbox{\checked}}}
\newcommand{\cR}{\text{\checked}}
\newcommand{\hh}[1]{\hL#1\hR} % hook - hook
\newcommand{\cc}[1]{\cL#1\cR} % cohook - cohook
\newcommand{\hc}[1]{\hL#1\cR} % hook - cohook
\newcommand{\ch}[1]{\cL#1\hR} % cohook - hook
\newcommand{\distinguishedString}[2]{\mathsf{ds}(#1,#2)} % distinguished string
\newcommand{\distinguishedSign}[2]{\varepsilon(#1,#2)} % distinguished sign

% Graph associahedra
\newcommand{\ground}{V} % ground set
\newcommandx{\graphG}[1][1=G]{#1} % graph
\newcommandx{\tube}[1][1=t]{\mathsf{#1}} % tube
\newcommandx{\tubes}[1][1=\graphG]{\mathcal{T}(#1)} % all tubes
\newcommandx{\tubing}[1][1=T]{\mathsf{#1}} % tubing
\newcommand{\connectedComponents}{\kappa} % connected components
\newcommand{\nestedComplex}{\mathcal{N}} % nested complex
\newcommand{\nonDisconnecting}{\mathrm{nd}} % non-disconnecting vertices
\newcommand{\neighbors}{\mathrm{ne}} % neighbors

% Representation theory
\newcommand{\field}{\mathbb{K}}
\newcommand{\cat}{\mathcal{C}}
\newcommand{\Hom}[1]{\operatorname{Hom}_{#1}}
\newcommand{\susp}{\Sigma}
\newcommand{\add}{\operatorname{add}}
\newcommand{\MOD}{\operatorname{mod}}
\newcommand{\End}[1]{\operatorname{End}_{#1}}
\newcommand{\spl}{\operatorname{sp}}
\newcommand{\Ksp}{K_0^{\spl}}
\newcommand{\Kg}{K_0^{\b{g}}}
\newcommand{\ind}{\operatorname{ind}}
\newcommand{\coker}{\operatorname{coker}}
\newcommand{\CC}{\phi}
\newcommand{\proj}{\operatorname{proj}}
\newcommand{\bsm}{\begin{smallmatrix}}
\newcommand{\esm}{\end{smallmatrix}}

% Extriangulated categories
\newcommand{\tc}{\mathcal{T}}
\newcommand{\ec}{\mathcal{E}}
\newcommand{\infl}{\rightarrowtail}
\newcommand{\defl}{\twoheadrightarrow}
\newcommand{\Modt}{\operatorname{Mod}\tc}
\newcommand{\modt}{\MOD\tc}
\newcommand{\kzero}[1]{K_0(#1)}
\newcommand{\eps}{\varepsilon}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% formating the part command
\makeatletter
\def\part{\@startsection{part}{1}%
\z@{.7\linespacing\@plus\linespacing}{.8\linespacing}%
{\LARGE\sffamily\centering}}
%\@addtoreset{section}{part}
\makeatother
\renewcommand{\thepart}{\Roman{part}}
%\renewcommand{\thesection}{\arabic{part}.\arabic{section}}

% formating the table of contents
\setcounter{tocdepth}{4}
\makeatletter
\def\l@section{\@tocline{1}{5pt}{0pc}{}{}}
\makeatother
\let\oldtocpart=\tocpart
\renewcommand{\tocpart}[2]{\sc\large\oldtocpart{#1}{#2}}
\let\oldtocsection=\tocsection
\renewcommand{\tocsection}[2]{\bf\oldtocsection{#1}{#2}}
\let\oldtocsubsubsection=\tocsubsubsection
\renewcommand{\tocsubsubsection}[2]{\quad\oldtocsubsubsection{#1}{#2}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title[The type cone of graph associahedra]{The type cone of graph associahedra}

\thanks{YP, VP and PGP were partially supported by the French ANR grant SC3A~(15\,CE40\,0004\,01). AP and VP were partially supported by the French ANR grant CAPPS~(17\,CE40\,0018).}

\author{Arnau Padrol}
\address[Arnau Padrol]{Institut de Mathématiques de Jussieu - Paris Rive Gauche, Sorbonne Universit\'e, Paris}
\email{arnau.padrol@imj-prg.fr.}
\urladdr{\url{https://webusers.imj-prg.fr/~arnau.padrol/}}

\author{Yann Palu}
\address[Yann Palu]{LAMFA, Universit\'e Picardie Jules Verne, Amiens}
\email{yann.palu@u-picardie.fr}
\urladdr{\url{http://www.lamfa.u-picardie.fr/palu/}}

\author{Vincent Pilaud}
\address[Vincent Pilaud]{CNRS \& LIX, \'Ecole Polytechnique, Palaiseau}
\email{vincent.pilaud@lix.polytechnique.fr}
\urladdr{\url{http://www.lix.polytechnique.fr/~pilaud/}}

\author{Pierre-Guy Plamondon}
\address[Pierre-Guy Plamondon]{Laboratoire de Math\'ematiques d'Orsay, Universit\'e Paris-Sud, CNRS, Universit\'e Paris-Saclay}
\email{pierre-guy.plamondon@math.u-psud.fr}
\urladdr{\url{https://www.math.u-psud.fr/~plamondon/}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{abstract}
We give a complete description of the type cone of graph associahedra.
\end{abstract}

\maketitle
% 
% \vspace{1.5cm}
% \centerline{\includegraphics[scale=.8]{typeConeCoarsenings}}
% \vspace{.5cm}
% \centerline{The type cone of the cluster fan of type~$A_2$.}

% \newpage
\tableofcontents

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage
\section*{Introduction}
\arnau{Introduce associahedron}
In~\cite{PPPP}, a new approach for studying the space of polytopal realizations of $\b{g}$-vector fans, based on McMullen's type cones, was introduced to study two generalizations of the associahedron: the generalized associahedra of finite type cluster algebras~\cite{FominZelevinsky-ClusterAlgebrasI, FominZelevinsky-ClusterAlgebrasII, FominZelevinsky-ClusterAlgebrasIV, HohlwegLangeThomas, HohlwegPilaudStella} and the gentle associahedra~\cite{PaluPilaudPlamondon-nonkissing}. 
\arnau{cite physicists and BDMTY}
% This approach sheds a new light on and extends earlier results of N.~Arkani-Hamed, Y.~Bai, S.~He, and G.~Yan in type~$A$ and of V.~Bazier-Matte, G.~Douville, K.~Mousavand, H.~Thomas and E.~Y\i ld\i r\i m for acyclic initial seeds.

It is natural to extend the approach to further families of generalizations of the associahedron. In this paper, we focus on graph associahedra. \textbf{Graph associahedra} were defined by M.~Carr and S.~Devadoss~\cite{CarrDevadoss} in connection to C.~De Concini and C.~Procesi's wonderful arrangements~\cite{DeConciniProcesi}. As illustrated in \cref{fig:specialGraphAssociahedra}, the graph associahedra of certain special families of graphs coincide with well-known families of polytopes: complete graph associahedra are permutahedra, path associahedra are classical associahedra, cycle associahedra are cyclohedra, and star associahedra are stellohedra. The graph associahedra were extended to the nestohedra, which are simple polytopes realizing the nested complex of arbitrary building sets~\cite{Postnikov, FeichtnerSturmfels}. Graph associahedra and nestohedra have been geometrically realized in different ways: by successive truncations of faces of the standard simplex~\cite{CarrDevadoss}, as Minkowski sums of faces of the standard simplex~\cite{Postnikov, FeichtnerSturmfels}, or from their normal fans by exhibiting explicit inequality descriptions~\cite{Devadoss, Zelevinsky}. All these realizations have the same normal fan, called nested fan. 
We study the type cones of these nested fans (see \cref{subsec:typeConeGA}): we describe their facet-defining inequalities in terms of certain specific pairs of neighboring tubings and count them for the specific families of graph associahedra described earlier. For instance the type cone of the permutahedron coincides with the classical submodular functions on~$2^{[n]}$, described by~$2^{n-2} \binom{n}{2}$ inequalities. In fact, we observe that the type cone of a graphical nested fan is never simplicial except in the case of the classical associahedron (when the graph is the path). Nevertheless, our results give a non-redundant description of all polytopal realizations of the graphical nested fans.

\subsection{Graphical nested complexes and graph associahedra}
\label{subsec:typeConeGA}

Graph associahedra were defined by M.~Carr and S.~Devadoss~\cite{CarrDevadoss} in connection to C.~De Concini and C.~Procesi's wonderful arrangements~\cite{DeConciniProcesi}.
For a given graph~$\graphG$, the $\graphG$-associahedron~$\Asso[\graphG]$ is a simple polytope whose combinatorial structure encodes the connected subgraphs of~$\graphG$ and their nested structure.
More precisely, the $\graphG$-associahedron is a polytopal realization of the nested complex of~$\graphG$, defined as the simplicial complex of all collections of tubes (connected induced subgraphs) of~$\graphG$ which are pairwise compatible (either nested, or disjoint and non-adjacent).
As illustrated in \cref{fig:specialGraphAssociahedra}, the graph associahedra of certain special families of graphs coincide with well-known families of polytopes: complete graph associahedra are permutahedra, path associahedra are classical associahedra, cycle associahedra are cyclohedra, and star associahedra are stellohedra.
The graph associahedra were extended to the \defn{nestohedra}, which are simple polytopes realizing the nested complex of arbitrary building sets~\cite{Postnikov, FeichtnerSturmfels}.
Graph associahedra and nestohedra have been geometrically realized in different ways: by successive truncations of faces of the standard simplex~\cite{CarrDevadoss}, as Minkowski sums of faces of the standard simplex~\cite{Postnikov, FeichtnerSturmfels}, or from their normal fans by exhibiting explicit inequality descriptions~\cite{Devadoss, Zelevinsky}.
For a given graph~$\graphG$, the resulting polytopes all have the same normal fan, called nested fan of~$\graphG$: its rays are the characteristic vectors of the tubes, and its cones are generated by characteristic vectors of compatible tubes.
In this section, we describe the type cone of the nested fan of any graph~$\graphG$.

\hvFloat[floatPos=p, capWidth=h, capPos=r, capAngle=90, objectAngle=90, capVPos=c, objectPos=c]{figure}
{
		\begin{tabular}{c@{\;}c@{\;}c@{\;}c}
			permutahedron &
			associahedron &
			cyclohedron &
			stellohedron \\[.2cm]
			\includegraphics[scale=.93]{permutahedron} &
			\includegraphics[scale=.93]{associahedron} &
			\includegraphics[scale=.93]{cyclohedron} &
			\includegraphics[scale=.93]{stellohedron} \\[.1cm]
			\includegraphics[scale=.93]{permutahedronTubings} &
			\includegraphics[scale=.93]{associahedronTubings} &
			\includegraphics[scale=.93]{cyclohedronTubings} &
			\includegraphics[scale=.93]{stellohedronTubings} \\[.2cm]
			complete graph &
			path &
			cycle &
			star \\[.3cm]
		\end{tabular}
}
{Some classical families of polytopes as graph associahedra. Illustration from~\cite{MannevillePilaud-compatibilityFans}.}
{fig:specialGraphAssociahedra}

%\begin{figure}[t]
%	\capstart
%	\begin{adjustbox}{center}
%		\begin{tabular}{c@{\;}c@{\;}c@{\;}c}
%			permutahedron &
%			associahedron &
%			cyclohedron &
%			stellohedron \\
%			\includegraphics[scale=.6]{permutahedron} &
%			\includegraphics[scale=.6]{associahedron} &
%			\includegraphics[scale=.6]{cyclohedron} &
%			\includegraphics[scale=.6]{stellohedron} \\
%			\includegraphics[scale=.6]{permutahedronTubings} &
%			\includegraphics[scale=.6]{associahedronTubings} &
%			\includegraphics[scale=.6]{cyclohedronTubings} &
%			\includegraphics[scale=.6]{stellohedronTubings} \\[.1cm]
%			complete graph &
%			path &
%			cycle &
%			star
%		\end{tabular}
%	\end{adjustbox}
%	\caption{Some classical families of polytopes as graph associahedra. Illustration from~\cite{MannevillePilaud-compatibilityFans}.}
%	\label{fig:specialGraphAssociahedra}
%\end{figure}

%%%

\clearpage
\subsubsection{Nested complex and nested fan of a graph}

We present the definitions and properties of the nested complex of a graph, following ideas from~\cite{CarrDevadoss, Postnikov, FeichtnerSturmfels, Zelevinsky}.

\para{Nested complex}
%
Let~$\graphG$ be a graph with vertex set~$\ground$.
Let~$\connectedComponents(\graphG)$ denote the set of connected components of~$\graphG$ and define~$n \eqdef |\ground|-|\connectedComponents(\graphG)|$.
A \defn{tube} of~$\graphG$ is a subset of vertices of~$\graphG$ whose induced subgraph is connected.
The set of tubes of~$\graphG$ is denoted by~$\tubes$.
The inclusion maximal tubes of~$\graphG$ are its connected components~$\connectedComponents(\graphG)$.
The tubes which are neither empty nor maximal are called \defn{proper}.
Two tubes~$\tube, \tube'$ of~$\graphG$ are \defn{compatible} if they are either nested (\ie $\tube \subseteq \tube'$ or~$\tube' \subseteq \tube$), or disjoint and non-adjacent (\ie $\tube \cup \tube'$ is not a tube of~$\graphG$).
A \defn{tubing} on~$\graphG$ is a set~$\tubing$ of pairwise compatible proper tubes of~$\graphG$.
See \cref{fig:exmNested}.
The \defn{nested complex} of~$\graphG$ is the simplicial complex~$\nestedComplex(\graphG)$ of all tubings~on~$\graphG$.

\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[width=\textwidth]{exmNested}}
	\caption{Some incompatible tubes (left and middle), and a maximal tubing (right).}
	\label{fig:exmNested}
\end{figure}

\para{Nested fan and graph associahedron}
%
Let~$(\b{e}_v)_{v \in \ground}$ be the canonical basis of~$\R^\ground$.
We consider the hyperplane~${\HH \eqdef \bigset{\b{x} \in \R^\ground}{\sum_{w \in W} x_w = 0 \text{ for all } W \in \connectedComponents(\graphG)}}$ and let~$\pi : \R^\ground \to \HH$ denote the orthogonal projection on~$\HH$.

\begin{definition}
The \defn{$\b{g}$-vector} of a tube~$\tube$ of~$\graphG$ is the projection~$\gvector{\tube} \eqdef \pi \big( \sum_{v \in \tube} \b{e}_v \big)$ of the characteristic vector of~$\tube$.
We set~$\gvectors{\tubing} \eqdef \set{\gvector{\tube}}{\tube \in \tubing}$ for a tubing~$\tubing$ on~$\graphG$.
\end{definition}

Note that by definition, $\gvector{\varnothing} = 0$ and $\gvector{W} = 0$ for all connected components~$W \in \connectedComponents(\graphG)$.
These vectors support a complete simplicial fan realization of the nested complex.
Examples are illustrated in \cref{fig:nestedFans}.

\begin{figure}[b]
	\capstart
	\centerline{\includegraphics[scale=.55]{nestedFans}}
	\caption{Two nested fans. As the fans are $3$-dimensional, we intersect them with the sphere and stereographically project them from the direction~$(-1,-1,-1)$.}
	\label{fig:nestedFans}
\end{figure}

\begin{theorem}[\cite{CarrDevadoss, Postnikov, FeichtnerSturmfels, Zelevinsky}]
\label{thm:nestedFan}
For any graph~$\graphG$, the set of cones
\[
\gvectorFan[\graphG] \eqdef \set{\R_{\ge 0} \, \gvectors{\tubing}}{\tubing \text{ tubing on } \graphG}
\]
is a complete simplicial fan of~$\HH$, called \defn{nested fan} of~$\graphG$, which realizes the nested complex~$\nestedComplex(\graphG)$.
\end{theorem}

It is proved in~\cite{CarrDevadoss, Devadoss, Postnikov, FeichtnerSturmfels, Zelevinsky} that the nested fan comes from a polytope.
For any subset~$U \subseteq \ground$, denote by~$\triangle_U \eqdef \conv\set{\b{e}_u}{u \in U}$ the face of the standard simplex~$\triangle_\ground$ corresponding to~$U$.

\begin{theorem}[\cite{CarrDevadoss, Devadoss, Postnikov, FeichtnerSturmfels, Zelevinsky}]
For any graph~$\graphG$, the nested fan~$\gvectorFan[\graphG]$ is the normal fan of the graph associahedron~$\Asso[\graphG]$.
It can be constructed as
\begin{itemize}
\item the intersection of~$\HH$ with the hyperplanes~$\dotprod{\gvector{\tube}}{\b{x}} \le 3^{|\tube|-2}$ for all tubes~$\tube \in \tubes$~\cite{Devadoss},
\item the Minkowski sum~$\sum_{\tube \in \tubes} \triangle_{\tube}$ of the faces of the standard simplex corresponding to all tubes of~$\graphG$~\cite{Postnikov}.
\end{itemize}
\end{theorem}

\para{Flips in the nested fan}
%
The following statement follows from~\cite{MannevillePilaud-compatibilityFans, Zelevinsky}.

\begin{proposition}
\label{prop:exchangeablePairsGA}
Let~$\tube, \tube'$ be two tubes of~$\graphG$. Then
\begin{enumerate}[(i)]
\item The tubes~$\tube$ and~$\tube'$ are exchangeable if and only if $\tube'$ has a unique neighbor~$v$ in~$\tube \ssm \tube'$ and $\tube$ has a unique neighbor~$v'$ in~$\tube' \ssm \tube$.
\item For any maximal tubings~$\tubing, \tubing'$ on~$\graphG$ with $\tubing \ssm \{\tube\} = \tubing' \ssm \{\tube'\}$, both~$\tubing \cup \connectedComponents(\graphG)$ and~$\tubing' \cup \connectedComponents(\graphG)$ contain the tube~$\tube \cup \tube'$ and the connected components of~$\tube \cap \tube'$.
\item The linear dependence between the $\b{g}$-vectors of~$\tubing \cup \tubing'$ is given by
\[
\gvector{\tube} + \gvector{\tube'} = \gvector{\tube \cup \tube'} + \sum_{\tube[s] \in \connectedComponents(\tube \cap \tube')} \gvector{\tube[s]}.
\]
\item The nested fan of~$\graphG$ has the unique exchange relation property.
\item The $\b{c}$-vector orthogonal to all $\b{g}$-vectors~$\gvector{\tube[s]}$ for~$\tube[s] \in \tubing \cap \tubing'$ is~$\b{e}_v - \b{e}_{v'}$.
\end{enumerate}
\end{proposition}

\begin{proof}
Points~(i) and~(ii) was proved in~\cite{MannevillePilaud-compatibilityFans}. Point~(iii) follows from the fact that
\[
\sum_{v \in \tube} \b{e}_v + \sum_{v \in \tube'} \b{e}_v = \sum_{v \in \tube \cup \tube'} \b{e}_v + \sum_{v \in \tube \cap \tube'} \b{e}_v = \sum_{v \in \tube \cup \tube'} \b{e}_v + \sum_{\substack{\tube[s] \in \connectedComponents(\tube \cap \tube') \\ v \in \tube[s]}} \b{e}_v.
\]
Point~(iv) is obtained by combining~(ii) and~(iii).
Finally for~(v), any tube~$\tube[s] \in \tubing \cap \tubing'$ that contains~$v$ or~$v'$ actually contains both (to be compatible with~$\tube$ and~$\tube'$). Therefore, $\gvector{\tube[s]}$ is orthogonal to~$\b{e}_v - \b{e}_{v'}$ for any tube~$\tube[s] \in \tubing \cap \tubing'$.
\end{proof}

%%%

\subsubsection{Type cones of graphical nested fans}

We now discuss the type cones of the graphical nested fans defined in \cref{thm:nestedFan}.
We first obtain from \cref{prop:exchangeablePairsGA} the following redundant description.

\begin{corollary}
\label{coro:typeConeGA}
For any graph~$\graphG$, the type cone of the nested fan~$\gvectorFan[\graphG]$ is given by
\[
\typeCone \big( \gvectorFan[\graphG] \big) = \set{\b{h} \in \R^{\tubes}}{\begin{array}{l} \b{h}_{\tube} = 0 \text{ for any improper tube } \tube \\ \b{h}_{\tube} + \b{h}_{\tube'} > \b{h}_{\tube \cup \tube'} + \sum_{\tube[s] \in \connectedComponents(\tube \cap \tube')} \b{h}_{\tube[s]} \text{ for any exchangeable tubes } \tube, \tube' \end{array}}.
\]
\end{corollary}

\begin{example}
For the complete graph~$\graphG[K]_n$, the admissible height vectors are precisely the submodular functions, \ie the functions~$\b{h} : 2^{[n]} \to \R$ such that~$\b{h}_{\varnothing} = 0$ and~$\b{h}_{A} + \b{h}_{B} > \b{h}_{A \cap B} + \b{h}_{A \cup B}$ for any~$A, B \subseteq [n]$.
This is precisely the description of the generalized permutahedra introduced by A.~Postnikov in~\cite{Postnikov} and E.-M.~Feichtner and B.~Sturmfels in~\cite{FeichtnerSturmfels}.
\end{example}

\begin{example}
\label{exm:typeConeGA}
Consider the nested fans illustrated in \cref{fig:nestedFans}.
The type cone of the left fan lives in~$\R^{13}$, has a linearity space of dimension~$3$ and $19$ facet-defining inequalities (given below). In particular, it is not simplicial.

\medskip
\centerline{$
\begin{array}{r|c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c}
\text{tubes} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeA1}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeA2}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeA3}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeA4}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeA5}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeA6}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeA7}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeA8}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeA9}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeA10}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeA11}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeA12}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeA13}}  \\[.6cm]
\text{$\b{g}$-vectors} & \compactVectorT{1}{0}{0} & \compactVectorT{0}{2}{0} & \compactVectorT{0}{0}{1} & \compactVectorT{0}{2}{-1} & \compactVectorT{1}{-2}{1} & \compactVectorT{1}{-2}{0} & \compactVectorT{1}{0}{-1} & \compactVectorT{-1}{2}{0} & \compactVectorT{-1}{0}{1} & \compactVectorT{-1}{0}{0} & \compactVectorT{0}{-2}{1} & \compactVectorT{0}{-2}{0} & \compactVectorT{0}{0}{-1} \\[.6cm]
\text{facet}		& 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & -1 & 1 \\
\text{defining}		& 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 & 0 & 1 & 0 & -1 & 0 \\
\text{inequalities}	& -1 & 1 & 0 & -1 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 \\
					& 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & -1 & -1 & 1 & 0 \\
					& 0 & 0 & 0 & 0 & 0 & -1 & 1 & 0 & 0 & 0 & 0 & 1 & -1 \\
					& -1 & 1 & -1 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
					& -1 & 0 & 0 & 0 & 1 & -1 & 1 & 0 & 0 & 0 & 0 & 0 & 0 \\
					& 0 & 1 & -1 & 0 & 0 & 0 & 0 & -1 & 1 & 0 & 0 & 0 & 0 \\
					& 0 & 0 & -1 & 0 & 1 & 0 & 0 & 0 & 1 & 0 & -1 & 0 & 0 \\
					& 0 & 0 & 0 & 0 & 1 & -1 & 0 & 0 & 0 & 0 & -1 & 1 & 0 \\
					& 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & -1 & 1 & 0 & 0 & 0 \\
					& 0 & 0 & 1 & 0 & -1 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
					& 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & -1 & 0 & 1 & 0 & 0 \\
					& 1 & 0 & 0 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 0 & 0 & 1 \\
					& 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 \\
					& 1 & -1 & 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 \\
					& 0 & 0 & 0 & 1 & 0 & 0 & 0 & -1 & 0 & 1 & 0 & 0 & -1 \\
					& 0 & 0 & 0 & 1 & 0 & 1 & -1 & 0 & 0 & 0 & 0 & 0 & 0 \\
					& 0 & -1 & 1 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\[.2cm]
\end{array}
$}

%sage: G = Graph([[1,2,3,4], [[1,2],[1,3],[1,4],[2,3],[3,4]]])
%sage: M = Matrix([g_vector_GA(G, (1,)), g_vector_GA(G, (1,2)), g_vector_GA(G, (1,2,3)), [1,1,1,1]]).inverse()
%sage: rays = {tuple(tube) : (g_vector_GA(G, tube)*M)[:-1] for tube in tubes(G)}
%sage: rays
%{(1,): (1, 0, 0),
% (1, 2): (0, 1, 0),
% (1, 2, 3): (0, 0, 1),
% (1, 2, 3, 4): (0, 0, 0),
% (1, 2, 4): (0, 2, -1),
% (1, 3): (1/2, -1, 1/2),
% (1, 3, 4): (1, -2, 0),
% (1, 4): (1/2, 0, -1/2),
% (2,): (-1, 2, 0),
% (2, 3): (-1/2, 0, 1/2),
% (2, 3, 4): (-1, 0, 0),
% (3,): (0, -2, 1),
% (3, 4): (0, -1, 0),
% (4,): (0, 0, -1)}

%sage: NF = Fan([Cone([rays[tuple(tube)] for tube in tubing]) for tubing in maximal_tubings(G)])
%sage: NF.rays()
%N( 0, -1,  0),
%N( 0,  2, -1),
%N( 1,  0,  0),
%N(-1,  2,  0),
%N( 0,  0,  1),
%N( 1, -2,  0),
%N( 0, -2,  1),
%N( 0,  0, -1),
%N(-1,  0,  1),
%N( 1,  0, -1),
%N(-1,  0,  0),
%N( 0,  1,  0),
%N( 1, -2,  1)
%in 3-d lattice N

%sage: TCNF = type_cone(NF)
%sage: TCNF
%A 13-dimensional polyhedron in QQ^13 defined as the convex hull of 1 vertex, 25 rays, 3 lines
%sage: TCNF.lines()
%(A line in the direction (0, 0, 1, -1, 0, 1, 0, 0, -1, 1, -1, 0, 1),
% A line in the direction (1, -2, -2, 0, 0, 0, 2, 0, 2, -2, 2, -1, 0),
% A line in the direction (0, 1, 0, 0, -1, 0, -1, 1, -1, 1, 0, 0, -1))
%sage: TCNF.inequalities()
%(An inequality (-2, 0, 0, 0, 0, 0, 1, 1, 0, 0, 0, 0, 0) x + 0 >= 0,
% An inequality (-2, 0, 0, 0, 0, 1, 0, 0, 0, 0, 1, 0, 0) x + 0 >= 0,
% An inequality (0, -1, -1, 0, 0, 0, 0, 0, 0, 1, 0, 2, 0) x + 0 >= 0,
% An inequality (2, 0, 0, 0, 0, 0, -1, 0, 1, 0, -1, 0, 0) x + 0 >= 0,
% An inequality (2, 0, 0, 0, 0, -1, 0, -1, 0, 1, 0, 0, 0) x + 0 >= 0,
% An inequality (0, 0, -1, 0, -1, 0, 0, 0, 0, 0, 0, 2, 1) x + 0 >= 0,
% An inequality (0, 0, -1, 0, 0, -1, 0, 0, 0, 1, 0, 0, 1) x + 0 >= 0,
% An inequality (0, 0, 0, -1, -1, 0, 0, 0, 1, 0, 0, 2, 0) x + 0 >= 0,
% An inequality (0, 0, 0, 0, -1, 0, -1, 0, 1, 0, 0, 0, 1) x + 0 >= 0,
% An inequality (2, 0, 0, 0, 0, -1, -1, 0, 0, 0, 0, 0, 1) x + 0 >= 0,
% An inequality (0, 0, 0, 0, 1, 0, 0, 0, -1, 0, 1, 0, 0) x + 0 >= 0,
% An inequality (0, 0, 0, 0, 1, 1, 0, 0, 0, 0, 0, 0, -1) x + 0 >= 0,
% An inequality (0, 0, 0, 1, 0, 0, 1, 0, -1, 0, 0, 0, 0) x + 0 >= 0,
% An inequality (0, 0, 1, 0, 0, 0, 0, 1, 0, -1, 0, 0, 0) x + 0 >= 0,
% An inequality (0, 0, 1, 0, 0, 0, 1, 0, 0, 0, 0, 0, -1) x + 0 >= 0,
% An inequality (0, 0, 1, 1, 0, 0, 0, 0, 0, 0, 0, -2, 0) x + 0 >= 0,
% An inequality (0, 1, 0, -1, 0, 0, 0, -1, 0, 0, 1, 0, 0) x + 0 >= 0,
% An inequality (0, 1, 0, 0, 0, 1, 0, 0, 0, -1, 0, 0, 0) x + 0 >= 0,
% An inequality (0, 1, 0, 0, 1, 0, 0, 0, 0, 0, 0, -2, 0) x + 0 >= 0)
%sage: len(TCNF.inequalities())
%12

\medskip
\noindent
The type cone of the right fan lives in~$\R^{11}$, has a linearity space of dimension~$3$ and $12$ facet-defining inequalities (given below). In particular, it is not simplicial.

\[
\begin{array}{r|c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c@{\;\,}c}
\text{tubes} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeB1}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeB2}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeB3}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeB4}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeB5}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeB6}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeB7}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeB8}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeB9}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeB10}} & \raisebox{-.4cm}{\includegraphics[scale=.6]{tubeB11}} \\[.6cm]
\text{$\b{g}$-vectors} & \compactVectorT{1}{0}{0} & \compactVectorT{0}{2}{0} & \compactVectorT{0}{0}{1} & \compactVectorT{1}{-2}{1} & \compactVectorT{1}{-2}{0} & \compactVectorT{-1}{2}{0} & \compactVectorT{-1}{0}{1} & \compactVectorT{-1}{0}{0} & \compactVectorT{0}{-2}{1} & \compactVectorT{0}{-2}{0} & \compactVectorT{0}{0}{-1} \\[.6cm]
\text{facet}		& -1 & 1 & -1 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
\text{defining}		& 1 & -1 & 0 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 \\
\text{inequalities}	& 0 & 1 & -1 & 0 & 0 & -1 & 1 & 0 & 0 & 0 & 0 \\
					& 1 & 0 & 0 & -1 & 0 & 0 & 0 & 0 & 1 & 0 & 0 \\
					& 0 & 0 & -1 & 1 & 0 & 0 & 1 & 0 & -1 & 0 & 0 \\
					& 0 & 0 & 0 & 1 & -1 & 0 & 0 & 0 & -1 & 1 & 0 \\
					& 0 & 0 & 0 & 0 & 0 & 1 & -1 & 0 & 1 & 0 & 0 \\
					& 0 & 0 & 0 & 0 & 0 & 0 & 1 & -1 & -1 & 1 & 0 \\
					& 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & -1 & 1 \\
					& 0 & 0 & 0 & 0 & 1 & 0 & 0 & 1 & 0 & -1 & 0 \\
					& 0 & 0 & 1 & 0 & 0 & 0 & -1 & 1 & 0 & 0 & 0 \\
					& 0 & 0 & 1 & -1 & 1 & 0 & 0 & 0 & 0 & 0 & 0 \\[.2cm]
\end{array}
\]

%sage: G = Graph([[1,2,3,4], [[1,2],[1,3],[2,3],[3,4]]])
%sage: M = Matrix([g_vector_GA(G, (1,)), g_vector_GA(G, (1,2)), g_vector_GA(G, (1,2,3)), [1,1,1,1]]).inverse()
%sage: rays = {tuple(tube) : (g_vector_GA(G, tube)*M)[:-1] for tube in tubes(G)}
%sage: rays
%{(1,): (1, 0, 0),
% (1, 2): (0, 1, 0),
% (1, 2, 3): (0, 0, 1),
% (1, 2, 3, 4): (0, 0, 0),
% (1, 3): (1/2, -1, 1/2),
% (1, 3, 4): (1, -2, 0),
% (2,): (-1, 2, 0),
% (2, 3): (-1/2, 0, 1/2),
% (2, 3, 4): (-1, 0, 0),
% (3,): (0, -2, 1),
% (3, 4): (0, -1, 0),
% (4,): (0, 0, -1)}

%sage: NF = Fan([Cone([rays[tuple(tube)] for tube in tubing]) for tubing in maximal_tubings(G)])
%sage: NF.rays()
%N( 1,  0,  0),
%N(-1,  2,  0),
%N( 0,  0,  1),
%N( 1, -2,  0),
%N( 0,  0, -1),
%N(-1,  0,  1),
%N( 1, -2,  1),
%N( 0, -2,  1),
%N(-1,  0,  0),
%N( 0,  1,  0),
%N( 0, -1,  0)
%in 3-d lattice N

%sage: TCNF = type_cone(NF)
%sage: TCNF
%A 11-dimensional polyhedron in QQ^11 defined as the convex hull of 1 vertex, 11 rays, 3 lines
%sage: TCNF.lines()
%(A line in the direction (0, 2, 0, -2, 0, 0, -2, -2, 0, 1, -1),
% A line in the direction (1, -1, 0, 1, 0, -1, 1, 0, -1, 0, 0),
% A line in the direction (1, -1, 1, 1, -1, 0, 2, 1, -1, 0, 0))
%sage: TCNF.inequalities()
%(An inequality (-1, 0, -1, 0, 0, 0, 1, 0, 0, 2, 0) x + 0 >= 0,
% An inequality (1, 1, 0, 0, 0, 0, 0, 0, 0, -2, 0) x + 0 >= 0,
% An inequality (0, -1, -1, 0, 0, 1, 0, 0, 0, 2, 0) x + 0 >= 0,
% An inequality (1, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0) x + 0 >= 0,
% An inequality (0, 0, -1, 0, 0, 1, 1, -1, 0, 0, 0) x + 0 >= 0,
% An inequality (0, 0, 0, -1, 0, 0, 1, -1, 0, 0, 2) x + 0 >= 0,
% An inequality (0, 1, 0, 0, 0, -1, 0, 1, 0, 0, 0) x + 0 >= 0,
% An inequality (0, 0, 0, 0, 0, 1, 0, -1, -1, 0, 2) x + 0 >= 0,
% An inequality (0, 0, 0, 0, 1, 0, 0, 1, 0, 0, -2) x + 0 >= 0,
% An inequality (0, 0, 0, 1, 0, 0, 0, 0, 1, 0, -2) x + 0 >= 0,
% An inequality (0, 0, 1, 0, 0, -1, 0, 0, 1, 0, 0) x + 0 >= 0,
% An inequality (0, 0, 1, 1, 0, 0, -1, 0, 0, 0, 0) x + 0 >= 0)
%sage: len(TCNF.inequalities())
%12
\medskip
\end{example}

In the remaining of this section, we describe the facet-defining inequalities of the type cone of the graphical nested fans.
Observe first that we have already indirectly described this type cone when the graph is a path in \cref{prop:extremalExchangeablePairsAsso}.
Recall that on the path with~$n+1$ vertices, the tubes of the path are the intervals of~$[n+1]$ and that two intervals~$[i,j]$ and~$[i',j']$ of~$[n+1]$ are exchangeable if either~${i < i' \le j+1 < j'+1}$ or~${i' < i \le j'+1 < j+1}$.

\begin{proposition}
\label{prop:extremalExchangeablePairsA}
Two intervals~$[i,j]$ and~$[i',j']$ of~$[n+1]$ form an extremal exchangeable pair for the nested fan of the path if and only if~$i = i'+1$ and~$j = j'+1$, or the opposite.
\end{proposition}

We now consider an arbitrary graph~$\graphG$ and describe the type cone of its nested fan.
We give a necessary condition for an exchangeable pair to be extremal in \cref{lem:extremalExchangeablePairsGAonlyif}, exploit it in \cref{exm:constructionsGA}, and prove that it is actually a sufficient condition in \cref{prop:extremalExchangeablePairsGA}

\begin{lemma}
\label{lem:extremalExchangeablePairsGAonlyif}
If two tubes~$\tube$ and~$\tube'$ of~$\graphG$ form an extremal exchangeable pair for the nested fan of~$\graphG$, then~${\tube \ssm \{v\} = \tube' \ssm \{v'\}}$ for some neighbor~$v$ of~$\tube'$ and some neighbor~$v'$ of~$\tube$.
\end{lemma}

\begin{proof}
Consider an exchangeable pair~$\{\tube, \tube'\}$ of tubes of~$\graphG$.
The inner normal vector of the corresponding inequality of the type cone is
\[
\b{n}(\tube, \tube') \eqdef \b{f}_{\tube} + \b{f}_{\tube'} - \b{f}_{\tube\cup \tube'} - \sum_{\tube[s] \in \connectedComponents(\tube \cap \tube')} \b{f}_{\tube[s]}.
\]

By \cref{prop:exchangeablePairsGA}, $\tube'$ has a unique neighbor~$v$ in~$\tube \ssm \tube'$ and $\tube$ has a unique neighbor~$v'$ in~$\tube' \ssm \tube$.
Therefore, $\tube \ssm \tube'$ and~$\tube' \ssm \tube$ are both connected. Assume that $\tube \ssm \tube'\ne \{v\}$, and let $w\ne v$ be a non-disconnecting node of $\tube \ssm \tube'$. By \cref{prop:exchangeablePairsGA}, $\tilde \tube \eqdef \tube \ssm \{w\}$ and $\tube'$ are exchangeable, and $\tilde \tube' \eqdef (\tube \cup \tube') \ssm \{w\}$ and $\tube$ are exchangeable as well. Moreover, we have
\begin{align*}
\b{n}(\tilde \tube, \tube') + \b{n}( \tube, \tilde \tube')
& = \Big( \b{f}_{\tilde \tube} + \b{f}_{\tube'} - \b{f}_{\tilde \tube\cup \tube'} - \sum_{\tube[s] \in \connectedComponents(\tilde \tube \cap \tube')} \b{f}_{\tube[s]} \Big)
+ \Big( \b{f}_{\tube} + \b{f}_{\tilde \tube'} - \b{f}_{\tube\cup \tilde \tube'} - \sum_{\tube[s] \in \connectedComponents(\tube \cap \tilde \tube')} \b{f}_{\tube[s]} \Big) \\
& = \b{f}_{\tube} + \b{f}_{\tube'} - \b{f}_{\tube\cup \tube'} - \sum_{\tube[s] \in \connectedComponents(\tube \cap \tube')} \b{f}_{\tube[s]} =\b{n}(\tube, \tube'),
\end{align*}
as $\tilde \tube \cup \tube' = \tilde \tube'$, $\tilde \tube \cap \tube' = \tube \cap \tube'$, $\tube \cup \tilde \tube' = \tube \cup \tube'$ and $\connectedComponents(\tube \cap \tilde \tube') = \connectedComponents(\tilde \tube) = \tilde \tube$.
Therefore $\b{n}(\tube, \tube')$ defines a redundant inequality and $\{\tube, \tube'\}$ is not an extremal exchangeable pair.
The proof is symmetric if~$\tube' \ssm \tube \ne \{v'\}$.
\end{proof}

\begin{example}
\label{exm:constructionsGA}
We now exploit \cref{lem:extremalExchangeablePairsGAonlyif} to show that certain height functions belong to the type cone of~$\gvectorFan[\graphG]$ and recover the classical constructions of the graph associahedron.

\begin{enumerate}
\item Consider the height function~$\b{h} \in \R^{\tubes}$ given by~$\b{h}_{\tube} \eqdef -|\bigset{\tube[s] \in \tubes}{\tube[s] \subseteq \tube}|$. Then for any tubes~$\tube$ and~$\tube'$ such that ${\tube \ssm \{v\} = \tube' \ssm \{v'\}}$ for some neighbor~$v$ of~$\tube'$ and some neighbor~$v'$ of~$\tube$, we have
\[
\qquad\qquad
\dotprod{\b{n}(\tube, \tube')}{\b{h}} = |\bigset{\tube[s]\in\tubes}{\tube \symdif \tube' \subseteq \tube[s] \subseteq \tube \cup \tube'}|,
\]
where~$\tube \symdif \tube' = \{v,v'\}$ denotes the symmetric difference.
This quantity is positive since at least~$\tube \cup \tube'$ fulfills the condition.
Thus, the height function~$\b{h}$ belongs to the type cone~$\typeCone \big( \gvectorFan[\graphG] \big)$.
The polytope~$P_\b{h} \eqdef \set{\b{x} \in \R^\ground}{\dotprod{\gvector{\tube}}{\b{x}} \le \b{h}_{\tube} \text{ for any tube } \tube \in \tubes}$ is the graph associahedron constructed by A.~Postnikov's in~\cite{Postnikov}.
\item Consider now the height function~$\b{h} \in \R^{\tubes}$ given by~$\b{h}_{\tube} \eqdef -3^{|\tube|-2}$. Then for any tubes~$\tube$ and~$\tube'$ such that ${\tube \ssm \{v\} = \tube' \ssm \{v'\}}$ for some neighbor~$v$ of~$\tube'$ and some neighbor~$v'$ of~$\tube$, we have
\[
\qquad\qquad
\dotprod{\b{n}(\tube, \tube')}{\b{h}} = - 3^{|\tube|-2} - 3^{|\tube'|-2} + 3^{|\tube \cup \tube'|-2} + \sum_{\tube[s] \in \connectedComponents(\tube \cap \tube')} 3^{|\tube[s]|-2 } \ge - 2 \cdot 3^{|\tube \cup \tube'|-1} + 3^{|\tube \cup \tube'|} > 0.
\]
Thus, the height function~$\b{h}$ belongs to the type cone~$\typeCone \big( \gvectorFan[\graphG] \big)$.
The corresponding polytope~$P_\b{h}$ is the graph associahedron constructed by S.~Devadoss's in~\cite{Devadoss}.
\item Finally, consider the height function~$\b{h} \in \R^{\tubes}$ given by~$\b{h}_{\tube} \eqdef |\bigset{\tube[s] \in \tubes}{\tube[s] \supseteq \tube}|$. Then for any tubes~$\tube$ and~$\tube'$ such that ${\tube \ssm \{v\} = \tube' \ssm \{v'\}}$ for some neighbor~$v$ of~$\tube'$ and some neighbor~$v'$ of~$\tube$, we have
\begin{align*}
\qquad\qquad
\dotprod{\b{n}(\tube, \tube')}{\b{h}} = \; & |\bigset{(\tube[r], \tube[s]) \in \tubes \times \connectedComponents(\tube \cap \tube')}{\tube[s] \subseteq \tube[r] \text{ and } \tube, \tube' \not\subseteq \tube[r]}| \\
& + \big( |\connectedComponents(\tube \cap \tube')|-1 \big) \cdot | \bigset{\tube[r] \in \tubes}{\tube \text{ or } \tube'\subseteq \tube[r]}\big|.
\end{align*}
Any connected component of~$\tube \cap \tube'$ certifies the positivity of this evaluation, showing that the height function~$\b{h}$ belongs to~$\typeCone \big( \gvectorFan[\graphG] \big)$. The corresponding realization~$P_\b{h}$ of the graph associahedron is new, to the best of our knowledge. 
\end{enumerate}
\end{example}

We now show that the condition of \cref{lem:extremalExchangeablePairsGAonlyif} actually characterizes the extremal exchangeable pairs of the nested fan~$\gvectorFan[\graphG]$.

\begin{proposition}
\label{prop:extremalExchangeablePairsGA}
Two tubes~$\tube$ and~$\tube'$ of~$\graphG$ form an extremal exchangeable pair for the nested fan of~$\graphG$ if and only if~${\tube \ssm \{v\} = \tube' \ssm \{v'\}}$ for some neighbor~$v$ of~$\tube'$ and some neighbor~$v'$ of~$\tube$.
\end{proposition}

\begin{proof}
By \cref{lem:extremalExchangeablePairsGAonlyif}, an exchangeable pair $\{\tube, \tube'\}$ is not extremal unless both $\tube \ssm \tube'$ and $\tube' \ssm \tube$ are singletons. We now need to show that all these pairs are extremal. Until we finish the proof, we will call such a pair a \defn{suspected extremal pair}.

Let $\{\tube, \tube'\}$ be a suspected extremal pair.
To prove that it is extremal, we will construct a vector $\b{w} \in \R^{\tubes}$ such that $\dotprod{\b{n}(\tube, \tube')}{\b{w}}< 0,$
but $\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{w}}>0$ for any other suspected extremal pair $\{\tilde \tube, \tilde \tube'\}$. This will show that the inequality induced by~$\{\tube, \tube'\}$ is not redundant.

Define $\alpha(\tube,\tube') \eqdef \set{\tube[r] \in \tubes}{\tube \symdif \tube' \subseteq \tube[r] \subseteq \tube \cup \tube'}$, where $\symdif$ denotes the symmetric difference, and define $\b{x} \in \R^{\tubes}$ be such that
\[
\b{x}_{\tube[s]} = -|\bigset{\tube[r] \in \tubes \ssm \alpha(\tube, \tube')}{\tube[r] \subseteq \tube[s]}|
\]
for each tube~$\tube[s] \in \tubes$.
For any suspected extremal pair $\{\tilde \tube, \tilde \tube'\}$ we have
\[
\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{x}} = |\alpha(\tilde \tube, \tilde \tube')\ssm \alpha(\tube, \tube')| \ge 0.
\]
Notice that $\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{x}} = 0$ if $\alpha(\tilde \tube, \tilde \tube') \subseteq \alpha(\tube,\tube')$ and $\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{x}} \ge 1$ otherwise.
In particular, if $\{\tilde \tube, \tilde \tube'\} \ne \{\tube, \tube'\}$ then $\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{x}} \ge 1$ unless $\tilde \tube \cup \tilde \tube' \subsetneq \tube \cup \tube'$ because $\tilde \tube \cup \tilde \tube' \in \alpha(\tilde \tube, \tilde \tube')$, and if $\tilde \tube \cup \tilde \tube' = \tube \cup \tube'$ but $\{\tilde \tube, \tilde \tube'\} \ne \{\tube, \tube'\}$, then either $\tube$ or $\tube'$ will belong to $\alpha(\tilde \tube, \tilde \tube')$.

Now, define $\b{y}\in\R^{\tubes}$ by
\[
\b{y}_{\tube[s]} = \begin{cases}
	-1 & \text{ if } |\tube[s]| \ge |\tube|, \\
	0 & \text{ otherwise},
\end{cases}
\]
for each tube~$\tube[s] \in \tubes$.
We have $\dotprod{\b{n}(\tube, \tube')}{\b{y}} = -1$. For any suspected extremal pair $\{\tilde \tube, \tilde \tube'\}$ we have $\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{y}} \ge -1$. If moreover $\tilde \tube \cup \tilde \tube' \subsetneq \tube \cup \tube'$, then we have $\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{y}} \ge 0$.

Finally, consider $\b{z} \in \R^{\tubes}$ given by
\[
\b{z}_{\tube[s]} = -|\bigset{\tube[r] \in \alpha(\tube, \tube')}{\tube[r] \subseteq \tube[s]}|,
\]
for each tube~$\tube[s] \in \tubes$.
It verifies $\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{z}} \ge 0$ for any suspected extremal pair~$\{\tilde \tube, \tilde \tube'\}$, and $\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{z}} = |\alpha(\tilde \tube, \tilde \tube')| > 0$ if $\alpha(\tilde \tube, \tilde \tube') \subseteq \alpha(\tube, \tube')$.

For $0 < \varepsilon < 1$, and $0 < \delta < \frac{\varepsilon}{|\alpha(\tube, \tube')|}$, we claim that the vector $\b{w} \eqdef \b{x} + \varepsilon \b{y} + \delta \b{z}$ fulfills the desired properties.
Indeed, if $\{\tilde \tube, \tilde \tube'\} \ne \{\tube,\tube'\}$ is a suspected extremal pair with $\alpha(\tilde \tube, \tilde \tube') \not \subseteq \alpha(\tube,\tube')$, then 
\[
\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{w}} = \underbrace{\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{x}}}_{\ge 1} + \underbrace{\varepsilon \dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{y}}}_{> -1} + \underbrace{\delta \dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{z}}}_{\ge 0} > 0.
\]
If $\{\tilde \tube, \tilde \tube'\} \ne \{\tube,\tube'\}$ is a suspected extremal pair with $\alpha(\tilde \tube, \tilde \tube') \subseteq \alpha(\tube,\tube')$, then $\tilde \tube \cup \tilde \tube' \subsetneq \tube \cup \tube'$ and 
\[
\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{w}} = \underbrace{\dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{x}}}_{= 0} + \underbrace{\varepsilon \dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{y}}}_{\ge 0} + \underbrace{\delta \dotprod{\b{n}(\tilde \tube, \tilde \tube')}{\b{z}}}_{> 0} > 0.
\]
However,
\[
\dotprod{\b{n}(\tube, \tube')}{\b{w}} = \underbrace{\dotprod{\b{n}(\tube, \tube')}{\b{x}}}_{= 0} + \underbrace{\varepsilon \dotprod{\b{n}(\tube, \tube')}{\b{y}}}_{= -\varepsilon} + \underbrace{\delta \dotprod{\b{n}( \tube,  \tube')}{\b{z}}}_{= \delta |\alpha(\tube ,\tube')| < \varepsilon} < 0.
\qedhere
\]
\end{proof}

The following statement reformulates \cref{prop:extremalExchangeablePairsGA}.

\begin{corollary}
\label{coro:extremalExchangeablePairsGA}
The extremal exchangeable pairs for the nested fan of~$\graphG$ are precisely the pairs of tubes~${\tube[s] \ssm \{v'\}}$ and~${\tube[s] \ssm \{v\}}$ for any tube~$\tube[s] \in \tubes$ and distinct non-disconnecting vertices~$v,v'$~of~$\tube[s]$.
\end{corollary}

\enlargethispage{-.1cm}
We derive from \cref{prop:extremalExchangeablePairsGA} and \cref{coro:extremalExchangeablePairsGA} all polytopal realizations of the nested fan.

\begin{corollary}
\label{coro:typeconenestedfan}
Consider a graph~$\graphG$ on~$\ground$ with tubes~$\tubes$. 
Then, for a height vector~$\b{h} \in \R^{\tubes}$, the nested fan~$\gvectorFan[\graphG]$ is the normal fan of the graph associahedron
\[
\set{\b{x} \in \R^\ground}{\dotprod{\gvector{\tube}}{\b{x}} \le \b{h}_{\tube} \text{ for any tube } \tube \in \tubes}
\]
if and only if~$\b{h}_{\varnothing} = \b{h}_{\graphG} = 0$ and
 $\b{h}_{\tube[s] \ssm \{v'\}} + \b{h}_{\tube[s] \ssm \{v\}} > \b{h}_{\tube[s]} + \b{h}_{\tube[s] \ssm \{v, v'\}}$ for any tube~$\tube[s] \in \tubes$ and distinct non-disconnecting vertices~$v,v'$ of~$\tube[s]$.
\end{corollary}

We also obtain from \cref{prop:extremalExchangeablePairsGA} the following surprising property.

\begin{corollary}
Any $\b{c}$-vector supports at least one extremal exchangeable pair.
\end{corollary}

\begin{proof}
Consider a $\b{c}$-vector~$\b{e}_v - \b{e}_{v'}$ for two distinct vertices~$v, v'$ in a common connected component of~$\graphG$. Let~$\tube[r]$ be a path from~$v$ to~$v'$ in~$\graphG$ and let~$\tube \eqdef \tube[r] \cup \{v\}$ and~$\tube' \eqdef \tube[r] \cup \{v'\}$. Then $\{\tube, \tube'\}$ is an extremal exchangeable pair with $\b{c}$-vector~$\b{e}_v - \b{e}_{v'}$.
\end{proof}

We derive from \cref{coro:extremalExchangeablePairsGA} the number of extremal exchangeable pairs of the nested fan.
For a tube~$\tube$ of~$\graphG$, we denote by~$\nonDisconnecting(\tube)$ the number of non-disconnecting vertices of~$\tube$.
In other words, $\nonDisconnecting(\tube)$ is the number of tubes covered by~$\tube$ in the inclusion poset of all tubes of~$\graphG$.

\begin{corollary}
\label{coro:numberExtremalExchangeablePairsGA}
The nested fan~$\gvectorFan[\graphG]$ has~$\!\!\!\! \sum\limits_{\tube[s] \in \tubes} \!\! \binom{\nonDisconnecting(\tube[s])}{2}$ extremal exchangeable pairs.
\end{corollary}

The formula of \cref{coro:numberExtremalExchangeablePairsGA} can be made more explicit for specific families of graph associahedra discussed in the introduction and illustrated in \cref{fig:specialGraphAssociahedra}.

\begin{proposition}
The number of extremal exchangeable pairs of the nested fan~$\gvectorFan[\graphG]$ is:
\begin{itemize}
\item $2^{n-2}\binom{n}{2}$ for the permutahedron (complete graph associahedron),
\item $\binom{n}{2}$ for the associahedron (path associahedron),
\item $3\binom{n}{2} - n$ for the cyclohedron (cycle associahedron),
\item $n-1+2^{n-3}\binom{n-1}{2}$ for the stellohedron (star associahedron).
\end{itemize}
\end{proposition}

\begin{proof}
For the permutahedron, choose any two vertices~$v,v'$, and complete them into a tube by selecting any subset of the~$n-2$ remaining vertices.
For the associahedron, choose any two vertices~$v,v'$, and complete them into a tube by taking the path between them.
For the cyclohedron, choose the two vertices~$v,v'$, and complete them into a tube by taking either all the cycle, or one of the two paths between~$v$ and~$v'$ (this gives three options in general, but only two when~$v,v'$ are neighbors).
For the stellohedron, choose either~$v$ as the center of the star and~$v'$ as one of the $n-1$ leaves, or $v$~and~$v'$ as leaves of the star and complete them into a tube by taking the center and any subset of the $n-3$ remaining leaves.
\end{proof}

To conclude on graph associahedra, we characterize the graphs~$\graphG$ whose nested fan has a simplicial type cone.

\begin{proposition}\label{prop:simplicialnestedfan}
The type cone~$\typeCone \big( \gvectorFan[\graphG] \big)$ is simplicial if and only if~$\graphG$ is a path.
\end{proposition}

\begin{proof}
Note that any tube~$\tube$ with~$|\tube| \ge 2$ has two non-disconnecting vertices when it is a path, and at least three non-disconnecting vertices otherwise (the leaves of an arbitrary spanning tree of~$\tube$, or any vertex if it is a cycle).
Therefore, each tube of~$\tubes$ which is not a singleton contributes to at least one extremal exchangeable pair.
We conclude that the number of extremal exchangeable pairs is at least:
\[
|\tubes| - |V| = |\tubes \ssm \{\varnothing, \graphG\}| - (|V|-1) = N - n,
\]
with equality if and only if all tubes of~$\graphG$ are paths, \ie if and only if~$\graphG$ is a path.
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\addtocontents{toc}{\vspace{.1cm}}
\section*{Acknowledgments}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage
\bibliographystyle{alpha}
\bibliography{typeConeGraphAssociahedra}
\label{sec:biblio}

\end{document}

### 2020-04-04 thirdPaper/draft/typeConeAssociahedra.tex
reshaped schematic diagram and created new paper on graph associahedra

@@
 	\node[diamond,aspect=3, text width=5cm, minimum height=1cm, align=center, draw=blue, fill=blue!10, inner sep=-2] (I1) at (0,1.5) {\ref{part:geometry}.\ref{sec:typeCone} -- Simplicial type cone strategy};
-	\node[rectangle, draw=black, fill=black!10, align=center] (I21) at (-6,-1.5) {\ref{part:geometry}.\ref{subsec:typeConeAsso} -- Toy example \\ Classical associahedra};
-	\node[rectangle, draw=orange, fill=orange!10, align=center, text width=5cm] (I22) at (0,-1.5) {\ref{part:geometry}.\ref{subsec:typeConeCA} -- Cluster algebras \\ \& generalized associahedra};
-	\node[rectangle, draw=green, fill=green!10, align=center, text width=5cm] (I23) at (6,-1.5) {\ref{part:geometry}.\ref{subsec:typeConeNKC} -- Gentle algebras \\ \& generalized accordiohedra};
+	\node[rectangle, draw=black, fill=black!10, align=center, minimum width = 5.3cm, minimum height=1.2cm] (I21) at (-6,-1.5) {\ref{part:geometry}.\ref{subsec:typeConeAsso} -- Toy example \\ Classical associahedra};
+	\node[rectangle, draw=orange, fill=orange!10, align=center, text width=5.3cm, minimum width = 5cm, minimum height=1.2cm] (I22) at (0,-1.5) {\ref{part:geometry}.\ref{subsec:typeConeCA} -- Cluster algebras \\ \& generalized associahedra};
+	\node[rectangle, draw=green, fill=green!10, align=center, text width=5.3cm, minimum width = 5cm, minimum height=1.2cm] (I23) at (6,-1.5) {\ref{part:geometry}.\ref{subsec:typeConeNKC} -- Gentle algebras \\ \& generalized accordiohedra};
 % 	\node[rectangle, draw=red, fill=red!10, align=center, text width=5.4cm] (I24) at (7,0) {\ref{part:geometry}.\ref{subsec:typeConeGA} -- Graphical nested complexes \\ \& graph associahedra};
-	\node[ellipse, draw=orange, fill=orange!10, align=center, text width=4.9cm, inner sep=2, minimum height=1cm] (II1) at (-4.5,-4.2) {\ref{part:algebra}.\ref{sec:clusterCategories} -- Cluster categories};
-	\node[ellipse, draw=green, fill=green!10, align=center, text width=4.9cm, inner sep=0, minimum height=1cm] (II2) at (4.5,-4.2) {\ref{part:algebra}.\ref{sec:extricats} -- Extriangulated categories};
-	\draw[decorate, decoration={shape backgrounds, shape=dart, shape size=2mm, shape evenly spread=8}, draw=blue, fill=blue!10] (I1.180) to [bend right, looseness=1.1] node[label={[shift={(-1.6,-1.5)}]applied to}]{} (I21.90);
-	\draw[decorate, decoration={shape backgrounds, shape=dart, shape size=2mm, shape evenly spread=3}, draw=blue, fill=blue!10] (I1.270) to node[label={[shift={(1,-1.)}]applied to}]{} (I22.90);
-	\draw[decorate, decoration={shape backgrounds, shape=dart, shape size=2mm, shape evenly spread=8}, draw=blue, fill=blue!10] (I1.360) to [bend left, looseness=1.1] node[label={[shift={(1.6,-1.5)}]applied to}]{} (I23.90);
+	\node[ellipse,
+% 	rectangle,rounded corners=10, 
+	draw=orange, fill=orange!10, align=center, text width=5cm, inner sep=2, minimum height=1cm] (II1) at (-4.5,-4.2) {\ref{part:algebra}.\ref{sec:clusterCategories} -- Cluster categories};
+	\node[ellipse,
+% 	rectangle,rounded corners=10,
+	draw=green, fill=green!10, align=center, text width=5cm, inner sep=0, minimum height=1cm] (II2) at (4.5,-4.2) {\ref{part:algebra}.\ref{sec:extricats} -- Extriangulated categories};
+	\draw[decorate, decoration={shape backgrounds, shape=dart, shape size=2mm, shape evenly spread=8}, draw=blue, fill=blue!10] (I1.180) to [bend right, looseness=1.1] node[label={[shift={(-1.6,-1.5)}]\textit{applied to}}]{} (I21.90);
+	\draw[decorate, decoration={shape backgrounds, shape=dart, shape size=2mm, shape evenly spread=3}, draw=blue, fill=blue!10] (I1.270) to node[label={[shift={(1,-1.)}]\textit{applied to}}]{} (I22.90);
+	\draw[decorate, decoration={shape backgrounds, shape=dart, shape size=2mm, shape evenly spread=8}, draw=blue, fill=blue!10] (I1.360) to [bend left, looseness=1.1] node[label={[shift={(1.6,-1.5)}]\textit{applied to}}]{} (I23.90);
 % 	\draw[decorate, decoration={shape backgrounds, shape=dart, shape size=2mm, shape evenly spread=10}, draw=blue, fill=blue!10] (I1.0) to [bend left, looseness=1.1] (I24.90);
 % 	\draw[decorate, decoration={markings, mark=at position 0.5 with {\draw [red, ultra thick,-] ++ (-.3,-.3)  -- ( .3, .3); \draw [red, ultra thick,-] ++ (-.3, .3)  -- ( .3,-.3);}}] (I1.0) to [bend left, looseness=1.1] node[label={[shift={(-.4,-1.7)}]not applicable to}]{} (I24.90);
-	\draw[thick, double distance=2pt, -implies] (I22.270)+(0,-1.3) to node[semithick, right, outer sep=0, pos=0.65]{used for} (I22.270)+(0,.15);
-	\draw[thick, double distance=2pt, -implies] (I23.270)+(0,-1.3) to node[semithick, right, outer sep=0, pos=0.65]{used for} (I23.270)+(0,.15);
-	\draw[thick, ->] (II1.0) to node[semithick, above, outer sep=0]{generalizes to} (II2.180);
+% 	\draw[thick, double distance=2pt, -implies] (I22.270)+(0,-1.3) to node[semithick, right, outer sep=0, pos=0.65]{\textit{used for}} (I22.270)+(0,.15);
+% 	\draw[thick, double distance=2pt, -implies] (I23.270)+(0,-1.3) to node[semithick, right, outer sep=0, pos=0.65]{\textit{used for}} (I23.270)+(0,.15);
+	\draw[thick, double distance=2pt, -implies, in=270] (I22.270)+(-1.5,-1.2) to node[semithick, right, outer sep=0, pos=0.55]{\textit{used for}} ([yshift=.2cm] I22.270);
+	\draw[thick, double distance=2pt, -implies, in=270] (I23.270)+(-1.5,-1.2) to node[semithick, right, outer sep=0, pos=0.55]{\textit{used for}} ([yshift=.2cm] I23.270);
+	\draw[thick, ->] (II1.0) to node[semithick, below, outer sep=0]{\textit{generalizes to}} (II2.180);
 	\draw let \p{top}=(I1.90), \p{left}=(I21.180), \p{bottom}=([shift={(0,-.15)}]I22.270), \p{right}=(I23.0) in (\x{left}, \y{top}) -- (\x{left}, \y{bottom}) -- (\x{right}, \y{bottom}) -- (\x{right}, \y{top}) -- (\x{left}, \y{top});
@@
 
-We still consider an essential complete simplicial fan~$\Fan$ in~$\R^n$, the $N \times n$-matrix~$\b{G}$ whose rows are the rays of~$\Fan$, and an $(N-n) \times N$-matrix~$\b{K}$ which spans the left kernel of~$\b{G}$ (\ie $\b{K}\b{G} = 0$).
+We still consider an essential complete simplicial fan~$\Fan$ in~$\R^n$, the $N \times n$-matrix~$\b{G}$ whose rows are the rays of~$\Fan$, and an $(N-n) \times N$-matrix~$\b{K}$ that spans the left kernel of~$\b{G}$ (\ie $\b{K}\b{G} = 0$).
 
@@
 
-\arnau{Vincent, can you please check the coordinates? C.\ Stump thought that two facets had some typo (a $\pm 1$ was in the wrong column)}
+% \arnau{Can you please check the coordinates? C.\ Stump thought that two facets had some typo (a $\pm 1$ was in the wrong column)}
 
@@
 \dim_{\field}\field_B & \textrm{if~$A\cong B$.}
-\end{cases}
+\end{cases}6
 \]

### 2020-04-15 thirdPaper/draft/typeConeAssociahedra.tex
minor changes type cones

@@
 \newcommand{\typeCone}{\mathbb{TC}} % type cone
-\newcommand{\ctypeCone}{\overline{\mathbb{TC}}} % type cone
+\newcommand{\ctypeCone}{\smash{\overline{\mathbb{TC}}}} % type cone
 \newcommand{\compatibilityDegree}[2]{(#1\,\|\,#2)} % compatibility degree
@@
 
-Moreover, we use a similar approach to study the space of polytopal realizations of the $\b{g}$-vector fans of another generalization of the associahedron: non-kissing complexes (a.k.a.
+Moreover, we use a similar approach to study the space of polytopal realizations of the \mbox{$\b{g}$-vector} fans of another generalization of the associahedron: non-kissing complexes (a.k.a.
 support $\tau$-tilting complexes) of gentle algebras.
@@
 Besides revisiting the construction of~\cite{ArkaniHamedBaiHeYan, BazierMatteDouvilleMousavandThomasYildirim} and extending it to any initial seed (acyclic or not) in any finite type cluster algebra (simply-laced or not), our type cone approach is also successful when applied to the $\b{g}$-vector fans of other families of generalizations of the associahedron.
-In the present paper, we explore specifically \textbf{Gentle associahedra}.
+In the present paper, we explore specifically \textbf{gentle associahedra}.
 These complexes where constructed in~\cite{PaluPilaudPlamondon-nonkissing} as polytopal realizations of finite non-kissing complexes of gentle bound quivers.
@@
 This is clearly the case when the type cone is simplicial as illustrated by the results of this paper: we naturally obtained all polytopal realizations of the $\b{g}$-vector fans of cluster algebras from cyclic seeds and of gentle algebras whose polytopality was only established very recently~\cite{HohlwegPilaudStella, PaluPilaudPlamondon-nonkissing}.
-% Even when the type cone is not simplicial, describing the type cone sometimes leads to relevant explicit realizations of the fan, as we illustrate on graph associahedra (see \cref{exm:constructionsGA}).
 We believe that this approach gives reasonable hope that the polytopality of further fans could in the future be established using our type cone approach.
@@
 \begin{coro:simplicialTypeCone}
-\label{coro:simplicialTypeCone}
 Assume that the type cone~$\typeCone(\Fan)$ is simplicial and let~$\b{K}$ be the $(N-n) \times N$-matrix whose rows are the inner normal vectors of the facets of~$\typeCone(\Fan)$. Then the polytope
@@
 
+\newpage
 \para{Schematic diagram of logical dependencies}
@@
 	\node[rectangle, draw=green, fill=green!10, align=center, text width=5.3cm, minimum width = 5cm, minimum height=1.2cm] (I23) at (6,-1.5) {\ref{part:geometry}.\ref{subsec:typeConeNKC} -- Gentle algebras \\ \& generalized accordiohedra};
-% 	\node[rectangle, draw=red, fill=red!10, align=center, text width=5.4cm] (I24) at (7,0) {\ref{part:geometry}.\ref{subsec:typeConeGA} -- Graphical nested complexes \\ \& graph associahedra};
-	\node[ellipse,
-% 	rectangle,rounded corners=10, 
-	draw=orange, fill=orange!10, align=center, text width=5cm, inner sep=2, minimum height=1cm] (II1) at (-4.5,-4.2) {\ref{part:algebra}.\ref{sec:clusterCategories} -- Cluster categories};
-	\node[ellipse,
-% 	rectangle,rounded corners=10,
-	draw=green, fill=green!10, align=center, text width=5cm, inner sep=0, minimum height=1cm] (II2) at (4.5,-4.2) {\ref{part:algebra}.\ref{sec:extricats} -- Extriangulated categories};
+	\node[ellipse, draw=orange, fill=orange!10, align=center, text width=5cm, inner sep=2, minimum height=1cm] (II1) at (-4.5,-4.2) {\ref{part:algebra}.\ref{sec:clusterCategories} -- Cluster categories};
+	\node[ellipse, draw=green, fill=green!10, align=center, text width=5cm, inner sep=0, minimum height=1cm] (II2) at (4.5,-4.2) {\ref{part:algebra}.\ref{sec:extricats} -- Extriangulated categories};
 	\draw[decorate, decoration={shape backgrounds, shape=dart, shape size=2mm, shape evenly spread=8}, draw=blue, fill=blue!10] (I1.180) to [bend right, looseness=1.1] node[label={[shift={(-1.6,-1.5)}]\textit{applied to}}]{} (I21.90);
@@
 	\draw[decorate, decoration={shape backgrounds, shape=dart, shape size=2mm, shape evenly spread=8}, draw=blue, fill=blue!10] (I1.360) to [bend left, looseness=1.1] node[label={[shift={(1.6,-1.5)}]\textit{applied to}}]{} (I23.90);
-% 	\draw[decorate, decoration={shape backgrounds, shape=dart, shape size=2mm, shape evenly spread=10}, draw=blue, fill=blue!10] (I1.0) to [bend left, looseness=1.1] (I24.90);
-% 	\draw[decorate, decoration={markings, mark=at position 0.5 with {\draw [red, ultra thick,-] ++ (-.3,-.3)  -- ( .3, .3); \draw [red, ultra thick,-] ++ (-.3, .3)  -- ( .3,-.3);}}] (I1.0) to [bend left, looseness=1.1] node[label={[shift={(-.4,-1.7)}]not applicable to}]{} (I24.90);
-% 	\draw[thick, double distance=2pt, -implies] (I22.270)+(0,-1.3) to node[semithick, right, outer sep=0, pos=0.65]{\textit{used for}} (I22.270)+(0,.15);
-% 	\draw[thick, double distance=2pt, -implies] (I23.270)+(0,-1.3) to node[semithick, right, outer sep=0, pos=0.65]{\textit{used for}} (I23.270)+(0,.15);
 	\draw[thick, double distance=2pt, -implies, in=270] (I22.270)+(-1.5,-1.2) to node[semithick, right, outer sep=0, pos=0.55]{\textit{used for}} ([yshift=.2cm] I22.270);
@@
 
-%\centerline{
-%\begin{tikzpicture}[every node/.style={inner sep=6, outer sep=8}]
-% 	\node[cloud, cloud puffs=25, cloud ignores aspect, text width=5cm, minimum height=1cm, align=center, draw=blue, fill=blue!10, inner sep=3, outer sep=5] (I1) at (0,1.5) {\ref{part:geometry}.\ref{sec:typeCone} -- Simplicial type cone strategy};
-%	\node[rectangle, draw=black, fill=black!10, align=center] (I21) at (-6,0) {\ref{part:geometry}.\ref{subsec:typeConeAsso} -- Toy example \\ Classical associahedra};
-%	\node[rectangle, draw=orange, fill=orange!10, align=center, text width=5cm] (I22) at (-3,-1.5) {\ref{part:geometry}.\ref{subsec:typeConeCA} -- Cluster algebras \\ \& generalized associahedra};
-%	\node[rectangle, draw=green, fill=green!10, align=center, text width=5cm] (I23) at (3,-1.5) {\ref{part:geometry}.\ref{subsec:typeConeNKC} -- Gentle algebras \\ \& generalized accordiohedra};
-%	\node[rectangle, draw=red, fill=red!10, align=center, text width=5.4cm] (I24) at (7,0) {\ref{part:geometry}.\ref{subsec:typeConeGA} -- Graphical nested complexes \\ \& graph associahedra};
-%	\node[ellipse, draw=orange, fill=orange!10, align=center, text width=4.9cm, inner sep=2, minimum height=1cm] (II1) at (-4.5,-4.2) {\ref{part:algebra}.\ref{sec:clusterCategories} -- Cluster categories};
-%	\node[ellipse, draw=green, fill=green!10, align=center, text width=4.9cm, inner sep=0, minimum height=1cm] (II2) at (4.5,-4.2) {\ref{part:algebra}.\ref{sec:extricats} -- Extriangulated categories};
-% 	\draw[decorate, decoration={shape backgrounds, shape=circle, shape size=2mm, shape evenly spread=8}, draw=blue, fill=blue!10] (I1.180) to [bend right, looseness=1.1] node[label={[shift={(.6,-1.5)}]applied to}]{} (I21.90);
-% 	\draw[decorate, decoration={shape backgrounds, shape=circle, shape size=2mm, shape evenly spread=8}, draw=blue, fill=blue!10] (I1.240) to [bend right, looseness=.6] node[label={[shift={(.6,-1.5)}]applied to}]{} (I22.90);
-% 	\draw[decorate, decoration={shape backgrounds, shape=circle, shape size=2mm, shape evenly spread=8}, draw=blue, fill=blue!10] (I1.300) to [bend left, looseness=.6] node[label={[shift={(-.6,-1.5)}]applied to}]{} (I23.90);
-% 	\draw[decorate, decoration={shape backgrounds, shape=circle, shape size=2mm, shape evenly spread=10}, draw=blue, fill=blue!10] (I1.0) to [bend left, looseness=1.1] (I24.90);
-% 	\draw[decorate, decoration={markings, mark=at position 0.5 with {\draw [red, ultra thick,-] ++ (-.3,-.3)  -- ( .3, .3); \draw [red, ultra thick,-] ++ (-.3, .3)  -- ( .3,-.3);}}] (I1.0) to [bend left, looseness=1.1] node[label={[shift={(-.4,-1.7)}]not applicable to}]{} (I24.90);
-%	\draw[thick, double distance=2pt, -implies] (I22.270)+(0,-1.3) to node[semithick, right, outer sep=0, pos=0.65]{used for} (I22.270)+(0,.15);
-%	\draw[thick, double distance=2pt, -implies] (I23.270)+(0,-1.3) to node[semithick, right, outer sep=0, pos=0.65]{used for} (I23.270)+(0,.15);
-%	\draw[thick, ->] (II1.0) to node[semithick, above, outer sep=0]{generalizes to} (II2.180);
-%	\draw let \p{top}=(I1.90), \p{left}=(I21.180), \p{bottom}=([shift={(0,-.15)}]I22.270), \p{right}=(I24.0) in (\x{left}, \y{top}) -- (\x{left}, \y{bottom}) -- (\x{right}, \y{bottom}) -- (\x{right}, \y{top}) -- (\x{left}, \y{top});
-%	\draw let \p{top}=([shift={(0,.2)}]II1.90), \p{left}=(I21.180), \p{bottom}=(II1.270), \p{right}=(I24.0) in (\x{left}, \y{top}) -- (\x{left}, \y{bottom}) -- (\x{right}, \y{bottom}) -- (\x{right}, \y{top}) -- (\x{left}, \y{top});
-%	\path let \p{top}=(I1.90) in node[rectangle, draw, fill=white, align=left, inner sep=4] (I) at (-6.15, \y{top}) {\ref{part:geometry} -- Discrete geometry};
-%	\path let \p{top}=([shift={(0,.2)}]II1.90) in node[rectangle, draw, fill=white, align=left, inner sep=4] (I) at (-5.8, \y{top}) {\ref{part:algebra} -- Representation theory};
-%\end{tikzpicture}
-%}
-%
-%\medskip
-%
-%\begin{center}
-%\includegraphics[scale=.9]{Schema}
-%\end{center}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-A hyperplane~$H \subset \R^d$ is a \defn{supporting hyperplane} of a set~$X \subset \R^d$ if~$H \cap X \ne \varnothing$ and~$X$ is contained in one of the two closed half-spaces of~$\R^d$ defined by~$H$.
-
-We denote by~$\R_{\ge0}\rays \eqdef \set{\sum_{\ray \in \rays} \lambda_{\ray} \, \ray}{\lambda_{\ray} \in \R_{\ge0}}$ the \defn{positive span} of a set~$\rays$ of vectors of~$\R^d$.
-A \defn{polyhedral cone} is a subset of~$\R^d$ defined equivalently as the positive span of finitely many vectors or as the intersection of finitely many closed linear halfspaces.
+A hyperplane~$H \subset \R^n$ is a \defn{supporting hyperplane} of a set~$X \subset \R^n$ if~$H \cap X \ne \varnothing$ and~$X$ is contained in one of the two closed half-spaces of~$\R^n$ defined by~$H$.
+
+We denote by~$\R_{\ge0}\rays \eqdef \set{\sum_{\ray \in \rays} \lambda_{\ray} \, \ray}{\lambda_{\ray} \in \R_{\ge0}}$ the \defn{positive span} of a set~$\rays$ of vectors of~$\R^n$.
+A \defn{polyhedral cone} is a subset of~$\R^n$ defined equivalently as the positive span of finitely many vectors or as the intersection of finitely many closed linear halfspaces.
 The \defn{faces} of a cone~$C$ are the intersections of~$C$ with the supporting hyperplanes of~$C$.
@@
 \end{itemize}
-A fan is \defn{simplicial} if all its cones are, \defn{complete} if the union of its cones covers the ambient space~$\R^d$, and \defn{essential} if it contains the cone~$\{\b{0}\}$.
+A fan is \defn{simplicial} if all its cones are, \defn{complete} if the union of its cones covers the ambient space~$\R^n$, and \defn{essential} if it contains the cone~$\{\b{0}\}$.
 Note that every complete fan is the product of an essential fan with its lineality space.
-For two fans~$\Fan, \cal{G}$ in~$\R^d$, we say that~$\Fan$ \defn{refines}~$\cal{G}$ (and that~$\cal{G}$ \defn{coarsens}~$\Fan$) if every cone of~$\Fan$ is contained in a cone of~$\cal{G}$.
-
-A \defn{polytope} is a subset~$P$ of~$\R^d$ defined equivalently as the convex hull of finitely many points or as a bounded intersection of finitely many closed affine halfspaces.
+For two fans~$\Fan, \cal{G}$ in~$\R^n$, we say that~$\Fan$ \defn{refines}~$\cal{G}$ (and that~$\cal{G}$ \defn{coarsens}~$\Fan$) if every cone of~$\Fan$ is contained in a cone of~$\cal{G}$.
+
+A \defn{polytope} is a subset~$P$ of~$\R^n$ defined equivalently as the convex hull of finitely many points or as a bounded intersection of finitely many closed affine halfspaces.
 The \defn{dimension}~$\dim(P)$ is the dimension of the affine hull of~$P$.
@@
 The (outer) \defn{normal fan} of~$P$ is the collection of the (outer) normal cones of all its faces.
-We say that a complete polyhedral fan~$\Fan$ in~$\R^d$ is \defn{polytopal} when it is the normal fan of a polytope~$P$ of~$\R^d$, and that~$P$ is a \defn{polytopal realization} of~$\Fan$.
+We say that a complete polyhedral fan~$\Fan$ in~$\R^n$ is \defn{polytopal} when it is the normal fan of a polytope~$P$ of~$\R^n$, and that~$P$ is a \defn{polytopal realization} of~$\Fan$.
 
@@
 Note that~$\b{K}$ is only defined up to linear transformation, as it depends on the choice of a basis of the left kernel of~$\b{G}$.
-Note also that, by construction, the coefficients of the normal vectors of the facets of~$\typeCone(\Fan)$ arise from a linear dependence among the $\b{g}$-vectors, and hence belong to this kernel.
+Note also that, by construction, the coefficients of the normal vectors of the facets of~$\typeCone(\Fan)$ arise from a linear dependence among the rays of~$\Fan$, and hence belong to this kernel.
 When~$\typeCone(\Fan)$ is simplicial, its $(N-n)$ facets are necessarily linearly independent, and hence form a basis.
@@
 	\capstart
-	\centerline{\includegraphics[scale=.8]{typeConeCoarsenings}}
+	\centerline{\includegraphics[scale=.7]{typeConeCoarsenings}}
 	\caption{The type cone~$\ctypeCone(\Fan)$ of the fan~$\Fan$ of \cref{fig:typeCone}\,(left).
@@
 
+\enlargethispage{.5cm}
 We now discuss the connection between convex combinations in the type cone and Minkowski sums of polytopes.
@@
 \end{corollary}
+
 \begin{proof}
-It suffices to express the projection of $\b{h}$ onto the left kernel of~$\b{G}$ in terms of $\b{h}^{(1)}, \dots, \b{h}^{(N-n)}$, and to separate those terms with positive and negative coefficients to express Minkowski sums and differences.
+It suffises to express the projection of $\b{h}$ onto the left kernel of~$\b{G}$ in terms of $\b{h}^{(1)}, \dots, \b{h}^{(N-n)}$ to obtain the coefficients of~$P_\b{h}$ as a signed Minkowski sum of dilates of $P_{\b{h}^{(1)}}, \dots, P_{\b{h}^{(N-n)}}$.
 \end{proof}
@@
 \label{exm:typeConeMinkowskiSum}
+\enlargethispage{.5cm}
 Consider the $2$-dimensional fan~$\Fan$ of \cref{fig:typeCone}\,(left) whose type cone has been described in \cref{exm:typeCone} and represented in \cref{fig:typeCone}\,(right).
@@
 It has $6$ facet-defining inequalities (given below), which correspond to the mesh mutations of \cref{thm:extremalExchangeablePairsCA} as illustrated in \cref{fig:labelFacetDefiningInequalititiesCA1}.
-
-% \arnau{Can you please check the coordinates? C.\ Stump thought that two facets had some typo (a $\pm 1$ was in the wrong column)}
 
@@
 					& 0 & -1 & 0 & 1 & 0 & 0 & 0 & 1 & 0 & 0 & -1 & 0 & \red \circled{D} \\
-					& 0 & 0 & 0 & 0 & 0 & 1 & -2 & 0 & 0 & 1 & 0 & 0 & \red \circled{E} \\
+					& 0 & 0 & 0 & 0 & 0 & 1 & 0 & -2 & 0 & 0 & 1 & 0 & \red \circled{E} \\
 					& 0 & 1 & 0 & 0 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 1 & \red \circled{F} \\
 					& 0 & 0 & 0 & 0 & 0 & -1 & 1 & 1 & 0 & 0 & 0 & -1 & \red \circled{G} \\
-					& 0 & 0 & 0 & 0 & 0 & 1 & 0 & -2 & 0 & 0 & 1 & 0 & \red \circled{H} \\
+					& 0 & 0 & 0 & 0 & 0 & 1 & -2 & 0 & 0 & 1 & 0 & 0 & \red \circled{H} \\
 					& -1 & 0 & 0 & 0 & 1 & 0 & 1 & 0 & 0 & -1 & 0 & 0 & \red \circled{I} \\[.2cm]
@@
 \dim_{\field}\field_B & \textrm{if~$A\cong B$.}
-\end{cases}6
+\end{cases}
 \]
@@
 We thank H.~Thomas for comments on a preliminary version of the paper and for informing us about the upcoming extended version of~\cite{BazierMatteDouvilleMousavandThomasYildirim}.
+We are grateful to C.~Stump for reporting a typo in \cref{exm:typeConeCA}.
 

### 2020-04-15 thirdPaper/draft/typeConeAssociahedra.tex
win one page...

@@
 
-\vspace{1.5cm}
-\centerline{\includegraphics[scale=.8]{typeConeCoarsenings}}
-\vspace{.5cm}
-\centerline{The type cone of the cluster fan of type~$A_2$.}
-
-\newpage
+%\vspace{1.5cm}
+%\centerline{\includegraphics[scale=.8]{typeConeCoarsenings}}
+%\vspace{.5cm}
+%\centerline{The type cone of the cluster fan of type~$A_2$.}
+%
+%\newpage
+\enlargethispage{.3cm}
 \tableofcontents
+\vspace{-.5cm}
 
@@
 
-\newpage
+%\newpage
 \section*{Introduction}
@@
 \medskip
+\enlargethispage{.4cm}
 Besides revisiting the construction of~\cite{ArkaniHamedBaiHeYan, BazierMatteDouvilleMousavandThomasYildirim} and extending it to any initial seed (acyclic or not) in any finite type cluster algebra (simply-laced or not), our type cone approach is also successful when applied to the $\b{g}$-vector fans of other families of generalizations of the associahedron.
@@
 \medskip
+\enlargethispage{.2cm}
 To conclude, it is our hope that the present paper will participate to the interactions between combinatorial geometry, representation theory, and mathematical physics; in particular through further developments of the geometric approach to scattering amplitudes that has flourished during the last years~\cite{ArkaniHamedTrnka-Amplituhedron,ArkaniHamedBourjailyCachazoGoncharovPostnikovTrnka-GrassmannianGeometryScatteringAmplitudes}.
@@
 
-\newpage
+%\newpage
 \para{Schematic diagram of logical dependencies}

### 2020-04-27 thirdPaper/draft/typeConeAssociahedra.tex
win one more page...
bold letters third paper

@@
 \newcommand{\D}{\mathrm{D}} % symmetrizer
-\newcommand{\simpleRoot}{\alpha} % simple root
-\newcommand{\fundamentalWeight}{\omega} % fundamental weights
+\newcommand{\simpleRoot}{\b{\alpha}} % simple root
+\newcommand{\fundamentalWeight}{\b{\omega}} % fundamental weights
 \newcommandx{\meshes}[1][1=\B_\circ]{\mathcal{M}(#1)} % meshes
@@
 \[
-\alpha \, h_{\ray} + \alpha' \, h_{\ray'} + \sum_{\ray[s] \in \rays \cap \rays'} \beta_{\ray[s]} \, h_{\ray[s]} > 0,
+\alpha \, \b{h}_{\ray} + \alpha' \, \b{h}_{\ray'} + \sum_{\ray[s] \in \rays \cap \rays'} \beta_{\ray[s]} \, \b{h}_{\ray[s]} > 0,
 \]
@@
 There are two natural ways this construction generalizes to arbitrary pairs of polyhedra.
-On the one hand, one can consider that ${P - Q = \set{x \in \R^n}{x + Q \subseteq P}}$.
+On the one hand, one can consider that ${P - Q = \set{\b{x} \in \R^n}{\b{x} + Q \subseteq P}}$.
 On the other hand, considering arbitrary differences of support functions gives rise to \defn{virtual polyhedra}, which is the Grothendieck group of the semigroup of polytopes with Minkowski sums~\cite{PukhlikovKhovanskii}.
@@
 \item the convex hull of the points~$L(T) \in \R^{n+1}$ for all rooted binary trees~$T$ with~$n+1$ internal nodes, where the $i$th coordinate of~$L(T)$ is the product of the number of leaves in the left subtree by the number of leaves in the right subtree of the $i$th node of~$T$ in inorder~\cite{Loday},
-\item the intersection of the hyperplane~$\bigset{\b{x} \in \R^{n+1}}{\sum_{\ell \in [n+1]} x_\ell = \binom{n+2}{2}}$ with the halfspaces $\bigset{\b{x} \in \R^{n+1}}{\sum_{a < \ell < b} x_\ell \ge \binom{b-a}{2}}$ for all internal diagonals~$(a,b)$ of \mbox{the $(n+3)$-gon~\cite{ShniderSternberg}},
+\item the intersection of the hyperplane~$\bigset{\b{x} \in \R^{n+1}}{\sum_{\ell \in [n+1]} \b{x}_\ell = \binom{n+2}{2}}$ with the halfspaces $\bigset{\b{x} \in \R^{n+1}}{\sum_{a < \ell < b} \b{x}_\ell \ge \binom{b-a}{2}}$ for all internal diagonals~$(a,b)$ of \mbox{the $(n+3)$-gon~\cite{ShniderSternberg}},
 \item the Minkowski sum of the faces~$\simplex_{[i,j]}$ of the standard $n$-dimensional simplex~$\simplex_{[n+1]}$ corresponding to all proper intervals~$[i,j]$ of~$[n+1]$,~\cite{Postnikov}.
@@
 Since~$\Asso[n]$ lives in a hyperplane of~$\R^{n+1}$, so does its normal fan.
-Let~$\HH \eqdef \bigset{\b{x} \in \R^{n+1}}{\sum_{\ell \in [n+1]} x_\ell = 0}$ and~$\pi : \R^{n+1} \to \HH$ denote the orthogonal projection.
+Let~$\HH \eqdef \bigset{\b{x} \in \R^{n+1}}{\sum_{\ell \in [n+1]} \b{x}_\ell = 0}$ and~$\pi : \R^{n+1} \to \HH$ denote the orthogonal projection.
 The following fans are illustrated in \cref{fig:lodayFans} in dimension~$2$ and~$3$.
@@
 \item the normal vector of the facet corresponding to an internal diagonal~$(a,b)$ of the $(n+3)$-gon is the vector~$\gvector{a,b} \eqdef \pi\big( \sum_{a < \ell < b} \b{e}_\ell \big) = (n+1) \sum_{a < \ell < b} \b{e}_\ell - (b-a-1) \sum_{1 \le \ell \le n+1} \b{e}_\ell$.
-\item the normal cone of the vertex corresponding to a rooted binary tree~$T$ is the incidence cone~$\bigset{\b{x} \in \HH}{x_i \le x_j \text{ for all edges $i \to j$ in $T$}}$.
+\item the normal cone of the vertex corresponding to a rooted binary tree~$T$ is the incidence cone~$\bigset{\b{x} \in \HH}{\b{x}_i \le \b{x}_j \text{ for all edges $i \to j$ in $T$}}$.
 \end{itemize}
@@
 For simplicity, we drop the mention of the coefficients for principal cluster algebras in the notations for seeds~$\seed = (\B, \cluster)$, for cluster algebras~$\principalClusterAlgebra$ and for variables~$\principalVariables$.
-Principal coefficients cluster algebras are $\Z^n$-graded (in the fundamental weight basis~$\{\omega_x\}_{x \in \cluster_\circ}$ of~$V$) for the degree function~$\deg(\B_\circ,\cdot)$ on $\principalClusterAlgebra$ obtained by setting
+Principal coefficients cluster algebras are $\Z^n$-graded (in the fundamental weight basis~$\{\simpleWeight_x\}_{x \in \cluster_\circ}$ of~$V$) for the degree function~$\deg(\B_\circ,\cdot)$ on $\principalClusterAlgebra$ obtained by setting
 \(
@@
 
-\newpage
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%\newpage
 \part{Grothendieck group and relations between $\b{g}$-vectors}
@@
 
-\newpage
+%\newpage
 \bibliographystyle{alpha}

### 2020-05-05 thirdPaper/draft/typeConeAssociahedra.tex
footnote graph associahedra

@@
 
-\smallskip
+\medskip
+\enlargethispage{.5cm}
 Further families of generalizations of the associahedron certainly deserve to be studied with our type cone approach.
-We are investigating in particular graph associahedra~\cite{CarrDevadoss, Postnikov, FeichtnerSturmfels, Zelevinsky}, brick polytopes~\cite{PilaudSantos-brickPolytope, PilaudStump-brickPolytope} and quotientopes~\cite{Reading-latticeCongruences, Reading-CambrianLattices, PilaudSantos-quotientopes}.
+We are investigating in particular graph associahedra~\cite{CarrDevadoss, Postnikov, FeichtnerSturmfels, Zelevinsky}, brick polytopes~\cite{PilaudSantos-brickPolytope, PilaudStump-brickPolytope}\footnote{A preliminary version of this paper contained the full facet description of the type cones of graph associahedra.
+As they are not simplicial, they lie slightly beyond the scope of this paper, and will be studied elsewhere.} and quotientopes~\cite{Reading-latticeCongruences, Reading-CambrianLattices, PilaudSantos-quotientopes}.
 In fact, as already mentioned, it seems sometimes easier to find all polytopal realizations of a fan (by describing its type cone in terms of certain specific pairs of adjacent maximal cones) than to identify one specific explicit realization.
@@
 For simplicity, we drop the mention of the coefficients for principal cluster algebras in the notations for seeds~$\seed = (\B, \cluster)$, for cluster algebras~$\principalClusterAlgebra$ and for variables~$\principalVariables$.
-Principal coefficients cluster algebras are $\Z^n$-graded (in the fundamental weight basis~$\{\simpleWeight_x\}_{x \in \cluster_\circ}$ of~$V$) for the degree function~$\deg(\B_\circ,\cdot)$ on $\principalClusterAlgebra$ obtained by setting
+Principal coefficients cluster algebras are $\Z^n$-graded (in the fundamental weight basis~$\{\fundamentalWeight_x\}_{x \in \cluster_\circ}$ of~$V$) for the degree function~$\deg(\B_\circ,\cdot)$ on $\principalClusterAlgebra$ obtained by setting
 \(

### 2020-05-06 thirdPaper/draft/typeConeAssociahedra.tex
replace footnote

@@
 Further families of generalizations of the associahedron certainly deserve to be studied with our type cone approach.
-We are investigating in particular graph associahedra~\cite{CarrDevadoss, Postnikov, FeichtnerSturmfels, Zelevinsky}, brick polytopes~\cite{PilaudSantos-brickPolytope, PilaudStump-brickPolytope}\footnote{A preliminary version of this paper contained the full facet description of the type cones of graph associahedra.
-As they are not simplicial, they lie slightly beyond the scope of this paper, and will be studied elsewhere.} and quotientopes~\cite{Reading-latticeCongruences, Reading-CambrianLattices, PilaudSantos-quotientopes}.
+We are investigating in particular graph associahedra\footnote{A preliminary version of this paper contained the full facet description of the type cones of graph associahedra.
+As they are not simplicial, they lie slightly beyond the scope of this paper, and will be studied elsewhere.}~\cite{CarrDevadoss, Postnikov, FeichtnerSturmfels, Zelevinsky}, brick polytopes~\cite{PilaudSantos-brickPolytope, PilaudStump-brickPolytope} and quotientopes~\cite{Reading-latticeCongruences, Reading-CambrianLattices, PilaudSantos-quotientopes}.
 In fact, as already mentioned, it seems sometimes easier to find all polytopal realizations of a fan (by describing its type cone in terms of certain specific pairs of adjacent maximal cones) than to identify one specific explicit realization.

### 2020-06-29 firstPaper/FPSAC/nonKissingComplexFPSAC.tex
FPSAC

%% if you are submitting an initial manuscript then you should have submission as an option here
%% if you are submitting a revised manuscript then you should have revision as an option here
%% otherwise options taken by the article class will be accepted
\documentclass[finalversion]{FPSAC2018}
\articlenumber{39}
%% but DO NOT pass any options (or change anything else anywhere) which alters page size / layout / font size etc

%% note that the class file already loads {amsmath, amsthm, amssymb}

\usepackage{enumerate}
\usepackage{paralist}
\usepackage{pifont}
\usepackage{xargs}
\usepackage{overpic}
\usepackage{blkarray}
\usepackage{mathtools}

% theorems
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem*{theorem*}{Theorem}%[section]

% math commands
\definecolor{darkblue}{rgb}{0,0,0.7} % darkblue color
\definecolor{green}{RGB}{57,181,74} % green color
\definecolor{violet}{RGB}{147,39,143} % violet color
\newcommand{\darkblue}{\color{darkblue}} % darkblue command
\newcommand{\defn}[1]{\textsl{\darkblue #1}} % emphasis of a definition
\newcommand{\set}[2]{\left\{ #1 \;\middle|\; #2 \right\}} % set notation
\newcommand{\bigset}[2]{\big\{ #1 \;\big|\; #2 \big\}} % big set notation
\newcommand{\dotprod}[2]{\left\langle \, #1 \; \middle| \; #2 \, \right\rangle} % dot product
\newcommand{\eqdef}{\mbox{\,\raisebox{0.2ex}{\scriptsize\ensuremath{\mathrm:}}\ensuremath{=}\,}} % :=
\newcommand{\ssm}{\smallsetminus} % small set minus
\renewcommand{\b}[1]{\mathbf{#1}} % bold letters
\newcommand{\symdif}{\,\triangle\,} % symmetric difference

% special
\newcommand{\R}{\mathbb{R}} % reals
\newcommand{\N}{\mathbb{N}} % naturals
\newcommand{\Z}{\mathbb{Z}} % integers
\newcommand{\C}{\mathbb{C}} % complex
\newcommand{\fS}{\mathfrak{S}} % symmetric group

% quiver
\newcommand{\blossom}{^\text{\ding{96}}} % blossom
\newcommand{\indeg}{\mathrm{indeg}} % in-degree
\newcommand{\outdeg}{\mathrm{outdeg}} % out-degree
\newcommand{\peak}{\mathrm{peak}} % bottom dissection
\newcommand{\deep}{\mathrm{deep}} % top dissection
\newcommand{\strings}{\mathcal{S}} % strings
\newcommand{\distinguishedWalk}[2]{\mathsf{dw}(#1,#2)} % distinguished walk
\newcommand{\distinguishedArrows}[2]{\mathsf{da}(#1,#2)} % distinguished arrows
\newcommand{\distinguishedString}[2]{\mathsf{ds}(#1,#2)} % distinguished string
\newcommand{\distinguishedSign}[2]{\varepsilon(#1,#2)} % distinguished sign
\newcommand{\peaks}[1]{\mathsf{peaks}(#1)} % peaks
\newcommand{\deeps}[1]{\mathsf{deeps}(#1)} % deeps

% non-kissing complex
\newcommandx{\NKC}[1][1=\bar Q]{\mathcal{K}_{\mathrm{nk}}(#1)} % non-kissing complex
\newcommandx{\RNKC}[1][1=\bar Q]{\mathcal{C}_{\mathrm{nk}}(#1)} % non-kissing complex
\newcommandx{\NKL}[1][1=\bar Q]{\mathcal{L}_{\mathrm{nk}}(#1)} % non-kissing lattice
\newcommand{\kn}{\kappa} % kissing number
\newcommand{\KN}{\textsc{kn}} % Kissing Number
\renewcommand{\top}{\mathrm{top}} % top
\newcommand{\bottom}{\mathrm{bot}} % bottom

% lattice
\newcommand{\meet}{\wedge} % meet
\newcommand{\join}{\vee} % join
\newcommand{\bigMeet}{\bigwedge} % meet
\newcommand{\bigJoin}{\bigvee} % join
\newcommand{\cS}{\mathcal{S}} % ground set
\newcommand{\closure}[1]{#1^{\mathrm{cl}}} % closure operator
\newcommand{\coclosure}[1]{#1^{\mathrm{cocl}}} % coclosure operator
\newcommand{\Bicl}[1]{\mathsf{Bic}(#1)} % biclosed sets
\newcommand{\projDown}{\pi_\downarrow} % down projection map
\newcommand{\projUp}{\pi^\uparrow} % up projection map
\newcommand{\JI}{\mathsf{JI}} % join-irreducible
\newcommand{\ji}{\mathsf{ji}} % join irreducible
\newcommand{\mi}{\mathsf{mi}} % meet irreducible
\DeclareMathOperator{\descents}{des} % descents

% geometry
\newcommand{\multiplicityVector}{\b{m}} % multiplicity vector
% g-vectors
\newcommand{\gvector}[1]{\mathbf{g}(#1)} % g-vector of the path #1
\newcommand{\gvectors}[1]{\mathbf{g}(#1)} % g-vectors of the paths #1
\newcommandx{\gvectorFan}[1][1=\bar Q]{\mathcal{F}^\mathbf{g}(#1)} % g-vector fan
% c-vectors
\newcommand{\cvector}[2]{\mathbf{c}(#1 \in #2)} % c-vector of the path #1 in the facet #2
\newcommand{\cvectors}[1]{\mathbf{c}(#1)} % c-vectors of the paths #1
\newcommandx{\allcvectors}[1][1=\bar Q]{\mathbf{C}(#1)} % all c-vectors with respect to the initial cluster #1
\newcommandx{\cvectorFan}[1][1=\bar Q]{\mathcal{F}^\mathbf{c}(#1)} % fan of hyperplanes orthogonal to all c-vectors
% points, hyperplanes, half-spaces
\newcommand{\point}[1]{\mathbf{p}(#1)} % vertex of the grid 
\newcommand{\HS}[1]{\mathbf{H}^{\le}(#1)} % half space
\newcommandx{\Asso}[2][1=\bar Q,2={}]{\mathsf{Asso}^{#2}(#1)} % associahedron

% others
\newcommand{\ie}{\textit{i.e.}~} % id est
\newcommand{\eg}{\textit{e.g.}~} % exempli gratia
\graphicspath{{figures/}}

%% define your title in the usual way
\title{Non-kissing complexes for gentle algebras}

%% define your authors in the usual way
%% use \addressmark{1}, \addressmark{2} etc for the institutions, and use \thanks{} for contact details
\author{
	Yann Palu\thanks{\href{mailto:yann.palu@u-picardie.fr}{yann.palu@u-picardie.fr}. Supported by the French ANR grant SC3A~(15\,CE40\,0004\,01).}\addressmark{1},
	\stepcounter{footnote}
	Vincent Pilaud\thanks{\href{mailto:}{vincent.pilaud@lix.polytechnique.fr}. Supported by the French ANR grant SC3A~(15\,CE40\,0004\,01).}\addressmark{2}, \and
	Pierre-Guy Plamondon\addressmark{3}\thanks{\href{mailto:}{pierre-guy.plamondon@math.u-psud.fr}. Supported by French the ANR grant SC3A~(15\,CE40\,0004\,01).}
}

%% then use \addressmark to match authors to institutions here
\address{
\addressmark{1}LAMFA, Universit\'e Picardie Jules Verne, Amiens \\ \addressmark{2}CNRS \& LIX, \'Ecole Polytechnique, Palaiseau \\
\addressmark{3}Laboratoire de Math\'ematiques d'Orsay, Universit\'e Paris-Sud, CNRS, Universit\'e Paris-Saclay
}

%% put the date of submission here
\received{\today}

%% leave this blank until submitting a revised version
%\revised{}

%% put your English abstract here, or comment this out if you don't have one yet
%% please don't use custom commands in your abstract / resume, as these will be displayed online
%% likewise for citations -- please don't use \cite, and instead write out your citation as something like (author year)
\abstract{
We introduce the non-kissing complex of any gentle bound quiver.
This complex provides a powerful combinatorial model for support $\tau$-tilting theory over gentle algebras, and it generalizes and unifies the previously considered situations of quivers defined from subsets of the grid or from dissections of a polygon (both generalizing the classical associahedron).
In this extended abstract, we report on lattice theoretic and geometric properties of finite non-kissing complexes: we show that their flip graphs are Hasse diagrams of congruence-uniform lattices, and that they can be realized by convex polytopes.
}

%% put your French abstract here, or comment this out if you don't have one
\resume{
Nous introduisons le complexe platonique d'un carquois aimable.
Ce complexe offre un modèle combinatoire pour la théorie du $\tau$-basculement à support des algèbres aimables et il généralise et unifie les cas particuliers définis à partir de sous-ensembles de la grille ou de dissections de polygones (contenant notamment le cas de l'associaèdre classique).
Dans ce résumé étendu, nous présentons des propriétés combinatoires et géométriques des complexes platoniques finis : nous montrons que leurs graphes de flips sont les diagrammes de Hasse de treillis congruence-uniformes, et qu'ils peuvent être réalisés par des polytopes convexes.
}

%% put your keywords here, or comment this out if you don't have them yet
%\keywords{Associahedron, non-kissing complex}

%% you can include your bibliography however you want, but using an external .bib file is STRONGLY RECOMMENDED and will make the editor's life much easier
%% regardless of how you do it, please use numerical citations, ie. [xx, yy] in the text

%% this sample uses biblatex, which (among other things) takes care of URLs in a more flexible way than bibtex
%% but you can use bibtex if you want
\usepackage[backend=bibtex]{biblatex}
\addbibresource{nonKissingComplexFPSAC.bib}
%% note the \printbibliography command at the end of the file which goes with these biblatex commands

\begin{document}

\maketitle
%% note that you DO NOT have to put your abstract here -- it is generated by \maketitle and the \abstract and \resume commands above

\section{Motivation: Non-kissing versus support $\tau$-tilting}
\label{sec:motivation}

The non-kissing complex is a simplicial complex of pairwise non-kissing paths in a fixed shape of a grid.
It was introduced by T.~K.~Petersen, P.~Pylyavskyy and D.~Speyer in~\cite{PetersenPylyavskyySpeyer} for a staircase shape, studied by F.~Santos, C.~Stump and V.~Welker~\cite{SantosStumpWelker} for rectangular shapes, and extended by T.~McConville in~\cite{McConville} for arbitrary shapes.
This complex is known to be a simplicial sphere, and it was actually realized as a polytope using successive edge stellations and suspensions in~\cite[Section~4]{McConville}.
Moreover, the dual graph of the non-kissing complex has a natural orientation which equips its facets with a lattice structure~\cite[Theorem 1.1, Section~5--8]{McConville}.
Further lattice theoretic and geometric aspects of this complex were recently developed by A.~Garver and T.~McConville in~\cite{GarverMcConville-grid}.

The interest for non-kissing complexes is motivated by relevant instances arising from particular shapes.
As already observed in~\cite[Section~10]{McConville}, when the shape is a ribbon, the non-kissing complex is an associahedron, and the non-kissing lattice is a type~$A$ Cambrian lattice of N.~Reading~\cite{Reading-CambrianLattices}.
In particular, the straight ribbon corresponds to the Tamari lattice, an object at the heart of a deep research area~\cite{TamariFestschrift}.
When the shape is a rectangle (or even a staircase), the non-kissing complex was studied in~\cite{PetersenPylyavskyySpeyer, SantosStumpWelker} as the Grassmann associahedron, in connection to non-crossing subsets of~$[n]$.

Other instances of such complexes arise naturally from the representation theory of associative algebras.  
The notion of support $\tau$-tilting module over an algebra was introduced by T.~Adachi, O.~Iyama and I.~Reiten in \cite{AdachiIyamaReiten}, and has proved to be a successful generalization of tilting and cluster-tilting theory.  
Over a given algebra, indecomposable $\tau$-rigid modules form a complex. 
For an account of the various algebraic interpretations of this complex, we refer the reader to \cite{BrustleYang}.  
For example, in the case of the path algebra of a straight line quiver, the support $\tau$-tilting complex is, again, an associahedron.

Our original motivation was to provide common interpretations to these different complexes. First, we realized any non-kissing complex as the support $\tau$-tilting complex of a well-chosen associative algebra.
The algebras that occur are certain gentle algebras, a special case of the well-studied string algebras of M.~C.~R.~Butler and C.~Ringel~\cite{ButlerRingel}.
Conversely, starting from any gentle bound quiver~$\bar Q$, we defined its blossoming quiver~$\bar Q\blossom$ and a non-kissing relation on the walks in~$\bar Q\blossom$ so that the following interpretation holds.

\begin{theorem}
\label{thm:motivation}
For any gentle bound quiver~$\bar Q = (Q,I)$, the non-kissing complex of walks in the blossoming quiver~$\bar Q \blossom$ is isomorphic to the support $\tau$-tilting complex of the gentle algebra~$kQ/I$.
\end{theorem}

In short, to any walk in $\bar Q \blossom$ corresponds a representation of $\bar Q$, and this correspondence takes non-kissing walks to $\tau$-compatible representations.
This theorem provides a dictionary between the combinatorially-flavored non-kissing complex and the algebraically-flavoured support $\tau$-tilting complex, thus opening a bridge to go back and forth between the two worlds.
It allows us, for instance, to combinatorially define mutation of support $\tau$-tilting modules.
This seems worthwhile, as the mutation of support $\tau$-tilting modules over an arbitrary algebra is generally difficult to carry out~explicitly.
%A similar result was obtained in~\cite{BrustleDouvilleMousavandThomasYildirim}.

The precise statement and the proof of Theorem~\ref{thm:motivation} can be found in the long version of this paper~\cite{PaluPilaudPlamondon}, as well as further representation-theoretic aspects of the project.
In this extended abstract, we focus on combinatorial and geometric aspects.
We first define in Section~\ref{sec:nonkissingcomplex} the non-kissing complex of a gentle bound quiver and show that this complex is a pseudomanifold (meaning in particular that there is a well-defined notion of flips in non-kissing facets).
In Section~\ref{sec:nonkissinglattice}, we show that the graph of increasing flips is the Hasse diagram of a congruence-uniform lattice and describe its canonical join complex.
Finally, Section~\ref{sec:gentleAssociahedra} is devoted to the geometry of finite non-kissing complexes: we construct their $\b{g}$-vector fans and show that these fans are normal fans of convex polytopes.
We refer to~\cite{PaluPilaudPlamondon} for detailed proofs and further properties of non-kissing complexes.

\newpage
\section{Non-kissing complexes of gentle bound quivers}
\label{sec:nonkissingcomplex}

\subsection{Blossoming quivers and non-kissing walks}

We fix a \defn{gentle bound quiver}~$\bar Q \eqdef (Q,I)$, where~$Q \eqdef (Q_0, Q_1, s, t)$ is a \defn{quiver} with vertices~$Q_0$, arrows~$Q_1$, and source and target maps~$s, t : Q_1 \to Q_0$, and~$I$ is a set of quadratic \defn{relations}~$\alpha\beta = 0$ with~$\alpha, \beta \in Q_1$ and~$t(\alpha) = s(\beta)$ such that for any~$\beta \in Q_1$ there is at most one~$\alpha \in Q_1$ such that~$t(\alpha) = s(\beta)$ and~$\alpha\beta \in I$ (resp.~$\alpha\beta \notin I$) and at most one~$\gamma \in Q_1$ such that~$t(\beta) = s(\gamma)$ and~$\beta\gamma \in I$~(resp.~${\beta\gamma \notin I}$).
See Figure~\ref{fig:exmQuiver}.
In all pictures, a relation~$\alpha\beta = 0$ is indicated with an arc connecting the target of~$\alpha$ to the source of~$\beta$.

A \defn{string} in~$\bar Q$ is a word of the form
\(
\rho = \alpha_1^{\varepsilon_1}\alpha_2^{\varepsilon_2}\cdots \alpha_\ell^{\varepsilon_\ell},
\)
where
	\begin{compactitem}
	\item $\alpha_i \in Q_1$ and~$\varepsilon_i \in \{-1,1\}$ for all~$i \in [\ell]$,
	\item $t(\alpha_i^{\varepsilon_i}) = s(\alpha_{i+1}^{\varepsilon_{i+1}})$ for all~$i \in [\ell-1]$, (by convention~$s(\alpha^{-1}) = t(\alpha)$ and~$t(\alpha^{-1}) = s(\alpha)$),
	\item there is no~$\alpha\beta \in I$ such that~$\alpha\beta$ or~$\beta^{-1}\alpha^{-1}$ appears as a factor of~$\rho$, and
	\item $\rho$ is reduced, in the sense that no factor~$\alpha\alpha^{-1}$ or~$\alpha^{-1}\alpha$ appears in~$\rho$, for~$\alpha \in Q_1$.
	\end{compactitem}
There is also an empty string~$\varepsilon_v$ for each vertex~$v \in Q_0$.
Strings are considered undirected, meaning that we implicitly identify~$\rho$ with~$\rho^{-1}$.
Let~$\strings(\bar Q)$ be the set of strings~of~$\bar Q$.

The \defn{blossoming quiver} of~${\bar Q = (Q,I)}$ is the gentle bound quiver~$\bar Q\blossom = (Q\blossom, I\blossom)$ obtained by adding arrows and relations at each vertex~$v \in Q_0$, so that~$v$ has precisely $2$ incoming and $2$ outgoing arrows and still fulfills the gentle conditions. See Figure~\ref{fig:exmQuiver}.

\begin{figure}[b]
	\centerline{\includegraphics[scale=.6]{exmQuiver}}
	\caption{A gentle bound quiver~$\bar Q$ (left), its blossoming quiver~$\bar Q\blossom$ (middle), and some walks in~$\bar Q\blossom$ (right). The dotted red and orange walks are non-kissing, but both are kissing the plain blue walk. See Figure~\ref{fig:exmFlip} for examples of non-kissing facets.}
	\label{fig:exmQuiver}
\end{figure}

A \defn{walk} in~$\bar Q$ is a maximal string in~$\bar Q\blossom$, \ie connecting two vertices of~$Q_0\blossom \ssm Q_0$.
A walk~$\omega$ is \defn{bending} if it has two opposite arrows and \defn{straight} otherwise.
For~$v \in Q_0$, the \defn{peak walk}~$v_\peak$ (resp.~the \defn{deep walk}~$v_\deep$) is the walk with two outgoing (resp.~incoming) arrows at vertex~$v$ and one incoming and one outgoing arrow at all its other vertices.
A \defn{substring} of~$\omega = \omega_1^{\varepsilon_1} \dots \omega_\ell^{\varepsilon_\ell}$ is a factor~$\sigma = \omega_{m+1}^{\varepsilon_{m+1}} \dots \omega_{n-1}^{\varepsilon_{n-1}}$ with~$1 \le m < n \le \ell$.
We say that~$\sigma$ is a \defn{top} (resp.~\defn{bottom}) substring of~$\omega$ if~${\varepsilon_m = -1 = -\varepsilon_n}$ (resp.~${\varepsilon_m = 1 = -\varepsilon_n}$), meaning that~$\omega$ has two outgoing (resp.~incoming) arrows at the endpoints of~$\sigma$.
Let~$\Sigma_\bottom(\omega)$ and~$\Sigma_\top(\omega)$ be the sets of bottom and top substrings~of~$\omega$ respectively.

Consider two walks~$\omega,\omega'$ on~$\bar Q$.
We say that~$\omega$ \defn{kisses}~$\omega'$ if~$\Sigma_\top(\omega) \cap \Sigma_\bottom(\omega') \ne \varnothing$, \ie if there exists a common substring~$\sigma$ of~$\omega$ and~$\omega'$ such that~$\omega$ has two outgoing arrows incident to~$\sigma$ while~$\omega'$ has two incoming arrows incident to~$\sigma$.
See Figures~\ref{fig:exmQuiver}\,(right)~\&~\ref{fig:kissingFlip}\,(left).
We authorize the case where~$\sigma$ is reduced to a vertex~$v$, \ie~$v$ is a peak of~$\omega$ and a deep of~$\omega'$.
Note that~$\omega$ can kiss~$\omega'$ several times, that~$\omega$ and~$\omega'$ can mutually kiss, and that~$\omega$ can kiss itself.
The \defn{non-kissing complex} of~$\bar Q$ is the simplicial complex~$\NKC$ whose faces are the collections of walks which are not self-kissing and pairwise non-kissing.
Note that no straight walk can kiss another walk by definition, so that they appear in all facets of~$\NKC$.
We thus consider the \defn{reduced non-kissing complex}~$\RNKC$ to be the deletion of all straight walks from~$\NKC$.
See Figure~\ref{fig:exmNKC}\,(left).

Our definition of non-kissing complex is largely inspired from and specializes to simplicial complexes defined from subsets of the grid~\cite{PetersenPylyavskyySpeyer, SantosStumpWelker, McConville, GarverMcConville-grid} or from dissections of polygons~\cite{Baryshnikov, Chapoton-quadrangulations, GarverMcConville, MannevillePilaud-accordion}. 
To the best of our knowledge, we actually provide the first connection between these two families, besides the observation that associahedra are instances of both.
In fact, the example of Figure~\ref{fig:exmNKC} is also a special case of both families.

\begin{figure}[t]
	\centerline{\includegraphics[scale=.59]{exmNKC}}
	\caption{A reduced non-kissing complex (left) and its flip graph~(right).}
	\label{fig:exmNKC}
\end{figure}

\begin{figure}[b]
	\centerline{\includegraphics[scale=1.2]{kissingFlip}}
	\caption{Two kissing walks (left) and a flip~(right).}
	\label{fig:kissingFlip}
\end{figure}

\subsection{Distinguished arrows and flips}

We now show that the non-kissing complex~$\RNKC$ is a \defn{pseudomanifold}, \ie that it is \defn{pure} (all facets have the same dimension) and \defn{thin} (there is a well-defined notion~of~flips).

A \defn{marked walk}~$\omega_\star$ is a walk~$\omega = \alpha_1^{\varepsilon_1} \cdots \alpha_\ell^{\varepsilon_\ell}$ with a marked arrow~$\alpha_i^{\varepsilon_i}$.
Consider two distinct non-kissing walks~$\mu_\star, \nu_\star$ marked at an arrow~$\alpha^\varepsilon \in Q\blossom_1$.
Let~$\sigma$ denote their maximal common substring containing that occurrence of~$\alpha$.
Since~$\mu_\star \ne \nu_\star$, their common substring~$\sigma$ is strict, so that~$\mu_\star$ and~$\nu_\star$ split at least at one endpoint of~$\sigma$.
We define the \defn{countercurrent order at~$\alpha$} by~$\mu_\star \prec_\alpha \nu_\star$ when~$\mu_\star$ enters and/or exits~$\sigma$ in the direction of~$\alpha$, while~$\nu_\star$ enters and/or exits~$\sigma$ in the opposite direction.
For a face~$F$ of~$\NKC$, we call \defn{distinguished walk} of~$F$ at an arrow~$\alpha$ the $\prec_\alpha$-maximal walk~$\distinguishedWalk{\alpha}{F}$, and we call \defn{distinguished arrows} of a walk~$\omega \in F$ the arrows~$\distinguishedArrows{\omega}{F} \eqdef \set{\alpha \in \omega}{\distinguishedWalk{\alpha}{F} = \omega}$.
The following statement is inspired from~\cite[Theorem~3.2]{McConville} and illustrated in Figure~\ref{fig:exmFlip}\,(left).

\begin{figure}[b]
	\centerline{\includegraphics[scale=.68]{exmFlip}}
	\caption{Flipping the red walk~$\omega$ to the orange walk~$\omega'$. The walks~$\mu, \nu$ involved in the flip are the blue and green walks. Distinguished arrows are marked with triple~arrows.}
	\label{fig:exmFlip}
\end{figure}

\begin{proposition}
\label{prop:distinguishedArrows}
Each bending (resp.~straight) walk of a facet~$F \in \NKC$ contains precisely~$2$ (resp.~$1$) distinguished arrows pointing in opposite directions (resp.~in the direction~of~the~walk).
\end{proposition}

%The next statement follows by double counting (each arrow has a distinguished walk, while each bended/straight walk has two/one distinguished arrows).

\begin{corollary}
\label{coro:pure}
The reduced non-kissing complex~$\RNKC$ is pure of dimension~$|Q_0|$.
\end{corollary}

Define the \defn{distinguished string} of a bending walk~$\omega$ in a facet~$F \in \NKC$ as the substring~$\distinguishedString{\omega}{F}$ of~$\omega$ located between the two distinguished arrows of~$\omega$.

\begin{proposition}
\label{prop:flip}
Consider a facet~$F \in \NKC$ and a bending walk~$\omega \in F$.
Write~${\omega = \rho \sigma \tau}$ where~$\sigma \eqdef \distinguishedString{\omega}{F}$.
%The distinguished substring~$\sigma = \distinguishedString{\omega}{F}$ splits~$\omega$ into~${\omega = \rho \sigma \tau}$.
Let~$\{\alpha, \beta\} \eqdef \distinguishedArrows{\omega}{F}$, and~$\alpha'$ and~$\beta'$ be the other two arrows of~$Q_1\blossom$ incident to the endpoints of~$\sigma$ and such that~${\alpha'\alpha \in I}$ or~${\alpha\alpha' \in I}$, and ${\beta'\beta \in I}$ or~${\beta\beta' \in I}$.
Let~$\mu \eqdef \distinguishedWalk{\alpha'}{F \ssm \{\omega\}}$ and~$\nu \eqdef \distinguishedWalk{\beta'}{F \ssm \{\omega\}}$.
See Figures~\ref{fig:kissingFlip}\,(right) \&~\ref{fig:exmFlip}.~Then
\begin{compactenum}[(i)]
\item The string~$\sigma$ splits the walk~$\mu$ into~$\mu = \rho' \sigma \tau$ and the walk~$\nu$ into~$\nu = \rho \sigma \tau'$.
\item The walk~$\omega' \eqdef \rho' \sigma \tau'$ is kissing~$\omega$ but no other~walk~of~$F$. Moreover, $\omega'$ is the only other walk besides~$\omega$ which is not kissing any other walk of~$F \ssm \{\omega\}$.
\end{compactenum}
We say that~$F \symdif \{\omega, \omega'\}$ is obtained from~$F$ by \defn{flipping}~$\omega$, and that the flip is \defn{supported}~by~$\sigma$.
\end{proposition}

\begin{corollary}
The reduced non-kissing complex~$\RNKC$ is a pseudomanifold without boundary.
\end{corollary}

\newpage
\section{Non-kissing lattices}
\label{sec:nonkissinglattice}

The flip of Proposition~\ref{prop:flip} and Figures~\ref{fig:kissingFlip} \&~\ref{fig:exmFlip} exchanges two kissing walks~$\omega, \omega'$.
The~flip is \defn{increasing} when their common substring is on top of~$\omega$ and on the bottom of~$\omega'$.
This yields the \defn{increasing flip graph}, where vertices are non-kissing facets and arcs are increasing flips.
%The \defn{peak facet}~$\set{v_\peak}{v \in Q_0}$ is a source and the \defn{deep facet}~$\set{v_\deep}{v \in Q_0}$ is a sink.
See Figure~\ref{fig:exmNKC}\,(right).
The main result of this section is the following~statement.

\begin{theorem}
\label{thm:lattice}
If~$\RNKC$ is finite, the increasing flip graph is the Hasse diagram of a congruence-uniform lattice, that we call \defn{non-kissing lattice} and denote by~$\NKL$.
\end{theorem}

Congruence-uniform lattices will be properly defined in Section~\ref{subsec:joinRepresentations}.
To achieve Theorem~\ref{thm:lattice}, we use a technique developed by T.~McConville for grid quivers~\cite{McConville}: we identify the non-kissing lattice with a quotient of a lattice of biclosed sets of strings.

\subsection{Biclosed sets of strings}
\label{subsec:biclosedSets}

A \defn{closure operator} on a finite set~$\cS$ is a map~$S \mapsto \closure{S}$ on subsets of~$\cS$ such that~$\closure{\varnothing} = \varnothing$, $S \subseteq \closure{S}$, $\closure{(\closure{S})} = \closure{S}$ and~$S \subseteq T \Longrightarrow \closure{S} \subseteq \closure{T}$ for any~$S,T \subseteq \cS$.
A subset~${S \subseteq \cS}$ is \defn{closed} if~$\closure{S} = S$, \defn{coclosed} if~$\cS \ssm S$ is closed, and \defn{biclosed} if it is both closed and coclosed.
Let~$\Bicl{\cS}$ be the inclusion poset of biclosed subsets of~$\cS$.
In~\cite[Theorem~5.5]{McConville}, T.~McConville gave simple sufficient conditions for~$\Bicl{\cS}$ to be a congruence uniform lattice.
In~\cite[Theorem~3.21]{PaluPilaudPlamondon}, we extended this criterion in the situation when the singletons of~$\cS$ are not biclosed so that we can apply it in our context of non-kissing complexes.

In a gentle bound quiver~$\bar Q$, we define the \defn{closure}~$\closure{S}$ of a set~$S$ of strings of~$\bar Q$ as the set of all strings of the form~$\sigma_1 \alpha_1^{\varepsilon_1} \sigma_2 \alpha_2^{\varepsilon_2} \dots \alpha_{\ell-1}^{\varepsilon_{\ell-1}} \sigma_\ell$ where~$\sigma_i \in S, \alpha_i \in Q_1$ and~${\varepsilon_i \in \{-1,1\}}$.
Let~$\Bicl{\bar Q}$ be the inclusion poset on biclosed sets of strings of~$\bar Q$.
For example, when~$\bar Q$ is a path on $n$ vertices with no relation, the strings are in bijection with pairs~${(i,j) \in \binom{n+1}{2}}$, the closure on strings translates to the concatenation~${(i,j) \circ (k,\ell) = \delta_{j = k} (i, \ell)}$, biclosed sets of strings are in bijection with inversion sets of permutations of~$[n+1]$, so that~$\Bicl{\bar Q}$ is isomorphic to the weak order on~$\fS_{n+1}$.
Figure~\ref{fig:exmLatticeQuotient}\,(left) illustrates the poset~$\Bicl{\bar Q}$ for another gentle bound quiver, with the empty set in the bottom and the set of all strings of~$\bar Q$ on top. The criterion of~\cite[Theorem~3.21]{PaluPilaudPlamondon} yields the following~result.

\begin{theorem}
When~$\bar Q$ has finitely many strings, the inclusion poset of biclosed sets~$\Bicl{\bar Q}$ is a congruence-uniform lattice.

\begin{figure}[t]
	\centerline{\includegraphics[scale=.59]{exmLatticeQuotient}}
	\caption{The inclusion lattice of biclosed sets~$\Bicl{\bar Q}$ with congruence classes of~$\equiv$ in blue (left), and the corresponding lattice of increasing flips on facets of~$\NKC$ (right).}
	\label{fig:exmLatticeQuotient}
\end{figure}
\end{theorem}

\subsection{Lattice congruence}
\label{subsec:congruence}

A \defn{lattice congruence} of a lattice~$(L, \le, \meet, \join)$ is an equivalence relation~$\equiv$ on~$L$ compatible with meets and joins: $x \equiv x'$ and~$y \equiv y'$ implies~$x \meet y \equiv x' \meet y'$ and~$x \join y \equiv x' \join y'$. 
It defines a \defn{lattice quotient}~$L/{\equiv}$ on the congruence classes of~$\equiv$ where the order relation is given by~$X \le Y$ iff there exists~$x \in X$ and~$y \in Y$ such that~$x \le y$ and the meet~$X \meet Y$ (resp.~the join~$X \join Y$) of two congruence classes~$X$ and~$Y$ is the congruence class of~$x \meet y$ (resp.~of~$x \join y$) for arbitrary representatives~$x \in X$~and~$y \in Y$.
For a finite lattice~$L$, an equivalence relation~$\equiv$ on~$L$ is a lattice congruence if and only if its congruence classes are intervals and the maps~$\projDown$ and~$\projUp$, sending an element~$x \in L$ to the minimum and maximum of its congruence class respectively, are order preserving.
%In fact, one can also define a lattice congruence directly by its up and down maps~$\projUp$~and~$\projDown$.

Following~\cite[Section~7]{McConville}, we associate to a biclosed set~$S \in \Bicl{\bar Q}$ the sets \\[.1cm]
\centerline{$
\projDown(S) \eqdef \set{\sigma \in \strings(\bar Q)}{\Sigma_\bottom(\sigma) \subseteq S}
\quad\text{and}\quad
\projUp(S) \eqdef \set{\sigma \in \strings(\bar Q)}{\Sigma_\top(\sigma) \cap S \ne \varnothing}.
$} \\[.1cm]
Here and throughout the paper, we denote by~$\Sigma_\bottom(\sigma)$ the set of bottom substrings for a string ${\sigma = \alpha_1^{\varepsilon_1} \dots \alpha_\ell^{\varepsilon_\ell}}$, \ie the substrings~$\alpha_m^{\varepsilon_m} \dots \alpha_n^{\varepsilon_n}$ for $1 \le m \le n \le \ell$ such that~$m = 1$ or~$\varepsilon_{m-1} = -1$, and $n = \ell$ or $\varepsilon_{n+1} = 1$ (and similarly for the set of top substrings~$\Sigma_\top(\sigma)$).

\begin{proposition}
\label{prop:latticeCongruence}
For any~$S \in \Bicl{\bar Q}$, the sets~$\projDown(S)$ and~$\projUp(S)$ are biclosed.
Moreover,
\begin{compactenum}[(i)]
\item
$\projDown(S) \subseteq S \subseteq \projUp(S)$ for any element~$S \in \Bicl{\bar Q}$,

\item
$\projDown \circ \projDown = \projDown \circ \projUp = \projDown$ and $\projUp \circ \projUp = \projUp \circ \projDown = \projUp$,

\item
$\projDown$ and~$\projUp$ are order preserving.
\end{compactenum}
Therefore, the fibers of~$\projUp$ and~$\projDown$ coincide and are the classes of a lattice congruence~$\equiv$ on~$\Bicl{\bar Q}$.
\end{proposition}

For example, if~$\bar Q$ is an oriented path with no relation, $\equiv$ is a Cambrian congruence of the weak~order~\cite{Reading-CambrianLattices}.
The congruence classes of~$\equiv$ appear as blue rectangles~in~Figure~\ref{fig:exmLatticeQuotient}.

\subsection{Non-kissing lattice}

Coming back to our original problem, we now aim to show that the increasing flip graph on non-kissing facets is isomorphic to the Hasse diagram of the quotient of the lattice of biclosed set~$\Bicl{\bar Q}$ of Section~\ref{subsec:biclosedSets} by the lattice congruence of Section~\ref{subsec:congruence}.
The next two propositions provide explicit maps between biclosed sets of strings and non-kissing facets illustrated in Figure~\ref{fig:exmSurjection}. It extends previous definitions of~\cite{McConville} for grid quivers.

\begin{proposition}
For~$S \in \Bicl{\bar Q}$ and~$\alpha \in Q_1\blossom$, let
\(
{\omega(\alpha,S) \eqdef \alpha_{-\ell}^{\varepsilon_{-\ell}} \cdots \alpha_{-1}^{\varepsilon_{-1}} \cdot \alpha \cdot \alpha_1^{\varepsilon_1} \cdots \alpha_r^{\varepsilon_r}}
\)
be the directed walk containing~$\alpha$ defined by
\begin{compactitem}
\item $\varepsilon_i = -1$ if the string~$\alpha_1^{\varepsilon_1} \cdots \alpha_{i-1}^{\varepsilon_{i-1}}$ belongs to~$S$, and~$\varepsilon_i = 1$ otherwise, for all~$i \in [r]$,
\item $\varepsilon_{-i} = 1$ if the string~$\alpha_{-i+1}^{\varepsilon_{-i+1}} \cdots \alpha_{-1}^{\varepsilon_{-1}}$ belongs to~$S$, and~$\varepsilon_i = -1$ otherwise, for all~$i \in [\ell]$.
\end{compactitem}
Then the set~$\set{\omega(\alpha,S)}{\alpha \in Q_1\blossom}$ contains~$2|Q_0| - |Q_1|$ straight walks and~$|Q_0|$~pairs of inverse directed bending walks, which are all pairwise non-kissing.
We thus obtain a facet~$\eta(S)$ of~$\NKC$ by identifying these pairs of inverse directed bending walks.
\end{proposition}

\begin{proposition}
For any facet~$F \in \NKC$, the set~$\zeta(F) \eqdef \displaystyle\closure{\Big( \bigcup\limits_{\omega \in F} \Sigma_\bottom(\omega) \Big)}
$~is~biclosed.
\end{proposition}

When the quiver is an oriented path with no relation, the map~$\eta$ should be thought of as the map from permutations to triangulations defined in~\cite{Reading-CambrianLattices}.
Conversely, $\zeta$ maps a triangulation to the minimal permutation in its fiber under~$\eta$.
For the straight quiver, $\eta$ plays the role of the binary search tree insertion while~$\zeta$ selects the minimal linear extension of a binary tree.
%
Using these maps, we show that the increasing flip graph on non-kissing facets is isomorphic to the Hasse diagram of the lattice quotient~$\Bicl{\bar Q}/{\equiv}$.

\begin{theorem}
The maps~$\eta: \Bicl{\bar Q} \to \NKC$ and~$\zeta: \NKC \to \Bicl{\bar Q}$ satisfy:
\begin{compactitem}
\item $\eta \big( \zeta(F) \big) = F$ for any facet~$F \in \NKC$,
\item $\zeta \big( \eta(S) \big) = \projDown(S)$ for any biclosed set~$S \in \Bicl{\bar Q}$,
\item for any facet~$F' \in \RNKC$ and~$\sigma \in \zeta(F')$, there exists an increasing flip~$F \to F'$ supported by~$\sigma$ if and only if~$\zeta(F') \ssm \{\sigma\}$ is biclosed.
\end{compactitem}
Therefore, the facets of~$\NKC$ are in bijection with the congruence classes of~$\equiv$ and the increasing flip graph is the Hasse diagram of the lattice quotient~$\Bicl{\bar Q}/{\equiv}$.

\begin{figure}[b]
	\vspace{-.3cm}
	\centerline{
	\begin{overpic}[scale=.5]{exmSurjection}
			\put(28,8){$\longrightarrow$}
			\put(29,10){$\eta$}
			\put(69,8){$\longrightarrow$}
			\put(70,10){$\zeta$}
			\put(13,-3){$S$}
			\put(46,-3){$\eta(S)$}
			\put(77,-3){$\zeta(\eta(S)) = \projDown(S)$}
	\end{overpic}
	}
	\vspace{.4cm}
	\caption{The maps~$\eta$ (left) and $\zeta$ (right) between non-kissing facets and biclosed sets.}
	\label{fig:exmSurjection}
\end{figure}
\end{theorem}

\newpage
\subsection{Canonical join complex}
\label{subsec:joinRepresentations}

In a lattice~$(L,\le,\meet,\join)$, a \defn{join representation} of~$x \in L$ is a subset~$J \subseteq L$ such that~${x = \bigJoin J}$.
This representation is \defn{irredundant} if~$x \ne \bigJoin J'$ for a strict subset~$J' \subsetneq J$.
The irredundant join representations of~$x \in L$ are ordered by containement of the lower ideals of their elements, \ie~$J \le J'$ if and only if for any~$y \in J$ there exists~$y' \in J'$ such that~$y \le y'$.
When this order has a minimal element, it is called the \defn{canonical join representation} of~$x$.
All elements of the canonical join representation~$x = \bigJoin J$ are then \defn{join-irreducible}, \ie cover a single element. Canonical meet representations and meet-irreducibles are defined dually.

A lattice~$L$ is \defn{congruence-uniform} if its join-irreducible elements are in bijection with the join-irreducibles of its lattice of congruences, and similarly for meet-irreducibles.
Congruence-uniform lattices behave nicely with join representations and congruence lattices.
In particular, congruence-uniform lattices are semi-distributive, so that any element admits a canonical join representation.
The collection of sets~$J$ which define canonical join representations in~$L$ is the \defn{canonical join complex} of~$L$.

To conclude our study of the non-kissing lattice~$\NKL$, we describe its canonical join complex.
We say that a string~$\sigma \in \strings(\bar Q)$ is \defn{distinguishable} if there is a facet~${F \in \NKC}$ and a walk~$\omega \in F$ such that~$\sigma = \distinguishedString{\omega}{F}$.
These strings are characterized as follows.

\begin{proposition}
\label{prop:characterizationDistinguishableStrings}
A string~$\sigma \in \strings(\bar Q)$ is distinguishable if and only if ${\Sigma_\bottom(\sigma) \cap \Sigma_\top(\sigma) = \{\sigma\}}$.
\end{proposition}

One checks that~$\closure{\Sigma_\bottom(\sigma)}$ is biclosed so that we can define~$\ji(\sigma) \eqdef \eta \big( \closure{\Sigma_\bottom(\sigma)} \big)$.

\begin{proposition}
The map~$\ji : \sigma \mapsto \ji(\sigma)$ defines a bijection between the distinguishable strings of~$\bar Q$ and the join-irreducible elements of the non-kissing lattice~$\NKL$.
\end{proposition}

Therefore, distinguishable strings are building blocks for canonical join representations in~$\NKL$.
A \defn{descent} of a facet~$F \in \NKC$ is a string~$\sigma$ which is the distinguished string of a walk~$\omega$ of~$F$ and is a bottom substring of~$\omega$ (so that the flip of~$\omega$ in~$F$ is a descent in the non-kissing lattice).
We denote by~$\descents(F)$ the set of descents of~$F$.

\begin{proposition}
The canonical join representation of~$F \in \NKL$ is given by ${F = \!\!\! \bigJoin\limits_{\sigma \in \descents(F)} \!\!\! \ji(\sigma)}$.
\end{proposition}

To conclude, we characterize which subsets of strings correspond to canonical join representations in the non-kissing lattice~$\NKL$.
Following~\cite{GarverMcConville-grid}, we say that two strings are \defn{non-friendly} if $\Sigma_\top(\sigma) \cap \Sigma_\bottom(\tau) = \varnothing = \Sigma_\bottom(\sigma) \cap \Sigma_\top(\tau)$.
We call \defn{non-friendly complex} the simplicial complex of sets of pairwise non-friendly distinguishable strings.

\begin{theorem}
The following assertions are equivalent for a set~$\Sigma$ of distinguishable strings~of~$\bar Q$:
\begin{compactitem}
\item Any two strings of~$\Sigma$ are non-friendly.
\item $\set{\ji(\sigma)}{\sigma \in \Sigma}$ is the canonical join-representation of a facet of~$\NKC$.
\item $\Sigma$ is the descent set of a non-kissing facet~$F \in \NKC$.
\end{compactitem}
In other words, the canonical join complex of~$\NKL$ is isomorphic to the non-friendly complex.
\end{theorem}

For example, when the quiver is a straight path with no relation, the non-friendly complex is isomorphic to the non-crossing partition complex.

\newpage
\section{Gentle associahedra}
\label{sec:gentleAssociahedra}

In this section, we provide polyhedral realizations for finite non-kissing complexes, using tools inspired from the finite type cluster algebras of S.~Fomin and A.~Zelevinsky~\cite{FominZelevinsky-ClusterAlgebrasII}.

\subsection{$\b{g}$-vectors and $\b{c}$-vectors}

Let~${\multiplicityVector_V \eqdef \sum_{i \in [m]} \b{e}_{v_i} \in \R^{Q_0}}$ be the \defn{multiplicity vector} of a multiset~$V = \{v_1, \dots, v_m\}$ of~$Q_0$.
For a string~$\sigma \in \strings(\bar Q)$, let~$\multiplicityVector_\sigma \eqdef \multiplicityVector_{V(\sigma)}$ where~$V(\sigma)$ is the multiset of vertices~of~$\sigma$.

For a walk~$\omega$ on~$\bar Q$, we denote by~$\peaks{\omega}$ (resp.~by~$\deeps{\omega}$) the (multi)set of peaks (resp.~deeps) of~$\omega$.
The \defn{$\b{g}$-vector} of~$\omega$ is the vector~${\gvector{\omega} \eqdef \multiplicityVector_{\peaks{\omega}} - \multiplicityVector_{\deeps{\omega}} \in \R^{Q_0}}$.
For a set~$\Omega$ of walks, $\gvectors{\Omega} \eqdef \! \set{\gvector{\omega}\!}{\!\omega \in \Omega}$.
Note that~$\gvector{\omega} = 0$ for a straight~walk~$\omega$.

Consider a bending walk~$\omega$ in a facet~$F \in \RNKC$.
By Proposition~\ref{prop:distinguishedArrows}, $\omega$ has two~distinguished arrows~$\distinguishedArrows{\omega}{F}$ around its distinguished string~$\distinguishedString{\omega}{F}$.
\mbox{The \defn{$\b{c}$-vector} of~$\omega \in F$} is the vector~${\cvector{\omega}{F} \eqdef \distinguishedSign{\omega}{F} \, \multiplicityVector_{\distinguishedString{\omega}{F}} \in \R^{Q_0}}$, where~$\distinguishedSign{\omega}{F} \eqdef 1$ if~${\distinguishedString{\omega}{F} \in \Sigma_\top(\omega)}$ and $\distinguishedSign{\omega}{F} \eqdef -1$ if~${\distinguishedString{\omega}{F} \in \Sigma_\bottom(\omega)}$.
Denote by~$\cvectors{F} \eqdef \set{\cvector{\omega}{F}}{\omega \in F}$.

\begin{proposition}
\label{prop:gvectorscvectorsDualBases}
For any non-kissing facet~$F \in \RNKC$, the set of $\b{g}$-vectors~$\gvectors{F}$ and the set of $\b{c}$-vectors~$\cvectors{F}$ form dual bases.
%
\begin{figure}[h]
	\centerline{$\raisebox{-1.5cm}{\begin{overpic}[scale=.65]{exmVectors}\put(60,-4){$F$}\end{overpic}}$ \quad \input{figures/gcmatrices}}
	\vspace{-.3cm}
	\caption{The $\b{g}$- and $\b{c}$-matrices of a facet~$F$ form dual bases.}
	\vspace{-.7cm}
	\label{fig:gcvectors}
\end{figure}
\end{proposition}

\subsection{$\b{g}$-vector fans and gentle associahedra}

We now use $\b{g}$- and~$\b{c}$-vectors to construct polyhedral realizations of finite non-kissing complexes.
Since the $\b{g}$-vectors of the walks~$\omega, \omega', \mu, \nu$ involved in the flip of Figure~\ref{fig:kissingFlip} satisfy the linear dependence $\gvector{\omega} + \gvector{\omega'} = \gvector{\mu} + \gvector{\nu}$, we get the following~statement.

\begin{theorem}
\label{thm:gvectorFan}
For a gentle bound quiver~$\bar Q$ with finite non-kissing complex~$\RNKC$, the collection of cones
\(
\gvectorFan \eqdef \set{\R_{\ge0} \gvectors{F}}{F \text{ non-kissing face of } \RNKC}
\)
forms a complete simplicial fan, that we call the \defn{$\b{g}$-vector fan} of~$\bar Q$.
\end{theorem}

\begin{figure}[h]
	\centerline{\includegraphics[scale=.59]{exmFanAsso}}
	\caption{The $\b{g}$-vector fan~$\gvectorFan$ (left) and the gentle associahedra (right).}
	\label{fig:exmFans}
\end{figure}

This fan is illustrated in Figure~\ref{fig:exmFans}\,(left).
Note that it was constructed in~\cite{MannevillePilaud-accordion} for dissection quivers and in~\cite{GarverMcConville-grid} for grid quivers. Both constructions extend the type~$A$ Cambrian fans of N.~Reading and D.~Speyer~\cite{ReadingSpeyer} obtained for path~quivers with no relations.

\newpage
We now aim at constructing a polytope whose normal fan is the $\b{g}$-vector fan of~$\bar Q$.
For two walks~$\omega, \omega'$ on~$\bar Q$, denote by~$\kn(\omega,\omega')$ the number of distinct kisses of~$\omega$ to~$\omega'$.
%Note that kisses are counted with multiplicities if~$\omega$ or~$\omega'$ pass twice through the same substring.
The \defn{kissing number} of~$\omega$ and~$\omega'$ is~$\KN(\omega,\omega') \eqdef \kn(\omega,\omega') + \kn(\omega',\omega)$.
When~$\RNKC$ is finite, we can define the \defn{kissing number} of a walk~$\omega$ on~$\bar Q$ as
\(
\KN(\omega) \eqdef \sum_{\omega'} \KN(\omega,\omega').
\)
%where the sum runs over all walks~$\omega'$ on~$\bar Q$.
%We obtain the following statement.

%\begin{theorem}
%\label{thm:associahedron}
%Let~$\bar Q$ be a gentle bound quiver with finite non-kissing complex~$\RNKC$.
%Define
%\begin{compactenum}[(i)]
%\item a point
%\(
%\point{F} \eqdef \sum_{\omega \in F} \KN(\omega) \, \cvector{\omega}{F}
%\)
%for each non-kissing facet~${F \in \RNKC}$,
%\item a halfspace
%\(
%\HS{\omega} \eqdef \bigset{\b{x} \in \R^{Q_0}}{\dotprod{\gvector{\omega}}{\b{x}} \le \KN(\omega)}
%\)
%for each walk~$\omega$ on~$\bar Q$.
%\end{compactenum}
%Then the two sets of~$\R^{Q_0}$ given by
%\begin{compactenum}[(i)]
%\item the convex hull of the points~$\point{F}$ for all non-kissing facets~${F \in \RNKC}$,
%\item the intersection of the halfspaces~$\HS{\omega}$ for all walks~$\omega$ on~$\bar Q$,
%\end{compactenum}
%define the same polytope whose normal fan is the $\b{g}$-vector fan~$\gvectorFan$.
%We call this polytope the \defn{$\bar Q$-associahedron} and denote it by~$\Asso$.
%\end{theorem}

\begin{theorem}
\label{thm:associahedron}
For a gentle bound quiver~$\bar Q$ with finite non-kissing complex~$\RNKC$, the $\b{g}$-vector fan~$\gvectorFan$ is the normal fan of the \defn{$\bar Q$-associahedron}~$\Asso$ defined equivalently as:
\begin{compactenum}[(i)]
\item the convex hull of the points~$\point{F} \eqdef \sum_{\omega \in F} \KN(\omega) \, \cvector{\omega}{F}$ for all facets~${F \in \RNKC}$,~or
\item the intersection of the halfspaces~$\HS{\omega} \eqdef \bigset{\b{x} \in \R^{Q_0}}{\dotprod{\gvector{\omega}}{\b{x}} \le \KN(\omega)}$ for all walks~$\omega$ on~$\bar Q$.
\end{compactenum}
\end{theorem}

For path quivers with no relation, we recover the associahedra of C.~Hohlweg and C.~Lange~\cite{HohlwegLange}.
The latter are obtained by deleting inequalities in the facet description of the classical permutahedron.
This property is lost for arbitrary gentle quivers: on the one hand, the Coxeter arrangement supporting the $\b{g}$-vector fan~$\gvectorFan$ is not necessarily of finite type; on the other hand, the $\bar Q$-associahedron is not always obtained by deleting inequalities in the facet description of the Minkowski sum of all $\b{c}$-vectors. See~\cite{PaluPilaudPlamondon} for a detailed discussion.
The $\bar Q$-associahedron was constructed in~\cite{MannevillePilaud-accordion} in the special case of dissection quivers.
An example of~$\Asso$ is shown in Figure~\ref{fig:exmFans}.
%The $\bar Q$-associahedron was constructed in~\cite{MannevillePilaud-accordion} in the special case of dissection quivers, generalizing the associahedra of C.~Hohlweg and C.~Lange~\cite{HohlwegLange} for path quivers with no relations.
%An example of~$\Asso$ is illustrated in Figure~\ref{fig:exmFans}. 
For grid quivers, our construction proves the polytopality conjecture for the $\b{g}$-vector fan stated~in~\cite{GarverMcConville-grid}.

This realization of the non-kissing complex has the following relevant property regarding the non-kissing lattice studied in Section~\ref{sec:nonkissinglattice}.

\begin{proposition}
When oriented in the linear direction~$(-1, \dots, -1) \in \R^{Q_0}$, the graph of the $\bar Q$-associahedron is (isomorphic to) the increasing flip graph.
\end{proposition}

%% if you use biblatex then this generates the bibliography
%% if you use some other method then remove this and do it your own way
\printbibliography

\end{document}

### 2020-06-29 firstPaper/FPSAC/nonKissingComplexFPSACRevision.tex
FPSAC

--- 2020-06-29 firstPaper/FPSAC/nonKissingComplexFPSAC.tex
@@
 %% otherwise options taken by the article class will be accepted
-\documentclass[finalversion]{FPSAC2018}
-\articlenumber{39}
+\documentclass[submission]{FPSAC2018Revision}
 %% but DO NOT pass any options (or change anything else anywhere) which alters page size / layout / font size etc
@@
 % theorems
-\newtheorem{theorem}{Theorem}[section]
+\newtheorem{theorem}{Theorem}
 \newtheorem{corollary}[theorem]{Corollary}
@@
 %% use \addressmark{1}, \addressmark{2} etc for the institutions, and use \thanks{} for contact details
-\author{
-	Yann Palu\thanks{\href{mailto:yann.palu@u-picardie.fr}{yann.palu@u-picardie.fr}. Supported by the French ANR grant SC3A~(15\,CE40\,0004\,01).}\addressmark{1},
-	\stepcounter{footnote}
-	Vincent Pilaud\thanks{\href{mailto:}{vincent.pilaud@lix.polytechnique.fr}. Supported by the French ANR grant SC3A~(15\,CE40\,0004\,01).}\addressmark{2}, \and
-	Pierre-Guy Plamondon\addressmark{3}\thanks{\href{mailto:}{pierre-guy.plamondon@math.u-psud.fr}. Supported by French the ANR grant SC3A~(15\,CE40\,0004\,01).}
-}
+\author{Yann Palu\addressmark{1}, Vincent Pilaud\addressmark{2} \and Pierre-Guy Plamondon\addressmark{3}\thanks{\href{mailto:yann.palu@u-picardie.fr}{yann.palu@u-picardie.fr}, \href{mailto:}{vincent.pilaud@lix.polytechnique.fr}, \href{mailto:}{pierre-guy.plamondon@math.u-psud.fr}.
+The three authors were partially supported by the French ANR grant SC3A~(15\,CE40\,0004\,01).}}
 
@@
 \usepackage[backend=bibtex]{biblatex}
-\addbibresource{nonKissingComplexFPSAC.bib}
+\addbibresource{nonKissingComplexFPSACRevision.bib}
 %% note the \printbibliography command at the end of the file which goes with these biblatex commands
@@
 It was introduced by T.~K.~Petersen, P.~Pylyavskyy and D.~Speyer in~\cite{PetersenPylyavskyySpeyer} for a staircase shape, studied by F.~Santos, C.~Stump and V.~Welker~\cite{SantosStumpWelker} for rectangular shapes, and extended by T.~McConville in~\cite{McConville} for arbitrary shapes.
-This complex is known to be a simplicial sphere, and it was actually realized as a polytope using successive edge stellations and suspensions in~\cite[Section~4]{McConville}.
-Moreover, the dual graph of the non-kissing complex has a natural orientation which equips its facets with a lattice structure~\cite[Theorem 1.1, Section~5--8]{McConville}.
+This complex is known to be a simplicial sphere, and it was actually realized as a polytope using successive edge stellations and suspensions in~\cite[Sect.~4]{McConville}.
+Moreover, the dual graph of the non-kissing complex has a natural orientation which equips its facets with a lattice structure~\cite[Thm. 1.1, Sect.~5--8]{McConville}.
 Further lattice theoretic and geometric aspects of this complex were recently developed by A.~Garver and T.~McConville in~\cite{GarverMcConville-grid}.
@@
 The interest for non-kissing complexes is motivated by relevant instances arising from particular shapes.
-As already observed in~\cite[Section~10]{McConville}, when the shape is a ribbon, the non-kissing complex is an associahedron, and the non-kissing lattice is a type~$A$ Cambrian lattice of N.~Reading~\cite{Reading-CambrianLattices}.
+As already observed in~\cite[Sect.~10]{McConville}, when the shape is a ribbon, the non-kissing complex is an associahedron, and the non-kissing lattice is a type~$A$ Cambrian lattice of N.~Reading~\cite{Reading-CambrianLattices}.
 In particular, the straight ribbon corresponds to the Tamari lattice, an object at the heart of a deep research area~\cite{TamariFestschrift}.
@@
 In this extended abstract, we focus on combinatorial and geometric aspects.
-We first define in Section~\ref{sec:nonkissingcomplex} the non-kissing complex of a gentle bound quiver and show that this complex is a pseudomanifold (meaning in particular that there is a well-defined notion of flips in non-kissing facets).
-In Section~\ref{sec:nonkissinglattice}, we show that the graph of increasing flips is the Hasse diagram of a congruence-uniform lattice and describe its canonical join complex.
-Finally, Section~\ref{sec:gentleAssociahedra} is devoted to the geometry of finite non-kissing complexes: we construct their $\b{g}$-vector fans and show that these fans are normal fans of convex polytopes.
+We first define in Sec.~\ref{sec:nonkissingcomplex} the non-kissing complex of a gentle bound quiver and show that this complex is a pseudomanifold (meaning in particular that there is a well-defined notion of flips in non-kissing facets).
+In Sec.~\ref{sec:nonkissinglattice}, we show that the graph of increasing flips is the Hasse diagram of a congruence-uniform lattice and describe its canonical join complex.
+Finally, Sec.~\ref{sec:gentleAssociahedra} is devoted to the geometry of finite non-kissing complexes: we construct their $\b{g}$-vector fans and show that these fans are normal fans of convex polytopes.
 We refer to~\cite{PaluPilaudPlamondon} for detailed proofs and further properties of non-kissing complexes.
@@
 We fix a \defn{gentle bound quiver}~$\bar Q \eqdef (Q,I)$, where~$Q \eqdef (Q_0, Q_1, s, t)$ is a \defn{quiver} with vertices~$Q_0$, arrows~$Q_1$, and source and target maps~$s, t : Q_1 \to Q_0$, and~$I$ is a set of quadratic \defn{relations}~$\alpha\beta = 0$ with~$\alpha, \beta \in Q_1$ and~$t(\alpha) = s(\beta)$ such that for any~$\beta \in Q_1$ there is at most one~$\alpha \in Q_1$ such that~$t(\alpha) = s(\beta)$ and~$\alpha\beta \in I$ (resp.~$\alpha\beta \notin I$) and at most one~$\gamma \in Q_1$ such that~$t(\beta) = s(\gamma)$ and~$\beta\gamma \in I$~(resp.~${\beta\gamma \notin I}$).
-See Figure~\ref{fig:exmQuiver}.
+See Fig.~\ref{fig:exmQuiver}.
 In all pictures, a relation~$\alpha\beta = 0$ is indicated with an arc connecting the target of~$\alpha$ to the source of~$\beta$.
@@
 
-The \defn{blossoming quiver} of~${\bar Q = (Q,I)}$ is the gentle bound quiver~$\bar Q\blossom = (Q\blossom, I\blossom)$ obtained by adding arrows and relations at each vertex~$v \in Q_0$, so that~$v$ has precisely $2$ incoming and $2$ outgoing arrows and still fulfills the gentle conditions.
-See Figure~\ref{fig:exmQuiver}.
+The \defn{blossoming quiver} of~${\bar Q = (Q,I)}$ is the gentle bound quiver~$\bar Q\blossom = (Q\blossom, I\blossom)$ obtained by adding arrows and relations at each vertex~$v \in Q_0$, so that~$v$ has precisely $2$ incoming and $2$ outgoing arrows and still fulfills the gentle quiver conditions.
+See Fig.~\ref{fig:exmQuiver}.
 
@@
 The dotted red and orange walks are non-kissing, but both are kissing the plain blue walk.
-See Figure~\ref{fig:exmFlip} for examples of non-kissing facets.}
+See Fig.~\ref{fig:exmFlip} for examples of non-kissing facets.}
 	\label{fig:exmQuiver}
@@
 We say that~$\omega$ \defn{kisses}~$\omega'$ if~$\Sigma_\top(\omega) \cap \Sigma_\bottom(\omega') \ne \varnothing$, \ie if there exists a common substring~$\sigma$ of~$\omega$ and~$\omega'$ such that~$\omega$ has two outgoing arrows incident to~$\sigma$ while~$\omega'$ has two incoming arrows incident to~$\sigma$.
-See Figures~\ref{fig:exmQuiver}\,(right)~\&~\ref{fig:kissingFlip}\,(left).
-We authorize the case where~$\sigma$ is reduced to a vertex~$v$, \ie~$v$ is a peak of~$\omega$ and a deep of~$\omega'$.
-Note that~$\omega$ can kiss~$\omega'$ several times, that~$\omega$ and~$\omega'$ can mutually kiss, and that~$\omega$ can kiss itself.
+See Figs.~\ref{fig:exmQuiver}\,(right)~\&~\ref{fig:kissingFlip}\,(left).
+Note that we authorize the situation where~$\sigma$ is reduced to a vertex~$v$, meaning that~$v$ is a peak of~$\omega$ and a deep of~$\omega'$.
+Observe also that~$\omega$ can kiss~$\omega'$ several times, that~$\omega$ and~$\omega'$ can mutually kiss, and that~$\omega$ can kiss itself.
 The \defn{non-kissing complex} of~$\bar Q$ is the simplicial complex~$\NKC$ whose faces are the collections of walks which are not self-kissing and pairwise non-kissing.
@@
 We thus consider the \defn{reduced non-kissing complex}~$\RNKC$ to be the deletion of all straight walks from~$\NKC$.
-See Figure~\ref{fig:exmNKC}\,(left).
+See Fig.~\ref{fig:exmNKC}\,(left).
 
-Our definition of non-kissing complex is largely inspired from and specializes to simplicial complexes defined from subsets of the grid~\cite{PetersenPylyavskyySpeyer, SantosStumpWelker, McConville, GarverMcConville-grid} or from dissections of polygons~\cite{Baryshnikov, Chapoton-quadrangulations, GarverMcConville, MannevillePilaud-accordion}.
+Our definition of non-kissing complex is largely inspired from and specializes to relevant simplicial complexes defined from subsets of the grid~\cite{PetersenPylyavskyySpeyer, SantosStumpWelker, McConville, GarverMcConville-grid} or from dissections of polygons~\cite{Baryshnikov, Chapoton-quadrangulations, GarverMcConville, MannevillePilaud-accordion}.
 To the best of our knowledge, we actually provide the first connection between these two families, besides the observation that associahedra are instances of both.
-In fact, the example of Figure~\ref{fig:exmNKC} is also a special case of both families.
+In fact, the example of Fig.~\ref{fig:exmNKC} is also a special case of both families.
 
@@
 For a face~$F$ of~$\NKC$, we call \defn{distinguished walk} of~$F$ at an arrow~$\alpha$ the $\prec_\alpha$-maximal walk~$\distinguishedWalk{\alpha}{F}$, and we call \defn{distinguished arrows} of a walk~$\omega \in F$ the arrows~$\distinguishedArrows{\omega}{F} \eqdef \set{\alpha \in \omega}{\distinguishedWalk{\alpha}{F} = \omega}$.
-The following statement is inspired from~\cite[Theorem~3.2]{McConville} and illustrated in Figure~\ref{fig:exmFlip}\,(left).
+The following statement is inspired from~\cite[Thm.~3.2]{McConville} and illustrated in Fig.~\ref{fig:exmFlip}\,(left).
 
@@
 Consider a facet~$F \in \NKC$ and a bending walk~$\omega \in F$.
-Write~${\omega = \rho \sigma \tau}$ where~$\sigma \eqdef \distinguishedString{\omega}{F}$.
-%The distinguished substring~$\sigma = \distinguishedString{\omega}{F}$ splits~$\omega$ into~${\omega = \rho \sigma \tau}$.
+The distinguished substring~$\sigma = \distinguishedString{\omega}{F}$ splits~$\omega$ into~${\omega = \rho \sigma \tau}$.
 Let~$\{\alpha, \beta\} \eqdef \distinguishedArrows{\omega}{F}$, and~$\alpha'$ and~$\beta'$ be the other two arrows of~$Q_1\blossom$ incident to the endpoints of~$\sigma$ and such that~${\alpha'\alpha \in I}$ or~${\alpha\alpha' \in I}$, and ${\beta'\beta \in I}$ or~${\beta\beta' \in I}$.
 Let~$\mu \eqdef \distinguishedWalk{\alpha'}{F \ssm \{\omega\}}$ and~$\nu \eqdef \distinguishedWalk{\beta'}{F \ssm \{\omega\}}$.
-See Figures~\ref{fig:kissingFlip}\,(right) \&~\ref{fig:exmFlip}.~Then
+See Figs.~\ref{fig:kissingFlip}\,(right)~and~\ref{fig:exmFlip}.~Then
 \begin{compactenum}[(i)]
@@
 
-The flip of Proposition~\ref{prop:flip} and Figures~\ref{fig:kissingFlip} \&~\ref{fig:exmFlip} exchanges two kissing walks~$\omega, \omega'$.
-The~flip is \defn{increasing} when their common substring is on top of~$\omega$ and on the bottom of~$\omega'$.
+The flip operation of Prop.~\ref{prop:flip} and Figs.~\ref{fig:kissingFlip} \&~\ref{fig:exmFlip} exchanges two kissing walks~$\omega, \omega'$.
+The flip is \defn{increasing} when their common substring is on top of~$\omega$ and on the bottom of~$\omega'$.
 This yields the \defn{increasing flip graph}, where vertices are non-kissing facets and arcs are increasing flips.
 %The \defn{peak facet}~$\set{v_\peak}{v \in Q_0}$ is a source and the \defn{deep facet}~$\set{v_\deep}{v \in Q_0}$ is a sink.
-See Figure~\ref{fig:exmNKC}\,(right).
-The main result of this section is the following~statement.
+See Fig.~\ref{fig:exmNKC}\,(right).
+The main result of this section is the following statement.
 
@@
 
-Congruence-uniform lattices will be properly defined in Section~\ref{subsec:joinRepresentations}.
-To achieve Theorem~\ref{thm:lattice}, we use a technique developed by T.~McConville for grid quivers~\cite{McConville}: we identify the non-kissing lattice with a quotient of a lattice of biclosed sets of strings.
+Congruence-uniform lattices will be properly defined in Sec.~\ref{subsec:joinRepresentations}.
+To achieve Thm.~\ref{thm:lattice}, we use a technique developed by T.~McConville for grid quivers~\cite{McConville}: we identify the non-kissing lattice with a quotient of a lattice of biclosed sets of strings.
 
@@
 A \defn{closure operator} on a finite set~$\cS$ is a map~$S \mapsto \closure{S}$ on subsets of~$\cS$ such that~$\closure{\varnothing} = \varnothing$, $S \subseteq \closure{S}$, $\closure{(\closure{S})} = \closure{S}$ and~$S \subseteq T \Longrightarrow \closure{S} \subseteq \closure{T}$ for any~$S,T \subseteq \cS$.
-A subset~${S \subseteq \cS}$ is \defn{closed} if~$\closure{S} = S$, \defn{coclosed} if~$\cS \ssm S$ is closed, and \defn{biclosed} if it is both closed and coclosed.
-Let~$\Bicl{\cS}$ be the inclusion poset of biclosed subsets of~$\cS$.
-In~\cite[Theorem~5.5]{McConville}, T.~McConville gave simple sufficient conditions for~$\Bicl{\cS}$ to be a congruence uniform lattice.
-In~\cite[Theorem~3.21]{PaluPilaudPlamondon}, we extended this criterion in the situation when the singletons of~$\cS$ are not biclosed so that we can apply it in our context of non-kissing complexes.
+A subset~$S \subseteq \cS$ is \defn{closed} if~$\closure{S} = S$, \defn{coclosed} if~$\cS \ssm S$ is closed, and \defn{biclosed} if it is both closed and coclosed.
+We denote by~$\Bicl{\cS}$ the inclusion poset of biclosed subsets of~$\cS$.
+In~\cite[Thm.~5.5]{McConville}, T.~McConville provided simple sufficient conditions for~$\Bicl{\cS}$ to be a congruence uniform lattice.
+In~\cite[Thm.~3.21]{PaluPilaudPlamondon}, we extended this criterion in the situation when the singletons of~$\cS$ are not biclosed so that we can apply it in our context of non-kissing complexes.
 
@@
 For example, when~$\bar Q$ is a path on $n$ vertices with no relation, the strings are in bijection with pairs~${(i,j) \in \binom{n+1}{2}}$, the closure on strings translates to the concatenation~${(i,j) \circ (k,\ell) = \delta_{j = k} (i, \ell)}$, biclosed sets of strings are in bijection with inversion sets of permutations of~$[n+1]$, so that~$\Bicl{\bar Q}$ is isomorphic to the weak order on~$\fS_{n+1}$.
-Figure~\ref{fig:exmLatticeQuotient}\,(left) illustrates the poset~$\Bicl{\bar Q}$ for another gentle bound quiver, with the empty set in the bottom and the set of all strings of~$\bar Q$ on top.
-The criterion of~\cite[Theorem~3.21]{PaluPilaudPlamondon} yields the following~result.
+Fig.~\ref{fig:exmLatticeQuotient}\,(left) illustrates the poset~$\Bicl{\bar Q}$ for another gentle bound quiver, with the empty set in the bottom and the set of all strings of~$\bar Q$ on top.
+The criterion of~\cite[Thm.~3.21]{PaluPilaudPlamondon} yields the following~result.
 
@@
 
-Following~\cite[Section~7]{McConville}, we associate to a biclosed set~$S \in \Bicl{\bar Q}$ the sets \\[.1cm]
+Following~\cite[Sect.~7]{McConville}, we associate to a biclosed set~$S \in \Bicl{\bar Q}$ the sets \\[.1cm]
 \centerline{$
@@
 Here and throughout the paper, we denote by~$\Sigma_\bottom(\sigma)$ the set of bottom substrings for a string ${\sigma = \alpha_1^{\varepsilon_1} \dots \alpha_\ell^{\varepsilon_\ell}}$, \ie the substrings~$\alpha_m^{\varepsilon_m} \dots \alpha_n^{\varepsilon_n}$ for $1 \le m \le n \le \ell$ such that~$m = 1$ or~$\varepsilon_{m-1} = -1$, and $n = \ell$ or $\varepsilon_{n+1} = 1$ (and similarly for the set of top substrings~$\Sigma_\top(\sigma)$).
+
+%These sets satisfy the following properties.
+%These sets, illustrated in Fig.~\ref{fig:exmProjections}, satisfy the following properties.
+%
+%\begin{figure}[t]
+%	\centerline{
+%	\begin{overpic}[scale=.5]{exmProjections}
+%			\put(30,6){$\longleftarrow$}
+%			\put(31,8){$\projDown$}
+%			\put(68,6){$\longrightarrow$}
+%			\put(69,8){$\projUp$}
+%			\put(12,-3){$\projDown(S)$}
+%			\put(50,-3){$S$}
+%			\put(85,-3){$\projUp(S)$}
+%	\end{overpic}
+%	}
+%	\vspace{.3cm}
+%	\caption{A biclosed set of strings~$S$ (middle) with~$\projDown(S)$ (left) and~$\projUp(S)$~(right).
+For readibility, $\projUp(S)$ is only partially drawn: the remaining strings are obtained by adding independently the two dotted arrows to all strings containing their left endpoint.}
+%	\label{fig:exmProjections}
+%\end{figure}
 
@@
 For example, if~$\bar Q$ is an oriented path with no relation, $\equiv$ is a Cambrian congruence of the weak~order~\cite{Reading-CambrianLattices}.
-The congruence classes of~$\equiv$ appear as blue rectangles~in~Figure~\ref{fig:exmLatticeQuotient}.
+The congruence classes of~$\equiv$ appear as blue rectangles~in~Fig.~\ref{fig:exmLatticeQuotient}.
 
@@
 
-Coming back to our original problem, we now aim to show that the increasing flip graph on non-kissing facets is isomorphic to the Hasse diagram of the quotient of the lattice of biclosed set~$\Bicl{\bar Q}$ of Section~\ref{subsec:biclosedSets} by the lattice congruence of Section~\ref{subsec:congruence}.
-The next two propositions provide explicit maps between biclosed sets of strings and non-kissing facets illustrated in Figure~\ref{fig:exmSurjection}.
-It extends previous definitions of~\cite{McConville} for grid quivers.
+Coming back to our original problem, we now aim to show that the increasing flip graph on non-kissing facets is isomorphic to the Hasse diagram of the quotient of the lattice of biclosed set~$\Bicl{\bar Q}$ of Sec.~\ref{subsec:biclosedSets} by the lattice congruence of Sec.~\ref{subsec:congruence}.
+The next two propositions provide explicit maps between biclosed sets of strings and non-kissing facets illustrated in Fig.~\ref{fig:exmSurjection}.
+These maps extend previous definitions of~\cite{McConville} for grid quivers.
 
@@
 
+\vspace{-.5cm}
+
 \begin{proposition}
-For any facet~$F \in \NKC$, the set~$\zeta(F) \eqdef \displaystyle\closure{\Big( \bigcup\limits_{\omega \in F} \Sigma_\bottom(\omega) \Big)}
+For any facet~$F \in \NKC$, the set of strings~$\zeta(F) \! \eqdef \! \displaystyle\closure{\Big( \!\!\bigcup\limits_{\omega \in F} \! \Sigma_\bottom(\omega) \! \Big)}
 $~is~biclosed.
@@
 
+\vspace{-.2cm}
 When the quiver is an oriented path with no relation, the map~$\eta$ should be thought of as the map from permutations to triangulations defined in~\cite{Reading-CambrianLattices}.
@@
 \begin{figure}[b]
-	\vspace{-.3cm}
 	\centerline{
@@
 	}
-	\vspace{.4cm}
+	\vspace{.5cm}
 	\caption{The maps~$\eta$ (left) and $\zeta$ (right) between non-kissing facets and biclosed sets.}
@@
 
+\vspace{-.1cm}
 To conclude, we characterize which subsets of strings correspond to canonical join representations in the non-kissing lattice~$\NKL$.
@@
 \begin{theorem}
-The following assertions are equivalent for a set~$\Sigma$ of distinguishable strings~of~$\bar Q$:
+The following assertions are equivalent for a set~$\Sigma$ of distinguishable strings of~$\bar Q$:
 \begin{compactitem}
@@
 In this section, we provide polyhedral realizations for finite non-kissing complexes, using tools inspired from the finite type cluster algebras of S.~Fomin and A.~Zelevinsky~\cite{FominZelevinsky-ClusterAlgebrasII}.
+\vspace{-.2cm}
 
@@
 Consider a bending walk~$\omega$ in a facet~$F \in \RNKC$.
-By Proposition~\ref{prop:distinguishedArrows}, $\omega$ has two~distinguished arrows~$\distinguishedArrows{\omega}{F}$ around its distinguished string~$\distinguishedString{\omega}{F}$.
-\mbox{The \defn{$\b{c}$-vector} of~$\omega \in F$} is the vector~${\cvector{\omega}{F} \eqdef \distinguishedSign{\omega}{F} \, \multiplicityVector_{\distinguishedString{\omega}{F}} \in \R^{Q_0}}$, where~$\distinguishedSign{\omega}{F} \eqdef 1$ if~${\distinguishedString{\omega}{F} \in \Sigma_\top(\omega)}$ and $\distinguishedSign{\omega}{F} \eqdef -1$ if~${\distinguishedString{\omega}{F} \in \Sigma_\bottom(\omega)}$.
+By Prop.~\ref{prop:distinguishedArrows}, $\omega$ has two distinguished arrows~$\distinguishedArrows{\omega}{F}$ surrounding its distinguished string~$\distinguishedString{\omega}{F}$.
+The \defn{$\b{c}$-vector} of~$\omega \in F$ is the vector~${\cvector{\omega}{F} \eqdef \distinguishedSign{\omega}{F} \, \multiplicityVector_{\distinguishedString{\omega}{F}} \in \R^{Q_0}}$, where~$\distinguishedSign{\omega}{F} \eqdef 1$ if~${\distinguishedString{\omega}{F} \in \Sigma_\top(\omega)}$ and $\distinguishedSign{\omega}{F} \eqdef -1$ if~${\distinguishedString{\omega}{F} \in \Sigma_\bottom(\omega)}$.
 Denote by~$\cvectors{F} \eqdef \set{\cvector{\omega}{F}}{\omega \in F}$.
@@
 	\caption{The $\b{g}$- and $\b{c}$-matrices of a facet~$F$ form dual bases.}
-	\vspace{-.7cm}
+	\vspace{-.5cm}
 	\label{fig:gcvectors}
@@
 We now use $\b{g}$- and~$\b{c}$-vectors to construct polyhedral realizations of finite non-kissing complexes.
-Since the $\b{g}$-vectors of the walks~$\omega, \omega', \mu, \nu$ involved in the flip of Figure~\ref{fig:kissingFlip} satisfy the linear dependence $\gvector{\omega} + \gvector{\omega'} = \gvector{\mu} + \gvector{\nu}$, we get the following~statement.
+Since the $\b{g}$-vectors of the walks~$\omega, \omega', \mu, \nu$ involved in the flip of Fig.~\ref{fig:kissingFlip} satisfy the linear dependence $\gvector{\omega} + \gvector{\omega'} = \gvector{\mu} + \gvector{\nu}$, we obtain the following~statement.
 
@@
 
-This fan is illustrated in Figure~\ref{fig:exmFans}\,(left).
+This fan is illustrated in Fig.~\ref{fig:exmFans}\,(left).
 Note that it was constructed in~\cite{MannevillePilaud-accordion} for dissection quivers and in~\cite{GarverMcConville-grid} for grid quivers.
@@
 The $\bar Q$-associahedron was constructed in~\cite{MannevillePilaud-accordion} in the special case of dissection quivers.
-An example of~$\Asso$ is shown in Figure~\ref{fig:exmFans}.
+An example of~$\Asso$ is shown in Fig.~\ref{fig:exmFans}.
 %The $\bar Q$-associahedron was constructed in~\cite{MannevillePilaud-accordion} in the special case of dissection quivers, generalizing the associahedra of C.~Hohlweg and C.~Lange~\cite{HohlwegLange} for path quivers with no relations.
-%An example of~$\Asso$ is illustrated in Figure~\ref{fig:exmFans}. 
+%An example of~$\Asso$ is illustrated in Fig.~\ref{fig:exmFans}. 
 For grid quivers, our construction proves the polytopality conjecture for the $\b{g}$-vector fan stated~in~\cite{GarverMcConville-grid}.
 
-This realization of the non-kissing complex has the following relevant property regarding the non-kissing lattice studied in Section~\ref{sec:nonkissinglattice}.
+This realization of the non-kissing complex has the following relevant property regarding the non-kissing lattice studied in Sec.~\ref{sec:nonkissinglattice}.
 

### 2020-06-29 firstPaper/exposeFPSAC1807/exposeFPSAC1807.tex
FPSAC

\documentclass[12pt,titlepage,landscape,a4paper]{article}

%QUELQUES PACKAGES PLUS OU MOINS UTILES
\special{landscape}
\usepackage[T1]{fontenc}
\usepackage[latin1]{inputenc}
\usepackage[english]{babel}
\usepackage{amsfonts, amsmath, amssymb, amsthm, stmaryrd}
\usepackage{aeguill}
\usepackage{graphics, graphicx}
\usepackage{xcolor}
\usepackage{geometry}
\usepackage{paralist}
\usepackage{multido,ifthen}
\usepackage{tikz}\usetikzlibrary{trees,shapes,arrows,matrix,calc,arrows.meta}
\usepackage{hyperref}
\usepackage{movie15}
\usepackage[abs]{overpic}
\usepackage{xargs}
\usepackage{extarrows}
\usepackage{shuffle}
\usepackage{multicol}
\usepackage{etoolbox}
\usepackage{dsfont}
\usepackage{pifont}
\usepackage{array, blkarray}
\usepackage{multicol, multirow}
\usepackage{ulem}
\usepackage{xifthen}

% ZONE DE TEXTE ET POLICE
\setlength{\topmargin}{-2.8cm}
\setlength{\textheight}{19cm}
\setlength{\oddsidemargin}{-1cm}
\setlength{\textwidth}{26.8cm}
\newcommand{\textenormal}{\fontsize{22}{28}\selectfont}
\newcommand{\textemoyen}{\fontsize{24}{27}\selectfont}
\newcommand{\textegrand}{\fontsize{55}{48}\selectfont}

% COMMANDE DE NOUVELLE PAGE
\newenvironment{slide}[1]
{
\newpage
\begin{center}
{\blue \textemoyen \uppercase{#1}}\\
\end{center}
\vspace{-1cm}
\rule{\textwidth}{0.5 pt}\\
\vspace{-.8cm}
}
{\vspace*{-3cm}}

% COMMANDE DE PARTIE
%\newcounter{partie}
%\setcounter{partie}{1}
%\newcommand{\thePartie}{Part \arabic{partie}}
\newcommand{\partie}[1]
{
\newpage
\vspace*{0pt plus 1 fill}
\begin{center}
%\thePartie \\[-.75cm]
\rule{.8\textwidth}{0.5 pt} \\[.5cm]
\fontsize{35}{35}\selectfont {\blue\uppercase{#1}} \\[-.35cm]
\rule{.8\textwidth}{0.5 pt} \\
\end{center}
\vspace*{0pt plus 1.2 fill}
%\addtocounter{partie}{1}
}

% COMMANDE D'EXPOSE
\newcommand{\expose}[2]
{
\newpage
\vspace*{0pt plus 1 fill}
\begin{center}
%\thePartie \\[-.75cm]
\rule{.8\textwidth}{0.5 pt} \\[.5cm]
\fontsize{35}{35}\selectfont {\red\uppercase{#1}} \\[-.35cm]
\rule{.8\textwidth}{0.5 pt} \\
\vspace{1cm}
\textemoyen #2
\end{center}
\vspace*{0pt plus 1.2 fill}
%\addtocounter{partie}{1}
}

% COMMANDE POUR LES BOITES
% centre
\newcommand{\cboite}[1]
{
\vspace*{.5cm}
\fcolorbox{blue}{grisclair}{
\begin{minipage}{.97\linewidth}
\vspace*{.3cm}
\begin{center} #1 \end{center}
\vspace*{-.1cm}
\end{minipage}
}
}
% alignement gauche
\newcommand{\gboite}[1]
{
\vspace*{.5cm}
\fcolorbox{blue}{grisclair}{
\begin{minipage}{.97\linewidth}
\vspace*{.3cm}
#1
\vspace{.3cm}
\end{minipage}
}
}

% AUTRES COMMANDES
% quelques couleurs manquantes
\newcommand{\orange}{\color{orange}} % couleur orange
\newcommand{\green}{\color{green}} % couleur verte
\newcommand{\violet}{\color{violet}} % couleur violet
\newcommand{\blue}{\color{blue}} % couleur bleu
\newcommand{\red}{\color{red}} % couleur rouge
\definecolor{violet}{rgb}{.5,.1,.9}
\definecolor{orange}{rgb}{.94,.57,0}
\definecolor{green}{rgb}{0.2,0.6,0.2}
\definecolor{grisclair}{gray}{1}
\definecolor{grisfonce}{gray}{.1}
\definecolor{bblue}{rgb}{.8,.8,1}
% maths
\newcommand{\set}[2]{\left\{ #1 \;\middle|\; #2 \right\}} % ensemble
\newcommand{\bigset}[2]{\big\{ #1 \;\big|\; #2 \big\}} % ensemble
\newcommand{\biggset}[2]{\bigg\{ #1 \;\bigg|\; #2 \bigg\}} % ensemble
\newcommand{\setangle}[2]{\left\langle #1 \;\middle|\; #2 \right\rangle} % ensemble
\newcommand{\dotprod}[2]{\left\langle\; #1 \;\middle|\; #2 \;\right\rangle} % produit scalaire
\newcommand{\ssm}{\smallsetminus} % small set minus
\newcommand{\symdif}{\triangle} % symmetric difference
\newcommand{\eqdef}{\mbox{\,\raisebox{0.3ex}{\normalsize\ensuremath{\mathrm:}}\ensuremath{=}\,}} % :=
\newcommand{\defeq}{\mbox{~\ensuremath{=}\raisebox{0.3ex}{\normalsize\ensuremath{\mathrm:}} }} % =:
\newcommand{\Fracfloor}[2]{\left\lfloor \frac{#1}{#2} \right\rfloor} % floor of a fraction
\newcommand{\one}{1\!\!1} % one bold
\DeclareMathOperator{\conv}{conv} % enveloppe convexe
\DeclareMathOperator{\cone}{cone} % cone engendre
\DeclareMathOperator{\vol}{vol} % volume
\newcommand{\C}{\mathbb{C}} % complexes
\newcommand{\R}{\mathbb{R}} % reels
\newcommand{\Z}{\mathbb{Z}} % entiers
\newcommand{\N}{\mathbb{N}} % naturels
\newcommand{\I}{\mathbb{I}} % set of integers
\newcommand{\K}{\mathbb{K}} % field
\newcommand{\fS}{\mathfrak{S}} % symmetric group
\newcommand{\cA}{\mathcal{A}} % algebra
\newcommand{\cF}{\mathcal{F}} % flip graph
\newcommand{\cN}{\mathcal{N}} % sorting network
\renewcommand{\b}[1]{\mathbf{#1}} % bold letters
\renewcommand{\c}[1]{\mathcal{#1}} % caligraphic letters
\newcommand{\f}[1]{\mathfrak{#1}} % frak letters
% autres
\setlength{\parindent}{0pt} % aucune indentation dans tout le document
\graphicspath{{figures/}} % les repertoires ou se trouvent les figures
\newcommand{\papier}[1]{\begin{flushright} {\violet \fontsize{15}{20}\selectfont #1} \end{flushright}} % citation papier
\newcommand{\theo}[2]{\gboite{{\blue \fontsize{18}{25}\selectfont #1.} #2}}
\newcommand{\HUGE}[1]{{\fontsize{35}{33}\selectfont #1}}
\newcommand{\esperluette}{ \\ --- \& --- \\ } % esperluette stylisée nouvelle ligne
\DeclareRobustCommand{\verylongrightarrow}{\joinrel\relbar\joinrel\relbar\joinrel\relbar\joinrel\relbar\joinrel\relbar\joinrel\rightarrow}
\renewcommand{\emph}[1]{{\blue #1}}

% POLYTOPES
\newcommand{\Asso}{\mathsf{Asso}} % associahedron
\newcommandx{\Brick}[2][1=k, 2=n]{\mathsf{Brick}^{#1}(#2)} % brick polytope
\newcommand{\Perm}{\mathsf{Perm}} % permutahedron
\newcommand{\Para}{\mathsf{Para}} % parallelepiped
\newcommandx{\Zono}{\mathsf{Zono}} % zonotope
\newcommand{\Hyp}{\b{H}^=} % hyperplane
\newcommand{\HS}{\b{H}^\ge} % half-space
\newcommand{\HH}{\mathbb{H}} % hyperplane
\newcommand{\Cone}{\mathrm{C}} % cone
\newcommand{\polar}{^\diamond} % polar
\newcommand{\vertex}[1]{\b{a}(#1)} % vertex corresponding to a maximal signed nested set
\newcommand{\face}[1]{\b{f}(#1)} % face corresponding to a signed nested set
\newcommand{\braidFan}{\mathcal{B\!F}} % braid fan
\newcommand{\secPoly}{\Sigma\mathsf{Poly}} % secondary polytope
\newcommand{\secFan}{\Sigma\mathsf{Fan}} % secondary fan
\newcommand{\rhs}[2]{\omega(#1, #2)} % right hand side of zonotope

% LATTICES
\newcommand{\meet}{\wedge} % meet
\newcommand{\join}{\vee} % join
\newcommand{\bigMeet}{\bigwedge} % meet
\newcommand{\bigJoin}{\bigvee} % join
\newcommand{\closure}[1]{#1^{\mathrm{cl}}} % closure operator
\newcommand{\coclosure}[1]{#1^{\mathrm{cocl}}} % coclosure operator
\newcommand{\Bicl}[1]{\mathsf{Bic}(#1)} % biclosed sets
\newcommand{\projDown}{\pi_\downarrow} % down projection map
\newcommand{\projUp}{\pi^\uparrow} % up projection map
\newcommand{\JI}{\mathsf{JI}} % join-irreducible
\newcommand{\MI}{\mathsf{MI}} % meet-irreducible
\newcommand{\Cong}{\mathsf{Cong}} % congruence lattice
\newcommand{\con}{\mathrm{con}} % congruence contracting a cover relation
\newcommand{\ji}{\mathsf{ji}} % join irreducible
\newcommand{\mi}{\mathsf{mi}} % meet irreducible
\newcommand{\Pos}{\mathrm{Pos}} % poset of regions

% NONKISSING COMPLEX
\newcommand{\blossom}{^\text{\ding{96}}} % blossom
\renewcommand{\top}{\mathrm{top}} % top
\newcommand{\bottom}{\mathrm{bot}} % bottom
\newcommandx{\NKC}[1][1=\bar Q]{\mathcal{NK}(#1)} % non-kissing complex
\newcommandx{\RNKC}[1][1=\bar Q]{\mathcal{NK}(#1)} % non-kissing complex
\newcommandx{\NKL}[1][1=\bar Q]{\mathcal{L}_{\mathrm{nk}}(#1)} % non-kissing lattice
\newcommand{\distinguishedWalk}[2]{\mathsf{dw}(#1,#2)} % distinguished walk
\newcommand{\distinguishedArrows}[2]{\mathsf{da}(#1,#2)} % distinguished arrows
\newcommand{\distinguishedString}[2]{\mathsf{ds}(#1,#2)} % distinguished string
\newcommand{\distinguishedSign}[2]{\varepsilon(#1,#2)} % distinguished sign
\newcommand{\peaks}[1]{\mathsf{peaks}(#1)} % peaks
\newcommand{\deeps}[1]{\mathsf{deeps}(#1)} % deeps
\newcommand{\kn}{\kappa} % kissing number
\newcommand{\KN}{\textsc{kn}} % Kissing Number
\newcommand{\gvector}{\b{g}} % g-vector
\newcommand{\gvectors}{\b{g}} % g-vectors
\newcommand{\gvectorFan}{\mathcal{F}^\b{g}} % g-vector fan
\newcommand{\cvector}{\b{c}} % c-vector
\newcommand{\cvectors}{\b{c}} % c-vectors
\newcommand{\allcvectors}[1]{\b{C}(#1)} % all c-vectors with respect to the initial cluster #1
\newcommand{\point}{\mathbf{p}} % vertex of the #1-associahedron corresponding to the cluster #2

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\titre}{More friends for the associahedron}
\newcommand{\auteur}{Vincent Pilaud}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\fontshape{sf}\fontsize{22}{28}\selectfont % police par defaut
\sf
\pagestyle{empty} % bas de page par defaut

%%%%%%%%%

\begin{flushright}
\vspace*{.3cm}

{\blue \fontsize{53}{50}\selectfont

NON-KISSING \\ COMPLEXES \\
FOR GENTLE \\ ALGEBRAS

}

\vspace{1.1cm}
\HUGE{Y. PALU} \\
Univ. Amiens

\vspace{1cm}
\HUGE{V. PILAUD} \\
CNRS \& LIX, \\ \'Ecole Poytechnique

\vspace{1cm}
\HUGE{P.-G. PLAMONDON} \\
Univ. Orsay

\end{flushright}

\vspace*{-18.5cm}%\hspace*{1cm}
\hspace*{-1.5cm}
\includegraphics[scale=1.43]{title}
\vspace*{-3cm}

%%%%%%%%%

%\expose{IV. NON-KISSING COMPLEXES \\ AND GENTLE ASSOCIAHEDRA}{\includegraphics[scale=.95]{justFans}}
%
%\vspace*{-.2cm}
%\papier{\textemoyen Palu--P.--Plamondon, \textit{Non-kissing complexes and $\tau$-tilting for gentle alg.}~('17$^+$)
%\vspace*{-.5cm}
%}

%%%%%%%%%

\partie{Non-kissing complex}

\vspace*{-1.5cm}
\papier{\textemoyen
	Petersen--Pylyavskyy--Speyer, \textit{A non-crossing standard monomial theory} ('10) \\
	Santos--Stump-Welker, \textit{Non-crossing sets and the Grassmann-assoc.} ('17) \\
	McConville, \textit{Lattice structures of grid Tamari orders} ('17) \\
	Garver--McConville, \textit{Enumerative properties of grid-associahedra} ('17$^+$) \\
	Palu--P.--Plamondon, \textit{Non-kissing complexes and $\tau$-tilting for gentle alg.}~('17$^+$) \\
	Br\"ustle--Douville--Mousavand--Thomas--Y\i{}ld\i{}r\i{}m, \textit{On the combinatorics of gentle algebras} ('17$^+$) \\
}

%%%%%%%%%

\begin{slide}{Gentle quivers and strings}

\hspace{-1cm}
\includegraphics[scale=1.3]{exmQuiver}

\vspace{-7cm}
\hspace{12cm}
\begin{minipage}{14cm}
\emph{gentle quiver} $\bar Q$ =
\begin{compactitem}
\item \emph{quiver}~$Q$ = oriented graph $(Q_0, Q_1, s, t)$ % \\ (loops and multiple edges allowed)
\item \emph{relations}~$I$ = forbid certain paths
\end{compactitem}
where
\begin{compactitem}
\item forbidden paths all of length~$2$ \\[-1.3cm]
\item locally at each vertex, subgraph of \raisebox{-.9cm}{\includegraphics[scale=.8]{localGentle}}
\end{compactitem}
\end{minipage}

\end{slide}

%%%%%%%%%

\begin{slide}{Gentle quivers and strings}

\hspace{-1cm}
\includegraphics[scale=1.3]{exmQuiver}

\vspace{-7cm}
\hspace{12cm}
\begin{minipage}{14cm}
\emph{gentle quiver} $\bar Q$ =
\begin{compactitem}
\item \emph{quiver}~$Q$ = oriented graph $(Q_0, Q_1, s, t)$ % \\ (loops and multiple edges allowed)
\item \emph{relations}~$I$ = forbid certain paths
\end{compactitem}
where
\begin{compactitem}
\item forbidden paths all of length~$2$ \\[-1.3cm]
\item locally at each vertex, subgraph of \raisebox{-.9cm}{\includegraphics[scale=.8]{localGentle}}
\end{compactitem}
\end{minipage}

\vspace{1cm}

\hspace{-1cm}
\includegraphics[scale=1.3]{exmString}

\vspace{-6cm}
\hspace{12cm}
\begin{minipage}{15cm}
\emph{string} $\sigma$ = 
\mbox{$\alpha_1^{\varepsilon_1} \dots \alpha_\ell^{\varepsilon_\ell}$ with $\alpha_k \in Q_1$, $\varepsilon_k \in \{-1,1\}$} \\
such that
\begin{compactitem}
\item $t(\alpha_k^{\varepsilon_k}) = s(\alpha_{k+1}^{\varepsilon_{k+1}})$
\item contains no factor~$\pi$ or~$\pi^{-1}$ for any path~$\pi \in I$
\item \mbox{contains no~$\alpha\alpha^{-1}$ or~$\alpha^{-1}\alpha$ for any arrow~$\alpha \in Q_1$}
\end{compactitem}
\end{minipage}

\end{slide}

%%%%%%%%%

\begin{slide}{Blossoming quivers and walks}

\hspace{-1cm}
\includegraphics[scale=1.3]{exmBlossomingQuiver}

\vspace{-5cm}
\hspace{12.5cm}
\begin{minipage}{14.5cm}
\emph{blossoming quiver} $\bar Q\blossom$ = \\[-.5cm]
add blossoms to complete each vertex to \raisebox{-.9cm}{\includegraphics[scale=.8]{localGentle}}
\end{minipage}

\end{slide}

%%%%%%%%%

\begin{slide}{Blossoming quivers and walks}

\hspace{-1cm}
\includegraphics[scale=1.3]{exmBlossomingQuiver}

\vspace{-5cm}
\hspace{12.5cm}
\begin{minipage}{14.5cm}
\emph{blossoming quiver} $\bar Q\blossom$ = \\[-.5cm]
add blossoms to complete each vertex to \raisebox{-.9cm}{\includegraphics[scale=.8]{localGentle}}
\end{minipage}

\vspace{4cm}

\hspace{-1cm}
\includegraphics[scale=1.3]{exmWalk}

\vspace{-6cm}
\hspace{12cm}
\begin{minipage}{13cm}
\emph{walk} $\omega$ = 
\begin{tabular}[t]{l}
maximal string in $\bar Q\blossom$ \\
from blossoms to blossoms
\end{tabular}
\end{minipage}

\end{slide}

%%%%%%%%%

\begin{slide}{Kissing or crossing}

\vspace{.5cm}
%Two walks~$\omega, \omega'$ with a common substring can either:\\[.5cm]
\centerline{KISS \hspace{6cm} or \hspace{5.5cm} CROSS}
\vspace{-1.3cm}
\centerline{\includegraphics[scale=2.5]{kissingCrossing}}

\vspace{1.5cm}
\centerline{\includegraphics[scale=1.3]{exmKissing1}\qquad\includegraphics[scale=1.3]{exmNonKissing1}}

\end{slide}

%%%%%%%%%

\begin{slide}{Non-kissing complex}

\vspace{.5cm}
%Two walks~$\omega, \omega'$ with a common substring can either:\\[.5cm]
\centerline{KISS \hspace{6cm} \phantom{or \hspace{5.5cm} CROSS}}
\vspace{-1.3cm}
\centerline{\includegraphics[scale=2.5]{kissing}}

\vspace{.5cm}
[reduced] \emph{non-kissing complex} $\NKC$ = % \\ simplicial complex with
\begin{compactitem}
\item vertices = [bending] walks in $\bar Q\blossom$ \\ (that are not self-kissing)
\item faces = collections of pairwise \\ non-kissing [bending] walks in $\bar Q\blossom$
\end{compactitem}

\vspace{.3cm}
\includegraphics[scale=1.3]{exmFacet}

\vspace{-17cm}\hspace{13cm}
\includegraphics[scale=1.1]{exmNKC}

\end{slide}

%%%%%%%%%

\begin{slide}{Simplicial associahedra are non-kissing complexes}

\vspace{.5cm}
[reduced] \emph{simplicial associahedron} = simplicial complex with
\begin{compactitem}
\item vertices = [internal] diagonals of an $(n+3)$-gon
\item faces = collections of pairwise non-crossing [internal] diagonals of the $(n+3)$-gon
\end{compactitem}

\vspace{1.5cm}
\centerline{\includegraphics[scale=3.5]{exmBijectionAssociahedron1}}

\end{slide}

%%%%%%%%%

\begin{slide}{Simplicial associahedra are non-kissing complexes}

\vspace{.5cm}
[reduced] \emph{simplicial associahedron} = simplicial complex with
\begin{compactitem}
\item vertices = [internal] diagonals of an $(n+3)$-gon
\item faces = collections of pairwise non-crossing [internal] diagonals of the $(n+3)$-gon
\end{compactitem}

\vspace{1.5cm}
\centerline{\includegraphics[scale=3.5]{exmBijectionAssociahedron2}}

\vspace{1cm}
\centerline{
\begin{tabular}{c@{\hspace{2cm}$\longleftrightarrow$\hspace{2cm}}c}
\hspace{3cm} diagonal \hspace{3cm} &  \hspace{3cm} walk \hspace{3cm} \\[2cm]
\end{tabular}
}

\end{slide}

%%%%%%%%%

\begin{slide}{Simplicial associahedra are non-kissing complexes}

\vspace{.5cm}
[reduced] \emph{simplicial associahedron} = simplicial complex with
\begin{compactitem}
\item vertices = [internal] diagonals of an $(n+3)$-gon
\item faces = collections of pairwise non-crossing [internal] diagonals of the $(n+3)$-gon
\end{compactitem}

\vspace{1.5cm}
\centerline{\includegraphics[scale=3.5]{exmBijectionAssociahedron3}}

\vspace{1cm}
\centerline{
\begin{tabular}{c@{\hspace{2cm}$\longleftrightarrow$\hspace{2cm}}c}
\hspace{3cm} diagonal \hspace{3cm} &  \hspace{3cm} walk \hspace{3cm} \\
crossing & kissing
\end{tabular}
}

\end{slide}

%%%%%%%%%

\begin{slide}{Simplicial associahedra are non-kissing complexes}

\vspace{.5cm}
[reduced] \emph{simplicial associahedron} = simplicial complex with
\begin{compactitem}
\item vertices = [internal] diagonals of an $(n+3)$-gon
\item faces = collections of pairwise non-crossing [internal] diagonals of the $(n+3)$-gon
\end{compactitem}

\vspace{1.5cm}
\centerline{\includegraphics[scale=3.5]{exmBijectionAssociahedron4}}

\vspace{1cm}
\centerline{
\begin{tabular}{c@{\hspace{2cm}$\longleftrightarrow$\hspace{2cm}}c}
\hspace{3cm} diagonal \hspace{3cm} &  \hspace{3cm} walk \hspace{3cm} \\
crossing & kissing \\
dissection & non-kissing face
\end{tabular}
}

\end{slide}

%%%%%%%%%

\begin{slide}{Simplicial associahedra are non-kissing complexes}

\vspace{.5cm}
[reduced] \emph{simplicial associahedron} = simplicial complex with
\begin{compactitem}
\item vertices = [internal] diagonals of an $(n+3)$-gon
\item faces = collections of pairwise non-crossing [internal] diagonals of the $(n+3)$-gon
\end{compactitem}

\vspace{1.5cm}
\centerline{\includegraphics[scale=3.5]{exmBijectionAssociahedron4}}

\vspace{1cm}
\centerline{
\begin{tabular}{c@{\hspace{2cm}$\longleftrightarrow$\hspace{2cm}}c}
\hspace{3cm} diagonal \hspace{3cm} &  \hspace{3cm} walk \hspace{3cm} \\
crossing & kissing \\
dissection & non-kissing face \\
simplicial associahedron & non-kissing complex
\end{tabular}
}

\vspace{.3cm}
\papier{McConville, \textit{Lattice structures of grid Tamari orders} ('17)}

\end{slide}

%%%%%%%%%%
%
%\begin{slide}{Simplicial associahedra are non-kissing complexes}
%
%\vspace{.5cm}
%[reduced] \emph{simplicial associahedron} = simplicial complex with
%\begin{compactitem}
%\item vertices = [internal] diagonals of an $(n+3)$-gon
%\item faces = collections of pairwise non-crossing [internal] diagonals of the $(n+3)$-gon
%\end{compactitem}
%
%\vspace{1.5cm}
%\centerline{\includegraphics[scale=3.5]{exmBijectionAssociahedron5}}
%
%\vspace{1.2cm}
%\papier{McConville, \textit{Lattice structures of grid Tamari orders} ('17)}
%
%\end{slide}
%
%%%%%%%%%%

\begin{slide}{Two more families of non-kissing complexes}

\vspace{.3cm}
\centerline{
\begin{tabular}{c@{\hspace{3cm}}c}
\includegraphics[scale=2]{exmDissection1} & \includegraphics[scale=.7]{exmGrid1} \\[.2cm]
dissection & subset of $\Z^2$
\end{tabular}
}

\end{slide}

%%%%%%%%%

\begin{slide}{Two more families of non-kissing complexes}

\vspace{.3cm}
\centerline{
\begin{tabular}{c@{\hspace{3cm}}c}
\includegraphics[scale=2]{exmDissection2} & \includegraphics[scale=.7]{exmGrid2} \\[.2cm]
dissection & subset of $\Z^2$
\end{tabular}
}

\end{slide}

%%%%%%%%%%
%
%\begin{slide}{Two more families of non-kissing complexes}
%
%\vspace{.3cm}
%\centerline{
%\begin{tabular}{c@{\hspace{3cm}}c}
%\includegraphics[scale=2]{exmDissection3t} & \includegraphics[scale=.7]{exmGrid3t} \\[.2cm]
%dissection & subset of $\Z^2$ \\[.5cm]
%\includegraphics[scale=2]{exmDissection3b} & \includegraphics[scale=.7]{exmGrid3b} \\[.2cm]
%dissection quiver & grid quiver
%\end{tabular}
%}
%
%\end{slide}
%
%%%%%%%%%%
%
%\begin{slide}{Two more families of non-kissing complexes}
%
%\vspace{.3cm}
%\centerline{
%\begin{tabular}{c@{\hspace{3cm}}c}
%\includegraphics[scale=2]{exmDissection4t} & \includegraphics[scale=.7]{exmGrid4t} \\[.2cm]
%accordion & $2457$ subset of $[n+m]$ \\[.5cm]
%\includegraphics[scale=2]{exmDissection4b} & \includegraphics[scale=.7]{exmGrid4b} \\[.2cm]
%walk & walk
%\end{tabular}
%}
%
%\end{slide}
%
%%%%%%%%%%
%
%\begin{slide}{Two more families of non-kissing complexes}
%
%\vspace{.3cm}
%\centerline{
%\begin{tabular}{c@{\hspace{3cm}}c}
%\includegraphics[scale=2]{exmDissection5t} & \includegraphics[scale=.7]{exmGrid5t} \\[.2cm]
%crossing accordions & crossing subsets of $[n+m]$ \\[.5cm]
%\includegraphics[scale=2]{exmDissection5b} & \includegraphics[scale=.7]{exmGrid5b} \\[.2cm]
%kissing walks & kissing walks
%\end{tabular}
%}
%
%\end{slide}

%%%%%%%%%

\begin{slide}{Two more families of non-kissing complexes}

\vspace{.3cm}
\centerline{
\begin{tabular}{c@{\hspace{3cm}}c}
\includegraphics[scale=2]{exmDissection5t} & \includegraphics[scale=.7]{exmGrid5t} \\[.2cm]
accordion complex & grid Tamari complex \\[.5cm]
\end{tabular}
}

\vspace{.2cm}
\papier{

\flushleft 
Baryshnikov, \textit{On Stokes sets} ('01) \\
Chapoton, \textit{Stokes posets and serpent nests} ('16) \\
Garver--McConville, \textit{Oriented flip graphs and non-crossing tree partitions} ('18) \\[1cm]
\flushright
	Petersen--Pylyavskyy--Speyer, \textit{A non-crossing standard monomial theory} ('10) \\
	Santos--Stump--Welker, \textit{Non-crossing sets and the Grassmann-assoc.} ('17) \\
	McConville, \textit{Lattice structures of grid Tamari orders} ('17) \\
	Garver--McConville, \textit{Enumerative properties of grid-associahedra} ('17$^+$) \\
}

\vspace{.3cm}
The associahedron is an example of both...

\end{slide}

%%%%%%%%%

\begin{slide}{Overview of the talk}

\emph{non-kissing complex} $\NKC$ = % \\ simplicial complex with
\begin{compactitem}
\item vertices = walks in $\bar Q\blossom$ (that are not self-kissing)
\item faces = collections of pairwise non-kissing walks in $\bar Q\blossom$
\end{compactitem}

\vspace{-3cm}
\hspace{18cm}
\includegraphics[scale=2]{kissing}

\vspace{-.3cm}
\emph{... generalizing the associahedron}

\vspace{.9cm}
\centerline{
\begin{tabular}{ccc}
Flip graph &
Associahedron &
Tamari lattice \\[.3cm]
\includegraphics[scale=.7]{exmFlipGraph} &
\includegraphics[scale=.7]{exmAssociahedron} & 
\includegraphics[scale=.7]{exmLattice} \\
\end{tabular}
}

\end{slide}

%%%%%%%%%

\partie{Distinguished arrows and flips}

\vspace*{-1.5cm}
\papier{\textemoyen
	McConville, \textit{Lattice structures of grid Tamari orders} ('17) \\
	Palu--P.--Plamondon, \textit{Non-kissing complexes and $\tau$-tilting for gentle alg.}~('17$^+$) \\
}

%%%%%%%%%

\begin{slide}{Distinguished walks, arrows and strings}

\vspace{1cm}
\includegraphics[scale=1.3]{exmFacet}

\vspace{-8.2cm}
\hspace{14cm}
\begin{minipage}{13cm}
$F$ face of $\NKC$ \\[.3cm]
\end{minipage}

\end{slide}

%%%%%%%%%

\begin{slide}{Distinguished walks, arrows and strings}

\vspace{1cm}
\includegraphics[scale=1.3]{exmCountercurrentOrder}

\vspace{-8.2cm}
\hspace{14cm}
\begin{minipage}{13cm}
$F$ face of $\NKC$ \\[.3cm]
${\red \alpha} \in Q_1$ \\
$F_{\red \alpha} = \set{\omega \in F}{{\red \alpha} \in \omega}$
\end{minipage}

\end{slide}

%%%%%%%%%

\begin{slide}{Distinguished walks, arrows and strings}

\vspace{1cm}
\includegraphics[scale=1.3]{exmCountercurrentOrder}

\vspace{-8.2cm}
\hspace{14cm}
\begin{minipage}{13cm}
$F$ face of $\NKC$ \\[.3cm]
${\red \alpha} \in Q_1$ \\
$F_{\red \alpha} = \set{\omega \in F}{{\red \alpha} \in \omega}$ \\[.3cm]
\includegraphics[scale=2.5]{crossing} \\[.1cm]
${\green \omega} \prec_{\red \alpha} {\blue \omega'}$ \emph{countercurrent order} at~${\red \alpha}$
\end{minipage}

\end{slide}

%%%%%%%%%

\begin{slide}{Distinguished walks, arrows and strings}

\vspace{1cm}
\includegraphics[scale=1.3]{exmDistinguishedArrow}

\vspace{-8.2cm}
\hspace{14cm}
\begin{minipage}{13cm}
$F$ face of $\NKC$ \\[.3cm]
${\red \alpha} \in Q_1$ \\
$F_{\red \alpha} = \set{\omega \in F}{{\red \alpha} \in \omega}$ \\[.3cm]
\includegraphics[scale=2.5]{crossing} \\[.1cm]
${\green \omega} \prec_\alpha {\blue \omega'}$ \emph{countercurrent order} at~${\red \alpha}$
\end{minipage}

\vspace{1cm}
\emph{distinguished walk} at~$\red \alpha$ in~$F$ = $\distinguishedWalk{{\red \alpha}}{F} = \max_{\prec_{\red \alpha}} F_{\red \alpha}$ \\
\emph{distinguished arrows} of~$\blue \omega$ in~$F$ = $\distinguishedArrows{{\blue \omega}}{F} = \set{{\red \alpha} \in Q_1}{{\blue \omega} = \distinguishedWalk{{\red \alpha}}{F}}$

\end{slide}

%%%%%%%%%

\begin{slide}{Distinguished walks, arrows and strings}

\vspace{1cm}
\includegraphics[scale=1.3]{exmDistinguished}

\vspace{-8.2cm}
\hspace{14cm}
\begin{minipage}{13cm}
$F$ face of $\NKC$ \\[.3cm]
${\red \alpha} \in Q_1$ \\
$F_{\red \alpha} = \set{\omega \in F}{{\red \alpha} \in \omega}$ \\[.3cm]
\includegraphics[scale=2.5]{crossing} \\[.1cm]
${\green \omega} \prec_\alpha {\blue \omega'}$ \emph{countercurrent order} at~${\red \alpha}$
\end{minipage}

\vspace{1cm}
\emph{distinguished walk} at~$\red \alpha$ in~$F$ = $\distinguishedWalk{{\red \alpha}}{F} = \max_{\prec_{\red \alpha}} F_{\red \alpha}$ \\
\emph{distinguished arrows} of~$\blue \omega$ in~$F$ = $\distinguishedArrows{{\blue \omega}}{F} = \set{{\red \alpha} \in Q_1}{{\blue \omega} = \distinguishedWalk{{\red \alpha}}{F}}$

\theo{PROP}{For any facet $F \in \NKC$, 
\begin{compactitem}
\item each bending walk of~$F$ contains $2$ distinguished arrows in~$F$ pointing opposite,
\item each straight walk of~$F$ contains $1$ distinguished arrows in~$F$ pointing as the walk.
\end{compactitem}
}

\end{slide}

%%%%%%%%%

\begin{slide}{Distinguished walks, arrows and strings}

\vspace{1cm}
\includegraphics[scale=1.3]{exmDistinguished}

\vspace{-8.2cm}
\hspace{14cm}
\begin{minipage}{13cm}
$F$ face of $\NKC$ \\[.3cm]
${\red \alpha} \in Q_1$ \\
$F_{\red \alpha} = \set{\omega \in F}{{\red \alpha} \in \omega}$ \\[.3cm]
\includegraphics[scale=2.5]{crossing} \\[.1cm]
${\green \omega} \prec_\alpha {\blue \omega'}$ \emph{countercurrent order} at~${\red \alpha}$
\end{minipage}

\vspace{1cm}
\emph{distinguished walk} at~$\red \alpha$ in~$F$ = $\distinguishedWalk{{\red \alpha}}{F} = \max_{\prec_{\red \alpha}} F_{\red \alpha}$ \\
\emph{distinguished arrows} of~$\blue \omega$ in~$F$ = $\distinguishedArrows{{\blue \omega}}{F} = \set{{\red \alpha} \in Q_1}{{\blue \omega} = \distinguishedWalk{{\red \alpha}}{F}}$

\theo{PROP}{For any facet $F \in \NKC$, 
\begin{compactitem}
\item each bending walk of~$F$ contains $2$ distinguished arrows in~$F$ pointing opposite,
\item each straight walk of~$F$ contains $1$ distinguished arrows in~$F$ pointing as the walk.
\end{compactitem}
}

\theo{CORO}{$\NKC$ is pure of dimension $|Q_0|$.}
\end{slide}

%%%%%%%%%

\begin{slide}{Flips}

\vspace{1cm}
\includegraphics[scale=1.3]{exmFlip0}

\vspace{1cm}
$F$ facet of $\NKC$ (ie. maximal collection of pairwise non-kissing walks)

\end{slide}

%%%%%%%%%

\begin{slide}{Flips}

\vspace{1cm}
\includegraphics[scale=1.3]{exmFlip1}

\vspace{1cm}
$F$ facet of $\NKC$ (ie. maximal collection of pairwise non-kissing walks) \\
${\red \omega} \in F$ we want to ``flip'' \\
\\
\\
\\
\\
\\

\vspace{-4.5cm}
\hspace{6.87cm}
\centerline{\includegraphics[scale=3]{flip1}}

\end{slide}

%%%%%%%%%

\begin{slide}{Flips}

\vspace{1cm}
\includegraphics[scale=1.3]{exmFlip2}

\vspace{1cm}
$F$ facet of $\NKC$ (ie. maximal collection of pairwise non-kissing walks) \\
${\red \omega} \in F$ we want to ``flip'' \\
$\{\alpha, \beta\} = \distinguishedArrows{\omega}{F}$ \\
\\
\\
\\
\\

\vspace{-4.5cm}
\hspace{6.87cm}
\centerline{\includegraphics[scale=3]{flip2}}

\end{slide}

%%%%%%%%%

\begin{slide}{Flips}

\vspace{1cm}
\includegraphics[scale=1.3]{exmFlip3}

\vspace{1cm}
$F$ facet of $\NKC$ (ie. maximal collection of pairwise non-kissing walks) \\
${\red \omega} \in F$ we want to ``flip'' \\
$\{\alpha, \beta\} = \distinguishedArrows{\omega}{F}$ \\
$\alpha', \beta' \in Q_1$ such that~$\alpha'\alpha \in I$ and $\beta'\beta \in I$ \\
\\
\\
\\

\vspace{-4.5cm}
\hspace{6.87cm}
\centerline{\includegraphics[scale=3]{flip3}}

\end{slide}

%%%%%%%%%

\begin{slide}{Flips}

\vspace{1cm}
\includegraphics[scale=1.3]{exmFlip4}

\vspace{1cm}
$F$ facet of $\NKC$ (ie. maximal collection of pairwise non-kissing walks) \\
${\red \omega} \in F$ we want to ``flip'' \\
$\{\alpha, \beta\} = \distinguishedArrows{\omega}{F}$ \\
$\alpha', \beta' \in Q_1$ such that~$\alpha'\alpha \in I$ and $\beta'\beta \in I$ \\
${\green \mu} = \distinguishedWalk{\alpha'}{F}$ and ${\blue \nu} = \distinguishedWalk{\beta'}{F}$ \\
${\red \omega} = {\blue \nu}[ \cdot, v ] \, \sigma \, {\green \mu}[w, \cdot]$ \\
\\

\vspace{-4.5cm}
\hspace{6.87cm}
\centerline{\includegraphics[scale=3]{flip4}}

\end{slide}

%%%%%%%%%

\begin{slide}{Flips}

\vspace{1cm}
\includegraphics[scale=1.3]{exmFlip5}

\vspace{1cm}
$F$ facet of $\NKC$ (ie. maximal collection of pairwise non-kissing walks) \\
${\red \omega} \in F$ we want to ``flip'' \\
$\{\alpha, \beta\} = \distinguishedArrows{\omega}{F}$ \\
$\alpha', \beta' \in Q_1$ such that~$\alpha'\alpha \in I$ and $\beta'\beta \in I$ \\
${\green \mu} = \distinguishedWalk{\alpha'}{F}$ and ${\blue \nu} = \distinguishedWalk{\beta'}{F}$ \\
${\red \omega} = {\blue \nu}[ \cdot, v ] \, \sigma \, {\green \mu}[w, \cdot]$ \\
${\orange \omega'} = {\green \mu}[ \cdot, v ] \, \sigma \, {\blue \nu}[w, \cdot]$ \\

\vspace{-4.5cm}
\hspace{6.87cm}
\centerline{\includegraphics[scale=3]{flip5}}

\end{slide}

%%%%%%%%

\begin{slide}{Flips}

\vspace{1cm}
\includegraphics[scale=1.3]{exmFlip5}

\vspace{1cm}
\theo{PROP}{$\omega'$ kisses $\omega$ but no other walk of $F$. Moreover, $\omega'$ is the only such walk.}

\vspace{1.3cm}
%\hspace{6.87cm}
\centerline{\includegraphics[scale=3]{flip}}

\end{slide}

%%%%%%%%

\begin{slide}{Flips}

\vspace{5cm}
\emph{flip graph} = 
\begin{compactitem}
\item vertices = non-kissing facets
\item edges = flips
\end{compactitem}

\vspace{-8cm}
\hspace{12cm}
\includegraphics[scale=1]{exmFlipGraph}

\end{slide}

%%%%%%%%%

%\begin{slide}{GOAL \& MOTIVATIONS}
%
%\theo{WHAT}{Understand the (increasing) flip graph:
%\begin{compactitem}
%\item vertices = non-kissing facets
%\item edges = (increasing) flips \\[.4cm]
%\centerline{\includegraphics[scale=2]{flip}}
%\end{compactitem}
%}
%
%\vspace{.5cm}
%\theo{WHY}{Several motivations
%\begin{compactitem}
%\item contains the associahedron
%\item usual questions on flip graphs (polytope, lattice, diameter, \dots)
%\item special case of support $\tau$-tilting complex over an associative algebra
%\end{compactitem}
%}
%
%\end{slide}

%%%%%%%%%

\partie{gentle associahedra}

\vspace{-1cm}
\papier{\textemoyen
	Manneville--P., \textit{Geometric realizations of the accordion complex} ('17$^+$) \\
	 Hohlweg--P.--Stella, Polytopal realizations of finite type g-vector fans ('17$^+$) \\
	Palu--P.--Plamondon, \textit{Non-kissing complexes and $\tau$-tilting for gentle alg.} ('17$^+$) \\}

%%%%%%%%%%

\begin{slide}{$\b{g}$-vectors \& $\b{c}$-vectors}

\vspace{.3cm}
\emph{multiplicity vector} $\b{m}_V$ of multiset~$V = \{\{v_1, \dots, v_m\}\}$ of~$Q_0$ \; = \; $\sum\limits_{i \in [m]} \b{e}_{v_i} \; \in \; \R^{Q_0}$

\vspace{-.1cm}
\emph{$\b{g}$-vector} $\gvector(\omega)$ of a walk~$\omega$ \; = \; $\b{m}_{\peaks{\omega}} - \b{m}_{\deeps{\omega}}$

\vspace{.3cm}
\emph{$\b{c}$-vector} $\cvector(\omega \in F)$ of a walk~$\omega$ in a non-kissing facet~$F$ \; = \; $\distinguishedSign{\omega}{F} \, \b{m}_{\distinguishedString{\omega}{F}}$

\vspace{.5cm}
\centerline{$\raisebox{-4cm}{\includegraphics[scale=1.3]{exmVectors}}$ \quad \input{figures/gcmatrices}}

\vspace{.5cm}
\centerline{
\begin{tabular}{c@{\hspace{3cm}}c@{\hspace{3cm}}cl}
& & $\swarrow \raisebox{.3cm}{$\distinguishedArrows{\omega}{F}$} \searrow$ & \\[-.3cm]
peak & \raisebox{-.8cm}{\includegraphics{deep}} & \includegraphics{distinguishedSubstringOut} & $\distinguishedSign{\omega}{F} = 1$ \\[-.3cm]
\raisebox{-.5cm}{\includegraphics{peak}} & deep & \includegraphics{distinguishedSubstringIn} & $\distinguishedSign{\omega}{F} = -1$ \\[-.3cm]
& & $\distinguishedString{\omega}{F}$ &
\end{tabular}
}

\end{slide}

%%%%%%%%%%

\begin{slide}{$\b{g}$-vectors \& $\b{c}$-vectors}

\vspace{.3cm}
\emph{multiplicity vector} $\b{m}_V$ of multiset~$V = \{\{v_1, \dots, v_m\}\}$ of~$Q_0$ \; = \; $\sum\limits_{i \in [m]} \b{e}_{v_i} \; \in \; \R^{Q_0}$

\vspace{-.1cm}
\emph{$\b{g}$-vector} $\gvector(\omega)$ of a walk~$\omega$ \; = \; $\b{m}_{\peaks{\omega}} - \b{m}_{\deeps{\omega}}$

\vspace{.3cm}
\emph{$\b{c}$-vector} $\cvector(\omega \in F)$ of a walk~$\omega$ in a non-kissing facet~$F$ \; = \; $\distinguishedSign{\omega}{F} \, \b{m}_{\distinguishedString{\omega}{F}}$

\vspace{.5cm}
\centerline{$\raisebox{-4cm}{\includegraphics[scale=1.3]{exmVectors}}$ \quad \input{figures/gcmatrices}}

\vspace{.2cm}
\theo{PROP}{For any non-kissing facet~$F$, the sets of vectors

\vspace{-.8cm}
\[
\gvectors(F) \eqdef \set{\gvector(\omega)}{\omega \in F}
\qquad\text{and}\qquad
\cvectors(F) \eqdef \set{\cvector(\omega \in F)}{\omega \in F}
\]

\vspace{-.1cm}
form dual bases.

\vspace{-.5cm}
\papier{Palu--P.--Plamondon, \textit{Non-kissing complexes and $\tau$-tilting for gentle algebras} ('17$^+$)}
\vspace{-.6cm}
}
\end{slide}

%%%%%%%%%%

\begin{slide}{$\b{g}$-vector fan}

\hspace{10.2cm}
\begin{minipage}{16cm}
\theo{THM}{For any gentle quiver~$\bar Q$, the collection of cones

\vspace{-.8cm}
\[
\gvectorFan(\bar Q) \eqdef \bigset{\R_{\ge0} \gvectors(F)}{F \in \NKC}
\]

\vspace{-.1cm}
forms a compl.\,simpl.\,fan, called \emph{$\b{g}$-vector fan} of~$\bar Q$. \\[-.8cm]
}
\end{minipage}

\vspace{-3.8cm}
\hspace{-1cm}
\includegraphics[scale=1.2]{exmFan}
\hspace{.1cm}
\raisebox{6cm}{
\begin{minipage}{10cm} \begin{center} stereographic projection \\ from $(1,1,1)$ \\[.5cm] \includegraphics[scale=.18]{stereographicProjection} \end{center} \end{minipage}
}

\end{slide}

%%%%%%%%%%%
%
%\begin{slide}{$\b{g}$-vector fan}
%
%\vspace{.5cm}
%\centerline{\includegraphics[scale=1]{exmFans}}
%
%\end{slide}
%
%%%%%%%%%%%

\begin{slide}{non-kissing associahedron}

\vspace{.2cm}
\emph{kissing number} $\KN(\omega) \; = \; \displaystyle{\sum_{\omega'}}$ number of times $\omega$ and $\omega'$ kiss \\
%\emph{kissing number} \(\KN(\omega) \; = \; \displaystyle{\sum_{\omega'} \kn(\omega,\omega') + \kn(\omega',\omega)}\)

\vspace{-.2cm}
\theo{THM}{
For a gentle quiver~$\bar Q$ with finite non-kissing complex~$\NKC$, \\
\begin{minipage}{14cm}
the two sets of~$\R^{Q_0}$ given by
\begin{enumerate}[(i)]
\item the convex hull of the points
\[
\point(F) \eqdef \sum_{\omega \in F} \KN(\omega) \, \cvector(\omega \in F),
\]
for all non-kissing facets~${F \in \NKC}$,

\item the intersection of the halfspaces
\[
\HS(\omega) \eqdef \set{\b{x} \in \R^{Q_0}}{\dotprod{\gvector(\omega)}{\b{x}} \le \KN(\omega)}.
\]
for all walks~$\omega$ of~$\bar Q$,
\end{enumerate}
\end{minipage}
\qquad
$\raisebox{-5.2cm}{\includegraphics[scale=.9]{exmAssociahedron}}$
\\[.1cm]
define the same polytope, whose normal fan is the $\b{g}$-vector fan~$\gvectorFan$.
We call it the \emph{$\bar Q$-associahedron} and denote it by~$\Asso$.

\vspace{-.3cm}
\papier{Palu--P.--Plamondon, \textit{Non-kissing complexes and $\tau$-tilting for gentle algebras} ('17$^+$)}
\vspace{-.6cm}
}

\end{slide}

%%%%%%%%%%%
%
%\begin{slide}{non-kissing associahedron}
%
%\vspace{2cm}
%\centerline{\includegraphics[scale=1]{exmGentleAssociahedra}}
%
%\end{slide}
%
%%%%%%%%%%%
%
%\begin{slide}{non-kissing associahedron vs zonotopes}
%
%\vspace{2cm}
%\centerline{\includegraphics[scale=1]{exmPermutahedra}}
%
%\end{slide}
%
%%%%%%%%%%

\partie{Non-kissing lattice}

\vspace{-.5cm}
\papier{\textemoyen
	McConville, \textit{Lattice structures of grid Tamari orders} ('17) \\
	Palu--P.--Plamondon, \textit{Non-kissing complexes and $\tau$-tilting for gentle alg.} ('17$^+$) \\}

%%%%%%%%%%

\begin{slide}{non-kissing lattice}

%\vspace{.2cm}
\theo{THM}{
For a gentle quiver~$\bar Q$ with finite non-kissing \\ complex~$\NKC$, the non-kissing flip graph \\ is the Hasse diagram of a \\ congruence-uniform lattice.

\vspace{1cm}
\hspace{.5cm}
\includegraphics[scale=2.5]{orientationFlip}

\vspace{-15.6cm}
\hspace{6cm}
\centerline{\includegraphics[scale=1]{exmLattice}}

\vspace{-.5cm}
\papier{Palu--P.--Plamondon, \textit{Non-kissing complexes and $\tau$-tilting for gentle algebras} ('17$^+$)}
\vspace{-.6cm}
}

\end{slide}

%%%%%%%%%%

\begin{slide}{lattice quotients}

\vspace{.5cm}
\emph{lattice} \; = \; poset $(L,\le)$ with a meet~$\meet$ and a join~$\join$

\vspace{.5cm}
\emph{lattice congruence} \; = \; equiv. rel.~$\equiv$ on~$L$ which respects meets and joins
\[
x \equiv x' \quad\text{and}\quad y \equiv y'\qquad\Longrightarrow\qquad x \meet y \equiv x' \meet y' \quad\text{and}\quad x \join y \equiv x' \join y'
\]

\vspace{.3cm}
\emph{lattice quotient} of~$L/{\equiv}$ \; = \; lattice on equiv. classes of~$L$ under~$\equiv$ where
\begin{compactitem}
\item $X \le Y \qquad \iff \qquad \exists x \in X, \; y \in Y, \quad x \le y$
\item $X \meet Y$ \; = \; equiv. class of~$x \meet y$ for any~$x \in X$ and~$y \in Y$
\item $X \join Y$ \; = \; equiv. class of~$x \join y$ for any~$x \in X$ and~$y \in Y$
\end{compactitem}

\vspace{1cm}
\centerline{\includegraphics[scale=1.7]{latticeQuotient}}

\end{slide}

%%%%%%%%%%%
%
%\begin{slide}{exm: Tamari lattice as lattice quotient of weak order}
%
%\vspace{.3cm}
%\emph{binary search tree insertion} of $2751346$ \\[.2cm]
%\centerline{\includegraphics[width=.9\textwidth]{bstinsertion}}
%%\emph{binary search tree insertion} of $2751346$ \\[.5cm]
%%\centerline{\includegraphics[width=.9\textwidth]{exmSurjectionPermutation3}}
%
%\end{slide}
%
%%%%%%%%%%

\begin{slide}{exm: Tamari lattice as lattice quotient of weak order}

\vspace{.5cm}
\centerline{\includegraphics[scale=1.3]{weakorder} \qquad \includegraphics[scale=1]{TamariLattice}}

\vspace{.3cm}
\emph{binary search tree insertion} of $2751346$ \\[.2cm]
\centerline{\includegraphics[width=.9\textwidth]{bstinsertion}}
%\emph{binary search tree insertion} of $2751346$ \\[.5cm]
%\centerline{\includegraphics[width=.9\textwidth]{exmSurjectionPermutation3}}

\end{slide}

%%%%%%%%%%

\begin{slide}{non-kissing lattice}

%\vspace{.3cm}
%\theo{THM}{The map $\eta$ defines a lattice morphism from biclosed sets to non-kissing facets.}

\vspace{.5cm}
\centerline{\includegraphics[scale=1]{exmLatticeQuotient}}

\end{slide}

%%%%%%%%%%

\begin{slide}{biclosed sets of strings}

$\sigma, \tau$ oriented strings \\
\emph{concatenation} $\sigma \circ \tau = \set{\sigma \alpha \tau}{\alpha \in Q_1 \text{ and } \sigma\alpha\tau \text{ string of } \bar Q}$

%\vspace{.5cm}
%$S,T$ sets of unoriented strings \\
%\emph{concatenation} $S \circ T = \displaystyle \bigcup_{\sigma \in S, \tau \in T} \sigma \circ \tau$ = 
%\begin{tabular}[t]{l} all strings obtained by concatenation \\ of a string of~$S$ with a string of~$T$ \end{tabular}

\vspace{.6cm}
\emph{closure} $\closure{S} = \displaystyle \bigcup_{\substack{\ell \in \N \\ \sigma_1, \dots, \sigma_\ell \in S}} \sigma_1 \circ \dots \circ \sigma_\ell$ = \begin{tabular}[t]{l} all strings obtained by concatenation \\ of some strings of~$S$ \end{tabular}

\vspace{.6cm}
\emph{closed} $\iff$ $\closure{S} = S$ \qquad \emph{coclosed} $\iff$ $\closure{\bar S} = \bar S$ \qquad \emph{biclosed} = closed and coclosed

\vspace{.5cm}
\centerline{\includegraphics[scale=1]{exmBiclosed}}

\vspace{.7cm}
\theo{THM}{For any gentle quiver~$\bar Q$ such that~$\NKC$ is finite, the inclusion poset on biclosed sets of strings of~$\bar Q$ is a congruence-uniform lattice.}

\vspace{.3cm}
\papier{McConville, \textit{Lattice structures of grid Tamari orders} ('17) \\
Garver--McConville, \textit{Oriented flip graphs and non-crossing tree partitions} ('17$^+$) \\
Palu--P.--Plamondon, \textit{Non-kissing complexes and $\tau$-tilting for gentle algebras} ('17$^+$) \\}

\end{slide}

%%%%%%%%%%

\multido{\n=1+1}{11}{%
\begin{slide}{non-kissing insertion}
\\[.5cm]
Surjection from biclosed sets of strings to non-kissing facets
\\[1cm]
\centerline{\includegraphics[scale=1]{exmSurjection\n}}
\\[.5cm]
$S$ biclosed, $\alpha \in Q_1$ \\
$\omega(\alpha,S)$ = \begin{tabular}[t]{@{}l} walk constructed with the local rules: \\ \includegraphics[scale=1.2]{localRulesSurjection} \end{tabular}
\\[.2cm]
\papier{McConville, \textit{Lattice structures of grid Tamari orders} ('17)}
\end{slide}
}

%%%%%%%%%%

\begin{slide}{non-kissing insertion}
\\[.5cm]
Surjection from biclosed sets of strings to non-kissing facets
\\[1cm]
\centerline{\includegraphics[scale=1]{exmSurjection12}}
\\[1cm]
\theo{PROP}{$\eta(S) \eqdef \set{\omega(\alpha,S)}{\alpha \in Q_1}$ is a non-kissing facet.} \\
%\theo{THM}{The map $\eta$ defines a lattice morphism from biclosed sets to non-kissing facets.}
\\[2.6cm]
\papier{McConville, \textit{Lattice structures of grid Tamari orders} ('17)}
\end{slide}

%%%%%%%%%%
%
%\begin{slide}{exm: binary search tree insertion again}
%
%\vspace{.5cm}
%\emph{inversion set} of $2751346$
%
%\vspace{.5cm}
%\centerline{\includegraphics[scale=1.2]{exmSurjectionPermutation1}}
%
%\end{slide}
%
%%%%%%%%%%
%
%\begin{slide}{exm: binary search tree insertion again}
%
%\vspace{.5cm}
%\emph{inversion set} of $2751346$
%
%\vspace{.5cm}
%\centerline{\includegraphics[scale=1.2]{exmSurjectionPermutation2}}
%
%\end{slide}
%
%%%%%%%%%%

\begin{slide}{exm: binary search tree insertion again}

\vspace{.5cm}
\emph{inversion set} of $2751346$

\vspace{.5cm}
\centerline{\includegraphics[scale=1.2]{exmSurjectionPermutation2}}

\vspace{.8cm}
\centerline{\includegraphics[scale=.9]{exmSurjectionPermutation3}}

\end{slide}

%%%%%%%%%%

\begin{slide}{non-kissing insertion}
\\[.5cm]
Surjection from biclosed sets of strings to non-kissing facets
\\[1cm]
\centerline{\includegraphics[scale=1]{exmSurjection12}}
\\[1cm]
\theo{PROP}{$\eta(S) \eqdef \set{\omega(\alpha,S)}{\alpha \in Q_1}$ is a non-kissing facet.} \\
\theo{THM}{The map $\eta$ defines a lattice morphism from biclosed sets to non-kissing facets.}
\\[1.45cm]
\papier{McConville, \textit{Lattice structures of grid Tamari orders} ('17)}
\end{slide}

%%%%%%%%%%

\begin{slide}{non-kissing lattice}

%\vspace{.3cm}
%\theo{THM}{The map $\eta$ defines a lattice morphism from biclosed sets to non-kissing facets.}

\vspace{.5cm}
\centerline{\includegraphics[scale=1]{exmLatticeQuotient}}

\end{slide}

%%%%%%%%%%

\begin{slide}{non-kissing lattice}

\vspace{.2cm}
\theo{THM}{
For a gentle quiver~$\bar Q$ with finite non-kissing complex~$\NKC$, the non-kissing flip graph is the Hasse diagram of a congruence-uniform lattice.

\vspace{-.5cm}
\papier{Palu--P.--Plamondon, \textit{Non-kissing complexes and $\tau$-tilting for gentle algebras} ('17$^+$)}
\vspace{-.6cm}
}

\vspace{.5cm}
Much more nice combinatorics:
\begin{compactitem}
\item \emph{join-irreducible elements} of~$\NKL$ are in bijection with distinguishable strings
\item \emph{canonical join complex} of~$\NKL$ is a generalization of \emph{non-crossing partitions}
\end{compactitem}

\centerline{\includegraphics[scale=1]{exmNFC}}

\end{slide}

%%%%%%%%%
%
%\newpage
%\phantomsection\label{thanks}
%
%\includegraphics[scale=1.65]{title}
%
%\vspace*{-9cm}\hspace{19.5cm}
%{\blue \textegrand THANKS}
%

%%%%%%%%%

\begin{slide}{Summary}

\emph{non-kissing complex} $\NKC$ = % \\ simplicial complex with
\begin{compactitem}
\item vertices = walks in $\bar Q\blossom$ (that are not self-kissing)
\item faces = collections of pairwise non-kissing walks in $\bar Q\blossom$
\end{compactitem}

\vspace{-3cm}
\hspace{18cm}
\includegraphics[scale=2]{kissing}

\vspace{-.3cm}
\emph{... generalizing the associahedron}

\vspace{.9cm}
\centerline{
\begin{tabular}{ccc}
Flip graph &
Associahedron &
Tamari lattice \\[.3cm]
\includegraphics[scale=.7]{exmFlipGraph} &
\includegraphics[scale=.7]{exmAssociahedron} & 
\includegraphics[scale=.7]{exmLattice} \\
\end{tabular}
}

\end{slide}

%%%%%%%

\newpage
%\vspace*{-1.5cm}
%\hspace{-1.7cm}
\includegraphics[scale=1.65]{title}

\vspace*{-2cm}
\hspace{18cm}
{\blue \textegrand THANKS}

%\newpage
%\vspace*{-1.5cm}
%\hspace{-1.7cm}
%\includegraphics[scale=.56]{banquet}
%
%\vspace*{-4cm}
%\hspace{12cm}
%{\color{white} \textegrand \textbf{THANKS}}

\end{document}

### 2020-06-29 firstPaper/exposeFPSAC1807/figures/gcmatrices.tex
FPSAC

\(
\begin{blockarray}{cccccccc}
	& & {\color{red} \bullet} & {\color{orange} \bullet} & {\color{yellow} \bullet} & {\color{green} \bullet} & {\color{blue} \bullet} & {\color{violet} \bullet} \\
	\begin{block}{cc(cccccc)}
	1 & & 0 & 0 & 0 & 0 & 0 & \!\!-1\\
	2 & & 0 & 0 & 0 & 0 & \!\!-1\!\! & 0 \\
	3 & & 0 & 1 & 0 & 1 & 0 & 0 \\
	4 & & 0 & 0 & 0 & \!\!-1\!\! & 0 & 0 \\
	5 & & 0 & 0 & 1 & 0 & 1 & 0 \\
	6 & & 1 & 0 & 0 & 0 & 0 & 0 \\
	\end{block}
	& & & & \multicolumn{2}{c}{$\gvectors{F}$} & &
\end{blockarray}
%
\qquad
%
\begin{blockarray}{cccccccc}
	& & {\color{red} \bullet} & {\color{orange} \bullet} & {\color{yellow} \bullet} & {\color{green} \bullet} & {\color{blue} \bullet} & {\color{violet} \bullet} \\
	\begin{block}{cc(cccccc)}
	1 & & 0 & 0 & 0 & 0 & 0 & \!\!-1 \\
	2 & & 0 & 0 & 1 & 0 & \!\!-1\!\! & 0 \\
	3 & & 0 & 1 & 0 & 0 & 0 & 0 \\
	4 & & 0 & 1 & 1 & \!\!-1\!\! & 0 & 0 \\
	5 & & 0 & 0 & 1 & 0 & 0 & 0 \\
	6 & & 1 & 0 & 0 & 0 & 0 & 0 \\
	\end{block}
	& & & & \multicolumn{2}{c}{$\cvectors{F}$} & &
\end{blockarray}
\)

### 2020-06-29 thirdPaper/draft/typeConeAssociahedra.tex
typo
FPSAC

@@
 \[
-R_\b{\ell} \eqdef \set{\b{z} \in \R^N}{K\b{z} = \b{\ell} \text{ and } \b{z} \ge 0}
+R_\b{\ell} \eqdef \set{\b{z} \in \R^N}{\b{K}\b{z} = \b{\ell} \text{ and } \b{z} \ge 0}
 \]
@@
 \label{prop:alternativePolytopalRealization}
-The affine map~$\Psi: \R^n \to \R^N$ defined by~$\Psi(\b{x}) = \b{h} - G\b{x}$ sends the polytope
+The affine map~$\Psi: \R^n \to \R^N$ defined by~$\Psi(\b{x}) = \b{h} - \b{G}\b{x}$ sends the polytope
 \[
@@
 \label{coro:allPolytopalRealizationsAsso}
-For~$n \in \N$, define~$X(n) \eqdef \set{(a,b)}{0 \le a < b \le n+2}$ and~$Y(n) \eqdef \set{(a,b)}{0 \le a < b-2 \le n}$.
+For~$n \in \N$, define~$X(n) \eqdef \set{(a,b)}{0 \le a < b \le n+2}$ and~$Y(n) \eqdef \set{(a,b)}{1 \le a < b \le n+1}$.
 Then for any~$\b{\ell} \in \R_{>0}^{Y(n)}$, the polytope
 \[
-R_\b{\ell}(n) \eqdef \set{\b{z} \in \R^{X(n)}}{\begin{array}{l} \b{z} \ge 0, \quad \b{z}_{(0,n+2)} = 0 \quad\text{and}\quad \b{z}_{(a,a+1)} = 0 \text{ for all } 0 \le a \le n+1 \\ \b{z}_{(a,b-1)} + \b{z}_{(a+1,b)} - \b{z}_{(a,b)} - \b{z}_{(a+1,b-1)} = \b{\ell}_{(a,b)} \text{ for all } (a,b) \in Y(n) \end{array}}
+R_\b{\ell}(n) \eqdef \set{\b{z} \in \R^{X(n)}}{\begin{array}{l} \b{z} \ge 0, \quad \b{z}_{(0,n+2)} = 0 \quad\text{and}\quad \b{z}_{(a,a+1)} = 0 \text{ for all } 0 \le a \le n+1 \\ \b{z}_{(a-1,b)} + \b{z}_{(a,b+1)} - \b{z}_{(a,b)} - \b{z}_{(a-1,b+1)} = \b{\ell}_{(a,b)} \text{ for all } (a,b) \in Y(n) \end{array}}
 \]

### 2020-06-29 thirdPaper/exposeFPSAC2007/exposeFPSAC2007.tex
FPSAC

\documentclass[12pt,titlepage,landscape,a4paper]{article}

%QUELQUES PACKAGES PLUS OU MOINS UTILES
\special{landscape}
\usepackage[T1]{fontenc}
\usepackage[latin1]{inputenc}
\usepackage[english]{babel}
\usepackage{amsfonts, amsmath, amssymb, amsthm, stmaryrd, mathtools}
\usepackage{aeguill}
\usepackage{graphics, graphicx}
\usepackage{xcolor}
\usepackage{geometry}
\usepackage{paralist}
\usepackage{multido,ifthen}
\usepackage{tikz}\usetikzlibrary{trees,shapes,arrows,matrix,calc,arrows.meta}
\usepackage{hyperref}
\hypersetup{colorlinks=true, citecolor=blue, linkcolor=blue, urlcolor=blue}
\usepackage{movie15}
\usepackage[abs]{overpic}
\usepackage{xargs}
\usepackage{extarrows}
\usepackage{shuffle}
\usepackage{multicol}
\usepackage{etoolbox}
\usepackage{dsfont}
\usepackage{pifont}
\usepackage{array, blkarray}
\usepackage{multicol, multirow}
\usepackage{ulem}
\usepackage{xifthen}

% ZONE DE TEXTE ET POLICE
\setlength{\topmargin}{-2.8cm}
\setlength{\textheight}{19cm}
\setlength{\oddsidemargin}{-1cm}
\setlength{\textwidth}{26.8cm}
\newcommand{\textenormal}{\fontsize{22}{28}\selectfont}
\newcommand{\textemoyen}{\fontsize{23}{27}\selectfont}
\newcommand{\textegrand}{\fontsize{55}{48}\selectfont}

% COMMANDE DE NOUVELLE PAGE
\newenvironment{slide}[1]
{
\newpage
\begin{center}
{\blue \textemoyen \uppercase{#1}}\\
\end{center}
\vspace{-1cm}
\rule{\textwidth}{0.5 pt}\\
\vspace{-.8cm}
}
{\vspace*{-3cm}}

% COMMANDE DE PARTIE
%\newcounter{partie}
%\setcounter{partie}{1}
%\newcommand{\thePartie}{Part \arabic{partie}}
\newcommand{\partie}[1]
{
\newpage
\vspace*{0pt plus 1 fill}
\begin{center}
%\thePartie \\[-.75cm]
\rule{.9\textwidth}{0.5 pt} \\[.5cm]
\fontsize{35}{35}\selectfont {\blue\uppercase{#1}} \\[-.35cm]
\rule{.9\textwidth}{0.5 pt} \\
\end{center}
\vspace*{0pt plus 1.2 fill}
%\addtocounter{partie}{1}
}

% COMMANDE D'EXPOSE
\newcommand{\expose}[2]
{
\newpage
\vspace*{0pt plus 1 fill}
\begin{center}
%\thePartie \\[-.75cm]
\rule{.8\textwidth}{0.5 pt} \\[.5cm]
\fontsize{35}{35}\selectfont {\red\uppercase{#1}} \\[-.35cm]
\rule{.8\textwidth}{0.5 pt} \\
\vspace{1cm}
\textemoyen #2
\end{center}
\vspace*{0pt plus 1.2 fill}
%\addtocounter{partie}{1}
}

% COMMANDE POUR LES BOITES
% centre
\newcommand{\cboite}[1]
{
\vspace*{.5cm}
\fcolorbox{blue}{grisclair}{
\begin{minipage}{.97\linewidth}
\vspace*{.3cm}
\begin{center} #1 \end{center}
\vspace*{-.1cm}
\end{minipage}
}
}
% alignement gauche
\newcommand{\gboite}[1]
{
\vspace*{.5cm}
\fcolorbox{blue}{grisclair}{
\begin{minipage}{.97\linewidth}
\vspace*{.3cm}
#1
\vspace{.3cm}
\end{minipage}
}
}

\newcommand{\chapitre}[1]{{\blue \fontsize{23}{25}\selectfont {Chap\,#1}}}

% AUTRES COMMANDES
% quelques couleurs manquantes
\newcommand{\orange}{\color{orange}} % couleur orange
\newcommand{\green}{\color{green}} % couleur verte
\newcommand{\violet}{\color{violet}} % couleur violet
\newcommand{\blue}{\color{blue}} % couleur bleu
\newcommand{\red}{\color{red}} % couleur rouge
\definecolor{violet}{rgb}{.5,.1,.9}
\definecolor{orange}{rgb}{.94,.57,0}
\definecolor{green}{rgb}{0.2,0.6,0.2}
\definecolor{grisclair}{gray}{1}
\definecolor{grisfonce}{gray}{.1}
\definecolor{bblue}{rgb}{.8,.8,1}
% maths
\newcommand{\set}[2]{\left\{ #1 \;\middle|\; #2 \right\}} % ensemble
\newcommand{\bigset}[2]{\big\{ #1 \;\big|\; #2 \big\}} % ensemble
\newcommand{\biggset}[2]{\bigg\{ #1 \;\bigg|\; #2 \bigg\}} % ensemble
\newcommand{\setangle}[2]{\left\langle #1 \;\middle|\; #2 \right\rangle} % ensemble
\newcommand{\dotprod}[2]{\left\langle\; #1 \;\middle|\; #2 \;\right\rangle} % produit scalaire
\newcommand{\ssm}{\smallsetminus} % small set minus
\newcommand{\symdif}{\triangle} % symmetric difference
\newcommand{\eqdef}{\mbox{\,\raisebox{0.3ex}{\normalsize\ensuremath{\mathrm:}}\ensuremath{=}\,}} % :=
\newcommand{\defeq}{\mbox{~\ensuremath{=}\raisebox{0.3ex}{\normalsize\ensuremath{\mathrm:}} }} % =:
\newcommand{\Fracfloor}[2]{\left\lfloor \frac{#1}{#2} \right\rfloor} % floor of a fraction
\newcommand{\one}{1\!\!1} % one bold
\DeclareMathOperator{\conv}{conv} % enveloppe convexe
\DeclareMathOperator{\cone}{cone} % cone engendre
\DeclareMathOperator{\vol}{vol} % volume
\newcommand{\C}{\mathbb{C}} % complexes
\newcommand{\R}{\mathbb{R}} % reels
\newcommand{\Z}{\mathbb{Z}} % entiers
\newcommand{\N}{\mathbb{N}} % naturels
\newcommand{\I}{\mathbb{I}} % set of integers
\newcommand{\K}{\mathbb{K}} % field
\newcommand{\fS}{\mathfrak{S}} % symmetric group
\newcommand{\cA}{\mathcal{A}} % algebra
\newcommand{\cF}{\mathcal{F}} % flip graph
\newcommand{\cN}{\mathcal{N}} % sorting network
\renewcommand{\b}[1]{\boldsymbol{#1}} % bold letters
\renewcommand{\c}[1]{\mathcal{#1}} % caligraphic letters
\newcommand{\f}[1]{\mathfrak{#1}} % frak letters
% autres
\setlength{\parindent}{0pt} % aucune indentation dans tout le document
\graphicspath{{figures/}{figures/diagonals/}} % les repertoires ou se trouvent les figures
\newcommand{\papier}[1]{{\violet\fontsize{15}{20}\selectfont #1}} % citation papier
\newcommand{\theo}[2]{\gboite{{\blue \fontsize{18}{25}\selectfont #1.} #2}}
\newcommand{\HUGE}[1]{{\fontsize{35}{33}\selectfont #1}}
\newcommand{\esperluette}{ \\ --- \& --- \\ } % esperluette stylisée nouvelle ligne
\renewcommand{\emph}[1]{\uline{#1}}
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{\node[shape=circle, draw, inner sep=1.5pt, scale=1] (char) {#1};}}

% POLYTOPES
\newcommand{\poly}[1]{\mathds{#1}} % polytope font
\newcommand{\Asso}{\mathds{A}\mathsf{sso}} % associahedron
\newcommand{\Quot}[2]{\mathds{Q}\mathsf{uot}_{#1}^{#2}} % quotientope
\newcommandx{\Brick}[2][1=k, 2=n]{\mathds{B}\mathsf{rick}^{#1}(#2)} % brick polytope
\newcommand{\Perm}{\mathds{P}\mathsf{erm}} % permutahedron
\newcommand{\Para}{\mathds{P}\mathsf{ara}} % parallelepiped
\newcommand{\Zono}{\mathds{Z}\mathsf{ono}} % zonotope
\newcommand{\deformedPermutahedron}{\mathds{D}\mathsf{efo}} % deformed permutahedron
\newcommand{\shardPolytope}{\mathds{SP}} % shard polytope
\newcommand{\Hyp}{\b{H}^=} % hyperplane
\newcommand{\HS}{\b{H}^\ge} % half-space
\newcommand{\HH}{\poly{H}} % hyperplane
\newcommand{\Cone}{\mathrm{C}} % cone
\newcommand{\polar}{^\diamond} % polar
\newcommand{\vertex}[1]{\b{a}(#1)} % vertex corresponding to a maximal signed nested set
\newcommand{\face}[1]{\b{f}(#1)} % face corresponding to a signed nested set
\newcommand{\braidFan}{\mathcal{B\!F}} % braid fan
\newcommand{\secPoly}{\Sigma\mathsf{Poly}} % secondary polytope
\newcommand{\secFan}{\Sigma\mathsf{Fan}} % secondary fan
\newcommand{\rhs}[2]{\omega(#1, #2)} % right hand side of zonotope
\newcommand{\typeCone}{\mathds{TC}} % type cone

% PERMUTREES
\newcommand{\up}[1]{\overline{#1}}
\newcommand{\upr}[1]{{\red \overline{#1}}}
\newcommand{\upb}[1]{{\blue \overline{#1}}}
\newcommand{\down}[1]{\underline{#1}}
\newcommand{\downr}[1]{{\red \underline{#1}}}
\newcommand{\downb}[1]{{\blue \underline{#1}}}
\newcommand{\updown}[1]{\up{\down{#1}}}
\newcommand{\updownr}[1]{{\red \updown{#1}}}
\newcommand{\updownb}[1]{{\blue \updown{#1}}}
\newcommandx{\tree}[1][1=T]{\mathrm{#1}} % tree
\newcommand{\decoration}{\delta} % decoration
\newcommand{\includeSymbol}[1]{\ensuremath{%
	\mathchoice
		{\raisebox{-.7mm}{\includegraphics[height=1.8ex]{#1}}}	
		{\raisebox{-.7mm}{\includegraphics[height=1.8ex]{#1}}}
		{\raisebox{-.6mm}{\includegraphics[height=1.4ex]{#1}}}
		{\raisebox{-.5mm}{\includegraphics[height=.8ex]{#1}}}
}}
\robustify{\includeSymbol}
\newcommand{\noneCirc}{\includeSymbol{none}}
\newcommand{\upCirc}{\includeSymbol{up}}
\newcommand{\downCirc}{\includeSymbol{down}}
\newcommand{\upDownCirc}{\includeSymbol{updown}}
\newcommand{\noneSquare}{\includeSymbol{noneSquare}}
\newcommand{\upSquare}{\includeSymbol{upSquare}}
\newcommand{\downSquare}{\includeSymbol{downSquare}}
\newcommand{\upDownSquare}{\includeSymbol{updownSquare}}
\newcommand{\Decorations}{\{\noneCirc{}, \downCirc{}, \upCirc{}, \upDownCirc{}\}} % all decorations
\newcommandx{\surjection}[2][1=\decoration, 2=\decoration']{\Psi_{#1}^{#2}} % surjection from #1-permutrees to #2-permutrees
\newcommandx{\Fan}[1][1=\decoration]{\mathcal{F}(#1)} % permutree fan
\newcommandx{\Permutreehedron}[1][1=\decoration]{\mathds{PT}(#1)} % permutreehedron

% TWISTS
\newcommandx{\twist}[1][1=T]{\mathrm{#1}} % twist
\newcommand{\duality}{^\star} % dual
\newcommandx{\Gkn}[2][1=k, 2=n]{\mathrm{G}^{#1}(#2)} % graph k n

% LATTICES
\newcommand{\meet}{\wedge} % meet
\newcommand{\join}{\vee} % join
\newcommand{\bigMeet}{\bigwedge} % meet
\newcommand{\bigJoin}{\bigvee} % join
\newcommand{\closure}[1]{#1^{\mathrm{cl}}} % closure operator
\newcommand{\coclosure}[1]{#1^{\mathrm{cocl}}} % coclosure operator
\newcommand{\Bicl}[1]{\mathsf{Bic}(#1)} % biclosed sets
\newcommand{\projDown}{\pi_\downarrow} % down projection map
\newcommand{\projUp}{\pi^\uparrow} % up projection map
\newcommand{\JI}{\mathsf{JI}} % join-irreducible
\newcommand{\MI}{\mathsf{MI}} % meet-irreducible
\newcommand{\Cong}{\mathsf{Cong}} % congruence lattice
\newcommand{\con}{\mathrm{con}} % congruence contracting a cover relation
\newcommand{\ji}{\mathsf{ji}} % join irreducible
\newcommand{\mi}{\mathsf{mi}} % meet irreducible
\newcommand{\PR}{\mathsf{PR}} % poset of regions

% WEAK ORDER
\newcommand{\inc}[1]{{#1^+}}
\newcommand{\dec}[1]{{#1^-}}
\newcommand{\less}{\lhd}
\newcommand{\bless}{\blacktriangleleft}

% HOPF ALGEBRAS
\newcommand{\product}{\cdot} % product
\newcommand{\coproduct}{\triangle} % coproduct
\newcommand{\shiftedShuffle}{\,\bar\shuffle\,} % shifted shuffle
\newcommand{\convolution}{\star} % shifted shuffle
\newcommand{\underprod}[2]{{#1}\backslash{#2}} % #1 under #2
\newcommand{\overprod}[2]{{#1}\slash{#2}} % #1 over #2
\newcommand{\F}{\mathbb{F}} % F-basis of FQSym
\renewcommand{\P}{\mathbb{P}} % P-basis of PBT

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\titre}{From permutahedra to associahedra, a walk through geometric and algebraic combinatorics}
\newcommand{\auteur}{Vincent Pilaud}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\fontshape{sf}\fontsize{22}{28}\selectfont % police par defaut
\sf
\pagestyle{empty} % bas de page par defaut

\vspace*{-1.1cm}\hspace{-.7cm}
\begin{minipage}{6cm}
\gboite{
\begin{center}
\includegraphics[scale=.40]{logoFPSAC20} \\[.5cm]
\includegraphics[scale=.69]{photos} \\[.5cm]
\includegraphics[scale=.69]{PPPP}
\end{center}
\vspace{-.6cm}
}
\end{minipage}
\hspace{1.5cm}
\begin{minipage}{20cm}
\begin{flushleft}
{\blue \fontsize{80}{45}\selectfont

On type cones \\ of g-vector fans

}

\vspace{1cm}
\HUGE{A. PADROL} \\[-.1cm]
(Sorbonne Univ.)

\vspace{.7cm}
\HUGE{Y. PALU} \\[-.1cm]
(Univ. Amiens)

\vspace{.7cm}
\HUGE{V. PILAUD} \\[-.1cm]
(CNRS \& École Polytechnique)

\vspace{.7cm}
\HUGE{P.-G. PLAMONDON} \\[-.1cm]
(Univ. Paris-Saclay $\to$ Univ. Versailles)

\vspace{-4.4cm}\hspace{7cm}\smash{\includegraphics[scale=.9]{typeConeCoarsenings}}

\vspace{4.9cm}
\Large slides: \url{http://www.lix.polytechnique.fr/~pilaud/FPSAC20.pdf}

\Large preprint: \url{https://arxiv.org/pdf/1906.06861.pdf}

\vspace{-.6cm}

\end{flushleft}
\end{minipage}

\vspace*{-3cm}

%\begin{center}
%{\blue \fontsize{50}{45}\selectfont
%
%Type cones of g-vector fans
%
%}
%
%\includegraphics[scale=1.1]{typeConeCoarsenings}
%
%\begin{tabular}{c@{\qquad}c}
%\HUGE{A. PADROL} & \HUGE{Y. PALU} \\[-.1cm]
%(Sorbonne Univ.) & (Univ. Amiens) \\[1cm]
%\HUGE{V. PILAUD} & \HUGE{P.-G. PLAMONDON} \\[-.1cm]
%(CNRS \& École Polytechnique) & (Univ. Paris-Saclay $\to$ Univ. Versailles)
%\end{tabular}
%
%\includegraphics[scale=1.1]{typeConeCoarsenings}
%
%\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\partie{Kinematic associahedron}

%%%%%%%%%

\begin{slide}{Associahedron}

\emph{associahedron} = polytope whose graph is the flip graph on triangulations of a polygon
%\begin{tabular}[t]{@{\;}l}
%	$n$-dimensional polytope whose graph is the flip graph \\ on triangulations of a convex $(n+3)$-gon
%\end{tabular}

\vspace{.5cm}
\centerline{\includegraphics[scale=3.3]{associahedronSecondaryPolytope}}
\vspace*{-3.5cm}
\begin{tabular}{r@{ $\leftrightarrow$ }l}
vertices & triangulations \\
edges & flips \\
faces & dissections
\end{tabular}
\hfill
\begin{tabular}{r@{ $\leftrightarrow$ }l}
vertices & binary trees \\
edges & rotations \\
faces & Schr\"oder trees
\end{tabular}

\vspace{.8cm}
\centerline{\papier{Tamari ('51) \qquad Stasheff ('63)}}

\end{slide}

%%%

\begin{slide}{Associahedron}

\emph{associahedron} = polytope whose graph is the flip graph on triangulations of a polygon
%\begin{tabular}[t]{@{\;}l}
%	$n$-dimensional polytope whose graph is the flip graph \\ on triangulations of a convex $(n+3)$-gon
%\end{tabular}

\vspace{.5cm}
Three families of constructions (with non-equivalent normal fans):

\vspace{.5cm}
\begin{tabular}{cc|ccc|cc}
\begin{minipage}[t]{8.5cm}
\centerline{\blue SECONDARY FAN}
\vspace{.5cm}
\centerline{\includegraphics[scale=1.5]{associahedronSecondaryPolytope}}
\vspace{.5cm}
\papier{Gelfand--Kapranov--Zelevinsky ('94) \\ Billera--Filliman--Sturmfels ('90)

}
\end{minipage}
&&&
\begin{minipage}[t]{8.5cm}
\centerline{\blue G-VECTOR FAN}
\vspace{.5cm}
\centerline{\includegraphics[scale=.78]{associahedronBinaryTrees}}
\vspace{.5cm}
\papier{Shnider--Sternberg ('93) \\ Loday ('04) \\ Hohlweg--Lange ('07) \\ Hohlweg--Lange--Thomas ('12) \\ Hohlweg--P.--Stella ('18)

}
\end{minipage}
&&&
\begin{minipage}[t]{8.5cm}
\centerline{\blue D-VECTOR FAN}
\vspace{.5cm}
\centerline{\input{figures/associahedronCFZ}}
\vspace{.3cm}
\hfill {\normalsize (Pictures by CFZ)} \hspace{1cm} \\[.5cm]
\papier{Chapoton--Fomin--Zelevinsky ('02) \\ Ceballos--Santos--Ziegler ('11)

}
\end{minipage}
\end{tabular}

\end{slide}

%%%

\begin{slide}{Associahedron}

\emph{associahedron} = polytope whose graph is the flip graph on triangulations of a polygon
%\begin{tabular}[t]{@{\;}l}
%	$n$-dimensional polytope whose graph is the flip graph \\ on triangulations of a convex $(n+3)$-gon
%\end{tabular}

\vspace{.5cm}
Three families of constructions (with non-equivalent normal fans):

\vspace{.5cm}
\begin{tabular}{cc|ccc|cc}
\begin{minipage}[t]{8.5cm}
\centerline{\blue SECONDARY FAN}
\vspace{.5cm}
\centerline{\includegraphics[scale=1.5]{associahedronSecondaryPolytope}}
\vspace{.5cm}
\papier{Gelfand--Kapranov--Zelevinsky ('94) \\ Billera--Filliman--Sturmfels ('90)

}
\end{minipage}
&&&
\begin{minipage}[t]{8.5cm}
\centerline{\blue G-VECTOR FAN}
\vspace{.5cm}
\centerline{\includegraphics[scale=.78]{associahedronBinaryTrees}}
\vspace{.5cm}
\papier{Shnider--Sternberg ('93) \\ Loday ('04) \\ Hohlweg--Lange ('07) \\ Hohlweg--Lange--Thomas ('12) \\ Hohlweg--P.--Stella ('18)

}
\end{minipage}
&&&
\begin{minipage}[t]{8.5cm}
\centerline{\blue D-VECTOR FAN}
\vspace{.5cm}
\centerline{\input{figures/associahedronCFZ}}
\vspace{.3cm}
\hfill {\normalsize (Pictures by CFZ)} \hspace{1cm} \\[.5cm]
\papier{Chapoton--Fomin--Zelevinsky ('02) \\ Ceballos--Santos--Ziegler ('11)

}
\end{minipage}
\end{tabular}

\gboite{
	\centerline{Unidentified Construction of the Associahedron = ABHY kinematic associahedron}
	\vspace{-.1cm}
	\centerline{\papier{Arkani-Hamed--Bai--He--Yan ('18) \qquad 
Bazier-Matte--Douville--Mousavand--Thomas--Y\i{}ld\i{}r\i{}m ('18$^+$)}}
	\vspace{-.1cm}
}

\end{slide}

%%%

\begin{slide}{Kinematic associahedron}

%\emph{associahedron} = polytope whose graph is the flip graph on triangulations of a polygon

%\vspace{.3cm}
\emph{kinematic associahedron} = 
\begin{tabular}[t]{@{\;}l}
	$n$-dimensional associahedron constructed in the \\
	$n(n+3)/2$-dimensional kinematic space as a section of an \\
	$n$-dimensional affine subspace with the positive orthant
\end{tabular}

\vspace{-1.8cm} \papier{Arkani-Hamed--Bai--He--Yan ('18)}

\end{slide}

%%%

\begin{slide}{Kinematic associahedron}

%\emph{associahedron} = polytope whose graph is the flip graph on triangulations of a polygon

%\vspace{.3cm}
\emph{kinematic associahedron} = 
\begin{tabular}[t]{@{\;}l}
	$n$-dimensional associahedron constructed in the \\
	$n(n+3)/2$-dimensional kinematic space as a section of an \\
	$n$-dimensional affine subspace with the positive orthant
\end{tabular}

\vspace{-1.8cm} \papier{Arkani-Hamed--Bai--He--Yan ('18)}

\vspace{1.3cm}
fix parameters $\b{\ell}_A, \dots, \b{\ell}_F > 0$ \\
$\b{z} \ge 0$ indexed by internal diagonals of $(n+3)$-gon

\vspace{-2.5cm}\hspace{-.6cm}
\begin{tikzpicture}
	\matrix (m) [matrix of math nodes, row sep=.7cm, column sep=.3cm, nodes={anchor=center, align=center, inner sep=0pt}]{
		&& \;\includegraphics[scale=1.3]{diagonalB3} & \node (c) {\red \circled{C}}; & \;\includegraphics[scale=1.3]{diagonalB7} && \\
		& \;\includegraphics[scale=1.3]{diagonalB2} & \node (b) {\red \circled{B}}; & \;\includegraphics[scale=1.3]{diagonalB5} & \node (e) {\red \circled{E}}; & \;\includegraphics[scale=1.3]{diagonalB8} & \\
		\;\includegraphics[scale=1.3]{diagonalB1} & \node (a) {\red \circled{A}}; & \;\includegraphics[scale=1.3]{diagonalB4} & \node (d) {\red \circled{D}}; & \;\includegraphics[scale=1.3]{diagonalB6} & \node (f) {\red \circled{F}}; & \;\includegraphics[scale=1.3]{diagonalB9} \\};
	\draw[->] (m-3-1) -- (m-2-2);
	\draw[->] (m-2-2) -- (m-1-3);
	\draw[->] (m-2-2) -- (m-3-3);
	\draw[->] (m-1-3) -- (m-2-4);
	\draw[->] (m-3-3) -- (m-2-4);
	\draw[->] (m-2-4) -- (m-1-5);
	\draw[->] (m-2-4) -- (m-3-5);
	\draw[->] (m-1-5) -- (m-2-6);
	\draw[->] (m-3-5) -- (m-2-6);
	\draw[->] (m-2-6) -- (m-3-7);
	\draw[red] (a) -- (m-3-1);
	\draw[red] (a) -- (m-3-3);
	\draw[red] (a) -- (m-2-2);
	\draw[red] (b) -- (m-2-2);
	\draw[red] (b) -- (m-2-4);
	\draw[red] (b) -- (m-1-3);
	\draw[red] (b) -- (m-3-3);
	\draw[red] (c) -- (m-1-3);
	\draw[red] (c) -- (m-1-5);
	\draw[red] (c) -- (m-2-4);
	\draw[red] (d) -- (m-3-3);
	\draw[red] (d) -- (m-3-5);
	\draw[red] (d) -- (m-2-4);
	\draw[red] (e) -- (m-2-4);
	\draw[red] (e) -- (m-2-6);
	\draw[red] (e) -- (m-1-5);
	\draw[red] (e) -- (m-3-5);
	\draw[red] (f) -- (m-3-5);
	\draw[red] (f) -- (m-3-7);
	\draw[red] (f) -- (m-2-6);
\end{tikzpicture}
%
\hspace{-.5cm}
\raisebox{4.5cm}{
\begin{minipage}{6cm}
\begin{align*}
%	\b{z} & \ge \b{0} \\
	\b{z}_{\includegraphics[scale=.7]{diagonalB1}} + \b{z}_{\includegraphics[scale=.7]{diagonalB4}} - \b{z}_{\includegraphics[scale=.7]{diagonalB2}} & = \b{\ell}_A \\
	\b{z}_{\includegraphics[scale=.7]{diagonalB2}} + \b{z}_{\includegraphics[scale=.7]{diagonalB5}} - \b{z}_{\includegraphics[scale=.7]{diagonalB3}} - \b{z}_{\includegraphics[scale=.7]{diagonalB4}} & = \b{\ell}_B \\
	\b{z}_{\includegraphics[scale=.7]{diagonalB3}} + \b{z}_{\includegraphics[scale=.7]{diagonalB6}} - \b{z}_{\includegraphics[scale=.7]{diagonalB5}} & = \b{\ell}_C \\
	\b{z}_{\includegraphics[scale=.7]{diagonalB4}} + \b{z}_{\includegraphics[scale=.7]{diagonalB7}} - \b{z}_{\includegraphics[scale=.7]{diagonalB5}} & = \b{\ell}_D \\
	\b{z}_{\includegraphics[scale=.7]{diagonalB5}} + \b{z}_{\includegraphics[scale=.7]{diagonalB8}} - \b{z}_{\includegraphics[scale=.7]{diagonalB6}} - \b{z}_{\includegraphics[scale=.7]{diagonalB7}} & = \b{\ell}_E \\
	\b{z}_{\includegraphics[scale=.7]{diagonalB7}} + \b{z}_{\includegraphics[scale=.7]{diagonalB9}} - \b{z}_{\includegraphics[scale=.7]{diagonalB8}} & = \b{\ell}_F
\end{align*}
\end{minipage}
}

\end{slide}

%%%

\begin{slide}{Kinematic associahedron}

%\emph{associahedron} = polytope whose graph is the flip graph on triangulations of a polygon

%\vspace{.3cm}
\emph{kinematic associahedron} = 
\begin{tabular}[t]{@{\;}l}
	$n$-dimensional associahedron constructed in the \\
	$n(n+3)/2$-dimensional kinematic space as a section of an \\
	$n$-dimensional affine subspace with the positive orthant
\end{tabular}

\vspace{-1.8cm} \papier{Arkani-Hamed--Bai--He--Yan ('18)}

\vspace{1.3cm}
fix parameters $\b{\ell}_A, \dots, \b{\ell}_F > 0$ \\
$\b{z} \ge 0$ indexed by internal diagonals of $(n+3)$-gon

\vspace{-2.5cm}\hspace{-.6cm}
\begin{tikzpicture}
	\matrix (m) [matrix of math nodes, row sep=.7cm, column sep=.3cm, nodes={anchor=center, align=center, inner sep=0pt}]{
		&& \;\includegraphics[scale=1.3]{diagonalB3} & \node (c) {\red \circled{C}}; & \;\includegraphics[scale=1.3]{diagonalB7} && \\
		& \;\includegraphics[scale=1.3]{diagonalB2} & \node (b) {\red \circled{B}}; & \;\includegraphics[scale=1.3]{diagonalB5} & \node (e) {\red \circled{E}}; & \;\includegraphics[scale=1.3]{diagonalB8} & \\
		\;\includegraphics[scale=1.3]{diagonalB1} & \node (a) {\red \circled{A}}; & \;\includegraphics[scale=1.3]{diagonalB4} & \node (d) {\red \circled{D}}; & \;\includegraphics[scale=1.3]{diagonalB6} & \node (f) {\red \circled{F}}; & \;\includegraphics[scale=1.3]{diagonalB9} \\};
	\draw[->] (m-3-1) -- (m-2-2);
	\draw[->] (m-2-2) -- (m-1-3);
	\draw[->] (m-2-2) -- (m-3-3);
	\draw[->] (m-1-3) -- (m-2-4);
	\draw[->] (m-3-3) -- (m-2-4);
	\draw[->] (m-2-4) -- (m-1-5);
	\draw[->] (m-2-4) -- (m-3-5);
	\draw[->] (m-1-5) -- (m-2-6);
	\draw[->] (m-3-5) -- (m-2-6);
	\draw[->] (m-2-6) -- (m-3-7);
	\draw[red] (a) -- (m-3-1);
	\draw[red] (a) -- (m-3-3);
	\draw[red] (a) -- (m-2-2);
	\draw[red] (b) -- (m-2-2);
	\draw[red] (b) -- (m-2-4);
	\draw[red] (b) -- (m-1-3);
	\draw[red] (b) -- (m-3-3);
	\draw[red] (c) -- (m-1-3);
	\draw[red] (c) -- (m-1-5);
	\draw[red] (c) -- (m-2-4);
	\draw[red] (d) -- (m-3-3);
	\draw[red] (d) -- (m-3-5);
	\draw[red] (d) -- (m-2-4);
	\draw[red] (e) -- (m-2-4);
	\draw[red] (e) -- (m-2-6);
	\draw[red] (e) -- (m-1-5);
	\draw[red] (e) -- (m-3-5);
	\draw[red] (f) -- (m-3-5);
	\draw[red] (f) -- (m-3-7);
	\draw[red] (f) -- (m-2-6);
\end{tikzpicture}
%
\hspace{-.5cm}
\raisebox{4.5cm}{
\begin{minipage}{6cm}
\begin{align*}
%	\b{z} & \ge \b{0} \\
	\b{z}_{\includegraphics[scale=.7]{diagonalB1}} + \b{z}_{\includegraphics[scale=.7]{diagonalB4}} - \b{z}_{\includegraphics[scale=.7]{diagonalB2}} & = \b{\ell}_A \\
	\b{z}_{\includegraphics[scale=.7]{diagonalB2}} + \b{z}_{\includegraphics[scale=.7]{diagonalB5}} - \b{z}_{\includegraphics[scale=.7]{diagonalB3}} - \b{z}_{\includegraphics[scale=.7]{diagonalB4}} & = \b{\ell}_B \\
	\b{z}_{\includegraphics[scale=.7]{diagonalB3}} + \b{z}_{\includegraphics[scale=.7]{diagonalB6}} - \b{z}_{\includegraphics[scale=.7]{diagonalB5}} & = \b{\ell}_C \\
	\b{z}_{\includegraphics[scale=.7]{diagonalB4}} + \b{z}_{\includegraphics[scale=.7]{diagonalB7}} - \b{z}_{\includegraphics[scale=.7]{diagonalB5}} & = \b{\ell}_D \\
	\b{z}_{\includegraphics[scale=.7]{diagonalB5}} + \b{z}_{\includegraphics[scale=.7]{diagonalB8}} - \b{z}_{\includegraphics[scale=.7]{diagonalB6}} - \b{z}_{\includegraphics[scale=.7]{diagonalB7}} & = \b{\ell}_E \\
	\b{z}_{\includegraphics[scale=.7]{diagonalB7}} + \b{z}_{\includegraphics[scale=.7]{diagonalB9}} - \b{z}_{\includegraphics[scale=.7]{diagonalB8}} & = \b{\ell}_F
\end{align*}
\end{minipage}
}

\vspace{-.1cm}
\gboite{
	Let $X(n) = \set{(a,b)}{0 \le a < b \le n+2}$ and $Y(n) = \set{(a,b)}{1 \le a < b \le n+1}$. \\
	For any~$\b{\ell} \in \R_{>0}^{Y(n)}$, the polytope
	\[
	\set{\b{z} \in \R^{X(n)}}{\begin{array}{@{}l} \b{z} \ge 0, \quad \b{z}_{(0,n+2)} = 0 \quad\text{and}\quad \b{z}_{(a,a+1)} = 0 \text{ for all } 0 \le a \le n+1 \\ \b{z}_{(a-1,b)} + \b{z}_{(a,b+1)} - \b{z}_{(a,b)} - \b{z}_{(a-1,b+1)} = \b{\ell}_{(a,b)} \text{ for all } (a,b) \in Y(n) \end{array}}
	\]
	is an associahedron. \hfill \papier{Arkani-Hamed--Bai--He--Yan ('18)}
	\vspace{-.1cm}
}

\end{slide}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\partie{Type cones}

%%%%%%%%%

\begin{slide}{Choosing right-hand-sides}

$\c{F}$ = complete simplicial fan in~$\R^n$ with~$N$ rays \\
$\b{G}$ = $(N \times n)$-matrix whose rows are representatives of the rays of~$\c{F}$ \\
for a height vector~$\b{h} \in \R_{>0}^N$, consider the polytope~$\poly{P}_{\b{h}} = \set{\b{x} \in \R^n}{\b{G}\b{x} \le \b{h}}$

\vspace{1cm}
\centerline{
	\begin{tabular}{c@{\quad}c@{\quad}c@{\quad}c}
		\includegraphics[scale=1.5]{typeConeFan} & \includegraphics[scale=1.5]{typeConePolytope1a} & \includegraphics[scale=1.5]{typeConePolytope2a} & \includegraphics[scale=1.5]{typeConePolytope3a} \\
		& A & B & C
	\end{tabular}
}
\centerline{}

\end{slide}

%%%

\begin{slide}{Choosing right-hand-sides}

$\c{F}$ = complete simplicial fan in~$\R^n$ with~$N$ rays \\
$\b{G}$ = $(N \times n)$-matrix whose rows are representatives of the rays of~$\c{F}$ \\
for a height vector~$\b{h} \in \R_{>0}^N$, consider the polytope~$\poly{P}_{\b{h}} = \set{\b{x} \in \R^n}{\b{G}\b{x} \le \b{h}}$

\vspace{1cm}
\centerline{
	\begin{tabular}{c@{\quad}c@{\quad}c@{\quad}c}
		\includegraphics[scale=1.5]{typeConeFan} & \includegraphics[scale=1.5]{typeConePolytope1b} & \includegraphics[scale=1.5]{typeConePolytope2b} & \includegraphics[scale=1.5]{typeConePolytope3b} \\
		& A & B & C
	\end{tabular}
}

\end{slide}

%%%

\begin{slide}{Choosing right-hand-sides}

$\c{F}$ = complete simplicial fan in~$\R^n$ with~$N$ rays \\
$\b{G}$ = $(N \times n)$-matrix whose rows are representatives of the rays of~$\c{F}$ \\
for a height vector~$\b{h} \in \R_{>0}^N$, consider the polytope~$\poly{P}_{\b{h}} = \set{\b{x} \in \R^n}{\b{G}\b{x} \le \b{h}}$

\vspace{1cm}
\centerline{
	\begin{tabular}{c@{\quad}c@{\quad}c@{\quad}c}
		\includegraphics[scale=1.5]{typeConeFan} & \includegraphics[scale=1.5]{typeConePolytope1b} & \includegraphics[scale=1.5]{typeConePolytope2b} & \includegraphics[scale=1.5]{typeConePolytope3b} \\
		& A & B & C
	\end{tabular}
}

\vspace{.3cm}
When is~$\c{F}$ the normal fan of~$\poly{P}_{\b{h}}$?

\end{slide}

%%%

\begin{slide}{Choosing right-hand-sides}

$\c{F}$ = complete simplicial fan in~$\R^n$ with~$N$ rays \\
$\b{G}$ = $(N \times n)$-matrix whose rows are representatives of the rays of~$\c{F}$ \\
for a height vector~$\b{h} \in \R_{>0}^N$, consider the polytope~$\poly{P}_{\b{h}} = \set{\b{x} \in \R^n}{\b{G}\b{x} \le \b{h}}$

\vspace{1cm}
\centerline{
	\begin{tabular}{c@{\quad}c@{\quad}c@{\quad}c}
		\includegraphics[scale=1.5]{typeConeFan} & \includegraphics[scale=1.5]{typeConePolytope1b} & \includegraphics[scale=1.5]{typeConePolytope2b} & \includegraphics[scale=1.5]{typeConePolytope3b} \\
		& A & B & C
	\end{tabular}
}

\vspace{.3cm}
When is~$\c{F}$ the normal fan of~$\poly{P}_{\b{h}}$?

\vspace{.5cm}
$\poly{P}$ polytope, $\poly{F}$ face of~$\poly{P}$ \\[.2cm]
\emph{normal cone} of~$\poly{F}$ = 
\begin{tabular}[t]{@{\;}l}
	positive span of the outer normal \\
	vectors of the facets containing~$\poly{F}$
\end{tabular} \\[.5cm]
\emph{normal fan} of~$\poly{P}$ = $\{$ normal cone of~$\poly{F}$ $|$ $\poly{F}$ face of~$\poly{P}$ $\}$

\vspace{-6cm}\hspace{17cm}
\includegraphics[scale=.7]{normalFanCube}

\end{slide}

%%%

\begin{slide}{Wall-crossing inequalities}

$\c{F}$ = complete simplicial fan in~$\R^n$ with~$N$ rays \\
$\b{G}$ = $(N \times n)$-matrix whose rows are representatives of the rays of~$\c{F}$ \\
for a height vector~$\b{h} \in \R_{>0}^N$, consider the polytope~$\poly{P}_{\b{h}} = \set{\b{x} \in \R^n}{\b{G}\b{x} \le \b{h}}$

\centerline{\includegraphics[scale=1.7]{wallCrossingInequality1}}

\end{slide}

%%%

\begin{slide}{Wall-crossing inequalities}

$\c{F}$ = complete simplicial fan in~$\R^n$ with~$N$ rays \\
$\b{G}$ = $(N \times n)$-matrix whose rows are representatives of the rays of~$\c{F}$ \\
for a height vector~$\b{h} \in \R_{>0}^N$, consider the polytope~$\poly{P}_{\b{h}} = \set{\b{x} \in \R^n}{\b{G}\b{x} \le \b{h}}$

\centerline{\includegraphics[scale=1.7]{wallCrossingInequality2}}

\end{slide}

%%%

\begin{slide}{Wall-crossing inequalities}

$\c{F}$ = complete simplicial fan in~$\R^n$ with~$N$ rays \\
$\b{G}$ = $(N \times n)$-matrix whose rows are representatives of the rays of~$\c{F}$ \\
for a height vector~$\b{h} \in \R_{>0}^N$, consider the polytope~$\poly{P}_{\b{h}} = \set{\b{x} \in \R^n}{\b{G}\b{x} \le \b{h}}$

\centerline{\includegraphics[scale=1.7]{wallCrossingInequality2}}

\gboite{
\emph{wall-crossing inequality} for a wall~$\b{R}$ = \qquad $\displaystyle \smashoperator{\sum_{\b{s} \in \b{R} \, \cup \{\b{r}, \b{r}'\}}} \alpha_{\b{R},\b{s}} \, \b{h}_{\b{s}} > 0$ \qquad where \\[-.2cm]
\begin{compactitem}
\item $\b{r}, \b{r'}$ = rays such that~$\b{R} \cup \{\b{r}\}$ and~$\b{R} \cup \{\b{r}'\}$ are chambers of~$\c{F}$
\item $\alpha_{\b{R},\b{s}}$ = coeff. of unique linear dependence $\displaystyle \smashoperator{\sum_{\b{s} \in \b{R} \, \cup \{\b{r}, \b{r}'\}}} \alpha_{\b{R},\b{s}} \, \b{s} = 0$ with $\alpha_{\b{R},\b{r}} + \alpha_{\b{R},\b{r}'} = 2$
\end{compactitem}
\vspace{-.3cm}
}

\end{slide}

%%%

\begin{slide}{Wall-crossing inequalities}

$\c{F}$ = complete simplicial fan in~$\R^n$ with~$N$ rays \\
$\b{G}$ = $(N \times n)$-matrix whose rows are representatives of the rays of~$\c{F}$ \\
for a height vector~$\b{h} \in \R_{>0}^N$, consider the polytope~$\poly{P}_{\b{h}} = \set{\b{x} \in \R^n}{\b{G}\b{x} \le \b{h}}$

\centerline{\includegraphics[scale=1.7]{wallCrossingInequality2}}

\gboite{
\emph{wall-crossing inequality} for a wall~$\b{R}$ = \qquad $\displaystyle \smashoperator{\sum_{\b{s} \in \b{R} \, \cup \{\b{r}, \b{r}'\}}} \alpha_{\b{R},\b{s}} \, \b{h}_{\b{s}} > 0$ \qquad where \\[-.2cm]
\begin{compactitem}
\item $\b{r}, \b{r'}$ = rays such that~$\b{R} \cup \{\b{r}\}$ and~$\b{R} \cup \{\b{r}'\}$ are chambers of~$\c{F}$
\item $\alpha_{\b{R},\b{s}}$ = coeff. of unique linear dependence $\displaystyle \smashoperator{\sum_{\b{s} \in \b{R} \, \cup \{\b{r}, \b{r}'\}}} \alpha_{\b{R},\b{s}} \, \b{s} = 0$ with $\alpha_{\b{R},\b{r}} + \alpha_{\b{R},\b{r}'} = 2$
\end{compactitem}
\vspace{-.3cm}
}

\gboite{
\centerline{$\c{F}$ is the normal fan of~$\poly{P}_{\b{h}}$ $\iff$ $\b{h}$ satisfies all wall-crossing inequalities of~$\c{F}$}
}

\end{slide}

%%%

\begin{slide}{Wall-crossing inequalities}

$\c{F}$ = complete simplicial fan in~$\R^n$ with~$N$ rays \\
$\b{G}$ = $(N \times n)$-matrix whose rows are representatives of the rays of~$\c{F}$ \\
for a height vector~$\b{h} \in \R_{>0}^N$, consider the polytope~$\poly{P}_{\b{h}} = \set{\b{x} \in \R^n}{\b{G}\b{x} \le \b{h}}$

\vspace{1cm}
\centerline{
	\begin{tabular}{c@{\quad}c@{\quad}c@{\quad}c}
		\includegraphics[scale=1.5]{typeConeFan} & \includegraphics[scale=1.5]{typeConePolytope1b} & \includegraphics[scale=1.5]{typeConePolytope2b} & \includegraphics[scale=1.5]{typeConePolytope3b} \\
		& A & B & C
	\end{tabular}
}

\vspace{-.1cm}
wall-crossing inequalities: \\[-.2cm]
\begin{minipage}{14cm}
\begin{align*}
\text{wall } 1: & \quad h_2 + h_5 > 0
\\
\text{wall } 2: & \quad h_1 + h_3 > h_2
\\
\text{wall } 3: & \quad h_2 + h_4 > h_3
\\
\text{wall } 4: & \quad h_3 + h_5 > h_4
\\
\text{wall } 5: & \quad h_1 + h_4 > 0
\end{align*}
\end{minipage}
\raisebox{-3cm}{\includegraphics[scale=.8]{typeConeABC}}

\end{slide}

%%%%%%%%%

\begin{slide}{Type cone}

$\c{F}$ = complete simplicial fan in~$\R^n$ with~$N$ rays \\
$\b{G}$ = $(N \times n)$-matrix whose rows are representatives of the rays of~$\c{F}$ \\
for a height vector~$\b{h} \in \R_{>0}^N$, consider the polytope~$\poly{P}_{\b{h}} = \set{\b{x} \in \R^n}{\b{G}\b{x} \le \b{h}}$

\gboite{
\emph{type cone}~$\typeCone(\c{F})$ 
\begin{tabular}[t]{@{\;}l}
	= realization space of~$\c{F}$ \\
	= $\set{\b{h} \in \R^N}{\c{F} \text{ is the normal fan of } \poly{P}_{\b{h}}}$ \\
	= $\set{\b{h} \in \R^N}{\b{h} \text{ satisfies all wall-crossing inequalities of } \c{F}}$
\end{tabular}
\hspace{-10cm}\hfill \papier{McMullen ('73)} 
}

\vspace{.2cm}
\centerline{\includegraphics[scale=1.5]{typeConeFan} \qquad \raisebox{.5cm}{\includegraphics[scale=.8]{typeCone}}}

%some properties of $\typeCone(\c{F})$:
%\begin{compactitem}
%\item $\typeCone(\c{F})$ is an open cone \hspace{3.6cm} (dilations preserve normal fans)
%\item $\typeCone(\c{F})$ has lineality space~$\b{G} \, \R^n$ \hspace{1cm} (translations preserve normal fans)
%\item dimension of $\typeCone(\c{F}) / \b{G} \, \R^n$ = $N-n$
%%\item Minkowski sums $\longleftrightarrow$ convex combinations
%\end{compactitem}

\end{slide}

%%%

\begin{slide}{Type cone}

$\c{F}$ = complete simplicial fan in~$\R^n$ with~$N$ rays \\
$\b{G}$ = $(N \times n)$-matrix whose rows are representatives of the rays of~$\c{F}$ \\
for a height vector~$\b{h} \in \R_{>0}^N$, consider the polytope~$\poly{P}_{\b{h}} = \set{\b{x} \in \R^n}{\b{G}\b{x} \le \b{h}}$

\gboite{
\emph{type cone}~$\typeCone(\c{F})$
\begin{tabular}[t]{@{\;}l}
	= realization space of~$\c{F}$ \\
	= $\set{\b{h} \in \R^N}{\c{F} \text{ is the normal fan of } \poly{P}_{\b{h}}}$ \\
	= $\set{\b{h} \in \R^N}{\b{h} \text{ satisfies all wall-crossing inequalities of } \c{F}}$
\end{tabular}
\hspace{-10cm}\hfill \papier{McMullen ('73)} 
}

\vspace{.2cm}
\centerline{\includegraphics[scale=1.5]{typeConeFan} \qquad \raisebox{.5cm}{\includegraphics[scale=.8]{typeCone}}}

some properties of $\typeCone(\c{F})$:
\begin{compactitem}
\item $\typeCone(\c{F})$ is an open cone \hspace{3.6cm} (dilations preserve normal fans)
\item $\typeCone(\c{F})$ has lineality space~$\b{G} \, \R^n$ \hspace{1cm} (translations preserve normal fans)
\item dimension of $\typeCone(\c{F}) / \b{G} \, \R^n$ = $N-n$
%\item Minkowski sums $\longleftrightarrow$ convex combinations
\end{compactitem}

\end{slide}

%%%

\begin{slide}{Type cone}

$\c{F}$ = complete simplicial fan in~$\R^n$ with~$N$ rays \\
$\b{G}$ = $(N \times n)$-matrix whose rows are representatives of the rays of~$\c{F}$ \\
for a height vector~$\b{h} \in \R_{>0}^N$, consider the polytope~$\poly{P}_{\b{h}} = \set{\b{x} \in \R^n}{\b{G}\b{x} \le \b{h}}$

\gboite{
\emph{type cone}~$\typeCone(\c{F})$
\begin{tabular}[t]{@{\;}l}
	= realization space of~$\c{F}$ \\
	= $\set{\b{h} \in \R^N}{\c{F} \text{ is the normal fan of } \poly{P}_{\b{h}}}$ \\
	= $\set{\b{h} \in \R^N}{\b{h} \text{ satisfies all wall-crossing inequalities of } \c{F}}$
\end{tabular}
\hspace{-10cm}\hfill \papier{McMullen ('73)} 
}

\vspace{.2cm}
\centerline{\includegraphics[scale=1.5]{typeConeFan} \qquad \raisebox{.5cm}{\includegraphics[scale=.8]{typeConeCoarsenings}}}

some properties of $\typeCone(\c{F})$:
\begin{compactitem}
%\item $\typeCone(\c{F})$ is an open cone \hspace{3.6cm} (dilations preserve normal fans)
%\item $\typeCone(\c{F})$ has lineality space~$\b{G} \, \R^n$ \hspace{1cm} (translations preserve normal fans)
%\item dimension of $\typeCone(\c{F}) / \b{G} \, \R^n$ = $N-n$
\item boundary of~$\typeCone(\c{F})$ = polytopes whose normal fan coarsens~$\c{F}$ = deformation cone
\item Minkowski sums $\longleftrightarrow$ positive linear combinations
\end{compactitem}

\end{slide}

%%%%%%%%%

\begin{slide}{Exm: submodular functions}

\centerline{
	\begin{tabular}{l@{\qquad}l}
		\includegraphics[scale=1.3]{braidFan}
		&
		\includegraphics[scale=1.3]{permutahedron}
		\\[-.3cm]
		\emph{braid fan} = 
		&
		\emph{permutahedron} = 
		\\
		$\quad \poly{C}(\sigma) = \set{\b{x} \in \R^n}{x_{\sigma(1)} \le \dots \le x_{\sigma(n)}}$
		&
		$\quad \conv \set{[\sigma^{-1}(i)]_{i \in [n]}}{\sigma \in \fS_n}$
	\end{tabular}
}

\end{slide}

%%%

\begin{slide}{Exm: submodular functions}

\centerline{
	\begin{tabular}{l@{\qquad}l}
		\includegraphics[scale=1.3]{braidFan}
		&
		\includegraphics[scale=1.3]{permutahedron}
		\\[-.3cm]
		\emph{braid fan} = 
		&
		\emph{permutahedron} = 
		\\
		$\quad \poly{C}(\sigma) = \set{\b{x} \in \R^n}{x_{\sigma(1)} \le \dots \le x_{\sigma(n)}}$
		&
		$\quad \conv \set{[\sigma^{-1}(i)]_{i \in [n]}}{\sigma \in \fS_n}$
	\end{tabular}
}

\vspace{.1cm}
\gboite{
	\centerline{closed type cone of braid fan = $\{$deformed permutahedra$\}$ = $\{$submodular functions$\}$}
	\vspace{-.1cm}
}

\end{slide}

%%%

\begin{slide}{Exm: submodular functions}

\centerline{
	\begin{tabular}{l@{\qquad}l}
		\includegraphics[scale=1.3]{braidFan}
		&
		\includegraphics[scale=1.3]{permutahedron}
		\\[-.3cm]
		\emph{braid fan} = 
		&
		\emph{permutahedron} = 
		\\
		$\quad \poly{C}(\sigma) = \set{\b{x} \in \R^n}{x_{\sigma(1)} \le \dots \le x_{\sigma(n)}}$
		&
		$\quad \conv \set{[\sigma^{-1}(i)]_{i \in [n]}}{\sigma \in \fS_n}$
	\end{tabular}
}

\vspace{.1cm}
\gboite{
	\emph{deformed permutahedron} = polytope whose normal fan coarsens the braid fan
	\[
	\deformedPermutahedron(\b{z}) = \bigset{\b{x} \in \R_{\phantom{\ge0}}^n}{ \dotprod{\one}{\b{x}} = \b{z}_{[n]} \text{ and } \dotprod{\one_R}{\b{x}} \ge \b{z}_R \text{ for all } R \! \subseteq \! [n]}
	\]
	for some vector~$\b{z} \in \R^{2^{[n]}}$ such that~$\b{z}_R + \b{z}_S \le \b{z}_{R \cup S} + \b{z}_{R \cap S}$ and~$\b{z}_\varnothing = 0$ \\
	\phantom{where~$\c{J} = \set{J \subset [n]}{|J| \ge 2}$} \hfill \papier{Postnikov ('09) \quad Postnikov--Reiner--Williams ('08)}
	\vspace{-.1cm}	
}

\end{slide}

%%%%%%%%%

\begin{slide}{Simplicial type cone}

$\c{F}$ = complete simplicial fan in~$\R^n$ with~$N$ rays \\
$\b{G}$ = $(N \times n)$-matrix whose rows are representatives of the rays of~$\c{F}$ \\
$\b{K}$ = $(N-n) \times N$-matrix that spans the left kernel of~$\b{G}$ (ie. $\b{K}\b{G} = \b{0}$)

\end{slide}

%%%

\begin{slide}{Simplicial type cone}

$\c{F}$ = complete simplicial fan in~$\R^n$ with~$N$ rays \\
$\b{G}$ = $(N \times n)$-matrix whose rows are representatives of the rays of~$\c{F}$ \\
$\b{K}$ = $(N-n) \times N$-matrix that spans the left kernel of~$\b{G}$ (ie. $\b{K}\b{G} = \b{0}$)

\vspace{.8cm}
Classical affine transformation on polytopes:
\[
\begin{array}{ccc}
\poly{P}_{\b{h}} = \set{\b{x} \in \R^n}{\b{G}\b{x} \le \b{h}} & \longrightarrow & \poly{Q}_{\b{h}} = \set{\b{z} \in \R^N}{\b{K}\b{z} = \b{K}\b{h} \text{ and } \b{z} \ge 0} \\
\b{x} & \longmapsto & \b{z} = \b{h} - \b{G} \b{x}
\end{array}
\]

\end{slide}

%%%

\begin{slide}{Simplicial type cone}

$\c{F}$ = complete simplicial fan in~$\R^n$ with~$N$ rays \\
$\b{G}$ = $(N \times n)$-matrix whose rows are representatives of the rays of~$\c{F}$ \\
$\b{K}$ = $(N-n) \times N$-matrix that spans the left kernel of~$\b{G}$ (ie. $\b{K}\b{G} = \b{0}$)

\vspace{.8cm}
Classical affine transformation on polytopes:
\[
\begin{array}{ccc}
\poly{P}_{\b{h}} = \set{\b{x} \in \R^n}{\b{G}\b{x} \le \b{h}} & \longrightarrow & \poly{Q}_{\b{h}} = \set{\b{z} \in \R^N}{\b{K}\b{z} = \b{K}\b{h} \text{ and } \b{z} \ge 0} \\
\b{x} & \longmapsto & \b{z} = \b{h} - \b{G} \b{x}
\end{array}
\]

\vspace{-.3cm}
\gboite{
All polytopal realizations of~$\c{F}$ are affinely equivalent to
\vspace{-.2cm}
\[
\poly{Q}_{\b{h}} = \set{\b{z} \in \R^N}{\b{K}\b{z} = \b{K}\b{h} \text{ and } \b{z} \ge 0}
\]

\vspace{-.2cm}
for any~$\b{h}$ in the type cone~$\typeCone(\c{F})$.
\vspace{-.2cm}
}

\end{slide}

%%%

\begin{slide}{Simplicial type cone}

$\c{F}$ = complete simplicial fan in~$\R^n$ with~$N$ rays \\
$\b{G}$ = $(N \times n)$-matrix whose rows are representatives of the rays of~$\c{F}$ \\
$\b{K}$ = $(N-n) \times N$-matrix that spans the left kernel of~$\b{G}$ (ie. $\b{K}\b{G} = \b{0}$)

\vspace{.8cm}
Classical affine transformation on polytopes:
\[
\begin{array}{ccc}
\poly{P}_{\b{h}} = \set{\b{x} \in \R^n}{\b{G}\b{x} \le \b{h}} & \longrightarrow & \poly{Q}_{\b{h}} = \set{\b{z} \in \R^N}{\b{K}\b{z} = \b{K}\b{h} \text{ and } \b{z} \ge 0} \\
\b{x} & \longmapsto & \b{z} = \b{h} - \b{G} \b{x}
\end{array}
\]

\vspace{-.3cm}
\gboite{
All polytopal realizations of~$\c{F}$ are affinely equivalent to
\vspace{-.2cm}
\[
\poly{Q}_{\b{h}} = \set{\b{z} \in \R^N}{\b{K}\b{z} = \b{K}\b{h} \text{ and } \b{z} \ge 0}
\]

\vspace{-.2cm}
for any~$\b{h}$ in the type cone~$\typeCone(\c{F})$.
\vspace{-.2cm}
}

\gboite{
Assume that the type cone~$\typeCone(\c{F})$ is simplicial. \\
$\b{K}$ = $(N-n) \times N$-matrix whose rows are inner normal vectors of the facets of~$\typeCone(\Fan)$. \\
All polytopal realizations of~$\c{F}$ are affinely equivalent to
\vspace{-.2cm}
\[
\poly{R}_{\b{\ell}} = \set{\b{z} \in \R^N}{\b{K} \b{z} = \b{\ell} \text{ and } \b{z} \ge 0}
\]

\vspace{-.2cm}
for any positive vector~$\b{\ell} \in \R_{>0}^{N-n}$.
\hfill\papier{Padrol--Palu--P.--Plamondon ('19$^+$)}
\vspace{-.2cm}

}

\end{slide}

%%%

\begin{slide}{Simplicial type cone}

\gboite{
Assume that the type cone~$\typeCone(\c{F})$ is simplicial. \\
$\b{K}$ = $(N-n) \times N$-matrix whose rows are inner normal vectors of the facets of~$\typeCone(\Fan)$. \\
All polytopal realizations of~$\c{F}$ are affinely equivalent to
\vspace{-.2cm}
\[
\poly{R}_{\b{\ell}} = \set{\b{z} \in \R^N}{\b{K} \b{z} = \b{\ell} \text{ and } \b{z} \ge 0}
\]

\vspace{-.2cm}
for any positive vector~$\b{\ell} \in \R_{>0}^{N-n}$.
\hfill\papier{Padrol--Palu--P.--Plamondon ('19$^+$)}
\vspace{-.2cm}

}

\vspace{.6cm}
Fundamental exms: \emph{$\b{g}$-vector fans of cluster-like complexes}

\vspace{.3cm}
\centerline{
    	\begin{overpic}[scale=.7]{gvectorLikeFans}
    	\put(425,30){\normalsize $\left[\begin{array}{@{}r@{}r@{}r@{}} 0 & -1 & 1 \\ 1 & 0 & -1 \\ -1 & 1 & 0 \end{array}\right]$}
%		\put(75,92){$\boxed{B_\circ \! = \!\! {\tiny}}$}
		\put(310,100){${\scriptstyle x_1}$}
		\put(334,140){${\scriptstyle x_2}$}
		\put(360,100){${\scriptstyle x_3}$}
		\put(380,107){$\frac{x_2 + x_3}{x_1}$}
		\put(285,70){$\frac{x_1 + x_3}{x_2}$}
		\put(298,158){$\frac{x_1 + x_2}{x_3}$}
		\put(400,150){$\frac{x_1 + x_2 + x_3}{x_1 x_3}$}
		\put(310,20){$\frac{x_1 + x_2 + x_3}{x_1 x_2}$}
		\put(215,150){$\frac{x_1 + x_2 + x_3}{x_2 x_3}$}
    	\end{overpic}
}

\centerline{
\begin{tabular}{@{\hspace{1cm}}c@{\hspace{1cm}}c@{\hspace{1cm}}c}
	\emph{sylvester fans}
	&
	\emph{finite type $\b{g}$-vector fans}
	&
	\emph{finite gentle fans}
	\\
	&
	wrt any seed (acyclic or not)
	&
	for brick and $2$-acyclic quivers
	\\[-.1cm]
	\papier{Arkani-Hamed--Bai--He--Yan ('18)}
	&
	\papier{BMDMTY ('18$^+$)}
	% \papier{Bazier-Matte--Douville--Mousavand--Thomas--Y\i{}ld\i{}r\i{}m ('18$^+$)}
	&
	\papier{Palu--P.--Plamondon ('18)}
\end{tabular}
}

\end{slide}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\partie{Type cones of g-vector fans}

%%%%%%%%%

\begin{slide}{Sylvester fan and classical associahedron}

\vspace{.3cm}
\centerline{
	\begin{tabular}{l@{\quad}l}
		\hspace{1cm}\includegraphics[scale=1.3]{sylvesterFan}
		&
		\hspace{-1cm}\includegraphics[scale=1.3]{associahedronBinaryTrees}
		\\[-.1cm]
		\emph{sylvester fan} = 
		&
		\emph{associahedron} = 
		\\
		$\quad \poly{C}(T) = \set{\b{x} \in \R^n}{x_i \le x_j \text{ if $i \to j$ in T}}$ \hspace{-.5cm}
		&
		$\quad \conv \set{[\ell(T,i) \cdot r(T,i)]_{i \in [n]}}{\tree \text{ binary tree}}$ \hspace{-2cm}
		\\
		&
		\hfill \papier{Shnider--Sternberg ('93)}
		\\[-.3cm]
		&
		\hfill \papier{Loday ('04)}
	\end{tabular}
}

\end{slide}

%%%

\begin{slide}{Sylvester fan and classical associahedron}

\vspace{.3cm}
\centerline{
	\begin{tabular}{l@{\hspace{1.4cm}}l}
		\hspace{1cm}\includegraphics[scale=1.3]{sylvesterFan}
		&
		\raisebox{.5cm}{\includegraphics[scale=1.3]{braidFan}}
		\\[-.1cm]
		\emph{sylvester fan} = 
		&
		\emph{braid fan} =
		\\
		$\quad \poly{C}(T) = \set{\b{x} \in \R^n}{x_i \le x_j \text{ if $i \to j$ in T}}$
		&
		$\quad \poly{C}(\sigma) = \set{\b{x} \in \R^n}{x_{\sigma(1)} \le \dots \le x_{\sigma(n)}}$
	\end{tabular}
}

\vspace{1cm}
quotient fan of the braid fan by sylvester congruence \\
(ie. $\poly{C}(T)$ obtained by glueing $\poly{C}(\sigma)$ for all~$\sigma$ in the same BST insertion~fiber)

\end{slide}

%%%

\begin{slide}{Sylvester fan and classical associahedron}

\vspace{.3cm}
\centerline{
	\begin{tabular}{l@{\quad}l}
		\hspace{1cm}\includegraphics[scale=1.3]{sylvesterFanTriangulations}
		&
		\hspace{-1cm}\includegraphics[scale=1.3]{associahedronTriangulations}
		\\[-.1cm]
		\emph{sylvester fan}
		&
		\emph{associahedron}
		\\
		\quad chambers $\longleftrightarrow$ triangulations
		&
		\quad vertices $\longleftrightarrow$ triangulations
		\\
		\phantom{$\quad \poly{C}(T) = \set{\b{x} \in \R^n}{x_i \le x_j \text{ if $i \to j$ in T}}$ \hspace{-.5cm}}
		&
		\phantom{$\quad \conv \set{[\ell(T,i) \cdot r(T,i)]_{i \in [n]}}{\tree \text{ binary tree}}$ \hspace{-2cm}}
	\end{tabular}
}

\end{slide}

%%%

\begin{slide}{Sylvester fan and classical associahedron}

\vspace{.3cm}
\centerline{
	\begin{tabular}{l@{\quad}l}
		\hspace{1cm}\includegraphics[scale=1.3]{sylvesterFanDiagonals}
		&
		\hspace{-1cm}\includegraphics[scale=1.3]{associahedronTriangulations}
		\\[-.1cm]
		\emph{sylvester fan}
		&
		\emph{associahedron}
		\\
		\quad chambers $\longleftrightarrow$ triangulations
		&
		\quad vertices $\longleftrightarrow$ triangulations
		\\
		\hspace{2.2cm} rays $\longleftrightarrow$ internal diagonals
		&
		\hspace{1cm} facets $\longleftrightarrow$ internal diagonals
		\\
		\phantom{$\quad \poly{C}(T) = \set{\b{x} \in \R^n}{x_i \le x_j \text{ if $i \to j$ in T}}$ \hspace{-.5cm}}
		&
		\phantom{$\quad \conv \set{[\ell(T,i) \cdot r(T,i)]_{i \in [n]}}{\tree \text{ binary tree}}$ \hspace{-2cm}}
	\end{tabular}
}

\end{slide}

%%%

\begin{slide}{Sylvester fan and classical associahedron}

\vspace{.3cm}
\centerline{
	\begin{tabular}{l@{\quad}l}
		\hspace{1cm}\includegraphics[scale=1.3]{sylvesterFanDiagonals}
		&
		\hspace{-1cm}\includegraphics[scale=1.3]{associahedronTriangulations}
		\\[-.1cm]
		\emph{sylvester fan}
		&
		\emph{associahedron}
		\\
		\quad chambers $\longleftrightarrow$ triangulations
		&
		\quad vertices $\longleftrightarrow$ triangulations
		\\
		\hspace{2.2cm} rays $\longleftrightarrow$ internal diagonals
		&
		\hspace{1cm} facets $\longleftrightarrow$ internal diagonals
		\\
		\hspace{.35cm} exch. rays $\longleftrightarrow$ pairs crossing diagonals
		\\
		\phantom{$\quad \poly{C}(T) = \set{\b{x} \in \R^n}{x_i \le x_j \text{ if $i \to j$ in T}}$ \hspace{-.5cm}}
		&
		\phantom{$\quad \conv \set{[\ell(T,i) \cdot r(T,i)]_{i \in [n]}}{\tree \text{ binary tree}}$ \hspace{-2cm}}
	\end{tabular}
}

\end{slide}

%%%

\begin{slide}{Sylvester fan and classical associahedron}

\vspace{.3cm}
\hspace{.65cm}
\raisebox{-6cm}{\includegraphics[scale=1.3]{sylvesterFanDiagonals}}
\quad
\begin{minipage}{13cm}
\emph{wall crossing inequalities} = \\
\hspace*{1cm} $\b{z}_{(a,c)} + \b{z}_{(b,d)} - \b{z}_{(b,c)} - \b{z}_{(a,d)} > 0$ \\
\hspace*{1cm} for all~$0 \le a < b < c < d \le n+2$

\vspace{.5cm}
\emph{facet defining inequalities} = \\
\hspace*{1cm} $\b{z}_{(a-1,b)} + \b{z}_{(a,b+1)} - \b{z}_{(a,b)} - \b{z}_{(a-1,b+1)} > 0$ \\
\hspace*{1cm} for all~$1 \le a < b \le n+1$

\vspace{.5cm}
\gboite{
$\Longrightarrow$ simplicial type cone \\
(\#\,facets = $\binom{n+1}{2} = \frac{n(n+3)}{2} - n = N - n$)
\vspace{-.1cm}
}
\vspace{.5cm}
\end{minipage}

\vspace{-.3cm}
\gboite{
	Let $X(n) = \set{(a,b)}{0 \le a < b \le n+2}$ and $Y(n) = \set{(a,b)}{1 \le a < b \le n-1}$. \\
	For any~$\b{\ell} \in \R_{>0}^{Y(n)}$, the polytope
	\[
	\set{\b{z} \in \R^{X(n)}}{\begin{array}{@{}l} \b{z} \ge 0, \quad \b{z}_{(0,n+2)} = 0 \quad\text{and}\quad \b{z}_{(a,a+1)} = 0 \text{ for all } 0 \le a \le n+1 \\ \b{z}_{(a-1,b)} + \b{z}_{(a,b+1)} - \b{z}_{(a,b)} - \b{z}_{(a-1,b+1)} = \b{\ell}_{(a,b)} \text{ for all } (a,b) \in Y(n) \end{array}}
	\]
	is an associahedron. \hfill \papier{Arkani-Hamed--Bai--He--Yan ('18)}
	\vspace{-.1cm}
}

\end{slide}

%%%%%%%%%

\begin{slide}{G-vector fans and generalized associahedra}

$B_\circ$ = finite type exchange matrix (acyclic or not, simply-laced or not) \\
$\c{A}(B_\circ)$ = cluster algebra with principal coefficients and initial exchange matrix~$B_\circ$ \\
$\c{F}(B_\circ)$ = $\b{g}$-vector fan of~$\c{A}(B_\circ)$

\vspace{.7cm}
\emph{Exm:} stereographic projections of type $A_3$ and $C_3$ cyclic $\b{g}$-vector fans

\vspace{.5cm}
\centerline{
\begin{tabular}{c@{\qquad}c}
	\includegraphics[scale=.6]{A3_fan_3}
	&
	\includegraphics[scale=.6]{C3_fan}
	\\
	$\left[\begin{array}{@{}c@{\;}c@{\;}c@{}} 0 & -1 & 1 \\ 1 & 0 & -1 \\ -1 & 1 & 0 \end{array}\right]$
	&
	$\left[\begin{array}{@{}c@{\;}c@{\;}c@{}} 0 & -1 & 2 \\ 1 & 0 & -2 \\ -1 & 1 & 0 \end{array}\right]$
\end{tabular}
}

\end{slide}

%%%

\begin{slide}{G-vector fans and generalized associahedra}

$B_\circ$ = finite type exchange matrix (acyclic or not, simply-laced or not) \\
$\c{A}(B_\circ)$ = cluster algebra with principal coefficients and initial exchange matrix~$B_\circ$ \\
$\c{F}(B_\circ)$ = $\b{g}$-vector fan of~$\c{A}(B_\circ)$

\newcommand{\fitClusterVariable}[1]{\parbox[c][1cm][c]{2cm}{\centering $#1$}}

\vspace{.3cm}
\hspace{-1.5cm}
\begin{tikzpicture}
	\matrix (m) [matrix of math nodes, row sep=1cm, column sep=.4cm, nodes={anchor=center, align=center, inner sep=0pt}]{
		\fitClusterVariable{\phantom{1}} & \node (e1) {\red \circled{E}}; & \fitClusterVariable{\frac{x_1 + x_2 + x_3}{x_2 x_3}} && \fitClusterVariable{x_3} & \node (c) {\red \circled{C}}; & \fitClusterVariable{\frac{x_1 + x_2 + x_3}{x_1 x_3}} && \fitClusterVariable{x_1} & \node (a2) {\red \circled{A}}; & \fitClusterVariable{\phantom{1}} \\
		& \fitClusterVariable{\frac{x_1 + x_2}{x_3}} & \node (f1) {\red \circled{F}}; & \fitClusterVariable{\frac{x_1 + x_3}{x_2}} & \node (b) {\red \circled{B}}; & \fitClusterVariable{\frac{x_2 + x_3}{x_1}} & \node (d) {\red \circled{D}}; & \fitClusterVariable{\frac{x_1 + x_2}{x_3}} & \node (f2) {\red \circled{F}}; & \fitClusterVariable{\frac{x_1 + x_3}{x_2}} \\
		\fitClusterVariable{\phantom{1}} && \fitClusterVariable{x_1} & \node (a1) {\red \circled{A}}; & \fitClusterVariable{\frac{x_1 + x_2 + x_3}{x_1 x_2}} && \fitClusterVariable{x_2} & \node (e2) {\red \circled{E}}; & \fitClusterVariable{\frac{x_1 + x_2 + x_3}{x_2 x_3}} && \fitClusterVariable{\phantom{1}} \\};
	\draw[densely dotted, thick] (m-1-1) -- (m-2-2);
	\draw[densely dotted, thick] (m-3-1) -- (m-2-2);
	\draw[->] (m-2-2) -- (m-1-3);
	\draw[->] (m-2-2) -- (m-3-3);
	\draw[->] (m-1-3) -- (m-2-4);
	\draw[->] (m-3-3) -- (m-2-4);
	\draw[->] (m-2-4) -- (m-1-5);
	\draw[->] (m-2-4) -- (m-3-5);
	\draw[->] (m-1-5) -- (m-2-6);
	\draw[->] (m-3-5) -- (m-2-6);
	\draw[->] (m-2-6) -- (m-1-7);
	\draw[->] (m-2-6) -- (m-3-7);
	\draw[->] (m-1-7) -- (m-2-8);
	\draw[->] (m-3-7) -- (m-2-8);
	\draw[->] (m-2-8) -- (m-1-9);
	\draw[->] (m-2-8) -- (m-3-9);
	\draw[->] (m-1-9) -- (m-2-10);
	\draw[->] (m-3-9) -- (m-2-10);
	\draw[densely dotted, thick] (m-2-10) -- (m-1-11);
	\draw[densely dotted, thick] (m-2-10) -- (m-3-11);
	\draw[red] (a1) -- (m-3-3);
	\draw[red] (a1) -- (m-3-5);
	\draw[red] (a1) -- (m-2-4);
	\draw[red] (a2) -- (m-1-9);
	\draw[red, densely dotted, thick] (a2) -- (m-1-11);
	\draw[red] (a2) -- (m-2-10);
	\draw[red] (b) -- (m-2-4);
	\draw[red] (b) -- (m-2-6);
	\draw[red] (b) -- (m-1-5);
	\draw[red] (b) -- (m-3-5);
	\draw[red] (c) -- (m-1-5);
	\draw[red] (c) -- (m-1-7);
	\draw[red] (c) -- (m-2-6);
	\draw[red] (d) -- (m-2-6);
	\draw[red] (d) -- (m-2-8);
	\draw[red] (d) -- (m-1-7);
	\draw[red] (d) -- (m-3-7);
	\draw[red, densely dotted, thick] (e1) -- (m-1-1);
	\draw[red] (e1) -- (m-1-3);
	\draw[red] (e1) -- (m-2-2);
	\draw[red] (e2) -- (m-3-7);
	\draw[red] (e2) -- (m-3-9);
	\draw[red] (e2) -- (m-2-8);
	\draw[red] (f1) -- (m-2-2);
	\draw[red] (f1) -- (m-2-4);
	\draw[red] (f1) -- (m-1-3);
	\draw[red] (f1) -- (m-3-3);
	\draw[red] (f2) -- (m-2-8);
	\draw[red] (f2) -- (m-2-10);
	\draw[red] (f2) -- (m-1-9);
	\draw[red] (f2) -- (m-3-9);
\end{tikzpicture}

%\begin{tikzpicture}
%	\matrix (m) [matrix of math nodes, row sep=.7cm, column sep=-1cm, nodes={anchor=center, align=center, inner sep=0pt}]{
%		& \fitClusterVariable{\frac{x_1^2 + x_2^2 + 2 x_1 x_3 + x_3^2}{x_2^2 x_3}} && \fitClusterVariable{x_3} & \node (c) {\red \circled{C}}; & \fitClusterVariable{\frac{x_1^2 + x_2^2 + 2 x_2 x_3 + x_3^2}{x_1^2 x_3}} & \node (e) {\red \circled{E}}; & \fitClusterVariable{\frac{x_1^2 + x_2^2}{x_3}} & \node (h) {\red \circled{H}}; & \fitClusterVariable{\frac{x_1^2 + x_2^2 + 2 x_1 x_3 + x_3^2}{x_2^2 x_3}} && \fitClusterVariable{\phantom{1}} \\
%		\fitClusterVariable{\phantom{1}} & \node (i1) {\red \circled{I}}; & \fitClusterVariable{\frac{x_1 + x_3}{x_2}} & \node (b) {\red \circled{B}}; & \fitClusterVariable{\frac{x_2 + x_3}{x_1}} & \node (d) {\red \circled{D}}; & \fitClusterVariable{\frac{x_1^2 + x_2^2 + x_2 x_3}{x_1 x_3}} & \node (g) {\red \circled{G}}; & \fitClusterVariable{\frac{x_1^2 + x_2^2 + x_1 x_3}{x_2 x_3}} & \node (i2) {\red \circled{I}}; & \fitClusterVariable{\frac{x_1 + x_3}{x_2}} & \\
%		& \fitClusterVariable{x_1} & \node (a1) {\red \circled{A}}; & \fitClusterVariable{\frac{x_1 + x_2 + x_3}{x_1 x_2}} && \fitClusterVariable{x_2} & \node (f) {\red \circled{F}}; & \fitClusterVariable{\frac{x_1^2 + x_2^2 + x_1 x_3 + x_2 x_3}{x_1 x_2 x_3}} && \fitClusterVariable{x_1} & \node (a2) {\red \circled{A}}; & \fitClusterVariable{\phantom{1}} \\};
%	\draw[densely dotted, thick] (m-2-1) -- (m-1-2);
%	\draw[densely dotted, thick] (m-2-1) -- (m-3-2);
%	\draw[->] (m-1-2) -- (m-2-3);
%	\draw[->] (m-3-2) -- (m-2-3);
%	\draw[->] (m-2-3) -- (m-1-4);
%	\draw[->] (m-2-3) -- (m-3-4);
%	\draw[->] (m-1-4) -- (m-2-5);
%	\draw[->] (m-3-4) -- (m-2-5);
%	\draw[->] (m-2-5) -- (m-1-6);
%	\draw[->] (m-2-5) -- (m-3-6);
%	\draw[->] (m-1-6) -- (m-2-7);
%	\draw[->] (m-3-6) -- (m-2-7);
%	\draw[->] (m-2-7) -- (m-1-8);
%	\draw[->] (m-2-7) -- (m-3-8);
%	\draw[->] (m-1-8) -- (m-2-9);
%	\draw[->] (m-3-8) -- (m-2-9);
%	\draw[->] (m-2-9) -- (m-1-10);
%	\draw[->] (m-2-9) -- (m-3-10);
%	\draw[->] (m-1-10) -- (m-2-11);
%	\draw[->] (m-3-10) -- (m-2-11);
%	\draw[densely dotted, thick] (m-2-11) -- (m-1-12);
%	\draw[densely dotted, thick] (m-2-11) -- (m-3-12);
%	\draw[red] (a1) -- (m-3-2);
%	\draw[red] (a1) -- (m-3-4);
%	\draw[red] (a1) -- (m-2-3);
%	\draw[red] (a2) -- (m-3-10);
%	\draw[red] (a2) -- (m-3-12);
%	\draw[red] (a2) -- (m-2-11);
%	\draw[red] (b) -- (m-2-3);
%	\draw[red] (b) -- (m-2-5);
%	\draw[red] (b) -- (m-1-4);
%	\draw[red] (b) -- (m-3-4);
%	\draw[red] (c) -- (m-1-4);
%	\draw[red] (c) -- (m-1-6);
%	\draw[red] (c) -- (m-2-5);
%	\draw[red] (d) -- (m-2-5);
%	\draw[red] (d) -- (m-2-7);
%	\draw[red] (d) -- (m-1-6);
%	\draw[red] (d) -- (m-3-6);
%	\draw[red] (e) -- (m-1-6);
%	\draw[red] (e) -- (m-1-8);
%	\draw[red] (e) -- (m-2-7);
%	\draw[red] (f) -- (m-3-6);
%	\draw[red] (f) -- (m-3-8);
%	\draw[red] (f) -- (m-2-7);
%	\draw[red] (g) -- (m-2-7);
%	\draw[red] (g) -- (m-2-9);
%	\draw[red] (g) -- (m-1-8);
%	\draw[red] (g) -- (m-3-8);
%	\draw[red] (h) -- (m-1-8);
%	\draw[red] (h) -- (m-1-10);
%	\draw[red] (h) -- (m-2-9);
%	\draw[red] (i1) -- (m-2-1);
%	\draw[red] (i1) -- (m-2-3);
%	\draw[red] (i1) -- (m-1-2);
%	\draw[red] (i1) -- (m-3-2);
%	\draw[red] (i2) -- (m-2-9);
%	\draw[red] (i2) -- (m-2-11);
%	\draw[red] (i2) -- (m-1-10);
%	\draw[red] (i2) -- (m-3-10);
%\end{tikzpicture}

\vspace{.3cm}
\emph{mesh mutation} = 
\begin{tabular}[t]{@{\;}l}
	mutation~$(B, X) \to (B',X')$ with $X \ssm \{x\} = X' \ssm \{x'\}$ \\
	such that~$b_{xy} \ge 0$ for all~$y \in X$
\end{tabular} \\[.2cm]
\emph{initial mesh mutation} = ends at an initial cluster variable~$x'$

\vspace{.3cm}
\gboite{
	facets of type cone of~$\c{F}(B_\circ)$ = $\b{g}$-vector dependences of non-initial mesh mutations
}

\gboite{
	\centerline{$\Longrightarrow$ simplicial type cone}
	\centerline{(\#\,non-initial mesh mutations = \#\,cluster variables $-$ \#\,initial variables)}
}

\end{slide}

%%%

\begin{slide}{G-vector fans and generalized associahedra}

$B_\circ$ = finite type exchange matrix (acyclic or not, simply-laced or not) \\
$\c{A}(B_\circ)$ = cluster algebra with principal coefficients and initial exchange matrix~$B_\circ$ \\
$\c{F}(B_\circ)$ = $\b{g}$-vector fan of~$\c{A}(B_\circ)$

\newcommand{\fitClusterVariable}[1]{\parbox[c][1cm][c]{2cm}{\centering $#1$}}

\vspace{.3cm}
\hspace{-1.5cm}
\begin{tikzpicture}
	\matrix (m) [matrix of math nodes, row sep=1cm, column sep=.4cm, nodes={anchor=center, align=center, inner sep=0pt}]{
		\fitClusterVariable{\phantom{1}} & \node (e1) {\red \circled{E}}; & \fitClusterVariable{\frac{x_1 + x_2 + x_3}{x_2 x_3}} && \fitClusterVariable{x_3} & \node (c) {\red \circled{C}}; & \fitClusterVariable{\frac{x_1 + x_2 + x_3}{x_1 x_3}} && \fitClusterVariable{x_1} & \node (a2) {\red \circled{A}}; & \fitClusterVariable{\phantom{1}} \\
		& \fitClusterVariable{\frac{x_1 + x_2}{x_3}} & \node (f1) {\red \circled{F}}; & \fitClusterVariable{\frac{x_1 + x_3}{x_2}} & \node (b) {\red \circled{B}}; & \fitClusterVariable{\frac{x_2 + x_3}{x_1}} & \node (d) {\red \circled{D}}; & \fitClusterVariable{\frac{x_1 + x_2}{x_3}} & \node (f2) {\red \circled{F}}; & \fitClusterVariable{\frac{x_1 + x_3}{x_2}} \\
		\fitClusterVariable{\phantom{1}} && \fitClusterVariable{x_1} & \node (a1) {\red \circled{A}}; & \fitClusterVariable{\frac{x_1 + x_2 + x_3}{x_1 x_2}} && \fitClusterVariable{x_2} & \node (e2) {\red \circled{E}}; & \fitClusterVariable{\frac{x_1 + x_2 + x_3}{x_2 x_3}} && \fitClusterVariable{\phantom{1}} \\};
	\draw[densely dotted, thick] (m-1-1) -- (m-2-2);
	\draw[densely dotted, thick] (m-3-1) -- (m-2-2);
	\draw[->] (m-2-2) -- (m-1-3);
	\draw[->] (m-2-2) -- (m-3-3);
	\draw[->] (m-1-3) -- (m-2-4);
	\draw[->] (m-3-3) -- (m-2-4);
	\draw[->] (m-2-4) -- (m-1-5);
	\draw[->] (m-2-4) -- (m-3-5);
	\draw[->] (m-1-5) -- (m-2-6);
	\draw[->] (m-3-5) -- (m-2-6);
	\draw[->] (m-2-6) -- (m-1-7);
	\draw[->] (m-2-6) -- (m-3-7);
	\draw[->] (m-1-7) -- (m-2-8);
	\draw[->] (m-3-7) -- (m-2-8);
	\draw[->] (m-2-8) -- (m-1-9);
	\draw[->] (m-2-8) -- (m-3-9);
	\draw[->] (m-1-9) -- (m-2-10);
	\draw[->] (m-3-9) -- (m-2-10);
	\draw[densely dotted, thick] (m-2-10) -- (m-1-11);
	\draw[densely dotted, thick] (m-2-10) -- (m-3-11);
	\draw[red] (a1) -- (m-3-3);
	\draw[red] (a1) -- (m-3-5);
	\draw[red] (a1) -- (m-2-4);
	\draw[red] (a2) -- (m-1-9);
	\draw[red, densely dotted, thick] (a2) -- (m-1-11);
	\draw[red] (a2) -- (m-2-10);
	\draw[red] (b) -- (m-2-4);
	\draw[red] (b) -- (m-2-6);
	\draw[red] (b) -- (m-1-5);
	\draw[red] (b) -- (m-3-5);
	\draw[red] (c) -- (m-1-5);
	\draw[red] (c) -- (m-1-7);
	\draw[red] (c) -- (m-2-6);
	\draw[red] (d) -- (m-2-6);
	\draw[red] (d) -- (m-2-8);
	\draw[red] (d) -- (m-1-7);
	\draw[red] (d) -- (m-3-7);
	\draw[red, densely dotted, thick] (e1) -- (m-1-1);
	\draw[red] (e1) -- (m-1-3);
	\draw[red] (e1) -- (m-2-2);
	\draw[red] (e2) -- (m-3-7);
	\draw[red] (e2) -- (m-3-9);
	\draw[red] (e2) -- (m-2-8);
	\draw[red] (f1) -- (m-2-2);
	\draw[red] (f1) -- (m-2-4);
	\draw[red] (f1) -- (m-1-3);
	\draw[red] (f1) -- (m-3-3);
	\draw[red] (f2) -- (m-2-8);
	\draw[red] (f2) -- (m-2-10);
	\draw[red] (f2) -- (m-1-9);
	\draw[red] (f2) -- (m-3-9);
\end{tikzpicture}

\gboite{
	$\c{V}(B_\circ)$ = $\{$cluster variables$\}$. \\
	$\c{M}(B_\circ)$ = $\{(x,x')$ exchangeable by a non-initial mesh mutation$\}$. \\
	For any~$\b{\ell} \in \R_{>0}^{\c{M}(B_\circ)}$, the polytope
	\[
	\biggset{\b{z} \in \R^{\c{V}(B_\circ)}}{\b{z} \ge 0 \;\;\text{and}\;\; \b{z}_x + \b{z}_{x'} - \sum_y \alpha_{x,x'}(y) \b{z}_y = \b{\ell}_{x,x'} \text{ for all } (x,x') \in \c{M}(B_\circ)}
	\]

	\vspace{-1cm}
	is a generalized associahedron. \hspace{3.1cm} $\overset{\big\uparrow}{\alpha_{x,x'}} = |b_{x,y}|$ if $y \in X$ and $0$ otherwise%\begin{cases} |b_{x,y}| & \text{if } y \in X \\ 0 & \text{otherwise} \end{cases}$

	\hfill\papier{Bazier-Matte--Douville--Mousavand--Thomas--Y\i{}ld\i{}r\i{}m ('18$^+$)} \\[-.2cm]
	\hspace*{0pt plus 1 fill} \papier{Padrol--Palu--P.--Plamondon ('19$^+$)}

	\vspace{-.1cm}
}

\end{slide}

%%%%%%%%%

\begin{slide}{Simplicial type cone}

\gboite{
Assume that the type cone~$\typeCone(\c{F})$ is simplicial. \\
$\b{K}$ = $(N-n) \times N$-matrix whose rows are inner normal vectors of the facets of~$\typeCone(\Fan)$. \\
All polytopal realizations of~$\c{F}$ are affinely equivalent to
\vspace{-.2cm}
\[
\poly{R}_{\b{\ell}} = \set{\b{z} \in \R^N}{\b{K} \b{z} = \b{\ell} \text{ and } \b{z} \ge 0}
\]

\vspace{-.2cm}
for any positive vector~$\b{\ell} \in \R_{>0}^{N-n}$.
\hfill\papier{Padrol--Palu--P.--Plamondon ('19$^+$)}
\vspace{-.2cm}

}

\vspace{.6cm}
Fundamental exms: \emph{$\b{g}$-vector fans of cluster-like complexes}

\vspace{.3cm}
\centerline{
    	\begin{overpic}[scale=.7]{gvectorLikeFans}
    	\put(425,30){\normalsize $\left[\begin{array}{@{}r@{}r@{}r@{}} 0 & -1 & 1 \\ 1 & 0 & -1 \\ -1 & 1 & 0 \end{array}\right]$}
%		\put(75,92){$\boxed{B_\circ \! = \!\! {\tiny}}$}
		\put(310,100){${\scriptstyle x_1}$}
		\put(334,140){${\scriptstyle x_2}$}
		\put(360,100){${\scriptstyle x_3}$}
		\put(380,107){$\frac{x_2 + x_3}{x_1}$}
		\put(285,70){$\frac{x_1 + x_3}{x_2}$}
		\put(298,158){$\frac{x_1 + x_2}{x_3}$}
		\put(400,150){$\frac{x_1 + x_2 + x_3}{x_1 x_3}$}
		\put(310,20){$\frac{x_1 + x_2 + x_3}{x_1 x_2}$}
		\put(215,150){$\frac{x_1 + x_2 + x_3}{x_2 x_3}$}
    	\end{overpic}
}

\centerline{
\begin{tabular}{@{\hspace{1cm}}c@{\hspace{1cm}}c@{\hspace{1cm}}c}
	\emph{sylvester fans}
	&
	\emph{finite type $\b{g}$-vector fans}
	&
	\emph{finite gentle fans}
	\\
	&
	wrt any seed (acyclic or not)
	&
	for brick and $2$-acyclic quivers
	\\[-.1cm]
	\papier{Arkani-Hamed--Bai--He--Yan ('18)}
	&
	\papier{BMDMTY ('18$^+$)}
	% \papier{Bazier-Matte--Douville--Mousavand--Thomas--Y\i{}ld\i{}r\i{}m ('18$^+$)}
	&
	\papier{Palu--P.--Plamondon ('18)}
\end{tabular}
}

\end{slide}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage
\phantomsection\label{thanks}

\vspace*{-9cm}\hspace*{-39.5cm}
\includegraphics[width=4\textwidth]{gvectorLikeFans}

\vspace*{-11cm}\hspace{15cm}
{\blue \textegrand THANKS}

\end{document}

### 2021-06-16 thirdPaper/draft/typeConeAssociahedra.tex
some edits suggested by reviewer

@@
 \DeclareMathOperator{\cone}{cone} % cone hull
+\DeclareMathOperator{\rank}{rank} % rank
 
@@
 \author{Arnau Padrol}
-\address[Arnau Padrol]{Institut de Mathématiques de Jussieu - Paris Rive Gauche, Sorbonne Universit\'e, Paris}
+\address[Arnau Padrol]{Institut de Math\'{e}matiques de Jussieu - Paris Rive Gauche, Sorbonne Universit\'e, Paris}
 \email{arnau.padrol@imj-prg.fr.}
@@
 We now give a more detailed overview of our main results and the structure of the article.
-In particular, some of the geometric realizations in~\cref{part:geometry} depend on algebraic results whose proves are delayed until~\cref{part:algebra}.
+In particular, some of the geometric realizations in~\cref{part:geometry} depend on algebraic results whose proofs are delayed until~\cref{part:algebra}.
 The goal of this section is to clarify their logical dependencies, summarized in the schematic diagram depicted at the end.
@@
 \end{itemize}
-A fan is \defn{simplicial} if all its cones are, \defn{complete} if the union of its cones covers the ambient space~$\R^n$, and \defn{essential} if it contains the cone~$\{\b{0}\}$.
-Note that every complete fan is the product of an essential fan with its lineality space.
+A fan is \defn{simplicial} if all its cones are simplicial, \defn{complete} if the union of its cones covers the ambient space~$\R^n$, and \defn{essential} if it contains the cone~$\{\b{0}\}$.
+Note that every complete fan is the product of an essential fan with its lineality space (the largest linear subspace contained in all the cones).
 For two fans~$\Fan, \cal{G}$ in~$\R^n$, we say that~$\Fan$ \defn{refines}~$\cal{G}$ (and that~$\cal{G}$ \defn{coarsens}~$\Fan$) if every cone of~$\Fan$ is contained in a cone of~$\cal{G}$.
@@
 The dimension~$0$ (resp.~dimension~$1$, resp.~codimension~$1$) faces are called \defn{vertices} (resp.~\defn{edges}, resp.~\defn{facets}) of~$P$.
-A polytope is \defn{simple} if its supporting hyperplanes are in general position, meaning that each vertex is incident to $\dim(P)$ facets (or equivalently to $\dim(P)$ edges).
+A polytope is \defn{simple} if each vertex is incident to $\dim(P)$ facets (or equivalently to $\dim(P)$ edges).
 
@@
 
-Fix an essential complete simplicial fan~$\Fan$ in~$\R^n$.
-Let~$\b{G}$ be the $N \times n$-matrix whose rows are the rays of~$\Fan$ and let~$\b{K}$ be a $(N-n) \times N$-matrix that spans the left kernel of~$\b{G}$ (\ie $\b{K}\b{G} = 0$).
+Fix an essential complete simplicial fan~$\Fan$ in~$\R^n$, with an (arbitrary) indexing of its rays by $[N]\eqdef \{1,\dots,N\}$.
+Let~$\b{G}$ be the $N \times n$-matrix whose rows are representative vectors of the rays of~$\Fan$.
+Let~$\b{K}$ be a $(N-n) \times N$-matrix that spans the left kernel of~$\b{G}$ (\ie $\b{K}\b{G} = 0$ and $\rank(\b{K})=N-n$).
 For any height vector~$\b{h} \in \R^N$, we define the polytope
 \[
-P_\b{h} \eqdef \set{\b{x} \in \R^n}{\b{G}\b{x} \le \b{h}}.
-\]
+P_\b{h} \eqdef \set{\b{x} \in \R^n}{\b{G}\b{x} \le \b{h}},
+\]
+where $\b{G}\b{x} \le \b{h}$ is the standard shorthand for the corresponding system of inequalities.
+
 We say that $\b{h}$ is \defn{$\Fan$-admissible} if $P_\b{h}$ is a polytopal realization of~$\Fan$.
@@
 \label{prop:characterizationPolytopalFan}
-Let~$\Fan$ be an essential complete simplicial fan in~$\R^n$. Then the following are equivalent for any height vector~$\b{h} \in \R^N$:
+Let~$\Fan$ be an essential complete simplicial fan in~$\R^n$. Then the following are equivalent for any height vector~$\b{h}\in \R^N$:
 \begin{enumerate}
@@
 It has five rays labeled~$1, \dots, 5$ and five maximal cones labeled~$a,\dots, e$.
+The matrices $\b{G}$ and $\b{K}$ are (for a possible choice of $\b{K}$): 
+\begin{align*}
+\transpose{\b{G}}&=\begin{bmatrix} 1 & 0 & -1& -1 & 0 \\ 0 & 1 & 1 & 0 &-1 \end{bmatrix},&
+\b{K}&=\begin{bmatrix} 1 & 0 & 0 & 1 & 0\\ 0 & 1 & 0 & 0 & 1 \\ 1& 0& 1& 0 & 1  \end{bmatrix}.
+\end{align*}
 Its type cone~$\typeCone(\Fan)$ lies in~$\R^5$, but has a $2$-dimensional lineality space.
@@
 For example, the height vector~$(\nicefrac{1}{2}, \nicefrac{3}{4}, \nicefrac{5}{4}, 1, \nicefrac{5}{4})$ belongs to the type cone~$\typeCone(\Fan)$, and the corresponding polytope is represented in \cref{fig:typeCone} (middle).
-To represent this type cone, it suffices to represent~$\b{K}\typeCone(\Fan)$ which is an essential simplicial cone in~$\R^3$.
+To represent this type cone, it suffices to represent~$\b{K}\typeCone(\Fan)$ which is an essential simplicial cone in~$\R^3$, given as the intersection of the open halfspaces:
+\begin{gather*}
+\b{K}H^>_{ab}: \; {x} - {y} +2 {z} > 0
+\qquad
+\b{K}H^>_{bc}: \; {x} + {y} - {z} > 0
+\qquad
+\b{K}H^>_{cd}: \; -{x} + {y} +2 {z} > 0
+\\
+\b{K}H^>_{de}: \; 2{x} + {z} > 0
+\qquad
+\b{K}H^>_{ae}: \; 2{y} + {z} > 0.
+\end{gather*}
 One can further reduce the dimension by intersecting with a transversal hyperplane to get a $2$-dimensional representation.
@@
 
-We still consider an essential complete simplicial fan~$\Fan$ in~$\R^n$, the $N \times n$-matrix~$\b{G}$ whose rows are the rays of~$\Fan$, and an $(N-n) \times N$-matrix~$\b{K}$ that spans the left kernel of~$\b{G}$ (\ie $\b{K}\b{G} = 0$).
+We still consider an essential complete simplicial fan~$\Fan$ in~$\R^n$, the $N \times n$-matrix~$\b{G}$ whose rows are the rays of~$\Fan$, and an $(N-n) \times N$-matrix~$\b{K}$ that spans the left kernel of~$\b{G}$ (\ie $\b{K}\b{G} = 0$ and $\rank(\b{K})=N-n$).
 
@@
 \item injective: Indeed, $\Psi(\b{x}) = \Psi(\b{x}')$ implies~$\b{G}(\b{x} - \b{x}') = 0$ and~$\b{G}$ has full rank since~$\Fan$ is essential and complete.
-\item surjective: Indeed, for~$\b{z} \in Q_\b{h}$, we have~$\b{K}(\b{h}-\b{z}) = 0$ so that~$\b{h}-\b{z}$ belongs to the right kernel of~$\b{K}$ which is the image of~$\b{G}$.
-Therefore, there exists~$\b{x} \in \R^n$ such that~$\b{h}-\b{z} = \b{G}\b{x}$.
-Therefore, $\b{z} = \Psi(\b{x})$ and~$\b{x} \in P_\b{h}$ since~$\b{h} - \b{G}\b{x} = \b{z} \ge 0$.\qedhere
+\item surjective: Indeed, for~$\b{z} \in Q_\b{h}$, we have~$\b{K}(\b{h}-\b{z}) = 0$ so that~$\b{h}-\b{z}$ belongs to the right kernel of~$\b{K}$, which is the image of~$\b{G}$ (because $\b{G}$ is of full rank).
+% : the $n$~columns of $\b{G}$ are linearly independent because $\b{G}$ is of full rank, and belong to the right kernel of~$\b{K}$ which is of dimension~$n$. 
+Hence, there exists~$\b{x} \in \R^n$ such that~$\b{h}-\b{z} = \b{G}\b{x}$. We have $\b{z} = \Psi(\b{x})$ and~$\b{x} \in P_\b{h}$ since~$\b{h} - \b{G}\b{x} = \b{z} \ge 0$.\qedhere
 \end{itemize}
@@
 In particular, its vertices correspond to triangulations of the $(n+3)$-gon and its facets correspond to internal diagonals of the $(n+3)$-gon.
-Equivalently, its vertices correspond to rooted binary trees with $(n+1)$ internal nodes, and its facets correspond to proper intervals of~$[n+1]$ (\ie intervals distinct from~$\varnothing$ and~$[n+1]$).
+Equivalently, its vertices correspond to rooted binary trees with $(n+1)$ internal nodes, and its facets correspond to proper intervals of~$[n+1]\eqdef\{1,\dots,n+1\}$ (\ie intervals distinct from~$\varnothing$ and~$[n+1]$).
 These bijections become clear when the convex $(n+3)$-gon is drawn with its vertices on a concave curve labeled by~$0, \dots, n+2$.
@@
 \enlargethispage{.1cm}
-We now focus on the normal fan~$\gvectorFan[n]$ of~$\Asso[n]$.
-Since~$\Asso[n]$ lives in a hyperplane of~$\R^{n+1}$, so does its normal fan.
+We now focus on the normal fan of~$\Asso[n]$.
+Since~$\Asso[n]$ lives in a hyperplane of~$\R^{n+1}$, its normal fan has a one-dimensional lineality.
 Let~$\HH \eqdef \bigset{\b{x} \in \R^{n+1}}{\sum_{\ell \in [n+1]} \b{x}_\ell = 0}$ and~$\pi : \R^{n+1} \to \HH$ denote the orthogonal projection.
-The following fans are illustrated in \cref{fig:lodayFans} in dimension~$2$ and~$3$.
+We denote by~$\gvectorFan[n]$ the intersection of the normal fan of~$\Asso[n]$ with~$\HH$, which is an essential complete simplicial fan.
+The following facts are illustrated in \cref{fig:lodayFans} in dimension~$2$ and~$3$.
 
@@
 \label{thm:normalFanLoday}
-In the normal fan~$\gvectorFan[n]$ of~$\Asso[n]$, 
+In the fan~$\gvectorFan[n]$, 
 \begin{itemize}
@@
 \end{theorem}
+
+% In view of \cref{def:gvectorCA}, it is convenient to express the $\b{g}$-vectors in the basis given by $\gvector{0,i+1}$ for $i\in [n]$.
+This is what we do in \cref{fig:lodayFans} and \cref{exm:typeConeAsso}.
+Note that in \cref{fig:lodayFans} and \cref{exm:typeConeAsso} we express the $\b{g}$-vectors in the basis given by $\gvector{0,i+1}$ for $i\in [n]$ (to be coherent with the upcoming \cref{def:gvectorCA}).
 
@@
 From the linear dependencies of \cref{prop:exchangeablePairsAsso}, we obtain a redundant description of the type cone of the fan~$\gvectorFan[n]$.
+To simplify the presentation, we embed the type cone in a larger space, adding dummy variables for the boundary edges of the polygon.
 
@@
 Consider the fan~$\gvectorFan[2]$ and~$\gvectorFan[3]$ illustrated in \cref{fig:lodayFans}.
-The type cone of~$\gvectorFan[2]$ lives in~$\R^5$ and has a lineality space of dimension~$2$ (this is the type cone studied in \cref{exm:typeCone,exm:typeConeCoarsenings,exm:typeConeMinkowskiSum}).
+The type cone of~$\gvectorFan[2]$ has dimension~$5$ and a lineality space of dimension~$2$ (this is the type cone studied in \cref{exm:typeCone,exm:typeConeCoarsenings,exm:typeConeMinkowskiSum}).
 It has $3$ facet-defining inequalities (given below), which correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso} and illustrated in \cref{fig:labelFacetDefiningInequalititiesAsso}\,(left).
@@
 
-The type cone of~$\gvectorFan[3]$ lives in~$\R^9$ and has a lineality space of dimension~$3$.
+The type cone of~$\gvectorFan[3]$ has dimension~$9$ and a lineality space of dimension~$3$.
 It has $6$ facet-defining inequalities (given below), which correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso} and illustrated in \cref{fig:labelFacetDefiningInequalititiesAsso}\,(right).
@@
 An important point is that mutations are involutions: $\mu_{x'} \big( \mu_{x}(\seed) \big) = \seed$.
-We say that two seeds are \defn{mutationally equivalent} when they can be obtained from each other by a sequence of mutations (we also use the same terminology for exchange matrices).
+We say that two seeds are \defn{adjacent} (resp.\ \defn{mutationally equivalent}) when they can be obtained from each other by a mutation (resp.\ a sequence of mutations).
+We also use the same terminology for exchange matrices.
 We denote by~$\variables$ the collection of all cluster variables in the seeds mutationally equivalent to an initial seed~$\seed_\circ = (\B_\circ, \coefficients_\circ, \cluster_\circ)$ with cluster variables~$\cluster_\circ = \{x_1, \dots, x_n\}$.
@@
 
-\begin{definition}[\cite{FominZelevinsky-ClusterAlgebrasIV}]
+\begin{definition}[\cite{FominZelevinsky-ClusterAlgebrasIV}]\label{def:gvectorCA}
 The \defn{$\b{g}$-vector}~$\gvector{x} = \gvectorFull{\B_\circ}{x}$ of a cluster variable~$x \in \principalClusterAlgebra$ is its degree.
@@
 
-\begin{definition}
+\begin{definition}[\cite{FominZelevinsky-ClusterAlgebrasIV}]
 The \defn{$\b{c}$-vector} of a cluster variable $x$ in a seed~$\seed$ of~$\principalClusterAlgebra$ is the vector
@@
 \]
-for any adjacent seeds~$(\B, \cluster)$ and~$(\B', \cluster')$ with~$\cluster \ssm \{x\} = \cluster' \ssm \{x'\}$.
+for any adjacent seeds~$(\B, \cluster)$ and~$(\B', \cluster')$ with~$\cluster \ssm \{x\} = \cluster' \ssm \{x'\}$ (with the usual convention that an empty sum is~$0$).
 Such a vector~$\b{h}$ exists, see the discussion in~\cite[Prop.~28]{HohlwegPilaudStella}.
@@
 Indeed, which of the two possible linear dependences is satisfied by the $\b{g}$-vectors of~$\cluster \cup \cluster'$ depends on the initial exchange matrix~$\B_\circ$.
-However, for cluster algebras of finite type, this linear dependence is independent of the choice of a seed containing~$x$ and~$x'$.
+However, for cluster algebras of finite type, this linear dependence is independent of the choice of the adjacent seeds containing~$x$ and~$x'$.
 As explained in \cref{corollary:UERPforCAproof}, this statement follows from~\cite[Thm.~7.5]{BuanMarshReinekeReitenTodorov}.
@@
 
-For example, the $\b{g}$-vectors of the blue, green, and yellow walks in the non-kissing facet of \cref{fig:exmNonkissing}\,(right) are respectively~$(0, -1, 0, 0, 0, 0)$, $(0, 0, 0, -1, 0, 0)$ and $(0, 1, 0, 1, 1, 0)$.
+For example, the $\b{c}$-vectors of the blue, green, and yellow walks in the non-kissing facet of \cref{fig:exmNonkissing}\,(right) are respectively~$(0, -1, 0, 0, 0, 0)$, $(0, 0, 0, -1, 0, 0)$ and $(0, 1, 0, 1, 1, 0)$.
 As the reader can observe on the example of \cref{fig:exmNonkissing}\,(right), the $\b{g}$- and $\b{c}$-vectors also form dual bases.
@@
 \[
-\langle \ell_B, x \rangle = \langle \ell_B, \sum_{A \in \ind(\cat)} \lambda_A [A] \rangle = \sum_{A \in \ind{\cat}} \lambda_A \langle \ell_B, [A] \rangle = \lambda_B \langle \ell_B, [B] \rangle.
+\langle \ell_B, x \rangle = \Big\langle \ell_B, \sum_{A \in \ind(\cat)} \lambda_A [A] \Big\rangle = \sum_{A \in \ind{\cat}} \lambda_A \langle \ell_B, [A] \rangle = \lambda_B \langle \ell_B, [B] \rangle.
 \]
@@
 \label{lem:mesh mutations and meshes}
-The set of positive mesh mutations~$(x,x')$ of \cref{def:positive mutation} is in bijection with the set~$\meshes$ of \cref{def:positive mutation}.
+The set of positive mesh mutations~$(x,x')$ of \cref{def:positive mutation} is in bijection with the set~$\meshes$ of \cref{def:meshMutation}.
 \end{lemma}
@@
 \begin{enumerate}
-\item For any~$X,Z\in\cat$, the realization of the split~$\mathbb{E}$-extension~$0\in\mathbb{E}(Z,X)$ is given bys~$\mathfrak{s}(0)=0$.
+\item For any~$X,Z\in\cat$, the realization of the split~$\mathbb{E}$-extension~$0\in\mathbb{E}(Z,X)$ is given by~$\mathfrak{s}(0)=0$.
 \item For any two~$\mathbb{E}$-extensions~$\delta\in\mathbb{E}(Z,X)$ and~$\delta'\in\mathbb{E}(Z',X')$, the realization of~$\delta\oplus\delta'$ is given by~$\mathfrak{s}(\delta\oplus\delta')=\mathfrak{s}(\delta)\oplus\mathfrak{s}(\delta')$.
@@
 \label{lem:index kzero extricat}
-The index descends to~$\kzero{\cat}$: For any conflation~$X\infl Y\defl Z$ in~$\cat$, we have~$\ind_\tc Y = \ind_\tc X + \ind_\tc Z$ in~$\kzero{\tc}$.
+The index descends to~$\kzero{\cat}$: for any conflation~$X\infl Y\defl Z$ in~$\cat$, we have~$\ind_\tc Y = \ind_\tc X + \ind_\tc Z$ in~$\kzero{\tc}$.
 \end{lemma}
@@
 Let~$X\infl Y\defl Z$ be a conflation in~$\cat$.
-Fix conflations~$T_1^XÂ \infl T_0^X \defl X$,~$T_1^Z\infl T_0^Z \defl Z$ with~$T_0^X, T_1^X, T_0^Z, T_1^Z\in\tc$.
+Fix conflations~$T_1^X \infl T_0^X \defl X$,~$T_1^Z\infl T_0^Z \defl Z$ with~$T_0^X, T_1^X, T_0^Z, T_1^Z\in\tc$.
 By~\cite[Prop.~3.15]{NakaokaPalu} and axiom (ET4)$^{\mathrm{op}}$, there are commutative diagrams of conflations

### 2021-06-16 thirdPaper/draft/typeConeAssociahedra.tex
more details in pf of Cor 4.35

@@
 
-More specifically: fix an additive category~$\cat$, and an additive bifunctor~$\mathbb{E}: \cat^\mathrm{op}\times\cat\to\mathit{Ab}$.
+More specifically: fix an additive category~$\cat$, and an additive bifunctor~$\mathbb{E}: \cat^\mathrm{op}\times\cat\to\mathit{Ab}$, where $\mathit{Ab}$ is the category of abelian groups.
 
@@
 First note that any injective object belongs to~$\susp \tc$, by \cref{lem:shifts of extriangles}.
+Indeed, if~$X$ is injective, then the extriangle
+\[
+X \overset{h_X}{\infl} \susp T_1^X \overset{\susp f_X}{\defl} \susp T_0^X \overset{(g_X)_\ast\delta_0}{\dashrightarrow}
+\]
+splits, showing that~$X$ is a summand of~$\susp T_1^X$.
 Let us prove that the converse holds.
 Let~$\susp T \infl X \overset{f}{\defl} Y\overset{\delta}{\dashrightarrow}$ be an extriangle with~$T\in\tc$.
-Since~$\cat(-,\susp T)|_\tc = 0$ and~$f$ is~$\tc$-epic, the morphism~$\cat(-,f)|_\tc$ is an isomorphism in~$\modt$.
+Since~$\cat(-,\susp T)|_\tc = 0$ and
+%~$f$ is~$\tc$-epic,
+$\mathbb{E}(-,\susp T)|_\tc =0$ (by \cref{lem:first consequences}),
+the morphism~$\cat(-,f)|_\tc$ is an isomorphism in~$\modt$.
 By \cref{prop:KRextricat}, there are morphisms~$Y\overset{s}{\to} X$,~$Y\xrightarrow{h}\susp T'$,~$\susp T'\xrightarrow{t} Y$, for some~$T'\in\tc$ satisfying

### 2021-06-17 thirdPaper/draft/typeConeAssociahedra.tex
massage

@@
 
-Our assumptions allow for a well-defined notion of index:~$\ind_T(X)=[T_0^X]-[T_1^X]\in\kzero{\add T}$.
+Our assumptions allow for a well-defined notion of index:~$\ind_T(X)=[T_0^X]-[T_1^X] \in \kzero{\add T}$.
 
@@
 
-Fix an essential complete simplicial fan~$\Fan$ in~$\R^n$, with an (arbitrary) indexing of its rays by $[N]\eqdef \{1,\dots,N\}$.
+Fix an essential complete simplicial fan~$\Fan$ in~$\R^n$, with an (arbitrary) indexing of its rays by $[N] \eqdef \{1,\dots,N\}$.
 Let~$\b{G}$ be the $N \times n$-matrix whose rows are representative vectors of the rays of~$\Fan$.
@@
 \label{exm:typeCone}
-\enlargethispage{.5cm}
+\begin{figure}[b]
+	\capstart
+	\centerline{{\includegraphics[scale=1]{typeConeFan}} \quad {\includegraphics[scale=1]{typeConePolytope}} \quad \raisebox{.5cm}{\includegraphics[scale=.45]{typeCone}}}
+	\caption{A $2$-dimensional fan~$\Fan$ with five rays $1, \dots, 5$ and five maximal cones~$a, \dots, e$ (left), its polytopal realization corresponding to the height vector~$(\nicefrac{1}{2}, \nicefrac{3}{4}, 1, 1, \nicefrac{5}{4})$ (middle), and the intersection of $\b{K}\typeCone(\Fan)$ with a hyperplane to get a $2$-dimensional slice (right).}
+	\label{fig:typeCone}
+\end{figure}
+%
 Consider the $2$-dimensional fan~$\Fan$ depicted in \cref{fig:typeCone} (left) (we will encounter this fan again in \cref{exm:typeConeCoarsenings,exm:typeConeMinkowskiSum,exm:typeConeAsso}).
 It has five rays labeled~$1, \dots, 5$ and five maximal cones labeled~$a,\dots, e$.
-The matrices $\b{G}$ and $\b{K}$ are (for a possible choice of $\b{K}$): 
-\begin{align*}
-\transpose{\b{G}}&=\begin{bmatrix} 1 & 0 & -1& -1 & 0 \\ 0 & 1 & 1 & 0 &-1 \end{bmatrix},&
-\b{K}&=\begin{bmatrix} 1 & 0 & 0 & 1 & 0\\ 0 & 1 & 0 & 0 & 1 \\ 1& 0& 1& 0 & 1  \end{bmatrix}.
-\end{align*}
-Its type cone~$\typeCone(\Fan)$ lies in~$\R^5$, but has a $2$-dimensional lineality space.
+For the matrices $\b{G}$ and $\b{K}$, we consider
+\[
+%\transpose{\b{G}} = \begin{bmatrix} 1 & 0 & -1 & -1 & 0 \\ 0 & 1 & 1 & 0 & -1 \end{bmatrix}
+\b{G} = \begin{bmatrix} 1 & 0 \\ 0 & 1 \\ -1 & 1 \\ -1 & 0 \\ 0 & -1 \end{bmatrix}
+\qquad\text{and}\qquad
+\b{K} = \begin{bmatrix} 1 & 0 & 0 & 1 & 0 \\ 0 & 1 & 0 & 0 & 1 \\ 1 & 0 & 1 & 0 & 1 \end{bmatrix}.
+\]
+The type cone~$\typeCone(\Fan)$ lies in~$\R^5$, but has a $2$-dimensional lineality space.
 The five pairs of adjacent maximal cones of~$\Fan$ give rise to following five defining inequalities for~$\typeCone(\Fan)$:
@@
 For example, the height vector~$(\nicefrac{1}{2}, \nicefrac{3}{4}, \nicefrac{5}{4}, 1, \nicefrac{5}{4})$ belongs to the type cone~$\typeCone(\Fan)$, and the corresponding polytope is represented in \cref{fig:typeCone} (middle).
-To represent this type cone, it suffices to represent~$\b{K}\typeCone(\Fan)$ which is an essential simplicial cone in~$\R^3$, given as the intersection of the open halfspaces:
+To represent this type cone, it suffices to represent~$\b{K}\typeCone(\Fan)$ which is an essential simplicial cone in~$\R^3$, given as the intersection of the following five open halfspaces:
 \begin{gather*}
@@
 This is the red triangle depicted in \cref{fig:typeCone} (right).
-
-\begin{figure}[htpb]
-	\capstart
-	\centerline{{\includegraphics[scale=1]{typeConeFan}} \quad {\includegraphics[scale=1]{typeConePolytope}} \quad \raisebox{.5cm}{\includegraphics[scale=.45]{typeCone}}}
-	\caption{A $2$-dimensional fan~$\Fan$ with five rays $1, \dots, 5$ and five maximal cones~$a, \dots, e$ (left), its polytopal realization corresponding to the height vector~$(\nicefrac{1}{2}, \nicefrac{3}{4}, 1, 1, \nicefrac{5}{4})$ (middle), and the intersection of $\b{K}\typeCone(\Fan)$ with a hyperplane to get a $2$-dimensional slice (right).}
-	\label{fig:typeCone}
-\end{figure}
 \end{example}
@@
 
-\enlargethispage{.5cm}
 We now discuss the connection between convex combinations in the type cone and Minkowski sums of polytopes.
@@
 \label{exm:typeConeMinkowskiSum}
-\enlargethispage{.5cm}
 Consider the $2$-dimensional fan~$\Fan$ of \cref{fig:typeCone}\,(left) whose type cone has been described in \cref{exm:typeCone} and represented in \cref{fig:typeCone}\,(right).
@@
 
-\begin{figure}[htpb]
+\begin{figure}
 	\capstart
@@
 
-\enlargethispage{.1cm}
+\pagebreak
 We now focus on the normal fan of~$\Asso[n]$.
 Since~$\Asso[n]$ lives in a hyperplane of~$\R^{n+1}$, its normal fan has a one-dimensional lineality.
-Let~$\HH \eqdef \bigset{\b{x} \in \R^{n+1}}{\sum_{\ell \in [n+1]} \b{x}_\ell = 0}$ and~$\pi : \R^{n+1} \to \HH$ denote the orthogonal projection.
+Let~$\HH \eqdef \bigset{\b{x} \in \R^{n+1}}{\sum_{\ell \in [n+1]} \b{x}_\ell = 0}$ and ${\pi : \R^{n+1} \to \HH}$ denote the orthogonal projection.
 We denote by~$\gvectorFan[n]$ the intersection of the normal fan of~$\Asso[n]$ with~$\HH$, which is an essential complete simplicial fan.
-The following facts are illustrated in \cref{fig:lodayFans} in dimension~$2$ and~$3$.
 
@@
 
-% In view of \cref{def:gvectorCA}, it is convenient to express the $\b{g}$-vectors in the basis given by $\gvector{0,i+1}$ for $i\in [n]$.
-This is what we do in \cref{fig:lodayFans} and \cref{exm:typeConeAsso}.
+\cref{thm:normalFanLoday} is illustrated in \cref{fig:lodayFans} and \cref{exm:typeConeAsso} in dimension~$2$ and~$3$.
 Note that in \cref{fig:lodayFans} and \cref{exm:typeConeAsso} we express the $\b{g}$-vectors in the basis given by $\gvector{0,i+1}$ for $i\in [n]$ (to be coherent with the upcoming \cref{def:gvectorCA}).
 
-\begin{figure}[h]
+\begin{figure}
 	\capstart
@@
 From the linear dependencies of \cref{prop:exchangeablePairsAsso}, we obtain a redundant description of the type cone of the fan~$\gvectorFan[n]$.
-To simplify the presentation, we embed the type cone in a larger space, adding dummy variables for the boundary edges of the polygon.
+To simplify the presentation and write the wall-crossing inequalities in a uniform way, we embed the type cone in a larger space, adding dummy variables for the boundary edges of the polygon.
 
@@
 \end{corollary}
+
+\pagebreak
 
@@
 For instance, the inequality~$\red \circled{A}$ above is given by~$\b{h}_{\includegraphics[scale=.3]{diagonalA1}} + \b{h}_{\includegraphics[scale=.3]{diagonalA3}} > \b{h}_{\includegraphics[scale=.3]{diagonalA2}}$.
-
-The type cone of~$\gvectorFan[3]$ has dimension~$9$ and a lineality space of dimension~$3$.
-It has $6$ facet-defining inequalities (given below), which correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso} and illustrated in \cref{fig:labelFacetDefiningInequalititiesAsso}\,(right).
-
-\[
-\begin{array}{r|cccccccccc}
-\text{diagonals} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalB1}}  & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalB2}} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalB3}} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalB4}} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalB5}} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalB6}} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalB7}} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalB8}} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalB9}} \\[.3cm]
-\text{$\b{g}$-vectors} & \compactVectorT{1}{0}{0} & \compactVectorT{0}{1}{0} & \compactVectorT{0}{0}{1} & \compactVectorT{-1}{1}{0} & \compactVectorT{0}{-1}{1} & \compactVectorT{-1}{0}{1} & \compactVectorT{-1}{0}{0} & \compactVectorT{0}{-1}{0} & \compactVectorT{0}{0}{-1} \\[.6cm]
-\text{facet}		& 1 & -1 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & \red \circled{A} \\
-\text{defining} 	& 0 & 1 & -1 & -1 & 1 & 0 & 0 & 0 & 0 & \red \circled{B} \\
-\text{inequalities}	& 0 & 0 & 1 & 0 & -1 & 0 & 1 & 0 & 0 & \red \circled{C} \\
-					& 0 & 0 & 0 & 1 & -1 & 1 & 0 & 0 & 0 & \red \circled{D} \\
-					& 0 & 0 & 0 & 0 & 1 & -1 & -1 & 1 & 0 & \red \circled{E} \\
-					& 0 & 0 & 0 & 0 & 0 & 1 & 0 & -1 & 1 & \red \circled{F} \\[.2cm]
-\end{array}
-\]
-\medskip
-
-%sage: B = Matrix([[0,1,0],[-1,0,1],[0,-1,0]])
-%sage: CA = ClusterAlgebra(B)
-
-%sage: CA.explore_to_depth(infinity)
-%sage: gvectors = CA.cluster_fan().rays()
-%sage: for gvector in gvectors:
-%....:     print gvector, CA.cluster_variable(gvector)
-%....:     
-%N(-1, 1, 0) (x1 + 1)/x0
-%N(1, 0, 0) x0
-%N(0, 0, 1) x2
-%N(0, -1, 1) (x0 + x2)/x1
-%N(0, 0, -1) (x1 + 1)/x2
-%N(-1, 0, 1) (x1*x2 + x0 + x2)/(x0*x1)
-%N(0, -1, 0) (x0*x1 + x0 + x2)/(x1*x2)
-%N(-1, 0, 0) (x0*x1 + x1*x2 + x0 + x2)/(x0*x1*x2)
-%N(0, 1, 0) x1
-
-%sage: TCCA = type_cone_CA(CA)
-%sage: TCCA
-%A 9-dimensional polyhedron in QQ^9 defined as the convex hull of 1 vertex, 6 rays, 3 lines
-%sage: TCCA.lines()
-%(A line in the direction (1, 0, 0, -1, 0, 0, -1, 0, 1),
-% A line in the direction (1, 0, 1, 0, -1, 1, -1, 0, 1),
-% A line in the direction (0, 1, 1, 0, -1, 0, -1, -1, 1))
-%sage: TCCA.inequalities()
-%(An inequality (-1, 0, -1, 0, 0, 1, 0, 0, 1) x + 0 >= 0,
-% An inequality (1, 1, 0, 0, 0, 0, 0, 0, -1) x + 0 >= 0,
-% An inequality (1, 0, 0, 1, 0, -1, 0, 0, 0) x + 0 >= 0,
-% An inequality (0, 0, 0, -1, 0, 1, 1, -1, 0) x + 0 >= 0,
-% An inequality (0, 0, 1, 0, 0, -1, 0, 1, 0) x + 0 >= 0,
-% An inequality (0, 0, 0, 1, 1, 0, -1, 0, 0) x + 0 >= 0)
 
@@
 \end{figure}
+
+The type cone of~$\gvectorFan[3]$ has dimension~$9$ and a lineality space of dimension~$3$.
+It has $6$ facet-defining inequalities (given below), which correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso} and illustrated in \cref{fig:labelFacetDefiningInequalititiesAsso}\,(right).
+
+\[
+\begin{array}{r|cccccccccc}
+\text{diagonals} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalB1}}  & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalB2}} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalB3}} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalB4}} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalB5}} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalB6}} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalB7}} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalB8}} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalB9}} \\[.3cm]
+\text{$\b{g}$-vectors} & \compactVectorT{1}{0}{0} & \compactVectorT{0}{1}{0} & \compactVectorT{0}{0}{1} & \compactVectorT{-1}{1}{0} & \compactVectorT{0}{-1}{1} & \compactVectorT{-1}{0}{1} & \compactVectorT{-1}{0}{0} & \compactVectorT{0}{-1}{0} & \compactVectorT{0}{0}{-1} \\[.6cm]
+\text{facet}		& 1 & -1 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & \red \circled{A} \\
+\text{defining} 	& 0 & 1 & -1 & -1 & 1 & 0 & 0 & 0 & 0 & \red \circled{B} \\
+\text{inequalities}	& 0 & 0 & 1 & 0 & -1 & 0 & 1 & 0 & 0 & \red \circled{C} \\
+					& 0 & 0 & 0 & 1 & -1 & 1 & 0 & 0 & 0 & \red \circled{D} \\
+					& 0 & 0 & 0 & 0 & 1 & -1 & -1 & 1 & 0 & \red \circled{E} \\
+					& 0 & 0 & 0 & 0 & 0 & 1 & 0 & -1 & 1 & \red \circled{F} \\[.2cm]
+\end{array}
+\]
+
+%sage: B = Matrix([[0,1,0],[-1,0,1],[0,-1,0]])
+%sage: CA = ClusterAlgebra(B)
+
+%sage: CA.explore_to_depth(infinity)
+%sage: gvectors = CA.cluster_fan().rays()
+%sage: for gvector in gvectors:
+%....:     print gvector, CA.cluster_variable(gvector)
+%....:     
+%N(-1, 1, 0) (x1 + 1)/x0
+%N(1, 0, 0) x0
+%N(0, 0, 1) x2
+%N(0, -1, 1) (x0 + x2)/x1
+%N(0, 0, -1) (x1 + 1)/x2
+%N(-1, 0, 1) (x1*x2 + x0 + x2)/(x0*x1)
+%N(0, -1, 0) (x0*x1 + x0 + x2)/(x1*x2)
+%N(-1, 0, 0) (x0*x1 + x1*x2 + x0 + x2)/(x0*x1*x2)
+%N(0, 1, 0) x1
+
+%sage: TCCA = type_cone_CA(CA)
+%sage: TCCA
+%A 9-dimensional polyhedron in QQ^9 defined as the convex hull of 1 vertex, 6 rays, 3 lines
+%sage: TCCA.lines()
+%(A line in the direction (1, 0, 0, -1, 0, 0, -1, 0, 1),
+% A line in the direction (1, 0, 1, 0, -1, 1, -1, 0, 1),
+% A line in the direction (0, 1, 1, 0, -1, 0, -1, -1, 1))
+%sage: TCCA.inequalities()
+%(An inequality (-1, 0, -1, 0, 0, 1, 0, 0, 1) x + 0 >= 0,
+% An inequality (1, 1, 0, 0, 0, 0, 0, 0, -1) x + 0 >= 0,
+% An inequality (1, 0, 0, 1, 0, -1, 0, 0, 0) x + 0 >= 0,
+% An inequality (0, 0, 0, -1, 0, 1, 1, -1, 0) x + 0 >= 0,
+% An inequality (0, 0, 1, 0, 0, -1, 0, 1, 0) x + 0 >= 0,
+% An inequality (0, 0, 0, 1, 1, 0, -1, 0, 0) x + 0 >= 0)
+
 \end{example}
+
+\pagebreak
 
@@
 
-\enlargethispage{.2cm}
 Combining \cref{coro:simplicialTypeCone,coro:simplicialTypeConeAsso} and \cref{prop:extremalExchangeablePairsAsso}, we derive the following description of all polytopal realizations of the fan~$\gvectorFan[n]$, recovering all associahedra of~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan}.
@@
 Define the \defn{Cartan companion} of an exchange matrix $\B$ as the matrix~$\A{\B}$ given by~$a_{xy} = 2$ if~$x = y$ and~$a_{xy} = -|b_{xy}|$ otherwise.
+
+\pagebreak
 
@@
 %
-\enlargethispage{.1cm}
 The $\b{g}$-vectors support a complete simplicial fan realization of the non-kissing complex~$\NKC$.
@@
 
+\enlargethispage{.1cm}
 It is proved in~\cite[Thm.~4.27]{PaluPilaudPlamondon-nonkissing} that the non-kissing fan comes from a polytope.
@@
 
-%\newpage
+\newpage
 \part{Grothendieck group and relations between $\b{g}$-vectors}

### 2021-07-16 thirdPaper/draft/typeConeAssociahedra.tex
pg new address

@@
 \author{Pierre-Guy Plamondon}
-\address[Pierre-Guy Plamondon]{Laboratoire de Math\'ematiques d'Orsay, Universit\'e Paris-Sud, CNRS, Universit\'e Paris-Saclay}
-\email{pierre-guy.plamondon@math.u-psud.fr}
-\urladdr{\url{https://www.math.u-psud.fr/~plamondon/}}
+\address[Pierre-Guy Plamondon]{Laboratoire de Math\'ematiques de Versailles, UVSQ, CNRS, Universit\'e Paris-Saclay, Versailles}
+\email{pierre-guy.plamondon@uvsq.fr}
+\urladdr{\url{https://www.imo.universite-paris-saclay.fr/~plamondon/}}
 

### 2022-06-17 thirdPaper/draft/typeConeAssociahedra.tex
Added reference in section 3

@@
 
-In~\cite{Auslander1984}, M.~Auslander showed that the relations in the Grothendieck group of an Artin algebra are generated by the ones given by almost-split sequences precisely when the algebra is of finite representation type.
-This result was generalized to $\Hom{}$-finite, Krull-Schmidt exact categories with enough projectives by H.~Enomoto in~\cite{Enomoto}, and to $\Hom{}$-finite, Krull--Schmidt triangulated categories with a cogenerator by J.~Haugland in~\cite{Haugland}.
+In~\cite{Butler} and~\cite{Auslander1984}, M.~Butler and M.~Auslander showed that the relations in the Grothendieck group of an Artin algebra are generated by the ones given by almost-split sequences precisely when the algebra is of finite representation type.
+This result was generalized to triangulated categories with certain finiteness conditions by J.~Xiao and B.~Zhu in \cite{XiaoZhu}, to~$\Hom{}$-finite, Krull-Schmidt exact categories with enough projectives by H.~Enomoto in~\cite{Enomoto}, to $(n+2)$-angulated categories by F.~Fedele in~\cite{Fedele}, and to $\Hom{}$-finite, Krull--Schmidt triangulated categories with a cogenerator by J.~Haugland in~\cite{Haugland}.
+Relations in the Grothendieck group of cluster categories have also been studied in~\cite{Palu-grothendieckGroup}.
 Inspired by these results, we will show in this Section that a similar statement holds (see \cref{thm:relations-g-vecteurs}) for the~$\b{g}$-vectors (or indices) of objects in a~$2$-Calabi--Yau triangulated category.

### 2022-07-19 thirdPaper/draft/typeConeAssociahedra.tex
minor changes
update biblio

@@
 \usepackage{tikz-cd}
-\usepackage{tkz-graph}
 \usetikzlibrary{trees, decorations, decorations.pathmorphing, decorations.markings, decorations.shapes, shapes, arrows, matrix, calc, fit, intersections, patterns, angles}
@@
 \address[Arnau Padrol]{Institut de Math\'{e}matiques de Jussieu - Paris Rive Gauche, Sorbonne Universit\'e, Paris}
-\email{arnau.padrol@imj-prg.fr.}
+\email{arnau.padrol@imj-prg.fr}
 \urladdr{\url{https://webusers.imj-prg.fr/~arnau.padrol/}}
@@
 Given a complete simplicial fan~$\Fan$, we consider the space~$\typeCone(\Fan)$ of all its polytopal realizations.
-This space was called type cone in~\cite{McMullen-typeCone} and deformation cone in~\cite{Postnikov, PostnikovReinerWilliams}, who studied the case when~$\Fan$ is the braid arrangement leading to the rich theory of generalized permutahedra (recently extended to all finite Coxeter arrangements in~\cite{ACEP-DeformationsCoxeterPermutahedra}).
+This space was called type cone in~\cite{McMullen-typeCone} and deformation cone in~\cite{Postnikov, PostnikovReinerWilliams}, who studied the case when~$\Fan$ is the braid arrangement leading to the rich theory of generalized permutahedra (recently extended to all finite Coxeter arrangements in~\cite{ArdilaCastilloEurPostnikov}).
 The type cone is known to be a polyhedral cone defined by a collection of inequalities corresponding to the linear dependences among the rays of~$\Fan$ contained in pairs of adjacent maximal cones of~$\Fan$ (see \cref{def:typeCone}).
@@
 They encompass two families of simplicial complexes studied independently in the literature: on the one hand the grid associahedra introduced by T.~K.~Petersen, P.~Pylyavskyy and D.~Speyer in~\cite{PetersenPylyavskyySpeyer} for a staircase shape, studied by F.~Santos, C.~Stump and V.~Welker~\cite{SantosStumpWelker} for rectangular shapes, and extended by T.~McConville in~\cite{McConville} for arbitrary grid shapes; and on the other hand the Stokes polytopes and accordion associahedra studied by Y.~Baryshnikov~\cite{Baryshnikov}, F.~Chapoton~\cite{Chapoton-quadrangulations}, A.~Garver and T.~McConville~\cite{GarverMcConville} and T.~Manneville and V.~Pilaud~\cite{MannevillePilaud-accordion}.
-The latter, sometimes called accordiohedra, have also~recently appeared in the mathematical physics litterature concerning scattering amplitudes~\cite{BanerjeeLaddhaRaman-StokesPolytopes, Raman-PositiveGeometry}, with realizations inspired by those in~\cite{ArkaniHamedBaiHeYan}.
+The latter, sometimes called accordiohedra, have also~recently appeared in the mathematical physics litterature concerning scattering amplitudes~\cite{BanerjeeLaddhaRaman, Raman}, with realizations inspired by those in~\cite{ArkaniHamedBaiHeYan}.
 It was shown in~\cite{PaluPilaudPlamondon-nonkissing, BrustleDouvilleMousavandThomasYildirim} that the non-kissing complex of a gentle bound quiver provides a combinatorial model for the support $\tau$-tilting complex~\cite{AdachiIyamaReiten} of the associated gentle algebra.
@@
 
-Since this precisely coincides with the description of the flip in the non-kissing complex (see \cref{prop:exchangeablePairsNKC}\,(i) or~\cite[Prop.~2.31]{PaluPilaudPlamondon-nonkissing} for an alternative presentation), we conclude that the flip of~$\omega$ in~$F$ creates a facet~$F'$ containing~$\omega'$.
+Since this precisely coincides with the description of the flip in the non-kissing complex (see \cref{prop:exchangeablePairsNKC}\,(i) or~\cite[Prop.~2.33]{PaluPilaudPlamondon-nonkissing} for an alternative presentation), we conclude that the flip of~$\omega$ in~$F$ creates a facet~$F'$ containing~$\omega'$.
 Therefore, $\omega$ and~$\omega'$ are exchangeable with distinguished substring~$\sigma$.

### 2022-07-20 firstPaper/firstPaperShort/nonKissingComplex.tex
minor changes
update first paper PPP

@@
 \newcommand{\outdeg}{\mathrm{outdeg}} % out-degree
-%\newcommand{\tai}{\mathsf{tai}} % target incompatible
-%\newcommand{\tac}{\mathsf{tac}} % target compatible
-%\newcommand{\soi}{\mathsf{soi}} % source incompatible
-%\newcommand{\soc}{\mathsf{soc}} % source compatible
-%\newcommand{\cso}{\mathsf{cso}} % cosource
-%\newcommand{\cta}{\mathsf{cta}} % cotarget
 
@@
 \title{Non-kissing complexes and tau-tilting for gentle algebras}
-%\title[Non-kissing complexes and tau-tilting for gentle algebras]{Non-kissing complexes and tau-tilting for gentle algebras \\ {\rm Preliminary version --- please do not distribute}}
 
@@
 \author{Pierre-Guy Plamondon}
-\address[Pierre-Guy Plamondon]{Laboratoire de Math\'ematiques d'Orsay, Universit\'e Paris-Sud, CNRS, Universit\'e Paris-Saclay}
-\email{pierre-guy.plamondon@math.u-psud.fr}
-\urladdr{\url{https://www.math.u-psud.fr/~plamondon/}}
+\address[Pierre-Guy Plamondon]{Universit\'e Paris-Saclay, UVSQ, CNRS, Laboratoire de Math\'ematiques de Versailles}
+\email{pierre-guy.plamondon@uvsq.fr}
+\urladdr{\url{https://www.imo.universite-paris-saclay.fr/~plamondon/}}
 
@@
 Moreover, the dual graph of the non-kissing complex has a natural orientation which equips its facets with a lattice structure~\cite[Thm. 1.1, Sect.~5--8]{McConville}.
-Further lattice theoretic and geometric aspects of this complex were recently developed by A.~Garver and T.~McConville in~\cite{GarverMcConville-grid}.
+Further lattice-theoretic and geometric aspects of this complex were recently developed by A.~Garver and T.~McConville in~\cite{GarverMcConville-grid}.
 
@@
 The \defn{arrow ideal} of~$kQ$ is the ideal~$R \eqdef \bigoplus_{\ell \ge 1} kQ_\ell$ generated by the arrows of~$Q$.
-A two-sided ideal~$I$ of~$kQ$ is \defn{admissible} if there exists~$m \ge 2$ such that~$R^m \subseteq I \subseteq R^2$ (the condition~$R^m \subseteq I$ ensures that~$kQ/I$ is finite dimensional, and the condition~$I \subseteq R^2$ ensures that~$Q$ can be recovered form~$kQ/I$).
+A two-sided ideal~$I$ of~$kQ$ is \defn{admissible} if there exists~$m \ge 2$ such that~$R^m \subseteq I \subseteq R^2$ (the condition~$R^m \subseteq I$ ensures that~$kQ/I$ is finite dimensional, and the condition~$I \subseteq R^2$ ensures that~$Q$ can be recovered from~$kQ/I$).
 The pair~$\bar Q \eqdef (Q,I)$ is then called a \defn{bound quiver} and the quotient~$kQ/I$ is a \defn{bound quiver algebra} and is finite dimensional.
@@
 For a quiver~$Q = (Q_0, Q_1, s, t)$, define its \defn{reversed quiver} by~$\reversed{Q} \eqdef (Q_0, Q_1, t, s)$.
-For a path~$\pi$ on~$Q$, define its \defn{reversed path} on~$\reversed{Q}$ by~$\reversed{(\alpha_1 \cdots \alpha_\ell)} = \alpha_\ell \cdots \alpha_1$, and extend it by linearity to a morphism~$kQ \to k\reversed{Q}$ of path algebras.
+For a path~$\pi$ on~$Q$, define its \defn{reversed path} on~$\reversed{Q}$ by~$\reversed{(\alpha_1 \cdots \alpha_\ell)} = \alpha_\ell \cdots \alpha_1$, and extend it by linearity to an anti-morphism~$kQ \to k\reversed{Q}$ of path algebras.
 We denote by~$\reversed{I}$ the direct image of~$I$ under this morphism.
@@
 \item $M_v$ is a~$k$-vector space for all~$v\in Q_0$, and
-\item $M_\alpha: M_{s(\alpha)} \to M_{t(\alpha)}$ is a linear map for all~$\alpha \in Q_1$, such that~$M_\pi \eqdef M_{\alpha_\ell} \circ \dots \circ M_{\alpha_1} = 0$ for any path~$\pi = \alpha_1 \dots \alpha_\ell$ in~$I$.
+\item $M_\alpha: M_{s(\alpha)} \to M_{t(\alpha)}$ is a linear map for all~$\alpha \in Q_1$, such that $M_\pi := \sum M_{\alpha_{\ell}} \circ \cdots \circ M_{\alpha_1} = 0$  for any element~$\pi =\sum \alpha_1 \dots \alpha_\ell$ in~$I$.
 \end{itemize}
@@
 \begin{theorem}[\cite{AdachiIyamaReiten}]\label{thm:mutationstautilts}
-Let~$N = \bigoplus_{i \in [n]} N_i$ be a support~$\tau$-tilting object, where each~$N_i$ is either an indecomposable representation or a shifted indecomposable projective representation.
+Let~$N = \bigoplus_{i \in [n]} N_i$ be a basic support~$\tau$-tilting object, where each~$N_i$ is either an indecomposable representation or a shifted indecomposable projective representation.
 Then for any~${i \in [n]}$, there exists a unique indecomposable representation or shifted indecomposable projective representation~$N'_i$ not isomorphic to~$N_i$ and such that
@@
 Moreover, the strings~$\varepsilon_v$ of length zero are depicted simply as~$v$.
-Be aware that even if the string is depicted linearly form left to right, it might have cycles since some substrings can be repeated along the string.
+Be aware that even if the string is depicted linearly from left to right, it might have cycles since some substrings can be repeated along the string.
 \end{notation}
@@
 \begin{itemize}
-    \item For each vertex~$v \in Q_0$, the vector space~$M(\varpi, \lambda, d)_j$ is equal to~$k^d$.
-    \item For each arrow~$\gamma \in Q_1$ different from~$\alpha_\ell$, the linear map~$M(\varpi, \lambda, d)_\gamma$ is the identity.
-    \item The linear map~$M(\varpi, \lambda, d)_{\alpha_\ell}$ is equal to~$J_d(\lambda^{\varepsilon_\ell})$, where
+\item For each vertex~$v \in Q_0$, the vector space~$M(\varpi, \lambda, d)_v$ as a copy of $k^d$ for each $0 \le m \le \ell$ such that $v_m = v$.
+\item For each $m \in [\ell-1]$, the linear map $M(\varpi, \lambda, d)_{\alpha_m}$ sends the copy of $k^d$ associated to $s(\alpha_m)$ to that associated to $t(\alpha_m)$ via the identity map.
+\item The linear map~$M(\varpi, \lambda, d)_{\alpha_\ell}$ sends the copy of $k^d$ associated to $s(\alpha_{\ell})$ to that associated to $t(\alpha_\ell)$ via the matrix~$J_d(\lambda^{\varepsilon_\ell})$, where
      \[
@@
      \]
-    is the~$d\times d$ Jordan block of type~$\lambda$.
+    is the~$d\times d$ Jordan block of type~$\lambda$, where we identify $t(\alpha_{\ell}^{\varepsilon_{\ell}})$ with $s(\alpha_{1}^{\varepsilon_1})$.
   \end{itemize}
@@
 \begin{lemma}[and Definition]
+\enlargethispage{.1cm}
 Let~$\rho$ be a string for a string bound quiver~$\bar Q$.
@@
 \qquad
-_{h^{-1}}\rho = \;\vcenter{\hbox{\includegraphics[scale=0.3]{exmString6}}}
+\rho_{h^{-1}} = \;\vcenter{\hbox{\includegraphics[scale=0.3]{exmString6}}}
 \qquad
@@
 	\item $\alpha^{-1}\rho'$ is a string of~$\bar Q$ and
-	\item $\rho$ ends in~$u$ or contains an arrow starting at~$u$ (see Figure~\ref{fig:def-attracts});
+	\item $\rho$ ends in~$u$ or contains an arrow starting at~$u$ and moreover, the arrow, if any, preceding this occurrence of $u$ in $\rho$ is not $\alpha$ (see Figure~\ref{fig:def-attracts});
 	\end{enumerate}
@@
 \label{coro: stautilt complex from strings}
-The support $\tau$-tilting complex of~$\bar Q$ is isomorphic to the clique complex of the graph whose vertices are the unoriented strings of~$\bar Q$ and whose edges link two strings which do not attract nor reach for each other.
+The support $\tau$-tilting complex of~$\bar Q$ is isomorphic to the clique complex of the graph whose vertices are the unoriented strings of $\tau$-rigid modules of~$\bar Q$ and whose edges link two strings which do not attract nor reach for each other.
 \end{corollary}
@@
 Note that any arrow~$\alpha \in Q_1$ is incident with~$6$ other arrows of~$Q\blossom_1$.
-Therefore, any~$\alpha \in Q_1$ can be continued to a string both at its source and target in two ways (switching or not orientation).
+Therefore, any~$\alpha \in Q_1$ can be continued to a string both at its source and target in two ways (switching orientation or not).
 It follows that a string in~$\bar Q\blossom$ is maximal if and only if it joins two blossom vertices of~$\bar Q\blossom$.
@@
 All these notations are illustrated in \fref{fig:pure}\,(right).
+Note that $\omega \prec_\alpha \mu$ so that $\mu \notin F$ by maximality of~$\omega$ in~$\prec_\alpha$.
 We claim that~$\mu$ is non-kissing with any walk of~$F$, contradicting the maximality~of~$F$.
@@
 
+\pagebreak
+
 Since each bending walk in a non-kissing facet of~$\RNKC$ has two distinguished arrows, we can consider the substring they surround.
@@
 
-\enlargethispage{.3cm}
 Using material from Part~\ref{part:lattice}, we will characterize distinguishable strings of~$\bar Q$ in Section~\ref{subsec:distinguishableStrings}.
@@
 In particular, $\omega$ cannot be distinguished at two loops.
-\item If the distinguished arrows~$\alpha, \beta$ of~$\omega$ are not loops, then~$\alpha \beta \notin I$ and~$\beta \alpha \notin I$.
+\item If the distinguished arrows~$\alpha, \beta$ of~$\omega$ are not loops, then~$\alpha \beta \notin I$ and~$\beta \alpha \notin I$, when these concatenations make sense.
 \end{enumerate}
@@
 The following statement is schematized in \fref{fig:flip}.
+
+\pagebreak
 
@@
 in the notations of Proposition~\ref{prop:flip} and Figure~\ref{fig:flip}.
-We note that these extensions have a flavour very similar to the results of I.~\c{C}anak\c{c}{\i} and S.~Schroll in~\cite{CanakciSchroll}.
+We note that these extensions have a flavour very similar to the results of  \.{I}.~\c{C}anak\c{c}{\i} and S.~Schroll in~\cite{CanakciSchroll}.
 In their paper, the middle term of an extension is obtained by resolving a crossing, while here, a kissing is resolved into a crossing.
@@
 \captionsetup{width=1.5\textwidth}
-\hvFloat[floatPos=h, capWidth=h, capPos=r, capAngle=90, objectAngle=90, capVPos=c, objectPos=c]{figure}
+\hvFloat[floatPos=h, capWidth=h, capPos=right, capAngle=90, objectAngle=90, capVPos=c, objectPos=c]{figure}
 {\includegraphics[scale=.45]{exmAuslanderReitenQuiver}}
@@
 
-This section focuses on lattice theoretic properties of non-kissing complexes.
-Referring to~\ref{sec:recollectionLattice} for proper definitions of the lattice theoretic concepts involved, let us immediately state the main result of this section.
+This section focuses on lattice-theoretic properties of non-kissing complexes.
+Referring to~\ref{sec:recollectionLattice} for proper definitions of the lattice-theoretic concepts involved, let us immediately state the main result of this section.
 
@@
 	\caption{Four sets of strings on the gentle bound quiver~$\bar Q$ of \fref{fig:exmBlossomingQuiver}\,(left).
-The first is neither closed not coclosed, the second is closed but not coclosed, the third is coclosed but not closed, and the fourth is biclosed.}
+The first is neither closed nor coclosed, the second is closed but not coclosed, the third is coclosed but not closed, and the fourth is biclosed.}
 	\label{fig:exmBiclosed}
@@
 The proof is inspired from that of~\cite[Thm.~6.5]{McConville}.
-The main difficulty is that~$\Bicl{\bar Q}$ does not satisfies Condition~(i) of Theorem~\ref{thm:characterizationCongruenceUniform} when~$\bar Q$ has a loop.
+The main difficulty is that~$\Bicl{\bar Q}$ does not satisfy Condition~(i) of Theorem~\ref{thm:characterizationCongruenceUniform} when~$\bar Q$ has a loop.
 For example, for the quiver~$\bar Q$ with a single vertex~$v$, a loop~$\alpha$, and the relation~$\alpha^2 = 0$, the biclosed sets of strings are precisely~$\varnothing$ and~$\{\varepsilon_v, \alpha\}$.
@@
 \[
-S \cup X \subseteq (R \cup \{\sigma\}) \cup \closure{\big( ( S \cup X ) \ssm (R \cup \{\sigma\}) \big)} \subseteq \closure{(S \cup X)}
+S \cup X \subseteq (R \cup \{\sigma\}) \cup \closure{\big( ( S \cup X ) \ssm (R \cup \{\sigma\}) \big)} \subseteq \closure{(S \cup X)}.
 \]
@@
 \begin{example}
-\fref{fig:exmLatticeQuotient} shows the complete map from the biclosed sets of~$\Bicl{\bar Q}$ to the non-kissing facets of~$\NKC$ for a specific gentle bound quiver.
+\fref{fig:exmLatticeQuotient} shows the complete map~$\eta$ from the biclosed sets of~$\Bicl{\bar Q}$ to the non-kissing facets of~$\NKC$ for a specific gentle bound quiver.
 Instead of drawing the image~$\eta(S)$ for each biclosed set~$S \in \Bicl{\bar Q}$, we have grouped in blue boxes the fibers of~$\eta$.
@@
 \[
-\zeta(F) \eqdef \closure{\Big( \bigcup_{\omega \in F} \Sigma_\bottom(\omega) \Big)}
+\zeta(F) \eqdef \closure{\Big( \bigcup_{\omega \in F} \Sigma_\bottom(\omega) \Big)}.
 \]
@@
 & = \big( \strings^\pm(\bar Q) \ssm \projUp\big( \strings^\pm(\reversed{\bar Q}) \ssm R \big) \big) \meet \big( \strings^\pm(\bar Q) \ssm \projUp\big( \strings^\pm(\reversed{\bar Q}) \ssm S \big) \big) \\
-& = \strings^\pm(\bar Q) \ssm \big(  \big( \projUp\big( \strings^\pm(\reversed{\bar Q}) \ssm R \big) \join \big( \projUp\big( \strings^\pm(\reversed{\bar Q}) \ssm S \big) \big) \\
+& = \strings^\pm(\bar Q) \ssm \big( \projUp\big( \strings^\pm(\reversed{\bar Q}) \ssm R \big) \join \projUp\big( \strings^\pm(\reversed{\bar Q}) \ssm S \big) \big) \\
 & = \strings^\pm(\bar Q) \ssm \projUp(T) = \projDown\big( \strings^\pm(\reversed{\bar Q}) \ssm T \big)
@@
 
-Recall Definition~\ref{def:distinguishedSubstring} for distinguishable chords.
+Recall Definition~\ref{def:distinguishedSubstring} for distinguishable strings.
 We now have all tools to describe the distinguishable strings in a gentle bound quiver~$\bar Q$.
@@
 Let~$\rho \in \closure{\Sigma_\bottom(\sigma)} \cap \Sigma_\top(\tau)$.
-As~$\rho \in \closure{\Sigma_\bottom(\sigma)}$, there exists substrings~$\rho_1, \dots, \rho_\ell \in \Sigma_\bottom(\sigma)$, arrows~$\alpha_1, \dots, \alpha_{\ell-1} \in Q_1$ and signs~$\varepsilon_1, \dots, \varepsilon_{\ell-1} \in \{-1,1\}$ such that~$\rho = \rho_1 \alpha_1^{\varepsilon_1} \dots \alpha_{\ell-1}^{\varepsilon_{\ell-1}} \rho_\ell$.
+As~$\rho \in \closure{\Sigma_\bottom(\sigma)}$, there exist substrings~$\rho_1, \dots, \rho_\ell \in \Sigma_\bottom(\sigma)$, arrows~$\alpha_1, \dots, \alpha_{\ell-1} \in Q_1$ and signs~$\varepsilon_1, \dots, \varepsilon_{\ell-1} \in \{-1,1\}$ such that~$\rho = \rho_1 \alpha_1^{\varepsilon_1} \dots \alpha_{\ell-1}^{\varepsilon_{\ell-1}} \rho_\ell$.
 Assume that there exists~$k \in [\ell-1]$ such that~$\varepsilon_k = 1$ and choose~$k$ minimal for this property (the proof is similar if there exists~$k \in [\ell-1]$ such that~$\varepsilon_k = -1$).
@@
 \captionsetup{width=1.5\textwidth}
-\hvFloat[floatPos=p, capWidth=h, capPos=r, capAngle=90, objectAngle=90, capVPos=c, objectPos=c]{figure}
+\hvFloat[floatPos=p, capWidth=h, capPos=right, capAngle=90, objectAngle=90, capVPos=c, objectPos=c]{figure}
 {\begin{minipage}{23.2cm}\vspace*{-1cm}\includegraphics[scale=.25]{all2}\end{minipage}}
@@
 \captionsetup{width=1.5\textwidth}
-\hvFloat[floatPos=p, capWidth=h, capPos=r, capAngle=90, objectAngle=90, capVPos=c, objectPos=c]{figure}
+\hvFloat[floatPos=p, capWidth=h, capPos=right, capAngle=90, objectAngle=90, capVPos=c, objectPos=c]{figure}
 {\includegraphics[scale=.27]{allFans3}}
@@
 \captionsetup{width=1.5\textwidth}
-\hvFloat[floatPos=p, capWidth=h, capPos=r, capAngle=90, objectAngle=90, capVPos=c, objectPos=c]{figure}
+\hvFloat[floatPos=p, capWidth=h, capPos=right, capAngle=90, objectAngle=90, capVPos=c, objectPos=c]{figure}
 {\includegraphics[scale=.27]{allAssociahedra3}}
@@
 
-We benefited form various discussions and several useful comments on a preliminary version of this paper.
-We are particularly grateful to F.~Chapoton for initially pointing us in the direction of this paper, to A.~Garver and T.~McConville for important inputs on Part~\ref{part:lattice} (including pointing out to us the need of Theorem~\ref{thm:characterizationCongruenceUniform2}), to T.~Manneville and S.~Stella for their help on Part~\ref{part:geometry}, to L.~Demonet for the observation of Remarks~\ref{rem:linDep} and~\ref{rem:polytope}, and to S.~Schroll for her valuable comments on Part~\ref{part:algebra}.
+We benefited from various discussions and several useful comments on a preliminary version of this paper.
+We are particularly grateful to F.~Chapoton for initially pointing us in the direction of this paper, to S.~Schroll for her valuable comments on Part~\ref{part:algebra}, to ChangJian Fu for his comments leading to a clarification of Definition~\ref{definition: dance and attract}(i)(b), to A.~Garver and T.~McConville for important inputs on Part~\ref{part:lattice} (including pointing out to us the need of Theorem~\ref{thm:characterizationCongruenceUniform2}), to T.~Manneville and S.~Stella for their help on Part~\ref{part:geometry}, and to L.~Demonet for the observation of Remarks~\ref{rem:linDep} and~\ref{rem:polytope}.
 We also thank T.~Br\"ustle, O.~Iyama, N.~Reading, H.~Thomas for discussions on their ongoing projects mentioned in the introduction.

### 2022-11-30 thirdPaper/draft/typeConeAssociahedraSubmitted.tex
minor changes history

--- 2022-07-19 thirdPaper/draft/typeConeAssociahedra.tex
@@
 They appear in representation theory in relation with cotorsion pairs~\cite{ChangZhouZhu-ClusterSubalgebras,ZhaoHuang-Phantom,LiuNakaoka-Hearts,Liu-LocalizationsHearts}, with Auslander--Reiten theory~\cite{IyamaNakaokaPalu}, with cluster algebras, mutations, or cluster-tilting theory~\cite{ChangZhouZhu-ClusterSubalgebras,Pressland,ZhouZhu-TriangulatedQuotient,LiuZhou-Abelian,LiuZhou-AbelianII,LiuZhou-Gorenstein}, with Cohen--Macaulay dg-modules in the remarkable~\cite{Jin}.
-We also note the generalization, called~$n$-exangulated categories~\cite{HerschendLiuNakaoka}, to a version suited for higher homological algebra.
+We also note the generalization, called~$n$-exangulated categories~\cite{HerschendLiuNakaokaI,HerschendLiuNakaokaII}, to a version suited for higher homological algebra.
 
@@
 Let~$\mathbb{E}_T$ be the additive sub-bifunctor of~$\cat(-,\susp -)$ formed by those morphisms that factor through~$\add\susp T$.
-Then~$(\cat,\mathbb{E}_T)$ becomes extriangulated by~\cite[Prop.~3.14]{HerschendLiuNakaoka} (this can also be checked directly).
+Then~$(\cat,\mathbb{E}_T)$ becomes extriangulated by either~\cite[Prop.~3.16 or Prop.3.19]{HerschendLiuNakaokaI} (this can also be checked directly).
 The extriangles of~$\cat$ are precisely the triangles~$X\overset{f}{\rightarrow}Y\overset{g}{\rightarrow} Z \overset{h}{\dashrightarrow}$, for which the morphism~$h$ factors through~$\add\susp T$.
@@
 Since the deflations in~$(\ec,\mathbb{E}_\tc,\mathfrak{s}_\tc)$ are precisely the deflations in~$(\ec,\mathbb{E},\mathfrak{s})$ that are~$\tc$-epic, they are closed under composition.
-We can thus apply~\cite[Prop.~3.14]{HerschendLiuNakaoka} to obtain that~$(\ec,\mathbb{E}_\tc,\mathfrak{s}_\tc)$ is an extriangulated category.
-With that relative structure, the objects in~$\tc$ become projective.
+We can thus apply~\cite[Prop.~3.16]{HerschendLiuNakaokaI} to obtain that~$(\ec,\mathbb{E}_\tc,\mathfrak{s}_\tc)$ is an extriangulated category.
+With that relative structure, the objects in~$\tc$ become projective
+(alternatively, one can directly apply~\cite[Prop.~3.19]{HerschendLiuNakaokaI}).
 Define~$\cat$ to be the full subcategory of~$\ec$ whose objects~$X$ admit an~$\mathfrak{s}_\tc$-conflation~$T_1\infl T_0\defl X$.

### 2023-02-21 thirdPaper/draft/typeConeAssociahedra.tex

@@
 \DeclareMathOperator{\rank}{rank} % rank
+\DeclareMathOperator{\oprays}{rays} % rays
 
@@
 \item \textbf{any initial seed}, regardless of whether it is acyclic or not (see \cref{exm:typeConeCA,fig:clusterFans,fig:labelFacetDefiningInequalititiesCA1,fig:labelFacetDefiningInequalititiesCA2} for examples in types~$A_3$ and~$C_3$~cyclic).
-In contrast, the proof of~\cite{BazierMatteDouvilleMousavandThomasYildirim} only treats acyclic initial seeds (although H.~Thomas announced in a lecture given at RIMS in June 2019 that this restriction will disappear in a future version of~\cite{BazierMatteDouvilleMousavandThomasYildirim}).
+In contrast, the proof of~\cite{BazierMatteDouvilleMousavandThomasYildirim} only treats acyclic initial seeds {\color{red} although the approach has since been extended to any seed in~\cite{BazierMatte-thesis} (as previously announced by H.~Thomas in a lecture given at RIMS in June 2019).}
 
@@
 In contrast, even with the acyclicity restriction, the result of~\cite{BazierMatteDouvilleMousavandThomasYildirim} is first proved in simply-laced cases ($A$, $D$ and~$E$) using representation theory of quivers.
-Extension to the non simply-laced cases is then argued by a folding argument.
-Although not presented in detail, this argument is subtle and technical.
+{\color{red} Extension to the non simply-laced cases can then be argued by a folding argument.
+This subtle and technical argument is presented in~\cite{ArkaniHamedHeLam}.}
 
@@
 \label{prop:characterizationPolytopalFan}
-Let~$\Fan$ be an essential complete simplicial fan in~$\R^n$. Then the following are equivalent for any height vector~$\b{h}\in \R^N$:
+Let~$\Fan$ be an essential complete simplicial fan in~$\R^n$ with $N$ rays. Then the following are equivalent for any height vector~$\b{h}=\left(\b{h}_{\ray}\right)_{\ray \in \oprays(\Fan)}\in \R^N$:
 \begin{enumerate}
@@
 For example, the height vector~$(\nicefrac{1}{2}, \nicefrac{3}{4}, \nicefrac{5}{4}, 1, \nicefrac{5}{4})$ belongs to the type cone~$\typeCone(\Fan)$, and the corresponding polytope is represented in \cref{fig:typeCone} (middle).
-To represent this type cone, it suffices to represent~$\b{K}\typeCone(\Fan)$ which is an essential simplicial cone in~$\R^3$, given as the intersection of the following five open halfspaces:
+To represent this type cone, it suffices to represent~$\b{K}\typeCone(\Fan)$, which is an essential simplicial cone in~$\R^3$, given as the intersection of the following five open halfspaces:
 \begin{gather*}
@@
 One can further reduce the dimension by intersecting with a transversal hyperplane to get a $2$-dimensional representation.
-This is the red triangle depicted in \cref{fig:typeCone} (right).
+Any affine hyperplane crossing all the rays of~$\b{K}\typeCone(\Fan)$ would work, here we take the hyperplane $x+y+z=1$ and we get the red triangle depicted in \cref{fig:typeCone} (right).
 \end{example}
@@
 We now focus on the normal fan of~$\Asso[n]$.
-Since~$\Asso[n]$ lives in a hyperplane of~$\R^{n+1}$, its normal fan has a one-dimensional lineality.
-Let~$\HH \eqdef \bigset{\b{x} \in \R^{n+1}}{\sum_{\ell \in [n+1]} \b{x}_\ell = 0}$ and ${\pi : \R^{n+1} \to \HH}$ denote the orthogonal projection.
-We denote by~$\gvectorFan[n]$ the intersection of the normal fan of~$\Asso[n]$ with~$\HH$, which is an essential complete simplicial fan.
+Since~$\Asso[n]$ lives in a hyperplane of~$\R^{n+1}$, its normal fan has a one-dimensional lineality (spanned by the all-ones vector).
+To factor out the lineality, let~$\HH \eqdef \bigset{\b{x} \in \R^{n+1}}{\sum_{\ell \in [n+1]} \b{x}_\ell = 0}$ and ${\pi : \R^{n+1} \to \HH}$ denote the orthogonal projection.
+We denote by~$\gvectorFan[n]$ the intersection of the normal fan of~$\Asso[n]$ with~$\HH$.
+Note that~$\gvectorFan[n]$ is an $n$-dimensional essential complete simplicial fan consisting of the projections under~$\pi$ of the normal cones of $\Asso[n]$.
+With the choice of a basis, we can identify $\HH$ with $\R^n$ and depict~$\Asso[n]$ as a full-dimensional polytope with normal fan~$\gvectorFan[n]$.
 

### 2023-02-21 thirdPaper/draft/typeConeAssociahedra.tex
minor changes

@@
 We denote by~$\gvectorFan[n]$ the intersection of the normal fan of~$\Asso[n]$ with~$\HH$. 
-Note that~$\gvectorFan[n]$ is an $n$-dimensional essential complete simplicial fan consisting of the projections under~$\pi$ of the normal cones of $\Asso[n]$.
-With the choice of a basis, we can identify $\HH$ with $\R^n$ and depict~$\Asso[n]$ as a full-dimensional polytope with normal fan~$\gvectorFan[n]$.
+Note that~$\gvectorFan[n]$ is an $n$-dimensional essential complete simplicial fan in~$\HH$, which is actually the normal fan of~$\pi(Asso[n])$ in~$\HH$. 
+With the choice of a basis, we can identify $\HH$ with $\R^n$ and depict~$\gvectorFan[n]$ and~$\pi(\Asso[n])$ in~$\R^n$.
 
@@
 Let~$\tau$ be a maximal common substring of~$\mu$ and~$\nu$.
-If~$\sigma$ and~$\tau$ are not disjoint, then~$\sigma = \tau$ and $\mu$ and~$\nu$ are not kissing at~$\tau$.
+If~$\sigma$ and~$\tau$ are not disjoint, then~$\sigma = \tau$ (as $\tau \subseteq \sigma$ and~$\mu$ and~$\nu$ differ at the extremities of~$\sigma$) and $\mu$ and~$\nu$ are not kissing at~$\tau$.
 We can therefore assume that $\tau$ appears completely before or completely after~$\sigma$ in both~$\mu$ and~$\nu$.

### 2023-02-21 thirdPaper/draft/typeConeAssociahedra.tex
remove red

@@
 \item \textbf{any initial seed}, regardless of whether it is acyclic or not (see \cref{exm:typeConeCA,fig:clusterFans,fig:labelFacetDefiningInequalititiesCA1,fig:labelFacetDefiningInequalititiesCA2} for examples in types~$A_3$ and~$C_3$~cyclic).
-In contrast, the proof of~\cite{BazierMatteDouvilleMousavandThomasYildirim} only treats acyclic initial seeds {\color{red} although the approach has since been extended to any seed in~\cite{BazierMatte-thesis} (as previously announced by H.~Thomas in a lecture given at RIMS in June 2019).}
+In contrast, the proof of~\cite{BazierMatteDouvilleMousavandThomasYildirim} only treats acyclic initial seeds although the approach has since been extended to any seed in~\cite{BazierMatte-thesis} (as previously announced by H.~Thomas in a lecture given at RIMS in June 2019).
 
@@
 In contrast, even with the acyclicity restriction, the result of~\cite{BazierMatteDouvilleMousavandThomasYildirim} is first proved in simply-laced cases ($A$, $D$ and~$E$) using representation theory of quivers.
-{\color{red} Extension to the non simply-laced cases can then be argued by a folding argument.
-This subtle and technical argument is presented in~\cite{ArkaniHamedHeLam}.}
+Extension to the non simply-laced cases can then be argued by a folding argument.
+This subtle and technical argument is presented in~\cite{ArkaniHamedHeLam}.
 

### 2023-02-21 thirdPaper/draft/typeConeAssociahedra.tex
corrections Yann

@@
 In particular,~$\Ksp(\cat)$ is isomorphic to a free abelian group over the set~$\ind(\cat)$.
-Considering the modified group~$K_0(\cat ; T)$ instead of the usual Grothendieck group is motivated by \cref{sec:applications-g-vectors}, where we study relations between~$\b{g}$-vectors.
+Considering the modified group~$K_0(\cat ; T)$ instead of the usual Grothendieck group is motivated by \cref{sec:applications-g-vectors}, where we study relations between~$\b{g}$-vectors (see also the notion of relative rigidity in~\cite{YangZhu-Relative}).
 
@@
 \end{corollary}
+
+\begin{proof}
+The proposition above can be restated by saying that the kernel of the sujective group homomorphism $\ind_T: \Ksp(\cat)\to\Ksp(\add(T))$ is the subgroup generated by the relations defining $K_0(\cat ; T)$.
+\end{proof}
 
@@
 satisfying~$(t')_\ast\eps_T=t_\ast\eps_T$.
+The long exact sequence associated with the extriangle~$T\to 0 \to \Sigma T \overset{\eps_T}{\dashrightarrow}$ implies injectivity of $s\mapsto s_\ast\eps_T$.
 We thus have~$t'=t$.

### 2023-02-22 thirdPaper/draft/typeConeAssociahedra.tex
thank referee
Reference Rup15 et answerPLMS.txt mis à jour

@@
 \item[(iii)] \emph{(}\cite[Thm.~7.5]{BuanMarshReinekeReitenTodorov}\emph{)} For any~$X,Y \in \ind(\cat)$, $\CC(X)$ and~$\CC(Y)$ are exchangeable if and only if~$\dim_{\field_X}\cat(X, \susp Y) = \dim_{\field_Y}\cat(X, \susp Y) = 1$.
-\item[(iv)]\emph{(}\cite{BuanIyamaReitenScott} and \cite[Thm.~5.1]{BuanMarshReiten-mutation}, adapted to the cluster categories of species of Dynkin type\emph{)} Let~$T'$ be any basic cluster-tilting object of~$\cat$.
+\item[(iv)]\emph{(}\cite{BuanIyamaReitenScott}, \cite[Thm.~5.1]{BuanMarshReiten-mutation} and \cite[Thm.~5.7]{Rupel15}\emph{)} Let~$T'$ be any basic cluster-tilting object of~$\cat$.
 Then the matrix~$B'$ of the associated seed~$(\CC(T'),B')$ is given by the multiplicities of the middle terms of the exchange triangles.
@@
 We are grateful to C.~Stump for reporting a typo in \cref{exm:typeConeCA}.
+We also thank an anonymous referee for relevant comments.
 

### 2023-02-23 thirdPaper/draft/typeConeAssociahedra.tex
correction last hole

@@
 \end{itemize}
-In \cref{subsubsec:simplicialTypeConeNKC}, we will restrict to a situation that avoids all these patologies.
+In \cref{subsubsec:simplicialTypeConeNKC}, we will restrict to a situation that avoids all these pathologies.
 \end{remark}
@@
 \item any (non necessarily oriented) cycle of~$\quiver$ contains at least two relations in~$I$,
+\item each string (resp.~walk) is self-avoiding (cannot visit twice the same vertex),
 \item any string of~$\quiver$ is distinguishable,
-\item no walk on~$\quiver$ is self-kissing.
+\item no walk on~$\quiver$ is self-kissing,
 \end{enumerate}
@@
 
-For a string~$\sigma$ of~$\quiver$, we denote by $\sigma\hR$ (resp.~$\sigma\cR$) the unique string of the blossoming quiver~$\quiver\blossom$ of the form $\sigma\hR = \sigma \alpha_1^{-1} \alpha_2 \dots \alpha_\ell$ (resp.~$\sigma\cR = \sigma \alpha_1 \alpha_2^{-1} \dots \alpha_\ell^{-1}$) with~$\ell \ge 1$ and~${\alpha_1, \dots, \alpha_\ell \in Q_1}$ and such that~$t(\alpha_\ell)$ (resp.~$s(\alpha_\ell)$) is a blossom of~$\quiver\blossom$.
+For a string~$\sigma$ of~$\quiver$ of length at least~$1$, we denote by $\sigma\hR$ (resp.~$\sigma\cR$) the unique string of the blossoming quiver~$\quiver\blossom$ of the form $\sigma\hR = \sigma \alpha_1^{-1} \alpha_2 \dots \alpha_\ell$ (resp.~$\sigma\cR = \sigma \alpha_1 \alpha_2^{-1} \dots \alpha_\ell^{-1}$) with~$\ell \ge 1$ and~${\alpha_1, \dots, \alpha_\ell \in Q_1}$ and such that~$t(\alpha_\ell)$ (resp.~$s(\alpha_\ell)$) is a blossom of~$\quiver\blossom$.
 These notations are motivated by the representation of strings used in~\cite{ButlerRingel, PaluPilaudPlamondon-nonkissing}, and the terminology usually says that~$\sigma\hR$ (resp.~$\sigma\cR$) is obtained by adding a \defn{hook} (resp.~a \defn{cohook}) to~$\sigma$.
@@
 The walk~$\hL(\sigma\hR) = (\hL\sigma)\hR$ of~$\quiver$ is simply denoted by~$\hh{\sigma}$, and we define similarly~$\cc{\sigma}$, $\hc{\sigma}$ and~$\ch{\sigma}$.
+For a string~$\sigma = \varepsilon_a$ of length~$0$, we cannot a priori not distinguish~$\sigma\hR$ from~$\hL\sigma$ (resp.~$\sigma\cR$ from~$\cL\sigma$).
+We then make an arbitrary choice enabling us to define the four walks~$\hh{\sigma}$, $\cc{\sigma}$, $\hc{\sigma}$ and~$\ch{\sigma}$.
 
@@
 Let~$\tau$ be a maximal common substring of~$\mu$ and~$\nu$.
-If~$\sigma$ and~$\tau$ are not disjoint, then~$\sigma = \tau$ (as $\tau \subseteq \sigma$ and~$\mu$ and~$\nu$ differ at the extremities of~$\sigma$) and $\mu$ and~$\nu$ are not kissing at~$\tau$.
+If~$\sigma$ and~$\tau$ are not disjoint, $\sigma$ and~$\tau$ must overlap as substrings of both~$\mu$ and~$\nu$ by \cref{prop:noSelfKissing}\,(ii), so that~$\sigma \subseteq \tau$ by maximality of~$\tau$.
+Since~$\mu$ and~$\nu$ differ at the extremities of~$\sigma$, this shows that~$\sigma = \tau$ (as substrings of both~$\mu$ and~$\nu$).
+By definition, $\mu$ and~$\nu$ are not kissing along~$\sigma$, hence along~$\tau$.
 We can therefore assume that $\tau$ appears completely before or completely after~$\sigma$ in both~$\mu$ and~$\nu$.
@@
 \]
+
+\pagebreak
 Observe moreover that since~$\omega$ has outgoing arrows at the endpoints of~$\sigma$, the common substring of~$\omega$ and~$\cL \sigma \tau'$ strictly contains~$\sigma$ so that $\lambda(\omega, \cL \sigma \tau') > \lambda(\omega, \omega')$.
@@
 \item[(iii)] \emph{(}\cite[Thm.~7.5]{BuanMarshReinekeReitenTodorov}\emph{)} For any~$X,Y \in \ind(\cat)$, $\CC(X)$ and~$\CC(Y)$ are exchangeable if and only if~$\dim_{\field_X}\cat(X, \susp Y) = \dim_{\field_Y}\cat(X, \susp Y) = 1$.
-\item[(iv)]\emph{(}\cite{BuanIyamaReitenScott}, \cite[Thm.~5.1]{BuanMarshReiten-mutation} and \cite[Thm.~5.7]{Rupel15}\emph{)} Let~$T'$ be any basic cluster-tilting object of~$\cat$.
+\item[(iv)]\emph{(}\cite{BuanIyamaReitenScott}, \cite[Thm.~5.1]{BuanMarshReiten-mutation} and \cite[Thm.~5.7]{Rupel}\emph{)} Let~$T'$ be any basic cluster-tilting object of~$\cat$.
 Then the matrix~$B'$ of the associated seed~$(\CC(T'),B')$ is given by the multiplicities of the middle terms of the exchange triangles.

### 2023-02-23 thirdPaper/draft/typeConeAssociahedra.tex
Mise à jour affiliation

@@
 \author{Pierre-Guy Plamondon}
-\address[Pierre-Guy Plamondon]{Laboratoire de Math\'ematiques de Versailles, UVSQ, CNRS, Universit\'e Paris-Saclay, Versailles}
+\address[Pierre-Guy Plamondon]{Laboratoire de Math\'ematiques de Versailles, UVSQ, CNRS, Universit\'e Paris-Saclay, Institut Universitaire de France (IUF)}
 \email{pierre-guy.plamondon@uvsq.fr}
-\urladdr{\url{https://www.imo.universite-paris-saclay.fr/~plamondon/}}
+\urladdr{\url{https://lmv.math.cnrs.fr/laboratoire/annuaire/membres-du-laboratoire/pierre-guy-plamondon/}}
 

### 2023-07-12 thirdPaper/draft/typeConeAssociahedra.tex
adresse Arnau
addresse Arnau
corrections type cone

@@
 \author{Arnau Padrol}
-\address[Arnau Padrol]{Institut de Math\'{e}matiques de Jussieu - Paris Rive Gauche, Sorbonne Universit\'e, Paris}
-\email{arnau.padrol@imj-prg.fr}
+\address[Arnau Padrol]{Departament de Matem\`atiques i Inform\`atica, Universitat de Barcelona}
+\email{arnau.padrol@ub.edu}
 \urladdr{\url{https://webusers.imj-prg.fr/~arnau.padrol/}}
@@
 We then use this algebraic result to derive geometric properties of the $\b{g}$-vector fan: we show that the space of all its polytopal realizations is a simplicial cone, and we then observe that this property implies that all its realizations can be described as the intersection of a high dimensional positive orthant with well-chosen affine spaces.
-This sheds a new light on and extends earlier results of N.~Arkani-Hamed, Y.~Bai, S.~He, and G.~Yan in type~$A$ and of V.~Bazier-Matte, G.~Douville, K.~Mousavand, H.~Thomas and E.~Y\i ld\i r\i m for acyclic initial seeds.
+This sheds a new light on and extends earlier results of N.~Arkani-Hamed, Y.~Bai, S.~He, and G.~Yan in type~$A$ and of V.~Bazier-Matte, N.~Chapelet-Laguet, G.~Douville, K.~Mousavand, H.~Thomas and E.~Y\i ld\i r\i m for acyclic initial seeds.
 
@@
 This construction provides a large degree of freedom in the choice of the parameters defining these affine subspaces, and actually produces all polytopes whose normal fan is affinely equivalent to that of J.-L.~Loday's associahedron~\cite{Loday} (see \cref{subsec:typeConeAsso}).
-These realizations were then extended by V.~Bazier-Matte, G.~Douville, K.~Mousavand, H.~Thomas and E.~Y\i ld\i r\i m~\cite{BazierMatteDouvilleMousavandThomasYildirim} in the context of finite type cluster algebras using tools from representation theory of quivers.
+These realizations were then extended by V.~Bazier-Matte, N.~Chapelet-Laguet, G.~Douville, K.~Mousavand, H.~Thomas and E.~Y\i ld\i r\i m~\cite{BazierMatteChapelierLaguetDouvilleMousavandThomasYildirim} in the context of finite type cluster algebras using tools from representation theory of quivers.
 More precisely, they fix a finite type cluster algebra~$\cal{A}$ and consider the real euclidean space~$\R^\cal{V}$ indexed by the set~$\cal{V}$ of cluster variables of~$\cal{A}$.
@@
 The type cone is known to be a polyhedral cone defined by a collection of inequalities corresponding to the linear dependences among the rays of~$\Fan$ contained in pairs of adjacent maximal cones of~$\Fan$ (see \cref{def:typeCone}).
-Our approach is based on an elementary but powerful observation: for any fan~$\Fan$, all polytopal realizations of~$\Fan$ can be described as sections of a high dimensional positive orthant with a collection of affine subspaces parametrized by the type cone~$\typeCone(\Fan)$ (see \cref{prop:alternativePolytopalRealization}); if moreover the type cone~$\typeCone(\Fan)$ is a simplicial cone, it leads to a simple parametrization of all polytopal realizations of~$\Fan$ by a positive orthant corresponding to the facets of the type cone~$\typeCone(\Fan)$ (see \cref{coro:simplicialTypeCone}).
+Our approach is based on an elementary but powerful observation: for any fan~$\Fan$, all polytopal realizations of~$\Fan$ can be described as sections of a high dimensional positive orthant with a collection of affine subspaces parameterized by the type cone~$\typeCone(\Fan)$ (see \cref{prop:alternativePolytopalRealization}); if moreover the type cone~$\typeCone(\Fan)$ is a simplicial cone, it leads to a simple parameterization of all polytopal realizations of~$\Fan$ by a positive orthant corresponding to the facets of the type cone~$\typeCone(\Fan)$ (see \cref{coro:simplicialTypeCone}).
 To prove that the type cone~$\typeCone(\Fan)$ is simplicial, we just need to identify which pairs of adjacent maximal cones of~$\Fan$ correspond to the facets of~$\typeCone(\Fan)$ and to show that the corresponding linear dependences among their rays positively span the linear dependence among the rays of any pair of adjacent maximal cones of~$\Fan$.
-When applied to the $\b{g}$-vector fans of cluster algebras (see \cref{subsec:typeConeCA}), the type cone approach yields all polytopal realizations of the $\b{g}$-vector fans and thus efficiently revisits and extends the construction of~\cite{BazierMatteDouvilleMousavandThomasYildirim}.
+When applied to the $\b{g}$-vector fans of cluster algebras (see \cref{subsec:typeConeCA}), the type cone approach yields all polytopal realizations of the $\b{g}$-vector fans and thus efficiently revisits and extends the construction of~\cite{BazierMatteChapelierLaguetDouvilleMousavandThomasYildirim}.
 This new perspective has several advantages, as our proof uniformly~applies~to:
@@
 \item \textbf{any initial seed}, regardless of whether it is acyclic or not (see \cref{exm:typeConeCA,fig:clusterFans,fig:labelFacetDefiningInequalititiesCA1,fig:labelFacetDefiningInequalititiesCA2} for examples in types~$A_3$ and~$C_3$~cyclic).
-In contrast, the proof of~\cite{BazierMatteDouvilleMousavandThomasYildirim} only treats acyclic initial seeds although the approach has since been extended to any seed in~\cite{BazierMatte-thesis} (as previously announced by H.~Thomas in a lecture given at RIMS in June 2019).
+In contrast, the proof of~\cite{BazierMatteChapelierLaguetDouvilleMousavandThomasYildirim} only treats acyclic initial seeds although the approach has since been extended to any seed in~\cite{BazierMatte-thesis} (as previously announced by H.~Thomas in a lecture given at RIMS in June 2019).
 
@@
 \item \textbf{all finite type cluster algebras}, regardless of whether it is simply-laced or not (see \cref{exm:typeConeCA} for an example in type~$C_3$).
-In contrast, even with the acyclicity restriction, the result of~\cite{BazierMatteDouvilleMousavandThomasYildirim} is first proved in simply-laced cases ($A$, $D$ and~$E$) using representation theory of quivers.
+In contrast, even with the acyclicity restriction, the result of~\cite{BazierMatteChapelierLaguetDouvilleMousavandThomasYildirim} is first proved in simply-laced cases ($A$, $D$ and~$E$) using representation theory of quivers.
 Extension to the non simply-laced cases can then be argued by a folding argument.
@@
 \item \textbf{any positive real-valued parameters}, regardless of whether they are rational or not.
-In contrast, the proof of~\cite{BazierMatteDouvilleMousavandThomasYildirim} naturally applies to rational parameters and then requires an approximation argument.
+In contrast, the proof of~\cite{BazierMatteChapelierLaguetDouvilleMousavandThomasYildirim} naturally applies to rational parameters and then requires an approximation argument.
 \end{itemize}
@@
 \enlargethispage{.4cm}
-Besides revisiting the construction of~\cite{ArkaniHamedBaiHeYan, BazierMatteDouvilleMousavandThomasYildirim} and extending it to any initial seed (acyclic or not) in any finite type cluster algebra (simply-laced or not), our type cone approach is also successful when applied to the $\b{g}$-vector fans of other families of generalizations of the associahedron.
+Besides revisiting the construction of~\cite{ArkaniHamedBaiHeYan, BazierMatteChapelierLaguetDouvilleMousavandThomasYildirim} and extending it to any initial seed (acyclic or not) in any finite type cluster algebra (simply-laced or not), our type cone approach is also successful when applied to the $\b{g}$-vector fans of other families of generalizations of the associahedron.
 In the present paper, we explore specifically \textbf{gentle associahedra}.
@@
 Moreover, we precisely describe the facet-defining inequalities of the type cone in terms of linear dependences of $\b{g}$-vectors involved in certain mesh relations.
-We thus automatically derive a construction similar to that of~\cite{ArkaniHamedBaiHeYan, BazierMatteDouvilleMousavandThomasYildirim} describing all polytopal realizations of the $\b{g}$-vector fans of these brick and $2$-acyclic gentle bound quivers as sections of a positive orthant by well-chosen affine spaces (see \cref{subsec:typeConeCA}).
+We thus automatically derive a construction similar to that of~\cite{ArkaniHamedBaiHeYan, BazierMatteChapelierLaguetDouvilleMousavandThomasYildirim} describing all polytopal realizations of the $\b{g}$-vector fans of these brick and $2$-acyclic gentle bound quivers as sections of a positive orthant by well-chosen affine spaces (see \cref{subsec:typeConeCA}).
 Again, this result mainly relies on finding which relations minimally generate the relations between the $\b{g}$-vectors in the non-kissing complex.
@@
 We are investigating in particular graph associahedra\footnote{A preliminary version of this paper contained the full facet description of the type cones of graph associahedra.
-As they are not simplicial, they lie slightly beyond the scope of this paper, and will be studied elsewhere.}~\cite{CarrDevadoss, Postnikov, FeichtnerSturmfels, Zelevinsky}, brick polytopes~\cite{PilaudSantos-brickPolytope, PilaudStump-brickPolytope} and quotientopes~\cite{Reading-latticeCongruences, Reading-CambrianLattices, PilaudSantos-quotientopes}.
+As they are not simplicial, they lie slightly beyond the scope of this paper.
+These results now appeared in a paper of A.~Padrol, V.~Pilaud and G.~Poullot on type cones of graph associahedra and nestohedra~\cite{PadrolPilaudPoullot-deformedNestohedra}.} and nestohedra~\cite{CarrDevadoss, Postnikov, FeichtnerSturmfels, Zelevinsky}, brick polytopes~\cite{PilaudSantos-brickPolytope, PilaudStump-brickPolytope} and quotientopes~\cite{Reading-latticeCongruences, Reading-CambrianLattices, PilaudSantos-quotientopes}.
 In fact, as already mentioned, it seems sometimes easier to find all polytopal realizations of a fan (by describing its type cone in terms of certain specific pairs of adjacent maximal cones) than to identify one specific explicit realization.
@@
 In particular, when the type cone is simplicial, any polytopal realization of~$\Fan$ has a unique representation (up to translation) as a Minkowski sum of positive dilates of these polytopes.
-For cluster algebras, it follows from~\cite[Sect.~6]{BazierMatteDouvilleMousavandThomasYildirim} that these polytopes are Newton polytopes of the $F$-polynomials.
+For cluster algebras, it follows from~\cite[Sect.~6]{BazierMatteChapelierLaguetDouvilleMousavandThomasYildirim} that these polytopes are Newton polytopes of the $F$-polynomials.
 It would be interesting to obtain similar algebraic interpretations for the rays of the type cones of the non-kissing fans of gentle~algebras.
@@
 Another question related to this paper is to understand the complete realization space of the combinatorics of the associahedra.
-The associahedra constructed in~\cite{ArkaniHamedBaiHeYan, BazierMatteDouvilleMousavandThomasYildirim} and the present paper describe all polytopal realizations of the $\b{g}$-vector fans, but there are other polytopal realizations of the combinatorial type of the associahedron with different normal fans.
+The associahedra constructed in~\cite{ArkaniHamedBaiHeYan, BazierMatteChapelierLaguetDouvilleMousavandThomasYildirim} and the present paper describe all polytopal realizations of the $\b{g}$-vector fans, but there are other polytopal realizations of the combinatorial type of the associahedron with different normal fans.
 Is it possible to similarly understand the complete realization space of the cluster complex, including all realizations not having the~$\b{g}$-vector fan as their normal fan?
@@
 The type cone~$\typeCone(\Fan)$ of~$\Fan$ (\cref{ssec:type cone}), introduced by P.
-McMullen~\cite{McMullen-typeCone}, is a polyhedral cone that parametrizes the set of all possible polytopal realizations of~$\Fan$.
+McMullen~\cite{McMullen-typeCone}, is a polyhedral cone that parameterizes the set of all possible polytopal realizations of~$\Fan$.
 These realizations can be described explicitly as affine sections of the non-negative orthant~$\R^N_{\geq0}$, where~$N$ is the number of rays of~$\Fan$ (\cref{prop:alternativePolytopalRealization}).
@@
 
-This gives a new point of view on~\cite{ArkaniHamedBaiHeYan,BazierMatteDouvilleMousavandThomasYildirim}, illustrated in \cref{subsec:typeConeAsso} for classical associahedra, that we then apply to two families of~$\b{g}$-vector fans generalizing the~$\b{g}$-vector fans of classical associahedra: the~$\b{g}$-vector fans of cluster algebras of finite type (generalized associahedra) in~\cref{subsec:typeConeCA}, and the~$\b{g}$-vector fans of gentle algebras (non-kissing associahedra, non-crossing associahedra, generalized accordiohedra) in~\cref{subsec:typeConeNKC}.
+This gives a new point of view on~\cite{ArkaniHamedBaiHeYan,BazierMatteChapelierLaguetDouvilleMousavandThomasYildirim}, illustrated in \cref{subsec:typeConeAsso} for classical associahedra, that we then apply to two families of~$\b{g}$-vector fans generalizing the~$\b{g}$-vector fans of classical associahedra: the~$\b{g}$-vector fans of cluster algebras of finite type (generalized associahedra) in~\cref{subsec:typeConeCA}, and the~$\b{g}$-vector fans of gentle algebras (non-kissing associahedra, non-crossing associahedra, generalized accordiohedra) in~\cref{subsec:typeConeNKC}.
 
@@
 
-And the second step follows from our main result in \cref{sec:clusterCategories}, which makes use of representation theory of finite dimensional algebras and additive categorification of cluster algebras.
+The second step follows from our main result in \cref{sec:clusterCategories}, which makes use of representation theory of finite dimensional algebras and additive categorification of cluster algebras.
 
@@
 \label{lem:MinkowskiSum}
-For~$\b{h}, \b{h}' \! \in \R^N$, the polytope~$P_{\b{h} + \b{h'}}$ is the Minkowski sum of the polytopes~$P_\b{h}$~and~$P_{\b{h}'}$.
+For any~$\b{h}, \b{h}' \in \typeCone(\Fan)$, the polytope~$P_{\b{h} + \b{h'}}$ is the Minkowski sum of the polytopes~$P_\b{h}$~and~$P_{\b{h}'}$.
 \end{lemma}
@@
 \begin{proof}
-This follows from the definition of~$P_\b{h}$ and of Minkowski sums:
+As~$\b{h}, \b{h}' \in \typeCone(\Fan)$, the fan~$\Fan$ is the normal fan of both~$P_\b{h}$ and~$P_{\b{h}'}$, and thus of their Minkowski sum~$P_\b{h} + P_{\b{h}'}$.
+Hence~$P_\b{h} + P_{\b{h}'} = P_{\b{h}''}$ for some~$\b{h}'' \in \typeCone(\Fan)$.
+Moreover, we have~${\b{h}'' = \b{h} + \b{h}'}$ since for any ray~$\ray$ of~$\Fan$,
 \begin{align*}
-P_\b{h} + P_{\b{h}'} & = \set{\b{x} + \b{x}'}{\b{x} \in P_\b{h} \text{ and } \b{x}' \in P_{\b{h}'}} = \set{\b{x} + \b{x}'}{\b{G}\b{x} \le \b{h} \text{ and } \b{G}\b{x}' \le \b{h}'} \\
-& = \set{\b{y} \in \R^n}{\b{G}\b{y} \le \b{h} + \b{h}'} = P_{\b{h} + \b{h}'}.
+\b{h}''_{\ray} 
+& = \max\set{\dotprod{\ray}{\b{x}''}}{\b{x}'' \in P_{\b{h}''}} = \max\set{\dotprod{\ray}{\b{x}''}}{\b{x}'' \in P_{\b{h}} + P_{\b{h}'}} \\
+& = \max\set{\dotprod{\ray}{\b{x}}}{\b{x} \in P_{\b{h}}} + \max\set{\dotprod{\ray}{\b{x}'}}{\b{x}' \in P_{\b{h}'}} = \b{h}_{\ray} + \b{h}'_{\ray}.
 \qedhere
@@
 
+\enlargethispage{.6cm}
 In this section, we study the type cones of complete simplicial fans arising as normal fans of two families of generalizations of the associahedron: the generalized associahedra of finite type cluster algebras~\cite{FominZelevinsky-ClusterAlgebrasI, FominZelevinsky-ClusterAlgebrasII, FominZelevinsky-ClusterAlgebrasIV, HohlwegLangeThomas, HohlwegPilaudStella} and the gentle associahedra~\cite{PaluPilaudPlamondon-nonkissing}.
@@
 
-\pagebreak
 We now focus on the normal fan of~$\Asso[n]$.
@@
 We denote by~$\gvectorFan[n]$ the intersection of the normal fan of~$\Asso[n]$ with~$\HH$. 
-Note that~$\gvectorFan[n]$ is an $n$-dimensional essential complete simplicial fan in~$\HH$, which is actually the normal fan of~$\pi(Asso[n])$ in~$\HH$. 
+Note that~$\gvectorFan[n]$ is an $n$-dimensional essential complete simplicial fan in~$\HH$, which is actually the normal fan of~$\pi(\Asso[n])$ in~$\HH$. 
 With the choice of a basis, we can identify $\HH$ with $\R^n$ and depict~$\gvectorFan[n]$ and~$\pi(\Asso[n])$ in~$\R^n$.
@@
 These polytopal realizations were first constructed for bipartite initial seeds by F.~Chapoton, S.~Fomin and A.~Zelevinsky~\cite{ChapotonFominZelevinsky} using the $\b{d}$-vector fans of~\cite{FominZelevinsky-YSystems}, then for acyclic initial seeds by C.~Hohlweg, C.~Lange and H.~Thomas~\cite{HohlwegLangeThomas} using Cambrian lattices and fans of N.~Reading and D.~Speyer~\cite{Reading-CambrianLattices, ReadingSpeyer}, then revisited by S.~Stella~\cite{Stella}, and by V.~Pilaud and C.~Stump~\cite{PilaudStump-brickPolytope} via brick polytopes, and finally for arbitrary initial seeds by C.~Hohlweg, V.~Pilaud and S.~Stella~\cite{HohlwegPilaudStella}.
-More recently in~\cite{BazierMatteDouvilleMousavandThomasYildirim}, V.~Bazier-Matte, G.~Douville, K.~Mousavand, H.~Thomas and E.~Y\i ld\i r\i m extended the construction of associahedra of~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} to acyclic seeds of simply-laced finite type cluster algebras.
+More recently in~\cite{BazierMatteChapelierLaguetDouvilleMousavandThomasYildirim}, V.~Bazier-Matte, N.~Chapelet-Laguet, G.~Douville, K.~Mousavand, H.~Thomas and E.~Y\i ld\i r\i m extended the construction of associahedra of~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} to acyclic seeds of simply-laced finite type cluster algebras.
 Here, we extend the construction of~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} to any finite type (simply-laced or not) cluster algebra with respect to any seed (acyclic or not) by providing a direct proof that the type cone of the cluster fan of any finite type cluster algebra with respect to any initial seed is simplicial.
@@
 Combining \cref{coro:simplicialTypeCone,coro:simplicialTypeConeCA,thm:extremalExchangeablePairsCA}, we derive the following description of all polytopal realizations of the cluster fan~$\gvectorFan[\B_\circ]$.
-This result was stated in~\cite{BazierMatteDouvilleMousavandThomasYildirim} in the special situation of acyclic seeds in simply-laced types.
-Note that our proof is quite different from~\cite{BazierMatteDouvilleMousavandThomasYildirim} as it relies on our type cone approach.
+This result was stated in~\cite{BazierMatteChapelierLaguetDouvilleMousavandThomasYildirim} in the special situation of acyclic seeds in simply-laced types.
+Note that our proof is quite different from~\cite{BazierMatteChapelierLaguetDouvilleMousavandThomasYildirim} as it relies on our type cone approach.
 
@@
 Relations in the Grothendieck group of cluster categories have also been studied in~\cite{Palu-grothendieckGroup}.
-Inspired by these results, we will show in this Section that a similar statement holds (see \cref{thm:relations-g-vecteurs}) for the~$\b{g}$-vectors (or indices) of objects in a~$2$-Calabi--Yau triangulated category.
+Inspired by these results, we will show in this section that a similar statement holds (see \cref{thm:relations-g-vecteurs}) for the~$\b{g}$-vectors (or indices) of objects in a~$2$-Calabi--Yau triangulated category.
 We will further generalize these results in Section~\ref{sec:extricats} to the setting of Ext-finite, Krull-Schmidt, extriangulated categories with Auslander--Reiten--Serre duality admitting projective objects with certain properties.
@@
 \]
-expressing cluster variables as Laurent polynomials in the variables of the cluster~$\CC(T)$ and which has the follwing properties.
+expressing cluster variables as Laurent polynomials in the variables of the cluster~$\CC(T)$ and which has the following properties.
 \begin{itemize}
@@
 \item A sequence~$X\xrightarrow{x}Y\xrightarrow{y}Z$ is called a conflation if it realizes some~$\mathbb{E}$-extension in~$\mathbb{E}(Z,X)$.
-In which case the morphism~$X\xrightarrow{x}Y$ is called an inflation, written~$X\infl Y$, and the morphism~$Y\xrightarrow{y}Z$ is called a deflation, witten~$Y\defl Z$.
+In which case the morphism~$X\xrightarrow{x}Y$ is called an inflation, written~$X\infl Y$, and the morphism~$Y\xrightarrow{y}Z$ is called a deflation, written~$Y\defl Z$.
 \item An extriangle is a diagram~$X\overset{x}{\infl} Y\overset{y}{\defl} Z\overset{\delta}{\dashrightarrow}$ where~$X\overset{x}{\infl} Y\overset{y}{\defl} Z$ is a conflation realizing the~$\mathbb{E}$-extension~$\delta\in\mathbb{E}(Z,X)$.
@@
 It is easily seen that~$\mathbb{E}_\tc$ is an additive subfunctor of~$\mathbb{E}$.
-Consider $(\ec,\mathbb{E}_\tc,\mathfrak{s}_\tc)$ endowed with the resctriction of the additive realization~$\mathfrak{s}$.
+Consider $(\ec,\mathbb{E}_\tc,\mathfrak{s}_\tc)$ endowed with the restriction of the additive realization~$\mathfrak{s}$.
 Since the deflations in~$(\ec,\mathbb{E}_\tc,\mathfrak{s}_\tc)$ are precisely the deflations in~$(\ec,\mathbb{E},\mathfrak{s})$ that are~$\tc$-epic, they are closed under composition.
@@
 \begin{example}[A gentle algebra]
-Consider the algebra~$\Lambda$ given the the path algebra of the quiver
+Consider the algebra~$\Lambda$ given the path algebra of the quiver
 \[
@@
 
-We thank H.~Thomas for comments on a preliminary version of the paper and for informing us about the upcoming extended version of~\cite{BazierMatteDouvilleMousavandThomasYildirim}.
+We thank H.~Thomas for comments on a preliminary version of the paper and for informing us about the upcoming extended version of~\cite{BazierMatteChapelierLaguetDouvilleMousavandThomasYildirim}.
 We are grateful to C.~Stump for reporting a typo in \cref{exm:typeConeCA}.
